\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/03/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 3, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Pseudo-Onseck, recording.

Minutes read.

Motion to commend the minutes for being in the tradition of Onseckretarial work passes 14-1-0+Spehn.

Note for the Skinner or Onseck: go back and fix last week's minutes.

\goto{Committee Reports}

\subsection*{Hasslecomm}
Hasslecomm is revising its rites. People should email them to comment
on whether the Rites are sane. Hasslecomm will happen Real Soon Now.

\subsection*{AlohaLenscomm}
Kate is now in Quadravisual. It's like the Four Seasons of Kate.
Except it's really like two seasons.

\subsection*{Star Chamber}
Brian processed 2 donations on Sunday. Andrew processed a donation
today. You may have more fine credit than you're used to. If you're
one of the donors. Our members have no (cents|sense).

There are a bunch of new magazines on the shelf. If you'd like to read
this month's F\&SF or Analog, they're up there.

\subsection*{Kvetchcomm}
Y'all should write for Kvetchcomm. It's about writing reviews. We have
determined that authors sometimes read our reviews. Elizabeth Bear
liked our review of her book. It's easy - take a book that's
been written sometime in the last decade, and review it. The more
recent the better - it will encourage publishers to send us new books.
Kvetchcomm is not interested in ``This book gets 3.7 stars.'' Maidens
are important. A few of the new books will be going on the shelves
soon. You should review them. Kate will review the vanity published
book ``in the proper fashion.'' Reviews should be the truth, they
don't have to be nice.

\subsection*{Bluebellcomm}
More books got covered. There's a pile over there, yay. Bluebellcomm
is attempting to stay on top of things.

\subsection*{MagazineInventoryComm}
Magazine inventory is coming up on Sunday the 12th. We will have a set
of known knowns, a set of known unknowns, and unknown unknowns. We
will attempt to make the last as small as possible, lest the Vogons
get involved. Send an email to Jake Beal or Magdex.

\subsection*{PseudoKvetchcomm}
AlohaLenscomm judges a book primarily by its cover, mentioning that it
apparently compares favorably to Red Mars, which AlohaLenscomm
detests.

\subsection*{PseudoPanthercomm}
Kate asks about Panthercomm. Let's deal with this later.

\goto{Old Business}
John M. Ford is now deceased. There is a nice obit on websnark.com. He
is credited as being one of the first cyberpunk authors. The book
``Web of Light'' is on the Skinner's to-read list.

A question about indefinite-time business results in the onseck losing
his place in the minutes.

Ig Nobels were sponsored in part by the Harvard Science Fiction
Society (HRSFA). Have we ever, do we now, and will we ever care about
the Ig Nobels? LSC will be handling this.

The Mythbusters don't believe in MIT, and consequently will be
arriving tomorrow to prove or disprove the existence of the mythical
'hosed freshman'.

Motion that we are all at Schroedinger's MIT chickens 4-2-8+Spehn.

Motion that we should all be glad that how much the Skinner hates
\emph{Fragile Things} didn't come up this meeting passes 21-3-2+Spehn.

Jake Beal's sources are 'comprehensive'. 

ALGOL

\goto{New Business}

Motion about whether the Skinner has to bing succeeds in its failure
7-8-0+Spehn. MITSFS is truly a Red Queen situation.

Move to ban both panting and de-panting fails for lack of a second.

Albanian motion fails for lack of a second.

Finger motions fail for lack of seconds.

\goto{Future Business}

The Skinner imagines impulses in Fourier space caused by binging. He
can create delta-functions with his bare hands.

Asa is going back to Colorado. He got into his school!

Motion to award Asa the Order of the Golden Banana and a free box of used books passes 12-2-2+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Pseudo-Onseck}

\end{document}
