\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/28/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 28th, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Margaret Gentile, LHE  and Pseudo-Skinner, presiding; Kate Kuznetsova, Pseudo-Onseck, recording.

Minutes read.

Motion to approve minutes as having a surprisingly attractive accent: passes 6-3-4+Spehn

\goto{Committee Reports}

%\subsection*{Onseck}

%\subsection*{War Council}

\subsection*{FrustratedAuthorComm}

Canada is slow. Margaret keeps saying that, but nobody changes things.

``Up above the Artic circle it is only 1 day for every 260 of ours''

\subsection*{PicnicComm}

The Picniccomm is grilled about setting days, learning about cons and the value of sending email. The Picnicomm apologozises and insists that the picture on the wall is completly accurate.

%\subsection*{HonestyComm}

\subsection*{InventionComm}

Motion to condemn the inventor of the dog watch and send him into the fiery pits of hell: Passes by a lot to something to 4+spehn

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

The Alpert donation will be finished about this week, if the Skinner stops being sick. 

``Its Zeno's donation!''

We have some new books by Menley Wied Weldman, who is an old and dead author.  Some people read them when they were a year old.

Motion to give all authors middle names passes by some amount that the Pseudo-skinner is too lazy to count.

Margaret's middle name is now ``The Albanian Destructor'',but shortened to ``Henrietta''. Or ``Hell''. Margaret really likes that one, but she is wrong. 

ALGOL 

Long awkward silence lasts the entirety of three dreadful, painful seconds.

Motion to procure a physics-violating bike to use for the library's nefarious purposes: passes 7-1-5+Spehn

Jamie warns people not to watch bright lights in refrigerators.

\goto{New Business}

\goto{Future Business}

In the future the Skinner will die of a deadly illness. Then he will beat people upside the head with a giant wretch. 

Everybody including the pseudo-skinner sings the adjournement song.

``Sing it like you mean it! Bah, you people are no fun. Meeting adjourned...''

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kate Kuznetova, Pseudo-Onseck}

\end{document}
