\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 17, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion to condemn the Onseck for sticking contraceptives in the time machine passes 10-4-4\ps.

\goto{Committee Reports}

\subsection*{Pseudo-PianoComm}
Welcome to Yelena Tsitkin, our newest keyholder!

MHG: ``You found the Necronomicon \emph{when} and  you didn't tell us?''

\subsection*{JourComm}
Although Kat's not \emph{quite} ready to start working on the next TZ, you should all feel free
to send in stories and reviews.  She intends to publish in May.

\subsection*{LHE}
Motion to have FinBoard studded with cloves and boiled fails 2-6-2\ps.\\
JM: ``Why don't you like them?  They give us money!''\\
MHG: ``Yes, but they don't give us ALL THE MONEY!''

\subsection*{FAC}
Obligatory whine.

\subsection*{BluebellComm}
BluebellComm still has so much work to do it hurts.

\goto{Old Business}

Philip is sent to Albania for comments involving Robert Jordan fanfic, motion passes 13-1-0\ps.

Motion to condemn the Skinner for non-existent short-term memory fails by Skinnerial decree.\\
Motion to condemn the Skinner for not listening banana fails by Skinnerial decree.

Malcolm would like the minutes to reflect that there are some of stupid grad students who keep
their theses on their keychains and don't understand backups.

MHG: ``Since I was playing with soapstone, my room is covered in what looks like either cocaine
or anthrax.''

Motion that the contents of the library and all of the Inventory be investigated for Turing-
completeness, abacus-completeness, and bowling-ball completeness passes while the Onseck is
distracted.

i,i ``liquid-nitrogen-cooled lemon fragmentation cannon''

According to Malcolm, podcasting first occurred in the \emph{Invasion of the Body Snatchers}.

%\subsection*{Onseck}

%\subsection*{Vox Sciurorum}

ALGOL
\goto{New Business}

HRSFA wants books, Cambridge University wants books if we can mail them, and so are Smith College, 
and a 
couple more.  We also sent a bunch of boxes of books to fans in Isreal this week.

i,i ``the Necromomnicon''

Motion to condemn the Skinner for having trouble finding his pants while he's wearing them fails 
by Skinnerial decree.
Motion to condemn the Skinner for abusing his power fails for lack of Skinnerial pants.

The Skinner ends the meeting halfway into a rousing chorus of ``The Skinner Has No Tail at All.''

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
