\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 22, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
John Carr, Vox Sciurorum and Pseudo-Skinner, presiding; Christian Ternus, Pseudo-Onseck, recording.

Minutes read.

Motion to condemn the minutes for not including how much the Skinner hates Fragile Things passes 4-2-0+Spehn.

\goto{Committee Reports}

\subsection*{PseudoPianocomm}
We love Kristin. She showed up during finals, when she had a final the next day, to apologize for not doing any Surgeon work that week.

\subsection*{PseudoHasslecomm}
The Great Purge has begun, and books were removed and put into boxes.   The boxes that we got were spiffy.

\subsection*{PseudoLHE}
The Deposit of Doom was counted and deposited.  The other (lost) deposit is being investigated.

\subsection*{PseudoSkinner}
The keyholder notes were reviewed by Kevin, and indeterminate things will happen with them.

\goto{Old Business}

Term is now officially deceased.  Finals are over, yaaaay.

Talking about the space shuttle's current problem ensues.  Apparently, the space shuttle is about to run out of life support and other essential things.

ALGOL.

\goto{New Business}

Usual boredom\footnote[1]{This meeting was more boring than normal. The pseudo-Onseck apologizes.}. Usual dismissal.

Motion to say more things in order to drive the pseudo-Onseck into insanity passes 8-4-0+Spehn.

\goto{Future Business}

In the future, we will go to dinner!

There will be Magventory over IAP.  The last estimate was 40 man-hours remaining. 

Perhaps in the future, the short stories will officially die.  That would be sad.

In the future, people who are not keyholders will be.  Also, things will happen.

In the future, the universe will die.  

In the future, people will be gone.

Motion to say goodbye to Asa passes lots-none-none+Spehn.

Motion to issue Asa a banana so he can dig himself out of snowdrifts 9-6-0+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Pseudo-Onseck}

\end{document}
