\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 22, 2006


\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Andrew Clough, Psuedo-Onseck, recording.

Minutes read.

Kevin would like to ammend the minutes to say that he still liked Fragile Things, even if it wasn't quite as good as Smoke and Mirrors.

Motion:  Correct the Psuedo-Onseck's volcal cords. Passes 12-0-7+Spehn
\bing

\goto{Committee Reports}

Not that much happened.

John complains he still can't get into the library.  Complaints about CAC lameness, and them needing us to give them information they'd previously told us not to collect.

Motion:  Authorize the skinner to use all necessary force against the CAC to get us our locks working.  Passes 16-4-0+Spehn

\bing

\subsection*{BlueBellComm}

The only box in the Alley marked ``BlueBellComm'' is supplies.

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

\subsection*{Vox Sciororum}

Johns squirrels are learning about tools.  T-minus squirrel takeover just decremented.

Motion:  Draft a battalion of armed squirrels to assault the CAC:  Passes 26-2-1+Spehn

\bing

\goto{Old Business}

The new reading room finally opened.  There were speaches which very carefully never mentioned MITSFS's plans for the reading room, but in the end we're all glad that it didn't become a TEAL classroom (``A Maelstrum of Suck'').

\goto{New Business}

New Prentice:  Jenifer Ford!

\goto{Future Business}

Two keyeholders are getting married tomorrow.  Soon at least one of Kat and Brian will have a new last name.

Motion:  Commend them on their newly wedded sciencefictional bliss:  Passes 21-0-8+Spehn+Sniffling

Matrix Vote:

Motion:  ``To include Skateboards but not bananas''  
Motion:  ``Miller Motion''
Motion:  ``Matrix Vote, and temporal continuity.''

5-3-2+Sphen
11-2-6+Spehn
4-5-0+Sphen

Det:  -3 and the universe is preserved.

\bing

The adjurnment song is sung.

\bing
\noindent
Meeting adjourned, 19:-30 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
