\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/11/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 11, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

A motion, ``Did people really talk about the first 10 years of a
decade'' passes 6-7-7+Spehn

\goto{Committee Reports}

\subsection*{Jourcomm}
KR was proofing TZ!

\subsection{Panthercomm}
The Mobcomm bolus has passed to Bluebellcomm.


\subsection{Bluebellcomm}
The Mobcomm bolus has been processed---see the New Books!

%\subsection*{War Council}

\subsection*{pseudoFrustratedAuthorComm}
Email from NY says ``more rejection letters *grumble grumble hiss hiss*''

\subsection*{pseudo-Niagaracomm}
We will be taking books to MGH! Only nice ones, though.
Malcolm is looking for sources for Dr Who books for his uncle.

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}
There are still cheques on the board.
Discussion about who signed for them determines it was probably Kate.

\goto{New Business}
KR has a friend! The friend has a podcast of old-style radio drama. KR
does not know the name of his friend. ``But he's a real person!''
Apparently Kevin's non-friend not-works for Fedora.

Discussion of Redhat and error messages results in JM commenting that
``This is why you must not comment your code---people will laugh at
you'' 

EKK and Kendra arrive, breathing life into the meeting. Also chaos.
``Dzur came out, Dzur came out, Dzur came out!'' 

BTS comments that Sylvester Stallone is making a new movie, decanted
back into a boxing ring.

``Dresden Files'', by Jim Butcher, is being made into a TV show on
SciFi.

BTS confuses Tim Powers and Tim Allen, but recovers.

EKK tries to explain \emph{Dzur} with very enthusiastic gestures

Arguments over the number 17 and whether it is rude to ask a
\emph{young} lady her age resolves without resolution.

A motion to age the fruit chickens 4-1-11 

A motion to age, dry, and pound the fruit into grain \\
``Huh?''\\
``It's a Miller Motion''\\
``Uuugh!''\\
fails  2-2-11+Spehn

A motion to condemn the Onseck for making up the truth instead of lies
fails 4-3-2+Spehn

\goto{Future Business}
In the future, there will be Robots!\\
In the future, there will be Frosh---August 20 is the beginning of
frosh.

A PROCLAMATION FROM THE SKINNER:\\
From August 20 to the Start of Classes, keyholders will get full
credit for unscheduled hours.

Discussion about 

Motion to cancel the first eight plans involving putting things on the
door, so we will attract more freshman using Plan 9 fails for lack of
a second.

``The hurd can boot!''\\
``The hurd shot round the world?''

``My complier runs my tests. What's wrong with yours, dynamic language
boy?'' -BTS to KR

The meeting devolves into philosophical discussions about programming.

A motion to acquire Banana tests to verify Society's connection to reality\\
A motion to compile Reality\\
And a motion to have Matrix Vote\\
\begin{tabular}{c|c|c}
8&4&1\\
8&1&5\\
3&10&5\\
\end{tabular}
All Fail!

A motion to commend the Onseck for doing the math by hand passes
11-4-3+Spehn

A banana motion fails for lameness.

Discussion on Babylon 5 

Skinner doesn't live on Babylon 5, he just lives on Mars! goes on for
a long time

``This banana is our last, best hope for peace''  passes 80-8-0+Spehn

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
