\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 12, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
The Society has received intelligence that the Harvard-Radcliffe Science Fiction Association 
(HRSFA) plans to conduct a raid on the Society during the meeting today.  Appropriate defensive
measures have been taken.

MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion to amend the minutes to change ``Hiiiiiiii!'' to ``Hiiiiiiii!\~{}'' passes by Skinnerial decree.//
Motion to approve the minutes as razor-sharp passes 9-6-7\ps.

The Society is heavily-armed today.

\goto{Committee Reports}

\subsection*{Star Chamber}
The Chamber has put out a plan to reduce the number of circulating titles in the Library.  
The Instrumentality has approved the plan, and implementation details are being worked out.

\subsection*{PicnicComm}
Invitations got written and sent out!  There's a sign-up sheet on the door for people who need
transportation or who can provide it.  Everyone should sign up!

``You mean meetings aren't just for funny quotes?''

\subsection*{War Council}
The Onseck got nomintated to the CAC Advisory Board.  It means he gets HTML mail.  He'll see if 
he's able to actually do anything useful.

\subsection*{FrustratedAuthorComm}
FrustratedAuthorComm got money!  She won honorable mention (third prize) in a writing contest.

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Physical Plant came in to fix the leaky air conditioner and was stymied by the
Cavin donation boxes stacked in front of it.  Since the Cavin donation has been
fully processed, Jamie moved the boxes into the Alley, whence Panthercomm can deal with them.
There are now two
Bondagecomm boxes and two trading stock boxes which need to be moved to the 
Lab.  Ed appears to be the only person who has access to the Lab right now, so 
it may take a while to do that.

Motion to decree that the word qwomen always be spelled with a silent 'q' in
the minutes passes.

Usual \&c.

\goto{New Business}

We're holding a joint MITSFS-HRSFA movie mob to go see \emph{X-Men 3} on May
26.  Details will be sent out in e-mail to the Society, or can be requested 
by e-mailing the Onseck.  May 20 is the deadline to request that we get a 
ticket for you.

\emph{click click clickclickclickclickclick}

The Society hears clicking outside and discovers that 
HRSFA has in fact arrived in suits and sunglasses, bearing dart-guns.  Our 
advance-guard neutralizes many before the rest of the Society even makes it to
the door, but the survivors fight hard and for the next minutes a ferocious 
gun battle rages in the hallway...

Although the HRSFAns fight honorably and well, they are no match for the battle-hardened Assassins 
of the Society, to whose skill its defense has been commended.
After all the invaders are slain, we resurrect them and invite them to join us
to finish the meeting and go to dinner afterwards.
Over the din of a Society suddenly doubled in size, various banana motions fail 
to gain seconds, accompanied by comments of ``Lame!''.  Some people start 
singing the Adjournment Song, and after the first chorus, which misses
`rousing' but manages `sort of mildly troublesome, much like a half-dead 
mosquito,' the Skinner ends the meeting.  We adjourn with many of the HRSFAns to 
Royal East for dinner.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
