\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 25th, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

\goto{Committee Reports}

Motion:  approve psuedo-Onseck's comeback passes 6-0-1\ps

Come and help at the midway.  It runs from 2 to 7.  Its in the Z center.

\subsection*{I Thought I was a Keyholdercomm}
ALC:  My card still doesn't work :(

KR:  We need a lock programmer.


On another note, we're losing ED and Susan to work issues soon.  :(

Motion:  Provide keyholders with GPS locators so we don't lose any more  Chickens 4-0-4+Raving Paranoia\ps

We have microfiche, some dating back to 1949.  Its deteriorating.  We should get it on CD or something.

We used to have a really old electronic word processor/typewriter.  The data we have for it only consisted of some woman's old high school essays though.  We don't have it any more.


%\subsection*{Onseck}

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

A new collection of wood pulp is trying to pass itself off as a Dune book.  

Jim Baen's Universe, a new SF mag edited by Eric Flint has launched.  Only in Ebook format.  Thats a little unfortunate for those of us trying to archive it.

\goto{New Business}

We need new T-Shirts!  We ought to order some soon

Motion:  Radio carbon date the T-shirts.  Fails for lack of second.

There's a new section of the library.  We shortened Damnation Alley and opened up some new space.  The LPs, particularly, are happier now but we also have bound magazines to read as well as foreign books.

Motion:  Thank those early SF magazine that engaged in plagiarism so that we now have thing we wouldn't otherwise.  Fails for lack of a second.

\goto{Future Business}

J:Get Kendra to say something!

K:  Hello :)

J:  Say something about the future.

K:  The future is Rush.

We have a space crisis, therefore our to be shelved pile is getting big.

Discussion of getting books off to libraries.

Discussion of putting out a TZ on reg day.  KR tries to find wood to knock on, but the closest he can find is the Psuedo-Onseck's head.

Motion:  Give Bananas to the members leaving for the anime club.  Passes 11-0-6\ps

\bing
\noindent
Meeting adjourned, 19:-10 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
