\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 6, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

Clunk!

\noindent
MITSFS meeting called to order, 1700 SST,
ESK, Lady High Embezzler and Pseudo-Skinner, presiding;
John F. Carr, Psuedo-Onseck, recording.

Minutes read.

Motion: Amend minutes to indicate that the Skinner did not in fact
like Fragile Things.  Passes by Pseudo-Skinnerial decree.

JM: Move to denounce the Skinner for hating Fragile Things so much.
Passes 13-5-6+Spehn.

\goto{Committee Reports}

\subsection*{Alohalenscomm}

I printed pictures.

\subsection*{PianoComm}

New prentice, Kristin Berry.  New keyholder Kendra ``massive bluebellcomm'' Beckler.

A bunch of donated stuff got counted.

\subsection*{Phonecomm}
Ring!  Somebody wants to know where we're going to dinner.

\subsection*{Phonecomm$_2$}
Ring!  (ESK)  ESK goes into the hall and says ``great!''

\subsection*{Phonecomm$_3$}
Somebody else starts beeping.

\subsection*{$\hbar$comm}

The corridor schedule still shows the summer schedule.

%\subsection*{JourComm}

\subsection*{Mobcomm}

Mobcomm has money again.  This may be related to a trip to the UA office?

\subsection*{Star Chamber}

Lock trouble continues.  John got a new card which supposedly
exists in the computer unlike the old one but still doesn't work.

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Motion in support of gavel-induced triboluminescence.
Passes \hbox{14-10-10+Spehn}.

As ESK mishandles the gavel, JFC reads the minutes from June 23, 2000
in which Jenwa drops the gavel on her foot.

\goto{New Business}

Katie brought a live flower in the library because she had
a class in which she had to write about later\footnote{The
pseudo-onseck is nearly certain he meant to use more or different words here.}.
In the process 19 people may have died due to fatal flower-induced allergies.
It would have been 20, but Jen Murphy doesn't come to meetings any more.

McDonalds wanted to survey our workers.  Nobody works here so
we took their coupons but not the survey.

We also got a handwritten card with a bunch of books to review,
including {\em The Stealth Planet}.

\subsection*{Phonecomm$_4$}
Katie starts beeping.

Motion to convert the library into a room as was found in
{\em Dirk Gently's Holistic Detective Agency} --- a place
where phones do not work except during time travel.
Passes \hbox{21-3-6+Spehn}.

% whang! thunk! thud!

Y talks about hunting extinct animals.

Becca considers becoming a sperm collector for money.

...

% 14 6 9 | 2 19 5 | 18 1 9

Penguins!  Yes, penguins!

Y makes a pun.  Fails due to lack of a second.

Miller motion!  Second!  Fails \hbox{16-20-Spehn}, after a fight for the gavel.

Second Miller Motion!  Second second!  Passes \hbox{26 + Kate's Mexican hat dance - 12 - Spehn}.

%\goto{Future Business}

\bing
\noindent
Meeting adjourned, 18:30 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Psuedo-Onseck}

\end{document}
