\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 26, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

\goto{Committee Reports}

\subsection*{Onseck}
A break is taken for the Onseck to open emacs, as she was taking
minutes by hand, and this is condemned as old-fashioned.

"It was a lot slower to start up when you had toget graduate students
to sing your .emacs file before you could open anything"-Jamie

\subsection*{Pianocomm}
Kendra is great! She shelved the To-Be-Shelved books. 
Of course, there was an overflow box hiding, so now the shelf is full
again, oops.

Eric wants to be a prentice. Kevin said so.

\subsection*{Vice} 

Naked greased muppets with most of the fur left on 

Move to catapukt the Onseck into a randomly chosen area of space time,
and catapult the Vice in the opposite direction.
Fails for lack of a second.

\subsection*{Warcouncil}
 Kevin is on the CAC Advisory Board. Phil Walsh volunteered
that the should talk about getting us more space, because we're too
crowded.

Motion to sacrifice a fatted ox to Phil Walsh
Passes 17-0-1+Spehn


%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Meanwhile, the Vice is waging an (unsuccessful) series of
assassination attempts against the new Skinner.
Vice: ``My coup will succeed by ranged weapons!''


\goto{New Business}
Margaret is moving to the Hinterlands.
"We oculd just glaze her"
"She looks pretty glazed already"

MHG will have money, which she wants to give to the library.

We got four boxes from Amazon today, and a review copy!
The Dexmistress and Mobcomm are planning to put up NegDex, books so
new they haven't arrived yet.

There is a new review dex!


\goto{Future Business}
``10s of thousands of books will be vanishing from libraries across the
world next Thursday''-BTS\\
``Thursday? What will happen with them?''-Jamie\\
``Mostly they'll just get checked out'' -BTS


Motion to dispatch a representative to DC with books, to talk to the
peopel and read books to keep from going bananas.\\
Fails 8-9-4+Spehn

Motion to send both Kelseys to Switzerland with a Banana\\
Fails 6-8-2+Spehn

5-4-1+Spehn\\
Miller motion 5-4-1+Spehn\\
Miller motion 1-0-5+Spehn\\
determinant : 0, all motions chicken

Motion to properly lubricate all the consonants in the alphabet
and feed them to Jamie with potassium supplements
thus enabling him to have a banana-based vowel movement.\\

Things are thrown at the Vice, but somehow the meeting ended, so
apparently it passed by Skinnerial headache.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
