\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/01/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 1, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

Motion to amend the minutes to say 18:30 SST like they should, with an
unfriendly amendment to replace all digits with their equivalents in
octal, and an unfriendly amendment to change Kat into Andrew, with a
friendly amendment "Only in the minutes".\\
KR calls for a matrix vote\\
KHA insists that there can't be a matrix vote without three motions\\
Passes 9-0-3+Spehn

Someone shows up!\\
KR: You have entered a meeting!
 
\goto{Committee Reports}


\subsection*{Pseudo and Actual Fweekcomm}
Our booth is manned and is doing well! ESK is there, and ALC is too.
Two new members today!

%\subsection*{War Council}
We have discovered new lands far to the north and conquered them!
They may have been our own lands, but we captured them anyway.
The Star Chamber, which has been hoarding these lands, complains.

%\subsection*{FrustratedAuthorComm}

%\subsection*{Pianocomm}
We have a new Prentice! Christian is our new prentice

\subsection*{Panthercomm}
SSDT has resigned her key, and therefore Panthercomm, after 20 years. 
We may need to request a new picture of WDS so we can put the one of
SSDT and WDS in the Family Album.


%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}
The Cavin Donation has begun being processed. Hooray! Not all of it is
in the Dexes, but some is!

"There are ... and 10 boxes personally signed by Livy. We'll get to
these later." -BTS

Motion to amend the definition of chair to include the floor passes\\
11+4 chair legs-0-3+Spehn


\goto{New Business}
There is a rocketship crashing into the moon at like 1:40 AM
Sunday. The French launched it about a year ago... and it's only now
getting there. 

Discussion about the Clementine orbiter, other Lunar orbiters, and
whether you can program anything to not melt results in a motion
"Aye yi yi yi yi yi yi" which passes 21-0-3+Spehn

A motion to condemn the Skinner fails for lack of the Onseck recording
it.\\

"I want the Skinner to invent new numbers for us. I'm bored with the
old ones" -BTS

Brian tries to make a motion, and gets tongue tied.

A motion to make the Star Chamber "more unique" fails by Onseckorial Decree.

Linear Temporal logic is discussed a bunch, which is technically a
bunch of motions about the Skinner will having been enrolled in a
class in said logic such that he can conduct the meetings eventually
passes with a determinant of 406 

\begin{tabular}{|c|c|c|}
11 & 5 & 3\\
4 & 4 & 9\\
5 & 3 & 13\\
\end{tabular}


The Skinner announces that he (and maybe other members) are taking a
class in Science Fiction Writing with Joe Haldeman.

\goto{Future Business}
KR has not actually read anything by Haldeman. He intends to fix this
in the next two days.

"In the future there will be more frosh!"-KR\\
"But we like the ones we have!"-KHA\\
"Just in case we use them up..."-JM

In the future we will have a new Schedule!\\
In the future meetings will be at 5:30!

***NEXT WEEK: MEETING AT 5:30!!!***

Several complementary banana motions occur, and fail 8-12-0+Spehn

A Miller Motion fails 8-9-1+Spehn

BTS reads a passage involving parents who did not want to let their
daughter marry a 400 pound rabbit.\\
"But we will give you her hand"

KR offers to give hBarcomm his hands *and* feet to poster.

A second Miller Motion passes 9-8-1+Spehn

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
