\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/13/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 13th, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Andrew Clough, Psuedo-Onseck, recording.

Minutes read.

Motion: Commend last week's Psuedo onseck for elaborating on just how
much the Skinner hates Fragile things.  Fails by Skinerial Decree

Motion: Correct last week's minutes to say that Kate is in fact LHE
and psuedo-skinner rather than president and skinner.  Passes by
Skinerial Decree

Motion:  No more voting on motions.  Passess by Skinerial Decree

Motion:  All future Friday 13ths should be totilitarian.  Passes by Skinerial Decree

\goto{Committee Reports}

\subsection*{LHE}

The LHE went to treasurer training

\subsection*{Psuedo-Pianocomm}

John's card troubles continue.

Motion:  Magnatize the gavel and swipe it through CJ's head to see if it opens up.  Passes by Skinerial Decree.

Kat's initials are now KAT.

There are four projects that need prentice help.  Updating the Magdex
this Saturday, running the magazine inventory soon, Niagracomm needs
help sorting by quality, and The Great Purge.

\subsection*{Alohalenscomm}

ESK has a hat in her picture now, and JC has taken a bunch more pictures.

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

The sunflower is old now.

Motion:  Give the sunflower a funeral.  Fails by Skinerial Decree.

The light of the sunset shining on the dome is pretty.

\goto{New Business}
This time the usual motion passes by skinerial decree, and there is no usual debate.

Discussion of who has how many hitpoints.

New books, and they have to be covered.

Miller Motion:  Fails by Skinerial decree.

Miller Motion:  Fails by Skinerial decree

\goto{Future Business}

The Adjournment song is sung.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
