\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 3, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion ``mew'' passes 9-4-4\ps.  JM: ``She may not meow who is dying inside.''

\goto{Committee Reports}

\subsection*{Star Chamber}
We've settled on an algorithm for weeding which optimizes for keeping all reserve copies and two
circulating, which should give us a list of about 4000 books to weed, which we will then give to
the keyholders to say, ``no, I like this book/author/series'' to create an approximation of 
popular things we should keep, which should then give us the about 3000 books we want to prune.

Ed will poke the SFWA people now that we have a real list of books thanks to Inventory.

\subsection*{Pseudo-Dexmistress}
It is difficult to determine the success of Inventory.

%\subsection*{LHE}

\subsection*{FAC}
Obligatory whine.\\
Obligatory beer.

%\subsection*{Pianocomm}

\subsection*{Onseck}
I bought two reams of stock paper for the memsheets (the three-hole punched reinforced paper) from
University Stationery today, and I'm in the process of getting more orange stickers for us.

%\subsection*{Vox Sciurorum}

\goto{Old Business}

People chuckle over the ``Birthday Dirge''---Andrew is another year older.

Sorority girls are scary.

ALGOL
\goto{New Business}

Margaret ``T.P.'s'' the Skinner.

A former Skinner, Marc Alpert, is dropping by next Friday with a bunch of magazines for us.
We may need to enlist the services of the Physics department to create an extra-dimensional 
pocket in which to store them.

MHG: ``Banana-colored squirrels romp through my brain.''

Congratulations to Yelena, our newest keyholder!

Motion to enlist the services of the banana-colored squirrels to conquer ``Pan-Hell'' and take
their space passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
