\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 2, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,

Minutes read.

Motion:  Condem for untimeliness.  Passes, 9-9-1\ps
\goto{Committee Reports}

\subsection*{Cluecomm}

Eight boxes have moved from the bannana colored couch to the lab.

\subsection*{Star Chamber}

The stuff from the chamber shelf has been cleared out, so some of you have fine credit.

And all of you keyholders should shelve books!

\subsection*{Hasslecomm}

Plans for the great purge are being made by Hasslecomm and the Dexmistress!  Looks like we'll be able to do it in a one day push.

Motion:  Use our unsalable books to construct a pulphenge to summon aliens. Passes:  9-6-2\ps

\subsection*{Kvetchcomm}

We want reviews.  Email them to kvetchcomm@mit.edu.

%\subsection*{Mobcomm}

\goto{Old Business}

MITSFS went to see X-Men 3 with HERSFA.  Not quite as good as the second movie, but still watchable.

Malcomm:  ``You cannot get the vice squad to arrest an Icon.''

Pandemonium Books seems to have resolved their dificulties and might be opening soon.

The V for Vendetta movie was good except for the addition of a love plot.

\goto{New Business}

We're going to summer hours next week.

Kevin won't be here for the next three weeks.

\goto{Future Business}

In the future the institute will experience New England weather.

Motion:  Procure a weather clock capable of withstanding the fearsome banana rain.  Fails 4-6-2\ps

The adjournment song is sung.


\bing
\noindent
Meeting adjourned, 17:-30 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Pseudo-Onseck}

\end{document}
