\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 8, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Bonus Pre-Meeting Quotes:

``Happy Birthday to Kate,
She acts like she's eight.
When she sees a camera,
she hides in a crate.

Happy birthday to Kate,
She knows it's her fate
to ta-a-ake Jamie
and defenestrate.''

MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Pseudo-Onseck, recording.

Minutes read.

Matrix Vote:\\
Motion to drop the whole Kevin-slash-Fragile Things thing: 10-0-1+Spehn\\
Motion to commend the Skinner for engaging in 'slash' with Fragile Things: 4-6-4+Spehn\\
Motion ``Goddamn you all'': 11-6-4+Spehn\\

Determinant: -42, all motions fail.

Motion to commend Lori for knowing her way around the library passes 11-0-1+Spehn.

Bing the thing that bings!

\goto{Committee Reports}

\subsection*{LHE}
Remember that trial deposit, and how we were hoping they wouldn't lose it? They lost it. That's where matters stand right now.

Kate submitted an expense voucher, payable to Miles Vorkosigan, for 'Dendarii Mercenary Payroll (Lunch)', signed by Simon Ilyan. It was returned with a Post-It attached, with the words ``unauthorized signature.'' She has been nominated for the Skinnerial Medal of Freedom.

\subsection*{PseudoTrojan}
We received a donation of seven boxes of books. It needs to be processed Really Quickly (oppose Real Soon Now). Don't put boxes on the floor, the floor seeps water. Christian is going to process this donation (the Joblove) on Saturday. Kelsey is going to process the Sherwood donation at the same time.

\subsection*{PseudoAnalogcomm}
You should sign up for IAP hours.

\subsection*{Star Chamber}
The Winter Break time warp will be happening between December 23rd and January 10th.

We haven't talked about doing an amnesty day this year.

W20 will be closed around Christmas and New Year's. They haven't finalized the dates yet.

\subsection*{Theftcomm}
Keyholders! If you're going to be out of town, contact Theftcomm and make sure they know this so you don't get eited.

\subsection*{PseudoOnseck}
The pseudo-Onseck has been going back and, in the fine tradition of 1984, correcting errors in the minutes so they never existed.

%\subsection*{Onseck}

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Veracon and Mystery Hunt do not conflict, Mystery Hunt and Arisia do. Jamie has canceled the spuds. We could go to House of Spuds.

Former MITSFS Skinner/Pope's astronomer/Generally Interesting Guy Guy Consolmagno will be the guest of honor at Boskone this year.

Why is the Pope collecting asteroids?

KAT and BTS arrive, bringing a 'Ships of the Fleet' (Honor Harrington) calendar. Instead of a calendar full of breasts, we've obtained a calendar full of phallic symbols. 

\goto{Time WARP to COMMITTEE REPORTS}
\subsection*{Jourcomm}
Kat has TZ! Widespread cheers ensue. We still need more art, dammit!

\subsection*{Vice}
The Star Chamber shelf is ohmygod full. We haven't trained our elves properly - it's the union. Since KR has talked about them, they're gone - or not, they'll annoy you whether you want them or not.

\goto{Time WARB to OLD BUSINESS}
% The spelling ``Time Warb'' is intentional - CJT

Mumblings about rumor-mongering ensue.

Kate wants the bookworm to be real, so it can be her parasite.

A Miller Motion fails 10-15-0+Spehn.

ALGOL.
\goto{New Business}

Someone's pastry appears to be being consumed by small fungus (the stuff that grows in Hawaii).

Christian is gloating. He has a copy of The Jennifer Morgue (the sequel to the Atrocity Archives), and you don't. He will be donating it in the future, so you can read it.

KR has obtained a copy of Land of Mist and Snow.

Kate has now turned 19.

\goto{Future Business}

In the future, we will have even more books, but still no space.

In the future's past (which is the same as the past of now, the now's past happenings) KR will have been having had a conversation with Phil Walsh about MITSFS's space needs. If you build it, it will be given to someone who isn't us.

Give me a year, and a hundred of my kin, and I would make this a place that donations would break upon like water!

Termites are like ants, only worse.

The pseudo-Onseck is tired of timewarping.

Motion to stop timewarping so we stop weakening the space-time fabric and annoying the pseudo-Onseck passes 14-12-2+Spehn.

What does not kill the space-time continuum strengthens it!

An almost-timewarp causes the pseudo-Onseck to experience a temporary drop in sanity.

In the future, we will have a way to scan microfilm. Unfortunately, the least expensive device has a few too many zeroes in its price. We also may be able to get some kind of grant from someone. 

A Miller motion passes 20-3-0+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Pseudo-Onseck}

\end{document}
