\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 17th, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Pseudo-Onseck, recording.

Minutes read.

Motion to add acid to Whitfield Diffie passes 9-7-3+Spehn.

\goto{Committee Reports}

\subsection*{UnknownUnknownsComm}
Magazine inventory is ongoing. People can now check out magazines without disrupting the inventory. We Need The Help of prentices and keyholders. There will be a magazine inventory party on Sunday, starting at noon until 'we burn out'. We have been finding the most amazing ads in magazines. You can use Listerine for anything.

Motion to commend the head of UnknownUnknownsComm for not knowing he belongs to the comm passes by Skinnerial Decree.

\subsection*{PseudoVGG}
Something about Phineas Phrogg III having to return the bananas of doom.

\subsection*{Bluebellcomm}
More books got covered. More books got taken off the 'New Books' shelf. Prentices should shelve them! We need to store books in 'the network', so people should check out these books.

\subsection*{PseudoJourcomm}
More art submissions are still welcome. With or without art, or perhaps with an avant-garde octuple-repetition of the MITSFS logo, TZ will be going out sometime this month.  

Motion to recess so we can go take the Stratton House photo passes by Skinnerial Decree.

\bing
MITSFS meeting called BACK to order.
Objection to the recess not having merry-go-rounds or swings was duly considered and ignored.

Motion to commend the MIT yearbook on their photographic technique passes 10-0-5+Spehn.

\subsection*{JourComm}
JourComm needs art! Four more 3x3 pictures are desired. Please don't make Kat draw! If you have the ability to scan it, that would be even better. In a Zelda-quest-like proclamation, Kat states that when she has four more pieces of art, she will publish.

\subsection*{Barcomm}
There are new posters! Willing volunteers are desired. Unwilling volunteers can be used if necessary.

\subsection*{Trojan}
Someone-whose-lawyer-Kat-needs-to-contact donated some books. This donation has been tied up for 3 years. It is a ``substantial'' collection. MIT is supposedly handling the acknowledgement and processing of these donations.

\subsection*{Lockcomm}
The microfilm scanning thing is expensive, like \$25,000 expensive. However, Google and/or Harvard may provide us with microfilm-scanning capabilities. MIT libraries may already have microfilm scanners. These magazines were originally transformed into microfilm through the MIT libraries, d'oh. Bondagecomm would like to use the the newly scanned copies to produce bound volumes - this is possible to a limited degree.

 

\goto{Old Business}

Some English banker had a movie made about him. He goes to Las Vegas or something with the king. ``I think it's called Casino Royale'' - BTS

In less happy news, Milton Friedman died recently. He's not science fiction related, but he was a fan of Heinlein. Let's not report on the death of everyone who was a fan of Heinlein.

An actual author died recently, but Kat can't remember who it was. It was on Neil Gaiman's blog this week. This person is Jack Williamson, in some sense the first science fiction writer - he has been writing since the 1920s. He was 98. He had been published in the last seven decades of Analog. He coined the word 'terraforming' in a 1942 story. 

Asimov is still dead.

John Ringo is signing at Pandemonium this week. 

ALGOL.

\goto{New Business}

From the 'beating a dead horse' department, we apparently have the new but not-so-new novel by Brian Jacques. 

Motion to investigate the geneaology of Johnny Depp, looking for stoats and Milton Friedman passes 15-2-5+Spehn.

There are no books on the new bookshelf that the Skinner hates more than Fragile Things. The non-motion fails by Skinnerial Decree.

Brian 'has to do this': A back cover reading of 'Living Next Door to the God of Love'. KR knows how this book escaped from the church library - it killed everything in its path. 

Motion to force anyone who reads a book cover aloud in the library to perform a Kvetchcomm review of the book (retroactively!) fails 15-13-3+Spehn.

Motion to recognize the schlock JFC is reading for what it is fails for lack of a second.

\goto{Future Business}

Someday 14-year-olds will grow up and develop taste.

Kvetchcomm's new motto: we read it so you don't have to.

Motion to acquire circulating version of the Bananas of Doom so ALC can check it out passes 15-10-7+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}



\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Pseudo-Onseck}

\end{document}
