\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 20, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read by Margaret Gentile, last week's pseudo-Onseck.  Whatever she's smoking will be 
distributed to the Keyholders to make Inventory less painful.  Motion ``squirrel'' passes 
11-1-1\ps.

\goto{Committee Reports}

\subsection*{SexSellsComm}
Amanda ``Woz'' Wozniak has poked us regarding advertising in the forthcoming ``Women of East 
Campus'' calendar.  We think we want to do \emph{some} kind of advertising in it, just not quite
every week.

\subsection*{Dexmistress}
There's an Inventory tomorrow!  Dexmistress reports that all the books are closing late tonight
and/or early tomorrrow.

%\subsection*{War Council}

%\subsection*{MobComm}

\subsection*{JourComm}
Buy a TZ!

\subsection*{BluebellComm}
BluebellComm is down to only \emph{four} overflow boxes!  (This is half of what we had a week ago.)
After that gets done, they can start on the Cavin donation.  (oy...)

\subsection*{LHE}
LHE processed \emph{lots and lots} of checks today.  Pick 'em up on the bulletin board.

\subsection*{FAC}
Obligatory whine.

\subsection*{Pianocomm}
Our brand-newest prentice (hi, Kate!) is coming to work Inventory tomorrow!

%\subsection*{Onseck}

\subsection*{Vox Sciurorum}
John had three different squirrels come to his window-ledge today.

\goto{Old Business}
Brian mentions a podcast called ``Slice of Sci-Fi'' with SF news and interviews---it's about 
45 minutes long.  BTS: ``It started out as a campaign to save \emph{Enterprise}, so that says 
something about the taste of the authors, but it's survived that.''

At Arisia, they staged a re-enactment of the old radio play ``The Chicken Heart,'' in which a 
tissue-cultured chicken heart takes over the world.

Motion to create a turducken executive chickens 11-0-12\ps.

ALGOL
\goto{New Business}

Woz shows up with a demo of the calendar page.  %It's a fundraiser for the James E. 

\emph{Star Trek: New Voyages} has its third episode in the can, written by D.C. Fontana and 
starring Walter Koenig.  David Gerrold has offered to write the fourth episode, and George Takei has
signed on to play Sulu.  They're freely downloadable online (use the BitTorrent mirror).

Motion to suggest that the new episodes will take over the world, starting with the festering heart
of Rick Berman, passes by a pretty decent margin.

BTS: ``Google told BellSouth to go jump in a lake.''
KHA: ``Google's been telling a \emph{lot} of people to go jump in a lake.''
SH (hartmans): ``There are a lot of people who need to be told to go jump in a lake.''

Motion to re-flood New Orleans, so that BTS (who's an evil person) can go jump in a lake, passes.

Motion to reinforce the levies in New Orleans to prevent Brian and Sam's flood with the unsold
banana-yellow TZs passes 12-0-4\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
