\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/29/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 29, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Sniffen, Onseck, recording.

Minutes read.


Motion to shame the Skinner for calling Gaiman dumb.  15-1-1\\
Another Motion to Stop mentioning the \emph{Fragile Things} debacle 11-4-2+Spehn \\
YET another motion to condemn the minutes for reminding us how much the Skinner hates \emph{Fragile Things} 10-2-7 +Spehn \\
The psuedo onseck learns to take determinants, and all motions pass. How exciting!


\goto{Committee Reports}

\subsection*{Pseudo-Kvetchcomm}
We got three books from Harper Collins, a couple of young adult books nobody recognizes. People should feel like reviewing them.
Various complaining about how once upon a time we got boxes of books, and then also about YA books are lamer these days.
Also, arguing about Jupiter books. And Asimov. Various existential debates about the purpose and quality of YA books.

The psuedo onseck realises that she spelled the committee name correctly, and we digress to spellchecking.
Motion to use auto complete function write the rest of the minutes, fails for lack of a second. The psuedo onseck is happy. And complains about the keyboard.

\subsection*{AlohaLenscomm}
Has pictures of Kate, and we have to pick one  to use for her. She seems traumatised. The logistics of putting it up 

\subsection*{Pseudo Trojan}
Donation letter sent to The Alpert. The onseck explains shift F3 for
capslock correction. Three donations are currently being processed.
Blair may be the small one. Apparently the stuff was marked for
Panthercomm.  Also, we have the three bears of donations, coming in
all sizes.


\subsection*{Psuedo MobComm}
We have new books, including the latest of the \emph{Wee Free Men} and the new Bujold book. 

\subsection*{Pseudo hBarComm}
We have a new board, with shiny books and it 's green and very pretty. It also has orange letters. And! New posters!

\subsection*{StarChamber}
Lori Ward emailed us today. QRSTs was wondering what happened to his check for the tshirts, so she sent that to him.

BY POPULAR DEMAND:
\goto{Old Business}
Kate hides under the table. We debate selling pictures of Kate

Motion to commend Kate for making an anti picture fortress! 19-1-0 +Spehn\\
Magdex is going on hiatus for a month, and will be doing magazine-y stuff so Prentices should get on that. \\
We debate Kate's social life and how she's not coming to dinner with us because she has a strategy meeting for starcraft.\\
We have fewer members today because people are LARPing for Song of Fire and Ice.\\
Motion investigate whether or not we're a LARP in disguise at our meetings. Fails because everybody is too scared to second. 

\goto{New Business}
LSC is showing night watch, which is a Russian movie! Apparently, it's like a Russian Matrix, and Russians hate it because the movie because it kills the subleties of the book. So Kate says with her Russian inside connections.

Tomorrow, JOE HALDEMAN OMG is going to be doing a reading  and signing at Pandemonium Books in Central.

On Thursday, November 16, the great and illustrous man will be giving a
talk on the craft of science fiction, in the Bartos theater from 5 to
7. in the evening, that is.  FINALLY, as stated in the Skinner's
email: December 8, at 6 PM, Joe Haldeman and curator Bill Arning will
give a gallery talk about the exhibition SENSORIUM at the List Gallery

Our meeting is an analogy for NASA---they sent the Rangers which didn't
have lens caps removed. Our Aloha LensComm had similar issues
photographing Kate. Clearly, glory, bureaucracy and excessively flash
dependent websites await us. Also, we could try crashing into the
moon.

Suggestion to make totally awesome bookmarks which aren't bright and happy and just you know, get them to virally circulate.

Existential debate about the purpose of motions, and providing a
simulacrum of democracy to keep the proletariat happy. The
psuedo-onseck wishes that motion about having food at the meeting to
send

\goto{Future Business}
Future business, which sort of blends with new business.  CLOCKS ARE
CHANGING! We gain an hour of our lives, and get two one am's on sunday
morning. At two it will miraculously become one.

\goto{TIME WARP TO COMMITTEE REPORTS}
\subsection*{Vox Sciororum (Mumbling about Rats)}
Squirrels have been fed, and hawks are coming. 
\goto{Time WARB to FUTURE BUSINESS}

Miller Motion: Fails 4-12-5 +Spehn\\
But we're not sure if we're supposed to be ending the world or not.

If life was a high fantasy novel, we would have to journey to find the
banana of righteousness to free Kate from her book carton prison.
It is so motioned, and the motion passes  8-0-1+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Sharmin Karim, Pseudo-Onseck}

\end{document}
