\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 29, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Andrew Clough, Psuedo-Onseck, recording.

Minutes read.

Motion:  Ammend minutes to note that our Skinner doens't actually think that Fragile Things is worse than Broken Mirrors, he likes them both.
Ammendment:  No, he doesn't.
Ammendment:  Applaud the P-Onseck for making the minutes even more confusing than the actual meeting.  Passes 18-2-+Spehn

\goto{Committee Reports}

\subsection*{Alohalenscomm}

I took pictures.

\subsection*{PianoComm}

Katie is now a prentice. Yay.

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Brian and Kat are married, and now Kat is Katherine H. A. Sniffen.  Her initials at MITSFS and username might or might not change.

KR:  ``Kat and Brian won the personal plot, Ariel won the comittee plot, everything went off well.''

\goto{New Business}

New cluster combo.

Struggle for shoelaces.

\goto{Future Business}

In the future, you'll be able to pay Virgin Galactic lots of money to get into space.

Lame Banana motion passes.  16-8-5+Spehn

\bing
\noindent
Meeting adjourned, 19:-45 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
