\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 6, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Margaret Gentile, Evil Overlord, LHE and Pseudo-Skinner, presiding;
John Carr, Pseudo-Onseck, recording.

Motion to comdemn John for squirrel porn passes by Skinnerial decree.

Minutes read.

Motion to approve the minutes as yellow, condemn as containing
references to Margaret's underwear, and condenm Margaret for having
her underwear on her head in the form of a hat, to comdemn John for
squirrel porn, and many more are all suppressed by the tyrannical
underwear-wearing Pseudo-Skinner.

\goto{Committee Reports}

\subsection*{Pseudo-Dexmistress}
Inventory January 21.  Is it one day or two?  Yes.  \emph{(Just one day, the 21st.  Keyholders and
'prentices should be signed up for a four-hour slot, ``early'' (noon-4) or ``late'' (4-8).  If
you haven't talked to Brian about this, please do so *now*. -ed.)}  

\subsection*{Ass.Comm}

The Skinner is not here today.

\subsection*{War Council}

\subsection*{TheftComm}

We have a schedule, but our calendar is an index card.

\subsection*{BorisComm}

Margaret spent all her money on water and cheap jewelry (pink sand and/or
garnets) so can not buy us a calendar.

%\subsection*{MobComm}

%\subsection*{LHE}

\subsection*{FAC}

Obligatory whine.

Margaret sent out more stories and will get more rejection letters.
Maybe she should send nano-squirrels instead, or a nice shiny barometer.
Margaret brought black nylon cubes, which she hopes to sell as misshapen
monoliths.  The monoliths have no eyes.  Jamie can't find MITSFS'
banana-colored monolith.  ``It smells like happy.'' Passes 4-3-3+Spehn.

%\subsection*{Pianocomm}


%\subsection*{Onseck}


\subsection*{Vox Sciurorum}

The Blue Jays are chasing my squirrels away.
I was ambushed by a squirrel last week.
Margaret predicts I will be killed in my bed by a pack of squirrels.

\goto{Old Business}

Miller Motion.  ``It's never too early to end the universe.''
Fails 7-12-something+Spehn.

Second Miller Motion passes \hbox{10-something- -3+Spehn}.

%ALGOL
%\goto{New Business}
%
%\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
