\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/07/2006}

\newcommand{\bing}{{\noindent\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 7th, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Jamie Morris, Pseudo-Onseck,
recording.

Minutes read.

Move to approve the minutes as Skinner-surprising chickens 2--1--3\ps.

\goto{Committee Reports}

% I'm taking these minutes and I'll darn well use a format I like!  So there!

\hskip\parindent
\textbf{Pseudo-Trojan:}
We just got a three-box donation from Ciaran DellaFera~'84 and it has
been processed.

\textbf{Mobcomm:}
We have yet more new books.

\textbf{Mobcomm:}
There are two MITSFS alums on the New Books shelf now, Guy Consolmagno
(the Pope's astronomer) and George Phillies (not the Pope's astronomer).
Malcolm notes that another MIT (but not MITSFS) author is Lofting,
who wrote the \emph{Dr.~Doolittle} books.

\textbf{MooComm:} \emph{Pirates of the Caribbean: Dead Man's Chest}
just came out.  The Tech has reviewed it.

\goto{Old Business}

Garrison Keeler told a penguin joke really badly and ever since people have
demanded he tell it every year.

\goto{New Business}

Readercon is happening in Burlington even as we speak.  Some of us are
even going tomorrow.

Andy hopes to run into somebody who knows somebody who could be usefully
shown her manuscript.

\goto{Future Business}

We should have an optical mouse on psi-phi soon.  Do not stare into laser
with one remaining eye.

The Japanimation society will be showing episodes of \emph{God (?) Save
Our King,} which begins with the protagonist flushing himself down the
toilet into another world, in which he is hailed as king.  The Society's
keen analytical minds detect a certain lack of proper electoral process.

Malcolm is reading \emph{The Rough Guide to Sci-Fi.}  They are aware
that the term ``sci-fi'' is frowned upon, but hey, it's a \emph{rough} guide.

It is theorized that the sci-fi which is a movie is not true sci-fi.

Jamie realizes that Joss Whedon $\neq$ JMS.  Oops.

Someone bought the rights to \emph{Worlds of If} and tried to revive it.
The fools!  It had been effectively killed off, on purpose, by its editor,
who also edited \emph{Galaxy} and hoped to merge the former's budget
into the latter's.  How \emph{eee}vil.

When \emph{Venture} went out of business they had a special offer: for \$10
you get your weight in back issues!  Michael actually went and did this.

Motion to send bananas to publishers of out-of-print science fiction magazines
such that they can make smoothies out of their slush pile passes 7--0--0\ps.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Grudgingly submitted,}
\centerline{Jamie Morris, Pseudo-Onseck}

\end{document}
