\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 1st, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Pseudo-Onseck, recording.

Minutes read.

Motion to commend the minutes for being read in one breath fails for lack of a second.

Motion to commend the minutes for being Kendra passes 8-5-6+Spehn.

\goto{Committee Reports}

There were committees, they did things.

\subsection*{LHE}
We have sent in a trial deposit to see if the new courier system works. If they don't lose this money, we will send in the rest of our ginormous deposit and stop being like a bank.

It would be good if this money were picked up by a girl with a skateboard named Y.T. ``No, really, it would be good if Yelena picked up the money.''

\subsection*{Vox Sciororum (Mumbling about Rats)}
The squirrel's mouth is like a big dark tunnel, like the Doomsday Machine from Star Trek. The actors in Star Trek would never act like nuts.

\subsection*{Star Chamber}
We've got mail. We received not one, but TWO copies of Stealth Planet. Is the series linear or geometric?

What does the Library of Congress do with all the self-published dreck they get?
\subsection*{Surgeon}
Kristin has started her Surgeon training! She can now deal with coverless paperback books, and she is qualified to do this on her own. We cannot see who she is unless she has bare feet.

\subsection*{PseudoUnknownUnknownsComm}
ALC: ``We did some new magazine [sic]''. We wrote down what they were. Inventory became much easier once we filed everything under ``book''.

Move to commend the magazine industry for not knowing the difference between Fantasy, Science Fact, and Science Fiction passes 9-8-5+Spehn. 

KR reads a quote from Locus about how a series about the history of Science Fiction is expanding because, ``The Seventies were complicated.''

Motion to censure the Seventies fails 6-8-7+Spehn.

ALC: ``Censorship is bad!''\\
ESK: ``So are the Seventies.''

\subsection*{PseudoJourcomm}

We have new art, which is slowly being incorporated into the next TZ. TZ is due out (all together now) ``Real Soon Now!''. TZ is supposed to be quarterly. The current publication schedule is, ``When it's done.'' Given that the current TZ is publishing on this schedule, we're doing better than Duke Nukem Forever.

\subsection*{PseudoPanthercomm}

The Panthercomm shelf is not being cleared. Bill does not include jhawk. ``What are you going to poke him with?'' ``Words.'' ``Sticks work better.''

Matrix Vote:

Motion: ``Getting Jamie a stick'': 10-6-8+Spehn\\
Motion: ``Get a Dianetics auditor in here to clear the shelf'': 6-5-7+Spehn\\
Motion: ``Poking jhawk into the Matrix'': 15-7-8+Spehn\\

Determinant: -11, all motions fail.

\goto{Old Business}

JFC has found an article about L. Ron Hubbard and how his books have been translated into 63 languages.

Geoffrey Landis will be speaking tomorrow, promoting his most recent book, ``Something Something Mars.'' a.k.a Mars Crossing.

There is a point where near-future SF becomes modern fiction.

ALC's motion, ``You cannot know that this motion is true'' chickens 10-2-12+Spehn.

ALGOL. 

\goto{New Business}

In Soviet Russia, usual debates you!

Pandemonium wants you to come there. Parallel discussions about Pandemonium and chainmail bikinis ensue. They, unlike us, have space. They, unlike us, want to attract random people off the street.

JFC ``doesn't trust German words.''

Yuki (yukikaze) arrives. ``Oh my God, there's people here!'' Aliens are people too. You have to latch onto their legs before they start running.

Despite all evidence to the contrary, KR has a brain. Ooh, there's hollow spots.
\goto{Future Business}

\goto{Time WARP to COMMITTEE REPORTS}
\subsection*{Philconcomm}
Philcon was awesome. It doesn't really have a focus.
\goto{Time WARB to FUTURE BUSINESS}
% Don't correct ``Time WARB'', it's intentional! - CJT

In the future, HRSFA's science fiction convention will happen. 

We acquired a copy of ``Nocturne! Explore the dark and terrifying realm of paranormal romance!'' Lots of motions rapidly ensue about getting rid of it.

KR is Not Collecting Kirk/Spock Either! The posters are the more worrying things.

Matrix Vote:

Motion: ``Mentioning a banana within 30s of Kirk/Spock is not suggestive'' 3-4-7+Spehn\\
Motion: ``We have not yet mentioned how much the Skinner hates Fragile Things'' 23-1-0+Spehn\\
Motion: ``We should not have a matrix vote.'' 1-5-8+Spehn\\

Determinant: 100, all motions pass.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Pseudo-Onseck}

\end{document}
