\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/18/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 18, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

Motion to commend the Onseck for having 88 votes passes 5-0-1+Spehn

Friendly Amendment: The Podcast is ``Second Shift''.  The ``friend''
is Brad Smith (yeah, yeah, the Skinner's imaginary friend is named
Smith. We believe him, of course we do.)

Motion to Manganelle a shuttle craft confuses the Society but Passes 4-0-0+Spehn

\goto{Committee Reports}

\subsection{PseudoMobcomm}
We got a juvie short story collection and juvie novel today. The
novel is ``Now a Major Motion Picture!''\\
``Harper Collins has sold its soul''\\
``No, that's what they have employees for''\\
``Right, they also gave us a copy of Tim Powers' new novel. We love
you Harper Collins!''
``Aren't corporations soulless anyway?''

A motion to start a fund to acquire souls for corporations fails for
lack of a second.\\
``For only \$0.50 per day, you too can feed a starving corporation''


\subsection*{Star Chamber}
The Skinner has requested the appropriate updates to the lock.\\
The LHE has processed all pending reimbursements.
We have a catalogue from ``Bulb Direct'' which sells lamps.

\subsection*{Onseck}
The cheques for new magazines will be going out soon.

\subsection*{Kvetchcomm}
Dzur came out. ``If there is anything I would use to descrive Steven
Brust, it is clever''\\
``If you dare spoil it, I will kill you''\\
``I won't spoil it... but I will say...''\\
ALC is encouraged to write a detailed review for Kvetchcomm.


Glen Cook's  \emph{The Tyranny of the Night} is awful, according to
Brian. He says in some ways it is reminiscent of \emph{The White
  Rose}.  He will be writing up a more detailed review about how it is
impenetrable if you don't have the real-world historical knowledge to
back it up.  \\
``If you make it past the first 500 pages, you'll finish''-BTS\\
``How many pages is it?''\\
``About 480''-BTS


``Did we have Old Business yet?'' -KHA
``Nope, but we should!'' -KR

\goto{Old Business}

``Enough talking about books! We don't do that here!'' -KR

Discussion of a book in which you can wish for any physical objects,
but once you have them you have to use them 8 hours a day.
Discussion of ``Little Red Riding Hood Cha Cha'' which 

A motion to acquire for the Library an accounting office, along with a
AAA+-certified operator therefor passes 5-1-1+Spehn.

\emph{This is apparently a reference to the Dragon and the George}

``Would that mean that there would no longer be No Accounting for the
  Society?'' -Y

``Which of us here is not subject to pedantry at times?''

\goto{New Business}
The Freshman are here!

A motion to greet the freshman passes 13+a ring-2-0+Spehn

Y has brought what appears to be a new magazine called Cool'eh.
It says that two lawyers in Florida were asked to play
rock-paper-scissors to determine where a deposition would take place.\\
ALC reports that a Japanese company was negotiating something to be
determined with RPS. They researched the game and won.\\
KKB reports that there is a RPS collectable card game.

\goto{Future Business}
'``Snakes on a Plane'' is coming out last night!'''-BTS\\
``What is it about?'' -JM

One of KR's friends complained that the movie was unrealistic---the
passengers had carryons.

A motion to suggest that the DOD that preventing knives on planes is compromising
Homeland Security fails for lack of a second.

The Activities Midway is two weeks from now, from 4-7 PM.  We will
need at least 3 people to help run it, who will need to be here at 2
PM.

Motion to acquire money from the Department of Homeland Security to
protect us from a New Threat: Bananas On A Plane! passes 15-5-2+Spehn

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}

% LocalWords:  Power's soulless LHE cheques Kvetchcomm Dzur descrive Brust ALC
% LocalWords:  KHA Cha
