\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/20/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 20, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Sniffen, Onseck, recording.

Minutes read.

Discussion over
Motion: to condemn the Skinner for being so lame about the adjournment
song and for hating Fragile Things so much.\\
Passes 28-0-0+Spehn


\goto{Committee Reports}

\subsection*{MobComm/Niagaracomm}
The minutes from last week are corrected to reflect what really
happened last week, which was sorting by quality.  More books were
ordered and received!

\subsection*{Trojan}
Donation is incoming! Run for your lives!

\subsection*{DexMistress}
Our negotiations with Hasslecomm are proceeding apace.  Hasslecomm may
have been taken over by the French.
\subsection*{Pseudo-Magdex}
The majority of the Analogs have been dealt with in a big party last
Saturday.  There will be another MagDex party again soon.

Motion to create Page19comm to study the accuracy and precision of 13
hour MagDex parties fails for lack of a second.

More discussion about MagDex, MagNatory, MagTrex, and MagTeX results
in an Albanian motion against BTS and JM.
Fails 11-16-1+Spehn

\subsection*{JourComm}
Real Soon Now! The second copyeditor will be returning it shortly.
It's about 30 pages, which is better than the last one, and has at
least one recent review.

\subsection{Phonecomm}
Is our donation.  ``Where in Cambridge are you?''

\subsection{BooksComm}
Please Shelve a Few!

Motion to increase the frequency at which we publish TZ such that we
are the second-most-frequent publisher of Zines--because ``at
Hertz, we're second-best but we  try harder.''

\goto{Old Business}
40th anniversary of Star Trek is coming up!
The Skinner's least favorite book has expired from the New Books
Shelf.
KKB arrives and is interrogated about the boxes labeled ``Magazines
displaced by bound volumes'' which were MagDexed. Procedure may have
been 

A motion to Dispatch Mag, son of Morian to find the bars of gold that should have
been in the boxes labelled ``Magazines displaced by bound volumes''
passed 14-4-3+Spehn

A motion to congratulate KKB on her defeat of MS Excel passes by
Skinnerial Decree, after he fails to be able to count properly.

\goto{New Business}
George R.R Martin, instead of finishing ``Song of Ice and Fire'', has published
a children's book.  It is in the same universe, though.

The Onseck is instructed to not put spoilers for Martin into the
minutes, but to tell people that All The Characters Die.

HRSFA is running a SoIaF LARP, for those of us who have read the books
and do that sort of thing.

The Skinner points out that a book being advertised in LOCUS has the
same cover artist as Harry Potter.

Also in LOCUS it says that Haldeman has submitted his next book to
Ace.  This boggles the Skinner, since Haldeman is teaching his class.

``Usual Motion''\\
``We had that already!''\\
``Oh.''

\goto{Future Business}
In the future, LSC will be showing ``A Scanner Darkly''\\
In the future, the phone will ring with our books.\\

A Miller Motion fails 6-10-2+Spehn
JM: ``We haven't had a new Prentice in a week, and there's a new
person sitting on the floor with a book''

ESK's picture has vanished again,
ESK is informed that she must have a picture. 
JFC: ``I've got a better one, with less writhing but more skin'' 

Something about an Italian Scallion prompts a  Miller Motion, which
chickens 4-8-12+Spehn


``Skinner still hates Fragile Things, why is he such scum?''
``Skinner still hates Fragile Things, he called Gaiman dumb''

JM insists that the Library is singing too well, and we need to be
more out of tune.

A motion to bing JM with the gavel, amended to be a banana,  until he goes back into tune
passes 17-6-4+Spehn

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Sniffen, Onseck}

\end{document}
