\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/04/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 4, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

A motion to approve the minutes as not being very informative at all
passes 6-1-2+Spehn

\goto{Committee Reports}

%\subsection*{Onseck}

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

\subsection*{JourComm}
TZ is coming soon! Jourcom needs only two things: cover art and
something that clearly isn't a Skinner rant, no no no. The Skinner
would never hold up the publication of TZ.

A motion to commend Jourcomm for flouting all tradition passes 10-4-1+Spehn

\subsection*{LHE}
Cheques are here! 

Mad magazine once published a magazine with a cover that was painted
by a monkey.  We will not be going into Building 66 for it.
%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}
Experimental binging with the wrong end of the gavel is
dissatisfactory.  Discussion of the pitch of the bing and whether it
is a pure tone results in a non-voted resolution to measure the tone.

\goto{New Business}
The Skinner does not play charades well.
Joe Haldeman published a new book!

``If the Skinner gesticulates wildly, eventually the Onseck will make
up the truth.'' 

``Ooh, Henry Jenkins has a weblog?''-KR\\
``Just recently''-KHA\\
``Everybody's doing it, then?''-KR\\
``Yup. This is why DOPA is dopey'' -KHA

A motion to commend Congress for being really stupid fails for lack of
a second.

KR puts in a plug for his company's new product, Hiveminder.com

KKB says ESG just got rid of a bunch of sci-fi books and she brought them
to us.  She left them in the annex.  \\
``They're free, and they're books, and there's a lot of them''\\
``Three good things!''

\goto{Future Business}

``In the future, ALC will have access to the Library''-ALC
KR has sent the list, which he will send again today.

A visitor who writes for a German fanzine wants to write about MITSFS
and especially the Perry Rhodan books. Apparently we have a very rare
poster on our wall in the first aisle. 

Disussion of the SNR of the minutes as compared to 
Discussion of what you call the first 10 years of a decade determines
``oughts'' or ``aughties''

Discussion of why there are so many vampire books (Buffy spinoffs?)
and not enough space (Firefly) books comes to no conclusion.

A motion to replace the CAC with a pile of banana-fueled monkeys so
they'll change our locks passes 10-i-i+Spehn

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
