\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/16/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 16, 2006

Boomtime, the 21st day of Confusion in the YOLD 3172

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST
Brian Sniffen, Viceand Pseudo-Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.


Motion to commend the minutes as timely passes 10-4-2+Spehn

Motion to commend the minutes for being misunderstood fails for lack
of a second

\goto{Committee Reports}

\subsection*{Pseudo-LHE}
LHE knows how to do reimbursement forms.\\
Rites have been updated.

\subsection*{hBarcomm}
The plan successfully concluded! 
CCCth has a CYOA game by clicking.

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

\subsection*{JourComm}
Still needs things to publish

\subsection*{Trojan}
The Alpert donation is nearly finished! Half the remaining boxes were
processed this week.

We figured out what happened to the two-box donation: it was two
donations, each of one box.

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

\subsection*{Vox Sciororum (Mumbling about Rats)}
Both JFC's squirrel friends had babies and have brought them to visit.

Motion to refer to all groups of squirrels as ``murders'' fails for lack of a second.

\goto{Old Business}
No reply about the Aurora shelves.  We shall attempt the
telephone. Their webpage appears to have gone away. If they
disappeared, we will have to look for some other distributor, who will
probably not be an MIT alum, and therefore less sympathetic to our
needs.

\goto{New Business}
``What about the usual vote?'' -KHA\\
``Hah! My coup is nearly complete!'' -BTS

There are new books. Many of them are on the Bluebellcomm shelf, since
all Mobcomm's Amazon books were processed.

The new movie ``Cars'' has at least one seen in homage to Asimov's
intelligent car. Much debate ensues over which story and why.
``Sally'' is mentioned as the name of the short story, and JM went to
look. Zelazny aparently had a non-3-laws car which ate people, named ``Jenny''.

\goto{Future Business}
In the future the Skinner will return, but not next week.
Brian the false prophet may get stoned if KR doesn't return.

Discussion about whether there will be an Inventory this summer (no,
probably not) and when the Purge will happen (this summer). Apparently
Inventories get less frequent as they get shorter. ALC suggests that
we could RF all the books.

Miller Motion fails 2-13-6+Spehn

``banana motion'' fails for lameness.

Move to end the meeting fails for lameness and a chance to explain to
the new people that it wouldn't have mattered.

Really really painful singing: 
Pseudo-skinner has no pseudo-tail at all, just a bloody pseudo-stump.

\bing
\noindent
Meeting adjourned, 1723 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
