\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 10, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion to commend last weeks' minutes for having been lost in translation passes 13-0-4\ps.

\goto{Committee Reports}
Motion to instruct TZ to send out rejection letters to people to encourage them to write better
material for us passes everyone to no one to someone \ps.

\emph{...<crickets>chirp chirp</crickets>...}

Margaret is trying to persuade iRobot or the Museum of Science to hire her.

YT: ``A full-time job is less full-time than MIT.  MIT doesn't do things I like, and Harvard's a
bunch of fuckwits.''

\*subsection{Onseck}
We got a self-published book in the mail from one Christoper A. Zackey, which appears to flout the
conventions of the self-published genre, in that the author knows how to spell `there' and `their',
and knows what the difference between them is and uses them approporiately.  Having read half of
the first story in it, the Onseck claims that it's like \emph{Jabberwocky}, but with more plot.

\goto{Old Business}

Motyn to approve of Jamy's status as an artystyc yndyvydual of yndetermynate gender passes 15-0-3\ps.

JM: ``Argh, I don't want to be in Yelena's mind.  It's dirty in here!''
YT: ``Oh, you're the dirtiest thing in there.''

Usual &c.

\goto{New Business}
There's a new Neal Stephenson book out.  (The Onseck wonders how he missed this...)  Jamie suggests
that a book called \emph{King of the Vagabonds} in paperback is probably only half of 
\emph{Quicksilver}, since it's a bit too unweildy a book to deal properly with the transition to
paperback.

JM: ``I made \emph{very sure} not to watch when William Shatner might have been reproducing!''

ALC: ``Never bring a shotgun to a gunfight.''\\
KR: ``Isn't a shotgun... a gun?''\\
JM: ``Shh... he hasn't figured that out yet.''

\goto{Future Business}
In the future, Margaret will get rejection letters.

Paige will be back in town Real Soon Now!

In the future, Yelena's card will work in the lock.

JM: ``He groped me when I was cross-dressing once.''\\
KR: ``Are there spoons in the PicnicComm drawer?  I have this pressing need to gouge my inner eye
out.''

MHG: ``Let's have a woad party!''

JM: ``There is \emph{not} an LD50 for explosions!''

The Onseck starts singing the Adjournment Song, and the rest of the Society joins in somewhat less
tunefully...

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
