\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 24th, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Pseudo-Onseck, recording.

Minutes read.

Motion to condemn the Pseudo-Onseck for taking more than one breath to read the minutes passes 3-3-2+Spehn.

\goto{Committee Reports}

\subsection*{Skinner}
The Skinner sent out the Fall Mailing. It is now officially fall, and also officially post-orientation. It would be nice to get a system that doesn't suck for sending this mail. This problem is harder than NP-complete.

We have not received any new books this week.

\subsection*{Pseudo-Trojan}
The good news is that the ``substantial'' donation is only 14 boxes. The bad news is that we don't have space for 14 boxes. We also don't know how large the boxes are. The problem is not square feet, the problem is cubic feet.

This is not the book the Skinner thinks it is.

\goto{Old Business}

It was Thanksgiving yesterday. Happy Thanksgiving, everyone. Michael is still full, but that's because he ate Thanksgiving three times. 

Discussion about Random's Thanksgiving dinner ensues. The dorm has a dozen or two dozen turkeys. Ooh, free turkey.

Motion to develop an antidote to L-tryptophan disappears into the sleepy void.

ALGOL. The usual debate is less vociferous than usual.

\goto{New Business}

We're just pretending the Barbie and Ken Star Trek set doesn't exist.

Ignorance is bliss. MIT is whacking the ignorance out of you. KR would love it if his classes stopped beating him up. 

JM: ``You have sent out invitations for the fall picnic, right? You know, the one where we all go out in the snow.''

On Tuesday, 21W.759 will workshop KR's story. He has been giving ``not so glowing'' reviews to his fellow classmates' stories. Haldeman lives in Florida for most of the time.

\goto{Future Business}

In the future, we will go out for dinner. 

Any objects that the Egyptians made with the help of aliens do not count as human-made. The government was going to cut the funding for ``The Guy'' who listens to the Voyager signals.

Motion to send out to Voyager a banana on which is inscribed an essay about how much the Skinner hates Fragile Things as well as a transcription of today's comic in the Tech about bananotechnology passes by Skinnerial Decree.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Pseudo-Onseck}

\end{document}
