\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 24, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion regarding the reading of the minutes fails for lack of a second.  We move on to committee
reports due to lack of enthusiasm from the assembled members\texttt{^H}.

\goto{Committee Reports}

%\subsection*{Skinner}
Andrew has sent mail about getting Yelena added to the access-list for the door.

Ed explains the TIF chart.

%\subsection*{War Council}

%\subsection*{MobComm}

%\subsection*{LHE}

%\subsection*{FAC}
%Obligatory whine.

%\subsection*{Pianocomm}

\subsection*{Onseck}
We've been receiving less mail than usual.  This is probably due to UA pantslessness.

%\subsection*{Vox Sciurorum}

\subsection*{Pseudo-Barcomm}
We've got a shiny new poster in the Infinite thanks to Kat.

\goto{Old Business}

The Skinner discovers that Pandemonium is moving to Central Square.

We get strange mail, part N: someone sent us an ``article concept'' about some (real life) SF 
author who sold a story to some movie moguls.  We clearly want to publish this in TZ.

The Society discusses \emph{Lost}.

Usual motion, &c.

ALGOL
\goto{New Business}

The Skinner is reading \emph{The Duke of Uranium} by John Barnes right now.  He says it reads
like early Heinlein, and he's enjoying it.

One of the prentices walks in!

A possible connection between the KGB and the rise of non-representational art during the
1950's is discussed.  ``I could see the KGB having \emph{one guy} on that project.''

Michael: ``I picked up a copy of \emph{Surfing Samurai Robots} on the recommendation of a friend.''\\
Malcolm: ``Is he still your friend?''

The Onseck just started Kelly Link's first short story collection, \emph{Stranger Things Happen},
and has fallen in love.  (With the book!  With the book!)  Kelly Link writes like the Onseck 
hoped Charles de Lint would write, before he'd read any Charles de Lint.  She seems to write 
practically only short stories, which is kind of unusual in this day and age, but they're good
short stories---mildly surrealist fantasy, a lot like Neil Gaiman's more surrealist stuff, 
\emph{eg.} ``Daughter of Owls''.

Motion to go downstairs and prop up the Skinner's blood-sugar level by feeding him some bananas 
passes 10-0-7\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
