\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 21st, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1800 SST,
Kevin Riggle, President and Skinner, presiding; Kate Kuznetsova, Pseudo-Onseck and LHE, recording.

Minutes read.

Motion to approve the minutes as micro-managed passes 9-0-1+Spehn

\goto{Committee Reports}

%\subsection*{Pseudo-Onseck}

KR ordered a new withdrawn stamp.

Kat mailed off the stuff on Sunday.

%\subsection*{LHE}

Reimbursements will occur. Rain doesn't like checks.

Bills will be paid. The LHE  is sufficently intimidated.

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Pseudo-Mobcomm}

There are many books. They multiply! We had about 3 boxes and then the next time there were 9.

KR wonders if we are using Ingram yet, but we are not.

JM interrupts a bing to whine about walking envelopes.

ALC should be kicked. Also, ALC should come to the library and work on the Alpert Donation. But, mostly, kicked.

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

KR has not researched warehouse space. JM may have. It will exist.

We have an old keyholder visiting! He was an assistant Jourcomm and Panthercomm and part of the MITSFS gang, which ruthlessly terrorized the countryside. He insists that the old days were never innocent. He was also chief crank. The pseudo-onseck has no clue what that means.

The Skinner remarks that TZs are not dated on the cover- tricky, that. There is a disscussion of how often TZ used to come out, is going to come out and so forth.

Lame ideas for fundraisers are suggested. The Pope's Astronomer is going to be a guest at Boskon. Also, he is our alum. And may have published in TZ. 

Usual Motion&, etc, etc.

\goto{New Business}

Michael donated a book coauthored by Henry Jenkins about Star Trek and Doctor Who fandom. The title is ``Science Fiction Audences Watching Dr. Who and Star Trek'' It is fairly old- back then there were only 4 incarnations of Star Trek.

Someone is advertising 'The First Season'' of Dr. Who on DVD. They aren't very smart. JM points out that it didn't get good until the /real/ third season anyway. There is a lot of disscussion of the original Dr. Who. Some people think that it was 'charming'.

``Two color presses? We could only afford one color when I was a boy...''

There is a disscussion of old shows with bad production values. 

``This deathmask wouldn't work. It is suffocating the guy underneath...guy underneath?! I thought we were getting a dummy! No, no, we couldn't afford one''
-On production values during the depression.

Mobcomm got us the first volume of the Star Trek Comics. The PseudoOnseck cringes. The alum wonder sif this is praiseworthy.

KR: ``Complitionist.'' 

They have released a set of Glash Gordon episodes that were made in West Germany way, way back. This makes Delorenzy look good by comparison.  KR mentions Hungarian Star Wars.  A certain Taiwanese translation is mentioned- apparently Leia's first line was:
``Oh, how I need a man. These robots are no good!''

/bing

\goto{Future Business}

According to JM, very soon we will all drown.

Andy is expecting the Horsemen of the Apocalypse real soon now. Also, during the night, a lot of bees decided to nest in her hair. Actually, the last sentence is blatanly false.

``Schroedinger's Cat has 3 states- dead, alive and bloody furious''


\goto{Old Business}
Time-warp to Old Business: Andy didn't pitch stuff at Readercon, but she may next time.

Timewarp ends.

\goto{Future Business}

KR describes an episode involving peopel playing Rush band songs at him for an hour. He pointed out that it was ``Rush Hour'' and was told not to.

Miller Motion fails 1-5-6+Spehn

KR:  ``If the first Miller Motion passes, are the lights in the Green Building defined to be off?''

A disscussion ensues. The consensus is 'no'. Also, if the universe is destroyed, there are no windows.

The second Miller motion passes by a lot.

\bing
\noindent
Meeting adjourned,  18Banana-banana-banana30 SST.

\vspace{18pt}

\centerline{Caligraphicly unsubmitted,}
\centerline{Kate Kuznetsova, Pseudo-Onseck}

\end{document}
