\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/28/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 28, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.
A motion to commend the minutes for all sentances involving rush hour passes 6-3-2+Spehn

\goto{Committee Reports}

\goto{Old Business}
\emph{A retroactive timewarp moves us to Old Business. I've put it
  here because linearity is fun}
Chip Hitchcock was the alum who was here last week.

A motion to retroactively table the Committee Reports chickens
1-2-6+Spehn

We have a new Tim Powers book as a review copy.

Motion to thank Powers for writing a book about the publication of TZ.
Passes 8-2-4+Spehn

``You do not want to know how the sausage is made'' -KHA\\
``I like to make it of Lawyers'' -JM\\
``It's scary vegetarian sausages. The smoke-flavoring is not you
friend'' -KHA\\
``I like sausages made of scary vegetarians'' -JM\\
``Yeah, but it's hard to make the ends meat'' -Y\\

KCR is a keyholder again. Hooray!

 Our Library Store order came in!

\goto{Committee Reports}

JM called the shelving people, and got their only address for
shelving, which is what he'd been emailing before. He fears they are
blacklisting MIT.

``I hope you told the shelving people to go shelve it?''\\
``More of those are going to leave me with an Aurora of pain''\\
``Are you seeing red?''\\
``the new Aurora shelves are scarlet''\\
``I don't give a damn''\\
``Hoovre does''\\
(something about electricity that the Onseck missed)

\subsection*{Star Chamber}
The LHE declines to given an LHE report

\subsection*{hBarcomm}
We have a new poster for the Midway. It's not done yet.
We need more informativeness on the poster.
It will have a rocketship soon.

``Motion to acquire somewhere between 90 and 100 dissertations from
Course 24 and attach them to the poster.  By attaching 95 theses, we
can increase the mass.''  -BTS\\
(Fails for lack of a second or ack by the Skinner)

Albanian Motion against Brian passes 8-6-4+Spehn\\
``I'm sorry love, I hate to do it, but you have to go''-KHA

\goto{New Business}
The meeting breaks up into several conversations. \\
The Skinner is reluctant to bing, and is taunted by the Onseck.\\
``Take control! Bing it!'' -KHA

\goto{Future Business}
``Ooh, good hangtime!'' -JM

In a very short time, we will have frosh!
Fall hours will be coming soon, too!

The Skinner motions to acquire bananas to feed the freshmen.

Move to censure the skinner for making an exceptionally lame banana
motion and tricking the Society into ending the meeting early fails 7-9-1+Spehn

Yelling about ``LAME!'' convinces the Skinner to withdraw the motion.

Discussion ensues about the PAE, and the tradition of each generation
of a title being one step junior to the prior incarnation.

Has NESFA been mailing us books when they publish them? Mobcomm should check.

``Skinner has no tail/good ideas at all...''

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
