\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion to correct last week's minutes to reflect that the motions to end the minutes were in fact
Miller motions, and condemn the pseudo-Onseck appropriately passes 9-0-3\ps.

\goto{Committee Reports}

%\subsection*{Onseck}

\subsection*{War Council}
We've moved stuff around in the Library!  We're working on getting shelves for one of the bookcases,
while preserving access to the lightswitch.  A bunch of things have been moved to the Lab---most of
the fanzine cabinets---and the new books now have a Real Shelf!  There's still some more stuff to
move around.

%\subsection*{FrustratedAuthorComm}

\subsection*{JourComm}
Kat is now \emph{officially} JourComm.  ``Oh, crap!  Now I'll \emph{never} be able to release 
another TZ!''  It's now taking submissions of fiction, reviews, thoughts, drawings, etc., ideally
in plain text or in whatever graphic format you can provide them.  They should be science-fiction 
related, and Kat doesn't promise to publish them, regardless.  She pimps the latest TZs.  Apparently
Hugo Gernsbeck was the reason we started TZ---he gave a speech suggesting that we publish a zine, 
since we would put real science in it.

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

\goto{New Business}

Motion to commend the Skinner for his new haircut (4-6-8\ps)
Motion to commend the squirrels responsible (12-0-4\ps)
Motion to condemn the Skinner for (9-1-4\ps)
Determinant is 8.  All motions pass.

LSC is showing \emph{Mirrormask} tomorrow!  And it's free to prefrosh.

Miller motion fails 0-8-6\ps.

The prefrosh leaves.

Motion to schedule a coup passes 6-4-1\ps.  The Skinner schedules it for the next elections.

The Society has recently acquired a copy of \emph{Unleashed in Space}, a rewrite of \emph{The Legion
of Space}, by Jack Williamson, which now stars a dog (namely Wishbone of the eponymous PBS kids' TV series.

In the future, the MITSFS Advanced Biblio-Warfare Facility will become the MITSFS Advanced Bibio-
Warfare Laboratory, so we can refer to it as ``The Lab''.

In the future, \emph{censored for national security purposes}.

We had a prefrosh who was trying to choose between Caltech and MIT.  Brian observes that ``We have 
a cannon.  They don't.  We made very sure of it.''

Motion to steal Harvard's statue and put it in Caltech's courtyard passes 17-1-4\ps.

The official word comes in that HRSFA lamed on invading us upon learning that this was our prefrosh
weekend, and didn't want to scare the prefrosh.  The prefrosh who stuck around to watch the raid is
disappointed.
``They're great at holding rituals wearing long black robes and saying long, cryptic things, but 
when it comes to planning a siege, they don't really know what they're doing.''  

The Skinner decides not to retaliate until they actually get off their asses and do something to us.

Motion to brick over the HRSFA office door with bananas chickens 4-0-4\ps.

Second Miller motion fails 9-12-2\ps.

Motion to acquire a jar of bananas in formaldehyde to stock our Bibilowarfare Lab passes 6-0-4\ps.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
