\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/21/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 21st, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion to pass a motion regarding the minutes without a second passes 7-0-0\ps.

\goto{Committee Reports}

There is an exceptionally loud bing, and the Onseck says ``Ow.''

%\subsection*{Onseck}

\subsection*{PianoComm}
Kate's card works now!

ESK: ``I wanted to live here when I visited over CPW, but nobody paid any attention to me, so I had
to live at Random.''\\
JM: ``We could have you bound...''

The Skinner and Michael recite Tennyson's \emph{The Charge of the Light Brigade}.

ALC: ``Kate, we still need to figure out if you're a demon or not... do we have any ducks around
here?''\\
JM: ``We have a devil duck...''\\
ALC: ``Okay, so if she weighs the same as a duck...''\\
JM: ``That's what you do to \emph{witches}, you idiot!''

Motion to declare Kate a miscellaneous supernatural being (12-0-2\ps)\\
Motion to submerge Kate in a vat of holy water and see what happens (5-0-1\ps)\\
Motion to submerge Kate in a vat of liquid nitrogen and drop her from the Green Building (2-5-1\ps)\\

Determinant is -45; all motions fail.

JM: ``I should have just combined those and dipped you in holy liquid nitrogen.''

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

ALC: ``The bing is important.  It has to be loud, but not too loud.''

We got a call from Marc Alpert asking where his tax donation letter is.  We've started processing 
it, and Andrew will work on it more this weekend.

ALC: ``We're all being replaced by computers soon.''\\
JM: ``Some people are more easily replaced by computers than others.''

Kate needs to read the PicnicComm rites.  The Onseck frobs the appropriate lists.

Usual \emph{\&c.}

\goto{New Business}

Next week the Coolidge Corner Theater is showing the original \emph{Gojira} (Godzilla) with the 40
minutes which were cut out of the standard American release.

Slashdot reports that ``TrekToday reports that Paramount has asked 'Lost' creator J.J. Abrams to 
direct a new \emph{Star Trek} film. The movie will be set at Starfleet Academy and will feature 
younger versions of James T. Kirk and Spock, chronicling their first meeting at the Academy and 
their first outer space mission. The movie is set for a 2008 release and will apparently be one of 
Paramount's biggest projects for the year.''

Motion to resurrect Jim Henson to make a \emph{Starfleet Babies} series properly passes 9-4-6\ps.

\emph{Ender's Game} has apparently been optioned again.

\goto{Future Business}

In the future, there will be a picnic.

In the future, the Skinner will have another degree (not quite by next month, but before next term,
he claims).

Motion to build a bananapult in the Blue Hills to protect our territory passes 2-12-6\ps.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
