\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 5, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion to approve them as Xena's minutes passes 7-1-5\ps.

\goto{Committee Reports}

\subsection*{PseudoPicnicComm}
The invitations will be going out... today.  The Skinner will abduct PicnicComm if necessary and
watch over her as she writes them.  Elections will be on Friday, May 19 and the picnic will be on
Saturday, May 20.  The Skinner will make sure that PicnicComm gets a room to use for the picnic in
case of rain, and make sure that PicnicComm coordinates transportation.

\subsection*{ClueComm}
ClueComm (Jamie) exists, officially.  The Skinner will make an appropriate list and send e-mail.

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}
Kevin has become old, bitter, and jaded already.  The eyeshadow may be accentuating this effect.

Kate walks in to wild applause.  ``This is about the picnic, isn't it?''  Kate, the Skinner, and
Jamie will come back to the Library after the dinner trip to deal with invitation.

The Skinner has finished about two-thirds of the Alpert donation.  Jamie quizzes the Skinner on the
current state of the other pending donations.

ALGOL.

\goto{New Business}

Kate made two people come to the meeting!  The Society decides that she has an awesome hat.

Motion to say ``Hi!'' to Lisa and Fiona in an embarassing fashion passes 12-3-1\ps.

All: ``Hiiiiiiiiii!~''

``We voted you Xena.''  ``Do I get a cool weapon?''

Motion to build a banana-stone pyramid enclosing MITSFS to keep our books sharp passes 12-7-8\ps.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
