\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 14, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

The Skinner would like the minutes to reflect that Margaret is not here.

Motion to approve the minutes as deserving of a larger audience passes by Skinnerial decree.

\goto{Committee Reports}

%\subsection*{Onseck}

\subsection*{War Council}
Kate's card still isn't working.  Andrew will kick the CAC again.  He will also look into scheduling 
elections.

The Onseck has received word of a CAC Advisory Committee, which we are attempting to join.
Motion to commend MITSFS for sinking its tentacles into the CAC passes 10-0-2\ps.

\subsection*{FrustratedAuthorComm}
FrustratedAuthorComm whines that she hasn't been rejected yet.  She's sent out more stuff with 
shorter lead times, though.

%\subsection*{JourComm}

\subsection*{Pseudo-Mobcomm}
We've got more books!  We don't have quite as many more books as we think we should have, but we've
got more books.

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Motion to build a new universe for MITSFS use only fails by Skinnerial decree.

Miller motion (the Skinner overrules Kate's and Margaret's votes by reason of ignorance and apathy)
fails.

Second Miller motion passes 11-0-1\ps.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
