\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion to approve the minutes as extremely logical passes 6-0-1\ps.  ALC: ``Boy, don't we have an
enthusiastic crowd last night.''

\goto{Committee Reports}

\subsection*{Pseudo-Dexmistress}
There were a bunch of people running around last week mumbling nonsensical things.  When the stack
of strangely-marked papers has been fully processed, we will know whether Inventory was a success
or not.  We're a little worried since it appears that book-loss per unit time has increased since
the last Inventory.  There may be other Societies in parallell dimensions, but they're not really
our concern for Inventory purposes at this time.  (We might want to annex them to store our 
overflow, however.)

\subsection*{SexySexyPriestComm}
Margaret shows off her vestments.

%\subsection*{War Council}

%\subsection*{MobComm}

%\subsection*{LHE}

\subsection*{FAC}
Obligatory whine.

%\subsection*{Pianocomm}

%\subsection*{Onseck}

\subsection*{Vox Sciurorum (Mumbling about Rats)}
The sparrows are getting better at stealing John's squirrel food.

\goto{Old Business}
There are squirrels here.

The 20th anniversary of the Challenger disaster, the anniversary of the Apollo 1 disaster, and
the anniversary of the Columbia disaster are all coming up within the next month or two.  Sorry,
NASA.

\emph{::crickets::}

ALGOL
\goto{New Business}
``Ah, IAP, that wonderful springtime of MIT when we don't have classess---except that it's during
the winter.''

MHG: ``AG.001 (Assassin's Guild): How not to be harvested for your spleen''

The LSC Science Fiction Marathon is tomorrow night.  It starts at 7ish and runs all night.  They're
showing \emph{Serenity}, \emph{E.T.}, \emph{12 Monkeys}, \emph{The Empire Strikes Back}, and 
\emph{Red Dwarf} episodes.  MHG: ``Oh, it's a good lineup.'' 
JM: ``No, no, it's supposed to be a \emph{bad}
lineup---the classic LSC Science Fiction marathon showed movies like \emph{Zardoz} which you 
couldn't stand to watch sober.''

We need to schedule a Star Chamber meeting with the Dexmistress to set upcoming Library policy.

\goto{Future Business}

An Albanian banana motion passes 10-1-5\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
