\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 10, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Ed Keyes, Vice and Pseudo-Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Ed gets a better bing.  Motion to make the Onseck continue reading the minutes
until someone thinks of a clever motion regarding them passes.

Motion to place the minutes in an endless recursion loop fails.  Motion fails
for lack of a first.

\goto{Committee Reports}

\subsection*{Onseck}
Maco has cleverly stopped making the rectangular orange stickers we use for 
marking magazines in the dimensions we want, so we're buying ones which are
larger and cutting them down to size.

Malcolm: ``Would it be practical for us to buy white stickers and spray-paint...''
Everyone: ``No.''

ED: ``So what we need to do is buy white stickers and feed PantherComm 
Cheetoes...  So the new policy is, `no food in the \emph{circulating} room.'''

%\subsection*{War Council}

%\subsection*{MobComm}

%\subsection*{LHE}

%\subsection*{FAC}
%Obligatory whine.

%\subsection*{Pianocomm}

%\subsection*{Onseck}

%\subsection*{Vox Sciurorum}

\goto{Old Business}

Dr. Marc Alpert, ex-Skinner, would like to congratulate the Society for putting
out another TZ.  He says we may be on track to beat his record of three issues
in two years.  Jamie points out that his (Jamie's) father put out six issues in two 
years a few years before Dr. Alpert became Skinner.

Dr. Alpert: ``I looked on eBay, but the old ones still aren't worth much.''

Dr. Alpert dropped off 20 boxes of old SF magazines---35 years' worth of 
collecting---for us today.  ``They're probably worth in insurance value
\$BIGNUM... unfortunately, if I could sell them for that, I wouldn't be
donating them to the Library.''

Jamie suggests that when we pull things, someone should sit down and check out
used-book dealers.  If something is moderately expensive, that means it is 
hard to replace, so we should consider keeping it.

ED: ``Usual debate, usual result.''\\
KR: ``Usual vote.''\\
Someone else: ``Usual motion.''

ALGOL
\goto{New Business}
Ed got a reply back from the SFWA representative, who said that we could just
integrate their books into our main collection.  They still need to be marked
as ``Property of SFWA,'' but we can put them on the shelves with everything
else.  This may require some Dex magic---Ed is working on it.

ED: ``I don't believe that they want them back.''

Sam moves to package one JHawk and all the bananas MITSFS has ever received
and send them to a gentleman who believes that libraries should keep all 
copies of all books and newspapers they ever receive passes 14-0-1\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
