\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 24, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Jamie motions to condemn the Onseck for truncating his motion regarding the reading of last week's
minutes to the point of unfunniness BORK BORK BORK chickens 6-2-14\ps.

\goto{Committee Reports}

\subsection*{War Council}

THIS SECTION MARKED CONFIDENTIAL---STAR CHAMBER'S EYES ONLY

\subsection*{CunningHatComm}
There is a cunning, knitted hat.

\subsection*{Onseck}
We got a proof copy of \emph{Infernal Devices} by Philip Reeve in the mail today.  Someone should
write a review of it.

\subsection*{TheGoodKindOfRingComm}
Two keyholders and former Society officers are engaged---congratulations to Kat and Brian!

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

\subsection*{Pseudo-Trojan}
Jamie has created the office of Trojan for the person in charge of handling donations.  (``Beware
of geeks bearing gifts.'')

Jamie processed the Dupree donation, and Andrew has started processing the Jacobs donation.

Malcolm moves to incite the Boxer rebellion.  (``Briefs!  Briefs!'')  Chickens 6-4-10\ps.

A CP just walked by and gave Margaret a strange look.

\subsection*{HassleComm}
Since Kate is going to be in town over Spring Break, the Onseck will poke Jake to see if he wants
to do a pass this week.

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

There's nothing old under the sun.

\goto{New Business}

It's Spring Break!

\goto{Future Business}

In the future, the Borders at the Cambridgeside Galleria will be having Wen Spencer discuss her
new book, \emph{The Wolf Rules}, on April 17.

Motion to save space in the Library by removing all books which are not by the best writer ever
fails for lack of a second.

Andrew is hoping to move stuff out of the warehouse and do some rearranging over break.  He'll
send e-mail about it.

[\emph{elided}] passes 4-1-3\ps.

Motion to save space in the Library by removing all books which do not contain bananas.
Motion to save space in the Library by removing all books which contain bananas.
Motion to save space in the Library by removing Yelena for failure to contain bananas.

4-7-6\ps
2-10-9\ps
0-2-16\ps

All motions pass with a determinant of 39.


\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
