\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/10/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 10, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Sniffen, Onseck, recording.

Minutes read.

A motion to approve the reading of the minutes as rapid and clear
fails 7-9-1+Spehn.  The Onseck complains that that is the slowest
she's read the minutes in some time. This is only partly because she
doesn't read them out loud at home, though she does always read them.


\goto{Committee Reports}

%\subsection*{Onseck}

%\subsection*{War Council}

\subsection*{FrustratedAuthorComm}
The Skinner has written a story! It is much longer than the last time
he wrote it.

\subsection*{JourComm}
TZ is coming very soon---it is written, edited, laid out, and the only
problem is that there are 6 instances of some art called ``Art to
Break up Blocky Text'' which look an awful lot like 

\subsection*{hBarcomm}
We have new posters!

An alum appears, Whitfield Diffie, announcing that ``I try to come
every decade, whether I need it or not''.  He last appeared June 2,
2000.

\subsection*{TableComm}
The last living person who knows the location of TableComm.  The
report of the Table Committee remains unchanged.  This time he also
purchases a TZ.

\subsection{AlohaLensComm} 
Has dramatic shots of the meeting, which could perhaps be used in TZ.

\subsection{Trojan}
Kevin sent off the Osbourne donation letter today.
Discussion ends up drifting to Niagaracomm. 

\subsection{PseudoMagInv}
Magazine Inventory this Sunday!
MagDex has been renamed to the MagTrix, still spelled ``M A G D E X''

\subsection{Onseck}
We have new reinforced hole punch paper.  We tried ordering Membership
Sheets from CopyTech, but they failed us---the holes were not
reinforced, and although the up-down parity was correct, the
left-right parity was wrong.

Discussion of Arabic and German membership sheets

\goto{Old Business}
David is trying to figure out how to turn our 1949 microfilms into
something readable by modern technology.  Apparently JM looked up the
half-life of the microfilm, and it was like 50 years.
Our readers may or may not actually function.

\goto{New Business}
Discussion of copyright issues continues over the Old/New boundary.

Cecila Tan is running an eBay auction to have someone write a short
story to ones specifications. BTS reports that the bidding is going
extremely high.

Alumna Ariel Segall is the Pandemonium Iron Gamer Miniature Painter.

Some complaints about the fact that the Skinner announced the New
Business are resolved with a motion to timewarp back and not announce
it. The motion passes by Skinnerial Decree.

JM tells us about the Star Trek Barbie in the Sacks, frightening the
Skinner. It is not brought out, on threat of violence.

Discussions about Amazon shipping delays and the fact that Ingram did
officially refuse to deal with us result in a lot of quietness.

\goto{Future Business}
There is a new SF movie being made---``Meet the.'' It has a
Tyrranosaurus Regulus, among other things.

KR has a friend at CMU, where they are filming a Dennis Quade movie
about smart people.

In the Future we will acquire a new picture of WDS. It will not have a
collar, because ``I don't do that'', says AlohaLenscomm.
Discussion about 

The Skinner moves that the next TZ cover not be Banana-colored.
It passes 18-0-0+Spehn.
\emph{Onseck notes that I intend it to be blue. Bananas should not be blue.}


\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Sniffen, Onseck}

\end{document}
