\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 19, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kevin Riggle, Onseck, recording.

Minutes read.

Motion to approve the minutes as inaudible (8-3-1\ps)
Motion to approve the minutes as R-rated for violence (13-5-1\ps)
Motion to approve the minutes as Q-rated (0-4-8\ps)

Matrix vote.  Determinant is 49; all motions pass.

\goto{Committee Reports}

\subsection*{PicnicComm}
We have watermelons, we have coconuts, we will soon have other tasty materials.  (``I would like to
make the point that, since you haven't seen those coconuts, they are Schroedinger's Quantuum 
Coconuts.'')  We also need to rent a car.  Pseudo-Picniccomm reports that there's only a 20% chance
of rain tomorrow.

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

\subsection*{Pseudo-Trojan}
We've received the donation letters for the Cavin, Jacobs, and Dupree donations back from the MIT
financial people, so they're all ready for Kat to mail.

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Malcolm reports that he recently saw a movie which was ``Not rated for reasons of language, 
violence, underage sexuality... and messy apartments.''  Also, the pharoah he thought was named
Snafu may have actually been named Snahfu.  ``Did he get made fun of by all the other pharoahs?''

Motion to pull the old Skinner's brain out of his nose properly so he can become a god fails by
Skinnerial decree.

Motion to pull Jamie's {nose out through his brain} brain out through his nose passes by Skinnerial
decree.

Pandemonium Books and Games continues to be closed.  They're running into bureacratic problems 
with the Cambridge zoning board.  ``The Licensing Committee meetings---if you have nothing else to
do---they can be kind of interesting.''

Usual \&c.

\goto{New Business}

ELECTIONS!

Kate is appointed Vanna for the meeting.

Motion to commend Vanna as the first person to hold that office in several years who can reliably
spell dies because the Skinner refuses to allow a vote during elections.

Onseck: the official candidate is Kat Allen, who was Onseck and Skinner before.  Other candidates 
include a small, carefully manicured topiary; Boba Fett; Kate's feathered hat; the beautiful
invisible peacock in the middle of the table (``No there isn't an invisible peacock there---I can 
see it.''); a 1963 Boeing weapons-grade squirrel retrofitted with Stinger missles; the Road Runner;
Wile E. Coyote; Bullwinkle; the number three; the number one (``I am not a number---I am a luncheon
special!''); and spam, eggs, bacon, and spam sausage and spam spam spam spam spam spam spam spam 
spamspamspamspamspamspamspamspamspamspam spam spam spam spam spam spam spam spam SPAAAAAAM spam 
spam spam spamspamspam....  oops, sorry, the current Onseck got distracted.

Kat Allen is elected Onseck.

LHE: the official candidate is Kate's hat.  Margaret nominates herself, so she can take the money
and abscond to Corning with it.  Other candidates include Nicholas Von Wrench, the high leadership
of Enron, Jimmy Hoffa and Igor, Mr. Potatohead, Libertarian Igor (``We're undead, not 
unpersons!''), a rabbit with nasty pointy teeth (``so we can have something more ferocious than 
Kate''), and Bun-Bun.  (The Onseck tries to make a paper airplane out of his vote and fails.  
``Somebody's not an Aero-Astro major.''  ``Or if they are, there are certain planes I won't be
flying on.'')

The new Onseck walks in.

Kate's hat is elected, and Kate is presumed to be the official spokesperson for the hat.  (``When
you are embezzling, you must wear the hat.'')

The Onseck and zir spouse-to-be play rock-paper-scissors for the position.  Kat wins again.

``As far as I can tell, it is the Vice's job to submit science fiction stories, howl madly, 
order Russian mail-order brides...''  (This comment is not in its original form.  It has been
formatted to fit your screen.)

Vice: Nominations go to Brian Sniffen, Finboard, if they can get themselves a salary; Aramark, if
they can get themselves a salad; Andrew; Yelena; Paige; Margaret; the Instrumentality; Hastur;
SIPB; the Grandmaster of the Assassin's Guild; the Chairman of LSC (who was not nominated but
laminated); the President of APO; Charles Vest; and a number of others better left unmentioned. 

ALC: ``Oh, I just realized... well, I know I won't be Skinner after this meeting.''

Brian wins.

President: Official candidate is Kevin Riggle; other nominations are one unnamed prefrosh; the 
other 999 unnamed prefrosh; the one annoying prefrosh on the mitmit LiveJournal community 
(``There's only one?''); the once-and-future Clough; Jade; Google; 99 bottles of beer on the wall; 
Kat; John F. Carr, maintainer of the 64-bit Solaris OCaml port; TC Skinner; TN Skinner; and 
several others.

Kevin is elected President; clockwork ninja kittens are his second.

\emph{See Brian's e-mail.}

First Miller motion fails, 14-15-1\ps.

Motion to anoint the new Skinner after the meeting with the Holy Banana Oil of Gor passes 28-0-2\ps.
``This will sting a little; be sure to close your eyes.''

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
