\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 10, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, Onseck and Pseudo-Skinner, presiding; Kate Kuznetsova, Pseudo-Onseck, recording.

Minutes read.

Motion to commend Kate, also \emph{last week's} pseudo-onseck, for succeeding at taking minutes in real time. passes 16-0-2+spehn
\goto{Committee Reports}

{bing}
\goto{Old Business}
Matrix Vote:\\
Move to condemn the Skinner for lying about meeting order: 5-9-9+Spehn\\
Move to commend the Skinner for lying about meeting order: 11-3-3+Spehn \\
Move to have a matrix vote: 5-13-1+Spehn\\
Determinant: 1032, all motions pass.

ALGOL

``We have wanking in these meetings? Oh my...''

Move that matrix votes suck:4-2-4+spehn
Motion Chickens.


\bing
``Hm...resonance''
\goto{New Business}

Kevinr is writing a paper on the relation between Westerns and Firefly. Unfortunatly, he is not being paid for it, its for a class.

``I'd like to see frogs eat firefly...''

There is actually a company that publishes essays on the topics like Matrix and Firefly. It has works by Mercedes Lackey, but not Julia Ecklar.

``Sometimes Meaow is just a Meaow.''

``It is a weird planet. They keep gravity on all the time-- even on weekends.''

\bing
\goto{Future Business}
``Did you just confuse a prognasticator with a prostitute?''

V for Vendetta is coming out soon! Yay! It is based on a comic by Alan Moore, who is going nuts because people are murdering his comic...again.

``That's why I don't let them make movies out of my works. They never get it right!''

But is has Hugo Weaving. And it is made by the Wachovskys. Yay. That means that it is going too be good, right?

A long disscussion- erm, slaughter- of the Matrix trilogy evolves into a disscussion of the three laws of Asimov.

``Is the human being going to ignorre its reptile brain? yes/no?''

Onion Newspaper Headline quoted: New Device prevents people from falling into the basement.

People speak of light-tubes. They pass light down into the basement from the top. They use complicated optics and are cheaper than simple glass with reflectors. With mirrors, the sunlight is directed into the optics tube. 

``It is a lot easier if you leave the air in the tube and evacuate the air in the building''

It is concluded that socks are not electrons.

Jamie starts singing the Adjorneyment song.

Move to take the society's fund, go to la Verde's, buy bananas and stuff them into Jamie's mouth: 10-0-2+spehn

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kate Kuznetsova, Pseudo-Onseck}

\end{document}
