\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/14/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July  14, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

A motion to approve the minutes as adequately entertaining fails for
lack of a second.

A motion to have the minutes repeated at the same frequency as the
penguin joke chickens 4-1-5+Spehn

The book is actually ``the rough guide to sci-fi movies''

``Two penguins were floating along an iceberg. One of them said to the
other '

\goto{Committee Reports}

\subsection*{Mobcomm}
We've gotten new books. Again. This is becoming a trend.

(Commentary on whether KR had binged or not is resolved without
binging on JM. He does not make a good noise.)

\subsection*{Onseck}
The Library Store doesn't sell 9.25'' center-slit rolls. This was
confirmed by email after their website failed to sell it to us.
But we will be getting center-slit 9.5'' and 8.5'' rolls.

The Onseck will mail the Neo-Opsis cheque ``today'', for some
definition of ``today'' that may or may not include it actually going
on its way.

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}
People went to Readercon last week. Apparently Friday is the day to
go. Saturday is a long drive, and the panels are very big.

JM notes that we have a note saying ``Copying Receits, back in 5
minutes'', and wonders why the generic ``Back in 5 minutes'' note
wasn't good enough.  BTS observes that, in addition, ``receits'' is
not ``receipts'', and ends up throwing away the sign after JM tries
putting quotes around the word ``receits''.

The status of the Diaspora is waiting for transit and storage
arrangements.

We're also waiting on buffer space, which would happen if we got rid
of the unsorted books.

``You're not allowed to open the NC-17 boxes anyway''-BTS
``Hey! Wait!''

\goto{New Business}
A motion to label Kate as NC-17 fails 4-5-0+Spehn

A motion to acquire booth babes for the Activities Midway fails for
lack of a second.

No one present has researched warehouses yet. BTS will write up a
report for the Skinner over email.
``It will be a 100 page power point document, using proprietary
document formats so Open Office can not open it, with embedded WMFs so 

An Albanian motion on Malcolm fails due to lack of a second and
complaints that KHA is over-sensitive to puns.

``Most Caucasians sunburn at a normal rate, because that's how I
define a normal rate. Kat is especially fair, because the sun shines
and she burns''

Motion to send Jamie to sensitivity training for skin tone
re-education passes 9-0-0+Spehn

``Use of a forward-looking time frame is against the Campus
Sensitivity Policies''

\goto{Future Business}
A retroactive Miller motion gets forgotten about.

A new Dr Who is coming out---not sure if it's a movie or a TV
show. Apparently they have a budget.

In the future, there may be Skinner Rites. Right now there are two
files, both probably incomplete.

In the Past, ``A Scanner Darkly'' came out. KR says it was good.

In The Future, ``Monster House'' will come out. It's claymation
horror, with a house that eats people.

Pirates of the Carribean broke the opening weekend and opening day
records, but not the inflation-adjusted record, which is still held by
Return of the Sith.

The Skinner is terrified that he has forgotten to do something, and so
is micromanaging.

A motion to get the Society a carton of milk to pour on its many
Banana Flakes passes 9-1-2+Spehn

We got a book by Andrew Menard! No, not that one.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
