\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/08/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 8, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

Motion to commend the minutes for being even more convoluted than
usual is seconded...\\
``This is where you vote'' -ALC\\
Motion passes 12-0-3+Spehn

\goto{Committee Reports}
\subsection*{fweekcomm}
Fweekcomm needs help typing up freshman names. Unfortunately, she left
them at her house. Oops.

\subsection*{Pianocomm}
We have another new Prentice! Kelsey!
\subsection{Theftcomm}
We have a new Theftcomm, ALC!
There will be a schedule soon.

\subsection*{Star Chamber}
KR picked up a package---Harper Collins sent us an advance copy of
\emph{Fragile Things} which KR is now reviewing. (Neil Gaiman's new
collection of short stories.)  It is explained that the Skinner is
reading the book still in the box, because otherwise it would've had
to go to Panthercomm and Bluebellcomm before being read.  The Skinner
is All Powerful.

\subsection{Pseudo-LHE}
ALC points out to ESK that she should go to the Treasurer Training.
KHA tells KR that he should go too, in case Kate falls into a black
hole or a problem set or something.

\subsection*{JourComm}
It will be published Real Soon Now---we're thinking October.

Discussion about whether we destroyed HRSFA last spring results in
comments about Dinner not being Destruction.

\goto{Old Business}

The discussion from Committee Reports continues.

\goto{New Business}
 ESK will talk to J about LHE stuff, even though he's old.

We will be removing the not-so-new-anymore books from the New
Books shelf.

KR is turning 21 on Monday!
Rebecca is also getting older on Monday!

\goto{Future Business}
In the future we will die from term\\
In the future we will have a dinner trip!\\
Apparently in the future there will be a Guild game, for which Prentice
Laura is assembling packets.\\
In the future we will send some books to MGH!\\

``It would be really cool if there was a company that bought books for
\$0.25 and then delivered them to hospitals''\\
``This would not make them very much money---that whole buying things
and giving them away thing...''

Motion to form a company to buy excess bananas from LaVerdes and sell
them to hospitals at a loss, frendly-amended to at a profit passes 21-4-2+Spehn


\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
