\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/09/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 9, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

Motion to note the pseudo-Onseck last week was ALC passes 3-4-5+Spehn\\
(yes, really)
Motion to condemn the Onseck fails\\
Motion to amend the minutes to reflect what didn't happen last week passes 12-0-1+Spehn\\

\goto{Committee Reports}

\subsection*{hBarcomm}
The FYSM is due 15 June. We have a plan. 

\subsection*{JourComm}
Jourcomm is accepting submissions! Please? Seriously, we need art and stories. 

\subsection*{Frustrated Authorcomm}
Hates Canada.

\subsection{Sayonaracomm}
MHG gets thrown out of the dorm tomorrow. :-(

Motion to all say how sad passes 9-2-1+Spehn

The Skinner will be gone for the next two meetings, but unlike
Margaret he returns on the 26th. 


\subsection*{Trojan}
The mystery old donation is now only one box---we're not sure why.
A number of our (old) letters have gone out.
A new donation is coming! Hooray!


\subsection*{Star Chamber}
Ed will be dispatched to give the Warehouse a check, unless he doesn't
want to in which case someone else will do it.


\goto{Old Business}
We have an old ex-Skinner and an old ex-LHE here.
\begin{itemize}
\item Michael Taviss '81
\item Carl Hylin '81
\end{itemize}
They say that back in the day they used the ViceGavel---it has burrs,
and the new Gavel is bigger and nicer.
  
Jamie has asked for an invoice for the new Shultz shelves, which will
be scarlet and wheeled and over by the windows in the Circ room, and
some experimental pieces to see if we can boost the rest of the shelves
in the Circ room to 10 high by replacing them with the Auroras.

\subsection{Pseudo-Magdex}
 The dexmistress has mail about the bondagecomm/magdex interface.

\goto{New Business}
Jamie demonstrates that he does know more of the usual motion than the
old people, but they have morphed over the years.

Jamie impresses the alums with his MITSFS-enriched parentage.

KHA is mocked for her Jourcomm coup.  \\
``You didn't get anything?''\\
``She got engaged''- Jamie\\
``I don't think that has any thing to do with it. I didn't get engaged\\
to the old Jourcommm'' -KHA\\
``What, he didn't tell you? If you can't manage to put out a TZ, how
can you put out a child?'' -Jamie\\
``Don't we have some future business to discuss?''

\goto{Future Business}
Much discussion between the alumni about how there are way more women
on campus than there were Back in The Day.

We have a new sophomore keyholder! JH is now a sophomore! 

PP is here, and will be back soon, hooray!

Pandemonium was going to open yesterday!

Motion: Now with 100\% more bananas!  Passes 7-6-0+Spehn

The alums note that the Society hasn't really changed.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen, Onseck}

\end{document}
