\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/31/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 31st, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andrew Clough, President and Skinner, presiding; Kate Kuznetsova, Pseudo-Onseck, recording.

Minutes read.

Motion to condemn the file for being confusing - fails for lack of a second.
Motion to condemn the pseudo-onseck for  using up all of her adrenaline on fear and not saving any for ferocity. Passes: 13-0-2+Spehn

\goto{Committee Reports}

\subsection*{Mortcomm}
Stanislav Lem is dead. He was Polish, famous and wrote lots of stuff. 

\subsection*{Pseudo-mortcomm}
Robert Jordan has contracted a possibly lethal blood desease. For real, this time. Median life expectancy is 5 years

``There is a finite number of puns you can make...once Pierce Anthony exhausts that...''

A disscussion of baths, Forsaken and illustrations follows.

``And all shall cry 'Beware, beware! His flashing eyes, his oily hair! Put some lotion on him thrice...''

The Skinner attempts to depose of Jamie by whacking him with the gravel.

Move to condemn the Skinner for having a personal genre involving women and hammers: Fails by Skinnerial Decree.
Move to commend the Skinner for having a personal genre involving women and hammers: Passes by Skinnerial Decree.


%\*subsection{Onseck}

\subsection*{War Concil}
Not enough people came by during office-hours to move stuff out of the warehouse. Later, people are coming by to move filing cabinets to the Annex in order to have more shelf space.

Jamie argues that this violates the prime principle of having all material available. Skinner admits that it was a hard decision, but continues with it.
 
%\*subsection{FrustratedAuthorComm}

%\*subsection{JourComm}

%\*subsection{Mobcomm}

%\*subsection{Star Chamber}

%\*subsection{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Slinkies are heard.
AR- evil silence- GOL.

``Were they telepaths? Were they emergency food supply?''
``No. They were not alchemists or mailmen or stateworkers. The cats were /just/ cute furry /pets/.''

\goto{New Business}

``We have three new pieces of furniture.''
``Really?''
``No. I jsut wanted to get the meeting on topic.''
``But we were talking about the platipus of doom!''

Move to commend the claim of catastrophe for being a claim of catastrophe: 10-1-4 + Spehn

The Skinner confesses to being a scientologist. The Skinner confesses to being a hallucination. 

``Are you saying that you are an agnostic solipsist?''

We have a Tamora Pierce book. We also have Samurai Pizza Cat.

Slinkies launched at the Pseudo-Onseck. The Pseudo-Onseck is duly scared. 

FrOm here On, all Ps and Os will be caPitalized everywhere because Jamie says it is mOre fun that way.

``I saw an episode about a giant ape that had a two-finger technique for making sushi out of robot monkeys''
``Kinky!''

With lazy vicioussness, the Skinner attacks Jamie for mentioning Kenya.

Motion to end the meeting (\emph{Miller motion. --ed.}) chickens 1-7-7+Spehn. The universe is saved.

``My squirrel which has /no tail just a bloody stump/ returned a few days ago...''

Second motion to end the meeting (\emph{Ditto. --ed.}) passes 8-1-6+Spehn

\goto{Future Business}

\bing
\noindent
Meeting adjourned, Something-pretty-long SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kate Kuznetsova, Pseudo-Onseck}

\end{document}
