\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/30/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 30, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read (from two weeks ago).

A motion to cause the minutes to have actually been last week's
minutes passes 9-0-4+Spehn

\goto{Committee Reports}
\subsection*{JourComm}
Needs a Skinner report

\subsection*{Ass.Comm}
Two Skinners too late, but a minor success was achieved!

``Make it sound like I was being smart'' -JM

\subsection*{Pseudo-hBarcomm}
Will put the summer schedule up for hBarcomm, since she is injured.
\subsection*{hBarcomm}
We are signed up for the Midway, and have officially rejected the
offer to put an (expensive) ad in the Hitchhiker's Guide.

%\subsection*{War Council}
%\subsection*{FrustratedAuthorComm}

\subsection*{Pseudo-Mobcomm}
Serenity Comics can go in SR now, as we have boards and bags for them.
Now there is much less confusion about how to deal with them.

Much discussion ensues about what Panthercomm does, and whether we
want an SR-CX shelfcode or just to put them out.

%\subsection*{Star Chamber}

\goto{Old Business}
The Chamber is back in town, hooray! We should get them all to come to meetings.

A motion to get a blue sticker and put it on the idea of a five-person
``love sack''  passes 10-  ... by Skinnerial decree.

\goto{New Business}
Science Fiction publisher Jim Baen, of Baen Books, passed away this
week.  There are a number of excellent obituaries, including the one
he asked for from David Drake.

Superman is in theatres, and Spiderman 3 has a trailer.

Semi-Alan Poe, a book of completions of an unfinished Edgar Alan Poe
story, has been published. The original piece appears to have been
less than half a page long.

A motion to commend them for making a maximum of hamburger helper with
a minimum of meat passes 7+where's the beef-0-3+Spehn

\emph{The Red Tape War} is a story where Jack Chalker and another
author alternate chapters, attempting to screw the other author over
as much as possible.
The meeting dissolved into several side conversations 

``In the Interest of Preserving Temporal Continuity, Future
Business!''

\goto{Future Business}

\subsection{Future Perfect business} 
The Intel corporation has released a legacy support package for
equipment which has not yet been released, to bring it up to
compatibility with other equipment which has not yet been released and
may be released first.

``I'd like to be more than half an octopus, because then I could be a
whole octopus, and not half of anything'' -Sami

Discussion about rap and hip-hop if they were mystically inclined.

Motion to build a large wall out of bananas to separate the two
conversations in this meeting, and put them in multiple places.

``Excuse me, my mind just exploded.''\\
``Yeah, that happens''

\subsection{Timewarp to Committee Reports}
\subsubsection{Pseudo-warcouncil}
Slocum's student center is still a possibility!  They've been sending
letters to alums, which got BTS' standard form letter explaining that
he will not give money while they don't have

A motion to end the timewarp and return back to future business so we
can have a banana motion and end the meeting passes by Skinnerial
Decree, thus ending the meeting and really surprising the Skinner.
This is the first time we've surprised the Skinner in Some Time!

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}
