\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

A MITSFS Tale 

Friday, January 13, 2006

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

Andrew walked down the hallway towards the MITSFS, glancing at his watch. The time read 5pm.

"Hm, I'm early." he said, staring at the door, which was currently closed- no sign of members or keyholders alike. He fished his MIT card from his pocket and slid it through the reader.

The light on the reader flashed green. He pushed the door open...

And instead of seeing a library, he saw a desert.

A vast, sweeping desert that stretched as far as he could see. A gust of hot, dry wing spat sand at him, and a single tumbleweed rolled lazily by for the sake of dramatic effect.

Andrew glanced around. "Huh... I must have the wrong room or something..." he said slowly, backing away from the door.

It snapped shut of its own accord. Andrew decided that it would just be best if he left.

20 minutes later...

Margaret walked towards the MITSFS, glancing at her watch. She was barely on time, as was typical. She had just spent the past several hours drilling tiny holes in aluminum plates and was slightly dazed. She approached the door, finding it closed, with a single member, Philip, standing outside waiting to be let in.

"Is anyone else here?" she asked.

He shook his head. "No, just me."

Margaret opened the door, taking a moment to officially open the library before letting anyone else in. Fulfilling her duties as LHE, she secretly wired several hundred dollars to her Swiss bank account.

Oh shit. Uh, never mind...

She opened the door again, and let Philip inside. He headed for the circulating room while Margaret logged into the computer. "If no one else shows up there's not gonna be a meeting. I get to make stuff up again in order to convince all the wanker no-shows out there that meetings are cool and they should show up."

A few minutes later, John walked in the door. He set his bookbag down and took a seat at the other desk, where the membership binders live.

"No meeting this week?"

Margaret shook her head. "Probably not."

John leaned forward in his seat, grabbing his bookbag. He pulled on the zipper...

And hundreds of squirrels started to leak out, flooding the library.

"Shit!" Margaret shouted, jumping onto the desk to avoid being swarmed.

Philip came out of the circulating room, holding a stack of Robert Jordan books in his arms, dropping them like stepping stones in order to avoid walking in the squirrels. "What did you guys do?"

"I don't know." John replied. "I had some squirrel cake in my bag..." his voice trailed off. "Damn."

"They're tearing up the books to make nests!" Philip exclaimed. "Even the good books!"

Margaret leaned over the desk. "I'll try reasoning with them. Chickoo chickoo."

A single squirrel poked its head up above the swarm. It was larger than the others, and had an eyepatch for some reason. Probably because it looked more menacing that way.

"Chickoo chickoo." it said.

"Chickoo?"

"Chickoo... chickoo!" It pulled a miniature chainsword from out of nowhere (anime physicsed) and pointed it at Margaret.

"Uh, it says 'No way in bloody hell.' They want the books to build their Unstoppable Superweapon(TM) and they're not leaving until they want to."

"We can call NSR." Philip suggested helpfully as he perched precariously atop a slowly shrinking stack of Robert Jordan books.

"NSR?" John asked.

"Ninja Squirrel Removal."

Margaret picked up the phone. "What's the number? Quick, before they cut the line."

"Area code (666) 666-6666."

"Oh, that's never a good sign..." she said as she punched it in. She raised the handset to her ear. "It's ringing."

"The squirrels are rising..." John said.

One of the ceiling panels above the keyholder desk slid back, and several figures in solid black silently emerged, crawling across the ceiling using their mad Anime Ninja Physics Skillz(TM). They dropped down into the squirrel swarm and drew their swords.

"They're fast, I'll give 'em that." Margaret said.

But instead of using their swords on the squirrel swarm, they all made a dash for John, Margaret and Philip.

"Shit! Everybody run!"

The three members made a scramble for the door, running carefully as possible to avoid stomping the squirrels. As much as they were a nuisance, they were still cute and I'll be saving any tasteless gratuitous violence for later, thank you very much.

"To the basement!" John shouted. "The Ninja can't follow us there!"

They ran to the basement, finding that indeed the Ninja didn't want to follow them there, which is usually a sign that something bigger and far nastier lives nearby. (One might wonder at this point how three average people were able to so easily outrun a horde of trained Ninja, but it wouldn't be a very interesting story if everyone just died in the middle of it, so there.)

"Now what?" Margaret heaved, leaning against the wall for support. "We're trapped down here!"

"No," John replied, shaking his head. "There's a second way out. I just have to remember where it is."

Philip glanced around. "Usually it works like: 'You look around and can't find a damn thing, then you casually lean against the wall and poof! You find the secret lever.'"

John rolled his eyes. "That's just in movies."

"Nuh-uh." Philip said, leaning against the wall and crossing his arms. The sudden weight of a human body against the wall caused something to snap. A panel next to Philip popped open and slid back, revealing a dark, sinister hallway lit by torches.

He pointed at the hallway. "See?"

"Somehow I get the impression that this is about to get a whole lot weirder." John said.

Margaret grinned. "Weirder than wading through a sea of squirrels in order to escape from a pack of bloodthirsty Ninjas?"

"All right, never mind then." He grabbed a nearby torch from its sconce and the three members ventured into the hallway. They all immediately noticed that this wasn't your standard dungeon-type place. There were lots of pipes sticking out of the walls, and a hell of a lot of random Jacob's ladders scattered around. No, this was a Mad Scientist Dungeon(TM).

They entered a large stone room. It was lined with pods, all of which were covered in frost. A dusty plaque near the door read: MIT Cryogenic Research Lab, BLDG W20-0666.

Margaret cautiously approached the nearest one and wiped away a patch of frost with the sleeve of his shirt. "Oh, crap."

John and Philip both turned around. "What?"

She glanced down at the pod. A small plaque affixed to the pod read: "Vergeltungsflotte- Nicht offen- UA ordnung 7936."

"Uh, I found the VGG..."

"Hey!" Philip shouted. "Come here!"

John and Margaret rushed over. Philip pointed to a particular pod. "Look!"

John peered inside. "It's a pirate!"

"All of these pods have pirates in them!" He gestured with his arms at what was at least 2 dozen pods.

"No wonder why the Ninjas didn't want to come down here. Their ultimate enemy is stashed down here... and the VGG for some reason." Margaret said. "Quick, thaw 'em out... but not the VGG. They're probably here for a reason and I suspect that they should stay here. I'm gonna look for weapons."

John and Philip both nodded, hurrying to shut down the cryogenic pods and thaw out the pirates.

A few moments later, a loud crash shook the room. John and Philip both whirled around to see a large section of wall crumble, and a suit of bright blue power armour (ARMOUR SPELLED WITH A U) crash into the room. It was adorned with a bunch of gratuitous skulls and red wax seals, and carried a chainsword that was easily bigger than a man.

"Look what I found!" a familiar and creepily enthusiastic voice shouted from underneath the helmet. "I loves me some Anime Physics!"

"And what do WE get?" John said, tapping one foot against the ground, his arms crossed.

"Philip gets to fight the Ninjas."

"Yay!" he exclaimed.

"And, uh, John gets to take the squirrels home with him."

There was a sudden, loud hiss, the sound of the power being cut. The lights on the cryo-pods flickered and died out.

"The Ninjas found the power grid."

"By now, the first of the pirates were stumbling out of the cryo-pods. "Arr..."

"Hello there." Philip said. "We need you to fight the Ninjas."

"Arr!"

"Huh?"

"Arr!"

"So all you can say is 'Arr?'"

"Arr..."

"Do you want to fight some Ninjas?"

The pirates all nodded. "Arr!"

Something shook the ceiling, stone dust filtered down to the floor. "They're coming!" John shouted. There was a loud, Stukka-like whine in the distance, then another crash. "It sounds like they brought Burma Jets!"

Philip used his powers of Anime Physics(TM) to pull a large pirate sword from out of thin air. "Come on, pirates! Let's kill some Ninjas!"

A loud, collective 'Arr!' rose from the pirate masses and they charged down the hall which would take them back to the student center.

"Me and Philip'll handle the Ninjas, you get the squirrels."

John nodded, producing a large piece of squirrel cake from his own Anime Mallet Space. He ran towards the fight, Margaret stumbling along behind in the power armor.

Outside, the campus literally swarmed with Ninja. Thousands of them, and they had air support for some reason. Burma jets in flight formation screeched by providing strafing fire. They quickly closed in on Margaret, Philip and the pirates as John rushed to collect the squirrels, rolling the squirrel cake along like a giant magnet.

Philip scythed into the advancing Ninja horde. Whirlwind of Death style, cutting a path towards the Charles. Margaret hurled the chainsword into the sky like a spear, catching a Burma jet. It blossomed into a red orange fireball and crashed to Earth, taking out a chunk of the Stata center on its way. (But no one ever noticed the damage, ssssh.)

John staggered up the stairs of the student center back towards the MITSFS. There were no Ninja around. They were too busy fighting Margaret and Philip and had little time for an unarmed guy pushing a giant ball of squirrels (think Katamari Damacy). He rolled the ever-enlarging ball into the library. The squirrels had constructed what looked like some kind of large laser weapon out of paper and had it pointed out the window. John, ignoring his common sense for the sake of humor, flicked the power switch...

FREEM.

Now, for a brief moment of clarification: the squirrels had set out to create a weapon capable of controlling the weather with the intent of making it Fall for the entire year, thus heavily increasing the output of tree nuts. (They didn't realize that MIT already had one of these and it sat atop the Green Building, cleverly disguised as a doppler ball. They also didn't realize that this plan was stupid and pointless, but hey, they're squirrels. Who else would try and make a weapons grade laser out of paper?) What they actually created was the world's first lightsaber, only a lot bigger. It shot out a giant beam of red (bad guys have red lightsabers, remember?) light which suddenly terminated in a physics-defying sort of way about fifty feet out, ending in a weird crescent-shape.

It kind of looked like a giant wrench.

John carefully grabbed the squirrel-sized controls and tried to scythe the laser down onto the Ninja horde. It crashed down onto a metal construction cover and went BING!

The giant ball of squirrels vanished. The Ninjas vanished, the Burma jets vanished, and the paper wrenchsaber vanished.

"Aww... I wanted to keep the squirrels..." he said.

A few minutes later, Philip and Margaret appeared in the doorway. They closed the door behind them, just in case there were any extra Ninja lurking in the Tech office or something.

"I was fighting Ninjas!" Philip grumbled. "Ninjas!"

"I had terminator armour!" Margaret whined. "And an Eviscerator! An Eviscerator!"

"And I had a giant ball of squirrels." John replied. "Stop complaining."

She sat down. "Kinda weird. I never actually started the meeting with a bing, so I wonder why everything went away."

John shrugged.

There was a collective murmur out in the hall. It sounded like a bunch of people talking in German. Someone knocked on the door.

"Why do I have a bad feeling about this?" Philip mumbled. 

Margaret slowly rose to her feet and cautiously opened the door.

A large group of creepy-looking uniformed and heavily armed men stood outside, each sporting his own Menacing Facial Scar(TM). They all wore matching helmets with a symbol on the front that looked like the Great Seal, only it was clutching a bomb and a sniper rifle instead of the standard arrows and olive branch.

"Uh, guys? It's the VGG..."

"Guten Abend, Fraulein," their apparent leader said, clicking his boots together. "Vergeltungsflotte Special Force, division of ze MITSFS, imprisoned by ze UA in a bid for power back in ze Eighties."

The last time we got library space... Margaret thought. "Why the accent?"

"Zis vay is more intimidating, ja?"

"Oh," Margaret hesitated. "Hold on a second." She held up a finger.

"Jawhol."

"They must have thawed when the Ninjas cut the power." John said.

"What do we do?" Philip asked.

"They don't appear to be hostile..."

"Uh," Margaret scratched her head through her hat. "I guess we have our own Unholy Army of the Night(TM) now."

"What do we do with it?"

Margaret shrugged, glancing at the VGG. "So, have you guys ever considered running for the UA senate?"

\end{document}
