\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/15/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 15, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Andrew Clough, Psuedo-Onseck, recording.

Minutes read.

Motion:  Commend as being a sorta, kinda, almost reading of the minutes.  Passes 2-3-5+Spehn.
\goto{Committee Reports}

\subsection{hBarComm}

We have new TShirts.  Buy two, they're cheap!  

%\subsection*{Onseck}

\subsection*{Psuedo-War Council}

MIT just approved a lot of new building.

ESK:  If they didn't build the new Media Lab expansion, Senior House could have a pool!

The Skinner says there will be a new mailing list, according to the
Tech, that will tell people about things happening on campus.
 
ESK:There is an Athena-inept mailing list, onto which people get put who
don't know how to use Blanche

\textbf{The Real Onseck surreptitiously takes over}

\subsection*{Theftcomm}
Yay, the new TIF is all shiny.

\subsection*{JourComm}
Real Soon Now! After Jourcomm gets married.

Discussion about 

\subsection*{Star Chamber}
21W.769, which the Skinner is taking, has its books on reserve in the
Library. He shall be telling the class about it soon, so they might
come and visit.

\subsection{Pseudo-LHE}
The real LHE will take treasurer training.

\goto{Old Business}
``Stuff happened, a long time ago... and now it's now.''-KR

The former-planet formerly-named Xena is now called Eris (The Roman
Goddess of Discord) because there was so much discord over the status.
Pluto is an improper, dwarf, EVIL pseudoplanet.

\goto{New Business}
``What about the Usual Debate?'' -several society members in chorus \\
``Too Late!'' -Skinner

There are less new books than there once were. But there will probably
be more soon (maybe in October) when we get more Amazon boxes.

Discussion about how to feed Panthercomm donations results in them not
being sandwiches.

KR does not like Fragile things as much as he liked Smoke \&
Mirrors. He says ``It's a very varied collection---you go from
Sherlock Holmes meets Lovecraft, to a poem, to a sort of weird take on
the Narnia books'' 

ALC says Josh Wheedon is taking over a comic book series called
Orphans. ``I've heard from people who don't really like comics that
it's really good.''  

Scott McCloud talked in the CMS department yesterday, and apparently
said interesting things. There may be a video podcast of it.

\goto{Future Business}
In the future we'll go to dinner.

In the future, we will have heard the jokes from the JokeMaster2000. A
member bought it at a yard sale.  It tells bad jokes, and if nobody
laughs it will supply the laugh track.

In the future, a movie called ``The Science of Sleep'' will open. It
appears to be about a character who can not distinguish reality from
his dreams.

Andi wants to know if there are pubs or bars that might show
BattleStar Gallactica's season opener.  Much discussion ensues about
whether the TIVO widget that lets  you watch TV from anywhere via the
Internet.

ALD motions that we determine a way to send things over the TV, like
Willy Wonka---blueberries, bananas, chocolate.
After some confusion, passes by Skinnerial Decree.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Allen, Onseck}

\end{document}

% LocalWords:  hBarComm TShirts ESK athhna Theftcomm Yay
