\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 15, 2006

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Pseudo-Onseck, recording.

Minutes read.

A Miller Motion fails 13-16-0+Spehn.

Motions about commending the Pseudo-Onseck and general relativity fail for lack of seconds.

\goto{Committee Reports}

\subsection*{PseudoVGG}
A member came in, all apologetic about a fine she owed. She wasn't in any of the books, so JFC couldn't take her money.

Why is there a jacket in the book drop? ``It's a book jacket!''

\subsection*{LHE}
The Metro Warehouse guys no longer want to kill us because we gave them money. On the other hand, those other guys still haven't done the thing.

Kate no longer trusts anything associated with anyone if it involves our money.

\subsection*{PseudoTrojan}
The Joblove donation got processed, yayfor. Moldy books got terminated with extreme prejudice.

The Sherwood donation did not get processed.

\subsection*{UnknownUnknownsComm}
The magazine inventory has reached a halfway point. Hopefully we can get a large team to finish it over IAP.

Mutterings about killing The Tech ensue.

\subsection*{Kvetchcomm}
There are three more reviews up on Kvetchcomm - ``mad props to Christian and Sukrit''.

Stealth Planet is possibly the worst book that JSB has ever read. The author committed many many sins in the writing of this book, which is why the review is so long.

Kvetchcomm solicits more reviews from anyone who wants to contribute.

The purpose of the list tz-reviewers is to request reviews from people.

We should set up an RSS feed for MITSFS reviews.

When you don't sleep during any of the days of the week, it gets longer.

\subsection*{PseudoJourcomm}
We're blocking on four pieces of art (where we were last week, and two weeks ago). 

\subsection*{PseudoAnalogcomm}
There's now an envelope up, just in case you don't do that crazy electronic mail thing. Or you could get up on the desk and start tap-dancing.

\subsection*{Theftcomm}
Christmas and New Year's have been removed from the online schedule, and the tiff got updated.

\subsection*{Star Chamber}
We Got More Books! We got the fifth volume of ``Girl Genius'', but we don't have the previous four novels.



%\subsection*{Onseck}

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

The problem with the Honor Harrington calendar has (supposedly) been dealt with.

Many people will be not here.

Motion to wish Rebecca Bon Voyage passes 8-0-1+Spehn. If Cthulhu eats the ship, that would be bad.

ALGOL.

\goto{New Business}

I debated before you debated!

We have a new magazine filing thingy! It contains ``all the news that's easy to gather.'' Q. How many different permutations of the shelves in the library are there? A. It depends on whether you have a hammer.

We got a donation of a Greenberg anthology thing.

There will be a Harry Dresden RPG coming out, as well as a Firefly MMORPG.

JSB has created the remaining four pieces of art for TZ! The pseudo-Onseck would report on what they were, but he was laughing too hard. Suffice it to say that they involve Stealth Planet.

Dave has an engineer for us. He doesn't know he's volunteered yet, but he will understand in due course. Discussion about library fire protection ensues. We could light someone on fire and use that to check whether the extinguisher works. There's an NFPA standard for setting people on fire. 

``I've read a lot of books this week.'' - CJT

Motion to commend Christian for becoming literate passes 15-1-1+Spehn.

Motion to condemn Christian for not removing the staple in the middle of the sentence passes 7-2-4+Spehn.

\goto{Future Business}

In the future, there will be more new business!

In the future, we will have more reviews!

In the future, there will be finals; some people will pass them. People should review the finals. ``This sucked. The professor has obviously never heard of 'show, don't tell.''' - KR.

In the future, Rebecca will pack before she moves.

In the future, Sami will be writing an Intercon game. She will also become a prentice, and do the really grungy work that even the other prentices won't do.

A Miller Motion was Miller Seconded, Miller Debated, and passes by Miller Skinnerial Decree. It's Miller Time. 

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Sniffen, Onseck}

\end{document}
