\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 26, 1968

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Meeting was called to order at 5:00 p.m. SST.

The Onseck being AWOL, the minutes of the previous meeting were not read.

Libcomm reported receiving donations of books in lieu of fines from evil overduers. 11 dollars in fines were also collected.

Cochran reported receipt of a letter addressed to Filthy from a captain in the USAF, who was under the impression that Pierre was in a position of responsibility; i.e., president of MITSFS. He is writing a thesis on the modern need to escape reality, and wants to survey some SF writers, to wit: Forest J. Ackerman; Brian Aldiss; Isaac Asimov; J.G. Ballard; Anthony Boucher; Ray Bradbury; L. Sprague de Camp; John Carnell; Arthur C. Clarke; Bruce Eliott; Langdon Jones; Damon Knight; David Masson; Michael Moorcock; Clifford D. Simak; Theodore Sturgeon; Dan Thomas; James Thurber; Van Vogt; Roger Zelazny. Don is replying in a suitable manner.

Minicult, Phillies- MIT has obtained 4 Inertial guidance systems from Atlas Missiles; Seitz wants one.

Minicult, Phillies- Forms have been received for, among other things, the financial request of our organization.

Minicult- The lawyer who had requested information on the story "John Jones' Dollar" has written back with comments on some of the numerous holes. Phillies and Cochran will split the 45-cent check he included for expenses.

Moocomm- Loeb refuses to have anything ever to do with Batmen of Africa. Dan Wiener has written a letter to Republic Films. It will be sent as soon as an address is found for it.

Seitz displayed maps of mica and beryl mines. The Government paid 90 percent of the exploration costs for the mines, 4.3 megabucks, which ultimately produced several pounds of beryl.

Minicult- A letter arrived at the library addressed to "One plus Spehn."

Theftcomm- The Lord High Embezzler has bought a new motorcycle.

Minicult, Phillies- The National Review, commenting on computers, pointed out that embezzlement night be even easier, perhaps by bribing programmers. Phillies also received a computerized notice from NR of his 2-months overdue bill which he had long since paid.

Jourcomm- Twilight Zine will be typed tonight. Everyone is automatically pressganged.

Cornelia Otis- 408 Entropies at the meeting 2 weeks ago. WCRB distributed such stickers as Repeal Ohms Law and Prevent Tooth Decay- Fluoridate Gin.

The creation of a new motion was suggested, to be named the 'Joe Ross Motion'- Out The Window.

Minicult- Today was an international strike day. Attendance at classes rose noticeably.

Pic(k)nicomm- Joe Ross has promised to stay away. There was dissension over what kind of meat to bring, so the Skinner compromised on 6 lbs. roast beef & 2 lbs. ham. The Skinner was subsequently unable to stem the wave of anxiety over his sudden democratic tendency. 50 pieces of chicken will also be brought. Seitz suggested 6 pair of croddle grapes and 12 lbs. blog. Several packages of scrumptious Salada products were donated by non-existent non-entities. Seitz can get 10 metric tons of dry ice to cool the drinks. Letvin and Minsky will be invited, plus Bova if he can be found.

It was moved and seconded to censure the Skinner for allowing democracy to rule. Passed 5-0-3 +Spehn, although the Skinner tried to repent by counting it 0-18-0 +Spehn. This was deemed insufficient by the Vice. To repent, Phillies must stand in the snow outside the Student Center during the month of June and supply his own snow.

Minicult- Bob Wiener reported that Burton now has G rifle teams, of which he has just been made a member of the G team. The G team beat the A team. The U.S. Army will be duly notified.

Miller motion failed 5-4-7 +Spehn. Miller motion passed 8-1-2 +Spehn. Adjourned 5:53 p.m.

\vspace{12pt}

\centerline{Reverently submitted,}
\centerline{Daniel Wiener, Onseck}

\end{document}