\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, January 26, 1968

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Wiener acts as Skinner.

No minutes.

M: minutes be accorded as not read.

M: amend, not blue.

M: amend seconded, thirded, and quartered.

Passed by fiat (1967).

Libcomm: Library in same place.

Treasurer's Report: Money taken in. No candy, 2 1/2 memberships taken. Thinking about spending money buying mags.

Pseudo-Libcomm (Wiener): Sheldon will see about reserving 26-100.

Old Business:

Move to censure treasurer. (Unheard.)

M: Make painting officer.

M: Make painting commissioned officer.

Point of info: who is treasurer?

Minicult: 500 Caltechs marched on NBC over Star Trek drop.

Something picketed tonight.

Point of info: against law vilifying ex-sponsors of Star Trek?

No Spock stickers, as Dr. Spock has same name.

Dr. Spock's head is pointed.

On buttons, omega=resistance, L=inductance.

LIHSPT

6 wants key.

Space war is illegal. Different varieties. Laser? Angular momentum Keller sum.

4: Miller motion.

2: "You don't look Scottish."

4: "I'm not."

4: "I have a motion."

Send Captain America, F.F., and Submariner to get the Hulk out of Korea.

3 tries to discuss SF.

Miller motion.

6: What's a Miller motion?

2: Move to amend constitution. Only Miller can make Miller motion.

3: Move to feed the plant bananas. 3-2-2 +Spehn.

\vspace{12pt}

\centerline{David S. Cunningham, Onseck}

\end{document}