\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, January 5, 1968

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Meeting called to order at 5 P.M. MITSFS time.

Libcomm report: Analog arrived 1 day after appearance on newsstands. Hardbacks have been numbered with numbers of copies.

Minicult: Stalactites and stalagmites growing in some subway station.

Treasurer's report: savings account will be moved from Cambridgeport to MIT, checking account from Harvard Trust to Charlesbank Trust.

Chairman: volunteer to arrange for printing new membership cards.

Minicult report: Asbury Park evening news: review on Judith Merrill's "Best of SF."

We have endeavored to bring culture to MIT. Memberships are for sale for 25 cents in the National Committee to Horsewhip Drew Pearson.

Seitz- presented aluminum hull- dented by gavel- (Concorde)

Motion to sandwich Onseck between the Techs.

Seldin- does entertainment of motion include dancing girls?

Amendment (Y)- that motion include girls.

Amendment (Cochran)- dancing purple elephants. 10-5-5.8 +Spehn.

Minicult- the Tech- TSE story.

Minicult (Y)- computer analysis of Odyssey- 6 persons, etc., etc. (ancient anecdote)

Jerkcomm: TZ marches on but no (sic) cover- needs intersession to come out.

Picocult: Scientific American feud- largest plane entry only flew 2 times length.

Libcomm: Feb issues are in- reserve books locked up. (Add Lib, Seldin guilts.)

Libcomm (Phillies): Key cards useless- no keys!

OBAlgol.

Motion to censure treasurer. Infinity-3-6 +Spehn.

Minicult (Y): Mark Twain- meetings with two living gods (left and right god).

Wanted, Jourcomm- volunteers.

Motion that Seldin does not exist. 13.8-1 (not Seldin)-1 +Spehn.

Moocomm: can get Fahrenheit 451.

Query- old Star Treks- money is all you need.

Motion that Seldin plan non-existent. 2-10-8 +Spehn.

Query- money from Finboard- no news.

New Business:

Motion that creation of Seldin is anti-Frank motion.

Amendment (Cochran)- that debt be divided among Seldin.

Amendment- to dissolve Seldin in Universal Solvent.

Amendment- to recover debt by fractional crystallization.

Amendment- to get 100 copies of Almagest from Setty (if we provide container).

Universe to be used as container, and throw in a banana.

Y: few words on great state of California.

Adjourned 5:45 PM.

\vspace{12pt}

\centerline{Introspectively submitted,}
\centerline{David S. Cunningham, Act. Onseck}

\end{document}