\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 15, 1968

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
5:10 PM. Minutes OK.

Libcomm: Fantastic, Mage's Books, Wiener to censure Pres & Lib out of, A. Asimov on J. Carson, Easter location argued.

LHE seeks out 108 dollars.

Moocomm- coup- new order has taken over. Movie 7:30, box stuffings <10 dollars.

Boskone 25 percent.

More garbage on J or Asimov.

8.732 R course.

MIT Microrep spazzed again- put on wrong number of microfiches.

OBA, Mc Treas unanimous.

Motion to add E.S. owes us 27 plus-or-minus epsilon dollars, epsilon need not be small. Amend: make him pay in gold. 9-1-2.2 +Spehn, passes.

Move to make a motion. 6.3-1.07-3.03 +Spehn.

Phillies: NM. 2500 Dem votes for Nixon. Pres Johnson- 1700 Rep votes. This is political insanity.

M: 1805 optics book- first man to put hand into solar oven.

Guy stood in forces. Strange thing about them- they keep going if they aren't.

Van der Graff derailor.

4:00 10-250, Dean Brown in a draft.

Louisville's 2S -> 2A.

Draft discussed. M to censure Sizer. 3.28-3-2.29 +Spehn.

Space war is great.

Phillies: Move to adjourn. 3 +Pres-3-3 +Skinner +Spehn. Motion chickens.

To New Business.

M: Shove banana down the-

Motion acceleration. I don't accept that a fourth can't be seconded- only fifthed.

Society is unanimously in favor of the Fifth- of [illegible].

Move to go in favor of the Staralgol. 2-2-5 +Spehn.

M to censure treas again. 5 effect-5 eyes-1 +Spehn.

Miller. 4-4-5 +Spehn.

M to curse Pres & Lib. 5-5-5 +Spehn.

M to curse 3 + the treasurer. 7-1-2 +Spehn.

Miller. 4-5.3-4 +Spehn.

Miller. 3-6-3.8 +Spehn.

Phillies: Banana. 6.2-4-5 +Spehn.

\vspace{12pt}

\centerline{David S. Cunningham, Onseck}

\end{document}