\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 22, 1968

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The Lord High Embezzler called the meeting to order at
5:00 P.M., Society Time. The real world was ten minutes fast.

The nonexistent minutes from the previous meeting were accepted as not read.

The treasurer has 15 dollars in his pocket, taken out of the drawer. The rest of the treasury is claimed to be in good hands. The treasurer did not specify which Latin American nation the good hands are presently located in.

Pseudo-Libcomm: About twenty more volumes have been wrapped to be bound.

Old Business Algol: Moved to censure the treasurer. Ignored.

More pseudo-Libcomm: Four comic books have been donated.

Minicult: Harold Stassen offered to withdraw his candidacy for President if LBJ will change his VietNam policies. (When LBJ heard the news, he burped.)

Senator Dirkson has been assigned a walk-on role in a science-fiction movie.

Isaac Asimov thinks Nixon will be the next President. He says that the only good thing about it is that he will beat Johnson.

Mad Magazine has done a parody on the "Invaders," in which Vincent asks the President to get the people to believe his story, and Johnson says, "Ah'd like to help yuh, but I can't even get the people to believe mah stories."

Miller, 2-3-1 +Spehn.

Miller, 2-0-1 +Spehn, approx. 5:30 P.M.

\vspace{12pt}

\centerline{David S. Cunningham, Onseck}

\end{document}