\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 13, 1968

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Minutes accepted.

Phillies talked about noble gases as anesthetics.

Proxy entered in minutes.

Moocomm: We need coolers- movie A Man and A Woman.

Treasurer: 1000 from Finboard.

Libcomm: VooDoo have been added to library.

Theftcomm: Swanson was appointed.

Seitz offered 3 1/2 hours of uninterrupted commercials.

Swanson was separated from gun and matches.

CDC and IBM have been commended for patriotic action, accusing each other of monopolistic practices. 9-0-10 +Spehn.

Minicult (Phillies): I saw a polite Boston cab driver. He was polite to an army truck with an anti-tank gun.

Miller- forgotten.

Minicult (Swanson)- randomness.

Minicult (Seitz)- Jan 15- anniversary of great molasses flood. Suggest national [illegible] week.

Miller (unseconded).

Motion to censor Mr. Swanson- amended to defenestrate in a suitable science fictional manner. 13-12-8 +Spehn.

Miller- 8-5-9 +Spehn.

Banana- ignored.

Minicult (Wiener)- we have fewer members.

Miller- forgotten.

Banana- 17-3-3 +Spehn.

\vspace{12pt}

\centerline{Dan Wiener, Onseck}

\end{document}