\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, February 12, 2009}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion ``DOOOOOOOOOOM!'' passes: 11-2-3 \ps

\bing

\goto{Committee Reports}

\subsection*{Catacomm}

Catacomm processed many boxes of magazines out of the library in honor of 
Boskone.

20 back issues of NYRSF are on their way here!

\subsection*{Rearranging Deck Chairs on the Titaniccomm}

Bookshelves were built and file cabinets moved next to the computer desk for
maximum shelving.  More changes to come; tune in next week!

\subsection*{Niagaracomm}

We're selling magazines at Boskone this weekend.  You should go and help out!

\subsection*{LHE}

Backlog done!

\subsection*{Libcomm}

Real soon now.

\goto{Old Business}

Old things are old.  And current.

Dun-dun-dun-DUN.  In the past there was the sound of drums.

ALGOL.

\goto{New Business}

OH!  I GET IT!

2012 ring premiere is tonight, but the design was leaked a week ago.

Boskone!  For the love of God, Monstressor!

\goto{Future Business}

In the future, we will have version control in which branches don't hurt.

In the future, we will have an online Pinkdex written by someone who didn't 
graduate 20 years ago which will use something more advanced than grep.

We all get distracted by a photographer who comes into the meeting.  He's stealing our souuuuuls!  Noo!  Oh wait, the Institute or the gavel keeps them safe, never mind.  Okay then, we have a new pet poitraiteur.  Wheee.

Motion to come up with a science quiddity about bananas and then take a picture of it: ``oh I already forgot''-2-2 \ps *click*

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
