\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 17 September 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

PW: Motion to commend a prentice for actually being at the meeting
and taking minutes passes by Skinnerial decree.

James: Fun.

(He had to go home and do stuff, so he missed last meeting.  And
home is a train-ride away.)

\bing

\goto{Committee Reports}

\subsection*{pseudoSeldon}

Seldon showing tonight at nine pm in 8-119.

\subsection*{Skinner}

SAPPHO has changed how we submit reimbursement requests, so we
need to deal with this.

Also, Skinner is trying to get the boxes out of the library.

\subsection*{hBarcomm}

We have a poster in the Infinite.  (Explanation that hBarcomm is
recruitment and publicity.)

\subsection*{Trojan}

We've been getting two donations a week, and so Trojan is so busy with
negotiating that she needs to have a Trojan party to process them.

\subsection*{Bluebellcomm}

Bluebellcomm needs to do work!

\goto{Old Business}

Writer E. C. Tubb died last Friday at age 90.
We have a bunch of books by him.  He wrote the Dumarest Saga.

KKB: Miller motion! fails 8-0-0\ps.

KKB: Miller motion! passes 9-2-5\ps.

\goto{New Business}

\goto{Future Business}

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
