\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, April 16, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to have a guest log: 8-4-4 \ps ``but we're not doing it'' sayeth the 
Skinner.

\bing

\goto{Committee Reports}

\subsection*{Magnificent Iron Titanium and Steel Fist of the Schism}

We will definitely not be attacking the Hoity-Toity Robotics Scientific
Fellows and Associates company (HRSFA) this Sunday at 6 PM.  We have definitely
not been in construction of a new and devastating top-secret weapon.

Nope.

\subsection*{Theftcomm}

Look!  We have a new TIF!

\subsection*{Picniccomm}

Elections are Friday, May 7th, and a picnic the following day.

\goto{Old Business}

KR delivered DVDs to NESFA on Sunday.  Yaaay!

There were prefrosh at CPW.

Usual total fail to accomplish ALGOL.

\goto{New Business}

\textbf{SPACE PIRATES!}

KCR: ``Yes, but one is regretfully forced to conclude that one CAN have too 
many books.''

Avatar is showing tonight at LSC.  There was a lot of ground-breaking technology
in the production of the movie, such as replicating the way in which the human
eye will focus in 3D scenes.

\goto{Future Business}

In the future, there will be a Concert Choir concert.

Also elections and a picnic!

Motion to get ALC some banana cuttings to take to the Marshall Islands: 11-0-2 
\ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
