\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, March 5, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes for their grog-infused nature YAR!: 8-6-6\ps

\bing

\goto{Committee Reports}

\subsection*{hBarcomm}

We made a new ad for the Tech to be printed during CPW.  Keyholders should take a look and send comments.

\subsection*{Pain of Spacecomm}

David made copies of the DVDs, but we do not have them.  Yet.

\subsection*{Amazoniancomm}

PP is now in Seattle, but dekeyed.  Wah.

Motion to delegate PP for the Committee for Exceptionally Experimental for Representing the Library in Less Space: 10-0-6 \ps

\subsection*{Bluebellcomm}

Prentice did Bluebellcomm.  Whee.

\subsection*{Theftcomm}

Theftcomm, caught in its recent transgression by the wary eye of the Star Chamber, has given back the hours it stole from DWR and JAJ, but has mysteriously stolen BTS off of the TIF entirely!

\subsection*{Musiccomm}

Concert Choir nommed another keyholder.  Yay, graduation requirements.

\goto{Old Business}

KCR: ``Hello, acute failure to care.''

BTS: ``Motion for immoral business.''

KR: ``That doesn't follow...''

\goto{New Business}

Alice in Wonderland (the movie) is coming out today.

Giving someone (even a police officer in execution of his duty) the middle finger is now a recognized and protected right under the First Amendment.  God Bless America.

Pandemonium Books is in the process of a legal hostile takeover (of one owner buying out the other) and closing the store.

Someone is trying to get the Supreme Court to apply the Second Amendment against the states (much like the First, Fourth, and Fifth are).  Heinlein would think this is \textit{awesome}.

Computer wankery ensues.

KCR: ``Mice are \textit{so} last century.''

Motion to remove from the library all books implying the existence of multiple OS platforms, as they are not science fiction but merely alternate history: withdrawn by more computer wankery.

Patrick Rothfuss has written a children's book!  The Adventures of the Princess and Mr. Wiffle.  This has nothing to do with The Name of the Wind, but it has pictures!

Time-warp to the Stone Age.

Motion to chocolate-dip the next person to go bananas to that extent: 15-0-9 \ps

\goto{Future Business}

We have no Future.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
