\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{kkb (KKB), LHE and PseudoSkinner}
\newcommand{\onseck}{kaduk (BJK), PseudoOnseck}
\newcommand{\meetingdate}{Friday, 26 November 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

Motion to commend the reader of the minutes for his brilliant work
and award him one banana for his troubles.

Passes by PseudoSkinnerial decree.

\goto{Committee Reports}

\goto{Old Business}

\goto{New Business}

\goto{Future Business}

Hi, I'm Steve Cass, Special Products Editor at Technology Review.
In the next year, we're looking to be commissioning some hard SF
stories; we already have a pet list of writers we'd like to get, as
the Editor-In-Chief and some of the other editors are sci-fi people,
but we hope to include in our considerations some more unknown authors.
Accordingly, we invite you all to submit short story writers (not
novelists) who you've come across who might be interested in getting
a big wad of cash.  We would be paying in the ballpark of non-fiction
rates for science fiction, which is an order of magnitude larger than
the \$0.06/word that Asimov's pays.  If you have any suggestions for
hard sci-fi writers who you would like to see a story commissioned
from, we encourage you to submit them to our consideration.

Michael: I can only come up with one off the top of my head,
Matthew Jarpe, who wrote {\em Radio Freefall}.

SC: We're looking for people on an axis that would include Greg Egan
through Vernor Vinge.

BJK: How shall we get names to you?

SC: I was planning to leave my card and you can put my email address
in the minutes.\\
{\em PsOnseck. Stephen is stephen DOT cass AT technologyreview DOT com.}

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
