\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Susan Shepherd, Onseck}
\newcommand{\meetingdate}{Friday, January 8, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the Onseck for wearing a scarf that makes her look more than usual like a Girl Scout passes 11-0-1\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudoKatiecomm}
Although not all of the Cox donation has been processed so far, several more bags from it have been dealt with and recategorized as ``Panthercomm's Problem.''

\subsection*{pseudoBoxerRebellioncomm}
Requests help in carrying boxes of books out to the car so that they may be further taken

\subsection*{Smilescomm, per request of Libcomm}
We are unbleeping the LPs, getting fewer books stacked or shelved in such a way as might injure their spines.

\subsection*{Pianocomm}
The MITSFS has a new prentice, Alcor. Yaaaay!

\subsection*{Libcomm}
There is a new shelfcode, R/H, for Reserve Hardcover. It's for all the SFWA books that we had only a single copy of, and really old old old old also old hardcover books like the Swifties.

The SFWA shelfcode will be folded into Hasslecomm. All in all, this nets us five shelf faces, which is awesome.

\subsection*{StarChamber for Hasslecomm}
There will be a Hasslecomming party next weekend; talk to Hasslecomm for details. You should come and help.

\subsection*{Libcomm}
Inventory is tomorrow.

\subsection*{Seldon}
There will be games tomorrow in building 56. It will be fun, you should come.

\goto{Old Business}

We got the first batch of scans back from the scanning place. They're good.

Motion to commend Kevin for getting the project all the way to this point passes 22-1-3\ps.

A note of coolness (coolnity?): we have a former Skinner in here! Well, technically we have multiple of them, but in this case it's a more former Skinner than many.

Avatar came out. Some discussion follows of the various confusing movie titles, including ``Avatar'' and ``The Last Airbender,'' as well as ``9,'' ``Nine,'' and ``The Nine.'' 

``The Collect Call of Cthulhu'' has been suggested as a candidate for a Seldon showing.

Margaret's mother has recently asked her whether Locke Lamora was trying to get into the network. The short answer was yes, but it turned out all right in the end.

Usual motion. Usual vote. Usual second. Usual result. ``Usual Cthulhu?'' The Skinner: ``No.'' ``Usual Hastor?'' ``No.''

\goto{New Business}

Negotiations involving robot assassins, Sukrit's brain, space considerations, Russian software and ``Hey, that looks like my house!'' ensues. So, really, we just need to get cupcakes to prevent the drones from allowing themselves to be hijacked, which passes 14-3-2\ps.

Joe Haldeman has a new book out, Starbound, the sequel to Marsbound.

Motion to appoint a commitee to count Jake's books and our Twilight reviews in case they have been stolen by Locke Lamora or Margaret's mother; these would be classified under the WRD shelf code along with the science fiction calendar, the science fiction encyclopedia, the circulating banana and the Book of Science Fiction and Rocks, (pause for breath) FAILS for lack of a second.

Motion to ``Banana'' fails alpha-beta-gamma\ps.

Discussion of odd name possibilities for the Skinner's family -- Manta Ray, Alpha Ray, Beta Ray, Death Ray, Freeze Ray -- and the Alpha-Beta-Gamma paper ensues.

Singing ensues.

\goto{Future Business}

The Onseck will be leaving for home soon, so we will be in need of a new Onseck this upcoming semester.

Motion to get Amol something else to eat, for example a banana, votes are 13-9-6\ps.
Motion to commend the Onseck for awesomeness, votes are 32-1-5\ps.
Motion that the books should not come and eat us, votes are 19-12-13\ps.
The determinant is -1205 and all motions fail. There is a collective ``Awwwwww'' from the audience.

The Skinner uses her godly powers to alter the results of the last two votes, in order to commend the Onseck and avoid having keyholders eaten by the books -- we need them for Inventory, dangit! *vehement fist*

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
