\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kendra Beckler, LHE and pseudoSkinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 17 December 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Eh. 2-1-4\ps

Motion to commend the creators of the time-warp for making it end
before it starts. 8-0-0\ps

Bah. 2-1-3\ps

And the determinant is 16 and all motions PASS!

\bing

\goto{Committee Reports}

\subsection*{pseudoPianocomm}

Due to popular demand from Kaleb there should be prentice work this weekend,
how about 14:00 tomorrow?  It will probably wrap up in time for Patrol.

\subsection*{Onseck and pseudoThunderbunny}

We are working on inviting two different people to give talks at the 
library!

\subsection*{Star Chamber}

PW and KKB purged the Star Chamber shelf!

\goto{Old Business}

In the past there were finals.

In the past, the Onseck was told not to put random wanking in the minutes.

Dinosaurs are very old business.

Edicaran fauna is even older business.

The last time George R. R. Martin published a book is possibly even older
business.

Motion to overcome stairs PASSES 6-2-1\ps.  E-LE-VATE!

ALGOL

\goto{New Business}

In the present there is an overness of finals.

In the present there is a phone call.

Motion to elaborate PASSES 4-1-3\ps.

Motion towards the prentice with the gavel by the pseudoSkinner PASSES by
pseudoSkinnerial decree.

In the present, we have a U-Mass Amherst student who is doing an internship
here.

Actual motion that might have some actual bearing at some point in the
future PASSES by Skinnerial decree.

Motion to not make a Miller Motion CHICKENS 3-1-7\ps.

\goto{Future Business}

In the future there will be IAP.  In the future there is Christmas.

In the future KKB will be running a 10-day.  In the future PW will
be running a 10-day.  These are not the same 10-day.

It is explained that Boskone is run by REDACTED ORGANIZATION,
which is a spin-off group of MITSFS that ran away to Albania.

Motion to speculate that the speculation on speculation should end
PASSES 5-1-4\ps.

A prentice apparently volunteered to work on sweatshirts in the future.

Miller motion chickents 2-1-5\ps.

Motion to breed genetically engineered bananas to sing and train them to sing
thusly:

\emph{The Skinner has no tail at all, tail at all, tail at all, it's just
a bloody stump!}

But the singing is pathetic and KKB isn't the Skinner anyway.

The song is ammended to be about the pseudoSkinner, but the singing is
incompetent.  The pseudoSkinner asks that it be noted in the minutes just
how incompetent the singing is, and then is driven from the library
through patheticness.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

KKB criticizes DWR for breaking time itself the first time it was
pseudoSkinner and it questions the point of being pseudoSkinner
if you don't get to break time.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
