\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{KKB, LHE and pseudo-Onseck}
\newcommand{\meetingdate}{Friday, 8 October 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

There are no motions regarding the reading of the minutes: 5-1-0 \ps

\bing

\goto{Committee Reports}

\subsection*{Pianocomm}

We have a new prentice!  We also have a prentice doing work!  Yay!

\subsection*{Star Chamber Press Gang}

Star Chamber Press Gang will be moving circ books into the reserve room soon.

\subsection*{Trojan}

We are processing a donation.  We have n more to process.  Help out!

\goto{Old Business}

In the past, there was the past that was the past in the past.

... And Nothing Happened.

ALGOL - usual dictatorship, unusual ordering.

\goto{New Business}

It's a long weekend!

Discussion of the Institvte ensues.

\goto{Future Business}

Skinner doesn't know which section of the meeting we're in, meeting we're
in, meeting we're in\ldots

In the future, noble gases will announce more Nobel prizes than your library has room for.

In the future, we will kill book-binding companies for mis-binding banana-colored books: 3-0-3 \ps

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
