\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 6 August 1860}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

KKB: Motion to change the date of the meeting to 1860 passes 7-0-5\ps.

\bing

\goto{Committee Reports}

\subsection*{Star Chamber}

We have a new cute pet named de Hume.  It protects the magazines and
books and is vicious and should not be messed with.

In other news, our magazines are being demoldified, without the aid
of radioactive material.

Attempt to reorganize the library this Saturday, next Wednesday, and a
week from Sunday.

\subsection*{pseudoSeldon}

We will have a pseudoSeldon showing of \emph{Hogfather}

\goto{Old Business}

KKB: Down with James Buchannan passes 5-0-1\ps.

DWR: Liberty and Union!  One and inseprable!

ALGOL

\goto{New Business}

EpicWizard: Motion to secede from the universe passes 8-0-2\ps.

Michael: Cory Doctorow has written a new book set in the new
future.

PW: The Sanderson book was good.

KKB: Motion to send aliens to the MITSFS from the elsewhere, so
they can visit passes 9-2-2\ps.

\goto{Future Business}

In 2010, the US Border Patrol will be stopping all southbound cars on
I-93 in New Hampshire.

DWR: Motion to notice that the Onseck has to leave in five minutes
with bananas passes 8-2-3\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
