\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 15 October 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

DWR: *silence* passes 4-0-4\ps!

\bing

\goto{Committee Reports}

\subsection*{Hasselcomm}

A prentice did Hasselcomm yesterday!

\subsection*{Star Chamber Press Gang}

Hardcovers will move into the reserve room this week!

\subsection*{pseudoSeldon}

There will be a Seldon showing tonight at 21:00 in 8-119.  We're
showing \emph{Buckaroo Banzai}.  People should come!

\goto{Old Business}

In the past there were elephants!  

A random guy in a suitcoat giving Michael a piece of paper and then
leaving passes 2-0-0\ps.

ALGOL

\goto{New Business}

In the present, there are circus people living on the railroad tracks!

It's family weekend!  There are parents here!  They're swarming!

Lemur shudders!  Naomi points out that they're nerd-breeding parents!

\goto{Future Business}

In the future it will be Halloween.

Boston Book Festival is tomorrow.  Lemur is lame and didn't look up to
see if any SF authors will be there, but you can check yourselves if you
want.  They have a website.

In the future we will have the whole Star Chamber at a meeting at the same
time and it will usher in a new era of banana-growing passes 3-0-0\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
