\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 27th August 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

DWR: Motion to condemn the minutes for not recognizing that it's still
1860.

KKB: Motion to condemn the Onseck for not remembering the contents
of previous weeks' minutes.

KCR: Motion to confuse EpicWizard.

And the determinant is 146 and all motions pass!

\bing

\goto{Committee Reports}

\subsection*{Bluebellcomm}

The Bluebellcomm overflow is dead again!

We have new book shelf copies of the Ted Chiang book, the new Laundry
book, and the new Temeraire book.  We also have a circulating copy
of the new Laundry book.

\subsection*{Catacomb}

We have lots of new magazines and, on the new mag shelf, a copy of
\emph{Science Fiction Studies} that talks about us and all
the other huge science fiction collections of the world.

\subsection*{Bottle-of-Rum-Comm}

We now have a fixed huge pirate chest in the library to give
the frosh rides in.

KCR: A stupid motion I didn't understand chickens 5-0-9\ps.

\subsection*{pseudoRedactedComm}

Redacted promises to send the library shiny things in the future.

Also, we have maple syrup cotton candy in the library!

\subsection*{pseudoROSFAP}

DWR may be turning into the new ROSFAP.

KCR: Fly, you fool!

\subsection*{pseudoSeldon}

There will be no Seldon showing this week

\subsection*{hBarComm}

Activities Midway 16:00-18:30 next Friday, please come.

Also, if you hold unscheduled hours this week, they will count for
full credit.

\subsection*{Star-Chamber}

The reserve compression is nearly compressed--it's a lot of compression!

We can now get at all of the magazine collection temporarily because
the window was fixed.

We have a new member of Libcomm.  The Onseck doesn't know who it is!

\subsection*{Onseck}

Our subscription to \emph{New York Review of Science Fiction} has
been renewed for another two years.

\subsection*{Magvintory}

We had a really productive meeting with the developers of the Needle
software, which might let us get the magazine information into a
computer-readable format in a sane way.

\subsection*{Libcomm}

Was muttering about something.  There should have been a twelve-thousand
line Zephyr, but there wasn't.  Maybe Zephyr can't handle a 
twelve-thousand line Zephyr.

\goto{Old Business}

PW: The summer, it's gone!

KKB: Except it's still 90 Farenheit.

PW: In the past, there was a TARDIS on Building 7, but now there's not.

BJK: There was a crack in the window.

Where are the Comic Books? The comic books are in California. Motion to
condemn Wayne B'Rells for his sex life with bicycles. Motion to condemn
Irwin T. Lapeer for his sex life with electric typewriters. Bruce Miller
is still skiing in Colorado. Motion to give Tom Galloway a better gag.
Isaac Asimov is still dead.  Hal Clement is still dead.  \emph{Twilight}
is still staked.  \emph{The Wheel of Time} is still unfinished.  Miss
Katie is still in Singapore.  The larva is still larval.  Redacted is
still in redacted.  Cthulhu is still dead.  And I think the Skinner
still has a sonic screwdriver. 

\goto{New Business}

PW: The Onseck's voicebox has been condemned to Albania.

KR: Note that you can't understand what we're saying.

PW: Yes it can.

Discussion of the fact that the library has an Albanian dictionary.

\goto{Future Business}

PW: In the future it will be term.

EpicWizard: In the future, I will hopefully be back for Arisia.

PW: In the future...mumble mumble...deep-fried ice cream.

KKB is apparently stalking people?  EpicWizard has a buisness card.
Which, unlike the one next to the calender, is not made of silk
and really pretty.

KCR: Motion to, in the future, get business cards made out of bananas
printed out.

ZEK: Something about a shark made out of a banana in Chinese.

KCR's motion chickens 6-0-11\ps.

KKB: Miller motion!  Fails 14-0-1\ps.

KKB: Miller motion!  Passes 11-2-2\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
