\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 9 July 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

There was much applause.

Michael: I only remember the bit about the mattress.

KKB: Motion to commend the onseck for being the most fictional
author in the library passes 14-0-1/ps.

\bing

\goto{Committee Reports}

\subsection*{Trojan}

We have been discussing potential donations with a couple of new donors
and we have boxes of stuff we don't have coming to us for free, so yay!

\subsection*{Kvetchcomm}

On the back cover of Charles Stross's new book, \textit{The Fuller Memorandum},
the Kvetchcomm review of \textit{The Jennifer Morgue} is quoted and cited
to the MIT Science Fiction Society.

\subsection*{Bluebellcomm}

The Bluebellcomm overflow is dead!  *singing* "Ding-dong the o-ver-flow is
dead!"

\subsection*{PseudoNiagracomm}

We have two possible ways of getting rid of magazines that we're working on.

\goto{Old Business}

NH: The \textit{Doctor Who} finale was awesome!

PW: The country's birthday was a couple of days ago.  Lots of explostions!

KKB: Boom today?

PW: No.  Maybe boom tomorrow?

KKB: There's always a boom tomorrow!

PW: Fireworks-making is one of those buisnesses that I have absolutely
no interest in going into.

Discussion of whether fireworks factories are more or less likely to
explode than silos.

KKB:  Where are the Comic Books?  The comic books are in California.  Motion
to condemn Wayne B'Rells for his sex life with bicycles.  Motion to condemn
Irwin T. Lapeer for his sex life with electric typewriters.  Bruce Miller
is still skiing in Colorado.  Motion to give Tom Galloway a better gag.

NH: In other words, things haven't changed.

\goto{New Business}

PW: The new season of \textit{Eureka} starts tonight!

DWR: I learned to make things this week!  Useful things!  With metal!
Now I just need to make a coffee cup out of aluminum!

KKB: I did not perform any coups this last week.

PW: Is that a yay or not?

KKB: Well, you're still in power....

PW: Yay!

\goto{Future Business}

PW: Guildcamp is next week, starting tomorrow, and students should do it!

NH: In the future I'm going to be in a play, \textit(The Importance of
Being Earnest} next Friday, Saturday, and Sunday.

PW: Two authors at Pandemonium in the next week!  Charles Stross on Tuesday,
13 July at 19:00 and Naomi Novik on Saturday, 17 July at 19:00.

Discussion ensures about whether Charles Stross is a member.  It seems that
despite having visited several times he is not; it is unclear why he is not,
maybe he declined it?

DWR: Motion to adopt IUPAC spellings of element names chickens 4-1-7\ps.

DWR: I move to purple bananas.

KKB: Friendly amendment to green bananas.

DWR: Reject amendment as unfriendly.

KKB: Then I make a separate motion.

DWR: Motion to annoy the onseck.

PW: I have three motions without seconds.

DWR: I second the one I didn't make, since I probably can't
second the other ones.

PW: Why can't you?

DWR: Okay, I second whatever motions the Skinner will let me second.

PW: Matrix vote!

KKB: You can't do that.  You can't have green and purple together!

PW: They're not together, it's a matrix.

Motion the First: 1-7-4\ps.
Motion the Second: 4-4-7\ps.
Motion the Third: 4-1-10\ps.
And the determinant is -84 and all motions fail!

And the Skinner was driven from the room by singing.

\bing
\noindent

KKB: *bangs gavel block with telzy toy*
KKB: Meeting adjourned, 68.4 Ksec SST.  And a coup!

PW: Reenters, and *bangs gavel block with gavel*.


\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
