\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 13 August 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

DWR: Motion to commend the minutes for confusing the Onseck passes 5-1-1\ps.

KR: Since when can the onseck make motions about the minutes.

\bing

\goto{Committee Reports}

\subsection*{pseudoSeldon}

We will have a showing of \emph{Hogfather} at 21:00 tonight.  We will have
a showing of something next week.  Suggestions?

\subsection*{hBarcomm}

Rush is coming up soon--email will be sent.

\subsection*{Star Chamber}

Another meeting to reorganize the library on Sunday.

\subsection*{pseudoRedactedcomm}

There is maple syrup cotton candy.  It is probably Kendra-safe.  Kendra
and Karl attack it.  Apparently it is Kendra-safe.

\subsection*{pseudoNiagracomm}

There will be a meeting tomorrow to deal with shipping magazines far, far away
Saturday from 12:00 to 15:00.  People, especially prentii, should come.

\subsection*{pseudoOnseck}

We are getting a complimentary subscription and some number of back issues
of the really awesome magazine \emph{Extrapolation}, which is a high-end
journal of SF criticism.

\subsection*{Downtrodden Membership}

EpicWizard: I was going to get here early, and then I didn't.

\goto{Old Business}

In the past, someone Kendra knows was allergic to trees.  They might still be,
actually.

In the past, The Maintainers said that you should use "emph" to get italics
in LaTeX, but who cares what they say?

In the past, it was 1860.  In the past it was also the years 1861-2010. 

In the past, KKB and DWR thought they knew the ALGOL.

\goto{New Business}

EpicWizard: Motion to route cat-5 through the wormhole fails through lack
of a second.

DWR: Motion to route fiber optic cable through the wormhole fails 2-6-4\ps.

KR: Thou shalt not violate causality within my historic light-cone.  Or else.

KR: Banana! fails for lack of a second.

DWR: Motion to obtain liquid nitrogen in 240 L aliquots for the purpose 
of freezing purple bananas for export to Honduras fails 7-8-2\ps.

EpicWizard: Banana! fails by Skinnerial decree.

KKB: Motion to ook and turn the Skinner into a banana passes 11-0-0\ps.

\goto{Future Business}

KKB: Motion that lemur is equivalent to [redacted] fails for lack of a vote.

KR: For lack of a meeting, really.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
