\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, March 12, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to grind the minutes into a fine powder, apply boiling water, and thus provide a healthful, if slightly overcaffeinated, tasane: 1-0-8 \ps

\bing

\goto{Committee Reports}

\subsection*{Moocomm}

We have Repo Men advance screening passes!  Tell us if you want to go and we'll give you details.

\subsection*{pseudo-AlohaLenscomm}

The Rogues' Gallery is complete!  Muahaha.  JAJ doesn't look like a demented elf anymore.

\subsection*{Star Chamber}

We changed the committee designations for a bunch of keyholders (as seen in the Rogues' Gallery).  Again.  Hopefully it's right this time...

The hunt for kaduk continues!

\subsection*{Theftcomm}

The TIF still has problems, but at least the algorithm for producing it is causal instead of acausal now!

\subsection*{hBarcomm}

The Tech has accepted our ad.  It will actually run.

Motion to place in the next MITSFS ad placed in the Tech a clause which says ``By printing this ad, we cede all space on the fourth floor of W20 to MITSFS'': 8-0-0 \ps

Oh, come on, even Spehn would have voted for that one, right?

\subsection*{Things passed bycomm}

A few things haven't happened in about 10-20 years, and we're going to try to get them to happen again: a new t-shirt (or sweatshirt!) design, updates to the MITSFS lore, and additions to the Things to Amuse the Members binder.

Ideas, assistance, complaints, etc.?  Talk to KKB or JPM.

\subsection*{Pianocomm}

We got a new prentice this week!  A member wandered in and decided to fix the romanizations of the foreign section, and we made her a prentice in exchange for the kindness.  We know, we're mean.

\goto{Old Business}

Silence.  Apparently we have no past.

\ldots  I wonder if I missed the dragon swooping in and eating us this week.  Something clearly happened to make time pass in jagged bits.  Perhaps we're in the Matrix?

ALGOL

\goto{New Business}

BTS motions something about prentices and unicode and upcase/downcase pairs.

Motion to extend the meeting 1/3600 of an hour \textit{past} the time a motion with the word 'banana' in it passes: wankery-wankery-wankery \ps

\goto{Future Business}

Yet again, we have NO FUTURE.

\bing
\noindent
Meeting adjourned, 66.601 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
