\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 28 May 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

MGH: Motion to condemn the minutes for containing insufficient pairs of
designer shoes PASSES 7/5/1\ps.


\goto{Committee Reports}

\subsection*{VanHelsingComm}

VanHelsingComm is moving, but will continue efforts from suburbia.

\subsection*{PseudoLHE}

We may have a new way to pay for Amazon, if legal approves it.

\subsection*{PseudoAnalogComm}

The new schedule starts sometime soon.  Probably on 6th June.

\subsection*{LarvalComm}

BTS and Kat expect to spawn in the next week.

\subsection*{PseudoKvetchComm}

BTS sent a really neat Harry Potter fanfic that's sort of Harry Potter
crossed with Miles Vorkosigan.  You should all read!

\subsection*{PseudohBarComm}

We put up new posters.  Or people did, anyway.


\goto{Old Business}

MKR sent all her books home.  It was under one hundred pounds.  Now she
just has the library to read.

SIR: How 'bout those South Koreans and that Submarine.

It was established that the Dear Leader would never lie.  And he has good
taste in liquor.

REDACTED wants the Dear Leader's DVD collections when he gets deposed.  SIR
says it's okay if they lead the strike team to take him out.


\goto{New Business}

General agreement that it might be New Business, but we're confused.

SIR: We should consider fishing.
REDACTED: We should consider fishing for Cthulhu.
SIR: If you get cheese, Cthulhu
REDACTED: We need to have a cage match between Cthulhu and Kim Jung Il.
SIR: He'd feel unclean coming out of there.

\goto{Future Business}

REDACTED: In the future I'll have to pay for my crappy Star Wars
novelizations.

REDACTED: Motion to change the official regalia color of MIT to bananas FAILS
3/1/9\ps.

REDACTED: Motion to stage a coup and install the larva as the head of its own
banana republic so that MITSFS can live in peace forever under the Dear Leader.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
