\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 29 October 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Lame PASSES 6-0-2\ps.

\bing

\goto{Committee Reports}

\subsection*{Bluebellcomm}

Help!  The books are eating us!

\subsection*{Hasselcomm}

Help!  The books are eating us, too!

\subsection*{Star Chamber Press Gang}

We replaced shelves and moved books and used prentice labor.

There's a \emph{lot} more work to do!  Prentices should do work!

\subsection*{Star Chamber}

Inventory is 8 January!

\subsection*{pseudoTrojan}

The books are eating us!

\subsection*{Trojan}

Everything is under control.  One less box of books is feral and
eating us.

\subsection*{LHE}

We broke SAPWeb.  We're sorry.

\subsection*{Nanocomm}

National Novel Writing Month write-ins will occur throughout
November 15:00-17:00 during NH's Saturday hours. 

\goto{Old Business}

Kaleb: In the past there was mold.

KKB: In the future there will hopefully not be mold.

Random \emph{Inception} references and paleobiology wanking
from people who aren't biologists.

KKB: Old TZs are hard to manuver.

DWR: In the past there was this big bang.

PW: In the past there might have been something before that.

DWR: In the past Steven Hawking recommended everyone go to
more movies PASSES 6-2-1\ps.

ALGOL

\goto{New Business}

In the present, the LHE tries to stage a coup.

Don't touch that gavel, the Skinner has a cold!

But if I get the gavel, I get ultimate power!  What's a cold
compared to ultimate power!?

Motion to declare the meeting to be taking place in a different
1880 PASSES 12-1-1\ps due to NH being dressed in a pretty
steampunk gown with a parasol and attack robot.

\goto{Parallel Business}

In the future it will be Pretend to Be a Time Traveller Day!
NH and DWR should find out when; NH didn't realize that existed.

In the future the Skinner might not feel sick.

In the future we'll all be chased by banana-colored robots!
In the future we're going to get a plush Momo, which hopefully won't
eat all the bananas!
Motion to annoy the Onseck!

And the determinant is -74 and all motions PASS!

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
