\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, March 26, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

Motion to get the pseudo-Onseck a spellchecker: 11-1-3 \ps

\goto{Committee Reports}

\subsection*{Star Chamber}
We keyed kaduk (BJK) after chasing him down for ``only'' 3 weeks.

Our lapstop was ordered.

\subsection*{Pain of Spacecomm}
DAV did something with all but a thousand of something else.  There were pretty pictures of magazine covers.

Motion to name the next thing to walk out of the door of the library ``Twilight Zine'' because that's the only way we're going to get one out the door: 10-something, 4, that's what it was-10 \ps

KR: In Microsoftland, version 3.0 is the first one that works!
BTS: And version 4.0 is the last one that works?

\subsection*{pseudo-Jourcomm}
It will be published much less late than the TZ which had 4 Skinner reports!  Coming out \textbf{Real Soon Now}.  There are strange rumors of TZ aready having articles!

\goto{Old Business}

Singing commences.  We are regaled with the tale of a french horn.

In the past, there were books, and we read them!

Beginners on the saxophone sound like ducks being strangled.

Move to express inertia (MKR: ``Why?''): Unusual vote, unusual result, unusual declaration of new business.

\goto{New Business}

Fortune Cookie: ``Book lovers never go to bed alone.''
BTS: *examines book* ``Have I been using this wrong?''

Ian: ``How high up the Amazon chain do you have to be before they'll airdrop books to you on a deserted mountain?''

\goto{Future Business}

In the future, there will be more books, and we will read them (by symmetry).

In the future, we will not attack HRSFA (on 4/18).  Of course not.

And perhaps a banana split for dessert?: 12-0-1 \ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
