\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 3rd September 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Michael would like to commend the minutes for being barely
intellible, but fails for lack of a second.

\bing

\goto{Committee Reports}

\subsection*{Star-Chamber}

We got about one-eighth of the freshman class to sign up at
the Midway.

We need to get rid of lots of boxes from the library this week.
A keyholder who can rent a Uhaul should help.

\goto{Old Business}

PW: The TARDIS rematerialized on the Great Dome from Sunday night
to Monday night.

ESK walks in and asks why there is a coffin.

That's not a coffin, it's a pirate chest!

ESK may be a pirate.

Discussion of the incompetence of Somali pirates who attack US Navy
ships.

ESK doesn't know the current going cost of AK-47s.  PW and KCR think
they must cost on the order of ten dollars.  Ammo might cost more.

Unusual motion.  Unusual second.  Unusual vote.  Unusual complaint.
Usual dictatorship.

\goto{New Business}

PW: The frosh are here!  But not in that coffin.

DWR: Seldon showing of Fourth Doctor \emph{Doctor Who} tonight if anyone
actually comes to it!

ESK: \emph{Jesus Christ Superstar} tonight and further nights, being 
performed by Musical Theatre Guild!

\goto{Future Business}

PW: In the future it will be term!

ESK: In the future there might be frosh here.

PW: Maybe next week?

PW: In the future I will get rid of these boxes.  And an electronic
checkout system.  And a Twilight Zine.  And \emph{Duke Nukem Forever}
will come out.

DWR: Actually, according to PC World, that's happening in 2011!

ESK thought that SIR was going to be here, because Zephyr said so.
She checks for him in the pirate chest.

And the Skinner was driven into a pirate chest through singing.
Sadly, it was not a very sturdy pirate chest.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
