\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, pseudoOnseck}
\newcommand{\meetingdate}{Friday, January 29, 2009}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes performed as interpretive dance by the pseudoOnseck.

Motion ``vigorous!'' passes: 8-0-4 \ps

\bing

\goto{Committee Reports}

\subsection*{Titanic Tetriscomm}
We punted a bunch of shelf parts out of the alley.  Yay floorspace in the
 alley.  They have been posted to reuse.

\subsection*{Mag*}
Mag* had prentices do work.  Also magventory data was cleaned up into an 
almost-usable format.  We could use someone to help with that.

Wankery about history of MITSFS publishing its magazine holdings ensues.

If we get a real dex of the magazines, we might call it the Kendex (after Ken 
Johnson).  But where is the Barbiedex?

\goto{Old Business}

THERE WAS A ZOMBIE APOCALYPSE.  Better dead than ZED.

MKR received a birthday cake via the mail.  Modern times are amazing.

Motion to pass around a fruit snack, perhaps a plantain or a banana fails: 
4-18-2 \ps

ALGOL

A newbie tries to overthrow the skinner.  He promptly goes insane at the 
attempt.  Learn, ye foolish mortals, what fate befalls he who messes with
our great and glorious skinner!

\goto{New Business}

Every now and again, you still hear about women named Livia.  Disturbing, not
admirable, guys, come on!

YASID wanking involving portals, Flatland, and relativity.  Then a large lime 
green dragon enters the room and eats us all for dinner, then falls asleep, 
allowing us to continue the meeting in one of its three stomachs.  No one 
notices, they are too busy wanking.

\goto{Future Business}

There is a movie called \textit{Wolfman} coming out soon.  Also 
\textit{Lensman}.  Also \textit{Solomon Kane}.  And Keanu Reeves in the 
live-action version of \textit{Cowboy Bebop}.  
Moviesmoviesmoviesmoviesmoviesmoviesmoooooooviesmoooooooooooooooooviesmoooooooooooooooooooooooooooooooooovies.

BTS: ``It's the 1920s all over again!''

KCR: ``BRIAN BLESSED.  That's in all caps please, maybe boldface.  BRIAN 
BLESSED!''

More people might die.  *gasp*

In the future, Utah might get back to us about the scans.  They must be aliens
from a different universe in which it would actually be profitable to abscond
with our microfilm.

In the future, there will be Reg Day and term and a career fair.

KCR: ``Thursday is coming.  Did you bring your coat?''

Burn, witches, burn!  Because this makes for good youtube watching.

Motion that in the future, we might have bananas: 6-6-1 \ps

Motion that in the future, we might have bananas... no, fuck that.  BANANA!: 
1-11-6 \ps

Any motion the onseck wants, therefore to DESTROY THE WORLD: 2-4-11 \ps

Determinant is 600, all motions pass, the meeting ends twice and the world is
destroyed.  Happy world destruction day, everyone!  First anniversary!

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
