\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Margaret Gentile, pseudoOnseck}
\newcommand{\meetingdate}{Friday, 11 June 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to coup fails by skinnerial decree.

\bing

\goto{Committee Reports}

\subsection*{Larvalcomm}

The larva may come to the library today.  Squee!

\subsection*{Pianocomm}

We have a new keyholder, Cathy Zhang, who shall be known as CZF.  
All glory to the MITSFS!

\subsection*{The Strange and Wonderful Magazine Conglomeration}

We had numerous -comms come into the library and deal with magazines
and lots of things happened. Wonderous things. Ten boxes left the
library in a solemn funeral procession where hired mourners wept
and threw flowers to demonstrate the significance of this event
to the masses.

\subsection*{Skinner}

People painted the ceiling and got paint where paint
should not be and it was sad.

\subsection*{Bondagecomm}

We finally have more than one copy of the Bondagecomm keys so that if
we lose the keys we don't lose Bondagecomm.  If you need a key, talk
to the Skinner.  No, there were no bodies in the woods--or were there?

\subsection*{Redactedcomm}

**THIS INFORMATION IS CLASSIFIED AT LEVEL GREEN.  IF YOUR CLEARANCE
IS ABOVE LEVEL GREEN, YOU ARE SEEING THIS MESSAGE IN ERROR.**	


\goto{Old Business}

KKB: Prentices did work today.


\goto{New Business}

Charles Stross is visiting Pandemonium on July 13th!

Naomi Novik is coming on July 17th!

Go to http://www.pandemoniumbooks.com for details.  Except that there
don't seem to be any details.

MGH: This is my last meeting.  It is sad.


\goto{Future Business}

NH: In the future more prentices will be keyed.

**DWR arrives by time travel.**
DWR: In the future there won't be any prentices left to do 
Hasselcomm?
**DWR disappears by time travel.**

The Sniffen-Spawn has arrived.  It is an adorable larva.  There is much
smiling at the larva.  We cannot contain cuteness of this magnitude!
Quickly, prepare the membership sheets!

Motion to commend the banana-coloured toy for capturing the 
attention of the baby.  Motion passes 13-0-0\ps.


\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
