\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 3 December 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the pseudoOnseck for not doing as KKB said and telling the
glorious tale of the meeting packed with author visits and time travel
that happened while they were on Thanksgiving vaction PASSES 12-0-1\ps.

\bing

\goto{Committee Reports}

\subsection*{Trojan}

Boxes of things keep coming in.

KKB is sort of tired PASSES 8-0-3\ps.

\subsection*{Star Chamber}

There will be a Time Warp between two weeks from Today and "whenever the
Skinner gets back from vacation".

KKB: I want my gavel back! (plaintively)
PW: It's my gavel.
KKB: It was mine last week.

\subsection*{psuedoKvetchcomm}

Thingie lemur said about a book that was donated for review being eaten by
the MIT mail system for a month and then vomited up a couple of days ago.

\subsection*{Libcomm}

Karl has magic powers and Dexhamster won't run unless he performs the magic
ritual on the relavent computer CHICKENS 2-0-7\ps.

Magic firework sparkle things happen when ZEK waves a wand or something; 
it was all very confusing.

\subsection*{Bluebellcomm}

ZEK and YT were non-lame and did work for Bluebellcomm, unlike the lazy
Onseck.

\goto{Old Business}

ZEK and KKB conspire to stage a coup by stealing the Skinner's gavel while
he's being distracted by a book.  Then KKB and the Skinner and afarrel start
wrestling over the gavel and people scream warnings about busting laptops.

We have no past; the world was created instantaniously just now.

ALGOL with broken arguments

\goto{New Business}

In the present there are some bacteria.  They're made of arsenic!

Actually, they're not.  But they're substituting at least some of their
phosphorus with arsenic.

Motion to make hors d'oevres with arsenic bananas CHICKENS 3-2-8\ps.

\goto{Future Business}

In the future it will be finals.  And dead week.  And IAP.  And Winter Break.
Not necessarily in that order.

ZEK is excited for inventory.

Also, ZEK is generally bouncy about overhead markers and overheads and
shiny.  But the LHE doesn't want to waste her running-away-to-South-America
budget on things like this, as she bounces a bottle on her head.

Argument about the fact that no one joined in with KKB when she was singing
"Skinner has no tail at all".

We have apparently renamed Mandarin "Glyph" because ZEK said so and then
translated "arsenic banana" into it as "shen xiang jiao",
which PASSED 6-1-3\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
