\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 1st October 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Michael moves that we approve the laconicity of the reading of the minutes.
PASSES 6-1-1\ps

\bing

\goto{Committee Reports}

\subsection*{hBarComm}

PW sent a welcome email to bananafrosh!

KKB moves that we commend Douglas Adams for having infinitely reusable text.
PASSES 10-0-0\ps

\subsection*{Trojan}

KKB: We've gotten a donation every three days throughout September.  Thus we're now
far, far, far, far behind again.  KKB is so intimidated that she can't even
talk.  Prentii and other people should let her know about weekends in October
when she might be able to enslave them to help deal with this.  

\subsection*{Star Chamber}

PW: We're having a big party to move boxes out of the library tomorrow at 13:00.

\goto{Old Business}

Attempted matrix motion on ending the universe with bananas fails for lack of a
second, and KKB is very sad and perturbed.

\goto{New Business}

KKB: Motion to take our books and secede from the universe is seconded by Casey.
CHICKENS 4-0-7\ps

DWR: Last Saturday I was in Salem by accident.  And I discovered a used book
store that was much further along in being eaten by the books than we are.
They didn't have shelves, just huge piles of books, and other piles behind those
piles.  The proprieter was still human, though, not a book golem.

Photos:
http://amiablebowfin.files.wordpress.com/2010/09/dsci0057.jpg
http://amiablebowfin.files.wordpress.com/2010/09/dsci0058.jpg
http://amiablebowfin.files.wordpress.com/2010/09/dsci0059.jpg


\goto{Future Business}

KKB: In the future the galaxy will implode.

PW: In the future we will go to dinner.

DWR: Two weeks from tomorrow is the Boston Book Festival.  Science fiction
authors are likely to be there, but I haven't checked yet.  It's likely to be
neat; it was last year!

And the Skinner was driven from the room by singing, leading the LHE to bang the
gavel with the Telzey Toy.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
