\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 22 October 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Michaels assertion that there are no motions regarding the 
reading of the minutes chickens from lack of enthusiasm.

\bing

\goto{Committee Reports}

\subsection*{Star Chamber Press Gang}

Some hardcovers have moved into the reserve room.  More movement of
the hardcovers will follow! 

\subsection*{Skinner}

The library is lacking in enthusiasm, probably because it's too hot.

\subsection*{Star Chamber}

The Skinner tried to turn down the temperature today, it might fix
itself eventually.

\goto{Old Business}

Unusual lack of a motion.  Unusual lack of a second.  Unusual lack of a
vote...but the usual BING!

\goto{New Business}

In January and February there will be Arisia and Boskone, as is usual.

\goto{Future Business}

Genetic engineering to develop an arctic banana passes 1-0-3\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
