\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kendra Beckler, LHE and pseudoSkinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 10 December 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

What's the usual motion CHICKENS 2-1-5\ps.

Motion to commend the Onseck for doing sufficiently expressive voices
in reading the minutes PASSES 6-1-3\ps.

A later motion--after the first two were voted on--that ZEK can have
chickens PASSES 8-1-5\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudoSkinner}

The Onseck is too busy with the minutes to make its committee reports,
so the pseudoSkinner is filibustering for it!

\subsection*{Downtrodden Membership}

Let's talk about arsenic bacteria, since we've now had time to read the paper!

\subsection*{pseudoSeldon}

Seldon showing of Hogfather tonight at 21:00 in 8-119!  You should all come!

\subsection*{Star Chamber}

Time warp will be Wednesday, 15 December until Wednesday, 5 January!

Inventory is 8 January!

Fear, uncertainty, doubt!  The details of this are above your security
rating, citizen.  If you think your security rating is above red, you
are seeing this in error and should contact friend computer.


\goto{Old Business}

In the past there were classes!  They are a thing of the past.  That is
very happy!

On one side of the Earth, the sun rose.  On the other side of the Earth,
the sun set.

ZEK wishes to know why she was not informed that the Earth has sides.
KKB explains that it was a very recent discovery.

KKB expresses concern that the sun is now considered old business.  BJK
notes that the Milky Way is very, very old business.  ZEK wants to eat it,
since it's a giant candy bar in the sky, but KKB says she can't because it's
clearly gone, since it's old business.

The use of arbitrary terms PASSES 4-2-1\ps.

Motion to give Michael multiple personality disorder so he can succeed in
his attempt to do ALGOL on his own CHICKENS 2-2-2\ps.

Motion to commend the Onseck for not killing itself while assembling
shelving units passes by pseudoSkinnerial decree because she doesn't
want a dead Onseck on her hands, just a dead Skinner. 

There is general agreement that "assemblying" cannot be a word, though
the Onseck had hoped it might be allowed to mean "having an assembly".

ALGOL

\goto{New Business}

ZEK is eating something that she says is on fire.  DWR points out that
we need to pour water on it.  The pseudoSkinner says she has to leave
the library, since neither fire nor water is permitted in the library.

PW is in Redmond, WA interviewing with Microsoft.

There is actually more than one prentice at the meeting.  Yay!

\goto{Future Business}

In the future there will probably be classes.  Awwwww.  But in the future
classes will end again.  In the future ZEK is teaching classes!

In the future we will watch \emph{Hogfather} and in the future it will
be Hogswatch.

In the future we will reconcile our books with our record of the books.
Keyholders should sign up for Inventory!  Prentices should also sign up
for Inventory!

Also, prentices should do work, so we can key them and make them do
even more work!  Also, committees should announce prentice work so
that prentices can!

In the future, the Universe will die a slow and painful and tepid death.

In a different future, the Universe will die a fairly quick and high-density
death.

Miller motion FAILS 1-2-4\ps.

Miller motion PASSES 7-5-1\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
