\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, April 30, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to BRAAAINS the reading of the minutes: fails due to skinnerial decree of no zombies being allowed in the meeting

\goto{Committee Reports}

\subsection*{Frustrated Authorcomm}

Script Frenzy ends at midnight and NH is going to finish DAMMIT even if it makes no sense.

\subsection*{Picniccomm}

Elections next week!  Picnic the next day, please sign up if you have not done so already!  Come help us sacrifice a virgin watermelon and play coconut baseball.

\subsection*{Trojan}

The United States Postal Service lost some of our books from our most recent donation, but that might be okay because they threw in some extra Spider Robinson.

\subsection*{Pseudo-hBarcomm}

New poster drafts are in hBar/posters in the locker, send comments and edits to the Star Chamber.

\goto{Old Business}

Oops, we were supposed to make an index of the microfilm.

Silly people continue to believe that multiple cars can exist in the same space at the same time.

Brian makes a complicated motion... *crickets*

Motion to send BTS to Albania: 3-7-9 \ps

Motion to send the Onseck to Albania, thus simplifying the job: 1-14-3 \ps

Aww, I don't get an Albanian dictionary.  Damnation.

ALGOL.

\goto{New Business}

MKR, CK, and BJK are singing in a concert on Sunday at 4 and another concert during^H right after the elections meeting next week.

Motion to consider the books lost to the United States Postal Service to be an offering to Nimbus blah blah blah banana: 13-1-4 \ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
