\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Karl Ramm, Libcomm and pseudo-Onseck}
\newcommand{\meetingdate}{Friday, March 19, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to get the Onseck some caffeine or soemthing so that she can record
motions spoken at a reasonable pace: 4-2-11 \s

\bing

\goto{Committee Reports}

\subsection*{Moocomm}

We saw Repo Men.  It was full of blood and gore.

Evil Dead: The musical is recommended.

\subsection*{pseudo-Trojan}

No more backlog!  We might even get the letters out before taxes are due!

\subsection*{*Chamber}

UC-Riverside is publishing information about SF libraries, keyholders were
mailed for suggestions.

\subsection*{Pseudo-25th Fist of the Republic}

Definitely not invading the HRSFA April 18th.  Definitely not bringing a
gift.  Do not talk to the Onseck about the lack of gift or lack of
loadouts.

Should this be recorded?  Well, if they read our minutes, they can't have
fair warning.

Google doesn't have the minutes from the last time we didn't try this.

Discussion that we need to not invade people more often so that we won't have room for our
books.

\subsection*{Pain-of-Spacecomm}

DVDs for NESFA are almost ready.  The test-labeled DVD is {\bf shiny}.

\subsection*{Libcomm}

Discussion of barcoding equippage.  We will get stuff and things.

\goto{Old Business}

``Term.''

He-who-shall-remain-nameless sings the doom song.

ALGOL

\goto{New Business}

Elizabeth Bear has a new book out, {\it Chill}, which is apparenlty a
sequel to {\it Dust}.

It's spring break!... although msot people here aren't undergrads.  (And
the undergrads are sad.)

Polo Bacigalupi has a new YA novel coming out.

\goto{Future Business}

In the future it will no longe be weird to be leaving work with the sun
still up.

Skinner, yelling, to kaduk: In the futre you're coming in to get keyed,
right?

In the future we will not be giving presents to HRSFA that do not include
giant beetles from the ground in Antarctica.

Discussion ensues of surprising shrimp found by NASA in Antarctica.

Observation that there would be lots of rooms for books there.

Motion to conquer the Dole banana partition and mvoe our books there:
13-4-4 \ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully but sadly unspiredly submitted,}
\centerline{\onseck}

\end{document}
