\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul  Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 21 May 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Kat: Motion that the Onseck be required to make LaTeX commands for the Brian
standard motions, to make them more interesting.  Friendly amendment from KKB
to include the ALGOL in this. (4/4/7\ps)

KKB: Motion to condemn the minutes for insufficient knitting. (8,11,4\ps)

BTS: Motion to have a matrix vote. (4,4,4\ps)

And the determinant is 69, and all motions PASS!


\bing

\goto{Committee Reports}

\subsection*{PseudoAnalogComm}

Send in your requests for hours.

\subsection*{LHE}

Got sufficient grades to continue to be a student and therefore LHE.

\subsection*{PantherComm}

PantherComm did work.

\subsection*{BlueBellComm}

Did work, and can't find a copy of \emph{Le Petit Prince}.


\goto{Old Business}

BTS: Thirty Years Ago \emph{The Empire Strikes Back} was released to theatres.

MHG: Thirty years ago Pac-Man was released.

BTS: Back when they were filming \emph{The Wizard of Oz}, they caught the 
world getting colorized.

\goto{New Business}

Suggestion that the Sniffens' daughter be named Susan Calvin.  This might
result in a child more comfortable with robots than people.  BTS: This might be
a survival skill.

A discussion of what might be a Furby, but sounds to MHG more like a Tickle-Me-
Elmo, which she'd like to set on fire.

KKB heard the word magazines.  They were her problem, but she gave them to
PantherComm, which made them her problem again as SmilesComm.

Windup Girl by Paolo Bacigalupi won Nebula for Best Novel.

Assistant Professor Haldeman was inducted as a Grand Master.

John Scalzi was elected SFWA President.

\goto{Future Business}

They're showing the newly restored, uncut Metropolis at the Coolidge Corner
Theatre starting June 4th.

Someone went to school with the son of a former Nazi.

KR went to school with the grandson of the former Burmese dictator.

JVS: My marshal's baton is the personification of unbending will power
for victory of the multinational Soviet people!

BTS: Motion to search the membership rolls of MITSFS for former dictators
of other (non-Burmese) banana republics PASSES 7/0/2\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
