\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 14 May 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST 
\skinner, presiding; \onseck, recording.

Minutes read.

Standard Brian Motion 14.  CHICKENS 4-0-6/ps.

\bing

\goto{Committee Reports}

\subsection*{PicnicComm}
We had a picnic.  It rained, but we did things anyway.
There was a big picnic, so hopefully it won't rain next time.

\subsection*{Skinner}
Also, we had elections.  The new book shelf was cleared, just in time for the
new books that came in yesterday.

\subsection*{Instrumentality}
Random stuff.

\subsection*{Seldon?}
There was a movie.  We went to see it?  It was much better than Repo Men.
Parts of it were horror, parts were drama.  It might have been titled Splice.
It might be recommended that people see it once--telling more would be spoilers.


\goto{Old Business}

BTS: Iron Man 2 came out.  It passes the Bechtell Test.  It has a lot of 
explosions.  There are two female characters.

MKR: I FINISHED!!

PW: Things that aren't finals are over for students.  The rest of you normal
people still have to work like normal.

ALGOL


\goto{New Business}

Discussion between new, old, and former skinners about whether it is
is necessary to announce "New Buisness".  MKR says you don't need to,
and it's more fun if you don't.

BTS: They changed the security gates for parking around campus--they're
now much smarter and broadcasting on RFID

PW: Apparently a new MIT ID can behave like a Charlie Card for passes at
least. 

BTS: That's a horrible idea!  Motion to recommend that Hell transfer its
ambassador to France to ambassador to the MIT Card Office in charge of
designing the new ID card, because this can only be an improvement. 
FAILS 4-3-5/ps.

MKR: In the future will be the reign of the great and glorious Skinner 
Paul, the Weaver.

General discussion of whether weaving is vegan; in general it isn't
necessarily.  You can use leather, but that's hard.  Sinews and gut
work better.  Weasels can be used as well--alive or dead.

KR: Motion to get someone at the VI/IX interface to get me an interface
for my laptop that lets me recommend things from MobComm. PASSES 8-0-1/ps.

KR: I send many emails to MobComm; some are things the library shouldn't
actually buy, such as French graphic novels.

BTS: Standard Brian Motion 17 (contains bananas).  PASSES 7-0-3/ps.

\goto{Future Business}

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
