\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 25 June 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the minutes for not containing enough sonic screwdrivers per volume passes
42-4-1 plus Spehn. 

\bing

The Skinner vanishes in a flash of light and the gavel crashes to the floor.  Simultaneously
a torrent of water falls from the ceiling, flooding the library shoulder-deep and rushing out
the open doors.

A chorus of screaming and shouts of "Oh my god, the books!"

KKB grabs the gavel and

\bing

"In the absence of the Skinner, I guess I'm pseudoSkinner!"

While everyone tries to overcome shock and figure out what to do, a tall gangly man dressed
in only a bow-tie and a banana-colored Speedo stumbles out of Damnation Alley, clearly as
confused as the rest of us.

KKB: (gesturing menacingly with the gavel) What have you done to the books?  And what
were you doing back there?

Bow-tie Man: Umm.  I think it must have been some sort of dimensional vortex?  I was in
the swimming pool in my library and then there was a flash and I was here and all the water
must've come with me.

KKB: What!?  What was a swimming pool doing in your library?  And why did you send it to ours?

Bow-tie Man mumbles something about L-Space while wandering towards circulating room.  Several keyholders begin to chase him.

A blue box, taller than the ZGT, slowly materializes in the doorway.  The doors open and the
Skinner jumps out, clutching a silver pen-shaped object with a glowing blue end.

Skinner: Give me that!  (grabs gavel) I think I can fix this, but first we need to end the
meeting.  Then we can go back in time and prevent any of it from happening.  (pushes Bow-tie
Man into the box, which starts to fade away)

Motion to condemn the man with the bow-tie and the banana-colored Speedo passes by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

The Skinner grabs the Onseck's notes and uses the gavel to warp back in time while muttering
something about buying a mattress.
