\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 12 November 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the minutes for not having Emmy in them, unlike this one
fails due to lack of a second.

\bing

\goto{Committee Reports}

\subsection*{Star Chamber Press Gang}

We finshed moving the hardcovers!

\subsection*{Star Chamber}

Our copy of \emph{Cryoburn} should be here by now but it isn't.  People
are sad.  The Skinner is looking into it.

We should look into inviting Charles Stross to visit; he'll be in Boston
in February.

\subsection*{pseudoNiagracomm}

Boskone is in February.  If you can help out with the Niagracomm table, you
should email Ellen (CC) to tell her if you can help out with the Niagracomm
table now so that she can figure out if we can have one.

\subsection*{Trojan}

Trojan made a lot of prentii do work, but there's still a lot of work to do.

\goto{Old Business}

There was no past, there is only current cuteness passes 10-0-0\ps.

ALGOL

\goto{New Business}

Down with filesystems passes 12-2-9\ps.

New SF movie exists.  Is called \emph{Megamind}.  It lacks minions, sadly.

At a mall last week, there was a photoop with minions.

Also, a new \emph{Harry Potter} movie is coming out.

Motion to condemn units for being insufficient chickens 2-0-4\ps.

\goto{Future Business}

Someday people will be less hosed, and the pseudoSeldon might be able
to get people to come to a showing.

A cute noise passes 14-0-2\ps.

Motion to commend bananas for being easily freezible and yet edible passes
6-4-3\ps even though KKB is still allergic to them.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
