\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 16 July 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

DWR: Motion to condemn the minutes for horrible typesetting fails 0-4-2\ps.

\bing

\goto{Committee Reports}

\subsection*{Membership}

A random member comes in to return a book; the Skinner signs it in and the
member discusses the failings of the book with the member.  (The book is 
\emph{Destroyer of Worlds} by Niven.

\subsection*{PseudoSeldon}

DWR is going to try to make Seldon showings happen again; it will email
out to keyholders asking for help finding things it wants to show.

\subsection*{Star Chamber}

The library partially flooded and we lost some magazines in bindable condition,
but not too many.  We will hopefully be able to replace them because they
were fairly new.

KR thinks he can help with organizing the magdex data using some software
from the company he works for.  Discussion of this with KKB.

Also, we have a new keyholder, alcor.

\subsection*{Trojan}

The Trojan backlog is getting beaten down with a stick and should be gone
very, very soon again.  Hopefully the gifts office will get letters to
us in less than fourteen months.

\subsection*{Hasselcomm}

I'm going to try to put together a Hasselcomm party sometime soon; an email
will go out with the date soon.

\goto{Old Business}

DWR: We talked to Charles Stross at Pandemonium on Tuesday, and he said he
might be able to come by and do a reading some time in February.

KKB: We should email him.  Also, apparently before writing the Family
Trade series he considered writing, but thought it would be too much
work...

\emph{World War I ended the way it by all rights should have, with British
tanks in Berlin in 1919 so there's no need to have a replay of it.  However
the British Empire is still on the decline, and as we know empires tend tend
to not go softly.  Anyway, we see the rise of British fascism and a world war
between the US and the Empire.  And about twenty years after that two OSS
agents named P.K. Dick and H. Ellison are sent on a mission in 
British-dominated Europe and their first stop is Berlin where they have
to infiltrate a gay club run by a certain former German infantry lance
corporal and his boyfriend Rudy before making their way to Ceylon where
a nefarious British Air Marshal Clarke is building an Orion-drive ship.}

People encouraged him to write it and offered to preorder it, but he
said it would be too much work and too much research.

PW: We got a copy of the proof of the fourth book in the Tiffany Aching 
subseries of Discworld!

DWR: We should post a photocopy of the back cover of \emph{The Fuller
Memorandum} on the door.

\goto{New Business}

DWR: Naomi Novik is coming to Pandemonium tomorrow at 19:00.

KR: Two weeks left for Hugo voting!

\goto{Future Business}

KKB: In the future there will be food.

BJK: In the future there will be less noise coming from that way.

PW: In the future we will take over this entire floor.

BJK: In the future it will be less than 32 degrees outside.

DWR: Motion to set two pi equal to tau.

PW: With bananas?

DWR: Yes.

The Skinner is hungry for bananas.  Passes 3-1-1\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
