\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, February 5, 2009}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to have Bing Crosby sell lime green dragons for reasons only known to the little green men living in BTS's brain: 4-2-14 \ps

Motion ``what?!'': 0-4-11 \ps

Motion to have an assistant to the Onseck whose voice is capable of uttering \textit{\textbf{``BRIAN BLESSED!''}}: 1-1-14 \ps

Note: the Onseck promises to bellow out the ``BRIAN BLESSED'' in the latter motion next meeting.  Also this: \textit{\textbf{``DOOOOOOOOOOOM!''}}

Determinant is 146, all motions pass.

\bing

\goto{Committee Reports}

\subsection*{Pianocomm}

Prentices need to email when they do hours.  We think that the little shoemaker prentices sneak into the library and do work and refuse to tell anyone!  Oh no!  We must stop them, for the safety of the galaxy.  Oh wait, no, we want prentices to do work.  We must deluge pianocomm in emails!  For the safety of the galaxy!  That's better.

\subsection*{Star Chamber}

We have a new Onseck.  I categorically deny this.

The LHE needs to do the secret voodoo rituals of the creation of more reimbursement sheets.  Beware the power of voodoo!

We have a new keyholder, DWR.  The village cheers!

\subsection*{Digicomm}

Amazon took away the TOR books and is plotting to take away one of our keyholders.  Noooooooo!  The village boos!

KR: ``I'm not sure I know anyone who lives at *that* wretched hive of scum and villainy!''

Forgiveness, permission, forgiveness, permission\ldots tomato, tomahto\ldots

KR's blog is covering the other section of digicomm's jurisdiction, the Google Books settlement issues.

\subsection*{Catacomm}

Catacomm will be doing work before Boskone next weekend.  We want to process Galaxy and Asimov's before then.  Contact KKB if you want to help.

\goto{Old Business}

Usual useless wanking.  ALGOL.

\goto{New Business}

KCR's laptop is bigger than yours.  *cue bad rap music*

Motion that Mobcomm not buy any TOR or McMillan books from Amazon until after Amazon relists the TOR and McMillan books passes: 27-3-0 \ps

More Digicomm wanking!  I wonder if that is jhawk wanking or one of his robotic, time-traveling clones.  We shouldn't trust the automata!  We must save human society!  DOWN WITH THE AUTOMATA!  All hail Joe McCarthy!  We must obliterate the automata presence from our midst!  Turn in your neighbors, turn in your friends!

\goto{Future Business}

The New York Times thinks that Amazon will supposedly relist McMillan books on Friday.  Isn't it Friday today?  Hm, they might work in a different space-time continuum than the rest of us...

Gather 'round, kids!  It's Amazon-lookup-time!

BTS: ``They're going alphabetical by next-to-last letter of author's last name, with an extra 'bite me, John' insterted between Y and Scalzi.''

\subsection*{Geography Lessons}

The governator will travel through time and beat people up because California goes bankrupt every few years.

Upper New York State shouldn't suffer for the sins of NYC, and vice versa.  But Philadelphia should suffer for the sins of both.  It's just that special.

Motion to mumble-mumble-mumble paint things yellow mumble.  Brian's really losing his touch.  Vote starts and then is hijacked by a clever thunderbunny crusading for better banana motions.  Damn, the vote restarted.  It passes: 12-BUNNIES!-10 \ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
