\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, February 19, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes for their prognosticatory nature, predicting what would happen a full year in advance and for predicting better version control: 9-0-4 \ps

\goto{Committee Reports}

\subsection*{Pain of Spacecomm}

We received our microfilm and microfiche back from the nice folks in Utah.  Some of it was scanned by amateurs (on our end, oops), but most of the quality is decent.

\subsection*{Bondagecomm}

We have 3 new Bondagecomms!  Bondagecomm will start doing stuff again.  Contact bondagecomm@mit.edu if your committee has something which requires binding, and we'll see what we can do.

Skinner is still safe!  We shall protect ze skinner from the zombies!  BRAINS.

\subsection*{Onseck}

We have lots of office supplies.  We also have de-adhesived, disinfected, cleaned, purged, and organized stashes of office supplies.  The Onseck's CDO (of course the acronym must be in alphabetical order!) is mollified.

\subsection*{Hasslecomm}

Need libcomm cluedump on dexhamster!  Like a zombie needs BRAINS.

\subsection*{Libcomm}

Pinkdex is now really, truly public.  This was way more work than it should have been.

BTS: ``But then the MITSFS subcommittee of the SIPB could just worry about the books and stuff!''

KCR: ``I'm not naming anybody.  I'm not naming anybody!  Yes, I'm talking about Quentin.''

BTS: ``They want to do coding.  We need someone to do [bar]coding.''

\ldots This could work!

\subsection*{Niagaracomm}

Boskone was last weekend.  We got rid of about half of the magazines and our box of strange non-SFnal sketchy books.  Yay!

We missed our chance to give our Seattle component a parting gift from the library of super-seekrit stealth boxes of BOOOOOOOOOOOOOOOOOOKS!

I still want to make a motion about flesh-eating bananas.  Flesh.  Flesh.  FLESH.  FLESH.  FLESH.  FLEEEEEEEEEEEEEEESSSSSSSSSSSSSHHHHHH.

There is another Miles book (by Bujold) coming out soon.  The anti-Bujold committee will protest diligently.  (Also quietly, because the Great and Glorious Skinner likes Bujold.)

\goto{Old Business}

Sunday is the 26th anniversary of MITSFS in this space.  Dude.  Have we bored holes into L-Space yet?

The zombie keyholders from the 1940s will rise up and bore holes into L-Space for us at the next full moon.  For payment in brains, of course.

KCR: ``OH RIGHT!  Because we missed last year but then a year happened.''
KR: ``As years are wont to do.''
KAT: ``... Raise your hand if that was before you were born? ... I thought so.''

ALGOL

\goto{New Business}

There is a Tim Burton version of Alice in Wonderland coming out.  (Side note: they have goth princess clothes available from Disney now!  Weird.)  Amazingly, this will probably be much closer to actual Lewis Carroll than the Disney version.

\goto{Future Business}

In the future there will be flesh-eating bananas!  (\textit{The Onseck is happy now.  The flesh-eating bananas are being discussed, well, at least until KCR goes off into computer-speak about this mysterious entity ``pixels.''  Maybe this is secret zombie code for ``brains.''  Isn't everything secret zombie code for ``brains''?})  There are NOW flesh-eating bananas!  All in favor: 1-1-like a bunch \ps

There will be 4 MITSFS-associated people in an upcoming concert choir concert.  Discussion of what qualifies as ``modern dissonant stuff'' follows.

MITSFS organizational practice-I mean orgawhat?- is so bad that other people have taken to labelling our boxes \textbf{for} us.  Oops.

KR: ``WDS came up with authors for many of them but didn't write them on the spine.''
BTS: ``I bet I can make up authors for them, too!''

Motion to analyze the data files for stegonographic implants: 5-0-8 \ps

Damn is this meeting good for spelling practice.  Did anyone know that I'm a third grader and desperately in need of spelling lessons?  Where did the skinner go?  Skinner\ldots Oh Skinner\ldots  Ah, she went for a dictionary.  Just in time, too.

Motion to breed a banana-eating stegonosaurus: 14-1-4 or 5 or something \ps

Save us from the stegonogranetaograpagraphy!  It's coming for us all!  The Cthulhu cultists chanting their obscene elder texts are right behind it!  Nooo!

Oh wait, no, they're just zombies.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
