\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Casey McNamara, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, 10 September 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes as buccaneery passes 4-0-1 \ps

\goto{Committee Reports}

Kendra knows no such words as Committee or Reports or why they would be conjoined in a sentence.

\subsection*{PseudoAnalogComm} 

Final report coming out soon.

\subsection*{PseudoSeldon}

PseudoSeldon: Seldon showing tonight.

Kendra: I think the Seldon is sick.

PseudoSeldon: Sort of agrees with this assessment.

\subsection*{BiowarfareComm} 

Everybody is sick.

\goto{Old Business}

Term started. Some freshmen arrived.  A few signed up as members.

Google's homepage was unusually volatile this week.

Discussion of Google Instant Search: Kendra thinks it's really creepy.  Paul says it's lowered his typing speed.

Usual motion.  Usual second.  Usual vote.  Usual result.  Usual grumbling at the world.  Usual dictatorship.

\goto{New Business}

The area near PW's house is being burned down.

The guild game Maleficium is happening this weekend.  So is Admiral Hackbar.

We have until 9/16 to put up our poster again.

LCS and the Assassins' Guild also need to put up posters.

\goto{Future Business}

In the future people won't be sick, hopefully.

In the future people will discover the universal vaccine and we won't get sick ever again until the nanoplague wipes us out.

Motion to develop nanobots that turn everything into bananas passes 6-0-1 \ps

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
