\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 4 June 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Motion to punish the Onseck with fire alarms and bananas FAILS 4/8/4\ps.

Minutes read.

\goto{Committee Reports}

\subsection*{PseudoLarvalComm}

Spawning successful.

\subsection*{VanHelsingComm}

I am become meme, destroyer of worlds!
http://i.imgur.com/uSYU6.jpg

\subsection*{PseudoAnalogComm}

New schedule starts on Monday!  Also, more people need to sign up for hours.  And if you haven't yet, you should tell TheftComm as well as PseudoAnalogComm.  And if you're not going to be around, you should tell TheftComm and Skinner.

\goto{Old Business}

ALC: Harry Potter and the Methods of Rationality is awesome.
DWR: Agreed.

REDACTED: Apartments are much cheaper in places that aren't 

\goto{New Business}

KKB: Five keyholders graduated today!

PW: Accuses the LHE of tricking him into new business, or staging a coup, or something.

\goto{Future Business}

ALC: In the future Charles Stross and Naomi Novik will be coming to Pandaemonium Books to talk about new books.

ALC: In the future SpaceX will be launching more neat things into space like they did today!

Discussion of the Falcon 9 rocket and Dragon capsule.  KKB: Why spend money on science when we can spend it on graft?

REDACTED: And now we'll never know if ants can sort tiny screws in space!

And the skinner was driven to percussive behavior with singing.  Later he fled the room.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
