\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, LHE and pseudo-Onseck}
\newcommand{\meetingdate}{Friday, July 30th, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read (while cackling).

Motion to commend last week's minutes for unaccustomed brevity: 7-0-5 \ps

\bing

\goto{Committee Reports}

\subsection*{Star Chamber}

We started purging a large part of reserve.

In other news, we have mold in the reserve magazines.

\ldots Believe it or not, those two statements are unrelated.

Motion to not allow Michael near anything radioactive: 5-4-1 \ps (Guess who voted against with all limbs?)

We have new rates for memberships.

\subsection*{Kvetchcomm}

Naomi Novik was at Pandemonium.

We have a loaned copy of Sanderson's \textit{The Way of Kings} on the new books shelf.  You should read it and review it for Kvetchcomm.

\subsection*{Trojan}

MIT Gifts Office is confused.  That is all.

\goto{Old Business}

It is very sad.  We failed to summon Cthulhu last week.

Ian: Motion to commend the High Priest of that ritual for useful incompetence: 6-0-6 \ps

For the record, the High Priest in question was lemur.

Ian: ``Motion stands.  Or, in this case, chickens.''

We should ask the MIT bio labs for spare eyeballs with which to watch the books.

ALGOL.

\goto{New Business}

It's never too late with Super-Skinner around!  Super-Skinner can just warp time and space!

The wormhole on the wall is out of order.

\goto{Future Business}

In the future, the Skinner will have no tail at all\ldots

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
