\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 18 June 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
010 MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

020 Minutes read.

030 Motion to commend the minutes for having such a strong description
of the valient struggle against the magazines, which was very
true to life passes 6-0-0\ps.

\bing

\goto{Committee Reports}

\subsection*{LarvalComm}

035 Kat says the larva is very cute.  Brian says that she is a ferocious
reader.  Or at least she devours books.

\subsection*{LHE}

040 I think I was on some committees that did something or something.

\subsection*{Star Chamber}

050 We still have a new keyholder---Cathy---but her initials might have
changed to something that I'm not sure I know how to put into
the minutes.

\subsection*{Onseck}

060 The dusting supplies people wanted---and the book repair tape---have mostly
come.

\subsection*{Skinner}

070 The Star Chamber did some work.

\goto{Old Business}

080 NH: Has anyone actually been picking up packages?

090 KKB: People have been picking up packages.  We got ten since Wednesday.

100 Star Chamber in General: We love SAO because we get our mail and
packages in a much more timely manner than we used to.

105 COME FROM 320

110 KKB: Isaac Asimov is still dead.  The magazines are still in California.

120 COME FROM 230

130 KKB: The entirety of ALGOL can be found in a recent version of the minutes
somewhere.

140 COME FROM 300

150 PW: Anyway, I'm going to assume ALGOL.

\goto{New Business}

160 COME FROM 110

170 KKB: We have a new banana-colored thing, which appears to be a knit
banana made by KKB.  It's a practice one for the one the larva will
get eventually, but that one may contain the king of Spain.

180 PW: E3 happened.  There will be a Portal 2 eventually.  The 3DS looks
amusing also.

190 DWR: *general expression of ignorance of computer games*

200 PW: *attempt to explain computer games to DWR*

210 BJK: There is a rupture in the boundary of the library.

220 PW: I should fix that.

230 People were bored and there was much discussion of Athena usernames.

240 COME FROM 130

250 KKB: There is a book entitled \emph{Kid Versus Squid}

260 PW: I wonder if that will be as interesting as the title sounds?

270 KKB: *dramatically reads the back cover*  There is a princess of the Lost
City of Atlantis.  So where's the giant squid?

280 DWR: Wonders if the witch is a giant squid.

290 PW: There's some stuff on my gavel block.

300 KKB: I wondered when you'd notice.  Definitely not a coup.

\goto{Future Business}

310 COME FROM 100

320 BJK: In the future W20 mail will continue to suck.

330 COME FROM 150

340 DWR: In the future the finale of the current season of Doctor Who will start tomorrow.

350 KKB: In the future we will eventually convince the Skinner that it is
future business.

360 NH: Something that definitely was not a motion.

370 Skinner: It chickens.

380 NH: But I didn't make a motion.

390 Skinner: *calls another vote*  The absense of a motion passes 4-0-4\ps.

400 NH and Skinner: *look over onseck's shoulder to see what they just
voted on*

410 Motion to have more motions chickens 0-3-1\ps.

420 KKB: Motion to have more motions fails by Skinnerial decree. 

430 KKB: Motion to have more motions fails by Skinnerial decree.

440 BJK: Motion to enter the part of the meeting where everyone shelves
three books passes 4-4-0\ps.

\bing
\noindent
450 Meeting adjourned, 68.4 Ksec SST.

460 PLEASE GIVE UP
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
