\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Brian Sniffen, pseudoOnseck and Onseck Edemeritus}
\newcommand{\meetingdate}{Friday, DAY MONTH 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

\subsection*{Theftcomm}

We have a new TIF.  You may have noticed.

\subsection*{Star Chamber}

We had Inventory.  You may have noticed.

It's Mystery Hunt this weekend.  Also awesome, but few are here.

\goto{Old Business}

Inventory happened.  Libcomm's head did not explode.  Two Libcomms is
helpful for this.  It might be more helpful if at least one of them slept.

Game night was awesome.

Our Onseck, Sueshep, has left for a term.  We miss her and wish her well.

ALGOL.  Usual Mammoth.  Mamoths are new!  But now usual.

\goto{New Business}

Wolfram Alpha now has a feature for calculating the results of MITSFS meeting
minutes:

http://www.wolframalpha.com/input/?i=det({{9,+3,+5},+{-6,+-9,+7},+{-1,+-8,+1}}) 

A brief interlude mocks New Kind of Science.

"Boris Vallejo is commended for startling realism in his pictures, as
well as more yardage of clothing than ever before seen" chickens 6-6-6+Spehn

Miler motion inspired by Vallego-Kincade partnership and by
*Bottle-fill Cartridge Converters of Gor* fails 4-1-8+Spehn

\goto{Future Business}

Hasslecomm party tomorrow: MKR explains what Hasslecomm does, and how
to help.  

Miller motion passes 14-2-0+Spehn.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
