\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, LHE and pseudoOnseck}
\newcommand{\meetingdate}{Friday, August 20, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion ``Hi, I'm EpicWizard!'': 4-0-4 \ps

\bing

\goto{Committee Reports}

\subsection*{Seldon}

We're showing Galaxy Quest tonight at 21:00 in 2-105.

\subsection*{Star Chamber}

Boxes should be gone into storage by next week.

We have a new prentice -- yay!

\subsection*{hBarcomm}

Skinner is hosed.  Skinner swears he'll send email after the game he's running tomorrow.

\subsection*{Random Committees}

Did work.

\goto{Old Business}

Motion that someone recommend a fifth book EpicWizard can take from the For Sale box succeeds due to reality.

Motion ``Green!'': 7-1-1 \ps

ALGOL.  Usual lack of enthusiasm.

\goto{New Business}

The Skinner is running a game tomorrow.  Eep.

New frosh are here already.  Oh no!

\goto{Future Business}

In the future it will be Rush.  And there will be more space for people to sit in the library at the meetings.

A rogue Zandra appears!

In the future, the Skinner will have a jetpack.  However, he doesn't want to \textit{be} a jetpack.  Strange.

Motion to send a probe through space and time to seek a habitable planet with climate around the equator such that banana plantations could be grown there: 10-0-1 \ps

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
