\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kevin Riggle, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, April 9, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Matrix vote.  ``No'' (2-8-5\ps), ``yes'' (6-5-7\ps), ``maybe'' (1-1-19\ps).  Determinant is -674, all motions fail.

\bing

\goto{Committee Reports}

There's a midway tomorrow.  People should show up.

Script-writing frenzy during NH's hours (3-5 tomorrow).

Oook.  (PW did work on the new web site.  It's not ready yet.)

DWR finally learned how to Hasslecomm.

Jake is \emph{not} getting Hasslecomm work done during

Nth Fist of the Republic:  We won't be invading HRSFA at 7p on April 18.  (Library: ``We won't?'' \ldots ``Oh.'')  Don't meet at the Library at 6p.  Don't wear pirate outfits or bring Nerf weaponry.

\goto{Old Business}

KR is going day-after-tomorrow to deliver the DVDs to NESFA.

\goto{New Business}

It's CPW!  There are prefrosh!

Prefrosh don't understand that you shouldn't stand still and clot the Infinite.

Deep-fried LN2 ice cream works!

Hugo nominees are out.

\goto{Future Business}

In the future, the prefrosh will leave.  Some of them may come back as frosh.

In the future, the Skinner thinks JHawk will grow wings and fly away.

In the future, LSC will be showing a bunch of trailers.  In the slightly further future, LSC will be showing Avatar (2-D).

In the future, there will be more new Doctor Who.

Motion to preemptively condemn the destruction of the weapons factories of Villengard and their replacement with a banana grove passes 9-0-3\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
