\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck and Anti-Zombie Gatling Pea}
\newcommand{\meetingdate}{Friday, April 23, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to surround the minutes with Wall-Nuts for their own safety: 5-0-10 \ps

\bing

\goto{Committee Reports}

\subsection*{Pain of Spacecomm}

We got the invoice from scanning and forwarded it on.  Someone else will pay for the project!

\subsection*{Titanic Tetriscomm}

The CAC took the tetris pieces outside the library and didn't charge us for them.

Noooo!  Not the trident piece!

\subsection*{Picniccomm}

Elections in 2 weeks, picnic the day after.  Sign up on the door.

The picnic will be awesome!  You should come!

\subsection*{Bluebellcomm}

Did many overflow boxes worth of work, yay.

\subsection*{Magnificent Iron Titanium and Steel Fist of the Schism}

We attacked HRSFA.  It is unclear if we saved the galaxy or not; we'll have to find out next year when they come attack us *ahem* I mean definitely not attack us.

The top-secret weapon succeeded at surprising HRSFA and being awesomely schtickful but needs some repairs.  The MITSFS will then have a pirate chest for books!  Our treasures!

We then ate them^H^H^H ate dinner with them.

Motion to build the next top-secret weapon out of sapient pearwood: 21-0-4 \ps

\subsection*{Niagaracomm}

We offloaded an entire box of books on the unsuspecting HRSFA as part of the attack.  Muahaha.  Brains.  We now have a brand new shiny For Sale box with new tasty brains.

\subsection*{Trojan}

The Gifts Office got back to us; all donation letters are sent and not my problem except two.

Motion to compensate Brian Leibowitz for his donation with a canticle for Walter Miller: 2-2-2 \ps

AND SPEHN CASTS THE DECIDING VOTE!

\goto{Old Business}

We have no need for the past.  We only have need for BRAAAINS.

ALGOL

\goto{New Business}

Evil Dead the Musical is running this weekend.  They have a chainsaw and zombies!  ZOMGIES!

PW recommends not reading the last 2 pages of the new Dresden Files book until the next one comes out.

Abby: ``Oh look, it's a meeting.''

\goto{Future Business}

PW et al will be going as Ring Wraiths to Ring Delivery.

Motion to surround the minutes with bananas, the natural predator of zombies, for their own protection: 12-0-12 \textbf{DAMMIT} um no 11 \ps

Don't you love skinnerial math?  Math is done by BRAAAINS.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
