\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck and Resident Pirate}
\newcommand{\meetingdate}{Friday, February 26, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

Arg, ye mateys, these be the MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion ``sharply leftwards'': 11-5-4 \ps

DAV: ``But I'm right-handed!''

\goto{Committee Reports}

\subsection*{Piratecomm}

Arrrrrg.  We arrrrg a pirate today.

\subsection*{Theftcomm}

Theftcomm made a new TIF and stole lots of hours from all of the new keyholders.  Oops.  This will be fixed this weekend.  Well, it \textit{is} Theftcomm.

\subsection*{Star Chamber}

We have two new keyholders since last meeting!  Welcome, BTS (again) and JAJ.

\subsection*{Panthercomm}

Panthercomm notes that we are in fact out of panthers and requests tha the Onseck order some of the free samples.

\goto{Old Business}

Motion to commend the library for creating immense amounts of space in *waves in a general direction*: 19-1-3 \ps

We got Viagara, Rogaine, and cell phones instead of jetpacks, flying cars, and AI.  Yet people seem to be happy.  Strange.  Discussion of flying cars versus walking on water ensues.

Word of the Day from Our Great And Glorious Skinner: ``LIQUID!''

The photographer (from two weeks ago, our pet poitraiteur) made prints for us!  Arg, the mateys be gettin' new pictures now.

\textit{The sleek black train steaming across the countryside carrying the thoughts of the instrumentality goes spiralling off the rail and up into the sky towards the nether dimensions.  I watch it sail off, acting more like a feather in a strong wind than a train of iron and steel.}

Motion to commend Canada for successfully hosting the Olympics and wonder which of the other states will do so next: 4-9-14 \ps

All of the McMillan books have now been relisted.  Yup, just this past week.

\textit{The train is still tossing and spinning in the stratosphere.}

\ldots

\textit{Still spinning, still floating.}

\ldots

\textit{Still.}

\ldots

ALGOL.  Usual apathy.  No one complains with any verve anymore.

\goto{New Business}

The movie version of ``Percy Jackson and the Olympians'' just opened.  However, we should wait for a movie made by people who have actually read the Greek myths.

\textit{I think the train has finally descended to earth again.  It might stay for a while.}

Hey kids!  Things that have happened since last meeting are what belong in New Business.  Things even slightly in the future should be in Future Business.  End lesson.

We got the new Jhereg and Malazan books in!  Commence the fighting over them!

BTS: ``A sargeant in motion outranks a lieutenant without a clue.''

\goto{Future Business}

There is a cyborg dance performance at the Media Lab this weekend.

David Tennant for cauldron lighter in 2012!

Dr. Who?  Fan service?  Nah.

KKB: ``Disclaimer: this may or may not have anything to do with the motion I'm typing into the minutes.''

Motion ``which one?'': I forgot - 19 \ps

Science will fulfill popular demands when it can make people live forever and prevent weight gain.

Timothy: ``I do \textbf{not} want to see Boston drivers after they have cars which can fly!  9/11 will look like just another car accident!''

Arrg.  I have a motion, mateys.  Arrg arrg arrrrrg let's go to eat the grog and bananas, mateys.  Arrrrg: ``\textbf{ARG!}'' - ninja - I think it fails quoth the Skinner \ps

DAV: ``So the third vote was for the robots?''
BTS: ``Don't forget the monkeys!''

THE SKINNER HAS NO TAIL AT ALL\ldots

Man, we got through almost two verses!

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
