\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, May 7, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to get an Onseck a time-turner set to about 20\% to allow her to comprehend the motions from the instrumentality: 11-1-4 \ps

\bing

\goto{Committee Reports}

\subsection*{Picniccomm}

Elections are in a few minutes.  If you didn't already know that, there's probably no hope for you.

Picnic tomorrow!  We got Nimbus a really big watermelon so hopefully it won't rain PLEASE PLEASE PLEASE!  Last year's watermelon was insufficiently virgin.

All other committees have been decreed (Skinnerially) to be unimportant.

\goto{Old Business}

Motion to form a new shorthand specifically for entering BTS's motions into the minutes effectively: 24-4-3 \ps

The last ever green dragon comes and absconds with the Onseck's computer.  Oooh, shiiiny.

Motion for there to be temptation to voice-record BTS: 10-6-5 \ps

Motion to parse everything she said after 'motion' as a motion: 3-2-12 \ps

Motion to have no recursive motions: 7-2-4 \ps

Determinant is 248, all motions pass.

ALGOL DAMMIT DURING THE ONSECK CALCULATING THE MATRIX VOTE I HATE YOU ALL.

\goto{New Business}

A comment for the preservation of lives of keyholders: we would like to remind those present that Sunday is Mothers Day and those who wish to survive until next Mother's Day should call their maternal units.

Elections!

Nominees for Onseck: lemur, all orders of higher primates, Jean Tannen, Lukas Fehrwight, lemur's hair, lemur's hat, all the blankets lemur is bringing to the picnic, sueshep's muppet, a voice recorder, mini-me (Margaret's laptop), Kendra's violin, Mary Chung's

And the winner is...lemur

Nominees for LHE: kkb, Lukas Fehrwight, Locke Lamora, Kvothe, Bast, The Egyptian Cat Goddess, kittens, Daleks, Cybermen, Neitzche, the Onseck's spellchecker (gee, thanks, Brian, I hate you too <3), Descartes, the horse, Philosopher's drinking song, dead composer's song, EtOH

And the winner is...kkb

Nominees for Vice: Naomi, jesseaj

And the winner is...Naomi

Nominees for President: pweaver, the office of Skinner, recursive Nominations, MITSO program, Spock (the only logical choice), John Stewart, the missing H, the letter H, the number H, ``this program was brought to you by the letter H'', all possible permutations of Jesus (individually), string theory, the Doctor (11th), Locke Lamora, miscellaneous transactions

And the winner is...pweaver

And the Skinner is...pweaver

\goto{Future Business}

In the future, we will all go deaf and Margaret will have a job.  In the future, there will be a new Doctor Who.

You're doing \textit{what} to the binding of our shiny new proof copy?

Oh my goodness.  Is that book published in Sans Serif?

Motion to not have books published in Sans Serif fonts in the future: 14-3-5 \ps

Motions to buy the author a complete set of Serifs: 10-7-4 \ps

Motion to have a third motion: 3-6-9 \ps

Determinant is 520, all motions pass.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
