\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, Onseck}
\newcommand{\meetingdate}{Friday, April 2, 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

No...?: 6-0-1 \ps

\bing

\goto{Committee Reports}

\subsection*{hBarcomm}
CPW is next week.  We need helpers for the Midway (Saturday 1 - 3 PM) and 
undergrads to show up to the meeting.

\subsection*{Star Chamber}
We got a new shiny this week and keep it under lock and key and guarded by a 
dragon and surrounded by a firey pit of lava.

\subsection*{Catacomm}
New mags!

\subsection*{Bluebellcomm}
Bluebellcomm needs to be less lame and keep up with the Cohen processing.  Lots
was done this week; more needs to be done.

\subsection*{Frutstrated Authorcomm}

Time warp back into the meeting!  \textit{Let's do the time warp again...}

Script frenzy write-ins will be held in the library during NH's hours 4/10 and
4/17.

\goto{Old Business}

Brian Leibowitz stopped by the library yesterday.

We can do \textbf{MATH}.

April Fools being National Census Day is just asking for it.

KR: ``What do you mean that it is not executable, I just executed it!''

Usual lack of second, usual Nap of the Onseck, usual nonvote, usual result.

\goto{New Business}

We have no present.  We also have no presents.  The Onseck likes presents.

\goto{Bionics Business}

MKR: My my, aren't we obsessive today.

National Geographic did a recent article of the current state of research.

In the future, we will implant computers where our kidneys used to be.

Mysterious Person: It is possible that someone who used to be on this wall
will read the minutes and recognize me.

[insert a detailed description of Mysterious Person here]

Timothy: I would definitely get \textit{that} implanted.

KR: What, you don't want a hunk of lead and lithium with the power density of
dynamite inside you?

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST, \textbf{BECAUSE I'M BORED} quoth the Skinner.

Ah ha!  We have discovered another way to end the meeting!

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
