\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 19 November 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes for unusual cuteness passes 4-0-2\ps.

\bing

\goto{Committee Reports}

\subsection*{Pianocomm}

Pianocomm has resumed recording prentice hours now that NH has
her computer back with the spreadsheet on it.

\subsection*{Nanocomm}

Nanocomm will hold one more write-in, tomorrow.

\subsection*{Star Chamber}

We got most of the books we were looking for.

The library will be closed on Thanksgiving because the Student
Center will be closed on Thanksgiving.

The entire Star Chamber is present for the meeting.  This is the third
time we've managed it in a row.

Motion to commend the universe for not collapsing in surprise
chickens 2-4-4\ps.

\subsection*{hBarcomm}

We now have a key to access our poster!

\goto{Old Business}

In the past emails were sent out about Inventory.  It's 8 January.
People should remember to sign up for hours.

The comic books are still somewhere.  Someone is still skiing somewhere.
Someone may still be dead.  Anyway, ALGOL!

\goto{New Business}

In the present, KKB is too hosed to read.  In the present, KKB is reading
anyway.

In the present, NH is reading horrifying pick-up lines for otherworldly
beings aloud from a book that the Onseck can't quite read the title of,
and isn't sure it would be wise to try to.

\goto{Future Business}

In the future there will be a movie called \emph{Cowboys and Aliens}
and from the trailer it looks neat.

DWR found a book in Baker Engineering Library that seems to have been
published next year.

In the future it will be Thanksgiving.  And then it will be the day after
Thanksgiving and we will still have a meeting!

Motion to feed the Skinner bananas passes 4-0-3\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
