\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 5 November 2010}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to let all Momos and Appas vote with all their limbs
PASSES 6-5-1\ps.

\bing

\goto{Committee Reports}

\subsection*{Nanocomm}

First write-in tomorrow!

\subsection*{Bendingcomm}

So many cute fuzzy things!  And they have so many votes!
And the prentice is wrong about relative awesomeness of
Appa and Momo.

\subsection*{Star Chamber}

Mail from Boskone.  It came to lemur's address by accident.

ASA meeting stuff.  We have various things coming up to deal with, but
they will update us when they actually schedule them.

\subsection*{Star Chamber Press Gang}

Prentices did work.  But there is much more to do.

\subsection*{Bendingcomm}

There are lots of cute things in the library!  Also, we should get
someone to write a Wikipedia article on Momo, because it's sad that
Appa has one but Momo doesn't.

\subsection*{Hasselcomm}

Prentices should do work!

\subsection*{Bluebellcomm}

Prentices should do work!

\subsection*{Trojan}

Prentices should do work!

\goto{Old Business}

In the past prentices did work.

In the past classes were hosing, which has unfortunate
implication on the present.

Motion to condemn classes for taking us away from science fiction 
passes 47-0-4\ps.

Motion to come up with a plan to do this in a feasible manner.
17-4-7\ps

Motion to condemn the prentice for thinking we do things in
a feasible manner.
16-11-8\ps

Motion to annoy the Onseck!
4-18-3\ps

And the determinent is -166 and all motions FAIL!

Motion to condemn math for confusing the Skinner does something 4-8-18\ps.

LHE: It's okay to be confused, Skinner.  Just hand me the gavel and
everything will be okay. 

Skinner: That's fine with me, as long as the delta-V is high enough.
Relative to you.

Accidental motion to wait a second please fails 7-18-2\ps.

ALGOL


\goto{New Business}

This weekend is the Microsoft College Puzzle Challenge!

This weekend we get an extra hour!  We stole it from last spring!

Members don't understand daylight savings time.

Motion to slip narcotics into people's drinks to make them
get extra sleep.
9-15-4\ps

Motion to condemn the prentice for bad ideas.
7-10-3\ps

Motion to increase the cuteness of the library.
27-7-16\ps

And the determinant is 8 and all mostions PASS!


\goto{Future Business}

In the future the last launch of the Space Transportation
System will be in February.

In the future there will be a Falcon Nine!  And it will be
partly reusable!

Discussion of space planes and how they have been cancelled.

Silly prentice proposes pseudo-physics drive.  Citation needed.

Motion to build a space elevator chickens because no one voted, ever.

Stupid wanking about whether it would be too long a trip to the top.

We can't seem to find out how much it cost to ship things across the
Atlantic in the 1800s.

Motion to appoint a committee to farm cabbages and bananas to feed
our cute new friends passes number to smaller number to number that
is smaller even when Spehn is added.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
