\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 7, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1712. The minutes were read and approved as usual.

\goto{Committee Reports}

We have 117.68 at 41 members in the treasury, reported Deanne Gross.

Theftcomm: no report.

Libcomm: there are as of now no shelves, therefore no report.

Moocomm: Duff says we can get it. (It being The Time Machine.) Also people and others are looking into The Shape of Things to Come.

The Special Committee to Write a Letter to L. Spraque de Camp Asking Him to Come If It Won't Cost Us Too Much (SCWLLSdCAHCIIWCUTM): no report.

Knockomm: Cohen's address has been found. We still have no sounding board.

War Council: failure- Holland was not seen by Court. Success- we have the Little Theatre on 21 October from 5:00 to 7:30.

Psico: there was a null-meeting and a null-report. Someone on Psico spoke for Easton and asked for intelligent book reports pro and con on books on psychic phenomena. Great laughter was heard at the word "intelligent."

\goto{Old Business}

We will show The Time Machine during reading period.

Humer found out that gradhouse (del-house) charges 3.00 for a roast beef dinner. Humer refused to wait on us.

Kentaylor went to Smorgasbord to steal a menu. They cost from 1.35 to 2.00 and are at 19 Providence, open from 1130 to 2100.

No box came to Burton House. Humer said one did. HUMER LIED! Lovecraft did not come!

\goto{New Business}

Psico wants comments on the Dean Drive pro and con. Many con comments were given to them. Psico tried to defame the RRS but as the Noble Secretary is President of the RRS nothing of the sort could be done.

F. Norwood, F. Cocks, and B. Austin.

MSP (Duff) to set up a provisional committee to look into the Dean Drive. 10-4-i. The above will.

MSD (Duff) to millerate at 1733, 9-12.

Pat just came in with a stolen poster.

We should invite Dr. Asimov to the smoker. Sarill will see Asimov. Lewis made an excellent suggestion.

MST (Norwood) that a committee to discuss science fiction be set up.

MSP (Humer) to table motion. 14-5.

It was felt by the Society that this has nothing whatsoever to do with our business.

MSP (Harrison) to Gafiate at 1744, 15-6.

\vspace{12pt}

\centerline{The whole ghastly mess by}
\centerline{ARLewis, Secretary}

\end{document}