\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 9, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1712. The minutes were read and approved.

\goto{Committee Reports}

The treasurer say we have 1 new member and 100 dollars.

Moocomm: Has Duff arrived yet? No! Well, he saw Perry this week. We have TWO, *2* Roadrunner cartoons.

Libcomm: Humer purchased 3 Prophetic Novels of H.G. Wells. The others have been ordered. If subscription: 3.00. Wall of Serpents: 1.20. Drunkard's Walk: 1.20. And tape for covers. Coop number is 44598. Humer read review of sf? movie Village of the Damned (Midwich Cuckoos) from the NY Times. No one showed up Wednesday.

Theftcomm: Ravin wants to resign but he can't until New Business. No report.

War Council: Bookase expedition- failure, i.e. furniture exchange closed.

Psico: absent.

\goto{Old Business}

IES meeting tomorrow.

Rod Serling will arrive here 23rd December.

Sarill cannot attend meetings so he is building a citizen's band transmitter.

No word yet from DeCamp.

\goto{New Business}

Ravin resigned.

MSP (Humer) to accept Ravin's resignation with many thanks. 12-1-2.

Skinner appoints a new Theftcomm: prime- Sandy Lensch, second- Bill Osten.

Ravin wants to be Editor- he is! Ravin spracht: nevermore!!! Write reviews, IES junk, fandoms send to Burton 413C.

Skinner: picture frames bought and pictures mounted. We have a new lock.

Library: Saturday 2-5 Whealton, Sunday 2-5 Columb, Wednesday 7-9 Lensch.

MSP (Lewis) to millerate at 1750, 14-2.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}