\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 2, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1709 by L. Court Skinner. Minutes were read and approved.

\goto{Committee Reports}

Treasurer: with 6 new members and the 8.37 we now have 99.90 in the treasury.

Libcomm: Invaders from the Infinite will be here soon- beware!!! One more bookovered. Donations: 2 from Pat, n from Steve.

Moocomm: no report- why is Kentaylor not a member?

Theftcomm: 4 posters.

War Council: no report.

\goto{Old Business}

The secretary read a section from the minutes of 15 April 1960 in which the Libcomm chair was requested to buy 3 Dover editions of H.G. Wells works. Since they have not been bought Humer was queried; after much acrimony he agreed to purchase them.

Lovecraft? Well, you know about him.

Members who want reimbursement for funds spent on refreshments should speak up (i.e. tell Deanne).

Cocks, editor of the JMITSFS, wishes to resign. He did.

The Library will be open 2-5 on Saturday and Sunday and 7-9 Wednesday.

Volunteers: general- Rudolph, Whealton, Colomb; Wed- Sandy Lensch; Sat/Sun- Rudolph, Norwood, Ravin; general coolies- Lewis, Skinner, Humer.

MSP (Rudolph) that keys be given out, 1 per each living (i.e. residence) group. 13-6.

ASP (Lewis) that the President choose the people who will get keys. 16-1.

Krupp asked why Gernsback sent mags to him. He was told why.

\goto{New Business}

Please do not eat the Ace Double Books.

A general discussion about coeds was held.

Some freshmen became obnoxious and made fools of themselves. The Noble Sec and Theftprime won the field.

Books should only be kept out for 2 weeks. Please do not take out more than 8 books. Stamp all books on the inside cover and page 85.

A discussion on bookases was held. Salient points: 1) We need them. 2) We don't have them. Decisions: Uhrmacker will look into this, Whealton will be his coolie, "Noisy" will see the Salvation Army.

We need picture frames for the pictures.

There will be an IES meeting 10 Dec.

Keys: Franklin, Baker 538; Gross, Bexley (i.e. Conner) 202; Lewis, Conner 410; Skinner, Burton 433; Taylor, Munroe 309.

MSP (Lewis) at 1803, 18-7.

\vspace{12pt}

\centerline{Done by}
\centerline{ARLewis, Secretary}

\end{document}