\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 18, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting emerged from order into chaos at 1710. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

Joessef, the Lord High Embezzler stated: 1) bankruptcy proceedings have begun; 2) seriously, we had 400.88. Good: 2.00, dues. Bad: 3.08, The Tech (boo hiss); 0.90, poster board; 0.39, new notebook. Grand total: 398.51; 3) he cannot find the Finance Board to tender the report as requested of us by they which be nonexistent.

Theftcomm: three posters stolen.

Libcomm: Vergeltungsflotte should move against Lintner for poster theft. Buy books, yes, yes: H.G. Wells at 3.95 each. No one has come up to Humer's room (511b Burton) to cover books. Ken Taylor was volunteered.

War Council: no report.

Moocomm: we have a bill for 52 dollars from the Bursar's office in re: projectionist fees.

\goto{Old Business}

Skinner failed in his assigned task, i.e. we still have no room.

The APO Carnival was discussed by Humer.

An attempt to defame the Noble Secretary was made by raking up the Clement letter. Those of you who have read the earlier volumes in this series remember how it seemed that the Noble Secretary would be disgraced in The Asimov Letter, or Norm Humer Strikes Out, but how he valiantly came through and triumphed in the end. Well, will the villains triumph? Will good lose out? No! The Noble Secretary will triumph again. Meanwhile, back at the meeting...

\goto{New Business}

Banquomm: no results as no one wishes to chair Banquomm.

MSW (Humer, Taylor) that 9.25 be appropriated to buy 3 Dover books and Knight's In Search of Wonder.

Discussion about books and Humer followed.

A letter from the Social Beaver was read. Joe read what is going to be in it next year about us (Boskone) amid jeers and derision. It passed anyway.

MSD (Lewis, Taylor) at 1739, 4-6.

A slight discussion of sf occurred but was quickly stopped by alert members.

MSP (Ravin), 8-2.

\vspace{12pt}

\centerline{Submitted by}
\centerline{ARLewis, Secretary}

\end{document}