\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 4, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1711 by Skinner. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

The treasury paid 2 dollars to Spiro and took in 2 dollars from new members. We have 101.79 on hand.

Theftcomm: four posters were put up.

Libcomm: the Library opened last Sunday. Pocketbooks are arranged on shelves and may be checked out. We have 490 pocketbooks. The Techshow trash has been moved out from our room. We now have 3 chairs and a desk. The library will be open from 2-4 PM on Saturday and Sunday. The janitor has been told not to open the library for anyone. Some of the empty soda bottles have been removed. There are many hardcover books missing.

War Council: Jerry Winston placed the check in the Institute mail. It will arrive next century.

Knockomm: no report.

A new Cock is being gotten for the inner door.

Moocomm: no report.

\goto{Old Business}

A freshman reported on sf discussions in Walker Memorial (50). One discussion puts MIT back in the 1400s.

MSD (Norwood) to form a committee to discuss sf at Walker after the meetings. 5-10.

Lovecraft has not come yet.

\goto{New Business}

Some IES stuff (i.e. Logic at Work) was put before the Society.

Norwood made a fool of himself.

MSP (P. Morris) to miller at 1741, 12-0!!!

8 minutes later Sarill arrived. DeCamp cannot come the 11th. Everything is vague.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}