\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 14, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1706 by L. Court Skinner. The minutes were read and approved.

\goto{Committee Reports}

The Treasury now holds 122.68, saith ye Keeper of Monies. The Coop refund has not yet been collected.

Theftcomm: notices of the smoker have been sent to book calendars.

Libcomm: Holland was seen- no shelves are forthcoming. The microfilm is home in 50-024.

Knockomm: still no word. Duff has not yet given Skinner Cohen's address.

Moocomm: no report.

Psico: books on psychic phenomena are under 133.07 in the Dewey Decimal System. A meeting may be held at 1300 Sunday in the Baker Lounge. The Plant Still Lives!!!

Special Committee to Write to DeCamp etc.: no report.

War Council: Holland was seen. He will not introduce Gernsback. A letter from Gernsback was read. We will meet in the lobby of Kresge. Asimov will be surrounded by coeds.

Ravin became obnoxious.

\goto{Old Business}

Shape of Things to Come is still doubtful. Metropolis may be gotten.

Sarill says Ed Emsh produces art (not sex) films.

MSP (Humer) that Sarill try to get these films for us. (17+i)-0-0.

ASD (Parlette) that Sarill be given funds and authority for this.

Lovecraft has not come yet.

\goto{New Business}

Ye Shelvef Queftion: 6 shelves, 6'x4' = 6 dollars. Arrgh. Sarill did not check with the lumber company.

Library will be closed until we have shelves.

Humer wants 25 dollars for shelves. Kentaylor says that he can get us a bookkase FREE!!!

Dinner: The Smorgasbord has no space for a group. We will eat in grad house (15-20 people).

Sarill says he may be able to get the films of some Twilight Zone shows for us.

Meeting adjourned at 1750 by standing vote.

\vspace{12pt}

\centerline{ARLewis, Secretary}

\end{document}