\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 8, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1710. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

The L.H.E. reports that we had 398.51 on hand. In: 6.00, IF subscription; 1.50, dues. Out: 52.00, projectionist fee; 60.00, Wenker for books. On hand: 294.01.

Theftcomm: no report.

Libcomm: not here.

War Council: no report.

Banqucomm: self-appointed chairman Joe Cohen investigated 6 restaurants as to menus and prices. The recommended date is 6 May at 6:30 PM. Probable guest Clement and/or Abernathy. Also, the Society should contribute 2 dollars/member.

Carnalcomm: Carnaval is close at hand; Theftcomm should make posters for the Carnaval.

Libcomm arrived, no report.

\goto{Old Business}

Lewis reports that Hal Clement will be at the meeting of 29 April.

Cohen: banquet 6 May 1960. Vote on restaurants: Window Shop- 5, Purcell's- 0, Union Oyster House- 6.

MSP (Cohen) that the Society defray the cost of the meal at the rate of 1 dollar/member. 7-6. Tentatively 20 people will attend.

\goto{New Business}

Sarill was here. He had been absent from the last few meetings due to I. Sickness: a. flu, asian (2), b. cold (with associated sore throat); II. Busy: a. fanzines (3).

Sarill met Shag (J.M. Graetz) who will drop by something.

Also, Original SF, Future SF, and Fantastic Universe have folded. IF may have folded or money may have been sent to the old publisher.

A new pseudo-sadistic fantasy magazine, Fear, exists. A new E.E. Smith (PhD, L2) will be published soon.

Humer: 2 new Conan fans exist in the Society, Lewis and Silverstein.

MSP (Lewis) at 1745, 7-3.

\vspace{12pt}

\centerline{ARLewis, Secretary}

\end{document}