\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 11, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1708 by Skinner in the Spofford Room. The minutes of the previous meeting were read and approved as usual.

\goto{Committee Reports}

There was no treasurer's report.

Theftcomm: four posters up and down.

Libcomm: some junk from the sf book club, inc. came. As per last year's discussions it was junked. Two books have been covered, to wit: The Day Index and The Incomplete Enchanter.

Moocomm: no report.

Knockomm: both the address and Joe Cohen have been found.

War Council: the 8.24 has not yet arrived.

\goto{Old Business}

Lovecraft has not yet arrived. Maybe in a year or so we should write to the University of Detroit.

A tape was attempted to be played- it wasn't.

\goto{New Business}

Both Humer and Ravin made fools of themselves individually.

The idea of different types of meetings was discussed.

MSP (Ravin) that Bexley Hall be designated Wing Zero of Conner Hall. 14-2.

MSP (Morris) to Millerate. 14-4.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\begin{center}

MITSFS Meeting Minutes

Friday, November 11, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The second meeting of 11 November was called to order at 2337 by L. Court Skinner in Room 202 of Bexley (Conner) Hall. Cookies were served. The minutes of the meeting of 22 April 1960 were read and heartily approved.

\goto{Committee Reports}

Treasurer's Report: some money was received and some spent.

Theftcomm: no posters were made for the meeting.

Libcomm: the library has not been open since the last meeting.

War Council: has not seen Holland since the last meeting.

\goto{Old Business}

The library thefts were discussed.

Lovecraft came and rotted in the fireplace.

\goto{New Business}

MSP (Ravin) to reimburse the coeds for the expenses of refreshments. 6-0-2.

MSP (Lewis) that Tablecomm be allowed to discuss sf at Walker at 1700 on Fridays. 6-2.

We should title our publication "The {\bf ASTOUNDING} Journal of the MIT {\bf SCIENCE FICTION} Society."

MSPU (Humer) to millerate at 2400.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}