\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 28, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1709. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

The Treasurer reported that we have one new member and 101.79 in the treasury. Carnival money is not here yet. The Coop refund came to 3.06. Our address is Box 617- Burton House.

Theftcomm: no report- no posters were put up this week.

Libcomm: Pickabookbooks sent us a notice that Invaders from the Infinite will be delayed and Valley of Serpents will be sent in its place. Harrison reported that there are now shelves in the Library. Humer says the library will be open from 2-5 on Sunday.

Warcouncil: the 8.37 check is on the way from Winston.

Knockomm: no report.

Moocomm: we have film- Time Machine. No word yet on Shape of Things to Come.

\goto{Old Business}

Lovecraft has not come yet.

Lewis will contact TechShow about their junk in the Library.

Sarill got a letter from DeCamp. He will try to come to the meeting 11 November. He will not charge for this.

Rod Serling will be here a week before Xmas- he will try to make it with 3 Twilight Zone films.

A meeting of the IES will be held at the Hotel Touraine in the Adams Room at 7:00 PM on 19 November 1960. Hal Clement will speak.

Norwood made a fool of himself.

\goto{New Business}

The names and addresses of the members will be sent to Mr. Gernsback so that he can send copies of Forecast 1961 to us.

The Gernsback suggestion of publishing a magazine was bandied about. Norwood was appointed publisher and chief coolie. About 13 people seemed interested in the idea.

MSP (Duff) to millerate. 13-3.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}