\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 18, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1712 by Skinner as usual. The minutes were read and approved.

\goto{Committee Reports}

Treasurer saith: we have four new members, 1 alumni member. Flux out: 4.40, sounding board; 6.25, membership cards; 0.85, ASF; 9.30, pictures.

Libcomm: there are donations. The Galaxy Reader has been reclaimed. The Mislaid Charm has been covered.

Theftcomm: no posters.

Knockomm: Cohen got the sounding board. FLUSH KNOCKOMM!!!

Moocomm: nothing much new. LSC is showing a free movie Wednesday night, i.e. Journey to the Center of the Earth. It was suggested that the Moocomm chair join the Society.

Warcouncil: check for 8.37 has finally come after much trouble.

\goto{Old Business}

A letter from the IES was read.

IBMembership lists were distributed.

A note from Mr. Gernsback was read. Frank Kosdon announced that H. Gernsback purchased 12 pictures from the mgp (money-grubbing photographer).

The JMITSFScomm talked somewhat.

\goto{New Business}

Nonalcoholic beverages will be served in Conner 413C at 8:00. All members are invited.

It was announced that the end of the world will occur on Friday, November 13, 2026, plus or minus 3 years. Following the end of the world, the Society meeting will be held at 1700 in 1-236.

MSD (Hoeper), 2-17.

MSD (Hoeper), 7-11-6. Roll call vote attached, 31 absent.

Has Lovecraft arrived? See last meeting.

MSP (Ravin), 20-1.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}