\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, May 13, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1710 by out-going president L. Court Skinner. The minutes of the three previous meetings were read and approved as usual (with dissent from the Humer-Palmer Clique).

\goto{Committee Reports}

The sometime-Lord High Embezzler Joe Cohen was not present to tender his report. The report is as follows:

Out: Sarill books, 16.00; Carnalval, 4.84; Meal (Clement and Abernathy), 3.93; Phone calls, 2.00; Banquet (Abernathy), 17.81; Grand total, 44.58. In: Dues, 3.00.

Balance on hand: 253.43 in good old chauvinistic US money.

Theftcomm: two posters stolen.

Libcomm: books are off library shelves. Present disposition of books: Markowitz, 1 box; Winsor, 1 box; Library, 1 locked coopbox (magazines); Humer, 1 locked coopbox (ASFs) and 1 box (hardcover books); 2-025, microfilms; Lewis, 1 box (paperbacks, about 250)and 1 box (old Amazings).

Moocomm: no report.

War Council: Holden has been seen again. We must get Techshow out soon.

Carnalcomm: a hero letter from APO was received- cash was not.

\goto{Old Business}

None.

\goto{New Business}

Sarill has 12 hardcovers to sell to the Society.

MSP (Wyman, Taylor) that books be bought from Sarill at a price of 16 dollars. 15-2.

Elections: Court read the part of the constitution (a farce) dealing with elections to the membership.

President:

Nominated- Anthony Lewis, L. Court Skinner, Ken Taylor.

MSP to close nominations, 13-0.

First ballot:

Anthony Lewis- 8

Void (note: inane votes not listed separately on first three ballots)- 7

L. Court Skinner- 4

Ken Taylor- 3

Total- 22

Second ballot:

Anthony Lewis- 9

L. Court Skinner- 8

Void- 5

Total- 22

Third ballot:

Anthony Lewis- 8

L. Court Skinner- 8

Void- 3

Total- 19

Fourth ballot:

L. Court Skinner- 11

Anthony Lewis- 9

Undecipherable- 2

John Wilkes Booth- 1

Total- 23

Fifth ballot:

L. Court Skinner- 13

Anthony Lewis- 7

Charles II- 1

Meaningless- 1

Total- 22

L. Court Skinner is the new President.

Vice-President:

Nominated- Robert Duff, Deanne Gross, Markowitz, Wm Sarill, Philip Spiro, Ken Taylor.

MSP to close nominations, 15-0.

First ballot:

Robert Duff- 8

Deanne Gross- 4

Wm Sarill- 3

Ken Taylor- 2

Markowitz- 1

Philip Spiro- 1

L'Allegro- 1

Machine-Gun Kelly- 1

Total- 21

Second ballot:

Robert Duff- 9

Ken Taylor- 4

Wm Sarill- 4

Deanne Gross- 2

Hereditary Machine- 1

Mikhail Tal- 1

Plant- 1

Pope Alexander VI- 1

Total- 23

Third ballot:

Robert Duff- 10

Wm Sarill- 4

Ken Taylor- 4

L. Court Skinner- 1

Foodini- 1

Paul French- 1

Plant- 1

Winnie the Pooh- 1

Total- 23

Fourth ballot:

Robert Duff- 14

Wm Sarill- 2

Ken Taylor- 2

Deanne Gross- 1

A coed- 1

N.S. Khrushchev- 1

Robert Heinlein- 1

Smith- 2

Total- 24

Robert Duff is the new Vice-President.

Secretary:

Nominated- Jon Ravin, Ken Taylor.

MSP to close nominations, 16-0.

First ballot:

Jon Ravin- 9

Ken Taylor- 6

Anthony Lewis- 2

Big Brother- 1

Blank- 1

God- 1

Plant- 1

Alcibiades- 1

43,000 years after- 1

Total- 23

Second ballot:

Jon Ravin- 9

Ken Taylor- 5

Anthony Lewis- 4

Kimball Kinnison- 1

Blank- 1

Void- 1

Henry IV (part I)- 1

Total- 22

Third ballot:

Jon Ravin- 9

Anthony Lewis- 7

Ken Taylor- 3

Either- 1

L. Ron Campbell- 1

Formulae- 1

Total- 22

After the third ballot, Ravin asked his supporters to vote for Anthony Lewis.

Fourth ballot:

Anthony Lewis- 13

God- 4

Jon Ravin- 3

Lovers- 1

Deanne Gross- 1

Total- 22

Anthony Lewis is the new Secretary.

Treasurer:

Nominated- Deanne Gross, Maynard Johnson, Ken Taylor.

MSP to close nominations, 14-0.

First ballot:

Deanne Gross- 11

Ken Taylor- 5

Maynard Johnson- 2

Anderson- 1

Wm Sarill- 1

Iry Baker Priest- 1

Ballot of Reading Gaol- 1

Total- 22

Second ballot:

Deanne Gross- 13

Ken Taylor- 6

Insull- 1

Wm Sarill- 1

Total- 21

Deanne Gross is the new Treasurer.

MSP at 1845, 15-1.

\vspace{12pt}

\centerline{Submitted by}
\centerline{Lewis, who is on the job for another year}

\end{document}