\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, May 20, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1710. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

The Lady High Embezzler Deanne Gross reported 237.43. We owe the Ravin 1 dollar.

Libcomm: Humer made a fool of himself. More books were bought from Bill Sarill.

Moocomm: absent.

Theftcomm: no posters stolen this week. Please return all stolen posters.

Knockomm: a sounding board has been obtained by Joe Cohen.

War Council: Court met with Art Hatch, Dean Holden, and TechShow, and we WON!!! We will start moving books into the room.

\goto{Old Business}

None.

\goto{New Business}

A letter from Hugo Gernsback was read to the Society.

MSP (Skinner, Lewis) that Mr. L. Court Skinner, in view of his fine work in obtaining a room, be granted the right to place a pediment above his door. 13-0.

Jerry Wenker will sell his ASF collection (complete) for 350 dollars. We could borrow this money from FinBoard, maybe.

MSD (Humer, Lewis) that we pay 150 dollars upon delivery and 100 dollars/year for 2 years about 1 week after the annual movie. 6-8.

ASD (Spiro) that a special assessment of 2 dollars minimum be made upon the members.

MSD (Humer, Whiton) that Mr. Wenker's collection be purchased for 350 dollars.

MSP (Humer, Whiton): see two motions back. 6-5.

Ken Taylor will be in charge of the library over the summer. Books will be moved in by the members at 2:00 Saturday.

Volunteers for Activities Midway: Jon Ravin, Deanne Gross, Frank Palmer, Pat Morris, Phil Spiro, Ken Whiton, noble secretary A. Lewis.

Court Skinner will contact Art Hatch and Deanne Gross will contact C. Greiner about the freshman midway.

\vspace{12pt}

\centerline{Done by}
\centerline{ARLewis, Secretary}

\end{document}