\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 16, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1718 by Skinner. Many of the members were absent in body (but not in spirit) due to an 8.031 quiz. The minutes were read and approved.

\goto{Committee Reports}

Although the treasurer was absent (see above), Court gave the total as 89.37.

Libcomm: money was collected from the treasurer. L.G. Bufours is an agent of Boskone. 5 more books covered.

Theftcomm: posters put up, stolen, more put up! Ah, life.

Moocomm: film for 19 January 1961.

War Council: no bookases, no report.

\goto{Old Business}

Duff question? Yes!

Lovecraft question? No!

There will be a birthday party in honor of Ludwig von Beethoven tonight at 2000 in Bexley 202.

The Journal was talked about.

Movies: Twilight Zone. Kentaylor saw Sarill who will see Serling during the holidays to convince him to leave the Twilight Zone films with us.

If there is a special meeting to see Serling posters will be upgeputten.

\goto{New Business}

Library will be open Saturday 2-5 (Whealton) and Sunday 2-5 (Skinner), perhaps Tuesday.

A report of activities at the last IES meeting was given to the Society.

Hugo Gernsback's Forecast 1961 was discussed.

We have 2 new members, one of which is a coed.

At 1756 it was noticed that snow was falling OUTSIDE.

At 1805 Ravin and others came wandering in from the quiz.

Ravin gave a journal report and read a letter from Asimov. A new Norbert Wiener joke was told.

MSP (Lewis) to Millerate. 9-6.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}