\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, September 23, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1713 by NP Court Skinner. The minutes of the previous meeting were read. The Skinner-Humer Cabal intimated that an error had been made. However, due to the resolute stand of the Noble Secretary and the lack of documentary evidence, the minutes were accepted as read.

\goto{Committee Reports}

The treasuress reported: we have 81.33 minus what we owe plus dues taken in.

Moocomm: no report.

Libcomm: Humer handed out a list of some things in the Library. Included was a matrix on which to indicate when one desires the library to be open.

Theftcomm: Ravin introduced itself. No posters stolen.

Knockomm: Court lost the address that J. Cohen gave him. As a result, we have no sounding board.

Sarill was introduced and explained.

War Council: Court will get the key. He has seen Holden.

\goto{Old Business}

Lovecraft has not come yet.

Abernathy is back this year.

Court lost the AOA check for 8.60.

Holden was seen last reading period.

Holland will be contacted in re bookcases.

A comment about bookcases in building 20 was made.

\goto{New Business}

A smoker will be held.

MSP (Lewis) that Mr. Sarill be empowered to write to L. Sprague de Camp to ask him what his cost would be to come see us and talk. n-1, 1<n<infinity! Skinner: excellent idea.

Some elliptical person (Easton) wants us to investigate psychic phenomena. After much acrid debate a new committee was set up.

Psico: Mac Easton- chief crackpot (psicoceramic), other crackpots- Colomb, Harrison, Speiser.

MSP (Duff, White) at 1757, 16-11.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}