\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, February 26, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1715. The minutes were read and approved. Phil Spiro has returned.

\goto{Committee Reports}

The L.H.E. is not here so no treasurer's report. However, 2 dollars have been collected in dues since the last meeting.

Moocomm: no report.

Theftcomm: no report.

Libcomm: the 41 Pick-a-Book books have arrived; they are in Norm Humer's room. The extra book, The Glory That Was by L.S. de Camp, is due to our joining their book-a-month plan. Humer read the list of books we received. The Society now has a Coop number, 44598. If you want your money back from now on, present a receipt with the number (even if you don't buy it at the Coop).

Some movie studio has paid Ray Bradbury 150,000 for the right to ruin The Martian Chronicles.

Money spent: Galaxy (4)- 8.50, Wm (3)- 11.00, ASF (3)- 9.00, tape- 1.21, total- 29.71.

Note: McCullough has a car.

The coopbox is now in Humer's room. Come to room 511b in Burton House at 7:00 PM Saturday and 1:00 AM Sunday to cover the new books. No uncovered books can be read.

\goto{Old Business}

Wenker forgot his list of books. He will sell them for roughly 1 dollar each. Available are old Amazings, Amazing Quarterly, Wonder Stories Quarterly, and Amazing Annual.

Since Padlipsky is doing his thesis on More Than Human we should ask him if we may make a copy for our library.

Skinner sent a list of books to Prof. Locke (of the libraries) that we recommend his son read.

\goto{New Business}

MSP (Lewis, Wenker) that 12 dollars be sent to Pick-a-Book for more Pick-a-Book books. 8-2-2.

Sarill was not here.

MST (Lewis): Miller. 5-5-0.

Humer then conducted voting on various sf books as we had done in the past.

Afterwards, the president, speaking for Boskone, broke the tie with a vote for adjournment, which we did at 1815.

\vspace{12pt}

\centerline{Submitted quite somberly by}
\centerline{Anthony Lewis, L4, Secretary}

\end{document}