\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, September 30, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent

Prologue: the following notes are transferred exactly from Mr. Ravin's works. The secretary thanks him for his efforts and sincerely hopes that he (Ravin) will not be the next secretary.

To begin: meeting called to order at 1710. Secretary was absent, minutes not read. Whiton acted like an idiot for a large fraction of the meeting.

\goto{Committee Reports}

Theftcomm: no report.

Libcomm: preference sheets tabulated and read. Preferred times: 2 to 5 Saturday and Sunday, 7 to 8 weeknights. Votes were received for Friday 5 to 6.

The Secretary arrived triumphantly at 1712. -Phew, Ravin and Theftcomm

Thus ends a most ghastly tale from the dark past handed down to us by means of a parchment so ancient that at the time of its manufacture, J.W.C. was not the editor of that magazine.

Here begins the saga:

Humer read a quote from Earthman's Burden which makes favorable reference to highly beloved J.W.C. Jr.

The minutes were read. As usual, an altercation arose. Some of the Psico members resented being referred to as psicoceramics (crackpots) and demanded that it be stricken from the minutes. Truth, retorted the Noble Secretary in ringing tones, must remain inviolate (or words to that effect). First of Libcomm Humer agreed that they were crackpots. The Ravin promised to swing the support of the Society for the Aesthetic Rearrangement of History behind the Secretary. Faced by such support of Lewis's stand, El Presidente Skinner ordered that the minutes be accepted as read; especially as the Secretary refused to change them even if ordered to do so.

Moocomm: no report.

However, Mr. Perry can get us The Time Machine so we can uplift the masses and gather piles of money.

Knockomm: no report. Situation as follows: Cohen gave Skinner company address, Skinner lost address, Skinner would write to Cohen but Duff lost Cohen's address.

Psico: has 5 members (of a phallic nature) and will meet in Baker 501 on 1 October 1960.

War Council: victory's laurels crown our Court. He got the key. He (Court) saw Holland. He (Court) saw a letter from Gernsback. Ergo: Holland will introduce Gernsback at the smoker if we tell him who Gernsback is.

\goto{Old Business}

Has Lovecraft arrived yet? No.

A big box has arrived at Burton House.

Membership cards have been ordered from Cambridge Press.

A room for the Gernsback Smoker on 21 October must be obtained.

\goto{New Business}

Bob Schildkraut (an outsider) will try to get us The Shape of Things to Come to show second term.

Spiro: how about Huxley?

Bob Duff: who gets keys?

We will decide later.

Kentaylor is assigned to steal a menu from the Smorgasbord.

Brodsky just came in at 1746.

Humer will check gradhouse about dinner for Gernsback.

Publicity: Ravin will draw 4 Megaposters and flunk this term. A notice will be put in the calendar of events.

Lewis will write to Herr Doktor Asimov asking him to come.

Jerry Wenker is back (or was) in town. No doubt looking for his money.

MSP (Lewis) at 1748, 21-5.

\vspace{12pt}

\centerline{Thus ends an epic by}
\centerline{ARLewis, Secretary}

\end{document}