\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 11, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1708 by the President of our August (March?) Body L.C. Skinner. The minutes were read and approved after a long fight with the forces of evil- but good will out.

\goto{Committee Reports}

The treasurer was not here but his report was.

On hand 2/19/60: 449.94. Receipts: dues- 8.00. Disbursements: Pick-a-book books- 12.30, Coopcard- 1.00, tape and plastic- 12.01, magazine subscriptions- 28.50, back issues of ASF- 3.25. Total on hand: 400.88.

The L.H.E. also got a letter from FinBoard of Inscomm, cursed be its name, saying that we (i.e. J. Cohen) have not submitted a financial report.

B.F. Wyman asked a stupid question about filibustering.

Theftcomm: two posters were stolen.

Libcomm: money report. Come up and cover the blasted books.

Moocomm: no report.

War Council: re room- Tarm Farqukar was contacted. He told us to see Bill Swanson, who referred us to Dean Holden. Court tried to see him but he was not in. "He might be in Monday," said the techretary. Monday: nope! Tuesday: Court saw the good Dean and explained the situation to him. Dean Holden said he would see what he could do.

Carnalcomm: Maynard Johnson, Chief Carnalee, held forth with three proposals. 1) Hieronymous Machine Hem!!! 2) Compound pendulum- 11. 3) Darts, moving target- 2. It was suggested that we toss in a coed for local colour.

\goto{Old Business}

No answer from Clement yet.

Wenker is here with his list of books (attached).

MSP (Lewis, Whiton) that the Society pay Jerome Wenker the sum of 60 dollars for the books on the list. 10-4-0. There was a great deal of discussion on the merits of such a move but the motion was passed.

\goto{New Business}

MSD (Palmer) that the Society thank the Secretary for the originality of his minutes. 3-9-1.

A letter from the IES was read to the Society.

It was moved at 1806, 14-3-2.

\vspace{12pt}

\centerline{Submitted by}
\centerline{ARLewis, Secretary}

\end{document}