\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 15, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was ordered at 1737. The minutes were read and approved.

\goto{Committee Reports}

The Lord High Embezzler was not present so no treasurer's report was heard.

Moocomm: no report.

Theftcomm: three posters stolen.

Libcomm: no one came up to cover books; Lovecraft did not come.

War Council: no word from Dean Holden.

Carnalcomm: infinity report- 1) a sneaky deal with APO was made by which we get all sorts of stuff free in exchange for a booth in dekagon (building 10), 2) volunteers are needed to man (or coed) Carnalcommvicecomm as M. Johnson is caught up in a mad whirl of conflict-of-interests, interlocking directorates, and the like.

[Drawing resembling Rube Goldberg machine in shape of circuitry diagram, with such components as "rocketship a la Anthony (Buck/Rogers)," "freeform SF," "ponderable matter," "clothesline," and "balloon"]

The whole cunningly drawn by A.R. Lewis.

\goto{Old Business}

Clement will be here 29 of April. Lewis (on behalf of MITSFS) will invite Abernathy.

A question in re the Finance board which wasn't was raised. It was suggested that it be sent to Inscomm. "It" being the report.

We decided that Robert Abernathy will be guest of honor at the banquet. It was also suggested that the overworked secretary inform him.

\goto{New Business}

MSP (Humer, which is a Libcomm, Morris, which is a coed) that the sum of 9.35 US currency be spent to purchase Dover books: 3 Prophecies of H.G. Wells, 7 SF Novels of H.G. Wells, 28 SF Novels of H.G. Wells. 8-3-0.

Bookplates were discussed but nothing was decided.

MSD (Lewis, Taylor). 2-4.

Someone mentioned that Brodsky wants in again. A sudden chill descended upon the group.

MSP (Lewis) at 1806, 6-3.

\vspace{12pt}

\centerline{Submitted by}
\centerline{ARLewis, Secretary}

\end{document}