\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 22, 1960

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1707. The minutes were read and approved.

\goto{Committee Reports}

Treasurer's Report: no change.

Theftcomm: 1 poster stolen, 1 given away.

Libcomm: 3 more Pick-a-Book books arrived, namely Sands of Mars (Clarke), Agent of Vega (Schmidt), and Second Foundation (Asimov). Books are not being covered.

Moocomm: no report.

War Council: no report.

Carnalcomm: Maynardjohnson: 1) I will not resign (good, hear, hear), 2) APO will provide us with a table, 3) we should give away certificates to people who play the game. Lewis: let us give away members as prizes.

\goto{Old Business}

Volunteers for the Carnalval are needed: Ravin, Skinner, Humer (after 3:30), Lewis, Gross, Morris (evening), and anyone else who can be coerced, cajoled, or beaten into line. Work will start at 10 Saturday morning and continue until 6 in the evening. Booths must be manned at 7:30 as the Carnalval will open at 7:45.

\goto{New Business}

Sarill was not here.

Lewis read to the group an article from the Saturday Review which discusses sf and in particular Amis' New Maps of Hell. A review of Level Seven was read.

MSP (Lewis, Ravin). 4-4; the president sided with the forces of evil and the meeting adjourned at 1741.

\vspace{12pt}

\centerline{Submitted by}
\centerline{ARLewis, Secretary}

\end{document}