\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING
\newcommand{\skinner}{Laura McKnight, President and Skinner}
\newcommand{\onseck}{James Hobin, Onseck}
\newcommand{\meetingdate}{Friday, 20 September 2013}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST, \\
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes for predicting the future. Motion passes: 7-5-4 \ps

\bing

\goto{Committee Reports}
Starchamber: There is starchamber meeting after this meeting, it will involve business. \\
Magazines: The magazines that sort of do not exist are existing less. \\
Donations: There are more of them sitting around and must be checked for mold. \\
Motion that books, like yogurt, should be checked for mold, because Tamoji
[spelling] yogurt between a few dates had to be recalled due to exploding after
mold contamination. \\
Motion passes 5-3-4 \ps \\
\bing \\
Seldon: Movie was shown, second half \\
Barcomm has devolved into the chamber, flyers are noted. \\
{\bf *deranged giggling*} \\
New paper dexes exist for the first time in four years!


\goto{Old Business}
The books are eating us, as usual.
The Star Chamber meeting will involve coherent planning.
Karl: Charities are sometimes picky about books they receive as donations.
Lemur: It turns out that having 500 copies of dune is less than ideal.
Skinner: We did successfully donate quite a few books to Engineers without Borders.

In the past, some guy wrote us a letter about how he used a flux capacitor to time travel.
{\em Letter read}
{\em Pamphlet read, spoilers}
Dean drive manuscript mentioned. \\
In the past, there was an open house. \\
Unusual motion to "is there a difference between the usual motion and unusual motion" \\
Unusual second

\goto{New Business}
The story of Realauthorscomm is told.
There is a new person in the library.
\goto{Future Business}
In the future, there will be more frosh in the library.
In the future, the skinner or onseck will send out reminder emails about emails.
In the future, Lemur will write all the rites ever of all time.
In the future, the ASA will cease pressganging.
MITSFS will not eat your soul without consent.
In the future, the chamber will be able to keep track of which part of the meeting it is in.

Motion to make some sort of motion involving bananas. \\
Seconded. \\
Motion passes: 80-2-0 \ps

\bing
\noindent
Meeting adjourned, 64.76 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
