\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 26 April 2013}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

\bing

Motion to commend the minutes for being short PASSES 7-2-1\ps
Motion to condemn the minutes for containing insufficient quantities of titanium FAILS 2-6-2\ps

\goto{Committee Reports}
Picniccomm- There's a lot of food in Random, Picniccomm will happen tomorrow
Mergatory happened
Mommycomm- 3 new keyholders!
Theftcomm- There's a new TIF!
Spring Cleaning is in 2 weeks!
Pseudojurcomm- Submissions due May 1st!
Hasslecomm- Trying to finally finish it's rewritting it's rites.



\goto{Old Business}
Something something Quentin Terentino
Motion to condemn the Onseck's taste in text editor FAILS 4-20-0 /ps
Usual stuff

\goto{New Business}
Elections!
Nominations for Onseck:
James Hobin
Capitilazition
Quentin Tarantino
EMACS
VIM
Microsoft Word
Cthulu Summoning Ritual
Hast#r
Moist Von Liprig
Lord Darcy
The Letter \"I\"
The Constant \"I\"
Fortran 4
The Set of Quaternions
The Set of QuaTernuses
Bora Horza Gobochull
James Hobin Wins 6- a smaller number

LHE
Locke Lamora
Sarah Coe
Lokas Fehrwright
Jean Le Flambeur
Bilbo Baggins
Spelling
Grammar Nazis
Reading, 'Riting, and 'Rithmetic
Congress
Captains Pedantic
Tyrion Lannister
The Inanimate Carbon Rod
Tyrion Lannister and Sarah Coe will be co-LHE

Vice
Mika
Littlefinger
Votesplitting
Sloth
Wrath
Gluttony
Hugo
Father
Fait, Hope + Charity
Scar
Captain Tyler
A vice
A Vise
Joe Biden
Grammar Nazis
Alexander Hamilton
Gerald Ford
Mika, for which vice and wrath counts, wins!

President
Gerald Ford's Head
Richard Nixon's Head
The Grand Canonical Ensemble
Laura Knight
lknight
Black, Red, and Green Knights
The Dunedain
Lex Luther
Baron Harkonnen
Laura McKnight
Nearly Headless Nick
Grand Admiral Thraun
The Smiler
lknight is the new President


\goto{Future Business}

In the future there will be a picnic!
In the surprisingly near future there will be a Twilightzine
In the future Onseck's will write minutes with a steady hand and butterflies PASSES 20-0-4\ps


\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
