\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING
\newcommand{\skinner}{Laura McKnight, President and Skinner}
\newcommand{\onseck}{James Hobin, Onseck}
\newcommand{\meetingdate}{Friday, 10 May 2013}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 64.8 Ksec SST,
\skinner, presiding; \onseck, recording.


Minutes not read.
Absence of minutes condemned.

\goto{Committee Reports}
Hasslecomm:
\begin{itemize}
  List of all books with too many copies on shelf printed
  KBX boxes exist, should be changed out for more to purge.
  KBX1000 exists, 14-16 boxes in the Annex labeled with words, must be converted to normal KBX
\end{itemize}
Mobcomm sez: New books exist, more will exist soon. \\
Smilecomm: To be shelved is scary. \\
New Trojan: Trojan work party will happen soon. \\
Bluebellcomm: Progress exists, more will exist soon \\
Seldon: Movie will be shown next week. \\
War Council: There is never enough space. \\
Chancellor: Recommendations for *chamber rites should be emailed to me. Recommendations given:
The *chamber needs to remind people to War Council. What the ASA does and why we care (allocates space) \\
Skinner: Labels should be reprinted \\
Winter project: Warehouse purge, Dexhampster can be run through phone internet.

\goto{Old Business}

In the past we have failed to have unstrangely productive meetings. In the past
most of boxed SFWA was Hassled. In the past, inventory happened. In the past,
during committee reports, we should look in to bugging Carl to reprint the DEX,
it should happen before the frosh show up. In the past, there was an ASA moratorium.
In the past, people made usual motions. \\
\goto{New Business}
In present, the Skinner is confused by usual motions. \\
Unusual Motion: usual absence of a second. Unusual second. \\
Unusual vote, unusual pass: 6-4-0 \ps

\goto{Future Business}
In the near future, 5-10 books should be shelved in a meeting. In the future,
more people should come to meetings. In the future, recruitment will happen.
Skinner decrees someone must motion. \\
Motion for a banana-flavored apocalypse passes 7-3-3 \ps \\
\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
