\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING
\newcommand{\skinner}{Laura McKnight, President and Skinner}
\newcommand{\onseck}{James Hobin, Onseck}
\newcommand{\meetingdate}{Friday, 27 September 2013}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST, \\
\skinner, presiding; \onseck, recording.

Minutes read. \\

In the future, the onseck accidentally deleted the minutes. \\

\bing

Motion to condemn the bing passes: 11-0-1 plus Spehn. \\

\goto{Committee Reports}
Pseudo-Seldon: Showing of the second half of The Colour of Magic will happen next week. \\
Hasslecomm: Hassle extras purge October 5th! \\
Chancellor: Keyholder rites updating will start next week. \\
Pressgangcomm exists with a mailing list and everything. \\
PseudoNaNocomm: November (NaNoWriMo) is coming up! \\
DoomComm: Lemur will hopefully be not ASA future recently. \\

\goto{Old Business}
In the past, Monk's Magic was checked out. \\
In the past, somebody owed us money. \\
In the past, Lemur donated a copy of HPMOR, which should be signed by Eliezer Yudkowsky. \\
In the past, fanfic was on the reserve shelves. \\

\goto{New Business}
In the present, people were terrible. Motion to condemn people for being terrible passes. \\

\begin{displaymath}n - m - 0 \textrm{ plus Spehn\xspace }\end{displaymath}

Onseck decides to prove the vote's passing via Skinnerial induction: \\

\begin{displaymath}n \in \mathbb{N}\end{displaymath}


\begin{displaymath}m \in \mathbb{N}\end{displaymath}

Induction base case: \\

\begin{displaymath}P(n=0): 0 > m\end{displaymath}

By Skinnerial decree, $m < n$. It follows that $m = -1$. \\
$P(n=0)$ holds. \\
Assuming $P(n)$ holds, $P(n+1) ::= n > m$ \\
By Skinnerial decree, $n > m$. Therefore, $P(n+1)$ holds. \\
$n > m$ by Skinnerial induction. \\
Space: removing circ. magazines gets more space, warehouse demunging is also a thing. \\

\goto{Future Business}
The future is a terrible place. \\
Motion to destroy the universe passes 9 - 8 - 0 plus Spehn \\
\bing
The universe was destroyed. \\
In the nonexistent universe, Miller motions were debated. \\
Lemur moves a banana across the room in the newly destroyed universe. \\

\bing
\noindent
Meeting adjourned, 64.76 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
