\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING
\newcommand{\skinner}{Laura McKnight, President and Skinner}
\newcommand{\onseck}{James Hobin, Onseck}
\newcommand{\meetingdate}{Friday, 27 September 2013}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST, \\
\skinner, presiding; \onseck, recording.

Minutes read.

\bing
Motion to condemn the minutes for containing references to the Love Boat
(to approve the minutes as extremely historically interesting.) \\
Passes 9-0-0 \ps

\goto{Committee Reports}
Pressgangcomm: Sold a bunch of books at Geek Central, getting loads of money and loads of space. \\
Historically everything was Star Chamber, now everything is Pressgangcomm. All glory to the pressgangcomm. \\
Kvetchcomm: May get more books! More reviews! More words! Some good, some bad, some unreadable. \\
PseudoNaNocomm: November (NaNoWriMo) is here! \\
Pianocomm: Meeting in future to talk about recruitment. \\

\goto{Old Business}
In the past, there was a write-in. It was reasonably successful and people showed up. \\
In the past, a person came in to talk about sci-fi in the TV industry, it was awesome. \\
In the past, Lemur accidentally corrupted Sueshep with power. \\
Susan is now the pseudo-pseudo-Skinner. \\

Motion to create current business. \\
Passes 5-5-1 \ps \\
Motion fails by pseudo-pseudo-Skinnerial decree. \\

\goto{Current Business}
The pseudo-pseudo-Skinner has gone mad with power. \\

\goto{New Business}
In the future, the pseudo-pseudo-Skinner will rule over the Instrumentality and Star Chamber with an iron fist. \\
In the future, there will be a continuation of the Warehousing. \\
In the future, we will get paid for the Geek's Central books. \\
In the future, NaNoWriMo continues. \\
In the future, we will read more books. \\
In the future, the OnSeck will be driven mad by the inability to distinguish between new and future business. \\
In the future, the Students' Center will be closed Thanksgivingish, emails to be sent. \\

Motion to condemn the psuedo-pseudo skinner for being driven mad with power and failing to bring about a banana-flavored apocalypse. \\
Chickens 4-0-8 \ps \\
Miller motion \\
Chickens 1-0-1 \ps \\

psuedo-Skinner moves a banana. \\

\bing
\noindent
Meeting adjourned, 64.76 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
