\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING
\newcommand{\skinner}{Susan Shepherd, Pseudo-Skinner}
\newcommand{\onseck}{James Hobin, Onseck}
\newcommand{\meetingdate}{Friday, 9 May 2014}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST, \\
\skinner, presiding; \onseck, recording.

\bing
That was really loud
\goto{Committee Reports}
There's a picnic tomorrow in PDR4, meet us in the library. There will be
banana-pierogie, banana-pie, and other things. Actual picniccomm is acquiring a
lovely bunch of coconuts. The vehicle for the quest for the coconut has been
prepared.

Lost books committee: Monk's Magic has been returned after 9 years.
Motion to commend Sueshep and Brian Sniffen for getting the fucking thing back passes 19 - 0 - 1 \ps
\bing
There's a huge pantercomm overflow menacing the hills of the library \\
Van Helsing in Exile-Comm: I have two staked copies of Twilight in my apartment, those should go away. \\
Warcomm: Reserves in Greendex will exist one of these days \\
Starchamber: The new keyholder rites are almost finished! \\

\goto{Old Business}
In the beginnning, there was DARPA. And DARPA created the routers and servers
and there was internet. And DARPA looked upon what it had created and saw it
was good.

\goto{Elections}
Onseck:
\begin{itemize}
  \item[11.] Cathleen
  \item[0.] The Earl of Lemongrab
  \item[2.] Devan Lochees (Chronicler)
  \item[1.] Thing
  \item[0.] Things
  \item[1.] Nothing
  \item[0.] Something
  \item[1.] Tetraxenongold(II)
  \item[0.] ClF_{3}
  \item[0.] Fire
  \item[0.] Water
  \item[0.] Air
  \item[0.] Wood
  \item[0.] Metal
  \item[0.] Earth
  \item[2.] Heart
  \item[1.] The Fifth Element
  \item[0.] The Eighth Element
  \item[0.] The Eighth Color
  \item[0.] The Element with atomic number 666
  \item[0.] Neutronium
  \item[0.] Unobtanium
  \item[0.] Scrith
\end{itemize}

Cathleen wins! \\

Lord/Lady High Embezzler (LHE): \\
\begin{itemize}
  \item[8.] Sarah
  \item[3.] Tyrion Lannister
  \item[1.] Baron Wolfenbach
  \item[0.] Lex Luthor
  \item[0.] Smaug
  \item[0.] Smog
  \item[0.] Tsmdksfls
  \item[0.] Toothless
  \item[0.] Meraxis
  \item[0.] Valerion
  \item[0.] Sabatha
  \item[0.] Nergal
  \item[0.] Hecate
  \item[0.] J.K. Rowling
  \item[0.] That gesture that sueshep made
  \item[0.] The act that that gesture represents
  \item[0.] Tetra
  \item[0.] Anne Bonney
  \item[0.] Florence Ambrose
  \item[3.] Tattletale
  \item[0.] Catwoman
  \item[0.] Harley Quinn
  \item[3.] Zeetha Daughter of Chump
  \item[0.] The Other
  \item[0.] The Jaegers
\end{itemize}

Sarah and Tattletale win! \\

Vice: \\
\begin{itemize}
  \item[12.] lknight
  \item[2.] Cheese pierogie
  \item[0.] Vice grip pliers
  \item[0.] Vice magazine
  \item[0.] Channel-lock brand pliers
  \item[2.] Vice
  \item[0.] Vise
  \item[2.] Vyse
  \item[0.] Ira Gamagoori
  \item[1.] Captain Levi
  \item[0.] Dende
\end{itemize}

A brief interlude: the plot of Consider Phlebas \\
Sightseeing, sightseeing, sightseeing, cannibals, sightseeing, MASS DEATH,
sightseeing, DEATH, DEATH, BETRAYAL, DEATH.

President: \\
\begin{itemize}
  \item[12.] Lemur
  \item[0.] Lady Satsuki Kiryuin
  \item[1.] Words that can be spelled
  \item[0.] The Albanian language
  \item[0.] Orangutan
  \item[1.] Phonetic spelling
  \item[0.] Kamina
  \item[0.] Homophones spelt homonyms
  \item[0.] Besmer process
  \item[0.] Haber-Bosch process
  \item[0.] Bourne approximation
  \item[0.] The elections process
  \item[0.] The doppler effect
  \item[0.] The Chandrashakar Limit
  \item[1.] Sansa
  \item[2.] lknight
\end{itemize}

Lemur wins!
\bing
\noindent
Meeting adjourned by skinnerial decree, 64.76 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
