\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING
\newcommand{\skinner}{Laura McKnight, Pseudo-Skinner}
\newcommand{\onseck}{Cathleen Nalezyty, Onseck}
\newcommand{\meetingdate}{Friday, 26 September 2014}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST, \\
\skinner, presiding; \onseck, recording.

\bing
\goto{Committee Reports}
hBarcomm : has been doing stuff; tomorrow there will be people talking about committees; it takes a lot to run mitsfs; 60k+books is a lot to work on; tomorrow at 3
in the future: federation day party, trivia, seldon showing, costume contest

niagracomm: sending out magazines; backstory of better world books; mostly so we can get more books in the library!
\bing

\goto{Old Business}
In the past, there were meetings a long time ago and fun stuff; meetings like this one, movies & board games and stuff

In the past, it didn't get dark as early

In the past, it was also warmer -- more like hot.
 
In the past, it was very briefly a pleasant temperature.
In the past, air conditioned buildings caused sadness.
In the past, 50\% of the *chamber was interning at Akamai, which keeps their air conditioning too cold.
\bing
\goto{Current Business}
In the present, this is the part of the semester where you start getting lots of work and get hosed.

In the present, lknight hasn't gotten enough sleep because 6.828.
In the present, lknight
In the present, this is a pretty quiet meeting.
\bing
\goto{New Business}
In the future, there will be events. 
In the future, they will be more fun when not hosage-time.
In the future, lknight will properly plan events!

\noindent
Motion for something about bananas: motion passes 11 to some # to another #
Meeting adjourned, some #Ksec SST
\noindent

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
