\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING
\newcommand{\skinner}{Laura McKnight, President and Skinner}
\newcommand{\onseck}{Brian Sniffen, Onseck Extraordinaire}
\newcommand{\meetingdate}{Friday, 2 May 2014}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST, \\
\skinner, presiding; \onseck, recording.

No meeting has been held in some time.  No minutes read.

\bing

\goto{Committee Reports}
War council: We have new space, shared with ESP.  This will replace
the old Bibliowarfare Laboratory.

Picniccomm: Sign up!  (Where's the sign-up sheet?) It'll be here soon!

Star Chamber: Elections are next Friday.

Pianocomm: Please congratulate/mourn kbeth on becoming a keyholder.

A finger motion is made and declared invalid. 

Trojan: Donations are processed; those boxes along the back wall are
all Panthercomm overflow.

Libcomm: The KBX-thousand series is now dead.

\goto{Old Business}
In the past, there were meetings.

In the past, we had a First Contact Day celebration.  There was food
and fun.

In the past, we had a Pi Day celebration.  There was pie and fun.

In the past, we listened to Nightvale.  Pay no attention to the dog
park or fun.

In the past, authors visited.

ALGOL.

\goto{Current Business}
Can we bring banana pierogi to the picnic?

Motion to condemn the meeting for being to quiet. Fails for lack of a second. 

Lemur: motion to commend the meeting for proper quiet in a library. Passed x y z \ps.

\goto{New Business}
In the future, we need a picnic sign-up sheet.  Who's picniccomm?
Kbeth.

A Miller motion is made.

\bing
\noindent
Meeting adjourned by skinnerial decree, 64.76 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
