\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Minutes of the MITSFS

Friday, February 4, 1977

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Having made their daring escape from the laboratory in Building 66, four modified E. coli bacteria met in the small intestine of Charles Milton Spofford at 5:00 PM Recombinant Standard Time to discuss the upcoming plague in which they planned to conquer the world and outlaw Ex-Lax. The meeting was called to order by gamma-Goldberg, Membraner of the MIT Science Infection Society.

The DNA transcriptase molecule was plugged into its inducer to record the proceedings. On some ridiculous pretense Bacterium LHE-beta-pi-10 accused himself of not voting and was censured for undergoing mitosis in public. A halt was called to this side-splitting affair by a call for committee reports; beta-pi-10 (having pulled himself together) reported an inaudible but nonetheless incredible amount of spare lipid in storage, but the condemnation that followed was inhibited by the appearance of a chi-JH phage particle which attempted to lyse everybody with its evil oral cilia.

Unperturbable, the Messenger RNA committee reported that the 29th Twilight Macromolecule had finished polymerization and was ready for active transport. He also reported that the thirtieth Molecule had begun the recombination process preparatory to transcription.

Pseudo mu-comm reported that everybody's favorite DNA tape, Dark Nucleus, would be playing next week. Denatured Libcomm reported receipt of a Witter shipment containing the dread virus Perry-rho-107, as well as a bunch of Lunar chromosomes. Witter was condemned for exchanging genetic information with fossilized Cheetos. The motion failed, with only the Frito Bandito in favor, the formidable force of Cheese that goes Crunch opposed, and a wishy-washy Cheese that doesn't go crunch as it falls under 1/6 lunar gravity chickening, but the Membraner was out of order and had to be adjusted. Strangle-complex gamma-Goldberg reported an attempt to contact the beta-Blob, a former Membraner, who had moved to Chicago to infect their physics department. The message had read:

PERRY RHODAN IN DIRE STRAITS. DIMINISHED DIGITS PROVE TOO TITILLATING FOR FRISKY FRUMPS. RESPOND.

We slid through old business and old business algol like an electron shuttling down a chain of cytochrome molecules. XJ reported a minicult in which a biologist expressed his confidence that the world would not become an Escheriscia Colisseum. It was moved to infect the biologist with T4 and leave him only with a ";". The motion chickened, with the entire E. Coli softball league in favor, and the E. Coli Polytechnic opposed, but the unbeatable 7-up, the E. Coli chickening.

A waste vacuole was discovered to have the word SPODFORD printed on it. At this point, the cow-lilies burst into bloom. The society, in consternation at infecting Spodford instead of Spofford, hurriedly adjourned back to the Bio lab where there was lots of nice sweet glucose solution, instead of all this shit.

\vspace{12pt}

\centerline{Recombinantly submitted,}
\centerline{alpha-Wechslerescia}

\end{document}