\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes 

Friday, November 4, 1977

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The deadly fireballs at last ceased to flash, the last ponderous shock waves swept over the Boston area, destroying everything still standing, and re-destroying everything else. A west wind blew the glowing isotope clouds out over the dying ocean. Boston burned slowly. Occasionally a dull crash could be heard as masonry collapsed somewhere. The Charles River, choked with the debris of Allston, Brighton, Waltham, and Watertown, overflowed its banks and began to seep through the porous wreckage that had once been Cambridge.

As the basement of the once-proud Building One began to fill with the ghastly, polluted, radioactive water, a curly head emerged cautiously from behind the remains of an oil canvas. Consulting his watch, the ruins of the Skinner of the MITSFS swing a star-mangled spanner over his head, letting it fall against a twisted piece of metal detritus in a display of hopeless futility and frustration.

"Meeting called to order," he said sardonically. "Onseck will read the minutes of the previous meeting."

"There aren't any minutes," quavered a voice from beneath an overturned table. "There isn't ANYTHING anymore. Our world has come to an end. Soon we'll all die of radiation poisoning, unless the Hitchcock Theory proves correct and it turns out that prolonged exposure to obnoxiousness DOES grant immunity. But that's an unlikely hope. In all probability we'll die terribly painful deaths in a matter of days, and you want me to read the minutes?! Are you out of your mind?"

But the Skinner had a new look of determination on his face. He remembered the final scene of "The Man Who Would Be King," where the hero bravely sings a hymn as he is being executed... and he realized, here at the end of the world, that The Show Must Go On. Even as the back of his mind was screaming "Bullshit!!" at all this sentimental trash, he said, "You're damned right we'll read the minutes. The MITSFS is the last vestige of civilization now, we can't die like cowards. We must maintain our dignity to the last. Move to approve the minutes as read!"

"Second!" said another voice, and miraculously undemolished MITSFS members began to appear from under every ruined piece of trash I could possibly describe, until there were quite a few of them there, facing the end of the world with bravado, bravura, and brouhaha.

The ghosts of the last 357 unread minutes voted in favor, vastly outnumbering "Middle C" and "Time enough for various things."

Pseudo-onseck and Blast-from-the-past Greg Ruffa also had no minutes, but they could not be not approved as unread because he wasn't a real onseck. Amazingly, he had suffered only minor cuts and bruises, and had even escaped the worst of the radiation because of his lead underwear.

Gathering courage the meeting forged into Committee Reports, fighting off the first wave of starving dogs as they did so.

Pseudo-LHE and Blast-from-the-past Guy Consolmagno and the real LHE, Brian "Dago" Pinette, had been lined up along a stray beam of Gamma-type quarks, and had suffered a most astounding personality interchange.

In tandem they reported 273 dollars in outstanding debts and 500 dollars in not so outstanding debts, while pointing out that LHE isn't really a committee at all.

Some administrative trouble with the library system was reported by Libcomm, which was amazing since Libcomm had now been atomized twice.

Pseudo-ROSFAP Ruffa presented the library with Collapzine from Champaign, Illinois. There was a peculiar motion but it was not seconded and the onseck forgot it.

In a more religious vein we reaffirmed our faith in the Great Pumpkin, although it was unlikely that a single unmutated pumpkin had survived the holocaust.

Pseudo-ROSFAP Ruffa again grabbed what was left of the floor to point out a plug for MITSFS in an article about CHUSFA in the Daily Illini from U of Illinois.

Jourcomm reported that there were no intact typewriters left in the civilized world, but that he was working on the problem and that the first post holocaust TZ would be out RSN. (Real soon now.)

Spitcomm Guy Consolmagno reported that when Tom Spizak turned 18 they abolished the draft.

Feeling more confident and cheerful moment by moment, the faithful MITSFSians continued the time-hallowed ritual, untarnished by war and destruction, shining bright in a hopeless world. They slid through old business algol into old business like nobody's business.

A miller motion was made, seconded, and voted on. It passed by half a boomerang, but shouting "I shall return" it failed by the inverse skinner rule.

In a string of minicults, GC got a questionnaire asking him to support universal gun ownership, Ruffa contributed learned theses on the imperturbability of the elevator operator, and Murphy's law with corollaries. GC reported that someone had said that the Hancock building doesn't just go up but really whooshed as well. Malcolm Y suggested a good hack: break a mirror at the base of the Hancock.

GJG pointed out the fine job done on the photography of Carl Sagan's off-color Italian Hand Gestures. Wechsler regaled the crowd with funny things to do to the toilets in the Prudential Building. Guy Consolmagno told a funny story about a building where the sewer and the storm drain were the same piece of pipe. I don't remember it but it had something to do with an eyewash. Wechsler explained how some people in South Dakota were going to catch Bigfoot using used tampons as bait.

Finally we realized that the boomerang looked like a banana and we had to adjourn to go find our dinner. We were confident now that we had absorbed enough obnoxiousness to stave off any radioactivity we came across.

It was a new world. I went over to the coffeehouse to get a donut, then turned to face it.

\end{document}