\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Minutes of the Banana Colored Meeting 

Friday, June 25, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

Minutes read. They were amazingly interesting and entranced the MITSFS for half an hour. Yup.

Motion to be deeply moved by the minutes. Motion passes by something higher than 3 to 3 to 3 +Spehn.

\goto{Committee Reports}

Speaker to Ingres: Shelfdex needs holes. The Onseck strikes himself in the head one week minus 24 hours from then as he realizes he forgot this. Inventory will be on Saturday the 33rd of June, as Sunday is the 4th of July.

Phonecomm: no, we haven't sent out an issue of the magazine since you sent your story to us.

Pianocomm: Morgan Gribarov is going through the long, grueling, extremely painful process of becoming a keyholder.

Long discussion follows, ending with:

Jamie: ah, but will she be fanatically devoted to the skinner? And if so, is she armed?

Seth: she can be trained. She is young and malleable.

\goto{Old Business}

Connie: as of July 1st, I will be an associate member of SFWA. Someday, I will donate a copy to the MITSFS, but they've only given me one copy, and at 3 cents a word, 2400 words, my money will get eaten up really quickly.

Jamie: Isaac Asimov is still dead. Paul- did the committee to find out whether Asimov is still dead actually do anything?

Paul: yes! But I can't tell you- you're not dead.

Jamie: I define everyone in the room to be dead.

Paul: okay. Isaac Asimov is in the room.

Jamie: Seth, I'm appointing you to be Algolcomm.

\goto{New Business}

Remind Jamie to look up Waldenbooks in the Yellow Pages.

\goto{Future Business}

Motion to censor and commend Fuzzy Heather for her banana colored drugs. Passes 4-4-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1733 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}