\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 9, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, LHE and Pseudo-Skinner, presiding; Scott Kullberg, Onseck, recording.

SG: Move to approve the minutes as done.

Motion chickens >2 to >2 to >2 +Spehn.

\goto{Committee Reports dronf}

Pseudo-Moocomm: Neil Jordan, director of Crying Game, is directing a movie based on Anne Rice's Interview With a Vampire.

Mobcomm: Books are being processed. If you can process, do it. Inventory will be the weekend after Patriot's Day. Keyholders and keyholder wannabes should show up and work.

Picniccomm: Sent off the letter to Hal, best date is probably 05/02.

Moocomm: Nothing. Consensus is that Crying Game is better than Unforgiven, but I can't see the relevance here.

\goto{Old Business dronf}

It's apparently boring to be 18.

Motion to censure the Librarian.

Motion to condemn Wayne Brells for his sex life with bicycles.

Superman is still dead. So is Isaac Asimov (we think). Someone is going to be killed to go and see and come back in a seance to report. We don't know Isaac's number so they'll carry a beeper.

Maybe Superman isn't dead either.

Usual.

\goto{New Business dronf}

Minicult: Israeli phone company is selling a phone to Orthodox Jews by sealing it in a plastic bag and writing "Telephone Kosher for Passover."

Motion to label Paul "Kosher for Passover." Passes >2-2-2 +Spehn.

SG: Motion to reaffirm the Society's faith in the Great Yellow Matzah. Chickens 1->2->2 +Spehn.

More Sherrian anagrams: last week was "leash in rear," this week is "hire arsenal," "in rehearsal," and "a real shrine."

Motion to reaffirm the Society's faith in the Great Banana-Colored Maypole. Fails due to lack of second.

Miller motion. Fails.

Second Miller motion! Fails for lack of second!

>2 Miller motion!

P: You mean it's Miller Time?

Motion chickens >2 to >2 to >2 +Spehn.

Banana-colored Miller motion. Passes >2-2-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17(>2) SST dronf.

\vspace{18pt}

\centerline{If you do not want a thing heard, do not say it. -Klingon proverb}
\centerline{Scott Kullberg, S. G. Onseck}

\end{document}