\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 29, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck fnord, recording.

We're offering 5 million dollars to new MITSFS members- NOT!

Minutes read.

No! Not another Pern book!

\goto{Committee Reports}

\goto{Old Business}

Seth: I'm older than I was yesterday.

Leah: we all are.

Jamie: I'm not older than Seth was yesterday!

\goto{New Business}

Seth: 5 million dollar program to convert non-Jews to Judaism.

Jamie: Marcus, you should raise 5 million to make people Peruvian-Egyptian.

Seth: if anyone wants to become Jewish, tell me so I can get a commission.

Marcus: only if we get a share of the profits.

Jamie: one word: kickbacks!

Jews aren't a disadvantaged minority. They can't get scholarships.

Leah: however, red haired, left handed women can...

\goto{Future Business}

Banana. No.

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck fnord}

\end{document}
