\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 7, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

Jamie: Minutes?

Marcus: How much of the minutes do you want to hear?

Jamie: Will the Onseck please read some reasonable amount of the minutes?

Minutes read.

Jamie: Right. Are there any comments concerning the minutes.

...

Jamie: Right. Are there any motions concerning the minutes?

Tony: I move that the new Onseck should shorten the minutes.

Leah: Seconded.

Jamie: All in favor?

Motion passes 10-2-0 +Spehn.

\goto{Committee Reports}

Jamie: Committee reports. Picniccomm?

Jamie: We should report on the results of the elections.

Tony: Skinner, Onseck, Vice.

Jamie: That will show up well in the minutes.

Tony: And the Lord High Embezzler. He's dead.

Leah: And who's going to pay us back?

Tony: Picniccomm has not been paid back. That should go in the minutes.

Derrick: Picniccomm should fill out a reimbursement form.

Jamie: Picniccomm has and has been given a check.

Jamie: Marcus, sign those out.

Marcus: Slave, slave, slave.

Pianocomm: We have a new keyholder. Leah is a new keyholder, and is also associate VGG with her own power to do VGG things unless overruled by Ellen, and should be receiving a physical key at some point so she can hold the library open. Tony is currently busily processing books, and Tod will be doing something, and is doing a bunch of reviews.

Jamie: Any more committee reports?

\goto{Old Business}

Jamie: Do we have the usual motion?

Tony: Second.

Leah: Usual second.

Jamie: Usual vote, usual result.

Marcus: What about the usual debate?

Jamie: The traditions have grown lax.

\goto{New Business}

Jamie: New business. Is there any new business?

Derrick: Miller motion.

Someone: Second Miller motion.

Jamie: Motion passes, some large number which I forget to some smaller number which I forget to three which I forget plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourns a bit after 1700 SST fnord!

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}