\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 2, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: The reading of the minutes!

SK: No tape means no minutes. Deal.

JM: Meeting existed and was taped.

SK: I went to find the tape and it wasn't there. It wasn't there means it doesn't exist. No tape, no meeting.

JM: Scott, what does your button say?

SK: "Another Triumph for Truth, Justice, and Automatic Weapons."

JM: Motion to approve the minutes as "Another..."

Motion passes 30-1-1 +Spehn.

\goto{Committee Reports}

SL: Committee reports.

Moocomm: We went, we bought, there are the boxes. Processing spree RSN.

Panthercomm: Up to date Pinkdex exists. Nathan did it.

Pianocomm: Marcus gets his key. Todd should probably be found something else to do RSN and a key should be found.

JM: He could write things for the TZ.

SL: Inventory RSN. Could be done 16th, 17th, 18th.

Moocomm: Blade Runner, Buckaroo Banzai.

Ass.comm: She still lives.

??: Prefrosh should be weirded out.

\goto{Old Business}

SHRIEK!

JM: Old business.

SL: I've been exiled to Iowa. Address by request. Email possible.

SL: Isaac Asimov award. (Should be posted- read it if you care.)

\goto{New Business}

Algol.

SL: Corrupt prefrosh.

DSK: Corrupt them even more.

(Nothing else worth mentioning happened.)

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}