\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 22, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Chris Hooker, LHE and Pseudo-Skinner, presiding; [Unknown], Onseck, recording.

Thunk. Dink. Dink.

Minutes read.

\goto{Committee Reports}

Making a lot of copies of Twilight Zine would be really expensive. Surprise. But advertisers might pay something. If they don't know what they're doing.

Sean: so they have some sort of mechanical arm with a laser scanner that swings down the aisle- maybe we should make one of those for the MITSFS. Just type in the name of the book you want, and the arm will go and get it- then we could pack the shelves really tight!

\goto{Old Business}

Harvard has an SF collection- they stored it in a vault in 1955 and threw away the key.

At this point a motion was made to barcode the minutes for 24 hour retrieval... it chickened, though.

\goto{New Business}

Dink.

Chris: I'm doing something wrong.

Sean: you need to hold it at the center of gravity.

Leah: yeah, I can smell that...

Marcus: isn't making fire in the MITSFS punishable by defenestration?

Chris: well, I didn't actually start a fire... yet...

Banana! Second. Hey, that's not a motion!

Keynote speaker at the Marvin Minsky something or other was Arthur C. Clarke, who spoke via telepresence from Sri Lanka, and he said "oh aba eh shra..."

\goto{Future Business}

Banana.

Banana banana.

That's a second banana.

Motion passes. \bing

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
