\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 5, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck fnord, recording.

Minutes read.

Motion to set up a 5 million dollar program to convert the minutes to Judaism? Motion passed!

\goto{Committee Reports}

Booksalecomm: we're having a booksale tomorrow. Hopefully there'll be a couple of people there besides keyholders. I said hopefully. On the other hand, our advertising has been fairly lame.

Chris: my guess is that at least one non-keyholder will show up.

Jamie: want to take bets on that?

Chris: but if they buy a life membership...

Jamie: then we'll make a 70 dollar profit.

Chris: minus the 40 keyholder hours...

Jamie: but I only care about the hours I spend.

Section on jerking off in the library deleted by the Thought Police.

\goto{Old Business}

Janice Eisen got a picture in Locus...

Jamie: Leah's getting pretty old.

Leah: no I'm not! I'm probably the youngest person here.

Jamie: how old are you?

Leah: 18.

Jamie: oh, you're senile.

Leah: yeah, well, you're more senile than I am.

Chris: he was probably more senile when he was 18.

Marcus: he probably has been more senile all his life.

Jamie: wait a minute- can you be born senile?

Leah: that's what's called your second childhood.

Jamie: but can you have your second childhood during your first?

\goto{New Business}

Leah's pretty new.

Booksale tomorrow!

\goto{Future Business}

Motion to set up a 5 million dollar program to convert bananas to Judaism? Motion failed...

Section during which Dark Jen was harassed by Jamie deleted by the Thought Police.

Motion to make poisonous darts from bananas?

\bing

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck fnord}

\end{document}
