\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 16, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: Minutes of the previous meeting.

SK: #include /afs/athena/user/s/e/sekullbe/mitsfs/min4-9.tex

SL: Motions concerning the minutes?

The minutes are not approved as "Thrilling beyond belief" but are approved as something inaudible.

\goto{Committee Reports dronf}

DisappearingSkinnercomm: the Skinner is being exiled to Ohio.

Moocomm: Movies suck.

...mumble...

SL: I had a character like that in a run once.

P: for arbitrary N, Sherrian has a character who N.

\goto{Old Business dronf}

SL: The Skinner is 22 and thinks she is ancient.

Eliminating the Skinner's thesis committee is viewed as a Good Thing.

Usual.

\goto{New Business dronf}

JM: Move to commend the comics for not bringing back a banana-colored Superman?

P: One of the Supermans is yellow.

SEK: Reality is not relevant here.

JM: Doesn't matter, it's not a suitable banana yellow.

SL: A motion is on the floor with the word "banafnordna" in it. Is there a second? (There is.)

SEK: The second banana isn't here.

Motion passes 9-6-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST dronf.

\vspace{18pt}

\centerline{The worms crawl in}
\centerline{The worms crawl out}
\centerline{The worms post to the net from your account}
\centerline{Scott Kullberg, Onseck}

\end{document}