\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 12, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jennifer Shih, Vice and Pseudo-Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

JM: Will the Onseck read the minutes? We don't have an Onseck but we do have minutes.

(The Onseck was off playing paintball at the time.)

Minutes read.

JM: Motions concerning the minutes?

??: ?? Motion passes some-none-none +Spehn.

\goto{Committee Reports}

JM: Mobcomm run in about a fortnight or so.

JWS: Any other committee reports? Do we have any other committees?

NW: I'm almost done with Pinkdex.

(Applause.)

JM: Telzey Amberdon: the Skinner and I are engaged to be married at the picnic. We should be getting a marriage license sometime soon.

(Applause.)

P: Am I doing the ceremony or not?

JM: No.

JWS: What happened to Mark?

P: Ve... took care of him.

JWS: Ahhhhhh... dry run.

JM: any other committee reports? ...bing and say "old business."

\goto{Old Business}

JWS: Old business? ...would you like me to demonstrate another bing?

P: Oh, no, thanks, I couldn't handle another one.

JM: You can with the Vice; she can always get another bing out of you.

P: Could you put that in the form of a motion?

JM: Yeah... consider that a motion.

Motion does something, 0-0-lots and lots and lots +Spehn.

\goto{New Business}

JM: Motion to commend the Vice for binging about as well as a banana.

JWS: But bananas don't bing!

P: A banana's too floppy!

JM: Motion amended to "Motion to commend the Vice for binging better than a banana."

Motion passes 6-11-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}