\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 24, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; [Unknown], Onseck, recording.

Thump! Struggle, struggle, \bing Meeting called to order in spite of resistance from Paul.

Minutes read.

Connie enters the room. The assorted members of the MITSFS fall down and worship her.

Jamie: hey! a real person!

Marcus: what, we're not?

Jamie: exactly.

\goto{Committee Reports}

A long, drawn out discussion about shelves, in which the MITSFS is referred to as a cancerous growth...

Seth: Star Trek this Saturday. The stunning conclusion to the stunning season finale that was stunningly unconcluded... (Editorial comment: it was stunningly unstunning.)

Connie: a fourth Star Trek coming up- current title suggestions include Star Trek: You Can't Kill It With a Stick, Star Trek: We're Going to Make a Lot of Bucks Out of This One Too, Star Trek: Better Than a Poke in the Eye.

Connie: Lois and Clark coming up too... there's a two sided triangle. Lois loves Superman, Clark loves Lois...

Jamie: and Superman loves Clark?

\goto{Old Business}

\goto{New Business}

A matrix vote is set up. The vote to have a matrix vote fails, as do the other two motions.

\goto{Future Business}

Connie: according to my friends who aren't geeks...

Marcus: what, non-geeks exist?

Paul: motion to form a committee to kill all non-geeks with a banana.

Motion passes by skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
