\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Minutes of the Banana Colored Meeting 

Friday, July 9, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

Jamie: Fermat's Theorem can indeed be undecidable, as long as it's unprovably undecidable.

Leah: something about orthogonal.

Jamie: I'd love to go orthogonal with you sometime, Leah, but currently we're having a meeting.

Motion to condemn the skinner for doing obscene acts. Chickens 4-4-4 +Spehn.

Motion not to decide the minutes. Passes 11-2-0 +Spehn.

\goto{Committee Reports}

Inventory happened.

Mobcomm: tomorrow, meeting at the MITSFS at 10. We need directions from Adina though.

Leah: I'd come except that there might be a very loud party in 3rd East tonight, and I might not sleep.

Jamie: you can sleep in my room-

Jamie cracks up.

Jamie: I couldn't say that with a straight face, sorry.

\goto{Old Business}

The skinner made a pass at Leah and was repulsed.

Motion to condemn the skinner. Inverse skinner rule- commend.

\goto{New Business}

Flatliners is interesting and different.

Jamie: different from what? Jurassic Park? I was expecting that!

Seth: you know, when I was a kid, anything I didn't like I called "interesting."

Jamie: as long as I'm going to be kept awake by the music, I might as well have some food.

Seth: well, will you be parallel or orthogonal to the food?

Jamie: potato chips don't have a good defined direction.

Seth: so clearly you must sum all of the vectors-

Seth suddenly started speaking in Albanian at this point.

\goto{Future Business}

A long time passes before Jamie got Seth unalbanianed in order to make a banana motion.

All in favor: millions. All opposed: negative fourteen. All chickens: none.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
