\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 5, 1993

[Most likely; these minutes were undated.]

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: Minutes of the previous meeting; we do not have any minutes.

(Mumbling about the computer and the tape recorder.

??: Motion to declare that the minutes are in fact not here.

Motion fails for lack of amusement.

\goto{Committee Reports}

SL: Moving on, committee reports!

SL: What is the official job title for the people who are supposed to be maintaining Pinkdex and (???)? Is there a job title for that?

JM: There's a job title for everything.

KJ: Last I heard, it was Panthercomm.

SL: I thought Panthercomm processed books.

JM: Panthercomm doesn't do (???).

SL: Well, at any rate we will be needing someone to replace the current Pinkdex...

JM: ...with an accurate one!

SL: ...person with someone who actually exists. If anybody is interested in getting involved with the Pinkdex, God forbid, come talk to me and we'll see if we can find Susan because learning to do that might be a reasonable keyholder project.

JM: (???).

SL: Moocomm: is there anything interesting and science-fictional out there?

(A resounding chorus of silence.)

SL: LSC is doing, and this is vaguely fantastic, but LSC is doing Buffy the Vampire Slayer and we are organizing a group of people to protest this as it glorifies violence against Undead-Americans with the... Seriously!

JM: But if no one hunted us, there wouldn't be any challenge!

SL: We are taking as our theme "Out of the Coffins and Into the Streets!" and we'll be making protest signs and doing something noisy in front of 26-100. Send me email if you would like to participate in making fun of absolutely every politically correct cause, most of which I personally support.

JM: Are you a vampire, or are you an evil wizard?

DSK: I am NOT an evil wizard!

??: Are you sure?

SL: In other Assassin-related commentary, the skinner is currently writing an Assassin game which will run on the 12th of February and I will very much appreciate people pouring food and Diet Coke and things in the appropriate orifice. Ever pour Diet Coke in your ears? It's a singular experience. And I'd like to remind people not to have secret meetings of any kind in the library, because if we end up doing Assassin stuff in here, Rob Fermier will start telling me how to run things, and we can't have THAT! Any more committee reports? Anything else particularly useful or pertinent?

SL: Pseudo-Analogcomm: all keyholders should request their spring hours.

JM: Pseudo-Jourcomm: people should write things, like reviews.

SL: Would she be interested in publishing my thesis?

JM: I doubt it.

SL: It's got science in it, and I made most of it up.

JM: Tell you what, when you finish it, give it to me and I'll read it and publish a review.

(What will be published?)

SL: We'll publish almost anything we can get. I once almost published a list of my old Baybank receipts. Of course, that was when I was LHE and the record of receipts apparently had some value to someone...

(Mumble.)

SL: How dumb do you think I am?

(Honest answers deleted.)

SL: Do you think I'm dumb enough to let you publish a review of my thesis in TZ? My thesis as a work of art stands alone; my thesis subjected to vitriolic Jamieflaming is something else.

(More thesis babbling deleted for irrelevance- I didn't even listen to it, actually.)

\goto{Old Business}

SL: Old business... well, Ken and George are here, they're pretty old.

\goto{New Business}

SL: Any new business?

(The banana hanger is discussed.)

SL: I think I'll get one of these for someone as a wedding present.

SL: New business, there are freshmen here and they're pretty new.

JM: They're getting bruised and rotten.

SL: Do they have freshmen holders?

JM: Right here.

SL: That's a banana holder, not quite big enough for freshmen. Oh well.

JM: We can dehydrate them first and make them smaller.

SL: Is there anything else we need to do?

KJ: BANANA!

(Second!)

KJ: Anyone want to be second banana?

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}