\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

da MINNITS!

the EXPURGATED version... the one without the gannet; I don't like them, they wet their nests.

Friday, March 5, 1993

"If you do not want a thing heard, do not say it." -Klingon proverb

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: Minutes of the previous meeting! Onseck...

(A time warp occurs.)

SEK: (Reads the minutes; cuts them short because they are very boring.)

SL: Are there any motions concerning the minutes?

(Mumble.)

SL: There is a motion on the floor to commend the Onseck for limping and to assume this has something to do with the minutes.

Motion fails 4-6-2 +Spehn.

(The onseck enters.)

SL: It's the Onseck!

(The onseck dives for cover.)

SEK: Where?!

(A time warp occurs.)

(Things get really recursive here; let's move on before people get confused- I'm a VI-3 and can deal, but there are human weenies about.)

\goto{Committee Reports}

SL: Committee reports!

SL: Mobcomm RSN. Someone should figure out the New Book List and do it. Adina can show you how.

(Assignments are handed out to the keyholder wannabes.)

SL: Inventory RSN, that counts as the better part of a keyholder project. Inventory as soon as we get a Shelfdex, and NO SHEET METAL! Count everything; lunch provided.

(Mumble.)

SL: There's a motion on the floor to rotate Paul 90 degrees and render him imaginary.

Motion passes N-j-0 +Spehn.

Picniccomm: the frosh are railroaded, cars are demanded, the van is lamented. Tell your friends with cars to come.

SEK: Start making friends with cars, too- that's even better.

Moocomm: Nada.

Greasecomm: People should either go or not go to the ASA meeting and vote or not vote for twinkies depending on who you believe.

(Mumble, mumble.)

#include "elements"

(Mumble, mumble.)

\goto{Old Business}

SL: Old business.

(None.)

\goto{New Business}

SL: New business.

P: Minicult- the two guys claiming leadership of the Waco cult decided to see who could resurrect the previous leader in order to prove who was really Christ. When it didn't work they shot each other.

Miller motion...

Miller motion...

SL: Meeting adjourned 1705 SST.

Miller time...

\bing

\vspace{12pt}

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}