\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 17, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

Will the Onseck please read the minutes? The onseck is not here; however, we do have the minutes...

Leah does an amazing job of reading and shortening the minutes. She conveniently skips certain revealing comments about spools of copper wire...

\goto{New Business}

Does anyone have any new business, or is this one of these really pathetic meetings where nobody even comes up with any clever banana motions?

(Editorial comment: meeting needs onseck, badly.)

Leah: probably because of you.

Seth: but that's okay, you're the skinner. Even if you're a gully dwarf.

Jamie: I define it to be your fault, Leah.

Leah: you can't do that!

Jamie: I'm the skinner. Of course I can.

Leah: you're pulling rank on me!

Leah refrains from the whip on Jamie...

Move that the Skinner couldn't make a banana if he tried.

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
