\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Minutes of the Peppermint Frappe with Peppermint Syrup Meeting 

Friday, June 18, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

Minutes read. They were amazingly interesting and entranced the MITSFS for half an hour. Yup.

ESD: Robin Hood, prince of dweebs. (The movie, not the character.)

\goto{Committee Reports}

Inventory as soon as we have a shelfdex, now that we have Mancinicomm and Speaker to Ingres working together...

Possibly a Mobcomm run in the near future. As soon as the onseck stops being lame.

\goto{Old Business}

What? Real business during a MITSFS meeting? Bad MITSFS members!

\goto{New Business}

Larry is going to be donating 1200 dollars or so, and his company will donate 4x that. Yay! Larry will be an official "Lord" member... to be given a tract of land- part of the Blue Hills.

The Blue Hills were given to MITSFS in 1876 for their aid in stopping Harvard from annexing Boston.

Motion to divide the MITSFS among its members.

Jamie: friendly amendment to change that to skinner.

Leah: you want us to divide the skinner?

Motion fails by skinnerial decree.

Let's give Heather a peppermint frappe with peppermint syrup.

\goto{Future Business}

Move to feed a banana to the onseck. Passes 10-4-1 +Spehn. Ack!

\bing

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
