\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

Minutes of the Plain MITSFS Meeting

Friday, July 30, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order (Jamie: July 23rd- Me: July 30th. Jamie: July 30th already? Right...), 1700 SST, Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck fnord, recording.

Jamie: will the onseck please read some kind of minutes?

Onseck: what, you mean there was a meeting last week?

Jamie: right, are there any motions concerning the extremely short minutes?

Jamie: do we have any motions concerning the minutes?

Jamie: do we have a second?

Jamie: all in favor?

Onseck: how am I supposed to record that in the minutes?

Jamie: carefully. Motion does something x-y-z +Spehn.

\goto{Committee Reports}

Fweekcomm: Marcus is Fweekcomm. He's going to set things up for Rush. Everyone should sign up- the undergraduates should sign up for lots of hours, the graduates should sign up for reasonable hours, other people should hold normal hours- we don't want people coming in and seeing the adults and getting scared. Grad students aren't grownups, since they're still in the ivory tower.

Pseudo-jourcomm: we're going to have a Twilight Zine in two weeks, so people should write lots of things, or we'll put a page in saying that you were lame.

Lots of random organizational TZ stuff and argument, deleted for easiness.

Does anyone have any interesting committee reports with the word banana in them?

\bing

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck fnord}

\end{document}