\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 26, 1993

"If you do not want a thing heard, do not say it." -Klingon proverb

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: Minutes of the previous meeting! Onseck...

SEK: (Reads the minutes; cuts them short because they are very boring.)

SL: Are there any motions concerning the minutes? ...there are no motions concerning the minutes.

SEK: Motion to make a circular motion with the minutes.

(A circular motion is made with the minutes on the floor.)

Motion passes lots-2-4 +Spehn.

\goto{Committee Reports}

SL: Committee reports!

SL: The Vengeance Fleet is retiring. Ellen Kranzer is very busy and needs to hand in her key. Anybody who is detail-oriented and is going to be around and involved in MITSFS for a while and is looking for a key or something else to do to be useful, preferably existing keyholders, but possibly if you can convince me you're really responsible and could learn how to do this, come talk to me and I'll see about making you die Vergeltungsflotte. The job involves a fair amount of work, going through people's sheets looking for overdue books, looking for fines, looking for keyholders who sign things in and out for members incorrectly and socking them with key fines, etc. It also involves sending letters to people who have overdue books out. It's a fairly time-consuming job and takes some time to get right, so if you're going to be around for a couple of years, you might want to think about it; if you're not, learn to do Pinkdex and help process books or something. There are people currently learning to do Pinkdex: Todd and [unintelligible] when you get a chance. Any more committee reports?

SEK: Moocomm: nothing relevant until the end of the month (Time Bandits, Blade Runner director's cut, and Buckaroo Banzai).

SL: Babylon 5 wasn't too bad; it was much more interesting than my thesis.

SL: The skinner is stupid and is writing another Assassin game [sordid details deleted].

??: Move that the skinner should learn to say NO!

SEK: I thought the proper phrasing was "Fuck off, I don't have time."

SL: Sarath Krishnaswam(yi) taught me to say "fuck that, I'm too busy." I obviously haven't learned. As a matter of fact, all existing copies of the parody of "I'm Just a Girl Who Can't Say No From Oklahoma," which was written about me at some point when I was serving on the High Council, have been destroyed, I hope.

SEK: (Evil laugh.)

SL: And that motion fails by skinnerial decree.

SL: We need to Mobcomm RSN... ha... I'm a little timid to get back in a car with MITSFS people as Karl and Adina and I got in an accident last time. We also need to do inventory real soon, but I have no idea when we should do that and I think we kind of need an updated Shelfdex.

SEK: Let the record show, and it will since I write it, that I'm offering my bicycle helmet to the Mobcommers. Mobcommmies? Mob of Commies? Run for the hills!

SL: Wonderful. Thank you, Scott.

\goto{Old Business}

SL: Old business? There is no old business. George is here, he's old. Ken is usually our old business. Oh yeah, on USENET a new newsgroup appeared: "alt.fan.ken-johnson".

\goto{New Business}

SL: Okay, is there any new business?

GF: There was a Boscon.

SL: When was it?

GF: Last weekend.

SL: Who went?

GF: Connie.

SL: As a fan or in her newly-found authorial capacity?

GF: Just as a fan.

(Unintelligible due to tape noise.)

??: Motion to play banana-tag.

???: Could you tell us the rules?

SEK: We'll tell you the rules after we pass the motion.

Motion passes 6-2-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}