\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 16, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck fnord, recording.

Minutes read.

Motion that last week's meeting was more interesting than this one is likely to be. Motion passed.

\goto{Committee Reports}

Jamie: Mobcomm?

Marcus: oh, yeah. Mobcomm happened.

Seth: and we owe the Ground Round 2 dollars in tips, or they will hunt us down and kill us and be really surly to us.

Jamie: that's true, plus we have decided that it is even more difficult to come up with Peruvian-Egyptian jokes than previously supposed.

(Editorial comment: thank god.)

Mortcomm: Drew Whyte died. I don't know who he is.

\goto{Old Business}

Motion to condemn Wayne B'Rells for his sex life with bicycles.

Paul: motion to censure bicycles.

Motion to x.

Paul: motion to censure x.

This goes on for a couple of motions.

Me: motion to make a matrix vote with all of Paul's censure motions.

Jamie: but you can't take a determinant of an 8 by 3 matrix.

Someone: then it would be undecidable, wouldn't it.

Jamie: right. All the motions are undecidable.

Someone: usual result.

Jamie: actually, a very unusual result.

\goto{New Business}

\goto{Future Business}

Jamie: right- will someone end the meeting?

Meeting deteriorates into a cacophony of MITSFS members attempting to sing. Finally, Paul inserts banana into the element song, thereby ending the meeting.

\bing

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck fnord}

\end{document}
