\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Minutes of the Large Reptilian Beings Meeting

Friday, June 11, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
"Are we going to have a meeting?"

MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

Minutes of the last meeting: "Minutes of the last meeting: Jamie will be doing inventory alone..."

Move to rotate the minutes through the imaginary airplane. Chickens 4-4-4 +Spehn.

\goto{Committee Reports}

Moocomm: Derrick is head lemming for a trip to Jurassic Park.

\goto{Old Business}

ALGOL.

\goto{New Business}

We're going to go pick up a lot of donated books sometime soon. Using a copy of the pinkdex.

\goto{Future Business}

Matrix vote!

Miller motion: 9-1-6, banana motion: 0-0.5-0, matrix motion: 10-5-1.

Determinant: -25.5. We're not having a matrix vote after all...

Miller motion. Passes an incredibly large number-an incredibly small number-a mediocre number +Spehn.

\bing

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
