\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

Minutes of the Secret Sacred Society Wars Election Meeting

Friday, April 30, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Heyy! Meeting starts halfway through the elections.

\goto{New Business}

(Sounds of furious scribbling, and Jeopardy in the background.)

Jamie: Thank you Sherrian, Jeopardycomm.

Jamie: People are spending a long time thinking of something witty to say.

Herb: Or rather, ways to insult Sherrian.

(Sherrian reads votes. Thark and Sherrian, Widgetess of Gor are in front early on. The Widget Gnomes of Zurich fall far behind... Shoot, Jamie seems to be
another popular vote.)

(Jamie spends eons counting votes.)

(Jamie tickles Sherrian.)

Sherrian: Shriek!

Jamie: Shoot him! (at the random person who poked his head into the meeting)

Sherrian (reading votes): Shoot him now, shoot him now! Point one.

Sherrian: Oops, I missed. Point one.

Sherrian: Sherrian stripped, washed, and sent to somewhere unspeakable, .01.

Sherrian: Shooting Jamie is a good idea, point one.

Jamie: That's Sherrian too.

Sherrian: No, its not!

Sherrian: Heyyy, Thark! Point nine.

Jamie: Okay, Thark won.

(Screams of joy, as MITSFS members realize Sherrian won't be elected to LHE.)

Sherrian: Now its the time to elect someone to be vicious, otherwise known as the Dark Jen look-alike contest.

Sherrian: Nominations?

Someone: The scantily clad dragonrider.

Jamie: The non-decrepit redhead.

(Jamie is nearly decapitated by Elizabeth.)

Someone: Denise the Vampire.

Jamie: Second!

Jamie: Telzey is appointed, not elected.

Someone: Telzey is usually paid off, not appointed.

Sherrian: Jamie's Telzey is the cutest little thing...

Jamie: Who Sherrian wanted to become Telzey a month or so early.

(Bad whistling.)

Sherrian: Jamie, what on Earth do you think you're whistling?

Jamie: Nonsense. You should send email to keyholders@athena saying we need people with cars. 

Sherrian: Sherrian, stripped and used as a tent, .1.

Sherrian: Denise, Widgetress of Gor, .1.

Sherrian: Lessa, the whore of Benden, .6.

Sherrian: Open Fire, .05.

Jamie: It's Denise.

Sherrian: Now, who should be trusted with the awesome responsibility of skinner?

Someone: Nobody.

Someone: I nominate the gully dwarf.

Sherrian: Derrick Thunderbunny Kong!

Someone: More widget jokes!

Sherrian: No more widget jokes. It was the worst experience of my life.

Jamie: Exactly, that's why we're trying to repeat it.

Sherrian: Yeah, like the stuff in my fridge.

Everyone, in chorus: The stuff in Sherrian's fridge!

Herb mentions his twins.

Sherrian: They must be assassin children - they're already having secret meetings.

Herb: I have .gif files in my directory of the sonograms.

Sherrian: One Widget to Rule them all, .1. One Widget to Bind them, .1. One widget to bring them all, .1. And in the darkness bind them, .1. In Jamie, where the shadows lie, .1.

Sherrian: Gully dwarf, not more than .2.
	
Sherrian: Who are you appointing skinner, Jamie?

Jamie: Me.

Dave: Sucker!

Jamie: Elections finished!

\bing

Jamie: Move to have Leah shoot Elizabeth.

Everyone except Elizabeth: Second!

Jamie: More than I can count to none to none plus Spehn.

Jamie: Any more new business?

\goto{Future Business}

Sherrian: Rabbits have no tails at all.

Jamie: Just a bloody stump, dammit.

Herb: Miller motion.

Jamie: Fails!

Herb: Second Miller motion.

Jamie: Motion passes 5 to 3 to purple plus Spehn. 

Herb: That was a long meeting.

(Sudden time warp to sometime much nearer the beginning of the meeting.)

\goto{Old Business}

Jamie: Hail, Queen of the Widgets.

Sherrian: No, that's Laura Baldwin, dammit.

Sherrian: Shall we jump ahead to the new business? Cause no one does the old business algol anymore...

\goto{New Business}

Sherrian: Nominations to the position of onseck.

Jamie: I nominate Sherrian! In an effort to recycle the Star Chamber.

Sherrian: I nominate Marcus.

Herb: No, no, bad idea.

Herb: I nominate Atlascomm. I nominate Tarl.

Sherrian: I nominate the chair of graduate admissions at the University of Iowa.

(More Jeopardy.)

Jamie: It is traditional to try to write down something clever - most people fail, personally, I'm not even going to try.

Jamie: So, clearly on days when Janet can't make it to elections, it should be the duty of Picniccomm to go to LaVerde's and buy candy in order to pass it around.

(The voting is furious; Sherrian, Queen of the Widgets, with a narrow lead over Atlascomm and Tarl...)

Jamie: For Jamie we have .15, for Tarl, .95 - Tarl is beating me. 3.05 for Marcus, and 3.75 for Sherrian, Queen of the Widgets.

Herb: We have to title Sherrian's picture Sherrian, Queen of the Widgets, 92-93.

(The gavel block enters the running.)

At this point, the tape ends, thankfully not recording the gruesome details of the onseck's election...

\vspace{12pt}

\noindent
Meeting adjourned, 17-18-10 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}
