\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 10, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; [Unknown], Onseck, recording.

Will the Onseck please read the minutes?

There was a conspicuous lack of minutes.

Are there any motions concerning the nonexistent minutes?

Motion passes 6-5-4 +Spehn!

\goto{Committee Reports}

Fweekcomm: Rush is over. We made about 300 dollars less than we should've.

Pianocomm: Leo Gonzalez and Mark Rouscoulp are working toward their keys, as have been Jessie and Arifa (in theory).

Shelfcomm: we are getting new shelves RSN. We can get unfinished wood shelves really cheap. If anyone knows how to finish shelves?

Seth: we could drop them off a tall building. That would finish them.

Jamie: right. We're going to drop Seth off the top of a tall building.

Leah: and that will finish him.

Jamie: then he'd be flat and we could use him as shelves.

\goto{Old Business}

Move to censure Wayne B'Rells for his sex life with bicycles?

Jamie: what shall we censure Leah S'chechter for?

Seth: her sex life with spools of copper wire?

Jamie: I'll second that one.

Motion passes 8-4-2 +Spehn!

\goto{New Business}

Someone should write up the old business clue to update the old business algol...

Marcus: Isaac Asimov is still dead.

Jamie: we have a committee looking into it.

Marcus: well, they're dead too.

Jamie: well, yes, but that doesn't change much where Paul is concerned.

Unidentified voice: Asimov was abducted by Elvis.

Jamie: our committee has said nothing of this. What information sources do you possess?

Voice: you don't need to know.

Jamie: but the question is, is he dead?

Voice: that's not important!

Jamie: our committee was made solely to look into whether or not he was dead- if he was abducted by Elvis or aliens or whatever is totally irrelevant, it only matters whether or not he's dead.

\goto{Future Business}

Motion to drop an unfinished bookshelf into a bottle of banana colored paint. Motion almost fails for lack of a second but is rescued. Motion fails 4-7-1 +Spehn.

Seth does a horrible rendition of rabbits have no tails at all...

Jamie: congratulations, you've induced Leah to whimper.

Marcus: I thought you needed spools of copper wire for that?

Jamie: apparently, Seth's singing reminds Leah of spools of copper wire, or nails across a blackboard.

Banana motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
