\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 19, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1655 SST,
Jamie Morris, LHE and Pseudo-Skinner, presiding; Scott Kullberg, Onseck, recording.

JM: Will the Onseck please read the minutes? No, because we don't have an Onseck, but we do have minutes. (Well, he was on time, y'all were just early.) Paul will read the minutes.

P: #include /mitsfs/min2-12

(At 1702 SST, 1727 real time, the Onseck enters on time.)

P: Motion to condemn these minutes for having too many comments by me in them.

Motion fails for lack of a second.

JM: Any motions concerning the minutes?

??: Move that the minutes be passed times two.

Seconded twice, motion passes 40-40-0-0 +Spehn +Spehn.

\goto{Committee Reports}

JM: Committee reports!

P: Weirdo-Moocomm: today at 19:30, the Bartos Theatre over on that side of campus is showing "Wax, or the discovery of television among the bees." It is set in NM where the main character designs gunsight displays, blah blah blah, he also keeps bees. His hive is filled with Mesopotamian bees which he inherited. Through these bees and the dead of the future which begin to appear,

(Random speculation from the peanut gallery; none is sufficiently weird.)

P: he's introduced to a new kind of destiny that pushed him away from the normal world in developing him in a grotesque miasma of the past and synthetic realities.

JM: That was my next guess.

P: And so on. It just gets weirder and weirder. It's tonight at 19:30.

SG: It's an ART film.

P: It may be, I don't know.

SG: If it's showing over in the bathroom building, it's an art film.

P: Hey, I worked in the bathroom building, you know.

JM: That's very appropriate, Paul. I'm glad you've found your place.

P: I've been there longer than you've been alive.

SG: Pseudo-Sitcomm: I have seen TimeTrax, and my god, what a bad show.

P: Pseudo-Shitcomm?

??: It's opposite the Simpsons.

SG: Oh, good, then it'll die quickly. It's even worse than Small Wonder.

P: Pseudo-Sad-for-Sitcomm: Space Rangers went away. Only 4 episodes.

JM: Any other committee reports?

SG: Pseudo-Sitcomm3: Babylon 5 real soon now (it was cool).

P: 23rd on channel 28.

SEK: Pseudo-Moocomm2: Clockwork Orange, this Sunday at LSC.

JM: Pianocomm: we have someone in the process of becoming a keyholder: Todd Anderson, who's sitting here. Alright, Todd, how much have you been told about what you're supposed to do?

TA: Nothing.

JM: Your mission, should you decide to accept it, and you have no choice, is to hunt down Susan Tucker, whose stats should be in the book- her email is "sst." She is the current Keeper of the Pinkdex, the person who takes the information that the people who process books write down...

P: Finger motion- he's doing business.

JM: You shall hunt her down and force her to teach you the arcane lore of maintaining the Pinkdex until you know everything she knows about it and can do all of it. You shall then go and enter in all the information that Panthercomm has written down that has not yet been entered into the Pinkdex. You shall then receive your key, we shall behead Susan or kill her in some other- preferably more unpleasant- fashion, and you shall become the new Keeper of the Pinkdex until eternity or you become as lame as she is and we do the same thing again.

TA: Or I graduate.

JM: That counts as becoming lame.

P: Motion to issue him a gun to go hunt down Susan with.

SG: A banana-colored gun?

TA: I prefer to use my bare hands.

P: Friendly amendment there!

JM: There is a motion to issue Todd Anderson a banana-colored gun to hunt down Susan Tucker with.

Motion chickens 4-0-4 +Spehn.

\goto{Old Business}

JM: Old business... do we have any old business?

(Pause.)

JM: Ken's here, he's old.

JM: Anyone want to do the algol?

??: Usual motion.

JM: Y'know, people used to do clever things with filling out various permutations on ALGOL or COBOL and all that has died. How sad.

P: Unusual motion.

Motion is thirded.

JM: Unusual result.

\goto{New Business}

JM: New business. We have someone new here, he's looking like he made a mistake; that happens when you wander into the middle of a MITSFS meeting, or in fact any part of a MITSFS meeting.

SG: Motion to have the visitor washed, stripped, and brought to my banana-colored tent.

(Seth is Albanianed.)

SG: Uremklv rojvrhy dnkrnop rgvgom! Gfoigje vmrnx.

JM: Motion fails for lack of a second. Do we have any other motions?

??: Miller motion!

JM: FAILS!

\bing

??: Third Miller motion!

???: Times two!

Motion passes twice.

\vspace{12pt}

\noindent
Meeting adjourned, 1703 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}