\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 12, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, LHE and Pseudo-Skinner, presiding; Scott Kullberg, Onseck, recording.

JM: Onseck, read the minutes.

(Silence. The onseck is not there. The minutes are not there. Sorry.)

MH: Has the real skinner ever hosted a meeting yet this year?

JM: Yes, many times.

EE: Move to pass the minutes as garbled.

Motion chickens 0-2-5 +Spehn.

\goto{Committee Reports}

JM: Any committee reports?

MH: When is inventory?

JM: Inventory is going to be sometime.

DSK: C, T, W, and hL is showing tonight. You want to go see it.

??: Science fiction?

DSK: No, not really, but it's kind of a neat movie.

JM: On the first night of the game? How irritating. I was going to go see that.

(About six people talking at once, and the tape recorder is only mono.)

MH: I just saw an article that said that Steven Spielberg is producing a miniseries for this spring called Sea Trek and it's set in 2018.

Y: TV Guide claimed that that wasn't going to be able to come out until next year or at least late in the fall.

JM: ???comm: the book Demons Don't Dream is coming out. It's the XVIth book in the Xanth series. Isn't everyone HAPPY?

MH: I want to know how many books are planned for the Robert Jordan series before I die of old age.

JM: Are you comparing the Wheel of Time (Sounded to me like Whale's Tongue.) to Xanth?

P: I'll notice when there are more Xanth books than ???? of Terra books.

MH: Does anybody have any idea how many Robert Jordan books there are supposed to be?

JM: I've been told 7.

Y: There aren't supposed to be ANY Robert Jordan books.

MH: I like the series!

JM: A large number, but I think you want to specify just the Wheel of Time.

MH: Okay, just the Wheel of Time.

JM: He's got a batch of Conan books out.

MH: That's how he broke into the biz; he wrote Conan books for several years and then they finally let him publish his own books.

JM: Mobcomm: there will be a Mobcomm run sometime in the next few weeks.

MH: Same time we do inventory?

JM: Hopefully not.

JM: Pianocomm: There is a person who is going to become a keyholder by apprenticing to learning to maintain Pinkdex. So, of course, his first task is to hunt down Susan. Assuming he successfully captures her alive, he'll learn to do Pinkdex and we can have Pinkdex.

DSK: Who is said person?

JM: I dunno, some chemistry graduate student. Anything else?

\goto{Old Business}

JM: Old business.

P: Superman will be alive again, however... um, in a month and a half.

??: How are they resurrecting him?

???: It's stupider than you could possibly imagine.

JM: That would be amazing.

P: Smaller breasts than Jean Gray, just as stupid.

EE: Imagine 4 creatures with different origins all claiming to be Superman, and they fight it out for a couple of months.

P: And then none of them is going to turn out to be the real one.

MH: Has anybody watched Star Rangers yet?

P: It's cool.

MH: I like it! It's better than Star Trek. Wednesday evenings at 20:00.

Y: Did anyone see the DS9 broadcast opposite the Super Bowl? What did you think?

MH: Which one was that?

Y: That was the one with the fugitive and the bounty hunter.

P: With the aliens bred to be prey. Great moral question, stupid episode.

Y: You've got to admit, they came up with a completely new interpretation of the Prime Directive. "We didn't know we were interfering with their customs, so let's run around and bash everybody on the head until things get back where they would be if it hadn't happened in the first place."

Usual.

\goto{New Business}

JM: Is there any new business?

P: These guys were here- they were weird and politically reactionary.

(Discussion of how Niven and Pournelle came and why nobody knew about it.)

(Discussion of weird politics and physics in books.)

(If you really want to know how a pulsar works, look it the hell up.)

P: Motion to send out a search mission for a banana-shaped pulsar.

Motion passes 5-5-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}