\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 1, 1993

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

The minutes were read. Both of them.

\goto{Committee Reports}

Chapter11comm: we're broke!

Paul: how can we be broke? We still have checks left!

Paul: so, Jamie, where are you getting the money from?

Jamie: you, Paul. We've decided to sell you into slavery. And you owe us 5 bucks for walking in the door.

Paul: you won't get much...

Marcus: hmm... funny... that deficit is about the right size for a trip to Bermuda.

Chris: I wouldn't know anything about that!

Jamie: if someone was flying to Bermuda and back, they'd have enough money left over to stay for a while in relative luxury- Chris!

Moocomm: Total Recall II is coming out sometime... subtitled, I forgot again.

\goto{New Business}

Motion to replace Jamie with a large banana on the basis that there would be no difference. Motion passes 18-none-none +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 or so SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
