\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Naomi Hinchen, Vice and pseudoSkinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 28 January 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

\subsection*{Onseck}

Our august Thunderbunny, Miss Katie Ray, sent the library a holiday card.
It has a knight and princess riding on the back of a huge flying (but wingless)
pig.

She reports that the Singapore Zoo has Bornean and Sumatran orangutangs, and
that she almost sent us one, but then decided we wouldn't have room.  She
reports that the weather is warm, but that she can't get avocados (the two
places that have claimed to sell them have in fact sold (1) peppers and (2)
salsa) or chocolate and that this is very sad.

Motion to wish her a happy new year PASSES by pseudoSkinnerial decree!

Also, Aaron Ucko (Vice, 1999-2001) and Yevgeniya Ucko (member, similar
vintage) sent us a holiday card with photos--they spawned!

\subsection*{Pianocomm}

CAK (Keach) is joining Pianocomm.

\subsection*{Star-Chamber}

We have a new keyholder, Kaleb Ayalew (KAA).  He will be on Picniccomm and
Hasselcomm.

\subsection*{pseudoSeldon}

We will be doing a showing next week.  We haven't decided on the film yet,
though, so you should tell us if you have ideas.

\goto{Old Business}

In the past we sold books at the science fiction marathon!

\goto{New Business}

Tonight is the Harry Potter: Year Seven Yule Ball!

Tomorrow night is the Shakespeare Ensamble's 24-Hour Show!  It's
20:00 tomorrow Twenty Chimneys in W20.

\goto{Future Business}

In the future DWR will stop being confused by the geography of this campus.

In the future one of our members will no longer be attending meetings
because she will be across the Atlantic.

In the future we'll get the real Skinner back to run meetings!

In the future Emi will stop eating books and become a member.

Discussion of eligibility of babies for membership and the ADA ensues.

Motion to replace all books in Emi's diet with bananas PASSES 10-2-1\ps!

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
