\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kaleb Ayalew, Vice and pseudo-Skinner}
\newcommand{\onseck}{Kendra Beckler, pseudo-Onseck}
\newcommand{\meetingdate}{Friday, 9 December 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the pseudo-Onseck on the reading of the minutes: 4-0-5 \ps

\bing

\goto{Committee Reports}

The committees are a lie.

\goto{Old Business}

In the past, Belgium didn't have a government.  Motion to commend it for getting a government: 9-0-0 \ps

In the past, the comic books were in California.  Isaac Asimov is still dead.  Anne McCaffrey is still dead.

Motion to commend the prentice for forgetting its past lives: 1-0-3 \ps

ALGOL

\goto{New Business}

You should come hang out with us tonight, as with every Friday night!

We got new books, also new prophecies.  If only they were as entertaining as prophecies of old when Oedipus hadn't yet married his mother.  Oh, I'm sorry, did you want me to call spoiler alert on something that premiered almost 2500 years ago?

Motions fail due to causing singularities in the universe.  Since when are we voting against those?  I OBJECT.  Thus says the pseudo-Onseck, SO SAY WE ALL.

\goto{Future Business}

The Doctor (yes, \textit{that} Doctor) will light the cauldron in the 2012 Olympics in London.

Motion to do something with bananas and the Seldon showing chickens.  But the first Miller motion passes!  The world, and also the meeting, ends.  Yay!

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
