\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 22 April 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the Onseck for a passionate reading PASSES 3-0-1\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudoPicniccomm}

We have a picnic in two weeks!  Also elections in two weeks!

\subsection*{Skinner}

Elections in two weeks!  Keyholders should email the Skinner if they want
to be elected to things.

\subsection*{pseudo-Keyholder-Since-Before-You-Were-Born}

We had a Fortieth-Anniversary-of-Being-a-Keyholder party for Jack Stevens
on Wednesday.  Kat made a neat knit banana for him.  Photos are online at:

http://ugcs.net/~rowlands/MITSFS/

\subsection*{pseudoPanthercomm}

We're down to the last couple of boxes of Panthercomm from the first Cohen Donation.

\subsection*{Bluebellcomm}

We have a backlog again.


\goto{Old Business}

In the past things were said, but the Onseck didn't hear them, and they
didn't sound like they mattered.

ALGOL


\goto{New Business}

It's Steer Roast this weekend.

Half the people in the library are undergrad keyholders!  And two-thirds
the people in the room are keyholders!


\goto{Future Business}

In the future we'll have elections!

In the future we'll have a picnic!

In the future term will be over!

Motion to commend the the existance of bananas CHICKENS 0-0-4\ps.

Motion to bribe Brian with bananas so he'll come to meetings
and give us more interesting banana mostions PASSES 3-0-0\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
