\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kendra Beckler, LHE and pseudoSkinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 11 March 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the meeting for being essentially essential
CHICKENS 3-0-4\ps.

\bing

\goto{Committee Reports}

\subsection*{Star-Chamber}

Patrick Rothfuss is doing a book tour for \emph{The Wise
Man's Fear}, the sequel to \emph{The Name of the Wind}.

He'll be at the Northeastern University Bookstore at
360 Huntington Ave. in Boston at 18:00 next Wednesday.

\goto{Old Business}

In the past the stars were right.  Then they stopped being right.

In the past, people were healthier.

In the past, people made motions.

ALGOL

\goto{New Business}

In the present, there is usual lack of understand of what was
going on PASSES 4-0-2\ps.

The onseck is caught up, so clearly we aren't talking enough.

However, while people are debating what they ought to talk about,
there is a sudden \textbf{crack} and a number of people in dark
robes with wooden wands in their hands appear in the middle of the 
library and run out the front door without explanation.  But
before anyone can get up to try and chase them one of them runs
back and shouts "Impedimenta" while pointing their wand into the
meeting.  For a second, everything froze solid, and then there was
a glitter of light and all the books turned into ravens, flew
out the door and devoured the invaders, robes, wands, and all,
and then returned to the shelves and became books again and the
meeting continued as normal, while a loud voice boomed "Tree
speaks to stone; stone speaks to water!"


\goto{Future Business}

In the future Spring Break has happened.  In the future PAX
East has happened.  In the future, the apocalypse has happened.

In the future someone made a banana motion, but it FAILED
0-3-2\ps.

In the future Kaleb will have caused there to be more undergrads
at meetings.

In the future there will have been time to travel to all the
infinitely many futures.

In the future there will have been much discussion of earthquakes
and the resulting firestorms, as well as civil engineering and
how water and gas mains are protected from earthquakes, construction
workers, and MIT students.

In the future the meeting will still not have obtained a defined
track, but people will still have hoped for it to.

And the pseudoSkinner was driven from the room by sadness due to
her lack of tentacles, which was emphasized in song.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST, so it took no time at all!

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
