\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{pennajm acting as pseudoOnseck}
\newcommand{\meetingdate}{Friday, 16 September 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to never read excerpts from The Eye of Aragon in the meeting minutes again. PASSES by skinnerial decree.

\bing

\goto{Committee Reports}

Seldoncomm: is once again showing movies. KKB: Please come the the Seldon showing tonight, where they are showing episodes of Avatar the last Airbender and the Movie cast a Deadly Spell, which involves Cthulhu. Retconn: Seldonconn has been moved back to building 2 in room 2-131.

Confusion on when Seldoncomm started showing movies and mockery of Nealson's novel Anathem ensues.

Ookcomm: switching to an electronic checkout system soon, pointed out that computers can mess things up but there is expressed optimism at the prospect. The system mostly words but there are paper back-ups just in case there is a failure. Awesomeness of a card catalog pointed out but explanation of the system of Dex's ensues. A barcoding project is being discussed and the enormity of the pursuit bears havily on the Skinner's mind. 

kkb: There's a frosh at the meeting, with the unpronouncable name!

skinner: He has a pronouncable name, it's just not pronouncable by many people, like you.

Once again it is pointed out that no real business goes on during meetings.

Star Chamber/barrcomm: We had an open house on Sunday and frosh came, lured in unsuspectingly and having resulted in many much memberships being sold.

smilescomm: They have a new dedicated prentice whom is helping put the circulating books back in order. Celebration of said prentice ensues.

\goto{Old Business}

In the past, PJM wasn't pseudoOnseck and didn't have the appreciation of Lemur he has gained while taking these minutes. 

In the past, the Harvard guy did not finish readen "Restaurant at the End of the Universe."
\goto{New Business}

Borders by Cambridge Galleria is closing down and may have good sales on science fiction. It is pointed out that Borders is failing miserably and shutting down because of its propensity to sell white chocolate-carmel lattes to people rather than actual books. When Borders closes, Prattle Book Store will have no more competition, except for Amazon, the evil conglomerate. 

The libraries finances need to be sorted out due to confusion on the part of the administration and possible mishandled checks.  

\goto{Future Business}

We wil try to get more floorspace by the grace of the old man in the sky and the bird of the galaxy. 

In the future, something will happen, and the skinner will eventually get his tongue back from the cat which stole it. It will also be the summer, unless it's winter.

Winter is coming. 

Global sauteeing is put forth as a better politically correct term for what used to be "global warming" and then "global climate change."

\bing

Usual motion, usual second. Usual complaint, and usual rejection by the skinner because it was done at the wrong time of the meeting. 

Miller motion, no second.

Miller motion redux, passes 12-3-8 plus Spehn. 
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
