\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 1 April 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the reading of the minutes for reminding
us of a time when the undergrads didn't have classes and 
ALC was on vacation FAILS 6-0-1\ps.

\bing

\goto{Committee Reports}

\subsection*{Nanocomm}

NH will be holding Script Frenzy write-ins starting now, since
it is Script Frenzy.


\subsection*{Theftcomm}

Has nothing to report, but has not given a report, so he'd
like to report this fact CHICKENS 0-0-6\ps.


\subsection*{pseudoPain-of-Spacecomm}

There's actually a prentice working on it!


\subsection*{Picniccomm}

Invitations will be ready to go out soon.


\subsection*{Star-Chamber}

DOOOOOOOOOM!  We're likely losing a room--hopefully the annex
because administration is taking away Walker without giving
students any different space.


\subsection*{pseudoSeldon}

We'll be showing "The Eleventh Hour"--the first episode of 
last spring's Doctor Who series--and "A Christmas Carol"--
this year's Doctor Who Christmas special--at 21:00 tonight
in 2-131.  You should come!


\subsection*{hBarcomm}

We will have a Midway booth and may have a Lobby 10 booth.
People are needed to help with this.


\goto{Old Business}

In the past, three people showed up for a meeting, and none
of them were keyholders.

In the past, there was doom.

ALGOL

In the past, the Pandoricon opened.


\goto{New Business}

In the present, lots of people are saying false things.  It's like
everyone is the Onion!

Happy San Serriffen Independence Day!

It snowed today.


\goto{Future Business}

In the future, there will be an ice age this summer.

In the future, the T will extend towards infinity.

In the future, it will be CPW!

In the future, Silence will fall!

In the future, banana trees will sway gently in
the breeze PASSES 4-0-3\ps even though the Onseck
is scared of global warming.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
