\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{lemur (DWR), pseudoSkinner}
\newcommand{\onseck}{Kendra Beckler, pseudoOnseck}
\newcommand{\meetingdate}{Friday, 3 June 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

\subsection*{PseudoRedactedComm}

Nom nom nom.

\subsection*{Algaecomm}

The radiators are overflowing again.  Facilities and the Star Chamber are dealing with it.

\subsection*{Bluebellcomm}

Bluebellcomm party soon!  Really soon!  As in, right after the meeting.

The minutes were read very well CHICKENS: 0-0-14 \ps due to LAAAAAAAME.

\goto{Old Business}

ZEK and the Skinner decreed something about the West Coast and weather.

Isaac Asimov is still dead; the comic books are still\ldots ALGOL.

\goto{New Business}

Seldon is going to show things over the summer!  Isn't that future business?

\goto{Future Business}

In the future, people will have motions??? CHICKENS 3-2-4 \ps

MILLER MOTION!  BOOOOOOOOOOOOM! FAILS 4-10-3 \ps

(Hey, \textit{I} voted for it!)

MILLER MOTION!  BOOOOOOOOOOOOM! PASSES 8-4-4 \ps

(I still voted for it.)

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
