\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kendra Beckler, pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 9 September 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the reading of the minutes for great enthusiasm
PASSES 11-0-3\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudoSeldon}

This week we're showing "The Eleventh Hour", the first Eleventh
Doctor episode, followed by the first half of \emph{The Colour of
Magic} this week.

Next week we're showing the first several episodes of \emph{Avatar:
The Last Airbender} and the second half of \emph{The Colour of Magic}.

They're making a new verion of \emph{The Hitchhiker's Guide to the 
Universe}.  Again.  Apparently it is good.


\subsection*{hBarcomm}

We had a booth at the Activities Midway and seemed to have convinced some
frosh and first-year grad students that we are sane.  We'll soon correct
them.


\subsection*{pseudoPicniccomm}

We sacrificed a watermelon to Nimbus at the Seldon showing last week,
in result of which Hurricane Irene missed Boston and the books were
undamaged, for which we are very thankful.

Motion to commend Lemur for providing the emergency watermelon
PASSES by pseudoSkinnerial decree.


\subsection*{pseudoRedactedcomm}

There is maple syrup cotton candy in the library again!  PseudoRedactedcomm
was non-lazy again!


\goto{Old Business}

Boston was not destroyed by a hurricane last week, clearly due to
our sacrifice.

Reference to the poem "Waiting for the Barbarians".

ALGOL


\goto{New Business}

David Navi has been spending a year in Jersey City, finding friends at
Stevens Institute of Technology.  He suggests that Niagracomm might
want to send them books; Niagracomm would be interested in hearing
about this.

It is established that the best part of MITSFS is having
enthusiastic people.

The new people are reminded that NESFA is MITSFS's first
spin-off and some entity in Seattle is the second. 

Lemur passed its candidacy exam!  It gets to stay at MIT, and keep
being Onseck!

\goto{Future Business}

Motion to insure our banana crops against all potential Biblical
and non-Biblical plagues PASSES by pseudoSkinnerial decree.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
