\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 11 February 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

This is boring FAILS due to apathy.

A pile of napkins to the top of the Onseck's head PASSES 7-0-1\ps.

\bing

\goto{Committee Reports}

\subsection*{hBarcomm}

PW made new letters for our poster, but still doesn't have a key to get
to the poster, and no key exists on campus.

\subsection*{pseudoNiagracomm}

APO sold some of the hardcovers we gave them.  They just asked us if
we wanted them back, and we said no, so they're going to give them
to Better World Books.


\goto{Old Business}

Louder next time PASSES 6-11-1\ps.

We actually had a dinner mob last week, for the first time in about
a month and a half, but we still failed to go to Mary's.


\goto{New Business}

It's Valentine's Day Weekend.

Brian Jacques died this week.  We should make lots of Redwall food.

Mubarak stepped down this morning.

Next weekend is Boskone.

MIT has a new Chancellor.

Class of 2013 Ring Unveiling is today.


\goto{Future Business}

In the future corporations may actually get a clue, but not yet.
(Apparently Dunkin' Donuts declared February "Chocolate-Lovers'
Month".)

In the future it will rain, just a drop.  A particular drop.
Or maybe several, but one is enough to kill you.

Motion that lemur should make a giant banana out of tinfoil
PASSES 4-0-3\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
