\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 14 October 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

\subsection*{Mobcomm}

We failed to order books today, because Amazon was froshed.  Our
secret infiltrator at Amazon is working on it.

\subsection*{Seldon}

We're showing an episode of \emph{Firefly} and the movie \emph{GATTACA}
after the meeting.

\goto{Old Business}

In the past, there was business.

\goto{New Business}

In the present, there is business.

\goto{Future Business}

In the future, there will be business.

The sun will come out tomorrow.

Tomorrow is the Boston Book Festival in Copley Square.  People should
go to it, it's neat.

Tomorrow, people should do lots of p-setting.

Motion to establish pathy FAILS due to apathy.

In the future there won't be apathy.  And the banana 
mafia something PASSES due to apathy.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
