\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Lemur Rowlands, pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 11 November 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Various people's amused expressions PASS 3-1-2\ps.

\bing

\goto{Committee Reports}

\subsection*{Seldon}

We're showing a movie tonight!

Next week, in place of a movie, Jennifer Chung (formerly JKC), the
author of \emph{Terroryaki} will be doing a reading from her book
in 4-231 after the meeting.

\subsection*{Star Chamber}

More people should come to meetings!


\goto{Old Business}

The absence of old business PASSES 3-1-1\ps.


\goto{New Business}

In the present it is:
\begin{itemize}
\item Veterans' Day
\item Armistace Day
\item Martinmas
\item Medieval Superman Day
\end{itemize}

Motion to commend the pseudoSkinner for balancing the gavel on its shoulder
PASSES 3-2-0\ps.


\goto{Future Business}



The library might not be open on the day after Thanksgiving, and will not be
open on Thanksgiving, because the Student Center will be closed.

The pseudoSkinner is upset that it has to do everything itself: Miller Motion 
passes by pseudoSkinnerial Decree.

\bing
\noindent
Universe ended, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
