\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kendra Beckler, pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 29 August 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the minutes for being apathetic with Lee's maniacal
laugter PASSes 5-0-1\ps.

\bing

\goto{Committee Reports}

\subsection*{Seldon}

The real Seldon is back!  And she is showing Tin Man, Disc 1 of 2 with 
dinner tonight!

If you have suggestions for Seldon, email them to seldon@mit.edu

Dinner with Jim Butcher went well!

\subsection*{Star-Chamber}

We did work this week.  Also we have a new prentice!  Also, she's here!

Motion to commend the prentice for existing PASSes by pseudo-Skinnerial
decree.

The Skinner comes back tomorrow, for some loose definition of tomorrow.

\subsection*{Bluebellcomm}

Bluebellcomm should do work!

\subsection*{All-the-Committees}

All the committees should do work!



\goto{Old Business}

Ghost Story came out.  Have you read it?

Congratulations, the prentice is no longer a frosh!

The Onseck feels old.

Motion to move on to New Business FAILs by pseudoSkinnerial decree.

Motion that the Magazines are in California PASSes by pseudoSkinnerial
decree.


\goto{New Business}

A prefrosh cme by!  Also, there are frosh!


\goto{Future Business}

Onseck has quals in two weeks.  *shudder*

Motion to send Lemur a two-weeks supply of bananas so it will have 
food while studying for quals PASSes 5-0-1\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
