\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, pseudo-Onseck}
\newcommand{\meetingdate}{Friday, 27 May 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

``Eh!'' PASSES: 1-0-0 \ps

\bing

\goto{Committee Reports}

\subsection*{Star Chamber}

SAO screwed up again, but at least it was in our favor?  We won't take advantage, we aren't evil, we \textit{swear}\ldots

The new Star Chamber has basically vanished for the summer, the old Star Chamber will take over for the summer.

\subsection*{SleepComm}

Term is over, sleep is here, the apocalypse is nigh PASSES: 2-0-0 \ps

\subsection*{AlohaLensComm}

New keyholders have photos!  The new LHE's picture includes both the human and
the shirt elected to the job, the new Vice's picture has a sword and virgin
sacrifice\ldots

The mind-controlling aliens secretly herding the populace that live in the ceiling approve!

\goto{Old Business}

In the past it was term.  In the past there were finals.  We are glad that they are in the past.

But are they ever really final?

Bwahahahahaha PW is embezzling money out of the big evil corporation!

ALGOL

\goto{New Business}

It's Memorial Day weekend!  YAY!

PW has an extra day before turning slave to the pieces of silicon.

MITSFS temporarily warped to Alaska for a few days earlier this week.  No wonder it is just now getting warm.

\goto{Future Business}

In the future, there will be silence.  And crickets.  And bananas.  PASSES 2-2-0 \ps

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
