\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 7 October 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

An Angry Bird CHICKENS 3-1-1\ps because the birds were angry and destroyed
the rest of the votes.

\bing

\goto{Committee Reports}

\subsection*{Star-Chamber}

The Skinner banged the gavel-block so hard it made the phone do
something, but we aren't sure what.

\subsection*{Seldon}

Seldon will hopefully be showing "The Trouble with Tribbles" and \emph{Serenity}
tonight in 2-131 after the meeting.


\subsection*{hBarcomm}

A new prentice is making a new poster!


\goto{Old Business}

In the past, there was no past.

In the past, they they announced some Nobel Prize winners.  One of them
was dead, but they decided to give him the prize anyway.

In the past, once again, the Nobel Prize in Literature was not for
science fiction.

\goto{New Business}

Motion to start a campaign to get major universities to
nominate science fiction writers for the Nobel Prize PASSES 12-0-0\ps.

Suggestions: Le Guin.  Bradbury.  Ellison.  Delany.

The Skinner will form a committee. 

In 2.009 the Skinner played Angry Birds 

Motion to use Angry Birds and seige engines for War-Council
FAILS 1-11-0\ps.

In the present, it will soon be the future.

In the present, it will be the past because "Black Ships" is running.

And there was much discussion of tenses.

The Skinner is not gonna trick ZEK with these tenses, because she took French.

\goto{Future Business}

The editor of Technology Review's SF Anthology showed up to explain that he's
doing an editorial appearance at Pandemonium Books at 19:00 this upcoming Wednesday.
There will be swag, probably involving USB stuff.

In the future, Keyholders will be trained and there will be electronic check-out.

In the future, the lazy undergrads will have as few days off as those of us
who are no longer undergrads already have off.

Motion to create a committee to create new tense system for English
to deal with all situations involving time travel and bananas PASSES 1-2-6\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
