\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 21 October 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the minutes for containing insufficient chuncks
of molton hot steel PASSES 7-4-1\ps.

\bing

\goto{Committee Reports}

\subsection*{Ookcomm}

The Skinner posted the Greenrites in the rites directory.
We will make members read them shortly.

\subsection*{hBarcomm}

We have a new poster!  It's outside!  Alexwest and some 
prentice made it!

\subsection*{Seldon}

Showing tonight!  Now!  \emph{Real Genius!}

A discussion of various shows the Seldon hasn't seen, including
\emph{Battlestar Galactica}, most types of \emph{Star Trek},
and other things.

There were only three \emph{Star Wars} movies, though George Lucas
promised us nine.  There was only one \emph{Matrix} movie made.
There were only three \emph{Indian Jones} movies.  There was only one
\emph{Blues Brothers} movie.  Timothy Zahn's \emph{Thrawn Trilogy}
are the sequels to Star Wars.  Motion PASSES 10-0-e\ps.

\subsection*{vanHelsingcomm}

It is clarified that the vanHelsingcomm gavel is tarnished silver, which
explains why it can kill werewolves.

\goto{Old Business}

In the past, Redacted rewrote part of their book.  It sucks less now.

Random trancendental numbers, physical constants, and complex integers.

\goto{New Business}

In the present, I'm trying to catch up on the minutes.

In the present, it's going to be the future soon!

But it's already past; the present is now.

The Onseck is confused.  The Onseck doesn't like being confused.
Therefore, things that confuse the Onseck don't exist.

SolidWorks makes you capitalize everything, which makes your emails
look like you're shouting, unless you talk about Justin Bieber, it
makes it okay.

In the present, we have a surprising number of new people at the meeting!

Squee!

One of the new people is from Harvard, but hasn't gotten around
to joining HRSFA yet.

\goto{Future Business}

In the future, HRSFA should remember to invade us!

In the future, they may actually have a working malaria vaccine!

In the slightly more distant future, we may have a general anti-viral

In the future, we should:
	Develop a vaccine for bananas 4-8-2\ps.
	Develop a vaccine made of bananas 12-0-4\ps.
	Develop a banana-based weapons system 8-4-3\ps.
And the determinant is ZERO and all motions CHICKEN!

And the Skinner was driven from the room through singing,
noting that the Lemur's singing is particularly bad.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
