\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 25 February 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.  

Motion to commend the minutes for being more confusing than
normal PASSES 3-0-1\ps.

\bing

\goto{Committee Reports}

\subsection*{Onseck}

Patrick Rothfus is doing a book-signing in Boston in a couple of weeks!

16 March at 18:00
Northeastern University Bookstore
Snell Library
360 Huntington Ave.
4 Ell Hall, Boston, MA 02115

He wrote \emph{The Name of the Wind} and just came out with a sequel,
\emph{The Fear of Fools}.  We invited him to come and visit MITSFS
while he's in town; maybe he'll even come?

\subsection*{Bluebellcomm}

Bluebellcomm did work!  Bluebellcomm should do more work!

\subsection*{Hasslecomm}

There will be a Hasslecomm party in the library tomorrow (Saturday)
from 12:00 to 18:00.  People should come, especially the prentii!

\subsection*{pseudoLibcomm}

The Hasslecomm party will count as Inventory make-up!

\subsection*{cryptoROSFAP}

We have a person who wants to come in to look at the fanzine collection
for research they're doing on the history of Fandom.  They're coming
tomorrow! 

\subsection*{Star-Chamber}

We have a permanent key to our poster cabinet! 

\goto{Old Business}

Most of the people here are old.

ALGOL

\goto{New Business}

In the present, there are a lot of committee reports.

In the present, the ten-day is still going on.  There are
mind-quakes!

There's a new restaurant in Cambridge.  There are details,
but no one showed the Onseck.  Apparently it's called
"Felonius Monkfish", but they don't serve monkfish.

\goto{Future Business}

Waiting for Recursive Business PASSES 4-0-2\ps.

\goto{Recursive Business}

Waiting for Recursive Business PASSES 4-02\ps.

\goto{Recursive Business}

Boskone has come and gone!  A good time was had by all
who went.

JA-J sold Charles Stross a piece of chainmail jewelry for
a person who we assume was Charles Stross's girlfriend.

\goto{Recursive Business}

Mumble mumble mumble banana PASSES by banana motion.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
