\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 18 March 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend Kaleb for getting us a frosh PASSES 6-0-0\ps.

\bing

\goto{Committee Reports}

\subsection*{Star-Chamber}

Rothfuss

Also, the Star Chamber shelf is overflowing.  This will be
corrected.

\subsection*{pseudoKevetchcomm}

The Skinner read Wise Man's Fear.  It was good.


\goto{Old Business}

In the past there were even less people in the room than
there are now CHICKENS 1-0-1\ps.

In the past it was the first half of term.

In the past there were classes.

"Said whistfully?" CHICKENS 0-0-0\ps.

In the past, people besides Spehn voted on motions.


\goto{New Business}

In the present it's Spring Break!

In the present, Science hates lemur LAMES because
the Skinner is too lame to count votes.

In the present, the Skinner is too lame to count votes
CHICKENS 0-0-6\ps.

In the present, pweaver has a new plan to take over the
world.


\goto{Future Business}

In the future, it will be spring FAILS 0-2-0\ps.

In the future, lemur has orals.  *shudder*

In the future, pweaver will make ice cream.

In the future it will be CPW.

In the future, more people will show up to meetings.

In the future, lemur will teach teach people how to make
Polish Easter eggs.

In the future, the Skinner will remember to make a
committee report.

In the future, the wormhole will work again, maybe.

Pweaver would like a wormhole to the West Coast, 
especially Caltech passes 4-0-0\ps.

In the future there will be newer and shinier and
more electronic alternative to doors.

In the future the Onseck will learn how to spell.

In the future we'll get a Course VI person to build
a voting robot, since we're too lazy to vote ourselves.

In the future Doctor Who Season 6 will start--both in the
US and the UK--on 23 April!

Ten seconds forward PASS by Skinnerial Decree.

In the future it will be some other time's past
with bananas PASSES 1-1-0\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
