\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 4 April 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

There are no motions regarding the reading of the minutes PASSES
3-0-2\ps.

\bing

\goto{Committee Reports}

\subsection*{hBarcomm}

It's PFW.  There will be a booth at the Midway tomorrow, because
there are prefrosh.  Otherwise we are being lame.

\subsection*{pseudoSeldon}

No one came to the Seldon showing last week.  It was sad.  We will
try again next week if anyone is interested.

\subsection*{Bluebellcomm}

Bluebellcomm did lots of work, and doesn't have as much of a backlog
anymore.  It should try to keep up in the future.


\goto{Old Business}

In the past, MIT was less old.

In the past, MIT was older.

Wait, what? PASSES 3-0-2\ps.

In the past there weren't prefrosh.

In the past, the Onseck ignored.

In the past, the Skinner ignored a motion.

In the past, a frosh was confused about where a hardware
store was.

In the past, Economy Hardware existed.

In the past, there was bad architectural taste.

In the past, there was a rock opera called "Tommy".

Motion to fail to have seconds on three motions fails due to
Skinneral assertion that this is impossible.


\goto{New Business}

In the present, there is no present.

\goto{Future Business}

In the future the Skinner needs to make banana cookies.

In the future there will not be a dinner mob.

In the future pennajm ate before he got here.

And, by Skinnerial decree, all motions PASS!

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
