\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 9 September 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the Onseck for speedy and goodly reading of the minutes
and to have the minutes read again backwards and have a matrix vote
CHICKENS 5-7-4\ps.

Finger motion.

\bing

\goto{Committee Reports}

\subsection*{pseudoSeldon}

This week we're showing episodes of \emph{Avatar: The Last Airbender}
and the second half of \emph{The Colour of Magic} (which is actually
based on \emph{The Light Fantastic}).  Next week we're showing the
classic \emph{Star Trek: The Original Series} episode "The City on
the Edge of Forever".

We're changing our Seldon location to 1-134, because members
complained about having an infinitely long walk to showings from
W20.


\subsection*{Oookcomm}

The electronic checkout system is done, and will be deployed in a
couple of weeks.


\subsection*{unintentionalPianocomm}

Apparently Google Books and Amazon show you different parts of books, 
allowing you to get fairly far before you have to buy the book.  Or,
of course, you could just check it out from MITSFS, especially if it's
something like \emph{Dance with Dragons}, where we have three circulating
copies.


\subsection*{Pianocomm}

Prentices should do work!


\subsection*{pseudovanHelsingcomm}

Redacted called the library and announced that she would be here 
real soon now, like in ten minutes, with a new vanHelsingcomm
project.

Motion to EMP the internet.  Fails for lack of a second.


\subsection*{pseudoPianocomm}

There was a large workparty for Jourcomm, Catacomm, and
Smilescomm, with lots of prentii and lots of work done.


\subsection*{pseudoDowntroddenMembership}

Please stop throwing your bags at us!


\subsection*{Star-Chamber}

We did lots of work!  And we're now having Star Chamber meetings
right before the real meetings; feel free to come and bug us.


\subsection*{hBarcomm}

At least five frosh seem to have shown up.  We have frosh!  We want
to get other people!


\subsection*{Hasselcomm}

Work for prentices during 


\subsection*{Onseck}

Help, the committees are eating me!

Motion to make ummprobablycomm fails for lack of a second.


\subsection*{asynchronousvanHelsingcomm}

Redacted showed up and brought us a sharpened gavel through 
a copy of \emph{New Moon}.  It shall be hung up and listed as
our review.


\goto{Old Business}

In the past there was the Activites Midway, but no classes.  There
were always frosh, and there shall always be frosh, world without
end, reprieve, or rest.

In the past MIT's weather machine malfunctioned.

ALGOL

\goto{New Business}

NASA wants more astronauts, even though they haven't any particular
way to launch them at the moment.  And probably no funding, anyway.

A Progress crashed on launch and didn't make it to the ISS.

Andrew's friend was on Kwajalen Atoll when SpaceX did one of their big
launches, and was able to see it an hour after all the Air Force
people gave up qand thought it would be weeks before it worked.

GRAIL, a neat mission to measure the moon's gravity field by having
two satellites in the same orbit with an interferometer launched this
week.  Apparently Maria Zuber, the PI, is PJM's UROP advisor.


\goto{Future Business}

In the future the Onseck will get the power to slow down time for
everyone else in meetings so it can actually take useful notes.

In the future someone will actually come up with a grammar
that actually makes time travel make sense.

The new person from Harvard will have readen \emph{The Restaurant
at the End of the Universe} tomorrow.

There is much discussion of paradoxes

In the future, there will be an open house on Sunday 15:00-17:00, 
and it would be great if people would show up!  We want to make the
frosh know that we exist.  

In the future...
\begin{quote}

\emph{The weather beaten trail wound ahead into the dust racked 
climes of the baren land which dominates large portions of the 
Norgolian empire.  Age worn hoof prints smothered by the sifting 
sands of time shone dully against the dust splattered crust of 
earth.  The tireless sun cast its parching rays of incandescense 
from overhead, half way through its daily revolution.  Small 
rodents scampered about, occupying themselves in the daily 
accomplishments of their dismal lives.  Dust sprayed over three 
heaving mounts in blinding clouds, while they bore the burdonsome 
cargoes of their struggling overseers.}

\emph{"Prepare to embrace your creators in the stygian haunts of 
hell, barbarian", gasped the first soldier.}

\emph{"Only after you have kissed the fleeting stead of death, 
wretch!" returned Grignr.}

\emph{A sweeping blade of flashing steel riveted from the massive 
barbarians hide enameled shield as his rippling right arm thrust 
forth, sending a steel shod blade to the hilt into the soldiers 
vital organs.  The disemboweled mercenary crumpled from his 
saddle and sank to the clouded sward, sprinkling the parched dust 
with crimson droplets of escaping life fluid.}

\emph{The enthused barbarian swilveled about, his shock of fiery 
red hair tossing robustly in the humid air currents as he faced 
the attack of the defeated soldier's fellow in arms.}

\emph{"Damn you, barbarian" Shrieked the soldier as he observed 
his comrade in death.}

\end{quote}

In the future, they're making another \emph{Conan} movie.  It
apparently sucks.  The books have been said to be good, but
only in comparison to things one might compare it to.

In light of the fact that personality disorders are caused,
in many cases, by vitamin deficiencies, motion to send Conan
the Barbarian a nice bunch of bananas PASSES 7-4-6\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
