\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 13 May 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to have the Onseck reread the minutes because Marty missed
the beginning FAILS 0-20-1\ps.

\bing

\goto{Committee Reports}


\subsection*{Star-Chamber}

There's a new Star Chember.  It's all here.


\subsection*{Hasselcomm}

There will be Hasselcomm parties in the future this summer.

One is likely to happen next weekend.


\subsection*{Picniccomm}

There was a Picnic last weekend.

Motion to commend KAA PASSES 10-1-1\ps.


\goto{Old Business}

In the past, Dead Week was a lie.

In the past, the Cake was a lie.

Some motion that probably didn't matter passed in the usual
manner involving Skinnerial Decree.


\goto{New Business}

In the present, the meeting is dead.


\goto{Future Business}

In the future, there will be finals.

In the future, the cake will be a lie.

In the future, there may be pierogi.

Friendly amendment to make them banana pierogi PASSES 5-0-3\ps.


\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
