\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kendra Beckler, LHE and pseudoSkinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 15 April 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Everyone in the room's facial expressions PASSES 5-0-4\ps.

\bing

\goto{Committee Reports}

\subsection*{hBarcomm}

Prefrosh Weekend happened, and there are prefrosh who will come to
MITSFS, unless someone invents a time machine or something and
prevents it from having happened.


\subsection*{Jourcomm}

Twilightzine is apparently coming out Real Soon Now.


\subsection*{pseudoSkinner}

We imminently have a new keyholder, Alex Westbrook, who shall be
known as AW.


\goto{Old Business}

Silver has always been cheaper in the past than it is now.

In the past, time machines were invented, but then time-travellers from
the future came back to destroy them.

Regular motion.

Usual motion.

ALGOL


\goto{New Business}

The Skinner is very busy being in a fantasy setting.

In the present we had a picnic invitation.  Now there is a picnic
signup sheet.  People should sign up, and list whether they will drive
and how many passengers they can take.


\goto{Future Business}

In the future, Science will hopefully hate the Onseck less.

In the future, term will end.

In the future, it will be summer.

In the future, we will have new keyholders.

In the future, Twilight Zine will come out.

In the future, committees will eat bananas PASSES 17,000-0-0\ps.


\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
