\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Naomi Hinchen, Vice pseudoSkinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 21 January 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Not really FAILS 1-4-3\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudoNiagracomm}

We're selling books at LSC Science Fiction Marathon tomorrow night--show
up at the library at 18:00.

\subsection*{Libcomm}

Inventory happened.  There will be make-up work and prentices should
help with that.

\goto{Old Business}

In the past it was Mystery Hunt.

In the past it was Aresia.

Unfortunately these were in the same past.

Motion to note that the magazines are still in California fails
for lack of a second.

Motion to rephrase that, more accurately, to note that the comic
books are still in California 2-3-3\ps.

\goto{New Business}

Its being Naomi's birthday PASSES 4-3-3\ps.

It's the LSC Science Fiction Marathon!  And the Harry Potter
Ten Day started 45-minutes ago!  And so we're managing to hold
a meeting without PW or KKB!

Motion to congratulate the contents of the library on doing
such a good job of holding a meeting without PW or KKB PASSES
13-0-2\ps.

\goto{Future Business}

In the future, the Vice will learn to bing properly.

In the future, Bluebellcomm overflow will be dealt with.

In the future, people will help ZEK sort things for the Ten
Day.

In the future, maybe the Onseck will be pseudoSkinner some day.

In the future, after the Ten Day, the Seldon and pseudoSeldon
will start showing things again.  we have a list!

In the future, ZEK will tell the Seldon to show the season premiere
and season finale of Season 1 of Merlin, since they're totally on Hulu.

In the future there will be motions regarding bananas fails for 
lack of a second.

And the library sings NH "Happy Birthday".

And there is a return of the portion of the meeting where everyone
shelves three books.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
