\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kendra Beckler, pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 26 August 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes for being very forward-looking PASSES 8-0-4\ps.

\bing

\goto{Committee Reports}

\subsection*{Seldon}

There is more Seldon this week!  We are finishing off Tin Man, Parts 2 and 3.

Also, we put together a schedule of things to show for the first half of term,
which will be released shortly.  Next week we're showing \emph{The Eleventh Hour},
the first episode of the Eleventh Doctor, and the BBC production of \emph{The
Colour of Magic}.

\subsection*{Theftcomm}

There's a new TIF!  Aww, Kendra's not so close to falling off the top.

\subsection*{Catacomm}

With two prentices working on it, we're actually Niagracomming some magazines!

\subsection*{Star-Chamber}

Next week, right before the meeting, we have the Activities Midway!  People should come!
And should come to the meeting!  And the Seldon showing!  There might be frosh!


\goto{Old Business}

There was an earthquake.  The books didn't notice.  Some of our members did;
others didn't.

ALGOL

\goto{New Business}

There's going to be a hurricane.  We will attempt to keep the books dry.

Motion to suggest we sacrifice bananas to Nimbus to protect the books
fails for lack of a second.

Motion to suggest that Lemur bring a small watermelon to the Seldon showing
so we can sacrifce it to Nimbus.

One week until Doom!  The Onseck has candidacy orals in a week.

Motion to wish Lemur good luck with its exams PASSES 16-0-2\ps.

\goto{Future Business}

In the future there will be many meals.  Of \emph{all} descriptions.
I mean all.

Miller motion fails due to lack of a second.  Tragically.

Motion to bring bananas to some future Seldon showing PASSES 8-2-2\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
