\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Lee Fuchs, pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 18 November 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

"It's very short." PASSES by pseudoSkinnerial Decree

We have a couple of reporters visiting from the MIT Division
of Student Life, so the pseudoSkinner explains how to vote to them.

\bing

\goto{Committee Reports}

\subsection*{Seldon}

Instead of our usual media showings, we have an author here, Jennifer
Chung!  Tomorrow we will have more authors!  Elizabeth Bear and Sarah
Monette are visiting the library at 15:00!

The awesomeness of Jim Butcher PASSES by pseudoSkinnerial Decree.

\subsection*{pseudoTrojan}

There was more Leibowitz donation and someone else's donation, and
prentices did work!

\subsection*{pseudoPianocomm}

We got a new Prentice, and it did work.

\subsection*{Surgeon}

There are books that are damaged.

\subsection*{pseudoWar-Council}

Our space application is submitted.  We're hoping for more space
this year!

Motion to pray that War-Council finally succeeds PASSES 7-0-1\ps.

\subsection*{pseudoKvetchcomm}

We had an author named Stephen Wilk visit yesterday looking for particularly
bad, quotably bad, books that have been pulished by real publishers (as opposed
to self-published or book-mill published).  He also recommended \emph{Galaxy
666} by Pel Torro as a particularly good example of this.  The Onseck read a section
aloud with great expression:

{\it
"Tell us what is happening," came the thought, as the alien's nearest pseudopod
touched Oski.

"This is Bronet's answer," said Oski.  "We are living in a corner of the 
universe that can only be described as
insane.  This is the negative to the positive universe in which we live.
This is the confusion which makes our order possible.  This is the chaos which
makes it feasible for us to live in a universe which is governed by scientific
principles.

Oski was getting almost eloquent in his oratory.

"This crazy galaxy is the price that the universe pays for order.  666,
eh?  By the seven green moons, it was well numbered!  There's something strangely
capreicious about this place.  Just as our universe is a motivated universe, this
one is motiveless.  The real universe, the universe to which we belong, has purpose.
This is purposeless.  Our universe is straight-forward; this one is whimsical,
fanciful, and fantastic.  This is a temperamental galaxy, an [sic] hysterical
galaxy, a mad galaxy.  This is an insane, freakish, wonton, erratic, inconsistent
galaxy; it's a completely unreasonable galaxy.  It's undisciplined, refractory, 
uncertain and unpredictable.  It's a volatile galaxy, a mercurial galaxy."

He turned round and shouted up an air vent: "It's a frivolous galaxy; it's inconsistant
and inconstant; it's variable; it's unstblae; it's irresponsible and unreliable.

He suddenly collapsed on he [sic] floor of the alien ship, his arm across his
face.  "This is a playful galaxy," he sobbed, "and we are the toys with which
it plays."}


Motion to never read anything Pel Torro wrote out loud again PASSES
10-0-1\ps.

Anyway, if anyone has other recommendations of things as bad as this or worse,
they should email the Onseck (onseck@mit.edu) and it will pass them on.


\goto{Old Business}

Jennifer Chung used to be a Keyholder, JKC.

Last weekend there was a Guild Game based on the lovely
Jim Butcher series, Dresden Files.

Jim Butcher is \emph{still} awesome.

JPW: Back in the day, prentices only worked for ten hours
before they were keyed.  Where's my cane?

\goto{New Business}

Jennifer Chung is an author!  And here!

We have Division of Student Life reporters here.

NaNoWriMo is going on.  There are write-ins during Naomi's hours!

Motion to commend all the people who aren't horribly lazy and
are doing NaNoWriMo CHICKENS 6-2-7\ps.

\goto{Future Business}

Motion to make Jennifer Chung start MITSFS West in Seattle
with all the other former keyholders there PASSES 8-0-4\ps.

The library will be closed on Thanksgiving and the day after
Thanksgiving.

Elizabeth Bear and Sarah Monette will be visiting the library
at 15:00 tomorrow.

Motion to develop a recipe for banana-colored turkey.  (1-2-9\ps)

Motion to develop a recipe for vegan turkey made of bananas. (11-0-1\ps)

Motion that all previous motions are completely transparent (8-0-0\ps)

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
