\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Lee Fuchs, pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 23 September 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

MIF appears and takes over being pseudoSkinner from the Onseck.

Motion to commend the Onseck for wearing way too many hats passes
by new pseudoSkinnerial decree.


\bing

\goto{Committee Reports}

\subsection*{Seldon}

We're having a showing in 2-131 directly after the meeting.  You should
come!

\subsection*{Onseck}

Jennifer K. Chung, formerly JKC, just published a book, \emph{Terroryaki!}!
She's coming to the library to do a reading on 4 November.  More details
will be forthcoming once they're worked out!

\subsection*{pseudoSkinner}

More people should come to meetings!

\subsection*{pseudoPianocomm}

There is lots of work for prentices!  Prentices should do work!  Hasslecomm
and Bluebellcomm will be having a work party from 17:00-23:00 next Thursday!


\goto{Old Business}

In the past, the speed of light was inviolate.

In the past, people were, reputedly unhosed. 

In the past, there were more people at meetings.

\goto{New Business}

Technology Review has a new magazine of SF short stories, largely
recommended by KR.  One of their editors came to give us an advanced
copy of it.  They're probably going to have a launch party for it, and
we might get invites.

There will soon be a website with a video up about the creation of the cover
by Chris Foss, who was a famous SF cover artist in the 1970s.  The
URL is http://www.technologyreview.com/sf

They'd like recommendations of new, up-and-coming authors, especially
women and international people, even if they haven't been published
in English before.

There is a long discussion of gender issues in comics and SF, and problems
with DC Comics.


\goto{Future Business}

There will be a Seldon Showing, there may be people!

In the future, we should be more careful about not changing the 
laws of physics when the experimentalists are watching.

In the future, it will be less muggy and hot, and the weather may
actually be tolerable.


\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
