\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kendra Beckler, pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 1 July 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes as "punchy" PASSES 3-0-0\ps.

\bing

\goto{Committee Reports}

\subsection*{Theftcomm}

We have a new TIF.  It is in fact up there.

\subsection*{Hasslecomm}

We hassled a bunch of books last weekend.  But there are many more to hassle.

\goto{Old Business}

In the past, John Quincy Adams was a Founding Son.

In the past, Carthage burned.

In the past, there was a Civil War.

In the past, there was an Aroostook War.

In the past, there was a Revolutionary War.

In the past, ALC was Skinner during KKB's freshman year.

In the past, various people were Skinner.

In the past, various people were young.

In the past, I was less bitter.

ALGOL!

\goto{New Business}

In the present, it is Dominion Day.  Should people perhaps play Dominion?

In the present, it is the beginning of a long weekend.

All weekends are long weekends for Michael.

No weekends are long weekends for KKB and DWR.

In the present, the pseudoSkinner is eight souls in debt.

\goto{Future Business}

In the future, there will be \emph{more} robots.

In the future, it will \emph{continue} to be July.

In the future, Jim Butcher might write things that aren't fantasy.

In the future, on 8 July, the last space shuttle will launch for the last time.

In the future, we might get an Orion Drive.

\begin{itemize}
  \item Motion to establish a space program using nuclear drives manufactured with the
     radioactive potassium found in bananas.

  \item Motion to commemorate John Quincy Adams' great contributions to American
     banana agriculture.

  \item Motion to have a matrix vote.
\end{itemize}

And all motions FAIL due to lack of a second.

Miller Motion CHICKENS 6-0-7\ps.

Attempts to drive the Skinner from the room through singing fails because he
is in Colorado and his hearing isn't \emph{that} good.

And the pseudoSkinner is driven from the room through singing.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
