\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Kendra Beckler, LHE and pseudoOnseck}
\newcommand{\meetingdate}{Friday, 4 March 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion ``Doesn't Charles Stross have a wife?'': 2-0-4 \ps

\bing

\goto{Committee Reports}

\subsection*{Hasslecomm}

The Hasslecomm party was successful and processed half of the hardcovers.  The Hasslecomm overflow is now Bluebellcomm's problem.

\subsection*{Picniccomm}

Details coming soon, to a MITSFS near you?

\subsection*{Star Chamber}

We still have a bulletin board.  We still have a key to a bulletin board.  These are even the same board.

We submitted a request for more money.  Yay, embezzlement.  My specialty.

\goto{Old Business}

The universe is old.  So are the invisible dragons that live in the sea.

ALGOL, usual apathy.

\goto{New Business}

PW went to a distant planet.  So did KAA.  Fun times.

Motion I'm a little teapot, short and stout.  Here is my candle, here is my spout.  You see, candles are more useful to summoning Cthulhu than handles: 3-0-0 \ps

\goto{Future Business}

In the future, there will be PAX East and then Vericon.  Discussion of Boston-area conventions ensues.

In the future, we will summon Cthulhu to eat ALL OF YOU.

Motion to buy tilapia and a bananafish: 8-0-nom nom bananafish \ps

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
