\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Naomi Hinchen, Vice and pseudoSkinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 18 January 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

An incoherent sound CHICKENS 1-0-1\ps and the pseudoSkinner sounds
disapproving.

\bing

\goto{Committee Reports}

\subsection*{Bluebellcomm}

Bluebellcomm did work.

\subsection*{Pianocomm}

Prentices are slowly progressing.

\subsection*{pseudohBarcomm}

PW finally got the poster fixed.


\goto{Old Business}

In the past, people made motions PASSES 5-0-3\ps.


\goto{New Business}

In the present, people make motions PASSES by pseudoSkinnerial decree.

In the present, people have all abandoned us for a Guild game.

Watson won on \emph{Jeopardy!}.  Like Ken Jennings, we welcome
the coming of our new computer overlords.


\goto{Future Business}

In the future, humans will be hunted in the streets by carnivorous
\emph{Jeopardy!}-playing mutant bananas CHICKENS 0-0-10\ps.

Motion to amend the previous motion to put the bananas in the
trees PASSES 6-0-0\ps.

In the future, people will make motions fails for lack of a second.

Second PASSES 3-0-0\ps.

In the future, the library will be less empty by pseudoSkinnerial decree.

Motion to repeal quantum mechanics "because it's confusing" PASSES
4-2-1\ps.

And we ran out of things to move, so....

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
