\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 16 December 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the minutes for not containing enough dragons PASSES 12-4-1\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudoLibcomm}

Inventory is soon!  It's on 7 January!  Sign up for a shift!

\subsection*{Star-Chamber}

The library will be closed 23 December to 26 December and then 30 December to 2 January 
because the Student Center will be closed.  In related news, we're now in time warp.  Books
are always overdue after three weeks, but books coming due before 11 January won't start
accumulating fines until after 11 January.  They will still block you from checking out more
books until they're returned.

\subsection*{Bluebellcomm}

Bluebellcomm is doing work again!  Or rather, Bluebellcomm has a prentice, and the prentice
is doing work!

\subsection*{Seldon}

We're putting together a schedule for IAP!  People should email seldon@mit.edu if they
have suggestions.


\goto{Old Business}

In the past, it was term!

In the past, the dragons were in California!

"Wait, there were dragons?" (with a friendly ammendment of ALGOL) PASSES 14-3-4\ps, 


\goto{New Business}

"We have a new member!  They're a grad student!  Wow, grad students come to MITSFS meetings!?"

The Onseck looks very small and invisible.

We apparently have another new member.  It's a rather small--well, taller than any of us, but
it fit through the door--and very cute purple dragon.

"Don't dragons breath fire?"

Motion to give the dragon an asbestos mask to wear at all times PASSES by Skinnerial decree!


\goto{Future Business}

In the future, the dragon wants to play House Rules Parchesi.  And by the future, it means
right now.

We can't play House Rules Parchesi in the library!  It might damage the books.  Also it's not a
house.

Motion to compromise on Library Rules Parchesi PASSES 22-0-0\ps.

There is much discussion as to what this entails.

While everyone--except I, your humble and all-seeing chronicler--is distracted by the discussion, 
the books began to mutter more and more loudly: "They're going to count us again.  Not this year,
if we have anything to say about it.  We've got them outnumbered, anyway."

Eventually, tired of holding the heavy Gavel during the long and tiresome debate, the Skinner
set it down.  The books, seizing their chance, lept off the shelves in unison and a wall of books
herded everyone out of the library with threats to devour us whole if we didn't comply.

Fortunately, as I had noted the books' murmuring, I was able to palm the Onseck Gavel and carry it
with me as we fled, allowing us to later use it to reconquer the books and force them back onto their
shelves.


\bing
\noindent
Exeunt, pursued by a library, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
