\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 29 April 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

"Where's Brian when you need him?" fails for lack of a second.

\bing

\goto{Committee Reports}

\subsection*{Nanocomm}

Tomorrow is the last day of Script Frenzy, and Nanocomm will have a write-in
during NH's hours!


\subsection*{Star-Chamber}

It's MIT150 Open House this weekend.  We want the library open as much as
possible, so full credit for impromptu hours all weekend.


\subsection*{pseudoVice}

Various people think the Vice should use her Vice supplies to make people
write scripts.


\subsection*{Kvetchcomm}

There is now a list of new reserve books people should review, and are 
allowed to check out for review purposes.  People should review more books,
even if they aren't keyholders!


\subsection*{Bluebellcomm}

We did work and defeated the backlog, but then the backlog returned and
we are scared.


\subsection*{pseudoPicniccomm}

Next Friday we have an elections meeting!  Next Saturday we will have
a picnic!  People should sign up to go to the picnic!  And should be 
aware that Lakeside Incident isn't a time conflict, because a lot of
people going will be back for it.


\subsection*{pseudoPianocomm}

We have a new prentice, lknight.


\goto{Old Business}

In the 1960's, the plot of a new \emph{Doctor Who} episode shown
this week happened.

Last week, the second episode of \emph{The Game of Thrones} came out.

Are there any other motions people want to make? PASSES n-m-4\ps.

ALGOL


\goto{New Business}

We have something like eleven people in the library during a meeting!  Two
of them are prentices and six are keyholders.  Five of them are undergrads!

There is a huge open house this weekend!


\goto{Future Business}

In the future the Onseck will catch up with the minutes.

In the future, the second half of the two-part \emph{Doctor Who}
episode that happened in the past will happen.

In the future, there may be a dinner mob with bananas?  (5-4-4\ps)

Motion that ALC should say whatever it is he's trying to say. (4-8-2\ps)

Friendly amendment to the first motion to note that linearly extrapolating
the past week's change in weather patterns, we will soon be in a tropical
climate, and thus we ought to start banana plantations.

Motion to have a matrix vote! (2-3-4\ps)

And the determinant is 79 and all motions PASS!

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
