\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 30 September 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes as being conversant with current events
PASSES 4-0-2\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudoSeldon}

We're doing a showing of \emph{Star Trek: Deep Space 9} "In the Pale Moonlight"
followed by the Cold War classic \emph{Doctor Strangelove} tonight at 19:00
in 2-131.


\subsection*{RealAuthorscomm}

We liked \emph{Terroryaki!} so much we decided to get the author as well!

Jennifer Chung (JKC), former keyholder and now a Real Author, will be doing
a reading from her novel in 4-231 on Friday, 18 November at 19:00 after the 
meeting and in place of a Seldon showing.  Note the change in date!


\subsection*{Oookcomm}

The electronic checkout system is basically done.  It will be released
when the Skinner says it is released.  Which will be before he says the
semester is over.


\subsection*{pseudoSmilescomm}

Please shelve books?  *wimper*


\subsection*{pseudoMobcomm}

We're redoing the way we order books.  New books will be ordered
soon, but things need to be arranged.


\subsection*{Onseck}

We are going to be competent and contact publishers about review books
and getting advanced copies.


\goto{Old Business}

There were some interesting news articles about science fiction this week.
Someone made a flowchart of the results of the NPR survey of the one hundred
most popular science fiction books: <http://www.sfsignal.com/archives/2011/09/flowchart-for-navigating-nprs-top-100-sff-books/>.

\emph{Reamde} came out.  We should get a copy. Also, Neal Stephenson was
in Brookline on Tuesday, but we didn't notice it until after the fact.
We should try harder at noticing authors. 


\goto{New Business}

In the present, it is the American Library Association's Banned Books Week.
People should read them; we have some.


\goto{Future Business}

The Boston Book Festival in Copley Square is Saturday, 15 October.  People
should go to it!  It's neat and might have SF authors, though we haven't
checked yet.

Vernor Vinge has a sequel to \emph{A Fire Upon the Deep} coming out
soon.  

Motion to use the new property of \emph{certain particles} to ignore
relativity to violate causality and communicate to the past and and
future PASSES 12-1-2\ps.

I AM THE ESCHATON.
I AM NOT YOUR GOD.
THOU SHALT NOT VIOLATE CAUSALITY WITHIN MY HISTORIC LIGHT-CONE.
OR ELSE.

The entire text of \emph{Singularity Sky} as a motion with a friendly
reminder of the Eschaton's message PASSES 1-0-7\ps.

In the future there will be more books, some of them by Charles Stross,
and we will read them.

Motion to read more books PASSES ($\infty$)-(-$\infty$)-0\ps.

Usual motion.  Usual second.  Unusual timing.  Predictable time travel.

In the future, there will be a \emph{Dresden Files} 3-Day Guild Game.

In the future, "Black Ships" will be running.

In the future, there will be IgNobel lectures in 26-100 tomorrow at 13:00,
but you probably need to get there an hour or two early.

In the future, the Nobel Prizes will come out.

Motion to note that, in the future, someone will win an IgNobel prize 
for breeding mutant neutrino-producing bananas.


\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
