\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kaleb Ayalew, Vice and pseudo-Skinner}
\newcommand{\onseck}{Kendra Beckler, pseudo-Onseck}
\newcommand{\meetingdate}{Friday, 15 July 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes not read.

\bing

\goto{Committee Reports}

\subsection*{Bluebellcomm/Hasslecomm}

Bluebellcomm is happening now, Hasslecomm is happening sometime Sunday, email if interested in helping.

\subsection*{Star Chamber}

In celebration of his upcoming book \textit{Ghost Story}, Jim Butcher will be doing a signing with the Harvard Coop on Wednesday, August 3rd.  The intrepid MITSFS has undertaken a devious scheme to steal some of his time before the signing.  He has fallen prey to our scheme and has acceeded to the temptation of dinner with the Society before the signing.

For details or to join in said event, please email.  Space will be limited.

\goto{Old Business}

BEST ALGOL EVER.  (By that we mean the most apathetic.)

\goto{New Business}

Motion to have a vivacious dictatorship CHICKENS: 4-4-5

WHOA SPEHN FORGOT TO VOTE!

\goto{Future Business}

Sword of the Stars II has a release date!  Yay!

Motion to go forward in time CHICKENS: 4-5-8

In the future will be the Big Stretch CHICKENS: 2-4-8

In the future, when the heat death of the universe occurs, the something something bananas FAILS by pseudo-Skinnerial apathy.

There is no banana luggage tag PASSES: 7-1-4 \ps (oh hi Spehn!  Good to see you back!)

\bing
\noindent
And thus the most apathetic meeting of this galactic year is hereby adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
