\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 7 January 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the minutes for having a pathetic rendition of
a pathetic singing of "The Skinner Has No Tail At All" FAILS
4-6-3\ps, mostly because the Onseck voted against it.

\bing

\goto{Committee Reports}

\subsection*{Libcomm}

Inventory is tomorrow!  Strictly speaking, it starts tonight.  The
Membership Books will be closing shortly after the meeting and will
be unavailable for checking things in or out until Sunday, probably.

\subsection*{pseudoVanHelsingComm}

Redacted sends her greetings to the library!  Sadly, she does not send 
VanHelsingComm's second victem--yet.

\subsection*{Code Nightmare Green}

The US Air Force has deployed a surveilance system in Afganistan
called "Gorgon Stare".  Sadly, this isn't quite the same name as
"Scorpion Stare".  Also, Charles Stross had a blog post asking people
to stop emailing him about it as he's now already heard about it.

\subsection*{Onseck}

We invited Charles Stross to a meeting in February while he's around for
Boskone, but it seems that he'll be too busy being the Guest of Honor, so
he said we should invite him next year, as he expects to be around for
Boskone again.

A suggestion was made and promptly redacted.

\subsection*{Star Chamber}

Break is over!  The Time Warp is over!  Things happened!  More books got
shelved!

\subsection*{Boriscomm}

We have a calendar!  It's actually a Boris calendar!

\subsection*{PseudoAnalogcomm}

The new schedule for IAP is up!

\goto{Old Business}

In the past it was winter break.

There is much wanking about snow.

ALGOL

\goto{New Business}

Motion to make a motion PASSES 8-0-2\ps.

Motion to quash previous motion PASSES 6-4-0\ps.

And the current business explodes.

\goto{Future Business}

Spring term is coming up.  As are Mystery Hunt, Arisia, and
Harry Potter: Year Seven.

In the future, there will continue to be wanking about the natures
of various conventions PASSES 3-1-0\ps.

Motion to translate the library into Albanian for the duration
of inventory 0-1-0\ps.

Motion to train bananas to translate the library into Albanian
for the duration of inventory 9-0-0\ps.

Motion to make a backup copy of the library in Galactic Standard
11-2-0\ps.

The determinent is 16 and all motions PASS!

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
