\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 4 November 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

The Universe destroyed 4-0-1\ps.

Kendra is upset by the fact that she was in L-Space, not the 
Universe when it was destroyed.

\bing

\goto{Committee Reports}

\subsection*{Mobcomm}

We got more books!

\subsection*{pseudoPianocomm}

Prentices showed up and did work!  Keyholders should do work!

\subsection*{Ookcomm}

Ookcomm did work!

\subsection*{Seldon}

We're showing movies!  People should watch them!

\goto{Old Business}

In the past, people made committee reports faster than the Onseck
could write them down.

\goto{New Business}

In the present, the Skinner said "New Business".

\goto{Future Business}

KKB: Motion to destroy the universe \emph{again}! 2-0-0\ps
\\ DWR: Motion to declare that out of order as moot, because
the universe was already destoyed a while ago. 4-0-0\ps 
\\ KKB: Motion to make Lemur go through a matrix vote with
only three people at the meeting. 4-1-2\ps

And the determinant is 2 and all motions PASS!

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
