\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 28 October 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

\subsection*{Nanocomm}

Nanocomm will be holding write-ins during NH's hours, Saturday, 10:00-13:00 throughout
the month of November, except over Thanksgiving Weekend.  It's National Novel Writing Month!

\subsection*{RealAuthorComm}

We have a Real Author coming on Friday, 18 November!  Jennifer Chung,
former Keyholder and author of \emph{Terroryaki!} will be doing a reading from
her novel after the meeting.

\subsection*{Seldon}

As usual, we're showing movies!

\goto{Old Business}

In the past, it was the present.

\goto{New Business}

In the present, it has been the past.

\goto{Future Business}

In the future, it will be Halloween and there will be bananas PASSES by Skinnerial Decree.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
