\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Lemur Rowlands, Onseck and pseudoSkinner}
\newcommand{\onseck}{Kendra Beckler, pseudoOnseck}
\newcommand{\meetingdate}{Friday, 8 July 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

No, there are no motions regarding the reading of the minutes passes 5-0-0 \ps

\bing

\goto{Committee Reports}

\subsection*{Pseudo-Seldon}

We're showing \textit{Real Genius} tonight!  It's a neat movie.  But if you are reading this by the minutes, it is probably too late.

\goto{Old Business}

Nothing happened before today except MITSFS receiving books, books, and more books, and us needing to shelve them.

\goto{New Business}

OH NOOOOOOOOOOOOOOO!  The pseudoSkinner announced the beginning of New Business!  The apocalypse is coming, yay!

Motion to buy more books passes 3-1-1 \ps

\goto{Future Business}

Readercon!  Tangled photons!  Motions lacking seconds!

The pseudoSkinner is driven from the room in terror of the wrath (or existence\ldots) of Rosfap muahahahahahaha.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
