\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{lemur (DWR), Onseck}
\newcommand{\meetingdate}{Friday, 4 February 2011}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

They were very sincere PASSES 4-0-0\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudoNiagracomm}

We took all the Niagracomm hardcovers to the APO book exchange.  Hopefully
some got sold, and none will come back!


\subsection*{Bluebellcomm}

Bluebellcomm actually did work this week!  Wow!


\subsection*{pseudoSeldon}

We were lame and didn't come up with a showing for this week.  Maybe
next week.


\subsection*{pseudoAnalogcomm}

There's a new schedule!


\goto{Old Business}

In the past it was IAP.  In the past James Penna was on pass-no record.  In
the past there was Year Seven.  But the Skinner doesn't remember the past,
so there is no past.

Motion to cast \emph{obliviate}...and we don't remember what happened.

In the past, people were less tired.

In the past the comic books were in California.

\goto{New Business}

The Skinner is still sick; he might get better eventually.

Motion to wish the Skinner good health PASSES 5-1-2\ps.

The Onseck's second fails due to lack of a second.

Slightly to the left CHICKENS 0-0-2\ps.

\goto{Future Business}

In two weeks it will be Boskone.  In two weeks it will also be
ADOR.  These are annoyingly on the same weekend.

Motion to build a hypoallergenic artificially-intelligent mechanical banana
PASSES by meetingarial apathy.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
