\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 1, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(CH) Move to have the minutes read in a more somber tone of voice.

Fails.

(KM) Move to read nasty, somber things to Jenny so she sounds more somber when she reads the minutes.

Seconded by many people but fails due to Skinnerial and Onsecknal decree.

(Malcolm) Move to approve the minutes as sincere.

Fails by "NAH!!!"

(RvdH) Move to approve the minutes as NOT being in a banana colored folder.

(AA) Second!

(SSDT) That one fails.

(KM) Move to approve the minutes as unapprovable.

Motion passes lots and lots-several +"Never, never, free silver"-3 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: TZ RSN. And if I don't get some pictures, this will be the first "All Clip Art" issue.

(AA) Moocomm: Howard the Duck opened today. If you want to get a message from Howard the Duck you can call 1-900-410-DUCK.

(BPS) Moocomm: A whole bunch of us went to see Aliens last Friday. It is a good movie.

(JME) Moocomm: Maximum Overdrive, Steven King's directorial review, has gotten several really pits reviews from newspapers, magazines, and exit polls.

(BPS) In Newsweek, Steven King says "It's a moron movie."

(RvdH) In Aliens, several of the marines had interesting graffiti scrawled on their armor.

(JME) People's Albanian Embassy: from the Glob- Albanians are meeting in Boston to celebrate the centennial of the arrival of the first Albanian in America and the 40th anniversary of the Albanian-American National Organization.

(SSDT) Pseudo-VGG Report: Someone just paid a 42-dollar fine for books taken out in 1977.

(JME) Pseudo-Fweekcomm: We need a bigger and more threatening notice on the board to get people to sign up for Rush duty.

(GF) Disastercomm: an SF library lost about 2/3 of its 7000 books in a fire.

(AA) Sitcomm: The Flight of Dragons is a good animated movie on this Sunday at 7 PM on ABC.

(SSDT) Pseudo-Fweekcomm: Thanks to Ellen Kranzer, we can do our tally sheets for the APO Book Sale the easy way this year.

(AA) Motion to commend Ellen Kranzer for convincing them to let us do this.

Much clapping ensues, immediately after which the commendee walks into the room to be greeted with an ovation. Comments she, "I love walking into this place."

(John) Pseudo-JamesEarlJonescomm: Dr. Strangelove playing at the Janus Cinema tonight. He plays the bombardier, not terribly recognizable by looks but with voice unmistakable even then.

\goto{Old Business}

(All) Hi Merryl!

(JME) Start thinking about writing for the NEXT issue of TZine.

OLBA: the usual stuffing, uv, ur.

\goto{New Business}

(KM) From the Herald- we're number 6! New figures for tuition have come out and MIT is number 6, ahead of Radcliffe and Harvard by 5 dollars.

(JME) The Glob says we're number 4.

(BPS) Minicult: from the Wall Street Journal- a Huggies plant in Utah is having difficulty disposing of the 20 tons of rejected Huggies they produce every day. The Huggies, stacked 12 feet deep in a local dump, have been causing fires that are nearly impossible to extinguish because the fire trucks can't get through the Huggies. The plan for "mainstreaming" the diapers to prevent the fires pleases the Kimberly-Clarke people because it will discourage the small black market in Huggies rejects that has been running in the area.

(JME) Minicult: from today's Glob- Edward F. Harrington, Republican candidate for attorney general, said today that he favors the decriminalization of small amounts of marijuana, but changed his mind six hours later.

(AA) A group of bank robbers in Italy who were attempting to get into the bank by burrowing in from the sewers got caught by people who heard funny noises coming from said sewers. One man, caught coming out of a sewer wearing nothing but his underwear and completely covered in slime, said he suffered from sleeplessness and was out for an evening stroll.

(BPS) BA-NA-NA.

Lots of people second.

Motion passes about 28 and a dead Onseck-much laughter-26 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely subservient,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}