\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 4, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (3/21/86) read and corrected.

Y gets Albanianed for moving to accept the minutes as banana colored, which everybody knows is RvdH's job. After some discussion, RvdH move to approve the minutes as read. Passes 42-sqrt(42)-cube root of 42 +Spehn.

\goto{Committee Reports}

SLP: LHE Report, March: Income- 400.26, Expenses- 200.95, Profit- 199.31, Equity- 3326.20.

KM tries to find out if anyone left a hardcover he found lying around, then reveals the candy wrapper inside it. There were no takers.

BPS: Pseudo-Cornelia Otis: Stevenson will run as an independent since he can't get rid of the LaRouchites. His Republican opponent is giving him no help at all.

ATS: Moocomm: Cocoon Saturday.

BPS: Bluescomm: After the concluding episode of Hill Street, an NBC man came on the air and said it will be picked up for one more season. Attached. Also, under Mars Needs Women, the people who run the Miss USA pageant tried to find the 34 previous winners for the 35th anniversary and came up 14 short.

\goto{Old Business}

SSDT: I found this in a book. It's a certificate; receivable on presentation, an order of Peking ravioli, hand delivered, to "Susan" and signed Andy. Okay, Andy, I want some ravs! Andy makes himself very unpopular by refusing.

BPS: Another article (attached) about Riverside, Iowa, where James T. Kirk will be born in 2228.

OBA: um, us, uv, ur. During this, KRJ moves to place "I want my ravs, Andy!" in the usual motions. Passes overwhelmingly, i.e., Andy is overwhelmed.

\goto{New Business}

BPS: Minicult: Here's the documentation (attached) about the alleged psychic that a jury awarded 1 million dollars for loss of her powers due to a CAT scan.

CH: WWN Report: 1) White House gatecrasher writes book; 2) car drives itself backwards in circles until it runs out of gas; 3) scientist turns milk into beer (sort of); 4) a plane that can land upside down on a second set of wheels; 5) computer use by exorcism team in Italy. All items attached.

SSDT promptly carries out her threat and reads 5 items (not attached) from the Boston Phoenix personal classified ads. They are surprisingly well liked.

BPS: Minicult: a local DJ was jailed for stopping an argument by shooting one of the participants to death. Attached.

BPS: Minicults: Articles attached on the court case against the Georgia sodomy law, a cardboard cop that slows down traffic, and "trench disco" by Chinese soldiers.

CH: There is a town so small that when I tried to call the fire department, I got his mother.

BPS: Finally, a letter to the editor (attached) commenting on Arnold Schwarzenegger's belief that "a good pump is better than sex": "Clearly, either I don't know how to pump or Arnold doesn't know how to make love."

Somebody moves to go out and have banana ravs. Passes everybody-1-some +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}