\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 28, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the 2/14/86 meeting read and corrected, having been approved the previous week. Minutes of the previous meeting (2/21/86) read and corrected.

GF: Move to approve the minutes as twice as strange as usual. Passes despite a vote of few-less-3 +Spehn.

\goto{Committee Reports}

SLP: LHE Report, January: Income- 345.03, Expenses- 962.11, Loss- 617.08, Equity- 3877.33. February: Income- 208.66, Expenses- 959.10, Loss- 750.44, Equity- 3126.89. The endowment fund will begin collecting interest when it goes over 5000 dollars. We can withdraw money from it except for what Sacks put in, but no one knows how. No one knows how much is in there, either. If you're going to give us money, don't give it to the endowment fund unless we have too much cash and are trying to hide some.

Discussion of why the equity dropped so suddenly, and some doublespeak as to why it is really a good thing that the endowment fund only gets 5 percent interest.

GF: Move to condemn the society for discussing 5 minutes worth of serious business at a meeting. Passes by acclaim.

SSDT: Catacomm: Ken Johnson got us a complete set of bound Phantom magazines at Boskone. This fills in almost half of what was lacking in our British magazine collection.

BPS: Freedomcomm: The Supreme Court let stand lower court decisions that an Indianapolis ordinance defining pornography as sex discrimination is unconstitutional. Article attached.

KM: Pseudo-Jourcomm: Write for TZ, or we'll be forced to print RvdH's cartoon. Our party is tomorrow evening, and don't you dare tell Chip.

BPS: Sitcomm: Hill Street actually went and killed a regular character, Joe Coffey. USA Today had a big article on it, which appeared the day before the episode.

CH: Famecomm: a Cambridge woman won the 50,000-dollar first prize for a 1955 predict-the-future-of-air-travel contest held by TWA. Attached.

\goto{Old Business}

SSDT: Here is a very technical item from Physical Review Letters, courtesy of Dave Caswell, about the possible discovery of a fifth fundamental force, which was mentioned in the papers last month. This is an intermediate range (less than 1 km) repulsive force that is probably linked to baryon number or hypercharge, and has the effect of decreasing G exponentially with proximity. Item attached.

OBA: usual van der Heide-isms. Clink.

\goto{New Business}

CH: WWN Report: all items attached. 1) A widow left 1 million dollars for a library to her town of 3000. 2) A dog ate 15 golf balls while being walked on a golf course. 3) A pack of racing greyhounds caught the lure when its motor slipped. 4) Tennessee Scare Goats faint with their legs in the air when frightened by a loud noise. Andy says it's a muscle enzyme deficiency. 5) Finally, a photo of the annual migration of the livers.

KM: Minicult: There was a TV show about the DECworld trade show in Boston on some local stations. For the benefit of DEC employees and customers, air time was carefully chosen so as not to conflict with Star Trek, according to DEC president Ken Olsen. Supplementary article attached.

BPS: Minicult: the District of Columbia fired a Harvard-trained cash-management analyst for insubordination, but before he left, he changed the district computer's password, and now finance officials can't get at their own data. He promised to put clues in classified columns and award prizes for solutions. Attached.

SSDT: Minicult: WEEI reported a man arrested for driving under the extreme influence of drugs after he crashed into 29 cars during a high-speed chase. He claimed there was a method to his madness: he "hit blue cars hard and white ones easy."

BPS: Minicult: Knight Rider is going into syndication, with episodes cut down to half an hour. Article attached.

Nat: Minicult: A man on Carson claimed to have discovered a new source of energy. He said there was more energy coming out of his mixture of metals than electricity going in, so it must be converting mass somehow. The part where he said he'd never taken a physics course in his life was very believable.

KM: Let's hope that Destiny Makers 2, by Mike Shupp '71, is not as bad as the first one, because here it is.

The second of two quick Miller motions passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}