\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 21, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(JME) Motion to approve the minutes as glowing yellow bananas.

(RvdH) Second!

(SSDT) Fails!

(BPS) Motion to approve the minutes as not having been interrupted by a Phonecomm this time.

(RvdH) Second!

Motion passes many many-1 and 2 "Ring!"s-2 and a buzz +Spehn.

\goto{Committee Reports}

(SLP) Moocomm: Star Trek IV next Wednesday.

(JME) Moocomm sub 2: The advertising has already started appearing, and from the commercials it seems they're trying to make this one funny.

(JAH) STrekcomm: this week, Good Morning America was running interviews all week long with the stars of STrek.

(JME) Pseudo-Moocomm: now that Sack Theaters has taken over the Janus and the Harvard Square, they're going to end the double feature every day. Sack now owns every first-run theater in Boston proper.

(KM) Move to change the name of Sack's to Sucks.

(BPS) That would be redundant.

(LAK) Famecomm: there's an article on Stanislaw Tem in the current issue of Discover.

(SSDT) IAPcomm: we're getting 100 dollars for our activities.

(JME) Jourcomm: please write for TZ and write book reviews. Please. Also, unless the older minutes show up again, I'm getting into recent territory- as recent as 1980- with appearances by, among others, Mr. Starr, Mr. Van der Heide, and Mr. Meltsner. Robert has one of the best-ever debuts at a meeting- three finger motions before the minutes were read.

(SSDT) Motion to commend Van der Heide's debut.

(DSK) Second.

Motion passes 10-none-5 +Spehn.

(GF via JME) Pseudo-People's Albanian Embassy: from the "Conspiracy" progress report. (Reads a section of the rules for Hugo awards concerning foreign editions of books that mentions Albania extensively.)

(BPS) Sitcomms: 1) NBC is allegedly about to sign Lee Majors and Lindsay Wagner to do a "Bionic Personages" thing as a one-shot TV movie. 2) NBC has extended Alf for the entirety of its first season.

(DSK) Addendum to that- there's a new Alf doll out.

(JME) Huntcomm: meeting after the meeting.

(BPS) Sitcomm: technically it wasn't SF or fantasy, but whatever Reagan did on Wednesday night wasn't reality either.

(JME) People Aren't As Dumb As You Think They Are Report: an LA Times poll showed that only 14 percent of the people polled actually believed the speech Ronnie gave after his press conference last week.

\goto{Old Business}

(JME) TZ got a LoC from John Boardman, a very old fan who first saw a TZ 25 years ago and was impressed that we were still around. I also got a LoC from Michael Ward, who was Skinner 1965-66. He was impressed that the library had gotten big enough to hold meetings in.

(KM) Really Old Business: I was on the subway last week when this middle-aged woman said "Do you know you look just like Jesus Christ?" I responded that I had been told that before, but when my hair was longer. She said "Oh," and then, "Are you related?" What's really scary is that I don't think she was joking.

(KM) We now have two Dole stickers toward the purchase of a Bananimal.

(SSDT) Harvard sent us that poster, and it's ugly.

OBA: um, us, uv, ur.

\goto{New Business}

(SSDT) Future New Business: no meeting next week due to Thanksgiving.

(JME) Minicult via John Dumas: a followup to the "Astronaut Barbie" Minicult. There is now a Cabbage Patch Young Astronaut doll. It comes in a white spacesuit with gloves, boots, and a helmet with a visor that opens and closes, and it carries a small American flag.

(BPS) Minicult: from the Glob of a little while ago- a policeman got ticketed for a 15-dollar fine for parking on street-cleaning day by a meter maid while parked at the scene of a burglary. He tried to get her to take it back but she refused. So he got in his car and followed her and her partner around town until he caught them double-parking, at which point he stuck them with a 30-dollar double-parking ticket.

(JME) Minicult: Ernest Hemingway's heirs had his name trademarked in order to use it on a line of outdoor sporting goods. It turns out that one of these items is an expensive English shotgun of the exact same model that Hemingway used to kill himself.

(BPS) Minicult: from USA Today- at Cornell, students and faculty opposed to Reagan's plan for mandatory drug testing lined up in front of a portable toilet and donated urine samples to be sent to the White House. The rally was sponsored by Patriotic Individuals Supporting Screening for Evil Drugs.

(JME) Addendum to that- there have been flyers posted downtown urging people to send their urine samples to the White House. They've been put up by the Committee to Flood the White House.

(JME) Minicult: one of my migraine medications turns out to have fairly decent street value. In large doses, it's an antidepressant useful for alleviating the down after taking crack cocaine.

(JME) At least one magazine, The New Republic, published a column in defense of getting high.

(KM) Miller Motion.

(SSDT) Fails.

(Malcolm Y) Motion to sell Janice's migraine medication on the street and use the money to buy a Bananimal.

Seconded by many.

Motion passes everyone-a sneeze-1+"Gesundheit" +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely subcreative,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}