\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 31, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (1/24/86) read and corrected.

Andy asks if there is a motion to approve the minutes, and CH makes a very nondescript motion. Passes lots-some-a couple of postmortem twitches +Spehn.

\goto{Committee Reports}

Whooshcomm: The Challenger went up, but not very far. MITSFS pays respects to the seven astronauts who died when it exploded 72 seconds after liftoff. The cause of the accident has not yet been determined.

ATS: Moocomm: The Marathon was, and it was fun. Also, 2010 next week, and The Gods Must Be Crazy. No SF movies Boskone weekend.

RvdH: Stonehengecomm: the sunset along the Infinite Corridor was really nice, especially with the colored glass in the lobby 7 windows. The new athletic center did not get in the way.

KM: I told the person who did that glass that it was a really good hack, and the person got really offended. It's an officially approved art project.

Discussion of the common superiority of hacks over art, with emphasis on baby fecal stains and burnt linoleum at the Hayden Gallery, as compared to the Mass Toolpike.

BPS: Prognosticomm: I would have been right except that 11 of Chicago's points defected. One was shot while escaping, but the other 10 made it over to New England.

SSDT: Panthercomm: a bunch of the missing books have been rediscovered. The few that are still missing are listed on the keyholder's desk.

CH: Concomm: flyer from SILiCON, attached. One of the games is a fight against an infection set inside a person's body.

JME: Jourcomm: Here's a dreadful looking submission- a story about a barbarian who gets transported to Chicago. Please write something for me; I don't want to publish this! Even the cover letter looks illiterate.

JME: Bananacomm: The president of Zimbabwe is named Canaan Banana.

RvdH: Move to commend the president of Zimbabwe for being named Banana. Chickens 8-8-24 +Spehn.

GF: Deathcomm: L. Ron Hubbard is dead of a stroke. It remains to be seen whether he will complete his dekalogy. Obituary attached.

BPS: Mobcomm: we got 570 dollars worth of books from New England Mobile today.

SSDT: I think I see what this object you handed me is. Some guy has been writing a journal of SF criticism, then wrote an SF novel based on his theories. He sent the whole mess to Georgetown University. They bounced it back to him, so he sent it to us. Most of it seems to be mathematical equations written in Elvish.

\goto{Old Business}

OBA: usual stuff, good enough.

\goto{New Business}

BPS: Minicult: a man went into a bank, gave the teller 6 fifties and asked for 3 hundreds, then tried to rob the bank. When that failed, he panicked and ran without even getting his 300 dollars back. The bank president thinks this is probably some kind of record.

CH: Minicult: a drug dealer, hearing a policeman at his door, flushed 4000 (or maybe 8000) dollars worth of heroin down the toilet. When it turned out the cop just wanted to say hi, the dealer got so upset he left town within the hour. Article attached. Also, the magnetic south pole has been found after being missing for 34 years. Article attached.

Phonecomm: it's a person who wants to sell us 75 Dr. Who books.

BPS: Adhesion in shortage on the Frankenstein poster...

CH: Move to send the president of Zimbabwe a membership, in honor of his being a banana. Passes despite a vote of 7-29-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}