\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 17, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (1/10/86) read and corrected by DSK, due to the real Onseck having gone underground.

Paul Dworkin: Move to approve the minutes as a mauve-y shade of pink-y russet. Passes enough-not nearly enough-7 +Spehn.

\goto{Committee Reports}

RvdH for JME: Jourcomm: Please write something for TZ already.

ATS: Concomm: There is a signup list for the MITSFS room at Boskone.

KM: Scavenger Hunt- rules are out now. You can enter if you weren't on the committee.

DSK: Triviacomm: Talk to me if you would be interested in forming a College Bowl team.

BPS: Ex-Jourcomm: I'm done. I finally got all the TZ36s mailed. After putting 3 stamps on each of 92 envelopes, I am truly tired of looking at Pearl Buck and Sinclair Lewis. 65.64, and I want my money.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

There doesn't seem to be any new business, just some childishness, with running commentary by BPS.

RvdH: Move to adjourn the meeting without mentioning the word banana. Passes a few-apathy reigns-some squawks +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}