\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 14, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
The MITSFS room at the Boston Sheraton is temporarily defined to be the Library. The gavel and gavel block are both present, but the electronic Onseck is not, much to the dismay of the organic one.

MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (2/7/86) read and corrected.

JME: Move to approve the minutes as well read.

Passes everybody-anybody who wants to jump-few +Spehn.

\goto{Committee Reports}

JME: PRcomm: Boskone has a panel discussion featuring Chip Hitchcock and Tony Lewis, called "40 Years of MITSFS."

JME: Deathcomm: Frank Herbert is dead. Obituary attached.

Discussion of Herbert's death as a loss to science fiction and L. Ron Hubbard as a loss to science fiction.

ATS: Skinner Report: I'm going to Ohio State Sunday to interview for med school. KM gets finger motioned for asking Andy if he's going by Red Line.

BPS: Ellacomm: I found some ribbons to refill Ella the typewriter.

JME: Boskcomm: tonight at 11 is a panel discussion called "Cute Aliens- Kill Them Now."

KM: Huntcomm: The Lithuanian Conspiracy leader says his group has 65 items. The judging will conflict with the art auction.

BPS: Sitcomm: Frank Furillo lives, barely.

\goto{Old Business}

BPS: It was 40 years and 1 day ago when they first booted up Eniac. Article attached.

OBA: um, us, uv, ur.

\goto{New Business}

JME: Minicult: Video Magazine claims pirated copies of Rambo are appearing in the Mideast with subtitles that convert Vietnam into the Philippines of 1943, with the bad guys being Japanese, to avoid offending Russia. Article attached.

KM: Minicult: American Craft magazine had an article (not attached) about a man who sculpts tree trunks using chainsaw and lathe.

ATS: Minicult: Esquire gave Sylvester Stallone the award for best primate.

JME: Move to condemn the architect of this hotel for reading too much Tolkien. (It has two towers and very confusing room numbers as a result.) Passes by acclaim.

JME: Minicult: American Express has James Doohan in one of their credit card commercials. It never refers to him as Scotty, but definitely assumes you'll know.

JME: Move to condemn Marcos with a banana for stealing our method of holding elections. Passes lots of "yo"s-few and a yoyo-fewer +Yoyodyne +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}