\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 17, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(CH) Motion to approve the minutes as omniscient.

(Chip Hitchcock) Second.

Motion fails 2-8-6 +Spehn amid puzzled exclamations of "Who? Huh? Why?" and "I didn't know I was omniscient" from the Onseck.

(BPS) Motion to approve the minutes as having a shiny pink underside.

(AA) Second.

Motion passes lots and lots-3-4 +Spehn.

\goto{Committee Reports}

(DSK) Concomm: next weekend (Oct 24-26) is Technicon '86 at WPI, sponsored by WPISFS. (This is pronounced  "Wuh-piss-fiss" which prompts much laughter.) Authors are Larry Niven and Ben Bova.

(LAK) Vice Report: the CPs found my permanent LSC pass. It was the only thing in a wallet they found- but it wasn't my wallet.

(SSDT) Addendum to that- the money drawer has a new lock.

(BPS) Moocomm: a whole horde of us went to see Peggy Sue Got Married. The consensus is that it was pretty good, worth seeing.

(LAK) Moocomm: Sue Hagadorn was wrong; Children of a Lesser God is not good- it's excellent.

(BPS) Moocomm: this Friday, LSC is showing Clue with all three endings- a different ending at each of the three showings.

(JME) Jourcomm: write for TZ please write for TZ we can't get an issue out in January if you people don't write for TZ.

(JME) People's Albanian Embassy: Paul Newman and the New York Post have been having a dispute over Newman's height. This week Newman wrote a letter saying that finding the truth in the Post was "as difficult as finding a good hamburger in Albania." The newspaper, as a postscript, wrote that "we are told that the hamburgers at Naun's Restaurant in downtown Tirana are in fact pretty good."

(SSDT) Skinner Report: anyone I catch going to an ice cream place in Union Square called Jolly's is going to lose their key. I got thrown out under threat of police summons for daring to suggest that the person behind the counter put the wrong flavor of sprinkles on my ice cream.

(BPS) Zoocomm: the zoo is in town. They've got a Barnum and Bailey train parked out in back of the reactor.

(JME) Addendum- their business has been flagging because of the baseball playoffs. Apparently a lot of parents are bringing their kids and also their portable radios, TVs, and so on.

(BPS) Sitcomm: it's mostly official- next fall, there will be a TV show called Star Trek: The Next Generation. The executive producer will indeed be Gene Roddenberry. It will be coming out as a syndicated thing.

\goto{Old Business}

(JAH) Herb Miller's here.

(JME) Shortly before the pseudo-summit in Iceland, the feds arrested about 10 LaRouche-oids for credit card fraud. LaRouche, in his press release, said he believed the reason for the arrests was that Gorbachev had demanded LaRouche's head on a platter before he would meet with Reagan in Iceland.

(SSDT) We've been getting Insight magazine for a while now. It's produced by the Washington Times, which is a front for the Moonies. In their publicity letter they claim to be "the publication that Reagan turns to first."

(JAH) Addendum to Connie's Minicult- after Jeopardy used questions on comic books in one show, the two people who put out the Comic Buyer's Guide called up the program's producers to find out how the managed to get intelligent questions up there. Turns out that one of the show's producers and the show's head writer are both avid comic-book collectors. The category got selected last because none of the people they get on the show read comic books. They intend to replace the two used questions and put the category up again on some future show.

OBA: um, us, usual "Yeahs", uv, ur.

\goto{New Business}

(JME) Minicult: Dottie Bean of Malden owns a 1976 Chevrolet which she loves. She was rather upset when pyromaniac squirrels burned up her car. The squirrels had nested in her air intake, clogging it with bits of burlap and half a bucket of hickory nuts. Many parts of the engine were completely melted when the squirrels chewed through the insulation on some of the wires, which ignited the burlap. Insurance coverage isn't clear. The most amazing thing is that a 1976 Chevy will still run with an air cleaner clogged with burlap and hickory nuts.

(BPS) Minicult: Brian Bosworth, a linebacker at the University of Oklahoma, was quoted in Sports Illustrated as saying "I love to tee people off." As an example of the ways he likes to do this, he told a story about what he did while working in a General Motors plant one summer. When bored, he would hide a random car part or a Coke bottle inside a car door or in some other inobvious place, creating a rattle. He would attach a note to the item saying "Ah ha! You found me!" in case the owner managed to track it down. General Motors is denying this happened while at the same time admitting that there's no way they can make sure it doesn't happen.

(JME) Warning- since there's a NotJustAnotherCon flyer up on the board, I want to mention that it was incredibly boring last year.

(Chip) Minicult: it could be worse than just a circus smell out on the siding. A few years ago, a bunch of roustabouts got annoyed at an executive who told them they couldn't park in his parking space. He came back a few hours later to discover that the roustabouts had arranged for every elephant in the squad to defecate on his car which was buried in elephant manure.

(BPS) Minicult: in New York City, a new 31-story apartment building faces, instead of the usual topping-off party, a lopping-off party. The contractor who filed the plans for the building apparently fudged the zoning lines to make it appear as if the building was outside an area with a 19-story limit on buildings. The people building the complex may have to get rid of 12 nearly completed stories.

(BPS) Minicult: CNN was cornering a number of UN ambassadors and asking them about the World Series. The Russian ambassador favors the Mets. Some people said he should have named the Cincinnati Reds as his favorite team. The Thailand ambassador commented that baseball was not the most popular sport at the UN; when asked what it was, he said "political football."

(JME) There was a headline in yesterday's Glob that speaks for itself: "Fight Breaks Out at World Peace Conference."

(CH) Minicult: Tom Brokaw, while interviewing the Prime Minister of Iceland, asked him if he, like 55 percent of all Icelandic people, believed in the Hulufolk, or Icelandic elves. The PM diplomatically replied, "Well, I've never seen one."

(JME) Minicult: an addendum to the Minicult of a few weeks ago, when Dan Rather was signing off his newscasts with "Courage"; Jay Leno the other night suggested that if we could just get Tom Brokaw to ask for a heart and Peter Jennings to ask for a brain, we could have a musical.

(BPS) We still have a hole in the roof.

(SSDT) I guess that's a report- we had a leak of the watery kind.

(JME) Motion to commend the Skinner for her precognition in knowing not to put any shelves there.

(SLP) That was my idea!

(JAH) That was my idea!

(JME) Make that a motion to commend the Star Chamber for its precognition.

Motion passes everyone-"There better not be any opposed"-3 +Spehn.

(JME) Motion to condemn the UMass (ed. note: ZooMass) SFS for daring to use our banana color on their flyer.

Motion passes by acclamation.

\vspace{12pt}

\noindent
Meeting adjourned, 1738 SST.

\vspace{18pt}

\centerline{Sincerely sub-omniscient,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}