\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 10, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

For the second week in a row, the reading of the minutes is interrupted by a Phonecomm. It is greeted with anguished screams and a cry of "Gavel it!" The Skinner answers the phone with "It had better be good." Upon finding out that it is Connie notifying people of her late-itudiness, people yell "Free Silver, Free Silver."

RvdH makes an interesting motion on one leg across the room, and RJG seconds it.

Before it can be voted on there is another Phonecomm which is again greeted with tortured screams, this time in chorus. It's the Vice with a Theftcomm: her room has been ripped off. Among the missing are the Vice's guitar and flute and the keys to both the MITSFS and the MITSFS money drawer. The Vice announces a "Wait for Phys Plant to change the lock on my room" party.

After some discussing of MITSFS and East Campus Security, the meeting proceeds. RvdH's motion passes by acclaim.

\goto{Committee Reports}

(JME) Cornelia Otis: Entropy strikes Dan Rather. Dan Rather was walking down Park Avenue in New York last week when two men in suits came up to him and said "Kenneth, what's the frequency?" When Rather informed them that he wasn't Kenneth, they started assaulting him. He ran into a nearby hotel lobby. The two men followed him but ran off when he called over a security guard. Nobody knows who the men were, who they thought Dan Rather was, or what frequency they wanted and why.

(There are comments suggesting that either Dan Rather is an agent of the Bavarian Illuminati or that an agent of the Bavarian Illuminati is running around wearing Dan Rather's face.)

(SH) Mike Royco is running a contest: "If you think you know what frequency Kenneth wanted..."

(SSDT) Cornelia Otis sub 2: I heard from coworkers that during a recent 8.01 exam, a female upperclassman snuck in to take the test. About halfway through the testing period, she stood up, shouted "I can't take it anymore! It's too hard!!!" and ran through the room and out the front door screaming her head off. It created such a disturbance that the test will not be counted.

(KM) This has happened in the past; in the old version, the guy got up in a first story classroom and jumped out the window yelling "I'm a vector! I'm a vector!!!"

(JME) Bananacomm: Dole as a promotional gimmick is selling these stuffed "Bananimals;" there's a Banilly Goat, a Banelephant, a Banangaroo, and a Banaceros. The Banangaroo has a little banana in its pouch and I think we should chip in and get one for the MITSFS.

(JME) Jourcomm: write for TZ (cubed)!!! PLEASE write for TZ!!!

(KM) Rosfap: I'm caught up now; the new zines should be on the shelf soon.

(SSDT) ASAreport: I actually went to the ASA's general meeting and MITSFS got mentioned. The president, Michael Franklin, went around the Institute looking at and rating bulletin boards; MITSFS got a "Good" classification.

(KM) Rosfap sub 2: There is a "Naiad Press" looking for SF and fantasy with a lesbian orientation.

(JME) Sitcomm: Twilight Zone is in the bottom ten rating of the new shows this season; it's up against Hunter and Spencer for Hire, which are both reasonably popular cop shows, and is on Saturday at 10, when most of the younger audience is not watching TV. Starman is also in the bottom ten (this is greeted with applause) and proving that I'm right about it being possible to underestimate the taste of the American public, Life with Lucy is in that same area.

(BPS) Sitcomm sub 2: Does anyone here watch or know anyone who watches Amazing Stories?

(Jim Rauen) WinstonSmithcomm: the Boston Community Information Project's second phase was launched this week, allowing people with IBM PCs to read news from the Associated Press and NY Times the day before it comes out.

(BPS) Libcommcomm: Ken Johnson, having been occupying his car when it totaled itself, has gotten alternate transportation. He came in the other day, saw the new safe, and was much impressed by it but thought it would look better with shelves.

(SSDT) Addendum to that: the safe originally contained a rack of index card files about six long and one high that would sit on top of the pair of filing cabinets. I tried to get it for us, but due to a timing error, before John Burns got to it it was compacted. We don't want it anymore. In atonement, John has volunteered to get some spare lumber and make shelf-like objects for the safe.

(JME) Moocomm: Peggy Sue Got Married has been getting rave reviews from everybody but USA Today; it opens tonight and we could get an expedition together if people are interested.

(SH) Moocomm: Children of a Lesser God, which is definitely fantasy because it bears no relation to reality, is also very good.

(JME) Semi-SortOf-Jourcomm/Famecomm: I'm now officially an editorial assistant at Aboriginal SF.

(RJG) Emercomm: yesterday, about 12:30, about six students and a professor from Emerson College came by to see our library. We got two new members out of the deal and some promises by people to come back when they have money. They're all doing papers on different authors. They asked why we used a large wrench as a gavel and I couldn't tell them.

(JME) Because it was there.

(BPS) Mmocbom: instead of Mobcomm taking money from the library, this is a Mmocbom; Larry Lendthoff and I together are donating 250 dollars to MITSFS and we're trying to con my boss into matching it.

(SSDT) Moocomm: I went to see Blue Velvet and I was disappointed, although it's definitely David Lynch. The main bad guy reminded me so much of the comic villain from Little Shop of Horrors that I started cracking up every time he came on screen.

\goto{Old Business}

(JAH) Onseck Peeve: during the reading of last week's minutes I got jumped on by two people for allegedly misreading something. Well, the tape bears me out- I was right and they were wrong, so there!!! Any further attempts to correct the Onseck's diction will be met with great scorn or possibly thrown missiles, depending on my mood.

(SSDT) The items for Stoneybrook went, transported by Merryl Gross, which saved us the postage. We sent them 425 magazines, plus 3 books that had extras on the "For Sale" shelf.

OBA: usual non-creative usuals.

\goto{New Business}

(BPS) Minicult: the board of aldermen in Chicago have done something to reduce the parking problem in Chicago, which is about as bad as it is here; they've passed a law to let the board of aldermen park anywhere they like and be immune to parking tickets.

(RvdH) Minicult: from Monday's NY Times- a man testified that he entered his home one Sunday morning, saw a rat, and whacked it with Sunday's NY Times, killing it instantly.

(AA) Minicult: from today's NY Times- there's a village on Long Island called Shirley; the people there want to change the name to Floyd.

(KM) Move to send the residents to East Campus.

(The Onseck comments "But they have to give it a female name- no man is an island." The resulting Albanian motion rebounds onto Rob Gates.)

(RvdH) Minicult: the latest Road and Track reports that a driver in Ontario who was driving erratically was pulled over by police who tried to give him a breathalyzer test. He refused on the grounds that the policeman had picked his nose then handled the mouthpiece. The judge ruled that this was in fact adequate reason for refusing to take the test.

(JME) Minicult: the eighth Congressional District race has not quite turned into a pissing contest, but it has turned into a bloodletting contest. Clark Abt publicly challenged Joe Kennedy to match him blood for blood and prove he was drug-free. Kennedy refused but Abt went through with it on national TV.

(CH) Minicult: next month Lotus will introduce a PC software program called Hal which stands for "human access language" which uses natural language to give commands. Originally the programmers had set it up so that if you put in "Open the pod bay doors, Hal," it would respond "I can't do that, Dave." The legal department made them change it; they're worried about lawsuits.

(KM) Motion to condemn the Lotus legal department as a bunch of spineless jellyfish wimps!

(BPS) Who will be first against the wall when the revolution comes!

Seconded by acclaim, passes by acclamation.

(BPS) Minicult: a small town in Pennsylvania that may be named Wilkinson is having its centennial this year. In 1962 they buried a small time capsule to be dug up this year. In order to keep it from being dug up and vandalized, the Star Chamber of the Chamber of Commerce got together for a secret meeting to decide where to bury it, and then they went and did it. They're all dead now, and no one knows where the thing is buried.

(KM) Move to commend the Gulf Corporation for mutant genetic engineering of Bananimals.

(AA) Second.

Motion passes everybody-3-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1801 SST.

\vspace{18pt}

\centerline{Sincerely subconscious,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}