\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 20, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of two previous meetings (5/30/86 and 6/13/86) read and corrected.

(SSDT) Motion to approve the minutes as 26.

(SLP) Second.

Motion passes 26-2.6-.26 +Spehn.

\goto{Committee Reports}

(SSDT) Pianocomm: Thom McKendree is gone, as is Herb Miller, temporarily. Sue Pitts will continue as LHE until a new one is selected.

(JME) Jourcomm: I just got an envelope addressed to Twilight Zone magazine, "Al Shawn Gramates." And the deadline for TZ is July 1st. I need more reviews.

(BPS) Mobcomm: My whole company just moved out to Lexington.

(JME) Gorcomm: I went to Provincetown and discovered that you can't walk more than 10 feet without hitting a leather shop.

(BPS) Move to send the Vice to Provincetown.

(JME) Second.

Motion passes just about everyone-2 raspberry frogurts-a few +Spehn.

(JME) Whooshcomm: I have a letter from Washington Monthly by Charles Pratt responding to an editorial that said another shuttle shouldn't be built for factories in space because we won't see them for a long while. Pratt says we'll see them any day now and accused the editorialist of being short-sighted. To which the editorialist replied, "Oh, twaddle."

(BPS) Combined Sit- and Moocomms: MTM is invoking a contract clause allowing them to hang onto Pierce Brosnan for two months after the cancellation of Steele and trying to peddle the show to another network. No one knows what effect this will have on his role as the new James Bond.

(SSDT) Panthercomm: Inventory July 19th and possibly 20th.

(KM) Pseudo-Panthercomm: Multics is going away in a year.

(BPS) Sitcomm: The Pepsi ad set in the 25th century won a Clio.

(CH) Move to commend Pepsi for having really neat commercials and never changing its formula.

(BPS) Second.

Passes about 12-1 and 2 halves-3 +a lamb +Spehn.

(JME) Porncomm: some justification for 7-11 giving in and taking the girlie magazine off the shelves- a letter from the Pornography Commission threatening to put 7-11 on its list of identified porn distributors, and an article by the Liberty Federation (formerly the Moral Majority) called "Pornography Causes Murder."

(BPS) On the brighter side, an anti-porn bill got stomped in Maine.

(CH) A friend reports that stores in Texas have taken Penthouse and Playboy off the shelves and have put offensive magazines such as Ladies Home Journal behind the counter.

\goto{Old Business}

(JME) Former Skinner Guy Consolmagno was in town briefly to do some research. He stopped by and said hi.

(BPS) 14 years ago Tuesday, Watergate took place.

(CH) The most recent People magazine had a one-page article on the banana slug of Santa Cruz.

(SSDT) A large anonymous donation came in last week and was traced via a Coop receipt to an expired member owing over 18 dollars in fines.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: Progressive Apparel, Inc. is marketing a line of armored underwear.

(JME) Minicult: the man who lobbied to let employees of the Texas lottery division play the lottery has become the only man to win it three times.

(JME) Minicult: a wide variety of items are being marketed cashing in on Liberty Weekend. Among them: charcoal briquettes, porcelain dolls, jigsaw puzzles, peanuts, chocolate statues, women's bend-over trousers, and a limited-edition Harley-Davidson motorcycle.

(KM) Some political groups are planning on offering Burger King and McDonald's coupons to young people to get them to vote.

(BPS) Minicult: Newsweek June 23rd- a SC pastor resigned his post, saying in his farewell sermon that for the last 14 years he had been under the spell of a witch. The "curse" was cast upon him by a Vassar coed he dated while at Yale. He did not elaborate.

(JME) Minicult: The Witches of Eastwick is going to start filming soon; a witches' anti-defamation league is protesting the portrayal of witches in the book.

(CH) Minicult: two people who, while waiting for rescue from a shipwreck decided to get married, actually got married once they were married.

(BPS) Playgirl magazine is bankrupt.

(KM) Motion to ask the Skinner to find out whether there are Constitutional Bicentennial Bananas.

Motion passes many, many-2 and a frogurt-Span +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Sincerely submerged,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}