\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 8, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(BPS) Motion to approve the minutes as Onseckular, which is not the same as On-secular Humanism.

(JAH) Second.

Motion chickens 8-5-7 +Spehn.

(LL) Motion to approve the minutes as funnier than slipping on a banana peel.

Fails by "Go away."

(JAH) Motion to approve the minutes as passed out.

Passes everyone-one vocal-a few +Spehn.

\goto{Committee Reports}

(SLP) LHE Report for June: Income- 1118.10, Expenses- 451.49, Profit- 666.41. For July: Income- 210.50, Expenses- 136.04, Profit- 74.46. That's the third month in a row we've made money. Equity- 3895.70.

(SSDT) The missing pieces of the shelves came in, finally.

(LAK) Moocomm: LSC is showing a double-feature of Altered States and Swamp Thing tonight. Tomorrow night is Strange Brew.

(SH) Moocomm: Sac is moving closer to a total monopoly on theaters in Cambridge. Not only have they bought the Harvard Square Theater and the Janus Theater, but the Brattle has filed for bankruptcy.

(SSDT) Pseudo-Concomm: we almost sponsored a convention. Jon Pertwee's agent called us asking if we could get Kresge for him for all of Halloween weekend, as Pertwee is on a lecture tour with a small convention tagging along behind him. I called LSC and they said he could have maybe two hours that weekend.

(BPS) Sitcomm: Pierce Brosnan is safe; it has been announced that Timothy Dalton, a British actor who has done some TV movies, will be the next James Bond.

(BPS) Pseudo-Moocomm: I saw a black Toyota/Subaru in Kresge Lot the other day with a Massachusetts license plate saying "Mad Max."

(BPS) Pseudo-Moocomm: apparently no one in America liked Howard the Duck.

(KM) Pseudo-Jourcomm: TZ is almost done. We could still use art.

(JME) Former Skinner Report: Ken and I are moving because our landlord decided to put the squeeze on his residents. The good news is we can afford to move because I just got a 4000/year raise.

(JME) People's Albanian Embassy: Albania just opened its first railway link with the rest of Europe. It's only for cargo, says an anonymous spokesman.

\goto{Old Business}

No old business.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: a family feud erupted at a Rhode Island wedding reception when the families got in an argument over how to cut the wedding cake. End result: the groom, his brother, and his parents were in police custody and the bride and her mother were in the hospital recovering.

(BPS) RvdH is moving tomorrow and he needs all the help he can get.

(Some discussion about whether these statements are necessarily connected.)

(BPS) Minicult: Melbourne, Australia- art thieves kidnapped a Picasso painting and are holding it for a ransom of government subsidies of artists. They threaten to destroy the painting in a week and steal others until their demands are met. The government doesn't seem willing to make concessions.

(BPS) Minicult: Concord, New Hampshire- Cathy Keaton, officer of Penthouse, president of Omni, and Robert Guccione's main squeeze, has been trying to sue Larry Flynt since 1975 for publishing nude photos of someone else and claiming it was her and for printing a cartoon suggesting that Guccione had given her a venereal disease. The case has gone through many states and courts until it got reinstated by the Supreme Court in 1983.

(KM) Today she got 2 million in damages.

(John) Famous SF authors in politics- during the hearings of William Lundquist's appointment as Chief Justice of the Supreme Court, Kurt Vonnegut was seen chatting with senator Joe Dayton, whom he described as a close personal friend.

(JME) A schizophrenic living in the woods of western Massachusetts has a tent full of Westerns and SF books and claims that Isaac Asimov is his favorite author.

(KM) Motion to commend all landlords with a banana.

(SSDT) Second.

Passes everyone-no one-people whose landlords haven't raised the rent recently +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely subordinate,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}