\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 7, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (1/31/86) read and corrected.

RvdH: Move to approve the minutes as being black and white and gray and turquoise and maroon and mustard and green. Passes everybody-a few-some people can't make up their minds +Spehn.

Note: the motion described the shirt the Onseck was wearing, which clashed with everything, including itself.

\goto{Committee Reports}

JME: Jourcomm: I warned you! Clem the Barbarian is even worse than I thought it was!

Janice starts reading the story at us, and after what sounded like four lines of Vogon poetry, we drowned her out with two choruses of Rabbits. Janice then changes her threat from reading two pages at each meeting to sending copies to everyone.

ATS: Concomm: There are 7 Scavenger Hunt entrants, mostly teams. Huntcomm immediately after the meeting.

JME: Deathcomm: The Church of Scientology took out a full page ad of tributes to L. Ron Hubbard. The first quote was from Sonny Bono about how Hubbard changed his life. The ad also said that the dekalogy did in fact get finished before he died. He wrote it as a novel so huge that it had to be chopped into ten books.

ATS: Pseudo-LHE Report: Sign up to man our Boskone table.

JME: More on Hubbard- he left most of his estate to the church in a will which was signed the day before he died and requested no autopsy. His body was cremated. An article with even more juicy details is attached.

DSK: Whooshcomm: I was there. It wasn't pretty. Memorial service noon Wednesday in Kresge.

BPS: Whooshcomm: Of the 3 major news magazines, US News and World Report was the only one that showed any class. They had a nice set of relevant pictures instead of just the fireball on their cover.

ATS: Whooshcomm: Reagan has appointed a blue ribbon commission, including Richard Feynman and the head of our Aero-Astro department.

JME: Whooshcomm: The New Yorker had to recall their latest issue due to a cartoon of one man telling another "I wish they'd sent my congressman up in the shuttle."

SSDT: Mechaniccomm: I'm performing a tedious but not dangerous ribbon-rewind operation on Ella, Paul Dworkin assisting.

BPS: Whooshcomm: Reagan mentioned the Orient Express space plane in his delayed State of the Union address.

JME: He also recommended cutting funding for Amtrak and all other forms of ground transportation.

GF: Right, he even quoted from Back to the Future- "Where we're going, we don't need roads," which is almost accurate.

TMc: He also said that we're in a race with the Russians to get to the future first. Everyone is very impressed, but predicts a draw.

\goto{Old Business}

BPS: Eight years ago we had a lot of snow right now. Let's do it again.

JME: Motion to commend Scott for being dead. Passes by acclaim.

OBA: um, us, uv, ur.

\goto{New Business}

JME: Oscar nominations are out. Not much SF, but Back to the Future got a couple, including best original screenplay. Spielberg did not get nominated for best director even though The Color Purple got nominated for everything else.

BPS: Minicult: NBC planned a minute of dead air so people could go to the bathroom during the Super Bowl. This was supposed to lower the water table 11", but it didn't happen. the game was such a blowout that people wandered away whenever they felt like it.

JME: STrek 4 is really in the works.

Andy has trouble differentiating Trek from Wars, and ends up getting condemned for not being not nearly not dead, the result of his first attempt at using the Inverse Skinner Rule. He is expected to improve with practice.

Rabbits starts up again, so Janice moves to commend LSC for putting banana color on part of their rainbow calendar. Passes many-almost as many-4 chickens and a goose +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}