\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 14, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(RvdH) Motion to approve the minutes as cobalt blue.

(DSK) No, I've got a better one. Motion to approve the minutes so that their genes may be mixed with the genes of a firefly so that they glow in the dark.

(RvdH) Second!

Passes everyone-1-3 +Spehn.

\goto{Committee Reports}

(DSK) LHE Report: this was a good month. Assets- 1978.63, Income- 1303.47, Expenses- 353.29, Equity- 2928.81, Profit- 950.18.

(BPS) Sitcomm: several. 1) ABC has canceled or at least hiatusized the new Lucille Ball show. There is hope for life on Earth. 2) Twilight Zone will come back for a probably very brief stay; it's being changed to half-hour segments and is to be run against The Cosby Show. 3) The A-Team has been canceled, thank God. Also, for those into participatory nonsense, tonight's episode allows the viewers to choose which way the show will end by dialing one of two 900 numbers.

There is a Phonecomm during the middle of the Sitcomm; it's a Harvard student whose drama group is putting on the play Pillar of Fire which is from a Bradbury short story. They're going to send us a poster and they want it made known that they are putting it on November 14 and 15 at 8:00 at Dunster House.

(CJH) Sitcomm: from the Herald- Crime Story is being moved into the slot Hill Street Blues used to occupy while Hill Street moves to opposite Moonlighting on Tuesday.

(DSK) I heard that it was a three-way switch also involving LA Law.

(Some flaming about which version is correct.)

There is a Phonecomm sub 2. It's someone who wants to know what time the meetings start.

(SSDT) Pseudo-Jourcomm: the MIT Archives are still planning on microfilming or microfiching our TZs. I'm trying to talk them into fiching it, since that's the reader we have.

(SSDT) STrekcomm: SEDS ran a STrek marathon Monday night through Tuesday. They had about 19 different episodes and the last two movies. They did quite well, managing to fill the Unified lecture hall.

(BPS) Addendum- there's a rumor that the opening of STrek IV has been moved up to November 26.

(SLP) There's going to be a sneak preview on the 25th. Channel 38 has been giving away tickets.

(JME) Standard Jourcomm: Please, PLEASE, PLEASE!!!

(JME) Jourcomm sub 2: someone wrote to us asking for information on advertising in TZ. He wanted such things as market surveys and media kits. Obviously we've been confused with Twilight Zone Magazine again.

(BPS) Whooshcomm: President Reagan today, by doing nothing, pocket-vetoed NASA's '87 appropriation. This doesn't affect NASA's current projects but it does kill off the shuttle replacement.

(JME) Huntcomm: another brief meeting after this meeting.

(JD) Famecomm: Bay Windows this week did an article on "Science Fiction in the Gay Community," a collection of articles that highlights the Galaxians, the local gay fandom group of which I'm a founder and so my name is mentioned about three or four times in here. And they spelled it right, too.

(Much flaming on spelling names correctly and incorrectly and so on, which the Skinner attempts to stop by banging the gavel.)

(RvdH) Motion to condemn the Skinner for making noises with her gavel while people are trying to talk.

(Seconded by all but fails by Skinnerial decree.)

\goto{Old Business}

No old business.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Bad News: Roger C. Carmel, better known as Harry Mudd, passed away yesterday at age 54.

(DSK) Minicult: from today's Tech- "Major corrected Minor error." A Captain Minor of the Connecticut National Guard was participating in a training exercise and fired a 105 mm Howitzer shell onto a Connecticut highway. He overshot his target by more than a mile. Major David Smith said that Captain Minor would not be allowed to participate in any more exercises.

(RvdH) Related Minicult: the Libertarian magazine Reason ran an article a couple of months ago about rent control in Berkeley. Some economist was quoted as saying "Rent control is the second best way of destroying a city, after aerial bombing." This month they ran a letter from someone who'd talked to a Palestinian student in Lebanon who said that they had very strong rent control in Beirut; landlords have been known to go to one or another of the factions and ask them to bomb their property.

(JME) Minicult: in a letter to Ikie's Magazine this month, a reader complains about the sexism she detected in a James Tiptree Jr. story and accused the writer of being a male chauvinist.

(JD) Minicult: ask for this under your Christmas tree- Mattel has come out with the Astronaut Barbie doll. She wears a two-piece pink and silver spacesuit with a bubble helmet with antennae. It says it comes with accessories- I guess that means Barbie's Dream Space Station.

(BPS) Minicult: from today's Glob- thirteen people pleaded innocent to insurance fraud. Among the defendants were the proprietors of Pat's Towing Service in Cambridge.

(CJH) Minicult: a patron of a library in Woodbury, Connecticut got very upset because the library had a pet alley cat named Fred living there. She took her protest to the governor's office in January; after several referrals, her case got discarded, but the cat is now internationally famous.

(JME) Minicult: the MBTA wants to replace the Green Line arborway trolleys with buses. People didn't like it; a referendum showed a 2:1 preference for trolleys, but the MBTA is going to keep taking surveys on the grounds that the referendum was too simplistic.

(BPS) Addendum to that- anyone who rides the subway has probably noticed that sometimes the trains just go right through the station without stopping. If you thought it was part of a brilliant plan to add another empty train to the line somewhere, you're wrong; apparently it's common practice for the train drivers to just speed through stations if they're running behind on their schedules. This practice may end soon; one of these trains went zooming past Mike Dukakis when he was in a hurry.

(JME) Minicult: Tank MacNamara has been science-fictional this week, apparently set in a futuristic high school. In one strip, the teacher is explaining how the verb "to Boston" came to be, as in "Well, he Bostoned at the last minute and failed the test."

(BPS) Or, "The spaceship Bostoned while trying to land." "I'm extremely sorry, Mrs. Frobush, your husband is Bostoned."

(CJH) Minicult: from sometime this summer- the Massachusetts legislature is considering a bill outlawing mooning. Other legislators are having trouble taking it seriously.

(RvdH) Move to put genes from a firefly into a banana plant to create glowing yellow bananas.

Passes by acclaim.

\vspace{12pt}

\noindent
Meeting adjourned, 1742 SST.

\vspace{18pt}

\centerline{Sincerely subsandwich,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}