\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 5, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(CJH) (Makes a variety of strange twitches, jerks, and jumps.)

(BPS) Second.

Motion chickens 5-4-lots and lots +Spehn.

(Someone else makes a strange motion and RvdH makes chimp noises. Someone seconds something.)

Motion passes many, many-6-2 +Spehn.

(SSDT) It passes, and I'm still not sure what it was...

\goto{Committee Reports}

(SSDT) Report from the Bowels of the Institute: They've coughed up our TZs, not much the worse for wear. I don't know when we'll be getting the microfiche.

(DSK) LHE Report, month of November: Assets- 2928.81, Income- 296.77, Expenses- 79.66, Equity- 3145.92, Profit- 217.11.

(BPS) Moocomm: if anyone hasn't seen Star Trek IV yet, you might as well. It's pretty good.

(SSDT) Addendum- not only are Star Trek V and Star Trek VI in the works, but also VII, VIII, IX, and X. Shatner directs V and VI. This is from a pretty reliable source.

(JAH) Onseck Report: my teeth's parole has been revoked- I'm back in braces.

(BPS) Sitcomm: just when you thought it doesn't get any dumber. CBS has an upcoming midseason replacement, the title of which I've mercifully forgotten, that involves four desperadoes and the sheriff pursuing them in 1899 who fall through a time warp into modern-day Houston and decide to open  a detective agency.

\goto{Old Business}

(SLP) We got another SFWA book in, and it was accompanied by the standard SFWA letter. But at the bottom of the form letter, there's a handwritten note from the editor that says "Is Tech still Hell? It was in 1953."

OBA: um, us, uv, ur, usual "What about the usual debate?", usual "Shut up!"

\goto{New Business}

(BPS) Minicult: some art gallery is getting into trouble for showing some of Andy Warhol's paintings of John Wayne. There is a firm out there that has trademarked John Wayne and claims nobody can use his name or appearance for anything without their permission.

(SSDT) Minicult: from the Phoenix- apparently, bad translations of advertising slogans into foreign languages are causing a lot of embarrassment for ad agencies. Some of the faulty translations that have been seen include "Budweiser, the Queen of Beers," a light beer that is "Filling. Less Delicious," a beer advertised as "the beer that will make you more drunk," the Chevy Nova whose name translates as "It doesn't go" in Spanish, "Coke Adds Life" which in Chinese became "Coke, the drink that brings your ancestors back from the grave," and, best of the bunch: Frank Purdue's boast that "It takes a tough man to make a tender chicken" came out in Spanish as "It takes a sexually excited man to make a chicken affectionate."

(CJH) Up in Newfoundland, there is an island called Belle Isle. A few years ago, a bull moose swam out to the island from the mainland. He's still there, and apparently he's getting lonely. He's been trying to make it with the local population of milk cows. The farmers, annoyed because he's upsetting the cows, are arranging to airlift a female moose in for him.

(SSDT) Up in Vermont, there's another moose trying to make it with one particular milk cow. Sarah Young of Awesome Records says her company intends to release a single about it entitled "Lovesick Moose."

(DSK) Is somebody going to make a Miller motion or what?

(BPS) Or what!

Miller motion fails.

(AA) Miller motion.

Motion passes about a dozen-half a dozen-half a dozen +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1727 SST.

\vspace{18pt}

\centerline{Sincerely exasperated at the Athena network,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}