\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 9, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

Meeting opens with discussion on novel ways to kill hamsters.

(DSK) Motion to approve the minutes as banana-colored.

(JME) Motion to approve the minutes as pumpkin-colored.

Passes about 18-4-4 +2 wings +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: write for TZ!!! Thank you.

(JME) Cornelia Otis: entropy in Louisiana. Louisiana has a long history of insane politicians, which now includes the mayor of Alexandria who has been taken away for psychiatric evaluation after showing up at the police station in February with shaking hands and an eye twitching while making wild allegations. Among the allegations he has made in the past are such things as claiming to be able to talk with the Kremlin through a ring on his finger and that gigantic dope rings were being run by the schoolteachers. Article in the interesting reading folder.

(BPS) Sitcomm: USA Today says Twilight Zone has been picked up for another season in a new time slot, Saturdays at 10 PM.

(JAH) Sitcomm sub 2: the new sitcom All is Forgiven is worth watching.

(VS) Picniccomm: somebody should have brought home two Walker Special knives that I took to the picnic.

(CH) Sitcomm: tonight, on various channels in the Boston area, these movies are being shown- The Exorcist II, Thunderball, The Birds, and a movie called The Tunnel about a transatlantic tunnel.

(JME) Moocomm: the first "cute robot" movie of the summer is out. It's called Short Circuit and is about a robot named "Number 5" that gets hit by lightning and starts acting like a human being. It has Steve Gutenberg and Ally Sheedy, and has gotten some good reviews. It's being billed as a comedy.

(KRJ) It's directed by the same person who did Wargames.

(LAK) Moocomm sub Vice: for those who like sex and violence, tonight LSC is showing Everything You Always Wanted to Know About Sex, and Saturday is Mad Max III.

(SSDT) Pianocomm: we're missing our list of the origins of various committees.

(JME) I have them; I'm using them for an article for TZ.

(BPS) The Mobcommobile now has a stereo and cassette player.

\goto{Old Business}

(BPS) An addition to our Jane Fonda picture collection: an ad for Barbarella from next Thursday's TV Guide listing.

(BPS) Jerry Falwell put a fundraising letter in Bay Windows talking about his losses from the man who programmed his computer to dial the Rev. Falwell's toll free advice line many times, thus forcing the Rev to go to a toll number. Bay Windows, however, after a little digging around came up with one last toll-free number for Falwell's organization and proceeded to publish it. Article attached.

OBA: um, us, uv, ur.

\goto{New Business}

(JAH) Minicult: Louisiana is having another Creationism vs. Evolution trial; the judge has scheduled it for the anniversary of the Scopes trial.

(JME) They got it to the Supreme Court this time.

(BPS) They should make Louisiana teach EVERY creation myth, not just the Christian one.

(BPS) Minicult: Ferdinand Marcos is in the wrong line of work, given that he won the Kentucky Derby last Saturday. A horse named Ferdinand came in as a 17:1 shot to win. Willie Shoemaker was riding him.

(SSDT) Minicult: the astronomers think they've found a black hole the mass of many, many galaxies- around a thousand trillion times that of our sun. It's either that or something called a cosmic string, which is either a crack in space or a high-density vacuum.

(BPS) Minicult: from today's Wall Street Journal- the Burger King ad campaign featuring "Herb" was disappointing in terms of sales generated. "Herb" was recognized almost instantaneously in 57 of 58 stores he visited except for one in Canada, where he had to stand beside his own poster for several minutes before he was noticed.

(JME) Burger King refused to pay one person who recognized Herb because the kid was only 15.

(JME) Minicult: apparently there is a passage in the Bible that proves to fundamentalists that pi is equal to 3. It describes a basin that was 10 cubits across and 30 cubits around.

(JAH) Minicult: from the Glob yesterday- a baby with two heads and stomachs and only one bottom that's doing just fine. It's named Jose and Pedro.

(BPS) I won the Gavel Toss and it didn't even get into the minutes or anything.

(HAM) You ALWAYS win the Gavel Toss.

(JME) That's Old Business.

(JME) TZ has been getting a lot of letters from amateur writers who seem to think they're submitting to a real magazine.

(BPS) MITSFS donation- to go with our Star Wars poster, I have a "Star Wars" poster! (Exhibits artist's conception of SDI taken from Discover magazine.)

(JME) Does anybody know what Grammarcomm, Secretary of H.E.W., and the Hub Overgovernment are? They're on the organizational chart but they aren't listed on the committee sheets.

(BPS) By-the-waycomm: this is the new Telzey.

(SSDT) His name is John Burns.

(Nathan G) There'll be something about ST IV on Entertainment Tonight next Tuesday.

(BPS) Delayed Sitcomm: Godzilla 1985 premieres on TV 8 PM next Friday.

(Many motions involving bananas and Jerry Falwell, a Miller motion, and the beginning of "Rabbits" all fail to close the meeting. Finally...)

(CH) Move to have Jerry Falwell commit an unnatural act with a banana.

Passes many-1-a barnyard +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}