\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 5, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting (8/22/86) read and corrected.

(JME) Motion to approve the minutes as not quite as weird as the Onseck.

Motion just barely passes 12-9+the Onseck's staunch defender-9 +Spehn.

\goto{Committee Reports}

(SSDT) Pianocomm: we have an LHE, Scott Kitchen.

(JME) Jourcomm: Proof positive that fans at conventions will buy anything- we sold 16 copies of TZ 37, 11 copies of 20 Years in the TZ, 3 copies of 36, and 3 copies of 35. Gross: 74.75, of which we get to keep 37.38. We also sold 3 t-shirts. Next year we'll bring chocolate-covered frozen hamsters on a stick.

(JME) Moocomm: I have a publicity flyer for ST IV.

(BPS) Sort of Moocomm: We just got a copy of V. MacIntyre's Enterprise: The First Voyage, and it's sorta good. There's an ad in the back for the novelization of ST IV which will also be done by MacIntyre.

(JME) Pseudo-Libcomm: We brought a lot of free books back from WorldCon, including two advance copies of the fifth volume of Mission: Earth, L. Ron Hubbard's decalogy.

(JME) Pseudo-Libcomm again: there's a new professional SF magazine that was being given out at WorldCon, Worlds of If. It's not related to the old If except that they bought the rights to the name.

(LAK) Whooshcomm: I heard on the radio today that they finally managed to launch a Delta rocket.

(JME) WorldCon Report: the Hugo winners and the bid winners are posted on this side of the fireproof door. It's New Orleans in '88 and (big surprise) Boston in '89. Judy Lynn Del Rey won the Best Editor Hugo and someone came up to read a letter from Lester Del Rey refusing the award on the grounds that they had only given it to her because she was dead.

(JAH) Michael Whelan got the Best Artist award again and in his acceptance speech announced that he wasn't going to run for it next year because he thinks some other artists should get voted for.

(JME) Harlan Ellison told off some TV reporter at the benefit auction for Manly Wade Wellman's widow, to the great delight of almost everybody. The highest-selling item was Steven King's notebook containing two unpublished stories; it went for 5200 dollars.

(BPS) Speaking of Steven King, we have IT. It is his longest work and shortest title to date.

(CJH) Addendum to WorldCon Report: Best Nonfiction Hugo went to Science Made Stupid.

(JME) Famecomm: my panel went really well; the room was almost full. One man is planning on writing us in as the beneficiary of his SF collection which is already about 7000 books even though he's only in his twenties. He's also talking about leaving an endowment for the care of said collection.

(GF) Best WorldCon Story: GOH Ray Bradbury went down to the Dealer's Room without his badge, and the gopher on duty said "You can't come in here without your badge." So he got it out and put it on, and the guy said "Okay, you can go on in, Mr. Brad- oh, shit."

(JME) Pseudo-ROSFAP: I picked up a new fanzine at WorldCon that is totally devoted to centaurs, and nothing but centaurs. It included a questionnaire for the readers with questions like "Why do you identify with centaurs?" and "Would you like to be a centaur?"

(At this point a freshman says "This is too weird for me!" and flees the library in terror.)

(GF) At WorldCon I picked up a book that is a collection of Terry Carr's fan writings. In an essay where he discusses jazzing up the Nebula Awards, he suggests that they include, at the opening of the ceremonies, an announcement of the terribly secret methods by which the votes are counted; the nominations are made by the members of SFWA, with careful consideration of who their friends are, and counted by a computer program written by members of the MITSFS.

(JME) Addendum to WorldCon Report: Jerry Pournelle, after Footfall lost the Hugo, went around all over the convention very drunk, muttering his line about how "bestsellers will get you through times of no Hugos better than Hugos will get you through times of no bestsellers" over and over again. Niven was there also but seemed in perfectly good spirits. Jerry Pournelle has the record for number of times nominated for Hugos without winning.

(SSDT) People's Albanian Embassy: from last week's Herald- a reporter who had relatives in Albania was actually allowed into the country and proceeded to report.

(CJH) Moocomm: Stand By Me is a very nice film. It's based on one of King's few totally non-horror stories and is supposed to be at least partly autobiographical.

(JME) Jourcomm sub 2: anyone who thinks they deserve a free copy of TZ should see me. Also, start thinking about writing for the NEXT TZ Real Soon Now. I'm going to keep a running list of books up for review up on the board; this is important because I got us on another review list while I was at WorldCon, BlueJay's.

(RJG) Fweekcomm: we ran the Hitchhiker's tapes during Rush week and we're going to run them again tomorrow. Fweek as a whole seems to be going pretty well.

\goto{Old Business}

(JME) Old MITSFSites met at WorldCon: Bruce Miller, who is "still skiing in Colorado," Russell Seitz, who's still a visiting scholar at Harvard dealing in nuclear weapons and things like that, Michael Tavis, who is apparently married, and Greg Ruffa, who still has our minutes and claims they're going to be hand-delivered in December. He bought two t-shirts.

(KM) Carl Hylin was supposedly at WorldCon but we didn't see him.

(SSDT) Addendum to a Minicult: the Congressional department that does Braille translations of 36 magazines wants to stop doing Playboy; they say it's because of budget cuts that just happen to be by the same amount that it costs them to do Playboy. They got hauled into court by the Civil Liberties Union, and Congress lost.

(JME) Followup on the Minicult about the man who lobbied to allow employees of the Texas lottery to play it and then became the only three-time winner: turns out that my source had been fooled. There is no Texas lottery.

(BPS) Also on a Minicult: the police got an anonymous tip on the location of the Picasso painting that was being held hostage in Australia.

OBA: um, us, uv, ur. "What about the usual debate?"

\goto{New Business}

(CJH) Minicult: Pontiac, MI- a woman caught some burglars in the process of robbing her house and gave them such a tongue-lashing that they stopped the theft, returned the stuff to her house, reinstalled her VCR, and waited meekly on the couch for the police to arrive.

(CJH) From the Glob- a piece of 20-foot-tall metal statuary that cost the city 8000 dollars disappeared one day, leading people to believe it had been stolen or lost in storage. Now everyone thinks it got mistaken for garbage and was thrown out.

(JME) Motion to pile debris around Transparent Horizons!

(Everyone in unison) Second!

Motion passes by acclaim.

(JME) Minicult: Henry Moore, sculptor of the Bronze Bunny, died.

(JME) Minicult: Harvard is having its 350th anniversary and Prince Chuck is in town for it.

(SSDT) Minicult: from a rather old Glob- up in New Hampshire, they're having the 5th annual Zucchini Festival, "Zucchinis Across America." Activities include a zucchini lookalike contest, as well as contests for the Most American, Nicest-Dressed, and Most Grotesque Zucchinis.

(JME) Minicult: the military is considering adopting the blimp as a surveillance vehicle because it flies low and slowly and is apparently invisible to radar.

(SSDT) Minicult: 29 years ago, a B-36 was flying over New Mexico and accidentally dropped a 10-megaton hydrogen bomb. It went "pop"- the trigger went off but not in the right way to trigger the bomb.

(RvdH) Move that the ugly sculpture near the pool that looks like a South African shanty have the word "Divest" spray-painted on it in banana-yellow in the hopes that the Institute will come and take it away.

(AA) Second.

Motion passes many, many-4+"No, no, never, unfair to African shanties!"-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1750 SST.

\vspace{18pt}

\centerline{Sincerely subdivided,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}