\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 24, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (1/17/86) read and corrected.

ATS: Move to approve the minutes as stunted. Passes go away anybody opposed-those people-3 +Spehn.

\goto{Committee Reports}

ATS: Pseudo-Jourcomm: One of the responses to TZ 36 said "Why am I getting Twilight Zine? Damifino." He thinks it started as a trade with something that doesn't exist much anymore.

SSDT: Catacomm: We won. Our life subscription to F&SF magazine is back.

ATS: I saw a late model Scirocco painted pink with lime green and turquoise polkadots.

DSK: Whooshcomm: Voyager's Uranus flyby (altitude 50,000 miles) was today. Ten new moons, one named Oberon. A man who predicted where the moons would be was right on six counts.

Various motions as to what to name the others, with no consensus.

BPS: Pseudo-Jourcomm: Janice probably wants me to remind people to write stuff.

ATS: Hitchhikercomm: the Hitchhiker's Marathon was, and we had a load of people and signed up 5 new members.

BPS: They got the disco music by taking Staying Alive, deleting every eighth note to make it 7/4 time, and playing it backwards.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

RvdH: You're supposed to bang the gavel at the end of Old Business! Clink, clink.

BPS: Minicult: Goodyear is claiming the blimp as its trademark, and is suing Fuji to stop them from using one for advertising purposes. Article attached.

Janice arrives and makes threats about there being no TZ if people don't write things, since so far there is only one submission and some cartoons.

BPS: There have been articles recently referring to Burma as Albania East, because of its very closed borders and because it stopped time in 1962 and hasn't restarted it yet.

JME: Minicult: Uncle Duke of Doonesbury appears to be dead. Also, the wife of President Marcos supported her claim that women don't belong in politics by describing her job as mayor of Manila as "just being a housekeeper."

BPS: Part of Marcos's image is that he was a great freedom fighter in WWII. Research in FBI records has revealed that he probably collaborated with the Japanese, and his freedom fighters did nothing except avoid fighting.

JME: Move to commend Barney Frank and Gerry Studds for publicly admitting that they are not going to the Super Bowl because they have no interest in football. Passes by acclaim.

CH: Coincidencecomm: the same week that Berke Breathed was finally getting around to the fate of Cutter John after the balloon crash, he wiped out in an ultralight. He has a compression fracture of the back, and we'll be reading reruns for a while.

CH: WWN Report: Communication with a ghost via home computer, article attached. Hooray for microchip links with the realm of the dead.

JME: Minicult/Randomcomm: Asimov's contains a story entitled Close Encounter With a Deity with the typo "Diety" in the title, although it's spelled correctly in all other places.

BPS: Minicult: A man who got very annoyed by TV evangelists programmed his home computer to dial Falwell's 800 number. It did this every 30 seconds for 9 months, costing Falwell 500,000 dollars. Article attached.

SSDT: Move to commend! Passes by acclaim.

Y: This weekend is the Creation Boston Science Fiction Media Convention.

RvdH: Nanocult: IAP lectures by the Nanotechnology Study Group.

SSDT: Don't waste your time. They're highly outlandish in what they say is real.

BPS: I'm sick and tired of hearing about the Super Bowl. Prediction: Bears, 57-0.

JME: Move to commend Cheers for explaining how a person in a nightgown looks like a banana. Passes, even though no one seems to know what she's talking about, everybody-2-some spastic chickens +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}