\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 12, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes half-read by pseudo-Onseck D. Scott Kitchen, completed by non-pseudo-Onseck.

(AA) Motion to approve the minutes as being read bisexually.

Motion passes Damn Near Everyone-2+"No, no, never"-2 +Spehn.

\goto{Committee Reports}

(SLP) LHE Report: not so good last month. Income- 354.76, Expenses- 2845.11, Loss- 2491.50, Equity: 1404.30.

(DSK) This is what I have to inherit?

(LAK) Pseudo-Analogcomm: Since Jack didn't show up for a month, I took all the cards and made up a schedule, intending to bring it in tomorrow morning. So of course, last night he came in to put up a schedule and wondered where the cards were.

(SSDT) Pianocomm: Val Stark is the new Boredcomm, and she has finally put our name in large letters on the board so that people don't think it belongs to Hillel anymore.

(JME) Jourcomm: TZ Real Soon Now! No, seriously, please review books.

(SSDT) Theftcomm: Our copy of Blood of Amber has walked off; if anyone took it home to review or hid it, please let us know.

(LAK) Moocomm: Back to the Future tonight.

(SSDT) Randomcomm: In the Sci-Tech section of the Glob this week there appeared two articles on the Chernobyl accident and they were so full of errors on the subject of nuclear physics that they qualified as science fiction.

(JME) Randomcomm sub 2: There was a photo in the Glob this week of a bunch of old Star Trek castmembers at their 20th reunion. The caption said something like "Isn't space travel supposed to keep you young?"

(DSK) Kingcomm: IT is number one on the New York Times bestseller list one week after release.

(SSDT) Kingcomm sub 2: In a recent TV Guide, various writers came up with their ideas concerning the mystery of Bobby Ewing's return on Dallas, including King, whose answer is that Bobby is still dead and has been reanimated as a zombie by JR's enemies.

(JME) Motion to change the name of Kingcomm to Kongcomm because Kingcomm is just too straightforward.

Several seconds, and SSDT passes it.

(Malcolm) TVGuidecomm sub 2: in the Fall Preview issue of TV Guide there is a preview of a show called Alf; it's apparently about a suburban family that adopts a cute, cuddly alien with a taste for housecats.

(JME) "Alf" stands for "Alien Life Force." (Why not "form?" I don't know.) I heard the alien is supposed to be somewhat obnoxious and not all that cute.

(Malcolm) Especially if you're a cat.

(AA) Sitcomm: another upcoming SF series is Starman, which is going to be a sequel from the movie, apparently; he comes back to Earth 14 years later and finds his teenage son. He comes back with a new identity too, which may explain why it's Robert Hayes (of Airplane), not Jeff Bridges, playing the part.

(LAK) Moocomm: some of us went to see The Fly last weekend. It's gross.

(SSDT) Pseudo-Coofcomm: James Lavalia of Salem State College is starting a science fiction society up there and is coming back here later to ask for advice.

(DSK) Concomm: some guys out at WPI are getting ready to hold their own con.

(SLP) Pathetic-Membercomm: I was sitting in here doing the books last week with the lights on and the door closed. Most members will knock on the door to find out if the Library's open, but one member came by and started scratching at it. I almost let him in...

(There is a whole bunch of noise and something about a backward pass being a sap which gets RJG Albanianed.)

(JME) Pathetic-Keyholdercomm: Rob is crying and whimpering in Albanian.

(JME) Pseudo-Analogcomm: the map of the MITSFS is incorrect; the spiral staircase leading to the MITSFS Mistress is supposed to be in Damnation Alley.

(LAK) Vicecomm: tough shit. It's been moved!

\goto{Old Business}

No old business.

OBA: um, us, uv, ur, "but what about the usual debate?"

\goto{New Business}

(JME) Minicult: the school board in Bay Reef, New Jersey has been investigating complaints that students have been leaving in the middle of class to answer telephone beepers, often to make drug deals. And on a related note, the House just passed an incredibly fascist drug bill that is likely to pass in the Senate too because it's an election year. Among other things, it gives the death penalty for drug dealers who are convicted of causing someone's death with their drugs and allows police to use illegally seized evidence in court if they weren't aware that they were doing something illegal when they seized it.

(SSDT) Minicult: Chicago- a disgruntled employee tried to sabotage the Encyclopedia Brittanica by rewriting history, substituting Allah for Jesus among other things. They caught him pretty quick because the changes are all tracked by computer.

(CH) Weekly World News Report: in England, an office worker accidentally swallowed her watch. X-rays showed the watch making its way through her innards, and doctors sent her home to await "the passing of time." (It's not my fault, I don't make 'em up, I just write 'em down... -JAH, Onseck)

(SSDT) Motion to Albanian the Weekly World News!

Passes by acclaim.

(DSK) Takes a licking and keeps on ticking!

(JAH) Albanian motion!

(JME) Minicult, urban myth department: the newest one spreading around concerns a woman who sees a celebrity in an ice cream shop and gets so flustered she puts her cone in her purse.

(Malcolm) Minicult: during WWII, the British Camouflage Division hired a magician, Jasper Maskelyne, and asked him to make the Suez Canal disappear. At another point, they asked him to make 10,000 gallons of camouflage paint from materials in a dump of cargo from torpedoed ships. The product he eventually produced was made of Worcestershire sauce and camel manure.

(JME) Minicult: for several newscasts Dan Rather signed off the CBS Evening News by saying "Courage." He got laughed at and eventually stopped saying it, but it became a joke on Today when Bryant Gumbel, at the end of a newscast, asked, "What, no sign-off word?"

Newsman John Palmer: "What's that?"

Gumbel: "No sign-off word?"

Palmer: "No courage."

Gumbel: "Oh, come on, we've got to have a word for you- maybe 'hot dogs' or something like that."

At the end of the next newsbreak:

Gumbel: "Hey, John, suggestions are pouring in for your sign-off word. How about 'valor'?"

Palmer: "'Valor'- not bad, not bad."

Gumbel: "We'll keep 'em coming."

At 8 AM:

Gumbel: "How do you feel about 'fortitude'? 'John Palmer, NBC News. Fortitude.'"

Palmer: "I'll think about that. Let you know in 30 minutes."

At 8:30 AM:

Palmer: "And so, Bryant, we leave you this morning with the word: 'Mazeltov.'"

(JME) Motion to define the banana-yellow shirt on the Albanian over there as being Albanian.

(AA) Move to award Jerry Pournelle a banana-colored Hugo.

(DSK) Miller motion!

(SSDT) Second!

Fails.

(People start chanting "Rabbits have no tails at all" but are cut off by:)

(SSDT) Miller motion!

(DSK) Second!

Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely subjective,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}