\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 11, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected by pseudo-Onseck Ken Meltsner.

(RvdH) Move to approve the minutes as wet.

(BPS) Move to approve the minutes as ALL wet.

(BPS) Move to change the minutes' diaper.

(KM) Second.

Motion passes about 12-1 and 2 halves-2 +Spehn.

\goto{Committee Reports}

(KM) Pseudo-Jourcomm: Submission deadline has passed, and we have a fair amount of material, but we need book reviews and artwork.

(SSDT) Pianocomm: HAM was here for the 4th, left his key. Andy Su also left his key recently.

(LAK) Moocomm: LSC is giving out free passes to a screening of Aliens for Friday night.

(BPS) Moocomm: Big Trouble in Little China is a good three dollar movie, not so good as a five dollar movie.

(SSDT) Farewellcomm: Andy left a nice goodbye note on the board with a Miller motion. It fails.

\goto{Old Business}

(BPS) Monday the 7th was Robert Heinlein's 79th birthday.

(LAK) The people who turned the Green Building into the Statue of Liberty were caught by a CP while tearing down the hack; the CP grumbled at them for a while, then commented, "The lady looked mighty nice; get your stuff and get out of here."

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) There's a pair of pink panties on the bulletin board.

(SSDT) The shelves came in; construction at 10 AM tomorrow.

(BPS) A Cuban refugee on the Staten Island ferry went berserk and started stabbing people- with a sword. It was the first sword attack recorded in America since the days of the saber charge.

(BPS) The Meese porn committee was not allowed to release their list of known distributors, but CBS is dropping its line of adult magazines anyway.

(KM) Miller motion.

Motion either fails or chickens 3-6-5 +Spehn.

( ) Minicult: new ugly art in lobby 7.

(KJ) Miller motion.

(SSDT) Second.

Motion passes, just barely, 7-3-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Sincerely substantial,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}