\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 21, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (2/14/86) impossible for anyone but the absent Onseck to decipher.

JAH: Move to approve the minutes as invisible. Passes pi-e-sqrt(2) +Spehn, and finger motions start flying for no apparent reason.

JME: Motion to commend whoever put the Jabba the Hutt on the model of the Enterprise. Passes by acclaim.

\goto{Committee Reports}

JME: Gavelcomm: a Labrador retriever is recovering after having a 10" wrench in its stomach for a month. Article attached. Also, Andy Porter showed up late at the MITSFS party and said George Scithers was fired from Amazing. He used to edit Asimov's.

JME: Whooshcomm: the Russians put up a fairly permanent space station, with private cabins and 6 docking ports, but haven't manned it yet. Article attached.

Someone's motion to commend the Russians for helping us keep on schedule passes lots-1 nyet-a few +Spehn.

BPS: Mobcomm: I filled in a few tiny gaps at Boskone, most notably the Dune Encyclopedia.

RvdH: We both got Heroes in Hell for MITSFS, free.

JME: Huntcomm: The Lunarians won. The most creative entry was from an individual. We asked for a monolith, and she brought a case of vaguely correct proportions. Then she opened it, and out fell all these stick-on stars.

CH: Moocomm: Monty Python's Holy Grail tonight at LSC.

ATS: Skinner Report: I was attacked by a Scientologist. Ad attached.

CH: Sitcomm: Monkees marathon coming, about 22 hours worth. Attached.

\goto{Old Business}

JME: Move to commend L. Ron Hubbard for still being dead. No vote.

JME: Write for TZ! Also, Infocom has been bought out by Activision. They should never have tried to go into business software.

OBA: um, us, uv, ur.

\goto{New Business}

JME: Minicult: The Missouri senate had to overturn a committee action which was going to renumber Bill 666 due to religious complaints. The difficulty was considered comparable to last year's flap over a proposed bill to regulate public nose-blowing. Article attached.

KM: Pepsi owns 7Up, and Coke bought Dr. Pepper. RC is looking for a deal with Coke too.

CH: WWN Report: A British Navy parrot was court-martialed for attacking Scottish people, and smokers are highway hazards. Articles attached.

Paul Dworkin: Gary Larson's lecture sold out Kresge. He showed slides of some Far Side cartoons that the papers wouldn't publish.

Phonecomm: No, Lisa Nanney isn't here.

Against a background of Rabbits comes a motion to send the British Royal Navy a dead parrot stuffed with bananas. Passes everybody-the parrot-the parrot's cousins +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}