\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 18, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (4/11/86) read and corrected.

After lots of motions that don't get seconded, BPS moves to approve the minutes as any of those. That gets all the seconding that wasn't used before, and passes general approval-3-several +Spehn.

\goto{Committee Reports}

TMc: Moocomm: Real Genius this Saturday. It's about a keyholder, um, I mean, character at Cal Tech during spring term who has a 15-year-old roommate, lives in a room with a large photomural of Saturn on his wall, and works on military applications of high-powered lasers. Any resemblance to myself is strictly coincidental.

DSK: Moocomm: Excalibur tonight.

CH: Moocomm: Also tonight, the Star Wars inspiration from Akira Kurosawa, The Hidden Fortress. It's got a pair of farmers who keep running away from one battle right into the next, but neither of them beeps much.

LAK: Lecturecomm: Professor Dyson, as in "sphere," gave two talks this week. In the one I saw, he envisioned the next Uranus probe as a genetically engineered creature weighing about 1 kg (when hungry). It would get there in 6 months using a propulsion method which would give it 2 months of constant acceleration by farting.

ATS: Moocomm: The TBA movies are About Last Night (formerly titled Sexual Perversity in Chicago), Commando, and After Hours.

DSK: Sitcomm: Twilight Zone is going off the air temporarily at the end of this season.

CH: Bananacomm: Right after our raid on Libya, an interviewer asked a Pentagon spokesman if Libyan anti-aircraft missiles had come anywhere near our jets (this was before we discovered one was missing), and the general said "Those Libyans couldn't hit a flying banana."

BPS: The next night, the Libyans suddenly started firing rifles, pistols, and more missiles into the air. They claimed they were shooting at an American reconnaissance plane, which made sense until they said it was an SR-71. If anyone hits one of those with a rifle, we ought to recruit him, his rifle, and the updraft that helped.

\goto{Old Business}

ATS: When a Russian helicopter returned the man who walked across the Bering Strait and the Eskimos said welcome back, he said he didn't want to come back. The CIA is debriefing him.

GF: The person doing the Noreascon 3 fanzine last edited a fanzine in 1967. It was TZ 22.

ATS: Judy Passman dropped in a little while ago. (People check under tables and chairs in case she's still here.)

HAM: What about the ravs? (Much discussion not suitable for reprint.)

OBA: um, us, uv, ur.

\goto{New Business}

SSDT: Minicult: Here are two pages (attached) from a really bad magazine describing some of the year's more interesting freak accidents. The best ones are the man who was driving down I-85 when he got hit by a motorboat, a woman who had no luck with one can of bug fogger so she tried 15 and blew the roof off her house, and a woman who needed 20 minutes of assistance from the fire department when she got trapped in a pair of designer jeans.

GF: Great Glob headline- Invasion by Planet Photon is Fought Off in Braintree. The town selectmen refused to license the game on the grounds that it's too much fun. Article attached. Cartoon show RSN.

ATS: Picture attached of giant sneakers walking up the side of the Westin.

TMc: Before the US bombed Libya, we asked our allies for support. The French refused to let us fly over their airspace, which made the mission at least twice as difficult. During the attack, we somehow managed to accidentally hit the French embassy in Tripoli.

BPS: An alleged piece of artwork will go up in the shuttle. The alleged artist talks like Kurt Vonnegut on drugs. Article attached. Also, the Times of London reported a man crashed his car into a bridge at 70 mph, got out and climbed a 132,000 volt power pole, caught fire, and fell to the ground. After the flames subsided, someone asked him what he was doing, and he said he had been trying to kill himself but was giving up. Article attached.

KM: Janice is going to be a gamester for Infocom, as soon as they send a game to test her.

CH: WWN Report: A gardener fried himself while using an electric pitchfork to catch worms, and Burma has outlawed rock music and breakdancing. Articles attached; retaliation followed.

CH: Minicult: A student's MCI code number was stolen and he got billed for 5000 dollars. He got that straightened out, but when the next month's bill was 15,000 dollars, he got fed up and canceled his service. Attached.

JME: Minicult: The actor who plays Lt. Castillo stopped a mugging by hollering "Miami Vice! Freeze!"

TMc: I got randomly interviewed by a man from Newsweek on Campus. They're doing a profile on MIT, so naturally I showed him MITSFS.

BPS: Believe it or not, Jimmy Breslen of the Daily News just won a Pulitzer for commentary. He writes like Mike Barnacle if Barnacle got hit on the head with a shovel more often.

CH: Motion to send flying bananas to the French embassy in Libya. Passes lots-some confused people squawking-less confused squawks +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1741 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}