\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 11, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (4/4/86) read and corrected.

JME: Move to approve the minutes as not looking like Peking ravs at all. Passes lots-few-slightly less than lots +Spehn.

\goto{Committee Reports}

JME: Jourcomm: I've been convinced to postpone my ultimatum until July 1.

BPS: Infocomm: Some people bring the boss home for dinner; my roommate brought him, namely Steve Meretsky, home to watch baseball. The Tech actually received phone calls due to their phone number being worked into his game Planetfall. He says he's now working on a game called Leather Goddesses of Phobos.

Chip: Pseudo-Moocomm: The Flying Karamazov Brothers are in New York for 2 1/2 weeks.

ATS: Moocomm: Black Cauldron tomorrow.

BPS: Anniversarycomm: The first space shuttle launch was 5 years ago tomorrow. Also, it's approximately the 25th anniversary of man in space.

ATS: Pseudo-Picniccomm: Harry Stubbs says May 4, 1986 is a good day for a picnic. Val Stark is appointed Picniccomm. Elections will be May 2. Civ.E. may give some trouble about the Spofford Room.

SSDT: Bananacomm: I saw a car window sign similar to the banana colored ones that say Baby on Board. It said Alien on Board.

BPS: Cornelia Otis: The only person in the NH Democratic primary for senator is a LaRouchite. No one else is willing to get trounced by Warren Rudman.

JME: Cornelia Otis: LaRouche stated that there's a worldwide conspiracy to kill him. So I don't know why he's bothering to give more people the idea.

\goto{Old Business}

Discussion of nonappearance of ravs, and stunning reappearance of the receipt for them.

BPS: 12 years ago was my first moving violation. I ran a stop sign which I didn't notice because I was too busy looking at some weird lights in the sky. Never did figure out what they were. The friend who saw them with me called me today for the first time in a year and a half, by coincidence.

OBA: um, uravs, us, uv, ur.

\goto{New Business}

JME: Minicult: Dallas cops have a new partner who is a robot. It's a battery operated machine with treads, a shotgun, a video camera, a speaker, and a water cannon. Attached.

ATS: A man walked from the US to Russia across the frozen Bering Strait. He was promptly arrested by Russian police.

JME: Minicult: College students, I believe at the U of Rochester, have taken to using the words "frood" and "froody" to mean cool, as per Hitchhiker's Guide, according to WWN.

Chip: Minicult: Smithsonian reports that in 1960, Dutch Boy Scouts retrieved the tail turret machine gun and its ammo from a WWII British bomber that had crashed in Dutch waters and restored them to working condition.

Y: In London during the blitz, a bomb seemed to have gotten under a building without making a hole on the way there. It turned out to be a zeppelin bomb predating the building.

BPS: The man who had his computer dialing Falwell's 800 number gave so many other people the idea that Falwell has been forced to get a toll number. Article attached.

BPS: Other pseudo-Baby on Board signs include Baby Driving, Nobody on Board, and Baby on Board Carries No Cash.

CH: WWN Report: Drivers with colds are more dangerous than drunks, a farmer got his last wish by having the hearse take him to his funeral at 70 mph, and this week's runaway car circling in reverse got put out of commission by a shotgun. Articles attached.

SSDT reads retaliatory Phoenix ads.

BPS: Minicult: British animal lovers have gotten a law passed prohibiting people from harming or even touching a bat. Also, they're blocking off roads for toad migrations. Article attached.

SSDT: Jane Wyatt will play Amanda in ST IV. Confusion of the names Wyatt and Wyman results in speculation on Ronald Reagan as Spock's father.

BPS: Minicult: When Reagan visits his ranch in California, a nearby airborne command 747 is cranked up, causing garage door openers to fail for miles around. Article attached.

\vspace{12pt}

\noindent
Five rounds of rabbits causes the meeting to adjourn at 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}