\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 16, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of previous meeting read and corrected.

AA: "Move to approve the minutes as two light-days out from Earth." Passes, lots and lots to "Never, never, no no!" (from the Loyal Opposition) to one lonely squawk plus Spehn.

SSDT: "No meeting next week; I'm being forced to work swing shift- all of it." Everyone else: "Awww!"

LAK points out that next week a lot of the regulars will be at Disclave. Brief discussion of whether to have a meeting at Disclave; final decision is "no," mainly because no one wants to haul the gavel block all the way to Maryland.

\goto{Committee Reports}

JME, Jourcomm: "Write for Twilight Zine- deadline July 1st, people!" Some discussion as to whether that should be in Old Business.

BPS, Cornelia Otis Skinner Report: It's official- former Massachusetts governor Endicott Peabody is running for the Democratic nomination for senator in New Hampshire because the only other declared candidate is a La Rouchite. For reasons no one can understand, Peabody's talking as if he thinks he has a chance of defeating the Republican incumbent.

BPS, C.O.S. Report-sub-2: An Illinois judge ruled that Adlai Stevenson the nth can abandon the Democratic nomination for Guv, but because he missed the filing deadline, he can't run as an independent. The La Rouchian Lt. Guv nominee tried to claim that with Stevenson fleeing in terror, he (the La Rouchatic) should automatically get the number-one slot on the ticket. He was bounced.

Connie tries to give a Cornelia Otis Skinner Report and JME tells her that it's just plain Cornelia Otis for Pete's sake. She then tries to give an Otiscomm report and is told, no, just "Cornelia Otis." BPS points out that Otiscomm deals with reports on elevators and narrowly avoids an Albanian Motion. Poor Connie finally gets to give her Cornelia Otis report, which is that the Nebraska gubernatorial race is between two women, the first time in US history that that's happened. Whichever of them wins will be Nebraska's first FemGuv, and if it's the Democrat, she'll also be the state's oldest elected Guv ever.

SSDT reports "Shelfcomm: I've ordered us some shelves; delivery in eight or nine weeks," and there is much rejoicing. There is considerably less rejoicing when someone asks how much this is going to cost us and is told "1422.15, plus about 100 in shipping charges." There follows flaming about the comparative wonderfulness of various flavors of bookcases in the library, and there is much boredom.

BPS, Sitcomm-sub-1: I saw the Entertainment Tonight report on Star Trek IV; it mostly dealt with wet actors in a big water tank in a Paramount parking lot pretending that they were on a splash-crashed Klingon ship in the middle of San Francisco Bay in the middle of a storm. The bad news is that it looks as though they're also supposed to be in the middle of 1986. A massive "Oh, no!" is heard from just about everyone present. There is some discussion of how nice it would be if their pet Klingon ship just happened to land in 1986 on top of Gene Roddenberry's yacht, and some more discussion of whether Kirk and Co. will go see Star Trek IV. By the way, the subtitle seems to be either "The Voyage Home" or "The Journey Home."

BPS, Sitcomm-sub-2: NBC's new fall schedule includes "Alf," which stands for "Alien Life Force," who's a cantankerous ET ripoff who moves in with an American family. Groans are heard. Also, Wilford Brimley, who played the grandfather in "Cocoon," will have a non-sf series. "Highway to Heaven" was renewed. Among the cancellations are "Knight Rider," "Misfits of Science" (much cheering), "Remington Steele" (much groaning), and the JME-recommended "All Is Forgiven."

SSDT, Panthercomm: The new Pinkdex is perforated; it has lots and lots of gaping holes in it, beginning in the middle of the V's and getting worse the deeper you go into the alphabet. The previous Pinkdex has been recalled to duty as a backup. Spencer believes he's fixed the problem with the reporting program and we should have a new Pinkdex by the middle of next week.

George Flynn, Cornelia Otis: the Guv of Louisiana's been acquitted. He was charged with fraud or racketeering or being a Democrat or something like that.

Connie, Sitcomm-sub-3: "Spencer For Hire" has been renewed. Some cheers are heard. BPS reports that it's been moved to Saturdays at 10 PM, which he thinks is the same time as CBS is showing "Twilight Zone."

\goto{Old Business}

JME: "Write for Twilight Zine."

BPS: From last Wednesday's USA Today sport section, "The Slugs Have It." The administration at U of California at Santa Cruz gave in to overwhelming student opinion and agreed to change the name of the school mascot from the Sea Lions to the Banana Slugs.

More stuff about the infamous Ravs, including threats to Andy that we'd write to the medical schools he's applied to and tell them that he welshes on his debts and they shouldn't loan him any money.

??? (Jenny?): The Newsweek photographer came back and took more pictures because his editor didn't like the posed shot he took earlier. The new pictures feature a completely fraudulent female to male ratio and are also pretty boring. ATS: "Those pictures that he took, they suck. To put it mildly."

BPS: J. Allen Hyneck, the UFOlogist who had a cameo appearance in "Close Encounters of the Third Kind," died April 27th.

JME: "Short Circuit" is getting pretty unanimously bad reviews; the best thing anyone's saying about it is "harmless." Gene and Roger said the robot was the only creative thing about the movie, and Gene didn't even like Ally Sheedy in it.

SSDT: Old biz regarding our attack on Libya- a Phoenix columnist asks readers the hypothetical question "If the IRA, a certified terrorist-Marxist organization with ties to Libya, did some really nasty stuff against Britain and the British decided to respond with punitive air strikes against known IRA sanctuaries outside Great Britain, hideouts where the terrorists receive arms, money, and training, would you as an American support such an action? If yes, you've just called for British planes to take off from Otis Air Force Base to bomb Charlestown." Charlestown resident RvdH admits that that makes him nervous.

Old Business Algol, The Usual, The Usual Ravs, The Usual Silver, Ravs! Ravs! The Usual Silver Ravs, The Usual Second, Second! Second! The Usual Vote, and The Usual Result.

\goto{New Business}

Minicult (JME): There is a Fundamentalist Christian interactive software game. It's called "Real Life- The Greatest Adventure of All," and it includes a United Protestant church run by (boo! hiss!) "Reverend Bruce, a practicing homosexual with a lisp who preaches about the virtues of communism and humanism and all those things." You also lose points for having casual sex with strangers and doing other fun stuff. You can't even amuse yourself by trying to lose as many points as possible because whenever you "sin," the game throws screens full of Scripture at you. JME assures us that no, this is not a slightly dis-temporized April Fools' Day hack.

Phonecomm: "RING!" SSDT: "Galactic Control Room. Hi, Larry." Everyone else: "HI, LARRY!"

Larry Robbins announces a party at his and Larry Lennhoff's and two other guys' house next Friday, which unfortunately coincides with Disclave.

JME: "Connie's wearing a really disgusting color combination." Larry Robbins: "What's wrong with pink and purple?" JME: "It doesn't go with your t-shirt, Connie." Connie: "Well, I'll kill myself, Janice." JME: "Good, good, yes, go ahead!" AA: "If you do it, make sure you do it in her living room." KRJ: "Do your shelves first." BPS: "If you're going to do it in their living room, at least wait until they get the camera attachment for their VCR."

Minicult (BPS): ABC and NBC both showed a videotape supposedly smuggled out of Russia by a Yugoslav tourist. It allegedly showed a Kiev hospital and the fire at the Chernobyl nuke reactor. A lot of people in Italy recognized the film as being from a recent fire at a cement factory in Trieste, and the hospital was architecturally identical to one in Rome. CBS didn't show the tape, and boy did Dan Rather look smug when he reported on the hoax.

Minicult (???): A British magazine reports that male (that's M-A-L-E, not M-A-I-L) childbirth is now theoretically possible. The details are too icky for words. Larry Robbins volunteers a certain senator from North Carolina to be the first one to try it. JME motions to impregnate Jesse Helms with a banana. Someone (BPS?) makes friendly amendment to make Jerry Falwell the mother. Amendment accepted, motion seconded, passes 3/4 of everyone to three plus "No, no, it's unfair to bananas!" to a few normal chickens plus one very confused chicken plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Minutes submitted with the utmost sincerity,}
\centerline{Bill P. Starr, Emergency Pseudo-Onseck}

\end{document}