\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 14, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (3/7/86) read and corrected.

DSK: Move to approve the minutes to be used to pave the road to the cemetery in space. Passes "everybody likes cemeteries"-"you're no fun anymore"-several +Spehn.

\goto{Committee Reports}

DSK: Boredcomm: Yawn. I'll do something about it tomorrow, suggestions welcome.

AA: Moocomm: Connie and I saw Highlander. It's lots of fun, with lots of violence and a 4000 year old punk.

BPS: Pseudo-Moocomm: I saw a slide preview of that and also one of Aliens at Lunacon. Aliens is the sequel to Alien and looks okay.

CH: Moocomm: It has been confirmed that House is not the horror version of Tracy Kidder's nonfiction book about building a house.

\goto{Old Business}

SSDT: Susan Pitts bought the cactus.

SLP: Here's an ad from the Scientologists offering a 75,000-dollar reward for help with a case against people they accuse of forging a 2-million-dollar check from L. Ron Hubbard's account in 1982. It goes on to complain that the government is helping cover up the alleged crime. Attached.

OBA: um, us, uv, ur.

\goto{New Business}

BPS: Minicult: a new study showed the most likely time to have a stroke is 8-9 AM, as was already known true for heart attacks. This is thought to be caused by the stress of getting up in the morning. Article attached.

CH: WWN Report: a weightlifter was terrorized and held prisoner for 3 days by his girlfriend's Boston terrier, a man got his money back from a pet store that sold him a defective parrot (it dropped dead), and the cat burglar raiding clotheslines in Nashville is a real cat. Articles attached. Also attached is a Herald article that belongs in the WWN about Imelda Marcos and her 2200 pairs of shoes.

BPS: Minicult: the president of the U of Colorado went into a Burger King and was mobbed by people who mistook him for "Herb." Article attached.

\vspace{12pt}

\noindent
The second of two Miller motions is forced through to adjourn the meeting at 1715 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}