\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 22, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected by pseudo-Onseck Bill Starr.

(SSDT) No meeting next week. (8/29/86)

(RJG) Sign up for minutes for Rush Week in spite of that.

(SSDT) Fill up the huge hole in the middle of the schedule!

(HAM) How about we fill the hole with the minutes?

(KM) Move to approve the hole as having been filled by the minutes.

(BPS) Second.

Motion passes about half-a-dozen and two very confused votes-"Yes, yes!" and four more people in favor-2 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: TZ RSN for real this time! The first 50 are here; the next 150 will be ready this weekend.

(BPS) Mobcomm: Mobcomm sub 2 run was made last Saturday. About 260 dollars spent on Saturday, total for two days 430 dollars. Lots of new books.

(SSDT) Pseudo-Panthercomm: the Pinkdex database has been updated to yesterday. The database is in the Panthercomm drawer and anyone processing books should use that. It has 13,457 entries at the moment.

(JME) Famecomm: I'm still going to be on a panel about SF libraries at WorldCon. Please come and heckle.

(JME) Pseudo-Libcomm: there's a new professional SF magazine called Aboriginal SF being published in Woburn. The cover is attributed to Courtney Skinner, who may or may not be our Skinner.

(KM) ROSFAP: an old issue of SFC has been recalled by the publisher for being miscollated. They sent us a free replacement copy.

(JME) Whooshcomm: NASA has announced that it can get the money to replace Challenger by scrapping all of its commercial ventures and doing only government and defense contracts. It was originally intended that the shuttle would pay for itself with the income from these commercial missions. The White House has stated that it expects commercial operations to set up their own space programs to do these missions.

\goto{Old Business}

(SSDT) I have a letter from Thom McKendree.

(She reads it.)

(SSDT) TZ RSN!

(JME) Start thinking about writing for the next TZ! Deadline late December/early January so we can have a collating party during IAP.

(KM) Herb Miller is here.

OBA: usual confusion, um, us, uv, ur.

\goto{New Business}

(BPS) Minicultses (sic): 1) from last Friday's Glob- a four-foot pine snake swallowed two lightbulbs, and I have a picture of the X-ray taken by the vet. 2) From last Friday's Herald- while digging a trench for new wiring on the U of RI's Mead Field, the electric company workers discovered that the field had been constructed on top of an old family graveyard. The workers discovered three grave sites between the 30 yard line and the concession stand. 3) The U of Minnesota Art Museum has had a painting called "Oriental Poppies," by American artist Georgia O'Keefe, hanging on their wall for about 30 years and they've finally rotated it 90 degrees so that it's hanging right side up. Somebody uncovered an old photo of it showing it in its proper orientation.

(KM) Steven King, fighting against the Maine censorship ballot resolution, made a commercial starting off with "Want to hear something REALLY scary?"

(BPS) Oct 7-19 at the Colonial Theater in Boston, there is going to be a stage play of Lord of the Rings. It is 140 minutes long and has about 60 characters, but most of them are puppets. Only four of the characters are played by actors in costume. No one speaks; the story is told by taped soundtrack.

(AA) Minicult: some postal workers saw that a package was leaking and opened it to discover five human heads. The FBI is looking into it.

(CH) Weekly World News Report: Russian scientists are teaching fish to come to a certain noise so that they can be caught more easily. They believe this learned trait will be passed down to the fishes' offspring.

(BPS) What do you guys want to do for dinner?

(SSDT) Banana Flat Dogs!

(BPS) Second!

Passes by Skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely subterranean,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}