\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 15, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(Malcolm) Move to approve the minutes as incorrect.

(JAH) Fails!

(SSDT) Dies for lack of a second.

(BPS) Motion to approve the minutes as obstinate.

Motion passes 6-2-3 +Spehn.

\goto{Committee Reports}

(BPS) Mobcomm: 174.89. That's a PARTIAL run. Sue and I are going back tomorrow for hardbacks.

(JAH) Pseudo-Jourcomm: I suppose Jourcomm still needs art for TZ.

(Malcolm) Move to insert "Art needed for TZ" into the OBA.

Fails by "No."

(SSDT) Porncomm: Mr. Fusion has been fixed but is now so low on paper that it prints out something like "Get more paper, you fool" every time you make a copy.

(SLP) Miller motion.

(SSDT) Fails.

\goto{Old Business}

(BPS) In reference to the woman who was awarded nearly a million dollars by a jury in Philadelphia for the loss of her psychic powers after having a CAT scan done: the judge of the case says the jury ignored his instructions concerning her award and calls it "so grossly excessive as to shock the court's sense of justice."

(SSDT) More hack "baby on board" signs: God on Board.

(JAH) I saw one that said Future Millionaire on Board.

(BPS) I saw one that said Stud on Board.

OBA: TZRSN, um, us, uv, ur.

\goto{New Business}

(SSDT) There is a new R/O schedule on the board. Sign up for lots of hours. There will be no meeting the week of the freshman picnic.

(Malcolm) A bid was placed at a tax lien sale for 1/64th of a googol. In a tax lien auction, the award goes to the lowest bidder. Apparently it was thought that a googol was one OVER a one followed by 100 zeroes.

(Laurie) The Boston Gay Chorus is looking for singing and non-singing members. I wonder what the non-singing members do?

(BPS) There's a video game called "Road Runner" up at 1001 Plays, based on the cartoon of the same name. It's unfair to give you an opponent (namely Wile E. Coyote) that you can't take seriously.

(BPS) Meanwhile, the Transformers movie is out there, utilizing, among others, the voices of Orson Welles and Leonard Nimoy.

(SSDT) A moment of mourning, please? That's enough.

(CH) Weekly World News Report: Some of the predictions for 1996: Brook Shields and Woody Allen get a divorce after a four-year marriage, teens pick up a new fad of acting like simpletons with some of them even getting lobotomies, and desert-based Saudi Arabia and heavily-forested Cambodia making a billion-dollar pact to produce sandpaper.

(CH) The Herald thought The Fly was gross but not too bad.

(BPS) Minicult: a thirteen-year-old in California turned in her parents for drug dealing.

(CH) A man in California was nearly crushed to death by falling books in a small earthquake.

(JAH) Banana slug.

Motion chickens 4.4-1-twice as many as voted for +Spehn.

( ) Miller motion.

Motion passes many-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely subcontracted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}