\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 3, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

There is a Phonecomm during the reading of the minutes; it is Thom McKendree with a Minicult. It is forward time-warped to New Business.

(BPS) Move to approve the minutes as determined.

(JME) Second.

Motion chickens 5+"Yay!"-12-13 +Spehn.

(Jim Rauen) Motion to not allow the Boston Globe to approve the minutes.

Motion dies for lack of comprehension.

(JME) Motion to approve the minutes as having been all a dream.

(Many people) Second!

Motion passes everyone-2+"No, no, never"-4+Mark Harris +Spehn.

There is a Phonecomm sub 2; it is former Skinner in exile Andy Su with a Miller Motion. He is greeted with a tremendous cry of "RAVS!!!!!" and responds, "Just like old times- Free Silver, Free Silver." When the Phonecomm runs on beyond reasonable length, the Onseck, faced with the prospect of listening to long minutes of silence on the tape, begins to chant "Rabbits have no tails at all" and others pick it up, which brings the Phonecomm to an end.

\goto{Committee Reports}

(SSDT) Real Business meeting after this one.

(DSK) LHE Report, wow!: Assets- 104.63, Income- 825.86, Expenses- 251.86, Equity- 1978.63, Profit- 574.00. WE MADE MONEY!!!

(JME) Jourcomm: write for TZ!!! I want to put out a January issue and I'm giving you people lots of warning this time, so write! Review books, too.

(SSDT) Pseudo-Jourcomm: I think we've been punted from Del Rey's review list.

(BPS) Whooshcomm: NASA has tentatively scheduled a shuttle flight for February 19, 1988.

(JME) Sitcomm sub 1: if you're tired of M*A*S*H, Get Smart! is being shown opposite it on weeknights on Channel 25.

(BPS) IDunnoWhatcomm: yesterday, the Senate overrode the President's South African sanctions. WBZ-TV sent someone over to MIT to talk to someone in the PoliSci department and they found Prof. Willard Johnson, the one who caused the trouble with Harvey/Grogo last year.

(JAH) Moocomm: The Boy Who Could Fly apparently isn't fantasy except at the very end.

(SSDT) Stonecomm: the magazines we're sending to Stoneybrook (the SF library who lost most of their collection to a fire) have been pulled from the shelves. I'd like some people to come by at around 4:00 tomorrow to pull some stuff off the For Sale shelf and unstamp and package them.

(CH) Sitcomm sub 2: One of the questions on Jeopardy! this week concerned "Frank Miller's Dark Knight."

(JME) Sitcomm sub 3: on Dallas, the cliffhanger was resolved by declaring the entire past season of Dallas and two episodes of Knot's Landing a dream.

(JME) Sitcomm sub 4: Alf, the alien from the TV show of the same name, is cohosting Friday Night Videos this week with Richard Mall from Night Court.

(SSDT) Infocomm: we got our poster from Leather Goddesses of Phobos. (Many oohs and aahs and "Don't those things hurt?")

(Jim R.) Nestlecomm: I'm baking between 3 and 4 batches of Nestle's Toll-House cookies tonight starting at 7:00 and everyone is welcome to come to 509 Bemis and help me eat them.

(JME) STrekcomm: Word on the new STrek film is that it has something to do with whales.

(JAH) Rumors on SFLovers have said that the plot involves some very powerful entity arriving in Federation Space and demanding to speak with a "Guardian." When no one can figure out what this is, the entity plays a recording that is identified as whale songs. Problem: all the whales were killed a couple of centuries ago. So the Enterprise crew get to go back in time and fetch a whale.

There is yet another Phonecomm, which is answered by Sue Tucker with "Albanian Motion!", no doubt startling Ken Johnson on the other end of the line. Ken wants to talk to Bill Starr.

(JME) There's a rumor going around that William Shatner was threatened with Harlan Ellison to get Shatner to bring his salary demands down to a reasonable level. Apparently, while they were haggling over salary, someone mentioned that they were trying to get Harlan Ellison to do the screenplay, and Ellison has stated many times that if he wrote a STrek movie, the first thing he'd do is kill off Captain Kirk. Soon after, Shatner settled for a substantially lower salary than the two million he originally asked for.

(CH) Sitcomm sub 5: the premiere of Twilight Zone showed two stories: "A Saucer of Loneliness," from the story of the same name by Ted Sturgeon, and "The Once and Future King," concerning an Elvis fan who goes back in time and accidentally kills Elvis before he becomes a star.

(GF) Sitcomm sub 6: after the Red Sox won the pennant, Channel 5 showed nearly two minutes of full frontal nudity. They were interviewing a player live in the locker room and other players were walking around naked in the background. They didn't notice until viewers started calling in.

(JME) Sitcomm sub 7: Most of the cast from last year's Saturday Night Live has been trashed.

\goto{Old Business}

No old business.

OBA: um, us, uv, ur.

\goto{New Business}

(TMc) Minicult by way of Phonecomm: I ran into Carl Hylin, a former Skinner, at a western California hotel.

(There is a boom as the Time Warp blows up.)

(JME) There was a partial solar eclipse today, not that you could notice it behind the cloud cover.

(CH) Minicult: a boxer dog swallowed a watch that plays "American Patrol" at 6:45 in the morning and night.

(JME) Minicult: Ottumwa, Iowa has won the right to use the name of Radar O'Reilly in promoting their town, but Gary Burghoff has refused to cooperate and show up at their Octoberfest.

(JME) Minicult: the American Film Institute has denounced the Turner Corporation's plans to add computerized color to over 150 old films on the basis that it degrades the films.

(CH) Minicult: they've come up with a test to determine whether or not an 18-year-old will come down with Huntington's Chorea in the future.

(CH) Minicult: Timothy Leary is working on a computer game based on Neuromancer.

(SSDT) A guy came in here last week looking for SF art to use as background for a computer game he's working on.

(SLP) SFWA sent us a block of paper.

(SSDT) Motion to condemn SFWA for being blockheaded.

(KM) Move to condemn Doubleday for sending us a non-banana-colored block of paper.

(AA) Second.

Motion passes about 16-8-less than 8 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1753 SST.

\vspace{18pt}

\centerline{Sincerely phone-y,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}