\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 18, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

(SSDT) Announcement- we got the new shelves built, but they're missing the decorative bottom pieces. They're on their way. Also, Inventory is tomorrow at 10 AM. If there is a shelfdex.

\goto{Committee Reports}

(JME) Jourcomm: Please draw some pictures for me. I will still take book reviews too.

(JME) Jourcomm sub 2: I gave our list of dead addresses to George Flynn to look at. Only a couple of them are dead.

(SSDT) Pseudo-LHE: I discovered that MITSFS has an account shared with about 500 other groups that we can use to get things from lab supplies, if we can get the requisitions signed.

(JME) Pseudo-Analogcomm: the star chart hanging on our wall was on TV last night in a Computer Chronicles episode, hanging on the wall of some astronomer's lab.

(BPS) Sitcomm: from next week's TV Guide, NBC still intends to cancel Remington Steele. But USA Today says it'll be returning for a fifth season. Pierce Brosnan may not be James Bond after all.

(JME) 1984comm: Republican representative Robert Dorman of California said in an interview on C-SPAN that he believes sodium pentothal should be used for job interviews when lie detectors won't work.

(LAK) Vecomm: My guinea pig died.

(SSDT) Anti-ESPcomm: James Randi, famed psychic debunker, got a MacArthur Foundation genius award.

(JME) Fear-and-Loathingcomm: a rumor from New York fandom- "NESFA has the bomb; WorldCon in '88, '89, '90, and '91- or else!!!"

(BPS) Cornelia Otis: according to Illinois law, the Democrats are not an "established political party" and therefore will not be able to hold a presidential primary in '88.

(BPS) Moocomm: Aliens has been getting really good reviews.

(SSDT) Moocomm: Ice Pirates and The Sword and the Sorcerer at LSC tonight.

(AA) Moocomm: Big Trouble In Little China is a fantasy about Chinese wizards and a demon who wants to find a woman with green eyes to marry.

(SSDT) Phonecomm: I'm gonna call Spencer Right Now.

Moments later...

(SSDT) Inventorycomm: it's printing!

(JME) People's Albanian Embassy: Massachusetts has one Albanian refugee.

\goto{Old Business}

(SSDT for GF) I ran into an old LHE, Mike Tavis, at a con recently and told him about the wonderful things that have been happening at the MITSFS.

(JME) Josh just appeared and disappeared.

(BPS) About 17 years ago man landed on the moon.

OBA: um, us, uv, ur.

\goto{New Business}

(SSDT) We have a visitor- an SF fan from Norway.

(JME) Minicult: parents in Alabama are suing textbooks for promoting "secular humanism." Among other things, they believe that referring to imagination as a "magic eye" promotes occultism.

(JME) Minicult: the New York Times has decided to allow the use of the word "Ms." in their paper.

(SSDT) An embassy in Argentina was referred to us when they inquired about where to do SF research.

(SSDT) Minicult: a pothole in Columbus, OH ate a Mercedes. The pothole appeared when an old sewer collapsed.

(JAH) Banana.

(BPS) Second.

Motion passes almost all-"never, never!"-about 4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Sincerely sublet,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}