\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 30, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected by pseudo-Onseck Bill Starr.

(RvdH) Move to second the minutes as black leather with spikes.

(KJ) How can you move to second the minutes?

(JME) Motion to approve the seconds!

(BPS) Second!

(CH) Third, third!!!

(SSDT) This could go on for hours.

Motion passes lots of bent limbs and squawks-five straight limbs +"No, no, never!!!"-5 +Spehn.

(KJ) Move to approve a second minutes!

(CH) Second the second minutes.

(SSDT) It fails!

\goto{Committee Reports}

(SSDT) No meeting next week, 6/6/86, due to shutdown at the reactor. Next meeting 6/13/86.

(JME) Jourcomm: I just got a submission in the mail that looks pretty bad. It's a pseudo-humorous essay about how electric hairdryers destroy brain cells. I'll print it if you don't write for Twilight Zine!

(KM) Move to send it to Twilight Zone magazine.

(AS) Second.

(SSDT) Any in favor? (Sounds of apathy.) Dead without the rest of a vote.

(LK) Moocomm: The Great Race is tomorrow night. And on Friday the 13th, there's a Friday the 13th double feature, Creepshow and Friday the 13th Part II. And the day after that is Remo Williams.

(JME) Pseudo-Moocomm: Pierce Brosnan of Remington Steele is the new James Bond.

(SLP) Concomm: for those of you going to ConFederation, Presidential is offering a flight for 115 dollars. The only problem is that it leaves Monday morning.

(Arguments about when planes should leave for WorldCon and whether or not anything happens on Monday anyway.)

(JME) Sitcomm: a Texas journalist from New Rochelle, New York wants his hometown to erect a monument to Rob and Laura Petrie, because he thinks the fairy-tale couple played by Dick Van Dyke and Mary Tyler Moore has made New Rochelle famous. The mayor of New Rochelle likes the idea. Mark Lewis, the journalist, thinks the monument should be something inexpensive, like the ottoman that Rob trips over in the opening credits.

(JME) Pseudo-Son of Famous Author: Bill Starr's perfect restaurant is one step closer to existence, says the Glob. Bill Corrowman, a Bay State businessman, has invented a microcomputer named "Beck and Call" for use by restaurants that allows customers to signal their waiter by pressing buttons.

(SSDT) Randomcomm: from Code of the Lifemaker by James Hogan. (Reads a mathematical passage from the book concerning spaceships and impulse.) You'll notice that the units don't match.

(KM) ROSFAP: SF Chronicle and Locus are not magazines and should not be processed as such.

(AA) I didn't know.

(Arguments about fanzines vs. magazines and whether or not the fanzines in question were ever orange-stickered. Argument is ended by BPS yelling "Real f------ business!!!")

(SSDT tries to move the meeting to New Business, much to the surprise of several members who wondered what happened to Old Business.)

(SSDT) Sorry, we're still in Committee Reports.

(CH) Adina and I went to see Poltergeist II. I liked it, she didn't.

(KJ) I'll recommend Short Circuit, which I saw last weekend.

(JME) Yeah, but you liked Gremlins.

(SSDT) And Remo Williams.

(George Flynn says something about Critters which prompts much discussion about Critters vs. Gremlins. Adina says it was stupider than Gremlins, Connie says it was better than Gremlins. Bill compares Adina and Connie to Gene and Roger.)

(SSDT) I have a UFO report which is unfortunately undocumented. The Brazilian airport reports sighting UFOs about the size and shape of golf balls flying around over their airspace. They sent up chase planes after them. One pilot got surrounded by these things and was followed by them until the planes got low on fuel and had to turn back.

(JME) Concomm sub 2: It looks like I may be on a panel at ConFederation on running SF libraries. I need suggestions.

(Suggestions are made that everyone from MITSFS at the con attend the panel and ask her the most difficult and obnoxious questions that they can think of. Janice says that at least the room will be filled that way.)

(BS) Moocomm: a report from the Cannes film festival on various B-movies being advertised over there. These include Volcana, about a beautiful female Hercules who lives inside a volcano, and The Panther Squad, starring Sybil Danning. The ad says "They storm and conquer a medieval fortress and achieve victory over enemy forces as their own space station is blown sky high." And there is a film here; the ad shows a John Candy lookalike wearing a mohawk trying to pick up a girl in a bikini. The trade paper synopsis refers to this film as a "film of wit and striking emotion about the meaning of the word 'friend.'" The title of this film is Fat Guy Goes Nutzoid.

(JME) Motion for everyone to write letters to LSC asking them to get Fat Guy Goes Nutzoid.

(SSDT) Passes.

(GF) SFTitlecomm: at Disclave I saw a book with the cover blurb "World's Worst (something) is about to be brought into the institute." This is different from the Book of the Institute that we have.

(BPS) We didn't buy it, though.

(KM) Yet another Moocomm: there is a new film being sneaked real soon- it's called The Big Screw. (Exhibits a poster with a Big Screw like unto that of APO on it.)

(JME) APO ought to sue.

(JME) Catcomm: at Disclave I saw a presentation by Mark Rogers about the new Samurai Cat book, which includes "The Empire State Strikes Back" as one of its stories and also includes an Arthurian one in which an academic adventurer by the name of Wisconsin Platt shows up.

(SSDT) I wonder what the Empire State strikes back against?

(BPS) New Jersey, one assumes.

(JME) It's actually called that because there's this big spaceship that looks like the Empire State Building.

(LK) Complete with occasional King Kong.

(SSDT tries to move the meeting into New Business again, but catches herself in time to go to...)

\goto{Old Business}

(JME) Write for Twilight Zine!!! Deadline July 1st!

(BPS) I retyped the Glen Cook bibliography and sent it to him for correction.

(SSDT) I have a letter from George Phillies. Nothing really great. He just mentions that the President is in danger of dying from terminal cuteness. Terminal cuteness, he says, requires three attacks to be fatal; she suffers one from heredity, one from having a snake named Klyd, and the third may be lurking in the shadows.

(JME) He doesn't know about Pumpkin, does he?

(SSDT) He also coins the term "Norman" as a unit of badness, where 1 Norman equals -1 Schmitz.

(JME) At Disclave we coined the term "Cybermusak" to mean bad ripoffs of Neuromancer.

(BPS) The police arrested a 24-year-old Frenchman and accused him of ripping off two US TV stations by selling them the fake footage of the Chernobyl disaster.

(SSDT) Old Business?

(Weird jingling noises in the background.)

(JME) I second that motion, whatever it was.

(SSDT) I didn't see any motion, just the usual Ken. Old Business Algol?

(Everyone) USUAL GARBAGE!

(Cries of "Usual garbage," "Usual Ken," and "Usual Ravs" continue for a while, ended by...)

(SSDT) Usual Vote, and the Usual Result!

\goto{New Business}

(JME) Minicult: the Bulvar-Litton contest was, again for the year, although the Glob made the mistake of calling it "a contest for horrendous mystery writing," as we well know it is a contest for horrendous writing in general. The winning first paragraph, by Patricia Presutti, is "The bone-chilling scream split the warm summer night in two, the first half being before the scream, when it was fairly calm and pleasant, the second half still balmy and quite pleasant for those who hadn't heard the scream at all, but not calm or balmy or even very nice for those who did hear the scream, discounting the little period of time during the actual scream itself when your ears might have been hearing it but your brain wasn't reacting yet to what you know." The panel, in reverential awe, called it "thuddingly anti-climactic."

(BPS) They got about 20,000 entries they had to wade through.

(KJ) The question is, were most of them better or worse than that?

(RvdH) That's what I'd call a slush pile!

(KM) Minicult 1: Space tour company books 250 passengers.

(KM) Minicult 2: Slime grows in radioactive pond at Three Mile Island.

(BPS) Minicult: they are having "guard geese" instead of guard dogs at West Germany's US bases.

(BPS) In Milwaukee, a frisky young bull led police on a four-hour chase through the city.

(BPS) In London, some people marketing a new mosquito repellent starved thousands of mosquitoes, then covered a model with the repellent and put her in the cage. The repellent worked fine until the mosquitoes got out of the cage and began attacking reporters.

(JME) Minicult: from Weekly World News- a company called Jolt is going to market a cola with "all the sugar and twice the caffeine of ordinary colas."

(ATS) Minicult: Massachusetts has a state muffin- the corn muffin.

(BPS) This was started by a group of fourth graders who threatened to cry if Dukakis wouldn't let it go through.

(JME) The corn muffin got a real run for it from the cranberry muffin which had many supporters.

(SSDT) Any more new business?

(GF) From the sports page last Friday- Steven King has made a bet with a sportswriter that the Red Sox will still be in contention on Flag Day. The loser has to pay for a chicken dinner for two and eat it in his underwear. Also, an article claims the Banana Slugs were rejected.

(Some discussion about whether or not this is the most current info. BPS states that the Glob puts a lot of out-of-date stuff in its sports yahoo section.)

(BPS) If anyone is interested, there was another article that explained the name of the banana slug. It has nothing to do with the fruit, except that these things are yellow and somewhat banana-shaped, and also occasionally get up to the size of small bananas. They were chosen because the UC Santa Cruz campus sometimes gets infestations of them.

(Someone, not SLP, says that she thought they were called banana slugs because they taste like bananas, and is promptly Albanianed.)

(BPS) Minicult: a footnote on the Falklands war of 1982; apparently the British frigate Sheffield, which was sunk in the conflict on May 4th with the loss of 20 lives, was sunk by a French-made Exocet missile fired by an Argentinian plane. According to a report in the Daily Mirror, which the defense ministry confirmed, Commodore James Sault, the Sheffield's captain, was making an urgent operational call to navy headquarters near London when the missile hit. The electronic countermeasures on the equipment on the ship was affected by the transmission. Apparently, when using the phone to talk to London, the electronic countermeasure equipment goes down.

(JME) Motion to designate the banana slug as the official MITSFS animal.

(BPS) I have one more thing that I found hanging in the office. It's a Charles Adams cartoon that may be the ultimate cartoon about programming. (Exhibits attached cartoon.)

(SSDT) Move to untable Janice's motion.

(ATS and several others) Second!

Janice's motion passes enough-not enough-a squawk and a banana +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Sincerely submarined,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}