\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 31, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

During the reading of the minutes, the Phonecomm is disconnected. It is reconnected after the danger of having a Phonecomm during the minutes is over.

(BPS) Move to approve the minutes as hung up.

(SSDT) I like it. It passes.

\goto{Committee Reports}

(DSK) Moocomm: LSC showing F/X tomorrow night.

(SSDT) Shelfcomm: We got these shelves from the ASA; thanks to Adam Mellis who pointed out their existence. The long rickety thing will be dismantled but not discarded; it is rickety mostly because whoever built it put legs of different lengths on it. It will come out again the next time we need shelves.

(DSK) Pseudo-People's Albanian Embassy: there was an ad for an EC party that listed "Free Food, Free Drinks, etc." right on down to "Free Albania" at the bottom of the list.

(BPS) That ad also listed "Dan Ing." I asked the person who did the poster who Dan Ing was and why we should come to see him, and she responded "Oh my God, I whited-out the C and forgot to put it back!"

(SSDT) Pseudo-Jourcomm: We've got about half a dozen letters of comment on TZ 37 accumulating in the mailbox. Several of our TZs are bouncing back "return-to-sender," including Fred Pohl's.

(BPS) Mobcomm: I didn't fall off of Quincy Quarry either, although there was one nut there who was jumping into the water from 60-70 feet up.

(BPS) Chokecomm: Boston Red Sox. After the Sox won two games, Leigh Montville wrote a letter saying that the black cloud that had hung over Fenway Park was gone. Well, it's back and probably sentient.

(BPS) Just Plain Weird: among the other weird stories that get brought out at times like these is one about a Lost in Space episode filmed in the 1960s wherein they had an alien passing as a human. In order to test the alien, they supposedly asked it "Who won the 1986 World Series?" The answer was "The Boston Red Sox." After someone talked to the script editor or some such, it turned out that there was a 1967 episode in which they asked "Who won the 1984 World Series?" and the answer was "The Mets." This was at a time when the idea of the Mets winning the World Series was considered science fiction.

(SSDT) IAPcomm: We have four listings in the IAP Guide, assuming they're all accepted. One is for Inventory, one is for a Hitchhiker's marathon, one is for the TZ 38 collating party, and one is for our meetings. I asked for 200 dollars.

(DSK) Pre-Moocomm: Friday the 13th is going to come back and haunt us; according to SF Chronicle, it's going to be made into a weekly series about Jason.

(BPS) I heard that the TV series would have nothing in common with the movie except the title.

(SSDT) Pseudo-Panthercomm: I asked Spencer for AuthorDex and TitleDex again; he didn't have it but he gave us a new computer account- it's on a vax called harlequin.

(JAH) BigBrothercomm: I found out today that it is possible on the Athena system to finger someone at "Reagan." Reagan is not a machine- it is a program that looks all around the network to find the person you're fingering.

(SSDT) International Committee to Map John Kenneth Galbraith Into the Complex Plane, Inc.: He's speaking tomorrow at 9 o'clock in 26-100.

\goto{Old Business}

(BPS) 1) 469 years ago today, Martin Luther started the Protestant Reformation. At last report, the Catholic Church was still trying to figure out how to respond to it. 2) 48 years ago today, a lot of people were very stupid- Orson Wells did his War of the Worlds broadcast. 3) 29 years ago, a Mobcomm was born. The Catholic Church hasn't figured out how to respond to this yet either.

(SSDT) Mr. Fusion is up and running. I bought new paper. It's real expensive. I also found out that if it ever breaks and we can't fix it, maintenance is 70 dollars an hour.

(??) In a review of that Ozzy Osbourne film, the reviewer noted that Osbourne was "unconvincing" in his role as a minister.

OBA: usual stuff.

\goto{New Business}

(People frantically search for some new business.)

(??) A study shows that 20 percent of the domestic marijuana crop is being grown in national forests.

(BPS) Minicult: someone out in the Midwest tried to increase business at his garage by hiring two young ladies to give car washes topless. At the last report, NOW was picketing the places which only made the owner happier about the additional publicity.

(BPS) Minicult: from today's Glob- a junior/senior high school in a small town that may be named Sharon has a Satanist's Club. It's got a lot of people worried but the sheriff is being amazingly cool and even-handed about it.

(John) Minicult: in Detroit, 217 people under the age of 17 were arrested for being out after curfew on Halloween night. The local police force was worried about arson.

Phonecomm: Ring. It's Connie. She's stuck at work but she found an apartment.

(DSK) Miller motion.

It fails.

(BPS) Meltsner motion.

(SSDT) I don't know what a Meltsner motion does!

(DSK) Miller motion.

Passes many-none-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Sincerely sublet,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}