\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 7, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (2/28/86) read and corrected.

JME: Move to approve the minutes as replulsive (sic). Passes lots-4-0 +Spehn.

\goto{Committee Reports}

JME: Jourcomm: the deadline is the end of the first week in April. If I don't have a significant amount of material by then, I resign.

SSDT: Moocomm: see Brazil. It's 1984 piped through Monty Python.

JME: Boredcomm: Yawn. Andy promises to bother DSK, who just took over the job from RvdH.

\goto{Old Business}

Janice provides documentation for the item in last week's minutes about DEC employees being Star Trek fans.

JME: The company offering to bury your ashes in space is in legal trouble for operating an unlicensed cemetery. It seems cemeteries must consist of at least 15 connected acres of land with a paved road. Article attached.

SSDT: The Boskone minutes which were illegible and incomprehensible are now legible and incomprehensible. And that's not all...

The Onseck then hauls a large cactus plant out of Damnation Alley. It belongs to AbM, but it's been here for a month and he hasn't been around to get it. SLP opens bidding at 6 dollars, but no decision is reached.

OBA: um, us, uv, ur.

\goto{New Business}

JME: After Mrs. Marcos arranged to ship her art collection out of the country, she also tried to ship out that of the National Museum of the Philippines. Also, the Marcos entourage bought 12,000 dollars worth of stuff from our base on Guam, and charged it.

George Phillies: Minicult: A Los Angeles D.A. is prosecuting one of those companies that will put you in cryogenic storage until medical science is capable of repairing you- for nonrefrigeration of corpses as a way of enhancing profits. Also, two Brazilians bearing uranium ore as proof of their sincerity offered New York City half interest in a Brazilian mine, so "New York could be safe and strong with nuclear weapons."

ATS: LSC's Doug Weems gave us their old small screen. The best suggestion on what to do with it is from KM- have a one-time-only screening of Attack of the Killer Tomatoes, and provide tomatoes.

SSDT: High-Speed, the new pinball machine downstairs, has nice music but is very loud and talkative. It also has a police siren and rotating red light. In the process of attracting attention to itself between games, it startled two presumably MIT students, eliciting the highly intellectual response "Holy shit, it's got a light on top." Later I witnessed another person playing the game and apparently breakdancing at the same time. For a finale when he lost the last ball, he hopped up on the machine with both feet at the same time while still keeping his hands on the flipper buttons.

There are two Miller motions, the second of which passes 3-<3-2 squawks +Spehn, with lots of people singing "Robots (or cacti) have no tails..."

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}