\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 21, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (3/14/86) read very quickly by KM in the slight lateness of the Onseck and corrected.

BPS: Move to approve the minutes as ha-fast backward (or forward; it was never really decided). Passes everyone-a couple-some +Spehn.

\goto{Committee Reports}

BPS: Pseudo-Jourcomm: Remember Janice's ultimatum.

BPS: Mortcomm: Arnie Sultan, producer of Get Smart, died yesterday.

TMc: Marscomm: The class I'm in that's designing a manned mission to Mars for 2007 or so concluded that the best spaceship drive to use would probably be antimatter.

BPS: Sitcomm: The TV movie Assassin, about an intelligent android running around killing people, was really pathetic. None of the characters seemed to notice the 15-year jump in the technology of everything needed to build the machine. Its power source was solar, through the eyes, and its self-destruct was centrifugally-driven.

JME: Cornelia Otis: The Illinois political system is accumulating lots of entropy. Due to a low turnout, LaRouchian candidates won the Democratic primaries for Secretary of State and Lt. Governor. Adlai Stevenson, the gubernatorial nominee, may have to set up a third party or end up telling people not to vote for his ticket. Documentation from BPS attached.

Discussion of how LaRouche started out as a Trotskyite, then moved further and further right and into the twilight zone.

SSDT: Move to commend JME for putting her report under the correct committee. Passes by acclaim.

\goto{Old Business}

KM: Seitz is now at the Center for International Studies at Harvard. At least he has practical experience in arms control!

OBA: apathetic mumbling of things like "sure" and "yeah."

\goto{New Business}

BPS: Minicult: one of the Larson lecture cartoons featured a dog in an operating room. Well, Hartford's chief medical examiner has admitted to keeping her Dobermans in the lab, but denies she fed them any table scraps. Article attached. "Pardon me, my dog ate the evidence."

CH: Minicult: California authorities are trying to figure out how, with no specific laws against cannibalism on the books, to stop an ultra-right-wing spinoff of Catholicism from their group's tendency of carrying the transubstantiation routine a bit too far. Also, from the Sun, here's an article (attached) about a non-needle injector very much like a Star Trek air hypo. Additionally attached are Sun articles about a family that lives in a gas station bathroom, and a man who suffered a shark bite in his living room.

CH: WWN Report: Articles attached about a toothpaste dispenser that won a Rube Goldberg contest and a planned theme park based on the Bible.

JME: Minicult: the only person rated more negatively in popularity polls than Jerry Falwell is Ayatollah Khomeini.

SSDT: Threat- if I keep hearing Weekly World News reports at meetings, I'm going to retaliate by reading Phoenix personal classifieds.

ATS: No meeting next week; I'm in Ohio and SLP's in Florida.

BPS: Minicult: An Air Force pilot managed to misjudge the width of a runway and got the plane, with Nancy Reagan aboard, stuck in the mud. A massive traffic jam was caused by all the people stopping to watch.

A Miller motion fails.

KM: Move to agree with Bill that there ought to be a motion concerning the new banana colored Beam-me-up-Scotty bumper sticker. Passes lots-a few-less +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}