\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 12, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(CJH) Motion to approve the minutes as going down for the third time.

(RvdH) Second.

Motion passes everyone-one "M'Aidez"-0 +Spehn.

\goto{Committee Reports}

(SSDT) We're appointing a new Den Mother______, Nancy Jo Buck, the person who's supposed to be here 9 to 5 in the manager's office giving out keys to the new lock on the door. She cuts out early on Fridays, so people who work until 5 are out of luck. We've attempted to arrange authorization for the night shift to give out keys, but I don't know yet if this will work. Another problem is that this person locked her desk before leaving, thus locking in the key cards that have to be filled out before keys can be given.

(DSK) Moocomm: Big Trouble in Little China tonight at LSC.

(JME) Jourcomm: We have a collation for TZ due for January and I have only two pages of submitted material. Get with it, people.

(At this point, some Old Business comes through the door carrying some New Business. The Old Business is Jim Mahoney, and the New Business is his 14 month old daughter Lynn.)

(SSDT) So that's what you traded for your key.

(JME) Pseudo-Moocomm: Don't go see Solarbabies; it's getting horrible reviews.

(SSDT) Theftcomm, maybe: I don't know what happened to the ladder we used to have.

(BPS) Opinioncomm: I just finished A Fionavar Tapestry by Guy Gavriel Kaye. It's very good.

(JME) STrekcomm: More proof that STrek has made it into mainstream pop culture. A week ago Thursday on LA Law, there was a scene between a depressed man and a concerned woman who wanted him to come home with her and be cheered up. As part of the coaxing, she said "I have all the Star Trek episodes on videotape," to which he responded "Even the one with the tribbles, where they multiply all over everything?" When she said yes, he agreed to come home with her.

(BPS) STrekcomm sub 2: George Takei got a star on Hollywood's walk of fame.

(JME) STrekcomm sub 3: Takei is keeping busy. On Letterman's show a while ago, they showed a hack documentary on the theme of proving that a TV personality was really a robot, and they got Takei to narrate it.

(CJH) Sitcomm: on TV next week, they're showing a reworking of Babes in Toyland with Pat Morita as the toymaker.

(JME) Sitcomm sub 2: the new STrek series seems to be pretty definite now. It's going to be produced for syndication and will take place in the 24th century, 100 years after the original series. Roddenberry will be in control.

(BPS) Addendum- It's going to be offered first to stations currently showing the old series. Roddenberry won't rule out guest shots by the current cast if someone writes a feasible script.

(JME) Namecomm: our car, named Excelsior after the ship in STrek, got trashed on the way back from STrek IV. No one was hurt, but the car was damaged for over 4000 dollars.

(CJH) Bananacomm: there's a billboard on Route 99 with a huge Chiquita banana on it.

(BPS) Pseudo-Theftcomm: my employer fell for it and matched the 250-dollar joint contribution that Larry and I gave a while ago two for one. So we should be getting 500 bucks from them soon.

(JME) This Wednesday evening I'll be interviewing Ben Bova over the telephone.

(BPS) Dribblecomm: the Boston Celtics issued non-voting shares in their company. The stock has gone from 18 3/8 to 17 1/8 since it opened.

(JME) Huntcomm: meeting after the meeting. Also, the guy who does publication for NESFA feebled. He didn't send me a copy of the progress report so I could check our entry.

(SSDT) Star Chamber meeting after the meeting. Very brief.

(SSDT) Skinner Report: I've taken up playing Gladiator rather fanatically, and if anyone knows how to get past the archer on the second level, please tell me. This is not what I'm calling the Star Chamber meeting for.

(JME) Infocomm: Infocom is cleaning out some of its older games for 14.95 apiece. I have details for interested people.

\goto{Old Business}

(BPS) Back in the November 5 issue of the Wall Street Journal, there was an article in which somebody at Harvard flamed at great length about how the nuclear winter theory was now thoroughly discredited. This article, which was trimmed from a longer article in a right-wing magazine called The National Interest, caused a letter war and was written by one Russell Seitz.

OBA: um, us, u"What about the UD?", u"Shut up!"

\goto{New Business}

(JME) Minicult: In Reykjavik during the pseudo-summit, the Assistant Secretary of Defense Richard Perlbrook heard that Reykjavik didn't have enough restaurants to serve all the people in town for the meeting. He brought two Hebrew National salamis with him and put them on his hotel windowsill to keep them fresh. They fell off, and two Icelandic security people, believing they were under attack, stomped on them and destroyed them.

(KM) Sum total of repairs to the Golf: 4700 dollars. The car is now 10 percent newer.

(JME) Bill's column has gotten a got of good comments in several LoCs.

(BPS) Minicult: A man who wrote a tax advice booklet called "Anybody Can Stop Paying Income Taxes" is starting a three month sentence this month. The charge: tax evasion.

(JME) Minicult: about 46 percent of the trash in Washington is paper as compared to the national average, which is 30 percent.

(AA) Minicult: I have an amusing article here from the Phoenix about Oliver North titled "Ollie Ollie In Free." (Reads excerpts.)

(JME) Minicult: There were 110,000 crossbows manufactured in Britain in 1985.

(CJH) Minicult: Headline- "I died and went to Heaven, met Elvis Presley, and took this picture to prove it."

(SSDT) In Woodbridge, Connecticut, a preacher trying to put Christ back into Christmas got a bit carried away and told youngsters in a sermon that Santa Claus is dead and Rudolph the Red-Nosed Reindeer doesn't exist, and parents who say otherwise are liars. He's in a lot of hot water.

Someone makes a Miller Motion.

It fails.

Miller Motion.

Motion passes enough-not enough-more than not enough but less than enough +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1742 SST.

\vspace{18pt}

\centerline{Sincerely after the fact,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}