\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 2, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order in the Spofford Room, 1700 SST,
Andrew Su, President and Skinner, presiding.

Minutes of the previous meeting (4/28/86) read and corrected.

(BPS) Motion to approve the minutes as about an hour away from being Skinnerial in their presentation.

Passes everyone wants to get this over with-go away you folks, free silver, free silver-many squawks +those God bless it pink velcro shoes +Spehn.

\goto{Committee Reports}

(JME) Bananacomm: from the 5/1/86 Glob- a TV commercial offered a stereo system for 299 bananas and 32 people took it literally. Article attached.

(BPS) Bananacomm sub 2: USA Today- the student body of UC Santa Cruz voted in a nonbinding referendum to change the school's mascot from the sea lion to the banana slug to represent the school's noncompetitive nature. The athletes didn't like it. Article attached.

(JME) Pseudo-Picniccomm: the remainder of the supplies for the picnic have been bought except for the bugles.

(ATS) Pseudo-Picniccomm: on the meat side, we have plenty of meat, cheese, fruit, and a nice virgin watermelon.

(JME) Pseudo-Picniccomm: weather division- Sunday should be sunny but cold and windy.

(JME) Jourcomm: TZ Real Soon Now. No, wrong default... write for TZ!!! Deadline is July 1st, otherwise it won't be ready for all those friendly frosh by R/O Week. I've already started two articles and I really don't want to fill up the rest of the fanzine...

(BPS) Coincidencecomm: July 1st is also when they are shutting down the bowling alley and pool room in the Student Center with no fanfare whatsoever.

(BPS) Mobcomm: run for your lives, Starr's got a new car! It is a red Jeep Cherokee that looks like a fire truck.

(SLP) LHE Report: things are back to normal. Income- 130.07, Expenses- 410.93, Loss- 280.86, Equity- 3045.34.

(RvdH) Jokecomm: how do you cook Chicken Kiev? Hold it out the window for 10 minutes.

(JME) Jokecomm sub 2: the one I heard was "What bird clucks and glows in the dark? Chicken Kiev."

(GF) Famecomm: I have some good news and some bad news. The good news is that we're mentioned in Locus; the bad news is they misspelled us as MITSF. This was in connection with our panel at Boskone.

(SLP) Look for the fall issue of Newsweek on Campus; MITSFS is in it.

(KM) With a picture perpetuating a bad stereotype- it had six men and only one woman.

(BPS) Pumpcomm: for those of you who recall Arnold Schwarzenegger saying that a good pump is better than sex, I have here photographic proof that he has just married a vampire. (Exhibits picture of Maria Shriver with a vampiric expression on her face at her wedding. Picture attached.)

(KM) Pseudo-Moocomm: somebody actually paid 100,000 to William Gibson to get the rights to make Neuromancer into a film. They originally wanted to make the sequel to Buckaroo Banzai but couldn't get the rights so they decided to make Neuromancer instead. It's a Cabana Boys production.

(DSK) Famecomm sub 2: MITSFS got mentioned in SFLovers last night. It says something about "Robots have no tails," and a girl named Kathy Kirby who got the book out of MITSFS and almost didn't return it.

\goto{Old Business}

(HAM) I think it's about time you gave her the ravs, Andy.

(People start chanting "Ravs, ravs, ravs" as LAK sneaks up and handcuffs Andy to his chair.)

(JME) Now how's he going to go get her the ravs?

(ATS) Any more old business? You aren't even going to get close to getting those ravs.

(BPS) You aren't even going to get close to getting that key...

(Much discussion about how Andy's going to get out of the handcuffs.)

(BPS) Old Business Algonquin.

(ATS) Old Business Algol...

(RvdH) The Usual Bullshit.

(JME) And the Usual Ravs.

(ATS) Sold!

\goto{New Business}

(BPS) Minicult: from the Glob of a few days ago- Swaziland has a new ruler, 18-year-old King Makhosetive Mswati III. Most of the day-long ceremony was improvised because nobody could remember how it was supposed to go. It was last done in 1921. Article attached.

(CH) Minicult: New York Times- Imelda Marcos is no art critic; she spent millions of dollars on junk when buying paintings for the Philippines Art Museum.

(BPS) Minicult: Jeep is discontinuing the Jeep CJ, which stood for Civilian Jeep, and is replacing it with the Jeep YJ. The Y stands for Yuppie.

(CH) Weekly World News Report: Psychologist claims machines have souls and can haunt us.

(BPS) Minicult: Here's an absolutely ridiculous picture of Jane Fonda showing how dignified she is. Picture attached.

(KM) Minicult: from the Sun- man with wooden leg eaten alive by termites.

(ATS) Unlock me from this thing, I can't reach the gavel...

(KM) Move to send emergency banana shipments to Kiev.

(ATS) Not quite, I'm not going to be around here much longer.

Election results, final ballot:

Onseck:

Yalda- 0.26

HS-149- 0.25

Kurt- 0.01

Jennifer Marlowe- 0.10

Jenny-Poo- 9.66

Gen-Jen- 2.05

Dead Simes and Gens- 0.71

Pumpkin- 1.26

Randoms- 11.45

LHE:

Ferd and Imi- 0.30

Herbie the Love Bug- 0.25

HAM- 11.23

John DeLorean- 1.19

B. King's Ad Agency- 0.25

Pumpkin- 2.70

Dead Sime and Gens- 0.61

Green Eggs- 0.41

Spam- 3.47

Randoms- 5.21

Vice:

Gary Larson- 0.30

Don Johnson- 0.10

Lisa's Accouts.- 10.60

John Norman- 0.30

Tarl- 0.10

Spam- 0.70

Pumpkin- 0.51

Dead Simes and Gens- 1.03

Gorbachev- 0.30

Judy's Fishnet Stockings- 0.10

Randoms- 1.02

President:

Peking Ravs- 1.20

Peeking Toms- 0.10

Dead Simes and Gens- 0.40

Sue "That's Enough"- 6.78

Desperately Seeking Spam- 2.10

Sue- 14.48

Randoms- 1.63

At some point during the voting, Andy is un-handcuffed from his chair and handcuffed to Sue Pitts. Sue Pitts says she will make Sue Tucker Skinner if Sue will give up all claim to the Ravs and make Lisa give her the key so she and Andy can go their separate ways. Sue gives up her claim on the Ravs by transferring it to Lisa. Sue Pitts makes Sue Tucker Skinner anyway. Pumpkin is declared Official Second.

(RvdH) Move to handcuff Andy to a redheaded banana.

Passes by acclaim and hunger.

\vspace{12pt}

\noindent
Meeting adjourned, 1920 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}