\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 24, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected by Pseudo-Onseck Janice Eisen.

For the third week in a row, there is a Phonecomm during the reading of the minutes. It is Val Stark; she is ill and wants her hours crossed off.

(BPS) Addendum to the minutes- our friend John Noun, famed lawyer, is indeed of Albanian descent. I'll have to ask him about that Noun's restaurant.

John whose last name I can't remember makes a motion that retroactively ceases to exist.

(RvdH) Motion to approve the minutes as read.

The motion dies of hissing.

(BPS) Motion to approve the minutes as better than dead.

Motion passes (just barely) 11-5-6 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: most of TZ's standard mailing has gone out. And you people better get writing, especially book reviews, so we can stay on people's review lists.

(BPS) Sitcomm: this Sunday, one of the networks will be running a made-for-TV movie entitled Who is Julia? about a brain transplant patient.

(JME) Moocomm: there's a movie opening called Trick or Treat about a heavy-metal fan who plays his record backward and conjures up a demon. It features Gene Simmons of Kiss and Ozzy Osbourne.

(BPS) Sitcomm: this Monday's Amazing Stories is an hour-long show directed by Robert Zemeckis and stars Christopher Lloyd. It involves two kids who use a spell on their dreaded headmaster that they learned from listening to rock and roll records backwards.

(JME) Sitcomm: no Twilight Zone this week.

(BPS) Addendum- I've heard it's scheduled for another hiatus but has been promised renewal, if you trust a network executive.

(SSDT) Moldcomm: MIT Archives wants to make microfilm of our old TZs.

(JME) Moment of Silence: Dan O'Day, an MIT student who hung around here a fair amount, committed suicide last week.

(BPS) Mobcomm: the Mobcomm did not fall off the side of a building, although he sure tried hard. I went out with the Spelunker's Club.

(JME) Sitcomm: NBC must be getting desperate about Alf; they kept inserting little promos for it into their coverage of the World Series.

(KM) Bananacomm: we've gotten one Dole banana sticker so far towards getting a Bananimal for the library.

(SSDT) Shelfcomm: ASA gave us permission to steal some standards from the Small Activities office.

(KM) Miller Motion.

It fails.

\goto{Old Business}

(BPS) The leak has stopped. We still have a hole in the roof.

(JME) I spoke to former Vice Merryl Gross today. She's doing fine.

(JME) The Dan Rather "What's the frequency, Kenneth?" incident has caught the public imagination. At least one outfit is selling "What's the frequency?" t-shirts.

OBA: the usual.

\goto{Minicults, AKA New Business}

(JME) Minicult: from this month's Harper Magazine- a forum appeared titled "Notes in an Interplanetary Bottle," based on the concept of what if we decided that the aliens out there might be hostile and wanted to send them messages saying "Keep off the Earth" or "Martians go home" or something similar. The forum included Carl Sagan, Mayor Ed Koch, Greg Benford, William Burroughs, and David Byrne. It's in the interesting reading folder.

(BPS) Minicult: there was a small note in the Glob about Disney and Steven Spielberg teaming up to produce a movie about which nothing is known save the title, which is "Who Framed Roger Rabbit?"

(BPS) Miller motion.

Passes by acclamation.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Insincerely subordinate,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}