\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 25, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the last two meetings read and corrected.

(RvdH) Move to approve the minutes as having a split personality.

(SSDT) All in favor?

(RJG) Yes and no!

(JME) Albanian motion!

(SSDT) All in favor or opposed?

Motion either passes or fails.

\goto{Committee Reports}

(JME) Jourcomm: Please (to the seventh power) draw me some pictures for TZine.

(SSDT) Pseudo-Panthercomm: The inventory was and it went very well.

(JME) Famecomm: It is now confirmed; I am going to be on a panel at WorldCon about managing SF libraries.

(BPS) Jourcomm sub previous: a story that appeared in TZ 36 recently appeared in Twilight Zone under a different title, with my editing intact for the most part.

(AA) Panthercomm: Terry Carr is sabotaging PinkDex by changing and rearranging the titles on his World's Best SF Anthologies, changing publishers and sometimes having numbers, sometimes not.

(BPS) Sitcomm sub one: ABC is making a series about Starman starring Robert Hayes.

(BPS) Sitcomm sub two: Fox is no longer thinking about resurrecting Star Trek with a new crew; they don't want to compete with the movies.

(CH) Sitcomm sub three: Ghostbusters is becoming a Saturday morning cartoon, but because of trademarking squabbles it will have little to nothing to do with the movie.

(BPS) Clue: The Movie is out on videotape with all three endings.

\goto{Old Business}

(JME) The parents in Tennessee who objected to the "magic eye" of imagination turn out to object to imagination, creative thinking, and criticism in all forms.

(JME) Mike Tavis, an old LHE, is also seemingly going to be on a random panel at WorldCon.

OBA: usual stuff, uv, ur.

\goto{New Business}

(BPS) On the grounds of Oral Roberts University, they have a sound and light show based on the Bible. They're only through Genesis at the moment.

(JME) Minicult: at Hartsfield Atlanta International Airport, a pilot rebelled against the endless delays by walking out of his plane while it was on the runway and taking early retirement.

(BPS) Minicult: Somewhere in the Carolinas is a very happy Saint Bernard; it has a luxury air-conditioned doghouse and many other amenities to help it survive the heat wave.

(AA) Minicult: the sheep that the Summer Theatre people are using in their play attracted a great deal of attention, especially after a misphrased call to the health department led officials to believe that the lamb had actually been slaughtered as part of the play. They descended on the play people in horror and had to be taken to pika so they could see the live lamb in the yard.

(SSDT) We have an official Fweekcomm: Rob Gates.

(AA) Move to assassinate Terry Carr with a banana.

Passes many-a few-as many as opposed +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely subatomic,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}