\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 10, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (12/13/85) read and corrected.

After several failed attempts by various people, BPS moves to approve the minutes as being more present than the Skinner's picture. Passes everybody-Scott-3 +Spehn. Andy says he'll rip down any picture he doesn't like.

\goto{Committee Reports}

SLP: LHE Report, December: Income- 157.64, Expenses- 274.85, Loss- 117.21, Equity- 5179.09.

ATS: Skinner Report: New teeth! No more hardware (almost)!

Phonecomm: Jourcomm: Janice says to write something.

\goto{Old Business}

JAH: I'll bring in the People magazine item on Harlan Ellison.

OBA: um, us, uv, ur.

\goto{New Business}

The first order of business is a motion which passes by acclaim, to put the small robot that is running around on the floor onto the gavel block, directly in the path of the gavel. KM escapes with his toy just in time, then is called back and permitted to give a demo.

BPS: Minicult: Canada, which outlawed the death penalty ten years ago, finally got around to dismissing the hangman. Article attached.

SSDT: Inventory, tomorrow at 11, and maybe on Sunday too. We have copycounts for H, HA, C/PA, in fact everything but C/P and circulating Ace doubles.

ATS: Sign up for hours on the new IAP schedule. Paul Mailman is resigning, and Jack Stevens will be the new Analogcomm.

CH: WWN Report: there is no WWN Report.

BPS: But here's a report on the notable lack of success of the psychics' predictions for 1985. Attached.

BPS: Minicult: in Dr. Ruth Westheimer's latest book, the accidental loss of the prefix un- from the word safe at one point reverses the truth of when one should avoid sex in order to avoid pregnancy, necessitating the recall of the book. Article attached.

KM: Speaking of typos, the latest issue of MacUser gives a nice review of the game Rogue, except they spell it Rouge.

TMc: Martin Marietta gave me an employment application when I went to an interview with them. While I was filling it out a week later, they called and offered me a job.

BPS: My roommate who works at Laureate got us four publicity balloons from L. Ron Hubbard's The Invaders Plan. (1 attached.) Andy proceeds to destroy one with the gavel.

RvdH: Move to note that one of the banana colored kickstools is now banana colored with a racing stripe. Passes lots-1-a few +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}