\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 13, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

The unminutes were unread and uncorrected.

(SSDT) Motion to disapprove the minutes as soft, as in they're still in the software.

(BPS) Soft and mushy.

(LAK) Second.

Motion passes everyone-none-1 +Spehn.

\goto{Committee Reports}

(SLP) LHE Report: we were in the black last month. Everybody signed up for new memberships. Income- 167.45, Expenses- 57.96, Profit- 109.49, Equity- 3154.83.

(SSDT) Atlascomm: A couple Sundays ago, when a drastic straightening took place and the couch moved over here, some of the old picnic gavel rocks were removed from below the bookcase and distributed to various fourth floor organizations. Three-quarters of them are still out in the hall; it seems no one knows what to do with them.

(JAH) Sneakercomm: I know most of you have already seen them, but I've got a new pair of atrociously colored sneakers, and I'm going to be voting with them.

(ATS) They're purple.

(BPS) They're blueberry frogurt sneakers.

(BPS) Sneakercomm sub 2: I tried to find Converse velcro sneakers; they're gone, discontinued forever. They're discriminating against lazy people; I object.

(LAK) Bananacomm: when I was home in Pennsylvania I stopped in Spencer's and saw a banana-phone.

(SSDT) Which end do you talk into? The stem end?

(LAK) No, the other end.

(SSDT) So it looks like the banana is growing from your ear.

(LAK) Yeah.

(BPS) I can't hear you, I've got a banana in my ear.

(LAK) They also had Gumby phones.

(BPS) MA Bell is selling duck-decoy telephones.

(LAK) They also had Budweiser beer phones, but I like the banana phone and Gumby phones best.

(RvdH) Move that the MITSFS buy a banana phone.

(SSDT) Move that you buy the MITSFS a banana phone. Fine, passes!

(RvdH) Meeting's over!

(SSDT) Good, that gets me out of here.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Sincerely substandard (the meeting, that is),}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}