\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 25, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (4/18/86) read and corrected.

Andy asks for motions concerning the minutes, and the Onseck makes a pronounced motion toward the wastebasket. This passes lots-some-some squawks +Spehn.

\goto{Committee Reports}

DSK: Moocomm: Legend is a see-it-at-LSC movie.

CH: Moocomm: Water resembles The Mouse That Roared on the Caribbean.

LAK: Moocomm: The Secret Life of Walter Mitty is the LSC Classic, and Monty Python's Life of Brian is tomorrow.

SSDT: Pseudo-LHE Report: We now have reimbursement forms that you can fill out if you want to be paid for something. They live in the front of the large drawer of the keyholder's desk for now.

BPS: Pseudo-Jourcomm: Got a letter from The Alpert, which comments on our maintaining a leisurely publication pace for TZ. He expects that his record of at least 2 a year for 2 years will not be broken soon.

BPS: Sitcomm: The Greatest American Hero is returning to television, and this time the suit goes to a woman. Article attached.

SSDT: Panthercomm: I thought I was going to complete the Pinkdex database today, but Sue Pitts is sitting there processing more things as fast as I can enter them.

ATS: Pseudo-Picniccomm: Don't forget elections next Friday in the Spofford room and the Picnic on Sunday.

BPS: Embassy to the Null Set: Overheard at a press hangout- if NASA picks Geraldo Rivera as the space journalist, they can study the effects of weightlessness on weightlessness. He just hosted the opening of Al Capone's vault, which turned out to be nonexistent.

\goto{Old Business}

Judy Passman is here.

OBA: um, us, uv, ur.

\goto{New Business}

BPS: Minicult: a preacher creature from Ohio thinks he has found backwards satanic lyrics in the theme song from Mr. Ed. CNN played it backwards twice and it was all French to me. Article attached.

CH: The University of Colorado has a holiday and a Student Union grill commemorating Alfred Packer, the only person ever convicted for cannibalism in Colorado. This year's theme was (ghastly pun based on a United Airlines slogan deleted for the comfort of the audience).

Connie is Albanianed and the U of C is declared the U of A by acclaim.

BPS: Minicult: More rear window signs- Brat on Board, and Ex-Spouse in Trunk. I saw that one on a hatchback.

HAM: Ravs on Board Carry No Cash?

CH reads the WWN Report in Albanian, but for some reason it doesn't make any less (or more) sense. A priest leads a Christian motorcycle gang, a man turned on his oven without remembering to remove his gun, the Batmobile is pulled over for not being street legal, and a dog ate a hole in a Corvette to get at the cat hiding in it. Articles attached.

SSDT reads Phoenix classifieds, one of which provokes a philosophical discussion of Peeping Toms, and another of which causes KRJ to get himself Albanianed.

BPS: Here's an item from a supermarket on how to select bananas, and a recipe for banana cream pie on the back. Attached.

DSK: Move to recognize Uranus as having a banana shaped magnetic field, according to Science '86. Passes everybody-"No, no, never! Free silver! Free silver!"-the Vienna Chickens Choir +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}