\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 19, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

There is a Phonecomm during the reading of the minutes; it turns out to be Sue Hagadorn, who says she is going to take a quart of Haagen-Dazs to the hospitalized Jourcomm, Janice Eisen.

(CH) Motion to approve the minutes as incredibly subjective.

Motion dies for lack of a second.

(DSK) Motion to approve the minutes as camouflaged.

More silence.

(BPS) Motion to approve the minutes as so good I wish I'd been there for the meeting.

(RvdH) Second.

Motion dies by "Nahhh!"

(Jim Rauen) Motion to watch the minutes pass.

Many seconds and the motion passes everyone-1-1 +Spehn.

\goto{Committee Reports}

(SLP) LHE Report: since September is the beginning of a new fiscal year, here are the totals from last year. Income, for dues- 2422, for fines- 754, for sales- 559, and for miscellaneous- 1937. Expenses, for books- 4147, for magazines- 769, for supplies- 289, and for miscellaneous- 3855. Miscellaneous includes two orders of shelves. We spent about 3000 more than we took in.

(SSDT) People had been complaining that the equity was too high; it's been fixed.

There is another Phonecomm; it's Dave Broadbent to talk to RvdH.

(SSDT) APOcomm: we got our unsold books back from the APO Book Exchange. We made about 21 dollars and were not massively ripped-off.

(BPS) Mobcomm: over the weekend I ate up our profits from the Book Exchange plus about 66 percent.

(BPS) Moocomm: Brazil is tonight.

(LAK) Sitcomm: Starman tonight.

(BPS) HillStreetBluescomm: LA Law premiered last Monday. It has a lot in common with the pilot of Hill Street, mainly in that it is caricatured and rough-edged the way Hill Street was. Whether or not it will also improve the way Hill Street did remains to be seen.

(DSK) Sitcomm sub 2: Crime Story premiered last night and I thought it was pretty good.

\goto{Old Business}

(BPS) Followup to a Minicult: wearing telephone beepers has become a status symbol for students in Detroit schools, so all of the students are wearing them, not just the drug dealers.

Things get warm in the MITSFS as there is a great deal of flaming about this.

OBA: the usual usuals.

\goto{New Business}

(BPS) Janice Eisen should be going in for surgery right about now. We have her hospital phone number so people can call.

(CH) Massachusetts is going to be putting out new license plates soon, so the Herald ran an article about what the new plates might say. Suggestions included It's Not Just Rotaries, 10,000 Tollbooths, Land of Potholes, I Lost My Car in Massachusetts, and Live Free or Charge It.

(LAK) How about "Boston Driver On Board?"

(CH) Some technical journal called EZN was advertising nuclear reactors for use as backup power for IBM computers.

People start singing "Rabbits have no tails at all." In spite of the LHE's desperate cries of "Miller motion! Miller motion!!!" it gets sung five whole times and the meeting is adjourned.

\vspace{12pt}

\noindent
Meeting adjourned, 1734 SST.

\vspace{18pt}

\centerline{Sincerely subtitled,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}