\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 7, 1986

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read by Pseudo-Onseck Janice Eisen.

Immediately after the Pseudo-Onseck reads the part of the minutes mentioning that the Phonecomm was disconnected during the previous meeting, there is a Phonecomm. The Skinner answers the phone with "Awesome timing, whoever you are." It turns out to be nobody.

There is a second Phonecomm soon after, answered by the Pseudo-Onseck who says "Go away." It's Connie, who says she wasn't the one who called the first time and she's coming as fast as she can.

(SSDT) Addendum to the minutes- we never reaffirmed the Society's faith in the Great Pumpkin last week, but remember that we had a Meltsner motion and I didn't know what it did? That must be it.

Passes everyone-none-1 +Spehn.

(BPS) Motion to approve the minutes as still ringing.

It dies of apathy.

(JME) Motion to approve the minutes as black velour.

(BPS) Second.

Motion chickens 2-4-lots +Spehn.

(KM) Motion to approve the minutes as painful, like having your chest hair caught in a zipper.

Motion passes lots-none-5 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: we got lots of LoCs, including a nice one from Ben Bova who wants us to write an article about the politicization of science fiction over Star Wars, a lovely postcard from L. Sprague de Camp, and a weird letter from J.K. Klein. Also, at WFC I learned that BlueJay Books, which put us on their review list, has folded.

(JME) Huntcomm: It's time to start working on the Scavenger Hunt for Boskone. Brief meeting after this one for those interested.

(JME) Sitcomm: Twilight Zone has been canceled. There is a small chance that it may come back at some future date.

(KM) ROSFAP: 1) Don't put SFC or Locus on the new magazine shelf, because they are not magazines, they are still fanzines. 2) SFR is going out of business. The guy who does it is too sick to keep doing it. We should try to get Orson Scott Card's Short Form as a replacement.

(JME) Jourcomm sub 3: write for TZ please write for TZ we announced a collation in January we can't have a collation if there's nothing on the pages and I am not going to fill the entire magazine.

(JME) Jourcomm sub 4: One of the LoCs we got, from Neil Caden, suggested that we would get more fanzines if we delegate people to write LoCs on the fanzines we got.

(JME) Jourcomm sub 5: We've gotten some more responses from "Where are they now?" and only one person has turned up dead.

(SSDT) Moocomm: Splash tonight, Star Wars IV tomorrow and our slide all three nights.

(BPS) Sit/Moocomm: Splash, ABC, Sunday night. Yay LSC.

(BPS) Sitcomm Sadness: Paul Fries, voice of- among other things- Boris Badinoff, dead at 66.

(JME) Abocomm: the next issue of Aboriginal SF should be out before Philcon. There will be no more flat copies; they're having them folded at the press since some bookstores complained when they got flat copies. It also has a letter from a reader complaining about Darryl Schweitzer's pan of Mission: Earth and accusing him of being a "psychologist."

(BPS) Mobcomm: I didn't fall off of a refrigerator last night or vice versa. There is now one less refrigerator in Waltham and one more in the Telzey's apartment. Never again. (Not the Skinner's idea.)

(AA) Infocomm: I picked up Leather Goddesses of Phobos the other day- it's out, and it's highly bizarre. I haven't gotten very far. The only thing I've acquired is a rubber hose.

(DSK) LHE Pseudo-Report: We're missing some money and I'm trying to figure out where it is. 5.12.

(SSDT) Skinner Report: the IRS is out to get us, we're doomed, etc. It appears to have been due to a bank error.

\goto{Old Business}

(KM) Dan's here.

(JME) Merryl will be in town briefly this weekend for a couple of interviews.

(JME) Mike Royco got some answers to his "Guess why Dan Rather got beaten up by two men who wanted to know what the frequency was" contest. The most popular answer was that the two men were aliens in disguise who had a third crewman named Kenneth who had run away and they were trying to find him to find the right radio frequency to call home. (Moocomm: "But all Lectroids are named John...")

(JME) I have a depressing article here about how the Rogers committee that investigated the Challenger accident did a lousy job.

OBA: um, us, uv, ur, "what about the usual Van der Heide?"

\goto{New Business}

(KM) Minicult: when a friend and I were talking about a transvestite and transsexual person we both knew named Roberta, someone else at the lab said "Roberta Van der Heide?"

(JME) Minicult: at WFC I found out what the big-name pros talk about at those closed parties. I walked into a room full of pros who were discussing smegma.

(AA) There was an exchange of letters in the New England Journal of Medicine discussing the use of zippers to close up incisions. At least one doctor advocated the use of zippers on patients whose innards must be reexamined. A zipper company objected on the grounds that they weren't sterile.

(SSDT) Minicult courtesy of Malcolm Y: from a California wine ad- the members of a city council in a village in France were worried that flying saucers might be damaging their wine. So they passed an ordinance prohibiting the landing of flying saucers and stipulating that any flying saucers that did land should immediately be taken to the pound.

(BPS) Minicult: the first round of lawsuits in the trial of Hasbro vs. Columbia Pictures over the Ghostbusters logo is over; Hasbro sued for 50 million in copyright infringement because the Ghostbusters ghost looked too much like Fatso from the Casper series. The judge ruled in favor of Columbia Pictures.

(JME) Minicult: how to lose friends and influence people division. Headline over the full-page ad in the Washington Post- "My daddy lost his job" with a picture of a sad-faced little girl. The ad is from Boeing and the thrust of it is that the way to give Kathy's dad back his job is to build a space station.

(AA) Minicult: someone has done genetic surgery on a tobacco plant to make it glow in the dark. They took the gene from a firefly that makes it glow, implanted it in the tobacco plant, and it really does glow.

(JME) Minicult: Word Publishing, a Christian publishing house in Texas, is distributing to religious bookstores copies of the Mees Commission's report on pornography. It includes highly detailed plots from Deep Throat and other lesser known works.

(BPS) Minicult: from the Glob, November 1st- a 24 year old man appearing in a New York courtroom to answer a weapons possession charge was arrested in the courtroom when they found he was carrying in a bag 76 vials of crack. Said he, "I forgot I had them with me."

(CH) Minicult: a Barnes and Noble ad for a globe suggested that you buy it because it lights up in the dark.

(BPS) The post-nuclear war edition.

(BPS) Minicult: for those of you who wonder why the Republicans did so poorly in the elections- Reagan, campaigning for Santini in Nevada, commented that there were probably some Democrats in the audience and said "Like millions I've run into across the country, they've found they can no longer follow the leadership of the Republican Party, which has taken them down the course that leads to disaster."

(JME) Minicult: Orbit is no longer in the Glob. (Cheers.)

(KM) Move to send the Glob a banana for canceling Orbit.

(CH) Associated Minicult: when the Glob ran an article on its comics page, Robotman wound up in both the top ten and the bottom ten.

(JME) Motion to build a banana shaped spaceship to land in this vineyard.

(John Dumas) In Touch for Men did an article on warlocks.

Banana motions pass many-none-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST. (1820 EST, due to a late start.)

\vspace{18pt}

\centerline{Sincerely submitted (I know it's boring but I'm tired...),}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}