\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Official Meeting Minutes 

Friday, July 15, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read and discussed. Minutes were also read from 28 April 1969, I think- gotta get those numbers right.

A motion was made that the minutes were late, and passed.

A discussion about meetings on the Web, similar to the discussion of last week, ensued.

\goto{Committee Reports}

Jourcomm: Twilight Zine has enough stories! Now we need some more reviews. I will put it together at home, and printing will be done either at Graphic Arts or a professional printing house, depending on the size of the run. Meeting next Wednesday (July 20) to talk about this.

Seth Gordon is going to be Jourcomm after this one. Yay! He's going to get an Athena account, too, so he can take care of it all.

Fweekcomm: we need to think about Rush. Anca volunteers for this since she's got an early return for MITSFS.

Some proposed activities: Hitchhiker's guide, filk and cookies, movies in the MITSFS.

The table for the Midway will be staffed and have some newer books from Mobcomm.

Speaking of which:

Mobcomm: Toby is looking into it.

\goto{Old Business}

There's no business like no business.

Anca: LSC has the slide.

\goto{New Business}

Wait, we're not supposed to talk about real business at these meetings! What have we come to? A discussion ensued about the validity of business conducted at MITSFS meetings. It was decided that since we all showed up, we might as well do some business so we don't have to meet again and will have time to read more books.

Miller Motion: fails.

Second Miller Motion: chickens.

Banana motion: passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Unofficial Meeting Minutes 

Friday, July 15, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes were read for 8 July and 28 April 1994.

M: minutes are very, very, late. 10-0-0 +Spehn.

\goto{Committee Reports}

TZ soon, really. We have lots of stories, some art, an ad. Need more reviews. Seth will take over Jourcomm later.

Mobcomm: Toby is working on it.

Pianocomm: Toby will get to it after Mobcomm. 3 keyholder potentials: Mike Moore, Andrea Humez, Bridget Spitznagel.

Moocomm: show HG during Rush. As PR.

Fweekcomm: Anca. Get apprentices to help. Post schedule for keyholders for Rush, Rush activities, Hitchhiker's Guide, postering, Midway, LSC slide.

\goto{New Business}

Magic MITSFS? Hmm...

Marcus dreams about Newbury comics selling cards.

Chat about English Motions.

\goto{Old Business}

Inventory happened.

M: Miller. Fails.

M: Miller. 3-0-3 +Spehn. Spain wins.

M: turn Jamie into banana and send him after the people who have our missing books. Many-0-few +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}