\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 15, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, Pseudo-President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

*Thunk* I definitely need practice.

A peon from the ranks says "No it's not! That wasn't a real bing." After disposing of his corpse, the meeting continues...

Will the onseck and pseudo-skinner read the minutes? Minutes read.

Motions concerning the minutes?

No one is very concerned about the minutes.

\goto{Committee Reports}

Mobcomm run.

All other committees seem to have disappeared.

\goto{Old Business}

Me: the Astronomer to the Pope is still coming.

Seth: and he's still old.

Jamie: but he's older now- by about a week.

Seth: but the Pope is older than the Astronomer.

Jamie: how old is the Pope?

Seth: probably older than the Astronomer.

The rest of old business gets real old real quick.

\goto{New Business}

Motion to send the IRS a message saying "we don't pay taxes! Nyah, nyah, nyah!" on banana colored paper.

Seth gesticulates wildly.

Paul appears.

Seth: you summoned Paul with the banana colored motion!

We'll have to kill Seth before he can do it again- we wouldn't want two of them.

\goto{Future Business}

Move to kill Seth for summoning Dworkin with a banana colored motion.

Motion passes by pseudo-skinnerial decree so the pseudo-skinner can hit the gavel block while Paul's head is still on it.

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Transcribed with fanatical devotion to the Pope,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
