\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 18, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

M: approve as yellow. Many-some-few +Spehn.

M: approve Marcus as paranoid. Passes.

\goto{Committee Reports}

Unnamedcomm: reads letter original and new, with golf claps.

M: approve John's hands as sniffed. Passes.

Boriscomm: we have a calendar. It's not signed. Marcus screams.

M: commend Boriscomm for a good job.

Who'swhocomm: lamed out. He's not near a phone from 9-5 daytime.

Mobcomm: a run on December 3.

SFWAcomm: there is lots of empty space on the shelves because duplicates have been moved to Damnation Alley.

Innocentcomm: taking interviews for teaching Marcus the way of the banana.

\goto{Old Business}

M: commend Marcus for not making a banana motion. 10-5-0 +Spehn, passes!

\goto{New Business}

New meeting called to order, 1715 SST.

Bunny song.

\vspace{12pt}

\noindent
Meeting adjourned, 1718 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}