\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 9, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

M: no motion concerning the minutes. Passes many-0-1 +Spehn.

Toby's office is now part of the library. Or perhaps...

M: declare Toby's office the Spofford room. 11-4-7 +Spehn.

There is much blaspheming while Marcus discovers the English language fails him.

\goto{Committee Reports}

Pentiumcomm: last week's matrix vote did not include FDIV.

Jourcomm: Finboard sucks. We didn't get money. Perhaps make TZ online mag? Not a good idea but until we can get money...

Alohalenscomm: Andrea is it.

Innocentcomm: Needs some help...

\goto{New Business}

We are missing Taltos by Stephen Brust.

"Wind witch."

Marcus likes his metal gavel. Motions concerning it fail.

M: all banana motions automatically fail (banana motions are interrupted, not fast affected), after a discussion of whether previous motion fails or succeeds.

M: bonk Jay on the head with a banana. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}