\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 21, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Nathan is a gully dwarf (before meeting).

M: bana-motion of some sort. 12-13-3 +Spehn. Few-lots-1 +Spehn.

Minutes read.

M: approve minutes as green. 15-0-6 +Spehn.

\goto{Committee Reports}

Run, a week from Sunday. Meet here 11:30.

M: commend Anca for determination. Passes by skinnerial decree.

Jourcomm: Dale quit. We need a person to sell ads for the new TZ.

Vice wants to see skinner's finger motion.

M: appoint Unnamedcomm (Anca). Have to reply to really hilarious stupid letter (see poster).

M: read letter at next meeting.

\goto{Old Business}

ALGOL. Usual motion, vote, result.

Telzey, telzey, telzey.

M: the world telzey is struck from the minutes.

Discussion of amnesia.

\goto{New Business}

M: bump Jay with a banana. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}