\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 10, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

Heated discussion of minutes.

Motion to put a link [illegible] to Anca. 14-5-1 +Spehn.

Jamie is beaten and abused.

\goto{Committee Reports}

Jourcomm: Marcus promises 2 stories. Rachel's stories. Advertise in Haldeman's class.

M: skinner commended for thinking. Lots-some-few +Spehn.

Jenkins: get him to be our Faculty Advisor?

Haldeman doesn't really care.

Jenkins: give him his own membership?

M: commend the skinner for being powerful.

M: condemn the skinner for being powerful.

M: have a matrix vote.

4-many (20)-3 +Spehn, 20-2-2 +Spehn, 4-10-12 +Spehn. Marcus can count to 20.

LHE calculates. The skinner is power mad.

\goto{Old Business}

T-shirts.

M: put the people concerning into iron maiden t-shirts.

We want half.

Rachel might chew on Sarofim's eraser.

Jesus at bat was really good.

Sherrian was here. Nathan is going to marry her for taxes and house appliances.

M: to throw Old Business in dumpster. 9-6-10 +Spehn.

\goto{New Business}

M: to gag Jay with a banana-colored stapler. 13-6-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}