\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 1, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

Yet another non-existent set of minutes from the quote unquote bastardly onseck.

The onseck tries to wriggle his way out by making a Galbraith motion. Everyone is confused.

Minutes read.

Motion to call the minutes Peruvian-Egyptian. Will they be Peruvian written in Eqyptian, or vice versa? They'll be in Peruvian-Egyptian, written in Peruvian-Egyptian.

\goto{Committee Reports}

Paul is now Pilecomm, the ancient and respected title for the keeper of the list of good SF books (gooddex).

Hasslecomm created. No one knows who it is except certain privileged people, hopefully including Hasslecomm.

\goto{Old Business}

We have a list of old officers which should be updated.

Galbraith motion: use 1/4 of the Society's treasury to take pictures of real spaceships on distant planets.

First meeting of the Society was Friday, March 16, 1951. Motion to make March 16, 1951 a holiday. Motion passes by skinnerial decree.

Where are the comic books? The comic books are in California.

Where is California? In the comic books.

You mean- like the old adventure games where you could put one object inside the other, then the other inside the first, and it would go poof and disappear.

\goto{New Business}

Picniccomm should be inviting an author for May 8.

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1707 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
