\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 9, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1630 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

Move to shut up Marcus. Passes lots-few-0 +Spehn.

Andrea wants to expunge Marcus' innocence.

\goto{Committee Reports}

Boriscomm has been created (Erin appointed).

Time warp to before meeting:

Boriscomm buys new calendar; not to be by Boris.

Timewarp to meeting.

Motion by Innocentcomm to fix skinner. Passes unanimously.

Plug for Jourcomm.

Motion to suppress Jay with paper bag. No second. Box is used instead. Move to define previous motion as "Boxer Rebellion."

Motion to exclude neutronium from library. Passes.

\goto{Old Business}

Motion to be nice to the skinner. Fails.

Motion to invert skinner. Fails 20-7-0 +Spehn (skinnerial falsitude).

Asimov is still dead.

Comic books are in California.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}