\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 23, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read and debated.

Motion to omit references to Telzeycomm. No second.

Motion to omit references to Telzeycomm so that they will appear in this week's minutes. 4-0-7 +Spehn.

\goto{Committee Reports}

There are committees.

Theftcomm: still nothing stolen by Theftcomm- any ideas for replacing posters?

Motion to appoint Anca to do poster. Lots-1-2 +Spehn.

Alohalenscomm: if Andrea's role gets done, there will be photos.

Toby shown Vice paraphernalia.

Motion to condemn skinner for not properly instructing vice.

Pianocomm: Andrew is a piano.

\goto{Old Business}

Toby and Kevin are old.

\goto{New Business}

Motion to hear Ingrid's story. Lots-3-1 +Spehn.

Story: Sat, PM- Jay tells Ingrid to tell Marcus he has a Telzey. Sun, AM- Ingrid asks Eric what Telzey is, has it explained. Ingrid asks Marcus to see him blush- he refuses.

Discussion degenerates.

Motion to pass motion without bananas. 13-12-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1719 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}