\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 7, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

M: commend Anca for legible minutes. Lots-4-1 +Spehn.

\goto{Committee Reports}

Theftcomm: mail soon.

Boriscomm: calendar before January.

513comm is here. Check back of Quik boxes. Bananas taste interesting rolled in strawberry Quik powder.

Onseck had to go to the bathroom. She'll be right back.

She switches to a new pen.

\goto{Old Business}

Toby- he's only 25.

Mock his quarter-century. Toby strips off his bowtie and wears funny headthing.

Print lore out.

\goto{New Business}

LHE has Swaggers, the velveteen banana.

M: commend J for paternal instincts.

M: mock him for being cute.

M: mock him for being insufferably cute.

11-8-11 +Spehn, 20-0-5 +Spehn, 16-16-3 +Spehn, passes!

We got 425 dollars from Finboard.

M: work Finboard over with banana. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}