\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 2, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

Time warp and finger motion definition.

M: minutes kinder and gentler. 12-8-1 +Spehn.

\goto{Committee Reports}

Jourcomm: TZ is here.

Marcus is embarassed by Circlet Press. Books will be in special reserve.

Hasslecomm: successful experiments with slave labor. Dave Kern was requisitioned.

M: meeting worked. Passes by skinnerial decree.

Skinner's mother came in, took pictures.

Moocomm: Jurassic Park at LSC on Thursday.

M: form Innocentcomm to look into CP. Lots-none-1 +Spehn.

M: take a picture of Jay in a suit. Passes by skinnerial decree.

Analogcomm: not until students have time.

\goto{Old Business}

It's getting older.

\goto{New Business}

A description of new writer's group. 6-8 core group. Write-in?

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}