\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 17, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosiov, Onseck, recording.

Minutes read.

Discussion of minutes as always. And recursiveness.

M: approve minutes as yellow. Lots-none-few +Spehn.

\goto{Committee Reports}

SIPB is developing its own Spain. Spehn.

Titledex is being printed, look in mitsfs/dex/rites.dex.

Pinkdex is printed.

Jourcomm: "My memory banks contain no better memory than logging in." (Marcus)

Does Marcus exist when he's not logged in?

\goto{Old Business}

OJ Simpson is a murder suspect.

The skinner gets off on being mentally unbalanced.

Marcus exercises his power and shoots down motion of being mentally unbalanced.

Onseck writes down anything she wants.

Jamie is power mad...

Magic cards are traded.

The librarian made a pass at Jesus.

\goto{New Business}

"Was I drunk again?" (MS)

(Censored discussion.)

Motion to violate harassment policy with a banana. Many-few-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosiov, Onseck}

\end{document}