\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 29, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding for the second to last time; the onseck is not here, but he has left minutes.

Minutes read.

Any motions concerning the minutes, which exist, even though the onseck does not (ed. note: I object to not existing, by the way).

\goto{Committee Reports}

Picniccomm: report.

Neel: invitations have been sent out.

Jamie: Yay- at long overdue last. Do you have a car? 

Neel: No.

Jamie: send email to keyholders saying that Picniccomm needs a car. Do not just sit and wait for a car to materialize. If there is no food at the picnic, we will kill you.

\goto{Old Business}

Jamie: Guy has indeed arrived, and he is old.

Neel: older than the pope?

Jamie: I haven't asked.

Chris: he didn't look older than the pope.

Jamie: anyone want to try to go through the old business Algol?

Long, long pause.

\goto{Future Business}

Motion to use a banana to end the meeting so we don't have to sit here anymore.

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Transcribed with almost fanatical devotion to the Pope, for the last time, with many fond farewells,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
