\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 8, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, President and Skinner, presiding; Marcus Sarofim, Onseck, recording.

The Onseck has minutes for once.

Minutes read. Comments made about what cream to use to get rid of pilecomms.

Motion to put the minutes inside themselves passes.

\goto{Committee Reports}

Neil: send out letter to Hal Clements ASAP. Picnic May 8th.

Motion to condemn Picniccomm for using EZ passes by skinnerial decree.

Power corrupts. Absolute power is kind of neat.

Skinner declares that this joke is funny.

Mobcomm run Tuesday at 10 AM.

Debtcomm: we'll be paying off our debts soon!

Pianocomm: new set of keyholder notes! Keyholders know what to do with them.

Consideration of making a Dworkincomm to thwart Paul. Society thinks better of it.

\goto{Old Business}

Isaac Asimov is not alive, but his body is missing. They dug lots of holes, and he wasn't in any of them.

Really old skinner is coming. He is Astronomer to the Pope.

The Pope told Hawking it was okay to study everything after Creation, but not the moment of Creation, because that was God's handiwork. Unfortunately, Hawking had just given a talk hypothesizing that there was no Creation.

Someone made a pulse at Wisowaty and was replaced. Oops.

\goto{New Business}

Xconq? No, there's only one terminal here and it's dialup!

\goto{Future Business}

Motion to stick a banana somewhere passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus Sarofim, Onseck}

\end{document}
