\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 3, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Some people were there. (Marcus, Anca, "Y", Thark and Geordi?)

Minutes from the last meeting were not read because there wasn't one. Anca missed the meeting before that and all the tapes aren't labeled, so we don't have those either. Bummer. Anca promises to get on the ball about it.

\goto{Committee Reports}

Jourcomm: give me TZ submissions. You get 1 dollar of fine credit for the ones I print, or 2 dollars if it's really good. Seth is teaching a writing course this summer; we might get some stories from there.

\goto{Old Business}

(This is sorted out from all the other stuff that happened so that the minutes, at least, can look organized. Hah!)

T-shirts: they are not to be found. Mail was sent to rcaileff (Rachel Caileff, APO Rep) and dbwilson (Dave Wilson- who was supposed to be in charge).

LSC slide: the design will be the same as on the shirts and will advertise the shirts and MITSFS. Will get done "soon." Money should go to LSC as Anca is broke and can't cover lots of things that need to be reimbursed.

\goto{New Business}

The usual motion.

Go see "City Slickers II" for free at LSC later this evening. It's not sci-fi, but what the heck.

\goto{Future Business}

The skinner passes various motions by skinnerial decree, but they are deleted from the minutes due to embarrassing nature. Aww!

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST. Bam.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}
