\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 2, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

LHE doesn't put down camera.

Minutes read.

M: commend skinner as banana-colored. Not enough-enough-superfluous +Spehn, fails.

Skinner recommends Kevin and Andrea read Weird Tales from Shakespeare.

\goto{Committee Reports}

Mobcomm: tomorrow, 10:00.

Pianocomm: Bridget is piano.

Pictures taken.

Digression- books need to be covered, small press.

Bunny song attempt- Marcus presses on.

\goto{Old Business}

Newt Gingrich is writing an SF book.

Marcus attempts to press Innocentcomm.

\goto{New Business}

Matrix vote: commend Marcus for blushing, Marcus is banana-colored, have a matrix vote.

Skinner: "I do not blush yellow." Vice: "You blush chablis."

Neel declares answer "4 and therefore positive."

Meeting is over, but during calculation, Vice creates Pentiumcomm to calculate matrix votes and appoints Neel.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}