\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 16, 1994

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

Motion to approve minutes as non-simply connected. Lots-7-3 +Spehn.

\goto{Committee Reports}

Theftcomm is to timewarp back to summer to arrange for drop poster.

Move to reserve space for drop poster for rush.

Motion to reserve Marcus for 5 years from today. Skinner will become circulating in a few weeks.

Motion to reserve Marcus for remedial Telseying by Innocentcomm in 5 years. Passes.

Neel has been defined as a piano. He will be fined for losing 87 of 88 keys.

Telseycomm reports that incriminating pictures of skinner have not been processed due to legal difficulties.

\goto{Old Business}

Move to condemn skinner on general principles. Lots-3-6 +Spehn. Inverse skinner rule applied; skinner commended for very specific reasons, or skinner condemned for having principles.

Skinner discusses clingy stiff metal bottlesuits for women.

\goto{New Business}

Motion to define Jay as speaking banana. Passes 17-12-2 +Spehn; 13 people present.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}