\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Carissa Skye, President and Skinner}
\newcommand{\onseck}{Rachael Skye, Onseck}
\newcommand{\meetingdate}{Friday, 04 27, 2018 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.3 Ksec SST,
\skinner, presiding; \onseck, recording.

Meeting... The opposite of adjourned! Commenced!

Minutes read.

\bing

\goto{Committee Reports}

\subsection*{Mancinicomm}
We got a massive Russian et al donation. Mancinicomm will go to work.

\subsection*{Picniccomm}
The picnic is happening:
By Skinerrial decree, the word picnic only has one c from here on out.

\subsection*{Smilescomm}
Bubbling is still ongoing.

\goto{Old Business}

We had a midway! It went well.

\goto{New Business}

\subsection*{Onseck}

Nominations:
Eileen Hu
Nestor-13
Fast Typing
The Jumpstart Typing Game Series

Votes counted. Eileen Hu (TA) wins and is declared onseck.

\subsection*{LHE}

Nominations:
Loch Lamora
Nolan Reilly
Kelsey Glover
Nestor-13
Mr. Poe

Votes counted. Kelsey Glover (KRG) wins and is declared LHE.

\subsection*{Vice}

Nominations:
Nestor-13: A Virtuous Pagan
Matthew Suazo: Pride
Wrath: Wrath
Ling: Greed
Rick Sanchez: Pride And Prejudice

Votes counted. Nestor-13 wins in a landslide! He is asked whether he would like to be vice. He beeps sadly (he is out of battery). Skinner acts as interpreter and says he says he will defer. Wrath: Wrath is runner-up. He is immediately brought up before Skinner for fighting in the library and forever banned.

Let it be known that Wrath is banned from the library!

Runner-runner up is Matthew Suazo (MJS). He agrees to embody the Vice of Pride. He is declared Vice.

\subsection*{President}

Nominations:
Carissa Skye
Nicole Thumma
Eleanor Graham
The President
Armin Thamzarian
Khazagoth the Nefarious, Lord of Cicadas
Joe Biden
Michelle Obama
Winnie ille Pooh

Votes counted. Eleanor Graham (LG) wins and is declared President.
President is asked to appoint a Skinner.
LG appoints LG to Skinner.

\goto{Future Business}

Declaration: In the future there will be kittens. RW informs us that the first Saturday (Caturday) of every month, there are kittens in the Boston Commons.

Motion that all bananas must be boneless or they are not bananas.
Seconded.
Votes counted.
32-1-2\ps
Motion passes! Meeting adjourned.

\bing
\noindent
Meeting adjourned, 69.5 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
