\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Carissa Skye, President and Skinner}
\newcommand{\onseck}{Rachael Skye, Onseck}
\newcommand{\meetingdate}{Friday, March 09, 2018 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.9 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

Subsequent scream from onseck.

Note a stuffed beaver squeaky toy is present.

\goto{Committee Reports}
\subsection{Smilescomm} 
There's a rolling bookshelf at the C's of the L's, and we could switch it out with the Y-Z shelf of the L's based on depths to get about 2 inches of extra clearance. Onseck agrees but is dubious about lost space in the back room. We will email keyholders and gather thoughts, for potential proceedings next week.

Onseck, in proxy for Analogcomm, reminds keyholders to remove hours if they are leaving for spring break.

Beaver squeaks.

\subsection{Niagara}
we're paying More Than Words to come get books in the next couple of weeks. We have at least 20 boxes.

Skinner: Nobody wants to be picniccomm so I'm appointing myself. Picnic will happen near the end of April.

\subsection{Picniccomm}
 is created.

\goto{Old Business}

Bubbling ongoes. Good job smilescomm.

Search for stores that haven't been bought out of bookshelves continues.

Inventory will probably happen over the summer.

\goto{New Business}

Hbarcomm: Gaming day sometime in the next two months.

Jourcomm exists!

\goto{Future Business}

Convince everyone to run for starchamber.

Contact star-chamber if you're interested!

Skinner declares the beaver cute.

\goto{MetaFuture Business}

The New York Times says that, in the short term, we probably won't die in a fiery apocalyptic wasteland.

Beaver squeaks.

Motion declared that the gavel be turned into a bannana.
Seconded.
12-6-11 \ps

Motion passes.

\bing
\noindent
Meeting adjourned, 67.1 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
