\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Eleanor Graham, President and Skinner}
\newcommand{\onseck}{Eileen Hu, Onseck}
\newcommand{\meetingdate}{Friday, September 7, 2018 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.34 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing
\goto{Past Business}
the summer happened \\
the star went out and the stars came back \\
the midway happened, CS thanks people for coming \\
we have lots of new books! \\

\bing

Skinner: decrees that we bing between each section

\goto{Current Business}

\goto{break for explanations to the fresh meat}
the star chamber looks down on everyone menacingly, burning at thousands of degrees \\
keyholders hold keys \\
prentices can escape from the black hole of prenticeship \\

\goto {Current Business again}
important business, we need to deal with the genre squid. The Skinner and the Lady High Embezzler present the genre squid. people propose sticking it on the ceiling. people propose putting it above the guide to navigating npr’s top 100 sf and fantasy books \\
vote to hang the genre squid \\
motion to find command hooks and hang up the genre squid “thereish” \\
motion seconded \\
vote is 17-3-7 \\
motion passes \\
also, a plea: if anyone knows where it came from please let us know, it mysteriously appeared one day and all email documentation as disappeared \\
motion ended \\
Skinner likes the hardware store \\
XDL expresses disdain for having so many people in the library during their hours \\
analogcomm is an immortal vampire probably \\

Niagaracomm: will contact more than words to deal with all the niagaracomm boxes \\
Dragoncomm: can show off the hoard to new frosh if they want to see it \\

tour of library! after the meeting \\
\bing

\goto{Future Business}
maybe we should restart the zine (Twilight zine), talk to the writing science fiction teacher
all frosh are stars to us \\
we’ll be putting in a new order for psiphi tshirts soon \\
note about bookshelves: we got 2 new oddly sized bookshelves from the son carrying on his honored father’s work \\
KD pubs a musical \\

a motion related to bananas: bring real bananas here and let us eat them except for XDL \\
motion seconded \\
15-5-8\ps \\
motion passes \\
\bing
\noindent
Meeting adjourned, 66.54 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
