\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 15, 1967

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Minutes accepted as green for once.

Treasurer: about 1400 dollars.

Minicult (Pres): letter from Louisiana State University asked for index.

M (Seitz): plant be censured for turning yellow.

Minicult (Ward): F.P. Songbook going out of print.

Libcomm: Star Book Store expedition, Galaxy, Amazing, some donations, futile plea for help (new checkouts).

Moocomm: S. Loeb (to be).

LSCcomm: treasurer slept through LSC meeting.

Free moris (?).

Motion to condemn Seitz. Amendment- to censure (accepted). 4-3-5 +Spehn (3-4-5 +Spehn right vote, Javier's hand not congruent).

Jerkcomm: TZ "real soon now."

Tuition rioters led by Dean of Students in caroling.

Motion to fill HoJo's card with pistachio ice cream.

Motion to commend chairs on gallantry and victory- 4-5-1 +Spehn.

Minicult (Pres): King of Greece in Buffalo last year- restaurateur looked at king as maitre d'.

Motion that Society move. 1-30-69 +Spehn.

Minicult (Ward): Will MITSFS be kicked out of Student Center?

Minicult (Seitz): R&R bands at Avatar benefit, 1200 watt amplifier.

Pseudo-pseudo-Theftcomm: poster on bulletin board.

Can we convince Finboard of Pierre's disappearance? F.P.- no letters.

OB Algol.

ARL- Toff photos.

M: above into Algol, 5-3-8 +Spehn.

Minicult: all whites for Hicks and vice versa.

Minicult: Hancock Tower.

Minicult (Treas): Urban Redevelopment, equivalent to city of 600,000 destroyed.

Minicult (Seitz): Troy, NY- massive program. 3/4 mile parking lot- more spaces than cars. Buffalo- bodies, safes, cars found.

M (Seitz): F. Lloyd Wright- "Burn it down and start over." 6-1-1 +Spehn.

Cochran: Walker Squash Courts (Pumpkincomm).

Minicult (Pres): McCarthy Committee- Bailey letter should support Johnson.

Minicult (Seldin): life created- duplicated work of Quaker oats.

Mini-reminder: last day for cancellation.

Seitz- NY Times- cyanide gases in aircraft, etc. "Cyanides... include oxygen, nitrogen, etc. and in the case of hydrogen cyanide contain hydrogen."

Miller- 10-1-n +Spehn.

Motion that chairman eat banana.

Miller- 6-5-7 +Spehn.

Miller- 10-2-3 +Spehn.

\vspace{12pt}

\centerline{David S. Cunningham, Onseck}

\end{document}