\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes 

Friday, April 28, 1967

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5 o'clock Society time; the real world was 8 minutes fast.

Since the Onseck was not present, the minutes were approved as not read.

The Treasurer was not present.

\goto{Committee Reports}

Libcomm: We can obtain Weird Tales for 200 dollars. This would seem to be a bargain, since we've been offered one issue for 30 dollars. The Skinner-Libcomm asked for discussion on whether we should buy Weird Tales or bind things we have. "Witches of Karres" has been returned, sundry things have come in. Some nut suggested we buy Italian SF. (The Acting Secretary hereby apologizes for not getting people's names; please claim your statements if you feel so inclined.)

Picniccomm: Money will be required next week.

Moocomm: Further reports will be in calculus. We will be showing a movie the first Monday of reading period (I know that doesn't make sense, but that's what I have down) in 26-100. Volunteers are requested for ticket-taking and other random duties. We should make 50 dollars, maybe. (We are a semi-pseudo-official LSC production.) It has not yet been decided what movie will be shown.

Coffincomm: Wrote to what's-his-name in Austin.

Libcomm continued: We are receiving Italian fanzines (free). 150 volumes are being sent out to be bound.

\goto{Old Business}

Old Business Algol: Phillies mentioned the Trans-Oceanic Fan Fund; the membership did not show much interest.

\goto{New Business}

M (Udin): Miller. Failed 1-2-3 +Spehn.

Minicult (Phillies): Elevators are the safest form of transport per million passenger miles. This was discussed at ridiculous length.

The validity of man hours per square foot per week as a measure of Library usage was questioned.

M: that we have bananas at the picnic. Failed 4-4+infinity-2 +Spehn. (The tie was broken by the Skinner.)

M: that we have selected rotten green peppers at the picnic.

M: that we not have bananas at the picnic. Failed 4-18-2 +Spehn.

Leslie entered.

Jourcomm: Progress is being made, but not much.

M (Udin): Miller. Passed 5-4-2 +Spehn.

The meeting was adjourned at approximately 5:30.

\vspace{12pt}

\centerline{Respectfully submitted,}
\centerline{Fuzzy Pink [Wisowaty]}

\end{document}