\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 1, 1967

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
5:05 pm, minutes of last week not here.

Libcomm: there are books in the library. New Vance Ro- Core Palace- in Coop. New Analog, F+SF.

Pres- conference on getting money from Finboard (1250 dollars).

Jourcomm: TZ marching on.

Libcomm: new cover on Pinkdex.

Moocomm: LSC has free movie.

Minicult (Y): 1967 Nuclear Science Abstracts- control of diseases in chimeras, examining handling of radioactive cadavers, laser effects on black widow spiders, also article on gleeps.

Seitz- (Filthy motion in Latin- I conjure you, Sword of Swords, etc.) 7-1-11 +Spehn.

Minicult: TEN giving directions on transmuting.

Minicult (Cochran): last night- [illegible] on TV- questions and answers. One of questioners Gerald Clarke.

Item, Seitz- Bethlehem Steel has porcupine processor.

Avatar proclaimed by mayor to be obscene- gave away 2000 free copies.

NASA cutting back 5 percent of jobs. Globe says "Why duplicate Russian research?"

OBALGOL-

ARL- Star Trek pictures for Toff.

New Business:

Motion (Y) to limit memberships to 10,000 persons. (No second heard (sic).)

Seitz- does library want a loan of Dict. of Angels?

Motion to censure Treasurer for not being here. 12-3-3 +Spehn.

Motion (Wiener) to raise limit on members to 20,000. (Debate, since 17 is largest finite number.)

Seitz- greater plant is ill.

ARL- moon is broke- down to last quarter.

Motion (Wiener): can we put a limit on non-members? 10-6-4 +Spehn.

(N.B.- Treasury had better grow by 4.5-dollar bill. SOON.)

Miller. 7-8-2 +Spehn.

Miller. 8-10-3 +Spehn.

Move not to adjourn. -3-3-3 +Spehn. Vote chickens.

Adjourned, 5:40 pm.

\vspace{12pt}

\centerline{David S. Cunningham, Onseck}

\end{document}