\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 8, 1967

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Minutes of 2 weeks ago read by Treasurer. Minutes accepted as read.

Libcomm: finite probability of existence, Lovecraft paperback "Color Out of Space," eventually Treasurer will pay book club.

Pres: Non-shelved returned books are frowned upon. Conversation with Finboard (Bruce Enders): 930 binding, 275 shelves, 200 acquisitions.

Treasurer: Vergeltungsflotte should try to get the 14.5 billion dollars. TZA tried to recharge us 400 dollars for bills.

Minicult (Treasurer): last week, Boston Public Library got permission to photograph Boston Sunday Advertiser (Flash Gordon).

Minicult (Pres): 2150 is (98 percent confidence) 100/100 damn much.

Jourcomm lives.

Pseudo-Theftcomm: poster half-life (Appleby) about 1 day. Treasurer running for LSC treasurer.

Wiener: Treasurer not thrown into showers on birthday. Treasurer should pay [illegible] out of 4.50 bill.

Moocomm: AudioVisual retrenching from Student Center- now next to Light Bulb Farm.

Index- idiot wrote letter complaining about mistakes and abbreviations.

OBALGOL.

ARL: Toff photos.

Treasurer: books in print. Hastings only had 4 Prime Valiant books.

Motion to censure treasurer for being here. 11-7-8 +Spehn.

Picniccomm: dead.

Banana. Died.

New Business:

Minicult (Treasurer): I have several. Taking Flash Gordon photos- Russian camera. Uses m synch for strobe, x for flash.

Motion (Ross) to congratulate president of France for his gall. Pres- recent phone call. Wilson planning to tour British Empire. De Gaulle to meet Wilson at Dover. Air or ferry? No, I'll walk. Amendment (Treasurer): that it be suggested that Seldin hit Phillies. OUT OF ORDER. Amendment (Treasurer): to add above to out of order (Phillies threatened Treasurer). Amendment (Ross): to recommend that Phillies hit Treasurer. 5-5-17 +Spehn.

Banana, died.

Miller, ignored.

Miller. Amendment (Seldin): to add banana. 1-6-1 +Spehn. Amendment (Wiener): to amend the prior amendment by inserting Miller motion. 1-3-2 +Spehn.

Motion to repeal law of gravity. (Seldin: Banana motion was split.) Amendment (Wiener, accepted): to exclude bananas. 18-17-19 +Spehn.

5:45 pm.

\vspace{12pt}

\centerline{David S. Cunningham, Onseck}

\end{document}