\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 7, 1967

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
5:12 pm.

\goto{Committee Reports}

Treasurer: circa 12 1/2 hundred dollars.

Libcomm: the new Analog hasn't come in.

Minicult (Tony): Fuzzy Pink is pregnant.

Fuzzy: What?

Tony: Aren't you?

Fuzzy: NO.

Tony: Thank God.

Phillies decided what colors to bind the new magazines in.

Jourcomm shrugged its shoulders.

Picniccomm: the picnic will be May 14.

\goto{Old Business}

Minicult (Leslie): The N3F has given Alma Hill the Kaymar Award.

Seitz: We really [illegible] use the Italian finz for barbecue fuel at the picnic.

Tony: And you know what we could cook over them- Seitz!

Phillies: r log- ignored.

\goto{New Business}

Ward: donate George Phillies to the Babson gravities research foundation.

Cory: move the sentence- George Phillies moved to repeal the law of gravity and was ignored- be inserted in OBA. Discussion- bah. 5-2-8 +Spehn.

Moved- any Phillies-gravity motion be equivalent to a banana motion.

Seitz: move to censure Sir Isaac Newton for starting this nonsense. Ignored.

Truman: I'm resigning.

It was suggested we think about showing movies again- (enter Pumpkincomm) we still have time to do it during reading period.

Pumpkincomm: pumpkins have no known psychedelic properties.

Minicult (Phillies): last week I made a suggestion Mike Ward write a Tom Swift book- I now think it should be entitled Tom Swift and His Electric Electric Pumpkin Incubation.

Tony: Talk about all such devices- make it an Elocutic Electric Electric...

Ward: And I'll put it in reversal typefaces- an Electric Eclectic...

Miller- 3-7-3 +Spehn.

Harter: But squash is somewhat different.

Seitz: What is located at 17 Hancock Street, Boston?

Phillies: The people who tried to hex my plane just managed to tag in Buffalo.

People talked about Islip and Iceland.

Miller- 6-4-6 +Spehn, motion chickened.

Minicult (Phillies): The Lost in Space script will be published in QRM.

Harter: Scientific American is printing filthy pictures.

Ward: Propose we depart Pierre to Iceland.

Miller- 6-5-5 +Spehn.

Adjourned, 5:42 pm.

\vspace{12pt}

\centerline{Cory Seidman, Onseck}

\end{document}