\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING
\newcommand{\skinner}{Cathleen Nalezyty, President and Skinner}
\newcommand{\onseck}{Lee Fuchs, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, 22 April, 2016}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST, \\
\skinner, presiding; \onseck, recording.

No meeting has been held in some time.  No minutes read.

\bing

\goto{Committee Reports}
\subsection*{RealAuthorsComm}
Work is happening! John Chu will visit us in fall (details to be determined) and Max Gladstone and Gwenda Bond emailed about possible visits over the summer. Exciting!

\subsection*{Picniccomm}
Picnic is happening, 10am, including the committee members
No, Tristan is not allowed to set a fire. No burning down the forest, that would be bad. Maybe a Zippo lighter or a match.

\subsection*{Pseudo-JourComm}
TZ is happening! Deadline is July 15! Emails will be sent to writing professors and classes. People should write things! Picniccomm should write a report

\goto{Old Business}
We got a ton of new Keyholders! YAY. Normal shenanigans.

CPW happened and we gave lots of books to pre-frosh. It was fun!

\goto{Current Business}
ELECTIONS!

\subsection*{Onseck}
\begin{itemize}
\item Tristan (TM) - Official Candidate
\item Alfred the Butler
\item Azrael, Angel of Death
\item Metatron (as appears in His Dark Materials)
\end{itemize}

Tristan wins with 7.98 votes!

\subsection*{LHE}
\begin{itemize}
\item Prime Minister of Iceland
\item Former Prime Minister of Italy
\item Carissa (CS) - Official Candidate
\item Moist von Lipwig
\item Sin of Greed
\item Lucas Fehrwright
\item Locke Lamora
\end{itemize}

Moist von Lipwig wins with 6 votes, and Carissa with 3.55 votes will act as his assistant!

Motion for brief moment of silence in honor of Sir Terry Pratchett goes uncontested and is summarily observed.

\subsection*{Vice}
\begin{itemize}
\item Harriet (HL) - Official Candidate
\item Harriet Tubman
\item Harriet the Spy
\item Harry Potter
\item Gluttony
\item Wrath
\item Andrew Jackson
\end{itemize}

Harriet is elected! Which Harriet is unclear.
Harriet the Keyholder's chosen Vice is Sloth (for not being here).
Harriet Tubman's is Wrath.
Harriet the Spy's is Pride.

So we will be particularly full of Vice this year

\subsection*{President}
\begin{itemize}
\item Donald Trump
\item Conrad Sanders
\item Matthew Davis
\item The Presidential Office
\item President Raif
\item Miles Naismith
\item Havelock Vetinari
\end{itemize}

In a surprise upset, write-in nominee Rachel Skye wins.

Onseck motions that if the keyholders do not settle down she reserves the right to shove bananas down her throat
Motion passes Some Number Greater Than The Other Two to 7 to 2 plus Spehn.

\bing
\noindent
Meeting adjourned 64.76 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
