\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachel Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, November 11, 2016}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection*{Mommycomm}
Mommycomm is going to start moving away from existing solely in Athena lockers due to high loss in institutional memory. Hours will tentatively be recorded on Google Drive, perhaps to be changed in the future.
The So You Want To Be A Keyholder Document has been updated to reflect current practices. Main changes are that members can be keyed during their first term, mommycomm gains the ability to add prentices, and the requirements to become a Keyholder are specified as needing to work for 10 hours doing things that account for at least three different kinds of library work.
In response to concerns about members being keyed, in general Star Chamber will key members in their first term but won't start holding hours until the next term barring exceptional circumstances.
Mommycomm requests that more work parties have food so more people will want to come, say if we can confirm at least 4 prentices are coming then we get food.

Motion to have new So you Want to Be a Keyholder in Entirety 
seconded
8-1-4
Motion Passes

 \subsection*{Seldoncomm}
Seldoncomm is trying to be up and running again. TM will be organizing a Mystery Science Theater 3000 showing to increase interest in MITSFS. Seldoncomm would like to be able to get some amount of money to provide food at this event to increase input, and TM thinks large social events like this should be bcc'd to increase turnout and interest in the library.

Motion for  Seldoncomm, Hbarrcomm, and Mommycomm  to be able to spend less than fifty dollars on a particular event.
Seconded
6-1-4
Motion Passes

LHE will send out reimbursement instructions some time soon. It will probably be placed where the TIF was previously. If you want to hold a work party and think it would benefit from free food, let Star Chamber know.

\subsection*{Niagracomm}
Niagracomm is talking to some people about book donation. In addition, niagracomm is attempting to contact a prison book donation program to see if they will accept many many boxes of books. We will think about how to transport the book to the donation center after we confirm they will take the books.

\subsection*{Hbarrcomm}
We need to get   a few sentences for why it is important MITSFS be accessable to the rest of campus.  If anyone wants to contact hbarrcomm with a few sentences along these lines that would be good.
Hbarrcomm is also holding a party on Saturday, December 4, people should come.

\subsection*{Star Chamber}
Star Chamber will be reorganizing committees later in the year, taking stock of which are still active, which are not but should be, and which should be officially dissolved.

\subsection*{IT from Albania}
The Psi-Phi computer needs a new hardrive. An outsider from the strange land of SIPB within Albania has agreed to fix the problem and put athena on the new hardrive.

\subsection*{Mobbcomm}
Mobcomm needs to buy a new hardrive for this to happen

\goto{Old Business}

\goto{New Business}

\goto{Future Business}

Motion to stick bananas in the air conditioner so the library smells like banana.
Seconded
6-2-2
Motion Passes

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
