\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachel Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, September 16, 2016}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection*{Star Chamber}
Star Chamber rewrote many Keynotes. 99 percent of changes were cosmetic, for example reflecting we no longer have a warehouse. Will send out status report later.

\subsection*{Mobcomm}
Mobcomm has a lot of new books. As soon as the fall budget comes in we will have more. Budget form will be sent in this weekend.

\subsection*{Hbarrcomm}
Hbarrcomm speaking to library representatives for official MIT Libraries.

\goto{Old Business}
Star Trek 50th aniversity

Motion to celebrate with bananas and brownies. Seconded. 
12 for no against no chickens

\goto{New Business}
New family albums we will try to update. Proposed creation of new committee to deal with albums. We have too many committees already. Can we have a committee consolidation committee? Albumcomm, Scrapcomm

Motion to name new committee  Scrapcomm
PASSES 6-2-7\ps
New committee named Scrapcomm will deal with albums.

Theftcomm being changed, changing punting deadline to before 1 week from before 2 weeks. TIF will now automatically update itself through sensor telling when libary door is closed. Issue of the privacy of the system, stems from question of using initials or kerberos. Kerberos convenient to contact people, many feel initial system provides uneccessary barriar to keyholders knowing each other. Concern is that kerberos causes lack in privacy. Due to many objections, will not be mandating a listing by kerberos. Most recent proposal says initials will now allow up to 8 characters rather than 3, so people can use kerberos but are not required to. Anything acceptable so long as it is unique to the keyholder. 

PW If people had more recognizable identifiers it would improve communication.
CS Encourage people to switch to kerberos or recognizable name, but don't mandate.
RS Would like to have a unified system, as having initials can make people feel a kinship to the library.
PW Searching for people won't map to them. 
CS Other privacy issues should be resolved by if you want to stick to your initials you can, opt in system.
PW We are a service organization and sometimes sketchy people show up, we have to deal with that.

Emailing the skinner will allow anyone to get their identifier changed. No manditated change at this time.

What should our motivators be in the new theftcomm? Any posting of a graph should be a subtle form of public approval/shaming. Some concern that if the TIF doesn't exist what will motivaiton be like. For now we will put the door up and just see what the results are. Replace graph with a prettier graph replaced every two months.

Official goals of the new Theftcomm system:
Reduce amount of effort Keyholders have to put into dealing with theftcomm. 
Try to keep the library open when we promise it will be as often as possible.
Reduce the work Theftcomm does.

If a keyholder leaves for 5 minutes to go to bathroom, data will show that hours were not held for that time. Star Chamber will overlook if over the course of a year keyholders miss something like an hour and thirty five minutes as a result of this.


\goto{Future Business}
What will the physical representation of the TIF be?

In the future we will have more books. Maybe we will have a credit card. Maybe it will be banana colored.

Motion to take all our banana books and put them in banana space and get new ones from L space.
Seconded.
10-1.5-7\ps
10 for
1.5 against
6 Chickens

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
