\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachel Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, April 29, 2016}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection*{OokComm}
Website is ready to go live after one more walk over. Have a new monitor and everything necessary for a door sensor. Haven't yet figured out way to set up electronic schedule for space in the infinite. Keys need to be found, can use guild's. If anyone has a clever way to run power to the infinite display that would be good. Door schedule expected to have lots of bugs.


\goto{Old Business}
Picniccomm should write a report. Other committees should write reports as well.

\goto{New Business}
Purge party is tomorrow. In the future we will hopefully get rid of the tif, since the schedule will be electronic and we'll have records of when the library and doors are open.

Motion that we recognize that our policies are unfair towards those with fewer than four limbs, and unecessarily large amounts of power to those with many.
Motion to white ballot, seconded.
PASSES

Motion that bananas are yellow again. No second.

Motion all banana groceries be sent directly to MITSFS. Seconded.
3 For
9003 Against
1 Chickens
FAILS 3-9003-1/ps

Skinnarial Dictation that all banana groceries be sent directly to MITSFS.


\goto{Future Business}

\bing
\noindent
Meeting adjourned, 68.04 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
