\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachel Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, October 28, 2016}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection*{Hasslecomm}
Hasslecomm did a ton of books

\subsection*{Theftcomm}
Theftcomm has officially implimented changes to TIF. PW will stop paying attention to theftcomm.

\subsection*{Hbarcomm}
Hbarcomm negotiations with MIT libraries are continuing, they apparently already have some access to our system so may be less effort than we thought. 
Everyone come to see Over the Garden Wall October 31 2016.
On MIT interactive map page MITSFS not listed on being on this building. Would be good to do this.

\subsection*{The Special Committee Which is PW and RS}
Initial rewrite of Keyholder notes has been submitted. Mostly shortening stuff and getting rid ofoutddated language, like no LARPing in the library. Looking at compiled things a few things may want to change. Goal to get renewals and membership section to one page. Also would be nice to add membership rates somewhere easier for keyholders to see. Apparently greendex rites are their own thing? Worth looking into if they can be compiled together. 

\subsection*{Ookcomm}
Are we still putting books on hold? Unclear if this is a thing that exists. This is a question for ookcomm. Present members do not know about that function if it exists at present.

\goto{Old Business}
Good.

\goto{New Business}
Jo Walton is coming into town on Halloween night from 4-6pm.

\goto{Future Business}
We should do the things on our committee reports. Expect to have small but functional quantum computers. We should go to Mars. 

Motion to have Onseck control color of bananas. Seconded.
Motion for previous motion to be vetoed by the Skinner. Seconded.
Motion for bananas to be considered vegetables. Seconded.

Matrix Vote
10000-0-0
0-1-0
0-0-1
Determinant 10000, all motions pass. Bananas are now vegetables, and in addition Onseck has the ability to control what colors bananas are with constant objection by Skinner.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
