\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 25, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to go with the minutes' suggestion and wish Katie a Happy Birthday passes 20-0-1+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Rearranging Deck Chairs on the Titanic}

KCR made a half-height bookcase.

With the P's additionally on top of the bookshelves they are now in danger of rainstorms

\subsection*{Hasslecomm}

Hasslecomm books now need to go first through Panthercomm now to get tagged.

Katie grimaces.

\subsection*{Libcomm}

Libcomm would like to report that Hasslecomm, despite now having write access to the Dex, does not have as much power as it thinks it has.

\subsection*{Pseudo-Kvetchcomm}

We have some review books on the New Books shelf.  Someone should read and review these.  Maybe we can bribe a prentice to read the vampire porn.

\subsection*{Pseudo-Frustrated Authorcomm}

Margaret got published!  She sent us a copy.  One of her short stories got published in AlienSkin online magazine, http://www.alienskinmag.com/.

Motion to commend DexHamster.  Motion to commend DexGerbil.  Motion to uncommend both.  All motions fail due to Skinnerial decree.

Motion to say that the Skinner isn't fun anymore passes 12-2-10+Spehn.

\goto{Old Business}

There was Mystery Hunt.  It was okay.

There was Arisia.  It was okay.

Gee, lots of excited people this meeting; how do they handle such emotion?

ALGOL.

\goto{New Business}

The tenday starts today.  This would be why the meeting has a lot fewer people than usual.

Drumroll please... Jake does a backcover reading of even more vampire porn.

Can we please declare the newish genre ``Paranormal Romance'' to be neither Fantasy nor Science Fiction?  We should revaluate our consumption habits of such ``literature.''

Someone: ``We need [later redacted to deal with a new rule]  about crazed Keyholders knocking off some of the more prolific bad authors.''

Motion to never mention MITSFS fanfics ever again, to ban the term ``MITSFS slash'' to the deepest of hells passes 6-4-5+Spehn.

\goto{Future Business}

The LSC Science Fiction Marathon is coming up.

In the future, Margaret a story about bananas.  Wait, she already has.  Maybe she'll write another?

Motion to have Margaret send us a story about bananas passes 10-0-1+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
