\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to ... oh never mind passes 14-5-0+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Theftcomm}

All keyholders should sign up for summer hours if they haven't already.

\subsection*{Star Chamber}

Star Chamber members can deal with the Star Chamber shelf themselves!

Discussion of the Skinner^WStar Chamber shelf ensues.

Discussion of murdering people with the wrench and the mechanics involved ensues.

\goto{Old Business}


AL\ldots{}

KCR: ``Usual debate!''

ESK: ``Usual dictatorship.''

\ldots{}GOL.

\goto{New Business}

But what about the usual complaint?

So, Guild Camp started.

Kate's game is going to be awesome and has no failure modes.

\goto{Future Business}

So, I hear we're in future business.

In the future, the iPhone will ascend.  Or descend.  Alter its
position vertically in some form.

Motion that the Society order Ternus a new, replacement banana-shaped
flashlight, Fourth Edition passes 11-0-10+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
