\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 7, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes as enthusiastic passes EIGHT-0-beep \ps

\bing

\goto{Committee Reports}

\subsection*{Star Chamber}

We got eight boxes of books from Amazon this week.  One of them was,
quote, ``frickin' heavy.''

\subsection*{Mortcomm}

Michael Crichton died.

\subsection*{Skinner}

The Keyholder titles have been mostly updated.  If yours is incorrect,
you should let the Skinner know.

Yaaay.

Similarly, the door has been updated.  Keyholders move forward en
masse to test whether they still have door access.

\subsection*{Niagracomm}

We are attempting to sell books online.  Let's see how this goes.

\subsection*{Cell 85 Morale Officer}

We're showing \emph{The Tick} tonight.

\subsection*{Pianocomm}

We have prentii!  They are Working!

\subsection*{Katiecomm}

We have various books, including Anathem and Robin McKinley's new book
(ALC: ``Heheheheh.'' MKR: ``...?'').

\subsection*{Onseck}

We still have membership sheets.

\subsection*{War Council}

There may be a new building being built.  It may or may not have space
for student activities!

Motion for the Skinner to repeatedly call the ASA and incant in a deep
voice, ``BUILD ME A LIBRARY WORTHY OF MITSFS'' until they do so passes
13-Mordor-6 plus Saruman.

KR paid ye November storage bill.  We're good for another month.
Sweet.

\goto{Old Business}

Sold!  To Old Business.

Is there any old business?  Well, there's jhawk.

CJT is reading the Terry Pratchett books.

There was a play with Keyholder(s) and Prentice(s) in it.

That wasn't a subtle hint; it was blunt, like the gavel.

Really Old Business: KR is sending off a roll of microf(ilm|iche) to a
place in... Utah.  Make sure to keep it out of the grasping hands of
Orson Scott Card.  And the Mormons.

I'm pretty sure that this place is run by Mormons.  I guess we could
intersperse porn with our SF.

Paper lasts longer than bits.  Still.

Film is not fiche, micro or otherwise.

``We need to perpetuate the history of the Library!''

``I'm pretty sure that's what we're doing by sitting here.''

``No, we're perpetuating the actuality of the Library.''

``No!  We're turning actuality into history!''

Motion to not let Them perpetuate the actuality passes 16 uprightly held limbs-0-5 \ps.

Speaking of Old Business, John McCain lost.

ALGOL.

\goto{New Business}

Usual lack of a complaint.  I'll complain if you want.  ``Usual complaint!''

Was this a debate about not complaining?

Yeah, Katie is right!  There was an election!

Discussion of the Butcher books.

Do robots have souls?  Wait until the season finale of BSG.

ESK: ``No!  Cylons are very subtle!''

CJT: ``Yes.  Subtle.  Like Tricia Helfer is subtle.  Like Tricia Helfer, Grace Park, and Lucy Lawless are subtle.''

BTS: ``I want to play a game.  Christian, can you name any \emph{male} Cylon actors?''

CJT: *very long pause* ``Yes!  But I'd give away spoilers from the end of Season 3.'' 

\goto{Future Business}

That was actually a really nice bing.

The Trek movie was delayed.  Again.

ESK:  ``I was looking forward to seeing Sylar in something that didn't suck!''

Various other movies were delayed, and un-delayed!

We also have, like, all these people here.

In the future, there will be a dinner mob!  Yaaaay.

Forget the hundred bucks, they take your pot!

A motion which Brian made and which nobody heard but which contained
the word banana and also some semblance of something which is blue and
banana colored and also the word costume was in there somewhere I
could have sworn that he was talking about Barack Obama passes
12-3-blue \ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
