\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 27, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kendra Beckler, Vice and pseudo-Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

All motions fail for whatever reason.

``Splunge'' passes 6-4-3+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Onseck}

The membership sheet situation has been dealt with.

\subsection*{Pseudo-LHE}

KKB has caught up on Katie's reimbursement backlog.

\subsection*{Libcomm}

Libcomm is Panthercomming something during the meeting.

Absolute Sandman III got Panthercommed and is now available.

\goto{Old Business}

The ritualistic dance of Please LaTeX Your Work ensues.

Ternus is suddently attacked by Reality.

The meeting pauses as the attendees admire and sniff the new Sandman
volume.

\goto{New Business}

KKB gave us a debate!

Unusual dictatorship.

Nobody is up to anything new, ever.

Yay, TARDIS.

Art form, you say?  passes 8-5-6+Spehn.

\goto{Future Business}

Guild Camp games run tomorrow and Sunday.

Field Day is still tomorrow!

Meeting ends by pseudo-Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
