\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 4, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kendra Beckler, Vice and pseudo-Skinner, presiding; David Nawi, pseudo-Onseck, recording.

Gavel falls to the floor.  Let's try that bing again, shall we?

Minutes read.

Kat: motion to pass minutes with amendments passes by pseudo-Skinnerial decree.

Brian: motion to get a steel meeting minutes template with magnetized words to play MITSFS mad libs: 7-0-2 \ps

\BING

\goto{Committee Reports}


\subsection*{Lamecomm}
KKB/DAV: ``Not keyholder, not keyholder, not keyholder... hmmm... (to the other keyholder in the room)  Did we do any work this week?''  ``Nope!''  ``Ok...''

\subsection*{Alumnicomm}
Kat/KKB/Brian: ``We had an alumni newsletter at least twice.''  ``Really?!''  ``It's on the desk!  (points out copy in plain sight)''

Discussion of our failed attempt at bilking alumni ensues.

bing

Bing

\goto{Old Business}

The Skinner is no longer hosed, but is not here due to parents.

Guild camp games ran.
Examples: Geisha dinosaurs in Feudal Japan (ESK's game), ancient Athens historicalish, psychological horror, Apocalypse: the Game.

ALGOL: usual motion, usual bing, usual fail at bing

\goto{New Business}

Amal: what *is* the usual motion?

Brian: motion to remodel the taking of library minutes using tree temporal logic, fails because pseudo-Skinner does not want to have to think that hard during the summer.

Amal: do you think if I email the Skinner she will send me the usual motion?
Brian: she will be capable of it, but whether she will actually do it is another question.

We have visitors who haven't been here in a year.  Yay!

\goto{Future Business}

Discussion of fireworks and collapsing bridges.

DAV: motion that we will look up the usual motion: 9-1-1 \ps
Kat/KKB: ``But I put up two against!''  ``But I _recounted_.''

Discussion of the pseudo-Skinner's temporary all-powerfulness ensues.

Miller motion: 4-5-1 \ps

KKB: In the future, the future will not be so nice and will get hot.

Brian: motion to open a restaurant which serves (among a very long list of things) bananas in Kremlin, Colorado fails for lack of a second.

Brian: motion to reconsider the second-to-last motion (the miller motion) chickens by pseudo-Skinnerial decree.  We do not reconsider the motion.  This does not count as a second vote on the motion.

\bing
\noindent
Meeting adjourned because the pseudo-Skinner is bored, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{David Nawi, pseudo-Onseck}

\end{document}
