\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 30th, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 18:00 SST,
Andrew Clough, Theftcomm Psuedo-Skinner, presiding; Karl Ramm, Libcomm and Psuedo-Onseck, recording.

Minutes read.

Motion:  We shall remain motionless.  Passes by Skinerial Decree.

\goto{Committee Reports}

\subsection*{Psuedo-LHE}

We have a check for 40 dollars.  Someone should deposit it.

\subsection*{Theftcomm}

Many people were gone this week.  We really need some new schedule
on the wall.

\subsection*{Libcomm}

I have used advanced information theory to temporarily compress the library.

\goto{Old Business}

Lots of people are away this week.

There were some movies out.  Some of us saw them.

ALGOL

\goto{New Business}

We're all happy to see that Ian Banks has dropped by while he's 
staying in Boston.  We don't actually get a reading, but we're all
happy to have him with us for dinner.

With that the motion to store all our bananas in banks passes 6-0-0+Spehn and the meeting is adjurned.  

\goto{Future Business}

\noindent
Meeting adjourned, 19:-60 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Karl Ramm, Psuedo-Onseck}

\end{document}
