\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 4, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Diane is unwilling to enter the library.

Motion to retroactively amend the minutes to state that the premiere
of Doctor Who is tomorrow passes 11-1-3+Spehn.

\BING

\goto{Committee Reports}

\subsection*{LHE}

The LHE rites have been written!

There are checks.  People should pick up checks, where by people, we mean Andy.

SAFO is really special.

\subsection*{Katiecomm}

Katiecomm did work!

Mag.* data entry proceeds.

\subsection*{Pseudo-Niagracomm}

Yaaay! We're getting rid of magazines!  Yaaaay.

\subsection*{Pseudo-Kvetchcomm}

We got an advance reading copy of Cory Doctorow's latest book, Little
Brother.  According to Neil Gaiman, it doesn't suck!

We want more Advanced Reading Copies!

\subsection*{Jourcomm}

People should submit to TZ.

\subsection*{Libcomm}

Libcomm has been kind of dead for most of the intervening week

\subsection*{Star Chamber}

Mail went out about scheduling a stakeholders meeting.

Bing the binger!  Bing the thing that bings!

\subsection*{Smilescomm}

Somebody should do it.

\goto{Old Business}

We have a Picniccomm!  CAK is Picniccomm.  CAK: ``May 10th or something, I think.''

The season premiere of Doctor Who is this weekend.

io9 continues to be sketchy.  And suck.

ALGOL.

\goto{New Business}

Wait, you debated after the bing!  That's the usual complaint.

Picniccomm!

It is no longer Spring Break.

The season premiere of Doctor Who is this weekend.

\goto{Future Business}

The season premiere of Doctor Who will have been this weekend.

Lots of motions, including banana and Miller motions, passes 9-2-5+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
