\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 22, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, slightly late SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to commend the look on ESK's face while the minutes were read: 4-0-4 \ps

Spehn's vote was counted!  Yay!

\BING

\goto{Committee Reports}

\subsection*{Fweakcomm/hBarcomm}
We need people to sit at the Midway table next Friday!  You should volunteer.

MITSFS could theoretically schedule a Rush event about random science fiction debates or something.  Nice, polite discussion.  No really.  We swear there would be no flaming.

A sample of one of these debates follows.  Kind of.  The pseudo-Onseck is busy formatting.

\subsection*{pseudo-Analogcomm}

Sign up for hours!

\subsection*{Skinner}

The Skinner made lots of charts.  The Skinner is making charts.  The Skinner will make lots of charts.

\subsection*{Mag*}

Did work processing magazines.  All the new magazines are fall-looking and ``no really we process magazines regularly'' to impress the new freshmen.

\subsection*{Trojan}

Prepreprocessing is done for Leibowitz donation 2 and he was emailed.  Trojan wants prenticy help please.

\subsection*{Bluebellcomm}

Got rid of most of the backlog.

\subsection*{The-vice-is-still-reporting-stuff-comm}

Star chamber shelf and mail cardboard box lid both half-emptied.  A good bit of the rest needs Skinner attention.

\subsection*{Smilescomm}

Posted new pretty things outside the door.

\subsection*{Katiecomm}

Katie is not in China anymore!  Yaaaaaaaaaaaaaaaaaaaay!

\goto{Old Business}

The campus used to be free of 2012 freshmen.

ALGOL

\goto{New Business}

Rush is upon us.  Run and hide and kill kill kill the freshmen with fire.  But not in the library!

Motion to turn the frosh that refuse to be prentices into bananas for forever and forever and forever: 9-1-3 \ps

\bing
\noindent
Meeting adjourned, not yet 900 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
