\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 9, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.  Next week's.  Wait, no, last week's?

Motion to declare last week's minutes to be next week's minutes: 12-3-0 +Spehn

\BING

\goto{Committee Reports}

\subsection*{Warcomm}

ESK is now on Finboard.  KR is no longer on ASA.

\subsection*{Libcomm}

KCR's coding block seems to be over.  Yayfor!

\subsection*{Picniccomm}

Picnic tomorrow!  Yum yum yum.  We want people with cars to come to the picnic and drive us there.

If there is good weather, we'll go to the usual location.  This requires the weather to be unlike today's weather.

\subsection*{Trojan}

Trojan.  Beware of geeks bearing gifts.  Beware of geeks writing donation thank-you letters.

Trojan needs volunteers for starting next weekend to really get donation letters out.  Email the Trojan if interested.

\subsection{Magdex Data Entry}

20 pages away from proofreading!  W00t!

\subsection*{Booksesesescomm}

Or Chamber report.  Whatever.

We now have our own copy of Cory Doctorow's Little Brother.  We also got LP versions of each of the books in the Sabriel trilogy.

\goto{Old Business}

Somebody or other wants to cruft the other old psi-phi.  No, not the other other old psi-phi which bursts into flames when you turn it on.

MKR's robot was not three-laws compliant.  It also wasn't AI-compliant.  It also made it past the first round of competition!  Yay!

Roast happened.  Some people had nifty scifi costumes.  Or pants.

Usual debate.  Usual second.  Unusual complaint.  Complete failure of ALGOL.

\goto{New Business}

Motion to declare this room to be the Spofford room for the purposes of elections: 11-1-2 +Spehn

Motion to declare KCR to be Alex (not Vanna!) for the purposes of elections passes by Skinnerial decree.

Elections!

Onseck: ternus, trojan horse, trajan horse, trojan cow, calinula's horse (Incantatus), Beocephalus, Bellenephon, Pegasus, that cow, <censored>, [Alex gets replaced by the *real* Vanna], a pterodactyl, the flying penguin, the flying spaghetti monster, all the penguins in the NE Aquarium, KKB's violin, CAK's hat, ESK's resurrected hat.  Also KITTENS!

KR is going to cause us all to die.

``There are a lot of big numbers here, and they all add up!'' -ESK.  Really.  She swears.

Winner! ternus!  Also kittens.

LHE: Miss Katie, the current LHE's hat, CAK's hat, Napoleon's hat, nation of Corsica, ``some island I can't spell'', Locke Lamora, stainless steel rat, Dalek [preemptive motion to nominate Miss Katie a Dalek: 7-0-2 + Spehn], Cthulhu, spoiler warning for Dr. Who, Hastur.

``This time I'm going to add them up.  But there are lots of numbers...'' -ESK.

Winner! Miss Katie!  EXTERMINATE.  ANNIHILATE.  DESTROY.

Vice: kkb, the new seven deadly sins, the old seven deadly sins, seven, Pluto, sleeping, Jupiter, Kate (by virtue of being a sin), CAK's hat, wearing a suit, efogg, spider Jerusalem, sport death, spork death, xkcd, sinfest, SCIENCE, liberal arts, explosions, all webcomics, satan, caffeine, Kate's diet coke, recreational drugs, non-recreational drugs, the internets, the intertubes, the big truck, competition, syllogisms, the election of 1912, the election of 2008, the election of 2000, Ron Paul, nominations for vice.

Oh man.  I might even win the first time around.

Winner! kkb!

President: ekate, the Konspiracy, ekate's hat, CAK's hat, ekate's khameleon hair, cybermen at the bottom of the Media Lab, the dragon coiled around the big dome, Harold Saxon and his cult of people who bang on the table, The Doctor, bloody death, nimbus, virgin watermelon, george clinton, Leeeeeeeeeroy Jenkins, Indigo Montoya, Ober something blah, Indigo Montana, diet coke [unanimous declaration of diet coke to be ekate], diet pepsi, mountain dew, diet sprite, coffee, tea, the letter T, the T, Mr. T, Cthulhu, Alien, Godzilla, Predator, space marines, creature from the black lagoon, Warren Ellis, the Loch Ness Monster, T Rex, T shirt, the gavel, DOOOOOOOM, the spice, Angleton, Chani, Quark, Pixel, Rho, Miss Katie's friend's cat, Ellis, Doctor Popular, Doctor Doom, Doctor Octagon, Doctor Awkward, Bill Nye the Science Guy, Doctor Worm, Onien, C elegans, Iron Man, Siddhartha, Lao Tzu, monkey king, the one, the elephant, the meditating KR, the two.

``Wait, wait!  I was going to nominate Kevin's exceptional ability to count to two!''

``It would be really sketchy to say I win without adding up the votes... I win!'' ESK.

Winner! ekate!

The President declares herself to be Skinner.  *gasp*

Karrie and Kendra have a Koncert tonight.

\goto{Future Business}

In the future, there will be a picnic.

In the future, Carrie will have large amounts of Doctor Who inflicted on her.

Motion to use bananas instead of tickets for admission to Kendra's Koncert: 18-1-0 +Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\centerline{Disrespectfully edited for proper spelling of Hastur,}
\centerline{Kate Kuznetsova, President and Skinner}

\end{document}
