\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 12, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

ALC's motion to commend the minutes for making me regret that I wasn't
there is seconded by KAT and passes 20-2-2+Spehn.  

Motion to banana
chickens for lack of a second.  

Motion to commend the gavel for making a phone call fails by
Skinnerial bing.

\goto{Committee Reports}

\subsection*{FrustratedAuthorComm}

Bribes arrived!  They went over well.  Bribes are tasty.

\subsection*{Theftcomm}

We have a new schedule.

\subsection*{Katiecomm}

Boxes arrived.

\subsection*{$\hbar$comm}

We have a new $\hbar$comm: keach!

Motion to commend $\hbar$comm for being active not during Rush fails
for lack of a second.

\subsection*{Trojan}

3 prentices helped out with Trojan today.  For the first time in
living memory, Trojan has no backlog!

\subsection*{Pianocomm}

We have a new prentice by name of Lauren!  Also, prentii that work,
they're awesome!

We found intergalactic space weevils nesting in a copy of Analog.
What?

\subsection*{Pseudo-Selden}

We're watching sci fi today!

\subsection*{Star Chamber}

A Special Meeting of the Instrumentality is being called for Saturday,
September 20, at 5PM or whenever the book-getting mob gets back,
whenever is later.

We have a new sign, which is white!  It turns out that the old sign
was also white... originally.  The fine sign, which is bright yellow,
was also originally white.

\goto{Old Business}

Classes started!  The radiator woke up mgentile this morning.

ALGOL.

\goto{New Business}

Usual bing.  What about the usual smear campaign?  What smear
campaign?  That's even more unusual than the usual debate!

Now Kate gets to wank about politics and pretend she's doing homework.

Motion to commend the current US election as being a choice between
science fiction and fantasy passes 17-0-10 \ps.

President Zod:  Kneel for Change

President Cthulhu:  Why Vote for the Lesser Evil?

President Spock:  The Only Logical Choice

President McCoy:  I'm A Doctor, Not A President

KCR's ``Dammit, this is an anthology'' passes 17-3-3 \ps.

We have Keyholders Emeritus BTS and KAT here!

\goto{Future Business}

In the future, KCR will keep better track of the New Books.

We bought / accepted vampire porn by accident.

NH just added a bunch of books to the list, none of which are vampire porn.

Future Business!  Welcome to the World of Tomorrow!

In the future, there will be science fiction!  And dinner!  

This science fiction will be accessible to people who say ``Doctor... who?''

Motion to give BTS a banana for a bad pun passes 21-5-2 \ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
