\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 25, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to commend the minutes for being in the glorious tradition of minutes by first time pseudo-Onsecks everywhere: 14-0-7 \ps

\BING

\goto{Committee Reports}

\subsection*{Frustrated Authorcomm}
Margaret is back!  Yay.

We will retake her soul if BU doesn't steal it first.

Frustrated Authorcomm wants people to give feedback on the book.

\subsection*{pseudo-Pianocomm}

The Prentice did work!  Hm... that sounds like n popular tv reality shows...

Motion to recommend a prentice for cannonization: 9-4-4 \ps

\goto{Old Business}

Readercon happned.

Elena: ``You people didn't go...''

Usual motion in honor of the banana: 6-11-2 \ps

Very much not ALGOL.

\goto{New Business}

Margaret brought us a sparkly glass banana from a fancy blown glass museum.  It is now the library's 'problem.'

Shards of Doom.  The sequel.  Part III, The Revenge.  WARNING: may be bad for children's teeth.

The pseudo-Onseck crawls into her shell and is bitter about excessive allergies now.

SHAMELESS PLUG TIME!

A new zine is in town!  Wooooo!

http://www.expandedhorizons.net

They are looking for contributions!  Stories 6000 words or under pay \$30 per story.  They also hope to add artwork.

Goal of zine is to promote diversity (minorities, women, LGBT, otherkin, etc. are especially encouraged) of speculative fiction.

\goto{Future Business}

SIR (for no reason): ``It's good, it's good, it's good!''
Margaret: ``In the future I will take classes... and in the future people will buy my book, or at least I like to believe that.''

Digression into obscure SF.

Digression back to Frustrated Authorcomm.

Publishing companies are mean and do not allow cheating by way of 1 pt font or silicon wafers.

More robots, less introspection!

Motion to take Margaret's banana and put it in a visible place in the library and construct for it an altar at which we can offer to it burnt offerings of Robert Jordan books: passes by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
