\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 16, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kate Kuznetsova, President and Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Something happens, there is lots of laughing, but the pseudo-Onseck has no idea what is going on.

Motion to commend the Skinner for quickly realizing the significance of her position: 10-1-2 laptops \ps

\BING

\goto{Committee Reports}

\section*{Katiecomm}

Work happened.  Jake might not move away, yay!

\section*{Libcomm}

There is a bug in dexhamster.  Oh, *shock*!

\section*{Pseudo-Picniccomm}

We didn't go to the usual place.

The pseudo-Onseck HATES YOU ALL.

No violations of causality in the library.  Unless you're the Skinner.

\section*{Trojan}

Trojan will be doing work tomorrow afternoon.  Please help her.

\goto{Old Business}

OWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWWW!!!!!!!!!!!!!  The bing hurts us, it hurts us!

Motion to replace the gavel with a banana for ESK to practice with: 3-5-0 \ps

Picnic happened.  Term happened.  We're all unhosed now!

MKR: ``I don't know what to do with all of my time now!''
Entire Library: ``Panthercomm!''
MKR: ``Okay!''

Yay!  Stuff happened.

ALGOL.  Mostly.  This is a usual dictatorship.

\goto{New Business}

KCR: ``You should have known better than to elect a Russian Skinner.''

The gavel and banana stand in for those thingies on the communist flag.

\goto{Future Business}

Keep things away from nearby moons and suns.  Motion to do ``all of those things'': 5-11-0 \ps

ESK stalks us now.  She gets *all the mail*.  All your internets belong to us.

Ooooooh, shiiiiiny gaaaaavel...

In the future, CAK will have a brain again.

Miller Motion: 2-13-0 \ps

The Skinner's bings cause the keyboard to literally jump into the air.  ARRRRRRRGH.

Motion to destroy a banana instead of the universe: 8-0-2 \ps

\bing
\noindent
Meeting adjourned, something-something-something Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck who hates you all!}

\end{document}
