\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 8, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

\BING
Motion to question the veracity of the authorship of the minutes passes 9-8-6+Spehn.

\goto{Committee Reports}

\subsection*{Libcomm}

The Online Dex should now accurately reflect what's on the shelves,
with the deletion of 300+ books.  It is always thus.  Books are now
moving back into the Stacks from the Stack of Found Books.

\subsection*{Hasslecomm}

Hasslecomm did Hasslecomm work.

\subsection*{Sitcomm}

The Writers' Strike may be ending soon.

\subsection*{Capital Laundry Committee}

\textbf{Charlie Stross will be coming to speak at MITSFS next Friday}.

\subsection*{Star Chamber}

There are now more membership cards.

What happened to the stamps that were supposed to be in the Onseck
Drawer?

KCR's extended raspberry motion passes 9-9-9+Spehn.  Are you
questioning the Skinner?

\subsection*{Pseudo-LHE}

The Skinner has a momentary bout of Tourette's regarding our account
at Metro Warehouse.  Not nearly enough variety, I should think.

There are checks on the bulletin board.

Extra Space Storage got paid.

KR's skull is made of wood.  Thunk, thunk, thunk.

\subsection*{Mag.*}

Magdex did work.  Magdex is doing work.  Magdex will continue to do
work, yea, verily, forevermore.

The Magventory sheets were scanned by Copytech and the new online data
entry system was put up.

\subsection*{TARDIScomm}

Don't blink.  Don't look away.  Blink and you're dead.

\subsection*{Mobcomm}

A bunch of books were ordered, including some that people asked for.
ETA sometime this month.

\goto{Old Business}

SOLD!  To the man they call Skinner.

CAK finished American Gods.  Now she, too, will jump on Neil Gaiman.
That's hardly assault at all!

CJT kind of wishes 6.005 was LISP.  Don't we all.

The 10-day happened.  And then it didn't.  Kofi Annan is taking
minutes right now.

Selling things at Boskone next weekend!  You all should get [Boskone]
memberships and come.

\goto{New Business}

CJT: ``Usual debate!'' SIR: ``But what about the usual complaint?''

Future Business is for the Future!

\goto{Future Business}

Discussion of detecting bings ensues.

Turns out that if you put a wombat between the tines of the gavel, it
makes less noise.  Who knew?

Our books don't care if the earth is salted.

Boskone will someday end.

Someday in the far far future, George R. R. Martin will finish the
fifth book.

Perhaps we should resolve the Vice molesting people.

Matrix Motion:

Motion to procure bananas for the Society for use as bananas: 9-2-9+Spehn\\
Motion to commend the Vice for molesting someone, anyone: 17-3-2+Spehn\\
Motion to create safe zones within MITSFS: 4-8-8+Spehn\\

Determinant is 985 and all motions pass.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
