\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Discussion of binging ensues.

Michael:  ``Andrew's not \emph{old}''.

\BING

\goto{Committee Reports}

\subsection*{Theftcomm}

Apparently Theftcomm was responsible for updating the schedule on the
poster in the Infinite!

\subsection*{Pseudo-LHE}

Motion to declare that the right of habeas corpus applies to our books passes 7-0-3+Spehn.

\goto{Old Business}

So Iain Banks was actually here, huh.

Motion to ice the minutes from May 30 because they are clearly cake,
as well as an Albanian motion, fail due to lack of seconds.

Motion to commend the Thunderbunny on his shirt chickens 0-0-0+Spehn.

KR mailed off that scan to that guy who wanted it.

ALGOL.

\goto{New Business}

We should possibly get another Panthercomm.
  
Guild Camp is starting on Sunday.  It got announced on web.mit.edu.

``Yes, we have no banana motions'' passes by Skinnerial decree.

\goto{Future Business}

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
