\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 6, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, something-something-something SST,
Kate Kuznetsova, President and Skinner and smasher of zombies with large wrench, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to question the minutes as being of very questionable truth: 1-8-2 \ps

Motion to flee from the Eschaton who will now kill us because we violated the timeline failed by Skinnerial decree.

\BING

\goto{Committee Reports}

\section*{Theftcomm}

New schedule!

\section*{Skinner}

Has been lame.  Will fix soon.

\section*{Mag*}

Data entry almost complete!  Please please please I hope we'll finish soon.

\section*{pseudo-Mobcomm}

A box of books arrived in the library after a long wait.  Also, we should be getting less vampire porn, yay.

\section*{pseudo-Katiecomm}

Katiecomm is in China.  Waaaaah.

\goto{Old Business}

*Cue old business walking in the door* (Malcolm)

*Cue more old business walking in the door* (Sukrit)

Term is over!

Apparently Iain Banks was here for the meeting last week... right...

More people walk in.  And by more people, we mean Karl.

Time warped and folded around the ALGOL so we skip it and then get many usual somethings and then get many many bings.  All hail skinnerial power over time and space.

ESK: ``Usual OW MY EARS!''

\goto{New Business}

Little Brother (by Cory Doctorow) was good.  Not quite as insane as expected.

We proceed to yank the skinner's chain.  Literally.

Motion to get the society some new bananas: 2-4-7 \ps

Motion to commend the skinner on a very nice bing BINGS by skinnerial decree.

The old computer probably got hard drive failure due to being on the same table as the gavel block.  Libcomm will get on this real soon now.

\goto{Future Business}

In the future, all the new graduates will have to be in the workforce.  Sucks to be them.

Discussion of Disney movies(???) ensues.

Motion that the society acquire a lead-lined fridge to keep bananas in: 10-2 plus 4 \ps

\bing
\noindent
Meeting adjourned, sometime SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
