\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 02, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kate Kuznetsova, LHE and pseudo-skinner presiding; Miss Katie Ray, pseudo-Onseck, recording.

Minutes read.

Move to commend the reading of the minutes as the reading of the minutes passes 1-0-0+Spehn

\BING

\goto{Committee Reports}

\subsection*{Picniccomm}

Picnic is May 10th, sign-up on the library door.

\subsection*{Katiecomm}

Hasslecomm happened, hasslecomm finished, hasslecomm insulted panthercomm, and now hasslecomm is no longer finished.  Hasslecomm and Panthercomm will have a rumble and the loser shall be Niagaracomm.  Sorry Niagaracomm.  (LHE wins, but the house always wins)

\subsection*{Libcomm}

The present avatar of Libcomm was in NC last week and if he gets any lamer, he'll probably stop breathing.  The absent avatar of Libcomm is off wearing leather pants.

\goto{Old Business}

Katiecomm finished her robot.  JHS brought in a roomba that is not three-laws complient.  A guild game happened.  The P-A-of-Libcomm consumed ice-tea and pork.

ALGOL

wait, no usual vote!

\goto{New Business}

Steer roast and TOV are going on, that's why no one is here.

``Neverwhere'' is cool.  So is ``Fables''.

We got a review book list from Tor.  Awesome.

There's this TV show called ``Dresden Files'' but... he has a life and a girlfriend and a happy childhood.  Um.

\goto{Future Business}

In the future this meeting will end. 

In the future the paolibcomm will become less lame or stop breathing.

Motion to turn the paolibcomm into a banana to help the process passes 1-0-0+Spehn  (only the paolibcomm voted).

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Miss Katie Ray, Pseudo-Onseck}

\end{document}
