\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 25, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the reading of the minutes as expeditious passes 4-0-4+Spehn.

\BING

\goto{Committee Reports}

WANK WANK WANK WANK WANK.

\subsection*{Hasslecomm}

Hasslecomm did some processing last night.

\subsection*{Star Chamber}

We had the Stakeholders Meeting.  People are markedly less confused now!

BTS and KAT got de-keyed, finally.

\subsection*{Pianocomm}

We have a new keyholder: NH!

\subsection*{LHE}

ESK (from the hallway): Checks were submitted.

\subsection*{War Council}

KR was stuck in his first ASA meeting.

\subsection*{Wankercomm}

Wank wank wank wank wank.

In that vein, I hear ROFLcon is happening this weekend.

WANK WANK WANK WANK.

\subsection*{Kvetchcomm}

JSB reads from the back of ``Pandora's Closet''.

Motion to ask Jake to come out of Pandora's Closet passes 10-0-3+Spehn.

ALC enjoyed reading the C99 specification.  It's clearly fiction.

\subsection*{Pseudo-Trojan}

We got a ``donation'' from a Scientology front organization.

\subsection*{Phonecomm}

We got a phone call from the Cambridge Chamber of Commerce.

\goto{Old Business}

The Picnic is still on May 10.  Yay, picnic.

Kate is not a frosh anymore.

ALGOL.

CJT: Usual vote, usual result, wank wank wank wank wank.

\goto{New Business}

KR: Indeed.

The Lies of Locke Lamora!  Death threats!

``The Lies of Kate Kuznetsova'' - we need more people for hBarcomm.

There's a game today.

Further CommitteeNewBusiness?

It was spring!  Now it's spring again.             

\goto{Future Business}

In the future we will have a picnic and it will be awesome yay!

In the future, the UA will suck less.

ESK would be very worried if she were interviewing with the NSA.

Discussion of Doctor Who ensues.

An incoherent adjournment song ensues.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
