\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 31, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Karl Ramm, Libcomm
and pseudo-Onseck, recording.

Minutes read.

Motion to do something about the minutes and move on with the meeting
passes by skinnerial devree.

\BING

\goto{Committee Reports}

Uplift report!  David Brin was here,  He signed a dolphin.  What did it get
shelved under?

It's shelved under D for Dolphin!  Duh?

Discussion about what you might shelve a dolphin under.

He also donated a book and talked to us for a while.

Libcomm: Working fulltime takes a little bit of getting used to.

Katiecomm: I have a chocolate house!

``So Katie, what are you panthercomming that under?''

``stomache, I'll bet.''

``I'm not panthercomming it!  It's leaving the library with me!''

``We could fix that...''

``That's not an acceptable solution.''

``We need her cooperation, don't antagonize her.''

\goto{Old Business}

Brin came to the library.  The skinner can stop stressing out.

We got the Graveyard Book by Gaiman, and a Dresden Files sidestory by
Butler.

Discussion of Dresden Files ordering.

HAHAH THEY GAVE THE MINUTES-TAKER CHOCOLATE!  FOOLS!  I'LL DESTROY THEM
ALL!  EXCEPT KATIE SHE GAVE ME CHOCOLATE.
EEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEE  etc.

Katiecomm:  I made a mold, but we didn't test it because people were
hogging the injection-molding machine. 

\Algol

\goto{New Business}

A cellphone rings, and it sounds like the skinner's phone, but it's NOT.

There's a guild game today, I'll bet a bunch of people are playing.  It's
also halloween.

\goto{Future Business}

[redacted]

``Chocolate's a vice, right?''

In the future, I will go with my friend to Mary Chungs.

In the future the election will be OVER.
The pseudo onseck goes a little bit spare.

In the future there will be flying bananas passes 14-0-0\sp
\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Karl Ramm, Libcomm and pseudo-Onseck}

\end{document}
