\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 28, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes unread.

\bing 

\goto{Committee Reports}

\subsection*{Theftcomm}

There is a new TIF.

Handwave, handwave, handwave.

We still haven't gotten stuff from Tor.

The UA is facedown in Cancun for Spring Break.

\subsection*{LHE}

ESK arrives.  Baaaag.  Baaaaaaaag.

The LHE is riteing the writes.

\subsection*{Katiecomm}

Katiecomm did work.

Can we move on to Old Business?

\goto{Old Business}

Woo.

Going to send magazines.  To this guy.  Yaaaay.

Old business, further old business.

Apparently there have been classes for the past two months.

Brilliant!

ALGOL.

\goto{New Business}

Usual complaint!  Wait.  Usual lack of timing.

Kate has a list of books that she is reading.

Everyone and their mother want to start an Asian Cultural Religion Dance Troupe.

Long discussion of library purge policies ensues and is subsequently
taken offline.

The taking-offline has then been taken offline.

Kate fangirls about the Malazan books.

\goto{Future Business}

Discussion of various SF shows ensues.

Orthogonally weird!

In the future, it will no longer be spring break.

Haven't you read Cordwainer Smith's classic epic of the genre, ``The
Future Will Suck''?

KR's ``Well, why don't you make a better banana motion then'' banana
motion passes 4-8-0+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
