\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 11, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes for having ``gypped'' ALC chickens 5-7-11+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Libcomm}

Inventory: Tomorrow!

Inventory prep: Tonight!

ESK walks in.  The Library:  ``Baaaaaaaag!  Baaaaaaaag!''

KR:  McClellan single-malt scotch is delicious.

The New Books shelf is once again the New Books shelf!  Questionably
present cheers ensue.

\subsection*{Suicide Hatcomm}

There is a hat in the library that seems to have hung itself.  It has left a note.

ESK proceeds to read the note.

\subsection*{Mobcomm}

Mobcomm hasn't been ordering books.  Yes, it has, we just haven't been picking them up!

\subsection*{Sort Of Trojan}

People keep coming in and handing KKB donations.  

\subsection*{Bluebellcomm}

Naomi did some Bluebellcomm work!

\subsection*{Onseck}

Discussion of the quality of pens ensues.

\subsection*{Strosscomm}

Woo!

Charlie Stross is coming in February!  He wishes to patronize a vegan
restaurant during his visit.

\goto{Old Business}

It was IAP.

It was the best of IAP, it was the worst of IAP.

There was some Libcomm stuff, but then there wasn't.  It may or may
not have had to do with Dexhamster.  The Attorney Onseck doesn't
recall.

The ASA and what army is going to kick APO out?

\goto{New Business}

It is IAP.

KCR was going to say something.

Farscape is a space soap opera.  And not a very good one at that!  Surprise!

David Tennant's major flaw is not being Christopher Eccleston.

``Firefly would have gone downhill had it continued.'' ``Kind of like John F. Kennedy.'' --KCR, CJT. 

\goto{Future Business}

Motion to commend the sacrifice of bananas in tomorrow's inventory passes 12-5-8+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
