\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the sacrifice of Robert Jordan books passes 6-1-4 \ps

NO FIRE IN THE LIBRARY.

Kate pauses to sign out a book to a member.

\BING

\goto{Committee Reports}

\subsection*{Algaecomm}

Apparently we have this thing called Algaecomm.  ESK found out about
this through jhawk.

Discussion of mold ensues.  Mold is bad, bad, bad.

\subsection*{Hasslecomm}

Hasslecomm has been doing things.  Hasslecomm has had prentices doing things!

\subsection*{Boriscomm}

CJT suggested that MITSFS acquire the Dresden Files cover-art calendar.

By fiat, there are no more committee reports.

\goto{Old Business}

People are hosed and sick.

mgentile: ``90\% of the content coming out of my mouth can be
ignored.''

Discussion of books and stuff.

CJT reads from the inside of ``Frontier Earth'', Bruce Boxleitner
(Legendary Sci Fi Captain Sheridan From Babylon 5 \texttrademark{}).

ALGOL.

\goto{New Business}

Usual structural damage.

So, this dude made this commercial space shuttle.  You can buy flights
for \$200K. 

KCR moves to amend the official responsibility of the LHE to abscond
to space.

All these really cool people get the knighthood cookie.

\goto{Future Business}

Discussion of the Activities Midway, $\hbar$comm, and the incoming
freshmen ensues.

Discussion of Evil/Stupid/Crazy, Random Hall, dining, Senior Haus
dining, regulations, and giant glass monuments ensues.

Motion to purchase a giant 52'' Sony TV as a monitor for psi-phi and paint it banana-colored passes 6-2-4 \ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
