\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 5, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to pretend that we hallucinated the reading of the minutes chickens 9-8-9 \ps

Spehn has been a key player in MITSFS voting recently.

\BING

\goto{Committee Reports}

We got banana-colored bookmarks!

``You can't say that!'' ``Yes, you can, as long as you don't say `motion to commend the banana-colored bookmarks!' ''

Motion fails by Skinnerial decree.

The Skinner sent out email.  All Keyholders need to answer this email or we 

Another motion fails 5-8-Hitler \ps

\subsection*{Star Chamber}

\textbf{Meetings are moving to 6:30PM starting with the next meeting.}
 
Mail will be sent out.

\subsection*{Pseudo-Pianocomm}

Dude, we have prentices!  3 so far this term, including Secret
Recycled Prentice Margaret!

\subsection*{Trojan}

We got a box in, but it can't be processed, making Kendra sad.

We got a lot of November magazines.  This makes no sense.  Maybe it's
a different planet.

There's some sort of time and space flux.

\subsection*{FrustratedAuthorComm}

There will be cookies soon.

\subsection*{Libcomm}

It's hard to write code during a meeting.

The database should accurately reflect which SFWA books are on the
shelf or boxed.  That's been broken since December.

That's December of 2007.  We operate in linear time unless Kate says
otherwise.  

We can now move forward on the SFWA stuff.  This will make Jake either
happy or sad, depending.

\goto{Old Business}

Classes started.  It sucked.  The MIT administration was slow on
getting papers back to Kendra, making her sad.

NH arrives.  ``Bag.  BAAAAG.''

Margaret explains a complicated plan involving Panhel, steampunk, and
a Portal gun.  KCR: ``Fighting Panhel with filk hadn't occurred to me
before.''

ALGOL.

Usual debate.

\goto{New Business}

Usual dictatorship.

We have prentii!  It's awesome!  On the other hand, we have classes.

KKB: ``Who's over there talking like an auctioneer?''

\goto{Future Business}

In the future Margaret will have a costume.

In the future this meeting will end!

CJT: ``Motion to commend the banana-colored banana bananas!'' passes 11-banana-4 \ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

Bonus Post-Meeting Quote: ``What's that?'' ``It's a weevil!'' ``Ohhh yeahhh!''

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
