\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 19, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to banana fails by Skinnerial decree.

Motion to commend the reading of the minutes as being fast but legible chickens 7-3-7 \ps

Kate has not slept.

\BING

\goto{Committee Reports}

mgentile shouldn't have sat next to the gavel.

\subsection*{Pianocomm}

We sent out mail about prentices.  Also, Nancy (nshen) became a prentice!

Pianocomm has sent out a list of projects that prentices should take!

The purpose of prentii is to flip out and shelve books.

Don't let the Gor books out!  No!  Nooooo!

\subsection*{Pseudo-Kvetchcomm}

mgentile is going to poison her brain in the name of science.

\subsection*{Jourcomm}

Jourcomm sent mail to the social list, so we should get more stories,
yaaay.

\subsection*{Pseudo-Selden}

I think there is science fiction today, but nobody knows.  It's a
surprise.  Maybe Farscape.

\subsection*{Onseck}

The Onseck reinforced some of the dividers and membership sheets.

Warcraft books in Chinese!  Uh, woo?

\subsection*{LHE}

The LHE got Treasurer-trained!

\subsection*{Libcomm}

Dexhamster is up to 7200 lines.

We should put some boxes.  Of books.  In the Secret Catapult.  On the
Moon.

\subsection*{Star Chamber}

The Thunderbunnies are not a mail handling system.

\textbf{There will be a special meeting of the Instrumentality
  tomorrow at 5 PM or whenever the book-getting mob gets back,
  whichever is later}.

\subsection*{Trojan}

Trojan would like to request a special Magic Dance.

\subsection*{Odysseycomm}

We are going on an odyssey off-campus tomorrow at 9:30 AM to pick up
an obscenely large number of books from a gentleman who has run out of
space.  We have \$300 of banker's boxes.

\subsection*{Titanic Tetris}

Kevin paid the warehouse bill, which was overdue. 

\goto{Old Business}

BTS tells us a story about his ancient check, issued to him for \$7.50
when he was an undergrad and subsequently reissued every so often.

KKB: ``So... you've come here to fight for your seven dollars?''\\
BTS: ``And fifty cents!''\\

\goto{New Business}

We'll just forget about the usual motion.

ALC: ``Yarr, it be --''\\
KCR: ``BANANA!!''\\
The motion is seconded, and passes 12-3-2 \ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

There is a talk being given about Tolkien and Language on Monday.

There is also a talk being given by Neal Stephenson on Sunday!

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
