\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 7th, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

KCR's Edvard Munchian pose passes 6-4-4+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Bluebellcomm}

We're out of book tape, and we should get more.

JPW is being hosed by grad school.

Thesis thesis thesis\ldots{}

\subsection*{Titanic Tetris}

The library's roof is not leaking\ldots{} yet.

\subsection*{Hasslecomm}

The Ring-Tailed Purge is proceeding.

Assume that we know what we're doing.

\subsection*{Mag.*}

In the past couple of weeks, Magdex has switched from doing general processing to edge-case processing.

Defragmentation is hard, but people need to do it.

50/150 sheets of data entry have been done.  We are getting closer; people should do data entry.

\subsection*{Libcomm}

Meh.  Grr.  Arg.

\subsection*{Envoy to ESP}

kkb's Spark class is tomorrow.

\goto{Old Business}

Steven Brust's Firefly novel is pretty cool.  Wanking^WDiscussion about formatting ensues.  CJT and KR need to get a life.

CC got wantlists.  There is a place for Ann McCaffrey to go.

\goto{New Business}

Usual complaint noted and ignored; redirected to /dev/null

KCR was trying to determine whether that was molestation or assault, and if it was assault, if they needed help.

\goto{Future Business}

In the future, someone will be wrong on the internet.  Oh Em Gee.

In the future, there will be a Guild game.

My, television really is full of things.

Torchwood has its moments.  And they're pretty gay.  Not that that's a bad thing.

Discussion of Doctor Who ensues.

Various banana motions fail by Skinnerial decree.

Motion to turn the Skinner into a banana so he stops failing motions passes 13-3-2+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
