\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 29th, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, a bit too late  SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Karl Ramm, LIBCOMM Pseudo-Onseck, recording.

Minutes read.

Motion to commend the minutes for saying Yay which was mostly the only part
I heard. ``passess'' 9-10-0 \ps

Motion to commend the mathematics of the previous vote?

The skinner has the power, dude.

\BING

\goto{Committee Reports}

\BING

boooo.

\subsection*{Jourcomm}

Somebody totally came up to me and said ``I want to submit to TZ''

\subsection*{Katiecomm}

Katiecomm is back from china!

Motion to YAY the katiecomm being back form china!  14-0-4 \s

\subsection*{Phonecomm}

This thing fails.

\subsection*{fweekcomm}

On mans!  We went to the activities midway

They're so tiny and enthusiastic

We should take their souls as soon as posisble

We made two mailing lists, one for people who read books and one for
people who want to hang out with us.

\subsection*{KKBcomm}

So I walked halfway to random and then I remembered the meeting.

\subsection*{fweekcomm}

We ran out of bookmarks so we drew things on punchcards.

\subsection*{Analogcomm}

Sign up for hours!  I'm on the analogcomm list and I know you haven't
signed up.

It's the end of the summer for I can now triumphantly remove the sign!

\goto{Old Business}

\BING

``Kendra I made you a beautiful.''  
``Oooh, verry pretty.''

Margaret went on a boat.  She named it the Exxon-Faildese.

Katie left the place she was staying 10pm thursday and got to California finally at
12:30pm on saturday.  Her sleep schedule was really screwed up.  She found
that her time sense was two hours off.

ALGOL

\goto{New Business}

\BING

We have, like, a grad student!  That's kind of like a freshman!

We signed people up for things!

\goto{Future Business}

In the future this meeting will end and we can all go eat!

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Karl Ramm, LIBCOMM and psuedo-Onseck}

\end{document}
