\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 21, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes for being grammatically interesting passes 5-2-4+Spehn

\BING

\goto{Committee Reports}

\subsection*{LHE}

Reimbursements got submitted!  You should submit reimbursements to the
large envelope on the ZGT.

\subsection*{Mortcomm}

Isaac Asimov is still dead.

Arthur C. Clarke joined him this week.

\subsection*{$\hbar$comm}

ESK submitted a blurb to the Arts Department, so prefrosh can find out
about us.

ESK: ``We all know someone who goes to MIT because of athletics.''
The Library: ``We do?''

We will have a booth at the Activities Fair, and will give out
magazines with bookmarks to the prefrosh.

\subsection*{Libcomm}

Deranged Libcomm is deranged.

\subsection*{Mag.*}

KR contacted NESFA who may be able to help us scan magazines.

CJT complains about 6.005.  ALC: ``My 6.111 project partner was
narcoleptic...''

\subsection*{Pseudo-Lastcomm}

Discussion of printers and their relative merits ensues.

\subsection*{Katiecomm}

The Purge continues.  Bluebellcomming also happened.

Katie did some data entry.

\goto{Old Business}

Hooray.

Gygax died a while ago and there was a d20 on Killian Court recently.
He had a pretty good roll.

Karl senses a Thinkpad in distress!

Discussion of nuclear war, and paranoia dealing with same, ensues.

Asimov is still dead.  ALGOL.

Usual debate!

\goto{New Business}

No complaint.  What about the usual complaint?  We had the debate!  

The Hugo Award Nominations are out.  Stross and Scalzi HAL-TING-STATE!

Anime Boston is this weekend.

Discussion of anime ensues.

Don't blame me, I voted for Kodos.

So, fascism!

Speaking of fascism, and things that are dead, the Guild game is dead.
Long live the Guild game.

Motion to found the Bananaism political movement passes 6-2-3+Spehn.

\goto{Future Business}

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
