\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/15/2008}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 15, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 17:00 SST,
John Carr, Vox Sciurorum and Pseudo-Skinner, presiding;
Susan Shepherd, Pseudo-Onseck, recording.

Minutes read.

Motion to commend last week's group for a successful revolution. Passes 10-0-1+Spehn.

%\bing

\goto{Committee Reports}

FrustratedAuthorComm: I feel like my head is on a chopping block.

The Pseudo-Onseck is silly.

Pseudo-FweekComm: Some freshmen are coming. The Freshmen Arts Program folk were here earlier taking pictures of the library to impress the new freshmen. They've shot a scene in which the librarian readily gives out information about patrons.

Pseudo-FweekComm$_2$: There should be someone here to indoctrinate the freshmen. 

PhoneComm: Someone has an idea for a science fiction TV show and wants to know whether his science will make nerds cry. He may send an enquiry via email later.

BING!

\goto{Old Business}

A long, long time ago, when dinosaurs ruled the earth, MHG was an engineer... and she'd make stuff. Like blaster guns out of WarHammer.

Once upon a time, MGH stabbed Hello Kitty and took her place among the cool kids.

Usual motion. Usual second, usual vote...

BING!

\goto{New Business}

Gray keebles! Bananas!

The meeting now has more than four people! Yay!

Discussion of giant wrenches and assorted-size gavels ensues.

BING!

\goto{Future Business}

...and the LORD did grin, and they did feast upon the lambs and carp and orangutans and breakfast cereal...

The Pseudo-Skinner commends MGH and her ability to recite dialogue both well and faster than the Pseudo-Onseck can type while laughing.

The Pseudo-Onseck will eventually stop hugging the book ``The Name of the Wind.''

Motion to have Han Solo banana the banana of bananas: Fails 6-2-7+Spehn.

Motion to harness the power of the banana-colored sun to vaporize Panhel and take their space. Passes 4-2-4+Spehn.

\bing
\noindent
Meeting adjourned, 17:31 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Pseudo-Onseck}

\end{document}
