\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 29, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Miss Katie, Pseudo-Onseck, recording.

Minutes Read

It's not fanfic if the author wrote it.  
Motion to commend the minutes for being read by Miss Katie passes 7-1-0+Spehn

\BING

\goto{Committee Reports}

\subsection{LHE}

We paid off Metropolitan Warehouse and Extra Space Storage isn't foreclosing on us

\subsection{Star Chamber}

We cleared out Metropolitan Warehouse and stuff was heavy.

\subsection{Katiecomm}

Panthercomm happened, Hasslecomm happened, Bluebellcomm needs to do work, shelving needs to happen, and Mag.* data entry happened.  More people should join in Mag.*.

\subsection{Libcomm}

The Ring-Tailed Purge got printed out.

\subsection{People's Albanian Embassy}

Movie: The Wizard of Space and Time.  Stuff happened.

\goto{Old Business}

Erikson is still good.  Consider the alternative.  He could be secretly Merlin.

Discussion of cyber-punk short stories.

ALGOL (with the usual debate, and no complaining.  *YAY*

\goto{New Business}

Angleton, Line, and Shell, are all cat names that are CIA related, sf-nal, and mathmatical.

Gah! Look at the mid-nineties webpage of doom!

Back in the day our dorm had cockroaches

Today is a leapday, it's various peoples birthdays.  Including the Gilbert and Sullivan Society.  It's 5.  They're singing Pirates of Penzance in celebration.

I hear there are candles on the dome (for Random.  Yay Random.)

\goto{Future Business}

In the future there will Nebula Awards, 

Michael Moorcock got a ``grand master'' award thingy.  

Motion to award a banana the title of ``Grand Master of the Science Fiction Society'' fails 4-6-0+Spehn

Motion to award the grand master the title of ``Banana of the Science Fiction Society'' passes 13-0-0+Spehn

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Miss Katie Ray, Pseudo-Onseck}

\end{document}
