\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 5, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

In the spirit of last week's meeting, Karl moves ``enh''.  The motion chickens 4-2-``enh''\ps

Motion to commend the minutes as being taken by a prentice chickens 5-2-meh \ps.

\bing

\goto{Committee Reports}

\subsection*{Skinner}

The Skinner is hosed.

\subsection*{Libcomm}

Libcomm is almost terminally lame.

The Skinner needs to harangue the Instrumentality about showing up to
Inventory next month.  Also, there will be a timewarp next summer.

\subsection*{Anticipationcomm}

One of our prentices has volunteered to do a lot of legwork.

Motion to commend the MIT dormitory system for introducing the system
of Chinese checkers to organization turkeys 0-5-5\ps.

\subsection*{Katiecomm}

Katiecomm didn't do any work.

Brian's motion involving precipitation and undecided votes chickens 2-5-5\ps
Motion to Albanian Brian chickens 2-2-ALBANIAAAAAAN\ps

\subsection*{Hasslecomm}

Hasslecomm may have done work, but Naomi didn't see it.

\goto{Old Business}

There was Thanksgiving.  Eh, eh, eh, yeah, I guess.  There was a
meeting since then, though.  MKR was in New Jersey.  Happy in New
Jersey?  How does that work?

Motion to commend Katie for successfully escaping New Jersey passes
7-4-2\ps


Did I miss the bit where that made sense?

How about immoral business?

ALGOL.

\goto{New Business}

Thank you!  Usual dictatorship.

Oh man!  So this person called the library.  The story of this person
is related at length.

This is the last Friday of term.

\goto{Future Business}

Mwahahahahahaha.

So the next meeting will be after the end?  No, it will be during the
end.  Making Miller Motions is better than the alternative.

Brian sets up a long pun that will not be related here.

Shadow Unit!  It's not a real show!

Motion to form a committe to investigate why the dark circles that
form under undergrads' eyes passes 5-0-4\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
