\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 11th, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Andrew Clough, Theftcomm and Psuedo-Onseck, recording.

Minutes not read read due to technical difficulties.

Motion to just move on with the meeting is not actually motioned because:

Minutes are read.

Motion to note that the correct minutes are now online passes by reality.

\bing

\goto{Committee Reports}

\subsection*{Hasselcomm}

Prentii are doing work.

\subsection*{Psuedo-Mobcomm}

New Brust books are here.  Jhegaala is shiny!

\subsection*{Trojan}

Everything we can do in less than 6-hour blocks is done.  We should
have stuff to send out shortly.

\subsection*{LHE}

Lots of things involving counting and arithmetic were done.  Other people's
counting and arithmetic errors have been corrected.

The meeting is temporarily distracted by Jhegaala again.

\subsection*{Kvetchcomm}

Go review stuff!

Also JSB will not be leaving the state.

\goto{Old Business}

Ternus re Saturn's Children:  "Good job Charlie, you wrote a late period Heinlein novel."

Discussion of the cover, and whether it is actually pornographic.

JSB:  "Stranger in a Strange Land is where Heinlein starts being a dirty old man."

KCR:  "No, Stranger is where he got popular enough to get away with it."

ESK:  "Fourth of July happened, stuff exploded."

ESK is conflicted about "Name of the Wind."

JSB:  "Whats our official policy about the books no longer fitting on the shelves?"

KCR:  "I hate you."  "Also, LSC and The Tech are evil and taking our space, and we need more tanks."

Miss Katie is alive in China.  The translation of A Civil Campaign into Chinese is just as interesting
as the translation into English.

Discussion of star mangled spanners and how the worst pun in golden age SF history was perpetrated by Clarke
rather than Asimov.

ALGOL

\goto{New Business}

Motion:  Enter "And Arthur C Clarke is still dead" into the ALGOL.  Passes 14-3-5+Spehn

\bing

JSB:  I'd like to read you the title of a book:  "This.  Is.  Outer.  Space!"

KCR quotes the Hitchhiker's guide on space.

Motion:  Douglas Adams is also still dead.  14-7-3

Motion:  Require these people to explain themselves.  7-11-9

Motion:  Have a Matrix Motion. 6-8-4

Determinate is 616 so all motions pass.

\bing

Motion: Recruit Dalek Keyholders and make the library non-discriminatory to Daleks
by eliminating stairs.  Passes 20-1-2+Spehn.

\bing

Motion:  Increase the amount of potassium in the library with yellow colored fruit.  Passes by enough.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
