\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 14, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, LHE and Pseudo-Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes as being somewhat more amusing than normal: 13-1-1\ps

Motion to commend the minutes' scrofulous precision and accuracy: 5-4-3\ps

Motion to not have any more motions: 1-2-4\ps

Determinant is 119 and all motions pass.

Brian's motion is mostly still, but kind of rotational in a global sense.

\bing

\goto{Committee Reports}

\subsection*{Katiecomm}

Katiecomm processed a bunch of paperbacks.  We also got a tube which
contained a poster, which was given to Margaret.  The tube was much
more entertaining than the poster.

Also, Someone bluebellcommed some books and did it incorrectly.

\subsection*{...}

KAT is on the speakerphone!  She reports that the Shuttle is launching in fifteen minutes.

\subsection*{Pseudo-Hasslecomm}

Jake and a prentice whose name escapes KCR did a fair amount of Hassling yesterday.

\subsection*{Libcomm}

KCR got the flu.

\goto{Old Business}

Margaret won \$100.

The bing was excellently well timed with the person coming screaming around the corner.

KAT is in neither Texas nor Florida, she is in Harvard Square.

Bruce Campbell was in town, but appears to have left without incident.

ALGOL.

\goto{New Business}

We're too apathetic for the Usual Debate.  It's a very usual usualness.

Term hates me!  That's not new.

Star Trek!  It's an odd-numbered movie.  Oh no.  The last one was
even-numbered and sucked...

Long discussion of Quantum of Solace and its EEEEVIL utility companies.

Motion to investigate quantum solodynamics as a possible grand unified
field theory fails due to apathy.  MKR can bing again, though!

\goto{Future Business}

In the future, Margaret will have Saturday finals.

Motion to commend the Pseudo-Skinner for her excellent banana-colored
watch to match her banana-colored shirt passes AAAAAGH-banana-0\ps

There's bananas in it, but no Millers, so it's safe.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
