\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 8th, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, president, Margaret Gentile, Pseudo-Onseck, recording.

Minutes read.

Motion to commend the minutes as enthusastic. Passes.5-0-2

\BING

\goto{Committee Reports}

\subsection*{Glorious People's Olympic Committee}

Reports that the olympics are going smoothly. NO PROBLEMS!
We got a phone call from someone who is actually there.

\subsection*{Star Chamber}
Star chamber processed things. Various entities which may or may not exist in this pane of reality.

\subsection*{Pianocomm}
We have another keyholder, pending the inevatable sweeping of the library.

\goto{Old Business}

A long long time ago, when dinosaurs roamed the earth...

MHG: I used to be cool, and now they make me take minutes.

ALC: I can type fine, I just can't spell.

Incoherent laughter ensues.

/All work and no play makes Jack a dull boy...

Usual motion.
Usual second.
Usual bing.
Usual debate?
Usual revolution...

\goto{New Business}

Real world news: Russia invaded Georgia. There were pictures of tanks and stuff may or may not happened involving airplanes. 

General sketchiness.

Ooh, look at me!

/All work and no play makes Jack a dull boy...

Skinner: That's why you don't fuck with people who have tanks.

"As long as we fight our war during the Olympics, maybe no one will notice."

Skinner: There was a sixteen ton globe lifted out of the floor.
Visitor: By ants?

Stuff is happening in the world and it is awesome.

You know what? I'm sick of this democracy stuff. /Coup.

Discussion of governments ensues. 

Motion to secceede and demand aid in the form of bananas.  
Motion Passes! 10-0-1+Spehn

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Margaret Gentile, Pseudo-Onseck}

\end{document}
