\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 18, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Carrie Keach, Pseudo-Onseck, recording.

Minutes read.

"No" fails 2-14-3+Spehn.

\bing

\goto{Committee Reports}

\subsection*{hBarComm}

We had a booth at the Activities Midway and gave away 2.5 boxes of books 
to excited prefrosh. 

"Science fiction is bigger than Jesus!" passes 17-0-5+Spehn. Let's not 
invite lightning bolts in the library.

We have bookmarks! They're awesome. Next time we need to cut out 
bookmarks, we should use LSC's paper cutter, which could cut the Skinner 
in half.

\subsection*{Libcomm}

KR gets to make a computerized circulation system for his UAP. MITSFS owns 
60 hours of his time!

Hopefully KCR's half of Libcomm will have some un-burnt-out-ness this 
weekend.

The Google Book Project is interested in scanning our stuff 
non-destructively. Free storage! They need it to be barcoded, though.

When scanning books, apparently it's cheaper to pay temps to flip all 
the pages than to cut off the binding.

\subsection*{*Chamber}

KR and ESK went through the Star Chamber's backlog. People get fine 
credit.

\subsection*{Jourcomm}

Submit to TZ!

\subsection*{Picniccomm}

The picnic will be on May 10. If you know of any science fiction authors 
whom we like and who are not dead, tell the Skinner and we'll invite them.

\subsection*{Pseudo-Kvetchcomm}

More reviews went up.

"No one should be set on fire!" "That's not true."

\subsection*{Pseudo-Niagaracomm}

We're going to send Niagaracomm books to soldiers in Iraq.

The US Postal Service has weird regulations re. sending magazines.

\goto{Old Business}

Edward Lorenz, the father of chaos theory, is dead.

Discussion of when the optimal time for undergrads to off themselves is.

\goto{New Business}

Can you debate your own motion that you seconded?

Apparently the MIT libraries have an enormous grant from a former 
keyholder to do something involving science fiction. Shouldn't we know 
about this? Wait, we do.

Kate's trying to be on Finboard. 

Kate read Lies of Locke Lamora. It was awesome and people should read it.

Some book is bad but the pseudo-Onseck didn't hear what it was. I hear 
there exist bad books.

We have Small Favor, finally.

KR is reading Little Brother. It is good. Doctorow has gotten better.

The new EEEPC is out. The pseudo-Onseck can't spell today.

\goto{Future Business}

There's a bag of chocolate in the library. We don't know why. Quick, eat 
it before somebody claims it!

In the future, there will be more Doctor Who. 

In the future, KR will need to figure out if he needs any 
available-in-Japan electronic products.

Discussion of Mercedes Lackey. Motion to stop talking about unicorn sex 
passes 11-1-2+Spehn.

In the future, it will be summer. In the future, it will be winter. In the 
future, there may be more Song of Ice and Fire books.

Something clever involving a banana passes 9-0-4+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Carrie Keach, Pseudo-Onseck}

\end{document}
