\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 14, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to squee eleven-something passes 11-8-10+Spehn.

\BING

\goto{Committee Reports}

Motion to see a motion chicken chickens 4-2-30+Spehn.

\subsection*{Katiecomm}

Bluebellcomm did work but something-or-other is blocking on book tape.

Please stop sending the Onseck mail about book tape.

\subsection*{Hasslecomm}

I hear some purge got done.

Mumble mumble failes by Skinnerial decree.

\subsection*{War Council}

The Skinner got himself elected to the ASA.  Ooops.

\goto{Old Business}

CC thinks giving away books to the prefrosh is a great idea!

The Shadow Mouse of Everjade should be filed under "Flavored with Bacon".

The banana-colored banana is banana-colored.

\goto{New Business}

The usual debate is lame.

There was a Guild game, but there no longer is.  There may be a Guild game in the future.

The Tech are intrinsically\ldots{}, uh, figpluckers.

Discussion of Boeing ensues.

\goto{Future Business}

The Skinner's potential house is not falling down.

People will be get their ham radio licenses!

Discussion of "21" ensues.

Motion to procure our tired-looking Onseck an espresso with a shot of banana syrup passes 14-0-1+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
