\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, Jan 4th, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Christian Ternus, Onseck and Psuedo-Skinner, presiding; Andrew Clough, Thunderbunny and Psuedo-Onseck, recording.

Minutes read.

No motion for them, I was gypped!

\bing

\goto{Committee Reports}

\subsection*{Chamber Report}

The money slot continues to be non-functional.  If there's too much
money in the drawer, let the Star Chamber know.

\subsection*{Libcomm}

\textbf{Inventory in 8 days}

\goto{Old Business}

One slightly annoying thing about the Tech's TV room being next door
is that they tend to play their video games a bit loudly.
Occasionally people are freaked out when sounds of violence and mayhem
eminate from the wall.

Discussion of what people are doing on New Years.  Christian was
flying, but comments that he got to see the Doctor Who special in
London.  Talk about how particularly useful some of the Doctor's
technology would be for us.

ALGOL

\goto{New Business}

Motion:  Relocate the society to somewhere warmer.  Passes 11-0-5+sphen

Discussion of tasty meat in Argentina and Brazil.

Discussion of space launches from Brazil, and how it can actually be
sort of hard to hit the Moon if you aren't careful.

And speaking of space flight, we have a new calender.

Motion: "Launch enough bananas into space to preform a statistically
significant analysis" 8-6-7+Spehn

\goto{Future Business}

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
