\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 17, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes for causing Diane to appear, not only on time, but early passes 15-4-1 \ps

\BING

\goto{Committee Reports}

\subsection*{Binging}

Today we are trying something new.  Today we are trying to bing in
such a way that doesn't cause the Onseck to lose hearing.

Motion to commend the glorious and alarming Skinner for her slightly glorious hair color passes 14-2-4 \ps

\subsection*{Worldcomm}

Still want prentii!  Where'd the prentice go?  It-prentii-prentice-pronoun may be hiding back there.

Motion to reboot Libcomm passes 14-5-4 \ps

\subsection*{The Transparent Committee}

David Brin is still coming to MIT on October 29 at 8:30 PM.  He said
he wanted to come, but he never mentioned leaving!

Motion to create a shelfcode for visiting authors passes 14-5-6 \ps

We haven't had a sticker prentice in some time.

Lee's brain isn't working right now.  If she expects the Inquisition,
we obviously can't have it.

\goto{Old Business}

The Saga Continues: BTS got his check!  Any number of Ns will do.
``I'll hold on to this for a year or two, thank you.''

A member shows up to inquire as to the status of his donation.

Katie voted!

A few hours ago, there was a student protest in Lobby 7.

ALGOL.  YAAAAAY.

\goto{New Business}

There is no usual debate, this is the usual (benevolent) dictatorship.

There will be a Forever War movie!

The Onseck's sister is here.  Oh, that's who you are!  She also does a
surprisingly good job of Ternus' facial structure.  ``Um, thank you?''
Now we're just going to move on.

BTS: ``I proposed a series of slash fiction involving Kirby, the video game char-''\\
KCR: ``ALBANIAN!''\\
BTS: ``-acter, and...''\\
CJT: ``AAAAAAAALBANIAAAAAAAAAAAAAAAAAAAAAAAAAAAAN!''\\

The Onseck should stop ending his sentences with backslash-N. 

\goto{Future Business}

There will be a run of Final Fantasy during Halloween - you can get a
two-for-one on your costume if you so choose!

In the future, we will run a third-party candidate for the Banana Party.  

We need to take the motion off the floor and dust it off a little.

Some motion or another chickens, it's unclear.

BANANA! chickens 13-13-13\ps

The meeting ends with the Adjournment Song.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
