\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 12, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to make this week's minutes equally sleep-deprived: 13-1-0\ps
Motion to make this week's minutes \emph{more} sleep-deprived: 2-11-5\ps
Motion to condemn the minutes as having insufficient REM cycles: 11-1-12\ps

Determinant is 1682 and all motions pass.

\bing

\goto{Committee Reports}

\subsection*{Libcomm}

Libcomm unlamed about GC'ing the n'ew b'ookshelf.

Prentices and others should shelve books on the Reserve bookshelf.

Libcomm may get a chance to get less lame.

\subsection*{FrustratedAuthorcomm}

Margaret is entering a writing contest.

\subsection*{Hasslecomm}

Hasslecomm actually happened!  Naomi saw it this time.  

Jake is not an undergrad.

\subsection*{Star Chamber}

\textbf{Inventory will be scheduled for the first weekend of IAP}.
This is the weekend that doesn't conflict with the ten-day and Hunt,
unlike ... every other day.

\textbf{The Timewarp will begin on the 19th and end on the 6th.}

If anyone asks Kate about Athena accounts, she will strangle them.

Discussion of the mechanics by which one might use the various objects
available in the Library to kill someone ensues.

\goto{Old Business}

The last day of classes happened.

Something something would make more sense in retrospect if the Onseck
would just type it in.

Do you want to be conscious right now?  Do you know that thing about
the MIT sleep fairy?  I'm not in Jitsu, it conflicts with the UA.

ALGOL.

\goto{New Business}

Usual dictatorship!  Usual dissent!  Usual gulag!  Usual war crimes
tribunal.

All the Jack Sparrows had to be removed from Disneyland due to
``inappropriate interactions.''

\goto{Future Business}

Finals, much like the Daleks, are coming.

Katamari Damacyyyyyyyyyyyy...

Lee and Naomi make the ``chilling laughter of the damned.''

Motion to have bananas fly around the library while MKR is gone chickens 3-0-5\ps.

Somehow all the air went out of the excitement of that motion.

Motion to provide banana shaped red pills.  Or blue pills.  Whichever
one it is, to the Star Chamber.  passes by SONG!

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
