\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 21, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

A correction: the flu got KCR \ldots{} ties 9-9-4\ps

\bing

\goto{Committee Reports}

\subsection*{Pseudo-Pianocomm}

We have a new prentice.  His name is Jesse; some of you may know him.

We should keep in mind the structural integrity of the floor.

\subsection*{Conestogacomm}

KR still hasn't heard back from Those People in Utah.

We're pretty sure the Tech staffers are no worse than rats.  They're
highly unlikely to have twinkie incisors.

\subsection*{Niagracomm}

We should give books to Splash's book exchange.  That'd give them
enough escape velocity.

\subsection*{Moocomm}

I refuse to believe that Hand of Fate is worse than Barn of the Blood
Llama.

\subsection*{Trojan}

We finally heard back from the Gifts Office re: the letters KKB sent
last September.

Katie took care of the one box of Panthercomm.  I'm not done with my
report!

\subsection*{Jourcomm}

How's that Twilight Zine going?  Real Soon Now.

ALGOL...

\goto{Old Business}

\goto{New Business}

F\&SF, Analog, Asimov's are dying.  Film at 11.  It would be nice if
they didn't suck.

Monsters vs. Aliens.  Looks fantastic.

KKB has developed an interactive hypertext non-hypertext story.

Don't buy an XO.  Don't be a chump.

\goto{Future Business}

In the future, there will be Thanksgiving!  Food will be forthcoming.
\textbf{The Library, in addition to W20, will be closed from 11PM on
  Wednesday to 8AM on Friday.}

In the future, Kate will be working in the area.

They're serving fries out of a food truck!  Sun Microsystems is doing
more business than that, and they're dead!

Long discussion about jobs.

Miller Motion!  Kate likes Miller Motions (*bounce*)!  All in Favor of
the Miller Motion!  Wheee, the universe ends!  The Skinner exists both
inside and outside the universe, and is thus unaffected by its
existence.  At any rate, the meeting is thereby ended!

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
