\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 1st, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Andrew Clough, Thunderbunny and Psuedo-Onseck recording.

Minutes read.

Motion:  Censure the minutes as incorrectly censured.  Passes 4-0-1+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Dexmistress}

We've figured out new places books should be hiding.

Discussion of Inventory, Indiana, and how there are some places man was not meant to go.

\subsection*{Psuedo-LHE}

Reimbursement for Metro Warehouse soon.  5-7 days is ways too long for reimbursement.  But we are making progress!

\subsection*{Magventory}

We've started playing around with the distributed proofreading system, we're got a test-install going.  We've sent the bulk of the sheets off to copytech for scanning.  When we get them back we can start prentices and keyholders on inventory.

\subsection*{Hasslecomm}

We hassled books, it was great.

\subsection*{Niagracomm}

We've got our huckster's table at Boskone on the 15th, so if you want please help us out.  If you want to show up and help us out either at the con or loading beforehand, we'd appreciate it.  If you have a small bookshelf or two to lend us we could use those too.

\goto{Old Business}

The LSC science fiction marathon happened.  The Skinner has now slept through Sunshine twice.

The Skinner is wasting time sleeping when he could be familiarizing himself with the Starship Troopers book.

ALGOL

\goto{New Business}

Its the Psuedo-Onseck's birthday today.

The Presidency of Hillary Clinton, oft prophesied in near future SF novels, may or may not draw closer on Tuesday.

Discussion of potential candidates.

\goto{Future Business}

Soon term will start.  The universe will also undergo its heat death.

Miller motion fails for lack of second.

Once this inventory is closed we have to start thinking about the next one.  Maybe in the summer.

Motion:  End the universe by replacing primitive vacuum with a banana.  Passes 5-7-4+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
