\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

BTS: ``Sticker prentice? ... but --''\\
KCR: ``Albanian!''

The Albanian fails 1-14-2 \ps.

CAK: Motion to condemn Jacky's chips for being painful to eat 14-7-5 \ps \\
JGC:  Motion to condemn Keach for whining 9-6-7 \ps \\
KCR:  Matrix motion 8-9-2 \ps

Determinant is -283 and all motions fail.  Let that be a lesson to you all.

Motion to commend [their]selves for not breaking the Onseck chickens 6-6-6 \ps

\bing

\goto{Committee Reports}

\subsection*{Theftcomm}

Look, there's a new TIF!  ESK: Hey, I'm still on it!

\subsection*{Upliftcomm}

David Brin is still coming here on Wednesday, October 29!

CAK has a shiny.

\subsection*{Titanic Tetris}

KCR and KKB moved a lot of processed boxes to the Annex.  Woo.

\subsection*{Bardcomm}

There's a play currently on, Midsummer Night's Dream, with prentices
and keyholders in it!

\subsection*{Onseck}

I'm so depressed: we keep running out of membership sheets.  So I made
more.  Don't talk to me about life.

\subsection*{Anticipationcomm}

Anticipationcomm is still looking for help.  Woot.

So, yeah.

\subsection*{Katiecomm}

Because Katiecomm doesn't do enough.

Katiecomm did a little work. 

\goto{Old Business}

There was someone who came into the Library who wanted to look at
really old minutes.  It's like Old Business.  Really Old Business.

We have Cthulhu in our filing cabinet.  Don't worry, that's the
Reserve Cthulhu.  Do we have a Circulating Cthulhu?  No, someone
checked him out and lost him.  The fine is... murder.

MKR reads ancient Soviet minuteski aloud.

Were these minutes taken by the Swedish Chef?

Ow.

Move to declare the Onseck^WVice^WLHE an honorary member of the Soviet
Worker's Party passes unanimous-2-5\ps

You found 1974 in the filing cabinet?

Oh my God, the Skinner is crazy.  ``I think I'm supposed to flail...'' 

\goto{New Business}

Usual suppression of usual complaint.  Usual disappearance of usual
dissidents.  Usual gulag.

All in favor of Number 9 chickens 9-9-9-Mein Fuehrer!  I can walk!\ps

We're submitting something to the Politburo.  Apparently, it's 9.

How can we do Watchmen for people who don't fear nuclear war?

The ghost just closed the door.

Motion to send Kevin's hat down Hatrack River to Orson Scott Card's
Cave o' Crazy fails for lack of a second.

\goto{Future Business}

Andrew's hair-related banana motion fails lame-lame-laaaaaaame\ps.

A confused-looking member arrives. ``I hear Ben Bova is in town.''
``Not that we've heard, but David Brin is coming!''  ``Who?  David
Bowie?'' ``No.''

Motion to .*banana and something something Uumin and Thuurin Hebrew
divination methods and a shiny for the Trojan passes an exodus-0-0\ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
