\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 11, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Carrie Keach, 
Pseudo-Onseck, recording.

Minutes read.

``No'' passes 7-2-1+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Kvetchcomm}

CJT's review of Little Brother will be going up soon. 

\subsection*{Pseudo-Niagaracomm}

A box of magazines was sent off Monday.

We have books to give to the prefrosh!

We have bookmarks to give to the prefrosh! Jasmine drew them and KR cut 
them out. Yay Jasmine and Kevin!

\subsection*{Hasslecomm}

Hasslecomm injured Libcomm last night. We hope they will work out their 
differences amicably.

Robert Jordan writes too many books.

\subsection*{Jourcomm}

Submit to TZ! It will be published RSN!

JFC is writing reviews of books by authors he's never read before. There 
is a reason he has not read some of them before.

\subsection*{Katiecomm}

Smilescomm did some work. 

The ring-tailed purge made the A-K hardcovers pretty. Why is it called the 
ring-tailed purge? Animals, handwave handwave. The next one can be called 
the tufted purge.

Panthercomm was done. 

Bluebellcomm is being done by YT.

\goto{Old Business}

Nothing happened last week.

Battlestar Galactica had its season premiere. So did Doctor Who. Torchwood 
had its season finale; KR will watch the next season.

Apparently the Doctor Who Christmas special will involve the Titanic.

In the past, there were dinosaurs. In the future, there will be 
intelligent octopi.

It is observed that the cover of a new book looks like clipart, which 
inspires JSB to give a dramatic back-cover reading.

People like cheese and bacon, not always together.

\goto{New Business}

YT got in the usual debate at the last second.

There are prefrosh EVERYWHERE AAAAAA

Books are forced upon the prefrosh in the library.

We need a For Sale Bucket.

We will have a booth at the Activities Midway. Help move books! Help force 
books upon more prefrosh!

Google Maps does not understand Boston traffic.

Ash doesn't believe that we don't bite.

\goto{Future Business}

In the future, there will be more Doctor Who.

In the future, we will need a clone of JSB. Katiecomm may consume 
Hasslecomm.

Katie appears! Speak of the devil.

The Skinner has to do everything himself this meeting.

UROPs are coming out of the walls.

Motion to put out ripe bananas to attract more UROPS for Jake (catch and 
release, of course) passes 10-0-2+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Carrie Keach, Pseudo-Onseck}

\end{document}
