\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kendra Beckler, Vice and Pseudo-Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the reading of the minutes as being exceptionally not-damp passes 19-3-5 \ps.

\goto{Committee Reports}

\subsection*{Trojan}

16 boxes of Trojan got finished.  Where is box number 16?  It's
fourteenth from the end, top row.  Fifteenth from the end, top row?
Somewhere on the top row?  Maybe I should just find it.

Found it!

\subsection*{Odysseycomm}

We retrieved 79 boxes of books and universally got lost on the way
there (but not on the way back!)

ESK appears.  ``Does anyone know \LaTeX{}?''  BTS vanishes to help Kate.

\subsection*{Libcomm}

Since September 6th of last year, we have added 703 \emph{titles} to
the Library and 1852 \emph{books}.  This obviously doesn't count the
most recent donation.  This is a testament to Katiecomm's dedication.

Motion to commend Karl for terrifying all of us (``someone's got to'')
passes 21-4-5 plus Spehn and Karl's hatred.  Threat level:  Scramble!

\subsection*{Star Chamber}

The Instrumentality has upheld the Star Chamber's decision to remove
John F. Carr's key.  

The rain really sucks.

Second West set fire to their brownies.

You could sleep in the Library!  Just move all the Trojan boxes.  Or
build a fort out of them.

\subsection*{Pseudo-Pianocomm}

A godawful number of prentices did work today, at least 5.  Prentices,
I applaud you.

Motion to ``yaaaay'': 12-3-10\ps \\
Motion to commence Prentice gladiatorial combat: 10-15-7 \ps  \\
Motion to bring a wrench set: 18-1-5\\

Determinant is -1946 and all motions fail.\\

\subsection*{JLabComm}

Don't Be A Physics Major. 

\subsection*{Selden}

There will be an SF showing tonight.  First three episodes of
Farscape.

\subsection*{Pseudo-Jourcomm}

Karl typed up a copy of the old article, ``Lore of the MITSFS.''

We have copies of all of the TZs in the unDA.

\goto{Old Business}

Today is the 25th Anniversary of the Day the World Did Not End, as
Stanislav Petrov disobeyed Soviet protocol and did not launch nuclear
missiles against America.

``No Miller Motions'', which may or may not be a Miller Motions,
chickens ``something to something to'' 21 \ps.

Kendra turned old.  It was sad.  Karl laughs hollowly.  She did not
complete her horrible plan.

Motion to commend Karl for reaching at least 3 deciKarls of age passes
by Skinnerial decree.

ALGOL.

\goto{New Business}

Ha.  It became usual.

KR gives KKB instructions.  For proper hand placement.  On the shaft.
(Of the gavel.)

We found Box 54.

Brian's check is on its way through the bureaucratic bowels of SAFO.  

BTS: ``Thank god!  I'm unemployed, I need the lucre.''

\goto{Future Business}

In the future, Karl's ears will stop ringing.

Motion to replace Karl's ears with the gavel passes 10-5-9 \ps.

mgentile:  ``I have a verrry small gavel.''

In the future, it will stop raining.  Very, very, theoretically.

Motion to replace the entire population of the earth with banana-based
clones because those don't make Miller motions passes 25-5-6 \ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
