\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 15, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

``No'' passes 42-6-7+Spehn.

\BING

\goto{Committee Reports}

\subsection*{LHE}

The universe hates us all!  But several members of the Star Chamber had heart attacks, and now affairs are back in order, yaaay.

\subsection*{Libcomm}

Lots of REF books got mixed in with the RAND books.  Many of the holes in Reserve that were noticed during Inventory have been filled.  Wooo.

\subsection*{Pseudo-Titanic Tetris}

Mostly thanks to armenard, two shelves are now taller.

``We'' cleaned out the Annex last weekend.

\subsection*{Mag.*}

Mag.* hates you all, especially the magazine editors

You all should do data entry in order to become KKB's best friend.

\subsection*{Katiecomm}

Katiecomm did work; there are now more Niagracomm books.

Katie did a lot of the online data entry.

\subsection*{Niagracomm}

CC and KR moved boxes to Boskone!  It is wall-to-wall magazines!

The status of the kilohardcovers is kind of like a space rock in The Moon Is A Harsh Mistress.

\subsection*{Capital Laundry Committee}

\textbf{Charlie Stross is here!}  General acclaim ensues.

\goto{Old Business}

I warrrned you!  I warrrned you!  The temporary shelf is not safe, said I.  And lo, so it was, as the shelf fell over when KR breathed on it.

CJT scared the hell out of the poor CAC door-lock programmer.

The UA's mail processing organ is lacking in pants.

ALGOL.

\goto{New Business}

Usual lack of caring, usual entry in the minutes.

Charlie Stross is here!  Charlie, take it away.

Motion to induct Charlie into the Order of the Golden Banana passes "a bunch"-6-2+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
