\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 22, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

```Entzverplant' is a pretty cool word'' passes 10-7-7+Spehn.

\bing

\goto{Committee Reports}

The \bing would make an awesome alarm clock.

CAK might be awake now.

\subsection*{Katiecomm}

Katiecomming happened.  But it probably shouldn't be called Katiecomm.

Katie is hosed.  Everyone else is also hosed.

Motion to condemn this week as having way too fvcking much homework passes 19-0-5+Spehn.

\subsection*{Pseudo-Trojan}

We got a very nice donation at the con from Small Beer Press, which is run by Kelly Link et al.

Sorting punch cards requires a special piece of hardware called a ``prentice''.  Ooh, they line up.

KR has met the mysterious Brian Leibowitz.

Abortive discussion of trig identities ensues.

\subsection*{Pseudo-Mobcomm}

We have acquired what seems to be a new, authorized, signed, out-of-print, first edition of a Malazan fanfic novel.

\subsection*{Niagracomm}

We sold 500 magazines and made money!  Woo!

The Wizard of Speed and Time is apparently fantastic in a good but dated way.

\subsection*{LHE}

Kate will be calling Extra Space Storage to see if they got our check.

\subsection*{Onseck}

Remember the vitriolic ranting the Onseck heaped upon parts unknown who liberated our envelope of stamps?  Yeah, they were under something in the Onseck Drawer.

\subsection*{$\hbar$ comm}

'e 'oster's 'ack 'p.  (The poster is back up).

\subsection*{Mag.*}

Mag.* needs people to do data entry!  And prentices.

\subsection*{Libcomm}

Libcomm has mostly been on a system administration weekend.

\subsection*{People's Albanian Embassy | Ellen}

Boskone was cool.  More people should come next time.

Charlie Stross won the Skylark Award!  Yay!

\subsection*{Pseudo-Titanic Tetris}

Andy replaced the ``wobbly-falling-over shelf'' with a ``not-wobbly-falling-over shelf''.

\goto{Old Business}

Charlie Stross was here.

There was a lunar eclipse!

The US Navy shot down a satellite.

The Guild game happened.

ALGOL.

\goto{New Business}

Ummmm... congratulations?

CJT's award of a banana is seconded, and passes 16-2-3+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
