\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 28, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kendra Beckler, Vice and pseudoSkinner, presiding; Lee Fuchs, pseudoOnseck, recording.

Minutes read.

Motion to commend reading of last week's minutes as .... reading.
Motion passes 5 to 1 to 2 plus Spehn

There are multiple gavels.

\bing

\goto{Committee Reports}

\subsection*{Libcomm}

Stuff happened.  Things got added to reserve shelves. There are lots of new books.

\subsection*{Star Chamber}

The Star Chamber is hosed.

\goto{Old Business}

Yesterday was Thanksgiving, and there was food. We went Om Nom Nom, and it was good.  Splash happened, and thousands of high school students descended. That wasn't quite as good as Thanksgiving. Twilight is bad.

Karl is hereby illuminated on the subject of Twilight.

Michael is never to utter the phrase juvenile vampire porn again.

Usual Motion, Usual Second, Usual Result.

\goto{New Business}

It is now the next section of the meeting.

There are lots of people who are not here. And attendees are lazy. Kendra won't kill anyone before they get back

Time warping to Very Very Old Business.  We have visiting cruft, Norman Humer! From the fifties/sixties.

Motion to indoctrinate the unwashed masses to get them to give us money to buy more books
Motion passes 10-0-0 plus Spehn

The history of the Miller Motion: Miller always wanted to end the meeting, so Back In The Day, it was simply the motion to adjourn.

There used to be plants.

Motion to add batteries to the TARDIS passes by pseudoSkinnerial decree.

\goto{Future Business}

In the future, there will many dinner mobs, but not today. Unless the world ends before the next meeting. kkb will prepare for impending doom by doing lots and lots of homework.

Wheeeeeeeee.

Motion we all go out to have a banana split sundae.
Motion chickens 4 to 0 to 6 plus Spehn.

Meeting adjourned (anyway; pseudoSkinner is bored).

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Lee Fuchs, pseudoOnseck}

\end{document}
