\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 3rd, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

No motions.  Laaaaaaaaaame.

\BING

\goto{Committee Reports}

\subsection*{Hasslecomm}

Hasslecomm happened and will continue happening weekly.  Prentices encouraged to do work.

\subsection*{Trojan}

More boxes from the Odyssey got processed.  Yay prentices.

\subsection*{Upliftcomm}

David Brin wants to visit the library.  Dude.

\subsection*{Selden}

The Selden is showing Firefly tonight.

Motion to rename the office of the Selden to Cell 85 Morale Officer: 14-2-10 \ps

\subsection*{Mag*}

In accordance with the Lore of the MITSFS #1 as represented in Twilight Zine #36, Mag* would like to motion to rename itself BACK to the canonical name of Catacomm (for ``cataloging the magazines''): 20-0-10 \ps

Bananas!!! 13-0-13 \ps

\subsection*{FrustratedAuthorComm}

FrustratedAuthorComm is in the wrong industry.  Y'know, getting her MBA rather than publishing books.

The Skinner squees like a cat being strangled.  AHHH MY EARS!

Motion that the Skinner never ever ever do that again: 36-0-0 \ps

\subsection*{Smilescomm}

Smilescomm did work.  The circulating shelves are much happier now.  The person who helped will be convinced to prentice REAL SOON NOW.

\subsection*{Anticipat-comm}

SIR is in charge 

Motion to commend the initiative of shelving people: 12-4-3 \ps

Motion to shelve Naomi first: 19-I can't understand the Skinner-0 \ps

Naomi acquires special Skinnerial permission to check herself out of the library and write a review of herself for TZ.

\subsection*{OldCommitteesComm}

We pass some motion about the old committees.

\goto{Old Business}

Dinokatanas ran.  Yay.

KKB does a full ALGOL, shouting above continuous binging: 

Where are the Comic Books?  The comic books are in California.  Motion to condemn Wayne B'Rells for his sex life with bicycles.  Motion to condemn Irwin T. Lapeer for his sex life with electric typewriters.  Bruce Miller is still skiing in Colorado.  Motion to give Tom Galloway a better gag.  Usual Motion!

\goto{New Business}

Susan: KKB is 9 years away from being awesome.

This opinion is struck down by the Skinner's disagreement.

\goto{Future Business}

The 25th aniversary of the MITSFS being in our current space is coming up in January.  KCR does NOT want to be in charge of it.

Motion that in the future dinosaurs will roam the earth and will be anatomically correct and have feathers: 21-0-0 \ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
