\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/18/2008}

\newcommand{\bing}{{(no bing here)} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 18, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

``Bing,'' says the Skinner.

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, semiconscious President and Skinner, presiding;
John Carr, Pseudo-Onseck, recording.

%Minutes read.

%\BING

\goto{Committee Reports}

\subsection*{Libcomm}

Inventory happened.
520 books MIA.
125 surprise books.
5 potential book-hole pairs that may annihilate.

Missing by shelfcode: ``Oh shit nevermind.''  (long pause)

\begin{tabular}{r|l}
Count & Code \\
1  & FH \\
18 & C/REF-H \\
23 & C/REF-P \\
5  & SR-LP \\
295 & C/P \\
   1 & LPA \\
   3 & R/REF-H \\
  19 & P \\
   1 & LP \\
  19 & C/PA \\
 151 & H \\
   4 & HA \\
   3 & SR-H \\
   1 & R/REF-P \\
   1 & A \\
   1 & SR-P \\
\end{tabular}

KCR says ``All of the SR's are probably there.''
The 546 missing books contain 520 distinct author/title pairs.

There may be systematic errors causing the excess books.

``That's a lot of missing books.''

There may be a different systematic error causing the missing books.

\subsection*{Warehouse report}

Most remaining stuff including all of the boxes has left the warehouse.
They are holding the remaining shelf bits hostage until we give them the
money we owe them.  UA continues their stellar tradition of performance
by not giving us mail, so we didn't have an invoice to pay until we got
one by hand.

The boxed SFWA books, aka hasslecomm overflow, are in the UNDA.

Do we need more hasslecommers?

KR: ``I hear we have prentices.''

KCR leads a long discussion of SFWA boxing policy including the
exclamation ``Merry Christmas Jake!''

\subsection*{Boxer Rebellion}

Boxer rebellion will need people and rites soon as we need to
recall books from oblivion and condemn surplus books.


\subsection*{Pseudo-mobcomm}

We got eight boxes from SAFO and four or five boxes from the UA.
This is why the new book shelf is the new book shelf face again.

The minutes of the last meeting were read during a lull in the meeting.

\subsection*{Katiecomm}

Katie processed a bunch of books.  They need to be covered.

Katie will be 20 on January 20.

Motion to make appropriate celebratory noises passes by acclamation.

``Yay.''

Motion to make banana-flavored cake for Katie.  Not to make
Katie into a banana-flavored cake.

Passes by Skinnerial apathy (he couldn't remember the vote).

%\goto{Old Business}
%\goto{New Business}
%\goto{Future Business}

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
