\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 18, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Susan Shepherd, Pseudo-Onseck, recording.

Minutes read.

Motion: Motion to approve the minutes as being of great historic interest. 3-5-6+Spehn

\BING

\goto{Committee Reports}

\subsection*{Name of committee}

\subsection*{PianoComm}
We have a new prentice! She is doing work!

KKB: ``We will eat her soul - I mean, she will have a good time here.''

\subsection*{TheftComm}

There has been a lot of turnover in hours in the past week.

Kate will soon stop feeling like a horrible Skinner and become a bad Skinner.

\subsection*{LibComm}

Announced that he has quit his job.

Motion: To applaud. 13-4-1+Spehn

Applause. The phone also applauded, due to the Skinner's friend having excellent timing.

The Skinner requested forgiveness for the phone call, and was promptly forgiven by the Skinner.

KKB pities the poor course 6 majors.

Motion: To commend ourselves for being old old old old people. 7-4-0+Spehn.

\BING

\goto{Old Business}

Old Business stuff may or may not have happend this week.

Diane met Charles Strauss several months ago. It was pretty awesome.

eKate read ``Old Man's War'', which was not about sheep, but rather about old men in space. ``Androids Dream'' is, however, about sheep.

Also, there has been more Doctor Who. A 'Doctor Who' discussion follows.

\BING

\goto{New Business}

Some guy came in and gave us stuff. We now have the storyboard for the 'Back to the Future' ride. The Skinner will take care of it later.

KKB has discovered the word leftsandrightstothebody.

Motion: To form a committee to investigate who Mr. Fusion was, and whether he runs on bananas. 8-3-2 

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Pseudo-Onseck}

\end{document}
