\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 19, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Utter silence passes.

\bing

\goto{Committee Reports}

KKB:  Can I have the green pill?
CJT:  No, it's not gluten-free.
KCR:  I'm going to have some green pills! *fetches*
KKB:  \ldots{} Oh \ldots{} I'm allergic to those.

\subsection*{Skinner}

If you had Athena accounts that were about to expire, well, now they aren't.

We granted Henry Jenkins a life membership.  He's pretty cool, but
we're looking for a new advisor.

The Cruft Collective: Resistance is futile, you will be assimilated.
ESK/KKB: Yaaaay!

\subsection*{Pain of Space-comm}

We got the test scans back from the place in Utah.  They look very
nice.  Unfortunately, we still need Money.

ESK:  I don't get it...\\
CJT:  Scanners Live in Vain!  The Pain of Space!\\
ESK:  But what does that have to do with microfilm?\\
KR:   Scanners!\\
KCR:  ... ALBANIAN.\\

\subsection*{Onseck}

The Onseck made new signs!

Also, someone failed to turn in their books properly.  Someone else
vomited all over the hallway!  The Onseck was very disgruntled.

\subsection*{Mortcomm}

Majel Barrett-Roddenberry is dead.

KCR:  Someone needs to be the bastard.\\
CJT:  And I never doubted it would be you.\\

\goto{Old Business}

Term!  Term is Old Business, and finals are dead!

When will the digital system be ready?  Eventually.

This would be a lot less funny if I was actually writing unit tests.

Anathem does not fit through the book slot.  The book slot is .75 Anathems.

Discussion of the book slot and how one might return books.

ALGOL.

\goto{New Business}

Usual... whatever.  Usual ... something.  Usual apathy.

Oh hey, it's, like, winter break now!

Discussion of real science fiction ensues.  Wow, we have time!

\goto{Future Business}

Speaking of the Doctor... he will be back in six episodes!

More discussion of science fiction!  Wow, again!

In the future, Lee will have a prentice project!

In the future, various people will be unhosed.

\textbf{Inventory will be on January 10th.}

The library will be closed for the next two Fridays!

Kevin's banana motion passes by ... white ballot.  Woo hoo.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
