\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 23, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kendra Beckler, Vice and pseudo-Skinner, presiding; David Nawi, pseudo-Onseck, recording.

Minutes read.

Kendra: ``Are there any motions?  Anyone?''\\
Michael: ``Hey, we voted on 'no' once...?''\\
Kendra: ``Motion to condemn you all for not speaking up!''\\

<crickets>\\

``Fine, whatever.''

\BING

\goto{Committee Reports}

\section*{Trojan}

We did work.

Donation letters were written, but there are a lot left to be written.  They will get done eventually.

\section*{Hasslecomm}

Kendra: ``Do tell, good angel of Hasslecomm!''\\
Naomi: ``Work was done, but there are lots of boxes left.''\\
Kendra: ``We should really start kicking our prentices to start shelving books.''\\

Kendra: ``We told the keyholders to go forth and finish finals, which they should have done, which would explain the little work that's been done.''

\goto{Old Business}

<crickets>\\

Kendra: ``So, the universe was created a week ago...''

ALGOL, but the usual objection was almost missed.

\goto{New Business}

(Pseudo-Skinner chides the psedo-Onseck for taking too many minutes.)

Finals should be over now (as of 1.5 hours ago).

Neil Gaiman is lecturing at 7 PM.

Robert Aspirin died at the age of 61.\\
Kendra: ``No more bad puns about myths and phules... <sniff>''\\
Agreed that Aspirin couldn't kill off his characters.\\
``He should have partnered up with George R. R. Martin!''\\

One more week of normal meeting hours, then meetings will start at 6 PM.\\
The Skinner will send a message about it... eventually.\\

Summer is here!\\
All of the Star Chamber is here for the summer for the first time in... a long time.\\

Michael links weather with giving up soup for lunch and compares Wagamama to Pu Pu Hot Pot.\\

Motion to have banana soup for dinner: fails for lack of a second.

\goto{Future Business}

Naomi: ``In the future, there will be more Dr. Who.''\\

Kendra: ``We'll all be unhosed... Oh, isn't that supposed to be now?''\\

Dr. Who is referenced in today's comics.\\
<Michael describes the comic in which it appears.>\\
Michael: ``Poor Toby, he gets no respect.''\\
David: ``It sounds like he deserves no respect.''\\

Motion to worship a banana as Satan to put us out of our misery: 3-0-0 \ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{David Nawi, pseudo-Onseck}

\end{document}
