\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 10, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

MITSFS MEETING FLOODED!!!  The meeting pauses to mop up the Coke which
was spilled by the bing.  We need to place two of every book in an Ark
to save them from the flood!  We've already done that, it's called
Extra Space Storage.

Minutes read.

Motion to EXTERMINATE ALL HUMANS passes 18-1-5 \ps.

Our previous phone was very durable.  You could beat several people to
death with it and then use it to call the police.  The new phone is not.

\goto{Committee Reports}

\subsection*{Hasslecomm}

If any prentices are free on Friday mornings, come help with Hasslecomm during NH's hours.

\subsection*{Theftcomm}

Theftcomm is pleased to note that people are signing up for hours.

\subsection*{Dolphincomm}

David Brin wants us to escort him from his hotel at 8:30PM on
Wednesday, October 29.  We should bring stuffed dolphins.

\subsection*{Anticipationcomm}

SIR needs help from a prentice to send us all to Anticipation.

\subsection*{Katiecomm}

Katiecomm did Katiecomm work.

Andy wants his money back.  I'm sure Katie and her \emph{associates}
can arrange that for us.

\goto{Old Business}

Lots of people failed lots of tests, or not, based on exit polling.

ToV happened.  It was awesome.  People went to the woods and killed
things with sticks.

``What?  Square dancing?  I played board games all weekend!''

Squares doesn't bother you.  EXTERMINATE ALL HUMANS.

Diane needs to show up on time to meetings doesn't work like that by
Skinnerial decree.

Daleks are awesome.

ALGOL.

\goto{New Business}

The Onseck couldn't hear much over the ringing in his ears.

Kate could go to graduate school, but she isn't planning to.

\goto{Future Business}

In the future, the meeting will end.

Motion to something something bananas war the Onseck can't hear anything evidently passes.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
