\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, September 11, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Remote Report

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
It's the ninth Remote Report, in the ninth month of the year! There's gotta be a word for that- not quite poetic or coincidental, but something along those lines.

\goto{Committee Reports}

None.

\goto{Old Business}

One term later, the library is still closed due to COVID. We've had to turn away a few donations as a result, although there might be some stuck in the SAO mailroom anyway. There may be some hope yet for the spring, but I dunno.

People are still asking about any of our collection being digitized, which it isn't, though it may become a priority someday.

\goto{New Business}

\subsection*{SIS}

There are a few new SIS actions to report on:

Operation DOMINO: The minutes have now been digitized through mid-1988. Now that \skinner has access to the remainder of the hard copies (as detailed later), this will continue at... some rate, depending on \skinner's classwork.

Operation INSOMNIA: The wiki has been updated with information from those newly digitized minutes.

And finally, the all-new Operation CAR (Constitutional Amendment Ratification): Based on the outlook for the coming year and some work done in the background, \skinner believed it was prudent to update our constitution. Four amendments were proposed.

1) Amendment 1 created a distinction between the Society and the Library.

2) Amendment 2 clarified the requirements to become a keyholder.

3) Amendment 3 clarified the wording of various sentences and added gender-neutral language.

4) Amendment 4 updated the Assistant Director position to the current iteration, Chancellor.

Two-thirds of the current keyholders were required to vote in favor in order for the amendments to pass. Of the 22 who could cast a vote, 19 voted in favor, 0 opposed, and 3 cast votes of abstention. As such, the newly amended constitution is now available in the locker.

\subsection*{Other Stuff}

We got a decent amount of interest at virtual Activities Midway!

SOLE has a form that allows student leaders access to their office/storage spaces; \skinner submitted it to see what that entailed. As it turns out, you get a scheduled timeslot to access the space and pick stuff up, but you have to be accompanied by an employee the whole time, as you don't personally have access. The form can be submitted multiple times if more pickups are needed, but it looks like the whole "Twitch virtual meeting" concept isn't feasible under the circumstances. \skinner picked up the minutes mentioned earlier, but otherwise there's not much else to go back for. Future meetings may be held over Zoom to do recruitment and stuff, but we can't really show off the library at all.

The whole "student leadership summit" thing is happening again, so \skinner's handling that too.

Also, Cory Doctorow sent us an email promoting the Kickstarter for his new DRM/EULA-free book.

\goto{Future Business}

Things are going great, and they're only getting better/I'm doing all right, getting good grades/The future's so bright, I gotta wear shades/I gotta wear shades

\noindent
End report.

\bing
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}