\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, March 13, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Remote Report

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
All further meetings (for the spring semester, at least) have been canceled due to MIT's new coronavirus policies, so unless some virtual format is decided on, until further notice the weekly "minutes" will mainly just be on things \skinner can do remotely.

\goto{Committee Reports}

None.

\goto{Old Business}

The Assassins' Guild pickup is on hold; the membership events survey is on hold; work parties are on hold.

\goto{New Business}

After the tumultuous past few days, the situation of the library seems to have shaken out as follows:

1) Effective immediately, we have instated a time warp until May 15 (although this may be extended based on the situation at that point); any books falling due during this time period will not accrue fines.

2) The library is closed until May 15 at the earliest, but if you can get access to the student center you can still put stuff in the book drop if you feel like it.

Donations should be declined until we reopen due to the uncertainty of being able to process them.

Operation ELATE (Email List Accuracy To Expand): \skinner started working on the keyholders mailing list to determine who's still active/local.

\goto{Future Business}

What will happen with elections? Is it possible for us to do publicity before Orientation? We shall see.

In the future, the Coronavirus Closure will end. Hopefully sooner rather than later.

\noindent
End report.

\bing
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}