\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, December 4, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.5 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

Discussion of MITSFS' lore and inner workings.

Discussion of the calendar enacted under the French Revolution.

\goto{Committee Reports}

Phoenixcomm: The Discord exists- in fact, we're holding the meeting in it RIGHT NOW.

Swancomm: exists. Might take more action over winter break/IAP since constituents will have a bit more free time.

Ye Downtrodden Membership: People are here! In the Discord, not the library, but they're participating in the meeting nonetheless.

Discussion of MIT history, particularly the dorms.

Thunderbunny: Kat Allen reports on Rainbow's End and the difficulties of "curbside pickup."

Discussion of former skinners.

Discussion of MITSFS' political people. (Mainly L. Court Skinner and George Phillies.)

Ye Downtrodden Membership: Friday! It's cool!

\goto{Old Business}

The Student Leadership Summit happened. Yay.

Discussion of personality tests.

Discussion of COVID impacts. Donations are being denied since we're still closed, and in some cases because it's stuff we don't want.

Discussion of double novels.

Discussion of old 60s pulp.

Discussion of authors putting politics in their books.

Discussion of books read for school.

Discussion of balancing your lifestyle in college. Sleep, kids!

Discussion of graphic novels and general book recommendations.

We held a couple of events, mainly the Halloween game night. That sort of stuff is probably going to be easier now that we have Discord.

\goto{New Business}

Kerberos renewals are happening.

We might reach out to authors at some point.

Discussion of author visits and banned authors.

Discussion of interesting MITSFS cruft, particularly Larry Niven, Fuzzy Pink, and Guy Consolmagno.

Discussion of old events (banquet previous to picnic) and MITSFS hours.

\goto{Future Business}

In the future, we will have access to the large collection of bananas in the library.

A crocheted banana was made for JHS's 40th anniversary as a keyholder.

Miller motion. 3-0-1 +Spehn, fails.

Second Miller motion. 3-0-0 +Spehn, passes.

\bing
\noindent
Meeting adjourned, 70.1 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}