\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, March 20, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Remote Report

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
It's the second Remote Report! \skinner is toying with the idea of holding virtual meetings using Twitch, since the setup worked when tested for our potential CPW event.

\goto{Committee Reports}

None.

\goto{Old Business}

Operation ELATE: keyholders and mahogany-row mailing list updates are complete. Further streamlining to come.

We've already had to turn away two donations: one from an alumnus, one from our very own Dan Wiener '70 (Onseck from way back when- he referred to it as OnSec).

Sidenote: in 1968, Dan Wiener was the Onseck and Robert Wiener was the LHE. Dan has confirmed that they were not related, thus preserving the Skyes' title of being the first siblings simultaneously elected to Star Chamber.

\goto{New Business}

Operation INSOMNIA (Improving New System Of (MITSFS' Notable) Information Access): Due to an abundance of free time, \skinner has been working on adding information to our new wiki (mitsfs-wiki.mit.edu). Most of the committees are now on there, along with a decent amount of related articles (MITSFS phrases, notable people, etc.). Will probably send out a general call for contributions/edits soonish.

\goto{Future Business}

In the immortal words of Squidward Tentacles from Spongebob Squarepants S1 E14a (SB-129): "Future... FUTURE... FUTURE!!!"

\noindent
End report.

\bing
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}