\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, February 14, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.6 ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

Valentinecomm: Happy Valentine's Day! \skinner is still forever alone, but that could change soonish. Hopefully.

\goto{Old Business}

Goddammit, forgot about the Assassins' Guild stuff again. The thread will be bumped tonight or tomorrow, for sure this time.

Mailing list cleanup will also probably start this weekend.

\goto{New Business}

DOMINO is underway once more- midway through 1997 now.

\skinner went to the mandatory financial training. TL;DR: use Buy2Pay or do reimbursements.

\goto{Future Business}

Next meeting will probably be the social one, since \skinner got unexpectedly hosed. If other people come, we can hopefully generate some CPW ideas.

Motion to rename Valentine's Day to Bananalentine's Day. A bit of a stretch, but it still passes 3-0-1 \ps.

\bing
\noindent
Meeting adjourned, 66.3 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}