\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Eileen Hu, Onseck\xspace}
\newcommand{\meetingdate}{Friday, May 8, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.6 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

\goto{Committee Reports}

None.

\goto{Old Business}

ALGOL.

Rerecognition happened; we will survive to see another year.

\goto{New Business}

GP emailed us again :) Alumni are wonderful.

\section{Elections}

Note: procedure modified so that everyone has one vote and gives fractions of the vote to each candidate.

\subsection{Onseck}

Nominations: cat videos, the video of that teacher who made up a song and all those lyrics were just screaming, Pepper Potts, Joan, Cordwainer Smith.

Votes counted. Pepper Potts is elected to the position of Onseck. Congratulations Pepper Potts.

\subsection{LHE}

Nominations: Eileen Hu, giant three-toed sloths, Smaug as per a zoom background present, Locke Lamora as per past tradition, Bernie Madoff, the song For the Love of Money by the O'Jays which is a bop.

Votes counted. Smaug is elected to the position of LHE. Smaug is banned for hoarding rather than embezzling, and also for smoking in the library. The runner up, Eileen Hu (EH), is declared the winner.

\subsection{Vice}

Nominations: The Giant Three-Toed Sloth (Sloth), A General Peacock (Pride), the NBC Peacock (Pride), COVID-19 (Pestilence), Archive of Our Own (Lust).

Votes counted. The concept of abstaining has been elected Vice as a write-in candidate. Abstaining take on the role of Sloth.

\subsection{President}

Nominations: Mathew Suazo, Donald Trump, Nimbus (even though he has not been kind in recent years).

Votes counted. Mathew Suazo (MJS) wins and is declared President. President is asked to appoint a Skinner. MJS appoints MJS to Skinner (aka nepotism time).

\goto{Future Business}

Think about remote events over the summer.

The future is unclear. 

In the future, KR will get the Murderbots novel.

In the future, we don't know when, COVID-19 will be over.

Miller Motion. 5-3-4 \ps. Motion does nothing.

Second Miller Motion. 4-0-5 \ps. Motion chickens.

Third Miller motion. 10-0-0 \ps. Motion passes.

\bing
\noindent
Meeting adjourned, 67.8 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}