\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, February 7, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.5 ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Time to do some ACTUAL BUSINESS! *gasp*

\goto{Committee Reports}

Bluebellcomm: there's a lot of books that need to be covered sooner or later.

Panthercomm/Trojan: also a lot of donations that still need processing. We just got a book donated from Australia, so that's pretty cool!

Surgeon: there's a lot of stuff piling up in the ZGT that's probably going to get moved back to the Annex, given that the position isn't terribly active currently.

LHE: we need to make a deposit, since we're pretty cash-rich right now. Also, scissors have been added to the shopping list, along with the computer we still need to replace.

\goto{Old Business}

The abatement happened! Props to Eileen for dealing with that whole thing. On the plus side, when we moved our stuff back in we were able to get rid of a bunch of old useless clutter (mainly shelves that don't fit our current bookcases) by skinnerial decree.

The Assassins' Guild stuff is still here. At this point we might consider delivering it to them, but \skinner's going to bump the email thread first.

We still don't know how we got this model of the Hungarian parliament building.

\skinner's Vegas trip ended with him breaking even, which is... anti-climactic, really.

\goto{New Business}

The card reader apparently got upgraded. No noticeable effects, though.

How many CX copies do we keep? Is there even a policy on that?

The reimbursement document on the ZGT was modified slightly in an attempt to clarify it, but it should probably be rewritten/streamlined at some point.

The keyholder complaint sheet on the door needs to be replaced, as we had 12 written complaints in 2019. Admittedly, there were a few particularly zealous reporters, but even so, a reminder: announce when you won't be holding hours and modify the Google calendar to reflect that.

Relatedly, \skinner is going to be reviewing the mailing lists to do some cleanup, so expect some emails asking whether you're still active in your position/whether you want to keep getting our more general mailings.

\goto{Future Business}

\skinner has a financial training event to go to. Fun.

We should start thinking about what we want to do for CPW. Fun!

Next meeting will probably be advertised to the frosh/prentice lists to get some more social activity going and to restore levity to the meetings. FUN!!!

Motion to condemn bananas for being lazy, because figs have to actually work to become fruit by dissolving wasps inside them. 2-1-0 \ps.

\bing
\noindent
Meeting adjourned, 67.9 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}