\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Eileen Hu, Onseck\xspace}
\newcommand{\meetingdate}{Friday, February 28, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.4 ksec SST,
\skinner, presiding; \onseck, recording.

\goto{Committee Reports}

Ookcomm: minutes page has been updated for the new year.

\goto{Old Business}

Wiki is operational at mitsfs-wiki.mit.edu.

\goto{New Business}

For CPW, must submit events March 1.
\begin{itemize}
\item Open house ideas: maybe add Twitch stream in case people don't want to come physically, all day open house
\item Movie screening (Mystery Theater style?)
\item TV show screening if a full feature length movie is too long
\end{itemize}

Minicult: Florida Man Tries to Burrow Into Gopher Tortoise Nest to Hide From Police, Found 'Throwing Dirt on Himself'

Prentices:
\begin{itemize}
\item Should host a work party for prentices to get hours: shelving? bluebell?
\item Set up a clearer system for prentice hour tracking (post table on the door)
\end{itemize}

Picniccomm has to happen at some point, find a frosh!

Found a temporary home for the genre squid- by the windows.

\goto{Future Business}

In the future, what's going to happen? We don't know, we're non-prophets.

Miller motion. 6-2-2 \ps. Motion fails.

Second Miller motion. 6-1-3 \ps. Motion passes.

\noindent
Meeting adjourned, 67.2 ksec SST.

\bing
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}