\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, March 27, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Remote Report

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
It's the third Remote Report! \skinner is also considering Zoom as a possible meeting place, although that limits the possible participants to those directly affiliated with MIT. So, we'll see this Friday, I guess.

\goto{Committee Reports}

None.

\goto{Old Business}

Operation INSOMNIA: more wiki updates; all the documents \skinner has on his personal computer are now available in the form of various pages. Next is the content from the locker, which may be an opportunity to clean it up at the same time. Cool.

\goto{New Business}

People are asking whether we have anything digitized for them to access online. We don't, but this brings up an important issue: once the Closure is over, should we scan some of our stuff? Most of it is probably accessible elsewhere, but at the least we should look into doing something with TZ. Maybe a temporary loan to MIT Libraries so they can put it online?

\goto{Future Business}

Future is as future does.

\noindent
End report.

\bing
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}