\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, February 21, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.9 ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

Bluebellcomm: most of the books in the queue have been covered.

LHE: our excess cash has been deposited into our endowment.

\goto{Old Business}

This feels like it should be some form of committee report, but in any case: shelve books! There's a lot of them on the cart.

Assassins' Guild responded; they should be picking up their stuff sometime this week.

Mailing list cleanup is still an idea in the ether, as well as the "social" meeting due to \skinner's hosage this week, but next week's looking better for those things, as well as for...

\goto{New Business}

SIS! It's back, baby! Operation WACK (Wiki, Allowing Compiling of Knowledge) is a go, as \skinner managed to get a copy of MediaWiki running in our locker. The link is currently long and complex, but we can submit a request to get an X.mit.edu address. So yeah, definitely a place for historical records, committee descriptions, and such, and we might want to add some of our rites documents too for easy editing.

What are we gonna do for CPW? More discussion next meeting, but one idea is an open house that's also livestreamed on Twitch for people at other events who can't stop by/want to ask quick questions remotely. Seems kinda interesting.

\goto{Future Business}

Motion to adjourn. 4-0-0 \ps. Doesn't count, though.

Motion to bananadjourn. 3-1-0 \ps.

\bing
\noindent
Meeting adjourned, 66.5 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}