\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, March 6, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
This meeting didn't actually happen due to \skinner having another commitment, but given that the minutes have mainly just been reminders for \skinner to do things as of late, the events of the week were still recorded.

\goto{Committee Reports}

Panthercomm: more Hassle has been produced.

\goto{Old Business}

Assassins' Guild has confirmed that a member will come to pick the stuff up soonish. \skinner knows said member and will probably bug her to get it done.

Apparently CPW has been canceled due to coronavirus concerns. RIP.

\goto{New Business}

We received a book in the mail from Roger Silverstein, LHE 1977-79! Pretty cool.

JHS suggested a wider survey of the membership about possible social gatherings and such for people who can't make the Friday meetings- makes sense. \skinner will probably send out a Google Form or something.

Some people came in during WDS's hours- they seemed to be touring the building to determine what improvements need to be made.

\goto{Future Business}

In the future, a work party will probably happen, because we need to level up our prentices.

\noindent
Meeting "adjourned," N/A SST.

\bing
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}