\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, May 1, 2020}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Remote Report

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
It's the eighth Remote Report! The semester's coming to a close, and with it, I won't have to deal with weekly updates for the sake of continuity any more. Nice.

\goto{Committee Reports}

None.

\goto{Old Business}

None... well, the Busy Beavers Discord server sent us a followup from the Midway, saying that they could host events for us on the server throughout the summer if we want, so maybe we could do something like that.

\goto{New Business}

Rerecognition time! Emails will be sent with a form for people to fill out, so keep an eye out for that.

Also, elections! \skinner's thinking about holding them next week, if we can work out the logistics/who's running for what by then. Keep an eye out for that email as well.

\goto{Future Business}

The future influences the present just as much as the past. (Friedrich Nietzsche)

\noindent
End report.

\bing
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}