\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Meeting of the MITSFS

Friday, May 16, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
There is a legend the Cajuns have about the mysterious, dark, and wet swamps which are located in the Louisiana wild. "Do not go out there alone between owl-rise and cock crow," they warn. "A THING inhabits the bayous, a THING so hideous, so wicked, so very mysterious and beyond the knowledge of all human ken, that even Isaac Asimov cannot explain it." They say the THING wanders the swamps forlornly, forever cursed, searching out what it cannot find. They say if the THING sees a human being, it will grab that human being by the throat, and it will ask one question: "Which way to the Spofford Room?" They say if the human being answers correctly, the THING will give him a set of matched luggage and 20 assorted SF paperbacks. If the human being answers incorrectly, the THING will rip his larynx out. This is what they say, and who is to say differently? Think about it, the next time you contemplate your navel.

The meeting was called to order, the minutes were read and approved. Pseudo-Lord High Embezzler report stated we had about 250 dollars in the bank, we were owed 1150 dollars, and have over 1000 dollars in debts. Theftcomm (Ruffa) reported the new poster was up, titled "New Turkeys for Old." Stevens reported he had a cover for TZ 31, a photo of one of the members. A motion was made to censure Stevens for allowing the outside world to see what society members looked like, which chickened the number of photos taken of society members to the number of cracked lenses that resulted to the number of new cameras that had to be bought. Jourcomm_2/2 insisted that TZ 29 will still come out before VOODOO 1, proclaiming above hoots and catcalls that the present 'tripe' was not funny, whereas the original VOODOO was.

Old Business Algol saw another Ruffa-powered saucer fly out the window and land unbroken on the Great Court (saucers are made out of a mono-molecular crystal). Ruffa said Boskone 12 took place 12 weeks ago, and Hitchcock informed us that Boskone 13 will take place on Friday, February 13th, which seemed appropriate.

The current invasion of the Russian Navy was brought up, but the Skinner allayed our fears by stating the civilized world need not fear, as their only reason for being here is to make a peaceful pilgrimage to MITSFS.

Panic was momentarily aroused by the arrival of Phillies; a few moments later, he was almost censured for reading ahem at a meeting- more specifically, the Boston Glob, which was agreed to be SF. The vote was (for) the number of letters to the Boston Glob, to (opposed) the number of intelligent letters to the Editor in the Boston Glob, to (chickens) several wiggling fingers and one rather pointed one belonging to a person with a rather pointed head, more specifically, a wedge. The motion chickened.

Onward to New Business and a Minicult (Skerry): He reminded us of the MAD Star Trek parody which was so silly, in which Kirk and Spock landed on a planet whose soil was made out of chocolate pudding; then went on to relate how in the recently published "Witch Queen of Mongo", Flash Gordon and Dale Arden find themselves struggling through a landscape which is composed entirely of banana splits.

Minicult (Bernstein), which he didn't give me and so I got to reproduce it here: An article in the New York Times (May 16) said, "COMPANY HAS INTERESTING WAY OF CHOOSING EMPLOYEES- Warbash, Barrow, Becker, Paraesque, Inc, has found a new and fascinating way of choosing their prospective employees." End of article.

Minicult (Ruffa) explained how it had been discovered that the sound transmission properties of the moon were amazingly similar to those of a certain type of green cheese. Bernstein said it was actually Limburger.

A Skerry minicult about the length and price of Lloyd Alexander's new book was almost voted as being the most boring one in at least 3 1/2 weeks, but judgment was deferred until it came that Hitchcock read his.

Minicult (Phillies): The 1ibrary recently acquired a book on alien visitors to Earth in prehistoric times, which cites as its primary reference Eric Von Daniken's work. Mr. Skerry moved to vomit, but a vote was not taken.

Minicult (Wechsler): A recent article in Scienterrific American by Carl Sagan stated that a project to contact extra-terrestrial intelligence would cost "only ten billion dollars." A confusing discussion ensued: Bernstein moved that, in order to discover extra-terrestrial intelligence, the next probe should include Carl Sagan and Johnny Carson. Ruffa pointed out that Candycomm has use of Society funds to send Carl Sagan out to bring back live specimens of extra-terrestrial intelligence; the purpose of this was that, as soon as he was out in space, Sagan becomes an extra-terrestrial intelligence. Phillies then wanted to include the words "extra-terrestrial life" as well as "extra-terrestrial intelligence" in the motion, for the purposes of sending Johnny Carson. This assumed that Carl Sagan had intelligence. After it was decided that this probe would most likely show any alien that at least one member of the human race possessed intelligence, the motion passed with (for) 'the number of extra-terrestrial life forms' to (against) 'the number of intelligent people on Earth' to (chickens) 'the number of extra-terrestrial intelligent chickens.'

Minicult (Goldberg): The greeting to the Russian sailors which the Boston Globe so thoughtfully printed in Russian contained at least two dozen spelling and grammatical errors. Hitchoock moved to commend the Globe for having no more errors in its Russian grammar than it normally has in its English grammar. Ruffa amended this to rule that the translation is actually in Albanian. The vote was unanimous to the person who translated the article into Russian to...

But the tail end of this motion was cut off when Paula entered the room, evoking a resounding WHOOSH from the membership. To top it off, she sat on the wrong side of the table. Bernstein demanded that Hitchcock now give his Minicult, this being the only action that can top Paula sitting on the wrong side. Hitchcock's Minicult came from Air PROgress magazine, and said that an airplane turning downwind is subject to different physics than that of an airplane turning upwind. This was greeted by a bored silence. As Hitchcock attempted to elaborate on the author's mistaken frame of reference, Bernstein moved to subject the following question to debate: "Is that minicult worse that Paula sitting on the wrong side of the table?" Wechsler said the question was either Paula Lieberman was capable of sustained flight, or the magazine was. It was moved the experiment be tried unless Paula moved to the other side of the table. Stevens noted that she was Air Force ROTC, and therefore may "know something." Then it was moved that when Paula went to Cheyenne mountain, someone should lock her in there.

Finally, Stevens moved that Paula, the Air PROgress magazine, and Hitchcock be abandoned in a landscape full of banana splits. It passed, unanimous to three bananas to the number of motivations to work Bernstein has. The meeting was adjourned.

Let it be noted that in this historic meeting, Paula Lieberman did not say one word!

\vspace{12pt}

\centerline{Gary Goldberg, Onseck}

\end{document}