\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 3, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The strange man walked hesitantly into the room and advanced towards the long table about which the people were sitting. He was tall and very slender, with bent shoulders and a lined face that told of a lifetime of hard work and weariness. He wore a simple gray overcoat that reached to his knees and a tiny, neatly clipped mustache. Clutching a little leather-covered book in his gnarled hands, he peered at its evidently small print through his round glasses. He said to the people, in halting English with a marked Hungarian accent, "I do not want this record, it is scratched."

One of the people at the table, holding a large, wrench-shaped gavel, said, "Huh?"

The man repeated, plaintively, "I do not want this record, it is scratched."

"No, no" said the Skinner, for it was indeed he, "we don't sell records here, this is the Spofford Room. See- Spofford Room." And he indicated a hanging oil painting of a distinguished gentleman.

Light dawned on the Hungarian's face. He leafed through his little book and then said, more clearly, "I do not want this Spofford, it is scratched."

"That's better," said the Skinner. "Sit down. The meeting will come to order." And the gavel banged down.

The minutes were read and applauded. There were some uninformative committee reports, and then some random comments from random Hitchcock led a freshman to say, "Telzey?" with a definite rising inflection, causing a Finger Motion which passed incredibly unanimous to no one that counts to Brad Schaeffer's shoe. A number of motions were immediately fired across the room by everyone, which were lumped into a "Why didn't you vote more than once" motion, which chickened number of such motions we have passed to number of such motions that should have been made in the first place to number of times such motions were humorous.

The members moved into Old Business Algol. Where are the comic books? The Skinner brought several, including, "the finest classic in 75 years of comic writing, deeply symbolic of the plight of mankind- HOWARD THE DUCK." Spontaneous applause caused Wechsler to move to nominate Howard for Skinner, whereupon Bernstein resigned, and the vote came out number of tail feathers on Howard the Duck to Bernstein's number of turkey feathers to the difference between the two, motion fails, but then got confused in technicalities: whether the Inverse Skinner Rule applied, whether the members paid attention or ignored RHB's resignation, the fact that the Skinner is appointed, and a motion to censure the comic book for bringing that particular skinner. Hitchcock summed it into three motions: to ignore RHB, to pay attention to him, and to censure him for being brought. A matrix vote was taken, with different members filling in the rows and columns like so:

(Inaudible) to 0 to jelly beans + (-1)^(1/2); The 5088 3M Portable Projector to aleph null minus 1 to 1 nerf ball; 6 to 6 to 3.

The Skinner defined 6 as half of 3, then moved to censure some members for saying 6, followed by Pinette censuring them for their six-life with numbers, resulting in a vote of six to six to six. RHB moved to note that motion was positively beastly.

The Hungarian, who had been sitting quietly until now, burst out with, "My yacht is full of eels." Hitchcock shot him a look and growled angrily, because that was what he was going to say. The meeting went into New Business, which began with a tug of war between half of Star Chamber and some members, using an extension cord (that was evidently for the 5088 3M Portable Projector). The war ended in a dented Skinner.

Minicult (RHB) told of a lawyer who stole over 15000 books from the NY Public Library. When asked how he had stolen all those books, he said, "In great quantity." When asked why, he said, "I like to read." Goldberg moved to laugh, which passed unanimous to none to none.

Minicult (Goldberg): On radio WEEI, there have been tips from the BBB about how the US is going metric, and how, during the transition, the ordinary 12" ruler would also show 34 millimeters.

Commotion was caused by the book of ahem that a freshman had brought; RHB moved to throw the book out the window, which passed number of nerf balls to number of nerfs in the room to one yellow cord- and so we couldn't do it, because it wasn't a Ross Motion and the Skinner specifically said- oh, forget it.

Stevens made a Gindin Motion on that loudmouth in the green shirt, passing unanimous to Gindin to one foot and a funny necklace.

Minicult (MTT) told of the casting going on for the new Superman movie; it looked like Burt Reynolds was favored for the lead, with Mary Tyler Moore as Lois Lane. Minicult (Miller) said the Alpert was in the library yesterday. The same freshman, I think, who did it before, did it again and said "Alpert?" with a definite rising inflection, bringing down a finger motion with a vote of Alpert to Phillies to Scott.

The first Miller motion brought a vote of nobody who counts to 5000 supermarket shelves to one very broken down deceased Skinner.

After the usual difficulties, Miller finally moved to strangle the Skinner with the banana-colored extension cord, which passed none to many many to number of people who will come near RHB when he starts swinging the gavel, adjourning the meeting to the tune of a pummeled nerf ball. The Hungarian said to Spofford, "You have nice thighs," and left with the others.

\vspace{12pt}

\centerline{Despicably submitted,}
\centerline{Gary Goldberg, Onseck}

\end{document}