\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

A Holiday MITSFS

Friday, December 12, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
'Twas the hour of the MITSFS, and all through the 'Tute

Not a creature was stirring, not even a newt.

The gavel was placed in the Spofford with care

In hope that St. Skinner soon would be there.

The Vice wasn't here, so I with my pen

Had just settled down for a long writing event

When from down the hall there arose such a clatter

We opened the meeting to see what was the matter.

When what to our study-dulled eyes did appear

But two crazy men and no tiny reindeer.

One twas a guy eating wheat bread for dinner

So I knew in a moment that it must be St. Skinner;

The other was dapper and infinitely cool

And as they approached us Bob called like a tool-

"Ho, Miller! Ho, Goldberg! Where's Stevens and Nussbaum?

Ho, Wechsler! Ho, Schaeffer! Leave, Gindin and Hitchcock.

To Committee Reports, to Old Business Algol,

Now chicken away, chicken away; chicken away all!"

At this point in narration the Onseck doth groan

And does not write the rest of the minutes in poem.

During the reading of the minutes Wechsler was finger-motioned for asking "Where's the Electronic Onseck?", Hitchcock was finger motioned just for fun, and the cool man in the back of the room was censured for only voting once (none-a stab from the past-26,000 unanswered letters); then a female type came in and was censured for not voting on the last motion. The interrupted Onseck returned to his reading of the minutes, asking rhetorically "Where was I?", and was ruthlessly finger motioned.

COMMITTEE REPORTS!!! LHE (RHB): noted 1150 dollars in the bank. Jourcomm_2/2 (Wechsler): "Cringe." Pseudo-Jourcomm_gamma/mu (Hitchcock): There's a new Charlie Tool story in Appaloosa. We trotted through OB to OBAlgol, whereupon it was observed that Tony Lewis made a pass at Fuzzy Pink. Word has it that he was repulsed. Hitchcock moved to censure Irwin T. Lapeer for his sex life with cactus leaves in the gutter (passed).

Sliding down the chimney into New Business: Minicult (Miller) from Newsday magazine, which quoted someone as saying that IBM stock dropped 6375 dollars a share in one day. Wechsler moved to double the amount of IBM stock the society owned (failed).

A kluge motion was made on Brad Schaeffer. An Inverse Ross Motion was made on Brad Schaeffer. As the Onseck labored to catch up in writing down the minutes, the Skinner asked him if he knew what was happening. The Onseck innocently asked, "No, what's happening?" He was prompt1y and unjustly finger motioned as he cried "Entrapment!"

Someone was finger motioned when, referring to the man in the back, they asked, "Who's that dapper looking gentleman back there?" Someone else quietly asked the man in the back if he were "Marc Albert", and was brusquely rebuffed as the man said proudly, for all to hear, "It's not 'Marc Albert': it's The Alpert." To prove it, he smiled and said, "I'm cool!"

The festivities continued as the Onseck was overturned by a cowardly villain who shall remain nameless, but whose initials are RHB. An Inverse Ross Motion on the airplane was passed and carried out, but the window got stuck, so an inverse Ross Motion was passed on the cold air. A Bowel Motion on Brad Schaeffer was passed (in favors to "5" to aleph null minus 1); a motion was made to censure the female human for saying "5" in response to a request for a number. She was finger motioned when she asked, "What's wrong with 5?" Together with a finger motion on Hitchcock, the result was a stacked finger motion. (Hitchcock, in a male chauvinist remark, moved to note the appropriateness of the stacked finger motion.) Yes to Uh to 1123 dollars in debt, You better not say "5" again to an exasperated sigh to e^(next number), 250 mg per cent to 20,000 copies of "The Way to Dawnworld" to aleph null sub i.

A millermotion unfortunately chickened, but we were saved when it was moved that Wechsler jump out the window for love of a banana.

\vspace{12pt}

\centerline{Merry MITSFS to all, and to all a good night,}
\centerline{Gary Goldberg, Onseck}

\end{document}