\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Foundation and MITSFS

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
It was nightfall. The naked sun, like a pebble in the sky, setting behind Boston's caves of steel, and the stars, like dust, came out slowly to shine across the currents of space. On this day, November 14, 1975, a large number of MITSFS members gathered in the Spofford room, among them the gods themselves (the Star Chamber), some hallowed stabs from the past, and the rest of the robots.

With his usual good timing, the Skinner opened the meeting at precisely 5:00 PM SST. During the minutes Hitchcock was commended by the Society for his excellent sense of timing, having come in just as the Onseck was reading about a "horrible distortion of a human being." A pseudo-Libcomm report was lost, due to the Onseck's inability to write fast enough (for the electronic onseck had not bothered to show up). The Vice graciously condescended to write the proceedings, using the skills garnered through years of being an Onseck and professional monk, and it was moved to impeach Goldberg and declare him a former Onseck. A subsequent attempt to overturn the Onseck resulted in an almost overturned t*b1*.

Some people stuck their heads in the door and were censured for not voting, for only voting once, etc, followed by a finger motion on MTT for asking "What motion?" RHB brought a folded, spindled, and mutilated LHE from his pocket and reported we had 708.06. Flamecomm (Ginden) complained there was not enough flame in the society; he was condemned for sitting in the library on occasion and reading quietly. Pinette came in and was chased out into the hall, whimpering, by the Skinner. (Jourcomm/n)n! said TZ 29 RSN, and MTT asked "What time is it?" for Greg Ruffa.

We moved to Old Business, wherein there was an inverse Ross motion on Ross (Joe) who just walked in the door, with a vote of (number of books in the society that have been read by the people in this room to number of books that have been read by the people that have been worth reading to change in cum of all the people), motion chickens.

Old Business Algol saw a stacked finger motion on Schaefer, Wechsler, Pinette, Timmreck, so everyone made a finger motion on the person to their left, passing (unanimous to 13 to 2002), showing we sure do learn faster than Finger. Then it was history time at the MITSFS as Ross regaled us with the anecdote of how "Tony Lewis made a pass at Fuzzy Pink and was repulsed;" he so moved and it passed (4 to total circulation of "Executive Mart" to random number).

Suddenly there was an assassination attempt on the life of the Skinner as Weschsler pointed a wire wrap tool at him, shouting "Squeaky Fromme lives!" Despite the quick assistance given by Secret Service agents, the attempt failed.

Into New business, and a Minicult by Professional Stab from the Past Bill Desmond: "Executive Mart" offers for sale a parking meter lamp for 64.80. The society voted not to have heard Joe Ross' bad pun. (BD mentioned "Exec. Mart" was an "advertising medium;" JR wondered if spiritualists use parking meters.) Minicult (MTT) as he fled the room: Marvel man will team up with some other idiots. A minicult by Wechsler caused the society to condemn him for tying to oust Hitchcock for the most boring minicult ever. Minicult (Ross) again gave us some real life history, noting Sunday was the 10th anniversary of the Northeast Blackout and the 8th anniversary of a huge snowstorm which immobilized Boston. Schaefer moved not to have a recount of the Inverse Ross motion on Ross, which failed, so there was a recount (unanimous to Ross to one shot), passed, and so an attempt was made to carry it out, much to the discomfort of Ross. Fortunately the window was closed with Ross still on this side of it.

There was a Minicult by Stevens, which he just inserted into the minutes without bothering everyone. (IAP guide 143.)

Minicult: Spencer Love wanted to steal 150 dollars to build a giant mind and put the library in it, but he was censured for conducting serious business. RHB demanded that we give him (RHB) no less than 12 motions at a time, which we did with gusto. The Onseck was overturned and declared no fun, followed by attempts on the part of everyone to flip him over, giving him such a paranoid complex he could hardly finish typing the minutes. Wechsler read some IAP activities from the guide, which brought on a series of Miller motions. Tired of writing, the Vice, pseudo-Onseck adjourned the meeting, despite attempts by the members to continue it.

\vspace{12pt}

\centerline{Inevitably submitted,}
\centerline{Gary Goldberg, Onseck}

\end{document}