\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

We Meet Again

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Something had changed. The people filing into the Spofford Room that Friday evening on the 7th of February, 1975, were not the happy, smiling people they had been only a week before. They walked with glum faces, with their shoulders bent as if the weight of all knowledge was upon them. For it was. IAP had ended the previous week. The spring term had begun with a vengeance. All of those nasty professors had been let out of their cages. This was the members' last hope; nor were they to be disappointed, as the pseudo-Skinner, Greg Ruffa (for the Skinner had gotten out of practice in his screaming and had a sore throat), climbed to the top of his chair, swung the gavel, and hollered: "This MITSFS meeting is called to order!"

Courtesy of the Onseck, the minutes of the previous meeting had not been provided. They were not approved as unread. The Star Chamber, outraged at the feeble showing of the members, moved to condemn them for being outnumbered by the Star Chamber. This passed at the number of Skinners since MTT to the number of good Skinners since MTT to the number of good Skinners.

The Lord High Embezzler noted that we have dollars in the bank. It was further noted that this is as good as having dollars in the bank. Old Ruffa, as pseudo-Skinner, said that we have a new Libcomm. He wasn't exactly sure who it was (it may have been Ruffa) because they had been resigning almost as fast as they had been appointed.

Guy Consolmagno walked in just in time to have a motion directed at him condemning him for not voting. It chickened, but a recursive motion on that man passed.

Stevens, not able to think of anything to say, gave an expressive shrug when asked the results of the IAP activity "Science Fiction without Guilt." Told to "write that down" he wrote "that" down. As pseudo-Wellcomm, he regretted the demise of Wellcomm, due to the demise of the only Wellesley member of the Society (apparently she had been spreading ugly rumors, i.e. the truth, about the society).

Spoffordcomm, reporting on the untimely disappearance of he who had supervised so many of our get-togethers, said that the old man was being refurbished and would soon return with a new frame and another coat of varnish.

The meeting Usualled from Old Business, through Old Business Algol, into New Business. Costello was immediately Fingered for asking about Hitchcock (this also showed rather poor taste). The pseudo-Skinner was so obviously pleased about the chance he had had to have everybody shout "Finger motion!" that Costello was also censored for giving the Vice this great opportunity (at 14-1-"what's it to you?").

Ruffa's request that the Society rule "no comment" about the color of Hitchcock's shirt passed (less than obviously) at one limp wrist to one stiff wrist to one slashed wrist.

Someone dredged an event up from part of the meeting long past and moved that it be declared that Stevens said "that" because he couldn't think, period. The ingrates passed this at unanimous to less than unanimous to 3 + a pen. This led naturally to GC's minicult. Al Solzhenitsyn understands capitalism: after he mentioned that he used Bic pens to write with, he was given a lifetime supply of them.

A minicult from the little Guy (on how one town had mistakenly passed an ordinance stating that if a pet was unclaimed for more than 24 hours, the owner would be destroyed) led to the successful motion to destroy SB and Hitchcock if they were not claimed by their owners.

The first Miller motion didn't do anything, but a motion to adjourn passed at a lot to the thing in the corner to Harris.

Goldberg read an ad offering to sell 1000 acre lots on the moon for only 4.98 each, and which remarked how nice it would be as a Christmas gift. Presenting us with a sheet of paper on which he had determined the cost of the entire satellite at this rate, he moved that the Society buy up the moon with its surplus 46,817,098.97. Costello, asking how much that came to per crater, was almost encouraged to go there to count them at the vote of the number of craters on the moon, to the number of craters on his face, to the number of dimples on a golf ball.

Consolmagno told of the company that offered a "unique, authentic" coat of arms to the "PHD" family.

To strange cries of "Feed me! Feed me!" from the back of the room, pseudo-Moocomm reported that the Midnight movie was to be Little Shop of Horrors.

As a tribute to the real Skinner, a motion to bring a friend to the meeting and stay home next week passed at unanimous to the number of germs in the Skinner's throat to S&s. An inverse Ross motion preceded the successful second banana-colored Miller motion, leading those formerly weary and unhappy people out the door in an aura of banana-colored happiness, until the next meeting or next homework set, whichever came first.

\vspace{12pt}

\centerline{Juxtaposed alternatively,}
\centerline{Jack Stevens, Vice and Pseudo-Onseck}

\end{document}