\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

Instead of the usual minutes, here are instead the minutes of a Moscow-based science fiction society.

\begin{center}

Mitsfski Meetink

Friday, 10 Oktobrja, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Meetink vas kalled to order by Skinnikni. Ze meenuts were red end approved. Zeudo-libkom (RHBski) zaid vee haf French encyclopedia, 2 Perry Rhodan buks, 2 lazer buks, end buk uf stillz from old SF mooviez, zo vee now owe more den 400 amerikan dollarz to kapitalist peeg Vitter. Zeudo-mookom (Chiczkok) zaid Metropolis vas playink at Bostonski Ziense Moozeum. RHBski moofed to declare dat Metropolis iz playink in Gatham City diz week: (Batmanski to Supermanski to Henry cabot Henhouse III end vatch out for dat tree, motion flashes by).

Vee moofed to Old Bizniss, end, zurprize zurprize, Stephans had zome: moofed that zosiety officially ignore stab from de past who didn't show up last veek (it's got to pass to not enough to make it fail to 1 foot=34mm + 1 pair of taps, passes).

At diz point, de serfs were freed, and middle class in Russia grew. In Olt Bizniss Algol, dere vere zeveral motions on who didn't vote and who voted but once. Stephans moofed to zensure dat man (Chiczkok) for sex-life vith bicycles, vich he doesn't even have de good grace to carry on in private; it chickenedski: (number of spokes on dis fellow Chicakik's bicycle to number of wheels on his bicycle to de number of tings on his bicycle dat Chiczkok has violated).

De poor downtrodden members, under the oppression of the bourgeois Starrr Chamberski, united end made two mozhionz at the same time, to zensure zomeone for not votink, end for existink, voted on at the zame time, according to (Art. VI, Sec. 1, Par. l, i.e., the Discrepancy Clause to de 5th Amendment to 32nd Amendment or Art. II, Sec. 8, Par. 18, Elastic Clause), mozhionz are impeached.

De peasants revolted and brought meetink into New Bizniss. Meenikultski (Stephans): Nature Study: Cats do not understand why it is that squirrels disappear when they 're on the other side of the tree.

Meenikultski (Bicycle fetishist): De Charvard Klee Glub was rehearsink a concert, including songs "Die Domine Tool", "Old Shed and Tool", "Hahvahd Foot Tool Song". It vas reported they vere preparink to sink before a Tool & Die konvention. Stephans moofed to zensure that man for a "tooly boring minicult." A Whooshink motion immediately followed, den first motion passed (number of tools that have died to number of tools that have lived to number of tools that can be packed into the tomb of the unkmown tool).

Havink nothink to lose but hiz chainz, de vice had another Meenikultski: The Star Trek blueprints haff sold 150,000 copies in two months, end iff it was book, it would head every best-seller list in country. Zince nobody in room could think of appropriate motion, RHBski moved we think about it for a week, passed (number of trekkies to Dave Ellis to one boot with funny yellow stamp on it).

Meenikultski (Goldberchikov) : Vergeltungsflotte has picture in Tech picture spread. Anodder Meenikultski (Goldberchikov): Isaac Asimov has written new book, "100 Original Lecherous Limericks."

Grumblinks arose from de proletariat. They staged armed uprising, cryink "Vee vant Miller Motion!" One was given, but it was not pessed. They rushed de Winter Palace of hated Skinnikni, shoutink "Workers of world, unite!" RHBski moved to censure Chczkok for dressink object of his fetishes in banana-colored lock, passed (unanimous to Chiczkok defendink his friend'z purity to 16 chains), end de serfs were satisfied, keepink Mitsfski a despot-run state.

\vspace{12pt}

\centerline{Gari Goldberchikov, Onseknik}

\end{document}