\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting

Friday, November 21, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
It was a dark and stormy night. Now, like, I'm not just saying that; some guys, you know, say it's a dark and stormy night just to give things atmosphere and all that jazz, but I'm not hot-dogging you, it was a dark and stormy night, the wind wrecked my umbreller, and umbrellers don't come cheap on an Onseck's salary, y'know; so it was a dark and stormy night, and the wind howled through the Skinner as the gavel creaked down and landed with a thud, and it was time for you-know-what.

The minutes were read and approved, natch. Pseudo-LHE (RHB) said we had an unspecified amount of money in the bank, and had an unspecified library grant, put in some unspecified file by some unspecified person. Cranstoncomm (Skerry) informed us that at the last minute the agency substituted personnel, so instead of the scheduled solar eclipse we had a lunar eclipse. There were some motions, notable among them being a motion that the society fall asleep.

We whisked through Old Business and Old Business Algol, sort of, and into New Business, and there was a Minicult from Ruffa (via RHB) of numerous happenings during eclipses. Minicult (Pinette): The Star Trek Technical Manual was out, containing such gems as a "photon accelerator" on the phaser. Minicult (Goldberg): "My 8.03 test was a snap." He was immediately overturned and chased out of the room, but managed to fight his way back in.

Minicult (Wechsler): From the Bryan Times of Bryan, Ohio, Nov. 19, 1975: printed in the paper was an "Abrabian proverb." Wechsler wanted to send an emissary to the planet Abrabia.

Minicult (Wechsler): From the Bryan Times, Bryan, Onio, Nov. 19, 1975: Betelgeuse, a first magnitude star in the Constellation of Orion, has a diameter of 700 million miles. This news, less than exciting to the members, almost caused the passing of an Abrabian motion on Wechsler.

Minicult (Wechsler): From the Bryan Times, of Bryan, Ohio, Nov. 19, 1975: The high temperature in Albuquerque was 65, in Anchorage 28, Asheville 70... The multitude lapsed into "rabbits have no tails at all," as Wechsler continued to tell us about New Orleans 75, New York 67, Omaha 73, until his Bryan Times was taken away from him by force.

A jelly-filled Inverse Ross Motion on the donut was passed; the first attempt to carry it out powdered Stevens's leg with sugar, but the second attempt succeeded. The donut did not break, and RHB moved to appoint Wechsler a committee of one to retrieve and eat the donut. An Abrabian motion on Mr. Skerry passed after he said that Space:1999 used the "it was only a dream" dea sex machina.

Goldberg moved to create a Goldbrick Motion, which would be made in lieu of overturning someone, so that no one would fall right over. Suddenly, he fell right over. The motion was seconded and passed (international monetary fund to Fort Knox to 1/national debt). Then RHB moved an Inverse Goldbrick motion, which no one acted on, thank goodness- otherwise they would have encountered the Anger of the Onseck (by Cordwainer Smith).

Minicult (Goldberg): Pet Rocks were selling by the thousands at Macy's, Neimann Marcus, etc. A well-deserved whooshcomm report followed Pinette's uncalled for question, "Are they sold by the pound or by the quartz?" Mr. Skerry moved to take the last minicult for granite.

Minicult (Goldberg): "Miller stole my minicult!"

Minicult (Miller): A Pennsylvania man was robbed of 66 dollars by an armed man in a wheelchair.

Minicult (RHB): The Skinner's sister broke into professional journalism recently by writing all the obituaries for a newspaper (not the Bryan Times).

In a very welcome motion, Stevens moved to look at all future eclipses through banana colored filters, bringing the meeting to a close.

\vspace{12pt}

\centerline{Just plain submitted,}
\centerline{Gary Goldberg, Onseck}

\end{document}