\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Minutes Meeting MITSFS

Friday, November 7, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Shortly before 5:00 PM SST the Skinner entered the Spofford Room and flicked on the lights with a careless gesture. As power surged into the fluorescent lamps, there was revealed before him the shape of a formless monster which cast not a shadow, a horrible distortion of a human being, an alien terror from a lower dimension. Startled at the sudden intrusion into its darkness, it advanced menacingly toward the Skinner.

"Back!" screamed the Skinner, holding his mighty Gavel before him with both hands. The monster stopped and cringed, for such beasts cannot stand the presence of the Gavel, and then it scurried to the wall and put its back against it defensively.

"Back from whence thou camest, o wretch," cursed the Skinner, making ominous signs in the air with the Gavel. The creature hesitated but a moment, then leapt into the picture frame on the wall, its homeland. Suddenly feeling secure, a complacent smile crossed its face and it put its hands in its pockets as the Skinner hurriedly placed the sealing spell on the picture frame before the other members arrived.

The meeting was called to order. After the minutes were read and approved the meeting started to go downhill. Jourcomm_2/2 reported the next TZ will come out "never." This moved us into Old Business, through Old Business Algol, and into New Business.

Minicult (Goldberg) reported two recent studies revealed good news and bad news about nuclear war. The bad news was we would probably have a nuclear war before 1999; the good news was that it would probably not destroy the entire human race, but that isolated pockets of primitive culture will still survive. RHB noted this meant that every Friday at 5:00 we'll still be here.

Minicult (Stevens) The institute will turn into a sun temple next Tuesday or Wednesday, when the sun will shine through Lobby 7 down a quarter-mile of corridor and out the other side to hit the chemistry building. He suggested the society put a giant Fresnel lens in Lobby 7, vaporizing anyone who wanders into the main corridor and melting a hole through the chemistry building. Amended by RHB to put Susan Weinberg at the focal point, it passed number of photons that will pass through the Lobby of Building 7 to none to 1 scorched chicken feather.

Some finger motions and other stuff happened then, notably an Albanian Motion on Starr. The Vice moved that all permutations and combinations of Finger motions, censuring a person for not voting, and for voting only once, be combined into one massive oh my god look who's coming in the door. Before someone could second the oh my god look who's coming in the door motion, we turned and saw the entrance of a stab from the past, dressed in business suit and carrying a briefcase as does any self-respecting stab from the past, come to visit our humble meeting because there was nobody in the library- Bill Desmond.

Overcoming his shock, the Vice completed his suggestion to create a new motion which would pass in such an incredibly short time span to make such an incredible density of motion per unit time as to totally intimidate anyone who ever thinks of asking a question or not voting at a meeting. RHB moved to commend Stevens for the most confusing motion ever. They were put together in a matrix motion with the usual one-too-many rows:

Number of people who said they gave blood because it feels good to number of motions that can fit on the head of a pin to "in favor or in chickens?"; Old Turkeys for New to "Who, me?" to equal to Row 2, Column 3; Random to length of Spofford's nose in furlongs per fortnight to number of black holes in Lobdell.

Minicult Starr to Minicult Wechsler: Marquette, Michigan voters have voted not to secede from Michigan to form a 51st state called Superior. Minicult Starr: A half page political advertisement in a newspaper proclaimed "We DON'T believe in telling the truth. We DO believe in false accusations, etc." The next day the newspaper apologized for mixing up the do's and don'ts in that ad.

Minicult (What's your name): In the recent Boston election there was elected to a post a man who had been two weeks dead. Starr moved to find out if this was the same guy who won the lottery a few weeks ago: vote was 'enough to pass' to 'nowhere near enough to make it, but two corpses comes pretty close' to 'a ridiculously low number if you think you can make this motion not pass,' motion fails.

There was some brief comedy relief as the Skinner chased the Onseck around with the Gavel, and eventually there was made a Miller motion, which unfortunately failed not enough to oh, Jesus to Joseph, Mary, and the National Lampoon editorial of Dec, 1974.

Fortunately for the sanity of the free world the second Miller motion passed 1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19 20 21 22 23 to 23 to all 23 of us, and that about does it.

\vspace{12pt}

\centerline{Finally ended,}
\centerline{Gary Goldberg, Onseck}

\end{document}