\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Meeting of the MITSFS

Friday, May 9, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
It was on everyone's tongue. People would stop each other on the street and ask, "Have you heard? There's been a shake-up in MITSFS! Almost the entire Star Chamber has been rearranged!" To which other people would reply, "MITSFS? What's a MITSF? Isn't that some Jewish thing?" Meanwhile, a milling crowd of two members wended their way to the Spofford Room to get the straight poop.

At the stroke of 5:00 PM SST, the meeting began as usual- save for one subtle difference. Instead of the much beloved Skinner of yore, the man holding the gavel was the recently elected LHE, Nick Nussbaum. Before the angry mob could tear him to shreds, the LHE rapidly explained his pseudo-Skinnership: the truth was, R. H.(Bob) was down with the plague. Immediately several motions were attempted, including commending the plague for its choice of victim, and censoring the plague for its poor taste; but none were seconded.

In Committee Reports, Stranglecomm (Nussbaum) noted that GC was last seen headed for Arizona via Minnesota. Pseudo-Picniccomm asked, "Where's the food we were promised?" It was rumored that a watermelon was seen on a library shelf with an orange sticker on it. At that precise instant in time, Ruffa showed up, carrying a camera, being the only former Star Chamber member to do so: show up, that is, not carry a camera. While he proceeded to use this to steal the souls of the members, Jourcomm_3/2 (Wechsler) reported that TZ 30 was tentatively planned to be a nostalgia issue, and that he was unable to find even one provocative quote to use. Several were then suggested, including "Against stupidity, the gods themselves contend in vain" and "The skinner is a fink!"

Theftcomm report (Ruffa): The photos he was taking were to be used in a new poster for the new takeover of MITSFS.

The meeting slid into Old Business Algol and then into Old Business Locus, where Libcomm reported we got one in. Then we moved into New Business. A motion was made to commend the pseudo-Skinner for wearing a filthy banana colored shirt, which passed 6 stalks worth to 2 feathers and a quockermodger (which is one of those 1ittle wooden stick puppets on a string) to Frank Perdue and one turkey farm +Spehn, thus closing one of the most boring meetings in MITSFS history. But the members agreed it was not the most boring meeting, because Hitchcock hadn't showed up.

\vspace{12pt}

\centerline{Gary Goldberg, Onseck}

\end{document}