\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting

Friday, October 17, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Go over the river Styx, and past the three-headed dog Cerberus, through the dark and vast caverns until you get to the man who is eternally trying to roll a boulder up a hill; then take a left, go on until you find the pool under the fruit trees, where the man who is not allowed to eat nor to drink stands; take a right, and continue to a dark niche lit by a single lump of tallow; and there you will find the Onseck, forever typing out the minutes.

The Skinner called the meeting to order at 5:00 PM SST on October 17, 1975. The minutes of the previous meeting were not read and approved, because the Onseck had left them in his niche. A motion was made to overturn the Onseck, which passed total numbers of words read at MITSFS Minutes to number of words that made sense read at MITSFS Minutes to number of funny words read at MITSFS Minutes. The motion was then carried out in a dastardly fashion, and the Onseck was declared "no fun."

In Committee Reports, Libcomm Miller said the Witter shipment was still in. Pseudo-LHE RHB bored us with the report of about 500 dollars in the bank and 1200 dollars in grants outstanding. Pseudo-Moocomm Pinette reported LSC was showing Dark Star and The Wizard of Oz, and in town A Boy and His Dog were playing, contrary to leash laws. Moocomm MTT reported, to the disgust of all, that the man who did the special effects for Dark Star has been hired to do them for Dune.

In New Business, MTT reported ITL was pleased with the city of Tucson and the surrounding desert. Wechsler moved to make a movie in which the city of Tucson played the city of Tucson, and Irwin T. Lapeer played the surrounding desert: this chickened number of grains of sand in the desert surrounding Tucson to number of grains of sand in ITL's skull to number of grains of sand in those cookies. Someone was censured for only voting once; then a literary discussion of comic books brought on a move to censure RHB for being a spherical work, a vote of a lot to number of motions RHB feels like voting on to something said by Hitchcock that I won 't write down because it would shock the members.

Minicult (Pinette)- from the Tech, a headline referring to the Skinner: "Slime Blob gives clue to how cells Differentiate." Minicult (Goldberg)- somebody has been trying to enchant the Lobby of Building 7 by putting a giant gold pentagram on the floor (more precisely, conjure up a demon there).

Stevens made a nerf motion on that nerf (Hitchcock), passing unanimous to 1 bombastic Harvey to 1 bombastic nerf. Minicult (Starr)- about a bunch of people who were getting rides on flying saucers. He moved to put a Deceased Skinner on the spaceship, which he seconded, and which he then voted on unanimous to unanimous to unanimous. Minicult (Hitchcock)- in the Globe there was a refutation of an Editorial which had said the polygraph was totally infallible as a lie detector. Stevens moved everything Hitchcock said is a lie, passed 1 falsehood to 1 untruth to 82. Contrary to expectations, Hitchcock then did not state, "I am lying."

Minicult (Pinette)- the people who brought you the giant apple are bringing you a neon rainbow over Briggs Field. It was moved to name (inaudible) and Nancy Wheatley as the MIT giant Yo-yo, passed a very large apple to 2750 rotting mushrooms to strings from which rotting apples used to hang.

After several desperate attempts at adjournment, Miller finally moved to adjourn, which took a vote of 11 to (Minicult (MTT)- Recent Mid-American report is out, showing the suckers who signed up; number 2001 is Harlan E1lison, and also listed are Irwin Strauss and Fuzzy Pink Niven) plus 8 to 4, motion passes. Aren't you glad?

\vspace{12pt}

\centerline{Gary Goldberg, Onseck}

\end{document}