\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

The Minutes of the MITSFS Meeting

Friday, February 14, 1975

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The sacrificial victim lay on a table in the library. Just at the stroke of 5:00 P.M. SST, the hooded and masked figure deftly swung the gavel, removing the heart (for this was Valentine's Day). The still beating organ was placed on the exact center of the gavel block. The aforementioned weapon was then swung, striking the mess and producing a loud "squelch!"

"The meeting is called to order," called the Skinner, voice muffled by his ridiculous outfit.

The Lord High Embezzler described the bank balance as consisting of 900.32, having 830 dollars in the checking account and taken in 1064 dollars in dues. The Skinner described the stomach ache he had acquired just then due to the LHE forgetting to mention the other 500 dollars we would get (Bernstein having spent it all, of course).

(Jourcomm/2)_1 announced his brilliant plan to alleviate the shortage of new issues of TZ. TZ 30 would be devalued and issued as TZ 29. Pseudo-Analogcomm didn't have anything to say but, as usual, said it anyway.

Old Business didn't do anything much; neither did Old Business Algol, which chickened through the usual motion, usual actions (though not in public) and usual vote.

The comics were brought to the meeting, for a change, there being a whole drawerful of them somewhere in the meeting room. The 8.14 notes made it, too, courtesy of Harris.

New Business brought a few minicults from our foreign correspondent, Paul Mailman, at the U. of Ill. (pronounced Ill). They certainly do strange things out there, like the man who tried to give away 10-dollar bills, then l-dollar bills- and couldn't. There is also the university official whose discovery of time travel was exposed only when an article on his activities kept getting confused as to exactly when was the future.

RB followed with a reference to Maharishi U. No one seemed to be laughing, though Bernstein seemed to still be feeling the effects of his earlier stomachache, but we were assured that he was amused when he admitted that it was "an inside joke." He just didn't let any of the humor out.

The first Miller motion flopped in the snow, So, also, had the LHE, who, it was reported, had been deposited in a snowbank before the meeting. The nasty grins on the faces of several attendees should have been warning to the person sitting behind the desk, reading (ahem!), but it wasn't. A second warning to Mr. Stallman came in the form of a unanimous motion to censure for said activity, but this didn't do it, either. It took an inverse Ross motion and the efforts of several people who tossed him into a convenient snowbank outside the door (while the rest of us marked time) to get some response. Staring at the person with the gavel, someone moved that we censure the ass who gave Stallman a key in the first place, but it came to naught.

Since there was no excuse for Stallman to wear a banana-colored shirt, the meeting slipped into a snowbank (with incredibly good fortune, just as Costello appeared at the door), and we all took our thumbs out of our books and picked up where we had left off before the meeting.

\vspace{12pt}

\centerline{Happily obfuscated,}
\centerline{Jack Stevens, Vice and Pseudo-Onseck}

\end{document}