\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Minutes

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
As the MIT Science Fiction Society Vice strolled into the Spofford Room, prepared for another ordinary meeting on this stormy September 12, 1975, he suddenly caught a glimpse of a dark shape out of the corner of his eye. Whirling about in horror, the Vice stared full into the face of the thing. His neck muscles tensed, his eyes widened, and his throat croaked out a piercing cry:

"YOU!"

"Yes, I," chuckled the figure, and stepped out into the light; back straight, hand on hip, gavel on shoulder, face bright behind a mass of hair. It was the lost President (the other one) of the MITSFS, Michael T. Timmreck!!! He had returned, and was here in our presence today to preside over the meeting because our Skinner, Bernstein, was busy. "Ha ha, is he busy," said Timmreck with a mysterious little laugh, but would not elaborate.

The minutes were read and approved by both the Onseck and the Vice, Pseudo-Onseck. Pseudo-LHE reported we had 409 dollars in money for new memberships. Hitchcock moved to censure the pseudo-Vice-Onseck for his sex-life with his shirt. When MTT shrewdly pointed out there was no such position as pseudo-Vice-Onseck, a vote was taken to create one, which passed 13-4-6 +SS. Hitchcock and Stevens moved to censure the Skinner for making an honest count and having an honest face. This passed lots to none to one +SS, thus letting MTT outsmart himself for thinking the Inverse Skinner Rule would be invoked. He had to be reminded, to his acute embarrassment, that the rule only works when the motion fails. To cover his blushing, MTT moved us into Old Business Algol.

Here, after Miller thoughtlessly referred to the gavel as a "wrench", a motion was made to censure the former Skinner for his sex-1ife with saucy wrenches. The vote was garbled due to the Vice playing with the Electronic Onseck, so it came out Several Saucy members to Saucy meatballs to Saucy Jack Stevens to 5 +SS.

After someone was censured for trying to find out Vergeltungsflotte's name, the members passed into New Business. The new show Space:1999 was brought up and put down. Goldberg moved to abandon Barbara Bain and Martin Landau on the dark side of the sun, which passed an enormous amount to none to none +SS. MTT commented that he thought Space:1999 was a really good program; an immediate motion came from Stevens to censure the former Skinner for not having any taste on the end of his tongue or anywhere else. The vote, by Stevens' count, was a horrible tongue with no taste on the end of it plus quite a few other appendages to three or four to an aluminum rod (on the table). This motion failed, but then was passed by the inverse Skinner Rule.

A kluge motion was almost passed when 311 members of the Honorary Electrical League voted for it, but when a new member asked what the HELL was a finger motion, followed by a motion for only voting once, were passed. Minicult (Goldberg)- from the Tech, hot off the presses: an LSC spokesman was saying the Isaac Asimov cost 150 dollars 12 years ago, but today he's worth 3000. Several motions followed, but none were seconded, although a motion by Pinette to sell Asimov to extraterrestrials for 24 dollars worth of beads was said to "have merit" by MTT. Instantly, Stevens made a "Merit Motion," which passed 20-1-4 +SS. Bernstein then defined the Merit Motion at the meeting of September 19.

The Onseck then reported a brilliant pun he'd invented. Its reception being less than spontaneous applause, MTT ruthlessly backtracked the Electronic Onseck and erased that portion of tape, thus forever preventing that remark from going down in the annals of MITSFS history. (It was that if Ursula K. LeGuin was ever cured by an exorcist, she would then be dispossessed.)

It was at that moment that the meeting began its long-awaited collapse. Miller motions flew right and left, and the first verse of the closing song was sung. MTT hurled us back into committee reports to find what Jourcomm had to say. Besides RSN, Stevens reported there were two freshmen who said they were comic artists who might help. Then we were thrown forward again into New Business, where Bruce Miller moved to adjourn. This tied, 8 to 9 to 8 +SS. To break the tie, Timmreck demanded pennies and more pennies, finally bringing enough to close the meeting and once again set the members free, out into an unsuspecting world.

\vspace{12pt}

\centerline{Gary Goldberg, Onseck}

\end{document}