\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Have Some More Turkey, Judah?

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Ah, what a glorious and festive occasion! The first night of Hanukkah always brings out the best in a MITSFS member, but moreover, today, the 28th of November 1975, was the day after Thanksgiving, and so we were all properly thankful this night. When the gavel banged down just in time to begin at 5:00 PM SST, we gave thanks that we lived to see another meeting. And then the Vice gave thanks, for our regular Skinner couldn't make it tonight, and so Mr. Stevens got his crack at wielding the gavel. The Pseudo-Skinner said he wasn't going to tell us why Bernstein couldn't make it tonight, but he gave us a hint: some people had mentioned that yesterday there had been a funny taste to the Commons turkey. And we all gave thanks.

The non-minutes were not approved as unread. Pseudo-LHE Miller claimed we had obtained 150 dollars to do TZ with. Therefore we passed through Old Business and mapped into Old Business Algol. Pseudo-Skinner Stevens (try to say that three times fast) moved to condemn Wechsler for making an unusual motion in mixed company, bringing a vote of (10 of Miller's toes + a rather unpleasant odor to less than ten but with a nicer odor to none), the motion is de-FEET-ed.

Into the valley of New Business we rode, and discovered a Minicult (Goldberg): Brentanos is now selling pet rocks, little stones that come with an instruction book on how to train your rock, which cost 4 dollars apiece.

Malcolm Skerry made a pass at the female present, but attempts to work this into an old business algol were unsuccessful.

Wechsler moved to commend Hanukkah as the Festival of Flame, which passed (8 little candles in a row to Hanukkah bush to a cricket). Minicult (Stevens), looking around the room at the members, observed that although yesterday was Turkey Day most of the turkeys made it back again today. And we all gave thanks.

Minicult (Starr): UPI: A life-size model of Hollywood sex goddess Raquel Welch is missing from the Toronto Wax Museum. It was discovered missing one morning, to the dismay of one museum official who said, "When we left last night, she was right there between Martin Luther King and Albert Einstein."

As the meeting had been grinding to a halt ever since the gavel banged down, Miller moved to adjourn. After the typical delays, it was passed (5 to 7 to two gobbles). And we all gave thanks.

\vspace{12pt}

\centerline{Respectively submitted,}
\centerline{Gary Goldberg, Onseck}

\end{document}