\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/5/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 5, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

We commend lyrical spherical diabolical denizens of the deep for allowing the
blue shinies to make it into the minutes.  12-2-Squirel on the gavel block\ps.

\goto{Committee Reports}
\subsection*{Pianocomm}
Paige and Hillary are new Prentices.  Yay.

JSS points out ``Don't be like me''

\subsection*{Skinner}

OSC.  Soon.  Sunday, November 7, and there are still some open slots
for the dinner with him.

Also, we could use workers for crowd control.

\subsection*{LHE}
The small change policy has been discontinued.  We can't make
reimbursements out of even petty cash.

\subsection*{MobComm}
We have received two funny Aussie books.  There's a box of
miscellaneous other books on the way.  And a box of\dots something
else.  I forget what.

\subsection*{PseudoSurgeon}
The boxes of books to be rebound will be leaving soon.

\subsection*{Theftcomm}
TIF rotation really, really, really soon.

\goto{Old Business}
The Onseck is almost albanianed for understanding Malcomm's jokes,
and then declared a Blue Shiny 12-4-2\ps, and thus more powerful than
we can imagine.

It's pointed out that we have a crowd.
Paige explains this as ``I poke people until they come!''.


Still no right lock on 401-D.  TZ real soon now.  We're down a couple
of active keyholders --- they're still around, just boring right now.

ALGOL
\goto{New Business}

A squirrel has been brought to the library.  It is duly blue-stickered
and removed from the library, with help.

\begin{quotation}
"Remember,  remember the fifth of November.\\
Gunpowder,  Treason and Plot.\\
I see no reason  why Gunpowder Treason\\
Should ever be  forgot."
\end{quotation}

It's the 399th anniversary.

Justin is Albanianed, I think for understanding the Onseck's votes.

\goto{Future Business}


The Onseck moves to have the pope burned, and it is instead decided
that we should blow up Parliament on the 400th anniversary next year.

First Miller motion fails 6-20-4\ps.

We still have a ladder.  Perhaps we'll throw it out.

LHE moves for an explanation of bananas and such, this is finger
motioned.

Jamie moves for an explanation of bananas, finger motions, miller
motions, and skinner has no tail at all 16-1-0-3\ps.  Yes, really.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
