\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/9/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 9, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

A Skinnerial Motion to condemn the Onseck for saying we've already
joined the International Banana Society is seconded by that suckup the
Chancellor chickens 0-3-4\ps.

\goto{Committee Reports}
\subsection*{AlohaLenscomm}
We've taken pictures of Die Comissar, and also just Margaret, and
he'll be sending these to major newspapers.  Vice (Margaret, Die
Comissar), suggests smiting him with a chainsword, which passes
7-3-1\ps.

\subsection*{Dexmistress}
95\% of the HAs are up in the air.  Susan and the other volunteers rock.

\subsection*{FrustratedAuthorComm}
has been rejected again.  John asks many questions, and FAC whines
about how her stories ``about aliens trying to make contact with humans
and then the guy accidentally licks\dots I'm just gonna shut up now''
are rejected.

She also abuses the slinky.

A motion to commend FrustratedAuthorComm for her new shiny helmet,
which looks much like her hair, and  which smells like pine-sol, passes
7-1+pinseol-pinesol\ps.  A motion to all go sniff Margaret's hair
fails by Skinnerial Decree.

\subsection*{Bluebellcomm}
We complain, for the Onseck has not ordered us the plastic we need.
``Oh woe is me, for lo I suck!'' says he.

``Seconded!'' rings from somewhere, and a vote is held, whose outcome
really isn't very important.

\subsection*{PseudoMobbcomm}
We have \emph{Commander Toad and the Planet of the Grapes}.  There is
a small amount of rejoicing.  Mobbcomm itself disclaims all
responsibility.  A motion to shelve it with \emph{Lord of the Flies}
fails 2-Dexmitress-2\ps.

\subsection*{Real Mobbcomm}
We now have the whole series of hardcover Telos Dr.\ Who novels, since
their license ran out.  So we have a Complete Set.  There's a new
series coming.

\goto{Old Business}

There is no Dr.\ Who crossover with the Lazarus Long books, and there
was much rejoicing.

There \emph{is} a crossover from Dr.\ Who to Battlestar Gallactica,
which has been left out of these minutes.  Oops.

Aliens may have abducted people to put them on a reality show and let
the winners---or losers---back.

There were explosions and rockets this week.  ``Where?!'' saith the
LHE.  But no sound towers this year, on the Cambridge side, so we
couldn't hear the music.

ALGOL\footnote{with a friendly amendment that Rick Berman is proud of
  having never seen an Old-Series Star Trek episode.}
\goto{New Business}

There's a new Trek movie in the works.  ``Mr. Breasts,'' the man
responsible for much of Enterprise, has been fired.  The movie will
deal with Romulans, and not have continuity with TOS or Enterprise.

There's somebody at her first MITSFS meeting, Diane (DLC).  The
society says ``Hi'', 7-0-1\ps.

\goto{Future Business}

LHE resolves to read Clough books, as they share his name

There are three new ``I, Robot'' trailers up.

We have some new Piers Anthony porn, \emph{Pornucopia} and
\emph{Firefly}.

There are more books on this side of the Library.  Maybe it's because
of the DNC.

A motion to rename the ``I, Robot'' movie \emph{Hard Wired} passed 13-0-1\ps.

There's no ``I have no Mouth and I Must Scream'' movie, but there is a
calendar.

Matrix: that it be noted the Skinner is not time imPeared, but time
Bananad; that Malcolm be Albanianed; and that this be a Matrix Vote 
passes with a score of 99:

\[
\left|
\begin{array}{ccc}
9 & 0 & 2 \\
9 & 5 & 1 \\
1 & 2 & 4
\end{array}
\right| = 99
\]

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
