\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/04/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 4, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

A motion that they be reread with interpretive dance fails 2-13-1\ps.

New procedures are established: $N * 2d6$ seconds per committee report.
It appears that $N=10$.

\goto{Committee Reports}
\subsection*{MobCom$_1$}
Visited SCC.  Box returned.  Lots of Dr.\ Who returned.
\subsection*{MobCom$_2$}
While there, a new banana-colored creature.  It's awfully disturbing.
It's a giant stuffed parasite of some sort.  


\goto{Old Business}

The Koala inhabiting the LP shelves leapt to its death, was cushioned
by to-be-shelved paperbacks, and has scaled the Gor shelves and
``planted'' its ``flag'' there.  It is commended 7-0-2\ps.

A censure of the Koala for not planting the Aussie flag passes 8-4-2\ps

The UA continues to vomit up mail, and has spread a mysterious white
powder around our mailbox.

There is a single undergraduate 'prentice.

There is a new BlueBellComm, SEB.

The HAs have escaped back onto some shelves.  Many of them are
awfully... sticky.  The white powder is claimed to be a dessicant to
keep the books from rotting while in the Sacks.

A condemnation of the Library for failing to distinguish Anthrax
Powder from Cocaine fails for lack of a second.  It is amended to be a
commendation and passes 7-2-5\ps.

AGLOL\footnote{Yes, AGLOL.  Usual Motion, Usual Second, Ususal BING! Vote,
  Usual Debate, Usual Result.}

\goto{New Business}

``Everybody should be stuffed, in boxes.  Jamie says so!'' ---BTS.
Passes 15-4-1\ps.

We have 8000 orange stickers and 120 (and 190 millionths) ells of book tape.

Pandemonium still doesn't give us a discount.  They seem to think this
is news, which confuses us.

A motion to censure C'thulhu for being cute fails for lack of a second.

There is also a banana Scorpio (A NeoPet) in the Library.

A motion chickens because nobody remembered what it was to tell the
Onseck, 3-3-5 plus Special Reserve \ps.

\goto{Future Business}

If J is still VGG in eighteen years, and no other keyholders born in
the interim are available to take the job, BTS agrees to take it.

Starting Monday, meetings will be at 6, which is 1700 SST.

\hspace{1in}\footnote{Absolutely nothing} chickens 4-3-7\ps.

If we irradiate the books, they well be readable in the dark.  And
probably critical mass.

A motion to acquire photoluminescent bananas passes
12-stickers-other~stickers\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
