\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/30/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 30, 2004


\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Approve minutes as ominous. 5-2-3 +Spehn.

\goto{Committee Reports}

\subsection*{Pseudo-PicnicComm}
Picnic next weekend; meet here at 10 AM.

Elections 5-232, twice as good as 5-216. Room needs a name. "New, improved star chamber?"

SCC moved- sort of in one day (move in one, open in about 3). 3 wonders: Montague. Get on Route 2, drive 93 miles, left at the light.

\subsection*{TheftComm}
Rotated with retroactive effects. Rotation was on Feb 15. Y: commend theft for rotating around imaginary axis. 3-0-0 +Spehn.

\subsection*{Pseudo-AnalogComm}
Request summer hours; Jade will generate proto-schedule May 15.

Steer roast now!

\subsection*{Minicult}
Asimov's is declared pornographic. Discussion of Asimov's reputation. D. Ho Manga.

\subsection*{Pseudo-Dex}
Dexes for libraries ready; libraries contacted but have not responded.

Jade: "Forgive me for being fixated on sexy manga."

\subsection*{Sitcomm}
New Dr. Who series, with better production values in preparation.

\subsection*{Vox Sciororum}
Air Force survival manual explains two ways squirrels can be helpful: 1) what they can eat, you can too, or 2) you can eat the squirrels.

\goto{Old Business}

Two vices visiting for picnic. A and Y.

UA office spit out more ancient mail. JM hunted for missing Loci; no luck. Ed thinks he read them. Is he an M.I. fan who burns after reading?

Mission Impossible was the first movie that made Jade not blame herself for not liking it, blaming the script instead. Y: "...bobobot..."

Jack Williamson turned in a novel: he's been writing for 76 years.

Usuals, second, etc.

SRD has contracted four more covenant books, swears "no more." (SF Chron. p. 9)

\goto{New Business}

Brad: robotic traffic cones, almost as accurate as people. Should the BBC buy them as Daleks?

Rock n' roll piper (SFC p. 24).

We haven't been using our free Tech ads.

Discussion of hacks... leads to "reaffirm Society's faith in the Great Pumpkin." (JM) 10-1-1 +Spehn.

Ed opens an envelope to find "How to design a universal artificial intelligence."

\goto{Future Business}

Martyn: in a week, the movie of "A Wrinkle in Time" is on BBC.

"Banana Guard"- individual plastic protectors for bananas in 9 colors.

Google's IPO filing calls for e billion dollars.

Compel Banana Guard to be sold in the USA. 9-0-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1739 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
