\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/11/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 11, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

A shriek from the Vice passes 9-3-0\ps.  Hanh-hanh, says she.

\goto{Committee Reports}
\subsection*{ Frustrated Author Comm}
She says she is as whiny as ever.  She has become one of those whiny
bitter pseudo artists.

A motion to send the intelligentsia of the Library into a very small
room to find an intelligent reason not to write passes
7+Slinky-3-4\ps.

\subsection*{MiniCultComm}
TV Guide asks if anything can be done about American Idol.  They
suggest allowing nonviewers to vote.

A motion to have reality TV destroyed goes unseconded for a while.
Then a motion to have reality destroyed happens, several seconds
happen, and then a vote is held which passes 12-0-2\ps.  A motion for
a matrix vote fails for lack of a second, though the Thunderbunny says
it's a bad joke.  All other motions on the floor fail by Skinnerial
decree.

\subsection*{PseudoFweekComm}
The ASA has been told whom to talk to regarding stuffing envelopes,
Jen Clay.

\goto{Old Business}

We still have a disturbing stuffed animal.

We have a spare shelf.  The skinnner, in her omniscience, knows why,
but asks Jamie to amuse him.  He says it's the same reason as last
time.

We got mail from Andy Su about his new address.

If J is still VGG in seventeen years and fifty-one weeks, and no other
keyholders born in the interim are available to take the job, BTS
agrees to take it.

We can charge fines to bursar's accounts.  This is particularly
terrifying to those still in the thrall of the Bursar.  The Onseck,
having been released from bondage, giggles.

Some evil laughter chickens 4-1-6\ps.

Usual Miller Motion fails 7-13-1\ps.

ALGOL(Condemn the UA)\footnote{Wait, that's indisputable!}
\goto{New Business}
Chronicles of Riddick looks like a WH40K movie --- well, Vice and
Onseck think so.

The Onseck raves about Hackmaster.

The Libraries want the Pinkdex.  They will pay us for it.
Shadowrunners will be dispatched to exfiltrate it.

\goto{Future Business}

There'll be a \emph{Firefly} movie.

The shelves from Avenue Victor Hugo have become ripe and are indeed
overripe.  They want us to arrange a pickup.  This must be done by the
fifteenth or unspecified terrible things will happen.

It is observed that the Library is seeming really fried tonight.

A motion to use lower-fat oils to fry the library, such as banana oil,
passes 7-1-7\ps.


\vspace{12pt}

\noindent
Meeting adjourned, 1600 SST.  No, shoot.  Oh, whatever, we'll deal
with the time shift later.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
