\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/25/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 25, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Margaret Gentile, Vice and
pseudo-Skinner, presiding; Susan Born,  pseudo-Onseck, recording.

Minutes read.

Motion to approve the minutes as being said, 5-1-buddhist cow thing +
0 + Spehn.

{\bing}

\goto{Committee Reports}
\subsection*{BlueBellComm}

All the HAs have been bluebellcommed.  BlueBellComm has no overflow.

\subsection*{HassleComm}

Box of HAs to be hasslecommed has been hasslecommed.  JM says these
are things that have accumulated over many years.

\subsection*{FrustratedAuthorComm}

Still as whiny as ever.

\subsection*{ShelfMovingComm}

Books were moved, and shelves screwed onto other shelves.

\subsection*{ChainswordComm}

It exists.

Motion to commend the chainsword passes by pseudo-Skinnerial decree.

Discussion of doubleheaded eagle on chainsword leads to discussion of
doubleheaded eagles in European national emblems in general, which
obviously was a result of Chernobyl, which hadn't happened yet.

Motion to declare the doubleheaded eagle as "noble, fearless, and
incredibly indecisive" passes 9-2-0+Spehn.

Because nobody would vote chicken where eagles are concerned.  The
forces of evil cause twisted and mutated animals to emerge, which is
why it's the symbol of some empire, not because Russians conquered the
universe.

Chainsword may need more weight in the handle to balance it.  Or more
weight everywhere so MHG can't lift it.

Motion for society to acquire Really Large airmail envelope so we'll
have something to open with the chainsword passes 11-0-2+Spehn.

Motion to hail the great ViceTelzeyToy passes 160-0-pi+Spehn.  The
good kind of pie.

Spiderman II is opening this week, it looks good.

Motion to commend Spiderman II for looking good chickens 3-0-5+Spehn.

\goto{Old Business}

The last cardboard guard on magazine shelving was put in today by ED
so magazines can nestle comfortably without scraping against concrete
or falling to their deaths.  Maybe old high acid paper magazines
should be on low shelves instead of high shelves so they don't get so
hurt when they fall off?  Yes, if there were low shelves.  JM says
that magazines will circulate up on top and down not on top so much
and in the alley and to the slime-covered public.

MHG suggests a cleansing alcohol mist or airlock at the door to take
care of the slime problem with the slime-covered public.  JM suggests
laminating the members.  ARM points out that if we had the space for
all this stuff, we'd use it for books.

MHG tries to hand off pseudo-Skinnerity to AC.  He bings weakly, over
which a duel nearly breaks out between MHG (with chainsword) and AC
(with gavel).  pseudo-Onseck feels under no obligation to explain
this, as MHG herself declares, "I have no idea what just happened."

ps decree - motion passed commending JM for his wise observations
about AC's excellence.

In Which it is Elucidated to All Concerned that the pseudo-Skinner's
soul does not reside in the gavel, and therefore if MHG cuts his head
off he will, indeed, die.  The pseudo-Skinner considers this
carefully.

ALGOL! (with rather unusual cry of Excelsior! from the hall)

Motion to provide alcohol to unfreeze members' brains passes
1-2-3+Spehn.  Power goes to AC's head quickly, he gets drunk, doesn't
know what he's saying.  Don't blame him.

\goto{New Business}

Canals.  Has anyone asked "What's with that plank between two shelves
that's very structurally unsound and should not have books hanging
from the bottom?"  No.  C/PAs have probably enough space, JM decided
things placed at their height probably don't need actual shelves, and
you could put them up in the air, but not everywhere or you'd just
lower the roof.  The current plan is going out to the instrumentality
at some point, as it has been Skinnerially At first there will only be
canals between the hardcovers.  Later there may be canals between
hardcovers and exterior shelves, but these are unnecessary now.  There
will first be canals at either end, so there is a circle.  Magazines
on the interior ring, C/PAs on the exterior ring.  Sometimes you will
be surrounded by anthologies, sometimes flanked by anthologies on one
side and magazines on the other.  We can add more canals internally,
which will give the magazines multiple loops.  These will probably be
popular magazines, which we and the members access more often.  So you
have loop of F\&SF, loop of Asimov's, etc.  Topological library filing
system.

Now that we have canals, should we call the circulating room Mars?  JM
was thinking of Venice, of which these are the opposite.  They are
solid, not liquid; above you, not below you; an obstacle, instead of a
means of transportation.

Suggestion to call them bridges and appoint a pontifex.
Motion to beat Malcolm severely passes by skinnerial decree.

Roof is leading again.  Two leaks by DA, one of which is new and
coming through a light fixture; one in circulating which has been
there for a while.  A facilities guy came, turned off the light, and
moved the light fixture.  Maybe he fixed the leak.

CAC thanked ARM for reporting leaks, because now they are reporting
building-related complaints.

You know how the fifth floor says to pick up packages in three days,
or they'll send it back?  They don't; we got one after a week.  Delay
in dealing with mail in our favor.


\goto{Future Business}

Motion to request MIT to build a thatch roof over the bookcases to
protect the books when the other roof leaks, with amendment to divide
the books into a fantasy and into a SF section to put thatched roof
over fantasy and corrugated tin roof over SF, with AC separating the
books (page by page if necessary), chickens by pseudo-Skinnerial
decree.

A dumbstrucken silence falls over the room, but not for long.

JM suggests a roof that from some angles looks thatched, from some
angles looks like a spaceship, and from other angles drives you mad.
If we had this technology, we should apply it to Dean Benedict's
office to subliminally convince him of things.  Or drive him mad.

Why are tin roofs science-fictionish?  Because they're shiny, and have
that whole cheap 50s movie spaceship and robot thing going.  Tin
robots are vulnerable to oxidation, so they don't have hearts to avoid
circulating blood.  You could use them in oxygen-free environments.
Five-yard penalty for excessive thinking called on the play.

Something is seconded and passes by pseudo-Skinnerial decree.  He
doesn't know what it was.  

When in doubt, fuck it; when not in doubt, get in doubt fails by
pseudo-Skinnerial decree.  He didn't know it was from the Principia.

Do we have a collection of magazine articles?  We have entire
magazines of articles and stuff.  Andrea is looking for
library-suitable reprints of some article in Japan Echo.  If someone
gives us a magazine with a sufficiently science-fictionish article, we
will keep the magazine in its entirety.

Motion to move the meeting for moving or not moving or something
trails off in search of a better one.

Motion to condemn the Skinner and Telzey for choosing to experiment
with coming to the meeting from work via dragons that feed on
blueberries and apples and raspberries and go hunting wolves and
romping through banana-scented forests while chasing small pigs passes
by pseudo-Skinnerial decree. 

\vspace{12pt}

\noindent
Meeting adjourned, 18 minus 15 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Born, pseudo-Onseck}

\end{document}
