\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/10/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 10, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

``I don't think I remember last week'' ---redgerly

``Did we make a \emph{day} for blue shinines?'' ---paigep

The minutes are commended as ``Chickoo''.  Pause, and reflect.  11
students-0-7 cruft \ps.

\goto{Committee Reports}
\subsection*{War Council}
\dots explains the 401-D bibliowarfare center.

``That sounds like cl-----fvck in the making'' --mgentile

We are part of the problem.  We're also part of the solution --katallen

\subsection*{Surgeon and Mobcomm}
We bound a bunch of books at ACME.  It did great at repairing things,
and many of the mass-markets came out quite well.  The paperbacks
which were rebound as hardcovers are now hardcovers, but still
shelfcode P or C/P.

It's not clear how to integrate these into the Hasslecomm ordering.

\subsection*{Vox Scirorum}
A robot squirrel has been released in Floridia and is being treated
as a squirrel by real animals.

The society chickens out on resolving to notify Piers Anthony of this
so that he may involve it in $X(A/N)^{TH}$

Also, squirrels have been implanted into microchips, or maybe the
other way around.

\subsection*{Mobcomm}
There's a bunch of books at Space-Crime waiting for a cheque.  It's
been requested from upstairs, they're sucking.

\goto{Old Business}

MIT Medical still sucks. --redgerly

The UA was having a survey on w20-1 where they gave out bubble tea to
find out what project they should be working on.  ``None'' was not an
option.  Andrew told them to make sure they should ensure they're not
generating negative utility before starting new work.

Margaret plans to infiltrate them, dressed in her Subtle Costume.

``A clock?  Your pancreas has a clock?''

The society chickens out from commending JFC and Margaret for being in
a centerfold together --- this being the \emph{Improper Bostonian}
16-0-17\ps.

Y explains why it is important not to cook your donuts at the wrong
temperature, lest the fat congeal inside the tasty-looking shell.  The
details are too horrible to describe.

There was a term.  Now there's not.

ALGOL
\goto{New Business}

Now there are finals.

There's a new \emph{Charlie and the Chocolate Factory} movie coming,
with Johnny Depp as Willie Wonka.  It's by Tim Burton.

Natter natter, lots of people can't figure out how to not talk when
others are talking.  Gosh, rude people suck.

Miller motion \emph{fails} 15-7-16\ps.

The TIF is gone!

\goto{Future Business}

The TIF will return --- maybe with simplified rules.

Malcolm and Brian trade stories on military intelligence and the
SR-71, RS-71, Firefly, and Lightning Bug projects.

w20 will be closing two and three weeks from now, and there'll be a
timewarp.

Miller Motion 16-5-1\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
