\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 03/19/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 19, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes are somewhat read, but mostly shown around.

Motion: to commend the Onseck for actually taking the minutes in comic
book form
Passes 4-0-1+Spehn

Motion: have the minutes recorded in metapost for better integration
with the Library's Tex-based system\\
Fails for lack of understanding of metafont.

Motion: Note that the Library considers comics interpretive dance\\
Passes 7-1-0+Spehn

Motion: Put Kat in an envelope\\
Chickens 2-2-7+Spehn

\goto{Committee Reports}
\subsection*{MobComm}
Motion: Replace JFC's usual report with a UTF-16 escape code\\
Passes 5-1-1+Spehn

\subsection*{WarCouncil}
Chaos and confusion in the CAC. This is not as good as it sounds---the
boss is on vacation and none of the employees know what he was talking about.
``We have exchanged emails and phone numbers''-ARM\\
``And now the dance begins'' -JM\\

Albanian Motion for JFC, Y and the skull\\
Passes 5-2-3+Spehn

Two boxes of Star Trek books have appeared on the couch.  We know not
why.

``There are bunnyfish.  My God'' -Kate

\subsection*{BurmaComm}
The White House's online store was recently censored since the Bush
shirts were made in Burma, despite Burma being on the
controlled-imports list for being a dictatorship.

\goto{Old Business}
The accumulated donation acknowledgement letters are being mailed
today.

The parts of Bluebellcomm which were not aware of the new covering
material are being made such.

ALGOL (with usual debate in Albanian!!!)
\goto{New Business}
Motion: Censure Malcolm for violating the rules of order\\
Failed for lack of a second.

``Who unchained the Gor books!?!'' -Ariel\\
We've been recently overrun by HS kids from the HSSP recently who are
taking a SF class. We think that the impressionable young minds we're
trying to protect from the Gor books may have unchained them.

About half of our donations have arrived through the MIT mail system.
Each arrival of a package causes the UA office manager to freak out
and send us email. This may put a damper on our plan to use the UA
office as a Library annex by mailing boxes to ourselves.

Motion: mess with KHA's brain\\
Passes: 6-0-2+Spehn

We got more review books from Baen---or, actually, two more copies of
the same books. The first set was to MITSFS, and the second might have
been to Sharion Lee.

``Can you make me Bosnian instead of Albanian?'' -JFC
``We've often in the past determined that Albania is full of many
diverse groups of peoples who do not understand each other's dialects''-JM

About a year and a half ago, a guy said he had 1200 books to donate,
and would happily inventory them for us. We warned him about the pain
this would involve. He sent us email back last week with a complete
inventory, and would like us to take them as soon as possible because
there's a baby moving in or something.

Hopefully, we'll have the allocation things happen.
``Maybe we can have the CAC manager's office. He's always on vacation''\\
``Somehow, the random MIT administrators don't like it when I suggest
that random MIT administrators should not be in the student center''

\goto{Far-Past Business:}
1950\\
``Women are not allowed in Walker after midnight'' but the Society was
granted an exception.

There is an article from someone in about 1950 about kidnapping the
Sophomore Class Presidents.  Brian attributes this and all the decline
of the Freshman Ties.

Motion: Buy The Tech a banana-colored thesaurus and send it back in
time\\
Passes 10-0-4+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
