\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/28/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 28, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Vice motions ``I want my helmet back'' passes 9-4-Spike\ps.  Her
ornate silvery helmet is remanded to her custody.

\goto{Committee Reports}
\subsection*{MobComm}
``I want the helmeh!''

Also, a bit more raiding of Ave.\ Victor Hugo.  It's not as interesting
now, because the letter P is relatively boring.

They close forever on Monday.  The Onseck moves that a holiday be held
in memorial of this on Mondays around this date forever more.  Passes 7-3-3\ps.

A motion to ensure that the new calendar this will require contain no
goats feet passes by Skinnerial Decree.

\subsection*{Bluebellcomm}
Books have been covered.  Shock, surprise.
Mobcomm is still beating it.  There is also ``some'' overflow --- two
drawers and more.

More tape is needed.

\subsection*{LHE}
He will be here this summer, programming a microprocessor for the
Media Lab's Tangible Computing people, 

A motion to commend the LHE for being tangible, or something similar,
passes 10-0-2\ps.

A motion to invite UN election inspectors fails by Skinnerial
Pentiumcomm decree.


\subsection*{PianoComm}
Julia Lieberman, a non-student non-alum seems to want to be a
keyholder, which is somewhat odd.

Mail will go out to all of the current 'prentices this week to tell
them they are prentices.

\goto{Old Business}

Vice is frustrated and whiny at her authorial attempts.

Malcolm moves to appoint a whine taster, which fails by Decree for
possibly violating the harassment policy, as well as for lack of a
second.

JM: Magazines have been moved around, mostly to high tiers.

The C/PAs have been moved to allow the HAs to come out of their
boxes.  They'll probably go back after Inventory.  We're still pulling
HAs out of boxes.

Many implausible---or illegal---War Council scenarios have been discussed.

ALGOL\footnote{Though the usual debate appears to have been unusually irregular}
\goto{New Business}

Niagracomm is founded to deal with liquidation and liberation of space
now in use by unwanted books surplus to requirements.  Ferengicomm is
also suggested as a name.

A motion chickens 4-3-4\ps.


\goto{Future Business}
John Ringo has written some new books.  Many are cool.

A motion to sing a congratulatory song to Ariel passes 10-4-8\ps, and
is truly awful.  Autoalbanian motion to prevent hearing this (by the
onseck) fails for lack of a second.  His next motion, to engage the
Cones of Slience, fails for lack of an \emph{audible} second.

The members begin singing Skinner Has No Tail at All.  When the
Skinner is driven off, the Vice boldly grabs the gavel, holds down all
the buttons, whispers ``meeting adjourned'' and slams it down.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
