\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 7, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

A fog of confusion descends over the meeting, and with a clap of
thunder all present are magically transported to the Spoffard Room: a
location out of legend, whose current form in the physical world goes
by the name ``5-232''.  The disorientation of teleportation from the
world of psets and final projects to the world of MITSFS legend and
lore hits the Onseck hard.  She is further disoriented when she
discovers that this mystical land is outside the influence of the
technological sphere---her MeetingMinuteTaker2000 is entirely dead
here, without the wireless power pervasive in her native realm.  She
is forced to fall back to a primitive method of minute-taking, using
the shredded and reconstituted pieces of large dead plants.

[Onseck's Note: Much of the original source to these Minutes
  was lost in the Great Returning of the Gavel Block.  These notes
  have been assembled from memory, ritual and the outright fabrication
  occasionally required of a disciple of the Meeting.  It is still the
  hope of historians that the original work might someday be found.]
  
[Note to the Onseck's Note: What is believed to be the original minutes has been found in the depths of our filing cabinet as part of 2019's Operation DOMINO. In the interest of preserving this interpretation, the original minutes will be included at the end of this document instead of being interspersed by section.]

Minutes read.


Motion: approve the minutes as having many excellent C-qualities.\\
Passes N-M-R+Spehn

\goto{Committee Reports}
\subsection*{MobComm}
Bought things in accord with its mandate.  SCC indeed moved in a
single day, though it took three to open.
\subsection*{LHE}
We got in all our FinBoard stuff before their deadline. There is much
rejoicing.

\goto{Old Business}
Victor Hugo is closing. JM will go there to look at their shelves.

ALGOL \goto{New Business} Elections: The competition is harsh---last
year's second, the Puppies, make a strong push for several positions,
while the Clockwork Ninja Kitten Princesses of Gor push hard for
President.  After fighting through many gruelling rounds, the
following winners emerge victorious: 

Onseck: Brian ``BTS''  Sniffen\\
Once and Future LHE: Andrew ``What Money?'' Clough\\
Once and Future Vice: Margaret ``Zim'' Gentile\\
President and Skinner: ``Clockwork Ninja'' Kat Allen\\


\goto{Future Business}
In the future, there will be a picnic tomorrow
\vspace{12pt}

Motion commending concerning clockwork ninja bananas\\
Passes foo-bar-quux+Spehn

\noindent
Meeting adjourned, 1730 SST,

As the heavy steps of Atlas-comm thunder slowly away, the glow of the
Spoffard room fades away as if it had never been, until the next
election.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 7, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion to condemn JFC's minutes for being illegible. Chickens 4-2-7 +Spehn.

Motion to commend minutes for being integrated. Chickens 6-0-7 +Spehn.

ED notes that this is the Spofford Room.

\goto{Committee Reports}
\subsection*{PicnicComm}
Food! Lots of food! MHG had to drag it all to the library. Lots of fruit.

"Maybe after [illegible] passes we'll ha." 4-2-0 +Spehn.

\subsection*{LHE}
3.40 in Finboard account. "Funny, we just received a pyramid scheme yellow pages check for 3.40."

\subsection*{hBarcomm}
"Foo bar." Passes 10-0-4 +Spehn.

Quux. Fails 6-7-1 +Spehn.

JM: "That way lies madness."

\goto{Old Business}

William Rice donation processed, the Elizondo donation moved to the couch because the Tellex donation arrived.

MHG's story is on the "short list" at NeoOpsis (the magnet magazine).

Discussion of how the last TZ published was done by Yevgenya...

Aaron and Yevgenya are here. Both former Vices, and permanent standing Picniccomm because they send us postcards.

Asimov once submitted things to TZ... how far we've fallen.

JM started turning the 9 row shelves into 9.5 row and 0.5 shelves. Socket wrenches are essential.

UA sucks. Passes 14-1-0 +Spehn.

"Haiku illuminati puppets?"

Avenue Victor Hugo is still closing. They will be selling shelves, so JM will go look at them. They might serve as proof of concept for the thin shelf space compression plan.

Usual.

\goto{New Business}

Elections!

Onseck: Brian.

Once and Future LHE: ALC.

Once and Future Vice: MHG.

President and Skinner: Kat Allen.

"I can't actually read the votes in Albanian. I'm just pretending." (ALC)

"Someone always falls under the table during elections." (JM)

\goto{Future Business}

The skinner is dead. Long live the skinner. 6-3-3 +Spehn.

"Skinner is a clockwork ninja."

\noindent
Meeting adjourned, 1850 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
