\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/24/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 24, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are condemned 3-0-1\ps for reminding Ed of the puns from last week.

\goto{Committee Reports}
\subsection*{Algaecomm}
Plant will pick up the bagged tiles soon.

Also, we have new filters, which are probably sucking up asbestos from
the air and will need to be abated in a few years.

\subsection*{War Council}
401d still has no lock, and as soon as the CAC figures out how to
glue metal, they'll move people to lockers and we may be able to
``move forward without the lock on the door'' to move us into
Altair-4.  That'll finish up the 2003 ASA space allocations, only a
year and a half late.

\subsection*{Mobcomm_{1,2,3}}
We ordered a used book through Amazon, which came with a special
discount because the seller ``needs the shelf space''.

An SCC run has happened.

\subsection*{FranklinComm}
We got a T-Shirt from Roswell Ltd.  We're not really sure why or what
for.  A bunch of the letter accompanying it is read, and after being
seconded midway through to stop the painful reading, chickens 3-4-7\ps.

\goto{Old Business}
We have \emph{System of the World}, share and enjoy.

ALGOL
\goto{New Business}
JFC starts telling a story.  To prevent this horror, BTS proposes a
Millar motion, which chickens 2-1-7\ps.

\goto{Future Business}
Jade's talked to the MIT library surgeon, who will be showing up on
Oct 8 to look at our backlog and giving advice on what can or should
be fixed.

We may or may not have a shelf-code for Surgery at some point in the
future.

The skinner is moved to desperation to move that the Assassins' Guild
be replaced with a banana.  It fails for lack of a second.

Chris is talking, the meeting has largely disolved.  I second some of
what he says.  It fails for lack of a second.  When this is pointed
out, it fails 2-4-2\ps, with the seconder providing all the votes against.

Miller motion passes 4-2-1\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
