\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/15/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 15, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; JFC, deluding himself in the way of Walter Mitty
that he is as cool as the Onseck, recording.

No loud bing, asks Jade?

Discussion of headaches and Brian's giant bottle of Excedrin follows.
The minutes are replaced by conversation.  JM intervenes to read them,
on the theory that he can't interrupt that way.

Minutes read by Jamie, because the Onseck is late thanks to fog.
BTS appears midway through and continues from here.

\goto{Committee Reports}
\subsection*{War Council}
There's a lock on the door of 401-D.  Now LCS and other such groups
can move in there, and we can move into the thus-vacated
space.\marginpar{JSS moves that this could be run at Intercon.  We
  think he's talking about RV4, something else  Chickens 1-4-12\ps}.

\subsection*{Surgeon}
WHUMP.  Squeak\footnote{heard from Damnation Alley\footnote{She lived.}}.

Jade's been doing some work with the MIT librarians, and they love
her.  They've been offering their resources and Space Age
Technology\footnote{Bronze Age, actually}.  Sadly, Jade is a grad
student and so will only be taking them up on this offer rarely.

\subsection*{Mailcomm}
We got mail from Byelorussia, from a librarian who wants an internship
in the USA.  We don't think we can pay him.

\subsection*{Bondagecomm}
Turns out the MIT Libraries also use ACME Binderies.  And they were
used by the \$10k gigantic Bhutan book.

This leads to a discussion of the fact that we and the Libraries have
``something going on,'' and we are payed for pollinating them.

\subsection*{Mobcomm}
Damn. --Skinner

We have \emph{Going Postal} and the new \emph{Dark Tower}.

\goto{Old Business}

\dots Speaking of manholes, there was an accident this week in which a
worker was trapped in a sewer and drowned.

Societas Delenda Est.

ALGOL
\goto{New Business}

After bumping into the AT--AT for the zillionth time, AMB raised it a
few inches.

There's a ladder in the Circ room.  After establishing that it's only
there for Plant's convenience, Jamie resolves to move it after the
meeting.

The surgeon is somewhat commended for creating space in the library by
declaring four books dead, 7-0-7\ps.

\goto{Future Business}

Soon there will be 25~lbs.\ of lead shot in the library, in big bags
in a box or something.  It should be placed someplace safe, so as not
to refloor the library with lead shot.  It should also be placed
someplace safe \emph{for us}, as while 25~lbs.\ of lead hurts no more
than an equal amount of anything else, it still leaves a mighty dent.

Miller motion fails 5-7-4\ps.

A motion to acquire bananas or plantains for weighting down the books
fails for lack of a second.

A motion to stuff J in a big bag of bananas until he smothers passes
8-$2\frac{2}{2}$-4\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
