\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/02/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}
\emph{Bonus Pre-Meeting Quote:}
``Your consciousness will still continue in emulation, imprinted in
the cosmic dust somewhere'' -ED

\emph{Bonus Pre-Meeting Physics/Philosophy Geeking}

MITSFS Meeting Minutes 

Friday, April 2, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Move to approve the minutes as having a positive determinant\\
Passes 8-2-1+Spehn

Move to commend the Onseck for obeying Kramer's Rules of Order\\
Chickens 8-1-8+Spehn

\goto{Committee Reports}
\subsection*{Pseudo-WarCouncil}
The Tech reports ``ASA allocation plan not yet final'', and ED/ARM are
misquoted.

\subsection*{Onseck}
Order forms have been submitted to the LHE's pile, to be sent upstairs
for checks and then mailed to magazine people.

\subsection*{Quasi-MobComm}
English books got picked up before the UA office manager managed to
yell at us about them.

\subsection*{hBarComm}
We have an LSC slide for RotK this weekend. It does not have Bananas
of Gor

\goto{Old Business}
Some of the boxes of donations have been unboxed.\\
``Scream and then invite all the enemy spies to the War Council is not
in the Dzur approved procedure manual''

Many many (180) Star Trek books arrived as well, including Shatner's
daughter's account of Shatner's experience in the making of Star Trek
V.

Motion to have Alan Dean Foster ghostwrite reality\\
Chickens 2-1-4+Spehn

Lack of Usuals

\goto{New Business}
In those old donations, we have new Klingon audio tapes, teaching
Power and Conversational Klingon.\\
``Power Klingon will help you discover the Warrior within''

HellBoy opened today and got rave reviews from the NYT and Salon,
``It's apparently a better depiction of Catholic theology than the
Passion''

\goto{Future Business}
In the future, pre-frosh will be here.

32 hours into the future, there will be a vast temporal discontinuity
which will wash over the continent from East to West.

\emph{Some discussion occurs, in which, at one point, JFC threatens to
  read more romance novel blurbs}

Motion to commend the Society for their Banana-based system of
timekeeping which is unaffected by the aforementioned temporal
discontinuity.\\
Passes 12-2-5+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
