\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/16/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 16, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes mostly-read by JFC, who can not read his own writing.

Motion: Condemn the minutes as inaccurate, illegible, inarticulate,
ininspiring, and interruptable\\
Passes 3-minutes-1+Spehn

Brian makes a motion. It hurts Ed, and fails for lack of a second

\goto{Committee Reports}
\subsection*{LHE}
Some confusing errors occurred and we gave JFC an extra \$0.05.  We are
going to start copying the FinBoard forms as well.
\subsection*{$Mobcomm_1$}
There are two more Dunesenny books.

The SCC is moving, Victor Hugo is closing, and Sasuga (in Porter) is
closing and will be web-only.

\subsection*{$MobCommm_2$}
We have ordered lots of paperbacks
JFC would like to have a MobComm run on May 1 with a Star Chamber
member and a keyholder of any flavor who does not inhabit the same
physical form. ALC volunteers.

\subsection*{PicnicComm}
Elections: May 7th\\
Picnic: May 8th

\subsection*{Onseck}
Magazine orders are going in.

BTS reads us something weird.

Y reports that the Mobile Book Fair has copies of ``How to Outwitt a Squirrel''

\goto{Old Business}
The Cavin donation arrived. 

Motion to allow the Cavin donation to vote\\
Passes 8-1-1+Spehn

A matrix of painful puns, Albanians and 

ALGOL
\goto{New Business}
``It seems that, since there appears to be a policy for fining people
for getting off rooftops, but not going up, and the policy is clearly
not codified in any way, perhaps WarCouncil can acquire the acres and
acres of free space across the street''-BTS

We have a report about Indian nuclear scientists who can extract juice
from bananas. 


Motion that people bringing strange bottles into the Library \emph{do
  something which was not recorded}
``We use fixer for that''-ED
``Fixer developer mixer... but I... but I...''-BTS

Motion: Its easier to Albanian BTS\\
Does nothing: 3-3-2+Spehn

More sadness from iRobot---their eyes glow red when they go insane.

Motion: send a team of killer robots after the scriptwriters\\
Passes 10-0-1+Spehn

Y suggests that we give the robots dark glasses before sending them out.\\
Fails for lack of a second, so the world is saved.

``Isn't that millenia?''-ED\\
``It says milleniums''-JFC

``It's sensuous and salacios'' -JFC\\
``That and Jesus doesn't mix'' -Woz

The sequel to QuickSilver is out.

``Human intestines were not intended to take the abuse of Goya banana
nectar'' -Woz

\goto{Future Business}
Theftcomm: Perhaps in the future, the TIFF will rotate. JFC notes a
protoTIFF near JM on the desk.

``In the future, if someone says ``Miko Miko Nurse'', run away.''-ALC
These instances are determined not to count.

Our practice with HSSP students has prepared us for prefrosh.

Discussion ensues of prefrosh-oriented activities which will cause
them sugar shock---chocolate science, free donuts, etc.

Motion to add to the prefrosh's impending sugar shock by providing
them with bananas (or maybe banana juice)\\
Passes 4-3-0+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
