\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 8/27/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 27, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Their last line, ``And now it is time for dinner'' 3-Neo-Opsis-2\ps.


\goto{Committee Reports}
\subsection*{War Council}

Altair-4: Real Soon Now, and then when it's done it'll be even Faster.
We'll get a code to the SAO as soon as possible.

\subsection*{I can't believe it's not Asbestos!}
There will be an abatement.  It'll have some warning and we'll get a
chance to influence the date a bit.

Maybe we can engineer something cool to get new rooms out of this?

\subsection*{LHE}

Yup, there are reimb--- reimbur--- um, money.  We now owe SFBC even
more money.  Soon!

\subsection*{Pseudo-Fweek}
We've got a frosh!  She's got a SIPB temporary tattoo, which makes her
even more disturbing than most of our cruft.

Activities midway next week.

\subsection*{Skinner}

Skinnerial Standard Time change the week after next week---that is,
the tenth.

George Flynn is feeling better and walking again; the card's been sent
to him.  He's in Wingate at Brighton, for anyone who wants to visit
or contact him.

Jade will be the Surgeon.  No training, but willing to go seek it out
and get it.

\subsection*{MobComm}

Pseudo: still a backlog at the New England Mobile Bookfair.

\subsection*{RSNComm}
Jourcomm.  Frosh.  Rescheduling.  Canals.  New England Mobile.

\goto{Old Business}

New detail about physics: some guy has a trick with the math involving
the famous two-slit experiment to figure out which slit a particle
went through, even though it's still generating an interference
pattern on the wall.

ALGOL
\goto{New Business}
The Banana Split is 100 years old.

U.~Queensland is trying to build a banana-based power generator.
We chicken out from commending them 15-0-6\ps.  Yes, 15-0-6.

\begin{quotation}
  \emph{Skinner cannot count at all, count at all, count at all.  Skinner
  cannot count at all beyond one bloody stump.}
  
  \emph{Skinner cannot count at all, count at all, count at all.  Skinner
  cannot count at all beyond two bloody stumps.}
  
  \emph{Skinner cannot count at all, count at all, count at all.  Skinner
  cannot count at all beyond three bloody stumps.}
\end{quotation}

\goto{Future Business}

Primitive gas masks sucked.

There are parents here\footnote{well, not here}.  Yech.

``Kill em all'' passes 7-0-3\ps.

A motion to kill them all and use them as power for the vast banana
and parent-powered generator which will fuel the War Council and the
vast War Machines led by space marine terminator frusterated author
commisar Margaret passes 8-4-3\ps.

Miller motion. 3-4-0\ps.

Except that was a matrix vote with a determinant of 24, so that fails
with a determinant of 24.

``Look, a virus!'' 

``Look, a banana colored virus!'' chickens.

Ed will be more theftcomm in the future.

``The Albanian word for banana is, um, banane'' passes 11-0-0\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
