\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/23/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

Bonus Pre-meeting Quote:\\
``Tentacle porn is not for Valentine's day''\\
``It's not nice to make Margaret cry''
\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 23, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Accept the minutes as very verbally read.\\
Fails for lack of a second

Motion: Woot!\\
Passes 10-1-1+Spehn

Motion: Somehow prevent this meeting from being ended by a banana
motion\\
Fails 10-1-4+Spehn

Motion to condemn the Skinner for messing with the space-time continuum\\
Passes 7-1-6+Spehn\\
\emph{Onseck's note: The inverse-skinner rule applies}

\goto{Committee Reports}
\subsection*{Pseudo-War-council Report}
We have to move now---we just got the ``How to move everything''
catalogue. We could buy billions of chairs, and then use the catalogue
to move them. Or, we could just push our rolling chairs around the
hall.

\subsection*{Onseck's Report}
I bought some tape.

\subsection*{Pseudo-Bluebellcomm}
ALC covered a book. He was trained for this express purpose.

\subsection*{MobComm}
Neil Asher, other new things are here. 

Move to express sympathy for the Age of Reason on the basis of the
company it's required to keep.\\
Passes 7-2-1+Spehn

Discussion of some of the absolutely awful things that are on the Baen
Free Library, and whether or not we actually still have a mouse, or
whether it has abandoned us for the Mecca of the Tech's office.

\subsection*{WarCouncil}
We have been told that the renovations requested are ``not
impossible'', and an outside contractor has been engaged in the
contingency that the move is, in fact, not impossible.

\emph{Onseck's Note: The meeting then broke into chaos, as JFC caused
  everyone to want  to look at the angel duck on Psi-Phi}

\goto{Old Business}
The Wheel of Time 0 book we got is the beginning of a trilogy.  Much
angst ensues.

Motion: Lock Jordan up and make someone else finish his books.\\
Fails for lack of a second.

There's a new Laurel K. Hamilton book, ``Seduced by Moonlight''.\\
``She's been seduced by everything else, why not?''-BTS\\
The warning on the back of the flyer now admits that there is ``lots
and lots of explicit sex'' in the book---SFBC, at least, feels
compelled to admit that they're publishing porn. \\
``It gives me hope that I may someday get published, as there is
writing out there worse than mine''-MHG

The Sci-Fi Marathon is this weekend, and we have a slide!

``Are you looking at pr0n?''-MHG\\
``No, I'm looking at cute female sci-fi authors''-JFC

Motion: Set JFC up with Anne McCaffery\\
Chickens 1-2-6+Spehn

``I don't want to go to Ireland''-JFC\\
``Just dress up like a dragon and she'll treat you well''-JM

An argument ensues about whether the dragonriders are intimately
involved with their dragons. MHG suggests that the dragons are Burma
Jets in disguise.

ALGOL
\goto{New Business}
``That's been patented''-BTS\\
``What, spam ads improving bings?''-JM\\
``Um... no, but now that you mention it''-BTS

KHA's laptop came back repaired from Apple in 3 days, because, though
they told her it was usually not covered under warranty, being willing
to yell at people will make them do things for you.

``That's not usually covered under warranty''\\
``But it should be!''\\
``Ok''\\

An imagined conversation':\\
``The reading room isn't for student groups''\\
``But it should be!''\\
``Okay''\\


Motion: to note that the Onseck is not a member of the Rubber-Band
Illuminati\\
Chickens 3-devil-duck-4+Spehn

Motion to condemn Richard Stallman for making emacs available to
automatically compile and execute code in open emacs buffers.\\
Fails for lack of a second

Albanian Motion against JFC\\
Passes 12-6-4+Spehn

Motion to send MHG on a mission to discover the difference between
porn and prawn (and not report back to us later)\\
Passes 8-4-0+Spehn

Move to note that the important thing about real estate in California
is ``default''\\
Fails for lack of a second

Motion that somebody should make a banana motion\\
Passes 7-1-0+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
