\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/23/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 23, 2004


\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Miko Miko Nurse\\
Chickens 3-0-4+Spehn

\goto{Committee Reports}
\subsection*{MobComm}
The large boxes of paperbacks have been working their way through the
large digestive tract of the Library. 
\subsection*{LHE}
The budget was submitted, and we have Ops money for the Picnic. All is
well, though complicated.
\subsection*{Onseck}
Magazine requests submitted, except for the new one.
JFC suggests that we get the magazine associated with PSPublishing. 

Motion to commend Google\\
Fails for ``It goes without saying''

Motion to recognize that Google is orders of magnitude larger than
everybody else and the source of all things \\
Fails for lack of a second.

\subsection{$MobComm_4$}
JFC reports that JD Robb and Nora Roberts have co-authored a book.
These are pseudonyms for the same person.  

``It could have been a clever publicity scheme, or maybe they lost
track of how many people they are''

``Maybe someone at the publishing house said ``Hey, I like
these two authors'' and sent them an offer, and the author said,
``Hey, I can get \$40,000 for writing one book, or \$30,000 for
co-writing... this is a good deal!''

Motion: Commend nefarious plots of this kind\\
Passes 4-0-1+Spehn

\subsection{$UA_{Sucks}Comm$}
Mail from last summer just appeared when ALC searched through the UA
back office.  We got at least one magazine a year late.

Discussion of Byzantine Policies which are somehow causing three door
instantiations to be less feasible than one door.  

Discussion of \$10,000 doors and bribing the four year old in charge
of the whole mess.

Discussion of arbetrage around the Institute Door Provisioning System.
Discussion of accidental door-sized holes appearing in rooms and
plausable deniability.

``But it's all in the minutes! Foiled Again!'' - ED

``Stata cost \$4 billion dollars. For that, we can build an entire
Student Center out of Lego...''

Discussion about how we will *NOT* have ``bookshelves that think'',
or MindStorm buildings.\\
``There are at least 50 books in this room alone that talk about how
that's a really bad idea''-BTS

In other WarCouncil rooms, there are clever plans to renovate the
basement and do clever things with it.  The Hobby Shop is definitely
moving into the place currently occupied by the Computer
Connection. This is a plan in the ``hmm, what should we do?'' stage,
but it has Professor Slocum involved.

``I think we should divide the sub-basement into three things: one
third for storage lockers, one third for video games, and one third
for the development of morlocks'' -JM

``Speaking of which, has anyone heard about what's moving into Arrow
Street?''\\
``They're certain that lots of people will be interested in paying
exorbitant rents and charging reasonable prices for excellent food.
Well, if not excellent, or even good, its food that, while
Benedict wouldn't feed his dog, he is happy to feed the students''\\
``And all this will happen Real Soon Now.  And, speaking of which,
have we heard about TZ recently?''\\

Motion to have TZ start selling advertising so that they can purchase
space downstairs?\\
Chickens 3-4-1+Spehn

Discussion about following the MicroSoft development model: have
multiple issues of TZ in the pipeline at the same time.  Other
discussion ensues concerning the possible repercussions of this model.

Discussion of telephone-pole and rubberband systems for renovations.

\subsection*{PicnicComm}
The directions will be better than ever, the invitations are going out
in a Real Soon Now manner entirely different than that of TZ, and all
is well. 

Elections May 7th\\
Picnic May 8th

\goto{Old Business}
``The Cavin donation can no longer vote, having moved out of its
member-imitating spot into a corner where it is doing no harm
whatsoever, except making it impossible for fat keyholders to get to
the lightswitch, and making it impossible to open the BondageComm
drawer. In fact, I took the liberty of welding the drawer shut, but
you can't tell, because its entirely obscured by the boxes.
But once I move the boxes, you still won't be able to open it up, so
don't bother nagging me about it'' -JM

ALGOL

Motion: Albanian Motion for anyone who has said the word ``Usual''
Passes 12-7-3+Spehn
\goto{New Business}

There are at least three people more than usual who are taking notes
on this meeting.  They're from Harvard, in an anthropology class on
SciFi and its greater implications for society.  Their paper
assignment is to observe a science fiction group.

\goto{Future Business}
The anthropologists make Brad nervous.\\
The ISS's gyroscope has broken. They are apparently doing spacewalks
to try to fix the problem. Coincidentally, they just launched the
gravity probe with the Best Gyroscope Ever---its a plot out of Hollywood.

In the future, we hope to get to the picnic without going to Cape Cod.\\
``There is a simple way to prevent this ...''-JFC\\
``You mean by blowing up Cape Cod?''-JM\\
``Two ways...''-JFC\\
``Blowing up the bridges?''\\
``Having the picnic in Cape Cod?''-Brad\\
``Okay, there are many ways to prevent this...''-JFC\\
``To prevent that mistake, Miller Motion''\\
Fails 9-13-0+Spehn

Singing begins: ``Skinner won't go to Cape Cod, to Cape Cod, to Cape
Cod...''\\
The singing somewhat continues as BTS makes a motion: \\
``To make sure that all of the food, the ham, the turkey, the gavel,
the bread, the watermellon, the banana, the frisbees, and all the
other picnic-related things be put NOT IN JUSTIN's CAR' so that if
this happens again we can still have a picnic.''\\
Passes 10-0-4+Spehn
\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
