\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/23/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 23, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, now, 1700 hours right here SST in the
library (now), Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Malcolm (Y) motions that the reading be commended as showing great
elocution.  Passes 4-0-2\ps.

The reading is condemned for insufficient electrocution,
many-120~volts-2\ps.

The Onseck in then commended for being flame retardant, 9-2-3\ps.  The
testing will happen \emph{outside} the Library.

\goto{Committee Reports}
\subsection*{MobComm}
1: We have new books, including some by Michael Marshall Smith.  Crazy!  It also
has a new sort of double.  Thrill!  Some samples are included.  Kaboing!

2: I want to SCC.  ``Eeeeeeeee!'' says MHG.  There's lots of new stuff.

3: We have a bunch of Gold\&Griffin Publications.  These are not
visible to our normal purchasing means, so this is cool.

Pseudo: SJW said he'll get us more Circlett press.

\subsection*{Onseck}
We're out of LHE reimbursement forms.  Lo, do I suck.  I'll go deal
this weekend.

\subsection*{Frustrated Author Comm}
Moo.

\subsection*{Algaecomm}
There's less of a flood, and it may be possible to stop them from
recurring if we use bleach on the A/Cs once in a while and get Plant
to change the air filters more often.

jhawk rocks.  Rock!

The last remaining leak is apparently still a problem, and Plant may
fix it by doing something which will flood us elsewhere, or the tech,
or, if MHG gets her way 

\subsection*{War Council}

The back room of the UA office has been entombed.  Oops.  Perhaps a
door will be added.

\subsection*{JourComm}

He's alive!  This nixes the major theory on why there is no TZ.
Now we think he may be pining for the Fjords.  

But he's done cool carpentry and expects a publication in well under a
month.

BTS moves to encourage jourcomm by nailing him to his perch if there
isn't a TZ in three weeks, but this 4-2-6\ps.

\goto{Old Business} 

Ave.\ Victor Hugo shelves have been circumsized
down to size so as not to be circumscribed by the ceiling.

Vice comments on their bottoms.

Onseck moves:

\begin{quotation}
       O proud left foot, that ventures quick within \\
       Then soon upon a backward journey lithe.\\
       Anon, once more the gesture, then begin:\\
       Command sinistral pedestal to writhe.\\
       Commence thou then the fervid Hokey-Poke,\\
       Mad gyration, hips in wanton swirl.\\
       To spin! A wilde release from Heaven's yoke.\\
       Blessed dervish! Surely canst go, girl.\\
       The Hoke, the Poke --- banish now thy doubt\\
       Verily, I say, 'tis what it's all about.\\
\end{quotation}

John moves to Albanian him.

The skinner then makes this a matrix vote, which has results
  $\left|\begin{array}{ccc} 1 & 7 & 5 \\ 5 & 0 & 8 \\ 9 & 7 &
  6\end{array}\right| = 413$

ALGOL
\goto{New Business}

\begin{tabular}{p{.4\hsize}p{.4\hsize}}
Vs jr pna trg fbzr anvyf, jr pna svk gur furyirf sbe gur arj P/CNf.

\verb*. .bua fgbccrq va Fxvaare Fgngr Cnex naq znffnperq fbzr zbfdhvgbrf.

L nfxf gur Bafrpx gb abgr gung gur Fxvaare xvyyrq avar ng bar oybj.

Gurer'f n arj zntnmvar sebz CF Choyvfuvat, \emph{Cbfgfpevcg}.  Jr
fubhyq fhofpevor, gubhtu abg gb gur Qr-yhkr uneqpbire rqvgvba, nf vg'f
cevprl.

Jr unir arj tybirf, juvpu L abgrf ner onanan pbyberq 7-1-3 cyhf Fcrua
.

&

If we can get some nails, we can fix the shelves for the new C/PAs.

John stopped in Skinner State Park and massacred some mosquitoes.

Y asks the Onseck to note that the Skinner killed nine at one blow.

There's a new magazine from PS Publishing, \emph{Postscript}.  We
should subscribe, though not to the De-luxe hardcover edition, as it's
pricey.

We have new gloves, which Y notes are banana colored 7-1-3\ps.
\end{tabular}

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
