\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/30/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 30, 2004
\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Condemn the minutes for not explaining why JFC was Albanian'd\\
Fails 5-8-0+Spehn

Motion to stuff JFC and MHG into a Burma Jet and see if it is better
than being intimate with a dragon\\
Passes 10-9-0+Spehn

Motion to augment MHG in the above motion with a wherry.\\
Passes 7-4-1+Spehn

Motion to purchase surplus Burma Jets for the Library\\
Chickens 4-5-12+Spehn

Discussion about whether the government will remove the secret weather
control satellites before selling us the jets.

Several motions fail for lack of a second

\goto{Committee Reports}
\subsection*{Pseudo-Bluebellcomm }
JFC covered the anti-superhero book

Discussion about composite wood-and-silver bullets which explode, and
how to get rid of invulnerable bad guys.

``Hey, meta-normal! I'll give you a really shiny barometer that I'll
give you if you go away''-JM\\
\emph{Explanation: There is a physics question about how to measure the
height of a building.  The real answer is not as funny as the wrong
answers, including:\\
Drop a barometer off the building and time its fall\\
Bribe the building manager with a barometer\\
Threaten the building manager with the barometer, etc.}


\subsection*{MobComm}
In order to not do anything, bought a book that he's now going to
donate because it's horrible.
We will not dignify the book by repeating it here

Motion to Albanian the book\\
Passes 19-0-0+Spehn

\subsection*{Onseck}
Bought a calendar for the Library, but it was a mutant. The Sentinels
will be coming for it shortly.

Purchase a Sentinel for the Library\\
Passes 14-0-4+Spehn

Move to send a representative to the fruit store to buy sufficient
dates for the new calendar\\\
Chickens 4-0-5+Spehn

\subsection*{WarCouncil}
We have an estimate on a set of renovations which may or may not be
what we want to be done, including \$5000 in painting.  
BTS suggests that we ought to get a mural of William Shatner in
Zardoz, because it won't cost more than we're already paying, and it
would keep the books from being bothered by patrons.

\subsection*{Coufcomm}
The other box came, dated September 12 or December 9, depending on how
you read it. They are the largest collegiate SF group in Britain, and
are only 10\% our size.  

Motion: Evil Laughter\\
Passes 15-0-1+Spehn\\
\emph{Onseck's Note: The Evil Laughter is recorded in the file
  ``LHElaughs.mp3''}

\goto{Old Business}
A few weeks ago, maybe longer now, this poster was put on the door
saying ``no food, we have a mouse''.  We decided that since the mouse
is not evident, the sign can come down.

Motion to Albanian JFC's drink\\
Passes 4-2-2+Spehn

Technique came by to shoot photos for the yearbook. They were
fascinated by the Gor books, so they took posed pictures of patrons
with the books.

Much discussion ensues about MHG and the Gor books and costumes, which
results in a motion that passes 12-8-1+Spehn

Motion to make sure Aloha-Lenscomm is there\\
Passes 8-4+pillowsandshinythings-1+Spehn

Motion to make today official Pick on Margaret Day\\
Passes 7-6-2+Spehn

The Skinner and Chancellor will be going to NESFA's business meeting to warn
them that we might be begging them for money soon.

ALGOL

\goto{New Business}
``The premise is that Nebraska has an earthquake, and floods''-JFC\\
``And gets replaced with a sea of creamy corn, or am I mixing up two things?''-JM
The clock says that it's raining in the circulating room.  MHG says
that the clock is redirecting signals from the Burma Jets and
Colorado.

Move that the Society post Burma Jet signs
Fails for lack of a second

Move that the the Society acquire Burma Shave signs and then turn them
into planes

We could rewrite the minutes in the Burma Shave format, and then post
them leading to the Library... or we could take a book that we have
too many copies of and then put the pages serialized along the
corridor.

``You know someone will complain if we only post every other page''\\
``Yes, but that's Jhawk: he's a keyholder, so he can let himself into
the Library and read them himself!''

Motion to post the last page of every Agatha Christy novel along the
Infinite, with a note saying ``Now that you've finished mysteries,
come read something better...''\\
Passes 10-2-0+Spehn

Motion: Make February ``Ask Members if they're Ebay addicts'' month\\
Passes 8-0-2+Spehn

Motion to declare March ``Ask Bananas if they're Ebay addicts'' month\\
Passes 7-0-4+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

Bonus post-meeting quote:\\
``Second generation people are cooler. They get special powers''-JM\\
``Like not being able to leave?''-JFC\\
``Yes.''-JM\\
---\\
``I don't make a habit of gazing into the bottom of the pen-cup''-JM\\
``That must be one of your special second-generation powers''-JFC\\

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
