\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/29/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 29, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are approved as being the very model of a modern major general.
12-5-2\ps.

\goto{Committee Reports}
\subsection*{Skinner}
Orson Scott Card lecture is happening soon --- November somethingth.
We need people to volunteer for crowd control.  You don't get a gun,
but you do get a six-year-old Colonel following you around and wiping
out whole species 9-2-7\ps.

Motion to allocate \$200 for tear gas and gas masks passes by
acclamation.

The shortest ever ASA General Body Meeting preceded Game 4 of the
World Series.  There's a new graduate member at large, who seems to
Have Pants and sympathize with our goals.

\subsection*{LHE}
I should go figure out how purchase orders work.  See below.

Lots of reimbursements went out in a batch today.

\subsection*{FAC}
Usual whine.

\subsection*{MobComm}
It's been requested that we switch to purchase orders or prepaid or
something, because the reimbursement process is badly broken.

The next batch of cheques will prompt an order for some unusual books.

\goto{Old Business}

There are three boxes of stuff (containing ``magazines and what'')
which we might like to get bound.

There's still a bucket in the circ room.  We can probably unplastic
the reserve room stuff now.  A motion to remove \emph{20000 leagues
  under the Sea} from the library fails for lack of a second, and a
motion to remove the Piers Anthony novelization of \emph{Waterworld}
with commentary by Kevin Costner leaving first chickens 5-3-12\ps.

ALGOL
\goto{New Business}

Paige's blue ribbons match Rebecca's cybernetic organs.

Frictionless motion has been developed in building 36.
Well, not ``I have a frictionless surface and it's mine and it's beautiful''---Kat.

\goto{Future Business}

The universe is censured for failing to end when the Red Sox won the
World Series, and a Miller Motion chickens 7-5-7\ps.

LHE's Second fails for lack of a Motion.  This leads to a train of
Seconds and Fifths, culminating in a ``NOOOO!'' from the Skinner.

ChrisK shows up at this point, so we timewarp to Committee Reports so
that he can experience the whole meeting.

New victim!  We say Hello to Kevin 8-0-1\footnote{He fears change}\ps.

Justin moves to commend the long-ago-read minutes for mentioning a
bananimal.  This is lame and fails by Skinnerial decree.

Three motions:  to trip that motion over a banana thus making it more
lame 6-3+a cyborg-2\ps.
To Albanian Justin for that, 4-7-9\ps
To have a matrix vote, 3-3-13\ps.

This passes with determinant $\left| \begin{array}{ccc} 6 & 3 & 3 \\ 4 & 7 &
    10 \\ 3 & 3 & 13 \end{array} \right| = 277$.

\vspace{12pt}

\noindent
Meeting adjourned, 1755 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
