\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/22/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 22, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are approved as being mathematically challenging, $\frac{16}{2}$-$\frac{12}{3}$-$1$\ps.

\goto{Committee Reports}
\subsection*{War Council}
401-D still has a lock.  CAC won't tell ASA what's going on, but there
may still be some asbestos in there so nobody can move in until the
abatement finished.

They swear it'll all be done by the end of IAP, and it sounds like
that includes the moves.

CRiSP appears to be run by a scientist.  We don't think he's fictional.

\subsection*{PseduoLHE}
Now we have to go to NE-49 to make deposits, rather than the Corridor.
We might be able to do small deposits through the CAC office upstairs,
or through night-deposits to Fleet wearing a CAC hat.

\subsection*{MobComm}
We have new paperbacks.

We also have \emph{Jonathan Strange and Mr.~Norrell}, Susanna Clarke's
new book.  It comes highly recommended by Gaiman and the usual suspects.

\subsection*{PseudoSurgeon}
We're sending some books to ACME, including a badly torn Potter.

The order will be filled out with some paperbacks being rebound as
hardcovers.

These books are having their covers taken off before being sent to
ACME, because the covers won't come back.

Also, some books are being withdrawn as unusable.

\subsection*{PseudoVGG}
At some point fallow members will be moved from the main rolls to a
special book.

\subsection*{Bluebellcomm}
We experimented with bluebellcomming things before they got
Panthercommed and this seems to work.

Jamie rants about how Bluebellcomm will fuck this up in general.

\goto{Old Business}

D\&D's 30th anniversary was, depending on how you count, earlier this
week.

Stephen Brust's commentary on George R.R.~Martin appears to be ``For
crying out loud, what's taking so long.''

ALGOL

Harlan Ellison is returning the money donated to his legal offense
fund, as he has apparently settled.

ALGOL Seconded.  We actually have a vote, it chickens 4-1-4\ps.

We have to do it by hand:
\begin{quotation}
Where are the Comics?  The Comic books are in California.

Where is Ed?  Ed is skiing in Colorado.

The Librarian made a pass at... Move to censure the Librarian.
\end{quotation}

\goto{New Business}

There's a $2\ell$ bottle of lead shot, about 1mm diameter.  It leads
to a discussion of the packing fraction for randomly distributed
spheres.

There's a bucket in the back!  Why?  We're not sure.  Also, the
ceiling has been replaced and appears intact across the whole Reserve
Room.  Neat.

New Harry Potter book coming next year.  Rowling's web site apparently
got 200 million hits in eight weeks, 600 hits per second in the window
when she was announcing the new title, \emph{Harry Potter and the
  Half-Blood Prince}.

\emph{I, Robot} is playing this weekend; Asimov is spinning ever
faster in his grave.

We need a bunch of bookends---about 50.  The Onseck'll run off and
order those.

It appears that the Print On Demand process has been patented, the
patent having been granted in 1995 and not enforced until now.

The society resolves to patent binging within two yards of a
buckyball-encased bananimal 8-0-7\ps

\goto{Future Business}

Publicity will start soon for the Orson Scott Card lecture, co-sponsored with
MIT Students For Israel and LSC.  We may be asked to help with crowd
control and publicity.  The society resolves to acquire the Vice a
Golden Chain-Plow 11-3-1\ps.  The Onseck is appointed to cuddle around
it and bring it to life.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
