\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 8/6/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 6, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are approved as unambiguously truthful and correct
4+precious-4-2+2 proxies\ps, demonstrating that John was possessed by
the spirits of correctness and the True Onseck.

``My precious'' passes 6-3-fearing the precious\ps.

\goto{Committee Reports}
\subsection*{Mobcomm}
Stuff arrived.  Yay.  We think it's matter.  It passes 10-0-6\ps.

\subsection*{Frustrated AuthorComm}
Thiiiiiis close.  They sent it back.  Frustrated.  But they said it
was only for space reasons, so please send it back to them.  Author!

\subsection*{Vox Sciorum}
I saw some chips.  And some monks.  Monks with chips.  But they were
cute and fuzzy, so I let them be.

\subsection*{Aloha Lenscomm}
Gibbers senselessly about a monk.  See what happens when he's not
possessed by the glory of the Onseck?

\subsection*{Onseck}
We have reimbursement forms.  They're in the right place.  I dare you
all to use 250 of them.  I'll go first.

\goto{Old Business}
``Let's see'' passes by Skinnerial Decree, because she likes
Visio\footnote{May have been ``vision'' in the original}.

Freshman mailings should now be received.

Andrew says something about Bayesian statistics and the statement ``it
is possible'', and nobody understands.  He is commended for this 6-2 plus the precious-0\ps.

Carpentry is hard, and finding the right wood is really hard, but
we're working on it.

Vice reports that Ugly things 1, 2 and 3 were made in the forge this
week.  Expect Ugly Things 95 and ME soon.

We'll be talking to Laurie Ward about finances.

ALGOL
\goto{New Business}

Y moves to commend Victor Hugo for silly reasons.

The Coop brought us a couple boxes of stripped books.  Take one!
They're basically no use to us.

\goto{Future Business}

There's an immobile bookshelf.  But it's at a funny angle, so it looks
mobile.  Zeno would be a--mused.

Preliminary scouting reports no door in Altair-4.

The Vice and JFC try putting Ugly Things from the forge into each
others orifices and are ejected from the library.

Y and BTS move to recognize the library as the home of the muses,
Terpsichore, Cleo, Caliope, Megaera, Banana, and Alecto.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
