\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 8/13/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday!, August 13, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

JSS moves to regard them as ``crispy''.  This passes 8-6-5\ps, despite
complaints that it's more creamy.

\goto{Committee Reports}
\subsection*{War Council}
There's a door to Altair-4!  No wall yet, but there's a door.  It's
attached to the wall of the next room over.

\subsection*{Pseudo-LHE}
We have a draft of a money policy.  By policy, we have money, instead
of giving it to Laurie Ward.

``My precious'' ---Vice passes 9-0-4\ps.

\subsection*{FAC}
Still waiting!  20/21 days gone.

\subsection*{MobComm}
Relatively new few books, waiting on moves.

He is condemned for just not having \emph{the moves} 7-4-the precious\ps.

\subsection*{Onseck}
We now know that the Library is at 84 Mass Ave, not 77.  Much
rejoicing.

We will soon be members of the International Banana Club, known in
many places and founded at some point by a guy people know about.  He
has beliefs.  Everyone has a title.  We may get degrees.

\subsection*{Mumbling about Rats (Vox Scirorum)}
The Glob talks about chipmunks and how they suck.

It is legal to kill them, but not to transport them, not even to
Australlia.

\goto{Old Business}
We're sending a Get Well card to George Flynn.

Stripped Books policy is under review.  Please no slicing books in
half, not even with the really cool guillotine paper cutter.

``Meep'' from the Vice chickens in the usual way, and is somehow also
the ALGOL.

\goto{New Business}

Vice shows off that she's a really cool craftsman in iron and glass,
if still also a frustrated author.

God is commended for threatening the Great Mouse Empire with Hurricane
Charlie, 13-0-4\ps

New \emph{Anita Blake} story.  Looks like it still sucks.  Actually,
the excerpt is all about sucking and hickies and lack of
self-confidence because Anita won't give you a hickie.  Ask the onseck
for the URL if you want to hurt.

SCC is taking donations of used books for sale for charity.

\goto{Future Business}
Porn policy is inconsistent.  The new \emph{Anita Blake, Incubus
  Dreams} demonstrates that really clearly.

The endowment is now just over \$40000.  Over the last 18 years,
that's about a 12\% increase.

Motions to condemn or commend Anita Blake for dating somebody
(``Micah'') who can turn into a banana longer than it is wide in a way
which would disturb your mother chicken and fail, respectively.

The Onseck bravely takes up the Bloody Stump of Fable and Song, ending
the meeting.

\vspace{12pt}

\noindent
Meeting adjourned, whatever time it is right now SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
