\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 03/26/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 26, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Bonus Pre-Meeting Quote:

``The world is full of people trying to find the right hammer to pound
in the wrong screw'' -ARM

MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion to use the minutes to light Brazil on fire\\
Passes 10-0-0+Spehn

\goto{Committee Reports}
\subsection*{WarCouncil}
Chaos and confusion resolved in favor of confusion---there is not
enough chaos to take advantage of. It seems likely but not certain
that we will be able to do the UA office renovation over summer if the
wheels of bureaucracy turn fast enough. ASA announcement imminent.

Motion to use the UA to set Brazil on fire \\
Fails for lack of a second

The last box of pending donations has come through. We need to tell
the other people who want to send us lots of books to drop them in the mail.

\subsection*{MobComm}
British books on the way---some from Britain, some from Canada.

\subsection*{BondageComm}
Jhawk and JFC went to the Acme Bookbinding Company, and got a tour, a
promotional video, and a poster. They are all high-tech.  ``If we have
a test jhawk, that means we have more than one jhawk, and that's not
something we want to consider''-BTS

``You people are so weird''-KHA\\
Passes 8-0-1+Spehn

JFC told us a lot about them---they have a scanning room where they
can scan in old books, and a printing room. They are making the
biggest book in the world with their printer which prints on 5 ft by
100 ft paper.

``This is a nonfiction book, right?''-JM\\
``Yeah''-JFC\\
``Good. We're not getting it''-JM\\

They have a big helical conveyer belt to kill time while ink dries,
and a Million Dollar Perfect Binder\\
``Million Dollar Perfect Binder, but I...''- JM

``Then we went into the place where some magic occurs and the books
are bound'' \\
``Would this magic perhaps involve glue?''\\

``So, you can take a file you have, which otherwise you'd have as a
disorganized pile of papers or a disorganized pile of bits, and pay
them \$20, and get a bound book?''-BTS

Their ``Library'' side is totally customized, and has actual little
old ladies sewing things.

\subsection*{Bluebellcomm/Onseck}
JFC wants more plastic paperback covering material.\\
KHA will be buying more magazine subscriptions.

The library mourned the lack of $\phi \rho \epsilon \delta$ shirts on
campus, and celebrated the asbestos underneath tiles all over campus.
We debated the relative merits of asbestos and hemp children's
pajamas.

\goto{Old Business}
``JM mentioned...''\\
``I did not!''\\
Motion to suppport JM\\
Passes 11-0-4+Spehn\\
``The story that JM denies telling about class council people being
kidnapped'' -JFC\\
 ``I should deny it. Brian told that story''-JM\\
``Anyway, the story JM denies telling---while that was going on, I was
being born''-JFC\\
``While the story was being told? You are young''-JM

ALGOL
\goto{New Business}
``I like bananas because they have no bones'' - Andy, who has a
headache and did not take high school physics, but did dissect frogs
without apologizing.

JFC explains that he was hit in the head as a child.

Y tells us about monkeys on fire, with no typewriters.
There was one on an elevator winch, and they published a photo with
the caption ``We've been waiting to use this line for years---there's
a monkey winch in the works''

Move to have that building and all its occupants sent to Albania\\
Passes 8-0-0+Spehn

Discussion about whether people can create new fonts that are nearly
but not quite like existing fonts.

Motion to create for the Library a ``Banana'' Font\\
Motion to create for the Library a ``Dancing Kat'' Font''\\
Matrix Vote\\
All motions pass on a +3

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
