\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/10/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 10, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen, surprisingly special pseudo-Onseck, recording.


The minutes are read in a very lossy and abstract way, which is to say
it is reported that Jourcomm, War Council, Fweekcomm, and FAC say
things will be done Real Soon Now.

\goto{Committee Reports}
\subsection*{PseudoWar} CAC decided they won't put a lock on the door until they do
the rest of the floor first.  It appears they may be talked out of
this, with at least an ordinary Schlage or something.

The Skinner shall brace them in the hallway and resolve this on the
field of honor.

\subsection*{PseudoFAC} Now on the short list!  One in three chance of being published

\subsection*{LH\$} Appeals soon.  This will be a request for more money to spend on
books, unless somebody has a better idea.

\subsection*{PseudoSurgeon} Jade has started being Surgeon and fixing books.
Hooray!

\subsection*{AlgaeComm} As of an hour ago, it looks like they bought some new tiles
and they'll glue them down next week.  Then everything will be
wonderful again.  We shouldn't have to move anything else out of the
way.  Leaks are otherwise looking mostly fixed.

\subsection*{WCBINAComm} The pipe in the ceiling over Damnation Alley is asbestos
and must be abated.  We should either put that material someplace or
cover it really well.

\subsection*{PianoComm} Jenwa held her last hours this week and covered a
dozen or twenty books, losing some mass to each one until she
evaporated into a far-off grad student.

\subsection*{ConComm} ``Margaret has a big shiny, basically, best in breed ribbon
from WorldCon.''  AlohaLensComm has a picture of her getting awarded,
and we should get some more from the digicams at the conn.  Susan and
Rickland both have good pictures too.

Also, we got a bunch of free magazines from WorldCon.

\goto{Old Business}

Motion to get a big plush yellow elephant cavalry for War Council
fails for lack of a second.

Two boxes of Hs boxed last year to make room have now been unboxed and
put back on shelves.  This takes advantage of some of the space made
available by moving the C/PAs and such.

We have an SAO code.  Well, the Skinner does, but got it from asking
Umberto Eco's best book.  It's actually a chocolate code, not a MITSFS
code.

ALGOL
\goto{New Business}

We have new Dexes, whose Mistress is installing them.

We need to use a hammer drill, allegedly.

Kat found a new way to the airport.

\goto{Future Business}

BTS is glad he won't have hours going til eleven at night.

New TV Series are starting.

There's a farscape made for TV movie coming.  Trailer on apple's web
site.

Kat knows what $e$ is.  And also $2$ and $3$ and $235792135$ and $\pi$
and lots of other numbers.  She's on TV for this\footnote{well,
  knowing it in the context of the google ad.}.  Some discussion of
normal and transcendtal numbers follows.

\vspace{12pt}

\noindent The minutes are read into the minutes by general motion 19-0-1\ps,
which is believed to adjourn the meeting---even by the Skinner.

\goto{Skinner's Log, Supplemental}

Much singing.

\vspace{12pt}

\noindent
Meeting adjourned by Skinnerial non-tone-deafness, 1730 SST.


\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
