\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/12/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 12, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Y moves that they be commended as entirely in the best traditions of
the MITSFS.  JM moves they be condemned for that reason.  Some shmuck
moves that there be a matrix vote.  Bastard.  It's not even committee
reports yet.

They have results of 16-5-6\ps, 5-16-4\ps, and 16-8-10\ps.  This has a
determinant of 789, so they all pass.

\goto{Committee Reports}
\subsection*{PseudoFweekComm}
This meeting is majority students.  Also lots of frosh.

\subsection*{FalloutComm}
``If Nuclear bombs fell on the earth, the American way of life would not
have to come to an end.  There have been several scientific studies
published which demonstrate this.''

\subsection*{Mobcomm}
I haven't been ordering things, but the books just keep coming in.

\goto{Old Business}
There is some discussion of how Kangaroos.

Rebecca's not dead.

The OSC lecture went well.  There's a movie of Ender's Game / Ender's
Shadow coming soon, and OSC seems to think it will be well done.  He
hasn't seen the script yet, bear in mind.

Next proposal to LSC: a celebrity death-match between Orson Scott Card
and Noam Chomsky, passes 27-1-5\ps

Magazines have been dug out of the mail.

A meeting with Boojum about prentice-stuff didn't happen.

Eric Levin is done taking pictures from the Improper Bostonian.  He
was here for a couple hours yesterday.  He took a nap.  Many of his
pictures were taken through the mobile.

Y is looking for devil-man.  It has disappeared completely in the last
few years.  He cannot account for this.  He has some, but not enough.

ALGOL
\goto{New Business}



Saith Rebecca: ``I'm not dead yet!''.  The skinner is offered
ninepence to take her off anyway.  Rebecca says she'll go for a walk.

There's a novel on futurefeedforward.com which begins with a license:

\begin{quotation}

YOU ARE HEREBY GRANTED THE FOLLOWING RIGHTS:
\begin{enumerate}
 \item  The right to read once, in its entirety, the BOOK.
 \item  The right to store in any biological storage device a derivative work in the form of a personal memory or recollection of the BOOK and its contents.
 \item  The right to advise others to purchase for themselves their own licenses for use of the BOOK.
 \item  The right to repeat aloud, without the aid of technical means of amplification - including but not limited to megaphones, public address systems, streaming audio, and cupped hands - passages from the BOOK not to exceed three (3) consecutive sentences, or a total of eight (8) sentences.
 \item  The right to a living wage and to a secondary and post-secondary education of modest quality.
 \item  The right to purchase products not produced or manufactured by the COMPANY, including any products necessary to personal hygiene or nutrition, but excluding Big Mac brand sandwiches and any item fairly characterized as a "fresh wipe."
 \item  The right to walk here and there for purposes such as you determine.
\end{enumerate}
\end{quotation}

Brad tells us about Frisian liberty caps.

Y moves to investigate the possibility that the message on the back of
the U.S.~Constitution was placed there by Smurfs\footnote{Should this
  be Smurves, by parallel with Dwarf?}, but this fails 7-17-3\ps.

The Tech admits that we're partly to blame for the OSC lecture, and
has published an erratum.

There's some discussion of sentient penguins.  Y makes some motion
regarding Pan Pan the penguin and the Antichrist.  It chickens 6-3-17\ps.

\goto{Future Business}
The ladder has been thrown out.  Hopefully Phys Plant will not bring
it back.

Perhaps soon a new shelf will be attached to the wall.

It is suggested  that all further minutes will be replaced with the text
``banana,'' 5-5-9\ps, but this chickens.

Banana banana banana banana banana.  Banana banana banana 33-2-4\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Banana banana, Banana}

\end{document}
