\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/19/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 19, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are not commended for the quantity of bananas therein, as this fails 7-18-6\ps.

Andrew ``motions'' something, but Jamie successfully moves that we
ignore all motions from those who think that ``motion'' is a verb 16-0-11\ps.

\goto{Committee Reports}
\subsection*{FACcomm} Rejection.  Sad.
\subsection*{Blueshinycomm}
Kat made one.  It's pretty.

It's broken.

\subsection*{PseudoSurgeon and BondageComm}

Three boxes of stuff have been dropped off at Acme.  They will soon
return those together with, we ask, a large bag of birdseed and an
inflatable anvil 23+rocket skates-0-1\ps.

\subsection*{Pianocomm}
Paige is commended for starting prenticework, 17-0-1\ps.

\subsection*{Mobcomm}
25 or 30 books unpacked today.  Some of them are interesting.

\goto{Old Business}
There is some discussion of squirrels and about nano-shrinking them
and injecting them into Margaret's bloodstream.

GURPS Technomancer short stories are being published, featuring an
Antarctic hive mind of penguins.

Carthago Delenda Est.  Fails IX-XII-VI\ps.

ALGOL
\goto{New Business}
There's some discussion of purchase orders.  The Star Chamber should
figure out whether we want to use it.  The alternative is mailing
cheques and waiting a bit longer.


\goto{Future Business}
Blade III coming soon.

People are scheduling LotR sleepover parties.

\begin{quotation}
  "Come!" cried Aragorn. "Down this winding path through the
  green-gold dappled woods of shadow we may yet find shelter for the
  night ere we reach the sylvan palace of the elves."

  "The fuck?" said Gimli. "Speak English!"

  "I thought I was," said Aragorn.

  "Nay!" stated Legolas. "You speak not the language of men or elves
  nor yet even the garbled tongue of the orcs, but some other stilted,
  forced and over-dramatic faggoty fake Shakespearean that even I, in
  my great ancient elfly wisdom which totally kicks the ass of your
  puny human brain, not that I'm bragging, know not. In fact, I know
  an epic song that vaguely relates to this same circumstance. Back it
  on up whilst I bust a rhyme."

  "I know a song, too," growled the dwarf. "It's called 'Shut the Fuck
  Up, You Tightass Blond Pooftah'."

  Meanwhile, the hobbits bitched and whined and Gandalf did nothing.
  He looked very wise while he did it, though.\footnote{Props to
  Courtney for the pointer}
\end{quotation}

Someday, there will be hats.  We have some Krispy Kreme hats.

The Con Dor is nearly extinct.

There will be a meeting next week, but the library --- and the
building --- will be closed on Thursday for Thanksgiving.

BTS says we cannot allow the library to close, not even for a day.  Miller
Motion!  But it fails 12-15-4\ps.

Kevin Riggle, our newest member, initiates a project to investigate
conservation of bananas 16-6-0\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
