\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/17/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 17, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are regarded as usual 4-1-1\ps

\goto{Committee Reports}
\subsection*{Theftcomm}
We're taking the TIF home for the holidays.  It will return at the
beginning of IAP\dots better, stronger, faster.  We have the
technology.

\subsection*{PseudoAnalogcomm}
There is a new protoschedule.  Keyholders not on it should \emph{get}
on it.

\subsection*{Mobcomm}
We got stuff from SFBC.  They are booklike\footnote{flat, mostly,
  didn't really thrill me and one of them is the latest in the SFBC
  omnibus Grimes series (Rim Runner)} and awaiting processing.

\subsection*{Bondagecomm}
Some of the books have been inadequately permeated with glue.  Jade
will be talking to them about getting this corrected.  The glue
appears to not have flowed into the notches across the spine.  These
books are otherwise unremarkable.  The magazines came out OK.

\goto{Old Business}

Good pictures of Margaret, Meetings, and Frosh at Meetings have shown
up from Aloha Lenscomm.

ALGOL
\goto{New Business}
Somebody's offered a 1--many F\&SF donation.

\emph{Wizard of Earthsea} is apparently on the Sci-Fi channel, but
Ursula K.\LeGuin appears to hate it, for the simple and excellent
reason that it is the D\&D movie with her characters.

The Onseck has brought us a new member.  Its name is Jack.  It is a
pointsetta.  It has not payed its dues, but its cheque is in the mail.

\goto{Future Business}

The time warp starts tomorrow.  It ends on the fifth.

There will be (Assassins') Patrol on Christmas and New Year's Day, by
Susan Born.  6-1-2\ps.

There will be no meeting in the Library on the 24th or 31st, because
the Library will be closed.  It may be relocated to the Skinner's
present location.

A mandate to write AOL CDs onto bananas and mail those out chickens
2-2-2\ps, apparently ending the meeting by Skinnerial decree.  Guess
she went bananas.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

Fortunately, she ended the meeting before Malcolm could say something
about the Bipolar Express.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
