\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/16/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 16, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Condemn the banana motion\\
Fails 4-7-2+Spehn\\
\emph{Onseck's Note: ALC is censured for trying to slip a banana motion
into the beginning of the meeting}

Motion to condemn the Skinner for the dissonant bing at the beginning
of the meeting\\
Passes 4-Sterling Engine-2+Spehn

\goto{Committee Reports}
\subsection*{MobComm}
MHG emulates a rabid animal when shown the Wheel of Time 0 book, and
JFC shows us a compilation, Legends II.

Motion to condemn Card for being a lazy jerk (for removing chapters
from his novel to be published in the Legends II book)\\
Passes 8-0-2+Spehn

Commend of Condemn card for allowing Ender's Game to be made into a
movie.(We don't know yet)\\
Does Nothing: 6-0-5+Spehn

A new book discusses California outlawing superheroes, as they all
come with super villains.

Approved by the Skinner:\\
\begin{itemize}
\item A War Hammer comic. It is Volume II, we do not
have V1
\item A romance novel with sci-fi elements.
\end{itemize}
MHG pre-emptively runs away to avoid romance elements in new books.

\subsection*{Pseudo-Bluebellcomm}
Jenwa got trained, KHA ordered the 9.25'' material from The Library
Store.

\subsection*{Dr. Evil-comm}
We got a crazy letter in the mail. It does not appear to have white
powder, but is written in pen and pencil, discusses jets from burma
(and has a sketch of one) and comes with accompanying illustrations of 
We wonder if, perhaps, this is someone reading the minutes and thinks
we are actually plotting to take over the world. MHG asks and is
granted permission to dress like Dr. Evil\\
\emph{Onseck's Note: If you are out there, please don't send us more letters}

\goto{Old Business}
\emph{Onseck's Note: This was a better bing.}\\

MHG has received another rejection letter, but not from Tennessee. She
has a good idea for a flame-tank (not plane-tank) story. Perhaps we
will launch jet-tanks from our secret base in Burma.

Discussion of how ticking packages would be processed by the UA or
CAC, and what would happen if they opened it for us.
JFC reports that, earlier this week, the 5th floor held our package
for over 3 minutes before telling us about it.

ALGOL

\goto{New Business}
Motion to commend the Skinner for redeeming himself with the \bing \\
Passes 10-0-1+Spehn

JFC points out the existence of the inverse-skinner rule, and that,
though the motions do cancel out, they cancel in the opposite
alignment from what was intended.

JFC also points out that we have neither Y nor BTS at whom to make
Albanian Motions.

Discussion of MHG's sterling engine and its possible utility as an
iron.  This requires looking up the thermal properties of Al: it boils
at 2792K, and melts at 933K.  JFC is nonplussed that the critical
temperature of Al is not listed.

The Assassins' Guild Sandman game starts tonight. Several people have
been by to read the books, which Jamie put all together out on the desk.

Memento is showing at LSC. JFC is planning on going to see it tonight,
so the discussion is hampered by trying not to spoil it for JFC, while
simultaneously trying to convince MHG that the movie is not
``avante-garde'' and therefore icky.

\section*{WarCouncil}
We met with the CAC guy to point at walls where we would want
doors. He is passing all that info to the carpentry crew to get quotes
for time and money, which will be correlated with potential sources of
money, and hopefully things will work out well.  We may have to absorb
some amount of the cost of this moving---so we may also have to take a
loan or something from someone. At this point, we will have ample use
for MHG and anyone else who can carry books. (According to ED's
calculations, we will need to move approximately 10 tons of books and
steel).

Discussion of $\omega$ and factors of error, dodecahedral universes
and pentagonal-faced non-dodecahedrons, which is out of the
comprehension of the non-8.033 Onseck.  MHG suggests that perhaps the
universe is a d-100, but JFC wants it to be a Platonic solid, with
pentagonal faces, no seams, and no manufacturers' insignia.

``Does it have the little place where you stick the needle to inflate
the Universe?''-MHG\\
``Or deflate... that's scarier''-ALC\\
``There's a really bad inflation joke here, but we'll skip it''-ED

More discussion of relativity, string theory, and black holes, and
muons diverging from the theory. Also discussed is G, which keeps
being measured inconsistently. Discussion of magnetic monopoles, and
whether the one predicted to be in the universe actually crossed the
experiment being run within the first year of its beginning.

Discussion of evil chemistry:  magnetic monopoles tied to the end of
cosmic strings trailing out of primeval black holes and wrapping
around neutrino stars.

Motion to examine all the bananas in LaVerde's for magnetic monopoles.\\
Passes 11-0-4+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
