\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/06/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 6, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Jackie is an E-Bay addict, but has never sold anything. She naively
volunteers to sell books for us.

Motion: Commend the reading of the minutes as eloquent, multiloquent, 
grandiloquent and (polysyllabic)\\
Chickens 2-0-4+Spehn because ``big words are scary''

Motion to commend the minutes as ``everyone else sucks''\\
Does nothing 3-3-2+Spehn


\goto{Committee Reports}
\subsection*{Pseudo-BluebellComm}
JFC covered Jack Vance flood victim books. They conveniently fit into
an empty space.

One of the Bluebellcomm prentices 

Motion: to commend Jamie for sounding like a Dirk Gently character.\\
Motion: to stare at Cassie, who is not Margaret\\
Motion: A suffusion of Yellow\\
Matrix vote\\
\begin{tabular}{c-c-c}
9&1&2+Spehn\\
7&2&0+Spehn\\
5&1&2+Spehn\\
\end{tabular}\\
All motions pass (19)

Discussion of books mutating into Sandman, Cassie's response to being
stared at, and the people in the Gor books.

Motion: Albanian Jackie and anyone who touches the Gor books\\
Passes 6-4-1+Spehn

\subsection*{Onseck}
The Library Store may or may not have an online web site. It appears to
have a Heisenbergan nature.

\subsection*{MobComm}
We got something by Katherine Kerr, ``Operation Roswell'', and something else.
The SCC has about 60 books waiting for us, including some bad ones.

\subsection*{WarCouncil}
We sent an expedition to NESFA, but discovered that they don't have
any money.  Their clubhouse used to be a dry cleaning establishment,
and apparently when said dry cleaner vacated said premises, he left
behind several leaking barrels of toxic chemicals. It cost them a
great deal of money to clean it up to the point where it was allowed
to be inhabited by humans, but never can it have a day care.

We did, however, get some pointers to other potential sources of
funding or ways to pay back loans. (Readercon, not Boscone since they
get their money from NESFA, Arisia)

There is a likely chance that some messages have been passed to levels
of Benedict's infrastructure and not been passed to WarCouncil.

\subsection*{Bluebellcomm}
Bluebellcomm reports the difficulty of finding covering material
appropriate for actual Blue-bells of the bovine or floral variety.

\goto{Old Business} 

Sunday and Monday people unofficially from the Cambridge Public
Library came by and went through a bunch of our excess and picked out
400ash paperbacks and 100ash hard backs, which we sold them at a 50\%
discount to replenish their science fiction section. They also took
about 2/3 of the non-sf romance box, and some mysteries.

7-8 boxes of Hasslecomm disappeared, and were exchanged for money! Hooray!

ALGOL
\goto{New Business}

Timewarp to WarCouncil: \\
ARM reports: ``We need a formal proposal from CRSP, yuck Benedict will
get back to us about the money.''  CRSP gets involved in anything
\$10,000 or more, and anything involving 2 or more construction
trades.
``This explains why Stata was done as 9000 separate projects''-BTS\\
``And that would explain the angles...''-JM\\
``I've heard that a camel is a horse designed by committee, but this is the first time I've seen a demonstration''-Y

Joe has completed the shelving!

\goto{Future Business}
The clock says it's raining again.

Motion: Barr all plants from the Library\\
Fails 1-4-0+Spehn

Discussion of Mandarin and Cantonese pronunciation, and printing
presses which do and do not have moveable type.
Discussion of Kanji as the world's longest-running practical 

Motion: Use Jackie's banana-tassled sword to carve LaVerdes bananas
into kanji characters\\
 Passes 8-1-2+Spehn

``Thus my sword has been used to cut the meeting short''

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
