\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/2/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 2, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

A motion to have the Skinner and Onseck be late, because the pseudos
are better at this than we are, combines with a motion to hire out the
Onseck as a car-ad reader and a motion for a suffusion of yellow

\[
\left|
\begin{array}{ccc}
12 & 1& 5\\ 
15 & 2& 6\\
2  &13& 5
\end{array}
\right|
= 76
\]

and so they all pass.

\goto{Committee Reports}
\subsection*{Bluebellcomm}
The covering material around 9.5 open-ended is out; we should get
10 inch instead.

\subsection*{KindaRandomComm}
A motion chickens.  It came out of Justin.

\subsection*{BananaComm}
There's a fruit collection.  We joined, because somebody Very Old
donated money for a membership for us --- we now have a membership in
the International Banana Club Museum, founded by Ken Bannister, in
Altadena.  They have 17000 banana-related articles on display.  They
have 9000 members.  A motion to ban nuclear-powered \emph{banana}
juicers from the library is seconded by the Skinner, but fails by ?-?-?\ps.

Malcomm ($Y$) has the lyrics to ``if I only had a hamster.''  A motion
to consider it a donation chickens 1-0-7\ps.


\subsection*{MobComm}
Books continue to roll in.  It's not my fault, I swear!

\subsection*{FweekComm}
Lots of fliers were stuffed.  Some volunteer from outside actually
ended up stuffing the MITSFS fliers because he didn't want to have
shown up and do nothing.

\subsection*{Dexmistress}
A mini-inventory of the HAs is going on.  Following that, we can box
them up and move them to their new home, hailing from the Frigid
North.

A motion to form a society for putting things, with a subcommittee for
putting them inside other things first, on top of other things meets
a simultaneous motion to form a ladies' auxiliary for taking them down
again.  There is a motion to make this a matrix vote:

\[
\left|
\begin{array}{ccc}
6 & 1 & 2 \\
6 & 1 & 3 \\
1 & 8 & 6
\end{array}
\right|
= -47
\]

And they all fail, including the motion that this itself be a matrix vote.

\subsection*{Vox Sciurorum}

I dreamed of being kidnaped by squirrels.  They picked me up, but I
walked away.

\goto{Old Business}

We have a magazine, which has not yet but certainly soon will reject
the Vicemistress' wiles.  Lo, out into the street shall she be thrown,
her words treated like those of a common hussy.  Rejection upon
rejection shall pile upon her.  She shall be sad.

Cassini got to Saturn.  It left in 1997, which was a while ago.  It's
a Nuclear Wessel, which almost Destroyed All Life On Earth.
Strangely, its plutonium core failed to irradiate Earth.  

A motion to commend Cassini for irradiating and viciously slaying all
life between here and Saturn passes 13-6-7\ps.

The X-prize project is mostly kicking ass, in that a related ship
(Scaled Composites SpaceShipOne) made it into, well, kinda space.
This wasn't an X-Prize entry, but it will be.

ALGOL
\goto{New Business}

Third Space Still Sucked.

The X-prize project is mostly kicking ass, in that a related ship
(Scaled Composites SpaceShipOne) made it into, well, kinda space.
This wasn't an X-Prize entry, but it will be.  (Yes, this is a
duplicate from above, but it was considered Old and New.)

We have a poster about Fantastic Planet.  It's really cool, and shows
the Fantastic Rites of The Incredible Draags of Ygam, and the
Fantastic Collar of Gold from which There Is No Escape.

Malcolm moves that if Judge Crater is found in the library, he be
covered with plastic does nothing 7-7-6\ps.

``There is something deeply wrong with the world.'' passes by
Skinnerial influence and innuendo.

Malcolm mentions that the Newton Library has a tape of Jonah in which
the role of the Prophet of God Almighty is played by a stalk of
asparagus.  A motion to note this fails by lack of a second.  The
Skinner has a copy too.  A motion to commend her for cultural
awareness fails 2-0-13\ps.

``Skinner has no rites at all\dots'' ---JSS

\goto{Future Business}

There's another Weber space-combat game coming.  It looks more
appropriate for Harrington than the existing Starfire, which is cool.

A motion to get a copy of the other new game ``Star Chamber'' passes,
and John is appointed to get a copy.

A new Stargate show, without Richard Dean Anderson, is in the works.

Brian shows a veggietales trailer, which is condemned for not casting
a Banana in the roll of God chickens 4-2-8\ps.

A motion to refer to the Omnipotent but Terrifying Bananas as the
Kindly Yellow Ones, the \emph{Euminidebananes} also chickens 6-0-9\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
