\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/18/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 18, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

The minutes are approved as being time-shifted 4-0-1\ps.

\goto{Committee Reports}
\subsection*{MiniCultComm}
BTS reports about the INDUCE act from Sen.\ Orrin Hatch

The Skinner moves to ban Children.  Passes 7-4+Commander Toad-1\ps.

Some arguing about copyright infringement and the Vessel Hull
Protection Act happens, and the Onseck learns 

\subsection*{Frusted Author Comm}
Squeek.

\subsection*{BlueBellComm}
\begin{verbatim}
OverflowDrawerCount -= 1;
throw(rock!);
\end{verbatim}

\subsection*{MIT Libraries}
``A folder still hasn't been delivered to us, but we gave you money!''

The message about the folder being ready didn't propagate to the right
Vice.  It went to Pride instead of Sloth.

A motion to commend the computer revolution for finding new ways to
lose mail passes 11-4+a french fry-3\ps despite the fact that the
Onseck does not support MIME or application/x-mitsfs-motion.

\subsection*{Vice}
Glormp

\subsection*{LHE}
Sorry for being lame, I'll explain a bit later.

\subsection*{PseudoNiagraComm}

Pandemonium will take books

\begin{itemize}
\item by appointment
\item in single bags at a time
\item that are sci-fi
\item and they don't have too many copies
\end{itemize}

\subsection*{Pseudotheftcomm}

He's more or less up to date after being away for a bit.

Vice: In the frozen land of Nador, they were forced to eat Robin's
minstrels passes 9-4-chicken finger\ps. And there was much rejoicing.


\subsection*{War Council}

Phil Walsh says a small renovation budget has been approved, so we'll
be able to move into the Annex soon.

Vice makes birdlike noises, the Chancellor mooes, and something in
here passes 7-1-5+moo\ps, proving $moo<2$ --- and that the Vice is
incomprehensible.

\subsection*{PseudoFweekComm}
Yet more reminders that June 27 is the day of the summer mailing.  We
know already.

\subsection*{Apparently we have a MalComm}
This old Analog bound set has a badly broken binding.  Somebody tall
should check the rest of them.

\subsection*{BondageComm}
ACME, the people who do a bunch of our binding, made the world's
largest book.  It's enormous, $5'$ feet by $7'$ feet.

\goto{Old Business}

The LHE's computer was failing.  He fed it to some caviar\footnote{127
  GB Western Digital Caviar}, and now it works fine again.  Vice got
to him.

If J is still VGG in seventeen years and fifty weeks, and no other
keyholders born in the interim are available to take the job, BTS
agrees to take it.  Chickens for lack of a second 5-2-7\ps.

The first few minutes of \emph{Pitch Black}, the made-first prequel to
\emph{Chronicles of Riddick} looked awfully cool.

Ave. Victor Hugo sent us some shelves.  The threatened but unspecified
terrible things have not happened.  Thanks to Ed Keyes, Andy Menard,
and Jamie Morris for going to get them.

All the HAs are on shelves.  Um, not quite.  As soon as SEB finishes
bluebellcomming some things, they'll all be up.  Some hardcovers need
to be Hasslecommed -- volunteers? 

``While Nature abhors a vacuum, the Skinner abhors air'' passes 8-0-3\ps.

Usual Miller Motion fails 7-14-3\ps.

What about the usual universe destroying?

ALGOL(now with usual complaining!)
\goto{New Business}

The AVH shelves are a bit of a pain: horribly unstable.  Also, the
magazine top-rack thing is problematic, perhaps chiefly in that it
doesn't exist.  This has been painful for many people, chiefly the
Chancellor, and really ultimately not worth the investment for this
crappy return.  Would have been nice if we'd gotten one of the others,
but we didn't.

\goto{Future Business}

The Onseck begins reading from \emph{Commander Toad and the Planet of
  the Grapes}...

Susan: ``Now if there were only a Commander Toad book about bananas''
passes 3-0-2\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1900 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
