\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/4/2004}
\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 4, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

There are no minutes regarding the motions of this reading passes 5-2-3\ps.

\goto{Committee Reports}
\subsection*{MobComm}

Not much done, but I have to fill the empty space.

\subsection*{Surgeon}

I met with the MIT Librarian today.  She was very helpful, and gave us
an extensive shopping list of useful stuff.

First deal is booklets, and covering the spineless decayed ones.  Y
moves that an invertebrate shelf section be created, and this passes
14-0-2\ps

\subsection*{War Council}
Lock on 401--D RSN.  They don't even have the door yet---they ordered
one and a jar was shipped by mistake.

\subsection*{Algaecomm}

Pipes replaced.  Turns out they're just at the beginning of the MTBF
for the copper-steel junctions.  Oops.  So the whole building will be
leaking like that over the next few years.

When they shut off the chilled water, it shut off heating in w91,
apparently with a causal relationship.  Keep the FOO counters turning!

\subsection*{Pianocomm}
Laura.  Given stuff to do.

\goto{Old Business}
Athena accounts which need renewal need renewal.  We should probably
go back to asking Prof.~Jenkins.

Term started.

Mumbling about \texttt{shock}

ALGOL
\goto{New Business}

``Visit DOJ's website www.lifeandliberty.gov, launched to educate
Americans about how we are preserving life and liberty by using the
USA PATRIOT Act.''  How do they preserve life and liberty?  The
Wonders of Cryogenics!  ``I think they dip it in formaldehyde'' ---Y.
The entire room erupted\dots well, oozed in laughter.

There are people camped out watching Mt.~St.~Helens.  Darwin is a
bloody god.  He demands sacrifices!

The Ansari X-Prize has been one.  Congratulations to Burt Rutan and
all those who worked with him.  The space station does still have trash.

\goto{Future Business}

Jamie will go visit Worth Systems, the local distributor for the
Aurora shelves.  He'll be looking at funny bits and prices.

A new movie, \emph{Robots}, by the \emph{Ice Age} people, with Robin
Williams, has a trailer out.  It looks great.  The trailer made BTS
fall out of his chair laughing.

\emph{Sky Captain and the World of Tomorrow} is great.  It looks like
real technicolor.  It is wonderful pulp.  It has Tom Swift Jr.\
references.  It may have stolen most of the plot from \emph{Tom Swift
  and His Diving Seacopter}.

Tomorrow Andrea Humez is marrying Jan Maessen (Andrea is an
ex-keyholder).

The meeting's breaking down in chaos, so BTS proposes a Miller Mition,
which fails 14-16-7\ps.  He arranges a surreptitious timewarp to New
Business and proposes the first Miller Motion of the meeting, which
fails for lack of a second.

There are new developments and understanding in the rule of apparently
superfluous human organs.  For example, the appendix, or the coccyx.
Skinner has no coccyx at all, coccyx at all, coccyx at all\dots

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
