\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/13/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

Bonus Pre-Meeting Quote:\\
``I think chocolate is evil, so I encourage others to indulge in it''-MW\\
``I think our religions may be compatible''-JFC

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 13, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Move to approve the minutes as being culturally useful\\
Does nothing 2-2-0+Spehn

Motion to condemn whomever's fault it is that the word ``Heisenbergan'' was not ``Heisenbergian''\\
Fails for lack of a second

Motion to condemn the maker of the previous motion for not adopting
Mark Twain'stheory that foreigners always spell better than they
pronounce''\\
 Passes 4-0-1+Spehn
 
 Discussion of misspelled and mispronounced names, and silent 3s, and
 how names mutate over time.

Move to commend David MacDaniels for noting that Russians pronounce words as if vowels were a Bourgeois luxury\\
Passes 5-4-3+Spehn

\goto{Committee Reports}
\subsection*{LHE}
We informed Finboard that we're going to be spending lots and lots of
money, but didn't directly ask them for the renovation money.

\subsection*{WarCouncil}
CRSP proposal was turned in. Benedict is on vacation. Maybe the
proposal is actually in the hands of CRSP, and maybe it is on Benedict's desk.

The Onseck is confused by something relating to orchestras, which results in a 

Motion: Albanian Motion (Y)\\
Passes 3-1-0+Spehn

Motion: *sung* ``Every Vote is Special''\\
Chickens 1-0-1+Spehn

\subsection*{MobComm}
Has books nobody will be interested in.

\goto{Old Business} 


There is evidence that the library we sold books to was not Cambridge
but Arlington. The general consensus is that it doesn't much matter...\\
``But it means that the Cambridge Library is still a sales prospect''-Y\\
``We just have to ensure that they have a flood''-ED\\
*evil laughter from the LHE*\\
``You know, Andrew, you don't *have* to contribute vice to the Library. That's Margaret's job... although she's not here'' -KHA\\
``It's okay. I don't mind being the pseudo-Vice''-ALC\\

According to the clock, the rain continues.

Move to donate the clock to the Cambridge Library
Passes by Skinnerial Decree


ALGOL
\goto{New Business}

Nonstop carnage\\
Passes {8+eyes}-0-1+Spehn

``My reign of terror will be commencing shortly''-MW

JFC reads something randomly chosen from a very bad book:\\ 
``The prostitute with the gun fetish was not homosexual;''

Miller Motion: end it all now!\\
Fails 7-8-3+Spehn

\emph{Onseck's Note: The aforementioned sentence had not been intended to be included in the minutes, as JFC's reading usually is not, but as it prompted a Miller Motion, it must be included for posterity}

While looking for the sentence to be included in the minutes, JFC remarks:\\
``It appears we motioned it out of existence''\\

Move to commend the society therefore\\
Fails 3-4-0+Spehn because it is premature... the sentence has not vanished.

``I was kind. I only read to the semicolin...''-JFC
Move to commend JFC for not going all the way to the period \\
``I'm not sure I want to second something that commends him for not
going all the way'' -MW\\
Fails for lack of a second

\goto{Future Business}
``In the future, all restaurants are Taco Bell''\\
Passes 8-1-1+Spehn

Discussion of invisibly writing carcasses on eternal golden thrones in
the 41st millennium.  They will 

``You used to be Stephanie'' -JFC\\
``Well, if I was, I sure missed a lot of fun'' -Stan\\
``Someone say something so I don't have to think about that'' -JFC\\
*albanian poetry* -Y\\
``Someone say something else'' -ED\\
``I didn't get it anyway. My laptop is missing the Albanian Language package''-KHA\\
``Oh, convenient'' -ED\\
*something in Norse* -MW\\
``No no no. No ancient languages in front of the books'' -KHA\\

Miller Motion\\
Passes 9-0-2+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
