\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/21/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 21, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Motion to commend, condemn, and candian airline the minutes as being a
shining example of paranoia and schizophrenia --- mostly the later.
Passes 19-7-2+a Schizophrenic Chicken\ps du.

\goto{Committee Reports}
\subsection*{Bluebellcomm}
reports... ``Hahahaha!  Nothing!''

\subsection*{PseudoBluebellcomm}
Gosh, books got covered.  Maybe gnomes?

Vice says it was her, a frustrated author, who got five rejections and
worked out her frustration on the plastic.

\subsection*{Pianocomm}

Ariel complains about nagging, but will show up and work soon if the
Skinner keeps her company.

\subsection*{Mobcomm}
has continued to loot Ave. Victor Hugo, which offers a great bulk deal
on bulk books which we can't afford to take unless it comes with more
space to put them in.

\subsection*{War Council}
We can't even shelve all the books on the ``to be shelved'' section.  Eek.

\goto{Old Business}
We got mail!  Somebody should remove the UA from the mud-soaked pit
where we left it after ceremonially wrestling for our mail.

We're now only three months behind instead of twelve --- so this may
be good.  Though it implies that in a little while, they'll be
delivering unsent mail, which will be interesting.

We now have \emph{Temple of HaShem}, an allegedly Jewish Science
Fiction book, which its author would like us to review.

Isaac Asimov is still dead. (Jamie)

But his magazine came to us. (JFC)

Where are the comic books? \dots Hey, John, you're supposed to answer
the question! (Jamie)

ALGOL
\goto{New Business}

``Stupid Einstein'' is being performed this week; look to the Glob
calendar for details.  It may be pantomime.  ``Far better that than if
the mimes don't wear pants.'' (BTS) A motion to condemn the Onseck
passes by Skinnerial decree.

A motion to add the bananas \textbf{of Gor} to the Freshmen Mailing,
appropriately chained for safety to the underclassmen, fails 4-9-3\ps.

There will be a new schedule for the Summer shortly, taking effect in
about two weeks.

Some motion (``Sure!'') chickens 4-3-9\ps.

\goto{Future Business}

The LHE may well be around for the summer, if he can be employed in
the next week.  Vice suggests ``Desk Barbarian'' at McCormick Hall.
Jamie suggests eunuchs to guard McCormick, but the Onseck points out
that VMS has better security properties.

Condemnation of the movie version of \emph{I,Robot} passes 10-0-2\ps.

The frogs come, on little flat feet, passes 5-0-1\ps with the friendly
amendment, ``For the bananas''.


\vspace{12pt}

\noindent
Meeting adjourned, 1600 SST.

``Augh, a 23-hour meeting!'' (ED)
``Eventually, I'll learn to tell time... right'' (Skinner)

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
