\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/20/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 20, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.


JFC suggests that the minutes might be wrong, in that the person's name was not Stan, but actually Marty(n)  He is clearly confused, as the minutes are never wrong.\\
Motion: Move to condemn JFC's memory for being always wrong, in much the same way that the minutes are always right.\\
Passes 8-2-0+Spehn

Phe4r the Albanians and the Onseck's reality-warping power.\\
Fails 1-5-4+Spehn

JM suggests that the CUSFS is to be the only target of inter-Library
violence because ``They started it''

Deplore the lack of gerbil-mechs in previous minutes\\
Fails for lack of a second

\goto{Committee Reports}
\subsection*{Pseudo-Bluebellcomm}
JFC covered two books.
\subsection*{MobComm}
There are 60ish books waiting in the Auburndale Post Office
\subsection*{CoufComm}
Apparently the ICSF has not yet gotten over the shock of JM's proposal
to pay them in books.

Motion: purchase only books guaranteed to be incapable of reproduction\\
fails for lack of a second

Discussion of Callahan, geiger counters and radioactive hometowns
\goto{Old Business}

Some amount of timewarping occurs.

``The Skinner'' is being translated into four languages\\
Move to determine how many human languages exist on earth and then
translate our Skinner into at least five more.\\
Passes 9-1-0+Spehn

We got a catalog on how to, as a Library, be a resource for
homeschooling parents.\\
Motion: Have the Library take appropriate precautions to prevent proto-humans from ever learning anything from Pierce Anthony and John Norman.\\
Passes 3-2-1+Spehn

ALGOL
\goto{New Business}
JFC brought old-style 3-D pictures of Mars, with appropriate glasses.

Motion: Nothing at all is very subtle indeed.\\
Passses 5-1-0+Spehn

Motion: That motion.\\
Chickens 2-1-4+Spehn

``Do not go to the 3-d glasses for council, for they will tell you
what's red and blue'' -JM

Discussion of anime commentary with drunk commentators discussing
undergarments.

Motion: BTS requests that the minutes note the first time in history that JFC abstained from bad humor\\
Passes 6-1-2+Spehn

JM asks what we should do with the semi-obscene, semi-technical
diagrams from Germany. KHA suggests we just throw them out. JFC
suggests that we put them in interdepartmental mail to Margaret or
Dean Benedict. JM suggests that either of those would violate the MIT
harassment policy.

JM has an orchid, courtesy of Amanda's scouring of the catering trays
and KHA's bobby pins.  

Motion: Declare JM's hairstyle proto-human\\
Passes 11-0-0+Spehn

\emph{Onseck's Note: There is discussion about whether this means ``don't read the Anthony or Gor books to the flower'' or ``send it back into space''}

``I am neither harassing nor hazing the flower in my hair''-JM

Motion: declare all ``evils as old as magic itself'' protohuman\\
Passes 6-2-0+Spehn

Motion: not to declare HamsterMechs protohuman\\
Motion: aquire them Gor books\\
Motion: gobble gobble gobble\\
All motions Pass (Det of 2)

Motion: condemn JFC for suggesting that the Onseck might move out of order\\
Fails for lack of a second.

Andrew suggests that we have streaming text from next week's minutes.
Discussion ensues about the errors in the minutes

Move to commend the Onseck for being completely intentional\\
Passes 7-0-0+Spehn despite the Onseck being born early.\\
(Ah, the power of the minutes)

Motion to correct all seismographic injuries to the earth mother
through the application of banana mushrooms.\\
Passes 7-0-0+Spehn


\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
