\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/03/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 3, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

There is a matrix vote regarding commendation of the minutes and
making them be sung contrapunctually, but nothing useful happens and
there is much confusion.  The Skinner holds some votes, makes it a
matrix vote by Decree then fails these all by Decree. Y points out
that she is The One, as she can control the Matrix.

It is resolved to end the world  15-1-4\ps.

\goto{Committee Reports}
\subsection*{PantherCom}
Lots of work happened.

\subsection*{Hasslecomm}
A bunch of work was done by JSB and AES, who is apparently not a
keyholder but did a bunch anyway.

\subsection*{War Council}
401-D is still not locked.  We still don't have space.

Y moves that the society acquire some bagels to go with the locks,
passes by 16-4-2\ps.

\goto{Old Business}

Once upon a time, the Skinner slept.  But not very recently.  It was old

Paige reports that Rebecca hypnotized her with a blue shiny\dots organ.

The people called the Romans they go to the house---LSC tonight at 8
and tomorrow night too.

And Margaret says ``Chickoo.''  Pause, and reflect.

ALGOL
\goto{New Business}
The pictures were published in the \emph{Improper Bostonian}.  He took
a few hundred pictures and published two---it's nice and non-harmful.
Some of the things are not true, but that's OK.

A blue shiny day for Paige and Rebecca is established 10-0-4\ps

\goto{Future Business}

One day it will known that an ion drive rocket made it from earth
orbit to lunar orbit.  They only have the metric system, see, so it
can't go badly as ours could 15-12-1+a foot\ps

A pillow fight breaks out, and then multiple conversations, so I can't
take any minutes.  Perhaps I'll just natter for a bit.  The Skinner
bings a lot.

Miller motion 15-16-2\ps

Nattering.

Miller motion 15-2-4\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1755 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
