\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/02/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 2, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST.
Kat Allen, in a play for pre-IAP supreme power, is the presiding 
Pseudo-Skinner and recording Onseck.

Minutes read. More minutes are read.

Motion to replace all instances of pseudo with comm, comm with
cabbage, cabbage with pseudo in the previous minutes. \\
Friendly amendment: three times\\
Fails for Lack of a second

\goto{Committee Reports}
\subsection*{Pseudo-Bluebellcomm}
JFC has covered a few more odd books, and KCR covered a few new
ones. (JFC left the covering material out, and he thought it was a
hint.) KHA is planning on clearing the shelf tonight.

Move to appoint a committee to find non-odd books in the Library\\
Passes 3 - 1  -2+Spehn 
\subsection*{MobComm}
We have  ``The World of Robert Jordan's Wheel of Time'', with lots of maps.
We have the new-oldest Heinlein novel. JFC is afraid to read it,
thinking there might be a reason he didn't want it published.

\subsection*{Pseudo-Pianocomm}
We need prentices.

\goto{Old Business}
We got a new-old anthology, in the small-mammal-crushing style. It
makes a loud noise when you drop it.

Move to note that the Harry Potter books are clearly a trap, given
that there is some property about them that causes Librarians to store
them on the highest shelves.\\
Fails for lack of a second, despite conversation ensuing, given that
JFC did not notice it was a motion.

Move to commend Kat for not insisting on seconds \\
3-0-0+Spehn\\
JFC asks that the minutes note that it's a defective bing.

ALGOL (with a less-defective bing)

\goto{New Business}
Discussion about whether anything suggested in the echo of the
less-defective BING would pass automatically.  

We have a new Boris calendar. KHA has deemed it to be slightly less
offensive than the December picture.  The girl in it could almost be human...

We do not yet have a non-Boris calendar. KHA says she'll get it.

Discussion of the Borris-like and non-Boris-like state of the pictures
on the calendar.

Motion to have Boris-comm aquire a banana calendar, and preferrably a
sci-fi banana calendar for the library.  \\
Passes by Pseudo-Skinnerial Decree

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
