\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/09/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 9, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion to commend the tongue twisting of the Onseck in the reading of
the minutes.\\
``I could twist my tongue better than that!'' -JFC\\
Fails for lack of a second

Additional discussion of last week's mammal-crushing anthology.
Apparently, ED bought himself a copy in Tennessee.

\goto{Committee Reports}
\subsection*{MortComm}
Joan Aiken, a British children's book author, died.

\subsection*{Bluebellcomm}
KHA covered all the 9.5'' books. JFC is not impressed.

\subsection*{MobComm}
Wheel of Time 0 is on its way to us, which is somehow related to the
novella. Additionally, we have some junk rescued from the Pandemonium
Black Hole.

Time-warp to New Business: \\
Frustrated Author MHG is up to two on her wall of shame, and has a
poem in Tennessee. \\
\emph{(Onseck's Note: Will Margaret's poem become part of
the next mammal-crushing anthology? The Tennessee connection is clear,
but only time will tell!)}\\
They bothered to remove the staple from one of her
short stories... but it was returned in under a week.

Discussion of poetry, magnetic chemistry-related poetry, etc.

\subsection{CoufComm}
We have received the second (but not the first) box of books from
Imperial College. MHG has applied a British stamp to her head.

\subsection{Pseudo-WarComm}
ARM seems cautiously optimistic, but no real news.  At this point,
only vehemently objecting people or limitations of money and timing of
moving can stop us... There are many technical difficulties in moving
the Library, which will have to be overcome, but that will happen
later.

BTS arrives with Krispy Kreme, and reports the difficulty of
Bluebellcomming the doughnuts. There is discussion of the 9.25''
material which KHA has forgotten to order.

\goto{Old Business}
The Canadian Magazines have arrived, and we are being advertised on
their website.

MHG got us new pillows. ``Everyone should bask in the pillow-enriched
glory''.  The pillows are pale yellow, indicating only color and not
flavor. The old pillows have been placed in the garbage, as burning
would defy several EPA regulations.

Discussion of dust colored cars, dust-colored planets, and
butterscotch-colored skies on Mars.

Thanks to Bill Nye the Science Guy, there's a sundial on Spirit, which
also functions as a color target.

One of our alums told us that a large shipment of bananas washed up
onshore in Lithuania, and the Health Officials Who Stole Christmas\\
http://www.cnn.com/2003/WORLD/europe/12/22/offbeat.bananas.ap/index.html

``It also seems they must ship a lot of fish that way... given how
many of them wash up onshore'' -BTS\\
Albanian Motion\\
Passes 13-2+Albanian-Spehn

Motion: Commend the bananas for bringing Christmas cheer to the people
of Lithuania, and Condemn the evil health officials for ruining that cheer.\\
Passes 10-1-4+Spehn, but a revote is called as people were unsure that
the motion actually contained ``banana''.\\
Passes on the revote, 12-1-6+Spehn

Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
