\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/14/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 14, 2004


\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read, though it is noted that many details have been lost to
history due to the vagaries of MIT's wireless service --- and because
the Skinner and ex-Onseck doesn't have Emacs installed on her laptop..

JFC moves that archaeological expedition be mounted to recover the
minutes.  Passes 9-4-7\ps.

\goto{Committee Reports}
\subsection*{MobComm}
Ave. Victor Hugo is still closing, now at a 75\% discount

JFC has arranged to buy much of their remaining and interesting stock.

The Skinner accidentally moves that all somethings are somethinged,
Margaret leaps on and seconds this in an insubordinate act which
passes 10-1-2\ps

Malcolm is noted to be in Albania with something that sounds much like
a weak pun, 10-9-0\ps.

\subsection*{BondageComm}
JFC has taken annoying 

\goto{Old Business}
The Skinner also accidentally moves that she get better at the Bing.
The Onseck joins the Vice in rebellion and seconds this, and it passes
10-0-1\ps.  The Chancellor, sniveling toady, cements his position as
Vizier 

JFC's sister once ate too many strawberries and got a rash.

JFC begins describing details of octopoid sex, and is rapidly sent to
Eastern Albania, where they're incomprehensible even to Western
Albanians.  Passes 7-5-0\ps.

Vice motions to commend the Skinner on her binging 4-0-4\ps.  They got
to her, too.

Term is ending.  To this disappointment of the students, this fails
3-4-1\ps.

``Margaret, are we going to have to tell you the story of the Man who
cried Albanian?''\\
``Is this the one who got eaten by a Oolf?''

Aaron and Zhenya Ucko visited us for the picnic, then went away.  They
may be back.  Yevgeniya volunteers to be jourcomm.  They also checked
out 9 books between the two of them, which they will mail back to the
Book Drop with some potential late fees.  The VGG, she has Ways of
Dealing with This Sort of Thing.

ALGOL
\goto{New Business}
A motion to Not throw things at the skinner, using only self-propelled
or melee attacks, passes 7-0-0\ps and 5-3-0\ps respectively.

Emily Warman is moving to Ohio.  The society says ``Noooooo'' in
unison, and is sad.  One less Keyholder.

\goto{Future Business}
A motion to commend the Skinner for discovering her new lusts for
absolute power fails by Skinnerial Degree.  By the reverse-Skinnerial
rule and its applicability, this may be irony.

Brian shows off a picture of his Banana Slug, which passes 9+\$31 -
4+\$19 - 1+cows+\$-6.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen,  Onseck}

\end{document}
