\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 03/05/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 5, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Correction: JFC did not say that he read all the Anita Blake books.  He
read only 1-10

Motion to condemn JFC for doubting the truth of the minutes \\
Passes 6-4-4+Spehn

BTS demonstrates that he can pull books off the ``to be shelved''
which are horribly painful.

``We do have good books in here, don't we?'' -ED

Motion: Have the Society experiment to see if you can read one of
``those'' books and a real book at the same time, since they use
different parts of your anatomy.\\
Passes 6-0-0+Spehn


\goto{Committee Reports}
\subsection*{Bluebellcomm}
WBS 
There are approximately 3.5 people working on Bluebellcomm---perhaps
there should be Bluebellcomm parties.\\
Discussion about whether there is a net loss in tablespace in the last
year.\\
Discussion about the psychology of quotas, complaints, and how to
remind people to do committee work with or without swords.

\subsection*{Onseck}
Is going to order cover material before putting the computer away
after the meeting today.

Y mentions TSR writers guides, in which they explain that they are
against Lichs and Ancient Evils Reawakening.

Motion: Get the society a TSR writers guide\\
Passes 11-0-1+Spehn

Why don't people ever melt down the token required to release the
ancient evil?
* They acquire powers of their own
* You might need to use the ancient evil to fight off the more-ancient evil.

\subsection*{MobComm}
Needs Star Chamber people to come assist in buying books.

\subsection*{Pseudo-Jourcomm}
TZ is real soon now as ever.  In particular, it has been admitted that
there are no difficulties between us and the completion of TZ---but
the delay may or may not be related to motor-biking through Chernobyl.

There is a new road from Moscow to Vladivostok.

``Can you say that again?''-KHA\\
JFC does so\\
blank look\\
``How about I spell it for you''\\
nods\\
``Oh, Vladivostok!''

Move to insert ``that'' word for word in the minutes.\\
Passes by Skinnerial Decree.

\emph{THAT word for word}

Discussion about AlohaLenscomm, which proceeds to torture the Onseck.

\goto{Old Business} 

JFC and ED encountered an apparition that claimed to be nothing at all
like Erin P.

JFC got email from Joy Sumner, who says to say hi to everyone.\\
Motion: Hi Joy!\\
Passes 8-0-1+Spehn

The Microcanonical Ensemble is really cool.  Its temperature varies.

ALGOL

\goto{New Business}
Larry Niven wrote a story called ``SmutTalk'' that appeared in
Playboy, which JFC does not recognize.

WarCouncil has no update. However, our current lease on warehouse
space ends either near the end of this month or beginning of April, so
we'll need at least a month more. 

Y gives a television report:\\
Enterprise was forcefully moved from 8-9 PM, which is said to describe
what video game characters do when not at work. Called something like
``Game Over''

BTS reports that the Firefly movie has gotten approved (Joss Wheaton's
sci-fi thing) and Alan Moore has totally disassociated himself from
the HellBlazer movie, after a messy lawsuit happened where some people
who'd pitched a script idea to Fox years ago that resembled League of
Extraordinary Gentlemen, before Moore wrote the comic.  They sued
Moore claiming that he'd been a patsy for Fox, so now he's not willing
to deal with it.

SFBC has sold out to spammers in Hong Kong, who send all-image html.

KHA is recycling labels for the calendar.

\goto{Future Business}
Extensive discussion about how running a Library involves chores, and
potential classes in Bluebellcomm disguised as origami.

Andy, who is visiting, reveals herself to be both a professional
Librarian and to do origami, but is not being drafted to Bluebellcomm.

In the future, the TIFF may rotate.

JFC starts to read, resulting in a \\
Fails 8-11-0+Spehn

Albanian Motion\\
Chickens 4-5-7+Spehn
JFC gets bored and stops reading anyway.

BTS starts singing ``John Carr has no tail at all...''

Miller Motion: make it stop\\
Passes 12-1-7+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
