\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 8/20/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 20, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

A motion to accelerate the reading of minutes next time passes 7-5-3\ps.

\goto{Committee Reports}

\subsection*{MooComm}
Free passes to the American advance screening of ``Shaun of the
Dead'', a romatic comedy with zombies.  The showing is Sunday night in
Bawstahn\footnote{MooComm is a townie}.

\subsection*{We Think It Might Not Be Asbestos Comm}
The floor tiles in the back of the room may be asbestos.  Oops.  And
mold too.  The mold might have eaten the asbestos.  Either way, the
abatement may end up being in Rush.  Suck.

ED suggests just carpeting over the floor, asbestos and mold and all.

The Vice rants about the idea of carpeting the library and how bad
this is, since it leads to moths, and she had to sweep them up in
Barker, so ``No moths'' passes by Skinnerial decree to soothe her.

\subsection*{ConComm(World)}
It's coming.  Margaret is going as a terminator space marine comissar.
Andy will be in the lobby with a hat looking for change to afford the
tickets.

\subsection*{MobComm}
Look, I bought books.

We owe the SFBC over \$200 from missing some payments.

Pseudo: We're going to New England Mobile Book-fair.  Somebody who's
gone before would be useful.

\subsection*{Chancellor}
You should talk to me before doing anything stupid.  Well.  You
shouldn't do anything stupid, but you should talk to me before doing
things which might be stupid, only you know they're not, so I can make
sure.


\subsection*{Pseudo-Theftcomm}
ED, in addition to SRK, is now Theftcomm.

\subsection*{War Council}
It's getting closer.  Real Soon Now.

\subsection*{FweekComm}
Frosh show up soon---the next thing should be the Midway.

\goto{Old Business}
Some animals have glass cutters, or John thinks they do, or
something---I was distracted by portraits of gorillas.

Some guy is now good at ripping books apart with his hands.  

\emph{Andromeda Spaceways} has not replied to the FA(Vice).

C/PAs will get ``worked on'' tonight.  They should be inventoried,
lofted, and boxed real soon.

A motion to add synchronized beach reading, including MobComm and
Panthercomm in bikinis\dots

ALGOL
\goto{New Business}

\dots fails 4-7+horror+my eyes my eyes-3\ps.

The year of the first successful War Council, 1952, is commended.

New \emph{Wyrld of Dyrkynss}.  New \emph{GURPS}.  New \emph{Paranoia
  XP}.  Gencon is cool.

APO has even less students than us.  This sucks for them.  But it's
because we're recruiting better than we are.

\goto{Future Business}

This card for George Flynn is going out real soon.

There's some discussion of the canal-building plan.  Boards are
expensive!  The rest of what we're doing is actually quite cheap.

``I need a banana lapel pin.  Y'all do too''  passes 10-0-5\ps.

Hey, we got a pointer to somebody at the Braintree library who knows
how to fix books, plus a potential introduction.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

And now it is time for dinner.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
