\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/01/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 10, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; First Squirrel and Pseudo Onseck John Carr, and
later Brian Sniffen, Onseck, recording.

Minutes read.

They are disapproved on the basis that they suggest that the society
has a system (Vote not recorded).

\goto{Committee Reports}
\subsection*{Algaecomm}
The tiles are gone!  Out, back, and gone for good!

\subsection*{PseudoAnalogcomm}
The fall schedule graphic is up.  Do we want Margaret to buy shiny
things for us?

\subsection*{Pseudojourcomm}
RSN.  Can this be put into the ALGOL yet?

\subsection*{MobComm}
Very little happened, but I have to say something.

\subsection*{Surgery}
Soon we'll know how badly off most of the books in here are.  Jade
looks increasingly competent, and will be, together with an MIT
Librarian, getting us a report on their quality soon.

\subsection*{What the heck is this Comm}

We have an installation guide for a Verso---unfortunately no
accompanying Verso.  But it claims to have a DVI port, and
macrovision.

Also, a phone/address book, blank---apparently from SFBC.

\subsubsection*{OldFartComm}
The Skinner has no idea what the Brother word processor behind the
dexes is.  She is informed by JFC that it is, in fact, a Brother word
processor, which can be used for filling out forms.  Like a pen, only
bigger.


\subsection*{LHE}
More money!

\subsection*{Our Loyal Public}
\begin{quotation}
Security has apparently always been something of an idiosyncratic
concept in Britain's government and royal buildings. In a letter to
The Independent this week, a Londoner named Andy Cullen described how
he had been allowed to take his penknife into the visitors' gallery of
the House of Commons, but had had a banana confiscated by a guard.

``When I asked why, he said it was to prevent me throwing it into the
chamber,'' Mr. Cullen said. ``I never understood why I could be trusted
with a knife but not a banana.''
\end{quotation}

We, on the other hand, are quite sure.

\goto{Old Business}
\subsection*{War Council}
Still no locks, still no keys.

Y: ``The lock and the key shall never meet again on the bonnie bonnie
banks of loch\dots'' and perishes under a hail of jeers.  The motion
chickens, as everyone but Y and BTS is confused.

Rumor has it \emph{Last Dangerous Visions} will be out soon, only 35
years late.  ``Repent, Harlan Ellison, said the Tick-Tock Man'' fails
for lack of second.

ALGOL
\goto{New Business}
Harlan settled with AOL, after the 9th Circuit pointed out that their
changing their DMCA-takedown address apparently for the purpose of
bitbucketing Harlan's complaints \emph{might} indicate that they
weren't acting in good faith.

Also, the \texttt{bnetd} folks have finally been completely screwed,
on the grounds that the EULA ``agree'' button apparently does bind you
to the contract, including the restriction on reverse engineering.

Apparently early rocket tests used Methyl Mercury, or had exhaust
plumes of $HF$.  Sadly, the fusion-ramjet never got tested.

Mount St.~Helens is erup\dots oozing.

It's Octogre.

\goto{Future Business}

Blade Trinity is coming in December.  It's the same length as ROTK
Extended, and has all the quality of a trailer.

The new Boris calendar picture has no bones---she looks like a
shoggoth sculpted into feminine form to lure in innocent hawks.

Andy's ``I like bananas because they have no bones.''  passes 7-4-1\ps

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
