\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/17/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 17, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST or so, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Y moves to approve the minutes as a classic of literature, 12-3-4\ps, even though it shouldn't be a classic until the author is dead.

\goto{Committee Reports}
\subsection*{AlgaeComm}
We have a floor!  And the volatile carcinogens are either wafting away
on the breeze or just glued to the floor.  Or just in big trash bag.
We probably shouldn't throw it out, because we'd be fined.

\subsection*{WCBINAComm}
Part of the pipe over Damn Alley is abated and Damn Rusty.  It's also
leaking way, way more now that they took the nice absorbent insulation
off.  There are not enough buckets.  We'll cover the Alley before we
leave for the night.  And maybe find some way to put in gutters.  Pity
Dvae Kern isn't a keyholder, or we could get him to kern the gutters.
Sorry about the typo.

\subsection*{MobComm}
We bought books!  Bags of books.

Also, many many donations processed.  Big boxes, some of Liz's, etc.

\subsection*{MOSFETComm}
Severe galium (arsenic?) overconcentrations in the mid-to-late P's of
the circulating hardcovers.  That is, a deficit of holes.

\subsection*{PianoComm}
New prentice! Laura Baldwin, \texttt{boojum@mit.edu}

\subsection{P\$eudoLHE}
Appeals tomorrow.  Wonder if Andrew's going, or whether one of us has to fake it.

\goto{Old Business}

The lock mentioned as not being on the door last week is in 401d,
Altair-4, not here.  CAC's lock policies, in general, are depressing.

ALGOL
\goto{New Business}
Sheets are wandering around the membership books.  That's funny.
Maybe they're ghosts, because the holes.  Maybe they're prisoners,
because of the lines.

We now deny everything we're forced to admit, 9-3-0\ps.

We also have a new person here, Karen, to whom we say ``Hi'' 13-0-7\ps.

Two scifi movies open this weekend: \emph{Sky Captain} and \emph{Ghost in the Shell 2}.

\goto{Future Business}
We have four students in the room out of twelve people in the room.  Hrm.

Miller motion chickens 7-2-8\ps.

\goto{CommRep:Vox Sciurorum}
Squirrels bury food.  News at 11 SST, which we've missed by 1719 or so. 

\goto{Future Business} 
The new surgeon may have more stuff from the old surgeon than we
thought, because we found a bunch of glue and card and stock and such.
Also, we got a bunch of pictures of how to do surgery.

Jamie sent 170 lines to some Snovers about shelves, including ascii art, which caused their mail-reading intern to go ``bing''.

Maybe we'll get a newer ver of sno this winter.

Sam gets tired of Brian's puns and moves that a banana be inserted
into the next person to make one, using a hole of the Skinner's
choice.  This passes $n$-2-$n-1$\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
