\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/26/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\setlength{\parindent}{0in}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 26, 2004

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Margaret Gentile, Vice President and
Pseudo-Skinner, presiding; Chris Kuklewicz,  Pseudo-Onseck, recording.

Minutes not read. Missing ... Grrr

(JM) Motion to Condemn Onseck For Lack Of Minutes.

\goto{Committee Reports}
MITSFS-Lite version 1.0
\subsection*{Frustrated Author-Comm}
Pseudo-Onseck whines and moans.
\subsection*{Moo-Comm}
Hero at LSC in December: unusual Thursday showing and also Saturday.

\goto{Old Business}
(JM) No progress on 401D room thing w/ lock.

This just in: Squirrels got fire.
Chickoo

(JM) Samplers (of, e.g., e-books) are still UN-taken outside door.
$<$discussion$>$

(JM) $<$History about TRON, tape-recording meetings, word for word minutes...$>$

ALGOL
\goto{New Business}
(JM) explains that MG screwed up the ALGOL recitation\\
(MG) Chickoo!

(JM) Tubs of books -- ``Medium Large'' donation from David Woodruff (member via
credit).  He wants the tubs back.

\goto{Future Business}

(JM) End of term RSN / IAP RSN.\\
(KevinR) twitch\\
(MG) Rant about some \"{u}ber-final

(MG )$<$takes out vice-whip things.../crack$>$ No one speaks of 2.005 again.\\
(JM) Yes miss Margaret\\
(MG) damn straight.  Keep coming up with things ..weak crack\\
(JM) Your whip cracks are getting less impressive\\
(MG) crack ---ow\\

JM and Kevin discuss IAP hours

banana banana banana

Discussion of IAP SF Marathon.
JM recommends use of proper chemicals before hand.

(KevinR) The first rule of hacking is there is no hacking\\
(KevinR) The second rule of hacking is the first night everybody hacks

$<$singing of philosophers' song$>$

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{... submitted without Respect,}
\centerline{Chris Kuklewicz, Pseudo-Onseck}

\end{document}
