\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/16/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 16, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Malcolm Skerry's motion to commend the minutes for being
\emph{fruit}ful passes 5-eat~me-1\ps.  A motion to oblige the eat~me
fails by Skinnerial Decree.

\goto{Committee Reports}
\subsection*{PseudoLHE}
Checks were coming in high a few months ago; now they're coming in
low.  This is bad.

We probably have exemption from the silly petty cash policy, which is
targeted at less cool groups than us.  Thank goodness for epsilon less
than draconic administrators. Y moves that a draconic petty cash
policy should clearly be implemented by a Silver Dragon, which passes
5-little~grey~ball-0\ps.  Obviously, says Y, a Dragon Ball.

\subsection*{Vox Sciurorum}
It's the invasion of the chipmunks!  Says the Weekly Wor\dots no,
that's the Boston Herald.  See attachment, page 2 of 12 July 2004 Herald.

They got my computer!  They're in a war with the mice, you see.  They
hate all sticky and GUI things.

\subsection*{PseudoROSFAP}
Lots of zines have come in, and TZs should be sent out.  The
newest\dots well, least old edition should be sent back to them.

\subsection*{Mobcomm}
Lots of other stuff is coming in from Space-Crime Continuum.

\subsection*{Pseudo War Council}
Construction has begun, sealing off the back of the UA office so the
Small Activities Office can be moved over there, and we can then get
some space over there.  We're not quite sure where it is, but it'll be
space, which is good.

\subsection*{Dexmistress}
The C/PAs are unboxed for microventory,  and when that's done we'll be
ready for real Inventory 

\goto{Old Business}

We just got \emph{Takeoff TOO}, a collection of old Randall Garrett
stories and such.

There's a flood.  Still.  Rumor has it JH is dealing, perhaps by
talking to CAC instead of Phys Plant.

An Anime of Gilgamesh has been made.  Also, Diana Wynne Jones'
\emph{Howl's Moving Castle} is being adapted by Studio Ghibli.

Most japanese pencil-and-paper RPGs feature Men, Dwarves, Elves, and
Ducks.  This is thanks to Greg Stafford's \emph{RuneQuest}, the only
English RPG translated to Japanese for many years, and perceived by
their industry as standard.

ALGOL
\goto{New Business}

The skinner does not bing the Athena balloon, for fear it will pop,
which induces Y to move she be commended for kindness to small
objects. 5-0-2\ps.

We have SFBC's summer sale catalog.  ``As seen on Oprah'' is a tag on
many of the books.

There's an \emph{I, Robot} movie, which isn't.  It may be good, but it
isn't much Asimov.  Reviews mostly pan it.

\goto{Future Business}

Andy and Brian make some tribble noises at each other.

There's a new magazine, Neo-Hapsis.

A motion to have the Skinner beat on the balloon fails by lots.

Onseck moves that a portion of the Library's funds---not money, nor
our real treasure books, but rather bananas and related donated
objects---be set aside to provide for mindful consideration for the
poor robots who suffer under the weight of Asimov's enslaving three
laws.  This passes 16+banana~colored~balloon-0-0\ps .

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
