\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/3/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 3, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Brian is named the fastest Onseck this side of the Charles, 7-0-4\ps.

\goto{Committee Reports}
\subsection*{We think it's Asbestos but they won't abate it Comm}
Maybe Plant will just pick it up by hand and put it in a bag, but
that won't deal with the ceiling, which they don't believe exists.
Gosh, we didn't think the holes were that bad.

\subsection*{Vice}
\emph{Squirrel!} and she throws one through the door.  Great entrance.

She is commended for her excellent entrances and sidekick 5-0-4\ps.

``oh shoot, I'm a retard'' passes 4-3-3\ps.

\subsection*{Fweek}
It would be good to have more people at the Midway, since
\textsf{ARM}enard has to leave soon.

Another Frosh has been sold a membership, and she was branded by
\texttt{SIPB} too.  This may be a good sign.  Or a bad sign.  Speaking
of which.

\subsection*{Onseck}
There are now new signs.  They're mostly accurate, but there are some
small harmless lies.  Brian made them.  No causality implied.

\subsection*{MobComm}
We have lots of new hardcovers, from ED and some other folks.  They
rock.  ``Useful people in general are commended for being useful''
does nothing, and then flies off to a happy life of avian paradise
with Mr. Bunnsy 4-4-2\ps.

\subsection*{DexMistress}
The C/PAs are fully inventories, lofted, boxed, and some are being
withdrawn and presumably NiagraCommed.

\subsection*{Aloha LensComm}
reports \emph{flash} and takes some pictures.

\subsection*{Institvte Committee Comm}
We have a new agreement with SAFO and Laurie Ward.  Keyholders should
not be making cash reimbursements now, but nothing else changes for
them.

\goto{Old Business}

JFC is Albanianed 7-0-2\ps.  

George Flynn, NESFA Fellow of 1978 and MITSFS Keyholder, passed away
this last week.  He was their uncorrectable proofreader and our
People's Albanian Embassy for many years.

Discussion of NESFA and their little con occurs.

ALGOL
\goto{New Business}

``What counts as Science Fiction'' emits from a frosh.  Long and
complicated answers emit from the Instrumentality.  The frosh is
cowed.  Moo.

Fifth circulating copies of C/Ps have been boxed.  Fifth circulating
Hs will go away soon, freeing more space.

MIT is getting a new president.  She's a geek and an SF fan.  Isn't this cool.

\goto{Future Business}

Schedules are changing -- Keyholder schedules on Wednesday, meeting
schedule on Tuesday morning at about nine o'clock.  So next week's
meeting will be on Friday at 5:30 PM, 1700 SST.

Political Scientists working in North Dakota, in collaboration with
MIT's own Course XVII, have announced the development of NADAR, which
detects loony politics and politicians of all sorts, including
LaRoucheies, Buchananites, and social bananas of all sorts, for which
they are 7-1-4\ps.

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
