\documentclass[10pt]{article}
%\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/30/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
%\newcommand{\ps}{ plus Spehn\xpace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 30, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1500 (sic) SST, Andrew Clough,
Pseudo-Skinner (pause for prompting), LHE and Pseudo-Skinner,
presiding; John Carr, Pseudo-Onseck, recording.

The Pseudo-Onseck makes up a story about the previous meeting, a story
of squirrels and bananimals, but before it can reach its bloody conclusion
Jamie the Pseudo-Pseudo-Onseck finds, formats, and reads the real minutes.

Y moves to approve the minutes as minimally unusual.  Motion passes \hbox{1-2-3$+$Spehn}.
JM notes you get what you pay for.  Passes \hbox{1-2-3$+$Spehn} by Psuedo-Skinnerial Decree.

\goto{Committee Reports}
\subsection*{War Council}  If you like doors, vote for Bush, because the
Democratic Party has caused the UA office construction to stop, leaving
a doorless room with windows.  Maybe next week construction will resume.

\subsection*{Pseudo-Onseck}  Still no money forms.

\subsection*{Mobcomm / Pseudo-LHE} \$60 payment leaves the society's
debt to Mobcomm at about \$900.

\subsection*{Vox Sciurorum}  The squirrels really are conspiring in
secret.  They send each other ultrasonic signals.  Other squirrels
are stealing golf balls and planting them in bird nests.  Are they
eating the eggs and substituting golf balls so the birds don't suspect?
Is it cargo-cult behavior, placing egg-like objects to induce the
birds to lay eggs which the squirrels will eat?  Are they using their
ultrasonic communication ability to coordinate with dogs?  More research
is obviously required.

\subsection*{Pseudo-Hasslecomm}  ARM hasslecommed two boxes of PAs.
We are ready for C/PA inventory.

\subsection*{Pseudo-Onseck}  JFC gave the Onseck a list of magazines
to subscribe to.  Since the Onseck is not here, obviously he failed
to subscribe and is too ashamed to show his face.

\subsection*{Mobcomm}
[JFC]~Books just keep coming in.
[MWP]~Isn't that a good thing?
[JFC]~Not if you're the structure of the Student Center.


\goto{Old Business}

[JM] Four boxes of books have moved to the Small Activities Office, as
has the circulating fanzine cabinet.

[JFC] A guy from the Card Office came to the library and stuck electrodes
into the door lock.
[JM] They shouldn't do that.

ALGOL (without Y!)
\goto{New Business}

[ALC] ``Let it be recorded that a motion approving the usual lack of the
usual debate passes \hbox{1-2-3$+$Spehn}.''

Paul di Filippo wrote a story with a guy dressing like an Albanian, or like
he thinks an Albanian would dress, and another story with a box labelled
``DEAN DRIVE -- ALL ENDS UP.''  They are in the collection {\em Neutrino Drag}.

JFC suggests naming our new room Altair-4.  The direct reference is
{\em The Tommyknockers}, where the alien device that makes things
disappear causes them to disappear to a place the humans call Altair-4.
The indirect reference is to {\em Forbidden Planet}.

\goto{Future Business}

New students will show up sooner than you think.

The Pseudo-Skinner declares a Miller Motion to have failed and a
second to have passed.  JM says ``that's lame.''

\vspace{12pt}

\noindent
Meeting adjourned, 16:40 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr,  Pseudo-Onseck}

\end{document}
