\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/27/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 27, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Approve the minutes as being fantastical\\
Passes 4-1-0+Spehn


\goto{Committee Reports}
\subsection*{Mobcomm$_1$}
There was only one box in the post office.  At this very moment,
Cassie is reading the new Lackey romance from that pile, to the
exclusion of her Prentice project.

Also included: Australian fiction, Dr. Who novels
\subsection*{Pseudo-Bluebellcomm}
Tomorrow, the last new hard cover leaves the new books shelf.
\subsection*{Onseck}
Will be ordering more covering material 

\subsection*{MobComm$_2$}
Apparently the second box got separated from the first, on an 80 mile
journey, and arrived 3 days later.

Motion: Note the Laurel K. Hamilton has been weighed in the balance and
been found wanting\\
Passes 4-2-1+Spehn

``Okay, okay, maybe it's porn'' -JM, about the Anita Blake books.

Discussion ensues in which JFC reveals that he has read all the Blake
books.

\subsection*{CoufComm}
The ICSF responded wrt the book-trading concept:\\
They agree in principle, within their budget of 50-75 pounds/year
This is still a good deal for us and for them.
Beyond that, we will pay them in money, which is okay.

Y suggests that we pay them in pizza. KHA mentions the pizzapieer,
which makes very interesting custom pizza, and delivers to MIT but
probably not Cambridge.

\subsection*{WarCouncil}
We have been fvcked by the Instvtvte again:\\
Phil Walsh says that any attempt to do significant renovations on the
4th floor will trigger the ``update room/floor to meet code'' which
causes the cost and bureaucracy to skyrocket.  We will perhaps get
some space on the 4th floor which would potentially let us get things
out of the warehouse.

``We were going to be blessed by a mixed blessing.  Not having to deal
with hospital food does not mean that not having the life-saving
surgery you were planning is a blessing.'' -JM

We can ask the ASA for some of their renovation money, since it isn't
going to be used now, to get custom shelves and things.

Someone talking to JM suggested that we use the ``book ash'' method of
compression---burn each book (separately) and put little bags with the
ask on the shelf.

\goto{Old Business}
JFC has read another bad book.  BTS proposed an \\
Albanian Motion: JFC\\
Passed 6-2-4+Spehn\\
before he could start telling us more about it.

Finboard Appeals were posted: \$750 for books, and ops money for the
picnic, which means we don't have to poster the Infinite about it.

Motion: Experiment by requesting an imaginary sum of money
fails for lack of a second

JFC has noted to the VGG that the life membership of Hal Clement has expired.\\
Motion: Have a moment of silence for the life membership.\\
\emph{Onseck's Note: The moment occurred before the motion was passed}\\
Passes 4-0-0+Spehn

All donations received in 2003 have been dealt with (have been
evaluated), and the last of the acknowledgments are about to be sent.

Jen Hawthorne (Class of '89, former Star Chamber) is moving back to
the area in May (and now has a membership bought from donation credit).

With the failure to get actual adjacent space and move, the
incremental space plans will resume.

ALGOL
\goto{New Business}

JFC finds evidence that Jen Hawthorne was co-existent with cameras.

Y has a supposedly lost novel by Jules Verne which was so unpopular
that it vanished entirely.  It was recently re-released.

We had a new piece of publicity: SpectrVm featured 2/3 Ed and 1/3
MITSFS.  (Brief discussion ensues about Tech Review and how two
versions are published---the one with MIT stuff and Alum notes, and
the one without that).
Ed is less than totally thrilled with the article, which he thinks was
poorly edited, and since it failed to integrate any of his requested
changes.\\
There was an article in TR about us in 2000ish.

A new BFG has appeared in the Library. JM thinks it might be MHG's,
either personal or by virtue of being Sgt. at Arms.

JM demonstrates that he does 

``My inclination to assume that my weapon is a phallic symbol has
betrayed me.''\\
Passes 12-0-0+Spehn

Motion: Note that the BFG has three balls\\
Passes 6-3-1+Spehn

BTS notes that it is orange, and thus should be on reserve, but also
has a big blue dot on the other side, and thus should be thrown out.

ALC notes that we could trade it for floor space.
ED: ``Or use it to conquer floorspace''
BTS: ``I'll trade these bullets for your floorspace''
     ``But we don't want any bullets...''
     ``That's okay.''

JFC begins reading.

Miller Motion:\\
Fails 6-8-4+Spehn

Miller Motion:\\
Chickens 2-0-4+Spehn

Motion: Beat JFC over the head with a banana
Passes 10-0-4+Spehn

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
