\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/09/2004}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 9, 2004

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Ed Keyes, Pseudo-President and Skinner, presiding; JFC, the unusual Pseudo-Onseck ("No, he's the usual." "Pseudo-unusual?"), recording.

Minutes read.

M: expunge William Shatner and all mention of WS from the minutes. 4 and camo-0-2 +Spehn.

"My camo cape doubles as a blankie!" (MHG)

\goto{Committee Reports}

Frustratedauthorcomm: 16 rejections.

Mobcomm: 3rd copy of Road to Damascus.

MHG is allergic to the library or her unwashed blankie.

War Council: ASA general body meeting; ARM reelected.

Cthulhu ate Amanda's lab report.

Theftcomm: "catching up." (JM)

Bluebellcomm: books have been covered; some are not known to have been covered by assistant Bluebellcomm.

Foo, bar, bar?

\goto{Old Business}

Our slide was shown at RotK, once blue and then normal.

MHG says "LSC... sucks!" and Amanda leaves.

Cavin donation: 1400 books. Where will we put them? Rerooming not yet approved, but nobody objected to proposal at general body meeting.

"Faceless bureaucracies of doom!" (MHG)

"Are there any usual motions?" (EP)

"Second!" (MHG)

ALGOL.

\goto{New Business}

MHG has pulled three feet of blue thread out of her blanket.

Silly spectrum article (with ED) reprinted in Tech Talk this week. MHG doesn't read T.T. because it has no comics.

MHG talks about Dave Barry. Favorite story about mango tree. Exploding whales also mentioned.

\goto{Future Business}

MHG will get a story published?

Prefrosh next week.

"Let the brainwashing begin." (MHG)

"My brain hurts!" (Andy)

Blah... "Hordes of gumbys..." blah.

Life of Brian being rereleased to take advantage of Passion mania. Singing follows and discussion of the movie being shown/described in Latin class.

Motion: declare Margaret a mongoose! 2 and "why the heck not"-0-0 +Spehn.

But we have no snakes. Discussion of lizards in basements, dead and alive, and black widow spiders, wasps, and rattlesnakes in Margaret's yard. Spiders tried to catch M's doglet.

JFC reads romance novel blurbs.

In the future: Worldcon, with MHG in costume.

LA may outlaw tentacle porn (hentai) in cars.

"What would pain and suffering be without glue?" (ED, after MHG)

Spaceballs is quoted extensively.

Col. Sanders may be MHG's next costume. Spandex.

Chris critiques M's performance: "Almost right!"

Miller motion. Fails 6-6-1 +Spehn.

Second Miller motion. Passes 8-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1746 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
