\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

(Note: The following is copied verbatim from L.C. Skinner II's original, which is being preserved for some hypothetical collection of Skinneriana. -DJH) [Editor's note: 60 years later, the legend never dies. -MJS]

\begin{center}

Minutes of the MIT Science Fiction Society

Friday, January 18, 1963

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Members present: 8.

The meeting was called to order at 5:07 PM by President Campbell. In order to fill the void ("In the beginning vas the void..." -The secretary) caused by the absence of the secretary, the treasurer gave a lengthy report. The minutes of the previous were not read.

Treasurer's report:

Money outgoing: poster- 1.35, movie- 3.00, entertainment license- 2.00, building 2 poster- 2.01, police protection for movie- 10.00, tickets for movie- 2.55, change for movie- 50.00; total before movie- 9.21.

Money incoming: movie- 454.54, entertainment license- 1.47; balance as of Jan. 18, 1963- 453.63. Cost of movie- 34.59, projectionist fee- 27.00.

Finboard report:

Budget- 500.00. Number of members- 82; 14 percent increase over last year at this time. Totals outgoing this semester- 319.22 on library, 51.22 on journal, 121.15 on movie expenses.

Enough random statistics.

\goto{Committee Reports}

Moocomm: rousing success.

Theftcomm: absent.

Vengeance Fleet in absentia: no report.

Ambassador to BU: absent.

Minicult: absent.

\goto{Old Business}

None.

\goto{New Business}

Skinner got letter from APO carnalcomm bubbling with enthusiasm. Bah, humbug.

MSD to adjourn (MacMillan-M. Harper). 2-6.

MSD to adjourn (Skinner-Harper). 3-5.

MSD to adjourn (Somebody-somebody else). 4-4.

Skinner keeps voting twice.

String of such nonsense interupted (sic) by arrival of Lewis (sicker). Oh well.

Libcomm report called for by Campbell.

Libcomm: we got some donations. How's that, enough. (Rather briefer than usual?)

Miss Harper and Mr. Lewis discussed money before the interested? onlookers for awhile.

Someone brought up something about some Unknowns which Lewis has evidently purchased during the summer for some exhorbitant (sic) fee. A bit of ill feeling followed and a few ill chosen comments heated the air for a bit.

At this point C. Chadwick (reluctantly reporting his name) so moved and V.P. Dyro seconded the motion.

MSD to adjourn (Chadwick-Miss Dyro). 5-4 (two people voting twice).

MSP to adjourn (Miss Harper-Chadwick). 4-?.

Announcement of adjournment at 5:23 by president Campbell.

\vspace{12pt}

\centerline{Respectfully submitted by your humble acting secretary,}
\centerline{L. Court Skinner, II}

\end{document}