\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, January 11, 1963

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:05 PM, as usual, by L.A. Campbell, as usual. The minutes were read and approved, as usual.

\goto{Committee Reports}

Treasurer and Moocomm reports, all mixed together: 82 members, 74.11. Infinite details were settled, or quasi-settled, for the movie. A Building 2-style drop poster will be made Saturday. Morris printed up some posters for the various bulletin boards. FinBoard wants some financial data on the noble Society.

Libcomm: Donations received from Hoylman, Speiser, and Lewis. Ballantine is reprinting Burroughs stuff. The library will be open during reading by Lewis, who has no finals.

Jourcomm: An issue will be published in grand style during midterm. Coolies were secured.

Theftcomm: Two posters up.

Vengeance Fleet: Still lonely.

\goto{Antique Business}

Zero.

\goto{Contemporary Business}

MSI (Tom) that the SFS field a tiddlywinks team. (No qualified players.)

Movie coolies: Harper; Hoylman; Morris; Olson- pardon me, Tom; Campbell; Skinner; Lensch. Correction to last week's minutes: flick is at 7 and 9:30.

Morris claims he got food poisoning from commons. (By now he should be immune.)

MSD (Some nebulous person) to adjourn. 6-9.

MSP (Lewis) to adjourn. 11-8. 5:30 PM.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}