\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, February 8, 1963

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:07 PM by Campbell. The minutes of the reading period meeting, a meeting held without prior announcement and contrary to tradition, were read by L.C. Skinner II. The minutes of the last real meeting were read by the noble secretary.

\goto{Committee Reports}

Theftcomm: Two posters up.

Jourcomm: Issue 9 is out.

MiniCult: (Morris) The President's Report is out. Read some nonvital statistics. (Humer) J.W. Campbell Jr.'s childhood desire was to be the editor of Scientific American.

Libcomm: Speiser donated over 10 Tarzan books. Other people donated other books. Hydrogen-5 has been found. Malcolm Y should have a key.

\goto{Old Business}

Hoylman read a letter from Uncle Hugo G., who wants to set a date in October. The secretary will write a reply.

\goto{New Business}

Lewis wants to invite Hal Clement Stubbs to a small informal meeting this term.

MI (Y) Something about writing letters to Gernsback.

MI (Skinner) Something about making motions to ignore motions.

Lewis announced that this was his birthday. He's expecting me to make some snide remark about it in the minutes, so I won't.

MI (Skinner) to sing "Happy Birthday" to Lewis.

TIMEOUT. As noted (negatively) about, the treasurer was absent at this meeting, so that no one was able to purchase a spring term membership. Only three persons present at this meeting, including Campbell, had paid previously, thus securing voting rights. This explanation was necessary to explain the following vote. Okay, back on the time track.

MSP (Tom) to adjourn. (1+epsilon)-1. 5:30 PM.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}