\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 9, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; John Hawkinson, Onseck, recording.

Minutes read.

Motion to have Jamie hit on the minutes passes.

\goto{Committee Reports}

Bluebellcomm: we can't cover hardcover.

Talk about black ribbons and blue backgrounds.

Erincomm created, Jamie appointed only member. Duty to report on Erin.

Erincomm reports Erin had dinner already.

Mobcomm: hardcovers bought, paperbacks on the way.

\goto{Old Business}

Phil Nesser will buy our magazines!

Motion to tickle Jamie. Happens.

Ancacomm reports she went to a con and was trapped in Houston for many months.

\goto{New Business}

Jamie declared Albanian.

Meeting devolves into Infocom games.

I give up taking minutes.

\goto{Future Business}

Meeting is assumed to end eventually.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}