\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 26, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Minutes read.

Motion to commend minutes as content-free. Passes 20-4-3 +Spehn.

\goto{Committee Reports}

Milkcomm: Milk got votes for Big Screw.

Pseudo-Picniccomm: Invitations should go out.

Pseudo-Pianocomm: 3-4 apprentices.

Time-warp for 10 minutes... and another 10 minutes... and another 10 minutes.

Pseudo-skinner fills in skinner.

Skinner resays everything people have said and is pestered into admitting no knowledge of anything. Arrival of skinner lames-out meeting and is boring.

Neal Dorrow wins Big Screw!

Bitch aobut Susan Allen...

Talk about prefrosh and complain about Milkjen not being an apprentice.

M: Milkjen is to be asked why she's not an apprentice at every meeting. Many-0-4 +Spehn.

Innocentcomm: Erin thinks Marcus is corrupted. Everyone disagrees.

Skinner loses control of the meeting...

Milkjen offers to perpetrate her one-ness with Tara.

Milkcomm says something about "sour milk," flames about Technique.

Eddie graces us with his presence.

\goto{Old Business}

Motion to commend/condemn Milkjen for being cute. Chickens 0-0-0 +Spehn.

Usual Algol. Skinner sighs.

\goto{New Business}

Banana-colored egg determined to be inherently unstable.

Furry guy arrives.

Banana motion fails 10-16-1 +Spehn.

Motion to have Jamie sit on egg till it hatches. Bunch-4-1 +Spehn.

We watch the egg not hatch.

Fight over Eddie's money. Milkjen litters pennies.

Jamie donates 1 cent to the library.

Jamie has fantasies about John Conger.

Pseudo-Onseck is questioned as to whether or not he's taking copious notes. Pseudo-Onseck defends his honor.

\goto{Future Business}

Banana motion passes 20-8-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1783 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}