\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 25, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Gabriel Valencia, Onseck, recording.

M: Neel elected pseudo-onseck. 3-8-0 +Spehn.

Minutes read from memory.

Motion to declare minutes memorable. 8-some-1 +Spehn.

M: onseck is [illegible]. Fails.

M: huh. 20-0-1 +Spehn.

M: chop off Neel's limbs. Chickens 8-0-14 +Spehn.

\goto{Committee Reports}

Mobcomm: new books.

Milkcomm: milk is running for UMOC.

M: commend Neel for reading through ears. Passes every-2-1 +Spehn.

Commcomm: Neel moved from Theftcomm to Hasslecomm.

\goto{Old Business}

Robert Jordan's characters are older by 2 years.

Discussion of length of Lord of the Rings.

ALH: I'm confusing authors; little children in Robert Jordan.

Motion to declare Jamie pleasantly irrelevant. Passes 14-0-4 +Spehn.

Motion to declare Jamie unpleasantly irrelevant. Passes some-more-less +Spehn; inverse skinner rule.

Matrix vote. Chickens 1-4-6 +Spehn.

Pentiumcomm? Finger motion.

M: when 3 motions are on the floor, do away with Neel. Passes 18-1-0 +Spehn.

Motion to have 3 motions. Motion to have second. Matrix vote.

Neel becomes null set, entity does matrix vote.

Jamie appointed Ambassador to the Null Set.

All motions indeterminate (result of having infinite number of chickens).

Neel fails for lack of 18.06.

\goto{New Business}

Auctioneer skinner: Ben wins a chicken.

Motion to sell skinner fails for lack of second. Passes by skinnerial decree (inverse skinner rule).

Miller motion fails.

JPM to AM: get your back(pack) up here.

Motion to separate his back from the rest of him. Passes what-what-what +Spehn.

\goto{Future Business}

Miller motion. Second. Fails 11-13-0 +Spehn.

Members: Skinner cannot count at all...

Skinner: Members cannot sing at all...

Members: Skinner has no tail at all... repeat.

Miller motion fails by skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, indeterminate time.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Gabriel Valencia, Onseck}

\end{document}