\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 15, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Gabriel Valencia, Onseck, recording.

Minutes read.

M: no one presiding. Passes 12-0-4 +Spehn.

\goto{Committee Reports}

Motion to finish ALH's motion. Passes 10-0-1 +Spehn.

Blah, blah, groan. Chickens 0-1-4 +Spehn.

Motion to assign Innocentcomm to skinner. Fails.

\goto{Old Business}

Motion to have louder bing; motion to have quieter bing. One of them passes 4.5-2-2 +Spehn.

ALH silences gavel with Onseck's sweater.

Motion to have reengineering committee covered with sweater. Passes by skinnerial decree.

Motion to declare sweater virgin. Passes over-under-less +Spehn.

Sex life of bicycles? Chickens 1-2-0 +Spehn.

Motion that motions don't need second dies for lack of second.

\goto{New Business}

Motion to reverse all motions this meeting. Fails 4-13-1 +Spehn.

Motion to shoot down all of Toby's motions. Dies because Toby is in favor.

Banana motion, Miller motion.

No. Passes by skinnerial decree.

Motion to commend Andrea for not getting paid. Passes.

Motion to have Innocentcomm take out Gabriel's sweatshirt for a good time. Passes 5-0-4 +Spehn.

Motion to put sweatshirt in Innocentcomm. Dies for lack of second.

Miller. Chickens 5-3-7 +Spehn.

Motion to give tardy member stern talking-to. Dies.

Motion to have Janelle second something. Passes 16-1-1 +Spehn.

Motion to condemn skinner for intimidating Janelle. Janelle seconds. Fails 1-10-1 +Spehn.

\goto{Future Business}

Nth + 1 Miller motion. Dies.

\goto{Recurse to Old Business}

N-1 Miller motion.

N-2 Miller motion. Fails 5-7-6 +Spehn.

M: motions fail for second; fails for lack of second.

Greetings. Passes 7-0-1 +Spehn.

Skinner: Wooo!

Motion to strike banana from last week's minutes. 7-10-3 +Spehn.

Motion to automatically fail all banana motions. Passes 12-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1733 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Gabriel Valencia, Onseck}

\end{document}