\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 31, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Erin, Keyholder and Pseudo-Skinner, presiding; Alana M. Starr, non-member and Pseudo-Onseck, recording.

Minutes read.

Motion to declare last week's minutes banana colored. Fails 5-6-0 +Spehn.

\goto{Committee Reports}

Boriscomm reports that it is still 1996.

\goto{Old Business}

Old keyholder.

The answer is 42.

The sands of time have buried many ancient cities.

Bags exist.

Dragons are cool.

\goto{New Business}

The Star Chamber is lame.

Motion to whip the Star Chamber. Passes 7-2-0 +Spehn.

Motion for Erin to dance an Irish jig on the keyholder desk. Passes 10-0-3 +Spehn, then failed by skinnerial decree.

Motion to note that Erin has no Irish blood in her. Chickens 3-2-8 +Spehn.

Erin turns red (as always).

William continues to type at the computer.

Motion to condemn William for not taking care of his keyholder duties. Fails 4-5-3 +Spehn.

Erin has never done this before (according to her).

Sean Connery was a BAD choice to do the voiceover for the dragon in Dragonheart. James Earl Jones would have been a better choice.

Giant red ant-like insects burst into the room and rip William away from the computer. The general consensus is that he is either being eaten or mangled by these insects. (There is much yelling, shrieking, and bone smashing going on in the hallway.) A debate ensues as to whether or not these red insects are breaking laws of engineering. The result of this debate is "yes, it is impossible for these insects to be this size and therefore they do not exist." The giant red insects again burst in and this time remove Bronwyn.

Motion to ignore these insects because they aren't real. Passes 3-2-2 +Spehn.

While more boring discussion ensues, the pseudo-onseck carefully figures out where the weak spot is on these creatures.

The monster insects take another helpless member from the library, thereby leaving only the pseudo-skinner and pseudo-onseck.

Erin looks at the onseck blankly and gradually pales as she realizes she is the closest one to the door now.

The ant things rush in again and try to grab Erin but the onseck, having carefully prepared for this moment, flies into action and quickly defeats these creatures, protecting the pseudo-skinner and, above all, the library from their evil plans.

The onseck thinks she deserves an honorable membership for her quick thinking and skilled defense of the library.

\goto{Future Business}

Motion that the red insects were really banana colored inside. Passes 4-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1706 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Alana M. Starr, Pseudo-Onseck}

\end{document}