\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 26, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; John Hawkinson, Onseck, recording.

Minutes read.

Motion to declare minutes green as opposed to red (as opposed to blue). Passes 6-4-2 +Spehn.

\goto{Committee Reports}

Moocomm reports SF marathon.

Motion to condemn few who have missed some of SF marathon movies. Passes lots-few-none +Spehn.

\goto{Old Business}

Talk about mammoths.

Black Cauldron motion passes by skinnerial decree.

[Illegible] motion. Passes 9-5-6 +Spehn.

\goto{New Business}

Neel gets confused. Chaos reigns. 14-6-1 +Spehn.

Motion chickens 5-5-many +Spehn.

Jay and Jamie declared Albanian. 14-0-1 +Spehn.

Motion passes. 4-0-0 +Spehn.

\goto{Future Business}

Nominal motion passes few sensed-few sensed-few sensed +Spehn.

Meeting ends (well, no, but we ran out of space on the paper).

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}