\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 2, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; John Hawkinson, Onseck, recording.

Minutes declared Albanian because they were unreadable.

\goto{Committee Reports}

Mobcomm: billing office closes at 4:30 PM. Sigh.

\goto{Old Business}

Usual stuff.

Usual stuff. \bing

What about the usual stuff.

\goto{New Business}

The sons of Larry and Curly are suing the son of Moe. The lawyer is Bela Lugosi Jr.

2 weeks from today Lois McMaster Bujold is coming- needs someone to entertain her 14 and 15 year old SF fans on Friday afternoon. Call NESFA (625-2311) for details.

Things happen. I write things down.

\goto{Future Business}

Move to censure the skinner for not bringing a banana fails.

Motion to end the meeting passes.

Skinner plays with star-shaped piece of metal. It dings- sort of.

Miller motion fails.

2nd Miller motion passes 4-7-9 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}