\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 13, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Gabriel Valencia, Onseck and Pseudo-Skinner, presiding; Ben, Pseudo-Onseck, recording.

Minutes read.

Motion to consider minutes puzzled. Passes 17-2-a little +Spehn.

\goto{Committee Reports}

Pseudo-mobcomm: new books.

Hasslecomm: groan.

\goto{Old Business}

Many \bing s. Pseudo-skinner attempting to make a good bing.

\bing Toby makes a good bing.

Motion to commend Toby on the bing. Passes all-1-1 +Spehn.

Motion to commend skinner on counting.

Motion to commend JM on birthday dies.

\goto{New Business}

Skinner has no clue at all...

Motion to declare everyone Jamie amended so that Jamie is Bill. Passes 10-7-3 +Spehn.

Second Miller Motion. Fails, dies.

Belated Motion reread. See minutes of 9-6-96.

Motion to condemn pseudo-onseck for lack of technology. Passes 12-3-3 +Spehn.

Motion to replace skinner with identical piece of rubber. Passes 12-5-1 +Spehn.

Description of "Quake Hold" fixative. Its purpose is to hold things on shelves during an earthquake.

\goto{Future Business}

Motion to adjourn. 13- -  +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1702 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ben, Pseudo-Onseck}

\end{document}
