\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 15, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, Ex- and Pseudo-Skinner, presiding; M. Whitson, Pseudo-Onseck, taking minutes in an effort to demonstrate worse handwriting than Toby.

Minutes read.

Motion made and passed to screw the Star Chamber for not being present.

Brownian motion re: minutes chickens 2-4-6 +Spehn.

\goto{Committee Reports}

Boriscomm: it's still 1996.

Pseudo-Mobcomm: lots of new books.

Motion to congratulate Erin for expecting and to ask who the father is. Passes 5-(-8)-2 +Spehn. (Determined that it is a clone of Erin.)

\goto{Old Business}

Usual x5.

\goto{New Business}

Erin is in the process of reproducing parthenogenetically.

Re: newspaper article about person in Starfleet uniform. She was let onto the jury, but was kicked out for talking to the press.

Moocomm reports Close Encounters (new edition) is on Sunday.

\goto{Future Business}

Motion that Neel has a banana-colored shirt. Passes lots-few-some +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{M. Whitson, Pseudo-Onseck}

\end{document}