\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 12, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; John Hawkinson, Onseck, recording.

Minutes read.

Motion to not move fails. Skinner clarifies that this means we have the option of moving or not. Sloth wins.

Skinner complains that Jens never tell him anything.

Move to desecrate Jen's reading list since she might be in Oregon or another far away place.

\goto{Committee Reports}

Pseudo-Aloha Lenscomm: Moves to pillory false Aloha Lenscomm, in an attempt to pillory Technique photographer. Since the pseudo-Lenscomm was Jay, we pilloried him instead.

Innocentcomm has been working on Marcus and reports results.

\goto{Old Business}

Picture taken. Skinner not decapitated.

\goto{New Business}

Motion to add to Flushcomm's responsibilities and make it responsible for making MIT fall down. Passes.

Toby appended to Flushcomm.

2 severed thumbs up for 12 Monkeys.

Matrix vote too complicated for onseck. There was a banana in it. Fails.

\goto{Future Business}

Motion to end the meeting passes.

Motion to declare Chris Albanian. Passes.

Motion to have a banana motion. Skinner says something unintelligible.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}