\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 1, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Gabriel Valencia, Onseck, recording.

Jay moves to block with Andrea in lap.

Called to order.

Minutes read.

Motion to regard minutes as gimpy; motion to not regard minutes; motion to have matrix vote. 3-3-10 +Spehn; 13-4-6 +Spehn; 5-10-2 +Spehn. Determinant negative; motions fail.

Jay displaces Andrea.

Motion to declare skinner less than romantic. Chickens 0-2-3 +Spehn.

\goto{Committee Reports}

Andrea attacks Jay with the little gavel. Jay: mine's bigger than yours is.

Commcomm: there are committees.

Mobcomm: new books.

\goto{Old Business}

Andrea sits on the block.

Motion to overwhelm Jay. Passes 11-3-3 +Spehn.

Pathetic \bing

ARM: back in my day, we had real bings.

Motion to commend Andrea for guarding gavel block. Passes 7-0-1 +Spehn.

\goto{New Business}

Motion to get hammer to use Telzey toys. Fails for irrelevance.

\goto{Future Business}

TE: We'll be getting new books.

ALH: Egg hatched.

Jay died and went to hell. Fails for lack of soul.

Jay to ALH: You're ruining our fliers! Edward: We have fliers?

Motion with too many words. Passes 2-0-6 +Spehn.

(\bing on garbage can.)

ALH: Skinner has no tail at all... but does he have a head pointer?

Members: Skinner has no tail at all...

\vspace{12pt}

\noindent
Meeting adjourned FINALLY (with dull thud).

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Gabriel Valencia, Onseck}

\end{document}