\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 5, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Gabriel Valencia, Onseck, recording.

Minutes read.

M: minutes better than they could be, but not much. Chickens 6-6-8 +Spehn.

Motion fails due to lack of skinnerial clue.

M: commend Mike for being tongue-tied. Passes by skinnerial decree, lots-1-5 +Spehn.

M: commend skinner for something or other.

M: Paul's in pain. 10-0-1 +Spehn.

\goto{Committee Reports}

M: create Andreacomm. Passes 12-4-3 +Spehn.

M: appoint Jay as a member of Andreacomm. Ties 9-9-1 +Spehn.

M: appoint banana as a member of Andreacomm. 5-lots-none +Spehn.

M: Jamie should give Andreacomm lots of money. All-0-0 +Spehn.

\goto{Old Business}

Fuzzy banana motion. 10-lots-7 +Spehn.

M: commend Isaac Asimov as still here. Passes by skinnerial decree.

\goto{New Business}

M: something I couldn't hear. Ties.

M: commend Jamie for something. Passes by skinnerial decree.

Tickle motion. Fails.

Something. 4-12-0 +Spehn.

M: commend reality for being warped. Passes by skinnerial decree.

?. Fails by skinnerial decree.

M: commend Mike for bashing his head. Chickens some-some-more +Spehn.

\goto{Future Business}

M: stuff bananas. Lots-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned later than it should've been.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Gabriel Valencia, Onseck}

\end{document}