\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 5, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Minutes read while Jamie complains that no one writes down cool stuff in meetings.

M: approve minutes for sex life with skinner. Passes.

\goto{Committee Reports}

New dexes same other than new info thing that pseudo-onseck misses while writing the rest of this.

Condo/condom? auctioned off. Chocolate, champagne, banana flavors.

"Put these on your banana" slogan.

Jamie: "Is there such a thing as a flaccid banana?"

Pseudo-Bluebellcomm: Bluebellcomm functional.

Minicult: consumer protection- "keep package closed when not in use and keep away from children" on baby powder.

\goto{Old Business}

Jamie reminisces.

M: turn on pseudo-onseck at meetings. Passes. Problem- who will do it? Significant glances wander around.

Algol.

Unusual discussion.

\goto{New Business}

Pseudo-onseck complains re: one-sided paper.

M: transfer minutes to Mobius strip. Passes.

\goto{Future Business}

M: buy pack of banana flavored condoms to turn on pseudo-onseck. Passes.

Skinner fails to notice meeting is over- this is pointed out.

\vspace{12pt}

\noindent
Meeting retroactively adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}