\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 8, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Gabriel Valencia, Onseck, recording.

Minutes read.

ALH: What happened to overwhelming Jay?

Eh? Passes what-what-11 +Spehn.

\goto{Committee Reports}

Eh! \bing

Panthercomm: lost data when Athena went down.

Apathycomm:

Motion that skinner be struck from last week's minutes. Dies for lack of second.

Motion to condemn skinner for receiving secret message. 15-1-0 +Spehn. Inverse skinner rule; skinner condemned for receiving public message.

Eternal eh.

Motion to have onseck read secret message. Passes.

Jay overwhelmed.

Secret message is payment of overdue fine.

Chaoscomm: success.

\goto{Old Business}

Lots of motions die.

Motion to appoint ALH to overwhelm Jay. Passes. Inverse skinner doesn't apply.

Jay intimidates Edward. Pleas of help die for lack of second.

Does anybody smell something burning? Passes 5-1-0 +Spehn.

Motion to tie Jay to banana stake and burn him. Fails 13-2-2 +Spehn.

\goto{New Business}

Andrea is ignoring us all. Passes 7-1-1 +Spehn.

Motion to condemn guy who lives with me for keeping up with meeting. Passes 7-0-2 +Spehn.

Ingrid, known as Zebra, stares at Jay.

Motion to condemn people who can remember 7 things at once. Passes 2-0-0 +Spehn.

Motion to have a second. Fails 7-9-2 +Spehn.

\goto{Future Business}

Miller motion. Fails.

Second Miller motion. 11-2-? +Spehn, chickens. Auction for votes. ?-?-ring +Spehn.

Miller motion. 8-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting agenda'd, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Gabriel Valencia, Onseck}

\end{document}