\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 4, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to confiscate the skinner. Passes 14-1-3 +Spehn.

\goto{Committee Reports}

Milkcomm: the Milk is alive.

Pianocomm: most of a keyholder project is figured out.

\goto{Old Business}

Motion to put off determining the status of the Belated Motion. Chickens 5-7-even more +Spehn.

Do something with it! Fails 3-8-6 +Spehn.

What paradox??

Usual motion passes by skinnerial decree. The Belated Motion dies a sad death.

\goto{New Business}

\goto{Future Business}

Miller Motion. Fails.

Gabriel's motion fails for lack of a second.

Neel's motion fails for lack of a second.

Motion to confiscate all books in the library during the meeting. Passes every-no-no +Spehn. (Resulting in Spehn not being in Universe.)

Motion to exempt bananas from previous motion. Passes 10-4+A-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1700001 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
