\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 28, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Gabriel Valencia, Onseck, recording.

Motion to time warp for 5 minutes. Passes by skinnerial decree.

Minutes read.

M: regard the minutes as long-forgotten.

\goto{Committee Reports}

Bluebellcomm has done some work. Commended.

\goto{Old Business}

The skinner is neither the oldest nor the youngest in the library. Motion to commend skinner passes.

\goto{New Business}

Mike yawns. New business begins.

We're about to have new signs listing all the keyholders.

M: commend Silvain's stereo for being louder than a MITSFS meeting. 3-2-1 +Spehn.

M: Mike may not think of... 3-3-2 +Spehn- nada.

Something happens. Pseudo-onseck arrives.

\goto{Future Business}

Banana fails 1-lots-1 +Spehn.

Pause until I rebutton my shirt.

Miller motion fails.

Banana motion fails.

Random motion fails.

Miller motion ties, runoff passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Gabriel Valencia, Onseck}

\end{document}