\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 6, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Minutes commended.

\goto{Committee Reports}

General complaint on temperature.

JM: rush was not good.

MS: Californiacomm exists. Overruled.

\goto{Old Business}

JM: blaming Susan Allen for RCA.

\goto{New Business}

JM: motion to put Marcus in charge of committee on (very long description of sharp objects) with the amendment that it must be made in one breath. Passes 22-2-1 +Spehn.

Motion to commend Bluebellcomm dies.

Lame motion. Chickens 0-0-lots +Spehn.

ALH condemned for speaking about unspeakables.

Motion to nail Marcus to the floor with (long description of sharp objects). Passes 12-0-2 +Spehn.

Motion to vote on belated motion to commend belated Boriscomm in two weeks. Passes.

MS and EMP commended for trysting in the corner.

Albanian motion on JM. Passes.

JM: prattle in Albanian. Albanian Consulate assures us it's of no importance.

\goto{Future Business}

Quantum matrix vote takes a banana curve and a prod with a banana motion with it.

Miller motion.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
