\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 20, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to have minutes ding. Chickens 9-5-lots +Spehn.

\goto{Committee Reports}

Panthercomm: need to take new books off the shelf to make room for other new books.

Motion to commend TSR for putting a square die in a round hole. Passes all-0-0 +Spehn.

\goto{Old Business}

Delay Belated Motion two more weeks. Passes 20-5-0 +Spehn.

Condemn Toby and Jen for discussing real business at a meeting. Passes every-no-no +Spehn.

Pseudo-boriscomm: it's still 1996.

Algol.

\goto{New Business}

Discussion of MIT and the real world.

Motion to declare Eddy Albanian. Passes 23-2-0 +Spehn.

Announcement of "Dark Skies."

Apathy vote.

\goto{Future Business}

Condemn Gabriel for putting mail in banana motion. Passes 18-1-7 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1700001 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
