\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 6, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Gabriel Valencia, Onseck, recording.

Minutes read.

Motion to declare minutes orange. 9-1-1 +Spehn.

\goto{Committee Reports}

None.

\goto{Old Business}

Cristy's not present.

Move to table pending motion. Passes 9-3-4 +Spehn.

\goto{New Business}

Edward: Intelligent animal chasing human. JFM: Lion, Witch, and Wardrobe.

Intelligent pre-lion beaver commended.

M: kill Jeremy Silvane for asking about D&D modules. Passes 7-1-3 +Spehn.

Long conversation. Passes by skinnerial decree.

Commend meeting for being more fun than LSC executive committee. Chickens 0-1-4 +Spehn.

River Ingrid. Passes by skinnerial decree.

Discussion of old traditions.

Motion to thwack Cambridge Trust. Passes 13-0-0 +Spehn.

Commend windows for being tall and reaching ground. Passes 17-0-3 +Spehn.

Commend Jay for not reaching ground and being tall. 18-0-3 +Spehn (twice; double \bing). Inverse skinner rule to one.

Skinner is his own inverse. Passes by skinnerial decree.

Commend Professor Lendon for banging on pans in eclipse. 15-4-1 +Spehn.

Commend Professor Lendon for being Lendon. Passes by skinnerial decree.

Motion to fire upon JFM. 8-7-1 +Spehn.

\goto{Future Business}

Motion to make rat a... er... joke. Passes 8-4-3 +Spehn.

Seconds too confused.

ALH: I'm mad.

JM hyperventilates.

Motion to commend Neel. Fails by consensus.

Oh yeah. Passes 18-2-2 +Spehn.

Fire at Neel for bringing in backpack. Passes every-none-none +Spehn.

All: Fire, fire!

JPM: Neel, don't eat the books. NK: But they taste good.

Commend Jay for sticking through things. Chickens 8-3-3 +Spehn.

Fails for lack of motion. Chickens 0-0-0 +Spehn.

Get Ingrid a ring. Fails 3-every-none +Spehn.

\goto{Post-Future Business}

JM and ALH: Skinner has no tail at all...

Neel scared away.

\vspace{12pt}

\noindent
Meeting adjourned because Neel left, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Gabriel Valencia, Onseck}

\end{document}