\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 13, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Gabriel Valencia, Onseck, recording.

Meeting adjourned because Eddy arrives.

Meeting restarts.

Minutes read.

M: minutes intuitively obvious. chickens.

M: minutes more interesting than this week's. Passes.

No matrix vote.

\goto{Committee Reports}

M: discover late Eddy [illegible]. Chickens.

Jamie: Hasslecomm has Hasslecomm-ed. Eddy: Yeah. Me and someone else, too.

Pianocomm: new apprentice. Refuses to elaborate.

M: beat identity of apprentice out of Pianocomm. Fails because skinner can't count.

\goto{Old Business}

Innocentcomm: skinner's a twit.

M: commend Innocentcomm for accurate and thorough reporting. Passes.

M: pending motion back on last week's agenda. Passes.

M: go back to last week's meeting to discuss pending motion. Passes.

\goto{Last Meeting}

Eddy: It all makes sense now! This is why it ended before it began!

Motion to confuse Eddy passes by skinnerial decree.

M: consider pending motion. Passes.

M: consider it blue. Passes.

Last week's Miller motion is seconded, so meeting ends.

\goto{Back To This Meeting}

Motion to spoonerize skinner or skinnerize Spooner. Passes.

Unusual algol.

\goto{New Business}

Jamie: It's raining. Fails.

M: condemn Eddy for having large umbrella, causing rain. Something about it fails.

Commend Jay for blue/green hair. Passes by skinnerial decree.

Opportunity for Jay to bing. Passes by skinnerial decree.

\goto{Future Business}

M: condemn future for poor bananas. Fails.

3rd Miller motion. Fails, out of order.

2nd Miller motion. Fails.

1st Miller motion. Fails by skinnerial decree.

0th Miller motion. Punted.

17th Miller motion. Fails due to Jay's perverseness.

M: end cycle by deposing skinner. Passes. Inverse skinner rule: end cycle by reinstating Jay.

"With a banana" appended to blue motion- passes.

M: consider last week's blue motion with a banana. Passes due to singing.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Gabriel Valencia, Onseck}

\end{document}