\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 27, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to fail for lack of a second. Passes 17-2-8 +Spehn.

\goto{Committee Reports}

Mobcomm: more books.

Theftcomm: other half of Theftcomm did something.

Pseudo-moocomm: Mario van Peebles in Solo cross between Michael Jordan and the Terminator.

\goto{Old Business}

Move to put Belated Motion into minutes. Chickens 2-3-everyone else +Spehn.

Onseck: Belated motion to belatedly commend a belated Boriscomm.

Commend onseck for simple addition (1+2=3). Passes 7-1-5 +Spehn.

Motion to put off voting for putting off Belated Motion 1 week (again). Both pass.

Matrix vote is negative.

Condemn Pentiumcomm for being slow. what-what-14 +Spehn.

Motion to get Skinner RAM and a pen to keep it in. 9-0-7 +Spehn. (Prompted by Jay's claim that he didn't have enough RAM to understand the meeting.)

Algol.

\goto{New Business}

(Abbreviated)

Motion to commend MITSFS for reminding Neel to turn in his problem set. Fails 15-8-6 +Spehn.

Andrew Menard commended for remembering to turn in his problem set.

Banana motion dies.

Miller Motion fails.

Motion to put new business in RAM pen. Passes.

Motion to end new business passes by skinnerial decree.

\goto{Future Business}

Onseck commended for using a full sheet of paper on the meeting.

Motion to read next week's minutes. Passes.

Next week's minutes: no meeting. Nuclear holocaust.

Third Miller Motion (first with second). Fails 12-15-0 +Spehn.

Motion to assign type banana to meeting. Passes 22-2-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1724 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
