\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 29, 1996

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Minutes read.

Minutes approved as fire engine red. 5-12-1 +Spehn.

\goto{Committee Reports}

Lamecomm: reports most members are not present.

Moocomm: no LSC movies. Lamecomm concurs.

Apathycomm:

\goto{Old Business}

No old people are here. Passes 8-2-3 +Spehn.

Old motion revivified. Passes 13-8-2 +Spehn.

Mobcomm commended for there being no TSR books on shelves. Passes 6-0-0 +Spehn.

Terry Goodkind commended for finishing Wheel of Time before Robert Jordan did. Passes 8-0-0 +Spehn.

\goto{New Business}

Neel asks that TSRcomm be formed, to encourage TSR to publish more books. Passes 22-0-0 +Spehn.

Neel appended to empty-set as member of TSRcomm. 25-3-3 +Spehn.

Sam's a sucker for a good torture scene. Passes 8-3-3 +Spehn. Particularly with forks. Passes 5-4-3 +Spehn.

\goto{Future Business}

Is none. See below.

\goto{Time Warp to Committee Reports}

Hasslecomm is lame- needs to do work.

MITSFS decides to take branch A.

\vspace{12pt}

\noindent
Universe ends, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}
