\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

"Friday", February 20, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order in room 889, 1700 SST,
Tim Huckelbery, LHE and Pseudo-Skinner, presiding.

(This meeting took place exactly one minute before the end of the last meeting and lasted exactly 59 seconds.)

Many bad motions concerning the minutes were made and ignored, including a very bad pun by Tom Galloway which receives loud moans and groans.

(TLH) Motion to approve minutes as almost as bad as Tom Galloway. Passes that looks good-I don't see anybody at all-3 +Spehn.

(JME) Albanian motion on Tom Galloway. That looks even better-1-one bare foot and an arm +Spehn.

\goto{Committee Reports}

(A^2) Vice Report: I'm back. And I'm not leaving.

(TLH) Skinnercomm: Where is she?

Merryl (People's Albanian Embassy) attempted to translate a motion made by Galloway. Unsuccessfully.

(JME) Etruscan motion on Malcolm Y. Passes by white ballot.

Phonecomm: ring!

(TLH) Motion to condemn A^2 for being coherent answering the phone. 15-half a leg-5 legs and 1 arm +Spehn.

(RCH) Moocomm: The movie schedule is over.

\goto{Old Business}

(Carl Gentilly) This is the first meeting I've attended since 1956, and they're exactly the same.

Old Business Algol.

(JME) Motion to give Tom Galloway a better gag. Passes 13-1-2 +Spehn.

UM, US, UV, UR.

\goto{New Business}

(Robert Sacks) MIT Treasurer's Office will be sending papers soon to establish endowment.

(JME) Motion to commend Robert Sacks for giving us money. Passes by acclamation.

(MJG) Minicult: Woman selling buttons didn't know and is mortified. But it probably won't cost her more than 3 sales, so she's not worried about it.

A Minicult was given in Etruscan. The LHE was able to understand it through the magic powers of the gavel. On hearing it, he changed his mind.

(Albanian) Minicult: In the Boskone book, Mack Reynolds says NESFA has access to a library second only to Forry Ackerman's (i.e. the MITSFS library).

(JME) Motion to generally condemn NESFA. Passes lots and lots-8-3 +Spehn.

Liz points out that 4 randoms aren't voting. They say they were told to vote by Liz, and therefore did not vote.

(JME) Motion to commend them for their good taste and restraint. Passes 43-3-5 +Spehn.

Rabbits have NO tails at all...

\vspace{12pt}

\noindent
Meeting adjourned, 17:00:59 SST.

\vspace{18pt}

\centerline{Warpedly submitted,}
\centerline{Janice Eisen, Onseck}

\end{document}