\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 25, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(TLH) Motion to approve the minutes as timely. Many-3-3 +Spehn.

Some comment in Albanian was made.

Dave suggests we send a letter to NESFA condemning them for referring to us as archives. (TLH) Friendly amendment- letter bomb. Dies for lack of second.

\goto{Committee Reports}

(TLH) LHE Report: JP and TLH went to Finboard dressed strangely (Judy- rosin colored nail polish, both- fake nose and glasses- unfortunately they breathed the mustache). They should have brought lightsabers.

(Dave) Move to commend Skinner and LHE for bravery and valor for going without weapons. Passes unanimously by skinner's selective eyesight.

Skinner discusses her brokeness as boredom increases.

\goto{Old Business}

1st prize in NESFA short story contest- George Phillies.

OBA: usual motion, usual second, usual vote, usual result.

\goto{New Business}

(TG) Boston Lifestyles have a display called I Robotics.

Some derogatory comments. Some Albanian comments occurred.

(PS) Minicult: book- An Albanian Historical Grammar. General surprise ensues.

(PS) Motion to have the Society purchase it in a banana-colored binding. Passes many-1-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1723 SST.

\vspace{18pt}

\centerline{Improvedly submitted,}
\centerline{Merryl Gross, Onseck}

\end{document}