\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 2, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(B*) Move to approve minutes as read quickly. Passes 12-0-3 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: We'll be printing TZ Wednesday night and Thursday morning and collating Thursday afternoon. Come help and get a free copy.

(Andy) Moocomm: Superman and Dr. Strangelove next weekend. Free for frosh.

(TLH) Best new video game is Star Wars, downstairs in game room. It is noted that STrek is also good.

Skinnerly interlude on the phone.

(JME) We got a letter from Gay Haldeman saying she and Joe would come visit us.

(TLH) Moocomm: STrek III will have lots of actors from TJ Hooker. Interstellar cops.

\goto{Old Business}

OBA etc.

\goto{New Business}

(TLH) Minicult: Freshman picnic going on even as we speak.

Some discussion of Paul E. "No-Neck" Gray '54.

(TLH) We may get moved to TCA's office. (With the back rooms.)

Tomorrow noon- Hitchhiker's episodes 1 and 2.

They left all our obnoxious signs up!

The t-shirts are beautiful! Buy one now!

Some banana motions get rejected.

An abortive attempt to sing the Adjournment Song.

(TLH) Motion to gag the singers with a banana. Passes by fiat.

\vspace{12pt}

\noindent
Meeting adjourned, 1701 SST.

\vspace{18pt}

\centerline{Janice Eisen, Pseudo-Onseck}

\end{document}