\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 8, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(Tim) Motion to approve the minutes as incredibly long. Passes many-2-Spehn alone...

Move to reaffirm the Society's faith in the Easter bunny. Passes 5-3-1 +Spehn.

JP: "No rabbits allowed! They multiply enough."

\goto{Committee Reports}

(Tim) LHE Report: We moved the bank and we got an ATM card. It says "MIT Science Fiction Society." (JP) We didn't get an identification picture taken because we didn't have the gavel with us.

(Tim) T-shirtcomm: The design! And it's nice! Color combinations were discussed. Hopefully done by end of term.

(Tim) Moocomm: Rock and Rule- incredibly loud soundtrack, good animation. Soon to come from the people who brought you Superman- Supergirl. And later, Santa Claus, "the world's greatest fantasy figure."

(Dave) VGG Report: We're getting books back! I suppose the new "threats from a distance" are working, hmm?

(Tim) Motion to commend the Society for not threatening the VGG. Passes many (>10)-1-3 +Spehn.

(Dave) We have something planned for those who don't want to return books. We're going to round them all up and make them watch every episode of Lost in Space.

\goto{Old Business}

Usual motion, second.

\goto{New Business}

(Tom Galloway) Minicult: The town of Natick has the largest concentration of Albanians in the US.

(GF) Move to appoint Tom Galloway ambassador to Natick. Passes by white ballot. (Tom) Does this mean I can buy a phrasebook?

(JP) The SCC people who are giving us a couch asked if we cared what color. We said no. He said "How about bright yellow?"

(Many voices) Move to trade SCC a banana for their couch. Passes 7-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Submittingly submitted,}
\centerline{Merryl Gross, Onseck}

\end{document}