\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 10, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(B*) Motion to dismiss minutes as pointless. Passes 7-about 0-4 1/2 +Spehn.

\goto{Committee Reports}

(B*) Moocomm: God help us all- Damnation Alley on NBC tomorrow night.

(TLH) Moocomm: Jedi finally came out. Mass indifference in the Library.

(JME) Vice Report: Not enough vice on Long Island, so I've returned.

(TLH) Boredcomm: Someone broke into the board and stole the small t-shirt.

Various proposals for boobytrapping shirt- all useless.

(B*) Son-of-Famous-Authorcomm: Someone asked him if he wrote those 2 SF books. First time this ever happened.

(Everyone) Zcomm: Zzzzzzzzzzzzzzzzzzzzzzzzzzzzzzzzz...

\goto{Old Business}

(GF) Many old alumni. An alumnus from about 15 years ago stopped by; said minutes were boring and banana motions declasse.

(TLH) Guy Consolmagno saw Mike Timmreck. He has a little Timmreck and another on the way.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) It has been noted that the MITSFS has not done anything really weird for quite some time. It has thus been proposed that a letter be written to Yuri Andropov requesting that, in the event of nuclear war between the US and the USSR, ground zero be moved from MIT to Harvard.

A motion was made and seconded NOT to write such a letter. It was cavalierly defeated by the Skinner, who obviously has no regard for the thoughtful effort and creativity that went into this motion. And is probably a secret Harvard sympathizer. (He does often look a bit crimson.) He received a Bronx cheer from the Vice.

TLH proposes writing a letter to Miterrand asking him to destroy France. Then tells a pointless story. This idea is rejected with great alacrity.

A long silence.

(GF) A banana motion (indecipherable). Chickens in some manner.

More silence.

(JME) Minicult: Battlefield Earth appeared on Time's best-seller list in position 9. God help us all.

Yet more silence.

(B*) Chaircomm: This chair squeaks. TLH: "But it was free."

(B*) Minicult: NASA has joined the fight against James Watt/against offshore oil drilling around Florida- to keep water clear for falling shuttles.

(JME) Miller motion 1. Fails 1-6-2 +Spehn.

(JME) Miller motion 2. Dies for lack of a second. What loathsome indifference.

Adjournment song is sung, to great disgust of Skinner. Nyaah, nyaah, nyaah.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Janice Eisen, Vice and Pseudo-Onseck}

\end{document}