\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 9, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(Larry) Move to approve the minutes as real soon now. Passes.

\goto{Committee Reports}

(JME) Jourcomm: We didn't print it (TZ)- soon as we can.

(Shawn) Jourcomm: We have competition (another TZ).

(JME) Motion to ask them to change their name- we were here first. Sent Best of TZ with letter.

Pseudo-Moocomm: See previous meeting.

(Shawn) Rosfap: Finally processing the fanzine backlog, would appreciate help.

(CJH) Moocomm: Karamazov Brothers.

Minicult: ???

(TLH) Lecturecomm: Asimov and Adams are [illegible].

LHE Report: 1161.61; we lost 853.03 by shelves. Sold 70-90 memberships in past week.

(TLH) Fweekcomm: Everything went about as planned.

(JME) No more big movies- too many problems, unless we get a bigger room.

\goto{Old Business}

(GF) Tom Galloway moved to Philly.

(A^2 and Shawn) Saw Carl Hylin this weekend (thrills!).

(JME) Note: 10 frosh bought t-shirts at Midway- proves frosh will buy anything.

OBA, usual everything, etc.

\goto{New Business}

(PS) Minicult: Talked to Paul Grey- he knows nothing about Rocky Horror.

(JME) Minicult: Rumor about assassination attempt, blah blah blah.

(JME) Hugos awarded.

(MJG) Move to commend SCC for getting us a banana-colored couch. Passes (so there!).

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Andy Su, your slightly deaf Onseck}

\end{document}