\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 4, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

Motion to accept minutes as multi-lingual. Many-1-3 +Spehn.

\goto{Committee Reports}

Jourcomm: Tom Galloway says collation on Sunday at 1 PM. Anyone who comes gets a free issue.

Picniccomm: May 8.

LHE Report: 530 dollars last month.

Sitcomm: Leonard Nimoy as TJ Hooker's former partner. TLH mentioned that TJ Hooker should be renamed TJ Kirk.

Moocomm: Lots of 'em. Reg day- Star Wars. Today- Raiders. LSC got lots of calls; most say "Starwars?!!" Starwars! 5 calls saying "There's an X-rated version?!"

\goto{Old Business}

Old Biz...

\goto{New Business}

Elect new Onseck.

TLH: I nominate Merryl (yeah!) and she'll win.

TG: I nominate the gavel.

TLH: I nominate the second.

Random discussion. TLH: typing and dictation.

Lots-boo, hiss-cowards +Spehn.

Not many-of course-what?! +Spehn.

Are you kidding-very reasonable-were you listening? +Spehn.

Move to make RMS receiver of gavel toss. Many-0-3 +Spehn.

Motion to get skinner a mutant banana (ah ghod I don't know). Fails.

Mack Reynolds just died.

Motion to buy onseck a new banana colored tape recorder. Passes 8-6-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Apprehensively submitted,}
\centerline{Merryl Gross, Onseck}

\end{document}