\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 2, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(Flynn) Motion to approve the minutes and disapprove the Society for going so long between meetings. Fails 4-9 or so-3 +Spehn.

(MJG) Motion to accept the minutes as overdue since they haven't been seen for over 3 weeks. Passes semi-unanimously.

TLH: "It's been a while, folks!" KRJ: "Since you had any?" JME: "Did you forget how to do it?" TLH: "I had a lot of practice by myself."

\goto{Committee Reports}

(Shawn and JME) Jourcomm: TZ ready to be collated. We will begin Saturday, January 7. Be there, please! You'll get a free copy.

B* asks if anyone's working on TZ 36 yet. The Society breaks into hearty laughter.

(Shawn) ROSFAP: It's finished- except for putting them all away.

(TLH) Shelfcomm: There's a new shelf up! Put in an ADB request for 750 dollars (half cost) for 10 new ones.

(MJG) LHE Report: equity level 1190.59, loss of 467.76 last month.

(A^2) Moocomm: Dark Crystal tomorrow night.

(TLH) Zorkcomm: New Zork books are out. Infocom made Time magazine.

\goto{Old Business}

OBA: um, us, uv, usual Broadbent, ur.

\goto{New Business}

(Malcolm) Minicult: Last week there was a lecture entitled "Bird Watching and the Home Computer."

(Flynn) Minicult: Joe Haldeman spoke to NESFA. He talked about his SF classes. He expected to find a bunch of illiterate techies, but he was wrong.

Merryl displays a package we got addressed to "The MIT Science Club"- it contains "Research Abstracts from the Republic of China."

(B*) Minicult: Harrison Ford signed up to do a third Indiana Jones movie.

(B*) At Who-comm, selling for 8 dollars, a story treatment for Star Wars 1, The Fall of the Republic.

(A^2) Minicult: There are 4 SF books on the Times bestseller list.

(JME) Motion to condemn Malcolm for arguing with the lovely, radiant, and banana-like Adina. Passes 2001-42-1984 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned sometime.

\vspace{18pt}

\centerline{Janice Eisen, Vice}

\end{document}