\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 5, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

Pseudo-Onseck read the minutes. The reserve banana was shown once more.

(Flynn) Motion to approve minutes as longer than the meeting. Passes 11 and 3 "oy"s-5-2 +Spehn.

\goto{Committee Reports}

(MJG) LHE Report: Equity level- 2014.64. We lost 195.19 last month.

Bananacomm: The pseudo-Onseck shows off her new banana-shaped pen.

(Lennhoff) Moocomm: The Star Chamber opens today. Now we will know who runs the world.

(A^2) Panthercomm: New Pinkdex is out. Make corrections in Authordex, please.

(TLH) Typewritercomm: We have a new typewriter. It's a cute little manual called Harlan.

A pointless discussion of video games ensues.

(JME) Entropycomm: Carolyn Jones- Morticia of The Addams Family- is dead. Some argument as to whether a description of her character as "ghoulish" in the Glob was deserved.

(JME) Bananacomm: Banana-shaped pens are not easy to write with.

(JME) Greg Ruffa has been asked to return our minutes. We'll see if he does.

(TLH) Shelfcomm: We have a new temporary bookcase to hold the overflow.

\goto{Old Business}

(TLH) Pat Kenny has been paid.

OBA... and so forth.

\goto{New Business}

JME reports that Dan Breslaw is a hero. He rescued her purse from a mugger who grabbed it outside of Toscanini's.

(A^2) Minicult: Heretics of Dune has been sent to the publisher. Everyone groans.

(B*) Minicult: FBI undercover agents pretending to be interested in buying a stolen 70mm print of Return of the Jedi arrested a teenager.

(TLH) Some theatre was skimming off the top of their income from RotJ. Fox took their prints and will never let them have their movies again. Other distributors will probably follow suit.

(JME) Minicult: Phoenix reported title of Krull must have come from the words "cruddy" and "dull."

(JME) Albanian motion on Larry Lennhoff.

Joe Shippman asks "What's an Albanian motion?" Finger Motion on him. He asks "What did I say?" Finger Motion on him. (B*) Motion to note he doesn't learn as fast as Finger.

(RcH) "Gag me with a spatula." Seconded.

All above motions are seconded and pass by decree.

Some discussion of Dr. Who, WGBH, and pledge weeks.

(JME) Motion to award Dan a banana for heroism. Passes white ballot.

\vspace{12pt}

\noindent
Meeting adjourned, 17:45:26 SST.

\vspace{18pt}

\centerline{Bananishly submitted,}
\centerline{Janice Eisen, Pseudo-Onseck}

\end{document}