\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 14, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

At this meeting, the Skinner attempted to affirm her existence by appearing. But I think she's a hologram.

(TLH) Motion to approve minutes as too legible since she could read them without pausing. Fails 1-4-1 +Spehn.

(KRJ) Motion to approve minutes as artificially colored and flavored. Passes many-0-2 +Spehn.

\goto{Committee Reports}

LHE Report: We suckered the Dean's Office and Finboard out of over 1000 dollars. (KRJ: "Most of which we owe to Witter.")

(TLH) Moocomm: Goldfinger tonight. Rollerball Wednesday. James Doohan Tuesday. TLH promises to bring him to the Library to sign things. Much discussion of what he should sign. Such suggestions as blueprints, tech manual, and all of Scotty's lines in the scripts.

\goto{Old Business}

Old Business Algol. Usual garbage gotten through desultorily.

KRJ: "Old Business Algol just isn't as much fun anymore."

\goto{New Business}

(JME) Minicult: The new governor of New Hampshire got his bachelor's, master's, and doctoral degrees from MIT.

(JME) Motion to condemn above for starting the takeover of the world without written permission from the Skinner. Dies for lack of a second. But that was a good motion! I mean, really, after all, what kind of people do we have here? When such an obviously meritorious motion doesn't even get voted on, what hope is there for the world?

The comment was made that what's wrong with the meeting is that there are no non-keyholders present to ask stupid questions. It was then noted that there was a non-keyholder present, but she was sitting with her back to all of us and not participating in the meeting.

(JME) Motion to censure the above-mentioned individual for not participating in the meeting. Passes many-1-2 +Spehn.

Flynn notes that tomorrow is the deadline for advance Boskone memberships; they'll be 19 dollars at the door.

(KRJ) Motion to nail NESFA to the door. 2-2-1 +Spehn. A tie! Skinner breaks it- motion chickens.

A banana motion fails.

A deep silence descends.

(JME) Miller motion 1. Fails 1-some random number-1 +Spehn.

(KRJ) Miller motion 2. Chickens 0-0-0 +Spehn.

Bill* begins singing the adjournment song. This prompts TLH to move that we send a banana to Ken Meltsner in California. Motion passes by acclamation.

\vspace{12pt}

\noindent
We were out of here at 17something SST.

\vspace{18pt}

\centerline{Belatedly submitted,}
\centerline{Janice Eisen, Onseck}

Immediately afterward, B* determined that the Skinner does weigh more than the gavel.

\end{document}