\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 15, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(Tim) Motion to approve the minutes as still too long. Dies for lack of second, HA HA!

(Tim) Motion to approve the minutes as Gross like the Onseck. Passes many-Gross-2 +Spehn.

\goto{Committee Reports}

(Tim) T-shirtcomm: They were ordered today. (Judy) "Yes, they're beautiful." (Tim) "Yes, trust us." (Judy) They're grey with maroon trim.

(Merryl) Picniccomm: This is the invitation!

Suggestions were made and rejected for the name of the committee to move the library. (Tim) "It'll be real nice."

(Tim) Moocomm: An envelope full of stuff! Buttons, pictures, and a piece of cardboard. (Ken) "I'll take the piece of cardboard, that's more useful!" (Shawn) "I get one of those!"

(Merryl) Moocomm: Monty Python tonight.

(Tim) Moocomm: Filming on Dune has started. (Bill*) "Oh boy! How did they get the film crews there?"

\goto{Old Business}

Old Biz etc...

\goto{New Business}

(Shawn) Move that the LHE take us all to Steve's and buy us banana splits! Passes many-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1716 SST.

\vspace{18pt}

\centerline{Barefootedly submitted,}
\centerline{Merryl Gross, Onseck}

\end{document}