\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 1, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(B*) Motion to approve minutes as verse than you could possibly imagine. Passes 12-2-5 +Spehn. JME: "I thought they were Poe-etic myself."

\goto{Committee Reports}

(MJG) LHE Report: I embezzled some money last night.

(JME) Jourcomm/2 sub 2: Real Soon Now. (See last week's report.)

(MJG et. al.) Apathycomm: Yawn.

(TLH) Moocomm: Vote on what films to see on VCR. Winners: Silent Running, Star Wars. We will see them Saturday, 7/16 at 3 PM. Admission will be 25 cents. Room TBA. Bob van der Heide is delegated to make posters announcing. Merryl volunteers to help.

(TLH) Pseudo-Fweekcomm: Freshman letter is done. (See door.) Dave Broadbent volunteers to be Fweekcomm, the fool.

\goto{Old Business}

(JME) Marc Alpert sent us a donation- a box of Omnis. Can I burn them? (TLH) Put them on circulating and let the members burn them.

\goto{New Business}

(A^2) Minicult: John Varley's new book: Millennium. Motion to censure for lack of originality. Passes 7-0-1 +Spehn.

One verse of the adjournment song.

(RCH) Motion to strangle a rabbit with a banana. (B*) Friendly amendment to choke the rabbit. Bananas moosh when you try to strangle with them. (TLH) Friendly amendment to impale the rabbit. Passes unanimously-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:37:52 SST.

\vspace{18pt}

\centerline{Boredly submitted,}
\centerline{Janice Eisen, Vice and Pseudo-Onseck}

\end{document}