\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 13, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(JP) Move to move the minutes to Kenya. Passes many-0-many minus 3 +Spehn.

\goto{Committee Reports}

(A^2) Moocomm: Mad Max tonight.

Here follows many comments on the movie.

(GF) Pseudo-Panthercomm: We received a book with the author's name misspelled on it.

(Merryl) LHE Report: A whole lot of money around.

\goto{Old Business}

Old Business Algol: um, uv, ue, etc.

\goto{New Business}

(JP) Motion to commend TLH for his unusual sex life with t-shirts. (Declared not heard.)

(TLH) New skinnercomm to old skinnercomm- a present (a mini gavel).

(A^2) Move to commend the new Skinner for his sex life with a banana. Dies for lack of second.

(JP) Move to commend the SCC for getting us a banana colored couch. (Tim) Amend- to include the new mail holder which I got in a bright banana color. Passes unanimously.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Andy Su, Onseck}

\end{document}