\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 7, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(B*) Move to "conden" the minutes. Friendly amendment- B-B-B-B. Passes many odd sounds-1-many +Spehn.

\goto{Committee Reports}

(A^2) Lecturecomm: D. Adams was. Not so good.

(JME) Jourcomm: Didn't print last Sunday. If Ken agrees, we'll print this Sunday at 10:00.

(MJG) LHE Report: We have more money. 1509.77 equity, took in 348.16 more than we spent. Yeah!

(KM) Moocomm: Bond is back. The real one. (Loud applause.)

(Random) Oldmoviecomm: Fritz Lang's Metropolis, somewhere in Harvard Square.

(JME) Awardcomm: William Golding awarded Nobel Prize- it was contested. We have some of his books.

(B*) Shakecomm: Move to condemn the Skinner for scheduling the earthquake at 6:20 AM.

(JME) Playcomm: Haldeman's play of Forever War is in Chicago. Good special effects.

(TLH) Plasticcomm: It's in! We can cover books!

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

(MJG for John Dumas) Minicult: From a friend. If Asimov got the Nobel Prize, he said he would fly to Stockholm.

(KM) New SF magazine in Boston 2 times a year- Sunspot. Pretty bad.

(B*) Minicult: Dr. Who convention November 19-20 at Sheraton. Tom Baker'll be there.

(TLH) Minicult: Adams will do a 4th book, So Long and Thanks for All the Fish. Doing a movie in LA, but having problems with the producer.

Minicult: Farmer put Gods of Riverworld out- this is the end (definitely).

(B*) Miller motion. Fails.

(B*) Miller motion. Ignored by the Skinner but not by anybody else.

(TLH) Move to award the Skinner a banana for putting up with this shit. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, sometime.

\vspace{18pt}

\centerline{Andy Su, Onseck}
\centerline{Amended by Janice Eisen}

\end{document}