\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 4, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(Flynn) Motion to approve the minutes as stopping the previous conversation. Passes 8 and a whirlybird-2 and a left arm-a leg +Spehn.

Adina removed her boots. B* moves to commend her and recommend further action. Passes by Skinnerial decree.

There is a brief discussion of Catwoman, Catwoman, and Catwoman.

\goto{Committee Reports}

Moocomm: B* didn't like Dracula. A^2 liked Frank Langella.

(JME) Motion to commend TLH for getting a good hand job- excuse me, job on his hands- at Wellesley. Passes semi-unanimously.

(TLH) Moocomm: Kirstie Alley (Saavik) will not be in STrek III. She asked for too much money. Replacement looks a lot like her.

(A^2) TVcomm: The Day After is having trouble getting advertisers. Nobody wants to be associated with a nuclear war. Discussion of Falwell and Schlafly's demand for equal time- "Nuclear Bombs Are Your Friend."

(B*) Moocomm: Testament (post-holocaust) to open.

Note that the Skinner is being infiltrated by the Commies.

Puff of green smoke.

\goto{New Business}

(KM and JME) Minicult: New video game at 1001 Plays- "Mr. Do's Castle"- you get to drop stone blocks on little unicorns. The directions, translated from the Japanese by the Japanese, ask us to "exterminate" and "subjugate" the unicorns.

(TLH) Minicults: 1) Rocky Horror (the play) maybe over IAP. 2) Haldeman will speak in the spring.

(KM) Motion to commend the Skinner for invading the SAA before they were taken over by the Cubans. Dies amid laughter.

(TLH) Minicult: Family Feud had cast of Lost in Space versus cast of Batman.

Discussion of whether TLH is getting any, how he hurt his hands, Dracula's castle, and other random things.

Lots and lots of dead bananas.

(B*) Miller motion. Fails.

Singing begins. Skinner wimps.

\vspace{12pt}

\noindent
Meeting adjourned, 1721 SST.

\vspace{18pt}

\centerline{Janice Eisen, Vice and Pseudo-Onseck}

\end{document}