\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 14, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

Note that during the reading of the minutes, B* beat MJG about the head unmercifully with an envelope.

(KM) Motion to approve the minutes as. Passes 13-1 +1 of the knights who formerly said "Ni!"-2 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: We did print last Sunday. One of the plates (the Want List) ripped after 123 copies. We'll finish up and have a collating party RSN.

(MJG) Whocomm: Something about changing Dr. Whos. Boring.

(Shawn) Moocomm: See Brainstorm.

(TLH) Lecturecomm: Graham Chapman was. He was good.

(JME) Apathycomm: According to today's Tech, a lecture held in 10-250 about the Boston mayoral race attracted all of 25 people.

(Shawn) ROSFAP: I've got it down to a foot and a half.

B* makes a motion but decides it's stupid and repeals it.

(B*) Whocomm sub 2: Who convention is heavily commercial and very expensive.

(TLH) Wittercomm: One of the most outstanding Witter shipments in recent memory. Such gems as Robots of Dawn, Valentine Pontifex, Gods of Riverworld, Worlds Apart.

KM staples this on- Infocom is publishing a series of choose-your-own-adventure Zork books, written by Steve Meretsky (LSC-type).

TLH staples this on- Douglas Adams is talking about doing a Hitchhiker's video game.

\goto{Old Business}

OBA, usual junk.

\goto{New Business}

(KM) Minicult: Our Skinner's in the New York Times. [Attached picture of ad featuring a muscular man holding a large wrench, captioned "Ben George is The Last of the Knucklemen."]

(Malcolm) Minicult: International Underwater Monopoly Marathon to take place at Boston Aquarium 10/29 and 10/30.

(Malcolm) Minicult: German SF film (Woman in the Moon) which Willy Ley worked on showing at the Harvard Film Archives tonight.

(Shawn) Motion to commend KM for finally sitting in the lap of the MITSFS Mistress. Passes 11-the MITSFS Mistress-5 +telephone +Spehn.

Several banana motions die.

(B*) Motion to award the Skinner a shit for putting up with all this banana. Fails by Inverse Skinner Rule.

Some singing about rabbits and tails infuriates the Skinner, who throws pieces of punchcard around the room.

\vspace{12pt}

\noindent
Meeting fades out, sometime.

\vspace{18pt}

\centerline{Janice Eisen, Pseudo-Onseck}

\end{document}