\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 29, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, Vice and Pseudo-Skinner, presiding.

The Pseudo-pseudo-Onseck (MJG) reads the minutes of the previous meeting. The equity level is applauded once again.

(Flynn) Motion to approve the minutes as not only talking about the weather but also doing something about it. Fails handily 2-many, many, many, many, many-3 legs and a squawk +Spehn.

(JME) Motion to condemn the random sitting opposite me for not voting at all on the previous motion. Passes just about everybody-1 and the random-2 +Spehn. JME: "Let that be a lesson to you."

\goto{Committee Reports}

(JME) Bananacomm: Thanks to a generous donation from Ellen Kranzer, we now have both a reserve and a circulating banana. The circulating copy is in the circulating paperbacks under Banana, Plastic. The reserve banana (it is shown) is on the new bookshelf. Its title is What's Big and Yellow and Puts Out Flames?

(MJG) Rockcomm: I've got a rock. (Applause as it is shown.)

(JME) Moocomm: The video movies did not do too well. KRJ asks when they were and is informed. We had Forbidden Planet instead of Silent Running. We had lots of fun heckling Star Wars.

A^2 points out that we never collected any money. (MJG) LHE Report: We can afford it.

(A^2) Panthercomm: New Pinkdex RSN.

Flynn: "Gosh-wow-boy-oh-boy."

(JME) Jourcomm/2 sub 2: We're still deciding about printing methods. We'll probably use APO's facility. Those of you doing book reviews, turn them in! I need them Very Soon (not Real Soon Now).

\goto{Old Business}

(JME) Blast from the past department- We got a letter and a story from George Phillies, our Permanent Deceased Librarian and President. (He won the last NESFA short story contest.) I haven't read it yet because it's real long. We may have to serialize it.

B* suggests a special George Phillies issue of TZ. Chip Hitchcock notes that the only things we've serialized have been things other magazines wouldn't touch with a 12-foot Hungarian. This degenerates into a brief discussion of Irwin T. Lapeer.

OBA, blah, blah...

\goto{New Business}

(Hitchcock) Minicult: The army has ordered 4802 slot machines for use in recreational facilities in bases around the world. He refers to this as "a new bargaining chip."

John Dumas asks if that was meant to be a pun. Dan Breslaw asks if we can trade some of their chips for some of ours. After a brief pause while everyone figures that out, a roar of laughter ensues. Someone seconds. Passes a few people-a hand and a rock-a few less than those in favor +Spehn.

(B*) Minicult: In an unrelated story, the army has decided not to shoot dogs to give their medics practice in treating bullet wounds.

Suggestions are made that they use Ronald Reagan and James Watt.

(Flynn) Minicult: Judge throws out case to recover UFO bodies; attached.

(JME) Minicult, Human Stupidity Department: Ronald Reagan went on the radio appealing for a liver donation for a baby girl. Hundreds of people called up and offered to donate their livers; they were very surprised when told that yes, they needed them to live, and no, they didn't have another one.

Some discussion of Python's Meaning of Life.

(JME) Motion that we ask the Organ Donors Central Bank to take these people's livers on the grounds that it's evolution in action. Passes overwhelmingly, just about everybody and the rock-nobody at all-2 +Spehn. (KRJ) Friendly amendment that they then give the livers to the army to use for target practice.

(Malcolm) Minicult: Movie business in Japan, which was really the pits, has been revived lately by a new film: E.T.

(JME) Minicult: The cast list for Dune is out. (It's on the fire door.) Jose Ferrer is the Emperor. Some unknown is playing Paul. Sting, who has been billed as starring, is playing Feyd-Rautha. (Group response: who?) KRJ: "Is it true they're going to use men in worm suits?"

(Hitchcock) Minicult: In Denmark, which has both an active organ donation program and narrow, winding roads, there are bumper stickers reading "Go ahead and pass- we can use your kidneys."

DCB announces that the Vice turns legal the next day and the Official Second turned legal this past week.

(A^2) Minicult: There's a new book out, Letters to E.T. One of the first letters is from an old woman who lost her contact lenses crying at E.T. and wants E.T. to buy her some new ones.

Phonecomm: Ring! DCB answers the phone "God-Emperor's Palace." (Hitchcock) Motion to define David as Feyd-Rautha. Passes white ballot.

Ken Johnson makes a bad pun which will not be repeated here. (JME) Motion to censure him for existing. Passes 13-7-2 +Spehn.

It was reported that Krull was opening, but nobody cared. (Dumas) Middlesex News called it "a sure cure for insomnia." (Hitchcock) Gene Shalit liked it. (Chorus) Gene Shalit likes everything!

(JME) Minicult: In the Glob's Names and Faces section, they reported that Brian Aldiss won the "prestigious" John W. Campbell Memorial Award for Helliconia Spring. They referred to it as science fiction, not sci-fi.

There was some applause. However, the Vice continued by pointing out that this award is a basically meaningless award given out by some teachers.

A long, dull discussion of reviews of Krull followed.

An attempt to sing the Adjournment Song is quelled sharply by the pseudo-Skinner.

(JME) Albanian motion on Chip Hitchcock. Passes by acclamation.

(RcH) Motion to commend Ellen Kranzer for bringing us our nice new bananas. Passes looks like everyone to me-I don't see anyone-nobody at all +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1741 SST.

\vspace{18pt}

\centerline{Pseudonymously submitted,}
\centerline{Paul French (aka Janice Eisen), Vice, Pseudo-Onseck, Pseudo-Skinner, etc., etc.}

\end{document}