\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 11, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(Chip) Move to disapprove the minutes as leopard-spotted. Fails 2-many-3 +Spehn.

(Shawn) Move to approve the minutes as leftover. Chickens 5-6-7 +Spehn.

(Pete) Move to approve the minutes as high-tech. Passes many-6-3 +Spehn.

(All) Yea!!!

\goto{Committee Reports}

(Shawn) Jourcomm: Oh boy. TZ 35- I need stuff! TZ 34- It's on the table waiting to be mailed.

(Pete) Moocomm: Tron tonight. (TLH) "Greetings, fellow programmers."

\goto{Old Business}

Old Biz Algol. Usual motion, usual second, usual vote, usual result.

\goto{New Business}

(Chip) Minicult: The top system hacker where I work made the computer allergic to him! He managed to do something which crunched the top level files, including the user identities. When he asked "Who am I?" it responded "Intruder alert!"

Skinner mentions that since she is not a 6-3, she cannot appreciate all the fine subtleties of this. (TLH) "Oh well." (Pete Smoot) "You lose." (JP) "Not me."

(JP) Move to censor everyone at the meeting for being terribly boring except for Andrew when I was unbuttoning his shirt. Passes (it doesn't matter because skinner declared all the votes in favor).

Many sounds of protest were made, including kvetches about the lack of gavel block in front of the skinner and an observation that the skinner unbuttoned Andrew's shirt before the meeting.

(TLH) Move to censure Jourcomm for printing TZ in the color of a banana. Passes many-3-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Delayedly submitted,}
\centerline{Merryl Gross, Onseck}

\end{document}