\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 6, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order in the Spofford Room, 1700 SST,
Judy Passman, President and Skinner, presiding.

(Shawn) Motion to approve the minutes as cute and bouncy, just like the Skinner.

(JP) I am not cute!

Motion to approve the minutes as cute and Merryl-sy. Groans follow along with Albanian motion (JME). Passes many-4-1 +Spehn.

Friendly amendment- "like Judy." Passes about 12-5-2 +Spehn.

\goto{Committee Reports}

(TLH) T-shirtcomm: They're in! They look magnificent! (Cries of "Take it off!", "Yea!", "You too, Merryl.", and other disgusting but amusing comments.) 5 dollars each.

(JME) Motion to condemn Tim for refusing to strip. Passes 3-7-2 +Spehn.

Motion to commend Tim for voting with a very nice leg as well. JP: "This one's going to pass so you might as well vote on it." Chickens 1-2-4 +Spehn. (Note: all 4 votes were from Tim.)

Moocomm: A Clockwork Orange tomorrow. (Merryl) Tomatoes on Sunday. (TLH) Airplane tonight.

Moocomm: For an even worse spoiler- the comic book version is out. (Must be Albanian.)

(JP) The picnic is Sunday. Meet at the office at 10:30, especially if you have a car. Pray for good weather.

(JME) Motion to pray to the great god Spofford for good weather. JP: "It's gonna pass, let's not vote on it."

(JP) Technique is out; they actually put in our officer list this year and put in the honorary dead plant, Andy... head of the Student Art Association.

(JME) Motion to condemn Technique for calling A^2 the vice president instead of vice. Passes unanimously.

Move to ask Technique to go through all copies with black magic markers. Passes many-0-3 +Spehn.

(JME and many others) "Pay attention, Andrew!" etc. Motions to condemn, commend, etc., all of which were totally ignored, especially by Andy.

Meaningless matrix vote- result: "Who cares?" (JP)

V was about as bad as you'd expect. Followed by more meaningless comments on the show. (Tim) Sequel time! (JME) They intend to make V into a series because of the good ratings- once again showing the great taste of the American public.

Still more comments...

\goto{Old Business}

OBAlgol, usual everything.

(JP) Okay, let's give Tom a memorial gag. (Yea!) Passes unanimously.

Much confusing and meaningless noise for a while...

(JME) Move to commend JP for her sex life with fishnet. Passes (inverse skinner rule).

\goto{New Business}

Elections (oh boy!):

President:

Nominations (among others): Guy Consolmagno, Perry Rhodan, JP, Pete Smoot, L. Court Skinner, JP's fishnet stockings, Spofford, Course VI faculty, etc. (including Tim)

Winner (after 3 rounds and a lot of hoohah- many suggestions concerning JP's costume): Tim. Appointed Skinner: ditto.

Vice:

Nominations: Marquis de Sade, Bikini (Macrame, blue), Belt (Cheryl's, studded leather), Pete Smoot, Chuckles the Clown, Janice, MITSFS Mistress, etc.

Winner (after 2 rounds and still more hoohah plus S&M suggestions): Janice.

LHE:

Nominations: Merryl, tuition, Pete Smoot, Jimmy Carter, L. Ron Hubbard, etc.

Winner (after 2 rounds): Merryl.

Onseck:

Nominations: Andy (me), Genghis Khan and friends, electronic Onseck, Pete Smoot, Oliver Smoot, Gertrude Asimov, etc.

Winner (after 2 rounds): me- Andrew Su.

Official Second: Pete Smoot.

Motion to acquire for the Spofford room a dead banana plant.

Adjournment song sung.

\vspace{12pt}

\noindent
Meeting adjourned, 1825 SST.

\vspace{18pt}

\centerline{Very lengthily submitted, but what do you expect with an hour and a half long meeting and if you don't like it you know what you can do with it,}
\centerline{Andrew Su, your new Onseck}

\end{document}