\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 29, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(Shawn) Motion to approve the minutes as hot pink like Judy's shirts. Passes 7-4-3 +Spehn.

\goto{Committee Reports}

(Tim) T-shirtcomm: T-shirts are in! "They're very nice- trust us." Unfortunately, all they got are the [illegible] baseball shirts through a screwup in the order. But they're okay- if you go for that sort of thing.

(Tim) Moocomm: Yet another discussion of how shooting for Dune is going and who's playing who. (Sigh.)

(Bill*) Moocomm: V, this Sunday and Monday.

(Tim) Moocomm/Jerkcomm: Tim gave away even more of the upcoming movie, with help from Bill Starr, but I won't tell you any of it, so if you did not attend the meeting, you can be surprised.

(Shawn) Moocomm: WGBH is serializing A Canticle for Lebowitz on the radio.

(Flynn) Pseudo-Moocomm: A bunch of Tron fans have started a fanzine called The Further Adventures of Flynn. (Laughter followed this comment, followed by rude remarks about Tron fans.)

(Tim) "And in a similar vein- LHEcomm! I just got a job playing video games!"

Envy runs rampant. Video games are discussed.

\goto{Old Business}

All the usual stuff!

\goto{New Business}

Judy announced that the winners of next week's election will be... (drumroll, please)

Skinner: Tim Huckelbery

Vice: Janice Eisen

Lord High Embezzler: Merryl Gross (yeah!)

Onseck: Andrew Su

and as the Official Second: Peter Smoot!

Pete: "If anyone votes for me, I'll strangle them!"

(Bill*) There seemed to be a Dalek on the last Hill Street Blues. All you Dr. Who fans know what that is, and all the rest of you don't. There also seemed to be some similarities to Harlan Ellison's "Brillo." We're sure he or his lawyer saw them.

(Tim and Shawn) In a tangled mess a motion was made to get bananas, go outside, and consume them, amended to "and to inflict Bill* on the weatherman." Anyway, it passes many-2-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1718 SST.

\vspace{18pt}

\centerline{My last minutes as Permanent Temporary Onseck!}
\centerline{Merryl Gross}

\end{document}