\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 28, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(JME) Motion to approve the minutes as lots more interesting than the meeting. Passes 17-3-3 +3 clucks +Spehn.

\goto{Committee Reports}

(TLH) Moocomm: Fantastic weekend! Poltergeist, Bond, Dracula ('79 version).

The last receives pants from some of the female members.

(Flynn) Pseudo-Moocomm: Science advisor for Brainstorm- Dirk Pearson.

(MJG) Playcomm: Joe Haldeman's play opened in Chicago. He liked it. Mixed reviews but lots of space.

(TLH) Incrediblyweirdcomm: Shroud of Turin lecture attracted over 500 people.

(JME) Bonzocomm: President Reagan gave a wonderful fantasy speech last night.

(B*) Whocomm: WGBH will not be showing the 20th anniversary Dr. Who special.

(TLH) Timecomm: We fall back Sunday morning.

(JME) Playcomm: Classic fantasy The Tempest by Shakespeare Ensemble this weekend.

In a cloud of orange smoke, we find ourselves in...

\goto{New Business}

(Broadbent) Minicult: My yearbook picture was taken at the keyholder desk.

(Flynn) Minicult: Pia Zadora will star in a low-budget SF film called Attack of the Rock n' Roll Aliens.

Skinner displays a bat his mother sent him.

(JME) Motion to reaffirm the Society's faith in the Great Pumpkin. Passes unanimously.

(Random) Minicult: Exeter Street getting original floor-show cast for Rocky Horror tonight.

(JME) Motion to commend the US for invading a banana republic. Passes by acclamation.

\vspace{12pt}

\noindent
Meeting adjourned, 17:24:32 SST.

\vspace{18pt}

\centerline{Janice Eisen, Vice and Pseudo-Onseck}

\end{document}