\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 21, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(A^2) Motion to approve the minutes as having no tails or end. Passes 7-eh-3 +a copy of the Tech +Spehn.

\goto{Committee Reports}

(JME) Apathycomm (noting dearth of attendees): There's obviously growing apathy among the membership. A^2: "Who cares?"

(TLH) Moocomm: The Right Stuff is opening.

(JME) Theatercomm: Tomfoolery opened.

(B*) Moocomm: Dead Zone opening.

(JME) Whooshcomm: John Glenn's campaign commercial has a real good whoosh in it. It's a pretty good commercial. The theme is "Believe in the future again."

The Skinner tells a tiresome story. B* tells an even more tiresome story.

\goto{Old Business}

(A^2) Someone named Melinda Lutz, who said that her father was the first secretary of the Society, bought a membership.

(JME) Today is the 34th anniversary of the founding of the Society. Rah-rah-rah.

(JME) Michael Taviss has moved from Alberta to Memphis, Tennessee.

(Skinner) BAMF!

\goto{New Business}

Merryl enters to a round of applause.

Minicult: Man with a Wrench still playing in New York.

(JME) Motion to commend the Skinner for wearing his fishnet stockings. Passes by acclamation.

Several bad puns flew about the room, collided in midair, and exploded. Thousands homeless.

(TLH) No new bitches.

(B*) Motion to condemn Ron and Eunice for disrobing in public and disrupting the meeting. Chickens 4-5-6 +a pair of lace bikini underwear +Spehn.

(TLH) Motion to award the Society a banana for 34 years of continuous (but discreet) silliness. Passes by decree.

\vspace{12pt}

\noindent
Meeting adjourned, 17:33:50 SST.

\vspace{18pt}

\centerline{Janice Eisen, Pseudo-Onseck and Vice}

\end{document}