\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 17, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Such a large group of random people gathered in the Library that Tim Huckelbery, President and Skinner found it advisable to exercise a measure of control by calling a MITSFS meeting to order at 1700 SST.

The pseudo-Onseck read the minutes of the previous meeting, interrupted by grunts, giggles, and moans of dismay. The phone rang during the reading of the minutes, for Adina. A motion of censure is ignored.

(RCH) Motion to approve the minutes as crimson. (A^2) Friendly amendment- like Tim. TLH: "Any other motions?" Unanimous-less than unanimous-even less +Spehn, fails by Inverse Skinner Rule.

(B*) Motion to invert the Skinner. A^2: "No, that's NOT to invert the Skinner." B*: "That's an inverse Skinner inversion." Motion passes.

(JME) Move to censure the Skinner as out of order for counting chickens before no's. (B*) Move to censure the Skinner for counting chickens before they were hatched. (TLH, loudly) I AM order! (KRJ) Second.

Phone rings again, this time for Ken Johnson. A motion of censure is ignored.

TLH: "One by one, all the MITSFS members are being called to the phone and replaced by pods."

\goto{Committee Reports}

(JME) Bananacomm: Presented a banana to the Skinner in hopes that his foot would soon be better and as a peace offering.

Everyone went "Aww!" The Skinner sniffed disdainfully at the banana and put it on the gavel block. This cavalier treatment of her thoughtful gift so annoyed the Vice that she peeled the banana, shoved it in the Skinner's mouth, and draped the peel over his head. He looked lovely. There was much applause.

(RCH) Motion to censure the Skinner for eating in the Library. JME rallied everyone to defeat the motion so that it would pass by the inverse Skinner rule. However, the Skinner refused to call on the inverse Skinner rule, so the motion failed overwhelmingly. The Vice then presented the Skinner with a raspberry. A^2: "I didn't think that was at the discretion of the Skinner." TLH: "It's my rule, isn't it?"

(JME) Jourcomm/2 sub 2: Real Soon Now. We're accepting contributions now, especially art, especially art, especially art.

(MJG) Poetrycomm: I want my poetry back! JME: "That's Nudzhcomm." Someone seconded Merryl's cry. Vice: "You can't second a committee report!"

(JME) Bananacomm: The World Almanac has only one entry concerning bananas in the whole book- a listing of their nutritional content. KRJ: "With or without the peel?" JME: "It didn't say."

TLH: "LHE Report- how much money do we have?" (MJG) LHE Report: Lots.

(JME) Vice Report: I would like to commend LSC for their promotion of vice by showing a movie Saturday night (Grease) of which the moral is: you want to get a guy, wear leather.

Motion passes lots-2-5 +Spehn.

(Malcolm Y) Motion to commend the Vice for promoting LSC. Dies for lack of a second.

(JME) Motion to give that motion a decent burial. (KRJ) Friendly amendment- to bury Malcolm with it. Passes many-2-3 and a squawk +Spehn.

(DCB) Greasecomm: I'm up to something.

(TLH) Shelfcomm: We're going to get some new shelves. Hopefully. B*: "Are they going to be attached to bookcases?"

(JME) Vicecomm: I'd like to know who donated the whip. KRJ: "Now when she bats her lashes at us, she's got three of them."

TLH asks for volunteers to Advicecomm to give the Vice suggestions on what to do with the whip. JME: "I've received many suggestions on various topics since taking office and after careful consideration have decided to ignore all of them."

(JME) Pseudo-Onseck: We received a letter nobody could figure out from someone named Mark Thompson. He deserves commendation for enclosing a self-addressed stamped envelope, a rare act of consideration in these troubled times.

Motion to commend is seconded. Passes by acclamation.

(B*) Reallifecomm: Sally Ride takes off in Shuttle tomorrow morning.

(MJG) Motion to commend Sally Ride for the way she deals with People magazine. Some discussion of the chauvinist questions she gets asked. (RCH) Friendly amendment to commend for the way she deals with idiots in the press in general. Passes unanimously.

Three motions concerning Albania are thrown onto the floor. This results in an Albanian matrix vote, an Albanian matrix being one containing one number. It is defined to chicken.

(JME) Vice: Motion to commend Lucasfilm for their promotion of vice by featuring a picture of Leia in her Gorean slave girl outfit in their ads for Jedi. Motion is seconded. Passes by three pants.

KRJ hits his head. JME seconds the motion. Passes 7-4-5 +Spehn.

(TLH) Skinnercomm: (Skinner is hissed.) Good ol' Mike Taviss, friend of the Library and all around good guy, donated the outstanding sum of 5 dollars to the Alumni Fund, which now contains 1505.00. He directs the pseudo-Onseck to write an appropriate letter thanking him for his generosity.

(JME) Motion to censure Michael Taviss. Rejected as real business.

(TLH) Also, we are now in the American Library Directory. Ken and George are our Acquisitions Librarians. Keyholders are listed as Librarians.

\goto{Old Business}

(JME) Dan Ebrom is still around. He bought a t-shirt. KRJ: "There's one born every minute..."

(TLH) We have a new t-shirt design. Slightly new. It will be easier to print and hopefully will last longer.

(JME) I have photographs from the picnic. Negatives are not for sale, but copies are available for cost.

(JME) Motion to censure the LHE. Fails 6-12-1 +Spehn.

KRJ: "Lewis made a pass at Wisowaty and was repulsed. Move to censure the Librarian. Talk about old business algol..."

OBA, all the usual.

\goto{New Business}

(JME) Minicult: In the World Almanac for this year, several old friends of MITSFS are listed under Notable American Fiction Writers, including Isaac Asimov, Ray Bradbury, Michael Crichton, Robert Heinlein, Stephen King, Ursula Le Guin, and Kurt Vonnegut. Harlan Ellison is notably absent from the list, but Dr. Seuss is on it. (Applause.) And out of that list, Asimov and Vonnegut are also in Who's Who.

Dumas: "May I suggest that you look under Notable American Whiners for Ellison?" TLH suggests the Playgirl directory of American bachelors. KRJ: "You forgot to look under Notable American Short People." (JME) Motion to censure World Almanac for not including Irwin T. Lapeer. Unanimously ignored.

(B*) Minicult: This week's TV Guide has an article about shows with cult followings, including Twilight Zone and The Prisoner. Also Star Trek. But not Dr. Who- the article is about long-canceled shows.

(JME) Let it be noted that sometime in the early seventies somebody lamented in TZ that within a couple of years Twilight Zone reruns would probably no longer be seen on any TV stations. (Malcolm Y) Motion to award TZ the Memorial Crystal Ball for Perfect Prediction. Passes many-2-4 +Spehn.

(B*) Mediacult: True to their word, channel 56 will be showing Star Trek weeknights at 6.

(TLH) Instead of showing 2 ST episodes on Saturdays, they now show one ST episode and 2 cartoons. (JME) Motion to write them a letter requesting that they supply barf bags to accompany the cartoons. (TLH) Friendly amendment to write it in crayon. (Meeny) Friendly amendment to write it on paper torn out of a spiral notebook. Passes many, many-0-about 6 +Spehn. The pseudo-Onseck was so directed.

(TLH) Minicult: John Cleese is now doing radio ads for candy.

Several bad John Cleese imitations are heard.

An attempt is made to begin the Adjournment Song. It is quelled after one chorus.

(Malcolm Y) Motion to provide the Vice with a recipe for whipped bananas. Fails 3-many-2 and a squawk +Spehn.

Another chorus of the Adjournment Song is sung.

(JME) Motion to censure KRJ for existing. (A^2) Friendly amendment- and to present him with the banana peel.

(Malcolm Y) Minicult: Some historian commented the fact that in the latter stages of WWII, a newspaper headline read "Allies Push Bottles Up Germans."

(JME) Albanian motion. Passes white ballot.

As the Vice attempts to explain her earlier motion, 2 more choruses of the Adjournment Song are sung. TLH conducted the second. TLH: "If John Williams was here, he wouldn't have this problem."

JME: "There is a motion lying on the floor, sobbing pitifully." Ken Johnson and John Dumas get up and stamp on it. KRJ: "We put it out of its misery."

Banana motion passes 6-I didn't catch how many were opposed-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:49:30 SST.

\vspace{18pt}

\centerline{Lengthily submitted,}
\centerline{Janice Eisen, Vice and Pseudo-Onseck (with a little help from Tron)}

\end{document}