\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 4, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(TLH) Move to approve the minutes as pre-electronic. Passes 9-2-4 +Spehn.

\goto{Committee Reports}

(Bill*) Oh lordy.

(TLH) Moocomm: Strek II (Wrath of Khan) in fantastic Dolby-Scope in Kresge. (Comments- Annoyance of Khan, Wrath of Ralph.)

(TLH) Jourcomm: We's working.

[Report redacted by black marker.]

(Bob) Move we solicit money from Jerry Niven and Larry Pournelle (what he said) because they make so much. Dies for lack of second.

(TLH) "Give us money! Give us money!"

(Bob) Pseudo-Jourcomm: Some stupid sucker was sitting at the Tuition Rally reading a TZ.

\goto{Old Business}

Albanian motion on Tom Galloway. Ideas for a Tom Galloway memorial motion were argued and laughed at.

Usual stuffies.

\goto{New Business}

(Bill*) "They're reprinting my daddy's book again."

Sighs and silence.

(Bill*) Saw Wizards and Warriors. Not as bad as you might expect.

A silence descends. The silence was attributed to stuck tape, preventing us from speaking.

"Rabbits have no tails at all..."

Peter Smoot comes in and Bill reads his button.

"Rabbits have no tails at all..."

(TLH) Motion to inflict the tape recorder with a banana. Fails observedly 3-many-3 +Spehn.

"Rabbits have no tails at all..."

"Rabbits have no tails at all..."

"Rabbits have no tails at all..."

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Comprehensively submitted,}
\centerline{Merryl Gross, Onseck}

\end{document}