\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 7, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, LHE and Pseudo-Skinner, presiding.

(KRJ) Motion to accept minutes as black and fishnet. Passes 7-2-2 legs +Spehn.

\goto{Committee Reports}

TG attempts to deliver a GAHcomm report.

(KRJ) Albanian motion on Tom Galloway. Passes many-none-none +Spehn.

(TLH) GAHcomm: It's back.

(KRJ) Moocomm: Dark Crystal opened.

(TLH) Moocomm: Slaughterhouse Five on Wednesday. Boy and His Dog a few days ago.

(TG) Gabble, gabble, gabble.

(KRJ) Othercomm: No report.

\goto{Old Business}

OBA.

After much incredibly pointless discussion, we got through the usual junk.

\goto{New Business}

(KRJ) Minicult: February F&SF has letters in letter column from 2 MITSFS members or ex-members: Michael Taviss and Kathy Romer. Neither mentioned MITSFS.

(JME) Motion to censure both of the above for not mentioning MITSFS. Passes many-1-3 +Spehn.

A motion of some sort was seconded, but we don't know what it is since it was made in Albanian. Passes 6 or 7-1-1 +Spehn.

RVH is appointed Stranglecomm by TLH. He requested the position so he could call Marc Alpert in the middle of the night and ask what Stranglecomm is. KRJ explained that his duties are to call at 3 AM, identify himself as Mark Swanson, and ask when TZ is coming out.

(TLH) Motion to award a phantom banana to the phantom Skinner. Passes 7-2-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:13:28 SST.

\vspace{18pt}

\centerline{Tiredly submitted,}
\centerline{Janice Eisen, Onseck}

\end{document}