\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 1, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(Bob) Move to approve the minutes as red. Fails 4-7-4 +Spehn.

(Tim) Move to approve the minutes as Pink in honor of tonight's movie (The Wall). Passes many-1-2 +Spehn. "The clods have it!" says JP.

\goto{Committee Reports}

(Shawn) Jourcomm: "I mailed it and ghod were they heavy!"

(JP, with a little help from Pete and John Dumas) Move to commend Jourcomm for- oh, I don't know... (John) Superhuman strength... (Pete) Above and beyond the call of duty! Passes many-3-1 +Spehn.

Jourcomm (continued): "TZ 35- write something goddammit!"

JP: "We want to get it out before the end of the semester."

The Onseck would like to note at this point that we've all heard that song before.

(Tim) LHE Report: We're switching banks!

Big deal, I say. That's real business and I won't put the rest in the minutes! Boy, you can tell I was in a wonderful mood when I wrote this!

(Tim) Foreigncorrespondencecomm: We got letters from Cheryl and Janice. Janice is writing something real similar to a story in TZ 34. Cheryl will be in the area sometime soon because of funky passport problems.

(Pete) Moocomm: The Wall tonight. (But you knew that!) 2001 tomorrow and Sunday. Mean and nasty MGM took back all the good 4 track magnetic prints and left us a crummy old one. We could have gotten a spiffy new one a month from now...

An undecipherable comment was made, something about a gavel falling and waking the dead. A few woken Dead jokes were made and the Moocomms went on, but you don't want to hear about them!

\goto{Old Business}

Usual etc.

Small fanfare was da-da'd by Tim and badly tromped upon by everyone.

\goto{New Business}

John Dumas brought a copy of the official paper of the American Library Association and we all scoffed at its lead story about SF. General impression- they have a very good background in 17th century SF, and that's it.

A bunch of motions were ignored here.

Minicult: from Instant Message 333- "4/1/83- Annual Chip Hitchcock Roast, 8 PM to whenever, to again attempt to flambe Chip. Dexion and electrical cord optional. There will be a special filmed presentation of Chip's most famous flames, including the outrageous Hynes Auditorium outtakes and the hilarious Typotech bloopers. Rated X. Rendezvous point will be decided at the Wednesday IM Collation on March 30."

(Tim) King Kong is returning to the Empire State Building!

A wave of apathy follows this comment. Bill* then explains the technology of this feat.

(JP) "No! No metallurgy!" (The original comment is mercifully lost.)

Minicult: Bloom County strip, attached.

Motion to commend Bloom County for realizing the Satanic significance of a banana. Passes by acclamation.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Be glad it's here,}
\centerline{Merryl Gross, Onseck}

\end{document}