\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 8, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(B*) Move to approve the minutes as mercifully brief. Passes 10-0-6 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm/2 sub 2: We have a beautiful cover. (It is displayed.) Motion to commend artist, Laramie Sasseville, for delivering it within 3 days of promise. Passes unanimously.

(MJG) LHE Report: We lost 133.29 last month. It is noted that knowing how much we lost is better than making money and not knowing how much. Equity level: 2209.83. (Applause.)

(TLH) Moocomm:  We'll show the films here. We can't charge admission because it's illegal. So just ask your friends for a donation.

(JME) Moocomm: Phantom of the Paradise Saturday night. Hitchcock double feature tonight.

(B*) Sitcomm: PBS is beginning Hitchhiker's Guide on TV again, Sunday nights at 10:30.

This somehow leads to a discussion of the new Sneak Previews guys versus the old ones. (B*) Roger Ebert used to be a fan; we even have a prozine with a story by him.

(TLH) Moocomm: Armed robber kidnapped a print of Jedi in Kansas.

Long discussion of video piracy.

\goto{Old Business}

Old Business Algol: um, us, uv, ur...

\goto{New Business}

TLH is moving some bookshelves Sunday. People should come help him.

JME announces MJG's birthday was Tuesday. She turned 20. Applause.

DCB announces that the Vice will be legal later this month. (Many comments.) Also the Official Second. And he is starting a Plot-A-Birthday-Party business.

(JME) Motion to condemn the weather of last weekend. (A^2) Friendly amendment to condemn the Skinner for liking that weather. (Flynn) Friendly amendment to condemn the Skinner for not doing anything about that weather. JME rejects friendly amendments because of fear of Inverse Skinner Rule (as well she should...). Passes 10-0-3 +Spehn.

(A^2) Motion to condemn the Skinner for not doing anything about last weekend's weather. Passes 8-0-1 +Spehn.

MJG begins adjournment song. JME shrieks in dismay.

(A^2) Motion to present Merryl with a banana as a birthday present. Passes white ballot. (Does that make it a white banana? No.)

\vspace{12pt}

\noindent
Meeting adjourned, 1739 SST.

\vspace{18pt}

\centerline{Blankly submitted,}
\centerline{Janice Eisen, Vice and Pseudo-Onseck}

\end{document}