\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 9, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

A random motion was made to approve the minutes. Passes many-not quite as many-less +Spehn.

\goto{Committee Reports}

(TLH) Skinner Report: We sleazed 500 dollars for new shelves from the ADB.

A silence falls.

(TLH) Moocomm: Road Warrior tomorrow. Seatbelts, Dolby, armor.

Um, er...

\goto{Old Business}

And a wave of apathy rushes us into...

\goto{New Business}

(B*) A coat of arms- "apathy rampant on a field of boredom."

The Skinner defines the time warp.

(B*) Christine opens today.

(A^2) Dune has finished shooting and they're ready for the special effects.

(JD) "And so it goes." (B*) "It's a long way to Tipperary."

Minicult: Milwaukee doll-airdrop plan plane-ly just a hoax. See attached.

(B*) Move to commend the Society for not mentioning the word "banana" in a motion. Passes by CLANG!

\vspace{12pt}

\noindent
Meeting adjourned.

\vspace{18pt}

\centerline{Incoherently submitted,}
\centerline{Merryl Gross, Pseudo-Onseck}

\end{document}