\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 30, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(JME) Note: TLH delayed the meeting to read Bloom County. (He laughed.)

(GF) Move to accept minutes as incomprehensible except for the Onseck. Passes 13-0-3 +Spehn.

\goto{Committee Reports}

(JME) Moocomm: Brainstorm, a movie coming out, pointed out a discrepancy in science- hitting one person's knee and another's leg goes up.

(JME) Jourcomm: Will be printed on Sunday.

(PS) Lasercomm: Constellation II was. (Note by TLH- pretty good.)

(JME) Ourgreatestenemycomm: saga of SAA continues. (Note: strongest conclusion- if the Dean's office interferes so much with the ASA, maybe the ASA shouldn't exist.)

(TLH) Cartooncomm: Bill Spitzak starts another satire- "Satire of the Jeti."

(JME) Badcartooncomm: Carol Yao is back.

(JME) Move to censure Carol Yao for giving Tech coeds a bad name. Passes (Skinner too lazy to count the vote).

(TLH) Lecturecomm: Douglas Adams next week.

(TLH) Shelfcomm: They're in. They won't be. They stink.

(JME) Fairytalecomm: Newly discovered Grimm's fairy tale found- will be illustrated by Maurice Sendak.

\goto{Old Business}

(JME) Thanks to JS we now have transcriptions and tapes of old meetings.

OBA, usual everything.

\goto{New Business}

(GF) Minicult: Among the new stories in Locus, Zelazny sold 3 more Amber novels for 6 figures. Rumor that Philip K. Dick isn't dead. Herbert sold Dune 6 for 7 figures. Tolkien (dead) has 2 more books coming out.

(JME) Report through Haldeman on Last Dangerous Visions.

(TLH) Note: LSC lecture ballots out soon. Haldeman and Pournelle are on it.

(JME) Phonecomm: Ring!

(GF) Minicult: Twilight Zone- someone referred to Jabba the Hutt as Boba Fett.

(JME) Move to condemn Dave for wearing a tie. Passes unanimously.

(JME) Motion to have the LSC ballots put on banana colored paper. Passes, so there.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Andy Su, Onseck}

\end{document}