\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 11, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

Motion to approve the minutes as irrelevant. Chickens 4-4-5 +Spehn.

Motion to approve the minutes as nouveau-Onseck is killed by Skinner who defines "chickens" as "passing" for the previous motion.

\goto{Committee Reports}

Jourcomm: Covers are in. There'll be a collation Sunday at 1. Still a free copy for anyone who appears.

Harlancomm: He was here. He was his usual obnoxious self. The best film he's seen recently was ET.

Moocomm: Blade Runner tonight, very awesome sound. Be there or be deaf.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

Minicult: Tech Review and Class Notes asked whatever happened to Cheryl Wheeler.

Minicult: First president and Skinner may be back, as his daughter is looking for a college.

Move to commend the Union Savings Banks for having more than 3 bananas in their ads. 4-5-3 +Spehn.

On one of Dr. Demento's albums is a song called My Wife Left Home With a Banana. Motion to buy it for the Society. Dies for lack of second.

Motion to commend Society for its good taste and restraint. Passes many-4-3 +Spehn.

Motion to award the Society a banana for its good taste. Passes many-2-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Confusedly submitted,}
\centerline{Merryl Gross, Onseck (with a very small amount of help from the Lord High Embezzler)}

Attached: business card for Court Skinner.

\end{document}