\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 18, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order in room 889 of Boston Park Plaza, 1700 SST (6:30 PM mundane standard time),
Tim Huckelbery, LHE and Pseudo-Skinner, presiding.

Guest starring: the absent Onseck!

Before the meeting, a space-time warp was established defining the room equal to the Library equal to the Spofford room.

Many people came in while the minutes were being read. Broadbent was obnoxiously greasy, getting beeped and making phone calls.

(TG) Motion to approve minutes as Rocky Horror (because of Time Warp). Withdrawn.

Many motions concerning minutes made and killed by general disgust.

(MJG) Motion to approve minutes as indescribable. Passes 15-6-6 and a knee +Spehn.

\goto{Committee Reports}

(TG) Pseudo-Moocomm: See attached article.

(TG) Sitcomm: Showing ST:TMP on TV with 15 minutes additional footage. Massive groans are heard.

(TLH) Pseudo-Jourcomm: TZ is out, price 40 cents. Buy it at a hotel room near you.

(TLH) LHE Report: Asked Finboard for 885 big ones.

(JME) Onseck Report: I have returned (temporarily). I'll definitely return for elections and picnic, and possibly before then.

(A^2) Vice Report: I exist. I'm alive. And I'm leaving.

Liz asks if A^2 is leaving on NESFA business. Finger motion on Liz.

(RCH) Motion to condemn Liz for suggesting A^2 might be connected with NESFA. (TLH) FA- to condemn Liz for even mentioning that hated word. Passes lots and lots-not very many-even less +Spehn.

\goto{Old Business}

OBA, usual stuff.

\goto{New Business}

(TLH) Minicult: Coming out of the elevator, I spotted 2 gorgeous blonde stewardii. Were with a... (I refuse to finish writing this Minicult. It's pointless.)

(TG) Someone downstairs is selling buttons: "I'm not a fan, I just read the stuff."

(TLH) Move to condemn person for stealing it and not paying us royalties. Passes 5-0-1 +Spehn.

(TG) Minicult: Harlan claims LDV will be pubbed next year.

(Liz) Motion to donate some money to Bob to buy new pants. Passes most everybody-5-6 +Spehn.

LHE refused to hear any non-banana motions. Many bananas died. And the adjournment song was (sort of) sung.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Temporarily,}
\centerline{Janice Eisen, Onseck}

\end{document}