\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 21, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, Onseck and Pseudo-Skinner (who was darkly attired and darkly tuned), presiding.

(B*) Motion to approve minutes as leathery and batwing. Passes 11-5-4 and an elbow +Spehn.

\goto{Committee Reports}

Moocomm: Mr. Galloway said something in Albanian.

(JME) Jourcomm: Submissions to TZ 34 are acceptable. (KRJ) Motion to name JME as editor to whom we would most like to submit. Passes many-0-0 +Spehn.

(KRJ) Motion to name TLH as the editor to whom we would least want to submit. Passes aleph 1-0-5 +Spehn.

\goto{Old Business}

(KRJ) Motion to give Tom Galloway a better gag. Passes thousands-1-3 +Spehn. Happiness ensues.

The usual motion, the usual result.

OBA: um, us, uv, ur.

\goto{New Business}

A motion was passed to censure a random for not having voted at all.

(KRJ) Albanian motion for Mr. Galloway. (Mr. Galloway was censured for coercing a vote.) Passes many-4 and random-1 +Spehn. Much joy resulted from the passed motion.

Phone call answered by JME, our pseudo-Skinner, to talk to JP, our actual Skinner, who informed her that the random we'd previously censured was a new keyholder- Greg Greeley.

B* censured for presenting committee reports out of order. Passes many-n (>8)-0 +Spehn.

The Albanian made a motion. It was seconded and passed.

Motion by amendment to make the new keyholder a green banana. Fails 7-15-1 +Spehn.

(DCB) Motion to censure the meeting for sexism. Motion passes 3-0-0 +Spehn.

(The preceding motion occurred as the result of a comparison of the sexual-enticement value assigned by Mr. Johnson and Mr. Starr to the modes of dress by the post and present Skinners and the pseudo-Skinner. As this is sexist and having just come from an IAP event on "International Sex Roles.")

The adjournment song was sung 5 times.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST. (Bunches of other stuff occurred, but I forgot some minor points. But did you really want to know how MITSFS became the latest nuclear power of the world?)

\vspace{18pt}

\centerline{Illegibly submitted,}
\centerline{Dave Broadbent, Pseudo-Onseck}
\centerline{Amended by JME, 1/23/83}

\end{document}