\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 23, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(Merryl/Adina) Motion to disapprove minutes as incomprehensible in parts. Passes 15-6-1 +Spehn.

\goto{Committee Reports}

(TLH) Asimov brought 2 brand-new books, autographed, and donated them to us.

(JME) Smootcomm: Pete just arrived.

(JME) Ourgreatestenemycomm: Immerman says SAA does not exist. If they don't exist, why can't we have their room?

(TLH) Greasecomm: Tim has been invited to a "leadership conference" on 10/1- sponsored by ODSA and UAP Mike Twitt. Two fantasy items: "The truth according to the ODSA" and "Balancing activities and academics."

(JME) Jourcomm: Printing 10/2. Need 3 people and a car.

(KRJ) Othercomm: Successful conclusion of a 10-year search for complete sets of "Monsters and Things" and "Monster Parade."

(JME) Postawfulcomm: We got a shipment of Witter returns delivered back to us. It's Andy's fault!

(JME) Motion to condemn Andy for not being here to be censured. Passes semi-unanimously.

(TLH) Moocomm: David Marcus will be in STrek III. Tim suggests he will be assistant ship's preppie.

(JME) Lecturecomm: Asimov lecture was. Some discussion of his lechery.

\goto{Old Business}

OBA: um, us, self referential discussion (is there a usual discussion), uv, ur.

\goto{New Business}

(TLH) Minicult: Tickets to Doonesbury musical are now on sale. Trudeau wrote it.

(B*) Minicult: Berke Breathed is threatening to quit Bloom County. He's fighting with syndicate.

A visitor for the SUNY/Stony Brook Science Fiction Forum introduces himself. Most of the attendees listen politely. Exchange of greetings, etc.

Banana motion by JP ignored.

(MJG) Move to award a nice banana to this nice person from Stony Brook for coming and talking to us so nicely. Passes by fiat.

\vspace{12pt}

\noindent
Meeting adjourned, 17:33:33 SST.

\vspace{18pt}

\centerline{Pseudo-submitted,}
\centerline{Janice Eisen, Vice and Pseudo-Onseck}

\end{document}