\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 12, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(RcH) Motion to approve minutes as red. Passes 8-3-5 and a whirlybird +Spehn.

(Hitchcock) Motion to condemn van der Heide as boring. Passes  about everybody-7-4 +Spehn.

\goto{Committee Reports}

(A^2) Moocomm: Remake of Body Snatchers tonight in Dolby.

(B*) Pseudo-Moocomm: A while back, Hollywood police arrested someone for having about 1200 cans of stolen film, including some film believed to be lost forever.

(MJG) StarWarscomm: On the radio today, plots for the other 2 trilogies reported. First 3- destruction of Jedi and rise of Empire. Will feature Obi-Wan, Anakin, and possibly Luke as a baby. Second 3- destruction of Empire and renewed rise of Jedi. May feature Luke as an old man. Characters appearing in all 9 will be C3PO and R2D2.

(Broadbent) Fweekcomm: Claims he can't get R/O office to tell him when Freshman Midway is. Tim suggests he pretend he's Shirley McBay.

(Dumas) Moocomm: New STrek movie (The Search for Spock) will start filming in about a week. It will feature Mark Lenard and Dame Judith Anderson, 82-year-old noted British Shakespearean actress.

Some discussion of Spock as a radioactive vampire.

(Dumas) Whocomm: 20th anniversary Dr. Who show soon.

(TLH) T-shirtcomm: Asks for suggestions on colors. All the suggestions are bad.

Onward to...

\goto{Old Business}

OBA and all the usual...

\goto{New Business}

(JME) Albanian motion on van der Heide. Ties 7-3-6 +Spehn. Skinner passes.

(TLH) Minicult: There will be a Dragonriders of Penn video game.

Robert van der Heide waves the Reserve Banana around in Albanian. Merryl translates it. Passes 47-32-12 +Hike! +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17something SST.

\vspace{18pt}

\centerline{Gloomily submitted,}
\centerline{Janice Eisen, Vice and Pseudo-Onseck}

\end{document}