\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 16, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

Miller motion by anonymous caller.

(GF and DB) 2 motions about minutes. Brings Albanian motion on DB.

(Shawn) Motion to approve minutes as scarcely legible. (JME) Friendly amendment- scarcely audible. Passes 11-7-6 +Spehn.

(A^2) Motion to censure a frosh. Passes 5-7-2 +Spehn.

\goto{Committee Reports}

(Shawn) Jourcomm: TZ 36 real soon now.

(JME) Jourcomm II: maybe TZ 35 [illegible].

(Shawn) Rosfap: Got backlog down to 4-foot pile.

(Ken) Pseudo-Moocomm: "LCS" has Isaac Asimov. LSG and MJG were mentioned.

(JME) Motion to commend Skinner for not giving us a report.

(TLH) Skinner Report: Working on an electronic gavel for Boskone.

(Ken) Motion to censure the Skinner for hitting the nice piece of titanium with that nasty wrench while people are trying to talk. Fails lots-7-3 +Spehn by inverse skinner rule.

(Ken) Note: Skinner likes to be abused.

\goto{Old Business}

OBA, usual everything.

\goto{New Business}

(TLH) Minicult: While selling tickets (reading Tech)- talk to MTG about doing Oh! Calcutta. (Several motions about this.)

(Shawn) Move to censure the man in the banana colored shirt for trying to push over a shelf before the meeting. Passes infinity-lots-much minus 3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:36:26 SST.

\vspace{18pt}

\centerline{Illegibly submitted,}
\centerline{Andy Su, Onseck}

\end{document}