\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 26, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(A^2) Motion to approve minutes as too disgustingly cute for words. Passes everybody-2-2 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: TZ ready. Just needs to be reproed. Will be out RSN.

(TLH) A boring report- something about Arthur C. Clarke and communications satellites.

T-shirtcomm: Tuesday at 7 PM- we're running new ones. Everybody be here.

Skinner submits a circuit diagram for a male chauvinist pig. (See fire door.)

(TLH) I had my wisdom teeth removed. I'm donating them to the Library. (He shows them. Sounds of disgust.)

(Flynn) Moocomm: Yor opened last Friday. It closed already.

(B*) Pseudo-Moocomm: They had a big fire in Hollywood, and several movie sets were destroyed. STrek III's were unharmed, though. William Shatner is reported to have manned some of the fire hoses.

(B*) Whocomm: New Dr. Who soon- named Colin Baker.

(Broadbent) Fweekcomm: We're getting there.

\goto{Old Business}

(JME) Judy's back. (She grins cutely.)

OBA, etc., etc...

\goto{New Business}

(JME) Minicult: The new MIT catalogs are out. They illustrate the lectures with a picture of the Good Doctor (looking fearsome).

(JME) Minicult: Broadbent is famous. (See New Yorker cartoon on door.) He claims "Broadbent" is a regular character in those cartoons.

MJG makes some random banana motion. Passes lots-fewer-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:34:37 SST.

\vspace{18pt}

\centerline{Tiredly submitted,}
\centerline{Janice Eisen, Pseudo-Onseck}

\end{document}