\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 28, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(Shawn) Motion to approve minutes as nuked blue. Dies for lack of second.

(TG) Motion not to approve minutes. Passes many-4-7 +Spehn.

(JME) Albanian motion on Tom Galloway. Fails (but not by much).

(Chip) Albanian on Bob van der Heide. Passes.

(JME) Sanskrit motion on Tom Galloway. Passes.

\goto{Committee Reports}

(JME) Pseudo-Picniccomm: A letter was sent to Harry Stubbs asking him to set the date.

(TLH) Moocomm: 5th SF marathon was. Record set for attendance.

(Shawn) Jourcomm: TZ 34 is being printed even at this moment.

(JME) Onseck announced she will not be here next spring.

(JP) Motion to commend Onseck for doing an extraordinarily superb job. Passes everyone-0-0 +Spehn.

Malcomm: Bang!

(KRJ) Etruscan motion on Malcolm Y. Ties 6-1-5 +Spehn. Skinner breaks tie- motion passes.

(JME) Techniquecomm: They said our ossifers list was too long. Also that the title LHE was libelous.

(TLH) Moocomm: Dune is coming out, starring Sting (lead singer of The Police).

\goto{Old Business}

Old Business Algol. All usual.

\goto{New Business}

(TLH) Motion to commend KRJ for his new job. Passes many-1 Etruscan-3 +Spehn.

(KRJ) Channel 56 will be showing 2 back-to-back episodes of Star Trek on Saturdays. They claim they'll be uncut.

(Flynn) Minicult: Actor who played ET is dead.

(Many people) Babel motion. Passes.

(JME) Ich bin ein banana. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Farewell for now,}
\centerline{Janice Eisen, Onseck}

\end{document}