\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 24, 1983

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Once upon a Friday dreary, while we pondered, weak and weary,

Over many a quaint and curious volume of John Norman's Gor-

While we nodded, nearly napping, suddenly there came a tapping,

As of someone loudly rapping gavel of titanium ore.

"'Tis our Skinner," we all muttered, "starting meeting as before-

Only this and nothing more."

Minutes read by pseudo-Onseck- last week's flaming, all of that dreck-

Were accepted as well-read upon Ken's motion from the floor.

There were several other motions, but they all were silly motions,

And they died, these stupid motions, since them all we did ignore.

"Modern record," noted Vice, "-six pages read, no less, no more-"

Filed here forevermore.

And the Onseck showed a letter written saying that they'd better

Give out barf bags if on Star Trek Club cartoons they showed once more.

Jourcomm said, "TZ Real Soon Now" and explained to all the room how

Book reviews and art are needed for a zine we can adore.

Apathycomm reported "Yawn." By Ghw, this meeting is a bore-

Yes it is, and nothing more.

Gemcomm said we must be fated to forever be elated-

Winning prizes of Black Stars of India to rest in a drawer.

An attempt was made by Skinner to skip Old Business and hurry to dinner,

But the Onseck was the winner and Old Business was once more.

Mr. Ebrom, an ex-Skinner, bowed 'midst apathy from the floor

-That was it and nothing more.

Starr's business from last week was heard: a third-rate burglary occurred

Eleven years ago last week (remember the tape on the door?).

Some discussion, much applause, and it almost gave us pause.

Then Glob transcript of JFK tapes (see attached) was really poor-

Every word was garbled and the speakers nameless evermore-

Merely this and nothing more.

Said Sitcomm: Channel 38, in order to commemorate

The movie Twilight Zone tonight is showing episodes, three or four.

Old Business Algol, all that guff, and all the usual stuff,

Till we thought we'd had enough of motions from the days of yore-

A.R. Lewis, Wisowaty, I. Lapeer, and many more-

Remembered are for evermore.

Kathy, purring like a kitten, showed a Star Trek fanzine written

By a young man named Dave Broadbent who was 14 then, no more.

David by this was quite flustered- ran away, the silly bustard-

But a posse soon was mustered, dragged him back in through the door.

He agreed to autograph it, though he was embarrassed sore-

Sat, and blushed, and nothing more.

Sally Ride on Earth has landed, and some repartee was bandied

Over whether shuttle hosted feelthy acts while it did soar.

When 'twas said that NASA did to fly with husband her forbid,

We condemned them, yes we did, for keeping us in suspense sore.

"What's it like in free fall?" One of the great questions, to be sure-

We shall wonder evermore.

MBTA this week stated: "Rear wheels wrong shape." A bit belated.

Note that when the shuttle landed out on California's shore,

Good news: "Beer's cold! Hip-hip-hooray!" Bad news: "It's 3K miles away!"

Skinner gave some minicults but we had heard them both before-

Souls got weight and trees can talk- yeah, yeah, why don't you tell me more?

Quoth the members: "What a bore."

Meeting started to get slower as our energy got lower.

We discussed some film cassettes that we'd vote on in one week more.

Motion to commend the MITSFS for being banana republic- by Janice-

And we passed it in some manner as we voted from the floor.

Meeting adjourned- 17something SST, I am not sure.

Quoth the Skinner, "Nevermore."

\vspace{18pt}

\centerline{Poe-etically submitted,}
\centerline{Janice Eisen, Vice and Pseudo-Onseck}

Attachment: EXCERPT FROM TRANSCRIPT

Speaker ?: (Words unintelligible).

(Unintelligible exchange continues in the distance.)

Speaker ?: Well, (words unintelligible) like this. (Words unintelligible).

Speaker ?: (Words unintelligible).

Speaker ?: Well, if you can get that polls...

Speaker ?: (Words unintelligible).

(Unintelligible exchange continues in the distance.)

(Phone rings.)

Speaker ?: (Words unintelligible).

Speaker ?: Yes. (Words unintelligible).

(Cough.)

Speaker ?: (Words unintelligible). He was looking for (words unintelligible).

(Background noises continue with occasional unintelligible conversations faintly heard in the distance.)

(Phone rings.)

(Background noises continue with occasional unintelligible conversations faintly heard in the distance.)

Page 10 from transcript of tapes, made at time of University of Mississippi integration, Sept. 29, 1962.

\end{document}