\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/18/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 18, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

M: silence. 11-2-1 +Spehn.

M: due to previous motion the minutes were not read or heard.

M: laconic motion. Passes- make up numbers here.

JFC was accused of being in CS- apparently they know his name.

\goto{Committee Reports}

Jadecomm: censored.

Jadecomm2: made Jade bark. She does tricks for food.

Mobcomm: big box of books. New shelf.

M: condemn JFC for taking all the business- monopolize it like Microsoft. 14-1-9 +Spehn.

Onseck: we'll have membership cards soon.

Mobcomm: we have lots of boxes of donations.

Jourcomm: 1 person submitted something. Still lots of virtual submissions. Note- bug Ed to write a review of Acts of the Apostles.

Pianocomm: have processed a few more boxes of donations.

Pseudo-pianocomm: will be getting back to work soon. (Justin)

Move to block something to block sunlight. Chickens.

Justin: "I am not a whipping boy, I'm Apathycomm."

Skinner: "AMU, you should let Yevgenia use the whip."

Yevgenia: wants to be continuous, but cannot make it.

Someone hands Yevgenia a whip.

Jade comes and sits by Natasha, where she'll be "safer." Justin fails to put stickers on her.

\goto{Old Business}

M: to move to new business. Passes.

\goto{New Business}

Phone call: fully transcribed, both sides of it, but censored.

Jade defiles my minutes!

Skinner on the phone: "we're not in the business of finding/looking for people."

Jade throws pens at JM. JPW: "It was this close, I swear!"

JPW: "Dangling things are interesting." "I wasn't aiming for Jamie, he's no challenge."

Motion: continue meeting. Passes.

M: condemn Jay for having flashbacks. Passes.

The meeting is back on crack.

Shelves are in bookcase involving Telzey toy as precision tool.

Jade keeps missing. JM threatens to spank her. Jade scores minutes with nailfile.

Someone should host a reshelving party.

M: score Natasha with nailfile. Fails.

\goto{Future Business}

Motion about Yevgenia's bananas. Fails.

Jade attempts to harvest Justin's head.

M: commend Natasha for sitting on banana colored chair. Chickens.

M: condemn skinner for not using banana colored powers. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 17(some-sort-of-nonsensical-moan) SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
