\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/21/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 21, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, Pseudo-President and
Skinner, presiding.  [Unknown] is the Pseudo-Onseck.

Minutes read.

Motion to commend reading a "capturing the spirit of last week's meeting precisely." Fails, lack of second, as do several other motions.

Motion to second a motion. Fails 5-0-8 +Spehn.

Motion to end meeting before skinner dies. Fails, lack of second.

\goto{Committee Reports}

Dex: inventory tomorrow.

Bob: stuff appeared on Panthercomm shelf.

Pseudo-pianocomm: Kat Allen is a prentice, NIM is processing magazines.

Pseudo-hasslecomm: lots of books remain to be done.

Skinnercomm: the skinner is not dead yet.

\goto{Old Business}

Toby Eliot donated 5 boxes of books.

CAC is dithering about locks yet again.

The bank may give us a new sig list soon.

Bruce Miller is skiing in Colorado.

Usual motion, usual result.

\goto{New Business}

A sorcerer in central Africa was sentenced to 4 years for raising the dead.

We have a new life member. In fact, we have two of them: Seph and Cordelia.

The Schultz books have been rearranged into a pyramid, with help from UFOs.

\goto{Future Business}

Donated stuff will be processed in the future.

Pentiumcomm has arrived!

Motion to condemn bananas for not being present at start of meeting.

Motion to have a banana colored vote.

Motion to have a banana vote. Chickens 2-0-4 +Spehn.

Motion to condemn Pumpkincomm for not doing its job. Fails 0-0-1 +Spehn.

Motion to name J Bananacomm. Passes 7-0-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}
