\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/8/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 8, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the board-frying Onseck.

Minutes read.

Motion: Commend the minutes for not exploiting dead authors.
Passes 13--2--3+Spehn.

[Jade] ``And the count was even accurate.''

\goto{Committee Reports}

Plantcomm: Our doorknob looks dented.  Jade denies any responsibility.

Jourcomm: Grrr!  People are not submitting.  Jourcomm throws dirty
looks at John and Jayhawk.  The Skinner rummages through the Vice drawer
to arm Jourcomm.  Yevgeniya accidentally whips Jade.  There are many
calls for kinky Vice-on-Skinner action, and a mention of the studded
leather banana.

Pseudo-Pianocomm: There are no more ``So You Want to be a Keyholder''
sheets.  This is Diane Duane's fault, for some reason.

Mobcomm: A couple of British books have been ordered.  They may or
may not send us the ones we want, though.

Bluebellcomm: John covered half of twenty-four books.  We now have
oodles of book tape.  Discussion of how much an oodle is, and is it
a metric unit.

Pseudo-Plantcomm hefts a battery.

Pseudo-Pianocomm: We need more prentices.

Mobcomm: Bought some books.  There is a discussion of the financial
form that Stephanie has been resolutely ignoring.

Panthercomm: The ZGT is cold.  [Jade] ``I hate sitting on the ZGT
when it's cold.''

Concomm: The Chicon souveneir book came out.  It's a double.

Jadecomm: Her hair thingy is a nice purple color, and it clicks
when tapped.

\goto{New Business}

People are instead thinking about future and old business.

Unusual motion.  Unusual second.  [Sam] ``I assert we're having
unusual debate!''  Indeed, lots of debate.  [Jade] ``I'm unusually
confused.''

\goto{Old Business}

The shelves are still here.  The clock has been moved to avoid the
shelves.

The ``free books'' people (Nibblebox) have specified the services
they want: they want an on-campus rep.  There is some sort of
connection to scifi.com.

[Sam] ``It's a new company.  New companies don't have products.''

Jade proposes Smitecomm to smite them.

Discussion of nuking CUSFS and the traitor Aaron.  Natasha is over
there now, though.  A call for a Natasha-impersonator to take her
place here.  A new office, Pseudo-Natasha.  A discussion breaks out
comparing Yevgeniya's and Natasha'a accents, which are somewhat
distinct.  ``From Russia with love.''

What's happening with the locks?

\goto{Future Business}

Another donation is coming, around 450 books from an MIT staff
member.

The Vice and Skinner have a meowing and growling conversation.

Motion: Condemn the Vice for whining.  Voting results in 4--13--3+Spehn.

Motion: Punish the Vice by putting her in a whine press.  Voting results
in 5--10--2+Spehn.

Motion: Have a matrix vote.  Voting results in 3--15--1+Spehn.

Pentiumcomm reports the determinant as 67, so all motions pass.
Jayhawk is confused about the self-referential nature of the matrix
vote.

Yevgeniya lies down on the minutes-in-progress, much to the confusion
and consternation of the Onseck.  There followed much poking fun at
the Onseck, which sadly cannot be recorded here because of the Vice
draped over the minutes.  Oh, well.

Our bulletin board got reallocated.  Yay, we have our old one.
Boo, we have our old one.

Magazine binding should happen next term.  Some discussion of how
to go about doing this.

Jade is tired of being shuffled around by the library system.  Time
to be dealt or cut?

Next year we'll get some new furniture, filing cabinets and so forth.

Jamie is pretty much the brains of the Star Chamber.  Jade has to
lose an eye to gain wisdom... is taking out a contact lens good
enough for just a little wisdom, though?

More discussion of Jade's hair.

Motion: Something about Skinner's hair and Slurpees.  Voting results
in 8--0--5+Spehn.

Motion: Or a banana!  Voting results in 7--1--1+Spehn.

Motion: Turn the Skinner's hair into a banana-flavored Slurpee.
Voting results in 17--infinity--3+Spehn.

A matrix vote proceeds for some reason.  Pentiumcomm reports the
determinant as +26*infinity, so all motions pass.

\vspace{12pt}

\noindent
Meeting adjourned at ``no time at all''.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
