\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/13/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 13, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the TGIFified Onseck.

Minutes read.

Motion: Commend minutes as horribly efficient.  Passes 9--0--1+Spehn.

Skinner complains about the gravitational constant G increasing this
week, as judged by the gavel weight.

\goto{Committee Reports}

Pseudo-Bondagecomm: Jayhawk is Bondagecomm, needs keys for cabinets.

% Jayhawk is John Hawkinson, username jhawk.  This is how I'll render
% his nickname, just for legibility.  - Ed

Douglas Adams speaking soon.  (Report by LSCcomm, Authorcomm?)

Batteries in the alarm still taste good, but need to be replaced.

Jadecomm: Skinner is not wearing pants, is missing an arm, and her
tummy feels weird.

Motion: Commend the Skinner's environmentally-friendly battery disposal
method (to eat them).  Passes 7--3--2+Spehn.

Motion: Commend the Skinner for her mathematical acumen.  Seconded too
late to count.

Mobcomm: We got some hardcovers to keep Jayhawk quiet.  Lots of new books
next week.  We got review copies from the one publisher who cares about
us.

Discussion of how to write good reviews without spoilers.  ``This book
was good, but not as good as the last one.''  ``This book was good.
I liked the taste of the paper.''

Theftcomm: Updated the online sche-

\goto{Old Business}

-dule.

One of the shelves moved into Damnation Alley.  Probably needs to come
back out.

Discussion of SFWA boxes under the dripping ceiling.  Ack!  This is too
close to real business!

Measurements for shelves still underway.  Buttloads of keyholders and
prentices will eventually be required.

[Jamie] ``It's BIG, John!  It's one big unit!''  (This was referring
to an aisle of shelves in the Reserve Room which is all connected.)

\goto{Future Business}

Could we just switch the circulating and reserve rooms?

Computer discussion.  AirPorts, IPs, SIPB.

``And then we're going to embezzle...''

Building shakes... huh?  Earthquake?

Motion: Comfort Jade.  Jade questions meaning of ``comfort'', is
reassured.  Chickens 1--2--7+Spehn.

Motion: Comfort Jade with a banana as large as it takes.  Chickens
lots--0--an immense amount+Spehn.

Adjournment song singing.  ``No, don't {\em harmonize}!''

\bing \bing \bing

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
