\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/15/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 15, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1737 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the pseudo-Onseck, soon to be Onseck,
maybe.

% Our previous Onseck, Merry Peck, turned out to be extremely lax in her
% duties, and was in the process of being ousted from office at this time.
% This became official shortly.  - Ed

% Incidentally, hi, I'm the new Onseck.  I'll get better at the minutes
% eventually.  - Ed

Various comments on 1700 versus 1737.

Minutes read.

Motion: Bring Laura into the Library to hear motion regarding the
minutes.  \bing  Passes by Skinnerial decree.

Hellos and scritches.

Motion: Onseck is authorized to correct Skinnerial mistakes.  Unfortunately
the motion is not seconded.

Motion: Condemn whoever Scotch-tapes the keyholder desk.  (Believed to be
Neel).  Passes 12--3--3+Spehn.

\goto{Committee Reports}

Pseudo-Fweekcomm: Some new members.

Pseudo-Plantcomm: Flickering light is bad.

``Laura hates us.''  Something about Jen's tapeworm.

Pseudo-Panthercomm: Glad we're not Panthercomm.  The shelf is exploding.

Jadecomm: Jade is violent.

Pseudo-Hasslecomm: Hasslecomm overflow boxes are gone.

Pseudo-Pianocomm: But they're just moved for a prentice to deal with.

\goto{Old Business}

``Awww...''  They won't take our books away.  We have readable books, not
collectable ones, silly us.

Collectors want unstamped books... darn it.  Baseball card analogy.  Julius
Caesar's uncut manuscript.

Creation of the Universe made possible by a grant from Texas Instruments.

Gavel aerobics with chainmail bikini... various pleadings to show that off.

Motion: Condemn the Telzey for not doing his job recently.  Fails
7--infinity--1+Spehn.  ``Better known as Skinnerial decree.''

``Jay's about to become Albanian.''  People getting older.  Continuous
versus discrete versus discreet bad puns.

\goto{New Business}

Yay!  Chair donations by the LHE.  Two of them, even.

Motion: Commend the LHE.  Twice!  Exclusive-OR the motions.  Passes
20--0--2+2*Spehn.

New newsletter, yay, even a funny one.

New Star Chamber in progress, including a part-Onseck.

Motion: Vote on which part to include.  Chickens 7--0--7+Spehn.

\bing \bing  ``Ooh, I like that bing.''

Motion: Warn people when you bing too loud.  Fails 7--infinity--0+Spehn.

Motion: Speak in a smaller font to allow the Onseck to conserve paper.
Passes 14--0--0+Spehn.

Motion: Say ``hi'' and embarrass the new people.  Passes 17--1--5+Spehn.

``Hiiiiiiii.''

``Algebra-la-la, la-la-la-la.''

Call to borrow some Vice instruments.

``This place needs a vice squad.''  Groans all around.

Puns continue.

Motion: Set off the Albanian nuclear bomb, turning everyone Albanian
for a ten-mile radius.  Fails by Skinnerial decree.

Motion: Albanian Jamie and his shirt with the banana-colored thing
on it.  Passes 17--cheese--1+Spehn.

``Are Albanians full votes?''  ``They have limbs, don't they?''

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
