\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/07/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 7, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, SF, Pseudo-President and
Skinner, presiding.  NM is the Pseudo-Onseck.

Minutes read.

M: commend minutes for salience. Fails 7-8-1 +Spehn.

JB: "That's the wrong stamp!"

M: commend minutes [illegible].

\goto{Committee Reports}

Dex inventory still 22.

Good condition books being Hassled.

M: condemn library members for weeping getting books wet. Fails for lack of second.

M: to the left. Fails 2-3-5 +Spehn.

JC: will drive 1500 miles for books.

Quote page 85. Time they all gone raving mad.

Book throwing. Be nicer to books.

Next one goes for head.

M: commend other rooms for not existing. 2-0-0 +Spehn.

\goto{Old Business}

JM found really old records. Classes renumbered. There is shorter number of 0s.

Page chapters end on: 85. Every last word.

M: condemn for not having life. 1-5-4 +Spehn.

\goto{New Business}

M: Albanian skinner. 9-0-1 +Spehn.

M: bend will of skinner. M: invert. Fails, skinnerial decree.

New alum list: 450 people. If one gives us a million dollars, we'd get.

M: to not sell off books- make land. 3-4-0 +Spehn.

M: in mysterious ways. 0-0-8 +Spehn.

M: Albanian Jamie for pun. 9-1-4 +Spehn.

Pseudo-pianocomm: pseudo-skinner checked in and signed first member, mighty fine.

Want giant stamp, soaks pages with ink. Radioactive books. What are those worth? Pseudo-skinner scores John points.

Jenwa out of country.

M: Albanian Jake. 8-0-4 +Spehn.

M: Albanian John. 12-1-1 +Spehn.

Albanian majority.

M: Albanian rest of room. No second.

M: make silly book Albanian. 6-0-0 +Spehn.

No umlauts.

Fix multi-author bus? Maybe.

Lots of RFEs in dex.

No Berke in alum mailing.

M: send alum newsletter on banana colored letters. 8-3-1 +Spehn.

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{NM, Pseudo-Onseck}

\end{document}
