\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/04/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 4, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, Pseudo-President and
Skinner, presiding. [Unknown] is the Pseudo-Onseck.

Minutes read. Pseudo-skinner pauses in middle to laugh hysterically.

M: approve minutes as apparently hilarious. 6-0-0 +Spehn.

\goto{Committee Reports}

Mobcomm: close to time to buy hardcovers... start thinking of time to go... Saturday? Discussion of days, traffic, closing times... decides on Monday at about 2 PM at T stop, meet at 12:45 at office.

Dex: very little was actually lost, almost everything that was missing was found behing shelves, vanished [illegible] from last year reappeared behind shelves too.

\goto{Old Business}

JM: Technology Review ed. emailed for info about MITSFS, gave her another update. Mentioned that in March the amount of space open equals amount of books received in hopes this will get into the article.

\goto{New Business}

MWP: losing hunk of flesh.

Skinner defends pseudo-onseck and tells Jamie to be nice to her.

JM: Jade's letters from China came- midway related useful info from Jamie.

JM has no opinion about something.

Jenwa had a good day- tells about it (might get a job editing an earth science textbook). Digression about geography of Union Square.

M: to commend skinner for wwriting textbook about an alien planet. 8-1-3 +Spehn.

Moocomm: Chicken Run was not anatomically correct- chickens had teeth and hands, never had feathered wings.

Disagreement ensues- skinner maintains that at times there were wings.

JM maintains that could have either arms or wings as needed- chickens of the future.

Skinner: what about X-Men? X-Men was good.

WDS complains about X-Files episode.

\goto{Future Business}

Doesn't seem to exist.

In the future John might give us money.

M: bananas as currency? Fails, lack of second.

Motion concerning bananas passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}
