\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/17/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 17, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the thirsty Onseck.

[Jade] ``I need to {\em bang} something!''

Minutes read.

Motion: ... (motion was aborted)  Chickens 2--0--5+Spehn.

Motion: Everyone should second things, since Jade wants to bing a
lot.  Passes 7--0--5+Spehn.

Motion: Commend the minutes for being as accurate as we would expect
from an oyster.  Passes 4--1--3+Spehn.

% The exact behavior of Spehn's vote in the case of a tie is not
% quite defined.  Previous recent Skinners tended to rule ties in
% Spehn's favor, while Jade seems haphazard about it.  - Ed

\goto{Committee Reports}

Jadecomm: Jade was shocked to find out that Jamie is actually ``James''.
James ``Jamie'' Morris.  This is treated as confusing by Jade for some
reason.

Motion: Give the Skinner a nice relaxing cup of cocoa.  Passes
10--0--3+Spehn.

[John] ``My body damps out vibrations.''  Wave-particle duality.  An
impromptu game of gavel baseball breaks out.

Mobcomm: I have done nothing useful this week.

Theftcomm: Bulletin board complaints from the ASA, we'll be dealing
with them.

Alohalenscomm: More prints.

Jamie fixes the Pinkdex.  Pinkdexcomm has an aborted report, moved to
new business instead.

Motion: [Jade] ``I'll shut up now.''  Fails by Skinnerial decree.
\bing

\goto{Old Business}

Shelves are ugly and still not holding books.  In fact they are blocking
a good photo of the library too.  Jade is reported to be almost fully able
to operate a camera.

The gavel is heavy.

\goto{New Business}

\goto{New Business, again}

John makes a bad pun about mean (mean-spirited) versus average.  This was
originally too horrible a pun to even record, but...

Motion: Condemn the Onseck for failing to write down the meeting.  Fails
5--infinity--1+Spehn.

There is a meeting with the MIT library people scheduled.  The ceremonial
passing of the Pinkdex, although we're not quite sure what they do with
it.  Jade will ``have words'' with them.  (This must be said with an
English accent, on request.)

Joe probably has a key.  Maybe not.  We might have to see a locksmith.

Pinkdex discussion.  More than one Pinkdex are ``Pinkdicies''?  It is
reported that before Dexmaster we had horrible Emacs manual editing,
magnetic tape, and punch cards.

\goto{Time warp to Committee Reports}

Jourcomm: People need to submit things they promised.  A meaningful look
at John...  The zine will happen during finals or IAP.  No drawings at
the moment means no cover, however.

Motion: Make Yevgeniya stare at the back of Jade's head instead of the
front.  Chickens by an unspecified vote.

Alohalenscomm take 2: Ed finally got a real print for his photo.  Deepak
is still elusive.  Stephanie is available in both normal size and in
miniature.

\goto{Back to New Business}

\goto{Future Business}

[Yevgeniya] ``There is no future, there is only Zuul.  And exams.''

Motion: Declare Yevgeniya Albanian.  Passes 5--3--1+Spehn.  The motion
was in fact retroactive so Yevgeniya's votes didn't count.

Motion: Study Albanian bananas.  There was no second, but voting
proceeds anyway.  John disputes this, and it is pointed out that he is
taller than the Skinner.  Voting gives 1--4--3+Spehn.

Motion: Commend Jade for having multiple ways to cut John's height
down.  Results are 4--3--1+Spehn.

Motion: Have a matrix vote.  Results are 4--a lot--1+Spehn.

Pentiumcomm calculates the determinant as 72, after deciding that ``a lot''
should count as 12.  ``Twelve is a lot.''  All motions pass.  \bing \bing
\bing

There is some more gavel baseball, and Jade clobbers the newly-painted
door.

Aaron reminds people that a banana motion actually passed.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
