\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/12/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 12, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: reading amazingly enthusiastic yet still baroque. Passes.

\bing

Onseck: "I saw a flash!" Oh, there was a flash...

\goto{Committee Reports}

Mobcomm: JFC offering a ride- "Especially if Star Chamber, come see me."

Jourcomm: TZ exists minus jhawk.

M: condemn jhawk for dodging TZ and hiss at him. Passes 18-1-0 +Spehn.

Pseudo-physplant: drip is being addressed. Discussion of toxicity/corrosivity of water dripping into library.

Picniccomm: we have drivers. We can put food in the cars and people in the trunk. M: put YN in the trunk. Passes.

Pseudo-pianocomm: 3 new keyholders. Justin: "I may actually graduate before I get my key." JM: "We'll ambush you at graduation."

JFC: "I can add zeros pretty fast."

JM: "If you check out a whole pageful of books at a time you'll get a lot of fines."

Jade: "I'm allergic to boring discussions." 8-8-8 +Spehn. (8 times.)

Moocomm: Battlefield Earth is worse than Plan 9 from Outer Space according to NY Times.

\goto{Old Business}

J: last chance to get a permanent membership with all the advantages associated from Jenwa.

People say lots of silly stuff and sing randomly.

Some motion.

JWH: "Shit, I can't remember any numbers anymore." Someone: "A true MIT graduate."

Usual motion, usual result, chorus: "what about the usual debate?"

JWH: "Let's have elections then."

\goto{New Business}

Justin as Vanna: "Elext-ions!!!"

Onseck nominations: Na-ta-shao's bananas, someone, Merry Peck, some daughter (Evil ARLewis), Tare, Wayne Barrell has-been, Jade's hair thing, jhawk's radio, jhawk's caffeine. Votes included: various people stripped/washed/tied/etc. and brought to people's tents, spanking Jade, Natasha, obsure 80s music references.

JM: "Don't try to break the skinner with your votes."

First round: Merry wins with 4.6 points (not enough to win), Natasha 2.3.

Second round: Merry 7.4, Food 1.5, Natasha's tied with spanking and happiness.

LHE nominations: Parker's Web, John's camera, Stephanie Fried, whiplash, web of Spiderman, invisible people, God and my parents, ASA, J's secret masters, Jade and Tasha tied together, fried Natasha, fried worms, Chainsaw Warriors of gore, banana + milk = Fried. Votes included: Fleet Bank, Finboard, Natasha's Bananas of Gor, Jade and Natasha stripped/washed/tied together/covered in whipped cream/caged/shipped to Gor, jhawk's widdershins, worms in alfredo sauce, Jade + Natasha = :).

First round: Stephanie 6.1 (did not win), worms 2.3, widdershins 1.2.

Second round: Steph 8.1, AAC 1.2.

Vice nominations: Yevgenia/Ebnerune, Sloth, Gluttony, Lust, Pride, Jamiehawk, Jenwa's tent, widdershins gasoline, LSC, clamps, seduction, MIT FOC. Votes included: defiled bananas, Boston Common, Yevgenia stripped/tied, seducing Chainsaw Warriors of gore, Vices including Nettrek (lust, gluttony, sloth, pride), Yevgenia and Aaron playing with supplies in vice drawer (do they both fit inside the drawer?), Star Chamber babes calendar swimsuit edition.

Yevgenia 9, Jenwa 1.3.

President nominations: Jade, silence, Talcum, diamond, Tough Passive Jade, Nessie, Nessus, Zorro, Kzinoegor, Larry and Pink Niven. Votes included: hamster the unsqueakable, Matlab, purple Pakprotector, but I... widgets, party in Jade's tents (after Jade, Natasha, Jenwa are dragged there one way or another), Bill Clinton and chocolate cigars, hot monkey sex to make the vice blush, visiting Jade's tent, Star Chamber's swimsuit calendar of Gor, various people on the centerfold, Jade eating a studded leather banana, books with hair, hair thingie of Gor, Goribaldi.

First round: Jade 5.9, sleep 1.1.

Second round: Jade 5, Jenwa's thesis 1.1, Gore 1.

Third round: Jade 8.7, Gore 1.1.

\goto{Future Business}

M: to end the meeting. 7-3-8 +Spehn.

M: to throw pens at JM. (JM: "Pens or pants?") Passes small-smaller-0 +Spehn.

M: act like bananas. 7-0-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST, 05/12/1899.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
