\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/28/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 28, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: Jade! 8-4-3 +Spehn. AMU: "I'm afraid of Jade!"

\goto{Committee Reports}

M: gavel the camera. Fails 4-10-5 +Spehn.

People who are annoying: it's Laurie Ward's fault that we aren't getting paper statements- she didn't feel like getting them so she stopped all student group statements.

Pianocomm: Armenard finished his keyholder project.

Dead body alert! TZ had another victim.

M: condemn cuteness in the library. Chickened 4-5-18 +Spehn. JPW: "I'm scared of cuteness!" (Being cute.)

Same motion that does nothing chickens.

Pianocomm: we want freshman (that we'd like) now!

M: shut up! Chickens ?-12-2 +Spehn.

Pseudo-picniccomm: Jhawk saw Hal and and invited him to picnic- though it's unclear whether he will make it because of proximity to Mother's Day.

Stranglecomm: kill Martin for playing with slinky. WDS: "No, I'm not opposed, just slow." Passes 14-2-6 +Spehn.

M: commend Jenwa for remembering the books that she put there so that she wouldn't forget them. 6-4-? +Spehn. Chickens.

"Secret ninja books!" (Justin)

M: there's lots of old bananas in the world. Chickens.

\goto{New Business}

JPW: "I'll be old. Oh, wait, that's future business."

JWH: "But we can move to future business."

JPW (threatening tone): "No one has anything to say, right?"

\goto{Future Business}

JWH: The ASA meeting about our rooms (and additional rooms) happened- no progress- not getting any more space any time soon. "LSC sucks!"

Some motion.

M: there will always be bananas. 14-4-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
