\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/14/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 14, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding. SEF is the Pseudo-Onseck.

Minutes read.

M: to commend SEF as possessed by Natasha. 13-4-6 +Spehn.

\goto{Committee Reports}

Mobcomm: big new box of books- lots of books, multiple series and series names. Description of new books coming... rather lame. Correction: very lame.

Jourcomm: deadline was in March. People should submit to YN.

JPM: motion to modify the Jourcomm's job to pounding. Passes 11-4-2 +Spehn.

M: to put J's legs above his head. Fails, lack of second.

Picniccomm: will try to address envelopes after meeting and send out soon. M: to stonewall. Fails for lack of second.

Alohalenscom: pictures last week. There's a good one of YN in a passionate embrace of doorjamb. Discussion of prentices between JM and JFC. Y wants to censor part of her, JPW refuses.

M: to make Alohalenscomm to make part web accessible. JPM and JM.

M: to declare J Albanian. Passes 12-0-4 +Spehn.

M: to condemn Yevgenia. Ignored.

Bluebellcomm: will update bulletin board.

Pseudo-bluebellcomm: did same.

\goto{Old Business}

JFC older than he was last week.

JM said something long and convoluted.

\goto{New Business}

Kendall Square is showing X- Japanese version of expose on Schrodinger's cat.

Lots of fighting in corner between JPW and JPM.

Jake asks if they're playing rugby.

JM: "golfball basketball."

\goto{Future Business}

End of term coming.

M: there is no future, there is only Zuul. 16-1-3 +Spehn.

JM: "sometime in the next couple months Jen will get her degree."

M: sometime in the next couple of months Jen will eat a banana. Doesn't do much 9-6-8 +Spehn.

Jake Beal: within the next couple decades, an increase in books will make MITSFS fall through the floor.

YN seconded a comment of J's about bananas but doesn't remember what.

M: to give Jenwa bananas. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{SEF, Pseudo-Onseck}

\end{document}
