\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/24/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 24, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and
Pseudo-Skinner, presiding.  Ed Keyes is the turkey-stuffed Onseck.

Minutes read.

Motion: Condemn the minutes for not being properly typeset.  Voting
gives 1--0--0+Spehn.  The Pseudo-Skinner flips a coin to break the
tie, and the motion goes under the desk.

[John] ``We should have asked for a recount.''

% Just on a historical note, at this time the country was deep in the
% troubles surrounding the various recounts of the 2000 presidential
% race in Florida.  - Ed

A hand recount proceeds.  One absentee ballot is recorded for Spehn.
The motion passes 2--0--0+Spehn.

\goto{Committee Reports}

Pseudo-Dexmistress: Made a pink spine label for the Pinkdex.

Pianocomm: Joe has a real key now.

Mobcomm: Got a box of books.

Pianocomm: We are running out of keys.  The latest word is that the
doors will be fitted with new locks by mid-November.  Ummm...

A discussion of thought-reading locks and hypnosis (it will let you
in if you {\em think} it should...).

Our LPs are overflowing the new book shelf.

Mortcomm: L. Sprague de Camp died recently.

Pseudo-Jourcomm: {\em TZ} real soon now.

\goto{Old Business}

Ugly shelves are still with us.  Can we take photos of them to help
reunite them with the right-size shelf pieces?

More waiting on the Alumni Association.

We still need a tall person to put our sign back up.  There are some
remarks on the ``Jade Wang Memorial Dent'' in the door.

\goto{New Business}

We have a new computer, yay.  Ellen will soon give us a monitor to
match, hopefully.  Discussion of net connectivity.  Plans to have a
secure server in the Sachs powered by a prentice with a hand-crank.

Member checks out a book.  Aaron gets a key fine.

[Jamie] ``Let the minutes show he was very very naughty.''

Motion: Give Jamie a banana for his joke.  Chickens 4--0--4+Spehn.

The Columbia University Science Fiction Society will probably drop
by when they're in town for Arisia.  They warned us not to use nukes
in New Jersey because of the danger of horrible mutants.

Have we planned selling stuff at the cons yet?  Probably Boskone,
maybe Arisia.

\goto{Future Business}

Jamie tries to fake a bing, but doesn't fool John.

A call for future predictions.  John wagers all the lint in his navel
that in the year 2001 we will {\em not} be sending a fully sentient
space probe to Jupiter.

Motion: (John silently contemplates a banana.)  This action is seconded,
and voted upon.  Passes 3+the banana--John's treacherous foot--John's
other foot and hand+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1739 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
