\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/07/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 7, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: to embarrass the onseck. Passes.

\goto{Committee Reports}

Mobcomm: Space-Crime Continuum books are here.

Aloha Lenscomm: JFC took a picture of Ed. (It even includes the face.)

Pseudo-panthercomm: books got processed.

Pseudo-pianocomm: Stephanie is not lame!

LHE: we don't have a statement from February.

Pseudo-hasslecomm: Hasslecomm pile is overflowing.

Pseudo-mobcomm: we have decided to acquire some graphic novels- the Sandman comics.

Sitcomm: "Secret Agent Man" (TV so bad it hurts (TM)) got cancelled. Discussion of whether the show is better or not than a test pattern.

WDS: "Very, very poor man's James Bond."

JM: "I'd like the water shaken, not stirred."

\goto{Old Business}

None.

\goto{New Business}

Jen Chung, new keyholder, gets her pic taken.

Prefrosh are here.

JPW: "They are not as scary as frosh."

Someone was flaming about some parent commenting "It's good for the prefrosh to not be allowed off-campus, especially the girls."

\goto{Future Business}

Discussion of Ana- possibility to get her as prentice- she doesn't want to sink more hours into more activities she does Shakespeare Ensemble.

M: retroactively destroy Shakespeare. 8-2-0 +Spehn.

M: commend Jade for fantasizing out loud during business. 8-0-2 +Spehn.

M: get a banana to be a LHE. Fails for lack of second.

M: get banana to be skinner (after Jade). Chickens 4-2-6 +Spehn.

\goto{Time Warp to Committee Reports}

Sitcomm: JFC watched Hitchhiker's Guide to the Galaxy.

Moocomm: Princess Mononoke is showing at LSC on Saturday- translated by Neil Gaiman- very good movie.

\goto{Time Warp to Old Business}

Can someone get a permanent membership on layaway plan?

Can someone get a mortgage on a permanent membership?

JM: "Some of the stories in the old Twilight Zine are actually pretty good."

\goto{Time Warp to Future Business}

M: bananas in the world- chickens.

M: replace JFC's middle name with a banana. 7-0-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
