\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/05/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 5, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner who turned in her thesis, presiding. JFC is the Pseudo-Onseck. ("Will you onseck me, John?")

Minutes read.

M: condemn pseudo-onseck for not knowing difference between "cuteness" and "antlers."

\goto{Committee Reports}

Pseudo-hasslecomm: 2/3 of Hasslecomm is lame, 1/3 is lame but makes up for it.

Auxiliary-hasslecomm: WDS did 8 or 9 books. Discussion of reassigning members.

Pseudo-picniccomm: if you have a car, sign up. Discussion of cars causing rain.

Panthercomm: we got a William Buckley Jr. books.

M: gavel WB Jr. 2-1-1 +Spehn.

Minicult: bananas barraging Miami city hall.

Pseudo-Jourcomm: YN threatens TZ next week.

\goto{Old Business}

Voyager was lame, with an old character.

The skinner is the youngest person here.

Old to-do list in JM's handwriting in skinner drawer. E.g. "Create rites," learn to access endowment, "try to get space," "alum mailing," "t-shirts."

\goto{New Business}

New space chart with flatter curve.

5/5/00 happened, but the sun rose in the east today.

WDS is processing new books.

\goto{Future Business}

Jay and Jade are/will mud wrestle.

Pseudo-pianocomm: active. New prentice Mery might get a key RSN.

M: banana. 7-0-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17-20something SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
