\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/14/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 14, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, Pseudo-President and
Skinner, presiding. Natasha Olchanski is the Onseck.

Minutes read.

M: minutes well-nigh unto dead. Chickens -2-0-1 +Spehn.

\goto{Committee Reports}

Moocomm: Boston area won't be able to see the IMAX version of Fantasia because Disney is being extortionist.

"No, Steve Jobs is not starring in the movie."

Motion to laugh at JM. Chickens 0-0-0 +Spehn.

Being a borg is not in character for Jamie.

Mobcomm: more books- Star Chamber is still lame.

Natashacomm: Natasha claims to be sick, but I don't believe her.

Move that Natasha fakes it at Jade's request. Chickens 0-0-1 +Spehn.

Jade: "If you're stripping, I'm leaving."

\goto{Old Business}

Had another theft.

Deposited more money.

\goto{New Business}

John "Acts of the Apostles" Sundman is coming to the Coop to do something related to his book.

JPW: let's destroy one of the books (Acts of the Apostles). JFC is slowly crushing books to coal.

JFC chases Jade off by taking off his socks.

M: to fold Acts of the Apostles into origami banana. Passes 3-lavender-1 +Spehn.

\goto{Future Business}

Meeting adjourned by skinnerial decree? No, banana motion.

\vspace{12pt}

\noindent
Meeting adjourned, 17010 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
