\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/28/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS meeting minutes

Friday, January 28, 2000

\end{center}

\vskip 12pt

MITSFS meeting called to order, 17:00 SST, January 28, 2000

Aaron Ucko, pseudo-skinner, presiding (``Where's our Jenwa?'' --- JM)

John Carr, pseudo-onseck (what's Natasha's excuse this week?)

\vskip 12pt

Motion: dream of electric cattle prods [JH].  Fails \hbox{6-8-4+Spehn}.
Jamie exclaims ``Dick Sucks!''

\vskip 12pt

\centerline{Committee Reports}

Motion to rename ``Jourcomm'' to ``Jourcomm Officer'' fails \hbox{7-15-Spehn}.

Panthercomm [JH] requests that review books get tags.  By this he means that
star chamber members should learn to recognize review books.

Mobcomm [JFC]: no new books.

Mopcomm [JFC]: the muddy floor is now dirty, a great improvement.
(``The library was being terraformed'' says Jamie.)

Officecomm [AMU]: We're probably not getting more space.

Jourcomm [YAN]: posters exist, email sent.
The posters feature a 13-fingered motie.
Pseudo-jourcomm: submit!
Jourcomm: especially if you can draw.

Pseudo-pianocomm: armenard is lame.  Justin is lame.

Pseudo-analogcomm: new hours request in {\it new} envelope.

{\bf BING!}

\vskip 12pt

\centerline{Old Business}

IAP happened.  The MITSFS IAP guide entry and marathon slide did not happen.
Natasha didn't get a shelf.  The star chamber is lame.

Locus acked our life subscription.

AMU is lame.

T.C. Skinner is not dead.  Yet.

\vskip 12pt

Usual motions, etc.

\centerline{New Business}

A semi-large but sub-Shultz donation is coming.
% JM: actual name Kravitz.  MITSFS name of the deceased was Shultz.

Motion: no new business.  Passes \hbox{8-1-5+Spehn}.  In spite of the
motion, the meeting continues with more new business.

The February {\it Asimov's} has a cute story about a Harvard person
and a redneck Cthulhu cult.

The Fetish Flea Fair (?) is tomorrow.
Yevgeniya says ``great minds think in parallel gutters.''

``John Carr is turning into Sam Hartman'' --- JH

``Some day we'll have a skinner back...'' --- JM

Motion: ``this picture'' --- JPM.  Passes \hbox{12-5-10+Spehn}.
The picture contained a banana so...

\vskip 12pt

%\centerline{Future Business}

Meeting adjourned 17:35 SST.

\end{document}
