\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/3/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS meeting minutes

Friday, March 3, 2000

\end{center}

\vskip 12pt

MITSFS meeting called to order, 17:00 SST, March 3, 2000

Jenwa Hsung, President and Skinner, presiding

John Carr, pseudo-Onseck (Natasha claims to be away for the weekend)

\vskip 12pt

The minutes of the previous meeting were read.  Towards the end, a
copy of {\it Editorial Humor} landed on the minutes.

Motion: approve minutes as fluttering copies of {\it Editorial Humor}.
Fails \hbox{6-13-Spehn}.

\vskip 12pt

\centerline{Committee Reports}

Walletcomm[WDC]: Bill Starr's wallet is full of cruft.

Theftcomm[AMU]: New ``What's New'' poster is going up on our bulletin board.

Jadecomm[JFC]: Jade went pant...grunt...wheeze this week.  There is a new
shelf in Damnation Alley.

Natashacomm[JFC]: Natasha is away for the weekend.
JM: We expect a full, accurate, {\it juicy} report.  Juicy is more
important than accurate.

Jourcomm[YN]: Submit work for TZ by end of March if you promised, or even
if you didn't promise, and especially if you can draw.  Yevgeniya will draw
if necessary to fill in space.  Why should we contribute then?  Because she
will draw badly.
JM: Put recent minutes in TZ.
JFC: How about this meeting's minutes?
JM: Say really funny things.

%{\bf BING!}

\vskip 12pt

\centerline{Old Business}

\vskip 12pt

Old donations still need to be processed: the Shultz donation (20 boxes),
the Sprague donation (6), and the Tuttle donation (19 boxes).  Some of these
have been partially cataloged.

Jade becomes older next week.  Remember to embarass her.  Maybe buy
her a present.  Is she 22?  Probably not.  Is Natasha 22?  Maybe.
Natashacomm votes no but isn't sure.

Motion: censure Natashacomm for not knowing how old Natasha is.
Passes \hbox{12-1-2+Spehn}.

Usual motion.  Usual result.  What about the usual debate?

\vskip 12pt

\centerline{New Business}

A wave of emptiness that had been moving around the P's is damping
out.  Some foreign magazines have been boxed and a new wave of
emptiness will be launched as the vacant shelf is allocated to store
paperbacks.  (Should we resurrect the Committee to Overdamp the New
Wave?)  The P's have been decompressed, and when the wave dies out
there will be 6.3'' of empty space per three shelves.  This should
last a year.

Connie Willis and another are doing a science fiction reading at MIT
on Monday.  Discussion follows about whether she is good, and how popular
she is, and someone wonders whatever happened to Connie Hirsch and whether
she is popular.

JM: Don't let Connie Willis sign anything.  Why not?  Because then the
book would be valuable and we would have to move it into Special Reserve.

There is discussion about {\it Ashes Of Victory}.  Jhawk has a copy, but
JFC can't remember if it is a MITSFS copy or not.

\vskip 12pt

\centerline{Future Business}

We didn't get any space in rerooming.  There is a small chance that we
might get some of LSC's space.

A moment of silence drags on.

Motion: make something happen.  Chickens \hbox{0-1-2+Spehn}.

JM: Damnation Alley will be respaced.

Motion: Strangle Marty with a banana.  Chickens \hbox{2-0-3+Spehn}.

Miller Motion.  Fails!  {\bf BING!}

Miller Motion.  Passes! {\bf BING!}

Meeting adjourned 17:30 SST.

\end{document}
