\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/07/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 7, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  AMU is the Pseudo-Onseck.

Minutes read.

M: approve minutes as being louder than usual. Passes.

\goto{Committee Reports}

Pseudo-Dexmistress: library is full.

Pseudo-Analogcomm: IAP hours exist.

Pseudo-Theftcomm: Theftcomm is lame.

Star Chamber should get new shelves.

Mobcomm not planning to curtail number of book purchases.

\goto{Old Business}
Do we have IAP MITSFS activities? No.

Prisoner marathon this weekend.

WDS has weird time schedule sense? Slept 16 hours last night. "Don't mix up the medications." "Let's mix it with walnuts and poison them both."

Natashacomm reports.

JFC: "Not even clothing can stop me!"

"The skinner may already be a winner!"

\goto{New Business}

New year: digits rolled over.

Millennium Pops: we're using non-Y2K compliant computers, but nothing much happened.

At this point Onseck is confused.

\goto{Future Business}

M: to get stung by a banana. Fails 3-4-0 +Spehn.

M: to have more creative banana motions in the future. Passes 9-0-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{AMU, Pseudo-Onseck}

\end{document}
