\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/1/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 1, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1715 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the very punctual Onseck.

Minutes read.

\bing Jade bings for no reason.  Maybe she's celebrating the minutes.

Motion: Commend the minutes for being worth celebrating.  Fails
7--3--3+Spehn.

Discussion of Jade's shirt and shirt-colored flesh.

\goto{Committee Reports}

Jourcomm: Maybe during finals or IAP.  Threats to John and Jayhawk.

Motion: Have the Onseck record that as ``{\em TZ} RSN''.  Passes
7--squeal--foot+Spehn.

Theftcomm: New bulletin board, yay.

There are calls for taking over the walls of the Infinite Corridor.

Randomcomm: Jumping Jupiter gives you the best of classic SF with
surprising twists... ummm.  Exploiting dead authors.

Motion: Mobcomm must buy everything.  Fails by Skinnerial decree.

It is reported that someone wrote a prequel to {\em Hamlet}.

Pseudo-Mobcomm: Someone offered us books for services unknown.  Sounds
cool but suspicious.

Is it legal to unleash someone's creativity in public?

Bluebellcomm: Eight down, eight hundred to go.

Pseudo-Hasslecomm: Seven overflow boxes now.  Discussion of Schultz
donation.

\goto{New Business}

New business is more interesting.  It is argued that it should be at
the end, like dessert.  The Skinner is not willing to wait that long.
``Oooh, shiny thing!''

Motion: Albanian Malcolm for his horrible ``dessert island'' pun.
Passes ton--pound--ounce+Spehn.

Jade crushes paper with the gavel.

The Shinner plans her rant for {\em TZ}.  It is proposed to tickle
her and publish her squeals.  Skinner refrigerator poetry.

John doesn't like the new cat calendar.  Jade does.

Motion: The Skinner always wins.  Passes by Skinnerial decree.

New office supplies, yay.

John moves a Panthercomm box without defying the laws of physics.

We need to gently tear the modem out of the old computer and gently
shove it into the new one.

Jamie is hypnotized by a flyer from a psychoanalytic organization.

\goto{Old Business}

Ugly shelves are still here.  Pictures of them have been taken.

LOGLA...  (The Algol backwards, since of course we're going from
New Business to Old Business.)

Our proposed {\em Tech} ad has been criticized for every aspect
except possibly the white space.

Jade is mad at the library people.

\goto{Future Business}

[John] ``Winter is coming.''  Finals too.  John doesn't even read
G.R.R. Martin, though.  Many conversations break out simultaneously.

Motion: Make the Onseck multitask.  Passes 11--1--3+Spehn.

Motion: Split the Onseck's brain along the corpus callosum.  Passes
13--1--0+Spehn ``even though it's complete bullshit.''

``Life is like a box of Onsecks.''  Reference to pearls from a
previous meeting.

The gavel is reported as being really crusty, probably from all of
the old Skinner souls in there.  Some of them are whiny.  Jade may
just be hearing voices.  Lots of people start speaking in echoing
voices to contribute to the Skinner's growing insanity.

Motion: In the future the Skinner will be tickled.  Fails by
Skinnerial decree.

Motion: Bananas, bananas, bananas!

Motion: Lame-ass banana motion!

Horrible singing ensues, and all pending motions pass to make it
stop.

\vspace{12pt}

\noindent
Meeting adjourned, 1747 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
