\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/30/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS meeting minutes

Friday, June 30, 2000

\end{center}

\vskip 12pt

MITSFS meeting called to order, 17:00 SST, June 30, 2000

Jenwa Hsung, skinner, presiding (and showing some skin)

John Carr, ex-pseudo-onseck (Merry is still not)

{\bf BING!}

\vskip 12pt

\centerline{{\bf Committee Reports}}

\vskip 12pt

Bill says something clever, or a motion is made to have Bill say
something clever.  Whatever it was, the vote was \hbox{5-0-Spehn}.

Mobcomm[JFC/WDS]: Mobcomm got 32 pounds of new books, but WDS did even
better with five bags of books costing over \$400.  New book shelf is
overflowing.

Panthercomm: The new book shelf will get emptier soon.

\font\sym=msam10

{\sym "} (The committee that dares not speak its name)[JM]: RSN

Dexmistress[JM]: Inventory still July 22.  There are two twinkie-weddings
that weekend.  But the people getting married didn't remember, so they forgot
to tell Jenwa.

Moocomm[WDS]: Moose and squirrel movie opened today.

Moocomm$_2$[JWH]: Titan AE was OK.

Pseudo-jourcomm[JM]: Reading lots of old TZ and has ideas.  40 years of TZ!
That's about one a year on average. But it's supposed to be quarterly...
We got a letter from The Alpert.  Some people didn't get TZ 42.
We could reprint it but it has an editorial flaming Jamie for not ranting.

Pseudo-gapdex[JFC/JM]: Dexmistress hasn't processed gapdex changes.  Will
try to do them before inventory.

Pseudo-gapdex$_2$[WDS]: Our {\it Omega Sub} collection is complete!

Dexmistress: Too late for new dexes; will wait until RO.  There is a long
discussion of the merits of three hole prepunched paper vs. hole punches.


\vskip 12pt

\centerline{{\bf Old Business}}

\vskip 12pt

WDS emailed some guy who used to hang out at MITSFS circa 1961.

Average age of members in the library is old.

How old is modern science fiction?  Is the library half as old?

[WDS] Surprise!  We have both editions of  {\it Marooned} by Caidin.

[JM] According to old members, Skinner's recollection of strict
parlimentary procedure and the repeating movie are fantastic.
``Recollections of old skinners are not to be trusted,''  says The Morris.

\vskip 12pt

\centerline{{\bf New Business}}

\vskip 12pt

{\sym "}: Jamie is updating the alumni association's list, mostly by deleting members.

[JM/JFC]: We have more bindable magazines than people who were not at
the libcomm debriefing thought.  They are in locked drawers.  Some of
them are too old to bind.  We have extra money, so we should bind bindable
magazines.  In some cases we will gain space by doing so (if we displace
loose magazines in Damnation Alley).

Motion[WDS]: Bind our money.  \hbox{7-0-Spehn}.


\vskip 12pt

\centerline{{\bf Future Business}}

\vskip 12pt

We will eat soon.

WDS: Anybody want a soon-to-expire T pass?  Discussion follows of using
dollar coins to pay fares, and whether Congress showed unprecedented
clue in mandating that the new coin be compatible with the old one, or
whether they just got lobbied in a way that turned out to be good.

Motion: Lobby congress to send MITSFS a lot of new almost-banana-colored
dollar coins for testing.  Passes.

\vskip 12pt

Meeting adjourned 17:20 SST.

\end{document}
