\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/23/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS meeting minutes

Friday, June 23, 2000

\end{center}

\vskip 12pt

MITSFS meeting called to order, 17:00 SST, June 23, 2000

Jenwa Hsung, skinner, presiding (``I'm not president.  Yes!'')

John Carr, pseudo-onseck (Merry is not today)

{\bf BING!}

\vskip 12pt

Motion to commend the minutes as legible and typed.  No second.

Motion to fail the motion for lack of a second.  \hbox{9-2-7+Spehn}?
``Wrong with all three numbers.''

Motion to commend the skinner for not being able to count.  \hbox{5-?-?+Spehn}.

\vskip 12pt

\goto{Committee Reports}

\vskip 12pt

Mobcomm[JFC]: 32 pounds of books coming.  Over \$300.  LHE can't sign checks.

Dexmistress[JM]: Inventory July 22 at noon.  JFC can't make it then;
he will be busy holding library hours.  Use the secret knock to enter.

Pseudo-sitcomm: Justin placed an agent in the cable TV networks.
Starz wants to win awards so they are making movies.

Moocomm: Chicken run started.  Cute.  Too many small children.

Jadecomm[JPM]: Chinese bureaucracy is like something out of Brazil.

Pianocomm: Two new prentices.  Joe Foley and Susan Born.

\vskip 12pt

\goto{Old Business}

\vskip 12pt

psuedo-hasslecomm[JFC]: usual.

pseudo-jourcomm[JPM]: usual.

Skinner sent us email.  But the skinner is here.  Not the skinner,
The Skinner.   He says MITSFS used to strictly follow Robert's Rules
of Order.  What are they?  State transition matrix for meetings.
``No, that's Rolemaster rules of order.  Roll on objection table.''
MITSFS used to show {\it The Day the Earth Stood Still} year after year.

\vskip 12pt

\goto{New Business}

\vskip 12pt

Motion[Y]: When onseck is present and non-functional, call her the offseck.
Passes \hbox{13-10-2+Spehn}.

Motion: Raise entropy level.  No second.

Motion: Commend laws of thermodynamics.  \hbox{9-2-6+Spehn}.

Motion: Say ``hi'' to new person.  \hbox{19-0-5+Spehn}.  But she has already left the room.

A banana motion fails.

Jenwa says ``This is my worst meeting ever.''

Motion to give Jenwa a banana.  \hbox{6-7-5+Spehn}

\vskip 12pt

\goto{Future Business}

In the future we will get endowment fund statements mailed to us again.

In the future we will have a skinner who can count.  Eventually.
Given infinite time to find one.

Motion: train a voice in Jenwa's head to do mathematics.
\hbox{10-8-7+Spehn}

Ellen Kranzer's friend may get a permanent membership.

Future freshmen are here.  What does CRSI mean?

Motion: Embed RSI people in concrete.  \hbox{9-6-3+Spehn}

Jenwa drops the gavel on her foot.  Unfortunately, she isn't wearing
her new steel-toed boots.  Is the gavel upset?

Motion: Drop the gavel on Jamie to appease it.  \hbox{17-1-4+Spehn}

\vskip 12pt

\goto{Hypothetical Business}

\vskip 12pt

Jenwa will miss ``Convergence'' with Gaiman as GOH.

\vskip 12pt

$\ldots$ The pseudo-onseck is confused.  Things may have happened. $\ldots$

\vskip 12pt

Miller motion!  Fails!

Miller motion!  \hbox{11-5-4+Spehn}

\vskip 12pt

Meeting adjourned 17:45 SST.

\end
