\centerline{MITSFS meeting minutes}
\centerline{December 15, 2000}

\vskip 12 pt

MITSFS meeting called to order, really late 17:00 SST, December 15, 2000

Jade Wang, President and Skinner (``We are all grateful.  I lie sometimes.'')

John Carr, re-pseudo-onseck (``I didn't say that; let's wait for Ed.'')

\vskip 12 pt
{\bf CLANK!}
\vskip 12 pt


The minutes of the previous meeting were read.

There is a discussion of inventorying Jade's organs, at least the
external ones.

Motion to commend the minutes as an exquisite mix of Ed and
John passes \hbox{4-0-1+Spehn}.

\vskip 12pt

{\bf BING!}
\vskip 12 pt

\centerline{\bf Committee Reports}

\vskip 12pt

Jade thrusts the gavel between her legs.  Jamie is disturbed.

Mobcomm$_1$[JFC]: We have a few new hardcovers.

Mobcomm$_2$[JFC]: Mobcomm run RSN.

Skinner report: Jade will do {\it anything} after next Monday.
JFC calls Tuesday.  ({\it pseudo-onseck log, December 19 2000: Tuesday came
and Jade refused.})

%\font\sym=msam10
%{\sym "} 

\vskip 12pt

{\bf BING!}
\vskip 12 pt

\centerline{\bf Old Business}

\vskip 12pt

JFC: I see shelves.

JM: Rearrangement soon.  He has a workaround.  Some shelf holders
will be discarded.

Jade's chair is shedding.

Jade's hair thing is irresistable.

Motion to commend Bill for avoiding a bad pun passes, \hbox{6-0-Spehn}.

\vskip 12pt

{\bf BING!}
\vskip 12 pt

\centerline{\bf New Business}

\vskip 12pt

There is a new pile of about 450 donated books awaiting Star Chamber
processing before it hits panthercomm.  Somehow, this leads to a
discussion about when fines increased from 10 to 25 cents per book per
day.  JM digs into the VGG drawer to investigate.

\vskip 12pt

{\bf BING!}
\vskip 12 pt

\centerline{\bf Future Business}

\vskip 12pt

Alohalenscomm will be taking pictures of books.

WDS activates the device and cleans up the mess Jade made on the floor.

Motion: Comdemn skinner for not being housebroken.  Passes \hbox{5-0-Spehn}.
The inverse skinner rule is applied to negate the word ``not.''

Term over, people gone soon.

Will we have meetings the next two weeks?  Probably.

The skinner will, in the future, have enough life force to balance one
foot on the other.

JFC tells the story of a drug bust caused by the inability of 
Massachusetts police to distinguish a gun and a banana.

Motion to pay off the CPs so they don't come after us for our bananas
fails \hbox{3-4-1+Spehn}.

Jade forgot how to do homogeneous and particular solutions of differential
equations.  ``No term is complete until I've been laughed at by a TA.''

The pseudo-onseck's finger is sore.

Miller motion!  Failed by Bill before the vote.  Failed by the skinner
after the vote, \hbox{2-3-2+Spehn}.

Miller motion! Passes \hbox{a bunch-0-1+Spehn}.

\vskip 12pt

Meeting adjourned 18:15 SST (18:15 EST)

\vskip 1in

\centerline{Respectfully submitted,}
\centerline{John Carr, re-pseudo-onseck}

\end
