\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/11/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 11, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: approve last week's minutes as banana colored. Fails 3-9-4 +Spehn.

\goto{Committee Reports}

Mobcomm: getting new books in time to fill new bookshelf coming soon.

Jourcomm: posters exist. Lots of hypothetical submissions, but no actual ones.

M: commend Yevgenia for working on peapole she has. 12-0-1 +Spehn.

Bingcomm: skinner is unsatisfied by quality of bings.

Pseudo-Hasslecomm: the hasslecomm shelf continues to fill up.

\goto{Old Business}

Phil Starr is not around.

The term is not as new as it was last week.

Jade is getting older.

The usual happens.

\goto{New Business}

Motion to condemn the skinner for holding back her powers. Passes 13-1-5 +Spehn.

We are getting a subscription to "Absolute Magnitude."

Motion to eliminate office of the skinner fails by skinnerial decree.

Motion to commend John for knowing the difference between electricity, magnetism, and gravity. Passes 8-5-1 +Spehn.

\goto{Future Business}

Jamie has suspicious documents.

The world will end.

We are special.

Motion to take over the male lavatory. Passes unanimously except for Spehn.

Motion to commend J for knowing that everything particular is bad. Passes 4-1-1 +Spehn.

Motion to give Lissa, Yevgenia, and Armenard a banana. Fails 4-0-3 +Spehn.

Miller motion. Fails.

Second Miller motion. Chickens 7-0-14 +Spehn.

J makes more banana motions than all the rest of MITSFS put together. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
