\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 03/24/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 24, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: commend minutes for being carefully observed. Fails, lack of second. (Some people are actually doing work! Gasp!)

\goto{Committee Reports}

Pseudo-panthercomm: has a lot of work.

Mobcomm: got 3 new hardcovers.

Pseudo-hasslecomm: has a lot of work. (Only a few hundred books to be covered!)

LHE: phone bill problem is fixed. Yay! Several people to deal with changed- the current one seems to suck less than some of the others. Some books' problems got fixed.

M: commend LHE and Onseck for having their minds in the sewer. Passes unanimously.

Jadecomm: Jade is wearing a nice clear plastic barrette.

Natashacomm: RSN.

M: have Natasha give an interim report. Passes.

Onseck: "I became a US citizen yesterday." (Commended for not being a communist anymore.)

JM: "Are you a capitalist?" NO: "I buy things..." JM: "Do you use a credit card?" NO: "Yes..." JM: "Extra capitalist points for credit cards."

JFC: "Even though jhawk is in Australia he is bidding for books."

M: Something about bananas. Chickens.

\goto{Old Business}

M: condemn skinner for lying. Fails by skinnerial decree.

Onseck: "No, I'm gonna lie about that."

M: condemn someone for aiding and abetting space crunch in the library.

Jade: "Never fly to Chicago." Why? "Because you can never get there."

\goto{New Business}

Jade: "Let's paint the checkbook invisible." (And the checks clear.) Passes.

JM: "Any progress with prentices?" JWH: "Unclear."

Maybe we should give Stephanie a different project.

MITSFS got a letter: "Isn't it time you found a job you love" from the Department of Retardation.

M: to hurry the future. Chickens 2-0-5 +Spehn.

\goto{Future Business}

M: to banana banana banana.

M: to commend Jade and Jay for canceling each other out.

M: something about Jay, Jade, and bananas. Passes unanimously.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
