\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 03/10/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 10, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

No motions concerning minutes. Chickens.

Apathycomm: yay.

M: approve last week's minutes as pleasing to Onseck by own admission. Passes.

\goto{Committee Reports}

Jadecomm: "Jade is allergic to soft liquor; she should be tested for hard liquor." (Jay)

JM: "A hangover is not technically an allergic reaction."

M: sing happy birthday to Jenwa. Chickens.

Pseudo-hasslecomm: Hasslecomm shelf is about to overflow.

M: for everyone to stare as Stephany. Passes.

Natashacomm: still working on the "juicy" report. Mission to Mars sucks.

\goto{Old Business}

Talk about how to film the building of a pyramid.

M: give Jade the power to do that. Passes 9-8-5 +Spehn.

JM: "She could wake up and discover that she put a pyramid on the great dome."

WDS: Secret Agent Man really sucked.

JFC: Empty shelfwave is dying out.

JM: processed some of some donation.

Usual motion, usual result, usual apathy.

\goto{New Business}

Yevgenia arrives.

Jade: "We should kill her for being late."

M: regurgitate what's left of Aaron into a banana. Chickens.

JFC: we have a special shelf for tiny books, like pocket dictionary and bibles.

\goto{Future Business}

We have four unlame prentices- wow!

Yevgenia should do some library work in addition to Jourcomm. Yevgenia: "I could bring a gun and kidnap Jenwa."

Pseudo-picniccomm: do we have a Picniccomm? Oops...

M: serve lots of bananas at picnic. Chickens 6-0-7 +Spehn.

M: get Jade smashed on banana vodka. 22-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
