\ifx\documentstyle\thisMacroOughtNotBeDefined
\else
  \immediate\write16{}
  \immediate\write16{ This is a plain TeX document, not LaTeX; process with}
  \immediate\write16{ tex \jobname}
  \batchmode \makeatletter @@end
\fi


\centerline{MITSFS meeting minutes}
\centerline{Friday, June 16, 2000}

\vskip 12 pt

MITSFS meeting called to order, 17:00 SST, June 16, 2000

Jamie Morris attempts to start the meeting but abdicates to...

Stephanie Fried, LHE and pseudo-skinner presiding (``what he said'')

John Carr, pseudo-onseck (still no joy in Cambridge)

{\bf BING!}

\vskip 12pt

The minutes are read.  ({\it Jamie prompts the pseudo-skinner.})
Any motions concerning the minutes?

Commend the minutes as legible.  Chickens \hbox{4-0-4+Spehn}.
(``I don't understand Spehn,'' the pseudo-skinner complains.
Finger motion.  Time warp to explain.)

{\bf BING!}

Motion: do time warp again.

\vskip 12pt

\centerline{Committee Reports}

\vskip 12pt

Mobcomm[JFC]: Big pile of books probably waiting for us in Northampton.

Dexmistress[JM]: Inventory date soon.  July 22 or July 29?
Does it conflict with a game?  Combine guild with inventory?
Use inventory as the combat mechanic.

Pseudo-libcomm[JM]: Found old lists of magazines.

Pseudo-VGG[JM]: Found old VGG stuff.

{\bf BING!}

\vskip 12pt

\centerline{Old Business}

\vskip 12pt

Judy Passman (sp?), ex-skinner c. 1982, sent us email.

Lily Edgerton, onseck c. 1952, sent us email.
``They made me an officer because I was the only coed member.''

In the mid-1960's women were not allowed in the MITSFS after midnight
(or anywhere else in Walker) but we got the policy changed.

In the 1960s most students were too busy protesting Vietnam to ask for
Finboard money, so we got lots of money and bought lots of books.

Motion: Invade a 3$^{\rm rd}$ world country so we can get more money.
Chickens \hbox{5-3-5+Spehn}.

Jamie found lots of old records, including page 1 of the money book
(c.~1951).

Until c.~1979 Richard M. Stallman was a keyholder.  Explanation
follows of who RMS is.

({\it Jamie prompts the pseudo-skinner about Algol.})

\vskip 12pt

\centerline{New Business}

\vskip 12pt

eichin is going to get a life or permanent membership, as is cwitty,
so we need to figure out what a permanent membership includes.
Discussion about evading the photo requirement.

Motion: say ``hi'' to new person.  Chickens \hbox{2-0-4+Spehn}.

The pseudo-skinner doesn't like the gavel's tone.  It's a flat A.

A banana motion fails.

Motion: commend the pseudo-skinner for remembering three numbers at
a time.  Passes \hbox{8-0-Spehn}.

\vskip 12pt

\centerline{Future Business}

A bill in the legislature would require the Massachusetts Highway
Department to use ``Liquid Emitting Diodes'' instead of incandescent
lamps.

Motion: install lights that emit banana juice at pedestrians.
Passes \hbox{6-0-2+Spehn}.

\vskip 12pt

Meeting adjourned 17:24 SST.

\end
