\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/2/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS meeting minutes

Friday, June 2, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 17:00 SST, June 2, 2000

Jamie Morris, chancellor and pseudo-skinner, presiding

John Carr, pseudo-onseck (we are merriless this week)

{\bf BING!}

Jenwa Hsung, skinner, takes over!

{\bf BING!}

\vskip 12pt

The minutes of the previous meeting were read.  A motion to deploy
600 eggs to defend our minutes passed, 4-2-2+Spehn.

{\bf BING!}

\vskip 12pt

\centerline{Committee Reports}

Pseudo-VGG[JFC]: A former member paid a fine for a book he lost in 1981.

Dexmistress[JM]: Dexmaster is improving daily.

Tablecomm[Whitfield Diffie]: Table committee is alive and well.
Discussion follows about why we don't want to know what this means,
but a search of the lore of the MITSFS reveals its meaning.

Pseudo-hasslecomm[JFC]: (Points to the stack of boxes.) Need I say more?

%{\bf BING!}

\vskip 12pt

\centerline{Old Business}

\vskip 12pt

Whitfield Diffie, former member and the first half of Diffie-Helman,
is here.

[JWH] ``Cool''

\vskip 12pt

\centerline{New Business}

[JM] Locks are still coming.  Jenwa talked to omnilock people; the model
we want will cost only a few hundred dollars more than the model CAC wants.
Locks 2000.  Y (Malcolm Skerry) makes a pun about ``bagel 2000'', that is
apparently seconded and approved.

Y is revealed to be an ex-vice.

[Y] Is it possible that Battlefield: Earth will be the worst movie of all time?

[JM] It's not a good cult movie like Planet 9 (sic).

Jenwa just graduated.

\vskip 12pt

\centerline{Future Business}

Marcus is coming back and may be a keyholder.

Motion: return to committee reports.  Passes 5-2-Spehn.

Jourcomm: Marcus and Y buy TZs!  So does Whitfield Diffie!

Bluebellcomm [ED]: Covered a lot of books, to circulate June 31.

Motion: go back to banana section of minutes.  Passes 4-0-1+Spehn.

Meeting adjourned 17:30 SST.

\end{document}

