\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 03/17/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 17, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: minutes be enshrined on a video with a pyramid. Passes 11-4-1 +Spehn.

\goto{Committee Reports}

Moocomm: JFC: Mission to Mars really really sucked. Someone: "you fool!"

Pseudo-hasslecomm:

Pianocomm: JWH: "Jen got her key." J: "Jen Murphy finally got her key. It's about time." Someone: "Not another J!" J: "There can be only one." JWH: "She is too young to be Chamber." Jhawk: "Only young innocent virgins can become skinner."

Still no Picniccomm yet.

Jade was tested for hard liquor allergy. Conclusion: no allergies found.

\goto{Old Business}

Commend PBS for actually building a pyramid.

Usual result.

\goto{New Business}

M: get Namco to add to the series of fighting games Soul (Edge, Caliber) a final one: "Soul Gavel." Passes 9-4-5 +Spehn.

M: minute of silence for "Science Fiction Age." 10 seconds of silence. Jhawk's watch was reset, but people failed to shut up.

February Locus still not found.

At a rental: movie "Love, Amoeba Style, Part A" marked "untranslated Chinese" but actually has English subtitles.

Discussion of Love, Amoeba-style.

\goto{Future Business}

Yevgenia volunteers to be Picniccomm. :)

Some motion about Yevgenia, Jhawk, and bananas passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
