\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 04/21/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 21, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: commend minutes for being 18 centuries old. 8-4-2 +Spehn.

\goto{Committee Reports}

JFC: Mr. Gorey died last week at 75. Heart attack in sleep. (Author of calendar)

Discussion of various calendars. Jewish, Mayan, etc.- which should we date the minutes in?

Picniccomm: invitations have been sent. jhawk is going to had Hal an invite personally at a con somewhere.

Jourcomm: (Essentially "please contribute")

Theftcomm: new shipment has arrived.

Discussion is too confusing for onseck.

Note: Jade is willing to be radio controlled. People discuss if she has a sticker.

Moneycomm: we have some.

Bananacomm: there are lots of bananas in the world. 6-7-18 +Spehn. "Small things to small things."

Pianocomm: we have a new keyholder, Deepak. Initials Dork (DRK)- middle name Roderick. His own fault.

Discussion of donations.

JFC: is "many" less than "lots?" 8 is fewer, but 12 items are less.

Justin was teaching Jade how to count.

Pianocomm: 3 new keyholders this month, but they're all old. Someone points out a freshman. JPW: "You! We want you now!"

\goto{Old Business}

Discussion of "budding" vs. "butting."

The gorilla who knew sign language died in the past week.

M: make a voodoo doll out of the gavel. 5-7-11 +Spehn.

\goto{New Business}

JM: young and fresh is not the same as yummy.

JWH: "And we all know how Jade likes vegetables."

\goto{Future Business}

M: killer banana. 15-8-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
