\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/25/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 25, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: commend minutes for saying "the meeting got back on crack." Passes.

\goto{Committee Reports}

Jadecomm: Jade is wearing a nice new shiny blue plastic... hairthingie.

MITSFScomm: Where is everyone? It's raining- they probably melted.

Crackcomm: apologies for the quality of the last shipment.

M: not to accept apologies. Chickens.

Some motion passes 10-0-0 +Spehn. (Mandatory practice in binging to weed out inappropriate prentices.)

Jourcomm: Zine should happen this term.

M: to not have Yevgenia try to die anytime soon. 10-0-9 +Spehn. (As long as she doesn't do it in the library and spurt blood.)

M: say hi to Natasha's brother. Passes.

M: commend Yevgenia for training AMU well. Chickens.

Natasha: "I know something Natashacomm doesn't know- my birthday is today."

M: ritually embarrass Onseck. 19-4-1 +Spehn. Happy birthday song duly sung loudly and almost out of key.

\goto{Old Business}

JFC is old. Chickens 0-0-5 +Spehn.

People talk about age. There are people older than Jay.

M: condemn JM for arranging books so that the Gor books are only partially chained up. Passes.

JFC: "Free John Norman!"

\goto{New Business}

Wave of emptiness is going around.

"Remain calm and soon there will be lemon scented napkins."

\goto{Future Business}

M: to prevent JFC from ever taking off his shoes in a meeting. Passes.

JFC: "But my socks have the strength of ten."

Do they read? No, they reek.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
