\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/19/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 19, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, Pseudo-Skinner and Thunderbunny, presiding.  Natasha Olchanski is the Pseudo-Onseck.

Minutes read.

M: reading quiescent. Chickens 4-4-6 +Spehn.

M: reading not as good as the previous onseck. Something.

\goto{Committee Reports}

Jourcomm: holds up a new TZ. M: oooh. Passes. Discussion of TZ. Someone: "There are subscriptions to TZ?" JM: "fanzines are valuable?" Jhawk: "Next version of IM will be IM-666." JM: "Malcolm is a more senior active member than Jack Stevens."

Mass confusion. What is chase? Jhawk encourages to look it up.

Mobcomm: JFC: "Run for books this Saturday. I can use two more small females, or one large one."

Dexmistress: should reprint dexes.

M: Picniccomm brought good weather to the picnic. Chickens 7-1-8 +Spehn.

Pseudo-picniccomm: received a notice from Hal that he couldn't attend Tuesday after picnic, postmarked Tuesday before.

Pseudo-bluebellcomm: we should "somewhat" flame Bluebellcomm for being lame.

Pseudo-hasslecomm: Hasslecomm sucks.

Jen becomes Theftcomm.

\goto{Old Business}

Picnic happened.

Usual motion, usual second, usual result, usual debate.

JFC: "There is an innovative thing attached to NO's hair- it must be sucking out her life energy."

Jhawk: "The Nebulas are this weekend in NY. We should all go..."

Pseudo-onseck reads TZ.

\goto{New Business}

M: commend people who are getting pieces of paper with funny writing on them. Passes 9-0-6 +Spehn.

Jhawk: new Wheel of Time coming out RSN.

We should straighten out some problems with our magazine subscriptions.

M: new business. Chickens 3-4-8 +Spehn.

\goto{Future Business}

There will be an alum letter.

Meeting will start being at 6 PM for the summer.

Jade left Boston, but not the country yet.

People discuss keys.

Jhawk and Jenwa flame about keys and how to get them and how not to get them and how hard it is to deal with CAC if you don't know what you're doing and whether the key shortage is real and whether keys in fact cost money and whether all-new keys are coming.

M: banana the keys, or the lock. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Pseudo-Onseck}

\end{document}
