\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/3/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 3, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the black-clad Onseck.

Minutes read.  There were no motions regarding the reading of the
minutes.  The Onseck threw a dirty look at Apathycomm.

\goto{Committee Reports}

Panthercomm: Did lots of work, lots of stuff got processed.

There followed a confused discussion about updating the labels on
the Keyholder Board.

Alohalenscomm: We have prints of various photos, including one of
Yevgeniya hugging a door.

Bluebellcomm: Is covering a book as we speak.  And making a horrible
botch of it, too.

Pseudo-Pianocomm: Would Pianocomm like to say something?

Pianocomm: Foley's a keyholder now.

[Jamie] ``He looks just like that drawing except three-dimensional.''

Jadecomm: Need to issue Foley his robes for the worship ceremony.
The Keyholder Notes now say, ``Thou shalt worship me.''

Motion: Approve the Skinner for being explicit.  Passes
\$12--\$0--\$0+Spehn.

What money do they use in Spain?  Liras, spainos, and rubles were
proposed.

Motion: Send a special ambassador to Spain to find out what they
use.  ``What they use for what?''  Passes something--nothing--nothing+Spehn.

\goto{Old Business}

Discussion of aging effects.  Realizing that we're already as old as
we were going to be in the year 2000.

Motion: Condemn the young people!  Passes infinity--3--2+Spehn.

Waiting for the Alumni Office to get back to us.  Ugh, cliffhangers.

[Jamie] ``You can hang my cliff anytime.''

\goto{New Business}

A slightly new reimbursement form, with our address on it now.  Is that
a new font, or just bad old copying masquerading as bold?  It needs a
banana-shaped watermark, or perhaps a font composed of bananas.

Bluebellcomm is still attempting to cover the book.

Jade says something about cute dragons.  ``It's cute, that's all
that matters.''

The safe is now officially ``The Sacks'' after Robert Sacks, who
recently passed away.  He was responsible for setting up our library
fund and more than a little responsible for its growth, including
right up to the end, with a final donation made through his life
insurance policy.

The Onseck attempts to record the next part of the meeting, but all
that comes out is a loud {\bf BEEEEEEEEEEEEEEEEP!} courtesy of the
MITSFS Minutes Censoring Bureau.

% The inappropriate quote was ``Thanks for dying, Bob.''  - Ed

Motion: Approve all MITSFS minutes, past and present, as being
inappropriate.  Chickens 4--0--4+Spehn.

``I'm not wearing any pants, film at 11:00.''  Discussion of Jade's
clothes.

Our door got painted, including the parts you never see.  A call for
a tall person to replace our sign.  Discussion of lighting inside and
outside the Library.

A MITSFS entry was submitted for the upcoming printed IAP guide.

\goto{Future Business}

A donation will be picked up tomorrow.

[John] ``We can't end the meeting before I finish this book.  I
did a really bad job, but I'm sticking with it.''

Discussion of the new Vice pictures.  ``Wow, you look like
Jayhawk!''

No one is seconding anything, despite several golden opportunities.

Motion: Have a motion with a banana and just get this over with.
Passes 10--2--6+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.  ``And I sort of like almost finished
the book.''

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
