\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/01/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 1, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding. [Unknown] is the Onseck.

Minutes read.

M: minutes as wacky pictures. 5-3-4 +Spehn.

\goto{Committee Reports}

Pseudo-cultcomm: 7 new members.

Jadecomm: Jade's back. Jade: "No."

Pseudo-[illegible]: truck stuck on drive. Yay geometry.

Sitcomm: New JMS show. Where? Not saying. Discussion of alien genitalia on TV. Desperately seeking B5 (brainwash on).

Star Chamber: Onseck is now ex-onseck. Ted is no longer a keyholder.

Jadecomm2: Jade info for sale.

Pseudo-jadecomm: Back of head is strange. (Hair stronger than gavel.)

Mobcomm: I want cash!!

M: Condemn LHE for real business. 0-0-2 +Spehn.

\goto{Old Business}

\bing \bing \bing More like that?!?!

M: all motions in writing. Chickens ?-?-? +Spehn.

J: "John's old." John: "Yes, but so will others." Not Jade.

Jamie processed some books. (More boxes left.)

Discussion of paying John.

M: turn fines into scritches. M: ? M: matrix vote. Passes. \bing

J: motion to ? my committee.

Discussion of scritch motion.

M: "J is Albanian" added to ALGOL. Passes 15-4-1 +Spehn.

Usual motion, usual second. Jamie prompts skinner. Usual vote. More prompting. Usual result.

\goto{New Business}

M: say hi to new people. Chickens. 7-73-8 +Spehn.

M: something. Chickens 0-3-8 +Spehn.

LHE taunted with existence of nearby items.

J: "Do not touch my Telzey toy." (Translated from Albanian.)

Jade: "More new?" No.

\goto{Future Business}

Jamie: more members.

Stuff will get done, really. (Ha, ha, ha.)

Albanian motion from J. Chickens 4-4-5 +Spehn. \bing

Jamie likes skinner's memory power.

Pseudo-pianocomm: Justin did stuff with stickers. Legal? Possibly. When done, first new stickers old again.

Jamie: "Wednesday is the lock meeting." ASA: locks info RSN.

J: M: ? ASA. 3-?-7 +Spehn.

Jen: locks? "We are getting some."

Jenwa: M: get banana flavored locks. Jade: "No! Be in favor." Passes 15-8-2 +Spehn. \bing

Motion for lemon locks.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
