\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/8/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 8, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1500 SST, no 1700!!, Jade Wang, President
and Skinner, presiding.  Justin is the Pseudo-Onseck.

% These minutes were typed up by Ed Keyes, a future Onseck, on October
% 21, 2000 from the original handwritten notes.  Be patient if they don't
% make much sense.  - Ed

``I'm presiding.''

Minutes read.

Motion: That was short for a three-hour meeting (1500 to 1800).
Passes 13--4--5+Spehn.

\goto{Committee Reports}

Pseudo-Analogcomm: Fall schedule is up.  The blocks of time everyone
wants are weekends 7--9 and 8--10.

Mobcomm: The new Pratchett is in America, not just England.

Mobcomm: Space-Crime does not want us.  (books)

Wellcomm: Wellesley has its own society now.

Theftcomm: Schedule in Jen's room, will be up at 7.

\goto{New Business}

``New is more interesting than old.''

Jamie reports new books coming from an alum.

Discussion of Library and anatomy.  (That is, Hasslecomm is like the
kidneys of the Library, etc.)

Motion: Commend Jenwa for irresistable kidneys.  Motion does nothing
11--3--lots+Spehn.

Discussion...

Jamie reports on a new feminist sci-fi journal.  Who are they?  We
don't know, but we might buy some anyway.

[Aaron] ``That's why we got rid of women.'' (as written in a future
history)

Motion: Forget he ever said that.  Passes ton--pound--302+Spehn.

[Jade] ``Why is the gavel sticky?''

Jamie suggests that (a) the gavel should be cleaned soon, and (b) the
gavel is not the Telzey Toy.

Motion: Don't ask that question.  Chickens 11--6--9+Spehn.

Discussion of Spehn.

\goto{Old Business}

Usual motion.  Jay is Albanian.  Usual second.  Usual result.

\goto{Old Business, again}

Aresia: Renew.  But are we even members or just cool?

[Jade] ``We should go kidnap Markus.''

Motion: [Jamie] Jen is in the corner, but she can't fool us!  Passes
13--6--1+Spehn.

\bing ... \bing  ``Better.''

Stickers are moving.  The latest count is three more new, seven
renewals since August.

LHE reports that July happened, but not in the books.

Discussion.  Books are expensive.

Discounted fractional memberships?

Motion: Notice Jamie has a banana-colored shirt.  Passes 10--6--6+Spehn.

\bing

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Minutes taken by Justin,}
\centerline{Submitted by Ed Keyes}

\end{document}
