\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/29/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 29, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the Onseck.

Minutes read.

Motion: Commend this Onseck for being faster than the previous two
combined.  ``We fear speed.''  Passes 6--0--5+Spehn.

``That's not a xylophone, that's my wife!''

\goto{Committee Reports}

Jourcomm: Posters exist, yay.  Moties recycled with the same number
of fingers.

Theftcomm: New book list updated, including {\em Telzey and Trigger}.

Pseudo-Panthercomm: Shelf regenerated again.  Darn overflow.
Hopefully the last box.

``Give me committee reports!''

Motion: Condemn Jadecomm for not remembering crucial report.  Passes
13--0--1+Spehn.

Jadecomm: Finally she processed two-year-old stuff on the Skinner
shelf.

``There's even comic stuff there!''

Pseudo-Pianocomm: Prentices are hosed.  One box left for Foley.
``Foley is cool!''

\goto{Old Business}

Motion: Condemn Skinner for being greedy.  ``That was commend,
wasn't it?''  Passes 12--1--2+Spehn.

Motion: Commend Stephanie for distracting Skinner.  Passes
infinity--0--0+Spehn.

Only one circulating banana.

Jamie proceeds to list {\em ALL} the banana-related things in the
Library.

Motion: Condemn Chancellor for this.  Fails by Skinnerial decree.

Letter for Paula Jacobson signed, yay.

% I presume this was for a donation.  - Ed

\goto{New Business}

``Shelves!  Shelves!  Shelves!  Yay, shelves!''

They still need some cleaning.

Now we have holders for the long pieces of metal which can hold books!

Motion: Commend the Skinner for having a new hole in her neck.  Fails
``cause it fails''.

Motion: Condemn Skinner for being demanding.  Passes 7--1--0+Spehn.
(Something involved the Telzey here but the Onseck is confused.)

Motion: Get Skinner a banana because she's hungry.  Motion kind of
hangs there at 9--9--3+Spehn.

Okay for us to use the AirPort in SIPB.

``If you'd turned your head faster, you could have killed John.''

Motion: Commend Skinner for strength of containment devices.  Passes
12--0--3+Spehn.

Skinner is still hungry and louder.

\goto{Future Business}

ET dinner mob maybe next week.

Time warp to Old Business.  A member from the 70's came in, but didn't
notice we were in a new room because it's as crowded as before.  Didn't
notice the gavel and block either... when did they come?  Used to have
a wooden gavel and block.

Motion: Make a motion concerning a banana.  Passes lots--1--3+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
