\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/14/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 14, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Stephanie, Pseudo-Skinner and LHE, presiding. [Unknown] is the Pseudo-Onseck.

Minutes read.

Motion to condemn minutes for lack of bings.

Motion to condemn pseudo-onseck for making a motion re: minutes.

Motion to matrix vote.

JM becomes pseudo-Pentiumcomm. Motions fail, as determinant is -54.

\goto{Committee Reports}

Dex: inventory in a week. Be there!

Hasslecomm sez: books were processed.

Panthercomm sez: books were processed.

Apathycomm sez: new Harry Potter book is misdated, but we don't care enough to fix it.

Bwa-ha-ha-to-panthercomm-comm sez: we got another big donation, this one from the original Analogcomm.

\goto{Old Business}

Pseudo-skinner is held together with safety pins.

Motion to commend LHE for being safe.

Alum newsletter RSN. Really. We mean it this time.

Motion to commend pseudo-onseck for being tabula rasa. 4-3-2 +Spehn.

Old MIT alum (Robert Laundes) has willed us a collection of 40s and 50s fanzines.

Discussion of the X-men movie.

The president is in China. She misses the US.

Bruce Miller is skiing in Colorado.

Usual motion, usual second, \bing usual result.

Hey, we skipped the usual debate.

\goto{New Business}

Move to say hi to new people. Passes 9-0-0 +Spehn.

\goto{Future Business}

Move to feed members bananas to increase lethargy. 7-0-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}
