\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/31/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS meeting minutes

Friday, March 31, 2000

\end{center}

\vskip 12pt

MITSFS meeting called to order, 17:00 SST, March 31, 2000

Jenwa Hsung, president and skinner, wearing a slit skirt, presiding

John Carr, pseudo-onseck (``thank you, John'')

{\bf BING!}

\vskip 12pt

Commend minutes for being ambiguous.  No second.

Commend pseudo-onseck for emulating the onseck.  No second.

Gratuitous failing banana motions fill the rest of the meeting but are
not recorded individually.

{\bf BING!}

\vskip 12pt

\centerline{Committee Reports}

LHE[JPW]: Yay! The books are up to date!  Do we have money?  She thinks
so, but what does that have to do with the books?

Jourcomm[YN]: After delays, Yevgeniya met with Jen on sunday.
There is a suggestion that she extract Jen's brain with a sword.

Jadecomm[JFC]: Jade's hair thing is a red constrictor this week.
Jade hides her hair.

Mobcomm[JFC]: Discussion of getting new books.  The Space-Crime
Continuum is on vacation.  We should get books for ``campus
preview weekend'' which starts next Thursday.  Open house will
bring prefrosh to MITSFS next Saturday.  Keyholders willing to
talk to prefrosh should come help.

Pseudo-panthercomm: Panthercomm is lame and they will regret it.

Pianocomm: Stephanie is doing hasslecomm!  We have three active
prentices.  (Yevgeniya whines.)  No, four!


%{\bf BING!}

\vskip 12pt

\centerline{Old Business}

\vskip 12pt

New donation and several old donations are unprocessed.

We still have a new keyholder.

No more old business!

\vskip 12pt

\centerline{New Business}

Ben Bova lecture Monday.


\vskip 12pt

\centerline{Future Business}

$1.2\mu = 1 {\rm eV}$.  This will still be true in the future.

Miller Motion.  Fails!

Miller Motion.  Fails!  {\bf BING!}

Motion: Replace UA candidate with a banana. Passes \hbox{8-0-5+Spehn}.

Meeting adjourned 17:20 SST.

\end{document}
