\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/25/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 25, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and Pseudo-Skinner, presiding.  Jenwa is the Pseudo-Onseck.

Minutes read.

M: consider minutes deceptive. 1-0-1 +Spehn.

\goto{Committee Reports}

Dexmistress: new dexes printed (correctness thereof ruined by WDS' diligence).

Mobcomm: got promised box of books. Next month when new Pratchett released- UIC book order- tell JFC suggestions. Small press publications? Michael McCullom publishing his newsbook himself.

Gapdex/Lostdex: books await on eBay. (Perry Rhodan.)

Fweekcomm: frosh arrived, grad students soon.

Pseudo-pianocomm: Kat Allen mumbling about actually doing a project if assigned one.

At least one frosh has gotten a membership (bought by sister Dawn Perlman).

\goto{Old Business}

Summer happened.

Alum mailing stalled- Jamie doesn't want to talk about it, but does anyway.

Locks- not before October.

Robert E. Sachs died last Friday. :( Not quite so... died of something heart related. (He started the endowment fund.)

Paulee Jacobs (an alum) donated several hundred magazines.

Usual etc.

\goto{New Business}

No new people here yet.

M: condemn the new people for not being here. Passes by pseudo-skinnerial decree. They can uncondemn themselves by showing up next week.

Everything is continuing statically.

New grad dorm may actually get built! University Park area.

Discussion of emergency showers.

\goto{Future Business}

Freshman will buy memberships.

Activities Midway is on Tuesday.

Carpe Librem shirts would sell? Discussion.

Bees are insects. Or bugs, or, um, whatever.

Miller motion. Second, fails.

Miller motion. Second. 5-0-7 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa, Pseudo-Onseck}

\end{document}
