\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/04/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 4, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, President and
Skinner, presiding.  Natasha Olchanski is the Onseck.

Minutes read.

M: minutes reflected Natasha's innermost heart. Passes.

\goto{Committee Reports}

Dexmistress: new dexes as of this morning.

Pseudo-dexmistress: they have a Y2K error.

Jourcomm: New posters with deadlines and 15-fingered motie. Got a cluedump from jhawk; have to do a lot more than suspected. Should talk to Jen more.

"Nothing's my fault." (YN)

Natashacomm: Natasha does not need an excuse. "Is Natashacomm switching loyalties to Yevgenia?"

JM: "Should we assign more men to you, Natasha?"

Vogt finally really died.

\goto{Old Business}

Skinner camped on the desert and went to mountains. Got an impressive tan. Got nice rocks and data.

\goto{New Business}

Got another big batch of fines this week as people are getting back.

Discussion of what the max possible fine could be.

Mobcomm: more new books in a couple of weeks. They think December and January are one month.

M: commend publishing industry for mathematical accuracy. Passes 7-2-2 +Spehn.

\bing

JM: "Ah, the master is back."

Skinner: "We are all too lame."

JFC amuses us by reading new book synopses.

\goto{Future Business}

Move to purchase all books that have bananas in the synopsis blurbs. Passes 11-2-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
