\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/26/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 26, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jenwa Hsung, Pseudo-President and
Skinner, presiding.  JFC is the Pseudo-Onseck.

Minutes read.

Approve the reading as more assertive than we're accustomed to. 9-3-0 +Spehn.

Jenwa is not listening to Jay.

\goto{Committee Reports}

Jourcomm: YV: 1218 is gone- for sale.

Justin: "Motion to destroy Jamie just for being Jamie."

Mobcomm: got more books- fat ones too.

Discussion on Jordan wannabes.

Panthercomm: stuff is done.

Lis: vouchers done. We can afford to buy books.

Jay: "Motion to move on." 10-6-5 +Spehn.

Still-no-titlecomm: alum newsletter Still Not Fans. Crustcomm? Keyscomm?

\goto{Old Business}

Still searching for MITSFS history. Jamie contacting alums. Skinner, people want minutes back.

The order of graduating and completing is set.

\goto{New Business}

Meetings at new time.

Jamie: combination and key-like atm PGP? Not a problem for non-MIT students. "We haven't talked to them yet."

Movie quotation ensues. Tongue readers are "discussed."

\goto{Future Business}

Late July/early August. Jenwa wouldn't mind if you did it without her, don't do it on Jonmon's wedding.

Logcomm: request summer hours.

Dexmistress/Pianocomm: changes made from gapdex? No reruns happen. (Justin)

Move to banana lock for door. (Aaron) Fails for lack of a second.

Motion to say aw about amount of people leaving for summer. 10-1-7 +Spehn. Apathycomm vetoes "with feeling."

Stories Jay quotes: band camp.

Banana camp? 8-0-15 +Spehn.

Jade sent us a letter. Canada is deploying 600 chickens to be banana colored. 4-0-18 +Spehn.

M: have a banana follow Jade around all summer and tell us what she does. 10-3-7 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
