\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/11/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 11, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie, Chancellor and Pseudo-Skinner, presiding. [Unknown] is the Pseudo-Onseck.

Minutes read.

M: to note that minutes were read incorrectly. Fails, skinnerial decree.

M: same as last without offending word. 8-0-1 +Spehn.

\goto{Committee Reports}

Mobcomm: got 2 dozen hardcovers.

Bluebellcomm: half covered. No new Xanth, but Piers Anthony anyway. May need to order new covering material at some point.

Sitcomm: producer of Survivor thinking of renting out Meir for future show. War Next Door is kind of fun.

Assistant Fweekcomm: people who signed up for R/O are cool. Others aren't.

\goto{Old Business}

WDS: X-Files episode still sucks.

JFC: we got a mail bounce from Florida. People from Florida won't be at the picnic.

JM: Phil Nesser was here (2 weeks ago).

WDS: Barnes had given instructions for changing safe combo when donating it. Doesn't remember where it went.

ALGOL.

\goto{New Business}

Anything?

Lots of new people- a bunch of new review books.

JFC: NASA is sending 2 rovers to Mars in 2003. Longnow foundation- 10,000 year clock and library. Try to recruit smaller frosh because we're running out of XL t-shirts.

\goto{Future Business}

WDS: get 3-ring binders that won't fall apart.

JFC: computerization...?

M: to reinstate JFC's motion from beginning. 10-4-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}
