\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/22/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 22, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the Onseck.

Minutes read.

Ed is commended for reading the minutes.  \bing \bing

\goto{Committee Reports}

Jourcomm: We're hosed, but posters coming soon.  Stories are a ``yay'',
drawings better, and reviews even better.  Some stories from the files
don't actually suck.  New list of books to review.

Motion: Make Jourcomm do everything during finals.  Fails by Skinnerial
decree.

Mobcomm: Trying to get books soon.  Pick-up on October 22?

Pseudo-Mobcomm: Victor Hugo may give us store credit for our for-sale
books.  Shitloads of Anthony for pennies apiece.  Books would be better
if they could teleport.

Motion: Move on to the real part of the meeting.  Chickens 7--4--8+Spehn.
``We fear reality.''

Motion: Move on to the complex part of the meeting.  Chickens
9--1--12+Spehn.  ``You're just imagining it.''  Groans all around.

Something about Albanians and geopolitics.

Apathycomm: Boo.

Pseudo-Pianocomm:  Magdexing powerhouse in progress.

Motion: Abuse the processing power of Foley.  Passes 14--0--5+Spehn.
\bing

% Check on the spelling of this apprentice name.  - Ed

Motion: Use his power only for evil.  Appears to fail 7--10--7+Spehn,
``but it chickens, dammit!''

``Chaotic neutral, chaotic neutral!''  ``Punish yourself harshly.''

Pseudo-Panthercomm: Too many confused Trek books.

Motion: Confiscate all the money used to publish bad Trek books.
Passes 12--0--3+Spehn.

\goto{Old Business}

``Wait for the bing...''  \bing

``She didn't say `Skinner says'...''

Buffy delayed because of the Olympics.

Olympics, bad vault set-up, people fell.  Oops.

``Run run run, bounce, little horsey-thing, land.''

Motion: Commend the Skinner for being overenthusiastic with blindfolds.
Passes 20--0--7+Spehn.

Panthercomm books regenerated after being processed.

Old shelves available for us to take now, yay!

``We can finally decompress the W's.''

Usual motion, usual second, usual apathy.

``Bing.''

\goto{New Business}

Soon an expedition to grab shelves.  Will involve Jade grunting, panting,
and wheezing...  Be sure to take pictures, or a tape recorder.  Needed
for permanent membership.

What?  Vice has purpose?

New stuff on Skinner shelf to be processed.  Supposed to be a note on
the bulletin board...

Minicult: Walgreens will no longer be selling singing fish, but now
lobsters instead.  Loudmouth Louie Lobster.

Talking to french fries.  Speaker to spuds.

Motion: Something about talking over Vice.  Chickens 0--6--7+Spehn.

Motion: Previous Vice to punish current Vice.  Passes lot--4--0+Spehn.

Motion: Make Aaron even more uncomfortable... with a melon?  Passes
4--0--1+Spehn.

Time warp to Old Business...  Neel agreed it was appropriate to kill
him for Scotch-taping the keyholder desk.

Motion: Know fear and stuff.  Chickens 2--0--3+Spehn.

Motion: Bow in silence to Yevgeniya, so she can speak.  7--1--3+Spehn.

% Note, on the handwritten minutes, Yevgeniya's name is often recorded
% as Yv for obvious reasons.

Motion: Laugh at previous motion's concept.  3--5--7+Spehn.

Motion: Have a matrix vote.  5.5--2--10.5+Spehn.

Pseudo-Pentiumcomm reports determinant as +214, all motions pass.

Discussion of Tech photos.

\bing \bing ``Wait for Future Business!''

\goto{Future Business}

Things Jade could do to be photogenic.

Strobe photo of person's head being hit by gavel.

Motion: Someone has to make a banana motion because Jade has to leave
soon.  Passes infinity--0--10+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1810 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
