\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/21/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 21, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, AMU, Pseudo-President and
Skinner, presiding.  JPW is the Pseudo-Onseck.

Minutes read.

M: move to approve minutes as "I'm hungry." Passes 7-2-0 +Spehn.

\goto{Committee Reports}

Pseudo-Dexmistress: still haven't printed new dexes.

Lunarcomm: rumor says dragon ate moon last night and spit it back out.

Jourcomm: hasn't tracked down Jen yet.

Pseudo-VGG: someone paid a 1984 fine.

\goto{Old Business}

John "Acts of the Apostles" Sundman may have been here. "Heisenburg Jola?"

M: define his momentum very precisely.

We are getting money.

\goto{New Business}

Groan.

No slide for marathon.

Malcolm suggests putting on a SFS play during the marathon.

Stuff gets discussed, like exploding T-shirts and nitrous cellulose.

Prentices get discussed.

"Eep!"

No new books.

Supernova- every review said it sucked.

Yawn, snore.

Boring discussion happens.

Pseudo-Onseck decides to doze for a bit until meeting gets interesting.

\goto{Future Business}

Jen walks in.

"Electric cattle prods."

"Eugheugh..." (Jen)

Wait, I think the meeting ended while I was tired.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jade Wang, Pseudo-Onseck}

\end{document}
