\centerline{MITSFS meeting minutes}
\centerline{Friday, December 29, 2000}

\vskip 12 pt

MITSFS meeting called to order, 17:11${1\over 2}$ SST, December 29, 2000.

John Hawkinson, ex-onseck and pseudo-skinner, presuding,  (``Thank you.'')

John Carr, pseudo-onseck

\vskip 12pt
Motion: Condemn onseck for Sacks-life with cards.  No second.
Fails \hbox{1-3-1+Spehn}.

{\bf CLUNK!}

\vskip 12pt

\centerline{Committee Reports}

\vskip 12pt

Mobcomm: RSN

Pseudo-calendar: New Gorey procured.  May he live as long
as the old Gorey.

Mobcomm$_2$: New odd and/or British books in ZGT.

Plantcomm: MITSFS will be snowed in shortly.  Remember \hbox{253-SNOW}.

\vskip 12pt
{\bf Bing!}

\centerline{Old Business}

\vskip 12pt
No more Omnis but we still have shelves.

Y: Commend society for having shelves.  Passes by pseudo-skinnerial decree.

Minicult: Tab includes an observation about beginning of millennium.

This is the last meeting of the millennium.

Motion: commend us all for being here at the last meeting of the millennijm,
and knowing the difference between second and third.  Passes \hbox{7-0-Spehn}.

Usuals...
\vskip 12pt

\centerline{New Business}

\vskip 12pt
Talk about getting door mat for the library.

\vskip 12pt

\centerline{Future Business}

Arisia and Vericon (Harvard) in January.

The next meeting will have future business.  ``Yea, verily,'' says jhawk.

IAP schedule in 5 days.

Motion: project last week's minutes on the Green Building in the
form of a banana.  Passes \hbox{7-0-Spehn}.

Meeting adjourned 17:39${1 \over 4}$ SST.

\end
