\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/22/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 22, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and Pseudo-Skinner, presiding.  John Carr is the Pseudo-Onseck.

The gavel is sticky.

Minutes read. Bill dusts Omnis.

M: approve minutes as less dusty than Omnis. 3-0-0 +Spehn.

\goto{Committee Reports}

Mobcomm: RSN. WDS: "I won't be on it."

Pseudo-dex: no November newdex.

Dex: new dexes soon.

Pseudo-jourcomm: TZ RSN.

\goto{Old Business}

WDS: "We used to not have Omnis all over."

JM: "An old shelf is being swapped for a younger, older shelf.

JFC: science library (not SFS library) has new differential equations book.

Discussion of Egan's "Luminous."

No new monitor yet.

JM: Sacks card has vanished from onseck slot. Mailed?

JM doesn't know when fines increased.

ALGOL!

\goto{New Business}

Janice's Lore of the MITSFS is not completely accurate. WDS: "There's no confusion."

New year, millenium, and car for JFC. Better for holding books.

JFC shows JM and WDS the tax-exempt form. Talk of buying furniture. We have approval but no checks. New shelves and/or file-cabinet-type-stuff coming soon.

Lots of Omnis lying around.

\goto{Future Business}

Soon, no more Omnis lying around on the desk. (WDS: "Make sure all 3 Omni lines get into the minutes, lest people be confused.")

WDS: "When will we break even on t-shirts?"

JM: next two weeks are boring and dead around here. Just alums, mostly.

Banana covered Galaxys. Passes 2-2-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1723 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
