\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/10/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 10, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1710 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the rain-speckled Onseck.

Minutes read, with many interruptions.

Motion: Condemn the minutes as inappropriate.  Fails 1--4--2+Spehn.

Lots of motions, none seconded.  The Onseck starts to record the
motions and then is forced to cross them out.  Discussion of this
policy, with most of the members in favor of the Onseck recording
even unseconded motions.

% This is usually what I've been doing when motions fail to be
% seconded, unless I've already completely written it down or it
% was a really good motion.  Maybe I'll change.  - Ed

Motion: Put the Onseck on a cross.  Passes 7--0--2+Spehn.

\goto{Committee Reports}

Mobcomm and Atlascomm: We have more boxes from donations, and John
probably strained something lifting them.  Yay, hardcovers.

Bluebellcomm: Boo, hardcovers.

Pseudo-Panthercomm: Panthercomm is falling behind.

Bluebellcomm: We're not falling behind very much, but not catching up
either, since it's not very fun to cover a hardcover anthology and
immediately toss it back in a box.  Bluebellcomm is the immune system
of the library (if a book doesn't ``feel'' a part of the library, we
engulf it in a protective vacuole).  Or it might be the part of the
oyster that makes pearls.

[Jade] ``Oysters will take over the world!''

Oysters were genetically engineered by aliens to create pearls as a
supply of interplanetary trade goods.  ``Oooh, premise, premise!''

A member comes in to renew his membership.  We're out of membership
sheets!  The Onseck will probably be blamed for this.

There is a call to pry open the Onseck to get at his pearl.  It is
remarked that oysters can be coaxed to open up with a few stiff
drinks.  Then there's the famous urban legend about the oyster who
wakes up in a bathtub full of ice with a note saying, ``Call 911,
your pearl has been removed.''

Somerandomcomm: Something about the alarm key.

Plantcomm: The lights in the Circulating Room were fixed, indeed very
quickly after we finally remembered to request it.

Lots of stuff, none of it seconded.  ``You can't second your own
motion!''

Jadecomm: Two hair thingies, two braids.  They don't match.

Motion: Commend the Skinner for having {\em huge} tracts of hair.
Passes 6--0--1+Spehn.

Fancomm: {\em Tech Review} has an article about us in it, towards
the back.  ``Are they the anti-{\em Tech}... lots and lots of
accurate quotes?''  The library expansion rate was off by a factor
of ten, but no one noticed.

Alohalenscomm: Foley bypassed us to put up a picture on his own.
Now he's in color!  There are various grumbles about new keyholders
only being entitled to one color: black or white.

Pseudo-Pianocomm: Is there anyone in the prentice pipeline as
cool as Foley?

Mobcomm: The flow of books from Harper-Collins continues.  Mobcomm
attempts to take credit for Jourcomm's accomplishment here.

Motion: Commend Mobcomm for being greedy and backstabbing Jourcomm
in Yevgeniya's absence.  Passes 7--0--2+Spehn.

Pseudo-Jourcomm: {\em TZ} is late, late, late!  It is remarked that
``fall'' actually extends to December 22, but Pseudo-Jourcomm sticks
by the initial report.  A short discussion follows about the seasons
and the Earth's motion, and there is much confusion on precession
versus procession.

% Jade reports that Merry doesn't like her, and there is some
% discussion on the former Onseck's status.  This sort of thing isn't
% really suitable for public Minutes, so I'm recording it as comments
% in the LaTeX only.  - Ed

The Onseck finally receives his Star Chamber key.  ``He didn't kneel!''

\goto{Old Business}

The Skinner is hungry and loud.

We had some authors come in, specifically Carl West and Katherine
MacLean.  They gave us some money and checked out a magazine.

The Alumni Office is still not getting back to us.  We'll go ahead
without the extra information, although this could in fact just be
a cunning bluff to shake the info loose.

Discussion of the size of keyrings.  Jayhawk wins, despite not
being present.

We probably never paid for our LSC slide, but they don't seem to
care.  Although, we ought to track this down just in case LSC has
found a way to tap directly into our endowment fund.

A bunch of old shelves are still sitting around.

Discussion of monetary donations.  There is much confusion about
the signs of the quantities on the report... a donation is a
negative expense, but only sometimes.

The usual stuff.

\goto{New Business}

``Your head would splatter like a ripe melon with a skull in it!''
It is explained that heads and ripe melons don't splatter the same
way, due to the presence of a skull.

Pens are mightier than swords if they have cool lasers in them like
James Bond's pens do.  And maybe if the sword is more of a letter
opener or a pocket-knife.

Discussion about the shelves.  Jamie is attempting to find shelves
for our shelf-holders.

Phonecomm: RING!  It's a wrong number.  The caller wants directions
to Kresge from Rhode Island.  Being the Center of the Universe
carries with it obligations like this, unfortunately, and John
attempts to provide directions.

Jade rebraids her hair.

Motion: ``... Hungry.''  Passes very much--very little--0+Spehn.
There is a very quiet bing because John's still on the phone.

Discussion of chairs.

Motion: Not to make any motions about bananas.  Passes 7--2.5--1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
