\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/18/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 18, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Pseudo-Skinner and Chancellor, presiding.  Jenwa is the Pseudo-Onseck.

Minutes read.

M: make correction Jenwa's already made. 4-9-1 +Spehn.

Jamie discusses frosh and possible existence thereof at next week's meeting

\goto{Committee Reports}

Mobcomm: big box of books for frosh arriving early next week (NOT pinata-style).

Pseudo-bluebellcomm: Yay! "All covered?" "Well, all gone."

Jadecomm: JFC needs money (about 100 dollars).

Dexmistress: inventory stuff and new dexes not yet done will be done before mobs of new frosh arrive.

Pseudo-fweekcomm: the freshmen are coming! The freshmen are coming!

\goto{Old Business}

Alum newsletter: chugging away. Got distracted by locks. Andrea to edit over the weekend.

Currently rich and well off in comparison to 5-10 years ago, but poor in terms of budget in comparison to decades in the past (by Consumer Price Index monetary inflation).

Matching funds from JFC's employer?

Movies used to get us net profit (1965) of 400-500 dollars (about 2500 now) the year we lost the right to show movies. Finboard gave us 1125 dollars (6000 now) on one request, probably because they felt sorry for us.

Usual etc.

\goto{New Business}

New member! Will there be elsewhere?

"Puh-see phee."

The president is back in the country.

The new member tries to identify the keyholder pictures of Jamie, JFC, and Jenwa. He IDs Jamie right away. We have to point out JFC. Discussion of Jenwa's "colorful outfit."

Discussion of Earth's magnetic field and what would happen if the core stopped moving and/or when the dipole reverses.

New rates are up. Presidentially approved!

\goto{Future Business}

Miller motion, seconded, fails.

Second Miller motion. 5-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa, Pseudo-Onseck}

\end{document}
