\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/20/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 20, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the usual Onseck, usually.

Minutes read.

Motion: Strike the explanation of the ``one big unit'' quote.
Passes 9--negative infinity--1+Spehn, immediately revised to
9--2--1+Spehn through vote renormalization.

\goto{Committee Reports}

Yescomm: Yes.

Nocomm: No.

Apathycomm: Yay...

Mobcomm: More small press books are in.  Mobcomm run tomorrow.

Pseudo-Coofcomm: Columbia University Science Fiction Society has
a constitution taking nuclear holocausts into account, appointing a
group of Elders to preserve science fiction for future generations.
Unfortunately their plan also includes stealing our hoard.  Letter
sent commending and condemning them for this.

New Jersey needs to be nuked first.  Pre-emptive strike on Columbia.
Columbia isn't in New Jersey, though... New York is probably close
enough, and downwind.  More tactical strikes are called for, perhaps
a Columbia-student tailored virus?

Motion: In the event of a holocaust, Columbia University should be
the first to go by means to be determined later.  Passes 7--1--1+Spehn.
Calls of ``Traitor!  Traitor!'' directed to the ``no'' vote.

Motion: Waste no time testing the method on the traitor Aaron.  Passes
6--4--0+Spehn. 

Pseudo-Hasslecomm: Violence may be in order, as we're up to four boxes
of overflow.

Pseudo-Panthercomm: Six boxes of overflow from donations.

Pseudo-Bluebellcomm: Bluebellcomm will be buried soon in donated
hardcovers.

Bluebellcomm groans.  The Onseck also groans, being part of Bluebellcomm.

Jadecomm: Jade changed her hair restraints to something small, metallic,
and ineffective.

Motion: Have Michael Crichton write a book and/or movie about the
inability of technology to contain Jade's hair.  Passes 10--1--0+Spehn.

Tuttle donation is reported to have 353 magazines and 1252 paperbacks.

\goto{Old Business}

Motion: July and August now exist.  (in the LHE's books)  Passes
2--0--1+Spehn.

Motion: [Jade] ``Speak!''  [John] ``Woof!  Woof!''  Chickens
0--0--1--3+Spehn, the third category being for canine votes.

New battery in the alarm, it kind of works.  Calls for an EE to fix it.

The Alumni Office has commented on our newsletter.  Revisions are in
progress.  We may have lost some alums in the files, but we have huge
quantities of info on those actually listed... except for the fact that
they were in MITSFS.  One member probably from 1951 is actually still
on campus, Professor Emeritus Jack Dennis.

Paperwork for the alarm box is filed under ``H'' for ``Hole in wall''.

Discussion of notifications for alumni gifts.  This is kind of real
business, since it involves looking at pieces of paper.  Grumbles
about this.

\goto{New Business}

It's un-cold again outside.

There's a proposal floating around to turn the fifth-floor reading
room into a physics classroom.  Universally derided as stupid.

[Stephanie] ``I hate to say I agree with an editorial in the Tech...''

Discussion of late fees on unpaid phone bills from the 1970's.

[Jade] ``We're consistent, but only sometimes.''

\goto{Future Business}

Jamie reports that the Skinner is exacerbating local gravitational
instabilities with the gavel.

In the future, Stephanie will have a cool gown.  (gallon, galleon?)
Sleeves are too short, though.

Motion: [Jamie] ``If this were your elbow, you'd be an orangutang.''
Passes 4--2--1+Spehn.

Motion: Have Jade practice with the Telzey Toy until she stops
squeezing too hard.  Fails by Skinnerial decree.

``Do we have a future?''  ``No.''  ``When the LHE says `no', we
might be worried...''

Discussion of MITSFS constitution and how serious it should be, versus
CUSFS's less-than-serious one.

Motion: Miller motion.  Fails 2--4--1+Spehn.

Motion: Second Miller motion.  Passes 10--0--3+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
