\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/27/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 27, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Yevgeniya Nusinovich, Vice and
Pseudo-Skinner, presiding.  Ed Keyes is the migraine-ridden Onseck.

% Due to the aforementioned headache, some aspects of the meeting have
% been skipped or glossed-over more than usual.  - Ed

Minutes read.

Motion: Condemn the Onseck for failing to correct the online minutes
with regard to the ``one big unit'' quote.  Passes 11--0--2+Spehn.

Motion: Condemn the reading of the minutes for involving the Onseck
looking at pieces of paper during the meeting.  Fails 4--6--5+Spehn.

\goto{Committee Reports}

Motion: [Jamie] ``It's always safe to bing.''  Fails 3--5--2+Spehn.

Bluebellcomm: Ugh.

Concomm: We're probably going to go to Arisia and/or Boskone.  The
plan is to sit at a table and sell stuff.

Discussion of other things to do at a con.

Mobcomm: There's lots of work for Panthercomm to do.  By going to
www.buybooks.com on the Web, you can wade through the ultimate
electronic slush-pile.  This is quite a pain for those of us trying
to collect all published science fiction.

Motion: Nuke them from orbit.  ``It's the only way to be sure.''
Passes 15--0--1+Spehn.

Eeep.  They have a block of 10,000 ISBN numbers, and they're not
afraid to use them!

Theftcomm: We're waiting on Panthercomm for the new books list.

Alohalenscomm: We came to take a picture of Deepak, but we relied
on a bad calendar.

We will shortly need a picture of Joe Foley.  ``Wouldn't know him
if I tripped over him.''

Discussion of Vice's sash.

\goto{Old Business}

The shelves are still here.  John's started covering them with
decorations.  Still missing some pieces of the shelves to make them
useful.  We will soon perhaps have an inventory of every shelf and
shelf-holder in the library.

Jamie looked through some old Tech archives, and found articles
about the construction of the Student Center, including the original
intention for the fifth floor.  (This is in reference to the proposal
about turning the reading room into a part-time classroom.)

Our T-shirt supply is stagnating.

\goto{New Business}

Motion: Staple the Pseudo-Skinner's mouth shut.  Fails by
Pseudo-Skinnerial decree.

Motion: [John] ``Help!  Help!  I'm being repressed!''  Passes 6--4--1+Spehn.

We can get a free ad from the Tech.  Can we use it to advertise for
Zine submissions?  Or make a flip book?  An apathetic takeover of the
Burma-Shave company is proposed.

Foley is finished with his Magdex work, will be a keyholder soon.

[John] ``Make a note: pounce on Stephanie.''

\goto{Future Business}

Columbia University Science Fiction Society people may come here
to worship us.

Discussion of our ancient box from the very dawn of MITSFS.

Motion: Form a committee to discover how the banana-colored animal
got into its cage.  Passes 5--4--1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.  ``FOOD!''

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
