\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/09/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 9, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SDT, John Carr, Pseudo-President and
Skinner, presiding.  Ed Keyes is the Pseudo-Onseck.

There has been a coup! Coop!

Shelf collapsed, minutes read.

M: minutes as stunningly accurate, better than Planet 9. 4-0-1 +Spehn.

Sandman approves too.

\goto{Committee Reports}

Apathycomm: Yay.

Pseudo-pianocomm: might have time soon.

Pseudo-hasslecomm: more books. Some Gor processed. Do we have a circulating Gor set yet?

Pseudo-plantcomm: plastic and buckets and water, oh my! Greenhouses and mildew?

Bluebellcomm: caught up, yay!

\goto{Old Business}

Graduations, now officially old and lame.

M: British Museum should return Rosetta Stone and pay fine. 6-0-0 +Spehn.

M: Carthage must fall! (Or be destroyed, friendly amendment.) 5-0-0 +Spehn. Carthago delenda est!

Was it Cato? Minor discussion of Roman history. "It was some dead Latin guy."

\goto{New Business}

Carthageland, a recreated theme park by Disney, Connection to Norman Spinrad, Elf Princess Rane. "Please do not feed the ancestors."

\goto{Future Business}

Some time the officers will reappear, we hope.

M: late fees for late officers. 7-0-0 +Spehn.

"Pseudo-skinner has no time machine at all, it's just a bloody clock." Starlight will never die!

Resurrection powers of the typical god? Avatars to form a soccer team... Vishnu, Yahweh. Who's the goalie? "Would make a cool anime series."

Was Jesus an avatar or a prophet? And what were his stats?

M: boring boring boring, with a banana on top! 4-0-5 +Spehn.

M: pass the previous motion. 4-0-4 +Spehn.

M: pummel to death with bananas. 5-4-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Pseudo-Onseck}

\end{document}
