\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/6/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 6, 2000

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the sleepy Onseck.

Minutes read.

Motion: Approve the minutes as context-free.  Passes 6--0--2+Spehn.

\goto{Committee Reports}

[Jade] ``Calculate the Doppler shift of this!'' as she mimes throwing
the gavel at a helpless member.

Pseudo-Panthercomm: New book pile has been killed off by Susan.

Hasslecomm: Down to three boxes of overflow.

Mobcomm: We will want money in two weeks.

E.T.A... E.A.T... T.E.A.

[Ed] ``I feel like I'm taking minutes for Dr. Strangelove... P.O.E., 
O.P.E...''

Discussion of ISO, UFS, AFS.

Jourcomm: Three people are going to write reviews.  We hope.  Need
drawings, too.

[John] ``Should I review the locked cabinet?''

Darn shelves, moving our chairs around.

Star Chamber met yesterday, decided things unspecified.

Libcomm is now ``Bondagecomm'', yay!  Discussion of Bondagecomm morphing
into Bondcomm, into Goldfingercomm or Oddjobcomm (TWINEcomm, Nocomm?).

% That would be 'The World Is Not Enough' and Dr. No.  - Ed

Stephanie showed up a week before the meeting, commended for promptness.

\goto{New Business}

[John] ``But I had old business.''

[Jade] ``I want to hear the new stuff.''

Motion: Introduce non-simply-connected time.  Passes 8--1--2+Spehn.

Jenwa donating computer?  Jen Murphy, probably.  Discussion of John's
Sparc.

\goto{Old Business}

``That was a harsh bing.''

Betting pool for when the shelves will have books.  ``What a radical
new concept.''

Self-replicating Anthony.  We're pretty sure Perry Rhodan ones don't
breed.

Elaborate plans in progress for shelves, fueled by hatred for those
in the circulating room.  ``Strata delenda est!''  (sunt?)

[Jade] ``I'm sure whatever Jamie will come up with will be horribly
efficient.''

[John] ``But we'll have to pick apart thousands of books with tweezers.''

\goto{Future Business}

Unusual motion!  Unusual second!  Nothing happens.  ``That's unusual.''

Motion: Mobius minutes!  With a half-twist... use the back of the page.
Passes 12--1--4+Spehn.

Klein bottle discussion.  Discussion of turning spheres inside-out
with a computer.

Jade's hair is two feet, one inch.  Comparison to John's, one strand
of which is at 17.5 inches.  ``Should I measure the rest?''

Motion: Measure the shelves with Jade's hair.  (John's?)  Passes
8--0--3+Spehn.

Motion: Okay, we're going to sit here until someone makes a banana
motion.  Passes 7--1--4+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
