\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/14/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}
Bonus Pre-meeting quote: ``But, Kat, where's your sense of... of... I don't know what it's
  supposed to be a sense of, but where is it?!?'' -ARM, distraught
  that KHA wouldn't want a Boris calendar.
\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 14, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Condemn the minutes for not including the phrase
``(censored)''\\
Passes 12-0-2+Spehn

Discussion of the Great and Awesome Responsibility of the Onseck
\goto{Committee Reports}
\subsection*{LHE}
Our Finboard report has been submitted
\subsection*{LHE$_2$}
SFBC has a check in the mail, and other people have checks on the board.
\subsection*{LHE$_3$}
Isn't it great that the LHE can make three reports?

Commend the LHE for counting to two.\\
Fails 3-3+devilduck-Spehn

\subsection*{MobComm}
Has some new books, inc. ``Children of Cthulu'', which may be like
``Children of Dune'', but we hope not.

Motion to condemn the short story collection for requiring instructions\\
Motion Passes 6-Instructions Bad-1+Spehn

We've been getting lots of donations.

Contradictory motions concerning JFC's laziness in not carrying the
donation boxes cancel for lack of seconds, in a startling display of
apathy appropriate to the subject.

Motion to condemn the seconds for being lacking\\
Passes 5-2-2+Spehn

\begin{itemize}
\item The Skinner is mesmerized by the multicolored toe socks.
\item Discussion of Choose Your Own Adventure books in HTML
\item Discussion of the overcrowded New Books shelf
\item Discussion of ASCII-art Star Wars things
\end{itemize}

\subsection*{Other Committees}
HassleComm and AlohaLenscomm have done nothing.

\subsection*{Pseudo-PlantComm}
The leak is back.

\subsection*{War Council}
Yup, we're at war.
More interesting news will follow when the ASA Room Allocations
Committee publish their results.  Apparently, people are preparing to
appeal the not-yet decided decisions, gaming the appeals board to
prepare for the expected appeals.

\subsection*{Onseck}
Is still planning on ordering stuff from The Library Store.
We're giving up on APO for the Membership Cards. Ed will order them.

Motion to commend Kat for having toys (In this case, a button saying,
`` Come on, people, I can only do six things at once, and one of them
HAS to be breathing'')\\
Passes 7-0-fowl+Spehn

\goto{Old Business}

Pretty-much all got covered in the committee reports.

Discussion of Computer Programmers vs Serial Killers, and the
difference between serial killers and mass murderers:\\
``I think to be a serial killer you have to kill one, wait a while,
and kill another one.  If you order the Extra Value Meal, you're just
a mass murderer'' -ARM

ALGOL
\goto{New Business}
Motion to Officially Note the Absence of Malcom and the Presence of
People Who are Not Often Here.\\
Passes 4-0-1+Spehn\\
\begin{itemize}
\item {ALC}
\item Cassie
\item Christina
\end{itemize}

The shelves have a third coat. That probably means they'll be
installed soon.


Motion: The War Council develop a Banana-Firing Rail-gun with which to
seize some more space for MITSFS\\
Chickens 3-1-1+Spehn

Motion: Get the War Council some help.
Fails for lack of a second and a mandate.

Motion to provide the War Council with a Mandate and a Banana. 
Passes 6-0-4+Spehn
\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1732 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
