\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/25/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 125, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent

Bonus Pre-meeting Quote: ``In the morning of the day of the Faxxua, I woke up and discovered that I had become a centaur.''  Quote from Gemstones by Tyree Campbell.

MITSFS meeting called to order at 1700 SST.  Ed Keyes is the presiding skinner and president, while Andrew Clough is the alien fighting Onseck. 

``Today is national bash-the-Onseck day.''

Motion:  Meeting should be called to Chaos.  Chickens 6-0-7+Spehn.

Minutes are read.

Motion:  ``Condemn minutes for their chaotic nature.''  Passes 9-0-3+Spehn

\goto{Committee Reports}

Some Mobcomm reports are too boring to be recorded.

Mobcomm$_2$:  We got Australian books, like the 'Hal Space Jock' trilogy.

Mobcomm$_4$:  Run on May 10th.

Bondagecomm:  We got a personalized letter from a tiny 'zine (which is quoted above).

Picniccomm:  Mailing real soon.

\goto{Old Business}

John:  Here is my mother.

Mother:  I'm John's mother.

Squirrels:  We're here too.

John:  We were also assaulted by Geese.

Discussion of gang warfare in nature, and whether the squirrels are calling hits on the Geese.

Motion:  Recognize Walt Disney for its wild animals program, the city for their sewers, and the combination for chocking the Charles with squirrels.  Passes 7-2-4+Spehn.

Squirrels:  We hate you all.

ALGOL  ``But what about the usual what about the usual what about the usual what about the usual what about the usual what about the usual debate?''

\goto{New Business}

Motion:  ``Condemn the recursion.''  Passes 8-3-1+Spehn

``We all live in a recursive subroutine, a recursive subroutine, a recursive subroutine (Sung to the tune of ``Yellow Submarine'').

Discussion of foolish wasps and Concords.

\goto{Future Business}

The Assassin's Guild is having a three day game based on Stargate.

We need a bigger Devil Duck.

Motion:  ``Condemn American currency for not having any appropriate denomination for getting over the river Styx.''  Passes 7-2-1+Spehn

Miller Motion:  Universe Saved 4-9-2+Spehn.

John notes the Tech headline ``Crowding to return in Fall, but sparsely.''

Motion: `` Form a committee to decide whether the X-Men are banana.''  Chickens 2-3-5+Spehn

Motion:  ``Eiiyay''  Passes 11-6-1+Spehn

Motion:  ``Dissolve the committee that investigates whether Jubilee's cat is banana colored.'' Chickens 6-3-5+Spehn.

Quotes the Onseck ``Reality is what you can get away with,'' from Robert Anton Wilson.

Miller Motion:  Meeting Adjourned 9-2-7+Spehn

\vspace{12pt}

\noindent
Meeting adjourned 18:-18 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
