\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/28/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 28, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Special, Pre-meeting quote:  ``Evil in a good way.''

MITSFS meeting called to order, 1700 SST March  28th, 2003, with Ed Keyes as the presiding president and skinner.  Andrew Clough is the apocalyptic Onseck.  Minutes are read.

Motion:  Condemn the minutes as needing corrections.  Passes 4-0-0+Spehn

\goto{Committee Reports}

Mobcomm$_1$:  New books, but a rather small pile.

Mobcomm$_2$:  We got 7 proof copies of recent books, though 

Mobcomm$_3$:  One of these is the proof copy of...Acorna's Rebels!

Mobcomm$_4$:  We ordered lots of Dr. Who books.  They are now being held hostage in the UA office.

Since I'm lucky enough to be Onseck I don't have to mention Jamie remark about ``Girl and Horse Stories.''

Meeting falls into the dulldrums of serious business, which not be further discussed here.

\goto{Old Business}

Patent 4187635 issued 1980, describes the Zube Tube, which sounds like a futuristic ray-gun.

Motion:  Us the Zube Tube to supplement the Gavel.  Passes 5-3-1+Spehn

\bing
{\bf Zhoong}
\begin{center}
\textit{Time-warp to Committee Reports}
\end{center}

Bondagecomm$_2$:  We'll take the boxes of books in to ACME.

Discussion of book covers, good and bad.  I make an observation that good books often have bad covers, and vice versa.  As proof, in book 7 of the Wheel of Time the cover actually started to reflect the author's descriptions of the characters, just as the series got boring.

Theftcomm:  Rotation of the TIF in 3 weeks.

\bing
{\bf Zhoong}
\begin{center}
\textit{New Business}
\end{center}

Motion:  Blast the UA with the ray gun.  Passes 7-0-5+Spehn

Discussion of Slinky murder, and ``all plastic lifeforms are known to eat their young.''

\bing
{\bf Zhoong}
\begin{center}
\textit{Future Business}
\end{center}

Someone has offered to donate, and we're planning to take him up, especially since we have all this new space.

The evil plan for MITSFS:EC continues.  Maybe if we didn't collect books there, it wouldn't hurt our fines income.

Motion:  Provide funds to get the cosmologists waist-baskets, since the new introduction of exparimental data into cosmology means that they might have to start useing them.  Passes 3-0-0+Spehn

Miller Motion:  ``I will destory the universe.''  Fails 4-8-3+Spehn.

Jamie: ``Not looking forward to the end of Spring break, huh Andrew?''

Motion: ``Make Joy die at least a little before the universe ends.''  Fails 5-6-3+Spehn.

Miller Motion:  11-0-2+Spehn 

\vspace{12pt}

\noindent
Meeting adjourned 17:83 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
