\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/31/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 31, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
``Where do I hold it for the best bang?'' -ALC

MITSFS meeting called to order, 1700 SST, Andrew Clough, LHE  and
Pseudo-Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: record the following in the minutes\\
Passes 1-0-0+Spehn

JFC would like to note that iBooks, while they do specialize in bad
books, is a publisher, not a bookseller.

Motion: sentence fragments\\
Passes 9-3-1+Spehn

Motion: Ban sentence abuse\\
Passes 5-4-1+Spehn

\goto{Committee Reports}
\subsection*{BlueBellComm}
Some books got covered. Upon elaboration, it is revealed that Bill
Starr covered books.

Motion: Commend the Passive Voice\\
Passes by Pseudo-Skinnerial decree

Discussion about retroactively defining grammar\\
Motion: Commend solipsism\\
Seconded, and JFC thinks it passes. \\
Rejected by pseudo-pseudo Skinnerial Decree (Kat) and the rejection is
approved by  \BING

``The probability of Linear Logic is significantly reduced when you
have no linearity and no logic'' - Malcolm\\
``That's profound'' 

\subsection*{MortComm}
Hal Clement died on Wednesday, unexpectedly.  He was a Friend of the
Society, and had been a guest at meetings.

\subsection*{MobComm}
Keeps buying books.

Some real LHE business is occurring in the background. It distracts the
Pseudo-Skinner.

``I might not have any more to say'' -JFC \\
Move: Commend JFC for not having any more to say\\
Motion fails 4-7-1+Spehn

\subsection*{WarCouncil}
Grr.  KHA expands on the mess with the WarCouncil

\subsection*{JourComm}
``Real Soon Now does not begin to convey the realness or the soonness of it''\\
JFC asks for a numeral from the date of the year in which TZ will be
published.\\
``2''

A digression to real business: How often should TZ really be
published, how long, etc.?  This will be discussed later.

\goto{Old Business}
More digressions to Real Business.

Discussions on whether JFC will look into requests or just mock them,
apparently some will be mocked and others just got forgotten about.

People are reading the small pulp-house publishing novels.

We have Method, Motive and Opportunity for the Salem
Donation. Conveniently, we also have a map.  The exchange will occur
this Sunday.

Discussion of the effects of alphabetizing on book selections.

ALGOL (with usual debate)

\goto{New Business}
JFC just finished a novel where at one point there is a choice
offered:\\
``The lands of man can be overrun by fire-breathing dragons or magical kittens.''

None of the Bananimals have costumes. 

Discussion of books of useless trivia and books intended to be full of
useless trivia, and how acquaintance with the former and latter may or may not
correlate with attending college.

Discussion of butchering cows, and walls dripping blood.

In a sample-size-one tradition of MITSFS, JFC reads Hal Clement's
shortest story, ``Avenue of Escape''

\goto{Future Business}
Tomorrow, it will be November.


Move to carve a banana jack-o-lantern\\
Move to expel JFC from the society for not liking bananas\\
Move to commend JFC for not liking bananas\\
5-2-2+Spehn\\
3-7-2+Spehn\\
2-6-5+Spehn\\ 
Determinant: 93


\vspace{12pt}

\noindent
Meeting adjourned, 18:-26 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
