\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/29/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 29, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding; JFC, oft-distracted Pseudo-Onseck, recording. (These minutes are not up to his usual standards because he was often distracted during the meeting.)

Bonus pre-meeting quote: Is it summer yet?

The minutes of the last meeting are read.

Motion: Next week Kat will do an interpretive dance of this week's minutes. Passes! Dance, Kat, dance!

\goto{Committee Reports}

A motion about motions passes.  The Onseck wasn't paying attention.

Motion to slap the Onseck with a wet noodle for including in the minutes that which the minutes said should not be included in the minutes. (Did it pass?  I forget.)

Mobcomm: We went to NEMBF to buy books. It was slow.

Discussion of turning money into books, or just spending money.

P-Bluebellcomm: Bluebellcomm covered books.

Margaret stole The Portable Door to show off to freshmen.

Discussion of J K Rowling's name. Discussion of middle names. JR's is fake. She took her grandmother's name when her publisher demanded another initial. We have a K.J.B.P.B. at the meeting.

P-bondage[JFC]: Susan Born was called by Cthulhu and that's why she's not doing bondagecomm stuff right the minutes.

Bondagecomm[SEB, via ALC]: We have lots of Amazing, Locus, and On Spec we'd like to get bound soon.  Something about On Spec. Susan will continue "real soon" with binding them at Acme. There is more illegible (to Andrew) handwriting. Charles Stross has a new book. We got it from a normal publisher even though Acme now expects us to bind a new copy of "Scratch Monkey" bound with every order.

LHE report: JFC has one check waiting for him but the people in charge of the money rejected the other two requests. Maybe a tiny little register receipt isn't good enough?

Is Black Bemis home to vampires?

\goto{Old Business}

Our easily distracted new freshman member from last week became the first to check out a second set of books. Well, graphic novels.

Discussion of Assassin's Guild fortune cookies.

The usuals happen.

\goto{New Business}

New members have joined, frosh are here, midway is in progress Frosh are fascinated by the German Harry Potter book. A new member is created during the meeting! Two! The meeting comes to a halt while this happens.

In return for a bunch of "choose your own adventure" fantasies we gave a member a four year extension.

Y renews. His MITSFS ID card dates from 1967. The back is nearly full of expiration dates and initials of keyholders past.

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1749 SST. I don't know why.

\vspace{18pt}

\centerline{Apologetically submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
