\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/28/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 28th, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, Friday 1700 SST February 28th, 2003.  Andrew Clough is the easily amused Onseck, and Ed Keyes is the president and skinner.  The Minutes are read.

Motion:  Approve minutes as unusually edited.  Fails 3-3-1+Spehn

\goto{Committee Reports}

BondageComm:  We bound magazines in a variety of styles.  The results of the binding were satisfactory.  Some of the magazines in our next lot will go to Wells Bindery.  Wells can do lines, but this is beyond the technology present at ACME.  (Onsecretarial Note:  No wonder the Wile E. Coyote failed).  However, the lover case is as yet undiscovered.  Some may be able to get ``seafoam'' coloring.

Mobcomm:  The new Gor book has arrived!  (Much wailing and gnashing of teeth erupts)  We hope it isn't bound too quickly.  This new book was written by the original author's daughter.

A reading, from pg. 66 of ``The Duke of Uranium.''  

``At his age I'd already belonged to a revolutionary underground, been arrested for inciting a riot, joined the secret police, and claimed political asylum on a sunclipper.  But I suppose everyone has to get through adolescence in their own way.''

Motion:  Condemn Onseck for not getting scissors yet.  Justice served 7-0-0+Spehn

\goto{Old Business}

One person is immune to Acorna's Rebels.  Jhawk actually did not laugh when it was read to him.

Perhaps John could get Acorna's Rebels out of his head by seeing ''Princess TuTu,'' one of the series at the anime club.

ALGOL, but with the usual apathy about the usual lack of debate.

\goto{New Business}

Margaret's first hours are tomorrow.

Motion: Pound on Jays back until she coughs up the banana.  Fails 5-5-1+Spehn

JRR Martin's new novella is had.  He needs to stop flaming on Usenet and write.

John seems to be on top of his new Cherryh, but you never know.
\goto{Future Business}

The Onseck will explore to see if the MITSGS still exists.

A pink dragon comes in to tell every body how great the Onseck is.

Onseck: ``Muuhahahaha.''

Discussion of consensus reality as applied by MITSFS, goes to teh use of psychoactive chemicals when writing, to an interesting anecdote of what happened when James Blesh was told that anything he wrote would be published.

The Newton Public Library just bought ``The Science of Super heros,'' which tries to debunk super heros, as when it claims that Bruce Banner took steroids.

Much angst about teh potential extinction of the banana.

Motion:  Save the banana with cryonics.  Passes 8-2-1+Spehn

\vspace{12pt}

\noindent
Meeting adjourned 17:70.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
