\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/7/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 7, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Special, Pre-meeting quote:  ``Evil in a good way.''

MITSFS meeting called to order, 1700 SST March  7th, 2003, with Ed Keyes as the presiding president and skinner.  Andrew Clough is the assassin Onseck.  Minutes are read.

Motion:  ``Approve the minutes as unusually psychoactive.''  Passes 6-1-2+Spehn

\goto{Committee Reports}

Bondagecomm:  We have Andromeda Space magazine's in-flight magazine.  The in-flight instructions are to go up somewhere.  This package has not been checked for terrorists!

Bondagecomm$_2$:  There will be a trip to Wells this Sunday.

Bluebellcom:  The new Gor book was covered...with a protective layer of plastic.
``Is it see through?  Can it be opened?''  ``Yes''  ``Then whats the point?''

Onseckreport:  ``Here are the new scissors I brought in on Tuesday.''

A discussion of astronaut Bowie knives , and how they can be used to chop ones way out of a Gemini spacecraft.  ``You're thinking too much or not thinking enough, one or the other.''

\goto{Old Business}

Some one sent email declaring a book was lost! >:|

More rearrangement in damnation alley.  Now ``Enter at your own risk.''  instead of ``Do not enter.''

More shelving needed.

ALGOL

``You should move for usual debate first next time''

\goto{New Business}

The slinky reproduced by fission!

``What is the past participle of fission?  Fizzed?''

Motion:  ``The past participle of fission is now farged.'' Passes 4-2-2+Spehn

``Oh yeah, I'll see you on Tuesday''

``And we never tried to take over the world, a real gap in my social schedule.''
``What are you doing tomorrow Pinky?''

``Why am I Pinky and not Brain?''

``You have a pink pen.''

Discussion of Tarzan and Elmo Lineen.  Mr. Lineen was very big, and the producers couldn't get him a stunt double, until they found someone who was exactly like him except 70 percent of his size; which made the animals seem bigger.  After hurting his hand on a safety pin supporting an actress's almost existing costume, he stormed off, and was only enticed to return with great difficulty.

\goto{Future Business}

Discussion of Parents, the emailing and phoning thereof, and money.

Discussion of SPAM, and not quite SPAM conspiracy emails that, if you put them in a book and shake, the Illuminanti will fall out of.  Just remember not to tell ``The Chairman'' that we talked about this.

A former keyholder, Tom Lang~'74, has sent us his short story ``Stranger Than
Fiction,'' a.k.a.~``'Dis Order of the Phoenix,'' a.k.a.~``Disorder of the
Phoenix,'' a.k.a.~``Not a Harry Potter Story,'' a.k.a.~``One Thing After
Another.''  He suggests MITSFS do a Harry Potter Clone contest.

Discussion of movie footage, editation, rating, and avoiding the dreaded G

Motion:  ``The Onseck is insane.''  Passes 7-2-0+Spehn  (What! No chickens!  I'll have to try harder)

Motion:  ``Censure all UA candidates who managed to get on to the ballet.'' 9-0-1+Spehn

``We had a 6-foot snake in EC.''  ``Silly, Snakes don't have feet.''

Motion:  ``Commend and recommend all Banana UA candidates.''  8-3-1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned 17:77 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
