\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/14/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 14th, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order at 1700 SST, the 14th of February, Valentine's Day, after a brief reading from Address: Centauri.  Ed Keyes is the presiding president and skinner, while Andrew Clough is the alliterate Onseck.

Motion:  Condemn Barry Longyear for stealing ideas form FL Wallace.  Passes 4-1-3+Spehn

The Minutes are read, though not with an entirely straight face.

Motion:  Condemn Onseck for reading minutes.  Passes 4-3-2+Spehn.

Motion:  Condemn Onseck for laughing.  Passes 4-3-2+Spehn

Motion:  Condemn Onseck for doing anything but laugh.  Passes 4-1-2+Spehn

Motion:  Declare Onseck Albanian for reading minutes.  Disaster Averted 4-8-2+Spehn.

John looks up Albanian fonts that the Onseck could have used, leading to a discussion of the Albanian alphabet, and how an Albanian Onseck would fair.  John finds online an article about ``The Struggle for the Albanian Alphabet.''  It starts off:  ``Nothing ever comes easily for the Albanians.''

``Lets have a big `Aaaaaww' for the Albanians.''  ``But we can't actually go 'Aaaaaw' since Albanian has no 'w.'

\goto{Committee Reports}

Mobcomm:  New Gor book.

Motion:  Censure whoever has read the most Gor books.  Passes 9-0-0+Spehn.

John admits to having read at least 7!  Censure him!

Mobcomm$_2$:  Book synopsis: Paper Mage.  First in a stunning new series inspired by the ancient art of oragami.

Mobcomm$_3$:  Wild-side press shipments are here.  ``Toast'' might be good.  This will be our second book with 'toast' in the title.  The other is ``The Brown Little Toaster goes to Mars.''

Bondagecomm:  Weird new mags coming in.  One is made by ``Theiv'in Kitty publications.''

Psuedobluebellcomm:  The new Frankowski book still needs a cover.

Alohalenscomm:  Good Picture of Margaret, but we still need a Brian pic.

\goto{Old Business}

We have a new stepstool and ladder.

Motion:  Change speed of light to 100,000,000 m/s for easier calculations.  3-4-0+Spehn.

Motion:  Condemn macros as weird.  Chickens 4-0-4+Spehn.

ALGOL

``We usually don't have it.''

\goto{New Business}

John shows a book titled ``The Very Virile Viking.''

A new member gave us all of the money in his wallet, all 21 dollars.

Motion:  Commend Andrew on his sales technique.  Passes 4-0-1+Spehn

\goto{Future Business}

India has SSMs.

US navy has marine mammels trained to catch enemy divers.

A newpaper article about a man who tried to rob a store with a banana is read.  Luckily, the clerk only gave him 10 dollars.

Motion: Commend the cashier for resisting the fearsome power of the banana.  Passes 5-1-2+Spehn.

\vspace{12pt}

\noindent
Meeting is adjourned 17:44 SST.

\vspace{18pt}

\centerline{Humbly Submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
