\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/9/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 9, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent

Bonus pre-meeting quote:  ``The Max speed of a boat without hydroplaning is inversely proportional to the square root of its water line, isn't it?''

``...''

MITSFS meeting called to order at 1700 SST, Friday, May the 9th.  Ed Keyes is the presiding president and skinner, while Andrew Clough is the 6.003 punting Onseck.  Minutes are read.

Motion:  ``Clarify that bit about renaming the route.''  Chickens 4-0-4+Spehn


\goto{Committee Reports}

Picniccom:  We're going shopping soon.

Mobcomm: There will be a run at 10:00 AM tomorrow.

Bondagecomm:  We got 850 dollars worth of binding back.  A discussion of binding style follows.

``If squirrels are the Mafia, the Seagulls are the Yakuza.''

John:  Once the bird stole my mother's hair, strand by strand.

A quote that came with a filk CD we got, by Larry Niven:  ``The music still runs through my head at odd moments, and some of it I can sing... these sons echo in your minds, calling up serendipitous realities.''

Mobcomm:  Bid Engine books went bankrupt, so we'll have to file a claim to get the money from our subscription back.  Of course, that's probably less than the postage cost of telling us this.

Bondagecomm:  Stuff was bound, like Charles Strauss's ``publishable'' book.

\goto{Old Business}

ALGOL

\goto{New Business}

Yay, we're back to normal.

``We're traditionalists''

``We make up new traditions every day.''

Science fiction from China is evidence that Marxism isn't good for SciFi.

John: `` Remember, our acquisitions department doesn't have good taste.''

We also have a scientology magazine.  John dared to crack its cover, but first told us to kill him if his eyes turned an odd color.  Jamie says he was planning on killing John anyway.

We read a SPAM that says ``Are your competitors keeping you up at night?  They should be.''  We all feel the need to be debriefed on strategies for keeping us ahead on our competitors.

Motion:  ``Make funny faces at Steph for being accepted to grad school.''  Passes 7-1-3+Spehn

\goto{Future Business}

Elections:  In about 1 week, when we track down ``The Table.''

Miller motion:  Universe saved 2-5-3+Spehn

Miller motion:  We're afraid  5-Aurialis-7+Spehn

A disonent chorus of 'La's finally drives away the skinner, and thus ends the meeting.

\vspace{12pt}

\noindent
Meeting adjourned 18:-12 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
