\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/21/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 21, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order on Friday, March the 21st.  Ed Keyes is the presiding skinner and president, while Andrew Clough is the flagrant Onseck.

Minutes are read.

Motion:  Condemn the minutes for not including the Skinner's joke, chickens 3-2-3+Spehn.

\goto{Committee Reports}

Bondagecomm:  Susan and I put together some boxes for ACME.  It will cost about 600 dollars.  We're also printing out and binding an unpublished Charles Straus book available online.

War-council:  We annexed part of EC!  No room for our expansion in the Student Center, but we got 500 ft$^2$ in the basement of Walker.  we're gazing covetously at the LSC space.  The room numbers are 50-032 and 50-028.

Motion:  Make Kat a red Union member so she can have fun taking down the wall between us and the LSC room.  Passes 8-0-1+Spehn.

Mobcomm:  New books next week.

One book in the SF book club has ``warning, explicit sex'' on the bottom of the description.  We consider this a nice marketing tactic.

Mobcomm$_2$:  We're getting the exclusive SFBC book mark!

Discussion of book marks made out of real books, and the presence of such at MITSFS.

\goto{Old Business}

The Slinky is still dead, and Ariel is still at large.

ALGOL, but with the usual debate this time.

``What about the 'what about the usual debate'?''

\goto{New Business}

Jamie:  ``well be using new, less orthodox, methods to increase shelf space.''  We will raise the roof of some of our shelves in order to add a tenth shelf space, increasing our book capacity for those shelve by 11 percent.  

Motion:  Commend Jamie for combining greatness and insanity.  Passes 6-2-1+Spehn
John has had 2 flat tires this week.  Sympathy pours forth.

\goto{Future Business}

Ed has a name tag due to being at the physics department open house.  He tried not to talk to prospective grad students so they won't flee in terror.  Why this is future business, I don't know.

A Miller Motion is made, but not seconded.

Miller Motion, Chickens 3-1-4+Spehn.

Andrew:  ``We should have passed it.  Then we'd know if a non-seconded Miller motion protects the universe from destruction.''  Unfortunately, not many people shared my views.

Adjournment Song Sung

\vspace{12pt}

\noindent
Meeting adjourned 17:48.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
