\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/25/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 25, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Andrew Clough, LHE and
Pseudo-Skinner, presiding; Kat Allen, Onseck, recording.

Minutes read.

Motion: commend the reading of the minutes as demonstrating literacy\\
Fails for lack of a second\\
\bing

Motion to follow all instances of this week's minutes with readings of
last week's minutes\\
Fails for lack of a second \\
\bing

Motion to involve tail recursion somehow\\
Passes 4-0-3+Spehn

Motion to commend the minutes as being in the grand tradition of
MITSFS minutes for the last 20 years\\
Chickens 2-2-3+Spehn

Motion to call the minutes ``Fondled by an Anvil'' \\
Motion fails by Pseudo-Skinnerial Decree

Motion that this week's minutes be replaced by appropriate
multi-cultural interpretive dance.\\
Motion passes 8-4-1+Spehn\\
\bing

The Onseck notes her objection to interpretive dance.

\goto{Committee Reports}
\subsection{Bluebellcomm}
Books got covered. -KHA\\
Enough books? -JFC\\
Enough for a committee report -BTS\\

Motion: The Library provide Bluebellcomm with guns, so they can cover
the books.\\
Passes 4-3-1+Spehn\\
``An armed Bluebellcomm is a polite Bluebellcomm'' -BTS

JFC went to a meeting today, and discovered, again, that his chair was
plugged in.

\subsection{Pseudo-Pianocomm}

We lost one keyholder, and will be losing another next month.

\subsection{Slinky-comm}

 Reports that the slinkies have forgiven us for mutilating
their child and are storing high-quality chocolate inside.
It could be a trap.

JFC reveals that he left the chocolate as an offering to the
Slinky-people. JM suggests that this only ensures that it is a trap.

\subsection{UA and CAC}

Have not updated the door locks within the promised 2 week time line,
and are apparently off by a factor of at least 10.  Andrew Menard
still can not get into the Library.

\subsection{Pseudo-Hasslecomm}

The boxes are stacking higher and higher, despite Hasslecomm's valiant efforts.

\goto{Old Business}

Discussion of whether retroactively doing interpretive dance if a
motion is retroactively passed asking for Kat to do interpretive dance
when reading the minutes is appropriate, photoshopped pictures of
Jamie doing interpretive dance, etc.

The unusual discussion is ended by:

Usual Motion\\
Usual Second\\
Usual Debate\\
Usual Vote\\
Usual Result\\

Time-warp to Committee Reports:\\
Discussion of squirrels, protected ants in Germany.

Time-warp to Old Business:\\
Susan-from-the-80's is here. She's an old member.

\goto{New Business}

\goto{Future Business}

Motion to coordinate an exact configuration of GPS coordinates and
triploid fruit to locate KHA's lab\\
7 - N - 4+Spehn

Discussion of parthenogenetic reproduction

Motion to commend bananas for reproducing parthenogenetically.
Passes by Pseudo-Skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
