\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 20, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion that the Onseck get a job as an auctioneer
Chickens 3+space-noises-1-4+Spehn

\goto{Committee Reports}
\subsection*{Bondagecom}
We now have a complete collection of ``On Spec'', thanks to the nice
people there. We should send them a thank-you card, or a TZ thank-you.

\subsection*{Pseudo-Jourcomm}
Jourcomm didn't meet the funding deadline...

\subsection*{Pseudo-LHE}
We didn't spend all our Finboard money, sadly.  LSC-slide had some
left over; TZ and Still-Not Fans didn't happen, so their money didn't
get spent. It has gone ``poof'', and we are sad.

The Vice is a reuse addict. She brought in micro-fiche that Barker was planning
to toss. She is going to paper her dorm with it.

\subsection*{Mobcomm}
A big box from the SFBC arrived. It's not very interesting, but they
are very nice to send us more books when we haven't paid for the
previous ones yet.

More: Last week the Boston Japanimation society showed Read or Die,
about a rare book collector working against the destroy-the-world plot.

\subsection*{Pseudo-Pianocomm}
Cassie came in and covered some books on Sunday. Hooray.

\subsection*{Moocom}
This is the week when SF stories like ``The Invasion of the Body
Snatchers'' and ``The Day the Earth Stood Still'' show on TV. 
\emph{watch your local listings}

Discussion about ``The Houseboat on the River Styx'', and the argument
between Shakespeare and Bacon about whether Shakespeare wrote Hamlet.

\subsection*{Bluebellcomm}
There are still books there.  2 less than we thought, since Cassie
covered stuff.  There might be more, if those darn Panthercomm or
those darn Mobcomm people 

\subsection*{Dexmistress}
Inventory scheduling has begun.  Dexes didn't get printed at the
beginning of summer. They may wait until fall.

\goto{Old Business}
Paul Dworkin (who made the good-dex, and may have been responsible for the
balloons on the calendar) is here. He is impressed that notes are
being taken in real time.

More discussion of microfiche. ``Free as in microfiche!'' -BTS\\
Discussion of whether we should aquire a magnifying glass.\\
``The fiche was dead'' -MHG

Discussion of selling manuscripts at Sothebys.

Unconnected notes: in the Manga version of ``Oh My Goddess'', we find
that the college-age hero has a book called ``Going Steady for
Dummies''

More discussions on Idiot's Guide to <foo>, and things that idiots
really ought to be able to figure out on their own, or things that
they really shouldn't do.

Malcom made a horrible joke, that the Onseck missed.

More discussion about the fiche, and what conspiracy they are involved
in and describing.\\
``It's a microfiche conspiracy'' -MHG

Bookshelves have been emptied, and will be offered to keyholders
first.  The Gor chain has been replaced.


ALGOL

``We have some very unusual microfiche'' -MHG

\goto{New Business}
Unusual motion\\
Fails 7-8-microfiche+Spehn

``The most important book ever is being published tonight at
midnight. Bookstores all over the state are 
``I've run a 5th order equation through the length of the previous 4
books, and if she keeps up at this rate of growth, the last book will
be 1800 pages'' - Paul Dworkin

Scholastic sued a Canadian woman and a Canadian paper for writing but
not publishing a review of the new Harry Potter book, even though no
one involved signed a confidentiality agreement.

Discussion about having psychics write reviews, having the Canadians
publish at 12:01, having Cassie read the book really, really, fast,
and then write a review, and the lack of goat-sacrifice invitations
that Rowling has received.  Discussion of ``consumer cultism'' and Ars
Magica, and how they might relate to the SCC, microfiche, and Harry
Potter. 

There is a superstition that when Shakespeare wrote M..B..., he
included several actual spells, which would explain the ``Week of
Three MacBeths'', and some of the varied and sundry superstitious
practices of the weird theatre people concerning ``The Scottish Play''

Our pinkdex was delivered to the MIT Libraries, and \$500 is being
transferred to our MIT account, per the usual agreement.
Discussion of whether we could get them to give us the money in a
physical form, and whether we would want silver, gold, paper, or
Something Else.

Discussion of the weight of silver, and how many silvers to a gold.

Discussion by old people about Back In The Day D\&D, and lead pieces, and mechanics.

\goto{Future Business}
Motion to retroactively approve last weeks minutes as not
banana-colored, but banana-flavored.\\
11-3+Space noises-2+Spehn


\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
