\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/2/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 2, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent

MITSFS meeting called to order at 1700 SST.  Ed Keyes is the presiding
President \& Skinner, while Andrew Clough is the mysterious
alien-fighting Onseck.

Motion: Condemn the minutes and Onseck for saying the ``Hal Space
Jock'' was a trilogy and misrepresenting Margaret's weekly noise.''
Passes 6-0-1+Spehn

\goto{Committee Reports}

Vox-Sciuorum: There was a squirrel on John's windowsill, but not
dancing this time.  It was safe on the other side of a non-opening
window, mocking him.

Squirrel: ``Neener, neener!''

Bondagecomm:  We got some stuff.

Mobcomm$_1$:  Perry Rhodan... In 3-D!

Motion: Commend Terry Rhodan's books for being lenticular.  Passes
3+3D-3-1+Spehn

Motion:  Condemn Terry Rhodan for being vexing.  Chickens 3-0-4+Spehn.

\goto{More Committee Reports}

John: On the panthercomm shelf we have this reserve banana with a
yellow sicker.  We already have a reserve banana, so this must be the
foreign one.

Mobcomm$_2$:  There is a run at 10:00 AM next week.

Pseudo-Bluebellcomm:   They seem to be slipping back into their old habits.

We look at ebooks, and an average picture in a pirated movie really is
about as big a file as 1000 words.  Its also noted that the first few
Robert Jordan books compress much less than the later books.  More
content?  You decide.

Alohalenscomm:  We still have a fuzzy picture of Kat.

Pseudo-Picniccomm: About a decade ago the route was renamed, and I
(John) am finally editing it.

Picniccomm:  Mail today!

\goto{Old Business}

Discussion of later Dune books and B-Movies.

Motion: ``Suppress those standing nearest the keyholder's desk!''
Does nothing 3-3-1+Spehn.

Kat:  How come I have to replace my fuzzy picture?

John:  Because I'm Aloha Lenscomm and I have absolute power.

Kat:  Thats what I was expecting.

Motion:  Read from past minutes.

We read past minutes from the days of the original Skinner, for a
little too long.  Motion: Stop. Passes 15-8-0+Spehn.

Motion: ``Recommend that the Onseck learn from these minutes.''
Passes 11-4-1+Spehn.

ALGOL

\goto{New Business}

We put in our new Finboard request.

The UA usually rubber stamps the Finboard's decision, as long as they
give the UA enough.

\goto{Future Business}

Picnic two weeks form tomorrow.

What about The Matrix?

Motion: ``Anyone who skips the voting and meeting to head to the
Matrix will be used as batteries.''  Passes 12-0-1+Spehn.

Motion: Anyone who evades battery-hood will have their midichlorians
harvested.  Passes 10-0-1+Spehn

Miller Motion:  Universe Saved 3-11-2+Spehn

Miller Motion:  We go or something.  3-6-4+Spehn

Motion: Resolve who gets to be the Onseck by mud wrestling with a
banana.  Passes 10-7-3+Spehn.

Jamie:  ``I would have them banana wrestle instead of mud wrestle.''


\vspace{12pt}

\noindent
Meeting adjourned 18:-17 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
