\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/21/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 21, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Interrupting a discussion of evil about pretty girls and boys, the meeting is called to order on Friday, February the 21st, 1700 SST.  Ed Keyes is the presiding Skinner and President, while Andrew Clough is the normal Onseck.

The minutes are read, and a plethora of motions are made; but none are seconded, so the minutes most stand without comment.

\goto{Committee Reports}

Alohalenscomm:  The test run of John's new key picture seems like a success.

Mobcomm:  I think something happened...  Yeah, we got books.  We got terrorist free books from Australia.

John reads the blurb from ``Acorna's Rebels'' again. See last week's minutes if you think you can  stand it.

The is a discussion of the continuing outrage provoked by www.bonsaikittens.com, or whatever its real address is.

Bondagecomm:  Its overflowing.

PsuedoBluebellcomm:  We need to get scissors.

\goto{Old Business}

We are show evidence of one of those rare beasts, a zepher flame war.

Motion:  Condemn those who didn't pay enough attention during the reading of the minutes.  Passes 6-3-3+Spehn.

It seems that the new ladder was actually used!

ALGOL

\goto{New Business}

Adjournment song is sung.
\vspace{12pt}

\noindent
Meeting adjourned 1733.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
