\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/14/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 14, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order Friday, March 14 2003.  Ed Keyes is the president and skinner, while Andrew Clough is the Ordinary Onseck.

Minutes are read.

Motion:  ``Recommend we go to Metric time''  Chickens 5-4-4+Spehn

``Argh, Communists''

Discussion of measurement systems, and what 8 slugs of lettuce would look like.

Discussion turns to eating earthworms, and how the eighth will taste great.

{\em Committee Reports}

No Bing!!!!

Pseudo-Jurcomm:  TZ real soon now.

Mobcomm:  Did nothing...  No, looked at the German Amazon.com site and put them through Bablelfish.  We're about 1000 books behind in the Perry Rhodan series.

Motion: ``Commend Society for being about 1000 books behind in the Perry Rhodan series'' Passes by Skinerial Decree

``How did we end up acquiring more books than were published in Endligh?''

``Ken was really good.''

Bondagecomm:  Well's Trip happened on Monday.  Trip report online.  Big Hammer!  Also a machine with a ``Smash pressure'' gauge.  No molten steel though...

``I hope you noted the Cattle prod Conversation.''  I did, see.

Bondagecomm$_2$: We dropped off stuff at Well's, and will send stuff to ACME this weekend.  We had 4 key holders together at 7:00 AM to do it too!

Magdex:  Box of FSF stuff lost their reserve status and are now circulating.  Also ``S and SF to be Circulated'' is now ``S and SF to be Sold.''

John:  ``I love stories with eyeball plucking, not gratuitously, but as a plot point.''

Why hasn't some one done a Tick/Matrix crossover, like this:  ``Spoon!''  ``There is no spoon.''


\goto{Old Business}

``Yes, Bing, Bing, Bing!''

\bing

Discussion of fools, having a paper with, ``the statement on the other side is false'' on one side and ``the statement on the other side is true'' on the other.

Discussion of book registers, book replacement, donations, and perl scripts.

The people who won the UA elections seem to be better than their competitors.

Discussion of the merits of vote buying.

ALGOL

\goto{New Business}

Discussion of, the Total Information Awareness Office's seal, we recommend that the Department of Homeland Security use the TIF.

Regarding the original seal:  ``They must want the Illuminanti vote.''

Jamie wishes he could join the world Jewish conspiracy.

John:  ``Good looking woman on cover = bad book.  Creepy Guy= good book.''

\goto{Future Business}

``Charles Strauss can make economics or computer science amusing.''

We have lots of 100+ year old books circulating.  Lets put them in special reserve.  If you find one, give it to panthercomm.

Motion:  ``Send rotten bananas to the designers of the UA survey.''  Passes 6-Charles Straus-3-3+Spehn

\vspace{12pt}

\noindent
Meeting adjourned 1765.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
