\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/18/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 18, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and
Pseudo-Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion to have the minutes checked for accuracy, as BTS claims at
least 5 errors.\\
Friendly amendment to have a pool to predict the number of errors.\\
Voting occurs, and motion fails by pseudo-skinnerial decree: No pools in the library, since they
are messy, even if you chlorinate them.

Motion to have the minutes corrected because Brian wasn't paying
attention, with no pools.\\
JFC seconds Brian's lack of attention\\
12- 2+Brian's professors - 2+Spehn

Motion to commend the minutes for being in line with other recent
Onsecretarial minutes (i.e. the minutes of the current LHE)\\
Motion chickens 4-4-4+Spehn

\goto{Committee Reports}

\subsection*{MobComm}
More insane British stuff with odd capitalization.

Motion to commend John for having opinions on British authors, and to
condemn the British authors for allowing such opinions to be formed.\\
Chickens 7-1-7+Spehn

Motion to consider the color of the hallway outside... something about
speckle and unannoteted drywall\\
Fails 0-7-3+Spehn

Motion to have BTS annotate any drywall in the library.\\
Passes by pseudo-skinnerial decree.

\subsection*{Pseudo-Bluebellcomm}
``Something seems to have happened to cause the Bluebellcomm shelf to
become full'' -JFC\\
``Would that, perhaps, be that you keep putting books there?'' -KHA\\
``Actually, no.'' -JFC

Move to analyze that title with spackeinferteromnetry (Title in
question: R-T, Margaret, and the Rats of NIMH)\\
Passes 7-1-2+Spehn

\subsection*{Pseudo-Skinner Report}
Dave Barry's novel is on the Skinner shelf. It is amusing, but JFC
claims it ought not to be in the Library.

\subsection*{DexMistress Report}
Inventory will be on Sunday August 10

Move that the minutes should read ``Ignore Previous Cancellation''\\
Fails for lack of a second

\goto{Old Business}
There are bids for two of the bookshelves for sale, and a potential
bid for a third.

Carl Whitty has finished purchasing his permanent membership. Hooray!
This is the second permanent membership ever.
This entitles him to a nude picture of the current Skinner.
Discussion of how Skinners can be evasive in providing this photo.

We got some mail for people who aren't here.

ALGOL

\goto{New Business}
``That's a *LOT* louder than the usual BING!'' -BTS

Move to commend the Postal Service for its rapid delivery of a Con
Report written in 2001\\
Motion Chickens 2-0-2+Spehn

The New Books shelf is packed full.
``I don't come with an off switch'' -JFC\\
``Oh yes you do. Just like the computer...'' BTS\\
``Actually, I guess I do if you don't pay me for a while...''-JFC \\
``Plugging you in would probably work'' -BTS

Time warp to Onseck Report: The Onseck bought orange square labels,
because they had no orange dots. She also bought markers for writing
on boxes, and book tape.

JFC has ordered all the in-print books listed on the books to request
sheet, and cleaned the Banannimal. It is smiling now.
The baby bannanimal comes out of the pouch, which disturbed the
Pseudo-Skinner.

Motion to declare banannimals a threatened species\\
Fails 3-5-0+Spehn

Motion to instead support the extinction of banannimals as appropriate
food for the alabanana species\\
Motion chickens 4-2-9+Spehn

\goto{Future Business}
Motion for the Onseck, in addition to the new office supplies, to
acquire us an alabanana, preferably not stuffed.\\
Motion fails 6-7-1+Spehn

Discussion on whether voting with all four limbs is occasionally rude,
and whether sometimes it's worth kicking Emily.

BondageComm will be doing stuff. MobComm is prompting her to buy more
stuff.

Motion to condemn the Anime Club for taking the Skinner away, causing
discussion of goat meat, and failing to supply the Library with bananas.\\
Motion passes 8-1-2+Spehn

``It's all explained in that T.V. show, `Touched by an Anvil'''
-Malcolm
(followed by groans and laughter)

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
