\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/7/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 7, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1500 SST February 7th, 2003, with Ed Keyes as the presiding president and prestigious skinner.  Andrew Clough is the obvious Onseck.  Minutes are read really righteously, and we make Myriad mysterious motions.

Motion:  ``Nien'' Chickens 7-3-7+Spehn.

Motion:  ``Reread the minutes in German,'' then ``More sound effects,'' then ``Matrix Vote!.''

Voting goes:

The determinant was 96, so all motions pass.

\goto{Committee Reports}

A rendition of Monty Python's book-head-banging from ``The Holy Grail.''

The spider on the Rogue's gallery is found to belong to Gen Clay.  She had it tied to her foot beforehand, but it must have abandoned her while she was in the library.  It is being allowed to stay on the board until Margaret's picture goes up or it gets bored.

Pianocomm:  2 new keyholders.  Brian Sniffen and Margaret Gentile.

Mobcomm:  One new book is Zero Hour, written by a MIT grad.

Thefrcomm:  Spring schedule full full now.  :)

Pseudo-Theftcomm:  John's race to the top of the TIF chart might slow down now that John is employed at a wireless Ethernet place.  ``He's going to catch the 'ether bunny.'''  Pantomime of an ether bunny hunt.

Pseudo-Bluebellcomm:  Some covering done!!!  Only one left from 2 the batch that came in 2 months ago.  ``It's only Leo Frankowski, so its ok.''  Discussion of 14 year old girls and Conrad.  ``I actually like 'A Boy and his Tank.'''  ``A boy and his Skank?''  More Monty Python pantomime and quote, this time from the Castle Anthrax scene.

Random Quote:  ``Its Peyaying four ze Fyoordes.''

Boriscomm:  New calendar from, space theme.  A profound lack of scantily clad ladies.

\goto{Old Business}

More of the really tall shelves are made and in use.  Happiness...

It was recently discovered that the alphabet doesn't really go S,R,N.  The shelves will be rearranged to bring them into accordance with this new theory of alphabetizing.

Margaret's cardboard chair is gone!  We wonder where it went...

ALGOL

\goto{New Business}

The Marvelous Mobile was Mysteriously Mangled by Monkeys Mimicking Marsupials, or something like that.

Biing, Bing, BAng!  The CD that once contained our LSC slide is smashed.  RIP.

Margaret:  ``Smashy, Smashy''

New membership sheets by me.Everybody admits what a swell guy I am.

Jacquie ``I became a member yesterday.''

John  ``Last weekend the floor was filled with insipid sorority chanting.  We didn't allow them to take over the men's bathroom again, though.''

Albania motion on usual suspect.  Passes 7-4-2+Spehn.  The pun is not ever going to be included in any copy of the minutes while *I'm* Onseck.

Reflections on the Skinners Albanian comprehending powers, and the general lack of Skinnerial limitations.

``Knowledge is power. Power corrupts.  Study hard, be evil.''

New step stool and ladder are ordered.  White stickers too, so we'd get free shipping.

\goto{Time warp Committee Reports}

Whooshcomm:  Down to 3 space shuttles.

Jacquie  ``Fear the wrath of Banana goth.  Doom doom doom...''

John read from book jacket:  ``When her lifemate Aari disappeared in the wake of a temporal disturbance, Acorna was left pining for his return.  But when her adopted aunt Karina has a vision of many crying cats, the Unicorn Girl finds a much needed distraction in joining her friend Jonas Becker on a mission to telepathically communicate with temporally displaced Terran unicorn hunters.  That mission is sidetracked when Becker's psychically endowed cat RK contributes to disabling their spaceship, so it has to be towed to the planet Makahomia.''  It goes downhill from there.

\vspace{12pt}

\noindent
Meeting adjourned 18:00 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
