\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/26/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 26, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Approve the minutes as filling in ALC on what happened\\
Passes 8-0-2+Spehn

\goto{Committee Reports}
\subsection*{War Council }
Armenard says : We'd be in a better position to get space if we
actually asked for it.  The Star Chamber assures the concerned
citizens that appropriate action will be taken in due time.

Motion: condemn the lateral thinking that requires you to ask for
things you want\\
Passes 5-2-3+Spehn

\subsection*{LHE}
Our funding appeal was denied, in total.  There is no joy in MudVille.
Many other people got money, especially the chocolatiers, but nobody
got all that they asked for.

\subsection*{Pseudo Jourcomm}
When asked ``Do you have a Jourcomm report?'', Andrew responded ``Wednesday''.
We wonder which Wednesday, and what will happen then.

Clearly, TZ will be done when Jourcommm has made a sacrifice to Odin
on his sacred day.

\subsection*{MobCommm}
``The Star Chamber has rescued the books from UA tyrrany'' --- JFC.  
We may or may not have two mailboxes in the UA office.
We got strange Canadian fiction, as well as British books.

Discussion of feminist apocolypse fiction.

``The book that's written in shorthand...'' -Andrew\\
``Emergence?'' -John\\
``Illegible?'' -Emily\\

We will be getting some replacements from the SCC: notably, American
Gods and a Bujold book.  ED suggests that we get ``Quicksilver'', the
new Stephenson book.

\subsection*{Bluebellcomm}
Covered some books. Yay!

(The Onseck takes this opportunity to note that there are *12* people
at the meeting! 12!. No, wait, 13!)

Discussion of the FDA regulations on monitors, microwaves, and x-ray
televisions going through Customs.\\
``There is always the magic word, 'wallet''' 

Discussion of the correct pricing for black-market Russian nuclear
reactors, and Customs stopping the exportation of nuclear technology
to the Soviet Union.

``Two branches of the government got into a fight ...'' --- JFC

Note from Sam: ``If you're a visiting alien, you can bring crypto in to the country,
but you can't take it back out.  You can take your shotgun shells,
though, leading to the conclusion that you should engrave your
one-time pads onto the shotgun shells.

\subsection*{Coufcomm}
We are about to trade some of our used books for some of their used
books.
``Slow boat to Britain''\\
``No, it's Express Mail -- it's just going through the UA office''

Discussion of using the UA for studying time dialation properties.

Motion: Commend Bluebellcomm and condemn Mobcomm for there being only
a very few new books on the shelf.\\
Motion chickens 9-5-9+Spehn

\goto{Old Business}

A guy who was a member in '56 sent us mail --- he is looking for the
short story that he wrote a thesis on for Course 21, which is in a
magazine that may have been accidentally donated by a friend of his.

ALGOL (inc. usual complaints about debate, despite the lack of Malcom)
Discussion of how Malcom is nothing at all like Emily.

\goto{New Business}
We got a catalogue from the people who make the ``Mammoth Book of
Whatever'' series.

John has a description of a book about the conspiracy to deny Mary
Magdaline's role in Christianity.  Extensive argument and discussion
ensues about the meaning of the word ``catechizer'', and books that
reference themselves in one way or another.

Motion: condemn MobComm for not buying us any books about
grasshopppers.\\
Fails for lack of a second.

Discussion of family feuds that begin by rejecting previous wedding
dresses, elephants.

Motion: MITSFS get a banaelephant RIGHT NOW!
Passes 11-9-4+Spehn

\vspace{12pt}

\noindent
Once the Skinner was informedd that the previous motion contained the
word ``banana''\\
Meeting adjourned, 1742 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
