\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2002}

\newcommand{\bing}{{\bf BING!} }
%\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{#1}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 30, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Andrew Clough, LHE and
Pseudo-Skinner, presiding; Kat Allen, usual Onseck, recording.

Minutes read.

Motion to untable and renew the motion to condemn the onseck for
impertince, fails for lack of a second.

Motion to commend the onseck for embellishing the story, and adding
value to the minutes.\\
Motion to condemn the onseck for being dismayed rather than happy that
she was unable to record the things said in Albanian\\
Matrix vote.\\
\begin{tabular}{c|c|c}
6 & 3 & 9+Spehn\\
5 & 10 & 4+Spehn\\
5 & 6 & 5+Spehn\\
\end{tabular}
determinant = -35  All motions fail \bing


\goto{Committee Reports}
Jhawk comes in and makes fun of the Pseudo-Skinner for not binging loud-enough.

\subsection*{Mobcom}
Lots and lots and lots of books. The SCC is apparently well-liked by
publishers, so they (and now we) are getting genuine advance-reading
copies. Hooray!

The German Invasion is coming.

\subsection*{Bondagecomm}
The order is trickling in. There is more to do.

Pseudo-Skinner asks if he can answer the phone ``Center of the
Universe, Pseudo-God Speaking'' 

JM and JFC argue about whether *any* keyholder can answer the phone
``God Speaking''

\goto{Old Business}
Tech Days start next Monday or something, so there will be a bunch of
old people around. 

``Older than us?'' -JFC

ALGOL

``What about our usual Skinner?'' -JFC

\goto{New Business}
Charles Maxson came in and donated four more cartons of books!

``We have six weird things in the library'' ---JFC

``Only six?'' ---KHA and Malcom, in Unison

``Six things marked with shelfcode WRD'' ---JM

JFC tells us that he is going to continue reading the statistics on
shelfcodes in the dex until someone says something interesting.

The National Virtual Observatory Project has gotten useful
information, so now there is a good way to deal with astronomy data.

``The total data collected each year is doubling, even though the money
spent is constant.''---JM

JM suggests that this means that astronomy is entering a new phase in
its existence.


\goto{Future Business}
Starting next week, meetings are at 6:00 for the summer.

JFC asks what it would take to drive Grackles and Cowbirds away from the bird
feeder. Malcom tells about a Hawaiian hotel did to drive away
birds: 

They pulled the nearby trees down and tied them. Once the manager saw
that the birds had landed, he ordered the ropes cut.

Then the tried an ultrasonic pulse generator, which got rid of all the
birds, but also caused people in the hotel to complain.

Discussion of birds, squirrels and how to keep them out of the birdfeeder.

Discussion of inflateable pterodactyls and chickens, and police
whistles, which scare chickens.

The pterodactyls: http://www.mit.edu/~jfc/pictures/Elaina-office-3.jpg

Motion to end the meeting, Seconded\\
Passes: 6-1-3+Spehn (but, of course, does nothing)

Miller motion fails for lack of a second.

Miller motion again fails for lack of a second.

Choruses of ``Skinner isn't even here'' drive the Pseudo-Skinner away,
without even adjourning the meeting. He returns, and 

\vspace{12pt}

\noindent
Meeting adjourned, 18:-13 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
