\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 1, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

The Skinner regrets not being here last week to witness the meeting,
as it was, clearly, a neat one.

Move to commend the minutes for containing the word parthenogenetic.
Move to commend the Onseck in the event she spelled it correctly.
Motion to ``dance Onseck dance''.

Votes: 
\begin{tabular}{ccl}
5 & 0 & 3 +Spehn \\
9 & 1 & 2 +Spehn \\
9 & 3 & 2 +Jamie + Spehn\\
\end{tabular}
Determinant: 37, so all motions pass. Luckily, they are not binding. There will be no
       dancing Onseck.


\goto{Committee Reports}
\subsection*{DexMistress}
Inventory is in one week and two days.

\subsection*{MobComm}
Has been reading instead of buying books.\\
Hooray!\\
``Oh, wait, I ordered half a dozen hard-covers... but that hardly counts.'' -JFC

\subsection*{Television}
Adult Swim on the Cartoon Channel is showing ``Furikuri''.  It is
strange, and has references to dirty Japanese teenage slang.

\subsection*{AnalogComm}
It's that time of that third of the year again. (i.e. that season).
Keyholders should submit hours and stuff.

\subsection*{Pseudo-Skinner}
The shelf is crowded.

\subsection*{PianoCommm}
Prentice Cassie is most of the way through her Bluebellcomm stuff, and
is coming in tonight to help JM in the alley.

Prentice Ariel also came in, felt guilty and covered books.

\goto{Old Business}

The oddly-capitalized British book is good, according to JFC.\\
There is an ``inadequately dressed'' woman, according to JFC, on the
cover of some mail we received.  \\
``Given that this is you, does that mean she has too much clothing, or
does it actually have less than a square foot of fabric?'' -ED

Sara Pickett sent us a postcard from Germany! It has an Omega Ray
Generator, which she and her Square Dancing Minions captured for the Library.

Discussion about romance novels, Danielle Steele, ``Ravyn's
Flight'', why you will \emph{only} have silk sheets on a space ship, and why
we do not need Baen covers of romance novels.

Discussion of under age ducks, under age ballet dancers, and how you can
tell they're under age.

Albanian motion for Brian, for saying that ballet dancers are under age
until they reach age ``2 2''\\
Passes 7-1-1+Spehn

Discussion of weird books, Quentin Tarrentino, and ``Winged
Migration'', which claims that ``Even fans of the Matrix will be blown
away!''  ``Blown Away'' is, apparently, a pretty awful movie, despite
featuring MIT.

Usual Motion, Usual Second.

Malcom asked for usual debate, which cause him to be sent to Albania.\\
This is also usual.\\
Motion passes 5-2-3+Spehn

\goto{New Business}

Some horrible pun was spoken in Albanian. We wouldn't have known, but
the Skinner told us it was bad.\\

Discussion of the new book,  ``Women Writing
Science Fiction Stories as Men'' It is, apparently, what it says it
is, though JFC has pre-judged it as a second-order, second-grade theme anthology.

Discussion of a new anthology, as yet unwritten, ``Women Writing in
the Style of Late Heinlein'', which is to say, ``Women Writing in the
Style of Having No Editorial Control''

\goto{Timewarp to committee Report:}
\bing

\subsection*{CoofCom}
Someone from the Smith Science Fiction Society was here Sunday, and
made them sound more organized than us, but their Library isn't open
in summer, because they aren't allowed to have keys.  However, they do
help run a Con.  The name of the Smith group is pronounced ``shys-i-phys''

Discussion of a MITSFS-run Con, and the terror it
strikes in the hearts of all FanDom.

They get large numbers of donations of recent hard covers.

\goto{Back to New Business:}

\bing

Discussion of Andrew's computer, how he can get wallpaper from a DVD,
and how he should get a not-Windows machine.

\goto{Future Business}

The Boston Globe reports ``Surveys Show Support for First Amendment
Increasing''

Discussion of How Inventory Goes to someone who asked. This year is
the beta test.  Discussion of why Jamie's Way Is The Best Way.

\goto{TimeWarp to Committee Reports:}

\bing

\subsection*{Pseudo-PianoComm, Pseudo-Surgeon}
Eric Armstrong came in and repaired some books.  He is really good at it.

\goto{Return to Future Business:}

Motion to send a banana to the SSFS group\\
Passes 11-1-6+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1741 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
