\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/10/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 10, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Move to approve the minutes as tuneful fails for lack of a second.\\
Move to approve the Onseck as a toon, and her minutes as ``not bad,
just drawn that way''\\
Chickens 2-Pen-3+Spehn'

\goto{Committee Reports}
\subsection*{MobComm}
pondered its existence, and ordered books from the SCC

\subsection*{Pseudo-Bluebellcomm}
Is lame. 
Move to put a glove box in the door so that non-keyholders can be on
Bluebellcomm.
Mercifully fails for lack of a second.

Discussion of whether we could get more keyholders to be Bluebellcomm.
\subsection*{Surgeon}
The current surgeon is leaving the country, having already left the
state. She's given her Surgeon Seal of Approval to Eric Armstrong, but
we should make sure that he's ready to deal with MITSFS-specific
stuff, and we should make her write the Surgeon rites before she leaves.
``If they coordinate between them, J and Eric know everything!'' -JM

\subsection*{LettersComm}
Neil Asher, author of  ``The Skinner'' sent us mail excited that we
have his book and ``that people were recommending it''. We're not sure
where the second part came from.
Maybe we could ask him to send his other book, which is out of print.

\subsection*{CoufComm}
The first shipment *almost* went out today, but was foiled by the
people at the post office, who did not believe that JM's light
bag was actually full of books. He is going to try to mail it after
the meeting in Central. The books will take 6-8 weeks to get to England.

``You might get funny looks carrying a dirty mail bag on the T'' \\
``I've carried weirder things on the T'' -ED
Discussion of what sorts of strange things one might carry on the
subway.

\goto{Old Business}
The usual sections of circulating hard-covers are overflowing. Joe
started working on the carpentry for the new shelf.

There are still donations in Salem. We need a car-having person to
pick things up. KHA is going to try to coordinate.

ALGOL
\goto{New Business}
We had a Stephanie here, but she left.

JFC won the auction for the BananaElephant. He is considering buying a BananaRhynocerous

The post office is very picky about their mail.

KHA describes the plan that will be proposed to the Senate about
Reading Room division and reallocation to student groups.


Motion passes: Change all references in JM's statement from JFC to JFC \\
Passes: 6-4-2+Spehn

``JFC has no sense of tact''

Motion: Change all references in Brad's motion to JFC.

To reduce confusion, the pseudo-onseck would like to note here
that the original statement involved Margaret.

There may or may have not been a meeting in the past where the minutes
were taken without vowels. JM suggests that we just take the minutes
normally and replace them later with a script that takes out A E I O U
and sometimes Y.

Discussion of whether the Onseck is made of wood, a witch, wiccan,
wise, or Y's.

The Onseck gives up on taking minutes, as the puns fly by.

\goto{Future Business}
KHA vows that she will take minutes in iambic pentameter when she has
a guaranteed A in Thermo.

``In the Future, we will have dinner'' -JFC quoting from Minutes March
23, 2001.

We will have Banana-colored pillow-slips for the new pillows.

The Harvard Post Office is open 7:30 to 3:00 on Saturday.

Motion to have Jamie ask the Post Office whether they will let us mail
a banana to England.
Fails 4-7-0+Spehn

``That's the problem with the Homeland Security thing. It's a lot
harder to send weird things through the mail'' -Brad

``A dormant Prentice, Kat Allen, is Undormanting herself'' -Minutes
from some time in 2001

Motion to condemn ``undormanting'' as a non banana-colored word.\\
Motion to have the Onseck bestir herself to demonstrate that
undormanting is a bad word.\\
Motion to have a Matrix Vote with Kat as PianoComm\\
Determinant: -66 all motions fail

Motion to hold the Pseudo-Onseck accountable, such that if he can not
account for his missing vowels, he will forfeit his rights to all the Banananimals.\\
Passes 7-4-1+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 18:20 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
