\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/16/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 16, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent

MITSFS meeting called to order, on Friday, May the sixteenth of 2003.  Ed Keyes is the currently presiding president and skinner, while Andrew Clough is the soon to be replaced Onseck.

Minutes are read.

Motion:  Commend Mobcomm for giving the 'dexes a vacation.  Passes 7-3-4+Spehn

\goto{Committee Reports}

Picniccom:  No coconuts yet!

Ed:  Maybe some coconut flavored items...

Someone:  We should get some ground coconut.  Some elmer's glue, and some fuzz...

Ed:   Its all about the proper tool for the job (of coconut smashing)... a wrench.

Motion:  In order to adjourn the meeting next time, we need a tape of Fancy Lala.  Passes 8-2-0+Spehn

Bluebellcom:  Maybe covering next week.

Motion:  Tell Margaret to turn of the scary light, so she can push the button.  Passes 9-0-4+Spehn.


\goto{Old Business}

ALGOL

\goto{New Business}

``We never have the usual debate, its not usual.''

We have elections.

For the office of Onseck the official candidate is Cat, while other nominations are the Self-Perpetuating Autocracy, The Songs of Angry Men, Fancy Lala, Fancy Mel, Spoo, Spoon, !\_, !*, Khorne, Chaos Lord of Darkness, and me.

Kat won, with 3.68/7 of the vote.  Runners up in include various songs, fancy cats, and 

|
-*
|

For the office of LHE the official candidate is Andrew Clough (me!), and other candidates include ALC, Chalk, the White Cliffs of Dover, Cthulu, K3W1Z, Unicron JLY, Galvitron, The Once and Future King, Nepotism, SymmetryyrtemmsyS, a Sherman Tank, an Abrams, a Panzer, Other tanks, and Thor.

Andrew won with 4.23/7 of the second vote, with other notable nominations including Vanna, The plant, K4w411, the Necronomicon, the Once and Future LHE, Maine, the girl on the candidate's shirt, Banana, and Unicron JLY. 

During the voting, Ed accuses Cthulu of being fiscally irresponsible.  There is some debate, but Ed reminds us that when you devour your loan officer, it isn't good.  Others point out that he takes a long term view, but Ed ends the argument by pointing out that the Great Old One's last bank went under (the ocean).

The official candidate for Vice is Margaret, and other candidates include Maggie, Richard Perle Prince of Darkness, Ed, Tzeentch, Sloth, Punning, Pride, the Blood Pact, Plaid, a hyper-intelligent shade of the color blue, Danger *, and That Guy.

``Panzer, but I just...''  ``I can't believe she's not butter.''
On the second voting, Margaret wins with 4.9/7 of the vote.  Other notable candidates were, in this order, Ed, Cthulu, various tanks, and Vanna.  Other candidates include The Cheese Stands Alone, Punning, Maggie, Marge, M., and The elder walrus.

Finally, we vote on President.  The glorious Ed Keyes I has decided to be reelected, but has still taken this opportunity to find out what the little people think by holding an election.  Other candidates include Butter, Puppies, Kittens, Bagpipes, Chocolate, Pink, Bob, Plush Beach Cthulu, Love, Justice, The American Pie, Mom, Apple Pie, and Justice and the American Way.

Ed:  ``Who can run against puppies!?''

Someone:  ``Thats not butter, thats puppies!''

That Guy who isn't as cute as puppies wins the election with 3.81/7 of the vote. Puppies are his second.  Other candidates include Cthulu, tanks, and Vanna; as well as slogans proclaiming revolution against the skinnererial autocracy and The Chocolate Bunnies of the Apocalypse.  

Anonymous:  ``Keyholders of the Instrumentality unite!  You have nothing to lose but your hours.''

Someone motions that we adjourn, and then someone makes a Miller motion, and someone else calls for a matrix vote.

Voting goes:

\begin{tabular}{clr}
4& 3& 4+Spehn\\ 2& 4& 4+Spehn\\ 4& 6& 4+Spehn\\
\end{tabular}

The determinant was -$\pi$, so all motions fail.

Motion:  Have a banana Cream Pie.  Passes 11-4-0+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned $\pi$ SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
