\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/4/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 4, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST April 4th, 2003, with Ed Keyes as the  president and  skinner.  Andrew Clough is the joty Onseck.  Minutes are read.

Motion:  ``Commend the minutes as more than adequate for one spring break.''  Passes 4-1-2+Spehn.

Motion:  Provide the Onseck with a supply of Random numbers for future minutes.  Fails 7-14-12+Spehn


\goto{Committee Reports}

Mobocmm$_1$:  We rescued the Dr. Who books from the UA office. They might have read them,, some when asked who the main character is, said 'who?'

Mobcomm$_2$ and Bondagecomm:  Stuff from Australia isn't here yet.

Jokes about C++ are made, such as the one about how it combines the power and elegance of assembly language with the maintainability and readability of assembly language.  We also hear that when you write ADA you might not know what you're doing but you can read it when you're done.

Minicult:  There will be a hearing soon on designating 6 as the official number of the Commonwealth of Massachusetts.

Motion:  Condemn the bill as not being prime:  Passes 4.5-3+John's Big Toe-0+Spehn

Motion: Declare 6 the official Prime of the Commonwealth.  Passed 9-0-0+Spehn

There are many, many more strange official thing of the Commonwealth, and much absurdity therein.

A discussion of the media lab, and how it might or might not be older than the Onseck, who is 21.

Bluebellcom:  Is lame.  In returning Blockbuster tapes as well.

\goto{Old Business}

A ``kinder, gentler'' black hole might let objects through while only exerting a finite tidal force on them.

Motion:  Commend the phrase ``kinder, gentler singularity.'' Passes 7-0-3+Spehn

ALGOL

\goto{New Business}

Ariel might be avoiding the library for fear of the slinkies.

Motion:  Commend MIT students for thinking up cool reasons to be lame.  Passes 5-1-1+Spehn.

Since the slinky company has been having financial troubles, we could also be looking at a slinky suicide.

Niven and Pournelle had a cage match at I-con...so we hear.

Motion:  Don't let THEM immanetize the Eschaton. Passes 10-0-1+Spehn

John:  ``Speaking of Chickens.''  Ed:  ``Speaking of non-sequiters.''

Anyways, John's mother might attend a MITSFS meeting.

Soon we'll have a new stapler.  John:  ``If Apple made staplers, they'd look like this.''  Jamie:  ``You can either staple with it, or you can lick it.''

Mobcomm$_3$:  More British books.

Lavel K. Hamilton's book ``Cerulean Sins'' is coming out.  Free brown paper bag included with every purchase.

Motion:   Commend Avalon books for so long concealing the fact that they were buying porn, airbrushing on fig leaves, and putting it on book covers.  Passes 3-1-0+Spehn

Miller Motion:  Chickens 2-1-3+Spehn.

Motion: Commend Donaldson for never using ``Banana Colored'' in his book titles.  Passes 7-3+Cerulean-3+Spehn.
\vspace{12pt}

\noindent
Meeting adjourned 17:03 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
