\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/5/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 5, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.  The reading of minutes is interrupted by an LSC
operative giving us a slide.  Meeting breaks down into discussion of
the declining quality of the Sci-Fi Marathon.

Motion: Commend the Pseudo-Kat and censure the Kat for taking good
minutes and then not reading them.
Passes 6-3-2+Spehn

\goto{Committee Reports}
\subsection*{Bluebellcomm}
KHA will not cover any more books until term is over, because she
wants to pass Thermo. 

JFC: I don't know if Thermo is worth it.\\
KHA: It's a required class. I'm getting out of here in 8 terms if it
kills me.\\
Y: At least you have an option.

\subsection*{Hasselcomm}
JSB processed things, and put some books into a box labeled
``Things What Suck'', which are not Hasselcomm output, but are related
to books whose third copies are inaccessible.


Discussion of L-Space, Mallet-Space(in Anime) and Katana-Space.

Motion: Library fund mallet-space research\\
Passes 8-stupid-chair-1+Spehn

Motion: award an honorary membership to Bugs Bunny, who can already
pull things out of thin air\\
Passes 5-2-1+Spehn

Motion: Question Bugs on Mallet-space\\
Passes 5-2-1+Spehn

\subsection*{MobComm}
``Blah blah blah black hole, blah blah closeouts.com''

\subsection*{LHE}
Apparently the 5th floor people were confused why we needed office space

``Does this place become a warehouse when the moon is full'' -Y

Discussion about office space, and the B-list folks we might be able
to evict.

\subsection*{Magazines}
We have a Neo-Opsis subscription now, and a lot of magnets.

MHG loses her chair to ARM, despite him having claimed he did not want
to sit.

\goto{Old Business}


``Do you think it's time for Malcolm's Albanian Exiling to be part of
the Usuals?''-JFC\\
``No'' -ED\\
``As Skinner, you have the power to make wrong decisions''-JFC\\
``As I have demonstrated time and time again''-ED\\

JFC tells us about the article sent to MITSFS last March, talking
about big power plants with gavel-size wrenches which may be powered
by old Skinners.

Move to commend gavel-sized wrenches\\
Passes 9-the tellsey toy-0+Spehn

ALGOL
\goto{New Business}
We have a new gargoyle. It appears to be eating a bananimal.
There is an IAP class for Science Fiction and the Environment.

According to The Tech, the oldest fossil definitely male has been
discovered, says Y.

Discussion of Gary Larson's lice species, Hitler bugs, and
reconstruction of fossil skulls based on a single tooth.

Motion: Commend Homework for ruining people's lives\\
Fails 7-11-0+Spehn\\
(Onseck's Note: All the current undergrads voted against this)

Y says, on the subject of Hitler-bugs, that all US Submarines had
to be named after the common names of fish. They began running out of
names, and so made a deal with someone in <field of naming things>,
that the scientist would choose a good name for a submarine and give
it as the common name to a fish which only had a Latin name. 

Motion to commend custom-named fishes.\\
Passes 13-0-1+Spehn

Motion to get the Society a fish tank with geneng'd glow in the dark
fish.\\
Fails for lack of a second, but spawns intense discussion about us
already having too much water, and about the other glow-in-the-dark
things we could have.

\subsubsection*{About the Hitler-Bug}
     {\em Anophthalmus hitleri} Scheibel, 1933 (blind cave beetle) Named by
       an amateur entomologist admirer of the Furher. It is found in only
       five Slovenian caves and is endangered by collectors of Hitler
       memorabilia. [Entomologische Blatter  33: 438]\\
       {\tt http://home.earthlink.net/~misaak/taxonomy/taxEtym.html}

JM reports that the C-P shelves have started being installed. Hooray!

Addendum to the Committee Report: SSDT was shelving books, and found
it easier than usual, as the books were apparently all Hasselcomm, and
so had nice spots where they'd been before.

We have a proof of the newest Arthur C. Clarke book.

Our frosh says that she found 
``The History of Middle Earth for Dummies'' in a bookstore.

Motion to commend the Dummies for expanding to all sections of human
experience\\
Motion to send MobComm to get it.\\
Matrix Vote\\
\begin{tabular}{ccc}
9 & 1 & 1+Spehn\\
11 & 5 & 1+Spehn\\
9 & 4 & 4+Spehn\\
\end{tabular}
Det: 108, so all motions pass


There are also Barbie LOTR dolls:\\
http://www.barbiecollectibles.com/shop/product.aspx?sku=B3449
       
\goto{Future Business}

Motion to charter a committee to write ``Bananas for Dummies''\\
Passes 13-4-2+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
