\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/31/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 31, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order 1700 SST Friday, January the thirty-first.  Ed Keyes is the presiding president and skinner, while Andrew Clough is the procrastinating Onseck.

Motion:  ``Condemn the minutes as not having enough lizards.''  Passes 7-0-0+Spehn.

Motion:  ``Condemn minutes as too short.''  Passes 7-3-2+Spehn.

\goto{Committee Reports}

AlohaLensComm:  Lots of Margaret Pictures, other pictures, etc.  A spider is guarding Margaret's place for her right now.

Margaret:  G'iah!!  G'iah!!  Ouch, my helmet resonated.

Discussion of game, Bakery Banzai, IronChef, and school girls.

Mobcomm:  Books from Space Crime, including Jordan's new brick.

Pseudo-Bluebellcom:  Still lame, but freshmen might be better.

\goto{Old Business}

Ed:  ``Where'd my IAP go.''

We got Brown's report on Russian Sci-Fi.

Margaret dances.

``Is she trying to make an unusual motion?''

``Unusual second''  ``Unusual result''  But no unusual debate.

\goto{New Business}

John:  ``I have a cardboard heart.''

Onseck:  ``Tomorrow is my Birthday.''  Cue heavenly light, singing, etc.

Me again:  ``I let the magic smoke out of an op-amp, and thus increased world magic levels.''

Lot of books to shelve.

\goto{Future Business}

John:''I will either teach Susan Bjon Bondage comm; or Margaret Bluebellcom.''  Also requests Margaret's helmet.

Margaret:  ``Nien, my helmet!''

Motion:  ``Condemn nature for lack of cold resistant flowers.''  Passes 5-2-2+Spehn.

``Some day I'll tell you about a mechanic where I got shot, recovered, and took over my family.''

A most horrendous rendition of ``Happy Birthday to You'' and we to to Bertucci's.

\vspace{12pt}

\noindent
Meeting adjourned 17:59 SST.

\vspace{18pt}

\centerline{Humbly Submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
