\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/10/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 10, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent

Bonus Pre-meeting Quote:  ``The plot, in the manner of a soup to which starch has been added, at last, begins to thicken.''  ``I think thats an appropriate time to start.''

MITSFS meeting called to order 1700 SST, Ed Keyes President and Skinner presiding.  Andrew Clough is the newly UROPing Onseck.

Motion:  Condemn inutes as ``Frightening and Disturbing and they have permanently disturbed me.'' Passes 7-3-3+Spehn

\goto{Committee Reports}

Pianocomm:  Whooh!

Bondagecomm:  Mostly readable bound magazines.  There is a new magic incantation: ``Sew through the fold.''

Psuedo-Pianocomm:  Reminds star chamber.

Poeple's Albanian Embassy:  Pormer Queen Geraldine of Albania died october 22nd.

Panthercomm: LPA, a large paperback anthology.

Alohalenscomm:  Margaret's picture is taken, with her in funy getup.  ``Do not taunt happy fun minutes.''


\goto{Old Business}

Motion:  Overweening the secretary, chickens 5-2-5+Spehn.

Strategic Games Society:  No weapons smaller than an 8 inch naval gun allowed in meetings.

\goto{New Business}

A duel commences between Margaret and John, interupting my interesting and profound story about my exciting and wonderful and happy UROP (boo).

``You can convert 100\% of the excess heat to work, if you do it immorally''

``You always know what time it is, but you never care.''

\goto{Future Business}

Motion:  They're an abomination of Chaos. Passes 8-0-3+Spehn

Motion:  I made a motion.  Fails 6-6-2+Spehn

Motion:  Dope.  Passes 8-2-0+Spehn.

Motion:  Let herrun screaming into the night.  Fails 2-8-1+Spehn

Buetiful Motion:  Aquire a little maker of prognostication purposes.  Fails 10-11-1+Spehn

Margaret falls out of her chair, anime style.

A modified adjournment song is sung, as follows:

Spiders have no tail at all, tail at all, tail at all

Spiders have no tail at all, but they have 8 legs.

\vspace{12pt}

\noindent
Meeting adjourned 18:00 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
