\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/19/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 19, 2003



\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Commend the Onseck for reading two weeks worth of minutes
while only tripping over her tongue a little bit \\
Passes 9-6-3+Spehn

\goto{Committee Reports}
\subsection*{LHE}
The finboard appeals form has been submitted and we have a time to go
plead before the ASA.  We will be taking no prisoners.

Discussion of Laurie Ward's Reality Distortion Field and appropriate
finance-sensitive sunglasses to wear.

Motion: Appropriate money for finance-sensitive sunglasses for the LHE\\
Passes 6-5-3+Spehn

\subsection*{MobComm}
Some international packages are not here. Where are they? Nobody
knows.  Perhaps strange things are afoot in the MIT Mail room?

We may have to backtrack through the possible places where they may
have sent our package.

\subsection*{BlueBellComm}
Is going to cover some books today. We need more keyholders to be Bluebellcomm.

\subsection*{PianoComm}
Shaina Jackson was here, but didn't do any Prentice work.
Where are our Prentices? We need to get them to materialize and be keyholders.

\subsection*{War Room}
Larry Benedict wants to renovate the reading room, still, but there is
no money --- and given the recent MIT budget news (35 million
deficit), it's unlikely that there will be random money for renovating things.

Discussion of warped space in the Stata Center.

\goto{Old Business}
MITSFS(the star chamber list) gets lots of spam. It's sad.
JFC is getting lots of viruses, and so is ED.  KHA and JM don't get as
much. Clearly, only UNIX people like Kat and Jamie, and Windows people like
Ed and John.

Discussion of oil tanks calling people and hanging up.

Discussion of weird prank phone calls and appropriately disturbing
comments, and what to do to people who repeatedly call the wrong number.

ALGOL (including usual random noise from Margaret)

\goto{New Business}
The MIT Alumni newsletter decided we were newsworthy, and so
interviewed Ed.  It is a hard-copy newsletter published by the Alumni
relations people.

We were visited by John Kuenzig, from Kuenzig Books, and he offered us
an extra 10\% discount when asked how much the discount ought to have
been.

John elected not to buy the Latin translation of Harry Potter, but it
is in the Coop.  If someone wants to donate it, though, we'll buy it.
``There's weirder stuff that we could buy for people to not read. In
fact, there's weirder stuff that we do buy that people don't
read'' -JFC

Discussion of pseudo-Latin incantations and what you'd use to replace
them in a Latin translation.  ``Linear B'', maybe? Greek? Phonecian? Egyptian? Hebrew?

Discussion of Ancient Greek god promiscuity and Egyptian lineage
one-upping, as well as the effects of Digital Rights Management on
Greek Culture between 1200 and 700 BC.  We have a book called
``Etruscans''. We don't really have ``American Gods'', because a
member has had it out for two years.

\goto{Future Business}
We should buy a copy of ``American Gods'' in paperback.

Motion to condemn JFC for not bringing any new banana animals into the
Library\\
Motion chickens 4-3-5+Spehn

The Koala did try to escape -- he was busily climbing down the cabinet
when JFC arrived.  JM suggests that we put the Koala into the
polyhedron, but the offspring of a Bananakoala and a Bananaroo would
be disturbing.

MHG is disturbed by the baby Bananimal.  JM points out the egg.\\
``Maybe you won't want to be around when that hatches'' -JM\\
``But it has been dormant for a while...'' -MHG\\
``Legendary creatures have a long gestation period'' -JM\\
``Anyone for omelette of legendary creature?'' -MHG

Malcolm tells JFC that face-huggers are not allowed in the Library,
since they prevent people from reading. 

Timewarp to Committee Reports:\\
\section*{Pseudo-Jourcomm}

Sara wrote a review for TZ.  The book has not been published yet, so
maybe it and the current TZ will coincide nicely.

Motion: Put the Koala-Bananimal and the Bananaroo in the same
polyhedral cage so that they will breed. \\
Passes 11-3-4+Spehn

(Post-meeting bananimal discussion) MHG wants to either sell the
offspring or use them as her unholy army of the darkness. JM thinks we
may need to keep them for scientific study.

\vspace{12pt}

\noindent
Meeting adjourned, 1746 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
