\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/22/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 22, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Bonus pre-meeting quote: ``I bet we could get a corporate sponsorship
from Dole...'' -ED
``But penguins don't wear sneakers'' -SEB

MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: Approve the minutes as abbreviated.\\
Passes 6-1-Quacking+Spehn

Motion: Approve the minutes as appropriately reflecting the section of
the meeting for which the pseudo-Onseck was present.\\
Fails 5-8-3+Spehn

Motion: Condemn the Onseck, Pseudo Onseck and minutes for being insufficiently inebriated\\
Passes 9-4-3+Spehn

\goto{Committee Reports}
\subsection*{LHE }
Went to treasurer training. Feels very good about himself.
Discussion of the endowment.

Move to commend the Lord High Embezzler for keeping three sets of
books, not just two.\\
Passes 11-1-0+Spehn

Much discussion of the complicated books the LHE keeps, the
importance between positives and negatives, and ways in which we can
torture or bind Stephanie to the Library until she teaches Andrew to
keep the books.

``Computer Associates'' gave us money. The machines like us.

\subsection*{BritainComm}
(Time Warped from Pre-Meeting)\\
We may be able to get Imperial College SFS to take our extra books and
give us money or neat British books.  JM is in negotiations, but fears
that their club president may have been eaten for his impertinence.

\subsection*{BondageComm}
Discussed talking about binding things next week.
The pre-pre-meeting meeting was very exciting.

Found Italian sci-fi share ware books which request a 10,000 Lira
donation.  These may be printed out and bound.

``If you don't have land bridges, bad things happen'' -SEB

The LHE suggests that Italy should have been conquered by the
Hapsburgs, so they could speak Spanish.\\
SEB suggests that it would be easier if they all still spoke Latin.

``Spanish is closer to Italian than French'' -ALC\\
``You mean `Freedomspeak''' -JM

Discussion of sending spare gubernatorial candidates to other
countries, eventually leading to new methods of measuring Pi.

\subsection*{AsYetUnnamedEBayComm}
We are so not allowed to have a PayPal account.  MIT has an e-commerce
thing, but it's not really designed for us.  We can use EBay, but we
can only accept checks made out to MITSFS.''

``The Tech was the load of bricks that broke the camel's back.  There
had been problems with people throwing bricks at the camel before''

We are allowed to ``launder'' books through a member, but we will not
be setting up money-laundering operations.

Move to commend the Onseck for being oblivious.\\
Passes 10-2-1+Spehn

\subsection*{FweekComm }
J signed up a member from the class of 2007. Hooray!

\subsection*{MobComm}
JFC went to the SCC and got some books, which are waiting to be
processed because ``Inventory went longer than it might have, if it
hadn't gone as long''

``If we had some ham, we could have ham and eggs, if we also had some
eggs'' -JM

More British Books. Why? Because John hates BlueBellComm.
``They seem to come in half-inch sizes. They must not believe in the
metric system'' -JFC

Tomorrow morning, they are going to New England Mobile to get
hard covers, because JFC *really* hates BlueBellComm.

\subsection*{JourComm}
Real Soon Now

\subsection*{NimbusComm}
There is a storm.

``I think we're out of committee reports'' - JFC
``Then we should move on.'' - KHA
``Or we could start some new committees''- SEB
``No, no.  I think we have quite enough'' - ED
``Committees are what Dark Matter are made of'' - JM
``As a physicist, that makes so much sense'' - ED

\goto{Old Business}

``That reminds me of yesterday, when we were planning to blow up the
Hoover Dam'' - JFC\\
``That should not go into the notes'' 

Extensive discussion of whether we should have disclaimers on the
minutes, of dead French Cardinals, and End-User certificates for buying
explosive charges.

JM is discussing custom-made shelves with wheels for the C/Ps, which might not be
worth it -- we might just use the metal ones. More discussion of
whether we could do strange and interesting things with the air
currents if we put enough bookshelves in front of the A/C.  This would
probably be poor, given that 

ALGOL

\goto{New Business}
JFC was on vacation last week in the land of the HyperIntelligent
Squirrels. He claims that they are no longer as intelligent -- this 

``Given that you spent time in their territory, we must now consider
you their subverted agent'' -JM

JFC also got animal porn -- he took pictures of dragonflies
mating. Apparently they are fond of boats, and look like balloon animals.

``Damn the mosquitos'' -ALC\\
``Full speed ahead'' -ED

JM read the new Robert Jordan book. Several people are impressed.
He points out that Jordan has not actually *told* people what causes
``Tarmon gai'don'', so it could happen at any point...


\goto{Future Business}

Next week we will be back to the 5:30 time.

The Bananimals have been reproducing, which is strange because there
was only one adult.  There is a bananasaur, and ``Bobby Banana'', on
loan from JFC.

Motion to tattoo iridescent bananas on each of the Skinner's arms, so
he can be the Car'acrn'n\\
Motion to condemn JFC for not donating the bananimals to the Library\\
Motion to do something entirely insufficiently specified.

Matrix Vote:\\
Voting occurs, and all motions pass by Skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
