\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/27/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 27, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Comment the minutes for being lengthy and humorous
Passes 6-1-4+Spehn

Motion to approve the minutes as flaming sharp cheese
Passes 6-4-2 +Spehn

Discussion of whether the minutes would burn, and whether the Onseck
should pause after saying ``BING''.  

Motion to do something.
Something passes, 3-0-2+Spehn

Discussion of whether we should use the other chain for the Anita
Blake books, or the Piers Anthony books.

\goto{Committee Reports}
\subsection*{Bluebellcomm}
Reports its existence, despite all other 
\subsection*{MobComm}
Got some books.

``The Gor books are trying to escape!'' -MHG\\
Move to commend the Gor books, fails for lack of a second.

MobComm's Harry Potter policy is when asked about buying the Harry
Potter book, the person who asks will be mocked.
The Onseck asked him to get the book, claiming that she does not mind
being childish, but MobComm did not mock her, other than asking if BTS
if she was always this childish. He declined to comment.

Move to condemn the Bluebellcomm backlog (seconded by Bluebellcomm representative.  BTS)\\
Passes 6-3-6+Spehn

Move to condemn the Bluebellcomm backlog to being suffocated and wrapped in
plastic.\\
Passes 7-1-3+Spehn

\subsection*{Bondagecomm}
Knows it needs to buy magazines. 

MHG is not being reimbursed for buying more chain, no matter how
pretty it is.

\subsection*{Moocom}
The movies mentioned last week are being shown this week.

\goto{Old Business}
The bookshelves that had been held up by punch cards are now being held
up by wood. 

The anti-radiator is dripping on us.  Discussion about why the
DustBuster can't be used to fix this.

Discussion of early vacuum cleaners, and whether the pump-action could
double as a super-soaker *and* a Larami gun.

Discussion of BTS and KHA's game, running under the Assassins' Guild
this weekend.

ALGOL

\goto{New Business}
The gifts office has received, on our behalf, the first part of the
collected works of Jack Vance, in approximately 40 hard-cover volumes.
John says that Prentices or bored, obsessive keyholders should flip
through the books to make sure all the pages are in order.\\
``But we don't have any ... wait, never-mind''

Move to institute a Board of Obsessive Keyholders\\
12-1-Micro-fiche+Spehn

Discussion of what happens if you send two people to Albania, and
whether they can talk to one another. The question is never fully
resolved, but the meeting moves on as everyone is distracted.

Motion to recommend that the Star Chamber nominate a more permanent
People's Albanian Embassy, or an assistant deputy secretary\dots fails
for lack of a second, but: 

Move to make BTS the assistant deputy secretary to the People's
Albanian Embassy.\\
Passes 14-4-1+Spehn

Discussion of Baen covers, Manga, Zen, dinosaur alcoholism, and
tasteful cloaks.

Move to commend James Baen for inducting so many people into SF by
such well-targeted advertising.\\
Passes 8-2-2+Spehn

Discussion of JM being the test case for the exploding chain-mail
chastity belt.

``Oh, dear. I said that, didn't I?'' -MHG

Discussion of plaid-shifting MHG with a really big catapult.

``I don't think I have anything else to share'' -JFC\\
``Oh, thank God'' -BTS

\goto{Future Business}
We have new Psi-Phi shirts, but the font is much smaller.
They are black.

Discussion of beaver-eyed monsters, and the MIT seal.\\
Discussion of the horrible MIT logo, and previous horrible logos.\\
Apparently MIT has not learned not to waste their money on ``image
consultants''.

Motion go commend the South Pacific for being banana-colored\\
Fails 5-7-2+Spehn

Discussion of whether Susan has a parasitic head slinky.

Motion to have the Secretary translate banana into Albanian.\\
Passes 9-8-0+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
