\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 6, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.
Motion to condemn the Onseck for leaving out sections of the
dex-stats. Onseck argues and motion fails for lack of a second.

Motion to commend the Onseck for not recording John's thought bubbles
Passes 6-3-2+Spehn

Motion to condemn the meeting for starting without the LHE.
Chickens 3-1-5+Spehn


\goto{Committee Reports}

\subsection*{Mobcomm}
The Germans are coming! The Germans are coming... the Germans are here!
Including ``Das Jesus Video'' -JFC

``Das Jesus Superstar?'' -Malcolm

Motion to instruct the LHE on the 30 years war\\
Motion passes 6-3-1+Spehn

The foreign stuff has moved!

\subsection*{Pseudo-notMobcomm}
The ZBT is full. Shame on y'all.

Fitting all the books into the Library is like Vaudeville, only less
funny and more work -JM

If you put books on the tops of shelves, it will make Jamie move books
around, but he will hit you in the head with a plastic bottle.

MHG came to the meeting and made a myna-bird noise.

``I owe you ten dollars, and I'm gonna pay you back, like it or not!''
-MHG to ALC

%The Gore books need a longer chain. The new shelf is too big. The
The Gor books need a longer chain. The new shelf is too big. The
chain is currently secured with duct tape.

Motion for the library to donate all its extra space to the Popular
%Front for the Liberation of Gore Books.
Front for the Liberation of Gor Books.
Chickens 4-7-7+Spehn

%Discussion of whether the women on the Gore books have bikinis. JFC
Discussion of whether the women on the Gor books have bikinis. JFC
brings us ``Bikini Planet'', which does have bikini-clad girls on it.
``Bikini Planet. Just those two words make me think of bikinis. And
planets. Er, and David Garnett.'' -Neil Gaiman

\subsection*{Ed's Second HatComm}
The Japanimation committee will be showing Read or Die.
The Anime Club will be showing all of Slayers.

MHG is entranced by the rainbow slinky.
``Wouldn't you like an unholy army of the Night made of Slinkies?''\\
``Sure, I'd love one, but I'd rather you not have one.

LHE needs to be all trained and stuff. Discussion about that.

Motion to blame MHG for anything done by a Slinky.\\
Passes 8-1-1+Chocolate Cylinder+Spehn

Motion to commend the Vice for providing a positive role model for
slinkies\\
Passes 12+slinky-2+decapitated-2+Spehn.

Motion to condemn the slinky for having a hand\\
Passes 8-3-4+slinky+Spehn

Discussion of whether non-square matrixes can have a pseudo-determinant

\goto{Old Business}
The C/P bubble has propigated completely, though not evenly.

MHG ran out of the room screaming, with a slinky on her neck.\\
The crowd asks Malcom what he said.\\
For posterity, it was ``Is the Slinky necking with you?''

%Discussion of Gore books in garlicbutter sold in small packages with
Discussion of Gor books in garlicbutter sold in small packages with
French labels.

The people in 35 or 37 or whatever lied about it being available.

BTS comments that the ``Student Street'' plans have been scaled back
and back, reminiscent of the ISS.

Arguments about whether the ISS has student group space.

Discussion of advertising-funded space missions.

There is an airliner painted to look like Pikachu.

The mayor ot Topeka changed the name of the city to ``Topekachu'' for
approximately 10 minutes.

Discussion of cats and such

ALGOL

\goto{New Business}
Move to welcome the shelf.\\
Comments on ``it looks like a Monolith''\\
The vice jumped on the shelf.\\
The Vice and JFC began\\
Move to remove the monkey\\
9-3-1+Spehn

Finger motion\\
Finger motion\\
Finger motion\\
Finger motion\\

``If you go by the registrar database, people level-up at the end of
the summer'' -JM

``You change tape rolls professionally?''-ED\\
``In an odd, roundabout way, yes!'' \\
``It was either that or work with windows, right?''-JFC\\
``Yeah''\\
``Good Choice''-ED\\

\goto{Future Business}
Miller Motion\\
Fails 2-12-0+Spehn

Miller Motion\\
Fails 7-9+0+Spehn

Motion to smite apple and Microsoft with the Power of a Bananna\\
Does nothing 8-8-2+Spehn

Motion to commend the Monsanto Company for Patenting a Bananna\\
Motion passes 8-6-2+Spehn
\vspace{12pt}

\noindent
Meeting adjourned, 1733 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
