\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/05/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 05, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Move to approve the minutes as suggested.\\
Passes 12-1-5+Spehn

Move to commend the minutes while being explicitly apologetic, while
condemning them for not being nearly apologetic enough\\
Passes 14-3-2+Spehn

Move to commend the minutes for being almost but not quite up to ALC's style.\\
Barely passes 7-6-3+Spehn



\goto{Committee Reports}
\subsection*{Pseudo-JourComm }
TZ is asymptotically approaching doneness.
People are writing reviews.

\subsection*{CoufComm }
The Imperial College Science Fiction Society (ICSF)
is interested in trading spares, buying spares, or doing useful
things like that.  We are working out details.

Move to commend Google for being a benevolent dictator\\
Passes 9-5-3+Spehn\\
(Even if it isn't, we want to be on it's good side)

Something strange was moved by Malcom. It failed for lack of a second.
\subsection*{fweekcomm}
We got 10 new members last Friday and Saturday, but have not yet put
them all into the list.

One of our new members is a pre-MIT fan of the minutes.\\
Motion to commend the recent Onsecks and pseudo-Onsecks\\
Passes 12-8-0+Spehn

Motion to commend the member, too\\
fails for lack of a second

On a mishearing, \\
Motion to commend the number ``2''\\
Passes 14-2-1+Spehn

\subsection*{Pseudo-BondageComm or Rosfap}
Some people sent us magazines. How nice of them.
They might be professional... they have COLOR COVERS!

\goto{Old Business}
Discussion of trinary logic gates, base 4 RAM, and analog computers.

Motion to commend the calendar for changing, and for being the least
sketchy Boris month yet.\\
Passes 8-2-1+Spehn

Motion to condemn the months ``September, October, November, and December''
for not being the 7th, 8th, 9th, and 10th months, respectively\\
Chickens 2-2-5+Spehn

ALGOL

\goto{New Business}
We have new plastic drawers to hold our T-Shirts. Hooray!

Discussion of scary Japanese Anime involving people made of bean curd.
Albanian motion to protect us from the bean curd\\
Passes 8-2-4+Spehn

A motion in Albanian occurred, which failed for lack of a second.

Our bulletin board is uncovered. It's a little worse for the wear.

We have a new black chair in the library. We're not sure how we got
it, but it has some topological issues.

\goto{Future Business}
Motion to condemn the chair for being insufficiently banana colored.\\
Passes 9-3-0+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
