\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2002}

\newcommand{\bing}{{\bf BING!} }

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 23, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion: condemn the minutes for not saying what room the meeting was
held in. (5-260)\\
Passes by Skinnerial Decree

%Discussion ensues about Kat breaking into the Spoffard room next time.
Discussion ensues about Kat breaking into the Spofford room next time.

Motion: condemn the other people for not believing the minutes\\
Motion: condemn and commend the minutes for being a fitting end to an
Onseck's career\\
Motion: matrix vote\\

The Onseck whines, and is told she can declare someone Pentiumcomm.

\begin{tabular}{c|c|c}
4 & 2 & 1+Spehn\\
8 & 4 & 2+Spehn\\
2 & 7 & 1+Spehn\\
\end{tabular}

Brian is made Pentiumcomm, but claims he has to compile Matlab first.

Andrew and Kat face off and get different determinants.

The meeting is entirely derailed attempting to calculate the matrix
vote. A member tries and gets a negative answer.

``Except 4*2 is 8'' -BTS\\
``Oh!'' -JFC\\

The Determinant of the Matrix is  24\\
Kat calculated it correctly, because Matlab says so, so all motions
pass. There is much rejoicing.

\bing

\section*{Committee Reports}

Motion: Everyone who got the determinant wrong should return their
brass rat\\
Chickens 4-0-4+Spehn

Discussion with a member about overdue fees and whether it is cheaper
for him to ``lose'' the books and replace them.

Discussion of max overdue fines, and what the maximum fine might have been.

The Onseck points out that she has never had a fine of any sort
(keyholder or member), and that she is the only keyholder who can
claim this. 

Motion: Motion to fine the Onseck for impertinence\\
Fails for lack of a second.

\subsection*{Mobcom$_1$}
There was a mobcommrun, leading to the dex vacation, 

Recap from last meeting: The reason it took so long for John to get
back from recovering the dexes is because he stopped to read them.

\subsection*{Bluebellcomm}
Bill Starr covered a pile, Kat covered a pile, but there are still so many...

Discussion of stupid square British books.

\subsection*{BondageComm}
We have gotten feedback on rebinding: a member chose to read the paperback because it
has bigger margins than the rebound hardback.

Discussion of digital slide rules.

Jamie suggests that we need to appoint someone to flushcomm,
traditionally in charge of flushing all the toilets in the Institute
at once in the thought that this would destroy the Institute's
plumbing. This, however, might cause the Library to flood.

Discussion of The Great Tech Flood: 
No, shit, there we were, pinned down by a huge puddle of water,
dripping out from beneath the door to the Tech Darkroom.  We set up
one inch-high dam of paper towels across the door, but the water kept
coming. The keyholders were madly bailing, but the water kept coming.  We set
up a second dam near the desks, but the water kept coming.  Then
someone from The Tech noticed.  There was much rejoicing.

Physplant came with their ``Washer-buffer squeegee machine''
and cleaned up after this, making the floors as clean as they had
ever been.  The Library blamed Natasha for bringing a flood with her
as she visited.

Jaime reads through some old keyholder excuse sheets:\\
``Mea Culpa! Mea Culpa! Mea Maxima Culpa!''

Discussion on whether Catholics are allowed to burn Lutherans.

Discission on whether Latin is prohibited or required in Mass, and
what would have happened if they'd gone directly from one to another.

``Big Red Cheese, or possibly Assistant to the Big Red Cheese''
--JM

Those in attendance demand that Jamie explain what Big Red Cheeses
have to do with keyholders, which prompts Jamie to
unlock secret $\star$ chamber documents with wills from previous skinners.
There are some keyholders discussed in these who are stilll keyholders.

\subsection*{Bondagecomm$_2$}
About $\frac{1}{2}$ the missing issues of On Spec have been ordered from the
publisher, and they may be able to dig up some of the out of stock
issues to complete our collection.

\subsection*{Theftcomm}
Keyholder complaint sheet has finally filled up, after 20.5 months,
for the first time since the TIF went up. Before the TIF, the
complaint sheets usually filled in 5 months.

\subsection*{Mobcomm$_{(n+1)}$}
We got the new Jack Williamson story collections.

There are more German Books coming.\\
``Why?'' -ED\\
``Because our collection is incomplete''-JFC\\
``There must be better foreign language stuff than Perry Rhodan in
German'' -ED\\


We got the new Adam Roberts novel.

\bing

\section*{Old Business}
JFC is reading a book.

JM reports that someone found Malcom through the MITSFS minutes.

The picnic happened, there are several sets of pictures.
ED may be able to replace his keyholder picture, but John likes it.

Timewarp to committee reports: AlohaLenscomm reports that Brian has
moved up 18 inches.

This is because ``Former keyholder Dave Kern has
gracefully voluntarily offered his resignation as required.'' --JM

JFC suggests that someone should colorize the TIF.

The Banannimal is put upright in the bucky ball. It has
evolved. There is much rejoicing.

BTS reports that the dust on Banannimal has set up a civilization, and 
Yaroslav Blagozevic has written again.  

He quotes from it, and it is amusing, but is not recorded here.

ALGOL

\bing

\section*{New Business}
JFC has rearranged the ``New Stuff'' area, so to best show off the 
``three-dimensional'' books.
 
``If the rest of the books were two-dimensional, they would be much
easier to store'' -JM

``A 50000 level deep tower of Hanoi'' -ED

Much discussion ensues about the apparently massless (or maybe not)
books, which may or may not have infinite density, and might or might
not collapse into one another.

``If our books were in a Black hole, we couldn't have any in German''
-Malcom \\
``Why?'' \\
``Because black holes can't have any herr!''-Malcom\\

Albanian Motion: Malcom\\
Passes by Skinnerial Decree\\

Discussion about the Albanian Alphabet and its lack of W.

Discussion about former Queen/King Zoog, later determined to be a
Queen.

Discussion in Albanian, which unfortunately the Onseck does not speak.

BTS reports that we do not have permission to view the Albanian
slash. There is much rejoicing.

\bing

\section*{Future Business}
There is a summer schedule prototype.
JM reports that Margaret no longer has the last hours on Saturday and
the first hours on Sunday.  She is signed up for four hours. 

Discussion of the TIF, TIF-racing, and who is the Median.

Discussion about the sadness a keyholder feels when nobody comes to
the library during their hours.

``The baby banannaimal is staring at me now'' -JFC

``It's saying `I've evolved. Have you?'''-JM

BTS suggests that marsupials are evidence that YWJH was a graduate
student once, too.

JFC discusses comments in genetic code.

Miller Motion:\\
Motion fails 3-14-3+Spehn. There is much rejoicing.


Second Miller Motion\\
Motion to commend the banannimal for evolving\\
Motion not to have a matrix vote\\

This time, the Onseck alone deals with the Matrix, having proven
herself in the last Matrix vote. 
The determinant is -270, so All Motions Fail.

Motion to commend the baby bananimal for staring at John\\
Passes 9-2-2+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
