\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/24/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 24, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, Friday 1700 SST January 24, 2003, Ed Keyes is the presiding Skinner and President.  Andrew Clough is the UN special Ops Onseck.

Motion:  Accept minutes as chaotic passes 4-4-1+Spehn

Motion "I I can sneak off to game and you can speak to this lizard as if all were well."  Passes 5-0-0+Spehn (boo lizards)

\goto{Committee Reports}

The Skinner didn't get the hours he wanted :(

"When Ceaser became Emperor he declared that the year would go on until the sun caught up with it, so why can't you do something similar."

\goto{Old Business}

Shelves now installed in damnation alley, and have mags living on them.

Andrew: "After a 5 match winning streak I was defeated."

\goto{New Business}

Margaret made a slide which ought to go in the marathon this weekend.

UNIT will strike soon.

Rogues gallery has been improved.

Dark City is good.

Motion:  "Somebody ought to make a banana motion."  Fails 4-0-8+Spehn.

Reflections on "Crossroads of twilight."

"A fine banana motion will better bring out the subtle flavor of my Assassin's Guild gaming."

\vspace{12pt}

\noindent
Meeting adjourned 17:59:59

\vspace{18pt}

\centerline{Hungrily submitted,}
\centerline{John Carr, pseudo-Onseck}

\end{document}
