\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/11/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 11, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion to correct the minutes: the opening of the NJ bookstore was
7 AM, not 9 AM.  \\
Motion passes 4-2-1+Spehn

Motion to approve the minutes as very imaginative\\
Fails for lack of a second, as "They were no more imaginative than usual" -JFC

\goto{Committee Reports}
\subsection*{MobComm}
Would've provided books, but the mobile is still broken, and the UA is
holding books hostage, so MobComm has done *NOTHING*!

Discussion of nasty potholes, and the public works departments who
don't fix them.

``The life of a traffic cone is not a happy one'' -JFC\\
Motion to nominate JFC to explore forming a new committee on the
proper treatment of traffic cones.\\
Motion passes nearly-unanimously: 8-0-0+thatguy+Spehn

\subsection*{PlantComm}
Reports in absentia that the air conditioner has been repaired, though
it is still dis-assembled.

Move to commend the air conditioner.\\
Motion chickens 1-3-3+Spehn

``Are you into rotating disks these days?'' -JFC \\
``Indeed, rotating magnetic disks... of PLASMA!'' -ED\\
``Do you deal with eight syllable words?''-JFC\\
``Magnetohydrodynamics? Yes'' -ED \\

Discussion of the thermal efficiency of various types of refrigeration
devices.

\subsection*{Bluebellcomm and Pianocomm}
Bluebellcomm tried to get Ariel to help, but Ariel doesn't like
Bluebellcomm.  Cassie may well have come in and covered books, unless
someone really likes her and is doing the work for her.

``If we have a poltergeist who is doing book covering pranks, *don't
do any exorcisms!*''-ED

``If there were a potter-hamilton crossover...'' -JFC\\
``No'' -ED

``Has any processing been done on this'' -JFC\\
``Yes. It has been lifted from the floor to the couch'' -BTS\\
``Perhaps I should do some pre-processing, then'' -JFC

``Lloyd Alexander as a child?  I thought he was born at 70.'' -BTS

BTS tells about the book of nanofiction left on his car.\\
``'The World's Shortest Stories of Life and Death.'  They are all 55 words
or less, mostly exactly 55 words.  There is no dedication, no note,
and (most disturbing of all), the price tag indicates that it was
purchased at Urban Outfitters in Harvard Square.''

Motion to commend Urban Outfitters for outfitting their clientele for
every possible occasion.\\
7-7-0+Spehn

Stuff happens with assigning fine credit for donations. 

\goto{Old Business}
There is a book for grades 5 through 5.

BTS reads from the keyholder notes: 
``This policy will be reviewed by the Star Chamber in Summer, 2000''
Apparently, JM is rewriting them, and is not planning to reprint until
he's done.   ``But these are going to look like the Talmud by the time he's done!'' -BTS

More processing of books.  The donation has an audio cassette of ``The
Restaurant at the End of the Universe'', which includes tips on
networking with Volgons.  BTS is forced to read the back of some teen
paperback fantasy novel, which is terrifying and mentions dragons.

BING!

ALGOL 

\goto{New Business} 

Timewarp to committee reports:
Pseudo-surgeon report Erin trained two people, Josh and Eric
Armstrong, but Eric was really training Erin, as he has Real Library
Experience.

Erin may be requesting Surgery supplies.

Move to have the society buy a bigger hammer\\
Passes 5-0-0+Spehn

Discussion on the hammer, the gavel, and whether larger gavels would
cause trouble for future Skinners.
\goto{Future Business}

Timewarp to Old Business: The Bookshelf Sale\\
So far, no offers have been passed to ED,
but JM may have some.  To ED's knowledge, no decision has been made.

JFC has pulled more third hardcovers off the shelf to make space, as
it has not been very long since he last put books on the shelf to
activate Jamie.

The spotlight on MITSFS got us some members. Hooray.

We got a substantial donation towards a life membership, \$1000 all in
20s. Discussion on the ATM per-day and per-transaction withdrawl
limits, and how you could mess with the IRS and your bank.  ``The IRS
responds to this by bending you over a table and hostilly auditing
you.  The IRS response teams are more heavily armed than the FBI!'' -BTS

Motion to end the meeting with a hostile bananna\\
Miller Motion \\
Motion for a Matrix Vote\\

The vote is  3-1-1+Spehn  before the skinner realizes the great evil about to occur, and by skinnerial
decree the bannana motion passes, the miller motion fails, and the
matrix vote motion fails.



\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
