\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/19/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 19, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion to answer the question ``What kind of city would be a banana
flying in space?'' as ``
Yellow, unless its wrapped in plastic, in which case it would be
Bluebellcomm fails for lack of a second.

Motion to comment that the meeting seems to make both more and less
sense than did the actual meeting.\\
5-1+devil-duck-0+Spehn



\goto{Committee Reports}
\subsection*{MobComm}
Got some new books.  Unfortunately, there are a couple errors in the
ordering system, and we may have gotten doubles. One of them is a Baen
book, with an exploding dress or maybe an exploding horses' head.
``There's something Alien in Denmark.'' It appears to have all the
requisite qualities of a Baen book: tentacled monsters, time travel,
Shakespeare plots, a woman with elf ears, and cabbages taking revenge
on their Irish tormenters.

``There's no cabbage! I own that book'' -BTS\\
JFC shows Brian the book cover. 
``Okay, maybe it's a cabbage... but it's not supposed to be.'' -BTS

Move to censure JFC for looking up the lady's cabbage\\
Passes 3-Randall Garret-1+Spehn

We got a replacement for the Glen Cook Omnibus that broke into pieces
when someone dropped it.

\subsection*{Pseudo-LHE}
We ended the semester with about \$50 in unspent funds, and the
Skinner.  Discussion of packing slips, womens' slips, Joe in a skirt
and blouse in the Library, and JFC not trying to look up Joe's cabbage
while continuously mistaking him for a woman.

``Having seen Joe in a skin-tight micro-dress, leaping off the wall and
shooting at me, I found nothing confusing about his gender'' -BTS


\subsection*{Pseudo-Hasselcomm}
Jake did a partial box of Hasselcomm. This probably means that there
is a box somewhere that changed from ``Hasselcomm input'' to
``Hasselcomm output''.

\subsection*{Bluebellcomm}
JFC covered two books, but Bluebellcomm proper did not get to any,
yet. Now that finals are over, more will get done.

\subsection*{Onseck}
Will order 9.25'' Bluebellcomm paper Real Soon Now. Really she will.

\goto{Old Business}
No new news WRT the space allocation. 

We sold a few T-Shirts over the last few weeks.  Discussion about
using T-shirts to get rid of KHA's sisters' cats.

ALGOL
\goto{New Business}
Discussion of Pratchett.
``Much like Goedl, Escher, Bach...''-BTS\\
``Nothing's like Goedl, Escher, Bach''-member\\
``Much like Goedl, Escher, Bach, you will find yourself tempted to
skip the odd chapters''-BTS\\
``Oh. That wasn't the analogy I was expecting'' -ED

Discussion about binding techniques, the Books of Ash, and the Holy
Roman Empire.

\goto{Future Business}

Move to have all occurances of the word ``Pseudo'' replaced with
``comm'', comm with cabbage, and cabbage with pseudo.\\
Fails for lack of a second.

Move to attach a generator to pseudo, comm and cabbage so that if it
starts rotating we can use it to generate electric power.\\
Passes 5-1-4+Spehn

Move to have all occurances of the word ``Pseudo'' replaced with
``comm'', comm with banana, and banana with pseudo.\\
Fails for lack of a second.

Motion to replace all instances of cabbage with ``banana banana''\\
Motion to not and say we did.\\
Everything fails for lack of a seconds.

Motion to put the Library's petty cash fund towards the development of
a banana-cabbage no smaller than 3 cubic yards.\\
Passes 6+Slinky-5-2+Spehn


\vspace{12pt}

\noindent
Meeting adjourned, 1800-on-the-nose SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
