\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/03/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 3, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}
Bonus Pre-meeting Quote: ``It's a heliobacterpylori! It's so cute!!!'' -SEB

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Move to accept the minutes as being subversive
Passes 3-1-1+Spehn

\goto{Committee Reports}
\subsection*{BluebellComm/PianoComm}
We've discovered a way to get books covered. The real Bluebellcomm
covers unpopular books, and 'prentices cover the popular things
because they want to read. Shana Jackson and Brad Johnson each
covered three books to get to what they wanted.

\subsection*{MobComm}
Got two boxes and a bag from the SCC. A few hardcovers and proofs have
been processed. We have the pre-publication David Eddings, a Robin
McKinley, and a ``brick'' by Lackey and Co., as well as a pile of
other interesting things.

We have a third copy of the Dune short story, and two of them have
CDs.

MobComm bought a new kind of double... New Shelf code!

We have a whole series of ``Angel'' books, because a Long Long Time
Ago, JFC was told to get the Buffy books, but had not been aware that
there were also Angel books, so we got all the ones that should've
been trickling in over the last three years.

Discussion of why remaindered books are not always bad books, and
``The Book That Almost Killed Baen''

Our copy of the new Bujold book is a signed first edition. The door is
now a signed first edition---or so it claims, though we have not found
anything other than ``Jade's mark'' that could be a signature.  

Motion: invite T.C. Skinner to come and sign the Library\\
Passes 6-0-1+Spehn

Liz Barnes came in and donated a new book.

\goto{Old Business}
Jade is here! \\
Discussion of whether Jade's mark on the door was an ``axe-ident''
Albanian Motion vs. Brad (seconded by Malcolm for maximum irony)\\
4-4-3+Spehn

As requested at the last meeting, though more or less by coincidence,
JFC has requested a Bananimelephant.

ALGOL
\goto{New Business}
The Slinky is getting black spots again.\\
``I guess it's time for spring cleaning again''\\
``Do we have to take it to the southern hemisphere?''

Albanian Motion against Brad (again)\\
Does nothing 4-4-2+Spehn

We have a banana-colored heliobacterpylori.

Discussion of which buildings at MIT would be best defensible when
attacked by rampaging armies or a siege.  Brad suggests Draper.

Motion: Condemn the lack of banana-colored architecture around MIT.\\
3-0-4+Spehn

\goto{Future Business}
Someone called the library and threatened to donate some books, but
they'd need to be picked up in Salem.
We should be happy about this, but We Need More Room!

Discussion of cool things in Salem.

Discussion of cool Halloween display in Pearl Art in Central

KHA is evaluating our need for office supplies. We will be
investigating the possibility of finding more small orange dots.

We're out of Membership Cards --- APO has not gotten back to us, but
we've gotten 60 new people (not renewals) since May.

The Vice got us new pillows! Pillowcases are coming.
She also got a fine.\\
``Can she use it as a down payment?''\\

Albaniam Motion to Malcolm:\\
Passes 8-4-0+Spehn

``Is there any business at all?''-ED\\
``Somebody Sing!'' -JFC\\
``There's NO business like SHOW business, like NO business I KNOW!''
-Brad

Meeting adjourned as the Skinner flees the show tunes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
