\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/18/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 18, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order on Friday, April the 18th.  Ed Keyes is the president and skinner, while Andrew Clough if the fulfilled Onseck.  The minutes are read.

Motion:  Commend the Onseck for leaving out the boring stuff.  Chickens 4-0-4+Spehn

Motion: ``Condemn the Onseck for leaving out the boring stuff,'' then ``Condemn Onseck for not saying how the motion on his self esteem affected his self esteem,'' then ``Matrix Vote!''

Voting Goes:

\begin{tabular}{clr}
7& 2& 3+Spehn\\ 5& 6+squeak& 1+Spehn\\ 2& 5& 2+Spehn\\
\end{tabular}

This leads to a determinant of 27, so all motions pass.

\goto{Committee Reports}

John: ``I've got committee reports.''

Andrew:  ``If they're boring, I won't record them.''

John:  ``I'll whap you over the head with them.''

Mobcomm:  We're actually caught up on Dr. Who!

John:  ``Let the minutes note that someone is reading 'A Shoggoth on the Roof'.''

Discussion on what people report they do first thing in the morning.

John wonders how they can do things without getting out of bed first, but Jamie says that his bed flows out around the entire house in the morning so that he won't have to get out.  John thinks Jamie should fix the hole in his water bed.

Mobcomm$_3$:  We need a new run soon.

Theftcom:  Rotation.

Pseudo-Pianocom:  Dave Cora is resigning or something.

\goto{Old Business}

Derrick is in the library.  ``Hi Derrick!''

Unicorn Jelly is over.  It was a very good serious web-comic that everybody should read (hint, hint).

Finboard gave us almost as much money as we wanted for such evil schemes as magazine binding and a digital camera.

Discussion of windows, and minesweepers, with discussion of whether it is addiction or meditation.

Minutes of May 3rd of 1991 read.  Whee!  Jamie's first minutes.

Another discussion of ``The Core.''  The biggest problem: its the geophysicist that figured out that its pacemaker failures that are killing people.  Come see the core with eh geophysics group.  People qualified to heckle it properly.

ALGOL

\goto{New Business}

A cool official type person came in and said he'd mention us to the library director.

Marines are hunting Gazzels in Iraq with rocks for food.

We're getting a Laurel K. Hamilton book donated.  No need for the brown paper bag.

John:  ``My niece is a mutant.  She's off the chart in size, coming out of a small woman.''

Motion:  ``Send the marines lots of copies of Larry Niven's 'Folk Tale' so they'll know the proper way to hunt Gazels.''  Passes enough-not enough-a little+Spehn.

Motion:  ``Avoid the sequel at all costs.''  Passes 4-2-2+Spehn

Motion:  ``Solve the magazine color problems by rebinding everything in banana.''  Passes 6-5-0+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned 17:65 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
