\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/12/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 12, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; SEB is the pseudo-Kat.

Minutes read.

Motion to commend pseudo-Onseck for reading minutes thoroughly fails
for lack of second.

Motion to condemn pseudo-Onseck for failing to read minutes in English
with Russian subtitles passes 2-0-1+Spehn

\goto{Committee Reports}
\subsection*{JFC}
Covered 2 books, which is more than Bluebellcomm did.  Skinner should
choose length of time for covered books to be kept up during timewarp,
to extend their life.

JM asks if hardcover buying trip scheduled before IAP, no.  JFC gave up
due to lack of interest.  If people are found to come along, they will
go, but should not before Christmas because it's just so awful.  ED
offers to scrape people together first week of IAP.  JFC says there
are about ten new books to cover now.  JFC says if went now, there
would be Christmas crowds, JM suggests doing Christmas shopping now.

JFC wants to know what to get his niece, who is turning one year old.
JM recommends getting her Dune and/or Xanth and sequels every year.
JFC worries about getting busted for abusing a minor.


\subsection*{MobComm }
JFC says some books have arrived, you can cover new Jack McDevitt if
you feel like it (Omega).  5th Dark Tower book, bunch of random
Wildside Press stuff - they had a 2 day sale after Thanksgiving.

\subsection*{CoufComm}
JM: Books getting to Imperial College before break, or January.  We
aren't sure.  (stuff was rumbling down the hall) Surprised we haven't
gotten our books already, don't know how they were shipping but should
be fast.  Did not email to see if they got our stuff yet, just sent
mail that we had sent it.  JM will ask them.

ED asks how space appeals went this week.  JM hasn't heard, but ASA is
planning to stick Counterpoint, Rune, and (murg?) together.  This is
just going to swap people around, because a) Tech feels it uses that
room and b) in last rerooming, ASA said would not add more people to
Tech's contested space.  ED: Tech is effectively A-list again? JM:
Yes.  While ASA and CAC met with Safety Office and said Cambridge said
SMAC lockers can go in hallways, SO said you _can_ experiment with it,
in _one_ hallway, but not clear how much floor space this will free
up.  Lockers along one hallway don't obstruct evacuation, but if
lockers are everywhere activities will pile stuff on and in front of
and around them and it'll all be a mess.  

JFC demonstrates the Star Wars Jabba's Palace pop-up book.  It plays
music and they dance if you bounce the book up and down.  Technically,
he bought it off the 90\% off black hole shelf.  JM decries cheapness
of annoying music chip technology.  Discussion of an old non-sci-fi
greeting card.

\goto{Old Business}
JFC finished Clarke book.  Decent, but not especially good; cowritten
with Baxter (Clarke outline and Baxter book).  Good parts, but yet
another moderns-in-ancient-times book.  Premise better than typical,
but if you don't like the genre, don't read the book.

ED warns Jamie not to slice his thigh open.

JFC: It doesn't have the American Civil War in it.

JM: analogcomm will generate prototype schedule this weekend, put it
online.  See who can be crammed in then who didn't submit requests.


ALGOL
\goto{New Business}
JFC does not revisit Albanian Motion.  JM likes cooling off period.

JFC reads book jacket about some Aussie space captain with a dying
wife, blah blah blah, black hole.  JM is going to write a blurb:
"People in blurbs always have too many troubles or a perfect life.
I'm going to write a blurb: Bob always thought he had just enough
troubles."  JFC complains that thumbnail-size black holes around
planets are not accurate.  The black hole is orbiting the planet, not
actually around it, it transpires.

Discussion of small black holes and relative size of Earth and Sun.
Sun is 800K miles in diameter, Earth 8K, Jupiter 80K, according to
JFC.  This makes a 3mm black hole out of one of the above.  And the
sun is slightly more dense than water, we think.  A thumbnail-size
black hole is thus reasonably close to the earth.

JFC: There's still this extra banana on the Mobcomm shelf, for now.
ED thinks if we covered it in plastic it would be a Bluebellcomm
banana.

JFC asks for name for committee to dispose of excess stuff.  JM thinks
we should have a method, or someone actively pursuing one, to get a
name.  ED says, like dotcomms, we need a name and t-shirt first and
then a business plan.  JFC's company spends money to make products
instead.  JM asks, are they reaching milestones?  JFC says they have
framed thingies that say they shipped on time, because they didn't
redesign their circuit boards, not because as JM suggests they didn't
ship on/off shifts.  

So, about the committee.  There are bunches of boxes of excess stuff
to be disposed of, but JM says there are more than that.  And people
labelling these boxes should be accurate (i.e., Hasslecomm !=
Hasslecomm-to-be).  JFC asks what would be bad about confusing the
two, and JM says it would waste time, confuse inventory, and generally
suck.  JFC: H-T-B == Things That Suck?  I think the upshot was that
they are, but you should really label things what they are instead of
what you think they might be.  Really.  There are lots of flavors of
Hasslecomm-<foo> boxes and they are not the same; do the right things
with them and do not call them all Hasslecomm.  


\goto{Future Business}
In the future, ED will be in Tennessee over Christmas and back for
IAP.  He disappears on the 20th and comes back around 5th January.  He
will be on line.  

Stuff that needs to be submitted for fall is submitted?  Don't
remember if we spent all our publicity money for slides this semester
or not.  The LHE needs to turn in all his stuff and turn in copies
when they should be copies.

There is a staggering lack of business of any sort.  JM is taping.

JFC notes that membership rates have not changed for four months.  ED
says they shouldn't change very often.  

ED asks for volunteers to end the meeting.  

Miller motion from Sam fails, 3-5-0+Spehn.  

ED likes the Universe sort of the way it is.  

JFC says James Blish destroys the universe in one of his novels, sort
of well.  Brane universes colliding, except with antimatter.  JM says
it's like that, only it doesn't make as much sense.  Our universe goes
forward in time, an antimatter universe goes backwards in time, we hit
and everything goes away, but there's an actual impact point in space.
But they can't bring their furniture along, says JFC.  JM says it may
or may not be the big bang, but the characters don't know.  They're
just tourists.  JFC says lots of universes and some guy in a pocket
universe is supposed to blow himself up, JM says you can maybe change
the new universe and this annoys him, because people trying to
influence it were being random, like God rolls 3d6 to determine
parameters of new universe and they tell him to reroll no matter what
he gets and they don't know what either means.  Then they get the
book, which will probably not help any of this make any more sense.
Now they have two James Blish books (Cities in Flight and Triumph of
Time) and it is not helping, except that we have steady state
universes in one spot.  JM: At least it's an inevitable collision in
three years.  In most science fiction they'd be stopping it.

The pseudo-Onseck is confused whether diaresis is the production of
urine or something like an umlaut, but suspects she just can't spell
it.  ED is not going to read this series.  And Blish's people
apparently do not understand simple algebra.  And Cities in Flight is
a Baen book, because it has an exploding spaceship on the cover, which
is an exploding city too, being flying you know.

JFC attempts a Miller motion motion, which fails for lack of a second.

ED wants someone to end the meeting.  JM is still reading the Blish
book.  "Each person gets to be their own Big Bang."  JFC, on sending
furniture one microsecond into the past: "Humans are more predictable
than tables."  This is all fifties stuff; that's why continuous
creation is cool because inflation was an 80s thing.  

JM is still reading.  JFC is waiting until end of universe to make
November motion.  ED wonders what kind of universe would be made from
a banana floating in space.  

JFC wonders what we will see when we finish mapping out cosmic
background radiation, some kind of message.  JM: "Whoops."  

JFC makes third miller motion, passes 4-2-1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
