\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/12/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 12, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read retroactively and recursively for continuity assurance.

Motion: Commend the minutes for being extremely brief.\\
Passes due to lame non-voters, 3-1-1+Spehn

\goto{Committee Reports}
\subsection*{BondageComm }
Learned to make binding slips, and made some

\subsection*{MobComm}
Ordered Books, and will order more. Also, MobComm is waiting for
British Books, which may be late, or may be UA hostages.

\subsection*{BluebellComm}
Looked longingly at the shelves. JFC covered three books.

\subsection*{War Council}
Office Space Wars starting again. Pfc. ARM  has clever plans. Some
not-so-clever plans suggested.

\subsection*{CoufComm}
Progress!  We're going to stop buying British books in preparation for
our annexation... er, ``arrangement'' with the ICSF

\goto{Old Business}
Discussion of strange animals and electricity.

ALGOL

\goto{New Business}
We got a Bananakoala, but the tag just labels it to the Genus,
``Bananabear''.  It has been hung from an Americam Flag, which seems inappropriate.

Discussion of appropriate numbers of stars and stripes for a Flagg
hung in the Library: 23 and 42?

\goto{Future Business}

Discussion of annexing Britain, Puerto Rico, and other strange
fictional places.

Motion: form a committee to draft the constitution and create the flag
of Bananimalia. \\
Passes 7-2-3+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
