\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/11/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 11, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
The MITSFS meeting was called to order on Friday, April the 11th at 1700 SST.  Ed Keyes was the President and Skinner, while Andrew Clough was the slurpy loving Onseck.

Motion:  Condemn the minutes as ``inaccurate, inaccurately pronounced, and inaccurately timed.''  Passes 6-1-1+Spehn

Motion:  Condemn the Onseck as having low self esteem.  Fails 0-3-0+Spehn.

\goto{Committee Reports}

Bluebellcom:  Not lame!

Mobcom:  We got a square British book.  Ed: ``Its metric.''

Motion:  Condemn the English time cube conspiracy. Passes 9-0-1+Spehn.

Motion:  Create a new tradition of reading random past minutes.  Passes 9-0-1+Spehn

The minutes from April 7th, 1989 are read.

Motion:  Condemn past minutes as being incorrect.  Fails 5-5-1+Spehn.

Motion:  Condemn Mobcom for being loquacious.  Passes 10-Tailspin-2+Spehn.

Mobcom$_2$: <Text deleted for being boring>

Vox-sciurium:  John's mother had a squirrel stalk her, following her all the way to California.

It seems a weird guy came into unified and tried to talk to the class about how small people are better drivers than big people. 

Motion:  Condemn bondagecom for being forgetful and loquacious.  Passes 7-5-1+Spehn.

\goto{Old Business}

The Stapler is looking very diabolic.

ALGOL

\goto{New Business}

Now Andromeda's is no longer ``Australia's Newest SciFi Magazine'' but now ``Australia's Pulpiest SciFi Magazine.''

Finboard is getting our proposal for bondagecom funding.

Alohalenscomm:  We what a digital camera too, oh, and Brian has got a petter picture up.

The large Rainbow Slinky is no longer a biowarfare experiment.

Motion:  ``Call it the Kat colored Slinky form now on.''  Passes 5-4-0+Spehn.

Kat:  ``No one is allowed to think.''

\goto{Future Business}

NASA made the decision to start developing a space plan.
Discussion of bad movies, like ``The Core'' or ``Armadillo in My Pants.''

Motion: Neal Asher shall be given a banana for having a book named ``The Skinner.''  Fails 7-0-7+Spehn.

Motion:  Condemn John for saying bad things about bananas. Passes 15-0-1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned 17:54 SST.

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
