\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/15/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 15, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent

MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding.

The minutes are retroactively read, for time stream continuity.

\goto{Committee Reports}

No Committee Reports were recorded.

\goto{Old Business}

Andrew (ALC) walked into the meeting. \\
``We should start Andrew pseudo-Onsecking'' -JM
Andrew becomes the pseudo-Onseck, by Skinnerial Decree.

``Step 1: Start Meeting \\
  Step 2: ...\\
  Step 3: Profit!'' -ED

\goto{New Business}

We haven't heard anything about any new (good) T.V. series.  Live
action T.V. is a wasteland.

Kat Allen and Jennifer Clay, we have your checks waiting for you. Come
on down!

Discussion of movie to book to movie to T.V. to ... conversion, and
the wrongness and potential paradox therein.

Jamie (JM) has an idea that, if an author allows a contradiction to
creep into a movie adaptation, then everything follows from a
contradiction, and the author clearly doesn't own everything, so they
lose all rights to the materials.

\goto{Future Business}

Discussion of expendable grad students,  (unintelligible writing -- Bardic?)
knowledge, and shelving.

Something with banana in it passes, 2-0-0+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 18:12 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
