\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/21/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 21, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding; John Carr, pseudo-Kat, recording.

Bonus pre-meeting quote: "There's also no meeting happening"

Bing!

"Now there's a meeting."

The minutes of the last meeting were read.

JM (Jamie Morris) moves to commend or condemn the minutes as "blah blah blah". Motion passes 7-2-Spehn.

\goto{Committee Reports}

ED tells BGJ (Brad Johnson) "You're not allowed to use Diebold electronic voting machines" after he votes twice with the same limbs.

Motion to use Diebold machines for the rest of the votes. No second, but passes -11-44-1+Spehn.

SEB (Susan Born) brought Russian candy for the Assassin Game, Krazny Oktyber. She is the quartermaster, and the quartermaster always has
candy.

pseudo-jourcomm[JFC]: TZ RSN. Less real, more soon.  It's Brad's fault. In the future it will be totally imaginary but right now.

pseudo-bluebellcomm[JFC]: I covered some books, bluebellcomm didn't.

mobcomm[JFC]:  JFC describes his plan to keep panthercomm busy every week, buying new books from the Space-Crime Continuum, remainders from an online store, etc.

Coofcomm[JM]: Today is six weeks since the M-Bag was mailed to ICSF, and theirs to us, so it is no longer too soon for the books to arrive.

A discussion of British books and conversion rates follows. JFC hasn't ordered any books from Amazon UK since the last time he ordered.

JM: "I can't remember my patronymic or last name. I have to think a bit to remember my first name."

"Does a lover's tiff cause a disaster?" -- JM

"No, it was a disaster." -- Andrea

"No, it was just entertainment." -- Susan

mobcomm 2: SCC trip today. Mobcomm went to Skinner State Park and saw chipmunks and squirrels but no bears.

Motion[BGJ]: have Russian candy at all meetings. Passes 4-0-2+Spehn.

\goto{Old Business}

BGJ successfully read an Infocomm book, Wishbringer by Craig Shaw Gardner. "It was rollicking fun." But not that good. Brad calls Adventure an Infocom game, but it wasn't.

We have an old ex-keyholder in the library who hasn't been to a meeting in a while.

JM: NESFA has created the position of Hal Clement Science Speaker at Boskone to bring hard science to the con.

"This is just an unusual meeting."

\goto{New Business}

BGJ: "What's this box of Lorna Doons here for?"

SEB: "Contraband."

Brad is trying to catch a ball with a giant Slinky. This is about as easy as using the transporter field in Expendable.

Minicult: Cornell U. Physicists have used a laser beam to pluck the strings of a silicon guitar. It twangs at about 40 MHz. They have also made a nano-drum and nano-xylophone. MIT people made a microbible, the New Testament inscribed on a 5mm square silicon chip.

ED was told not to eat anything at the nanotech conference.

JFC reads from Acorna's Triumph, "The Triumphant Conclusion" to the Acorna series. We have four months to prepare.

Women like Gor.

\goto{Future Business}

Thanksgiving is coming next week.  The Student Center will be closed on Thursday.

Finboard will decide our budget next week.

War Council: tentative ASA plan is planned, depending on permission from safety office and CAC "to do certain things".

BGJ, in the green chair, feels really oppressed by the bananimals. The banelephant is staring at him.  He hasn't been sleeping much. "It's not paranoia if the elephant really is out to get you."  The banelephant is bright yellow, and therefore safe, because yellow means it has fed recently.

Miller motion. Second. Fails 0-10-2+Spehn.

Look, a second Miller motion! No second.

Don't let Brad sleep until he finishes the Crisis! scenario. 4-6-Spehn. "I'm incapable of not sleeping until then."

Motion: Give the pink banana elephant a pivotal role in the Crisis scenario. Passes, 6-0-2+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1807 SST.

\vspace{18pt}

\centerline{Sloppily submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
