\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 13,(ooh) 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion to approve the minutes as being banana-colored\\
fails 7 - 9+Space noises - 0+Spehn

\goto{Committee Reports}
The former Onseck reports that he could skip the meeting, and wouldn't
have to tell anyone. (Of course, he is here anyway)

\subsection*{Bluebellcomm:} There is a plan. Once the boxes are out of the Onseck's
apartment, the books will get off the shelf.

Motion:  Commend Bluebellcomm for following the trickle-down theory\\
Fails 3-7-4+Spehn

Motion: Free Silver! Down with the Fed!\\
motion passes 8-2-3+Spehn

The Onseck is confused, but the LHE and Vice began to sing.

The Gor Books tried to escape! Discussion on whether Duct Tape really
is forever.

\subsection*{BondageComm}
The Slink-y bought no magazines.

Discussion of trimesters of college.

\goto{Old Business}
The Vorkosigan Books are just as good as everyone says, according to
the LHE. (Unfortunately, we can not number the prequel -1, as the dex
won't let us)

Motion: Condemn whomever is responsible for us not having a
circulating copy of Brothers in Arms (Vorkosigan 2)\\
Fails for lack of the Skinner hearing the second

The ongoing shelving plot has moved forward by several sets of shelves.

Motion: Commend Jamie for obscuring the Perry Rhodan books\\
Passes (enthusiastically) by Skinnerial Decree!
 
Pandemonium now has Plush Cthulu and Plush Nyarlethotep\\
 (http://www.toyvault.com/cthulhu/nyarlethotep.html)\\
They also have access to more plushies... Hastor is coming.


Motion: Acquire the plushies for the Library\\
Passes 12-2-3+Spehn

Discussion of the omniscience and mind-reading powers of Google

Discussion of ``Hello Cthulu'', Cthulu in the ``Hello Kitty''
universe. The Vice finds it for us. \\
       http://doggerel.wuice.net/comic/022.gif

ALGOL

What about the lack of usual debate?

\goto{New Business}
Discussion of slumber parties and whether Cthulu would be allowed at
one. ``He wouldn't think of it as corruption, but if you were a human
and you wanted to name the effects, that might be one you come up
with'' -JM

Discussion of supply-your-own-explosives exploding parrots.

Motion to add to the order of plush Cthulu ``The Beast of Argghhh''\\
http://www.entertainmentearth.com/prodinfo.asp?number=TYVMP011\\
Passes: 7-1-3+Spehn

``Disturbing nucleates more Disturbing! Wait, did what I say even make
sense'' -Vice

``It's okay. We'll put it in the minutes and let posterity figure it
out''-ED

``I think the minutes have already used up all the slack posterity is
going to give them'' -JM

\goto{Future Business}
 
Motion: Condemn the Anime Club for having banana-colored posters\\
Passes: 11 - 1+spacenoise - 3+Spehn

\vspace{12pt}
 
\noindent 
Meeting adjourned, 1730 SST.
 
\vspace{18pt}
 
\centerline{Respectfully submitted,} 
\centerline{Kat Allen,  Onseck}
 
\end{document} 
