\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/24/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 24, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Move to approve the minutes as being Shakespearian\\
Fails for lack of a second

Motion: Quack\\
Passes 5-0-1+Spehn

\goto{Committee Reports}
\subsection*{Pseudo-Jourcomm}
JFC asked about the mysterious Wednesday, and apparently he meant
Wednesday October 1, 2003.\\
``So now we're missing specific deadlines instead of general
deadlines'' -ED

\subsection*{Skinner}
Processed things on the Skinner shelf\\
We have some Choose Your Own Adventure books now.
\subsection*{MobComm}
JFC reads a strange sentence from the back of a book that he got from
the remainder place in Waltham.  ``an earthbound comet named Kali''...

We got an Amber prequel from a place that specializes in bad books.\\
We have a 119 page Terry Goodkind book. The meeting is collectively in
shock.

``I really enjoyed 'Wizard's First Rule', when I first read it, but
every book since has been exactly half as good as the book before, and
they're on about book 8...'' -ED

A horrible Pun from Malcolm results in an Albanian Motion\\
Passes 6-1-0+Spehn

\subsection*{Bluebellcomm}
Will work on getting at least the new Pratchett covered.

\subsection*{Pseudo-plantcomm}
JFC says that the leak we had a few years ago is just like the new leak.

The super washer-buffer squeegee machine was back to clean up the
Technique flood, which was compared to a mini-zamboni.

Motion: Charter a committee to evaluate the possibility of taking the
ice rink as Library space.\\ 
Passes: 6-1-0+Spehn

\goto{Old Business}
KHA email'd the Salem donator, and will try calling her.

CJ Cherryh books are really popular donations.

ALGOL without a usual trip to Khatavar.
\goto{New Business}
No new Bananas this week, but there are some new people.

The CPs have decided that sending their officers to visit 4-5 FSILGs
per night is a good idea.

``I assume they are checking for alcohol, freshmen and other
controlled substances'' -BTS

``If freshmen are outlawed, only outlaws will have/be freshmen'' -ED

There is a Dead Chicken mode.  If you don't have a number you need,
you just pick something and move on. It has incredible performance.

Amazon has taken 120,000 books and made them full-text search able, and
they are working on putting in more.  ED searched on himself, and
found that someone had quoted a section of his web-page in a book.

ED wrote the original HackMaster, and is thus a scapegoat for the loss
of millions of bytes of data on Palms.\\
JFC, looking at the web page, notes that the page was last updated in
1998.


BTS motions that, given JFC and other people's inability to use
computing machines,  we start acquiring all the documents relating to
``Interface Guidelines'' which claim that normal people might be able
to use Computing Machines, and reclassify them as Science Fiction.\\
Fails for lack of a second, with the Albanian-translated comment that
nobody in the Society knows what a normal person looks like.

New people are checking out books. They tried to apologize, but we
told them that we *wanted* books to be checked out.

``That's Chinese with a Swedish accent, in Albanian'' -ED about
Malcolm.

Discussion of HackMaster the Game, HackMaster in ``Knights of the
Dinner Table'', and AD&D 3rd Edition.

JFC relates a favorite quote from Project Athena about doing UNIX on
old Macs: ``Here is where it patches the ROM''

BTS and ED reminisce about the Palm OS and the Mac OS, and how each
have evolved.

Our Illustrious Skinner is featured on a webpage, ``between a generic
       teenage basement hacker and a serial killer'' -JFC\\
       http://www.item.ntnu.no/~peterc/pilot/ga/gallery.html


Motion: to compensate all people who make applications for teensy
weensy software with a banana\\
Passes 8-0-4+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1734 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
