\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 7, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

The Onseck stumbles over finding the minutes.

Motion to approve the minutes as empty.
Motion chickens 3-0-5+spehn

Minutes read.


"Motion regard minutes fragmentary good" -JM\\
Passes 9-2-1+Spehn

Move to note that Kat is the very model of a modern major onseck\\
Passes 7-0-4+Spehn

\goto{Committee Reports}

\subsection*{Bluebellcomm}
The shelf was empty!  Apprently, though, there were some things in a drawer.
New people have been assigned to Bluebellcomm.
J needs to be trained, but KCR has already been trained.
There exists 9.25" high material, but it only comes pre-cut in 19" lengths.
We'll probably get some, and inquire whether they have rolls.

Discussion of book sizes.

\subsection*{Onseck}
The Onseck is going to be buying things from the Library Store. 
Discussion of shipping things to Alaska and whether we can aquire
floorspace.

Discussion of the thermodynamic properties of books.

\subsection*{Pseudo-PlantComm}
There was a flood, and there are some hardcovers that need recovering
because of it. Supposedly, it has been fixed---they turned a valve that turned off
the leak.

Discussion of overdue fines and the people who get them.
Motion to approve complementary mental defects (i.e. absent-mindedness
and obsessive-compulsiveness)\\
Passes 12-3-1+Spehn

\subsection*{Pseudo-LHE}
Electrons are being transferred from us to CopyTech.  This is probably
more work than just handing them money.

\subsection*{WarCouncil}
ARM says ``Grr.  People are very very not interested in going to
Walker, even if we bribe them''\\
Discussion of whether they were asked if blackmail or threats would
work better than bribes.  They are searching for more bribes.

They are also working on an iCampus proposal to get a closet with a
rack and many many servers so that people whose offices are justified
on the grounds of ``but we have a computer!'' can be consolidated.

There is no space in Stata. Brad suggests that \emph{The Big U} is a
handbook on taking over campuses, except for the part where they blow
things up at the end.

``But you wouldn't know it was Stephenson, otherwise!'' -JM

Discussion about Walker, its long-delayed renovations, and how much it
would cost to make it not flood.

Discussion of charging rent for student groups such that the
coffeehouse is rented as student group space.

The UA has indefinitely tabled the 5th floor plan.

JFC tells us about squirrel-eating grannies.

\subsection*{MobComm}
Almost didn't manage to get a report in. Is buying things from Out West.


An interesting referendum passed Out West: 
Measure G\\
``Vote for Bolinas to be a socially acknowledged nature-loving town
because to like to drink the water out of the lakes to like to eat the
blueberries to like the bears is not hatred to hotels and motor
boats. Dakar. Temporary and way to save life, skunks and foxes
(airplanes to go over the ocean) and to make it beautiful.''

Yea: 314\\
No: 152

Motion to make Kat the committee to build rockets to get the Society
off this Planet.\\
Passes 14-2-)+Spehn

\goto{Old Business}
JM sat down with Matlab and some numbers, and discovered why shelving
things in SR is harder than he thought: \\
SR has been expanding at 11 times the normal rate. 
(Vance and a bunch of proofs from SCC account for the majority of the growth)

There are some bokes under the table which have been labeled JKC for
years, so they should be labeled in some other manner, or moved, or
something.

Move that the Society hold a garage sale\\
Passes 6-2-1+Spehn
Move that the Society buy a garage\\
Passes 9-2-2+Spehn

ALGOL
\goto{New Business}
We went and picked up the donation from Salem.  There were 7 boxes,
mostly SF, but also some pulp. There are definitely repeats in the
set.

``I was really disturbed 6 or 7 years ago ...'' JFC\\
``No, you've been really disturbed for longer than that. Don't try to
pass it off as a one-time occurance'' JM

Move to commend JFC's grandmother\\
Passes 10-1-3+Spehn

``No, it's my mother who likes chickens''\\
``Do you egg her on?''\\
Albanian Motion for Malcolm\\
Chickens 3-3-7+Spehn\\
``Guess that's egg on your face!'' -Brad
Albanian Motion for Brad
``Let's not get trigger happy''-JM


There are visible results of the shelf extensions in the hall, drying.

There were big solar flares recently.  The largest solar flare ever
just went directly away from earth.

Move the Society run and tell the king.\\
Move that the Society recognize that Dewey beat Truman, even on the
show.\\
Fail for lack of seconds.

Apparently, due to the solar flares, NASA had to reboot the probe
going to Mars.
Discussion of whether the Martians have been shooting down the probes.

Motion to not be talking about Science Fiction\\
Fails 5-8-1+Spehn

JFC reads from a Richard Calder book.\\
Albanian Motion for Calder.\\
Passes 8-Calder-1+Spehn

We discover that this has not stopped JFC from talking, just Calder,
but that prevents the titles of Calder books from being read.

Discussion about whether the apparent W is actually a Venutian Runes,
driving JFC mad, whether JFC is North Korean, and mentioning that BTS
is sitting within arms reach of the Gor books. JFC is not frightened
by the threat.

Motion to have JFC read banana of Gor\\
Passes 6-3-3+Spehn

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1808 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
