\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 28, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}
Bonus pre-meeting quote: ``But we don't have a pre-meeting quote!''
``That's it, right there!''
\noindent
MITSFS meeting called to order, ``17:00 for some loose value of 17:00''
SST, Ed Keyes, President and Skinner, presiding; SEB (Susan Born) is
the pseudo-Kat, recording.
Onseck should not type while reading minutes from previous meeting.

During minutes, Y moves to censure JFC for not ordering any books since
the last time he ordered.  Motion passes 4-3-2+Spehn.

Discussion of banelephant tipping during minutes reading.

Minutes read.

Y moves to approve the minutes as discouraging color-blindness.\\
Motion passes, 4-2-yellowpinkcolorblindness+2+Spehn.

Motion to make elephant stop staring at Jacquie fails for lack of a second.

``Its eyes follow you around the room.'' -ED
``But its tusks don't.'' -JFC

\goto{Committee Reports}
\subsection*{Bluebellcomm}(JFC) 
Bluebellcomm and pseudo-Bluebellcomm (Karl) covered a lot of books
this week.  Books covered 4 weeks ago in to-be-shelved pile.

\subsection*{Made-up-committee}(JFC)
 There are 99 books to be shelved.  Ed took
care of one, Susan may take care of another.  Still plenty of work for
Bluebellcomm to do.

\subsection*{MobComm}(JFC)
is waiting for Susan to catch up.  Despite failure to
get new books to overload PantherComm, plot still succeeding because
PantherComm did not process all books last week.  New books should
arrive in the next week.

Motion to create committee to do everything obviously duty of a
committee but for which no committee exists fails for lack of second.
What Star Chamber is for.

A clipping is handed to JFC.  It is a cartoon. This distracts him long
enough for someone else to get in a report.

\subsection*{LHE}(ALC)
 Finboard did give us money; 60\% of what we asked for, reasonable
compared to our past performances.  We didn't ask for a whole lot, so
our \% is higher but number lower -- about a thousand \$ for books,
subsidizing picnic and LSC slides for spring.  JFC shouldn't spend it
all this month, but can continue spending as he's been spending.  ED
hasn't seen what he's been spending, though.

\subsection*{Pseudo-LHE}(JFC): 
Movement with reimbursements -- they go in, checks come back, checks
haven't been bouncing.  The envelope has streamlined the process,
possible for people to figure out what all the forms mean.  JFC
wonders if typing has anything to do with what we're saying.

\subsection*{Unnamed Committee For Good Reason}(JFC) 
JFC wants a name and a committee responsible for evicting books
from library once provisionally excreted by Hasslecomm and Magdex,
like for sale books.  ED wants to stick MHG on it.  JFC just wants it
to be named.  Y says excess books, new people joining, we should pick
out less bad extra books and give one as present to everyone who
joins.

ED: ``We'd get them back as donations.'' \\

 JFC: Discussed with AMB, who has occasional unpredictable access to
unlimited supply free magazines, overstocks of three big SF magazines.
How many copies should he get for mitsfs?  Would want only 2 or 3, but
if had 20 could give away to old members, new members, or people.

ED: Does Victor Hugo accept trade-ins?  Can we get rid of books for
store credit and pick up things we want?\\
JFC doesn't know.  \\
Y: Does Macintyre and Moore pay enough for the trouble? \\\
JFC: Close thing when looked into a few years ago, places didn't want
to give significant money or credit.  We hoped shipping them to
Britain would help.  I offered non-SF to Space Crime Continuum, not
interested in mysteries.  We talked about eBay and should put someone
into it.  \\
Y: Used book store on Newbury has some name, may be there,
not Victor Hugo.  Down from sidewalk.\\
ED: Pandemonium has a ton already. \\
JFC: Pandemonium's books were flushed down black hole.\\
ED: How does it work? \\
JFC: You throw your books down the black hole, they pass
through the singularity and are discraded.  Black hole has six layers,
event horizon is 5th, 6th is warp.  Books put on top shelf at 5\%, 15\%
each layer.  If they don't sell at 90\% off, they are discarded.
Returnable books returned at 45\% off.  Books unwanted put on top shelf
black hole and nature takes its course.  A decent bunch of our books
lately came from Pandemonium black hole.  Doubtless more is there.  I
should have said this a month ago.  I went to that remainders place in
Waltham, and a MITSFS member was manning the register.  DSR,
Dan-something.

\subsection*{Pseudo-Theftcomm}
(JFC): TIF has rotated, November 18.  People who overflowed were given
credit if appropriate.  There was a time when I was not TIF leader, as
Emily had four hours on me.  This has since been rectified.  Bill
caught up but did not exceed, 2 keyholders sucked under.  

ED: Armenard has put in lots of ours on rerooming.  \\
JFC: Garbage collection has compacted keyholders into contiguous
columns.\\
ED: Not to imply that any of our keyholders were garbage.

\subsection*{Pseudo-Pianocomm}(JFC)
JFC: We have active prentices.  Discussion of various prentices and
doing and thinking about doing and not thinking about doing committee
work. 

Motion for society to think about commmending prentices for some of
the above.\\
Passes, 3-0-0+Spehn.

\goto{Old Business}
Usual motion, usual second, usual vote, usual result.

ALGOL
\goto{New Business}
JFC: Has albanian motion for Malcolm been put into minutes yet?  Name
of committee to deal with stuff we want to dispose of, I've been
putting more clear labels on many boxes with specific committee to
which box belongs, and I don't know what to label hasslecomm output
boxes.

Names suggested, like things the pseudo-Onseck can't spell and are
thus not recorded.  Tabled.

ED: We have new membershiped cards, new and improved with society
logo.  Gotten from Kinko's, good job copying but off-center in
places.  Y: So are we.  ED: We have about 1200 of them.  We'll get
through that stack before my term is up.  (ED has signed about an inch
of membership cards.)  We signed up 60 new members over past month or
so and have a backlog of people who need cards.

JFC: We still have no small orange dots.  The Onseck has been
notified.  They are allegedly hard to find.  Not the
micro-.5centimeter dots, .25, .375 of inch.  Medium dots are... very
hard to find, and .75 inch.  We have no dots of any color that's
smaller.  If reinforcing things were orange, we could use them.  ED:
And didn't have holes.  Y: Could we dye the reinforcement things?
They're partially made of cloth.

Onseck is confused by lack of old business.

JFC reads ironic author blurb on SM Stirling, who is claimed to write
``best straight-on SF,'' which is ironic because 1) the novella is
nominated for a Sideways award, and 2) Stirling has a lot of
lesbians.  The reviewer is amazing.

Y says there is children's book about school 86 stories tall with 1
room/story, title ``Sideways Tales from Wayside School.''  Unrelated.

JFC: Mary Gentle blurb: ``Her stories are never comfortable.''
Walter John Williams ``exhibits tenaciousness.''  Y: With friends like
this... ED: He submits stories again and again until accepted by
editor

Y was in H$^2$ hour ago, traffic stopped by accident in which number 1
bus collided with another \#1 bus.  JFC: Five minute spacing sometimes
not enough.  Exciting damage?  Y: Vehicles no longer have fenders to
bend.  JFC has seen car hit guard rail and slide until bumper fell
off, in old days when cars had bumpers.  Alfa-Romeo, at least 20 years
old.  Y: Nothing fell off, when I left vicinity heard bus drivers
talking about fact nobody had gotten passengers off the dinged bus.
JFC: Bus accident in NJ, people rushed to get on bus so could claim to
be injured in the accident. 

JFC: We have a banana colored thingy.  It's labeled as such.  ED
presumes it to be a safety papercutter.  It's on the corkboard.  JFC
tries to test it on a piece of scrap paper.  Gravity does not help
him, but he does cut the paper.  He deems it not sufficiently
convenient, and declines to cut a piece of silk in midair.  ``In Japan,
the hand is a deadly weapon, but it can't cut a tomato.''  ``In China,
some martial artists trained with the tiger claw, which can cut a
tomato if it's small enough.''  ``Neatly?  In the commercial, the tomato
did end up in 2 pieces, but not in a very edible form.''  ``It does work
on coconuts...  After he went through a couple of bricks.''  ``A brick
is brittle and a coconut has enough resilience it could hurt you.''  Y:
Coconuts don't break falling off trees.  JFC: Why make the inside
edible if nothing's supposed to get in and eat it?  The inside happens
to taste good to baby coconuts, and that animals like it is a
coincidence.  ED speculates on coconut farming.  JFC thinks of
stereotypical island with one coconut tree in middle.  Have
generations of shipwrecked sailors cut down coconut trees that didn't
taste good?  Plenty of time for selective breeding.  Inedible trees
become boats.  ``A sailor is only a coconut tree's way of making more
coconut trees.'' -ED Much not commenting on subsequent comments
happens.  Y saw division of fruit-eating birds into 2 categories, one
digests only pulp, one digests seeds too.  Seed-eaters are
counterproductive in terms of getting new plants.

What is the seed in the coconut?  It's the coconut itself, not
supposed to be eaten.  Gets washed into ocean, lands on a beach, takes
root and grows a new tree.  Like a potato?  Y: Coconut milk morphs
into-- JFC:  coconut cheese.  Jacquie: If you shake it enough you get coconut
butter.  Not a lot of milk in a coconut, you have to squeeze to get it
out.  Y went to demonstration on Oahu, how to demonstrate coconut to
get milk out, let tourists drink and then told Hawaiians don't drink
it because it's a laxative.  You cook with it.  Some tourists try it
twice.  Was suspicious when told native word for penetrating tool is
sharp stick.  Jacquie thinks it splits and the roots go down, not like
a potato, more like a conventional seed.  Jacquie likes the delaware
quarter with the tree.  

Y was staying for summer vacation where hordes of red squirrels were
in trees and put out 5 pounds of peanuts.  Then walnuts.  Squirrels
were ok, but chipmunks weren't.  Jacquie has never seen a chipmunk.
Many suggestions for chipmunk viewing were given -- parks, blue hills,
Y's backyard, Colorado.  Y encountered chipmunk in park in Newton by
Charles on very well-worn-down path, was very sneaky and got up close
to chipmunk, who chirped and zipped away and clunked bottom of hole.
Popped back up and started yelling ``I'll get you, I'll get all your
relatives!''  Amateur rabbit climbed out of bush to get away from
ferocious chipmunk.  Chipmunks used to be chipping squirrels, because
taxonomists didn't know what to make of dinosaur bones.  They are some
sort of giant lizardlike thing.  Some of the species names were
different.  Scientific names change; duckbill platypus used to be
something I can't spell paradoxis, but now it's something else.

People not JFC have heard of the capybara.  If one were at Jacquie's
house, it would gnaw the legs off her table.  Some are at the Franklin
Park Zoo.


\goto{Future Business}

JFC: The last world war is coming when the aliens invade Missouri.

Y: I know God hates Kansas, but Missouri?  Is there any spot in the
world where people wouldn't mind if the aliens invaded?

JFC: <reads book jacket more> All of the world minds.

ED: I'd let them have Washington DC for a while.

Y watched Day the Earth Stood Still again, lines he'd forgotten about
authorities' failure to find alien: ``-They're only human.  -They're
not human, they're Democrats!''  MITSFS used to show it a lot, but
stopped showing moves by early-to-mid-60s.  Jamie found references in
still not banned research.  Would be competition with LSC.  Jacquie:
but we could show good movies!  Y: That would be unfair competition.

A member had quicksilver out overdue and mailed it back.  \$8 in
postage.  Book probably \$25 or so.  Would it fit in flat-rate
envelope?  You can fill it up with neutronium if you want, but if it
fits in the envelope you mail it at the flat rate.  It holds a pound
or two of paper, but if you wanted to mail metal and you could keep it
from breaking out of the bag... Like when they found way to refine
zichronium cheaply and mailed samples to customers in envelopes; when
you pass through automatic cancelling machine the machine blows up.
We don't know why finely powdered zichronium does this.  Finely
powdered iron is pyrophoric.  

ED: Rooming reassignment in progress, no significant updates yet.  ASA
giving report Soon.  Cross your fingers.  JFC: Is it better if you
cross pairs of crossed fingers?  ED: You need an odd parity.  The
largest odd number of crossing is best.

Motion to cross banana fingers fails for lack of a second.

Motion to integrate finger dfinger over crossing fingers fails for
lack of a second.

If we move, it'll probably be over IAP.  All of IAP.

JFC: JM said year's worth of work for Panthercomm and Bluebellcomm in
boxes.  

Who's Neo Opsis?  Editor of new Canadaian SF magazine.  Actually is
just Opsis, but first magazine went under, so this is Neo-Opsis.

Mary Gentle is an expert swordfighter, says the jacket by way of JFC.

Miller motion\\
fails 1-4-1+Spehn.

Cricket noises from Jacquie, singing from Y.  

Collection of short stories we didn't pay the price for by John
Wyndham is discussed.  This is the sort of book we should have,
because members won't.

Second Miller motion\\
Passes 6-1-1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1758 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
