\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 4,(BOOM!) 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Motion to condemn last week's minutes as being not-nearly long enough \\
Passes 5/3/1+Spehn

\goto{Committee Reports}
\subsection*{PantherComm}
The shelf of Panthercomm and Bluebellcomm is all full.

\subsection*{MobComm}
Mobcomm failed in its Harry Potter policy.  It paid too much for Harry
Potter, but that's okay since ``it's the Library's money, and it's my
job to spend the Library's money.  If the Library has bad taste,
that's not my fault'' -JFC

``The Library has poor taste. This is not in dispute'' -ED

Motion to set up a betting pool for how many Harry Potter books will
be donated. Discussed, but fails for lack of a second.

NJ blue laws prevent bookstores from being open at midnight on a
Saturday, so the ``poor'' people in NJ had to wait for Harry Potter
until 9 AM.

Motion to commend the government of NJ for protecting the moral
innocence of its constituency\\
Passes 8-0-1+Spehn

Discussion of books which tell you how to end the world by playing
Beethoven's 9th Symphony.

The MobComm mobile lost a battle with a speed bump today. All the oil
is now on Vassar street.

\goto{Old Business}

Motion to commend the speculative fiction act for promoting government.\\
Passes 7-0-1+Spehn

Move that all future minutes should have a section reading ``the usual
minutes''\\
Passes by Skinnerial Decree

Minutes from 10-15-1999 read very quickly.  JFC ( who was that day's
pseudo-onseck) says ``That's a lot faster than I remember that
meeting.''

ALGOL to prevent more singing from Malcom

\goto{New Business}
They're going to re-enact a big battle later tonight, in about 4
hours.\\
``Do you know which one?'' -JM\\
``Moscow is traditional'' -JFC\\
It is explained that the 1812 overture is about the Battle of Moscow.

\goto{Future Business}

``wheeeeer BOOM!'' -Malcom

``I live near the Charles river. Not this one, the one upstream'' -JFC\\
``Is that not the same river?''-ED\\
``It is, but not such that you can tell'' -JFC\\

The explosions start at 10:30. Discussion about it being late, and how
this is likely for advertising reasons.

Discussion of the SuperBowl.

Discussion of glow-in-the-dark football, with no illumination.

Discussion of the glowy stock-market desk toys, and whether we can get
them to flicker in ``Pokemon Time'', 13 cycles per second.

JFC is very upset that they need power, and are not powered by
vibrations, or like Magic 8 Balls.

Motion to condemn the stock market for being bananna colored.\\
Motion does nothing 3-1-3+Spehn

Estonian wife-carrying competitions are upsetting the Finnish, reports BTS\\
\begin{verbatim}       http://online.wsj.com/article_email/0,,SB105709469097077300,00.html\end{verbatim}
``The Finnish wife-carriers are like the Boston Red Sox -- they're fun
to watch, but you know they'll never win'' 

Motion to ask ESPN to give us money to have a wife-carrying team\\
Thankfully, fails for lack of a second.

Apparently, the women must be 49 kilograms or more, the weight of the
last Finn to be crowned Miss Universe.

JM suggests that MIT have a Wellesley-girl carrying team, which
requires that you carry the girl back to MIT.

Move to commend the Finns and Estonians for having good taste (they
require bananna-colored backgrounds)\\
6-3-2+Spehn 

\vspace{12pt}

\noindent
Meeting adjourned, 1731 SST.

Special post-meeting link: \begin{verbatim} http://www.gameops.com/spot/promo/_hamster.htm\end{verbatim}

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
