\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/17/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 17, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, Friday 1700 SST January 17th, at 1700 SST; Ed Keyes the president and skinner presiding.  Andrew Clough is the culinary martial artist Onseck.

The Minutes are read.

Motion:  Condemn the minutes as no spell-checked.  Passes 6-0-2+Spehn.

\goto{Committee Reports}

Mobcomm:  SFBC mousepad!  Free (oohlala)!  We got some books with it, too.

Motion:  Condemn Mobcomm for having only some, and not all, books about ants.  Fails 2-5-1+Spehn.

Mobcomm2:  We got some British Books, too.

Discussion about Michael Crichton's new book, Prey.

Motion:  Condemn Michael Crichton for being silly.  Passes 7-0-2+Spehn.

Sitcomm:  Simpsons has been renewed.  The show has officially been on for a loonnggggg time now.

PsuedoMobcomm:  In December apparently John paid us 700 dollars for the privilege of purchasing our books...

Motion:  Commend John's generosity.  Fails 0-1-0+Spehn.

Alohalenscomm:  Here are some keyholder photos (all very impressive) for Margaret to choose among.  

PsuedoPianocomm:  Prentices do work, and we might have 2 new keyholders by the end of IAP.

PsuedoBondagecomm:  Binding could happen in the future.

``There's a correlation between being an anthology and being really f-ing thick.''

\goto{Old Business}

``Copyright laws can be so complex.''  ``Especially the ones that have sentences.''

Some really big honking shelves were just built, and are now in the alley; which is now even more damned as you have to be skinny to get into it.

\goto{New Business}

Argentina is atually going to pay of 1M dollars of its debt, provided it can get a 1M dollar loan immediatly afterwards.

Arisia starts this weekend, and one of our members will be on stage with the singing wookies.

Assassin's guild 10 day begins.  The Onseck needs a memorable taunt for his cook/martial artist character, and here were some suggestions: ``I will cleanse the stain on my honor w/ the club soda in your beins.''  ``My arts will bring out the subtle flavor of your liver.''  (I finally decided on ``I'll put you between my frying pan and the fire!'')

There has been a Teddy Bear recall due to loosly attached parts; so if one bit a lizard, we'd find a jaw attached to a tail, and no animals.

Miller Motion:  Universe saved 0-6-1+Spehn.

Second Miller Motion:  I go off to game 5-5-1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned 1800.

\vspace{18pt}

\centerline{Hunmbly submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
