\documentclass[10pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/17/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 17, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Bonus Pre-meeting Quote ``He does not realize the difference between
real gravity and things that just look like gravity... but he makes an
excellent physics demonstration'' -BTS

MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Kat Allen,  Onseck, recording.

Minutes read.

Move to commend the minutes as not having been taken by the Onseck\\
fails for lack of a second.

Motion to remove all failed motions containing ``Bluebellcomm''\\
fails for lack of a second

Move to consider W as a vowel, amended to consider it as two vowels.\\
Passes 4-2+Welsh&devildog+Spehn


\goto{Committee Reports}
\subsection*{MobComm}
``So there I was on my way to North Hampton to get books, and right in
front of me was this bear.  I wasn't going to stop, because I had to
go through him to get books. And he looked at me, and he ran away
because I had to go through him to get books'' -JFC

And he got some books.

SEB suggests that JFC deal with the flood, instead of the bear.
BTS relates the story of the person who came to look at the leak, who
did not know there was a 5th floor in this building.


\subsection*{BluebellComm and PantherComm}
There is Bluebellcomm overflow and PantherComm is encroaching on BluebellComm.
BTS suggests that we get metric-sized book covers, since a large
numbers of our books are not the right size for the center-slit
covers. Apparently the Library Store does not sell center-slit covers in metric sizes.

Discussion of the Nantucket Nectars bottle labeled ``I belong to
Kat'', which does not contain ``eyeball of cat''.

Motion that Library require its members to drink only drip coffee in
honor of the roof. Fails because ``drip coffee is bad!''
KHA suggests that we use a percolator.\\
BTS suggests that having to go through slow decompression in order to
leave the Library would increase readership, but decrease repeat
visits.\\
JFC tells us that people in heavy decompression use 99\% hydrogen 1\%
oxygen mixtures.\\
SEB demonstrates a sparky toy. They gave it to her at work because
they asked for them, but sadly this does not work for raises.
It winds up and runs around the floor, and is cool.

Motion: commend Susan's toy for an excellent performance\\
Passes 6-2-0+Spehn

\subsection*{CoufComm}
Successfully mailed the books from Central.

JFC says there's a company that sends pizza overnight to Israel, and
one (perhaps the same one) which sends pizza to Iraq.\\
BTS says they bought one of the old Concordes, but he is lying.\\
The Onseck says the minutes will preserve the veracity of all
statements made in the Library, but she is probably also lying.\\

``I think with a single meat-lovers pizza you could offend most of the
religious people in the world'' -BTS

JM corrects, given that you would need to give them a book explaining
how the pizza was made, in order to truly offend everyone.

Malcom relates a story where some gods came to MIT to prevent ham and
cheese sandwiches from being served.


\goto{Old Business}

JFC got a pink BananaElephant, which is next to Bobby the Banana.\\
``Since it's pink, can we get a S.E.P. field for it?'' -SEB

BTS suggests we get the giant stuffed alligator-banana.\\
JFC suggests that that may be what the egg hatches into, and says
``Maybe when we get a bigger Library''

SEB asks why Vikings are offended by meat-lovers' pizza.\\
``We love Real Meat! If it didn't come out of a goat, it doesn't
count!'' -BTS, paraphrasing a follower of Odin\\
``You made up the part about the goat'' -SEB\\
``Actually, tomatoes. All red things were offensive to the Vikings''
-BTS

ALGOL including Usual Weirdness


\goto{New Business}

We have keys to the Walker Rooms now! Unfortunately, they are all full
of old computer things.

Motion: say hi to the new member\\
Passes 5-0-0+Spehn\\
``Hi new member!'' (Kunal) - the meeting attendees

Brief Timewarp to Old Business:\\
No, not Timewarp, teleport:\\
Ok.\\

BTS relates the story of the Very Rude Member:\\
He came in with some books that were massively overdue. When we told
him, he said ``Well, I guess that's the last time I use the Library''.
ED says we don't *usually* take advantage of the fact that we can ask
the Administration to keep people from graduating, but we don't
usually bother. \\
BTS says ``but I've never seen a justification this good before!''

SEB asks if ``a political science grad student, and an objectivist''
is a religion. 

In contrasting news, an expired  member's father donated a large
quantity of books, which he had directed to his daughter's large fines.

\goto{Future Business}

JFC is reading ``The Platypus of DOOM!'' He reads the introduction to
us. It is... strange.

Nothing has happened since the last meeting with the Salem donation,
but it will happen soon.

Bujold is bad for Thermodynamic grades.

The Skinner has much work in the ZGT, some of which were rescued from
the ``Black Hole'' in Pandemonium.

JFC starts reading something.
BTS starts singing about MobComm having no tail.

Motion: send BTS downstairs to get a banana
Passes 8-4-4+Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 1738 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kat Allen,  Onseck}

\end{document}
