\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/3/2003}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 3, 2003

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, Friday 1700 SST January 3, 2003,
Jamie Morris, Chancellor and pseudo-skinner, presiding
(``let's have the meeting so we can go to dinner'').
John Carr, pseudo-onseck ((stomach rumbles) ``yes!'')

Pre-meeting, much flaming about shelves.

The ``sloppily submitted'' minutes of the last meeting were read.

Motion: Approve the minutes as sloppily submitted and sloppily read.
Passes by pseudo-Skinnerial decree.

\goto{Committee Reports}

Pianocomm:
Prentice Brian Sniffin finished repackaging the SFWA Ps.
Prentice Kat Allen finished her bluebellcomm batch and helped with
SFWA reboxing.

dexmistress:
We have new (year's) dexes, with new spine labels.

bluebellcomm: Bluebellcomm is lame.

mobcomm:
No new books imminent.

\goto{Old Business}

The Tuttle donation is fully prepreocessed.

More minutes are in HTML; JFC may be to blame for one of Andrew's
typos (``12 pt'' instead of ``12pt'').

Usual motion, usual everything.

\goto{New Business}

JM will print new-style membership sheets on hole-punched, reinforced paper.

A couple membership renewals have already been sold this year.

Laura Baldwin came in with overdue books, but the time warp saved her from
being the first member to pay a fine this year.

Professor Ronald Mallett of the University of Connecticut designed a
time machine.  He is using lasers.  Ultra-slow lightspeed and rotation
are involved.  Press release online:
{\tt http://www.advance.uconn.edu/01091012.htm}.
The government pulled his funding when he started getting results.
Now he is raising funds to finance his own research.
This may be related to the Institute for Advanced Study superluminal
propagation research.

Doemic Mercurio is teaching an ESP spring course, {\em Time and Time Travel},
which will discuss this time machine.  Unlike other schools, MIT didn't
refuse to allow a course on time travel that wasn't about science fiction.

This discussion lasts about an hour, during which time past, present,
and future business meld together into a possibly-immutable whole.

The pseudo-onseck amuses himself by failing to comprehend the finer
details of a QM/GR paper on time travel by Novikov.

\vspace{12pt}

\noindent
Meeting adjourned 17:55:60.

\vspace{18pt}

\centerline{Hungrily submitted,}
\centerline{John Carr, pseudo-Onseck}

\end{document}
