\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 8, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; Marcus Sarofim, Pseudo-Onseck, recording.

Minutes read.

Purple chickens running around the MITSFS overwhelm many motions.

Motion to commend skinner for being a chicken pioneer. Chickens by skinnerial decree.

Motion to have an Albanian chicken matrix. Chickens.

\goto{Committee Reports}

Boriscomm: it's still 1995, but not for long.

Chickens!

Pseudo-Mobcomm: a shipment of books.

Theftcomm: steal the bulletin board and replace it with a new one.

Erin is commended for sticking pins in Jamie. Jamie's voodoo doll screams in pain somewhere else.

Hasslecomm: will deal next week. Doesn't have [illegible].

Discussion on "guy" classes. Final project: pick up babe. Scoring done by student, not professor.

\goto{Old Business}

Erin and Marcus are commended for being young.

Erin tickles Jamie.

Jen's milk chickens are old.

Erin's banana and Jen's milk aren't the same person.

Miller motion fails.

Jamie's Miller motion.

Usual stuff.

\goto{New Business}

Pseudo-onseck's brain overloads from too many chickens. Chickens, chickens everywhere, and not a drumstick to eat.

Chicken motion chickens.

Milk Jen is now official Milkcomm, investigating biogenetic evolutionary activity.

Sekrit motion: the result was sekrit.

\goto{Future Business}

Erin waves banana around. Seconded and passed.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Marcus "Chicken" Sarofim, Pseudo-Onseck}

\end{document}