\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 12, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS election meeting called to order in the Star Chamber (5-216), 1700 SST,
Marcus Sarofim, President and Skinner, presiding; John Hawkinson, Pseudo-Onseck, recording.

Minutes read.

The pseudo-onseck was pleased to read the minutes.

Motion to censure something. Passes 5-7-2 +Spehn.

The door was closed.

\goto{Committee Reports}

Theftcomm: it's here.

Moocomm: TimeCop tonight.

Asscomm: head start tonight.

Mobcomm: new bookseller.

Innocentcomm: it's too late.

OFFICIAL Innocentcomm report: no statements on Innocentcomm from non-Innocentcomm members, please. END OFFICIAL Innocentcomm report.

Motion to command Innocentcomm. 27-7-2x4 +Spehn.

Picniccomm: picnic SOON!

\goto{Old Business}

There are no old people.

Motion to declare MCS old. 27-2-3 +Spehn.

Inverse skinner rule applies: MCS is young.

Motion to declare MCS jailbait. 27-7+1-7+1 +Spehn.

LHE dares skinner. Skinner declines. Innocentcomm commends.

Finger motion.

Motion to declare Richard Robert. 27-2-4 +TimeandSpehn.

Pass algol?

Usual answer.

\goto{New Business}

Motion to have elections. Motion passes 4-27-1 +Spehn.

Official candidates: jhawk for onseck, Jay for LHE, Toby for vice, Chris for president.

Voting procedure explained. Discussion ensues.

Erin places a large letter A on the blackboard.

Voting for onseck:

Candidates: Marcus, Marcus' hair, nothing, Nessus, Ted, THE CENSOR, The Censored.

Motion to close nominations. 10-4-6 +Spehn.

Finger motion.

jhawk elected.

Voting for LHE:

Jay elected.

Andrea departs.

Voting for vice:

Toby elected.

Voting for president:

Skinnerial decree: all votes for Marcus are counted as votes for Thark. Thark elected.

Motion to vote on Telzey. Passes by skinnerial decree.

Motion to open nominations. Fails by skinnerial decree.

jhawk declared Telzey.

Rescinded after a display of affection.

\goto{Future Business}

Miller Motion. 3-1-none +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17something SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, now-Onseck}

\end{document}
