\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 26, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
John Hawkinson, Onseck and Pseudo-Skinner, presiding and recording.

The skinner arrives and confiscates the gavel.

Minutes read.

Motion to make minutes legible, actively supported by the Onseck. Passes 9-4-2 +Spehn.

Motion to regard minutes with healthy skepticism. Chickens 1-2-5 +Spehn.

Matrix vote. 5-1-1 +Spehn.

9 4 2

1 2 5 => 42. Motions pass.

5 1 1

\goto{Committee Reports}

Moocomm: Batman III, sometime this summer.

Pseudo-Moocomm: Johnny Pneumonic tonight.

Pseudo-shelfcomm: Skinner is lame, we have shelves that need to be steel-wooled, etc., etc.

Motion to declare Jamie Albanian. Passes 6-0-2 +Spehn.

Jourcomm: is becoming EuroJourcomm. Wants money for books. Wants people to write. Discussion ensues.

Motion to declare Jourcomm greedy rival. Friendly amendment: "treasonous greedy rival." Accepted. Passes 5-2-1 +Spehn.

Motion to declare Jay and jhawk a commie mutant traitor. Passes by skinnerial decree.

Sheriann has been fined.

Onseck: we've talked with the evil ARLewis and are considering the practice of forordaining the happenings of the meeting in advance.

\goto{Old Business}

Consideration of Algol again.

Motion to declare Albania the Banana Republic. Fails 3-8-3 +Spehn.

Pseudo-Analogcomm: remember to request your hours.

Jourcomm: skin the skinner.

Unusual motion. Unusual second. Unusual result.

\goto{New Business}

Miller motion. Fails.

Second Miller motion. Fails.

Finger motion.

\goto{Future Business}

Miller motion. Fails 3-4-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}