\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 20, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Eric Mumpower, Pseudo-Onseck, recording.

Minutes almost found. Pseudo-Onseck commended for this action.

Something about "cubic punts."

Skinner offers to hit Neel with the gavel.

The Real Wonderful Onseck called and said she'd be here in 5 minutes, 3x OST, I think.

Discussion of the advantages of having 3 Ancas.

\goto{Committee Reports}

Discussion of picnics, and Isaac Asimov's attendance warding us vs. rain. Skinner points out that if Asimov does show up, it would be considered "in bad taste" to point out to him the fact that he's dead.

\goto{Old Business}

The usual.

Marcus is really old again. So he's new. Or something.

\goto{New Business}

A week and 10 minutes until Filk and Cookies; GNU party shortly thereafter.

Motion to call the Onseck banana-colored passes 20-5-9 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST. Onseck arrives shortly thereafter.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Eric Mumpower, Pseudo-Onseck}

\end{document}