\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 28, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Neel K., Pseudo-Onseck, recording.

Minutes read.

M: Neel cruelly impressed into pseudo-onseckly position. Everyone-none-a couple +Spehn.

M: jhawk and Neel identical. Passes 15-13-2 +Spehn.

Discussion.

\goto{Committee Reports}

Stealth Moocomm discussion.

M: elect [illegible]. 19-3-6 +Spehn.

Ow! Ow? Yes, ow!

Mobcomm: new books next week.

Panthercomm: SFWA books.

Pseudo-Jourcomm: Review!

M: skinner to miss a motion. 17-11-3 +Spehn.

\goto{Old Business}

Jamie: motion to appoint a committee to find out what happened to Parl? Neel: Whose Parl? Jamie: Our Parl.


\goto{New Business}

M: we [illegible] as PSD.

Jamie can't do clever things.

\goto{Future Business}

M: con. Second, second, second.

Miller motion. Passes 13-3-9 +Spehn.

Banana motion.

Banana motion.

Tensor motion.

STACK OVERFLOW.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Neel K., Pseudo-Onseck}

\end{document}