\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 14, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Toby Elliot, Vice, presiding; John Hawkinson, Onseck, recording.

Minutes deciphered.

M: impossible. Pi-e-infinity +Spehn.

\goto{Committee Reports}

Decent bing: 7.5.

Panthercomm rants about how it only took 4 hours to do inventory, and Jamie molests a banana.

Mobcomm does something obscene on the 29th.

Jamie rants about how he needs something "hard."

\goto{Old Business}

Decent bing: 7.25.

Jamie tries to claim that you don't age while at MIT, so he's young.

jhawk's on a power trip and is fined for incorrect fining, and Chris declares special jhawk rate of 10 dollars.

Jamie puts everyone to sleep lecturing on proper fining technique.

Chris realizes we're still in Old Business, decides to bing the failed Miller motion on Jamie's head.

jhawk is fined for giving himself fine credit.

Toby drools over jhawk's member sheet.

Jamie sucks up to Chris, and confuses him.

Boring discussion of new rules. Jamie is instructed to be obnoxious, but waives right to skinnerial support.

Chris begs for algol, then end of meeting.

\goto{New Business}

2 motions to end meeting fail.

\goto{Future Business}

M: Jamie is Albanian. Passes 20-0-4 +Spehn.

As he sings an adjournment song...

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}