\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 17, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

M: add "update minutes on web" to Algol. Passes due to sensibility.

Discussion of Skinner box.

Matrix vote passes by decree.

M: commend skinner for passing motions. Passes.

M: commend Innocentcomm for saying "fuck you." Passes.

Innocentcomm commended.

\goto{Committee Reports}

Mobcomm: new books exist.

M: commend Kevin for having little sibling. Passes by unanimous and then some.

(There is an objection.)

M: Neel Albanian. Passes unanimously.

\goto{Old Business}

ALGOL.

M: Neel to be Atlascomm due to brawn. (Innocentcomm) 1-1-1 +Spehn.

M: offer reward for Kevin's lost conversation. Passes.

Kevin asked what reward- says he'll join MITSFS.

Time warp to committee reports: Table committee alive and well in Kentucky, Minneapolis, West Coast. But we've never heard of it- it is looked up.

\goto{New Business}

Bridget hypothesizes New Business eloped with Kevin's conversation.

Onseck needs new pad.

Miller motion- fails.

2nd MM- 9-8-11 +Spehn.

3rd MM- 14-4-8 +Spehn, passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}