\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 1, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Toby Elliot, Vice and Pseudo-Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Minutes read by fabulous pseudo-onseck.

M: declare minutes dated.

M: commend Eddy for dating minutes.

M: Eddy to tell us about sex life with minutes.

Matrix vote, but no Pentiumcomm. Jamie does matrix- all pass.

\goto{Committee Reports}

M: commend Toby for counting. Chickens.

Mobcomm: many books this weekend.

Dark Jen (as Committee to Overdamp the New Wave): her birthday is this weekend.

M: condemn Dark Jen for having birthday. Passes.

\goto{Old Business}

Null motion. Passes 20-0-0 +Spehn.

Some bad pun fails by pseudo-skinnerial decree.

Toby is now pseudo-Jehovah.

\goto{New Business}

Speculation as to what happens if we leave Toby alone running meeting.

M: condemn Toby for not knowing difference between sitting and standing. Lots-small but insignificant-some +Spehn.

\goto{Future Business}

Miller motion fails.

2nd Miller motion fails.

3rd Miller motion passes 9-12-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}