\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 27, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Minutes read.

3 blind mice called the Real Wonderful Onseck- not there. (Or here.)

Onseck called us, but she was the Vermont Better Business Bureau. Skinner asked if we have schedule; they said no.

Real Wonderful Onseck committed to the BBB.

Skinner says Asimov would be smelly if he came to the picnic.

Motion to call the minutes.

Motion to have a matrix vote, motion not to have a matrix vote, motion to note the minutes are on banana-colored paper. Pi-2-e +Spehn, 7-3-4 +Spehn, i-42-7+i +Spehn.

[Mathematics, working out determinant using FDIV.] Motion chickens- it's complex.

\goto{Committee Reports}

Pentiumcomm celebrates.

Ancacomm made a slide.

Very nice good person arrives with lots o' filk.

\goto{Old Business}

Skinner's mother calls.

Skinner speaks in Peruvian-Eqyptian.

Skinner wants foreign tongues.

\goto{New Business}

M: kill the skinner, M: matrix vote, M: banana motion. Skinner decrees chicken- fascist running dog lackey of the capitalist monopolist devils.

Banana motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}