\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 3, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; John Hawkinson, Onseck, recording.

Minutes read with many false starts.

M: declare minutes [illegible]. 4-6-7 +Spehn.

M: check to see if this is the real jhawk. 17-10-8 +Spehn.

M: disbelieve minutes. 6-8-15 +Spehn.

M: have matrix vote. 8-15-5 +Spehn. This and previous two motions pass.

M: commend jhawk for reading LR4.

\goto{Committee Reports}

Pseudo-Bananacomm reports.

M: Jen and Tara declared separate people. 15-17-3 +Spehn.

M: milk Milk Jen. 5-5-8 +Spehn.

Pumpkincomm: pumpkin brawl manifested at Fenway.

Pseudo-Pumpkincomm: execute Neel for above.

Pseudo-Toothfairycomm: it's Eddie's birthday.

M: sing Happy Birthday really badly. Passes by skinnerial decree.

\goto{Old Business}

MCS is gone.

\goto{New Business}

M: dissolve all cancellations. 15-3-6 +Spehn.

Finger motion.

\goto{Future Business}

M: remind [illegible] that pumpkins are not bananas. 17-11-7 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}