\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 15, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner and member, presiding; John Hawkinson, Onseck, recording.

M: commend skinner for being member.

Minutes read.

M: commend the Illuminati for concealing minutes of last meeting.

Argument and chaos ensue, of course- they're brainwashing us.

Did Neel steal the minutes? No, he just took them.

M: lose this week's minutes (and maybe make them translucent green with purple specks).

\goto{Committee Reports}

Mobcomm: no books.

?comm: book sale happened.

Digression about tape recorders in ancient Rome.

M: commend Andrea for being exasperated with others. Passes.

Stuff happens.

\goto{Old Business}

M: commend Chris for screwing up screwing-up.

Algol.

\goto{New Business}

Jay acts dumb.

Marcus talks about old stars.

Chaos.

Some motion chickens.

M: commend skinner for losing control of meeting.

Matrix chaos.

Matrix: kill Toby, matrix vote, Jay Albanian.

30 10 infinity

3 13 3 => infinity.

2 13 9

\goto{Future Business}

Brownian motion passes.

M: someone cute to feed Jamie banana. Passes! (Whew.)

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}