\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 6, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Marcus Sarofim, President and Skinner, presiding; Anca Mosoiu, Onseck, recording.

Minutes read.

Finger motion. 7-2-2 +Spehn.

jhawk fingered.

Chaos ensues with dagger, fingers.

M: minutes provide role model. 11-8-mrow +Spehn.

Snarling noises and more chaos.

M: call meeting short. 7-8-2 +Spehn.

Round of Miller motions. 1st fails, 2nd fails 4-6-7 +Spehn.

M: call Marcus "tail-challenged." 8-8-3 +Spehn.

Motion to strike "challenged" from minutes. 0-0-0 +Spehn.

More chaos, Jay loudly suppressed.

3rd Miller motion fails.

\goto{Committee Reports}

Brownian motion. Lots-4-1 +Spehn.

Brownian motion among members ensues due to skinner's misinterpretation.

Albania = albanian.

Motion to strike "finger" from minutes.

Marcus struck.

Chaos.

Miller motion. Lots-4-5 +Spehn. Passes!!!!

\vspace{12pt}

\noindent
Meeting adjourned, 17tired SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosoiu, Onseck}

\end{document}