\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 24, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
John Hawkinson, Onseck and Pseudo-Skinner, presiding; Kevin, Pseudo-Onseck, recording.

Minutes read.

Motion to declare minutes "something" fails.

Finger motion. No second.

Chris arrives and assumes the throne.

Various attempts at humor fail (this is an observation, not a motion).

Motion to sum the minutes. Fails 4-6-2 +Spehn.

\goto{Committee Reports}

Pussycomm and Panthercomm have nothing to report.

jhawk reports a water leak. Nobody cares.

Miller motion fails.

\goto{Old Business}

Malcolm is here. He's old. But nobody cares.

Someone reads an ad for Phantom Something. Nobody cares.

Discussion of PhilCon. Nobody wants to go. jhawk wants people to go, but then, he's a desperate dude, isn't he?

Motion to commend MITSFS for being apathetic fails because nobody cares enough to second it.

Usual motion, usual debate, usual vote, usual result.

\goto{New Business}

Discussion of unusual absence of usual lack of debate.

\goto{Future Business}

Motion to declare lack of usual debate un-banana-like. Passes 5-1-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned to general apathy, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin, Pseudo-Onseck}

\end{document}