\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 7, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Anca Mosiov, Pseudo-Skinner and Pseudo-Onseck, presiding and recording.

Minutes read.

M: extremely poor minutes. Passes lots-0-1 +Spehn.

M: condemn skinner and [illegible]. No second.

M: condemn both the skinners for dampening bing. 8-3-3 +Spehn.

\goto{Committee Reports}

Pseudo-Mobcomm: 62 books.

Pseudo-Panthercomm: inventory tomorrow.

Apathycomm report? No.

\goto{Old Business}

M: commend Andrew for being profound. Fails 3-14-3 +Spehn.

Jamie: plastic toy is fun to [illegible].

A-pro-lost. ?-?-[illegible] +Spehn.

Marcus: no. Chris: no? 2-1-6 +Spehn

Skinner does not demonstrate Chris's motion.

UM, US, UV, UR.

\goto{New Business}

Miller motion. Fails.

M: condemn Jay for throwing out recycling. 16-2-1 +Spehn.

Good pity discussion.

2nd Miller motion. Chickens by Marcus.

M: condemnify Marcus. 9-5-3 +Spehn.

Condemn, confirm.

M: Holy Trinity of MITSFS. Command: 8-4-9 +Spehn. Condemn. Confirm: 14-4-7 +Spehn. Negative determinant, all fail.

\goto{Future Business}

M: confirm [illegible] has blinding speed of a banana slug. 10-0-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Anca Mosiov, Pseudo-Onseck}

\end{document}