\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 17, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christopher Hooker, President and Skinner, presiding; John Hawkinson, Onseck, recording.

Minutes read.

M: approve minutes as misspelled. 19-2-4 +Spehn.

M: commend skinner for pre-fall effort. Fails by skinnerial decree.

M: commend skinner for phase slip.

\goto{Committee Reports}

Moocomm: Mary Poppins.

M: commend Mary Poppins for corrupting children.

MT: Pencil Man, blah, blah.

Anime showings, Taiwanese Film Society; Hard Boiled.

M: declare onseck's writing hand Albanian. Passes 9-5-8 +Spehn.

(IN ALBANIAN)

M: commend skinner for not allowing seconds.

\goto{Old Business}

Malcolm Y is here. He's even older than last night.

Discussion on MY [illegible].

M: instruct Malcolm to donate the books he donated next week this week. 10-6-3 +Spehn.

M: condemn Jay for something. 12-0-3 +Spehn.

Eddie seconds a boring motion.

M: declare Jen and Tara separate people and call Jen "Milk Jen" (not "Light Jen"). 20-5-5 +Spehn.

M: declare Milk Jen and Tara the same person. Passes by skinnerial decree.

Search for Tara. Milk Jen found.

M: leave skinner and onseck out of statistics. Passes 6-0-0 +Spehn.

M: Jay to take out only Slash for the next 4 months. Passes by skinnerial decree.

Algol.

\goto{New Business}

Motion that we add the Usual Protest to the Algol.

Motion to have all [illegible] shot.

Matrix vote.

Motion to table pending arrival of i586comm.

Motion to determine outcome of all motions with coin flip.

Motion to declare Tara and Milk Jen separate people. Fails by skinnerial decree.

SF Chronicle hasn't been got in a while.

Leonardcomm: sport of Clown Racing [illegible] is out of clowns. [Illegible]

Motion to console [illegible] for being out of clowns.

Onseck anal, skinner decisive.

\goto{Future Business}

Banana motion. 10-18-8 +Spehn.

Skinner memories.

Miller motion. Seconded. Fails.

Motion to vote down/up all banana motions. Fails.

2nd Miller. (Finger motion passes.) 10-12-6 +Spehn.

M: substitute banana motion for Miller. Fails.

M: commend anti-banana voting block. 8-12-1 +Spehn.

M: commend skinner's banana memory. 15-19-5 +Spehn.

M: commend skinner's memories for being most voted down.

Banana motions in area.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Hawkinson, Onseck}

\end{document}