\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

June 22nd, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, June 22nd, 1990,
1700 SST, John Conger, President and Skinner presiding.

(E D) Motions concerning the minutes?

(RGvdH) [Makes a motion.]

(HAM) I'll second Robert's motion, with a friendly amendment of ``banana.''

Motion passes, minus Herb's amendment, a lot to some to a few plus Spehn.

\vspace{.15in}
{\em bing!\/}  {\bf Committee Reports\/}

(C H) I saw {\em Dick Tracy\/} --- it's too big for a little screen.

(WDS) I finally saw {\em Back to the Future III\/} --- it's a good movie.

(HAM) Moocomm sub negative one --- {\em Robocop 2\/} opens today.

(C H) The {\em Globe\/} hated it.

(HAM) All five Star Treks are this weekend.

(WDS) StreckComm --- the season finale is tomorrow night.

(WDS) Cornelia Otis: Canada may be on the verge of dissolution.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(RPP) I'm 20 now --- I'm no longer immortal.

(WDS) The Holy Flag Amendment is now Old Business.

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(C H) Minicult: From TX: ``Please elect John Silber.  You deserve a fine
moralist, and we would just as soon see him stay out of Texas.''

(WDS) Yeah.  Daniel Pinkwater is doing at least one radio ad for Ford.

(RPP) Harlan Ellison's essay....

(WDS) I am now a college graduate.

(C H) I am going to take a course in C programming in DOS this summer.

(WDS) The universe is back where it belongs, or at least our section of it.

(E D) [Awards Bill, Rob, and Rob the Banana of Congratulations.]  Any seconds?

(C H) Yaaaaaay!

Meeting adjourns, 17:15 SST?

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
