\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.1in}
\setlength{\evensidemargin}{-0.1in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

January 26th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, January 26th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(HAM) Move to make DK play \underline{Slinking Terror} for as
many days as these minutes are old.

Motion passes 7 to 2 to 0 plus Spehn.

\vspace{0.15in}
{\em bing\/} {Committee Reports}

(PJN) Moo Comm - LSC Science fiction marathon on Wednesday.  Robocop,
Trouble with Tribbles, Jedi, Creature from the Black Lagoon, First Men
on the Moon, something else, and Highlander.

(LAK) Jour Comm - I still don't have any reviews.

(HAM) Lenscom - Canon has announced that they are discontinuing the
Lenscom's type of lens, so it looks like I am going out to buy a new
camera soon.  I expect MITSFS to pay for the lenses at least.

(WDS) Sit Comm - \underline{Beauty and the Beast} is dead, but it
might come back from the dead.  Apparently Lifetime is interested in
picking it up for a series of specials.

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

(WDS) Ken and Janice were here last week.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(PD) I wandered on over to Pandemonium Books and spoke to Mr. Tyler
Stewart.  Everything is 10\% off, he's carrying more new stuff than
used stuff, he has horror, he got quite a lot of videotapes and is
planning on acquiring more. (That includes TV and movie stuff).  It's
a \$1.90 rental per video per night.  He also said kind of fuzzily that
MITSFS members could get 15\% off.

(PJN) Time warp to Old Business: Hi Rob!

End time warp.

(HAM) Banana.

Motion passes 6 to 1 to 1.

Meeting adjourned 1715 SST

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
