\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

February 9th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, February 9th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(HAM) Motion to not approve the minutes.

Motion passes, 8 to 0 to 2 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(WDS) Moo Comm - {\em Ghostbusters II} at LSC tomorrow.

(PJN) Moo Comm sub I - Next Saturday is Mike Jittlov Day.  LSC is
doing 3 movies and 2 lectures.

(WDS) Con Comm - Next Saturday is Boscon.

(WDS) Strek Comm - Tommorrow night, because no one demanded it, deja
Q.  Stories about Star Trek VI being Star Trek: First Adventure are
making their way through normal media channels, i.e. with a great deal
of credibility.  It seems that Paramount is serious about doing a Star
Trek: The Early Years, with little or none of the original cast.

(S K) Pseudo Whoosh Comm - Remember when John Glenn was attacked by
that wierdo?  Well he was found innocent by reason of insanity so that
he might undergo treatment of severe mental illness.

(PJN) Pseudo Whoosh Comm sub I - The final course 16 space design
class this year is establishing a lunar base and a manned mission to
Mars.  I'm working on the propulsion team.

(PJN) Piano Comm - Steph is doing the picnic.

(HAM) Aloha Lenscom - We have the new camera with the new flash.
Donations for zoom lenses will be appreciated.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

Scott Kitchen is here.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(S K) Miller Motion!

Motion fails.

(WDS) The Japanese government has discovered that they have a huge
collection of counterfeit gold coins, which are made out of the same
amount of gold, in their vaults.  The reason that this works is that
when the government minted these Emperor Hirohito Commemerative gold
coins in 1986, they said these coins would always be redeemable with
the government for 100,000 yen.  At the time they did this, the value
of the gold in the coins was only about 40,000.  Somebody out there
got their hands on 2 tons of gold, some good counterfeit dies, and
produced a huge quantity of these, selling them at 100,000 yen.

(HAM) Motion to protect John Glenn from getting punched out in public
by sending him to Mars by propelling the spaceship by throwing bananas
out the hatch.

Motion passes, 6 to 4 to 2 plus Spehn.

Meeting adjourned, 1714 SST 

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
