\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

June 8, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, June 8th, 1990,
1700 SST, Derrick Kong, LHE and Pseudo-Skinner presiding.

(D K) Motions concerning the minutes?

(JRP) Motion to approve the minutes as {\em anemic\/}.

(S G) Motion to approve the minutes as broadly interpreted.

(RGvdH) I liked the first one better.

(WDS) Motion to approve the minutes as liking the first one better.

Bill's motion passes 5 to 2 to 4 plus Spehn.

\vspace{.15in}
{\em bing!\/}  {\bf Committee Reports\/}

(RPP) {\em Total Recall\/} is out.  Good psychological thriller, bad SF.

(WDS) This is what I keep hearing --- it's two thirds of a good movie.

Moocomm sub two shows up in the door and says something about ``There will
be no sequels'' to {\em Back to the Future III\/}.  Bill argues.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(WDS) Time warp to committee reports.  Dr.~Bob comm, Robert van der Heide
got his Ph.D. finally.

(KRJ) We got a visit from the original Skinner.

(Time warp evaporates by Hawking radiation\ldots)

ALGOL.  Klunk.

\vspace{0.15in}
{\bf New Business\/}

(WDS) (Tells amusing anecdote about a pesky tyke in Florida legislature.)

(S G) (Tarl snoozes\ldots)

(WDS) Move to adjourn.
(Gets beaten up.)

(WDS) Minicult: Romanian uprising was a KGB plot.

(JRP) You know, before Perestroika, Russia was this big, efficient monster machine.  Now that they're our friends, they're just as bad as we are.  It's just like comic books where the really awesome villain becomes mediocre when he turns good.

(S G) Miller Motion.

(D K) Fails.

Second Miller Motion passes 4 to 1 to 1 plus Spehn.

Meeting adjourns, 17mumble SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
