\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

September 7th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, September 7th, 1990,
1700 SST, John Conger, President and Skinner presiding.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(WDS) CuteComm --- boy does Stephanie look cute.

(S T) FweekComm --- We got nine-hundred and something dollars.  And we didn't
have to pay for the VCR.

(WDS) PianoComm --- We apparently have a new keyholder: Lisa Miller, whose
picture you never would recognize.

(JCC) Yeah, we have Steph and Alia Atlas as new keyholders for real.

(D K) WhooshComm --- they're still sitting there.

(E D) TheftComm --- someone is breaking into fourth floor offices.

(C H) MooComm --- I saw {\em The Witches\/}.

(JCC) MooComm --- {\em Predator\/} is tonight, {\em Doctor Strangelove\/} is
Sunday, {\em Teenage Mutant Ninja Turtles\/} is Reg Day.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(WDS) Today is Queen Elizabeth I's birthday.

(LAM) Andy Su is coming to town.

Old Business ALCOHOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

BEER.

(C H) On Rec.arts.comics, they mentioned that the shuttle pilot of the failed
flight is named Guy Gardner, and the captain is Vance Brand.

(JCC) We are solvent.

(JCC) We have a new shelving list.  And sign up for hours, DAMMIT!

(WDS) On the back of the Archie MacPhee catalog, there's a big picture of a
bananna colored baked duck with a peace sign.

(HAM) Move to make some bananna beer!

Motion passes as many as needed to fourish to 2 plus Spehn.

Meeting adjourns 1717 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
