\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

Friday, May 4, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, May 4th, 1990,
1700 SST, Philip J. Nesser, President and Skinner (for the last time)
presiding.

Minutes are read by WDS

(HAM) Move to handcuff the minutes.

Motion passes many to 1 to a few plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(S G) Mort Comm --- Georgia Nagel

(S T) Picnic Comm --- Picnic is Sunday, 10 AM.  If it rains, we'll be in
Talbot.

(A A) Picnic Comm sub II --- I called Craig Shaw Gardner.  If a previous
engagement falls through, he will show up.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

(C H) We have a letter from Case Western Reserve from Andy Su --- he's
graduating.

{\bf ALGOL}  {\em Klannng!\/}

\vspace{0.15in}
{\bf New Business}

(WDS) Mini Cult --- Four Florida prisoners are filing a \$1.4 million lawsuit
vs. deputies for smoke free cells.
Sub two: A mugger stole \$478 million in financial certificates from a
messenger in London.

{\bf Elections}

Onseck: Rob Wins; Derrick's predicament is second.

LHE: Derrick wins; Derrick's predicament is (again) second.

Vice: Elizabeth wins; the vowels come in second.

President:  Time warp to committee reports:

(C H) Moocomm --- Time Bandits is Sunday, Lost Boys on TV Saturday.

{\em Time warp collapses\/}

John Conger wins; Thunderbunny is second.

The official second is Derrick's predicament.

Meeting ends in confusion, 1845 SST.

John Conger wields the gavel, declares himself Skinner:

{\em Rinnnnnnnng!\/}

(WDS) [in awed voice]  He really {\em is\/} the Skinner!

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
