\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

April 13th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, April 13th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(HAM) Motion to arrest the minutes for assaulting a police office.

Motion passes 7 to 0 to 3 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(S G) Cornelia Otis - Shanty Town III.

(WDS) Sit Comm - The {\em Twin Peaks} 2 hour movie was very David
Lynch.  Amazingly odd and very high production quality for television.
I'm not sure whether I liked it or not.

(PJN) Moo Comm - {\em The Adventures of Robin Hood} tonight as the
classic, and {\em Peter Pan} tomorrow.  Just as a note, {\em The
Little Mermaid} broke all sorts of records at LSC by getting 1630
people.

(WDS) Cornelia Otis - Back last December, when the US invaded Panama,
Secretary of Defense, Dick Cheney announced that 2 Stealth
fighter-bombers were used and delivered their bombs with pinpoint
accuracy.  In reality, Plane A hit target B on the dot and Plane B
missed everything by about 300 yards.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

(PJN) I got a letter from a former keyholder who is a professor of
physics and astronomy at a New England college.  All his students have
to do what is apparently the equivalent of a thesis.  Some girl there
is doing hers on science-fiction, and they need someone to act as
outside examiner.  They want some suggestions from us...

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(WDS) Mini Cult/Whoosh Comm - Someone is claiming that tomatoes which
will be grown from seeds up in low-earth orbit for 6 years could be
poisonous.  NASA is not happy at all....

{\em Seth makes a very bad motion that the Onseck refuses to repeat.}

Motion fails 3 to 7 to 4 plus Spehn.

(WDS) That was about the most inane banana motion that I have ever
heard.

Motion passes 7 to 6 to 1 plus Spehn.

Meeting adjourned 1713 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
