\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

**** DATE *****

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, April 27th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(C H) {\em Baaa!}

Motion chickens 4 to 3 to 4 plus Spehn.

\vspace{0.15in}
{\bf Committee Reports}
(S T) Picnic Comm - I made a thing.  I'm sending it out tomorrow.

(HAM) Lens Comm - There's a balloon loose in the library.

(PJN) Mob Comm - New England Mobile trip tomorrow.

(WDS) Moo Comm - {\em The Wizard of Oz} tonight, {\em Witches of
Eastwick} tomorrow, and Sunday the TBA is {\em Blaze} at LSC.

(PJN) Moo Comm sub II - {\em Various details about the Drop Date Eve
Movie}.

(WDS) Sit Comm - {\em Twin Peaks} is definitely fantasy.  It's
definitely weird.  It's fairly brilliant, and god, can David Lynch do
a dream sequence.

(PJN) Skinner Report - The election meeting is Friday in Star Chamber.

\vspace{0.15in}
{\bf Old Business}

(WDS) 156th birthday of Ulysses S. Grant.

Old Business Algol: usual <bing>

\vspace{0.15in}
{\bf New Business}

(WDS) In at least one housing project, they are ripping out all their
pay phones and replacing them with rotary dial phones.  The idea is to
discourage drug dealers from using beepers that can do digital
transactions over touch-tone phones.

(RPP) Motion to put Steph in charge of procuring Rocky Mountain
Oysters for the picnic.

Passes by Skinnerial decree.

(C H) Mini Cult - I saw a small article in the {\em Sun} about how
bananas can extend your lifespan.

(HAM) Move to condemn Steph for not taping up Dave's hair with
banana-colored tape.

Motion passes 6 to 2 to 3 plus Spehn.

Meeting adjourned, 1716 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
