\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

July 27th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, July 27th, 1990,
1700 SST, John Conger, President and Skinner presiding.

{\em bing\/} {\bf Committee Reports\/}

(KRJ) Well, whatever I am, I could report on PulpCon.  I spent lots of money
buying only a small number of things.  Amongst our purchases: I got three more
issues of Dusty Ayres and his Battle Birds.  I bought {\em Weird Tales\/}
--- three issues from 1926 at a hair over \$50 apiece.  (That's the cheapest
I've seen one of these in a long time.)

(WDS) How much of our collection does this fill in?

(KRJ) A miniscule amount.

(WDS) BrokeComm --- We have no money.

(JCC) So don't buy anything!!!

(WDS) Maybe that should be TrumpComm.

(WDS) MooComm / SitComm --- I saw the ad for {\em Arachnophobia\/}.  Where the
fuck are Terry Racoda and Tipper Gore and all the rest when you {\em need\/}
something censored on TV?  Yecch!  Goddamned spiders crawling out of pipes...

(RGH) SitComm sub two: I saw Richard Nixon live.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(WDS) Twenty-first anniversary last week of the moon landing.

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(JCC) Zwitter press thingy --- something nominated for a Readercon small press
award from a former MIT student.  Something called {\em Weisenbaum's Eye\/} by
George Stetton.

(WDS) What's that doing on our door?

(KRJ) Harold Zitzow died.

(WDS) MiniCult --- anyone have the misfortune to see or hear Roseanne Barr's
rendition of the Star Mangled Spanner?

(A A) Tom Galloway might be stopping by in the near future.

(D K) Miller motion.

(JCC) Fails.

(WDS) Miller motion redux.

(JCC) Passes!

Meeting adjourns, 1710 and 33 seconds SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
