\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

June 29th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, June 29th, 1990,
1700 SST, John Conger, President and Skinner presiding.

\vspace{.15in}
{\em bing!\/}  {\bf Committee Reports\/}

(WDS) We have found the missing Red Sonja novel!

(WDS) WhooshComm... sigh.

[They fucked up the Hubble space telescope.]

(D K) WhooshComm sub two: There's a leak on {\em Atlantis\/}, just like the
one on {\em Columbia\/}.

(WDS) Yeah, they grounded the whole fleet, as if any of them were going to take
off tomorrow.

(A A) MobComm --- we're going to New England Mobile tomorrow.

(LAM) PianoComm --- Alia Atlas is becoming a keyholder soon.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(LAM) Donations are being done.  That's Old Business!

(HAM) Scott Kitchen is allegedly engaged, and supposedly getting married at
some point.  They met over Usenet.

ALGOL.

Klunk.

\vspace{0.15in}
{\bf New Business\/}

(JRP) 1234567890 will be happening in a few days.

Time Warp.

(JCC) {\em Alien\/} and {\em Aliens\/} are tonight.

Whoosh.

(HAM) Move to condemn somebody for donating a book by Margaret Wonderbanana.

Motion passes lots to 2 plus Mark Sylvester to 1 plus Spehn.

Meeting adjourns 17:10 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
