\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

Friday, May 11th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, May 11th, 1990,
1700 SST, John Conger, President and Skinner presiding.

Minutes are read by RPP.

(JCC) Motions concerning the minutes?

(HAM) Cowabunga.

(A S) (Waves hands wildly.)

(WDS) This guy's gonna practice medicine!

(HAM) Practice, that's the key word.

(C H) I'll second {\em that\/}.

Motion passes 9 to 3 to 1 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(WDS) People's Albanian Embassy: Albania is starting to de-isolate itself; I
think the end of the world is near myself.

(A S) In addition to that, I put up an article on Albania.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

(C H) Andy's here!

{\bf ALGOL}  {\em Klannng!\/}

\vspace{0.15in}
{\bf New Business}

(WDS) Mini-Cult: Madison, WI: A smoker who thought his nicotine fit
constituted an emergency faces a possible jail term and fine for calling the
911 emergency center to have cigarettes delivered.  The geek called the center
at 9 PM Monday and asked for an ambulance; when the paramedics arrived, he
told them he was having a nicotine fit and needed cigarettes.  Quote: ``I just
want what I have coming to me.''

(KRJ) And he's gonna get it!

(HAM) Do we have Janice's mini-cult she brought us, about the galaxy shaped
like the space baby?

(John holds up clipping from a rag.)

(JCC) New galaxy discovered, shaped like a human fetus --- and scientists
detect a heart beat!

(WDS asks about caution signs for parts of library.  Suggests ``Caution:
Corrosive Materials --- Wear Required Protection'' for GOR novels.)

(JCC) What's wrong with the Gor Novels?

(WDS) Move to force John and Stephanie to read out loud to one another from
imaginative sex!

(JCC) Oh, I don't think that's a good idea; I'll destroy that right now.

(LAM) Move to commend Andy for wearing a bananna colored shirt with Teenage
Mutant Ninja Turtles on the front.

John seconds it.

Motion passes 7 to 2 to 3 plus Spehn.

Meeting adjourns 1710 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
