\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

March 9th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, March 9th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(HAM) Move to approve the minutes as ``Kowabunga!''

Motion passes, 9 to 2 to pizza plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(S G) Moo Comm - {\em The Handmaiden's Tale} opens today: frontiers of
feminism.  {\em He compares the covers of the book and movie poster.}

(HAM) Aloha Lenscom - We have embarrasing pictures of people, mostly
John and Stephanie: get them before John does.

(WDS) Moo Comm sub II - {\em The Hunt for Red October} is just sort of
there.  {\em There are several dissenting opinions.}

(PJN) Moo Comm sub III - LSC is showing {\em Lap\"{u}ta} tomorrow
evening.

(PJN) Twit Comm - Someone broke and stole 12 of LSC's 18 subwoofers in
26-100.  It will cost LSC about \$5000 to replace them.

(S G) Grease Comm - Kate Mahoney is now President of ASA, Elizabeth is
treasurer, I am Secretary, and Glenn Berry is member-at-large.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

(PJN) We have a Titledex.  It is 232 pages long.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(S G) Mini Cult - I noticed a {\em Weekly World News} article: Doctors
Cure Gays With Electric Cattle Prods.

{\em Donna walks in.}

(C H) Cornelia Otis - I heard that there was a sort of tax riot over
in England.  [The reason is that a poll tax has been proposed.]

(S G) Motion to attack Margaret Thatcher with an banana-colored cattle
prod.

Motion passes, 8 to 2 to 6 plus 3.  [Three is defined as equal to Spehn.]

Meeting adjourned, 1719 SST 

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
