\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

June 15th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, June 15th, 1990,
1700 SST, Elizabeth Ditchburn, Vice and Summer-Skinner presiding.

(E D) Motions concerning the minutes?

(WDS) Motion to commend the Onseck for his fine work, and to award him a
temporary life membership.

(RPP) But what about a permanent life membership?

(WDS) Don't push it, kid.

Motion passes unanimously, minus Spehn.

\vspace{.15in}
{\em bing!\/}  {\bf Committee Reports\/}

(HAM) He's dead, Jim.

(D K) What?

(HAM) The Onseck just died.  Look.  He's slumped over in the chair, and his
face is all blue and everything.

(WDS) Ooooh, baby, light my fire.  Scald my flesh all night long.

(LAM) But not in the library, Bill.

(C H) Saug meinen Abschlepwagen?

(RPP) [In a dead tired voice.] Jawohl.  [Turns purple.]

(HAM) Banana.

(E D) Fuck you, Herb.

(A A) But not in the library!

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(WDS) This is getting old.

\vspace{0.15in}
{\bf New Business\/}

(Harlan Ellison) Fandom sucks!  [Gets the shit beaten out of him.]

(E D) You know, this Kool Aid is good, but it has a funny aftertaste.  Who
made it?

Meeting adjourns, 26:42 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
