\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

July 6th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, July 6th, 1990,
1700 SST, Derrick Kong, LHE and pseudo-Skinner presiding.

No Onseck.  No minutes.

(JRP) Motion to approve the minutes as ethereal.

Motion passes 6 to 4 to 4 plus Spehn.

\vspace{.15in}
{\em bing\/} {\bf Committee Reports\/}

(SST) MortComm: Whistle, splat.  David [unrecognizable], 4th year Mech E
student, fell off the Senior House balcony.

(XXX) People's Albanian Embassy: The revolution has started.

(WDS) MooComm: Unlike its predecessor, {\em Die Hard II\/} is fantasy.

(D K) MooComm sub two: The original {\em Die Hard\/} at LSC tomorrow at 8:00.

(C H) It's a BIG SCREEN MOVIE --- see it at a theater.

(XXX) MooComm sub three: {\em Robocop 2\/} is also fantasy...

(WDS) Cornelia Otis: something about unemployment in the U.S.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

ALGOL.

\vspace{0.15in}
{\bf New Business\/}

(C H) The new {\em Wild Cards\/} book is out.

(SST) I tried to visit the aircraft carrier in Boston Harbor today.  Wait time
was 4 hours.

(C H) I hear the Soviet space exhibit is really good.

(A A) Miller Motion.

(D K) Fails.

Second Miller Motion passes a lot to 1 to 4 plus Spehn.

Meeting adjourns, 17:13 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
