\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

April 20th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, April 20th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(HAM) Motion to approve the minutes as better than plan B.

Motion passes, 9 to 6 to 7 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(HAM) Moo Comm - {\em Blues Brothers} on Sunday.

(JCC) LHE Report - We have lots of money and should go to New England
Mobile soon.

(S T) Picnic Comm - After 5 minutes of heavy deliberation, we have
decided May 6th as the day of the picnic.

(PJN) Skinner Report - Elections will be May 4th at the appropriate
time.  The results will be Robert Poole as Onseck, Derrick Kong will
be LHE, Elizabeth will be Vice, and John Conger will be President.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(PJN) Mini Cult - Deutch does the right thing and blasts ROTC for
being anti-gay.

(JCC) Miller Motion!

(PJN) Fails!

{\em Several motions are proposed and a matrix vote is taken, as
everyone sings Rabbits Have No Tails.  In the end, the result is
negative, so all motions fail.}

(RVH) Motion to vivisect a rabbit with a banana.

Motion passes many to a couple to a few more plus Spehn.

Meeting adjourned, 1714 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
