\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

April 6th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, April 6th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(C H) Hello Lisa!

Motion passes 5 to 0 to 0 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(C H) Con Comm - There was a ReaderCon.

(P D) {\em Various Toon Comms}

(PJN) Moo Comm sub I - {\em Princess Bride} tonight.

(PJN) Moo Comm sub II - {\em Little Mermaid} tomorrow night.

(C H) Sit Comm - On Sunday night, they're showing the pilot episode of
{\em Twin Peaks}, David Lynch's new soap opera.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

(HAM) They vetoed the abortion law in Idaho.

(C H) The King of Belgium had himself temporarily removed as head of
state so that he could avoid signing a pro-abortion bill.

\vspace{0.15in}
{\bf New Business}

(PJN) I'll just read the headline: ``Dean McBay To Step Down''

{\em Not much else in New Business worth mentioning.}

(C H) ReaderCon - July, 1991.

(HAM) Banana.

Motion passes 6 to 3 to 2 to plus Spehn.

Meeting adjourned, 1714 SST. 

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
