\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.60in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

January 12th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, January 12th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motion concerning the minutes?

(WDS) Move to approve the minutes in absentia.

Motion chickens 3 to 3 to 3 plus Spehn.

(ESD) Motion to approve Derrick as short, sweet and to the point.

Motion passes by Skinnerial decree.

\vspace{0.15in}
{\em bing\/}  {\bf Committee Reports}

(C H) Panther Comm - I'm working on Pinkdex.

(PJN) Christmas Comm - We got a Christmas card from the Los Angeles
Science Fiction Society.

(WDS) Sit Comm - {/em Beauty and the Beast} has apparently been
cancelled.

(WDS) Sit Comm sub II - The geniuses who run {/em Quantum Leap} have
finally clued in that not everyone who watches has seen the first
episode, so they worked in a synopsis of the situation in the opening
credits.

(M W) Moo Comm - In the wake of the disappointing box office returns
for Star Trek V, the sixth Star Trek movie is going to be set at Star
Fleet academy a few decades before V, with a whole new cast playing a
young Kirk, Spock, etc. 

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(PJN) Mini Cult - We got an article by Harry Stubbs about the new
decade.

(PJN) Motion to note that the shirt Sue is wearing is not banana
yellow.

Motion passes 8 to 6 to 5 plus Spehn.

Meeting adjourned 1719 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
