\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.60in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

January 19th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, January 19th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(C H) Motion to censor Robert for using the b word in a motion.

Motion passes, 4 to 1 to 2 plus Spehn.

(WDS) Cornelia Otis - They finally nailed Marion Bradley.

(J E) Banana Comm - A man who survived a 1928 trip over Niagra Falls
in a barrel, slipped on a banana peel and died.

(PJN) Moo Comm - LSC's Cartoon Festival is Wednesday.

(PJN) Skinner Comm - I got a letter saying that Federal Express will
refuse to deliver to MIT because we don't pay them on time.

(J E) Strek Comm - Wil Wheaton has been really upset over how little
time he has gotten this season.  He hasn't said anything, but I
wouldn't be surprised if he leaves the show.

(WDS) Sit Comm - Probably the last episode of {\em Beauty and the
Beast} on Wednesday.

(LAK) Jour Comm - I haven't had any reviews yet.

(J E) I Don't Know What To Call This Comm - At the memorial service of
Graham Chapman, John Cleese got up to speak: ``Graham Chapman,
co-author of the dead parrot skit, is no more,'' etc.

(C H) Panther Comm - We have a vague form of a Series Dex.  We have
about 15,000 titles in the library according to a not-completly
updated data base.

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(HAM) The Skinner has a new picture in the Rogues Gallery.

(C H) Motion to shoot this dying meeting with a banana.

Motion passes a lot to a loud few to a few plus Spehn.

Meeting adjourned, 1716 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
