\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

May 25th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, May 25th, 1990,
1700 SST, John Conger, President and Skinner presiding.

(JCC)  [gripes about Onseck not being here, and lack of minutes]

[Onseck's Note: There actually were no minutes from the week before, owing to
the fact that there was no meeting --- seems that no Star Chamber members
showed up.  Bleah.]

Some kind of motion is made.

(S G)  Second.

Motion passes 7 to 1 to 1 moose plus Spehn!

\vspace{0.15in}
{\em bing\/}  {\bf Committee Reports}
(C H)  I think there's a game this weekend...

(S G)  Moocomm:  {\em Total Recall\/} is opening RSN.

(D K)  Moocomm sub two:  {\em Back to the Future III\/} opens today.
Boston Herald ran a full page color ad.

(C H)  Marion Zimmer Bradley is real sick.

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

ALGOL.

\vspace{0.15in}
{\em bing\/}  {\bf New Business}

[Seth whines about wanting to be a keyholder.  Ken slaps him around and
does some neat martial arts tricks.]

(C H)  MiniCult: Boston Globe: College memories times seven in Kansas.
[A woman hacks a yearbook as seven personas.]

(C H)  Jim Henson, Kermit dies.

(E D)  Motion to make Seth a magic bananna.

Motion fails 5 to 7 to 0.

Someone makes a Miller Motion.  Fails.

Second Miller Motion passes by Skinnerial decree.

Meeting adjourns 17:07 SST.


\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
