\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

February 25th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, February 25th, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(HAM) No motions.

Motion passes, 7 to 2 to 2 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(WDS) Cook Comm - I got our copy of Glen Cook's {\em Tower of Fear}
autographed.

(RPP) Fame Comm - On Tuesday, I opened up the {\em Hartford Current}
and said ``Gee, that's funny.  I didn't know I worked for the Drug
Enforcement Agency.''  The article had to do with efforts to defoliate
coca plants with caterpillars and using soil fungus to ruin marijuana.

(WDS) Strek Comm - The big night is tomorrow.  It lives, the return of
Tasha Yar, for one night only.

(WDS and PJN) Bat Comm - Next Tuesday, Adam West.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(???) Miller motion!

Fails.

(WDS) Second Miller motion!

Motion chickens, 1 to 1 to 6 plus Spehn.

(HAM) Second second Miller motion.

Motion passes, 6 to 0 to 2 plus Spehn.

Meeting adjourned, 1709 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
