\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

August 3, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, August 3rd, 1990,
1700 SST, Derrick Kong, LHE and pseudo-Skinner presiding.

Minutes read by Herb Miller.

(D K) Motions concerning the minutes?

(KRJ) Motion to accept the minutes as day-glo.

(WDS) Yeah.

Motion passes a bunch to a few to less plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(KRJ) MortComm: Ed Ensch died.  NYT obit did not mention that he was an artist.

(Whoever) People's Albanian Embassy: Albania has resumed formal ties with the
Soviet Union.

(G F) (Something)Comm:  Brand new edition of the {\em Science Fiction
Encyclopedia\/}.  Someone should tell them that MITSFS is not now knows as
NESFA.

(KRJ) Whoever told them this should also tell them that Boskone is now known as
Readercon.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(HAM) Usual.

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(WDS) Minicult: Trial of some alleged drug kingpin, which got decided by a jury
of 11 people because one got kicked out.  In an attempt to find out more info
about something regarding the case, this juror called the Median Cartel and
asked them for some information.

(C H) 1-800-225-DRGU.

(WDS) 1-900-KINGPIN.

(C H) Semi fwoosh-comm.  Burglary at Cambridge building.  Man had a hobby that
got out of hand.  Warrant to seize his house's contents.  He had a lot of
weapons.  A lot of weapons.  He used to work for MIT.  Very bad.

(RGvdH) I have a donation for MITSFS.  (Bananna party decoration.)

(Someone) MiniCult:  I seem to be an Admiral in charge of starbase 24 in the
Star Trek universe, at least according to the Peter David comic.

(LAM) Move to appoint Robert in charge of putting up the bananna.

Motion passes A lot to none to a few plus Spehn.


Meeting adjourns 1715 or so SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
