\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

March 23rd, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, March 23rd, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(S G) Motion to approve the minutes as ``Seth is a geek.''

Motion passes 6 to 1 to Andy Su plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(HAM) Way Back Comm - This Saturday at Coolidge Corner is the special
Jay Ward tribute show.

(PJN) Twit Comm - Saturday morning, LSC realized that they should get
the power amplifier in 26-100 (which was used to drive the
subwoofers), but they were beaten to it. 

Phone Comm - {/em It was Andy Su}

(S G) Twit Comm sub II - Mags Harries is working on a sculpture for the
Student Center, a giant hairball to be hung in the atrium.

(WDS) Strek Comm - They had a bad episode last week which a
disproportionately large number of people thought was great.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

(LAK) Andy says he might be coming up in May.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

Time warp to Committee Reports

(C H) Moo Comm - I actually saw {\em Handmaiden's Tale} last week.  I
wasn't terrible.  They just didn't go far enough and there were too
many inconsistencies.

(RVH) Moo Comm sub II - {\em Joe vs. the Volcano}: eh.

Time warp collapses.

(C H) Cornelia Otis - New potential abortion restrictions in Idaho and
Guam.

{\em Lots of inane silliness here.}

(RVH) Motion to gag Robert with a banana.

Motion passes 9 to 1 to 3 plus Spehn plus Andy Su.

Meeting adjourned, 1720 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
