\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

January 5th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, January 5th, 1990,
1700 SST, John Conger, LHE and Pseudo-Skinner presiding.

(JCC) Motions concerning the minutes?

(HAM) Move to minute the motions as Connie and Bob.

Minutes passes 5 to 0 to 2 plus Spehn.

{\em bing\/}{\bf Committee Reports}

(WDS) Mort Comm - Apparently Robert Adams has finally died.

(RJG) Mort Comm sub II - Doc Edgerton has died.

(HAM) Mort Comm sub III - Alan Hale Jr.

(WDS) Move to note that his character's name was in fact Jonas Grumby.

(LAK) Jour Comm - Write for TZ or I'll run over you with my car.

(WDS) Strek Comm - New episode on Saturday.

(WDS) Sit Comm - It has popped up on the net that Beauty and the Beast has been cancelled.

{\em bing\/}{\bf Old Business}

(WDS) Isaac Asimov is 70.

(HAM) I got some mail from Scott Kitchen who was talking with a guy who was the Skinner back in 1954.

Old business Algol - Usual everything: {\em bing\/}

{\em bing\/}{\bf New Business}

(HAM) Banana.

Motion passes lots to none to just a little bit plus Spehn.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
