\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

February 2nd, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, February 2nd, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(D K) I second the 15 seconds of silence that just occurred.

Motion passes, 7 to 0 to 1 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(PJN) Moo Comm - LSC is showing {\em Earth Girls Are Easy} tonight.
Sunday is {\em Heavy Metal} and Monday is {\em Indiana Jones and the
Last Crusade}.

(PJN) Piano Comm - I've got a new sucker.

(PJN) Phone Comm - {\em Ring.  Herb makes a Miller motion, but it
fails.}

(PJN) Piano Comm cont. - I've got Steph to do the picnic this year.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

(JCC) With regards to the nebulous 15\% at the bookstore, I went down
and talked to the owner today, and he said, yes, if you present your
MITSFS membership card, you get 15\% off.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(G F) After going through Noriega's house, U.S. soldiers found a bag
of stuff that they thought was cocaine.  It turned out to be tamales.

(JCC) Miller motion!

Motion passes, 7 to 1 to 2 plus Spehn.

Meeting adjourned 1709 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
