\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

October 19, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, October 19th, 1990,
1700 SST, John Conger, President and Skinner presiding.

(DKK) (Reads minutes very fast.)

(KRJ) motiontoapprovetheminutesasmumble.

Motion passes lotstononetomaybealittleplusspehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(WDS) FameComm: (Something about a local guy who claims to have invented the
carbon 12 diamond.)

(RPP) CorneliaOtis: The BBC is starting a sitcomm called {\em Heil Honey, I'm
home\/}.  The premise is that Adolf Hitler and Eva Braun are living in an
apartment in Berlin next to a Jewish couple.  This is supposed to be funny.

(WDS) StreckComm: Brent Spiner is a really cool actor.

(RPP) There was an article in NewsWeek about the new Trek.  It's supposedly
more popular than the old show ever was.

(Malcolm) Last Sunday's {\em Land of the Lost\/}, they actually are getting to
the good episodes.  This last episode they showed was scripted by Larry Niven.

(JCC) On {\em Twin Peaks\/}, they just introduced signals from space to
explain away the supernatural stuff.

(WDS) The two top editors of {\em Omni\/} have quit in protest of the cover of
the latest issue.  An ad was visible on the cover through an oval hole.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(JCC) I was going to get an LSC slide for MITSFS.  Well, I was busy.

(S G) Motion to commend the Skinner for his promptness.

Motion passes lots to 1 to 1 plus Spehn.

(C H) SnakeComm: In the {\em Boston Globe\/}: Apparently, a pet distributor
sent out a shipment of deadly poisonous snakes as garter snakes.

(Malcolm) Madonna is threatening to spank 18 year olds who do not register to
vote.

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(D K) Kendall and Friedman won the Nobel Prize.

(C H) {\em Total Recall\/} tonight.

(S G) Motion to cleverly disguise a deadly East-Asian water snake as a
bananna.

Motion passes 9 to 2 to 3 plus Spehn.

Meeting adjourns 1717 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
