\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

September 14, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, September 14th, 1990,
1700 SST, John Conger, President and Skinner presiding.

(WDS) Move to approve the minutes as snately.

Motion passes 7ish or to 3 to 4 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(WDS) MooComm --- Jay Carr of the {\em Globe} who didn't like {\em Akira}
doesn't like {\em Hardware} either.  Maybe this is a point in its favor.

(D B) We got a phone call a while back which was an invitation to a free
showing of {\em Hardware}.  Random people went.  On a scale of 1 to 10, we
rated it a 2.5.

(RPP) The Flash is coming to CBS.

(D B) Pumpkincomm --- what is it?

(D K) MooComm --- Saturday: {\em Hunt for Red October}

(C H) MooComm: 1 AM tonight they're showing {\em Get Crazy} on channel 56.
Also, Akira Kurosawa has a new film out called {\em Dreams}.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(G F) Two former editors of TZ have won Hugos!

(D K) I found about 5 inches thick of printed covers for TZ 36.

Usual usual of usuals.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(WDS) MortComm --- Kliben died.

(RPP) Narc in Senior House is living in Runkle Towers.

(JCC) We have a new Shelfdex now.

(G F) There was a WorldCon.

(WDS) Bananna!

Motion passes 13 to 4 to 4 plus Spehn.

Meeting adjourns 1721 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
