\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

March 2nd, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, March 2nd, 1990,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(RVH) Motion to approve the minutes as whatever.

Motion passes 4 to 3 to 2 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(RVH) Mr. Fusion Comm - It's back.  The {\em Wall Street Journal} had
an article about real scientists at real place like Los Alamos finding
tritium.

(WDS) Strek Comm - They redeemed themselves for the entire 2.N year
run in one episode last Saturday.  It was very impressive.

(PJN) Piano Comm - March is Keyholder awareness month.

(WDS) Moo Comm - {\em Hunt for Red October} opens today.

(PJN) Moo Comm sub II - LSC will be showing {\em Teenage Mutant Ninja
Turtles} Sunday morning at 1am.

(WDS) Sit Comm - This Sunday at 8pm on channel 2, there will be {\em A
Very British Coup}.  It is sort of an alternate timelime story about
Great Britian after the election of a blatantly and obviously
socialist Prime Minister.

(WDS) Sit Comm sub II - It's unofficial, but very likely that {\em War
of the Worlds} is dead meat.

(KRJ) ??? Comm - I heard through the grapevine what William Shatner's
next project as a director will be: {\em Kingdom of the Spiders, Part
II}.

(HAM) Ex-Skinner Report - Monday will be exactly two years since we've
had an inventory.

\vspace{0.15in}
{\em bing\/} {\bf Old Business}

(C H) Hopefully, I will be able to get something together this weekend
for Pinkdex.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

{\em There isn't much new business worth mentioning.}

(HAM) Motion to condemn the old ex-skinner for letting me get away with
passing a motion with the words ``Teenage Mutant Ninja Bananas'' in
it.

Motion passes by Skinnerial decree.

Meeting adjourned 1715 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
