\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

August 31st, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, August 31st, 1990,
1700 SST, John Conger, President and Skinner presiding.

(C H) Move to approve the minutes as MIA.

Motion fails 2 to 5 to 3 plus Spehn.

(LAM) Move to not approve the minutes as stateless.

(JCC) All in favor of not approving the minutes as snateless.

Motion passes lots to 1 to 4 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(WDS) Whooshcomm.  (Flames about the space thing that failed in the shuttle
bay.)

(JCC) MooComm -- we were going to show Hitchhiker's Guide, but I'm not
convinced people will show.

(HAM) Aloha Lenscomm -- we're moving soon.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(JCC) We have no money.  (whimper)

(WDS) Happy 102nd anniversary Jack the Ripper, wherever you are.

John flakes out on Nostradamus.

Phonecomm.

Adina is not here yet.

John didn't know who it was.

It was probably Richard.

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(JCC) We're going to get money soon.

(HAM) Sell the Harvard Bridge by the Smoot!

(C H) MiniCult -- if you wash your cat once a month, it won't give you allergy
problems as much, but getting the cat to allow it will be hard.

John wants a shelfdex.

(WDS) WeeklyWorldNewsCon -- ``What it feels like to be electrocuted -- seance
interview with Ted Bundy.''

(HAM) Move to condemn Bill for saying Bananna.

Motion passes 9 to 2 to 2 plus Spehn.

Meeting adjourns 1711 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
