\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

September 28th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, September 28th, 1990,
1700 SST, John Conger, President and Skinner presiding.

(A S) Motion to approve the minutes as thoughtless.

(LAM) Second.

Motion passes 5 to 2 to 3 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(RPP) StreckComm: There's a new netnews newsgroup called\\
alt.~french.~captain.~borg.~borg.~borg.

(JCC) Sitcomm: The season opener of {\em Star Trek: The Next Generation\/} is
tomorrow.

(LAM) {\em Quantum Leap\/} season premiere.  MooComm: Tuesday, LSC is showing
a free sneak preview of Fantasia.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(A S) Hi!  Well... that's about it.

(JCC) (Reads something about the original Spehn.)

(LAM) Ex-skinner report.  Janice is expecting.

(A S) She seems to be doing pretty well.

(LAM) I finally got my ravs!

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(JCC) We have an inventory tomorrow.

(JCC) Jenkins' Science Fiction Literature class is going on a field trip to
the MITSFS.

(A S) Move to send many tons of banannas to Iraq to feed those poor, starving
terrorists.

Motion fails.

(KRJ) Miller motion.

Fails.

Second miller motion passes.

Meeting adjourns 1714 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
