\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

October 26th, 1990

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, October 26th, 1990,
1700 SST, John Conger, President and Skinner presiding.

(HAM) Motion to mumble the minutes as approved.

Motion passes 6 to 4 to 4 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(WDS) MooComm: LSC is having a horror triple-feature this weekend:
{\em Tremors\/}, {\em An American Werewolf in London\/}, and
{\em Wall Street\/}.

(S T) There's a vampire movie marathon at Coolidge Corner.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

ALGOL, COBOL, SNOBOL

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(C H) I have a review of {\em Grim Fairy Tales\/}, which is playing at the
Nickelodeon.  It's basically western horror stories with suspense and
supernatural elements.  It has James Earl Jones.
Also, there was a letter in the {\em Globe\/} flaming about a column by David
B. Wilson transmitted from another planet\ldots

(KRJ) Followup to last minutes: The garter snake story from the last minutes
was a hoax after all.

(S G) Motion to condemn MIT for printing this Noan Loat on bananna colored
paper.

Motion passes 10 to 7 to 2 plus Spehn.

Meeting adjourns 1711 SST.

Time warp to meeting: We reaffirm our faith in the Great Pumpkin.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
