\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 19, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to approve the reading of the minutes as being taken on film fails 2-7-3+Spehn.

\goto{Committee Reports}
\subsection{PseudoLibcomm}

We have LibComm here.  We have explored the depths of one of the old magazine cabinets that nobody knew what was in (the $\beta$ cabinet).

If somebody actually cares, we could do something.

\subsection{Star Chamber}

Christian Ternus is now officially the Onseck.\\
Motion to congratulate the pseudo-onseck on a succesful coup passes 9-4-1+Spehn.\\
Motion to rename chickens to pigeons (because we're talking about a coup) fails by Skinnerial decree.\\
We got new books!  They are shiny.\\

\subsection{Pianocomm}

We have two new keyholders!  Sukrit Ranjan (SIR) and Miss Katie Ray (MKR).

\subsection{Hasslecomm}

The Purge proceeds apace.  We processed six boxes yesterday.  JSB was happy to purge Eddings, Dickson and Donaldson.  

Discussion about methodology of the purge ensues.  Donaldson produced a ``giant hole'' in the shelves.  Evidently somebody else decided they didn't like Thomas Covenant, because we have a new, shiny set thereof. 

The purged books are going out to Darkest Waltham, not being sold.  The last time we asked MIT Libraries about more space, they said ``No, and please take back the stuff you have here.''  So don't talk to the MIT Libraries staff without asking the Skinner.

\subsection{Pseudo-Trojan}

We may someday figure out what the Gadouri donation is.  KR: It's the thing we need to process.

\subsection{Magventory}

There will be magazine inventory during the last week of IAP.  \textbf{All keyholders will be required to put in four (4) hours, similar to actual inventory.}

There are a lot of weird magazine caches in various places.

\subsection{Onseck}

We now have new membership sheets.  Something happened, but it went down the memory hole.

\subsection{$\hbar$ comm}

Some Extremely Nice People decided to Creatively Modify Our Poster In The Infinite.  

\subsection{LHE}

The books are being maintained.  Everything is status quo.  Nothing to see here, move along.

\goto{Old Business}

There was a Mystery Hunt.  It happened.

Arisia came and went.

We haven't gotten back at HRSFA.  JM: ``Let's go to dinner and skip out on the check!''

W20 Speaker: ``Testing, testing one two three.''  Everyone: ``IT WORKS!''

ALGOL.

\goto{New Business}

Nooo, that's not the usual result.

Albanian Motion passes 20-0-2+Spehn.

The Skinner would like to commend Mobcomm for acquiring the entire set of Girl Genius, not that he needs more crack.  JFC: ``Why... why?''  ALC: ``Because they're good!''

We have new scissors.

ALC just recently learned that water has an actual LD50 (the dose at which it is lethal to 50\% of the people who consume it.

On a related note, Kate does not mind what you inject into her veins as long as she's unconscious at the time.  This includes coconut milk and orange juice with pulpy bits.

You have now entered... the Twilight Zone.

The next Twilight Zine will have a ten-page rant by the Skinner about how much he hates Fragile Things.

Motion to second fails by Skinnerial decree, whatever the hell it was.

JSB and KR went through the Keyholder Notes last night and mapped years -> number of keyholders.  We've keyed four people this month, and it's only January.

Motion to go to the store and get an emergency ration of prentices passes 12-7-3+Spehn.

We have a large proportion of active keyholders.

An attempt to convince Stephanie Lin (the only non-(ex)keyholder in the Library) to become a prentice ensues.  ``Become a prentice!  You can do Book Origami!\footnote{Bluebellcomm.}''

The Skinner is emacs?  No, but he can run it occasionally.

KR just finished Land of Mist and Snow.  ``It's like the history of the Atrocity Archives.''

CJT: The description of Accelerando (``It makes hallucinogens obsolete'') is accurate.

ESK: The Malazan books are awesome\footnote{Kate also likes the Warhammer books}.

\goto{Future Business}

A Miller Motion fails for lack of a second.

Discussion about Star Trek spinoffs ensues.  We apparently have \emph{two hardcovers of Worf's First Adventure}.  WTF.

JSB almost finished a Dramatic Cover Reading, but he was \emph{denied} by many simultaneously proposed and seconded Miller Motions.
\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
