\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 2, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent

Bonus Pre-Meeting Quotes: ``No, Kate, you did not embezzle the balloons.  Bank robbers don't
embezzle money from a safe, no matter how physically close they are to it.''

MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to approve the reading of the minutes as nobly read passes 18-12-1+Spehn

Motion to send the prentices to Mordor to figure out the pronunciation... to be able to translate 

\goto{Committee Reports}

\subsection*{Pseudo-Pianocomm}

Our prentices and keyholders have been mapped onto balloon-space.

We have a new prentice - Amy! Yayyyy.

\subsection*{Pseudo-Trojan}

The Sherwood (Part I: A New Hope) and Joblove donation letters got sent out. 

\subsection*{LHE}

We embezzled balloons, we embezzled soda, and we gave money to Metropolitan Warehouse!

Does Kate embezzle her problem sets when she does them? 

Ba-dum-pish.

We got money from Finboard to buy books!  Woooooo!

We also found out lots of stuff, like why we weren't getting our money originally.

Finboard wants to see book prices.  Dude, when did Finboard start having pants?

\subsection*{Star Chamber}

Kevin is in the process of processing the ``to be processed'' books on the Star Chamber shelf.

90\% of everything is crap.  This includes MITSFS donations.

Motion to - not yet fails by Skinnerial decree.

Mail got processed.

\subsection*{Pseudo-Theftcomm}

Theftcomm sucks and didn't change the schedule.  Theftcomm should deal with this.

ALC: ``Wait, what?''

\subsection*{Panthercomm}

Panthercomm processed lots of books.  Prentii should shelve them.

I hear we have prentices.

\subsection*{Pseudo-Magventory}
 Magazine inventory in the circ room is almost finished!  Once that's done,
 we can stop checking out magazines on the Keyholder Desk sheet.

\subsection*{Pseudo-Magdex}
 Lots of Magdexing is being done by KKB and Carrie, such that the under-the-desk
 space is currently overflowing. 

\subsection*{Onseck}

So, remember those orange stickers that the Onseck was really excited about finding
because he thought they didn't exist?  Yeah, they don't exist. 

We got our binder and some binder clips.  Everything else sort of vanished, mostly
because the noble proprietors forgot to email MITSFS.

\subsection*{Pseudo-Transylvaniancomm}

Books which fell due during the timewarp are now at Max Fine (ominous organ music).

The Skinner then proceeds to hum a tune, about which many questions are asked.

JM: ``If you didn't understand it, assume that Kevin just sucks.''

\subsection*{Pseudo-Hasslecomm}

The Purge is proceeding.  The hardcover shelves don't have any space, ahhh.

\goto{Old Business}

The Keyholder Notes are still waiting for people to read them.  ESK: ``The first three pages are
exciting!''

Do you know how much violence there is in the Keyholder Notes?  JM cannot grep dead trees.

A Dramatic Back Cover Reading from ``A Key for the Nonesuch'' ensues.  It turns out that the presence
of ``keyholders'' on the back cover is not a coincidence - Geary Gravel is a MITSFS alum. 

All in favor of (something involving the Onseck|Nothing|Paige)? 11-4-3+Spehn.

I hear we have prentices.  ``All over the place!  We need a flyswatter.''

There will be more singing!  Tomorrow!  Free: 10:59:59 in 10-250.

A motion to construct a rubber, helium-filled Portuguese man-o'-war feels like a bad plan.  Keyholders
are sort of stationary.

Lambda lambda lambda lambda lambda lambda CONS CONS!

My god, it's full of car's!

ALGOL.

\goto{New Business}

There was no complaint!

So, these balloons here are not the Skinner's fault.  Kate \emph{STOLE} them from The Tech.  Guard
them with your life.  Guard them with other people's lives too.

It's like amusement-park voodoo.

The slippery slope sucks, yes, especially when it involves Charles Darwin injecting people in order
to make them produce clones.

A loud chorus of ``nooooooo''s ensues while Kevin considers keeping this book.

\goto{Future Business}

Motion to commend our newest prentice for being stealthy and ninja-like passes 11-2-7+Spehn.

Paige, you should scold him!  He has neglected the poultry!

In the future, stuff will happen.

In the future, we will be unhosed.  That future is not now.

In the future, the Purge will be over.

In the future, we will have more space.  That future isn't now, either.

In the future, the beginning-of-term mailing will go out!

Motion: In the future, there will be explosions! passes 22-2-3+Spehn.

Motion to put banana-colored hats over all the prentii's heads so they can't see what's going on passes 9-8-3+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
