\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 29, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christian Ternus, Onseck and Interim Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to have Ternus and Kate do the Mexican Hat Dance at the same time: 17-4-8+Spehn

\goto{Committee Reports}

\subsection*{MagDex}

MagDex got through about 10 years of F&SF in last Saturday's MagDex party.  Lots of Reserve and Circulating magazines were replaced.

Our magazines greatly increased in quality!  Awesome!

\subsection*{Panthercomm}

We got Charmed spin-offs.  Slightly less awesome.

MKR was added to Panthercomm.

``What is Panthercomm?''  Finger Motion!  ``What is a Finger Motion?''  Finger Motion!

Both Finger Motions pass by pseudo-Skinnerial decree.

\subsection*{pseudo-Hasslecomm}

There is a box near the keyholder desk labeled ``Whose box is this?''

It wants a home and someone to claim it.  If you claim it, let Hasslecomm and the star chamber know.

Kate says hi to the center of the universe via the mysterious powers of zephyr.  Entire library: `` HI KATE!!!''

\goto{Old Business}

Rambling about summer and jobs and movies.  The weather was hot.

In the past, HRSFA gave us the ancient slinky of peace.  Then we lost it.  But we later got a pseudo-ancient slinky of peace.

\goto{New Business}

We had the usual debate AGAIN!  We're getting good at this.

CJT realizes that he should cut off the usual debate by talking really fast.

MKR is reading Gardens of the Moon!  Yay!

Lots of Tim Powers books are good.

CAK finally read the review in TZ about how much the Skinner hates Fragile Things.  His review is cleverly disguised as a good review.  Tricky Skinner...

Pseudo-Skinner hates Fragile Things!

\goto{Future Business}

In the future, it will be the Fourth of July.

Motion to give CJT's parents a banana for coming all the way to Cambridge to visit: 16-2-6+Spehn

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
