\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 17, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Christian Ternus, Onseck and Psuedo-Skinner, presiding; Andrew Clough, Thunderbunny and Psuedo-Onseck recording

Minutes read.

Motion:  Move on with the meeting.  Chickens 10-4-12+Spehn

\goto{Committee Reports}

\subsection*{DeckchairsOnTheTitanicComm}

We raided the warehouse!  New people have been added to the acls on the warehouse, and we ran off with some shelf parts that we need.  We should be sending more ninjas to the warehouse for a raid in the future.

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

\subsection*{JourComm}

You should all write stuff!

\subsection*{Mobcomm}

Some books were ordered, but not a huge number since I'm a bit over budget.

\subsection*{hBarcomm}

We've got our first new member of the year, but not yet our first new undergrad member.

Discussion of the finances of MITSFS, and how to get rid of books that are too worn out to take up our shelf space but still deserve a good home.

New plans are hatched, which will have to be run by the Star Chamber.

Discussion about what people think about Harry Potter.

Motion:  Acknowledge Christian for psuedo-hating Fragile Things until Kevin comes back.  Psuedo-Passes  26-0-1+Spehn


\subsection*{Katiecomm}

Please shelve a few books.

\subsection*{Hasselcomm}

The purge continues!

\subsection*{Warcouncil}

Tell me how much we're purging

\goto{Old Business}

Some of us haven't seen Galaxy Quest (gasp!)

Some old donation boxes back there have CJT's name on them.

Motion:  Summary gavelling of anyone who doesn't like Diane Dwain.  Passes 16-5-4+Spehn

ALGOL

\goto{New Business}

Discussion of how Carl got injured in moving and spilled a bit of blood on the gavel, thereby nourishing the souls of former skinners.

Award Carl a purple heart for service to the library!  12-0-2+spehn

Motion:  Feed me something that isn't a banana 'cause I don't like bananas.  15-2-0+Spehn

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
