\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 3, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Christian Ternus, Onseck and Interim Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to commend the gavel for having mysterious properties of DOOM: 16-0-0+Spehn

Motion to commend the Carrie/Jackie amalgam for being generally Cthulhuoid: 17-0-4+Spehn

\goto{Committee Reports}

\subsection*{Mobcomm}

We have received 188 new books in the last two weeks!  Panthercomm, thanks to MKR's inhuman capacity to do Panthercomming, is not too far behind.

\subsection*{Dexmistress}

KCR is now on Dexmistress!

Motion to approve speaking on the third person on general principles: 8-4-7+Spehn

Wombat is a funny word (somehow a motion- a wombat motion?): 13-4-6+Spehn

\subsection*{Aloha Lenscomm}

WDS wants us to have pictures of the library on a web page.

\subsection*{Pseudo-LHE}

Mobcomm is a wonderful, amazing entity who submitted receipts in TWO batches!  KKB is very happy.

Pseudo-Skinner is approving of KKB's pink sandal's (also a motion): 12-4-6+Spehn

Digression about Joe Haldeman and his MIT Science Fiction writing class.

\subsection*{Katiecomm}

MKR did Panthercomming, Bluebellcomming, and Hasslecomming.  Other people also did lots of work.  Just like always.

Motion to order the Skinner to purchase banana-colored binders: 7-14-2+Spehn

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

Digression about Night Watch and our recently-obtained sequel to it, Twilight Watch.

KCR is twitchy.  The books are coming, coming, always coming for him.

Move to travel to Seattle and purchase Carrie a banana from Amazon: 11-6-2+Spehn

%\goto{New Business}

%\goto{Future Business}

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
