\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 13, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, (on Friday the Thirteenth!)
Christian Ternus, Onseck and pseudo-Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to commend the minutes for being well-written, contrary to Onseckatorial tradition: 7-1-6 + Spehn

Wasn't there a motion regarding Fridays the Thirteenths a while back?

\goto{Committee Reports}

\subsection*{Panthercomm}

MKR has done about three boxes of Overflow, yay!

\subsection*{pseudo-Mobcomm}

We went and bothered the CAC until they let us into the UA office to get our books.  There were about 25 boxes of books from the past month and a half.

Motion to condemn the UA on general principles passes by pseudo-Skinnerial decree

\subsection*{pseudo-LHE}

KKB went to Metropolitan and made it so that we don't owe them more money, at least for a while.

\subsection*{Onseck}

We have a new money book.  We no longer have an antiquated money book.

\subsection*{Vox Sciurorum}

JFC got a picture of a fox squirrel!

\subsection*{Aloha Lenscomm}

Got a picture of MKR's eyelids.

\subsection*{Assistant Surgeon}

KLB fixed books!

\subsection*{Anti-Aloha Lenscomm}

MKR: ``Stop taking pictures during meetings!''

\goto{Old Business}

MKR saw the new Harry Potter movie.

ALGOL

\goto{New Business}

Blah, blah, blather, blah...

What anti-crack is ALC smoking?

A bunch of people are falling asleep.  No, seriously.

Motion to bing the gavel passes by pseudo-Skinnerial decree.

CJT: ``Is the gavel ringing or is that my ear?''

MKR tries to steal KLB's shiny pants.  Unsuccessfully.

\goto{Future Business}

MKR and KKB will be away for their respective family functions next week.

A verrrrrry tired version of ``Skinner has no tail at all.''

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
