\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 7th, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to have the minutes read by a Kzinti next time: 8-5-3+Spehn\\
Motion to declare Ternus equivalent to a hungry Kzinti: 6-4-2+Spehn\\
Motion to have a matrix motion to preserve temporal continuity: 16-2-1+Spehn\\

All motions fail.

\goto{Committee Reports}

\subsection*{AlohaLenscomm}

JFC is irradiating us all with photons!  KCR's new keyholder picture is of him being driven mad by Perl.

\subsection*{Star Chamber}

Dexmistress has become Libcomm!  Libcomm should have $1d2+1$ members, but currently it is just KCR. 

Paige has become Atomcomm.

\subsection*{Libcomm}

Mostly KCR hasn't been working on Dexhamster very much this week.

\subsection*{ConComm}

The Skinner went to a convention over the summer, but failed to meet Fuzzy Pink Niven.  However, as he is 
Skinner again, he can do no wrong.

But he was always the Skinner!  Perhaps he was the Skinner in Absentia.  Or Exile.

\subsection*{Jourcomm}

People should submit to Jourcomm.

\subsection*{Vox Sciororum}

JFC had nut fragments dropped on his head.  That seemed like the kind of thing he would enjoy.

\subsection*{Hasslecomm}

The Various Purges are going out to Planet Self Storage Real Soon Now.

\goto{Old Business}

Paige passed her NRC nuclear reactor operator exam!  Yay!

Alas, summer is now over.

ALGOL.

\goto{New Business}

The usual debate is going on over Email.

Random?  Have a long and wankerous argument?  \emph{Never.}

Where did the Gooddex go?

Jourcomm has to be motivated.  Don't worry, it won't be hard.

Four keyholders and prentices are taking 21W.759.

Monday at 10AM, there will be a moving party from Metro Warehouse to the Library.

\goto{Future Business}

In the future, various people will be in the woods.  Sinisterly stabbing people.

Various attempts to strike up a woodsy adjournment song fail.

Motion to find a replacement for the boffer gavel fails for lack of a second, or possibly because it sucks.

Motion to form a committee to create a Science Fiction Society Starter Kit, containing a box of books, a Starter Gavel, and a Starter Banana passes 17-0-7+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
