\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 30, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes for not talking to us or stabbing us in the back chickens 2-3-7+Spehn.

\BING

\goto{Committee Reports}

\subsection*{LHE}

Once upon a time, approximately ten years ago, we had these things called the Books.  Then the Treasurer went to the Bahamas.  The LHE has brokered an extradition treaty with the Bahamas, and now \textbf{the books are done!}

You know how most keyholders don't worry about keeping the money book neat?  They should start, or the LHE will fine them!

\subsection*{Star Chamber}

Over the summer, several thousand dollars were stolen from MITSFS.  Keyholders should have received email with regards to the new money policies.  A police report is being filed.

The Onseck picked up the mail.  We got more boxes from a person named Brian Leibowitz!

\subsection*{Onseck}

CJT took the check over to the Rage Warehouse.

If there are any magazines that need to be renewed or that we should be subscribing to, contact the Onseck \emph{via email}, not in person, or he will forget.

\subsection*{Libcomm}

We're doing inventory on January 12th!  You should have received a sleep-depped email from KR.

We're also removing all the stuff from the Rage Warehouse.

%\subsection*{Alohalenscomm}

\subsection*{Katiecomm}

There was some Panthercomming, and some Bluebellcomming, and some Hasslecomming done.  Jake is out of town next week.

\subsection*{War Council}

ASA space allocations happened!  We didn't lose any space, but we didn't gain any either.

\subsection*{Bondagecomm}

JSB talked to the Libraries!  Cool stuff may be happening on that front; more on that later.

Our Seriesdex is the most advanced \emph{in the world}.

\goto{The Forever Business}

Haldeman is coming to MITSFS to give a reading on December 14. He will be reading from \underline{The Accidental Time Machine}! You all should come.  Bring your friends and enemies!

\goto{Old Business}

Discussion of SFWA's Surface-To-Foot Missiles incident occurs.

Oh hey, the writer's strike.  It's going on.

ALGOL.

\goto{New Business}

Ah, New Business.

ESK is reading Cordwainer Smith.  Turns out that Space Travel Really Sucks.

The Eschaton was... ORDER!  ORDER! \bing

The Golden Compass may or may not be a good book.

Motion to immanentize the Eschaton chickens 6-1-13+Spehn.

\goto{Future Business}

ESK bounces about the Watchmen movie.

Watchmen is a comic book.  YT: ``Graphic Novel, \emph{please}.''

In the future, term will be over.

Next Tuesday, Andrew Plotkin (an MIT person and a noted author of Interactive Fiction) will be speaking on the topic of IF and digital writing (6PM in 14N-233).

The Onseck attempts to swim inertially across the floor of MITSFS using his swivel chair, to stunned silence.

In the future, we will sing!

The Skinner still hates Fragile Things, Fragile Things, Fragile Things\ldots{}

Motion to persuade a banana to do a reading for us over IAP passes 14-3-1+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
