\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 12, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes as expeditious passes 13-3-7+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Titanic Tetris}

Kate just really wanted the name.

There are a lot more shelf parts in the library now than there were last week.  Hey, the reuse pile is gone!  Dude!

The Perl is more or less Karl's bitch now.

\subsection*{LHE}

They said there were problems, and there weren't problems, so \emph{we can has PO}.

\subsection*{Panthercomm}

\emph{The Onseck would like to note that this section of the meeting consisted of three minutes of KCR screaming.}

The Dex has various non-orthogonalities.  Karl explains this via interpretive dance.  And screaming.

\subsection*{Onseck}

The Onseck reads aloud Matthew Jarpe's blog post about the previous meeting.

\subsection*{Star Chamber}

First the Onseck, then the Skinner reads aloud a fictional statement about what the Library will be like in the future, and the Skinnerial response to such.

\emph{The Onseck would like to note that this section of the meeting consisted of three more minutes of KCR screaming, mostly in response to the assertion that the Hasslecomm books never left the library.}

\subsection*{Aloha Lenscomm}

Aloha Lenscomm took a picture of a chickadee eating out of his hand.  It's not library-related, but it's camera-related.

\subsection*{Jourcomm}

Jourcomm has a story!  It's the one from Maine.  Spiffy.

\subsection*{Lastcomm}

KCR scrounged a monitor!

\subsection*{War Council}

ASA Space Allocations are open.  If we got more space, \emph{bunnies unicorns ponies rainbows fairies}, that would be great.

\subsection*{Pianocomm}

Sophie covered a Boris Vallejo book, and was Noticing it.

\goto{Old Business}

KR often makes the mouse go red.

ESK, KR: ``Oh man!'' ``Isn't that old business?''  ``What?'' ``\ldots{} Maybe it's new business.''  ``How do you know?''


ALGOL.

\goto{New Business}

But what about the usual debate complaint?  We just skipped the debate and went right to the complaining.

Everybody's tired today.

We have Rising Stars Vol III.  Kate quickly and bouncily explains why everyone should read these books.

Batman's pretty nuts.  Questionably.

The Onseck's father is here.  Hello, Ternus' father.

We got in a bunch of Doctor Who (\emph{*taptaptaptap* *taptaptaptap*}) ancillary material.

\goto{Future Business}

JFC\ldots{} Has a Plan for the banana-colored couch.  Motion!  Rotation!  Rearrangement!  Moving boxes out of the way!  And that's how you put butter on the bread.  If you don't have a cat.

In the future, KR and ESK will have space in their rooms.

In the future, we will have another calendar!

Motion to declare the Boris Vallejo book to be a banana passes 7-1-2+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
