\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 16, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend that last sentence for not making any sense at all passes 8-3-7+Spehn.

\BING

\goto{Committee Reports}

\subsection*{42nd Army of the Society}

We attacked HRSFA!  It was awesome.  We beat them a lot.

\subsection*{Katiecomm}

Katie processed books.  JFC also processed books, including The Last Chronicles Of Thomas Covenant No Really We Mean It This Time.

\subsection*{Strosscomm}

We also got The Merchants' War.  Hopefully it won't suck.  Stross' books don't \emph{suck}, they just ``aren't as good as The Atrocity Archives''.

\subsection*{Boxer Rebellion}

We moved a bunch of stuff out to the warehouse.  The 104 Boxes of the Great Purge, the Lesser Purge, the Dexmistress|Libcomm Purge, etc.

The canonical location of the data that comprises the Pinkdex is now on the Monolith.

Monolith should probably have a UPS.

Client support for barcodes should probably happen this weekend.  Cool!

\subsection*{Onseck}

The Onseck mailed magazine subscription requests, and has more in the queue.

\subsection*{Skinner}

The Skinner responded via email to a gentleman who wanted to donate ~2000 hardcovers to MITSFS.

He also responded to a request to find two ads in the same magazine: one critical of the Vietnam War, one in support thereof.

If you ever go to the 

\subsection*{Theftcomm}

There is a new TIF!  Yay!

\subsection*{Vice}

KKB contradicted her job description as Vice by actually doing something: she went to the ASA Town Hall Space Allocation Meeting Shindig.  It was wankerous and mostly useful to MITSFS.

We may be able to get space in Walker.

\subsection*{Really Bad Bookcomm}

Spike\texttrademark{} versus Dracula Fight The Nazis.

\subsection*{Kvetchcomm}

People should write Kvetchcomm reviews!

\subsection*{Chamber Report}

Haldeman is coming to MITSFS to give a reading on December 14. He will be reading from \underline{The Accidental Time Machine}! You all should come.  Bring your friends and enemies!

Somebody should Bluebellcomm \underline{The Merchants' War}.

\subsection*{Trojan}

If any prentices want a substantial prentice project, they should contact KKB for Trojan (book donation processing) training.

\goto{Old Business}

But it's all Old Business!  Or none of it is.

ALGOL.

\goto{New Business}

Can I complain about us having the usual debate?  Anyone can complain about anything the want to.

Usual complaint about 6.002.  CAK complains about the complaining, but KCR finds that complaint completely unacceptable.

Discussion of manual labor and Splash ensues.  Dammit, we sold our country to China and they won't give us cheap computers in return!

If we make Niagracomm boxes look valuable, thieves will take them away for us.

\goto{Future Business}

Best bing of the meeting, if KR may say so himself.

The birds on the monitor have always been there.  They are the ViewSonic birds, and they have been there since Back In The Day.

In the future, Kate will suffer from brain damage.

Robert Jordan is like bad alcohol: it numbs your brain.  It's not that good, but at least there's a lot of it!  ALC: ``Shut up.''

Discussion of absinthe ensues.  Apparently it's now legal in the US!

In the future, the Star Chamber Fridge should be cleaned off.  Kate wants people she knows in her fridge!  Diced up, in a plastic bag, in the freezer.

In the future, there will be no bananas - Motion - 

Meeting is adjourned by the Adjournment Song, modified to include Fragile Things.

The Onseck still hates the Dark is Rising Movie, the Dark is Rising Movie...

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
