\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 24, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kendra Beckler, Vice and Psuedo-Skinner, presiding; Andrew Clough, Thunderbunny and Psuedo-Onseck, recording.

Minutes read.

Motion:  Approve the minutes as being metric:  Passes 4-3-1+Spehn

Motion:  Approve the minutes as being shorter than the actual meeting: Passes 3-2-1+Spehn

Motion:  Have another motion about the minutes: Passes 5-2-2

Motion:  Commend the psuedo-Onseck as being able to read his own spelling:  Passes 5-0-4+Spehn

\goto{Committee Reports}

\subsection*{Dexmistress}

Aaaaaaaaaah!

\subsection*{Katiecomm}

Books came in and were shelved.  A pile of donations were also processed and people were slowly shelving them.  Shelve them faster.

Yelena is doing a bit of panthercomm too.

Motion:  Commend Katie for guilting people into doing work Passes by Skinnerial decree.

\subsection*{LHE report}

ESK: I'm back!

\subsection*{Interim LHE report}

I'm glad Kat will no longer be mad at ME
\subsection*{Star Chamber}

The Skinner will be back real soon.

\subsection*{Panthercomm}

ESK:  I'm back.

\subsection*{Magventory}

It continues.

\subsection*{Dexmistress}

I'm almost ready to start a normal Panthercommer on my new software.

Some books seem to be randomly appearing and disappearing.  We also need more space and more bookshelves.

Motion:  Commend Ekate's hair cause its pretty.  Passes 9-1-4+Spehn

\subsection*{Alohalenscomm}

We've gotten a new MITSFS photo-book.

\goto{Old Business}

Voyager was launched about 30 years ago.

And Mt. Vesuvius erupted in 79AD on this day.

Motion:  Commend the spacecraft Voyager for being a badass example of human technology.

Motion:  Commend the mountain for being a badass and blowing its temper.

Motion:  Commend the spacecraft Voyager for being better than the TV show.

18-1-0
10-8-2
18-0-4

All motions pass!

Discussion of how Enterprise got slightly better before it was canceled.

ALGOL

\goto{New Business}

We've sold memberships to freshmen now!

JFC:  Earlier this week I was walking down the hall and there it was!  A mountain of bacon unguarded!  So I ate some.  I wish that happened more often.

Discussion of T-shirts, unknown T-shirts, and whether aliens could have interesting things printed on their T-shirts

\goto{Future Business}

In the future the CAC won't hate us.

In the future the frosh will be prentuses

KKB:  "Mmmm souls".

We have the activities midway to man next Friday from 4:00 to 6:30.

Our hardworking Dexmistress is busy arguing with his predecessors, and doesn't notice the ravening Diane sneak up behind him!

ESK:  "The vice has no height at all, height at all, height at all.
The vice has no height at all, just a little gnome."

Motion:  Replace the song with a banana.  Passes by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
