\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 23, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to approve the reading of the minutes as having been in English passes 11-4-1+Spehn.

\goto{Committee Reports}

\subsection*{Onseck}

Checks got mailed.

This weekend, which became this weekend, is still this weekend.

\subsection*{LHE}

We have a statement for January!

\subsection*{Mobcomm}

Yet more books were ordered.

\subsection*{Panthercomm}

This is a donation of pain, and the person who gave it to us should die.

Motion to authorize Kate for license to kill fails 15-16-2+Spehn.

\subsection*{Star Chamber}

Mail got processed, which turned into books on the Panthercomm shelf.

\subsection*{Pseudo-Pianocomm}

Our prentii have been doing work!

We have a new prentice - Scott Morrison!  Yay!

\goto{Old Business}

We still have not-enough-space.

The space allocation meeting happened, but we were all too hosed to make it.

ALGOL.

\goto{New Business}

Nya nya nya, noted and ignored.  Or maybe just ignored.

We're going to give JSB the ring-shaped Dusty Spark USB drive as an award for having read ``Stealth Planet.''

If the Skinner had devious plans, he wouldn't share them with us

Miller Motion: 20-8-6+Spehn

Motion to condemn the Skinner how much he hates Fragile Things: 16-8-10+Spehn

Motion to censure the Onseck for making such an improper suggestion: 3-8-14+Spehn

Determinant is -288 and all motions fail.

\begin{tabular}{|c|c|c|}
\hline
20 & 8 & 7 \\
\hline
16 & 8 & 11 \\
\hline
3 & 8 & 15 \\
\hline
\end{tabular}

Yes, that was the tangent!

Motion to commend the Onseck for not knowing what's going on fails by Skinnerial decree.

So, how about that Imperial starfleet. 

In that vein, Bad Taste is coming up a week from tomorrow (3/3/07) at 10:59:59.

Amy: ``I don't know computering!''  KR: ``I computered with your mom last night.''

Kevin then proceeds to make a ``Your Mom'' joke.

JM: ``Any one with better standards than you likes Fragile Things.''

Motion to condemn the Skinner for having standards that are not only lower than slime, they're lower than
slime with a banana peel floating in it fails by Skinnerial decree.

\goto{Future Business}

It's ringing wrong!

Malcolm: ``Three rings for the Elven-kings under the sky...''

ALC tries to quote from The Lord of the Rings and fails.

Signs you're in a geeky crowd: they're critiquing your pronunciation of the Black Speech.

Motion to go to Mordor to figure out the Black Speech pronunciation for the word 'banana' passes 27-22-1+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
