\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 25, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Andrew Clough, Thunderbunny and Psuedo-Onseck, recording.

Minutes read.

Motion:  Commend Minutes as ``Thought Provoking'' Passes 10-5-1+Spehn.

\goto{Committee Reports}

\subsection*{LHE Report}

The LHE will not be here over the summer, so if you need reimbursements talk to KKB the psuedo-LHE.  If something needs to be Dealt With wait for ESK to get back.  And there are checks.

\subsection*{Skinner Report}

KR will also be missing, he'll still be reachable but Christian will be the Skinner for the summer.

\subsection*{hBarcomm}

We have a redoing the poster party today and tomorrow.

\subsection{Warden of the Far Marches}

We're going to be moving some boxes to Planet Self Storage.  

\{Panthercomm}

ESK says she's going to be doing a lot of panthercomming before she leaves.


\goto{Old Business}

Finals are over! Term is Dead!  Long Live The Summer!

Pirates of the Carribean 3 came out.

ALGOL

\goto{New Business}

The new Megatokyo book is out.  A discussion of the virtues of explosions ensues. 

ESK:  We're in new business, thats new.

\goto{Future Business}

In the future the chamber will vanish.

Two weeks from today we're going to start summer hours, meeting at 6:00 instead of 5:30.

Motion:  Replace the Star Chamber with a banana for the duration of the summer.  Passes 12-0-3+Spehn

\bing
\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
