\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, Septober 14th, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Ekaterina Kuznetsova, Pseudo-DisOnseck and Lady High Embezzler, recording.

Minutes read.

Motion to commend the minutes for having a very precise method of time keeping: 7-3-4+Spehn, Motion passes.

\goto{Committee Reports}

\subsection*{Alohalenscomm}

We have pictures of shelves. And books. We could put them in the next TZ and terrorize the ASA. 

\subsection*{Katiecomm}

Katiecomm hassled everything! 

Katiecomm panthered a lot of things, but can't shelve them! 

Katiecomm is awesome like that. You should shelve books and Katiecomm will still be awesome.

\subsection*{Pseudo-Piano Comm}

A prentice tried to shelve things, but was thwarted by lack of space.

\subsection*{Chamber Report}

The Skinner went and scribbled a lot. We can has signed membership cards!

Oh, and the fall mailing went out on time. The world is coming to a rapid end, as the very foundations of our procrastinating lifestyle crumble under us. 

\subsection*{Pseudo-Onseck}

The pseudo onseck is getting creative with these minutes and nobody knows about it. Well, they do now. But they can't stop me! MWAHAHA!

\subsection*{LHE report}

``We are mailing the LHE to the Barbados?''

According to JFC there was once a plan to mail books to ourselves and save space that way. The LHE will get stuff done RSN-er, Monday.

Finboard has institutional memory worse than that of the goldfish on speed. They didn't give us enough money, as always.

\subsection*{Rearranging Deck Chairs On the Titanic}

A bunch of stuff to go in SR got unboxed by ARM . We now have a cabinet! Full of shelves! (but it is sadly taken by the to be shelves pile. Boo! Shelve things, minio-er, prentii, prentii. Prentii should shelve things).

\subsection*{Theftcomm}

Keyholders are holding hours. The TIF is advancing father than 2 hours per week. Maybe it is on stereoids. Maybe people like hours a lot. And the people who were lagging are catching up! Dramatic music! Special effects! Kendra! Er, no, wait, Kendra is on the TIF.

The TIF is the JFC Job dissatisfaction index. The less he likes his job, the more he likes us. JFC and ALC are locked in a perpetual battle of renweing the TIF whenever JFC gets to the top. The end is uncertain. Dramatic music still plays over the library.

This Sunday people stop getting full credit for unscheduled hours.

\subsection*{Mortcomm}

Madeleine L'engle is dead.

\goto{Old Business}

Back in 1967 someone patented software playlists. Or tried to. Now they are suing everyone. They'll preobably settle because it is too much battle to fight the system. Back in the day, someone sued Random Laundry, but we fought the law and we won. Or had piror art or something.

ALGOL
\goto{New Business}
21W.759 books are on reserve. Don't take them out of MITSFS. Also, read them, if you are in the class.

On October 5th there will be a reading of Radio Freefall at the meeting. It is a new novel. The author wanted to come and read for us. The Skinner says that it is not-sucktastic (it is coming from TOR), though given his hatred of Fragile Things his taste is suspect.But apparently, this is a legit book and not just Joe Selfpublished, so it could be fun! The author works for a biotech company.

Join MITSFS-soc! It is your friend! It is made of candy! I mean, erm, happy. Not candy. The Pseudo-onseck should stop making stuff up.

The PM of Japan resigned and then was hospitalized. The Pseudo-Onseck didn't make that up. 

Old people talk about the Japanese Real Estate Market. It turns out that negative interest rates are bad fgor the economy. Go figure. People continue talking about history.

The Skinner escapes into...
\goto{Future Business}

In the future, we will eat. [Newcomer: ``I hope so...''. The tradition is explained.]

In the future term will continue sucking our souls.

In the future Arkham Horror is getting reprinted. It is based on Lovecraft.

In the future the Skinner will continue playing Lurking Horror, which is set at MIT and is very old. So are people here, because they are discussing the history of SIPB many years ago. 

In the future, the sun will turn into a giant red giant and swallow the earth. What are we going to do about it? According to JFC, it may also spit us out after it swallows, and there has been an astronimical discovery of a planet ~1au from its sun, which is currently a dwarf. It is likely that Earth will be swallowed and it plausible that it will be spit out again. 

Motion to take the excess material out of the sun and take it out and make it go really fast and .... Motion fails for length and lack of a second. 

Motion to realize that the Sun will is a giant banana and that earth is part of the Galactic Banana Split. The Gas giants are the icecream.

``Where do you think the sun got its color?''

Motion Passes 3-5-7 + Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

``You count as well as Jade did!''

Timewarp: We may be getting a new calendar, which will hopefullyget here faster that Starship I. 
\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kate Kuznetsova, LHE and Pseudo-Onseck}

\end{document}
