\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 7, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.


Minutes read.

Motion to approve the minutes as re[a]d:  4-3-3+Spehn\\
Motion to approve the minutes as blue: 16-3-5+Spehn\\
Motion to censure the Onseck for being color blind: 15-6-6+Spehn\\

Determinant is 6 and all motions pass.

\BING

\goto{Committee Reports}

\subsection*{LHE}

Our spies report that a safe got stolen from the ASA office upstairs.  So if you were sad that the LHE didn't reimburse you\ldots{} you wouldn't have been reimbursed anyway.

\subsection*{Theftcomm}

Theftcomm Reminds You (keyholders) to send mail if you're going to be gone over Winter break.

\subsection*{Bluebellcom \& Pianocomm}

Jacky came in and covered some books - she is now trained.

\subsection*{Onseck}

The box of stationery supplies came in.

\subsection*{Star Chamber}

The time warp begins on the 21st.

%\subsection*{Alohalenscomm}

%\subsection*{Katiecomm}

%\subsection*{PianoComm}

%\subsection*{Chamber Report}

%\subsection*{Pseudo-Onseck}

%\subsection*{LHE report}

%\subsection*{Rearranging Deck Chairs On the Titanic}

%\subsection*{Theftcomm}

%subsection*{Mortcomm}

\goto{The Forever Business}

Haldeman is coming to MITSFS to give a reading on December 14. He will be reading from \underline{The Accidental Time Machine}! You all should come.  Bring your friends and enemies!

\goto{Old Business}

According to Diane, Andrew Plotkin came and talked about many things, not including text adventures.  Alas.

Term is almost over!

A Miller Motion fails by Skinnerial Decree.

The correct motion here was:

ALGOL.

\goto{New Business}

Kevin took the first and second parts of his SF text adventure and \emph{smashed them together}, resulting in massive amounts of energy and a devastating explosion.

Discussion of 21W.759 stories ensues.

Kate would be a very good Viking.  ``BeoKate!''

None of the keyholders would be eaten by a grue. KCR and CJT would save us all with their flashlights.

Diane wants to be a CMS undergrad.

KCR's hatred of the Tech exceeds Kate's hatred thereof.  Ack, a Tech!

Charles Stross!

Secretly, Kate is very serene.

KCR has a stupid idea.

\goto{Future Business}

In the future, MIT will be exactly like Harvard if the administration gets its way.

KCR suddenly knows a lot more people from Maine than he used to.

The second Miller Motion of the meeting passes "a dozen"-6-2+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
