\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 2, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to condemn the minutes for not noting specifically that I wasn't there passes 9-1-6+Spehn.

Motion to ask the Onseck to note that he wasn't there today either fails due to lack of a second.

\goto{Committee Reports}

\subsection*{Pseudo-Analogcomm}
Grr!  You didn't schedule your hours!  We have a partial schedule.  If it isn't up by ALC's hours on Sunday, he'll put it up himself.

KR may be able to get out of the lab by taking Concert Choir - this scores Influence Points with the music department.

Motion to prohibit the Skinner for writing any songs about his vast and improbably strong hatred of \emph{Fragile Things} passes 20-6-2+Spehn.

\subsection*{AlohaLenscomm}
There may or may not be more pictures than last time.  He can't remember when he put them up.  KLB and SIR's pictures may have changed.

Motion to end the meetings with song passes 22-13-2+Spehn.

\subsection*{Vox Sciurorum}
Today, JFC gave a walnut to a squirrel, then watched it run into the neighbor's car and return without a walnut. 

\subsection*{Kvetchcomm}
There's a new novel awaiting review, entitled \emph{Celestial Pursuits in the Hub of the Universe}, which is apparently Boston.  Kvetchcomm would like to encourage somebody braver than he to read this book.  It's ``almost certainly'' better than Stealth Planet. KR: ``This doesn't mean anything.'' JSB: ``You didn't read Stealth Planet.''

\subsection*{Cluecomm}
The keyholder notes have been read by 7.5 keyholders!  The other 17.5 keyholders are encouraged to read them.

\subsection*{Hasslecomm}
The Purge continues apace.  We are on the C/P pass, and we have purged Robert Jordan (ALC: ``Nooo!'').  The C/P purge is the largest.

\subsection*{Magventory} 
There's Magazine Inventory tomorrow.  Prentices are encouraged to join if they want.

\subsection*{Pianocomm}
Everybody's still a keyholder who was last week.  Pardon KR for having things to do besides run the Society.  He's aware of everything that needs to happen. 

\subsection*{Onseck}
The Onseck will be making a trip to University Stationery Very Soon.  You should email the Onseck with any requests. 

KKB: ``We liberated a bunch of bookends from the CPs last night.''\\
JSB: ``Wait, you mean Circulating Paperbacks or Campus Police?''

Motion to commend KKB and MKR for defragmenting the bookshelves passes 44-0-2+Spehn.

\subsection*{Pseudo-Trojan}
Kat and @people finished processing the Sherwood donation.

%\subsection*{}

%\subsection*{}

\goto{Old Business}

Moving along.  What happened last week?

There was game.  It ended.  ALC:  ``It's always great when you have massacres as part of your political process.''  ESK got executed!

StarCraft is happening soon.  It doesn't count as roleplaying, but it counts as game.

ALGOL.

\goto{New Business}

Good bing!

Vericon was fun.  There was a LARP.  It wasn't like Guild - it was more like an excuse to hit people with boffers.  There was a lecture by Kay, which we kind of slept through.  It was about how he writes fantasy instead of historical fiction for many reasons you can probably figure out by yourself.

A Dramatic Reading from \emph{The Sherwood Game} ensues.  ESK:  ``Can someone please shoot me?''

Miller and multiple matrix motions fail by Skinnerial decree.

There was an anti-war protest in Virtual Reality (Second Life).  They got so many avatars in one place, the region crashed.

\goto{Future Business}

``Skinner still hates Fragile Things, Fragile Things, Fragile Things...''

\bing
Meeting adjourned, 1830 SST.

Boskone is happening in the Convention Center.  It's a very ``booky'' convention.

Next Saturday:  British SF marathon at Random Hall.  '70s Dr. Who, The Prisoner, etc.  ``We don't have to watch all of it.''  


\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
