\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 15, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christian Ternus, Onseck and Interim Skinner, presiding; Kendra Beckler, Interim Onseck, recording.  

``Wait- I'm not the Interim Onseck!  You're the Onseck!''

Minutes read.

Motion to commend the minutes for not containing any grapefruits: 6-0-0+Spehn

\goto{Committee Reports}

\subsection*{Bluebellcomm}

There were books covered.  The Bluebellcomm shelf is being eaten by the Panthercomm shelf.

\subsection*{Mobcomm}

We have discovered tons of Charmed media spin-offs.  

The percentage of actually good quality books being ordered is decreasing as Mobcomm discovers more and more media spin-off series.

Digression about how many books there are in various series.

We have over 600 Star Trek books and over 500 Dr. Who books!  Oh no!

\subsection*{Aloha Lenscomm}

Some people who have spent years being unglossy are now glossy.

\subsection*{MagDex}

Thank you to everyone who showed up to last weekend's MagDex party.  MagDex keyholders and non-MagDex keyholders and prentices showed up.

We got through about 1/3 of processing F&SF into the circulating room.

Also, KLB was added to MagDex.

\subsection*{Hasslecomm}

Hasslecomm has done some work and has started working through the backlog.

\subsection*{War Council}

The ASA is doing rerooming in the fall.  Begin the bribery, threats, and blackmail!

\subsection*{Kesselruncomm}

The Millenium Falcon model is finally hanging from the ceiling again!

\goto{Old Business}

MKR is back from home.  PP has a hat which says she can operate a crane.

ALGOL

\goto{New Business}

Motion to appprove last week for having the usual debate: 3-0-6+Spehn

Vox Squirrorum digression.

\goto{Future Business}

Motion to condemn the future for containing bananas: 6-0-5+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
