\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 9, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Ekaterina Kuznetsova, LHE and Pseudo-Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend last week's minutes on giving us a precise and accurate report of how much the Skinner hates \emph{Fragile Things} passes by threat of photography.

\goto{Committee Reports}

\subsection*{Onseck}

It's like Christmas, except instead of Santa, it's the Onseck, and instead of presents, there are office supplies.  Everyone who asked for something either got what they wanted or have what they wanted on back order.  If you want something else from University Stationery, contact the Onseck {(\texttt{onseck@mit.edu}}) \emph{this weekend}.

Motion to have the Onseck acquire stockings full of coal for all those keyholders who are negative on the TIF passes. 16-0-6+Spehn.

This is not Soviet Russia.

\subsection*{Magventory}

We looked at magazines.

Magventory happened.  We have $\frac{2}{3}$ of the magazines written down on paper.  JFC: ``Soon they'll be on punch cards!''  We have just a little bit left, and we'll be done.

We have begun data entry.  It is slow.  Anyone who missed Magventory has been emailed for their assignment for makeup.  Anyone who would like to volunteer for Magventory can have their souls indexed.

Motion to reward BTS and KAT for braving the boxes and boxes of crazy foreign-language magazines by appointing them ambassadors to the Axis Powers passes 33-0-2+Spehn.  

JFC: ``Are my ears bleeding yet?''

\subsection*{Pseudo-Hasslecomm}

We're up to Moorcock in C/P.  There's a split.

\subsection*{Star Chamber}

We got mail, including a book that the Onseck doesn't care about.

Motion to commend Bluebellcomm for the Bluebellcomm shelf still being empty passes 11-2-6+Spehn.

\subsection*{Pseudo-Pianocomm}

We have a new prentice, Carrie Keach!

Motion to commend Carrie for doing work already passes 16-0-0+Spehn.

Matrix Motion:

\noindent
Motion to condemn Sukrit for getting confused about Pseudos: 16-7-11+Spehn.\\
Motion to make Sukrit a pseudo-Sukrit: 25-1-4+Spehn\\
Motion to end all motions: 15-6-12\\

\begin{tabular}{|c|c|c|}
\hline
16 & 7 & 12\\
\hline
25 & 1 & 5\\
\hline
15 & 6 & 13\\
\hline
\end{tabular}

Determinant is -402 and all motions fail.

JFC: ``Hey, you woke up my screen saver!''

Motion to commend the bing for having telepathy with the computer fails for lack of a second.

\goto{Old Business}

The December issue of Locus has an extended obituary for Jack Williamson, who died in November after having written sci-fi for over sixty years.

We had another person come in to look at the fanzines.  We also had someone come in and look at the magazines today.  Cool! 

ALGOL.

\goto{New Business}

Usual complaint about the bing in my ears.

Motion to have Kate bing again fails 7-14-3+Spehn.  That was an OK baby bing.

Motion to have Kate bring us cookies fails by Skinnerial decree.

Oh yeah, cookies!

ESK is teaching a 6.001 recitation.  ``They don't like the apocalypse, they want cookies.''

Relevant things!

Motion to return Amy to alien life forms passes 14-3-0+Spehn.

All motions fail for lack of seconds.

\goto{Future Business}

In the future, the phone will fall off unless you... never mind.

Motion to motion the something something about the phone fails by \emph{explosion.}

ESK: ``You can't blame me, I have the gavel.''
JFC: ``We can blame you, we just have to do it from more than six feet away.''

Now that Magventory has mostly happened, Magdex will resume entering donations into the Library.

If you're mean to the books, ESK will hit you with the gavel.

In the future, Pandemonium may close.  They're in trouble with the IRS and may fold.

Motion to send Pandemonium a support banana chickens 5-1-10+Spehn.

``Pseudo-Skinner also hates Fragile Things, Fragile Things, Fragile Things, Pseudo-Skinner hates Fragile Things, just like Skinner does.''

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
