\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 22, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kendra Beckler, Pseudo-Skinner and Vice, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the reading of the minutes as being exceptionally easy to understand fails for lack of a second.

Motion to condemn the previous minutes for not containing Fragile Things at all passes 10-2-3+Spehn

Finger Motion passes by Pseudo-Skinnerial decree.

Albanian Motion passes 10-9-3+Spehn. 

\goto{Committee Reports}

And by Old Business, you mean Committee Reports.

\subsection*{Magdex}

There will be a Magdex party at 2PM tomorrow.

Motion to grant Kendra a ring of levitation passes 16-2-3+Spehn

\subsection*{Hasslecomm}

We did another box of backlog.

\subsection*{Pseudo-Skinner}

The lock didn't like SCP, but it does now.

Motion to commend the lock for liking keyholders again passes 12-2-3+Spehn

\subsection*{Pseudo-Kvetchcomm}

A lot of reviews went up this past week.

%\subsection*{Onseck}

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}

CAK went to Fiddle Camp.

In the past, the weather was good.

Malcolm brought in an old copy of MAD Magazine that parodies the original Battlestar Galactica.

Motion to commend Kendra and Kristin for maintaining the midnight vigil and preventing the Library from being flooded passes 12-2-4+Spehn

Kristin has spawned a clutch of Mountain-Dew shaped Alien Babies.

\goto{New Business}

We had the usual debate again!

Move to commend Kristin's new antennae for being squiggly passes 22-0-1+Spehn.

MKR finished the Atrocity Archives!  CAK has not yet read it!

CJT ascended.

\goto{Future Business}

Motion to commend the Skinner for being on Zephyr 'just passes by Everyone's decree'.

Miller Motion fails 2-0-4+Spehn.

Motion to commend Ternus for doing the Mexican Hat Dance passes by Pseudo Skinnerial Decree.

Miller Motion passes 12-2-6+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
