\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.
Minutes read.

Motion to approve the minutes as having (at one time) been read passes 10-5-3+Spehn.

PP:  ``Your laptop may be an extension of your body, but it is not a limb!''

\BING

\goto{Committee Reports}

\subsection*{LHE}

If you've submitted reimbursement forms recently, well, they've been turned into SAFO.  Yaaay.

When submitting reimbursement reports, paper-clipping them is acceptable.  Stapling them is marginally acceptable.  Gluing them together is not.

\subsection*{Theftcomm}

Look, shiny new TIF.

\subsection*{Star Chamber}

KR went to the ASA General Body meeting.  We may not get our money back, but we may get a splufty new card reader.

\textbf{The Winter Break Time Warp begins a week from today.  Time during the time warp does not count towards fines.}  

\subsection*{Onseck}

CJT and CAK brought over the last two boxes of books. 

\subsection*{Hasslecomm}

JSB began the Incremental Purge, also known as The Forever Purge.

\subsection*{Explosionscomm}

Kate is going to be doing a Book Talk on Gardens of the Moon.

\subsection*{Not-Yet-Mortcomm}

Terry Pratchett was diagnosed with early-onset Alzheimers.

I'm not sure that Objectivism is in the book of mental disorders.

\subsection*{Libcomm | Rearranging Deck Chairs On The Titanic}

Much of the Reserve Section got moved around.

KCR shelved the remainder of the Circulating To-Be-Shelved books.

Motion to award Karl the Order of the Yellow-Colored Fruit, First Class passes 10-2-6+Spehn.

\subsection*{Skinner}

The Skinner feels like he did something, but he can't remember what.

\subsection*{Pianocomm}

Paige is done with 170, so she will be unhosed now.

I hear that 170 is done with 170.

\goto{Old Business}

Things happened last week.

ALGOL.

\goto{New Business}

Without the usual content.

So, I hear there's this guy.  He wrote a book, or something.  Teaches a class or two.

All-around awesome guy - \emph{Professor Joe Haldeman!}

Haldeman:  ``Well, I do have [The Accidental Time Machine] memorized, but if you guys have a copy...''

\emph{Professor Haldeman reads from The Accidental Time Machine, to much acclaim.}

KCR:  ``Children of the 80s!  This \ldots{} is \ldots{} a \ldots{} Magtape!''

KCR picked up a \$20 infrared webcam.

\goto{Future Business}

I hear there are finals soon!  Then, people will be going home.

\textbf{Inventory will be happening on January 12th.  Warehouse cleanout will be on January 16th.}

In the future, there will be network again in W20.

Motion to send a banana into the future to determine MIT's fate passes 19-2-3+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
