\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Motion to feed the Onseck fried bananas fails for lack of a second.

Motion to commend the Onseck for the many references to bananas in the minutes fails for lack of a second.

Motion to commend the minutes as being tired passes 4-2-3+Spehn.

Minutes read.

\BING

\goto{Committee Reports}

\subsection{Pseudo-LHE}

Kate made some necessary changes to our account setup, so people will be getting reimbursed.

\subsection{Approximately Libcomm}

A representative from the MIT Libraries showed up during Jake's hours yesterday.

Most of the clever ideas are Hard, and we need to start taking Steps.  Unfortunately, we don't keep enough metadata in our Dex to make certain cool things possible.

If you want science fiction biography or criticism, you should hit up the MIT Libraries.  They make a point of collecting that stuff.

\subsection{Star Chamber}

The Winter Break timewarp begins \emph{today}.

\goto{Old Business}

\textbf{Inventory: January 12}

\textbf{Warehouse Cleanout: January 16}

Harvard still does the thing where finals are after the break.  Haha, sucks to be them.  Eit.

ALGOL.

\goto{New Business}

Enh.  Anything new happen?

KR still hasn't heard back from Stross.  He's going to poke him this week (KR poking Stross, that is) now that he has free time.

We had some money stolen.  This isn't new business.

``Kevin, don't move your feet for a second.'' ``What is it?'' ``It's a scorpion!  A giant, poisonous scorpion!'' ``No, it's an eraser.'' ``That's not poisonous.''  ``It's\ldots{} an eraser.''

\goto{Future Business}

We have a non-hypothetical calendar!  Awesome!

Neither mathematicians nor keyholders can do mental math.

CJT is irritated.  The Stephenson book that he thought MITSFS didn't have was already in the library under a pseudonym.

Eh, fsck off.  It's not lint, it's a moth.  A little moth!  Kill it!

Motion to hire a banana to ghostwrite interesting epsiodes of television series passes 6-2-3+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
