\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 16, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Andrew tries to be clever and then realized that he wasn't.

\goto{Committee Reports}

\subsection*{Star Chamber}

We moved stuff around.  The donations which were Panthercomm overflow moved to
the back of the library.  

In essence, the library was defragmented.

\subsection*{Hasslecomm}

The purge of the hardcovers has started.

No, we won't bribe the janitor to trip over the power cord keeping the Jordan books in suspended animation.

\subsection*{Pianocomm}

Prentices are doing things!  All the prentices are allocated to various projects.

\subsection*{War Council}

SIR is now on War Council.  War Council will have an offline report.

\subsection*{LHE}

There would have been more reimbursements, but the snow likes your money and is keeping it until Monday.

\subsection*{Cluecomm}

Cluecomm has resigned.

\subsection*{Onseck}

The larger orange stickers suck, don't use them.

\subsection*{Pseudo-MITSFS-root}

Much like a dysfunctional phoenix, the new-Psi-Phi has caught fire without being reborn.  It has
been replaced with old-Psi-Phi.

\goto{Old Business}

Back in the day, it was warm.  What happened to that?

Begone, ALC!  You have no power here!

This week felt like an eternal Thursday, and I've never gotten the hang of Thursdays.

In a week, it will be Spring Break, but that is Future Business.

\goto{New Business}

In the past, PP ate lunch, but that was old business.

\goto{Future Business}

If you don't see Kevin over spring break, it's because he's in bed.

Carrie has been up for 31 hours.

In the future, it will stop snowing.  This future is not now.

A banana motion fails due to lack of seconds.

In the future, there will be St. Patrick's Day.

Motion to acquire for the Society banana splits at Deli Haus passes 18-3-5+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
