\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 20, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christian Ternus, Onseck and pseudo-Skinner, presiding; Andrew Clough, Thunderbunny and pseudo-Onseck, recording.

Minutes read.

Motion:  The minutes were read               11 - 1 - 5

         Have the minutes become well rested 10 - 3 - 6

         Have a matrix motion                3  - 5 - 2

                     Determinent is -61 and all motions fail. 

\goto{Committee Reports}

\subsection*{Aloha Lenscomm}

Carry's skin is too high albedo for the camera to lock onto properly.

\subsection*{Hasslecomm}

Thanks to the work of WDS and my two lovely assistants we've been able to put lots of boxes safely above flood level.

\subsection*{Kvetchcomm}

Books continue to be reviewed, and now MKR is also reviewing a lot of books.  You could help too.

%\subsection*{Onseck}

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

\subsection*{Star Chamber}

We got more boxes of books.  Including a Piers Anthony self-published book.  

Motion:  We shouldn't be wasting our money on Piers Anthony books, but should spend it on more worthwhile series.  Passes 14-8-1+Sphen

Talk drifts to authors we don't like.  JSB brings up the time Asimov encourages people to steal our books and so we revoked his lifetime membership.

Motion:  The Skinner must hold a seance for the purpose of telling off Isaac Asimov.  Pass

MKR isn't here.

Motion:  Commend MKR for doing lots of stuff and reducing our motivation.  Passes 15-5-1+Spehn

%\subsection*{Vox Sciurorum (Mumbling about Rats)}

\goto{Old Business}

We have a new Hammer's Slammers.

Discussion goes through autobiography, writing our own biographies, Calvin and Hobbes, and flamethrowers.

Motion:  Condemn anyone who drops a flamethrower off a building without a ground crew.  12-8-1+Spehn

Motion: Condemn anyone who drops a flamethrower off a building with a ground crew.  7-4-1+Spehn

Motion:  Don't fuck with anyone who has a flame thrower.  31-0-1+Spehn

Determinant is 16 and all motions pass.

Miller Motion: Fails  6-12-4+Spehn

ALGOL

CJT:  I have squashed the usual debate.

\goto{New Business}

Motion:  Unusual Meta-Debate  Succeeds 13-6-3+Spehn.

CJT:  If you like Charles Stross you're welcome to apply for the upcoming Guild game.

JSB:  Regails us with stories of Guild camp and this horrible game he wrote about the partition of Germany.  ``Once you've got a bad idea you have to ride it out properly.''

\goto{Future Business}

JSB is going to have to review Unshaply Things.  ``Let me read the back cover''

Albanian motion on JSB chickens 13-8-13+Spehn.

Soon there will be Potterdammerung.

Motion:  Twenty years ago today Apollo 11 failed to carry a banana to the moon.  Passes by Skinerial Decree.

\bing
\noindent
Meeting adjourned, 19:-30 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
