\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 06, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to second the minutes passes 17-5-6+Spehn.

Motion to commend the Skinner for the Sonic Death Ray passes 11-8-1+Spehn.

\goto{Old Business}

And by Old Business, you mean Committee Reports.

\goto{Committee Reports}

Yeah, that one. 

Motion to commend the Skinner on finding excuses for extra bings passes 22-6-1+Spehn.

Motion to censure Kate for not having appreciation of bings passes 12-2-3+Spehn.

Motion to censure those who cannot tolerate bings as inferior \emph{Fragile Things} passes 16-2-3+Spehn.

Motion to Albanian Jake Beal passes 26-0-0+Spehn.

Welcome to Albania, Jake.

\subsection*{Picniccomm}

The Picnic is tentatively scheduled for Saturday, May 12.

Suggestions for people to invite should be directed to {\texttt picniccomm}.

\subsection*{Pseudo-Magdex}

Albanian Jake:  There is a naked man on the cover of this magazine!

\subsection*{Magdex}

Prentices have continued to be awesome!

Albanian Jake: I commend you!

\subsection*{Hasslecomm}

We got through McCaffrey.

We Need More Space.

The Purge Boxes will be making an exodus to Darkest Waltham.

Albanian Jake:  Bribe Foley.

Hasslecomm measures its productivity in flux.

\subsection*{Bluebellcomm}

More books got covered.  MKR was actually Able To Shelve Them!

Albanian Jake:  Books are overflowing!

SIR doesn't know Albanian.

\subsection*{LHE}

Finboard is stupid.  They're limited to one significant figure.

Albanian Jake: The Albanian revolution will crush all in its path!

Motion to commend the Skinner for his excellent grasp of Albanian. 

\goto{Old Business}

People should still read the Erikson books!

Blindsight got nominated for a Hugo, as did Pan's Labyrinth.

Discussion of comic book movies ensues.

The Lies of Locke Lamora is really good.

Vacation finished; we're all hosed again.

SAFO is clever and knows about sig figs.

\goto{New Business}

Yeah yeah yeah, we heard it all already.

The Vorkosigan books are good.  Alice is not Miles.

KKB: ``Miles is the really short guy, right?  ... I still have to read those.''

An Albanian Back Cover Reading of ``Brak the Barbarian versus the Sorceress''  partially ensues.

The Onseck has been spending a lot of time in the Library recently.

\goto{Future Business}

In the future, the LHE has gone to DC.  She has programmed in a special language no-one had ever heard of.

In the future, the LHE's 6.170 team has been named the Black Legion.  They had found a way to avoid Demonic Possession.

Java, APL, ADA, and Dho-Nha geometry curves were discussed.

Motion (in Albanian) that all Englishmen are bananas passes 20-5-2+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
