\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 6, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christian Ternus, Onseck and Interim Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to change the finger motion in last week's minutes to a meta-finger motion: 7-8-2 + Spehn

Motion to condemn the pseudo-Skinner for not using his great pseudo-Skinnerial powers fails by pseudo-Skinnerial decree, to much laughter.

\goto{Committee Reports}

\subsection*{Faminecomm}

People are hungry.

\subsection*{Star Chamber}

We got the new Bujold book donated by SCP and processed, along with many other new donated books.

KKB cleared off half of the Star Chamber shelf.

\subsection*{Bluebellcomm, Panthercomm, and Hasslecomm}

The library digested books.  A *lot* was done.

\subsection*{MagDex}

MagDex party this weekend!  Come!  It will be at 1 PM on Saturday.

\subsection*{Jourcomm}

CAK is now Jourcomm!

Motion to commiserate with CAK: 17-0-2 + Spehn

\subsection*{Onseck}

All hear!  The Undu adhesive remover is in the Onseck drawer, not missing.

\subsection*{Hasslecomm}

We need to move the purge boxes, preferably before term starts.  Email mitsfs@ to say you want to help and what weekends you are free.

\subsection*{pseudo-Surgeon}

Lots of books were repaired, including the second Bartimaeus book.  Yay!

\subsection*{pseudo-Panthercomm}

We found and processed second copies of Gardens of the Moon and of The Jennifer Morgue, as both of them are always checked out.

\subsection*{pseudo-Kvetchcomm}

Another review written by not-Jake!  YOU should write a Kvetchcomm report.

Motion to commend the pseudo-Skinner for admitting his deep and abiding hatred of Fragile Things: 7-4-2 + Spehn

CJT: ``You caught me [in my hatred of Fragile Things].  Oh no.''

\subsection*{pseudo-Onseck}

These minutes are going to be really long.  There are too many committee reports.  Too much library work was done this week!

CJT: ``Not enough library work was done, dammit!''  KKB: ``How much of it did *you* do?''

\subsection*{pseudo-Skinner}

Let the record show that the pseudo-Skinner did ``very important things.''  Which are not fragile.

\goto{Old Business}

The Fourth of July happened.  Yuki is looking for book recommendations.  The library is a din of people shouting various books and authors.

Motion to commend CAK for being the devil: 17-2-2 + Spehn.  Congratulations.

Motion to eat the cute banana fails for lack of a second and people shouting ``Noooo, noooo!''

CJT dances with a broken hard drive.

ALGOL

\goto{New Business}

CJT: ``I beat you this time!''

Motion to throw something at the pseudo-Skinner fails by pseudo-Skinnerial decree.  People ignore this and throw things at the pseudo-Skinner anyway.

KLB has a cool shirt.

Digression about Alice in Wonderland.

CJT's family is in Cambridge, and half an hour ago said they didn't know where they were but were 15 minutes away... they still aren't here...  Hey, they showed up!

\goto{Future Business}

Motion to commend the pseudo-Skinner on his excellend bing: 28-0-1 + Spehn

The next Harry Potter installation will come out 7/21.

Motion to establish a communist state in which all bananas are held in common: 20-8-5 + Spehn

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
