\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to approve the minutes fails 3-10-8+Spehn.

\goto{Committee Reports}

\subsection*{Hasslecomm}

The Great Purge is finished!  Widespread cheers ensue.  Unfortunately, there are still 80 books on the front of shelves.


\subsection*{People's Albanian Embassy}

Albania is spreading!  Apparently there's a Russian meme going around encouraging stupid people to go 'learn Albanian.'

\subsection*{Star Chamber}

We 

\subsection*{Skinner}

JH (jhawk) is no longer a Keyholder.

\subsection*{Magdex}

Magdexing is happening tomorrow.

The Skinner read a book, and it was better than Fragile Things.

Motion to send Kendra into space to build an orbital library: 19-0-4+Spehn

Motion to declare the MIT Science Fiction Society to be on the equator and build a sky-stalk 10-3-7+Spehn

Motion to declare that space is big, and the final frontier, and not the final frontier 6-14-3+Spehn

Determinant is -1290 and all motions fail.

Motion to recalculate the determinants fails 10-13-2+Spehn.

\subsection*{Magventory}

Behatted Kendra reports that Magventory nearly has the Circulating room complete, with about 2 hours of work left.
Discussion of cats and rabid Dobermans ensues.

\goto{Old Business}

Steven Erikson is still good!

People were hosed.  There were all these prefrosh.  Lots of prefrosh had a really good time.

The Library didn't explode.

\goto{New Business}

Entire Library:  ``Usual complaint!''

People are still hosed!  All the sophomores are old now (they have Brass Rats!).

KR:  ``Back in my day *waves gavel* why's my damn cane so heavy!''

There's a Guild game this weekend!

Harvard's prefrosh weekend is this weekend!

Motion to allow Kendra to review the really shiny book passes by Skinnerial decree.

\goto{Future Business}

Testing whether people with big ears are more in pain from the bing is a Great Idea.

``Skinner has no banana at all NO NO FRAGILE THINGS WAIT WHAT''

Motion to give Kendra a banana for reviewing the shiny book passes 12-10-2+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
