\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/28/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, Deccember 28, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, ``it's still 2007'' 1700 SST,
Andrew Clough, Thunderbunny and Psuedo-Skinner, presiding;
John Carr, Vox Sciurorum and Pseudo-Onseck, recording.

Present:\\
Keyholders: \texttt{ALC JFC $|$ DAV}\\
%Prentices: \texttt{}\\


Minutes read.

Motion to approve the reading of the minutes as condensed passes \hbox{1-0-Spehn}.

\bing

\goto{Committee Reports}

\subsection*{Onseck}
The Pseudo-Onseck notes that the meeting minute template includes a
section for Mortcomm.  The Pseudo-Skinner directs the Pseudo-Onseck
not to permit this to adversely influence reality.

\subsection*{Niagaracomm}

KCR took a box of books to feed the hungry sailors in Buzzards Bay.
He wanted a box of Heinlein juveniles but didn't feel like working
to excavate them.

%\subsection*{Alohalenscomm}

%\subsection*{Katiecomm}

%\subsection*{PianoComm}

%\subsection*{Chamber Report}

%\subsection*{Pseudo-Onseck}

%\subsection*{LHE report}

%\subsection*{Rearranging Deck Chairs On the Titanic}

%\subsection*{Theftcomm}

%subsection*{Mortcomm}

\goto{Old Business}

With a rattling of chains, a ghostly spirit emerges from the Gavel.
It is the Ghost of Skinners Past, come to warn the Society of the
True Meaning of Winter Break.  After noticing that there are no
students here it withdraws into the Gavel, confused.

Usual debateless stuff.

\goto{New Business}

The gavel stirs again.  The Ghost of Skinners Present rattles its chains
and emerges.  Looking around it sees its shadow, ensuring six more weeks
of winter.  Confused, it returns to the depths of the gavel, or perhaps
darkest Iowa.

\goto{Future Business}

Once more the Gavel stirs, shaking the block beneath.  It is --- surprise! ---
the Ghost of Skinners Future.  With a chain-rattling groan it emits its
ghastly warning: No matter how low the bid, do not rent nanodisassemblers
to digitize our books.  With this last warning the ghost is consumed from
within leaving a puddle of gray goo that begins to eat away at floor of
the library.  From the puddle the yellow tip of an elongated object emerges.
And another.  And another.  Exponentially the numbers of yellow fruit increase.
The Skinner strikes one with the Gavel and it splits in two.  From each half
sprouts two more, their peels straining at the human flesh just beyond their
grasp.  A torch!  We need a torch!  It is the only way.  Alas, burning torches
are against library rules.  The burning of tobacco, books, and mythical beasts
is strictly prohibited.  We can only hope these minutes propagate faster than
the speed of a wave of total banana conversion to warn future --- or is it
past? --- generations.

A motion to propagate the warning of Total Banana Conversion to past and/or
future generations passes by Pseudo-Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
