\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 28, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Various motions fail for various reasons, mostly relying on ALC's low SNR.

Minutes read.

\BING

\goto{Committee Reports}

That one, sorry.  Ow.

Jade once refused to dance.

\subsection*{Panthercomm}

We got more Star Trek books.

Mobcomm books came in!  Panthercomm will process \emph{new} books, instead of old books.  We can train somebody.  Like one person.

\subsection*{Pianocomm}

If prentices are interested in Bluebellcomm training, such is available.

%\subsection*{Alohalenscomm}

\subsection*{PseudoLHE}

We have a Purchase Order for Planet Self Storage!  Let there be much rejoicing:

The Library:  ``Yaaaaaaaay.''

\subsection*{Trojan}

KKB got trained as Trojan, and even processed a fairly large donation!

%\subsection*{Katiecomm}

%\subsection*{PianoComm}

%\subsection*{Chamber Report}

%\subsection*{Pseudo-Onseck}

%\subsection*{LHE report}

\subsection*{Rearranging Deck Chairs On the Titanic}

\textbf{The day after Columbus Day (Tuesday, Oct 9), there will be a trip to the warehouse to raid books.  Meet at noon at the library.}

\subsection*{Rearranging Boxes of Books on the Titanic}

We have a new chair, generously hauled over here by KCR.

\subsection*{Libcomm}

Libcomm has ideas for things that prentices could be doing, like noting the books that people whose membership has expired still have checked out, so we
can stop trying to get rid of things.

There are two new shelfcodes:

\texttt{VLH}: Very Large Hardcovers, located on the shelves above the Orson Scott Card.
\texttt{C/MM}:  Circulating Mixed Media, which we value very much for its unique contribution to the Library.

If anyone wants to learn Python, they should contact KCR.

\subsection*{Mag.*}

KKB walks into the library, looking extremely sleep-deprived.

\goto{Old Business}

Somebody shelved all the books!  ``I believe that was Sophie's fault.''

JFC shelved a book, but nobody saw him.  If John shelves a book and nobody sees him, has he really shelved it?

Y makes a motion, and is Albanianed.

ALGOL.

KCR:  ``Usual debate!''
KKB:  ``We had the usual debate twice!''

\goto{New Business}

\textbf{Next Week, In W20-473, \emph{In Stereo}, Matthew Jarpe reads Radio Freefall!  During the meeting!  Bring your friends (and enemies!)}

Every zombie movie has to have a clone army with psychokinetic powers.

Marcel Marceau died.  Let's all have a moment of silence.

KKB:  ``There exist brains.  I don't know.  I just eat them.''

KKB is allergic to brains, but only banana-flavored brains.

KCR: ``No molds in the library.''

Quack.

\goto{Future Business}

In the future, 

KCR, CJT: \texttt{*tap*tap*tap*tap* *tap*tap*tap*tap*}

The actor who plays Captain Jack Harkness (on Doctor Who, and Torchwood) got married.  To his boyfriend, to the surprise of nobody who watches the series.

The Sims Movie?  There's a what?  This fact was discovered in a previous meeting.

They're making a movie called The Dark is Rising.  To quote (a source the Onseck can't remember): they only changed 3 things from the book:  They changed the main character's age from 11 to 14, they changed the main character's nationality from English to American, and they changed \emph{absolutely everything that happens in the story.}

The Onseck screams and twitches as he instantly disintegrates this fact from his mind.  Again.

More Neil Gaiman movies will be made.

JFC would like to note that he is no longer the cruftiest person at the meeting.  Hi, Malcolm.

The Ig Nobel lectures will be happening on the Fourth of October.

Chickens.

\ldots{}

Motion to improve the new Dark is Rising movie (Onseck: ``AAGGGHHHHH'') by changing the main character's age to 9 and the main character's nationality to banana passes 16-6-9+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
