\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 26, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Kendra Beckler, pseudo-Onseck, recording.

Minutes read.

Motion to commend the beautiful rendition of CJT's scream passes: 14-0-1+Spehn

\goto{Committee Reports}

\subsection*{Katiecomm}

Non-Katie people did Katiecomm work!  Yay.

\subsection*{PianoComm}

The Skinner was sick and thus missed his hours, so dnawi didn't have an opportunity to get keyed.  Real soon now, we swear.

\subsection*{Jourcomm}

CAK needs to learn 

Motion to create a committee in charge of finding Kat and Brian: 11-0-5+Spehn

Motion to name said committee Avoid-the-Bedroomcomm: 11-5-3+Spehn

Motion to have this motion be something other than a motion for a matrix motion: 9-0-4+Spehn

Determinant is -5, all motions fail.

\subsection*{Libcomm}

[Insert 5 minutes of screaming from the Skinner here.]

Motion to get a pet 10x10x10 storage gelatinous cube fails for lack of a second.

\subsection*{Rearranging Deck Chairs On the Titanic}

More Purged books were discovered in the DA after the other boxes were packed away.  Oops.

\subsection*{MagDex}

MagDex processed 5 boxes out of the library!  Yay for prentices and MagDexers.

\subsection*{Pseudo-Mobcomm}

This month's worth of books has been ordered and will get here in about a week.

\subsection*{Theftcomm}

A new TIF has been posted!

The average keyholder continues to hold more than 2 hours per week.  No keyholders are failing to hold hours without a good reason.  Yay!

\subsection*{Pseudo-Onseck}

The Skinner bought a new red stamp pad and some CD-Rs.  W00t!

\goto{Old Business}

Everybody was hosed this week.

ALGOL

\goto{New Business}

Hm, overdamped gavel.

Discussion of physics.  As in, MIT classes.  Borrrrring.

HRSFA has a meeting this Sunday.  And every other Sunday after that.

\goto{Future Business}

In the future, the Skinner will recover.  Also, he will finish HP7.

Hasslecomming will continue during JSB's hours.

Kat walks in.  Motion to make her part of the committee to find herself and Brian: 24-0-0+Spehn.

Wait, didn't we fail to create the committee?  We added Kat to a committee that doesn't exist!  We have awesome powers that way.

Motion to send bananas to the future to determine when time-travelers defy gravity: 15-0-7+Spehn

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
