\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 4, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kate Kuznetsova, LHE and Psuedo-Skinner, presiding; Andrew Clough, Thunderbunny and PsuedoOnseck, recording.

Minutes read.

Motion:  Condem the onseck for not putting up Kendra's motions fails by Skinerial Decree

ALC:  Thats Psuedo skinerial decree

Motion:  Condem the onseck for not being here fails for lack of a second \bing

\goto{Committee Reports}

Picniccomm:  Elections is on Friday the 11th, picnic is on saturday the 12th

High First Report:  HERSFA invaded, there was much fighting, we have a truce now so we can have a meeting.

Magdex:  We finished magazines in the circulating room.

%\subsection*{}

%\subsection*{}

%\subsection*{}

\goto{Old Business}

Motion:  Condem the psuedo skinner for not haveing a resonant bing passes 20-0-1+Spehn much better \bing

People were hosed from 6.170

Motion:  Condem the psuedo-skinner for confusing herself and the psuedo-Sukrit.  17-5-3+Spehn \bing

\goto{New Business}

Motion:  Kate having power over life and reality is scary!  Motion chickens 7-2-7+Spehn \bing

HERSFA is here.  Some of them have suits and boffers.  And the ancient slinky of peace.

\goto{Future Business}

In the future there will be dinner.  In the future there will be finals.  In the future there will be summer.  In the future there will be elections.

Motion:  Elect a banana for president.  Passes 7-2-5+spehn \bing

\bing
\noindent
Meeting adjourned, 19:-15 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Psuedo-Onseck}

\end{document}
