\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 2, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the Onseck for putting sidenotes into the minutes passes 13-5-1+Spehn

\BING

\goto{Committee Reports}

\subsection*{Vox Sciororum}

One of JFC's pictures was posted to Digg and got 150K+ views.

\subsection*{Pseudo-Mag.*}

Kate's hat was taken and a ransom note was left.

\subsection*{Pianocomm}

Yeah yeah yeah, working on it.  dnawi's initials will be DAV; his last name is a Secret.

\subsection*{Libcomm}

Libcomm was on vacation last week.

The database-backed version of the datadex will be Much Faster than the current iteration.

\subsection*{Katiecomm}

Radio Freefall is off the New Books shelf and is now available!  You should read it, because it's excellent.

%\subsection*{Alohalenscomm}

%\subsection*{Pseudo-Onseck}

%\subsection*{LHE report}

%\subsection*{Rearranging Deck Chairs On the Titanic}

%\subsection*{Theftcomm}

%subsection*{Mortcomm}

\goto{Old Business}

There was a pretty singalong thing on Thursday.

There's a talk by Susan Cooper coming up, but there's a waitlist.  Alas.  It'll be in 32-123.

Stata may not be worthy of a number, as it's nontraditional.

Discussion of diminutive names and nomenclature ensues.

KR emailed Stross!  He'll be in town in February and may come to MITSFS!

ALGOL.

KCR:  ``Usual debate!''

\goto{New Business}

We had the usual debate this time!

Usual head-scratching about ALGOL.

We haven't heard anything about the warehouse.

\texttt{jasminef} cares about comics!

We have new people!  We should encourage more people to come to MITSFS.

\goto{Future Business}

Discussion of horrible horrible soul-tearing things that people do to books ensues.  It is extremely painful and will not be related here.  Suffice it to say that it partly involves bacon.

Why don't people make shiny book covers?  Or even books with glued bindings.

It is noted that Katie looks like a Cylon.  Specificially, Number Eight (aka Boomer, aka Grace Park).

In the future, Katie will destroy humanity!  There will be many copies.

Motion to replace all perfect-bound books with books bound in banana peels to improve their durability passes 12-6-1+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
