\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 5, 2007\\
12th Day After Christmas
\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Brian Sniffen, Vice and Pseudo-Skinner, presiding; Kat Sniffen, Onseck, recording.

Minutes from 12/22 are read.

Motion to condemn the 12/29 pseudo-onseck for not getting his minutes
online passes 12-4-5+Spehn.  The 12/29 minutes are also read.

A motion approving those minutes as being brief and to the point
passes 8-1-2+Spehn.

\goto{Committee Reports}

\subsection*{DexMistress}
Jake is boxing books in bags in boxes. They may need dessicant before
being sealed and stored. Or mothballs. Or some other magic powder.

%\subsection*{FrustratedAuthorComm}

\subsection*{JourComm}
A New TZ has arrived. The Pseudo-Skinner points out that they are
printed, or at least some are stored upside down.

\subsection*{Pseudo-Analogcomm}
There is an IAP Schedule!


%\subsection*{Mobcomm}

\subsection*{Star Chamber}
The keyholder notes are undergoing revision. Jamie criticizes the
Skinner's linguistic style criticism and says he's still working.

%\subsection*{Vox Sciororum (Mumbling about Rats)}

\goto{Old Business}
Kristin is here.  

John Greever sent us a story about the founding of the society and the
backroom deals among Phi Kappa Sigma brothers who helped us get
recognition. He is also sending us a donation of books.

A motion to add him to the Society's Christmas List passes 12-0-0.

\bing

\goto{New Business}

We should probably get a slide for the Sci-Fi
Marathon. They will probably not be showing Snakes On A Plane 5 times,
because it's really expensive.

There is a really cool video on YouTube with Snoopy fighting the Red
Baron.  They actually built the barn and flew it. (Small-scale)  It
is a U2 video, though apparently they have a neat video for several of
their new songs.

Hicks in Florida have been being abducted by aliens and have had their
city cousins made them a blog.  It appears to be an advertisement for
a movie about said Floridians.

Discussion about bad movies ensues.

``David Bowie made good movies. At least in Labyrinth he entertained
half the audience by wearing leather pants.'' - BTS\\ 
``Ooh! I need to go watch Laybrinth again!'' -Andi

\goto{Future Business}
In the future we may know where the books are going.

Arisia is this coming weekend! They may overflow, because they have a
really small hotel. Check online and prepare to be potentially turned
away. (They lost the Park Plaza because some mundanes got freaked by
the FFF, and the hotel management decided Arisia was too similar to
risk.)

``Sounds like they need pants.''\\
``They could borrow them from David Bowie''\\

A motion to flay and tan enough banana skins to make leather pants for
everyone in the Society passes 11-4-2+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Katherine Sniffen, Onseck}

\end{document}
