\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 18, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to approve the reading of the minutes as containing matters which should not be known to mortal man passes 11-0-1+Spehn.

\goto{Committee Reports}

\subsection*{Pianocomm}

Carrie A. Keach (CAK) has been keyed!  Yay!

Also, the prentices should get their posteriors into gear. 

\subsection*{Picniccomm}

There was a picnic, it was good!  ALC won the gavel toss\ldots{} all three times.  We had great weather!

\subsection*{Skinner}

The glorious new magazine rack has been replaced by The Skinner's Rack. 

\subsection*{Magventory}

Magventory is finished!  Yaaaaay!

\subsection*{Magdex}

CAK is now on Magdex!

\subsection*{TowerDefenseComm}

Kate is losing, but she's on the forty-third level.  Don't Panic!

\goto{Old Business}

Classes are over!  Classes are now old business.

We sent more books somewhere, probably to fans in Israel.

Jamie took abstraction way too far.

ALGOL.

\goto{New Business}

Usual yawn.

KR finished Timelike Diplomacy.

We have the Emperor's New Recycling Bin.  Also, the Emperor's New Bookcase Wall Anchoring.

Eventually, we will have more space!

KKB has pinwheels on her head.

It's really raining.

\goto{Future Business}

In the future, there will be a giant banana over Texas.

Motion that the Society be the first to suggest that the giant banana dirigble be split passes 18-2-3+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
