\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 26, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to censure the LHE for having the books shipshape passes 10-2-3+Spehn.

Motion to censure the minutes on general principles fails on general principles.

\goto{Committee Reports}

\subsection*{Jourcomm}
TZ \#48 is now accepting submissions!

According to another fanzine writer, TZ \#47's artwork ``looks like it was drawn by engineers'', but our minutes are as loony as ever.

We already have submissions for TZ \#48, ``yours, and that guy's.''

Reviews will not be a problem, but stories will be.

\subsection*{Star Chamber}

We have some weird mail with no return address.  ``You must admit, though, my work isn't normal, is it?''  Crazy people send us lots of things.

\subsection*{Phonecomm}
KR: ``Go away.''

\subsection*{AlohaLenscomm}
I took pictures!  I printed pictures!  Keyholders who are upset with their pictures should, like, complain or something.

\subsection*{Trojan}

We have a bunch of donations that need processing.  You should come in during Kat's hours (4-8 on Sunday) and help process them, but please don't try to process a specific donation unless you know how.

\subsection*{Cluecomm}

There are new Keyholder Notes.  The Skinner should initial them, at which time he should go around to all the keyholders and say, ``Haha, we changed the rules!''  Keyholders can poke the Skinner in extenuating circumstances.


\subsection*{Pseudo-Vox Sciororum}

Last week, National Squirrel Appreciation Day happened!

\goto{Old Business}

Stuff.  And things! 

The Guild game is still going on, but a large chunk of it has passed.

ALC updated the TIF!

ALGOL.

\goto{New Business}

The usual debate happened already.

Keyholders!  All of them!  You, up against the wall!  You should sign up for spring term hours!  You should also sign up for Magazine inventory hours.

Motion to skill the kinner, er, kill the Skinner fails by Skinnerial threat.

Niki (ahuhn) shows up! ``Hello!''

If we could throw all the magazines out the window, Kat would not cry. 

Large numbers of people talk at once.

Was that a ``Future Business?''

\goto{Future Business}

\emph{That} was Future Business.

We don't have enough manpower for MITSFS to reasonably help HRSFA run Vericon - as a Society, at least.  Vericon's not very ``booky'', though they have interesting authors this year.

People who have fallen off the bottom of the TIF are still keyholders, for now.

We disapprove of ``the eternal Prentice.''  Prentii are good, slaves are bad.

A motion to brainwash MIT students into becoming keyholders fails due to redundancy.  ``We already did that - where do you think the current keyholders came from?''

Motion to condemn the Skinner for all the deeds he doesn't remember committing passes 17-0-0+Spehn.  ``Especially the one with the squash. I know the Skinner doesn't like Fragile Things, but he didn't have to show it \emph{that} way!''

Motion to condemn the Skinner for not yet forgetting his condemnation of Fragile Things passes 19-0-0+Spehn.

KR to CJT: ``Die faster!''

KAT: ``Stop aiming that at me!''  She then flees in terror before the All-Seeing Eye of Aloha Lenscomm.

Motion to replace Kat with a banana so that AlohaLenscomm can have something to take pictures of passes 11-4-4+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

Bonus Post-Meeting Quote:

The phone rings.  Andrew Uhmeyer waves money around.  KR answers the phone, ``Center of the Universe; not my problem!'' 

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
