\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 30, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to condemn the minutes as too short fails for lack of a second.

Motion to commend the Onseck for solving the Mystery of the Missing Minutes passes 18-0-0+Spehn.

\goto{Committee Reports}

\subsection*{Pseudo-Anti-Hasslecomm}

We got a bunch of new books in, including new Haldeman and Glen Cook.

\subsection*{Theftcomm}

We have a new TIF, yaaaay.

\subsection*{Pseudo-Picniccomm}

MKR and ESK are Picniccomm, yay!

\goto{Old Business}

Spring Break is almost over, but we still have a weekend!

Taxes happened.  Several people got \$26 back.

Gonzo is here!

Discussion about how it is or isn't possible to fall asleep ensues.

\goto{New Business}

Usual motion- beat you.

You can't complain if you didn't make the motion!

The Hugo Award nominees were discussed.

ALC related some fascinating new developments in biology that happened recently, though he's not
a biologist.

\goto{Future Business}

In the future, it will get even warmer.

In the future, there will be prefrosh, because it will be CPW!

In the future, the Skinner will be going to California for the summer!

Motion to not go to Royal Bengal because the banana fritters are scary passes 6-2-4+Spehn.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
