\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 23, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion that the minutes were read passes 4-3-5+Spehn.

\BING

\goto{Committee Reports}

\subsection*{Libcomm}

Libcomm regrets to announce that he hasn't written much in the way of code, as he's been very sick.

\subsection*{Bluebellcomm}

Bluebellcomm covered books!  The second book of The Last Chronicles Of Thomas Covenant No Really \&c. and The Merchants' War were both covered.

We don't actually have a category for reserve hardcovers, but this will change soon

\subsection*{Kvetchcomm}

Discussion of Sword of Truth, and the latest book thereof, ensues.

``It's not like you're saying, `can we get back to the Good Stuff?',
because there is no Good Stuff.  It's just different flavors of
Shitty.''

\subsection*{Skinner}

The Skinner hasn't heard back from the guy who wants to donate 2
kilohardcovers to the Library.

\subsection*{Chamber Report}

Haldeman is coming to MITSFS to give a reading on December 14. He will be reading from \underline{The Accidental Time Machine}! You all should come.  Bring your friends and enemies!

\goto{Old Business}

Thanksgiving happened.

ALGOL.

\goto{New Business}

So, what's new?  KCR:  ``Who cares?''

KR doesn't want to drag this out any longer than it has to go.

Discussion of OLPC hardware ensues.  The OLPC project is in fact
making a lot of money.

KR's text adventure game has an expansion out!  The dragon's name
begins with an X, which is a relevant hint.

\goto{Future Business}

In the future, there will be cake.  And then there will be cake!

Motion that the banana-colored cake is a lie passes 4-3-7+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
