\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 9, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST, - OY!  SHUT UP!

Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes for sparing us the description of the horrible things people do to books passes 9-1-7+Spehn.

\BING

\goto{Committee Reports}

%\subsection*{Alohalenscomm}

%\subsection*{Katiecomm}

\subsection*{PianoComm}

Welcome DAV (David Nawi), our newest keyholder! Hip-hip-hooray!

\subsection*{Onseck}

\emph{The Onseck begins to say something, but is interrupted by JFC's catalog of wenchwear.}
\begin{verbatim}
\ldots{}
\end{verbatim}
Anyway\ldots{}
\begin{verbatim}
\ldots{}
\end{verbatim}

\subsection*{Chamber Report}

We no longer have a PO for the sketchy warehouse, because Kate canceled it.  The sketchy place was sketchy!

Does the space have rats?  It damn well better not.

A warehouse in the Boston area was recently found to contain a dead body in a cooler.

Yay, storage for bodies!

Haldeman is coming to MITSFS to give a reading on December 14.  He will be reading from \underline{The Accidental Time Machine}!  You all should come.

\subsection*{Skinner}

There was something that KR was going to talk about this week, but it was probably a figment of his imagination.

\subsection*{AlohaLenscomm}

KCR brought in a baby gavel.  It didn't bing very well, but we should give it time.

\subsection*{Onseck (second try)}

The Onseck filled out several subscription requests, and by several he means three.  If you can think of any more magazines that need to happen, email the Onseck.

\subsection*{Titanic Tetris}

We're going over to the warehouse tomorrow to move the giant mountain of boxes.  If you can help, please come, particularly if you have a car!

\subsection*{42nd Army of the Society | Coofcomm}

HRSFA is having a meeting on Sunday at 7PM.  Bring disc guns.

\subsection*{Pseudo-Libcomm}

KR was talking with KCR about electronic checkout.  He estimates that he is two Normalized Karl Programming Days away from having a working \ldots something, that something being a version of Dexhamster.  It'll still write out a flat file!

MONOLITH.MIT.EDU should have a UPS.  Soon.

%\subsection*{LHE report}

%\subsection*{Rearranging Deck Chairs On the Titanic}

%\subsection*{Theftcomm}

%subsection*{Mortcomm}

\goto{Old Business}

Does everyone here who lives in a dorm live in Random or EC?  No.

Discussion of twinkiedom ensues.  MITSFS is indeed a pillar of twinkiedom.

CJT will submit his story, but TZ may not actually want it.  TZ will publish Real Soon Now.

ALGOL.

\goto{New Business}

We sort of talked about the usual debate, though.

A finger motion fails to materialize.

We have a new Haldeman book: \underline{The Accidental Time Machine}!

Apparently the Beowulf movie is coming out.  jasminef has a Jasmine Discovery Moment when she realizes it's computer-animated.

\goto{Future Business}

In the future, we will have a Thanksgiving holiday!  The Library will presumably be closed.  In Grand CAC Tradition, they haven't told us when (or if) it'll be closed.

Why don't our minutes record everyone who's present?  

In the future, Stata will be fixed/marginally-less-broken.  

Discussion of people being buried in the foundations of buildings makes no sense.

In the future we will get food, but only if someone makes a motion containing a banana passes 7-2-6+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
