\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 16, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the reading of the minutes for being just as atonal as the singing was chickens 7-2-12+Spehn.

\goto{Committee Reports}

I'm not sure why I'm thanking people in German today.

\subsection*{Panthercomm}

ESK got training in Panthercomm, and processed a box of books (PP helped).

Motion to make Sukrit a pseudo-Sukrit chickens 25-14-2+Spehn.

In this Library, there \emph{is} a privileged viewpoint.

\subsection*{Pseudo-ConComm}

Harlan Ellison did something sketchy at LACon.

Apparently Boskone is happening tomorrow at the Weston Waterfront hotel.  Sadly, we're all to hosed to go.

\subsection*{Pseudo-Trojan}

The donation letters got sent out for signatures.

\subsection*{Magdex}

Now that Magventory has happened, Magdex will resume, yay!

\subsection*{LHE}

LHE is still waiting for monthly statements.  Once the monthly statement arrives, the LHE
will put in ink all the stuff from January.

The LHE reimbursed people!  Yay!

Apparently we've been using the boxes as structural support for the bulletin board.

\subsection*{Onseck}

University Stationery still has not gotten back to us with regards to the stationery supplies that were
on back order.  Therefore, if you want more stationery supplies.

Motion to question whether University Stationery hates us more than the Skinner hates \emph{Fragile Things} passes by 96-4-2+Spehn.

Motion to define $4 \times 17$ to be $96$ so the Skinner is never wrong passes 96-4-4+Spehn.

Remember: one limb, one vote! 

\subsection*{Pseudo-Pianocomm}

We have a new prentice: Jacky!  Yaaay.

\subsection*{Hasslecomm}

We purged through Tepper in the paperbacks!

%\subsection*{}

\goto{Old Business}

Matrix Motion!

Motion to commend the Skinner for his awesome: 37-6-8+Spehn\\
Motion to commend the Skinner for his amazing bing: 32-7-8+Spehn\\
Motion to not have a Matrix Vote: 27-8-2+Spehn\\

\begin{tabular}{|ccc|}
37 & 6 & 9 \\
32 & 7 & 9 \\
27 & 8 & 3 \\
\end{tabular}

Determinant is -402 \emph{- same as last meeting -} and all motions fail.

ALGOL.

\goto{New Business}

JM: ``Good whine, Kate!''

This is Wizard Chess.  It has different rules.

Under Massachusetts law, an object must have at least 12 LEDs to qualify as a bomb.  KR: ``Most
of our rooms would count...''

Ken Johnson is in California with the comics!  Old business is dead, just like Asimov.

Apparently Asimov has a brother.

The minutes will note that the Skinner expressed his opinion of Fragile Things at this point, with
the sentence, ``Fragile Things: Worst Book I Ever Read.''

KR is permanently in his sight-singing lab.  However, he's hosed this term.

The Onseck has been elected Random Rush Chair.

Motion to surround MITSFS with the stealthy, mysterious field from \emph{Stealth Planet} during
CPW passes 23-3-4+Spehn.

Knock it off, kids! KR: ``Back in my day *waves gavel*...''

Motion to commend the Skinner for being old and crufty passes 30-4-2+Spehn.

JM: ``We could ride our dinosaurs?  I had to \emph{drag} mine.''

\goto{Future Business}

In the future, there will be more bings!

All right, let's put an end to it.

Miller Motion passes 44-3-2+Spehn.

\section*{Game Halt!}

This also adjourns the meeting.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
