\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 23, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the Onseck for plot-saturated minutes passes 6-0-1+Spehn.

\goto{Committee Reports}

Right, that one, sorry.

\subsection*{Magdex}

Magdex has gotten 20+ hours of work done this week, and is making huge amounts of
progress.  Prentices have been awesome.  Carrie and David have been doing an especially
large amount of work.

\subsection*{Mobcomm}

Mobcomm ordered 95 books today, and will order 100 more boxes later.  Amazon is sometimes slower
than Panthercomm.

\subsection*{LHE}

We have checks now, woo!  The snow gave our money back.

\subsection*{Pseudo-Hasslecomm}

We are now purged through Harrison.  ``The Stainless Steel Rat Goes To Hell'' went to Hell.
Hell is other student groups.

%\subsection*{}

%\subsection*{}

\goto{Old Business}

Quoting TMBG does not end the meeting, unless they have songs about bananas.

Pain happened last week.

ALGOL.

\goto{New Business}

Usual complaint in an alternate universe!

Spring Break is starting, unless you have extensions.

Random discussion ensues.

\goto{Future Business}

Discussion about whether the Onseck should app for a SIK game ensues.

Motion to hope that Ursula Vernon's new book causes less hatred in the Skinner than Fragile Things passes 11-0-3+Spehn.

Now would not be the time to mention that 

In the future, the Wheel of Time will continue spinning. 

A non-motion about Mary's and bananas passes 13-0-12+Spehn.

Motion to declare that the last motion about bananas was not a motion passes 12-0-3+Spehn. 

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
