\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 21, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to condemn the Onseck for making stuff up: 19-1-1+Spehn\\
Godzilla: 20-1-4+Spehn\\
Motion to have a matrix motion to preserve temporal continuity: 1-16-1+Spehn\\

\texttt{ (- (+ (* 19 1 2) (* 1 5 1) (* 2 20 16)) (+ (* 2 1 1) (* 1 20 2) (* 19 5 16)))\\
-879}

All motions fail.

Motion to commend the minutes for not preserving temporal continuity passes 19-2-4+Spehn.

\BING

\goto{Committee Reports}

%\subsection*{Alohalenscomm}

\subsection*{Katiecomm}

Katiecomm did no work, as she was hosed.

Gasps of horror and shock.

\subsection*{Libcomm}

A strange black object has appeared in the center of the library.

It appears to be Uplifting the Dex.

Grace Kane: ``I have become sentient!''

\subsection*{PianoComm}

There are prentices!  The prentices should do work.

\subsection*{Mag.*}

JSB and JFC did a little more Magventory.  We're almost done with the Reserve Room.  There has been a fair amount of data entry going on.

\subsection*{PseudoKvetchcomm}

CJT does a back-cover reading of \emph{Swamp Master}.  Discussion about bad books ensues.

\subsection*{Jourcomm}

I hear people are writing science fiction in a class.
%\subsection*{Chamber Report}

%\subsection*{Pseudo-Onseck}

\subsection*{LHE report}

The PO thing is being dealt with Upstairs.

%\subsection*{Rearranging Deck Chairs On the Titanic}

%\subsection*{Theftcomm}

\subsection*{Mortcomm}

James Oliver Rigney, otherwise known as Robert Jordan, has passed away.

\goto{Non-Temporally Continuous Business}

ALGOL.

What about the usual Old Business?

There is no business in this library.

Matthew Jarpe is reading Radio Freefall during the meeting in two weeks.

The xkcd meetup is on Sunday.

Further business?

Tomorrow is KKB's birthday.

Motion to give Kendra food that isn't a banana passes by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
