\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/10/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 10, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
CLANG!

MITSFS meeting called to order, 61.2 Ksec SST,
Christian Ternus, Interim Skinner and Onseck, presiding;
John F. Carr, Pseudo-Onseck, recording.

Minutes read.

Move to note that Y wasn't even here at the time.  Chickens \hbox{2-0-10+Spehn}.

\goto{Committee Reports}

\subsection*{Katiecomm}
``[Katie] always has committee reports.''
No bluebellcomm.  Panthercomming was done.  The Lesser Purge of hardcovers
has been done, mostly by John (auxiliary Katiecomm?), Katie is still
fiddling with shelves.

\subsection*{Pseudo-hasslecomm}
Jake acquired more Banker's Boxes.

\subsection*{Panthercomm}
MKR: The UA is hoarding our boxes again.  We will have to mount an
expedition.  This explains why the massive influx of books threatened
by Mobcomm has not arrived.

\subsection*{War Council}
Soon we will have taken over the UA office with our books...

\subsection*{Pseudo-pianocomm}
MKR: Somebody shelved the books.  Yay!  Maybe KCR did it.

\subsection*{Pseduo-dexmistress}
KCR is slowly going insane from an overdose of Perl.  The books are
going to get him.  May have already got him.  He's not here.  That
could be why.

Y moves to commend Jamie for being so slow going insane.  After some
dispute of the accuracy and propriety of this motion it dies a silent
death without a vote.

\subsection*{Aloha Lenscomm}
Aloha Lenscomm has been taking pictures.  He may take a new picture
of ALC, who is dissatisfied with the picture of him holding coconuts
that Christian thinks look like ``German meat chunks.''

Blizzard books are still coming to get us.

We should extend the reserve date of the last Harry Potter book for any
foreign students who have been living under a rock.

Y: Move to cleanse and sterilize any foreign student who has been living
under a rock.

\goto{Old Business}

(silence)

Usual motion, etc.

\goto{New Business}

Y: Since last time Y has devoted an unreasonable amount of time studying
the Sci Fi network guide to science fiction television which tells you much
more than it should about episodes of a large assortment of science fiction
and ends with a listing of 50 programs which we'll probably never hear of again
from obscure early science fiction like the old British series Space Patrol
which preceded the American series Space Patrol which only the two oldest
people in the room have heard of.  Warning: the book contains spoilers for
really old shows.  MST3K missed an opportunity by not mocking bad old SF
series like {\it Voyage to the Bottom of the Sea}.

\goto{Future Business}

In the future many people will come back.  Kevin and eKate are both
early returns.  eKate visits this weekend and returns in a week and
a half.

Motion to give Jacky a banana to plug her ears from the sound of
Aloha Lenscomm's capacitor (which has already been turned off).

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
