\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 11, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to condemn the reading of the minutes as being accurate (as far as ALC can tell) passes 16-0-5+Spehn.

Motion to change the MITSFS election structure fails 16-15-4+Spehn.

\goto{Committee Reports}

\subsection*{Mobcomm}

More books were ordered.  More receipts were filed.

\subsection*{Picniccomm}

There is a picnic tomorrow!  You should come.

\subsection*{Skinner}

The Skinner answered email.  The Skinner always answers email.  Spamscreen is like the memory hole.

\subsection*{Pseudo-AlohaLenscomm}

KCR took pictures of Carrie.

\goto{Old Business}

HRSFA attacked us last week.  We successfully fended them off, yay.

Random discussion about many different things ensues.

ARM suggests that MKR should beat up her 'old-lady' teacher and take control of the class.

We should put a Non-Denominational Holiday Shrub on the Great Dome.

ALGOL.

\goto{New Business}

Taunt the next Skinner.

\goto{Elections}

\subsection*{Nominations for Onseck}:

Christian Ternus

The Dread Computer Roberts

Emacs that Hates America

America

Alucard

et al.

Lego Wars

Moon

Eris

the Goddess of Discord

Zombie King

Good Morale

Bad Morale

Smeagol

the Reactor

Bzzebedumebadah

Gavel

Captain Planet

all of the above

Math

Scheme

Maths

Miles Vorkosigan

Cordelia Vorkosigan

Famine, War and Pollution

Fragile Things

Kittens (to make the meeting pointy)


\emph{Kittens win.  Ternus is declared to be equivalent to kittens.}


\subsection*{Nominations for LHE:}

ekate

Kate's hair-dye


the money

UA

the books

the UA's money

space which is big

the Producers

the Chaos Marines

the Eschaton

the rules

Bzzebamadebah

the person who will be elected LHE

the person who will not be elected LHE

George W. Bush

Guild

light

L

gravity

QED

xkcd

raptors

velociraptors in F-22s


\emph{Kate is re-elected LHE.}


\subsection*{Nominations for Vice}:

Miss Katie *

Kendra *

Sukrit *

Mortal Combat between the 3 previous candidates

the Space Pen

Sloth

Greed

Pride

Stupidity

the Impossible

the class of candidaes which blah

set-car!

the space-time continuum

zombie space-crime continuum

Rock of Gibraltar

KBX boxes

Jamie Morris' good twin

Jamie Morris' evil twin

\emph{Kendra is elected Vice.}

\subsection*{Nominations for President}:

Kevinr

Paige

Potted Palnt

Trail Mix

Skinner

George W Bush

Hilary Clinton

Bill Clinton

Al Gore

Other nomination

All possible entities which can be nominated at a MITSFS election

Ender

HP Lovecraft

Boba Fett

Darth Sidious

the Doctor

Good Morale

Good Omens

Bad Omens

Gavel

Reactor

\emph{Winner: Kevinr}

\subsection*{Skinner}
Kevinr appoints himself the Skinner.

\goto{Future Business}

Motion to violate causality fails by Skinnerial decree.
Motion to send the Eschaton an appeasement gift of a banana passes by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
