\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 9, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to condemn the reading of the minutes as being extremely sleep-inducing fails 7-16-8+Spehn.

Motion to condemn Amy for hating the minutes (but not as much as the Skinner hates Fragile Things) and simultaneously condemn the minutes for not having anything to do with pickles passes 35-3-3+Spehn.

\goto{Committee Reports}

\subsection*{Pianocomm}

We have Prentii!  PP is now Pianocomm.  The prentii should do stuff.

\subsection*{Pseudo-Hasslecomm}

The purge of the paperbacks is over!  The purge of the hardcovers begins soon.

We have space, until we get more books.

\subsection*{Onseck}

The new binder got instantiated.  Member sheets that were particularly sad got reinforced.

Motion to reinforce the Elven-Kings' page with three rings passes 23-7-4+Spehn.

\subsection*{Magdex}

We have lots of donations that are clear to be processed and will be processed Real Soon Now.

An Albanian Miller Motion fails because it's too early in the meeting for that.

\subsection*{Bluebellcomm}

I covered more books!  Woo!

Usually we give Bluebellcomm to prentices, but you're being far too efficient at it.

%\subsection*{}

\goto{Old Business}

Did Theftcomm stop sucking?  I... dunno. 

We still have a very big magazine rack.  We want a smaller one.  There's this thing in the catalog that we're going to get.
We'll deal with this offline.

Surely something happened.

The first 6.001 test happened this week.

On Wednesday the Surgeon had the epiphany that she really likes fixing books. 

\goto{New Business}

I'm the usual motion around here!

Are you really Kevin, or are you an alien?

Kevin's pinky is fine.

Moving on.

\goto{Future Business}

In the future, dot dot dot.

You have no idea how much work there is in the afterlife.

Discussion about shirts ensues.

In the future, Neil Gaiman's Stardust will come out.

In the future, we will get less weird email.

Motion to go to Mary's and buy everyone some banana-blossom tea fails due to lack of a second.

Meeting adjourned by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
