\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 5th, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes for being terse and accurate passes 15-5-14+Spehn.

Motion to note that the Skinner will like the Dark is Rising movie more than Fragile Things passes 16-13-2+Spehn.

\BING

\goto{Committee Reports}

\subsection*{LHE report}

So, you know that PO we had last week?  So, ``have'' is non specifically defined here, in this case, defined as ``don't actually have''.  But we will have it next week!

On a slightly shinier note, Finboard gave us money!  

Yay, paragraphs. 

Reportedly, Steven Erikson is still good!

\subsection*{Libcomm}

If you're a regular grepper of the dex, you may notice that the codes that begin with HASSLE now begin with KBX.

Motion to grant Karl a fire extinguisher to postpone his burnout as long as possible passes 25-2-5+Spehn.

\subsection*{Bondagecomm}

Magazine Inventory has gathered data on all the magazines which are not behind a lock.

Bondagecomm's favorite magazine numbering story:

There was a Swedish magazine with seven issues, numbered thusly: 

\texttt{1 2 3 4/347 2/348 3/349}

\subsection*{Mag.*}

Magdex is trying to organize a prentice party soon!  Email \texttt{magdex@mit.edu}.

\subsection*{Jourcomm}

CAK's friend in Maine will be submitting a story!

\subsection*{Strosscomm}

We have just acquired two copies of ``On Her Majesty's Occult Service'', which is the Bob Howard omnibus.

Also, Halting State came out!

\subsection*{Katiecomm}

Katiecomm did lots of Katiecomm work.

We got Making Money, donated by Sukrit!

\subsection*{42nd Army of the Society}

We need to find a way to notify HRSFA something something.  Wait, there's a spy!

\subsection*{Star Chamber}

KR cleared off the Star Chamber shelf!

JFC: ``We should resume causing difficult problems that only the Star Chamber can solve.''
CJT: ``Wait, you stopped?''

%\subsection*{Rearranging Deck Chairs On the Titanic}

%\subsection*{Theftcomm}

%subsection*{Mortcomm}

\goto{Old Business}

Various people were Nazis.  And hippies.  In a SIK game.  It was, reportedly, awesome.

\goto{New Business}

\textbf{\emph{Matthew Jarpe reads an excerpt from his book, Radio Freefall, to much applause.}}

Mr. Jarpe has donated a signed copy of his book, as well as a T-shirt and several CDs of music from the book, recorded by Rajnar Vajra.

Kevin is taking 21W.765, and is in the process of creating a MITSFS text adventure.

\goto{Future Business}

In the future, there will be a review of this book, and all the rest of you can read it.

\textbf{In the future, we will be meeting on Tuesday at noon to drag things out of the Rage Warehouse.}

Rearranging Deck Chairs On The Titanic should be renamed to Titanic Tetris.  Or Tetriscomm.  Or Rearranging Deck Chairs 
On The Nautilus.  Or Poseidon Adventure-comm.  Or Titanic Under The Sea.

The X-Men are not SFnal in this book, because they are accountants, Damn You, Magneto, I Told You Double Booking!

Jake Beal proposes that we send HRSFA a declaration of war written on the Skinnerial Banana.  It is so moved, and passes 37-0-0+Spehn. 

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
