\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 12, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Kevin Riggle, President and Skinner, presiding; John Carr, pseudo-Onseck, recording.

On the twelth day after Christmas the Onseck left for me...some minutes
that were read.

JM: Condemn the minutes for failing to record all those things we said about
how the Skinner hates {\em Fragile Things}.
Fails \hbox{3-6-1+Spehn}.

\goto{Committee Reports}

\subsection*{ClueComm}
Revised keyholder notes are almost done.

\subsection*{Pianocomm}
We have two new keyholders -- Christian Ternus and Kristin Berry --- and will
soon have several more.  Soon we may have MKR, Miss Katie Ray.

\subsection*{Pseudo-Trojan}
We have a new one box donation from a previous donor.
Some other donation was ``processed,'' by which the Skinner
means ``counted.''

\subsection*{BluebellComm}
The Bluebellcomm shelf filled up over break, proving that the
committee is working properly?
The Bluebellcomm shelf is the beating heart of the society.

\subsection*{P-hasslecomm (MKR)}
Purging continues, A through Cherryh is done plus some random
stuff in the middle.  There are 11 boxes so far, ``back there.''

\subsection*{Magdex}
Jake wants to have a giant inventory thing the last weekend of IAP.
Inventory is suspended until then.  It's like real inventory, except
the opposite.

\subsection*{$\hbar$comm}
Christian has been made $\hbar$ comm.  He is responsible for getting
us an LSC slide.

%\subsection*{Onseck}

%\subsection*{War Council}

%\subsection*{FrustratedAuthorComm}

%\subsection*{JourComm}

%\subsection*{Mobcomm}

%\subsection*{Star Chamber}

%\subsection*{Vox Sciurorum (Mumbling about Rats)}

\goto{Old Business}

JFC reads an advertisement from the January-February 1971
issue of {\em The Progressive Teacher}:
\begin{quotation}
New ``Compulogical Tutor'' is world's first computer designed for home use

A full-fledged computor for use in the home? It's now a reality with
the introduction of the COMPULOGICAL TUTOR, the first computor ever
available at a popular price.

Comparable in functions and performance to bulky academic computer
trainers, the Compulogical Tutor weighs only 4 lbs. and is constructed
as a desk-size portable to take up a minimum of space.
\end{quotation}

The same issue contains a song by JFC's grandmother and an
article by Vice President Spiro Agnew titled ``Good Child
Care One Key To Final Solution.''

We still have new TZs, for the low, low price of \$1, a 50\%
discount from the previous price!  Back issues for only 25
cents!

Usual stuff.

\goto{New Business}

Before opening the library JFC found a bunch of Vericon posters
guarding the entrance.  They were not very tall, so he stepped
over them.

KR:
Robert Anton Wilson, author of the Illuminatus! trilogy, died this week.
He was about 60.  The cover story is cancer.
JM assumed he was already dead because he hadn't been writing new books.

Y: The issue of NeoOpsis on the new magazine shelf has a table of
contents that could have come from the 1950s.

\goto{Future Business}

Something about calendars.

There is a new movie out called {\em Pan's Labyrinth}.  This is
somehow related to the David Bowie movie mentioned in last week's
minutes.

Neither of the previous items was actually about the future.

David Bowie provides the voice in a new animated fantasy movie.
This is in fact distantly related to last week's minutes, but
may not be related to the future.

KR notices a new stack of boxes of books and utters a four letter word.
In the future the Gadouri donation will be dealt with somehow.
``Find me another room and we'll talk.''

It would be helpful if somebody donated books that had all the pages
replaced with \$100 bills, or books that were made out of solid gold.
What if the books are ticking?
The Skinner warns: ``I do not want a radioactive library.''  He is then
instructed on the difference between a clock and a Geiger counter.

Y expresses regret for the demise of housing shortage science fiction,
which was a microgenre popular for about a year after WW2.  Counterexamples
to the demise of the genre are noted, such as ``Billennium,''
{\em Make Room! Make Room!}, {\em Stand on Zanzibar}, and more.

Mystery hunt talk is not recorded.
In the future the Skinner will be on the team that acquires a penny.
Or a banana?  A banana.
This is motionized and passed by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-Onseck}

\end{document}
