\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/31/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 31, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Christian Ternus, Onseck and Pseudo-Skinner, presiding;
John Carr, Aloha Lenscomm and Pseudo-Onseck, recording.

Are there any motions concerning the minutes?

Y: "No but I move to commend the binging for being above and beyond
the call of duty."  Passes \hbox{13-1-5+Spehn}.

We thought Sophie was a puppet from Heinlein's {\em Puppet Masters}.
But she really did leave her backpack at the door, so maybe she
isn't.  Maybe.

\goto{Committee Reports}

\subsection*{Phonecomm}
``Bring the {\em what} back to Random?  The {\em couch}?''

Kevin is wondering if there are a couple of keyholders here
who want to move books back to here so he and Andrew can take
the couch, that is the couch, back to random.

The couch?

There's a couch.

Carrie is deemed expendable, being neither Christian nor John,
and is dispatched to the Midway.

\subsection*{Star Chamber}
All of the Star Chamber is now back except three quarters of
it is not actually back.

The Star Chamber is explained to Sophie, and the distinction
between the President and the Skinner.

%\subsection*{Dexmistress}

%\subsection*{Katiecomm}

%\subsection*{LHE report}

%\subsection*{Interim LHE report}

%\subsection*{Pantercomm}
%\subsection*{Panthercomm}

%\subsection*{Magventory}

%\subsection*{Dexmistress}

\subsection*{Alohalenscomm}
Took pictures, as usual.

\subsection*{Pseudo Vox Sciurorum}
The squirrels in Harvard Yard were in a frenzy running all over the
place and appearing excited.  Y assumed this was because of the
influence of fresh nuts.  (Or was that influx?)

\subsection*{Onseck}

Somebody replaced the other binder that sucked.  The new low quality
binders hold up better than the old high quality binders that the
Onseck bought.

With Term we will be able to free our books from UA domination.
Move to send an expedition to scale the mountain of books.
Chickens \hbox{1-2-6+Spehn}.  Discussion of Spehn follows.

The Pseudo-Onseck doesn't want to give any more committee reports
because he would have to type them up.  Motion to condemn the
laziness of the p-Onseck. Passes \hbox{6-3-4+Spehn}.

\goto{Old Business}

Y: Motion to encourage the mountain of books to come to Mohammed.
This prompts discussion but no voting.

Christian: Term is now over.  Summer is now over.  Term that was not
term is now over.  Term has not yet started.

John reads from the December 21, 2001 minutes, in which Jamie gives
the gavel a thorough, wet massage.

\goto{New Business}

``I quash the usual debate.  There are no usual complaints in
Soviet MITSFS.''

Y reads from a review of Seaview.  ``Nobody ever said Nazis were
practical people.''

Christian thoroughly massages the wet gavel.

John starts to read the Acorna's Rebels SFBC blurb and is forced to stop halfway.
Discussion follows concerning things to do with a time machine and Anne McCaffrey.
Are time machines for procreating or writing?
Motion to draft a modified Nuclear Test Ban treaty to ban
Anne McCaffrey proliferation.  \hbox{14-0-2+Spehn}.

\goto{Future Business}

In the future we will have more freshmen.  Some of the freshmen will
become prentices.  ``Which are...?'' asks an unsuspecting future prentice.

Prentices are the cool kids.  The relatively cool kids.
``Actually, I can't think of anyone we are cool in comparison too.''

``Nerds!'' passes \hbox{7-0-0+Spehn}.

We're totally cool in comparison to somebody.  We must be.
Anne McCaffrey!  That's it!  Motion in favor passes \hbox{16-0-0+Spehn}.

Motion to lure freshmen with fruit, including bananas.
``Is eating allowed in the library?''
Nobody said the freshmen were allowed to eat them.
Passes \hbox{12-0-6+Spehn}.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
