\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 8, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christian Ternus, Onseck and Interim Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to commend the minutes as perfectly and exquisitely accurate: 6-0-8+Spehn

\goto{Committee Reports}

\subsection*{Aloha Lenscomm}

New keyholder pictures and pictures of the picnic are coming.  Coming to get us.

\subsection*{pseudo-Analogcomm}

We have a summer schedule!  Yay.

\subsection*{MagDex}

MagDex party this weekend!  Email CAK or KKB to help.  Anyone is welcome, prentices especially encouraged to show up.

\goto{Old Business}

Term is dead.  Yay!  Lots of people are finally getting back for the summer.

Not-ALGOL.

\goto{New Business}

No complaint!  We got the debate in before the vote!  W00t!

Graduation was today!  No keyholders graduated.  We think.

Window washing is over.  (We aren't sure that they actually did wash the windows.)
The furniture and random stuff in the library can be reinstated.

\goto{Future Business}

``In the future, we will graduate.'' - CAK

``That future is a long way off!'' -CJT

KR is far away but contactable via zephyr, so...

Entire library: ``HI SKINNNER!!''

Everyone should read Nightwatch.  And Last Call.  

Motion to give CAK a farewell banana- 10-2-2+Spehn.

``Welcome to summer!'' -KCR

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
