\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 27, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Christian Ternus, Onseck and Interim Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

The Sims computer game has a spin-off movie coming out?!

Move to commend the pseudo=Onseck for a good gimp reading of the minutes: 5-0-8+Spehn

Motion to commend the pseudo-Onseck for great bravery in light of ALC's atrocious spelling: 12-0-3+Spehn

Motion to remand our computer to Eric Flint for correction: 10-0-3+Spehn

\goto{Committee Reports}

\subsection*{Panthercomm}

MKR did a lot of Panthercomming.  We are down to 24 boxes of overflow.  Yay.

Mobcomm gave a lot of money to Blizzard and these books are now on our New Books shelf.

\subsection*{Potterdammerungcomm}

Yeah, yeah, we have Harry Potter #7.  It's on the New Books shelf.

Digression about potterdammerung.

Related hacks on campus included a ``Broomstick Parking'' rack in the Stata Center and the Death Eater symbol posted above the Student Center.

\subsection*{Kvetchcomm}

Tony Valentyne isn't nearly as good an author as he thinks he is.  A review is coming soon!

Review books; it's fun!

Meta motion discussion about letting Jake do a back cover reading.  Through the meta wanking, it passes 15-0-2+Spehn.

Motion to have another book cover reading: 15-2-4+Spehn.

These two are, respectively, the most generic male book ever and the most generic female book ever.

\subsection*{pseudo-Mobcomm}

The Coop, which mistakenly got one of our boxes of books, managed to return it to us before the official channel for our mail gets boxes to us.

Hmm... an obvious plan suggests itself.  MITSFS, c/o The Coop...

\goto{Old Business}

Harry Potter is now old business forever!

Digression about bad Pride and Prejudice spin-offs and other bad literature and fanfiction.

The Beatles were psionic empaths.  Why is JSB connecting this to Anne McCaffrey's books?

Finding one's sister annoying?  Unheard of!

ALGOL

\goto{New Business}

CAK is reading Atrocity Archives!

Move to commend Charles Stross on general principles passes by pseudo-Skinnerial decree.

JSB's talents for finding bad books has extended to finding bad cover art.  Is that a poptart in space?

Digression about Robert Jordan.

\goto{Future Business}

Motion to eat a banana: 5-6-1+Spehn

Motion to not eat a banana: 5-2-1+Spehn

Motion to have a matrix motion: 6-6-2+Spehn

Determinant is -12, all motions fail.

MKR eats a banana while the pseudo-Skinner collects votes.

Motion to not have any more matrix motions (except those involving bananas) that have ``motion to have a matrix motion'' as its last motion passes by pseudo-Skinnerial decree.

\bing
\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
