\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2006}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 19, 2007

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Kevin Riggle, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes for containing interpretive dances passes 13-5-5+Spehn.

\BING

\goto{Committee Reports}

That one.  Yeah, details.

\subsection*{Hasslecomm}

Hasslecomm did Hassle-work on Thursday during JSB's hours.  We had lots and lots and lots of help.

\subsection*{Katiecomm}

Katiecomm did more work.

That couch is almost empty!  

There are now circulating copies of Making Money and Halting State.

\subsection*{LHE}

The Rage Warehouse is getting more expensive.

\subsection*{Pseudo-Libcomm}

Libcomm has gone to Florida.

The barcodes showed up!

JPW was playing with the barcode scanner until she realized that there was nothing to scan.

\subsection*{Pseudo-Pianocomm}

We have more prentii: Ian (\texttt{ianyh}) and Jasmine (\texttt{jasminef}).

\subsection*{Pseudo-Niagaracomm}

Boxes of books were donated to the MIT Used Book Fair.

\subsection*{Mag.*}

Magdex party on Sunday!

%\subsection*{Alohalenscomm}

%\subsection*{Katiecomm}

%\subsection*{Chamber Report}

%\subsection*{Pseudo-Onseck}

%\subsection*{LHE report}

%\subsection*{Rearranging Deck Chairs On the Titanic}

%\subsection*{Theftcomm}

%subsection*{Mortcomm}

\goto{Old Business}

Discussion of Guild games ensues.

\goto{New Business}

\begin{verbatim}
\ldots{}
\end{verbatim}

Asimov is dead.  Long live Asimov!

The Dark is Rising movie (\emph{AAAAAGGGHHHH}) came out.

You should blanche yourself on to mitsfs-social.  Or get the Onseck to.

The clock is (possibly) dead.  Long live the clock!

Various books are good.  And authors.  Including Steven Erikson!  And Jim Butcher.  And Charles Stross, again.

\goto{Future Business}

There will be a run of Condition Echo Blueshift, the Stross Guild game, this Saturday.

In the future, KR will read more books!

Ian: ``Randall Munroe is good, but I'd actually jump on Neil Gaiman.''

In the future, there will be authors showing up!

Motion to lure Neil Gaiman into the library with a banana passes 20-2-0+Spehn.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
