\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, pseudoOnseck}
\newcommand{\meetingdate}{Friday, 14 September 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

\subsection*{hBarcomm}

We need to put up a new schedule on the bulletin board.

\subsection*{pseudoMommycomm}

We had a work party last weekend and three prentices came
and they seemed to really like it and like meeting people 
and doing work.

We should have another one this weekend.


\goto{Old Business}

In the past MIT was full of creepy stalkers.  We'd like to
keep that in the past.

In the past, the LHE got a new toy.  But it isn't very good
at SSH, so it's hard to write Guild games on it.

In the past, there was too much student government.  It ate souls.

Motion to \bing passes by Skinnerial decree.


\goto{New Business}

In the present, we have an armenard.  He might show up on campus more often.

In the present, Black Hole has \emph{all} the milks.  Including hemp
milk.

In the present, we have creepy 3-D author heads.  It is proposed we
paint them.  This is determined to be a \emph{really terrible} idea.

Tomorrow is the Cambridge Dumpling Festival in Central Square.
Sadly, no pierogi, I think.

In the present, someone changed Psi-Phi's error bell to be a rather
disturbing bubbling sound.

\goto{Future Business}

In the future, ariels and armenard are going to sell lots of
chocolate at Arisia.  Two weeks before the ten-day they're writing.

The Skinner recommend chocolate books.

Motion for banana-shaped chocolates made out of banana-flavoured chocolate
PASSES by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
