\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 17 August 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.


\goto{Committee Reports}



Libcomm AHHHHHHHH

Motion to condemn last week's minutes for being too short and too quite PASSES 5-0-1 \ps

Mortcomm reports Harry Harrison passed away this past week.

RealAuthorsComm invited Dotorow and Stross to visit during Rush.

Mommycomm finished Bluebellcomm's backlog.

Sheets were digitized.

\goto{Old Business}

Prentices did work! 

In the past we didn't have an RF-ID thing.

\goto{New Business}

ARGHHHHHHHHHHHHHH the onseck got so confused that this section of time was complete erased leaving a gap in the space time continuum which will eventually devour the entire universe

\goto{Future Business}

In the future there will be inventory

In the future there will be freshmen, and they will eat the book.

Motion to distract the freshmen with bananas instead of books so they don't eat the books. PASSES 7-2-0 \ps

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
