\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 31 AUGUST 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 64.3 Ksec SST,
\skinner, presiding; \onseck, recording.


\goto{Committee Reports}
Realauthorscomm Cory Doctorow will be visiting next Friday at 2 pm!

Oh man there's a frosh in the library

Hbarcomm made bookmarks with the rush schedule on them, and is actually doing rush events! 
The schedule for those interested is:
9/2 2:00-5:00 Open House
9/3 2:00 Short Story Reading [Golden Age of Science Fiction]
9/5 8:00 Short STory Reading [Bad Scifi Dramatic Reading]
9/7 5:30 MITSFS meeting
9/7 6:00 Seldon Showing [The Fifth Element]
9/8 3:00 Short Story Reading [Steampunk Stories]
9/9 2:00-6:00 Prentice Hours

Motion to show the frosh a motion FAILS 0-11-1\ps

Hasselcomm will have a party next weekend

Mommycomm reports that the midway happened! We now have the e-mail addresses of SO MANY FROSH!

\bing

\goto{Old Business}

Inventory happened, the midway happened.

In the past, there were prefrosh.

\bing

\goto{New Business}

In the present we have a list of frosh.

\bing

\goto{Future Business}

In the future there will be prentices and new members and events! YAY!

In the future we will develop nanites that will reprogram other students brains in to giving us more space!

Motion to explain banana motion to rhkeeler PASSES ?-?-?\ps

\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
