\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 25 May 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.0 Ksec SST,
\skinner, presiding; \onseck, recording.

\bing
Motion to condemn the bing for being unenthusiastic FAILS due to lack of second.

\goto{Committee Reports}
LHE might submit RFPs
Jourcomm might happen, probably not
There's a new TIF!

\bing

\goto{Old Business}
Finals are done!
Super unenthusiastic yay.
aclough came to the meeting.
alexwest finished something and can now return it to aclough.
Usual motion passes to skinnerial decree

\bing

\goto{New Business}
Happy towel day! 
Rhode Island is dumb.
\bing

\goto{Future Business}
In the future there will be a hasselcomm party
In the future there will continue to be no finals
In the future there will be TOV and FI
In the future aclough's business will be bought
motion to higher any 38 studio employee as long as they're willing to work for bananas PASSES due to skinnerial decree
\bing
\noindent
Meeting adjourned, 64.8 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
