\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, DAY MONTH 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST,
Lemur, Vice, presiding; \onseck, recording.

Minutes read.

\bing

Motion that the minutes were excellent PASSES 5-0-1/ps

\goto{Committee Reports}

Mommycomm: There will be NO prentice hours this weekend

Starchamber: is hosed! The events.mit.edu account was fixed, so that people other than Miss Katie have minutes.

\bing

\goto{Old Business}

In the past we had commitees that did work.

In the past, people probably had energy or something.

In the past there were more bayonets, and wars and stuff.

Motion to commend the past for having more bayonets FAILS due to lack of second.

In the past there were redwall books.

\bing

\goto{New Business}

In the present, lknight and Lemur got SO HUNGRY due to not having eaten enough today that she ate the entire library, increasing their mass to the critical point, creating a miniature black hole that destroyed Cambridge and the surrounding areas, eventually eating the entire world.

The Boston Book Festival is tomorrow in Copley Square.

\goto{Future Business}

In the future we will or won't be hit by a hurrican.

In the future, Emily Lydic is organizing a letter to Leonard Nimoy.

In the future, Thursday November 1, 2 pm, W20-491 lecture by Professor Ian Hunter, organized by the MIT future society on making the future happen.

Motion to go eat bananas due to BEING HUNGRY passes by pseudo-skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
