\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Vice and pseudoOnseck}
\newcommand{\meetingdate}{Friday, 30 November 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the pseudoOnseck on its reading of the minutes
and to extend the meeting by thirty minutes FLOPS by Skinnerial decree.

\bing

\goto{Committee Reports}

pseudoTrojan: We got a large donation of books and the donor doesn't want anytihng in return!  Yay!  We can make prentices check them for mold, and then give them to Panthercomm.

Skinner: A couple of weeks ago, we started merging.  Well, actually we just boxed some of PA, but that was practice for merging.

On 12th January, in place of Inventory, we'll be having a massive merging-reserve-into-circulating party!  Mark your calendars!

pseudoAlbaniacomm: Lemur will probably be organizing a mob to Arisia.  It will email out shortly to find out if anyone is interested.  (Note that this will conflict with Mystery Hunt, but as ASA Treasurer, it doesn't get to do Hunt anyway.)

\goto{Old Business}

In the past there was not electricity.

In the more recent past, there was electricity and then wasn't and then was again.

\goto{New Business}

In the present everyone is exhausted.  And incoherent.

In present, kevinr is checking out a book.


\goto{Future Business}

In three weeks, kevinr's book will be due.

In the future, there will be finals.  And then various and diverse science fiction convinetions.

Motion to have the Earth be destroyed by a banana-shaped Death Star PASSES by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
