\documentclass[10pt]{article}
\usepackage{xspace}
\usepackage{html}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 6 January 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes for containing the word "exeunt" PASSES 15-0-2\ps.

\bing

\goto{Committee Reports}

\subsection*{Libcomm}

Libcomm would like to remind the Skinner that is not too late to cancel inventory.

The Skinner will consider this interesting option.

An ill Keyholder gasps that we should be careful and not listen to what the books are saying.

Libcomm would like to remain on good terms with the books, and would like to remind
everyone that the books are our friends and that we should trust them.

\subsection*{Seldon}


\goto{Old Business}

In the past, it became a new year.

In the past, we had a purple dragon join the library.

In the past, we ran off the schedule.

In the past KKB checked out too many books, so now she can't check out the
one PW gave her to read two hours ago.

Usual motion.  Unusual third.  Usual location of the Magazines.  ALGOL.


\goto{New Business}

In the present, we're still getting prophesies from the Fundamentalist Church
of Jesus Christ of Latter-Day Saints.  The Skinner thinks they're probably SFnal,
but we're not really clear on this.  They're getting angrier, though.

In the present, Project Gutenberg has a list of \htmladdnormallink{"Precursors of Science Fiction"}{http://www.gutenberg.org/wiki/Precursors_of_Science_Fiction_(Bookshelf)}
It has some neat stuff, like a Roman author who wrote about sailing between the Pillars
of Hercules and thus to the Moon.  We could also suggest some of the stuff they
missed, like Kepler's book about traveling to the moon with the aid of the demons
of astronomy, which can only do so during a lunar eclipse because they don't like
sunlight.

\goto{Future Business}

In the future, it will be IAP.

In the future, there will be an Inventory.  But how far in the future? 

In the future, like next week, there will be a science fiction convention.  It's
called Arisia, and is held in the Boston Westin Waterfront.

But, there will also be Mystery Hunt next weekend.  If you want to do that and don't
have a team, talk to someone here and we can get you one.

There'll be another convention, Boskone, run by our splinter group in the hills of
Albania.  It's in February, also at the Boston Westin Waterfront, and we'll be
sending a mob.  We'll also maybe sell books.

Miller motion FAILS due to lack of a second.

Motion to recognize the overlordship of the catalogied items, viz. books, bananas, et
cetera PASSES 12-4-4\ps.

The conversation was eaten by Mayans, and so I found it useful to gibber incoherently
in Atlantean to end it.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
