\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 12 October 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST,
\skinner, presiding; \onseck, recording.

\bing

\goto{Committee Reports}
Theftcomm: there will be a new TIF this weekend

Warcomm: We talked to MIT libraries, and they're going to talk to more people, and maybe at some indeterminate point in the future, something happen

Mommycomm: Prentices hours 2-6 Sunday

Nanocomm: Naomi may hold more hours to encourage people to come write in the library!

\bing

\goto{Old Business}
In the past, there was a four day weekend

In the past, it was not this cold

In the past, aclough got a kindle, and it's shiny and glows

\bing
\goto{New Business}
In the present, it is near ComicCon

In the present, the wormhole between the library and Caltech started to malfunction, and instead making it so that the library was fluctuating between Cambridge and Albania, and eventually collapsed so that Albania and Cambridge were actually in the same place, and that place was on the bottom of the Atlantic Ocean, causing the Ocean to displace, flooding much of North-East America and Europe, sending the world in to a state of panic and chaos.

\bing
\goto{Future Business}
In the future, the library will be merged. No really guys, it's happening!

In the future, alexwest will try to get RA Salvatore to come to the library!

In the future, aclough is going to a Renn Faire tomorrow.

In the future, Naomi will be in a Halloween show.

In the future, aclough will be starting a new job at Vecna.

Motion to make aclough eat a banana so he won't sing the skinner song PASSES by skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
