\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 20 April 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the terrifying enthusiasm with which the minutes
were read PASSES 6-0-4\ps.

\bing

\goto{Committee Reports}

\subsection*{Picniccomm}

The elections meeting will be two weeks from today, with the picnic the
day after.  An invitation should be going out this evening.


\subsection*{Theftcomm}

There is a relatively new TIF.  People should hold hours!

Lemur is already off the top of it, but no one else is close.
"I'm sorry.  I didn't mean to."


\subsection*{RealAuthorscomm}

2005 John W. Campbell Award winner Elizabeth Bear and Scott Lynch, 
the author of The Lies of Locke Lamora and Red Seas Under Red Skies, 
will be visiting MITSFS at 18:30 next Wednesday, 25 April, for an informal 
visit. Feel free to come! We might take them out to dinner! 

Also, we need people to help make and put up posters for this event!
Poke the Star Chamber and hBarcomm if you're interested in helping.


\subsection*{hBarcomm}

CPW Midway is tomorrow, 13:00-15:00, in Johnson.  We have a booth;
people should come staff it!


\subsection*{pseudoMobcomm}

Paul tried to order books yesterday, but he got sick and forgot.


\subsection*{pseudoPianocomm}

We have a new prentice!  They're a grad student!  Maybe they'll do work?


\goto{Old Business}

There was Babylon 5.  Paul killed Andrew, and they were on the same
team!  But it was fun.

There was a Neal Stephenson interview!  It was neat.  The Skinner got
to eat dinner with Neal Stephenson!  That was even more neat.  It was
like eating with a bunch of old MIT professors.


\goto{New Business}

It's CPW!  Campus is infested with prefrosh!  They're not bitter
yet!


\goto{Future Business}

In the future there will be elections and a picnic.  In two weeks.
The same day as Steer Roast, but earlier in the day.

On Monday, 14 May, Jean-Christophe Valtat will be doing a book-signing
at the Harvard Book Store.

On Friday, 15 June, John Scalzi will be doing a book-signing at the
Harvard Book Store.  We'll try to persuade him to come to MITSFS, or
maybe to go out to dinner with us.

Motion to attract John Scalzi to the library by sacrificing a bunch
of Redshirts on a pyre of banans FAILS 4-2-5\ps.

Motion to offer offer John Scalzi a bacon banana (not a bacon-wrapped
banana; we can do better than that) PASSES 9-0-2\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
