\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 20 July 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Through a series of mishaps there were no minutes for last almost month so there was nothing to read!

Motion to condemn the past for not having happened PASSES 4-0-1\ps

\bing

\goto{Committee Reports}
Bluebellcomm discovered two boxes
Hasselcomm still has a lot of work to do
Pierogicomm will have a shopping part on Sunday, there will be another after sometime after inventory for people who can't make the first.
Trogan has some news maybe.
Starchamber- we might get an RFID lock sometime this summer
Clockcomm- why does our clock still not have clockness?

The library is currently experiencing some space-time anomalies, please enjoy this picture of a puppy while we work it out: http://images1.fanpop.com/images/photos/1900000/Puppy-3-dogs-1993802-1024-768.jpg

\bing


\goto{Old Business}
In the past we failed to have meetings
In the past prentices did work

Usual motion, usual debate, usual etc
\bing

\goto{New Business}
In the present we have four keyholders at the meeting! More people should come to meetings.

\bing
\goto{Future Business}
In the future everyone will be out of town
In the future there will be inventory
In the future, these will hopefully not be at the same time!
Banana! Passes by skinnerial decree.
\bing
\noindent
Meeting adjourned, 66.8 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
