\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 11 May 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes summarized.

\bing
Motion to condemn old skinner for not causing a flame war.
 9-12-11\ps
Motion to condemn the current skinner for making the current onseks life too easy
12-12-11\ps
Motion to condemn aloha comm for forgetting his memory card
42-4-12\ps
All motions FAIL, the determinant was -180

\goto{Committee Reports}
Alohacomm, having forgotten his memory card, sucks despite the previous motion failing. 
Picniccomm successfully ran a picnic, at which Sukrit became the new champion of gavel tossing.
Seldon will be showing Small Ville tonight.
Rosfap intends to do stuff based off of the current magazine system.
\bing

\goto{Old Business}
In the past there was a picnic, there was an election, the minutes talked more about trains and before that dragons, and the skinner was a peasant.
\bing

\goto{New Business}
A prentice came to the meeting! No really! There was a physical human body who was prenticed in the library!
We used to have more prentices, but then they were keyed, which was probably a good thing. There are a lot of inactive prentices.
\bing

\goto{Future Business}
In the future...
\n Term will be over! The ex-skinner will be done with all his assignments forever. Lemur will be leading a keyholder pierogi mob. Monolith will need to be updated. Seldon will consider organizing mobs to see super hero movies that are coming out this summer. Lemur will organize a mob to a folk thing. KKB will create an rpg based on the laundry file. wkalb will create an rpg based off a story he read once. wkalb will postpone his birthday until after finals. pweaver will get the electronic checkout system done. The library generally disagrees, given that it was originally supposed to be done in January 2006 or 2007. Alohacomm was taking pictures of the gavel, and stealing its soul, except that it was not possible. Banana motion, the skinner decided that it passes.
\bing
\noindent
Meeting adjourned, 60.0 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
