\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Lemur Rowlands, pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 13 January 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the Skinner for causing unInventory to happen
PASSES 15-0-4!

\bing

\goto{Committee Reports}

\subsection*{pseudoLibcomm}

Inventory didn't happen.  Inventory will happen some time this summer instead.
For now, the books are appeased.

\subsection*{Star-Chamber}

We had a massive work party on Saturday.  We got through about three-quarters
of the Hasselcomm backlog.  Shelves were cleared to extend the circulating
hardcovers more, and to extend the circulating hardcover anthologies, and to
move some small circulating shelfcodes.  Also, Mancinnicomm did a partial
inventory, and boxed the foreign Perry Rhodans.

\goto{Old Business}

A prominent local filker, Alice Washburn, also known as Badger, died late
last December.  Her funeral was at the MIT Chapel today.

UnInventory is Old Business.

Spehn is Old Business.  Apparently he was only at MIT for one year, 1964.  There
was a Risk gameboard in the old MITSFS library in Walker Memorial, and that was
his downfall.

Catacomm does not wish to comment on the location of the magazines.  ALGOL

\goto{New Business}

We have lots of visitors, who are stopping by after Badger's funeral.
Former keyholders Sue Isaacs and Fred Isaacs--commonly knowin as SI-FI, 
apparently--along with a large clutch of teenagers: Annie Isaacs, Kevin 
Card, Rex Powell, and EKVI.

One of the teenagers wanted to see the Thrawn Trilogy and one of them 
wanted to see the Pratchett stuff.  

The Pratchett one apparently annoyed Pratchett when 
she was an epsilon at N-4 by asking a question about a tortoise
when he was doing a panel discussion and fed up with questions
about turtles.

The Sue Isaacs had a story about being in a hospital emergency room
next to a Break-Me-Own-Arm Dibbler, who broke his arm playing
Ultimate Frisbee and who apparently made a living making Internet
sausage.  (She also recommended a Doctor Crapp at Mt. Auburn as
competent.)

Arisia is New Business!

\goto{Future Business}

Boskone is Future Business!  This February!  We'll have a mob!  You should
buy a membership now, and should come join our mob!

Vericon is Future Business!  This March!

Readercon is Future Business!  This summer!

We were warned that Annie might try to sneak in in the future,
possibly by baking us very good cookies.  She also threatened to
give us a large collection of stuffed animals so that we might
be the "Island of MITSFS Toys".

We were given a "Profane Version"--it's profane becaused it's effable and,
in fact, efft--of a cookie recipe called "Honey Badger Biscuits", apparently
the work of the late Alice Washburn.  There may be an effort to manufacture
some of these for a future meeting, when the Onseck isn't ill.

Motion to note that epsilons like to chase people around with
sharkbannanas PASSES 18-0-5\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
