\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, DAY MONTH 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

Realauthorscomm- Cory Doctorow and Charles Stross visited the library, we have a copy of their most recent book and they left 3D printed version of their heads.

hbarcomm- there are frosh in the library!

Theftcomm- there is a new TIF!

\bing

\goto{Old Business}
In the past there was worldcon, and people won Hugos!

In the past, we got creepy phone calls from Worldcon

In the past there was dragon con

In the past, term started

In the past, Cory Doctorow and Charles Stross visited and talked to us about copyright law. 

\bing

\goto{New Business}

Motion to not explain things to the frosh FAILS 7-9-2\ps

There will be a Seldon Showing of the Fifth Element after the meeting.

\bing

\goto{Future Business}

In the future there will be prentice hours on Sunday from 2-6pm.

In the future we will steal the souls of ALL OF THE FROSH and then the library will be so full of souls that it will IMPLODE and take the world with it when it goes. MWAH HA HA HA HA!

Motion to order dinner with Bananas at the Seldon showing PASSES by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
