\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lee Fuchs, pseudoOnseck}
\newcommand{\meetingdate}{Friday, 09 March 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Lee is named Emeye, and is the demon-Onsek-replacement.

Minutes read.

Motion why does Kendra's code fail passes 4-0-1 \ps

\bing

\goto{Committee Reports}

\subsection*{Trojan}

Trojan got more boxes of doom



Everything is a case for rm -rf
Everything is a case for pseudo rm -rf /

\bing

\goto{Old Business}

The Skinner does not remember anything in the past. He knows only the present.

Motion for Kendra to destroy the universe passes 4-1-2 \ps

\bing

\goto{New Business}

The Skinner is probably deciding not to be a student next term, but may be again in the future. He has a job offer!

It is the bungee cord to MIT!

Apparently, graduating is better than not graduating.

There may have been an LED which is more than 100 percent efficient. This may violate the 2nd law of thermodynamics, which technically only says it's highly improbable.

\bing

\goto{Future Business}

In the future the Skinner will do stuff.

In the future other people may do stuff or make motions.

In the future kevinr's hosting provider may reboot his server.

In the very near future there will be Avatar Day!

In the future the Skinner might regain his sanity, and maybe even get sleep.

Motion to welcome our future banana overlords passes 9-0-0 \ps

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
