\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Kaleb Ayalew, Vice and pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 24 February 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

WHAAT!? PASSES 7-0-1\ps.

\bing


\goto{Old Business}

Two weeks ago there was Charles Stross.  He read us a chapter
from \emph{The Apocalypse Codex}, so we know it's real, although
Kendra still doesn't want to believe in it.  He also told us
about some of the other books he will have coming out soon.
\emph{Neptune's Brood} sounded really neat, it's a space opera
set in the far future of the universe of \emph{Saturn's Children},
and is hard SF without even near-light-speed travel.  He's also
writing a sequel to \emph{Rule 34} that will deal with transgender
issues in the near future.  And said that there will be about
nine Laundry books, and that the fifth is where everything changes.

Last week was Boskone.  There was much filk.  There was also
trivia for chocolate.  And sword demonstrations by people from
the Higgens Armory Museum in Worcester.  And a talk by Guy
Consolmango, an ex-Skinner Jesuit at the Vatican Observatory
who talked about the history of astronomy and major errors people
made because they had too much trust in their models. 


\goto{New Business}

We have new keyholders.  Laura McKnight, LAM; Emerald 
Ferreira-Yang, EFY; and Cathy Douglass, CED!

We may know what's going on with the neutrinos.  It looks like
there were some loose wires, which makes the Onseck feel much
better about all the loose wires in its lab.

Apparently there are rocket squid!  A new study in the
\emph{Journal of Mollusc Studies} found that squid can save energy
when traveling long distances by flying above the surface, powered
by a rocket of water.  http://www.nature.com/news/squid-can-fly-to-save-energy-1.10060

All hail our new rocket-squid overlords!


\goto{Future Business}

There was a motion to put what the Onseck said about having
possibly deleted the minutes into the minutes.

Motion to chastize the bananas in the library for reminding
Lee that she wishes she'd brought the ones she had at home
FAILS for lack of a second.

The apocalypse comes in the future.  Motion for us all to look 
forward to that day PASSES 10-0-2\ps.

Miller Motion PASSES 12-01\ps.

\bing
\noindent
Universe adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
