\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lee Fuchs, pseudoOnseck}
\newcommand{\meetingdate}{Friday, 4 May 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the pseudoOnseck for the terribly enthusiastic reading 
of the minutes CHICKENS 2-0-6\ps.

\bing

\goto{Committee Reports}

\subsection*{RealAuthorscomm}

Talking to Scalzi's publicist; he might actually be able to come!

Scalzi, that is.  (Well, his publicist might come, too.)

\subsection*{Skinner}

Is going to send out an email which might start a flame war this weekend before 
he hands over power.

\subsection*{Hasslecomm}

We need to schedule a work party after finals.

\subsection*{Star-Chamber}

Lots of new books arrived.  Aaah, the books are coming to eat us!

\subsection*{Picniccomm}

There's a picnic tomorrow!

Motion to note CD's shifty eyes passes 7-0-4\ps.

\subsection*{Smilescomm}

If people want to shelve reserve books they should, because there are a bunch that
are going to be coming off the new book shelf soon.

\goto{Old Business}

Bear and Lynch were here and they were awesome.

In the past keyholders were less hosed.

"I feel like we always say that, and I feel like it was never actually true."

"You look through all the minutes, and every time someone doesn't say it, it was true."

Discussion of hosage ensues.


\goto{New Business}

In the present, there are ELECTIONS!

The Skinner explains the traditional election rules of the Society.

The LHE announces that votes may be made in multiples of one third.  Everyone
has one vote, and non-positive components are allowed, unlike most years.

The Onseck will be Vanna, since it doesn't have a computer and so isn't actually
the one taking minutes.

Kendra is happy that her introduction of the term Vanna caught on.  It's in the
Picniccomm rites, though, so maybe it existed before her and she just restarted it?

\subsection*{President}

Official Candidate:

\emph{Alex Westbrook (AW)}

Unofficial Candidates: 

\emph{Cthulhu; the apple on Alex's butt; Alex's hat; all hats currently in the room; the orange bag; the gavel; the gavel block; the entity that ends up getting elected; Lemur's exponentially growing ball of Goo; Miles Vorkosigan; Mitt Romney; all pairs of mittens ever owned by Mitt Romney; the "The Rent is Too Damn High" Party; the Big Screw; the Big Shaft; motions to end nominations; seconds}

Motion passes 2-0-0\ps.

Alex would do her best to appoint the Skinner

No one could hear Cthulhu's speech and live

Alex says that the speed of an unladen swallow 
(NOT asking if it is African or European) is 24$\frac{miles}{hour}$

Traditionally all votes must be positive, but that wasn't specified. Oops.

Alex West is elected president (with $\frac{21}{3}$ votes)

\subsection*{LHE}

Explanation of the obligation to embezzle, but not get caught.

Official Candidate:

\emph{Mika Braginsky (MB)}

Unofficial Candidates:

\emph{Locke Lamorra, Bilbo Baggins, alexwest's tee-shirt, all the nominations for every past election ever, Londo Mollari, Valiant and Balk, all the goblins in Gringotts', gold, glod, pressed Latinum, Vlad the Impaler, Kelsier, Vlad the Impaler's 17th Impalee, the Sleeper in the Pyramid, Littlefinger, the Teapot}

Mika will embezzle money, then corrects herself that she will acquire money 
in unspecified ways. Occasionally.

Mika: $34\frac{2}{3}$

Teapot: $\frac{2}{3}$

Locke: $\frac{5}{3}$

Kelsier: -30

Littlefinger: $\frac{2}{3}$

Kelsier: 1

Glod: $\frac{-1}{3}$

Vlad: $\frac{1}{3}$

Londo: $\frac{1}{3}$

Mika wins


\subsection*{Onseck}

Official Candidate: 

\emph{Laura McKnight (LAM)}

Unofficial Candidates:

\emph{The act of nomination, Kvothe, entity with lowest total votes, entity with the highest total votes, a paradox, entity whose votes total has the highest ratio of imaginary parts to real parts, Sazed, the picnic, $\lim_{n\rightarrow\infty}(n\,lbs\,roast\,beef)$, an entity that is not nor will by on the list of nominees for Onseck, Alex's pset, a contradiction, Denmark's finest havarti, $(\phi^{n}-\frac{1}{5^{n}})^\frac{1}{5}$, MITSFS, the Telzey, entity most likely to cause alexwest's work the most confusion}

lknight promises to only create one world-ending paradox per meeting

lknight: $3\frac{1}{3}$

Kvothe: $\frac{4}{3}$

Sazed: $\frac{1}{3}$

Pset: $\frac{1}{3}$

a piece of paper: $\frac{1}{3}$

paradox: $\frac{1}{3}$

lknight is elected!


\subsection*{Vice}

The Vice is the embodiment of seven deadly sins, although the Skinner 
and president-elect encourage this Vice to reach out to the other deadly 
sins besides sloth.

Official Candidate: 

\emph{Lemur Rowlands (DWR)}

Unofficial Candidates: 

\emph{the picture distracting everyone; sloth; gluttony; greed; lust; envy; pride; wrath; puppies; kitties; tiny little animals that fit in palms; postering violations; Reddit, all the chans; stick figures, all of them; Sonic the Hedgehog; Edward Elric; Bob Howard; Sonic the Hedgehog gene, Contents of the vice drawer; Dean Colombo, Lemur's initials}

Lemur lost one third to...things, gets an extra third

Kittens: $\frac{1}{3}$

Puppies: $3\frac{1}{3}$

Lemur: $5\frac{12}{3}$

love, faith, charity: each $\frac{1}{3}$

Elric and postering: each also got $\frac{1}{3}$

Lemur is elected!


Recommendation for next year's Onseck: write $\hbar$comm in LaTeX for the name of hBarcomm

Motion to the President-elect to learn crazy:

Motion to summon Cthulhu:

Passes 12-0-2 plus Spehn

Motion to find out which motion just passed FAILS 17-0-4 plus Spehn

Motion to have Alex read the crazyvote PASSES 16-0-2 plus Spehn

\bing

Motions failed before getting seconds.

\bing

Congratulations--and condolences--to everyone who won the elections.

\bing

\goto{Future Business}

In the future our chants will cause Cthulhu to come back. \emph{4-0-1\ps}

Self-seconding motion fails due to lack of a second. \emph{0-0-0\ps}

In the future some of us will graduate. Maybe. 
Or put off graduate for a few more months. 
And a few others seem unlikely to graduate \emph{0-0-6\ps}

And the determinent is zero, and all motions CHICKEN.

Motion to have a picnic tomorrow PASSES 3-0-1\ps.

And the Skinner is driven from the room through singing.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
