\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, Vice and pseudoSkinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 13 April 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the minutes for siding with the tasty humans. (12-10-3\ps)

Motion to recognize that the stars are now right. (10-8-15\ps)

Motion to note that in strange aeons, even death may die. (15-0-12\ps)

And the determinant is 1868, and all motions pass!

\bing


\goto{Committee Reports}

\subsection*{Panthercomm}

The backlog from the last big Mobcomm order has been dealt with.
It's Bluebellcomm's problem now.


\subsection*{Bluebellcomm}

No it isn't; we dealt with it, too.  Now it's Smilescomm's problem.


\subsection*{Smilescomm}

*Makes a sad face.*


\subsection*{pseudoMobcomm}

It must be time to order more books!


\subsection*{Picniccomm}

We have new Picniccomm members: Cathy Douglas (CD) and Emerald 
Ferreira-Yang (EFY).  They're working on an invitation now.
The picnic will be soon: probably one of the first two weekends
of May.


\subsection*{Kvetchcomm}

The new Laundry Files book, The Apocalypse Codex, has arrived! 
Someone should write a review of it!

The Paul and Lemur have read it, and confirm that it is good and
that the last sentence is \emph{terrifying}. 


\subsection*{pseudoKvetchcomm}

After an Earth-scarring apocalyptic battle, the meta-humans have turned back a massive invasion of super-science powered Nazi war machines--and at least driven whoever is in ultimate control of them to pause and regroup. Now meta-hero organizations Echo and sometime Russian ally CCCP must go on the offense and battle back. Task one: to hunt down the secret puppet masters behind the Nazi robot invasion, the Thule Society. To do so, the heroes of Echo, led by Bulwark and Red Djinni, face the guardians of a hidden trove of Nazi armor. Meanwhile, a sadistic genius super villain arises who is determined to defeat both heroes and Thulians alike--a villain who just may have the wealth and cunning to pull it off.

One question remains...is this satire, or just a failure of the editors...
and who will read \emph{World Divided} by Mercedes Lackey to find out which?


\subsection*{hBarcomm}

Technology Review Science Fiction is having a power-style 
interview with SF author Neal Stephenson. It's a public event
and MITSFS will help with publicity in exchange for free seats.

The event is Tuesday, 17 April from 16:00-17:30 and called "A 
Long Evening with Neal Stephenson". It's in 10-250.

Email the Onseck (onseck@mit.edu) if you want to be added to 
the list for free tickets. 


\subsection*{RealAuthorscomm}

2005 John W. Campbell Award winner Elizabeth Bear and Scott Lynch,
the author of \emph{The Lies of Locke Lamora} and \emph{Red Seas 
Under Red Skies}, will be visiting MITSFS at 18:30 on Wednesday, 
25 April, for an informal visit.  Feel free to come!  We might
take them out to dinner!


\subsection*{Seldon}

No Seldon showing this week, because Seldon is playing in Babylon 5.
There will be a showing next week; movie to be decided on shortly.


\goto{Old Business}

In the past, there was PAX East last weekend.

In the past, there was Anime Boston last weekend.

In the past, the MBTA opened an extra entrance of the Hynes/Convention 
Center station to accomodate all the extra geeks. 

In the past, when Lemur wasn't the Onseck, the minutes talked less
about trains.


\goto{New Business}

In the present, there is a Babylon 5 Guild Game!

Who are you? PASSES 9-7-5\ps.

What do you want? CHICKENS 3-3-5\ps.  

The Vorlons are back!  The Shadows are scary!


\goto{Future Business}

Next weekend is CPW!  Next week, a film crew from the MIT News Office
will be coming to the meeting!

In the future, there will be the Neal Stephenson interview.

In the future, there will be a visit from Elizabeth Bear and Scott Lynch.

In the future, Seldon will show more movies.

In the future, we will have a picnic.

Motion to serve bananas at the picnic PASSES 15-0-13\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
