\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 16 March 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the pseudo-Onseck for her insight in identifying the
Onseck as a demon.

Motion to note the minutes as having been read by Batman bin Suparman.

Motion to commend the Skinner for not adjourning the meeting just because
of a little thing like adjourning the universe.

The matrix is:

5, 1, 1 \ps

3, 1, 1 \ps

1, 2, 2 \ps

and the determinant is -2 and all motions FAIL!


\bing

\goto{Committee Reports}

\subsection*{Pianocomm}

We have a new keyholder, iridium (CD) who will have a photo on the Rogues'
Gallary soon!  Also, Ducky Ben (DUK), who will also have a photo on the Rogues'
Gallary, and whose initials may also be shown as an image of a duck.

\subsection*{Mobcomm}

Mobcomm ordered another hundred books.

\subsection*{Picniccomm}

Picniccomm will be activated shortly.  There will be several of them.  And
then there will be a picnic!

\goto{Old Business}

A professor wrote a novel.

An administrator came to Quiche Cabal in Random Hall and admitted to reading
science fiction.  We need to capture them.

\goto{New Business}

Spring Break is a week away!

\goto{Future Business}

Tomorrow the year is 3066.  Congratulations, it is the future.

Three weeks from now, the year will be 2255.

Sweet!  MIT can finally travel through time!

In the future, it will be CPW, and there will be an Activities
Midway, and we might have a table.

Bananaward PASSES 2-0-1\ps.

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
