\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Vice and pseudoOnseck}
\newcommand{\meetingdate}{Friday, 1 June 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.0 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the minutes for being posted PASSES 13-0-10\ps.

\bing

\goto{Committee Reports}

\subsection*{Hasslecomm}

Hasslecomm work party in two weeks, on Saturday, 16 June!

\subsection*{pseudoMommycomm}

There will be cookies at the work party!

\subsection*{pseudoAnalogcomm}

The Summer Schedule starts in a week.  If you haven't sent your hours
in to Analogcomm yet, you should do so immediately.

\subsection*{Skinner}

Next week, meeting will be at 18:30 again.  This will become a restored
tradition, since 17:30 is apparently too early for people during the
summer.

\subsection*{pseudoSeldon}

There's a Seldon showing tonight!  We're going to start having these
more regularly again.

\goto{Old Business}

In the past, there was term.

In the past, there was exhaustion.

In the past, there were comic books.

In the past, the comic books migrated to California.

In the past, there was a person.

In the past, the person went skiing in Colorado.

And thus a programming language was born.

ALGOL


\goto{New Business}

In the present, people are lame.

But at least they are reading!  And there are a lot of them!


\goto{Future Business}

In the future maybe we can have meetings where people make motions?

In the future, maybe there will be bananas?

Or perhaps a dinner mob?

Motion to have a dinner mob to a restaurant where all the dishes
are made entirely of bananas PASSES 14-13-12\ps.


\bing
\noindent
Meeting adjourned, 64.8 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
