\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 27 January 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
Lemur Rowlands, pseudoSkinner, presiding; Lee Fuchs, pseudoOnseck, recording.

Minutes read.

Motion to commend the readings for being so detailed as to transport kkb back to the day such that she though the meeting was actually over PASSES 5-0-0 plus Spehn.

\bing

\goto{Committee Reports}

\subsection*{psuedoSkinner}

The gavel is a good tuning fork. We don't know what for, but it is.

\subsection*{Theftcomm}

There is a new TIF

\subsection*{kkb}

"If I have any committees, I abdicate and run far, far away... which won't work very well because MITSFS won't let me."

\subsection*{peudoPianocomm}

We have lots of prentices, they have been doing work.

We think that after pseudo-inventory there will be key-ings.

\subsection*{Mobcomm}
Finances are straightened out! And we are once again ordering books... faster than panthercomm can process them.

\subsection*{Bluebellcomm}

Bluebellcomm needs to do work.

\subsection*{Seldon}

There'll be a new schedule and showing next week.

\goto{Old Business}

There was Arisia and Mystery Hunt last week.

In the past, the dinosaurs roamed the earth.

Usual motion, usual second, usual debate, usual vote

\goto{New Business}

Usual query, why did the skinner allow the usual debate?

There is a Guild Game going, it is about people becoming gods and things. In New York. Only not so much anymore.

Newt Gingrich wants to go to the moon. This apparently violates some standing treaties that we have--which is currently to keep anyone other than government actors from doing things in space.

Motion to send Newt Gingrich to the moon:
Motion to commend Newt Gingrich as an SF writer fails by skinnerial decree

Motion to have a vote chickens and runs away with its head cut off because its so scared of itself 4-4-4 plus Spehn. It does not turn into the null set, or implode, or explode.

We got the most bizarre book around, according to armenard, called Taft 2012. Sadly, it seems to have been written to make bad fat jokes.

Motion that we collaboratively write a book in which Ben Franklin goes to the future to run for president on the platform that the banana planations in the south have got to go (finished and seconded by kkb):
4-0-confused:4- infused:0 - and the motion fails i - pi - e plus Spehn

Note that the pseudoOnseck doesn't know how to do those math symbols in LaTeX. Ooops.

\goto{Future Business}

Boskone's in the future! There will be a mob, people should come!

It's gonna be the future soon!

PseudoSkinner wants to go to England.

In the future we will have a spelling reform so that ough will be pronounced the same way?

Motion to reform spelling so that all pronunciations are obvious from their spelling, and such that 'bananas' are not confused by 'baanaanaas' or something? Fails for lack of a second.

Motion to condemn Andrew for not knowing whose banana motion is whose passes 8 - 4 - 1 plus Spehn.
\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Lee Fuchs, pseudoOnseck}

\end{document}
