\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Kaleb Ayalew, Vice and pseudoOnseck}
\newcommand{\meetingdate}{Friday, 23 March 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

"Wheee!!!" fails due to lack of a second.

\bing

\goto{Committee Reports}

\subsection*{Onseck}

The Onseck is lame and isn't here.

"Wheee!!!" passes 3-0-1\ps.

\subsection*{pseudoKvetchcomm}

We're going to get an Advanced Reading Copy of a book by one of our
favorite authors.  Yay!

\subsection*{pseudoPanthercomm}

We got one hundred new books!  They need processing!

\subsection*{Millercomm}

We're making adequate progress on destroying the universe.


\goto{Old Business}

In the past, it was midterms week.  Most people were dead.

\goto{New Business}

In the present, it is spring break.  At least for the undergrads.  But that
means they're alive again.  "The undergrads are zombies!  Run for the hills!"
fails by Skinnerial "BRAINS!".

\emph{Technology Review Science Fiction} is having a power-style interview
with SF author Neal Stephenson.  It's a public event and MITSFS  may help 
with publicity in exchange for free seats. 

The event is Tuesday, 17 April and called "A Long Evening with Neal Stephenson".
It's in 10-250.


\goto{Future Business}

"In the future we may see Neal Sephenson, and maybe we can give him bananas, or
maple syrup cotton candy." passes 1-0-0\ps.


\bing
\noindent
Meeting wimpily adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
