\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Vice and pseudoOnseck}
\newcommand{\meetingdate}{Friday, 22 June 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to approve the minutes as expedicious FAILS due to Skinnerial
apathy.

\bing

\goto{Committee Reports}

\subsection*{Theftcomm}

New TIF by the end of the weekend...

\subsection*{RealAuthorscomm}

John Scalzi visited last week as part of his \emph{Redshirts} tour, which
is why we didn't have a meeting.  He was very awesome and talked and signed
our copy of \emph{Redshirts}.


\subsection*{Downtrodden Membership}

There's a thing called the Clarion Write-a-Thon where you write words
or something and you can have people sponsor you or something and something
and the money goes to Clarion


\subsection*{Hasslecomm}

We had a work party, and got through most of the P backlog.  But we have
a whole bunch of HAs to hassle, and will need to have another work party
in the near future.


\subsection*{Star-Chamber}

We moved more books to the Warehouse.


\subsection*{pseudoMommycomm}

We got new prentices!  Multiple of them!


\subsection*{Oookcomm}

PW is having more trouble with the electronic checkout system, and may
need to reinstall postgres.


\subsection*{pseudoTrojan}

We might actually make progress soon: we have a meeting with the Gifts
Office.


\goto{Old Business}

In the past it was even hotter.

In the further past it was even colder.

In the even further past it was even hotter.

In the past, the cycle of the seasons has cycled many times before.

In the past, AW watched all of \emph{True Blood}, and it was good.

In the past, there was summer.  For some people, there still is.

In the past, days were getting longer.

ALGOL


\goto{New Business}

In the present, the days are getting shorter.

There is not a dinner mob in the present: no eating in the library!

There might be one in the near future?

In the present, the Skinner is tired and hungry.


\goto{Future Business}

Motion to eat bananas in the future PASSES by Skinnerial apathy.


\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
