\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 05 October 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 63.4 Ksec SST,
\skinner, presiding; \onseck, recording.


\bing

\goto{Committee Reports}

Mommycomm: There was a prentice party last weekend, where prentices did all the Bluebellcomm! There will also be another prentice party this Sunday from 2-6 again!

\bing

\goto{Old Business}

In the past maybe someone mentioned something about making a MITSFS award, but this sounds like work so is unlikely to continue in to the future. 

In the past it was an awful two weeks. But they're over.

\bing

\goto{New Business}

In the present it is no longer this week. 

In the present, alexwest has a paper due at midnight. 

\bing

\goto{Future Business}

In the future, we'll figure out how to merge the library. 

In the future, lknight will be in NYC visiting her parents, and alexwest's parents will be in Boston visitng.

In the future, there will be a banana sundae motion that will in the past have ended the meeting.

\bing
\noindent
Meeting adjourned, 66.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
