\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, President and Skinner}
\newcommand{\onseck}{Lemur Rowlands, Onseck}
\newcommand{\meetingdate}{Friday, 6 April 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\emph{The Apocalypse Codex}, by Charles Stross is too interesting
for the Skinner to bother to actually hold a meeting.

\bing

\goto{Committee Reports}

\subsection*{Star-Chamber}

Technology Review Science Fiction is having a power-style interview 
with SF author Neal Stephenson. It's a public event and MITSFS will 
help with publicity in exchange for free seats.

The event is Tuesday, 17 April from 16:00-17:30 and called 
"A Long Evening with Neal Stephenson". It's in 10-250. 

Email the Onseck (onseck@mit.edu) if you want to be added to the list
for free tickets.


\subsection*{RealAuthorsComm}

Elizabeth Bear and Scott Lynch will be visiting MITSFS on Wednesday,
25 April at 18:30.  We might take them out to dinner or something
afterwards.


\subsection*{pseudoTrojan and Star-Chamber}

We got a big fine credit donation recently, with a surprising
number of new-to-us books.  More work for Panthercomm!


\subsection*{Seldon}

Despite the short notice, we're in fact doing a showing today!
It will be awesome!  Emily Lydic even emailed us all the way
from Ohio to tell us it would be awesome!


\subsection*{pseudoKvetchcomm}

The new Laundry Files book, \emph{The Apocalypse Codex}, has
arrived!  Someone should write a review of it!


\goto{Old Business}

In the past, there was Spring Break.

In the past, people went to New York City.

In the past, New York City was the archetype of The City.


\goto{New Business}

In the present, there is PAX East this weekend.

In the present, there is Anime Boston this weekend.

In the present, the MBTA is opening an extra entrance
of the Hynes/Convention Center station to accomodate all
the extra geeks.


\goto{Future Business}

In the future there will be a picnic.

In the future \emph{The Apocalypse Codex} will be published.

In the future, Bob Howard will use bananas to prevent CODE
NIGHTMARE GREEN!

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
