\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Alex Westbrook, President and Skinner}
\newcommand{\onseck}{Laura McKnight, Onseck}
\newcommand{\meetingdate}{Friday, 29 June 2012}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.6 Ksec SST,
Lemur, Vice, presiding; \onseck, recording.

Minutes read.

Motion to condemn the reading of the minutes as profunctory PASSES 6-1-4\ps

\bing

\goto{Committee Reports}
\subsection*{TheftComm}
There is a new TIF, as promised.

\subsection*{Hasselcomm}
There will probably be an unexpected hasselcomm party this weekend.

\subsection*{pseudoSkinner}
The doorlock situation should be fixed, if you still can't get in, tell the skinner. Apparently the situation will get worse in the future.

\goto{Old Business}
In the past, the Onseck was hosed with a stupid workshop, and temporarily stopped existing.

In the past, a robot learned to beat people at rock paper scissors.

In the past, the summer solstice happened. 

Usual motion

\bing

\goto{New Business}

In the present, the library clock's sucks.

In the present, we have a copy of the GSC.

Motion to redact [redacted] PASSES by pseudoSkinnerial decree.

Nyah Nyah the future archeaologists who are trying to figure out what the redacted thing was.

The library then proceeded to time warp to the 26th century to tell those poor archaeologist what they were missing out on.

\goto{Future Business}
In the future, it will be the present, because we're currently in the 26th century.

In the local future, but the absolute past, there will be a dinner mob.

Motion to return to the 21st century CHICKENS, leaving the library permanently stuck in a state of ambiguous temporal locality.

Motion to in the future acquire a large number of sharkbananas because unlike our current stuffed animals they'd be good for gaurd duty PASSES 7-2-2\ps

\bing
\noindent
Meeting adjourned, 68.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
