\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 23, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion passes to approve the minutes as zaftig.

\goto{Committee Reports}

Boardcomm raves. The board's beautiful.

Moocomm: Watership Down's the LSC movie. It could be worse.

\goto{Old Business}

Null.

Algol- usual motion... etc.

\goto{New Business}

Minicult: Former Onseck is suspected of stealing women's underwear. The complaintant has a lousy height and weight sense. (See other side of page.)

Motion passes to have Ken donate his underwear collection to the Library.

Someone came in and got scared away and left at this point.

Minicult: A famous Swiss artist (a la Alien) was in the Coop. His newest work is New York City- now that's gross and strange and alien.

Motion flounders to get a waterbed crib for the Library.

Minicult: The shuttle's on pseudo-schedule again.

Miller motion 1 chickens.

Ken may sound silly at any time now.

Minicult: In the fall, 1 out of 10 grouse go insane and fly about bizarrely. A moment of silence- albeit a brief one- ensued.

Motion to find out who the hell Frank Harris is. He seems to be dead about now.

Motion passes to say we need a motion involving a banana.

\vspace{12pt}

\noindent
Meeting adjourned, 17:26 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

Attached: Former Onseck, may he rest in peace. [Short article with composite sketch about suspect in "the rash of recent campus underwear thefts."]

\end{document}