\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 20, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
E. Carl Hylin, President and Skinner, presiding.

Minutes of the minutes of the minutes of the meeting of the MITSFS read by the Onseck and amended.

Minutes approved as liquid paper white. Chickens 3-2-6 +Spehn.

\goto{Committee Reports}

(KM) Pseudo-Picniccomm: Tasteful letter, epitomy of tasteful writing. Attached.

(KM) Boredcomm: I resign.

Pseudo-Boredcomm: MITSFS sign removed again.

Pseudo-Boredcomm 2: New ideas in the making.

Timewarp to last curse on bulletin board. Curse amended to curse all unauthorized personnel adding or deleting articles of any sort in any spare time.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

(KM) Minicult: MITSFS famous for lack of space with Boston N.O.W.

Minicult: El Salvador "textbook" case of communism aggression, from NY Times.

(Malcolm) Minicult: Knights of Malta (ca. 1412) were filthy rich. Pope and king of France wanted money and tried to disband them- Malta condemned and cursed them. Both died. Succession troubles left both without leaders for several years.

Move to commend Malcolm for the oldest Minicult. Passes by acclamation.

Members present have not voted. Said individuals condemned to eat with John Costello alone in Lobdell on commons.

Timewarp- (Malcolm) Starcrossedcomm: 38 has Sleeper at 8 PM- end timewarp.

Finger motion to condemn skinner. Overruled.

Motion to commend Carl for his banana-colored shirt. Myriads (really 4)-1-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1731 SST.

\vspace{18pt}

\centerline{Ken Meltsner, Onseck}

\end{document}