\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 24, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
E. Carl Hylin, President and Skinner, presiding.

Move to approve the minutes as crimson. Passes 6-1-2 +Spehn.

\goto{Committee Reports}

Picniccomm: Picnic May 10, election meeting May 1. (Total cost so far- 3.55.)

(Chip) Whooshcomm: You should have heard the whoosh the shuttle made- outdoes any whoosh.

\goto{Old Business}

OBA, the usual flush.

\goto{New Business}

(Chip) Minicult: 1) Condemn former skinner and onseck for attempting to be respectable. 2) Condemn science for having Consolmagno. 3) Appoint a committee to find out what the University of Arizona is feeding I.T. Lapeer or to what they are feeding him.

Matrix motion: 4-2-1 +Spehn, 7-4-8 +Spehn, 8-23-7 +Spehn. All fail. Finger motion passes.

(Starr) Minicult: To congratulate Excalibur ad for spelling it "Excaliber." Passes many-0-3 +Spehn.

We recognize Armenia- passes by decree.

Mazeltov.

Miller motion fails.

Miller motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 17:38 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Ken Meltsner, Onseck}

Attached: Excalibur ad, picnic invitation.

\end{document}