\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 8, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion to thank the Onseck for reading minutes. Rubber stamped. (This means pass, by the way.)

Motion to accept minutes as Wendy's hair. Rubber stamped.

(Hi there... you don't know me, but I'm the new scribbler here. So, bear with me (or without me, if you prefer). I'll get the hang of it. Maybe, someday- if you all believe, and clap your hand real hard...)

\goto{Committee Reports}

Pseudo-Picniccomm didn't have much to say- no one real's coming.

Albanian motions are discussed, but to no avail.

The chair was overturned and kicked out at this point.

\goto{New Business}

Minicult: 1) Depressingly macabre and morbid divorce story. 2) Discussion of unicorn breeding.

Miller motion? What's a Miller motion? (Finger motion.) And why's Chip talking Albanian- who can understand him??

Something happened to Miller motion 1.

Miller motion 2 was a tie, but it was broken. (Funny, it didn't look broken...)

\vspace{12pt}

\noindent
Everything stopped at 17:23 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}