\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 6, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion chickens to approve minutes as flattened. That's an incredibly dull motion.

\goto{Committee Reports}

Moocomm: Popeye will be eating spinach on the silver screen Saturday.

Miller motion 1 fails.

Miller motion 2 fails.

Our eternal member was in attendance.

\goto{Old Business}

No old business.

Old Business Algol- S.O.S.

\goto{New Business}

Minicult: Ken barked. The Shuttle didn't go. The Detroit News published an advanced article praising its flawless launch.

Motion passes to move author of Shuttle article "Columbia Does Encore" to the appropriate alternate universe where Dewey won for president.

Motion chickens to have MITSFS buy an ad on the 21-cent stamp- probably coming out any day now.

Our lifelong member may not be a member much longer if he persists in voting with all limbs simultaneously, losing contact with local surface of lowest potential energy.

Motion passes that we still need a motion containing a banana.

\vspace{12pt}

\noindent
Meeting adjourned, 17:23 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

P.S. The article about the article about the shuttle is enclosed.

\end{document}