\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 1, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order by the once and past Skinner, 1700 SST,
E. Carl Hylin, President and Skinner, presiding.

Minutes suspended due to lack of Onseck.

\goto{Committee Reports}

Picniccomm: Only one car so far- 2 or 3 people if they're small.

No other committees (by definition).

\goto{Old Business}

OBA, UM, US, UV and R.

\goto{New Business}

Elections (oh, boy).

President:

Nominations: Guy Consolmagno, Woodstock, Cheryl Tiegs, winner (2 rounds): Cheryl Wheeler (I think).

Vice:

Nominations: LHE's camera, Cheryl's studded leather belt, elephants, Xaviera Hollander, winner (3 rounds): Adina Adler.

LHE:

Nominations: J. Paul Getty, Woodstock, Cheryl's belt, winner (2 rounds): Judy Passman.

Onseck:

Nominations: The Book, the Belt, the Candle, winner (1 round): Wendy Rowe.

Official Second: Cheryl's studded leather belt.

Alright- I'm in charge here!!

New Star Chamber in effect, with Cheryl as Skinner!

\vspace{12pt}

\noindent
Meeting adjourned, 18:30 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Ken Meltsner, Onseck}

\end{document}