\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 11, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion passes, under protest, to approve minutes as much less green than Wendy's freckles.

\goto{Committee Reports}

Moocomm: Warners was grossed out that LSC had its greasy hands on Superman II.

Boardcomm: Ken Meltsner gloated over his purty new sign.

\goto{Old Business}

The usual.

\goto{New Business}

The Green building hasn't fallen down yet. And two lovesick refrigerators haven't jumped off it yet.

Said Ken, re: using an organ pipe to knock down the Green building: "Ah, that's just a pipe dream." Groans. Alan is Organcomm. He is reminded to bring his organ to the next meeting.

Steve Starnofsky moves over the phone that Bill Starr's nose be replaced by a banana. The motion chickens 0-0-n>3 +Spehn.

The Skinner edicts that the entire room be censured for apathy. But who cares.

Motion passes chickenless to commend Boardcomm on tasteful banana paper.

\vspace{12pt}

\noindent
Meeting adjourned, 17:12 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}