\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 30, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion passes to approve minutes as 37 seconds.

\goto{Committee Reports}

Libcomm commends the production of Z. Link and Daily Reaver (a doubleheader).

Boardcomm: Motion passes to condemn Ken for boring office board.

\goto{Old Business}

No old business.

Old Business Algol- Motion passes to define the scone motion. 37th seconded.

\goto{New Business}

Minicult: Glob reported a police helicopter nearly shot down by laser. It was accidental, though- just a random with a laser for Halloween.

Pseudo-Moocomm: Stand and Dead Zone may be released at the end of the year (inside sources report...). Creep Show's coming too, eventually.

Minicult: Garfield's new book is out, as is Doonesbury's In Search of Reagan's Brain. The latter shall be considered fantasy if said brain is found.

A hockey stick was unshelved at this point. (Oops! The meeting was adjourned at this point.)

Motion passes to get a lucite block for the replacement office banana.

\vspace{12pt}

\noindent
Meeting adjourned, 17:24 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}