\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 20, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
E. Carl Hylin, President and Skinner, presiding.

Minutes read by the Onseck.

Minutes corrected.

Minutes have no motions concerning them.

\goto{Committee Reports}

Pencomm: My pen died.

Jourcomm: RSN.

Pseudo-Jourcomm: Elise sold some TZs, gasp!

(KM) Starcrossedcomm: Memory lapse.

(KM) Pseudo-Picniccomm: Picnic on May 10- Asimov replied.

(KM) Moocomm: Mary Poppins.

(Starr) Pseudo-Moocomm: Final Conflict: Damien vs. Son o' God (3 falls takes all)- with a "real" actor.

Coofcomm: Former keyholder (Larry Lenhoff) is present; phantomized for break.

\goto{Old Business}

OBA: um, us, uv, ur.

(Great amazement that we have our gavel block back?!)

\goto{New Business}

(KM) Move to belabor all the twits sitting around ignoring the meeting with a banana on the head, shoulders, and other body areas. All-3-3 +Spehn (I-aiii!-squawk), passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1713 SST.

\vspace{18pt}

\centerline{Respectfully,}
\centerline{Ken Meltsner, Onseck}

\end{document}