\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 10, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
E. Carl Hylin, President and Skinner, presiding.

Minutes read by the Onseck.

(Bob) Motion to declare the minutes as banana colored. Out of order.

(Bob) Move to approve minutes as red. Out of order.

Move to approve minutes as chartreuse. 3-4-7 +Spehn.

\goto{Committee Reports}

(MALT) Pseudo-Moocomm: Star Wars at Charles.

(MALT) Pseudo-Moocomm 2: Earthbound very funny.

(MALT) Pseudo-Moocomm 3: Metropolis tonight.

(MALT) Pseudo-Moocomm 4: Animal Farm Sunday.

(MALT) Pseudo-Moocomm 5: Star Wars non-theatrical release in the fall.

(MALT) Randomcomm: I Scream Clone is interesting.

Discussion of what to call committee about plays.

Pseudo-Picniccomm: Invite famous types. Onseck wants addresses.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

(KM) Minicult: Shuttle feebles again!

Minicult (by order of Skinner, not a Microcult): Read Bloom County!

Minicult: Skinner's floor had a strawberry daiquiri party to commemorate 6:50 AM liftoff.

Move to commemorate shuttle launching on Sunday with banana daiquiri and hashish smoking party. 9-0-0 +Spehn.

Finger motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Ken Meltsner, Onseck}

\end{document}