\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 13, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
E. Carl Hylin, President and Skinner, presiding.

Whole Star Chamber is here, as is Bill Starr.

Minutes read.

Motion to move Bill to a chamber. 4-2-3 +Spehn, passes by a tie.

(MALT) Mooncomm: Catholics don't exist.

Move to approve minutes as ordinal, not cardinal. 4-1-2 +Spehn, passes.

\goto{Committee Reports}

(KM) Starcrossedcomm: Gunsmoke is the Buck Rogers of the past.

(MALT) Throgcomm: "I don't always show my legs off."

(MALT) Moocomm: George Lazenby as Bond in On Her Majesty's Secret Service.

\goto{Old Business}

OBA: um, uv, ur.

\goto{New Business}

(Starr) Autographcomm: Nice signed picture of Jittlov.

(Starr) Minicult: Boston Herald says San Francisco coroner is holding workshops on S&M safety in gay community of SF. Attached.

Move to fail to reimburse Bill Starr for Jittlov autograph (1 dollar). 3-0-1 +Spehn, passes.

Great confusion on what we wanted to do and how to do it.

Finger motion on all of you twits.

Move to impeach Skinner. Out of order.

Previous motion for reimbursement passes and fails.

(MALT) Move to Hoboken. Nope.

(MALT) Move to Tulsa. Yech!

Move to condemn the cast and crew, etc. (this means you, MALT) of the Tech Show for their intimate involvement with the MITSFS banana. Many-1-? +Spehn, passes.

\vspace{12pt}

\noindent
Meeting adjourned, 17whatever SST.

\vspace{18pt}

\centerline{Respectfully,}
\centerline{Ken Meltsner, Onseck}

\end{document}