\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 4, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Making his dubiously triumphant return as pseudo-Onseck! (Who?)

The meeting commenced at 5 PM SST,
Cheryl Wheeler, President and Skinner, presiding.

Move to approve minutes as pseudo-read. Passed at 6-pseudo-Onseck-5 +Spehn.

\goto{Committee Reports}

ASAcomm: The Skinner attended an extremely dull ASA meeting (even more dull than this meeting?) at which Sam Austin and Arnold Contreras were elected President and Treasurer of the ASA.

\goto{Old Business}

T'weren't none.

Old Business Algol- the process followed its usual standard of usualness.

\goto{New Business}

(Flynn) Pseudo-Moocomm: Flynn saw "The Creature from the Black Lagoon" at the Science Museum.

The Skinner (or her name) appeared in Tuesday's Tech ad for the 1982 Who's Who Among Students in American Universities and Colleges; she disclaims knowledge of any of this.

(Adler) Pseudo-Pseudo-Moocomm: LSC continues its fine tradition of science fiction movies on Wednesday nights during IAP.

Starr started griping about the lassitude of contemporary meetings: "No Goldberg, no Bernstein, no Spofford..."

(g) Move to relocate Spofford to the library.

(Starr) Amended to place him alongside "The Apotheosis of Feelthy Pierre." Passed at 9-0-6 +Spehn.

(Starr) Minicult: According to this week's TV Guide, NBC paid about 20 million to show Star Wars three times, beginning around late 1983.

(Starr) Sitcomm: A documentary on The Making of Raiders of the Lost Ark will be on PBS tomorrow night.

(g) Move to note that the ventilation system in the library is now a full semitone flat. Chickened out at 3-1-N>10 +Spehn.

Starr mentioned his receipt of mail from Jerry Falwell and still had a business reply envelope address to Lynchburg, VA.

It was moved and amended to send Jerry a radioactive lead banana with a half-life long enough to survive transit through the U.S. Mail, passed at 9-2-4 +Spehn.

\vspace{12pt}

\noindent
It was all over at 1726.

\vspace{18pt}

\centerline{Eternally submitted,}
\centerline{Gregory James Ruffa ('74, former Onseck, former Vice, and still former pseudo-Onseck)}

\end{document}