\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 9, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion passes to approve minutes as hot pink and lime green in honor of the preppie who's going to speak downstairs.

\goto{Committee Reports}

Moocomm: A pseudo-Monty Python movie was sneak previewed. Time Bandits is its name- includes 2 Pythoners (John Cleese, Michael Palin) and Sean Connery.

Boardcomm: Will do things soon. Ken needs the key.

Motion to commend the sender for sending us a box of the lightest reading in 8 years.

A discussion of the maliciousness of gavels commenced. Many motions writhed together while in the throes of death, disinterestedly.

\goto{Old Business}

Chip moved to define the current motion. Also dies disinterestedly.

Old Business Algol- the usual et. al.

\goto{New Business}

Minicult: A discussion of bananas was postponed.

Motion passes to commend Bloom County's artist for using bananas in interesting ways.

\vspace{12pt}

\noindent
Meeting adjusted, 17:19 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}