\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 25, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion passes to approve minutes as incarnadine.

\goto{Committee Reports}

Boredcomm: They put glass on the board and confused Ken. But our key opens all three cabinets.

An uncommitteed Josh reports he's not on any committee.

\goto{Old Business}

There's nothing like it.

Old Business Algol- the usual. Finger motion occurred for asking when it happened.

\goto{New Business}

Minicult: George Dome is thinking of getting a tentacular blue toupe. He's going punk.

Sky Art is happening.

Motion moved and passed (n>>1) to get contingency plan to move the blue pseudo-octopus onto George Dome.

Motion failed to rival Sky Art and Visual Studies with a banana.

Miller motion 1 chickens.

Miller motion 2 dies for lack of interest.

Obscene motion fails.

A long, boring pause followed, incredibly apathetically.

Miller motion 2 reincarnated passed with a broken tie.

\vspace{12pt}

\noindent
Meeting adjourned, 17:14 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}