\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 16, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion passes to approve minutes as 1.67 percent of an hour each.

\goto{Committee Reports}

Boardcomm finally got its act and key together.

Commcomm: Steve Straussman volunteers to be Bloomcomm. He says he'll read next week's Glob after dinner. That should be pretty hard to do- maybe he should look at next week's sports results while he's at it.

Organcomm: Strict mechanical stimulation works best.

\goto{Old Business}

Motion chickens to define gavels as unmalicious if not provoked. But it almost passed. And it was a good one, too. It DESERVED to pass. Really it did. The poor motion is going to have a complex. So's the Onseck, who invented this downtrodden and rejected motion. Just wait til, someday, an undefined, yet unprovoked and malicious gavel attacks. THEN you'll be sorry.

There was a demonstration of a finger motion, so we'd be in practice.

\goto{New Business}

Gorbookmarkcomm: We've got lots of cover illustration bookmarks. We've got them because the bookstore dealer can't get rid of them fast enough. Our supplier said he asked for them, but he had a reason.

The peanut gallery replied, "I'm just a pimp- I don't use the stuff!"

Finger motion to Steve Straussman for being confused- lucky we were in practice!

Motion passes infinity-epsilon-1 +Spehn in favor of condemning Ken Johnson for smashing the office banana into many small pieces.

\vspace{12pt}

\noindent
Meeting adjourned, 17:19 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

Attached: Guardsman of Gor promotional bookmark. [Front: illustration of voluptuous woman in scant clothing, rear: book info with tagline "Will Jason Marshall find the means to wrest the girl he seeks from bondage?"] Maybe she doesn't want to be wrested from bondage...

\end{document}