\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 2, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Someone applauded minutely.

Motion passed to approve minutes as sea mint green.

Motion passed to censure members for only voting once. Passes recursively.

\goto{Old Business}

There is no old business.

Algol- usual motion, usual second, usual vote, outcome, and result.

\goto{New Business}

The Onseck respectfully submits the missingness of something about a book and a movie.

Minicult: Harlan Ellison is suing 1984, a magazine, for plagiarism.

Minicult: Shock Treatment, the Rocky Horror sequel, has hit Boston. The saga of Brad and Janet lives on.

Motion chickens to commend Larry Lenhoff for becoming a keyholder for the 3rd time.

A motion about Miller skiing for a long, long time died for lack of interest.

Motion passed to get more interesting people at meetings by threatening them with a banana.

\vspace{12pt}

\noindent
Meeting adjourned, 17:16 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}