\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 11, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion chickens to approve minutes as legible and the Onseck as illiggillbe (or illegible, whichever you prefer).

\goto{Committee Reports}

No committees present and reporting.

\goto{Old Business}

There was no old business.

Old Business Algol did its thing.

\goto{New Business}

Pseudo-Bloomcomm: Bloom County was subtle, but cute. (Included here for the honorable and distinguished membership to honorably and distinguishably read.)

Moocomm: And Now for Something Completely Different is Saturday night.

Miller motion 1. 1 funny noise-1-3 +Spehn.

Spehn is a country in Europe, near Portugal.

Generic SF is available now at a grocery store near you.

I'm sorry, I don't believe people can censure themselves for not voting and then not vote. Must've been in some other universe.

Miller motion 2 fails again... damn, damn, damn. Gosh darnit gee willikers!

A mouse motions to cross the office. Passes.

Motion to set a mouse trap using a banana as bait. Passes 5+"Oy" (with feeling)-some-some other +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:27 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

Addendum to minutes: 17:43 SST, 12/11/81, correction to previous week's minutes. [Attached article on CBS paying 20 million to show Star Wars three times.] -CW

\end{document}