\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 20, 1981

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion chickens to approve minutes as just as dull and lackluster as the meeting was.

\goto{Committee Reports}

Moocomm: Everyone's least favorite fantasy movie, L.O.T. Rings, is being shown by LSC (without even benefit of our favorite 4th Wester and his rat). And the finders (about 8 of them) of the L.O.T.R. LSC ring hunt found it in a lamppost near the bushes in front of President Gray's house. They were stopped by suspicious CPs.

Minicult: The best street cleaning in Boston in the past n years was done by last week's rain.

\goto{Old Business}

No old business.

Old Business Algol- the usual (motion second vote outcome result).

\goto{New Business}

Motion to have the Skinner not send a spaceship not shaped like a banana and not containing Arnold Contreras on an exploratory mission not to Andromeda. 29-1-1 +Spehn, passes!

\vspace{12pt}

\noindent
Meeting adjourned, 1716 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}