\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

July 26th, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, July 26th, 1991,
1700 SST, Derrick Kong, Skinner and President presiding.

(P) Motion to approve your gavel as a banana.

(JM) I have to read the minutes first.

(P) No you don't.

(JM) Yes I do, dammit, you know how long I spent last night typing these
suckers up?

(DK) Read the minutes.

(Minutes are read.  They are far too long.  Also they are incoherent.)

(DK) Motions concerning the minutes.

(silence)

(JM) No.

(DK) I'll take that as a motion!

Motion fails 0 to 2 to 0 plus Spehn.

(?) Motion to make this meeting last forever.

Motion fails by Skinnerial decree.

(?) Motion to end the meeting.

Motion passes 1 to 0 to 0 plus Spehn.

(JM) Now all we have to do is adjourn the meeting.

(DK) Right.

(DK) Are we going to end this stupid thing?  Does anyone have anything
to say?

(JM) No.  I feel that I can't make a motion about my own minutes.
Someone else stop it.

(P) No, I'm just going to let the meeting go on forever.

This section ended by Whooshcom.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(JM) The situation with the lack of shelves is getting really pathetic.

(DK) Yes, I know, I know.  They're coming.  When they'll get here is
another story.

(P) They're not even breathing hard.

(DK) Yeah.  Right.  Anyone want to end this meeting?

(JM) Miller motion.

Motions fails.

(JM) Second Miller motion.

Motion passes 1 to .9 or so to .01 plus Spehn.

Meeting adjourns 1705 SST.

\vspace{0.15in}
\begin{center}
Doing the minutes out of order,

Jamie Morris, Onseck
\end{center}
\end{document}
