\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

April 5th, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, April 5th, 1991,
1700 SST, Derrick Kong, LHE and Pseudo-Skinner presiding.

(someone) Motion to approve the minutes as tentative.

Motion fails 3 to 11 to 4 plus Spehn.

(S G) Motion to approve the minutes as red haired.

(S G) Motion to approve the minutes as no fun.

Motion passes lots to 2 to not quite enough plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(WDS) Sitcomm, Denise Crosby showed up on {\em The Flash\/} last week acting
like Denise Crosby.

(S G) Motion to commend the MobComm for his grammar.

Motion passes lots to 4 to 1 plus Spehn.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(WDS) Nimoy had his 60th birtday only a few days after Shatner's.

(S G) Passover is almost over.

USUAL.

BING.

USUAL tickling of pseudo-Skinner.

RAVS.

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(S G) MiniCult --- there is a {\em Daily Reamer\/} for the first time in a
decade.

(WDS) I found out how to get a lot of mail --- I posted a question to
rec.arts.tv about the answer to a Final Jeopardy question.

There is some kind of banana motion.

Motion chickens 6 to somewhat under six to lots of chickens plus Spehn.

Another banana motion.

Motion passes 7 to 6 to 3 plus Spehn.

Meeting adjourns 1712 SST.

\vspace{0.15in}
\begin{center}
Scoot over,

Robert Poole, Onseck
\end{center}
\end{document}
