\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

May 17th, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, May 17th, 1991,
1700 SST, Derrick Kong, Skinner and President presiding.

(HM) Miller motion!

(DK) EHHHHHHH! Fails.

(DK) We have no minutes.  The minutes were very soggy last night and
they haven't dried out yet.  Motions concerning the minutes?

(someone) Motion to have the motions stripped, washed, and sent to my
tent.

(two someones) Second!

Motion passes 7 to 1 to 3 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(various people) things that were too quiet for Tarl to quite catch.
something about someone's advisor.

(B?) Sitcomm, Knight Rider 2000 Sunday 9 pm.

(DK) Awww.  I don't even want to ask.

(B?) It's set in the year 2000.  A futuristic spinoff of the original
(something) series.  Same cast.  It's still the voice of William
Daniels, that's the only thing that matters.

(DK) Greeeat.

(SG) Does this have like a plot?

(B?) Probably not.

(someone saying something)

(DK) PseudoPicnicComm.  The picnic was nice.  My allergies were
horrible but otherwise it went pretty well.  It didn't rain.  It was
nice and sunny.  We had more than enough food.

(?) Ken and Janice made it.  They saw the ???

(B?) Oh, Bostone weekend?

(?) Yes.

(B?) Uh, we had a gavel toss?

(DK) Yes, we had a gavel toss.

(?) Even remembered to bring the gavels.

(B?) Not bad.  Did anybody win?

(DK) Yes.

(?) Who?

(DK) No, guess.

(?) Boskone weekend.

(?) No, we were going to toss Boskone weekend

(DK) but Ken and Janice objected, so.

(?) A fine idea.

(M?) I don't know, she got downright upset, it was very strange.

(DK) Yeah.  Ya know, (something)

(something)

(?) Me?

(DK) Except for you!

(B?) I don't know, I don't pay attention.  Usually by the time the
competition is over I'm too busy thinking of my arm going to fall off
to really worry about-

(?) But it never fell off, did it?

(B?) No.

(?) You weren't throwing hard enough, then.

(something)

(B?) Hal Clement.

(DK) Not that old!

(B?) Bully Desmond?

(something)

(R?) The Skinner is a fink!

(?) Isn't that in the old business algol?

(many people) Second.

Motion fails.

(?) I've made my reservation for Seattle.

(DK) Ah, that's good, when is it?

(?) Um, June 15th, I'm going to leave on June 15th and come back on July
27th.

(?) You reserved the whole city?

(?) No, I reserved a space on continetal airlines.

(B?) Can't.  You have to work thru Jeff Meyers to reserve the whole
city.

(?) You can, however, reserve Disney World.

(?) Michael Jackson did it.

(?) This is nowhere near Disneyworld.

(?) That's what I want to know.  How much did it cost?

(B?) You can reserve judgement.

(?) It's somewhere in the 100's..

(DK) That's it?

(?) That's it, huh?

laughter

(?) I've got it right here in my pocket!

(DK) No, seriously, I mean how much do you think it takes in on a single
operating day in the summer?

(something)

(DK) Yeah, but think about the number of visitors and how much it costs.
I would have thought they'd have taken in more than that.  I would have
thought around maybe you know millions.  30 million or so.

(B?) Does that include the (?).

(DK) Possibly.

(B?) The quality of the animation is going down over the years slowly.
All the good artists are doing 100-dollar bills.

(DK) Any other old business?

(?) And they move, too.

USUAL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(something)

(DK) I'll second that.

laughter

(?) Do you _want_ the job?

(DK) No, I just made someone else Skinner.  As the Skinner I have the
power.

(?) Can you Pass this motion by Skinnerial decree?

(?) SubSkinner?

(DK) Yes, I'll subcontract.

laughter

(DK) Any new business?

(B?) Um, we finally got our own copy of the third book in The Fionavar
Tapestry.  (something) And no longer will people get hooked on the first
two books of the series then be forced to sit here reading our SFWA
copy!

(?) Um, there was some Sitcomm. (something).  foocom this week.  You
know.  It was something that (something).

(something)

(B?) Hey, did anyone ever record that Kevin P. Revoll died?

(?) No, (something).  Among other things he was the guy who shrunk
MITSFS' valence.  He was a 7 foot 4 scientist, you can, he would rarely
play basketball, he got really sick of it, so he decided to figure out a
way to make himself shrink.  Only he overdid it a little bit and now he
can shrink down to 7 inches tall.  And has to like wear his clothes
don't shrink with him so ended up having to buy Michael Jackson doll
costumes.  He was terribly upset about.

(B?) Also he's the fellow who decided to (something).

(?) Oh really?

(B?) And I think he was also the guy inside the predator.

(?) Not bad, not bad.  Um, I mean, Harry and the Hendersons, you know,
it's a kids' movie, but, you know, one of the things, it's hard to
act well with a nonstupid role inside a costume.  And for that he did
a fairly good job.

(something)

(?) Ah, that's an English job.  But once again, you know, sometimes it
makes all the difference  for a movie.  Whether or not it's believeable,
whether or not things would work for it or not.

(something)

(?) Yes, I know, I'm glad about that, cause I was thinking about what I
was going to have to say would be continental ticket takers when I went
to pick up my ticket.  I mean, I made my reservation which is you can't
break a I mean you're out all your money-

(?) You really canceled for that?

(?) Well, if I had had a choice, I would have canceled.

(?) Make an exception for (something).

(?) I was thinking about you know calling them in advance and saying
you know I'm not going to be wearing makeup and you know if you have
to put me in a special area of the plane you know I just want to warn
you in advance.  

(?) Somebody pointed out that they should make the bald women (?).

(?) Shatner factor?

(?) (?)

(DK) Any other new business?

(something)

(?) Motion to commend the Skinner for having a ??? gavel ??? moment
of inertia.

(?) What?

(?) Second.

(B?) In the year 2000.

Motion passes 9 to 1 to a few plus Spehn.

bonk.

\vspace{0.15in}
\begin{center}
Actually doing minutes,

Jamie Morris, Onseck
\end{center}
\end{document}
