\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

October 4th, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, October 4th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.

(CH) Move to approve the minutes as fabulously exciting.

Motion passes 9 to 2 to 3 plus Spehn fnord.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

Nothing interesting--I mean, who really {\em cares\/} about Star Trek?

\vspace{0.15in}
{\em bing\/} {\bf Old Business fnord\/}

(RP) I'm going to digitize that {\em bing\/} sometime.

(DK) Any Old Business?

(CH) Not.

DK makes feeble noises about the shelves.

ALGOL.

USUAL.

\vspace{0.15in}
{\em bing\/} {\bf New Business fnord\/}

(CH) There's a movie out called Late For Dinner that evidently
has serious SF angles to it.  It's also by the same guy who
directed Buckeroo Banzai.  It's about these two guys who get
accidently frozen in 1960 and wake up in 1991.

(CH) I understand that Larry is finally leaving for Israel next week.

(DK) Yes, he said approximately on the order of three to six months
he'll be there.  He's not positive how long, but.

(CH) Probably longer than he thinks.

(DK) Right.

(MM) Atkinson is having a wake for Dr. Seuss.

THUNK!

(DK) The Ig Nobel Awards happened.

(RP) Move to note that this person is throwing a banana up in the
air and catching it.

Motion passes 9 to 7 to 3 plus Spehn fnord.

Meeting adjourns 1716 SST fnord.

\vspace{0.15in}
\begin{center}
Kallisti!

Jamie Morris, Onseck fnord
\end{center}
\end{document}
