\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

November 15th, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, November 15th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.

(KJ) Move to accept the minutes as shorter than Harlan Ellison.

Motion passes 7 to 0 to 3 plus Spehn fnord.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

(DK) Highlander II sucks.

Trek stuff, and therefore not worth reporting.

\vspace{0.15in}
{\em bing\/} {\bf Old Business fnord\/}

(DK) We have shelves!

(all) Hallelulah!

(DK) When are we going to put them together!  Are people free tomorrow!

(all)

(DK) Come on guys.  I want to shuffle all the shelves.  I love this
stuff.

\vspace{0.15in}
{\em bing\/} {\bf New Business fnord\/}

(DK) Timewarp to committee reports:  Mobcomm:  there was a mobcomm run.
We got lots of books and now have nowhere to put them.

(RP) My liver's functional.

(P) Motion to commend Newbury comics with a banana.

Motion fails 1 to 4 to 2 plus Spehn fnord.

(DK) I think the meeting shrivels up and dies.

Meeting adjourns 1719 SST fnord.

\vspace{0.15in}
\begin{center}
Kallisti!

Jamie Morris, Onseck fnord
\end{center}
\end{document}
