\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

March 1st, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, March 1st, 1991,
1700 SST, John Conger, President and Skinner presiding.

(MSY) Move to approve the minutes as pastel pink because they weren't
completely read.  (Heh.)

Motion passes 7 to 1 to 4 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(JCC) MobComm --- Tomorrow at 10:00, Adina will be here to pick up people to
go on the N.~E.~Mobile run.

(DKK) Whooshcomm --- {\em Discovery\/} was pulled off the pad because its doors
have cracks in the hinges.

(S G) Rosfap report --- Three SF related classes will be taught by me to
local HS students under auspices of the MIT ESP.

Lots of flaming about whether it is a good thing to have lots of local
High School kids touring {\sc MITSFS}.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(JCC) Got a note from Brian Knight, says he used to be a keyholder.  Left us
a donation of \$50.  Says he still has his key.  We should write him a letter
for the donation.

ALGOL mubles the USUAL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(S T) {\em BladeRunner\/} is this weekend.

(C H) I saw {\em Silence of the Lambs\/} this past weekend, and it is damn
good.

(S G) Minicult --- Penn and Teller are here.  Go see them.

(MSY) Minicult --- In the {\em Globe\/}, there was a woman who wanted to give
her cat a belated present of a video called ``Video Cat Nap,'' and she said
she couldn't find it anywhere.

(JCC) There is a motion on the floor to make a video to entertain bananas.

Motion passes 14 to 4 to 2 plus Spehn.

Meeting adjourns 1716 SST.

\vspace{0.15in}
\begin{center}
The narc was here to pay his fine,

Robert Poole, Onseck
\end{center}
\end{document}
