\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

March 8th, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, March 8th, 1991,
1700 SST, John Conger, President and Skinner presiding.

(S G) Motion to approve the minutes as traditional.

Motion fails 6 to 7 to 3 plus Spehn.

(S G) Motion to approve the minutes as drugged.

(KRJ) These are the minutes.  These are the minutes on drugs\ldots

(RPP) {\em I'll\/} second that!

(DKK) Motion for a matrix vote.

(JCC) No!

Ken's motion passes 10 to 1 to 1 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(S G) Rosfap report --- The drug crazed urchins, er, I mean the local high
school students in my SF class toured the {\sc MITSFS}.  One of them bought a
one year membership, another is going to buy a one year membership, so there.
Nyeah.

(JCC) OK, that'll pay for the books they stole\ldots

(RPP) Sitcomm --- I heard {\em Twin Peaks\/} is back on the air.  Also a
Moocomm, {\em Predator 2\/} tonight at LSC.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(JCC) People keep telling me to make it quiet and make it short.

(Raucous laughter.)

(new person)  (Something about changing the lock on the door, and issuing keys
only to keyholders who keep their hours.)

(JCC) We bought too many books at New England Mobile.

(DKK) We have more money now.

(S G) Motion to rotate real business ninety degrees.

Motion passes lots to not enough to almost no one plus Spehn.

ALGOL, SNOBOL, COBOL, FORTRAN, PASCAL\ldots

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(JCC) We got a birth notice --- Ken and Janice's kid was born, named William
Gregory Meltsner.  Born February 15th, 1991, seven pounds, thirteen ounces.

(WDS) (Something about Boskone Weekend Meltsner.)

(JCC) (Something about the endowment fund, and a guy who is calling and asking
if we use it, and the hope of possibly milking more money from this guy.)

(WDS) Move to end the meeting.

Motion passes lots to two to a few plus Spehn.

(JCC) I guess the meeting is ended, now anyone want to adjourn?

First Miller motion fails.

Second Miller motion fails!  Oh, no!

(Seth sings ``Rabbits Have no Tails at All.'')

Second second Miller motion passes.

(JCC) It's Millah time.

Meeting adjourns 1717 SST.

\vspace{0.15in}
\begin{center}
Penn and Teller are Dead,

Robert Poole, Onseck
\end{center}
\end{document}
