\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

February 23rd, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, February 23rd, 1991,
1700 SST, John Conger, President and Skinner presiding.

(JCC) (Makes an ass of himself.)

(M Y) Move to commend the minutes as being ridiculous to write up.

Motion fails 2 to 3 to 1 plus Spehn.

(KRJ) (Makes an ass of himself.)

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(JCC) Mobcomm report.  There wasn't a New England Mobile run or anything.
(Or maybe there was.)
Adina said something about not getting something finished.  (Explains what
New England Mobile is to a new person.)

(Adina walks in.)

(A A) There will be a New England Mobile run next weekend.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(WDS) What will be Ken and Janice's kid's name?

(C H) William Gregory Meltzner.

(New Person) I move that we change the kid's name.

Motion passes 10 to 6ish to 2 plus Spehn.

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(M Y) (Talks about an inflatable fashion show...)

(A A) Move to free the Banannimal from its cage in honor of Ken and Janice's
baby.

(S G) Motion to express our hope that Ken and Janice's baby is well fed with
banannas.

Motion passes 8 to 5 to 4 plus Spehn.

Meeting adjourns 1712 SST etc.

\vspace{0.15in}
\begin{center}
Regretfully submitted,

Robert Poole, Onseck
\end{center}
\end{document}
