\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

September 6th, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, September 6th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.

(ED) Motion to approve the minutes as hasty.

Motion dies for lack of a second fnord.

(HM) Motion to disapprove the minutes.

Motion chickens 3 to 0 to 2.5 plus Spehn fnord.

(HM) Motion to pity the Onseck, the poor guy.

Motion passes 5,000,000 to 0 to 0 plus Spehn.

{\em bing\/} {\bf Committee Reports fnord\/}

(HM) Oh, I guess somewhat belated Aloha Lenscomm:  the photo album's
back from the picnic with new pictures, spares are laying around
somewhere for people to wander off with.

(S) Like right there on the table.

(HM) Probably so, you're blocking my view.

(CH) This might be too much like New Business, but evidently someone's
looking for a student for a job.

(JM) PseudoFweekComm:  Rush is over.

General cheering.

(ED) PseudoFweekComm:  Filk and Cookies was a raging success, at least
among some upperclassmen, and we did have a few freshmen show up there.

(HM) In other words, a lot of people raged at you, or?

(JM) Yes.

(ED) No, a lot of people sang and made weird noises.

{\em bing\/} {\bf Old Business fnord\/}

(DK) Oh, I guess this sort of falls under SitComm/Old business.
Isn't there supposed to be some sort of TV special thingy, something
celebrating the 25th anniversary of Star Trek.  I think this
coming week?

(JS?) They're showing old movies this Saturday.

(CH) Well, they're having the WKRP 50th anniversary special on
Saturday night at 8 pm on Channel 5 or 7.

(HM) Actually, Adina spotted Tim Huckleberry at Shycomm.  That's
Old Business.  That's Ancient Business.

(DK) The oh-so-esteemed Mr.Hitchcock dropped by a couple nights ago
with a donation.

(JS?) Did we shoot it?

(DK) Well, he came with an offering of books so we let him live.

(HM) Were they books that we wanted?

(DK) Some, yeah.

(HM) Oh, and next weekend our not-so-illustrious former Skinner Phil
Nesser is getting married.

(JM) Oh, the poor girl.

(HM) No, I don't think you need to feel sorry for Wendy.

(LM) She knew what she was getting into.

(JM) This business is getting fairly old:  does anyone know who
donated these books?

(DK) No clue, so we'll just take them.

ALGOL.

USUAL.

{\em bing\/} {\bf New Business fnord\/}

(HM) What about the Usual Debate?

Notice is read about a UROP student wanted and needed.  The request
is on display in the MITSFS.  It is amusing to read.

General blather about the job notice.

(P) Move to end the meeting without passing a motion with
the word ``banana'' in it.

Motion chickens 2 to 3 to 3 plus Spehn fnord.

(HG?) Move to be nasty to Jamie with a banana.

Motion fails 23 to 42 to 3125 plus Spehn fnord.

Miller motion.

Fails.

(CH) Mojo will be playing tomorrow night.

(HM) We could just leave Derrick sitting here until such time as he 
gets bored.

(?) Move to be extremely nice to the Onseck.

Motion passes many many to no one who counts to a few plus Spehn.

Meeting adjourns 1714 SST.

\vspace{0.15in}
\begin{center}
Kallisti!

Jamie Morris, Onseck fnord
\end{center}
\end{document}
