\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

April 19th, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, April 19th, 1991,
1700 SST, John Conger, President and Skinner presiding.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(WDS) SomethingComm --- Terry Brooks is going to be autographing books at
Copley Square.

(HAM) AlohaLensComm --- We have no pictures for SC, SG, and SL, and if we
don't get any, I'm going to pick candid shots from the picnic.

(WDS) SitComm --- The {\em Nova\/} episode about the Cuckoo's Egg hack-in
is on Tuesday.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

ALGOL.

USUAL.

IT.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(JCC) I've got a flier for some shelves.  I'm going to order some.  (Begs for
someone to dial the number...)

Timewarp to Committe Reports.

(RPP) MooComm --- {\em Edward Scissorhands\/} tonight.

Timewarp collapses.

(WDS) Boston Globe and one other paper are running a list of obscene
publications because of some weird statute.

(S G) Move to commend the Onseck for wearing a banana colored shirt.

(RPP) (Makes a colorful second.)

Motion passes 7 to 1 to 6 plus Spehn.

Meeting adjourns 1707 SST.

\vspace{0.15in}
\begin{center}
They pay me good,

Robert Poole, Onseck
\end{center}
\end{document}
