\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

June 8th, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, June 8th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.


(S G) Move to approve the minutes as blue-shifted, Federally Expressed...

Motion passes lots to 1 to 1 plus Spehn fnord.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

(WDS) Sitcomm --- There's some new half-hour show that's done in the form of
flashbacks from the year 2035\ldots

(JCC) Sitcomm sub two --- {\em Twin Peaks\/} has been officially cancelled.
Also, there's a new show called {\em Dinosaurs\/} premiering\ldots

(newbie) Picnicomm --- (something about groceries)

(JCC) The picnic will be May 12th.

(WDS) Sitcomm --- last week, the show {\em Superforce\/} premiered.  It has
the lowest coherence value of anything I've ever seen in my life.

(S G) Motion to recommend that the Skinner watch the next episode while
tripping.

\vspace{.15in}
{\em bing\/} {\bf Old Business fnord\/}

(WDS) Bill Shakespeare had a birthday.

(C H) {\em Warlock\/} is out.

(What the hell is this doing in Old Business?)

ALGOL.

KLANG.

\vspace{0.15in}
{\em bing\/} {\bf New Business fnord\/}

(C H) Personalcomm --- I got accepted into the Clarion Writers' Workshop.

(JCC) I'm going to be staying here for grad school!

(RPP) Beast Roast will happen the day before the picnic.

(WDS) MiniCult --- (Quotes from a blurb --- read the article.)  ``This remake
of Alfred Hitchcock's suspense thriller is about a teenage girl living in a
midwestern town and her seemingly gentle uncle who is visiting but in truth is
a murderer.''

(S G) Second second Miller motion!

Motions passes lots to not enough to not enough plus Spehn fnord.

Meeting adjourns 1714 SST fnord.

\vspace{0.15in}
\begin{center}
Dejah Voo, man.

Jamie Morris, Onseck
\end{center}
\end{document}
