\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

March 22nd, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, March 22nd, 1991,
1700 SST, John Conger, President and Skinner presiding.

(C H) Move to approve the minutes as having a really novel way of being
excused as unfinished.

Motion chickens 5 to 5 to lots plus Spehn.

(new keyholder) Motion to approve the minutes aaaaaaassss\ldots

Motion passes 10 to 5 to 1 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(WDS) The founding father of Fender Guitars died.

(WDS) Diana Muldauer's character got killed off on {\em L.~A.~Law}.

(JCC) {\em Twin Peaks\/} is going to be on on Thursday.

(Not really, but anyway.)

(WDS) (Mumbles about {\em Quantum Leap}.)

(C H) {\em Northern Exposure\/} returns to television!

(WDS) {\em The Flash\/} returns to CBS real soon now.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(WDS) William Shatner is 60 today.

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(C H) Lunacon report.  The moderator of a panel, Catherine Cramer,
was drunk and tried to punch
one of the panelists.

(C H) There is poetic justice!
A gaybasher has contracted AIDS from gaybashing.

(WDS) Minicult --- I'm looking at the back of a comic book, and on it there
is an ad for an upcoming comic series called {\em Ape Nation}, which combines
the worlds of {\em Planet of the Apes\/} and {\em Alien Nation}.  I think this
is a sign of the collapse of Western civilization or some such.

(Paul) There will be a new {\em Lost in Space\/} comic book.

(WDS) Technically, {\em Quantum Leap\/} and {\em Magnum P.~I.\/} take place
in the same universe.  Imagine a crossover!

(WDS) Hint-comm: Bananna!

(JCC) (Stops and adjourns the meeting.)

Meeting adjourns 1722 SST.

\vspace{0.15in}
\begin{center}
William Shatner wears a banana colored toupee,

Robert Poole, Onseck
\end{center}
\end{document}

