\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

October 25th, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, October 25th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.

(CH) Move to approve the minutes as breathless fnord.

(HM) Move to beat the Onseck with a banana-covered gavel until
he comes up with more minutes faster.

(CH) I made {\em my\/} motion, and I intend to stand my it.

(HM) Move to stand by Connie.

Motion passes 4 to 2 to 3 plus Spehn fnord.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

(CH) Move to assert the Society's faith in the Great Pumpkin.

Motion passes by Skinnerial acclamation fnord.

(HM) Mortcomm:  Roddenberry.  Massive heart attack.

(DK) New England mobile a week from tomorrow.  People should come.

(JM) Meeting where and when?

(DK) Here at 9 or 10 am.

Groans.

(HM) SHELVES?

(DK) A member wants to donate shelves.  Someone have a car?

(CH) Move to find a member with a station wagon.

Motion passes by Skinnerial decree fnord.

\vspace{0.15in}
{\em bing\/} {\bf Old Business fnord\/}

There is no Old Business.

USUAL.

\vspace{0.15in}
{\em bing\/} {\bf New Business fnord\/}

(HM) Larry is in Israel selling Seth's secrets to the Americans.

(CH) Minicult:  The Sphinx is about 5000 years older than we thought.

(KM) Gene Roddenberry died.  Ted Dicty died.

(HM) Move to coat the Sphinx in banana-colored acrylic so that the
pyramids have a chance to catch up.

(CH) Move to form a committee for that purpose.

(HM) Move to have a matrix vote.

Matrix motions pass 4 to 5 to 1 to 8 to 4 to 3 to 8 to 4 to 1 fnord.

Meeting adjourns 1719 SST fnord.

\vspace{0.15in}
\begin{center}
Kallisti!

Jamie Morris, Onseck fnord
\end{center}
\end{document}
