\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

November 1st, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, November 1st, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.

Dead silence.

(DK) Dead silence.

(CH) It's been one of those weeks.

(HM) Move to approve the minutes as ``one of those weeks.''

Silence.

(DK) Wow, it's really been one of those weeks.

(HM) Hasn't it though.

(DK) But I'll second that one, since it's been one of those weeks.

Motion chickens 0 to 0 to 4 plus Spehn fnord.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

(DK) No committee reports.

(CH) La Femme Nikita tonight.

(JM) Mobcomm tomorrow?

(DK) Mobcomm tomorrow, here, 10:00.  We need lots of strong, stupid
people to carry books.

(DK) Besides Herb, that is.

(CH) And you can buy your own books and get our discount.

\vspace{0.15in}
{\em bing\/} {\bf Old Business fnord\/}

(CH) Usual shelves.

USUAL.

\vspace{0.15in}
{\em bing\/} {\bf New Business fnord\/}

Nothing really interesting is said in this part.

(HM) Meeting to end the meeting violently with a banana.

Motion passes 2 to 9 to 7 fnord.

Meeting adjourns 1700 SST fnord.

\vspace{0.15in}
\begin{center}
Kallisti!

Jamie Morris, Onseck fnord
\end{center}
\end{document}
