\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

May 10, 1991

\end{center}
\vspace{0.15in}

Note that these minutes were taken by hand, not by Tarl, and so are not
complete.  Also they were taken in something water-soluble and were
repeatedly sprayed by the Vice's watergun during the meeting.  We
apologize for the inconvienience.

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, April 26th, 1991,
1700 SST, John Conger, President and Skinner presiding.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(?) Move to approve the minutes as ``the best x-y-z + Spehn yet''

Motion passes ? to ?' to ?'' plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(HM) Aloha Lenscomm --- We have incriminating pictures of everyone.

(?) Motion to appropriate money for a MITSFS van.

Motion passes 12 to 3 to 3 plus Spehn.

(SL) Twilight Zine?  Please?  We need review books?

(?) Moocomm --- movies this weekend.

(random people) random talking

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

ALGOL.

KLANG.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(?) MiniCult --- says something or other

\vspace{.15in}
{\em bing\/} {\bf Elections\/}

Announcement of winners.

Steph is set equal to Vanna.

Vanna removes a vowel.

Onseck nominations --- John Conger, Skippy, JC junior, Colin, the guy
with the glasses, that noise, Jen Marlow, Phil Nesser, Dan Quayle,
Yalda the Crimson Queen, a banana.

Nominations closed.

Voting.  5.47 guy with glasses wins by not enough.

Voting take II.  Steph announces, ``I deserve to be eaten.''  John asks
to be shot now.  Wizbeth complies.  7.12 the glasses win.

Sherrian hides under the table and squeaks.

Sherrian is set equal to that noise under the table.

Sherrian's name loses the S.

LHE nominations.

Voting.  John asks to be shot again.  Wizbeth complies.  The minutes get
thoroughly trashed.  John calls Wizbeth a bitch.  5.68 the noises win
by not enough.

Son of the Vote.  John says he wants to take Steph out for dinner, buy
her flowers, and CENSORED.  Noises win with 7.5.

Vice nominations.

John whines.

Floozy wins.

President nominations.

The minutes are extremely wet and the Onseck-elect says to the hells
with them.

Meeting ends, eventually.
\vspace{0.15in}

The losers are:  Derrick Kong, President and Skinner; Elizabeth
Ditchburn, Vice; Sherrian Lea, Lord High Embezzler; James Morris,
Onseck.
\vspace{0.15in}

James Morris, Onseck

\end{document}
