\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

May 24th, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/} {\bf It's\ldots{}.\/} MITSFS meeting called to order, Friday, May 24th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding.

Part 2:  The Lama

\vspace{0.15in}
{\em bing\/} {\bf And now for something completely different--Committee Reports\/}

(Man) The llama is a quadruped which lives in big rivers like the
Amazon.  It has two ears, a heart, a forehead, and a beak for eating
honey.  But it is provided with fins for swimming.

(Guitarist + Dancer) Llamas are larger than frogs.

(M) Llamas are dangerous, so if you see one where people are swimming,
you shout:

(G + D) Look out, there are llamas!

\vspace{0.15in}
{\em bing\/} {\bf And now for something completely different--Old Business\/}

(Barber) I'm a lumberjack and I'm OK,
I sleep all night and I work all day.

(Mounties Choir) He's a lumberjack and he's OK,
He sleeps all night and he works all day.

(B) I cut down trees, I eat my lunch,
I go to the lavatory.
On Wednesday I go shopping,
And have buttered scones for tea.

(MC) He cuts down trees, he eats his lunch,
He goes to the lavatory.
On Wednesday he goes shopping,
And has buttered scones for tea.
He's a lumberjack and he's OK,
He sleeps all night and he works all day.

(B) I cut down trees, I skip and jump,
I like to press wild flowers.
I put on women's clothing
And hang around in bars.

(MC) He cuts down trees, he skips and jumps,
He likes to press wild flowers.
He puts on women's clothing
And hangs around in bars\ldots{}.?
He's a lumberjack and he's OK,
He sleeps all night and he works all day.

(B) I cut down trees, I wear high heels,
Suspenders and a bra.
I wish I'd been a girlie,
Just like my dear Mama.

(MC) He cuts down trees, he wears high heels,
Suspenders\ldots{} and a bra?!?!?!?

\vspace{0.15in}
{\em bing\/} {\bf And now for something completely different--The
Spanish Inquisition\/}

(Everyone) I didn't expect the Spanish Inquisition!

(Cardinel Ximinez) Nobody expects the Spanish Inquisition!  Our chief
weapon is surprise\ldots{} surprise and fear\ldots{} fear and surprise
\ldots{} our two chief weapons are fear and surprise\ldots{} and
ruthless efficiency.  Our {\em three\/} weapons are fear and surprise
and ruthless efficiency and an almost fanatical devotion to the Pope
\ldots{} Our {\em four}\ldots{} no\ldots{}{\em amongst\/} our weapons
\ldots{} amongst our weaponry are such elements as fear, surprise
\ldots{} I'll come in again.

\vspace {0.15in}
{\em bing\/} {\bf And now for something completely the same--The Spanish
Inquisition\/}

(Everyone) I didn't expect the Spanish Inquisition.

(CX) Nobody expects the Spanish Inquisition.  Amongst our weaponry are
such diverse elements as fear, surprise, ruthless efficiency, and
an almost fanatical devotion to the Pope, and nice red uniforms--oh,
damn!

(Biggles) Can we torture them with a banana?

Meeting adjourns 1730 SST.

\vspace{0.15in}
\begin{center}
It's\ldots{}

Jamie Morris' Flying Circus (Onseck)
\end{center}
\end{document}
