\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

September 13th, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, September 13th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.

(CH) Second.

Motion passes 12 to 2 to 2 plus Spehn fnord.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

(CH) Moocom:  There is a movie on HBO called ``Cast a Deadly Spell''
which involves Los Angeles in the 40s, when all magic works.  It's a
private detective movie, the private detective's name is Howard Philips
Lovecraft.  Involving a stolen copy of the Necronomicon, I haven't
seen it but I hear it's actually pretty funny.

(DK) Cute.

(CH) And it's showing on and off throughout the rest of the month
and into October because they're just repeating it over and over and
over again, so anyone who has access to HBO may actually be able
to see it.

(RP) The question is, were they intending it to be funny?

(CH) It seems so.

(DK) Whooshcom.  It went.  Amazing that.

(JM) PseudoSitComm:  Evidently someone aired a showing of ``To Save
a Child,'' which is supposed to be about a town of witches which
steal peoples' babies and do nasty things to them.  Apparently it
sucked, although I haven't seen it myself.

(CH) What, you mean stealing babies for witchcraft ceremonies?

(JM) No, the actual show sucked.  Although I haven't stolen a baby
for that either.

(CH) Moocom sub 2, Moocom sub 3 actually:  I did catch a showing of
Brana's latest ``Dead Again.''  Interesting movie.  A little bit
overdone, but still worthwhile seeing.  Because it does have a fantasy
element in it, so--it's worth seeing.  Too much music.

(DK) I guess Moocom sub 4:  The various information leaks, etc about
Star Trek six are growing and growing.  If anyone cares, I can tell them
about the latest things.

General cries for Derrick to tell about the latest things.

(DK) This is from someone on the Net who went to a showing of all
five Star Trek movies in a row and was subsequently a drooling idiot.
Paramount did a special thing in which in one theater in each major
city in the universe they showed all the Star Trek movies and clips
from the sixth, after which they forced all the attendees to play
Russian Roulette.  Among them, they had:  The Enterprise escorting
a Klingon ship to Earth to discuss treaties with marsupials.  Suddenly
the Enterprise opens fire and turns the Klingon ship into many, many
little pieces, each of which is totally incapable of brushing its
teeth, much less making treaties.  Oops.  Kirk is confused.
Then it cuts to a scene where most of the crew is on an ice planet
and Captain Sulu of the Excelsior comes to rescue them.  Yes, Sulu
does get his own ship.

(RP) This sounds amazingly like the plot of one of those Trek novels.

(DK) Doesn't it though.

\vspace{0.15in}
{\em bing\/} {\bf Old Business fnord\/}

Strange whispers of the Old Business Algol and various plots
to take over the world and dismember pieces of it, followed by

\vspace{0.15in}
{\em bing\/} {\bf New Business fnord\/}

A random member explodes.

(RP) I've been driving with an expired license.  I was sentenced
to be hanged but they ran out of rope.

(DK) Rabbits make good hats.

The world ends.

Meeting adjourns 1723 SST fnord.

Wizbeth tickles Derrick.

(DK) Hey!

(JM) Vice and Telzey seem to be offices that go together very well.

(DK) You can let go now.

\vspace{0.15in}
\begin{center}
Kallisti!

Jamie Morris, Onseck fnord
\end{center}
\end{document}
