\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

February 15th, 1991

\end{center}

\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, February 15th, 1991,
1700 SST, John Conger, President and Skinner presiding.

(Steph) (Moves to advertise for a new Onseck in the {\em Phoenix}.)

Motion passes 6 to 4 to 4 plus Spehn.

(KRJ) If we can't get an Onseck, can we get the lady wrestler?

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports\/}

(JCC) Mobcomm...  Adina said she didn't have the stuff done for this week,
so she'll hopefully have it done for next week.  Pianocomm --- Robert van der
Heide turned in his key because he is in Japan.

(New Person) (Introduces self, and wants to be a keyholder.)

(WDS) Concomm --- Bhoskone, this weekend...  Nowhere near here.  Springfield,
Massachusetts.

\vspace{.15in}
{\em bing\/} {\bf Old Business\/}

(HAM) I'm feeling really old today.  Final freeze for our product was today,
because it ships out...

ALGOL.

\vspace{0.15in}
{\em bing\/} {\bf New Business\/}

(WDS) New legal precedent --- A God now has legal standing in the court (in
England).  The God Shiva was listed as one of the five plaintiffs in the
lawsuit.  (Something about a really expensive statue that got stolen by
British imperialist pigs.)

(HAM) {\em tiredly\/} Miller motion.

(WDS) Second Miller motion.

Meeting adjourns 1706 SST.

(JCC) Rob, I know you never listen to these...

{\em Ah, but I do, John.}

(JCC) ... but if you do, please write it up for next week.

(HAM) Your name is MUD.

{\em Actually, it's Muck, so Fuck You.}

\vspace{0.15in}
\begin{center}
Anal retentively submitted,

Robert Poole, Onseck
\end{center}
\end{document}
