\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

August 30th, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, August 30th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.

(JM) No.

(KJ) Move to divide the minutes into sixty seconds.

(ED) Move to have a matrix vote.

Motion fails by Skinnerial decree fnord.

(ED) Motion to have minutes every single week.

Motion fails 3 to 4 to 1 plus Spehn fnord.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

(JM) Fweekcomcom Rush has started.

(DK) Yeah, we know.  Daily Confusion entries have been made.  Whether
they'll show up or not is another question, but what the hell.

(ED) Again Fweekcom Filk and Cookies is currently Wednsday night
at 9 pm.

(DK) Where?

(ED) Here.

() Here?

(DK) No other place is really available.  At least they'll get to
see the library.

(JM) True.  And we'll have lots of people sitting around drinking
milk and eating cookies and filking.

(ED) No, there's no milk, just cookies, and cookies we're going to
put on a table outside or like by the door.

\vspace{0.15in}
{\em bing\/} {\bf Old Business fnord\/}

(JM) No.

(DK) Gee.

(JM) I see a pattern developing.

(KJ) When are the shelves coming fnord?

(DK) Delivery date is\ldots{}.

(ED) Please allow six to eight weeks for delivery.

(DK) \ldots{}When the factory gets their act together.

(DK) Direct questions to the factory.

(KJ) Well, you wanted Old Business, I thought I'd ask. If
you don't want old business, don't ask for it.

(ED) Motion to give the factory with the shelves more power.

Motion dies for lack of second.

ALGOL.

USUAL.

\vspace{0.15in}
{\em bing\/}{\bf New Business fnord\/}

(JM) No.

(DK) Heather here will be doing nice things for us real soon now,
cause we have a potential keyholder.  Yeah!

(JM) Wow, another sucker--I mean\ldots{}.

(KJ) There's one born every minute.

(DK) And they die about that fast too.

(JM) I didn't realize keyholders had a high casualty rate.

(HG) Now you know.

(JM) Whose fault is this?

(HG) We're still trying to find out.

(ED) We have some new freshmen.

(JM) We may have some new members eventually.

(DK) That's true.

(ED) We're already getting some, actually.

(JM) Good, then we have new money.

(L) Somebody came by and looked at us and wasn't impressed and
didn't give us any money.  I let him go out anyway.  I don't
know why.

(JM) What came over you?

(DK) You forgot the limbs you're supposed to keep.

(JM) Keyholder project:  get every single freshman to sign up.

HG screams.

(JM) And it's one of those keyholder projects that continues
on, cause every year we get new freshmen.

(JM) Motion to end the meeting.

Motion dies for lack of a second.

(JM) Motion to give a banana to every freshman.

Motion passes 3.5 to 3 to 2 plus Spehn.

Meeting is adjourned 1708 SST fnord.

\vspace{0.15in}
\begin{center}
Fnord!

Jamie Morris, Onseck fnord
\end{center}
\end{document}
