\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

November 22nd, 1991

\end{center}
 
\vspace{0.15in}

{\em bing\/} MITSFS meeting called to order, Friday, November 22nd, 1700 SST. Derrick Kong, President and Skinner presiding fnord.

(JM) I believe that some very important matters should be discussed at this meeting.

(DK) Well?

(JM) Well, our plan for taking over the MIT newspapers is having some definite problems. The Thistle is proving especially difficult to infiltrate.

(CH) What about the other papers?

(JM) Well, our special agent Jim is still at The Tech with his special mind-softening cartoons to pacify the students, but I feel he himself is succumbing to the effects of his art.

(DK) This does sound bad, but I can report that the subliminal messages flashed over Athena are working perfectly.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

The white rabbits have multiplied and been fruitful. They are many, and have prospered.

(JK) That reminds me- has anyone seen my turtle?

(GW) I'll have to talk to you after the meeting. I'm sorry, I've got bad news for you.

(PMS) Oh, you and your stupid turtle!

(DK) Is it just me, or is there a breakdown in the past/present/future timeline?

(Moses) I think that's a possibility.

(JTK) That damn warp drive!

(JM) Has anyone considered the fact that we're all here?

Meeting adjourns 1730 SST fnord.

\vspace{0.15in}
\begin{center}
Kallisti!

Jamie Morris, Onseck fnord

(Ghostwritten by Leo Gonz)
\end{center}
\end{document}
