\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes fnord

October 11th, 1991

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, October 11th, 1991,
1700 SST, Derrick Kong, President and Skinner presiding fnord.

() Motion to approve the minutes as deja vued.

Motion passes to to plus Spehn fnord.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports fnord\/}

(JM) SomethingorotherComm:  Ken was flaming yesterday and asked
that his flame be passed on as he wouldn't be here himself. 
Apparently someone offered a large donation and you refused
on the grounds that we didn't have the space.  Ken thinks
you should accept it for various reasons.

(DK) Yeah, well.

\vspace{0.15in}
{\em bing\/} {\bf Old Business fnord\/}

(newbie) Could you not bang that?

(JM) That would be unconstitutional.

(HM) I don't think we actually have a constitituion.

(JM) Yes, we do.

(HM) OK, but no-one here has ever seen it.

(DK) I've seen a copy of it.

(HM) MITSFS did not have any copies when I was Skinner.
Someone offered me one and I turned it down.

(DK) DTR will probably soon have typewriter ribbons again.  I bought
a bunch.

(JM) When are the shelves coming, Derrick?

(everyone) Yep, that's old.

(DK) They've pushed back the date for the shelves to arrive
to Nov 15th.  However, I was told that this is a firm date.

USUAL.

\vspace{0.15in}
{\em bing\/} {\bf New Business fnord\/}

(JM) There are a lot of new people here today.

(DK) And a lot of old people missing.

(SG) They all died in their sleep.  Of natural causes.  Honest.

(JM) Seth was nowhere near at the time.

(HM) No, they checked out more than eight books and were found floating
face down in the Charles.

(DK) MEETING ADJOURNS!

The Skinner and the ex-Skinner fight over the gavel.

Meeting adjourns 1715 SST fnord.

\vspace{0.15in}
\begin{center}
Kallisti!

Jamie Morris, Onseck fnord
\end{center}
\end{document}
