\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 1, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, President and Skinner, presiding.

Minutes of the previous meeting read by Pseudo-Onseck Lisa Kroh.

(JD) Motion to replace the minutes with five pages of Miss May.

Motion seconded, passes by Skinnerial decree.

\goto{Committee Reports}

(JME) Jourcomm: I've gotten some more really nice art, submitted by two of the best fan artists in fandom (one of them has won a Hugo, the other has been nominated several times) but if none of you write anything, this will be the all-art issue of TZ.

(SSDT) Electioncomm: we almost didn't get the Spofford Room. Last year they wouldn't give it to people outside the CE department until one day before they needed it; this year I called two weeks early and found out they'd already given it to someone for that day and the people weren't in the CE department. They've only reserved the room until 5:30, though, so unless they run over we should have it.

(JME) Sitcomm: Max Headroom, which had been doing okay but not spectacularly in the ratings, suddenly jumped to number 16 last week. Last week's episode was an improvement over the last couple of weeks, too.

(SSDT) Headroom sub 2: Doonesbury is doing a "Ron Headrest" thing- it's working very well.

(BPS) Sitcomms: first, in the season finale of Crime Story, which concerned a policeman's feud with an up-and-coming mobster, the episode ended with the bad guy driving out of Las Vegas right into the heart of an aboveground nuclear test. The producer kidded that "The character might come back next year- he'll just be the character who glows in the dark." And then, on the finale of Sledge Hammer!, Sledge was trying to disarm a nuclear bomb. He says "Trust me, I know what I'm doing," and then the screen goes white- then to footage of an atomic test in the desert. Fadeout. after the messages, they come back with the scene of a totally nuked city, you hear Hammer's boss yelling "Ham-MER!!!" and the words come up on screen "To be continued next season."

(TMcK) Sitcomm: Sledge Hammer! was the most popular show at Caltech over the last semester.

(AA) Sitcomm: I saw The Charmings, finally. It's not that bad-kind of amusing.

(JME) Sitcomm: some anti-allergy medication is running science-fictional ads.

(KM) ROSFAP: we've got lots of neat new fanzines, including Short Form, edited by Orson Scott Card, and Neology, which contains a really rave review of TZ 38. They want to trade for Neology, I want to trade for TZ, and to clinch it I'm buying the Skinner a full membership in the Edmonton Science Fiction and Comic Arts Association. We also have a new Robots and Road Runners and Thrust 26, and an 8 1/2 by 11 zine which is a sheet of paper with weird silly art on it.

(GF) Pseudo-Moocomm: some of the wonderful things coming from Hollywood: "Slime Girls from Beyond Infinity," "The Video Dead," and "Assault of the Killer Bimbos."

(SSDT) Pseudo-LHE Report: by some miracle, Finboard gave us our money. We got 1,065 plus 100 dollars in IAP funding.

(JME) Personal Report: It's exceedingly likely we'll be leaving the area after Ken graduates. This is going to be my last issue of TZ so I want it to be a good one. We don't know where we'll be headed- Schenectady is a possibility.

(SSDT) Pseudo-LHE Report 2: Does anyone know where the LHE is? He disappeared last Tuesday when we were halfway through the budget.

(BPS) Pseudo-Weathercomm: it's about 62 degrees and sunny out there- 72 hours ago it was snowing.

(BPS) Mobcomm: my car and I are celebrating our first anniversary.

(JME) Moocomm: Slaughterhouse Five this Sunday.

(JAH) Picniccomm: we have the Mezzanine Lounge as a rain room for the picnic if we need it.

\goto{Old Business}

(All) Hi Tom!

(JME) There's a book out called Martian Spring dedicated to, among others, former skinner Guy Consolmagno. They spelled it Consamagno.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: from yesterday's Glob, "Man charged with killing gerbil." A man bit the head off a live gerbil on a dare during a party and soon after was arraigned on a charge of malicious injury and killing of an animal.

(BPS) Minicult: there's a picture in the Glob of three really ugly pieces of pre-Columbian art. The museum removed them from the exhibit after finding out that they weren't pre-Columbian art worth thousands of dollars, but 18-dollar sculptures mass produced in the 1950s.

(GF) Minicult: there was an army unit that was selling weapons illegally to the Contras- its codename was "Yellow Fruit."

(SSDT) Minicult: from last week's Phoenix: "Dr. Alan Guess and several colleagues at MIT are thrashing out the exact physical requirements for creating a universe similar to our own. This raises several questions: was our universe created this way? Could we ever find out? Could we, should we ever use such godlike power? Isn't calling up a cosmos going a bit overboard? Frankly, Dr. Guess, we'd settle for a little extra parking."

(JME) Minicult: the FCC has decided to crack down on indecent radio broadcasts. They haven't done anything except yell so far, but they're threatening.

(BPS) Minicult: Al Lewis, who played Grampa (a vampire) on The Addams Family, celebrated his 77th birthday by opening an Italian restaurant in Greenwich Village. Asked if the garlic in the food would conflict with his image, he replied, "No, I love garlic. Back in 1275 I started that whole rumor about vampires and garlic. I found it made people more secure since they thought they could slumber safely."

(CCH) Minicult: Giant Egg Found Floating In Space.

(BPS) Minicult: from Insight magazine- on March 21, a money machine in Washington DC started dispensing five-dollar bills instead of 20-dollar bills and vice versa. The bank claims it's the fault of the Wells Fargo company that supplies the money to the machines.

(KM) Move to commend the CIA for using banana-colored codewords.

(JME) Motion to commend the skinner for wearing totally non-banana-colored pants.

(RJG) Motion to commend the Vice for using banana color in the bracelet she made for me.

(SSDT) Looks like we've got a matrix vote.

Motions seconded, 18-9-5 +Spehn, 10-8-13 +Spehn, 0-8-8 +Spehn. Matrix remains indeterminant for a while, and then fails by -354 votes.

(KM) Motion to condemn the MITSFS for having a banana-colored matrix with a negative determinant.

Motion passes by skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1806 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}