\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 30, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of 2 of the previous 3 meetings read and corrected.

(Seth Gordon) Move to approve the minutes as a special double edition.

(John Dumas) Amendment- a special Halloween double shocker feature.

Motion seconded, passes everybody here-no one-2 +Spehn.

\goto{Committee Reports}

(BPS) Pseudo-Moocomm: Adina said the movie of Night Flyers was terrible and bore almost no resemblance to a certain novella by a certain George R.R. Martin.

( ) Addendum- I agree, but it's already left town so we don't have to worry about it anymore.

(CH) Sitcomm: V, the miniseries, will be on next week.

(BPS) Sitcomm: I heard a rumor that Denise Crosby may not be long for Next STrek. She's been demanding more money and Gene Roddenberry is not going to give it to her.

(DSK) Moocomm: I've seen previews for a movie called The Hidden, in which an intergalactic criminal comes to Earth, followed by the intergalactic police.

(BPS) Addendum- The reviewer from McPaper loved it; the reviewer from the Glob really hated it.

(KG) Addendum- The reviewer from the Times, trying to describe a scene, said "I guess you had to be there, but on the other hand, why would you?"

(CH) Addendum- It does star Kyle McLaughlin, who was Paul Atreides in Dune and also in Blue Velvet.

(DSK) Moocomm2: Ghostbusters tonight, Road Warrior Sunday at LSC.

(BPS) Cornelia Otis: in place of the "no Bork" buttons, we can now all go get ones that say "Who is this guy?"

(DSK) Reagan nominated some guy named Ginsberg.

(Seth) Pseudo-Mobcomm/Mortcomm: it is now more than a month since my 18th birthday, and I have not yet registered for the selective service. Any leads on jobs in Canada?

(DSK) Pumpkincomm: It's time to renew the Society's faith in the Great Pumpkin.

(CH) Move to affirm the Society's faith in the Great Pumpkin. Passes by Skinnerial decree.

\goto{Old Business}

(CH) We had a minicult a while back about a sandpiper (bird) that established a four-day record of 28,000 miles traveling to Venezuela or Brazil, where it was killed. It is a new world's record for a small bird's flight.

(BPS) In 6 hours and 10 minutes I'll be thirty.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: Taxi drivers in France want to electrify the back seats of their taxis to administer a 52,000 volt shock through the legs and back of a person sitting there.

(J Dumas) Minicult: from the most recent Smithsonian magazine- soon Americans may be able to buy their towels according to where the Hitchhiker's Guide's Ford Prefect bought his, as Marks and Spencer, the British department store chain, is considering opening stores in the US.

(MJG) WBCN is sponsoring a raffle where the winner gets to steal a 20,000-dollar car with some sort of finding system, and if they can't find the car you get to keep it. Does anyone here have a Faraday Garage?

(CH) Radio, continued- WZLX had a DJ for a day contest, where the winner was to receive a full scholarship to the Connecticut School of Broadcasting in Waltham. I heard the guy who won, but he turned out to be the pastor of the United Church or Christ in Warwick, RI, so we don't know if he'll take up the offer of a career in radio.

(BPS) Minicult: a woman in Florida got a conviction for child abuse following the suicide of her 14 year old daughter. It's believed to be the first time a parent was convicted of child abuse for a child's suicide. The mother apparently forced her daughter to be a nude dancer.

(GF) Move to affirm the Society's lack of faith in the Great Banana.

Motion seconded, chickens a few-less than a few-more than a few +Spehn.

(VHS) Motion to condemn Mike Freedman for wearing yet another day-glo banana colored shirt. (HAM) With the stripes going the wrong way.

Motion seconded, passes 15-believe me not 15-14.5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}