\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 27, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

Phonecomm: it's Tom McKendree with a Minicult. It is time warped to New Business.

(BPS) Move to approve the minutes as Phonecomm.

Motion seconded, fails 0-many-3 +Spehn.

Phonecomm: it's Dave Broadbent for Janice. She has what he wants. (For ReaderCon, that is.)

(SLP) Motion to approve the minutes as better than The Hitchhiker's Guide to the Galaxy.

Motion seconded, fails 2-5-4 +Spehn.

(RvdH) Motion to approve the minutes as being in a banana colored binder!

Motion seconded, fails by "Go away, Bob!"

(JAH) Motion to approve the minutes as "Go away, Bob!"

Motion seconded, passes (finally!) many cheers-1-the same one +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: the TZ mailing hasn't even gone out yet and we've already gotten our first letter of complaint, from Ben Bova who picked up his copy at Boskone. He complained because in his transcribed interview, the name of his title character from Orion got spelled as O'Ryan. Well, at least I didn't misquote him.

(BPS) Mobcomm Report: the Mobcomm got a new job! (And attended the meeting in a three-piece suit from Sears, with a clip-on tie. -JAH) I get to have a company-supplied PC at home.

(DSK) LHE Report: LHE Report RSN!!! Finally got the bank statements at the same time I got a new job and got sick, so I'll have two months worth of statements next week.

(JME) Boscomm: as of last Sunday, the Sheraton informed NESFA that they don't want any SF convention business again, including future Boskones as well as Noreascon 3 in 1989. NESFA is grovelling at the moment, trying to get them for at least Noreascon. NESFA is planning on cutting down on its con programming for next year, including running films only at night and not giving out any costuming awards.

(KM) In the past, there have been years when NESFA has lost the use of the Sheraton, even without the fire alarms. It seems to be a tradition for the Sheraton to get pissed off at Boskone every three years or so.

(BPS) Serious-and-grimcomm: last week we had an honest-to-God murder at the Student Center. A man got stabbed to death after a dance given by Alpha Phi Alpha, the national black frat.

(BPS) Coolstuffcomm: the gift of the Class of '86 was a really neat plasma sculpture that's now sitting on the third floor of the Student Center at the top of the stairs.

(SSDT) Skinner Report: I have an alter ego who drives an ice cream delivery truck. I found this printout on the sidewalk that tells driver S. Tucker to deliver Haagen Daaz and Dole Fruit Bars to the Coop.

(DSK) Moocomms: Aliens has been released on VHS. Also, Nightmare on Elm Street III is out today.

(BPS) Sitcomm: On Entertainment Tonight, they had David Gerrold rambling on about the new Star Trek show. The new ship is the nth generation of the Enterprise and is 2100 feet long as compared to 900 for the original; it will carry a crew of 907.

(BPS) Moo/Sitcomm: back when the movie Supergirl came out, the movie posters got a big laugh because they showed her flying past the Statue of Liberty, which was holding the torch in its left hand instead of its right. ABC is now showing it on TV, and in the ad for it in TV Guide, they have the same stupid mistake.

(CPS) Motion to make the Moo/Sitcomm a Sitting Bull Comm.

Motion seconded, passes by skinnerial decree.

(SSDT) Skinner Report: the Skinner wants to commend the Telzey for doing a particularly good job last weekend. (When asked "At what?" the Skinner replies "No comment.")

(JME) Othercomm: there are no more committee reports.

\goto{Old Business}

No old business.

OBA: um, us, uv, ur.

\goto{New Business}

(TMcK) Minicult by way of Phonecomm: a science fiction club is forming at CalTech; last week they got Larry Niven to speak, and next week they're getting Greg Benford. At every meeting they play an episode of The Hitchhiker's Guide to the Galaxy (so far they've had two meetings). He's going to send us a flyer with the address of the guy who's starting the club.

(JME) Minicult: on October 30, 1986, Ralph Forbes, shortly before losing his bid for an Arkansas Senate seat, filed suit to stop the observation of Halloween, which he referred to as "the Rites of Satan," in the Russelville school district. Listed as defendants in the case were the Russelville school district, various governmental departments, a state education official, and Satan. The case is still before the courts, and attorney John Wesley Hall Jr. has asked that Satan be dropped from the case on the grounds that it cannot be proven that he has transacted business, owned property, or committed torts in the state of Arkansas, and also because the state court has no business interfering in arguments between Jesus Christ and Satan.

(BPS) Minicult: in the Wall Street Journal, I think, there was an article about retired bowler Earl Anthony, in which they talked about how he was making an appearance somewhere and someone had brought this young kid to meet the great Earl Anthony. When a nosy reporter asked "Isn't today a school day?" the father replied "This is special." When the reporter happened to ask what the man did for a living, he responded "I'm the superintendent of schools for this district."

(JME) Minicult: in Canada, a self-proclaimed male witch who's a follower of the Wiccan religion has filed suit to receive paid leave for his faith's holidays, Beltane and Samhain. He's filing suit because of a clause in his contract that provides for paid leave for religious holidays.

(SSDT) Minicult: from Tom McKendree by mail- it's a piece of a report that got passed out where he works that talks about how the Russians are spying on our unclassified technology by sending spies to colleges and universities. There's a table showing how many times colleges got visited by Soviet spies; MIT's leading.

(DSK) Addendum- I saw a report a couple months ago listing the fifteen organizations whose data the KGB would most like to have. MIT was ranked 13, and Boeing was number 1. I got to MIT, and I work for Boeing.

(BPS) Minicult: Lawrence Welk fans got a surprise if they bought a disc labeled "Polka Party;" some of the records were mislabeled and actually contained pieces of the soundtrack from the hard punk rock movie Sid and Nancy.

(JME) Minicult: George Schultz's wife fessed up yesterday- George Schultz does indeed have a tiger tattooed on one of his buttocks.

(CH) Minicult: "Gay Vampire Catches AIDS."

(JME) Minicult: in Doonesbury this week the running gag is the unwillingness of people to combat AIDS by speaking frankly of the subject. The ad agency Mike Doonesbury works at is talking about "safe whoopie" and using the euphemism "condominiums." Ironically, a newspaper in Deseret City, Utah is refusing to run Doonesbury this week because they consider this too explicit.

(CH) Minicult, English variety: an animal rights advocated was quoted as saying that we don't need to experiment on animals any longer because we now have all these AIDS patients who only have a few weeks to live anyway.

(KM) Move to recommend that we experiment instead on gay vampire bananas with AIDS.

Motion seconded, pass/fails lots-more or less-1 +Spehn.

Confounded by the Skinner's failing of an obviously passed motion, people begin to sing "Rabbits" and manage to get through five verses. The Skinner, suitably chastened for her arbitrariness, adjourns the meeting at 1758 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}