\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 23, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(RvdH) Motion to approve the minutes as not being in a banana-colored folder.

Motion fails by "No" and "Go away."

(SSDT) Motion to approve the minutes as red!

(BPS) Second.

Motion passes everyone-3-5 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: thanks to Bill Starr, I now have three current book reviews. If anyone has anything else, they'd better get it to me tonight as tonight is the final final final final deadline if TZ is going to be ready in time. Collation is scheduled for a week from tomorrow.

(BPS) Pseudo-LHE Report: The search for the missing 500 dollar check is on hold until the employee at Chase Manhattan Bank who is the entire Matching Grant program gets back from vacation on January 27.

(CJH) Sitcomm: Network people don't understand heredity. They're shooting a pilot where The Six Million Dollar Man and The Bionic Woman get together and have a child. The kid, of course, gets in an accident and loses various body parts.

(JME) STrekcomm/Sitcomm: David Gerrold is going to be some sort of consultant for the new STrek series. There was a piece about the series on Entertainment Tonight last night, but they didn't show any scenes from it because the studio apparently won't let anything from the sets and so on be shown.

(JME) Huntcomm: we got two more team entries for the Scavenger Hunt. This is a lot more than I expected; I may have to ask for a larger room. One of them is the Lunarians, who won last time and apparently wrote me a letter a month ago that failed to get to me.

(SSDT) Speaking-of-the-mailcomm: we got a box in the mail from Airborne Express that was addressed to NESFA at Box G. I took it downstairs and the guy at the Post Office refused to have anything to do with it because it wasn't stamped. Turns out you can't send Express mail to a post office box. I left it in the Student Center manager's office and called Airborne Express' customer service line; they said they'd come and get it and bounce it back to the sender, who should have known better. I still don't know why it came to us.

(JME) Pseudo-Panthercomm/Finger: do we have a new PinkDex?

(SSDT) We have a new ShelfDex. It's in the blue and white ring binder. No PinkDex yet, but the ShelfDex looks healthy.

(DSK) Moocomm: Cartoon Film Festival Saturday night from LSC. Marathon Nine from Outer Space on Wednesday.

(BPS) Cornelia Otis Followup: the president of Ecuador was released by the rebellious paratroopers when he released the general they wanted freed and granted total amnesty to the people involved. The president is now trying to weasel, of course, and the opposition is trying to get him impeached because of it. Unfortunately, after the drama of the kidnapping was over, the media coverage went away and we don't know how it ended.

(CJH) Sitcomm: on LA Law two weeks ago, a lawyer shot himself in the courtroom. Last week on The Equalizer, a crooked judge did the same thing at the end of the episode. Yesterday in real life, the soon-to-be-ex state treasurer of Pennsylvania, soon to be sentenced to fifty years or so in jail, shot himself during a news conference with all the cameras on him.

(JME) Addendum: most TV stations refused to show it, and the few in Pennsylvania that did got a lot of complaints. Amid the complaints, though, were two calls by people who wanted to know when it would be shown again so they could tape it on their VCRs.

(JME) On a similar note, some video company has put together a tape called "Faces of Death" which is spliced together news footage of people dying in various graphic ways. It's a big seller; it sold so well that there are now two sequels to it.

(JME) Whooshcomm: it's almost the one-year anniversary of the space shuttle disaster, and in USA Today, the head of NASA is quoted as saying the Civilian in Space program is on hold, perhaps forever.

Phonecomm: it's someone who wants to get a hold of NESFA. He is given a phone number and quickly hung up on.

(BPS) Phonecomm: there's a company selling stupid recordings you can put onto your own answering machine. One of them is a Rod Serling imitator who tells callers they've reached "The Answering-Machine Zone." It's pretty twittish.

\goto{Old Business}

No old business.

OBA: um, ur, us, uv, and ur once again. "What about the UD?", USU.

\goto{New Business}

(BPS) Minicult: a supposed human being named Oral Roberts claims that God has given him a goal to raise eight million dollars, and a deadline to do it before March of '88 or God will "take Oral Roberts." Oral Roberts hasn't explained why he doesn't want to be taken by God, which I thought was the whole point of Christianity.

(BPS) Ancillary to that: Gays and other people are still calling Falwell's 800 number and harassing him. He doesn't like it but he can't do anything about it.

(RvdH) Con Report: Esotericon was, in New Jersey, and it was pretty cool.

Phonecomm: it's Old Business, Thom McKendree. He wants to know the dates of WorldCon in London.

(JME) Minicults: 1) the Michigan Department of Transportation has started using the smiley face on signs in construction zones to let people know how much further they have to go. The signs get progressively happier as the motorist gets nearer the end of the construction. But the Federal Highway Administration says the signs violate traffic control regulations and wants Michigan to analyze them because they're afraid the signs will confuse people. 2) A computer programmer who got laid off his job is creating something of a media stir by dressing up as an archetypal nerd to earn extra money. He's gotten TV interviews, newspaper coverage, and calls from women who want to go out on dates with him.

(At this point, aliens begin beaming messages directly to Tarl in the hope of contacting intelligent life, an effort heroic but doomed to failure. The incoming transmissions do succeed, however, in obliterating a section of the minutes including a Minicult by Janice about the British Labor Party and several other unidentifiable comments, most of which seem to be by Bill Starr, but I can't be sure.)

(AA) There's a new Darkover book out called The Other Side of the Mirror. It has a Darkovan Chronology in the front of it that is missing about five books in the series.

(The aliens, after a respectful pause for Adina, continue to transmit, trashing a Minicult by Janice that I think concerned the Miranda rule.)

(BPS) Minicult/Moocomm/Sitcomm/Whatever: there seems to be a new mentality of "Rambo-bashing" going around in pop culture. In the new Rutger Hauer movie Wanted: Dead or Alive, one of the atrocities committed by the Egyptian terrorist, played by Gene Simmons of KISS, is that he blows up an occupied movie theater. The movie being shown was Rambo. And on The Equalizer, when the Equalizer and his sidekick caught onto some bad guys who had a case of anti-tank missiles, the sidekick said "Rambo used one of those" and our hero responded "Rambo who?"

(CJH) There is this interesting flyer recruiting people for "Earth Shift" communities, set up to survive the coming calamity when the Earth shifts in its orbit. The person setting these things up is a 17-year-old man who, in the same issue, advertises for a wife who likes computers and science fiction.

(JME) Minicult: the neighbors of Ollie North say he's shown signs of a paranoid mentality, including telling his neighbors that the KGB tore down his fence and poisoned his dog.

(CJH) Minicult: I was reading an article about mass-murderer John Wayne Gacy that said that one of the articles that he was carrying in his pocket when they caught him was a dildo shaped like Santa Claus.

(BPS) Minicult: Pat Buchanan has announced that he will not run for president. Presumably this means he won't accept a vice-presidential nomination, thus killing our hopes for a Republican ticket in '88 of "Pat and Pat," Robertson and Buchanan. Some friends of mine have taken to referring to Pat Robertson as the Dark Horse of the Apocalypse.

(JME) Minicult: the person-powered flight team of MIT had two victories this week with the Michelob Lite Eagle. Lois McCallan set the human powered flight record of 9.9 miles on Wednesday, and Glenn Trimble handled a plane for 37.2 miles. This is preparation for a human powered flight from Crete to the mainland, 69 miles.

Connie makes a terrible pun question which gets her the Albanian Finger.

(JME) Motion to give Connie an Albanian Finger Banana.

(JAH) Shaped like Santa Claus!

Many seconds. Motion passes lots and lots and a person falling over backwards-one Albanian-another Albanian +Spehn who is not Albanian.

\vspace{12pt}

\noindent
Meeting adjourned, 1752 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}