\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 6, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(JAH) Motion to pass to minutes on the first motion this week.

Motion seconded, passes enough to get this over with-0-6 +Spehn.

\goto{Committee Reports}

(KM) Boscomm: Boskone 25 will not be held in downtown Boston according to the latest Instant Message. NESFA is actively looking for a site somewhere in the suburbs. Total reg at Boskone 24 was 4425.

(DSK) LHE Report, January: Assets- 2769.26, Income- 223.34, Expenses- 36.87, Equity- 2955.73, Profit- 186.47. February's LHE Report RSN! The February bank statement is late, like January's was. Also, the LHE has been a non-student at MIT for the last month! I got a note from the registrar yesterday saying I was registered for zero credits, so I went and registered.

(JME) Jourcomm: write for the next issue of TZ! I want it out before next R/O week.

(BPS) Sitcomms: Channel 2 is starting to show the Colin Baker Dr. Who episodes. Also, next Tuesday at 9 PM is a 2 hour TV movie called Time Stalkers. TV Guide liked it.

(Some random) I got a flyer in the mail saying that a seventh doctor has been picked.

(JME) Sitcomm: Outlaws has been canceled.

(BPS) Moocomm: there's going to be a Zippy the Pinhead movie. Randy Quaid beat out John Lithgow for the leading role.

(JME) Pseudo-Moocomm: The Wizard of Oz is on TV tonight for the 47 zillionth time.

(SSDT) Panthercomm: the SFWA paperbacks have replaced the reserves; I take credit for exchanging them, Phil Nesser gets credit for reshelving the now-circulating paperbacks.

\goto{Old Business}

(JAH) Thom McKendree sent us that flyer he promised us last week.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: both Playboy and Penthouse have expressed an interest in having Fawn Hall, Oliver North's former secretary.

(DSK) Minicult: the National Weather Service issued a false weather bulletin stating that Rockford, Illinois had been destroyed by tornadoes. They were trying to test their Emergency Warning System and somebody pressed the wrong button.

(JME) Minicult: a federal judge in Alabama has banned 45 textbooks on the grounds that they promote secular humanism. The state of Alabama has not yet decided whether to appeal; if they don't the ACLU and the People for the American Way will.

(DSK) Minicult: in Longbranch, New Jersey, it is now against the law to tell ethnic jokes on the job.

(JAH) Motion to commend Sue Hagadorne for not being a banana.

Motion seconded, passes everybody-Janice-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1728 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}