\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 4, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected copiously.

(BPS) Motion to approve the minutes as Rob can't spell or type. Motion seconded, passes all the keyholders who count-all the keyholders who don't count-everyone else +Spehn.

\goto{Committee Reports}

(TG) Albaniacomm: Albania and Greece are finally at peace, having decided that World War II is finally over. (The Skinner notes that 1987-1945=42.)

(DSK) Skinner Report: Brazil "Washington" was all right.

(BPS) Sitcomm: Sunday at 11 PM, Channel 2 is showing "Trial of the Time Lord" part one- that's with Colin Baker. Channel 2 may be punting Doctor Who to this time slot permanently.

(TG) Moocomm: Little Shop of Horrors and The Purple Rose of Cairo respectively this Wednesday and Tuesday.

(HAM) Sitcomm: the new Doctor Who in Britain starts September 7- we may get it within a month.

(BPS) Moocomm/Cornelia Otis: in Jerusalem there is a rule against showing movies on the Sabbath but cultural events (such as a short lecture followed by a movie to illustrate the lecture) are okay. Various ultra-fundamentalists have been rioting because of this, so some theater owners are showing Body Heat, Little Shop of Horrors, and The Life of Brian in response.

(KM) Hugocomm: Winners are posted on the door. Joe Haldeman is one of the Pro guests of honor in Holland in '90.

(CH) Moocomm: The Brattle Theater is showing classic silent comedies.

(JH) Moo/Bookcomm: Wordsworths in Harvard Square is moving stuff around. Among the signs showing how to find the SF section is "New SF books aren't in the eighth dimension, they're in New Jersey- no, wait, they're over by the window.

(BPS) Adamscomm: from the McPaper- Doug Adams, commenting on his second and last Dirk Gently book: "Having given the world a four part trilogy, I feel I owe it a two part trilogy just to even things up."

(KM) Move to ask Piers Anthony to stop writing books for the next five years. Motion seconded, passes by acclaim (much rejoicing).

(HAM) Aloha Lenscomm: You're all safe now, the batteries in my flash just died. (Much rejoicing.) (KM) Move to commend the batteries. Motion seconded, passes by acclaim.

(JME) Jourcomm: TZ real soon now. Addendum- my last issue, Ken and I are moving to Schenectady in November.

(JME) Pseudo-Picniccomm: I have a picture of a woman I think we should recruit for MITSFS. She really knows how to sacrifice a watermelon.

(TG) Flushcomm: A Calvin and Hobbes about going to the bathroom in hyperspace is now on the ZGT.

(JME) Whooshcomm: A private foundation has launched an advertising campaign to promote the US space program. One ad features Willie Nelson and Frank Sinatra.

(JH) Pseudo-Fweekcomm: Activities Midway this week.

(JME) Pseudo-Libcomm: Harbingers' used bookstore appears to be closed.

\goto{Old Business}

(BPS) I know someone who can get Meretsky's home phone number, but Planetfall is out of print, so the Tech's number can't be removed without a recall.

(HAM) My wallet is still missing.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: A dentist was suing Johnny Carson because he was offended by a monologue on dentists, and demanded a smirk-free apology. Carson's response was another series of jokes direct at the Long Island dentist, including: "Were it not for dentists, we would never have the opportunity to look up a grown man's nose."

(BPS) Minicult: from August 13 Globe: a woolen mill owner accidentally fell onto a spool and was suffocated as hundreds of yards of yarn were automatically spun around him.

(BPS) Minicult: in Louisiana a lawyer stood up in a boat during a thunderstorm, raised his hands, and proclaimed heavenward, "Here I am!" Moments later a lightning bolt struck him dead. At the time of his death, the lawyer was representing a man accused of recklessness in a boating accident that killed three on the same lake.

(CH) Minicult: "Man, 82, bikes 80 miles a day on bananas." He claims to eat only raw bananas, never cooked or with fancy sauces. (TG) That doesn't sound very appealing. En masse: Albanian.

(BPS) Minicult: a pilot fell out the back of a small passenger plane. The copilot notified the Coast Guard and made an emergency landing five minutes later, after which he discovered the pilot still hanging onto the stairs outside the plane by his feet and one hand. The pilot suffered only minor abrasions.

(JME) I was going to make a banana motion. (BPS) But I still have more Minicults. (JME) Then save them up and dole them out in small doses. (This results in an unintentional Albanian motion on JME and a Finger motion on some random.)

(Malcolm Y) Minicult: I spoke to a convention of bellydancers. They had never heard of SF conventions, so I told them to get in touch with MITSFS if they wanted to learn more.

(BPS, Albanian translation from JME) Motion to give anyone who calls us up about SF conventions Steve Meretsky's home phone number and a banana. Motion seconded, passes 20-19.9-much less than 20 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1729 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}