\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 16, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

There are no minutes, or Onseck.

(JME) Motion to commend the minutes as more concise than usual.

Motion seconded, passes 20-less than 20-4 +Spehn.

\goto{Committee Reports}

(JME) Sitcomm: the last episode of Max Headroom is being shown tonight.

(BPS) Addendum- the Glob's TV columnist said the main reason the show failed was because you had to pay attention to watch it.

(JME) Jourcomm: TZ Real Soon Now. If anyone can do nice simple block lettering please talk to me after the meeting; I need something lettered.

(KM) Rosfap: I've been thesizing so Rosfap stuff hasn't really been getting done.

(BPS) Cornelia Otis: Reagan wanted to give a TV speech encouraging all Americans to write to their senators, encouraging them to vote for Bork. None of the three networks would carry it. It only appeared live on CNN.

( ) Motion to commend the networks for finally showing some intelligence. Seconded- acclaim.

( ) Pseudo-Fweekcomm: the manager of the UA convenience store was a close friend of the UA president. In a letter to the Tech, the UA stated that accusations of favoritism were insults. (The manager has resigned.)

(BPS) Acquisitioncomm: I have a few posters from my housemate for Eyes of the Dragon, and CJ Cherryh.

( ) Bananacomm: The international banana association had protested to PBS because an upcoming program on safe sex hosted by Ron Reagan Jr. features a condom being peeled over a banana, saying "the banana is an important product and deserves to be treated with respect and consideration." Article attached.

(BPS) Stupidcriminalcomm: A bank robber in Marlborough claimed he had a bomb in his satchel. He took the money and left the satchel behind. Police examined the satchel and discovered men's toiletries and the thief's driver's license. He was arrested. Article attached.

(BPS) Moocomm: we saw The Princess Bride last Friday. Personal review: they said it couldn't be done, and they were right. It falls far, far, far short of reading the book.

(JME) STrekcomm: channel 5 is running STrek tonight instead of tommorrow this week. Last week's sequel was a lot better than the original episode The Naked Time.

(BPS) Addendum- Gene Roddenberry can die a happy man; he finally got to show a woman's navel on Star Trek.

\goto{Old Business}

En masse: yawn.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: last Friday a police officer in Brooklyn radioed he had found a possible nuclear warhead in a privately owned truck. A crowd of emergency workers discovered two sealed metal containers, each holding about 5 grams of radioactive iridium-192, used to treat cancer patients. Article attached.

(JME) Minicult: a Texas woman was charged with theft by deception after being baptized into the Mormon church for about the sixtieth time. She was doing this to gain the food, furniture, and rent assistance from churches across the country. Article attached.

(BPS) Minicult: an 11 year old Mensa member with an IQ of 142 wanted to get the license plate "STUPID" for his car. The Connecticut DMV turned him down, saying it might be viewed as a negative comment on the DMV or the driver who reads it. Article attached.

(BPS) Minicult: I have a subscription to Time, and found three separate blow cards for subscriptions at 1.12, 0.89, and 0.56 an issue in the same week's issue. Copies attached.

A Miller motion is made and fails by Skinnerial decree.

(RvdH) Motion to commend Ron Reagan Jr. for being hung like a banana.

(JME) Amendment- and award him a banana-skinned condom.

Motion seconded, passes more than enough-less than enough-not enough +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1712 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}