\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 3, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the two previous meetings read by Pseudo-Onseck Scott Kitchen.

(RvdH) Motion to approve the minutes as coming in bunches, like bananas.

Fails by "Shut up, Robert."

(JD) Motion to approve the minutes as comprehensive.

Motion seconded, fails 8-lots-2 +Spehn.

(Amid a flurry of motions comprehensive, comprehensible, incomprehensible, and reprehensible, RvdH begins to sing Rabbits.)

(JME) Motion to condemn the meeting as getting less and less comprehensible.

Motion seconded, passes overwhelmingly.

(SSDT) But we still haven't done the minutes...

(JME) Motion to approve the minutes as "Shut up, Robert."

Motion seconded, passes plenty-none, not even Robert-3 +Spehn.

\goto{Committee Reports}

(JME) Sitcomm: Max Headroom premiered. It had flaws, but it was real science fiction, and practically state of the art at that. Rather like Cyberpunk. It was very good.

(RJG) Off of SFLovers' Digest- several old series will apparently be coming back next year; one such series is Lost in Space.

(JME) Sitcomm: Joan Rivers' talk show is getting such bad ratings Fox is trying to get out of the [illegible] to cancel it.

(JD) People's Albanian Embassy: from the [illegible] Goldwyn was producing a program [illegible] centered on the subject of homosexual [illegible] to him, "You can't make this picture- it's about Lesbians!" and he replied "That's all right, we'll change it to Albanians."

(SSDT) Report on Small Swimming Things: we now have TZ on microfiche up to 37. It includes 20 Years and some of the MITSFS Mitigators.

(DSK) LHE Report, March 1987: Assets- 2729.72, Income- 75.06, Expenses- 437.46, Equity- 2367.32, Loss- 362.40.

(BPS) Theftcomm: the radio got stolen from my car Saturday night or Sunday morning.

(RJG) Moocomm: Raiders of the Lost Ark Saturday.

\goto{Old Business}

(JME) Former Skinner Guy Consolmagno was apparently here; he left a note and Mike Timmreck's new address. Also, we're going to see Merryl, so we'll say hi to her for everybody.

(SSDT) The covers of TZ 39 and a recent Tech Talk have very similar fractals on them.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: from this week's Times magazine- a woman had a vision of the murder of a nurse she didn't know and went and told the police about it; they said to go away. So she organized a search, found the body, and told the police; they said "Thank you, you're under arrest." She was held for four days, at which time the real murderers turned up. She promptly sued for false arrest. A judge ruled that she had cause, and it goes to the jury this week. She's asking for 750 grand in damages.

(SLP) Disneyland has a new ride called Star Tours that puts you on a 40-seat starspeeder that takes you on a flight to the moon of Endor.

(SSDT) Minicult: Athena computers' time clocks are going to be off one hour until April 26- this is because the old day for the daylight savings time change is hardwired into the Athena system.

(RvdH) Minicult: There are persistent [illegible] three sources that they've come up [illegible] will function at 13 degrees Celsius.

(DSK) Minicult: Oral Roberts came [illegible] now says people should send him 8 million a year until the Second Coming of Christ.

(LAK) Minicult: Jim Bakker got back on PTL briefly to say that it was not because he committed adultery that he left the program, but to avoid a "hostile takeover" of his ministry.

(SSDT) Minicult: from WEEI radio- a passenger plane cruising at 30,000 feet collided with a fish. Apparently there was an eagle carrying its lunch at that height that saw the plane coming, decided it was a bigger bird, and dropped the fish which then hit the windshield of the plane.

(JD) Motion to plug Bill's ears with bananas.

Motion seconded, passes without a vote.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}