\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 2, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, Skinner, presiding.

Minutes of previous meeting read and corrected.

(JME) Motion to approve the minutes as the last ever featuring TG. Motion seconded, passes about 50-no one at all-everybody else +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: TZ Real Soon Now.

(CH) Moocomm: The Princess Bride has a sneak preview tomorrow night and opens for real all over the place next week.

(JME) STrekcomm: The new STrek series premieres this Saturday. Get your VCRs ready.

(BPS) If you have cable, it will be on WPIX out of NY Monday at 8 PM.

(CH) STrekcomm: The preview blurb for the series reads "naked" in the New England Weekly.

(SSDT) The Herald describes the new commander as having all the warmth and caring of an IRS inspector with a toothache.

(DSK) Skinner Report: I just finished up the second half of my thesis requirement. It's over.

(JME) Cornelia Otis: Michael Dukakis and Joseph Biden.

(SSDT to random) The Miami Herald caught them spending a weekend in a townhouse.

(BPS) Followup, Dukakis spoke at a luncheon in Iowa. Not a single question from an Iowan was about the Biden tape. When Dukakis met with the press afterward, not a single question from the press was not about the Biden tape.

(CH) Cornelia Otis: Bob Woodward's new book claims he met with Casey in his hospital room, and Casey admitted knowing about the Iran Contra scandal. Casey's widow calls him a liar.

(SSDT) It should be remembered that Casey was suffering from a traumatized brain at the time.

(BPS) Originally Casey's widow and the CIA were saying Casey would never have met with Bob Woodward. They've since revealed that according to the file the CIA kept, he met with Woodward at least 6 times.

(JME) Cornelia Otis 4: Entropy increased in California this morning. It wasn't even San Andreas.

(  ) Nobody's fault. Albanianed by acclaim.

(CH) Sitcomm: I saw Beauty and the Beast. It didn't fall apart that badly in the second half; I liked it.

(JME) Point-counterpointcomm: I also saw it and I thought the second half totally ruined the first half.

(BPS) Gavelcomm: I've got a donation. I found it in the street.

DSK performs a Gavel Test. Several CLINK!s later he is applauded en masse.

(HME) Gavelcomm2: I had to borrow the sport gavel this week to make an adjustment to my radiator when they turned on the heat and it started to leak.

\goto{Old Business}

(JME) Joseph Biden appeared in spirit at the British Labor Party's annual conference in Brighton this year. After an impassioned left-wing speech, one of the delegates said, "In homage to the current fashion of transatlantic oratory, I hereby give Neil Kinnock permission to use any part of my speech, now or at any time in the future." Apparently Kinnock published a book shortly before the conference and sent a copy to Senator Biden. A Labor Party spokesman said "It was a bit naughty of us, but you never know, he may have found something else to lift." Article attached.

(BPS) Move to commend Switzerland for containing TG.

Motion seconded, passes apparently by Skinnerial decree. An addendum by JME to redefine Switzerland as Albanian was deemed unfair to Switzerland and failed to be seconded.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Dumb Criminal Report: A colorblind counterfeiter printed fake bills with the serial numbers and treasury seal in black instead of green.

(JME) Minicult: 9/28 globe, 5 people were arrested after nearly 170 people holding tickets on a canceled airline flight besieged an Eastern Airlines counter at Miami International Airport. See attached article.

(JME) Picocult: A proposed amendment to the California State Constitution would prohibit all members of the California Bar Association from holding public office or practicing law in California courts.

(JH) Minicult: I saw a black and white comic called Honor Among Thieves written by Julia Eclar.

(KM) Minicult: We now have authors' series from A to Z, Piers Anthony's Clthon series down through Zelazny's Alien Speedway. None of these books are actually written by the named author.

(CH) Household Fun Minicult: 1- "Thirsty Gardener Gulps Down Gal's Diamond Ring," 2- "Golfball CAke is a Real Blast," 3- "Harebrained Housewife Blows Home to Bits," 4- "270 Gallons of Oil Swamp Cellar When Worker Goofs." See attached articles.

(JME) Minicult: the city of Burbank, CA has just outlawed toy guns that look like real guns in the city limits.

(BPS) The Daisy Company has announced that its line of bb guns and such are now going to have day-glo orange barrels.

(JME) I'm not so sure Ken and I should move to Schenectady. They just sentenced a woman today for killing one of her eight children, and they suspect her in the deaths of seven others. Supposedly they all died from sudden infant death syndrome; now they think she smothered them all.

(VHS) One of the claims from the earlier trial was that the deaths were caused by an extremely rare genetic disorder, present not only in the six natural children but also in the one who was adopted.

(KM) Those jumping genes are really amazing.

(HAM) Motion to send a banana-colored day-glo toy pistol that's a member of the California Bar Association to Burbank.

Motion seconded, passes everybody-nobody-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1737 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}