\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 11, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, Skinner, presiding.

Minutes of previous meeting read and corrected.

(BPS) Move to approve the minutes as bounced. Motion seconded, 6-7-maybe 4 +Spehn. Motion fails.

(HAM) Move to approve the minutes as we've done this one already. Motion seconded, passes 10-5 and a chair making a rude noise-1 +Spehn.

\goto{Committee Reports}

(S??) Moocomm: Masters of the Universe tomorrow at LSC.

(DSK) Moocomm2: LSC has revealed the 1988 IAP schedule. They're showing American Werewolf in London, Monty Python's Life of Brian, Rollerball, Barbarella, Predator, and the Sci-Fi Marathon is the 27th, Heavy Metal, and the Reg Day movie is Robocop.

(BPS) Klutzcomm followup: if you do forget to put the cap on your pen before putting it in your pocket, Wisk works very well; I managed to save the shirt.

(VHS) Onseck report: following the new trend among MITSFS members, I've decided not only to go to Schenectady but also to go in the hospital to get my ear operated on during IAP, so I won't be around for most of IAP, but hopefully I'll be able to translate Herb's mumbling in the minutes afterwards.

HAM is unanimously Albanianed for muttering "Ear, ear!" (I'm not that deaf, Herb.)

(BPS) Audiocomm: On the drive over, I heard a radio ad for the book 2061. It was supposed to be HAL talking, but the guy they had didn't sound anything like Douglas Rain.

(BPS) Strekcomm: A, it's true, they are in reruns; B, they finished up their first-run season with their best (only good) episode so far, the one about Jewish mothers in space.

(BPS) Dullcomm: what a dull meeting.

Phonecomm (time warp from New Business): Ring. It's a Jourcomm report from Lisa: Write for TZ.

\goto{Old Business}

(HAM translated from the Albanian by order of the Skinner) The new Dr. Who premiere that was supposed to be Jan 15 on NJN is now Jan 9.

OBA: um, us, uv, ur.

\goto{New Business}

(KJ) That person who was supposed to be here doing research will not until later. He was impressed with the amount he got done in one day.

(HAM once again translated per the Skinner) Minicult: There was an article in a newspaper in Sydney (undocumented): the police got a phone call that someone had locked a wombat in a telephone booth. They went expecting to find a drunk and instead found a wombat in a telephone booth. They lassoed the wombat, set it free in the scrub, and on the way back they saw another wombat in a telephone booth. They caught that wombat and released it. Then they got a phonecall of a third wombat trapped in a telephone booth. Catching on, they finally found the guy who was putting wombats in the phone booths and arrested him. They released him to be charged later because they couldn't find anything that said it was illegal to lock wombats in telephone booths.

(VHS) Minicult: Unfortunately also undocumented, and with corrections by Ken Johnson- in Thursday's NY Times was an article about some guy working for Lyndon La Rouche Jr. He was sent to Boston to see what the federal investigators were digging up, and instead he went to a Star Trek convention in Scranton, PA, where he called headquarters, said he was in Boston, and the feds were really finding things out.

(Seth) Minicult: also undocumented, this fellow who founded an organization called Homosexuals Anonymous, supposedly to "cure" gay people, hadn't quite changed himself. A lot of people who went through the "therapy" say it was actually a cover for sexual abuse. The guy liked to give his clients nude massages so that they could get used to being in the company of another man without any sexual activity going on.

(KJ) The roads are less safe than they were two days ago. Kathy Godfrey got her drivers license yesterday.

(Random) Minicult: someone in my dorm got a letterbomb, and as soon as he opened it up and realized what it was, he tried to wiggle the wires and figure out why it didn't work. 

(HAM) Move to send a bunch of undocumented bananas to the person who sent the bomb.

Motion seconded, passes 10-5-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}