\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 13, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, at Boskone, in Room 736 of the Boston Sheraton, which is temporarily defined as the library for the duration of the meeting.
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting unread and uncorrected.

(Chip) Motion to commend the Onseck for not showing up.

Motion seconded by some random.

Motion fails 9-11-5 +Spehn.

(Something unidentified happens and there is a flurry of Albanian Finger Motions and other highly random exclamations. Passes by Skinnerial decree.)

\goto{Committee Reports}

(JME) Jourcomm: TZ exists! No thanks to the incompetent bozos at Graphic Arts whom we are NEVER EVER EVER dealing with again! There's a reason they're so cheap.

(All join in on a chorus of "GRAPHIC ARTS SUCKS!!!")

(JME) Their final screwup was ordering the wrong cover stock which could not take double-sided printing, so the inside front and back covers are now an inserted page at the end of the zine. Earlier, they tried to screw up our pagination and they did a lousy job on the Xeroxing. It still looks good though, if I do say so myself. And Connie managed to sell one of the free extra covers we got to someone for 50 cents, which is clear profit.

(SSDT) Huckster Table Report: Profit estimated at 100 dollars.

(JME) STrekcomm: Just read in the Glob that Channel 5, the local ABC affiliate, is going to be carrying the new Star Trek series, starting in September. After Channel 5 has run them twice, probably in a 7:30 to 8:30 time slot on Saturdays, Channel 68, which recently acquired the old series, gets to show the new series as reruns.

(BPS) Mortcomm: ABC's science editor Jules Bergman passed away last Wednesday at age 57.

(JME) Huntcomm: Scavenger Hunt was, and was quite successful. We had a large audience and we have candy around here somewhere. The Lithuanians destroyed the Lunarians this year, and the Lunarians are vowing revenge. We got to drink a very tasty glowing green and very alcoholic Pan Galactic Gargle Blaster thanks to the Lunarians.

(SSDT) Pianocomm: the position of Titancomm goes to Scott Kitchen for holding the pseudo-gavel block for this meeting.

(JME) Famecomm: the best suggestion we've gotten so far for commemorating the 40th anniversary of MITSFS at Noreascon 3 is a gavel catch limited to NCFI members.

(KM) Pseudo-Jourcomm: while I was working the table in the Huckster's room, who should walk by and purchase a copy of Twilight Zine but Tappan King, editor of Twilight Zone. This was after I spent several minutes begging him not to sue the shit out of us. His response was "Part of my job is to protect people like you from people like Viacom." Basically, as long as we don't do anything stupid like writing the corporate heads and asking their permission, they won't know and he won't tell them. He also bought a Best of TZ, so he's a great guy in our book.

(DSK) LHE Report: there is still no LHE Report, as the bank still hasn't sent us the statement.

(BPS) People's Albanian Embassy: they are almost perfect in Albania, according to Time. In Albania's recent parliamentary elections, every one of the Albanian Labor Party candidates got 100 percent of the votes. One vote got ruled invalid, though, so they'll have to try again next year.

\goto{Old Business}

(KM) There are a lot of old MITSFS people in the room right now. Including an Albanianed Seth Brinebard and the ever-present George Phillies.

(It becomes necessary to call on the Pseudo-People's Albanian Embassy (BPS) to translate for the Albanianed Seth, and due to an on-tape request, the translation session is hereby transcribed.)

(Albanian) Zolkug Seth Brinebard.

(P-PAE) I'm Seth Brinebard.

(Albanian) Zolkug Ex-Keyholda.

(P-PAE) I'm an Ex-Keyholder.

(Albanian) Left leg memba muchaka ourg ba-jzing!

(P-PAE) My left leg was a member for much longer than I was.

(There is a discussion of a Courtney Skinner who has artwork in the art show but is absolutely no relation to the MITSFS's L. Court Skinner.)

(KM) Motion to condemn Courtney Skinner for sounding like our Skinner!

Motion seconded, passes 18-6-5 +Spehn.

(George) I recommend that we define Courtney Skinner to be related to our Skinner.

Motion seconded, passes by acclaim.

(SSDT) Motion to define Courtney Skinner (Onseck's note: who is male) as L. Court Skinner's daughter, the one who goes to MIT kinda sorta maybe.

Motion seconded, passes many-2-3 +Spehn.

OBA: um, us, uv, ur, "what about the usual debate?"

\goto{New Business}

(JME) Minicult: apparently Mexico City has a horrible air pollution problem. When one official was asked what he intended to do about it, he replied that individuals should be willing to take some responsibility for alleviating the problem by breathing through their noses.

(LAK) Minicult: in Rekon-5 this year, the players could choose who they wanted to be. One player chose Ronald Reagan. He didn't show up. At the closing ceremonies, the GMs said it was because he was still taking a nap.

(JME) Minicult: a new use for a Brass Rat. At the Boxboro party last night, they required proof of age before they'd let you drink, and I hadn't brought any. The guy at the door noticed I was wearing my brass rat in the "graduated" position, and said "I've only known one person who graduated from MIT before being of legal drinking age, so I guess you're okay."

(SSDT) Minicult: this may or may not be true. Rumor has it that the Apple Corporation bought a new Cray computer to design the next Apple on. Well, when this got back to Seymour Cray, he said "That's funny- I'm designing the new Cray on an Apple."

(JME) Pseudo-Timewarp to Jourcomm: this issue of TZ has an article I wrote about meetings that was extensively researched and includes the entire contents of the Old Business Algol.

(KM) Minicult: scientists have discovered that they can make extremely sensitive biosensors from common supermarket items. A banana, for example, can be used to detect a certain brain enzyme.

(George Phillies) Minicult:

(SSDT) Minicult: two Western newspapers ran an article about a new, very potent hallucinogen called Akima that produces, supposedly, an unparalleled high. The papers further stated that the column of paper the article was printed on had been coated with the odorless and tasteless drug, and that all anyone had to do to get high was to crumple up the column and suck on it for more than 3 minutes. Hundreds of people did so, failed to get high, and called the newspaper asking for stronger copies.

(JME) Minicult: stupid Anglos department. Miss New Mexico, in the Miss USA pageant, wore a Hopi Indian outfit that got the Hopi Tribe very upset, as the outfit she wore was very religious to them- almost sacred in nature.

(AA) Stupid Anglos Minicult part 2: Delta Airlines was doing an ad in Spanish. They wanted to say "sit on leather" to represent the leather-upholstered seats in their planes, but they didn't realize that the phrase "sit on leather" is Spanish is idiomatically equivalent to "sit naked."

(George Phillies) Minicult: a Gallup poll tried to determine where Americans thought Nicaragua was. All they required was the correct continent. Most people thought Nicaragua was either Burma or Bangladesh.

(SSDT) Minicult: the medical profession won the top place on the Unicorn Hunters' Dishonor List of Inharmonious Uses of the English Language. The prizewinner was the phrase "The patient did not fulfill his wellness potential." This not only obscures the fact that the patient died, it also places the blame for it on the patient.

(BPS) While looking through my roommate's Publishers' Weekly, I noticed that the title of a new nonfiction book due out soon by a doctor about the medical profession is "Try to Kill As Few Patients As Possible."

(BPS) Minicult: Erno Rubik, inventor of the Cube, had his villa in Budapest burglarized by someone who used brute force to get in and then seemingly rifled through Rubik's papers, including some of his plans for new puzzles. The police think he may have been looking for the solution to one of Rubik's puzzles, but apparently not finding what he wanted, he settled for Rubik's VCR instead.

(BPS) Minicult: from Sunday's Glob- Hamilton Collection, which puts out collector plates for various things, has started putting out Star Wars plates, of which plate number one is the Han Solo plate.

(At this point, the Onseck and some Old Business, Merryl Gross, walk into the room. Just in time for...)

(KM) Move to commend scientists the world over for finding new and better uses for bananas.

Motion seconded, passes everyone-2-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1738 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}