\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 13, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(HAM) (Waves arms, making a "Herb" motion.)

Motion seconded, passes nearly everyone-a few-the same as a few +Spehn.

Phonecomm: it's Rob Gates, calling for LAK.

\goto{Committee Reports}

(DSK) LHE Report: LHE Report RSN!!! Due to lab reports, no LHE Report this week.

(BPS) Mobcomm Report: I think I'm technically unemployed this weekend.

(KM) Pseudo-Jourcomm: write for TZ!!!

(BPS) Sitcomm sub 1: Outlaws is gone, but at the same time NBC has renewed Alf.

(SSDT) Panthercomm: we have a new keyholder phantom, Justyna.

(CH) HappyBirthcomm: today would have been L. Ron Hubbard's birthday. As of last report, he's still dead.

(DSK) HappyBirthcomm sub 2: tomorrow would have been Albert Einstein's 108th birthday.

(BPS) Sitcomm sub 2: I watched Time Stalkers. It was marginally above average as TV movies go, and was frustrating in that it had enough good stuff to make the stupid moments very annoying.

(SSDT) Theftcomm: what happened to our membership sheets?

(CH) Bookcomm: Wild Cards II is better than Wild Cards I.

(BPS) Strange Variations on Moocomm: the advertising for Nightmare on Elm Street III includes some exit polls of movie patrons, including some teenager who says "It's better than all of them put together!" which implies that the first two had a negative value.

\goto{Old Business}

(All) Hi Herb!

(SSDT) Last week, between Thursday and Friday, someone scribbled on our schedule with felt tip, which is removable only by alcohol, which also removes the coating on the plastic. So please try to show up for your hours so our schedules won't get vandalized.

OBA: um, us, uv, ur.

\goto{New Business}

(SSDT) Last Sunday I tried calling the library, and Simson Garfinkle answered and told me I'd gotten the campus police.

(BPS) Minicult: some radio station is, as part of the effort to combat AIDS, giving away condoms- with the radio station's call letters on them.

(JME) Minicult: a nuclear physicist in Florida has succeeded in transmuting gold to lead.

(CH) Minicult: an interesting religious pamphlet- it says "Beware of religious fanatics handing out pamphlets!" It's from Jews for Jesus.

(JME) The Tennessee National Guard came up with this great plan for increasing patriotism among high school students- they staged mock invasions of several schools, including having helicopters deliver soldiers who fired rifles with blanks, followed by someone giving a speech and passing out American flag decals. They did this to 18 schools until criticism forced them to stop.

(KM) If they tried that at my high school, they might meet armed resistance...

(BPS) On yesterday's Family Ties, they did a very nice surrealistic treatment of the "dealing with death" theme.

(JME) Minicult: 109 subscribers to National Geographic have canceled their subscriptions to protest the magazine's changing over to metric measurements.

(KM) Janice, we forgot to bring the Bananimal!

(JAH) Motion to condemn them for leaving the Bananimal at home.

Motion seconded, passes everyone-"No, no, not Ken and Janice! Awwww!"-Janice +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}