\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 12, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Hawthorne, Summer-Skinner-it-still-sounds-dumb, presiding.

Minutes of the previous meeting were read and corrected.

Move to approve the minutes as the result of having been run through an Albanian spell-checker on auto-correct.

Motion seconded, passes everybody but the Pseudo-Onseck-a few-a few squawks +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: write for TZ, pleeeeeeeeease write for TZ- I'm serious! If I'm gonna get an issue out before Ken and I have to leave the area, you've got to get it to me this summer, and I would really like to put another issue out. Please!

(JH) Skinner Report: we now have a non-pseudo type Onseck (read: sucker) for the summer- it's Ted Ts'o. So what?

(JH) Pseudo-Pianocomm: if anybody knows of any keyholder tasks that need to be done, I have some suckers- er- prospective keyholders who need things to do.

(KM) RosfapReport: we got a bunch of new fanzines, including one that got misfiled somehow- the May issue got processed after the June issue. We also got a very nice fanzine No Void, Instant Message, which is the NESFA (for the sub-fan interested in Robert's Rules of Order).

(SSDT) Whooshcomm: three rockets went whoosh by mistake. They got struck by lightning while sitting around on the launchpad. Two of them went off on their normal trajectory where they were supposed to be tracked, but the tracking systems weren't on because it was the wrong time. The other one was pointed completely the wrong way and hit the water very quickly.

(KM) Meyercomm: apparently NESFA is real close to signing contracts for its Springfield Boskone- they will be roomed in a Marriott and in a Sheraton Terra- not enough room in one Springfield hotel. Promise to hotels: "While casual clothing is acceptable in the restaurants, nudity, costumes which shed,  etc. are not." Membership will be 25 dollars.

(CH) PersonalAchievementcomm: I bought my own Mac! Mine! Mine! Mine!

(JME) Moocomm: Witches of Eastwick is opening tonight. Probably the greatest typecasting in history- Jack Nicholson as the devil. It's been getting good reviews.

(BPS) Moocomm II: Predator probably opens today or tomorrow given the intensity of the publicity. It got bad reviews.

(Editor's note- I saw it on Saturday. It was awful!!!!!)

(JME) Pseudo-Moocomm for a pseudo-movie: there is a movie opening today, which I won't even dignify by giving its name, which is basically sponsored by Glad trash bags and is starring Tom Bosely who does their commercials. It's a promotion- you get a list of clues and then you see the movie and if you can figure out where a million dollars was hidden based on the clues and the movie you get to be in a drawing for a million dollars. Most nonsentient beings should figure it out...

(JAH) From the Department of Wretched Excess: This came in the mail from Greg Press- "Classic SF now on sale- offerings from the masters of the genre." What you really get: hardcover versions of, for the most part, incredibly awful Star Trek novels at 8.50 a shot.

(JAH) Sitcomm, sort of: I was examined this week by a Dr. Peter Blight. For those of you who don't watch St. Elsewhere, Dr. Peter Blight was a character on the show who turned out to be a rapist and was shot by a woman he was trying to rape.

(BPS) Mobcomm: I got an AT clone that operates real, real fast; I got 40 megs of hard drive operating at 28 ms, I got a copy of RBase system V; all I gotta do now is figure out how to use any of this stuff.

Phonecomm: RING!

\goto{Old Business}

(JD) One more final reminder- Gay Pride march tomorrow. You are still invited.

(JME) Fawn Hall- while she didn't smuggle documents in her underwear, she did smuggle them out in her clothing. She was being questioned about this by the committee, and she said, "Well, what if the KGB was coming to the door," and one of the committee hastened to point out that it was not the KGB that was arriving, but the FBI.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: graduates of the Harvard School of Public Health this year celebrated by tossing condoms in the air. The condoms had the Harvard School of Public Health in Latin on them. It also had in Latin the equivalent of "For safer sex." Some of them had been blown up like balloons...

(BPS) Minicult: from the Glob- two men armed with a cicada stole 25 dollars from a Cincinnati restaurant's cash register after using the bug to scare away the cashier. They walked into the Grand Slam restaurant, brandishing a cicada, which is big and ugly but harmless. They thrust the bag at the cashier, who then fled from her post. When she returned, she found 25 dollars missing. There probably won't be any followup on this, but God, I wish I was the judge sentencing these guys...

(JME) Minicult: problem in East Lowmeadow (hick place way out west)- after implementing a sex education program (which parents can refuse to have their children participate in), there is a group of parents lobbying to abolish it because other children are telling their children what they learn in class. To quote a parent with an 8th grade girl: "All children should be told about sex is that when God wants you to have a baby, you'll have one."

(BPS) Minicult: PTL today filed for protection under Chapter 11. This unfortunately doesn't mean they're going bankrupt- quite the contrary. Still, it's nice to see them going through some of the motions of dealing with the real world.

(JME) Free zines available over there on the table. I won't make any guarantees whether you'll like them or not, but they're free.

(CH) Minicult: "If you need cocaine, call us." A lot of people called this number, and it was actually a hospital treating cocaine addicts. It was in Los Angeles; maybe they all thought it was legitimate.

(CH) Minicult: "Toys that teach the right stuff." Parents who have long complained that children's toys are too violent and unhealthy now have an alternative, thanks to a new toy company that is rocking the business world with success with toy characters from the Scriptures. Its Heroes of the Kingdom action figure sets feature characters like David and Goliath and Samson and Delilah. Each set comes with two figures, an authentic costume, a full-color book, and a cassette tape with "original music and sound effects." Prince of Peace Pets is a collection of 24 stuffed animals with names like Born Again Bunny and Guardian Angel Bear. "Our toys teach children the values of love, cooperation, sharing, and obedience, in contrast to many of today's toys and many of today's television venues."

(BPS) Minicult: in France, the government has veto power over children's names. The local government official- the local prosecuting attorney- sent policemen to confiscate the family book and ordered the girl to be known by her middle names. He said he didn't like those names much, and could have voided them too, choosing names of his own choosing, but he "wanted to be a nice guy about it." Various French names which have been flushed are the French words for cherry, Manhattan, etc.

(JME) Minicult: the Virginia DMV pulled an interesting one recently- in 1983, the agency issued a vanity license plate reading ATHEIST. For three years nobody made any fuss about it. In 1985, someone filed an anonymous complaint that he or she was offended by it, and on the basis of that complaint, the DMV ordered that he surrender the license plate, and he sued, claiming it violated his freedom of expression. This week, the Supreme Court refused to give him a hearing.

(JD) Minicult: there's now a book out called Maldicta- it is a collection from the journal of the same name. Maldicta is a scholarly journal about obscenity, verbal abuse, verbal aggression, and tasteless humor, all of which is meticulously analyzed. So half of it is scholarly and half of it is unprintable. They have an article in the collection on what the government considers unmentionable license plates, like QQQQ- you figure it out.

(CH) Minicult: they're working on a new version of 1-2-3. It's codenamed Gallifrey. They are also working on a natural language add-in for it; this is codenamed Daleks.

(JME) Minicult: Zenith has the slogan "The quality goes in before the name goes on." Well, on an annual report recently, there was a metallic sticker that had that phrase. If you peeled off the sticker, you would find a misspelled version of the same slogan.

(SSDT) Minicult: Louisiana is running a special on execution- three in the last week. The last man they executed's last words were "I'd rather be fishing."

(JME) Minicult: East Berlin got the closest it ever gets to a riot. There was an open air rock concert being played in West Berlin, and the East Germans wouldn't let the teenagers on the wall or even near it to hear the concert, and they got fairly close to a riot. Apparently television cameras on the West Berlin side of the wall (elevation being a good thing) got really good footage of all this; despite all that, the East German government is denying that there were any riots or scuffles or anything.

(JME) Motion to award Adina a banana if she starts coming to meetings again.

Motion seconded, passes enough-not nearly enough-somewhat more than not nearly enough but less than enough +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17-something 'cause I lost my watch on the T SST.

\vspace{18pt}

\centerline{Submitted without really knowing what I'm doing...}
\centerline{Theodore Ts'o, Suckered Into Being Summer Onseck}
\centerline{Note: any blank spaces are not to be construed that I didn't know who the speaker was; it signifies that the voice was a disembodied speaker from the void, and therefore couldn't possibly be identified.}

\end{document}