\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 24, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read.

(DSK) Note that the Vice and Phil Nesser, during the reading about the Lazer-Tag incident, cocked their toy automatic pump-action eight-gauge sawed-off shotguns.

(JME) Addendum to the minutes: during last week's meeting, Ken succeeded in cleaning off the blotch Mike Friedman left on the blue chair. He used Bestine, which not only did not dissolve the chair, but left it a much brighter blue than it used to be.

(Optional section- to be read if "Presence Mike Friedman = No")

(LAK) I think we should make Michael Friedman a small splortch on the chair.

(JAH) Motion to make Michael Friedman a small splortch on the chair.

(BPS) But not to read this motion correctly at the meeting next week if Michael is present at the time...

Motion seconded, passes plenty-"No, no, unfair to blue splortches"-1 and 3/4 +Spehn.

(End optional section)

(There are a bunch of random motions made involving hair, blue splortches, and no weapons zones, all of which eventually get smushed into one motion.)

(JAH) Motion to approve the minutes as being concatenated.

It passes by Skinnerial decree.

\goto{Committee Reports}

(JME) Bananacomm: I found a listing for BananaRag, the literary magazine about bananas. It sells for 2 dollars a copy and it's an annual. The address given lists the editor as Anna Banana.

(BPS) Mortcomm: Actor Dick Shawn, who played Ellis Dee in The Producers died at age 63 in what may be pathetic or triumphant for a comic actor: he collapsed on stage from a heart attack and the audience at first thought it was a gag.

(CCH) Mortcomm sub 2: Mr. Greenjeans died.

(JME) Jourcomm: I got more art. One person even wrote in thanking me for requesting art. Also, PWFTZ.

(JAH) Pseudo-ROSFAP, sort of: a person named Tomiko Toland from Columbia University called on Tuesday. She and some other people are trying to put together a professional-type science fiction magazine produced by and primarily for college students. They're looking for someone to be their representative at MIT, and they're actually offering money. I have a name and number for anyone who's interested.

(JME) Meyercomm: among the sites under consideration for the next Boskone are Springfield and Hartford. They can't get any place large enough in Boston. The closest site to Boston they're considering is Marlborough.

(BPS) Sitcomms: the season-end episode for Sledge Hammer! is supposed to be a cliffhanger involving Sledge trying to defuse a nuclear bomb. Star Trek: The Next Generation has chosen ILM to do their special effects, and rumor has it that in the time of the new show, not only will there be peace with the Klingons, there will actually be Klingon crewmembers on the ship. Last Tuesday's Max Headroom came perilously close to plagiarizing Neuromancer in several ways; the one I noticed was the use of the term "ice" to represent computer security systems, as in "We need someone to crack some ice." This was probably swiped directly from the book. Also, the show seems to be getting weaker as the season progresses.

(JB) Picniccomm: The flyers are ready and need to be addressed and stamped, so if anyone wants to help... The date has finally been set for May 10.

(JME) Somecomm: Anyone who's here is missing the "Writers of the Future" event, a free pseudo-convention awards ceremony sort of thing being held on top of the World Trade Center in NYC.

(BPS) Cornelia Otis: Federal agents have seized everything of Lyndon LaRouche's they can get their hands on, including his estate. He and his associates owe approximately 21 million in federal contempt of court fines. LaRouche himself is in West Germany and blames the KGB for these events.

\goto{Old Business}

(JME) Greg Ruffa, who still has our minutes, has bought an attending membership to the 1988 Worldcon, which I also plan to attend. If he still hasn't given us our minutes by then, I will try to cooperate with other people to ambush him and beat him until he gives us our minutes back.

(BPS) When the Red Sox were celebrating the 75th anniversary of Fenway Park last week, somebody commented that 75 years ago, when Fenway opened, the Titanic sank and the Red Sox won the World Series. Last year, the Titanic was found and the Red Sox sank.

(JME) There had been a rumor that an old Lost in Space episode had predicted that the Red Sox would win the Series in 1986. Well, "Ask the Glob" went and checked this out and discovered that no, what had been said on the episode was that the Angels would lose to the Mets in the 1984 Series. Neither of those teams was anywhere near the series that year.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Jim Shooter, editor-in-chief of Marvel Comics for the past ten years now, has been replaced as head of Marvel by his New World Pictures superiors. The comics world rejoices.

(SSDT) There is a magazine called PC Clone that put its first issue out recently, but the printer screwed up and replaced the center pages of the magazine with the center pages of Playboy. So some copies of PC Clone contained five pages of Miss May.

(CCH) Minicult: I have an ad here for "The 'Word' Processor" which is a software program that allows you to scan the Bible for specific passages.

(JME) Minicult: The Reagan administration has decided that it will no longer test cigarettes for tar and nicotine content- instead, it will use the figures provided by the tobacco companies.

Phonecomm: it's someone. No one bothers to tell Tarl who, what, or why.

(JME) The sky turned green today for a while. The midwesterners I know say that the sky turns that color before a tornado, but we don't get tornadoes here. Very often.

(JME) According to a newspaper poll that appeared in Harper's recently, 45 percent of Americans polled believe the phrase "From each according to his ability, to each according to his need" comes from the US Constitution.

(BPS) Brave defender of law and justice Ed Meese was trying to get a convicted Nazi war criminal asylum in Panama until other people in the law department who thought this wasn't such a great idea leaked it to the press. The Panamanian government backed out immediately.

(KM) The Reagan library will not be at Stanford- it will go to southern California.

(SSDT) Microcult: I saw an interesting combination of diamond shaped car sign and bumper sticker. The sign said "Baby on Board" and the bumper sticker said "Go ahead, hit me- I need the money."

(KM) Minicult: The UA is having a "Go Bananas!" Spring Weekend kickoff: all the banana based food you can eat for one dollar. It's sponsored in part by Chiquita Banana, in Lobdell.

(RvdH) Motion to commend.

Motion seconded, passes more this time-none-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}