\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 5, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Hawthorne, Vice and Pseudo-Skinner, presiding.

Minutes of the previous meeting were read and corrected.

(GF) Move to condemn the minutes for something concerning Malcolm.

(KM) Let it be noted that it wasn't Malcolm who said that.

Motion seconded, fails 5 and a roonk-7 and an ARGH-a couple +Spehn.

(JME) Move to condemn Malcolm for being confused with George Flynn.

Motion dies.

(CH) Move to call the minutes an enlarged lymph node.

Motion seconded, passes 8-1-3 and a gleep +Spehn.

\goto{Committee Reports}

(RJG) LHE Report: books are done for April and May. April- income 1249.04, expenses 178.26, profit 1070.78, equity 3438.10. May- income 450.04, expenses 1140.61, loss 690.57, equity 2747.53.

(JAH) Skinner Report: still no summer Onseck, Justyna hasn't been reached. Still looking...

(BPS) Picniccomm: we had a picnic. It went well. Gavel toss winners: men's- BPS, women's- Barbara Stone, famous authors'- Hal Clement.

(JME) Bananacomm: Globe article- cure those banana blues. Lots of banana recipes and banana facts. In the Koran, the forbidden fruit of Eden was a banana. In Hindu legends, Adam and Eve were wearing banana leaves- not fig leaves- when they left Eden.

(SSDT) HackReport: Caltech hacked the Hollywood sign and made it read Caltech.

(JAH) Bookcomm: The Uplift War is out. New Douglas Adams book is also out.

(BPS) Mortcomm: Alice Sheldon, aka James Tiptree Jr., died.

(KM) RosfapReport: we got lots of fanzines including lots of back issues of Yandro, a Hugo-winning fanzine, and the 100th issue of Steffantasy, all letterpressed.

(JME) Jourcomm: Write for TZ or Ken will break your face. Deadline has to be the end of July- write!

(BPS) Sitcomm: USA Today claims Sledge Hammer has been renewed.

(SSDT) HackReport II: a 19-year-old flew a Cessna past all of Russia's air defense, landed in Red Square, and signed autographs until apprehended.

(BPS) Whooshcomm: a 4.5 inch wrench was fished out of the engine of the shuttle Discovery, after 4 years and 6 flights. And Sally Ride has resigned from NASA.

(JAH) Pianocomm: Pete Smoot has turned in his key. He's off to sunny California for grad school.

(BPS) AARRGGHHcomm: The winning entry of the 6th annual Bowler Written Fiction Contest...

Editor's note: I refuse to repeat it... it's BAD!!!!!

(JME) AARRGGHHcomm II: Hugo nominees are out. One of those up for best novel is "Black Genesis" by L. Ron Hubbard.

(JME) Nailcomm: I stopped biting them.

\goto{Old Business}

(JME) Guy Consolmagno was in town and and stopped by MITSFS.

(KM) One of the two people to ever have the right to membership in the MITSFS revoked, Patrick Gunkle, is getting lots of news coverage lately. He's developing a new science of ideas.

(JME) Fawn Hall was the one responsible for the account number mistake, not Ollie North.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: Texas evangelist Phil Phillips has put out a new book on children's toys warning Christian parents about children's toys, especially those linked with cartoons. Among his revelations: Rainbow Brite's rainbow is not a symbol representing God's rainbow following the Great Flood, but a symbol representing the rainbow bridge between man and Lucifer. GI Joe and Masters of the Universe bear occult symbols. And Care Bears are actually establishing their own religion and rituals; the symbols on their stomachs (hearts, cupcakes, etc.) are NOT Christian.

(JD) Minicult: kitty AIDS.

(JAH) Minicult: they have successfully frozen and thawed a dog.

(JD) Minicult: headline- Tribble Cleared of Cocaine Charges.

(RJG) Minicult: someone from outside of New England asked what a Fribble was, and it was described as: a frappe with a tribble in it.

(JME) Minicult: a sheriff was installed in a small MA town, and a couple of days later, his unmarked sheriff's car was stolen. A few weeks later, a woman saw a man abusing a goose by the side of the road. She yelled at him as he was kicking the goose and throwing himself on top of it, whereupon he threw the goose into his car and drove away. She then called the police and reported the license plate number of the car; it was the sheriff's car. They tracked the car to a hotel, but neither the man nor the goose was found.

(RJG) Sounds like a bunch of fowl play to me...

(JME) Albanian motion.

Phonecomm: RING! It's for a random member.

Motion seconded, passes many many many-one soon to be Albanianed-one squawk and one Albanian squawk +Spehn.

(BPS) Minicult: the Nashville radio station WSM has been asked to refrain from using a promotion that says "I'm Ronald Reagan, and whenever I'm in Nashville, I listen to Radio 650 WSM, the 50,000 watt blowtorch of the south" that was done by Ronnie.

(JME) Motion to condemn that horrible impression of Ronald Reagan.

Motion passes by skinnerial decree.

(CH) Minicult: the Reagan administration is considering stopping its campaign to protect the ozone, and instead encouraging the use of sunglasses and suntan lotion.

(SSDT) Minicult: headline from the Glob- Snowballs from Space May Cause Depletion of Ozone.

(JME) Minicult: Howard Heflin is on the Iran panel and was talking to the press about things he expected to be revealed in testimony, one of which was that Fawn Hall had smuggled secret documents out of the National Security Council in her underpants and bra. Fawn Hall was very offended and said she'd never done any such thing and wondered where he had gotten that idea. Heflin sheepishly admitted that he could have sworn he had read that in the newspaper somewhere, but I guess he didn't.

(BPS) Bimbocomm: apparently Donna Rice's lawyer told her she should tell everyone her story so that things wouldn't get all confused and rumors start the way they did with Chappaquiddick. Her response was "Like what?"

(JME) People's Albanian Embassy/Timewarp to Moocomm: (translated from Albanian by JME for RJG) there is apparently going to be a Wheel of Fortune movie starring Pat Sajak and Vanna White.

(JME) Continuing timewarp: apparently there is going to be a live action TV series based on The Far Side. (Editor's note: how this will work is beyond comprehension, except maybe by the space cows.)

(CH) Moocomm: I saw a promo for Masters of the Universe. At best dumb fun, but great costuming.

Time warp explodes!!!!!

(JME) Minicult: in Arizona, a top educational reform lobbyist claims that schools should not try to discourage students who believe in creationism on religious grounds. When asked what should happen if a student proclaimed flat Earth beliefs on religious grounds, he said that if a student wants to say the world is flat, the teacher doesn't have the right to try to prove otherwise. The schools don't have any business telling people what to believe.

(BPS) Minicultses: The July issue of Playboy will have an eight page pictorial on a woman paralyzed from the waist down. Also, the Saturn awards were handed out. Sigourney Weaver won best actress; The Fly won best horror film.

(SSDT) Minicult: a guy walked up to a woman on the sidewalk and shot and killed her for no reason. When questioned, he seemed embarrassed. Apparently he's nearsighted and wanted to kill his wife... and made a mistake.

(JAH) Minicult: at the Indy 500, there was a fatality. But not on the track itself- it seems that in a crash, one car lost a tire, it bounced off another car, careened into the stands, and landed on and killed someone.

(CH) Minicult aside: on Saturday Night Live during the News Roundup, they said why shouldn't Playboy do a pictorial on a woman dead below the waist- they've been doing pictorials of women dead above the neck for years.

(BPS) Minicult: USA Today has put a bunch of their people on a bus, and it's going around the country doing Americana type stuff. Their entry on Massachusetts is quite interesting. They went to Cambridge and spoke to a Harvard senior who said "There is no more obnoxious organism on Earth than a Harvard freshman" and to an MIT grad student who said "People here are intelligent and humane. If they could just learn to be polite, they'd be perfect."

(BPS) Minicult: on Boston sports, the editor of the Harvard Lampoon said "The Celtics almost always win, the Red Sox almost always win."

(JME) Awardcomm: at the Nebula Awards, Speaker for the Dead won best novel. Two in a row for Orson Scott Card. Other awards went to Lucius Shephard, Kate Wilhelm, and Greg Bear. A grandmaster Nebula was awarded to Isaac Asimov.

(CH) The woman in the Playboy pictorial appeared on Phil Donahue. She said she would have posed for Playboy even before her accident. She was well spoken.

(BPS) Minicult: the magic team of Siegfried and Roy had their animal truck stolen. It contained two white tigers. The truck was later recovered in the Bronx, tigers still within.

(JME) Minicult: Polar bears ate a child. Apparently they were swimming in the bears' moat and were teasing the bears. Only one child was eaten, but the other two fled, leaving their clothes there. When the police arrived, they had to shoot the bears to see if all three had been eaten, but only found the one child. Animal rights activists have been furious.

(JD) Motion to send a bananimal to the zoo.

Fails to "Nyuhhhhh."

(KM) Move to commend the bears for choosing children over bananas.

Motion seconded, passes quite a few-fewer than few-a few squawks +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1757 SST.

\vspace{18pt}

\centerline{Submitted in English,}
\centerline{Rob Gates, One Last Time, Pseudo-Onseck}

\end{document}