\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 18, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, president and skinner, presiding.

Minutes of the previous meeting read by pseudo-onseck HAM.

(SSDT) Motion to approve the minutes as short and furry.

Motion seconded, passes 5pi-not even pi-maybe pi +Spehn.

\goto{Committee Reports}

(BPS) Cornelia Otis 1: X-rays of Gary Hart's head reveal nothing.

(BPS) Cornelia Otis 2: Just as last year I brought in photographic proof that Maria Shriver is a vampire, I have here photographic proof that Paula Gold, the Secretary of Consumer Affairs for Massachusetts, has no nose. I don't know how she smells.

(SSDT) Theftcomm: they got BU's condom dispenser.

(BPS) Approximatelyrelatedcomm: A couple of weeks ago, Geraldo Rivera did a syndicated special on the state of sex in America. There was one moment where a person who was advocating the use of condoms demonstrated that people who don't bother with condoms because they think they'll just tear anyway didn't know what they're talking about. He took a condom, unrolled it over one hand, put his other hand in, working it down over his head, his ears, and his nose, and then proceeded to puff it up until it was about the size of the conehead things from Saturday Night Live, at which points he flipped it loose from his head and it flew around the room like a balloon. He then said that he only breaks about one out of every 30 doing that demo.

(LAK) More Condomcomm: In the news today, researchers here and in California have announced they think they may be on the trail of something bioengineered that might be able to keep AIDS from progressing in people's bodies. They haven't worked out all the problems yet and will be doing animal trials this year, and, if it doesn't prove toxic, hope to do human testing in about a year.

(DSK) Timecomm: several important dates to remember. No meeting next week because it's Christmas, no meeting the week after because it's New Year's. Next meeting is Friday, January 8, 1988. Also, a timewarp goes into effect starting December 23. No fines will accrue until January 4 when IAP starts up.

(BPS) Moocomm: I think Batteries Not Included opens today.

(DSK) Den Mother      : Looks like we got a new Den Mother      . Barbara Fineman is bitching at us because of the hole in the wall. Apparently we're 750 dollars behind on payments and I don't know why.

(BPS) Xmascomm: I have a calendar for us, the same type as this year's only 1988.

(BPS) Aerodynamiccomm: (Something flies to DSK.) 150 dollar donation to MITSFS.

Time warp from Old Business:

(LAK) Jourcomm: write for TZ.

(DSK) Jourcomm 2: I got a letter from a Linda Leech from Michigan. She says she'll be sending artwork for the next TZ.

End time warp.

\goto{Old Business}

(DSK) The gameshow taping was. I wasn't- didn't do very well at all. I get to embarrass myself on Fed 1 at 7 PM. Out of that I got a sweatshirt, a camera, and a remote control, not attached to anything in particular, but programmable for VCRs and TVs.

(SSDT) I got a piece of email from Judy Passman. She says hi.

OBA: um, us, uv, ur.

\goto{New Business}

(LAK with BPS) Move to commend the Skinner on the manliness of his CLANG!

(KJ) Move to commend the Skinner on demonstrating his skill with his tool.

Motion seconded, passes by Skinnerial "right." (Demonstrated twice.)

(BPS) Minicult: one of the rages of the holiday season is a 20 dollar toy called the Revenger. It looks like a radar detector and mounts on your dashboard. It has various switches and toggles on it for things like Grenade Launcher, Machine Gun, and Death Ray, each of which generates its own sound effect. Apparently some people have been wiring their CBs into it.

(DSK) Minicult undocumented from the Glob: they're taking all the unsold Ollie North dolls and making them into Mikhail Gorbachev dolls in honor of the summit.

(BPS) Minicult: In Gloucester, RI, police have charged a 19-year-old high school student with murder. Apparently, his 16-year-old friend died after he was shot in the back of the head. The suspect's parents were away at dinner at the time of the shooting. The suspect told police that his friend was working on the computer when he came down with the hiccups. The guy went to his parents' room, took a revolver which he assumed was unloaded, and held it at the back of the friend's head. Hoping to scare the hiccups away, he shouted "Bang!" The gun went off, killing the kid.

(BPS) Minicult: the Nevada Supreme Court has upheld the state's ban on the use of card cheating devices, ruling against a man who used a hidden microcomputer on his person to improve his odds at blackjack. The microcomputer was strapped to his left calf. Wires ran to switches in his shoes that he could tap with his toes and keep track of the cards that had been played. The computer calculated his advantage or disadvantage versus the house, and then informed him to stand or take another card. The way it did this was by sending vibratory signals to a special receiver located inside an athletic supporter.

(LAK) Minicult: police in Des Moines, Iowa, arrested a 16-year-old boy for breaking into a shoe salesman's van and stealing 12 athletic shoes, all for left feet. All the shoes showed signs of having been worn. The police may check past burglary reports for any mention of the prints of two left feet.

( ) Minicult: "A lot of people are afraid of bats, but not Ginny Doolittle, who saved the life of a baby bat by keeping it in her bra for the summer. She admits the wiggling under her sweater raised eyebrows in the supermarket, and says everybody is fascinated when they find out the cause."

(HAM) Miller motion.

Seconded, fails.

A motion by BPS is seconded by SSDT. 25-not nearly 25-2.5 +Spehn. Motion passes, whatever it was.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}