\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 27, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the 3/13/87 meeting read by Pseudo-Onseck Janice Eisen.

(BPS) Motion to approve the minutes as CCH.

Dead silence.

(JME) Motion to approve the minutes as better than all the Nightmare on Elm Street movies put together.

Motion seconded, passes everyone-3-3 +Spehn.

Someone asks "Are you allowed to vote for and against a motion?" and is promptly Finger Motioned.

\goto{Committee Reports}

(JME) Bananacomm: there exists a "little" magazine, a literary magazine with a very small circulation, called BananaRad that prints only material that mentions bananas in some way.

Phonecomm: it's Larry, looking for Sue Hagadorne, who isn't there.

(CCH) Motion to appoint Janice to get us a copy of this magazine.

Motion seconded, passes.

(BPS) Sitcomm: I watched the most recent episode of The Colbys backwards just to see if the rumors were true. Apparently they are; one of the characters does indeed get taken away by a flying saucer at the end.

Phonecomm: it's Ken Johnson.

(JME) Jourcomm: I've got an interesting LoC here from someone who says how much she likes TZ but asks to be taken off the mailing list because she's gafiated completely. Also, write for TZ!!!

(JME) Meyercomm: next year's Boskone is going to be limited to 2000, not 2500. Also, they may not be allowing open parties to serve alcohol.

(SSDT) Inverse Hacker Report: the Reactor's office building has a roof access because the Radiation Protection Office has a piece of equipment up there they need to get to. Somebody put this on our roof access. So we took bolt cutters to it.

(BPS) IH Report sub 2: the plasma sculpture left, so we went to the Stud Center manager's office to find out where it went. Turned out they came in one day to find that all four bolts holding it down had vanished, so they've put it in there until they can find some better way to secure it.

(SSDT) Skinner Report: I get a raise on March 30th.

(JME) Sitcomm: the Glob says The Charmings is okay; their critic gave it 2 1/2 stars out of four. He gave four out of four to the new Max Headroom show premiering soon.

Ken Meltsner is Albanianed for doing something to his wife with a whip.

(CCH) There's a Christian rock group called Stryker nowadays, but Jimmy Swaggert still says rock-n-roll is a tool of the devil. This in spite of the fact that his first cousin is Jerry Lee Lewis.

(JME) Whooshcomm: NASA feebed again. They launched something during a storm that got struck by lightning, veered off course, and had to be blown up, taking with it an 83 million dollar satellite.

(JME) Sitcomm: on the Spitting Image Movie Awards, the plot centered around a scheme by Mr. Spock to get the Best Actor Award for himself. It was pretty nasty.

(DSK) Oral Roberts made his 8 million- and he still wants more.

\goto{Old Business}

No old business.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: from the latest SFChronicle- there's a letter from Michael Moorcock here stating that he doesn't favor censorship of Norman's Gor novels, he just wants them placed out of reach of kids. He states, however, that he would like to see Norman garroted in one of his own bondage harnesses and his publishers taken out by any means, conventional or nuclear.

(CCH) Con Report: I spent over half my time at LunaCon in the Japanimation room.

There is a Bananimal motion; it chickens 5-5-5 +Spehn.

(CCH) Condom Report: Prince Phillip, while on tour in Japan, went through a condom factory. Upon noticing they had black condoms, he asked if they were meant for mourning or something.

(JME) Motion to award RvdH a banana for not being here and not singing "Rabbits have no tails at all."

Motion seconded, passes everyone-4-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}