\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 6, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

Motions concerning the minutes include 1) approve the minutes as (atma) banana colored, 2) atma go away, Herb, shut up, Robert, and get it right, Scott, 3) someone singing rabbits, 4) atma unrelated to any fruit whatsoever, 5) atma unapprovable, 6) have a matrix vote. All motions fail by Skinnerial decree or general disinterest. The Skinner declares the minutes approved.

\goto{Committee Reports}

(BPS) Pumpkincomm: from Mon (11/2) McPaper- two skydivers fumbled a midair pumpkin handoff. It dropped about 1/3 mile, punctured a roof, and entered a woman's home. The skydivers were charged with reckless conduct. Article attached.

(JAH) is Albanianed for saying the topic has been squashed to death.

(CH) Moocomm: The Hidden was very good. Recommended; it's at general cinemas and sacs.

(HAM) Moocomm2: Attack of the Killer Teddy Bears Saturday at LSC.

(DSK) Addendum- he means Return of the Jedi.

(BPS) Mortcomm: the rumor of Alfred Bester's death has been confirmed.

(S??) Cornelia Otis: Reagan's next Supreme Court nominee has admitted to smoking the devil weed.

(KJ) Addendum- he's also one of the people who invented computer dating.

(BPS) Addendum- Secretary of Education William Bennett urged today that Ginsberg withdraw his nomination.

(S??) Videocomm: it's the 25th anniversary of computer games.

(BPS) Sitcomm: according to TJ Burnside, George R.R. Martin is story editing Beauty and the Beast.

(CH) Addendum- I heard that Beauty and the Beast will last out the season; it's doing pretty well in the ratings. But the producers want to shut it down because the cost overruns on each episode are considerable.

(HAM) Pseudo-Jourcomm: Janice said to say hi to everyone and you should all call her.

\goto{Old Business}

(RvdH) Time warp from New Business: Ken Johnson's picture hasn't been stolen yet.

(BPS) Addendum- the Rogues' Gallery is mostly complete; we still need a picture of Justyna.

(End time warp.)

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: People near Lake Washington in Washington state have for years been reporting their own version of the Loch Ness Monster. This morning, a sturgeon was found dead on shore, approximately 11 feet long and 1000 pounds. Estimated cause of death: old age. They think it was born around the turn of the century. They don't think there are any more of them in there.

(HAM) Its name wasn't Theodore, was it? (Albanianed.)

(CH) The newest member of the Tyee Club- where you have to catch a chinook or spring salmon of over 30 pounds with lightweight tackle and artificial lure, trawling from a boat with no motor- landed a 39-pound salmon on a 20-pound test line in 45 minutes. This was the biggest fish in 60 years. The new member is a 6 year old boy who weighs 70 pounds.

(BPS) Minicult: Brazil has banned MSDOS. Article attached.

(S??) Minicult: In today's Glob, a fundamentalist Christian woman lost custody of her son to her deceased husband's homosexual lover. The judge ruled that he'd provide a more stable home environment than the mother.

(RvdH) (translating from Albanian for HAM) Move that MITSFS send Janice a banana bouquet.

(BPS) Amendment- and drop it from 2000 feet.

Motion seconded, passes 30-2 and a couple of ork-orks and a poor Connie imitation-5, two sirens and a sheep +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}