\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 19, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Hawthorne, Vice and Pseudo-Skinner, presiding.

Minutes of the previous meeting were read and corrected.

(SSDT) Move to approve the minutes as armed with a cicada.

Motion seconded, passes 11 cicadas-1 very confused cicada plus a few unconfused cicadas-5 cicadas +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: there is a brand new, beautifully laserwritten review book list up on the cabinet. If you want to write a review on one of these books, go right ahead- I'll take it. Please, please, please contribute; please contribute this month, please, please, please. Contribute and save yourself a lot of pain.

(BPS) Sitcomm: This Wednesday at 8 PM on channel 2, and also channel 11D if you get cable, is the production Live From Lincoln Center- The Comedy of Errors, starring The Flying Karamazov Brothers. (Much laughter.) We're talking a variant version of the play. The four brothers play the two twins; the fifth one, who doesn't speak, plays Shakespeare, who according to at least one review, stands off to one side of the performance looking on in mounting disbelief.

(JME) Moocomm: opening this week- Inner Space, which is an updated version of Fantastic Voyage, in which Dennis Quaid is miniaturized and accidentally injected into the wrong person played by Martin Short. He can also apparently communicate with the person in which he was injected. Also opening this week is Spaceballs, which is Mel Brooks' parody of Star Wars starring John Candy and Rick Moranis.

(KM) ROSFAP: we got some new fanzines. Specifically, Thrust. I had described Thrust as a more liberal equivalent of SFR, which is a now deceased fanzine which was quite good. To show me I'm wrong, Dick Geis is writing a column for Thrust.

(CH) Boocomm: The Witches of Wenchar is out. It's a sequel to Ladies of Mandrigyn by Barbara Hambly. It's sort of a fantasy/mystery.

(RG) Committee of Wretched Excess: Out of Phase by Piers Anthony is out. The fourth book in his trilogy- is he ever going to learn how to write a trilogy? Is he ever going to learn how to write a book?

(JME) Committee of Wretched Excess II: The Glob had a review of Dirk Gently's Holistic Detective Agency by Douglas Adams. Basically the person liked it but said that it was based on the computer game- what that's supposed to mean I'm not quite sure.

(CH) Boocomm II: Erica Jong's newest book is Serenissma. It's about a woman time traveler who travels back in time to romance Shakespeare in Venice.

(BPS) Italy recently had its elections to Parliament and everything. One of the wacko candidates was a 37-year-old stripper/porn star named Ilona Staller. She tended to do things like pose topless for the press during the campaign. She won a seat in the Parliament!

(BPS) Pseudo-Pianocomm: our Rogues' Gallery is getting pretty impressive on the women's side- we now have three dominatrixes and one virgin bride.

(CH) Cornelia Otis: Of the questionnaires that NYT sent out, Richard Gephardt returned his completed, including signing over his FBI freedom of information rights. Basically, the NYT sent a questionnaire to all the major presidential candidates that was a) mildly offensive in terms of why can't you guys do your own research/why should we tell you who we went to college with, etc. and b) also wanted candidates to sign a waiver to their confidentiality rights to their FBI and other Department of Justice files.

(BPS) Freedomcomm: the good news- the Supreme Court today overturned the Louisiana law mandating the teaching of creationism (loud cheers). The bad news is that the vote was 7-2, which means two of these people actually thought it was a good idea.

(JME) Pseudo-Whooshcomm: According to a Glob article today, some Canadian astronomers now have really excellent evidence of planets around a bunch of stars. They have this new instrument that can measure variations in rotation speed up to 25 mph. So they can now detect the effect of planets abou the size of Jupiter, which is a start...

(JH) Last chance for committee reports. I mean it, I'm going to hit this gavel in a moment...

CLICKCOMM!

\goto{Old Business}

(JME) Donna Rice was interviewed by Barbara Walters last night, but she refused to answer the question of whether she slept with Gary Hart or not.

(BPS) Fifteen years ago last Wednesday, a third-rate burglary occurred.

(CH) There was an in memoriam in the Glob today for Julius and Ethel Rosenberg.

OBA: um, us, uv, ur.

\goto{New Business}

(SSDT) Four months ago, a group of highly schooled, expensively equipped physicists made a scientific breakthrough that may revolutionize electric power transmission and transportation. Last week, a group of high school students reproduced the same breakthrough- their cost? 2 dollars.

(BPS) There have been reports of a 90F superconductor... (cough, hack, choke). More believably, there is a real superconductor at 150K, which is getting into the Freon refrigerator range...

(JME) Minicult: the New Republic did a special issue on the Constitution, it being the 200th anniversary and all, and asked their readers and various figures to submit what amendment they would most like to see made to the Constitution. Three most popular ideas were limiting campaign spending, limiting congressional terms and/or erasing the limit on presidential terms, and abolishing the designated hitter rule in baseball!

(General flaming about baseball.) \bing (JEH) New business!

(JME) Motion to condemn the Skinner for banging her gavel when people are trying to talk.

(JEH) The Inverted Skinner Rule applies... motion passed.

(The skinner has been inverted.)

(BPS) Minicult: according to Newsweek, if you can... (Skinner takes out whip, film at 11; I think she really doesn't want to be inverted...) occasionally when Fawn Hall was away from her desk, before all of this broke, they put a sign on her desk that said temporarily removed from exhibit.

(BPS) Minicult: a woman in Nashville, TN, won a radio station contest. What she won was a free breast enlargement surgery. It doesn't say what she used to be; she is now 34C and very happy. To decide what breast size she wanted, she and her husband went to a shopping center and looked at other women. And then she walked up to some of them and asked, "May I ask you a personal question..." She said most women didn't mind telling her their brassiere size. (SSDT) Did she ask them what they weighed?

(BPS) On a more wistful note- they have announced a bunch of new people that will be getting stars on the Hollywood Walk of Fame. The only one worth noting is that they're posthumously awarding one to Rod Serling. The main way you get on the Walk of Fame is someone has to be willing to put up 3000 dollars to sponsor you.

(BPS) While I'm on a roll- Boston office of Consumer Affairs and Licensing has approved an entertainment license to transform the Spinoff Rollerskating Rink in Kenmore Square into the state's first Photon franchise. (Yeah! You can now buy photos at a reasonable price!) It should be opening in a few months.

(KM) Motion to condemn me for not making banana bread?

(CH) Motion to commend me for not bringing any Minicults?

(JEH) Move to pass one of these before it becomes a matrix vote?

It just did! MATRIX VOTE!

(KM) Move to award Adina a cicada banana for not making this meeting.

Motion seconded, motion cicadaed, lots of noise but very few limbs-two loads of no and a couple of limbs-lots of squawks +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned to three verses of the Adjournment Song, the theme from Mission Impossible, and general chaos.

\vspace{18pt}

\centerline{Submitted knowing a little bit more than last time,}
\centerline{Theodore Ts'o, Summer Onseck}

\end{document}