\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 17, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, Pseudo-Skinner, presiding.

Minutes of the previous meeting read.

(CCH) Move to approve the minutes as extremely sincere.

Silence.

(Malcolm Y) Motion to approve the minutes as an extremely sincere pumpkin patch.

Fails by "Try again in six months."

(KM) Motion to approve the minutes as an out-of-phase but very sincere pumpkin patch.

Motion seconded, passes almost everybody-not nearly everybody-2 +Spehn.

\goto{Committee Reports}

(BPS) Public Safety Report: Thanks to a ballpoint pen in the back pocket of Mike Friedman, we now have a splort on the blue comfy chair. Don't sit there until something gets done about it.

(LAK) Vice Report: Merryl isn't the only one going to Tufts! They're paying my tuition and giving me 800 bucks a month to corrupt- I mean, teach freshmen biology.

(JME) Jourcomm: We've got more LoCs, more art, and more fanzines. Enthusiasm seems to increase the further the letter-writer gets from the MITSFS. I got a really enthusiastic letter from Australia. Also, write for TZ!!!

(JAH) Compcomm: Rob, Lisa, Laura Baldwin, and I are writing a real-time, real-space roleplaying game based on Katherine Kurtz's Deryni books. Well, Rob managed to get us an account on the Student Center machines called "deryni." I was working on it the other day when I got a write message that said "I love your books! Can I have your autograph?" I fingered deryni at prill to find out what was going on and discovered that the account was in Katherine Kurtz's name. I wrote the guy back and explained what was going on.

(KM) ROSFAP: First, we have a new fanzine well-known for its putridity. It's called Holier Than Thou and is known for both good writing and gross-out humor, and it was a Hugo nominee last year. We also have the latest Instant Message.

(JME) Mortcomm: Terry Carr is dead.

(BPS) Sitcomm: In last Wednesday's episode of Magnum PI, Magnum got seriously blown away in a gunfight, and then, at the end of the show, actually died and went to heaven. Oddly enough, there's going to be another season...

(BPS) Opuscomm: Penguin wins Pulitzer. Bloom County by Berke Breathed has won the Pulitzer Prize for political cartooning.

(JME) Sitcomm: Max Headroom continues to be good.

\goto{Old Business}

(DSK) Herb's here.

(HAM) Hi.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: last Sunday, the Miami Herald printed the retraction to end all retractions. (She reads an impressively long list of things that were reported incorrectly in a single article.) Apparently, the whole story was made up by somebody out of whole cloth.

(BPS) Minicult: last Sunday, Tokyo Diamond Merchants unveiled the world's most expensive swimsuit. It's a black leather one-piece studded with 1.5 million dollars in diamonds totaling over 62 carats.

(CCH) Minicult: Strange Australian pet tricks from the Sun. "Man Teaches Chimp to Help Him Rob Banks" and "Purse Snatcher Stopped by Boxing Kangaroo."

(JME) Minicult: from the Glob- Police in Chicago arrested a bank robber who foiled his own getaway by leaving the keys to his car in the bank. The robber got away with 800 dollars, then ten minutes later was caught when he returned to the bank for the keys. Also, sometime last week the Glob reported that a man crashed a helicopter while trying to steal it because he didn't know how to fly a helicopter or anything else. At the time of the crash, he was already on probation for trying to steal another helicopter.

(JME) Minicult: a Canadian journalist was in Libya to cover ceremonies commemorating the first US bombing there when he was found dead at the base of a thirty-foot building. The Libyan press released a statement saying he had committed suicide after seeing photographs of the damage done by US bombers. Apparently the Libyans can't tell Canadians from Americans either.

(KM) Minicult: Sherrie Tepper's son is a grad student in my department. She based a rather insane character in The Flight of Mavin Manyshaped on him and put in a whole bunch of weird but real physics at one point in her book. He listed this book as a reference in one of his published papers.

(BPS) Minicult followup: I reported about a kid getting killed playing Lazer Tag on Friday of last week; by Saturday the outcry I predicted had started. Dr. Carol Lieberman, a clinical professor in psychology, has an article in the Glob claiming that "the boy was a victim of overexposure to society's promotion of violence and to toymakers' promotion of their violent toys long before he was a victim of a real gun."

(Seth Gordon) During WWII, when Canadian and American draft dodgers were dodging over the borders both ways, the guards at the borders told Americans apart from Canadians by having them recite the alphabet; the Americans would end with "Zee" and the Canadians with "Zed."

(KM) There's a picture in this month's Computer Update of a man whose head is a peeled banana.

(JAH) Motion to make that a motion.

Motion seconded, chickens more than a dozen-one-many loud chickens +Spehn.

Someone makes a motion to make Bananimals count.

Motion seconded, passes many-2-quieter chickens +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1737 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}