\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 28, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Rob Gates, LHE and Pseudo-Skinner, presiding.

Minutes of the previous meeting were read and corrected.

(JME) Move to approve the minutes as the moral equivalent of nitrous oxide. (HAM) Amendment- without the stutter (editor's note- I'll get even). Motion passes oodles and oodles-quite a few but not quite oodles and oodles-lots of chickens +Spehn.

\goto{Committee Reports}

(JME) Goodnewscomm: William Proxmire will not be running for another term in the Senate in '88...

(KM) Rosfap: we have more fanzines. Including Texas SF Inquirer, and the new SFC.

(KM) Infocomm: apparently the Tech's phone number was used in the creation of Planetfall (designed by a former LSC groupie). The Tech has been receiving a number of calls from people who find it in the game. They were giving out Steve Meretsky's phone number and saying to call at 2 AM. But he moved, so the Tech has written a letter to Infocom saying remove the number or we'll take legal action.

(BPS) Followup- if you dial the number for Sierra Software in one of their games, not only do you get a spiel for their tip book, but you also get 10 points.

(JME) Followup II- Stationfall, the sequel to Planetfall, is out. No news yet as to whether the Tech's phone number is in this one...

(HAM) Crimepayscomm: my wallet was stolen. They got my ID, license, MITSFS membership card with JME's initials on it, and my Baybanks card...

(TG) Is this just the initial report? (En masse) ALBANIAN! Passes by overwhelming agreement.

...if the thief had bothered to steal the watch on the table next to the wallet, they would have gotten the password which is stored in the memory in my watch.

(JME) Jourcomm: TZ real soon now.

(CH) More Phonenumbercomm: in Montreal, there were flyers appearing on people's windshields saying something like call this number and I'll give you some real hot information. If you called, you got a spiel about AIDS, and a 2 dollar phone charge, which went towards AIDS research.

(JC) Fweekcomm: keyholders, sign up for R/O hours. Moneyholders, show up and look impressive.

(RJG) Attache to the Albanian Embassy (from TG): Gamblingcomm: I won 300 dollars in Vegas using a system from a Mack Reynolds book.

(RJG) (Albanian translation from TG) I'm not moving to Albania, but I am moving to Switzerland.

(BPS) Whooshcomm I: They still haven't done the horizontal test of the shuttle due to lots of technical problems.

(BPS) Whooshcomm II: The Newsweek article is in the blue folder on the desk. It's depressing reading.

(RJG) (Albanian translation for TG) Arthur Clarke is working on a sequel to Rendezvous With Rama.

(BPS) Followup- tentative release January '88, 2060: Odyssey Three.

(BPS) Mortcomm: John Huston died today.

The universe is sinking... oh my god...

(RJG) It looks like if we move at all, it will be to our advantage.

\goto{Old Business}

(JME) Both the Tennessee and Alabama textbook cases have been overruled. A woman was quoted as saying something like judges have a conditioned belief to ignore fundamentalists and let the secular humanists rule everything.

(RJG) Merryl, Herb, and Tom Galloway.

(BPS) It's been twelve years since I arrived at MIT.

(RJG) Pianocomm: I gave a spare key to Herb; I'll try to find one for Merryl.

OBA: um, us, uv, ur.

\goto{New Business}

(CH) Minicult: Eric Baucher, better known to his fans as Jello Biafra, won a court case in LA. He was the lead singer for the now disbanded band The Dead Kennedys and was responsible for the writing of lots of their songs. He once described the band as art terrorists; instead of blowing up buildings, they blew people's minds. Their last album Frankenchrist had a poster with a picture of disembodied genitals getting it on. A case was brought against him by an irate parent. He won 7-5, and Jello signed copies of the poster for the seven jurors who voted for him.

(BPS) Followup- this is the second case about the album which has been in court. Four Shriners from Ohio sued when a Newsweek photo of them was used as the cover for Frankenchrist. The Shriners lost.

(JME) Minicult: a Mississippi circuit judge was sick and tired of all the lawsuits being brought into his court, and when a Moose Lodge won a case, his ruling included (apologies to Bob Dylan...):

They'll sue you when you fail to pay the claim/They'll sue you for a bad ??? no matter who's to blame/They'll sue you when you're driving to go home/They'll sue you when you're parked and all alone/But I would not feel so much abused/Everybody must get sued.

(JME) Minicult: a Miami woman was arrested on the subway because her kids were eating on the train. The case was thrown out of court.

(BPS) Moocomm: a minor role in The Fourth Protocol is played by Matt Fuhr, the actor who does Max Headroom.

(BPS) Max Headroom will be back and will be dumbed down for the American public.

(JME) Minicult: the USSR took out a nine page ad in the Wall Street Journal. There were ads for Soviet businesses. Glasnost strikes again.

(RJG) (Albanian translation for TG) They are negotiating to open up a Ben and Jerry's in Moscow...

(JME) Minicult: Al Neuharth, the USA Today guru, thought his execs were doing poorly, so he invited them to a meeting. When they arrived, he was there, standing in front of a large wooden cross with a table laid out with matzo nearby. "I am the crucified one," Neuharth said... this man is ill.

(CH) Minicult: from the WWN, aliens visited Earth 20,000 years ago and left a space potty behind. The rest left out by editorial decree.

(RJG) (Albanian translation for TG) Religious fanatics were handing out pamphlets about prophecies and such... loonies.

(JME) Hypocult: Oooops, mentioned last week... RoboNorth posters.

(SH) I need a place to live.

(JME) Motion to lynch Robert's landlord with a banana.

Motion passes quite a few-a couple but not many-a few squawks, a moo, and some feet +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1732 SST.

\vspace{18pt}

\centerline{Submitted ad infinitum,}
\centerline{Rob Gates, LHE and temporary everything else}

\end{document}