\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 6, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
D. Scott Kitchen, Pseudo-Skinner, presiding.

Minutes of the previous meeting (1/23/87) read and corrected.

(BPS) Move to approve the minutes as heroically translated.

Silence.

(JAH) Motion to approve the minutes as heroic but doomed to failure.

Motion passes 20-a whole lot less than 20-5 +Spehn.

\goto{Committee Reports}

(BPS) Starrcomm: We finally, mostly through the heroic efforts of Susan Tucker, managed to pry that 500 dollars loose from the Institute. The main problem was that the concept of someone who didn't graduate from MIT giving MIT money completely befuddled the Alumni office.

(JAH) Moocomm: Marathon 9 from Outer Space was, about two weeks ago. It was reasonably watchable, except for Zardoz, an incomprehensible movie that features Sean Connery in a bright orange diaper.

(DSK) LHE Report: there is no LHE Report. The bank statement isn't in yet. I also have two Committee Reports from Janice, who's in absentia. Pseudo-Jourcomm: TZ RSN! Should be here early next week. Pseudo-Huntcomm: Scavenger Hunt, Sunday, 11 AM, Boskone. 5 individual entries, and 4 teams.

Phonecomm: it's the Skinner, who's at home in bed with chills. (Cries of "Who's Chills, and does John know about him?" are heard.) She has several reports. The first is about a letter for Huntcomm from some people who want to join the Scavenger Hunt- with only three days left to gather their stuff. (The letter is given to JME, who returned from absentia in the middle of the Phonecomm.) The second is that setup for our dealer's table at Boskone is going to be open from 12 to 4 but not from 4 to 5, and people are needed to help set up, as well as one person with a car. Third, there is an Activities Midway on the fourth floor of the Student Center on the Tuesday after Boskone, and someone should be here to keep the library open.

(JME) Jourcomm sub 2: we WILL have TZ for Boskone.

(BPS) Sitcomm: for people who think no new ideas ever come out of TV writers, I have an entry from this week's TV Guide for last Tuesday's episode of The Wizard. "Simon believes an orphan girl, thought to have multiple personalities, is really experiencing a psychic connection with an unknown twin sister who is being terrorized by a renegade gypsy."

(JME) Whooshcomms: 1) There's a nice memorial to the Challenger astronauts somewhere in Florida. The engraved plaque with the astronauts' names on it had Judith Resnik's name spelled wrong. Some philanthropist recently donated the town enough money to have the plaque remade. 2) NASA and the Defense Department have agreed that there will be no major weapons systems on the proposed space station, something that had worried the potential European and Japanese partners. They established that the station will be civilian in character but that the Pentagon will be allowed to do research there. 3) The NASA official who okayed the launch of the Challenger, who had been transferred to another part of NASA, has now resigned to take a job in private industry. 4) According to a book coming out soon about the Challenger incident called Prescription for Disaster, Michael Deaver tried to muzzle Krista McCauliffe's political opinions. Apparently, shortly after her selection for the teacher in space program, McCauliffe gave an interview in which she expressed admiration for John F. Kennedy and the Kennedy family, and Deaver told NASA's then-administrator to tell her to shut up and not talk about Kennedy. 5) According to a book about Krista McCauliffe which was excerpted in the Glob, the Challenger referred to their computer as "Spock."

(BPS) Mortcomm: Richard Safer, co-creator of the Destroyer series, died on the 27th of January at age 50.

(LAK) Famecomm: "Casey resigns; Robert Gates appointed head of CIA." This is especially appropriate since our Robert Gates played the head of the CIA in the fall Assassin game.

Phonecomm: it's Ken Johnson, looking for Sue Tucker. He's told she's at home in bed with chills. He doesn't ask who Chills is. He wants to know if anyone knows anything about "the package in Central Square." Silence replies.

(JD) People's Albanian Embassy: in the Daily Journal, they published a political cartoon about how best to reorganize the Boston public schools. It said "A) Move Boston Tech to Medical Park, B) Move Latin Academy to Boston Tech, and C) Move school committee to Albania."

(JME) Pseudo-Moocomm: nominations are out for the 14th annual Saturn Awards, which are for achievements in the field of fantasy, horror, and SF movies, given out by the Academy of Science Fiction, Fantasy, and Horror Films. Leading the field were Aliens and STrek IV, which each had 11 nominations.

(SLP) Concomm: the rates for Noreascon go up after February 15th, so get your money in now if you want to pay the lower rate.

(JME) Famecomm sub 2: Noreascon 3 is going to be the 50th anniversary of the founding of WorldCon and the 40th anniversary of the founding of the MITSFS. The Committee is interested in potentially doing something to commemorate this. Start thinking of things that might be done.

(LAK) Pseudo-Moocomm: LSC is getting Nimoy this term. He's getting 10 grand for it.

(GF) Famecomm sub 3/Pseudo-Jourcomm: I have a report on fanzine sales at Confederation. We were one of the top sellers.

\goto{Old Business}

(BPS) Ronald Reagan, 76 today.

(JME) Addendum to a Minicult: the dog that Ollie North said was poisoned wasn't really poisoned at all; it died of cancer. Also, in a report on North, a reporter said that North once bragged to him while they were on an airplane that he had made a deal to sell arms to Iran in exchange for hostages. Apparently, he wasn't believed because he had a reputation for exaggerating.

OBA: "clink, clink," um, us, uv, ur.

\goto{New Business}

Phonecomm: It's Connie- she's going to be here and so will Adina, but not together.

(JME) New Futures in Children's Television: going one better on the children's shows that are really half-hour long commercials designed to sell toys, coming out next fall are two shows, Captain Power and Tech Force, that are meant to be viewed with accompanying toys that fire lasers and rockets that are activated by the sounds given off by the TV during the shows, turning the TV set into a video game that can be played only if the child buys the toys.

(JAH) There's a small hope on the horizon; one of the networks is planning on bringing back the old animated program Johnny Quest with new stories and animation.

(BPS) Action for Children's Television is protesting the video game shows.

(JME) Minicult: a survey from Purina showed that "today's canines are in tune with today's fitness trend. Half the owners questioned say their dog enjoys jogging more than any other sport."

(BPS) Minicult: from the Glob's sports section- center Bobby Joyce of the Santa Anna High School basketball team has been suspended. After his team lost in the semifinals of a tournament to another team by one point, he shoved a soda machine in front of the officials' dressing room door, preventing them from leaving.

(JME) Jourcomm (time warped): I just got a manuscript submitted for TZ, and the cover letter is worth quoting. "I have absolutely no idea what your magazine is like, but our local librarian came across your address while looking for another one. If you would, mail a copy to this God-forsaken country." It's from Missouri.

(BPS) Minicult: from the February 2 Time- in California, a woman was driving in the carpool lane which requires there to be more than one person in the car. She got a 52 dollar ticket, but appealed on the grounds that she was not alone in the car since she was five months pregnant.

(JME) Minicult: in Golden Gate Park, there's a mystery prankster known as Klaus who's running around the park sowing bits of a plant known as South African capeweed. The park gardeners have been unable to catch the man and have had to spend thousands of dollars to undo the damage the fast-growing weed has done to the park.

(BPS) Minicult: they recently had a trial around here when a woman claimed that a character in the novel The Bell Jar was based on her, and that character was mistakenly portrayed as a lesbian when the book was made into a movie, which she finds objectionable. One of the prerequisites for serving on the jury for this case was that you had to not read books.

(JME) Minicult: there's a Liberace phone now available that features a small plastic Liberace that, when the real phone rings, picks up a small plastic phone and begins to move his mouth as if speaking into it while playing the piano.

(BPS) Minicult: Time ran an article on strange names for sports teams a while ago and got several letters in response. When Webster University began its athletic program in 1984, they called their team the Gorloks and made their mascot an extraterrestrial being.

(JME) Minicult: I have here a summary of papers from a "scientific journal" called Creation Research Society Quarterly devoted to, of course, creation science. Among the important issues they tackled were "What did Noah do with the manure from the animals on his ark?", "What did the animals eat?", and "How did marine life survive a freshwater deluge?" There's also a report by a man who thinks dyslexia is due to the Tower of Babel and that people are genetically programmed to read either left-to-right or right-to-left, and when they try to read against that programming dyslexia results.

(KM) Move to commend Jenny for wearing both a banana colored blouse and a banana colored T-shirt over it.

(JD) Second.

Motion passes 20-about 5 and Chills-about 5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1759 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}