\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 8, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, in the Spofford Room. Susan S.D. Tucker, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

RJG enters with bathing trunks, towel, and sunglasses.

(RvdH) Motion to approve the minutes as "the last time."

Motion seconded, chickens 11-5-lots of squawks +Spehn.

(KM) Motion to approve the minutes as Val's problem.

Motion seconded, passes overwhelmingly.

\goto{Committee Reports}

(JME) Sitcomm: it looks like the new STrek series is going to be delayed. Casting has not been completed; they're supposed to have the first season scripts done, but apparently Gene Roddenberry and Dorothy Fontana are still arguing over the pilot.

(JAH) The main parts have been decided, however. No female captain or first officer.

(BPS) Sitcomm: Tuesday marks the end of an era. They're showing the final first-run episode of Hill Street Blues.

At this point, to show respect, King Herod (RJG) takes off his glasses and hat at the same time (glasses being on top of the hat).

(SSDT) Panthercomm: I updated the database and put a new book listing in the front. It was all right until 3 this afternoon when we got some SFWA books.

(KM) Sitcomm: Max Headroom has been picked up for next season.

(CCH) Sitcomm: St. Elsewhere is picked up for next season as well.

(JME) Jourcomm: I'm sick and you all have to feel sorry for me and write for TZ.

(KM) ROSFAP: we have new Locus, Otherworlds, and random fanzines. Also the Mad Three Party, which talks about how NESFA (MCFI) is dealing with the loss of the Sheraton for Noreascon 3. Apparently they didn't have a contract but they did have a signed letter of intent which is almost the same. NESFA has several real lawyers in addition to fannish lawyers working on it.

(JAH) Awardcomm: I think the Nebula Awards have been announced. I'm not sure but I think Speaker for the Dead won best novel.

(KM) Moocomm: the poster for A Clockwork Orange says "Winner of 11 awards including the Hugo."

(BPS) Cornelia Otis 1: Gary Trudeau has been writing a Ron Headrest gig on and off for a couple of weeks. In Thursday's, Ron told teenagers to call for information about safe sex and gave the main number of the White House switchboard. The White House responded by referring all callers to the number of the main office of the syndicate that carries Doonesbury.

(BPS) Cornelia Otis 2: Gary Hart.

(JME) Cornelia Otis 3: on Wednesday a witness at the Iran/Contra hearings was being asked about how he spent the money in his Swiss bank account. The congressman questioning him said "You could have bought a Caribbean island for that money!" Witness's response was "Yes, but I didn't go to Bimini."

(BPS) Cornelia Otis 3b: Secord told Ghorbanifar over the phone "We're thinking of terminating you." He meant terminating the deal; Ghorbanifar took it the wrong way.

(DSK) Gavelcomm: Consumer Information Center is growing banana-colored gavels (shows pamphlet).

(BPS) Weathercomm: Sunday looks good, breezy mid-70s, with a slim chance of a thunderstorm late afternoon or early evening.

(DSK) Pseudo-Picniccomm: Justyna has the money; she'll be shopping tomorrow.

(SSDT) Skinner Report: I've finally bought myself a life membership.

(KM) Pseudo-Libcomm: I spoke to an ex-MITSFS member who works at the Cambridge Public Library. The library is going to dump a bunch of sf hardcovers and paperbacks in addition to some furniture. I'll get them RSN in a large car.

(JME) We should give him a year or two membership in exchange for the books.

(JAH) Libcomm 2: somebody called and asked if we take donations. He'll be bringing some by sometime soon.

(JME) Can we get cardboard donation boxes to the dorms this year?

\goto{Old Business}

(JME) We're donating a replacement to Martian Spring, a book our mysterious book thief stole from the reserves.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: in 88 days it will become legal in MA for an unmarried couple to live together for the first time in over 200 years. Dukakis signed the repeal Wednesday and it takes effect 90 days from when he signed it.

(JME) Minicult: over 60 percent of Americans polled believe the president has the right to dissolve Congress.

(SSDT) Microcult: every Sunday afternoon a so-called musical group makes noises to the soundtrack of The Sound of Music for hours on end right down the hall from the Library. Their rendition is slower than any other I've heard. Since they didn't have a group name on their door, I posted one reading "TSoM Half-Speed Society. Meetings every Sunday afternoon in W20-409." As far as I can tell it was ripped down as soon as they discovered it.

(CCH) Minicult: remember the old joke about how Russians are 25 years ahead of us on vacuum tube technology? Apparently audio engineers are going back to vacuum tubes. One of the hottest selling brands is imported from Russia. They're called "Virgin Commies." Ad attached.

(RvdH) Nanocult: Vacuum tube computers are immune to electromagnetic pulses.

(BPS) Minicult/Old Business: the plasma lamp is back.

(RJG) It's gone. It wasn't there last night.

(SSDT) It was there this morning.

(KM) Move to commend the library for using banana-colored post-it notes.

Motion ignored.

(BPS) Move to hold the elections.

Motion passes without a vote.

Election results (final ballot):

Onseck-

Anyone Jenny wants: 1.0

Jennifer's ankles: 0.67

Klyd: 0.3

VHS: 7.1

Randoms: 1.49

LHE-

Free Silver: 0.1

Monkey Business: 0.13

Lt. Col. Oliver North, An American Hero: 0.47

RJG: 9.72

Randoms: 1.88

Vice-

JAH: 8.59

DSK: 0.1

Jim and Tammy Bakker, naked in bondage: 0.21

Randoms naked in bondage: 2.46

Other randoms: 0.6

President-

FCC: 0.1

DSK: 9.43

JME's new nephew: 0.3

Yalda the Crimson Queen: 0.1

Radical lesbian feminists of Gor: 0.1

Randoms (including Spofford) naked in bondage: 4.3

At some point during the voting, an Albanian Defenestration motion is attempted on RvdH. DSK and JAH enthusiastically pulled open the bottom window as wide as possible. The top window simultaneously came down and closed securely, making a Polish motion. This is followed by 2 minutes and 23 seconds of hysterical laughter that crops up again randomly throughout the voting. It is noted that DSK is on the floor laughing and SSDT is crying.

Naked In Bondage is declared Official Second. DSK is Skinner.

(JME) Motion to thank SSDT for a very good banana-colored year.

Motion seconded, passes by "Oh, hell, Skinnerial decree!"

\vspace{12pt}

\noindent
Meeting adjourned, almost 2000 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Val Stark, Onseck}

\end{document}