\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 13, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(VHS) Motion to approve the minutes and send them to 20 of our friends.

Motion seconded, passes 20-Merryl-a couple of sheep +Spehn.

\goto{Committee Reports}

(JAH) Bookcomm: new out at Wordsworth today- 2061: Odyssey Three by Arthur C. Clarke, A Man Rides Through, the second half of Donaldson's Mordan's Need fantasy, and the newest Crossroads, this one set in Steven Brust's Jhereg world.

(BPS) Acquisitioncomm: we have a doorknob.

(JME) Jourcomm: TZ Real Soon Now, leave me alone I'm recuperating.

(DSK) Famecomm/Skinner Report: MTV called me; they're taping the game show on December 16, air date still unknown.

(JME) Pseudo-Moocomm: Arnold Schwarzenegger in The Running Man opens today. It's based on a Richard Bachman (Steven King) novel, and getting really bad reviews. They cast Richard Dawson, the game show host, as a game show host.

(BPS) Pseudo-Concomm: from Kathy Godfrey and TJ Burnside about last week's BSTA STrekbash- apparently it was really feeble, unless you were into getting Jimmy Doohan's autograph. T-shirts included: "Get a Life!", "Damn It, It's Only a TV Show!" (and Saturday Night Live ran that skit with William Shatner the night of the con), and "He's dead, Jim. You take the tricorder and I'll get his wallet."

(JME) STrekcomm: Next STrek has been getting feebler.

(KM) Rosfap Report: I've been extraordinarily busy. I will have the unprocessed fanzines processed before I leave for Schenectady.

(JME) Addendum- official move day is Nov 25.

(BPS) Meteorologycomm: last Sunday we had smoke, and on Wednesday night we had snow. Environmental Control is screwed up. (DSK) I'm working on it.

(DSK) Pianocomm/Skinner Report: The skinner is pleased to announce the selection of a brand new Telzey Amberdon, Janice Bushman. (Picks up the bar BPS found on Oct 2) I'm going to make this the Telzey's gavel.

(BPS) There's a new show on ABC that can't be seen locally because of Next STrek called Sable, based very loosely on what used to be a good comic book. The show is pretty feeble, so don't bother.

(DSK) Cornelia Otis: Ginsberg. Cornelia Otis 2: Caspar Weinberger. Cornelia Otis 3: Kennedy.

(HAM) ?????comm: continuing my great academic tradition, I have just dropped another course.

(S??) Pseudo-Sitcomm: There's a disgusting TV game show for kids called "I'm Telling," kind of like The Newlywed Game with brothers and sisters instead of husbands and wives.

(JAH) Sitcomm Children's TV 2: they canceled Dangermouse on Nickelodeon.

(JME) Sitcomm Children's TV 3: "The Little Clowns of Happytown" are even more disgusting than the Smurfs.

\goto{Old Business}

(KM) There was an outline for a book called Mars: The Movie floating around, about filming an SF movie on location on Mars. The book has been bought, and will be out in the normal 2 years or so.

(BPS) Addendum to last week's minutes: the boy who the mother lost custody of to her dead husband's homosexual lover was about 15, so his wishes probably influenced the judge's decision.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: from the Albany Times-Union Nov 7- "Correction: because of a reporting error the Dear Abby column should have said 'carbon dioxide' instead of 'Hiccups can be cured temporarily by use of carbon monoxide.'"

Phonecomm: ring. Lisa 0, Phonecomm 1.

(JME) Minicult: in Boulder, Colorado, a bank robber walked into a Mellon-Boulder bank and demanded money. But the bank is liquidating its assets and no longer maintains deposits. When told the bank did not have any money, the robber gave the teller a puzzled look, turned, and left.

(JME) Minicult: in Denver, a soldier and his buddy stole a tanklike armored vehicle with a 150mm cannon and took it on a 75-mile joyride until it broke down in a residential neighborhood. Article attached.

(HAM) Move to condemn Mike Friedman for not wearing a day-glo banana colored shirt with the stripes in the wrong direction. Motion seconded, passes 20-2 and the Telzey-3 and the Telzey doing chicken imitations +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1723 SST.

\vspace{18pt}

\centerline{Illegibly submitted,}
\centerline{Val Stark, Onseck}

\end{document}