\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 23, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(JME) Motion to approve the minutes as unrecognizable.

Motion seconded, passes 10-2-4 +Spehn.

\goto{Committee Reports}

(JME) Cornelia Otis: the main character of Heinlein's The Moon is a Harsh Mistress takes the party name Comrade Bork during the preparations for the revolution.

(DSK) Cornelia Otis 2: Wall Street.

(BPS) Cornelia Otis 3: Apparently the Senate rejected Bork today, but CBS News doesn't give any useful information like the voting numbers.

(JME) Jourcomm: TZ Real Soon Now.

(KM) Rosfap: we've got a lot of new fanzines, but I think this is the funniest- "8 1/2 by 11 Zine," featuring a picture of Spuds Headroom, the original electronic party animal.

(BPS) Sitcomm: Last Friday's Next STrek was interrupted by an ABC news bulletin about 20 minutes before the end about getting that 18 month old girl out of the well. In fact, all three networks interrupted their regular programs to show it. They did get off the air by 9, so the (probably only) airing of the last episode of Max Headroom wasn't interrupted. The channel 5 repeat of STrek is always on after Monday Night Football, which always runs over time. Apparently they've rescheduled this for Saturday at 2 AM, but with daylight savings it's anyone's guess what they mean.

(BPS) Followup- the ending wasn't very good, so you didn't miss too much. The episode after the next one is written by Diane Duane and J. Michael Reeves, according to TV Guide. They also say that Patrick Stewart has a sign on his dressing room that says "Beware- unknown British Shakespearean actor within."

(DSK) Skinner Report/Sitcomm: the skinner is going to be on TV. I've been selected by a contestant search for a new MTV game show. It will probably air sometime between November 7 and the end of the year.

(JME) Bananacomm: Oliver North's erstwhile secretary Fawn Hall was given a 10-dollar citation for eating a banana in the subway station in Washington DC. Article attached.

(JME) Pseudo-Libcomm: If you see Charon's Ark by Rick Gauger, please do something about it; it's missing.

(BPS) Incrediblyluckycopcomm: A Florida federal agent had his gun out while making an arrest. The bad guy fired at him, and the bullet struck the agent's gun barrel. Half of it lodged in the barrel and the other half took off for parts unknown. The agent was not injured.

(JME) Pseudo-Moocomm: Nightfliers, based on a novella by George R.R. Martin, opens today.

(BPS) Sitcomm juvenile: The GI Joe cartoon show is amazingly good.

( ) Pumpkincomm: It's the Great Pumpkin Charlie Brown is on tonight on channel 7 at 8.

(JME) IAPfingercomm: are we doing anything for IAP?

(BPS) Next week's Beauty and the Beast is their Halloween special.

(DSK) Whooshcomm: NASA has officially announced the new launching schedule for the schedule. First one June '88.

(JME) Sitcomm: The first episode of Philip Morrison's PBS show, The Ring of Truth, was very good.

(BPS) Local Famecomm: In this year's Nobel sweepstakes MIT has definitely outclassed Harvard.

(JME) Concomm: the 1990 NASFC will be in San Diego when the Worldcon is in Holland.

(SSDT) Ex-Skinner Report: I finally managed to fix my bicycle. It had two flat tires and a busted brake cable at the same time.

\goto{Old Business}

(SSDT) Time warp from New Business: our books came back from APO. I have no idea if we made any money.

( ) Move that the chief executives of ABC, NBC, and CBS be stuffed headfirst down a well in Texas.

(BPS) Amendment- a well which has already been sealed with concrete.

Motion seconded, passes by skinnerial decree.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) The coop rebate checks are in.

(BPS) Not only is the new John M. Ford STrek novel called "How Much for Just the Planet," but according to my housemate, it goes on the NY Times paperback bestseller list starting this Sunday.

(JME) Gene Wolff's sequel to The Book of the New Sun, The Earth of the New Sun, is just about out. MITSFS doesn't have it yet but I do.

(KJ) Rumor has reached me that Alfred Bester has died.

(RvdH) Move to condemn Michael Friedman for having a day-glo banana colored shirt.

Motion seconded, passes more than enough-not even close to enough-six and a sheep +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}