\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 18, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous two meetings read and corrected.

(KM) Move to approve the minutes as more awake than you (DSK) are. Motion seconded, passes everybody-nobody who counts-5 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: TZ Real Soon Now.

(DSK) Skinner Report; I've had a cold for about a month now.

(JME) Infocomm: Stationfall includes the Tech's phone number backwards; after all the Tech's threatening letters about their number being in Planetfall.

(SSDT) Committee to Overdamp the Atmosphere: Planetary control system is obviously screwed up; it's been raining on weekends and not in the middle of the week. Perhaps this has something to do with DSK's cold.

(JME) Sitcomm: the new season of Max Headroom starts tonight.

(DSK) Sitcomm2: there's a new syndicated show about a girl who's the child of an alien father and an Earth female.

(JME) Sitcomm3: there's also an updated Beauty and the Beast on CBS.

(JME) Sitcomm4: Sledgehammer last night included a poke at Max Headroom.

(BPS) Sitcomm4b: the last season of Sledgehammer ended with a nuclear explosion. This season started with a replay of that scene, then an announcement: "The following season of Sledgehammer takes place five hundred years before that nuclear explosion. Thank you." Title frame was "Sledgehammer (The Early Years)."

(KM) Motion to commend the writers for not saying it was all a horrible, horrible dream. Motion seconded, passes by acclaim.

(JME) Sitcomm_n: in the end of last season's Crime Story, the villains were escaping across Utah through a nuclear test site. Apparently the villains will be back this season, bandaged and burned but otherwise OK.

(KM) Rosfap: I just processed a whole bunch of fanzines. Well, not really, REALLY processed, but people should take a look at them anyway. There are several worth looking at.

(TG) Sitcomm_whatever-the-hell-number-we're-up-to: according to Starlog, a Klingon is third in command of the Enterprise.

(BPS) Sitcomm_whatever-sitcomm-we're-on-b: the STrek: The Next Generation ad contains footage from STrek 1, 2, and 3 and no new footage at all.

(HAM) Pianocomm: I've got a new keyholder sheet; everybody who should sign it should sign it where they should sign it.

(KM) Sitcomm_n+2: MTV had a short clip on William Gibson in which he says "The people today who rip your stereo out of your car and take the hubcaps off your wheels are going to be the people in the future who mess with your bank account and credit cards."

(VHS) Moocomm: this Wednesday they previewed Hellraiser on campus at 8 PM. My Writing Genre Fiction class was 7-10 and after passing out the class schedule, Joe Haldeman adjourned our class to 26-100 to study the horror genre and got us a block of seats in the third row.

( ) Moocomm: review of Hellraiser- very, very, very bloody, lots of violence, a decent amount of sex; highly recommended (especially if you like meathooks).

(TG) Moocomm: The Princess Bride is supposed to be opening this Friday or next. Goldman is doing his own script.

(BPS) Concomm: TJ Burnside, back from England, said the con was lots of fun, especially since they did the movie programming in a real movie theater across from the hotel. The hotel management were acting like a bunch of dweebs, and people started sticking post-it notes to the walls with jokes such as "How many hotel managers does it take to cover the roof? Only one if you slice him thin enough," "How do you save a hotel manager from drowning? Take your foot off his head," and "How can you tell the difference between a dead hotel manager and dead skunk in the road? There are skid marks leading up to the skunk." The hotel employees were adding to these.

(GF) Addendum- the bartenders were giving out free drinks for the best ones.

(JME) Concomm2: a "Weaponscomm" was held- the weapons policy being that you must carry a weapon at all times, even if it's only a paper dagger. Report from an attendee is that their weapon policy wasn't followed either.

(GF) Concomm3: the hotel closed the pool for the duration of Worldcon, half the convention room was under construction, the day before the con the committee learned that the bars would not be opened half the time they were supposed to be open, and the hotel locked people out during the fireworks display.

(JME) Motion to condemn HAM for stealing people's souls. Motion seconded, passes by acclaim.

(BPS) Motion Herb (mumble mumble mumble) eats the camera. Motion seconded, passes by acclaim.

(BPS) Addendum to GF- TJ Burnside mentioned that the fireworks display had to officially notify the nation of France in advance so that they wouldn't think we were launching artillery at them.

(KM) Famecomm: MITSFS appeared briefly in Newsweek on Campus, September issue. They said we called ourselves "Misfits."

DSK makes and passes a motion to summarily condemn Newspeak.

(CH) Sitcomm: Frank's Place starring WKRP's Tim Reed is about a businessman who inherits a creole restaurant in Louisiana.

(JH) It's being billed as Cheers with voodoo.

(BPS) Sitcomm: the new season of Kate and Allie opened with a 12 year old character as an adult coming back to the old building with his son and telling a story in flashback. No weird references like "Of course, that was before the war."

\goto{Old Business}

(BPS) I took my bomb home with me last week.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: from 9/11 Glob- a burglar on probation was arrested for lighting a pipe full of crack in a police station lobby. Article attached.

(TG) Minicult: there was a comic book cover from about 20 years ago with the villain on the front exclaiming "You can't hurt Bork, but Bork can hurt you!"

(SSDT) Minicult: a woman was killed by a runaway escalator in New York. Article attached.

(BPS) Minicult: from 9/16 Glob, as a followup to last week's "Few Aliens with Guns Have Hunting Permits," is "US Probes Gun Trade by Aliens in Massachusetts."

(BPS) Pseudo-Moocomm: comedy actor Doodles Weaver- in our movie poster "The Clones"- is the brother of Pat Weaver who ran NBC and therefore the uncle of Sigourney Weaver.

(TG) Minicult: a month ago the Weekly World News ran 10 warning signs of how to tell if your neighbor was a werewolf. A few weeks later a woman wrote to thank them because her neighbor fit these exactly and now she was sure.

\vspace{12pt}

\noindent
Meeting adjourned, ? SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}