\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 9, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

Phonecomm: it's Janice, she's going to be late.

(CJH) Motion to approve the minutes as slightly stopped up.

Motion chickens 6-3-10 +Spehn.

(HAM) Motion to approve the minutes as unapproved.

Various seconds. Motion passes lots-"no, no"-2 +Spehn.

\goto{Committee Reports}

(JAH) Onseck Report: I'm going to be here next term after all, so Sue doesn't need to find a new Onseck.

(DSK) LHE Report, following good news with bad news: Assets- 3145.92, Income- 126.49, Expenses- 503.15, Equity- 2769.26, Loss- 376.56.

(KM) Pseudo stuff: 1) Pseudo-Jourcomm: TZ RSN!!! Last chance to get something in. 2) Pseudo-Huntcomm: Huntcomm needs to decide on a list of questions by the end of this weekend. Non-Pseudo-ROSFAP: we keep getting fanzines; if anyone is interested they can ask me about them.

(SSDT) Inventory Report: we're going to have one, in spite of a few glitches in the PinkDex program.

Phonecomm: it's Janice again; she'll be here soon but won't be able to make the inventory.

(BPS) Sitcomm: tomorrow, CBS, a 2-hour made for TV movie called Return of Sherlock Holmes in which Watson's great-granddaughter finds Holmes in cryogenic suspension and wakes him up in the present day. Sitcomm sub 2: Outlaws is really bad.

(CJH) Rainbowcomm: James Garner has threatened to personally punch Ted Turner in the nose if he colorizes The Americanization of Emily.

(BPS) Brustcomm: Teckla is out. Opinions vary. I didn't like it.

(CJH) Bookcomm: Wild Cards is out and it's very enjoyable.

(HAM) Anthonycomm: Bio of a Space Tyrant V is out if anyone cares.

(SLP) Sitcomm: Remington Steele is back on Mondays.

(BPS) Sitcomm: last Tuesday's Moonlighting was a montage done on the them of Rona Barret investigating why there wasn't a new show. It was very strange.

(SLP) Another Sitcomm: Stingray is back and it was good the last time it was on.

(CJH) Sitcomm: a tinted version of The Thief of Baghdad is on tonight on Channel 2. It was tinted in the original too, so this isn't really a colorized version.

(BPS) Sitcomm sub n: tomorrow at 10 on PBS is part one of a three part miniseries adaptation of Day of the Triffids.

(JAH) Moocomm: I have not yet heard a bad review of Little Shop of Horrors.

(KM) Sitcomm: if you get cable, channel 11 is showing The Prisoner on Sunday evenings.

(DSK) Moocomm sub 2: Mad Max tonight at LSC.

(BPS) Whooshcomm: NASA announced the commander for the next shuttle flight in February of '88; it's Francis Hauck, who got his masters' degree in nuclear engineering at MIT.

\goto{Old Business}

(HAM) I'm here.

OBA: Usual Garbage.

\goto{New Business}

Phonecomm: it's Adam.

(BPS) Minicult: too many people won the lottery, so they had to lower the big prize to 900 dollars a year for 20 years.

Miller motion from somewhere.

It's seconded. It fails.

Miller motion from somewhere else.

Motion passes 15-4-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1738 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}