\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 9, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Rob Gates, LHE and Pseudo-Skinner, presiding.

Minutes of the previous meeting read by pseudo-onseck.

(MY) Motion to approve the minutes as day-glo yellow.

( ) Motion to declare the minutes pseudo-minutes.

(KM) Motion to approve the minutes as banana yellow.

Forbidden by pseudo-skinner. In the end, a motion is made to declare the minutes as "No." Motion seconded, passes many, many, many-not many-a few baas and a moo +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: TZ Real Soon Now. I'm sick, don't bother me.

(JME) Pseudo-Libcomm/Moocomm: Asimov's magazine is serializing Harlan Ellison's-

Phonecomm: ring. It's the vice, and RJG won't get off the phone. (JME) Move to condemn the vice in absentia. Seconded, passes by acclaim.

-never produced screenplay of I, Robot in three parts starting in the current issue.

(BPS) Mobcomm: I got hung up at work and didn't get home until late. I got home and found my porch and front door all painted, complete with wet paint signs. I had to duck under a fence to use an obscure side entrance.

(JME) Pseudo-Moocomm: Princess Bride opens locally today.

(BPS) Sitcomm: Next STrek premiered last Saturday, and Monday, and Monday and this evening at 9 PM. It has holes, but it's pretty good. This coming Saturday at 8 on channel 5 is episode 2; 3 is next Friday at 9, also on channel 5.

(JME) Addendum- the next episode is apparently a sequel to The Naked Time.

(GF/MY) Positroncomm: according to the Herald, the series Once a Hero has come close to the all-time world record by getting canceled after two episodes, which were not shown on the local stations at all.

(BPS) Followup- Not only has Once a Hero, a TV series about a comic book character, been canceled, in its time slot will be Sable, which is a TV series about a comic book character. And channel 5 still won't carry it.

(JME) Sitcomm: in the second week of the new season, Max Headroom came in 72nd. It may not have a long life ahead of it.

(BPS) Sitcomm: they resurrected Thomas Magnum, rather believably, also.

(KM) Rosfap: there are new fanzines.

(BPS) Mobcomm: we now have the ninth and latest volume in the Mission Earth decology.

(BPS) Mortcomm: according to the Tech, they're dropping like flies.

HAM is Albanianed for saying someone told him to drop in for dinner.

\goto{Old Business}

(KM) Not only did Bridge Publications give an advertisement for all of L. Ron Hubbard's books after promising not to talk about them at Worldcon in Brighton, but it turns out the Mission Earth logo was on the cover of the pocket guide to the con, and it included many full page advertisements for Bridge Publications.

(BPS) Happy birthday, Sputnik- five days late.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: a book has just come out called "Man Suffocated by Potatoes," which is a compilation of minicults. Why didn't we think of it first?

( ) Move that people not be allowed to read from this collection.

Motion seconded, apparently passes by pseudo-skinnerial decree.

(BPS) Minicult/Whooshcomm: there is a joint US/Soviet space project going on involving, among other things, a couple of monkeys in the Russian satellite. One of the monkeys, whose name is Russian for troublemaker, apparently managed to free its left arm from the restraints and has been happily playing with everything within reach. They first noticed something was wrong when a camera pointed at the monkey showed his nameplate was no longer on his helmet. Article attached.

(JME) Minicult: according to Spike McPhee, the current bestselling book at the Science Fantasy Bookstore is The Death Sun, a comedy/mystery set at an SF con.

(JME) Minicult: from the Glob- a train carrying hundreds of tons of corn derailed in Montana in 1985, and some of the corn was left at the site. The corn has now fermented and has been drawing bears from all around who get falling-down drunk on the fermented grain. Article attached.

(JME) Minicult: also from the Glob- four officers suffered minor injuries subduing a man who had dozens of pins and needles stuck through his palms and arms. The man was also carrying a 12-inch Bowie knife, a Navy survival knife, two throwing knives, and a buck knife. Article attached.

(JME) All of you had better come visit me when I'm in the hospital for surgery.

(BPS) Minicult/Sitcomm: according to McPaper, the premiere of Next STrek got incredibly good ratings. Article attached.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST, after only half a verse of rabbits.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}