\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 10, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Hawthorne, Vice and Pseudo-Skinner, presiding.

Minutes of the previous meeting were read and corrected (massively).

(JME) Move to approve the minutes as bringing new heights of creativity to the art of spelling.

(SST) Motion to approve the minutes as Dirty Gently Sadistic Detective Agency.

Skinner protests matrix vote and removes matrices from existence inside the MITSFS.

(RvdH) Move to go on to Committee Reports and bypass this whole issue.

Motion seconded as passes many-a few-a couple +Spehn.

\goto{Committee Reports}

(JME) Bananacomm I: In Evansville, Indiana, a burglar pried open the door of an apartment and apparently stole a banana belonging to the 70-year-old woman who lived there. The peel was found in the bedroom. The police did not estimate the value of the damage done to the front door but the value of the banana was listed as five cents.

(JME) Bananacomm II: A South Carolina man, Joseph Frazier, shot his brother Randolph in a dispute over a banana. Joseph told the police that Randolph had attacked him with a hammer and handsaw after noticing that one of two bananas was missing from the kitchen of their father's Georgetown home. "I had seen the banana on the counter," Randolph said, "and when I came back it was gone." Their father, John Frazier, told the police he had eaten the banana in question while Randolph was out. There was another banana left but his sons weren't interested in that.

(JEH) Inventorycomm: Inventory on the weekend of August 1 and 2 unless nobody can make it (general hissing).

(JME) Jourcomm: please write for TZ, please write for TZ. In response to complaints, Ken (if he ever gets here) will put up an alphabetized by author list of the review books, equally nicely laserwritten. Now c'mon people, the only person who has submitted anything so far is Bill Starr, who wrote two essays. The least a couple of you can do is to review a couple of books that you probably read anyway.

(JEH) Birthcomm: Robert Heinlein turned eighty last Tuesday, which is pretty good for a guy who was told that he wouldn't live past thirty. Although he is getting pretty braindead in his old age.

(JME) On a related note, we do have the new Heinlein opus: To Sail Beyond the Sunset, a.k.a. to fuck everything that moves. It is the memoirs of Lazarus Long's mother/wife/daughter... it gets really weird.

(JME) Pseudo-Albanian People's Embassy: by way of Tom Galloway (sp?), which is appropriate since he probably had the highest earned Albanian average of any one meeting attendee. He submitted an editorial from the Los Angeles Times headed "Remember Albania" which notes how xenophobic and crazy they are, that private cars are banned, and that long fingernails for women and long hair for men are banned. They are actually opening up a little bit. About 6000 tourists per year are allowed to enter, although Americans and Soviets need not apply, but the article points out that there is little to do once you get to Albania anyway.

(JME) Infocomm: This is a new game by Infocom, called Lurking Horror, which is inspired by Lovecraft, but takes place in a school peculiarly resembling a certain institution that we may be familiar with. (RPI?) This institution fronts on Massachusetts Avenue, has a Great Dome, a Great Court, an infinite corridor, temporary buildings left over from World War II, a separate, very tall building called the Brown Building... Anyone who wants to see the little booklet that came with it may. The game features characters including a computer nerd with an enormous number of keys hanging from his belt, and an urchin that runs around stealing things from various offices and laboratories. It features the Department of Alchemy.

\goto{Old Business}

(JME) Regarding "Dirty Gently Sadistic Detective Agency," there was a slight problem in England. Douglas Adams needed a number for the detective agency, so he called British Telephone and got a nonexistent telephone number. Unfortunately, in typesetting the book two of the numbers got reversed, and the number was actually that of a government office in Islington. Which probably by now has changed its phone number.

(JME) On that Supreme Court decision, it should be noted that the two people who voted in favor of Creationalism thought it was dumb. Their reasoning was that the legislature said that it wasn't a religion and that they were the legally elected representatives.

OBA: um, us, uv, ur.

\goto{New Business}

(SST) Two articles from the Seattle Times/Seattle Post-Intelligencer: Wild pig downs Pakistani jet. The Pakistani defense minister has acknowledged that its air force lost an American-built F-16 fighter jet- regarded by many Pakistanis as an invincible aircraft- in a one-on-one with a wild pig. The 18-million-dollar, high-tech fighter hit a boar as it roared down the runway, the nose gear broke as it struck the pig, and it caught fire and was destroyed.

(JEH) Minicult: while picking up some stuff at the Rite-Aid pharmacy the other day, I spotted this new confection staring me in the face- quite new on the market. It's called Tribbles. (JEH gives samples- bleah!)

(JME) Motion to condemn and remove that horrendous calendar over there (the one with the cute little bears on it).

Motion seconded, passes many many many-4-2 +Spehn.

(JME) Minicult: story from the Wall Street Journal entitled "Thank Goodness We Have Courts That Can Settle Issues Like This"- there are two heavy metal groups that are involved in a lawsuit over the name Megadeath. As those of you who have seen Dr. Strangelove know, it's a term from Nuclear Disaster meaning 1 million dead people. The two groups are Megadeath and Megadeth (without the second a). The first group plays in LA clubs while the second tours the world, has two records, and appears on MTV. Bob Rickets, alias Thor Gunderslau, of the first band, says "We were playing around first, and we have the rejection slips to prove it." As another name, they are considering the alternative "Leather Armpit."

(SST) Minicult: In Boulder, Montana, there's an old mine that isn't being used as a mine anymore. The thing is, it's full of radon gas, just under the limit of what you're allowed to expose civilians to, and a bunch of people hang out there to cure their arthritis and everything. The company that owns the mine is running it for this purpose and charging admission.

(CH) Headline Minicults: "My Husband Can't Go to Heaven With Missing Parts- Wife wants mate's transplanted organs back," and "Your Psychic Powers Can Help You Do the Housework."

(JME) Minicult: Pet Goldfish Raped, Left for Dead, as Lust-Struck Cane Toads Hit Ponds. The president of the Townsville Aquarium Society, Mr. Paul Devine, recently came home to find his goldfish pond surrounded by about eighty toads. The next morning, seven of his goldfish were dead. "I've never had this trouble before," said Mr. Devine, "but then I did a bit of reading and realized that the toads had taken a fancy to my goldfish. They were jumping in and trying to mate with them." A zoologist from the local James Cook University, Dr. Ross Alford, confirmed Mr. Devine's theory. Dr. Alford said that at this time of year, cane toads are sex-crazed. "I have stood on the edge of a pond and had a cane toad try to mount my boot," he said. "They aren't really the sort of beast that you want mating with your boot."

(SST) Oral Roberts is claiming that he has raised dead people, or at least sleeping people. He has also said that come Judgment Day, we will be sitting alongside Jesus meeting our judgment. His son gave an example- during one of his sermons, a mother screamed that her baby had died. She ran up to Roberts, who touched the baby, and wonder of wonders, it was alive. Since babies are known to stop breathing for no particular reason, it was probably a case of that. Sort of like Uri Geller and watches.

(JME) One last Minicult: after two racing buses crashed into a train, killing 35 people, some residents of Karachi, Pakistan, rioted and attacked other buses. Similar riots have occurred following recent bus accidents. According to an AP dispatch, Pakistani bus drivers compete for riders, racing each other to groups of waiting passengers. Long-promised reforms have not materialized, largely because many bus companies are owned by police and government officials.

(SST) From the advice columns: a person reported that the phone company, after the breakup, sent a bill for 0 dollars. So they threw it out, and a little bit later, they got another bill for 0 dollars which said "this is overdue." So they called up the phone company and said this is silly, and the phone company said that they would take care of it. Next month, they got a bill that threatened to sue them if they didn't pay the 0 dollars. So they got disgusted and wrote a check for 0.00 and sent it to the phone company, who thanked them and sent them a 5 dollar rebate. And this has been happening every month for two years.

(KM) Miller motion. Failed.

Miller motion. Motion seconded, passes many-few-many plus Oli North +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1747 SST.

\vspace{18pt}

\centerline{Submitted in English,}
\centerline{Rob Gates, One Last Time, Pseudo-Onseck}

\end{document}