\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 16, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(Paul Dworkin) Motion to approve the minutes as well-defended.

Motion passes 7-one nonexistent freshman-0 +Spehn.

\goto{Committee Reports}

(SSDT) Skinner Report: inventory was last Saturday. It went very smoothly; we were done in time for people to go and have dinner at a reasonable hour. There were a lot of missing things in the Small Comics Reserve section, though.

(BPS) Pseudo-LHE Report: we're still trying to find that 500 dollar check; we haven't managed to get anyone to acknowledge its existence.

(KM) Pseudo-Jourcomm: write for TZ or die a horrible painful death. We could still accept book reviews and artwork at this late date.

(BPS) Cornelia Otis Report on Political Weirdness: Rebel paratroopers have captured the Ecuadorian president and are holding him at an air force base. The vice president has taken over and the first thing he's done is declare a state of emergency.

(SSDT) Cornelia Otis Report sub 2: someone wrote in to the Glob wanting to know if she was still alive. Apparently she died in 1979.

(BPS) Sitcomm: I watched both Outlaws and The Return of Sherlock Holmes last week and Outlaws was by far the better show.

(DSK) Moocomm: Enemy Mine Wednesday night at LSC.

(BPS) Moocomm: the Orson Welles Theater is still closed indefinitely after last summer's fire; the SF marathon that always runs opposite Boskone will however still be held at the Somerville Theater in Davis Square.

(GF) Boscomm: deadline for Boskone preregistration is today.

(JME) Jourcomm: I am putting together final copy on TZ the weekend after this one. We have no current book reviews. Also, Huntcomm: we have 2 team entries and 4 individual entries, including one headed by Bruce Pelz of LA Fandom and SMOFdom.

\goto{Old Business}

(BPS) Happy 100th anniversary or 133rd birthday, Sherlock Holmes.

OBA: um, us, uv, ur.

\goto{New Business}

(Mike F) The MIT phone system is having a weird problem- it's allowing you to call anywhere long-distance for free.

(JME) Minicult: there's an entrepreneur in Austin, Texas named Jeffrey Knight Bird who's selling guaranteed drug-free urine samples by mail. It comes either freeze-dried or liquid. Bird says he wants to become America's first urine millionaire but insists he is motivated by concern for civil liberties.

(SSDT) Minicult: an ad for the Wall Street Journal has appeared on the radio several times. It's one of their news stories about Japanese overproductivity. The government is worried that the overproductivity will eventually hurt the economy, so they set up a Bureau of Leisure to try and convince workers to take it easier. It didn't work, though, because people would come in to work at the Bureau of Leisure on weekends.

(BPS) Minicult: Coleco has forecast a large loss for the fourth quarter of 1986 due to a huge collapse in the sale of Cabbage Patch Kids.

(JME) Minicult: I have the greatest Jews for Jesus pamphlet here; it's based on Star Trek IV.

(JME) Pseudo-Minicult: Harlan Ellison was found innocent of all charges of libel against him for referring to a comic book writer as "bugfuck and certifiable" on the grounds that it was an expression of opinion that was about the work and not about the person and that it wasn't intended as an insult.

(SSDT) Minicult: Nippon Airlines in Japan has found that painting eyes on the engines of their planes prevents birds from striking them. Over a test period, the painted engines experienced one strike while unpainted engines experienced an average of 22.

(BPS) Minicult: from the Wall Street Journal a couple days ago- the ad campaigns for Kent Cigarettes on billboards and magazines feature silhouettes of people with the words "the experience you seek." Unfortunately, some people are seeing the shadowy figures as ghosts, not silhouettes, which leads them to think of the link between smoking and lung cancer/heart disease. It's gotten several awards from various ad agencies as "bad idea of the year."

(BPS) Minicult: up in Canada, they don't know what to do with the warehouse full of contraband liquor that's been seized by customs officials when Canadian citizens try to buy cheap liquor in the US and take it back to Canada. They can't pour it down the sewers; it's considered dangerous because it's flammable. They used to get rid of it by donating it to veterans' hospitals, but as the government says, "There aren't enough veterans anymore- we haven't been in a war in a long time." They can't sell it because only the Quebec Liquor Corporation monopoly can sell liquor and they won't buy it from the government. The best suggestion they've had is to dye it all blue and sell it as windshield wiper fluid.

Phonecomm: it's Rob, looking for Lisa Kroh.

(DSK) Motion to commend Mike for wearing a banana-colored shirt.

(JME) That's so boring!!!

(DSK) Miller motion.

(SSDT) It fails.

(JME) Motion to condemn the bananas Ken brought me for not being banana colored.

Somebody seconds it.

Motion passes many-2-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}