\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 10, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous meeting read and corrected.

(RvdH) Motion to approve the minutes as baby blue and laced up.

Silence.

(JAH) Motion to approve the minutes as M-E-L-T-sner.

Motion passes with overwhelming support.

\goto{Committee Reports}

(BPS) Sitcomm: I sat down and watched the first two Max Headroom episodes back to back. The production values are incredibly high although the scripts have some weak points in them. It's still definitely worth watching though, especially for the glorious computer graphics.

(KM) ROSFAP: Janice has gotten us on the mailing lists for some very good fanzines, including Lan's Lantern which won the Hugo this year.

(KM) Pseudo-Jourcomm: write for TZ!

(BPS) Mortcomm: from John Dumas- British actor Patrick Troughton, who was the second Dr. Who, passed away last week.

(CCH) Apparently he died in his hotel room at OpusCon, where he was the guest of honor.

(Ken Meltsner gets Albanianed for commenting, "They must have had a fun Dead Dog Party.")

(CCH) Crashcomm: Tuesday night I got rear-ended by a drunk driver who proceeded to drive off without saying a word to me. I managed to get his license plate number, though. I was totally unhurt but it's going to cost 1,891 dollars to get my car repaired. In case you happen to see it, it's this color. (Pulls out a piece of blue wreckage.

(BPS) Mobcomm: My car now has a low-jack system, a dual-lock anti-theft system, a Bensi box, a new radio, and next week it's getting armor on the steering column. I'm serious.

(JME) Jourcomm: We've gotten more LoCs on TZ, including one from L. Sprague DeCamp, who makes several nasty cracks about Reagan. We also got some art submissions and some zines in trade. Also, people can write anything they like for TZ- it doesn't have to be about SF or fantasy.

\goto{Old Business}

(SSDT) We got a letter from George Phillies. It has a Minicult which I will read later in the meeting.

(JME) A report from Merryl; the bad news is that she didn't get a job up here, the good news is that she got accepted to Tufts and, if all goes well, will be starting there in September.

OBA: um, us, uv, ur.

\goto{New Business}

(SSDT) Minicult: from George Phillies- he makes note of the fact that it is now possible to make laser printer type look like thermofax print.

(BPS) Minicult: somewhere in California, a bunch of high school kids were in the habit of playing Lazer Tag on the grounds of their school at night. A few days ago, somebody spotted this and called the police. The deputy arrived, saw somebody holding something that looked like a weapon, and shouted "Police! Halt!" The person turned and pointed the weapon at the cop, at which point the cop fired one blast from his shotgun and killed the 17-year-old kid. You can expect a bunch of legislation prohibiting things like Lazer Tag any day now.

(CCH) Minicult: "SpinOff," in Kenmore Square, is looking to change its license from being a roller rink to being a Planet Photon franchise. They're also building a Planet Photon in Agawam.

(CCH) Famecomm: anyone who checks out the Boston Glob editors' column might notice a familiar name: Janice Eisen.

(JME) Motion to commend the not-yet-coffee stained banana colored rabbit.

Motion seconded, passes 13-1-1 and 2/2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}