\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 20, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(SSDT) Motion to approve the minutes as not as effective as carbon monoxide.

Motion seconded, passes everybody-sorry, Connie-12 +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: It's a TZ!

(BPS) Sitcomm 1a: I have the 10/23/87 Boston Phoenix review of Next STrek. It's a very good review; I'm putting it in the blue folder. 1b: Paramount has renewed Next STrek for another season.

(JME) STrekcomm: I'm posting the rules for "Next STrek- The Party Game." It includes such events as spotting missed opportunities for Wesley to get killed.

(DSK) Sitcomm 2: Empire Strikes Back at 8:30 Sunday night on ABC.

(RJG) Sitcomm 3: Dangermouse is shown every weekday at 8:00 on Channel 68.

(JME) ????comm: there is a notice on the board of Ken's and my last party before we depart for the wilds of Schenectady. It's on Wednesday in building 13. Our new address and phone number is up there as well.

(BPS) Hackcomm: as pointed out in the Tech, Starvin' Marvin's cafe briefly became the Salmonella de Puerto Rico.

(DSK) Hackcomm 2: they flipped Lobby 7, a mirror image down the Infinite Corridor, including the second and third floors.

(Phil Nesser) Addendum- there were only 4 things we couldn't get: the backlit map, the TV hanging on the left side, the giant black thing on the third floor, and a little plaque that says "gift of the class of 68" on the second floor. We put the gift on the other side, but the plaque was cemented to the wall.

(HAM) Hackcomm 3: Due to the inability to get enough paint together in time, nothing interesting will happen to the Harvard-Yale game, because 3rd East blew it.

(JME) ????comm 2: apparently Jerry Pournelle's wife is leaving him, because he told her he was going to Worldcon and instead went to Europe for two weeks with a female fan about half his age.

(SSDT) Report from the Ambassador to Null Space: I went to another ASA general meeting. A new constitution- not the one we spent two hours revising last meeting- was passed unanimously; if it hadn't passed unanimously we would have missed the quorum.

(BPS) Sitcomm sort of: based on last night's NBC lineup, starting with Night Court at 8:30 and ending with LA Law at 11, I am about 70 percent certain that somebody has bombed the NBC censor office.

(BPS) Sort of Sitcomm 2: from last night's TV Guide, one of the greatest pieces of understatement I've seen- the 11:00 movie for channel 2 was the AIDS educational show hosted by Ronald Reagan Jr. After a detailed description of what subjects would be covered was the warning "Channel 2 plans to announce that this show may not be suitable for all family members."

\goto{Old Business}

(BPS) While you were gone we held a mini-coup, and decided to rename the Telzey's Gavel the Telzey Toy.

(JME) Addendum- that's actually the title of one of the Telzey Amberdon books.

Meeting is called back to order by DSK after several conjectures relating the Telzey Toy to certain features of the Klingon anatomy.

(DSK) Concerning the chain letter I got last week, it's been eight days and I haven't died yet.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS)Minicult: in Arizona a child molester was sentenced to 2,975 years in jail before he's eligible for parole, due to 85 counts at 35 years apiece. Article attached.

(DSK) Motion to commend. Passes by acclaim.

(JME) Minicult: there's food hoarding going on in Yugoslavia because, in an effort to combat inflation, the government is raising food prices 30-70 percent. Apparently Yugoslavia is moving closer to Albania.

(BPS) Minicult, almost Moocomm: this weekend Warner Bros is releasing the first new Daffy Duck (7.5 minute)short since 1968. It's called The Ducksorcist, a takeoff on The Exorcist. Mel Blanc is doing the voices. Article attached.

(CH) Related semi-Moocomm: there was a review of the Mighty Mouse cartoon series in one of the comic review magazines that was really favorable.

(KM) It's almost a thesis.

(SSDT) Minicult: from last week's Newsweek- a lieutenant colonel in the Army, who is a high priest in the Temple of Set, is being investigated for possible child abuse. Apparently the Army feels it's okay if you're a Satanist (they've given him a security clearance).

(JAH) Miller motion. Seconded, fails.

Motion made and seconded again, 35-2 and a loud Connie-3 and a strange Rob +Spehn. Motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}