\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 20, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

Minutes of the previous two meetings read and corrected.

There is a Phonecomm during the reading of the first set of minutes. It's Larry (presumably Lendthoff) who says he'll be here in time for dinner.

(KM) Move to approve the minutes as longer than you can possibly imagine.

(BPS) I don't know, I can imagine quite a bit.

Dies for lack of second.

(KM) Move to approve the minutes as long enough to reach the ground.

Motion seconded, fails 8-9-6 +Spehn.

(JAH) Motion to approve the minutes as hours.

Motion seconded, passes everybody-3-3 +Spehn.

\goto{Committee Reports}

(DSK) LHE Report: LHE Report RSN!!! Bank statement's in.

(KM) ROSFAP: Worlds of If will have its second issue Real Soon Now. The first issue came out at WorldCon.

(SSDT) Pseudo-Catacomm: Kathy- there are some magazines in the ZGT that got picked up mint at Boskone and one that Witter sent.

(BPS) Moocomm: Sigourney Weaver got an Academy Award nomination for her performance in Aliens. And the movie itself comes out on VCR tape this week or next.

(CH) Sitcomm: St. Elsewhere is on hiatus for March.

(KM) Sitcomm: Twilight Zone is going to Sundays at eight until they use up what unshown episodes they have left.

(KM) Sitcomm: A great rumor from Tom Galloway saying that Harlan Ellison has been hired to write a script for Moonlighting but it's being held up by the need to get the rights to use Godzilla.

(CH) Sitcomm: Spencer for Hire filmed at Lotus today!

Phonecomm sub 2: it's Chris Phelan, leaving a number for JAH.

(BPS) Sitcomm: I'm watching a pseudo-SF thing on TV called Amerika.

(KM) I'd rather watch the collected best of Alf.

(KG?) Sitcomm: a new series premiering on ABC next month: The Charmings. Mr. and Mrs. Prince Charming and the mother-in-law move to Suburbia. Sample dialogue: "After a thousand years, Snow White, a man has needs." I am not making this up.

(MY) Sitcomm: a syndicated animated cartoon series called Comic Strip is premiering soon. It was scheduled to have a segment based on Alan Dean Foster's Spellsinger, but someone must have decided it might have been worth watching because they pulled it out and replaced it with a cartoon about frogs.

(BPS) Moocomm: somebody is making a movie based on the first book of the Gor novels. They are filming it in South Africa.

\goto{Old Business}

(BPS) 25 years ago John Glenn became the first American and therefore the first person who mattered to orbit the Earth.

(KM) I talked to another editor of Twilight Zone about TZ and he also was perfectly reasonable and also did not want to talk to the folks at Viacom about it. Not only that, he gave me a souvenir lighter.

(SSDT) The midway was but almost not. I decided we weren't going to have a table after all since it was in Lobby 13. The Central Square package turned out to be a long overdue Weinberg shipment. And the table at Boskone took in 140 dollars, all but 20 of which is profit. We also got 26.47 from the APO book sale, and our For Sale shelf is down from five shelves to one. We still haven't gotten rid of those InSight magazines, though.

OBA: um, us, uv, ur, "what about the usual debate?" "Shut up."

\goto{New Business}

(BPS) Minicults: 1) the Freemasons have decided that beheading and ripping out the tongue are not fit punishments for violating Mason rules. They appear to have been on the book for a long time but have been used mostly for scaring off new members. 2) In England, a robber was convicted of several holdups. His attorney said that he wore nothing but a stocking mask over his face because he didn't want to be recognized by his clothes. Witnesses identified him "by physical characteristics."

(RvdH) Minicult: also from England, People Magazine has an article about a "liberal peer" who is a Buddhist and a vegetarian and who has requested in his will that when he dies, his body be given to a London home for stray dogs, chopped up, and fed to them. The stray dogs home refused because they didn't want to have to chop him up.

(CH) Minicults: the first three of which are all from England.

(MY) Move to commend England!

Passes by Skinnerial decree.

(CH) Minicult: 1) A paralyzed driver continues to drive his car by using a table leg to push the pedals. 2) A mayor was presenting a check to a school for guide dogs when one of the dogs present grabbed it and ate it. 3) A purse-snatcher had hysterics after he tried to snatch a lady's purse and came away with her artificial arm instead, which clamped itself around his wrist and resisted all his attempts to shake it loose. The purse-snatcher started screaming his head off, apparently believing he'd actually pulled her arm off.

(DSK) Move to commend England for some of the weirdest criminals of all time!

(SSDT) Absolutely!

Passes by Skinnerial decree.

(CH) Then there's this article about a man selling colored toilet paper for hunters so they don't get shot while going to the bathroom in the woods. It comes in orange, brown, and green.

(Paul Dworkin) There's a Dr. Who marathon tonight over in Talbot Lounge.

(GF) Minicult: a New York police station has given its first humanitarian award to Richard Nixon.

(KM) Move to commend Richard Nixon for having a banana-shaped name.

Motion seconded, passes lots-less-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1752 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}