\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 25, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(JME) Motion to accept minutes as not quite read.

Motion seconded, passes 15-12-not quite 15 +Spehn.

\goto{Committee Reports}

(JME) Sitcomm: from the Glob- last week's premiere of Max Headroom involved the arrest and trial of the character Blankredge for zipping (hacking network TV transmissions) which carries the death penalty. The Glob printed a photo from today's show with the caption "Celebrating Blankredge's escape from the death penalty are..." before the show aired.

(BPS) Sitcomm2: Last night's Cheers marked the premiere of Lt. Saavik as the owner of the bar.

(JME) Sitcomm3: Beauty and the Beast premieres tonight.

(TG) Sitcomm4: it has been noted that Bork looks like the guy who used to play King Tut on the Batman TV show, and if we bonk him on the head with a brick it should keep him from going through because King Tut probably wasn't Christian.

(BPS) Addendum- the actor was the late great Victor Buono.

(DSK) Sitcomm 4b: Bork also looks like John Corley, MIT's Concert Band director.

(JME) Pseudo-Moocomm: The movie The Princess Bride won best film in the Toronto Film Festival.

(JME) Pseudo-Moocomm2: Amazon Women on the Moon opens today. A reviewer compared it favorably to Kentucky Fried Movie.

(BPS) Addendum- the ad says "Starring: lots of people."

(TG) Albanian Embassy: a professor at the University of Tirana says "Although English is the second language of Albania, Albania is not opening up to the West. Albania will remain Albania."

(JME) Jourcomm: TZ Real Soon Now, Leave Me Alone, I'm Sick.

(BPS) Mortcomm: choreographer Bob Fosse of All That Jazz.

(JME) Pseudo-Sitcomm: John Cleese won an Emmy for his appearance on last season's Cheers.

(DSK) Moocomm: Peggy Sue Got Married tomorrow night at LSC.

(JME) Preemptive Albanian Motion (on TG). Seconded, passes by acclaim.

(BPS) Cornelia Otis: in the Piled Higher and Deeper department, Reagan said that Bork would not only be appointed, but would go down in history as one of the greatest Supreme Court justices of all time.

(BPS) Cornelia Otis 2: Joseph Biden.

(JME) Cornelia Otis 3: Photograph in the paper today of Ronald Reagan spinning fingers around his ears.

(BPS) Cornelia Otis 4: Gary Hart at BC said he was thinking of joining the Doug Flute campaign because by the time this is over he might be the only one left. Addendum- Gary Hart's autograph looks like Larry Flint's.

(TG) Penthousecomm: Jessica Hahn is in Playboy this month.

Time warp from time warp to Old Business from New Business.

(TG translated from the Albanian) Pseudo-Moocomm: STrek 3 is being shown on TV this weekend- could this have anything to do with a certain show that's premiering next week?

(JME) Sitcomm: I saw a new promo for STrek: The Next Generation.

(SSDT) Moocomm/Minicult: I saw a sign that had been hacked to read "Elderly Crossing- 10 points."

(DSK) Sitcomm: NBC is running The Terminator Sunday night at 9.

End time warp.

\goto{Old Business}

(DSK) I still have my cold, which has developed into pinkeye.

(SSDT) Addendum- the weather was terrible last weekend also.

(RvdH) Addendum- just so it would rain while we were moving.

(JME) Addendum- not only am I still sick, I'm getting hot flashes.

(BPS) Move to add "Herb mumble mumble mumble eat the camera" to the um. Motion seconded, passes by acclaim.

Time warp from New Business.

(SSDT) The ads for Robocop say "11 weeks and still hasn't stopped for donuts."

(JME) Tomorrow night's Saturday Night Live is a repeat of the show with William Shatner and has a very funny Star Trek sketch.

(BPS) Spike's discount policy for the Science Fantasy Bookstore is now posted by the desks.

End time warp.

OBA: um, us, uv, ur.

\goto{New Business}

(TG) Minicult: the new Truth or Consequences hostess is Carol Merril's daughter.

(LK) I got a new car- '82 Ford Escort.

(JME) Ken had his first publication in some artificial intelligence book.

(CH) Minicult: from the Glob- Navy 1, Air Force 0. A Navy F-14 shot a USAF reconnaissance jet with a sidewinder missile.

(RvdH) Minicult: AIDS, Italian food, and the vanishing ozone layer may cause vampires to be almost extinct by the year 2000.

(JME) Related Minicult: a Japanese researcher has new garlic with all the taste and none of the aftertaste/odor on the breath.

(BPS) Minicult: from the Glob- undercover police responding to a call at Mayor Koch's home in NYC found a guy in the kitchen stuffing his sack with silverware. They asked who he was; he responded "I'm a burglar." They said "Well, we're cops," at which point he offered to put everything back where he found it and leave; they didn't go along with that.

(TG, Albanian not translated by order of the Skinner) Bananardwm- fru xss gladz lassezj ser gkjnd: "Banana xor svenz wwsguigb... trmmmu banana sdlfn tgnkas sigsef dgkfjhak sdg banana skdgfjlskdf... sgksjt, lkgjdj skdgjei rbn. Dskgh sfij skdf slsiieerg er gdlr deekwkeril."

As KM tries to blue sticker TG, TG says, "This is also my last meeting before I move to Switzerland."

(JME) Move to commend TG for going to Switzerland and request he take that banana article with him.

Motion seconded, passes everybody-nobody especially TG-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}