\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 7, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jen Hawthorne, acting Skinner, presiding.

Minutes of the previous meeting were nonexistent.

Some sort of motion concerning the nonexistent minutes, which was washed out by the sounds of a lightning strike.

\goto{Committee Reports}

(JEH) Inventorycomm: there's one tomorrow, starting at 10 AM. Be here, all of you.

(JME) Jourcomm: Real Soon Now... but it might not be ready by R/O week.

(BPS) Sitcomm: for those of us who are old enough to remember the days when Hill Street Blues was real good, and then they simplified it because they got too many complaints from people who said they couldn't understand it- well, Max Headroom is going to get screwed over also. Producer Peter Wag said that the ABC series about a computer generated hero will be made "more accessible."

(JME) Moocomm: two movies opening today. Masters of the Universe, live action. I've seen the advertisements- it involves someone with a sword fighting someone with an energy blaster. There's also a new Care Bear movie and apparently they've decided to bring in some characters from Alice in Wonderland; the Care Bears have to rescue Wonderland from an evil witch. But they screwed up- they include the Jabberwock but they called him the Jabberwocky.

(SSDT) Followup- you forgot the other lead actor- Frank Langella is playing Skeletor.

(JEH) Moocomm: Robocop was shown as a sneak preview here, starring Buckaroo Bonzai- I mean, Peter Wellers. It's actually pretty good if you're expecting it to be bloody.

(JME) Moocomm: the new James Bond movie, The Living Daylights, is also out. I haven't seen it personally but Siskel and Ebert didn't like it. Bond was pretty good, but the female lead was hopeless.

(LK) Moocomm: Lost Boys, which is about vampires in California. It's really great- sleep all day, party all night, stay young forever and never die- it's great to be a vampire. Also out is Superman IV, which is pretty good. It's about as good as II, after the fiasco with III.

(JME) Sitcomm: the new STrek series, for which my expectations are getting lower and lower, will be airing on channel 5 this fall.

(BPS) Sitcomm: coming this season of Sledgehammer, they're going to film one of their shows in black and white and then computer colorize it.

(JME) Whooshcomm: low-tech meets high-tech- at Johnson Space  Center some workmen accidentally broke into a water main and flooded thousands of gallons into the computer center.

(JME) Globcomm: our navy is so high-tech that they don't believe in minesweepers.

(JME) Infocomm: anyone who is interested in testing a new Infocom game on Saturday the 22nd, please talk to me after the meeting. It's codenamed Beyond Zork- a text adventure with elements of fantasy.

\goto{Old Business}

(CH) I was at the Atlanta Fantasy Fair. On Sunday night, as I was going up to my room, who should get on the elevator with me but Chris and Janet Morris! (Adina) Connie kept on suggesting that we go over to their room with fire extinguishers, but I said it wasn't permanent enough.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: in NYC, cockroaches driven into a frenzy by the heatwave in Manhattan swarmed through a city bus at rush hour, forcing the driver to pull over and let disgusted passengers off.

(JME) Minicult: showing the dangers of reading children too many fairy tales, young Prince William of England, the eventual heir to the throne, was at a birthday party and- like many five year olds- was being rather obnoxious. He was sternly told to stop it and to clean up the mess. He turned around to whoever was taking care of things and said, "But when I'm king, I'm going to send my knights round and kill you."

(BPS) Minicult: there is a new Bloom County book. The Billy and the Boingers bootleg, with a 45 rpm record in it. Unfortunately, the record doesn't include "Let's run over Lionel Ritchie with a tank."

(JME) Minicult: while in his car at a drive-in teller's window  in Lancaster, Ohio, John J. Spires, a diabetic, found himself unable to speak or control his movements. When officials of the Fairfield Savings and Loan company told him to move, he didn't react, so they called the police. When the police arrived, they ordered him out of his car. When he didn't respond,they applied a "wrist drag" which is designed to cause pain and thus movement. When he failed to move, they dragged him out of the car through the window and handcuffed him, breaking his arm in the process. When they took him to the hospital, they discovered that he was suffering from insulin shock. Nevertheless, the two officers filed charges against him for criminal trespass and resisting arrest.

(CH) Minicult: they wondered why the penguins in the Birdworld Park in Barnum, England were swimming lower and lower in the water, and they were getting worried, so they took them to the vet, who x-rayed them and found more than four dollars worth of change in each penguin's belly. Penguins had been zipping around the pool, happily swallowing everything the visitors threw at them.

(BPS) Public alert- the new giant Star Trek novel, Strangler from the Sky, by Margaret Wonderbananas- God, is it horrible! Avoid like the plague. There's going to be a killer review in TZ.

(JME) Motion to forcefeed tribbles to Margaret Wonderbananas until she promises to never write again.

Motion seconded, passes anybody who counts-just Connie-lots of chickens +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1729 SST.

\vspace{18pt}

\centerline{Submitted (and you should be grateful for that)}
\centerline{Theodore Ts'o, Summer Onseck}

\end{document}