\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 20, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Susan Tucker, Skinner, presiding.

\goto{Committee Reports}

(JME) Jourcomm: write for TZ 39! Lots of books are up for review.

(DSK) LHE Report, month of February 1987: Assets- 2955.73, Income- 320.81, Expenses- 546.42, Equity- 2729.72, Loss- 225.61.

(JME) Bananacomm: Ken and I have a Bananacomm. (Ken produces a Banangaroo complete with Banjoey in its pouch. He proceeds to read the attached card.)

(JME) Albanian Motion on the Dole Banana Company!

Seconded but fails by Skinnerial "No, not yet!"

(KM) Erroneouscomm: I made a mistake; I talked with Aaron Agison when he called- the Aaron of "Shut up, Aaron!" He's doing a show for Boston Cable called "Fantasy Life" and he wants us to do something on it.

(SSDT) I told him we'd have to see it first before we'd use it.

(JME) Meyercomm: According to NESFA, next year's Boskone will have a limited attendance of 2500 people. No one under 18 will be allowed to attend the con if unaccompanied by an adult unless they were a gopher or something like that at previous Boskones. They won't be listing in the prozines, just the semiprozines, and they are sending publicity out to select groups of people only.

(KM) ROSFAP: we got a very nice fanzine from the Cornell University Student Association; we also got a donation of a whole bunch of Dr. Who fanzines which I'll be processing RSN.

(JME) Readercomm: Readercon is looking for people to help out at the con.

(BPS) Hagacomm: Sue Hagadorne called- she's moving on Sunday the 29th and needs help.

(SSDT) Panthercomm: there are two more keyholder phantoms in addition to Justina- Phil Nesser and Ted T'so. We also have a keyholder aspirant named Laurie.

(SSDT) Picniccomm: the picnic is going to be on May 2.

(DSK) STrekcomm: Nimoy's lecture was and was pretty good. Lisa Kroh invited him up to the library but he didn't come. Rumor has it he left the auditorium and sprinted for his car.

(Adina walks in at this point and exclaims over the Bananimal.)

(KM) Move to note that Adina recognized that we have a Bananimal.

Motion fails by "Shut up, Ken!"

(BPS) Mortcomm: Richard Levinson passed away last week. He wrote a lot of good teleplays including Columbo.

\goto{Old Business}

(JME) Since Connie isn't here, I'd like to add a Hirsch Motion to the OBA, saying that the MITSFS should abide by a monetary policy of free coinage of silver.

Motion seconded, fails by Skinnerial "What monetary policy?"

OBA: um without weird economics, us, uv, ur.

\goto{New Business}

(AA) Minicult: spring is here! I saw a Hari Krishna downtown.

(JME) Minicult: there's a Massachusetts program for welfare recipients called ET (for Employment Training). Ted Kennedy has introduced a proposal in Congress for a national program to be called JEDI, for Jobs for Employable Dependent Individuals.

(JME) Three of the ten candidates for mayor of East St. Louis, Illinois this year are convicted felons: one for forgery, one for extortion, and one convicted for trying to murder the forger.

(JD) Minicult: the glob reported that the people in Hinkley, Ohio are holding a festival because they've spotted the first buzzards of the year.

(JME) Minicult: a US district court ordered two transcendental meditation groups to pay a former member 135 grand because they tried to convince him he could fly.

(JME) Minicult: the city council of Washington DC has passed a law preventing individuals without a license from practicing interior design.

(BPS) Minicult: Jim Bakker, a TV evangelist, resigned as head honcho of The PTL Club in favor of Jerry Falwell because it has come out that he had sex with a woman other than his wife in 1980 and since then paid somebody about 25,000 in blackmail money to keep this quiet.

(JME) Minicult: from the Glob- there's a new, very effective drug available for treating obsessive compulsive disorders. The only problem is that a very small proportion of people taking it have side effects of uncontrollable yawning and uncontrollable orgasms. Of the four people from the large trial sample who had these side effects, three asked to be taken off the drug and one asked for an extended course of treatment.

(BPS) Minicult: there's an obnoxious series of ads on TV that claims that the Nynex Yellow Pages are the only real yellow pages. One of these ads features a family sitting around a fire, and the kids are asking the father questions which he answers until one of them asks why anybody would want another Yellow Pages. From Cliff Garbaden's "Hot Dots" column: "And now, a heartfelt parent-to-parent note to that TV-ad dad who doesn't know why anyone would want anything but a Nynex Yellow Pages. I mean, honestly, who COULD know? This guy knows why grass is green: "chlorophyll," he answers patiently. "Dad," pipes up his young son, "is the moon really made of green cheese?" Twitters of condescending amusement run through the family. Patiently, Dad steps in. "Oh, no, son, the moon is made of molecules." Molecules. Right, fool. Molecules. Green fucking cheese is made of molecules too, you sanctimonious twit! No matter what kind of yellow pages you keep in your house, your son's gonna grow up and murder you in your bed. Molecules, indeed! Real scientific answer, Dad! Drop dead, okay?!"

A collaborative effort is made, producing a motion to commend the Nynex Yellow Pages for being made of banana-colored molecules.

Motion seconded, passes 2+ delays and a bananimal-less or more-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1737 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Jennifer Hawthorne, Onseck}

\end{document}