\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 15, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting were read and corrected.

(J?D) Move to approve the minutes as being 2 minutes and 23 seconds of laughter and crying.

(KM) Friendly amendment: ...and rolling on the floor.

Motion seconded, passes 20-much less than 20-5 and a couple of oinks +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: write for TZ... PLEASE? We got another fanzine with a review of TZ in it. It was a positive review, but the notable thing about the review was that it referred to our very funny parody of club minutes.

This brings forth peals of laughter, and many imitations of Tweety Bird saying "Dey don't know us vewy weww, do dey?"

(JME) Jourcomm (continued): please write. If you're looking for inspirations, we have art that you could write around.

(KM) Jourcomm: write for TZ or I'll break your face.

(DSK) Skinner Report: I'm going home on Sunday for the summer. There will be a Star Chamber meeting after this meeting to appoint a summer-type-Skinner.

(SSDT) Pseudo-Willcomm: I have a list of things for you that have to get done.

(JME) Pseudo-Willcomm II: Me too.

(JME) Whooshcomm: The US is considering a manned moon base to assert its leadership in space. The moon base is gaining support as an option that would be quicker to achieve than a major exploration of Mars and would help prove the technology to make such a mission possible. NASA administrator James Fletcher is quoted as saying "I think the right way to go to Mars is by way of the moon."

(BPS) Whooshcomm II: Right next to that article in the Glob was one giving the blame to the Air Force for the satellite launch that got struck by lightning a couple of months ago. Apparently it was Air Force meteorology that gave bad information.

(SSDT) Whooshboomcomm: The star chart fell down and took some damage in the process.

(Malcolm) Move to commend God for joining the Air Force.

Motion fades into the sunset.

(SSDT) Whooshboomcomm II: A person from ComElectric had a bad day in the field. At about 10:50 last night he was trying to do some work that would complete the recovery from a power outage earlier this week and connected two phases of a three phase line 180 degrees out of phase. The resulting explosion caused a breaker switch made out of lots of pieces of 1/4 inch plate metal to partially vaporize, partially turn to ash, and the rest melt. At the magnet lab. In addition, the feedback blew manhole covers ten feet into the air and blew a main transformer in Central Square. The power was out at the reactor for over eight hours, which is something of a record.

(KM) ROSFAP: we have yet more fanzines.

(LAK) When Ken goes away, Rob and I are trying to convince Phil to be the new ROSFAP, so we'll probably have a replacement for Ken.

Discussion of Phil's masochistic tendencies ensue.

(CH) Publichappeningcomm: On Saturday June 6th, The Duck's Breath Mystery Theatre will be playing at the Somerville Theater. They're best known for their spots on NPR's "All Things Considered" as Ian Scholes and "Ask Dr. Science." They offer an extremely polished and very mixed blend of satirical comedy and comic silliness, from transvestite farmers to ????? zombies to nuns to glee club directors to "Zarda, Cow from Hell." Flyer posted.

Random discussion of Boskones to come.

(DSK) Sitcomm: last showing of Hill Street Blues was Tuesday night. End of a TV era.

(LAK) Moocomm: LSC can be half decent sometimes...

A calendar of summer movies with a naked man (or at least almost naked...) on it is passed around.

(KM) Pseudo-Huntcomm: The Lithuanian Conspiracy is asking/demanding that they be allowed to run next year's Scavenger Hunt.

(JME) Sitcomm II: some rather oddly phrased support for Max Headroom from TV Guide this week. They basically said it's great ABC put this on, and we hope they pick it up. It's the best dumb fun we've had in years.

(JD) Motion to commend/censure TV Guide for being dumb viewers.

Motion dies because it's too obvious anyway.

(BPS) Sitcomm III: Dead but still moving, Twilight Zone returns again.

(JME) Sitcomm IV: Steven Spielberg's Amazingly Bad Stories is not on the fall schedule... thank God.

(SSDT) Acquisitions Engineering: It is now possible to use the copier without unplugging the typewriter, the microfiche without unplugging the copier, etc.

(Malcolm) Acquisitions Engineering: you can open one out of three safes immediately, because one out of three safe owners do not change the combination that is put in in the factory. Which is either 25-0-25 or 50-25-50.

(BPS) Mobcomm: bought myself a PC/AC clone from Zenith. Got a good deal on it. Deal was really good, because they didn't know they were giving me the 40 meg hard drive that was in it. Unfortunately, I have to give it back.

(SSDT) Moocomm II: I believe LSC is showing Body Talk tonight. The alternative programming group (CCC, et al) is showing Star Trek III at 8:30 in 26-100.

\goto{Old Business}

(JME) The election meeting sign is still on the door. And the keyholder schedule sheet still shows Sunday as being taken up by the picnic.

(LAK) Leafing through the SCA directory for the local area, I found that Guy Consolmagno is a member of the SCA.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: Gallup polls asked Americans whether they believed in extraterrestrials. 57 percent of the college educated Americans said they did, and 46 percent of the Americans who didn't attend college said they did. You tell me what that means... In another poll, 8 percent of American children between the ages of 8 and 17 say they have 5 or more living grandparents.

(BPS) Minicult: from the Glob, an article about the making of a Miller Lite commercial with Tip O'Neil. It mentions that O'Neil observed that he has already done magazine ads for American Express and Hush Puppies. Many companies have called him and asked him for endorsements, but he's passed on most. One was an insurance company for senior citizens; instead of endorsing it, he had a congressional committee look into it.

(JD) Minicult: last night on 20/20, they talked with C. Everett Coop, who told the interviewer that one group had published a pamphlet in which they said that C. Everett Coop was not only in favor of, but was practicing handing out condoms to eight-year-olds. Coop then proceeded to make comments on their intelligence based on the size of an eight-year-old's penis.

This brings forth comments on what eight-year-olds do with condoms, including LAK's mentioning of putting bananas in them.

(KM) Move to commend the people in Pennsylvania for putting bananas in condoms.

Motion fails to a chorus of Go Away Ken.

(JME) Minicult: the Glob today concluded a report on Robert Mcfarland's last day of testimony in the Iran-Contra hearings. At one point he expressed regret that as National Security Advisor, he had not expressed to President Reagan his opposition to the Nicaragua policy being proposed. He explained this by saying that he feared that people like Jean Kirkpatrick and Caspar Weinburger would "say I was some kind of commie."

(RvdH) Minicult: One of the eight wives of a Mormon fundamentalist in the backwoods of Utah, where they still sometimes practice polygamy, said that it's a very feminist lifestyle: "I can go off 400 miles to law school, and there's still someone there to take care of my kids."

(BPS) Minicult/Timewarp to Cornelia Otis: Only Ollie North, an American Hero, could transpose two digits and put 10 million dollars in the wrong Swiss bank account without noticing. And only in Switzerland, I suspect, could a businessman find ten million dollars in his account and think he could get away with withdrawing it and keeping it.

(JME) Minicult: your tax dollars at work funding our elected officials. On Wednesday evening, the Massachusetts House Ways and Means Committee held a major hearing on welfare benefits. Lots of people testified, live TV coverage. The chairman of the committee was not present; he was in his office watching the Celtics.

(CH) Minicult: Chernobyl chicken is 6 feet tall!

Connie is stopped before she can go further with that one.

(CH) Minicult: Farmer Claims Cows Are UFO Aliens! A spaceship beamed the herd down, he says. The herd appeared and no one can explain where they came from. "They look and act differently from my cows; they look dazed and confused. They stay away from the other cows and stay together. Every time I look in their eyes, I can tell they're thinking things ordinary cows aren't thinking."

(JME) Motion to send the strange and confused cows several ripe bananas.

Fails by "not yet."

(DSK) Minicult: rumor has it that Pat Boone will be taking over Jim Bakker's daily show on the PTL Club.

(JME) Minicult: in addition, Jerry Falwell, who is now running the PTL Club, has said that if they don't raise 7 million dollars within some short amount of time, the PTL Club will be disbanded. He did not credit God with this threat...

(BPS) Minicult: correction to Scott's report- Pat Boone was the leading vote getter in a poll of PTL members on who should do the show.

(SSDT) Minicult: according to WEEI, we're being invaded by friendly flying cockroaches from Florida. They like people and bright lights and will fly in your face and crawl up your legs.

(AA) Also, the 17 year cicadas are due out again, but they're harmless. They just make lots of noise.

(JD) Minicult: on June 13, there will be a first for fandom and for the gay rights movement. The Galaxians, the local gay fandom organization, will participate in a gay pride march. It will be the first time a fannish organization has participated in a gay pride march.

(BPS) Minicult: marginally related, I found a source for "Dump Reagan" bumper stickers.

(JD) Minicult: again marginally related, July Analog reviewed two collections of gay and lesbian science fiction. The review was bad and heterosexist.

Ken was beamed up to the spaceship to replace the cows.

(Malcolm) Move to commend Ken for going poof.

Motion seconded.

(JD) Friendly amendment... with a banana.

Amendment fails to "Naaaahhhhh."

"Rabbits Have No Tails at All" for one round...

(JME) We have a book called "How to Fold A Banana and 146 other things to do when you're bored."

(JME) Move to fold a banana and send it to the confused cows in Scotland.

Motion seconded, passes almost everyone-maybe 5-definitely not enough +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Confusedly submitted, how'd I get into this mess...}
\centerline{Rob Gates, Sorta, Kinda, Almost, Just This Once, Pseudo-Onseck}

\end{document}