\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 11, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of previous meeting are still somewhere on tape.

(TG) Motion to approve the minutes as seconded.

Motion thirded, passes 20-1-10 +Spehn.

\goto{Committee Reports}

(BPS) Mortcomm: TV producer Quinn Martin who did the Invaders. Also Lorne Greene, aka Commander Adama.

(TG) Pseudo-Moocomm: Some channel is showing pilot episodes of bad SF series this Sunday, including Land of the Giants, Time Tunnel, and Lost in Space.

(DSK) Moocomm: Platoon tonight, STrek IV tomorrow night.

(CH) Sitcomm: Channel 38 at 8:30 and 9 AM is showing The Addams Family and The Munsters.

(TG) Bookcomm: Cvltvre Made Stvpid is out. The back cover announces, "Winner of the 1986 Hugo- you know, one of those European cars."

(BPS) There was an unfortunately live band at the Activities Midway. They were very loud but no one pulled the plug.

(DSK) Skinner Report: I got Cat Daley's old job at the Plasma Fusion Center.

\goto{Old Business}

(BPS) US470 in Virginia opens 52 years after construction began.

(DSK) Time warp from NB- Star Trek starts in 3 weeks. Copies of the Writer's Guide are available for anyone who wants to look at them.

(HAM) Aloha Lenscomm: Only 26 pictures left on this roll.

(TG) Rencomm: Renaissance Fair opens this weekend. (End time warp.)

OBA: um, us, uv, ur.

\goto{New Business}

(JH) Minicult: a new piece of MIT ugly art appeared on the 3rd floor of building 66. Next to the card explaining the title, someone had pasted one reading "You have got to be kidding."

(TG) Minicult: they finally have shelves for the "C" books at Wordsworths in the SF section.

(BPS) Minicult: have a bomb. (Deposits on gavel block.) (DSK) If this explodes on me you're dead. (BPS) Very likely. (After a few threatening motions with the gavel, the bomb is removed.)

(BPS) Minicult: a convicted loan shark was back in federal prison because he ate a poppy bagel. Article attached.

(BPS) Minicult: Tilted Arc is being removed from a Manhattan plaza after 4500 complaints. Article attached.

(TG) Motion to donate it to the contras. Motion seconded, passes by acclaim.

Random: why the banana fixation? En masse: Finger motion.

(CH) Minicult: "UFO Aliens Helped Congress Write the Constitution."

(BPS) Minicult: "Few Aliens with Guns Have Hunting Permits" -Glob.

(CH) Globcomm: Headline in the glob: "Bush Tied to Contra Pipeline."

Random: why do they call them UFOs anyway? If- En masse: Finger motion.

(TG) Motion to commend the earthquake in the can for choosing a tasteful banana colored stripe.

Motion seconded, passes 15-negative 15-not more than 15 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}