\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 14, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Hawthorne, Pseudo-Skinner, presiding.

Minutes of the previous meeting were read and corrected.

(BPS) Move to approve the minutes as strangled and spelled Skeletor.

Motion passes many-the usual opposition-a couple of chickens +Spehn.

\goto{Committee Reports}

(JME) Jourcomm: TZ Real Soon Now.

(JAH) Inventorycomm: Was. Thank you thank you thank you to everyone who showed up. It went  pretty smoothly except that Ken Johnson got kidnapped by the Martians during the lunch breaks. We're still waiting for the ransom note.

(LK) Moocomm: Masters of the Universe isn't all that bad. There aren't that many scenes of him using a sword to fight someone with a blaster. (JME) On a related note, one of those crazy fundamentalists said that Masters of the Universe is obviously satanic since there's only one real Master of the Universe and you better not forget it.

(JME) Moocomm: two movies opening today. One called I Was A Teenage Zombie and one called Monster Squad. Both of them, the Glob reviewer said, were disgustingly horrible- not even bad enough to be funny.

(LK) Moocomm: while I was seeing Masters of the Universe, we saw an ad for "Garbage Pail Kids: The Movie."

(JAH) Pseudo-Moocomm: somebody had hacked one of the "This property protected by Robocop" posters by cutting out the face and sticking a new one in, and changing Robocop to "RoboNorth."

(KM) RosFap: we have a bunch of new fanzines. TZ got mentioned in NASFA Shuttle: "TZ was a hell of a lot more interesting than NESFA's zine."

(KM) Pseudo-Libcomm: the Bane Fantasy logo, which is a dragon perched on top of a shield, looks a lot like Snoopy doing his vulture act.

(JME) Infocomm: Infocom and Avon Books are going to release a series of "Infocom books," set in the universe of the Infocom games. The first projects will be Planetfall and Wishbringer.

(CH) Pseudo-Famecomm: Xappa, which is a fanzine dedicated to comic books, has its fiftieth anniversary next issue, and in New Mutants one of the characters is wearing a Xappa 50 t-shirt; considering that there's only 25 of us, the artist was nice enough to put us in.

(JME) The-Onseck-can-make-up-a-commcomm: the latest issue of Technology Review has a big article on Soviet science fiction. It's written by a Soviet expert, not an SF expert, which is evident throughout the article; she refers to the material as Sci Fi.

(BPS) Whooshcomm: This week's Newsweek has a blistering condemnation of NASA, the US space program, and those who run it. I'd say it's almost required reading. It's almost enought to make you emigrate to the Soviet Union.

(CH) End-of-the-worldcomm: on Sunday the 16th, lots of people are going to get together and hum a lot so the world doesn't end by 2012. If they succeed, we will enter into a period of "world enlightenment."

(JME) Strekcomm: it looks like the Strek series is in trouble. There's the upcoming director's strike. Also, no one is getting along, and Gene Roddenberry is totally incompetent at running the set and keeping everyone together. If this keeps up they may just release the pilot and be done with it.

Phonecomm: BUZZ.

(JME) The-Onseck-can-make-up-a-commcomm II: a publisher is planning to release a controversial biography called L. Ron Hubbard: Messiah or Madman. (Is that an exclusive-or?) It hasn't been released whether they will pronounce him a madman or messiah.

(BPS) Sitcomm: from the Glob- Max Headroom's stutter may be bad for children, says a speech therapist.

(BPS) Sitcomm II: I finished Dirk Gently's Holistic Detective Agency. Several plot concepts, and one particular plot device, were lifted from Doctor Who episodes from the 1.5 years when Douglas Adams was a story editor for Doctor Who.

(JME) Sitcomm III: There's an article in TV Guide by Isaac Asimov about the TV series Alf. It's mainly a sarcastic article but I'm not sure most of the readers will realize that it's supposed to be sarcastic.

(JME) Meyercomm: while they haven't released any details yet, the latest issue of the Mad 3 Party sounds like they have reached an agreement with the Sheraton.

\goto{Old Business}

(BPS) It's been ten years since Elvis Presley died, and I still don't care.

OBA: um, us, uv, ur.

\goto{New Business}

(CH) Minicult: "Two week vacations of Mars: see the breathtaking canals, glaciers, etc. Trips to the moon also available." More than 6000 tourists paid 10 grand each for one of the most incredible hoaxes of the century. An Italian travel agency actually got away with this.

(JME) Minicult: Inmate uses margarine to escape from cell. A thin inmate covered himself with margarine and squeezed himself out of a 13" by 6" window. He was 6 feet tall and 135 pounds. Not only did the margarine allow him to escape, but it meant the police dogs couldn't track him.

(JME) Minicult: there were some people in New York who didn't like the music the radio stations were playing, so they got out in a boat, sailed into international waters, and began broadcasting as Radio NewYork International.

(JME) Minicult: in one of the strips in the new Bloom County book, Binkley is wearing a shirt which says Calvin and Hobbes rule.

(BPS) Almostseriousbusinesscomm: Spike McPhee would like it to be known that the 15 percent MITSFS discount applies only to new paperbacks.

(HAM in absentia) Minicult: a carpet salesman expressed indignation that during the Iran-Contra hearing a reference was made to "making policy decisions with rug merchants." He said it was an insult to rug merchants everywhere.

(BPS) Goodcomebacklinecomm: according to George Will, when congressman Pat Schroder was asked why she was running for president as a woman, she replied, "Did I have a choice?"

(CH) Minicult: a woman in Toronto is divorcing her husband because he thinks he is Batman. The final straw came when he started redecorating the basement to look like the Batcave and cut a hole in the floor so he could slide down into the Batcave.

(TG) There's a new book from Octavia Press called Superman at 50: The Persistence of a Legend. They're going to be donating 1 percent of the gross to Neverending Battle, a nonprofit organization who has commissioned an international artist to create a Superman sculpture in downtown Cleveland, the home of the creators of Superman.

(JAH) Motion to condemn the Stockholm inmate for not smearing himself with bananas to escape from his cell.

Motion seconded, passes lots and lots-the loyal opposition-several chickens +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Submitted in a hurry,}
\centerline{Theodore Ts'o, Almost Ex-Summer-Onseck}

\end{document}