\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 4, 1987

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jennifer Hawthorne, Vice and Pseudo-Skinner, presiding.

Minutes of the previous meeting read and corrected.

(BPS) Motion to approve the minutes as better than they were a few minutes ago.

Motion seconded, passes 12 or so plus behind you, too, Jen-all of RJG's various limbs plus two or three extras-many chickens and Seth's favorite sheep +Spehn.

\goto{Committee Reports}

Phonecomm: (Timewarp from reading minutes) Ring. It's DSK with a STrekcomm. They're showing movies one, three, and four and lots of the TV episodes in E51-329.

(JAH) STrekcomm: I was going to give a STrekcomm about the marathon but Scott beat me to it.

(HAM) Sitcomm fairly early: Lionhart has released Time and the Rani which is the first episode with the new Dr. Who in Britain in the US. It will be shown Jan 1 on WHYY in Philadelphia and Jan 15 on WNJN in New Jersey.

(RJG) Jourcomm: write for TZ and if you're going to Boskone speak to the Jourcomm real soon about taking some TZs with you.

(S??) Cornelia Otis: the elections in Haiti.

Phonecomm: ring! It's JME calling from Schenectady. She and Ken made it to Schenectady okay but when they arrived they found out the water heater was busted. They miss everyone; they're at home now with a fire going and it's cozy.

(BPS) Cornelia Otis/Sitcomm: last Monday night NBC ran a first ever of its kind interview- Tom Brokaw interviewing Mikhail Gorbachev. It came in a distant third in the Nielsens and people were calling in complaining because NBC preempted Alf.

(SSDT) Followup- Gorbachev's rating did beat that of the presidential candidate debates the next day.

(BPS) Sitcomm: CBS is running their string of Twilight Zone episodes in reruns Saturdays at 9 PM.

(JAH) Mootooncomm: animation festival tonight. Also STrek 2 Sunday.

(JAH) Sitcomm: Next STrek enters reruns after this show.

(BPS) Klutzcomm: make sure the cap is on a pen before putting it in your shirt pocket or you'll ruin a perfectly good shirt.

(Malcolm Y) Concomm: Boskone preregistration deadline is next week.

(BPS) Mobcomm: I've picked up a couple of NY Times bestsellers; the good, the bad, and the ugly, so to speak. (Holds aloft The Tommyknockers by Stephen King and The Doomed Planet, L. Ron number 10.)

\goto{Old Business}

(SSDT) The committee on discipline knocked down MIT's porn policy.

(SSDT) Remember the Peachtree reactor that got shut down because the operators were asleep at the switch? They're in trouble again; half a dozen of the operators were busted for being on speed. At least they had the right idea.

(BPS) Going into the blue folder of interesting things is an old TV Guide article about Kirstie Allie, the REAL Lieutenant Saavik.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: from the Nov 7 Newspeak- Fawn Hall has been awarded a gold banana from the International Banana Association after being ticketed for eating a banana in a Washington subway. Article attached.

(KJ) (Timewarp from adjournment) We have someone coming next Mon-Wed and Sat-Thurs to do research. Please try to keep your hours, especially evening and weekend hours.

(JAH) Move to censor the skinner for being bananas.

Motion seconded after SSDT determines it will work even with the Inverse Skinner Rule, and passes many, many, many-nobody who matter and a sensitive Connie-a couple of limbs and Rob's favorite mare +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}