\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 27, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JM, Pseudo-President and Skinner, presiding; JFC, Pseudo-Onseck, recording.

M: reading of minutes deferred. Lots-0-0 +Spehn.

M: approve minutes deferred. 4-4-0 +Spehn.

M: banana motion for chickens. 4-3-4 +Spehn.

\goto{Committee Reports}

Mobcomm: books.

Panthercomm: processed.

M: condemn mobcomm for not getting good books.

Pseudo-mobcomm: more Weber at Baen website.

Pseudo-pianocomm: prentices doing work (or one is?).

\goto{Old Business}

"3rd space sucks." (WDS)

"It's been a long time since I ran a meeting." (JM)

"Reading Jordan backwards helps." (jhawk)

Phonecomm: ring!

Jenwa is in Davis Space.

M: never have Thanksgiving again! 5-4-0 +Spehn.

JH made a bad pun.

\goto{New Business}

"Something wicked this way comes." (JH)

Theresa walks in.

No libcomm yet. JH will donate a subscription to the NY review of SF.

\goto{Future Business}

M: approve JFC's quest for a clean banana chew toy. 12-3-7 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1712 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
