\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 11, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: minutes are lossly compressed and have gaping holes. 12-8-2 +Spehn.

M: commend skinner for remembering number from votes. 14-3-9 +Spehn. (Applause)

\goto{Committee Reports}

Key fines all around. Hahahahahaha?

M: commend whatever he is fining himself for. Some-some-10 +Spehn.

Pseudo-mobcomm: should have hardcover run soon.

M: commend skinner for living underneath her rock. But she has a Telzey! But her Telzey is just as hosed.

M: give skinner a rock big enough for two. 22-4-1 +Spehn.

\goto{Old Business}

3rd space still sucks. Star Trek still sucks... in a new and improved way.

Skinner: aren't you still sick? But she just turned in some project thing at 4 PM and she feels good. "So when do the drugs run out?"

M: commend wealthy alums and give us happy couches. 11-2-6 +Spehn.

M: commend lawyers for being more powerful than duct tape. 18-6-6 +Spehn. Fails because skinner said so.

Still doing alum mailing in February?

M: commend someone/something for having a sex life with a bicycle. Onseck gets tired and confused.

\goto{New Business}

Discussion of bookends. "Wild stampeding bookends!"

M: "We got mail from Stonybrook SFS and mocked them for being young (30th anniversary)." 17-0-1 +Spehn.

M: get other and therefore lesser SFS to pay us a tithe of 10 percent of their income. 40-0-0 +Spehn.

Discussion of xmas meeting. Singing xmas carols. (Justin)

A person walked in. "It's jhawk." "That's not a person."

"I found a webpage with over 11000 haikus on Spam." (JPW)

Lots of xmas cards about Spam.

jhawk holds up and asks: is that James?

J: "No, not even vaguely."

M: commend for not looking like James. 8-1-14 +Spehn.

\goto{Future Business}

Singing about spam forces adjournment.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
