\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 6, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

These minutes were written with a Microsoft pen.

Minutes read.

M: approve minutes as read correctly no matter how it was written. 11-1-7 +Spehn.

\goto{Committee Reports}

We have "Dragon" (Steven Brust's book).

Pseudo-hasslecomm: most hassles have been commed.

Sitcomm: 7 Days starting to suck. 7 Days in the past: time travel discussion. They used to be good but now it sucks seems to be the consensus.

M: have them go back in time and redo. 12-0-4 +Spehn.

M: to count abstentions. Fails by skinnerial decree.

Discussion of using gavel to whack Jay. Gavel is indestructible. But is J? His soul is in the gavel because all skinner's souls are in the gavel. This is a surprise to Jen.

M: move to approve money. Many-0-1-2 +Spehn.

Discussion of Assassin's stuff.

Finished reshelving. Ex-LHE did the books! Yay!

Skinner bows. Skinner curtsies.

M: bow and curtsy at the same time. 11-0-5 +Spehn.

\goto{Old Business}

\goto{New Business}

Weekly week! Snakes are not everywhere!

Sunday: either X-Files premiere or B5 movie.

M: commend B5 for making us an offer we can't understand.

New rites for prentices out. We only have 2 prentices: one dormant and one...? Skinner has already given herself a papercut on them.

M: commend skinner's blood for making us strong. 20-0-0 +Spehn.

M: pass around skinner's blood to strengthen us. 11-0-9 +Spehn.

M: orange-sticker the blood of skinner so it "doesn't circulate." 4-13-0 +Spehn.

M: blue-sticker that joke! 14-0-3 +Spehn.

Weekly week snakes story is really good.

M: commend St. Patrick for driving snakes out of Ireland.

"Path of Daggers" here. About as good as you'd expect.

Discussion about length of story.

Thud-comm: NRA went thud.

\goto{Future Business}

M: as it I to shape if banana.

M: have fond memories of Lovecraft's Mountains of Misfits.

M: move to pretend there was a banana in the previous motion. 11-0-9 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
