\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 27, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: regard as epic and sweeping. 9-4-0 +Spehn.

M: make this week's even more so. Buttload-2-0 +Spehn.

M: Jay to give keys to LHE- amendment "loan", passes by decree of skinner.

\goto{Committee Reports}

Jourcomm: laying out Zine this weekend. Photocopy next weekend, so submit stuff on Friday...

Pseudo-mobcomm: "Unidentified Flying Oddball" plus 55 real books. Yay.

Picniccomm: if people submit reviews to Zine, Picniccomm rites will be written.

\goto{Old Business}

No old business by skinnerial decree.

\goto{New Business}

M: why no old business? 13-0-0 +Spehn.

M: force skinner to answer. 13-0-0 +Spehn.

Inverse skinner rule.

M: skinner to act out answer. 14-0-0 +Spehn.

Inverse skinner rule.

Little song about skinner's tail... don't ask.

\goto{Future Business}

Miller motion fails.

2nd Miller motion. 7-0-6 +Spehn.

Darn, close call...

3rd Miller motion. 13-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, at an undefined time...

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
