\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 5, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Skinner-Regent, presiding; JFC, Pseudo-Onseck, recording.

Minutes read.

M: give JWH a list, to not be listless. Pass with loud \bing 5-1-1 +Spehn.

M: approve minutes as unusually detailed. Fails, no second.

M: disapprove minutes as unusually detailed. 7-1-2 +Spehn.

\goto{Committee Reports}

Panthercomm: most new books processed. "Buttload" of new books on shelves.

Pseudo-bluebellcomm: most new HC covered.

Mobcomm: real new books soon.

M: compliment Toby on something. Nothing 4-4-3 +Spehn.

Dexmistress: inventory this summer. Say when you can come.

\goto{Old Business}

VGG and JFC are here.

M: commend JWH and Jill for being young. Passes 9-6-0 +Spehn. \bing (Toby: "Lame bing.")

Incoming magazine donations possible.

Usual stuff.

"I don't want to bing." (JWH)

\goto{New Business}

Clinton spoke to grads, said stupid things about internet and technology.

M: send Clinton a large banana studded with vacuum tubes. Fails, no second.

Pseudo-moocomm: "Truman" opens tonight.

\goto{Future Business}

Miller Motion. Fails.

Second Miller Motion. Passes several-none-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1700 SST (by skinnerial decree).

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
