\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 6, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: condemn minutes for mentioning Jen's fillings. 5-5-4 +Spehn. (Thanks to Justin's counting.)

\goto{Committee Reports}

Pseudo-picniccomm: talked to AMU. Rites done soon.

Jourcomm: there are lots of things going on in my life right now.

\goto{Old Business}

"We got mail about 'breast cancer and you.'" (JM, looking through mail)

M: Justin's motion. ("To Jamie and due, unspecified.") 4-5-7 +Spehn.

People discuss being old again. (J notes that there really should be, as Ellen is here.)

\goto{New Business}

M: to commend the VGG for enthusiasm. 2-0-1 +Spehn.

Discussion of alumni mailing.

Bronwen arrives.

M: to have Bronwen donate 1 dollar in will to the MITSFS. Unanimous, passes save for Spehn.

"Fine. I'm embezzling the 4 cents." (Jen)

M: commend LHE for embezzling. 5-2-4 +Spehn.

\goto{Future Business}

Sitcomm: watch Xena this weekend. All musical this week.

M: commend Toby for being in touch with 12-year-old boys. 7-4-2 +Spehn.

M: condemn ACC for being in touch with 12-year-old boys. 5-5-3 +Spehn.

M: produce Zardoz Troopers. 4-10-0 +Spehn.

M: begin preparing now for banana shortage. Fails.

Miller motion fails.

2nd Miller motion fails with some vote.

3rd Miller motion passes with some vote.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
