\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 31, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Miller Motion. Fails, no second.

M: something about motions from 2 meetings also failing. 9-2-5 +Spehn.

\goto{Committee Reports}

Panthercomm: inventory happened.

Debate about whether or not JM is Panthercomm.

Sitcomm: "Thirdspace sucked to this very moment."

Pianocomm: new keyholder over there.

M: everyone say hi to Jake. 7-7-2 +Spehn

"Bing." "Ow." "Motion binged."

M: commend motion for getting a bing. 14-1-0 +Spehn.

M: commend that motion for getting a bing.

M: shut up. 11-12-0 +Spehn.

M: condemn that motion for getting a bing.

\goto{Old Business, no bing}

Bill's still old (40).

"That's one year for every finger and toe." (JM)

Plea for end to old business.

People fail their math rolls en masse.

M: commend Bill for being 4000 years old. 11-3-0 +Spehn.

ALGOL mangled.

"What about the usual bing?"

\goto{New Business}

Miller Motion. Seconded. Ignored.

Floorcomm: we need to move everything off of the floor.

TZ: hilarious laughter.

M: condemn Justin unilaterally. 16-0-1 +Spehn.

M: shut up, you banana. 12-15-3 +Spehn.

Skinner starts asking people for their fucking member.

M: end the meeting. Ignored.

M: commend skinner for providing banana flavored cookies. 7-0-shit +Spehn.

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
