\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 30, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, Pseudo-Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: commend JFM's fillings for interacting with gavel. 0-1-1 +Spehn.

M: commend Jen for ruling meeting with iron fists/fillings. 10-0-4 +Spehn.

\goto{Committee Reports}

Pseudo-moocomm: "You've read the movies, now read the book." Zardoz based on screenplay by John Boreman.

Omri: "May I recommend the Gor series for the next SF marathon."

JM: "They played ST5 which was much, much better than Zardoz."

WDS: "ST5 was better because it was shallower."

Jourcomm: once the product ships at work, TZ will happen. Feb 30th.

Calendar reform schedule discussion.

Mobcomm: new books. Bunch of ST, TSR. Pay me!

Panthercomm: bleh.

Onseck comments that the pseudo-skinner is being nice to her and considerate.

\goto{Old Business}

Tim Huckelbery here last week.

WDS finds LS coffee mug.

"Usual motion." "Flibble x3."

\goto{New Business}

Kinar-Bujold-May.

Heinlein in a [illegible] movie? "15 years now."

Professor X origin drawn for Yul Brynner.

M: *snore* (WDS). 7-0-4 +Spehn.

\goto{Future Business}

WDS: "There was no banana in that, none whatsoever." "Passes" 5-0-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
