\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 10, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: to pronounce the minutes unpronounceable. 7-1-5 +Spehn.

\goto{Committee Reports}

Silly Tech green-light column.

Panthercomm: recently purchased books have been processed.

Moocomm: haven't seen Lost in Space. Discussion of Lost in Space. "That explains why I get warm fuzzy feelings when I think about baseball."

LHE: bank deposit next week.

"X-rays of Jen's foot show nothing."

M: to condemn Jen for having painkillers and not bringing enough to share with everybody. Nearly unanimous-0-0 +Spehn.

\goto{Old Business}

M: *groan* I'm old. 3-4-8 +Spehn.

Usual...

\goto{New Business}

"We're not getting any space. Waaah!"

Prentice-project: cleaning the library.

\goto{Future Business}

Writers coming: Nancy Kress and somebody else.

Pandemonium is now selling Spammers- college internet card game.

Principia Discordia as reference for Illuminati? N-no...

Theoretically we'll get alum money... once Ed does the mailing.

M: to commend Jen for caning people. Passes by skinnerial decree.

M: to replace Jen's cane with a banana. 14-0-8 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
