\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 19, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Skinner-Regent, presiding; [Unknown], Onseck, recording.

Minutes read.

M: make following corrections: toy + spanner = 4.5 pounds, insert gavel behind vice gavel block. 6-9-3 +Spehn. Passes, doesn't pass, fails. Discussion ensues. Skinner remembers 2 numbers.

M: introduce flaws into 6/12/98 minutes. Passes 11-1-1 +Spehn. Skinner remembers numbers this time.

\goto{Committee Reports}

Scalarcomm: orange ruler donated to library.

Skinner-regent: inventory is 7/25.

[Unreadable] plans to dodge wild gavel swings.

Panthercomm: buy 100 for-sale books for Xmas presents!

Sitcomm mumbles about bad SF series on TV...

"Bing." (JWH)

\goto{Old Business}

Jamie consumed large mounds of cake with his bare hands.

Skinner admits to being a history major studying the ancient study of medieval studies.

M: start research into recent medieval studies. 9-2-5 +Spehn. Skinner remembers numbers AND gets a good \bing.

Skinner manages to keep track of current phase of the meeting.

JM has been fondling magazines.

Real business discussed!!! (Shock and horror ensue.)

JM defends himself by claiming "It's not all that real..."

\goto{New Business}

More whining about magazines. "We've got too many of them."

M: about something about future medieval studies. Dies in confusion.

M: a banana medieval studies nothing. 10-0-9 +Spehn.

"And so, the meeting continues." (JWH)

Pseudo-moocomm: proportional-files open today.

Food coupons for free!

\goto{Future Business}

Horrible singing, primarily by JM, dies in apathy.

M: don't tell anyone that the maltese falcon is stuffed full of bananas. 16-0-1 +Spehn.

JWH delays the end to inquire whether it's "end meeting then bing" or "bing then end meeting."

\vspace{12pt}

\noindent
Meeting adjourned, 17somethingorother SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
