\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 18, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1799 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: commend minutes for being multicolored. 10-1-9 +Spehn.

Spehn is now less than one person. Spehn should be worth i votes.

M: condemn skinner for faulty counting. 0-2-0 +Spehn. Chickens by skinnerial decree.

Suggestions for media in transition authors: Piers Anthony? Robert Jordan? Hal Clement didn't draw enough. Anthony would draw more.

Tech to burn for fuel.

Thistle and observer discussion.

Extropians running counterpoint now. How are they dealing with it being joint with Wellesley? "Don't admit women to MIT" according to the extropians.

M: move on?

M: have no further motions. 7-9-8 +Spehn.

\goto{Committee Reports}

Jourcomm: I didn't work on it this week. Might next week.

Cyniccomm: yeah, right.

M: forgive skinner. "Valley skinner?" "Filet skinner?" Unanimously passes.

M: commend skinner for voting. Chickens: everyone who lives in Spehn.

Sitcomm: lots of new SF series. They'll all be awful. Sentinel is JFM's favorite bad SF series. "I watch it for its explosions and half-naked men.

M: commend skinner for taste in TV. 11-1-3 +Spehn.

M: gavel notes got higher as you rotate it higher. 0-2-2 +Spehn.

\goto{Old Business}

Thirdspace still sucks. What is that?

"Who is JMS?"

M: men in black sequel. Ignored.

Discussion of token blondes in Star Trek.

\goto{New Business}

M: talk about food after meeting. 10-0-5 +Spehn.

Robot show at Hyatt Regency, Sunday 10-4. Brochures on the desk.

M: condemn Bill Gates for Microsoft cat. 14-0-0 +Spehn.

"Is the cat compatible with the house?"

Microsoft house: upgrade as necessary? Comes with a roof and lawn! "Dinner will be a little late, dear, I need to reinstall the kitchen."

Long apathetic silence.

M: banana on account of apathy. 8-1-10 +Spehn.

M: (blank). 0-0-0 +Spehn.

\goto{Future Business}

"I don't believe in future business."

Silence.

Meeting ends after discussion of how ? continues way past end of meeting.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
