\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 2, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Anonymous, Pseudo-President and Skinner, presiding; JFC, Pseudo-Onseck, recording.

Minutes read.

Anonymous skinner presiding talks about her day: asleep during all-nighter and desk shift, bombing job interview (in suit and heels), not finishing assignment, late lab report, sitting on bronze bunny.

M: declare minutes really, really lengthy. 3-4-a lot +Spehn.

Finger motion to new member who asked "what's a chicken?"

\goto{Committee Reports}

M: inform member about chickens and MITSFS. 2-8-8 +Spehn.

"We got 1000 dollars from finboard." (Jenwa)

Mobcomm: we have books.

"Anyone want a big roll of plastic?" (Jamie)

MW: "Thank you Jenwa for poking me."

Alumcomm: alum office has a damn lot of meetings.

\goto{Old Business}

M: bing better. 6-1-3 +Spehn.

M: give grudging acceptance to bing. 4-2-3 +Spehn.

M: commend pseudo-onseck for instructing skinner. 6-3-5 +Spehn.

M: commend pseudo-onseck for instructing skinner again. 0-0-0 +Spehn.

She gets it wrong again!

M: send Jay to Xanth. 12-4-3 +Spehn.

M: (Jade) change Jay's name. 18-0-0 +Spehn.

\goto{New Business}

JM: Mass RMV sucks.

The skinner gets talking mail from Bell Atlantic.

M: commend Toby for being susceptible to advertising. 6-4-4 +Spehn.

M: about Jay and Monty Python (I missed the details). 10-0-3 +Spehn.

M: another similar motion I didn't hear. 10-0-2 +Spehn.

\goto{Future Business}

The skinner doesn't believe in future business.

M: first shoot Bill Gates, then send him a talking banana. 8-0-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
