\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 3, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Murphy, Pseudo-Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

\bing "Mammoth."

M: nwbp-ppht! 14-0-0 +Spehn.

M: Thank WDS for pinning to the board so we didn't lose them. 17-0-2 +Spehn.

\goto{Committee Reports}

Jenwa becomes (well, not quite...) Jourcomm.

Panthercomm: I'm not looking forward to this.

Bluebellcomm: [Illegible] "No, they have jackets of dust."

\goto{Old Business}

"You don't look like a hedge." "Camouflage."

M: commend Justin for completely missing the point. 10-0-7 +Spehn.

"Does MASH count as science fiction?"

I should buy rubber stamps- discussion of Toby's book processing.

\goto{New Business}

We now have a fan opera.

M: "I could do more dramatic reading from the book." 0-many-0. "What about Spehn?" "That comes when I bing."

Picnic is probably on May 10.

"I'm not going to be in the country during exams."

Boblingen = IBM.

M: that Jen will be spending summer bubbling. Fails by skinnerial decree (the 3rd so far this meeting).

M: to commend Jen for spending the summer burbling. Lots-0-0 +Spehn.

M: include translation of Boblingen. 4-6-1 +Spehn.

M: to commend Toby for putting the front cover on the back of the book. 12-0-1 +Spehn.

M: to have a really long meeting. 3-12-3 +Spehn.

M: to continue the meeting until the bananas are ripe. 13-0-13 +Spehn.

M: make Jen talk for a really long time while we ignore her. 4-2-5 +Spehn.

\goto{Future Business}

Talk about Jen and German summer.

...and MBAs and "measurable metrics." ("Lines of perl" -Toby)

...and Toby's processing.

M: BANANA! 10-0-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
