\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 24, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, Skinner-Usurper, presiding; [Unknown], Onseck, recording.

1703 SST: reigns of power seized by skinner.

Minutes read.

No motions re: reading of minutes.

\goto{Committee Reports}

Panthercomm: inventory tomorrow.

Zat Sealead.

Sitcomm: Thirdspace sucked.

Malecomm: mail from thesis student about SF librarianship. "Why'd we establish this collection?" The first reading from the constitution of the MITSFS. "Why'd we establish it? To get chicks."

\goto{Old Business}

\bing

WDS: old puppet.

Mumbling about MST3K robot.

JM: "What's the thing that sounds like microfiche but isn't?" "Microfilm?"

Plea for end of old business.

\goto{New Business}

(exceptional bing)

M: commend skinner for exceptional bing. 5-4-1 +Spehn.

M: commend library for passing its first motion this meeting. Fails, no second.

M: submit it to North Umbria. 5-5-5 +Spehn. Chickens.

Meeting ignores skinner through an entire motion, thanks to debate about "definition of SF."

Plea for end to new business. Inquire as to whether or not it ever started.

Banana motion fails for no seconds.

Plea for future business yields apathy and mention of inventory.

Second try to move to banana the balls. Kills skinner's RAM.

\bing

Oh, it passed.

\goto{Future Business}

Debate about whether or not skinner has ended the meeting. Skinner-usurper seized power and adjourns.

\vspace{12pt}

\noindent
Meeting adjourned, unknown time.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
