\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 9, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1530 SST,
Jay Muchnij, President and Skinner, presiding; Brian Sniffen, Pseudo-Onseck, recording.

Minutes read.

Motion to commend the Society. Passes.

\goto{Committee Reports}

Bluebellcomm: 1 metric shitload of hardcovers covered.

Jourcomm: it's coming.

Motion to appoint pavement inspector for Jourcomm. Fails.

\goto{Old Business}

Library filling.

Carthage must be destroyed. 12-0-1 +Spehn.

\goto{New Business}

Motion to create Carthagecomm. 11-0-1 +Spehn.

Motion to appoint Brian to Carthagecomm. 17-2-0 +Spehn.

You're all lame. Skinnerial decree.

Photocopier coming?

Motion to commend Jen for being here. 19-0-0 +Spehn.

\goto{Future Business}

TZ coming soon.

Motion to condemn Jourcomm for using frame. 3-3-7 +Spehn.

Motion to publish TZ in Carthage. Chickens.

Motion to corner Killian. 9-4-3 +Spehn.

Motion to plant bananas. Some-2-8 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Pseudo-Onseck}

\end{document}
