\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 24, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: compliment her on the Cliffs' notes. 8-7-5 +Spehn.

\goto{Committee Reports}

Picniccomm: can't get star-chamber until 6 PM.

Sitcomm: Merlin TV series. "Has Martin Short on it just in case you're undecided."

Discussion of Bill's oldness- do you remember?

Jay depressed Toby about Challenger- generation after his (Star Wars).

\goto{Old Business}

Discussion of 1969 man on moon: WDS, Jen's mother.

Shitload of old books for WDS to process.

WDS: "Anyone want a 10 MB hard drive?" MIT society for retro-computing.

Professor: universe is stoichastic. Quantum Reuse.

Lots of old books on the shelf.

The usual confusion.

M: to prevent that from happening by chaining Jen to library. Unanimous save Spehn.

Revoke real skinner, skinner-regent.

Talk about Jen's 120 email messages. 50-60 fun, 5 work, 15 personal, rest random crap.

\goto{New Business}

Jen turns 21 on September 6, and the day will last 32 hours (plane flight).

Steve from the bookstore downstairs: Black Now wants to do an article about him. He'll be filmed in the library on May 5.

Discussion of Radcliffe degrees (to change soon) and the HRSFA people coming to the picnic.

Paranoiacomm: weird noises up there (switching to summer "heating" system).

Skinner-box. "Sorry, I get those two confused." (WDS, on Huxley and B.F. Skinner.)

So can we combine the skinner box and Schrodinger's cat? (You never know if he's conditioned or not.) Under certain stimuli, turns into a vaguely green monster... "I can't come in to work today, I'm on a psychotic rampage. Maybe tomorrow."

\goto{Future Business}

M: put a banana in the skinner box. 22-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
