\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 13, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: commend minutes for containing awful joke. 12-0-3 +Spehn.

\goto{Committee Reports}

Mobcomm: RSN.

Libcomm: debriefing last Sunday, so now we know how to deal with magazines, but because nothing was done for last year, we haven't bound in about 7 years?

Sitcomm: 7 days pulled out a bit of suckdom. Voyager: Geordi La Forge.

\goto{Old Business}

(Silence)

(Breathing)

History happened.

M: approve history. 7-7-3 +Spehn, read as "12-0-3sin(theta) +Spehn."

"If you knock yourself unconscious while trying to vote, does your vote count?"

\goto{New Business}

Christian Soldiers: the only humorous magazine about soldiers. "Guns and Moses." Connecticut Yankee in King Arthur's.

B5 River of Souls didn't suck as much as 3rd Space.

"Love bat."

Discussion of 14 year old annoying kid who is worse than Wesley. Memo to JMS- you can't write comic relief, so don't try.

B5: if you find an alien artifact, run like hell.

Jen is sick today. Her body temperature is "AC."

Potato powered clock. Human powered? "If you are going to steal someone's power then don't take it from Jen. She's the skinner and she doesn't have more to spare."

M: Transfer Justin's power to Jen. 20 or so-8-3 +Spehn. "She doesn't deserve it!"

Spacecomm: a tiny bit more space since computer went bye-bye. Did he take the wrong computer? Yes, he took the original AC. Confusions about computer number and type.

M: nothing new under the sun. 4-about 8-6 +Spehn, "4-about 12-6 +Spehn."

So Jen should be calling soon saying she feels a surge of vitality.

New book supplies!

M: commend skinner for whatever she is doing now (5:58-6minutes). 20-1-2 +Spehn.

\goto{Future Business}

M: Monkey Magic replaced by Bananas in Pajamas. 12-0-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
