\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 4, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: defer minutes from 11/20/98. 10-2-6 +Spehn.

M: define Jen as embarrassed. Fails for lack of second.

M: not to defer last week's minutes. 8-0-0 +Spehn.

\goto{Committee Reports}

Tapatatapatacomm: new keyboard which works for *all* keys. "I am so cool, yay."

Theftcomm: "What's new" now going to be posted.

LHE: turned in Finboard funding form 10 minutes late. Asked for 1500.

"How's the plot to go to Brazil going?"

M: declare Jenwa "pina-colada flavored." 15-0-0 +Spehn.

Mobcomm: no new books this week. "Are any of them new?" We should go get new hardcovers for IAP.

"Unified Twinkie": 19.01 and 19.02.

M: whoever gets the new calendar should get one that doesn't SUCK! 20-0-1 +Spehn.

Robcomm: We were robbed! The door was open... was the door locked or unlocked? Open, but unlocked. When do keyholders unlock the door? How much was stolen? We don't know. CPs? Not relevant... what would that do?

\goto{Old Business}

LHE's job is to steal from us and then run away to Brazil.

M: commend Brazil for not being attractive to LHE. 8-5-5 +Spehn.

"Hey, Justin, how's your project going?" "Yay."

Discussion of Lenscomm and the Rogues' Gallery.

Old business with "new" on it.

We have an inequities folder with nothing in it.

M: put jhawk in inequities folders. 8-10-7 +Spehn.

\goto{New Business}

Someone just walked in the door.

How's the wheel of time backwards? "It's better that way." (jhawk) Not really backwards, really from the middle; he's not done writing yet.

Secret plot to assassinate Robert Jordan.

Connie Willis discussion.

M: condemn us for not having any good books I haven't read (JM). 4-6-6 +Spehn.

\goto{Future Business}

M: suggest Jamie something banana. x-x-5 +Spehn (GAPING holes where numbers should be)

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
