\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 7, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: declare the minutes more interesting than the meeting. 14-0-3 +Spehn.

\goto{Committee Reports}

Sitcomm: Third Space continues to suck.

Mobcomm: we have the novelization of Lost in Space. "Ooohh." We have the novelization of Armageddon. "Damn, it's thin."

Panthercomm: we have a shitload of new books, still.

M: "I have no idea what that was."

M: Help, help, I'm being suppressed.

M: matrix vote!!!

All fail by skinnerial decree.

End of committee reports by skinnerial fiat.

\goto{Old Business}

M: shut up. 4-4-6 +Spehn. Chickens.

Inventory results discussed again.

M: put an exploding dye packet in our next Brust book. 15-0-0 +Spehn.

\goto{New Business, no bing}

Floor will be waxed; hopefully they'll miss the books.

M: wax all books by Piers Anthony. frAm. whack; fr.Am wane. 4-4-10 +Spehn.

Bill admits to being on acid and sees elephants.

Elephant defeats Boris by skinnerial decree.

We say "hi" to new people.

Vani flees.

Telzey toy's heart is exhibited.

\goto{Future Business}

Discussion of R/O.

"Frosh will exist, eventually."

"SAE won't, eventually."

JM makes airplane joke about drinking problem.

M: condemn JM unilaterally. Hmm-oh-wow +Spehn. Chickens.

Bill sets up the MITSFS computer to mimic his home box.

M: MITSFS to be really boring with a banana. 10-3-10 +Spehn.

Singing.

M: make that last vote pass. 7-0-lots +Spehn.

M: commend the poultry. 8-4-4 +Spehn.

Miller Motion. Fails.

Miller Motion. 15-0-14 +Spehn.

Singing.

Begs and pleas to (unreadable).

M: take away (unreadable) voting. 10-0-17 +Spehn.

Singing.

Miller Motion. 14-0-14 +Spehn.

M: chickens all for Miller Motions. 0-0-15 +Spehn.

M: stuff bananas down throats of chickens. 10-0-20 +Spehn.

Singing.

M: banana. 19-0-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
