\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 28, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: minutes read with pain but not good enough. 14or20-0-2 +Spehn.

\goto{Committee Reports}

Missivecomm: guys with brains only found at the SF library.

Shera Damon.

M: act upon information. 11-2-8 +Spehn. (Passes?)

\bing

M: condemn skinner for apologizing. 16-2-8 +Spehn.

"So there!"

Fweekcomm: M: say hi to frosh. "Hi." 9-5-1 +Spehn. "HI!"

Dexmistress: new dexes.

Sitcomm: next Friday is old Star Trek. Tuesday weeknights at 7:30 PM.

M: explain matrix vote. Etc.

Permission to inquiry. Skinner ignores JPM. Cheers.

\goto{Old Business}

Leave us money in his will. Does he plan on dying?

M: instruct skinner to use of Albania. Fails, lack of second.

"Jenwa's still in Germany."

M: commend Jenwa for running meeting from Germany. 7-5-4 +Spehn.

\bing

M: ignore previous motion. 14-0-9 +Spehn.

Usual motion.

Usual second.

Usual debate.

M: put Brian Sniffen's membership on a pointy stick for him. 18-0-1 +Spehn. "Somelarge-0-1 +Spehn."

\goto{New Business}

M: condemn Jen for all of Jenwa's mistakes. 33-0-0 +Spehn.

Name for Martian hour? Email jfc(at)mit.

Leap hour?

"Usses." M: blue sticker and Albanian Jay. 20-4-1 +Spehn.

\goto{Future Business}

M: all meetings conducted in Albanian. 4-18-1 +Spehn. "Some numbers."

M: commend frosh for being old and cynical. "Something to smaller to irrelevant."

M: ask onseck where banana shirt is from. Fails. "Don't care."

M: adjourned by sentient bananas. 15-0-less +Spehn. "Fifty to zero..."

\vspace{12pt}

\noindent
Meeting adjourned, 17something SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
