\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 9, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: approve minutes for being non-talkative. "They're written in MIME format!"

Albanian! Fails by skinnerial decree.

\goto{Committee Reports}

Panthercomm/mobcomm: "Deathlands," "Earthblod." Books are skinner's fault. "I had really bad taste in high school."

M: use Jay's foot as gavel block. Fails by skinnerial decree.

M: use Jay's foot as gavel. No second.

Sitcomm: Mercy Point is "ER in space."

ER/space = 10000/1

Alumcomm: alumni office doesn't allow sendings in the fall because they do their own mailing then. Maybe in February, but it doesn't look good.

What if we buy a mailing list from like "Guns and Ammo" and tell them they owe us money?

Are all sprinkler systems connected? Lighter test proposed...

Firebomb a health food store.

\goto{Old Business}

"Very soon I will be old." (Justin)

This was an excuse for a bad rendition of Happy Birthday to begin.

Talk about the girl who got drunk and passed out at MIT.

They had postered in Boston as "FijiPunch."

Skinner squeaks.

Isaac Asimov is still dead.

TZ Real Soon Now (TM).

Onseck quits due to NJ joke.

\goto{New Business}

Skinner placates onseck by skinnerial decree.

M: commend skinner for multiple bings. 11-2-13 +Spehn.

M: condemn MITSFS for missing Justin with bookstand. 20-1-3 +Spehn.

M: commend 4th West for their choice in tutors. 20-1-6 +Spehn.

Newbury Comics now selling Cheesypoufs. They already look stale.

M: get bananas for dinner. 6-7-8 +Spehn.

Sign-of-Apocalypsecomm: on Star Trek seven of nine book, "Resistance is futile! (TM)" They trademarked it! Paramount went to the Navy to sue them for having a ship called "Enterprise."

M: commend M for missing every episode of Seinfeld. 15-7-2 +Spehn.

Moral of Star Trek: Kirk and Spock should never go on shore leave.

ST5 vs. Highlander II: ST5 comes out better. "Highlander II: there should have been only one."

Mr. Potato Head.

\goto{Future Business}

M: Mr. Banana Head? 24-1-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
