\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 17, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Plea for motions.

M: approve reading of minutes as supercalifragil...etc. Fails 8-9-3 +Spehn.

\goto{Committee Reports}

Mobcomm: we got a couple of books. "Given the amount of money you spent..."

Panthercomm: they were processed, they're over there and over there and over there...

Furniturecomm: this chair's broken.

Mumbling about Dr. Who.

Plea for the end of committee reports.

Dexmistress: inventory. Be there.

Plea for the end of committee reports.

Sitcomm: Time Cops sucks.

Plea for the end of committee reports.

\goto{Old Business}

JM: books rearranged.

M: Roy Rogers to be stuffed and mounted. "Eww..." Chickens 4-0-5 +Spehn.

Algol mangled by skinner.

Skinner cajoled into finishing.

\goto{New Business}

M: shut up. Passes 8-6-4 +Spehn. "8-something-4 +Spehn."

M: commend skinner for having more RAM. Fails; no second.

M: say hi to Vani and embarass her. "Hi." "Oh, we should pass it then." 20-4-2 +Spehn. "Something like 20 to something like 4 to 2 +Spehn."

"I don't get embarrassed by 'hi's." "Oh, stare." "She clearly hasn't taken enough drugs."

Plea for more business.

Skinner informed we're in new business.

M: sell the DoD a stealth banana. Chickens 11-4-11 +Spehn. (Yes, with Spehn as well.)

\goto{Future Business}

M: neutrinos have mass. "Better not vote this down." 15-14-1 +Spehn.

M: neutrinos have so little mass they... 16-1-3 +Spehn. "Motion passes something to something." Hand waving.

\vspace{12pt}

\noindent
Meeting adjourned, 17something SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
