\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 3, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie, Chancellor and Pseudo-Skinner, presiding; Ed Keyes, Pseudo-Onseck, recording.

Minutes read.

M: banana! Fails without vote. Too early to end meeting.

M: laughing. Chickens 1-2-2 +Spehn.

\goto{Committee Reports}

Dexmistress: still July 25.

Pseudo-Hasslecomm: new "withdrawn" stamp for books.

We lost a member (AMT).

Shelfcomm: rearrangement almost done, woohoo!

Tons of stuff donated. We have years of life now.

Walk-in-comm: books donated.

Panthercomm: we got a donation now.

M: commend donation. Passes 2-0-6 +Spehn.

Discussion of obscure dates on "time to explode" graph.

M: who cares which Jordan books are checked out. Passes 2-0-3 +Spehn.

M: commend math of pseudo-skinner. Passes by fiat.

Donation is a bag of Star Wars books.

\goto{Old Business}

Tomorrow the country is 222 years old.

Pentiumcomm: check that math (declaration vs. constitution).

Discussion of Schoolhouse Rock, Star Trek, and the writing style of the Declaration and Constitution.

M: condemn Constitution for no copyright or acknowledgment. Passes 1-2-4 +Spehn.

M: love that gavel! (Chastely, please). Does everything 2-2-1 +Spehn.

Donation is, in fact, 17 Star Wars paperbacks.

Discussion of book burning techniques.

Scientific units: yay for dynes and slugs and ergs.

Finger motion.

Usual junk.

\goto{New Business}

Armageddon opened.

M: commend everyone for not noticing. Passes by fiat.

Bruce Willis, 12 Monkeys, Die Hard, Hudson Hawk, Bill and Ted, Time Bandits, consistent time travel, general relativity.

M: praise movies with consistent time travel, unless they're boring. Passed yesterday.

Para-doctoring paradoxes from "All you zombies" by Heinlein.

M: I'm hungry. Passes lots-few-few +Spehn.

M: everyone's not hungry. Fails by fiat.

M: commend Teresa for not recognizing a book. Passes everybody-nobody-nobody +Spehn.

\goto{Future Business}

M: end meeting. Amend: with a pineapple. Passes 3-0-2 +Spehn.

\bing

M: something with a blue banana. Fails, no second.

M: morse code. Passes 2-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Pseudo-Onseck}

\end{document}
