\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 20, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: minutes worse than Wesley. 14-0-4 +Spehn.

\goto{Committee Reports}

Pseudo-sitcomm: Voyager (ship) was crashed into an iceberg.

M: condemn Voyager for stealing plot from Titanic. 14-1-1 +Spehn. "But Titanic has no plot!"

Mobcomm: new books. "Yay!"

Pseudo-pianocomm: 2 new prentices- Courtney is here!

Flushcomm: took a long time and wasn't easy, and finally got rid of Patriots.

\goto{Old Business}

Back to using old keyboard after Swapfest ended where you could find a "cord" of keyboards. Talk about keyboards.

M: plug Jamie's brain into AC. 9-9-7 +Spehn.

M: condemn Eddie for no. 11-0-10 +Spehn. "11-10-0 +Spehn."

M: commend skinner for confusing skinner. 15-1-2 +Spehn.

M: condemn Christa for reading Anthony in public. 9-9-12 +Spehn. "I oppose; I support a woman's right to choose."

M: note nothing with an orange ribbon is allowed to leave the library. Fails for lack of second.

Other new prentice Natasha.

M: say hi to Courtney and Natasha. 22-0-0 +Spehn.

\goto{New Business}

JFM: I have a Telzey! Someone from 3rd East (Santiago Rivas). "So bring him here so we can give him the Telzey Toy." JFM pants.

M: even Santiago Rivas has to read the Telzey rites. 0-10-0 +Spehn. "Inverse skinner rule." "Telzey \bing equals skinner."

M: can I have my energy back? (Justin)

She needs it! That's how she got a Telzey: he was impressed by her energy. Better not tell him it's Justin's.

M: give Justin more energy. 6-5-4 +Spehn. Where are you getting it from? Jen Hawthorne- won on Jeopardy (Jenwa squeaks upon hearing the name).

Showing in January. Roger Silverstein is the other one.

Discussion of Jeopardy. How do you study for it? She won 9001 dollars so we should hit her for a donation.

M: "You bastard! I'm going to have to spank you!" 4-0-6 +Spehn. She's the Pikan spanking chair!

M: commend Transparent Horizons for being liked by 2 people.

M: store member's energy in the banana-colored "soul-ovoid" for use by skinner. 13-something-12 +Spehn.

"Okay, so Spehn comes back and kicks my butt."

\goto{Future Business}

M: commend Spehn with a banana. 12-0-10 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
