\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 30, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: approve minutes for having a tiny little Canadian flag on her shirt. 9-0-5 +Spehn.

\goto{Committee Reports}

Pseudo-sitcomm: weekdays at 11 PM, Channel 2, PBS: Red Dwarf, seasons 2-3. Because evil Bruins ate up 7 Days, Voyager on Sunday at 8, Saturday at 11 just because "Voyager sucks less in German."

M: broadcast in foreign languages B5, Voyager, and Red Dwarf. 13-4-4 +Spehn.

M: broadcast in Chinese. 0-0-5 +Spehn.

M: have a matrix vote anyway! "Fails by something."

Pseudo-pianocomm: Ed Keyes got keys.

M: "One of my votes to get a second." Fails, no second.

\goto{Old Business}

"Really old dude in space, man..."

Shelf rearrangement of NC paperbacks still ongoing.

Tomorrow William will be 41!!!

M: commend for being prime. Fails for lack of second.

M: declare J Albanian. "We can't declare an Albanian- it's only for puns." "No, I've been Albanianed for all sorts of things." 18-4-1 +Spehn.

M: Jay is a low ranking Albanian. 9-0-2 +Spehn.

"Jay looks like a young Steven Tyler before most of the drugs."

M: commend Andrea for being sultry. 4-2-4 +Spehn.

Comic books are in Albania- stolen from California.

Isaac Asimov is still dead, but his body was stolen by Albanians.

\goto{New Business}

Halloween? "Given that it's my birthday, I'm going to sleep a lot." Rendition of Happy Birthday.

M: commend Jen for being a polyglot. 12-7-5 +Spehn. Jake voted about 10 times...

"Do you get more votes per sultry women on your lap?" "2 less, because of them being on your lap." "Depends on how good your balance is." "Or what you define as... limbs..." (JFM)

M: commend skinner for having a dirty mind. 18-0-0 +Spehn.

M: commend for being fast. 0-0-0 +Spehn.

Stop buying used books. Space problems. New books attract members. "Buy a finite number of books, please."

\goto{Future Business}

M: have skinner go to Hallow Ranges as a banana. 8-0-9 +Spehn.

Miller Motion. Fails.

Second Miller Motion. 7-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
