\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 25, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1705 SST,
Jenwa, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Summons Jen Murphy.

M: commend skinner for responding to summons. 20-1-3 +Spehn.

M: condemn boring.

Minutes read.

M: commend minutes for being confident. 0-11-15 +Spehn.

M1: condemn skinner for crappy bing. M2: commend skinner for being well dressed. M3: matrix vote!

(Lots of icky math done on the side by someone who doesn't remember what a matrix is)

The magic number is: 1732.

No one believes me. Sigh.

\goto{Committee Reports}

Shelfcomm: reserve PA.

M: move spare stuff shelf to where Justin is sitting. 18-12-2 +Spehn.

"Blood of a warrior will make the wall strong."

M: make Jen throw shoe.

M: take off price tag first.

M: to do something to someone's really old thesis thing.

Mobcomm: books mailed this weekend.

Cyniccomm: yeah, right.

\goto{"New Business... no, wait, Old Business"}

M: commend skinner for being retroactive. 6-4-lots +Spehn. "4-no, I want to vote for the in favor!"

M: start stockpiling dustbuster parts. 0-0-1 +Spehn.

M: insert "banana" in all motions. 11-20-1 +Spehn. "Chickens."

M: have skinner play 8th notes with the gavel. 4-3-many +Spehn.

M: have skinner create a standing wave front with the gavel. 7-1-3 +Spehn.

M: raid The Tech for supplies and hostages. Fails by skinnerial decree. "We've already done that."

M: declare treaty is just a piece of paper.

\goto{New Business}

\goto{Future Business}

M: declare banana greater than treaty. 13-1-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
