\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 23, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: approve minutes as "supposed to drip." 17-1-2 +Spehn.

M: that was a pathetic bing. 20-1-2 +Spehn.

M: that sentence should be shot. 11-2-3 +Spehn.

M: someone else should bing the gavel. 11-3-2 +Spehn.

\goto{Committee Reports}

Panthercomm: more books are coming in.

Mobcomm: more books because pseudo-mobcomm has been sifting. 8-1-3 +Spehn.

M: bing motion. 9-9-0 +Spehn.

"If you bing the skinner, your dues automatically disappear." "Not unless you're the Telzey..."

M: elect a Telzey? 4-0-6 +Spehn.

Sitcomm: new production staff does nothing for Voyager.

Pseudo-sitcomm: new B5 season in 5 days.

Jordan's 8th book is coming out. "The asymptotic series..."

Brimstone premieres tonight at 8 PM.

M: condemn major league sports for taking up valuable TV time which can be devoted to sword fights, explosions, and "scantily clad humans of the appropriate gender." 18-1-0 +Spehn.

\goto{Old Business}

Palm Pilot party was fun. "But did the Palm Pilot have fun?" "It got to blow out the candle." "Okay, the skinner blew out the candle." "She didn't stick her finger in its serial port..." "But that's because she's Catholic."

M: commend the skinner for practicing good computing. 16-1-1 +Spehn.

M: commend Jenwa for beating up J. 5-1-7 +Spehn.

M: (a) assume a spherical metal chicken... 18-2-1-4 +Spehn.

"...who might want to go to Arisia/Boskone?"

M: the silly putty thing has successfully dripped. 6-0-10 +Spehn.

M: score on John for coming up with a pathetic banana motion. Some-some-some +Spehn. Chickens.

Time warp this Sunday!

Cthuloids: "what's the new sacrifice?" "Hot dogs."

Jamie: "Because Brian doesn't know the difference between Cthulhu and Aras!"

\goto{New Business}

\goto{Future Business}

Miller Motion! Fails by skinnerial decree. "Say fail!"

Second Miller Motion! 9-0-11 +Spehn.

Rendition of "Skinner has no tail at all..."

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
