\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 4, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

(These minutes have been colorified beautifully)

(highlight blue)

Minutes read.

(/highlight blue)

M: "I'm speechless." 9-1-4 +Spehn.

Skinner forgets the votes already.

\goto{Committee Reports}

"Bitch JWH regarding JFM for leaving 1.5 years of LHE books undone."

Fweekcomm: we got frosh.

M: condemn the frosh for not showing up. 8-4-2 +Spehn.

Plea for more comm reports.

(highlight orange)

\goto{Old Business}

(/highlight orange)

Thirdspace still sucks.

ALGOL punted.

Lethargic meeting continues.

\goto{New Business}

"Ray" may end up being the Martian hour. Somebody better break the news to him soon.

Discussion of sundials on spaceships.

JM arrives and can't tell there's a (underline highlight pink) meeting (/underline highlight pink) going on.

Plea for more business.

M: say hi to Miriam.  -0-5 +Spehn.

Plea for more new business.

M: cootchy-coo new people. Fails for lack of second. "Thank God!"

Bill brings JM's mind back to what's important: money.

\goto{Future Business}

M: make sundial banana colored. 10-1-11 +Spehn.

Boo, hiss... Skinner let motion pass just as the meeting got going.

\vspace{12pt}

\noindent
Meeting adjourned, unknown time.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
