\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 1, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: aah! 25-1-1 +Spehn.

\goto{Committee Reports}

Panthercomm: old crap processed.

Non-bluebellcomm: hey!

Bluebell-assistant-com: help me!

Pianocomm: apprentice (Jade) working on Magdex soon.

JMS RSN.

Pseudo-picniccomm: we need drivers.

Teresa Tet has a truck with a camper shell and will go to the picnic. :)

Pseudo-picniccomm: need fridge space.

\goto{Old Business}

(Pause.)

WDS: "I'm not saying a word."

Carthage must be destroyed!

M: have Carthagecomm sharpen up his pointy stick so he can go kill Carthage. Buttload-4-5 +Spehn.

\goto{New Business}

Jen: we have to wait for appeals for finboard. (She gave blood, passed out, and forgot about it.)

M: greet the new person. Amazing amount-0-2 +Spehn.

M: to commend unidentified woman in subway train for not only wearing a white dress with black polkadots but also for walking 2 dalmatians. 7-2-4 +Spehn.

M: Jake: "This is the first MITSFS meeting I've been to." Passes, skinnerial decree.

M: mourn loss of WDS's monitor. (Taps.) 16-5-10 +Spehn.

M: to condemn people's musical skills. Passes by skinnerial decree.

M: retroactive banana motion. 15-1-17 +Spehn.

New membership rates.

Justin leaves for 2.70.

Discussion of 6.836- Jake's project.

M: TT: "I like your gavel." (The Telzey overrules that motion.)

\goto{Future Business}

Jen: I will not turn over the books to the new LHE without having them be balanced. (After elections, before she leaves in 2.5 weeks.)

M: you should not go over there if you don't have a place to live. Buttload-10-3 +Spehn.

We should check the books for transfers to deutchmarks. I haven't done them yet!

Discussion of MIT German program, sackage of the.

"In the future, I will get everything important in writing."

Ed refuses to be Atlascomm this year.

ST:V just had an episode set in their future.

"I canna' do no more, captain, the hamsters are tired!"

M: to declare Jake's timing sucky. \bing It's a law of nature.

Jake will be a prentice.

M: to set up committee to deal with year 10K problem. 16-16-2 +Spehn.

M: to define the 10K problem as being that it's over 8000 fuckin' years away! 23-?-12 +Spehn.

Discussion of Spehn.

Miller motion fails second.

M: damn those Miller motions. 23-2-4 +Spehn.

M: banana! 31-1-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
