\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 22, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa, Skinner-Regent, presiding; [Unknown], Onseck, recording.

Minutes read.

M: minutes in training. Chickens 7-4-6 +Spehn.

Why chickens?

M: read upside down. 15-0-2 +Spehn. "Ooh." "Ahh."

\goto{Committee Reports}

Panthercomm: 1/3 donation processed. Stuff to [unreadable]. Stuff. Hasslecomm stuff. Space estimates.

Commcomm: Gabriel is Theftcomm, but wants a different committee.

WD-40 donated to library. Orange stickered.

M: Sitcomm needs a committee to murder NBC. 12-1-3 +Spehn/12-1-2 +Spehn.

Why? Wednesday night: Law and Order and 3rd Rock, Seinfeld before, plus 10 minutes, screws up taping!!!

Skinner gets a phone call!!!

Houston and midwest are smoky because of fire.

\bing Oops.

\goto{Old Business}

I'm getting old.

States and relativity and Tree of Life are bad.

The planet is too close to the sun. Ouch!

Marcus is old. Not Marx!

Magazines are old.

Comic books? California. No comic books.

Random motions from old minutes. Refusal to bing for them. JPM collapses in grief. Need a sugar-free bing substitute. Never tasted because tech bits.

\goto{New Business}

Aaron finished business. Condiments as follows. Paper finished.

Move on.

\bing

"Ooh!"

\goto{Future Business}

Tradition passed on. Rejoicing.

M: New England needs more crop circles. 8-0-6 +Spehn. "Ooh." "Ahh."

M: Theresa should contact aliens to do it. 7-1-5 +Spehn.

Handed paper. Disneyland is to update the futureworld exhibit. Retro.

"Skinner has no clue at all..." (Tickling and general wrestling ensues.)

Phonecomm: RING! Ack!

M: something unintelligible.

M: "what the fuck?!"

M: bananafuck! 13-6-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Onseck], Onseck}

\end{document}
