\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 16, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: commend minutes for luring Jenwa back. 12-1-4 +Spehn.

\goto{Committee Reports}

TZ: Not This Week.

Mobcomm: mumblemumblemumble.

Sitcomm: Mercy Point cancelled.

M: cancel UPN. Fails by skinnerial decree.

M: placate skinner with another show featuring half-naked men. "Buffy is going to have a bunch of half-naked men in the next episode." Toby goes "Yay."

M: commend Toby for firm grasp of what's going on. 12-2-0 +Spehn.

Voyager: "Where no one can hear you yawn."

M: condemn Voyager for existing. 12- -11 +Spehn.

Xena is going to be on SNL. How are they going to spoof a spoof?

Toby does a rendition of Joxer song...

More Sitcomm: "Brimstone" moved before premiere.

TOO MUCH SITCOMM!!!!

Long discussion of Highlander trivia.

\goto{Old Business}

"We want the Mammoth Book of Erotica."

Description.

Talked to Pat Cadigan and got her business card. Should contact authors early if you want them around at the picnic.

M: commend skinner on general principle (she leaned into the gavel and hurt herself). 10-2-1 +Spehn.

\goto{New Business}

"What about the usual debate?"

M: commend skinner for banging (gavel the right way again). 16-0-1 +Spehn.

M: Art Bell? 6-0-5 +Spehn.

Discussion of radio talk shows.

M: congratulate Toby for missing premiere of Mercy Point. 12-10-2 +Spehn.

\goto{Future Business}

Monday the 19th, Random Hall basement: Palm Pilot party by JFM.

M: banana smiley face on skinner's shirt. 17-1-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
