\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 21, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: condemn skinner for resisting singing songs. 11-2-1 +Spehn.

M: condemn skinner for having the 10-vote problem.

\goto{Committee Reports}

Pseudo-mobcomm: we got hardcovers. They're even covered.

Pseudo-pseudo-mobcomm: printed out Echoes of Honor Ch. 1-10.

Fweekcomm: frosh will exist. Keys, sign up for hours.

Pseudo-somethingcomm: Thirdspace still sucks.

Concomm: there was Worldcon.

\goto{Old Business}

Plea for old business.

Floor was waxed. Maybe.

M: commend JWH for having DNA. 7-2-2 +Spehn. "Passes a not very large but more than the smaller numbers."

M: mrr. 1-0-3 +Spehn.

Lame attempt at the ALGOL, inserting Thirdspace Suckage.

Subtle transition to New Business.

\goto{New Business}

Very subtle transition to Future Business.

\goto{Future Business}

Discussion of various kinds of business.

M: whack Jamie over the head with a very large banana. 9-0-8 +Spehn.

M: condemn skinner-regent for counting correctly. No second.

M: banana. 14-2-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1764 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
