\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 6, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read or something.

M: onseck, keep up the good work. Passes.

\goto{Committee Reports}

Jourcomm: TZ waiting for Meisha Merlin ad.

RCA purge is good. (8 months to 4 hours.)

Pseudo-mobcomm: 1st time in 4 weeks.

\goto{Old Business}

M: commend those book people for giving us an ad. Passes.

M: I already voted? Passes on much handwaving.

\goto{New Business}

Marcus, gavel.

M: commend skinner for banging his gavel in front of a mirror. 5-4-4 +Spehn.

"An announcement." "RSN?" Second. Motion passes.

M: leave MIT, spend all of the [illegible] on the MITSFS. Unanimous (except for Spehn).

Period of not telling Jen about B5, Lyta-Zach love plot.

M: nothing. 7-5-5 +Spehn.

M: end new business.

\goto{Future Business}

Miller motion fails.

Miller motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
