\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 10, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa, Skinner-Regent, presiding; [Unknown], Onseck, recording.

Minutes read.

M: commend minutes as enigmatic. 2-7-3 +Spehn.

\bing Passes, not fails, that's right.

M: those are the right numbers. Fails, lack of second.

M: those are the wrong numbers. Passes 9-0-0 +Spehn.

Skinner forgets spehn.

\goto{Committee Reports}

Pseudo-mobcomm: Mobcomm's here but not reporting. We're getting a shitload of books.

Mobcomm: a shitload.

Pseudo-mobcomm: a shitload.

Skinner ponders, realizes old business is neat.

\goto{Old Business}

Anyone? Anyone? Bueller?

Old skinner-regent is back.

TE claims to read JPM's mind. "Ick."

WDS: W20 is throwing out bad chairs.

This reminds Y of Japanese society.

Discussion of perils of sitting down in the dark.

Armageddon gets reamed by Siskel and Ebert but gets good reviews from Brunching Shuttlecocks and Post-Feminist Playground.

Lethal Weapon 4 today. "Last I heard, it was still being made." "It is."

\goto{New Business}

Actually a decent bing.

M: commend skinner for it. Fails for no second.

M: all remaining motions be thirded this meeting. 8-1-mumble +Spehn. Fails, because nothing would ever get done.

M: miller. Fails. "I'm not binging for that." \bing

M: timewarp next week's minutes to several weeks hence. "No." (WDS) Fails for lack of second.

WDS mumbles about Roy Rogers' death. Promises universe for [unreadable].

M: set Roy to star in next Buckaroo Bonzai flick. Passes 11-0-1 +Spehn.

Plea for more new business.

\goto{Future Business}

No Future is a Dr. Who book. We have it.

Martyn flees.

M: commend book for being had. 5-0-0 +Spehn.

M: replace gavel with a softer banana. Ignored completely.

Y describes poor ferret. "One of the most nervous animals known to science." Brought to fireworks.

Skinner urges Toby to try again.

M: threaten ferrets with bananas. Passes 13-0-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1764 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
