\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 23, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Meeting thinks it's starting, but doesn't. Ho hum.

\bing

Minutes read.

M: minutes unfair to Jourcomm. 5-7-6 +Spehn.

It is decided to bing on catalogs brought by ex-skinner Huckleberry.

\goto{Committee Reports}

TZ in 4-ish weeks, says Jourcomm.

Then Picniccomm rights will be written. AMU to be Picniccomm.

Catalogs insufficient; Tech added.

Jen leaves because of interaction between gavel and her new fillings.

Some motion chickens 4-3-a lot more +Spehn.

\goto{Old Business}

"Exceptionally old ex-skinner" is here. Whee. He gives a report of his great deeds.

MITSFS discusses its empire-building goals.

Old folks try to out-old each other. Only one person present was not born by 1976.

We have pictures taken.

Motion: avoid Boris calendar in future by replacing with "Hunters of the MITSFS" calendar. Passes.

Motion about paper bags fails for lack of second.

Discussion of farmer (calendar) Mad Libs.

Boris vs. Tolkien war continues.

Some people introduce themselves- they have a writing workshop for people trying to publish horror/SF. They leave flyers.

\goto{New Business}

Oh. I guess they were in New Business.

Some news about Stephen King- he's writing an X-Files. So is William Gibson. (Something about Jeopardy and aluminum-covered book.)

\goto{Future Business}

Carthage must be destroyed again.

Some cool motions fail.

SF marathon tomorrow. Snafu with Star Trek at LSC.

Toby tricked us into admitting Highlander 2 exists. Motion to commend Jamie for this glorious deed passes.

Too much TV talk.

Motion for Buffy/Highlander crossover passes.

Ho-hum. Pseudo-onseck refuses to record this silly discussion.

\goto{Recursive Business}

"Don't go there."

Motion to enter recursive business fails for lack of second.

Motion to not have any banana motions so meeting will go on for a while. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}
