\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 20, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Brian Sniffen, Pseudo-Onseck, recording.

Skinner abuses pseudo-onseck.

Minutes, which are confusing, read.

M: minutes be confused. Passes.

\goto{Committee Reports}

LHE: we have 700 dollars, and 300 dollars due for Finboard. But we have some cash from endowment fund.

General depression.

M: commend LHE for good try (read 1000s as 100s). Passes.

LHE gives more reports. Confusion reigns. But we have some money.

Pseudo-mobcomm: "Rejoice! We now have Sea Quest books!" And some Blake's 7 books.

\goto{Old Business}

None.

\goto{New Business}

Martyn: there was a lecture. (On sci-fi.)

Justin: no undergrads.

We bask JMS some.

M: J to be disappointed. Passes, as onseck arrives after nap. J is excited.

"Hey Jenwa, was that you who gave me lots of money earlier?"

Some members cannot distinguish among female Star Chamber members.

Moose to the rescue.

Dots, dots, dots. M: put another dot on gavel. Fails.

New old people arrive.

M: quit it.

Nothing happens for some reason.

\goto{Future Business}

Miller motion fails.

2nd Miller motion: vote gloriously carried by Moose and [illegible].

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Pseudo-Onseck}

\end{document}
