\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 11, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

(Beautifully decorated minutes...)

(red ink)

Jenwa escapes!

M: commend Jenwa. 18-6-4 +Spehn.

4 motions happen.

M: dismiss the motions.

Skinnerial decree: no matrix vote.

M: commend skinner for abusing power. 16-11-9 +Spehn.

M: Albanian Jay and Jake. 20-8-4 +Spehn.

(/red ink)

(green ink)

Photo of JFM at the Albanian embassy.

(/green ink)

(blue ink)

Minutes read.

M: commend minutes for being nicely highlighted. 10-1-9 +Spehn. "Ah, I'm spinning." (JM)

(/blue ink)

\goto{Committee Reports}

(green ink)

Panthercomm: lots of books.

Jourcomm: plan to work on dec. May have more art. "Potentially this term now."

Discussion of Twilight Zine.

M: make Jamie Albanian. 9-12-3 +Spehn, said as "some to many to less."

M: commend Jenwa for infiltration of skinner.

(/green ink)

(red ink)

Passes. Lots and lots and lots-1-6 +Spehn.

Fweekcomm: rush happened, got frosh, scared frosh.

M: commend Theftcomm for not being lame. 20-2-7 +Spehn.

Bluebellcomm: eventually stop being read.

\goto{Old Business}

Skinner!

M: commend skinner for being old. 76-2-1 +Spehn.

"Happy Birthday" sung very very very badly. Ouch.

(/red ink)

(green ink)

Birthday in German???

Attempt for German Telzey?

M: condemn Germany for having icky people. 10-5-3 +Spehn.

No single guys who don't smoke there.

3rd Space still sucks.

Comic books still in California.

M: commend skinner for having sex life with milk. Ended by skinnerial decree. (11-3-many/many/many14 +Spehn.)

\goto{New Business}

Usual motion.

Usual second.

Usual vote.

(/green ink)

(blue ink)

Albanian robot: cart thingy.

Albanians got the wheel!!!

"Meanderer": expelled from all groups' doors.

Pleas for asylum at MITSFS.

M: blue sticker Meanderer. 26-0-0 +Spehn.

M: ship Meanderer to Albanian and say Albania is on the 4th floor. 6-12-0 +Spehn.

(/blue ink)

(red ink)

Is Jen Murphy the real Jen Murphy? Or has she been altered to a robot? She's been cloned a lot before.

M: commend Jen for having DNA :) can't be cloned. 4-5-12 +Spehn.

M: say hi to Pipa. 23-0-0 +Spehn.

Place to get your car back from being towed is inaccessible by foot (expressway). He parked, then they put up parking signs. Sell the car.

M: donate money to MITSFS. 0-2-2 +Spehn.

\goto{Future Business}

M: go to Vinnie Testa's and get banana garlic.

M: make Neel buy a life membership. 20-0-0 +Spehn.

Walking the edge of real business.

M: feed Jamie a banana. 16-0-0 +Spehn.

(/red ink)

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
