\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 25, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JM, Chancellor/Pseudo-Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: commend history for not recording the end of last meeting. 8-0-1 +Spehn.

\goto{Committee Reports}

Dexmistress: shelfdex prettier than ever.

Mobcomm: order this weekend, if MIT FTP works.

Panthercomm: big donation from Tim Kelly.

Phonecomm: RING!

Hasslecomm has HC/PB of "Garden of Rama."

There is a French cookbook in damnation alley.

WDS rearranged boxes so larger-than-weasel lifeforms can fit in damnation alley.

M: call Jamie a midget weasel. Zillions-0-1 +Spehn. Inverse pseudo-skinner rule! JM is a giant weasel.

Weather is bad...

...long digression ending in names of silent gods.

\goto{Old Business}

Inventory is July 25.

Usual stuff.

\goto{New Business}

Arisia is the weekend before MLK weekend. (Copley Westin)

\goto{Future Business}

M: start weasel on diet of solid bananas. 7-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
