\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 14, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

M: condemn skinner for apologizing for interrupting discussion. A lot-0-0 +Spehn. Passes.

Minutes read.

M: highly commend minutes for puzzling Andrea at several points. 11-2-1 +Spehn.

Pbbbbt.

\goto{Committee Reports}

M: commend. 8-6-9 +Spehn, no, 8 +Spehn.

"Wait, I can't count anymore."

Fweekcomm: frosh show up in more than 20 minutes. Frosh come as regular, well-done, and rare.

Meeting will be at 1700 next week.

M: commend people for showing up a half-hour early. 8-6-6 +Spehn.

Fweekcomm: sign up for more hours.

\goto{Old Business}

Albert donated old magazines. He was skinner when JM was born.

M: commend Jamie for being about as old as the magazines. 12-1-4 +Spehn.

\goto{New Business by WDS fiat}

Ding-dong Mike Larnick is dead.

JM is lightly punished for teasing the Andrea.

Meeting disintegrates.

JM walks the line of conducting real business.

JM crosses the line.

M: condemn JM for conducting real business at the meeting. Lots and lots and lots-0-3 +Spehn. "Passes, lots to small numbers."

M: commend people for having unsavory meeting-lust. 9-4-3 +Spehn. "Passes by some large number."

Andrea reads scathing review of a band.

M: commend the library for being inert and aggravated. Manyagain-1-3 +Spehn.

Discussion of whether or not we're in New Business.

M: something incomprehensible from Malcolm. 2-2-4 +Spehn.

\goto{New Business}

\goto{Future Business}

Singing ensues. Fails due to apathy.

Minicult: Malcolm tells us of anime characters watching each other on TV.

\goto{Some Business, I don't really care where}

M: import a banana. 11-3-11 +Spehn.

"I can't end the meeting by skinnerial decree."

"Oh, you mean you don't want to."

"It's all the same in my mind."

M: have Jenwa make a banana so large she can't lift it. 22-0-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17pbbbbt SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
