\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 15, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: illegal minutes. 13-something-9 +Spehn.

\goto{Committee Reports}

Pseudo-mobcomm: novelization of HH CDrom Klingon. Second "Mortal Kombat." 2nd "Stargate."

When's Jen leaving? We need her signature.

(Confusion)

Donation of 2K books.

Shelving space/magazine culling.

\goto{Old Business}

JMS and some other person spoke.

Autographed poster leads to criticism of autographs.

Mentioned Carthage.

Classes are old.

Condemnation of Seinfeld.

Is Red Dwarf a sitcom? Regular middle class morons say it's a sitcom. Regular middle class British? Not a regular middle class situation

M: have obnoxious monster eat cast and producers of Seinfeld. Passes many-some-0 +Spehn.

Usual motion. Usual second. Usual vote. Passes.

\goto{New Business}

Star Chamber!

M: something unheard something announcement. 12-4-4 +Spehn.

Picnic: bash watermelon with sport gavel.

"Dead for all tax purposes." (Long silence.)

\goto{Future Business}

Miller Motion. Lacks second.

Second Miller Motion. 14-10-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
