\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 29, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa, Skinner-Regent, presiding; [Unknown], Onseck, recording.

Minutes read.

M: minutes read and much rejoicing. Chickens 4-0-9 +Spehn.

"Wow, numbers. Should I bing?" (JWH)

\goto{Committee Reports}

Jamie suggests badgering Neel since Ed thinks Bluebellcomm needs help.

Hardwarecomm: donates hardware to library.

Panthercomm: more fun to come!

Muttering about inflicting donations on a hospital. Crusties badger Jenwa into giving in to their fiendish plots.

Pseudo-mobcomm: Dave and JM spent lots of money but managed to find "stuff we were looking for" anyway.

Pseudo-pseudo-mobcomm: more books.

\goto{Old Business}

"Ah!" (JWH, but she manages a decent bing anyways)

Circulating room running out of space. JM filling in for JPW in culling magazines. Discussion of reserve room space.

\goto{New Business}

Another decent bing. JWH eventually realizes that she should announce new business.

Flaming about R/O and administrative stupidity.

We have a fan, but it doesn't read stuff. (Cymbal noise.)

Pakistan saber-rattles.

Mediocre \bing Skinner-regent bemused for 1/2 minute.

\goto{Future Business}

M: funnybing! 2-1-8 +Spehn. "Something very small to 0 to 8 +Spehn" (JWH)

JWH wanders around, apparently listless.

M: make JWH run a lap around the library before the end of the meeting. Doesn't matter: 3-3-3 +Spehn. "Um, I don't remember." (JWH)

M: library by [unintelligible] banana-colored running shoes. 6-12-0 +Spehn.

Miller Motion. Fails.

"I feel a song coming on..." (Martyn)

Second Miller Motion. "(garble)" 8-7-4 +Spehn.

\bing "Ow..."

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
