\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 27, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

\goto{Committee Reports}

Bluebellcomm: shelf clear.

Pseudo-mobcomm: real Mobcomm says there are more books on the way.

Jourcomm: slept through break.

Pseudo-mobcomm: Addams Family Values, a 25 cent book.

Mika something or other thingy!

Prentice project webpage: catalog fanzines. ekclarke/Calvin Clarke, c. 1988.

\goto{Old Business}

Break. It mostly happened.

Summer school for nerdy kids discussion. We could probably convince Anna Hubert to run one.

\goto{New Business}

Sniffen promised that Magdex would get done.

Need alumni mailing.

Talk about rooming allocations.

Jen has nervous breakdown about all the MITSFS stuff she needs to do.

"The letter!" (Picniccomm) Argh.

Jen plans out her life.

We talk about balancing the books.

\goto{Future Business}

I'm just paying the phone bill.

M: stuff should get done. (Justin should do the stuff.) 5-8-0 +Spehn.

Talk of snowstorms.

M: Mmm-hmm. 3-2-2 +Spehn.

M: for a meeting to happen next week. Unanimous, save Spehn.

Belated Minicult: BU School of Hospitality.

M: give them a banana in honor of their learning.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
