\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 17, 1998

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: all these people, not a single motion! 15-0-1 +Spehn.

\goto{Committee Reports}

Picniccomm: Jade- new prentice.

Picniccomm posted invite, working on list.

Yet another TV production of Brave New World.

"War is peace, freedom is slavery, BNW is good."

Discussion of misquoting, quoting Shakespeare in library.

M: commend Andrea for hiding very cleverly. 8-5-1 +Spehn.

\goto{Old Business}

(With deference to old people to not deafen them.)

Albanian motion.

Science fiction people talk happened. They disagreed a lot; it was amusing.

Maltese falcon spoiler- JMS.

People will show up to JMS lecture in Psicop uniforms- sad.

Something about ZOC. Die, evil ozone, die!

Is there a gong in here?

\goto{New Business}

SF author from talk was invited to the meeting, didn't come. \bing \bing

\goto{Future Business}

JMS coming May 4. NO!

M: he just yawned under a banana! 12-0-10 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1708 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
