\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Carissa Skye, President and Skinner}
\newcommand{\onseck}{Rachael Skye, Onseck}
\newcommand{\meetingdate}{Friday, September 15, 2017}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection{Mancinicomm}
Mancinicomm wants permission from the instrumentality to do the thing. We contend that because we stamp books, we might as well stick a bar code on them. Putting book tape down first will be taken into consideration.

We will order barcodes and stick them on foreign-language books.

Declaration of intent: Mancinicomm will do the thing.

\subsection{theftcomm}
Do we trust hours-held reports? We should be doing something.
Idea: theftcomm should print out a graph.

Could print out normalized graph: the point is to show outliers. We could also cut off outliers at 2 standard deviations to avoid skewing too much. This will generate a bar graph showing keyholders TIF score over time, to print out each month, posted in old TIF spot.

Motion: Run this by theftcomm and implement.

7-3-1\ps

Motion passed.
\bing

\goto{Old Business}

Sasha's favorite dinosaur is some normcore thing like t-rex.

The first female MIT student was also the first female MIT professor and also she helped build most of Eastern Cambridge's water system and now it's a very steampunky museum so they hold a bunch of sci-fi events there.

\goto{New Business}

Let's print more bookmarks.

Motion to add a subsection dealing with business from alternate timelines.

4-7-1\ps

Motion fails.

Alternate timelines are kept firmly in their home dimensions.

\goto{Future Business}

Someday Xavier will die.  Hopefully not too soon, because we need prentices.

\bing

Motion to officially designate the chain-mail banana a book

13-1-2\ps

Motion passes
\noindent
Meeting adjourned, 67.2 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
