\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachel Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, January 27, 2017}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
We are a boring below average adult. We wait by the campfire. Someone gropes us. It's a thief! We pick him up by the scruff of his neck apparently. We threaten to hurt him. He offers to give us treasure. Apparently we can't kill him? Bogus. Ugh, we decide to spare his life. I thought this was a choose our own adventure game, not a book just tells us what to do and we have no free will game. Blah blah blah fire fire fire. The thief halfling has beautiful brown eyes. We ask him to tell what he knows, halfling begins a tale. He's like man everything was great untill those magic users showed up, racist. Magic users apparently made everything worse, crops and junk. He doesn't have a lot of evidence, but our basic boring avatar seems likely to believe him at face value.
So halfling ran away somewhere, and some guy found him while he was hiding. Then he paralyzed him. Oh, now he's not gonna tell us the frightening things he saw. Oh no, what a shame. Please tell us more, I was so enjoying your long boring story. So I guess when the halfling said all the world's treasure he meant the halfling's treassure he saw this one time that  this magic user guy stole. And halfling teleported into forest.
Okay now the book is telling us we feel sorry for him? So not only do I not get to choose my own adventure I don't even get to pick my feelings?
So halfling is to scared to show us the treasure he promised, which was supposed to be the whole reason why we were keeping him alive. So anyways he brings us to a mountain, because I guess we had nothing better to do. Oh, and now we're offering this halfling to be our companion. So now the halfling is our companion. There's a skeleton and he's looking at a thing, and the skeleton is looking at a message telling us watch the water that is not water and beware the bassilisk. 

FINALLY! FREE WILL!
Motion that we investigate hole in the wall. If we don't, that means we investate leaves.
Investigate hole in wall.

FAILS 8-13-0\ps

Motion fails, we check the leaves.

So we step in the pile, way to check leaves. So we fall through it. THAT'S NOT WHAT CHECK LEAVES MEANS BOOK. Now we're falling. Oh noooo what a crazy random happenstance. And now halfling is following us. Wait, you followed us because you thought we'd been eaten? You are the worst companion. I'm listening to lord of the rings music right now and let me tell you you are like the anti samwise. yes you're that bad, you're as terrible as samwise was great. Hang on, pin in that thought, we're fighting an orc now.

Motion to fight if fails hide

PASSES 20-4-0\ps

Side corridor. We have to fight! No, we want to fight. Jeez, why is this guy the worst. So we take our cloak off to fight, the halfling gets in our way, our cloak wraps around ork, cloak is best character best girl. Killed orc yaay! What do you mean you've never killed an orc before? Lorris you've still never killed an orc, cloak did all the work. Cloak is the real mvp. Anyways we walk around and there's a big babboon it's got clothes on it looks drunk and it has a sword. Oh, the sword is rusty. Oh how surprising, a baboon is depressed and underground. 

Motion to face the baboon. This isn't a real choice

PASSES 13-6-6\ps

We go after the baboon even though it's ugly. The baboon is even more of a coward than Laurus. It speaks in sign language. Unfortunately we aren't particularly inclusive adventurers and can't understand this alternate mode of speech. Oh wait the baboon is attacking and we don't want to attack it any more? Why not? But apparently the baboon isn't the greatest fighter, shocking. The baboon suicides. It's a great victory for us, but we're pretending to be sad and try CPR. A white cloud floats away and the baboon turns out to actually be a merchant who is somehow more annoying than Laurus and also makes terrible jokes. Wow mysterious. Now we run around and see more corridors described in obnoxiously explicit detail familiar to all those who have tried to map dungeons the DM is - Goblin! Something about limbs. 

Motion to fight the (hob)goblin

PASSES 16-4-4\ps

So good we're not running. They hate elves. Oh so we tell them elves are coming, and the hobgoblin believes us. What a clever trick on our part. So we tell it to fight me, wait is the point of our bluff for it to fight us or not fight us? Wait, so it runs away? It will discover the trick soon (how?) so it runs, we run down corridor. There's grinding stone.
Somethings wrong halfling! I just realized bringing you was friggin dumb! Something roars, there's a cave in, we can only go forward. Wasn't this already true? We fell down a hole, we weren't going out back through the entrance. Anyways, there's a well now. So the halfling is afraid of wells. Well. Well well well. There's something horrible in the well. Well isn't that vague and unhelpful. 
What kind of monster? I don't know, I've never seen anything like it before. Okay, that doesn't mean you can't describe it, I mean number of eyes? Teeth? Whatever. So we look in the well, shouldn't we be being more careful about looking places what with the basilisk? Okay so there's a key, will we reach into it or not. Oh, nevermind that's not our choice yet. There are bones. Man, so we're throwing a...
Lauris, bring us a bone. Halfling brings three foot bone. I bet he takes like five minutes to bring it as many feet. Bring a smaller bone, jeez. Anyways, so we throw something in and it turns out the monster is a waterweird (real creative naming). So you try to remember everything. Wells and erruptions and snakes. It will attack any living thing and also bones apparently. Okay, choice so fight, right, or left.

Motion to fight.

PASSES 15-5-4\ps

Lean against wall and try to figure out what to do next. Should we leave? Okay cool your stupid face lorris, we can distract it with your sacrificial body. So we throw a rock in and see the key. Throw rock into opposite side of pool, plunge bone into water, try to get key. Oh no, we failed. Oooooh nooo. Are you still alive? The bone touched nothing? How rough. So It's on the cieling, and the water reflected it? I call bull. No water is that still, especially when bones are being dropped in especially when there's a giant living thing in it. Okay, so we need to get the key. Honestly writer, this would've been a great time to kill us. You set it up with the water that is not water and blah. 

OOH CLOAK IS BACK BEST CLOAK YOU GO CLOAK YES CLOAK GETS THE KEY ALL PROGRESS IS MADE BY CLOAK GO CLOOAK! I'm gonna name you... cloaky? I'll think of something better later. So the water weird tries to attack the cloak NOOO NOT CLOAK! Cloak gets away! Stupid snake, mess with the best lose like the rest. So now we're choosing where to go. See? Thanks to cloak we made progress. Go left to breeze and up or right to down. Crow man is down so...

Motion to go left?

FAILS 5-14-2\ps

We go right.

Skinnarial Decree cloak's name is Clo-E. (Pronounced Chloe).

There's a sandy corridor, we want to go down, no free will book decides what we want. So there's an enormous wodden beam near the entrance. You know I beleive that, caves are very good at preserving things, I believe it hasn't rotted yet. So there's a mining hill giant inside of a mountain, okay. Do we ambush it? Obviously.

Motion to ambush 

PASSES 13-6-1\ps
13 As
6 nays

WE'RE KILLIN THE GIANT! LET'S GO LAURIS FORTUNE FAVORS THE GIANT SLAYERS! We draw our sword and Lauris draws his tiny dumb little daggar. So we ruin our weapons, awesome plan, rocks fall on the giant and giant dies in the debris. Presumably, we should all die too, turns out caveins aren't just... whatever we totally survived. Woo, yay. Makes sense. Hey, six emeralds! Lauris's wife will like one of those? Lauris took half! Okay, he can take them all for his wife if it'll be enough to make him LEAVE.
We carefully get to choose to go left or right. Why is it this book sells itself as we get to make choices but we just keep making random choices between left and right. 

Motion to go left

PASSES 12-6-1\ps

Smooth and well lit corridor. Mocking laughter. Well done, ooh it's crow man! Yaay crowman is back! Lauris is like oh no we should turn back, we want the treasure though for some reason so we're going forward

PASSES 24-0-0\ps

We manage to pul up our big boy britches and go forward. There are coins and stuff. Sparkly treasur woo. It's incredible we have no more breath to talk about how incredible it is. We congragulate Laurus because he wasn't lying, that's a low bar. Speaking of low bars, there's a gate in the way and crosses and diamonds and a wierd keyhole and bunch of statues. Some of the statues are remarkably lifelike and clutching the bars, this couldn't possibly because of the aforementioned basilisk. But we have a key so we're good. Everyone hates dwarves. Wow creepy statues. We're pretty stupid and aren't remembering the...wait...oh....no...Laurus....what if....it was the basilisk! Oh my god, no way! We sob about the people who were weak and stupid enough to get turned into stone. Fortunately Laurus is good at polishing shields, even if he's not good at anything else, and our shields are mirrors. I think we see the basilisk or something and we tell Laurus not to turn around but he does because he's a useless dunce. The magic-user makes a great speech worthy of the Chamber of Secrets. We're scared and stuff. We have a stupid idea though. Does it involve Clo-E? Because if it doesn't it's not going to work. But our mirrors - ahem, shields - turn the basilisk to stone. I guess Clo-E isn't reflective. 

Motion to open the door.

PASSES 23-1-0\ps

23 for
1 nay
0 chickens

Touch lock, earsplitting screech, are we donna die finally? Grr how dare you turn my pet to stone! lihtning is thrown at us, Lauris does something helpful and holds the wizard down. CHLOE STAYS BEHIND AND SAVES US AS WE RUN LIKE COWARDS! Chloe saves us from being turned into centipedes. I really like how Lauris tackles the wizard, and our response isn't to attack the wizard or ask Lauris to let go, but to ATTACK LAURIS. FINALLY, AT THE LEAST CONVENIENT MOMENT. Lauris stole just a tiny bit and we left Clo-E behind. Bad end. 

\goto{Old Business}

\goto{New Business}

\goto{Future Business}
Motion that Clo-E is almost as good as a banana.

Motion Clo-E is a banana seconded

PASSES 1000-4-0\ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
