\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachel Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, February 24, 2017}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection*{hbarcomm} 
Wants to hold another hbarrcomm meeting with McKay.

\subsection*{scrapcomm} 
Continues to happen. We are waiting for new albums. Still lives in CN's bedroom and starchamber shelf.

Motion to move rosfap to annex
26-2-2\ps

\subsection*{Archives}
Brad Verter wants to get together a bunch of archive stuff. Looking at options to give things to him to get things recorded in a proper archive. He would find a proper home for the Assassins Guild stuff, skinner will email out to the High Council for permission to do this. Harvard has a policy of never dissolving Archives, so the records would never be destroyed. Libraries do not have space, MIT museum hasn't gotten back to us yet. He's interested in our unofficial fandom stuff: minutes, tapes, fanzines, fan indexes. Everything will be stated that it is being given away by email before it is removed. Some dubiousness about sending out fanzines. One party or another should keep a copy of minutes.
First going to get approval from the Assassins guild and giving him everything nonphysical.

\subsection*{Seldoncomm}
Will make something happen some time maybe.

\subsection*{Realauthorscomm}
Nina emailed out about it. Hbarrcomm is in contact with libraries because they're bringing a chinese author whose name has a y in it. He wrote something called the paper dragon. It is unclear if it is a story, anthology of stories, or somehting in an anthology of stories, but basically it's cool and he's coming to talk about it. For some reason MIT Libraries doesn't have enough money to make it happen, so they got approval to get related MIT societies to fund it.

\subsection*{Dragoncomm}
Is interested in uploading a spreadsheet of what is in the annex.

\subsection*{Picniccomm}
Will be emailed out to to be created.

\goto{Old Business}
Fredrick Brown's Nightmares and Geezinstacks, long unfindable except in MITSFS's archives, has again gone into print.

\goto{New Business}


\goto{Future Business}
CN is going to a steampunk thing and wants to make a Steampunk escape the room and wants to invite keyholder and library people to be involved. An email will be sent soon.

Bluebellcomm is officially being poked. There are a lot of bluebellcomm things.

Sang Star Trek songs until Skinner ran from room.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
