\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Carissa Skye, President and Skinner}
\newcommand{\onseck}{Rachael Skye, Onseck}
\newcommand{\meetingdate}{Friday, MAY 19, 2017}
\newcommand{\wtv}{WEST TO VALINOR}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

None.

\goto{Old Business}

\subsection*{Complaints}
Rachael would like to lodge a complaint, re: her name is spelled incorrectly in all minutes predating \meetingdate.
Complaint acknowledged

\goto{New Business}

\subsection*{Choose Your Own Adventure}
RW taking over for \onseck, who is too lazy to type out the full adventure.
\subsubsection*{Creating a character}
Our skill is 10.

Our stamina is 22.

Our luck is 10.

We have a sword, leather armor, a shield, 10 provisions, and a lantern.

We also have a magic potion for one of the stats.  We would be sad to run out of luck so we're taking that one.

Prentice XDL is always out of luck.

Supposedly we're also going to have to make notes and draw a map.  I am not drawing a map in \LaTeX.

\subsubsection*{Starting our adventure}
Only a foolhardy adventurer would embark without gathering rumours.  We're super classist but the peasants liked us anyway.  Except they probably were lying to us anyway?

We are going to FIRETOP MOUNTAIN.  The mountain has a TREASURE CHEST with TWO LOCKS, and a WARLOCK of INDETERMINATE AGE.

Blah blah blah goblins, obstacles, regular ferry service, apparently we're really racist against goblins...

We seduced all the women before we left.  \skinner chooses to believe that we're female and bi.

Now turn over.

Something was clawing at the cliff.  At least we think it's a cliff, technically we never found out what it's a face of.

FIRETOP MOUNTAIN is named FIRETOP MOUNTAIN because it has funny-looking plants.

We dramatically sheath our sword, and make our first decision!  West or east?

Motion to go east.
Seconded.
0-8-3\ps

Motion failed. We go west.

We see a sleeping goblin and TEST OUR LUCK.  Rolled 10, so the goblin stays asleep.

There's a door with someone snoring.

Motion to open the door.
Seconded.
8-10-0\ps

Motion failed.  We don't open the door.  TM is sad despite voting against.

Another door!  This time we don't hear anything.  \skinner uses their dictatorial powers to decide we skip it and go north.

A third door!  Hideous singing behind.

Motion to open door.  Seconded.
10-7-0\ps

We have successfully opened a door!

It's pretty gross inside, and there's a box under a table.  There are two drunk goblins, we can either try to kill them or run away.  Diplomacy is not an option.

Motion to attack the goblins.  TM says that they are probably underage and should be punished for drinking.
Seconded.
16-1-2\ps

Oops, they were orcs!  We're totally not racist...

Complicated battle stuff happens.  First orc dies.  Second orc dies.

We wipe our bloodied sword on the mattress.  No, that's not a euphemism.  They smell even worse dead.

The box says 'Farrigo Di Maggio'.  We open the box.  It has a book, titled The Making and Casting of Dragonfire.  Farrigo Di Maggio teaches us the Dragon Fire spell to fight evil dragons.  To keep it from falling into the wrong hands he puts it in a random box in a dungeon.

THE POWER OF DESTRUCTION IS OURS.  But if we misuse it we'll die.  ``EKIL ERIF.  EKAM ERIF.  ERIF ERIF.  Di Maggio.''  Added the spell to our inventory.

3-way junction!  We go west.  Good thing we're totally mapping all of this out.

New door with angry shouting!  Given the possibility that there could be a domestic violence situation going on, it is our duty to investigate.  On the other hand, this book's fights are really slow...

There is an ORC CHIEFTAN with a whip, beating someone else smaller.  It really is a domestic violence situation!

We attack!  The guy he was beating also attacks us...domestic violence is complicated.

With our new streamlined combat system we defeat them handily.  They were just trying to have a private, consensual moment...

But that's okay, because there's a chest!  It's locked but we use BRUTE FORCE to SMASH the LOCK.  It flies several meters away.

There's gold, a potion, a silky black glove, and a dart.  The dart hits us in the stomach.  -3 stamina, 19 remaining.  25 GP, potion of invisibility, and silky black glove (mystery) addded to our inventory.

We still feel weak from the dart, so we stop and eat food.  9 provisions remaining.  +4 stamina, back to 22.  We go west, towards Valinor.

There is a WELL-USED DOOR, with a man inside screaming for help.  Do we interrupt another totally consensual scene, or move on?  Obviously we keep interfering and break down the door.

The hobo inside rushes at us and screams.  We SHOUT at him to CALM him down.  ``YOU ARE FREED, OLD MAN!''  He weeps loudly, as you do.

Many years ago, he was an adventurer like us, then he \strikethrough{took an arrow to the knee} got captured.  Right-hand lever to open the gate at the end of the passage.  Keys to the ferry are guarded by a man and his dog.  +1 luck.

We found another silent door.  We might be going in circles...  Door is locked.  We slam into the door and force it open.  It's a different door!

There's yet another door, this one's metal.  Someone is screaming behind it.  This one isn't locked!  

\onseck takes back the keyboard.
Behind it is a dwarf being tortured by hunchbacked creatures. He dies as soon as we enter.

Initiate matrix vote.
Run away
12-5-2\ps
Fight the dudes
5-13-0\ps
Torture the dead dwarf
17-7-5\ps

Determinant: 283. We run away, down a corridor to a portcullis with two levers. We pull the right one. The door opens. We go through and turn \wtv. To a north-west junction; continue \wtv:||

In a skinny corridor, we hear a maniacal laugh. We are forced to crawl and finally turn back. Turn north at the first junction, then west again. The path turns north, then gives way beneath us. Turn back. Turn north-east. A wild wooden door appears! Go through.

There is a small room with a greybeard inside, and a small winged beast on his shoulder.

Motion to sit down and gamble with him.
7-0.5-3\ps
Motion passed

He offers a wager. We bet 10 gold pieces. He rolls 2, we roll 6 and win.

Update gold piece count: 35 gp.
Update skill: 12
Update stamina: 24
Update luck: 12

We enter a weird tiled room. We walk across, stepping only on the stars. Go through and \wtv.
Go through a passage with a river. We jump in and head downstream. We find ourselves on the south bank of a large cabin. We pay the ferryman to talk us across. He's jacked up the price, and when we protest he mutters about inflation.

Motion to pay him or threaten him.
12-8-2\ps
Motion passes.

Update gp: 32

We make it safely across. There is a smooth mossy cliff. Go northwest, through a wooden door (north) or east. We go through the door. We are knocked senseless.

Update stamina: 22/24

Wake up in a small room with four men with green-gray skin. There are a bunch of weapons around which apparently belong to a distinctive socio-economic strata.
Motion to attack:
4-4-2\ps
Motion fails. We talk to them.

They can't speak. We run away, but fall and are forced to fight.

Update luck: 14

We winnnnnn!!!! They die. Probably their master knows they're dead, by our freaky intuition. There's a scream! We check out the barrels. They have rum.

Update luck: 15
Update stamina: 24/24
Update inventory: add rum barrel.

Cool. Go check out the screaming. We go to a crypt. Investigate coffins. An undead thing comes out. Draw swords! It grabs our blade. Crap. Oh well. We kill it anyway because we are OP af. It's a vampire. Looting time!

Update gp: 63
Update inventory: -fire book, +y-shaped stick, +book
Update luck: 18

Find a crossroads. \wtv.
Find a signpost. It says ''under construction''
Singing comes.  ''Hi-ho, hi-ho, it's off to work we go!''
There are dwarves wooo

Update stamina: 26/26
Update skill: 13/13

Go north.

We're at the top of a narrow staircase leading downwards.  We go down.

Passageway into a chamber stinking of putrefying flesh.  We can search one of the three bodies or keep going.  We try to search number 2, but we kicked 3 and now it's attacking us.  We were lucky and dodged.  What a surprise!

Now we're fighting the ghoul.  We defeat it.  (Cheating tells us that if we lost, it would have sunk its teeth into our rump).  +6 GP, +2 luck, +earrings.
Update luck:  20.

Body 2 has 8 GP, a bottle of liquid, and a piece of parchment.  We ``test'' the liquid.  We start glowing, and feel euphoric and drunk.  It's ogre holy water!

Turns out we really shouldn't have ever gone up above our initial stat levels...too late now.

The parchment has a map of the Maze of Zagor.  Two rooms are marked ...GER and SM...P...LE but we can't read much else.  We climb some stairs and go east.  Something creaks.  The way back is blocked!

Check the walls for secret passages?  Well, since you're asking...

No secret passages.  Something is coming towards us!  It's a ...wandering monster table!  We kill it. \wtv.  Wait, that was the portcullis again.  East.

North-south corridor.  Up the passage, check for secret passages, or south?  We killed the wandering monster table so we might as well check...

Wow, there was one!  This is a complete shock, and clearly didn't have anything to do with one of us looking up a map.

Secret corridor leads to a crossroads.  \wtv.

Dead end.  Go north.  Another crossroads.  Passage \wtv, door north.  \wtv.

Another dead end, we investigate the wall.  No secret passages, but as we press the wall and hear a click.  We're dizzy and faint, teleporting us to somewhere else.

We are back at the crossroads.  South.  3-way junction, cobbled passageway north, west, and east.  \wtv.  Dead end.  Back, and go north.  North-south passageway, door in western wall, passage east, door ahead to the north.  \wtv.

Old man.  Not the gambler this time.  He doesn't recognize us.

Be nice or obnoxious? 12-8-0\ps

He is enraged by our pleasantries.  We pass out again and we're back in the maze.

We head back to the guy, navigating through sheer rage.  We're mean to him and he hides behind his desk.  He is the MAZEMASTER.  He is a WIZARD of SOME POWER.  He tells us where to go.  We listen.  ANOTHER crossroads.  Stupid old man...

We go north.  Again.  There is a door.  We reached the minotaur!  Yay?  We kill him.  +8 GP.  +1 red key marked 111.  +2 luck.  We leave and go back to the crossroads.

\wtv.

Dead end to the north.  No way onwards so we go find that pansy MAZEMASTER again and ignore his advice.  We have a REAL map.

A bunch of identical twisty passages later, we spend HALF AN HOUR trying to find our way out of this dratted maze, even having pulled up TWO DIFFERENT MAPS of the place involved. 

Having dragged this onto the LONGEST MEETING IN LIVING MEMORY, we finally come to a spooky dragon cavern and use the spooky dragon spell after being annoying enough to make the dragon breathe fire.

ELIK ERIF
EMAK ERIF
ERIF ERIF
DI MAGGIO

RS plays We Didn't Start the Fire

No loot dammit it

Door

Small old man - again, this is clearly a retirement center.

Looks harmless, has cards.

We choose to STAB

Old man is not impressed and teleports. His laugh is not feeble, which means he's not old because old people apparently can't laugh. His glaring eyes make us shiver.

We get our invisibility potion.

(Side note to find out what happens if we fight him with the y-shaped stick. It's broken. Rip.)

(Side note: we can also make a cheese pun)

He can see through our invisibility, kind of.

He's sniffing us out.

We beat the warlock because we're op. We seem to have the requisite keys to open his door. There's a big chess. From all around, AND YET FROM NOWHERE, oooooooo, there's thunder. SpoooooOOOOOOooooky. We try to crush the box and there's a lightning. We're lucky. But we don't have the keys so we sit on the chest and weep because we didn't find all the keys.

We declare that we have enough keyholders in the room to justify having keys and turn to the final change. We find riches and also the warlock's spell book. We declare ourselfs the new WARLOCK OF FIRETOP MOUNTAIN.

We win.

\goto{Future Business}

No.

The bannanas declare that the meeting is adjourned

Infinity-0-0\ps
Motion passes.

\bing
\noindent
Meeting adjourned, 73.2 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
