\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachel Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, March 10, 2017}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection*{Picniccomm}
Picniccomm has been formed! Consists of ML and ERG and needs help and poking. First thing to do is to send out doodle for when

\subsection*{Hbarrcomm}
Have a board game coming up on the 18th! Have a few resonses of people saying they will come. 
Also Hbarrcomm has an event during cpw and is being poked fo rit

\subsection*{Niagracomm}
4 Boxes removed from the annex and forced upon an unsuspecting chairity guide. 

\subsection*{Hasslecomm} 
Will have ameeting next friday the 17th around 6:30.

\subsection*{Star Chamber}
We should form a new committee to investigate whether we are actually the world's open stack selection of science fiction and fantasy. Currently operating under the name of Egocomm.

Motion to create Ummaccomm, short for Um, Actually Committee to determine if MITSFS really still has the largest walk in stacks of Science Fiction books. Also known as Egocomm.
Seconded
14-3-3\ps
Passes

\subsection*{Ummaccomm}
Carissa added to head Ummaccomm.
Some library at some university claims to have many more books than we do. Greendex has the number of books we have, we have 1.7 books per title because we have two copies of most things but not everything. 

\goto{Old Business}
Phillip K Dick and Piers Anthony still not dead.
Carissa added someone to our contract so we can get a two for one deal on killing Piers Anthony and some other terrible author.

\goto{New Business}
Greatest Author of the 22nd Century was born yesterday! MITSFS
Mailing lists will be created for ummaccomm, umactuallycomm, and egocomm.


\goto{Future Business}
Questions:
None

Comments:
In the future there will be new synthetic versions of bananas different from what we recognize. 

Move to recognize GMO bananas as bananas in the event of the death of the cavendish banana.
seconded
12-1-3\ps
Motion Passes


\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
