\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachael Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, April 21, 2017}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 62.3 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection*{Hbarcomm}
Hbarcomm was a huge success over cpw! One prefrosh even called us crazy. Propose do the same next year. Dumped multiple boxes of niagracomm on prefrosh and it was great.
Proposal that Hbarcomm hold events during rex? Seldoncomm is poked to make this happen. 

\subsection*{Picniccomm}
Picniccomm is having picniccomm Sunday.

\subsection*{Umaccomm}
Egocomm thinks we're probably still the largest library, the difference lying in collections including various non books when they list their items, such as newspaper clippings and such. 


\goto{Old Business}
Got new keholders this year! 6 new people! Kelsey, Michaye, Eleanor, Ryan, Benjamin, and Eileen.

\goto{New Business}
Elections!

\subsection*{Onseck}
The shark (which shark is defined by which definite article you are using)
Punctuality
Rachel Skye (RS)
A typewriter
Dvorak keyboard

The abstract concept of punctuality would be the best onseck. Be there at every meeting, on time, ready, on time. 

Rachel Skye uses her power as Skinner to declare she would be best Onseck.

The dvorak keyboard (no) the dvorak keyboard (no) I believe that is all there is to say.

Dvorak keyboard wins by 100 votes
The shark in absensia with 2 and a half votes
Rachel with 2 and 1/3 of a vote
Punctuality with 1 vote

\subsection*{LHE}
Nominate Saturn
Nominate Tristan McLaurin (TM) with 4.5 votes
1 Second
Large Happy Eraser

Tristan
Eraser
Time Saturn

\subsection*{Vice}
Kelsey Glover
The Door to Mitsfs
Sloth
Greed
Wanky Email threads
flame wars where people exchange notes in long scripts

Keysey wins with 2.7 votes and a typewritter outside of mitsfs' door
Sloth is vice if Kelsey cannot be found

\subsection*{President}
Obama
Nicole
Carissa Skye (CS)
Sauron
Large Fluffy Lazy Sleepy Old Koala
Giant flaming Meteor of death
The Candidate Who is About to be Nominated

Carissa wins by a margin of $|{e^{5t}*\cos(3t)}}|$

President Declares Carissa Skye as Skinner

Motion no one is allowed to ask if Nicole wants to be president until next election
PASSES
10-2-2\ps



\goto{Future Business}
No one will be able to ask Nicole when going around next year asking who wants to be who

Motion to have bananas at the picnic
GuysImGonnaMissThis-ItsBeenAPleasureServingYou-TristanOUT\ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
