\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Rachel Skye, President and Skinner}
\newcommand{\onseck}{Tristan McLaurin, Onseck}
\newcommand{\meetingdate}{Friday, February 10, 2017}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection*{hbarrcomm}
A professor is running a class on world creation and literature and so if you're interested it is 21L-something, 
MIT libraries are impressed by how many books we have
Submitted an event for CPW, reading a choose your own adventure book.

\subsection*{Niagracomm}
We have no more niagracomm! It's really great, they have all the boxes and now all that's left are...

\subsection*{Hasslecomm}
...Only 12 more boxes of hasslecomm! Lots of Prattchet.

\subsection*{Mobcomm}
Just got a new shipment of books!

\subsection*{Dragoncomm}
Annex has basically been completely cleared out with exception of filing cabinets

\subsection*{Mommycomm}
Mommycomm still does not have any hours from Inventory...

\subsection*{Picniccomm}
Stores in Sommerville carry coconuts. Picniccomm will be formed probably early March.

\goto{Old Business}

\goto{New Business}
Brad Verter is putting together a collection of boston area archival material so we need to decide him what we want to give him. He expressed interest in Assassins things, fanzines, old minutes, all archival materials. There are many things in our library we should decide whether we want to give to him or if we want to keep it. If we want to keep it, we should decide why. We won't give anything to them without thinking about it, and an email will be sent out asking about things people think we should repeat. Doesn't want anything that was commercially distributed. 
No opinions, questions, or concerns.

\goto{Future Business}
Time flies like an arrow. Fruit flies like a banana.

Motion that we hire a banana assassin to go out and kill Piers Anthony with frozen bananas
Seconded

18-13-1\ps

Motion Passes

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
