\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 7, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Minutes lame.

\goto{Committee Reports}

Ex-pseudo-onseck Toby claims pride at past office.

\goto{Old Business}

General apathy.

\goto{New Business}

Motion to commend Jay for keeping meeting going. Passes more-less-some +Spehn.

Motion to have more bings. Passes by unanimous decree.

M: commend Jen for attending. 66-0-3 +Spehn.

Motion to replace gavel block with camera. (Kevin taking Technique photos.) Hell of a lot-none-none +Spehn.

\goto{Future Business}

Motion to have Jay bing. Fails. \bing

Motion to have gavel block replaced with camera. Passes 11-7-5 +Spehn.

Motion to have all members donate good stuff to Twilight Zine. Dies and chickens 0-1-2 +Spehn.

\goto{Post-Future Business}

M: commend EK and JPM for getting bookshelves. 20-0-0 +Spehn.

M: call bing a banana. 16-4-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
