\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 11, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to strike non-existing Star Wars quotes from minutes. Fails.

TE: "If you strike it down, it will become more powerful than you can possibly imagine."

M: commend onseck for accurate description of Star Wars quotes. Passes 12- -  +Spehn.

\goto{Committee Reports}

Jourcomm: today is the day.

Jamie: "Steven Bergauer is desperate."

Dexmistress: dex will be in perl (don't give Toby write access).

Moocomm: Wizard of Speed and Time at Harvard May 7 and 9.

Strap. Fails 0-hell-2 less +Spehn.

No dying. Passes lots-1-2 +Spehn.

Motion to keep diseases limited to unbedridden. Passes 15-1-5 +Spehn.

Martin enters.

\goto{Old Business}

Bings can be heard in stairwell.

Motion to keep meeting to correct minutes. Fails by skinnerial decree.

M: kill future business. Passes 13-0-3 +Spehn.

Asimov still dead. Asimov continuing dead. Piers Anthony not dead.

\goto{New Business}

Algol.

M: I didn't notice New Business. Passes 15-4-0 +Spehn.

\goto{Old Business}

Algol.

\goto{New Business}

JM: leaving grad school, doing computer work for money, "even if I embezzled money from MITSFS I couldn't make enough to live."

Hi prefrosh.

Jen was last previous prefrosh.

Motion to commend Wizards of the Coast for buying TSR. Passes 19-0-1 +Spehn.

Long discussion of The Strategic Review (TSR).

Miller motion. Fails.

2nd Miller motion. Passes 13-6-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
