\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 24, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Murphy, Pseudo-Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: approve minutes as unrehearsed. 3-0-6 +Spehn.

\goto{Committee Reports}

Jourcomm: 1 week. Just 1 week. Give us stuff, please!

Bluebellcomm: 3 new books ready to be read and reviewed.

Sitcomm: Timecop still sucks.

Sitcomm2: Timecop is cancelled.

Dexmistress: Dexmaster mostly converted into Perl.

Pseudo-moocomm: Gattaca- except that it was Wednesday. "A science fiction picture that isn't blatantly insulting." (Ed's friend)

\goto{Old Business}

There was a [illegible] of Gattaca.

The ceiling is still dripping.

We're still running out of space, but now we have charts!

M: commend PhysPlant for hitting the motherload. 10-4-1 +Spehn (against law of nature). "Now if only we could get them to pay us to mine it."

Discussion of storm door, other problems (doorjamb, leak in back near air conditioner, phone equipment change).

Jamie goes, with screwdriver, to storm door to see if he can open it up and replace the battery. (Screwdriver idea from WDS...)

\goto{New Business}

M: have skinner replace her neck. Fails by skinnerial decree (and lack of second). "A preemptive failure."

Computer center?

Pause: turn gavel block over (to hide what Jamie noted looked like bird shit but was actually Tech bits from J).

5 celebratory bings. "And all's well!" (Eric)

\goto{Future Business}

What, not even going to wait for us to make a banana motion? 18-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}