\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 7, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

M: to put down revolution. Passes.

Minutes read.

M: condemn skinner for putting down revolution. Passes Hell-0-0 +Spehn.

\goto{Committee Reports}

M: suppress Jamie for being clever. Passes 19-0-1 +Spehn.

Jourcomm: submit.

Pianocomm: Jenwa started project.

\goto{Old Business}

Sounds like Jamie, Martin, Toby.

TE: "Are we playing sounds like games again?"

Simon says submit to Jourcomm. Chickens 0-0-0 +Spehn.

M: not to do anything unless preceded by Skinner Says. Somethings not-not-not +Spehn.

\goto{New Business}

I'm Akiko.

M: to attach Akiko and Gabriel with umbilical cord. Fails 10-12-2 +Spehn.

Jamie to ACH: "She does that scrunchy thing with her mouth."

Yayayayayaha (Jamie laughing). Passes by skinnerial decree.

\goto{Future Business}

Jay: "Sorry, I can't hear you, I have a gavel in my ear."

Banana (from Jen telling knock-knock joke). 4-2-1 +Spehn.

Condemn Jen for telling banana knock-knock joke. Passes 0dear-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1700 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ninja Drag Queens from the Planet Zeist}

\end{document}
