\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 31, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Minutes read.

M: minutes incomprehensible. 9-2-3 +Spehn.

\goto{Committee Reports}

Sitcomm: last Timecop episode preempted by speculator report re: stock drop.

Pseudo-jourcomm: this is it.

Sitcomm2: Sunday: season premier of X-Files, plus part one of four of House of Frankenstein.

\goto{Old Business}

Today is Bill's 40th birthday.

M: sing happy birthday to Bill. Passes by skinnerial decree despite objections.

M: commend Bill for being born on Samhain. Fails, insufficient pagans.

Jen's trying to track down elusive CAC guy to fix ceiling.

\goto{New Business}

Aaron might want to be a keyholder.

Tor has rereleased Crown of Swords. Bill misheard as Chronosources.

\goto{Future Business}

Next Friday, Starship Troopers premieres. (Vaguely based on Heinlein novel.) Likely good stupid action movie.

M: commend appropriate deity for not putting RAH in name. 12-2-1 +Spehn.

M: execute people who vote for failing motions or against passing motions, resulting in consensus. Fails for lack of a second (just a "save").

Deutch talked about CIA, but not alien coverup.

Alien: Resurrection out soon.

Alien III like ST I: good movie hidden.

M: nuke Alien from orbit. Passes 12-4-1 +Spehn (predeclared).

\vspace{12pt}

\noindent
Meeting adjourned, 1708 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}