\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Banana-Colored Meeting Minutes 

Friday, September 26, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Murphy, Pseudo-Skinner, presiding; William D. Starr, Pseudo-Onseck, recording.

Minutes of previous meeting read by pseudo-onseck WDS, who noted that they don't say that the previous meeting was ever actually adjourned.

Motion to approve the minutes as adjourned. Chickens 4-1-4 +Spehn.

\goto{Committee Reports}

Jourcomm (Jen Murphy in her alternate identity): deadline for Twilight Zine submissions is October 31st. There is going to be an issue, even though just about all they've got so far is some poetry and a bad twenty-page vampires-in-space story. Some guy emailed us at our web page and he's going to be doing the cover art and some interior illustrations.

Sitcomm (WDS): Timecop sucks.

Sitcomm2 (WDS): The Visitor sucks too.

\goto{Old Business}

Martin reports that he is old.

\goto{New Business}

The new bookcase is shelved; now it just has to get moved to someplace useful.

This leads to a discussion of the Bobcat monitors on top of the bookcases since the new bookcase isn't the same height as the one that it'll be back-to-back with- won't this lead to the monitor not being stable atop same and therefore not able to carry out its prime function, to wit, anchoring plastic sheets when the roof inevitably leaks again? This leads to an "Alas!" which is seconded and passes 3-0-1 +Spehn. Toby tries to convince us that the monitors' prime function is actually to monitor us and that contrary to appearances they're all on right now. Everybody pretends not to believe him.

(Long silence.)

\goto{Future Business}

(Another long silence.)

Discussion of whether skinner or pseudo-skinner can arbitrarily adjourn a meeting; suggestion is made that as long as the skinner hears the Adjournment Song in her head, she can adjourn the meeting regardless of whether anyone else hears it. Theory is saved from being tested when WDS points out that there's no lower limit on how much of the Adjournment Song has to be sung before the skinner can adjourn the meeting and then sings the single word "rabbits."

\vspace{12pt}

\noindent
Meeting adjourned, 1707 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{William D. Starr, Pseudo-Onseck}

\end{document}