\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 29, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Murphy, LHE and Pseudo-Skinner, presiding; Jamie Morris, Pseudo-Onseck, recording.

Minutes read.

Move to approve the minutes as nasty, brutish, and short. Passes 7-4-2 +Spehn.

Motion to condemn the Onseck for not being here now that she's back. Passes 8-5-4 +Spehn.

\goto{Committee Reports}

Pseudo-fweekcomm reports rush for us is sorta slow, hopefully the Drop Poster will help.

Jourcomm reports not even close to rush.

\goto{Old Business}

Motion to get rid of Toby's blood and replace it with a frosh's blood. Passes 10-3-8 +Spehn.

Motion to allow line-item veto votes. Fails by confused pseudo-skinnerial decree.

Motion to unconfuse the pseudo-skinner. Chickens 0-less-7 +Spehn.

\goto{New Business}

What happened to the Algol?

The AC is faster! Lots!

Motion to replace the AC with a space station with money out of Toby's pocket. Passes 20-0-6 +Spehn.

The skinnerial tendency to have a two-item stack is noted.

\goto{Future Business}

Miller motion fails.

Second Miller motion fails.

Miller motion with bananas on top fails for lack of a second.

Singing Miller motion with bananas on top passes 14-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jamie Morris, Pseudo-Onseck}

\end{document}