\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 25, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
J Mchnj Prsdnt nd Sknnr prsdng.

Mnts rd.

Bng nsck fr bd rdng f mnts. Psss 8-2-6 +Sphn.

\goto{Cmt Rprts}

Jrcmm: sbmt, ddln nxt wk.

M-prnts-drggd-m-t-stpd-sght-cm: 294 stps to Bnkr Hll nt wrth th vw.

Mntn f Rl Bsnss nd Mny.

\goto{ld Bsnss}

Ctlgng f Cmbll stff frmth lprt lprt.

\goto{Nw Bsnss}

Gld Mtng n Sndy.

Mr rl bsnss bt mny.

\goto{Ftr Bsnss}

Mv t strk ll vwls frm th mnts. Pssd 13-1-2 +Sphn.

Mtn t Stp n Sknnr's hd. Chckns 0-0-4 +Sphn.

Wrp tht thng n cshn. Psss Lts-Mny-1 +Sphn.

Wrp t n bnn pl. Psss.

\vspace{12pt}

\noindent

Mtng adjrnd.

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Unofficial Meeting Minutes 

Friday, April 25, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Jay Muchnij, President and Skinner presiding.

Minutes read.

Booing onseck for bad reading of minutes. Passes 8-2-6 +Spehn.

\goto{Committee Reports}

Jourcomm: submit, deadline next week.

My-parents-dragged-me-to-stupid-sight-comm: 294 steps to Bunker Hill not worth the view.

Mention of real business and money.

\goto{Old Business}

Cataloging of Cambell stuff from the Alpert.

\goto{New Business}

Guild meeting on Sunday.

More real business about money.

\goto{Future Business}

Move to strike all vowels from the minutes. Passes 13-1-2 +Spehn.

Motion to step on skinner's head. Chickens 0-0-4 +Spehn.

Wrap that thing in a cushion. Lots-money-1 +Spehn.

Wrap it in a banana peel. Passes.

\vspace{12pt}

\noindent

Meeting adjourned.

\end{document}
