\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 12, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: more or less commend the onseck for more or less reading the minutes more or less enthusiastically. 17-1-2 +Spehn.

\goto{Committee Reports}

Jourcomm: please submit stuff. Really.

\goto{Old Business}

Jamie: "I'm 25 today."

M: commend Jamie for being older than Toby. 13-3-8 +Spehn. Toby: "I'm too old to care."

M: commend Erin for being young at heart. Something-very few-9 +Spehn. "Damn, I don't know what this motion does."

\goto{New Business}

"Usual motion."

\goto{Time Warp to Old Business}

Usual vote, usual result.

\goto{New (Moderately) Business}

We have a new shelf with shelving.

Bright red metal bookshelf. Want? Yes.

The SF speakers flyer.

\goto{New Business}

M: Jourcomm, go to that thing and get everyone there to write something for the Twilight Zine. 8-0-6 +Spehn.

M: no! Invite them all to the picnic. 15-0-5 +Spehn.

M: oooooh. Something piddly-something piddly-15 +Spehn.

M: commend Jamie for making lewd gestures with his fingers. Passes by Skinnerial decree.

M: commend the Vice (on general principles). 8-5-9 +Spehn.

Erin gives Jamie a broom (because she was instructed by the skinner to give him something embarassing).

\goto{Future Business}

M: to all be doomed. Motion fails. Doom is hereby banned from the library (only Quake, Duke Nukem, etc. allowed).

M: to be shocked at Erin for having lewd thoughts. Some number not all that big, like tennish-infinity-er, something +Spehn.

"Skinner has no thoughts at all, his head's just empty space." Died after one verse!

M: to get the red bookshelves that Arun discovered and paint them banana colored. 27-0-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}