\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 16, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: approve new onseck's taking of minutes as a good omen (or something like that). Passes 16-0-0 +Spehn.

\goto{Committee Reports}

Volunteers for Aloha Lenscomm- Erin agrees.

\goto{Old Business}

Jen and Eddy walk in late.

\goto{New Business}

Elections.

Jen is Vanna. J summarizes election process. Pens distributed. Potential for abuse pointed out.

M: J to pass donut holes. Passes by skinnerial decree.

Nominations for President:

"Not me" by Karol. "This donut hole thing" by Justin (later half eaten). "What was this office again?" "This donette" by Jen.

Split pastry vote! Oh no!

Marcus (by Erin). The guy, etc. "The oldest orange dot sticker in the library" by Justin.

Nominations closed, official candidate being "Not me." J claims his being the official candidate for candidate is self-evident.

Discussion: fractions vs. irrationals vs. the 2 decimal place rule.

J (1 vote for Not me). J, etc.: .98. Not me: pi - e. This donette: 1 + e - pi. The wall Jen ran into: 1. Something too confusing. Something else too confusing. Something else something too confusing.

J: epsilon. The donette: 1 - epsilon. Something else too confusing. Yet another too confusing vote.

"Sorry, my head twinged." (Jen, in response to J whistling)

Not me (J): 4. The donut hole thing: .92. The donette: 1.66. Marcus: .2. The guy, etc.: .2. Orange dot: .25. The wall: 1. Various B5-related things: 1.3. Not a majority. Vote again.

The votes are read and counted. I refuse to enumerate. (2 or 3 votes counted for being >1.)

Marcus with interesting things done to him and then brought to Jamie's tent: vote (well, some percent).

M: all future votes be normalized. Fails.

The President is J, with 8.99 votes. The donut hole is runner-up. President appoints himself Skinner.

Nominations for Vice:

Erin is the official candidate. Monty Python. Greed. Green. Sloth. ESMER (evil sadistic Machiavellian egomaniacal redhead). Dad spelling. Angel. Erin's spelling? Impact-resistant watermelon.

J closes the nominations.

Votes read and counted in a complicated manner; reverse Jamie and Marcus vote, Jen discounts a vote for too many decimal places.

Erin 2.31, Greed .82, flying [illegible] 1.99, ESMER 1.15, watermelon 1.1, greed .8? (something like that), green .2, bad spelling [illegible] each, greed .2, sloth .1.

Next vote. Votes read and counted (yawn). Lots of versions of redheads. .4 arithmetic sequences =). 1 "for Erin who needs more vice in her warm and fuzzy life." Erin 5.41, assorted food items 1.48.

Nominations for LHE:

Jen is the official candidate. The milk. The wall. Wall of milk. Milky Way. Short nominations. People who sit next to me in [illegible] morning classes. Jen's concussion.

Nominations closed.

Cute and harmful .3, Pink Floyd .3, various parts of room, galaxies in general and in specific. We think the wall will probably win... "It gives the answer the LHE wants." (What the calculation does by definition.)

The wall 7.86 (the majority), Jen 3.81, Eddy 1.85, Susan Bora .02.

"I think the wall is Jen." (Jamie)

"It doesn't like people talking about it in that way." (Jen, on milk)

Next vote. Random samplings. Reverse Polish [illegible]. One way streets: .2. Jen... taken to the Med Center to be treated.

Andres' Jedi mind tricks work on Jen. 7.57 Jen (me!), others with 31 (3.1? maybe?) and with 1.15.

Nominations for Onseck:

The pseudo-onseck is the official candidate. The ghost of Onsex past. Longest horned person in the room. Second. The youngest female in the room. The female frosh. Zog. Zuul. Zathrios. Zort. Aloha Lenscomm. A suffusion of yellow. Twat. The person whose first initial is J. The wall.

Votes read and counted. .12 hair, .14 Z, .11 Miller, 1 Eddy (as a punishment for bad B5 quotes).

Random aside: (boing)

...

(Boing)(boing)(boing)(boing)(boing)

Jenwa 3.32, the wall 1.83, B5 1.3, Eddy 1, second .8, other .75, yellow .67, ET .13.

Votes read and counted. Jenwa, washed, dried, fed, and given a good book; .1 no toad-onsexing; .5 Jenwall. "Zathrios counts for zero." [Drawing of a stick figure]

Jenwa 7.59, other 1.5, the wall .4, Jamie and Eddy .27.

Elections concluded.

\goto{Future Business}

M: nail Eddy's foot to the floor so he has to stay here until next time and give his vote then. Passes unanimously save Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
