\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 28, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: approve the minutes as kiwi-colored. Passes 12-3-4 +Spehn.

\goto{Committee Reports}

Moocomm: Justin reports that Starship Troopers is extremely good and closely follows the Heinlein book.

Moocomm2: Sam says Alien: Resurrection sucks. Not enough combat and gore.

Jourcomm: Submit! RFSN, we promise!

\goto{New Business}

M: Marcus to take off his shirt and swing the gavel "for old times' sake." Passes 18-3-12 +Spehn.

M: annual affirmation that you can get anything you want at Alice's Restaurant. Fails 3-12-4 +Spehn.

M: commend this meeting for unparalleled efficiency. Chickens 3-8-17 +Spehn.

Erin models for a Boris calendar.

M: commend Erin for going to such lengths to get MITSFS a calendar. Passes 18-3-5 +Spehn.

\goto{Old Business}

Everyone claims to be old. Bill wins argument. Marcus sulks.

Andrea, as is tradition, insults the skinner.

Ed promises to finish the alum mailing list "RSN, as soon as the TZ gets published (snicker)."

Jen is sick.

M: condemn Ed for promising to never get his key. Passes 23-0-1 +Spehn.

M: commend Martin for eating a banana in the library. Fails 10-11-9 +Spehn.

M: sell off onseck and replace with v3.2 of Microsoft Jenwa. Chickens 5-10-10 +Spehn.

\goto{Future Business}

M: commend Jamie for showing off his banana-colored underwear. Passes 23-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1723 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}