\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 7, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read, stiltingly.

M: move last week's minutes to this week's minutes so the onseck could take the last week off. 8-7-7 +Spehn.

\goto{Committee Reports}

Jourcomm: it's getting put together this weekend.

LHE: more tiles on the ceiling.

Addendum report: need different desk.

\goto{Old Business}

What are we doing to Eddy today? What alterations to his vision are we making with Elmer's glue- pentestone on forehead.

M: to declare Eddy an un-self-respecting alien species. 9-7-3 +Spehn.

\goto{New Business}

M: commend skinner for great picture in the Tech. "Fails for lack of a second." (J didn't hear Arun's second.)

Discussion of 2-tube epoxy.

"We'd like to introduce ourselves." (Michele and Tamara, Smith SFS) Passes by unanimous decree.

Apathy motion. Second. Dies for a second.

M: "your brain's getting stuck in the glue." Something-10-2 +Spehn.

(Cough, hack) 0-something-8 +Spehn.

M: for more people to come introduce themselves and giggle. 10-1-2 +Spehn.

\goto{Future Business}

M: to eventually get rid of the Tech. 24-1-2 +Spehn.

M: to replace it with a banana. 25-0-9 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}