\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 3, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Last week's minutes not read (not found).

M: move this week's minutes into last week to preserve continuity of the minutes. 9-9-4 +Spehn.

\goto{Committee Reports}

Moocomm: MIB tonight but Mark of Zorro has more science fiction content.

M: commend the skinner for talking to his gavel. 8-0-6 +Spehn.

M: to have the skinner stick a banana in his ear while listening to Slayer. 0-2-2 +Spehn.

M: apply the inverse skinner rule. Something big-something small-5 +Spehn.

\goto{Old Business}

None.

\goto{New Business}

M: have the Society take a new policy towards alcohol. 14-1-0 +Spehn.

M: prohibit prentices from dying in the library. 6-2-6 +Spehn.

\goto{Future Business}

M: clone this meeting and send it to both meetings. 7-4-1 +Spehn.

M: censure meeting... something about sex with gavels. 3-12-5 +Spehn.

M: finger motion. 6-0-0 +Spehn.

Miller motion. 8-12-1 +Spehn.

M: deprive onseck of her nose. 11-4-1 +Spehn.

M: implement the onseck's nose by means of a banana. 12-2-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}