\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 14, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Pseudo-Onseck, recording.

Minutes read.

M: condemn last week's onseck. Fails for lack of second.

M: commend last week's onseck. Passes 7-0-2 +Spehn.

M: commend Jen for being sick. Fails for lack of second.

M: condemn Jen for being sick. Fails for lack of second.

\goto{Committee Reports}

Jourcomm: no one's listening to Jen.

M: dead LHE? 12th? Passes 12-0-1 +Spehn.

\goto{Old Business}

Time warps (many).

M: stop going forward for a while. Fails, lack of second.

Lingering motion?

Pending motion?

Time warp to several meetings ago when there was a pending motion.

M: postpone pending motion until next week. Passes by skinnerial decree.

Time warp back to today.

"Where are the comic books?" "Probably so old we forgot about it already."

\goto{New Business}

Odyssey is read by Jay in a silly deep voice.

M: attach Jamie's ? to the minutes. Chickens 3-0-3 +Spehn.

Time warp to Committee Reports. Apathycomm says yay. Time warp back.

Jamie bitches about money.

\goto{Future Business}

M: make sure there's current business next week. Chickens 4-1-4 +Spehn.

Someone walks in late.

M: "review books," Jen commands. Chickens 2-1-4 +Spehn.

M: for Jen to crawl home. Chickens 2-2-2 +Spehn.

M: declare titanium block banana colored. Chickens 3-2-hell of a lot +Spehn.

M: instruct Jamie to point it (MIT in buildings) out.

M: have Jen tell Jay to end meeting. Passes by Jen coughing.

M: have Jen eat lots of bananas to get well. Fails, lack of second.

\goto{Post-Future Business}

M: put Jen out of her misery. Chickens 4-0-6 +Spehn.

M: kill all people chickening banana motions. 10-8-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST. "Less apathetic than I thought it would be." (Jay)

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
