\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 1, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Ben Wieland, Pseudo-Onseck, recording.

Minutes read.

Motion to commend Pseudo-Onseck for being able to read minutes. 17-?-? +Spehn.

\goto{Committee Reports}

Panthercomm: inventory.

Pianocomm: new apprentice.

Discussion of Algol.

No Bluebell backlog for first time in 1.5 years.

Moocomm: all should see Arcadia.

Other Bluebellcomm sad: has to do other work.

Motion to say "Aww" to Bluebellcomm. 15-0-1 +Spehn. "Aww."

\goto{Old Business}

"Ow."

Bings going well; table collapsing.

Books mailed (paid for last week).

Jen is no longer involved in either CCC.

Eddie sends Necronomicon info to Roger.

The comic books are in California.

\goto{Time Warp to Committee Reports}

Pseudo-apathycomm: pseudo-apathy going strong.

\goto{Time Warp to Old Business}

Asimov is still dead. Still producing books like Heinlein, Hubbard.

Usual motion, etc.

\goto{New Business}

If we got a net drop, we might get a nice computer.

LPS: Library Positioning System.

\goto{Future Business}

Motion to declare all members banana-colored. 1 English Buttload-4-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ben Wieland, Pseudo-Onseck}

\end{document}