\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 28, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

\goto{Committee Reports}

We have new books, they have been processed.

Jourcomm: submit now.

\goto{Old Business}

M: Jamie mailed his sister his christmas present today. 0-5-12 +Spehn.

\goto{New Business}

Pending motion mentioned.

M: change pending motion to a pendulum motion. Fails for lack of second.

M: to defer all pending motion until next week. Fails for lack of second.

M: to delay all pending motions until next week. Fails 5-8-0 +Spehn.

\goto{Future Business}

Apathycomm happy.

M: commend 3 people who've already written stuff for Jourcomm as "visionaries of the future." 4-0-4 +Spehn.

M: give Toby a bad name (T: "too late."). 16-0-0 +Spehn. Motion fails because it's already been done.

\goto{Recursive Business}

M: ? 5-0-0 +Spehn.

M: condemn Jay for missing a bing. Passes 7-0-2 +Spehn.

\goto{Iterative Motions}

2nd Miller motion. 6-2-5 +Spehn. Motion doesn't do anything at all.

1st Miller motion. Fails for lack of second.

0th Miller motion. Fails for lack of second.

Miller motion. 2nd. 12-0-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST. (T to Jay: "we didn't even get A tome you're so confused.")

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
