\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 14, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: "to just give up on the minutes." 6-8-5 +Spehn.

M: turn the minutes into hours. 8-8-1 +Spehn.

\goto{Committee Reports}

The Observer is not quite as effective at stopping bings as the Tech.

Pseudo-jourcomm:

Ocomm: we should deny membership to anyone from NY because a high percentage owe us money.

M: repossess NY. 14-0-0 +Spehn.

\goto{Old Business}

The Tech and Observer worked quite well.

Need Pillowcomm, to provide pillow for the gavel.

M: appoint someone to rub the skinner's gavel. 2-2-16 +Spehn.

\goto{New Business}

"Oh no, the Tech and the Observer are becoming intertwined!"

M: instruct skinner to rub his own gavel. 1-1-9 +Spehn.

"I can neither confirm nor deny we are in Classified Business right now."

M: "whatever they said in the back corner." 6-Eddy-0 +Spehn.

M: move library to non-linear time. 4-6-1 +Spehn.

Penn and Teller will be on B5.

M: commend Jamie for having a pickle for breakfast. Something-6-1 +Spehn (passes).

M: commend the pickle instead. 6-1-2 +Spehn.

M: "we're in a pickle now." 5-4-1 +Spehn.

\goto{Pickle Business}

M: change official mascot from banana to pickle. Lot-not a few-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}