\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 4, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to second. Passes 7-3-5 +Spehn.

\goto{Committee Reports}

Jourcomm: deadline next week.

Picniccomm: more keys.

Motion to commend ARM for lateness. Passes 16-3-7 +Spehn.

\goto{Old Business}

Martin: that's me.

Lack of second from lack of understanding. Nothings ?-9-8 +Spehn.

Motion to abolish seconds. Fails 9-12-4 +Spehn.

Motion to fail all future motions. Passes 16-6-2 +Spehn.

Miller Motion. Fails.

Second Miller Motion. Fails.

\goto{Future Business}

Time warp to New Business.

\goto{New Business}

Chickens 4-1-more +Spehn.

Complaint of motion chickening.

Only future motions skipped.

Warp to skip New Business.

Reenacting Neel's Battle. Chickens Something.

\goto{Future Business}

\goto{Recursive Business}

Motion to curse. Passes 13-3-4 +Spehn.

Cries of damn, phooey, and aw geez.

Motion to bing. Passes. \bing

Motion not to bing. Passes 19-0-2 +Spehn. No bing, motion does not exist.

Frivolous damaging of eardrums ensues.

Invoking the inverse skinner rule. Nothings.

Condemning the inverse skinner. Fails.

Coup happens. Jen takes the gavel. Lame Star Wars quotes ensue at result of obtaining reserve book room. Violence narrowly avoided.

Motion to have matrix vote. Passes.

Inverting you + Star Wars quote + inverting inversion = 4.

Motion to commend Pentiumcomm for predicting the result. Passes unanimously.

Iterative motions.

Leave J's virtue alone. Chickens 0-2-hell of a lot +Spehn.

No altering of J's virtue in the library. Passes.

Virtuous acts with a banana. Passes Hell-1-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
