\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 10, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: to censor the skinner for his binging. 17-0-1 +Spehn.

M: who knows. 18-0-2 +Spehn.

\goto{Committee Reports}

Jourcomm: deadline October 31st. We WILL publish.

Sitcomm: "Timecop still sucks. I don't know why I'm still watching it." (WDS) "Starring John Travolta (and Nicholas Cage) as Hamlet." (Justin)

M: all committees go to [illegible]. 2-12-8 +Spehn.

\goto{Old Business}

M: to prevent Jen from speaking. 12-19-1 +Spehn.

M: condemn [illegible] for spending 200 dollars a week on pizza (cost of 2 TZ publications). Unanimous-0-0 +Spehn.

M: investigate how much it would cost to produce the TZ on pizzas. 4-12-1 +Spehn.

\goto{New Business}

33 months- library will explode.

Minimally ADA compliant.

Wednesday lecture- Haldeman and Gregory Benford and someone else.

M: condemn Jen for not being apathetic enough. Buttload-0-2 +Spehn.

M: ? Chickens 8-7-8 +Spehn.

Miller motion. Second. Fails.

Anti-bing motion. Passes by skinnerial decree.

\goto{Future Business}

Everything passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}