\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 5, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read. J had fun last week.

M: to commend the minutes as more accurate. 21-0-1 +Spehn.

\goto{Committee Reports}

Pseudo-mobcomm: new books Sunday.

Jourcomm says: Soon! (Eddy: "Maybe by Rush!")

M: take pity on poor Jourcomm. 27-1-3 +Spehn.

"Someone want to explain to me the rant about the chickens?" "No!"

Finger motion!

\goto{New Business}

M: say hi to the new person. 25-0-0 +Spehn.

\goto{Old Business}

Jamie's mind is going! Passes by skinnerial decree.

Lecture yesterday. Martin got one of them to come (in the library?).

M: condemn purple polka dots for sucking. Whatever the hell-5-? +Spehn. Chickens.

\goto{New Business}

Reserve room rearranged.

ASA walkthroughs Monday. 4-6 PM. Inspection of fire code, ADA, offices (including guild office).

M: take pity on visiting author and suspend the gavel ringing for rest of meeting. Passes by skinnerial decree.

M: commend for damping. Something-small number-0 +Spehn.

\goto{Future Business}

M: commend Alexandra for sitting on the banana colored couch with banana colored hair. 11-12-4 +Spehn.

Miller motion. Second. Fails.

Second Miller motion. 19-2-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}