\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 2, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Eei ae o oe 17:00.

eii.

iue ea.

oio o ie a ooa. a 15-4-1 +e.

\goto{oiee eo}

Ouo: eaie e ee.

Aa.

\goto{O uie}

Ouo eaie oeie.

A.

A.

Ooeei oio o e ee. ae 11-5-3 +e.

Oio o ae ue eieua a:1. ae 16-0-0 +e.

Oio o a.

\goto{e uie}

Aiieo ae o. ae 9-3-4 +e.

Uii o eiiio o o oo.

Oaiiie a ii o oo.

Ee ee: aaa oio. ai 7-9-5 +e.

Oio O a eii aaa ooe. Aie 5-e-* +e.

oio o eoaie a eiou oio.

Ai o aiui.

Oio a a oio ai.

Ie o a eo.

\goto{uue uie}

Oio o a a oio. ae 16-8-10 +e.

\vspace{12pt}

\noindent
eei Aoue.

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Unofficial Meeting Minutes 

Friday, May 2, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to strike all consonants. Passes 15-4-1 +Spehn.

\goto{Committee Reports}

Jourcomm: deadline next week.

Apathy.

\goto{Old Business}

Jourcomm deadline sometime.

Postpone pending motion to next week. Passes hell-5-3 +Spehn.

Motion to maim skinner's exponential tail. Passes 16-0-0 +Spehn.

Motion to damp.

\goto{New Business}

Amplifier on gavel block. Passes 9-3-4 +Spehn.

Quibbling of definition of Scrod Books.

Probabilities of finding Scrod Books.

Neel enters: banana motion. Fails 7-9-5 +Spehn.

Motion to call ceiling banana colored. Fails 5-hell-8 +Spehn.

Motion to retroactively pass previous motion. Fails for ambiguity.

Motion that all motions fail. Dies for lack of second.

\goto{Future Business}

Motion to pass all motions. Passes 16-8-10 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned.

\end{document}
