\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 17, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: mumble (regarding minutes). 8-0-1 +Spehn.

\goto{Committee Reports}

Jourcomm: my sister's writing for TZ now. Deadline October 31st.

M: commend Jourcomm for nepotism. 13-0-1 +Spehn.

Pseudo-Mobcomm: Library of Congress whenever in DC... during Thanksgiving.

\goto{Old Business}

Gavel weird harmonics discussion.

Yesterday was the launch date of Jupiter 2.

Discussion of cryptography patents.

M: to decrypt Jen. 7-3-1 +Spehn.

The ceiling is still dripping.

\goto{New Business}

Pandemonium- Haldeman signing, demonstration of dilation.

The alum mailing will happen soon, right Ed?

Discussion with our circulating special reserve (books on tape).

Discussion of Tarl (chained up)- protagonist in Gor novels.

Jen's mother will buy at least 12 copies of TZ to send around.

We explode in 30-34 months.

\goto{Future Business}

When to deal with the new shelves?

Japan, Korea, or Colorado for Eddy's summer. He has to decide by Monday.

M: to have Eddy not forget to write. 1-0-14, no Spehn!

M: sometime in the future there will be a meeting that ends with a motion that involves a banana. Everyone-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}