\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 8, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Pathetic \bing

Minutes brilliantly read by pseudo-onseck.

Motion re: minutes fails.

M: commend pseudo-onseck for courage and perseverance. Chickens.

\goto{Committee Reports}

Dexmistress: inventory was fast.

Jourcomm calls apathetically for submissions.

\goto{Old Business}

Bill's not kidding. S/O is old and binged.

Hi, archaeologists. How are you?

Jamie says: lots of books missing.

Discussion of inventory notation.

We don't know how many books are left.

\goto{New Business}

Quiet confusion. R/O to happen someday.

Skinner has less hair.

M: commend skinner for having less hair. Passes. Inversed incomprehensibility.

\goto{Future Business}

Skinner to be absent for work.

[Illegible]

M: put off fall semester for a month. Passes by skinnerial decree.

Various songs sung a lot.

Compromise prevails.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}