\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 30, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: regarding the minutes as read with great [illegible]. 5-2-7 +Spehn.

\goto{Committee Reports}

Jourcomm: next semester. (Not.)

Panthercomm: books have been processed.

Next book run- probably around rush.

Discussion of J as rush chair and ET as part of MITSFS.

Moocomm? Season finale- Buffy the Vampire Slayer on Monday. Lots of sarcasm (Toby's fault). Eddy wants Vampire the Buffy Slayer.

\goto{Old Business}

M: condemn Jamie for talking about movies that don't exist (Highlander II). 8-0-0 +Spehn.

Discussion about deaths of advisors, UROPs, etc.

\goto{New Business}

? 1-0-0 +Spehn.

\goto{Future Business}

Miller motion (2nd one). 5-1-6 +Spehn.

Almost June.

\goto{Time Warp to Committee Reports}

Industrial Rubber Boot Committee: concert in Copley Square fountain.

\goto{Time Warp to Future Business}

The long dark tea-time of the MITSFS.

Apathy. Passes.

Finally! Someone sings a bit of Doe-a-deer.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}