\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 6, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Notes go to pseudo-pseudo-Onseck to be translated then go back to pseudo-Onseck.

Minutes read.

M: minutes are illegible. 20-1-5 +Spehn.

\goto{Committee Reports}

Pseudo-Onseck becomes confused. Notes go back to pseudo-pseudo-Onseck.

M: commend pseudo-Onseck for being confused. Some-4-buttloads +Spehn.

Definition of buttloads and decibuttloads (metric).

M: move meetings to 1700 SDT. 15-5-4 +Spehn.

M: make the above retroactive. Hell-8-4 +Spehn.

M: reverse pseudo-Onseck to pseudo-pseudo-Onseck until next banana motion. 0-2-0 +Spehn.

\goto{Old Business}

Finger motion.

\goto{New Business}

M: do ALGOL. 19-6-0 +Spehn.

\goto{Time Warp to Old Business}

ALGOL.

\goto{New Business Mk. II}

M: commend New Business for being stacked. 6-8-12 +Spehn.

M: commend pseudo-Onseck. Infinity-0-0 +Spehn.

Complaint by pseudo-pseudo-Onseck. Ignored! Threats to control/alter minutes.

\goto{Future Motion, Er, Business}

M: some tricky motion about the zine. 6-3-3 +Spehn.

M: rename zine to "Mission Impossible." Most-less-less +Spehn.

Miller motion fails.

Pseudo-Onseck sings "Skinner has no tail at all."

Skinner asks "Do you really want me to show you?"

M: table skinner's tail. 12-0-0 +Spehn.

M: Recursive Business. 4-8-2 +Spehn.

Miller fails for lack of second.

M: Matrix vote? 19-1-1 +Spehn.

M: find eigenvectors in Perl. 17-0-6 +Spehn, but fails anyway.

M: find eigenvectors in Matlab; somehow turns into Miller motion. 22-1-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SDT.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}