\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 21, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to declare minutes incomprehensible. 10-0-1 +Spehn.

\goto{Committee Reports}

Moocomm: Empire Strikes Back.

Jourcomm: submit, get fine credit.

Pianocomm: we need more projects.

Motion to go slower. Died.

Motion to go faster. 4-0-3 +Spehn.

\goto{Old Business}

Alum letter should go out soon.

Star Wars still in theaters.

Motion to have George Lucas donate to MITSFS. 12-3-2 +Spehn.

\goto{New Business}

Erin is here.

M: commend Erin for being here. 2-1-4 +Spehn.

\goto{Future Business}

Return of the Jedi: out real soon now.

Motion to have dinner trip. Dies.

\goto{Post-Future Business}

Computers to bring back best of all possible worlds.

\goto{Recursive Business}

Brownian motion. Passes.

Motion to declare. Lots-some-1 +Spehn +Cow.

Miller motion. Fails.

2nd Miller motion. 10-some-15 +Spehn.

3rd Miller motion. Dies.

4th Miller motion. Recurse to 2nd to 3rd. 22-2-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
