\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 25, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SDT,
Jay Muchnij, the oh-so-honorable President and Skinner, presiding; Ed Keyes, Pseudo-Onseck, recording.

Minutes read.

Motion for minutes to be similarly apathetically banana-colored. 0-6-1 +Spehn.

\goto{Committee Reports}

Inventory next week.

Jourcomm begs for materials for R/O.

Hardcover run sometime soon.

Foocomm reports "foo."

Colorcomm: complains no spine-color index for book-like objects.

Radio/tachyon messages from the future should be received in a book titled with "Earth/Green/Star" words.

1038 books with "Star" in the title (yay!).

\goto{Old Business}

"It was here last week."

Bing disturbs inner ear of Eddie. "I'm still dizzy."

Check for 112 paperbacks on the for-sale shelf has been received. Yay!

Hasslecomm shelf is hard to find despite labels.

\goto{New Business}

Rush is soon, fresh blood to feed upon.

Threat of tickling.

Firestar is not new business!

Motion to condemn the first page of last week's minutes to not have disappeared as the others. 3-0-0 +Spehn.

"Let the fools rot in their own stew." (Jay)

\goto{Future Business}

Motion to condemn meeting for not being able to count bananas. 10-0-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned at an unknown time.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Pseudo-Onseck}

\end{document}