\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 24, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Murphy, Pseudo-Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to make minutes shorter. Chickens 7-0-8 +Spehn.

\goto{New Business}

\goto{Time Warp to Old Business}

Will be Twilight Zine- submit stuff.

Usual motion, usual second, usual vote, usual result.

Motion to adjourn. 10-0-1 +Spehn.

Motion to move to Future Business. Passes by skinnerial decree.

\goto{Future Business}

Motion to only end meeting with banana motion or Miller motion. Chickens.

Motion to return pseudo-skinner to position as psuedo-skinner. Passes.

Announcement: IAP Sick and Twisted on Thursday night.

Item call for next meeting. TV Guide subscription for many many years. Attach item to door.

Return to this week's future business with back to the future \bing

Miller motion. Fails.

Miller motion. Fails for lack of second.

Miller motion. Passes 9-8-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
