\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 28, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to declare minutes a challenge. Passes 6-4-1 +Spehn.

\goto{Committee Reports}

Jourcomm: submit!

Motion to commend Jourcomm for dominating. Passes.

Pianocomm: still need projects.

\goto{Old Business}

Motion to commend guy for slouching in the back. Passes 8-7-0 +Spehn.

Algol.

\goto{New Business}

TE to J: we can now clone you. Sheep and humans are pretty much the same.

Motion to declare Toby a sheep. Passes 8-0-2 +Spehn.

\goto{Future Business}

TE: there is no such thing.

Motion to commend J for warping things. Hell-no-1 +Spehn.

J: move that slavery is freedom. Passes 7-6-1 +Spehn.

Motion that freedom is slavery. Passes 12-5-0 +Spehn.

\bing \bing \bing \bing (Sound of many motions dying.)

Motion that twinkies have lives. Passes 19-1-0 +Spehn.

I love paradox. Fails for lack of a motion.

Singing: skinner has no sheep at all...

Move to clone a banana. Passes hell-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
