\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 14, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij (wearing the imperial orb), President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to condemn onseck for inconsistencies. 8-0-2 +Spehn.

\goto{Committee Reports}

Apprenticecomm: more apprentices!

Moocomm: Empire Strikes Back is next week.

Jourcomm: submit.

\goto{Late Business}

Jen walks in.

\goto{Old Business}

"I LOVE recursive minutes." (Ed Keyes)

Motion to recurse to find proper environment. Fails (small stack space).

Fiddler fails.

Toby's glare is getting old (Jen usurps chair). 17-0-0 +Spehn.

\goto{New Business}

Game delayed 2 hours. Damn them to hell. 10-0-2 +Spehn.

Motion to have more new business. Dies.

Ed Keyes' slurp sounds like X-Files.

Xena: lesbian subtext is no longer subtext.

TE: great episode.

Andy Menard: "Ever had the joy of attacking a computer with a butane torch?"

Discussion of merits of series Wizards' First Rule.

\goto{Future Business}

We need more space.

\goto{Post-Future Business}

Motion to declare bananas extinct. Fails 10-12-4 +Spehn.

Bananas shall rule the world. 18-7-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1700003 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
