\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 21, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: "Jamie's motion." 7-1-buttload +Spehn.

"Are you hitting-"

\goto{Committee Reports}

Pseudo-something: Orson Scott Card was here yesterday; he was cool.

M: to tap two islands and counterspell. 9-15-1 +Spehn.

(Eddy- I don't know what it was but it was a cheesy magic voice.)

Geekcomm: M: that was geeky! 2-4-12 +Spehn.

M: "Sam, stand up over here." (JM) 14-0-0 +Spehn.

Moocomm: Jose Chung episode. Dead by Midnight.

M: ? 2-2-3 +Spehn.

\goto{Old Business}

Martin: "I'm the old."

M: commend Bill for being so old. 6-2-4 +Spehn.

M: I'm old and my glasses are dirty.

M: some B5 reference, forgotten.

M: to declare everything in the MITSFS. Everyone-no one-none +Spehn.

(J broke the table.)

\goto{New Business}

M: the new Reserve.

M: to have Andrea give J grief. Just about everyone-0-0 +Spehn.

Time warp last motion to Old Business.

M: to substitute the old grief for brand-spanking-new grief. "No spanking grief here!" (J)

M: to get a clue. 9-4-none +Spehn.

M: achoo! 4-8-0 +Spehn.

M: not everything has to be a motion. 8-11-1 +Spehn.

Pseudo-banana motion. 10-23-0 +Spehn.

M: pseudo-banana contains the word banana. Piddly-16-0 +Spehn.

\goto{Future Business}

Miller motion. 8-11-3 +Spehn.

Chaotic singing. Skinnerial laughter and gloating.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}