\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 21, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 17? SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: [illegible] minutes down to microseconds. 4-7-6 +Spehn.

\goto{Committee Reports}

Jourcomm: deciding April 11.

First? Passes  - -3 +Spehn.

Jourcomm wants people to review books.

Someone walks in late.

Ronocomm: apprentices exist, still.

\goto{Old Business}

Richard Spehn email (onseck 1963).

Someone else walks in late.

Twilight Zine is looking for onseck.

Discussion of Spehn's soul. And Marcus's... and Chris's... and Jamie's.

Pending motion. M: to delay to next week. Passes 10-1-7 +Spehn.

\goto{New Business}

Jay makes his binging more quiet due to Andrea's request.

M: bing more loudly. Fails, lack of second.

M: Japanese Newtonian Appletree experiment. Passes 10-6-1 +Spehn.

\goto{Future Business}

We had new business this time.

M: new version of Netscape to cache. Passes hell of a lot-0-0 +Spehn.

Yay, pyramid schemes.

Discussion of George Flynn being the People's Albanian Ambassador and signing out a reserve book.

Subtitles? French?

M: go into Recursive Business. 17-0-3 +Spehn, again and again.

\goto{Recursive Business}

M: go into business selling recursiveness. And more. Fails for lack of second.

M: tickle Jamie using feathers.

Discussion of cleaning chickens.

Discussion of sorts.

Crank magazines lost- ordered, not to be found. Jen asks "what budget?" Ken?

M: commend Jen for conducting real business during the meeting. Passes by skinnerial decree.

M: go back to Future Business. Passes oh god that's a lot-fewer-even fewer +Spehn.

\goto{Future Business}

M: to iterate matrix vote! (Jamie) 3-4-1 +Spehn; motion does something really wacky.

M: to banana. Fails 12-20-1 +Spehn.

"Former MIT alum" novel.

"Something interesting may happen midnight of 26th" (next month).

M: accept offer to altar of MITSFS. "Burn it, burn it, burn it in duplicate." Passes more-1-9 +Spehn.

M: commend skinner for being quantum indeterminant. Fails 5-6-chickens don't count +Spehn.

M: protect from banana plague. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
