\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 23, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: burn last week's minutes. Passes 14-13-1 +Spehn.

\goto{Committee Reports}

Pianocomm: new apprentices.

Finger motion.

\bing "Wow, that cleaned out my ears." (Jen)

Mobcomm: we have a Mobcomm shipment.

Panthercomm: we'll process them RSN(tm).

\goto{Old Business}

There was a picnic. We forgot the sports gavel.

Marcus has no hair.

Asimov is still dead (as of last report).

The Alpert is sending us old pictures of the library. Discussion.

M: to have a meeting in the box. Passes 18-8-3 +Spehn.

Atlascomm: "I'm half an inch shorter."

M: to declare Jamie Eddy. Chickens 0-0-1 +Spehn.

Finger motion.

Something about magazines? What?

Jourcomm: TZ end of summer (out for rush).

\goto{New Business}

Eddy's in a box!

Usual motion, second, result.

Scramble to get Jen a Phillips head screwdriver.

M: it's one of those evil 6 pointy things. Passes 9-1-helluva lot +Spehn.

M: hunt Eddy down, put him in the box, and keep him there. 7-not more-almost as many +Spehn.

M: commend Erin for resonating while [illegible] in Fifth Element t-shirt.

\goto{Future Business}

M: do next week's minutes in Gabriel's handwriting. Chickens 8-1-9 +Spehn.

M: commend Erin for gesticulating in the library, even if she is Vice. Doesn't really do anything 9-9-2 +Spehn.

M: put Erin in the box with Eddy. Fails.

"Gosh am I good." (J)

M: invest in some reflexes for Jen. Passes 13-1-10 +Spehn.

M: start walk on a really big banana cream pie for next year. Fails 11-13-2 +Spehn.

M: cannibalize Eddy's last remaining reflexes and install them in Jen. Everyone-0-0 +Spehn.

Friendly amendment: append the word banana to that. 11-6-7 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned "and flashily rides off into the sunset," 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}
