\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 5, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; Jenwa Hsung, Onseck, recording.

Minutes read.

M: install air conditioning to eliminate confusion. 13-5-5 +Spehn.

\goto{Committee Reports}

Jourcomm: "Please submit some."

M: commend the skinner's ability. 15-0-4 +Spehn.

Pianocomm: new apprentice- Justin. Old longtime apprentice realized his job was already done and wants another (Brian... Sniffen, as opposed to Perrin).

Skinner threatens Ed Keyes.

M: commend onseck for having gotten older over the summer. 7-6-5 +Spehn or something like that.

M: commend the onseck for having gotten older since the last minutes. Buttloads-2-2 +Spehn.

M: to commend the skinner for his old age. Something small-15-something like 5 +Spehn.

Toby claims Jay'll never be older than him.

Motion. 9-0-5 +Spehn.

M: go to Young Business. 20-7-1 +Spehn.

"The young HAVE no business!" (Toby)

\goto{Young Business}

In about 40 months we'll run out of space.

Motion. 10-9-1 +Spehn.

Young Business ages into Old Business.

The usual.

\goto{New Business}

M: time warp to Committee Reports. Something like 9-15-2 +Spehn.

Boston film festival.

Future Business is discussed and then declared.

\goto{Future Business}

Jen's birthday is tomorrow.

M: commend Jen for getting a year older between today and last year. 15-7-2 +Spehn.

M: declare Jen's birthday RSN so we don't have to celebrate quite yet. "You're the skinner, just make people up." 15-19-1 +Spehn.

[Illegible]. 6-everything else minus Spehn-0 +Spehn.

M: to not fix the banana leak in the ceiling. 8-9-13 +Spehn.

Miller motion.

Second Miller motion. Fails 18-15-1 +Spehn.

"Skinner cannot count at all." "He's just a Pentium."

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa Hsung, Onseck}

\end{document}