\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 10, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to regard minutes as proof of Tara and Milk Jen being same. 14-0-0 +Spehn.

\goto{Committee Reports}

Pseudo-mobcomm: selling books.

Mobcomm: buying more.

Flogcomm: crack!

Pseudo-analogcomm: new schedule.

Pseudo-moocomm: UHF playing.

Motion to commend UHF passes by skinnerial decree.

\goto{Old Business}

Bye! (Janelle leaves.) 6-6-6 +Spehn.

Reverse all decisions from last meeting?

Marc Alpert wrote (was skinner when Jamie was born).

\goto{New Business}

Skinner does assassin thing.

Toby was dissed.

New apprentices doing stuff.

\goto{Future Business}

Bad B5 jokes.

M: F/NR for freshman. 8-9-10 +Spehn.

Motion to have lackey enterprises donate money to MITSFS. Passes 8-?-? +Spehn.

Motion to declare Ted an iguana. Lots-few-some +Spehn.

\goto{Post-Future Business}

Finger motion.

Motion to commend Iguana for choice of reading material. 10-40-4 +Spehn.

M: summarize Earth. 5-4-4 +Spehn.

M: banana. \bing Lots-less-few +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
