\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 9, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Motion to have next week's minutes in iambic pentameter. Passes 15-8-0 +Spehn.

\goto{Committee Reports}

Jourcomm: deadline next week.

Moocomm: go see Wallace and Gromit.

\goto{Old Business}

Hint. Passes by skinnerial decree.

Motion to insert motion here [arrow to "Hint"]. Fails for lack of second.

Motion to insert this motion. Chickens 2-0-3 +Spehn.

\goto{New Business}

Apathy- who cares.

New wave of apathy not reported.

Sam isn't dead.

Move to counteract Sam rising from dead until he finishes picnic stuff. Passes 9-0-2 +Spehn.

Motion that all further motions be in iambic pentameter. 16-0-0 +Spehn.

\goto{Future Business}

Egads, the time for a Miller motion. Fails.

Oh no, another Miller motion here. Passes 9-0-7 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST. TE: the Skinner has no hair.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
