\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 11, 1997

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jen Murphy, Pseudo-Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

It is very loud.

Too loud.

So loud, in fact, that I'm losing my brain.

Minutes read.

Motion to declare the minutes unreadable.

Motion to declare the minutes a vector field.

\goto{Committee Reports}

Pseudo-Hasslecomm reports that the Hasslecomm shelf exists.

\goto{Old Business}

Too loud.

Neel: "Jen bonged." Jen: "I binged."

Discussion of the legality of bongs, tobacco, cigarettes, and smuggling in Canada.

Jen's family smuggled food from Canada to the US during WW2 in large volumes (in her mother's diaper pail).

Discussion of young at MIT.

Pseudo-Onseck flees the room.

Pseudo-Onseck takes the fifth.

Neel is old.

Neel is living in Somerville.

The comic books were bound for theological reasons.

Deaf!!

Jim Henson is dead.

Algol.

\goto{New Business}

Blurbs are being sent out.

Neel will be corrupted after the meeting.

\goto{Future Business}

Motion to condemn Neel for having a briefcase large enough to carry thousands of bananas across the Canadian border. Lacks a second. Seconded telepathically. Chickens.

Pseudo-Onseck goes insane due to constant banging noises.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}