\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 25, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

The Thunderbunny graduated!

M: commend the Thunderbunny for the fact that the \bing still makes her jump. Passes.

\goto{Committee Reports}

Pseudo-mobcomm: used paperbacks purchased.

\goto{Old Business}

Silence.

\goto{New Business}

More boxes of magazines picked up, may have more books coming.

\goto{Future Business}

Only 6 more months of shopping before Xmas.

Only 3-4 weeks before inventory.

Only some time before masquerade.

Skinner's birthday is this Sunday! "In celebration, I'm leaving town."

Discussion of dark side vs. light side of the Force. "Beware the dark side. It might be fun."

"Ithaca is more fun to say than Cambridge." Discussion of Cornell and attempted suicides.

Motion to go get burgers and banana splits at Diesel Cafe. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
