\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 19, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: reading of minutes interrupted. Passes.

\goto{Committee Reports}

T-shirtcomm: t-shirts are here. There were non-MITSFS shirts in the boxes. Jen also ordered a Buckaroo Banzai shirt.

jhawk spent 6.5 hours with Katherine Kurtz.

Mobcomm: still need to make a run for books.

\goto{Old Business}

Motion to condemn AMU for a bad bing. Chickens.

\goto{Time Warp to Committee Reports}

Pseudo-pianocomm: it may work better to get the prentices into the library and threaten to shoot them if they don't choose a project NOW. (They hadn't replied to skinner's email.)

Discussion of people's keyholder projects. WDS got his key in 1976... no one could beat that. Jade: "I don't want to discuss it." ED: time elapsed since beginning of keyholder project about 3 years. The shortest time: less than a week.

Prentice project being to rent them out- makes money for the library too! Must not be broken when returned- minor psychological damage is okay...

M: to thoroughly tie up and ding up the prentices. Fails by skinnerial decree.

M: to chastise pseudo-skinner AMU for being no fun. Fails.

\goto{New Business}

Today is the last day that the date is all odd digits- this won't happen for some 37 generations.

M: say hi to pseudo-Telzey. Passes.

Lots of people shout "Bag!" jhawk: "We're supposed to bag the pseudo-Telzey?"

\goto{Future Business}

There is no difference between the rule for leap years in the US and Russia...

Motion to sympathize with Julius Caesar because his calendar died.

M: encourage Jade to throw more articles of clothing. Passes.

Several motions fail for the lack of comprehension (others and my own).

M: to end the meeting. Passes.

M: something about bananas. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
