\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 8, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; DDC, Pseudo-Onseck, recording.

Minutes read.

M: approve minutes as Jamie. 6-0-7 +Spehn

\goto{Committee Reports}

Mobcomm: NERO committee tomorrow (roo).

Plantcomm: they'll seal the leak in the machine room soon. jhawk donating books.

M: commend it for being large and in view. 4-0-1 +Spehn.

Phonecomm: ring!

Sitcomm: new Addams Family bad. Sentinel back on TV.

M: define W as being at Arisia. Many-5-1 +Spehn.

Equipcomm: we have vaporizer-like opus discussion as to what to do.

Skinner leaves. Onseck takes over.

\goto{Old Business}

M: say hi to perso (he just walked in). 13-0-0 +Spehn.

\goto{New Business}

Plantcomm discusses climate control and thermometers.

M: turn Jenwa into a pumpkin. 1-8-0 +Spehn.

Discussion of borcon in framingham. "Let Ellen be the mailing list." January 15th and 18th. (former keyholder Jen)

M: Jenwa's earrings are rowdy. 6-1-9 +Spehn.

\goto{Future Business}

M: note that two of the seven strops on Jenwa's jacket are not banana colored. Some-less-less +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1726 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{DDC, Pseudo-Onseck}

\end{document}
