\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 21, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

Motion to motion about the minutes. 6-2-4 +Spehn.

M: commend skinner on improved \bing 9-6-2 +Spehn.

\goto{Committee Reports}

Mobcomm: new books. New Dr.-less Who book.

Skinner: "Shut him up. Just stick something in his mouth."

475 gets new ceiling tiles: polka dots.

Phantom Menace looks good, not much else.

Pseudo-pianocomm: onseck now has a key.

Pseudo-analogcomm: people should sign up for hours.

Skinner almost done with the books.

\goto{Old Business}

Skinner: "Do I have to bing?" Ex-ta: "Subtlety does not suck."

Previous skinner sick again.

Some motion passed unanimously.

\goto{New Business}

M: to move into maneuve business.

JM: "We have new magazine thingies to hold magazine thingies... some magazines were moved to Damnation Alley."

M: move jhawk into a sink in space. Motion fails for lack of second- "there are no chickens in space."

M: say hi to people. 17-0-1 +Spehn.

\goto{Future Business}

"No future... we can be in the alternate reality business."

M: commend jhawk for not knowing the alphabet. 8-0-1 +Spehn.

M: commend Seph for having a banana colored disc gun.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST. jhawk: "Wait! I didn't find it!"

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
