\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 22, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: commend minutes for being typed. 7-1-2 +Spehn.

\goto{Committee Reports}

Pseudo-ROSFAP: discovered Philip K. Dick's FBI file and Life: Choose Your Own Adventure (which should have been thrown out long ago, date 2/95).

Onseck has decadent dreams and writes about it. 10-20-0 +Spehn.

Mobcomm: boring, nothing new.

Sitcomm: not enough time to watch anything.

Pseudo-pianocomm: something about a prentice starting a project- we have a prentice!

Assistant Jadecomm: entered a magazine into Magdex. Magdex almost got buried alive.

Jay and Jade are decadent.

Look at the FBI report... his name, age, sex, height, build, and misc. are blacked out.

M: to request Jade's FBI report. Passes.

AMU mutates into Jenwa.

M: condemn onseck for not paying attention. Passes.

A flurry of motions pass in aggregate.

Skinner doesn't feel like having a tensor vote.

Pseudo-pianocomm: found a pile of 5 year old alumni mailing addresses.

jhawk: "Complaining is more fun." Jay: "I gather you have a lot of experience..."

People object to Magdex being filed under M in a straightforward location. There is only one new entry in Magdex featuring jhawk's favorite author Somtow.

M: to go "ooh" for Yevgenia being dressed up. Passes. "Ooh."

\goto{Old Business}

Verbal bing.

M: commend skinner for extraordinary bing. Chickens.

M: to have a banana motion to get this over with. Chickens 5-3-9 +Spehn.

T-shirts real soon now. Jake defaces the minutes.

M: to burn Jade's hand at the stake for being unholy. Passes 4-0-1 +Spehn.

M: commend onseck for brightly banana colored shirt. Chickens 8-4-12 +Spehn.

Second Miller Motion chickens.

M: to record minutes in shape of a banana probably chickens. [Minutes were from this point onward written inside an outline of a banana.]

\goto{New Business}

Plush Cthulhus now sold cheaply (no tartan colors).

M: to have Jade or Jay investigate what Cthulhu does not wear under his kilt. Chickens?

Move to find price of banana colored Cthulhu. Fails.

\goto{Future Business}

Some stupid banana motion ends the meeting.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
