\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/29/1999}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS meeting minutes

Friday, October 29, 1999

\end{center}

\vskip 12pt

MITSFS meeting called to order, 17:00 SST, October 29, 1999.

Jenwa, skinner, presiding.

John Carr, pseudo-onseck (oh where or where has Natasha gone...).

The meeting decides to have the minutes of the previous week's meeting
read instead of the ``Airplane~2'' rules.  There are no motions concerning
the minutes and a motion to orange-sticker the meeting chickens \hbox{6-1-7+Spehn}.

{\bf BING!}

\vskip 12pt

\centerline{Committee Reports}

Moocomm: LSC sneak was weird but cool.

Sitcomm: ``Harsh Realm go flush.'' ``I never heard of it.'' ``That's part
of the problem.''

Pseudo-theftcomm: We are running a slide this weekend because LSC was nice.
We missed the deadline.

Pianocomm: Prentice Debbie ``ex-hex-wife'' Moore got a project.

JFC hears Jamie ask ``John, talk through the slinky.''  He does,
but it turned out Jamie actually {\it said} ``toss me the slinky.''
A motion to commend the skinner for laughing and binging at the same
time passes 8-1-5+Spehn.

Jenwa lost blood today, but it was intentional.

Justin's sister met the guy who played Angel, or maybe the guy who didn't
play Angel.

Moocomm$_2$: WDS got some Doctor Who books.

\vskip 12pt

\centerline{Old Business}

WDS will be 43 in 2 days (i.e. Halloween).

OTPQ's father was 43 a few years ago.  (OTPQ = Obsessive Terry Pratchett
Quoter, aka Vanna, who may also be known as Sam.)

T-shirts RSN.

Justin was stuck in an elevator until he opened the door.

JM: We are (still) short on money, keyholders, and space.

JFC: But we have a prentice who will be skinner-eligible in two years
(i.e. will still be an undergrad).  Someone corrects JFC, pointing out
that we actually have {\it two} sophomore prentices.  A skinner and an
LHE!

\vskip 12pt

\centerline{New Business}

Justin inherited Jen's health.
Jenwa has allergies (instead of a sinus infection or mono).

Frat rally tomorrow.

Microsoft might be UMOC.

The bomb squad was at MIT twice this week.

JM still hasn't replied to the Seitz query.

tip: To get a traveler in trouble, sprinkle East Campus courtyard
sand in his luggage.

OTPQ's professor was wearing a ``Chuck Vest'' shirt.  But he's not
really a professor.

tip: Never wear a T-shirt with a message you don't understand.

\vskip 12pt

\centerline{Future Business}

OTPQ quotes Pratchett: ``Give a man a fire and he's warm for a day.
Set a man on fire and he's warm for the rest of his life.''  This
sentiment is approved 10-0-1+Spehn.

Jenwa has no plans to pierce her tongue.
A man in China had three tongues, one of them nearly a foot long.
Motion: transform the skinner's tongue into a banana, leaving it in
place.  Passes 14 to less to a little~+~Spehn.

Meeting adjourned 17:35 SST.

\end{document}
