\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 8, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Jade Wang, Pseudo-Onseck, recording.

Minutes read.

M: commend JWH for making John dance. X-Y-Z +Spehn.

M: commend reading as especially lively. Something-5-2 +Spehn. "I can't seem to remember numbers anymore."

M: then you should use colors. Red-suffusion of yellow-ultraviolet +Spehn.

\goto{Committee Reports}

Mobcomm: September 26, 2 PM, 40,000th book entered (volume, not title- "indexed object"): Archangel by Sharon Shinn.

Mobcomm or Pseudo-pianocomm (JPW: "Make up your mind!" JFC: "It's you I'm talking about!" JM: "Jadecomm!"): between Magdex and 2 much Magdex there may be 8,000 index.

More Jadecomm: we're not as badly off as we thought.

M: put people on Jadecomm temporarily. Purple-green-brown +Spehn.

Jadecomm sub 3: Jade is wearing a rainbow-colored thingy. "An artifice of female attire."

Sitcomm: 4th season of Buffy Tuesday, 1st Angel season. Buffy is bad. Green-red-purple +Spehn. Fails.

Sitcomm2: Roswell premiered but WDS hasn't watched yet.

JFC: "I turned on my TV last week." M: commend JFC for learning how to turn on his TV. Infrared-ultraviolet-really dark purple +Spehn.

JFC: "I found ads for sexual aids in a German magazine." He goes to show Jamie. Big rush to crowd around magazine to see this.

M: Jade looks cute all the time, especially with tongue out. Passes 100-20-3 +Spehn. [Stricken from official record.]

\goto{Old Business}

No t-shirt.

Ex-skinners who are punting meeting and are in town.

Jamie's last day of work.

M: be louder and faster? A lot-Jade-0 +Spehn.

\goto{New Business}

JPW: "Lost bookbag, so now have new one. Yes, there were MITSFS books in it." Meeting gets sad.

Jenwa says bing instead of binging.

M: commend Jenwa for an exceptional bing. Passes something-something else-else +Spehn.

M: no new business. 1-2-4 +Spehn.

\goto{Future Business}

M: condemn skinner for not continuing to count in colors like banana and chart or something. Large elephant-2-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JPW, Pseudo-Onseck}

\end{document}
