\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, MONTH DAY, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

Motion to entertain onseck in less naughty ways than last time.

\goto{Committee Reports}

Sitcomm: Crusade premiered last week. Petition going around to keep the actress from it.

"Speaking of gods-" Jade walks in. Motion to offer appropriate sacrifices to Jade. Lots of chickens. Motion to spoil Jade- "she's only 12." "We can take away her sushi and then give it back to her as a sacrifice." Jade: "It has to be something I've never had."

Bluebellcomm: have more hardcovers needing to be covered.

There is no Fweekcomm.

\goto{Old Business}

Motion for Jenwa to tell us about her life. 17-0-3 +Spehn. Works at Lindgren Library (Earth and Planetary Science and maps), bought books (Pandemonium) because skinner has cash, skinner should deposit paychecks (should get direct deposit? Would get "stubs" or "deposit advisory".)

Jade was taking pictures of skinner, Jen. Flash flashes at exact frequency to cause epileptic seizures. "Stand back! She's blinded and she's wielding a gavel!"

Discussion of assassin games.

The picture on the front of the Tech looks like the battlefield in Phantom Menace.

Jade: "Are you saying that MIT graduates look like droids?"

\goto{New Business}

Skinner is not wearing all black.

Discussion of Sport Death items (skinner's t-shirt, zippos, machetes).

"We need MITSFS machetes." "We have a sword!"

Motion to inscribe sword with "we're not fans, we just read the stuff." "How about 'twist to remove'?"

Discussion of Windows viruses.

\goto{Future Business}

Motion that Jamie is the only one who likes bananas.

Discovery: Jamie is a tripod (has 3 legs).

Motion that does not exist.

Motion to never stuff bananas up Jade's nose until she behaves. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1733 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
