\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 16, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; WDS, Acting Temporary Interim Substitute Pseudo-Onseck Pro Tem, recording.

Minutes of previous meeting are read. A few motions get made that are too lame to even get seconded.

\goto{Committee Reports}

Sitcomm: Buffy season finale was finally shown. High school students with flamethrowers attacking a giant snake. The school was not a happy thing afterward.

Pianocomm: Prentice Jen did another 6 hours of work. All the hardcovers and probably all the large paperbacks from the big donation are done. Nine boxes of paperbacks left. Big boxes.

Pseudo-hasslecomm: Hasslecomm books are piling up.

Mobcomm: John Carr: "we're running out of space for the New Books, even with the addition of the new box with mysterious inserts."

Other Mobcomm: WDS: "ribbed for your pleasure..."

Teresa Tutt: "Johnathan Scott Taylor and Amy Wright- same person?" (Teresa's perusing a copy of the novelization Damien: Omen II, which apparently comes with photos of JST, whoever he is. Amy Wright's an Indigo Girl.)

Brief discussion of novelization of movies that were based on novels in the first place, and of the similarity- singular- between the Ian Fleming novel Moonraker and the movie made from it.

\goto{Old Business}

"We don't need no steenkin' Old Business." Seconded, chickens 1-1-6 +Spehn. CLANG!

Thirtieth anniversary of Apollo 11 moon landing mission.

An Ender's Game movie in production is announced. Great dubiousness is expressed; Justin mentions that he has a script for the movie that's seven years old now, justifying this thread's presence in Old Business.

"Is there any more Old Business?" Silence.

Usual motion, second, and result. "What about the usual debate?"

\goto{New Business}

Lobdell tried to kill the Skinner and Jen Chung tried to kill Jay. Both failed.

It's hot out.

WDS: "I want to state for the record that my ancestors did not evolve on this planet."

\goto{Future Business}

Scientists are changing their mind about the Cosmological Constant again, so maybe the universe won't keep expanding forever after all.

Retroactive Sitcomm: new TV show "Good vs. Evil" premieres this Sunday. Undead good guys fighting undead bad guys.

Skinner announces inventory on the 31st (a Saturday). Says that check-out will be frozen on Wednesday or Thursday preceding it. Is corrected by somebody or other: the database gets frozen about then but the sign-out books aren't sealed until Friday night.

Mobcomm: John Carr: "Should we get another copy of 'Seeker's Mask?'" Skinner: "I thought I already said to get it." JFC: "No, you only asked me for my opinion." Sk: "Well, get it."

It's noted that at least two SFWA books are known to be missing and therefore will probably be noted as missing at inventory.

Silence.

Skinner: "Eh, we can sit here for a while."

Anybody doing anything about t-shirts? "No, we haven't even assigned anyone to it."

Discussion about the Skinner's problems in sending email to Prentice Courtney and/or in having it acted upon by her.

How many active prentices do we have? Skinner: "Well, if we count Justin..." (Pause for laughter.) "...and Daniel who's in California for the summer, four, I think. Between one and four, anyway."

Miller Motion fails.

Somebody: "I move a banana." Somebody else: "Ouch!" Seconded, passes 7-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{WDS, Acting Temporary Interim Substitute Pseudo-Onseck Pro Tem}

\end{document}
