\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 24, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

Minutes read.

M: Aia Aia Hastur. Chickens 5-7-10 +Spehn.

\goto{Committee Reports}

Illuminaticomm: Ariel's onto ASA, might be in charge of rerooming.

Theftcomm: BSU has overrun our position.

M: condemn Jade for not knowing what flew past her head. No second.

M: "Hi Jade! Just wanted to look at you." Nothing 7-7-4 +Spehn.

LHE: got new checkbook, found old one. Suggestions include having complex checks.

M: condemn the Dr. Who books for flagrantly violating the MITSFS rules on clothing.

Pianocomm: old keyholder coming back, possible new apprentice. ED stunningly fails the keyholder system.

M: implement keyholder escrow. 14-0-6 +Spehn.

Skinner ignores other committee report.

\goto{Old Business}

M: say hi to Stephanie. Passes 14-0-10 +Spehn.

\goto{New Business}

M: new person.

M: dealloy Justin. No second.

M: fail Jamie. Passes 14-0-4 +Spehn.

M: skinner mortally offends the pseudo-onseck.

M: shut up.

M: matrix vote.

6-6-7 +Spehn, 2-10-11 +Spehn, 4-12-5 +Spehn. All fail.

M: give J's ego a laxative. Passes something-0-5 +Spehn.

M: commend skinner for a good bing. Passes huh?-what?-eh? +Spehn.

M: bing as loud as bananas. Fails 9-12-3 +Spehn.

\goto{Future Business}

M: commission a book by Harry Potter Lovecraft. Passes something-5-1 +Spehn.

M: Miller. Fails.

M: Miller, the second. 15-0-0 +Spehn. \bing

Phonecomm: ring! "Hold phone to gavel block." "Here, it's Chad."

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}
