\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 13, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jay Muchnij, Pseudo-President and Skinner, presiding; John Carr, Pseudo-Onseck, recording.

Minutes read.

M: consider minutes perfectly normal. 4-7-4 +Spehn. Fails.

M: commend minutes for writhing Christas. Fails, no second.

\goto{Committee Reports}

Mobcomm: new books.

Panthercomm: half of post-inventory done, half books found in back of shelves.

Pseudo-fweekcomm: JM: Fweekcomm is behind.

Pseudo-bluebellcomm: Bluebellcomm is being lame.

Stickerboy is being lame too.

\goto{Old Business}

jhawk criticizes Jay's gavel technigue.

JM's old sign for midway is still available.

"All hail Kludges." 10-4-4 +Spehn.

jhawk cut up a book. It was good.

JFM: "Chutes and ladders of Catan."

\goto{New Business}

WDS lost hair; JFC's plot to have jhawk killed by aliens was foiled by a pager.

Mobcomm run soon.

R/O schedule soon. Didn't we just do one last year? Long babble about R/O.

JM: use fallbacks and timeouts for meetings. 6-3-6 +Spehn.

Someone moved the t-shirt box and JFM can't find it.

JM throws away the alien nation poster! (Recovered.)

T-shirt order Monday. WDS: "Pointless Sigma Phi shirts too?" Yes, but it's Psi Phi. How many Greek letters are pointless?

"When did the guy with the ray gun grow a third leg?"

"Jay, what have you done with textiles?" Passes.

"No comment." 0-13-3 +Spehn. "I've worn a lot of them."

JM finally meets whoever it was he was meeting.

One month from now: Space 1999 begins!

JM: "The world won't end for a partial eclipse."

M: condemn JM for falling for their evil plan. 5-3-2 +Spehn, loud \bing "Ow!"

\goto{Future Business}

Kurtz bought the rights to write her book.

A member offers money to check in books during a meeting.

M: CCC should sponsor swim test. 12-1-0 +Spehn.

M: put banana in pool during swim test. 4-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
