\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 9, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

No motions regarding minutes.

\goto{Committee Reports}

Mobcomm: we have lots of bags and boxes of books, some of them at 50 percent off.

Pianocomm: new apprentice Jennifer Chung- has done 8 hours of work. "We should freeze the acceptance of prentices whose names start with J."

Damnation Alley is a fire hazard/earthquake hazard but not an ignition hazard.

Boxcomm: we have too many boxes.

\goto{Old Business}

"Bing." "Bong." "Bang." "Shouldn't go on."

Getting a discount at Your Move Games. (10 percent cash, 5 percent credit.)

The prentice shows up. "Hi, Buffy."

\goto{New Business}

Buffy lost season finale is being aired this Tuesday.

Another lost episode talks about shooting at schools. "Let's shoot up the school. Yeah, it's getting downright trendy these days." (Shot about a week before Columbine.)

Jade shows up. "The Goddess is here!"

Move to make skinner make a loud noise. 8-2-1 +Spehn.

\bing

Jade: "Louder." Jenwa: "Stand closer."

\goto{Future Business}

NASA gives up on the fly-by approach. Operation Deep Impact ran into the target.

Discussion about people dying (moonwalkers). An ex-astronaut died in a motorcycle crash.

Discussion of South Park movie. Surprisingly good. Much more intelligent than Austin Powers.

Motion to banana sticker Justin. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
