\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 3, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: condemn JM for denying us minutes. Passes.

M: commend onseck for being confused and not knowing what's going on. Passes.

\goto{Committee Reports}

Pseudo-fweekcomm: Midway happened. Freshmen were slow to commit themselves. M: condemn the freshman class. Passes.

Fweekcomm: the LSC slide is in (we think)- Reg Day movie is The Matrix (WDS: "And it starts at the beginning.").

M: commend onseck for streaking. Passes.

\goto{Old Business}

Still running out of space.

Contest of age proposed: without saying age, who remembers older things.

Crusade is now old, or former, business- 13 episodes all shown.

Discussion of authors/writers who can't write endings.

M: commend WDS for convincing portrayal (or betrayal) of a human. Passes 14-0-1 +Spehn.

"Bing." "OW!"

JM: "Some of us are humans and some of us are just wearing funny suits."

WDS takes over from JFM in telling us about how something sucked.

Debate of whether we should move on to New Business.

William Shatner speaks Esperanto (poorly). Yay consistency!

\goto{New Business}

Onseck has grape-colored hair. "No, it's Egyptian Plum!"

Next week is a pseudo-Y2K date: 9/9/99. The world will end next Thursday. 6 days before moon explodes. "The sky is binging! The sky is binging!"

The Osaka baseball team is cursed because one year they hired an American player. The victory ritual: find a player lookalike on the street and throw him in a river. They went into a KFC and threw the cardboard colonel in the river- never won since.

M: blue sticker JM for giving onseck a neck rub. Passes. Sticker battle ensues.

\goto{Future Business}

We need to get more keyholders. We need to enroll more members.

M: throw a banana shaped statue in the river.

\vspace{12pt}

\noindent
Meeting adjourned, 1727 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
