\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 17, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Jay, Pseudo-Onseck, recording.

Minutes read as written.

M: condemn NO for turning into J. Passes something-0-2 +Spehn.

\goto{Committee Reports}

Bitching about Crusade.

Jamie admits that he thought Austin Powers 2 was "brilliant." Derision reigns.

WDS says 13th Floor is "fairly good but too goddamn American." "Fairly predictable," says JWH.

Commcomm: Keeper of the Schultz was JM's mother; Schultz died recently and donated 27 boxes of books.

\goto{Old Business}

Thirdspace still sucks.

Jenwa threatens experiments with the nature of space and time.

M: "what." 1-7-6 +Spehn.

Dawn and Jade arrive.

Dawn assaults Jamie sexually. Bill: "These two have never met before."

Jade: "I took this drug..."

Debate about the value of a 1/4 year rejuvenation.

M: commend Jade for damped oscillation. 8-1-4 +Spehn.

Discussion of "fiat bi" and "bi fiat." JM: "In Latin, you can do it either way."

Carthage still needs to be destroyed.

Jade laughs unconvincingly at the Babylonians.

"There were a lot of river civilizations." "Yeah, like most of them."

RDL is in the country. "Who is he and why should he be in jail?" "He's an asshole."

Jamie's got a gray hair. Discussion of how unwashed and unhygienic his hair is.

M: commend skinner for rolling in mud, perhaps with Telzy, without becoming unhygienic. Squashed by skinner.

Skinner declines to make up interesting things about Jade's week.

M: condemn skinner for not entertaining us. Squashed by skinner.

Dawn sings. M: condemn opera. Fails lots-1-1 +Spehn.

Bill puts the moves on Dawn.

Jamie provokes confusion.

Discussion of selling shelves.

We give Dawn our approval of her killing jhawk.

Discussion of names and of AMU's lameness as vice.

M: commend Dawn's mother for being Al Gore. 11-1-3 +Spehn.

Dawn's mother had sex with Al Gore.

M: commend Jade for being older than Dawn. 7-0-4 +Spehn.

\goto{New Business}

Ladies Tea and Terrorism society is meeting again, so our banner might happen.

Jamie admits that he didn't realize that when Jade said "I'm twelve," she was talking about age. Derision reigns.

M: have Jade wear only 12 square inches of clothing. Passes 19-4-0 +Spehn. She decides she'd be willing to pass on the clothes for a sword.

Bill figures it'd be worth it to be killed by a naked Jade.

\goto{Future Business}

M: get bananas to eat. 13-0-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, ooh, I can't count, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{J, Pseudo-Onseck}

\end{document}
