\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 16, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

Impressive \bing.

M: approve minutes. 12-7-8 +Spehn.

\goto{Committee Reports}

Pianocomm: Natasha's a keyholder now. We can applaud anyways. "Applaud!" (Jen) Obedience ensues.

Where's picnic? Kresge? Turf? Condemned ground.

Skinner not having a good day.

Anyone heard from Hal? Something.

M: thwap Martyn for suggesting something sensible. Skinner decree: {thwap) "Ow."

M: no, not another Shatner novel! Passes by skinnerial decree.

Concomm: something about Balticon on new books shelf. Sara wonders why it's not ROSFAP. Jen destroys something. (Applause)

Jamie has good drawn picture of Natasha. "She has lots of hair, right?"

Dave Weber -> next book is prequel in Path of something universe. Apocalypse, basilisks, same thing...

M: condemn Bill for not knowing the difference between a basilisk and a troll. 25-1-4 +Spehn.

HW: relevant entries in monster manual. Glow in the dark basilisk: you can stare at its eyes in the dark!

Bluebellcomm: we've covered all hardcovers... until this donation.

\goto{Old Business}

Sore throat, stuffy nose, thesis due in 2 weeks. 1 week has passes since she said that last.

Bag bag bag bag bag bag bag.

Raytheon (RI) and Keenan (here) -> job offers for Jen.

Documentation of submarine.

Usual motion, usual second, usual ignorance of motions in favor of talking of Jen's life.

Someone's having a baby or something and will think about MITSFS afterwards.

Have we got a good report from People's Albanian Embassy (George Flynn, MITSFS branch)? We need one in rapid-fire style. Stuff on Kosovo refugees. How many can we hide in here?

M: not to send him to get firsthand report.

M: end meeting. Passed. "The onseck gets annoyed when I say a lot, to more to none."

{\bf THE ONSECK NEVER GETS ANNOYED, DAMMIT!!!!!!}

\goto{New Business}

How many jellybeans can fit in a 737/747? Fit lots of humanitarian meals in 737, thrown at Kosovo refugees, size/shape/texture of bricks. So how many can fit in a brick? With or without the crew?

Meat jello! 4 pig hooves and water.

M: approve skinner for first rate gavel sitting. Fails by skinnerial decree... you have to.

"I'm confused." M: commend ROSFAP for being confused. 10-0-7 +Spehn.

We had lots of prefrosh and then they... disappeared.

"Skinner has no prefrosh at all..."

\goto{Future Business}

Meeting adjourned, apparently.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
