\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 9, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: she made up that last part! 8-0-3 +Spehn.

\goto{Committee Reports}

Mobcomm: British guy- we have his new book.

Picniccomm: mailing going out in the next few days.

Panthercomm: forty pounds of books are processed. "Only 2 worth reading." (WDS)

\goto{Old Business}

Alum mailing failing to happen. Who to blame? Ed for not forcing them and alums for being lame.

Keyholder -> tenured. Hard to get rid of.

Tyrannical Iron Fist!

\goto{New Business}

New books. "I said that already."

A zillion prefrosh, some of which are here.

M: say hi to prefrosh. 12-0-1 +Spehn.

Some lecture thing.

Acoustic management of wildlife. "The once and future ping." Murphy's Law probably true.

SF reading series not being sponsored.

Tool-in...

Phonecomm: ring! Jenwa not here.

Chuck Vest: It's really cute you're all here and stuff...

Complaining about everything. Octarine ribbon campaign?

M: (chair squeaky sound). 8-10-7 +Spehn.

Futurama still doesn't suck according to WDS. Buffy still in reruns. VCR tech: watches TV so you don't have to.
Decoding Futurama alien writing... but Klingon language attempted decoded by fans.

M: approve computer operating systems in Klingon. No! Expects you to be very rude.

M: the other 28 who don't know what you're talking about. 15-4-8 +Spehn. (But they're a bad 28!)

We have more chance now... not too many nominations. Activities vote, not individuals.

Jenwa enters! And convinces prefrosh to actually come in.

TV talk. Not true: the less you see a show, the more chance you have of seeing different episodes.

Meeting segments into talkers A, talkers B, watchers, and prefrosh.

Funny, no listeners...

\goto{Future Business}

Yada yada yada.

Meeting adjourned by pseudo-skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
