\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 17, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: to have naptime again. 11-4-2 +Spehn.

\goto{Committee Reports}

Mobcomm: might get better books next week.

Pseudo-t-shirtcomm: so where the fuck are the t-shirts? We already paid Jen- she successfully embezzled.

Moneycomm: where is the checkbook? We can make paper airplanes out of the old checkbook.

Apathycomm: yay.

Everything fails apathetically. Argument over whether we have enough energy to say "yay."

\goto{Old Business}

Apathy.

Term started.

Skinner can't give us a report on the booksale. We don't know how many books we sold, we don't have the money yet. Skinner fails to track the books. Why don't we track books through the computer system? We don't have a netdrop and Justin told the other part. Justin, the Apathycomm: "Yay."

\goto{New Business}

Jay: "Nine."

6.001 was not meant for music majors.

We are running out of undergrad keyholders, as we don't have any freshmen/sophomores.

Move to graduate. 8-3-1 +Spehn.

\goto{Time Warp to Old Business}

Last Sunday the moon was blown out of orbit.

Labyrinth: disturbing people whose sexual identity was shaped by watching Labyrinth at 12. Many: "Jade, don't watch Labyrinth!"

There is an anime series where the character is male at night and female during the day. "Must be interesting the morning after."

\goto{Future Business}

Brattle is showing an anime Sunday- poster up on the door.

Tickets for Stephen Hawking lecture at Harvard sold out within an hour- like a rock concert. "Black holes leak."

New animated series based on Starship Troopers. Called "Rough Necks."

Some motion with banana passes. 10-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
