\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 7, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; DDL, Pseudo-Onseck, recording.

This is brought to you by the letters S and A and the pseudo-onseck DDL.

Minutes read.

M: commend pseudo-onseck reading minutes. "L. Ron Hubbard votes yes." 8-0-1 +Spehn.

(random pause)

\goto{Committee Reports}

M: commend SK for continuing in usual style right to end. 12-0-0 +Spehn.

Mobcomm: still have new books.

Pseudo-panthercomm: old books still there (why?).

"Prom night entertaining."

Hasslecomm: being lame.

"What's a semi-formal?"
Less naked people at Senior Haus since it's in the Student Center.
"Have naked people carry swords!"

Old-time warp back to comm.

Picniccomm: about 50 people coming. All is going well. It's next Sunday (5/1x). No famous authors :(

Time warp (back?) forward.

\goto{Old Business}

M: make nice comment to Jen. 8-2-3 +Spehn.
"We like you Jen."
Cool, "no one yelled inverse skinner rule." JFM

Lowdown on Jen's thesis woes.

"People that die are in Tech." "Once they discover them."

We learn about new department head of 21W.

Term almost over, JFM nearly crusty-old alum.
JFM will live in Davis w/Johanna and 2 others.
They plan to have parties (alcohol okay).
"She is capable of sustained noise." TMI

\goto{New Business}

Phantom Menace novelizations and screenplay already on sale.
Discussion of people waiting in movie lines.
Danna Stephen King is beyond prolific.

"Twilight Zine RSN." "Yeah, right!"

M: condemn Jamie for taunting SK. No second.

Discussion of "weapons of mass destruction" analog dmg calculators.
Public needs to be educated on the US's 88 different nuclear weapons.
JFM gotta learn lethal radius by hand.
Pu bombs w/ 20 "diameter oh no!" JFM is not going to switch.

Random person comes in to buy t-shirt. There is a crash.

"Need more medium-sized people." "No more dinner trips."

"We are a benign dictatorship." HR Sci-Fi also dictatorship but name? Radcliffe no longer exists.

\goto{Future Business}

JFM mostly resistant to future business.

In the morning she will remember and has a list.

Jamie is putting the SK to sleep.

M: support the gavel with a banana. 10-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{DDL, Pseudo-Onseck}

\end{document}
