\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 30, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

"The door alarm does not shut up once you close the door again." Motion to condemn Jamie for idiocy. Passes.

Search for alarm key. Jay or Jamie: "is the door alarm Albanian?"

Jen coughs. Motion passes.

"So Jen didn't get all the worth out of her life membership.

\goto{Committee Reports}

Dexmistress: inventory tomorrow.

Any committee reports? "Someone covered some books."

\goto{Old Business}

Running out of space.

Some books wandered around. "Is that really old?"

Good vs. Evil vs. Manhole last weekend. Lost power because of flood. Fire in the storm drain: copper burns green.

Discussion of green polo shirts.

\goto{New Business}

JFC: "I read a few books." "By yourself or with the help of a friend?" M: commend John for reading ally by himself. Passes.

Motion to pass. 0-0-0 +Spehn. Confusing discussion of motion.

Discussion of why we don't allow renewal of books without actually bringing in the books.

New restaurant Jumbalaya. Discussion of availability of Cajun food.

\goto{Future Business}

Something about postponed Buffy episode showing.

Jade comes in. "You should save a seat for me." "You can sit in my lap, little girl." "I think I'll just sit here..." Discussion of Jade's age and innocence. Jade wants to be able to shoot JM, but not actually do it.

M: commend the probe for stopping at a banana. Nothing.

M: to hand Jade a vorpal banana. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
