\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 6, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, Pseudo-President and Skinner, presiding; John F. Carr, Pseudo-Onseck, recording.

A skinnerless, onseckless meeting.

Minutes read.

M: commend minutes for being read in an exciting manner. 5-2-10 +Spehn. Christa: "Am I allowed to reuse limbs?"

M: commend minutes as having bike shorts on underneath. Passes!

\goto{Committee Reports}

Inventory happened.

CTcomm: nothing interesting there. Discussion of the unused 4-level stack interchange on I-84 west of Hartford.

Phonecomm: ring!

M: condemn Jay for being so darn sweet! 8-0-notenough +Spehn.

Is Christa a nun? She once dyed her hair gray-green.

Books piling up in ZGT.

Discussion of whether bondage is subset of S+M.

Panthercomm: Dexmistress forgot to unlock datadex.

\goto{Old Business}

No young people here.

Jay and Christa are not melting.

Discussion of the spelling of Christa.

M: commend Professor (something) for (something). Christa goes on the floor! 6-Christa writhing on the floor-? +Spehn. Passes!

"It's Professor Muchnij." "No, Steve Tyler."

MITSFS has a mirror. Long discussion of "closer than it appears."

Usuals!

\goto{New Business}

Jen is melting into a coughing puddle of slime, like an Ellison short...

(Undef)

Cryptonomicon might have a good ending.

Let Neil Stephenson write "Wheel of Time" (and Jordan write "Snow Crash": "current trickled across the net...").

\goto{Future Business}

In the future, the real skinner will be here...

Motion fails, no second.

M: have Jamie scritch a banana. (Christa twitches.) 15-writhing Christa-2 +Spehn.

Jade enters to applause. "The goddess enters!"

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST, Jade now presiding.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John F. Carr, Pseudo-Onseck}

\end{document}
