\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 26, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JM, Pseudo-President and Skinner, presiding; JFC, Pseudo-Onseck, recording.

Minutes read.

M: approve minutes as well-recorded on web.

M: what? 5-1-1 +Spehn.

No 't's in minues, says JM. I obey.

Pseudo-skinner: when he was onseck, aped mee ings

M: commend curren onsecks for being lazy, passes!

\goto{Committee Reports}

Assis an bluebellcomm: covered books.

Pseudo-assis an -bluebellcomm: non-ass bluebellcomm is lame! 5-0-1 +Spehn. He covered one book!

Hasslecomm is lame.

Mobcomm: weird books. Bri ish books coming soon.

Concomm: Bal a con next week.

Pan hercomm: backlog cleared.

\goto{Old Business}

 hird space sucks. Nimoy is 68. wri e  o NESFA  o ge  money for magazine binding.

M: no! 4-6-4 +Spehn.

"Happy bir hday... Leonard Nimoy."

We wan  se  h  Gordon back! No Bruce Miller.

M: commend Albania for suppor ing MI SFS wi h airfields. 5-1-1 +Spehn.

Usuals.

\goto{New Business}

People are away, excep  1 undergrad.

Pre pre prefrosh in library? Son of member.

" au zero" says jhawk.

"Every decade is an age." (JM or jhawk)

"Cow zero." (WDS)

\goto{Future Business}

M: banana colored apples of chaos (pronounced cows). Fails!

Discussion of  Z, color, and cow zero.

 Z should use a house name for s ories.
 
All JM's mee ings are lame, says JM.

M: Florida is  he banana and OJ s a e , wi h no ' ' s, 7-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
