\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 5, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: condemn low fidelity music recording. 7-1-0 +Spehn.

\goto{Committee Reports}

Mobcomm: new Niven book! Started as collaboration between Niven and Pratchett but Niven just went and wrote it.

Discworld, Ringworld, whatever.

"Strata."

Jen is going to pick *him* (point) up and go gamble! Ten dollars! "See you next week when you're rich..."

M: denounce casting James Vanderbilt as someone in Star Wars. 6-2-4 +Spehn.

\goto{Old Business}

We're still getting full.

Bluebellcomm: still not covering. Wait a couple of weeks.

\goto{New Business}

M: "I'm sick." 10-4-1 +Spehn.

"That's a pretty good length."

"Let's replace Jade's hair with bananas."

M: second what? 4-1-10 +Spehn.

Good.

\goto{Future Business}

M: commend US for placing tariffs on foreign bananas. 8-1-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Onseck], Onseck}

\end{document}
