\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 23, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: condemn minutes for not being written on Christa with nail polish. 18-1-5 +Spehn.

\goto{Committee Reports}

Pseudo-picniccomm: people should sign up for the picnic. They're being catered by ARA. 5 dollars a head.
Talk about picnic in 20 Chimneys. Gavel toss can be held on condemned ground. Gavel toss: do bounces count?

ROSFAP: requested more index cards. Oh yeah.

More reports of fanzine reader sightings.

Has anyone read and reviewed Song of the Swan? So someone should. Fine credit for reviewing.

Bill's almost a published editor.

Pseudo-hasslecomm: real hasslecomm isn't hard? No.

Mobcomm: makes skinner cower. Real books coming.

M: approve as "was mailed tomorrow."

\goto{Old Business}

Another SF reading last night-- Melissa Scot and Louis McMaster Bujold. Series might be dead or dying... what are their expenses? Money for authors, recording authors, etc. Email address from Melissa Scot.

...boy, black nail polish is sure distracting...

M: commend for being self-referential. 7-1-12 +Spehn.

"Some to many to many more." "Be careful, you might annoy the onseck- she just got her nails painted."

Jen wields the nail-polish remover.

More on the Skinner Saga. Isn't that just usual business? Jen gets sick from many different things.

M: declare Jen a microbacteriological park and charge admission to fund MITSFS.

Happy part of skinner's life: job offers, a total of 3. Sara explains how you have to wear skirts and pantyhose and high heels at Intersystems. Yes, even the guys!

Sara disassembled the doorknob.

DoE is more security than DoD -> atomic weapons.
Talk aobut DoE and DoD has assassins and how someone here is one of them.

M: violently overthrow the government. 18-0-21 +Spehn.

M: lean on the government until it falls over. 21-0-3 +Spehn.

Jen likes 14... she likes the number 14...

Phonecomm: ring!

Jamie thought Ken Johnson was the Telzey.

M: make telemarketing a capital crime. 24-0-6 +Spehn.

M: embarrass the onseck. 35-6-1 +Spehn.

Sing! Sing!

(Silence as everyone expects the onseck to do something cool. She whimpers.)

Usual motion. Usual second. Usual premature bing.

M: censure skinner for premature binging. 11-3-3 +Spehn.

M: express our sympathy for Telzey for skinner. Premature bing!

\goto{New Business}

\bing
\bing
\bing
\bing
\bing
\bing

Ooh, the skinner has multiple bings and the Telzey isn't even here!

\goto{Future Business}

Rota died. Hi held class outside sometimes.

Jen abuses her power. Onseck or Skinner abuses power? The onseck should abuse herself? No, that's the vice's job.

M: get onseck a pen sword. 2-0-4 +Spehn.

M: whatever-whatever-whatever +Spehn. Fails.

Miller motion.

M: stuff Jamie with a banana. 12-0-8 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
