\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 2, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

Motions fail or chicken.

\goto{Committee Reports}

jhawk attempts to sell tickets to a readercon.

\goto{Old Business}

Jenwa: "I'm 21 now."

Discussion of age leads to discussion of Star Trek. Bill is 24 days older than Denise- actress who plays someone in Star Trek.

\goto{New Business}

Discussion of shooting of new Lord of the Rings movie.

Motion to strike all references to [Jar Jar] from minutes. Passes unanimously.

Problems with transportation at the airport.

jhawk complains about having to attend his annoying cousin's wedding. "I wish there were no flights next weekend. That way I could skip my wedding and go to readercon." "Are you getting married?" "No..." "You could kill your cousin and get married in his place." "Or you could kill him and collect life insurance."

Discussion of sci-fi series.

Does "splat" mean asterisk? Like "bang" for exclamation point.

Skinner has feet.

3 power outages coming in the next few weeks on Thursdays, lasting 12 hours and beginning at 7 PM. Explanation: high voltage power switches have been decertified (product flaw) and they will be changing them.

"No open flames in the library."

Discussion of torches, electric and otherwise. The British don't know what a flashlight is.

jhawk saw "Wild Wild West."

Discussion of origins of movies and series such as Men in Black and Highlander.

Some new authors are coming in the fall.

Blah blah blah.

"Hello, friend Laureen!" She can sit with Jenwa's stuffed animals.

\goto{Future Business}

Twilight Zine. "That's not future, that's hypothetical."

Skinner is bored.

jhawk implies he has webbed feet.

\vspace{12pt}

\noindent
Meeting adjourned as I'm out of paper, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
