\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 2, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

(Note: these minutes were written with the left hand of the onseck, as her right one hurt too much. Isn't that impressive? If you want to gaze at the original in awe, you'll have to ask the current onseck to find it...)

Minutes read.

M: commend minutes for having no t. 11-3-1 +Spehn.

Jen putting earring in mouth.

\goto{Committee Reports}

Mobcomm: 40 pounds of books.

Bluebellcomm: still books to be shelved.

"I've typed with my nose by hunt and pecking."

M: put harmonica on gavel and pound it. 11-5-6 +Spehn.

Moocomm: WDS liked The Matrix! Wow!

M: commend SF. Passes by skinnerial decree.

Star Wars trailer discussion. Comes out Wednesday of finals week.

Computer people can work anywhere. They're coming out with a computer that runs on a crank. Some computer discussions. Computer monitor and back massager.

Sitcomm: Futurama didn't suck.

\goto{Old Business}

Onseck begins to ignore rest of meeting... too much hand hurts.

M: hurry meeting along.

Style points go down. Need new country to make fun of. Lots of suggestions. Russell Miller (aka the one eyed man in the kingdom of the blind) is now the ambassador to sloan. Brain discussion.

\goto{New Business}

"I'm the Skinner, I don't need a second!" "You don't need a second to commit seppuku?" "I have something that's very 'sheep.'"

M: Jen getting job. 17-7-2 +Spehn.

Talk about space. Move to E51? NOOOOOOOOOooooooooo...! E51 couches creepy. Jen has slept on it before. "With who?" (Ambassador to Sloan)

\goto{Future Business}

(Crossed out) Bill Gates banana.

M: hand that hurts should be bathed in banana flavored steam bath (Jenwa). 1000000-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
