\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 14, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

ELECTION MEETING!

M: I need a better pen. 14-3-3 +Spehn.
SK chased by chair.
"Bad chair, no biscuit, no SK for you." 10-0-5 +Spehn.
"If the shoe is higher than the table, it counts as a vote."

\goto{Committee Reports}

Dexmaster confused about new and old books. JM fixed it.

Mobcomm: SK is now a SB member again; new books.

Bluebellcomm: 1/2 day empty.

Hasslecomm: never empty. Are they dead?

Panthercomm: Phantom Menace copy already.

Door propped open by eraser courtesy of Sara.

ROSFAP got index cards!

Picniccomm: still going well, ordered food, etc.

Pseudo-analogcomm: request summer hours! Either by person or by mail if you *suck*!

Our-advisor-might-comm: we should put him on our mailing list.

Honorary membership or something.
Lenscomm? Where? Died...
(sound of many pages tearing)
Discussion of getting cameras.
Camera suddenly appears.
Pictures of Ed and Justin happen.
Junk food happens.
M: commend Sara for the food. 17-2 "I don't have any"-5 +Spehn.
"You can eat gummy care bears if you promise to eat them feet first so they suffer longer."

\goto{Old Business}

Jen's thesis still not funny. Supposed to be done 1 week ago.
Jamie: "these taste funny, are they poisonous?"
Sara: "they taste like care bears."
Food keeps passing by.
Discussion of Jen's advisor's living or non-living state.
M: commend Jen for having a holographic zephyr-bot advisor. 21-0-5 +Spehn.
(She hasn't touched him, how would she know he isn't one?)

\goto{New Business}

The table has one segment too many.
It's for extra safety when summoning demons.
Care bear gummies making us nice and friendly people.

Elections!!!

Skinner recommends candidates:

Jenwa: LHE to Skinner.

Aaron: Vice to Vice. Bill complains that Aaron doesn't look like a Vice, even with that tie. He wants Jade to be Vice. "Jade's only 12." "Even better."

Jade: Onseck to LHE.

Natasha: Nothing (keyholder without key) to Onseck.

Talk about Assassin vs. SWE. Is SWE still claiming all females at MIT?

Care bears have hearts on them...

Natasha should be onseck. Can she read and write? "I've never seen her read." (JFC) Well, then she must not be able to read and write. She's a witch!! So she weighs more than a duck.

Vanna: that compulsive Terry Pratchett quoter. "I have blonde hair."

Elections: 

Onseck nominees: Jen's thesis, The Fish, Gummi Care Bear Collective, The Lost Watches, assistant Vice, the person who isn't here, The Hallucinations, NO, Unclosed Nominations, Fargo accent, confusion.

LHE: "1 full vote, divide any way, 1/10 precision."

"This is too small. You may not fold your votes this small, because instead of unfolding the 37 layers and reading it, I'm going to eat it." Skinner eats it. Applause.

Skinner performs "NOOOOOOOoooooo..." Applause.

"This is also too small..." but she throws it out the window instead of swallowing. "It's not too small if you don't eat it!"

LHE: "I can't add." "Use the calculator." "She's just trying to hide the fact she can't use it." "She was traumatized as a child by a calculator."

Skinner: "As I was walking down the stairs/I met the one who wasn't there/She wasn't there again today/I think she's from the CIA." Applause.

The last word of Jen's thesis is "barriers."

LHE nominees: beings contained in tight leather clothing (recorded as "tight leather people" by Vanna), The Velveteen Jade, Jen (Jenwa: "She did a shitty job last time!" "Jenwa holds a grudge!"), Jenwa's grudge, Finboard, the filtered, the dead fish, the yellow thing on the floor, how much sleep did you get last night ("Jamie's already thought of his vote." "You planned for this!"), old jokes, 12-year-olds in tight skimpy leather clothes, Nabokov Nabokov.

Jen thinks chicks = Chuck Vest... hmmmm... Pictorial ballots confuse her.

Jen expouses on her thesis as Jenwa counts.

Vice nominees: Vanna's handwriting, Velveteen Jade instead of Al Gore (now with leather), snuffle, Snuffleumpagus, don't ever say at Hubba-hubba ("Does this come in children's sizes?"), CIA, KGB, and other TLAs, TLAs in general, TLAs in specific, Sara, Sara with dead fish, hard chewing gum, Jenwa's expertise (i.e. leather gerunds).

Jen sings M-I-C-K-E-Y M-O-U-S-E. Jen sings again.

Aaron wins with "things that are AMU-like."

President nominees: sound of silence, mighty Cthulhu's 17th tentacle ("Where do you start counting?" "Don't ask."), behold the pudding moveth, Jenwa's expertise, Telzey's girlfriend ("Evaluated when?" "Carefully."), a small pudding on the last 4 skinners on 4 tentacles of Cthulhu in 3 cubic centimeters of leather.

Jenwa's declared as Cthulhu's representative to MITSFS. "When stuck in... I was forced to survive by eating Cthulhu."

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
