\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 17, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

Motion to approve minutes as being an inspirational end of the Millennium. X-7-6 +Spehn.

\goto{Committee Reports}

Sitcomm: there is going to be another TV movie of Flowers for Algernon. Collective groan.

Mobcomm: more new books. Many not worth reading.

AMU: "There should be more good books." Someone mentions Dune. Argument whether late authors are better than dead authors.

M: take the spare breast from Amazon.com and auction it off on eBay. Passes.

\goto{Old Business}

Toby, an old keyholder, came by.

35 t-shirts have been bought so far.

We have had a 75 dollar fine this week.

John Norman's real name is John Frederik Lange Jr.

Should we process the Apostles books- still waffling- let's process 2. Let's give one of them to Ed to read and have him send an email telling how good it was. It's in a small font too...

M: use the small font to baptize John Norman. Passes.

\goto{New Business}

Boxes for Cheerios called Millennios sighted in supermarket.

People mill around looking for new business.

\goto{Future Business}

M: congratulate skinner for having somewhere to go after the meeting. Passes.

Skinner should read "Nine Taylors" by Dorothy Sayers because it's about bell-ringing.

Next meeting should be negative length or elsewhere. The only Star Chamber person here will be JM- move meeting to Star Chamber.

Any business- "I don't care what kind." (Skinner)

M: risky business. Passes 9-2-X +Spehn.

M: invest our endowment fund over Y2K in a stock charting the number of bananas in the market. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
