\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 3, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: approve minutes as stuffed and covered with gravy. Motion turkeyed.

M: minutes less tasty than turkey. 4-1-1 +Spehn.

\goto{Committee Reports}

Mobcomm: new books appeared. JFC: "The Diana W. Jones book is not my fault."

Motion to acquire Diana Wynne Jones for the library. Passes 13-3-0 +Spehn.

Bluebellcomm: not Y2K compliant. Some books circulating till X/X/1900.

Tackycomm: got plastic bookcovers. We now have one covered paperback in circulating.

jhawk ordered a couple of books to be circulating copies.

Mobcomm: Star Chamber are too lazy or not lazy enough (i.e. too busy).

M: commend Mobcomm for reminding skinner about GREs. Passes.

Let's go on a bookrun 5 hours ago! Maybe that's why the money's missing. Jade: "We actually discovered time travel..."

Skinner: not going to be here for IAP.

M: all prospective Natashacomms should turn the stalking up a notch. Passes.

Jadecomm: Jade has glasses.

\goto{Old Business}

WDS: "Some attempt to land something on Mars. News blackout about outcome."

\goto{New Business}

MITSFS is going to celebrate millenium by running out of space.

\goto{Old Business}

We still have a Quaker Oats box of juggling balls- apparently they belong to some member. M: get Jenwa to juggle. Passes by skinnerial decree.

Cops now know about our missing money problem. WDS: "We should rig a death trap."

\goto{Future Business}

M: hide petty cash inside a giant banana. Chickens.

M: same, inside a small banana. Chickens 12-3-15 +Spehn.

M: hide onseck inside a large banana. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
