\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 5, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; JFC, Pseudo-Onseck, recording.

Minutes read.

M: regard minutes as brilliant. 4-0-0 +Spehn.

M: seal away minutes. 14-0-2 +Spehn.

\goto{Committee Reports}

LHE: phone bill paid.

Pseudo-sitcomm: nothing useful on TV. Missed sentinel.

Pseudo-picniccomm: AMU again.

Theftcomm: new hours, sign up says pseudo-analogcomm. Prentices should finish, says Justin. (Who grew a beard since starting.)

Sitcomm: Dilbert was okay.

Discussion of ficus (masculine form of FICA).

"No tax-sexing." "How to bleach your home."

Mobcomm: books!

JM: is this brown chair ours? Digression into what to do with a chair we don't have.

Concomm: Boskone next week. See Ellen if you want to go.

Justin: WYSIWYG fnord program. Jenwa has a good grip on it.

M: condemn skinner for binging with us, not Telzey. Fails!

M: condemn skinner for abusing power. Passes!

\goto{Old Business}

Classes started.

Jen is sick.

Visitor sits in keyholder chair.

Jen yawns.

\goto{New Business}

New term! Everyone is happy!

JFM taking 72 units, all required to graduate.

17.805 uses incomprehensible vocabulary and is joint with Harvard.

M: dondemn Harvard for interesting without classes. 7-0-4 +Spehn.

Alum mail RSN! Money money money!

Jay is sucking Jenwa.

\goto{Future Business}

After 0 verses of the skinner song, meeting is adjourned by skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
