\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 10, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

Some motions about minutes being written by not Norman (author of Gor books) fail for lack of second.

\goto{Committee Reports}

Pseudo-mobcomm: book run tomorrow.

M: slap Justin silly. Passes.

Jourcomm: failed to hunt down sci-fi class; it's taught in the spring and not by Haldeman.

\goto{Old Business}

Galaxyquest: a fake series- like Austin Powers. Anniversary on TV.

Mars probe still missing.

\goto{New Business}

Article in Glob: take cells of your pet for cloning in the future. Charges for samples and storage.

\goto{Future Business}

M: world is ending in 21 days. Fails 5-7-3 +Spehn.

Skinner: "Is there any more future business? I'm going to start reading my book again..." "She's playing with his slinky."

Miller motion. Fails a couple of times.

Tertiary Miller motion. Chickens 10-0-10 +Spehn.

Jenwa threatens to read her book again.

M: insert a banana into Jenwa's book. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
