\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 23, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

Motion to announce minutes as mumbled. Passes?

\goto{Committee Reports}

Move to redye Onseck's hair. Passes 5-0-0 +Spehn.

Mobcomm: did something clever: bought cheap books, turned them in for store credit, and got SF books for us.

Do we have an appraiser? No. Do we have a clue?

Sitcomm: "Good vs. Evil" did premiere last week. WDS: "My VCR watched it." Discussion of VCR opinions of shows.

Door alarm is presumably fixed. Will police know when it goes off?

Discussion of bugs and other listening devices. "Is a one-way string possible?"

\goto{Old Business}

None.

\goto{New Business}

Discussion of answering machines and the value of turning on the volume on them.

Discussion of telephone usage.

"JM wanted to move the bookshelf in the new books." Decision to permit this: "Yeah, let him do all the work."

When are we going to get rid of our old computers?

\goto{Future Business}

Radioactive spacecraft of death Cassini is hurtling towards Earth.

Banana song.

Banana motion chickens.

Blah blah blah.

Jade comes in wearing a banana colored shirt. And there was much rejoicing. "How did you get them to fix the alarm?" Jade: "I asked them politely." "What does that mean in your culture?"

Jade learned how to spell her middle name in high school, but recently found out that she'd been spelling it wrong.

Motion to replace Onseck's pen with a banana. Chickens.

Safe lock does not like Jade.

Motion to commend Jade for banana colored shirt. Passes! "Aaaahhh-\bing"

\vspace{12pt}

\noindent
Meeting adjourned, 1743 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
