\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 19, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: commend pseudo-skinner for getting the year right. 3-0-10 +Spehn.

M: bblt you could have told me before you went ahead and started! 3-0-2 +Spehn.

"All the motions thus far have failed for lack of a second."

Pseudo-skinner begs for someone to albanian J.

M: make J French. 6-0-6 +Spehn.

M: declare J Spehn-ish. 7-0-20 +Spehn.

\goto{Committee Reports}

Sitcomm: something about ABC's trigger.

Pseudo-ROSFAP: classified all not-zines.

"Is at Garbage?"

"No one's seen him for a fucking year and a half, but he's STILL a keyholder?"

Panthercomm: new list. Short list of books or something.

M: instruct onseck to compile a list of how many meetings Jen has missed. 12-3-2 +Spehn.

Pseudo-somethingcomm: Neil Gaiman spoke and was spiffy.

JEN TAKES OVER

\goto{Old Business}

New book shelf is getting old but that might change.

"Term was halfway done (whimper)." (Jen)

Seth Gordan still in Israel.

"Don't kiss Leanna." (JM to Jen)

JFM knows 6 Leannas.

M: commend JFM for Leanna knowledge. 10-1-7 +Spehn.

Notzines box now empty.

M: commend JFC for being unobservant. 7-3-5 +Spehn.

Muttering about duplex.

\goto{New Business}

Updated graph of space implosion thing.

Justin is going to run for undergrad member at large for ASA exec.

"When the bulk mailing tells me to, I will do stuff." (JFM)

Junk mail, assisted by sleep deprivation, has taken over our skinner.

6.170 is more important to Justin than MITSFS.

Have we given Pinkdex to libraries? Nope, we should get money.

Minicult: legislature is in session and no one is safe. Legal to eat roadkill, illegal to sell urine.

We want to get funded by the media lab.

24 hour headset thing.

Telzey is a geek. Argument about whether he is or isn't. Table top roleplaying.

Little \bing.

Talk of SFS and twinkies and stuff.

Christa's reading Xanth again...

M: ureghhehchh. 15-0-2 +Spehn.

"Jamie is old... almost as old as Jade!"

M: Jade++. Bigger and better. 13 is better than 12- a skinner's dozen. "I don't want to be a skinner's dozen!" "Well, whose dozen do you want to be?" "Can't I be my own?"

M: commend Jade for being self-contained. 14-3-5 +Spehn.

Keying stuff: whatever happened to the Great Lock Change? (Shh! Lame people will change at an inconvenient time without previous warning.) Getting keys for other groups is hard.

What happened at the SBM? Not much.

Justin is advertising Cthulhu.

M: commend Jamie for not looking like Cthulhu. What happens when you pass a motion about Cthulhu? Usually nothing.

Talk of how Cthulhu will eat us.

Skinner powers while in MITSFS!

M: commend skinner for using skinner powers only for good.

Why skinner is pissed and upset now: Oracle. No job offers yet? Aww...

Oracle: 1 hour November: Yay! 1.5 hours Mariott: yay, 99 percent chance of getting job. Wednesday: went to plant, went okay. Today: california to headquarters for interview. New Hampshire: California, nah, nah, we don't want her and you probably don't want her. Called and rejected!

M: commend Jen for not working for Microsoft. 22-0-0 +Spehn.

Texas, Austin? Technical writing.

\goto{Future Business}

M: change dancing paperclip to dancing banana. 11-5-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
