\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 4, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: \bing Does not pass.

\goto{Committee Reports}

Mobcomm: new batch of hardcovers here and already covered by the real Bluebellcomm.

M: say hi to Thunderbunny XXX. Fails.

Skinner: "The Thunderbunny doesn't have an XXX, it took her forever to get a Telzey..."

\goto{Old Business}

Sitcomm: the TV channel 56 is being assholeesque about the 2 hour long Star Trek Deep Space 9 season finale- showing it as two separate episodes. Buffy finale indefinitely postponed, though shown in Canada.

"Silent time warp"- we're not on committee reports anymore.

Jay: "Fish!"

Term is really over- now more people at the meetings after graduation.

Blah, blah, blah...

Skinner isn't hosed because she hasn't decided what she's doing this summer.

Skinner stuck her tongue out at LSC for waving a sheet of metal around.

\goto{New Business}

No new business?

Lots of new books- people should read them. (Though April books are still up.)

Hardcovers cost about 360 dollars.

We are running out of space. Okay, no more Stephen King, no more Jordan.

\goto{Future Business}

Inventory? Round up apprentices- all two of them.

Stickerboy: how can we figure out how many hours he's actually putting in?

Silence...

Skinner: "If you don't say anything, I'm gonna start reading my book."

Prentice project: edit Twilight Zine. Last one published 5 years ago. Jay: "Hype the coming of the Zine!" We have enough text, but need art. There was a deadline for turning in stuff for Twilight Zine!

We have too many empty boxes.

Discussion of shelf space; will have to cut back to 2 circulating hardcovers. There is space for one more shelf?

Onseck is bored. Motion to entertain the onseck. Passes 8-0-? +Spehn.

We should have our meetings live on the web.

\bing Motion chickens.

Motion to find out if onseck would be entertained by a banana. Onseck is duly entertained by the bananas :)

\vspace{12pt}

\noindent
Meeting adjourned (finally!), 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
