\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 29, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

"Would anyone like to make motions on the minutes?"

M: no. 2-1-0 +Spehn.

\goto{Committee Reports}

Theftcomm: not able to get slide in on time. Does that mean it will be ready for next year? It was the usual slide. "Usual slide!" "Usual debate!"

Mobcomm: new books coming soon.

Pseudo-jourcomm: jhawk and someone working on book reviews. RSN!

\goto{Old Business}

"Usual stuff."

\bing

(long confused silence)

\goto{New Business}

Next marathon? Each IAP (LSC). Jackie Chan marathon. "What do you get if you stay through the whole thing?" "Sick!"

New term.

Alumni people will stop saying no.

Hour requests.

Stop talking = more people coming in. Scaring them away? (scribble)

"Any more new business?" "Oh, the meeting, right!"

(Silence)

Prentice projects... need 2 weeks done... somebody needs to run them down...

(Silence)

Suddenly, a big glowing purple airplane shoves through the window and steals the minutes!

M: condemn most dead people for staying dead. Pseudo-apathycomm: yay. Fails for lack of second.

(Even longer silence ensues)

M: to bring back Jen because her meetings are more interesting. 5-2-0 +Spehn.

J complains that his reign was the "good old days..."

William Shatner singing CD. "We have to get it!" "No we DON'T." "It's not a suicidal society." "What about our space problem?" "We should ask people to pay us not to play it."

Housing space: house all frosh in L-space! "Genius!"

M: install bathroom in L-space.

M: banana dispenser in L-space.

(Long silence)

Minutes reappear.

M: mmmhmmmmmn. 0-0-0 +Spehn

Apathycomm claims victory!

(Members fall asleep)

God of apathy, god of procrastination discussion.

Truth vs. skepticism. Bravery vs. procrastination. Love vs. indifference. Long discussion of game. Really long discussion of game.

\goto{Future Business}

Adjournment by decree

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
