\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 20, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, Pseudo-President and Skinner, presiding; Jade Wang, Pseudo-Onseck, recording.

Minutes read.

The Gavel is rusted!

Everything we see was inside a star once. Discussion of whether novas produce iron.

Thunderbunny reacted with the metal of the gavel and had to run away.

Various people "rub the gavel." "Don't scotch tape the gavel."

Boring motions about the minutes fail.

Jade: "All those in favor." "Of torturing you?"

M: for Jade to splatter people's brains with the gavel.

M: to commend Jade for doing a good job. Passes.

Jade gets practice binging.

\goto{Committee Reports}

Mobcomm: book run tomorrow morning.

Pseudo-bluebellcomm: must cover the new books.

Fweekcomm: people should sign up for more hours. Fweekcomm is still behind.

M: commend onseck for raising her voice. Passes.

Pseudo-hasslecomm: Hasslecomm is behind.

Jade must control her power and not let it control her.

\goto{Old Business}

Some freshman are arriving- leadership programs, etc.

\goto{New Business}

Several motions to commend Jade for wonderful binging. Passes by a lot.

Magdex is done! Jade has finally earned her key.

Frosh get here real soon. Frosh are a good source of energy and nutrition.

M: commend frosh for being slightly less innocent than Jade pretends to be. Passes.

\goto{Future Business}

R/O week next week- actually, now it's just "O" week, as in "the story of." No mandatory events this year.

Jenwa is back on the 25th.

Justin keeps selling his souls to Cthulhu- how many souls does he have?

Pseudo-pianocomm: Justin changed a sticker last week. "Much rejoicing."

M: commend Jade for having a partially banana-colored shirt. Does nothing.

Jade becomes aggressive and adjourns the meeting.

\vspace{12pt}

\noindent
Meeting adjourned, 1783 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jade Wang, Pseudo-Onseck}

\end{document}
