\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2000}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 30, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JWH, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: condemn onseck for not spe-- 8-8-2 +Spehn.

M: commend pseudo-skinner for her bing. "Much better than Jen's." "Not even premature."

\goto{Committee Reports}

Mobcomm: more books.

"I'm reading a book called Prom Night." (JFC)

LHE: turned in budget request.

Thundercomm: not much longer. 20-0-1 +Spehn.

M: commend Jay "Thuuuuunnderbunny" Munchnij for being. 10-8-2 +Spehn.

\goto{Old Business}

M: Jenwa, tell us a story! 18-5-0 +Spehn.

"What kind of story?" "Kinky!" "Involving Jen!" "Not both..."

Once upon a time there was a Jamie who moaned and groaned a lot. One day he was on his computer and trying to figure out how to find an onseck and not getting far. So Jen and Jenwa had to figure it out.

Jamie doesn't think it's a good story.

\goto{New Business}

Alum bureaucracy: trying to navigate around it.
Is it already too late? Well, we can mail by Tuesday; still 2 weeks.

M: tickle Jenwa. Fails, Jenwa's grumpy, she threatens to hit people with the gavel.

M: make Jenwas take another bite of sandwich so she won't be as grumpy. 20-0-0 +Spehn.

"Skinner has no prescurse at all..."

Steer roast discussion.

\goto{Future Business}

"Yay!"

M: approve future business. 4-11-1 +Spehn.

"We have no future..." (Jade)

"Hey, that's bad for moral (sic)!" (JM)

M: make Jane the moral (sic) officer, 14-3-1 +Spehn.

Grumpcomm: goddamn Patriots.

Mars rover being tested. Navigation can't tell difference between air, thin bushes, and lizards.

M: tickle pseudo-skinner. This time, fails (no second).

Niles introduces himself.

M: condemn Jenwa for not noticing my brilliant pun. 11-6-0 +Spehn.

M: banana. 7-8-0 +Spehn.

M: force pseudo-skinner to consume rest of banana colored bagel. 16-4-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
