\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 12, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: no! 10-1-5 +Spehn.

\goto{Committee Reports}

Pseudo-bluebellcomm: covered new books.

Mobcomm: British book order! Email JFC if you want them. Banks and Pratchett we don't have/are notable.

\goto{Old Business}

40 hardcovers still waiting for covers.

3rd space still sucks.

Crusade is going to die.

Usual apathy.

\goto{New Business}

M: Jade's old. "How old is she?" 12-1-4 +Spehn.

M: commend Jade for being 12. AMU doesn't call the vote. Yay, 12.

Neil Gaiman something speak.

Sentencing noisy people to listen to Barney. 2 guys in Seattle were watching Analyze This and one guy wouldn't shut up so the other shot him. "About time."

Unveiling of second trailer for Star Wars Wing Commanders. Statistics for Wing Commander.

"Anakin is still cute." The cuteness that JMS would have conniptions about if he appeared on B5.

"McCaulay Culkin as Ender." NOOOO!!!

M: Ender's Game as a movie. Fails for lack of second.

M: sorry. 8-5-4 +Spehn.

(Cough cough)

(Cough)

Found another soon-to-be missing book. Make the books out of glass so we can see past them.

\goto{Future Business}

M: obvious: condemn Food. 12-1-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}