\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 22, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: commend minutes for being artistic. 9-5-1 +Spehn.

\goto{Committee Reports}

Mobcomm: got books after meeting. Fourth new Weber book in 4 weeks.

Pseudo-libcomm: Jade discovered it wasn't what she thought it was. Efforts to revoke her key are in progress.

Pseudo-theftcomm: asked finboard for money for LSC slide, so we should do it.

(Click! Flash!)

\goto{Old Business}

Running out of space!

Derrick Colm was in town and commented on lack of space.

M: say hi to technique people. 3-1-2 +Spehn.

Spehn less than 1?

Usual motion.

\goto{New Business}

(Muttering in background)

Units of time on Mars: minute = minute! Tirade by JM. "Every human being has an intuitive sense of how long a minute is! Even newborns in the womb!" "What about premature babies?" "Their schedule is messed up!" "Because of daylight savings?" "No, they have a Y2K problem."

M: to flay (filet) people who are messing with the martian minutes. 8-4-0 +Spehn.

Bookcases, so some people should go see if they're useful.

(Long silence)

M: apathy motion.

\goto{Future Business}

M: Miller Motion! Seconded. Fails. \bing

M: Second Miller Motion! Fails. \bing

M: Third Miller Motion! 10-9-1 +Spehn. Chaos ensues.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
