\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 12, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: approve minutes as having lots of mention of bananas. Fails 4-12-6 +Spehn.

\goto{Committee Reports}

Pseudo-natashacomm: Jadecomm sucks.

M: appoint Natashacomm to monitor Natasha's activities. 24-6-0 +Spehn. Discussion of logistics- trial week- then report and appoint 3 best people permanently.

New MIT webpage.

Jade to JM: "You should keep up with the times." JM: "You don't read the Tech and don't know about the Capital campaign." Jade: "What capital campaign?"

Pseudo-pianocomm: Debbie came in and talked to JM about Magdex, then said she would come in yesterday and didn't.

Moocomm: 6-string Samurai showing this weekend.

Mobcomm: should do a run for new books soon to have books for IAP (because skinner isn't going to be there).

Anti-mobcomm: got flyer from a place that buys up collections of books from libraries going out of business.

Pandemonium sale this weekend- 25 percent off. "People buy cheap-ass games on sale?!?"

T-shirtcomm: t-shirts RSN. If we were really evil we would hide one of the t-shirt boxes.

\goto{Old Business}

Move to commend Natasha for being big. 12-12-12 +Spehn.

Move to call Natasha something that means "small" in Chinese.

Some motions about nicknames for Natasha fail.

M: swap Jay and Jade's names. Passes 17-12-0 +Spehn.

M: call all members Natasha. Fails.

\goto{New Business}

Library needs more shelves.

Jay's [actually Jade's] brother (1 year younger than Jay [actually Jade]) got a girlfriend- Jay [actually Jade] outraged. "He turned into one of those guys who only hangs out with girls- it's him and a gaggle of girls." WDS: "How awful for him."

M: condemn and commend Jay and Jade and their respective siblings. Passes 14-smaller-much smaller +Spehn.

\goto{Future Business}

M: commend Cthulhu for wearing Yevgenia under it. Passes.

Discussion about Cthulhu.

Motion to obtain banana colored Cthulhu for the library. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1733 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
