\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 1, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: condemn Jamie and Jade for conducting real business during meeting. Passes X-4-3 +Spehn.

M: reading of minutes vague- matrix vote? Passes.

Bogus motion about Albania passes bogusly.

\goto{Committee Reports}

Mobcomm: new box of new books, 3 of them worth reading.

Theftcomm: bulletin board redone.

Pseudo-pianocomm: new "So You Want to Be a Keyholder" sheets out, maybe someone will want to.

Sitcomm: "7 Days" season premiere really bad. WDS couldn't watch it. M: commend WDS for not watching a bad show.

WDS: "Why are those people having a meeting over there?" JFC: "If Jade called you over, wouldn't you come?"

Marion Zimmer Bradley died last Saturday.

Evan Vogt is not dead yet, though institutionalized.

\goto{New Business}

We demand new business!

T-shirt distributor is still being lame- the t-shirts are still not here.

\goto{Old Business}

M: condemn society for discussing real business. Skinner squashes.

M: commend skinner for being a dictator.

M: nothing's ever passed in the history of MITSFS. Passes.

People should send MITSFS more good postcards.

Skinner: "Could someone besides Jade tackle Jay for me?"

M: to have a chicken in every pot.

M: to put a banana in every pot. Fails something-something else-something +Spehn.

M: commend skinner for being a math major. 11-4-4 +Spehn.

Math majors can't add, EAPS people don't know where they are.

\goto{Future Business}

M: commend skinner for knowing how continents move on the surface of the molten banana. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
