\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 26, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: reader has such *cute* things in her hair. 12-1-2 +Spehn.

\goto{Committee Reports}

Sitcomm: coming soon... Total Recall 2070!

Pseudo-computercomm: AC no longer asks for F1 when you boot it. Added a virus to make it work better.

Skinnercomm: skinner has wet stuff on her fingers. "It's actually Canadian nail polish." "...is it compatible with the Total Recall thing which changes color when you hit it?" "No, but if you hit it hard enough..." "The new Colormaster 2000(TM), i.e. the Gavel." "Would you like to try?" "No, I don't color my nails."

Pseudo-fluffcomm: buffy. Really missed out.

Sitcomm query: 6 hours of Storm of the Century by Stephen King. Should I bother? No one watched it.

(Music from outside)

Can we close the door or I will record music?

\bing

Secret meeting of the MITSFS! No!!!

M: something onseck for being able to record music, 13-0-2 +Spehn.

Discussion of computer chips and playback and how I'm a biological chip?

Stock market has nothing to do with reality, just with expectations.

Justin gives long explanation of stock market.

M: jolt Alan Greenspan. 14-1-3 +Spehn.

Pete Gamache to Jolt Keg. Justin knows a lot about Jolt. So does Jen. New flavors of Jolt!

\goto{Old Business}

"Last week I was sick." Me too. Me too (three). Me too (four). Four. "I went to the medical center." "Why would you...?"

Talk.

M: commend sentient abnormalities. 12-0-5 +Spehn.

Why medical center? Because insurance and cheaper.

This meeting has too much to do with reality... stock market, insurance... grr...

Justin has a parent who eats at the food trucks.

Jen is taking a driving test soon. If it's in Watertown, Moody Street must be involved. Isn't Moody Street in Waltham? Whatever.

\goto{New Business}

Justin is becoming something complicated to do with Harvard.

Telzey and skinner went to masquerade ball as... evil genius immortals from Highlander. We didn't prepare! Tinfoil sword fell apart- should've made a katana. I don't bring weapons to other people's parties. Not the right parties...

Massachusetts weapon law. So all you have to do is bring your wall? No, it's "transport." So all you have to do is tesseract.

\goto{Future Business}

M: BANNANNA!!! 13-0-8 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
