\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 5, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Whine: something about leopard spots. "Don't tell me, I don't want to know."

Motion passes. "Why are we having this motion?" No, we're not having this motion.

Minutes read. Minutes interrupted. 5-0-1 +Spehn.

\goto{Committee Reports}

Pseudo-panthercomm: lots of not quite new books to be shelved.

Jadecomm: Midway sign was getting mangled- moved. Why Jadecomm? Because there's no Natashacomm.

\goto{Old Business}

Man in NY suing for 25M because he was stuck in an elevator- Justin should too. Then we can build a new shelf to collapse this building.

Lobdell closes earlier now, though Harvard serves meals at midnight.

Discussion of Pritchett food. Stops because we can't bring food to library.

T-shirtcomm: t-shirts RSN.

\goto{New Business}

New Sandman book out. We don't have Sandman series- lameness and expense.

Discussion of whether people could go into MIT libraries.

Old and slow business: slide got only JFC's applause at Friday's Star Wars showing.

Discussion of how silly a movie "Wing Commander" is.

Hair does grow after you shave it, or does it? JFC: "I got a haircut- look what happened to my hair."

Scavenger hunt: find the man with a hole in the back of his head.

Discussion of which way is closer to stairs or elevator, if you use the proper door passing technique.

\goto{Future Business}

Banana monkey business motion chickens. Making bananas motion chickens.

Jay: "Skinner has no hair at all." Song.

M: club all singers with large bananas. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
