\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 19, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: you've got a noodle... Seconded! No vote called.

\goto{Committee Reports}

Plantcomm: ordered ceiling tiles.

Pseudo-mobcomm: Baen books = books to nominate for the Hugo if we're going to Worldcon in Australia.

Pseudo-concomm: Boskone. Sold books, lame people, good con, decent money.

Pseudo-sitcomm: sentinel was cheesier than usual. Enough half-naked men? No, sports episode. "I thought they did the olympics naked."

\goto{Old Business}

M: condemn efficiency. Fails by skinnerial decree.

M: condemn Bluebellcomm. Passes by skinnerial decree.

"Evil ARLewis suggests NESFA will give us money to bind magazines."

Lecture yesterday by SF people. All the excuses come out as to why people weren't there.

2 more business cards and authors coming by and email... yay.

\goto{New Business}

Review more books? Membership fine credit!

Fundraising stuff. Senior rep for 1999 is Jen!

Jamie doesn't remember what gift his class gave.

JFM is now an existing lackey.

M: commend JFM for existing. 9-4-1 +Spehn.

JFM's head is not here... it's under the blankets...

JFM wants to tell all seniors to earmark their donations to MITSFS.

M: "If I only had a banana." \bing

Ed says the Alumni Association hasn't been responding and he will beat them.

LHE hosing self with assassin's game!

Banana in liquid nitrogen and smashed picture. Inscrutability of picture comments.

Chinese calculator discussion which responds with a suffusion of yellow if answer is greater than (or less than?) four.

"If you eliminate the improbable, whatever's left, no matter how impossible, must be true."

No. No. No. No.

M: YES! 9-6-8 +Spehn, read as "12-6-8 +Spehn."

\goto{Future Business}

Miller Motion! etc. 5-8-0 +Spehn.

2nd 3rd Miller Motion.

3rd 2nd Miller Motion. 11-4-10 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
