\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 15, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
JFM, President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

No motions on minutes.

\goto{Committee Reports}

Mobcomm to panthercomm (or vice versa): where are all those books you promised? Supposed to come in but didn't.

\goto{Old Business}

Skinnerial travel woes.

Job interview today in Washington.

(This section of the minutes has been edited out due to technological limitations. Please consult the original for a full description.)

Train? 13 hours, because it stops at New York. "That's your problem, lady. New York."

M: let's blow it up. 14-1-1 +Spehn.

"Isn't it too warm for a room like this?"

\goto{New Business}

Repeat of last week: Jen (ex-keyholder and *chamber) on Monday and tonight.

Sticky fingers of time?

Discussion of dark and light Jen. Skinner was "milk" Jen because milk carton for UMOC and won.

Dr. Who marathon tonight at 6 PM.

Discussion of Dawson's Creek.

(Mumbling)

(Odd picture of cartoon girl because onseck is weird)

Holocaust films discussion. Wet feet discussion. We all get bored.

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
