\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/15/1999}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS meeting minutes

Friday, October 15, 1999

\end{center}

\vskip 12pt

MITSFS meeting called to order, 17:00 SST, October 15, 1999.

Jade Wang, pseudo-skinner presiding.

John Carr, pseudo-onseck (so whatever happened to Natasha?)

The pseudo-onseck read the minutes of last week's meeting.

On request from the skinner, the pseudo-onseck read the minutes of last
week's meeting out loud.

Motion: commend minutes as the truth, the whole truth, and nothing but
the truth!  Despite what Jade may say.  Passes 13-4-2+Spehn.  {\bf BING!}

Pianocomm: J. Goldstone wants to de-dormant.

Pianocomm$_2$: A prentice (Stefanie) shelved books!  Just like the
``So you want to become a keyholder'' document says.

Pseudo-Jadecomm (Justin): Roswell was ehhnnn.

Pianocomm$_3$: Armanard is here.  Motion to say ``hi'' passes 9-1-6+Spehn.

Motion: ``I think so'' passes 4-0-3+Spehn (Spehn is apparently less than 1).

\vskip 12 pt

\centerline{Old business}

JM reminds JPW to bing.

Motion: Commend Jay for having been clairvoyant.  Passes 9-2-1+Spehn.

We have a person here who was a keyholder before someone was something.

T-shirts in another week.  Add ``T-shirts RSN'' to Algol.

Justin has a pointy knife.
Jade has a gavel.
Hers is longer.

Jade adds ``weight also matters.''

Jamie: query about ex-MITSFS member Russell Seitz led Jamie to find a
``Boskonian'' reprinting a {\it Globe} article from 1969 saying that he
had the parts to make a nuclear missile.

Justin feels old.  Jade feels ancient.  ``13?'' asks Jamie.  ``No, 100''
replies Jade.

The usuals$\ldots$

\vskip 12pt

\centerline{New Business}

There is food here.

Jamie: We got spammed by a company I won't name.

There is a brief discssion about Pinkdex changing fonts from Bookman
to Times.

\vskip 12pt

\centerline{Future Business}

Motion: Print Pinkdex in London?  (fails, no second)

Motion: ... or Dingbats? (fails, no second)

There is talk about mailing Andrew back to IBM, followed by a motion
to squash any proposals that would involve stripping Andrew.  Motion
passes lots and lots to some to very little plus Spehn.  Andrew remains
unstripped.

Motion: say ``hi'' to eggplant.  Chickens a few to zero to lots plus Spehn.

Motion: commend pseudo-onseck for being incapable of writing and listening
at the same time.  Passes 8-0-2+Spehn.

The ASA rerooming process is starting.  There is a long discussion including
``Damnation Room,'' ``Annex Laverdes!'' and discussion of taking over the LSC
space when they go broke.

Motion: Just kill LSC and get this discussion over with!  Passes 8-0-1+Spehn.

%Jade laughs at Justins little, pointy $\ldots$ knife.
Jade laughs at Justins little, pointy ... knife.

Sitcom: ``Battle Jade'' premieres next semester.  Everyone ``aww''s Jade.

A motion to end the meeting is declared out of order by the pseudo-onseck.
``You should at least put a banana in it'' passes a lot to very, very little
to less plus Spehn.

Meeting adjourned at something like seventeen-something SST.


\end{document}
