\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 28, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: Onseck should be more assertive reading the minutes.

\goto{Committee Reports}

Mobcomm: NEBM run tomorrow.

Skinner: we are getting 800 dollars from Finboard. "We should get a bookstore to finance the library."

Sitcomm: Buffy showing delayed this week.

Phonecomm: ring.

\goto{Old Business}

Shortly before meeting skinner told "Christian groupies" that she was with the Campus Crusade for Cthulhu.

Discussion of a "ban of genetic material in Cambridge."

Dweebcomm: "Someone at LaVerdes paid for OJ and a bagel, costing 3.64, with a hundred dollar bill and got away with it."

CSB: "Some professor thought I was a math major for the longest time..." NO: "Probably because of the turtleneck."

\goto{New Business}

The son of Nikita Khruschev is studying for the US citizenship test.

Discussion of "trans-Siberian vodka pipeline."

Mystery of ceiling tiles.

\goto{Future Business}

M: undo changes to books.

Equip an S and M dungeon out of a Farming catalog: cattle prods, artificial insemination, branding irons.

Bondagecomm: to bind mags. Have bindable mags to bind.

T-shirts: hope prentices will get to it.

estevate (v)- (1) what an animal that is dormant in the summer does; (2) watch movies with Martin Sheen in an air conditioned theater.

Headline: "What black men like between covers."

Skinner: will send mail about inventory. "Did Jen do anything as skinner?" "Should I try to bing in a different way?"

If colors on X-ta were reversed, she would be banana-colored.

Upholstery motion chickens.

Motion to instruct Vice to do interesting things with banangaroo. Passes.

Motion to insert the word "banana" into the Croatian constitution. Passes unanimously 16-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
