\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 10, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jenwa Hsung, President and Skinner, presiding; Natasha Olchanski, Onseck, recording.

Minutes read.

M: reading of minutes is fried. Passes.

\goto{Committee Reports}

Mobcomm: none of the new books are worth reading.

Pseudo-mobcomm: Harry Potter books are worth reading. "They are the Teletubbies of books."

Moocomm: LSC is reshowing Matrix on Sunday at 4 PM.

Sitcomm: Playboy had pictures of actress who played Ivanova in B5.

It was worth paying money to put slide in LSC- people cheered.

Pseudo-mobcomm: debate on children's books. When are we getting Sandman?

Pseudo-analogcomm: nothing to say.

Pianocomm: Justin: starting to get going again. Put on 12 stickers.

People are lame.

T-shirtcomm? T-shirtcomm? JWH: "Where the fuck are the t-shirts?"

Mistcomm: Jade was missed in the mists of time. "Huh?"

\goto{Old Business}

TARL may be used to record meetings! Does it still work? It needs an Albanian function.

Usual motion, usual second, usual result.

\goto{New Business}

We can get moving shelves if we can convince MIT to give us 60K.

jhawk beeps.

ASA is becoming too evil for Brian.

Skinner needs a new shirt.

Monday the 13th the moon is gonna be blown out of orbit.

Jade sold a membership!

M: commend Jade for being tickled and making squeaky noises. Passes. Jade does not oppose- skinner to the rescue.

Are women monopoles or dipoles?

Are we going to use the data to figure out when people buy memberships?

\goto{Future Business}

M: to have naptime. 17-0-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Natasha Olchanski, Onseck}

\end{document}
