\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 12, 1999

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
AMU, Pseudo-President and Skinner, presiding; [Unknown], Onseck, recording.

Minutes read.

M: No! 3-7-2 +Spehn.

\goto{Committee Reports}

"Snickle snickle snickle snickle snickle snickle."

Pseudo-bluebellcomm: stacks of hardcovers which Bluebellcomm isn't covering.

Theftcomm.

Boscomm: Boskone almost started. JFC offers ride tomorrow.

Yawncomm: yawn.

\goto{Old Business}

Apathy.

Have we sent mail?

\goto{New Business}

"For this I woke up." "For this I stayed awake."

M: commend meeting for being exciting. 3-1-6 +Spehn.

\bing "Oops."

Pseudo-skinner has a calculator watch. "Eww!" Comes in handy! Never know when you'll need to know the square root of 19. "Don't you memorize it? That's what I keep *this* (points to brain) for." "Oh, I thought that was just to fill the hole in your head." Balance is off without it. Hats help with that.

M: condemn hats. 3-4-1 +Spehn.

\goto{Future Business}

M: commend hats for rubbing off JFC's banana-colored hair. (delay) 3-6-0 +Spehn.

Skinnerial decree ends meeting.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
