\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 22, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to commend the minutes for being completely indeterminate passes 11-4-2\ps.

Thunderbunny eKate: I never had help remembering the numbers.
MKR: You never seemed to need it.
KCR: Maybe it was because you said them more assertively.
eKate: Oh. Well, most of the numbers were a lie.

KKB has finished her thesis yay.

Motion to commend the thesis for being done passes 20-0-1\ps.

\bing

\goto{Committee Reports}

\subsection*{HassleComm}
HassleComm did work on hardcovers. Now BlueBellComm has to do work.

KKB: There seem to be a lot more people with power to do timewarps. The revolution is coming.

\subsection*{Trojan}
The people who want to donate keep emailing us. Trojan will take care of this now that her thesis is done.

\goto{Old Business}

There was a picnic.

Usual motion. Usual complaint. All this has happened before and will happen again.

\goto{New Business}

Summer is here.

There are pretty signs in the Infinite. Trust the Core. Remember Byron.

Any motions? Sold.

The motion to ``sold!'' chickens 0-6-8\ps.

\goto{Future Business}

KCR: In the future there will be telepathic space goths.
EKate: Chekov is totally not a space goth...
KCR: I wasn't talking about him.

Motion to annoy the onseck fails for lack of a second.

KCR: I don't like being hit over the head with metaphors.
eKate: But he's pretty...

Motion to send a banana back in time to annoy the Minbari government passes 13-0-3\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
