\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 21, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, Lord High Embezzeler and pseudo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to commend the minutes for being more entertaining than we can easily handle passes 13-0-2 \ps.

\bing

\goto{Committee Reports}

\subsection*{FrustratedAuthorComm}
They had an event where they lowered an agent in a shark cage into a room full of starving writers and you could ask them questions.

\subsection*{Star Chamber}
The new membership rates have actually been printed.

\subsection*{pseudo-AnalogComm}
You should send in your hours preferences, soonishly.

PW: Hopefully this time they'll get my initials right, meaning hopefully this time I will send them the correct set of initials.

\subsection*{pseudo-Trojan}
The large number of books we received this and last week has been dealt with. Now it is MIT Gift Office's problem. Yay.

\subsection*{Trojan, the actual one}
We got a lot of donations. Mr. Joblove has sadly passed away, and left MITSFS his science fiction and fantasy collection in his will.

\subsection*{VanHelsingComm}
I need a copy of Twilight, damnit.

\subsection*{hBarcomm}
The sign in the Infinite Corridor is slowly improving.

\subsection*{Onseck}
The TVTrope ``Woobie: Destroyer of Worlds'' is now in the minutes. It deserves it.

\subsection*{pseudo-PainOfSpacecomm}
The scanners can be put into storage now. The NESFA guy came, looked at our microfilm and microfiche, and decide that he liked what he saw.

\subsection*{pseudo-Skinner}
Rush is coming soon! The week after Rush, Keyholders will get full credit for any impromptu hours held, in order to encourage Keyholders to keep the library open as much as possible so new frosh can stop by whenever is convenient for them. Email will be sent out on this subject Real Soon Now.

\subsection*{pseudo-Seldon}
We do not currently have a Seldon for the spring, and are looking for one. ACL volunteers for the position, tentative until Miss Katie Ray approves it. 

\goto{Old Business}

MGH: They apparently make cotton candy out of maple sugar. If I can acquire some, I will share it with the library.

General library: Wait, could we modify a centrifuge to make a cotton candy machine?

PW: Let us *not* modify lab equipment for that purpose.

MGH: It kind of unnerves me that people might consider using reuse lab equipment for cotton candy machines.

KKB: As long as most of the hydrofluoric acid is gone...

Discussion of cotton candy, prions, ebola and other such ensues, concluding with MGH saying ``Prions, delicious delicious prions.''

MGH: Back in the day . . . when the Tree of Life was just a twig . . . and Andrew Clough was an undergrad . . . 

Discussion of the Midway, student groups, Matthew Jarp, Radio Freefall, seasons, hot summer weather, Kendra reading a book for money for MITSFS, hardcoreness, burning of 8.022 notes, fire, smoking, and other things ensues.

Usual motion. Usual second. Usual third. Usual fourth. Usual fifth. Usual debate. Usual pi? Arrrrrgh. Usual bing. Usual revolt.

\goto{New Business}

KKB: It's hot outside.

\goto{Future Business}

PW: We're going to get a hurricane. KKB: What?! ALC: We aren't going to be hit directly, but it's coming close. We're going to get a lot of rain Sunday night.

Timewarp.

KKB: Soon the froshlings will descend upon us. We must prepare the Wall for assault from the Others.
SAS: ``I am the Sword in the Darkness. I am the Watcher on the Walls. I am the Horn that Wakes the sleepers, the Shield that guards the realms of Men. . . ``

pseudo-Skinner is driven from the room through singing.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
