\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 30, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Karl Ramm, Libcomm
and pseudo-onseck, recording.

Minutes read.

Motion to recompile tex 3-2-1 \ps

\goto{Committee Reports}

\subsection*{KatieComm}
``We got Regenesis.''

\subsection*{FrustatedAuthorComm}
I'm submitting my book to that contest, so I can be optimistic for a month.
Also, I'm three pages away from being unlame.

\subsection*{PseudoKvetchcomm}
I think one of our prentices submitted a review of Princep's Fury.

\subsection*{PseudoAnalogComm}
People should send in requests for spring schedule

\subsection*{PhoneComm}
Some people just called wanting to join remotely.  A company on Ohio..

(mass confusion and speculation)

\subsection*{VisitorComm}
Art People With Scarves?

<Albanian speech>
Don't encourage him, he'll speak more.

Bing?

\goto{Old Business}

In past there was a big white box behind the medcenter, that was full of
rice of tasty thing.  I haven't seen it in a few weeks.

``I didn't steal it...''

Discussion of Massachuseetts winter ensues.

ALGOL.

\goto{New Business}

Stross is rumoured to be coming back to the frozen North.  We should, like,
give him that membership we were going to give him last year.

There's a guild game going on, with people dieing.  Discussion of killing.

Miller motion; passes 8-2-4 \ps 
\noindent
Universe adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Karl Ramm, Libcomm and pseudo-onseck}

\end{document}
