\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/06/2007}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 9, 2008

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Any of the motions, some of which are to reread the silence, pass.

\bing

\goto{Committee Reports}

\subsection*{Star Chamber}

Inventory will be happening tomorrow!  If you are a keyholder or a
prentice, you should show up.

The library will closed during Inventory.

\subsection*{Pseudo-Trojan}

Trojan finished processing the Cohen donation at 5 AM last night.

There's a Trojan donation FAQ going up soon.

Motion that the Society give a simultaneous ``mmmm'' of skepticism passes 9-3-''mmm'' \ps.

\subsection*{Magventory}

Margaret did about 50 of the remaining 175 sheets.

Sold!  To Old Business.

\goto{Old Business}

Old Business never pays.  We tried to send some collectors after it,
but they decided it was too old.

Winter Break ended.  We didn't have meetings for two weeks.

Motion to change the name of ``Old Business'' to ``Crime''.

If you're going to run away to somewhere, why would you run away to the Ukraine?

KR: ``Kate, you now have access.''\\
ESK: ``To... the Ukraine?''\\
KR: ``Well, probably.''

\goto{New Business}

We don't have a debate, we're a dictatorship.

We have a new prentice!

\goto{Future Business}

The suffering of Libcomm is never-ending.

All in favor of exactly one of the motions?

Exactly one of the banana motions pass.  ``Take that, Spehn!  I have
Skinnerial power!''

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
