\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 6, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent

\bing

(Meeting fails to be called to order.)

Wanking about relative intelligence of SF authors ensues.

MITSFS meeting called to order, 66.4 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

Motion to condemn the minutes for suggesting that the prentices should be replaced by roombas: 7-3-4 \ps
Motion to bring the process of feeding prentices through roombas to the Institutional Review Board: 7-3-0 \ps
Motion to explain WHAT THE HELL IS GOING ON: 7-7-1 \ps
The determinant is 112 and all motions pass.

NH: Hentairific is an awesome word!

EK: Grues can't eat me!  I have the gavel!

Motions about launching all the nukes, fire all the gas, and replacing
the MITSFS rules of order with the rules of Family Feud.  All motions
are seconded but fail for lack of the pseudo-Onseck, who is
calculating the determinant.

\bing

\goto{Committee Reports}

\subsection*{Nocomm}

KAT vaguely talking about the Keith Laumer Retief books.

\subsection*{Pianocomm}

sueshep (SAS) is getting killed-*ahem*-I-mean-keyed as we speak!

\subsection*{Star Chamber}

We have an advisor!  Kate Delaney.  CYBERPUNK IS DEAD.  LONG LIVE CYBERPUNK.

We can now do useful things like renew athena accounts.  She probably can't get us more space, though.

SIR: Oh, huzzah, that's actually relevant.

\subsection*{Trojan}

The Cohen donation is now Panthercomm's problem (and partially Catacomm's).  Whee.

The motion ``Good thing that wasn't a motion'': 0-0-3 \ps

Theoretical computer programs to make cookies, sadly, do not produce actual cookies to eat.

\goto{Old Business}

EEEEEEEEEEEEEEEAAAAAAAAAAAAAAAAAAAAAAAAARRRRRRRRRRRRRRRRRRRRRSSSSSSSSSSSSS.  Discussion ensues.  The Onseck might have them, but he isn't here.

We have a donations FAQ on the website.  This actually is old news.

The Watchmen movie is out!  (How the hell is this old business?)  Discussion ensues.

Isaac Asimov is still dead... I guess that counts as ALGOL.

\goto{New Business}

Inertia is a usual motion?  Sex with bisons?  Bicycles?

Weird squeaky noises ensue.  I wonder if someone is choking over there.  Moving on.

Oh no!  Someone is trying to *fizzle* summon *pssssssh* *beeeeeeeeeeeeep This has been a test of the emergency broadcast system do not change the channel*

Mice have been spotted in the library.  Eat and you will be deleted.

Spark!  To time traveeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeee

\goto{Future Business}

CPW is being special.  CPW is in the future.

More prentii are in the pipeline!

Motion to lay on more work upon the prentices until they go bananas: 9-11-0-0-1 (sorry Spehn, you don't get to vote) and for some reason...

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
