\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 12, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, LHE and psuedo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to include the premeeting quote, ``We can't run the rain test - it's raining!'' passes 10-0-0\ps.

\goto{Committee Reports}

\subsection*{hBarcomm}

hBarcomm sent out an update to MITSFS-social.

Motion to commend hBarcomm for having the only report to report this week passes 4-0-1\ps.

Margaret: I can make shit up.

\subsection*{frustratedAuthorComm}

My book is navigating the warp of time and space.

\goto{Old Business}

Usual motion, second, complaint & dictatorship.

\goto{New Business}

The Transformers movie is coming out soon.

\goto{Future Business}

They're making some more Farscape episodes, sort of like the sequel to pigs in space.

Margaret: I liked that until they turned it into alien porn.

Brian: Ghostbusters 3 movie is in post-production.

Miller motion fails by pseudo-Skinnerial decree.

History session on how MITSFS folk test the universe's concurrency and how you can put two Miller motions into the Matrix.

Second Miller motion passes by pseudo-Skinnerial decree.

Brian: The people outside the meeting who 
Margaret: So it's a large box containing the universe and a large number of Miller motions? And a smaller box containing MITSFS.

There are concerns over whether we would be protected from a large black hole by space cardboard.
Ian: No one said we had to stay nearby...

Brian is describing Ian in terms of a recipe involving butter. He then explains it so that it appears logical. God help us all.

Brian: We could use a large box, so we could store books into it.

Brian: Bring a large chain sword.
Ian: Fun for the whole family!
Margaret: That could be true...

What should we smuggle into a fashion show? Stick insects! Dressed (by Margaret) in frilly pink clothes.

Onseck leaves the comments in the minutes as evidence that she was clearly not paying attention. (The Miller motion ended the meeting some time ago.)

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
