\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 6, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; lemur (Daniel Walter Rowlands), pseudoOnseck, recording.

Minutes read.

Motion to commend the meeting of the minutes for its "fidelity and verve" passes 11-0-5/ps.

\bing

\goto{Committee Reports}

\subsection{PainOfSpaceComm}
Still no check.

\subsection{WarComm}
The application has been submitted, finally.

\subsection{NanoComm}
Write in tomorrow, NH's hours.

\subsection{HassleComm}
Discussion of new books.  Elizabeth Bear is on TVTropes.  Specifically \emph{All the Windwracked Stars}; battle-shoggoths that make sense in context.

\subsection{LibComm}
Getting dexes printed.

\subsection{BoxerRebellion}
Books are being moved to the warehouse one at a time.

\subsection{pseudohBarcom}
T-shirts are getting printed soon; do people have particular things printed?  Do they trust her on colors?  Discussion of seal vs. Psi-Phi; we want shirts with the new official logo.  Discussion of scrollwork on seal--"Mens et Manus" is pithier than our logo in Latin.

\subsection{pseudoTrojan}
We are caught up with the Cohen donation.

\goto{Old Business}

Halloween happened.  Susan threw pumpkins off the Green Building; they went splat.  The music wasn't working too well, that was sad.  Obviously what we need is more power.

MKR: It's so quiet in here.  Someone else: The better to hear you with.  Discussion of having trouble hearing binging, then \emph{Heros} drinking game.  You drink when they do things that suck, or someone whose name might not actually be Spider-Man (Peter) forgets what his powers are.  Also any time they are incapable of any kind of rational thought.  NH: I finally quit \emph{Heros}.

There was a community sing.  The concert choir sings in Lobby 10 and anyone can join.

Usual motion.  Usual vote.  Uusual result.  Bing.  What about the usual debate.

\goto{New Business}

Some old MIT class is trying to take away our study space (the plinths) in Lobby 7.  The Tech had an article.  People seem unhappy.  Maybe we should put some chairs, or hire undergrads to stand on them.  Or a matress on top.  There was an article in the Tech a few years back saying that their being empty showed our "un-elitest nature".

There was a writeup of us in the Technology Review.  It was about the getting things scanned; and was quite accurate and good.  The article mentions that we're utterly pressed for space.  Once the check comes from REDACTED, there will be a nice letter sent to the Technology Review from PainOfSpaceComm thanking them for their generous donation.  Something about a non-zero number with many, many zeros before the decimal place wanted as a donation from generous alums.

Suggested to go through the library's list of people who have been bad, and Google them to see if any have become venture capitalists.  If such a list were Googlable, not saying they owe us money, but that they once did, would be a good thing.  Discussion of whether we have a list of everyone who's been a member and their balance--it seems we don't.  How far back do the LHE records go?  LHE claims they're pretty complete.  Former LHE says Jamie told her to throw them out at some point because they were older than she was.  It would be nice if LHE could get a list of everyone who's been a member--we have a list of who the Alumni Association things was involved, but that's different.  We also have a list of everyone who was ever a Star Chamber member.  Jamie had some secret file which may go very far back--people apparently konw where this is.

Someone should write another issue of \emph{Still Not Fans}.  Also, the Skinner should lean on people to make TZ happen.  It might be an IAP project.

A time has been reserved for Inventory.  An email was sent in October.  Another should be sent.

\goto{Future Business}

There is going to be an Assasin's Guild thing this Sunday; one of the bits will be science-fictional.  A story from the recent \emph{Asimov's} about a bus of aliens, similar to "Journey to Vega", titled "A Bucket, and Accidental Mastery of Space-Time", might make a good Guild Game.

In the future there will be IAP.

Drop date is coming up soon (18th November).

In the future there will be motions.

Miller Motion fails 15-16-3/ps.

Motion to throw a banana at the one person who made the motion fail or possibly one-sixteenth of a banana at each of sixteen people passes 16-9-1/ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{lemur (Daniel Walter Rowlands, pseudoOnseck}

\end{document}
