\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 1, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to take a picture of the Onseck with an Orson Scott Card book in one hand and a gleam in his eye passes ``later''-0-0 \ps.

\bing

\goto{Committee Reports}

\subsection*{Picniccomm}

PW will be done with the picnic invitations this weekend.  It'll
probably be the 16th.

ESK is sick.  It's probably the swine flu.

Discussion of swine flu ensues.

You can find peace and love on YouTube.

\goto{Old Business}

Metaphors are not one-trick ponies.  One-trick ponies are metaphors, though.

\goto{New Business}

What happened to the usual everything?  Oh, that's what we were supposed to do.

So, KCR finally garbage-collected the New Books shelf.

One, two, three...

\goto{Future Business}

In the future, there will be elections.  Week after next.

I didn't mean ``run for office,'' I meant ``run from office.''

Two weeks should get them far enough!

78877777777777777777777777777777777777777777777777777777777777777777777777777777777777777...  the Onseck's head hits the keyboard.

We send our support to Kat and adjourn the meeting.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
