\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 18, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to bite their arm off chickens 5-1-6\ps.

Motion to condemn this meeting for blank apathy is noted in the minutes.
Sukrit: I would second it, except that would defeat the purpose.

\bing

\goto{Committee Reports}

\subsection*{PainOfSpaceComm}
PainOfSpaceComm was unable to go to the NESFA meeting - bridal showers, we all agree, take precedent - but the next meeting is in early October. We are hopeful.

\subsection*{Bluebellcomm and Panthercomm}
They did work.

\subsection*{Skinner}
The fall mailing has gone out.

\subsection*{Trojan}
A lot of boxes are being moved, so we have more space.

\subsection*{Warcomm}
The war continues.

\subsection*{hBarcomm}
The Library is now listed in the elevator directories.

\goto{Old Business}

A long time ago SpaceHulk came out. It was the best game of all time, and had a library equipped with chainswords and Elder Gods.

Sukrit: Wait, what's a chainsword?
Brian breaks Sukrit's poor physics brain.

Back in the day - an arbitrarily long time ago - when God was still deciding what the heck an atom's ``Spin'' actually meant . . .

Motion to remove Libcomm to YETZIRAH chickens 8-1-9\ps.

Motion that there be at least one motion that doesn't chicken this meeting is noted in the minutes.

Usual motion. Usual second. Usual vote, usual result -- 

\goto{New Business}

SpaceHulk is apparently coming back into print.

Discussion of Warhammer 40K. Apparently you could read it, or you could just watch the movie Aliens to get the general flavor of it.

KKB has actually gotten an email from John Lambshead the author of Lucy's Blade thanking her for her critique of his work.


Motion to commend John Lambshead for being nice to his fans passes 12-2-2\ps.
Motion to commend the newly arrived undergrads for injecting life into this meeting passes 10-1-5\ps.
Motion to consider Kendra an undergrad until such time as she passes five feet 6-12-7\ps.

Matrix motion. The determinant is -74. Onseck is going to learn how to stick code in and get a shiny answer *quickly* 

Motion to commend John Lambhead anyhow passes 9-3-5\ps. 
Motion to eat a fish passes 8-7-4\ps.

Question about voting policy in regards to disabled people. Absinthe and absence are punned. Also, timewarp.

Question about whether to continue the war against HRSFA. ``Who do we know there?'' ``Um, dankane.'' ``Oh! Duh. Right.''

\goto{Future Business}

In the future, someone will say something. In the future, the U in the Garamont font for Latex will be corrected, if KR has anything to say about it. Technical advice follows.

Motion to develop a new font specifically for MITSFS with ability to integrate easily into slot machine displays with full specification including ability to display coins, cherries, bananas and assorted fruit 9-7-9\ps.

Motion to commend Spehn for casting the deciding vote on a banana motion passes 15-3-12\ps. 

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
