\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 1, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Lee Fuchs, pseudoOnseck, recording.

Minutes read.

Motion to thank the library for preventing Kat from going bananas  chickens 7-3-11 \ps

Motion that someone opened a hole in the universe and someone fell in passes 30-3-5 \ps

\bing

\goto{Committee Reports}

\subsection*{Moocom}
New Star Trek movie! Which, despite being odd numbered, actually seems to be good. For
IMAX? Sit at the back.  Eric Bana's facial hair is not that interesting.

Motion to retract the assassins after Nick Burma in CA fails for lack of second.

\subsection*{Trojan}
Dear KevinR whenever you read the minutes:

We processed the Cohen Donation magazines (again) and there's a message in the KBB from
kkb (or actually Trojan).

~~ Trojan

In other Trojan news, there are letters asked for a year ago dated, uh... in the future.
Fail.

Motion to condemn Hell to Hell, especially the MIT Gifts Office passes 19-0-2 \ps

\subsection*{Picniccomm}
Picnic is happening on the 16th.


\goto{Old Business}
Discussion of ALGOL ensues.

Suggestion to make a prentice go back and read old minutes to find out when it was modified

Motion to not give a shit fails for lack of a second.

Neat shirt made by Margret!

In the past, Miss Katie read books. In the future she will read more books.

In the past, kkb tooled. In the future, she will theoretically graduate.

\goto{New Business}

There is... apparently no hope for Dance of Dragons coming out.

On the other hand, there is a lot of hope for Charles Stross books.

If you do a Fourier transform of Star Trek movie goodness by number, there in fact would be
a spike around this one.

Motion to reboot the minutes passes 15-3-2 \ps

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 1, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Lee Fuchs, pseudoOnseck, recording.

Motion to thank Society for preventing Kat from going bananas passes 17-0-2 \ps 

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Lee Fuchs, pseudoOnseck}

\end{document}
