\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 17, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, LHE and pseudo-Skinner, presiding; Kendra Beckler, pseudo-Onseck, recording.

Minutes read.

Motion to condemn the minutes as not yellow: 3-7-3 \ps

\bing

\goto{Committee Reports}

\subsection*{Pseudo-Seldon}

Tron showing tonight, 8:30 PM.  You should come!

\goto{Old Business}

Nothing that resembles ALGOL at all.  The pseudo-Skinner apologizes and offers to do a timewarp in order to rectify the situation.

ALGOL

\goto{New Business}

Nada.

\goto{Future Business}

Guild camp games are running next weekend.  Most of them have sci-fi themes.

``There was that email... about a banana...'' 0-8-4 \ps

LAAAAAAAAAAAAAAAAAMMMMMMMMMMMMEEEEEEEEEEEEE.

But the meeting is adjourned anyway... the pseudo-Onseck doesn't know what's going on.  To Tron!

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
