\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 6, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Under no circumstances whatsoever will I be doing a matrix motion for
you people.

I am not going to make the Onseck do a matrix vote.

``Why are the minutes inaccurate?''\\
``Because I \emph{wrote} them that way!''\\
``The minutes are \emph{always} right!''

Various non-matrix motions chicken.

``You don't need to kill people to get blood, haven't you seen Buffy?''

``I've already had my brain eviscerated!''

``We want discriminate violence!''

\goto{Committee Reports}

``I'm going to channel Kevin very loudly.''

\subsection*{Pain of Space-comm}

``Thing!''

``Still no word from NESFA, despite them claiming they'd get word to us
about the money after their meeting on Feb 1 (and despite my
poking). If I don't hear from them soon, I'll corner their president
at Boskone.''

\subsection*{Cell 25 Morale Officer}

``Is there interest in Friday SF showings?'' 
``Yes.''

\subsection*{Pseudo-Niagracomm}

``Are you interested in selling things at Boskone?''

\subsection*{War Council}

``We should insert a student into the ASA.''\\
  ``Good luck with that!''  

``I want to be a minion.''\\
``Great!  Apply to be on the ASA!''\\
``The what?''

``I want a couch!''\\
``We have a couch!  See, it's right there!  Under the boxes!''

``It's aliiiive!''

\subsection*{Catacomm}

``We have a prentice!  The prentice did work!  That one, over there!''

\subsection*{The National Committee to Map John Kenneth Galbraith Into The Complex Plane, Inc.}

``I'm glad I remembered this before it was last week.''

``All in favor?  Skinnerial decree.  Pass.  I'm too lazy.''

\subsection*{Analogcomm}

``Signing up for hours makes you a better person!''

``I'll sign up for hours!''\\
``Really?''\\
``Yeahhhh.''\\

``I smile!  I'm friendly!''\\
``Ignore the brains!''\\

\subsection*{Worldcomm}

``You need to poke people who owe you money a little more vigorously.''\\
``Oh. Yeah.  Karl, you owe us money.''

``The Student Society of Physics Students?  You guys need to talk to
the Society of English Majors.''

\subsection*{Trojan}

``Lord help us all, I hope they get back to me soon.''

\goto{Old Business}

``Oh, oh, oh, Committee Reports!''

``It's official, OK?  Move on.''

``That groundhog was a lying bastard.''\\
``Burn him!  Burn!''

``How does he talk back?''\\
``He writes letters!''

``I want to Albanian the universe.''\\
``I don't think that works.''\\
``It worked for Albania!''

``Second the motion!''\\
``FAIL!''

``Oh whatever, you're asleep like a groundhog.  Motion fails.''

\goto{New Business}

``I passed 18.06!''\\
``I think we're obliged to have a matrix vote!''\\
``NOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO. I
CAN'T HEAR YOU LA LA LAAAA.''

``There was a new Trek trailer.  It was good.  It was during the Super
Bowl.  The Super Bowl is a game ...''

``Term started!  It's kind of like Blood Bowl!''

``Unusual repetition of the usual motion!''

\goto{Future Business}

``ONSECK HAS NO CALCULATOR AT ALLLLLLLLLLLLLLLLLLLLLLLLLLLL...''

``I guess all motions chicken.  I guess we're still here.''

``Motion to gag the Onseck with a banana!''\\
``... Ow!! This doesn't actually fit in my mouth!''

``Motion to export the minutes to Bananamax passes because it was better.''

\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
