\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 23, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to commend Naomi on having 'chocolate' shirt on passes 14-0-0\ps.

\bing

\goto{Committee Reports}

\subsection*{Hasslecomm}
Hasslecomm happened. At this rate, we might even get done before the end of the world.

\subsection*{Trojan}
We're making sure Hasslecomm doesn't finish before the end of the world. Trojan is down to just 12 active donations, wheeeeeee.

Also, Trojan is answering mail via timewarp.

\subsection*{Niagaracomm}
Brief mention of the book sale this IAP, said in passing.

\subsection*{pseudo-Pianocomm}
We have a new prentice, Alex West.

\subsection*{Pianocomm}
Prentii, do work! Please? Really, you can show up just about whenever, and the keyholder will be glad to give you something to do.

Motion to have a Matrix vote - votes: 8-2-2\ps.
Motion to help the Onseck use the new utility she has just opened on her computer screen - votes: 6-8-3\ps.
Motion to give the Onseck exactly what she clearly wants - votes: 9-1-10\ps.
Determinant is 394 and all motions pass.

Motion to commend the previous motion for not contradicting itself fails 10-11-2\ps.

\subsection*{PainOfSpaceComm}
Still no word from redacted, we'll be emailing them shortly.

Motion to redact the word REDACTED from the minutes passes just because.

\subsection*{Onseck-slash-Catacomm}
We'll be meeting to get a handle on which magazines we're subscribed to, which ones we've let slide, and which ones we need to subscribe to.

\subsection*{PhoneComm}
We've gotten a lot of phone calls recently. A theater called us to let us know about a play entitled ``Sleep No More,'' which they thought might interest us.

Motion to commend them for figuring out that they should talk to MIT students about a play entitled ``Sleep No More'' passes  9-0-3\ps.

We also got a phone call regarding a book about music and sci-fi; the author would apparently like to show it off to us.

The third phone call ... let's not talk about it.

\subsection*{YASID}
We've helped a few more people find books. ``On that note, does anyone recognize this title?'' Three seconds later: ``Oh, that's Dead Man's Switch.'' Man, we are good.

\goto{Old Business}
The prologue to Republic of Thieves is no longer on Camorr.com. Now it is on a table in MITSFS! Worth reading.

6013 years ago today, Bishop Usher says the world started.
Motion to put bananas on the world's birthday cake passes 12-10-2\ps.
Timewarp! 

\goto{New Business}

It never happened. Eep.

\goto{Future Business}

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
