\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the minutes for working out pretty well passes 22-0-2\ps.

Motion to send someone's assassins after someone else fails due to, ``No.''

\bing

\goto{Committee Reports}

\subsection*{Jourcomm}

We're going to have a TZ!

\subsection*{Picniccomm}

We're going to get drinks tonight!  The Picnic is tomorrow!

LCS or someone else claims that we should claim that the picnic is a potluck.

\subsection*{Trojan}

Someone wants to donate some books to the Library this weekend.  I'm
assuming ``nah hah hah hah hah'' is not an appropriate response.

\subsection*{SIDComm}

JMS is coming to MIT!  He made... Babylon 5?

No!  That is the wrong incantation!  Repeat after me: ``He made... Babylon... 5!'' 

\goto{Old Business}

keach is done!  No finals?

All this has happened before, and all this will happen again.

ALGOL.  Usual dictatorship.

\goto{Elections}

We will do this again and again until someone gets it right.

First we begin with the Onseck, that being the most glorious and
exalted position of the Society.  I said it, so that makes it right.

$*$ keach\\
$*$ sueshep\\
Lee\\
The beautiful square\\
A drunk republican\\
a purple cow\\
the Stay-Puft Marshmallow Man\\
angry superhero ninja\\
war on drugs\\
war on terror\\
war on abstract nouns\\
war on concrete nouns\\
war on abstract nuns\\
this piece of chalk (because it's awesome at writing)\\
ternus' laptop\\
kittens\\

SAS (Susan Shepard) is elected.

Second, we will elect the LHE.  No LHE so far has succeeded in running
off to the Caribbean with our money.

The LHE ensures that kevinr and armenard get reimbursed.

Banging my head on the table may have been a tactical error.

$*$ kyoki\\
$*$ pweaver\\
zombies\\
brains\\
sukrit's brains\\
igorth\\
Locke Lamora\\

For Vice we have one candidate.  And that would be:

$*$ kittens (ternus)\\
puppies\\
fluffi bunnis\\
dead (?) kittens?\\
disapproving rabbits\\
fuzzy cthulhu\\
munchkin cthulhu\\
summer fun cthulhu\\
stephen colbert\\
the skinner's hat\\
schr\"{o}dinger's cat\\
schr\"{o}dinger's hat\\
MIT\\
Lukas Fehrwight\\

Kittens (and thus ternus) are elected Vice.

President:

$*$ Miss Katie\\
Katiecomm\\
Chancellor\\
ephen Col''''''bert\\
what they said\\
Jon Stewart\\
TARDIS\\
Richard W. Cheney\\
Wisconsin\\
Daleks\\
bananas\\
plantains\\
Locke Lamora\\
Jean Tannen\\

MKR is elected President, and 

\goto{Future Business}

Brian is sent to Albania for lying about The Lies of Locke Lamora.

Discussion of the picnic ensues.

The meeting adjourns with the Adjournment Song.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
