\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 26, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Susan Shepherd, Onseck and pseudo-Skinner, presiding; Kendra Beckler, pseudo-Onseck recording.

Minutes read.

Someone stole the pseudo-Skinner's line.

``Any motions regarding the reading of last week's minutes?'' passes 9-1-4 \ps

\bing

\goto{Committee Reports}

\subsection*{Joint Onseck-Catacomm Committee of DOOOOOOM}

Magazine subscriptions have been looked at.  We are looking at our subscription expirations as well as looking into any SFnal magazines which we do not currently get.

\subsection*{Pseudo-Seldon}

Pseudo-Seldon is showing Cast a Deadly Spell next Friday.  You should come!

\goto{Old Business}

ConCertino happened.

\goto{New Business}

Usual fail at ALGOL.

BTS now has a copy of the movie White Dwarf.  Yay.

\goto{Future Business}

\ldots

*crickets*

Predictions of death ensue.

*more crickets*

A new Transformers movie has come out.  It is absolutely shit.  From what we hear.  Because this is totally future business, right?

Motion that the Society get a baby porcupine to eat a banana so that we can watch it on YouTube passes 4-1-3 \ps

This caused an unstable state of the meeting instead of ending it.  Don't ask.  I think L space had something to do with it.

Motion to retroactively Albanian Brian for his premeeting actions chickens 6-5-1.23481834983470854 \ps

Miller Motion passes by pseudo-Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
