\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 2, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to have Miss Katie drink this coffee in order to wake her up fails by Skinnerial decree. ``Ew! No, I'm not touching that stuff.''

We're trying to determine two things: Does it taste like coffee, and is it exothermic? Regrettably, while we have not tasted it, the coffee does not appear to be exothermic.

\bing

\goto{Committee Reports}

\subsection*{Lastcomm}
We have a new computer with the cluster install on it. Anecdotal evidence would suggest that it still boots up more 

\subsection*{Niagaracomm}
We learned how the MIT space reserving system works and are working to organize a book sale. Also, the Vice has found another possible solution in the form of an organization which will pay us to send them books, then send us a good portion of the proceeds from the sale of said books. KCR: ``This sounds entirely too good to be true. We should take advantage of it as quickly as possible.''

\subsection*{Star Chamber}
Rooms have been reserved for the after-meeting Seldon showings. Yaaay!

\goto{Old Business}

Zombieland had a sneak peek showing yesterday. The movie was quite good and quite gory.

Both the Onseck and Lemur had tests last week. Apparently test season is starting.

Usual motion, second, vote, result...

\goto{New Business}

We can apparently levitate mice now. Also, a keyholder is getting married tomorrow! We wish them the very best.

In other news, it's October. There's a new Stargate Series starting tonight.

The Skinner has started reading ``DM of the Rings,'' a webcomic.

\goto{Future Business}

The motion 'Apathy' is suggested and passed - ``because the Skinner didn't want to have to count the votes.'' I guess this counts as a successful apathy. Congratulations, MITSFS, ye have apathed well.

Matrix banana vote.
Motion to have a banana motion so we can go eat - votes are 4-13-1\ps.
Motion to give people bananas - votes are 0-8-10\ps.
Motion to have a banana matrix vote - votes are 4-4-8\ps.
The determinant is 584, which is positive, so all motions pass.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
