\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{lemur (Daniel Walter Rowlands), pseudoOnseck}
\newcommand{\meetingdate}{Friday, November 13, 2009}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to commend the reading of the minutes for their fidelity and sarcasm fails
6-8-8/ps.

\bing

\goto{Committee Reports}

\subsection{WarComm}
ASA has failed and not sent anything to use even though they said they would.
Also, they scheduled release of results on Thanksgiving when they'll be out
of town.

Motion to have the ASA sanctioned chickens 0-something-20/ps/

\subsection{pseudoNaiomi}
There was a lovely write-in during NH and KKB's hours; they make a convenient
four-hour block for writing.  People made word-counts.  (Skinner wants to see
them.)  It looks very immortal.  If you come next time, you can be immortalized,
too.

\subsection{Trojan}
Trojan is on verge of giving up on finding information on the Greever and Kelley
donations from late 2006-early 2007; and information or recollection should be
emailed to KKB.  Or any memory of that era.  They're processed into the library,
but the records are unclear.  Also, the last three Leibowitz letters are going
out, along with one to a former keyholder (Bogatin) who donated a copy of a
book he wrote.  Andrew found an email he's forwarding to KKB that has Kelley's
email address.  Discussion of whether Brian processed it in June 2006.

MATRIX VOTE
Motion to put the good Mr. Kelley in contact with ALBANIAN and the Board of
Directors of the Boston Public Library. (4-14-7/ps)
Motion to Albanian Brian. (13-12-2/ps)
Motion to have a matrix vote. (4-13-6/ps)

Determinant is 42 (awesome) and all motions pass.

\subsection{TheftComm}
We have a new TIF.

\goto{Old Business}

Last week there was Muppets 40th anniversary cookies.  Also Sesame Street characters
on the Google homepage.  Kat is laughing.  Skinner wants to know why.  Brian said
something in Albanian.  Prentice (Will) instructed to get an Albanian dictionary.
If it isn't there, we have a problem.  Not that we'll never be able to understand
Brian again, but that books are disappearing.

Will's chemistry professor has never read "The Last Question" so, in response to a
long lecture on entropy, he sent it to them.  He did not explain why it could
be measured in bits.  Also, the physics colloquium discussing Boltzmann branes and
entropy failed to mention "The Last Question".  References to Lovecraft and
Boltzmann branes making cosmic horror work.

ALGOL

\goto{New Business}

Brian's Albanian gibberish was seconded.  It's not gibberish to the Skinner, but it
is to everyone else.  Motion chickens 2-3-14/ps.

Kendra is being multiplied by i.  She is going from positive and real to positive
and imaginary.  Discussion of poking and anti-poking people with non-real 
(or non-positive) values.

Will is concerned about it being Friday the 13th because bad things will happen
to him.  Other people are happy because they can watch.

MKR's mother wants her to solve for initial conditions to give maximum number of
Fridays the 13ths.

Brian and Skinner have conversation in Albanian, with Kendra imagining it.

Tomorrow there will be puzzles (Microsoft College Puzzle Challenge).

Will wants to commend Random Sanderson for making the last three books (publisher says
it's official) of Wheel of Time better.  People don't trust publisher because
it's in their profit-motive to claim this anyway.

Brian said something in Albanian, which the Skinner refuses to translate.

Motion to probe the universe for the existence of Boltzmann bananas passes 10-12-3/ps.
Motion to assume there are an infinite number of them from our armchairs didn't happen.

Everyone shelves three books.

\goto{Future Business}

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
