\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 17, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to investigate the inside of an abandoned Krispy 12-3-5\ps.


``Come in!  Come in!  Welcome to the MIT Science Fiction Society!  We
don't bite!''  ``Kate, they're fleeing.''


\bing


\goto{Committee Reports}

You can vote with all your limbs!

Katiecomm:

We got Last Watch!  And Turn Coat!

Pianocomm:

We're keying somebody, right?  We're keying Paul Weaver!  Yay!

General applause.

Catacomm:

I processed in the magazines from the mail!

Woo, magazines!

FrustratedAuthorcomm:

I lost, but there are cookies, so it's OK.

Peoples' Albanian Embassy:

Albania is now in NATO.

The fact that HRSFA is here means we cannot make any announcements
about any invasions of HRSFA.  Which is good, because I don't 

KKB: Kill kill kill kill kill...

CJT: Here, Kendra, have a strawberry.

KKB: Nom nom nom nom nom...

\goto{Old Business}

There was the past!  It had test!

ALGOL?

\goto{New Business}

What happened to the usual motion?

General outcry about the lack of usual motion.

Discussion of the history of ALGOL.

ALGOL '68 will never catch on.

Oh my god you guys, we have prefrosh!

The booth downstairs went pr

\goto{Future Business}

Business of the future!

Prefrosh, do you have questions?  Don't mind the crazy, we're like
this all the time.

Motion to pray to George R. R. Martin until shelves and space fall out of the sky!  Motion passes?  11-8-7 plus, uh, Spehn?

Motion to pray to St. Asimov for the Blessing of Bananas, who will roll in his grave for being called that passes 14-2-3\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
