\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 23, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Kendra Beckler, Vice and pseudo-Onseck, recording.

Minutes read.

\goto{Committee Reports}

\subsection*{Hasslecomm}

Hasslecomm didn't happen this week but has happened since NH went to a meeting.

\subsection*{Star Chamber}

We officially have a new pianocomm!  PP is no longer pianocomm, NH and JGC are now pianocomm.

\subsection*{Trojan}

The Cohen Donation is still done!

\subsection*{Mortcomm}

Khan died.

No. 6 died.

Waaaaah.

Something is stricken from the record.  Which wasn't here to begin with.  Maybe I should more diligently take notes.

\goto{Old Business}

Magic happens.

ALGOL...?

\goto{New Business}

There's a tenday going on.  That's why they aren't here.  They're in ANCIENT EGYPT!

We devoutly hope that the Onseck is not currently recompiling TeX.

\goto{Future Business}

In the future, term will start.  Doom doom doom-dy doom doom DOOM.

Motion: Banana banana banana-banana? fails 2-6-3 \ps

Motion to turn all of the boxes in the unDA into bananas and give them to a local food bank to get them out of the library: 6-2-1 \ps

\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kendra Beckler, pseudo-Onseck}

\end{document}
