\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{lemur (Daniel Walter Rowlands), pseudoOnseck}
\newcommand{\meetingdate}{Friday, December 4, 2009}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Skinner has difficulty recalling her name.  Discussion.

Minutes read.

There were gavel lessons last week, in place of meeting (three people present).  It is a very good gavel, you might not notice incremental improvement.

Motion to commend Jayhawk for perfect attendance at Stratton House chickens 1-2-9\ps.

Motion to commend the alien inside the Skinner's head for reminding of her name (it's a friendly alien, it has a soul, disagreement of what the Vatican says on this) passes 29-2-1\ps.

Motion to commend the Skinner for her dedication to something because she obviously has not slept (She says she slept more than four hours last night, but didn't sleep the night before.) fails for lack of a second.

\bing

\goto{Committee Reports}

\subsection*{LHE}

Filled out finboard application.

\subsection*{pseudoNaNoComm}

No one showed up to the last one.

\subsection*{WarComm}

We keep our current space, are in C category for more space, and will appeal this.

\subsection*{Trojan}

PantherComm has four (secretly seven) more gifts.

\subsection*{pseudoOnseck}

New boxes and ink came in; boxes in Damnation Alley, ink in Mailbox.

\subsection*{VanHelsingComm}

Motion to have a review solely consisting of the staked book for Twilight on the website passes 23-9-5\ps.

\subsection*{LooComm}

We got tickets for something?

\subsection*{PainOfSpaceComm}

We mailed out the microfilm and microfiche today, no insurance because it's irreplacable.  Google and our physical copies of the magazines are our insurance.  We seem to have at least some MITSFS members at Google.  MKR talked to MIT lawyers.  PW and others want to talk to MIT Legal a bit more.

KKB: Ball pit!!!

There is an ongoing class-action lawsuit against Google and all the involved libraries that MIT Legal probably will want to wait until after settles.  We need to phrase the question in such a way as to not make them make the conneciton.

Anything pre-1928 or where the author died before 1930 is out-of-copyright.  Also, anything pre-1970's where the right paperwork wasn't filled out is out of copyright.

There was an email from someone who wanted to fund the scanning project; we should tell him that we already have funding, but we could ask him to fund endowment.  Could we clear the BondageComm cabinet with enough money?  We have someone around who has done it (Jay and Carl) and we have a prentice who is interesting.

Also, could we say to the ASA "If you give us rooms now, we have a donor who will pay for improvement projets."  If the Cambridge Fire Department function collapses the right way, but it won't until after we've done it.  Star Chamber will take care of it, which means PW will.

PW will have his brain back tomorrow; MKR will have hers back on Thursday.

\goto{Old Business}

It was Thanksgiving.  Splash happened.  KKB was on Splash Security, but she didn't get a nice top hat.  They used to give our nice hats, and then realized they could give out cheap ones.  ESP always has extra money that they don't know how to deal with.

Usual motion, usual second, usual complaint, usual vote, usual debate.  The magazines are in California.  Isaac Asimov is still dead.  Robert Jordan is still dead.  Wheel of Time is still going.


\goto{New Business}

Motion to do something about Robert Jordan passed-13-something or other-2\ps.

LHE is producing black holes and strange loops, according to LHE.  He corrects this to LHC.

Motion to power up the LHE and see if black holes form passes by Skinnerial Decree.

Storage bill was paid.  Maybe we could get rid of some of the 13 copies of Dune.  Get Amazon.com to move the KBX boxes to move to Seattle with someone who's moving there.

Caltech tried to hack us last week, but no one but CPs noticed.

Motion to make sure that MIT's cannon hasn't run away passes 11-3-1\ps.

Motion to send Caltech a make-up present consisting of a series of bananas wired together resembling a cannon.

Caltech never does a very good job, but they try harder than Harvard.

Motion to send the Onseck to next week's HRSFA meeting to read this week's minutes.

Motion to really annoy the Onseck.

Matrix vote is {{14,12,2\ps},{12,3,3\ps},{1,16,13\ps}}.  Determinant is 1709. All motions fail.

Motions to send Caltech a single banana on a small plate as appropriate compensation.  It's not on wheels and doesn't play music.  Can we bioengineer it?  It's a BANANA!

Motion to send Caltech the banana-colored (most recent) copy of Twilight-Zine with a bill for two dollars inserted as a bookmark.

Discussion of when the most recent TZ was published.  When the Skinner was a frosh.  There was a #46, there might be a #47, or not, if there was it sold out.

Skinner panics trying to find old copies of Twilight-Zine.  Discussion of where they're supposed to be.

All outstanding motions presumably fail for lack of a second.

We have more t-shirts out now.

KR goes into Damnation Alley to find a box of TZ #47.  If he's not back in 20 minutes, don't send a search party because they'll get eaten, too.

Tomorrow, 20:00-23:00, KKB is running a guild game tomorrow in place of Patrol.  Has SF references.

KKB vanishes into Damnation Alley having been called to find books from a Cohen donation.

Four people, including Skinner, vanished into Damnation Alley, but a hallucination of KKB returned.

Miller motion.  Fails for lack of a Skinner?

Motion to nominate the current animate contents of the library to AssComm.  Then Skinner can assassinate her self.

The Skinner fails to be driven from the library through multiple verses of song.  She notes there are only tweo veres, and the repeat.  Skinner walks around with gavel threateningly.

It is determined that the Skinner didn't remember that she was supposed to run out of the meeting screaming.


\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
