\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 3, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

``What?'' passes 14-1-0 \ps.

\bing

\goto{Committee Reports}

\subsection*{hBarcomm}

We don't have a booth at the CPW Festival, unfortunately, but we may
be doing something else in Lobby 10.

\subsection*{Jourcomm}

TZ is coming out Really Really Soon Now.

KKB: ``I can draw a magazine eating me.''

\subsection*{War Council}

pweaver met people over spring break.  They were somewhat helpful.

\goto{Old Business}

CAK read The Lies of Locke Lamora.

CJT read about eleven books.  Many of them were by Jim Butcher.

Break.  Break is old business.

CAK went to California!  She'd never been west before!

There are all these old people.  Who are these people?

Skinnerial ALGOL.

\goto{New Business}

ESK is on to KKB's nefarious plan, as soon as she figures out what it
is.  Wait, is that chocolate?  It will disappear soon.

\goto{Future Business}

In the future, there will not be chocolate in the library.

In the future, there will be no rats in the library that are not made
of stainless steel.

All in favor of that motion that he seconded for some reason, the one
that involved a banana?  Ooh, me!  passes 3-I guess one-1 \ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
