\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 29, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion for Jim Henson, other person and third person to look into timewarps as well as for coherent multiworld theory involving goatees chickens 5-1-7 \ps.

The signed book ``Shadow Engineer'' has been donated by a former keyholder, Eric Bogatin. This is pretty cool. Especially since the back cover actually makes it sound like the book is not crap. 

Motion to commend the chancellor's slot for being big enough chickens 4-0-what was that like 8\ps.

Motion to commend the title ``S Parameters, Signal Integrity, and you'' passes 13-0-2\ps.

\goto{Committee Reports}

\subsection*{Catacomm}
JayHawk is stalking the Locus.

\goto{Old Business}

There were finals. Now they are over. It is good.

Usual motion. Usual second. Usual vote. Usual result. What about the usual debate? Usual lack of complaint. What, that was a complaint! Usual complaint, then.

JMS (the babylon 5 guy) came and did a lecture. The storytelling part was good, but the questions afterward were painful. Apparently this was still somewhat better than the questions for the Neil Gaiman talk last year.

\goto{New Business}

Somehow we've gone to new business.

Humorous discussion of Green Lantern ensues. He was very important to the crisis on Infinite Earths. Very important.

\goto{Future Business}

The screenplay for the Lensman series is being written. The result should be interesting.

Motion to ask Joseph Michael Strazcinscy whether he would eat us if we were bananas fails by skinnerial decree.

Motion to ask JMS whether, since we are NOT bananas . . . ``NO! Just NO!''

Albanian motion in Brian's direction passes 10-0-8 \ps.

Motion to condemn bananas for being the bane of the Green Lantern passes 11-0-1\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
