\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 30, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to commend last week's minutes for the REDACTED chickens 9-1-10\ps and redacted.

\bing

\goto{Committee Reports}

\subsection*{Hasslecomm}
Hasslecomm has done work. Yay.

\subsection*{reverseVanHelsingComm}
Look, I've bought a book for the library: ``Baby's First Mythos,'' a Cthulhu baby book. We are stamping it in quickly, before it escapes to wreak havoc on the wider world.

\subsection*{Seldon}
People still need to send me suggestions for movies to show. Also, SGS would like to arrange a joint meeting of the SGS and the MITSFS

\subsection*{PainOfSpaceComm}
Finally heard back from redacted, who said ``We're giving you the grant, where should we send you the check?'' We're hopeful but also somewhat skeptical. You know - eggs. Baskets. Counting.

\subsection*{Panthercomm}
Panthercomm will do work, and will also poke Bluebellcomm to make them do work.

\subsection*{WarComm}
WarComm will finish the application for more space soon.

\subsection*{FrustratedAuthorComm}
FrustratedAuthorComm has been rejected again. Some discussion of agents and online publishing ensues.

\goto{Old Business}

Seldon's computer broke last week. FrustratedAuthorComm's computer caught on fire. I think we know who wins that exchange: neither.

There is a second scanning project - we've gotten some donated F&SF that are very nice indeed except for the mold. We're considering cutting the spines and scanning the pages, thus preserving them for interested future readers.

Terry Pratchett wrote a new book, which is apparently about football. American football? Apparently the Brits are having fun laughing at us. At least it's less weird than Australian football, which involves an oval pitch.

Also, there is a group which has emailed some MIT mailing lists in order to get interested people to form a Quidditch team and join the intercollegiate Quidditch competitions which is apparently already in play.

Usual motion, usual second, usual vote, usual result.

\goto{New Business}

Usual Cthulhu? Usual insanity. It's Halloween tomorrow. At 11:59 p.m. tomorrow, the Onseck and her Stickmanly comrades will fling pumpkins from the Green Building roof.

Discussion of pianos smashing cannon mockups ensues. It made sense in context.

Elizabeth Bear has another book out. The first chapter, which is available online, is pretty good.

Soon we will receive more books.

\goto{Future Business}

Soon there will be food.

Motion to welcome the shark banana to the library passes 14-1-5\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
