\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 25, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to ride the pig GIR chickens 6-1-8\ps.
Motion to remove the cupcake from Libcomm's head passes 12-0-5\ps. 
Motion to let everyone know they should watch Invader Zim 1-0-12\ps.
Matrix vote - the determinant is -150.

Starbucks is bringing out a product called via, which may be delicious and may or may not be exothermic. KCR: ``This has zero, and I do mean zero, failure modes.'' SAS: ``Wait, what if you dropped a large amount of it into a natural lake?'' KCR: ``\emph{No} failure modes.''


\bing

\goto{Committee Reports}

\subsection*{ICan'tBelieveIt'sLegalComm}
There is a vendor who sells maple sugar cotton candy. It is as delicious as it is asbestos-like in appearance.

Motion to recognise the anniversary of the 1911 Great Molasses flood passes 15-2-8\ps.

Discussion of the flood ensues. It was apparently rather gruesome - when the tank burst, a tidal wave of hot molasses hit anyone nearby, and if they got hit they likely drowned or suffocated. Eeep. But the filk song about it is pretty reasonable.

Wheel of Time discussion briefly ensues, followed by a cylon reference.

Motion to ``Fucking toasters!'' chickens 8-2-9\ps. 

The New England Conservatory of Music has put together a program consisting solely of prologues.

\subsection*{Libcomm & Lastcomm}
We have a Domesday Book now.

\subsection*{Lastcomm}
MITSFS has a new computer. We have not really decided which software to put on it.

\goto{Old Business}
Murder of Jefferson Douglass ran, and was good, and died. Or not. We shall see.

There was a free movie showing of Surrogates. Apparently none present actually got to see it, although someone was

Motion to commission the collected works of Philip Dick by Piers Anthony to adapt into a movie in the style of Firefly. ``ALBANIAN!'' The rest of the motion description is difficult to understand ...

Back in the day, Piers Anthony was a very good writer. ``Wait, when?'' Waaay back in the day. The blob plot is somewhat disturbing. 

MG: The sugar

Usual motion. Usual vote, usual result...

\goto{New Business}

SciFi is making a miniseries about RiverWorld by Philip Jose Farmer.

Brian Sniffen says something in Albanian which gets turned into a motion and it passes 18-0-5\ps.

\goto{Future Business}

Motion to stab the next VanHelsingcomm with a banana passes 12-5-6\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
