\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

These are \emph{awesome.}

Motion to commend the prentice for taking \emph{awesome} minutes
passes 27-0-2\ps.  No-one has any limbs left.

27 is three to the third power!  So that's why you have your feet up like that.

\bing

\goto{Committee Reports}

\subsection*{Hasslecomm}

Hasslecomm happened!

\subsection*{Skinner}

MHG (Margaret Gentile) got keyed! 

Her initials are not MGH.  ``That's sick!''  ``No, Brian.  No, it
isn't.''

Motion to rename Magventory to ``Cataclysm'' passes $5^2$-2-$2^3$\ps.

``I wonder if that's how you spell Cataclysm.  Damn, I got it right.''

Um yeah.  \emph{That} was a committee report!

\subsection*{Katiecomm}

Katiecomm happened!

\subsection*{Vice}

The Vice successfully embodied all the deadly vices!

LCS gives candy to people!  That's an anticrime!

CJT is broken, and recites the Rainbow Squirt Pledge of Purpose.

All in favor of, uh, that?  3-11-19\ps.  It's all primes!  It's also
an arithmetic sequence.  You get lame bings when things chicken.

\subsection*{Star Chamber}

We got two Amazon boxes.  They only had one book each.

``AAAAHHH!  Don't let the Gor books out!  You don't know what you're
doing.  Aviv, take your hand off the chain right now or I will hit it
with the gavel.''

Keyholders should check their mail.

Keyholders should also check their mail if they're very excited about
identifying stories for random people on the Internet!

\subsection*{Libcomm}

Libcomm has been excitingly lame!

Just for that, if you subscribe to this mailing list, you will get the
contents in EBCDIC.

\subsection*{Cataclysm}

Catacomm (?) processed lots of boxes!  Lots of prentices got hours.

\subsection*{hBarcomm}

Do not take chocolate from Kendra.

I can't believe we're still in Committee Reports.

We may want to get a Lawyercomm.

Everything is in a quantum state of being recorded in the
minutes... and not.

\subsection*{Mortcomm}

Philip Jos\'e Farmer died. 

\goto{Old Business}

I Can't Believe It's Not Committee Reports!\texttrademark

MHG mentions Pride and Prejudice and Zombies.

\begin{quote}
  ``Dear Scalzi,\\
  What happened with this book that I ordered?  P.S., if you're ever
  in the area, Charles Stross said we didn't suck!''
\end{quote}

Don't put that in the minutes!

ALGOL.

\goto{New Business}

Usual cheers!  Usual apathy.  Usual ennui.

Wise Man's Fear got delayed.

P.S. Your tears are delicious to me.

\goto{Future Business}

Next week there will be Spark!

Just think about it this way -- every week you can punch a frosh, and
they're not allowed to complain!  Anyway.

There's a book called The Best of the Best of Trek ... and there's The
Best of The Best of Trek II.  This implies the potential existence of
the Best of the Best of the Best of Trek!

Roombas are not Three Laws Compliant.

Motion to build the MITSFS Roomba out of bananas passes 3-4-0-5-``huh??''\ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
