\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 11, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to commend the minutes for containing sufficient chainswords per unit volume passes 24-8-3 \ps.

Karl: Can you have enough chainswords?

\bing

\goto{Committee Reports}

\subsection*{PainOfSpaceComm}
Still waiting for NESFA to get back to us. Their next meeting is this Sunday; PainOfSpaceComm will visit during the meeting and poke them.

\subsection*{LHE}
We have money in our accounts. If you're waiting for a reimbursement, it will happen as soon as SAFO gets done dealing with the checks and such.

\subsection*{Libcomm}
Would like to remind the Skinner to think about planning the next Inventory. Also, the old Inventory will finish real soon now.

\subsection*{Skinner}
Would like to remind keyholders to think about book sales during IAP.

\goto{Old Business}

In the past, there was Rush. ``That's kind of . . . old.''
In the past, there was Sorority Rush. Communal ``Ewww!'' Description of singing and chanting and suchlike ensues.

There was a W20 block party. We got about five or six new frosh.

Discussion of deals with Cthulu ensues. Karl: Yes, this plan has no failure modes.

It's Shoggoths all the way down.

Elder Gods and Internet discussion ensues. MGH: Let the record show that Karl is biting his arm to prevent himself from talking. WK: Let the record show that Al Gore invented the Internet. MGH: Wait, stop, Karl might bite his arm off. PW: The Internet is a series of tubes.

Usual motion, second, vote, result, debate and complaint. 

\goto{New Business}

CT: I miss the previous Skinner's usual dictatorship. Skinner: I'm not a dictator. CT: You're also not as angry as Kate.

In the future, more science fiction movies will come out.

Discussion of movie names ensues. Commences. Progresses. Ensallies. Onseck snarls at the assembly.

PW currently has a new email, warning him about the flu.

Live forever! Or die trying.

A man lives as long as he lives and not a day longer. Now, we simply have to find this man, and stop him.

Wanking about death and immortality and Twilight ensues.

\goto{Future Business}

In the future, we may have some energy for our meeting. When it's not raining.
Lemur: In the future, it will stop raining. Lee: in the future, there may be food.

Random second involving laundry. Chores ensue. Second ensues. ``That wasn't a motion!''

The motion that totally wasn't a motion darn you all but it involved bananas passes 19-0-1\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
