\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 6, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, Epoch \texttt{1234567890}.
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to strike Andrew's previous remarks about the groundhog passes 13-groundhog-2\ps.

``There are actually eleven of the little buggers, and five of them saw their shadow.''\\
``It's a \emph{vote}?''\\
``Isn't he dead?''\\
``Six more weeks of zombie plagues!''

``Why don't we just use moles for this sort of thing?''

\goto{Committee Reports}

*blink*

\subsection*{Pseudo-Analogcomm}

Yay!  New schedule!  Boo!  Still in plain text!

There are no other committee reports.  I think there were prentii who
did work.  Something like that.

\subsection*{Niagracomm}

We moved a bunch of boxes to Boskone.  Hopefully they are being
boosted to escape velocity right now.

We should break into houses and give people books!  It's like a reverse Italian Job.

\goto{Old Business}

These boxes of inventory stuff are still here and still unmolested.

Giving people books is like anticrime!

Entirely irrelevant.

\goto{New Business}

MKR is like the Skinner in Exile, like the White Tower in the later
books of the Wheel of Time.  The Gavel is like the Oath Rod!

The ground shakes.  Bings!  Bings in the deep!

Ldots.

We're already in new business.

\goto{Future Business}

``I would prefer brontosaurus porn to the Malazan Book of the Fallen.''\\
``Really?  How far did you get?''\\
``About where they get the clothes off the brontosaurus.''\\

In the future, both term and Boskone will continue.

Motion to give a free banana to people who buy a lot of books passes 6-0-1\ps.

\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
