\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 9, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to have them published in the Twilight Zine under the title ``Best MITSFS Minutes Ever'' on the grounds that they were taken fails 4-8-3\ps.

Motion involving bananas fails by Skinnerial decree. Nice try there, Brian.

The ``Have you read this?'' question on the front of the prologue to 'The Gathering Storm' may or may not be a trap, given that there is technically a fine for writing on reserve items. After some discussion, the consensus is that it is not intended as a trap. 

\bing

\goto{Committee Reports}

\subsection*{Star Chamber}
We have a new Seldon - Lee!

\subsection*{Lastcomm}
We breaked (not broke) the lock for keeping Domesday in the library. Right now we're brute forcing the combo. General hilarity ensues...

``Did you say you 'bricked' the lock?'' ``No, breaked it.'' ``As opposed to transforming a useful electronic item into a brick.''

\subsection*{War Council}
There was an ASA meeting. The armies of MITSFS are gathering...

\subsection*{FrustratedAuthorComm}
FrustratedAuthorComm has been rejected again. She is sad.

Motion to award FrustratedAuthorComm the Hugo and the Nebula for wanting to publish a book. Votes are 18-0-2\ps.

Motion to become the people who give that award out. 1-16-2\ps.

Motion to create a bubble universe: votes are 6-0-12\ps.

The determinant is 3456, no really. (According to the online calculator)

Somebody who hasn't attended a meeting before decides to leave, commenting ``This is weird.'' Well . . . yes.

\goto{Old Business}

``Have you seen the first line to the new Dresden book?'' ``Possibly you shouldn't read it - there may be spoilers.'' People crowd around to see. Karl reads it aloud. ``So -- Karl can read it but he can't?'' ``Karl can take care of himself if a spoilered person tries to get revenge.'' ``Ahhhhhh.''

Usual motion, usual second, etc.

\goto{New Business}

There is some discussion about the arms MITSFS has. It's rather amusing. Also, we may have things in pocket dimensions which normal folks would not know about.

Miss Katie Ray reads from an old record from the library.

Today, Obama was given the Peace prize.

Apparently the words ``Also, on the fourth floor, MIT has MITSFS, the world's largest collection of science fiction books'' has become part of the MIT Tour Guides' spiel. PW: ``Apparently MITSFS controls several of the tour guides.'' ``Really? Who? How?'' ``Brain slugs?''  ``Well, I don't care how the hBarcomm does it,
as long as it happens.'' ``Brain slugs? I wouldn't use brain slugs. It's not like I'm a biolog -- um.'' *pause* ``Brain slugs, like the 'h,' are silent.''

Motion to commend Brandon Sanderson for finishing the Wheel of Time book passes 20-0-1\ps. ``He's finished it?'' ``No, but he says he will.''

\goto{Future Business}

Eventually North America will be crushed by a huge ball of ice.

We have bombed the Moon. Twice!

Motion to commend Jet Lee for remaking Highlander 2 as the One instead of Shaun Connery and better special effect, so that you don't go bananas every time they swordfight passes 21-1-5\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
