\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 24, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Andrew Clough, Theftcomm and pseudo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to hire Bruce Biseler to write recording software \emph{``So good it feels like you're there''} chickens 1-2-4\ps.

\bing

\goto{Committee Reports}

\subsection*{pseudo-Seldon}White Dwarf will be showing next week.

Brian: I suggest that we see the Lost Skeleton of Cadavra.
Karl: I'm not drunk enough to see that movie.
Brian: You have to be in the right mood.
Susan: Yes, drunk.
Karl: No \emph{I} need to be drunk.

\subsection*{Theftcomm} If you are cancelling your hours less than two weeks in advance, you don't need to attach ``Theftcomm take note'' at the bottom.

Motion to hack into Theftcomm's brain passes by pseudo-Skinnerial decree.

\goto{Old Business}

In the past, people got sleep.

In the past, people saw Tron and realized that the Captain was a computer simulation the entire time.

In the past, people saw Tron and realized it was good for what it was.
Karl: No it wasn't.
Susan: Oh lord, accept ye my Frisbee of power...

Usual motion. Usual second. Usual vote. Usual complaint? But we did it right this time!

\goto{New Business}

They've invented zombie robots.

Brian: Wait, so they are flesh eating robots that \emph{were} alive but unlike other robots are no longer alive yet still moving?

Pseudo-Skinner fails at a bing and has to redo it.

\goto{Future Business}

In the future, there will be many things.

Motion to evacuate pizza, cashews, sunflower seeds, \emph{steampunk} bananas and other such food as might attract them from the library before the attack of the zombie roomba mecha ninja robots passes 12-0-1\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
