\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 5, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, LHE and pseudo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to condemn the minutes as being eerily accurate passes 4-1-1\ps.

\bing

\goto{Committee Reports}

\subsection*{hBarcomm}
The summer mailing slides have been prepared for eddification of the prefrosh.

\goto{Old Business}

Motion to deny all recognition of a past passes 4-0-2\ps.

\goto{New Business}

David Eddings passed away this week. He wrote ``very good crap,'' the literary equivalent of Dunkin' Donuts coffee, and brought lots of people into reading fantasy.

There will be a book signing in the greater Boston area this week. hBarcomm fails at recalling details.

\goto{Future Business}

In the future, there will be ConCertino. The flyer is sadly lacking in details, but it will be in later June.

The motion adjourns by pseudo-Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
