\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Susan Shephard, Onseck}
\newcommand{\meetingdate}{Friday, November 20, 2009}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

Motion to condemn the minutes for failing to appreciate the supremacy of Spehn does not get seconded.

Motion to condemn the Onseck for failing to appreciate the supremacy of Spehn chickens 9-2-9\ps.

``You mean to say 'Pseudo-Onseck,' right? Since the Onseck didn't do last week's minutes.''
``No, I mean the Onseck.''

\bing

\goto{Committee Reports}

\subsection*{NaNoComm}
There was another write in. NH is behind but other people seem to be doing quite well.

\subsection*{WarComm}
The ASA failed less badly this week; they came to see the library around 6:30 p.m. yesterday afternoon, while people were here.

\subsection*{Hasslecomm}
Stuff happened.

ESP: ``Can somebody bring us paper towels?''
``No!''
(Skinner rushes out to give them paper towels.)

\subsection*{pseudoSurgeon}
Person with acronyms EPA (non-keyholder) will be helping Jade 

\subsection*{StarChamber}
Google has started talking to us again regarding the issue of getting the library scanned.

\subsection*{Onseck}
Banker's boxes, a red stamp pad and staples have been ordered for the Library's use.

\subsection*{pseudoPainOfSpaceComm}
It's going well; we're hopeful.

The refrigerator theory of antigravity is discussed. It's the coolest theory ever.

\goto{Old Business}

Usual motion. Usual second. Usual vote. Usual result.

\goto{New Business}

The new movie (two part miniseries) of The Colour of Magic is apparently awesome. Also, Hogsfather is apparently quite good.

Discussion of punnish things ensues. ``You don't say punnish, you say punny.'' Arrrgh.

Splash is tomorrow.

We're thinking of moving the MITSFS-SGS meetings and gameplay night to after Inventory.

The next book in the Codex Alera is coming out in four days.

MobComm is in Tennessee. ``What's in Tennessee?'' ``Trees, fog.'' ``Good reasons to leave.'' ``For a while last summer, lots of Shepherds and Marises.'' ``Mountains.'' ``Mountains? I dispute.''

\goto{Future Business}

In the future, there will be Thanksgiving. There will also be Stratton House pictures.

More discussion of copyright and Google and cookies ensues. The cookie embargo of Amol begins. 

Possible Miller motion, possibly containing the word banana passes 20-6-9\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
