\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 20, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Something passes by Skinnerial decree.

\goto{Committee Reports}

\subsection*{Pianocomm}

We have a new keyholder - MIF, Lee Fuchs!  She is short, but she swept
the library!

\subsection*{Picniccomm}

We have a Picniccomm, so we will be having a picnic.

\subsection*{Capricomm}

There are lights in the library!  Ignore them.

\subsection*{FrustratedAuthorcomm}

MHG is in a contest!  You all should write reviews.

Less angst, and more robots.

If you are expecting magical weirdshit to descend from the sky, that
doesn't happen.  

\goto{Old Business}

Back in the day, there were wars.  They were just weird.

\goto{New Business}

MHG: Usual dictatorship.\\
ESK: Thank you.

They could elect Kittens again.

MKR: It's Spring Break!  It's Spring Break!  Finally, it's Spring Break!

\goto{Future Business}

MKR demands Feeling.  That didn't even merit the name of bing.

You can bing it without binking it.  Everyone's a critic.

It's nice to have demands.

Motion to have another banana bing passes by Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
