\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 28, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, LHE and pseudo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to commend the minutes for being good with ketchup and prions passes 11-7-4\ps.

\bing

\goto{Committee Reports}

\subsection*{VanHelsingComm}
Report of success. VanHelsingComm is looking for recruits - the original book has spawned sequels, which must also be put down.

Maniacal laughter.

Motion that we are unimpressed with the maniacal laughter passes 11-2-4\ps.

\subsection*{hBarcomm}
Paul and I have sent in an advert for MITSFS to be published in the Tech, hopefully on Tuesday and, if not then, on Friday. Also, the bulletin board is about three-quarters finished - it has a schedule up now - and the email regarding full credit for impromptu hours has been sent out.

\goto{Old Business}

David Eddings died this June.

Usual motion. Usual second. Usual vote. Usual result. What about the usual debate. Usual dictatorship. Usual rebellion, crushed mercilessly by the usual bing.

\goto{New Business}

Discussion of a course aiming to study science-fiction in terms of anthropology ensues.

Motion to go back in time and do ... something ... passes 16-2-1\ps.

There are frosh. They should be brought into the library.

MG: We rent shelf space from the frosh.

Motion to change membership to new members from the old method to being based on the risk of plantation closures in the plantain and banana growing areas of Brazil passes 12-6-0 \ps.

\goto{Future Business}



\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
