\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 24, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
MKR, LHE and and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

ESK arrives midway through the meeting.

Motion to condemn the minutes for driving off MKR and confusing the Onseck passes 12-3-4\ps.

\bing

\goto{Committee Reports}

\subsection*{Picniccomm}

You have to give yourself some time to get your pants together and buy a watermelon.  Words to live by!

KAT's story may have some... factual inaccuracies.

Paige's watermelon was very small.

\subsection*{Pseudo-Kvetchcomm}

There are three whole reviews and none of them by Jake Beal.  There are 99 reviews up!

\subsection*{LHE}

We asked Finboard for money to do the microfilm stuff... but we didn't
get it.  Oh well; maybe they'll get drunk this year.

\subsection*{Pianocomm}

Brian!  Brian is a prentice!

In these lax days, when anyone can pick up a key... and hold it...

\goto{Old Business}

Some of the prefrosh were not entirely bad.  There were frosh also,
but there are always frosh.  Some of them are not entirely bad.

I don't think they're scary.  I think one of them is smaller than the
gavel.

AL... GOL?

\goto{New Business}

There's a new Trek movie coming out!  It's coming out in two weeks.

The movie looks every bit as good as the originals.

Something...? fails by Skinnerial decree.

KKB says something.  Oh, it's regarding J. Michael Straczynski's
visit!  It's the Friday of finals week in the evening.

It's the thought that counts.  Seconded!  chickens 0-0-4\ps.

\goto{Future Business}

In the future, KAT will figure out why there appear to be \emph{no}
ends to her string.

In the future, the world will end.  That will be delightful!

The world ended while I wasn't looking.  Sorry, Ternus!

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
