\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 13, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Motion to commend the Skinner for her innovative use of arithmetic fails 0-1-3 \ps

\bing

\goto{Committee Reports}

\subsection*{hBarComm}

We will be having a booth at the Activities Midway.  We also have an
activity at the CPW Festival.

Book Jenga!  If you're particularly good at reorganizing the books, we
have a Job for you.


This is why I don't feel bad for you!  We need to fight compulsions,
unless they involve Diet Coke!  Kate can drink one can of Diet Coke,
which she has translated into one can per hour.  That's only one can
in the frequency domain!  

Kate will not get Asteroid Cancer.

\subsection*{Panthercomm}

Panthercomm did work!  We started on the first box of the Cohen
Donation.

Kendra looks nice!  It's because of MITSO.

\goto{Old Business}

You have successfully avoided the horrible bing!  I am very proud of
you.

Some stuff happened.

\goto{New Business}

Usual apathy.  We're in New Business.  Complaining is whiny, and
angsty, and usually ignored.  I'm just saying, in general.

Today is Pi Day As Observed.  Today is also a Friday the 13th that
falls on a Friday; that's the worst kind.

One hurdle has been hurdled successfully that would put the LHE in
China this summer.

Much discussion of jobs and the Singularity ensues.

You know, I think we're in Future Business now!

\goto{Future Business}

Spring Break is soon.

Wocka-wocka-wocka-wocka-wocka-wocka-wocka-wocka-wocka-wocka-wocka-BLINNNG-wocka...

In the future, tests will be over.

CJT once more brings out Fake Star Wars (Star of the Guardians).

Meeting adjourned via the Adjournment Song.  Bet you didn't expect that, huh?

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
