\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 10, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, LHE and pseudo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to commend Cast a Deadly Spell for existing passes 7-0-3\ps.

Motion to commend Lee Fuchs on phone call professionalism passes by pseudo-Skinnerial decree.

\bing

\goto{Committee Reports}

\subsection*{AnsweringThePhoneComm}
Very interesting phone call, don't know who was calling. It started out vaguely legitimate sounding - about a con or something - and ended with a query about submitting a story to MITSFS in return for free membership. Then the conversation kind of derailed, eventually getting to the quote ``Did you know George Bush wasn't in Iraq for oil? He was looking for the particular quality of sand found in Saudi Arabia'' at which point Lee decided to bring the conversation to a close.

Timewarp!

\subsection*{pseudo-Seldon}
White Star will be showing in two weeks; Tron may show in the interim.

Lets do the Timewarp again!

\subsection*{pseudo-Seldon}
Next Friday there WILL be a seldon showing of Tron, because apparently some undergrads incuding KKB are not aware of its premise.

\goto{Old Business}

Cast a Deadly Spell was last week and was wonderful. Vaguely modern urban noir fantasy; even Cthulu manages to put in an appearance.

\goto{New Business}

Motion to commend the City of Tokyo for building a 60-foot Gundam passes 8-1-1 \ps.

John Bajak brings up the philosophy of computing; the meaning of life is refrigeration and the purpose of life is to make ice.

\goto{Future Business}

Timewarp request, again. To committee reports - again!

Motion that the following report is not a pseudo-albanian report fails 3-6-2 \ps.

Mifuchs: Miyazaki, who did Spirited Away and Howl's Moving Castle, is going to be at ComiCon.

What's that? A buckyballish thing. What's that egg-like thing? A banana.

Motion to commend the bananas for existing in the library passes 11-5-1 \ps. KKB: Laaaaaame!



\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
