\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 20, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Lee Fuchs, prentice and pseudo-Onseck, recording.

Minutes read.

Motion to condemn the minutes for using brotosaurus and porn in the same sentence passes 13-3-6\ps

\bing

\goto{Committee Reports}

\subsection*{Pianocomm}

Prentii did work.

\subsection*{Catacomm}

Three more boxes were processed to replace what was gotten rid of at Boskone. 
Prentii did work. More such will happen.

\subsection*{Hasslecomm}

It happened. Naomi wasn't there to document, but it happened.

\subsection*{Niagracomm}

Boskone happened. Lots of books were sold. Ninety books for thirty dollars?

\subsection*{Painofspacecomm}

Waiting on March 1st.

\subsection*{Seldon}

Coraline tonight--movie nights will happen after next week otherwise.

\goto{Old Business}

Token bing.

Onseck and pseudo-Onseck are in the process of dying.

Things happened.

Boskone happened. It was awesome. They had the cover art for Pretender. And
the Planters Peanuts peanut getting destroyed by a squirell. Rock. Also,
duelling bananas. And lots of cats. Mostly cute, but one or two creepy.
Boskone now offers student memberships, which would have been more helpful
last week. Oh well.

Discussion of Guild Games, zombies, souls, and spleens. And dvp failing at
eating the right spleen.

Further old business, 'cause this is REALLY old business...

Usual Motion, Usual Dictatorship, Usual Debate, Unusual Algol... etc.

\goto{New Business}

Nothing's new under the sun.

"We could just get a new sun."\\
"That would be awesome."\\

Crank, Fantasy Commentator, Expanse, and Fantasy Review are all new!

The Triumverate of Not Reading Bujold has been formed (Margaret, Kendra, and
Lee). And no, Kate, it's not because of Miles' inch-to-four of height over two
of the Triumverate.

We want new books. Third Lynch book, another book... Dresden in April! And others!

"A sapling makes a \emph{good} weapon for an angry dragon."

Peter Jackson bought the rights to alternate-history with dragons-in-Napoleonic-Wars.

"The correct use is thickness-challenged. Page-number challenged!"

Katie finished a book.

\goto{Future Business}

In the future, Margaret will have a midterm that is a case study on the viability
of banana farms. No, really, for realz.

In the future, pweaver will be killed, beaten by a banana. But only after we've gotten
more work out of him. This will only affect the number of warm bodies, as MITSFS claims
souls upon prenticing and death will not change the number. Although he could always
be kept warm artificially. 

"We could turn them all into dreadnaughts."\\
"Banananaughs."\\
"Second!"\\
"Lame..."

Motion fails 2-8-3\ps

bings

Motion to thank Skinner for being more moderate in her delivering of pain fails by
Skinnerial decree.

In the future all this dining wanking will end. ("It will?") And it will require
mandatory bananas.

And before you're all forced to eat bananas, you should come eat Chocolate on monday.

Motion to introduce mandatory chocolate covered bananas for everyone who wants one
passes 17-0-2\ps

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Lee Fuchs, prentice and pseudo-Onseck}

\end{document}
