\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 4, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to accept Brian's apology for last week's motion regarding bananas and plaintains fails by Skinnerial decree. Angry fist.

Motion to condemn the minutes for not containing enough chainswords per volume passes 37-3-7\ps.

Lee: Oh, I see. Chainsword.

\bing

\goto{Committee Reports}

\subsection*{Pianocomm}
If any frosh are interested in becoming librarians - we call them keyholders - talk to us after the meeting. 

Discussion of the prenticeship process and general abuse of power ensues.

\subsection*{LHE}
Paul has prevented SAFO from embezzling money.

Motion to comment Paul for ``whatever the hell he did'' passes 20-7-8\ps.

Motion to give the chainsword its own independent vote passes 28-3-9\ps. 

\subsection*{Trojan}
We're going to send out letters ``real soon now.''

\subsection*{hBarcomm}
The Midway happened and appears to have been successful.

\subsection*{pseudo-Seldon}
The way Seldon showings work is described.

\subsection*{hBarcomm again}
We ran an add in the Tech last week.

\goto{Old Business}

Miss Katie Ray is back from China. New frosh have appeared in the dorms. MHG has met many more engineers who are trying to take over the world; they were apparently at the Midway.

Motion to commend the frosh for having an amusing ringtone fails for lack of a second.

Kat and Brian Sniffen have returned from Israel.

MHG has successfully staked the Twilight book.

Debate over whether or not there will be more Twilight books ensues. The Onseck maintains that the world is not so dark and evil a place as would allow more Twilight books to emerge from the deeps. Trojan is not so confident.

Usual motion. Usual bing. Usual reluctant deference to the Skinner. Usual Chainsword. ``That's not usual, that's unusual.'' ``Not for me!''

\goto{New Business}
There are a lot of new people.

``Join MITSFS!'' ``That's not new.''

Totally not hazing the frosh ensues.

Discussion of Google searches, Google's opinion of humanity, and the unfortunate search ``Is Edward Cullen real?'' ensues. MHG tries to commit seppuku via the chainsword.

Usual complete lack of remembering where we left off in the meeting.

Bad back-cover reading time follows. ``Katalo's own future is in peril. From the ocean's depths rises an impossible blend of fantasy and danger, a creature whose voice is seduction incarnante . . .'' 

Kendra is threatened by the chainsword until she stops reading. Our ears! They bleed...

Motion to apply rosin to the vampires chickens 11-8-13\ps.

Motion somehow involving bond salesmen chickens 6-3-14\ps.

Motion to have a Matrix vote passes 22-7-2\ps.

The determinant is 1044, apparently. Please God have mercy on the poor Onseck's soul.

Back in the day, during the Cretaceous period, Spehn would chicken. Every single time. So whenever he missed a meeting, others in the society would add in his vote anyhow, because they knew how he would vote. Now, even though he misses most meetings, we still include him.

MITSFS: Better institutional memory than most student groups.

We have a grad student!  They exist?  It's called Lemur!  Maybe that's strange enough to counterbalance the existing bit?

\goto{Future Business}

In the future, we will move on to future business.

In the future, Onseck will review determinants.

In the future, MITSFS may be listed on the lobby and elevator directories. 

``Why bananas?'' passes 42-1-4\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
