\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 16, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Miss Katie Ray, President and Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion for Kendra to eat Sukrit's brains fails 15-8-2 \ps. ``What?'' ``She's the Skinner, she can do that.''

\bing

\goto{Committee Reports}

\subsection*{WarComm}
Warcomm Starts today. We hope to get more space. Gather the armies! Pillage! Burn!

Motion to condemn WarComm for imitating the factual accuracy of the thistle something something . . . Onseck fails at getting it all down. It sounded awesome, though, Brian, if that's any consolation.

\subsection*{Onseck}
Onseck will become a faster typer soon now, no really.

\subsection*{Catacomm}
Catacomm exists! Also, Catacomm has done work despite being out of state due to the existence of the awesome prentice named Ben. Yaaay Prentices.

\subsection*{pseudo-Surgeon}
Surgeon did work.

\subsection*{Seldon}
There is a showing tonight. Also, if you have suggestions OTHER THAN Twilight, email Lee.

\subsection*{pseudo-Libcomm}
There is a function in the Dex that should tell us where the bugs are located.

\subsection*{LHE}
MITSFS got 1000 dollars finboard funding. This was less than we were hoping for, but good to have nonetheless.

\subsection*{Trojan}
We've received more of the Cohen donation in the mail. Raised eyebrows are indeed an appropriate response.

\subsection*{Theftcomm}
Would like to commend the prentice who knows Pearl; he has been useful.

\subsection*{MooComm}
We have tickets for a free showing of The Fourth Kind for next Thursday.

\goto{Old Business}
There is a prequel to Republic of Thieves on Camorr.com. Probably worth checking out.

The Apocalypse is coming soon. Someone should check to see if George R.R. Martin is about to finish Dance with Dragons. 

Codex Alera is coming out soon, to general excitement and discussion of angst.

Usual motion, usual second, usual vote, usual result, usual complaint.

\goto{New Business}

There are parents here this weekend. ``Ah. That's why there's no parking.''

Brandon Sanderson has offered to complete the Song of Ice and Fire, after he finishes the Wheel of Time. (Note, this is likely a joke.)

The last book of the Wheel of Time has turned into three books. The curse begins again . . .

``The problem with Epic Fantasy is that it really should have an ending.'' ``The problem is that books without endings are NOT Epic Fantasy.''

\goto{Future Business}

In the future, cables (a knitting reference) will get easier.

In the future, Alera will burn. And there will be a LARP tomorrow.

A motion to collect half a dozen of our female feline pets, comb the hair from them and turn the hair into knitting yarn so that Kat can knit Cat-Six Cables. Votes: 2-7-15\ps.

Motion to commend BrioVotes: 16-1-5\ps. 

Motion to torture the Onseck. Votes: 7-5-11\ps.

The determinant is 82. 

Motion to tax the citizens of Albania on a per head per hill basis and to set aside a fund for the treatment of damaged Onsecks who have been driven bananas passes 15-1-4\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
