\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Miss Katie Ray, President and Skinner}
\newcommand{\onseck}{Susan Shepherd, Onseck}
\newcommand{\meetingdate}{Friday, December 11, 2009}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Sukrit does an evil thing and hands the Skinner an Internet article called ``Why Men Shouldn't Write Advice Columns.'' It is quite excellent.

Minutes read.

``Mold! We hates it, we hates it, we hates it FOREVER!'' passes 17-6-9\ps.

Addendum motion to commend last week's minutes for their excellent time displaicement properties passes 10-1-9\ps.

Motion that anyone can use their limbs as proxies for any other limbs fails 10-10-2\ps.

Many things are established to be just as they are in Afghanistan.

\bing

\goto{Committee Reports}

\subsection*{PainOfSpaceComm}
The microfilm and microfiche arrived in Utah and are getting scanned.

\subsection*{WarComm}
The appeal was sent in. SIR: Rawr! SAS: Sings a line from March of Cambreadth

\subsection*{StarChamber}
There will be a timewarp coming up. Also, Inventory is on the 9th of January. Also, District 9 is showing this weekend as LSC for 4 dollars.

\subsection*{Catacomm}
The ritual changing of the guard - the changing of old for new magazines on the shelf - has happened successfully all semester.

\subsection*{pseudoPanthercomm}
We have received several more boxes of books for Panthercomm to deal with.

\goto{Old Business}
The Skinner's brain has returned, and the MITSFS has a Skinner again.

Discussion ensues regarding the alien which may or may not be controlling the Skinner.
KKB: Brainslugs!
SAS: Can't be brainslugs, *I* control the brainslugs. Maybe it's the Titans from Puppet Masters.

In the past there were classes. Now there are only finals.

Motion to condemn the Skinner for bragging about not having finals FAILS. Seriously, did you think that would work?

Usual motion, usual second, usual vote, usual result, usual rebellion, usual anarchy! Usual tyranny. I mean, usual dictatorship.

\goto{New Business}
Motion to commend the Skinner for increased decisiveness regarding stern putdown of the mob. The dissidents will be whipped by devils, or something. And chased with angry mobs supporting the Skinner.

Motion to give pitchforks to the angry mob chickens 10-13-12\ps.

Miller motion, fails something-18-10\ps.

Motion to instruct the scientists in Sciencetown to produce a banana-colored weather control ray to induce an Ice Age and have everything freeze to death passes lots-1-5\ps.

\goto{Future Business}

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
