e\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 7, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, LHE and pseudo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to change the designation of last week's minutes from minutes to seconds passes 7-0-1\ps.

Motion to commend Karl for managing to stick the word ``banana'' in last weeks minutes \emph{fails} by pseudo-Skinnerial decree, because damnit we're not falling for that again.

\bing

\goto{Committee Reports}

\subsection*{pseudo-Seldon}
There was a showing of White Dwarf last week. It was, um, \emph{interesting.} The first half was not particularly memorable, the second half was excellent; on average it was enjoyable and had both quotable moments and emotional punches.

\subsection*{Onseck}
We have much better membership sheets now.

Motion to replace Fweekcomm with PhysEdcomm for dealing with physically weak frosh fails for lack of a second.

\goto{Old Business}

There are old people at the meeting. Well, technically if they're all over 30 then all of them are awesome rather than old...

Way back in the day, JFC got a book about a guy who got gills due to lung cancer and swam among the kelp for a while, then died from toxic waste exposure. He cannot remember the book title, which may be just as well.

Brian may speak slowly and clearly so that the Onseck can actually get his comments down. The Onseck doubts this will last.

Usual motion. Usual second. Usual mistake in the order. Usual bing coming in three, two, one --

\goto{New Business}
A trailer for Tron 2 is out. It looks shiny.

JFC: Back in the day, we had Tron, and we didn't even call it Tron I, and we liked it.
Brian: Now the light cycles can make turns other than at right angles.

District 9 is coming out, and is allegedly good. Basically, aliens get to the solar system, run out of gas and park above Johannesburg in South Africa. Plotful stuff ensues.

JFC: I should now take this opportunity to recommend you NOT read ``Illegal Aliens'' by Robert Soyer. The science was just bad, the book was just bad... I didn't like what I read.

Discussion of authors who deliberately pursue awards ensues.

\goto{Future Business}

In the future, JFC will read some of the stories in the anthology he's holding, ``Year's Best SF 26''.

Last year, there were fourteen different ``Best Stories in Fantasy'' or ``Best Stories in SF'' anthologies. Hum.

Miller motion fails 5-7-4\ps.

eKate enters, and her hair is brown. Yay Thunderbunnies!

Motion to note that if your head is four degrees off it is highly uncomfortable passes 6-0-2\ps.

The second Miller motion passes by pseudo-Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
