\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 19, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, Lord High Embezzler and pseudo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to ``Fist of an angry god!'' passes 18-4-2\ps.

eKate: Think about what happened to the last guy who used his fists! (Everyone stares at her) No, guys, I didn't mean that in a sketchy way!

\bing

\goto{Committee Reports}

\subsection*{Catacomm}
Someone is obsessed with Philadelphia.

Discussion of a recent trip to Philadelphia ensues, touching on the interesting condom sign, the tiger exhibit with ``the other leopard'', the kitties, some of whom were big and striped, because they were tigers, and the phallic fountain in JFK plaza.

\subsection*{Scanners do not live in vain}
We are going to receive a grant from NESFA. Essentially, we have a lot of magzinges stored on microfilm, which is not a very durable format (and has the additional problem of being not terribly useful). We would like to move it from microfilm to a better, more durable format, such as the Intarweb.

Discussion of Cordwainer Smith ensues. He was pretty awesome.

\goto{Old Business}

Usual Albanian election! Usual Albanian protest! Usual Fist of an Angry God! Usual Iranian dictatorship!

\goto{New Business}

Stuff is happening in Iran.

ConCertino is happening this weekend.

\goto{Future Business}

In the future, eKate will go ``Poof'' and appear in Ohio.

In the future, Tennesee will be hot.

The Skinner has no tail at all...

The meeting ends by song and by pseudo-Skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
