\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 14, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Paul Weaver, LHE and pseudo-Skinner, presiding; Susan Shepherd, Onseck, recording.

Minutes read.

Motion to commend last week's minutes for anticipating Andrew Clough's reaction passes 9-0-0\ps

\bing

\goto{Committee Reports}

\subsection*{Star Chamber}
There are new membership rates. The first one starts at $13, then $24 for two years, $33 for three, and $40 for four. Lifetime memberships are now $260, permanent are $2600.

\subsection*{FrustratedAuthorComm}
Last week she got a thick letter, and was excited. But then it turned out to be a rejection letter printed on really thick cardstock for some reason.

MHG: They printed a rejection letter using an entire sheet of paper. It means they care.

\subsection*{pseudo-Analogcomm}
Would like to remind everyone to think about which hours they will want for this upcoming semester.

\subsection*{hBarcomm}
The application for a table at the Midway event has been sent in.

\subsection*{Theftcomm}
Theftcomm promises another TIF will appear this Sunday. Via magic. He notes that no one has reached the top yet.

\subsection*{pseudo-Seldon}
There would have been a showing this week, but it was displaced by a Quidditch match.

\goto{Old Business}

MHG: Back in the day . . . when Dinosaurs roamed the Earth . . . and I was an undergrad . . .

Discussion of oldness vs awesomeness, the scourge of acne (DIE, acne! DIE!), Intro to Japanese, and getting carded for R movies despite having graduated MIT some years ago ensues.

Onseck has now actually gotten drunk. The effects were not terribly interesting. This is unlikely to ever happen again. What's the point of taking alcohol if its main effect is similar to sleep dep and you don't even get the clumsiness and slurring that the movies claim drunkeness will cause? Piffle.

Usual motion. Usual second. Usual bing. What about the usual debate? Usual dictatorship. Usual revolution. ``We're doing it wrong . . .''

\goto{New Business}

District 9 is out. MGH: I give it 4.5 squees out of 5.

Quidditch is tonight. You should come and play, or watch if you would prefer.

\goto{Future Business}

MGH: It is the future. Where's my jetpack?

TWH: I want two gravity belts - one to wear, and a back up.

Miller motion fails 4-7-2\ps.

Miller motion passes 9-1-1\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Susan Shepherd, Onseck}

\end{document}
