\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Paul Weaver, Lord High Embezzeler and pseudo-Skinner}
\newcommand{\onseck}{Susan Shepherd, Onseck}
\newcommand{\meetingdate}{Friday, December 18, 2009}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

Motion to commend last week's minutes for accurately predicting this week's Ice Age fails 3-6-3\ps.

\goto{Committee Reports}

\subsection*{pseudoSurgeon}
Just finished typing in titles for a box of uncovered books; there will soon be rather nicer covers for them.

\subsection*{WarCouncil}
There were appeals last week. We have hope. According to their piece of paper, they would release their conclusions today, but they have so far been quite bad at following what their piece of paper said.

\subsection*{pseudoKatiecomm}
The John Cox donation will be processed over winter break.

\subsection*{Star Chamber}
The time warp is beginning; please return books on the 6th of January if they're going to be late during 

\subsection*{pseudoKvetchcomm}
There is a new review of Twilight up. It is exactly a thousand words long, if the old saying holds.

\goto{Old Business}
Finals happened. Now they are over. Yaaay! 

Usual motion. Unusual silence. Usual dictatorship.

\goto{New Business}

ESK: I hear Joe Haldeman is the new SFWA Grand Master. 

There is chocolate in the library if anyone wants more. SAS: Wait, there's CHOCOLATE?!? (Shortly later) Om nom nom nom.

\goto{Future Business}

In the future, there may be more Doctor Who Christmas specials.

In the future, more people should read The Blade Itself by Joe Abercrombie.

In the future, there will be winter break and IAP. And hopefully, there will be more people to see Avatar.

In the future, our collection may become more complete. We have the one book written by God, but not the other two. We have the Bible and the Bhagavad-Gita, but not the Torah or the Koran.

Motion to make the signs in MITSFS banana-colored in order to make them more prominently visible to patrons fails 3-10-1\ps.

The pseudo-Skinner has no bing at all, bing at all, bing at all, the pseudo-Skinner has no bing at all, just a little thump.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
