\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 10th, 2009

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
Ekaterina Kuznetsova, President and Skinner, presiding; Christian Ternus, Onseck, recording.

Minutes read.

Discussion of rats, stainless steel and otherwise, fails for lack of a second.  

\bing

\goto{Committee Reports}

Sorry, Brian.

\subsection*{Onseck}

We got our office supplies!  Finally!  We have enough red pens for the
next hundred years of VGGs.

\subsection*{hBarComm}

CPW is next week!  We have a booth in the Student Center for all of
Thursday.  Wooo!

Margaret, you're demonstrating a disturbing knowledge of the
\emph{inside} of the Gor books.

Motion to Albanian MGH fails 12-13-``didn't you vote already?''\ps.

Ha ha!

Motion to declare Margaret an Albanian chicken passes 24-2-7\ps.  Beep!

\subsection*{Pseudo-Pianocomm}

Hey, look, there's a prentice doing work!  Yaaaay!

SAS flees back to lab.  Booo.

\subsection*{Star Chamber}

MKR does a ``dramatic back cover reading'' of the description of a
terrible B-movie, ``Alien Trespass''.

ESK makes some strange noises.

Going once!  Going twice!  Sold! To:

\goto{Old Business}

Four days ago, the man who inspired most of the science fiction
stories ever told passed away.  RIP, Dave Arneson.

A moment of silence descends upon the Library.

Right, so, what else happened this week?

Turn Coat came out!  Harry's life sucks.

\goto{New Business}

Once more, the usual dictatorship.

Where are the comic books?  California.  And Asimov is still dead... I think.

There's an analgesic coordinate transform that puts the sun back in
its original location.  Huh?

Everyone is tired.

\goto{Future Business}

In the future, there will be CPW, and prefrosh, and a four-day
weekend!

Congratulations, Kate!  You clearly have the temperament to go to grad
school (you're good at scrounging for free food).  I'm sure it's like
riding a bike and thus will not go away.

In the future, Kate will be a citizen.  Good luck!

I think you may be confusing ``tyranny'' with ``losing.''

``What's the matter, Kendra?'' ``They just killed the Wicked Witch of the East!''

Motion to replace the Wicked Witch of the East with a banana passes 12-2-4\ps.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

Bonus Post-Meeting Quote:

``There is absolutely no way that we can get from standing here to that pew in 23 minutes.''\\
``Greater Teleport!''\\
``I haven't leveled up that far, and if I try at this level, I'm
likely to end up in an abandoned Krispy Kreme in Allston.''\\

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Christian Ternus, Onseck}

\end{document}
