\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, April 9, 2021}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 70.3 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

\goto{Committee Reports}

Ye Downtrodden Membership: Wow, 3 people at the meeting this time! Welcome, Victoria and Catherine!

\goto{Old Business}

GBM attended, CP* Discord joined, still waiting on some Midway details.

\goto{New Business}

Operation INSOMNIA: \skinner updated the wiki with the committees/various info from 1987 onward.

Elections soonish- probably about a month from now. More info to come.

More emails asking if the library is open or if we're accepting donations. The answers are still no and no.

Yet another ASA event to attend- transition workshop on the 28th.

Minicult: "Alaska Costco shoppers say ravens are stealing their groceries."

\goto{Future Business}

In the future, there will be 4 people at the meeting! And the server containing our sensitive data will never crash! And we'll have genetically engineered glowing trees as streetlamps!

Motion to meet in person to eat banana bread muffins together. Motion passes 10-1-1 +Spehn.

\bing
\noindent
Meeting adjourned, 71.3 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}