\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Victoria Longe, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, June 4, 2021}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 69.69 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read, because we wasted enough time while \skinner looked into our system for taking minutes.

\goto{Committee Reports}

Committees are pretty much shutting down for the summer.

Realauthorscomm: asked about the potential author event in the Discord, but there was general disinterest.

Dominocomm: Minutes through 1981 are on the web; only 20 more years to go! Although \onseck is probably more than 80 percent done with them at this point.

\goto{Old Business}

ALGOL.

Rerecognition happened- we survive yet another year.

\goto{New Business}

Setting up work for prentices will happen RSN.

We also might plan some fun stuff. Stay tuned.

Minicult: 'Stand your ground' defense rejected in iguana killing. Also, Indian government employee declares himself reincarnation of Vishnu, skips work to go to '5th dimension.'

\goto{Future Business}

In the future, the library will get more books. Also, \skinner will return the four Vampire: The Masquerade books she still has.

The future will either be Blade Runner or Star Trek. Let's shoot for Star Trek.

In the future, we'll finally figure out all the secrets of Machu Picchu. Discussion of Mesoamerican archaeology.

Motion to eat a banana before the end of the summer. 5-1-6 +Spehn, motion chickens.

Let's try that one again. 7-0-5 +Spehn, motion passes.

\bing
\noindent
Meeting adjourned, 69.691 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}