\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, April 2, 2021}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 69.3 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

\goto{Committee Reports}

Phoenixcomm: We sent out some recruitment emails, resulting in 3-4 prospective prentices/ASA reps! Looks like we'll be able to hang on after all.

Ye Downtrodden Membership: Catherine's here again and will be serving as Minicult for this meeting!

\goto{Old Business}

None.

\goto{New Business}

Operation DOMINO: \skinner digitized yet more minutes- 1987 is now complete.

The ASA GBM is Monday and Activities Midway is on the 17th. \skinner will take care of the former but should probably notify keyholders about the latter.

Minicult: "Taiwan urges citizens not to change their name to 'salmon' to get free sushi."

\goto{Future Business}

Discussion of flying cars, Peachtree City in Georgia (where they primarily drive golf carts), marble trash cans, kid-run towns between WWI and WWII, preteens driving tractors, the southwestern United States, and national parks.

Discussion of possible ways the universe will end. In the future, the colonization of Mars will take place. At some point. Discussion of alien civilizations. 

Motion to make chocolate-banana bread on the radiators in the library when we're back in person. Motion passes 7-0-1 +Spehn.

\bing
\noindent
Meeting adjourned, 71.5 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}