\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, March 19, 2021}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 69.4 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

\goto{Committee Reports}

Phoenixcomm: There's a decent amount of interaction going on in the Discord- asynchronous discussions seem to be generally more popular than scheduled events, but a few people have been showing up to the game nights and such- thanks y'all! Also, a bit more advertisement happened in the form of dormspam.

Swancomm: \skinner has been digging a little deeper on space allocations, and it seems like they might be a bit more under CAC's purview than the ASA, so we might be able to work out some sort of arrangement where we're sponsored by SOLE and maintain CAC space even if we're derecognized by the ASA? Maybe something to look into.

Ye Downtrodden Membership: We've got chuang7 hanging out in the voice channel today! She recently read Station Eleven and Dune and gives them a recommend.

\goto{Old Business}

The library's still closed. A recent Reif email tentatively forecasts that space access will be back to normal in the fall.

Officer financial training happened, though the info didn't really apply to us.

\goto{New Business}

Operation DOMINO: \skinner digitized some more minutes. We're up to 1987 now.

A bit of discussion about keyholders, then more discussion about MITSFS lore/procedures.

Discussion of recent reads.

\goto{Future Business}

Miller motion. 5-2-1 +Spehn, motion FAILS!

Second Miller motion. 7-0-1 +Spehn, motion passes!

\bing
\noindent
Meeting adjourned, 70.4 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}