\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, May 7, 2021}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 69.6 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

\goto{Committee Reports}

Mommycomm: Punted, but will get back to it soonish.

Realauthorscomm: Ditto.

ROSFAP: A guy emailed asking about our fanzine collection. We directed him to the MIT Libraries rep that oversaw the donation.

\goto{Old Business}

Cruft (aka old people) are here!

The campus, and thus the library, is still closed.

ALGOL.

\goto{New Business}

We have two new keyholders- Victoria Longe (VLOJ) and Peter Choza (initials to be determined)!

ASA group rerecognition is due by May 21.

Operation DOMINO: almost done with 1985. Speaking of which, given that \skinner won't be skinner much longer, the SIS is now retired. \skinner creates Dominocomm and Insomniacomm to take over DOMINO and INSOMNIA's respective responsibilities and appoints himself to both.

Minicults: 1) Bill and Melinda Gates are getting divorced. 2) In England, police arrested a man on a canal barge after an eight-mile 4mph chase. 3) A farmer moved a 200-year-old stone, and thus the French-Belgian border.

\section{Elections}

As with last year, everyone has one vote and gives fractions of the vote to each candidate.

\subsection{Onseck}

Nominations: LAM, "pretty scarf to my right," Discord, Cleric Chih. Votes counted.

LAM: 4.25

Discord: 1.45

Cleric Chih: 0.75

Pretty scarf to my right: 0.55

LAM is elected Onseck!

\subsection{LHE}

Nominations: Peter Choza, the rocket currently launching, Jan Van Eck, the concept of money, the bartering system, For the Love of Money by the O'Jays. Votes counted.

Peter Choza: 3.25

Concept of money: 1.1

For the Love of Money: 0.9

Bartering system: 0.65

Rocket currently launching: 0.1

Peter Choza is elected LHE!

\subsection{Vice}

Nominations: COVID (Pestilence), Netflix (Sloth), Miami (Vice), Pierogicomm (Gluttony). Votes counted.

Adjustable (Vice): 1.9

Miami (Vice): 1.30001

COVID (Pestilence): 1.29999

Netflix (Sloth): 1

Pierogicomm (Gluttony): 0.8

SARS-CoV-2: 0.5

Lemur: 0.1

KHA: 0.1

Adjustable (Vice) is elected Vice!

\subsection{President}

Nominations: VLOJ, the office of Skinner, RS's hairbrush, JHS's Pez dispenser robot B4, all the books, all the non-moldy books, L. Court Skinner, JHS's 40th keyholder anniversary crocheted banana, the Gros Michel banana, the sports gavel. Votes counted.

VLOJ: 4.5

Non-moldy books: 0.8

Office of Skinner: 0.45

Gros Michel banana: 0.35

Sports gavel: 0.35

L. Court Skinner: 0.3

Crocheted banana: 0.2

Pez dispenser robot: 0.05

VLOJ is elected President! VLOJ is asked to appoint a Skinner. VLOJ appoints herself Skinner and appoints MJS to Skinner's Bitch, aka Skinner's Very Special Helper, aka Chancellor.

\goto{Future Business}

In the future, we'll be back on campus- hopefully this fall.

Motion to appoint JHS's 40th keyholder anniversary crocheted banana to Telzey Amberdon. Passes 15-2-7 +Spehn.

\bing
\noindent
Meeting adjourned, 73.9 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}