\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, April 23, 2021}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 69.1 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

We have 4 people here today! Great success!

\goto{Committee Reports}

Realauthorscomm: The Blumenthal event is still pending. vlonge will take the lead on responding and polling the Discord.

Seldon: No formal events yet, although there may be a watchalong with a new show coming out.

Mommycomm: Working on setting up some remote prentice tasks. The primary one at the moment is compiling book purchasing recommendations for Mobcomm.

\goto{Old Business}

Griping about emails/glounge.

March 16 was the 70th anniversary of MITSFS' first official meeting. "Happy Birthday" to be sung as the Adjournment Song.

The student leadership transition thing is this week; \skinner shoulders the burden.

ALGOL!

\goto{New Business}

Discussion of membership dues and endowment funding.

\skinner got his first shot!

Minicult: 1) Florida police capture loose lemur, another still on the run. 2) Man demands girlfriend stop breastfeeding their baby because it 'makes him feel weird'. 3) Bizarre 'worm tornado' in New Jersey has scientists baffled.

\goto{Future Business}

In the future, we will have 5 people at the meeting! Very ambitious.

In the future, it will be the present.

Happy Birthday to MITSFS is sung loudly and out of sync due to Discord lag. \skinner refuses to leave and revels in others' discomfort until RS uses her admin powers to kick him from the call, crashing his Discord client.

\bing
\noindent
Meeting adjourned, 71.8 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}