\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, April 16, 2021}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 70.1 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

\goto{Committee Reports}

Phoenixcomm: We're setting up a dedicated group of interested people on the Discord to facilitate the prentice-to-keyholder transition.

\goto{Old Business}

Midway happened! A few people joined our newest banana-frosh mailing list, so that's good.

\goto{New Business}

Operation DOMINO: \skinner did more minutes. Mid-1986 now.

An author event might happen soonish- details to be determined.

Minicult: The Lego black market is on the rise- thefts of Lego sets are increasing in frequency.

\goto{Future Business}

In the future, we will get vaccinated! Hopefully RSN.

In the future, specifically next pandemic, people will spend their eight months of quarantine by traveling to Mars- hopefully we'll be there by then.

In the future, we'll generate energy via panels of photosynthetic bacteria. And we'll have other living technology, like in the Flintstones.

Discussion of Hanna-Barbera cartoons.

The chosen Adjournment Song is the classic "I Know a Song (That Gets on Everybody's Nerves)." After three verses, \skinner flees the Discord call.

\bing
\noindent
Meeting adjourned, 71.7 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}