\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}

%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner\xspace}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck\xspace}
\newcommand{\meetingdate}{Friday, February 19, 2021}
%%%

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 70.9 ksec SST,
\skinner, presiding; \onseck, recording.

No minutes read.

\goto{Committee Reports}

Phoenixcomm: The Discord has now reached over 100 members. Yay! Possible events will be discussed shortly.

Swancomm: A copy of our will with MIT Libraries has been found, but it's somewhat nebulous on the matter of what exactly happens with our endowment or particular parts of our collection.

Mahogany Row: Cruft are here, spanning multiple generations- late 1990s, late 2000s, and mid 2010s are all represented.

\goto{Old Business}

The library's still closed. Returns, donations, and the like are still on hold.

An IAP Activities Midway was held, but it wasn't very well publicized and a decent amount of groups didn't get any visitors. Including us.

\goto{New Business}

Now that the semester's starting, we need ideas for events.

A Star Trek watchalong and a Project Gutenberg group will probably get going soon.

Game nights will likely become a regularly scheduled thing (party games, online boardgames are possibilities- we could set up some polls to see what people want).

The idea of asynchronous events is brought up- choose your own adventure with one decision poll per day, daily discussion threads, etc.

Discord-specific discussion. More ranks (prentice, etc.), rank-specific channels? At minimum we'll add one for keyholders. How about custom emotes- stake through Twilight book? Someone getting bonked with the gavel? Maybe if we can find an artist.

We should probably dormspam for the Discord again now that the new semester's starting.

The student leader financial summit's coming up- never fear, the skinner's here to bear the burden! Of boredom, that is.

\goto{Future Business}

In the future, we will have flying cars. Actually, in the present we have flying cars. So in the future, we'll have flying cars in showrooms that actual people can buy and use without dying. RSN, we promise.

In the future, there'll be more electric cars. Discussion of car companies' electrification plans, and region-specific sales of models.

Discussion of recent reading, book recommendations, and punctuation.

Motion to mail bananas to members in absentia. 3-1-2 +Spehn; motion does nothing.

Miller motion. 4-4-0 +Spehn. Motion fails.

Second Miller motion. 4-0-0 +Spehn, motion passes.

\bing
\noindent
Meeting adjourned, 73.6 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}