\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 14, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

Special guest star pseudo-Onseck- TLH! (WER, where are you?)

Motion to approve minutes as la-de-da. Passes 10-4-2 +Spehn.

\goto{Committee Reports}

Moocomm: Conan opens, lots of gore and fun.

Moocomm: Wrong is Right is good.

Moocomm: Sword and the Sorcerer- (censored). Avoid.

LHE Report: 7-cent interest added to bank account.

\goto{Old Business}

The usual routine, etc.

\goto{New Business}

Silence reigns for some time.

Everyone looks to Judy for guidance. Gets none.

Motion to forget all about Bill Starr. Passes many-none-2 +Spehn.

Starr leaves as finger motions fly.

Finger motion for someone asking who wrote Hitchhiker.

Motion to entice Bill* back with a banana. Passes 5-4-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1714 SST. LAST meeting of the year!

\vspace{18pt}

\centerline{Humbly submitted,}
\centerline{Tim Huckelbery, LHE and Pseudo-Onseck}

\end{document}