\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 9, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion passes to approve the minutes as the color of the solid part of the Skinner's shirt.

Motion to send the Skinner on a guilt trip because the snow prevented her from getting Ruffa's gold plated membership card. Passes 8-0-4 +Spehn.

\goto{Committee Reports}

Libcomm: Asimov said the 4th Foundation book was just brought to the publisher. So, we'll probably see it in about 6 months.

\goto{Old Business}

Nil.

Algol- S.O.S.

\goto{New Business}

Motion passes to blow up the building outside that's blocking our sunsets.

Larry Lenhoff has an interesting phone answering technique. "What!" and "Good intention paving... go to hell" or some such.

Minicult: for 295 dollars, you can get a 72-lb chocolate bunny from Bailey's.

Motion passes to define the holy spirit as coming from the Skinner. There is only one true Skinner- at a time, that is.

Motion dies neglectedly to observe that rabbits have no eggs at all.

Motion fails (foo!) to suggest that next year the Easter bunny deliver colored bananas.

Motion fails to sing "Rabbits have no eggs at all."

Motion fails to get Ken Meltsner here to get the song sung more often.

Motion passes to welcome Larry back with a banana. (Creative suggestions are encouraged.)

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST. ("If you want to welcome someone with a banana, you need a Skinner.")

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}