\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

To the National Endowment for the Quasi-Humanities:

Sketch for a Proposed Meeting of the MITSFS on

Friday, October 15, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
First, what say the Still Pseudo-Onseck [Janice Eisen] run this one and have the One and Eternal Member take minutes?

Many motions relating to the minutes, concerning their possible but unlikely approval, were bandied about.

(KRJ) Move to do this motion (waving notebook laterally, as opposed to longitudinally) to the minutes. Passes 15-6-4 +Spehn.

\goto{Committee Reports}

Pseudo-Moocomm: A Boy and His Dog opens tonight all around Boston; the words "Hugo Winner" are printed larger than the movie title.

Othercomm: There aren't any other reports, are there?

\goto{Old Business}

Naah, we don' need no stinking Old Business...

OBA: The usual "et cetera" with the usual outcome.

\goto{New Business}

We could have done SOMETHING here- I dunno... maybe we did... well, that's OK... couldn't have been important... I hope.

Oh yeah, it was moved to censure L. Ron Hubbard and St. Martin's Press for false advertising for declaring Battlefield Earth the hit of Chicon. But this died for lack of a second.

(Flynn) Minicult: The President (of the U.S.&A.) has named an SF writer to the National Council on the Arts: Alan Drury.

It was noted that Drury couldn't be a real SF writer, since we have no entries under Drury in Pinkdex. (It's so nice to have an absolute reference handy...)

(g) Motion that a letter be sent to Reagan challenging his choice. (KRJ) Amendment- ...and that John Norman be substituted on the Council. Amendment chickened 4-6-9 +Spehn, motion passes 12-3-4 +Spehn.

"Which of the 26 letters should we send him?" Much vehement discussion followed, including the Great Q vs. R Debate, now best lost to history.

(KRJ) Move that we send Reagan four Qs. Chickened 8-6-a lot of chickens +Spehn.

Move to send ERGO a letter either accusing them of altruism for giving us a free plug or demanding to know their hidden motive since we KNOW they're incapable of altruism. Chickened under 10-under 10-somewhere around 10 +Spehn.

Move to sell MITSFS to Frank Purdue. Chickened 5-1-everyone +Spehn.

Move to note that we are no longer a one-chicken Society. CHICKENED!! 2-1-aleph one +Spehn.

Hitchcock came in to observe that A Boy and His Dog etc., etc. It was universally and boisterously pointed out that Pseudo-Moocomm had already said this.

Move to condemn Hitchcock for coming in after the Committee Reports.

Move to commend Hitchcock for having the good taste not to show up until after the Committee Reports.

Move to have a third motion so we can have a matrix vote. Passed 16-6-3 +Spehn.

Move to remain apathetic about Hitchcock entirely.

21-4-8 +Spehn, 12-10-9 +Spehn, 4-3-8 +Spehn. Consider two rival mathematical systems: [Various mathematics follow; system I solves by making each vote a vector and calculating trace of tensor, system II solves via the classic 3x3 matrix.] Determinant already declared negative, so all the motions are dead. It should be obvious to the most casual observers that Systems I and II are homeomorphic and both are totally inconsistent with Zermelo-Franckl, which is fine by me.

(Flynn) Motion that meetings are more interesting without the Star Chamber. Passed many-2-1 +Spehn.

A motion to declare the Star Chamber a banana failed to gain substance due to lack of a second. Yet a similar-sounding motion to declare a banana equivalent to the Star Chamber passed at 14-3-6 +Spehn.

\vspace{12pt}

\noindent
The meeting totally lost all incoherency at 17:25 SST and disappeared.

\vspace{18pt}

This meeting will require 10-20 live actors (or their designated surrogates), one large wrench, one titanium block, and one case of ginger beer to produce in all its requisite splendor (or squalor).

Thank you for your consideration of this proposal.

\centerline{Recklessly submitted,}
\centerline{Gregory Ruffa(TM), a Pseudo-Pseudo-Onseck}
\centerline{and wholly-owned subsidiary of Western Union Telegraph Company}

\end{document}