\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 5, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion passes to approve minutes (to approve m- whoops... deja vu) as superannuated.

\goto{Committee Reports}

Pseudo-Commcomm: Looks like there are no committees.

The Skinner's annoyed that Technique won't list occifers. It was pointed out that perhaps they didn't like the 160 person list we sent last year. The Skinner corrected that: only 30-40 people.

\goto{Old Business}

There's never any old business.

There was a discussion of Old Business Algol, during the course of which the Onseck was finger motioned (which passed without a vote since the Skinner didn't want to count- it's been a tough term).

\goto{New Business}

Miller motion 1 was ignored. Some nerve!

LSC may get Star Wars next fall.

Miller motion 2 was ignored after a discussion about ignoring Miller motion 1. Arrgh!!

Motion passes (but just barely) so that next time we have a new book reading catchup, we have it with a banana and french fries.

\vspace{12pt}

\noindent
Meeting adjourned, 17:24 SST. Stamp out apathy!!

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}