\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 30, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion chickens to approve minutes as sickly green.

\goto{Committee Reports}

Picniccomm: Most of the food has been purchased.

Motion passes to censure a nameless (not really- rumor has it she has a perfectly good name) member for attempting to conduct real business.

Pseudo-Analogcomm: Something vague happened.

\goto{Old Business}

Old business and Old Business Algol happened.

\goto{New Business}

Elections!!

And, many ballots later...

President: Judy Passman

Vice: Adina Adler

LHE: Tim Blueberry

Onseck: Wendy E. Rowe (Hah! I wrote that one down before the results of the election.)

I'm going to leave if this isn't over... it is.

Motion passes to commend the new Skinner, aka the Prez, for having the foresight to wear a banana colored shirt.

\vspace{12pt}

\noindent
Meeting adjourned, 18:42 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}