\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 19, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, LHE and Pseudo-Skinner, presiding.

A deep silence descends.

(RVH) Motion to approve minutes as Earl Grey tea. Dies for lack of second.

(TG) Motion not to approve minutes.

(TLH) Motion to approve minutes as heavily editorialized. (TG) FA- to give Onseck a second to catch up. Passes 6+gavel-4-3 +Spehn.

\goto{Committee Reports}

(JME) Pseudo-Moocomm: The Last Unicorn and Empire Strikes Back open today. Also, Q.

Much discussion about Q's relation to James Bond.

(TLH) Moocomm: Dragonslayer tonight.

(TG) GAHcomm: It's been canceled. But who really cares? TLH: "Just when it was getting interesting, too."

(TG) Shuttlecomm: Shuttle came down.

(TLH) Ellisoncomm: Harvard tried to cancel Ellison- "We don't have the money." His reply- "Tough luck. I'm coming. You're paying. We have a contract, fuckheads!"

Much applause.

(Smoot) Whocomm: Dr. Who's 19th birthday. (Sang "Happy Birthday to Who.")

(Man in corner) Albanian motion on Pete. Finger motion on TG for asking which corner. Albanian motion passes 8-4-3 +Spehn.

\goto{Old Business}

Old Business Algol. Enough about Tom Galloway and gag, already! Passes many waving hands and legs-not quite as many waving hands and legs-2 legs +Spehn.

\goto{New Business}

(TG) Minicult: West Virginia TV station showing Green Slime cut to an X-rated movie.

(TG) Motion to condemn West Virginia TV station for showing Green Slime instead of green banana. Fails 4-11-about as many +Spehn.

(TLH) Motion to nail Skinner to library door with a banana, thus keeping her here all of the time. Passes quite a lot-2-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1716 SST.

\vspace{18pt}

\centerline{Rejectedly submitted,}
\centerline{Janice Eisen, Onseck}

\end{document}