\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 3, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, LHE and Pseudo-Skinner, presiding.

(Chip Hitchcock) Move to censure the minutes as being too coherent.

(TLH) Move to censure the minutes as being too long.

They second each other's motions. (Tom Galloway enters. TLH: "Damn. Why couldn't you have been Judy?" What a metaphysical question.) Both motions pass 7 or so-4 and a finger-3 +Spehn.

(Hitchcock) Motion to condemn 2 randoms for not voting at all. Chickens 2-2-my goodness, quite a few +Spehn.

(TG) Motion to commend 2 randoms for not voting at all for good taste. Passes 4 and a touchdown-1 extra point-3 needs to use bathroom +Spehn.

\goto{Committee Reports}

(TLH) Moocomm: Sometime within the next year, a movie will come out called The Star Chamber.

(TG) Motion to quickly copyright "Star Chamber" and sue the movie company. Dies.

(TG) Moocomm: From Russia With Love tonight.

(TLH) Moocomm: National Air and Space Museum showing Just Imagine as part of SF film series.

(B*) Sitcomm: CBS making Man from UNCLE TV movie. Patrick Melke as director of UNCLE.

\goto{Old Business}

Old Business Algol: um, us, uv, ur.

\goto{New Business}

(TG) Motion to buy Skinner a teleprompter. (Especially pseudo-Skinners who lack sleep.) Passes 11-3-6 +Spehn.

(JME) Minicult: Microsurgeon, by Imagics- a video game cartridge. Apparently based on Fantastic Voyage. (MG) And Commie Mutants from Outer Space. (TLH) And Custer's Revenge.

(TLH) Motion to buy Commie Mutants for the Society. (TG) FA- And not to buy a TV set and Atari. Passes lots and lots of bouncing boys and girls-2-5 +Spehn.

(JME) Motion to buy the Society a banana-colored Albanian phrasebook. Passes 10 1/2-9-7 +Spehn. Amendment to be discussed next week.

\vspace{12pt}

\noindent
Meeting adjourned, 17:20:48 SST.

\vspace{18pt}

\centerline{Boredly submitted,}
\centerline{Janice Eisen, Onseck}

\end{document}