\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 17, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

Minutes read.

Motion to have minutes read as hours. Passes >6-<6-n +Spehn.

Motion to censure Skinner for not knowing how to count.

Motion to censure person who censured Skinner.

3rd motion to get matrix.

Skinner: "It passes." Everyone refuses to vote after it passes.

\goto{Committee Reports}

Moocomm: Star Wars happened.

Pinkdex exists (sort of).

Motion to condemn Panthercomm for double vision. FA- to condemn Society for ddoouubbllee vviissiioonn. Passes 15-10-3 +Spehn.

TZ has been achieved but does not exist. Needs typing.

Motion to censure the Onseck for something or other. Passes a lot-0-2 +Spehn.

Motion to return all the chairs. Fails somehow.

\goto{Old Business}

OBA, etc., etc. "God that was fun." "I want more enthusiasm."

\goto{New Business}

Motion to create enthusiasm committee dies for lack of second.

Motion to censure for disgusting rework. 20-4-16 +Spehn.

Motion to make vote approximately equal 1. Chickens approximately 20-approximately 20-approximately 11 +Spehn.

Minicult: Spielberg receives Peace Medal.

Motion to send Spielberg a piece of banana metal passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Disgustingly submitted,}
\centerline{Tim Huckelbery, LHE and Pseudo-Onseck}

\end{document}