\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 10, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(All of 6 people here- sheesh!)

The Skinner, in honor of the end of the term, appeared in a low-cut black spandex leotard, black fishnet stockings, heels, and nothing else. She reported that she was wearing black lace underwear, but it was unfortunately not visible. (Now aren't you clods sorry you missed it!)

The LHE presented the Society with a new gavel which he had obtained from a government surplus warehouse in Taunton.

The Onseck did nothing special to mark the occasion, being neither as resourceful as the LHE nor as sensuous as the Skinner. She just read the minutes.

(MG) Motion that the minutes be approved as read very nicely, thank you. Passes 5-1-3 +Spehn.

(JP) Motion to flog the LHE for not making a deposit. LHE gets very excited at the prospect, panting at the Skinner's S&M outfit. Passes 4-1-3 +Spehn.

Finger motion on the Skinner for asking "Where is everybody?"

\goto{Committee Reports}

(TLH) Moocomm: There is a strong probability of a Lost in Space movie coming out soon. Producer-director Irwin Allen.

\goto{Old Business}

There would have been old business if the Onseck had written down the amendment last week. But she couldn't, since the meeting had been adjourned. So it's really not my fault, but the LHE's, for not having a vote on the amendment first. So get off my case, okay?

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Motion to form a committee to investigate what the government was doing with one of our gavels. After much discussion on name, Plumbcomm is chosen. (After MITSFS Plumbers, dolts!) Passes 7-0-0 +Spehn.

(TLH) Minicult: A company called Starpool is making cardboard figures of Kirk and Spock that you can put in the back seat of your car if you get lonely. The Spock figure waves a Vulcan salute, the Kirk figure a communicator. (Editorial comment: How about a cardboard figure of the sensuous Skinner?)

(TLH) Motion to name the Skinner MITSFS Playmate of the Year. Passes by acclamation.

(TLH) Motion to get the Society a new banana to smash with the new gavel. Fails 3-5-1 +Spehn.

(RVH) Motion to buy the Skinner a pair of banana-colored fishnet stockings. Passes 4-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST. A wild orgy followed, whose details shall be forever unspecified.

\vspace{18pt}

\centerline{Submissively submitted,}
\centerline{Janice Eisen, Onseck}

\end{document}