\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 5, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(TG) Move to approve minutes as incoherent. No second.

(SG) Move to approve minutes as Paul Grey.

(SG) Move to approve minutes as Pale Grey. Second. (JP) FA- with pinstripes. (Everyone stealing chairs throughout.) Fails.

Move to approve minutes as pale grey with green pinstripes. Passes many-some-not many +Spehn.

Finger motion on TG for asking why JP isn't holding the gavel.

\goto{Committee Reports}

(TG) Pseudo-Lecturecomm: Ellison at Hahvahd on Nov 29.

(GF) Pseudo-Moocomm: Mini-film fest tomorrow.

(DB) Pseudo-Concomm: Columbia has a con soon.

(SG) Jourcomm: Next week. (Meekly. She actually said "This time for sure.")

(TG) Move to condemn Jourcomm for not having antlers (see Rocky and Bullwinkle, I think). 7+Boston Globe-0-3 +Spehn. Motion fails (because of Globe).

(B*) Motion to condone Jourcomm. Chickens.

(TG) Pseudo-Moocomm: Hitchhiker tomorrow on 3rd floor.

Followupcomm: GAH lost his instruction book.

(TG) Move to get him a Xerox machine. Passes 10-1-2 +Spehn.

\goto{Old Business}

Algol, the usual dull yawning stuff.

\goto{New Business}

(KRJ) Minicult: Bradbury in Time on occasion of his first plane ride.

Minicult: obscene Hitchhiker personal ad in Phoenix.

(KRJ) Move to condemn TG for being curious. (DB) FA- to make it 26 years [illegible]. Passes.

Lots of finger motions.

(TLH) Banana motion (literally). Lots of amendments. Passes! Ta dah!

\vspace{12pt}

\noindent
Meeting adjourned, 1719 SST.

\vspace{18pt}

\centerline{Bananaly submitted,}
\centerline{Tim Huckelbery, LHE and Pseudo-Onseck}

Attached: obscene Hitchhiker ad- "Galactic Hitchhiker- pretty, pun-loving, slightly spacy SWF, 29, seeks SWM who really knows where his towel is. (Smokers welcome) Box 9784"

\end{document}