\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 29, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

Skinner says something incoherent. Also, Full Moon coming soon!

Skinner boos Albanian motion by Hitchcock on Skinner. Passed by Skinner.

(GF) Move to approve minutes as Albanian.

(SG) Move to approve minutes as basic black.

(LJL) Move to approve minutes as basic black Albanian.

(CH) Move to approve minutes as Trotskyite.

Pseudo-Onseck breaks down and cries.

Matrix vote: pi-42-6 +Spehn, 9-e-i +Spehn, 0-23-46.61235 +Spehn. Skinner rules positive, so they were finally approved as basic black Trotskyite Albanian.

Discussion of Albanian.

\goto{Committee Reports}

(SG) Jourcomm: "Presently." Skinner: "Screw 'em typos."

(SG) Pumpkincomm: Move to move Great Dome over Transparent Horizons and thus reaffirm faith in Great Pumpkin. Many (about 15)-2-4 +Spehn.

(CH) Pseudo-Moocomm: Hitchhiker's tomorrow.

Move to censure BBC for stupid timing of episodes dies with strange gurgling noises for lack of second.

(GF) Pseudo-Moocomm: New Dr. Who episodes on 2.

(LJL) Pseudo-Moocomm: Greatest American Hero meets aliens.

Stallcomm.

\goto{Old Business}

Old Shit Standard. MITSFS keeps old standards.

(GF) Result first, vote later.

\goto{New Business}

(TG) Move to condemn Society for not wearing costume. No second.

(GF) Move to put pseudo-Onseck on tape and excite him. Passes 8-6-2 +Spehn.

(TG) Move to reaffirm faith in Great Banana. Fails 7-9-3 +Spehn.

(SG) Move to satisfy pseudo-Onseck by costuming Society as bananas. Passes many-4-6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST. Yawn.

\vspace{18pt}

\centerline{Never again,}
\centerline{Tom Galloway, Pseudo-Onseck}

\end{document}