\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 8, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, LHE and Pseudo-Skinner, presiding.

(Again, only 25 percent of Star Chamber is present.)

Motion to note that Brad Schaefer is probably as dumb as Spiderman. Dies for lack of second.

Motion to approve minutes as more interesting than the meeting. Passes lots of yells-0-4 +Spehn.

\goto{Committee Reports}

Telephonecomm: Ring!

(TLH) Moocomm: Not much SF at all this weekend, but Dr. No.

(KRJ) Othercomm: Got Witter shipment. 2 copies of Foundation's Edge. And L. Ron Hubbard's new book! (See Minicult of 9/25.)

(B*) Greasecomm: Grease pencil is missing.

\goto{Old Business}

(KM) Move to declare that Ken Johnson's real name is Bruce. Dies for lack of second.

Old Business Algol: all the usual.

\goto{New Business}

(JME) Move to follow the lead of the GA and serve banana daiquiris at our next meeting. Passes quite a few-2-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1714 SST.

\vspace{18pt}

\centerline{Submitted by}
\centerline{Janice Eisen, Still Pseudo-Onseck}

\end{document}