\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 12, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion to approve the minutes as nondeterministic. Passes x-y-z +Spehn. (x>y>z+1)

\goto{Committee Reports}

Boredcomm: Gone fission.

Moocomm: Young Frankenstein tonight.

Jourcomm: Real Soon Now.

ROSFAP: Lazy (not to mention out of this dimension).

Bloomcomm: Nuked.

\goto{Old Business}

Old Business ALGOL.

Motion to censure Irwin T. Lapeer for his sex life with electric typewriters. Passes a-b-c +Spehn. (a>b>c+1)

\goto{New Business}

(CW) Minicult: In this year's officer list, which Technique refuses to print, Official Deceased Plant has been chosen to be the banana.

Motion to censure the banana for ceasing. Fails b-a-c +Spehn.

(Many hisses of dismay are heard.)

Motion to censure random members for kissing the banana. c-a-b +Spehn. Tie! (a=b+1) Tie is broken and utterly demolished. (I speak, of course, primarily of the male sex.)

Motion to censure random who asked where the SAA is. Friendly amendment- with a banana-shaped neutron bomb. Chickens b-c-a +Spehn.

(CW) Minicult: In an alternate universe, the Boston Glob has reported that bananas cause cancer.

Motion to forcefeed all Glob reporters carcinogenic bananas. Passes a-b-c +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:20 SST.

\vspace{18pt}

\centerline{Undersigned, inscribed, superscribed, and copyrighted by}
\centerline{Cheryl Wheeler, Pseudo-Onseck}

\end{document}