\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 22, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(TG) Move to approve the minutes as eternal (accompanied by much applause). Passes 15-5-4 +Spehn.

The Pseudo-Onseck requested a better pen and was showered with plastic objects full of ink. She strenuously objected.

Skinner: "I didn't learn how to count- just made the numbers up."

(TG) Motion to commend Skinner for finding a reasonable alternative to knowing how to count. Fails.

(GF) Motion to declare Skinner a No-Account. Passes.

\goto{Committee Reports}

Moocomm: It's the Great Pumpkin, Charlie Brown on Monday.

Moocomm: Star Trek, the Motionless Picture tonight. And a Mike Jittlov short.

(TG) Motion to commend LSC for getting Mike Jittlov's underwear. Chickens about 5-2-8 +Spehn.

(TG) Move to commend KM for chickening by doing the Funky Chicken. Chickens about 6-0-8 +Spehn.

(KRJ) Move to give Tom Galloway a better gag. Passes many-a random gurgle-1 +Spehn. KM carries out motion with a polyester scarf, and you should've been there.

Moocomm: Fantasia opens in Boston today.

\goto{Old Business}

Yeah, yeah...

OBA. Everything proceeded as semi-usual.

\goto{New Business}

(Liz Zitzow) Minicult: Christopher Reeve starring in Monsignor. Liz quoted the ad- I won't. Much discussion as to how this classifies as SF. It was not very wonderful and is thankfully lost to posterity.

(Liz) Minicult: Atari coming out with ET cartridge.

(RVH) Albanian motion on Tom Galloway. Passes many-3-3 +Spehn.

Tom Galloway gives his impression of a floundering Chinese opera singer attempting to make a motion. He appears to be appealing to the Skinner.

Skinner says it's time to legitimize the pseudo-Onseck. KRJ expressed enthusiasm. But I'm illegitimate by definition.

(MJG) Move to appoint JME Onseck since Wendy abandoned us and moved to Albania. Passes many-5-6 +Spehn.

(RVH) Move to censure KM for not bringing banana daiquiris to the meeting. Chickens, any numbers you want +Spehn.

(RVH) Move to gag Moon Zappa with a banana. Chickens out (Skinner: "...make 'em up.").

Rabbits have no (tails at all) x3.

Rabbits have no tails at all, just a powder puff 5 times.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Disrespectfully submitted,}
\centerline{Janice Eisen, Onseck}

\end{document}