\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 10, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Adina Adler, Vice and Pseudo-Skinner, presiding.

Move to approve the minutes as electric neon orchid. 18-9-3 +Spehn.

Move to censure the individual who didn't vote. Passes.

Finger motion for the pseudo-Onseck who asked who was the individual.

Motion to censure Zaphod Beeblebrox for voting too many times. 19-7-3 +Spehn.

Matrix: Motion to censure Janice for trying to censure someone who had voted, motion to censure the individual from the first motion for voting, third motion to have a matrix vote. Vice: "It will pass." 13-8-5 +Spehn, 17-5-5 +Spehn, 0-28-3 +Spehn. Onseck: "Looks positive to me."

\goto{Committee Reports}

Jourcomm: TZ 35 wants contributions. TZ 34 next week, by God.

Panthercomm: Pinkdex tonight!

Move to SIPB as God. Fails 11-18-5 +Spehn.

Moocomm: Star Wars tonight! And Hardware Wars!

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

Move to gag the Onseck with a banana. (Finger motion- passes.) 18-11-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Gumbily,}
\centerline{Ken Meltsner, Pseudo-Onseck}

\end{document}