\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 2, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Skinner: "I almost forgot how to do it, it's been so long."

Motion passes to approve minutes as implausible.

\goto{Committee Reports}

Ruffacomm: Greg Ruffa is finally going to get his gold plated membership card. (He's the one with the inheritable life membership.)

Picniccomm: Isaac said the picnic should be May 2, and we should invite his son.

Election meeting will be April 30.

Analogcomm- responsible for making sure foreign students put Sunday comics on their bulletin board.

ASFcomm was responsible for getting some "and so forth"s from a certain prof who sprinkled his lectures liberally with them.

\goto{New Business}

Minicult: Computerworld reported someone buying non-functional computer junk for 25 million to use in a movie, since it would cost more to make a fake.

Motion passes not to include the Focus' ad for the International Banana Company in the minutes. [Ad attached.]

\vspace{12pt}

\noindent
Meeting adjourned, 17:24 SST.

\vspace{18pt}

\centerline{Irreverently submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}