\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 1, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, LHE and Pseudo-Skinner, presiding.

(Note that only 1 member of the Star Chamber was present.)

Move to accept the minutes as confusing.

Move to accept the pseudo-Onseck as confused.

Move to accept the matrix vote as confusing.

Matrix vote: 4+uh-4-2/3 +Spehn, 1-1 yawn-2/3 +Spehn, 6-looks like 5-2/3 +Spehn. Determinant: 3 yawns and a headache. Motions pass.

Move to accept results as indeterminate. Dies for lack of second.

\goto{Committee Reports}

Nullcomm: No committee reports.

There was a futile attempt to sing the adjournment song which was quelled by the pseudo-Skinner.

\goto{Old Business}

All the usual junk.

\goto{New Business}

(LJL) Minicult: Aliens are draining the life energy of MITSFS members. That's why we're so desultory.

(TLH) Moocomm: Time Bandits.

Move to censure the pseudo-Skinner for not knowing where he is. Passes quite a few-not enough-very little +Spehn.

Random (Brad Schaefer): "Boy is Spiderman dumb." Passes many arms and legs-1 single arm-a lower thigh +Spehn.

Motion to award Bill* a banana for showing up late. Passes looks like about 20 to me (LHE: "I have things to do.")-about 3-many turning pages +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:11:40 SST.

\vspace{18pt}

\centerline{Rather conceitedly submitted,}
\centerline{Janice Eisen, Still Pseudo-Onseck}

\end{document}