\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 24, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

Motion to approve minutes because the person who will not be mentioned in this motion was not mentioned in the minutes and that all mention of it be struck out. Passes about 10-0-about 7 +Spehn. [The motion is struck out.]

The pseudo-Onseck is now very confused.

Move to accept the minutes as fine minutes. (Ken Johnson: "About as approving as I can get.") Skinner: "I don't know- make up a number and all decide." Motion chickens x-y-z +Spehn, where z>=x and z>=y.

Finger motion to unmentionable person for suggesting we explain voting procedure to randoms. Passes many-1-1 +Spehn.

\goto{Committee Reports}

Moocomm: Time Bandits tonight.

\goto{Old Business}

OB Algol: um, us, uv, ur.

\goto{New Business}

Motion to commend Society for apathy. Dies for lack of second.

Motion to commend Society for lack of apathy. Dies for lack of second.

Minicult: A restaurant in LA is operated by Spielberg's mother.

Minicult: See news clipping below. [Battlefield Earth book ad.]

Motion to distribute bananas to all who showed up at the meeting. Passes many-3 who won't get bananas-something +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Messily submitted,}
\centerline{Janice Eisen, Pseudo-Onseck}

\end{document}