\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 12, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Judy Passman, President and Skinner, presiding.

(KM) Motion to correct minutes (Boston GLOB). Passes 8-2-6 +Spehn.

(JME) Motion to approve minutes as deplorable. Dies for lack of second.

(SG) Motion to approve minutes as royal blue. Dies for lack of second.

(KM) Motion to approve minutes as better dead than red in honor of Brezhnev. Passes 15-1-4 +1 mole +Spehn.

(GF) Move to amend minutes to show I was here 10/1- phone company causing trouble. Dies for lack of second.

(KRJ) Move to amend minutes to show George was here 10/1 if he says so. Passes many-2-2 +Spehn.

\goto{Committee Reports}

(SG) Jourcomm: It's in Judy's drawers. LJL wants proof and tries very enthusiastically to get it.

(A^2) Panthercomm: Pinkdex is here. Inventory Sunday.

(TLH) Treasurycomm: We have some large sum of money. I don't know how much. Nobody tells me anything.

\goto{Old Business}

OBA- all the usual.

\goto{New Business}

Various dull motions were made, none of which were worth recording. I don't care, I have a headache.

Something or other chickened. Chip Hitchcock was hissed.

(KM) Minicult: Brezhnev's dead. KRJ: "Brezhnev who?" KM: "A famous metallurgist."

(TLH) Shuttlecomm: Shuttle did.

Motion to condemn Tim for his horrible lack of order.

Motion to commend Tim for his horrible lack of order.

Motion to be ambivalent about Tim for his horrible lack of order.

Matrix vote- 42-pi-3i^2 +Spehn, 2-0-null +Spehn, 100-hbar-nu +Spehn. A tie (predetermined result by Skinner).

(KM) Motion to put a banana into orbit. Passes 12-6-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Depressedly submitted,}
\centerline{Janice Eisen, Onseck}

\end{document}