\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 19, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

The minutes of the previous meeting were approved as the color of the cover of Jack Williamson's and James E. Gunn's first paperback edition of Star Bridge, a mind-jolting experience in a world beyond time.

\goto{Old Business}

Motion passed tense but past hence.

Old Business Algol- Lewis made a pass at Wisowaty and was repulsed. Move to censure the librarian. Motion to censure Irwin T. Lapeer for his sex life with electric typewriters. Both motions were seconded.

After much informed, witty, and quick-paced discussion, the motions passed 99991-23-17 +Spehn.

\goto{New Business}

The office was cleaned to increase shelf space. All books were discarded.

Moocomm: A movie was being shot depicting the sex life of the Library waterbed, mistress, and Skinner. Any similarity between the characters in the movie and any real people, living or dead, was purely coincidental. The director was also shot.

Skinnercomm: The Skinner seems to have disappeared mysteriously, along with the MITSFS Mistress and a large suitcase dripping water. The office waterbed is also missing.

Miller motion 1 chickened 0-0-100031 +Spehn.

Motion failed unanimously to beat each other over the heads with bananas.

Motion died for lack of second to store bananas on our now-empty shelves.

Miller motions 2-79 failed unanimously.

Motion was ignored to declare bananas endangered species.

Miller motions 80-126 failed unanimously.

Motion failed unanimously to investigate the use of bananas as aids in toad sexing.

Miller motions 127-64k chickened, null-null-aleph null +Spehn.

Motion failed to stab the next person voting against a motion containing a banana or even the word "banana" with a banana.

At this point, a berserker tried to stab all but 6 of the 100031 voting members with a banana, but the motion failed.

Rabbits have no tails at all, tails at all, tails at all. Rabbits have no tails at all, just a powder puff.

Rabbits have no tails at all, tails at all, tails at all. Rabbits have no tails at all, just a powder puff.

Rabbits have no tails at all, tails at all, tails at all. Rabbits have no tails at all, just a powder puff.

Rabbits have no tails at all, tails at all, tails at all. Rabbits have no tails at all, just a powder puff.

Rabbits have no tails at all, tails at all, tails at all. Rabbits have no tails at all, just a powder puff.

\vspace{12pt}

\noindent
Meeting adjourned, 16:45 SST. (This meeting brought to you from an alternate universe.)

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}