\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 16, 1982

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Cheryl Wheeler, President and Skinner, presiding.

Motion sort of like this (insert appropriate motion here [diagram of Ken Meltsner doing something like a squat jump]) passes unanimously, almost.

\goto{Committee Reports}

Pseudo-Picniccomm: Invitations were sent to Ben Bova, Harry Stubbs, and David Asimov. The picnic's May 2.

Ruffacomm: The Skinner has seen the card! The card will be picked up Tuesday. There's a suggestion that we bake it into a cake for him.

\goto{Old Business}

Algol- as usual, the usual.

\goto{New Business}

Pinkdexcomm: The Skinner says it compiles partially.

A paper trained cart stopped in at this point, and its tail was wagon.

The meeting was interrupted at this point to ponder the question of "What is truth?"

Moocomm: Wizards is tonight's movie.

Motion passes to change our name to the Albanian Student Association (to get the sympathy of the ASA exec committee) and engrave this new name into a banana.

\vspace{12pt}

\noindent
Meeting adjourned, 17:15 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Wendy Rowe, Onseck}

\end{document}