\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 26, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(KM) Move to approve the minutes as banana yellow. Motion zapped.

The Onseck moved the minutes across the table. Janice said that a motion involving the minutes has been made. Passes arms/leg/snake-fewer...-0 +Spehn. Motion passes (snakes).

\goto{Committee Reports}

(SLP) Moocomm: Repo Man tonight. Strek II tomorrow night.

(BPS) Jourcomm: TZ needs stuff; book reviews! of books on the list! Fliers concerning this are flying out with the picnic notices RSN! A feature of the new TZ will be a "state of the MITSFS" report, if JME writes it; it'll deal with the scavenger hunt, the invasion of the snake people, etc.

(KM) Sitcomm: Here's a copy of a pseudo-Hill Street Blues episode that seems to kill people off to cut costs. (Reads it.)

(BPS) Sitcomm sub 2: USA Today did a readers' survey of which characters should be bumped off of Hill Street; the top 3 candidates were Stan Jablonsky, Fay Farillo, and J.D. LaRue.

(HAM) Picniccomm: Newsletters are going out RSN as soon as I kill Dan Bond. (Janice made comments here about Tarl's diode.)

(JME) Skinner Report: I got a nasty threatening letter from the institute saying that I owed them money and how I wasn't going to graduate unless I paid them, so I called them and I owe them a grand total of 14.85... which my energy rebate will probably cover.

(BPS) Sitcomm: Street Hawk (the motorcycle show)- remember when it was canceled and a newspaper article said that ABC was threatening to bring it back? Well, they brought it back; it's on Thursday against Cosby and Magnum.

(JME) Bananacomm: We should all mourn Banana Computer Co.; this is not a motion. (A very short moment of silence.)

(RvdH) Theftcomm: They haven't touched my car! (Applause.)

(KM) Telzey Amberdon Report: Looked at an apartment in Malden today; it wasn't quite right, so we're still looking.

Janice says "So we aren't recommending this apartment to anybody, Ken?" and Ken replies "What the hell, I don't like these people anyway."

(JME) Skinner Report sub 2: reminder- election meeting in Spofford on May 10. Vote for OUR favorite candidates.

(BPS) Pianocomm: There's a new joint keyholder picture featuring Bill Starr and Susan Tucker in a domestic scene.

(JME) Pseudo-Libcomm: Ken Johnson's picture has been removed again. Fortunately, Adam has 5 other copies. Ken suggested auctioning some off first.

(JME) Pianocomm sub 2: Greg Greely has said that he will be turning in his key, though he hasn't done it yet.

(JME) Pianocomm sub 3: We have two more proto-keyholders- Farsad Azsani and Scott Kitchen.

\goto{Old Business}

Lisa Kroh will not be shelving duplicate fanzines; Lisa, Scott, and Farzad are going to be inventorying the circulating paperbacks. Said Ken J., "You're a mean and evil skinner." The decision at the Pinkdex meeting last night was taken to add new shelf codes for circulating paperbacks, circulating anthologies, etc. with numbers after them to indicate the number.

OBA, usual garbage, sold.

\goto{New Business}

(JME) Minicult: from the Phoenix- first the British rockers got together to form Bandaid, then the American rockers got together to form USA for Africa, then a group of Canadian musicians formed Northern Lights; these recordings have already raised millions of dollars for African famine relief, and now other musicians have jumped on the bandwagon to collaborate on fundraisers of their own. Who will be next: the mutants, according to the Marvel Comics group; some sixty writers and coming strip artists including Harlan Ellison and Steven King have joined forces to put out a famine relief comic book. ("You eat it," said Ken M. Ken J said "Good, I thought that they were going to sing.") Article attached. The idea is that the mutants can save the universe but not those who are hungry, but we can. Sigh. Many critical comments.

(BPS) Minicult: from last Friday's Glob- an 87-year-old driver mistook an airport runway for an interstate highway and drove off the end, flying off a seawall and splashing into Tampa Bay.

(JME) Minicult: Racial intolerance rears its ugly head in Milton- a black man just won a suit and 420,000 against Milton for when he was arrested and beaten because he was waiting for his daughter to leave a friend's house. He is a Polaroid executive and his daughter is a Harvard student. Various people interviewed by the Glob insisted that it was not a racial incident, and one person said that he should have just cooperated; when told that he told the police that he was just waiting for his daughter, the person replied, "Well, yes, but those people don't have a reputation for telling the truth."

(JME) Minicult: The international association of left-handers gave its left-hander of the year award to James Michner, but he's right-handed. Apparently somebody made a mistake on one of those lists of famous left-handers by listing him.

(BPS) Minicult: Regarding the Madonna query on the bulletin board... (Tarl trashed it- tape ended.)

(KRJ) In "The Making of Star Trek," the bio of Captain Kirk was that he was born in a small town in Ohio. Apparently some small town in Ohio has decided that it's going to be them; they want to turn themselves into a tourist trap. It should have been Iowa- all the same.

(JME) Minicult: A Department of Education official resigned after saying that handicapped people should stop demanding things from society because the universe is inherently unjust. Said Robert, "It was bad karma they picked up in a previous life."

(BPS) Move to commend Adina for having the least banana-colored shirt that I've ever seen in my life. (Tarl was told that the shirt is a shocking shade of fluorescent pink.)

Passes many many many +snake-fewer but two snake-slightly more +no snakes +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}