\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 15, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (11/8/85) read and corrected by JAH in the absence of the Onseck.

JME: Move to approve the minutes as the same shade of grayish-pink Jenny's sneakers are now. Passes lots-a couple-3 +Spehn.

\goto{Committee Reports}

JME: Concomm: Ken and I went to Psicon 7 in the resort town of Virginia Beach, Virginia, which is a depressing place in the offseason. We had a great time and heard Ellison do a postmortem on his Twilight Zone episode.

JME: Strekcomm: Ken said he's going to be late, because the Excelsior lived up to its name.

JME: Mythcomm: The MythAdventures comic book is likely to die after issue 8, due to internal conflicts.

BPS: Freedomcomm: The good news is the Cambridge anti-porn amendment was defeated. The bad news is there are 9400 people in town who thought it was a good idea. (13,000 voted against.)

People flamed for a while, then concluded that Andrea Dworkin is part of a plot by the Illuminati.

\goto{Old Business}

JME: If people don't write something for TZ, I'm going to resign.

BPS: TZ 36 mailing RSN. Does anyone know how to mail stuff off cheaply?

Discussion of which is cheaper, Shawn Gramates or RKW.

OBA: um, us, uv, ur.

\goto{New Business}

JME: Minicult: George Lucas is suing to stop a pro-SDI group from using the term "star wars" in their TV commercial. Lawyers predict he'll lose because he didn't protest the usage earlier and it has become commonplace. Articles attached, courtesy of GF.

Connie/BPS: Minicult: Two people hanging around a bank with what looked like machine guns got arrested when the bank forgot to notify police that the United Way was filming a commercial with Bonnie and Clyde characters there.

BPS: Minicult: On Nightline, Z. Brezhinski described a test of the plan to evacuate the president from Washington if the country is under attack. Not only did it fail to make the time limit, but the people running it forgot to notify the Secret Service. When the emergency helicopter landed at the White House, it nearly got blasted.

KM: Minicult question of the week: What is this a key to? (Finger motion!) Answer: It's the key to the documentation racks. Oh well, I thought people might be interested.

BPS: Personal Minicult: After working 3 weeks of extra hours on a product scheduled for release next Monday, this Monday I was told the project was being dropped.

A Miller motion from RvdH fails.

JME: Spielberg is directing a grownup movie that's not even science fiction- The Color Purple, from Alice Walker's novel. He offered Tina Turner a part in it 3 times, but she turned it down. Spielberg also has something to do with The Young Sherlock Holmes, which is about exactly what its title says.

BPS: Orbit is still dreadful. It's amazing that the same man who does Duffy can do anything that ghastly.

ATS: That was a committee report. Any more New Busi-

Andy gets drowned out by lots of sounds, many of which are Miller motions. One of them passes more than enough-everyone singing Rabbits-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}