\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 21, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (6/14/85) read and corrected.

There was a very long silence and finally somebody moved to approve the minutes as boring. Passes everybody who's anybody-nobody-even fewer than nobody +Spehn.

\goto{Committee Reports}

SLP: LHE Report: Last month's income was 167.18, expenditures 688.80, for a loss of 521.62, making the equity level 4736.65.

ATS for AbM: Infocomm: The new titles for the keyholder chart will be up real soon now.

BPS: Moocomm: Openings tonight- Cocoon, from Ron Howard, and Lifeforce, based on Colin Wilson's The Space Vampires.

ATS: Nuptialscomm: The ex-Skinner and the ex-Telsey are getting married this weekend.

\goto{Old Business}

ATS: Legendary former keyholder Paula Lieberman stopped by this week, and she said I was the cutest Skinner she'd ever seen.

OBA: everyone mumbles yeah.

\goto{New Business}

SSDT: Minicult: In Osaka, Japan, reporters and TV crews took pictures and interviews as two men broke into the apartment of an accused criminal and killed him. Article attached.

ATS: UPS sucks even more! They sent back our banana-colored kicksteps!!! To Wisconsin! So yesterday I raised some serious hell with them.

SSDT: If they return a Witter shipment to Wisconsin, it'll be gone forever.

BPS: Minicult: Mail delivery on a residential block in Houston has been suspended until a mockingbird there is done raising its family, at which point it will presumably stop attacking the postmen who walk past its nest. Article attached. The bird doesn't attack the residents, only postmen. And another Minicult: The Cubans are pointing to the change in the taste of Coke and the associated uproar as a sign of America's ongoing moral collapse. Attached.

ATS: Ken Johnson and I are going to the New England Mobile Book Fair tomorrow. If anyone wants to join us, we're leaving from here at 10 AM.

AA: Merryl will probably be in town next weekend.

ATS: Move to condemn UPS for sending our pretty banana-colored kicksteps back to Wisconsin. Seconded. Passes just about everyone-nobody, thank goodness-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}