\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 10, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order in the Spofford Room, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (5/3/85) read and corrected.

AbM: Motion to approve the minutes as not brown and scaly. Passes 23-17-6 +Spehn.

\goto{Committee Reports}

JME: Skinner Report: Thesis!!!

HAM: Picniccomm: Picnic tomorrow morning; how about some help carrying food?

JME: Whooshcomm: 1) Ray Bradbury rejected a suggestion that he take a ride on the space shuttle, saying "What are you trying to do, scare me to death?" Article attached. 2) Coca-Cola has developed a can for dispensing carbonated beverages in space. Article attached.

KM: Move to have Coca-Cola design new toilets for the space shuttle. Passes many-nobody who counts-7 +Spehn.

AbM: Whooshcomm 3: The Garn may have been defined as a new unit. When asked how the monkeys were, an astronaut replied, "Two Garns."

ATS: LHE Report: The reign of Eisen was incredibly profitable. Also, I have two weeks off at the end of the summer for Brazil.

KM: Telzey Report: This is my final Telzey report. (No, it's not because I'm leaving Janice.) My oral presentation is scheduled for the 22nd, and if you read the proposal, you'll agree that my science fiction writing talents have definitely evolved, especially the parts about what has been done to date.

ATS: Pseudo-ROSFAP: I brought in all of SF Lovers volume 10, about 1000 pages so far, and am taking suggestions what to do with it. Suggestions included burn it, bind it, and bind it and gag it.

BPS: Skinnercomm: I can't believe that's the same "The Bride" shirt you showed us last week. I didn't think it would fit around you, much less cover you.

Janice assures him that it was the same one.

SSDT: Chronocomm: There's going to be a leap second on June 30th. Don't forget to adjust your atomic clocks.

JME: Jourcomm: A really geeky looking person submitted a really geeky looking story called "The Three Gods and Their Blonde Anomaly" or something similar.

ATS: Squeakcomm: Hold on to your snakes! (As he brings out a toy mouse given to him by Shawn Gramates.)

BPS: Sitcomm: God help us. NBC is showing V reruns... (Agonized howls.)

AA: Sitcomm 2: Another NEW Hill Street Blues episode next week. (Happier sounds.)

SLP: Moocomm: See "Creator;" it's very good.

JME: Moocomm 2: On Her Majesty's Secret Service tonight, Return of the Tall Blonde Man tomorrow.

JME: Pianocomm: We have a new keyholder (Farzad Ehsani) and two new phantoms (Scott Kitchen, Lisa Kroh).

AbM: DoubleVisioncomm: MITSFS has a stereo picture in this year's Technique.

\goto{Old Business}

Two special guests present at the meeting were introduced: the Permanent Deceased Librarian and President, and Grand Ol' Wedge of the S.G.S., George Phillies, and his Vice, Mark Swanson. Janice noted that last year we had a picture of George Phillies at the election meeting, and maybe this year we should have brought a picture of Paul Newman. George said he is moving to eastern Massachusetts and will be around often. He also identified Robert Wiener, whose beard has suddenly vanished, as his "Treasurer."

OBA: um, ugarbage, what-about-us?, uv, ur.

\goto{New Business}

JME: Minicult: from the Glob- Moslem fundamentalists raided an X-rated movie and forced the men in the audience to help fill sandbags on the Green Line in Beirut, rather than "wasting time watching depraved movies." Attached.

RvdH: Move to put sandbags on Boston's Green Line! (No vote.)

KM: Actually, it's the Red Line that's getting sandbagged.

AA: Theodore Sturgeon is dead. Obituary attached.

In an effort to cheer people up, Adam points out that Arthur C. Clarke is still alive.

JME: Minicult: A man who has been arrested over 40 times in 15 years for stomping on women's feet wants to stay in jail for fear he'll continue his habit. Article attached.

RvdH: Minicult: I wrote a prayer for agnostics based on Zelazny material and got it printed in the Tech, in case any agnostics want to bless their lab.

SSDT: Minicults: 1) According to an advice column, the most concise blooper in an errata column occurred when a small-town newspaper referred to the "defective branch of the police force" and the next day corrected it to the "detective branch of the police farce." 2) In Florida, a drunken man tried to punch out an alligator, and the alligator fought back and drowned him. Local police think he deserved it and will not press charges against the alligator. 3) From the Herald- a county coroner failed to notice that a sailor who died recently had a wife and two kids, and sent the body to the sailor's girlfriend instead. The wife is suing the coroner's office for 450,000 dollars.

GF: Minicult: I just proofread Atomic Tourism, a life-after-the-bomb science fiction story, for the Atlantic Monthly.

AbM: Minicult: A Florida man keeps getting arrested for being topless in violation of a local ordinance. He is suing on Constitutional grounds.

George Phillies: Minicult: In Texas, a man who found his wife in bed with another man could legally shoot and kill both. Texan wives have now been given the same right. (Applause.)

MTG: It applies only if their husband is in bed with another man?

Mark Swanson: Minicult: Also in Texas, you can't take a bankrupt man's gun, horse, or car. This has been extended to include a man's last plane.

During elections:

George Phillies: There was a Massachusetts law whereby Massachusetts residents were legally required to shoot Connecticut residents on sight. It was repealed in 1975 or so.

RvdH: I heard that story concerning Rhode Islanders, and a man tried to use it as a defense in court recently.

BPS: A few months ago the mayors of Rome and Carthage finally signed a peace treaty.

Election results, final ballots:

Onseck:

Noah's Ark- 0.01

Noah Ward- 0.84

Montgomery Ward- 0.04

Robert Wiener's beard- 0.91

The Lesser Plant- 0.54

The Greater Plant- 0.72

Zeus- 0.70

Susan S.D. Tucker- 12.86

Randoms- 5.58

LHE:

Bank of Boston- 0.07

Shawmut Bank- 0.15

Susan L. Pitts- 13.82

Robert Wiener's beard- 0.16

Robert Wiener's reptile- 0.35

Ken Dumas- 0.00

Alexandre Dumas- 0.60

E.F. Hutton- 0.01

Randoms- 6.21

(Note: the results of a preliminary LHE ballot are attached as an example of how random the random candidates can get.)

Vice:

Sloth- 0.11

Susan's leather accouterments- 0.10

Steven Spielberg spelled K-i-n-g- 0.05

Shirley McBay and her 3-foot screw- 0.50

Adam G. (or b.) Mellis- 12.89

Yalda the Crimsom Drag Queen- 1.00

Various snakes- 0.80

Randoms- 3.83

President:

Yalda the Crimsom Queen- 0.53

Prince the Purple Spaghetti- 0.05

Opus- 1.22

Andy Who- 12.54

Dr. Su- 1.05

Janice Eisen- 0.10

Adam Mellis- 0.79

George Phillies- 0.40

Randoms- 4.83

Yalda the Crimsom Queen in several incarnations, including Yalta the Crimsom Conference, was declared the Official Second. The meeting's conclusion was dominated by an unusually loud and off-key version of Rabbits. BPS moved to adjourn, and Janice explained that such a motion was not allowed. Under cover of the noise, Andy Su, who eventually declared himself Skinner, took the gavel. A Miller motion failed, and a second one passed about 3,000,000-0.7-a couple squawks and a wave +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1930 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\vspace{18pt}

Attachment: LHE first ballot, compiled by Adam Mellis while temporarily unemployed.

(1st) SLP- 8.06

SLP's smoke- 0.2

All three smokes- 0.2

(6th) Plants- 0.73

(2nd) RKW's beard- 1.88

RKW's chin- 0.5

James Beard- 0.07

Grandma Chicken- 0.2

SCC- 0.2

Ester Lester- 0.64

LHI- 0.24

(5th) EF Hutton- 0.87

Those who still listen to EF Hutton- 0.3

Ronald Reagan- 0.5

The Alpert- 0.3

Warren G. Harding- 0.09

Fred- 0.1

JME's pink Harley-Davidson t-shirt- 0.1

SSDT's leather accouterments- 0.1

(3rd) Ken Dumas- 1.6

John Dumas- 0.5

Yaldeh- 0.3

Alexander the Great- 0.3

Caesar's ghost- 0.1

Alexandre Dumas- 0.6

Alexandre Dumas in Albanian- 0.2

RvdH's beard- 0.2

Herb's beard- 0.42

Ken's beard- 0.1

Mars- 0.01

Jupiter- 0.01

Saturn- 0.01

Zeus- 0.72

Drib Phos- 0.01

Apollo- 0.01

Kill- 0.01

Other Magnum PI references- 0.01

Transition- 0.1

Fred- 0.1

Keyholder Notes- 0.2

Purple chairs- 0.2

(4th) Bank of Boston- 1.56

\end{document}