\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 4, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (9/20/85, Gloria was last week) read and corrected by Scott Kitchen, due to the slight lateness of the Onseck.

JME: Motion to approve the minutes as not nearly as much fun as the party Ken and I are having tomorrow night. Passes everyone-3-a few +Spehn.

\goto{Committee Reports}

ATS: Plugcomm: SFC had an item telling how to make contributions to MITSFS, but nobody knows how it got in there. Maybe somebody read Twilight Zine. Item attached.

JME: Inmemoriamcomm: We've lost E.B. White. (A genuine moment of silence follows.)

BPS: Jourcomm: Punt! JME: Jourcomm: Catch! I'd like to get TZ out 2 or 3 times a year, so start writing things. (Andy suggests that the gavel block is not a good place for Janice to keep her hand.)

SSDT: Compcomm: MITSFS has an account on prill. It's 250K for the moment. You're welcome to use it if you can guess the password.

BPS: Jourcomm: The author of the TV child story in TZ bought ten copies, thereby doubling our sales. Maybe accepting her story wasn't such a bad idea after all. Whooshcomm: The Atlantis was launched Thursday amid large clouds of exhaust and secrecy.

RKW: Snakecomm: Klyd is a girl.

ATS: Strekcomm: Gene Roddenberry was here on the 23rd, complete with the blooper reels and the black and white print of The Cage. He overflowed Kresge.

BPS: Sitcomm: The premieres of Twilight Zone and Amazing Stories were on. The first half hour of Twilight Zone was based very faithfully on Ellison's Shatterday. The second story was just piffle that resembled The Girl, the Gold Watch, and Everything, with a weird ending and an empty headed main character. Amazing Stories was so Spielberg you could barf. Unfortunately he's writing all the stories for this season.

JME: Concomm: Spike McPhee is part of a committee which is planning Readercon, a convention with the emphasis on books, for summer of '87 in Boston.

GF: Strekcomm: Pocket Books recalled and destroyed all they could of the first edition of Killing Time, a Trek fan novel that somehow never got proofread. It's gone back to press with all references to a Kirk-Spock relationship deleted.

\goto{Old Business}

SSDT: Three items. 1)The Solwind satellite that was used as a target in the ASAT test was providing useful data up to the moment it was hit, and its destruction came as a complete surprise to the scientists using it. The DOD claims it was about to fail anyway. Article attached. 2) A talk show host discussed the mailing of rocks as a way to get yourself off of mailing lists. You attach the business reply card to a box of rocks that will cost the bothersome sender a fortune in postage and mail it. However, it only worked back in the good old days, not anymore. 3) In the early seventies, our money ledger was kept even more detailed than the money book is now. I found an entry that said "5 cents found under a lot of junk."

OBA: usual stuff, sold. (Janice's luggage gets removed from the gavel block so we can proceed to...)

\goto{New Business}

DSK: Minicult: British Airways decided that a pole vaulter's pole is no longer acceptable as carry-on luggage.

JME: Minicult: A study of 6 and 7 year olds playing with a computer drawing program found that they weren't actually drawing at all, but using the computer on the starship Enterprise and flying.

BPS: Minicult: There is a fan campaign to get the Post Office to issue a stamp commemorating the twentieth anniversary of Star Trek. Article attached.

GF: Among the crossword clues I proofread for the Atlantic this week were "Planet created by Frank Herbert (7 letters)" and "Shirefolk of Middle Earth (7 letters)."

DSK: The Infocom escapade got written up in the Tech; article attached.

Connie: Misfits of Science has a two hour premiere tonight.

JME: Come to our housewarming tomorrow night. We bought lots of junk food.

A motion to censure Ken and Janice for not buying bananas for the party is passed enough to do the job-"go home, people"-some really weird squawks +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}