\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 13, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (9/6/85) read and corrected.

ATS: Move to approve the minutes as amazingly abbreviated. Passes 18-less +a pink velcro tennis shoe-4 +the other pink velcro tennis shoe +Spehn.

Andy announces that Adam has resigned as Vice, and that he has selected Susan Pitts as the new Vice in addition to LHE. Letter attached.

\goto{Committee Reports}

SSDT: Onseck Report: Ella died again, which is why the minutes were so brief.

HAM: Catacomm: Micro Information Concepts in Dallas wants to microfiche our Weird Tales and is sending a proposal.

BPS: We're going to need about ten pounds of tranquilizer for Ken Johnson when he hears about this.

SLP: Fweekcomm: 112 new members, 21 renewals so far.

BPS: Ex- and possibly future Jourcomm: Shawn Gramates has returned.

\goto{Old Business}

ATS: KRJ clipped the obituary of Philip Morse, who made a large donation about a year ago. Attached.

OBA: um, us, ud, uv, ur.

\goto{New Business}

TMc: New Business Algol!

This idea is met with much puzzlement.

ATS: There are new fine rules and keyholder fine rules for you to read and sign.

BPS: Minicult: ASAT test any moment now.

Shawn: Minicult: In San Francisco, two robbers discovered that their victim had no money, so they took the clothes he was wearing instead. Attached. Also, in LA, a man was arrested on suspicion of indecent exposure for wearing a chain, chaps, shirt, shoes, and a g-string, but no pants. A second man, who was using the chain to lead the first, was not arrested since the police couldn't think of a charge. Attached.

Connie: Minicult: A Miami housewife was terrorized by a six-foot long boa she found curled up on her toilet. Attached. Also, two fishermen set a Georgia record for the tarpon when one that was six feet long and weighed 142 pounds decided to follow a trout the men were reeling in and jumped into their eighteen-foot boat. Attached. (The article, not the fish or the boat.)

BPS: Minicult: A New Zealand park has decided to quit using Siberian tigers as guards for the daily receipts. The local bank is happy that it will no longer have to deodorize the deposits. Attached. Also, Edward Teller said he doesn't like being called Father of the H-Bomb, seeing as he never got a Father's Day card from one. Attached.

HAM: Minicult: The BBC refuses to comment on a rumor that after an 18-month hiatus, it will bring Dr. Who back as promised, but then kill all the characters after only one season.

ATS: David Brin will be in 9-150 at 8 PM Monday October 14 for a lecture NESFA is sponsoring with us. He'll be doing signings at Spike's and anyplace else he can find.

BPS: Spike has decided to give MITSFS people the 15 percent discount on used books also. The policy is subject to change whenever he thinks about it next.

A Miller motion fails without vote, and the second one passes billions and billions-4 1/2-2 +Spehn just in time to cut Rabbits off after one verse.

\vspace{12pt}

\noindent
Meeting adjourned, 1726 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}