\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 8, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (11/1/85) read and corrected by JAH, as the Onseck was having a miserable time at a model UN in Philadelphia.

ATS: Move to approve the minutes as more fun than a poke in the eye. Dies for lack of a second.

JAH: Move to approve the minutes as something else. Passes everybody-a few-those damn pink velcro tennis shoes again +Spehn.

\goto{Committee Reports}

SLP: LHE Report: Income- 869.91, Expenses- 782.81, Equity- 5194.75.

ATS: Moocomm: Ghostbusters tonight. TMc is projecting the first show.

BPS: Whooshcomm: Nobody noticed, but the Challenger came down with as many people as it went up with. Also, they installed some kind of power steering on the nose wheel.

SLP: Concomm: Went to the World Fantasy Convention. It's in Providence next year, and membership will be limited to 750.

BPS: Concomm: Visited the Boston Trekkiecon. I saw Adina, Connie, and a few others there, and I think they got eaten by it, seeing as they haven't been heard from since. (Note: Connie brought an Esotericon flyer.)

\goto{Old Business}

TMc: I mentioned to my roommate that somebody had actually made it to the end of Dahlgren, and he said, "Oh, yeah. I read it again last month; it's better the second time."

ATS: Whittlecomm followup: I spoke to Jeffrey Carver at Spike's, and he said he'd drop by if he's ever in Boston again.

OBA: the usual, sold.

\goto{New Business}

BPS: Minicult: It has been scientifically proven that the giant panda really is a bear, not a raccoon.

KRJ: Minicult: Monday's Wall Street Journal had an article about the controversy over the British sport of dwarf-tossing; attached.

Connie: Time for "Best of the Weekly World News," with your hostess, CH. 1) In California, a 73 year old woman took her driving test, passed it, and proceeded to drive right through the wall of the licensing office. 2) Under the dramatic headline "Cough syrup can make you pregnant!" is the information that Robitussin really does contain an ingredient that increases the chances of pregnancy. 3) A church group in Florida borrowed an old coffin from a funeral home to use in a  Halloween party and were really surprised to find that it came complete with an old skeleton. It was a surprise to the funeral home, too. All articles attached.

SLP: Little Myth Marker is out.

Andy mentions that Merryl phoned in a Miller motion just before the meeting started. It is seconded at this time and Andy fails it. Another Miller motion is passed 320 plus or minus 2-3-a few +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1728 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}