\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 1, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (10/25/85) read and corrected.

GF: Move to approve the minutes as having a timeless quality. Passes everybody-Connie-4 +Spehn.

\goto{Committee Reports}

ATS: Moocomm: Starman tonight. (This gets lots of hisses but for some reason Andy's "LSC..." is answered with total silence.)

BPS: Mobcomm: Saturday's excursion cost us 620 dollars, AFTER counting 20 percent off paperbacks, 30 percent off hardcovers, and no tax.

SSDT: Onseck Report: After seven weeks of trying, I finished Dhalgren.

ATS: Whittlecomm: Jeffrey Carver will be autographing at Spike's tomorrow.

BPS: Move to retroactively renew the Society's faith in the Great Pumpkin. Passes unanimously with 2 +Spehn abstaining.

SSDT: Porncomm: There is a prize available for anyone who fixes our copier- a "Mr. Fusion Home Service Representative" button I picked up at the SEDS hucksters' booth in Lobby 10.

Connie: Sitcomm: Channel 11 is showing the first Dr. Who episode tomorrow at 5 or 3.

SSDT: Pseudo-Panthercomm: Every single circulating book has been inventoried for a copy count, which is kept in Shelfdex. Please maintain it.

BPS: Sitcomm: I watched a "deal with the Devil" episode of Highway to Heaven. God, it was abysmal.

SSDT: Lecturecomm: Radu Florescu gave a really good presentation on his "Search for Dracula" on Wednesday. He autographed the two books of his that we have.

BPS: Concomm: A Trekkie-con this weekend from Boston ST Association, in the East Boston Ramada Inn.

Someone: Lecturecomm: LeGuin spoke at Harvard on Wednesday. She said that there's a screenplay for Left Hand of Darkness, and she's looking for 8 million dollars and some androgynous actors.

Someone else: Whooshcomm: The Challenger went up with a record 8 people, a roller coaster, and some mission control done from Germany.

As over half of the committee reports were done via short range time warp, Andy closes it, saying he won't reopen it for anything, and declares that we are now in...

\goto{Old Business}

JAH: So Long and Thanks For All the Fish is out in paperback.

SSDT: We got a letter addressed to the Back Issues Department of Twilight Zone, International Science Fiction Society.

OBA: um, us, good enough.

\goto{New Business}

BPS: Minicult: Jesse Helms put an amendment outlawing tax exemptions to groups promoting Satanism and witchcraft on the 1986 government appropriations bill. He was forced to withdraw it under heavy pressure from witches. Article attached.

Connie: Minicult: The Dictionary of American English (A-C) is out. An article listing some of the quainter entries is attached. Also, scientists are going to try to capture an alleged dinosaur in the Congo. Article attached. And yet a third Minicult from the Weekly World News: the London Zoo's latest attraction is Urban Man, as portrayed by Spanish impressionist Alberto Vidal.

JME: Minicult: Frank Zappa took some recordings of several senators speaking during the Commerce Committee hearings on album warning labels and included them on his upcoming record "Porn Wars." Attached.

Connie: Minicult: When a reel got dropped during the British TV miniseries Hollywood Lives, only two dozen of the 9 million viewers called to ask what was going on. Article attached.

At this point Janice asks for a time warp. Sure enough, Andy defines her as an exception to the anything that he said he wouldn't reopen the time warp for, at least long enough for her to tell people to please write something for TZ.

A Miller motion from SSDT fails, and a second one from DSK passes 17 1/2-17-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}