\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 13, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (12/6/85) read and corrected.

AA: Move to approve the minutes as banana colored.

ATS: Cut that out! Do I have to do this every time? (All this gets Andy is a finger motion.)

There follows more arguments and finger motions until someone moves to approve the minutes as having motion sickness. Passes lots-a few-the pink velcro tennis shoes +Spehn.

\goto{Committee Reports}

SLP: LHE Report, November: Income- 250.80, Expenses- 266.46, Loss- 15.66, Equity- 5179.09. The endowment fund is over 5000.

SSDT: Smootcomm: Another truck got in an argument with the Storrow Drive bridge, only this time instead of an outright loss it got a draw. The bridge was closed while experts checked how badly broken it was.

SLP: Moocomm: Clue is out, with 3 different endings (pick which one you see by which theater you go to), all reputed to be equally bad.

CH: Moocomm: Jewel of the Nile is pretty decent. The Flying Karamazovs are in it juggling a lot.

KM: Sitcomm: Joe Haldeman's short episode is on Twilight Zone tonight.

SSDT: Moocomm: Rambo at LSC tonight, complete with protesters, if they aren't still lost. The poster, signed "Somewhere over the Rambo Coalition," calls for a protest outside 26-100 prior to the screenings. Unfortunately for them, the film is being shown in Kresge. Poster attached.

BPS: Moocomm: Something is seriously wrong with the universe. At the Orson Wells, half a dozen people are still protesting Hail Mary, and NOBODY is protesting PeeWee's Big Adventure.

JME: Jourcomm: So far I have the Glen Cook piece, a bunch of cartoons from a non-member, and several promises.

BPS: Mortcomm: Judy-Lynn Del Rey died after a massive stroke at age 41.

\goto{Old Business}

JME: The episode Ellison tried to do for Twilight Zone was to have been an anti-bigotry Christmas story about a racist welfare worker. The CBS executive who blocked it, thereby causing Ellison's resignation, felt it had "no value for the Christmas season," but would have approved a similar story with no Christmas connection. Article attached.

AA: Former keyholder Steve Swernofsky is marrying Elise Weinstein, alias Elise Levenson.

ATS: Merryl's back!

OBA: um, us, uv, ur.

\goto{New Business}

JME: The New York Times reports that in South Dennis, a mother is trying to have choose-your-own-adventure Zork books banned from school on the grounds that they promote demonic worship and glorify violence. The woman, who swears to fight Zork: The Malifestro Quest with her dying breath, calls herself a "kamikaze for Jesus." Article attached.

JME: Our picnic grounds have been desecrated. Nine freshmen from Theta Chi were caught dressed in camouflage fatigues cutting down pine trees at the Blue Hills Reservation.

It is unanimously agreed to destroy Theta Chi and salt their ground with pepper.

CH: WWN Report: list of top TV shows in foreign countries- Dynasty and Dallas were the big winners.

BPS: Minicult: At the Trekkiecon a while ago I got us a Battlestar 1 (Galactica fans) pen that doesn't write well. (Lose it!) Also, MCA Home Video is including a useless 1-page glossary with Dune. Adina says they were handed out in theaters too. Attached.

JME: Motion to, after we salt the ground of Theta Chi with pepper, plant banana trees there. Passes everybody-1-pink +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}