\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 5, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (3/29/85) read and corrected.

(BPS) Move to approve the minutes as more fun than the meeting was. Seconded.

Said Janice, "That's been done so many times, but all in favor?" Failed some fairly unenthusiastic arms and legs-some slightly more unenthusiastic arms and legs-a few dully waving arms and legs +Spehn.

(JAH) Move to approve the minutes as the man from C.A.R.L. Passes more enthusiastic limbs-a Herald-0 +Spehn.

\goto{Committee Reports}

(RvdH) Theftcomm: Sometime between 11:00 Tuesday and 8:00 Wednesday somebody else took my car.

Jenny suggested that Robert's Rabbit was the Easter Bunny. Some random made a comment that got him immediately Albanianed. Then Jenny said something about basket cases, and she too was Albanianed. Adam remarked that the meeting was really hopping along, but the Albanian motion didn't seem to affect him. Finally, Ken Johnson said "you shouldn't egg them on like that," and was, of course, Albanianed.

(JME) A-Little-Bit-Too-Latecomm: We received a letter from Connor Moran (Student Center manager) asking us not to tape things to the newly painted doors because there will soon be bulletin boards for the 4th floor.

(RKW) Snakecomm: Abel was lost and reappeared two weeks later.

Commented Janice, "See, Robert, there's hope for your car."

(JME) Picniccomm: We have the other half of Picniccomm now; it's aspiring keyholder Dan Bond.

(JME) Pseudo-LHE Report: Equity level 5189.86. Ken Johnson wanted to buy more Weird Tales, but Janice said that we'd be buying bookshelves and perhaps de-acidifying our Amazings. Profit- 71.87, due entirely to the LHE discretionary fund, which means that keyholders are screwing up in money book entries.

(JME) Postawfulcomm: How come something addressed to M. Timmreck, 84 Mac, Cambridge, MA 02139 got to the right place?

(JME) Moocomm: Dune tonight, 7 and 10 in Kresge.

Adam said that we should yell "LSC sucks!" as we decided on that two weeks ago. After this reverberated down the hall, we heard a "Thank you" and so Adina replied "You're welcome."

(SSDT) Pseudo-Panthercomm: There's a new Pinkdex, but no one can find it. Spencer said he would bring it by Sunday and it can't be found.

Corrected Janice: "That's not a question of not being able to find it, that's a question of Spencer not having brought it."

(BPS) Theftcomm: Bill's roommate, who works at Lauriets, has acquired a poster for Footfall, by Niven and Pournelle, in which the earth is apparently invaded by baby elephants.

(JME) Pseudo-Pianocomm: Our particle physicist is now ROSFAP.

Adam said that it should be noted that she prefers the title "particle physicist" to that of "ROSFAP." Janice said that it should also be noted that she's also constantly being Albanian motioned, so we know what that says about her.

After calling for more new business, Janice observed that Jenny hit her head with a large chemistry textbook. Despite the fact that Ken Johnson was speaking Albanian, when he said "That's something that Albanians do," everyone laughed. Ken then took the book (the 5.12 text) and hit himself on the head with it; it was then passed to Adam.

\goto{Old Business}

(JME) We've received a letter from George Phillies, an ancient Skinner, and (added Bill) Grand ol' Wedge of the SGS. The letter is fairly brief and concerns Old Business; specifically, it documents the contents of Old Business Algol. Phillies sent this in after a story by Janice in TZ 35, in which one of the pseudo-pivotal plot points was a Skinner not knowing the contents of Old Business Algol, and hence proving that she was not a robotic surrogate. (Letter attached.)

OBA, and Robert said "the usual schmeal." Ken added, "All the good things that you just read off."

\goto{New Business}

(JME) Minicult: Channel 4 wimps out. They were going to have on their show "People Are Talking" the editors of a book about lesbian nuns (the editors were also lesbian nuns). The Catholic Church complained and the station dropped the story.

Ken suggested that maybe they could find some Teenage Mutant Ninja Turtles. Commented Kathy (Godfrey), "Believe me, when you see a cover, you'll know this is it."

After a little flaming about whether what Jenny was about to say was a Minicult, Microcult, Nanocult, or religious cult, she finally said: The newest Bloom County collection is out; it's called Penguin Dreams and Other Strange Things. Bill claimed that the cover was an Opus fantasy that you wouldn't believe; "even if you see it, you won't believe it."

(BPS) Minicult: Tech SciFi may be doing all right, but today Tech HiFi, completely and without warning, went out of business, much to the surprise of all the employees who came in to work and found security guards there with letters signed by the president of the company telling them to give their keys to the guards and go home. The president is in hiding.

A few minutes of flaming about the new Zelazny manuscript "Trumps of Doom."

(Kathy Godfrey) Minicult: The Sack 57 is having a sneak preview of Ladyhawk tomorrow night at 8.

There was lots of flaming about sneak previews, a recap of the story about the Dune sneak previews, and Heaven's Gate.

(AA) Move to censure the Easter Bunny for not delivering bananas. This eventually got changed to "for being banana-colored" after a lot of arguing and shouting and yelling, and then somebody yelled "Seconded."

Passed just about everybody-slightly fewer-even fewer +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}