\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 9, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (8/2/85) read and corrected.

RvdH makes a spastic motion which fails 2 and a squiggle-way too many-2 +Spehn.

Andy declares the minutes approved because he says they are.

\goto{Committee Reports}

ATS: Shelfcomm: They're here, and will be installed as soon as the air conditioner condensate pan is blown out with air. Physical Plant will probably do that right after they finish impressing the freshmen by destroying the front of the Student Center.

BPS: Jourcomm: The deadline is essentially here. I got 1000 heavy sheets of cover paper for 25 dollars.

ATS: Moocomm: Timerider tonight.

KM: Moocomm: Let's go see Real Genius, a Cal Tech type hacker film. There are two other hacking films playing, namely Weird Science and My Science Project.

BPS: Very Pseudo-Moocomm: The full length video of The Power of Love by Huey Lewis and the News features a bunch of kids joyriding back to the fifties in Emmett Brown's DeLorean.

Connie Hirsch: Fright Night is a good vampire movie directed by Tim Holland, who must have read Salem's Lot 8 or 9 times and then went to see Animal House.

ATS: Culturecomm: The China exhibit at the Museum of Science is very nice and covers a broad range of subjects without being very massive. You get your 5 dollars worth, including many live demos.

BPS: Whooshcomm: The Challenger came down a lot better than it went up. More importantly, we now have an agreement with Chile to have use of Easter Island for emergency landings. Article attached.

\goto{Old Business}

OBA: um, us, uetc.

\goto{New Business}

Connie: Minicult: A Wisconsin jury didn't buy a teenager's Dungeons and Dragons defense and found him guilty of murdering his foster father. He got life plus five years.

BPS: They should have made it life plus 1d6.

RvdH: Microcult: Ronald Reagan squeezes his pimples. See NY Times interview fragment attached.

BPS: Minicults: 1) Chinese health authorities are trying to convince children to stop trying to catch fish with their mouths. 2) Rambo prequel First Blood has been released in China, where reviewers have labeled it high culture. 3) A Connecticut couple has placed a toilet and a bathtub on their front lawn and painted their house assorted colors, as a "work of art" and a tribute to Walt Disney. 4) West Virginia named an airport after Chuck Yeager, who is very pleased because "normally you have to be dead to have something named for you." 5) The inventor of the pacemaker has had one implanted. 6) The Boy Scouts of America have expelled a scout for not believing in a supreme being. All articles attached.

A Miller motion fails and the second one passes by Skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}