\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 22, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (11/15/85) read and corrected.

RvdH: Move to approve the minutes as a shade of purple-gray. Seconded. Fails miserably, no one-everyone-anyone left over +Spehn.

ATS: Move to approve the minutes as the color of the sunset in Florida, which is where I'd rather be. This gets naahhed to death on the grounds that Andy can keep his sunset and hurricane Kate along with it.

SLP: Motion to not approve the minutes. Passes everyone but 4 or 5-4 or 5-gee, we seem to have more people here +Spehn.

\goto{Committee Reports}

BPS: Sitcomm: There's a bad Ghostbusters ripoff on ABC Thursdays at 8.

AA: Sitcomm: Tonight's Twilight Zone includes William F. Wu's Hugo nominee, "Wong's Lost and Found Emporium."

BPS: Sitcomm: On Sunday there's a new live action Ewok thing called "The Battle for Endor." (Many sounds of pain and nausea.)

ATS: Pseudo-Skinner Report: A pair of psych students at Spalding University trained two teams of rats to compete at pseudo-basketball. Attached.

Lots of people try to Albanian motion Andy for referring to this as pseudo-Skinner.

SSDT: Moocomm: Sack chickens. They canceled their booking of Hail Mary, Godard's film setting the birth of Jesus in modern times. It focuses on Mary's contemplation of the relationship between body and spirit and contains nude scenes of her. Catholic critics initially praised it, but the Church didn't like it, and the Pope broke with tradition by personally denouncing the film as blasphemous. Sack received numerous protests against the movie and even threats of violence, so it's going to the second bidder, the Orson Welles. Now there are a few protesters there, an even fewer number protesting censorship, and some very bored cops. Lack of parking space is helping minimize demonstrations.

ATS: Kangaroocomm: A female SF fan named Phil from Australia sent us a very strange letter and a copy of her club's newsletter, "Ethel the Aardvark Sings the Body Electric."

SSDT: Plugcomm: I can have fannish buttons custom made for people for 1.25 each. Say anything you want that's scene.

BPS: Platypuscomm: Scientists have finally found out how the platypus can swim underwater with its eyes and ears shut and still find food. It's one of the few animals that can sense electric fields. If you put it in a tank with a dead fish and a live battery, it'll go for the battery every time.

\goto{Old Business}

ATS: Tim sent us a letter and a bunch of Robotman strips. He (bewilderingly) expresses admiration for "Misfits of Science," and wants his TZ and a Boskone application. He also talks about twitching ganglia.

KM: The Tech got a new flatbed cart. Unfortunately, it's 4 inches longer than the elevator is wide. They'll be using the old one for a while.

OBA: um, good enough.

\goto{New Business}

ATS: Tomorrow is National Tribble Day. It's exactly 17.9 years from the first time Mr. Spock told Cyrano Jones that's how long it would take him to clean up K-7. Article attached, courtesy of Nathan Glasser.

Random: The Arts and Media Technology Building is getting about 5 seven-foot blimps, which will be computer controlled to float around the atrium like a school of fish. Suggestions on what else they could do?

Put them in the building 11 fishbowl. Is this our tuition or a federal grant? Have them go belly up and float near the ceiling. (No, there's an air vent up there and they'd get stuck.) Give me a gun and I'll take care of them! Have you read John Varley's Gaea series? Sometimes hacks approach art, but this is a case of art approaching a hack... Have them carry up water balloons. (No, there's only 5 ounces to spare.) Then have them carry paper airplanes. Make it propelled airplanes, and then you have ASAT weapons. Sponsor one- adopt a blimp!

ATS: The winter exhibit at the new Hayden Gallery is entitled "Nude, Naked, Stripped," according to the Art at MIT mailing. The description says it examines the varied attitudes to the body without clothes. Mutterings about whether McBay and ProFemina know about this.

Larry Lennhoff: Glen Cook answered a bunch of questions I sent to him. Now we have an "interview" for TZ.

BPS: LeGuin's latest work is about the people called the Kesh, and the paperback is selling for 25 dollars. My roommate said they should knock off 3 dollars and sell it as Kesh-22.

Connie: WWN Report: A freak accident started by a paper plane burned down a house, and a See-and-Say that got dropped now speaks obscenities. Also, a Minnesota hotel offers a complimentary cat with their rooms, and a pet python that escaped in Wilmington, DE, prompted a law that snakes can't appear in public unless they're on a leash. Articles attached.

TMc: Minicult: two weeks ago I had an interview for Hughes Aircraft's Denver facility, which they are careful not to advertise. They gave me an address and I sent my transcript. It came back marked as "no such street in this town."

BPS: Minicult: Scientologists are trying to block the release of secret, sacred documents obtained by the LA Times. The papers reveal the Church of Scientology belief that mankind's problems were caused by an evil interstellar tyrant of 75 million years ago named Xemu. Attached.

AA: Move to award a banana to Ethel the Aardvark. Passes everyone-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}