\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 6, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (11/22/85) read and corrected by DSK in the lateness of the Onseck.

Phonecomm: Ring! It's for AA, who isn't here yet.

RvdH: Move to approve the minutes as being in a banana-colored binder.

ATS: Now cut that out!

There are many motions that people don't like, and finally someone actually move to approve the minutes as read. Passes lots and lots-3-3 +Spehn.

\goto{Committee Reports}

AA: Panthercomm: Star Chamber, when you open boxes of books, remove the review notices and insert a marker saying "review copy" when appropriate, so we'll have a regular system and less confusion.

RvdH: Concomm: The Imperial Wizard Society convention was at the Boston Marriott. The hucksters' room contained an electron microscope and a laser, both set up and working. An IBM lecturer discussing fractals proved himself an incompetent Trekkie.

ATS: Pseudo-LHE Report: There should be an LHE Report, but the LHE and the Vice skipped out. Together. In the same body, even. Anyway, the Sunday, November 24, 1985 Doonesbury features the LHE of the future, a computer that automatically makes reservations to Rio for you when you use it to embezzle company funds. Cartoon attached.

ATS: Moocomm: I have it on good authority from LSC that King Solomon's Mines is the most dismal movie since Megaforce.

BPS: When Lisa saw it in Pennsylvania, they turned on the theater heat for the first time since last winter. Some dust in the vents caught fire and they had to evacuate while it was extinguished. She said it was the best part of the movie. Road Warrior tonight.

RKW: Snakecomm: There will be a snake demo and party at 7 PM, January 21, 1986, in the 8th floor playroom of NE43. Don't bring any couches. Also, if anyone is interested in an eight foot python...

ATS: Phonecomm: It's a Miller motion from SSDT. Fails.

BPS: Sitcomm: Zone- there's another Ellison episode tonight, One Childhood, Furnished in Early Poverty. Also, he's quitting over the killing of a segment by CBS Standards and Practices. It was to be a shocker of a social statement starring Ed Asner. Sigh, we all knew it was too good to last. Article attached.

KM: Another Zone episode that probably won't make it is about an Elvis imitator. Many states have laws against imitating someone without permission from either the person or the estate.

CH: Concomm: Jacqueline Lichtenberg will be at Boskone and wouldn't mind a party with Ambrov Mitar. And she's working on a vampire novel.

KM: Concomm: Jim Henson will be at SILiCON, the Rekon convention.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

KM: Minicult: There is a magazine which in its requirements for submissions says no science fiction, pornography, or occult.

DSK: From the Herald, courtesy of SSDT- Tuesday's Far Side cartoon, a picture of a praying mantis looking at a gramophone, with no caption, confused lots of readers. It turns out the idea is that a mantis is the only insect that can tilt its head like the RCA dog. Attached.

DSK for SSDT again: Ten comic strips, including B.C. and Wizard of Id, will move from the Glob to the Herald next year because they are represented by News America Syndicate, which Herald owner Rupert Murdoch got hold of fairly recently; their contract with the Glob expires 12/31. Move to condemn Murdoch and the Herald! Passes by Skinnerial decree. Article attached.

BPS: Minicult: A burglar fell through the false ceiling of a San Diego bank office and was stuck dangling for 48 hours. Picture attached.

BPS: Bill Scott, voice of Bullwinkle and Dudley Do-Right, is dead. Obituary attached.

RKW: The latest collector's items for fans are hand and foot prints of various SF celebrities. Ad attached.

BPS: Minicult: I got a flat tire and took the corpse to Cambridge Tire, and there was Chip Hitchcock doing the same thing.

DSK: Last week on the Dr. Demento show, there was a song called "Marvin the Paranoid Android." He was singing.

CH: WWN Report: 1) A pet parakeet that escaped out a window, got stunned, and froze stiff, was flushed down a toilet by the owner, who thought it was dead. An hour later it started chirping and a plumber found it in an air pocket in the pipes. The owner was so freaked out that she gave it away and got a kitten. 2) Exerlopers are spring-loaded shoes that make it possible to run backward almost as fast as forward. They average over ten pounds and will sell for 140 dollars. Articles attached.

Phonecomm: It's for Adina again, who is here this time.

Phonecomm: It's for Adina, who is still here.

JME: A person has actually responded to the list of books to be reviewed. Thank you, Connie.

RKW: Minicult: DC Comics has launched a series of graphic novels, including works by Bradbury, Bloch, and Silverberg. None by Jim Shooter.

JME: Minicult: Just over the Connecticut state line on I-84 is a restaurant, The Traveler Restaurant, where if you buy a meal you get a free book. This practice got started when the owner bought a set of books at an auction because he wanted two and had to find something to do with the other 14,998.

DSK: Minicult: commercials are out for Robotman and Stellar dolls.

AA: Move to send Rupert Murdoch a pair of banana colored Exerlopers and weld them to his feet (or face). Passes everyone-no one-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}