\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 1, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Merryl Gross, Vice and Pseudo-Skinner, presiding.

Minutes of the previous meeting (1/25/85) read and corrected.

(RvdH) Move to approve the minutes as being the same color as the end of the whip. Passes 7pi-14 1/3pi-squawk +Spehn. It was loudly pointed out that this actually failed, but that didn't seem to bother Merryl.

At this point in the meeting, RKW arrived with two snakes, one of which was Merryl's. It is called Tansy.

\goto{Committee Reports}

(ATS) Moocomm: The LSC SF marathon was; highlights- during Destroy All Monsters, when Godzilla had his big scene, the song Godzilla by Blue Oyster Cult was mixed in with the soundtrack for the film. It was noted that this was done very well. Many people apparently thought that the song was part of the film.

(BPS) Sitcomm: OtherWorld was terrible, abysmal, the pits. (At this point, Susan Pitts complained. Bill called it Lost in Space updated.) Next Monday at 9 PM, Channel 2's American Playhouse is featuring an SF work: Overdrawn at the Memory Bank, described as a science fiction tale set in a futuristic society run by corporations. Bored with his computer job, Aaron Final accesses the restricted cinema file and screens Casablanca unaware that he is being watched.

There was much flaming about the absurdity of this description. An ad for this has the caption "They want to control his mind but they can't even find his body."

(RvdH) Sitcomm sub 2: As if to prove that there is no situation that cannot be made into a sitcom, a producer is trying to get a show going about the aftermath of a nuclear war (called The Only Folks Around) and claimed that it was going to be a sensitive treatment of the issues of isolation, similar to Gilligan's Island. See SF Chronicle, September 1984.

(MTG) Move to strand the producer on Gilligan's Island. Friendly amendment by RvdH: "...and then nuke Gilligan's Island." Accepted. Motion passes lots lots lots-not very many at all-a few lonely squawks +Spehn.

(ATS) LHE Report: Loss of 271.04 due mainly to t-shirts. Equity level of (Phonecomm: RING!) 4980.95. (Ken notes that the caller was Bruce Johnson.)

(KM) Telzey Amberdon Report: Ken got his car today; it is a Rabbit. Also, Ken and Janice put the down payment on their honeymoon.

(ATS) Boscomm: Interesting ideas needed for a sign behind the table in the huckster's room.

(MTG) Boscomm sub 2: Please help with the scavenger hunt.

(AA) Panthercomm: Inventory tomorrow; also, a replacement is needed for Pete Smoot.

(BPS) More Sitcomm: This Saturday, Gene and Roger will be looking at SF; this Wednesday on The Fall Guy, there will be cameo appearances by ex-astronauts.

(MTG) Move to commend John Glenn for not appearing on the show. Passes by Skinnerial decree.

\goto{Old Business}

(Deathly silence.)

OBA: um, us, ur. ("What happened to the usual vote?" Merryl: "We don't need votes!")

\goto{New Business}

(KM) Minicult: three Minicults, all from the Herald. Blind workers were hired to remove labels reading Made in Japan from various products. Three men were arrested for attacking two phone booths with a car. And a 10-year-old girl in Texas found clues to a murder that the police had overlooked because she is a murder mystery buff. See attached articles.

(Jenny) Minicult: The newest Myth book is out- Mything Persons- and is full of references to Elfquest.

(AA) Minicult: Robin McKinley just won the Newbury for her latest book: The Hero and the Crown.

(RvdH) Minicult: There is some small comics company that will soon be coming out with a comic book whose artwork is done entirely on a Macintosh.

(GF) Minicult: A comic book is in existence that deals with the adventures of Mother Teresa. Also, last week in France, President Mitterand visited a comic con, and while he was looking at comics, the Minister of Culture declared that comics were the art form of the future.

(KM) People's Albanian Embassy: Last night a character from Cheers was singing a song about Albania; apparently it was devised to allow one to remember facts about Albania.

Shawn declines to give a Jourcomm report.

(BPS) Moocomm: Contract negotiations have finished and STrek IV starts filming in the fall, directed by Leonard Nimoy.

(AbM) Moocomm: 1984 opens tonight in Boston.

(BPS) Sitcomm: The ad for V in the TV Guide has a picture of Lydia and Diana and says "Lizard Ladies Battle to the Death?" Attached.

Much flaming.

(BPS) Minicult: A West German policeman was attacked by the pet rat of a punk rocker that he was trying to arrest. He eventually completed the arrest, but the fate of the rat is unknown. Attached.

(BPS) MITSFS has a discount again at Spike's, because out of BSTA, NESFA, and MITSFS, MITSFS used the discount the most last year.

(AbM) Infocomm: All of the pictures have been completed, with the exception of JP.

Bill made various comments on his picture. Phonecomm: RING!

Miller motion. Fails. Miller motion. Passes over the loud and obnoxious cries of Rabbits.

\vspace{12pt}

\noindent
Meeting adjourned, 17:38:23 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}