\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 18, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (10/11/85) read and a lot fewer than people expected.

ATS: Move to approve the minutes as nonexistent. Passes a lot-slightly fewer-a massive squawk +Spehn.

\goto{Committee Reports}

ATS: Moocomm: Return of the Jedi tonight, 4 shows. Death to the Ewoks!

JME: Sitcomm: Twilight Zone was good. Amazing Stories wasn't. Wasn't on, that is. Lecturecomm: David Brin was entertaining, intelligent, and bizarre.

BPS: Pseudo-Moocomm: I watched Ninja 3: The Domination on HBO. It's really great for late at night.

\goto{Old Business}

GF: Yesterday I sold a membership to George Phillies.

JME: Write stuff for Twilight Zine, people. BPS suggests as a motto "Write whatever you like, it'll probably get published."

OBA: um, us, uv, ur.

\goto{New Business}

JME: Minicult: for 31.50 you can buy a baby Jesus doll, complete with glow-in-the-dark halo, in any of three races. Article attached.

DSK: The I-70 Series starts tomorrow. Kansas City and St. Louis.

GF: When I was in Missouri, I saw a big sign that said MIT. It turned out to be Missouri-Illinois Transport.

JME: The circus is in town. The train is parked behind the reactor.

Andy and Scott start discussing their Psycho class, and Janice moves to condemn them for bringing up serious academics. Passes by acclaim.

Janice then moves to condemn Andy for not wearing any banana colored clothing, thereby making it difficult for us to end the meeting. Passes pi-3-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}