\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 8, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (3/1/85) read and corrected.

(Shawn) Move to approve the minutes as not worth comment. Seconded. Passes 12 +RvdH-7-6 +Spehn.

\goto{Committee Reports}

(ATS) LHE Report: Last month we came out 46.88 ahead, which is good considering that we're usually way in the red this time of year. Equity level 5027.83.

(JME) Skinner Report: We still hate Finboard, especially Chiquita White; she sent us a note saying that our Finboard meeting is tomorrow morning. We got the note this afternoon. Janice said we should rename her as she doesn't deserve to be named after a banana.

(Shawn) Move to rename Chiquita "Sunkist." Passes 18-1-5 +Spehn.

(MJG) Wittercomm: We got a shipment; it included Mercenaries of Gor.

(BPS) Moocomm: Preview of Ladyhawk last Tuesday. Grumbling about the soundtrack by Alan Parsons Project. We also received a copy of the novelization by Joan Vinge.

(JME) Moocomm: You Only Live Twice tonight, for the 37th time, and The Tall Blonde Man With One Black Shoe tomorrow night.

(JME) STrekcomm: James Doohan is "beaming down" to Lechmere's in Framingham and Danvers on Sunday. He's promoting the Star Trek video cassettes.

(JAH) Dr. Who Report: The BBC's new director has decided to suspend the filming of Dr. Who for the next 18 months. (Mixed applause.) Janice thought that we should write to them and say that we support their decision.

(ATS) STrekcomm sub 2: LSC has managed to obtain Gene Roddenberry as a lecturer for this fall.

Someone starts to chant "flame, flame, flame..." Jenny said "This meeting is going down in flames," and AbM promptly Albanianed her. Janice enthusiastically endorsed the motion with the traditional affirmation of "I don't care."

\goto{Old Business}

Phonecomm: Ring! It was for George Flynn; Jenny had told these people who had been trying to find GF for a year that he might be here in the Library. AbM, in another Phonecomm report, noted that Dave Broadbent called earlier and wanted it to be known that Xerox has a matching grants program and he was considering donating money to the MITSFS. Robert suggested that we give money to Dave, who would donate it back to us, etc.

(SSDT) Re the LHE Report: The Institute did to her what the Libraries did to us, except they took it back. All 7000 dollars. Many "aw"s.

(RKW) Very Old Business: When Robert was Onseck, they made an arrangement with Donald Grant to buy new releases directly from him; Robert, we can try to start this up again.

(JME) I've finished the Hitchhiker's Infocom game.

OBA: um, us, uv, ur.

\goto{New Business}

(AA) Plug- Friends of Darkover meeting on Sunday. End of plug.

(JME) Minicult: A man in Maine who had a vasectomy last year is about to become the father of sextuplets.

Flaming on birth control, etc. Janice requested that something be struck from the minutes. However, it didn't keep AbM from saying "I thought that'd be a skinner report." He was given a deadly glare from Janice. Jenny said "This meeting is slithering to new depths." People flamed about whether or not she could be Albanianed again, or Lithuanianed, etc.

(SSDT) Minicult: A 14-year-old MBTA buff drove off with a bus and pretended to be a bus driver for a while; when he was finally apprehended, he was charged with, among other things, assault with a deadly weapon (the bus).

AbM: "Boy, they really busted him." Janice said that people couldn't do anything to the Onseck except for physical violence. Merryl got out her whip.

JAH displayed some elfquest posters; nasty comments were made about smurfs.

(Shawn) Minicult: Jordache is suing a couple of women who are selling jeans for women size 16 and over for calling the jeans "Lardache."

People flamed about Jesus jeans, for which the slogan is "Those who love me, follow me."

Miller motion. Seconded. Fails 4-17-5 +Spehn.

Miller motion. Seconded. Someone made a bad comment about it being Miller time.

Move to commend Mrs. and Mr. White for naming their daughter after a banana. Someone made the mistake of asking if the Whites had more than one daughter, and Merryl said "Yeah, a whole bunch." Passes 21 and a pair of scissors-11-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1727 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}