\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 2, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (7/26/85) read and corrected.

RvdH: Move to approve the minutes as being nice and short. Passes lots-less and a bagel-even less +Spehn.

\goto{Committee Reports}

ATS: Moocomm: On the productions chart in SFC is a movie called Breakdancers from Mars, no relation to Invaders from Mars, also in production. Also, Warren Beatty will star in the Dick Tracy film, for only 6.5 million and 20 percent of the profits.

SSDT: What if the profits are negative?

BPS: Ex-Telzeycomm: Ken went over to the Tech to tell them to turn down the music a while ago, and I think they've devoured him. (Note: Tarl picked up the music quite distinctly.)

GF: Pseudo-Moocomm: They're going to make a movie from the Destroyer series.

SSDT: Warped Analogcomm: Tarl got a bit fresh with Ella, and when I typed a carriage return, she punched him out.

BPS: Pseudo-Moocomm: Robert Zemeckis is doing a movie based on the old radio show The Shadow. He says he's going to do it straight, because he hates the word "camp."

Flaming about Ronald Reagan returning to acting.

Phonecomm: Ring. It's a person looking for Janice.

ATS: Jourcomm: Tim Huckelbery sent a letter including the conclusion of Science on the March for the TZ.

\goto{Old Business}

There was nothing else interesting in Tim's letter.

OBA: usual routine. Sold.

\goto{New Business}

BPS: Minicult: From Games magazine, here's an article about intentional bugs, known as Easter eggs. For instance, if you put the disk for Karateka in upside down, you get the game upside down. Attached.

ATS: A moment of silence for Cordwainer, our dearly departed typewriter.

...

ATS: That's enough.

GF: Minicult: Coleco is making Rambo dolls. Accessories, such as the entire country of Vietnam, are extra.

SSDT: Move to commend Tim's letter for being banana colored. Passes quite a few-5 and half a bagel and a honk-the square root of pi +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}