\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 25, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (10/18/85) read and corrected.

Somebody moves to approve the minutes as not inspiring creativity. Passes lots-1-a couple +Spehn.

(SSDT: But they're too short to inspire creativity!)

\goto{Committee Reports}

Lori Zieran: Gorcomm: I've finished the series. Analysis RSN.

ATS: Skinner Report: I've been immortalized in LSC malfunction slides.

SSDT: Pseudo-Panthercomm: Our hardcover copy-count inventory is back. I found it in the fourth dimension.

ATS: LSC Report: We had our 2 millionth customer Saturday during Blues Brothers. He got a giant pass and a giant box of popcorn.

KM: Concomm: Janice and I bought supporting memberships 14 and 15 in Readercon.

HAM: Brustcomm: Brust is quitting his job to write full time.

\goto{Old Business}

JAH: NESFA finally got a clubhouse. Maybe they'll even get a phone.

ATS: The Harvard Crimson mentioned that Brin was autographing at Spike's, and completely neglected the fact that he spoke here. Article attached. Also, we got a note of thanks from Brin.

OBA: um, us, uv, ur, clink.

\goto{New Business}

SSDT: Minicult: You remember the song "One Piece at a Time?" Well, a man got arrested for swiping F-14 parts and selling them to another guy who was selling them to Iran.

JAH: Ursula K. Le Guin will speak at Radcliffe next Wednesday.

Connie: Here's a newspaper photo of a car accident in Alabama. The number of highway signs present is adequate reason for the crash. Photo attached. Also in the Weekly World News was an article about a woman who was driving along minding her own business when an airplane landed on her car. The vehicles were trashed, but the people were fine. Thirdly, there was an article about a teacher who finished a mountain climb despite breaking her ankle 5/6 of the way up.

SSDT for AbM: Minicult: About a week ago a man came into the Computer Museum, said he was Steven Spielberg's personal secretary, and got a deluxe tour by saying that a sequel to ET was being filmed and Spielberg was interested in using the Museum for a part. The man spoke about the film in great detail, but when confirmation calls were made, he turned out to be a hoax. Fortunately, nobody bought the ET sequel stock he was offering.

Micah Doyle: Reruns of The Prisoner are starting midnight Saturday on Channel 7.

BPS: Minicult a la Pseudo-Sitcomm: Gilligan's Island on sale for 8.75 million. Article attached. (ATS: A NY penthouse went for 8.2.) Minicult a la Pseudo-Phonecomm: The Glob reports that today all 23 million phone numbers in France are being changed. Half the people don't understand the new system, and 20 percent can't even figure out their own number. Ordinary Minicult: An accused robber leapt to his own defense in court by calling the witness a liar and saying he should have blown her head off. After a pause, he added, "If I'd been the one that was there." He was convicted.

RvdH: Lecture tonight at 8 about the history and future of Anarchism.

TMc: Minicult: Visa is coming out with a platinum card, which is the same as a gold card only more expensive, and American Express with a blue card, which lets you borrow against your assets. If you don't pay, they repossess your house and your car.

RKW starts talking about snakes too softly for Tarl to hear, Jenny says Thieves' World 7 is out, and KM moves to commend her for wearing a banana colored shirt. Passes 42-24-2 or 4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned at no particular time, since the Skinner didn't bother to mention it.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}