\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 22, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

The Skinner, due to the absence of the Onseck, read the minutes of the previous (3/15/85) meeting.

(BPS) Move to commend the minutes for being pretty good considering that they were written by someone for whom English was not his first language. Seconded. Passes 372-2 fingers-4 +Spehn.

Someone made a comment about what a wonderful Onseck the MITSFS has, but the exact wording of this comment was unclear.

\goto{Committee Reports}

(BPS) Skinnercomm: The Skinner just had a good question; what was it?

Replied Janice: "The question in the Bitch-to-the-Skinner book was 'if someone crosses off his hours and wants to work someone else's hours and those hours are crossed off, how would you do that?' The answer is that you uncross their hours and write your initials in."

(BPS) Spikecomm: Spike has announced that he is extending the MITSFS discount forever, or for at least as long as he's around, or at least until something happens. (Applause.)

(JME) Pseudo-Pianocomm: We lost a keyholder- Shawn Gramates- but she will continue to ROSFAP until we find and train a replacement. Beware that we are looking for one.

(BPS) Theftcomm: Thanks to Larry Lenhoff, we now have a xerox of the manuscript for Trumps of Doom by Roger Zelazny.

(JME) Jourcomm: We'd like to put out a TZ over the summer; start volunteering now, you can get lots of brownie points.

BPS suggested that we put out TZ 22 or something like that as the new TZ, and no one, particularly finboard, will ever notice.

(JME) Moocomm: The Secret of Nimh tomorrow night.

Much flaming about the book and the movie. It was noted that Mrs. Frisby's name was changed to Miss Brisby because the Wham-O company complained.

(KM) Telzey Report: If you come by the MITSFS and the painters are painting the doors, try to stick around the Library. If you come by and the doors are left open to dry, shut them, even if the painters complain.

More flaming, this time about insurance and a MITSFS clubhouse. Said Janice, "Well, flame flame flame flame flame."

(KM) Pinkcomm: Anybody who wants to can buy about 200 yards of pink pinstriping material from Jerry Co. Surplus; it might look really nice on the newly painted walls.

\goto{Old Business}

(JME) Since Robert isn't here, I will report that Robert got his car back. It was found at Burlington Mall; the ignition lock was taken out, but there was no other apparent damage. He was told over the phone that there was a great deal of debris in the car, but according to Robert, it could be described that way at any time.

(KM) Judy Passman is going to be turning in her key.

OBA: um, us, uv, ur. Janice noted the absence of the debate, and Ken M. said "usual debate."

\goto{New Business}

(JME) Minicult: New England Telephone is extending to all of Massachusetts a service that has been met with great success in Worcester in the past few years. It is called Dial-a-Friend; this involves calling one of three numbers (teenage, adult, or senior) in which you are connected with up to four other callers. If there is no one else on the line, then a telephone company employee will talk to you until someone else comes on. This is apparently very popular.

(JME) Minicult: Bob Guiccone Jr., whose father runs Penthouse, is starting a magazine called Spin, which he says will be what Rolling Stone should be, namely a magazine about off-beat groups that one normally wouldn't hear about. The cover of the first issue will feature Madonna.

(KRJ) Minicult: A local TV station advertised its new hour and a half comedy lineup: The Munsters, The Addams Family, and pro wrestling.

(BPS) Minicult: According to this week's TV Guide, the new version of the Twilight Zone will be an hour long, and the music will be written and performed by the Grateful Dead.

(JME) Minicult: There was a mention in the Glob's weekend section about a new heavy metal band from Japan which is referred to as Japan's Van Halen. Its name is Loudness. Presumably, this follows truth in advertising.

(KRJ) For all you dinosaur fans, Baby opens today. (Groans.)

(JME) Minicult: DelRey announced that Joan Vinge is writing the novelization for the Disney Oz movie (the new one based on all of the Oz books except the first one). Janice called her the female Alan Dean Foster.

(BPS) Minicult: Spike reports that a few weeks ago he received four copies of the new Gor novel and still has all of them.

Move to commend the good taste of the Cantabrigian science fiction reading audience with a banana. Amended to "with a chained banana." Commented Bill, "bananas in bondage." Passes lots times 4-nobody-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}