\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 25, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(MTG) Move to approve the minutes as close to reality. (Ignored.)

Janice waves the minutes in her hand and calls for a second. Motion seconded; passes lots of waving limbs-fewer stationary limbs-wings, elbow, squawk +Spehn.

\goto{Committee Reports}

(RvdH) Heathen-Infidelcomm: Atheist discussion group meeting on Tuesday; it was successful.

(Shawn) Heathen-Infidelcomm sub 2: Lots of serious people showed up at the Pagan Students Group meeting.

(BPS) Bondagecomm: We have a new electric Onseck: Tarl, and he is chained to the bookshelf.

(ATS) Moocomm: We have a schedule for the LSC SF marathon. Attached. (During this report, the Onseck was hissed at by the Skinner for eating crackers.)

(ATS) Boscomm: Keyholders and would-be keyholders are encouraged to sign up for hours for the MITSFS table in the hucksters room. The Star Chamber will take up any extra slack. So sign up!!!

(JME) Boscomm sub 2 (or WHY NESFAsuckscomm): We received a call from Houghton-Mifflin who thought that we are running Boskone. Every year they have a table in the hucksters room where they sell their books for half-price; this year NESFA returned their check telling them that there was no more room available.

Robert Wiener related a similar story. BPS noted that sometimes NESFA has some characteristics in common with LSC.

(JME) Moocomm: Thunderball tonight; Streets of Fire tomorrow.

(Shawn) Jourcomm: We'd like to have a TZ really soon; Shawn requested that someone else check into reproduction- this was clarified to magazine reproduction. Says Janice: "When you find that person you can call them Porncomm."

(Shawn) Jourcomm sub 2: We need book reviews; a list of review books that we received will be posted.

(SSDT) Randomcomm: The new TV show Street Hawk, referred to as Knight Rider on a motorcycle, seems to have physics problems. The motorcycle takes about 60 gees on jumps and 250 gees on turns. It was noted that this was enough to liquify any riders.

(JME) Pseudo-Moocomm: The movie 1984 is out and has been getting good reviews. It has John Hurt (movie version of The Elephant Man) as Winston Smith and Richard Burton (in his last role) as O'Brian. Music is by the Eurythmics; their song "Sex Crime" has been refused play by some radio stations who think that it's about rape.

(BPS) Sitcomm: Tomorrow night at 8 PM on CBS is the premiere of Otherworld. According to the Wall Street Journal: "A family this wholesome ought to be pitching granola bars, not falling through a space-time warp inside the Great Pyramid." Articles attached.

(JME) Boscomm sub 3: The MITSFS has after all decided to enter the club division of the Boskone scavenger hunt; people are encouraged to help. A list of what we need will be posted.

FLAMING FLAMING FLAMING FLAMING inundates the MITSFS and the Onseck.

(BPS) Prisoncomm: The good news is that videotape episodes of The Prisoner will be available soon; the bad news is that there's only one episode per tape and each tape costs 39.95. There are 17 episodes.

(AA and JME argue about a Panthercomm report; AbM reports that he spoke with PS last week and that PS said he would have all of the changes entered in one week.)

(AA) Panthercomm: Probably an inventory a week from tomorrow; everyone should come and read shelves, especially people who want to become keyholders.

(RKW) Snakecomm: On January 1, I got a 29 inch boa named Abel; he only weighs 5 ounces. Abel, like Klyd, is a Sime.

\goto{Old Business}

(JME) The magazine processing party was a great success and we had cookies afterwards, and we now have about 6 boxes of magazines for sale.

Ken Johnson then informs Janice that he was saving some magazines for trading, and that they're no longer useful for that.

(JME) The Hitchhiker's marathon was not that great of a success, but we did manage to sell some memberships. It was noted that the weather was very bad.

(JME) The t-shirt run was also a great success, and now we have 16 dozen t-shirts for sale (bright red on gray).

(AbM) The Alpert made a 40-dollar donation to the MITSFS endowment fund.

OBA: um, us, uv, ur.

\goto{New Business}

(KM) From this week's Newsweek: in North Carolina, the director of sanitation in Hayesville came to work one morning to find that hundreds of telephone calls, all within seconds of each other, had been placed from two phone lines the night before. It turns out that the calls were placed by two Coca-Cola machines trying to phone home; both had been equipped with computers to let the local distributor know when they were out. The computer they were calling wouldn't answer so they just kept trying.

(JME) Minicult: A magazine page containing dehydrated foods in plastic bags was patented. See attached.

Janice suggested that Analog use this so that when the stories become too much, you can just eat them. Ken suggested empty pouches for the more obvious response. Robert said he can't wait to see the next issue of High Times.

(SSDT) DeanDrivecomm (This gets changed to a Minicult): Someone sent away for more literature from an ad in Whole Life Times and received a 10-page report on a device called "The Raydon," which supposedly neutralizes harmful radiations.

There was much flaming. Note: the person who gave SSDT this article is filing a complaint with the FDA. Attached.

(KM) Minicult: A hack of the Rockwell recruiting. Attached.

(MTG) Robert van der Heide conveniently helped color the tip of the whip red. (Details withheld from the minutes.)

(AbM) We had our picture taken today.

(BPS) Miller motion. Fails 3-7-something +Spehn.

(KM) Miller motion. Passes by some vote, which was drowned out by people singing Rabbits.

\vspace{12pt}

\noindent
Meeting adjourned, 1555 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}