\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 18, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Note: Due to the unexplained absence of Tron, the Onseck was forced to try to record the minutes by hand in real time. This will probably cause slight aberrations in people's memories of the meeting. Sigh, reality strikes again.

Minutes of the previous meeting (1/11/85) read and corrected.

(JME) Move to accept the minutes as not at all resembling John Dumas. Passes lots of arms and legs +snake-fewer arms and legs +snake-squawk, a leg, and no snake +Spehn.

\goto{Committee Reports}

(SLP) Moocomm: there is both good and bad news from LSC. Good: Repo Man has been pulled from the Boskone weekend. Bad: LSC will show Buckaroo Bonzai instead. It was noted that LSC still sucks.

(JME) Bananacomm: We have a new magnetic banana toy from BPS; now we have one on reserve and one circulating.

(JME) McPapercomm: The Midas Plague.

(Jenny) NoSurprisecomm: According to Time, Isaac Asimov is the most prolific author. This caused much confusion and flaming.

(JME) Boscomm: We got information from NESFA on our half-table.

(JME) Magazinecomm: Magazine processing party tomorrow, 1:00.

(AA) Panthercomm: Inventory on February 2 (Groundhog Day).

There was some slight commotion when KRJ asked a question and was subsequently Albanian and Finger motioned.

(SLP) Snakecomm: Risa is here; she lives in an aquarium with Klyd.

Some discussion about the morality of snakes (and Susan Pitts) follows.

(JME) T-shirtcomm: 7:00 Tuesday night.

Moocomm: Mad Max on Friday, cartoon festival on Sunday, and Time Bandits on Wednesday.

(Shawn) Heathen-Infidelcomm: The Pagan Students Group met last Sunday night; the IAP Committee called Pam Keller and made the group promise not to hold animal or human sacrifices on campus. Presumably plant sacrifices are ok.

(BPS) Vcomm: V seems to have permanently introduced a new character, who was described as "Prince Dirk Blackpool as an alien."

(JME) InvisibleMancomm: Tom Lang came to the Library today- almost during a meeting.

(JME) Foodcomm: Jade Terrace has a new menu- it's really good. Said Ken M.: "The food's good too."

(BPS) Trekkiecomm: Leonard Nimoy got a star on Hollywood Boulevard.

Many people noted with pleasure that William Shatner does not. Malcolm related a story about Hollywood Boulevard from an old radio show that is being rerun on WMMV.

(JME) Fishcomm: Hitchhiker's Guide radio show marathon on Sunday.

\goto{Old Business}

(AbM) Susan Fine called last week to see if we had any information on NESFA; it was a member from the mid-70s.

(AbM) College Bowl was, and we lost to Senior House. We did manage to confuse the judges, though, because the four Senior House people were dressed normally, and the MITSFS team had two people with MITSFS t-shirts and two with Sport Death shirts.

OBA: um, us, uv, ur.

\goto{New Business}

The Surman and the Dorn are characters in a new Infocom game called Sorcerer.

(JME) We received a free copy of a hack book: Science Made Stupid.

(AA) A student agreed to return the 1000 dollars he won for a short story he plagiarized from Zelazny's "The George Business." Article attached.

Pointless flaming on dragons and Georges. In some real magazine, Roger Zelazny was referred to as a "noted author," not an SF author.

(BPS) Minicult: Gene and Roger came out with their Best and Worst movies of 1984 (attached), with Duena s the worst big picture of 1984. Said one of them: "I had more fun with sand at the beach."

(SSDT) The police blew up a typewriter because they thought it was a bomb; one of the policemen observed that "This is a lot like Scrabble- I've got an H and an M." Attached.

(Malcolm) Move to commend the Glob for matter doesn't matter.

(BPS) JME looks like Liza Minnelli.

Lots of FLAMING.

(JME) Tech SciFi (Trivial Pursuit team composed of MITSFS and The Tech) lost to Andy Eisenman and others.

Miller motion, and another Miller motion. Passes 73000-1-23.5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}