\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 11, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (10/4/85) read and corrected.

SSDT: How about somebody approving the minutes as costing me 70 cents?

This gets seconded but not moved.

ATS: Move to approve the minutes as not worth the paper they're printed on. Passes less than half-less than that-those pink velcro tennis shoes again.

Therefore, in the interest of not wasting paper, there are no more minutes this week. One item attached.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\vspace{18pt}

Attachment 1 of 1:

LHE Report, September: Income- 1740.08, Expenses- 1435.69, Profit- 304.39, Equity- 5107.65. For the fiscal year ending in August, income was 2184.50 dues, 908.90 fines, 848.79 sales, 2389.37 misc; expenses were 1869.13 books, 511.01 mags, 856.15 supplies, 1547.17 misc.

Sitcomm: Ken M. reports mixed reviews for Twilight Zone's latest, and more Spielbergness in Amazing Stories.

Moocomm: Remo Williams, based on the Destroyer series, opens tonight. So does Silver Bullet, from King's Cycle of the Werewolf. SSDT saw the sneak preview and says it's pretty bad. The Howling comes to TV next week.

Whooshcomm: The Atlantis is back.

Ken and Janice's housewarming was. Ken thanks everyone who bothered to show up.

SLP gives her endorsement of the Expanded Visions exhibit of light sculpture just off Lobby 10.

SSDT mentions that just as the multi-year lawsuit for ownership of Fenway House reached the point of decision, the judge died.

See article below for two Minicults also involving ownership courtesy of DSK.

Janice sends a Miller motion by phone. It fails. A second one passes lots-no one-2 +Spehn, ending the meeting at 1720 SST.

P.S. Orson Wells is dead.

\end{document}