\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 6, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (8/30/85) read and corrected.

BPS: Move to approve the minutes as reasonable. Passes 42-less-in between +Spehn.

Andy declares the meeting will be freshman-friendly.

\goto{Committee Reports}

ATS: Moocomm: LSC has Tron, Dr. Strangelove, and Buckaroo Banzai.

JME: Moocomm: Little Shop of Horrors is being remade.

SLP: LHE Report: Income- 573.06, Expenses- 686.67, Loss- 113.61, Equity- 4803.26.

JME: Comicscomm: Orbit stinks, but at least it replaced Tyler Two.

ATS: Moocomm: Poltergeist 2. Aauggh.

SSDT: Move to condemn, sight unseen. Passes lots-2-10 +4 snakes +Spehn.

TMc: Moocomm: At Cal Tech I lived in the same dorm room used by the hero in Real Genius.

SSDT: Pseudo-Treasurer Report: Someone left a Band-Aid in the book drop, probably as a comment on the condition of our circulators.

ATS: Kingcomm: Steven King wants to write about a killer toilet.

ATS: People's Albanian Embassy: There's an Albanian bookstore on Franklin Street.

\goto{Old Business}

BPS: I've been with MITSFS 10 years now.

SSDT: For our 1966 Boskone, we rented a movie called Sex Kittens Goes to College (sic).

OBA: um, us, uv, ur.

\goto{New Business}

JME: An impromptu experiment showed that lidocaine is the best way to get roaches out of your ears. Attached.

BPS: Hardy Boys are back and unfortunately updated. They also get condemned sight unseen. Attached.

SSDT: Science Museum is selling real estate on the moon. Attached.

GF: An Austin paper quoted Ben Bova as publisher of Omni, and said fans used to be called Trekkies. Austin and its paper get condemned.

SSDT: Too much aspirin made a woman keep hearing songs in her head. Attached.

BPS: A Utah killer is suing for 2 million for damages suffered during a prison escape he was "forced" to take part in. Attached.

Connie: A woman got impaled by a steel rod that came up through the bottom of her car.

SSDT: A letter to the editor in the Glob complains that the Post Office has a good delivery service called Red Star, but you can't use it unless the package weighs at least one pound. The writer must therefore mail rocks to bring her parcels up to weight. Letter attached.

BPS: A clerk found an old warrant for the arrest of Ed Meese for not paying a jaywalking ticket. The same clerk also found a similar warrant for CIA head William Casey. Article attached.

JME: ATO hacked the Sheraton sign again, without even waiting for a renewal of the permission they got last year. Attached.

ATS: NESFA is helping bring David Brin to MIT on October 14 at 8.

SSDT starts waving a real banana over her head. The motion passes lots-2-some snakes, squawks, pink velcro tennis shoes, and Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1742 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}