\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 20, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (9/13/85) read and corrected.

ATS: Move to approve the minutes as not nearly as interesting as the farm catalog. Passes everybody-nobody+2-3 +Spehn.

\goto{Committee Reports}

DSK: Ellacomm: Ella's fixed.

SSDT: The reason she was sick was a ribbon wheel installed backwards.

DSK: Infocomm: Herb and I and a random play-tested Spellbreaker, a new expert level Infocom game, for 20 hours at the Science Museum this weekend. A Wellesley team beat us by about 15 minutes.

SLP: Shelfcomm: New shelf maintenance map going up.

SSDT: Metriccomm: The latest Tech Talk contains a classified ad (attached) promoting the metric system, and it includes the line "You have a legal right to use metric units wherever you want."

ATS: Pseudo-Whooshcomm: We have a halon fire extinguisher, which we hope will be useless.

SSDT: Gavelcomm: A Panasonic copier ad (attached) features a copier malfunction symbol which appears to be a repairman about to cream the competition with a gavel.

\goto{Old Business}

OBA: um, us, ud, uv, ur.

\goto{New Business}

DSK: Minicult: Yesterday's 800-dollar double jeopardy answer on the game show Jeopardy was "So Long and Thanks for All the Fish is the fourth book of this Douglas Adams trilogy." And it was answered correctly.

TMc: Minicult: I got a complete set of a Cal Tech poster war. 1) "Young Americans for Freedom presents Dr. Paul Cameron on 'Homosexuality: Everybody's Problem'." 2) "Young Americans for Fascism presents Dr. Wally 'Boy' George on 'Homosexuality: The Final Solution'." 3) A Young Americans for Fascism recruiting poster sponsored by The Peoples (sic) Army For The Honest Naming of Political Action Groups. 4) "As you can see, the fags are upset with us- show up at 7:30 to see the fireworks." All posters attached.

ATS: What I found so fascinating in the farm catalog was the section on cattle prods. I haven't decided which one we should get yet.

TMc: I'm donating this copy of Playboy which contains a story Joe Haldeman wrote in his class here. He says that Playboy is the highest-paying short story market.

SSDT: Minicult: A professor at the Massachusetts College of Art is in hot water for stripping in class and encouraging students to do the same. He is defending his action on the grounds of academic freedom. Article attached.

ATS: Doc Edgerton spoke on Wednesday, and in commemoration, I stole this bullet and banana postcard from Technique's door.

Move to commend Doc for taking a wonderful picture of banana pudding. Passes unanimously with Spehn abstaining.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}