\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 15, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (3/8/85) read and corrected.

(AA) Move to approve the minutes as punishing.

(JAH) Move to amend the minutes as pungent. Seconded. Passes 15 +a copy of Cats Have No Lord-the Skinner's secret number minus "fingers don't count as appendages"-6 +Spehn.

\goto{Committee Reports}

(RvdH) Theftcomm: They got my car!

Ken, in an attempt to console Robert, said "Think of it this way: how far are they going to get on the starter?" Replied Robert: "I finally got that fixed." He was given an "aw" by Skinnerial decree. Adam suggested that the MITSFS sing "Robert has no Rabbits at all," but no one else seemed to think that this was a very good idea.

Janice called for more committee reports, and after people started talking among themselves, someone said, "I have a Moocomm," and Janice exclaimed "Well then, say it, say it, before this meeting deteriorates into a mob scene. Please!"

(RKW) Moocomm: I went to the preview of the new Woody Allen movie "The Purple Rose of Cairo," and it's a fantasy; it's also very good.

(JME) Moocomm: This is Spinal Tap tonight; bring your earplugs, I suppose.

(BPS) Sitcomm: Two deaths to report- V and Otherworld.

After everyone in the room responded with loud applause, Ken suggested that we yell "LSC sucks!" just because it seemed appropriate. It was decided to wait until they show Dune.

After three calls for "any more committee reports," Janice moved into...

\goto{Old Business}

(JME) Regarding last week's Minicult about the woman whose husband had a vasectomy but who is having sextuplets anyway (the woman, not her husband)- not only is she not having sextuplets, she's not even pregnant and is currently under observation at a mental hospital. It was pointed out post hoc that her claim was not very believable, as she said she was having three sets of identical twins.

(JME) In the mail this week, we got a response to a VGG notice sent in 1982 by Liz Zitzow. A check for 9.82 for overdue fines was included. Move to commend Liz Zitzow. (Ken: with a banana. Amendment Skinnerially ignored.) Passes by acclamation.

OBA: um, us, uv, "usual flaming," ur.

\goto{New Business}

Proxy Minicults from the absent LHE read by Janice.

The first described a mechanic at a FL airport freeing the stuck landing gear of a plane by reaching through the sunroof of a car traveling along the runway at about 90 mph and releasing the gear of the plane hovering overhead. Commented Ken: "That's service!"

The other one was about a man who died after receiving three heart transplants (including one artificial one) in 46 hours. He will be cremated and his ashes saved for burial in space. According to his sister, he felt "it would be really neat to be up there forever, just circling around and around."

(BPS) Minicult: the new comic strip in the Glob, Robotman, is apparently not a real comic strip in that it is really a promotion for a line of toys that was developed before the comic strip. In fact, the person writing it is just someone who was hired to write it. Move to commend the Glob for their good taste in going along with this wholeheartedly.

After a suggestion from Janice, it was decided to pass over Robotman as not worthy of having a motion made about it.

(Malcolm) Move to condemn Creighton for dying before he had enough hearts for a flush. Albanian motion passed by Skinnerial decree.

(MJG) Move to commend SCC for painting the 4th floor this interesting sort of off-banana color. Seconded. Booed to death.

Flaming... flaming... After some flaming about how to end the meeting, a compromise was reached.

(JME) Move to commend Adina for having a shirt with banana-colored eyes on it. Motion passes overwhelmingly, many times n-1-some randomness +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}