\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 17, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, new President and Skinner, presiding.

Minutes of the previous meeting (5/10/85) read and corrected.

Phonecomm: Ring! It was for Ken J.

Chip Hitchcock: Motion to approve the minutes as "crimsom." Passes 14.4-14.3-.3 +Spehn.

\goto{Committee Reports}

JME: Ex-Skinner Report: I got a job at the Department of Public Welfare in the Budget Office of the Budget Analyst, responsible for either food stamps or refugee assistance, and located right on the fringe of the Combat Zone.

ATS: Moocomm: Terminator tonight, Airplane tomorrow.

SSDT: Moocomm: LSC's Terminator poster is handwritten and says "Arnold S. is coming in The Terminator, and he's going to rip the guts out of the jerks who keep stealing posters from this showcase."

JAH: ROSFAP: The SF-Lovers have been bound.

Chip: Moocomm 50 years later: Oz witch Margaret Hamilton died at age 82.

JME: She turned down a 1973 offer to repeat the role so that kids wouldn't be freaked out by the witch coming back to life.

ATS: Moocomm: LSC's Earthquake and Towering Inferno/"Shake and Bake" double feature in this advertisement.

An Albanian motion on LSC passes everyone who counts-no one at all-5 +Spehn.

Here Tarl trashed one report, the essence of which was "Disclave next weekend."

JME: Sitcomm: Last night's Hill Street Blues made a great deal of progress toward getting rid of several characters... (Flaming.)

ATS: Porncomm: McBay better not see the textbook Molecular Biology: The Cell. On page 689 is a graphic description of coupling between developing muscle cells.

BPS: Jourcomm: I still need reviews, stories, artwork, anything else that can fill up a Twilight Zine...

SSDT: Gavelcomm: Winners of the gavel toss at the picnic- Men's Division: 1st Bill Starr, 2nd Robert Wiener, 3rd John Woods. Women's Division: 1st Lisa Kroh, 2nd Jenny Hawthorne, 3rd Barbara Stone.

\goto{Old Business}

OBA: the usual routine. Okay.

\goto{New Business}

JME: A Florida postmaster refused delivery to a "clothing optional" condominium because his mail carriers might be offended, although he hasn't actually asked them.

Dave Barrington made a pun out of this and was Albanianed as not worthy of notice.

A Tab article featuring Ken Johnson discussing folk music was submitted, causing flaming about how to pronounce the word kvetch when referring to Ken. Attached.

DSK: Minicult: Indonesian authorities have given up trying to stamp out breakdancing. (He got Albanianed for adding that Indonesia got a break.) Article attached.

AbM: Minicult: There was a full page ad in the NY Times with Muppets waving banners that said "MIT- Muppet Institute of Technology."

JME: Minicult: Now we have Rice Paddy Babies in toy stores, complete with 39.95 fee for immigration from Hong Kong, not to mention illegal immigrant Shanghai Kids.

Chip: Minicult: Sneak preview of a new Jane Fonda/Anne Bancroft movie tonight, but they're not saying what it's called. Janice says it's Agnes of God.

Andy commends RKW for bringing in pictures of the gavel toss in a motion which eventually passes 12-7-4 +Spehn after some flaming ("every single one of us except RvdH looks like a total klutz") and lots of intermediate Albanian and finger motions.

And then there were more Albanian motions until there were only about two non-Albanians left in the room. People started singing Rabbits in Albanian, and in desperation Andy passed a motion commending Chip for bringing in a banana-colored cake.

\vspace{12pt}

\noindent
Meeting adjourned, 1732 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}