\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 26, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting read and corrected by AbM due to the late appearance and somnolence of the Onseck.

BPS: Motion to approve the minutes as rude. (They woke up the Onseck when returned to her.) Passes lots-one limb and a snake-2 +Spehn.

\goto{Committee Reports}

ATS: Famecomm: We got a listing in SF Chronicle. Attached.

AbM: Pseudo-Moocomm: Godzilla lives again. A Japanese film company is making "Godzilla 1985," complete with Raymond Burr. Attached.

AA: Moocomm: The Black Cauldron sucks. Read the books.

ATS: Moocomm: Dirty Harry and Firefox tonight, Top Secret tomorrow.

CC: Blintzcomm: Two weeks from Sunday I'm cooking dinner for anyone who shows up. Signup sheet on the board.

ATS: Confessioncomm: Charles Platt, who wrote an SFC review of a porn novel allegedly written by Steven King, now admits that he imagined the existence of the novel. King is still threatening to sue. Article attached.

AbM: Pseudo-Moocomm: The NY Times review of After the Fall of New York says it's incredibly bad. Article attached.

SSDT: Onseck Report: The reason I'm asleep is I spent all my sleep time mopping up my room which leaked, a lot.

\goto{Old Business}

OBA: usual routine. Sold.

\goto{New Business}

ATS: MIT sucks. Tech Talk reports that MIT may have "rolling blackouts" this summer. Attached.

Flaming about what this would do to computer systems, the reactor, etc. and how horrible it is that such things should be done on purpose.

SSDT: Minicult: In Vermont, a high school principal's office was broken into and trashed by a deer. Article attached.

KM: Minicult: Two of the former TWA hostages put in for frequent flyer mileage and got it. Article attached.

RvdH: Move to commend! Passes by acclaim.

BPS: Minicults about firefighters: In NYC, five were fined for loading the firehouse soda machine with beer. In Dayton, two were relieved of duty when it was discovered that they are legally blind. Attached.

AbM: Minicult: AT&T has installed one telephone on Pitcairn Island (of Mutiny on the Bounty fame). MCI called the move "an absolute coup." Article attached.

BPS: The new typewriter is named Ella, since it's salmon colored. It's on permanent loan from me.

GF: Move to commend that man in the banana colored shirt for stealing our souls. (Dave Caswell with camera.) Passes lots and lots-two feet and a camera-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1724 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}