\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 29, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (3/22/85) read and corrected.

(KM) Move to approve the minutes as "Lonely Silver."

This spurred a chorus of "What?" and led Ken to explain: there was an old tradition of approving the minutes as Travis MacDonald (corrected BPS: "MacGee;" said Adina: "yes, it was something Chip did all the time"). Continued Ken: "We ran out of colors and we ran out of Chip (Bill suggested that we delete the word "of" from the last sentence, so it would read "ran out Chip")... and apparently there is a new Travis MacGee novel out called 'The Lonely Silver Something-or-other,' but I did remember that it was lonely silver."

Sighed Janice: "Ok, motion on the floor to approve the minutes as lonely silver." People seemed to take this as a cue to interpret the phrase "motion on the floor" in a literal manner. Summed up Janice: "Ok, it's dead."

(AA) Motion to approve the minutes as chained. Died because it fell flat.

(AbM) Move to approve the minutes as Gratefully Dead. Passes many, many-only 1 many-many and a half +Spehn.

\goto{Committee Reports}

(ATS) Moocomm: LSC has a weekend wonder this weekend: Sound of Music tonight, Slaughterhouse 5 tomorrow night, and Attack of the Killer Tomatoes on Sunday (sucks!). Applause.

(RvdH) Move to commend LSC for having ONE good science fiction movie. (Added AbM: "Seconded, if that refers to Sound of Music.") Motion dropped by Skinnerial decision.

(JME) Pseudo-Pianocomm: We've lost another keyholder- Judy Passman. The end of a black leather era.

(AbM) Infocomm: The Rogues' Gallery has a new picture- Jenny Hawthorne. (Applause.) She's called "Particle Physicist," because for lack of anything else, she's the VGG's assistant, which we were going to call "Boson's Mate," but boson reminded me of mesons... (At this point, the Onseck was attacked by the Skinner with a gavel.)

Said Janice: "I'm Albanianing that picture." Some flaming on pictures followed.

(KM) Telzey Amberdon Report: The Excelsior has been lightly backed into. This caused a small crack on the cheap grill on the front, once again proving that they don't make starships like they used to. Also, a Boskone XXIII report- the latest Instant Message is predicting an attendance for Boskone 23 of 4000.

(JME) Preemptive Boskone Report sub 2: Rekon will not be held at Boskone next year, but Janice thinks it will be a failure because they're trying to do too much, like running a 24-hour film festival.

(RvdH) Genicomm: Genericon was. RPI students are even gnurdier than MIT students.

Janice said that beer companies go to RPI to test market new products. Some flaming.

(RvdH) Theftcomm: In what I hope is the end of this saga, I noticed a flutter in my steering, went to have the wheels balanced, and found out that they had managed to break the inside of the rim of one of my nice new wheels.

Some MORE flaming, Robert discussed debris (said Ken: "[illegible] as theft"), and Janice wanted to rename Theftcomm Propertycomm.

(GF) Boscomm sub 3: It will be in the Sheraton next year. (Wild applause.) The Marriott has decided that we're not their sort of people.

Much flaming about Copley and the Sheraton. George mentioned that the most recent Locus mentions MITSFS with regards to the scavenger hunt.

(Herb) Theftcomm sub 2: I had my backpack with all of my notes and books stolen from me on the train to Philadelphia. 

(JME) Pseudo-Picniccomm: Herb is now half of Picniccomm.

Bill wanted to know if he was pic or nic. It was noted that Picniccomm should get two coconuts this year. More flaming about the picnic... and more flaming about the MITSFS board.

(ATS) Cosmoscomm: Mark Washburn, a Glob writer, is trying to help Carl Sagan with a lecture and wants to know if we have any pictures of comets, particularly those about to crash into the earth.

(BPS) Theftcomm: Followup from last week- the new Amber book ends long before the story does; it's the first of three, but it's still really good.

\goto{Old Business}

After a tie vote that Janice broke, it was decided to have the Onseck read the Boskone minutes.

Adam read the Boskone minutes- all five pages of them.

Some flaming about why Jesus jumps.

(JME) The Glob called the movie about King David "a disaster of Biblical proportions." This was followed by John Wayne flaming.

OBA; said Bill, "the usual schmeal." (RvdH) Move to commend Bill for shortened out meeting. Approved by Skinnerial decree.

\goto{New Business}

(KM) Minicult: Since the Canadian beer strike is over, they're stuck with lots of beer. Since it won't sell, they're thinking of giving it away.

Said Janice: "Flame flame flame."

(BPS) Minicult: A story on woodpeckers who caused a power outage to 170,000 people in Florida. Article attached.

Flaming on Florida and Coke.

Minicult: In celebrating the 30th anniversary of Disneyland, they released a picture of Ronald Reagan from their opening.

Phonecomm: Ring. It was the man from Carl Sagan. Janice wanted it to be noted that someone finally appreciated Robert vdH.

Said Janice, after about 5 minutes: "Flame flame flame flame flame."

(GF) There's a new Heinlein novel that's been sold for 1 million dollars.

(AA) Move to commend the Onseck for wearing a banana-colored shirt. (JME) Motion to commend MIT accounting for ceasing to send their report on banana-colored paper. Passes everyone I can see-nobody I can see-E +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1760 or 1800 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck (at the last minutes)}

\end{document}