\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 12, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

(Robert made a motion and it was duly seconded. Passed a lot of people-fewer people and a bleah-4 or 5 chickens +Spehn.)

\goto{Committee Reports}

(RvdH) Theftcomm: The Boston police found my car again on Friday. It was in Dorchester.

Ken suggested that rather than replace the ignition, which was ripped out, Robert should just put in a toggle switch.

(BPS) People's Albanian Embassy: A sad, sad day- Enver Hoxha died after 42 years as Albania's ruler. (Article attached.)

Janice said that it should be noted that Albania split from the Soviet Union because they didn't think that the Soviets were repressive enough after Stalin.

Whooshcomm: Celine came by to tell us that the Spacefair people needed people to help them out. This was a Whooshcomm report because much of the spacefair seemed to deal with the shuttle, which goes "Whoosh!"

(JME) Whooshcomm sub 2: On this shuttle flight they have taken a variety of toys, such as a slinky, a yo-yo, a wind-up mouse, etc. They are planning to play with these and make a film for educational purposes.

(JME) Whooshcomm sub 3: NASA still claims that Senator Garn was chosen solely based on his qualifications, and not because he is chairman of the subcommittee in charge of NASA's appropriations.

(RvdH) Whooshcomm sub 4: It didn't blow up on the pad. (Applause.)

(BPS) Whooshcomm sub 5: They were an hour late because there was a cargo ship in the area where the boosters were going to fall.

(KM) Pseudo-Analogcomm: The people who do the Analytical Laboratory, which appears in June but chronicles all the things that happened in 1984, at least in this issue are sort of confused by the fact that there aren't a lot of women writers writing for Analog.

Ken suggested that this had something to do with the fact that their stories are often known as "rivets." Janice suggested that women had better taste than to write for Analog.

(JME) Flamecomm: In the first Confederation progress report, there's a little ad from a Libertarian fanzine which lists authors who are Libertarians or anarchists or "at least have not denied being so." This list includes such "well-known" Libertarians as Ursula LeGuin, who has said that she doesn't believe in easy answers like the Libertarian SF writers do. Out of a list of 15 names, about 5 had asterisks, which meant "confirmed." In other words, they've written to all of these people and they're going to use their names until they're told not to.

Janice said that Ursula LeGuin doesn't consider herself any kind of "ist" or "ian."

(SSDT) Pseudo-Panthercomm: We got the new Pinkdex, but it's deformed. Spencer put number signs in front of all of the numbers in series.

(BPS) Moocomm: Arguably the finest science fiction movie ever made, arguably one of the best movies ever made, tonight at 7 and 10 in 26-100: 2001: A Space Odyssey.

After a medium-length flame on the Sunday LSC movie, Deathtrap, and an accusation against Janice that she gave away the ending, Bill moved to note that Rosebud was his sled.

Phonecomm: Ring. Mass "hello, Adina." (We knew something was up when we heard Janice say "What? You're kidding.") Adina said she heard something on the radio about the Golf being recalled.

(KM) Telzey Amberdon Report: I was in California last week, so there.

\goto{Old Business}

(BPS) This Monday 73 years ago, the Titanic sank. This is also the anniversary of FDR's death.

OBA: um, us, uv, ur.

\goto{New Business}

(MJG) I got a new computer- a 512K Mac.

Janice postponed this discussion until after the meeting.

(BPS) Minicult: Dr. Who will return in 1986. See the attached form letter.

Commented Janice: "Aw damn."

(Dan) Minicult: In Canada, The Inuvik Drum, a weekly newspaper, awards a golden shovel every year to the driver who drives off the road and into a ditch more than anyone else. See attached article.

(JME) Minicult: You may have heard a couple of weeks ago about a man who was flying from Germany to Oakland, CA and was to change planes in Los Angeles. They announced the flight for Auckland, New Zealand, onto which he got. Aside from the fact that the airline flew him back and he's been appearing on lots of talk shows, the movie rights to his story were bought for 25,000.

Exclaimed Robert, "What the hell kind of a movie is that?"

People then started to exchange stories about other people getting on wrong planes. Ken said that one person who was going to New York ended up in Los Angeles instead and didn't realize this for about a week. Janice told a story about a man who, while on his way to Rome, got off the plane in New York instead. He noticed that there were lots of people speaking English, but thought that they were all tourists and that the street signs were also for the tourists' convenience. When he went up to a policeman, the policeman just happened to speak Italian. Eventually, after trying to speak to some other policemen, he was told that he wasn't in Rome but in New York. He wasn't convinced and was finally put back on a plane to San Francisco. (Note: because Tarl ran out of tape during this story, part of it was missed.)

(BPS) Minicult: The Ringling Brothers and Barnum and Bailey Circus is trying to foist off as a unicorn an animal which looks like a goat with a horn sticking out of its forehead.

Bill couldn't think of any appropriate motions, except to point out that the circus sucks. Much flaming on circuses and unicorns and egresses. It was noted during random flaming that the Masters of the Universe movie is out and that the Care Bears film was among the top ten grossing films last week.

(BPS) Minicult: Someone is making a movie of Enemy Mine, starring Lou Gosset Jr. as the alien astronaut. Also, flaming about movies.

(BPS) Minicult: George Lucas hasn't decided yet whether there will be a 4th Star Wars film; in September there will be two Star Wars-based Saturday morning cartoons. Pre-production has begun on the 3rd Indy Jones movie, and Lucas and Jim Henson are producing Labyrinth for Tri-Star, starting production soon.

Adam said that the sequel to Road Warrior has finished filming, but they haven't decided whether to call it Road Warrior II or Mad Max III. Janice suggested "Road Max."

(JME) In Walter Scott's Personalities on Parade, someone wrote in and asked if it was true that Steven Spielberg kept his appearance secret so as to avoid being kidnapped. The answer was no, and Walter Scott published a picture.

Miller motion. 4 or 3-8-6 or 7 +Spehn. Fails.

Miller motion. 9 or 10-7 or 8-5 or 6 +Spehn. Passes.

\vspace{12pt}

\noindent
Meeting adjourned.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}