\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 30, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (8/9/85) read and corrected.

KM: Move to approve the minutes as breaded. Passes 10-8-0 +Spehn.

\goto{Committee Reports}

BPS: Jourcomm, with fanfare: We have a TZ 36! Only a dollar apiece.

DSK: Moocomm: Buckaroo Banzai comes to Reg Day. Tron next Friday.

RvdH: Moocomm: ZBT is showing rush movies- Buckaroo Banzai, Repo Man, The Terminator, and Road Warrior. They must be looking for violent freshmen.

Y: Moocomm: Off the Wall is showing Amphibianman, a shlock movie made from a Russian propaganda novel.

BPS: Fweekcomm: The freshman picnic is taking place now, but indoors. Last year when it wasn't raining, I was the only person in the Library at this time.

ATS: Fweekcomm: Sign up for lots of hours on the R/O week schedule.

SSDT: Atomcomm: Boston Edison's ads show the "Oilybeest" getting wiped out by alternative power sources, but they neglected to include nuclear on the grounds that there's no way to show it. Article attached.

BPS: Son-of-Famous-Authorcomm: Harlan Ellison somehow got the impression that my father and I have reconciled, and said so in his latest flamethrower.

KM: Pseudo-People's Albanian Embassy: I saw a hack software licensing agreement involving a company from Albania.

Flaming follows until Andy starts complaining, thereby bringing torrents of abuse upon himself. Just as the argument reaches its peak, Robert Wiener opens his briefcase, takes out a Radio Shack electronic ray gun, and starts zapping away at the Skinner. This has no effect on Andy, but manages to stop everyone else from flaming at him.

\goto{Old Business}

JME: This is so old the newspaper's turning yellow. Officer Obie of the Alice's Restaurant song and movie has retired as police chief of Stockbridge, MA. Article attached.

RvdH: Real Genius was quite good. They actually researched their topic and setting. They copied a Cal Tech dorm right down to the graffiti.

JME: A movie from four years ago is finally being released. UFOria, with Harry Dean Stanton, is about born-again Christians who believe in flying saucers.

SSDT: According to GF, Carl Hylin came in on 8/19 and bought a new membership and a t-shirt.

OBA: usual stuff, sold.

\goto{New Business}

JME: Minicult: The heavy metal group Dio brings us the Middle Ages, complete with laser-dueling knights. New weapons for the SCA? Article attached.

Y: Minicult: An actor trying to deliver a Rambogram wandered into City Hall somewhere and had most of the local SWAT team come after him.

JME: Minicult: The Kenyan Brewing Company switched bottle colors at the same time the government started a birth control campaign. Naturally, people got suspicious, and sales plummeted.

JME: Minicult: A Florida man tried to surprise his girlfriend by delivering flowers while disguised with a paper bag. He got arrested and may even be guilty of something, since a law aimed at the KKK forbids people over 16 from wearing hoods when on other people's property.

JME: Here's a boring Glob report on the Creation Convention held at the Sheraton.

Y: USA Today seems to have confused Dr. Who with Ronald Reagan. It has the good doctor eating jelly bellies instead of jelly babies. Attached.

BPS: Public service announcement- rumors that Spike MacPhee is closing are WRONG. Please help quell them. Flyer attached.

Y: Move to commend the meeting for degenerating into chaos.

ATS: Fine, but that doesn't help us any.

SLP: Move to commend Ken for wearing a banana colored shirt. As Janice wails "Oh, that's so boring!" Mr. Fusion gets his cover flap caught in his slide tray and produces some very loud raspberries. Everyone seconds Mr. Fusion's opinion of the motion, and it dies.

A Miller motion fails and the second one passes by Skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}