\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 12, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (7/5/85) read and corrected.

ATS: Move to approve the minutes as emanating electromagnetic radiation at a wavelength of approximately 6500 angstroms. Passes billions and billions-merely millions and millions-3 +Spehn.

\goto{Committee Reports}

ATS: Shoulda-seen-it-comingcomm: The return of the Real Thing, to be reintroduced as Coke Classic, making a total of six kinds of Coke. Also, both Coke and Pepsi spacecans are on the shuttle, which was scheduled to launch at 1630. Coca-Cola spent 250,000 developing their spacecan, and Pepsi spent 14,000,000.

Flaming about Coke as a stomach soothant.

JME: Gavelcomm: Gavels have made it to the status of high art. Robert Harmon has an exhibit of wrench sculpture at Bromfield Gallery. Article attached.

SLP: LHE Report: Income last month was 1237.95 (Finboard grant finally came in), expenditures 485.39, profit 752.56, equity 5489.25.

BPS: Jourcomm: I got another book review. That makes four. More stuff, folks!

RvdH: Moocomm: Theater of Blood and The Raven tonight. Also, The Lift is a really great Dutch movie about an elevator system that runs riot when a lightning bolt reprograms its Japanese brain. They actually took this theme and did a good job with it.

BPS: Moocomm: More people think Back to the Future is really great, specifically everyone who's seen it.

SSDT: Moocomm: Mad Max Beyond Thunderdome stinks. About half an hour in, he runs into a tribe of lost children and spends the rest of the movie babysitting.

BPS: Moocomm: Explorers opens tonight. Janice says it was written by a clerk in an SF bookstore, probably Change of Hobbit.

LAK: Moocomm: Last night there was a preview of Weird Science, in which two high school boys invent a girl.

JME: Again, dangerous Moocomm: Back to the Future is doing well for its star, Michael J. Fox. It's being used to help advertise him in a TV movie.

Connie Hirsch: Moocomm: Cocoon was good, not corny at all.

ATS: Moocomm: I hear Silverado is pretty good, but haven't seen it.

JME: Official Second: Waldenbooks has an SF club that costs nothing to join and gives some discounts. Spike's is preferable, but if you're trapped in some foreign city...

\goto{Old Business}

Motion to name our new copier Mr. Fusion is untabled and passes more than enough-anybody who wants to leave-3 +Spehn. Andy states that he wants no more filthy invasions by Robert's Rules.

ATS: We got a boring letter from Tim Huckelbery, and a cute Peanuts comic strip (attached).

OBA: usual garbage. Sold.

\goto{New Business}

ATS: Minicult: Reagan's helping a boy get money for a kidney transplant. A senior aid said "This is America, and we don't allow six-year-olds to die." Janice suggested that he meant to say "Republican six-year-olds."

BPS: Minicult: An Atlanta disc jockey locked himself in the control room and played nothing but Bob Seger's Old Time Rock and Roll for three days. Attached.

ATS: The kicksteps are in.

KM: Move to commend the society for buying school bus colored kicksteps. Dies for lack of a second.

BPS: Minicult: Miami golfers are certainly dedicated. They kept right on playing even when the clubhouse caught fire and smoke and firehoses were all over the course. Article attached.

ATS: Minicult: Andy starts to read a hack memo concerning Institute employees who die on the job, but nobody wants to listen to it because it's been around for years. Memo attached.

BPS: Minicult: A suicidal man stole a plane and threatened to crash it into the restaurant where his wife worked. An FAA official said "He wasn't having a very rational day." Article attached.

CH: They got the voice recorder from the Air India disaster, and now they got the flight data recorder from a depth of 6700 feet using a robot submersible.

Rabbits is sung for one verse, then the effort collapses.

JME: Minicult: I forget the details. Never mind.

ATS: Move to name our pretty banana-colored kicksteps Huey, Dewey, and Louie, after the robots in Silent Running. Passes enough-no one-

Suddenly, Janice remembers her Minicult, and voting is suspended!

JME: Minicult: A step in some direction for equality of the sexes- Mayor Koch got described as a sixty-year-old bachelor in a Glob photo caption.

BPS: Minicult: The Playboy/Penthouse race to publish the Madonna pictures turned out to be a dead heat.

ATS: End of time warp! Motion passes enough-DB, in other words, no one-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}