\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 8, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding. It was noted that this was the last meeting before Boskone.

Minutes of the previous meeting read and corrected.

(JAH) Move to approve the minutes as vice-versa. Seconded. Albanian motion. Motion passes for-against-chickens +Spehn.

(Janice accidentally knocks the phone into the garbage can; someone makes a comment about something being phone-y. He was Albanianed and Fingered.)

\goto{Committee Reports}

(AA) There was an inventory. Thanks to all those who showed up, and the rest of you suck.

Janice stated that we now have a new Pete Smoot: Susan Tucker. Susan denied that she was Pete Smoot.

(JME) Boscomm: There will be a meeting for people working the MITSFS huckster's table. The meeting will be here in the Library tomorrow at 3. It's really important!

(AbM for ATS) Boscomm: People are urged to sign up for huckster's table hours, particularly the hours from 4 to 6 on Friday. Also, we received a letter from Andy Eisenman asking student activities to suggest changes to the 4th floor.

(JME) Skinner Report: We have a new typewriter- an IBM, but not a selectric. Boscomm: Boskone approved our request for party supplies, so we'll have at least a couple cases of coke. There will be a MITSFS meeting at the MITSFS room at 1700 SST; the conversion to local time has not been decided.

(GF) Pseudo-Moocomm: Dune has closed everywhere except for Salem.

(BPS) Sitcomm: Overdrawn at the Memory Bank was incoherent. Presumably, John Varley is not pleased.

(JME) Bonzocomm: Reagan, the same day that he twice cited Luke to support growing defense budgets, mentioned that among the religious symbols he could see from the White House celebrating Passover was a giant menorah.

(GF) NESFAcomm: NESFA bought a clubhouse. The phone number is 92-NESFA.

Motion to condemn the NESFA clubhouse except for the telephone. Passes by Skinnerial decree.

(BPS) Sitcomm: Last week on OtherWorld, things were livened up a bit by the presence of Mark Leonard, who got to play his typical Romulan-like role.

(JME) Moocomm: Raiders of the Lost Ark is tomorrow night. HarrisonFordcomm: The new movie with Harrison Ford called Witness is causing a furor among the Amish because they are afraid that it will lead to increased tourism.

(BPS) Move to commend the Amish for not wanting tourists. Passes some-fewer-more than fewer but less than some +Spehn.

(BPS) Academycomm: 2010 was nominated for makeup, visual effects, sound, costume design, art direction, Greystoke for costume design, Ralph Richardson (posthumously) for best supporting actor and Jeff Bridges for best actor in Starman, and Dune for best sound. Does anyone know if there has ever been anyone who's received an award for best actor, etc. for a non-human character?

Some flaming. People start singing Rabbits, and Janice yells "I don't hear you; we're still in Committee Reports." JME threatens Adam with the gavel, and he stops singing, but then Ken says Miller motion, followed quickly with a second by Adina. Janice again growls "I don't hear you." Janice calls for Old Business before she destroys Robert's head with a gavel.

\goto{Old Business}

(BPS) 7 years ago today, Boston was digging out from the Blizzard of '78.

(JME) The Telzey and the Skinner's car has been named the Excelsior after the ship in STrek III that went putt-putt-putt.

(JH) The scavenger hunt people are still looking for objects.

OBA: um, us, ur, uv. (And that's the order it went in.)

\goto{New Business}

People immediately begin to sing Rabbits and make Miller motions. Janice tries to battle the confusion.

(BPS) Minicult: Only one person has used their MITSFS membership at Spike's.

Robert says he'll have a sign up RSN, and it is pointed out to him that the discount is only good for February.

(JME) Minicult: Documents from WWII indicate that during the Roosevelt administration, a committee proposed to resettle refugees on other planets, namely Mars and Venus.

(GF) A Greek Orthodox nun smuggled 6000 bees into Kenya under her hat but was subsequently caught when she took the bees to the Ministry of Agriculture to have them examined.

(JME) We have a handle on the money drawer due to the effort of BPS. Also, we seem to be missing Time Enough for Love again.

Bill donated a book on the whereabouts of the antichrist. Albanian motion on Bill for something. Much flaming. Janice asks for help.

Move to buy the Telzey a pink skirt; passes overwhelmingly too many-nobody, not even the Telzey-0 +Spehn.

(Shawn) Jourcomm: resigns. Otherwise, the next TZ will be out first month of summer.

(SSDT) I won't be Pete Smoot, I'll replace him.

(AA) Miller motion. Motion fails 6-numerous people-clucks +Spehn.

(AbM) Move to commend AA for her banana-colored shirt. Declared boring. Passes.

\vspace{12pt}

\noindent
Meeting adjourned.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}