\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Sunday, February 17, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Note: Prior to the start of the meeting, the MITSFS room at Boskone (room 1332 in the Copley Marriott) was declared the Library, and the occupants were informed of the time warp; Janice made lots of whooshing sounds and swung the gavel to and fro. As the gavel block was not present, an ashtray was used instead; when the gavel was pounded on the ashtray to signal the start of the meeting, the ashtray released a high-pitched ring, and various people made exclamatory sounds. Merryl noted that it (the ashtray, not the gavel) didn't even chip, and Adina made a motion to commend the ashtray. This was seconded and passed pretty unanimously by Skinnerial decree.

The Onseck read the minutes of the previous meeting (2/8/85); there were various interruptions due to people talking about stuff like parties. Also, there were various comments about the Onseck's pronunciation of certain words. Finally, Janice made a bad pun about now being able to handle the money drawer, but no one had the audacity to make an Albanian motion.

(JME) Motion to approve the minutes as unpronounceable.

Robert Sacks claimed that there was an error in the minutes, as NESFA hadn't bought a clubhouse. It was explained to him that the minutes are supposed to be a record of what happened at any particular meeting, not necessarily to be a reflection of reality.

Motion seconded. BPS: "Move to approve the minutes as unpronounceable posthumously;" seconded. Passes many many many-few few few-even fewer +Spehn.

When Janice tried to strike the ashtray with the gavel, she found RvdH's hand there and said "Get off the ashtray, dummy!"

Adina warned that if we weren't quieter, we would be shut down.

\goto{Committee Reports}

(MJG) Vice Report: The Vice has a new whip; it's a cat-o-five-tails.

RvdH noted that the whip didn't have blood on the ends, and Adina and Merryl asked him if he was offering to donate; Robert didn't reply.

(KM) Telzey Report: The Excelsior did not live up to its name, as it performed flawlessly (said Janice: "It outdid itself") and carried lots of stuff over from MIT.

(KM) Pseudo-NESFAcomm: They did not get a clubhouse, as the option on the building was taken by someone else. This is apparently bad because it means that NESFA is still out on the streets.

(JME) Boscomm: The party is tonight, but NESFA has managed to screw us over TWICE. First, they announced that the party was last night, and then they announced that it was tonight at 9 instead of at 8. The other Boscomm report is that we won the scavenger hunt. Many thanks to the many people who helped. We had 90.5 points out of 100, with the next highest score being 64.15. We were awarded not only lots and lots of ribbons, but also two very tasty boxes of chocolate (the chocolates were tasty too!), and there is one box currently left, for after the meeting.

(Robert Sacks) New York Report: I regret to announce the demise of the New York in '89 bid. They are returning checks and would like to find a Mr. Phil Hutchinson of Bedford, MA.

(Robert Sacks) Errata Report, aka Randomcomm: The MIT Report of the Treasurer is in error in listing the MITSFS endowment fund as having 3144.00; as of Friday, they're off by 1000 dollars. (Much applause.) Said Janice, "Give the man a piece of chocolate or something!"

(RvdH) Boredcomm: I put the sign up for Spike's. Someone rather obnoxiously commented "Well, it's about time."

(JME) Boscomm: The huckster's table did really well, even if we didn't move many t-shirts; we made somewhere between 100 and 200 dollars. Ken M. observed "There's at least 150 dollars worth of cash that wasn't there when we started."

(SSDT) Lucascomm: George Lucas will design a ride for Disney based on Star Wars. Janice fueled the rumors by saying that she heard they were going to revamp Tomorrowland entirely and make it Lucasland.

(KM) Frethcomm: 1) Dark Tangent will be coming out; if you are a subscriber to the Dark Tangent series, they will mail you a revised number 1. (At this point during the meeting, certain people- who shall remain unnamed- started complaining that NESFA spelled their names wrong, and this pointless flaming garbled Ken's report.) 2) Ken is going to try to get Freth (??) on Project Athena.

(JME) NESFAsucks! Report: (Much flaming, before the report is even issued.) They spelled my name, both Roberts' names (this presumably means both the Roberts, not both of Robert's names), and Ellen Kranzer's name wrong. Said Ellen, "They join the large number of publications that have not gotten my name right; almost every publication has spelled it wrong." Janice made the observation that the Tech got it right, and Ellen countered that they got it wrong once too. Flaming... flaming... flaming...

(JME) It should be noted that the second place team in the scavenger hunt had 64.15 points.

(KM) Pseudo-Panthercomm: Witter thought that the last batch of returns that we sent him was really nicely packed and wants it done that way again. Unluckily, AbM didn't remember doing anything special that time.

(JME) Further Pseudo-Panthercomm: The library has a few new acquisitions from the convention; we got the Boskone book (Late Knight Edition), as well as a really bad book from Houghton-Mifflin, but we got it because they were selling it for 5 dollars instead of the list price of 15.95- it's called The Secret. (Ken said that the author was described as being a really great TV writer. There were lots of groans.) Also, Ben Bova was giving books away- his new book Orion. MITSFS got a copy because Herb didn't want to read the one that he got.

It should be noted, with regard to the saga of Houghton-Mifflin, that they did eventually get a table. Ken commented that they were really trying to emphasize SF- they've even started to subscribe to Locus. Robert Sacks was wondering why he saw both a man and a woman wandering around the convention with nametags that said "Houghton Mifflin." It was explained that they bought a set of memberships and have been passing them around their workers. Ken thought that they had a great brunch on Saturday.

Janice called for any more committee reports. "Going once, going twice," and as the gavel hit the block someone said "Sold! To the girl in the funny hat."

\goto{Old Business}

(Robert Sacks) Ex-Skinner Report: Tim Huckelbery won a ribbon for the most illegible pre-registration letter transferring his membership to someone else. It was written in silver ink on green paper on the back of an old LSC poster. The "most illegible" award was silver ink on silver. He was in California and so was unable to accept the award in person.

(JME) More Old Business: The infamous Librarian A.R. Lewis bought a t-shirt from us today. Someone indicated that the freshmen didn't know who he was and didn't ask him if he was still making passes at Wisowaty and being repulsed.

Adam made the innocent comment "Gee, isn't that one of the usual motions?" and Janice then explained "Yes, that IS the usual motion: 'Lewis made a pass at Wisowaty and was repulsed; move to condemn the Librarian.' That's the one that moves us into new business." Added Bill: "That, and move to note that Bruce Miller is still skiing in Colorado." Janice said that was part of the Old Business Algol, but that didn't keep Ken M. from commenting "...and condemn Wayne Brells for his sex life with a bicycle." This led Janice to say "...and move to give Tom Galloway a better gag. That's the most recent edition."

(CC) Another Ex-Skinner Report: THE Skinner (as in L. Court) showed up in the Library last weekend and spent some time around with his wife and daughter, as his daughter is currently applying to MIT. (Upon hearing this, the people in the room groaned, but they all went "oohhhh" upon learning that he was a son named L. Court. Said Janice: "We'll get a dynasty if we're not careful.")

Adam observed that his daughter seemed somewhat fazed by the fact that every time someone would walk into the Library and was told who was visiting, their reaction would be "Wow, you're L. Court Skinner?!" As Janice noted: "Hey, he was beloved, otherwise why would I be wearing his name?" Robert Sacks said (rather flippantly), "Do you want an answer for that?" Replied Ken, "Remember, the Telzey is also pledged to defend the honor of the Skinner." Bill said, in a falsetto, "That's more than she ever did."

(JAH) I made use of my 15 percent discount at Spike's last week, and he implied that if we made sufficient use of the discount, he would extend it, perhaps permanently.

(Paul M.) Elise Levinson was in town and she bought two t-shirts. Exclaimed Adina, "Wow!"

There then occurred some flaming about who was a keyholder and who wasn't, and finally Janice said: "It doesn't matter. I declare her an ex-keyholder."

(AA) REAL Ex-Keyholder Report: Warren Dew was around; however, he did not buy a t-shirt. Some "aw"s.

Janice called for any more old business, and then said:

Old Business Algol. Robert Sacks chimed in: Usual Motion, and various people replied Usual Second. Some rather obnoxious people yelled "Usual discussion," Janice changed that to usual second with a t-shirt, and then started to explain why she changed this, but then changed her mind. Someone observed "Unusual discussion," and Janice complained "You people are obtuse, that's all I have to say." At this point, Robert Sacks and someone else made bad puns about people being "acute" (sic). In the confusion that followed, there were about a dozen Albanian motions made. After things quieted down a little, Bill asked, possibly rhetorically, "Can we Albanian people who gave us large amounts of money?" but Merryl replied "Yeah, why not." After more confused (and parallel) flaming, Janice decided that the two puns collided in midair and wiped each other out so that neither of them was heard. More flaming, until Janice rather forcefully said "The usual vote and the usual result." Everything seemed fine until Merryl chimed in with "What about the usual debate?" This started more flaming until Janice called for...

\goto{New Business}

(JME) George Flynn sort of went over to the other side by providing one of the competing scavenger hunt teams with a Tom Swiftie: "'Oh no, my arm is caught in the airlock,' said Tom off-handedly." Janice said that it got a bigger groan at the awards ceremony. It was noted that George Flynn DID help us with a number of items. Jenny wanted to know if we could Albanian motion him in absentia, but it was loudly pointed out to her that George Flynn IS the People's Albanian Embassy. Susan Tucker wanted to know if we could Albanian Tom Swift.

(JME) Time warp for People's Albanian Embassy: There's an Atlantic Monthly in the Skinner and Telzey's hotel room for some reason, and it has a very long and serious article on Albania; it's about what'll happen when Hoja dies and the Russians try to take over Albania.

Bill asks, again apparently rhetorically, "Where will the Russians find suicide troops willing to enter Albania?" Robert van der Heide replied "They'll draft them," but Robert Sacks said "Afghanistan." Someone indicated that Albania doesn't border the Russian Empire (sic), and someone else remarked "It will now."

After twice calling for more new business, Bill said "It should be noted that the folks from UMass in the scavenger hunt pulled a very nice prop. One of the items was a creature that thrives on quadri-triticale; they came up with two: a tribble and a human being."

(KM) Joe Haldeman is writing a book that will be set (as in "setting" and not "typesetting") in the MIT-Cambridge area; it started as an exercise in his writing class. The main character, who's really a spy, is going undercover as an MIT professor of linguistics. It was noted that it is NOT supposed to be Chomsky (the character is in semiotics, not syntax).

Robert Sacks said that he was speaking with one of the deans at MIT (Dean Hannon), namely the person responsible for getting the writing program to bring in a professor of science fiction. Robert thought that, considering the dean is being shipped off to become the head of some other university (Vice-Chancellor of [illegible] University), MITSFS should write him a letter of thanks. People objected to this on the grounds that we didn't really know this person, and that, as Janice said, "Well, I think that's appreciation enough for anyone."

(RvdH) Minicult: The Boston Glob technology section on Monday had a report from China about the discovery of some sort of 4-foot-tall hairy-all-over semi-human ape man.

When asked the question "Dead or alive?" the reply was "I forgot." This brought much derision. Someone suggested trying to crossbreed with a panda. Robert tried to excuse this report by saying "Minicults are supposed to be strange." Janice's response was "Elevator motion." Adam then asked, "What's that mean, he gets the shaft?" Said Janice, "No, it means everybody surrounds him and then suffocates him."

Janice called for any more new business before she fell asleep. Someone said Miller motion and was chastised by Janice because that was not new business. Adina noted that it had been seconded. People began to sing Rabbits. During the second verse, Adina screamed Miller motion, and someone else screamed out a second, but Janice said, for some unfathomable reason, "I'm enjoying this." For the third verse, the melody switched to Beethoven's 9th. The melody of the fourth verse was unrecognizable. The fifth verse was the normal (unrecognizable) melody.

Janice: "Meeting adjourned. 17N SST." Applause.

\vspace{12pt}

\noindent
It should be noted that the Onseck, in preparing these minutes, attempted to be very detailed. It should also be noted that he will never attempt this again.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}