\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 19, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Janice called to order several times, but Tarl didn't note what she was ordering...

Due to the absence of the Onseck, Janice took it upon herself to read the minutes.

(MTG) Move to approve the minutes as the Miss Spelling of the Year Award. Fails miserably all for-all against-no chickens or other poultry +Spehn.

\goto{Committee Reports}

(Herb) Picnic May 12/elections May 10 in the Spofford Room. The car list is up on the door and invitations will be transmitted RSN.

(JME) Boardcomm has been directed to put a sign on the BULLetin Board and also, while you're at it, Robert, in the Library. "For sure."

(AA) Panthercomm: We received a list from J. Spencer Love that contains a lot of suggestions for Pinkdex. So while we're at it, how about any other suggestions from random people out there in the audience?

(BPS) Jourcomm: We found this real sucker to be the editor of the next TZ. Said the poor soul, "Anything to get out of doing shelves..." Anything??? The deadline is sometime in July, i.e. before R/O week. If you want to read a reserve book, you can, but it must be a review copy that we've recently received, and you must review it. There will be a flyer flown regarding the new TZ; maybe it'll accompany the picnic announcements.

(JME) Pseudo-People's Albanian Embassy: Albania continues to be on the snooze; on Saturday, Albania rejected the condolences of the USSR on the death of Enver Hoxja and said they felt the Soviets were a threat to their existence. Astute international observers speculated that this was meant as a rebuff of the Soviets. Ramese Allia was elected unanimously as the new leader of the People's Wonderful Albanian Free Republic.

Telzey Report: By the Telzey himself- the Golf has been fixed! Well, so much for little golfs.

(SSDT) People's Albanian Embassy: Last week, in our own MITSFS library, an amazing event occurred- Tarl started HEARING Albanian. Some people said that gee, wasn't it lucky that it was ONLY the reading of the minutes that got trashed.

On a related note, an interview with Tarl later in the week revealed that he was considering switching permanently to Albanian if more nasty pointy sharp comments were made about what, in his opinion, is the highlight of the meeting.

Holy Wonder, Batman! Merryl's room was attacked by a jackhammer at 9 in the morning. The reason for this was to knock a little hole in the wall to get at the pipes behind it. Stay tuned, same bat time, same bat channel for more during Old Business (as to why Merryl was going to be up at 9 anyway).

More religious (well, holy, in any case) flaming.

(ATS) Whooshcomm: Due to an unforeseen problem of severe insect infestation, the space shuttle astronauts were forced last week to attach a flyswatter to the end of their robotic arm. They missed the bugs, but did manage to hit a satellite, although that didn't seem to do much either.

(BPS) Whooshcomm sub 2: Well, let's say they hit a bird and blew a tire. No major damage. Landing in Florida.

(ATS) Whooshcomm sub 3: The Atlantis has just been finished, and it's sitting at Cape Kennedy.

(JME) Whooshcomm sub 4: The Glob said that the Synergetic Civilization wants to colonize Mars. They're a bunch of actors and ecologists funded by a Texas millionaire. Apparently some people are taking them seriously.

Phonecomm: Ring. Hi Ken! Hi Bruce... Some rumors about the people who want to go to Mars. "They're sort of like moonies," said Robert. After a small fire, Bill said it's boring too. Ken wished everybody a nice meeting.

(BPS) Moocomm: Clockwork Orange tonight; 2nd Kubrick movie in ONE week. Maybe they'll have a nice print. It was noted that MGM/UA sucks.

(SSDT) SCC movie Saturday: Heavy Metal. (Mixed reaction.)

\goto{Old Business}

Batman continued- a mistaken case of... Big Mac attack. Merryl's 512K Mac was really only a 128K Mac. After a bureaucratic debate (entablature) I finally got the larger Mac.

(JAH) Max Factor part III- the real name of the Mad Max III/Road Warrior II movie is Beyond Thunderdome??? You've got to be kidding...

BPS said something so Janice finger motioned him. Oh well.

(SSDT) A long time ago, I sent a letter to the post office complaining about the timing of their most recent rate hike. They sent me back a REAL LETTER, not a form letter; it was a whole page!

OBA, Robert: usual bull routine. Sold.

\goto{New Business}

(JME) Minicult: Glob- a serious effort is underway to make the rock-n-roll classic Louie Louie the anthem of Washington state. The Whalers, the Kingsmen, and Paul Revere and the Raiders joined a rally to support the adoption of this song. The Glob noted that Louie Louie has enjoyed a cult-like popularity over the years. This report is being changed to Popcult.

Bill moved to note that they're really called the Raiders. Ken noted that Paul Revere is dead. Janice said that the New Jersey state rock song is Born to Run, a song about getting out of New Jersey.

We received a free sample pen with the MITSFS name embossed on it. Asked Janice, "Is it right?" Susan: "It should."

New keyholder aspirant. Lisa: file the duplicate fanzines.

Janice wanted to end the meeting with an interesting motion, but people finally started to sing Rabbits and the pen was commended for having a banana-colored stripe.

\vspace{12pt}

\noindent
Meeting adjourned sometime, somewhere, somehow.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}