\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 1, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

Move to approve the minutes as Wigawaty. Seconded. Passes many, too many to count-2-3 +Spehn. Bill got Albanianed for saying that he thought the vote was "many-many-count."

\goto{Committee Reports}

(JME) Pseudo-Pianocomm: Our phantom Jenny has become solidified and has her key. Herb also has his key.

(AA) Sitcomm: On "Discover: The World of Science," there will be a film clip of the 2.70 contest. Description: "An MIT competition where students design clever devices to compete in a rollicking table-tennis game."

(JME) Barfcomm: It is now possible to get a special collector's edition of Battlefield Earth which includes the soundtrack to the book, composed by L. Ron Hubbard. Price: 225 dollars. The ad claims the value is going up daily.

(JAH) Scavenger Hunt- there's still stuff that people haven't picked up yet, so get it or it'll be auctioned off.

(John Dumas) Pseudo-Moocomm: Wizard of Oz is on TV tonight for the millionth time.

(JME) Moocomm: Last Starfighter is tonight, and Das Boot is tomorrow night. And Jungle Book on Sunday.

(AbM) Boatcomm: Today we sold Avenue Victor Hugo two copies of the 2nd edition Gunslinger for 35 dollars each.

(ATS) LHE Report: for the moment at least, we love the MIT Libraries, as they gave us two checks for 600 dollars instead of just one.

(SLP) Pseudo-People's Albanian Embassy: A real Albanian came in today. Well, second generation. He wanted to know why we had a PAE.

Phonecomm: Ring. It was for RvdH.

(AbM) Missile Command Report: The list of feelthy members has been computerized, and we have 600 books overdue, 79 of which are hardcovers. In addition to the overdue fines, which in most cases are 5 dollars/book, there are about 1600 dollars in fines outstanding. The most feelthy member is Josh Shaine who has 60 dollars and 12 books outstanding.

(AA) Panthercomm: Del Rey sent us lots of freebies, so we now have circulating paperbacks of Julian May's four book series.

\goto{Old Business}

Janice asked for any comprehensible old business, and Bill (who was Albanianed) offered his opinion. Whatever Bill said was seconded and passed by SD.

There was lots of flaming.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: from the Glob of this past week- beaver barbecue.

(MJG) We need a time warp.

(JME) Time warp for the vice...

STrekcomm: George Takei was here. He signed a copy of his book, which is on SR, and one of the scripts. He said he'd tell his friends about the library and maybe they'd send us copies of the STrek movie scripts.

Janice desperately calls for new business.

KRJ said "move to commend March for arriving," and someone added "with a banana." After the confusion died down, RvdH said "move to commend March for being a good month for eating bananas in." Seconded by acclamation.

Passes everybody who counts-a bunch of people who don't count and a snake-nobody +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}