\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 3, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected, and the Onseck warned George Flynn, "George, you don't want to try to proofread these minutes."

(BPS) Move to approve the minutes as deceased.

It was noted that death is a much better way of silencing people than an Albanian motion is. Passes several-several fewer-several even fewer +Spehn.

\goto{Committee Reports}

(JME) Skinner Report: We have an apartment; it's in Malden. It has two bedrooms, one and a half bathrooms, and a little kitchen, as well as carpeting and air conditioning and a dishwasher and a disposal; it's 650/month, going up to 700 in September.

Adina noted that Janice just described Adina's apartment.

(JME) Electioncomm: I need a volunteer to carry the gavel block to the Spofford.

This would be Atomcomm; not surprisingly, Adam volunteered. It was noted that he will attempt to rename the committee Adamcomm.

(KM) Foodcomm: Forbidden Planet will donate the proceeds from the latest Harlan Ellison edited anthology, Medea, to the Ethiopian African relief fund. Hopefully he won't sing either.

(Dan) Picniccomm: Rain space for the picnic is the Mezzanine Lounge (downstairs).

(ATS) LHE Report: Equity level 5258.30, profit of 68.42. We cannot figure out where the profit is coming from. Rita Lee will give us last year's finboard money next week.

(BPS) Jourcomm: So far I've gotten ONE whole submission. C'mon people!

(JAH) Pseudo-Jourcomm: A person came into the library earlier today and wanted to know if she would be allowed to contribute to TZ.

(JME) Whooshcomm: On Monday, an experiment to measure urine production in zero g sort of leaked, so the astronauts spent a lot of time chasing droplets around with paper towels. On Tuesday this was compounded by the leakage of "foul smelling food and feces" from rat cages, forcing the astronauts to wear surgical masks until they cleaned up the mess.

(BPS) Whooshcomm sub 2: They also had problems with the monkeys, including one of them getting space-sick; NASA has admitted that the zero-gee toilet idea will have to go back to the drawing board.

(JME) Whooshcomm sub 3: NASA spokesmen said that the air filters in the shuttle should eventually get the smell out. Well, stay away from the Challenger for a while.

(JME) Pseudo-Pianocomm: Our proto-keyholders will become real keyholders as soon as they get their real-keyholder training. They did the inventory, which was a heroic feat, and they all should be congratulated for it. (Applause.)

(BPS) Jourcomm (again): With regards to the state of the MITSFS report that will be in the next TZ, there is now a sheet posted for ideas about what to include in this report.

(GF) Whatever-committee-covers-live-theatre: On June 18th the Boston Shakespeare Company will present the world premiere of a multimedia adaptation of Philip K. Dick's "For My Tears, The Policeman Said." (Audible gasps heard from the people present.) It's a novel about solipsism. George suggested that perhaps it's a one-man show.

(BPS) Rubbercomm: A new toy for MITSFS- a rubber stamp that says "Withdrawn from the MITSFS Library." I have here some Church of Scientology literature; I'm ready to break this in. Robert (vdH) suggested that in that case the stamp should say rejected. The stamp is a donation from Bill. (Applause.)

Janice said that there weren't any Moocomms, but Adam said that Fanny and Alexander was moderately strange and that it definitely had fantastical elements in it.

\goto{Old Business}

A letter from Tim Huckelbery is read. Letter attached.

A letter from George Phillies is read. Letter attached.

(JAH) More old business- while going through A Pliocene Companion by Julian May there was a reference to a limited-edition gilt-bound book with drawings by Steve Fabian.

OBA, usual routine...

\goto{New Business}

(JAH) The new Zelazny novel is out in hardcover. The cover art is ridiculous.

(JME) We have also received Cathouse: Dune.

(GF) Some people are making a movie called Transylvania 6-5000 about werewolves, and they want to call a werewolf Lawrence Talbot, but Universal still owns the name so instead they're going to have a werewolf named Lawrence Malbot. (Ken M. thought that they should be awarded the Mrs. Fridby award.) Also, yesterday, consumer groups, in attacking secretary of labor William Brock, said that they were surprised he turned to the dark side of the force so quickly. The science fictionalization of political terms continues.

(JME) Minicult: There's some famous British explorer by the name of George who sailed down the Washington state coast in a ship named Discovery mapping it and left out the area where this town currently is. On the anniversary of when he passed by, the townspeople usually wade out into the water and yell "Hey, George!" This year they found someone to yell back. There's a British ship called the HMS Discovery sitting in London, and they sent the crew some money, told them to buy the beverage of their choice, and to please yell back at the appropriate time.

(HAM) On Compuserv's SF/Fantasy forum this Saturday, the guest author will be Steven Brust. On June 22, live from London, they'll be having Tanith Lee.

(JAH) Brustcomm sub 2: To Reign in Hell is out in paperback and has some very nice cover art for a change.

(BPS) Minicult: The Hugo nominations have been done. Best Novel: Neuromancer (William Gibson), Job: A Comedy of Justice (Heinlein), Integral Tree (Niven), Emergence (David R. Palmer), and The Peace War (Vernor Vinge). Dramatic Presentation: Dune, Ghostbusters, Last Starfighter, Trek 3, 2010.

Janice admonished Robert not to drip on the floor because roaches like honey.

Janice said that she read in a NY newspaper that the following conversation was overheard on a bus: She- Your place or mine? He- I don't know. She- Well, I just got my place fumigated, and I've only seen about 2 or 3 roaches since then. He- Your place.

(BPS) Minicult: Hill Street Blues will have a new episode next week. Watch Channel 10.

(JME) Move to commend Ronald Reagan for starting a banana war against Nicaragua. Passes many many many-a lot fewer-even fewer +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}