\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 22, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Due to the absence of the Onseck, the Skinner read the (partial) minutes of the last meeting. (Note: when informed of the terrible illness that the Onseck bravely suffered through, the members of the MITSFS expressed their deepest feelings concerning his health.)

( ) Move to approve the minutes as incomplete. Motion failed because it was too obvious.

(BPS) Move to approve the minutes as truncated. Seconded. Amended to "rounded down." Seconded. Chickens 3.2-pi-many many many +Spehn.

\goto{Committee Reports}

(JAH) Sitcomm: Star Trek II on TV Sunday night.

BPS, in a friendly addition to the Sitcomm report, noted that Kirstie Alley appears twice this week on TV in non-human roles; supposedly, the other (non-STrek) role is that of a Playboy bunny in "A Bunny's Tale," based on a magazine article by Gloria Steinem.

(JME) Pseudo-Pianocomm: We have a new phantom- Jenny Hawthorne.

This report was followed by a diatribe by Janice against strange keyholder marks, particularly Elvish runes. This had just ended when Herb commented "It would rune (sic) everything." Albanian motion passed by Skinnerial decree.

(JME) Skinner Report: Finboard SUCKS! They gave us a notice today that our budget must be turned in by 5 PM Monday.

Random flaming for a while...

(JME) Final Boscomm report- the party was, and went well despite NESFA; we have hung one of the scavenger hunt ribbons from the ceiling of the Library, and anyone who wants their stuff back from the scavenger hunt can beat on Jenny for it. Also, Robert K. Wiener is looking for a pair of gloves that he left in the MITSFS suite Sunday night.

(KM) Preemptive Boscomm number XXIII report- Leslie Turek has discussed with a number of MITSFS people the possibility of having MITSFS run next year's scavenger hunt.

Much paranoid flaming on NESFA and contamination by NESFA, among other things...

(MJG) Vice Report: I'm here.

(GF) People's Albanian Embassy: Regarding Coach, the person from Cheers who sang a silly song about Albania- a few weeks later he dropped dead. The people of Albania deny any responsibility for this. Janice suggested changing the name of the motion.

(BPS) Sitcomm sub 2: In next week's TV Guide, a review of Street Hawk appears, just in time to coincide with ABC's announcement of its cancellation. However, a Glob article indicates that ABC is threatening to bring back Street Hawk later in the year.

George F. thought that the show was a good thing, as it would reduce the population of dumb people by encouraging the riding of motorcycles.

(JME) And speaking of dumb people, not meaning to be callous, but an MIT graduate student died after falling into the Charles last night as he was walking across it (it was frozen). Evolution in action!

\goto{Old Business}

(BPS) Next Thursday night on NBC: the pilot episode of Hill Street Blues. Be there (aloha). Lots of gasps, wows, etc.

(JME) The Excelsior continued to perform flawlessly, as it brought everything back to the MITSFS. Also, we had lots of old MITSFS members show up at the party, the only really notable one being Leslie Turek; Tony Lewis bought a t-shirt.

Ken chided the freshmen for not recognizing him, but Jenny said that she saw him at the party and asked him if he was still making passes at Wisowaty, and he replied "No, she's married; why would I do that?" Merryl then queried him as to whether or not he was still being repulsed, and he apparently was still confused and didn't get it. Ken said, "He didn't get them either; that's why he was being repulsed." Janice made a Lithuanian motion, but then there was a Phonecomm report; it was Ken Johnson. There was some rather confused flaming, and then a motion from Janice to condemn Robert for bringing his private jokes out of the closet. Seconded. Passed by Skinnerial decree.

Adina suggested that Robert Sacks be commended for giving uup another 1000 dollars. He was appropriately commended.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: For any of you who are interested, there has now been posted information on how you can order your very own quartz clock with a picture of Jesus on it. The advertisers call it the Holy Clock.

(Someone indiscreetly asked what happened to the Old Business Algol. Janice said "I punted it. We forgot. I'm sorry. Aaargh!" There was a quick time warp.)

(BPS) Minicult: NBC is negotiating with John Williams to compose new themes for the NBC Nightly News and the Today Show. Also, according to Tuesday's Glob, Mickey Mouse began his first visit to China; he will be honored with a traditional Peking duck dinner.

Andy noted that a few days ago, the voice of Donald Duck died.

(BPS) Another Minicult: After someone jump-started a car that was in reverse, it started to go backwards in circles. After half an hour, a dump truck was moved into the path of the car, and the car stopped. The car was totaled, but the truck was essentially undamaged. See attached article.

(JME) We have photographs of the costume party people at Boskone.

Miller motion. Seconded. People start to sing Rabbits. Fails 8 or 9-10 or 11-an ouch, a foot, and some rabbits +Spehn.

Miller motion. Passes everybody-nobody who counts, just Herb-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}