\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 11, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (12/14/84) and Onseck both absent.

\goto{Committee Reports}

(Punchcard memo) LHE Report: equity 5251.99, profit 531.92.

(BPS) Motion to condemn Andy for being too cheap to put in the extra penny and get a round number. Passes 72-2-1 +Spehn.

(JME) People's Albanian Embassy: Articles on Albania mention that the language is unique and that they shoot people trying to get into the country. Last year they got a Greek forester and a French tourist. Attached.

(JME) Boscomm: We have half of a huckster's table to sell t-shirts, used books, and copies of The Gunslinger. We need people to work it, especially prospective keyholders.

(BPS) If NESFA has the other half, see that we don't have the bottom half.

(RvdH) Moocomm: I saw Starman. Lots of people liked it; I didn't.

(JME) Moocomm: Goldfinger tonight, Yellow Submarine on Sunday, and Blade Runner next Wednesday. Patton, which may count as fantasy, Saturday.

(BPS) Post-Moocomm: Road Warrior on NBC was surprisingly unchopped.

(JME) T-shirtcomm: T-shirt run on Tuesday 1/22 at 7 PM in the plateburning room. All keyholders and prospectives are urged to attend. If you come, you get a shirt at cost, or free if you bring your own.

(JME) Flakcomm: MIT Council for the Arts is giving the Library a listing and will be here Tuesday or Thursday for photographs. Also, Andy is trying to write a pamphlet about the MITSFS. Talk to him if you have any ideas.

(John Dumas) Boredcomm: Yawn.

(JME) Open question- when is a good time for a magazine processing party?

Saturday 1/19 at 1 PM is agreed upon. BPS suggests imitating the Italian post office, which allegedly dumps its backlogs into the Mediterranean.

(JME) Bowlcomm: Our team plays College Bowl against Senior House Wednesday at 1 PM. (Players: JME, AbM, RvdH, Jenny Hawthorne.)

\goto{Old Business}

(SSDT) An old member named John Costello dropped by around Christmas and said to mention him.

OBA: um, us, uv, ur.

\goto{New Business}

(SSDT) Disastercomm: George Lucas is doing two Saturday morning kids' shows about R2D2 and C3PO and the Ewoks. (Many screams of agony, and one "Gag me with a Smurf!")

(BPS) Minicult: A man shook a Coke machine that ate his money, and it fell on him and killed him. Article attached.

(KM) Minicult: The pound is now nearly equal to the dollar.

(JME) Sunday is Ken M.'s birthday.

(BPS) Street Hawk, a sort of Knight Rider on a motorcycle, is a new show on ABC. I haven't seen it, but it's expected to die.

(KM) Another midseason replacement is OtherWorld.

(JME) Roger Ebert chose Dune as worst movie of 1984, and Cannonball Run II was second.

(BPS) Have you ever noticed how the critic on the left always absolutely hates a movie, while the one on the right only dislikes it?

RvdH sneezes, and Janice blesses him.

(BPS) For about 68 cents, I got us a reserve magnetic half-banana.

(KM) Janice and I got a new VW Golf.

A motion by JRD to commend the Pseudo-Onseck for taking notes so diligently she just wore out a pen is passed by decree, and followed by flaming about VW steering systems.

(BPS) Comics version of Mythadventures 4 is out.

(JME) Minicult: In San Francisco, a 16 year old girl killed a 15 year old girl who beat her out for the cheerleading squad.

(KM) Half a motion to commend Bill Starr for the half-banana. The half-motion is firsted, seconded, and passes 73 1/2-2.5-negative 1/2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 1/2 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Pseudo-Onseck}

\end{document}