\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 19, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (7/12/85) read and corrected.

JME: Motion to approve the minutes as all too accurate. Passes several attempts-one feebleness-wilted attempts +Spehn.

\goto{Committee Reports}

JME: Blintzcomm: Ellen has posted a signup sheet for her fifth annual Blintzkrieg.

BPS: Jourcomm: I got a very professional looking short story addressed to The Twilight Zone. I called the author and she seemed confused, but said yes we can use it. She got our address from the local library. In Seattle.

ATS: Skinner Report: I got a break from work when an incinerator caught fire on the floor above me in E17. When I got back, the whole hallway was flooded. Flames about flames and false alarms.

JME: Moocomm: The Birds and High Anxiety tonight, Conan the Librarian tomorrow. ET reopens tonight, and there's a preview of The Black Cauldron in 70mm animation from Disney.

BPS: Moocomm: Explorers isn't really bad, it just isn't any good either.

JME: Moocomm: The Glob's critic got a compare-and-contrast essay question, and found Back to the Future lacking in ET's "philosophical beauty." Some people.

BPS: Moocomm: Gene and Roger tried to trash Red Sonja, but were laughing so much they couldn't describe what was so funny. Finally Gene said, "Well, I guess you have to see the movie," and Roger said, "No! We don't want them to see the movie!"

\goto{Old Business}

BPS: The shuttle didn't launch last week. At t minus 3 seconds, the computer decided they were having too much fun and made a valve fail.

OBA: usual routine? Why not.

\goto{New Business}

JME: Minicult: Pepsi has a commercial showing mission control talk a thirsty astronaut through a can of Pepsi while he's waiting for liftoff.

Long discussion of good Pepsi ads.

JME: Minicult: The infamous Foxboro Board of Selectmen, which kept Michael Jackson out of town last year, is now contemplating Bruce Springsteen.

Discussion of the possibility of bad elements, like americium, being attracted.

BPS: Here's a Hitchhiker's keyring for the Library.

JME: Minicult: Some strongly religious people in Weymouth have managed to force their cable company to give away devices that can be used to lock out MTV, but now they're at a loss for a way to get rid of MTV entirely.

Support of all that MTV stands for is expressed with a fanfare, using a high pressure gas line for a trumpet.

SSDT: Yeah, and Pat Boone was complaining about satanic imagery in music from the Live Aid concert.

JME: Even worse are various Southern groups trying to get rid of the Playboy channel even as an option on the grounds that it causes family disharmony.

BPS: Move to note that there are a lot of animals out there that fool you by walking around on their back legs. Passes by agreement of the Skinner.

SSDT: Minicult: Here's a long article from the Phoenix about how little kids mangle the lyrics to religious and patriotic songs. Good part of article attached.

BPS: Playboy is changing format from stapled to bound. No more convenient centerfolds. Now for a real Minicult: the front cover blurb on Approaching Oblivion is "Harlan Ellison is my favorite writer. Good author! Good author!" -Richard Dawson, host of Family Feud.

KM gives a further demonstration of his "trumpet." BPS: Move to note that he has an instrument you can play around corners. The motion is overlooked, but the hose is declared the official MITSFS trumpet.

SLP: Andy and I are going to New England Mobile tomorrow.

JME: Minicult: There were fewer complaints about New Coke in New England than other regions, apparently because here people drink more diet sodas. And I got my first paycheck yesterday.

SSDT: Minicult: A WEEI report speculated that the Air India disaster may have been caused by a collision with a piece of Soviet space junk that was falling in the area then.

JME: Motion to commend the man in the banana colored shirt for reading a banana colored book. Passes lots-no one who counts-2 squawks +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}