\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 5, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (6/21/85) read and corrected.

JME: Move to approve the minutes as embarrassingly short. Passes lots and lots-2-4 +Spehn.

\goto{Committee Reports}

JME: Blisscomm: The former Skinner and Telzey got married a week ago last Sunday. Our honeymoon was in St. Lucia, and except that I got food poisoning, it was fine.

BPS: Moocomm: Back to the Future is great!!! Go see it!

BPS: Pseudo-LHE Report: The LHE brought all the money together to do the books, and as a result, there is zero change in the drawer.

JME: Reprimand! Reprimand! Ten demerits!

BPS: Move to note that at this meeting Star Chamber outnumbers non-Star Chamber 3 to 2. Passes by sheer obviousness.

SSDT: Moocomm: Red Sonja isn't as bad as is claimed by the Glob, Herald, NY Times, etc. If you go in expecting nothing, you'll like it.

JME: Moocomm: Return to Oz reviews say it's good on its own, suffering only in comparison to the original.

SSDT: I thought it lived up to the original, but then, I didn't like the original that much.

BPS: Another quote for the ad campaigns!

AbM: Smogcomm: Astronomers have found clouds of automobile exhaust floating around the galaxy.

BPS: Jourcomm: So far I have one poem and 3 book reviews, 2 of which I've written myself. I NEED stuff, folks.

JME: Gippercomm: Reagan's latest open-mike comment concerned the hostages: "Now that I've seen Rambo, next time I'll know what to do."

ATS: Stars-and-stripescomm: July 4th was yesterday, and it was fun.

BPS: Yeah, they blew off some ammunition over the Charles. Move to note that yesterday the Beach Boys were in Washington performing and James Watt wasn't. No vote taken, but lots of cheers.

JME: Doonesburycomm: Sinatra is suing.

BPS: I wouldn't be surprised if one day Trudeau turns up in a car trunk with a bullet hole in his head.

\goto{Old Business}

SSDT: Overreaction of the month of June- in Yugoslavia, a man wanted to watch a panel discussion about the soccer riot in Belgium. His wife wanted to watch Love Story, and she changed the channel on him. So he killed her.

BPS: Good evidence in favor of government-sponsored second televisions. Article attached.

OBA: um, us, uv, ur.

\goto{New Business}

SSDT: Minicult: In the cafeteria of a Connecticut high school, a student tossed a gallon of salad dressing in the air and yelled "Food fight!" About 200 students joined him, producing a mess that cost several hours and 500 dollars to clean up. Article attached.

BPS: Minicult: A man who has built what he says is an energy-producing machine based on previously unknown magnetic properties of copper coils is asking a federal judge to order that a patent be issued for it. If he's convincing enough in court, we'll have a perpetual motion machine by judicial fiat. Article attached.

There was then flaming about the legislation that defined pi as 3.

BPS: A Boston cat that was summoned for jury duty was granted a waiver, not for being a cat, but for not being able to speak English. Its name got on the jury list when city census takers saw it listed on its owner's door. Article attached.

ATS: We got a copier, which will be allowed to stay if it's functional.

BPS: Move to name the copier Mr. Fusion. Seconded.

Adam moves to table the motion since not enough people have seen the relevant movie. Andy recovers from this sudden attack of Robert's Rules, and declares the motion tabled.

BPS: That new cabinet back there is the Vault of Horrors. It locks.

JME: Minicult: Egypt is running out of mummies. In the 19th century, people were grinding them up for medicinal purposes, and now there's a shortage.

Susan wonders aloud if they could make some new ones.

BPS: Move to commend Janice for donating a whole appropriate garbage bag full of Star Trek novels. Passes by acclamation.

As people try to chant Janice's name, she points out that she's keeping Eisen as her last name. Said Janice, "Hyphenating Jewish names doesn't work."

Andy sticks a magnetic half-banana to the gavel and waves it.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Sincerely submitted via manual typewriter,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}