\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 14, 1985

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Andy Su, President and Skinner, presiding.

Minutes of the previous meeting (5/17/85) read and corrected.

BPS: Motion to approve the minutes as Onsexy. Chickens big fat zilch-more than zero-even more +Spehn.

GF: Motion to approve the minutes for being in a folder the color of an elongated yellow fruit. Vote was 8-10-6 +Spehn, but passes anyway due to Skinnerial impatience.

\goto{Committee Reports}

BPS: Jourcomm: Things are about the same as last time...

ATS: Skinner Report: I actually got a job for the summer.

KM: International Committee to Overdamp the New Wave: The best selling SF authors in Sweden are Heinlein and Haldeman. (Flaming.)

ATS: Pseudo-Moocomm: Herb sent in a story treatment of SWIII: The Fall of the Empire. There is also a flowchart on how to write a science fiction story. Attached.

ATS: Pseudo-LHE Report: The new LHE will be trained soon. Also, our 970 dollars came in from Finboard. Also, our new shelves should arrive in August, and our banana kicksteps.

There is a close-enough-to-standing ovation as the ex-Skinner walks in.

ATS: UPS Sucks: UPS came to the building twice but instead of coming to the door and reading the sign as they are required to do, they just phoned here. No one answered, so they sent a shipment back to Whitter. (Much flaming.)

SSDT: In September, Whitter is going to wonder why he's been delivered kicksteps.

BPS: Moocomm: Something called D.A.R.Y.L. opens today. It's about an artificially intelligent eleven-year-old who can fly an SR-71 and is hunted by the military but adopted by an all-American family with 2.3 children... it looks horrible. RvdH suggests: And at the very end, the robot boy turns around and kills the wonderful family. BPS: My God! The evil military was right all along!

BPS: Pianocomm: We have a picture of Lisa Kroh. The other new keyholders are stickfigures. Also, there is a bisected picture of Ken Johnson, so we will have to find out if the thief liked him or the Weird Tales.

\goto{Old Business}

ATS: A letter from George Phillies tells how The Seitz is alive, well, and Doing His Job! A letter from Seitz debunking the concept of nuclear winter made it into Nature magazine. See attached.

OBA: um, us, usual everything.

\goto{New Business}

SSDT: Minicult: A West Tisbury third grade class vote recommended a bulletproof old jalopy as Reagan's primary means of transportation. The class is now threatening to expand their survey and send the results to the Washington Post. Article attached.

JME: Several newspapers have censored Doonesbury's attack on Frank Sinatra. Some didn't print the strips, and even worse, some made changes to them without mentioning that there was tampering.

The Doonesbury issue generates flames and more flames which rise higher and higher until eventually the ceiling tiles begin to char.

AbM: Minicult: The NY Times had an article on the image of scientists in fiction, including the fact that on prime-time television, scientists get killed more often than members of any other profession. Attached.

BPS: Minicult: In 1981 a 12-foot-high 120-foot-long rusty steel wall entitled "Tilted Arc" appeared in Federal Plaza in Manhattan, causing a war of words between art critics who claimed that removal of the object would be tantamount to censorship, and the rest of the people of Manhattan, who were sick of a work of art that takes such a long walk to get past it. The General Services Administration, which commissioned the work, has finally agreed to move it somewhere. If the new location turns out to be the city dump, maybe we can convince them to take Transparent Horizons too.

Lisa Nanney: Minicult: You know how you go to the Hayden Gallery and say "What is this shit?" Today it really was: about twenty "baby fecal stains" hanging on the wall, complete with a description of what the baby had eaten on that day.

JME: Minicult: Every year at Princeton, they have the same salutatory speech in Latin. The students get transcriptions, complete with notations of when to clap, hiss, laugh, and so on.

GF: Minicult: William Gibson won the Philip K. Dick Award and said "Now I can invite everyone up to my room to see my Dick."

Albanian motion on Gibson passes enough-nowhere near enough-3 +Spehn.

AbM: SteveMcDonaldcomm: Hi there!

ATS: Move to condemn UPS for not having delivered our banana-colored kicksteps. The motion is naaaahed to death.

KM: Move to commend the Star Chamber for ordering banana-colored kicksteps. Passes a few-much fewer-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Onseck}

\end{document}