\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/26/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 26, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the half-hour-early Onseck.

[Jade] ``I will be very disappointed if this isn't a short meeting.''

Minutes read.

Motion: Commend the bold, defiant reading of the minutes as an act of
rebellion against the hyperintelligent squirrels.  Does nothing
5--0--4+Spehn.

\goto{Committee Reports}

Panthercomm: Revised the catalog format.

Bluebellcomm: The covering material was ordered, finally.

Picniccomm: The appropriate letters have been mailed.  [Jade] ``And he
has God as his copilot.''  Elections are on the 10th, and the picnic
on the 11th.  We might be doing rental cars this year.

Pseudo-Analogcomm: Summer requests envelope is going up on May 1.

hBarcomm: Some postering happened, since LSC is showing {\em Fellowship
of the Ring}.

\goto{Old Business}

The minutes for 1981-3 turned up in the Jourcomm drawer for some reason.
In related news, the file cabinet rearrangement is in progress, making
such strides as putting the phone books out on the desk now.

Bank transfer is still in progress.

Usual stuff.

\goto{New Business}

Our new bulletin board is apparently one spot over from our old one,
for no apparent reason.  Aesthetics?

John called in to say that he's winning again.  But he's not here.
He finally told his boss what he thought of him and now has much more
free time.

Motion: Congratulate the hyperintelligent squirrels for finally
destroying John's life.  Passes 4--2--2+Spehn.

Motion: Condemn the hyperintelligent squirrels on general principles.
Not seconded.

There is a proposal to fund NASA with a 1\% tax on science fiction
products.  This is a pretty silly idea.  According to Jamie, taxing
particular types of media based on content is almost certainly against
the First Amendment.  The proposal was from a political candidate in
Alabama... the same state that has suspended jury trials as being too
expensive.

[Jamie] ``Wow, this is a good time to commit crimes in Alabama...
Road trip!''

The same candidate is also thinking ahead about constitutional conventions,
planning one for when 30,000 colonists are on the moon or Mars.

\goto{Future Business}

[Steph] ``In the future my life will not suck as much!''  That is,
after term.

We should do a general revision of the keyholder notes to remove
references to Ken Johnson.

Motion: Miller motion.  Fails 0--7--4+Spehn.

Motion: Second Miller motion.  Passes 7--2--3+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1755 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
