\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/11/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 11, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and Pseudo-Skinner, presiding.  Ed Keyes is the back-from-Tennessee Onseck.

Minutes read.

M: note that the Onseck has a good future in high-redshift astrophysics, due to facility for deciphering low signal-to-noise data, namely John's handwritten minutes. John seconds his own motion. 4-0-1 +Spehn.

\goto{Committee Reports}

Chroniccomm: heard back from Alum Office, finding the proper successor to talk to. Form to fill out, SNF1 needs a few edits. Use prentices as envelope-stuffers.

Pseudo-Pianocomm: newly volunteered prentice came in and started being spontaneously helpful.

Discussion of shelf rearrangement. A hole was cut in a shelf back to accommodate an electrical outlet. (John) "So if they fall on a member, they'll both fall on the member?" with regard to bolting shelves together.

Jadecomm: Jade is going into hibernation to deal with game and work. (John) "This is why we should destroy the Guild."

New floormat exists. Amazingly enough the Onseck did his job.

Pseudo-Analogcomm: request envelope for spring hours is up. Request hours by Wednesday.

Pens are walking off.

Jourcomm: needs to bug people, contemplating a review-lite TZ. John intends to do a review, "hopefully by last March."

War Council: waiting for deans to arrange schedules, and for various councils to assign reps.

Alohalenscomm: Jen wouldn't let us take a picture of her.

\goto{Old Business}

Does anyone still use the modem? Apparently not, so the second computer will disappear soon.

Another discussion of moving shelves in the former for-sale area and the circulating room. There will not be a for-sale shelf for the near future, relying on mass purchases at Arisia. Maybe rearrange room in warehouse to put boxes of books if we have to.

Damnation Alley is still an enter-upon-pain-of-death area. The bodies would mess up Jamie's boxes.

\goto{New Business}

Someone apparently took the "Infinity Shore" seriously and read it on the beach... came back full of sand.

Someone came by looking for "John" when they meant jhawk.

Another person got a 4-year membership at the new rate.

Our mailbox has moved... somewhere due to UA office construction. Mailed us a note telling us where it is...

Anyone of artistic ability can make a slide for the sci-fi marathon. Use our free Tech ad.

Talk to Jen Clay about being Pubcomm?

\goto{Future Business}

Perhaps one day someone will cover Pratchett's rat book.

(Jamie) "Would anyone care to try to end the meeting?"

M: Miller motion. 5-barely 7-0 +Spehn. Whew. The universe was saved once again.

Emily asks for prentice project.

(Crickets chirp)

Discussion of the longest (non-election) meetings. The dedication of the AC, including the reading of its inspired short story, was pretty long.

M: have the meeting never end. 1-1-7 +Spehn.

M: Second Miller motion. 9-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting has an emergency adjournment, 1759 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
