\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/19/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, Mass. 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 19th, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
\bing
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Andrew Boardman, who shows every indication of being
the onSeck, recording.

Jade and Jay fled.

Minutes read, with numerous 

Jamie moved to approve the minutes as a postmodern interpretation.
The motion does nothing 4/2/3+. \bing

\bing \goto{Committee Reports}

Mobcomm got a box of books from SCC!  The mailman was there when MOBcomm
was, after which the latter was promptly encumbered with some free
vanity-published science fiction.

hBARcomm: The minutes are to read that Jen Clay cures headaches.

Dexmistress: inventory is saturday 3 august.  emily says that she is looking
forward to it.  No, really.  JFC is proven to be a lousy barcode scanner.

JFC wants to form a committee to keep track of mad scientists, one of
whom has created an artificial polio virus.  Another one has created a
mosquito which is supposed to not transmit malaria.

NASAcomm reports on N's research into building a beanstalk.

Theftcomm reports a one-year anniversary of the TIF, which has
demonstrated that certain keyholders are really being kinda lame.

\bing \goto{Old Business}

The Working Group should really be doing stuff.

JFC may have a plan to dispense with the bubble in the library, involving
noting hyperlinks from one section of books to another.  It is generally
agreed that doing this for the entire library is a bad idea.  Even with
doubly linked lists.

\bing \goto{New Business} {The Usual Stuff}??

Psi-phi failed to take Athena 9.1.  AMB will find a larger disk.

NYRSF has been renewed; Analog and Asimov's are next.

We got money from the libraries!  Yay!

JFC submitted a reimbursement request for a box of books from SCC.  He
also reports the possibility of dealing directly with Ingram.

\bing \goto{Future Business}

HyperIntelligentSquirrelComm reports advances in the plan of the
squirrels.  The use of organic body cream is not advised, as it may make
the HIS population take you as one of their own.  JFC is unaffected, but
for an isolated instance of Sciurusian interaction.

Jamie moves to create the committee Speaker to Sciurus, who will deal
with said population and attempt to save the universe from them.
``two-legged groveller''.  Motion passes, 8-4-0+. \bing

\vspace{12pt}

\noindent
Meeting adjourned, 1758 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jamie Morris, pseudo-Onseck}

\end{document}
