\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/26/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 26, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Ed Keyes, President and Skinner, presiding.
John Carr is the green pseudo-onseck.

Minutes read.

Motion to condemn the minutes as daring to correct Jamie's errors.
Passes \hbox{6-3-2+Spehn}.

\goto{Committee Reports}

Mobcomm[JFC]: Several boxes of British books arrived.

Mobcomm$_2$[JFC]: I want money.  Ed may test the system for getting
money next week.  A discussion follows of the new money getting procedure,
dots, and rites.  A green sticker is labeled ``orange.''

Pianocomm/Hasslecomm: ARM and prentice Ariel have processed several boxes.

Vox Sciurorum: Scientists have built a better mouse.  Injection of
a particular chemical into a developing mouse causes its brain
surface area to increase.  The mouse brain becomes folded like a
human brain.  Soon there will be all sorts of hyperintelligent
rodents.

Motion[Y]: Give Viagra to the squirrel Malcolm saw eating a plastic
wrapper instead of the muffin inside the wrapper, to keep the species
intelligence low.  Passes \hbox{8-0-4+Spehn}.

Aloha Lenscomm[JFC]: Susan broke my camera.

\goto{Old Business}

Our bank account is closed and we hope our MIT account has the money
that was in our bank account.

The shelf bubble has been distributed (by Joe and Jake, in penance for
missing inventory).

\goto{New Business}

We have {\em Stone}, the third monosyllabically titled book by Adam
Roberts.  Somehow this leads to a discussion of {\em The Wasp Factory}
by Iain Banks.  We don't have this book.  It is disturbing.  ``Of
course it is, it's a Banks book.''  No, really, this one is
disturbing by Banks' standards.

\vspace{12pt}

\goto{Future Business}

AMB will upgrade $\rm \psi\phi$, then Jamie will update it.

If the hyperintelligent squirrels join MITSFS, can they use their
tails to get five votes each?

The Skinner looks at the clock.

Miller Motion!  Second.  Fails, \hbox{4-6-3+Spehn}!

Second Miller Motion!  Second Second!  Passes, \hbox{7-5-1+Spehn}.

\vspace{12pt}

\noindent
Meeting adjourned, 17:53 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-onseck}

\end{document}
