\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\raggedright

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/29/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 29, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding (``shall we have a meeting?'').
John Carr, pseudo-onseck (``why not?'')

Minutes read.

A motion involving chaos, posssibly a motion to declare the minutes
as chaotic, passes \hbox{3-0-1+Spehn}.  This leads to a discussion of
Wisdom and Sussman's chaos course, and their papers.

\goto{Committee Reports}

bluebellcomm: Bluebellcomm is lame again.

Bondagecomm: Closer to binding.  IASFM can't be bound in a matching color.

War council: The UA may have recorded only the first 1,000 votes on the
reading room survey.  The cutoff may have been around the time Ed sent
email to members about the survey.  Only electronic votes were recorded,
not the paper surveys left around the reading room and MITSFS.  0.2\% of
respondents claim they use MITSFS every day.  20\% want us moved upstairs.
40\% want the reading room renovated.  82\% never use MITSFS but 20\% would
use MITSFS even less if it moved upstairs.  Therefore, at least 2\% of
respondents are lying or confused.

Malcolm makes a motion noting that the UA has revived Campbell's ``Analytic
Laboratory,'' which had invented statistics.  This passes \hbox{3-0-Spehn}.

\goto{Old Business}

The usual stuff happens.

\goto{New Business}

Malcolm: ABC has twice announced the earthquake episode of Munk, and
has twice preempted it by special news reports.  They will try again
this week...

Campus is dull today.


Snow is falling.

Malcolm read two favorable reviews of {\em Treasure Planet}.  Members
discuss other remakes: {\em Lifepod}, {\em Forbidden Planet}, etc.

\goto{Future Business}

Motion: Provide all members present with a banana apeice.
Passes \hbox{1-4-Spehn}.

\vspace{12pt}

\noindent
Meeting adjourned, 1737 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Thanksgiving-break pseudo-Onseck}

\end{document}
