\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad --  \quad 10/32/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 32, 2002

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST.  Ed Keyes, President and Skinner, presiding.  Andrew Clough is the Rastifarian Onseck.

Minutes are read.

Motion:  Approve/Condemn the minutes for being mostly willing to move forward despite any obstacles, but not completely.  Passes 2-7-0-1+Spehn.

\goto{Committee Reports}

Asscom:  Britney Spears was executed for brainwashing, coke wins the cola wars, and green is the color of the new millennium.

Mobcomm:  LSC is distributing flyers for the SciFi marathon.  

We are informed that Zardoz has flying stone skulls and Sean Connory in a diaper.  The preface is read from.  You'd run away screaming in terror is you heard it too.

Motion:  There was much wailing and gnashing of teeth. Chickens 3-2-6+Spehn

Bluebellcomm:  Still lame.

``You could use tinkerbell to make Pinnochio into a real boy, but then it wouldn't be PG.

Jourcomm: Bantam-Spectra's advertising budget must have gone down.  We're getting smaller covers.

Would you visit a planet named ``latent Emanation''?

\goto{Old Business}

The woman from England will take the tea pot, and thus validate all ethnic stereotypes.

Christmas lights make good aisle lights, if your projector is one of the least powerful ever made.

\goto{New Business}

Discussion of book covers, looks generated by such-and sundry other SciFi paraphernalia.

Forrest Ackerman, a famous fan, won't be going to any conventions soon :(  

Dragons ruined the climate of California because they couldn't stand another episode of ``One Man's Family.''

\goto{Future Business}

Motion:  Have Michael Crichton write a movie about a giant stone head regurgitating bananas on Sean Connory in an attempt to end his career (Note, ``his'' left intentionally ambiguous).  Passes 12-2-1+Spehn.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
