\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}


\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/22/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 22, 2002

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order,1700 SST Friday, November the 22nd.  Ed Keyes is the presiding President and Skinner, while Andrew Clough is the ordinary Onseck.

Motion:  The next meeting should be called to disorder!  Passes 10-1-3+Spehn.

The minutes are quickly read.

Motion:  Recommend that the Onseck get a job reading the fine print in commercials.  Passes 11-0-1+Spehn.

We have new banana art.

\goto{Committee Reports}

Motion:  Condemn MITSFS for discriminating against non-bananas.  Fails 6-10-2+Spehn.

Bondagecomm:  Started on stuff.  Found old TZs numbered 31-41.  They're bound!  Found article on scifi porn and other interesting stuff...

ACME book binding, ``Free anvil with every purchase!''

Chickencomm:  pukpukpukpukpukp'hKWAAAAHHK!!

Discussion of various historical sinking ships, and a debate as to whether the titanic ever caught on fire, and applauding that ship that sunk in port, due to having too many gun decks, whatever its name might have been.

Pseudo-Bluebellcomm:  Still lame, pile still there, we should reconsider buying the cattle prod.

War council: Proposal was shown to the UA at their meeting.  Despite the presence of our representative, they still seemed surprised by us being there.  They have decided to have a survey on whether to let the move go forward or not.

Pianocomm:  2 prentices repackaged stuff, but were defeated by Harry Harrison.

\goto{Old Business}

A Games Workshop store just opened in Harvard Square, and our freshman, Margaret, is very excited.

In ``Einstein's Bridge'' the superconducting supercollider destroys the world, but Dan Quayle saves it.

Margaret, upon seeing a GW catalog:  ``GiigiigigigiqiigiiqiGimmeGimmeGiimmeee!''

Usual motion, and stuff.

\goto{New Business}

CD smash!

The MIT librarys are starting to stock manga.

Albania Motion on Malcolm, after he describes some hideous animated series.  Passes 12-0-1+Spehn.

Budget request submitted to UA.

Motion:  Fund 0\% of Margaret's robot development if she turns it into a banana cutter.  Passes 8-1-1+Spehn.

Meeting is adjourned 17:32 SST

\vspace{18pt}
\begin{center}

Respectfully Submitted,

Andrew Clough, Onseck

\end{center}
\end{document}
