\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/29/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 29, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1715 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the it's-spring-break? Onseck.

Minutes read.

Motion: Condemn the minutes for implying that the shelf construction
had ``ouch''es in it.  The tongues of the workers were of course
removed as a safety precaution.  Passes 5--0--mmmmph+Spehn.

\goto{Committee Reports}

John isn't here so silence reigns.

\goto{New Business}

There's a bunch of new shelving in the circulating room from building
some of the Aurora shelves.  The new hardcover space is being
distributed.

Jade's parents are coming tonight to take her away.  To Cape Cod.
As an escape from her thesis.

Motion: Have Jadecomm steal a trick from Stranglecomm by calling up
Jade at 3:00 am to remind her about her thesis.  Passes 3--0--1+Spehn.

Jade requests that someone she doesn't like be assigned this task,
so that she won't feel bad when she kills them.

\goto{Old Business}

Damnation Alley is now close to re-opening.

A member is still interested in helping to repair books but has
been unable to contact the Surgeon.

\goto{Future Business}

[Jade] ``In the future we will eat cheesecake... raspberry
cheesecake.''

[Jamie] ``The road to hell is paved with raspberry cheesecake...  You
might have wondered why it was so squishy.''

There will be a lot of pre-frosh on campus next week, so Jade is
escaping.  [Jade] ``All my pent-up sarcasm gets wasted on you guys.''

Motion: Send a contingent of pre-frosh with banana-raspberry cheesecake
to Stanford to harass Jade.  Passes 5--1--0+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
