\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/1/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 1, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the hey-it's-my-mom's-birthday-today
Onseck.

Minutes read.

Motion: Seal last week's minutes in a cornerstone.  Chickens 3--3--7+Spehn.

\goto{Committee Reports}

Chronicomm: Except for a few copies, {\em SNF} hasn't come back to undo
the mailing.  We're still getting new addresses and sending out more.

Mobcomm: I want \$900.  Do we have it?

Pumpkincomm: On behalf of Paul Mailman, an alum we contacted:

Motion: Reaffirm the Society's faith in the Great Pumpkin.  Passes
8--0--1+Spehn.

Mobcomm$_2$: Some books from SFBC... arrived.

Boriscomm: John's attempt to get a Boris calendar failed, as SFBC
was out of stock.  Jade points out we have a calendar already.
[John] ``But it doesn't have nearly naked fantasy women on it... at
least on this page.''

Violin playing proceeds continually from down the hall.  Not bad.

There is a discussion of where to stop in Hambly's {\em Dragonsbane}
series, the concensus being either stop at one or go to the end.

Bluebellcomm: Bluebellcomm is lame.

\goto{New Business}

Tom Holt just keeps writing and writing.  He's finally settled down
into the ``mediocre'' category.  Ed tries to get John to compare Holt
to Pratchett and Rankin, but has to ignore whatever he says when it
is revealed that John actually doesn't like Pratchett and is therefore
clearly insane.

Jerry Marty quit his job to attempt to become a novelist.  He probably
used to be a member, we think.  Going out with a member, anyway.

\goto{Old Business}

Apparently 19th century Spanish people were pleasantly politically
incorrect.  John proceeds to read a horribly anti-feminist sentence
about characteristics of ``true'' men and women.  Aspects of Gor...
[John] ``Aren't you glad I got this book for us?''

The violin is starting to be overpowered by a vacuum cleaner.

The Tyrannical Iron Fist chart has gotten shifted, revealing a fresh
new sheet for keyholders to conquer, and also revealing how the pages
yellow over time.  There is a comparison of the rotating of the chart
to the turning of the Wheel of Time.

Malcolm makes a horrible pun about ``running fingers through Monet''
about art books in libraries.

Motion: Albanian!  Passes 8--4--1+Spehn.

We had a visit from R. H. Bernstein, Skinner in 1976, this week.  He
was here on campus to give a talk about misbehaving neutrinos.  [Jade]
``Damn neutrinos.''

The Skinner tears up a bulletin board note.

Motion: Someone discover an excited MITSFS meeting.  Chickens
4--0--11+Spehn.  John criticizes the tone of the bing.  Jade considers
using his head instead.

\goto{Future Business}

The shelf bubble propagated a bit.  Jamie thought he reported it earlier,
and chastises the Onseck for not reading the thought bubbles above his
head.

The new-book shelf has an annoyingly non-Gaussian distributions of a
few British authors.

John ran across Justin's sticker-progress note in all of the bubble
propagation.

Motion: Replace Justin's note with a banana.  Passes 9--1--2+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
