\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}


\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/18/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 15, 2002

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting is called to order 1700SST.  Ed Keyes is the presiding president and skinner.  Andrew Clough is the sorrowful Onseck.

The Minutes are read.

Motion:  Condem Minutes for not Having a Matrix.  Passes 4-0-3+Spehn

\goto{Committee Reports}

Psuedo-Pianocom:  A new name is entered into teh book!

Psuedo-Jurrcomm:  Added lines to the review.

Mobcomm:  Books, books, and more books.

Psuedo-LEG report:  The rate at which donations go to the wrong account is increasing!

Bluebellcomm:  We'll have to cover son.  Cat-o-nine tails ready to flog members into action.

Random-what-the-hell-happened-here-comm:  We asked for a tewenty year subscription to Azimov's.  Instead, they gave us twenty one year subcriptions!!!  We also got a letter asking us to renew our subscription!  Grrrrr!!

\goto{Old Buisness}

The researching grad student has mailed us our books back.  Plus some reference material and a farside cartoon.

Usual Motion, but without the usual vote, though it had the usual second and usual lack of debate.

The adjournment song is sung, and a bannana motion passes 4-0-2+Spehn.

\vspace{18pt}
\begin{center}

Respectufully Submitted,

Andrew Clough, Onseck

\end{center}
\end{document}
