\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/09/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 9, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding. JFC is the Pseudo-Onseck.

Minutes read.

M: last week's minutes are erroneous. 3-0-0 +Spehn.

\goto{Committee Reports}

Mobcomm: Gryphon books; need money in advance. We will further test the new regime.

\goto{Old Business}

Inventory happened. New procedures were made- main part went quickly, rest too slow. JM said it was fast, but in wrong order and people were misallocated. "Next year should absolutely fly."

40000 volumes in 5 hours is "pretty damn amazing." (Ed)

JM is finishing dex update now, after checking membership sheets. Merge process is unnecessarily computationally expensive.

Algol.

\goto{New Business}

Alum wants to donate about 1000 books, shipped from Ohio.

Upper Calgary SF collection- we're number 2? They want 300000 dollars to preserve the collection. LHSFS will probably win big if Ackerman dies and gives them his collection.

\goto{Future Business}

Full schedule soon. "Usual" TIF method for R/O: less advance notice required for credit.

Prentice flakes, John ends the meeting with Romance.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
