\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}


\begin{document}
\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 25, 2002

\end{center}
\vspace{18pt}
\setlength{parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding.  Andrew Clough is the returned Onseck

Minutes are read.

Motion:  We want to hear less about bowel movements in the future.  Fails for lack of a second.

Motion:  Condemn the heretical notion that motions can pass with out Skinnerial approval.  Passes, somehow...

\goto{Committee Reports}

Bluebellcomm:  Lame with regards to covering hardcovers.

Barcomm:  ``I am bad,''  same old slide again.

Mobcomm:  ``Witches on the Loose'' was the mistyped title of ``Witches on the Noose.''  Somebody named Martin ``Greenberger'' edited Apprentice Fantastic.  Any relation to Martin Greenberg, we wonder.  Finally there is the book Ganglo-rds

\goto{Old Business}

The $\rm \Psi\Phi$ software is happy.

Motion:  Get a mouse with a zipper, so as to replace many buttons.  Passes 6-1-1 +Spehn

``So you're one of those literary SciFi types.''  I'm not a type, I'm an instance''

Discussion of the black hole at the center of our galaxy, the measurement and existence of.

Cope of ``The Skinner'' donated, as is ``Dangerous Vegetables.''

\goto{Future Business}

Motion:  A Banana should go to the Assassin's Guild game now.  Fails for lack of a second.

``So, the banana has to split.''

The Closing song is say, and the meeting adjourns at 17:40:38 SST.

\vspace{18pts}
\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Onseck}
\end{document}

