\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, Mass.  02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, 14 June, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order (\bing), 1710 SST, Our beloved Ed,
President and Skinner, presiding.  Andrew Boardman might be the Onseck.

Minutes read.  No motions thereto pertaining took flight.

\goto{Committee Reports}

FleetComm: Fleet will do denomination exchanges if you tell them you're a
customer; proof, however, is not required.

Jayhawkcomm: everything is jhawk's fault.  Request for clarification
deferred.

Mobcomm: SFBC has left us books; SCC (whoever they are) has left us even
more books.  A Robert Rankin novel has arrived.  The Skinner likes
looking at the pretty covers.  Alas, the books were at one time nicely
stacked, but jhawk restacked them most rudely.  Everything is thus
jhawk's fault.  ("No human would stack books that way.")  Oh, and Mobcomm
wants money.

Bluebellcomm: there are some books that need covering.

LHE: petty cash seems sufficient.

More Mobcomm: it is entirely unclear how to send money to the UK.

\goto{Old Business}

A Chinese reprint of an Onion article was officially retracted.  How dare
the Onion print something plausible!

\goto{Committee Reports}

The Center for Public Integrity reports a story from 12 June report of US
surveillance operations being available all over Europe via satellite
broadcast, encrypted via rot13.

Usual motion, usual second, usual result.

\goto{New Business}

Long pig: A fantasy concerning cannibals, quartz, and other consumers.

Jourcomm: JFC will be writing cover reviews for the next TZ.

Realtor smut has helicopters *and* hats.

Jamie moves to comdemn john for discriminations against IP packets.
Motion is seconded and passes, 6/3/0+. \bing

Ed Sussman donated 5 more boxes of magazines on Sunday.

SFBC thinks we should buy more books.

JFC should get over the leather stuff already.

TZ prototype real soon now.

\goto{Future Business}

Inventory is nigh.

Athena accounts people actually want a reason!  How dare they!

Interzone needs to be renewed.  Maybe.  Or not.  Shame on the ex-onsec.
No, really.  It needs to be renewed so much so that we seem to have never
even gotten a copy.

The Skinner is a magazine.  He may have subscribed to himself, confusing
the issue.

There's a new 'prentice.

New/old business: there is a new window.  It is very nice.  We should
arrange for a similar treatment for existing windows.

JFC was almost trapped forever in a magical clearing.  He didn't
apologize to the bush, though.  He has returned.  Oh, well.

Miller motion fails, 2/5/0+.
Miller motion #2 passes, 4/1/3+.

\vspace{12pt}

\noindent
Meeting adjourned (\bing), 17:54 SST.


\vspace{18pt}

\centerline{Irrespectfully submitted,}
\centerline{Andrew Boardman, pseudoOnseck}

\end{document}
