\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/01/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 1, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1705 SST, Jade Wang, President and Skinner, presiding.  Ed Keyes is the soon-to-be-in-sunny-California Onseck.

Minutes from two weeks ago read since the Onseck forgot to make up something for last week.

The Onseck is encouraged to improv something.

M: commend the Onseck for putting up with the pseudo-skinner over the last two weeks. 5-3-1 +Spehn.

(John) "If you close your eyes and press on your eyeballs..."

\goto{Committee Reports}

Theftcomm: sanity-checking the chart as we speak. Bottom chart will vanish when 5 more keyholders make it to the top panel. Hold more hours!

(John) "There are only 18 hours in a day."

(Jade) "Can I just hit things now?"

Mobcomm: we are getting The Skinner, which features giant leeches and the severed head of the legendary repulsive Skinner.

Jade prepares to destroy a Cocoa Puffs CD-ROM. It's a game plus an AOL CD. Also includes a "Moop and Dreadley" game demo.

Can we make a committee for banging things with the gavel?

Mobcomm: our shipment of British books came with an interesting dent and a note from the post office. We now have a copy of "Nostradamus Ate My Hamster" for the Onseck.

Bluebellcomm: the massive wave of IAP books has moved off of the new book shelf.

(Jade) "Gnats don't have testicles, do they?"

Alohalenscomm: using the powers of blackmail, we have a photo of Jen Clay now. Threatened to take a picture if she didn't provide one.

Pianocomm: prentices have been pretty lame over IAP.

\goto{Old Business}

The CAC's policy with regard to our vanishing mailbox has been to embargo mail for a month and then deliver it all last week, in reverse chronological order.

\goto{New Business}

Jade tries to smash a CD in a metal box but misses. \bing Thump! Thump! \bing Thwack! She then returns the pieces to John who nearly cuts himself on the shards.

(Jade) "I don't want a Cocoa Puffs game!" She destroys another one, scattering shards over the floor since the packaging was flimsy.

The P's have more space allocated to them, shifting in progress.

Someone offered to index our fanzines for us, in the month of embargoed mail.

A new alleged autobiography of Asimov, put together by his wife. Contains a "shocking revelation..."

An 8500 dollar copy of Lord of the Rings. Is it bound in elven skin? 5000 dollars for first edition of the hobbit, uncertain if it is the authorized or unauthorized one.

\goto{Future Business}

Term is starting soon. Jade may be graduating with luck.

Discussion of FROGs and intense electric fields creating particles.

(John) "If you try to do something sufficiently cool, nature will screw with your experiment."

The VA is being a lame-ass about the War Council. Discussion of Reg Day and John's experience with traffic jams.

M: move the skinner provide the registrar with a supply of succulent world-dominating bananas in lieu of a late registration fee. 5-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17... 1745 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
