\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/17/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 17, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding; Andrew Clough, the proud new Onseck, recording.

It is noted that the Skinner forgets to mention the time at first, and that Jade laughs.

Minutes read.

Motion: commend creative pronunciation. Passes 6-0-1 +Spehn.

Motion: we are appalled at the completeness of the minutes. Fails, for lack of a second.

\goto{Committee Reports}

Alohalenscom: Pictures pretty much done. The minutes would like to inform the people whose pictures have not yet been taken that they can come out, nobody's going to take their pictures, really.

Mobcom: Money?

Pseudo-LHE Report: We got money, but unfortunately not Laurie's head.

Jourcom: Soon. John has a problem with things going out of print while he's reviewing them. He proclaims that next election nobody will be allowed to have any decimal points.

Picniccom: The Picnic happened, though the path was really rocky, so they should be renamed the "Red Hills." Segues to: discussion of the plight of exploited Christmas Trees. Segues to: flocks of goldfish, sometimes spontaneously generated.

Pseudo-Analogcom: Schedule!

Pseudo-Bluebellcom: The members of the Star Chamber present admit that they have not read the rites.

\goto{Old Business}

An old 1978 letter was recently discovered in which a former skinner chewed out the Magazine of Science Fiction and Fantasy for canceling our subscription. It seems that they don't normally grant lifetime subscriptions to organizations. However, it seems that in 1978 an old letter from 1968 was unearthed that proved that they knew about our organization-hood when granting us the membership. So ha!

\goto{New Business}

New donation, big donation, good donation, yay. This donation includes the surprisingly (for its title) good anthology "Prom Night."

Evil boxes obscure painting, plot revolt.

Discussion of evils of signed books, and how signed books can be sold into the "ebay trade."

As many Andrews as Jens among keyholders now.

A freshman that "John remembers with special delight" was frightened away by the number of J names.

\goto{Future Business}

Finals next week.

John has an interview with "XML cult" but promises to avoid any Kool-Aid they offer him. They sing "well formatted chants."

Motion: give the monkey responsible for the name "Attack of the Clones" a banana. Passes 10-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1750 SST, closing time given without the prompting of former skinners.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Andrew Clough, Onseck}

\end{document}
