\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/30/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 30, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding. JFC is the Pseudo-Onseck.

Minutes read.

M: condemn someone. No second.

\goto{Committee Reports}

Mobcomm: new British books. One square book.

Condemn Collonce for not using golden ratio. 4-0-4 +Spehn.

Mobcomm2: Ranging title- Hollow Chocolate Bunnies of the Apocalypse.

Fweekcomm: Midway in progress. Skinner upset to receive more help than he had planned. We should poster with real books.

The banana-cloth guy weighs less than -3 helium balloons. Are free-floating ads allowed?

Good flow of non-members.

We got good placement in the book of activities. At least 3 Cambridge students have joined.

\goto{Old Business}

New dexes are here except for Pinkdex, which is at the midway.

\goto{New Business}

New donation today (3 boxes) from Mark Costa will replace Sussman donation on couch.

\goto{Future Business}

"Maybe next year." -Justin

Stephanie may hold fall hours.

Classes soon.

JFC has no romance.

JFC will buy "watching trees grow" to make JM's brain hurt. JM's refusal to read it will not deter this plan.

Weird Tales subscription will expire "soon" (2004).

Stickers should be checked every 5 years. Justin has been a prentice for 5-6 years. Time to start over.

A member makes frog sounds.

M: commend Stephanie for constructing a plausible alien at the midway out of one of our T-shirts and a bunch of banana-colored helium-filled porpoises-no-balloons.

M: diagram that sentence.

M: inject porpoises with helium to see how they compare to balloons.

3-0-4 +Spehn, 4-5-4 +Spehn, 7-5-3 +Spehn, determinant: -90. All motions fail.

M: inflate JFC with banana-filled porpoises to get him to stop objecting to redoing the computations on a banana-colored processor. Passes 3-0-7 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1742 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
