\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/26/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, Mass.  02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, 2 August, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Ed Keyes, President and Skinner, presiding.
Andrew Boardman is not entirely unlike the Onseck.

Minutes read.

[JFC] A motion to commend minutes as more accurate than expected
chickens, \hbox{3-0-3+Spehn}.

\goto{Committee Reports}

Dexmistress reports preparations for the impending Inventory.

Alohalenscomm[JFC]: A bit of work has been done.  Some people are just
too picky about their pictures.

Mobcomm[JFC]: Books have been obtained.

Students are reported to be impending.

Bluebellcomm[JFC]: A book has been covered.

pseudoAnalogcomm[JM]: The solicitation envelope for Autumn hours is up.

Vox Sciurorum[JFC] report a rabit looking at him oddly.  JFC was,
however, allowed to pass.

Jourcomm[AMB]: TZ real real soon now.  Preferably in August.

JFC will review new the new Jack McDevitt novel ('Shindi'?) for TZ.  Maybe.

\vspace{12pt}

\goto{Old Business}

Jen Murphy will be/has been ordering t-shirts.

The C/P bubble was propogated, but there's still some space left at the
end.  Discussion of how to allocate the final frontier follows.

Phil Walsh has a proposed draft of the plan for the working group for
MITSFS to have half of the reading room upstairs.  A discussion of the
finer points of the plans ensues; things appear to be proceeding
generally apace.  (Where the pace is slow.)

\vspace{24pt}

\goto{Ed Iterates through the Algol into New Business}

The new 'Anita Blake' book has been received, and reportedly sinks even
deeper into bondage porn.

JFC reports that British authors are all insane.  Cornell's British
Summertime is held up as a prime example.

We've gotten almost unbearably chirpy email from a UK SF society who have
found us.  They're talking about making transatlantic links.  A
discussion about how to get books from the UK ensues, and the
practicality of a trade program, ensues.


\vspace{12pt}

\goto{Future Business}

The Inventory is tomorrow.  Everyone come.  Jamie's wonderful new
inventory code will be *great*!!!  (If it's done.)

JFC reads from the back of a book.

A motion to demand tribute of frankensence, myrrh, and bananna coloured
metal from the Imperial College Science Fiction Society passes,
\hbox{7-0-1+Spehn}.

\vspace{12pt}

\noindent
Meeting adjourned, 17:51 SST.

\vspace{18pt}

\centerline{Irrespectfully submitted,}
\centerline{Andrew Boardman, pseudoOnseck}

\end{document}
