\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/3/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 3, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and
Pseudo-Skinner, presiding.  Ed Keyes is the proto-librarian Onseck.

John demonstrates the procedures of Bluebellcomm to a prentice.

Minutes read.

Motion: Condemn the minutes for not mentioning my (John's) name enough.
Fails 2--4--2+Spehn.

[John] ``I would have chickened the motion, but it would have involved
kicking Emily.''

Motion: Condemn the minutes for not being comment-worthy enough.
Passes 2--1--2+Spehn.

\goto{Committee Reports}

Jadecomm: Jade gave her masterworks presentation, but now has to give
a longer version at Lincoln Labs, so is hosed now.

Pseudo-Theftcomm: [John] ``I'll finally be able to spend more time at
MITSFS.''  The use of words like ``incompetent'' featured large in his
resignation letter.

Theftcomm: The Tyrannical Iron Fist sheets will probably rotate in June.

Analogcomm: The hours request envelope is up.

The Star Chamber has been slightly less lame recently, as we have plastic
now, but no money quite yet.  Soon, though, as the forms have been turned
in for the transfer.

Pianocomm: We have a new keyholder, Susan Born.  She will be SEB to avoid
the SB confusion with JSB?

Pseudo-Bluebellcomm: We have gloriously large amounts of covering material,
and already four covered books to show for it, due to the efforts of
prentice Emily.

Minicult: The brothels in Tazmania have been put on alert because a US
aircraft carrier is coming into port.  Apparently they wore out the workers
in Perth a few months ago.  [John] ``Be proud of our men in white.''

\goto{Old Business}

We got a letter from Sherrian Lea with a wonderfully overdone story about
avoiding a \$2 overdue fine, due to a tongue-in-cheek poke sent by the VGG.

Ex-Skinner Tim Huckleberry '84 is now at Games Workshop and is arranging to
get us some of their Black Library stuff.

ALGOL!

\goto{New Business}

NASA is irradiating plants with microwaves to see what happens.  ``Are these
live plants or dead plants?''  ``At the beginning or end of the process?''

This veers into a discussion of power satellites, the Illuminati, NASA,
orbital mind control lasers, and using atomic bombs to light cigarettes.

We have a new filing cabinet thrown out by the UA.  Or are our file
cabinets breeding?  In any case we'll use it to replace one in Damnation
Alley that's rusty.  At the moment it may be permanently locked until we
set jhawk loose on it.

A new Finboard request was put in.  Just a usual request, since we don't
have to refrain any more in order to put in a big request for the Reading
Room move.

Outside bank accounts for groups are apparently going away.  This sucks,
and was only even announced now because the info was leaked.

The Los Angeles Sci-Fi Society, to support the war against terrorism,
will pull sensitive materials from their site... or put some up and then
pull it if there isn't any there already.

Motion: MITSFS should support the war on terrorism by reporting the
LASFS to the government and then claim their Century Fund as war spoils.
Passes everyone--traitors--the faint of heart+Spehn.

\goto{Future Business}

Elections are in one week in 5-216, the Star Chamber, with even more
in-jokes.  The picnic is the following day, meeting at the library at
10:00 am.  At the moment we even have enough cars.

A discussion of rental cars and paddle-shifting in particular.  Audi
faked gears in their continuously-variable transmission to avoid
confusing people.  There is a suggestion to put speakers in electric
cars to make engine noises for the benefit of pedestrians.

The summer rates will shortly go up.  We will even have a summer-only
membership, since the VGG approved the idea.

We never actually check to see whether non-members pay us \$2 for the
picnic, although it doesn't come up much.  Old picnic invitations have
references to co-ed members making the sandwiches.

In the next two weeks, Emily will become famous as the designated
{\em Star Wars} fan in a Boston {\em Herald} story.  A discussion of
the {\em Star Wars} movies, old and new, and special effects, old and
new.  There is an ASCII animation of {\em Star Wars} on the web.

No one is planning to graduate soon...

Susan is now sweeping the library as part of her new keyholder duties.

Jamie tries to get people to sing, to no avail.

Motion: Miller motion.  Fails 2--3--2+Spehn.

Jamie tells people the lyrics to the adjournment song.  John tells a
story about rabbits and the use of their tails to hide themselves.

Motion: Second Miller motion.  Not seconded.

Motion: Third Miller motion.  Third second!  Passes 5--0--3+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1742.3 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
