\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/23/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 23, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding; Andrew Boardman, unreasonable facsimile of the Onseck, recording.

[AMB] The mysteriously terse and unlikely minutes were read.

A motion was made to commend the minutes as tragic and poignant, which did nothing, 4/4/1+.

\goto{Committee Reports}

[JFC] Mobcomm reports the acquisition of hardcovers, somewhat under budget, due to a misapprehension of our prevailing discount at NEMBF. Due to this misapprehension, the new Battlestar Galactica sagas from Richard Hatch remain unbought. So sad.

The equivalency of space and money, particularly as it applies to Library acquisitions, is discussed.

[JFC] Bluebellcomm has covered a book!

[JM] The War Council reports not much happening with our Fifth Floor colonization plans; there's a proposal floating around in AdminSpace, but nothing much has happened lately. Nothing is blocked on any action by MITSFS, anyway.

[JFC] pseudoFweekcomm: They're here... Midway is in a week! Any volunteers?

Leaks in the stacks are reported, with the relevant sections now under plastic covers; fixit was called but couldn't find them. They're due to be called again with more precise directions.

[JM] The Dexmistress will print a new dex tonight.

\goto{Old Business}

Our sign, as previously noted, has broken.  The ESG sign has now done the same. (In sympathy?)

\goto{New Business}

A delightfully apologetic yet hopeful letter was received from T. Mandalay, along with eight copies of Terrapin Or; [insert full title]. Three have been committed to the Library, while the rest are being given away.

[JM]: The dexmistress reports that AMB has been naughty, specifically by dint of recording large "RH" paperbacks as "P" in the signout sheets. AMB is dubious but repentant.

[AMB]: TZ RSN. Ed promises a rant.

[AMB]: Our Asimov's and Analog subscriptions will hopefully get 20 year renewals this week.

[JM]: JM has moved, and is now more than five minutes from campus. The end of the world as we know it?  He'll have to get up earlier for meetings, anyway.

\goto{Future Business}

The impending return of keyholders, and commensurate filling-in of holes in the schedule, is discussed with great hope.

[JFC]: JFC is finished. Snakes fear him. The squirrels have gone underground.

JFC, not finished after all, reads the blurbs from romance novel sales catalog..

The reasons for this are unclear, but seem rooted in tradition. One new novel recounts the tale of a handsome and manly software engineer, inferred to be male (there must be one in the galaxy, yes?), and the woman who loves him.  All goes sour when he (predictably) turns out to be gay. (Or something like that.)

JFC moves to commend Shannon Donnelly for committing to paper the sad yet inspiration tale of Elanor Glover; shy Elanor Glover agrees to a marriage of convenience--and a Christmas Eve wedding--to Geoffrey Westerly, Lord Staines, to please Westerly's dying father. But the only wedding gift Elanor desires is the only thing she things he won't give her---his banana. Motion passes, 3/1/2+.

\vspace{12pt}

\noindent
Meeting adjourned, 1742 SST.

\vspace{18pt}

\centerline{Irrespectfully submitted,}
\centerline{Andrew Boardman, just an Onseck kinda guy}

\end{document}
