\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/8/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 8, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1705 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the differentially frazzled Onseck.

Minutes read.

Motion: Commend the minutes as ``...and we would have done it too,
if it weren't for you kids and your pesky neutrinos!''  Motion does
nothing by a count the Onseck failed to note.

\goto{Committee Reports}

Mobcomm: Another box(es) of British books is/are in the mail, but
not including {\em The Skinner}.  Another book by Roberts with a
short title: {\em On}, {\em Salt}, and something else.  Is the
sequel to {\em On} called {\em No} or {\em Off}?

John still intends to write a book review in March of some year.

A discussion of the ultraspace field theory that someone sent us to
review.  We still have the Dean drive patent application in our
files somwehere.  There was an old {\em Twilight Zine} story about
the MITSFS conquering the universe with a working Dean drive.

Pseudo-Pianocomm: Shanna and Emily are doing Bluebellcomm and
Panthercomm work, and shelving stuff next week.

Mobcomm$_2$: I still want \$900.  We need to do a transfer to get it.

\goto{Old Business}

It is another youth-dominated meeting.  Is Jade a grad student or an
undergrad or both?  There is a horrible digression about the eigenstates
of the Skinner.

Progress from the War Council?  Should we encourage prentices to run
for office?

Usual stuff.  Usual Jade ALGOL: ``What's going on?''

\goto{New Business}

[John] ``Jamie fined me yesterday, and I will have my revenge.''  His
wrath should actually be directed to Jenwa and Steph.

The Onseck is chastised by a member for being so out of date with
minutes on the web.

Pseudo-Theftcomm: [John] ``I am winning again!''

\goto{Future Business}

A comparison of the online minutes to real meetings.  The Onseck is
chastised again for sometimes using actual intelligible English.
The next meeting should be all in equations... from the ultraspace
field theory!

Glen Cook's next novel {\em Angry Lead Skies} is coming out next
month.  Discussion of various alloys... solder, pewter, etc.

We will in the future get a large donation once an alum dies.  This
may be soon due to the danger posed by a too-full home library?

In the future Jen Chung will try to put some for-sale books on eBay.
She is an eBay addict and is collecting plush chocobos.

Motion: Boost our eBay profits by including a banana-flavored thing
with every box of books.  Passes 8--2--... 2+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
