\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/12/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 12, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, ``late'' SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the tax-dreading Onseck.

Jade is sleeping... 1700 SST... 1710 SST... 1720 SST... 1730 SST...
1740 SST...

Jade bings the gavel by an amazing display of telekinesis, courtesy
of Jamie's arm.

Minutes read.

Motion: Denounce the minutes as a hyperintelligent squirrel plot.
Passes 7--0--2+Spehn.

Jade is sleepy and moving in slow motion.  Jamie continues to bing
quietly for her.

Motion: Denounce the minutes as not noting ``I'' wasn't present.
Passes 7--0--1+Spehn.

\goto{Committee Reports}

Dexmistress: The reserve paperback shelves have new labels.

War Council: Ed gives a report on the first meeting of the Reading
Room working group, but since he's giving the report he didn't get
a chance to write any of it down here simultaneously.

Bluebellcomm: Ed is lame.  Also, one of the Jordan books actually
wore out its plastic cover.  [John] ``It was one of the early ones...
you know, where things happen.''

Motion: Have the Onseck look suitably ashamed of himself.  Jade wakes
up to call a vote.  Fails 4--8--3+Spehn.

There follows a discussion on sleep deprivation.  [Jamie] ``It works
better now that I'm on amphetamines.''  There is a rumor of a drug
being tested by the FDA which completely removes the need for sleep,
apparently now being prescribed for narcolepsy.  A discussion of
possible psychological effects.

Motion: Encourage LaVerde's not to sell this drug.  Not seconded.
Jade gives her philosophy on drug control: ``You shouldn't restrict
anything, because it'll weed out all the dumbasses in the world.''

Google is put forward as an extension of one's long-term memory.
[Jamie] ``I consider it an extension of my senses.''

Motion: Do a series of experiments on the drug with hyperintelligent
squirrels out to the LD50 level.  Passes 7--4--0+Spehn.

Mobcomm$_2$: After some quick accounting, it turns out that we've
been spending about \$6500/year on books.  [Sam] ``It is good for
libraries to buy books.''

\goto{Old Business}

Bob Klein actually made a large donation on Saturday, a big pile
of boxes which is reportedly about half of what he has to give us.
The rest is probably to come after we finish processing this.

John has heard of rumors about a squirrel-proof birdfeeder, which tips
over when a squirrel climbs on it.  One variant of this might actually
be illegal due to cruelty to squirrels.

It is noted that the ideal bird-feeder is {\em almost} squirrel-proof,
so you can watch them try over and over again.  Reportedly adding
capsaicin to the seeds annoys the squirrels but not the birds.

[Jade] ``I'm tired, let's go home.''

A random thing found at Palmer and Dodge: an ad for a book on how to
use science in legal arguments.  There's no particular emphasis on
actual scientific evidence, just how to argue with confidence.

Usual stuff.

\goto{New Business}

John discovered the books {\em Satan's Mistress}, {\em Satan's Love
Child}, etc.

Motion: Feed Satan's mistress a banana.  Fails 2--8--0+Spehn.

Andrew Boardman went to a British con and came back with a bunch
of free books, which were mostly given to us.

Motion: Put Satan's mistress in a birdfeeder for hyperintelligent
squirrels... blah blah blah banana.  No, wait, {\em give} her a banana
and put her in one of those new birdcages so we can see squirrels fall
and break their backs.  Passes.

\vspace{12pt}

\noindent
Meeting adjourned, ``late'' SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
