\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}


\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/06/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 6, 2002

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

MITSFS meeting called to order, Friday December the 6th, at 1700 SST.  Ed Keyes is the President and Skinner, presiding, and Andrew Clough is the Onseck.

John, last week's pseudo-Onseck reads the minutes, since he is needed to decompress them.  He succeeds, though with with frequent interruptions.

Motion: Accept minutes as being ``Screened but not filtered.''  Passes 6-0-4+Spehn.
lat
\goto{Committee Reports}

Bondagecomm:  Covers and bindings have been gotten.  They should have everything together to send next week.  There is a surprising and pleasing agreement on color.

Motion:  Write to ACME bindings to see if they can give us a bound Roadrunner.  Passes 6-0-3+Spehn.

War council:  UA decided not only not to approve, but passed a different proposal taking out the parts benefiting us.  We still hope though, as the decision percolates upwards.  Luckily, the UA proposal doesn't contradict ours, it just subtracts the good stuff.

Here, one of our new members comes to return a book, and luckily is prevented from taking his book into the back (where the Defbots would shoot him).

Bluebellcomm:  Mostly lame.

\goto{Old Business}

MIT endowment grant has lost value, so there is no longer any interest on student accounts. :'(

We're getting copies of the Fandom Dictionary.

\goto{New Business}

Due to impending IAP, it might be time for boxing of excess copies.

We could get more room by saying that the books must be returned *exactly* 3 weeks after they are taken out.  This would get us more money too...

Discussion of the True Names of authors.

Margaret upon seeing the Black Library sheet:  ``Mwi Mwi Mwi Mwi!''
John:  ``Do you want to see?''
Margaret:  ``Nyaaaaay!''

Discussion of Casino Royal.  The look on the skinners face after John mentions that Woody Allen might have been bond was very memorable.

\goto{Future Business}

$ \exists $ tours in IAP.

The new books inquiry is answered.  The correct book was, in fact, a book of time travel stories, which is why this appears in Future business instead of Old Business.

Miller Motion: Universe saves 2-10-3+Spehn.

Miller Motion: We go eat 10-3-1+Spehn.

\vspace{18pt}
\begin{center}

Respectfully Submitted,
Andrew Clough, Onseck

\end{center}
\end{document}
