\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/18/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 18, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, John Carr, Pseudo-President and Skinner, presiding.  Ed Keyes is the ultra-low-power Onseck.

Minutes skim-read.

(John) "We buy the books, we run the library."

M: approve the minutes as practically perfect in every way. Amended as impractically perfect. 2-0-0 +Spehn.

\goto{Committee Reports}

The Onseck's rug has been rotated.

Mobcomm: a year ago got us a subscription to a British publisher, a book a month. Falling behind, new offer for a book every quarter.

The stealth Bluebellcommer has been at work again.

\goto{Old Business}

The skinner is not here, nor the Chancellor. (John) "The Guild must die."

Damnation Alley still closed.

Usual motion.

\goto{New Business}

The new Lackey books is about to circulate, but have no fear, because two more are already in the pipeline.

"Bikini Planet" is better than it looks. A thousand words versus a picture...

Someone called up and insisted we were a writing group. Also insisted that NESFA has a regular schedule.

Pseudo-Theftcomm: Dave Kern is about to hit the bottom of the TIF.

Ed claims the 5-6 hour today.

Greg Bear wrote a book about bacteria ruling the Earth. Tapping into the power of mitochondria...

\goto{Future Business}

(John) "Sing for me, Onseck."

M: bacteria-infested rotting bananas could rule the world. (John) "I'd do what they told me." Passes yoga exercise-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1718 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
