\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/22/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 22, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Stephanie Fried, LHE and
Pseudo-Skinner, presiding.  Ed Keyes is the too-to-two Onseck.

Minutes read.  Applause.

Motion: Condemn the minutes as falsely implying unanimity on the
criticism of Tad Williams.  Chickens 5--5--5+Spehn.

A discussion of who Spehn was and why.

\goto{Committee Reports}

Chronicomm: It's out!  It's out!!  It's OUT!!!  There was a big
envelope-stuffing party yesterday, and we filled up two mailboxes.
The newsletter was sent out to alums and interesting folks.

[Jamie] ``Steph isn't ripe yet, so she doesn't get one.''  Young and
succulent indeed.  Jamie is too bony to be succulent, it is noted.

A discussion about the use of botulism poison to prevent wrinkles.
People are confusing this with the use of bubonic plague.  Food
poisoning on your forehead.  [John] ``What if you lick the person's
forehead?''

Mobcomm: We didn't do anything at all this week, except for starting
a list of books we don't have.

Pseudo-Pianocomm: Andy became a prentice.  Brian Sniffen also became
a prentice, yay.  Bluebellcomm stuff in progress.  Eric Armstrong
offered to help repair books.

\goto{Old Business}

{\em SNF}!  It's done!  It's done!  Ed can have his key finally.
There follows a discussion of the symbolism of keys versus cards,
and banana-shaped keys.

This segues into a discussion of all of the banana-shaped things
in the library.  The Skinner's studded leather banana is pulled out,
causing a member to remark, ``Oh wow, that's... special.''

A discussion of time-sharing Jens.  ``I'll trade you two units of
Jen Chung for a unit of Jen Clay.''

[Laura] ``I'm going to hide behind my hair now.''  This is one of the
least old meetings in a while due to all the people Steph brought.

Usual stuff.

\goto{New Business}

We have two new sponges, to be used with non-adhesive stamps.

[Steph] ``Become an apprentice.''  ``Why?''  ``To stop me from killing
you.''  This argument, plus a few others, appears to work.

When Ed thinks of cloning, corruption, and power, he thinks of John.
Namely a flyer for a book.

Potatoes from flakes?  Are flakes better than powder?  Can you deep-fry
either of them?  Deep-fried mashed-potato balls with cheese.  [John]
``I'd eat those.''  Do it twice to get an extra coating, like candles.
There is a discussion of whether potatoes are flammable.  Almost
everything is flammable with enough heat and oxygen, except maybe
sapphires.

``She's like an angst vampire with a soul.''  ``Jen Clay will eat us
all!!!''  Angst agriculture for civilized angst vampires.

[Laura] ``You're talking about me!  You're talking about me talking!''
Steph is planning to use Laura's voice for some sort of music project.
John pulls out Tarl, but it was just a bluff.  Laura proceeds to squeak,
and John pulls out the oil.  Harmful or fatal if swallowed...

[Laura] ``So... about that monkey...''

Jamie looks for volunteers on Monday for a shelving expedition from among
the new prentices.

\goto{Future Business}

John pulls out a CD for Steph to destroy.  [John] ``Would you like
Earthlink or Cocoa Puffs?''  BANG!  BANG!  CLANG!  THUD THUD BING!
Everyone gathers around to examine the shards, and admires them.

[Laura] ``Ooooh I wish I were an Oscar Monkey weiner...''

Motion: [Laura, singing] ``Bananas... in pajamas... are coming down
the stairs.''  Passes 7--0--0+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1750 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
