\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad M/D/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, Mass.  02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, 21 June, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Our beloved Ed, President and
Skinner, presiding.  Andrew Boardman seems to be the Onseck.

Minutes read.

Move to accept the minutes as transparent passes, 4/0/1+. \bing

\goto{Committee Reports}

pseudoPlantcomm: the curculation room now has an ADA-compliant handle.
The doors with handles instead of knobs are reported to have an added
feature: an intellgent pit bull can learn to open them.  Why this is
relevant to MITSFS remains blissfully unclear.

Mobcomm is uncharacteristically speechless.  This is seconded, and does
nothing, 4/0/3+. \bing

Eos has provided us with a new review hardcover!  A review will, of
course, be written.  Newly review books: 'Light Music' by Goonan, and an
advance proof of 'Across the Nightingale Floor' by Hearn.

Mobcomm goes on at great length.  (Some things just don't last.)

Pianocomm reports a new prentice, in the person of Ariel Segall.  Yay Ariel.

The interim Onseck is promised bits.

The Skinner is going to go to Tennesee to attempt to get run over by a
bus.  This has made a lot of people very angry and been generally
regarded as a bad idea.

\goto{Old Business}

A report has surfaced that T. C. Skinner has been enrolled in the
International Bananna Club, some number of years ago.  Not that they've
sent us anything.  But they have a web site.

Andrew Boardman has been ratified as Onseck.

\goto{New Business}

Many new books are about to become non-new books.  Come and get 'em!

A new donation: Harry Potter and the Philosopher's Stone.

\goto{Future Business}

The skinner is leaving!  (Long live the skinner!)

We got some new members this week!

Jen Chung will be putting books on Ebay!

The pinkdex stuff was dealt with!  The libraries should be paying us for
it forthwith!

The forthcoming book list has been received from Space-Crime-Continuum.
JFC wants to sit down with a star chamber member and think about where
our money is going and whether we want it to keep going there.

TZ Real Soon Now.

Miller motion with a bananna on top is irregularly seconded and chickens,
1/3/8+.

Second miller motion with a bannna on top is seconded and passes,
2/1/1+. \bing

\vspace{12pt}

\noindent
Meeting adjourned, 17:47 SST.

\vspace{18pt}

\centerline{Irrespectfully submitted,}
\centerline{Andrew Boardman, pseudoOnseck}

\end{document}
