\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/19/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 19, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1715 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the hour-early Onseck.

Minutes read.

Motion: Note that unlike the old Ace Doubles, the minutes make the
Onseck look stupid because he's reading things sideways.  (The Ace
Doubles made you look stupid because you looked like you were reading
them upside-down.)  Passes 4--0--0+Spehn.

Motion: Commend the minutes for a detailed reporting of the
beginning of the meeting.  Passes 4--0--0+Spehn.

\goto{Committee Reports}

Mobcomm, Bluebellcomm, and general lameness-comm: We have no money,
so we're not getting books.  And we have no book-covering material,
so we're not covering any.  John's life is very easy.  The Onseck
tries to explain how we're not actually {\em out} of covering
material, but only out of the {\em good} covering material, but is
ignored and laughed at.

Mobcomm$_2$: Stuff is still trickling in from things John started
before we ran out of money, though.

Jadecomm: Jade is wearing mismatched hair constrictors.  The color
is somewhat trying to match the blue-green {\em Skinner} book.

Chronicomm: We sent out four more {\em SNF}'s, retrying addresses that
had been fixed from feedback on earlier cycles.  This is probably
the last of the batch, and responses have tapered off too.

Cofincomm: Can't seem to find a good physical address for him.  (The
Onseck needs to look up this reference in the Lore.)

Pianocomm: Two Andrews are shortly coming on-line as keyholders.

Pseudo-Jourcomm: Probably a skinny {\em TZ} RSN.  John still claims
to be doing a review some March, but he has to reread the book in
question now since he's kind of forgotten what it was about.

Mobcomm$_3$: Mobcomm takes no credit for getting our copy of the
latest Laurell K. Hamilton fantasy porn book, {\em Caress of
Twilight}.  [Jade] ``You don't believe in pointless sex scenes?''

Jen Clay's committee, formerly Pubcomm, is now hBarcomm.  For the
record, that is obtained by the sequence publicity to pub to bar,
and then adding the ``h'' as a reference to a sci-fi story which
used ``bheer'' to denote non-alcoholic beer.  The coincidence with
Planck's h-bar is pure happenstance, of course...  The ``h'' is
silent when pronounced, by the way, but its committee folder is
naturally still alphabetized under ``h''.

\goto{Old Business}

John just finished {\em Satan's Mistress} before the meeting.
[Jade] ``Don't tell us about it.''  Now he has to read the sequels.
It is described as sort of Lovecraftian.

Armenard reports that the renovation costs for the Reading Room
are expected to be \$100,000.  It is unclear what this actually
includes in the way of things bought for the Society versus things
bought for the rest of the room.

John fears that the battle against the hyperintelligent squirrels
is lost.  They somehow mind-controlled John's mother into just giving
them nuts, bypassing the bird-feeders entirely.

The T-shirts are running out, and we'll be putting in a replacement
order soon, possibly with APO now that their screen-printing people
are on the ball again.  The ``psi-phi'' shirts seem to sell a little
better.

\goto{New Business}

The Chancellor tries to get the Skinner to chant the ALGOL and
uphold the sacred traditions of the Society.  She's having none of it.

The Oxford English Dictionary has started putting in words from fandom,
and are asking for early citations.  Jamie found three of those for
them, from first editions we happened to have and a 1950 fanzine.

On Saturday, the LPs and that general corner of the reserve room were
moved into an ``artistically exciting'' arrangement.  Namely one that
is an efficient use of space.  John attempts to demonstrate how members
can get their heads stuck in the shelves.  Jade tests and pronounces
it suitable.

A new filing cabinet was inserted, and a rearrangement is in progress.
The banana-colored couch is finally free!  You can actually sit and
even lie down on it!

And Damnation Alley is now open again.  John goes in search of {\em
Satan's Love Child} in special reserve.

\goto{Future Business}

Ingram (a major book distributor that the Space-Crime Continuum uses)
has a section which sells directly to libraries at a 40\% discount,
compared to the 20\% we get from SCC.  We should pursue this to see
if we can switch, and perhaps hardcovers as well.

Motion: Investigate whether Ingram has a special section catering
to hyperintelligent squirrels and bananas.  Passes 5--0--2+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

[John] ``A squirrel was looking at me funny yesterday.''

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
