\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 8 February 2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 8, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and Skinner,
presiding.
John Carr is the reluctant pseudo-onseck, persuaded by Jade's amazing
pre-meeting stretch to overcome his laziness.

Minutes read.

Motion: Commend the pseudo-onseck.

Motion: Condemn the pseudo-onseck for reading the minutes all in
the same font.  The pseudo-onseck defends himself by pointing out
that although the minutes may have been read in a single font
family, they were {\em not} in a single font.

Motion: Tell us Isaac Asimov's shocking secret!

The pseudo-onseck calls for a matrix vote but somebody objects that
none of the motions were seconded.

Motion: Condemn the lack of interpretive dancing accompanying the
reading of the minutes.  John offers to dance.  The motion chickens
\hbox{3-0-4+Spehn}.  John starts to read the minutes again while
dancing.  Jade pretends to cover her eyes, but she was peeking.

\goto{Committee Reports}

Jade talks to Jamie about LHE stuff.  SFBC bills are cumulative so
we don't pay all the latest bill, only the part for which there is
no check in transit.  ``I'm so confused,'' says Jade as usual.

Pseudo-theftcomm: Jamie stared at the TIF for a long time before
the meeting.

Pseudo-ROSFAP: ROSFAP answered the mail from the guy offering to index
our fanzines.

Pseudo-panthercomm: The new book shelf will explode soon.

Pseudo-dexmistress: Jamie got hole punched paper.

Mobcomm: Two boxes of books from Wildside Press arrived this week.

Mobcomm$_2$: The last British book arrived, replacing a copy that fell
out of a hole in one of the boxes containing the last shipment.

Mobcomm$_3$: About fifty books from the Space-Crime Continuum arrived
today.  None of them are new and interesting.  Some of them are old
and interesting.

Mobcomm$_4$: The mobcomm box contained a new Robert Rankin book.

Mobcomm$_5$: I'm going to ask for \$700 as soon as I figure out
the pound-dollar exchange rate.

Pianocomm: Prentice Laura came with parents.

Pseudo-bluebellcomm: Bluebellcomm may be lame.

Pseudo-alohalenscomm: I will start stalking DRK soon.

\goto{New Business}

Object bashing is postponed until next Friday.

\goto{Old Business}

Jamie tossed a bunch of old stuff (three computers, and soon
typewriters and Tarl).

Rearrangement continues.

JFC put tops on two shelves without losing his thumbs.

Two new shelf faces are coming this weekend.

Jade reads a card from Aaron and Yevgeniya (mailed early December,
received late January, forgotten last week).

Is
\begin{picture}(20,20)
        \put(10,6){\circle{12}}
        \put(10,6){\circle*{1}}
        \put( 8,8){\circle*{1}}
        \put(12,8){\circle*{1}}
        \qbezier(10.0,2.5)(12.5,2.6)(13.5,5.0)
        \qbezier(10.0,2.5)( 7.5,2.6)( 6.5,5.0)
\end{picture}
a smiley face?
Jade says no, because it has a nose.  Is it a smiley nose-face then?

Motion: Condemn the Skinner for having a nose and therefore never
smiling.  Passes \hbox{5-0-Spehn+1}.

Old Skinner Rob Bernstein '76 is coming Monday.

\goto{Future Business}

SNF Real Soon Now!

SFBC will be paid, after weeks of discussion.

Jade's lab got a monochrometer.  Apparently this is a device that
measures a fixed frequency.  It is calibrated by the manufacturer
by applying adhesive numbers to show the frequency it will report.
FROGs will devour Jade.

Motion: Jade and a large, sensuous frog with a banana.  Passes \hbox{4-1-Spehn}.

\vspace{12pt}

\noindent
Meeting adjourned, something$^3$.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, the dancing pseudo-onseck}

\end{document}
