\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 9/6/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 6th, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Jamie Morris, pseudo-Onseck, recording.

Minutes read.

Move to burn the minutes and bury them where nobody will ever find them
again.  Maybe in the Onseck slot?  Passes 3--0--1+Spehn.

\goto{Committee Reports}

Mobcomm: Has anyone heard of the ``Dumarest of Terra'' series?  (We have now.)
Well, we just got the conclusion.  I thought the series was well-known but
nobody I've asked has heard of it.  Along with it we got a dozen books by
the same author that we didn't have, possibly due to being British 
publications.

Gryphon publications has come out with their own line of doubles.
These are expected to make the Dexmistress gnash his teeth, but it is
revealed that since they're numbered they'll be handled by just sticking
an entry in the shelfcodes table.

Fweekcomm: A new member is reading books at a rate sufficient to finish
the Library during her lifetime, including new titles as they come in,
if she keeps it up.

\goto{Old Business}

Ironically, most Keyholders' photos on Rogues' Gallery are more
recognizable than Aloha Lenscomm's.

We have stickers!

AMB bought \$810 worth of subscriptions (renewals) to \emph{Analog}
and \emph{Isaac Asimov's Science Fiction Magazine} for us at WorldCon,
where they were offered for about 20\% off.

\texttt{ALGOL}.

\goto{New Business}

A mystery donation has appeared on the banana-colored couch.
Anyone know about it?

The author of \emph{On}, \emph{Salt}, and \emph{Stone}---those are three
different titles---has published ``Park Polar'' in \emph{Infinities}.
His multi-word-title capability is noted.

The mailing list of people who signed up for email information/reminders
(at the Activities Midway) has sixty-six usernames.  We've sold a bunch of
memberships but as usual it's hard to tell which are new and which are
renewals without resorting to the actual sheets.

\goto{Future Business}

Member Brad Johnson wants to become a Prentice (just renewed his membership
after a long lapse).

The new members this year seem to include more people inclined to have
interesting discussions about science fiction, as opposed to casual readers,
than there've been for a while.

Mobcomm starts rationing out horrible blurbs from his latest mailing
from the Space-Crime Continuum.

Motion to grow mutated bananas to read these things for us so we don't
have to bother with them ever again.  Fails for lack of a second.

This weekend our LSC slide should show.

Motion to \ldots{} banana\ldots{}.  Fails 1--3--4+Spehn.

Move to bring in a bunch of stuffed bananas so that we can
have a puppet government.  (Groans.)  Passes 5--0--2+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1742 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jamie Morris, pseudo-Onseck}

\end{document}
