\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}


\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/18/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 8, 2002

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting is called to order 1700SST.  Ed Keyes is the presiding president and skinner.  Andrew Clough is the not exceptionally punctual but still not late Onseck.

The Minutes are read.

Motion:  Change ``English'' to ``British.'' Passes 5-0-2+Spehn

\goto{Committee Reports}

Jourcomm:  TZ real...real soon now.

Pseudo-Pianocomm: $ \exists $ Enthusiastic Frosh.

Bluebellcomm:   Still lame, but the prentices aren't.

Pseudo-Borriscomm:  We should get a calender.

Some one tries to sit on the boxes.  ``Blast my foolish, poor eyes.''  ``Thats a flat surface, it must be used to sit on.''

War council:  Final (?) meeting of the moving group.

``In Kindergarten there were classes in basic body movements, are there any remedial courses here?''

The master central computer of Microsoft is in fact a SPAM filter, with interesting implications for TRON.

Mobcomm:  More books this weekend.

Mobcomm$_{2}$:  There is a great imbalance in the LP section that must be corrected by buying more books.  ``Millions of pages cried out in pain.''  ``When the cow decides that eating all the grass is its function, instead of producing milk, we turn into the Sahara.''

Animal Penicillin:  ``You should see the size of that petri dish''

Phonecomm:  \textbf{RING!}

``Its a mad chia cow!''

Motion:  Acquire a cattle prod to prevent mobcomm from turning us into the Sahara Desert.  No second.

Motion:  Commend voter apathy.  No second.

Motion:  Not have a matrix vote.  

Motion: A  Motion: B  Motion: C





\goto{Old Business}

Marcus was here, he may someday manage to become a prentice.

$\exists$Emily

Motion:  Give everybody a banana before they all leave.  Fails 6-7-4+Spehn.

Motion:  Use a cow magnet to clean up the blood from us hemorrhaging.  Passes 9-2-0+Spehn.

Reflections on teapots and bad sitcomms...And how the person with the teapot is the only one who doesn't know who it belongs too.

Miller motion: Universe is saved  4-8-3+Spehn.

Miller motion:  We go to eat 10-3-1+Spehn.
\vspace{18pt}
\begin{center}

Respectfully Submitted,
Andrew Clough, Onseck

\end{center}
\end{document}
