\documentclass{article}
\usepackage{fullpage}

\title{Minutes for 9/20/02}
\author{Andrew L Clough}

\begin{document}

\begin{center}
MIT Science Fiction Society\\
84 Massachusetts Avenue\\
Cambridge, MA 02139
\end{center}

\begin{center}
MITSFS Meeting Minutes\\
Friday, September 20, 2002\\
\end{center}

MITSFS meeting called to order, 1700 SST, Skinner Ed Keyes presiding.  Andrew Clough is the ever improving Onseck.

The minutes are read.

Motion: Was that last meeting?  Fails for lack of a second.


\textbf{BING!}
\begin{center}
\textit{Committee Reports}
\end{center}

Mobcomm: Buffy books are apparently considered children/young adult books.

Mobcomm$_2$: The new, Battlefield Earth 20th Century edition is coming
out.  On a related notes, it was false advertising way back when, when
a previous edition claimed that it would soon be made into two Major
Motion Pictures.  The sound track that came with this earlier edition
also lacked instructions, such as ``play it loud with the lights off.''
There is a general agreement that headlights don't count here.

Phonecomm: Ring!

Motion:  Commend the losing of Battlefield Earth books.  Chickens, 2-2-3+Spehn.


\textbf{BING!}
\begin{center}
\textit{Old Business}
\end{center}

The Onseck (that's me) recently learned how to use \LaTeX, and type up the minutes.  Learning to print, and then to spell are on the list.

In the old days, cavemen typed up their documents on dedicated electronics, which only worked as word processors and nothing else.  

The existence of people majoring in Materials Science is debated.

Usual stuff

Our bank account has bottomed out.


\textbf{BING!}
\begin{center}
\textit{Timewarp To: Committee Reports}
\end{center}

Pseudo-Jourcomm: TZ real soon now, like maybe March.


\textbf{BING!}
\begin{center}
\textit{Future Business}
\end{center}

We got trade advances for October

Due to endowment returns being calculated over the average of 5 years, we're still in the dotcom boom.  

Out way of securing our safe is analogous to that of our countries way of securing its nuclear devices, in that there is no one person who both knows the combination and the special technique of entering it.

Motion:  Get a new safe, which needs both a combination and the consumption of a banana within 30ft to open.  Passes 8-0-2+Spehn

Meeting is adjourned, 1739 SST



\begin{center}
Respectfully submitted,\\
Andrew Clough, Onseck
\footnote{With stealth spell-checking and error-correction by John Carr}
\end{center}

P.S.  We forgot to read the synopsis from {\em The Big Book of Lesbian Horse Stories}.

\end{document}





