\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/7/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 7, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order with a horrible {\bf BiNg}, 1700 SDT,
The usual Ed Keyes, President and Skinner, presiding.
John Carr is the pseudo-onseck.

Minutes read.

Jamie's remarks are not recorded.

Motion: Commend the minutes for clarity.  Passes \hbox{6-1-2+Spehn}.

\goto{Committee Reports}

Mobcomm[JFC]: New books coming soon.

Mobcomm$_2$[JFC]: Will work on budgeting soon.  Need to get into the
locked LHE drawer.

Old people are here, with young people in tow.  One visitor --- an MIT
alum from the 1980s --- wants to buy a summer membership to check out
Lord of the Rings for one night.  The price structure is explained.
On hearing the difference between temporary and permanent life
memberships a little girl comments ``that's just wonderful, daddy.''
A boy (class of 2010) grabs the gavel and practices binging.

Pseudo-jourcomm[JM]: TZ not real soon now because JFC hasn't submitted
a review.

\goto{Old Business}

Jamie has a bunch of rolled pennies, mostly thanks to Dawn Perlner,
and will try to deposit them.

Is the universe older than MITSFS?  Or was all ancient history
created along with MITSFS in 1949?

Derrick Kong walked in.  There is a discussion of library crowding
and the 5$^{\rm th}$ floor reading room.

Recent research determined that large dinosaurs were probably not
capable of running.  Scientists compared dinosaurs to some of their
closest living relatives, chickens and alligators.  The square-cube
law says chickens can run but dinosaurs can't.  {\em Science News}
magazine had an article summarizing the paper.  An illustration showed
a scaled up chicken running alongside a T. Rex.

Jamie remarks ``the Olympics are being sued by alligators for racism.''

The life membership is a great deal for a ten year old.

We got the warhammer books, for free.  The books have both US and UK
prices on the cover.

We still have Marcus' {\em Analog} donation sitting on the souch.

\goto{New Business}

\vspace{12pt}

All of the new business was time warped to other parts of the minutes.

\goto{Future Business}

\vspace{12pt}

Ed wants to leave by 7:00.

Ed describes a scale-invariant paper.  The pseudo-onseck didn't get
the joke and will not attempt to explain.

A Chinese newspaper with circulation over one million reported an {\em
Onion} article as fact.  They did not publish a retraction.

Ed wants to leave every meeting by 7:00.  JFC should add the Anime
club to his list of groups to destroy.

Motion: Nail Ed's foot to the floor.  Chickens \hbox{2-0-7+Spehn}.

Miller motion!  Second.  Fails, \hbox{3-7-Spehn}.

Second Miller motion, with a banana on top!  Second with whipped
cream.  All in favor with a cherry on top?  Passes \hbox{4-6-Spehn}?

\noindent
Meeting adjourned, 17:53 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-onseck}

\end{document}
