\documentclass{article}
\usepackage{fullpage}
\title{Minutes for 10/4/02}
\author{Andrew Clough}
\begin{document}

\begin{center}
MIT Science Fiction Society\
84 Massachusetts Avenue\
Cambridge, MA 02139\
\end{center}

\begin{center}
MITSFS Meeting Minutes\
Friday, October 4, 2002\
\end{center}

Meeting Called to order at 1700 SST, Ed Keyes, president and skinner, presiding.  Andrew Clough is the punctual Onseck.\

The Minutes are read, such as they are.\

Motion: ``I don't have anything to say without ``banana'' in it.'' Fails 4-2-8+Spehn.\

Motion:  ``Commend the minutes as read with a goatee.''  Passes 7-0-1+Spehn.\

\textbf{BING!}
\begin{center}
\textit{Committee Reports}
\end{center}

Mobcomm:  The books just keep coming, I can't stop them.\

Skinner:  ``If it doesn't look like a bill, we won't treat it like a bill.''\

Pseudo-bluebellcom:  The big mess of RO week hardcovers is circulating.\

Pseudo-Theftcomm:  ARM is no longer underflowing.\

Motion:  Lower people who fall off TIF into a vat of leeches.  Passes 5-0-2+Spehn\

Foocom:  Frosh mail sent, lists updated.\

Pseudo-bluebellcom:  Did a little postering.\

\textbf{BING!}
\begin{center}
\textit{Old Business}
\end{center}

A member from 1968 came i and commented on his being happy that he was still getting ``Still Not Fans.''\

Due to the Magic of Technology, blackmail is getting easier.\

It is commented on that a new show is premiering at 3:00 AM.\

ALGOL\

Motion:  We reaffirm that Bruce Miller is still skiing with our comic books in Colorado.  Passes 8-0-1+Spehn\

Motion:  Condemn authors who put feet on Venus Flytraps.  Chickens 2-2-2+Spehn.\

New monitor stand!  Looks like another computer...\

Miller Motion: Fails 2-5-1+Spehn.\

Motion:  This is not a banana motion.  Passes 8-5-0+Spehn.\

Meeting is adjourned 5:37 SST.\

\begin{center}
Respectfully submitted,\
Andrew Clough, Onseck\
\end{center}
\end{document}
