\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/31/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 31, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding. [Unknown] is the Onseck.

Minutes read.

Motion to commend minutes for turning [illegible] around a few 360s. 2-1-3 +Spehn.

\goto{Committee Reports}

Mobcomm: decent pile of books waiting at Space Crime Continuum.

A discussion of things best not attempted while driving, like juggling.

Alohalenscomm: Susan almost came, but she learned John was here and decided not to go, claiming to have a "bad face day."

It is noted that when the orange-stickered gavel is taken to the picnic, the now-former skinner's authorization to take it out lapses, allowing us to extort money.

A [illegible] sound is noted from Damnation Alley.

Bluebellcomm: someone has emptied the Bluebellcomm shelf! Jen Clay is accused.

\goto{Old Business}

(John) "Hyper-intelligent squirrels appear to undergo lamenting rather than Darwinian evolution."

Motion to raid the hyperintelligent squirrels for spice. 4-2-0 +Spehn.

The mysterious noises from Damnation Alley appear to be Jourcomm.

A discussion follows on the organ trade, and the relation of the Commonwealth of Massachusetts to such. Will we see organ leggers soon?

ALGOL!

\goto{New Business}

Got a bunch of magazines.

John was almost attacked by ducks recently. Squirrels were in the area! Luckily ducks don't have teeth, but there are worries about the evolution of ducks into velociraptors.

Sam Shefield seems to have written both "Big Game" and "The Big Game." John, reading the books, finds no evidence of differing plots.

\goto{Future Business}

(John) "Soon we will eat."

Ex-skinner Huckelbery from Genres Workshop might get us some books.

(John) "Hungry!"

Discussion of the lore and history of Bondagecomm.

First motion to end meeting chickens 4-4-5 +Spehn.

Miller motion chickens 6-5-6 +Spehn after some prodding by the skinner.

Second Miller motion passes 5-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Onseck}

\end{document}
