\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/20/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 20, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, Chancellor and pseudo-Skinner, presiding.
John Carr is the by-popular-demand pseudo-Onseck.

Minutes read.

At first the Cambridge students refuse to make motions concerning
the minutes, or the reading thereof, but finally Joy moves to frame
and hang the minutes.  The motion passes \hbox{4-0-1+Spehn}.  Jamie
decided not to add ``and the pseudo-Onseck'' to the motion.

\goto{Committee Reports}

Mobcomm[JFC]: A big box of books from the Space Crime Continuum has
arrived to pack the ZGT.\footnote{This item was taken unchanged from
the October 18 minutes which the pseudo-Onseck used as a template.}

Pseudo-bluebellcomm[JFC]: Prentice Ariel covered some books.
JFC saw her and said ``come be my slave,'' and after some
reluctance (``what does that mean?'') she did.

Pseudo-surgeon[JM]: Jamie has repaired some of the high priority books
in the surgery.  Maybe.

There is a discussion of dinner, stalking, pika, Joy, editing Le Guin,
Banks to Britain, coals to Newcastle, and things called oysters that
are {\em not} oysters and should not be eaten.

Christine leaves us, as usual, but this time she doesn't even try to
make an excuse.

Pseudo-pianocomm: Will there be enough keyholders available to allow
the overeager prentices to complete their projects during the first
week of IAP?  Yes, says Jamie.  Past inefficiencies have been the
fault of undereager prentices.

Pseudo-hasslecomm[JFC]:  Armenard did a box (or partial box) of hasslecomm
books.  Only three overflow boxes to go!

Brad Johnson advises all present not to read {\em The Cybernetic Samurai}.
Jamie says ``too late.''

Theftcomm: The TIF rotated Tuesday night.  The IAP schedule is up and
sparsely populated as usual at this time.

\goto{Old Business}

More {\em Analog}s arrived this week!

The missing {\em Fandom Directory}s also arrived.

The usual stuff happens.

\goto{New Business}

Somebody offered to donate the Vance Integral Edition to the MIT Libraries.
The MIT Libraries offered it to us instead (conditional on the donor accepting
the transfer).  We will get 44 or 45 volumes.  We don't know if it will be the
special expensive version or the cheap thousand-dollar version.  It will be in
a specially designed font.  Jamie repeats his earlier criticism of the motives
and practices of the VIE team.

Jeff Noon books arrived in the latest box.  They have flashy covers and
very strange contents.

A prototype update of the member sheet is on the bulletin board.

Yesterday (near the end of exams) was very busy.

\vspace{12pt}

\goto{Future Business}

We discuss infiltrating the UA.

Another ambitious membership-rate-system-to-end-all-rate-systems will begin in
January.

Joy sings to end the meeting, but she is too good and the meeting continues.

Miller motion!  No second.

Banana motion.  No second.  The mention of plantains would have ensured a
second at a normal meeting but Jade is not here today.

Miller motion!  Fails!

Miller motion!  No second.

\vspace{12pt}

\noindent
Meeting asymptotically approaches adjournment, 1840 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-Onseck}

\end{document}
