\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/22/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 22, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the okay-now-I'm-ready Onseck.

Minutes read.  Jade excuses herself in the middle of the reading to
visit the little girls' room.  No one pays attention to the minutes.

Note that the minutes were ``Ed''ited as usual.

\goto{Committee Reports}

[John] ``Is that a coffee stain on your shirt?''  He was referring
to the Lucent logo on Jade's sweater.  Probably it's a blood stain,
since it's red.

Mobcomm: Nothing much to report.  This was after requesting the
Onseck to re-read back last week's report to check what had already
been said.

Bluebellcomm: A member of Bluebellcomm covered a few books.  We're
out of the short covering material.

Alohalenscomm: Finally got a picture of Deepak.

\goto{New Business}

Jamie is banging shelves in the circulating room.  BANG!  CLANG!  OW!
He's supervising construction of four of the lawyer shelves.  The old
shelves were difficult to remove, as they were stuck to the floor
with an impromptu glue.

We will get Joe Foley coming in here with power tools to complete
the disassembly.  [Jade] ``Remind me not to be here...''

The meeting is indeed loud enough to annoy, but not loud enough to
get complaints.  Yes!

We picked up a donation in Harvard Square.  Ten boxes of books, plus
a mint-condition {\em Star Trek} Barbie.

John consults his notes on things to talk about in the meeting.  He
reports that apparently someone tried to curse him, but that God is
missing... namely John witnessed but was not involved in three car
crashes in the last week.

Jade has to run away now.

Motion: Placate the great banana demon by leaving all the cool things
to report until next week.  Passes by Skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, ``17... like 20 or something'' SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
