\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/28/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 28, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, JM, Chancellor and Pseudo-Skinner, presiding, having killed Ed and stole his banner pages. JFC, flaming about ASA shell scripts, is the Pseudo-Onseck.

Minutes read from online.

M: condemn as online! 7 Luddites-1 other-0 +Spehn.

\goto{Committee Reports}

Pianocomm: prentice Eric has distributed the HA bubble space evenly. Prentice Ariel has done some Hasslecomming and will do more tonight. Erin is unaware that she should be teaching Eric surgery.

Minicult: 2002 Roswell UFO committee sent mail to MIT asking for something to be posted on a bulletin board. MIT sent it to W20-201, who sent it to us. 55th anniversary, sponsored by Roswell Chamber of Commerce! "Alien costumes are encouraged."

Mobcomm: Childhood's End, ISBN.

\goto{Old Business}

LHE gave letter from MITSFS to MIT treasurer to student activity financial office asking to close our bank account and send us a check. Don't know if SFBC check cleared; all before 2 weeks ago have.

ALGOL!

\goto{New Business}

Formerly new H's are waiting on the to-be-shelved pile. Prentice was supposed to go to JM for instructions but has not yet.

Speaking of prentices, Justin walks in!

"Attack of the bad Star Wars novels."

Long discussion of Star Wars and Star Trek and other big series.

\goto{Future Business}

M: give JM a banana for chopping off jhawk's head. 7-0-5 +Spehn.

"Who was the 7th vote?" John asks suspiciously.

"I don't record names of voters for privacy reasons."

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
