\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/10/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 10, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1715 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the sniff-sniff-these-are-my-last-minutes
Onseck.

Everyone moves over the 5-216, the Star Chamber.

Minutes read.

John corrects the minutes from a week ago: it is squirrels who use their
tails to hide themselves, not rabbits.

Motion: Laud the minutes to the heavens as being the proper end to the
mighty saga of Ed.  Passes 9--0--2+Spehn.

\goto{Committee Reports}

Pianocomm: We have food, a minivan reserved, and everything is proceeding
according to plan.  This makes us worried.

Pianocomm: Emily Warmann is a new keyholder, or will be when she reads
the keyholder notes.

Mobcomm: We're not doing anything because we have no money.

Pseudo-LHE: Stephanie promised John the head of Laurie Ward, or our
money.  The outside bank account stuff sucks.

Alohalenscomm: We're stalking all the new keyholders,  Susan is next on
the list... where does she live?  But watch out, since Susan has a lot of
assassin reflexes.

Discussion of how radiation affects digital cameras.

[Jamie] ``First rule of space exploration: let the next guy know what
killed you.''

hBarcomm: We need to make up a flyer for the summer mailing.  Will grab
someone to squeeze the creativity out of them.  Jamie found a pile from
1986 with cool blue pictures for their summer mailing.  [John] ``Hey, my
father got this when he was a freshman!''

\goto{Old Business}

Good resonance on the bings due to the tables in 5-216.

Another alum sent us mail asking if we wanted a donation of magazines.
{\em F\&SF} and {\em Galaxy} will be useful to us.

Usual stuff.

\goto{New Business}

Elections!

John is appointed Pseudo-LHE, and moves up into the position of power
next to Jade.  Only one decimal place is allowed this year.  Jamie
explains the election rules.  How does the ASA let us get away with this?
If no one objects, it's all good.

Any volunteers for the post of Vanna?  Emily is volunteered, and doesn't
object strenuously enough to avoid the duty.

Election of the Onseck!  The official candidate is Andrew Clough, which
is pronounced like ``enough''.  Other nominees are: the swarm of tissue-paper
fish, Andrew's shirt, Andrew's other shirts (let them fight it out), and
the hyperintelligent squirrel that was stalking John today.

Voting begins.  Other votes were variously cast for: ``I guess that looks
like Clough'', the trunk on many feet, impulsive fish, impressive frogs,
Clef (that should have an upside-down phonetic `e'), the expectation value
of Clough, \underline{\underline{Vanna}}, Fourier transform of tissue-paper
fish, squeeee, snuff for kids, swarm of hyperintelligent tissue-papered
squirrels, young visitor to Mars, squirrels rule, and Andrew Cl... Cl...
whatever.

The Pseudo-LHE tallies the votes.  [John] ``I'm curious to see what the
total adds up to.''  There were 10.3 votes cast by 10 people according to
John's math, and Andrew got 4.1 of them.

Second round of votes!  Additional votes were cast for: swarms of toilet
paper Cloughs, John's arithmetic, sounds like ``enough'', bow down to the
squirrels, (the bass clef sign), Vanna's second underscore, what's-his-name,
and Moose.

The Pseudo-LHE tallies again... 7.7 votes for Andrew, and Moose beat out
Squirrel.  [John] ``It adds up to 10.  Who cheated?''

Next, the election of the LHE!  The official candidate, not present, is
Stephanie Fried.  Other nominees include: she who is absent, that horrible
buzzing sound, sidhe who is absent, Qwlghmian-Australian conspiracy,
Bufferd, Bufford, Buffard, Aylee, Pete because he's evil, and Andrew again.

The voting begins.  Additional votes were cast for: Qwlghm Vowel Donation
Fund, she who isn't really absent but is just pretending to be, Hastur
Hastur Hastur, please tickle Jade, Alan Greenspan, laser death rays of
princes of Gor, Jade and her degree stripped washed and taken out to eat,
that'll teach her to be absent, Squirrel, Vanna (what no underscores?),
and Moose... with chocolate.

The votes are tallied.  Meanwhile Jamie explains about Hastur.  Actually
``Hastur'' is Babylonian for ``unspeakable'', and not his {\em real}
unspeakable name.  Steph wins with 5.5 votes, and Squirrel beat Moose
this time.

The election of the Vice!  The official candidate is Emily Warmann.  Other
nominees: the prettiest little underscore in Kansas (this was written by
Vanna as the ``previous'' little underscore), the subsequent little
underscore, Darth Vader, Darth Vanna, her hordes of loyal little underscores,
the dark side of the underscore, Old Blue Eyes, Ross is missing sleep,
Darth Sajak, the rebel planet Squirreline (home of Jabba the Nut), and the
game of badminton.

Voting begins.  Additional votes are cast for: oh Vanna my Vanna come
corrupt the force with me, \underline{\underline{\underline{Vanna!}}},
underscores of Gor, the devil you do, the devil you don't, the devil you
did, \underline{Darth} \underline{\underline{Vanna}}, underscores will
rule the universe, ancient underscore conspiracy, and the missing sheep of
the Ross ice shelf.

Votes are tallied, with Emily getting 5.7 votes, and 6.8 counting the
underscores.  Moose beat Squirrel.

The Presidential election!  The official candidate is Edward Keyes, who
is taking the minutes so is guaranteed to win in the eyes of history no
matter what.  Other nominees: this week's minutes, this week's hours,
Boris and Natasha, the Moose Collective, overvoltage, no one (who is much
overlooked), everything Ed rhymes with, the minions of underscore, and
the One Bing.

Voting begins.  Additional votes are cast for: Moose Collective rhymes
with Ed doesn't it, this week's seconds, this week's thirds, belovED,
$\heartsuit$ Vanna $\heartsuit$, can I be one of your minions, the Illuminati,
El Penguino Du Muerte, the evil overlord, All of the Above$^{TM}$, the
nice one, Ed is not a talking horse, Darth Wang the dark Jade-i, evil
things done to squirrels with underscores, and Squirrel (with about a dozen
underlines).

Votes are tallied... the LHE computes... results are... Vanna with 1.4
votes as the official second, and Ed wins with 5.8!

Any more new business?

\goto{Future Business}

Emily may be a famous artist, or a psychologist, as judged by her doodles
on the scrap paper.

The adjournment song...

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
