\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/12/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 12th, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Ed Keyes, President and
Skinner, presiding; Jamie Morris, pseudo-Onseck, recording.

Minutes read.

(JFC) Move to note that it was actually an Adjournment Chant rather than
an Adjournment Song.

Motion vanishes in a puff of dragons.

\goto{Committee Reports}

(JFC) Mobcomm: Updated statistics on what books cost us are about \$13.50
cover price or \$11 S-CC price per two regular paperbacks (not trade pbs).

(ED) Those nicely bracket the one-year membership rate, so we'll keep
the same rates this year.

Mobcomm could do an extra hardcovers run to fill up the bubble in the
hardcover space.  'course, then we wouldn't have that space anymore and
it would suck.

hBarcomm: We think the summer mailing probably happened ok but don't
remember whether we've actually asked hBarcomm to be sure.

\goto{Old Business}

There \emph{is} a prentice theoretically assigned to distributing the
rest of the hardcover bubble, Brian T.~Sniffen, but he was given too many
options for when to come in and be instructed on it so he hasn't been able
to pick one yet.  Should re-ping him about that.

Maggie Gee's \emph{The Ice People} is discussed.  It has wacky Wiccans,
chemical castration, and good grounds for class-action lawsuits.

Ex-Keyholder Ted Allison is here (at MITSFS) while visiting the area.
Is he responsible for JFC's cold?  Are the books carriers of disease?
Should we laminate all the members' hands to protect us?

We'll scan in all our books and abandon their physical forms, right after
Hayden gets around to doing that for all \emph{their} books.  The MIT
Libraries do have an ongoing program scanning some stuff in, including
theses---students are required to turn in extra hardcopy of their theses
for the Libraries, which the Libraries then scan in and store digitally,
which is sort of inefficient when the theses are all being written online
in the first place.

\goto{New Business}

JFC tried to cheat with the voting to ratify AMB as summer Onseck, but
his evil machinations were foiled.  The Skinner gloats triumphantly.

Ted Williams, the famous baseball player who is \emph{not} the same
as Tad Williams the SF author, has disappeared posthumously.  He may have
been frozen.  Senator John Glenn was asked to intervene to have the body
thawed and cremated.  It is unclear whether Glenn's Senatorial position or
experience as an ex-astronaut is what makes him a good candidate for hunting
down a missing corpse.

Some people think there is ``a technical solution for death.''  Why does
freezing your head help?  Because in order to debug something you've got
to be able to reliably reproduce the bug first\ldots.

The new rates are up.  They look a lot like the previous/current rates.

Still need to get prentice Eric together with the Surgeon so he can work
on the Surgery backlog.  In the meantime he might work on the hardcover
bubble.

\goto{Future Business}

Soon the count of indexed-online items will reach 45,000.
The distribution of \#copies is approximately Poisson, with a
bit over 40\% chance that we have at least $n+1$ copies of a book that we
have at least $n$ copies of.

Inventory will be on Saturday August 3rd.  The announcement will go out 
shortly.

Miller Motion fails.

Second Miller Motion passes 3-3-1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1752 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jamie Morris, pseudo-Onseck}

\end{document}
