\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/15/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 15, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1710 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the poster-sessioned Onseck.

Minutes read, while the Skinner and Chancellor carry on a publicity
discussion.

Motion: Commend the minutes for not including any animated JPEGs.
Chickens 2--0--4+Spehn.

[John] ``Chickens are not scared of cats.''

\goto{Committee Reports}

[Jade] ``It's like I touch it, and it clicks.''  The Skinner is still
discussing an event calendar thing.

Mobcomm: British books arrived.  Apparently they consider the various
Dr. Who books interchangeable, since the invoice is wrong.

Mobcomm$_2$: The SFBC books arrived, also with a book substitution,
but less nice.

A girl claiming to be from Jupiter, or maybe Oregon, comes in.  Jade
is confused.  [Jamie] ``Jupiter is in Oregon, right?''  [Jade] ``She
could be a chocobo in disguise!''

Is there a meeting going on now?  [Jade] ``So should I bing to prove it?''

Bill Starr sent John 968 words of the requested 1000-word essay on
Dr. Who books.

[Jade] ``If I eat candy, I'll go weird.''  ``I ate a cake for lunch.
It was a cake in a box.''

The Skinner's hand was injured and may fall off.  Can she still bing?
[Jade] ``... Gavel-Wielder of Gor.''

Bluebellcomm: Some new hardcovers to cover.

Mobcomm$_3$: We finally got the first in the {\em March} series.  (That
is, {\em March to the Sea}, {\em March Upcountry}.)

Jadecomm: [John] ``So I made Jade scream earlier.''  Namely with the
sight of a romance novel advertisement.  Jade demonstrates on the
members and people flinch at the horrors of a romance book club.

There is a discussion of the eBay committee.  eBaycomm?  Maybe Baycomm
transformed to Gulfcomm.  Where'd the ``e'' go, then?  How about
Gulfcomme?

\goto{Old Business}

The title of the third Roberts book is {\em Stone}.  {\em On}, {\em Salt},
and {\em Stone}.  There is a discussion of how to translate ``on'' into
French... as a preposition or an adjective?  John pulls out the
dictionary.

The shelf bubble in the reserve paperbacks has finish propagaing around.

Jade gets older on Monday: the big 1--4...

John tells the story of the glowing clock-radio he and his roommate
built.  Lots of sparks and threats of fire hazards.

Jamie pulled a bunch of metal out of the warehouse.

A discussion of the code words on the AOL CD.  Jade comes up with
the ultimate gavel exercise: wrapping AOL CDs with bubble wrap!!!

\goto{New Business}

BING-POP!  BING-POP!  BING-POP!  The bubble wrap fuses together
with the force of the impact.

Motion: Replace ``Crackle'' with ``Bing''.  John attempts to vote with
the romance book club ad.  Motion does nothing something--less--something
minus one+Spehn.

There is a reported potential return of cold fusion with sonoluminescence.

Motion: Confiscate all lab benches as potential fusion reactors and
therefore dangerous to the public.  Passes 8--4--1+Spehn.

Little tags that say ``this car is stolen.''  See the GM.

\goto{Future Business}

What musical note is the bing?  Jen Chung claims it as a B.  Maybe a
G first, and then a B in the ringing.  John plans to record it and
run the sound through a FFT.

[Jay] ``We can check it against the dial tone.''  Jen claims the dial
tone is a little flat.  John records the bing on his pocket digital
recorder.  The {\em Tech} is perhaps going to complain about the
excessive binging.  The recorded bing is pretty bad.  Jen plays a B
on her PalmPilot for comparison... it is noted the gavel is a little
flat.  In the future we will bing enough to annoy people but not enough
to get them to complain.

Jade tried to get an alumni email address but they won't do it yet.
The default password is ``ILOVECH33ZPIZZA''.  [Jen] ``My password
is six spaces.''

Motion: Declare Jamie out of order.  A mutiny in progress, and the
motion fails by Skinnerial decree.

[Jade] ``Motion fails and everyone should die now!''  There ought to
be a better past tense of ``die''.  ``Doed''?  ``Pining for the
fjords''?

Motion: Resurrect the MITSFS at some point in the future.  Motion
does nothing 5--6--5+Spehn.

What will happen to the shelves out in the hall?  Various people
may want them.

Motion: Since everyone is dead, we should hold a showing of the
bad movie {\em Life Force}.  Not seconded.

Motion: Arrange for us to be lazy after we die by propping up daisies
with banana splits.  Chickens 6--a what--10+Spehn.

Motion: Bludgeon to death the person with the temerity to come back
to life... something something... death banana.  Not seconded.

Motion: [Jade] ``Death bananas of Gor.''  Passes 7--1--3+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

[Jen] ``It's closer to a B than an A...''

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
