\documentclass{article}
\usepackage{fullpage}

\title{Minutes for 9/14/02}
\author{Andrew Clough, Onseck}

\begin{document}

\begin{center}
MIT Science Fiction Society\\
84 Massachusetts Avenue\\
Cambridge, MA 02139\\

MITSFS Meeting Minutes\\
Friday, September 13, 2002\\

\end{center}

MITSFS meeting called to order, 1700 SST, Ed Keyes, President and Skinner, presiding.  Andrew Clough is the newly returned Onseck.

Minutes are read in my usual way.

Motion to approve the minutes as green passes 6-0-4 + Spehn.

\textbf{BING!}

\begin{center}
\textit{Committee Reports}
\end{center}

JadeComm: Present location is downstairs.

Moocomm:  Farscape might be coming back!  This is the possible result of a new phenomenon: a successful internet letter writing campaign.

Certain people are reported to think that 2004 is real soon.  Luckily, they run a scifi magazine, so they can be forgiven.  

Motion to commend the personnel of the Newton public library for their great adaptability, having accepted a Japanese language video without hesitation, Chickens 4-0-6+Spehn.

Mobcomm$_2$:  The Space Crime Continuum should ship to us soon.

It is noted that we've learned that some of the Warhammer stuff that we didn't want and that they didn't want to give us, we didn't get.

Pianocomm:  Brad Johnson is now an prentice.

Mobcomm$_3$:  We should avoid the SciFi book club for popular books, as their bindings are of lesser quality.

Motion: Condemn popularity for messing with our books.  Passes 7-0-3+Spehn.

Somebody might or might not have protested something at this point, but I'm sure that, whoever they might be, they'd be happier knowing that less people know about whatever they might or might not have protested.

Motion: Add this thing that might or might not have been protested to ALGOL.  Fails 5-0-3+Spehn.

\textbf{BING!}

\begin{center}
\textit{Old Business}
\end{center}

People are reading less books with the start of class.

The mysterious donation was revealed to have been a donation for credit.

Motion to prevent members from manipulating the sign fails for lack of a second.

\textbf{BING!}

\begin{center}
\textit{New Business}
\end{center}

We have 4 new shelf codes, Yay!

Steven Baxter has a new topological book out.

New member asks ``what are the Gor novels?''  Said member is then regaled with, and indeed shown the horror of said novels, such as ``The Assassin of Gor,'' ``The Bloodletters of Gor,'' and ``Beasts of Gor.''  New member says: ``I guess he has great respect for how much cold women can take.''

Motion: Condemn Lendem for leaving MIT.  Passes 8-0-3+Spehn.

Motion: Condemn MIT for not offering his fiance enough to come here.  Passes 6-0-3+Spehn.

Motion:  End new business.  Passes 7-1-3+Spehn.

Leo Frankowski has another book coming in Hardcover.

The MIT accounting office sent us, not only our own expense forms, but those of the CAC as well.  The delicious possibilities are discussed with much relish; but not actually consumed.

\textbf{BING!}

\begin{center}
\textit {Future Business}
\end{center}

Miller Motion:  Chickens 4-1-6+Spehn.

Banana Motion: Passes 5-1-2+Spehn.

Adjournment Song is sung.



Meeting Adjourned, 1759 SST.

\end{document}


























