\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/24/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 24, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Ed Keyes, President and Skinner, presiding.
John Carr is the spell-checked pseudo-onseck.

Jamie finishes Wurts-bashing.

Minutes read in Andrew's style.

Motion to correct the minutes like this (John holds up the minutes
of the last meeting, covered with red ink).  [The Skinner stops time
to allow the onseck to catch up.]  Motion passes \hbox{5-0-1+Spehn},
Ed says confidently.

\goto{Committee Reports}

Pseudo-onseck: Need to fix Andrew the onseck's pronunciation,
spelling, and comprehension.

Mobcomm: Got a lot of hardcovers today.

Bluebellcomm: Jade covered about ten of them.  When do we start
the Chinese book torture on the rest of the committee?

Pseudo-pubcomm: Stuff happened.

Alohalenscomm: Susan Born provided a recognizable drawing of herself.
It is not only recognizable, it is an accurate drawing (as opposed to
a caricature).

(Jamie reads a letter by an author, begging us to honor his book by
placing it in our library.  We like this kind of letter.)

There is a discussion of numbers in titles, C. J. Cherryh, and
shredding books.

Pseudo-VGG: A member mailed us a \$1.00 check to pay a fine.

\goto{Old Business}

John: The ``legendary, repulsive Skinner'' in Neal Asher's novel is named Jay.

Jamie: The endowment fund principal is now a round number, \$36,150, thanks to
Jamie's \$120.29 gift.  George Phillies' \$250 donation prevented the balance
from being a multiple of \$100.  John plans a one cent donation.

Jamie: Outside bank accounts are still going away by June~30.
MIT says the internal system is great.  We will test the ``paperwork
by 11:00~AM, check by the next morning'' policy.

Ed will go after the Magazine of Fantasy and Science Fiction to
retrieve our missing issues.

{\bf Algol!}

\goto{New Business}

There are a lot of new magazines in the mailbox.

We received a donation from Brian Leibowitz, who buys books that we
don't have circulating copies of and sends them to us.  ``Brian's
Great,'' says Jamie.

Jake Beal is here.  He went a year between meetings.  John once went
several years between meetings.  Ed went over 20 years without coming
to a meeting.

Jake declares himself Albanian, but the motion does nothing, \hbox{2-0-1+Spehn}.

There is a discussion of voting and counting votes.  Math jokes fly.
(``If you rotate the votes by 90 degrees, do they become imaginary?'')
Emily moans in pain.  If John takes off his shoes and socks, his feet
count as negative votes.  $\heartsuit$~Jade loves John's bare feet.~$\heartsuit$

The nature of the minutes is indeterminate.

Motion to rotate the pseudo-onseck by 90 degrees.  No second.

Motion to have the Vice rotate the pseudo-onseck by 90 degrees.
\begin{picture}(20,14)
        \put(10,6){\circle{12}}
        \put(10,6){\circle*{1}}
        \put( 8,8){\circle*{1}}
        \put( 8,4){\circle*{1}}
        \qbezier(13.5,6.0)(13.4,8.5)(11.0,9.5)
        \qbezier(13.5,6.0)(13.4,3.5)(11.0,2.5)
\end{picture}
No second, alas.

A discussion of human hamster wheels follows.
Pika's came before EC's, but Pika's didn't get in {\em The Tech}.
It was built in a day.

Jamie: If we laminate the members they won't sweat on books.

Jake: Ghostbusters~2 and Robocop novelizations were written by the 
same person, Ed Naha.  He also wrote {\em The Suicide Plague}.
The back cover blurb on {\em The Suicide Plague} causes John to
explain why he believes HP is controlled by space aliens.
They are funding a von Daniken theme park.

Motion to strike Jake.  Passes!

The vice is handed the cat-of-five-tails but doesn't use it.
Jake describes a cat-5-tails, a whip made out of Ethernet cable.

Motion: Albanian Jake!  Passes, \hbox{9-0-Spehn}.

Jamie sings the adjournment song.
\begin{picture}(20,20)
        \put(10,6){\circle{12}}
        \put(10,6){\circle*{1}}
        \put( 8,8){\circle*{1}}
        \put(12,8){\circle*{1}}
        \qbezier(10.0,3.5)(12.5,3.4)(13.4,1.6)
        \qbezier(10.0,3.5)( 7.5,3.4)( 6.6,1.6)
\end{picture}


\vspace{12pt}

\noindent
Meeting adjourned, 17:50 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-onseck}

\end{document}
