\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/04/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 4, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and Skinner, presiding. JFC is the Pseudo-Onseck.

"Are you ready?" \bing

Minutes read.

Andrew asks about rates- the events in last week's minutes have already happened.

M: commend minutes as being more complete than expected.

JFC interpolated, but JWH wrote most of them.

M: commend as interpolated. 5-6-0 +Spehn.

\goto{Committee Reports}

Jadecomm: Jade is back after an exciting winter break.

Mobcomm: did nothing.

Dex: new dexes soon. Need to give a copy to the MIT Libraries.

Dawn polls us- how many would see Harry Potter and the Sorcerer's Stone at LSC? (Few.) Philosopher's Stone? (More.) Nobody prefers the American version?

Long discussion of SF movie marathon: movies and schedule.

New book shelf is overflowing.

\goto{Old Business}

Damnation Alley is still closed off but getting better.

"I don't think I ever want to be affected by a demon banana." (JPW)

AMB quickly takes advantage of the new reduced 4-year rate.

\goto{New Business}

Rate sign has moved and changed format. We will adjust rates every month instead of writing "subtract 1 dollar in November," which confused keyholders. 3 different prices in November. JFC just gave a member a 2 dollar refund.

Somebody needs to take cash to cashiers office to replenish our activity account which went negative to pay for our net drop.

JFC and JPW cleared space on the work desk, partially by rotating typewriters.

\goto{Future Business}

Discussion of making a demon banana.

Jade rhymes "poolboy" with "drill toy," discussing a brochure we got for creative writing courses.

Wrede book has a recipe for after-battle 3-layer chocolate cake; prisoners make a fire.

JFC discusses a new member who is our only hope.

M: have JFC stop prophesizing.

We get 40-30 new members.

Discussion of the types of members.

A member volunteers, maybe, to be a prentice.

M: Jade vs. demon bananas. Winner eats loser; either way, she isn't hungry. 11-0-1 +Spehn

\vspace{12pt}

\noindent
Meeting adjourned, 18, wait, 1739 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{JFC, Pseudo-Onseck}

\end{document}
