\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/5/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 5, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Stephanie Fried, LHE and
Pseudo-Skinner, presiding.  Ed Keyes is the asymptotic Onseck.

Minutes read.

Motion: Consider the minutes well-paved.  Chickens 7--5--whole bunch+Spehn.

\goto{Committee Reports}

John consults his notes.

Mobcomm: A box and a bag from the Space-Crime Continuum.  Someone
accidentally got a second copy of {\em Southern Vampires} because it
was initially processed with the wrong author name.  Some more British
books came in, but they're still interchanging Dr. Who books on us.
And Amazon sent us a weird videotape for no reason, too.

Pubcomm: There is a person associated with the committee now, namely
Jen Clay.  This was split off from Theftcomm since the TIF is enough
work by itself.

Mobcomm$_2$: We broke the bank because the LHE is lame.  The new book
{\em The Skinner} arrived as well.  It is more blue-green than Jade
usually is.

Bluebellcomm: The Onseck has been lame about getting more slit-back
short book covering material.

Pseudo-Sitcomm: {\em Legend of the Rangers} is mostly dead.

Alohalenscomm: John has a new possible keyholder picture of himself
posing with a chicken.

Motion: Restrict the picture of a chicken to only the outside of
the library.  Not seconded.

\goto{Old Business}

John will not be here last week.

Bob Klein has written us again looking for times to come and donate
things.  Possibly tomorrow.

A pre-frosh interrupts to ask about the chain on the Gor shelf.
Jamie explains.  Pre-frosh are too young to be allowed to be corrupted
by Gor.  John claims the first one isn't all that bad, but the rest
of them (he claims to have read seven or so) tend to blur together.

It is noted that Chewbacca is dead in the new {\em Star Wars} books.

Usual stuff.

\goto{New Business}

Steph's bing quality varies a lot.

There was a new bank deposit, so we can partially pay John now.

There are a lot of people in the libary.  ``One, two, many, manyone,
manytwo, manymany, manymanyone, manymanytwo, lots.''  Jade must be very
glad to be 3000 miles away from the scary pre-frosh.

John engaged in a battle of wits with a squirrel and lost, even with
the aid of technology.  [Jamie] ``Thus bringing your record to 0--3.''
Various methods of dealing with hyperintelligent squirrels are
discussed.

\goto{Time Warp to Committee Reports}

Fweekcomm: Holy shit!  Pre-frosh!

\goto{Future Business}

Carthage must fall!

In the future the pre-frosh should come back.  One of them asks about
fantasy gaming groups around campus... yes, there are lots.

We need to implant tracking beacons in promising pre-frosh.

The foreign bookshelf is pointed out to someone who mentioned Russian
sci-fi.  There follows a discussion of various good Russian authors
and books.

Motion: Build a dense protected ring of bananas around our birdseed
reserves to protect against marauding squirrels.  Passes 11--4--10+Spehn...
no 11--4--9+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1541 SST... no, 1740, I corrected myself!

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
