\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 7/5/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 5, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and
Pseudo-Skinner presiding, Eric Armstrong, Pseudo-Onseck recording.

Minutes read.

Motion: Approve the minutes as eloquent as usual. Passes 3-0-1+Spehn.

\goto{Committee Reports}
                                      
Mobcomm: Wheel of Time \#10, \emph{Crossroads of Twilight,} is due
in November but its cover is out already.  Terry Pratchett is coming 
out with a new Discworld book, \emph{Night Watch.}  Michael Moorcock is
writing a new book with tie-ins to Sept.~11, and his toes have been chopped
off.  This is not in fact a political statement but rather an effort to
stop gangrene.

Squirrelcomm: Hyper-intelligent squirrels have brainwashed people so
that they feed the squirrels. Other people, related to MITSFS members,
grease their bird feeders. Squirrels that assault such bird feeders
wind up standing around on branches trying not to fall off.

Mobcomm: Hartwell has turned in a massive ``mammal crushing'' book. It is
unclear from the review if this is a book that can be used to crush
mammals or a book about crushing mammals. It may even be both.

Reimbursement requests and the book of payments do not easily
correlate. Two requests are paid with one check and the other way
round. Mobcomm will report on this to the Star Chamber later.

A discussion ensues on why an invoice shows us as having paid SFBC
3~cents. It turns out that it is an error on their end and we have
overpaid them by about 30~dollars.

\goto{Old Business}

There is an old note in the mailbox of things we should buy. We still
need to buy most of them.
   
George Alec Effinger died of an stomach ulcer, but had lots of other
health problems.
   
The giant bubble in the hardcovers is still in the same place it was a
month ago.

Usual motion, usual second, usual vote, usual result.

\goto{New Business}

The rates for the August--August membership cycle should be looked at
and if we are going to change them, they should be changed before the
new students get here.

\goto{Future Business}

The date for inventory is not yet decided, but it may be July~27 or
August~3. July~27 is more likely. We really want the big bubble
distributed by then.

Come and beta-test Jamie's new Inventory code.

The Skinner should be back next week, but the summer Onseck will still be
gone [at Readercon].

Miller Motion.  2-3-1+Spehn fails!

The Adjournment Song, with what might technically be called ``clapping'' as
long as any connotations of rhythm are ignored.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Eric Armstrong, Pseudo-Onseck}

\end{document}

   
