\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/18/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 18, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Ed Keyes, President and Skinner, presiding.
John Carr is the occasionally distracted pseudo-onseck.

Minutes read.

The respelled minutes were read.  A motion to approve the minutes as
brilliantly corrected passed \hbox{3-0-3+Spehn}\footnote{Well, {\em I}
say the motion passed even if the skinner disagreed}.

\goto{Committee Reports}

Mobcomm[JFC]: A big box of books from the Space Crime Continuum has
arrived to pack the ZGT.

Mobcomm$_2$[JFC]: Would you buy a book from this man?  The picture
of author Robert Rankin on his book {\em Hollow Chocolate Bunnies
of the Apocalypse} is displayed.  Most people are disturbed.  Mike
Whitson is excited.

Pianocomm: AMB trained prentice Brad Johnson to do magdex, and
he did.

Pianocomm$_2$: EMP trained prentice John Weaver and non-prentice
jhawk to do surgery, but has not yet trained prentice Eric Armstrong.

Theftcomm: There are now two schedule files instead of one.
Otherwise, life goes on as usual.

Theftcomm$_2$: Next week ARM will probably cease to be the most
lame keyholder.

War Council: The proto-draft of the Reading Room proposal has become a
read draft and has floated up through the bureaucracy, one step closer
to nirvana.

\goto{Old Business}

Filing cabinet rearrangements have concluded.  The process by which
Jamie creates space is like the math puzzles where by slicing and
rearranging triangles, the total area increases.

\goto{New Business}

$\rm \Psi\Phi$ has a new monitor.

Donations: David Tuttle dropped off five boxes of books.  Robert Klein
will bring us boxes of books soon.  Gain Standish~'85 may mail us some
boxes of book.  Friends of EMP may give us books.  And finally, monsieur
Skinner, a wafer-thin zine...

The bulletin board has been updated.  If somebody posters on our
board, can we collect the fine?

\vspace{12pt}

\goto{Future Business}

We need a slide RSN for {\em Minority Report} next week.

A discussion of funding and accounting ensues.

MITSFS is invaded.

\vspace{12pt}

\noindent
Meeting adjourned while the pseudo-onseck was not paying attention.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-onseck}

\end{document}
