\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/27/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 27th, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, John Carr, Mobcomm and Pseudo-Skinner
presiding; Jamie Morris, Pseudo-Onseck, recording.

Minutes read.

Move to approve the minutes as unread.
Motion does nothing, 1-1-0+Spehn.

\goto{Committee Reports}

Apathycomm says ``Yay.''  Is Justin here?

Mobcomm: Due to intensive preparation for being Pseudo-Skinner this week,
I was unable to do serious Mobcomm work.  Might have ordered a few British
books.

MiniCult: DARPA's funding a Sloanie's software for finding terrorists
and criminals by analyzing and correlating Web sites, email, etc.

Bluebellcomm: The pile hasn't changed since last week, including a dozen
new books.

Dexmistress: New dexes soon for the new year.  Also, the shelfcode system
may be revamped soon; this would be user-visible.  Also, the bibliographic
database may be revamped, with design starting soon; this would \emph{not}
be user-visible until much later.  Also, the system for tracking what's
in boxes instead of shelves will be revamped very soon, to decouple the
prescriptive and descriptive functions.

\goto{Old Business}

The phone bill claims the same amount owed as the N bills that have yelled
angrily about it, but the yelling itself has vanished.  Did Ed's attempt to
have it charged to our account convince them we're trying and shouldn't be
yelled at (even if it didn't actually \emph{work} so far), or did they just
decide we're not listening anyway?

All 2002 minutes so far that hadn't gotten into HTML yet now have,
including the minutes for October 32nd.

The boxed SFWAs may manage to be repackaged before IAP starts since there
are some workers around.

JFC asks JPM to divide the Prentices into naughty and nice, but doesn't
think the list needs to be checked even once, let alone twice.

NESFA has made GF (more) canonical by defining ``to~george'' and 
``to~georgify.''  Oddly, the definitions only involve asking George to
proofread things, not getting him to bless their final forms.

The Tuttle donation is almost processed enough to write the acknowledgement.
It and the Klein donation will both be done and their acks out (barring odd
delays getting signatures) well before Jan 31st, which is the general date
by which charities send out donation acks.

\goto{New Business}

Analogcomm: We have amusing IAP schedule headers.

Margaret isn't present but JFC proxies a \emph{Screeeeeeeeeeeeehhh!} for her.

The donor of the Vance Integral Edition to the MIT Libraries is going ahead
with it knowing it'll get passed to us, even though the donor turns out to
be the publishers, who have some amount of anti-SF sentiment.  It'll arrive
in halves, in early 2003 and in late 2003 or early 2004.  The MIT Libraries
may or may not be sending acknowledgements for us.

The Star Chart has fallen and it can't get up.

Only a Boris calendar awaits the New Year.  Save us!

\goto{Future Business}

Move to have the Architecture department design a new, infinitely
expandable, hyper-banana-shaped building to house MITSFS.
Passes 7 hypervotes to none to 2 Heinleins plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 or so SST.

\vspace{18pt}

\centerline{Sloppily submitted,}
\centerline{Jamie Morris, pseudo-Onseck.}

\end{document}
