\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/15/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 15, 2002

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the very much colder Onseck.

Minutes read, complete with a large smiley-face visual aid.

Motion: Commend last week's minutes as enthusiastically something-something.
Passes 2--0--many hearts+Spehn.

The ispell program corrected the spelling of ``noseface''.

\goto{Committee Reports}

Pseudo-Plantcomm: Apparently the side radiators can blow warm air,
although the central one only blows cold air.

Jamie attempts to lift a box of {\em SNF} onto the ZGT.

Chronicomm: {\em SNF} \#0 is now copied and stapled and stuff.  We're
looking for a cheaper color copy place for \#1.

Jadecomm: She was accepted to Stanford, yay!  A discussion of visiting
colleges and whether they reimburse you for travel expenses.

Andy volunteers to be a new prentice.  The cloud of doom wafts over
and takes position over his head.

Pianocomm: We got a prentice!  His name is a Norman word meaning a
depression by a hill (Clough, pronounced Clef).

A discussion of how Jamie's Russian/Polish Jewish family ended up
with ``Morris''.  Morrisovich?

Jade invites everyone to a celebration dinner.  Unfortunately a
Guild game starts tonight.

Mobcomm: By mistake more than intention, we got both the British and
American editions of the same book.  They have the same page count but
a 50\% difference in bulk... I guess those Brits have different trees to
make paper from.

There are retroactive cliches in {\em Memory, Sorrow, and Thorn}.
That is, the ending ruined the earlier cool parts of the book.

A discussion of ``plot coupons''.  The usual structure of trilogies.
Prophecies and whether trying to follow them actually works.

Jamie proceeds to spoil the ending of {\em Lord of the Rings} for
John.  [Jamie] ``Read the bloody books, dude!''

Mobcomm$_{n+1}$: We missed a Lackey book last week.

A discussion of why profile shots of people on magazine covers always
face to the right.

\goto{New Business}

Jade goes to find something to destroy with the gavel.

Did our outside bank report get turned in?

\bing \bing  The little banana guy falls down, maybe from the gavel
shock wave.  [Jamie] ``And the suction cup can be on top of the ball
if you like, so they can mind-meld.''

John reads an interesting cover blurb into the minutes.  ``A child
and a dead cosmonaut, joined in the brain of a giant whale!''  This
is from {\em The Jonah Kit}.

We got a deactivation sticker in the mail.

There are some new spaces on tables where computers and stuff used
to be.  Phys Plant may or may not have just trashed the stuff in the
hall, but that's okay.

\goto{Old Business}

The bulletin board is momentarily completely clean, except for the
thermometer.  [Jade] ``What does it read?''  [John] ``Robert Jordan,
mostly.''

The reserve paperback bubble has propagated farther.

\goto{Future Business}

We need to get some envelopes for {\em SNF}.

Jamie finds some planet identification posters in the stationary
drawer.  There is a discussion of where to post them: inside or outside
or outside facing inside.  We are missing Pluto.

Someone should remind John to bring his digital recorder.

It is reported that boring everyday birds are called LBB's by bird-watchers:
little brown bastards.  Sparrows and stuff, that is.

{\em SNF} RSN.

We have a future.

Jade contemplates the depressing candy hearts put out by despair.com.
``The only consistent feature of all your dissatisfying relationships
is you.''

Jamie starts trashing stuff out of the WTF? box.

Motion: Have despair.com come up with something depressing involving
mixing chocolate and bananas together... apparently the combination is
bitter.  Passes 8--0--1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST, no sorry, 1750 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
