\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.25in}
\setlength{\textwidth}{6.5in}


\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/13/2002}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 13, 2002

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

``Ganga, lots and lots of Ganga.''

MITSFS meeting is called to order on Friday, December the thirteenth of 2002.  Ed Keyes is the presiding President and Skinner; while Andrew Clough is the newly spell-checked Onseck.

Minutes are read.

Motion:  Commend the minutes as being properly spell-checked.  Passes 7-0-1+Spehn

\goto{Committee Reports}

Bondagecomm:  Dropped off the magazines, and should be done in three to five weeks; then we'll see which horrible mistakes John has made.

UsefullFactscomm:  Ringworld Engineers was originally serialized.  It also belongs to the Big, Dumb Object genre.

``They should have just called it "Return to Ringworld'''

Motion:  Send the Ringworld to remedial schooling.  Passes 11-1-3+Spehn

Margaret:  ``Yay, I said a motion.''

Pseudo-LEGcomm: We got 90\% of the money we wanted.

For the second meeting in a row, a member comes to return their book.

Pseudo-Analogcomm:  Schedule prototype generated.

Pseudo-Boriscomm:  Failed again.

Motion:  Make a committee to assist Boriscomm called Natashacomm.  Fails 2-3-1+Spehn.

Goldilockscomm:  We now have a mama slinky, a papa slinky, and a baby slinky.

Erin had had the slinkies arranged so that it was intuitively obvious to the casual observer how new slinkies are made.

John:  ``The rainbow gene is dominant.''

We succeed in reaching the second harmonic of slinky oscillation.

Mobcomm:  Big Box of Books from the Space Crime Continuum will come soon.  Also, there was a recent run in which John, Margaret, Cassie, and I the Onseck went.  We contemplated leaving Cassie there in Nirvana.  She says she might have noticed after 3 or so books.

\goto{Old Business}

Bluebellcom:  Still lame.

ALGOL

\goto{New Business}

Margaret:  ``Squiiiiiiii''  John gets the oil.

``That one looks much more suggestive than the frog''

``A steeple would make the cluster much more interesting.

Andrew Boardman got our Asimov's situation straitened out, with the ``20 year subscription(s)''  We don't even have to send our current issues back.

``If you take your collar off can you spin your head around?''

``When Russians get together it helps them be gloomy.''

\goto{Future Business}

``Radioactive goats could not get through the New York subway system undetected.''

Motion:  Gatorade should have a banana colored drink.  Passes 13-8+Spehn-0 or 13-0-8+Spehn or 8+Spehn-13-0 or something.

Meeting is adjourned at 1800 SST

\vspace{18pt}

\begin{center}
Respectfully Submitted,
Andrew Clough, Onseck.
\end{center}
\end{document}
