\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.60in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

December 1st, 1989

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, December 1st, 1989,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

Various motions are proposed and just sort of sit there.

(PJN) Vote on one the motions, whichever you like.

Motion passes, 6 to 0 to 3 plus Spehn.

{\em bing\/}  {\bf Committee Reports}

(WDS) Moo Comm - Go see \underline{Back to the Future II}

(PJN) Jour Comm - We just got a bunch of review books.  Write for TZ!

(JFC) LHE - In October and November, we broke even.  However, Finboard
doesn't want to give us any money.

(JFC) Moo Comm - LSC: Star Trek V on Saturday

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

(WDS) Dick Clark is 60.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(DSK) There's a sequel to \underline{Rendevous to Rama}:
\underline{Rama II}, by Clarke and Gentry Lee.

(DSK) For those who actually care, there's a new Pern book out:
\underline{Renegades of Pern}.

(JFC) Miller motion!

(PJN) Fails!

(WDS) Miller motion!

Motion chickens, 2 to 1 to 4 plus Spehn.

(WDS) Second second Miller motion!

Motion passes 8 to 1 to 6 plus Spehn.

Meeting adjourned, 1712 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
