\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 7, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. 

The Onseck was elsewhere, however, fast asleep and dreaming about the wonders of paraquat poisoning.

(WDS) No!

Motion passes, a few, to a few less, to bleh, plus Spehn.

\goto{Committee Reports}

(L K) Jour Comm - Write for TZ already.

(PJN) Quest for Power Comm - Finboard is doing their interviews for next year's finboard members this Wednesday. We only need a majority.

(PJN) LHE report - We're almost down to breaking even for the year, but we've bought on the order of 2300 books.

(HAM) Pseudo Picnic Comm - reserve your calenders for either April 28th and 30th, or May 12th and 13th. (Election meeting and picnic.) Election results will be: Derrick for Onseck, John for LHE, Donna for Vice, and Phil as President.

(L K) Cornelia Otis - The (Tufts Administration) Conference board managed to book a militant animal rights group in the biology building.

(HAM) Mob Comm - There's going to be a mob comm run tomorrow.

(R P?) Moo Comm/Trek Comm - Star Trek V - Harvey Bennett is going to make a cameo as a Star Fleet Admiral.  Also, they've got the whole thing, all they've got to do is put in the special effects.

(WDS) Sit Comm - Monday night, 8:30, NBC.  The debut of a new half hour sit comm called Nearly Departed.  (Beetlejuice rip-off?) The young husband ghost is played by Eric Idle (Monty Python). Sub II - The pilot episode of Quantum Leap wasn't that bad.

(HAM) Moo Comm - 2001, Sunday. Sit Comm - rumors that BBC is going to cancel Dr. Who.

(WDS) Strek Comm - they ran a bad episode last Saturday.

(L K) Skinner/Telzey Report - We're moving to Newton!

(WDS) Morte Comm - The Science Fantasy book store in Harvard Store is indeed dead. It was shut down finally last Friday. Official souvenirs gained: bookmarks, Mission Earth buttons, ugly poster.

(time warped, but Tarl neglected to inform me, therefore lost in transit.)

(S T) cont. - Dan Quayle invited John Kenneth Galbraith to a meeting of the Republican Senatorial inner circle. Distinguished Americans who have already joined: Bob Hope, Arnold Schwarzenegger (sp?), Stephanie Zimbalist (sp? jr), George Schultz, and Mario Andretti. The return letter from Galbraith which critiques his spelling, etc.

(end time warp)

\goto{Old Business}

(RVderH) Ken and Janice visited last weekend!

O.B.A. usual 4.

\goto{New Business}

(S T) Mini Cult - An MIT grad student named Michael Picard lost his car the other day.  He left it in front of his apartment, the city decided it had been abandoned, and they towed it away and crushed it. (There's a new law - a car that sits on Comm Ave. for 72 consecutive hours is 'abandoned'.) The city has not yet admitted they made a mistake.

(WDS) Mini Cult - April First Moron Fake Disaster Reports. (see article.)

(Seth) MiniCult - Inview - a new, 'charming' magazine on campus.

(HAM) Move to take that banana colored poster, that Bill so kindly brought us, paste it across the door of the Tech while they're all inside, liberally coat it in kerosene, attach a Mission Earth button, and set it on fire.

Motion passes, a few, to no-one, to no-one plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1732 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
