\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 14, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(C H) A strange sort of moaning sound.

Motion passes about 10 to 3 to a very worn out Connie plus Spehn.

\goto{Committee Reports}

(M G) Mort Comm - Mel Blanc died.

(WDS) Mort Comm sub II - Sir Laurence Olivier.

(WDS) Moo Comm - The latest James Bond film opened today and is getting fairly good reviews.

(C H) Moo Comm sub II - Lethal Weapon II opened last weekend.  It is really, really good.

(HAM) Moo Comm sub III - When it comes out, everyone should go see UHF to at least prepare themselves to see Gandhi II. (Note by Bill: UHF is a Weird Al Yankovic production)

(LAK) We've started getting LOC's for TZ40 (LOC's = Letters Of Comment), 5 actually, so start writing for TZ41!

(PJN) Moo Comm sub IV - LSC is showing Temple of Doom tomorrow.

(WDS) Strek Comm - A fresh episode of Nextrek tomorrow, the second to last fresh episode of the season.

\goto{Old Business}

(WDS) It's Bastille Day.

(LAK) Anniversary report - There was a pretty neat TV show last night about the anniversary of the moon landing.

(C L) They will be running the original NBC newsreel footage on TV of the Apollo 11 liftoff, landing and splashdown.

(MJG) Janice is in Seattle; they're having a pool party Saturday.

Old business Algol - Usual everything: \bing

\goto{New Business}

(C L) This is in today's Wall Street Journal, a analysis of the National Endowment of Arts to find out how much "literature" Americans read. (Article is in the blue folder.)

(KRJ) I noticed that one of the cable stations is showing the Mike Hammer movie with Mickey Spillane playing Mike Hammer.

(HAM) Mini Cult - The Grateful Dead testified before Congress this week on tropical rain forests. They've been involved for the last 20 years in raising money to save forests.

(G F) For the second week in a row there was a unattended plane accident. Apparently the pilot was a gun collector and had a gun in the cockpit. Upon impact with the water, the gun went off and wounded him in the stomach area.

(WDS) Mini Cult - The stealth bomber has proved that it can run at 100mph without taking off.

(SST) Three fighter jet engines were stolen from an Air Force base.

Some obscure motion with the banana in it is chickened.

Finally, the Skinner gives in and adjourns the meeting after four simultaneous and bad versions of Rabbits Have No Tails.

\vspace{12pt}

\noindent
Meeting adjourned, 1727 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
