\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 21, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

The Onseck gives vague details on the exciting events of the last meeting.

Some visual motion almost dies, but passes, a few to less, to even less, plus Spehn.

\goto{Committee Reports}

(PJN) LHE Report - Our bank account is now positive.

(HAM) Pseudo High Comm - Derrick, the new speaker to High Smith, called up and bitched at them.  The new date for our backs is April 27th or 28th.

(WDS) Pseudo Colonial Office Comm - There is some chatter of starting up a science fiction association at Northeaster.  Suggested name: Science Northeastern Association Fiction University. (SNAFU)

(C H) Pseudo Random Information - Hugo Box Stuffing, see ballot (not attached, probably on door :))

(L K) Moo Comm - everyone should go see Field of Dreams; it's really cool.

(WDS) Pseudo Moo Comm - Siskel and Ebert upset at She's Out of Control for wasting not only six bucks, but also two hours.

(Malcolm) Pseudo Moo Comm - Split.

\goto{Old Business}

(C H) News from S., Janice got into Clarion West.

O.B.A. usual, etc. x4, \bing

\goto{New Business}

(Seth) Mini Cult - Massachusetts Citizens for Life Newsletter printed an editorial about an abortionist in Sweden hearing a fetus scream (while performing the abortion) and promptly got out of the business. The source?  Weekly World News.

(WDS) Mini Cult - The typographical quality at Baen publishers is way down. (Bill proceeds to read an excerpt from Sheepfarmer's Daughter by Elizabeth Moon.)

(Malcolm) Mini Cult - The Sun (?) announced that NASA's space probes have succeeded in taking photographs of Heaven.

(HAM) Motion to condemn Robert for failing to make his whatever tetrahedron with banana colored paper.

Motion passes, several to not enough, to an albanian chicken plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, somewhere between 1715 and 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
