\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 17, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Onseck exists, within question, but minutes don't.

Morton Downey Jr. makes a motion, it fails.

(Seth) Motion to approve the Onseck as provisionally resurrected.

Motion passes, many, to less, to a transmuted Robert or Connie plus Spehn.

\goto{Committee Reports}

(HAM) Skinner Report - People may have noticed that we are asymptotically approaching new book shelves.

(WDS) Moo Comm - Leviathan opens today. Bill and Ted's Excellent Adventure is still playing in some places.
 
(L K) Jour Comm - Second Installment of terror, courtesy of Seth and xerox machines.  She reads:

"'Of course you may use the telephone, please come in.' The man invited. 'Thank you,' Doug said. 'The telephone is this way, please follow me. The telephone is in the master study, I'm afraid only one of you may go in there, the other two must wait out here.' 'I'll make the call.' Doug told the man. (Insert silly comments 'but you can't make the call, but I must make the call') Doug was led into the study while Gary and Mike waited. When the man closed the door to the study they could see Doug dialing the phone. The man said 'I'll return in a moment.' The two boys waited and waited. 'Doug has been in there a long time, what in the world is he doing?' Mike exclaimed.  'Let's see,' Gary suggested. They opened the door to the study. They didn't see Doug but there, still holding the phone, was Doug's hand and a trail of blood leading to the wall. 'Oh my God!' exclaimed Mike."

(G F) Banana Comm - column on humor - Banana is funny; Apple is not funny.

(WDS) Hard Time on Planet Earth is now as bad as it potentially could be. Return of the Jedi on TV (Sunday at 9). Likewise Wizard of OZ.

(Seth) not-exactly moo Comm - Student One Acts.

(HAM) Moo Comm for real - Repo Man on Sunday, Concert in Bad Taste, midnight Saturday.

(C H) Peter Pan is either tonight or next Saturday night.

(R P) Whoosh Comm - Shuttle is up there, it's going to come down sooner or later.

\goto{Old Business}

(AA?) Ken and Janice are supposed to be in town on the weekend of April 1st.

O.B.A usual => \bing

\goto{New Business}

(WDS) Mini Cult - interrupted by a Phone Comm, then cousin Larry re-reperforming his keyholder task - general gist: Morton Downey Jr. autographing session at Lauriets in Down Town Crossing, Saturday at 4.

(HAM) - Speaking of autographing sessions, Douglas Adams, Long Dark Tea-Time of the Soul, Harvard Coop, Wednesday at 12:30 - 2:30.

(AA?) Mini Cult - Wall Street Journal, Zen and the art of Auto-sales. Man Car Relationships, it's here, read it.  It's recommended.

(Seth) Mini Cult - Political quote of the year.  Julian Bond on Dan Quayle: "He thinks Roe vs. Wade are options for crossing the Potomac."

(C H) Weekly World News (undocumented)  Off duty policeman thumps on floor with assault rifle to tell guy below to turn down stereo. Shoots guy above.

(AA?) Someone at Ludicon had ordered an anatomically correct chocolate heart. It came with a catalog.  All sorts of neat things. (pocket uterus? heart cufflinks?)

(RvD) Motion to have Chris Coon bring a banana to the Morton Downey Jr. show and do something appropriate.

Motion passes, lots, to know one, to very few, plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, time uncertain.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
