\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 11, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

(PJN) Motions concerning the non-existent minutes?

(HAM) Motion to send the minutes that we don't have with Meryl to act as insulation in the walls of her apartment.

Motion passes, something to a little bit less to something plus Spehn.

\goto{Committee Reports}

(WDS) Moo Comm - Abyss has opened.  I've avoided seeing all reviews of it. Herb makes some bad comments in Albanian, which he thinks escape being Albanianed, but the Onseck catches in time.

(LAK) Jour Comm - Write for TZ!

(WDS) Strek Comm - There is absolutely nothing new to report about Star Trek.

(LAK) Old Skinner Comm - Andy Su was here last Sunday.  He's alive and doing fairly well in Ohio.

(PJN) Another Ex-Skinner Report - Scott Kitchen is making vague rumbling noises about being up in the area in the next couple of weeks.

(C H) Moo Comm - I saw Parenthood (Steve Martin, Rick Moranis, etc.) and it was actually pretty good.

\goto{Old Business}

(WDS) Fifteen years ago last Wednesday, we finally got that dick out of the White House.

(MJG) I talked to Janice the other day.  She's back at Clarion and has her secret decoder ring.

Old business Algol - Usual everything: \bing

\goto{New Business}

(HAM) Some muttering in Albanian about Roger Zelazny.

(C L) Newsday (A Long Island newspaper) had a review of some science fiction books, one of which was a Zelazny collection.  In the opening brief, it explained to everyone who Zelazny was.  They said that he is one of the writers to move move most quickly from a studying apprenticeship to a comfortable middle-age.

(WDS) Mini Cult - A group of witches in Rhode Island have been granted tax-free religious status by the RI Supreme Court who stated that they met the state's requirements for a religion.

The Skinner is bombarded with several versions of Rabbits Have No Tails(including to the tunes of Ode to Joy and the Star Spangled Banner) and thus ends the meeting.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
