\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 24, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous meeting dutifully read (in under three minutes including interruptions) and corrected.

(HAM) Motion concerning the minutes?

(WDS) I'm concerned.

Motion passes, we won't bother with the count.

\goto{Committee Reports}

(Seth) Whoosh Comm - You may recall that a while ago a chimpanzee went up in a Soviet space craft and wreaked havoc by getting one of its arms free from the restraints and messing around with the ship's electronic components.  Alexander Covern writing in The Nation observed that there was a lot of stuff written about this in the Soviet press, but there weren't actually any pictures although there was a functioning camera in the space ship.  Well, it turns out that most of the time this chimp had his hand free, he was using it to masturbate.

(WDS) Morte Comm - James Bond, dead at 89. (An ornithologist whose name Mr. Fleming appropriated for his novel.)

(HAM) Skinner Report - The shelves are in the mail, as well as the clips for the shelves are in the mail. Also in addition, we made a minor altercation to the keyholder notes. Basically you now have the same fine for putting the multiple wrong date (signing in or signing out) instead of two different fines.

(WDS) While noting in passing that if there is a world wide conspiracy to undermine Islam, it is almost certainly being lead by the Ayatollah Khomeini. It will be pointed out that The Satanic Verses by Salman Rushdie is fantasy. We should get a copy of it.

(PJN) Anniversary Comm - People who are going to Noreascon III please come talk to me. It's the MITSFS' 40th anniversary so we are at least going to attempt to do something.

(S T) Lib Comm - An ad for fancy writing instruments - the displayed samples have our Lib Comm's name engraved on them. (Ken Johnson)

(WDS) Sit Comm(s) - On Mission Impossible they actually killed off one of their regulars; coming up on TV this week you have Get Smart Again, Sunday at 9pm; From the Dead of Night, in two parts on Monday and Tuesday; and something really terrible called Hard Time on Planet Earth, premiering Wednesday at 8 on CBS; and lastly, Next Strek had another good episode.

\goto{Old Business}

O.B.A. um, us, uv, ur, \bing

\goto{New Business}

(Seth) Mini Cult - From the Gay Community News, quote of the week: "Men have legitimate problems when because of Big Brother in Washington and affirmative action, they are passed over for a promotion, and a woman who is maybe not as well qualified is given the job."  This quote comes from South Carolina State Senator, Ryan Sheeley, who plans to introduce a bill to create a state commission on men. This commission would combat what Sheeley calls "the steady erosion toward men becoming whips."

(S T) Mini Cult - (courtesy of Tom McKendrie) - Montana Ca.  What might have been expected when a bumbling bank robber dropped his loot on the street: a crowd quickly gathered to grab what was blowing in the wind. What might not have been expected was that the bystanders returned almost all of the money to the bank. (All but 20 dollars out of 2900) Also, a warranty card: Thank you for purchasing a McDonnell-Douglas military aircraft. (See blue folder)

(WDS) A MIT student very nicely hacked the Morton Downey Jr. Show. (See Tuesday's Tech and NAMBLA.)

(WDS) BANANA!

Motion passes by just enough, to other things, to other things plus Spehn.  

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
