\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 28, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous two meetings abbreviated etcetera.

MINUTES ABOLISHED! \bing

abol.ish /*-'ba:l-ish/ /-*-b*l/ /-m*nt/ vt [ME abolisshen, fr. MF aboliss-, stem of abolir, fr. L abo]le-re, prob. back-formation fr. abolescere to disappear, fr. ab- + -olescere (as in adolescere to grow up) - more at ADULT 1: to do away with wholly : ANNUL 2: to destroy completely SYN syn ABOLISH, ANNIHILATE, EXTINGUISH mean to make nonexistent. ABOLISH implies a putting an end chiefly to things that are the outgrowth of law, custom, and conditions of existence; ANNIHILATE may apply to the wiping out of existence of anything material or immaterial; EXTINGUISH implies complete destruction and suggests a gradual means such as stifling, choking, smothering - abol.ish.able aj - abol.ish.er n - abol.ish.ment n

\goto{Committee Reports}

(PJN) Capital Request Report - you see before you six spanking new filing cabinets.

(HAM) BOOK MOVING PARTY - as soon as our backs arrive, providing it doesn't conflict with Steer Roast, Beast Roast, etc.

(HAM) Picnic - invitations are done!

(Seth) Strek Comm - they (LSC) showed the trailer for Star Trek V last week.

(PJN) Morte Comm - Lucile Ball, dead at 77.

(???) Bored Comm - will get glass put up soon (i.e. over the summer).

(JCC) Moo Comm - Transformers, The Movie = drop date movie.

(HAM) Strek Comm - Fresh episode of Next Strek tomorrow night; Riker meets his father unexpectedly.

(R P) Piano Comm - Keyholder notes are almost complete; y'all be ready to sign the back of them.

(C H) Moo Comm - pretty vague, hopefully more detail coming up.

(WDS) Whoosh Comm - Atlantis didn't fwoosh today.

\goto{Old Business}

(HAM) In relation to the Hugo's and ballot stuffing - one of the authors who was nominated for best novel (Todd Cameron Hamilton, P.J. Beese) and best professional artist withdrew himself from it when he found out he got in because of the ballot stuffing.  (side effect stuff)

(PJN) Salary for summer - employer finally told me I'd be making 30 dollars a week more than the maximum they originally told me I could make.

O.B.A. usual... \bing

\goto{New Business}

(Seth) Mini Cult - Kindler Gentler News - see blue folder.

(PJN) Motion to condemn Donna for falling asleep on a banana colored couch.

Motion passes, a few to less, to even less.

\vspace{12pt}

\noindent
Meeting adjourned, 1721 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
