\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 26, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(WDS) Yo.

Motion passes, about 3 to none to 2 plus Spehn.

\goto{Committee Reports}

(LAK) Moo Comm - I saw a neat show that said that this is going to be the summer of the sequel and there are going to be more Roman numerals floating around than after the Superbowl.

(WDS) Sit Comm - Last week's Nextrek was pretty terrible.  Tomorrow's is the episode that had the working title of "Send in the Clones", but apparently they've changed it.

(LAK) Ex-Skinner Report - Herb has a car and it's banana colored.

(WDS) Jour Comm - Write for TZ!

(PJN) Meetings for the summer will be at 6:30 starting two weeks from today.  If we have the interest, we'll have a meeting every week, otherwise we'll hold off to every other week.

\goto{Old Business}

(WDS) Neil Armstrong was talking to reporters, and he now claims that that "One small step", etc. thing was made up on the spot.

(PJN) About an hour ago, a guy walked in claiming that his wife was President back in 1962.  The name was either Lang or Long.

Time warp to committee reports as Herb walks in:

\goto{Committee Reports}

(HAM) Aloha Lenscomm - I picked up Mandor, my banana yellow CRXSi, and it's very happy. (Mandor = Merlin's older brother in the second Amber series.) (Garbage actually appears here, as HAM had been Albanianed for a year)

\goto{Old Business}

Old Business Algol - um, us, uv, ur, \bing  

\goto{New Business}

(PJN) An Assassins game is going on, and you can throw out anybody from the library if they're annoying you.

(C H) My car died.

(LAK) Move to comdemn the Albanianed ex-Skinner for wearing a banana-colored shirt.

Motion passes by a little bit more than it would have failed by, to a few chickens.

\vspace{12pt}

\noindent
Meeting adjourned, 1713 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
