\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 10, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Miller, Onseck, recording.

An Onseck with impressive minutes of the previous meeting, read aforementioned minutes to the delight and joy of all present.

(Seth) Motion to approve the minutes as easy-real stewed.  

Before the motion can be considered, Seth knocks the universe off of its axis.  While repairs are made, the motion passes lots, to hardly anyone, to "why don't you do the Witter shipments, Rob, as long as
you're here" plus Spehn.

\goto{Committee Reports}

(L K) Psuedo-Panther Comm - All for a quarter apiece!

(HAM) Psuedo-Piano Comm - We have a new keyholder, Robert Poole, who is our new Piano Comm also.

Herb redefines minutes as keyholder notes. The Onseck tries to use this sudden twist of fate to her advantage - to no avail.

(WDS) Sit Comm - Ann Rice is developing a TV series for the Fox Network that would find an Irish Catholic cop living with an "exotic dangerous female ghost."

(WDS) Move to withdraw from MITSFS everything that we don't have!

Motion passes.

(L K) Jour Comm - TZ out real soon now! (Prospective date - August)

=> introduce time warp

(WDS) Moo Comm - The Fly II; Astronomy Comm - They've spotted the Neutron Star that developed out of 1987's supernova. "Rotating at 1967 rps, with a diameter of six miles - this would mean the surface is moving at almost a third of the speed of light!"  Never expect the Globe to get science right.

(PJN) Moo Comm - This weekend A Fish Called Wanda, Who Framed Roger Rabbit, and The Meaning of Life.

<= time warp wanders off to sample the cheese dip

\goto{Old Business}

(WDS) Old and New - State of California: 7, Charles Manson: 0.

O.B.A. um, us, uv, ur, \bing

\goto{New Business}

(Seth) Mini Cult - Frontiers of Entrepreneurship Department.  The Cookie Monster of PS 224. (Selling junk food to students is illegal in New York - in over six months Virginia Noville (principal) made a
profit of 1000-3000 dollars.)

(RVderH) Mini Cult - The World Wrestling Federation did in fact state publicly that it's all a game and they aren't really fighting for real.

(WDS) Weekly World News Comm - "The Picture EVERY American Wants To See. Inside: First Photo of Ted Bundy's Dead Body!"

Connie arrives amidst a clatter of collapsing time warps and attempts to escape using a rope cleverly unraveled from a handy nearby sweater.

(R G) Move to commend Connie for trying to escape with a banana colored sweater.

Motion passes, many to a few no's with a banana colored sweater to almost no one plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17something SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
