\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 20, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

No minutes anywhere.

(G F) Move to approve the minutes as in a virtual energy state.

Motion fails.

() Motion to approve the minutes as being platonically ideal.

Motion passes, many to just Ken Johnson, to almost no-one plus Spehn.

\goto{Committee Reports}

(WDS) Sit Comm - Last week Next Strek had an episode that had the possibility of being good. They actually had a real story, and they had sixty minutes worth of script - they really tried hard.

(WDS) Move to commend the city of Miami for having the most impressive pre-Superbowl activities they've ever had in the history of the game.

Motion passes.

(HAM) Skinner report - We didn't have a shelf building last week, but show up Sunday the 29th at 10 o'clock am, and then the shelves will really feel like being built.

(WDS) On the same subject, what's the status of Jour Comm?  Is there ever going to be a TZ-40?

(HAM) Real soon now.

(Seth) Strek Comm - The National Inquirer says that it has divulged the secret plot of the forth coming Star Trek V.  It's posted in the LSC office - if you have an inquiring mind....

(HAM) Moo Comm - Aliens, Bladerunner, this weekend.  Also Throw Momma From the Train this Wednesday; sounds like a good idea if not necessarily SF or fantasy. 

(WDS) Moo Comm - The Somerville Theater, the current and probably permanent home of the Orson Wells Science Fiction Marathon, is back in business after being shut down for a bit more than the weekend in a major dispute with their owners about their lease. I don't know how it's been settled but...

(C H) Somerville has the lease for another year, it looks like after that after that it will be turned into another shopping center. Let's go lynch the capitalists bastards.

(G F) (murphel) Comm - the guest of honor at Boskome 1990 is Glenn Cook.

(Most of that last comment was missed because Bill yelped loudly.)

(Seth) Flame Comm - A few days ago the MIT student housing committee had a meeting on building MIT unity. It was a surreal experience. They're going to be having another meeting on the same topic it appears this coming Monday at seven o'clock.  Maybe we can turn this into something interesting.

\goto{Old Business}

(WDS) Move to note that *it* was nineteen and a half years ago today...  six months from now it will be July 20th, 1989 and it will be twenty years ago today, does that help? (Moon landing, richard
nixon?)

(Skinner desperately tries to get rid of 1980 Techniques.)

O.B.A. um, us, uv, ur, usual \bing

\goto{New Business}

(WDS) The Skinner's not here, man. (The Skinner's character is not here, being in jail charged with second degree murder, possession of a deadly weapon (a lesser charge because the weapon was not concealed).)

(Seth) Mini Cult - Q. What is a dit switch. A. It happened at noon.

(HAM) Boskone is in slightly under a week.  And those of you who aren't going to be there can come up and visit our wonderful shelves and help build them. And we may have an inventory sometime in
February.  

(Malcolm) Pseudo boring Mini Cult - I believe that Superman the Movie is the only motion picture ever taken directly from a comic strip that was successful. According to today's Herald, there are no less than ten movies in various stages of preparation taken from comic books or comic strips- Roger Rabbit has laid a deadly toll on the
community.

(G F) Mini Cult/Sit Comm/Fame Comm - I was recently shown a video tape taken from the BBC, of a program about Pandom, which of all people, I was visible.

(WDS) I've got new glasses? Does that count?

(PJN) Motion to chastise Bill for getting new glasses that didn't have banana colored rims.

(RVanH) Motion to commend the skinner for having a banana colored "I'm not here" button.

Both seconded, second motion passes, a few to not that many, to even less, plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
