\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.60in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

October 20th, 1989

\end{center}
 
\vspace{0.15in}
{\em bing\/} MITSFS meeting called to order, Friday, October 27th, 1989,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the multiple minutes?

(HAM) Move to approve the minutes a whiskered.

Motion passes, 6 to 4 to 2 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(HAM) Aloha Lenscom - We have pictures over on the table of various people.

(PJN) Strek Comm - A model of the Enterprise went up in Lobby 7 the
night before Shatner's lecture.  This monstrosity is currently in the
hands of phys plant, and will hopefully soon go to the MIT Museum to
go on display for a week or two, and then come to MITSFS.

(LAK) Jour Comm - I have no book reviews and I'm not going to publish
until I have some.

(WDS) Quake Comm - They've upgraded it from 6.9 to 7.1

Motion to commend the earthquake passes by Skinnerial decree.

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

(WDS) The big chess match was, and Kasparov apparently defeated Deep
Thought without very much effort.  Various experts were surprised by
the feebleness of Deep Thought's game.

(WDS) Move to reaffirm the Society's faith in the Great Pumpkin.

Motion passes, 9 to 2 to 2 plus Spehn.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

Time warp back to committee reports:

(JCC) LHE Report - We made \$1,200 in dues in September from 84
memberships, including both new and renewal.

(C H) Mini Cult - Diana Muldaur, now that she has been dropped as Dr.
Pulaski from STTNG, will be a featured character on L.A. Law.

(WDS) Mini Cult - Shatner did speak last Tuesday, in Kresge to 450
people, which translates to about 840 empty seats.

(C H) I finally saw an episode of {/em Quantum Leap} this week.  I
gather this was not the usual sort of story, as the guy Sam ended up
in the body of female, Samantha.  It was very strange, sort of
refreshing almost.

(WDS) Mini Cult - Sometime I think that Jim Davis should not be
reading comics that children read.  This week's {\em Garfield} is a
case-in-point.

{\em Rabbits Have No Tails at All} breaks out among the crowd.

A first Miller motion fails.

A second Miller motion is proposed and passed, 12 to 2 to 2 plus
Spehn.

Meeting adjourned, 1726 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
