\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 8, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(HAM) Move to approve the minutes as longer than most meetings.

Motion chickens by some count that had more chickens than anything else, plus Spehn.

(LAK) Move to approve the minutes as go away Seth.

Motion passes, everyone to no one to a few chickens plus Spehn.

\goto{Committee Reports}

(ESD) Fweek Comm - I need people to sign up to keep the library open on Saturday from 4-6 and 7-8:30. (Connie and Herb volunteer.)

(C H) Moo Comm - I saw Millenium. I didn't pay full price. In every iteration, it gets worse.

(RVH) Moo Comm II - Wizard of Speed and Time is still going until next Thursday at least. Call the Nickelodeon for times.

(LAK) Related Moo Comm - Herb and I went to the 20th Century Fox Presents slideshow at Worldcon and they had a slideshow from an upcoming movie called Night Breed, based on Clive Barker's book Cabal.

(WDS) Moo Comm III - LSC's reg. day movie is Bill and Ted's Excellent Adventure, which I just saw a couple of nights ago. It's worth seeing as an LSC movie.

(LAK) Jour Comm - Write for TZ already!

(WDS) Strek Comm - Season three of Nextrek starts real soon now. Whoopie Goldberg will be back for 8 episodes.

(PJN) Who Comm - They've just done something to Dr. Who that may spell the death of the series. If you want to know, come ask me or Herb.

(PJN) Skinner Report - The Skinner now has a car up here.

\goto{Old Business}

(HAM) If Meryl ever shows up, this will probably be her last meeting.

(WDS) Noreascon was last weekend. It went off rather well, at least as seen from outside.

Old business Algol - Usual everything: \bing

\goto{New Business}

(WDS) There's going to be a TV show this fall which is a spinoff from Alien Nation.

(C H) The Hugos are falling apart, literally.

A chorus of Rabbits Have No Tails at All starts.

(S G) Miller Motion!

Motion fails.

(S G) Second Miller motion!

Motion passes, by some overwhelming vote.

\vspace{12pt}

\noindent
Meeting adjourned, 1727 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
