\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 14, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes from the previous two meetings read and corrected.

(C H) Move to denounce the minutes.

Motion passes, by one.

\goto{Committee Reports}

(HAM) Pseudo-LHE Report: The LHE blew it big time. (Forgot to put money in correct account before writing NEM a check.) Pseudo-Picniccomm: May 14th. Invitations going out soon.

(RVderH) Moocomm: Bill and Ted's Excellent Adventure is actually a rather cleverly done time-travel story and worth seeing.

(HAM) Moocomm sub II: Scrooged tonight. Saturday is the festival of animation.

(C H) Jourcomm: mailing list- real soon now and other excuses.

(WDS) Phonecomm: Northeastern mnemonics alt-11bm (alternate libraries at MIT).

(G F) Concomm: On the door is the next copy of the Hugo Ballot. Also, D.C. in '92 just folded.

(WDS) Mortecomm: New Hope, Pennsylvania- Abby Hoffman, dead at 52.

(C H) Moocomm sub III: Baron Munchausen, worth seeing in a theater on a large screen.

(WDS) Sitcomm: Nearly Departed is harmless. Eric Idle is fun but nowhere near John Cleese's class.

Phonecomm: ring. Warren Du, Liz Arheart, blank shrugs.

(WDS) Sitcomm sub II: Hard Time on Planet Earth finalist for all time dumbest episode, any category: "Jesse's win on The All New Dating Game pairs him with a woman already involved with a man who dates women in order to burglarize their apartments."

\goto{Old Business}

O.B.A. Usual nothing x4.

\goto{New Business}

(L K) Minicult: William Shatner is entering authordom. Tekwar accepted for publication.

(HAM) David Garrold accepting donations which will be given to an AIDS research group. For 50 dollars, he will name a non-speaking character in his next book after you; 100 dollars for a speaking character; 150 dollars for a worm.

(RVanD) Minicult: "MIT Nerds for Choice" a common chant on the march route. (Pro-choice March on Washington.)

(WDS) Move to note that the MIT Museum Shop has, for 60 cents plus tax, the postcard of the favorite Edgerton photo of a bullet piercing a banana.

Motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
