\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.60in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

November 3rd, 1989

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, November 3rd, 1989,
1700 $+ \sigma$ SST, Philip J. Nesser, President and Skinner
presiding.

(PJN) Motions concerning the minutes?

(HAM) {\em hahahahaha!}

(PJN) Motion fails, 2 to 5 to 3 plus Spehn.

(CMA) Motion to approve the minutes as non-dairy milk \underline{        }

Motion passes 11 to 1 to 3 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(G F) People's Albanian Embassy - A couple of months ago, Boston
Magazine had an article on food which included the following joke:
I've read books on Cooking with Flowers, Cooking with Sun-Ripened
Tomatos, Cooking with Kiwis, and Cooking with Albanians, etc.

Lots of silly motions are proposed and either shot down or passes by
Skinnerial Decree.

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(S G) {\em Something about a buffet for Men Who Cook}

(HAM) Mini Cult - Robert Heinlein has been put on the ballot for
Commencement speaker.

(HAM) Motion to ignore that with a banana.

Motion fails 4 to 6 to 1 plus Sphen.

Phil seizes upon a totally obsure and unknown motion with the word
``banana'' in it, and enforces a vote upon it.

Motion passes, 6 to 4 to 2 plus Spehn.

Meeting adjourned, 1710 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
