\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 22, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(HAM) Motion to condemn the Onseck for not returning with a teenage-mutant ninja banana.

(PJN) "Fuck off and die."  \bing

(WDS) Motion to approve the minutes as "Oh sorry."

Motion passes, 9-0-5 +Spehn.

\goto{Committee Reports}

(HAM) Who Comm - There are two rumors about Dr. Who floating around. One is that John Nathan Turner is going to leave Dr. Who and no longer be producer. The other is that the BBC is going to sell him the rights to Dr. Who, and he is going to produce it privately.

(PJN) Moo Comm - LSC is showing The Last Temptation of Christ tomorrow in Kresge.

(C H) Pseudo-Moo Comm - Apparently, Bill and Ted's Excellent Adventure II is in preproduction.

(WDS) Sit Comm - Quantum Leap is back. You also needed a satellite dish last Wednesday because CBS's satellite lost it in the middle of Wiseguy.

(C H) Disaster Comm - One of the people who survived the LaGuardia crash in good shape was a man on his way to get married in Wilmington, S.C., which was hit by Hugo. He was still planning to go through with the wedding if the church was still standing. However, he had contracted to honeymoon in St. Croix.

(LAK) Jour Comm - I haven't gotten any reviews yet.

(WDS) Strek Comm - I don't when we will ever get the new season of Nextrek.

(KRJ) Sit Comm - I saw Alien Nation. It's better than one would expect of a TV science-fiction series. By the way, I want to make it clear that I am not the Kenneth Johnson that was the executive producer and writer on that episode.

(PJN) Den Mother Comm - Remember how we had so much trouble over the summer with keys? Well, today I went to get some LSC keys.  Steve Worley, the current chairman and I went up to the Campus Activites Office and Steve said  "Hi, I want to add someone to the LSC keylist. This is him, give him two keys."  They said, "Great.  Here's the list. Add his name, here are two keys."

(C H) Sit Comm - I saw The People Next Door. It wasn't too stupid, but it wasn't too funny either. The basic premise is a Thurber-like cartoonist whose imagination comes to life.

(   ) Bat Comm - I'm looking for people 30-37 who watched Batman when it was first on for a research survey.

\goto{Old Business}

(LAK) I talked with Scott Kitchen last weekend.  I'm going to go visit him next weekend for a couple of days.

Old business Algol - Usual everything: \bing

\goto{New Business}

(WDS) Harlan Ellison is Watching is out. It is a collection of his film flamings. It includes stuff from over 30 years of columns.

(PJN) Mini Cult - Hugo.

(C H) Last night, @u(48 Hours) did a special on Hugo. This reporter from Maryland went into a wind tunnel and was strapped down in a 110 mile/hour wind.

(Anon) Miller motion!

(PJN) Motion fails!

(KRJ) Miller motion!

Motion passes, 5-2-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1723 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
