\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 28, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(DSK) Motion that apathy reigns.

Apathy reigns for a minute, thereby passing the motion by definition.

\goto{Committee Reports}

(WDS) Strek Comm - Even if you didn't see last week's episode, you've probably seen most of it.

(PJN) Skinner Report - I think I've fathomed the reason why Highsmith thinks we owe them money.  They sent us a copy of the invoices that they think we haven't paid and one of them has Bill To: MITSFS and Ship To: Mark Kantrowitz, Business Manager of the Tech for a set of walnut bookcases that we never got or ordered.

(PJN) Piano Comm - Things are finally straightened out with the Campus Activities Office upstairs.

(PJN) Jour Comm - Write for TZ, write for TZ.

(WDS) Moo Comm - Connie and I can do a good Siskel and Ebert here because I give Lethal Weapon II every bit a large thumbs down as Star Trek V.

\goto{Old Business}

(WDS) The City of New York won its legal battle with Paramount, or whoever, so that the company will stop running the ad for Friday the 13th, etc. in which the I Love New York logo is shown.

Old Business Algol - A couple of usuals: \bing

\goto{New Business}

(C H) Weekly World News Report - "Cool Cows Produce More Milk" and "Baby With Four Ears Has Quadrophonic Hearing."

(MJG) Miller Motion!

Motion fails. \bing

(RJG) Motion to commend Rob for waving around a banana-colored shirt.

Motion passes, 6 to a couple of finely misted cows to 2 plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
