\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 27, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous three meetings skimmed.

(WDS) Move to send the tape that nobody can decipher to the NSA and see what they can do with it.

Motion passes a fair number, to an unfair number, to a number most foul plus Spehn.

\goto{Committee Reports}

(HAM) Moo Comm - Vampires from the Beach this Sunday (The Lost Boys), and the SF marathon Wednesday: Star Trek IV, Spaceballs, The Empire Strikes Back, the original Blob, This Island Earth, Jason and the Argonauts, Outland.  They weren't able to get hold of the feature length Wizard of Speed and Time.

(WDS) Sit Comm - Another new episode of Next Strek tomorrow and that's all I know about it.

(L K) Jour Comm - Going to the printers on Monday, deadline for TZ-41 is June, hopefully coming out by August. Justification for TZ-40 coming out in 1989: fourtieth birthday of the MITSFS.

(HAM) Pseudo Skinner Report - We're having a shelf building, Sunday, 10 am.  Come, help.

\goto{Old Business}

Old Business Algol, um, us, uv, ur, \bing

\goto{New Business}

(WDS) Mini Cult - From the January 24th of this year Globe, Norwalk Connecticut. According to police, an eight month old mixed breed shepard, named Ebony, nudged George Valone out of his car when Valone opened the door at a red light in order to spit. The car rolled through the intersection and came to rest against a building. The dog was unhurt.

(P D) Robot Report - For the next two hours over in the Sloan school on the sixth floor, they will be having an AI robot olympics.

(HAM) The next one of those is out. (Katherine Kurtz, Volume I of the heirs of Saint Camber.)

(K J) Speaking of new books that are out, this arrived in my mail recently.  You may remember Martha Barter who came here and was doing research. (The Way To Ground Zero)

(WDS) Mini Cult - You may be aware that baseball card collecting is now a big time thing in America. There are three companies that produce baseball cards, being Topps, Fleer, and Donruss. The Fleer 1989 cards are out, and one particular card is an incredibly hot item - it's going at trading shows for about 100 dollars, and unopened packs are going for huge prices. It is of Billy Ripkin, who I think is on the Orioles. He is standing there with a baseball bat over his shoulder holding it in such a manner that the handle end of the bat is visible to the camera.  Unbeknownst to him, the photographer, or the folks at Fleer, a teammate of his had written two words on the end of the bat which faces the camera. The second word was 'face' and the first was almost but not quite 'duck'.  The cards got printed with this still on it and still legible. Donruss is frantically trying to recall these with no luck whatsoever.  They are of course going to print them from now on with this little message air-brushed out. Speculation on how this will appear in future listing on baseball card prices: Billy Ripkin expletive vs. Billy Ripkin expletive deleted.

(HAM) I'm not sure where it goes - i.e. more mail for Nestfa ends up delivered to mitsfs.

(PD) Motion to send a banana by Interdepartmental Mail to box G.

Motion passes not too many, to a very deep voiced Connie, to almost no one else plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1825 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
