\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 5, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip Nesser, Almost-President and Skinner, presiding. Donna Bell, Onseck, recording.

The Onseck relays the sad news to those gathered that the minutes have indeed been abolished.  She urges everyone to overthrow the established, cruel regime and elect a kinder, gentler president who will re-instate the minutes to their full glory.

(D K) Motion to call the minutes second?

Motion passes to about six, to Robert Poole, to expensive imitations plus Spehn. \bing

Whereupon Derrick is Albanianed for the above motion.

\goto{Committee Reports}

(L K) Jour Comm - TZ 40 is about to get mailed out, so write for TZ 41 already.

(PJN) LHE Report - I submitted all the MITSFS' budget requests today; it came out to several figures.

(PJN) Piano Comm - Initial the new keyholder list on the door.

(R P) Real Piano Comm - There are errors in the new keyholder notes; nobody sign them yet.

(E D) Picnic Comm - All the invitations are out!

(PJN) Pseudo-Skinner and High Smith Report - The backs arrived yesterday at 12:15. Obviously the threats of sending members of the Assassin's Guild out to Wisconsin payed off.

(PJN) Psuedo Insane Herb Comm - We had enough shelves! And we're shifting books this Sunday at 2 o'clock.

(PJN) Next week's meeting will take place in room 5-216, and it's the elections meeting. Bring a sleeping back.

(R P) Whoosh Comm - the obvious. (Magellan thing on its way.)

(WDS) Sit Comm - Next Tuesday at 9 on CBS, Murder by Moonligh) - a murder mystery set on the moon in the relatively near future. Also, last week there was a wimpy Next Strek episode and there probably will be another one this week.

(WDS) Advanced Mort Comm - Berke Breathed is deactivating Bloom County as of August 6th.

(WDS) North Comm - GUILTY GUILTY GUILTY (3 votes).

(R P) Pons and Fleischmann (cold fusion).

\goto{Old Business}

O.B.A. usual... \bing

\goto{New Business}

(Seth) Mini Cult - The winner of list night's Mr. Spring Weekend was Tony D. running for GAMIT.

(A A) Mini Cult - Wall Street Journal: People's Construction Bank of China was designed exclusively for children so that kids will deposit their small change rather than buying candy.  Quote from child "I know that if my little friends and I make small deposits, the money will eventually will become a big amount that can be used for the construction of the Socialist Motherland."

Bill, however, believes this is what the translator told the reporter the child was saying.

(WDS) Mini Cult - Apparently as part of someone's Master's Thesis, a plywood structure has gone up in the Kresge Oval. It's very impressive.

(A A) Mini Cult - The 2nd Annual Percy Awards are out, for fuzzy, obscure, or laughable communications in government. "My God, no one is perfect. I'd like to see your production line sometime."

(Seth) Motion to award Tony D. a congratulatory banana.

Motion passes, people who want to go to Steer Roast to people who don't to a few undecided chickens plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1719 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}
\centerline{Farewell, mortals; don't drink the soup}

\end{document}
