\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 25, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

(PJN) We don't have last week's minutes.  Motions concerning the minutes?

(MJG) Motion to approve the minutes as transparent.

Motion chickens.

(WDS) Another motion regarding the minutes.

Motion passes, unanimous plus Spehn.

\goto{Committee Reports}

(LAK) Jour Comm - If you don't write for TZ, I'm going to break your kneecaps.

(MJG) Pseudo Sit-Comm - This is from Connie, who phoned in.  There was a TV show Sunday night, called Nick Knight, about a vampire who's also a police detective. It was actually pretty good. TV Guide billed it as a Crime-Drama.

(PJN) Skinner Report - Very soon, in 2 Fridays, meetings will be moved back to 5:30.  The library will also be closed during Worldcon to keep random people from wandering in and stealing books.

(A2) Moo Comm - I saw Abyss. It had a lot of neat special effects.  I thought the plot was thin at times, and then events occurred which made it even thinner.

(WDS) V'ger Comm - Voyager 2 is leaving the Solar System after its encounter with Neptune.

(PJN) Fweek Comm - Elizabeth still needs people to sign up for hours during Rush.

\goto{Old Business}

(PJN) Val Stark is back.

Old business Algol - Usual everything: \bing

\goto{New Business}

(A2) I have the Noreascon Scavenger Hunt list.

(RVH) Motion that we make a holster for the gavel out of banana skin leather and carry it around the Con.

Motion fails by Skinneral decree.

(KRJ) Motion to paint the gavel yellow so that we can sneak it into Noreascon as a banana.

Motion also fails by Skinnerial decree.

A chorus of Rabbits Have No Tails begins.

(KRJ) Motion to paint Phil Nesser yellow so that we can sneak him into Noreascon as a banana.

(PJN) Inverse Skinner Rule: \bing

(A2) Miller motion!

Motion fails.

(A2) Second Miller motion!

Motion passes, a lot, to not enough, to not enough plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1717 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
