\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 17, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Phil Nesser, LHE and Pseudo-Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous reading read and corrected.

(Seth) Motion to approve the minutes as not being made of any fruit, whatsoever.

Motion passes, about seven to three to a Robert doing a better Connie than I do plus Spehn.

\goto{Committee Reports}

(L K) Jour Comm - Review books for the next TZ!!

(HAM) Pseudo-Piano Comm - we have a new keyholder, Cousin Larry.

(WDS) Sit Comm - Next Strek last week was fairly good.  The Federation should trade Riker to the Klingons for a good left handed relief pitcher and a player to be named later.

(WDS) Sit Comm [2] - On Jeopardy Wednesday night during their teen tournament, they materialized and dematerialized the Tardis.

(Larry) Moo Comm - Somerville Theater Science Fiction Marathon Sunday noon to Monday noon.

(Seth) Moo Comm - Sunday night, A Clockwork Orange.

(HAM) Moo Comm - Without a Clue is Saturday. Also, this past weekend during the blackout, the Telsy, the Vice, the LHE and I screened Return of the Killer Tomatoes.

(WDS) Pseudo-Moo Comm - The Academy Awards nominations came out, and science fiction and fantasy films once again got screwed over good. 

=> Introduce Time Warp

(HAM) We're still looking for a Picnic Comm.

<= Time Warp collapses as Derrick gets attacked by Elizabeth

\goto{Old Business}

(HAM) Scott called.

(WDS) How old is Scott?

O.B.A. um, us, uv, ur, \bing

\goto{New Business}

(Seth) Great Moments in Toy murphle... a convenience store chain has apologized to a Houston woman whose eight-year old nephew purchased rubber-ducky brand condoms from a toy's store rack.  The company said employees were fooled by the cartoon style packaging.

(WDS) Related note - This month's Consumer Reports cover story is on condoms; in fact, about one-third of the cover is taken up by the word "condoms" in letters about five inches high.

(L K) Move to send for a gross of banana colored condoms from Japan.

Motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
