\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Special Meeting

Sunday, September 3, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding.

Motion passes (15-3-4 +Spehn) to censure the Onsec for failing to be at Worldcon.

\goto{Committee Reports}

Jourcomm: Write for TZ.

A. Joseph Ross: When is TZ coming out?

A chorus: Real soon now.

PJN: State of the Library Report- We're trying to get the whole 5th floor of the Student Center, but they probably won't give it to us. The current officers are: President and Skinner, me; Vice, Donna Bell; LHE, John Conger; Onsec, Derrick Kong.

A comment from the crowd: Some of you would be quite surprised to see how big the library is now.

A. Joseph Ross: Does MITSFS still have the copier I donated?

PJN: Alas, Mr. Fusion has died.

PJN and Herb Miller: We got 6000 dollars from Finboard last year.

Mike Ward: MITSFS owes me 5 dollars.

?: Somebody wants to donate bookshelves, but hasn't made any specific arrangements.

PJN: The hole in the wall was paid off with this year's endowment fund interest.

Robert Sacks: Endowment fund report as of 6/30/89- at 7/1/88, endowment = 7357.97, available funds = 1011.73; 88/89 activity, income = 549.89, expenses = 500.00; balances at 6/30/89, endowment = 7857.97, available funds = 1061.58.

Mobcomm: I spent 500 dollars on books last week.

KenJohnsoncomm: filled in a gap in our pre-WWII British SF collection.

Herb Miller: For the next ten years, everything is Scott's fault.

\goto{Old Business}

Elaine Miller: We resent that.

Report on the People's Albanian Embassy: He's busy at the art show.

Old Business Algol. Bill Starr: Move to note that Bruce Miller is still skiing in Colorado.

\goto{New Business}

Mike Ward: I found someone who was an original member of the MITSFS.

Several people attempt to tell the story of the Smoot marks and rebuilding the Harvard Bridge and really mangle it in the process.

Robert van der Heide: Move to play gavel toss in the hall. Overruled by skinnerial decree.

Ken Meltsner shoots Phil with a "Banana Blaster" (a banana shaped watergun).

Discussion about whether or not the gavel is classed as a weapon under Noreascon's weapon policy.

PJN: "Whoever shall pull the gavel from the concrete..."

Rob Gates: "Move to comment the man with the squirting banana."

Passes enough-not enough-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1718 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Illegible], Pseudo-Onseck}

\end{document}