\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 30, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(According to PJN, "The motion was Lisa sucking Herb.  Take that any way you want to.)

Motion passes, 5 to 2 to 3 plus Spehn. 

\goto{Committee Reports}

(LAK) Jour Comm - TZ has actually been mailed! Start writing for TZ41.

(WDS) Moo Comm - Yow!  I give Batman an 8 or 9 out of 10. Moo Comm sub II: I saw a review of Miracle Mile, but I'm still not sure if it's science fiction of not. It's about some guy who gets a call which seems to be from one of the missile control officer in NORAD in one of the silos, who has gotten word that the Russian missiles are coming, has launched his missiles and is calling his father to say goodbye, but he dialed the wrong number.

(PJN) Early Moo Comm - LSC is showing Last Temptation in mid-September. The LSC schedule is also going in the freshman mailing.

(PJN) Piano Comm - Read the bleeping Keyholder notes.

\goto{Old Business}

Old business Algol - Usual everything: \bing

\goto{New Business}

(WDS) I have here from last Sunday's Boston Globe, the ad for a Kraft Official Star Trek V/Kraft Marshmallow dispenser. Not recommended for children under 3.

(PJN) I'll bet it's on the Noreascon Scavenger Hunt list.

(LAK) Motion to permanently Albanian Chip Hitchcock.

Motion passes by Skinnerial decree.

(HAM) Some incomprehensible Albanian muttering.

(HAM) Motion to wave a magic banana over Larry Lenhoff the next time he comes in and turn him into Connie.

Motion passes, a lot to almost no one to a couple plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1711 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
