\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

September 29th, 1989
\end{center}

\vspace{0.15in} 
{\em bing\/}  MITSFS meeting called to order, Friday, September 29th, 1989,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(WDS) Shut up.

Motion passes, 6 to 5 to 1 plus Spehn.

\vspace{0.15in} 
{\em bing\/} {\bf Committee Reports}

(WDS) Strek Comm -- Tomorrow's the big day; the people in Boston get
to see the first episode of the third season of Nextrek.

(HAM) I'm Not Sure What Comm - Due out in November: Amber 9, Knight of
Shadows.

(C H) Sit Comm - I managed to catch Free Spirit last weekend.  The
acting was OK, the writing wasn't   , but the timing was really great.
There was one bit of stage business, where one of the teenage
children, going for the throat, leaped at the other one, and the
father caught the kid.

\vspace{0.15in} 
{\em bing\/}  {\bf Old Business}

Old business Algol - Usual everything: {\em bing\/}

There is no old business.

\vspace{0.15in} 
{\bf New Business}

(WDS) Mini Cult - August 15th, AP: Toledo, Ohio.  The body of a
trucker was found in the cab of a tractor-trailer that sat in a
parking lot for nine days with it's engine running.  No foul play was
suspected.

(S G) Motion to commend the author of {\em Albanian Softshoe} for not
letting his banana succumb to metal fatigue.

{\em Motion dies for lack of a second}

(G F) There has been a moose sighted in Newton.  The peculiar thing is
that it was sighted on the inside, or east side of Rt. 128. 

(S G) Motion to condemn the moose for not appearing in a banana-colored
binder.

(PJN) Motion fails miserably.

(HAM) Miller motion!

(PJN) Passes!

(WDS) First Miller motion!

(PJN) Fails!

Meeting adjourned, 1718 SST.

\vspace{0.15in} 
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
