\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 3, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous meeting read by the pseudo Onseck and corrected.  

(Seth ?) Motion to approve the minutes as almost but not quite duck-faced.   

Motion passes, many to no-one plus somebody who isn't Scott, to almost no-one to Connie's not here plus Spehn.

\goto{Committee Reports}

(L K) Jour Comm - Ta-da! Easy real-stewed already. (Actually TZ real soon now.) TZ 40 is now on sale for a buck fifty.

(G F) It contains an error.

(WDS) Move to approve the latest Twilight-Zine as being ex-cathedra.

Seconded, ignored, and defined.

(S T) Con Comm - Boskon was, I was there. It was notable that the other two people with me also did not buy next year's memberships because they were also waiting to think about it and consider going to the local alternative, it's called something like ARISIA - held President's Day weekend the same as Boskcon in Boston.

(Seth ?) It's being run by a bunch of ex-Genericon people, and it's going to be media and costume oriented.

(HAM) We temporarily have appointed the Telsey speaker to Highsmith, and she called them up and 'the other two backs are in the mail.'

(WDS) Sit Comm - Last week's Next Strek was. Apparently they have finally tumbled to the fact that Brent Spiner is the best actor they've got in the cast and are utilizing it.

(Seth) Strek Comm - From the net, this woman works at some sort of ceramics company where one of the materials they work with is transparent alumina and another is dilithium oxide.

(WDS) Morte Comm - Ted Bundy is toast.  Sadly, the death at age 101 of the ultimate aeronautical engineer, Sir Thomas Sopwith, whose company which he founded and during the course of his administration there built airplanes ranging from the Sopwith Camel to the Harrier Jump Jet.

(HAM) Moo Comm - The marathon was; it was very long, and my hawaiian hat seems to have vanished at some point during the course of the evening.

\goto{Old Business}

(WDS) Thirty years ago today was the day the music died.

(G F) At a party at Boskon, Janice was the prime mover in the development of a new conspiracy theory.  Aliens are stealing our chocolate - this is why our chocolate bars are getting shorter.

(Seth) Addendum to that?  The theory has been propagated on the net that after Reagan was shot by Hinkley he actually died and was replaced by a stunt double.

(HAM) "You fools, you've captured their stunt doubles!" - Spaceballs

O.B.A., um, us, uv, ur, and as always, \bing

\goto{New Business}

(WDS) Mob Comm - I just got for MITSFS a copy of Sherlock Holmes vs Dracula. You just paid me for that.

(Seth) Mini Cult - Great moments in computer security - part 3573. (MIS training institute sent out an ad for 'A three day conference on micro computer technology and its impact on security, control and audit.  With the recent front page coverage of the computer virus... one needn't be a security specialist to be aware of the problem.'
So, what's the first big benefit offered by the conference? "Special Feature: Software Bonanza - software swap.")

(HAM) Something of an addendum - Three or four days ago the first public domain version of Scheme for pc came out, and one day later the report was out that the copy distributed on the net already had a virus. 

(Seth) Motion to observe that a motion is being made which contains the word 'banana' in it.

(HAM) Does that work?

(L K) We could pass it and find out.

Motion passes, a lot more people than we usually have at a meeting at all to a lightly bearded Connie that can't figure out how to get his monitor to work, to a few chickens, plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
