\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 3, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding.

No onseck, no minutes, no regrets.

(HAM) Motions concerning the minutes?

(R P) Kill them all.

Minutes dutifully struck down in the prime of their existence and given a brief, yet respectful burial.

Motion passes, a lot, to no one, to Seth saying obnoxious, controversial things, plus Spehn.

\goto{Committee Reports}

(L K) Jour Comm - Connie called and she's working on the mailing list, so TZ will go out real soon now. Write for the next TZ already!

(Seth) Moo Comm - Alien Nation, tomorrow night at 7:30 and 10pm.

(WDS) Sit Comm - Hard Time on Planet Earth did indeed premiere on CBS last Wednesday. It wasn't as bad as it might have been.

(HAM) Skinner Report - Still need a Picnic Comm.

(HAM) Skinner Report - The Skinner, in a continuing quest for jobs, seems to have found a likely possibility today interviewing with BBN. When I walked in there and the person who was interviewing me turned out to have lived across the courtyard from me for several years, took as long to graduate as I am, and had a worse GPA than I do.

(WDS) STrek Comm - Puberty is a horrible thing.

\goto{Old Business}

(WDS) .... concord .... still losing money.

(Seth) George Bush xerox, "read my lips."

(L K) I still want my ravs.

O.B.A. um, us, uv, ur, \bing

\goto{New Business}

(WDS) Mini Cult - Eastern Airlines is moving towards a mechanic's strike at midnight... and George Bush took decisive action by deciding not to get involved in the whole thing.

(L K) Motion to shove a banana between George Bush's lips.

Motion passes very few, to even less, to an unheard Seth plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1712 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
