\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 12, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding (for the last time, thank god). Donna Bell, Onseck, recording.

(HAM) Does the Onseck have anything to read, Onseck?

At this point, Donna relates a tale of woe and misfortune and quotes the dictionary on the meaning of abolished.  In the end, she successfully squirms her way out of reading the minutes, partially due to the fact that they are, in actuality, back in the library.

(HAM) Motions concerning the minutes that we did not have because they were exterminated.

(WDS) Move to approve the minutes as the hell out of here.

Motion passes, John and lots of other people to nobody to Vanna Eisen plus Spehn plus Bill.

\goto{Committee Reports}

(J E) Pseudo-gavel Comm - Ken and I recently made a trip to England and much to our surprise as we toured the Tower Bridge, we discovered an entire rack of gavels of different sizes. I have a picture of it here. Unfortunately, they were bolted in.

At this point, Wendy arrives and Tarl says hello to her.

(HAM) Almost-but-not-quite-Skinner report - I will, with a little luck, a week from Saturday, be picking up new transportation, banana-colored transportation. As in, if everything gets together with the loan people, I will be getting a 1998 CRXSi in Barbados Yellow.

(EDS) Picnic Comm - Speaking of transportation, I need someone with a car tomorrow for shopping.

Dead silence falls, despite an appeal from HAM.

(WDS) Mort Comm - Guy Williams, who at one time in his life, started what some people claimed was a science-fiction series. (Lost in Space.)

(LAK) Sit Comm - On a similar note, Channel 27 is also starting Space: 1999.

(WDS) Vaguely Related Sit Comm - There was a made for TV movie on last week called Murder by Moonlight. Despite a lack by acting ability by virtually anybody involved and incredibly contrived love story between the American and Russian investigators, who were fortunately of different genders, it actually wasn't as nearly as bad as it could have been.

(HAM) Moo Comm - Dark Star Sunday.

(PJN) LHE Report - Herb ends his year with a loss for him, because we haven't gotten reimbursed for the filing cabinets, but all-in-all over the year, we've made something like 450 dollars.

(LAK) Jour Comm - Write for TZ 41 already!

\goto{Old Business}

(J E) Ken and I went to this MIT club thing in Schenectady because Lester Thurow was speaking, and we didn't know anybody, and we were looking around when we saw someone with a nametag: Wayne Burrell (of Sex Life With Bicycles). He was amazed that people still heard of him; his wife was there and she looked nothing like a bicycle. He said that he might stop by an MITSFS reunion.

(HAM) Last Friday, I came by and saw a note on the door from Jeffrey Landis, who is a Hugo nominee in the shory story/novella category, (I forgot which) and is apparently an old MITSFS member.

(LAK) Old Skinner Report - Scott Kitchen is again exiled to New Jersey, but will hopefully be able to make it to Noreascon.

(HAM) Last we heard he was flying out to Chicago for a job interview.

(HAM) Almost real business almost intrudes, but as it shall not be covered in the minutes, it shall not have occurred.

(HAM) Witter claims that they are open for business again.

(HAM) Old business algol... \bing

\goto{New Business}

(L E) Mini Cult - One of our Vice-President's epigrams, in speaking to the United Negro College Fund: "It's such a waste to lose your mind, or not to have a mind.  It's true."

(WDS) Mini Cult - The 8th International Bullwor-Litton Fiction Contest has published its winner.  (Onseck refuses to repeat it here.)

(WDS) Mini Cult - This year's winner for the Mattias Rust Piloting Award: The guy Alfred Hunter, who after killing his ex-wife, stole a Cessna plane and buzzed Boston for three hours firing at random with an automatic rifle.  Half the cops want to kill him, the other half are pretty happy now that they have this great story to tell at the cop convention.

(HAM) Let's have the elections:

Nominations for Onseck are: Humphrey, Fawn Hall, the Dark Night, King Kong, Hong Kong, Derrick Kong, and Fay Wray.

The winner is Derrick Kong with 7.42 and Humphrey second with 3.06.

Nominations for LHE are: Adina, Jim Wright, Where was Robm, Highsmith, Dennish, John Conger, Whoever is supposed to win, John's glare, Eels, and John and a 20 dollar drink.

The winner is John Conger with 7.47 and Dennish second with 1.34.

Nominations for Vice are: Dan Quayle, Sarah Foster Tate, Skippy, Adina, Lust, Guttony, and Sloth (running as a team), Salman Rushdie, Donna's name on the board, Bella Donna, and Janice's banana.

The winner is Donna with 8.05 with Lust, Guttony, and Sloth second with 1.64.

Nominations for President are: Rorschtact, Phil, Noriega, Moretsky, My 3 Sins, Dennish + Humphrey, Wendy, What are we voting for?, Herb mumble mumble, A really tacky smoking jacket, Hunter Rose, Pons + Fleishman, Parkay + Noxema, Don't fool wth Mother Nesser, Dukakis, Ollie North, and Linden Larouche.

The vote is Phil with 6.89 and other much less, but this is not a majority, so a second round is called for.

In the second round, Phil wins with much more than necessary with Dennish as official second.

At this point, Phil offers the Skinnership to Herb, who then turns it down. Phil then appoints himself Skinner and issues a few Skinnerial decrees.

(PJN) One, we are time-warping back to the beginning of the meeting and reestablishing the minutes.

(PJN) Second motion: Herb, you have just been Albanianed for a year for all the things that you said as Skinner that we couldn't Albanian you for.

(PJN) From now on, there will be no -er jokes in the library.  Anyone who does it will be Albanianed for as long as I can.

Janice waves her arms up and down with a banana that is seconded by Connie.

Motion passes, a loud few, to an even louder less, to almost too many chickens plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1940 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
