\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 16, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

(PJN) Motions concerning the absent minutes?

(M G) Motion to approve the minutes as transparent.

Motion passes, 10 to nothing to 8 1/2 plus Spehn.

\goto{Committee Reports}

(P ?) Bat Comm - Da, na, na, na, na.

(LAK) Moo Comm - LSC is showing a double feature of Top Secret and Airplane tonight.

(PJN) Moo Comm - Ghostbusters II opens tonight.

(PJN) Piano Comm - Keyholders: read the Keyholder notes.

(PJN) Hunt Comm - Noreascon is having a scavenger hunt. If you're interested, talk to me after the meeting.

(LAK) Jour Comm - We've got lots of review books, a list three pages long now.

(G F) Peoples' Albanian Embassy - I recently found a book by Dean Ing, which is not science-fiction, about Albanians.

\goto{Old Business}

(A2) I have Janice's address at Clarion West, if anybody wants it.

Old Business Algol: um, us, uv, ur, \bing

\goto{New Business}

(M G) I'm going to have a new job in September; I've accepted a job with IBM in Texas.

Miller motion fails.

Second miller motion passes, by some count that's more yes than no plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1711 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
