\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.60in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

October 20th, 1989

\end{center}
 
\vspace{0.15in}
{\em bing\/} MITSFS meeting called to order, Friday, October 20th, 1989,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(WDS) Note that we don't have any motions.

Motion chickens, 1 to 1 to 6, plus Spehn.

(WDS) Motion to note that the first motion failed.

Motion passes, 5 to 2 to 2 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(WDS) Quake Comm - Tuning in for the World Series Tuesday night was an
interesting experience.

(S G) Cornelia Otis - San Francisco.

(LAK) Jour Comm - I got a letter from a guy in Roxbury named Franklin
Hummel, who is urging us to vocally complain to Channel 5 that they
keep cutting into Star Trek in progress, because of football.

(PJN) I Don't Know What Comm - LSC: Shatner will be here Tuesday.

(S G) Related Comm - Shatner is a write-in candidate for UMOC.

(WDS) Whoosh Comm - Two points to NASA for staging an earthquake as a
diversion so that they could launch the Shuttle in peace.

(KRJ) Lib Comm - At Worldcon, I spotted one of the obscure magazines
that we were missing, Whiskers \#1.  Unfortunately, it was going for
50 dollars, as it was a signed copy.  I lameted to a friend, Mark Owing,
about the poor pickings, including this in particular, so he gave me a
copy free.  The second donation is the result of a visit by a German
journalist a few months ago.  In leaving, he asked if we wanted
anything from Germany.  Thus we have, free, a German science-fiction
encyclopedia that came out last year, in German.

(WDS) Chess Comm - Coming up soon is the long awaited match between
Kasparov and the current computer chess champion, Deep Thought.

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

(WDS) The Soviet new agency TASS went bonkers last week and started
reporting UFO landings.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(WDS) Mini Cult -  Three guys were trying to break into a pickup truck,
when the owner arrived.  He chased them, then hailed a police car
which continued chasing them.  Two of the three guys then climbed a
fence on to some other property where they were caught.  The other
property was San Quentin Prison.

(S G) Mini Cult - In the African country of Benin, Matthew Bioa was fined
for destroying the national Air Force.  An avid golfer, he had just
teed off, when Benin's 4 plane air force make a low-level flyby over
the golf course.  The ball went through the cockpit of one plane,
causing it to crash into the other three.  All 4 were destroyed.

(WDS) Mini Cult - In terms of the recent debate over Alfred Packer: A
bunch of experts who dug up the common grave came to one conclusion:
Guilty. 

(WDS) Mini Cult - The Vatican is training priests for missionary work
in outer space.

(HAM) Miller motion!

Fails!

(Anon) Second Miller motion!

Motion fails, by some unknown count.

(WDS) Second Second Miller motion!

Motion passes, 4 to 3 to 2 plus Spehn.

Meeting adjourned, 17?? SST.   

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
