\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 10, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

The Onseck, in a vain attempt to outwit fate, buried the minutes, only to have the evil, I mean resourceful, Skinner summon the minutes by seance. Minutes summoned and corrected.

(WDS) Move to approve the seance as amazing, Phil.

Motion passes, a few to even less, to no-one plus Spehn.

\goto{Committee Reports}

(HAM) High Comm - elusive back panels for shelves expected March 29th.

(J K) Jour Comm - This is a threat. If you don't write for the next TZ soon, this is what's going to be published. (From aspiring author: Jimmy Lee Rushdin of Leesville, SC)

She reads: "Mike moved carefully down the hallway Gary had taken, on the floor Mike saw the bear trap that had been sharpened till it was razor sharp and in the trap he saw Gary's foot, he knew it was Gary's foot because of the shoes. Mike couldn't scream all he could do was run he checked one window then another, finally he found one that wasn't locked. He slide the window open and stuck his head out as he did came down the blade that cut his head away from his body. A large hand reached out and picked up the head and took it down to the basement where there was a hand and foot packed in ice."

(HAM) Skinner Report - Job search: two down, seven to go.

(WDS) Sit Comm - Next Tuesday night on CBS starting at eight o'clock is Aliens in a three hour time slot which, if TV guide has its information correct, the show is actually padded with an additional eight minutes of footage that wasn't in the theatrical release.

(HAM) A week from Saturday: The Concert in Bad Taste.

(WDS) Moo Comm - Terry Giliam's The Adventures of Baron Munchausen opens tonight.

Meanwhile a happy, potentially dead Onseck skips off to confirm that it really is the French version of The Tall Blonde Man With One Black Shoe showing this weekend.

\goto{Old Business}

O.B.A. usual*4 => \bing

\goto{New Business}

(Seth) [see attached Not To Worry, Nature Lover]

The congregation attempts to do something meaningful and sounds terrible; meanwhile Robert VD makes some banana motion involving someone's legs which is quickly seconded and passes by some number, to some number, to some other number, plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1721 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
