\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 24, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous two meeting ridiculed and corrected.

A chair, supporting WDS, motions its way across the tiled floor.

This is seconded by a multitude of scraping chairs, and a pen falling to the floor.  The Onseck is not amused. Tarl whirls ever onward, lulled to sleep by it's own twirling innards.

Motion passes, many to somebody who's going to have to try to transcribe that, to almost no-one, plus an Albanian, plus Spehn.

(Scrape, scrape, shuffle, clang)

\goto{Committee Reports}

(WDS) Fwoosh Comm - The Navy did their first submarine test launch of a Trident II missile. It came up above the surface of the water, ignited its main engines, chased its own tail for four seconds, and self-destructed.

(Shuffle, shuffle, creak)

(WDS) Morte Comm - The Science Fantasy Book Store: next Friday is going to be the end.

(Wind, wind, strain)

(D K) Pseudo Picnic Comm Report - the letter has been sent out.

(WDS) Moo Comm - Something called Split is opening today which apparently is a science fiction movie about chaos theory. Favorable review: Globe, unfavorable: Tech.

(Clank, thud, squeak)

(HAM) No meetings for a while, Buckaroo Banzai next week.

(HAM) Pseudo LHE report - Finboard bought the line again; we got 600 dollars for books, 654.34 for three five drawer filing cabinets, 480 for magazine bindings.

(WDS) Sit Comm - There's a new series on NBC called Quantum Leap. At this point, the droll humor of those assembled proceeds to drag in all the names of all the bad science fiction or fantasy t.v. shows, including ALF. The Onseck, however does not write this out because she's losing her game of tetris.  And a new episode of Next Strek this weekend.

(WDS) People's Albanian Embassy - Albania was the correct answer to a question on Jeopardy last week.  "In 1938, Mussolini's son in law was best man at the wedding at this country's King Zod."

\goto{Old Business}

Old Home Week at the MITSFS: Thomas Kindin, '77 vice; Brian Knight, keyholder still; Sue Hagadorn; Susan Tucker, ex-skinner; Cousin Larry.

(Whirl, whirl, sli-ide)

(C H) Peter Pan and psychological ramifications.

(SST) Our phone number in the Tech Talk has been fixed.

(Click click cl-click-click)

(HAM) Douglas Adams, Mort. Jr., sign things.

(HAM) The Chorallaries Concert was last weekend, was in bad taste, and was hacked. A streaker during Dave Oh's solo.

O.B.A. um, us, uv, ur, \bing

\goto{New Business}

(A2) Mini Cult - someone wrote into the Globe to complain about Zippy's attack on a method of oil painting shown in the PBS series "The Joy of Painting."

(S T) Mini Cult - From the Tech - Iranian Leaders took to the airways yesterday. See attached.

(Clatter, scrape, clatter)

(WDS) What is the most heavily armored land vehicle in the world?  An Iranian Book Mobile.

(S H) Are there any physicists in this room? Is there anything to this stuff? (Room temperature fusion, which leads to an odd, silly, and now lost forever discussion.)

(WDS) Move to note that Louis Alberez is now in a Heisenberg uncertainty state.

(??) Along with Schrodinger's cat.

(Clang, clang, SLAM)

(WDS) Mini Cult - the latest food to be afraid of is potato chips and bananas.

(HAM) A banana colored crane-like object was doing nasty kind of motion things in that corner of the roof.

Motion passes, like this, to no-one plus Spehn.

(CLANG, clatter, clatter, stra-in. click.)

\vspace{12pt}

\noindent
Meeting adjourned, 1743 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
