\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 19, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, John Conger, Pseudo-President and Skinner, presiding. Derrick Kong, Onseck, recording.

John, in a confused state, asks that the minutes of the last meeting be read.

Minutes read.

(RVDH) Motion to commend the minutes for not mentioning Grandma Chicken.

Motion passes, about 6 to less to not enough chickens plus Spehn.

\goto{Committee Reports}

(WDS) Moo Comm - Indiana Jones and the Last Crusade, starring Sean Connery with Harrison Ford, opening sometime this week.

(G F) Moo Comm - It appears that the new movie, How to Get Ahead in Advertising, is a fantasy. The advertising executive grows a second head in the course of the movie.

\goto{Old Business}

Dead silence falls.

John, in a more confused state, consults the notes given to him by Donna and is finally prompted to an Old Business Algol by the Onseck.

Old Business Algol: um, us, uv, ur, \bing

\goto{New Business}

(G F) Move to condemn the Pseudo-skinner from a Sex Life with Gavels.

Motion fails by Pseudo-skinneral decree.

(S G) Move to condemn the Pseudo-skinner for not using a banana instead of a gavel.

Motion passes too many to not enough to something plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
