\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 18, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(HAM) Motion to approve the minutes as several versions of Rabbits Have No Tails.

Motion chickens.

(HAM) Hippity-clunk.

Motion passes, a lot, to no one, to a few plus Spehn.

\goto{Committee Reports}

(LAK) Moo Comm - I saw the ads to Millenium, coming to a theater near you real soon.

(WDS) Moo Comm - On Sept 1st, 2nd, and 3rd, at midnight, the feature length version of Wizard of Speed and Time will be shown at Nickelodeon theater in Kenmore Square.

(LAK) Jour Comm/Fame Comm - TZ made it to Locus under Magazines Received, so write for TZ!

(WDS) Cook Comm - The 5th Black Company book is out and has a completely different set of characters from the 4th book.

(LAK) Pseudo Jour Comm - I have a new car.

(WDS) Strek Comm - Gene Roddenberry has said that from now on anything licensed by Paramount must only involve original characters and concepts that actually appeared in the original series or movies.

\goto{Old Business}

(HAM) Scott Kitchen has resurfaced on the net again.

Old business Algol - Usual everything: \bing

\goto{New Business}

Time warp to Committee Reports.

\goto{Committee Reports}

(WDS) Snip Comm - I was mistaken as to who is holding our scissors hostage. It is not the Technique; next suspect is the TCA.

(HAM) Aloha Lenscomm - My car was attacked by a flying muffler yesterday on Route 3. The car escaped with minor injuries; the muffler fled and is wanted at present.

Time warp closes.

\goto{New Business}

(WDS) George Steinbrenner has shot another manager and has replaced him with Bucky Dent.

(WDS) Move to set up a study to determine whether Herb and Lisa together are as cute as a banana.

Motion passes, 12 to 2 to 3 plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1718 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
