\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.60in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

November 10th, 1989

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, November 10th, 1989,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(D O) Motion to declare the minutes as approved when the fat man, Phil
Nesser sings.

Motion fails by Skinnerial decree.

(HAM) Motion to approve the minutes as plus or minus David Oh.

Motion passes, 6 to 2 to 4 plus Spehn.

\vspace{0.15in}
{\em bing\/} {\bf Committee Reports}

(S G) Cornelia Otis - The Berlin Wall

(WDS) Mort Comm - Barry Sadler died last Sunday after being shot and
critically wounded in Guatamala sometime in 1988. 

(D K) Moo Comm - The drop date eve movie is \underline{Death Race
2000}.

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

(D O) Motion to declare Phil Nesser old business.

Fails by Skinnerial decree.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(RVH) Greenpeace newsletter - They're having a problem with Marianas
fruit bats, also known as flying foxes.  The natives of Guam prefer
their bats boiled, fur and all in a mixture of coconut milk, water,
onion, and spices.  As a result, they are importing bats from nearby
islands.

(HAM) Blue Folder - I have here for the blue folder a copy of
\underline{Forgetfulness of the Daleks}, a Dr. Who parody off the net.

(HAM) Move to not pass any of these motions that just went by with the
word banana in them.

Motion passes 12 to 2 to 4 plus Spehn.

Meeting adjourned, 1711 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}
