\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 9, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(WDS) Motion to be creative about the minutes.

Motion passes, about 6 to 0 to 3 plus Spehn.

\goto{Committee Reports}

(WDS) Moo Comm - Minority report here: I saw Indiana Jones and the Last Crusade and did not like it very much when I was watching it and liked it even less afterwards when I thought about it.

(PJN) Moo Comm - STrek V opens tonight. In a related note, Batman opens June 23rd. Ghostbusters II opens sometime this week.

(WDS) Sit Comm - Apparently there's going to be a spin-off series from Alien Nation. CBS has ordered it, whether for their fall lineup or as a replacement, I don't know.

\goto{Old Business}

Cousin Larry walks in.

Old Business Algol: um, us, uv, ur, \bing

\goto{New Business}

(WDS) Weekly World News Report - A couple of weeks ago, I noticed on the front page what I hesitate to call the ultimate Weekly World News headline, because I know they'll find a way to top it: World's First Interview With Satan.

Time warp back to Committee Reports.

\goto{Committee Reports}

(WDS) Sit Comm - For those who care, CBS has ordered 12 new episodes of Beauty and the Beast, for purposes of plugging it in when one of their new fall shows crashes and burns.

End of time warp.

\goto{New Business}

(WDS) It did not deluge on the MIT commencement and it did deluge on the Harvard commencement.

Motion to commend the MIT Weather Control Department, passes by Skinnerial decree.

Miller motion fails.

Second Miller motion passes, about 10 to nothing to nothing to nothing plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
