\documentstyle[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{-0.60in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\begin{document}

\begin{center}
MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{0.2in}
Minutes

December 15th, 1989

\end{center}
 
\vspace{0.15in}
{\em bing\/}  MITSFS meeting called to order, Friday, December 15th, 1989,
1700 SST, Philip J. Nesser, President and Skinner presiding.

(PJN) Motions concerning the minutes?

(C H) Where's Adina?

Motion passes, 8 to 0 to 3 plus Spehn.

\vspace{0.15in}
{\em bing\/}  {\bf Committee Reports}

(WDS) Sit Comm - {\em Beauty and the Beast}: They actually did kill
off Katherine, in a fairly improbable manner.  They even did an
autopsy.

(LAK) Jour Comm - Write for TZ!

(WDS) Strek Comm - Star Trek V available on videotape, December 20th.

(PJN) Skinner Report - An official time warp is declared from the day
after finals end to the day before IAP begins.  We will be selling IAP
memberships for 3 dollars with upgrades to full memberships at the end
of the month.

(PJN) Hack Comm - Someone on Tuesday put this very grumpy looking ball
of fuzz in place of the Athena owl in the xlogin window.

(WDS) Stuff Comm - People have started marketing certified pieces of
the Berlin Wall for 8.95.

\vspace{0.15in}
{\em bing\/}  {\bf Old Business}

Meryl walks in.

Old business Algol - Usual everything: {\em bing\/}

\vspace{0.15in}
{\bf New Business}

(C H) Mini Cult - A man in Maryland had his lawn rabbit stolen.  It
had been missing for 6 months, when it turned up on his car with a
stack of 30 pictures of it in front of all these famous national
monuments, etc.

(WDS) Mini Cult - There is this computer virus going around which
someone went through a hell of a lot of trouble to market and package.
It is estimated that it cost around 3 dollars per disk to produce and was
sent to lots of people, packaged in the form of information on AIDS.

(DSK) Miller Motion!

(PJN) Fails!

(DSK) Second Miller Motion!

Motion passes, 8 to 7 to 3 plus Spehn.

Meeting adjourned, 1725 SST.

\vspace{0.15in}
\begin{center}
Respectfully submitted,

Derrick Kong, Onseck
\end{center}
\end{document}

