\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 7, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(WDS) Move to approve the minutes as coming along nicely.

Motion passes about 10 to 4 to 5 plus Spehn.

\goto{Committee Reports}

(WDS) Mort Comm - An actor by the name of Vic Perin died at age 73 yesterday. He did the voice over on Outer Limits.

(A2) Sit Comm - I went to a Beauty and the Beast marathon last weekend: Beastathon II.  We did a count of how many people Vincent killed over the two seasons: it was 38.

(WDS) Strek Comm - I think I have finally figured out what has been going on with Nextrek. There has been a bizarre intersection of two different parallel universes in the vicinity of Hollywood. There are two, completely independent, completely different people named Gene Roddenberry, etc., both of which are cranking out episodes. Sometimes we get one from Group A and sometimes one from Group B.

(G F) Fame Comm - We were mentioned on page 141 of the August Analog.

(A2) Moo Comm - Ladyhawke is on TV tonight.

(WDS) Moo Comm - LSC is showing Road Warrior tonight and Ghostbusters tomorrow night.

(PJN) Piano Comm - We've got a new keyholder. His name is David Wilson.

(PJN) Jour Comm - Write for TZ41!

\goto{Old Business}

(C H) Janice hasn't gotten any letters.

Old business Algol - Usual everything: \bing

\goto{New Business}

(PJN) Mini Cult - On Tuesday, a Mig-23 took off from Poland, at which point, the pilot ejected and set it on auto-pilot.  The plane made it all the way to Belgium before crashing and killing a man.

Much random, but interesting conversation follows.

(WDS) Move to not have a banana colored matrix vote.

Motion passes a lot to a few to some stunned people who are laughing too hard plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1724 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
