\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 4, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(Various people) Bing!

Motion passses, a lot of bings, etc.

\goto{Committee Reports}

(LAK) Jour Comm - Write for TZ. We still need book reviews, lots of book reviews.

(PJN) Skinner Report - An Assassins' game is going on. If people in here are doing Assassins' stuff and are bothering people, tell them to stop.

(WDS) Mort Comm - Bloom County is in it's last few days.  This Sunday is the finale.

(PJN) Phone Comm - Ring. (The caller is Andy Su.)

\goto{Old Business}

(HAM) By now, Val Stark should have moved on campus.  She said that she'd be in Westgate by August 1st.

Old Business Algol - A couple of usuals: \bing

\goto{New Business}

(WDS) Mini Cult - An undercover NYC police detective was testifying before a grand jury about some drug work he was doing, and he recognized one of the grand jury members as being a suspect that he had been looking for from a previous case.

(S G) I just was alerted to a federal regulation that was passed shortly before the first moon landing. Code of Federal Regulations, Title 14, Section 1211 prohibits having sex with an extraterrestrial.

(S G) Motion to condemn peyote mushrooms for not being banana colored.

Motion passes, about 12 to none to 6 plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
