\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 23, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

The minutes are nearly forgotten by the absentminded Skinner, but are eventually recalled and saved.

(PJN) Motions concerning the minutes?

RVH makes a motion.

Motion passes, about 10 to 2 to 5 plus Spehn.

\goto{Committee Reports}

(WDS) Moo Comm - As everyone in the universe knows, Batman opened today. There is also something I know nothing about other than it's SF, a movie called Miracle Mile, which is playing at the Copley.

(PJN) Piano Comm - Read the Keyholder notes.

(LAK) Jour Comm - We have more books for which I want to hurt Sue Pitts for not putting the slips in my drawer.

Motion to hurt Sue Pitts passes by Skinnerial decree.

(EDS) Fweek Comm - The flyer exists.

(C H) Moo Comm - Ghostbusters II was seen by me last week.  It had some good special effects and some good lines, but it was sort of like reheating a souffle.  Wait until it comes around to LSC.

(WDS) Preview Moo Comm - Apparently the movie rights to Watchmen have been acquired by Terry Gilliam.  (Minor correction: The rights have been acquired by the studio that has hired Terry Gilliam, who is currently doing directorial duties.)

(WDS) Moo Comm - Honey, I Shrunk the Kids, a Disney film, opens today I think.  It is prefixed with an 8 minute original Roger Rabbit short. 

(PJN) Den Mother Comm - Highsmith sent us a letter today saying that we owed them 4.80 for the extra clips, and that was all fine and dandy, but they also want 85 dollars for shipping our backs to us. I wrote them a nice letter saying the equivalent of "Fuck off and die."

(PJN) Mort Comm - Witter officially dissolves June 30th.

(WDS) Strek Comm - They are having a new episode Saturday, featuring the return of Troy's mother.

(C L) Non Moo Comm - Blockbuster Video, the largest video chain in the U.S., has announced that they will not be carrying Last Temptation in any of their own stores, but they are allowing their franchisee owned stores to decide whether or not they want to.

(WDS) Supreme Court Comm - Let's go out and burn a flag!

\goto{Old Business}

(WDS) Four days from today is the 20th anniversary of the beginning of the Stonewall Riots.

Old business Algol - Usual everything: \bing

\goto{New Business}

(G F) Item from the Thursday Globe Calendar: Rubber Duck Derby. Donate 10 dollars to sponsor a duck.

(WDS) Mini Cult - The Kraft company recently sponsored a contest in which just about everybody won. Various lawyers are cranking up their engines.

A motion with the word banana in it is proposed and seconded.

Motion passes 10 to 2 to 3 to 4 plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
