\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 21, 1989

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Derrick Kong, Onseck, recording.

Minutes read.

(PJN) Motions concerning the minutes?

(WDS) A jungle type sound. (The Onseck refuses to explain further.)

Motion passes about 7 to 2 to 3 plus some very good sound effects by Robert plus Spehn.

\goto{Committee Reports}

(WDS)  Pseudo Mort Comm - Morton Downey has been cancelled.

(PJN) Mort Comm - The famous conductor of the Berlin
Philharmonic, Herbert von Caron(sp?), died on Sunday.

(M G) Strek Comm - Season finale tomorrow.

(WDS) Bridge Comm sub I - I am told that the Smoots have reappeared on the Harvard bridge.

(WDS) Bridge Comm sub II - From Hollywood Hotline, June 22nd: Rhino Records will release the new album by Edgar Winter, called Mission: Earth, based on L. Ron Hubbard's series.

(WDS) (No Comm) - Thirtieth anniversary of Plan Nine From Outer Space.

(LAK) Jour Comm - Write some reviews for TZ 41, or I'll hunt you down and kill you.

(WDS) Moo Comm - Licence to Kill is very good.  It's a more stripped-down, lean and mean James Bond, which I liked.

Much more is said, but none of it is worth repeating.

\goto{Old Business}

(WDS) Probably the best book written about the Gemini and Apollo days at NASA, Carrying the Fire by Michael Collins, is back in print. I really recommend it heavily.

Old business Algol - Usual everything: \bing

\goto{New Business}

(A2) Mini Cult - From today's Wall Street Journal: Are Organic Foods Spiritual Enough?  (The rest is not worth repeating.)

(C H) Ted Turner is giving up about 500,000 dollars worth of advertising to broadcast a pro-choice documentary on his superstation about abortion.

(RVH) Motion to put a Chiquita banana sticker on the sunroof of Herb's car.

Motion passes, 12 to none to 3 plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Onseck}

\end{document}
