\documentclass[10pt]{article}

\usepackage{xspace}

\setlength{\topmargin}{-0.5in}

\setlength{\oddsidemargin}{0.0in}

\setlength{\evensidemargin}{0.0in}

\setlength{\textheight}{9in}

\setlength{\textwidth}{6.5in}



\renewcommand{\thepage}{p. \arabic{page}}



\newcommand{\bing}{{\bf BING!} }

\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}

\newcommand{\ps}{ plus Spehn\xspace}





%%%

%%%  FROB THESE BEFORE THE START OF THE MEETING

\newcommand{\skinner}{Cathleen Nalezyty, President and Skinner}

\newcommand{\onseck}{Laura McKnight, Onseck}

\newcommand{\meetingdate}{Friday, May 8, 2015}

%%%





\begin{document}



\begin{center}



MIT Science Fiction Society



84 Massachusetts Avenue



Cambridge, MA 02139



\vspace{12pt}



MITSFS Meeting Minutes



\meetingdate



\end{center}



\vspace{18pt}



\setlength{\parskip}{6pt}



\noindent

MITSFS meeting called to order, 63.4 Ksec SST, \\

\skinner, presiding; \onseck, recording.



No meeting has been held in some time.  No minutes read.



\bing



\goto{Committee Reports}

An awesome alum wants to give us money for space! But this is difficult because there is no space. No where. The space is all gone, gone forever, in to a little dot. Fwoomp.



\goto{Old Business}

Harriet was made a key holder!



\goto{Current Business}

ELECTIONS!



\begin{itemize}

\item Jarvis

\item Spencer

\item Margarent Thatcher

\item Peggy Carter

\item Space-Time Continuum

\item Iron Man

\item Hal 9000

\end{itemize}



Jarvis and Spencer jointly win!



\begin{itemize}

\item[9] Harriet

\item[1] Tyrion Lannister

\item[3] Smaug

\item[0] Gringott's Bank

\item[0] The Feeral Reserve

\item[0] The worldd bank

\item[0] Donald Trump

\item[1] ketchup

\item[1] ``me''

\end{itemize}



Harriet wins!



\begin{itemize}

\item[5] Sarah

\item[0] Gluttony

\item[0] Greed

\item[3] Steer Roast

\item[1] Sloth

\item[0] Pride

\item[1] Miami

\item[0] Lust

\item[3] Irene Adler

\item[1] Carmen Sandiego

\item[0] Wrath

\item[0] Envy

\item[1] heat death of the universe!

\end{itemize}



Irene Adler wins! and Sarah guesses that since she took second place she'll help her out. Sarah chooses greed as her vice, on account of having been LHE for so long.



\begin{itemize}

\item[8] Cathleen

\item[2] 42

\item[0] Obama

\item[2] Jack Florey

\item[1] James E. Tetazoo

\item[1] J. Arthur Random

\item[0] Stephen Harper

\item[0] Reif

\item[0] Harrison (Ford, Wells, George)

\item[1] coral reef

\item[1] flip phones

\item[1] third law of robotics

\item[1] nobody

\item[1] king george

\item[1] dumbledore

\item[1] harrison ford

\item[1] everyone named harrison

\end{itemize}



sarah  motions to eat banana yea-14, nay- 0, chicken-4

motion passes, yay!



\bing

\noindent

Meeting adjourned by skinnerial decree, 64.76 Ksec SST.



\vspace{18pt}



\centerline{Respectfully submitted,}

\centerline{\onseck}



\end{document}

