\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 6, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, sort of, 1700 SST,
Janice Eisen, Pseudo-Skinner, presiding.

(JME) Motion to approve minutes as deja vu. Passes 13-9-10 +Spehn.

\goto{Committee Reports}

(MJG) LHE Report: We have money! Equity level: 1402.20. We only lost 7.71 last month.

(A^2) Panthercomm: We now have Heretics of Dune. (Note: here follows an incredible lack of enthusiasm.)

(Chip) Pseudo-Moocomm: As with Return of the Jedi, there will be a charity preview of Indiana Jones and the Temple of Doom at the Sack 57 on the day before it opens- possibly also May 23. (As with ST III.)

(JME) STrekcomm: Saw someone with a ST III t-shirt on already. With the date of the premiere, but I didn't see it.

(GF) Pseudo-Pseudo-Moocomm: In the comic book version, the title came out as Indiana Jones in the Temple of Dune.

(ABM) Totocomm: Walt Disney Productions is doing an Oz film called Oz, based on Ozma of Oz or Land of Oz.

(JME) It actually might be decent- with a real little girl as Dorothy who was quoted as saying that Judy Garland had appeared to her in a dream and said "It's okay, you're Dorothy now."

(A^2) Tarzancomm: Greystoke is out- reviews say jungle scenes okay but England scenes are boring. (RH) Only version authorized by the ERB estate.

(KM) Moocomm: Zelig has good special effects but otherwise bleh. (JME) I disagree, etc., etc.

Here follows an incredibly tedious discussion of whether Zelig is SF, Fantasy, speculative fiction, or whatever.

(JME) Why are we talking about this? Move to condemn the Society as being stupid. Passes everyone-no one-3 or 4 +Spehn.

(JME) Photocomm: Our new Society picture is in- see Skinner for a copy at 1.50.

Flaming.

(B*) Pseudo-Moocomm: Novelization of V is coming out, about 400 pages by "famous SF author J.A. Crispen." (Many groans.) Part II of V (final part) is May 6.

\goto{Old Business}

(A^2) Carl Hylin, ex-Skinner, called last weekend to say hi.

OBA, etc. (AbM) What about "usual debate?"

Susan hits Adam with a Locus.

(JME) Motion to condemn Susan for hitting Adam with the Locus instead of the gavel. Passes several-fewer-3 or 4 +Spehn.

Much flaming. Bob gets Albanian motioned.

\goto{New Business}

Merryl shows off her new prefrosh.

(B*) Minicult: We now have a comic version of Another Fine Myth (Aspirin).

More flaming.

Adjournment song attempt fails.

(GF) Move to stick a banana in KM's mouth. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST. My God, that was a flaming (flameful) meeting!

\vspace{18pt}

\centerline{Calmly submitted,}
\centerline{Andy Su, Onseck}

\end{document}