\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 9, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, almost 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(ATS) Move to approve minutes as redefining the word "incomprehensible." Passes 17-12-5 +Spehn.

\goto{Committee Reports}

(TLH) Moocomm: Brainstorm tonight.

(JME) Jourcomm: Post Awful is being an asshole about mailing TZ- no longer book rate, won't accept our envelopes.

Suggestions to go to another post office.

(Adam) Surveycomm: SF survey attached.

(TLH) Lecturecomm: Dr. D and Weird Al and Tom "T-Bone" were, and those of you who didn't go really missed something.

(JME) Retraction of "What-are-we-coming-to-comm?"- Eat It by Weird Al was on WBCN.

(TLH) Moocomm: Empire Strikes Back is coming next term on LSC.

(JME) Greasecomm: I'm going to be working for the Dem. State Committee this summer. (TLH) Gag me with a gavel.

\goto{Old Business}

(JME) Move to censure McGovern's people for misspelling Arlo Guthrie's name.

(TLH) Patrick Michael Gunkel returns! (The skinner assaulter.) Chased away when campus police were called. I was waiting for him to try something- I wanted to hit him.

Some more flaming on Gunkel.

OBA, usual everything.

\goto{New Business}

(ATS) Zzzzzzz (interminable wait).

(TLH) Minicult: Campus Crusade for Cthulhu is starting an MIT chapter!

(JME) Minicult: A 77-year-old woman was arrested for husband beating. (He was 80 years old.) Even though she was confined to a wheelchair, she kept him terrified for 3 days.

Adjournment song sung.

\vspace{12pt}

\noindent
Meeting adjourned, ~1720 SST.

\vspace{18pt}

\centerline{S-L-O-W-L-Y submitted,}
\centerline{Andy Su, Onseck}

\end{document}