\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 12, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (10/5/84) read and corrected.

It should be noted that due to the absence of the Onseck (in both mind and body) Janice took it upon herself to read and criticize the minutes. Well, Adam can't spell Ecclesiastes, and he can't spell Kerry- he spelled it "Carry;" gee, he must be a Stephen King fan ha ha ha. Well, let it be known that the Onseck will have his revenge, yes he will, it's the nature of the job.

(JME) Move to request Adam prepare the minutes at the last minute from now on so that they'll be more accurate. Seconded. Passes about 9 or 10-7 or 8-3 or 4 +Spehn.

\goto{Committee Reports}

(JME) Pseudo-Boredcomm: The board is getting boring. Boredcomm mutters "Real Soon Now."

(JME) Pianocomm: We have a new keyholder: Susan Tucker. (Applause.)

(Ken) Moocomm: Silkwood (tonight) is sort of science fiction.

Janice points out that there's also Dr. No tomorrow. Ken makes the mistake of saying "Doctor Who? No..." and Janice makes an Albanian motion; seconded and passes "pretty unanimously."

(Adina) Sitcomm: The Twilight Zone marathon was. The color-added episode was fairly neat-looking, and it had Robert Duvall in it too.

Y says that he has a Minicult, and Janice says "That's new business; why can't anybody understand that?"

(BPS) Sitcomm: The return of V on NBC starts Sunday night. First a repeat of part 2, and then the series starts about a week later.

(JME) Notsciencefictionbutyououghttoseeitanywaycomm: Jeeves Takes Charge is really great and anybody who can scrape up the money to see it should.

(BPS) Same comm as she just reported- Little Drummer Girl is also very good.

(JME) Pseudo-Moocomm: This Friday, Brother from Another Planet opens; it's about an alien who lands in Harlem (Bill notes that the alien is black). Y mentions that if anyone cares, there's a review of it in today's Glob; nobody cares.

At this point in the meeting, some random walks in and asks if somebody by the name of Adam Mellis is around. Bill replies, "No, fortunately for him," and Janice makes a Finger motion. She asks if she can leave him a message and is directed to the bulletin board.

\goto{Old Business}

OBA: um, us, uv, ur, blah blah blah, this is boring.

\goto{New Business}

(Y) Minicult: A genuine ghostbuster went to see the movie Ghostbusters and was impressed by how authentic it was; the only thing that he found to be unrealistic was the ectoplasmic confinement device.

(JME) Sic transit gloria mundi- Scott Carpenter came to MIT to speak and they put him in Kresge, and only about 150 people showed up. Move to note that LSC still sucks. Seconded. Passes by Skinnerial decree. People flame about him and Harlan Ellison.

(Y) Move to commend the Skinner for conducting the entire meeting by herself. Dies due to resistance. Meanwhile, somewhere in Albania, a duck says "Well, I guess she's not that good of a conDUCKtor after all. Quack! Quack!"

(RvdH) Miller motion. Fails 10-15-1 +Spehn.

(Y) Move to commend the Skinner for making an accurate count. (A chorus of neaaas are heard.) Motion dies for neahing.

(SSDT) A personal ad in the Phoenix classified says: "Very attractive, intense single Jewish male, MIT professor, 30, seeks open, interesting, warm SJF for cozy times together. So, what else is new? Box 8250." (The Onseck speculates that the box number, 8250, is an MIT extension.)

(JME) Minicult: BU advertised for a special collections manuscript technician to take care of "the papers of Martin Luther King, Bette Davis, Dan Rather, Issac Asimov..." Note that Asimov's name is spelled incorrectly.

(John Dumas) Move to condemn BU for spelling Isaac Asimov wrong. (JME) That should be a motion to commend them...

(RvdH) Miller motion. Seconded. Passes 10-7-5 +Spehn.

\vspace{12pt}

\noindent
Meeting (yawn) adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}