\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 13, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(ABM) Move to accept minutes as combustible. Passes lots-1-6 +Spehn.

\goto{Committee Reports}

(ABM) Thrillercomm: Mayor Flynn has gotten Michael Jackson to come to Boston- something to do with his upcoming American tour. (Groans, "please no!", etc.)

(TLH) Moocomm: American Werewolf in London tonight. It's great- see it or be stupid. (ATS) Or go see it and be stupid. (TLH) Great special effects, some are pretty funny.

(KM) Move to commend the Skinner for his interesting sense of humor, just hope he doesn't inflict it upon us. Fails by Inverse Skinner Rule.

(A^2) Tolkiencomm: Yet another set of notes dragged out by son Christopher called The Book of Lost Tales Part I, implying that there will be a Part II in the picture. (KM) Almost as good as Hitler's diaries.

Some random from The Tech interrupts, asking for Janice.

(TLH) Move to condemn the person from The Tech. Passes unanimously +Spehn.

(JME) I was talking to a publisher saying how amazing it was that Tolkien is still turning them out after he's dead, and the publisher said "Yeah, but the real trick is that we have some autographed copies!"

(TLH) Bloomcomm: The new Bloom County book is out- in color- at the Coop, Harvard Square, Wordsworth. Also, The Best of X-Men is out.

(A^2) Douglas Adams' The Meaning of Liff is out at Paperback Booksmith for a ridiculous 9 dollars less 15 percent- very small.

(TLH) Skinner Report: Picnic tentatively set for May 6 (depending on whether Hal Clement likes that date) with elections on May 4 in the Spofford Room.

\goto{Old Business}

OBA, usual motion, second, debate, result.

\goto{New Business}

(A^2) Fuzzies and Other People, the "lost" Fuzzies book, is coming out in August.

Dave Broadbent is still competing for the "Big Screw" award- in selling a new membership he neglected to explain the inner workings of the Library. (Either that or the new member was a real mental midget. Which is more likely?)

(KM) Move to condemn Dave for being too engrossed in eating his banana while selling this person a membership. Passes semi-unanimously +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:19:44 Hike SST.

\vspace{18pt}

\centerline{Andy Su, Onseck}

\end{document}