\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 17, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order in Boston Park Plaza Hotel Rm. 913, Boskone, almost 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(TLH) Forget the old minutes.

(John Dumas) Motion to approve the minutes as invisible. Passes 13-12 1/2-7 +Spehn.

(JME) Motion to commend the Skinner on his infinite mathematical wisdom. Passes many-not as many-some crushed potato chips +Spehn.

\goto{Committee Reports}

(MJG) LHE Report: We got money- I'm not saying how much. Brazil is very nice.

(JME) Vice Report: Not enough vice at Boskone yet, but plenty in this room.

(TLH) Moocomm: For Your Eyes Only, Saturday.

(AJM) Moocomm: We missed Metropolis. (Awwww!)

(TLH) Motion to change Adam's initials to ABM. Passes WB +Spehn.

Utter chaos; in changing pages, lots of Albanian being spoken.

(TLH) Techcomm: Does Ken really read Heavy Metal? (KM) Yes.

(JME) Radiocomm: I was interviewed by WMBR in the huckster's room (about MITSFS).

\goto{Old Business}

OBA: um, us, uv, ur.

(JME) Move to give Tom Galloway a better gag. Passes WB +Spehn.

\goto{New Business}

(TLH) Due to the magic powers of the gavel, TV, etc., we are in New Business.

Some (lots) more Albanian.

(JME) Motion to wish Adropov a speedy recovery. Passes.

Various hacks on NESFA, et al, some questions and finger motions.

Adjournment song sung.

\vspace{12pt}

\noindent
Meeting adjourned, about 17:10.497 plus or minus 0.002 SST.

\vspace{18pt}

\centerline{Andy Su, Onseck}

\end{document}