\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 28, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (9/21/84) read and corrected.

(Adina and The Great Purveyor of Truth As We Know It argue about the minutes. Reality sides with the Great Purveyor.)

(MTG) Move to approve the minutes as a minute and a half. Seconded. Fails 1-many many many-several +Spehn.

(ATS) Move to approve the minutes as probably going to be longer than the meeting itself. (Pause.) AbM exclaims, "Not at this rate."

(John Dumas) Move to approve the minutes as more or less correct.

Ken and Janice argue over whether or not the motion to approve the minutes has to pass. Ken says he's been here longer than Janice and knows what the deal is. Reality once again takes a stand and sides with Janice as Adam says "Move to approve the minutes as less correct." Seconded. Passes by Skinnerial decree.

\goto{Committee Reports}

(SLP) Snakecomm: Robert Wiener has a new baby boa constrictor named George, about four months old.

(JME) Ministry of Truth: Another person gone from the keyholder list, but he was voluntary (Larry Lenhoff). Bill P. Starr, Son of Famous Author, asks how long Matt Lehman has been gone and George Flynn and Janice simultaneously say Finger motion.

David Broadbent reads a paragraph from The Tech that claimed that Geraldine Ferraro unfavorably compared JFK's policies with Reagan's. Reality arranged some papers on a stand which it had taken earlier as David explained that what the Tech did is called semantic dissonance. The story was written by Janice and she pointed out that it had been edited by someone else, the bottom line being that it wasn't her fault. Ken mused over the fact that JFK's policies weren't really that good now anyway, as he (JFK) is dead.

(JME) Famecomm (not Flamecomm): MITSFS was mentioned at the end of a TechTalk article on...

(JME) Lecturecomm: There will be a series of readings sponsored by the writing program called "1984 and Counting" starring science fiction writers. See enclosure. One of the consequences of this is that Joe Haldeman's science fiction writing class gets a display case in building 14 next month. It will have MITSFS books in it and a pointer to where more MITSFS books can be found. Reality finishes folding some paper and it flies out the window.

(Some random freshman) Jittlovcomm: Mike Jittlov is planning on making a movie about the making of The Wizard of Speed and Time. Reality coughs and looks confused. Adina explains that the movie is about a guy (reality is heard to say "He's just zis guy, you know?") who is an animator. Some twit mutters "Animator!? I just met her!" and reality clubs him over the head with some steam tables. Mike Jittlov stars and an updated version of Wizard appears in the film. MITSFS also received (via The Tech) a letter from Jittlov. See enclosure.

(JME) Papercomm: New stationary. See enclosure.

(AbM) Pianocomm: Keyholder Notes are really here. Reality looks surprised (and doubtful).

(JME) Move to condemn Merryl for leaving. Passes unanimously.

(Ken) MackReynoldscomm (for dead authors): H. Beam Piper has another book out. Adina says satirically "Wow, that's so new, Ken."

George says he heard a radio interview with Walter Tevis, who died last month. The interview didn't mention he was dead.

(Same random freshman as before) Fingercomm: Dr. Who/Star Trek convention next week. (JME) Motion to ignore that. Seconded. RvdH asks "Ignore what?" (JME) Finger motion!

(JME) Infocomm: Some keyholders still don't have pictures. They are represented by stick figures or Szerbesko Emmer. Dave, whose picture is not up, mentions that he recently found lots of ID photos in his office. They are of Greg Greely.

(JME) Pseudo-Moocomm: Buckaroo Bonzai opens in Boston tonight.

(BPS) Boardcomm: Boy, is this a boring meeting. Reality said that he hadn't noticed as he had dozed off. He said that it wouldn't happen again as he dozed on.

(JME) Motion to note that the people who make it boring are all here right now. Someone says second, and Janice indicates that it doesn't need a second. No, it doesn't take very long at all.

JME calls for more committee reports and exhorts "Speak! Speak!" Barks are heard in the foreground. Reality found this strange as he thought that bark, and trees for that matter, didn't make sounds, but then he lost it again so it didn't matter anyway.

(Ken) Committee to Map John Kenneth Galbraith into the Complex Plane, Inc.: Paul Samuelson lectured today on thermodynamics, showing once again that economists shouldn't really deal with physics.

(BPS) Albanian motion. JME disagrees, saying that it wasn't obnoxious enough.

(Same random freshman as before- reality says that that doesn't sound very random to him, but what does he know?) Janice exclaims, "Come on, don't be so self-effacing!" The random freshman (Jenny) talks about a comic book that mentions the MTA. She thinks that this refers to the T and is corrected.

(JME) Motion to console the freshman because it isn't fair. Passes by unanimous "aw"ing. BPS mutters "Awesome" and is not Albanian motioned.

\goto{Old Business}

OBA: um, us, uv, ur. MTG asks what about the usual debate? JME threatens her with the gavel.

\goto{New Business}

(Adina) Move to commend Merryl for catching Janice off guard. Second. Long discussion about the Inverse Skinner Rule.

(George) Minicult: The Tech says that the rebuilding of the Harvard Bridge will begin in spring of 1986 and the headline says that the bridge will be rebuilt by 1985. Therefore, the MDC has time travel.

JME says that maybe the headline writer has time travel, and BPS adds "Or at least is tripping." Adina ventures forth an Albanian motion and it is seconded. Passes by Skinnerial decree. JME tells George not to translate but to recognize Albanian when it is spoken.

(John Dumas) Minicult: The new South of the Moon is out, and it appears that Marian Zimmer Bradley is no longer an APA : OE. Motion to discard Minicult as too obscure for words. Seconded. Passes anybody with any sense-people with no sense whatsoever-people with half sense +Spehn.

Albanian motion passed on someone who said something.

(JME) Move to note that the entire Star Chamber is present at a meeting "in Roscoe only knows how long." (AbM in body if not in mind.) (John Dumas) Move to commend the Star Chamber on knowing which portion of themselves to show up. He explains that this means mind or body. Dies for lack of a second. Reality mourns its passing.

(AbM) Rabbitcomm: RKW pointed out that we've been leaving out the last few lines of Rabbits: "Same song, next verse, never gets better, never gets worse."

(Adina) Move to commend Robert Wiener by presenting him with a banana.

Miller motion. Fails. Miller motion. Chickens 2-1-chickens +Spehn.

AbM gets the circulating banana and throws it to the Skinner. This is a banana motion. Someone throws the other banana to her. Passes everybody-nobody who's anybody-even fewer people +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}