\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 27, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(ABM) Move to approve the minutes as well attended. Passes 9-8 1/2-8 +Spehn.

\goto{Committee Reports}

(KM) Infocomm: I bought Planetfall and Janice finished it already. It was supposed to take a while to finish but it didn't. Over the summer it'll be available to people who are nice to me.

(A^2) Phroggcomm (as in James T. Phrogg): An article in the NY Times about bookstores mentions a specialty store with an autographed copy of Herbert's newest book Heretics of Dawn selling for about 75 dollars.

(JME) What I want now if for Robots of Dune to come out.

(B*) More-of-the-samecomm: We got a copy of this week's Newsweek article on Herbert and Dune with the title of the seventh Dune book- Chapter House: Dune.

(B*) Frustrationcomm: About a year ago, NBC showed a good TV movie called Special Bulletin and WBZ (or WBOZO) preempted it for a Celtics game. This Sunday when NBC is showing it again, WBZ is preempting it for some mystery movie starring Anthony Hopkins.

Some random flaming and Dave Broadbent, for some reason, says "Damn, this isn't NESFA."

(JME) Move to condemn Dave for being upset that this isn't NESFA. Passes. (Rah!)

(Tom McKendree) Thrillercomm revisited: Jackson is having a full-scale working copy of Pirates of the Caribbean (from Disney World) built as an addition to his house.

Many "Arrgh!"s.

(B*) Sequelcomm: Someone at MCA (the parent company of Universal) said that Spielberg is planning to do an ET sequel "as soon as Steven finds a story he likes."

(TLH) Working title is "ET 2" and being written now.

(B*) Crapcomm: They've started the advance advertising for V: The Final Battle.

(B*) Move to root for the aliens. Passes. (PS) Go Aliens!

Much flaming on how bad V is.

\goto{Old Business}

OBA, usual motion, usual etc.

\goto{New Business}

(JME) Belated Picniccomm: Did you get hold of the Haldemans?

(ATS) Yes, they can come!

(B*) Wow, you mean there might be competition in the Famous Authors division of the Gavel Toss?

(Tom McKendree) He (Haldeman) told a joke that a Polish SF author told him: There are four dogs- French, American, Polish, and Russian. The French dog says "It's so terrible- I had to bark 2 hours last night before my master would give me any meat." The American dog says "You have to bark to get meat?" The Polish dog says "You get meat?" And the Russian dog says "Your master lets you bark?"

(B*) Move to commend Janice's shirt. (Banana-colored.)

Simpson doesn't get this.

(A^2) Move to commend Simpson for having a button that is the same color as Janice's shirt.

(TLH) And for not realizing that they're both banana colored.

Cries of "He said it!" and "Ni!" Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 17:24:25 SST.

\vspace{18pt}

\centerline{Andy Su, Onseck}

\end{document}