\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 13, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(KM) Wheeeeeeee! (Mechanically.) B* seconds. Passes 2-0-1 +Spehn.

\goto{Committee Reports}

Jourcomm: TZ 35 is here. TZ 36 RSN.

Panthercomm: No inventory if MULTICS doesn't come up. If it is, it will be at 10 AM tomorrow.

Exoduscomm: We start moving on the 28th. We close the Library starting on the 21st.

Some discussion of the time warp, which is over.

NESFAcomm: Somebody came in trying to buy a Boskone membership.

Sanitycomm: Broadbent has dumped his Boskone responsibilities. He recommends no one work for Boskone.

We ramble along about random topics for a while. Then the Skinner takes a phone call on LSC business.

(JME) Motion to condemn the Skinner for taking calls about LSC business during meetings. Passes by my decision.

Authorcomm: Time magazine (1/2/84) reported that Isaac Asimov is in the hospital recovering from a triple bypass. He now has 286 books out and 14 at publishers, making 300 total.

LHE Report: equity 1315.64, loss 35.02.

Vice bitches about delinquent keyholders.

\goto{Old Business}

OBA, etc., etc.

\goto{New Business}

(JME) We're taking submissions for TZ 36 now.

(JME) It's Ken Meltsner's birthday.

(A^2) Minicult: A friend of mine has invented banana-strawberry-daiquiri jello. (She distributes some.)

(KM) Motion to commend above friend. Passes unanimously +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1722 SST.

\vspace{18pt}

\centerline{Signed,}
\centerline{Janice Eisen, Pseudo-Onseck}

\end{document}