\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 2, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (10/26/84) read and corrected.

(JME) Move to approve the minutes as instantaneous. Passes 2 "oy"s and lots of arms and legs-6-a squawk, a snake, and a leg +Spehn.

\goto{Committee Reports}

(JME) Note that Judy Passman just arrived and said that she wasn't really here. (KM) Note also that we've known this for a long time.

(Shawn Gramates) Jourcomm: Sometime sooner or later there will be TZ 36. People are encouraged to review books for this.

(JME) Pseudo-ROSFAP: We received in the mail today a Bulgarian magazine or fanzine. It is noted that it has a picture of a scene from The Empire Strikes Back.

(JME) Skinner Report: Barbara Feinman is Den Mother       again. MITSFS will have to pay 250 dollars per semester until our debt for the hole in the wall is paid off. The Star Chamber will be meeting with the aforementioned Den Mother       next Friday at 4 to discuss fundraising; she considers bake sales a real possibility.

(AbM) Pseudo-LHE Report: Equity level of 3872.85, and this month we lost 236.33 due to the hole in the wall.

(KM) International Committee to Overdamp the New Wave: Thomas Disch did speak on campus and he was lots of fun. He's probably the last of the New Wave... the rest have been hunted down by Omni writers. Gregory Benford was with him and said that his latest novel, which will be out this spring, will be partially set at MIT. It involves a materials scientist, but he got my lab in the wrong place.

(MTG) House-holdingcomm: I'm starting a house-holding in the Sime-Gen universe. It's called MITAR, and we'll have pledges and colors and things like that later on.

(JME) Charge of 10 dollars for free advertising.

(JME) Libcomm: Ken Johnson is now apparently up and walking around.

(AA) He'll be getting the cast off in about a week or two.

(KM) Skinner update- I have your resume; it's available to anyone for a small fee, to be determined by auction.

\goto{Old Business}

(AbM) We have a get well card for Ken Johnson; everyone is invited to sign it. (JME) It'll make us feel good for doing the right thing.

AbM inquires as to whether or not we have an old member with us, and he replies that he's only moderately old; it is noted that he was once a member of the T____ Committee (R.I.P.) and knows its current location. Many hisses and boos are heard and Janice reprimands him.

OBA: um, us, uv, and the ur. A cry of "But what about the usual debate?" is heard.

\goto{New Business}

(AA) Minicult: Bizarre but tragic- a woman received a 600,000-dollar court settlement from DEC when a cow wandered off some land that they own and was hit by a car, and several minutes later, this woman drove by and hit the cow and crashed.

(AA) Minicult: SF Chronicle reports that a 16-year-old media fan was conned out of thousands of dollars and much of his time by someone who convinced him that he had contacts with George Lucas and Steven Spielberg. The 16-year-old ended up stabbing the other person to death. (KM) That was the revenge of the Jedi.

(JME) Minicult: The guy who dumped gasoline all over his wife and set fire to her after watching The Burning Bed on TV apparently bought the gasoline a couple of days in advance of having seen the movie.

There is a protracted discussion of various lists from The Book of Lists. Janice requests that these stop; they do.

(JME) Minicult: We now understand what's in the strange mystery meat in Lobdell after having seen on Hill Street Blues last night the arrest of a restaurant owner who was serving cat.

(JME) Keyholders are encouraged to initial the keyholder notes if they haven't yet done so.

The Onseck begins singing Rabbits, and lots of people join in. As the fifth verse is finished, Janice swings the gavel down and says "Meeting adjourned."

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}