\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 23, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(A^2) Move to approve the minutes as intelligible. Passes lots-1-few voices +Spehn.

Here follows several juicy raspberries to test Tron's mike response.

\goto{Committee Reports}

(A^2) Moocomm: Deathstalker was indeed horrible- it managed to make sex and violence boring.

(Adam) Moocomm: Ice Pirates- ok in parts but takes itself too seriously sometimes (wow).

(B*) Pseudo-Moocomm: ST III rumors- Christopher Lloyd as a Klingon commander, James B. Sikking (from Hill Street) as captain of Excalibur, return of Kevin Reilly. (TLH) Note- in ST II Mr. Kyle returned as a transporter operator. (B*) One of the ships will be the USS Grissom (after our Gus Grissom), plot- old Enterprise bridge crew and Scott and McCoy hijack the Enterprise to find Spock, may end with the second court-martial of Kirk.

(A^2) Dunecomm: Heretics of Dune is out at Paperback Booksmith.

(Adam) Grogocomm: Technique misspelled TLH's name as "Buckleberry." It will be corrected but will remain in the B's.

(Adam) Screwcomm: Dave Broadbent did well in Big Screw.

(B*) Note on ST III- sneak preview May 23, opening early June.

\goto{Old Business}

OBA, usual motion, second, vote, result.

\goto{New Business}

(ATS) Minicult: A sad note- the 80-year-old man whose wheelchaired wife terrorized him for 3 days died this Monday.

(TLH) A moment of silence, please (but only a short moment).

(TLH) Miller motions, please?

Adjournment song barely started...

\vspace{12pt}

\noindent
Meeting adjourned, 17:11:25 SST, so there.

\vspace{18pt}

\centerline{Andy Su, Your faithful Onseck}

\end{document}