\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 19, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding. Due to the absence of the Onseck, Janice read the minutes.

Minutes of the previous meeting (10/12/84) read and corrected... and criticized again.

(RvdH) Move to approve the minutes as banana-colored. Seconded. Ruled out of order; the Onseck was instructed to obtain more orders.

(BPS) Move to approve the Onseck as absent. Dies for lack of a second; "Strange- I thought that it had more than enough time."

(KM) Move to approve the minutes as Garfinkled- for the lack of spelling. Motion nahed. Says Janice, "Ken, that's a Tech inside joke; go away." It is explained that Simson can't spell.

Janice calls for motions concerning the minutes that don't concern Simson Garfinkle. The Onseck does not recall any minutes that concern Simson.

(KM) Move to approve the minutes as having no resemblance to Simson Garfinkle. Seconded. Passes damn near everybody-about 5-3 or 4 +Spehn.

\goto{Committee Reports}

(JME) Pseudo-Boredcomm: Yawn.

(KM) Moocomm: Infocomm has a new game out called The Hitchhiker's Guide to the Galaxy. Note that there was a slight argument over whether this was a Moocomm or Compcomm report.

(JME) IAPcomm: If anyone has any ideas concerning activities over IAP, speak to Janice or Susan Pitts.

Janice deplores the current state of the MITSFS; no more committee reports.

(MTG) Vicecomm: I've been gone for two weeks; I'm back.

Janice, in a desperate attempt to rescue the meeting from the grips of boredom, asks George if he has a committee report or if he was just resting his hand; he was resting his hand.

\goto{Old Business}

(BPS) Brown University students voted to have their medical department stock suicide capsules for use in the event of a nuclear war. See attached article.

OBA: um, us, uv, ur. "But what about the usual debate?"

\goto{New Business}

RKW asks if MITSFS would be interested in occasionally getting printed sheets of fantasy or science fiction color work; Janice answers to the affirmative, and RKW displays an example. After a chorus of oohs and aahs, Janice makes a motion to commend overwhelmingly; passes by acclaim (and applause).

(GF) Minicult: Anyone who hasn't seen today's Bloom County should. BPS points out that this is usually true.

(JME) Minicult: Two newspapers in West Virginia have already dropped Doonesbury as having too much political content and also as being unfairly critical of the president. Merryl adds, "Like they expected different?" (Note that as Janice was starting this Minicult, she said "The freshman is out of order." The random freshman's name is Jenny.)

At this point, a conspiracy of members begins to sing Rabbits but fail after one incorrect verse.

Tom McKendree walks in and says Miller motion. It is noted that this is a McKendree motion. Seconded. Fails 3 or 4 or 5 or 6-3 or 4 or 5 or 6 or 7-2 or 3 or 4 or 5 +Spehn.

Merryl states, "That's all. We're going to get some enthusiasm in this place." She proceeds to remove the whip from a drawer. Various people make appropriate comments, and Herb mutters, "I guess you could call this a lash minute attempt." MTG: "Albanian motion!" Passes by Skinnerial decree.

(SLP) V, the series, starts tonight. Janice hisses, and RvdH says that that's the sound they make. Ken exclaims, "Wow, the entire MITSFS imitates the lizards of V!"

(JME) Minicult: Steven King is doing an American Express commercial. People flame and flame and flame and flame...

(RvdH) Miller motion. Seconded. Passes 10-8-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}