\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 9, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (11/2/84) read and corrected by the pseudo-Onseck (KM).

(BPS) Move to approve the minutes as dead.

(KM) Friendly amendment to change "dead" to "burning dead."

Lots of unenthusiastic yeahs-0-2 +Spehn.

Time warp- someone who might have been Robert vdH called before the meeting with a Miller motion. Too early.

\goto{Committee Reports}

(SLP) Moocomm: TBA at LSC will be STrek III and A PORN FILM.

(JME) Moocomm: Duck Soup and Right Stuff tonight.

(JME) Skinner Report: Barbara Fienman is no longer Den Mother      . She was nice today.

(JME) Lecturecomm: Joan Vinge on Thursday.

Flaming about Dune, Return of the Jedi novelizations or storybooks. Flaming about Dune in general.

(JME) Lecturecomm: Joe Haldeman at 5:05 AM for a reading (24 hours).

(BPS) Spikecomm: 15 percent off to NESFA, MITSFS, and Boston STrek Association until the end of the year on all books. R dv/dH has been assigned to make a good sign.

Dunecomm: Movie sucks. Parody "Doon" by National Lampoon also sucks. 2 copies here.

Sitcomm: Channel 2, 10:30 PM on Tuesday- Double Lunar Dogs from Heinlein's "Universe"- futuristic video. See old bookdrop for more info.

Sitcomm sub 2: PBS will film a John Varley book.

Skinner has good taste in LeGuin stories (she doesn't like "Lathe of Heaven").

Pseudo-Onseck Report: AbM should be here, but he isn't. Neither is Tron.

\goto{Old Business}

SIGH, for Reagan's victory.

Robert Weiner has a copy of our constitution- yow! It's a true rarity. He also has a baby dinosaur with fake documentation (unfortunately with Liquid Paper(TM) on it- an anachronism).

Albanian motion on Scott Kitchen passed by Skinner.

(John Dumas) Move to condemn the Constitution for being sexist.

OBA: um, us, uv, ur. "But what about the usual debate?"

\goto{New Business}

(AA) Minicult: D&D has the antichrist in it and Texans are blaming the death of 2 teenagers (suicides) on it. 700 Club also blames the death of another kid- parents are suing TSR Hobbies.

Move to commend the parents. Passes 327-72-negative 3 +Spehn.

John Dumas has more gunk on this; he will provide us with copies.

Oohs and aahs over Robert Weiner's empty bookplates.

(BPS) Minicult: Senator Jake Gain will be sent on a shuttle ride. (He does, of course, chair a NASA committee... He's also a colonel and has 10,000 hours of air time.)

(Creaking chairs.)

(KM) Old Business time warp- 2 old pictures from Technique about me!

(TMc) Susan Tucker summarized "The Night of the Ripper" (Robert Block) list of tortures as "boring." She's so jaded.

(JME) Watch for people stacking books.

(RKW) Minicult: Don Grant has a bunch of copies from the 2nd printing of King's "The Gunslinger" for 20 dollars- some twit in Florida is selling it for 190 dollars!

(AA) Miller motion. Fails 2-7-6 +Spehn.

(AA) Miller motion. Passes nearly everybody-few-5/6 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kenneth J. Meltsner, Pseudo- and Former Onseck}

\end{document}