\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 2, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, Vice and Pseudo-Skinner, presiding.

The Vice is here, but no Skinner.

Phonecomm: ring. "Collect..." (JME) This is the MITSFS. Collect.

(JME) Motions concerning the minutes?

(MG) Move to accept as back where they belong. No second.

(B*) Move to accept as [illegible]. No second.

(JME) Move to accept as the color of Susan. That's enough [illegible].

(MG) Move to accept as about 500 angstroms.

Decree- red is green for the purposes of this meeting.

(B*) Move to redefine the angstrom as 1/500 of the wavelength of red. (KM) "Redshift." 15-7-2 +squawk +Spehn.

(Tom) Move to have minutes declared colorblind.

(JME) Move to have minutes declared colorblind +500 angstroms. Everybody-a few legs-2 +Spehn.

\goto{Committee Reports}

(MG) LHE Report: equity level 1409.95, gained 467.27 this month due to ADB.

(A^2) Moocomm: Something Wicked, based on Ray Bradbury.

"Hart isn't Greasecomm. He's real power."

(MG) Name for report on pies- MiniTruth?

Tom: "He came."

(JME) Hart opposes Star Wars (Reagan version).

Tom moves to declare visitor's jacket 500-odd angstroms. Lots of smiling happy faces-some boots/shoes/hands-tongue, finger, wrong hand +Spehn.

Librarycomm: Star Trek and Star Wars models hanging from ceiling shortly.

(John Dumas) Move to declare the Klingon ship red. Everybody-negative everybody-0 +Spehn.

(KM) What's the wavelength of white?

(JME) Passes by decree (finger motion).

(JME) Lecturecomm: Haldeman lecture was good, but not many people showed.

\goto{Old Business}

OBA, usual motion.

\goto{New Business}

Minicult: LSC is jealous of the fun we have with our office.

Move to declare LSC more boring, [illegible]. Everybody-nobody-foot +Spehn.

(JME) Albanian motion on KM. 7I rad 3-1I.253-4 for small [illegible] of 4 +Spehn.

(B*) Small Moocomm: Star Wars on TV came in 5th in Nielsen ratings.

(JME) Someone has been [illegible] unprocessed fanzines- please stop.

(A^2) Making of Star Wars movies on TV.

What are we coming to report- Michael Jackson's Thriller beat The Police based on video.

(B*) Badtastecomm: Michael Jackson's movie Firestarter.

(B*) "What's all this fuss about Michael Jackson anyway?"

(JME) Newsweek- Gary Hart couldn't get above 3rd.

"Rabbits have no tails at all..."

1st Miller motion. 0-0-0 +Spehn, fails.

2nd Miller motion. Feet and hands and legs and mouths-1 whirling leg and the Tech-2 +Spehn, passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}