\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 20, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

Move to accept the minutes as ignored. Passes many +snake-3 feet-few others +Spehn.

\goto{Committee Reports}

(JME) Snakecomm: There's a snake in the room.

(B*) Snakecomm revised: There's at least one snake in the room.

(KM) Moocomm: An abundance of niches- LSC has Excalibur and Evolution (short), at Harvard Square is The Road Warrior and Blade Runner.

(TLH) And on TV, Forbidden Planet and also Sgt. Pepper's Lonely Hearts Club Band with the Bee Gees. (Many boos and hisses- the snake tried). Octopussy tomorrow at LSC with Fishheads.

(ATS) Picniccomm: Hal Clement says the weather will be absolutely perfect on May 13, so we have set Picnic Day on May 13, and elections will be on Friday, May 11 at 1700 SST in the Spofford Room. Be there.

(B*) Coofcomm: James Madison U has formed an SF society. Their money person is also called the Lord High Embezzler.

(SG) Rosfap: The Great Fanzine Shift is proceeding.

(A^2) Panthercomm: We have a new Pinkdex! RAH!!! It's only one month out of date.

(B*) Goodnewcomm: Science Fantasy Bookstore has survived the purge (old building being blown away). Opening May 1st at 8 JFK Street over the Wursthaus (formerly Govinda's).

(TLH) We ought to go help him move- we have experience.

New office buildings going up there- Science Fantasy survived, though many did not and have vanished.

(TLH) Shuttlecomm: Shuttle comm went up and fixed a satellite.

(RH) Jim Roberts, an aero-astro type, mentioned that it's interesting how the first satellite made to be able to be fixed by the shuttle breaks down so conveniently, letting the shuttle show off. Planned obsolescence!

(B*) TVshuttlecomm: This last launch was the first time all 3 major networks didn't show the shuttle launch (or any manned space launch) live; basically a good thing, shows they are becoming blase and people are accepting this as an everyday type thing.

\goto{Old Business}

OBA, etc.

\goto{New Business}

Much flaming.

(B*) Minicult: My Favorite Martian is taking off in China.

(TLH) Move to commend good old American capitalism in all its splendor. Passes.

Much more flaming with some good jokes, including:

(TLH) How many mice does it take to screw in a lightbulb? 2- the hard part is getting them in there.

(JME) How many Wellesley girls does it take to screw in a lightbulb? First of all, they're Wellesley WOMEN, and second of all, that's not funny!

(KM) How many people does it take to change a banana?

Passes...

\vspace{12pt}

\noindent
Meeting adjourned, 17:17:17 SST.

\vspace{18pt}

\centerline{Your Onseck,}
\centerline{Andy Su}

\end{document}