\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 16, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(JME) Move to approve minutes as acoustic. Chickens 3-7-7 +Spehn.

(B*) Miller motion. Fails.

Minutes chicken for lack of a reasonable motion.

\goto{Committee Reports}

(JME) Pseudo-Moocomm: Android opens today- good reviews.

Much flaming on this and Ice Pirates.

(TLH) Moocomm: Splash is out- good reviews from many people.

(A^2) Moocomm: Deathstalker is out.

Again much flaming (on how bad it will be).

(JME) Pseudo-Moocomm: Monty Python and the Holy Grail tonight.

(GF) Pseudo-Greasecomm: Our Skinner is so greasy, he appears in 2 separate stories in the Tech. (TLH) Yeah, they even spelled my name right in one of them.

(Adam) Junkcomm: Emily and the other dead microfiche reader may leave, but the Office of Facilities Management sent us a 5 page form and said we'd only be charged a nominal fee to remove them.

(JME) ASAcomm: The Skinner was rejected as secretary of ASA by a short, greasy female.

(JME) Enthusiasmcomm: It's obvious that the Skinner loves meetings.

Phonecomm: Ring.

\goto{Old Business}

(B*) Gunkelcomm: He called up the dean's office complaining about our behavior. (TLH) "Bunch of punks."

OBA, usual everything.

\goto{New Business}

(MJG) Ken Meltsner is thinking of reviewing some of our books for the Tech, as we keep getting free review copies.

(JME) Books will be available for review- see me.

(GF) Minicult: Tomorrow is the deadline for Hugo nominations.

(TLH) Gavelcomm: A fantastic display of sheer circus-quality talent by our Skinner as he balances the gavel in his hand.

Miller motion. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 17:14:32 SST (Hike!).

\vspace{18pt}

\centerline{Lovingly submitted,}
\centerline{Andy Su, Onseck}

\end{document}