\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 5, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (9/28/84) read and corrected.

(JME) Move to approve the minutes as last minute. Seconded. Passes everybody-I don't see anybody-3 or 4 +Spehn.

\goto{Committee Reports}

(ATS) LHE Report: equity 4109.18. We made 1035.13 last month.

(JME) Pseudo-Boredcomm: The Darth Vader bulletin board appears to have been fairly effective. One person (said the Skinner) walked by it and stopped dead in his tracks and looked at it for about five minutes. Janice commends RvdH.

ATS says "I must leave." and walks out of the room. Janice moves to condemn him. Seconded. Passes by Skinnerial decree.

(RvdH) Boredcomm: I'm going to come up with a replacement Real Soon Now.

(JME) Lecturecomm: Gardner Dozois was. He was really good. Everybody who missed him (most of the people in the room) lost out. (George points out that last night at the lecture he didn't recognize anybody except in the front row, where he recognized everybody.)

Famecomm:  The TechTalk story which mentions the Skinner has been reprinted in the Watertown Press, the Cambridge Chronicle, and the Somerville Journal, with the latter printing the headline "MIT hosts sci-fi confab." See attached article.

(JME) Boscomm: We got our half-table at Boskone, but we almost didn't because the person processing our request thought someone was asking for a half-table and just using MITSFS as a mail drop. We were put on the waiting list, and someone else found this and said "You don't want to put MITSFS on the waiting list." The person still wouldn't believe we were MITSFS until shown a check.

(JME) Move to condemn NESFA for business as usual. Seconded. Passes just about everybody-really nobody-two and two dropped newspapers +Spehn.

(BPS) TZcomm: (Short argument over whether this should be Sitcomm, and Bill says "No. I won't make the report then.")

(JME) Sitcomm: There's a Twilight Zone festival on channel 38 tonight that starts at 8 PM and goes until 5 AM the next day. The first three episodes being shown have not been shown before. There's also one with computer-added color, and Nightmare at 20,000 Feet with William Shatner. Adina notes that yesterday's Glob remarked that Twilight Zone combined science fiction and drama.

(JME) Den Mother      : We have a new den mother      ; it's no longer Barbara Feinman, but the Student Center Committee. After promising us money for the door last year, they have now decided not to give us any, as we didn't ask them earlier.

(JME) Infocomm: Still keyholders who don't have pictures on the door.

(JME) Stupiditycomm: When Bryan Knight heard Janice mention that we lost a keyholder shelf reader, he noted that he wasn't assigned any shelves; this situation did not last long.

(BPS) Mooreviewcomm: Buckaroo Bonzai- the Glob hated it, the Phoenix liked it. In fact, almost everybody in the room liked it.

(JME) Statcomm: The Glob reported that 1 out of every 5 Americans has mental difficulties. The Skinner left it to the people in the room to compute how many keyholders that works out to. As Bill said, "Look at the four people next to you; if they look normal, then you're in trouble."

Someone who looks very confused starts to walk into the Library.

(JME) Move to welcome the new person. Seconded. Passes by Skinnerial decree.

\goto{Old Business}

(Ken) Cheryl Wheeler by Mr. and Mrs. Wheeler has been in Pinkdex for quite a while; now she is a paperback.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: Neither of the Massachusetts candidates for US Senate seem to be able to count. At a debate, they were asked to name the top three problems facing Massachusetts; Shamie named two, and Kerry named four.

(Adina) Move to make them watch the Spanish Inquisition sketch from Monty Python. Passes oh, I don't feel like counting-definitely fewer-not too many +Spehn.

BPS talks about All That Jazz (tonight at LSC) as being either a Minicult or a Moocomm; this seems to escape most people in the room.

JME points out that at the Gardner Dozois lecture, the question arose as to what people would do if they knew the world would end in 5 hours; Ken would eat at McDonald's. Ken said that Janice would eat hot fudge sundaes. She claimed that she didn't specify, but had just said that she was a sensualist.

(BPS) Minicult: A group of students at Brown University have requested that the medical department stock suicide pills in case of nuclear war. It was noted that people at MIT have no use for these, as we are ground zero.

JME asks what's wrong, there being so little new business. Adina is heard to say "There's nothing new in the world." Janice points out that that's new. Tom McKendree tells Adina to read A Rose for Ecclesiastes. Janice says, amid cries of confusion, "Understood and commended."

(JME) Move to direct Bill to go read A Rose for Ecclesiastes with a banana. Seconded. Passes anybody with any sense-some people who think they're really ready to die-even fewer people +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

(Please note that these minutes have more liquid paper and corrections than any others in known history. It should also be noted that they were prepared a full five days in advance, unlike the minutes of the previous week, which were prepared approximately 2 seconds before the Skinner walked into the MITSFS to start the meeting. -Psi, Adam)

\end{document}