\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 21, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Gavel falls. Onseck says something. JME says put that in the minutes.  Onseck declines. MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (9/14/84) read and corrected.

(Y) Motion to applaud the minutes as read. Dies for lack of a second.

(Chip) Motion to approve the minutes as cinnamon. Dies for lack of a second.

A new member says something. Chip says Finger motion.

JME explains that we aren't fingering new members, and BPS is heard to say "Is this your first time?" JME: "Don't worry, we'll be gentle." MTG gets out her whip.

(AA) Move to approve the minutes as snakeless. (SLP) Second. Passes a lot-about 5 or 6-0 +Spehn.

\goto{Committee Reports}

(JME) Bananacomm: A woman in Florida paid for a used car with 999 bananas, according to the Globe. Chip notes that the seller of the used car will not make this offer again. Y asks rhetorically if she got a lemon. JME proposes an Albanian motion; it is seconded and declared passed.

(BPS) Moocomm: Return of the Jedi today and tomorrow. He is corrected by Adina (Empire Strikes Back). AbM reports that LSC got a really bad 35mm Dolby print and that a brand new 16mm print will arrive at the airport at 6. Susan Tucker asks what room it will be in, Chip says move to yawn, and JME growls. Flaming follows about projectors, etc.

Carmencomm: still lost.

JME asks about Pianocomm; AbM squirms and then explains how It Wasn't His Fault, and they'll be ready tomorrow. JME moves to commend RvdH for being right (about how notes will be out RSN). Seconded. Passes 3pi-pi/2-Spanish pi +Spehn.

(JME) Skinner Report: Two people's photos are missing from the keyholders' Rogues' Gallery. (BPS) Let this be a lesson to you all. (JME) You too can become an unperson. J. Spencer Love and HTF.

Ken reports on his list... Chip is (unluckily) heard to say "If he doesn't want to tell us about his Liszt, he can tell us about his Chopin." Most people say: Albanian motion. Passes by Skinnerial decree.

Ken entered into a PC a list of all the American pro SF magazines and which ones MITSFS has; we have 97.06 percent.

(JME) Ocomm: There was an activities open house, and they had an artist there doing caricatures of all the student activities presidents. (She displays it and BPS asks "Who's that supposed to be?")

(MTG) Whipcomm: I fixed it. (BPS) Was it broken? (JME) Finger motion.

The Onseck asks BPS what his Minicult was, and JME screams "We haven't gotten to that yet. It's new business!" Someone said something about a Finger motion, but the Onseck just can't seem to remember what that was about. (JME) As someone once said about the Supreme Court, the Onseck is not final because he is right, he is right because he's final.

\goto{Old Business}

(JME) Note from Hy Tran; I suppose that's old business. BPS inquires about what he's doing, and JME points out that the note says "Hello. Hy Tran." JME moves to commend Hy Tran for brevity. Seconded. Passes unanimously-nothing-0 +Spehn.

OBA: um, us, uv, JME yells "No debate!" AbM says "But I miss the debate." (JME) Motion to console Adam. Seconded. KM adds "with a banana" and is drowned out with boos. JME says "Rejected."

\goto{New Business}

Someone claims that we have a motion on the floor, and JME says that she stepped on it. Y says something and Janice comments that she heard something in Albanian.

(BPS) Minicult: Someone has created an art version of the Tesla coil. See attached article. The creator sent one to Arthur C. Clarke, and Clarke wants to use one in 2010.

(BPS) Minicult: A terminally ill man who will die before the end of the year is offering to take messages from the living to the dead for 20 dollars each. JME wonders what he's going to do with the money and KRJ answers "Take it with him." MTG wants to know what happens if he recovers and KRJ points out that he can always unrecover. (BPS) In the Wednesday Globe it was reported that he has been deluged with calls from people responding to his offer and considers himself to be in over his head. This is perhaps ironic given that he is dying of a brain tumor.

(RKW) Addendum to first Minicult- the person who did that was from the Center for Advanced Visual Studies.

(JME) Den Mother      : Barbara Feinman, the new head of Campus Activities, responded to complaints about the leak by saying "Oh yeah, I heard about that my second day here. Put down plastic, all right?" We all know what she can do with her plastic.

(AA) Move to award Barbara Feinman a banana. (JME) No, too good for her.

Y motions for attention and Janice says "There's an Albanian waving his hand." People laugh. BPS: "That's a variation of the Albanian motion." People boo. Albanian motion. Passes.

People begin singing Rabbits... JME points out that the people forgot to say "just a powder puff" and that it must be done again. People flame about Albanian.

(KM) Move to commend Robert van der Heide for having a banana colored shirt. Seconded. Passes 17 1/2-a fist, some feet, and a few fingers-an elbow or two, a hockey stick, and a few others +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}