\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 18, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, last meeting of the semester;
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(Shawn) Move to approve the minutes as not worthy of comment. Passes 13-12-4 +Spehn.

\goto{Committee Reports}

(Susan) Picniccomm: We were 17 cents under budget. (Applause.)

(JME) Motion to commend Picniccomm for a first. (AA) Second. (AbM) Third. Passes by decree.

(AA) Moocomm: Sneak preview of Gremlins tomorrow night.

(KM) Moocomm: Never Say Never Again, Kresge, 7 and 10.

(JME) Pseudo-Picniccomm: The picnic was a great success, and if you missed it you lose. (AA) Despite the fact that SOMEBODY forgot to bring a knife. (JME) And somebody else forgot to bring a coconut.

(JME) Skinner Report: Please note that new membership rates are up on the door for the summer. Also, we have a special Hugo nominees section, compiled by Ken Johnson. (B*) Where are the reels of film for the best dramatic presentation? (JME) We're working on it.

More flaming by B*.

(JME) Albanian motion on Bill Starr. Passes everybody, including Bill-nobody-2 +Spehn.

(AbM) Pianocomm: the keyholder notes are waiting for comments; they'll be waiting for about another week and a half.

(MTG) Vicecomm: I want to know who took my whip. I get a whip with this job, and I want it.

(KM) Move to allow the Vice to use the whip on whoever moved it. Passes (no vote taken). (B*) Now everybody's going to be moving it.

(AbM) Pseudo-Moocomm: Fritz Lang's Metropolis has been set to music, like Adam Ant and Pat Benatar.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

(KM) Minicult: We have a new organization, the Campus Crusade for Klingons- the anti-anti-pornography backlash. "After all, they only beat on human beings in those films." (AA) But there aren't any Klingons in Wrath of Khan. (JME) They're behind everything. (Susan calls Spock "Spark" and many jokes ensue.)

Critical discussion of The Search for Spark.

(KM) By the way, my thesis is done. (Applause.)

Random flaming and argumentation.

(JME) Motion to commend Susan for being totally confused about when and where she is. Passes (no vote taken).

People begin singing "Rabbits have no tails at all," and Janice says "I'm not as much of a wimp as Tim; you've got to go through five choruses." People continue to sing Rabbits. People stop singing Rabbits.

(AA) Motion to award Ken a banana for his remarkable exploit in completing his thesis. Passes n, where n is greater than five and less than fifteen-x, where x is much, much less than n-some random number less than either of the above +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST; have a good summer.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}