\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 26, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

The Onseck read the minutes of the (boring) previous meeting. (Note: during the reading of the minutes, Janice pointed out that freshmen who are ruled out of order don't have names; let this be a lesson to you all!)

(John Dumas) Move to approve the minutes as being better than being there. Seconded. Passes "Oh Lord, too many to count"-"not enough to bother counting"-0 +Spehn.

Here a discussion follows about chickens, particularly those prone to appearing in 10-250 during random lectures; the Onseck makes a fowl comment, and Janice explains that Albanian motions are ineffective against him. Laura Daly blows on his antennae and Janice asks that they retire to a private room if they want to continue; Laura wants to sell tickets to the event.

\goto{Committee Reports}

(JME) Pseudo-Boredcomm: The board has been changed. Says Bill: "Good, it was starting to smell."

(AA) Sitcomm: V: The Series actually begins tonight. (JME) And the Glob liked it.

(JME) Libcomm: Our Librarian, Ken Johnson, has been the victim of an unfortunate accident and won't be around for a while. The Onseck has been instructed to obtain an appropriate card so the MITSFS may sign it and send it to him. Notice also that his picture is missing from the keyholder's picture board; Ken suspects that someone stole it and put pins into it. AbM noted that Kathy Godfry thinks that someone may have taken it because they wanted a picture of the cover of Weird Tales 1.

(SLP) Moocomm: Apocalypse Now tonight.

(TMc) In the October issue of Omni, President Reagan says that he made the decision not to pursue an anti-satellite treaty with the Soviet Union upon an article in Omni of several months past.

(AbM) Move to commend Omni for ruling the nation. Amended by Janice to read "commend Omni for attempting to rule the nation but failing miserably because MITSFS rules the nation." Seconded, but never voted upon because "nobody liked it." When asked if MITSFS ruled Omni, Janice replied, "Who'd want to rule Omni?" Said Adina, "Even Ben Bova had the sense to leave."

(AbM) Infocomm: We got a picture of Tom Lang, but it hasn't been posted yet.

(JME) Pumpkincomm: Since Halloween is Wednesday, it's time for the Society's reaffirmation of its belief in the Great Pumpkin. And also Bill Starr's, Cheryl Wheeler's, and Dwight K. Brown's birthdays. Bill indicates that at one point 10 percent of the keyholders had their birthdays on Halloween.

(JME) Lecturecomm: Next Thursday, Thomas Disch in the "1984 and Counting..." reading series.

(BPS) Theftcomm: We now have a copy of Knight Rider: The Novel. (Cheers heard in the background, for some reason...)

\goto{Old Business}

(BPS) We received a change of address card from somebody called "Alpert, The." He moved from Terrytown, NY to Penllyn, PA.

(JME) Tim Huckelbery, ex-Skinner, has turned in his key. It was noted that he had pressing commitments, and questions arose as to just how pressing she is.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Nabisco, the company that brought you Fig Newtons (TM of the Nabisco Corp.), the first practical use for figs, has now brought out the totally unnecessary Apple Newtons; several members note that the Blueberry Newtons are actually rather nice.

(SLP) Move to ban Apple Newtons. Seconded. Passes 25-negative 73-several squawks, some arms and legs, and rad 3 +Spehn.

Herb makes a comment about Wayne Newtons and is promptly unanimously Albanianed and Finger motioned. Ken makes a comment about how Wayne Newton already has a band, but he is, luckily for him, ignored.

(BPS) The Glob recently ran an article on how the star witness in a fraud scam trial claimed to have once occupied the body of actress Jean Harlow, even though she had died five years before he was born. See attached article.

(RKW) A new color sheet! Includes The Gunslinger. Many oohs and aahs.

(JME) Boskone XXII fliers are out. Sample attached.

(KM) Move to commend the newest keyholder Susan Tucker for having a banana-colored shirt. Seconded. Fails some nahs and about 6-almost everybody-2 and a squawk +Spehn.

Some random freshman makes three Minicults, all concerning the current game of Assassin.

(KM) Move to charge them 10 dollars for advertising time. Seconded. Passes by Skinnerial decree.

(TMc) Minicult: In the Arabian Nights edited by Joseph Campbell, story 666: "All in the city who refused Islam were slain."

(JME) Terror in the Isles is a really bogus movie made up of all the "good parts" of various horror movies. The commercial for it said "Now you don't have to sit through all of the boring parts of the movie waiting for the good parts."

(AbM) We have at least two people here tonight who have never been to a meeting before: Sue Hagadorn (a prospective keyholder) and Lisa (also a prospective keyholder).

Merryl points to a nameless freshman and says "She tied my whip to the chair." Laura Daly points out that the proper response is to tie her to the chair with the whip. Janice instructs that it should be noted in the minutes that Susan Tucker has just wisely removed herself from the vicinity of Merryl and Jenny.

(MTG) McKenzie motion! Janice: "Out of order until you learn the names of the keyholders."

Herb waves his hands and it is explained to him that even if one's name is Miller, only the original Miller can make a Miller motion by moving. Let it be noted: Bruce Miller is still skiing in Colorado.

People sing two verses of Rabbits; they stop when Laura howls.

(AA) Miller motion (the second one!). Seconded as the Society wimps out. Passes lots of people-fewer people who don't want to wimp out-3 or 4 and an old squawk +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}