\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 4, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, NOT 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(JME) Move to approve minutes as more fun than the actual meeting was. Passes.

\goto{Committee Reports}

(JME) Pseudo-Moocomm: There was an announcement in Locus that there will be 2, count 'em, 2, movies being made out of Battlefield Earth.

(KM) Note: Moocomm was originally for LSC movies only but now is for SF movies in general.

(TLH) Another Pseudo-Moocomm: There are plans afoot to make a live-action version of... (pregnant pause...) The Jetsons!

(Everyone) ARRGH!

(GF) Pseudo-Moocomm: Tonight Mad Max is on Channel 56 (8 PM).

(MJG) LHE Report: We had an equity level of around 1240 dollars (that's bad) and we lost 106 dollars last month.

(JME) Where did it all go?

(TLH) Moocomm: Blue Thunder on Saturday at LSC.

(Everyone) SUX!

(TLH) Picniccomm: Andy said to say he's trying to get the announcements addressing starting about 11:00 tomorrow. Everyone is urged to show up, and Picniccomm is told to show up.

(JME) Note that, with the weather predictions for this weekend, it was right to ask Hal about the date (and thereby change it to next week).

\goto{Old Business}

OBA, usual everything.

\goto{New Business}

(TLH) Minicult: Tomorrow night on SNL, the group Spinal Tap will be playing. It's going to be really good. Also, there is going to be a Spinal Tap album out- The Black Album.

(GF) Minicult: I was proofreading this article about Sheldon Glashow and it told about how, in 1949, Glashow, Steven Weinberg, and Joel Feinberg were all in an SF club for the Bronx High School of Science to discuss an SF magazine called Amazing Wonder Stories.

(TLH) Minicult: Stephen King has bought a radio station in Bangor, ME, renamed it WZON for The Dead Zone, and he's playing all his favorite music on it (rock and roll).

(JME) Hugo nominations are out and will be posted soon. The Best Novel ones are fairly predictable- Robots of Dawn, Millennium, Moretta: Dragonlady of Perm, Startide Rising, and Tea with the Black Dragon.

(B*) Minicult: Take note of the Space Shot(TM) ad on the door- "Send a message to outer space..." Yes, this is the same as the Wall Street Journal article on the door.

(JME) Someone was here with a video camera taking pictures of the Library. He was doing a project for some class and he was up from Virginia. He was awed by the Library, especially the magazines.

(JME) Move to commend the Lunacon art show committee for giving an award to a work called Breast of the Bunch for "Most creative use of a banana." Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 17:34:34 SST.

\vspace{18pt}

\centerline{Your Onseck in absentia,}
\centerline{Andy Su}

\end{document}