\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 11, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Room 1-236 (the Spofford Room);
Tim L. Huckelbery, President and Skinner, presiding.

(B*) Miller motion. Fails.

(TMc) Motion to accept the minutes as unprepared. Seconded but fails.

(B*) Motion to approve the minutes as brown and scaly. Seconded. Passes something-7-10 +Spehn. Skinner is heard to exclaim, "Some people are only voting once!"

\goto{Committee Reports}

(JME) Techniquecomm: Commends Technique for finding two creative misspellings of Robert van der Heide's name. At this point, there is flaming about whether or not this falls under New Business. Report retracted.

(Shawn) I'm finished! (Applause.) (Ken) I'm not.

(Susan) Barbicomm: Ken Johnson is the writer and producer of V.

(TMc) Barbicomm II: Postponed until Minicults.

Picniccomm: Susan discovered yesterday that the picnic was Sunday and not Saturday.

(KM) Moocomm: Friday- The Meaning of Life. Sunday- Young Frankenstein.

(TLH) Skinner Report: This is the last meeting that I will run.

(B*) Picniccomm finger- what time are people supposed to show up tomorrow at the Library? (JME) 10:30. (Various people mention that the picnic isn't until Sunday, and the Skinner says "Well, you want to make sure to get there early.")

\goto{Old Business}

(JME) Very old business: somewhere in a pile of pictures at The Tech, Janice found a picture of George Phillies, the library's Permanently Deceased Librarian and President.

OBA, usual motion, usual second, usual discussion, usual result, etc.

\goto{New Business}

(TMc) Minicult: WSJ of two days past- Ken Johnson is a police target. One of the eight ex-convicts the Minneapolis Police Department said is most likely to commit serious crimes now that he is out of prison.

(George) Minicult: A struggling California science fiction author, unhappy that their science fiction novel was turned down by twenty publishers (even as a donation for a charity telethon by a TV station), tried to burn copies of his book and almost burned down the house. Also, there was a contest for the worst opening line of a novel. It was "The lovely woman-child Kaa was ruthlessly chained to the cruel post of the warrior-chief beast, with his barbarian tribe stacking wood at her nubile feet, when the strong clear voice of the poetic and heroic Handsomas roared, "Flick your bic, crisp that chick, and you'll feel my steel through your last meal."

(Shawn) Minicult: A letter from Ursula LeGuin in Science News (April 20, 1984) explains how she would have designed Rolls-Royces and research scientists.

(B*) Crapcomm: Next fall there will be a regular TV series of V.

(AA) Minicult: Stephen King's Firestarter opened today. (Flaming about why this is a Moocomm.)

ELECTIONS:

ONSECK

Nominations: Klyd, Tim Huckelbery, R. vanser Hude, Adam Mellis, Spofford.

Final vote:

Klyd- 2.53

Tim- 0.41

(Studs)- 0.09

Adam- 16.44

Tron- 0.05

Random- 3.29

LHE

Nominations: Ken Dumas, Klyd, Janice's R. antennae, naughty bits of Mr. Edwin Meese, Mr. Ed, Andy Who, Dr. Su.

Final vote:

Various naughty bits- 0.09

Klyd- 2.62

Random- 4.27

Ken Dumas- 4.50

Andy- 8.40

Janica: "I took 18.01 and 18.02 and that's a majority."

VICE

Nominations: Spofford, Klyd, Merryl, Susan That's-enough, second, Mick Jagger, McMuffin, Opus, closed, I can't read this, we seem...

Final vote:

Opus- 0.01

Klyd- 3.17

Random- 3.79

Merryl- 11.02

SKINNER

Nominations: Simson L. Garfinkel (messiah), Dune (Messiah), Robots of Dune, Heretics of Dawn, Janice (goddess), excited nude Skinners of Gor, Tim's handwriting.

Final vote:

(ATS) "This is incredibly arbitrary; Janice won."

Janice appoints herself Skinner amid cries of "We want Klyd."

As the Skinner let the gavel fall upon the block, the refrains of "Rabbits have no tails at all" could be heard drifting from the Spofford Room.

\vspace{12pt}

\noindent
Meeting adjourned.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Adam Mellis, Onseck}

Addendum to the minutes by the Lord High Embezzler:

Final vote for Skinner:

Klyd- 2.05

Random- 6.003

Janice- 10.22

Enclosures: photograph (George Phillies), ballots (3), newspaper articles (3).

Addition, 18 May:

(JME) Klyd is official second.

\end{document}