\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 7, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
Bill Starr and Janice exchange insults. As a special suspension of the rules, Janice declares that people who are here for the first time may not receive Finger motions; she also explains the general mechanics of a meeting.

MITSFS meeting called to order, 1700 SST, first meeting of the new term (cheers in the background),
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (5/18/84) read and corrected.

(B*) Move to approve the minutes as unreasonably accurate. Dies for lack of a second.

(KM) Move to approve the minutes as green and horned. Dies due to a crushing popular rejection.

(JME) Move to approve the minutes as brown and scaly. (AA) Second. Passes 14-9-6 +Spehn.

\goto{Committee Reports}

(KM) Moocomm: Romancing Your Clone. (JME) And the Exorcist.

(JME) Move to commend Tim Huckelbery for no longer being here. Passes by decree.

(AA) Moocomm sub 2: Return of the Jedi won the Hugo for best dramatic presentation.

(B*) We're getting dangerously close to real business.

(JME) Do we have a vice report?

(MTG) Vice Report: I still don't have my whip, and I'm ready to use it on whoever took it!

AbM points out that the whip is in a desk drawer and the Vice retrieves it. The Vice fails to find her Smurf(TM) disintegrator ring and is told that it's currently locked away. JME notes with pleasure that there are no Smurfs(TM) in the room.

(ATS) LHE Report: We made 770.88 last month, but because the books were done a little late, that includes some of this month's transactions. (Many heavy sighs in the background.) (ATS) It's not my fault. Nothing's ever my fault. Equity level 3062.24. (Cheers for the equity level.)

(SLP) Fweekcomm: Over 100 new members.

(JME) Move to commend the new members for being new members. Seconded. Passes just about everybody-almost nobody-no one worth speaking of +Spehn.

Pointless flaming by many people. Janice threatens with an Albanian motion. Conversation changes to a different subject.

(JME) Official Second (Klyd) has received an honorary membership and even signed his membership sheet all by himself. It is noted that it is good until Susan graduates or Klyd dies.

(JME) We have a new Untitledcomm, Robert van der Heide, to write funny letters from the MITSFS to funny people.

\goto{Old Business}

Finger motion on AbM for not knowing when to present a Minicult. Passes by Skinnerial decree.

(AA) Greetings from E. Carl Hylin. (Mutterings of "That's OLD business.")

OBA: um, us, uv, ur. (AbM) But what about the usual debate? (Much flaming.)

\goto{New Business}

(KM) Minicult: Janice and I are engaged.

Several people ask the traditional rhetorical question: "In what???" Ken replies, "If you need to ask, you probably wouldn't understand anyway!"

(RvdH) Minicult: Boston Phoenix review of the Philadelphia Experiment says movie is based on a real incident that the Navy covered up.

(JME) Note on offensensitivity: A woman came to the MITSFS Activities Midway table last night and turned over John Varley's Demon because she was offended by the cover.

It was noted that she was a math graduate student and that this apparently had nothing to do with her actions. More flaming. John Dumas says "Yeah, but she's tons of fun," referring to the 50-foot-tall Marilyn Monroe lookalike on the cover. JME says "Enough! Enough! It's getting serious."

(AbM) Minicult: Rolling Stone claims that the most promiscuous college in the US is BU and the hardest is MIT.

(KM) There's also a guide to colleges that says the best dormitory to live in at MIT is Senior House. It also says that Senior House is the worst. Best party: Steer Roast. The reason for this is that V. Michael Bove filled out the entry.

(JME) Motion to commend RvdH on finishing his thesis. Passed some not terribly enthusiastic arms and legs-fewer not terribly enthusiastic arms and legs-several squawks and a few wings and thighs +Spehn.

(BPS) Minicult: In the national parliamentary elections in Canada, the Rhinoceros Party, on a theme of sex, drugs, and rock-n-roll, came in 4th of 12 competing parties. They got 101,000 votes, but not enough for a parliamentary seat. See attached.

(JME) We now have a priest as a member. Now we have a priest to give last rites and a campus policeman to take away the body.

(AA) Minicult: Greece has lifted its import ban on bananas.

(JME) Motion to commend Greece for their action in favor of a fruit that shall remain unnamed. Seconded. (RvdH) Friendly amendment- to commend Greece for their newfound belief in free trade. Seconded. Passes everybody who's anybody-a few randoms-"rad 3" +Spehn.

People start singing rabbits have no tails at all; four verses, including to Beethoven's Ninth.

(BPS) Miller motion. Fails.

(MTG) Miller motion. People start singing Rabbits during the vote. 8-4-??? +Spehn (as final vote is taken, people finish singing Rabbits. Janice cries "Meeting adjourned two ways!!!").

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}