\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 14, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (9/7/84) read and corrected.

(RvdH) Motion to approve the minutes as "Read." (AA) Second. Motion declared invalid by Skinnerial decree.

(MTG) Motion to approve the minutes as hot off the presses. Passes lots and lots of happy boys and girls-a few unhappy boys and girls-some very confused boys and girls +Spehn.

\goto{Committee Reports}

(MTG) Fweekcomm: We have on the order of 144 new members this freshman week. Unclear how many are new members and how many are renewals.

(KM) Moocomm: Star Wars tonight. (Unenthusiastic applause.) Also, Wizard of Speed and Time (much enthusiastic applause and BPS is heard to say "...with Star Wars as the trailer..."). Someone asks "Is it in Kresge or 26-100?" and Janice makes a Finger motion. RvdH claims it's a sensible question, but JME points out that this is a meeting. Says she: "Go next door and ask."

(AbM) Pianocomm: New version of the keyholder notes will arrive tomorrow. RvdH says "real soon now" and AbM insists tomorrow.

(AbM) Infocomm: The Know-Your-Keyholder Rogues' Gallery is on display behind the keyholder's desk for people's perusal. JME notes that some people are portrayed as stick figures and BPS notes that some people are portrayed as Szerbesko C. Emmer.

(JME) Motion to commend Szerbesko Emmer. (AbM) Second. Motion dies when Skinner says "Whatever, let's ignore it."

(MTG) Warning to all of you pictured as stick figures- people are free to hack up figures in an attempt to encourage you to bring in pictures of yourselves.

(GF) Move instead to have people's figures changed to stick figures. (JME) Second. (RvdH) Friendly amendment: using a chainsaw. Accepted. Passes 25-9-something less than what it passed by +Spehn.

JME admonishes those who are only voting once.

JME says "Any more committee motions?" BPS says "...reports." JME: "Whatever. The Skinner defines it. If I call it a committee motion it is a committee motion. Any more committee motions?" KM: "Seconds." Passes.

As JME is about to say that we move on to old business...

(KM) Moocomm: We received a press kit for Night of the Comet. (Description follows.)

JME calls for more committee reports and is about to move into old business when...

(RvdH) Revenge of the Jedi next week.

Robert is abused for various reasons, and JME lets the gavel fall and declares...

\goto{Old Business}

(JME) We got a letter from Marc Alpert, former Skinner, who congratulates us on our new Library and wants a picture of it. He also sent us some donations and wants a letter for tax purposes. It was not decided which letter to give him. BPS at one point interrupts to say "He's cool!"

OBA: um, us, uv, ur. RvdH says "Usual debate" and is ruled out of order.

\goto{New Business}

(John Dumas) Minicult: This personal appeared in the Phoenix. (He holds it for all to see. JME observes of its size: "That's a real mini-cult." After some slight deliberation, Attocult is settled upon. Someone who shall remain anonymous for their personal safety says "Att-a-boy.") John reads the ad: "GORIAN WARRIOR. DWM 6'4" 220 lbs Ivy grad seeks tall 5'8" to 6' Earth woman superb of figure and intelligence for a sane sophisticated highly imaginative and creatively sensual exploration of Gorian contra culture. Box 8801." JME authorizes RvdH to write the person a letter. BPS wonders what counter-culture on Gor is, and is corrected to contra-. Various remarks about Nicaragua. KM suggests that a picture be enclosed. Janice declines.

(SLP) Carmen has been missing for a week. Boring discussion follows.

JME wonders where all the new business has gone.

JME invites people to think of nasty and interesting things to do to J. Spencer Love.

(Some poor random) Motion to censure the Skinner. The Inverse Skinner Rule is explained to him.

(AbM) Motion to commend unnamed woman on her banana colored shoulders. Passes just about everybody I can see-I don't see anybody (many boos)-nobody +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}