\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 10, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(George) Motion to have the minutes displaced. Passes by Imperial (Skinnerial) decree.

\goto{Committee Reports}

(B*) No telepathy in the library!

Exoduscomm: We're here.

(TLH) Grand opening, Thursday at 5:00.

(George) Finger motion. Fails for lack of a second.

LHE Report: Someone threw away the assets sheet- it disappeared after a meeting with the UA accountant. (TLH) Tune in next week for the LHE Report- and the LHE. (JME, sounding concerned) This sounds like real business.

(TLH) Moocomm: Ken Dullea will be in 2010. Mel Gibson will be in Mad Max III. There will be an X-Men movie, currently budgeted at 22 million. It will not follow straight from the comics, but will begin at around issue 139.

JME commends LSC for the Movie Marathon. (Cries of "Ro-man" heard in the background.)

Chip Hitchcock mentions that Dark Star contained the lyrics "kill the beach ball" sung to Die Valkyrie by Richard Wagner.

(Merryl) War Games, Saturday night.

\goto{Old Business}

OBA, usual... etc.

\goto{New Business}

(A^2) Minicult: Adult film canceled at MIT- quotes from the Skinner appeared in the Boston Globe about the film (see attached clipping).

(A^2) Minicult: To celebrate the 200th anniversary of hot air balloons, there will be a Star Trek belt buckle. See attached clipping from the TV Guide.

(Y) Move to commend the above. Fails, no second.

(TLH) Minicult: MITSFS phone number- we have received calls for LSC, the Folk Dance Club, ATO, Charlie-the-Tech-Tailor, Chinese Student Club.

(AbM) We also got a call from a girl in East Campus who dialed 29 on her dormline telephone.

New keyholders: Susan That's-enough ("Gee, that sounds Greek"), Tom McKendree ("That doesn't sound Greek"), $A\theta\alpha\mu Me\delta\lambda\lambda\epsilon\sigma\alpha\theta\rho\omicron\sigma$ ("Adam Mellis").

(JME) Move to note that this is not a NESFA meeting.

Phonecomm: ring.

Move to commend Susan That's-enough for wearing a banana-colored shirt. Passes (n+1)-n-(n-1) +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, time? Time to leave!

\vspace{18pt}

\centerline{Duly recorded and noted by,}
\centerline{Adam Mellis, for Andy Su, Onseck}

\end{document}