\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 7, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting REcalled to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

(JME) Even though the meeting hasn't officially begun yet, we've already passed a motion that Adam officially sucks and an Albanian motion on Herb.

(BPS) You'll never know what the Albanian motion was for, Adam!

Minutes of the previous meeting (11/30/84) not available. (Pre-previous meeting was 11/16.)

\goto{Committee Reports}

(ATS) LHE Report: equity level 4720.07 as of 11/84, and a profit of 847.22 mainly from a 600-dollar check from the MIT library fund. (Bravos.)

(JME) Skinner Report: We're trying to put together a MITSFS team for the College Bowl as was done last year very successfully. We need 4 people, and anybody interested should talk to me soon since the deadline is next Friday. Preferably students.

BPS says "That's not Adam either" as a random person walks in.

(Somebody) Flattercomm: On the other side of Judy Brown's (I Like Them Big and Stupid, The Homecoming Queen's Got a Gun) only album is a song called "I Married an Alien."

(AA) Panthercomm: We now have Douglas Adams' new book, So Long and Thanks for All the Fish- as all the advertising says, the fourth book in the Hitchhiker's trilogy.

(JME) Motion to commend the advertisers for accuracy. (KM) With a banana! Naahed to death.

(ATS) Godotcomm: I'm still waiting for my Macintosh, but my copy of Hitchhiker's: The Game has arrived.

(JME) It contains such accessories as a microscopic battle fleet, a piece of fluff, no tea, peril-sensitive sunglasses, a promotional brochure, and destruction orders for a home and a planet.

Discussion of possible Mac attack via Vogon poetry. Repeat of BPS's "That's not Adam either" with another random.

(JME) IAPcomm: We have 3 listings in the IAP guide, including an announcement of the Hitchhiker's marathon on Sunday 1/20.

Comments and discussion on activities.

(BPS) Moocomm: 16 years later, it's 9 years later, and 2010 opens tonight. (Yawns.) Mixed reviews. At Sack Charles and 2 of the Somerville 12.

(KM) Which would amount to about 1/4 of a real screen.

(JME) Moocomm: Being There tonight, and Bringing Up Baby with Cary Grant as a paleontologist, and I can't think of much that's more science fictional.

(Discussion of Spenser Tracy as MIT computer expert.

(BPS) Sitcomm: V is getting a lead nasty named Charles, as you will have Charles and Diana. (Clapping.) He'll be played by Duncan Regger, the actor who plays Dirk Blackpool on Wizards and Warriors.

(JME) Sitcomm: Twilight Zone returning to TV. They've hired Harlan Ellison to make sure their scripts haven't been done millions of times before.

(KM) Also, "Amazing" will be the name of a show.

Repeat of BPS's "That's not Adam either" with yet another random. Long interruption for discussion of the broken clutch-pedal support the person is holding.

\goto{Old Business}

(SSDT) Glob's TV guide reported The Ewok Adventure as "first TV premiere by George ("Return of the Jedi") Lewis." The Ewok Adventure will also be released as a Christmas movie.

(MTG) Move to commend the Glob for saving George Lucas's good name. Passes by Skinnerial decree and acclamation.

Something with a thick Albanian accent (nobody noticed the accent) about Rudolph the Red-Nosed Reindeer turning 20 and drinking in Massachusetts.

(MTG) The famous author Maurice le Blanc must have discovered a time machine; when he couldn't sell his novel The Secret of Sarek, he sent it back to 1920 and sold it then. It's not about Vulcans. We have a circulating hardcover.

(JME) If the publishing company had any sense they could reissue that now.

Repeat of BPS's "That's not Adam either" once again.

OBA: um, us, uv, ur, watud? Repeat of BPS's "That's not Adam either."

\goto{New Business}

(JME) It snowed. Also, Dean McBay managed to annoy not only LSC and the pro-porn forces, but Elizabeth Smela and the anti-porn forces.

(BPS) Isn't Pro Femina something you get from whole wheat?

Much discussion of other cases of administrative oppression. Another "That's not Adam either," and a Miller motion is no-not-yelled.

(RKW) I picked up the 120-dollar first edition of The Talisman, but I don't have slipcases for them yet.

(KM) Glob story on ADP sex scandal managed to mention the Thursday sex scandal of 7 years ago, which we never seem to be able to get away from.

(JME) New books in: Merchants' War (sequel to Space Merchant), Mars in My Pocket Like Grains of Sand (Delaney) (another "That's not Adam either"), a Soulrider, a V book, Champions of the Che, the 8th novel of the Diadem trilogy...

Reminder to write in new hours when when you cross yours out.

A motion to commend a wiffle bat for being banana-colored is ignored.

Another "That's not Adam either," the subject of which says "I've walked in 3 times and haven't turned into Adam yet." BPS: "Well, keep working on it."

A Miller motion fails 9-too many-4 or 5 and a bunch of squawks +Spehn. Another Miller motion is drowned out by 5 verses of Rabbits.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Susan S.D. Tucker, Pseudo-Onseck}

\end{document}