\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 16, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Janice Eisen, President and Skinner, presiding.

Minutes of the previous meeting (11/9/84) read and corrected.

Due to the absence of the Onseck, Janice read the minutes; also note that the Onseck walked in while the minutes were being read.

(Y) Move to approve the minutes as being better than it actually happened. Says Janice: "That's been done before."

(KRJ) Move to approve the minutes as partially read. Susan Pitts asks what the motion was and is promptly Finger motioned. Seconded. Passes due to Skinnerial lassitude.

\goto{Committee Reports}

(GF) People's Albanian Embassy: Here's a poster celebrating the 40th anniversary of the liberation of Albania (attached). Also, George proofread an article on Albania which is almost SF- it projects the scenario that after Enver Hoxha dies, the USSR moves in with paratroops, the West collapses, etc.

Pseudo-PAE: The magazine New Albania is organizing a competition on the occasion of the 40th anniversary; it is called "What do you know about Albania?" Flaming about Albania follows.

(RvdH) Moocomm: The Terminator is a wonderful B movie...

Robert states that he was not the caller last week who made a Miller motion.

(GF) Moocomm: Brother From Another Planet is pretty good; Shawn thinks that it is "exceedingly good" and that everyone should see it.

(JME) Barbicomm: Ken Johnson is back. (Applause.)

(BPS) Sitcomm: I watched about the first seven minutes of "Double Lunar Dogs" and couldn't take any more. It is an "artsy" video "inspired" by Heinlein's universe; the next day, the Glob said it was based on Ray Bradbury's universe.

(JME) Moocomm: Splash tomorrow night; The Seven Percent Solution on Sunday.

(JME) Skinner Report: There's a symposium on the future at Nichols College in Dudley, MA; on December 5, Fred Pohl will speak. Pamphlet attached.

(SSDT) Committee to Overdamp the New Wave: I was telling my mom about the Society, including the gavels and the special powers granted to the Star Chamber, when after a long pause she said, "You aren't mixed up in some kind of cult, are you?"

(Y) Move to commend her mom for having great perception. Seconded. Passes several-many fewer-not as many as the fors +Spehn.

(Y) Moocomm: Tonight at 7:30 the Carpenter Center (at Hahvahd) will be showing Bulgarian animation.

(JME) Meetingcomm: Wow! Meetings are getting popular.

(GF) Yes, we're running out of hooks for coats.

(KM) Yeah- we need more hookers.

(BPS) Climatecomm: First snow of the season last Tuesday.

(JME) Pseudo-VGG: 1) Remember when signing in overdue books to initial the sheet. 2) Fines for keyholders are going up next term.

\goto{Old Business}

(TM) While talking to my father, I mentioned the story from the last meeting about the people who were killed playing D&D, and he mentioned that there was a similar D&D slaying outside of Denver.

OBA: um, us, uv, ur.

\goto{New Business}

(JME) Minicult: from the Glob last Friday- a convicted forger who was in prison in Concord, NH forged his release papers and escaped.

Move to commend the individual for doing that. Passes unanimously.

(RvdH) Minicult: Last week's NYT Magazine had a long article about Albania.

(BPS) Moocomm: The movie Night of the Comet is being released! Many people groan.

(KM) At a Smith and Wesson plant, seagulls are taking the golf balls off the company golf course and dropping them on cars and people, because the gulls think that the golf balls are clams.

(JME) Minicult: Rabbits of Dawn is being advertised on radio.

(Y) Minicult: A long time ago there was a similar problem at a beach with seagulls dropping clams on cars; the mayor told the police to do something, and they posted a sign saying "No Dropping Clams on Cars."

(JME) Everyone say hello to Dan Breslov.

(GF) Minicult: Douglas Adams had writing block while writing So Long and Thanks for All the Fish; he solved it by staying at this small inn in England, and he liked it so much he bought the inn.

(AbM) We received last week another JRR Tolkien book: The Book of Lost Tales, Part II, and I was a bit surprised to learn that this was only the second of four books that would be coming out soon by Tolkien.

(JME) The trick is when he starts autographing them.

(SSDT) Move to exhume Tolkien to see if he's still there. Passes by Skinnerial decree.

(JME) In The Tech's "ideas" section, there's a review of bookstores, including the Science Fantasy Bookstore, and the review says "It is more than a bookstore, it's a cult center rivaled in Cambridge only by MITSFS." Susan, send this to your mother.

(KM) Joan Vinge was here and gave a lecture and people who didn't go lost out really big.

(JME) No meeting next Friday (Thanksgiving vacation).

(JME) Move to commend the Albanian liberation poster for being banana-colored. Seconded. Passes everybody-nobody-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1750 SST.

BORING BORING BORING BORING BORING BORING BORING BORING BORING BORING

\vspace{18pt}

\centerline{Sincerely submitted,}
\centerline{Adam Mellis, Onseck}

\end{document}