\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 20, 1984

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, not 1700 SST,
Tim Huckelbery, President and Skinner, presiding.

(B*) Move to approve the minutes as drunk. Fails 3-more than 3-about the same amount +Spehn.

Move to approve minutes as da... (Dies.)

(TLH) Move to approve the minutes. Passes, so there.

\goto{Committee Reports}

(JME) NESFAcomm: TLH received a call asking for TLH, president of NESFA.

(John Dumas) Whocomm: Tom Baker's 50th birthday.

(TLH) Moocomm: Casino Royale Saturday- good print. Heavy Metal Sunday, Dark Star Wednesday.

(A^2) Panthercomm: Inventory was- thanks for the help.

(MJG) Draftcomm: I hate drafting.

(JME and TLH) Exoduscomm: Meeting at Sunday at 2:00- be there. Closing at midnight tonight.

(TLH) Note- Charlie Horning has turned in his key.

(B*) Calendarcomm: We have an embarrassment of riches (abundant number of calendars).

(TLH) Moocomm: During the first showing of Cat People, we had a girl who gave a long moan in the middle of the show. (Aaaaah!)

\goto{Old Business}

OBA, etc., etc.

\goto{New Business}

Think, think, think...

(MJG) I'm drawing the new room if anyone wants to see it.

(A^2) Miller motion. Fails.

(KM) Miller motion. Passes.

\vspace{12pt}

\noindent
Meeting adjourned, even more after 1700 SST.

\vspace{18pt}

\centerline{I'm back, everyone; it's about time, isn't it?}
\centerline{Andy Su, Onseck}

\end{document}