\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner}
\newcommand{\onseck}{Elena Romashkova, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, May 17, 2019}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.5 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}
Mommycomm: ERA is officially a keyholder!

Chancellor: ERG now has a lifetime membership!

Ookcomm: The monitor is borked on the left computer (psi-phi).

Seldon: Movie showing tomorrow. They get 20 dollars for snacks.

Mancinicomm: Will rearrange to be in shelf code order, not english language order.

\goto{Old Business}

Algol.

Yesterday, CS learned the FORTRAN index convention.

\goto{New Business}

SIS (Skinnerial Initiative System) (a system to give acronyms to everything \skinner~does):
Operation MIDST (Miscellaneous Items and Door Signs Touchup): \skinner~cleaned up the door and consolidated several signs.
Operation DOLDRUMS (Don't Open Locked Drawers; Results in Unintended Movement of Stuff): The bottom drawer in SR-L might be 'kinda borked', so try not to use it very much. The heavier stuff in that drawer has been switched with the lighter stuff of a drawer above to alleviate the problem.
Operation BOSS (Bequeathment of Summer Skinner): \skinner~appoints Vice, ERA, because she is here over the summer.

Minicult: Kitten Stowaways Survive 400 Miles Inside Steel Column.

\goto{Future Business}

RS: In the future, the bananas will graduate. Motion to award bananas honorary degrees in Course 20. Seconded. 9-1-7 \ps, motion passes. 

\bing
\noindent
Meeting adjourned, 67.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}