\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner }
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, November 1, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.4 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

Panthercomm: has been processing some of the mound in Damnation Alley. Trojan should also take a look at the portion that hasn't been recorded as donations yet.

Hasslecomm/Niagaracomm: both now have partial boxes in Damnation Alley, with the rest in the Annex. Let \skinner know if they get full and he'll move them back/bring out new ones.

\goto{Old Business}

Operation DOMINO has made it through 2001.

MIT Libraries finally picked up the last of our fanzines, including a partial set of TZ. Our full set, bound in special reserve, will stay with us; they'll direct scholars to us if they want to look at the full collection.

ALGOL.

\goto{New Business}

Stop the presses: we have a new prentice! Ooooh, ahhhh. We should probably hold a work party soonish anyway.

Speaking of adding prentices, \skinner will probably update/clean up some of our mailing lists.

\goto{Future Business}

In the near future, it will be \skinner's 21st birthday. In the far future, it will be \skinner's 100th birthday, fingers crossed.

\bing
\noindent
Meeting adjourned by skinnerial decree, 66.4 sec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}