\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner }
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, December 13, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

Analogcomm: submit your IAP hours requests!

Hasslecomm/Bluebellcomm: stuff is piling up. If you've got some free time, do some of it.

\goto{Old Business}

Cast your mind back to August, when Facilities first wanted to abate the tiles in the Annex. ESP, being the main resident of the room, has gotten them to hold off indefinitely, but now that IAP is coming up, they're reaching back out to us about getting it done during that timeframe. \skinner will coordinate with ESP as to when this will take place, with the intention of going along with whatever they're planning since we're pretty dormant as it is and they probably have more undergrads available to commit to it.

\skinner is going to send the Assassins' Guild email tonight because he forgot about it until he looked at last week's minutes.

ALGOL.

\goto{New Business}

DOMINO is starting up again since \skinner has now finished up his schoolwork for the semester. Woo!

This will likely be the last meeting until February due to \skinner flying out on Tuesday and staying home over IAP.

\goto{Future Business}

In the near future \skinner will lose money in Vegas. Gamble responsibly? Bah!

Solipsistic motion: condemn the couple who bought a banana duct-taped to a wall for 120 grand, and commend the guy who took it off the wall and ate it. Because it's not art, it's a fucking banana. 4-0-0 +Spehn.

\bing
\noindent
Meeting adjourned, 66.3 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}