\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner}
\newcommand{\onseck}{Carissa Skye, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, May 10, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.0 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

Seldon/hBarcomm is holding a movie next Saturday!

Algaecomm got emailed by facilities trying to autocomplete someone who's name starts with Al.

\goto{Old Business}

None.

\goto{New Business}

That was a really nice bing. Resonated.

\skinner~is starting SIS, the Skinner Initiative System, wherein \skinner~retroactively acronyms everything he does. First is Operation RUM, Realizing Unborked Minutes. Ookcomm is poked to go look at the 'latest' function, but otherwise they're working. Second is Operation CORGI, Cleanup Of Rogues' Gallery Images. Poke \skinner~if he screwed up your committee labels.

\onseck~offers to internet-stalk the Vice to get an image and is rejected.

Minicult reports that someone tracked down one of those sketchy ads where a doctor begs listeners to give up this vegetable now, and concluded that the vegetable is probably corn. 

Should probably update prentice list.

We are putting staff-pick sticky notes on the shelves.

\goto{Future Business}

One-handed bings are working really well.

XDL's paper about Mesoamerica will be finished in the future.

We attempt and fail to sing. \skinner~is convinced to leave when someone points out that there's an acronym outside the door.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
