\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, October 11, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.3 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

BSTcomm: \skinner  cut his thumb on a filing cabinet drawer while looking for stuff for the final fanzine donation. Press F in the chat.

\goto{Old Business}

Operation AORTA has officially concluded now that the remaining boxes to be donated to MIT Libraries have been set aside. The annex is fairly orderly now.

ID card renewals happened and now all keyholders should have library access again. Email \skinner  if you're still having issues.

\goto{New Business}

Unprocessed donations have moved back to Damnation Alley for increased visibility. Conversion to Hassle is not urgent, but highly encouraged as we've got quite a few boxes building up.

\goto{Future Business}

In the future, there's a holiday weekend! Enjoy the time off, everyone.

Miller Motion. The skinner takes a visit to FFE-135 to get a second from the Multiverse Ambassador. Motion fails.

Second Miller Motion. 6-0-2 \ps. Motion passes.

\bing
\noindent
Meeting adjourned, 65.9 sec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
