\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner}
\newcommand{\onseck}{Rachael Skye, Acting Onseck}
\newcommand{\meetingdate}{Friday, May 03, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

Motion to declare \skinner bad at binging. Motion over ruled; he will learn.

\subsection{Picniccomm and MITSFS Mistress}
Elena is commended for dedication to the picnic. The watermelon sacrifice shall go down in history as the first to contain special effects for the pleasure of Nimbus and the enjoyment of the onlookers. Elena used chicken hearts and coco powder to create a lovely dripping effect when the sacrifice was made.

\subsection{Trojan}
Did not do their work. They will do it when outside obligations end.

\subsection{Mommycomm}
Keyholder gained.

\goto{Old Business}

\subsection{Special Report: Bananas}

SJW has special report on the status of the banana joke.
\vspace{18pt}
MIT Voodoo Magazine is a publication that goes back to early time, and they have many banana-related articles. The most relevant: May 1966, they awarded a Banana of the Month to the best letter, idea, or drawing sent to them. CS Reports that Skinner '67, Phillies, does not remember bananas, but JHS does, setting an earliest date on the emergence of the banana joke. 
\vspace{12pt}
The archive is here, but may need an MIT Certificate to access:
\vspace{12pt}
http://web.mit.edu/voodoo/www/archive/
\vspace{12pt}
See specifically the May 1966 edition.

Thank you SJW for your contributions to banana lore.

\goto{New Business}

\subsection{ASA}
We took care of the ASA membership confirmation thing and passed on the Knowledge of the Mailman to new chamber.

\subsection{Operation GeCCO}
Step one: everyone guess what GeCCO means. \skinner informs us it means General Committee Creation and Overhaul.
\vspace{12pt}

The new Meeting Procedure and Officers and Organization List is declared canon by Skinnerial Fiat. Copies will be sent out. Available in the library as well. Report egregious temporal discontinuities to Star Chamber.
\vspace{12pt}
\skinner extends MITSFS's official condolences to \onseck for the delay this meeting is causing in their French paper.
\vspace{12pt}
Running through committees to make sure the active list is correct. Committees which need members:

\vspace{12pt}
CS is appointed to ASS.comm, ERG assisting (purpose to assassinate the skinner). Barnhart appointed DenMother~~~~~~. FlameComm left open. ERA appointed MiniCult. MTM is appointed Official Second. MJS is appointed OldCommitteesComm. WolframAlpha is appointed PentiumComm. CS is appointed QuoteComm. XDL is appointed Random And Sundry Keyholders.  Xcomm is created to keep track of XDL. Zcomm is currently a placeholder for the last committee we ever create.

\subsection{Minutes}
Need to be unborked. They are borked. Somebody with website experience fix this. Problem with sameness between locker and GitHub? Poke ookcomm.

\goto{Future Business}

SJW motions that the future be cancelled.
Seconded.

17-2-4 \ps

Motion passes.

\subsection{bananas}
There was a banana-related study break today that was not affiliated with us. Objections raised. There is also a banana-related hackathon tomorrow we are not associated with.

Motion to annex the Banana Lounge
Seconded.

20-0-4 \ps

Motion passed.

\bing
\noindent
Meeting adjourned, 69.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
