\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner }
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, September 13, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.8 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

If a Skinner conducts a meeting and no one is around to hear it, will it have actually happened? Let's find out.

\bing

\goto{Committee Reports}

BSTcomm: Had to force open a filing cabinet as part of Operation OFFCAST (to be detailed later), narrowly escaped unharmed. Did receive multiple small cuts on fingers, though, although moving a lot of paper makes that inevitable.

\goto{Old Business}

ALGOL.

\skinner 's meeting with MIT Libraries happened; they're happy to take the whole fanzine collection off our hands, although we have to put it in boxes first because they don't have space for the entire filing cabinet bank. However, when they get the on-campus movers to transport the boxes, they can haul away the empty cabinets as well for disposal. Since we don't really have any more use for them and they'll just take up space, this seems like a good idea.

Minicult: absent.

\goto{New Business}

SIS:

Operation OFFCAST (Our Forgotten Fanzine Collection Archived, Soon Totally): \skinner used all the boxes MIT Libraries gave us for the first wave of fanzine pickup, and as such will contact them to have them taken away and more boxes delivered.

Operation ODDS (Overhauling Damaged Door Signs): After Facilities took signs off of our door for painting, they left them just inside the library. The tape used to attach each sign to the door stuck to each sign below it, and so some were damaged. \skinner salvaged a couple, but had to redesign one since its origins (digital file, etc.) are unknown; the prototype is now on the door, and depending on keyholder opinion may be printed in a larger format.

Operation CHIDE (Chamber History In Digital Entry): \skinner digitized the "Star Chamber List" into an Excel file. There were a lot of weird bureaucratic decisions/special elections, but it turns out we are currently in the 60th administration of the MITSFS and the 50th since L. Court Skinner himself ruled.

Operation ROOF (Redecoration Of Outside Facade): Probably more for Future Business, but \skinner wants to rearrange/repair some of the decorations on the outside of the library. Most prominently, one of our largest posters directs people to a website that hasn't been active for 4 years, so that's probably safe to get rid of. Pretty much everything else is fine though.

People wander into the library, but they're just browsing. Someone in the ESP office hollers.

A model of the Hungarian parliament and an unopened bag of Lindt truffles were found in the annex in the process of boxing zines.

\goto{Future Business}

In the future, TZ 48 will come out. (Sidenote: it turns out that despite us having metric tons of copies of TZ 46 in the annex, that's not the most recent TZ. TZ 47, which we have only two copies of, came out in 2007, and AFAIK is the latest one; Mahogany Row/Thunderbunnies may be poked to confirm that 48 in fact does not exist yet, although it was mentioned in minutes as early as 2011.)

In the future, more people will attend the meetings. Hopefully.

Miller Motion. Shit, there's no one here to second it. That rules out the Banana Motion as well. We've gotta do an Adjournment Song.

\skinner attempts to drive himself out via a rendition of "Semi-Charmed Life" and is distressed to find the sound following him wherever he goes. He flees the library.

\bing
\noindent
Meeting adjourned, 68.5 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}