\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Eleanor Graham, President and Skinner}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, March 15, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 66.0 Ksec SST,
\skinner, presiding; \onseck, recording.

\bing

Minutes read.

\bing

\goto{Committee Reports}

Mobcomm: Declared new rites a couple of weeks ago; seeing no opposition, we will vote on instatement this meeting. Also received a shipment of books.

Mommycomm: In the process of acquiring a new prentice, who is busy on Fridays so will be encouraged to do work on Mondays.

Picniccomm: Has been chosen; is happening.

Mancinicomm: DID THE THING!!! OMG!!!

hBarcomm: Applied for a Midway booth, scheduled an open house following Midway, ordering new shirts in usual colors, may order banana stickers. Skinner may use said banana stickers to plaster over Apple logos in Athena clusters.

BSTcomm: Bubbling continues. Will end Real Soon Now.

Smilescomm: Took on new prentices, currently removing stickers from books.

\bing

\goto{Old Business}

Covered by committee reports.

Elizabeth Bear had a book release party. No one went because we heard about it too late. Twittercomm is encouraged to keep us up to date on such things.

\bing

\goto{New Business}

Time to vote on the update to Mobcomm rites. Seconded; vote 11-1-4 \ps. Motion passes; Mobcomm has new rites.

hBarcomm wants to know if we can create posters for CPW weekend, should we have the manpower/enthusiasm. Skinner would prefer to do this during REX. hBarcomm agrees and withdraws motion.

\bing

\goto{Future Business}

In a few months, ERG will not be Skinner. True Fact. ERG feels old.

Skinner will start poking undergrads to become Star Chamber.

Motion that we order the SHASS office to send us any future banana bread they order. Seconded; 11-4-2 \ps. Motion passes; meeting adjourned.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
