\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner}
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, October 4, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.4 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

None.

\goto{Old Business}

MIT Libraries took the last of the fanzines in the filing cabinets, allowing for the boxes clogging up Damnation Alley to be moved back where they belong. However, following this movement, a few more boxes labeled as ROSFAP and uncategorized magazines were found, so there will likely be one last pickup once it is determined which portions of these will be donated.

Posters were found in the annex that may be used to change up the decorations on the outside of the library.

ID card renewals are happening.

\goto{New Business}

SIS:

Operation AORTA (Annex Organization, Redistribution, and Tentative Arrangement): following the freeing up of space in the Annex and consolidation of all our boxes in said location, \skinner  reorganized the contents of the space to be grouped somewhat logically. Most of the space is taken up by Catacomm overflow, but Hassle/Niagara/Trojan boxes now all have their own areas. \skinner  also performed a general cleanup on the various random things we have lying around in there and also vaguely grouped these by process (Bondagecomm, Surgery, etc.). Further labeling will occur soonish.

Operation TOM is a bit by the wayside, but still ongoing.

\goto{Future Business}

In the future, more meetings will occur, come hell, high water, or lack of attendance by persons other than the skinner.

The skinner is tired, and having come across precedent for the action via Operation TOM, forcibly ends the meeting by skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.6 sec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
