\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner }
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, December 6, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 64.8 Ksec SST,
\skinner, presiding; \onseck, recording.

No meeting was held last week due to the student center's closure for Thanksgiving break.

\goto{Committee Reports}

None.

\goto{Old Business}

MIT Libraries sent an update regarding the fanzines; they've finished their initial assessment and starting next year will have a cataloger create records for all of it. They're also thinking of digitizing parts of the collection. They promise to keep us updated.

ALGOL.

\goto{New Business}

\skinner spoke to someone in the Assassins' Guild about returning the old game records we have sitting behind the t-shirt chest; rightful ownership will be restored once \skinner remembers to email them about a pickup.

No progress on DOMINO lately due to \skinner being hosed, but it'll probably get back on track tomorrow.

\goto{Future Business}

Change is coming; you'd best be ready for it.

A search for "banana" on Wikipedia to find an interesting motion leads to ten minutes of being lost down a rabbit hole.

Solipsistic motion: pursue a hostile takeover of Chiquita Brands International, which despite being based in Switzerland, basically has a monopoly on bananas. 2-1-0 +Spehn.

\bing
\noindent
Meeting adjourned, 66.1 ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}