\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner }
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, November 8, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.1 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

Mobcomm: has added books to the Amazon cart; pending order placement by LHE, our new books shelf will be populated again.

Concomm: we got an email from NESFA. Boskone 57 is happening in February. The website is boskone.org if you're interested.

\goto{Old Business}

Operation DOMINO is midway through 2000.

ALGOL.

\goto{New Business}

By skinnerial fiat, the Solipsistic Motion is established. Its purpose: to automatically provide a second to \skinner's motions should there be no keyholders to do so (i.e., at 8/10 meetings so far this semester). Constant use of the phrase "skinnerial fiat" is no longer necessary.

Motion to establish a distinction between the MIT Science Fiction Society and the MIT Science Fiction Library: the first encompasses the social aspect, while the second encompasses the administrative aspect. Motion passes 2-0-0 +Spehn.

Does anyone actually read the minutes anymore? We say "minutes read" at the start of each meeting instead of actually reading them nowadays, so no one does in person at least. If someone is reading this, either now or in the future- oh, wait, then it should be in future business.

\goto{Future Business}

If you're reading this, send an email to mitsfs(at)mit.edu with the line "On November 8, 2019, MJS said I could have a dollar in fine credit," and you'll get a dollar in fine credit. One redemption per person. To future keyholders: this is a skinnerial decree, so until it gets overruled by some future skinner, it's a thing. Boom.

Motion to declare the banana the national fruit of MITSFS's Martian colony. 3-1-0 +Spehn.

\bing
\noindent
Meeting adjourned, 67.2 sec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}