\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner }
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, October 18, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.3 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read. Let it be noted that the size of last week's minutes' tex file was 2019 bytes, which is A Cool Coincidence (TM).

\goto{Committee Reports}

None.

\goto{Old Business}

MIT Libraries will take the last zines off our hands either next week or the week after, depending on how free the moving company is.

Operation TOM is officially complete! Hooray! (Pause to bask in the uniformity of our minutes archive.)

With regard to the donations in Damnation Alley, unopened boxes and open boxes with return addresses should go to Trojan, but the unlabeled open ones can likely go straight to Panthercomm. Hopefully this'll help us process them quicker.

\goto{New Business}

SIS:

Operation TEUTONIC (Trial and Error Until TeXes on Net (Implied Conversion)): \skinner, after troubleshooting an issue with the latex2html command with the help of Ookcomm (props!), has generated html versions of the Operation TOM minutes, meaning that all currently digitized minutes are now visible on our website (although some new hyperlinks may be necessary for easier access). Notice how I said currently digitized minutes- this leads into...

Operation DOMINO (Digitizing Old Minutes In Nonspecified Order): \skinner has started typing up stuff from the Minutes drawer behind the keyholder desk. In the interest of decluttering, minutes which have some form of significance (containing drawings or old Minicult articles, typewritten classics, etc.) will be moved to a box in the annex, and minutes without any defining characteristics (printouts, things messily handwritten on scrap paper, etc.) will be recycled.

\goto{Future Business}

In the future, it will be the present. Yup.

\skinner decrees upon his laptop honorary MITSFS membership and plays "Jack and Diane" off of Spotify. Suitably repulsed by this "singing," \skinner exits the library.

\bing
\noindent
Meeting adjourned, 66.4 sec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}