\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Eleanor Graham, President and Skinner}
\newcommand{\onseck}{Eileen Hu, Onseck; Rachael Skye, Stand-In}
\newcommand{\meetingdate}{Friday, MONTH DAY, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}
\subsection{Special report} 
From the committee of SJW. She has taught us all how to update minutes in the website index, and so your correct reading of these minutes is brought to you by her effors. A Skinnerial commendation is extended. This information is being added to the rites.

\subsection{Hasslecomm}
Additional commendation to CS for not letting a box set of anthologies into the library.

\subsection{Smilescomm}
Is caught up on bubbling the shelf bought one year ago. Proceeding apace to the one bought three months ago.

\subsection{Mobcomm} 
Will have a new CVC, controlled value card, from SAO in the next week. This will ease purchasing and stop our card from getting cancelled every few months. Updated rites are in the works with this new information and will go out when complete.

***
Everyone left.
Skinner's gone.
Onseck stand-in  is alone (with 6 other people).
Where are they.
Where are we.
How can we proceed without our leader to guide us?
We don't know. But we are forced to acknowledge in our misery that the banana-colored couch has not been washed since the year 2000.
Ah! A noise!
Skinner returns.
Back to minutes.
***

\subsection{Mancinicomm} 
Has been stood up by the expected Chinese speakers they wanted. To be rescheduled. But as soon as that happens, all FL books will be recorded and barcoded. As soon as that happens, a motion can be set before StarChamber to open FL to check-out.

\subsection{Picniccomm}
Should be created soon.

\goto{Old Business}

None.

\goto{New Business}

\subsection{Proposal} 
From MJS:
Change the name of Smilescomm to BSTcomm (blood-sweat-tears comm), to represent the 2/3 of these he has put into bubbling. No comment as to which is left out.
Proposal modified to create new sub-committee for the hard work of bubbling.
Seconded.

Put to vote.

22-3-7\ps

Proposal passes.

BSTcomm created. Official directive: Smilescomm does the little things that make people happy. BST does the big things that make people happy at their own expense. They are recognized for their contribution.

\subsection{Election of the Honorary Plant}
A nameless juniper bonsai has been brought to the libary by an anonymous apprentice. The juniper has been put forth for the position of Honorary (Dead) Plant. Challengers are being accepted.

Nominations:
Nameless Juniper Bonsai
Weirdly Sticky Rock
The Anti-Leak Noodle Left In The Back Room By Buildings And Grounds
The Trilby Banana

***
Pause to fulfill the functions of a library. Books are checked out
***
Votes:
Nestor <3: 1
Elenarom: 1
Groot: 1
Contents of Library: 1
Sal: 1
'Can't we all be honorary dead plants together': 1

ALNLITBRBBAG: 7
Bonsai: 25
Rock: 23
Banana: 19

A close race, but the bonsai wins!

Nameless Juniper Bonsai declared Honorary (Dead) Plant. NJB Accepts.

\subsection{Online Library}
MIF has been looking into bringing e-books to the library. This proposal has been discussed and heartily accepted. MIF is dispatched to research these options. Overdrive is an online library system which allows libraries to have 'special collections,' which could be perfect. This will be explored and reported on later.


\goto{Future Business}

Create picniccomm.

Starchamber elections are horrifyingly soon. You should talk to us if you are interested. Date to be set soon.

MJS (current Vice) is interested by does not want to lose again to Nestor-13 and Wrath as in the great upset of 2018 (resolved only through luck). Skinner declares she will use the power of skinnerial fiat to democratically insure MJS will win over the aforementioned.

Motion to clean the banana-colored couch.
Heartily seconded.
23-3-3\ps
Motion passes, meeting adjourned.

\bing
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
