\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Eleanor Graham, President and Skinner}
\newcommand{\onseck}{Eileen Hu, Onseck}
\newcommand{\meetingdate}{Friday, April 26, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.8 Ksec SST,
\skinner, presiding; \onseck, recording.
\bing

Minutes read. Minutes were the result of much hard work by RS.

\goto{Committee Reports}

\subsection*{Picniccomm}
Prentice will buy coconuts tomorrow. Hmart recommended.
Cars are being covered by TM and CS.
Bear and Gladstone contacted by the Skinner, cannot make it to the picnic but Bear expressed interest in visiting in the fall.
Rain might be looming on the horizon.
Suggested that we put extra effort into the sacrifice for next year. Do we know what makes a virgin watermelon? The answer is no.

\subsection*{ManciniComm}
Shelves will need to be reorganized, will happen soon.

\subsection*{TrojanComm}
will be dealt with soon.

\subsection*{BSTcomm}
MJS tells us that the sharp corner of the table is now OSHA compliant. Reverse bubbling happening.

\bing
\goto{Old Business}
XDL should get sleep.
Midway happened was sucessful. Prefrosh wanted animorphs. We do not have animorphs. They are small books but creepy, loom large in the mind, existentially horrifying to adults. The best animorphs is where they turn into horses.

\bing
RS screams in response to the bing.

\goto{New Business}
The taking down of the cpw open house sign.
Shirts ordering will happen at some point. Designed already. Someday banana stickers will happen.

ELECTIONS
\subsection*{Onseck}
Nominations:
Eileen Hu
monkey signed by David Brin
\latex
Natasha (the AI of the guy who wants to bribe his son into MIT)

Note: All the knowledge of accents that CS once posesssed has been replaced by irregular verbs.

Votes counted.Eileen Hu (EH)  wins and is declared onseck. Natasha got second place. We may communicate this to the guy. Natasha may be useful on the war council.

\subsection*{LHE}
Nominations:
Eleanor Graham
Eleanor's credit card
Bernie Madoff
the guy from catch me if you can
William Nobreaga?

Question: Why do they scream? because they are alive.
A question for the world from RS. What is this button on Firefox that changes things? SJW replies that it is reader mode.
DNA and Cas13 RNases are invading the votes as write-ins on the scratch paper side of the votes.

Votes counted.Eleanor Graham (ERG) wins, blowing them all out of the water and is declared LHE.

\subsection*{Vice}
Nomination:
Margarita Misirpasheyeva: Sloth
Elena: Overthinking
Elena's plant: Death
The kitten that lives inside Al's suit: Fuzzy
Free Will: Pride
The Grinch: Wrath
Sarek: Being a bad father

A very very serious stump speech for the local peasantry is given by Elena. The watchers of Full Metal Alchemist are condescending towards those who have not seen it and cannot name all the seven deadly sins.
Margarita is probably singing right now. Her stump speech is transmitted to an adoring audience.
CS contains multitudes.
Nestor has had emergency surgery but it didn't work.

Votes counted. Elena wins and is declared Vice. Elena will embody the Vice of Overthinking.

\subsection*{President}

Nominations:
Mathew Suazo running under the slogan Make MITSFS bureaucratic again.
Nestor
Leia Organa
The OSHA-compliant corner
The cardigan of SJW
The genre squid
The dormant office of official second
The letter E
The meme E

There is a mystery vote for Oulipo, very clearly written but meaning unknown. We resolve the mystery. Oulipo is no one in greek. Probably from SJW but she's not admitting it.

Votes counted. Mathew Suazo (MJS) wins and is declared President. 
A round of applause.
President is asked to appoint a Skinner.
MJS appoints MJS to Skinner.

Note to picniccomm. Do not get moldy coconuts.

\goto{Future Business}

In the future there will be a picnic. If we are lucky they will shut up and stop cheering in the future.

Miller Motion
Seconded.
12-9-2
Motion fails!

Miller Motion again.
Seconded.
17-6-2
Motion passes! Meeting adjourned


\bing
\noindent
Meeting adjourned, 70.2 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
