\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner}
\newcommand{\onseck}{Eleanor Graham, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, September 27, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.0 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

Mobcomm: SAO ate one of our boxes. I need to go during business hours and find it.

\goto{Old Business}

MJS found truffles and a model of the Hungarian parliament in the annex. They're unclaimed. ERG suggests using the truffles to bribe freshmen. 

ERG will buy a new computer. Probably a new one this time, since the crufted one didn't last very long.

Pickup of fanzines by MIT libraries is back for a second round, October 1. After that all the labeled boxes will be gone. More space! Though mostly in the annex.

MJS is thinking about decorating the outside of the library more. Some of the posters have very outdated links.

\goto{New Business}

MJS needs to do ID card renewals. It's that time of year.

SIS: Operation TOM. TeXing Odd Minutes. Athena locker has some old minutes that aren't TeX, instead just simple .txt files. And .etc files, whatever those are. MJS will change these to be more readable.

\goto{Future Business}

In the future, TZ 48 will happen. It lives on. In the annals of history. It's coming real soon now. 

In the future, there will be swag. T-shirts and stickers. Maybe the MITSFS NASA logo that's on the door now. Send vectors to ERG. 

Motion to make tiny MITSFS shirts for all the bananas in the library. Motion seconded. 
5-1-2\ps
Motion passes.

\bing
\noindent
Meeting adjourned, 65.8 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
