\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner}
\newcommand{\onseck}{Eleanor Graham, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, September 6, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.4 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\bing

\goto{Committee Reports}

Mobcomm: We made an order of books in late August. Most of the books are here now and are being gradually processed by panthercomm. The new book shelf has new books on it! You won't be able to check them out until the date on the sticker, as usual.

Trojan: We have a donation backlog from over the summer. Also a mysterious box of books, many of them brand new, was found outside the library by MTM. We don't know why we have this and we aren't sure we need new books, but it's ours now.

MJS explains what the Skinner is. The phone rings. Phonecomm says that KKB wants people to know that an Assassins Guild game is happening tomorrow and is short on players. ERA explains the Assassins Guild. ERG explains tomorrow's game. 

ERA introduces herself as vice, explains that vice doesn't have an official function. However, she is mini-cult, which is a thing. She also has committees. She sacrificed a watermelon full of chicken hearts, kind of a bad idea in retrospect. MJS explains that the vice runs under one of the seven deadly sins, usually sloth in practice.

ERG introduces herself as LHE, her actual position. She was also Skinner last year. And is acting as Onseck right now. She has never been vice but has many vices. 

EH isn't here right now but is the actual Onseck.

All of this follows under the general umbrella of visitorcomm, because there are frosh here. This was also a stalling tactic to allow ERG to write up her own committee reports while MJS talked. 

MJS explains how he keeps track of the names of committees. He has a chart and mnemonics. It's very impressive.

\bing

\goto{Old Business}

Algol. Nobody except MJS knows what algol means. Apparently it was a shorthand for algorithm, specifically an algorithm running through common old business. I'm not going to write all this down but there was something about comic books and bicycles and sex and ski trips and gags. And then the usual motion. The full text of this algol is sitting on a piece of paper and is very old. 

Minicult: a bear walks into a hotel, takes a nap. A bear went into a sink in Montana and took a nap. It was removed by hotel staff. It was a young black bear, very cute. 

\goto{New Business}

Over the summer, computers started to suck. MULTIVAC and microvac swapped names. The computer on the left, microvac (maybe now called MULTIVAC) still works in Gnome section. MULTIVAC, the old one, on the right, is in pieces. It's almost certainly broken. By skinnerial decree, ERG will buy a new computer in her capacity as LHE to replace MULTIVAC. ERG will also buy a new surge protector because it's apparently fifteen years old and sketchy.

The MIT libraries emailed to say they had a collection of our fanfiction zines from the 80s. We don't know why or how they have it, but the rest of our zine collection is taking up space and collecting dust so we're going to give what we have to the libraries so we can have a complete collection. MJS needs to meet with them in an official capacity, which wasn't possible over the summer. The fanfiction will be leaving our collection soon-ish.

There is asbestos in the annex. We kind of expected that. A few tiles broke, ESP next door sent in a work order. Facilities came in and decided they wanted to remove the whole floor. This is not great because MITSFS and ESP have a ton of stuff in the room. It's not terribly urgent so we're putting it off. ESP is trying to push it to IAP. We don't have to move the safe because that's too big for anyone to move. We have nice things in the safe and file cabinet, like money and Star Trek scripts and porn.

Midway happened. We have people here. Yay!

People graduated. We need a new mommycomm to replace TM. This just involves tracking prentice hours. ERA volunteers to be mommycomm. Mommycomm may or may not host work parties. We need a new Seldon to replace CS. ERG says Chamber usually runs events anyway, MJS takes that as an invitation to make her Seldon. Titanictetriscomm is the last new committee, also was CS. MJS volunteers because he's already BSTcomm.

SIS is going to happen. Skinnerial Initiative System. MJS likes acronyms. DOLDRUMS: don't open locked doors, results in unintended movement of stuff. MJS broke a cabinet last meeting. 

\bing

\goto{Future Business}

In the future, MJS will get the Skinner keys back. In the future, MJS will attend the new prestigious mandatory leadership summit. Libcomm needs to hold inventory someday. ERG was going to poke them over the summer but realized that nobody was around over the summer to do inventory anyway. In the future there will be social events.

ERA: motion to fry a banana. MJS says that's too concrete, last time we gave them all degrees in 22. ERA retaliates by proposing eating a banana. That's even more mundane. ERG says most of the bananas in the library are not edible. 

Motion to pay off the bananas' student debt after they got their degrees in course 20. Seconded.

21-1-4\ps

Motion passes!

\bing
\noindent
Meeting adjourned, 67.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
