\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner }
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, October 25, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.5 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\goto{Committee Reports}

Mobcomm: (AMB is briefly here) We should order more books, because the new books shelf is looking somewhat bare.

\goto{Old Business}

Operation DOMINO continues. Everything should be digitized from 2002 onward at this point.

\goto{New Business}

Happy Halloween! WOOoooOOO! Spooky.

This past Monday was the 70th anniversary of MITSFS. We probably should've done something for it, but meh.

Someone came to meeting! Although not another keyholder, so we still can't hold motions, but it's a start at least.

\goto{Future Business}

In the future, there will be the heat death of the universe. But, more immediately, ice cream. And that's good enough for me.

Meeting adjourned by skinnerial decree.

\bing
\noindent
Meeting adjourned, 66.0 sec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}