\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{plus Spehn}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Mathew Suazo, President and Skinner }
\newcommand{\onseck}{Mathew Suazo, Pseudo-Onseck}
\newcommand{\meetingdate}{Friday, September 20, 2019 }
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 65.6 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

The show must go on.

\goto{Committee Reports}

None.

\goto{Old Business}

ALGOL.

Operation OFFCAST: the first round of fanzine donation happened on Tuesday, with G-Z fanzines picked up and multiple old filing cabinets disposed of. The second round will be happening on October 1, when the A-F and unorganized fanzines will be taken and more filing cabinets will be thrown out. Following this, we'll check in with cruft to see if there are any more unlabeled/incorrectly labeled fanzines around to constitute a third wave of donations.

Operation ROOF: no action yet; waiting on input of other keyholders. We'll see if anyone shows up next week to discuss it, but otherwise \skinner may be forced to take drastic action...

Minicult: absent.

\goto{New Business}

As part of OFFCAST, some things were consolidated into our largest/best quality cabinet in the annex, leading to the discovery that we have tons of surplus copies of basically every TZ since 30. We could consider giving these out as promotional materials, because who doesn't want a 30 year old amateur publication? Maybe most people.

\skinner will begrudgingly attend the student leader summit tomorrow. If anything actually productive comes out of it, this will be noted at next week's meeting.

\goto{Future Business}

In the future, more than one person will attend the meetings. See, the standards have already lowered.

Miller Motion and Banana Motion still inaccessible for lack of a second. On second thought, since \skinner has ultimate power over reality within confines of the library...

\skinner sidesteps into the 4th dimension and sifts through the local parallel universes; coming across a Simpsonesque universe, \skinner steps in, startling his canary-colored counterpart.

Motion to make the banana-hued Skinner of Dimension FFE-135 the Multiverse Ambassador to our chapter of MITSFS (Dimension S-013). Seconded. 6-1-1 \ps . Motion passes.

\bing
\noindent
Meeting adjourned, 67.4 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}