\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 4, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous meeting not read nor corrected.

(L K) Move to approve the minutes as decomposed.

Motion passes, not that many, to people saying 'ow' and other noised, to chickens plus Spehn.

\goto{Committee Reports}

(PJN) LHE report - see that hole in the wall?  It's not there anymore. Actually, it's all there now. It's our hole in the wall.

(HAM) Skinner Report - You may have noticed we have a replacement for Ella here, known as DTR (Dread Typewriter Roberts/Data Terminal Ready) because it wears a mask and takes no prisoners.

(WDS) Pseudo Fame Comm - which everybody already knows about (except for Robert). (Referring to virus attacking internet.)

(C H) Reader Con Update - George Alex Effinger isn't coming. Anyways, it's still in two weeks, it's still twenty dollars, it's still up in Lowell, it's still going to be wonderful.

(L K) JourComm - projected new date for TZ: sometime before '89.

(WDS) Self Comm - about once every eight years I shave off the mustache and beard in order to remind myself why I have a mustache and beard. It's under construction at the moment.

Discussion degenerates into pumpkin drops and folks remember last year when some skydivers playing catch with a pumpkin drop it through some poor random woman's kitchen roof. Which technically belongs under old business, therefore, on to...

\goto{Old Business}

(WDS) I feel old.

On the discussion of time warps, Skinner starts teasing Onseck about putting the incorrect date on the October 21 minutes, which she hadn't realized because she didn't read the minutes (the pseudo Onseck Derrick read the minutes that week) nor had she typed up the minutes where those minutes were read and corrected because her narcotics had started decomposing. (An odd variation on her chem lab.)

OBA um, us, uv, ur, u \bing

\goto{New Business}

(C H) Morte Comm - Halloween evening in the Can Tab Lounge, one of the neighborhood locals strolled in dudded up as a hunchback, proceeded to throw a rope over one of the beams, and hang himself. Well, he was a guy who's well known for his practical jokes, and it was evident from anybody who looked at him, that he had indeed rigged up a harness that went underneath his arms so that he could hang from that. After he'd been hanging there for about ten minutes, somebody asked him if he was okay and he said 'fine.' After another ten minutes went by and they noticed he wasn't moving too much, they cut him down only to find that he had indeed asphyxiated.  Evidently, the lesser know asphyxiation by compression as opposed to asphyxiation by strangulation.

(WDS) Yes, he was killed by his safety harness, evolution in action.

(WDS) Morte Comm sub two - It is interesting to note that Professor Charles W. Kingsfield, aka John Houseman, died on the 50th anniversary of the rather famous War of the Worlds broadcast which he co-produced along with Orson Wells.

(C H) Addendum to that addendum - Evidently they did a rebroadcast of War of the Worlds in Portugal (we assume it was in Portuguese) and there was quite a panic.  When they found out it was a hoax, they went down and tried to storm the radio/television station.

(HAM) All these people desperately upset because Martians were invading New Jersey.

(WDS) I believe I read that they altered the script to make it some small town somewhere in Portugal.

(PJN) Another addendum to that - supposedly on Halloween eve they did another broadcast currently in 1988 of War of the Worlds. I heard it was very amusing.

(WDS) Mini Cult - the Civil Liberty's Union of Massachusetts is selling, for one dollar each, buttons or bumper-stickers that proclaim you a card carrying member of the ACLU.

(Robert) Mini Cult - I hear on the radio station that SHARP in England had wrote an advertisement for their calculators saying 'with our calculator, anybody can be a genius' and it showed Ronald Reagan with an Alfred Einstein haircut. The American Embassy complained and SHARP pulled the ad.

(PJN) Motion to give Donna some non-decomposing narcotics so she can get the minutes done in a banana colored binder for next week.

(WDS) If the narcotics are good enough, it will look banana-colored to her no matter what color it is.

Motion passes lots of really drugged out people, to some decomposed narcotics, to the ACLU plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17(mumble) SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
