\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 11, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding.

We don't have an Onseck, wait.. we have an Onseck - a breathless Onseck materializes out of thin air. Sigh, minutes from two weeks ago read and corrected.

In the middle of the reading the minutes, the phone (RING!) cries out for Larry, but Larry isn't there to answer.

(RJG) Motion to approve the minutes as unbelievable.

Motion passes almost no-one, to no-one plus Connie, to an Albanianed chicken plus Spehn, plus two points for Phil.

\goto{Committee Reports}

(HAM) Skinner Report subtitled "Your Tuition Dollars at Work" - I had great fun earlier this week spending 1600 dollars to buy new shelves for MITSFS, 1500 of which is coming out of all of your tuition.

(WDS) Cornelia Otis - Wimp beats shrimp. Cornelia Otis sub two - one of the congressional fights down in Georgia, the republican incumbent - a guy with the apparently incredibly appropriate name of Pat Swindal, who was indicted for all sorts of flummery, managed to get himself defeated rather handily by a Democrat by the name of Ben Jones. Ben Jones is rather interesting in that he is an ex-actor. He played Couter, the mechanic, Dukes of Hazzard. We now have a Couter and a Gopher in the US House of Representatives.

(PJN) LHE report - During the month of September, the MITSFS made almost 800 dollars. By the end of October though, our yearly profit had fallen to about 575 dollars due to the purchase of DTR.

(WDS) Move to declare all months hence-forth as September!

\bing Motion passes!

(C H) Pseudo Fame Comm - I will be moderating the workshop panel at Reader Con, with such notables as Algiss Budryss, James Patrick Kelly under my power. Reader Con in one week.

(WDS) Sit Comm - Beauty and the Beast makes its season premiere next Friday, and I watched the third episode of Something is Out There. As they say, three strikes and you're out.

(HAM) Pseudo Mob Comm - Several of us are going out to New England Mobile tomorrow in an attempt to erase the deficit in our collection.

\goto{Old Business}

(HAM) Now that we finally had a decent rain during this past week where we didn't have a roof-leak, I think they're going to finally sign off the job to Phs-plant which means that, in theory, they will come replace our roof tiles once our Onseck writes a letter to Steve Immerman saying "we want our roof-tiles replaced and please reimburse us for the books that were damaged." It should be noted, by the way, just to heap public abuse upon the Onseck, that she was asked to do this back in R/O week.

(RJG) Ex-Skinner Report - Our beloved ex-skinner who shall not be named may be joining the FBI soon.

OBA um,us,uv,ur, \bing

\goto{New Business}

Psuedo People's Albanianed Embassy - Louise Waugh read some articles donated to her by the Albanianed Seth. See attached, highlighted articles.

(HAM) For The Blue Folder - posted to the net, from Carnegie Mellon, a parody of Amber, called the 'Dying of Ember.'

(WDS) Mini Cult - They drew a number for the Massachusetts Mega-Bucks on Wednesday night. (Six numbers between 1 and 36 inclusive.) The number drawn was 1-4-5-6-8-9.  There were 60 winners, each of whom got a before-tax amount of 100 dollars.

Phone Comm - RING! Adina for her sister.

Not only were there 60 winners, but there were apparently like hundreds and like thousands of people who won the 40 dollars for matching 4 of 6 or 5 of 6.  Massachusetts is full of bozos who just go out there and play 1-2-3-4-5-6 as their megabucks bet, secure in the knowledge that if they win they'll get 3.22 back or something. People are dumb.

(WDS) After seven years of everybody in the universe knowing about it, the Defense Department has finally admitted that gosh-wow, golly-gee, we really do have a stealth fighter after all. And they released one photograph of it.

(C H) Wilds Card Five is out; also Barbara Hambley's new vampire hardcover book Those Who Hunt The Night. Reader Con next weekend.

(HAM) In the most recent Locus it mentioned that Clive Barker was out in San Francisco signing his new book; one of the people who came up in line got up there, pulled out a razor, slashed his own arm so that Barker could sign it in blood. He took this in stride and did so.

(L K) Move to hypnotize an Albanian with a banana so that we can convince him to moo like a chicken.

Motion passes, several who really don't care, to Connie who's really been working on Reader Con too long, to an Albanian and some other things plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1731 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
