\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 15, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(BPS) Move to approve the minutes as vivisected.

Motion seconded, passes enough to pass it-not enough to oppose it, especially not Connie, who is probably going to get vivisected by Robert if he has anything to say about it-maybe 2 +Spehn.

\goto{Committee Reports}

Phonecomm (time warp from minutes): it's Rob for LAK.

(DSK) Skinner Report: election will be Friday May 6. Election results will be Onseck- Donna Bell, LHE- Phil Nesser, Vice- Rob Gates, President- Herb Miller.

(DSK) Cornelia Otis: looks like Gore might be next, after New York.

(DSK) Cornelia Otis2: Italy now has its 48th government in the 43 years since World War 2.

(BPS) Cornelia Otis3: Former White House spokesman Larry Speaks stated that he made up quotes and attributed them to Reagan.

(CH) Addendum- Reagan's spokesman said Reagan wasn't very upset at this.

(LAK) Pseudo-LHE Report: Rob says hi.

(VHS) Pseudo-Ex-Skinner Report: Sue Tucker, who has been looking for her Darth Vader for President button for weeks now, finally found it. The MIT mail office had it in a bin somewhere.

(BPS) Sitcomm: there is a fresh episode of Next STrek tomorrow. The next six will be new ones as well.

(DSK) Cornelia Otis4: there was a lab explosion in building 6 last week. Never add anything to acid.

(BPS) Sitcomm2: Probe has finished its six week run. It had the greatest upwards delta in quality that I have ever seen between the pilot and the actual series.

(HAM) Sitcomm3: the rumor is out that after this year, John Nathan Turner, who produces Dr. Who, will quit.

(BPS) Moocomm: they had the Oscars. Not a very good year for fantasy or science fiction. Innerspace for best visual effects, and Rick Baker, the man who made Vincent what he is today, for makeup for Harry and the Hendersons.

(CH) Radiocomm: a DJ in Dallas on the air suggested people send the station 20 dollars. Now he has over 250,000.

(GF) Concomm: the Sheraton has signed the contract with Noreascon.

\goto{Old Business}

(BPS) Did they or didn't they? The world may never know. (This in reference to Beauty and the Beast.)

(CH) This episode was like Beauty visits thirty-something.

OBA: usual Phonecomm. Scott is condemned for being boring. It's Larry Lenhoff and everybody says hi.

OBA2: um, us, uv, ur.

\goto{New Business}

(S??) Minicult: from Spy magazine- the members of the New York Athletic Club were sent a letter asking them to maintain the high standards of the club by not entering wearing inappropriate garb such as athletic gear.

(RvdH) Minicult: tomorrow is the 45th anniversary of the discovery of LSD. Somebody put up really good posters all around the Institute.

Whoever that was is commended by Skinnerial decree.

(BPS) Minicult: I saw in an old copy of People magazine that Buzz Aldrin was planning to be married on Valentine's Day. The engagement ring contained a cut and polished piece of moonrock instead of a diamond.

(AA) Minicult: I bought a new car. It's a silver Corolla FX.

(BPS) Minicult: from yesterday's Glob- in Italy an injured bicyclist and his stretcher fell out of the back of the ambulance when attendants failed to shut the door properly. The guy hitchhiked to the hospital.

(BPS) Minicult: according to Magnum, Magnum was Annapolis class of '68, as was Lt. Col. Oliver North. On this coming May 1st, North's retirement from the Marines becomes official, and the last first-run episode of Magnum is shown.

(S??) Minicult: an April Fool's message that warned of April Fool's messages was an April Fool's message.

(HAM) Dave Barry just won a Pulitzer Prize, part of it based on his speech on why Pulitzer Prizes are really stupid things.

(VHS) Move to vivisect the banana-colored balloon over by Bill.

Motion seconded, passes enough-Connie, stop that-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}