\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 19, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Phil Nesser, LHE and Pseudo-Skinner, presiding.

Minutes of the previous meeting were nonexistent.

(BPS) Motion to squash Rob.

Motion seconded, passes 7-2-2 +Spehn.

\goto{Committee Reports}

(SSDT) Ex-Skinner Report: I got a new bike.

(JAH) Infocomm: looking for recommendations for good games for a PC. Especially Infocom.

(JAH) Fweekcomm: Fweek is in a couple weeks. Schedule to be up soon. Midway is all set up timewise and such. More info to follow. I'm also thinking of working up an SF/MIT fun trivia quiz.

(BPS) Sitcomm: Writers' strike is over. New shows will happen.

(BPS) Moocomm: Good things are being said about A Fish Called Wanda. It's great. Connie likes watching the dog get squished under a concrete block.

(GF) Somethingcomm: Something about a satellite dish at Kresge. (Ed Note: lots of mumbling about Kresge, Sri Lanka, travel, and a satellite dish- I didn't understand a word of it.)

(BPS) Meteorologicalcomm: it's over. At least temporarily.

(PJN) LHE Report: Books are closed up through the end of June. We can finally use the endowment fund. Finboard rep is away for the summer.

(CH) Addendum- is our new fine policy making a difference? (PJN) Too early to tell, but income over the past year was way down.

(BPS) Cornelia Otis: De Laurentis Films has filed for bankruptcy. Such is deserved by a man who believed he could make lots of money off a remake of King Kong.

(CH) Somethingcomm: Margo Adams' case against Wade Boggs was thrown out of court.

(BPS) Cornelia Otis: Bye, Ed.

(BPS) Cornelia Otis: Remember when Ed Meese got lots of laughs by accepting the pornography report standing in front of the statue of Lady Justice (which has one breast exposed)? Well, to prove his stupidity, his final press shot as he left office was from in front of the same.

\goto{Old Business}

(BPS) Hackcomm: Matthias Rost was released from Russia. He left in a much larger and more scheduled plane than he landed in Red Square with a number of months back.

\goto{New Business}

(AA) Minicult: Someone did a study to show that men lie about sex- or in order to have sex.

(CH) Minicult: A couple in England bought a new vacuum cleaner and went to plug it in when it hissed. It turns out that, as a bonus, they had received a three foot long Mediterranean Water Snake. They got a free replacement vacuum cleaner.

(CH) Minicult: Woman mistakes two tiny UFOs for aspirin and swallows them... nuff said.

(BPS) Minicult: Math at work in the real world. Yonkers, NY is being fined for not accepting a federal court judge's order for desegregation. On August 3, he started an assessment of the fine... 100*2^(n-1) dollars per day.

(BPS) Minicult: The Hamilton Collection has added matching mugs to their Star Trek plate collections. Oh joy, oh rapture.

(BPS) Sitcomm: Beverly Crusher down in flames- it's official, she's leaving the show. Wesley will get a bigger role, and Jordy will be transferred to engineering.

(BPS) Phonecomm: no ring, no dialtone, no phone.

(AA) Old Business: Jim Mahoney is moving to Vermont to be the Physics Department at some small non-science-oriented college.

(BPS) Whooshcomm: It looks like a September launch may happen.

(JAH) Move to fill a banana with oxygen and hydrogen and set it on fire.

Motion seconded. Passes many-not enough-almost as many +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Lyingly submitted,}
\centerline{Robert Gates, Vice, Summer Skinner, Speaker to Babs, and hopefully for the last time, Pseudo-Onseck}

\end{document}