\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 18, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes from the previous two meetings read and corrected.

(WDS) Move to approve the minutes as not being at ReaderCon.

Motion passes, ain to an honorary Connie and a pseudo Connie, to almost no-one plus Spehn.

\goto{Committee Reports}

(HAM) Piano Comm - We have a new keyholder, Jesse "he who shall not be spelled" Parelius. Interesting point to note, this is the first time in about four years that we've had a keyholder with the initials JP (and nobody cares.)

(WDS) Cornelia Otis (sub 1) - All along throughout his campaign, George Bush promised that he'd continue the fiscal policies of Ronald Reagan and the business community said "yeah, yeah, we should support George Bush." Then he got elected and immediately afterwards he stock market went down about a hundred points, the dollar plummeted, and all of these big money movers are terrified at the thought of what George Bush is going to do. (sub 2) - Senator John Carey (D, Mass) has apologized for comments he made jokingly stating that the secret service has orders that if the president's life is seriously in danger they are supposed to shoot Dan Quayle.

(Seth) Addendum to that - Apparently there was actually somebody at MIT who posted "shoot Quayle first" to netnews and received a visit from the secret service.

(WDS) I can't wait to see what the secret service makes of the 24-hour coffee house downstairs. Quote of the year "Shoot Quayle first"

(HAM) Moo Comm - New Disney movie comes out tonight: "Oliver and Company."  

(WDS) Whoosh Comm - The Soviets finally managed to put their Burin (Buran) shuttle up. Went around for two orbits, came back down, landed, no trouble - and they can do it with nobody on board.

(HAM) Sit Comm - from Turner land - the next colorizing project is going to be the original King Kong.

(WDS) Sit Comm (sub 2) - Season premier of Beauty and the Beast tonight at eight. Starting next week, NBC is going to move Something is Out There from Fridays at nine to Fridays at eight.

(HAM) Plug Comm - Reader Con is this weekend.

(J P) Peoples Estonian (sp) Embassy - Estonia has declared that it can now overrule laws given by the Soviet government (this is acting on its autonomy.)  Lithuania is expected to do the same today. And the leaders from Estonia have been invited to Moscow to discuss the situation.

(HAM) Addendum to that - Apparently the only two ways in which they said they are not independent are defense and foreign policy.

(WDS) Cornelia Otis - Pakistan, which is a moslem republic, has elected a woman to lead it.

(WDS) Crash and Burn Com - The USAF has lost its second B1B bomber in nine days.

\goto{Old Business}

(HAM) I got a phone call today from the Central Co-operative Bank which apparently we closed an account with four years ago. They have an outstanding check for us from around six years that we never cashed for 140 dollars (or something), and "would we like it?"

(HAM) Phone Comm (otherwise titled "how did they find us") - Now that the Student Directory and the Faculty Directory is out, and our phone numbers, which are different in both of them, are wrong in both of them. But it's ok, people will still be able to find us, because the contact person's phone number (mine) is also wrong.

(WDS) that would have been Mob Comm - Last Saturday, the Skinner, the LHE, the alleged Ken Johnson, and the alleged Mob Comm (myself) hit New England Mobile. It did not hit back.

OBA um, us, uv, ur, u \bing

\goto{New Business}

(WDS) A three-hundred foot diameter radio telescope at the National Radio Astronomy Observatory in Green Bank W.Va fall down, go boom. (See attached article.) It was also pointed out that it was 26 years old and had outlived its expected lifespan.

(HAM) The expected IAP tee-shirt run for new MITSFS tee-shirts looks like it's not going to be able to happen because the silk-screening room is already booked solid every day through IAP.

(HAM) We had an exciting meeting of fourth floor activity people. We pointed out to them the fact that anybody can wander upstairs and ask to add someone to a key list and won't ask you for an id.  (Herb flames for a while - end result, the situation hasn't changed.)

(L K) Miller motion. 

Fails.

(Seth (in Albanian)) Miller motion.

Motion passes, not that many, to an honorary Connie with Bill doing a poor Connie imitation, to something incomprehensible in Albanian plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
