\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 22, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(JAH) Move to approve the minutes as twisted, like my pretzel.

(BPS) Friendly amendment- twisted and half-eaten.

Motion seconded, passes a twisted and half-eaten bunch of 10-a twisted Seth-a twisted cow and a couple others +Spehn.

\goto{Committee Reports}

(DSK) Cornelia Otis: we lost Al Gore.

(BPS makes an addendum I couldn't catch. Seth continues with some other random comment about delegates.)

(BPS) Cornelia Otis 2: Today the IRS revoked the PTL's tax-exempt status.

(LAK) Jourcomm: I'm going to try and get out a TZ for R/O Week, so before you leave, give me things or I'll come and find you and break your legs.

(HAM) Pseudo-Picniccomm: the invitations are almost ready to go out, and it looks like we have on the order of 280 members, plus or minus 15.

(BPS) Sitcomm: last night CBS had a documentary (48 Hours) where they talked with Isaac Asimov about the current state of NASA. Asimov has gotten very old recently- a quantum leap. This show was in the timeslot of Asimov's co-creation, Probe.

(BPS) Sitcomm 2: there was indeed a new Next STrek last Saturday. Boy, is Jean-Luc Picard a slow on the uptake twit. Who did he blackmail to get command of a spaceship? At least James Kirk knew how to talk to demented computer systems.

(BPS) Mortcomm: ding, dong, the witch is dead! Louise Nevelson ("Transparent Horizons") croaked, finally.

\goto{Old Business}

(BPS) Update on UMass Amherst- they decided to throw out the results of the election which put an avowed communist in office as co-president. The reason they gave for this was that their constitution did not allow for a co-presidency.

(S??) Update on last week's story on the DJ- apparently he's giving all the money to charity, because direct solicitation on the radio is apparently illegal.

(BPS) It was a guarantee that a science fiction film would get Best Visual Effects. The only nominee (besides Innerspace) was Predator.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: a 15-year-old in Pennsylvania came home with a bad report card and took 74,000 from his father's wall safe and went to Ocean City, MD instead of showing his parents the report cart. He spent/lost about 21,000 of it before store owners called the police. A few of his instant friends are under arrest for having ripped him off. His father is "a little upset." Article attached.

(S??) Minicult: someone's trying to cash in on all the excitement over the two-headed murder case- there is now a similar story about a two-headed woman in Nigeria. She's pregnant; one head wants to have the baby, the other doesn't.

(CH) Minicult: Weekly World News- "UFO aliens made us a success as rock musicians." Article attached.

(CH) I guess Ken and Janice will be at the picnic.

(S??) Move to put Transparent Horizons under a large banana colored tombstone.

Motion dies.

(CH) Move to telepathically transport Transparent Horizons to the rabbit creatures on Pluto.

(S??) Amendment- and put a banana colored tombstone in its place.

(DSK) What? I think I just lost the motion.

(BPS) Move to note we just had a long inarticulate motion that involved the word banana.

Motion seconded, passes enough-not enough-definitely not enough +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted in absentia (Happy Steer Roast!),}
\centerline{Val Stark, Onseck}

\end{document}