\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 8, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected by pseudo-onseck RJG.

(SSDT) Move to approve the minutes as stellar.

Motion seconded, passes 8-less than 8-6 +Spehn.

\goto{Committee Reports}

(RJG) LHE Report: Finboard sucks. Finboard for Den Mother     .

(Donna) Move to displace the nova to Finboard. Passes by skinnerial decree.

(DSK) Cornelia Otis: we lost Paul Simon and Pat Robertson this week.

(LAK) Jourcomm: write for TZ. Real Soon Now, honest.

(DSK) Sitcomm: Max Headroom is coming back on ABC Thursday nights against Cosby.

(BPS) Sitcomm2: On Probe last night they dealt with the alleged visitation of an alien. The episode title was "Plan 10 from Outer Space."

(DSK) Motion to censure Probe permanently. Seconded, passes by decree.

(HAM) Moocomm: Innerspace tonight, Excalibur Sunday.

(CH) Sitcomm: Season finale of Beauty and the Beast tonight. Will they have a kiss?

(BPS) Awardcomm: the 1988 Edgar Award nominations (mystery's equivalent of the Hugo) are out. One of the nominees for best paperback original novel is Bimbos of the Death Sun.

(CH) Moocomm: I saw Vice Versa. It was pretty good.

(BPS) Related Moocomm: 18 Again opens today; yet another body-switch comedy, this one with George Burns.

(KJ) Moocomm: I saw Beetlejuice; that was pretty good also.

\goto{Old Business}

(BPS) A while ago one of the nightclubs in Kenmore Square was going to convert to a Photon game. They got over the community fuss about it, then the owners changed their minds and decided to make it a modern pool hall with 37 tables.

OBA: um, us, uv, ur.

\goto{New Business}

(HAM) Minicult: on April 1, someone replaced Eddie's login message with "Hi, I'm Eddie, your shipboard computer, and I'm feeling just great..." This week someone decided the message was inappropriate and removed it. The system crashed; it hasn't been happy since. The disk drives don't work, the modems don't work. He's not feeling great anymore.

(BPS) Minicult: the Massachusetts no-smoking law goes into effect soon.

(BPS) Intensely morbid Minicult: last weekend in North Carolina, an experienced skydiver with hundreds of jumps to his credit was killed when he jumped out of an airplane at about 10,000 feet and had apparently forgotten to put on his parachute. He was preoccupied with video equipment he was going to use to film other jumpers and didn't realize the weight on his back was not his parachute.

(DSK) Addendum- the video shows him spinning around and around and then reaching for a ripcord that wasn't there; I saw it somewhere.

(Adina) Minicult: I have a new job and a real office with a door and everything.

People sing two verses of Rabbits and are interrupted by a phonecomm. They continue singing as DSK talks.

A Miller motion is made and fails. Made again, passes 15 and a powder puff-nobody, especially not Connie-2pi +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1724 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}