\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 29, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Rob Gates, LHE and Pseudo-Skinner, presiding.

Nonexistent minutes are read by the nonexistent Onseck. Because there are no minutes, there are no motions concerning them.

Non-motion is seconded, non-passes lots-a couple-a sheep plus one +Spehn.

\goto{Committee Reports}

(LAK) Jourcomm: I want 700 bucks for a publishing seminar in St. Petersburg, Florida.

(RJG) LHE Report, addendum to Jourcomm: no way, Lisa.

(HAM) Pseudo-Panthercomm: supposedly, we're doing inventory February 14. Everyone should come and help.

(LAK) Pseudo-Onseck Report: We got a letter from The Alpert. He's being bored in Pennsylvania, and he liked TZ. He protests using the sport model gavel for the Gavel Toss and coconut bash. We should use the original gavel to maintain purity of tradition.

(S??) Moocomm (time warp from Old Business): Robocop is playing Reg Day, and Heavy Metal on Sunday.

\goto{Old Business}

(LAK) The Marathon was.

(HAM) We once again have no minutes. Scott failed to delegate anyone to take over the meeting, and in general, Scott's not here.

(S??) Motion to commend the Skinner as well-organized.

Survey says: naahhhhh.

OBA: um, us, uv, ur.

\goto{New Business}

( ) Motion to give LSC a resounding hiss for not showing Animato for the second year in a row.

A few yeahs and hisses are heard.

(HAM) Amendment- motion to hiss Seth (S??) when we're done for not knowing what Animato is.

Motion seconded. A few-no one-a sheep plus one plus a pig +Spehn. Motion passes, although not by very much.

(HAM) Motion to commend Rob for covering up his banana colored t-shirt with a blue sweatshirt.

Motion seconded, passes lots, lots, sounds good-not even a free silver-free silver +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1705 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}