\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 1, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of the previous meeting read and corrected.

(VHS) Motion to approve the minutes as being read just in time before Jennifer got here.

Motion seconded, passes everybody except Jen-Jen and a speech-2 +Spehn.

\goto{Committee Reports}

(DSK) Cornelia Otis: Daylight Savings Time on Sunday; set your clocks ahead.

(DSK) Cornelia Otis2: Richard Gephardt. Bob Dole.

(DSK) Cornelia Otis3: the Justice Department, except for Ed Meese.

(BPS) Cornelia Otis4: remember, a vote for Jesse Jackson is a vote for George Bush.

(BPS) Cornelia Otis5: the commies are taking over UMass Amherst. (And there was much rejoicing from the MITSFS.)

(VHS) Onseck Report: after a trip home during Spring Break I'm now back to hearing sort of in stereo, hopefully permanently.

(VHS) Onseck Report2: the Onseck traded in the engagement hat she received about the time of the MITSFS Picnic two years ago for the real thing.

(VHS) Onseck Report3: the Onseck is going to spend next year in Europe before coming back here with a new name, thus disrupting the Star Chamber.

( ) Star Chamber goes nova, film at 11.

(S??) Moocomm: Princess Bride tonight, LSC.

(HAM) Lenscomm: (Tarl objects and shuts himself off. After a few minutes Tarl is revived.)

(HAM) Lenscomm: click! No, still working. The pictures of Rob and the Wastebasket are in fact here. I did get a new toy, but not an orc; it comes from some nameless place like Taiwan, but it refuses to admit where. (Tarl, apparently offended, shuts off again. The Onseck bribes him with a new tape and the meeting continues.)

(HAM) Lenscomm yet again: my new toy, which doesn't have a name, is in color, which is very important since of course I'm colorblind.

(BPS) Pseudo-VGG: Gustav Hasford, an Academy Award nominee for adapting his novel to the Full Metal Jacket screenplay, is wanted by the campus police at California Polytechnic State University, who discovered nearly 10,000 library books in storage lockers he had rented. Hasford's lawyer claims most of the books were purchased at library sales.

(DSK with JAH) Move that this man never be allowed to leave the MITSFS.

\goto{Old Business}

(BPS) It looks like that alleged proof of Fermat's Last Theorem is falling apart.

(GF) At Lunacon famous pro Janice Eisen will be on two panels, one accompanied by someone called Ken Meltsner.

OBA: Usual Scott-waiting-for-the-um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: starting today, Northwest Airlines is banning smoking on all flights in North America. Also, Supercarrier had a long detailed explanation of how a stealth ship works, and the captain interrupted him and said "OK, so he's got a cloaking device."

(DSK) 23rd century meets 20th century, film at 11 after the nova.

(BPS) Minicult/pseudo-LHE Report: some people have been coating checks with a substance that makes them dissolve. They open an account and deposit a large out-of-state check. The bank waits to see if the check is returned for lack of funds, but the check disintegrates en route to the clearinghouse and they don't hear anything and assume it's OK. The check-passer withdraws a large sum of money and disappears. Article attached.

(HAM) Motion that the LHE get us a bunch of that stuff. Passes by skinnerial decree.

(BPS) Minicult: Prudential had insured a shipping company that went bankrupt. They claimed they were owed 93 million. This turned out to be a typo; they were actually only entitled to 92,885. Prudential was given the proceeds from the sale of the ships (67 million) minus 11 million for the typo. Article attached.

Rob throws a can at the wastebasket (the real one this time) and misses. He hits Scott with the liquid in the can. The can also misses (just barely) Paul, who was entering the library but changed his mind. Rob is commended for his timing.

(Names removed for their own protection) Motion to censure the skinner for letting Rob wet his pants.

( ) Rob wets Scott's pants, film at 11. (BPS) After the nova; you always open with the local fire.

(RJG) Move to roast a banana over the nova.

Motion seconded, passes 12-nobody?-1 or 2 feet +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1721 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}