\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 23, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Herb Miller, President and Skinner, presiding; Donna Bell, Onseck, recording.

Minutes of the previous meeting mutilated by the Onseck and corrected by the locals.

(CH) Move to approve the minutes as mispronounced.

(Unenthusiastic chorus of "nahs," much
to the relief of the Onseck.)

(BPS) Move to approve the minutes as MITSpronounced.

(HAM) I like that! Second.

Motion passes, many-not so many-Seth saying dumb things (Dumb things translates into
"insert favorite animal noises.") +Spehn.

\goto{Committee Reports}

(HAM) Charcomm: For some unknown reason today, like maybe I didn't get enough sleep last night, I decided that I would find out if despite all the high tech exterior gloss, Lobdell is still the same Lobdell that we've all come to know and um... something. And indeed, the soda was flat as soon as it came out, and warm; there was no ice available. The pre-cooked hamburgers, which, as opposed to sitting in a vat somewhere in sight is now sitting in a vat somewhere out of sight so you don't know how long they've been sitting there, were burned, cardboard-like, and completely dried out. And the rolls were burnt. The same old Lobdell we all remember.

(BPS) In short, it is a vast improvement over the previous Lobdell.

( ) The clam chowder wasn't too bad.

(HAM) In my hamburger? That's what it was.

(BPS) FameComm, sort of: I wrote an article in the previous TZ savaging Isaac Asimov. He responded with an editorial in the October 88 issue of his magazine savaging me. The sad part is that he was right. I sent him a letter of apology, and also mentioned that I was going to publish that letter of apology in the next Twilight Zine. I got a letter from Isaac back: "Dear Mr. Starr, Your fine letter of apology to me, personally, is all I need. If this letter reaches you in time to stop you from running it in Twilight Zine, please stop. I see no need whatever of you flagellating yourself in public. I'm not that hurt." It goes on from there. I am heartened to notice that Mr. Asimov apparently typed this letter himself, by hand, with lots of mistakes.

(HAM) I was going to say, is it typed the same way that Donna pronounces things?

(SST) No, words are switched.

(BPS) We11, they aren't switched so much as crossed out. He changed his mind about his phrasing at one point, crossed out what he'd written and wrote in the correct phrasing by hand.

(HAM) Wow. I bet if we had Donna read it, it would sound right.

(BPS) It's a very short note, I suppose I should read the rest of it for those interested. "I must simply explain what it was that hurt me. Taking credit that is not mine strikes me as unethical behavior, and I try as hard as I can never to do anything unethical. (We are all human of course, and I may tumble sometimes- to my own utter humiliation.) It bothered me that you assumed I was unethical and accused me of it without ever checking with me to hear my explanation. Somehow, I don't think you'll ever do this sort of thing again, with anyone. And that's good enough for me. I don't need anything more." And it's signed Isaac Asimov, in handwriting almost as bad as mine.

(HAM) That's pretty amazing, I mean, that the handwriting is that bad.

(SST) Den Mother: Formal note that the first (sorta), second, and third floors of the Student Center are actually open. I think they look pretty nice, except that they look a lot like the medical department, but with green trim instead of purple.

(HAM) It gives you the right kind of feeling. I mean, if this were the medical department, you wouldn't have to go anywhere after you ate. It's a false sense of security.

(L K) And you can compare the shade of their faces to the green colored tiles.

(Seth) I do give the architect some credit; on the second floor, there is a very nice lounge that is just perfect for sleeping in.

(HAM) It would be interesting to see how long those nice chairs stay there.

(BPS) An addendum, pointing out something that Susan originally noticed. Under the new architecture, you can now throw someone over a railing and he will fall for two stories. This is a one story improvement over the previous architecture of that area.

(Seth) Shall we have a pool to see when the first person will commit suicide?

(HAM) We had a pool. It got taken away.

(SST) I think it really is three stories because the second story is equivalent to two in height.

(BPS) Okay. A long way. A longer way than it used to be.

(HAM) Interactivities Liaison: As some keyholders may know, there is currently an Assassin's game going on. Unfortunately, at times, there is a heavy overlap between MITSFS and the Assassin's Guild.

(L K) Like all the Star Chamber.

(HAM) MITSFS has been declared a no-game-zone. What that generally means in reality is, certainly no combat/game-action may take place in here. If anybody is in here during your hours, involved in the game, and they're getting too loud or starting to annoy you, feel free to ask them to step outside. If they continue to cause trouble, you have my permission to beat them over the head with the gavel. The exception to this being, of course, myself.

(BPS) You mean Lisa's fair game.

(HAM) Lisa's running the game.

(BPS) Sitcomm: Multiple entries of Star Trek relevance. First of all, two McPaper entries on Next STrek regarding new cast members. Whoopi Goldberg...

(Piercing laughter, courtesy of Connie, interrupts Bill and swamps Taro.)

(BPS) ...Whoopi Goldberg has been cast in the recurring role of Guinan, an alien humanoid hostess of Ten Forward, the Starship Enterprise's newly created set. It is a recreational lounge that will let viewers see the characters off-duty. Apparently the holodeck isn't good enough; they now have to have a recreational lounge.

(HAM) I guess... the recreation lounge supposedly doesn't break as easily as the holodeck.

(BPS) Even of more interest, the doctor, who will be replacing Dr. Beverly Crusher since Gates McPhadin is leaving the series, is Dr. Katherine "Kate" Pulaski, and will be played by Diana Muldaur. She now will be tied with Muszhel Barret Roddenberry for most different roles played on Star Trek- namely three. Throw in Mark Lenard also if you want to count the movies.

(SST) There's another multiple roles as alien creatures in costume.

(BPS) You mean Jan-Oats Pershorka? That was mostly stunt work- I'm not counting that. He was inside a lot of the "monster" costumes.

(CH) Emote! Emote, Jan-Oats! Crawl threateningly... now crawl piteously! Okay, good. Can it.

(BPS) Their final line in their little blurb about Whoopi Goldberg says "Goldberg says she's always been a trekkie."

(HAM) What a frightening concept.

(BPS) What a believable concept. Other thing on Star Trek, related, some car company has an add featuring Melanie Shatner, the daughter of William Shatner, in which she talks about how cool the car is- driving just right for the next generation. And in the tagline of the ad, William Shatner just materializes in the passenger seat; doing Captain Kirk, he just says "steady as she goes."

(Insert moans and laughter from rest of room.)

(BPS) It sounds sick, but it pointed out something I hadn't really realized before, and that is Shatner is really comfortable with the role of Kirk and he's doing it really well. You got the impression that was Admiral Kirk and not William Shatner. He's really come into the role over all these years.

(DYO) How are the ratings on that program (Next STrek)- is it doing well?

(BPS) For a syndicated show, it's a phenomenal success. It is inspiring a whole slew of syndicated series next year, there's a War of the Worlds, a Superboy, Twilight Zone is going to syndication, Friday the Thirteenth is going into its second season, Freddy's Nightmare is just coming out. And almost all of this is because Star Trek is, by syndicated values, an incredible success in cost vs. profit.

(HAM) Perhaps it's a good thing my TV set blew up the other day.

(Seth) Sitcomm: Sunday, debate between dweeb and other dweeb.

(BPS) Sitcomm: I've been watching NBC's Olympic coverage with Bryant Gumble with his brow incredibly furrowed. He's beginning to look like Lt. Warf's long lost brother.

(SST) Somebody-else's Den Mother or Possibly Den Children: there is a full page ad in the
Herald. It contains a clip of something from Boston Magazine. An example of biting the hand that feeds you. "In a local revival of Mommy Dearest, the Pieminister Plastic heirs apparently thought nothing of firing their mother as chairwoman of the board of the family's first Phillips corporation, and then having her escorted under armed guard from the Acton offices of the family's magazine, The Rob Report." The mother has taken out this enormous ad here, and also in a couple of other papers I believe. The ad says "When a mother gives life to a child, she is filled with secret dreams for that child's future happiness and success. This is how I felt with the birth of each of my five children. But in my own worst nightmare, I could never have imagined what my children would become or how poorly they would treat me. Unfortunately, the facts reported in Boston Magazine are true. On at least one occasion, Boston magazine has given an award of worst for one year and then best the next. Maybe there is hope for my kids.

(BPS) Move to send this woman a letter to the effect of "What ye sow so shall ye reap" given that she apparently raised them and they turned out like this. There's a cause and effect probability here.

(Time Warp from some as yet unspecified time in New Business.)

(BPS) Famecomm: MIT's move into NCAA division three football made headlines in McPaper. The Thursday edition, the top story (banner headline across the top and an article underneath it) of their sports section was just about MIT, for the first time since football was voted out in 1900, is back in the NCAA level. They did mention that we've been doing the club level for a bunch of years now. And they gave fair amounts of stats on the team: the average height, weight, etc. of the players. Basically, it was not at all snide- it was your normal story in which they mentioned that, no, of course we don't expect to do all that well, MIT has never been an athletic powerhouse and we don't have football scholarships. They did mention MIT's SAT average of 1380. The blood is thin.

(End of time warp.)

\goto{Old Business}

(Seth) I'm getting old. More details in New Business.

(HAM) Old Business Algol. Um, us, uv, ur.

\goto{New Business}

(Seth) My 19th birthday will be Sunday...

(Extremely loud exclamation from Bill, followed by an imperative, also from Bill, for Seth to,
and I quote, "get out of here!")

(Seth) Well, anyway, I'm having a little birthday party on Saturday night, and I suppose you're
all invited.

(BPS) But you're not going to tell us where it is.

( ) ...or when or anything...

(Seth) It's tomorrow, five o'clock at night, at my apartment in scenic Somerville- 60 Sommer Street, Apt l. Bring your own munchies and some sort of recreation device. It's relatively informal.

(HAM) Minicult: If anybody saw today's Tech, the pricelists for the year are out. Pot is 200 dollars an ounce.

(PJN) LSD was a dollar a hit.

(HAM) And coke was 80 dollars a gram. There was a whole bunch of articles about drug use at MIT. And someone put in a nice column of the most commonly used drugs at MIT in order, including alcohol, and current going market rates.

(SST) It reads like a shopping list. It also lists advantages and disadvantages, and in some cases, where to get the stuff.

(SST) Other thing from the Tech. This is an ad and I didn't think we were allowed to have ads like this. It's attacking another business that is not a competitor. It's from the Cambridge Trust Company; it says "Where to re-COOP your losses. If you need to replenish your supply of cash after shopping at the MIT Tech COOP, you should open an account, blah blah blah. Remember, when the COOP leaves you at a loss, you can cross the street and re-coop instantly."

(Skinner snaps his fingers, the telsey refuses- in reference to a Swiss army knife.)

TIME WARPED FROM THE BEGINNING OF OLD BUSINESS:

(BPS) Minicult: the Rapture did not take place when it was supposed to. Apparently some born-again-Christian-type has a book out called Eighty-eight Reasons Why The Rapture Will Be In 1988. It gives precise dates of events that are supposed to lead up to the apocalypse. The Rapture was supposed to take place during the Jewish holiday of Rosh Hashanna, which was September 11th through the 13th. After that, after all of the good Christians were bodily elevated to Heaven, Israel was supposed to sign a treaty with the Antichrist on September 21st. And World War Three would break out on October 4th. The New Republic, with their usual tongue in cheek, points out that if the predictions do pan out (this was written in advance of the fact) most analysts believe that Bush will be helped by the renewed focus on defense issues, while Dukakis will benefit from a lower turnout amongst evangelicals.

(BPS) Related only in that it is also in the same issue of New Republic. From the Talahasi Bureau, a report that Republican State Representative Luis Morse of Miami has spoken out against literacy on the grounds that literacy encourages Communism. In a floor debate over a bill that would allow Florida college students to teach adults to read, Morse argues that that's exactly what Castro did in the mountains and the Sandinistas did in Nicaragua.

(Seth) This is true.

(HAM) Now there's a good reason not to elect any of the people currently running for President. They can probably all read, so they must be Communists.

(BPS) The report from Miami also mentions that a bomb was set off under a car in a parking lot at the Cuban Museum of Art and Culture in Miami. Factions on that museum's board of directors are evenly divided on the question of whether a local Cuban museum of art ought to admit that there is art in Cuba, or simply ignore it in favor of the work of the exiles. This bomb, everyone realized immediately, was a response to the museum having displayed art by painters who have something to do with Cuba.

END TIME WARP.

(BPS) As part of NBC's coverage of the Olympics, they've been doing features on Korea and Seoul in general. Apparently there is an incredibly large and thriving black market in US goods which soldiers and their wives, usually Korean wives, buy in huge quantities at the US army subsidized PXs, then sell at a small profit to middlemen, who sell at a large profit on the black market. What is particularly amusing about this is that one of the hottest or more popular items is something which is apparently the national snack food of Korea- the banana.

(C H) A slightly vaguely related item. Evidently the Korean police are looking with a very prejudiced eye towards ticket scalping. I read about one American tourist who was put in jail for five days for making a total profit of 33 bucks on some Olympic tickets. They probably wanted a bribe, so they threw him in jail when he didn't fork over, but still...

(BPS) Move to commend the South Korean security guards, including the one who tried to attack a boxing referee after he gave an unpopular decision, for wearing banana-colored blazers.

(CH) Hang-time on the motion. A related item, evidently, speaking of Korean security guards: one of them was found sneaking into a woman marathoner's room late one night while she was sleeping, and began to fondle her feet. He has been dismissed.

(BPS) Well, if you've got a foot-fetish, I guess a marathoner is sort of your ultimate dream.

(HAM) It's possible he was a communist infiltrator... did they find out if he was literate?

(Seth) Friendly Amendment- move to support MITSFS by selling black market Korean bananas.

(HAM) That okay with you, Bill?

(BPS) Fine by me by if you get caught- I don't know nothing about it. I disavow any knowledge of you or your activities. Good luck Jim.

(HAM) We can sell the literate ones to North Korea and the illiterate ones to South Korea.

(Motion crashes to floor due to gravity.)

Motion passes, all of it.

\vspace{12pt}

\noindent
Meeting adjourned, 1743 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}