\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 5, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of 2 of the previous n meetings read and corrected.

After a flurry of motions, three of which are seconded, DSK declares all previous motions go away. BPS makes a motion to approve the minutes as approved by the Comics Code authority. Passes 10-3-almost but not quite 10 +Spehn.

\goto{Committee Reports}

Phonecomm (time warp from minutes): Ring. Merryl's brother's car was stolen.

(BPS) Sitcomm: I actually saw the Skinner on that game show.

(JAH) Concomm: I got a call from someone at Brandeis' Science Fiction Club. They're putting on a smallish con on the second weekend of spring break (March 27). It's a one day con on a Sunday, 3 dollar admission fee; they're trying to round up some speakers. The only one who's confirmed is Margaret Wonderbananas. The proceeds go to charity- half to the Comic's Legal Defense Fund and half for urban development in Boston. Incidentally, the Comic's Legal Defense Fund is against a case of blatant censorship that should be fought by all right-thinking peoples everywhere.

(VHS) Onseck Report: the Onseck can hear in stereo for the first time in 12 years.

(BPS) Sitcomm: One Life to Live is advertising that one of their plotlines will involve time travel.

(LAK) Addendum- I think he wakes up.

(BPS) Addendum 2- Bobby Ewing is still dead on Knot's Landing.

(S??) Whooshcomm: Galileo will have about 20 pounds of plutonium. If this goes the way of Challenger, we're in trouble.

(HAM) Addendum- Galileo's trying to get to Jupiter, but they're sending it towards Venus first, then back to Earth, then to the asteroid belt, then back to Earth, and then to Jupiter.

(BPS) Cornelia Otis: the town of Emmetsburg, Iowa held their quadrennial Cesspoll- they told people when to flush their toilets in support of a given candidate. Mike Dukakis won on the Democratic side, registering a one foot drop in the town's water tank. On the Republican side, Dole got a 0.8 foot drop.

(DSK) Cornelia Otis 2: Iowa caucuses are next Monday.

(BPS) Cornelia Otis 3: apparently General Noreyega and Lt. Col. Oliver North were conspiring to frame the Sandinistas, except that Noreyega got paranoid of being double-crossed, so he double-crossed North first and kept the weapons himself.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

(CAH) Minicult: from the net- How many Enterprise crewmen does it take to change a lightbulb? Answer: nine. Scott calls in from Engineering to say the bulb doesn't work. Kirk sends McCoy to check it out. McCoy examines the bulb and pronounces it dead. Kirk leaves Sulu in charge ("You have the com, Mr. Sulu") while he, McCoy, Spock, and three red-shirted crewmen beam down to the nearest planet to look for more lightbulbs. The three red-shirted crewmen are immediately killed by the natives, who take the rest of the party captive. Kirk falls in love with the chieftain's daughter. She tells him her father is very ill. McCoy cures him and in gratitude the chief lets the landing party go and presents them with a lightbulb as a token of his esteem. Spock figures out a logical way to transport and install the lightbulb, Uhura notifies Starfleet Command that everything is under control, Kirk returns to the bridge, and the Enterprise continues on its five year mission, while McCoy makes an exasperated remark to Spock.

(S??) claims he has a similar joke about the Democratic presidential candidates, but we are thankfully spared.

(BPS) Minicult: Walt Disney's Epcot Center is seeking applicants from foreign countries who can speak the language fluently and are able to authentically present the history, customs, and culture of their homeland. Starting pay is 4.65/hour, and transportation and relocation are the responsibility of the applicant.

(DSK) I could make more than that at McDonald's.

(BPS) I'm about to be unemployed.

(S??) Motion to present the Skinner with a banana colored Craftmatic Adjustable bed.

(BPS) Amendment- motion to put the Skinner on a banana colored Craftmatic Adjustable Bed.

Motion seconded, everybody-Connie-maybe ten but less than everybody +Spehn (all on the Craftmatic Adjustable Bed with the Skinner). Motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1728 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}