\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 12, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

The Onseck and the minutes are absent yet again.

(RJG) Move to cancel going through the motions of canceling the minutes.

Motion seconded, passes 20-1, Connie, and Free Silver-maybe 2 +Spehn.

\goto{Committee Reports}

(S??) Cornelia Otis: Gary Hart.

(BPS) Skinner Report: the Skinner's feet have no clothes.

(DSK) Cornelia Otis 2: today has weather; there are several inches of slush outside.

(SSDT) Mortcomm: according to sources on the net, Randall Garrett is dead.

(DSK) Timecomm: no inventory tomorrow again. Inventory WILL be held March 5, three weeks from tomorrow.

\goto{Old Business}

(DSK) Andy Su called. He thought the meeting was at 5; he was wrong. He didn't mention the ravs.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult/Sitcomm: This weekend's episode of Next STrek that would have been shown tomorrow at 9 PM is being shown today at 8 PM on channel 5.

(S??) Miller motion.

Seconded, fails.

(RJG) Miller motion.

Motion seconded, passes nearly everyone-Jennie's two fingers-not nearly enough +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1706 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}