\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 16, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Philip J. Nesser, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes from the previous two meetings read and corrected.

Connie makes a motion, not necessarily concerning the minutes.

(PJN) All those in favor of Connie's motion?  Motion passes, enough to very boring, to about three or four plus Spehn.

\goto{Committee Reports}

(WDS) Sit Comm - Next Strek actually cranked out a very good episode. Star Trek does cyberpunk; they get it mostly right.

(PJN) pseudo Skinner report - You'll notice several new signs up on the door; there won't be another meeting until January 6th, the traditional time-warp which wasn't traditional last year (December 23rd to January 8th), the IAP membership are only three dollars. Read all about it at your leisure.

(WDS) Mob Comm (sub 1) - There's a New England Mobil run tomorrow; we're going to capture a load of hardcovers. Mob Comm (sub 2 - referring to myself) Boy did I get screwed over by Boston University (Summary - accepted as Transfer Student, but accepted no credit from MIT transcript from 1975-77 years.) Anyways, Northeastern is willing to give me credit for the MIT stuff so I'm going to be going to Northeastern starting the first week of January.

(HAM) Moo Comm - Tonight, Bull Duram, which isn't really anything remotely sf-ish, but tomorrow night is BIG, which sorta is. And LSC IAP schedule is out and is very heavily SF oriented. And this spring
we get exciting things like who framed Roger Rabit and The Last Temptation of George Bush. Reg Day film is Die Hard.

(C H) Moo Comm (sub whatever) - Somewhat against my will I saw My Stepmother is an Alien last week; AI rated it on a ten scale, a two, however my companion rated it a minus five. It was really really bad.

\goto{Old Business}

(WDS) Old Business - There's this amazing fascinating exhibit at the Boston Museum of Science on special effects which includes a lot of original matte paintings and a full scale mock up of Ripley and the exoskeleton vs. the alien. It apparently closes up on January 31st. You really should make an effort to see it; it's really interesting.

(HAM) Moo Comm - update on the story with the marathon. It's still going to be, but they're revising the movie schedule and it's not looking as good.

(L K) Old Skinner Report - Scott did indeed make it into Boston last week, stayed for the weekend, had a good time, left us some champagne. Now he's going to grad school in Ohio State.

OBA um, us, uv, ur \bing

\goto{New Business}

(WDS) The Weekly World News Is For Sale!

(WDS) Mini Cult - A person in Nebraska, age 19, had been charged with possession with intent to sell 49 capsules of the drug known as Ecstasy. He was acquitted because the state legislature misspelled the drug's chemical name when it passed the bill that outlawed it.

(WDS) Move to note that the correct answer to a final Jeopardy sometime earlier this week was "What is a banana?"

\vspace{12pt}

\noindent
Meeting adjourned, most heartily, 17(obscured) SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
