\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 19, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Minutes of three of the previous n meetings read and corrected.

(KJ) Motion to accept the minutes as plentiful.

Motion seconded, passes 20-pi-2 +Spehn.

\goto{Committee Reports}

(DSK) Timecomm: inventory will be held Saturday March 5. We have a shelfdex.

(S??) Pseudo-Libcomm: Someone anonymously donated a copy of John Norman's Imaginative Sex.

(KJ) We already have a copy in Special Reserve; that one will circulate.

(BPS) Mortcomm: Dr. Richard Feynman. Mortcomm 2: a housemate of mine claims that Erland Vanden '75, who played Grossburger in Stir Crazy.

(SSDT) Mortcomm 3: Lyn Carter. 4: C.L. Moore, last April.

(S??) Moocomm: Gods Must Be Crazy, Saturday.

(SSDT) People's Albanian Embassy: I saw a bumper sticker that said Albanian and Proud.

(DSK) Cornelia Otis: Pat Robertson's miracle in Iowa wasn't in New Hampshire.

(S??) Cornelia Otis 2: Babbit and Pete DuPont.

\goto{Old Business}

(BPS) There was a 31-story building that, due to zoning regulations, might have to deconstruct the top 9 or 11 stories. Recently, the NY Supreme Court has upheld a lower court decision requiring that the top floors be removed. The builder claims NYC supplied him with erroneous zoning maps.

(CH) I got a message from Judy Passman over the net. She says hi.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: two quotes from actress/singer Cher, 40, who's currently going out with a 23-year-old man. Upon seeing this person in Greenwich Village (I don't know if this was the first time she saw him or not): "I like him. Have him stripped, washed, and brought to my tent." Somebody asked her why she went out with younger men, and she said, "Because 20 goes into 40 a lot more times than 60 goes into 40."

(SSDT) From the Glob: "One diehard smoker on the Long Island RR threw a kicking and hitting tantrum when no-smoking rules took effect in NYC. The man was removed from the train and charged with two counts of harassment and criminal possession of a controlled substance (the substance was later identified as Valium).

(BPS) Minicult: from last Friday's McPaper- I'm putting an article in the blue folder about Beauty and the Beast.

(S??) There was an article in last Sunday's NY Times about family TV shows, and Beauty and the Beast was considered a very good example of such a show.

(BPS) Minicult/Sitcomm: an upcoming series about two ex-yuppies who run a daycare center had a scene in which a yuppie friend was asked if she wanted to hold a six-month-old baby. She said, "No, there are some things I just don't hold. Babies. Plutonium."

(HAM) Move to take the surplus minutes, wrap them around a banana, put them on a Craftmatic adjustable bed and send them to Epcot to accurately represent the culture, language, and customs of the MITSFS.

Motion seconded, passes everybody-stop that, Adina-not nearly enough to overturn this +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1727 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}