\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 15, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Rob Gates, Vice and summer Skinner, presiding.

Minutes of previous meeting read and corrected.

(S??) Motion to approve the minutes as abridged.

(RvdH) Motion to approve the minutes as a Bridge Publication.

Bill "nahs," Seth seconds the motion, and it fails a few-a few more-not many +Spehn.

(LAK) Motion to approve the minutes as a Miller motion. Motion seconded, passes quite a few-Seth whining-1 +Spehn.

\goto{Committee Reports}

(LAK) Jourcomm: the deadline for submitting things to TZ is August 1.

(BPS) Rubblecomm: the rubble around this desk was cleaned up by the three people who showed up Saturday to process the piles of books.

(BPS) Sitcomm: There's another made for TV movie this weekend, about a cop from 2088 traveling  back to 1988 and teaming up with his cop great-grandfather to catch a time-traveling villain.

(RJG) Pianocomm: Jay Bushman sends her regards to everybody from the University of New Mexico. She will be back in a year.

(BPS) Sitcomm2: while flipping channels I saw George Takei simulcast in a pre-STrek voyage to the bottom of the sea and a post-STrek Hawaii Five-O.

(LAK) PseudoFamecomm: a woman named Lauren Seeley called from NOVA. PBS and the BBC are teaming up to make a science fiction movie, and she talked to Scott Kitchen in NJ, and wants to come here to look for a book. Put your suggestions on the list by the desk.

(BPS) Deadzonecomm: Student Center shuts down tomorrow 7 PM-7 AM.

(LAK) PseudoSkinnercomm: Herb's still wasting away in Philadelphia.

(GF) Mortcomm: E. Hoffman Price, who until a few weeks ago, was the oldest living/still functioning science fiction writer.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

(S??) Minicult: a guy in Oregon got a new phone calling card that advertised it was super-secure because the 4 digit security code was not printed on the card. Among the card's new features was a magnetic strip on the back, allowing for "extra convenience;" you could just slide it in the machine and not have to enter your password or security code.

(BPS) Carrie, the musical, is officially the most expensive flop in Broadway history at 7 million dollars for 16 performances. But Stephen King liked it.

(BPS) Minicult: SFchronicle had a letter from the lawyer defending Lyndon LaRouche- the government response to LaRouche's claim he had begun to uncover the Iran Contra scandal in 1985 was to claim in open court that the defense theories were science fiction. They then filed a memorandum which described the theories as "Orwellian fantasies." After a time, a prosecutor called the defense theories "Ludlum fantasies." The lawyer said he thought the change from Orwellian to Ludlum meant that the story was getting closer to the truth, but the quality of their prose has fallen dramatically.

Phonecomm: Ring. It's Adina.

Phonecomm: Ring. It's Adina again.

Motion to create a Bush/Banana ticket is made by combining several comments. Motion seconded, passes many-not quite enough, even though it's unfair to bananas-a small farm +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully, if illegibly, submitted,}
\centerline{Val Stark, ex-Onseck}

\end{document}