\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 7, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous meeting decimated by the Onseck with help from everybody.

(SST) Motion to approve the minutes as shorter than Pinkdex.

(HAM) Motion passes, nearly as long as the minutes, to no-one, to almost no-one, plus Spehn.

THUD!

(i.e. Herb, being Herb, decided strike the gavel with the block.)

\goto{Committee Reports}

(BPS) Sit Comm sub Several - The syndicated modern TV series War of the Worlds, will premiere this weekend. The old and somewhat revered, very strange British SF series Blake's 7 is being run on channel two, Sundays at eleven pm. The second season of Star Trek - The Next Generation is projected to open sometime in late November, around Thanksgiving. The revival of Mission Impossible should begin on October 23rd.

(SST) Nasa Comm - The Commander of the latest mission that came back down in one piece, Hauck, used to work at the MIT reactor.

(L K) Banana Comm - When the Skinner, the Vice and I were grocery shopping the other night, we found a whole bin at Heartland of bananimals including a banacorn (unicorn with a banana horn), a banabear (koala bear grasping a banana), and a banabird (parrot with a banana beak).

(BPS) Whoosh Comm - The Shuttle Discovery launched, did its stuff, and came back down with no serious problems.

(HAM) Panther Comm - We finally have the fuzzy account to do the new Pinkdex on.

(BPS) Cornelia Otis - Various Republican Bigwigs are claiming that Dan Quayle won the debate against Benson on Wednesday night.

(Time Warp from New Business)

(L K) Moo Comm - Last Saturday The Princess Bride premiered on both HBO and Showtime.

(BPS) Moo Comm - Alien Nation opens today.

(HAM) Phone Comm - We still don't have a working phone.

(End Time Warp)

\goto{Old Business}

(SST) [murphle] - In discussing Next STrek, it was pointed out on the net that we know of another ship that has a black bartender and a bald captain and one of the crewmembers kids running all over, and a doctor that used to be married.

(Groan. For those uncorrupted by bad television, the vessel's name was The Pacific Princess; the name of the show will not be mentioned.)

(HAM) Olympics Side Note - NBC had Gene and Roger review the Olympics.

Old Business Algol. um, us, uv, ur \bing

\goto{New Business}

(BPS) Mini Cult - MacPaper article - see attached.

(BPS) Move to commend the banana colored painting on the railings down on the first floor.

Motion passes, not so many, to an unenthusiastic few, to even more unenthusiastic, plus Spehn. \bing

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
