\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 2, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Derrick Kong, Pseudo-Onseck, recording.

Minutes of the previous meeting read by the Pseudo-Onseck and corrected.

(WDS) Move to approve the minutes as ignoring Robert.

Motion passes, many many not including Robert, to still not Robert, to not Robert plus Spehn.

\goto{Committee Reports}

(HAM) Skinner Report - The shelves that you don't see right there where Mike Earl is sitting, those amazing looking shelves that aren't here yet, will be not here for a bit longer. We also finally got reimbursed for our New England Mobile run, after Rita left the check sitting on her desk for two or three weeks. I think that Rita is now our new den mother, again, replacing Bar and Bar.

(PJN) LSC Sucks/Moo Comm - LSC decided to cancel the SF marathon over IAP for this year because of financial reasons.

(WDS) Sit Comm - The second season of Star Trek - The Next Generation has begun, and it's every bit as lame as the first season.

(HAM) Addendum to that - Having had Jesus last week, this week we get to look forward to the usual nameless entity that doesn't exist, and next week once again we get to see Data play Sherlock Holmes.

(L K) Jour Comm - TZ real soon now.

(WDS) Con Comm - Reader Con was two weeks ago.

(Time Warp from New Business)

(Connie) Sit Comm - There's a show on Sunday mornings at nine-thirty a.m. on channel 38 called My Secret Identity.

Phone Comm - RING! Susan Tucker calls asking about a dinner trip.

(Connie) My Secret Identity: It's a Canadian syndicated show, it's about this kid who accidentally got secret powers in an experiment that the friendly genius scientist next door was doing.  I really recommend it.

(HAM) Sit Comm - Next week the two hour special on Mystery on channel two, they're doing Hounds of the Baskervilles.

(Larry) The Wall Street Journal continued its series on what's going on in what it fondly thinks is the real world of comics by having a front page article on the Batman movie and the fact that it is not being well received by comic fans.  The Wall Street Journal really doesn't have a clue as to what's going on, as among other things, they apparently do not understand the distinction between Batman, the T.V. character, and The Batman, the grim avenger that comic book fans know and love.

(End Time Warp)

\goto{Old Business}

(HAM) Phone Comm - I had one of my suite roommates come up to me earlier this morning and offer to trade rooms with me because he's the person who's phone number is listed as my phone number in all the Student Directory's as contact person for MITSFS and apparently he got about three phone calls a day looking for me for things about MITSFS.

(Seth) Mini Cult - Remember the great Internet worm? Jean Spafford of the University of Purdue put out a technical report on it, and being such a nice guy, made it available online by anonymous ftp to everybody else who was on internet.  Naturally there were so many requests for it that Purdue University had to close down its Internet notes. 

OBA um, us, uv, ur, \bing

\goto{New Business}

(WDS) Weekly New York Times Report - Last Saturday, that would be the November 26th Times, they had an article about Cyberpunks that was inspired by Mr. Morris and his magical worm, but they're talking about the underground hackers and so on. And I quote from the article here: "The hackers themselves, as well as some social scientists, have begun to use a new term 'cyberpunk' to describe the members of this underground. It is a reference to a popular Science Fiction genre that deals with an intersecting world of high technology and outlaw society." The article will go in the famous blue folder.

(Seth) Mini Cult/Weekly World News Comm - "Elvis Has A Twin Brother - And He's Alive."

(WDS) Mini Cult - From Orlando, Florida.  "Film captured parrot, and caught the burglars, too." (see attached article.) sub two - "Stolen Art Found." (also attached.)

(Seth) Mini Cult - There is a new organization starting up in the area for people who are upset by all of the hype and commercialization surrounding "The Holiday Season" known as the Grinch Army Faction. We will be caroling in front of room 9-150 starting at about a quarter to eight tonight.

[Connie arrives amidst much clapping and cheers]

(WDS) Mini Cult - vaguely related to Sit Comms, whoever the advertising agency for Honda who built their full scale mock up of the B-2 so they could wheel it out before they air force wheeled theirs out - they had the engine space too far apart. Other than that, they seem to have nailed it perfectly.

(Connie) Sort of a Mini Cult - I was dupping several tapes of the panel at Reader Con, and while most people sound like chipmunks, Darrel Switzer sounds like a chipmunk on speed.

(Connie) Adina won't be here today. She had her wisdom teeth out on Wednesday.

(WDS) Move to note that Adina probably can't eat anything more solid than a banana.

Motion passes lots of people who really want this meeting to end, to Connie (herself) yelling "No! Free silver", to Robert making yellow noises, plus Spehn! \bing

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Pseudo-Onseck}

\end{document}
