\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 11, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jennifer Hawthorne, Vice and Pseudo-Skinner, presiding; Val Stark, Onseck, recording.

Minutes of the previous 2 meetings read and corrected nervously by the Onseck as the Vice swings her whip and threatens to use it if the minutes refer to her as "Connie" one more time.

( ) Motion to approve the minutes as sounding a lot like Connie.

Motion seconded, passes "a large number of turkeys"-no turkeys-3 +Spehn.

\goto{Committee Reports/New Business}

Note- the confusion as to what this really is doesn't matter, since half the meeting is interminable time warps anyway. Reports listed as appeared.

(S??) Cornelia Otis: Gary Hart. Jack Kemp.

(JAH) Moocomm: LSC Witches of Eastwick tomorrow.

(BPS) Sitcomm: I watched both "episodes" of Probe. It was like watching two different TV shows- obviously an attack of Roddenberry disease. Asimov co-created it, but had nothing else to do with it. Did you realize that (according to the pilot) liquid nitrogen exists at -300 degrees Centigrade, 27 degrees below absolute zero?

(VHS) Onseck report/old business: not only am I back to hearing in mono, but I am now allergic to every antibiotic known to science.

Time Warp From Much After Herb Was Albanianed:

(HAM) Lenscomm: It looks like probably next week I'm going to buy myself a Gork. (Or Dork, or something like that. -VHS)

End Time Warp (Actually, the time warp was not ended until several New Business items later.)

(BPS) Cornelia Otis: At Galluadet University, which is the most prestigious university for the deaf and hearing impaired in the country, in 127 years, they have never had a hearing impaired president. The presidency became open, 2 deaf and one not deaf persons applied, and the hearing person who did not even know sign language was given the job. The students protested, and after 5 or 6 days the new president has resigned.

HAM is Albanianed by pseudo-skinnerial decree, and there is much rejoicing.

(LAK) Jourcomm: write for TZ; I'm going to try to put it out real soon, like over the summer.

( ) Moocomm: Next Friday, the Brattle theater will be showing three films the Onseck has no idea how to spell- the "Coydermass Trilogy"?

Same( ) Musiccomm: Blind Idiot God will be playing in Jamaica Plains; they do music based on Lovecraft.

(BPS) People's Albanian Embassy: On Jeopardy a couple of days ago, the answer to a question was Albania.

(Malcolm Y) Minicult-

(JAH) This is Committee Reports. Any more committee reports?

(BPS) Cornelia Otis: Today Robert "Bud" McFarlane pleaded guilty to four misdemeanors of lying to Congress. Stay tuned for my indictments, etc., which I predict Reagan will pardon the day after elections.

\goto{Old Business}

(BPS) Andy Gibb and I are both thirty years old. He died of natural causes yesterday, therefore I am old.

(BPS) Last Sunday, the Travellers building fall down, go boom.

(Malcolm Y) RandomDestructioncomm: (JAH: Now we're in Old Business, but go ahead) George Bernard Shaw once came across the place where they parked part of the original Crystal Palace. He found that the local kids had broken all the windows save one, and if a cop hadn't come by, he would still be there looking for a rock.

(Someone adds "instead of dead.")

(HAM) We're still waiting for the alleged "pictures of Rob and the wastebasket" to come back.

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: A Japanese mathematician thinks he's solved Fermat's Last Theorem.

(Malcolm Y) Pseudo-Minicult: Some place that sells hats advertises that if a hat is ever lost, damaged, or fails to give satisfaction, they'll replace it free of charge. One customer has a hat of this model which has been eaten by an elephant three times. He says there was no reason to invoke the guarantee; he just washed it off and wore it.

(HAM requests a time warp to Committee Reports which is not granted. Then JAH changes her mind.)

(BPS) Minicult: Once again there is a list of the greatest-ever insurance claim forms. (Article attached, see it yourself. -VHS)

(S??) Cornelia Otis: The UA activities bill.

(BPS) Old Business (without a time warp): We had an inventory that went pretty quickly.

(JAH declares that both the existent, already cancelled time warp and the one that was never there explode.)

(BPS) Also old business- the best banana-based palindrome I could find was "See, banana bees!"

(JAH) Motion to make Bill come up with a palindrome with the word banana slug in it.

Motion seconded (I guess), quite a few people-Bill's foot and most of Seth-a few chickens plus random slug noises and Seth as a sheep +Spehn. Motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 17something SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}