\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 21, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes of the previous two meetings read and corrected.

(Seth) Motion to approve the minutes as having no tails at all.

Motion lays there, panting on the floor, and expires.

(DYO) Motion to dispense with the reading of the minutes.

Motion passes, a few to hardly anyone plus Connie, plus Mike holding his fingers in his ears.

\goto{Committee Reports}

(PJN) LHE Report - Finboard, oh is Finboard so nice. They gave us three thousand dollars for this term. A lot of it will go towards shelves and books.

(HAM) Skinner Report - During my hours on Wednesday, the original skinner dropped in from California. He was in town on business, and said that he might be again sometime, and threatened to drop in on a meeting. He was president from 1959 to 1961.

(BPS) Sit Comm sub One - Regular series premiere of Something Is Out There tonight at eight. Its real time slot is going to be Fridays at nine. Sit Comm sub Two - A listing from TV Guide for an episode from Tales from the Dark Side: "An Egyptian mummy comes back to life to destroy those who have disturbed his tomb and is challenged to a game of strip poker by his intended victim."

(Seth) STrek Comm - There was some discussion on Netnews about Dan Quayle.  The theme was battered around that the reason Bush chose Quayle was because Quayle was the only possible candidate who wouldn't overshadow Bush.  So the question naturally arises, who would be Dan Quayle's Dan Quayle? So somebody suggested Lieutenant Riker of Star Trek, the Next Generation.

\goto{Old Business}

(HAM) We still don't have a phone. The line still doesn't do anything. I am told by various persons the line should do something but we're not allowed to complain yet because we not supposed to know that the line should do something.

(BPS) The Saturday prior to last Friday, Columbia University's football team won an NCAA football game, thus breaking their fourty-four game losing streak. The next game after that they lost again, so they're starting a new one.

Old Business Al---. um, us, uv, ur. \bing

\goto{New Business}

(BPS) Couple of Mini Cults Regarding Harlan Ellison - from TV guide for the week prior to the one expiring today, an entry about the newest new Twilight Zone, the syndicated half-hour thing. Jay Michaels Bozenski, the story editor, has said that the new zone "is not about special effects and explosions. It's about people making hard choices."  Harlan Ellison, the 1985 Twilight Zone's creative consultant, disagrees: "Mr. Bozenski's a good friend, but he is stuffed full of wild blueberry muffins. The shows that we did were more humanistic than the one-punch gimmicky amputees that they're putting on now. (Amputees?) Because they're only twenty-two minutes long." However, he is writing an episode for the series called Crazy as a Soup Sandwich. Harlan Ellison sub two. According to the media scene in the latest Locus, Harlan has signed with Chevrolet as an on-camera spokesman for Chevrolet's geo-imports from Japan. The first six commercials to be seen as thirty and sixty second spots, will be shown first on the West coast, and if successful will go nationwide. Each geo will also come with a copy of Harlan's latest book Angry Candy. I know this will get me Albanianed; nonetheless, it does give new meaning to the expression 'selling short.' THUD!

(JAH) Motion to resolve that the Skinner be stuffed full of banana nut muffins.

[Adina arrives] (A A) Plug - Everyone should come to ReaderCon, November 18-20th at the Lowell Hilton.

(Seth) Miller Motion (seconded). FAILS!

(A A) Miller Motion!

(HAM) Passes! \bing

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
