\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 22, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

There are yet again no minutes, because DSK still hasn't tried to type them up. (Thanks a lot, Scott. -VHS)

(HAM) Move to approve the minutes before Rob puts the check in.

(BPS) Amendment- approve the minutes as being put in the envelope before it was sealed.

Motion seconded, passes 15-only the LHE-1 +Spehn.

\goto{Committee Reports}

(BPS) Pseudo-LHE Report: Somebody left 2 dollars in quarters on the arm of the chair back there.

(LAK) Famecomm: Janice is now doing book reviews for Aboriginal SF, and they have a little blurb about her that mentions that she was president of MITSFS. The building she lives in in Schenectady was once a department store, and the directory is still next to the elevator, so she knows that she lives on the floor that was once the toy department.

(CAH) Addendum- Ken Meltsner is also listed under the editorial staff.

(LAK) Jourcomm: write for TZ.

(RJG) LHE Report: the books will be done Real Soon Now. I'm catching up on the checks in the envelopes.

(DSK) Concomm: Boskone next week in Springfield.

(BPS) Sitcomm 1: on Night Court last night, John Astin reprised his role as the main character's sort of stepfather. He's getting old.

(HAM) Moocomm: SF marathon next Wednesday. Predator tonight.

(BPS) Sitcomm 2: There was a fresh Next STrek last Saturday.

(CAH) Sitcomm 3: they're showing the second part of Earthstar Voyager, which stars Duncan Rigare. Maybe the second half will be better if he takes off his shirt once or twice.

(SSDT) Atomcomm: watch the Boston Sunday Herald- MIT's reactor is about to get blitzed in the newspaper. The Hub's "secret reactors" are about to be exposed, all three of them. (CAH) Did someone tell them about Mr. Fusion?

\goto{Old Business}

(DSK) Time warp from New Business: there is no inventory tomorrow, it's been rescheduled to Saturday Feb 13 due to lack of Shelfdex. Also don't panic, HGTG starting Sunday at noon.

(BPS) The chain letter going around IBM and also the deadly copy of Gostis (?) floating around reproducing itself was picked up by real world news on CNN.

(HAM) Addendum- that hit MIT last week and people have sent warnings like "Whatever you do, don't forward this letter, and send 10 letters to your friends warning them not to continue the chain."

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Miniculti: 1- from the 1/11 Glob, a team of West German physicists revealed that they had cooled a small block of metal to 12 millionths of a degree above absolute zero. The article also says that teams at MIT are working to reduce the temperature of sodium to just above absolute zero to make accurate clocks for measuring physical phenomena. 2- The biggest winner in the history of NBC's Super Password turned out to be a wanted criminal. He appeared on the show under a false name but with his real face and was recognized. When he showed up at the NBC office to pick up his check for 58,000 which he legitimately won on the show, the Secret Service arrested him.

(CAH) Minicult: there's a Minnesota based advertising agency that has several big accounts nationwide. For one of their local campaigns, they showed a Dynasty ad that showed the faces of Krystle, etc. and above them were the words "Bitch, bitch, bitch." A female college administrator sent them a polite letter commenting about what this does to the image of women. They sent her back a letter with a picture of an African boy kissing the rear end of a cow saying "Does this disturb you too?" The woman showed this to her council of women educators and they sent a letter asking if the reply was serious. One of the presidents of the advertising agency sent her an offer of a one-way ticket to Africa so she could investigate further and the other sent her a pith helmet. The Council for Women Educators sent copies of the letter they sent around to various ad clients and the agency got many nasty letters and lost at least one account.

(G F) Addendum- Time magazine printed a copy of the original letter, and if that's a polite letter, I never want to see a rude one.

(BPS) Sitcomm: from various sources, including Newsweek and McPaper- the son of a dying 83-year-old woman requested her head be removed and frozen with cryonics on the grounds that somebody someday might find a use for it. Apparently it costs 100,000 to freeze and maintain an entire body but only 35,000 for just the head. Apparently there's some legal trouble because although she was not awake and conscious at the time, nobody had declared her dead before the head was removed. The LA coroner's office wants the cryonics firm to release the head to them so that they can determine the precise cause of death.

(CAH) We got a letter from the Down Under Fan Fund in Melbourne, which sends an Australian fan to an American convention once a year. They sent vote slips for the Rogers Street Laundry Door for DUFF, which has held up a lot of fans at parties. You can send money if you want. I suggest we bring them to Boskone and put them on a table someplace. In a related fan item, the LA Science Fiction Club sent a 10-foot industrial shaft to the Philadelphia Science Fiction Club. The Philadelphia people were contributing to a time capsule of science fictional items and the LA people thought they might like it. They didn't, and sent it to NESFA, where it originated.

(BPS) Minicult: the induction ceremony to the Rock n' Roll Hall of Fame finished up with an impromptu jam, with Mick Jagger and Bruce Springsteen duetting on I Can't Get No Satisfaction, accompanied on guitar by John Fogerty and Bob Dylan, with Mike Waldorf on one side with a tambourine.

(HAM) Move to send a circulating banana to an Australian convention.

Motion seconded, passes everybody-Connie requesting the door-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}