\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 9, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Donna Bell, Onseck, recording.

Minutes not read nor corrected.

(WDS) Motion to approve the minutes as being as much here as is Scott.

Motion passes, some, to an honorary Connie plus Phil, plus some, plus Spehn.

\goto{Committee Reports}

(Seth) Moo Comm - FX tonight.

(HAM) Moo Comm - Last night there was a free preview of Working Girl, which was actually pretty funny.

(WDS) Moo Comm - My Stepmother Is An Alien, or something like that. And nobody's really sure why.

(HAM) Moo Comm - I think it's hit the theaters by now, the sequel to Attack of the Killer Tomatoes. I'm not quite sure if it's Return of the Killer Tomatoes or Attack of the Killer Tomatoes II. It shows promise of being every bit as bad as the first one.

(HAM) Moo Comm/Skinner Report - IAP Science Fiction Marathon, right now the theoretical line up looks like Star Trek IV, The Empire Strikes Back, in some order Video Drone, Attack of the Killer Tomatoes, the original The Blob, and possibly Temple of Doom for the last movie, but maybe not, but maybe Outland.

(WDS) Sit Comm/Strek Comm - Last Saturday we found out what Jean-Luc Picard does when it looks like surrendering isn't going to work; he activates the self-destruct.

(WDS) Sit Comm - vaguely related, Thirtysomething had their season opener in which as usual reality is what you make of it.

(HAM) Sit Comm - This past Thursday and repeating I believe Sunday and possibly tonight, Jeremy Brett, Hounds of the Baskervilles.

\goto{Old Business}

(HAM) Ghosts of Skinners Past - Scott Kitchen may or may not be popping in sometime during the course of the meeting.

OBA um, us, uv, ur \bing

\goto{New Business}

(HAM) Anything? Did you ever get the impression it was the end of the term?

(WDS) Motion to ride Scott out of town on a banana.

Motion passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
