\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 14, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding.

Humphrey, the Onseck banana, is sitting in for Donna, but Humphrey, lacking in voice, cannot read the minutes, so the grateful masses are spared.

(The Onseck knows why everyone always arrives twenty minutes late.)

(L K) Move to approve the minutes as as short as they'll ever be again.

Motion passes, not that many plus Seth, to even fewer including Connie, to almost no-one, plus Spehn.

\goto{Committee Reports}

(BPS) Roof Comm - After the last rainstorm, we found a minor leak near the E.T. mobile.

(HAM) Roof Comm sub Two - I went up and had a little chat with them about this, and they passed the blame onto Athena.

(Seth) Motion to send the people in charge of construction a nice big batch of fooled styrofoam.

Motion passes. \bing

(BPS) Moo Comm - Alien Nation open and nobody really noticed or cared. Sit Comm sub One - the NBC series Something Is Out There premieres next Friday at eight o'clock. The syndicated War of the Worlds thing had its two hour opening last weekend.

(C H) Sit Comm - evidently Superboy premiered last weekend, Saturday at five. Herb wishes it a quick and painful death.

(GF) Albanian Embassy - the serfs have been rioting.

(HAM) Janice sent us an Albanian Banana Comm.  "Performance Arts - Banana Power. Anna Banana performs a healing ritual with humor."

(BPS) Personal Comm Thing - Bill had a distressing experience involving cockroaches and The Mandarin.

(Time Warp from Old Business)

(HAM) Piano Comm - David Oh, a prospective keyholder, is re-writing the keyholder notes.  

(BPS) Piano Comm sub Two - On the maintenance map, there was a section of shelves, between 3 and 4, that had not been assigned. I named it pi and has gone to Sue Pitts.

(HAM) Roof Comm - I have pictures. (Of the damages caused on that fateful night when the roof leaked.)

(HAM) Almost, I guess, a Committee Report - As part of the new season of S.T.T.N.G., they are showing a special with The Cage.

(End Time Warp)

(Another Time Warp, this time from New Business)

(BPS) Mort Comm - The man who in the mid to late 50's bought The New York Inquirer and renamed it the National Inquirer is finally dead.

(C H) Addendum to that, he was an MIT Grad.

(HAM) Not anymore.

Someone is very quickly and very loudly albanianed \bing (for commenting that the man is now an under-Grad, i.e. under-ground) and Tarl is completely and utterly swamped. Minutes latter we return to find...

(C H) In the spirit of the Weekly World News Comm - Patricia the cat was smart enough to not to try and prove that cats always land on their feet. When she found herself 25 hundred feet above ground after napping in the outside wheel well of a small plane, she waited until the plane landed and the engines stopped before jumping.

(End Time Warp)

\goto{Old Business}

(BPS) You gotta take off the top nine floors. A continuing report about a building with nine floors too many. The Supreme Court ruled that even though the New York City zoning office had misinformed the builders as to the maximum floors allowed on some random plot of land, the builders still have to reduce their 31 floors down to 23. Estimated cost - nine million dollars.

(Derek) Reference to Dr. McCoy and Star Trek Five - The scene that someone, somewhere objected to is where Dr. McCoy takes his father off of life support because his father had a terminal, incurable disease.

(BPS) Addendum, apparently the title for Star Trek Five is going to be The Final Frontier.

(C H) Arthur C. Clarke - The reason it took them so long to correctly diagnose his condition as post-polio syndrome instead of Lugario's disease is because they never knew he ever had polio. His bout of paralysis in 1962 was never diagnosed as they thought it was a spinal thing.

Old Business Algol, um, us, uv, ur \bing

\goto{New Business}

(BPS) Museum of Science has an exhibit dedicated to Hollywood special effects type things. Really interesting and worth going to.

(BPS) Mini Cult - Slightly related to something time warped back to Committee Reports in that it involves airplanes - Pan Am's comment on Donald Trump buying from the Eastern Airline Shuttle and renaming it Trump Shuttle or Air or something. "We think that it's a fine name for the number two shuttle."

(BPS) Mini Cult - On the Walk of Fame in Hollywood, they've dedicated a star to Rod Sterling.

(BPS) Visual Mini Cult - see attached.  People who have seen episodes of The Prisoner will find this somewhat eerie. (i.e. Rover)

(G F) Addendum - There is a new The Prisoner comic book out.

(Nested Time Warp from Old Business via Committee Reports)

(BPS) Semi-Serious Business - did we ever get a bottom line report on the APO Book Exchange?

(HAM) No comment with some degree of certainty.

(End Nested Time Warp)

Miller motion, seconded and FAILED! \bing

A second miller motion, accompanied by a certain song.

Motion passes a few with a bunch of rabbits in the background, to not enough, to some people really off key, plus Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}
