\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 9, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Herb Miller, President and Skinner, presiding; Donna Bell, Onseck, recording.

Minutes of the previous meeting NOT read and corrected.

(BPS) Move to approve the minutes as having been eaten by a giant mutant star goat.

Motion passes a few aahs-not that many-not that many +Spehn.

\goto{Committee Reports}

(JAH) Fweekcomm: fweek, fweek. We're going to be running the Hitchhiker's Guide to the Galaxy Radio Tapes, which we have parts one through twelve of, this Sunday. The first six at 1-4; the second six from 6-9.

(HAM) Skinner Report: various and assorted things. In digging through the VGT, we dug up that poster (gestures at poster presently hanging over door) which I don't know who donated, but that looks like a good place to put it. And we threw up the Orson Scott Card poster that we found in there.

Connie mumbles something; could be approval, could be disdain. The skinner tries not to hear and Tarl garbled it anyways.

(HAM) Our ex-skinner from last year, Scott Kitchen, will be showing up this evening. He'll be around this weekend. We set him free and he didn't come back, so we have to hunt him down and kill him.

(BPS) Den Mother: I think we sort of have, by white ballot/unanimous consent, a new Den Mother who may last us for quite some time: the sheer geniuses in Bar and Bar construction company, who are currently demolishing the Student Center under the guise of rebuilding it. The end of last week, they tore up all of the plastic sealant from the fourth floor roof in order to lay down the new and better plastic sealant. (You may or may not be aware that the fourth floor extends a bit further out from the building than the others, so we have a roof around the edges.) They laid down the new and better plastic sealant on three sides of the building. Then they went home for the weekend and it rained. This is why we have tiles missing from our ceiling, this is why we have water stains on the tiles that are there, this is why we have plastic sheeting all rolled up from where we had it down covering the books. We're keeping it where it is so that when it starts raining again, if the water still comes through, we'll be able to deploy it in under three minutes.

(L K) We came out lucky. LSC lost an entire computer system. Including their hard drive.

(HAM) Fortunately, Bill and Phil, and Robert Van der Heide, were here to direct things. The reserve swimming pool is still sitting back there. For a while we had a circulating swimming pool; they have since removed it. I believe they needed it elsewhere. But the aisle where the magazines are got hit kinda hard, and several rows of mags had to be pulled. They did get somewhat wet.

(HAM) Addendum to that, I went up onto the edge of the roof today with Donna, and we looked. Indeed as promised, where there used to be this big hole in the roof, they have now put down a new sealant. It seems to work so far, but then again it's not really raining all that hard.

(Weather: pleasant, clear, sunset fading away.)

(BPS) Further Fweekcomm reports: other "Welcome Freshmen" awards go to: again, the Bar and Bar construction company for having the Student Center rebuilt in time for the freshmen to arrive, as they promised they would; to the Institute and AT&T for crashing the dormline system. They promised MITSFS a phone that works by when?

(HAM) Now. As you can see, the phone is sitting on the floor because it works so well that we want everyone to have easy access to it.

(PJN) LHE report: interesting graphs on the table over there (there being the keyholder on duty desk) for those of you who want to look at them. Most of them specifically say that "Scott, we have reason to kill you."

(BPS) They all seem to be going downwards.

(HAM) You noticed that.

(RJG) Magazine expenditures were up last year, as were miscellaneous expenditures.

(L K) Jourcomm: we actually sold a couple of TZs at the midway, mostly the twenty years end. And TZ 40 will be out real soon now.

(HAM) Activities Midway Report: we made 356 dollars. The four year membership for the price of three seems to be very popular this year. Hopefully we'll probably do it again next year; that won't be my problem. We also seemed to get a fair number of members off of the Hitchhiker's video tapes...

(C H) Off of the video tapes?

(HAM) Well, it won't take much more, let us say, for us to make more money in September than we did last year. And follow up, more pseudo-LHE/skinner report, hopefully, as far as the Institute is concerned, that hole in the wall should be paid off by sometime within the next couple of weeks.

(C H) Plugcomm: As it happens, I am a member of the Reader Con Committee. Reader Con is a "literary convention" that will be held in Lowell on the weekend of November (mumble, most likely the weekend of Friday the 18th). We have a flier up on the inside of the door. I also brought a progress report- I can bring more. It's reasonable, Lowell's very nice- you can reach it by commuter rail for five bucks. We have a fairly fabulous list of guests considering what a small convention we are. (Our own Janice will be one of the fabulous guests.)

(BPS) Sitcomm: that failed TV pilot that I mentioned a couple of weeks ago as being upcoming and looked so bad in TV Guide that I probably wouldn't even bother watching it, well, I watched it anyway. It was Badlands 2005, or 2005 Badland depending on which segment of the credits you believed. And it was better than you'd expect. The premise was sort of a Road Warrior type thing in the American West about 15 years after a really terrible drought caused the water table to crash and everyone abandoned the American West.

(HAM) Moocomm: Beetlejuice on Registration Day.

(BPS) Twangcomm: twang. (Rubber band fight in progress.)

(BPS) Not Quite Real Business: the WorldCon was this last weekend down in New Orleans following the Republican convention there. Somebody posted here (by hole in the wall) a listing of the winners for the Hugos. In no particular order: Best Novel- The Uplift War by David Brin (news flash: Orson Scott Card did NOT win best novel this time round. He did, however, win best novella, Eye for Eye.); Novette, Buffalo Gals Won't You Come Out Tonight by Ursula K. Le Guin; Short story, something called Why I Left Harry's All--Night Hamburgers by Laurence Watt Evan; Michael Whela won both best professional artist and his art collection book Works of Wonder won for best non-fiction; The Princess Bride for dramatic presentation; etc, etc. The brand new Other Forms category was won by Alan Moore's Watchmen.

(C H) Best Fanzine was won by Tex. S.F. Inquirer. A remarkable feat considering that the woman who wrote and edited it was dismissed by the fan club that writes it and is now doing Pirate Jenny.

\goto{Old Business}

(HAM) Beaver postcard from ex-skinner Janice (she couldn't find one with a banana); letter from ex-skinner Andy Su stuck in Cleveland, now in his third year of med school. (Everyone says hi.)

(BPS) Followup to the Report on Geometric Progression Fine in Yonkers: a higher court has modified the fine such that it will continue progress geometrically per day but will max out at one million dollars per day. This has somewhat, though not overwhelmingly, extended the financial lifespan of the city of Yonkers.

(HAM) The phone still doesn't work. I'm told that if we ever have a phone, the number will be 253-1429. Remember it, write it down, engrave it on your palm. That way, the phone will arrive tomorrow and the number won't even be close. For those who have seen our board (building four, infinite corridor), the phone number there is also wrong. At the moment, we can't change the board, because Scott, our ex-skinner, doesn't know where he put the key.

(BPS) Somebody actually managed to repair our Klingon Battle Cruiser which suffered a broken neck in a fall from the ceiling a couple of weeks ago. So we need, eventually, to rehang it.

(HAM) We've dug out the all-new old, now all-new again "Bitch to the Skinner Book."

Old Business Algol? Um, us, uv, ur.

\goto{New Business}

TIME WARP TO COMMITTEE REPORTS:

(BPS) I caught on, of all things, the Sports News, an interview with Michael J. Fox. His part of filming Back to the Future II will begin on December 1.

END TIME WARP.

(JAH) Minicult: I was walking from Porter to Harvard Square today and I spotted a new hair store that had opened up and the name of it was Judy Jetson Inc. I have no idea if this is actually someone's name or if they're trying to indicate that they do futuristic hairstyles.

(RJG) Minicult: the state of California voted against the banana slug as the official state mollusk.

(BPS) No, the state of California voted for it; the governor of California vetoed it.

(BPS) Addendum to my first "Welcome Freshmen" report: it should also be pointed out that when the freshmen arrived, the first headline of the first issue of The Tech they saw announced that an MIT student was being indicted on a charge of attempted rape, assault, and kidnapping. This is traditional.

(HAM) Pseudo-something-Minicult: I gather from the stats I have heard, if we're looking for extra space for shelves, there are at least ten rooms in Senior House we could take over and no one would object at this point.

TIME WARP TO A FLAMECOMM:

(HAM) We were all here earlier holding a Star Chamber meeting and the fire alarm went off. I never knew that the Student Center HAD a fire alarm.

(PJN) I have to point out that Herb did not choose to go down with the library.

Time warp never ended. Meeting degenerates.

Lisa starts singing.

(PJN) Miller motion! Failed.

(PJN) Miller motion!

Motion passes many people in pain-those who aren't-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}