\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 3, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Rob Gates, Vice and Summer Skinner, presiding.

There were no minutes to the previous meeting so they are not read and corrected.

(MJG) Move to approve the nonexistent minutes as transparent.

(BPS) Horizons.

This is apparently both a friendly amendment and a second. Motion passes, quite a few-not many-lots of abstentions +Spehn.

\goto{Committee Reports}

(RvdH) Moocomm: I saw Willow. It was boring.

(RJG) Pianocomm: Scott, our beloved ex-president and skinner, now honorary plant, has turned in his key and is now residing in glorious New Jersey.

(BPS) Atlas/Titancomm: I used an incredibly highly accurate Sears bathroom scale to weigh the various accoutrements of the MITSFS. (All readings taken in a gravity field of approximately 1 G (9.8 m/sec^2). -BPS, 6/19/88)

Telzey Toy, 3 lbs; Star-Mangled Spanner, 4; Sport Model Gavel, 10; Vice Gavel, 12; Real Gavel, 14; Gavel Block, 49.

(LAK) Pseudo-Skinner Report: the real skinner is residing in Pennsylvania now and is very bored.

(BPS) Sitcomm: an expanded version of Dune is being shown on TV this Monday and Tuesday at 8 PM on channel 56.

(BPS) Sitcomm2: a few weeks ago on a really stupid game show called Win, Lose, or Draw, the four stars were Michelle Nichols, James Doohan, Michael Dorn, and Marina Sirtis.

Phonecomm: ring. It's SSDT, asleep. She won't be here.

(S??) STrekcomm: they reran Jewish Mothers in Space last week.

(BPS) STrekrumorcomm: there are unsubstantiated rumors that Gates McFadden, who plays Dr. Crusher, is starting to make noise about wanting more money. 2 down, 7 to go.

(MJG) Sitcomm: I heard they're resurrecting Twilight Zone again. They're doing Nightfall. There's also a movie version of Nightfall that's bombing in a theater near you.

(LAK) TelzeyViceReport: we're having an apartment-warming party next Friday at 8 PM. I'll have invitations here Monday.

\goto{Old Business}

OBA: um, us, uv, ur.

\goto{New Business}

(RvdH) Minicult: the Weekly World News- an amateur operatic troupe was performing in West Germany. The director made the mistake of holding his nose and laughing in the wings while the 300-lb soprano sang. She was wearing a helmet with horns on it. She charged him, gored him, and put him in the hospital.

(BPS) Minicult: A couple weeks ago, a 737 lost both engines and managed to do an emergency landing outside of New Orleans. An acquaintance of mine's daughter was on this flight and told what happened afterwards. They got everybody off the plane, put them and their luggage on buses, and drove them to the airport tarmac. Then, they pulled up on the airplane side of the terminal and rolled a portable staircase up to them so they could enter through the same way as if they were on a plane. The reason for this was that it was an international flight and they had to go through customs.

(S??) Minicult: someone here has translated the Bible into calculus.

(MJG) Move to condemn that translation for being on banana-colored paper.

Motion seconded, passes many-an odd Seth-a few +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1715 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Summer Onseck}

\end{document}