\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 16, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Herb Miller, President and Skinner, presiding; Donna Bell, Onseck, recording.

Last day of the Freshman Policy.

Minutes of the previous meeting read and corrected.

(BPS) Move to note that if a sex-starved moose comes galloping into the library anytime soon, it's Vanderheide's fault.

(RVderH) Motion to approve the minutes for being in a banana-colored binder.

(HAM) Go away, Robert.

(Seth) Motion to approve the minutes as not pursued by a sex-starved moose.

Motion passes a few limbs-less limbs-not that many limbs +Spehn.

\goto{Committee Reports}

(Seth) Den Mother: the second floor of the Student Center will open for public food service Friday, September 23rd. There's going to be an article in next Tuesday's Tech.

(HAM) Pianocomm: We have a new keyholder, who isn't here, who we don't have a picture of. She looks like Linda Cordella. Someday her picture wil be up there under Merril's.

(E. Carl Hylin) Old Government: an ex-skinner, namely me, was in town to see his ex-Telzey get married tomorrow.

(BPS) Sitcomm/Famecomm/Old Business combination: Roger Silverstein, MIT class of '79, former keyholder and our LHE during the 78-79 year appeared on the TV gameshow Jeopardy this week. Won 13400 first day; came back and lost the second day. In the little bits where they talk to contestants, he did not mention MITSFS at all or express any interest in science fiction. But I felt we should send him a letter of congratulations and ask him to give us some of it.

(L K) Jourcomm: the tentative release date for TZ 40 is hopefully going to be sometime around Halloween.

(Susan) Report from the Ambassador to the Null Set: In Don Fetter's Herald Tuesday, pro-censorship column for high school students, he referred to Jean Owles' Clan of the Cave Bear as a prehistoric sex novel. I think he has it confused with The Valley of Horses.

(Seth) Motion to send a sex-starved moose to Don Fetter.

Motion seconded, passes. \bing

(Harry and Eon walk in.)

(HAM) Skinner Report: All keyholders should note that we have a new shelf chart up.

(Seth) Pseudo-Moocomm: I saw a trailer for an upcoming movie called Alien Nation. It's some kind of cop story about aliens.

(BPS) Partially Whoosh-Relatedcomm: The launch date for Discovery has not yet been set because NASA wasn't sure what Hurricane Gilbert was going to do to it (speaking of whoosh...). As of a few days ago, Hurricane Gilbert is officially the grossest storm in the Western Hemisphere since they started recording such things.

(BPS) Cornelia Otis: The Wednesday MacPaper refers to a CBS poll released Tuesday on the subject of the Pledge of Allegiance, which has somehow become a campaign issue. 70 percent believe teachers should be required to lead the Pledge; 50 percent believe it should be required even if it is unconstitutional.

\goto{Old Business}

(HAM) AS already noted, we have an ex-skinner here. Also, the reserve swimming pool is gone; the circulating swimming pool is still gone.

(L K) It seems to be ex-skinner month; Scott Kitchen did indeed visit last weekend as promised.

(BPS) Addendum to that- showing up in the mailbox today was a postcard from Scott Kitchen, postmarked September 1, informing us that he's going to be up here on the weekend of the 9th.

(Seth) Motion to send Scott a sex-starved moose.

(HAM) Stop that.

(BPS) To close the books on the city of Yonkers, the city council of Yonkers finally caved in on the day that the geometric increase in fines entered the 800,000 dollar range. The federal judge agreed not to charge them for that day.

(GF) Talked with Janice and Ken this week.

(C H) Plugcomm: Reader Con still continues preparations.

(HAM) Old Business Algol, um, us, uv, ur.

\goto{New Business}

Minicult: There's a handbook that lists representatives, experts, and such of old TV programs and radio shows. So if you want to look up an expert on something random, you've got it.

(BPS) Minicult: Arthur C. Clarke has post-polio syndrome.

(Seth) Plugcomm: the Educational Studies Program will be running a one-weekend program, Splash (weekend of December 3). You can teach anything you want (within bounds of legality) and applications are due before September 30.

(GF) Hospital Report: Barry Saddler shot in the head while in Guatemala.

(BPS) He is now in a hospital somewhere in the US.

(C H) Soldier of Fortune paid for a jet to bring him back to a hospital in Nashville.

(BPS) It looks as though it was political/military as opposed to personal/accidental/hot tempered. The newspapers continue to list him as the person who wrote the theme song for the Green Beret's movies and a series of what the Globe terms "adventure novels."

(BPS) Minicult: From Aviation Week, the folks at Elgen Air Force Base are building a building with a porthole in the wall for their rail-gun concept. They will be firing payloads (up to a couple of kilograms) out into the wild blue yonder and seeing what happens.

(Room breaks into hysterics.)

(BPS) I believe they have their own gunnery range and they will be taking advantage of this facility. The really amusing thing is that the power supply for the rail-gun consists of, and I quote from the article, 14000 over-the-counter automobile batteries hooked up in series (this is later corrected to connected in parallel).

(L K) Minicult/Space Cadets on TV: there was a rerun today of a Donahue show featuring Princesses of Jewish, Catholic, Protestant, Italian, and Black persuasion. Such a lineup of bubbleheads has never been seen in one place before.

(HAM) Minicult: BU is going to start enforcing a policy (probably in the spring term) prohibiting guests in dormitory rooms from 11 PM to 8 AM on weekdays and 1 AM to 8 AM on weekends. The only exceptions are prospective students and blood relatives of the same sex as the host.

(Seth) Minicult: last night on Nightline, they said that during the Iran Contra affair, Reagan was so entirely spaced out that there was the possibility of invoking the clause in the 25th Amendment where the Vice President and the majority of the cabinet relieve him of his duties.

( ) Addendum to that. Reporters interviewed his advisors from that time who talked about signing his initials to documents because he wouldn't read any of them. Then these same reporters went to Reagan and said that he seemed totally alert and attentive.

(C H) Minicult: Statue of Elvis Found on Mars. A secret Soviet probe saw an eight foot statue of Elvis with alien writing on it. They also picked up the popular song All Shook Up.

(C H) Sideways addendum to the rail-gun Minicult: a channel 7 special entitled In Search of Ancient Americans showed some students doing experiments on an atlatl (spear-thrower). They reached a force 200x of that without the atlatl.

(Seth) Motion to condemn the atlatl for not being in a banana colored binder?

(HAM) No. Motion to replace Reagan with a banana colored cactus because that way there'd be some point to it. (Pun.)

(Chorus) Noooo.

(L K) Albanian motion.

(HAM) Can't Albanian the skinner.

(Chorus) Inverse skinner rule.

(BPS) Move to approve the skinner as being an albanian banana.

(Chorus) Nahhhh.

(Sue) Move to approve the skinner as not being an albanian banana.

Motion fails not many-a truly appropriate number if not quite enough-no one +Spehn.

(BPS) Move to note that the previous motion, which had the word banana in it, failed.

( ) Move to note that an ex-skinner is sitting in a banana-colored chair.

(HAM) Which one?

(BPS) We have two ex-skinners sitting on banana colored things.

(PJN) Move to note that he seconded a motion with the word banana in it.

Motion passes enough-not enough-a moose call +Spehn.

\bing accompanied by unenthusiastic clapping noises.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Donna Bell, Onseck}

\end{document}