\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 1, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Herb Miller, President and Skinner, presiding for a change.

Minutes of the previous meeting read and corrected by pseudo-onseck Lisa Kroh.

(S??) Motion to approve the minutes as in calculus.

(BPS) Friendly amendment- incalculant (or something like that).

Motion seconded, passes many-not many-nobody but Seth (S??) +Spehn.

\goto{Committee Reports}

(S??) Cornelia Otis: the Ligget Group tobacco company lost 400,000 dollars in a lawsuit on behalf of a woman who died of lung cancer. The company argued unsuccessfully that there is no proof smoking is bad for you, the woman was perfectly aware that smoking is band for you and did it anyway, and, without conceding that smoking causes cancer, the cancer the woman had is not the type caused by smoking. Article attached.

(BPS) People's Albanian Embassy: Yugoslavia is discontinuing the only international train line running into Albania because it is unprofitable.

(S??) Sitcomm: from an LA Times report on the impeachment trial of former Arizona governor Evan Meacham- "One woman said she and her friends watch every day and she was angry that the senators were questioning Meacham. She said if they didn't straighten out, she'd turn off the TV." Article attached.

(BPS) Sitcomm2: ABC recently resurrected a 1985 movie called Starcrossed, which was similar to Something Is Out There. I saw it, and there was a reason it sat on the shelf for 3 years.

(S??) Stupidcriminalcomm: a man tried to rob a cafe in France with a revolver made from nougat. The owner called the police, but by the time they arrived, the realistic looking revolver had been eaten. Article attached.

(SSDT) Bananacomm: the top part of the reactor's core tank got painted last week. Guess what color?

\goto{Old Business}

(LAK) Rob and I had our apartment-warming party. (A rambling discussion of pay TV and porno versions of fairy tales ensues.)

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) Minicult: there is hope for human civilization. A scheduled June 23 Michael Jackson concert in Lyon, France has been canceled because the promoters could only sell 16,000 of the 30,000 tickets.

(LAK) Minicult: I saw a show on the Playboy channel called "Dueling for Playmates." It included the male contestants mud wrestling and doing a striptease for the playmate, who scored them.

(BPS) Pseudo-Weekly-World-News Report: from the Glob- a Toronto jury has acquitted a man of second-degree murder in the slaying of his mother-in-law, saying he was sleepwalking when he drove 14 miles to her home, beat her with a tire iron, and stabbed her to death. Article attached.

(BPS) Minicult: Leonard Matlovich, a gay Vietnam veteran who fought for years against discrimination in the Air Force, arranged to get the last word. The tombstone he ordered while dying of AIDS bears the inscription "A gay Vietnam veteran. When I was in the military they gave me a medal for killing two men- and a discharge for loving one." Article attached.

(S??) Minicult: NYC mayor Ed Koch has given 5000 dollars to New York University to help defray costs of preserving video archives of his press conferences and other events.

(BPS) Minicult/Cornelia Otis: from June 2, when Jesse Jackson still had a campaign- reporters on the Jackson trail have a collection of "pocket terminators," boxes that produce sound effects such as missile launcher, tommy gun, and death ray. Article attached.

(At this point, Seth reads yet another article from the entire page of them he brought along that I am not going to bother to type in. If you want to read it, see attached "Nature's Way" blurb.

(BPS) Minicult/VGG: in Chester, SC a librarian signed a warrant for the arrest of a woman who had two books 52 days overdue. The woman was given a one-day suspended sentence, which she plans to appeal.

(Seth is at it again; this time the blurb is called "Sweet Smell of Freedom.")

(BPS) Minicult: in an event similar to the end of Raiders of the Lost Ark, a London grad student has rediscovered a funeral wreath and a harvest of fruit and grains from King Tut's tomb. The material was retrieved from apparently forgotten cardboard boxes stores for more than fifty years in the basement of the Royal Botanical Gardens in London. Article attached.

(BPS) Minicult: British Petroleum has dropped its bid to drill for oil next to a southern English forest where A.A. Milne conjured up Winnie the Pooh 60+ years ago. They were getting a lot of bad publicity, such as Christopher Robin Milne, 67, showing up at the hearings and testifying against them.

(HAM) Move to approve this meeting as having in no way involved a banana, the banana was not responsible for shutting down the meeting, and we shouldn't have been messing around with a banana in the first place.

(BPS) Friendly amendment- and everybody knows that bananas don't cause cancer anyway.

Motion seconded, passes everybody-nobody-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Summer Onseck}

\end{document}