\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 29, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Phil Nesser, LHE and Pseudo-Skinner, presiding.

Minutes of previous meeting read and corrected.

(JD) Motion to approve the minutes as pseudo. (LAK) VERY pseudo.

Motion seconded. Motion passes many-not as many-very few +Spehn.

\goto{Committee Reports}

(SG) Cornelia Otis: Samuel Huntington, public utility head, was killed by lightning.

(BPS) Cornelia Otis: Sun rises in west, Pope revealed to be Jewish, Michael Dukakis gives rousing speech.

(PJN) Pianocomm: Val has turned in her key and is preparing to leave for Europe. Postcards expected.

(PJN) Pseudo-Skinner Report: Keyholders with weekend hours should note the student center closing schedule posted on the door. Sign up for hours during the week instead.

(PJN) LHE Report: May and June books closed. The slight downward trend continues, but will hopefully reverse soon.

(LAK) Real Pseudo-Skinnercomm: Herb's still wasting away in Philly. Herb will preside at the meeting on August 19, by which time he'll be back.

(BPS) Mobcomm/Cornelia Otis: Middlesex County managed to have both Bill Starr and George Flynn for jury duty on the same day. Alas, neither was selected.

(LAK) Jourcomm: Write for TZ, deadline is August 1 for submissions, unless you prostrate before her. She wants stuff.

(SG) Moocomm: A friend at work found the Masters of the Universe movie good.

(BPS) Theftcomm: Someone finally stole Sue Tucker's bike. She was happy.

(SG) People's Albanian Embassy: From the Voice of the Revolution: Albanian delegation visits Canada. Everything you always wanted to know about Albania but would never believe if you read it.

\goto{Old Business}

(BPS) Moocomm: Out of Time, mentioned a short while back, foild my attempts to tape it. I got 2 hours of CNN instead. Probably an improvement.

(BPS) 10th birthday of Louise Brown, first test tube baby.

Old Business Algol: um, us, uv, ur, usual ravs.

\goto{New Business}

(SG) Minicult: a television addict was granted rights to a jury trial after cutting down a large tree in a neighbor's yard for better reception on his satellite dish. Now he gets the Disney Channel.

(BPS) Sitcomm/Minicult: Ron Perlman, of Beauty and the Beast, has cut an album. Not of singing, but of recited poetry- sonnets and such.

(JD) Minicult: Latest Blue Oyster Cult release has a spoken intro by Stephen King.

(SG) Minicult: The CIA is checking up on its own activities during the era with Bush as head. William Baker stated: "In a general way, we try to anticipate some of your questions, so I can respond no comment with some degree of knowledge." Robert Gates, deputy intelligence chief, explained it affects his inflection.

(BPS) Cornelia Otis: Ed Meese. The special prosecutor's report both totally vindicates him and is a disgrace.

(BPS) The last Playboy Club is closed. The 44 page handbook for bunnies said "Your bunny tail is your proudest possession. Make sure to keep it white and fluffy at all times."

(SG) Motion to give Christine Hefner a white and fluffy banana.

Motion seconded. Passes many-not as many-a small barnyard +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1716 SST.

\vspace{18pt}

\centerline{Intelligently submitted,}
\centerline{Robert Gates, Vice, Summer Skinner, Deputy Chief of Intelligence, and Sometimes Pseudo Summer Occasional Onseck-Type}

\end{document}