\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 29, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Scott Kitchen, President and Skinner, presiding.

Herb Miller, the pseudo-insect, reads the minutes of the previous meeting.

(S??) Motion to approve the minutes as fast.

Motion seconded, fails a dozen-more and louder than a dozen-some chicks +Spehn.

(RvdH) Motion to approve the minutes as being in a banana-colored binder.

(DSK) Stop that!

(HAM) Motion to approve the minutes as not being in a banana-colored binder.

(DSK) Stop that still!

(En masse) GO AWAY HERB!!!!!

(DSK declares all motions fail.)

(HAM with friendly amendment by BPS) Motion to approve the minutes as almost but not completely unlike what Robert just did.

Motion seconded, passes enough to pass-Connie, as usual-2 +Spehn.

\goto{Committee Reports}

(RvdH) Smothercomm: the shelves are covered in plastic. When I was here at 3:00 yesterday some Phys Plant guys came in and said there'd be a lot of rain and they knew we'd been complaining about the roof leaking and they were working on the roof but didn't trust it not to leak.

(HAM) Move to commend Phys Plant with a banana.

(DSK) Stop that!

(JAH) Pseudo-Picniccomm: we need drivers for the picnic. Sign the door.

(S??) STrekcomm: last week- Junkies in Space. (BPS is heard shouting "Bring back Spock's brain!")

(DSK) STrekcomm2: Tasha bites it this week. See it Saturday.

(HAM) Sort-of-STrekcomm3: apply now for the official Star Trek Enterprise card- a Visa card with a picture of the new Enterprise on it. Terms are slightly worse than for a Citibank card.

(BPS) Sitcomm: I have discovered a new dimension of horror. Howard Cosell interviewing Henry Kissinger. Cosell now has a half hour syndicated non-sports interview show.

(DSK) Mortcomm: Clifford Simak died.

(BPS) Moocomm: they've started the casting for Millennium, the John Varley version of the Ben Bova story. Kris Kristofferson as the CAB investigator and Cheryl Ladd as Louise Baltimore.

(DSK) Sitcomm: in 10 days NBS is starting this thing with interstellar something-or-others. (Tom McKendree) It's called Something Is Out There.

(DSK) Moocomm: Mad Max Beyond Thunderdome, Sunday night.

(CAH) Pseudo-Moocomm: they've started filming Indiana Jones 3. Sean Connery will play Indy's dad.

(HAM) Moocomm: Real Genius tonight.

(Tom McKendree) Which remarkably parallels my first semester at Caltech. See the old minutes to find out more.

(S??) STrekcomm: There was an interview with Denise Crosby in People. (Lots of STrek jokes follow.)

(DSK) (In a tone of rising panic) Any more committee reports?

(SSDT) Did anyone do the mortcomm?

(DSK) Yes.

(CAH) Speaking of mortcomms, the Baltimore Orioles losing streak. A few weeks ago a Baltimore DJ swore he was going to stay on the air until they won. He's regretting it.

(LAK) Jourcomm: write for TZ before you go home for the summer. ESPECIALLY SCOTT; I want a last will and testament.

\goto{Old Business}

(HAM) Tom's here.

(BPS) Someone described a Saturday morning kids' game show version of the Newlywed Game with siblings called I'm Telling. It's been cancelled.

(BPS) I saw Mirror, Mirror on Star Trek a few days ago.

(HAM) He's gone and done it. Foundation -1 showed up on the new book shelf.

(SSDT) More about the alleged rousting of rats that depressing the central artery is going to cause. I hope I misheard this: they're expecting 100,000 rats. To prevent this they're instituting a 10 million dollar program. That's 100 bucks per rat!

OBA: um, us, uv, ur.

\goto{New Business}

(BPS) For those interested in filking: tomorrow night at the Nameless Coffeehouse in Harvard Square, world famous filker TJ Burnside will be doing a set, as well as one with her group, Technical Difficulties.

(CAH) Minicult: Starlog had an article about writing for Beauty and the Beast by one of the show's writers. It's in the general interest folder.

(CAH) Minicult: from Time- in 1942 Frank P. Horgen's PhD thesis was rejected by the University of Chicago's Poly-Sci department. The Department has reversed its decision and plans to award Horgen, 77, his doctorate this June, just 47 years late.

(Tom McKendree) Minicult: the Steer Roast bonfire was lit at 5:25 Boston Mundane Time.

(SSDT) Minicult: I heard Senator Jesse Helms say something intelligent a few days ago. "I don't care if you don't want to get married. Go ahead and live together, just do it one at a time!"

The following motions are made, but with random seconding:

(JAH) Motion to commend Jesse Helms with a banana.

(HAM) Motion to beat Jesse Helms over the head with a banana.

(RvdH) We should come up with something more interesting to do with it.

(S??) Motion to suggest that Jesse Helms live with only one banana at a time.

(JH) Motion that the MITSFS assign RvdH the task of writing a thesis on interesting things to do to Jesse Helms with a banana.

(SSDT) This is more than a matrix vote.

(DSK) No! No matrix vote!

(RvdH) Motion to attach all the previous motions together into one motion...

(BPS) ...and to keep in mind the fact that they all have the word banana in there somewhere...

(HAM) ...but are not a matrix vote.

Since almost every person present at the meeting put something into the final motion, it passes lots-no one?-not enough +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Val Stark, Onseck}

\end{document}