\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 28, 1988

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Herb Miller, President and Skinner, presiding. Derrick Kong, Pseudo-Onseck, recording.

Minutes from the previous meeting read (rather well I might add) by the pseudo-Onseck and corrected.

(Seth) Motion to approve the minutes as very well read.

(RVderH) Move to approve the minutes already.

Motion passes, many, to October 24th, to almost no one plus Spehn.

\goto{Committee Reports}

(BPS) Whoosh Comm - The Soviets are scheduled to launch their shuttle tomorrow. They're going to do this unmanned and land it with a pilto on the ground controlling it by radio.

(HAM) Phone Comm - We almost have a phone. What you see before you is half of a phone. Basically, we can call out, other people on the new phone system can call us, but people not on the new phone system (i.e. dormline, outside calls) can't call in. The number is 258-5126.

(HAM) Skinner Report - We just received a shipment from Witter today along with a nice note saying that we will be receiving no more shipments because they're in the process of moving and all is Chaos.

(BPS) Sit Comm - I saw the premiere of Something is Out There. We are talking new heights in dumb. The premiere of the New Mission Impossible ran - they put a new wrapper around a previously used plot from the old show. It is nice to know that MIT is still serving as a cultural icon for technological excellence - one of the 'team' is Grant Collier, son of Barney Collier, a guy who graduated from MIT at age 16. Also worth noting, the bad guy, a hit man, was played by John De Lancie, whom Next Strek fans may remember as the actor who played Q.

(G F) Sit Comm - I saw the Tales From the Dark Side referred to in the minutes. Yes, he does play strip poker with the mummy - the mummy was played by Arnold Staing.

(HAM) Sit Comm n+1 - They've just finished the first storyline of the new season over in Britain for Dr. Who, which apparently didn't turn out too bad. You get to see someone almost turning on the first broadcast of Dr. Who ever on TV in the episode, because it takes place November 23rd, 1963. We also get to see Daleks finally climb stairs.

(RVderH) Sit Comm - there's a very bad song about Dr. Who on the radio.

(BPS) It's an even worse video.

(C H) Moo Comm - thumbs up for the new Sherlock Holmes movie Without a Clue.

(HAM) Sit Comm sub 7 - For anybody who watches PBS, they just started this past week a new series of Return of Sherlock Holmes with Jeremy Brett.

\goto{Old Business}

(BPS) This Monday, I'm going to be 31.

(G F) Follow up story about Barry Saddler being shot - one of the greatest headlines: Shot in Head - Saddler Improves.

OBA um, us, uv, ur, usual \bing.

\goto{New Business}

(BPS) In the Commonwealth of Massachusetts Probate Court, Middlesex division, on October 26th of this year, the person named Bill Pharen Starr did legally change his name and shall henceforth be known as William December Starr. (WDS)

(G F) Move to note that elections and polls may be hazardous to your health. Robin, in Batman, has just been killed by a poll. (William corrects - not a poll but a 'phone-in-to-vote-thing.' And it wasn't
the original Robin, this was Jason Todd - not Dick Grayson, who went on to become Nightwing.)

(C H) Tabloid Comm - This week in the Sun they've reached a new low in celebrity bashing. Headline - Flipper is Gay.

(Seth) Mini Cult - Presidential Campaign Cigarettes on sale at Kristi's Market in Havard Square.

(WDS) News Items - In one of the 62 thousand Massachusetts towns which begins with the letter H (i.e. Greensfield), they are searching for a murderer (18 years old, wanted in the mutilation slaying of a female college student.) He's a very strong fan of the Friday the 13th movie; they think he may be so deranged that he thinks he is Jason. The townsfolk are considering postponing Halloween this year. Lechmere's, however, who have for several weeks now been advertising and are scheduling a Halloween appearance by 'Jason' have no intention of canceling.

(RVderH) Mini Cult - The MIT Pro-life had a booth set up in Lobby 10 and a little tiny pumpkin saying 'adopt a baby pumpkin.' There was a counter demonstration for a while.

(WDS) Move to affirm the society's faith in the Great Pumpkin. \bing

(Seth) New Book List - There's a book called Don't Panic out of the making of The Hitchhiker's Guide.

(HAM) a tag on - the new Douglas Adams. The Long Dark Tea Time of the Soul is out.

(WDS) Info Comm - Info Comm is about to release Zork Zero, the prequel.

(C H) Plug Comm - Reader Con in less than three weeks.

(Seth) Motion to affirm the society's faith in the Great Banana (the approximate date being October 24th) in a pool with five dolphins.

Motion passes, lots of people, to almost no-one, to five dolphins in heat, plus Spehn. \bing

\vspace{12pt}

\noindent
Meeting adjourned, (some time not heard by Tarlm- 17??) SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Derrick Kong, Pseudo-Onseck}

\end{document}
