\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 16, 1992

[Most likely; these minutes were undated.]

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: The old minutes will not be read because the Onseck is tooling and not letting me play Civ on his computer back at the suite.

All: Awwwwwwww.

JM: Motion to pity the Skinner.

Motion passes 10-2-2 +Spehn.

\bing

(Frivolity and dilitoritude happens.)

\goto{Committee Reports}

Kristincomm: Star Chamber should sign the bureaucracy.

Pseudo-Jourcomm: TZ mailing list printed, sending soon. This ensures we continue to get review books, which is important.

Moocomm: Dracula is amazingly good.

Mobcomm is going to try again before October 31 (= December 25), time TBA. Probably a Saturday. Unless we get hit by a truck.

Calendarcomm: we need a new calendar. Paul is volunteered. Whether he is able to GET or BE a calendar is discussed. No naked women- get something respectable like Star Trek. Or sewer trout. Nothing that would give the Skinner an inferiority complex.

SL: The Skinner, in the nude, looks like a bowl of uncooked bread dough. That is just NOT aesthetic.

Important skinnerial announcement re: books and October 25 break. See the door for more details.

\goto{Old Business}

None!

\bing

Algol.

\goto{New Business}

(Long and interesting discussion of Judaism with a lot of words I cannot even pronounce, much less spell, deleted.)

(Discussion of Where You Go When You Die.)

It is decided that Frisbeetarianism (when one dies, one's soul goes up on the roof and gets stuck) is the One True Faith.

\bing

(Tappety tappety tap, someone is typing very fast on the AC.)

Y: Move to commend the assembled membership for entropy +-N (N>0).

Motion chickens 7-2-lots +Spehn.

SG: Motion to commend the Lubbovicherrebbi for not writing his proclamation on banana-colored paper on the Sabbath.

Motion passes 18-8-2 +Spehn, \bing

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}