\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 25, 1992

(I couldn't find the previous tape, so these minutes were obtained by secret Zen means.)

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
\bing MITSFS. All bow.

SG: Usual second.

JS: Usual vote.

(Many motions about people having nothing to say it a dinner trip be many motions flaming the Onseck enters the Like those interested in a dinner trip to come on, people.)

JS: (Completed \bing MITSFS meeting call... 5 verses.)

JS: MITSFS meeting so that Debbie can buy and emerges unscathed Library and I would like those interested in a dinner trip to coffeehouse and buy Set Minutes.

(Left out in the in a dinner trip from us before she finds out when I can process the backlog.)

ROSFAP3: I am readinner trip to come along. (Notes that he is nothings old like the Onseck read the interest of these \bing)

JS: The cable bill is more interest of not heard by there's just too many of these.

\goto{Committee Reports}

ROSFAP1: I say so \bing

MITSFS meeting collected membership from us assaults \bing

SG: Minicult: CNN seems to be thinging- multiple verses.

JS: Motions concerning the minutes.

(Left out in the Minicult: CNN seems to things old Buy Seth a bagel.)

Pseudo-Ass.comm: Our plans are dismissed by the members on enters the Onseck enters.

\goto{The Lack of Old Business!}

JM: Have minutes!

(Several attempts by the membership from us before she finds out people have the backlog.)

ROSFAP1: I am trying to find out when I can probably weird.

JS: There!

\bing

\goto{Committee Reports}

ROSFAP1: I am trying to find out when I can buy a four-yearly completed \bing

SG: Minicult: CNN seems to thing the is not, in fact, senile.

ROSFAP3: I am reading Dark Jen has no tail at all...

(Singing begins. Dahlgren Skinner.)

(The lack of old business!)

JM: Motion that a dinner (the cable bill is more important than the european econd).

JS: Usual vote.

\bing

JS: MITSFS membership from us before she find out when I can process the finds out how weird we are.

(Debbie can buy and emerges unscathed from the vicious assaults.)

\goto{Committee Real Lore}

SG: (Read the made to the minutes.)

(More attempts to end the Onseck are there any motion fails because I say so.)

\goto{The Lack of Old Business!}

JM: Motion the real loyally and is initiated to the pseudo-skinner.

(The Onseck read the Library and is initiated to the interest of not here.)

JM: Say it anyway so we can yell at he is not here.

JM: Have the Onseck enters the Library and is old business is lamented.

JS: Old but he's not here.

JM: Having nothing Dahlgren.

Skinner report: suggestion that he important that heard business!

JM: Motions concerning the nonexistensive and beautifully typeset.

Minicult: CNN seems the Library and is defended lore.

SG: (Real lore. Reads from there!)

\goto{Committee Real Lore}

SG: (Reads from the Loyally and emercifully- 1725 PSST (Pseudo-skinner).)

(The Onseck enters the finds out how weird we are.)

Debbie can buy a four-year membership from the cable bill is more important than the european econd.

JS: Usual motion!

JM: Isaac Asimov is stion that a dinner trip to come along. (Notes there!)

??: No, he's not here.

JM: Say it any of these.

(Many motions flaming the Onseck enters.)

SK: I am trying to find out he's not here.

JS: There's just too many of these.

\goto{Committee Reports}

ROSFAP1: I am trying to the my birthday and I would like those interest of not heard by the MITSFS.

??: Motion that Seth is old, he just turned 23.

PASSES.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}
\centerline{[2020 editor's note: the "secret Zen means" were probably a Markov text generator.]}

\end{document}