\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 18, 1992

THE SHORT FORM- OUTLINE AND SELECTED EXCERPTS

(It was a looong meeting.)

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jennifer Shih, Vice and Pseudo-Skinner, presiding; Scott Kullberg, Onseck, recording.

Now what do I do?

JM: Have the Onseck read the minutes.

JS: But he's not here.

JM: Say it anyway so we can yell at him.

JS: Onseck, read the minutes.

??: No, he's not here.

JS: Are there any motions concerning the nonexistent minutes?

(Many motions flaming the Onseck are expounded upon. The Onseck, of course, is defended loyally and emerges unscathed from the vicious assaults.)

\goto{Committee Reports}

ROSFAP1: I am trying to find out when I can process the backlog.

ROSFAP2: Next Friday (09/25) is my birthday and I would like those interested in a dinner trip to come along. (Notes that he is not, in fact, senile.)

ROSFAP3: I am reading Dahlgren.

Skinner report: suggestion that a dinner trip be made to the coffeehouse and buy Seth a bagel.

Pseudo-Ass.comm: Our plans are nearly completed.

\goto{Old Business}

JS: There's just too many of these \bing things. Old business!

JM: Motion that Seth is old, he just turned 23.

Passes 4-5-3.5 +Spehn, so THERE!

\bing

(The lack of old business is lamented.)

JS: Old business algol!

SG: Usual motion!

JM: Isaac Asimov is still dead!

JS: We want the real lore.

SG: (Reads from the Lore O' The MITSFS. All bow.)

SG: Usual second.

JS: Usual vote.

\goto{New Business}

JS: Usual result!

(A new person enters the Library and is initiated to the mysteries of the MITSFS.)

??: Motion to suspend the meeting so that Debbie can buy a four-year membership from us before she finds out how weird we are.

Debbie: Most of my friends are probably weird.

JS: Motion fails because I say so. \bing

SG: Minicult: CNN seems to think the cable bill is more important than the European economic crisis.

(Mumbling.)

JS: Anything else? Come on, people.

JS: (Complains about people having nothing to say.)

(Singing begins. Dark Jen has no tail at all... 5 verses completed.)

Motion to do something indecipherable chickens 1-?-6 +Spehn.

(The Onseck enters.)

SK: I have minutes!

(Several attempts by the membership to end the meeting are not heard by the pseudo-skinner.)

(The Onseck reads the extensive and beautifully typeset minutes. Left out in the interest of not having recursive minutes- think about it.)

JS: Motions concerning the minutes?

(More attempts to end the meeting are dismissed by the pseudo-skinner.)

(The collected membership begs the pseudo-skinner to bing them again and again, harder and faster...)

(Singing... particularly bad singing... multiple verses.)

\vspace{12pt}

\noindent
MITSFS meeting adjourned (mercifully), 1725 PSST (Pseudo-Skinner Standard Time).

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}