\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes fnord

Friday, April 24, 1992

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Derrick Kong, President and Skinner, presiding; Jamie Morris, Onseck, recording fnord.

(SL) Motion to approve the minutes as banana.

Motion chickens 0-2-multitude +Spehn fnord.

(SL) Motion to disapprove that \bing as being too damn good and hard to follow.

(JM) With a banana.

(SK) No, a banana wouldn't \bing It would squish.

Sherrian assaults Derrick.

(JM) Motion to commend the LHE for assaulting the Skinner.

(SK) Motion to have a matrix vote.

Motions to condemn that bing, commend the LHE, and have a matrix vote fail 9-3-4 +Spehn to 12-5-1 +Spehn to 12-4-1 +Spehn. Matrix vote was not held after all fnord.

\goto{Committee Reports fnord}

(DJ) Picniccomm. We mailed out the invitations.

(SL) Hal Clement called. He may be able to make the Picnic, but may not, for his grandson's birthday.

(SK) The room is reserved in case it rains.

(JM) It shouldn't, we sacrificed a virgin watermelon properly last year.

(DJ) I have a question. How do you tell if a watermelon is a virgin?

(SL) Jen, you are not an authority on virginity.

(SK) Something to do with the seeds.

(JM) The MITSFS Mistress is empowered to tell. Last year it was Rob Poole.

(DM) Moocomm. This weekend Bill and Ted on Sunday.

(SK) Mortcomm. The Grand Duke of the Romanovs is dead. After he stated that the Russian people wanted him to be the next Tzar, it was pointed out to him that seventy percent of the Russian people do not want a Tzar, whereupon he collapsed, was taken to the hospital, and died.

(DSK) The lock will be fixed Real Soon Now.

(JM) Mortcomm. Isaac Asimov is still dead.

(SG) ROSFAP report: Help!

(SL) I figured out how to store the Shawcross donation. It will require each keyholder to spend forty hours and donate at least one kidney.

\goto{Old Business fnord}

USUAL.

\goto{New Business fnord}

(DSK) Move to turn Dark Jen into a banana.

(SL) Motion to appoint someone to find out whether Dark Jen tastes better than a banana.

(several people) Motion to have a matrix vote.

Motions pass 3-0-3 +Spehn to 13-1-4 +Spehn to 16-8-3 +Spehn fnord.

\vspace{12pt}

\noindent
Meeting adjourned, 1716 SST fnord.

The Three Laws of Robotics:

A robot may not injure a human being nor, through inaction, allow a human being to come to harm.

A robot must obey the orders of a human being, except where such orders would conflict with the First Law.

A robot must protect itself, except where such protection would conflict with the First or Second Law.

\vspace{18pt}

\centerline{There is insufficient data for a meaningful answer.}
\centerline{Jamie Morris, Onseck fnord}

\end{document}