\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 9, 1992

(I think- meetings are not timestamped.)

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: Minutes of the previous meetings!

SEK: Most of the previous meetings' minutes should be deleted for the sake of propriety.

SL: Would you care to put that in the form of a motion, Mr. Onseck?

SEK: I so move.

SL: I second it; I know what's in them.

Motion passes 11-0-0 +Spehn.

\goto{Committee Reports}

SL: Pseudo-Moocomm: No good SF movies at LSC. Go see the director's cut of Blade Runner; it's way cool. And take me with you.

SL: Pseudo-Kristincomm: random bureaucracy from the middle of nowhere. According to the laws of the state of MA, we are required to distribute to all of our members a copy of the MA laws on hazing. And I explained that this was absolutely silly as we have 500 members, most of whom are alumni, and they informed me that it would be sufficient if this was read aloud at a general meeting. Sorry about this; it is my legal obligation, and now I can sign the form that says I did this.

??: Y'know, we have 1 percent of the membership here.

SL: WHO CARES?

??: I don't...

SL: Garble marble fouth gurblefunf greeblok etc. (This is all in Albanian that will be explained later.)

SL: There we are; I have now discharged my legal obligation.

SK: Motion to define the laws of MA as being in Albanian.

SL: Seconded!

Motion passes 13-0-0 +Spehn.

(Some mumblage the losing tape recorder didn't pick up.)

SL: File a complaint with the State of Massachusetts, there you go.

SL: We have instituted a new office for Derrick Kong: Department of Mindless Bureaucracy, KRISTINCOMM!

DK: I thought that was supposed to be Speaker with Animals, but...

SL: No, SwA is the person who deals with the ESP meetings.

SL: No more committee reports? Form a committee, appoint yourself to it, report on something!

SL: Mobcomm: oh, Derrick, it has been suggested that we have a Mobcomm run last Saturday.

DK: Last Saturday? Bad idea.

SL: I think that's a bad idea, but we will have all been dead by then.

SL: Unilateral policy declaration from Head Bitch in Charge: Random Assassins should not be doing game business or having secret meetings in the MITSFS like the people I found in here.

SK: That's against the rules of the game.

SL: It's also against the rules of the MITSFS and will have been dealt with by the Skinner of the MITSFS and the GMs of the game. If you find Assassins doing game business in here, please ask them to stop.

(Stories of a bunch of nasty Assassins having a sekrit meeting in the MITSFS, for which they are duly chastised on the Brown Couch; probably the cleanest business ever done on the brown couch.)

SL: Any more committee reports?

P: The ( ) is still looking for members.

SL: How about my thesis advisor?

(Repeat of Moocomm for DK.)

P: Perotcomm: it's almost SF. He'll be on TV later.

SL: For people who get tired of lying, cheating, and betrayal in Assassin, you can go see it in real life.

\goto{Old Business}

SL: Old business? No old business. New business?

??: What about the Old Business Algol?

Old Business Algol.

\goto{New Business}

SL: Is there any new business? ...would you like to put that in the form of a motion?

SL: Let the record show that Paul motioned towards the windows with a bananananana.

P: I've been used!

Motion fails 1-5-3 +Spehn. \bing

SL: Phil never binged better than that...

P: It's not the size of the banana... it's the feel of the peel.

SL: I don't suppose you'd like to put THAT in the form of a motion.

P: I don't suppose you'd care for it either.

SL: I refuse to be involved in the motion of your peel-feeling banana.

SL: This should have been under Committee Reports: Mobcomm run RSN, but not during the game.

P: Actual business- finger motion!

DK: Unclear whether NE Mobile actually counts as business.

SL: When we determine a date, we'll go. And there's a discount, and it's sorted by publisher, and it's much fun.

Miller motion fails.

(It is determined that the skinner cannot be impeached because either she is a god or because she will Albanian any such motion.)

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}