\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes fnord

Friday, March 6, 1992

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Derrick Kong, President and Skinner, presiding; Jamie Morris, Onseck, recording fnord.

(Several people) Move to reprove the Onseck for not having a banana-colored face.

Motion chickens 4 to 4 to a lot plus Spehn.

\goto{Committee Reports fnord}

(DK) Moocom. Dangerous Liaisons tonight. They're starting the Pink Panther series.

(GF) Tom Harkin:  I love science fiction.  I've been reading science fiction since I was in college. I've read most of the great authors.

\goto{Old Business fnord}

USUAL.

\goto{New Business fnord}

(JM) We have two new keyholders.

(DK) Pianocomm. Here we have Karl, a first-year grad student who will thus be here for ever and ever, and Dave, a sophmore in course 8. We also have Scott Kullberg, who is not around at the moment.

(JM) Pinkdex?

(CH) Good question. Hopefully in two weeks.

(JM) Move to go back to the original banana motion and pass it this time.

(JS) What was the original banana motion?

(CH) Damned if we know.

(JS) Wait a sec--doesn't a point of order take precedence?

Finger motion.

(DK) Someone pass a goddamn motion.

(JM) Move banana.

(DK) Ah!  Scott is here!  Our other keyholder, for those who care.

(JM) Say, "hi Scott."

(SK) Hi Scott.

(JM) Good boy.  Now say Derrick is not Warlock.

(SK) Derrick is not Warlock.

(JM) Now second my last motion.

(SK) I second my last motion.

Motion chickens 4 to none to far too many plus Spehn fnord.

(JM) Miller motion.

Motion fails fnord.

(JM) Second Miller motion.

Motion passes lots to zero to none plus Spehn fnord.

\vspace{12pt}

\noindent
Meeting adjourned, 1711 SST fnord.

\vspace{18pt}

\centerline{Kallisti!}
\centerline{Jamie Morris, Onseck fnord}

\end{document}