\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 30, 1992

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: The Onseck has run off to parts unknown, but left us with the minutes. Pseudo-Onseck, read the minutes?

Minutes read.

SL: Motions concerning the minutes?

??: ??

SL: \bing Motion fails for lack of a second. Any more motions concerning the minutes?

\goto{Committee Reports}

SL: Committee reports.

Pseudo-Ass.comm: They did a pretty good job.

??: Which is your injured arm?

SL: The one that is in my pocket because it should be in a sling, but I'm just not the kind of person who walks around with her arm in a sling, because I like using it for things and then wincing.

CH: (Something about a shawl.)

SL: Carl (Witty) is probably in need of sympathy more than I am... he got hit with the broken glass and was covered with a bunch of little cuts.

CH: He got stitches...

SL: None of them were awful, but all of them put together just... He had injuries. I don't know about Adina.

CH: She's sore, but she's the least affected by all this.

SL: Because she crunched our side of the car!

CH: She threw you in front of herself...

SL: The skinner has decided that she is really a gaming nerd at heart... I'm lying there in the ambulance thinking "I sure couldn't fight, and I couldn't use technical skills right now, but there's really no way a damage system could mechanic this... And I was honestly trying to come up with a gaming damage system to describe what had just happened to me.

P: Trying to make your peace with the universe in your own way.

SL: Apparently so.

CH: Let's pass the minutes as "whiplashed."

Motion passes 16-2-2 +Spehn. \bing

SL: Mobcomm: LSC's Paranoid Dystopian Weekend- 451F, JFK, Handmaid's Tale, Brazil. Those of you who are not irrational conspiracy theorists may wish not to sit with those of us who are. If you are, come sit with me.

P: "If you have nothing nice to say, come sit by me..."

??: Which version of Brazil?

P: Mobcomm2: The uncut Brazil is showing in the Brattle this week. Recommend that we take a trip to go see that.

SL: Mobcomm3: When was that vampire movie with Anne Parillaud that you described released or going to be released?

P: FINGER MOTION! That's a question!

CH: It's out already and called "Innocent Blood," and I don't know if it's still around.

SL: I'm asking video.

CH: 6 months, I guess.

SL: 6 months from September release?

CH: Yeah. It's a guess...

SL: Please do not tell anyone in my Vampire run about this...

(If they're here, it's too late now! MUA HAH HAH HAH HAH HAH HA!)

(Snickering from the peanut gallery.)

P: What about people in other people's Vampire runs?

SL: People in other people's Vampire runs are fine; I don't have to GM them.

P: Mobcomm4: Addams Family and other things in SCC lounge this evening.

SL: Mobcomm: I don't know if we're going to try again or not. If we are, I'm not going.

P: You didn't make it?

SL: Accident was on the way there. We got no books. Someone should try and organize this RSN.

\goto{Old Business}

SL: Old business?

??: Motion to bring back last week's meeting. Sounds like more fun.

Motion fails lacking a second. \bing

SL: New business! \bing

SL: Old business Algol?

(A chorus of usuals.)

\goto{New Business}

SL: Greg Benford wandered in here last week looking for critical works on Jules Verne and will probably be coming in to next week's meeting to talk to us. Keyholders, if you are on duty and he wanders by, I said he could have a life membership. He didn't get one before because I hadn't okayed it already. Those of you who wish to take more initiative than that are more than welcome.

P: Is Lobby 0000 0111 new business?

SL: Yes.

(Description of a truly wonderful hack, and the wedding performed therein.)

P: Motion to send Mike and Eri a banana as a wedding present.

Motion passes N-3-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1720 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}
\centerline{Amusement: anagrams of science fiction society}
\centerline{once scientific society}
\centerline{scientific cone society}
\centerline{scientific since coyote}
\centerline{scientific coco syenite}

\end{document}