\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 8, 1992

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, NEW President and Skinner, presiding; Scott Kullberg, Onseck, recording.

Minutes read.

PD: motion to approve the minutes as top banana. Chickens 2-3-3 +Spehn.

\goto{Committee Reports}

Pseudo-Moocomm: ST VI 7 and 10 26-100.

Pseudo-Panthercomm: Look what I did (processed many books). (Applause.) The things previously sitting in cardboard boxes behind the desk.

PD: Motion to commend the Skinner as being goddesslike. Second. (Laughter.) 3-2-5 +Spehn.

\bing

Y: Motion to commend the skinner for understanding the New Math. Seconded.

PD: Motion to have a matrix vote.

Out of order- only 2 motions on the floor.

??: Motion to have a second matrix vote.

SL: Frivolous and dilatory, now shut the fuck up.

8-0-2 +Spehn. Passes.

\bing

Pseudo-Moocomm2: Beauty and the Beast Saturday, Die Hard Sunday.

Y: Japanimation "Iron Man" may be among us this summer. Where/when not known. Moved from December through May so far.

\goto{Old Business}

SL: there is no old business.

DK: Andy Su is no longer here.

DSK: Isaac Asimov is still dead.

SL: as opposed to mostly dead.

Usual motion, usual second, usual vote, usual result, NO usual discussion.

\goto{New Business}

SL: this meeting may be followed by a dinner trip for those interested in seeing ST VI.

(Singing begins.)

\vspace{12pt}

\noindent
Meeting adjourned, 1710 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}
