\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society fnord

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes fnord

Friday, April 10, 1992

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Sherrian Lea, LHE and Pseudo-Skinner, presiding; Jamie Morris, Onseck, recording fnord.

(Newbie) Motion to approve the minutes as pink and fuzzy.

Motion fails 5-lots-1 +Spehn fnord.

\goto{Committee Reports fnord}

(SL) Picniccomm!

(SK) We haven't gotten our response from Hal Clement yet.

(JM) Mortcomm. Isaac Asimov died.

(SL) We're sending a contribution to the memorial fund.

(SL) Jourcomm has instructed me to say TZ Real Soon Now.

(JM) People should write reviews and stuff.

(DKern) Computercomm. The computer was bad. It got better.

(JM) FilingCabinetcomm. The filing cabinet was bad. It still is.

\goto{Old Business fnord}

(N) Move to approve the \bing as lame.

Motion passes 14-0-0 +Spehn.

USUAL.

\goto{New Business fnord}

(SL) New business? New business?

(SL) The filing cabinet is still locked. If you have stuff in there, which is mostly me and Derrick, you're...

(JM) Fucked. I have Derrick's walkman in there.

(N) Move to commend Derrick as Fucked.

Derrick enters.

Inverse-Skinner rule invoked. Motion to commend everyone in the Library but Derrick as Fucked passes lots-none-none +Spehn fnord.

(DSK) Move to approve that \bing as less lame than the previous one but still pretty lame.

Motion passes by a whole big bunch.

The Skinner reads us a story. "The Last Question," Isaac Asimov, out of The Edge of Tomorrow. Everybody claps.

The new computer is named "the A.C." As the Skinner wills, so mote it be.

Derrick is commended for having a bigger \bing than Sherrian.

(N) Motion to commend this guy over here for wearing a nice cheerful banana-colored smileyface on his shirt.

Motion passes 11-10-4 +Spehn fnord.

\vspace{12pt}

\noindent
Meeting adjourned, 17-gods-know-what SST fnord.

The Three Laws of Robotics:

A robot may not injure a human being nor, through inaction, allow a human being to come to harm.

A robot must obey the orders of a human being, except where such orders would conflict with the First Law.

A robot must protect itself, except where such protection would conflict with the First or Second Law.

\vspace{18pt}

\centerline{There is insufficient data for a meaningful answer.}
\centerline{Jamie Morris, Onseck fnord}

\end{document}