\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 23, 1992

[Most likely; these minutes were undated.]

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order (such as it is), 1700 SST, Sherrian Lea, President and Skinner, presiding; Scott Kullberg, Onseck, recording.

SL: The reading of the minutes of the previous meeting.

(The Onseck reads the minutes- this takes a while...)

SL: Motions concerning the minutes?

AW: Fnord!

JM: Second!

SEK: Motion to make a motion with the minutes.

JM: I like mine better.

SEK: Motion for a matrix vote.

SEK: I withdraw my motions.

JM: Good; that leaves mine, errr... the one I seconded.

SL: All those in favor?

SEK: Of?

JM: The motion I seconded.

Motion passes 7-4-2 +Spehn.

\goto{Committee Reports}

SL: Mobcomm: tomorrow, 10:00, here.

(Explanation of Mobcomm- periodic trip to N.E. Mobile Book Fair to buy stuff cheaply although sorted by publisher.)

(DELETED FOR SECURITY REASONS.)

SL: Those who want to come to Moocomm- errr, Mobcomm- are welcome to come.

SEK: Move to define the letter O as being identically equal to the letter B.

RT: Second!

SEK: Friendly amendment- the letter O only when it follows another letter O.

RT: Second!

Motion passes 8-0-6 +Spehn.

JM: Motion to set the letter M equal to the letter T.

SEK: How would you pronounce "committee" if that were to be done?

SL: Motion fails by skinnerial decree.

JM: PBBBBBT

RT: So what about Mo(o/b)comm?

JM: You should \bing

\bing

SL: Mo(o/b)comm: Batman Returns, pseudo-SF.

SEK: Next weekend: Handmaid's Tale and Brazil.

SL: Dystopian weekend.

SEK: JFK, but that doesn't count.

SL: It's completely SF; everyone knows the (DELETED) got him fnord.

SEK: I think Oliver Stone got him; it's just a coverup.

??: I did it.

SL: You weren't even born yet!

JM: Pretty sneaky, using an assassin who wasn't even born yet... it's part of the coverup.

SL: Do the Time Police know about you?

JM: I AM the Time Police.

SL: The hell you are, you're never at the meetings!

JM: I don't have to go to the meetings, I run the damn organization! What's the use of being God if you have to go to the meetings?

SL: I'm God and I'm at the meetings!

JM: Well, you're silly about it. I just go to other people's meetings; that way I can just make fun of them. (Silly noise.)

SL: Old business?

\goto{Old Business}

SL: There is NO old business. New business?

\goto{New Business}

??: You're making a mockery of the meeting. (This should be deleted as it is clearly impossible, but without it this editorial comment would make nowhere near as much sense.)

???: When is the Library open?

SL: It's posted on the door.

???: ??

SL: We're trying- a lot of people are crossing off their hours; it's around midterm time and there was an Assassin game.

(Discontinuity while the tape is flipped. We return you to our regularly scheduled irregular meeting already in progress, such as it is.)

(Discussion of impacting structural members of buildings at substantial fractions of c, and the resulting destruction. Remember, kids: 186,000 miles per second; it's not just a good idea, it's the LAW!)

SL: If you have a problem with someone not showing up, just write it down on the complaint sheet.

(Skinnerial raving! People are writing down stuff on the complaint sheet, mostly keyholders writing silly stuff about themselves. Ben Bitdiddle is not a member of the Society.)

JM: So FINE them.

SL: Is there a fine for that?

HAM: You're the skinner; you can make any fines you want...

JM: There's a fine of 50 cents for annoying the keyholder on duty.

SEK: Move to turn over anyone who annoys the Keyholder On Duty to the Bloodthirsty Goon (AKA Stalker and Provider).

JM: We don't want to kill our keyholders, we just want to fine them.

SL: Don't write silly things on the complaint sheet. Ben Bitdiddle does not have a membership.

JM: Motion to give Ben Bitdiddle an honorary membership.

SL: Is there a... I'm afraid to ask. Is there a second?

??: Anti-second.

JM: Second!

SL: You can't do that!

JM: I got away with it before.

SL: What was I drinking?

JM: Nothing; it's easy to get away with things with you.

HAM: Especially when he lies and said he did when he didn't.

SL: Any more new business?

(Apparently someone ate the stapler.)

SL: No dinner trip tonight; movie at 1900.

??: Move to have a banana for dinner!

(Motion amended to be a bunch of bananas for dinner.)

(Motion added to NOT have a bunch of bananas for dinner.)

(Motion to combine the motions into a motion to have or not have zero or more bananas for dinner.)

Motion fails 12-lots-1 +Spehn.

(The skinner is called an idiot; someone is threatened with the gavel.)

Miller motion fails.

Second Miller motion chickens.

\bing

Second second/third Miller motion.

(Singing begins.)

\vspace{12pt}

\noindent
Meeting adjourned, 17something SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Scott Kullberg, Onseck}

\end{document}