\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 20, 1995

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST,
Jamie Morris, LHE and Pseudo-Skinner, presiding; [Unknown], Pseudo-Onseck, recording.

JM: Will the Onseck please read the minutes?

(Silence.)

JM: I do see that there appears to have been some minutes left here by the Good Minute Fairy, and it says... (Scott really needs to learn how to use the minutes format which is in the file...)

(JM reads the minutes, such as they were.)

JM: Are there any motions concerning the extremely short minutes?

(Silence.)

JM: Motion passes!

\goto{Committee Reports}

JM: Committee reports!

CH: Rosfap, we have processed everything except the Shawcross donations, and I think Seth was telling me that he doesn't need an assistant any more because we're done.

JM: Oh, well, how long did it take you?

CH: I don't really know- he did some while I wasn't here- a few hours.

JM: What the fuck are these things doing here?

CH: What are they?

JM: One of them appears to be Seriesdex and the rest of them are random folders.

CH: Those are probably us- we've been using them.

JM: Then you should probably get rid of them.

CH: Pseudo-Moocomm- Birmingham cable now has the SF channel.

JM: Mobcomm- should be another one near the end of this ??? since the last one crashed and burned.

(Explanation of the irony of that statement.)

JM: Onto...

\goto{Old Business}

JM: Old business! Any?

{The usual usuals happen.)

\goto{New Business}

JM: New business? Anyone? Anyone? Bueller? Bueller? YOU! Make up some new business!

??: The universe is expanding!

A motion is chickened to continue the expansion of the universe, 2-2-2 +Spehn.

JM: Let's move back to old business!

\goto{Old Business}

P: Dracula has the biggest opening.

JM: How wide was it?

(Unintelligible.)

JM: Anyone want to end the meeting?

??: Move to expand the universe to be banana-shaped!

Motion passes 3-1-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1703 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{[Unknown], Pseudo-Onseck}

\end{document}