\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/27/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 27, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the 8-no-16-no-24-bit-color Onseck.

Minutes read.

\goto{Committee Reports}

Mobcomm: The British are coming! The British are coming! Revere probably reported this with more enthusiasm.

Jade digs into the for-sale boxes.

Dexmistress: we have a shelfdex, yay.

Jadecomm (reported by Jade): The Alewife bus cracks the LL bus mirror and window.

Jadecomm2: Mostly monochromatic today.

Bluebellcomm: Still have a Tolkien backup. Bumper stickers with "Keep on Tolkien." Groan...

\goto{New Business}

The TIF has a Hubbard illustration now, cool despite being Hubbard.

John complains about the pins in the TIF poster, and brags that his nearsighted eyes can focus close enough to poke himself on them.

The C/Ps are now redistributed. 5/6 shelves disappeared rather completely. The Hs will be moved as part of inventory prep.

\goto{Old Business}

The AOL droppings on the gavel block are still here. 

A new visitor recounts how he came to know of MITSFS since a young lad reading Niven. Tracked us down 25 years later. (Rick Rather, aka the stranger in the aloha shirt.)

"I didn't expect Spain!" "Nobody expects Spain!"

John attempts to find a new home for a tape ring.

\goto{Future Business}

Inventory... yay...

John looks forward in time on the Boris calendar.

Magazines will be sold.

John recounts a sad story of being flustered by the mysteries of toilet paper being shipped cross-country.

Jade smashes the tape dispenser ring. \bing \bing 
\bing \bing \bing Thud. The plastic bag gets holes banged into it.

Experiments with the Telzey toy, not very effective at binging.

Miller motion. Fails something-something-something +Spehn.

Second Miller motion. Lots-0-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
