\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/28/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 28, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the beatnik Onseck.

Minutes read.

M: reread the part John didn't hear. No second.

\goto{Committee Reports}

Mobcomm: a dozen Buffy books on the new books shelf, more next month.

Bluebellcomm: not scared, because we're out of covering material. The Onseck has dealt.

Pseudo-Bondcomm: jhawk has probably been lazy. Need to talk to Foley about suitable punishment. Foley has been shown the whips, wasn't that thrilled. Maybe guns or blades.

Mike: "Huh? Blades? What?"

Pianocomm: some possible prentices possibly clamoring for possible projects. One of them is bugging Steph... which one?

\goto{New Business}

Very high pitched bing.

Jamie retrieves our APO books. 216 returned books and a check for 21.38. About 30 books or so sold.

Jenwa is reading the Buffy serial novel.

We will probably need to rent a truck to pick up the law form's shelves. Lots of confusion still. Far more than will fit in a car or van. We'll just show up there in ski masks and take their shelves. Probably get 20-100 percent of the shelves we currently have.

The LPs have 13 inches of space left, maybe end of year. The shelf bubble in the P's has been propagated about halfway so far.

New dexes still in post-Inventory clarifications.

Comparing first sentences. "Pardon the stench." "There was dried chicken blood under my fingernails."

New rates about to become effective. In fact, being posted right now.

Mobcomm has noted a lot of revised editions coming. out. Like remastered CDs...

Jamie admires the strong stomach of a member who made it all the way through the Dune series and liked all of them.

"Serving American twice." (A weird Tech ad.)

A newly-activated netdrop and net access in theory. We have "psi-phi.mit.edu". We will get mitsfs.mit.edu from Jen Murphy later. Should get "fuzzypink" for our database server. Note that you should add "Niven" for a good web search.

Fuzzy Pink Niven's Law: "Never waste calories." Jamie launches into an aside on the origin of the name.

The old minutes used to note "Malcolm Y made a pass at Fuzzy Pink and was rejected." (Check this.)

John: "You'd be amazed what you find when you type 'Gentle' and 'Grunts' into a search engine."

Jade is slowly losing her shields against losing her innocence.

Minicult: an attempt is being made to revive the Burlesque Revival Association.

Mike: "Huh? Burlesque? What?"

The Enterprise premiere happened. There was a shuttle named that.

It took us a while to hit the moon originally.

Jade is repulsed at some of the APO book covers.

Jade: "The captain was that guy in the other show!"

Mike: "I still say the word 'Bakula' sounds fairly naughty."

The intro music sucked. "Not so much let down as hurled."

"To boldly split infinitives..." They FIXED it.

\goto{Old Business}

Someone yells in pain from down the hall.

M: commend the skinner for long-range gavel use. Intercontinental ballistic gavel. 12-0-1 +Spehn.

Before the meeting there was bad music coming from the darkroom.

M: release fireflies in the darkroom! 9-1-1 +Spehn.

M: commend skinner for ringing differently. 5-1-4 +Spehn.

\goto{Future Business}

Jamie: "John, get a memory!" After he looks at Ed's old file-cabinet note.

Jade's teacher doesn't consider romance a genre. Or maybe literature, even.

On the final episode of PBS's "Evolution," they had a bunch of genuine anti-evolutionists. "So, we're supposed to mate with apes and make fish?"

Mike: "Huh? Mate with apes? What?"

M: feed Mike a banana instead. 8-0-5 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17...(Jade counting the hands on the clock)...40 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
