\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/14/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 14, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the shellshocked Onseck.

Minutes read.

M: condemn last week's minutes for clarifying the cleaning lady situation. No second.

M: ... Seconded. 5-1-2 +Spehn.

\goto{Committee Reports}

Pseudo-Bondcomm: jhawk?

M: commend the skinner for forgetting what jhawk told her. 7-3-1 +Spehn.

Should we have the Vice punish him? Does Foley have a Vice outfit?

Bluebellcomm: we're scared of the ZGT. Jamie brought some of the Schultz books out.

Pianocomm: new prentice: Josh Weaver. We should dub him "Secret Angel Prentice-Prentice." The Onseck groans.

Pseudo-Pubcomm: we need a real pubcomm. In theory we had a slide at some LSC showings. Will they bill us?

Minicult: The new Vampire Hunter D movie is coming to Brattle later this season. Unknown if it's any good.

Minicult: We're at war but we don't know with whom yet.

New dexes waiting on post-inventory stuff. A lot of missing books turned out to be there. John makes a confusing report about confusion with his membership sheet and inventory.

John is destroying someone's backpack. John: "Ooh, it's like leather or plastic or something." Cow skin or dinosaur skin.

Jade wants to destroy an Earthlink CD. It is a sacrifice from John's collection. \bing \bing \bing THUD! \bing Jade is not satisfied... not excited about banging CDs.

Jamie: "It was supposed to be Earthlink-shattering."

John: "Tell us the truth, Jamie... Malcolm's your real father, isn't he?"

Pseudo-Jourcomm: "TZ RSN and then glare at Jade." Harper-Collins sent us a review Bradbury book. Bradbury is not on Jade's list of recently dead authors.

Jamie: "Is this a newspaper list or a to-do list?"

Aaron and Yu sent us a magazine. 11-20 years old and imperfect, so 75 cents... like a lot of undergraduates.

M: Institute a committee responsible for anything not covered by a committee... Dotcomm? Lot-1-John falling over +Spehn.

\goto{Old Business}

F+SF finally found our life membership, will start us back up. What about missing issues?

M: sent a letter asking F+SF where the lost Aprils are. Fails by ominous silence.

The shelves are now overfull. Need to box some stuff.

\goto{New Business}

John still has some hearing left from teenage years.

We need more new members. John used to sell a lot more, as the minutes used to show. Ed: "And it's all searchable..."

M: commend Onseck for rubbing hands and cackling with evil glee. 12-0-1 +Spehn.

Jade is fascinated by John's book "Come Be My O.R.G.Y." by Ted Mark. John (perusing the cover): "Would he look that grouchy if he was unbuttoning?"

Jamie requests that the Onseck provide quotes out of context in the future.

Sent donation acknowledgments out for Dr. Who donations.

Jade: "There are pretty books on the Bluebellcomm shelf."

Jade: "I think our LHE is dead." Someone logged in as her last night. Ed jumps to the likely confusion: "Her account's been hacked AND she's dead!"

Bashing John's head is proposed as a new method of ending the meeting.

M: send a SWAT team heavily armed with banana-colored machine guns to rescue the LHE. 5-0-4 +Spehn (does nothing).

In fact, Jenwa saw LHE yesterday and just now caught up to the meeting.

M: commend LHE for not being dead. No second. Apparently some disbelief about this.

Miller motion. 2-...7-0 +Spehn.

The Microsoft spellchecker considers an ellipsis to be an error. Puts a wavy line under it. Is it a grammar error instead? Green or red wavy line?

\goto{Future Business}

Jade: "Beef jerky is not in my future!"

John is reading a beef jerky package as a reading addict. Made from the finest beef and jerks.

M: wire John's jaw shut and send him to the beef jerky factory. 6-1-5 +Spehn; does nothing.

Second Miller motion. 5-0-4 +Spehn; does nothing.

Anime showing in 50 minutes.

The room next door will be eaten by Cthulhu. Jade considers goatees as science fictional.

Third Miller motion. Lots-0-4 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
