\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/09/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 9, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Jade Wang, President and Skinner, presiding. Ed Keyes is the putting-in-the-c2's Onseck.

Minutes read.

Photo taken of the library with John's digital camera just before the meeting.

The proper committee was  "Sitcomm."

M: abuse the onseck for not correcting this. No second.

M: condemn the minutes for not noticing the absence of Mobcomm. No second.

M: have the onseck retroactively slavishly obey the skinner to correct the minutes to "Sitcomm." 6-0-1 +Spehn.

\goto{Committee Reports}

Mobcomm: got new books despite not even being around. 4th class mail from SFBC. A complete circulating set of Ken MacLeod books.

Chroniccomm: a draft of SNF which needs comments.

Pianocomm: ...Jade gets easily distracted. Some Bluebellcomm activity, and Gapdex too. Prentice reassigned to shelf minion.

Disturbing discussion of jhawk's love life.

Pseudo-Telzey: the Telzey appears to be falling down on the job, as the skinner is not enthusiastic about love.

Shrek vs. Trek vs. "Sexy Beast."

Meaning of "to thine own self be true."

Trying to figure out which sci-fi movie involved time travel and investment tips.

\goto{Old Business}

Jade is very good at banging the gavel.

A few more boxes of the Schultz donation have been processed.

A person claiming to be an ex-skinner visited last week: Guy Consolmagno. He looked at Bill Starr and said "Oh, nothing's changed."

Reasons why we won't get our minutes back from Greg Russo.

The law firm probably moved on Monday. Hopefully shelves will become available.

Susan Tucker invented T.C. Skinner.

Still the bubble in the P's.

Meeting with UA on the Reading Room proposal will happen. A few wacky proposals for how to share the space.

Usual stuff. Jade is prompted.

\goto{New Business}

(Jade) "I hate that ALGOL."

A person wrote us asking about a speculative fiction writing workshop. Anyone interested in participating? Some are.

Also, someone auctioning some stuff off, older SF collection. Perhaps filling in magazine holes.

The October Newdex is now up.

Discussion of the "Ninja Burger" website. "Your food within 30 minutes or we commit seppuku." Just like Snow Crash opening.

(Jamie) "China is famous for its rice patties."

There is also a Ninja Burger RPG, which is actually pretty hilarious.

Anyone see the Trek premiere? Not too bad.

This week's Counterpoint is extremely bad, but it does have bananas in it. Titled "Getting Some." With statistics that Jade completely mistrusts.

When John came to MIT, the administration gave the freshmen sex instructions.

(Malcolm) "Insert tab A..."

The Lesbian Sheep Paradox. Female sheep show sexual receptivity by standing very still.

M: commend Counterpoint for making up its deficiencies by showing pictures of bananas. 3-4-1 +Spehn.

(Jade) "That doesn't look like a banana to me."

Jade just loses some innocence by hearing about putting condoms on bananas for practice.

\goto{Future Business}

M: commend people who lick bananas and other things. 8-0-6 +Spehn.

Discussion of whether Mike gets a vote for his injured arm.

(Jade) "Now I wish I counted more carefully."

\vspace{12pt}

\noindent
Meeting adjourned, 1810 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
