\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/18/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 18, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the ecchi Onseck.

John asks the Skinner to take off some clothing, and she complies.
The purpleness matters, evidently.  Is it Purple Clothing Day?

Minutes read.

Motion: Approve the minutes as purple.  Not seconded.

Motion: Purple the minutes as being approved.  Passes 4--0--2+Spehn.

\goto{Committee Reports}

Anti-Pianocomm: Yevgeniya and Aaron have turned in their keys, boo.
Two fewer keyholders... we need a new Theftcomm or two.

Bluebellcomm: A couple of medium-sized books were covered.  Bad jokes
follow about it not being the size that matters.

Mobcomm: John hasn't done anything in a while.  A hardcover run should
be soon, although Jamie stole John's thunder with that suggestion.

Jadecomm: Jade will be away for a week or two.

Pseudo-LHE: We've been getting a lot of dollar bills recently.  Steph
will be gone soon.

A discussion of our new chair and its squeakiness.

Alohalenscomm: Pictures will be made available eventually.  Jade's
shirtsleeves were made transparent through the magic of flash
photography.

The Science Fiction Book Club bill should be paid eventually.  Finboard
reports are also due soon.

The Louisiana State University Press is trying to send us herons.
Or maybe pelicans?  A blend of 300 waterfowl.

Motion: Form a conglomerate of over 300 birds with a blender and dye
it purple.  Passes 6--1--1+Spehn.

[Jamie] ``We should make more poetic motions so he Onseck can write
purple prose.''

Motion: Declare Jamie to be Albanian.  Passes 8--4--0+Spehn.

{\bf CLUNK!  Clang!  Bong!  Bing!}\vskip 12pt \centerline{{\em{Old Business}}}

John has made a box of books he will buy.

Alcoholic deer are mentioned somehow when the Onseck wasn't listening.

\goto{New Business}

Motion: Mock and scorn John for now knowing it was Purple Clothing Day.
Fails 4--5--0+Spehn.

[John] ``So this actually belongs anywhere but now...''  The decade
on John's trip to the moon mentioned in a previous minutes was off
by one.  It was actually the 50's.

We got a new bad comic from a publishing company called ``Crushed
By Mommy!''

Motion: Commend TeX.  Passes 3--0--1+Spehn.

They sent us six copies, so we can color some of them.

The universe splits in two somewhere between 3:00 and 3:30 in the
morning.

We had trouble shelving hardcovers, due to the fullness of the shelves.

The comics are donated to Jade for use as purple coloring books.

{\bf CLANK!  Bing!}\vskip 12pt \centerline{{\em{Future Business}}}

A Mobcomm trip should happen.

Summer meeting times perhaps should be 6:30 instead of 6:00.

Motion: Observe that the Skinner is giving up six.  Voting doesn't happen
because the Skinner doesn't get it.

Aerial surveys are very useful for locating Roman ruins.

Motion: Mail Stephanie a banana in France every day so she doesn't
forget about us.  Fails 3--5--1+Spehn.

Discussion of the correct wasy to pronounce ``MITSFS''.

Motion: Miller motion.  Fails because the Skinner forgot to count.

Motion: Second Miller motion.  Passes, also without numbers.

\vspace{12pt}

\noindent
Meeting adjourned, ``go ahead, make up a time'' SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
