\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/23/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 23, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1705 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the dry-cleaned Onseck.

Minutes read.

Motion: Approve the minutes as drastically condensed.  Passes 6--2--2+Spehn.

\goto{Committee Reports}

Mobcomm: One new book last week.  Eight new books this week.  Sixty-four
new books next week if we're lucky!

Jourcomm: We still want submissions.  There follows a discussion of file
format issues, and Yevgeniya complains about essentially all of them
except for ASCII text, and really even that.  [John] ``It is my mission
to write HTML and make you like it!''

Pseudo-Pianocomm: The ``88 keys'' thing for the derivation of the name
is explained to the Onseck, who groans.  John claims credit for a new
potential prentice, but it's really because the new sign-up sheet was
seeded by James T. Phrogg.

Pseudo-Panthercomm: Panthercomm is being lazy, and is encroaching on
the Bluebellcomm half of the shelf.

Bluebellcomm is also not impressing John.  [Ed] ``But you're Bluebellcomm!''
[Jade] ``I'll impress you into the floor!''

The Japanimation Society has no officers or people who want to be officers,
but still has showings... somehow.

Apathycomm: Yay...

ThiswouldbeSmilescommifSmilescommwassomethingelsecomm: We got a new
poster of a dragon which complements the yellow chair.  It is explained
to John that this report might actually be appropriate to Smilescomm
after all.

\goto{Old Business}

[John] ``So the Skinner was complaining that her slot was too small...''
John enumerates some of the old papers accumulating in the slot, including
a blank monthly statement.  Written in invisible ink for extra security?

We got a new Highsmith catalog, and found out that our shelves are too
different from the ones currently being sold.

Motion: Condemn them for not building shelves to conform to our
book-throwing practices.  Passes 5--0--1+Spehn.

The flowerpot holder with the heart-shaped handles was claimed by
someone on reuse.

\goto{New Business}

Yevgeniya's Spanish class has a virtual exchange program, and she wants
a good picture of MITSFS to share with them.

Jade demonstrates a total lack of wrist strength with the gavel.
[Jay] (sings) ``Skinner's got no strength at all, strength at all,
strength at all, she's just a limp wrist.''

There is a discussion of upcoming keyholders.  [Jay] (sings) ``Skinner's
got no successor at all...''

\bing

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

[John] ``How long has it been since an adjournment song actually worked?''

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
