\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/31/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 31, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1705 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the fraternal birthday Onseck.

Minutes read.

M: approve reading as a brilliant cure for the mentally ill. No second.

M: commend as entertaining for the mentally ill.

M: commend as pointing the way to further research to exploit the power of the mentally ill to save or destroy the world. 8-0-4 +Spehn.

\goto{Committee Reports}

Pseudo-Theftcomm: John: "I win, let's play a new game." John tapes a small column on top of his column, for future use.

Pseudo-Pubcomm: posters up all over the place. Some cool ideas, some of which will turn into posters. Many were posted low to attract short people.

Dexmistress: new dexes RSN. Bunches of scrap paper for Ed... no, it's double-sided, doh!

Mobcomm: may get more books, depending on John's sister.

Pseudo-Fweekcomm: Midway happened, few memberships but a lot of interest. John's tour-giving abilities are legendary: "Here are the A's..."

Pseudo-Gossipcomm: The Tech was evicted from the little room next door, although appeals are pending and will probably be revised.

John returned with more books than he started with when shelving the C/PAs.

\goto{Imaginary Business}

"UNDERSTAND the mentally ill. MENTAL ILLNESS. Can it be cured? Prevented? Harnessed as a cheap, efficient power supply?"

It's illegal to set off an atomic bomb in Cambridge. Can we just move it to Somerville?

M: move on to real business. No second. "Real business isn't allowed!"

M: condemn John for claiming skinner made a point of order. Infinity-0-4 +Spehn.

John threatens to take off his shoes, to various cries and threats of violence.

\goto{New Business}

Inverse ALGOL. "First!" The skinner is now confused.

Unusual motion. "Second!"

\goto{Old Business}

The air conditioner is leaking again, Phys Plant came and took it apart then left. Will they leave another flashlight next time?

M: Albanian John before he tells us what he means by "Jade should try to 'nice' to them." Lots-0-some +Spehn.

The darkroom attacked us with poisonous fumes last night. Overheard: "Shouldn't we call Hazmat for this, it's corroding through the floor."

Retribution with Xanth, Gor, isopropyl alcohol, and lemon spray is proposed.

The Globe had an article about a dangerous NaCl contamination in Chelsea.

Harnessing the mental illness of members could fix the flickering light.

M: find out how many mentally ill people will it take to power lightbulbs without increasing the entropy of the universe. Chickens something that bounces-smelly things-paragraph +Spehn.

Jenwa is vainly trying to get past a paragraph in her book.

\goto{Future Business}

Jamie is really hungry, wants food in the future. Jade is full of sushi, since it fills you up in a stealthy sense.

M: have skinner eat banana-fish sushi. Vote is horribly interrupted by John removing a shoe.

Adjournment song.

\vspace{12pt}

\noindent
Meeting adjourned, 1736 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
