\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/8/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 8, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and Skinner,
presideing.  Ed Keyes is the post-birthday Onseck.  John Carr is the
ambitious pseudo-onseck.

Minutes read.

Jade forgets the procedure.

Motion: Commend minutes as flaky and baked into a light pastry shell.
No second.
Condemn?  No second for that either.

Jade tried to drink water and fails.  Her shirt gets a drink.
As she cleans herself off...

Motion: Commend the Skinner for having a drinking problem.  Passes \hbox{6-3-1+Spehn}.

JPW: ``I can still bing.  I haven't lost it all.''

Motion: Be concerned about a lack of motions concerning the minutes.
Passes \hbox{6-1-3+Spehn}.

\goto{Committee Reports}

Mobcomm: Will get some more books one of these days.

Motion: Commend the Skinner for being covered with an even layer of woad.
No second.

Jade unbuttons her shirt.  Or is she buttoning it?  A discussion of the
difference follows.  John went to a private school and choked himself with
buttons and ties.

Bluebellcomm[JFC]: The new book shelf is shiny.

Dexmistress[JM]: Need to print out dexes.

Pseudo-theftcomm: Jen Chung is now theftcomm.  We need a new smilescomm.

Jamie exhibits the Iron Fist spreadsheet and everyone is scared.

Discussion of inventory scheduling.

Jade has stolen jhawk's hours, MUAHAHAHAHA!  (Jade)  ``It's all logical, be quiet!''

Tag-team onsecks.  Ed tags John.

I'm in charge here now.  Your minutes are {\em mine}!

Marcus abandons us.  Jade holds her gavel and sucks her thumb.
Jamie holds Jade and sucks...well, the pseudo-onseck isn't sure what.
(Jade) ``It's either me or him'' (referring to Ed).

Jadecomm[JM]: Our Jade is back.

Jade's skirt is below her knees.  Is that long for a skirt?  Or just a
long skirt?

Napcomm: Kidnap graduating seniors to keep them here.  Put them
to sleep and then...  Jamie does a bad Italian accent.
(Jade) ``The senior gift thing is at 39\%''


\goto{New Business}

Jade has given up six for the summer.

Jamie sold 100 books, 68 to a dealer and 38 to Sara Pickett.  The
dealer won't be back but maybe the readercon guy will buy our stuff.
Books are sorted into good, middle, moderate, bad, coverless, falling
apart, cover prices \$0.50 or less, cover prices \$0.50 to \$1.00,
etc.  Falling apart books are in the trash.  The cheapest books are in
two boxes.  The intermediate price books are in three boxes.  Jamie
came to the library, sold books, sorted all our used books, read {\em
Thief of Time}, but did not reshelve the to-be-shelved circulating books.

It is the season when people check out a stack of books and return them
a day or two later to get a new stack.  They also renew their memberships.

Talk of our endowment fund follows.

``There's a kitten in my soup,'' says Jade.  Or maybe she said ``suite.''
Bad people brought a cute kitten.  Cats know when they are not wanted.
Jade is going to hot ass, then she will move again.  Keyholders tend to
live together.  More talk of apartments, roommates, etc., is not
transcribed verbatim, although the pseudo-onseck got the definite
impression that things would have worked out differently if the
sequencing of various events had changed.

(Although Jade did button her shirt earlier, it has now slipped off
her shoulder so she is still showing skin.)

Used book prices doubled this week.  The people who bought lots of
books got a discount.

``Walk a mile in somebody else's shoes, wearing heavily padded
socks, {\em then} judge them.''

Jade tries to use the gavel to unscrew Jamie's foot, but his leg is
too thin even though Jade's neck is not.  Is this normal?  Malcolm
talks about ``wrenching your neck.''  Jade says ``I have a strong...oh
never mind.''

Everyone in the library is old.  Someone seconds this, or maybe Jade
calls a vote anyway.  The motion fails five to ``wait'' to three to
five to two plus Spehn.

Jamie says ``dirty and old are not the same, Jade.''

The cute stuffed banana creature has fallen off the Moon Gravity.
Jade says ``replace the banana guy!'' and passes the statement by
Skinnerial decree.

Jamie reminds Jade, to her surprise, that she just ended the meeting.

\vspace{12pt}

\noindent
Meeting adjourned, 17:50 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-onseck}

\end{document}
