\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/30/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 30, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and
Pseudo-Skinner, presiding.  Ed Keyes is the Emotion-Engined Onseck.

Minutes read.

Motion: Condemn the minutes as fast and abbreviated.  Chickens very
philosophically philosophical conundrum--philosophical quandary--0+Spehn.

\goto{Committee Reports}

Mobcomm: Eight books this week, restarting the cycle.  We'll fit a curve
next week.  One-point fits are easier, though.  We got the {\em Ultimate
Mallworld} for jhawk.

Hasslecomm boxes are being converted to for-sale boxes at a good clip.
A discussion of ``used-book arbitrage''.

Pseudo-Rosfap: The pile is a little larger.

Pianocomm: A dormant prentice, Kat Allen, is un-dormanting herself,
yay.  John proposes a project to look up books we don't have, in order
to fulfill the library's purpose in becoming complete.  The next step
in Gapdex, perhaps.

Pseudo-Jourcomm: {\em TZ} RSN.

Jadecomm: Jade is feeling ill and is hiding in her room.  The squad
has been dispatched.

\goto{Old Business}

The donation from last week was picked up, consisting of six boxes
including all Tolkien stuff imaginable and some multimedia additions
to our collection.

The extra shelves were ordered.

Bluebellcomm is lame, lazy, and shiftless.  John covered one book, and
didn't sniff any more isopropyl alcohol.

We're getting even more rain, and John is worried because he's only
fifty feet above sea level.  John has a spider in his apartment and
is happy about it.

The ALGOL is immediately triggered to prevent John telling his
cockroach-in-the-mouth story.

\goto{New Business}

We should put up the plastic sheets before we go.  Eeek!  We have a
leak now!  No, wait, it's just Jamie hallucinating.

\goto{Future Business}

In the future a section of shelving will be dedicated to the memory
of the Schultz.  The wording of the plaque is being worked out.

John suggests we build a dock out the window to prepare for flooding
up to the fourth floor.

Motion: Come out from under the banana-colored couch and pray for the
return of the banana-colored light in the sky (amendment) while
reaffirming the Society's faith in the Great Pumpkin.  Passes
philosophical conundrum--philosophical quandary--rainbow-colored
Slinky+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
