\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/16/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 16, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the mad-coding Onseck.

Minutes read.

Motion: Commend the minutes for being typed.  Pass 5--4--3+Spehn.

Motion: Condemn the minutes for being strongly typed.  ``Run-time
polymorphism!''  Strongly passes 13--0--3+Spehn.

\goto{Committee Reports}

Mobcomm: A new book.  At this rate, the library won't explode.
John got the book and jhawk didn't.  (insert diabolical laughter)

Pseudo-Picniccomm: The letter to Hal went out, with seven choices
for dates.  Jade reads the letter and chuckles.

Bluebellcomm: John covered two books this week.

The Alpert walks in, Skinner from 1971-72.  It is revealed he left
Boston before Jade was born.

\goto{Time Warp to Old Business}

Motion: Say ``hi'' to the Alpert in an embarrassing fashion.  Passes
ton--0--3+Spehn.  ``Hiiiii...''

The Alpert remarks on the nice gavel resonance that Jade has mastered.
However, the gavel smashed a coconut back during the Alpert's reign.

\goto{Committee Reports}

Bluebellcomm: We still have an overflow box.

Pseudo-Pianocomm: Susan selected Gapdex for part two of her prentice
project.

In response to a question by the Alpert, Jamie reports the Society
current membership at three or four hundred, down from a high of
450 or so.  In comparison to the Alpert's day, we have fewer money
problems, but space and prentices are scarce.

Concomm: Boskone started, and we're selling {\em TZ}'s there.

Jourcomm: We want some fresh meat to print in {\em TZ} 46.  John
demands that Jourcomm stop killing off prentices.  The Alpert compares
the hassle of Jourcomm in the pre-desktop-publishing era.  John says
something about using Jello for printing presses in jail.

The Alpert has the record for the highest {\em TZ} press rate (four
or five issues in two years).  John tries to pull out one of these,
and then Yevgeniya and Jade get pulled into the search as well.
``It's in a box somewhere.''  Apparently we also have an unpublished
Campbell manuscript in a box somewhere.  Yevgeniya discovers a {\em TZ}
1 submission in her drawer, and everyone admires the blue painting on
the cover of {\em TZ} 26.

Is George Phillies running for Libertarian office?

There follows a discussion confusing to the Onseck about a guy named
Guy, apparently an astronomer and Jesuit, who submitted to the {\em TZ}
under the pseudonym Erwin T. La Peer (spelling unknown).  The Onseck
resolves to research this so he'll be less confused the next time.

The Alpert's family is around on campus, but is too embarrassed to
accompany him to the meeting.  It is reported that the daughter of
the original Skinner also never came by, despite attending MIT.

The Alpert has to leave, and a \bing sees him on his way.

All of this is retroactively designated Old Business.

\goto{New Business}

[Jade] ``Sustain is cool.''

The new shelves are both the same and not the same as the old ones,
perhaps an evolved version.

We have a large stack of {\em TZ} 36 covers for some reason.

\goto{Time Warp to Old Business}

A search progresses through {\em TZ} 37 and 38 for the Lore of the
MITSFS.  It is discovered that Bootcomm is the committee for the
Alpert himself, and Stranglecomm is the committee to call the Alpert
up at 3:00 in the morning.

\goto{Future Business}

In the future we may do wacky things with the circulating paperbacks.

Jade contemplates sharpening the gavel to make it even more dangerous.
Her neck is too big to comfortably fit in the gavel.

In the future net drop rates will be cheaper.  Perhaps we can get a
net drop now at the cheaper rate if we ask nicely.

John has taken money for the majority of memberships this year for
some reason.  [Jade] ``John is a bully!  John is a bully!''  ``John
is poaching!  John is poaching!''

Jade likes traffic lights, but only when they're green.  Monty
Python sings about APO.

Motion: Apply for a grant to study the crystal structure of banana
molecules.  ``Sec... ond.''  Fails flailing hands--John-- ... no,
it passes tickling hands--John--nothing+Spehn, after Jamie's hands
stop flailing.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
