\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/29/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 29, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, \_\_\_\_ SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the freshly-employed Onseck.

The Skinner surprises a visitor with the opening bing.

Minutes read.

Motion: Include a ``Jade's wardrobe'' comment in every minutes from
now on.  Passes 11--something--lots--1+Spehn.  The Skinner confuses
the Onseck with those votes.

[Jade] ``I see invisible people.''

\goto{Committee Reports}

Pseudo-LHE: The Alumni Office sent us a gift record with an ``Appeal: 9''
note on it.  Is that maximum appeal?  Or a mistake between \$52 and \$5200
that was appealed, perhaps to the wrong fund.  We're probably out \$5180
somehow...

Pseudo-Theftcomm: We have a Tyrannical Iron Fist chart.  Everyone should
cower in fear.  It's just in time for John to go on vacation and fall
behind.  [Jade] ``You can comment on the design, the layout, and if you
say it's crooked, Jamie will kill you.''  [Jade] ``John, stop fondling
our chart.''

Jadecomm: A nice shiny red and black combination.

T. C. Skinner may already have won some big prize!

Pianocomm: There's a prentice on the couch.  She's not running away,
amazingly.  [Jamie] ``You're supposed to use the nice voice...''

Mobcomm: [John] ``...''  [Joe] ``Oh, shit.''  Someone should make a deposit
to pay John.

The TIF board is confusing Jade now.  We should sort the keyholders by
height so everyone writes at eye level.  [Jade] ``I'm not understanding
anything today... I feel Albanian.''

\goto{Future Business}

Inventory will be July 28.  We're trying to sign people up for specific
time slots this time to spread people out.

It will probably rain soon.  John attempts to comment on today's
weather, but that's not in the future, so Jamie is forced to slit his
throat with a papercut.

\goto{Old Business}

The hardcover shelves are getting more crowded.  We have a new space
chart, showing that our rate of growth has increased by 10\%.

We're still trying to find if our shelf company still exists.  The last
we heard from them, they were going to talk to lawyers.  Were they
attacked and devoured by lawyers?  This is plausible.

Motion: Declare the rest of us Albanian so we can understand Jade.
Seconded, but no vote taken.

Motion: Have Jade speak into the gavel to use it as a universal
translator so we can understand her.  Seconded, but no vote taken.

\goto{New Business}

Buildings E10 and E20 are going away because of the Media Lab construction.
The whole building's going up on reuse tomorrow!  Any useful office
furniture for us?  We may need people to move things, although we need to
make an appointment with Phys Plant to get in.

The libraries are redoing a lot of magazine shelving, and may have some
surplus for us.

Jade is tired of standing.  A banana motion is invited.

Motion: Include bananas in Jade's wardrobe.  Passes lot--2--lot+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 17:35:22 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
