\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/13/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 13, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1710 SST, Jade Wang, President and
Skinner, presiding. JFC is the nice Pseudo-Onseck.

JFC refuses to read last week's minutes. JPW says to read the minutes from 2 weeks ago.

Motion: approve last week's minutes as unread. Passes 2-1-0.5 +Spehn

\goto{Committee Reports}

Pseudo-mobcomm: JWH bought us 3 books, but MW donated one of them.

Mobcomm: got a long thin box of books, and a few hundred foam peanuts. JWH talks of sculpting the kind of packing material that reacts with water.

"You can sculpt a banana." (JPW)

"... and move up to dragons." (JWH)

Are dragons carnivores or omnivores?

Pseudo-theftcomm: JH says the TIF should be the pink fuzzy something.

Pseudo-LHE: JFC deposited a check. Are we broke? He also asked for more money.

Joe deposited 471.75 in time. Yay!

We can probably pay JFC and the SFBC.

Bluebellcomm: unprocessed paperbacks on Bluebellcomm shelf. "I blame Jamie." (JFC)

Pseudo-pianocomm: Katherine Reid helped Joe Foley with Magdex. Katherine Reid and Andrew Boardman helped loot E/O. AMB and MW are both big, brown, and fuzzy.

Pseudo-Jadecomm: Black and tan clothes; pink and blue hair constrictors.

\goto{Old Business}

JFC blames JM for the shelves cluttering the library.

JM swapped 4 shelves in a cycle, causing H to gain some space, and is preparing to give PA an extra shelf.

More flooding last week.

C/P gained 5 shelves of space (12 faces of C/P can hold 10 rows, and we recently freed up extra shelf pieces to fill them up).

\goto{New Business}

New book dealer came over, bought 5 boxes of paperbacks (about 360 books). Will buy essentially all of our for sale magazines at 25 cents each. He will repeat in the future, every 6 months or so. We gave him half price on the Ps (he wanted about 20 percent of the saleable ones). Old book dealer may also take some.

...More talk of disposing of used books...

Used Anthony sells worse than McCaffrey.

A member was obstructed by the books in damnation alley recently.

\goto{Future Business}

Jade's arms will fall off, but be replaced.

Time warp to Old: behind the C/P shelf (which was moved) was a cool old Star Trek "pins and threads on velvet" art.

"Banana motion." (JM) Passes 8-0-5 +Spehn (the pseudo-onseck lets Jade get it wrong).

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
