\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/12/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 12, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the prodigal Onseck.

Minutes read.

Motion: Note that the minutes were inaccurately read.  This motion was
not seconded and thus ordinarily wouldn't have been recorded, but...

Motion: Instruct the Onseck to record the motion anyway.  Passes
15--3--1+Spehn.

Motion: Commend the Skinner for remembering how to count after
Christmas break.  Fails 5--7--2+Spehn.

\goto{Committee Reports}

Pseudo-Coofcomm: Our cunning plan to misdirect the Columbia University
Science Fiction Society has apparently succeeded.

Jadecomm: Jade's back, wearing an old hair thingy.

Motion: The Skinner is very entertaining.  Passes 19--0--3+Spehn.

Mobcomm: We got lots of hardcovers.

Pseudo-Bluebellcomm: Bluebellcomm has been lame, or absent, or both.

Jourcomm: By end of IAP.

Pseudo-Plantcomm: (Hefts a battery in stoic silence.)

Discussion of the back of the minutes, which are some kind of book
catalog.  In future years, the scrap-paper backs of the minutes will
provide a treasure-trove of archaeological information.

Motion: Other people need to be entertaining.  Passes ``because I
said so'', otherwise known as Skinnerial decree.

Committeereportcomm: No more committee reports to report.

\goto{New Business}

There are lots of new members.  At least three... no, two.  Well,
maybe one and a half.

``Do couples often shove fifty dollars in your face?''

The Skinner paid a fine, even though she had fine credit.  Can fine
credit be redeemed for valuable prizes?  A permanent membership,
perhaps, although that would just get the Skinner a photo of herself.

It's IAP now.  There's a new schedule, although it's pretty sparse
and mostly crossed-off.

Motion: Bing.  The motion was not seconded, but it happens anyway.

[Jade] ``I needed an excuse to bing.''  Jade missed her gavel over
break, everybody says ``awwww...''

\goto{Old Business}

Motion: Commend John for his diligence (in preventing a member from
checking out a new hardcover).  Chickens 3--4--6+Spehn.

There follows a weird discussion of fifty dollars, gavels, threesomes,
couples, etc.  Don't ask.

Next month John will be one third of a century old.

The CUSFS delegation finally shows up.

\goto{Time Warp to Committee Reports}

Pseudo-Coofcomm: They're here.

\goto{Time Warp to Old Business}

Marcus is still old, though he denies it.

The shelves are still here.  Calls to put this report into the
ALGOL to save time.

Motion: Have the Skinner chain/entertain us again.  Not seconded,
in part because of confusion about whether the motion involved chains
or not.

\goto{Future Business}

Jay actually had some old business after all.  It is remarked that the
business will probably still be old next week.

We need to unwedge Jamie to fix the shelves.  The fifty dollars might
help.  Or we could collapse the Internet economy, thus firing him from
his job so he has time to deal with the shelves.

Motion: Appoint John as the Committee to Unwedge Jamie.  Passes
10--3--2+Spehn.

\goto{Time Warp to Committee Reports}

Pseudo-Pianocomm: There is no sign of prentices, but we have a can of
Pledge to clean the library now.  It's on the random crap/Skinner
shelf.

\goto{Time Warp to Future Business}

``If you find them and threaten them, they will come.''  This is of
course in reference to locating prentices.

Discussion of VGG spelling.  The Onseck resists trying to put that
into the minutes without looking it up.

Motion: Commend John for being the worst offender.  Passes 17--0--1+Spehn.

Mobcomm$_2$: There's a big box coming Sunday from the Space-Crime
Continuum.  We'll need lots and lots of money.

Discussion of the financial form the LHE has been resolutely ignoring.
Turns out a different one is needed.  This is produced and signed.

Motion: Bing right now!  (The form was on the gavel block at that
instant.)  Passes by Skinnerial decree.

We need pens full of blood.  The Onseck is chastized for not having
any of them.  Special astronaut's pressurized blood pens are requested.

The Ucko donation has arrived.  Discussion of how to make this
appropriate for future business.  Perhaps in the future someone will
record this donation on the donation sheet.

What's the RDA of Jamie?  The LD/50?  ``That depends on the method
of ingestion.''

Jade insists on changing the subject.  ``I'll just bing repeatedly
until you shut up.''

Motion: Determine the LD/50 of bananas.  Passes 5--0--3+Spehn, even
though there are numerous outcries of protest at the vote tally.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
