\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/07/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 7, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1740 SST, Jade Wang, President and Skinner, presiding.  Ed Keyes is the cameraless Onseck.

Minutes read.

M: note that the minutes were incomplete as usual. 8-3-1 +Spehn.

\goto{Committee Reports}

Mobcomm: no time to get more books last week. Trying to get us to spend 100 dollars on Jack Vance collection. "Jack fans?!"

Pianocomm: new apprentice, Laura.

And neither of the people Steph brought in live in ET.

Signatoriumcomm: skinner needs to sign more cards. Jade does so while we wait.

Pseudo-pianocomm: one of our prentices has been doing Bluebellcomm off the shelf instead of her box. This is an old report but John missed it.

The TIF chart is getting dirty.

Pianocomm: a couple of prentices probably getting keys from helping with shelving.

Pseudo-theftcomm: jhawk briefly pulled ahead of John, but John jumped ahead again, on the way to Nirvana.

(Mike) M: "I am the serenest!" 4-7-3 +Spehn.

(John) "God grant me the wisdom to fear serenity."

The lock has been periodically updated and fixed. We need to do something with the old keys. Make a miniature gavel, or add to jhawk's collection.

Pseudo-JoeFoleycomm: we're screwwwwed!

Jadecomm: Jade's ponytail has reproduced. Soon she will be Medusa. We should shave her head to prevent the ponytails from eating her brain.

War Council: the Tech reported that there was a vote to move ahead with the proposal. Reasonably impartial article, except for "MITSFS claims to have 90 percent of sci-fi."

Pseudo-Chroniccomm: we will apparently not be sending SNF to G. Gordon Liddy. A problem with puns creeping into officer lists over the years.

\goto{Future Business}

The TIF will eventually move down by a row, and will do clever things to people not here over IAP.

(Jade) "The future is now, and it sucks."

Jade's thesis is about frogs. Frequency-resolved optical gating.

Rejecting rejection letters. (John) "Please accept me or I will have to work."

An ivory tower built from unicorns, using virgins as bait.

The invention of the knife allowed people to wear animals without their insides.

\goto{Old Business}

Shelving project is completed. Bought more equipment, shelves: some in storage, some in here. More than a ton of shelving, which was a pain. Large reimbursement forms will shortly be coming in. Keys to be awarded. A purple banana for wounds obtained, too.

(Jade) "She does something, I forget what, that makes her strong."

Jade's jacket and Jamie's shoes are getting old.

You should wear gloves but not sneakers when moving heavy objects. And when Jamie asks you to move shelves, you say NO!

(Jamie) "Anyone who bitches is volunteering to put them together."

Ellen's friend helped us move shelves as a birthday present.

\goto{New Business}

A new working group for the RR proposal is forming. Ed is our rep.

Implanting chips in people works better if they aren't random chips.

5 new members in the last 2 weeks.

\goto{Future Business}

M: miller motion. 2-11-1 +Spehn.

M: take all the snow that falls during IAP and make it into a giant banana-shaped Slurpee to reward the skinner for getting into grad school. 14-3-0 +Spehn.

(Bill) "This chair makes it easy to cast 4 votes."

\vspace{12pt}

\noindent
Meeting adjourned, 1817 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
