\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/22/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 22, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the actually-here-for-the-whole-meeting
Onseck.

Motion: [Jamie] ``Commend last week's minutes as `some parts match my
memory better than other parts.'\,''  Passes 4--2--2+Spehn.

Minutes read.

\goto{Committee Reports}

Mobcomm: We have new books, \$280 worth.  Give me money.  Our Pseudo-LHE
can't actually move to deposit cash, though.  We're pretty sure it's
because his appendix was removed.

Motion: Commend the Vice for having his appendix removed, but retaining
his index and table of contents.  Passes 3--0--2+Spehn.

Dexmistress: We got some hole-punched paper, and will have new dexes soon.

Panthercomm: The Schultz donation has started --- ta da! --- flowing.

Jadecomm: Jade has nice blue socks with Eskimos with green hair.
They were a gift.  [Jenwa] ``Yeah, they, uh, look like a present.''
[Jade] ``Once again we dissect my wardrobe.  Can we move on?''
[John] ``Gavel crush scissors cut clothes cover gavel...''  [Jade]
``Gavel beats everything.''

Pseudo-Plantcomm: Physplant did two useful things.

\goto{New Business}

Despite the Covenant of the Rainbow, there was another flood.
[Jamie] ``The bastard promised us...''

The visit of Natasha coincided with a flood from the {\em Technique} or
{\em Tech} darkroom.  Some punch cards and cardboard had to be tossed, but
pretty much everything survived.  The flood is also credited with
cutting off the building W20 network.  15 gallons of water were
cleaned up from the library.

Physplant started with a vacuum, then moved on to using the super
washer-buffer-squeegee machine which really impressed John.  Is Natasha
a Rain God, bringing her cloud worshippers with her to visit the library?

In cleaning up, we found some cool stuff including a larger companion
rainbow slinky.  Also on the plus side, the floors are cleaner now.
[John] ``It was not the usual afternoon in MITSFS.''

Let the minutes note that Jenwa is reading {\em Sense and Sensibility}
instead of sci-fi.  [Jamie] ``It sounds like it could be a Xanth novel.''
Looks of horror all around.

We have newly-accurate figures on membership, with many fewer undergrads
than we thought.  250 members, 105 undergrads, 70-80 grads, 45 alums,
10 staff, and 15 random.  This is ignoring people we know to be out of
the area, the ex-Skinners, authors, etc.

\goto{Old Business}

We got a bounce back from the picnic mailing.  It was sent accidentally
to one of the banned people in the membership books.

\goto{Future Business}

We should retaliate for the flood by annexing the {\em Tech} and
{\em Technique} spaces.  The fourth floor should be largely renovated
in a few years.  Plans for grabbing more space in the process.

Inventory will be scheduled soon.

Jade doesn't believe in the future anymore.  But she does believe that
the members ``exist''.

Motion: [Jade] ``I ate a banana recently.  It made me hungry.''  John
recalls a juvenile book (that wasn't {\em The Phantom Tollbooth}) where
entropy is reversed, leading to the possibility of a negative banana.
Motion chickens 1--0--11+Spehn.

Motion: Say ``hi'' in a chirpy and embarassing way to the member in a
banana-colored shirt.  Passes a couple--0--1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
