\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 07/20/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, July 20, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding. Ed Keyes is the parent-visiting Onseck.

Minutes read.

M: commend the reading as surprisingly coherent, as read from John's "fevered scribblings." Only John votes, motion does nothing 1-2-1 +Spehn.

Jade destroys an AOL CD with the gavel. It shatters but does not poke anyone's eyes out.

In Lincoln Lab bus, Rule 7 is "Do not be destructive." John was sent to the principal's office for being smashed into a bus window.

We got a piece of mail with a "Bang Head Here" pad.

\goto{Committee Reports}

The AOL CD has left some cardboard remnants. The heat of the impact melted the titanium?

Bluebellcomm: we need someone willing to cover Tolkien books. Jade may be willing to learn the black arts of Bluebellcomm. "But jhawk scares me and John doesn't." (Jade) A pat on the head is recommended in dealing with scary jhawks.

Mobcomm: books processed, on the shelves. No idea if they are any good.

Mobcomm2: The British publisher is finally getting around to sending us books.

Mobcomm3: Also have a possible source of British books.

Mobcomm4: (John is reading from notes.) The check from last week probably didn't bounce.

Discussion of where to hang the "Bang Head Here" block.

Jadecomm: "Are those your usual pants?" (John) "That sounds like the beginning of a bad pickup line." (Jade)

\goto{New Business}

How may AOL CDs can be smashed at once?

"My company had a mandatory outing in a park today..." (John) "Who did they out?" (Jamie)

The story continues with how 10 software engineers managed to get a barbeque started. Liquid oxygen is suggested.

New space in the circulating room. 10 shelf-rows in H, one new in PA. C/P have 5-6, due for 1-2 more.

Jamie wanted some quick help moving "a few shelves." "Eighteen hours later..." (John)

The "Bang Head Here" block is just a training for the true hardcore banging-head-against-gavel-block members.

A new copy of Seeker's Mask! Fulfilling the command of Skinner Jenwa from 2 years ago.

John tests the block, finds it mounted a little too low.

It is a good height for Jade, though, so it stays.

We accidentally got two copies of the latest Cherryh simultaneously, in defiance of Einstein. 

\goto{Old Business}

The second of 3 Bobcats has now left the library. People did not immediately pounce on the reuse posting.

Jamie remarks on an ad for the book Zen Sex. Zen and wozen? "Pretty wozen, walking down the street..."

\goto{Future Business}

Ed is reminded about F+SF.

Inventory, a week from tomorrow!

We need to do some fund-shuffling.

Realms of Fantasy still in print?

\goto{Time Warp to New Business}

The Tyrannical Iron Fist is now in effect. Jen Chung is winning so far.

M: not have a banana motion. 4-3-4 +Spehn.

M: keep Jade's shirts on because she might have a banana under it. 5-8-1 +Spehn.

Adjournment song.

\vspace{12pt}

\noindent
Meeting adjourned, 1745 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
