\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/07/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 7, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the power-ground-confusing Onseck.

Minutes read.

M: condemn minutes for including explanations. 4-3-1 +Spehn.

\goto{Committee Reports}

Pseudo-Plantcomm: Phys Plant fixed the air conditioner by turning it warm, no more water condensation. Also fixed the circulating room lights, sort of. Still flickering, maybe the same light and maybe not.

M: Send Phys Plant a letter saying they've become an efficient repair agency. If they can send us letters saying we're fixed, we can do the same. 2-0-4 +Spehn.

Pseudo-Theftcomm: John now plans to work down on the TIF.

M: rename John's column the JFC job dissatisfaction index. 9-0-0 +Spehn.

M: tie John's TIF performance to a large hamster wheel. Fast enough will power the lights. 1-1-2 +Spehn.

M: ow. (from the \bing) 4-0-1 +Spehn. Skinners get too good at binging...

The Tech has a bizarre report on freshman class size and FSILG participation.

Jourcomm: "TZ RSN." Jade: "...and don't stare at me like that."

Bluebellcomm: our new trainee (Jade) is working hard.

Mobcomm: I'm lazy but we got books anyway.

Pseudo-Bondcomm: is the month over yet? Should we punish jhawk with a giant hamster wheel? Take away keys one at a time?

jhawk stories abound. He claims to have an apartment, but won't even tell his girlfriend where it is. Should we use cemetery plots as permanent addresses?

Jade is starting to get hungry.

\goto{Old Business}

We helped rub the cleaning lady with a towel. (Err, rather helped her rub the slippery floor.)

Shelves getting full. 2 new in C/P. Harness the energy stored in high-pressure shelves.

M: commend Society for superior data-compression techniques. 5-1-1 +Spehn.

M: compress the books by converting to binary, then throwing out all the zeroes. 7-1-2 +Spehn. A friendly amendment was just generically friendly.

M: replace gavel with banana. 2-0-10 +Spehn.

Usual stuff.

\goto{New Business}

A guy at John's work has a dog with no tail. It instinctively herds small children.

M: make the corridor slippery by rubbing it with a banana peel. No second.

Dr. Whos going into circulation.

Getting too many ET new members. Malcolm: "Do they phone home regularly?"

M: commend anime makers for turning Das Rhinegold into a space opera.

Carl is slicing things up with a banana-colored knife.

M: take the banana-colored knife away and dispose of it in a suitable sci-fi manner. No second.

M: go home and take a banana-colored nap. No second.

John has no reason to leave if there's no dinner trip.

Plant a tracking device on jhawk to find out where he lives. Carl tries to look him up online.

\goto{Future Business}

M: condemn this phase of business for being very boring. 4-2-1 +Spehn.

The Anime Club will have a special sci-fi themed show next week, co-sponsored by us.

Jade is very tired. Time to adjourn for 6 days and 23 hours?

M: suck this meeting into infinite recursion. No second.

John thumbs through Hacker Art.

M: skinner should go buy a banana at LaVerde's then go home and go to sleep. 8-4-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
