\documentclass[12pt]{article}
\setlength{\topmargin}{-0.75in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/15/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 15, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and Skinner,
presideing.  Ed Keyes is the botmeister Onseck.  John Carr is the
backstabbing assistant onseck.

Minutes read.

Motion: Repeat the last motion in the minutes.  No second.

Motion: Commend the minutes as not being the Onseck's responsibility.
Passes because John's feet (which voted ``no'') defeat everything.

Motion: Commend the Onseck for being irresponsible.
(Jade threatens to saw off John's feet with a pocketknife.
Motion: Get John's feet out of the library.  Passes \hbox{10-0-2+Spehn}.
John offers to remove his socks.  A compromise is reached: John's feet
can remain in the library if he puts shoes on them.)
Passes.

\goto{Committee Reports}

Mobcomm: Will get some more books one of these days, maybe Sunday.
John will wear shoes while getting books.

Jadecomm: Jade's color balance is off: lemon and khaki.
Even her hair constrictor is a different color.  People
call for a blacklight.

Bluebellcomm: There seem to be fewer overflow boxes.

Jamie finds an extra overflow box near the couch.

Bluebellcomm$_2$: Never mind.

Pseudo-theftcomm: The week-by-week schedule seems to be working.

Pseudo-pianocomm: Katherine Reid was here and got pinged.  We should
mug her the next time she omes into the library --- grab her and lock
the door --- because that is easier than mugging her elsewhere and
dragging her back here.

\goto{Old Business}

People are continuing to check out stacks of books.

Jade forgets the usual procedure.  Jamie functions as a teleprompter.
Or is it a guide vocal?  No, it would be a guide vocal if he were
singing, and nobody wants that.  Jamie sings badly unless there are
a lot of other people singing badly too.


\goto{New Business}

Jade comments about singing in the library: ``I didn't say they weren't
trying to be bad, just that they succeeded.''

ASA may move us to the reading room.  This will probably cost us a lot.
There may be paid keyholder hours.  MIT libraries probably won't be able
to contribute any money, unfortunately, and they no longer control the space.

Jade exclaims, ``It's hot!!''  Discussion follows about whether the Earth
will spiral into the Sun due to gravitational radiation, solar wind
pressure, Poynting-Robertson drag\footnote{Although this does make
the Earth spiral into the Sun, John meant to say the Yarkovsy effect}, etc.

Motion: Encourage the MIT Libraries with their infinite resources to
air condition the outside.  Does this mean they will dump all the heat
inside?  Passes \hbox{a lot-4-4+Spehn}.

{\bf TAG!}

Any other cool motions?  Apparently not.

Jamie talks about a tag-team marathon.


\goto{Future Business}

Jamie: There is a new theftcomm envelope on the ZGT.  Use it.

We got an Archivalware catalog, so now we can order containers to
help preserve our coin and stuffed animal collections.

The Telzey approves of the Skinner's motions.

More acknowledgement letters will go out soon.

Jade predicts bananas will melt in the heat.

Jamie moves to get the skinner her favorite treat: a chocolate covered
arctic banana.  Jay offers a friendly amendment, or rather a {\em very}
friendly amendment: ... stripped, washed, and brought to his tent.
Passes unanimously.

\vspace{12pt}

\noindent
Meeting adjourned, John-is-pissed-at-Jade-time.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-onseck}

\end{document}
