\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/26/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 26, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the grayscale Onseck.

Minutes read.

Motion: Minutes are wrong, wrong, wrong!  Passes infinity--4--5+Spehn.

\goto{Committee Reports}

Panthercomm: We're not lame!

Pseudo-Panthercomm: (points to the rather full Panthercomm shelf)

Jourcomm: {\em TZ} is essentially complete except for jhawk.

Pseudo-Jourcomm: Is disco back?  (referring to Yevgeniya's outfit)
[Jade] ``The voices, the voices told me to dress like this.''

Discussion of Jade's gavel art.

Mobcomm: T.C. Skinner is now a member of the Science Fiction Book Club.

Jourcomm$_2$: We're doing a reprint of {\em TZ} 42 as well, and even
scanning it in for online preservation.

Cardcomm: We have a bunch of new punch cards from the reactor, but
some have too many holes to be really useful.

Discussion of the Society's logo.  ``When did the guy with the blaster
grow a third leg?''

Motion: Condemn the Chancellor and the Skinner for having their own
meeting.  Passes lot--0--3+Spehn.

Pseudo-Pseudo-Jourcomm: We commend Jourcomm for being between the
gavel and Bill (to block the sound).  Fails 6--7--2+Spehn.  The bing
had an ``agonizing sustain''.

Jade drove a van to Vermont last week.  [Jamie] ``Never go to Vermont
without hostages.''

Pseudo-Pianocomm: We are sad.  No new prentices are popping up.

\goto{Old Business}

Someone processed the first three boxes of some donation.

A package arrived from and by George Phillies, the ``permanent
deceased librarian'' on the old organizational chart.

John is decorating the ugly gray shelves.

Motion: Condemn John to death for lying to the Skinner.  Passes
7--4--0+Spehn.  John asks to be able to choose the method of his
execution, {\em a la} Monty Python.  The Vice, however, refuses.

\goto{New Business}

And just as we arrived at the present day...

\goto{Time Warp to Old Business}

The floor got dirty because John stopped thinking about getting a
floor mat.

Motion: Condemn John for not having enough dirty thoughts to keep
our floor clean... to death!  Passes 7--4--0+Spehn.

\goto{New Business}

John discusses eating dirt.

Our ad showed up in {\em The Tech} on Wednesday, but no one was
probably here to handle the hordes of weak-minded folks able to
be influenced by advertising.

\goto{Time Warp to Committee Reports}

Bluebellcomm: We're not as lame as usual.

\goto{New Business}

A bunch of stuff piled on top of the ZGT falls on Jamie.  All of the
members are glad that we no longer store fluorescent light bulbs up
there.

\goto{Time Warp to Old Business}

Some old papers were discovered in the junk that fell.  A spacewalk
poster, too.  Some empty poster tubes, which the Vice immediately
claimed in order to beat people with.  A magnetic tape, probably an
old copy of Pinkdex.

Motion: John time warps too much, so is now trapped in an infinite
time loop.  Passes lots--8--0+Spehn.

John demonstrates the use of Pledge on an old painting.  It's
probably hazing to put pledges inside of aerosol cans.  It is advised
to never use Pledge on pianos.

\goto{New Business}

John tries to say something but is trapped in a different time.

Our promised yearbook photographer is lame.

Also on top of the ZGT is a collection of ASCII art of women in and
out of bikinis.  Very dusty, and quite unimpressive.

\goto{Future Business}

The photographer guy might be here soon.

There will be a massive reshelving next weekend.

The female members are immune to being offended by ASCII art.

Something about Picniccomm business.

The photographer is here.  Past photos have always been involving
gavels and bananas, and the tradition continues.

Motion: Not to make any banana motions.  Passes 8--0--1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1805 SST.

The photo happens.

John is reported to be almost as good as the Telzey Toy.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
