\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 1/19/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, January 19, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Yevgeniya Nusinovich the
Great, Vice and Pseudo-Skinner, presiding.  Ed Keyes is the
dish-installing Onseck.

2001 is the monkey year... you know, the one with the dancing ape.

Minutes read.

Motion: Approve the minutes as entertaining.  Passes 5--3--2+Spehn.

\goto{Committee Reports}

Pseudo-Panthercomm: Panthercomm is lame, lame.

Pseudo-Bluebellcomm: Bluebellcomm is lame, lame, lame.

Pseudo-Coofcomm: The Columbia delegation came and took away some of
our rites.  Rights?!?

Bluebellcomm: Our razor has vanished.  This is a minor crisis because
at least one of our committee members is not allowed to use scissors.

Motion: Buy crutches for Panthercomm and Bluebellcomm (because they're
lame).  Chickens 4--0--4+Spehn.

Pseudo-Pianocomm: Should we draft (former Skinner) Marcus as a prentice?

Jourcomm/Pseudo-Pianocomm: We found a sucker to be a prentice {\bf and}
help with {\em TZ}.

\goto{Old Business}

Yevgeniya clanks instead of binging.  This might be due to interference
from her brass rat.  Discussion of physics and center of percussion.

Motion: Command the Pseudo-Skinner for being unhinged.  Passes
8--0--2+Spehn.  The Pseudo-Skinner ponders overriding the vote count
but eventually doesn't.

Shelves still here, usually.  Usual stuff.

\goto{New Business}

[Yevgeniya] ``Binging is fun.  Gratuitous binging is even more fun.''

John cleaned out the bottom of the ZGT, uncovering a long-lost little
sign that says, ``Please keep this space neat.''  He threw away some
broken glass, kept an empty frame.

We might be trapped in this meeting because the hallway is barricaded
by furniture and police tape.

\goto{Future Business}

Boskone is coming soon.

Jerry Anderson is still alive and apparently working on some sort of
top-secret project.

Random discussion of old sci-fi series that the Onseck has neither
seen nor heard of.  Purple wigs?  Attuning oneself to crop-harvesting
cycles.  Tangaean mind-melding works by physically interpenetrating
someone's head.

Discovery of spoons in the drawer.  John attempts to play the
adjournment song on the spoons.

Motion: Scoop a banana out with the spoons.  Passes 5--0--1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1725 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
