\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/28/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 28, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie, Pseudo-President and Skinner, presiding. Jenwa is the Pseudo-Onseck.

Minutes read.

M: pseudo-onsecks duke it out. Lazily chickens 0-0-3 +laziness +Spehn.

\goto{Committee Reports}

Mobcomm: S-CC new books box came in. Bill got 4 bags of books and spent more money, beating John. Each got a Warhammer book, but they were different ones.

\goto{Old Business}

Foley came with power tools, attacked the coatrack holder, and left his hat here... or maybe it's not his hat...

No more For-Sale shelf.

Circ room reshelving progressing slightly.

Damnation alley in awful state- not safe to go back there.

ALGOL.

\goto{New Business}

New poster about Harry Potter, LoTR, and Star Wars.

Bank of jhawk was closed today- he was [illegible], shockingly.

New membership rates up, making R/O special permanent (4 years for the price of 3, all the time).

John wants an atomic membership (tied to the Doomsday Clock).

There is no IAP membership. Possibly no summer membership either. The timewarp cost us 25 cents.

\goto{Future Business}

M: appoint Jamie Supervisor of Banana Activities. Passes 5-0-0 +Spehn. With lots of bananas watching.

\vspace{12pt}

\noindent
Meeting adjourned, 1723.75 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Jenwa, Pseudo-Onseck}

\end{document}
