\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/23/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 23, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and Pseudo-Skinner, presiding.  Ed Keyes is the turkey-gobbling Onseck.

Minutes read.

Discussion of first occurrence of Jadecomm.

M: condemn the onseck for not looking this up. Unfriendly amendment to change to "commend." 0-2-2 +Spehn.

\goto{Committee Reports}

Mobcomm: 31 new books. Some Dr. Who, no Buffy.

Pseudo-Panthercomm: jhawk processed the one book he approved of already.

Mobcomm2: update: actually two Buffy books. Awesome comic fantasy.

Pseudo-Hasslecomm: 3.5 boxes of overflow. Need to assign prentices over IAP.

MITSFSrootcomm: we have a color monitor from Ellen, small but lots of pixels at least. The s key is broken.

Pseudo-Theftcomm: jhawk has almost caught up to JFC due to holding lots of isolated hours? A stealth keyholder using pencil to sneak up.

Pseudo-Pianocomm: Josh Weaver started on third and largest box of Bluebellcomm stuff. C/P rearrangement ongoing and not helping a whole lot due to decompression.

Chroniccomm: a new draft of SNF1 ready for proofing. Requests that any members dying should change name to a sci-fi pun to make our job easier for donations.

War Council: the UA mostly approved the RR proposal, a vote at the next meeting. If it passes, a working group will be formed to work out the detailed proposal. Goal is the Strategic Planning Committee (TM), to fit in with the Plan. 18 month delay is in there somewhere. Optimistic ideas of IAP or summer are impossible. The Tech seemed to approve in their article.

Jadecomm: Jade is in NJ. The long-distance stalking plan is in progress.

\goto{Old Business}

M: commend Jade for putting on a new jersey. GROAN.

Attempting to grab lawyer shelving soon, since we will have to survive in this space for 18 months. Store rest of it in a warehouse? Will cost, but less than buying shelves.

ALGOL...

\goto{New Business}

(John) "What about the usual everything?"

New book "The Grand Ellipse," just crying for a sequel, the grand parabola, etc.

The "Discrete Log" is a book on crypto, or on softly-talking trees?

(John) "Hasn't it been a few weeks since we got a new Xanth book now?"

\goto{Future Business}

Mobcomm run soon. Schedule around shelving run.

The lock has been installed, and has been taking mostly everyone's card. John tests this.

A large donation from Bob Mason soon.

Purchase of a floormat for the snow season?

jhawk has a new keyholder picture, although kind of small.

Miller motion. 2-4-1 +Spehn.

Monsters, Inc. is a good movie. Is this a Moocomm report?

John wants money.

Jamie is desperate to have a motion to end the meeting...

M: move to prod jhawk with a banana. 3-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1752.5 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
