\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/19/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 19, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the music-videoed Onseck.

Minutes read.

M: correct the minutes from "censure" to "censor" jhawk. 3-1-3 +Spehn.

M: condemn JFC for caring about spelling of the minues. No second.

Jade destroys another CD. Not very thrilling. \bing \bing

John: "I've watched my kettle boil."

John has recently stopped receiving AOL CDs. Ed: "Are you sure you're still alive?" He's been going by his employee ID number now.

\goto{Committee Reports}

A parent comes in, and is scared by the sheer size of the library.

Pseudo-Theftcomm: John moves the complaint sheet down 2 inches to make it more visible.

Mobcomm: shipment coming in a few days. Quote from Terry Brooks in SFBC newsletter: "Although the number and size of my books sometimes mystifies and bewilders me..."

Pseudo-Telzey: we need a more durable heart-shaped slinky. Is the Telzey an assigned committee post? The skinners usually try it, anyway.

Pianocomm: Jade sent out emails, a prentice is actually here too! Doing Bluebellcomm, shelving.

A pre-meeting argument broke out about lengths of book-covering material between Jade and John.

Chroniccomm: SNF RSN.

What committee is the lock?

Plantcomm: the light fixture is still not totally fixed.

Dexmistress: our net drop has been... more activated. All sorts of weirdness in IS case tracker. The bad block check on the drive is taking way too long.

Pseudo-Theftcomm: tomorrow John will break into the third sheet of the TIF.

John: "I just remember it had a flying skull and Sean Connery in a diaper."

"Bheer" is an SF reference to non-alcoholic beer. "Whine" too. So should Pubcomm be Phubcomm? Bheercomm?

Jade: "You made a twisted piece of... thingy."

The investment value of beer vs. tech stocks. Beer is better in the can recycling profit.

Pseudo-Bondcomm: what should we do about jhawk?

Jamie: "People have been asking that for years." Bondcomm vs. Bondagecomm vs. Bond(age)comm.

\goto{New Business}

An anime convention in Boston Hynes, this weekend.

Lock progress. They're really about ready to be changed, but 4 people have no record in the card office. And amazingly enough, they agreed to delay the installation. Also have a card for George Flynn now.

\goto{Old Business}

Jenwa is reviving her old jacket. With safety pins.

Jenwa: "It's almost more comfortable broken."

Aside about Old North Church bell dissonance.

Weird Malcolm story about a bell-tuner drinking ink as a poison antidote. All the Yale bells were donated by a plumber, so the students flushed all the toilets at once.

M: flush all the toilets in Harvard at once in protest of their bells! 8-0-1 +Spehn.

John: "Anyone want to see a picture of chickens on a bicycle?"

M: revive the skinner by feeding her a banana. No second.

Jamie's throat is sore, so no adjourment song.

John: "The one time I got complimented on my pronunciation in French class was when I had a sore throat."

\goto{Future Business}

M: stuff a banana down the back of John's throat. 2-4-2 +Spehn.

M: count the items in the Infinite Banana Buffet. No second.

Miller motion. Fails something-5-1 +Spehn.

M: demonstrate our faith in the skinner's world-shattering power by stuffing a banana down the back of John's throat. Something+Jamie-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 174... no, 1750 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
