\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/21/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, September 21, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Stephanie Fried, LHE and
Pseudo-Skinner, presiding.  Ed Keyes is the laptop-toting Onseck.

Minutes read.

M: commend minutes for having 15 percent less context than previous minutes. 6-2-2 +Spehn.

Steph: "I'm in ocean engineering, there's a lot of WAVES, okay?!?" (Reference to lack of bing resonance)

M: condemn meetings Steph's been to recently as being too orderly. Fails by skinnerial decree.

\goto{Committee Reports}

Mobcomm: a dozen Buffy books in the ZGT. Should we continue to get these? Jenwa reports them as at least partially good. Quite silly, but good, and quick to read. One is a serial novel, even.

Pseudo-Fweekcomm: sent out a second mail to MITSFS-midway with the term schedule.

Bluebellcomm: a little less scared, a wall of paperbacks hiding some of our hardcovers.

\goto{Old Business}

The shelf vendor has finally sort of replied. A law company is still interested in donating shelves assuming we can put a good word in with President Vest.

John provoked Jamie into rearranging shelves again by shelving books badly.

M: condemn John for being very very bad. No second.

M: condemn Jamie for trying to condemn John. 5-8-0 +Spehn.

Steph donates a pen that is almost out of ink and capless.

APO book exchange happened; we need to pick up money and leftover books.

The reading room issue is still being debated in the ASA. The GSC doesn't care.

Finboard is really, really dumb.

Usual stuff.

\goto{New Business}

Bings are improving. Finboard is dumb, Steph starts ranting about this. Asked us to appeals to ask where our library is.. though they're 30 feet away from us, in the UA office, at the time.

Call for more prentices... step up the recruiting, says Steph.

Jourcomm has a new skinner rant and a story from her. John is still pretending to write a review, to some degree. The book he intended is now out of print.

M: commend whoever it is for producing paving material (i.e. the road to hell...). No second.

Tor is coming out with a young adult line, starting with a 2-part "Eye of the World." A condensed version? You can make any books sound terrible by summarizing it. "There was this cuckoo trying to kill a white whale..."

John sold 3 memberships yesterday, but only one is new, and Jade should get the credit.

New magazine subscriptions soon... "Dreams of Decadence."

\goto{Future Business}

This year's rerooming may be swifter than usual... IAP instead of summer.

John's TIF will be completed later than it first appeared.

M: install in John's hamster cage a banana-colored night light so he can keep running. 8-1-0 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned... 1750, yeah, 1750 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
