\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/24/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 24, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the scrap-paperless Onseck.

Minutes read.

M: approve readings as "scrappy." (We are down to 5 pages of scrap paper.) 4-3-2 +Spehn.

\goto{Committee Reports}

Pseudo-Somethingcomm: Tech violated Rush rule with a newspaper ad to join the Tech. John: "Oh, that's why all their stuff is in the hall." Jade: "Maybe we'll get their space!" Turned over to the Thistle?

M: use character pointers for a gavel cozy. 8-2-0 +Spehn. (The Onseck probably didn't hear that right.) "Counterpoint."

The AOL CD is pounded by the gavel. Beat but not shattered... cool.

M: commend skinner for breaking another record. 7-0-3 +Spehn.

John: "Can you read the bits?"

The gavel block is wrapped in Counterpoint.

Mortcomm: Fred Hoyle died this week, cosmologist and author. Wacko theories that sometimes turn out right. Named the Big Bang.

Discussion of interesting theory for how universes can cross in extra-dimensions to simulate a Big Bang without a singularity. Heat up everywhere almost at once. The Onseck resolves to find this paper.

Crossover to the Brookhaven destroying-the-universe bit. "If it's going to end, we might as well cause it ourselves."

James Blish wrote a couple novels where he destroyed the universe. The Onseck resolves not to read this series upon hearing it further described.

Pseudo-Pubcomm: Bulletin board has been refreshed.

Bluebellcomm: "We got another one." The skinner can now cover books.

Pseudo-Theftcomm: The median on the TIF has advanced by 10 hours over 5 weeks. Yay!

Pseudo-Fweekcomm: There are froshlings here. Eeep!

We have about 400 Star Treks and about 300 Dr. Who. There is one crossover novel, even.

People throw money at John for mysterious reasons. More money follows when it's revealed this will keep him from singing.

Shelfcomm: the shelf vendor still exists, working on our request.

\goto{Old Business}

Summer happened. Still?

The Chamber is theoretically engaged in reviewing the fine-credit-for-membership policy.

Transfer from endowment to bank account has happened, money for shelves and binding.

Usual stuff.

\goto{New Business}

M: condemn froshlings for not being here. Does nothing 5-4-something +Spehn that works out.

New Pinkdex given to MIT Libraries, 500 dollars for us, yay, if we get the account number right.

Minicult: The Herald review of Ghosts of Mars says it's not as memorable as "Plan 9 from Outer Space."

T.C. Skinner received a special invitation... they wanted to know if it was Mr. or Mrs. It's Miss!

We've asked the Libraries to sponsor a card for George Flynn.

The skinner is hungry. John vetoes the dinner trip until 7 since he signed up for hours.

The little yellow creature has acquired a toy, and the junk book box is now empty. Jamie gave "The Road Ahead" to the Salvation Army.

Discussion of how things melt, including candy and humans. Diamonds just vaporize, evidently.

The new schedule's been posted. Jade may need to switch hours because of her yoga class. She may switch to akido. Jamie took a cool yoga breathing and posture class.

\goto{Future Business}

\bing \bing \bing \bing The skinner abuses the Counterpoint on the gavel block. Carbonized some of the paper.

In the future we will probably get two donations. Circulating copies of Dr. Who, yay.

M: frosh should buy memberships. 8-0-8 +Spehn.

The new Andre Norton "Time Traders" Omnibuses have been edited from the originals. Should we still get them? Yes. 50s references updated?

Jade is starving.

Future meetings will be at 5:30, just like now.

"TZ real soon now." Jade should write a 14-page rant? 7 pieces now.

\goto{Imaginary Business}

Minicult: in Japanese, "blue" means green.

MIT women only have one thing on their minds: dinner.

Jade triple-dog-dares Ed to make a banana motion.

Ed: "Second." 8-0-1 +Spehn under protest.

\vspace{12pt}

\noindent
Meeting adjourned, 1750 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
