\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/4/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 4, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and
Pseudo-Skinner, presiding.  Ed Keyes is the guest-lecturing Onseck.

Minutes read.

Motion: Approve the minutes as Gor-y.  Passes two arms--no 
one--philosophical conundrum+Spehn.

\goto{Committee Reports}

Pseudo-LHE: John both took and spent all our cash.

Motion: Warn the LHE that someone is taking her job.  Not seconded.

Motion: Make a third motion.  Not seconded.

Pseudo-Picniccomm: The invitation got sent out, after a ``trial run''
with a bad mail script.  There are some problems with a hundred-person
limit on the MIT mailer.  We have a car for grocery shopping, but we
still need people for it.

Mobcomm: I am lazy, but we still get more books.

Pseudo-Hasslecomm: They're two boxes and a shelf away from the
ground state.

Motion: Collapse Hasslecomm's wave function.  ``Passes without an
actual punchline'' 5--1--3+Spehn.

Pseudo-Bluebellcomm: Bluebellcomm is falling behind again.  There
are lots of weird new books, because they say so.  The obligatory
``I get weirder things free in my breakfast cereal'' quote is
produced on cue.

\goto{Old Business}

We have some ex-Skinners in the meeting, and email from even more
of them, passing on news to us and congratulations to Jourcomm.

The Star Chamber met, but the contents of the meeting are a deep,
dark secret.  [Jamie] ``I could tell you, but then I'd have to kill
you.''  [John] ``Can you just give me a hint and hurt me a little?''

\goto{New Business}

Our two slinkies (the rainbow-colored one and its new heart-shaped
girlfriend slinky) were apparently having sex, in violation of
Skinner policies.  The heart-shaped slinky is [Jamie] ``the perfect
gift for someone who wants to make your heart go thump-thump-thump...
down the stairs.''

There is a new donation from Sherrian Lea.  There was also an
anonymous donation of about a hundred books in really pristine
condition.

The summer rates are now up.  In the fall, the rates will inch up
to \$12/year, with a monthly discount for mid-term memberships.
Now we have to hurt John, as a Star Chamber secret was revealed.

For the first time, Yevgeniya has rejected a submission to Jourcomm.
Rather, it was rejected for being bad, as opposed to bad fanfic.
[Jamie] ``Unfortunately she wrote `no' in the wrong place, and now
is no longer marrying Aaron.''

\goto{Future Business}

A hand-picked Star Chamber is ready for election.

Motion: Alter the procedure to tentacle-pick the Star Chamber instead.
[Jamie] ``That's a slinky, not a tentacle.''  The motion fails
no tentacles--several limbs--Cthulhu+Spehn.

We will transfer some funds around in the future.

In the future the LHE will be in France, embezzling funds in francs.
Maybe she can pick up the 2200 Perry Rhodans from Germany.  John
will be in Acton.

Elections are in one week.  We'll meet here, then migrate over to
the Star Chamber, 5-216.

Motion: Note that in the distant future, someone will set fire to
all the Perry Rhodans, thus ruining the atmosphere.  Not seconded.

On that note, John heard that global warming will fix the hole in
the ozone layer, by promoting more atmospheric mixing.  [Ed] ``Strip
mining prevents forest fires.''  John sprays an aerosol can to
celebrate... ooh, lemony...

Motion: Polish the floor with a banana peel.  The motion was lightly
killed and covered in chocolate, 4--1--5+Spehn.

Motion: Pass a banana motion and split.  Chickens 3--1--4+Spehn.

Motion: Combine that with an Albanian motion on Malcolm.  Passes
3--2--3+Spehn.  There follows a bad pun involving a wave-motion
cannon, but no one but the anime fans get it.

Motion: Beat all the chickens in the room over the head with a
banana.  Passes 15--0--John+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

Oops, we forgot the Jadecomm report.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
