\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/9/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 9, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the 310K-blackbody Onseck.

Minutes read.

Motion: Continue the trend to not have any motions regarding the
minutes.  Passes 11--1--7+Spehn.

[Yevgeniya] ``My limbs are too busy to vote.''

\goto{Committee Reports}

Pseudo-Theftcomm: The plastic covering on our bulletin board is
coming off.  We need to get some plexiglass or something.  The new
schedule is online.

Jourcomm: {\em TZ} is here!  {\em TZ} 46 RSN.

Mobcomm: The book trickle continues.

Pseudo-Whateverjamiewouldhavecalleditifhewereherecomm: The shelves
got moved, yay!  With pizza.  The hardcovers may have been scrambled
a little bit.

\goto{Old Business}

The shelf moving happened.  As a byproduct, the shelf codes that no
one ever looks at (mainly the various doubles) have been moved in
order to give the LP's some space.

Tempuscomm: The clock has been moved back to where it used to be,
now that the shelf isn't blocking it.  John didn't notice.

George Phillies sent us a book of his, and it's even weirder than
the back cover blurb, which is impressive.

Term started.

Usual stuff.

\goto{New Business}

There are vending machines where you can buy worms and other creepy
stuff.  Does dirt count as worm food?  A minor debate over how worms
breathe.  A bad pun about opening a can of worms.

The Japanimation Society may be showing Pratchett's {\em Wyrd Sisters}
tapes because they have a poor grasp of geography, confusing the
island of Britain with that of Japan.

Religious-based time travel?  Science fiction novels with a discussion
section for schoolkids.

Motion: Have John think in one of the cans after we get the worms out.
Passes 15--0--6+Spehn.

John's infamous picture of the hairy chicken.  A connection to
peril-sensitive sunglasses and towels.

``Sadly, this is true.''  ``Truly, this is sad.''

Jamie has a revelation about the shelves to be purchased.  There is
a request for a hammer if we have to put any more of them together.
Or a mallet, really.

\goto{Future Business}

There is apparently no future.  Calls for more bings.  \bing \bing \bing

We will be ordering shelves soon, and will get them at least three bings
in the future.  ``Three bings for the elven kings...''  There are groans
all around.

Discussion of the {\em Lord of the Rings} movies, and movie release
schedules in general.

In the future we don't need Bill, because we now have a new tape
dispenser that doesn't require his skill and strength to change spools.
There is a proposal to implant a giant electromagnet in the tape
dispenser to prevent its leaving the library.

Motion: Acquire a banana monopole.  Passes lot--1--5+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
