\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/6/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 6, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1715 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the Debianized Onseck.

Minutes read.  The Skinner kneecaps herself with the gavel during
the reading.

Motion: Read last week's minutes next week, or maybe just that last
motion over and over.  Passes 5--0--4+Spehn.  [Jade] ``Putting your
foot on top of the table doesn't count!''

Motion: [Malcolm] ``Move to table the foot.''  Not seconded.

\goto{Committee Reports}

Mobcomm is brought to you this week by the number 25.  We can blame
jhawk for ruining the numerical progression.

Pseudo-Jourcomm: Although she denies it, Yevgeniya would be happy to
get book reviews in the next week or two.

There is some confusion about Amazon sending us review books.  Who
ordered it?  Probably Bill... no... maybe Amazon just likes us.
[Jamie] ``That's why they aren't making any money.''

Motion: Thank the Easter Book Bunny for the new book.  Not seconded.

Motion: Come up with a good meaning for the phrase ``thank the bunny''.
Passes 12--0--1+Spehn.  ``Nice sustain.''

Jamie reads a blurb about rednecks and trailer parks.  Characters so
real you can smell them...  We don't want any {\em multi}media novels.
No smell, taste, vertigo, etc.

Motion: Move to approve tasteless novels.  Not seconded.

Motion: Make the Skinner happy by tasting her in the library.  Fails
by Skinnerial decree.

Pseudo-Hasslecomm: Stuff was done, yay.

Pseudo-Bluebellcomm: Bluebellcomm is lazy, shiftless, incompetent,
and so forth.

Motion: Commend Bluebellcomm for being nasty, brutish, and short.
Passes 9--0--1+Spehn.

Motion: Use Andrew as the new standard for height, Jade for niceness,
and Ed for civilized (that is, if you're shorter than Andrew, meaner
than Jade, and less civilized than Ed, you're ``nasty, brutish, and
short'') (amendment) and have them plated with iridium.  Passes
9--0--2+Spehn.

[Jamie] ``You know the penalty for voting twice...''

\goto{New Business}

The Media In Transition series has apparently asked Arisia for money,
which is a bit odd.

It's Campus Preview Weekend.  Someone should review the campus for
the {\em TZ}.  Does MIT have more or less corridor than the Kremlin,
or was that ever actually settled?  Do catacombs count?  MIT versus
the Vatican versus Mammoth Cave.

John is amazed at MIT-brand bottled water.  ``Distilled drinking water,
absolutely the purest, freshest, best-tasting water you'll ever drink.''
It is probably better than John's brown sink water.  Is rust brown or
orange-colored?

[Jade] ``Did you guys see The Cheez-Whiz People?''  Everyone thinks
she is hallucinating, and further explanations only reinforce this
conclusion.

Minicult: According to {\em Skunk Works}, Lockheed couldn't get a
contract for the stealth fighter because their predictions for the
stealth capabilities were too good.  The model test failed because
the radar was reading the pole instead of the plane model on top
of it.  They needed to make a stealth pole to proceed.

[Jamie] ``What do they use on the plane?''  ``Cheez-Whiz.''  It's
mostly geometry, actually.  The stealth tech came from a paper that
wasn't secret, just amazingly hard to read.

[John] ``To bring this back to the subject of spiders...''  Bats
use radar, of course.  They kept bouncing off the stealth planes.

Motion: Send John as an ambassador to The Cheez-Whiz People to talk
to them about spiders.  Chickens 4--1--4+Spehn.

Someone sent us a \$3.50 check wrapped in a piece of paper labeled
``Stabilization of the Post-War Economy''.  The LHE can finally close
our World War II books.

\goto{Old Business}

Negotiations are in progress with the local shelving company.  We
hope they don't go out of business in the mean time.  Evidently once
before a company burned down while we were in the process of buying
stuff from them.

Discussion of magazines and the Skinner shelf.

John cleaned out the right-hand side of the keyholder desk, disposing
of tons of loose staples, etc.  It's now organized, yay.  Susan is
credited with dealing the with the kamikaze attack staples (that
disable the stapler).  Did we just destroy a growing staple
civilization?  Upon further discussion it is revealed that the
evolutionary sequence is actually paperclips to coathangers to
bicyles.

\goto{Future Business}

In the future all the prefrosh will be gone again.

Discussion of the beloved status of the Onseck.

[Malcolm] ``I have seen the Schultz.''  The nickname came from a talking
beer mug in an old commercial.  Jamie's mother was the matching mug,
named Doolie.  Fuzzy Pink was named around the same time.  Discussion
of the timelessness of the Society.

Motion: Request the Onseck to suggest an audiovisual aid for the
future reading of the minutes (amendment) plus taste, smell, etc.
Passes 9.5--1--1+Spehn.

Motion: Calibrate our multisensual devices against an iridium-plated
standard banana.  Passes 6--1--4+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
