\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/12/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 12, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1707 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the office-moving Onseck.

Minutes read.

John: "I won a staring contest with a sheep once."

M: declare last week's minutes 100 percent context-free. 1-1-3 +Spehn.

\goto{Committee Reports}

Pseudo-Pianocomm: people still need projects, severe shortage of undergrads.

Apathycomm: Jade: "Yay..."

Bluebellcomm: who covered books? Some amateur work.

TV Guide continues its record. First new season episode of "Andromeda" was listed without info at all.

Andromeda is a galaxy, a constellation, "and also a strain." (John) Holo-Andromeda arguing with robo-Andromeda.

Jade does weird things with heart-shaped slinky pieces.

Jourcomm: could use some reviews. Andrew tries glaring and looking sad. Mars needs women, and TZ needs reviews. A missing original of Jade's gavel fashions?

The Nobel Prize was awarded for "making atoms sing together."

Jenwa: "If anyone finds a hair thing, it's probably mine."

Jadecomm: the skinner is wearing a ----- outfit.

Jadecomm: the skinner is reading "a lush and haunting novel of a city steeped in decadent pleasures."

M: commend the skinner for decadent pleasures. 14-0-1 +Spehn.

The Onseck is surprised he missed this Hambly novel.

SFBC is still sending mail to a 27-year ex-skinner.

Mobcomm: even more Buffy books in hardcover we could get. Andrew donates an "Aboriginal SF" issue. Are they still publishing that?

Pseudo-Theftcomm/VGG: Ellen reports that we have half the bookdrop slips, perhaps because of TIF. Or because of the contact poison on the bookdrop.

In completely unrelated news, the frequency of abandoned books outside in the hall has gone up. Phys Plant usually takes care of the bodies.

John grabs the gavel and bings to prevent Malcolm's pun. Everyone gasps.

\goto{New Business}

jhawk was upset at using the APO slips as bookmarks, so he sliced them up. We have twice as many now. Jade prefers them fat, though.

M: censure jhawk. Second is overridden.

M: censure jhawk. 4-0-2 +Spehn.

There is a huge gap in the Laurel K. Hamilton section of the shelf. Is this Jade's fault? Partially.

A "sextette" is a set of six female things? Jamie checks the dictionary; impressive use of a reference book we have.

2 new overflow boxes for anthologies.

\goto{Old Business}

Got responses from lawyers, got a contact person. Still checking on how much they have. Large but not overwhelming, probably. Logistical discussion of the move.

The shelf bubble has moved a few feet.

John found a fossilized eraser with alien writing on one end. It's actually a signature stamp, old Chinese.

M: Plant fossilized banana-colored erasers in the desk for future keyholders to discover. 4-0-9 +Spehn.

M: lay an egg. Chickens 1-0-2 +Spehn.

Was the discussion about bisexual roosters before the meeting?

M: Mike: "Hmm???" 4-0-1 +Spehn.

\goto{Future Business}

John's transmission did bizarre things on the way to work. He has also started signing email with employee ID number instead of his name.

Miller motion. No second.

M: moving bananas. 3-3-0 +Spehn. Does nothing.

Adjournment song singing.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
