\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/25/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 25, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and
Pseudo-Skinner, presiding.  Ed Keyes is the $50 \Omega$ Onseck.

Minutes read.

Motion: Commend the minutes as more exciting that Danielle Steele's
{\em Lone Eagle}.  Chickens not even John--not even John--not even
John+Spehn.

\goto{Committee Reports}

Mobcomm: We have lots of new hardcovers, and John has most of our cash.

Bluebellcomm: John covered ten books, and Ed only covered half of the
remainder.  We couldn't finish off the roll of covering material,
though.

Mobcomm$_2$: We finally got a copy of {\em Greetings, Carbon-Based Bipeds!}
Assigned a shelf code of CH.

Jourcomm: jhawk was reminded about the want list.  We also need the
rant, minutes, and reviews.

Mobcomm$_3$: We need to remind the Space-Crime Continuum to send us
more books.

\goto{Old Business}

The Schultz donation ought to be unpacked soon, once the backlogs are
taken care of.

Discussion of the time scale of magazine binding.

Starting a sci-fi library in Quebec?

Discussion of the mailbox.  How did we get signed up for an AIDS
magazine?

\goto{New Business}

The new shelf replacements finally arrived, and they've been replaced,
yay!  We are actually gaining space from this by some interesting
shuffling.  The shipping box has some rhyme about Kalamazoo on it.

Discussion of Tim Power's {\em Expiration Date} and methods for
trapping ghosts.  John is just fascinated by this rhyme...

New member, yay.

The Fibonacci challenge to the seniors: they can donate to the MITSFS and
a rich alum will match it.  There are issues with getting membership
out of it, and with tax-freeness.

\goto{Future Business}

Kat Allen has been Hasslecomming.

We have a new banana.  A discussion follows about where it should go.
Maybe another foreign banana: the German Perry Rhodan Banana?  Jamie
is consulted for the banana list.

Motion: Bluebellcomm is instructed to cover the Bluebellcomm Banana
appropriately.  Passes banana--none--none+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
