\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/30/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 30, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Jade Wang, President and Skinner, presiding.  Ed Keyes is the animation apprentice Onseck.

Minutes read.

M: commend the foreshadowing in the latter half of the minutes. 7-2-0 +Spehn.

\goto{Committee Reports}

Mobcomm: as was noted, it was a while since a Xanth book, and we got one. About 500 dollars worth of hardcovers from New England Mobile.

The skinner pays a fine rather than forgiving herself.

Mobcomm2: Jen Clay noted that we are missing like 3 Buffy books.

Discussion of judging books by their covers, or by their books.

(Jenwa) "I've tried checking out hardcovers recently, but it never works."

Pseudo-Pianocomm: Our comics are distracting our prentices.

\goto{Old Business}

Monday and last night, the shelving was dismantled in preparation for transporting tomorrow.

Who are Alice and Bob? An amusing cryptography essay.

A later Tech editorial criticized the RR plan. A little unclear about whether the RR is used or not.

(Sam) "Has the Tech's office space appeal gone through?"

A perfect letter to the editor opportunity...

Discussion of the "no sex in the library" rule. The skinner does not remember making this rule.

(Mike) "Sex and science fiction... fans... do not mix."

(Jade) Until we get the space, "have as much sex in the Reading Room as you like."

A cunning plan to make people use the RR less...

\goto{New Business}

How to model Jade's behavior?

(Mike) "Thor did not wear a chainmail bikini!"

We have new furniture-moving equipment and rope. Two new rubber doorstops, too.

A new prentice coming soon.

(Jamie) "It's a staple." (Jade) "It's a short pointy thing."

(Jade) "Shopping is hard, let's do math."

Building shelving form the laminated bodies of small children.

Jade is fascinated by lamination technology.

(Jade) "Mmm... liquid plastic."

M: let's laminate everything! 2-0-2 +Spehn.

John fixed the s key.

Can Jade automatically end the meeting by going to...

\goto{Banana Business}

M: miller motion. 3-4-2 +Spehn.

John forgot to get the book by Margaret Wonder-banana...

M: let's laminate Jamie. Does nothing, motion tied.

M: future ties between yays and nays should be called bananas. 4-1-4 +Spehn.

M: second Miller motion. Fourth! (Second second) Can we get bananas drunk with Miller motions and laminate them? Passes.

\vspace{12pt}

\noindent
Meeting adjourned, 1810 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
