\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/21/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 21, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 17:00 SST, Jamie Morris, Chancellor
and Pseudo-Skinner, presiding.  John Carr is the edless pseudo-Onseck.

Minutes read.

Jamie: ``We had a motion last week to note that next week's minutes will be
incomplete as usual.  All in favor of last week's motion which floated to
this week.''

John: ``Move to note that it did not come to pass.''

Jamie: ``I'll take that as a second''

Motion passes \hbox{0-``not even the reader''-1+Spehn}.

Jamie gets the gavel drunk again.  ``It likes it,'' he rationalizes.
Next week: cocaine.

\goto{Committee Reports}

Mobcomm: new books Sunday.  Nothing notable.

Pseudo-analogcomm: IAP schedule is up, including JMC.

Pseudo-VGG: Laura Baldwin renewed her membership so our financial
situation should improve.

Discussion of Laura's return leads to a discussion about posting
new rates.  (The current rates expire with the new year.)
This leads to a discussion of Jade.  Jamie then describes the
revised proposed new rate policy.  The goal is to increase the
number of long term memberships.  Proposed rates are \$12 per
year up to three years, and ${3 \over 4}$ of that for four or more
years.  At this point Jenwa laughs loudly\footnote{This may have been
caused by a {\em Buffy the Vampire Slayer} book.}.  After we computerize
we may go to three membership categories, short (one to three years),
long (four years or more), and until-death; extendible in one month
increments.

Pianocomm: Prentice Susan Born did some gapdex then fell asleep.

(Jamie keeps spraying the gavel with alcohol.)

Pianocomm: Prentice Shaina Jackson came here too.

Pseudo-theftcomm: In the absence of Jen Chung, Jamie is acting theftcomm.
If you don't email {\tt theftcomm} instead of Jen, you will lose.

Pubcomm: Jamie fixed the $\infty$ corridor bulletin board and updated its
contents.  We need more durable construction.  Pieces keep coming loose,
especially when struck by passing book bags.

Martyn Peck remarks ``I don't know where my head is right now.''

\goto{Old Business}

The last bobcat is gone.

A messy floor is now exposed where some old file cabinets were.

We still have a BBC-Turbo PC labeled property of Ken Johnson.

(Jamie is still spraying and rubbing the gavel or gavel block.)

\font\sym=msam10

{\sym "}: The final? draft of Still Not Fans \#1 was sent to the Alumni Office.
Shortly thereafter we discovered that our contact no longer worked there.
Maybe Stu knows what to do, but he isn't saying.  With luck, SNF may be
in the mail soon.

ALGOL!

\goto{New Business}

Stephanie brought some friends to the library.  One of them was asking about
the ``no sex in the library'' policy; he wanted to know exactly where sex was
prohibited.  A while later, Jamie and Jade disappeared into the back room, and
the next day everything was rearranged and there was a looseness in the shelves.

(Time warp to old business: The C/P bubbles have propagated almost completely
around the first half of the alphabet.)

(Jamie applies more alcohol and rubs harder.)

Jade and Jamie went over plans to use the new shelves and shelf parts
to help survive for the next 18 months.

Some filing cabinets and their contents were rearranged.

The ``for sale'' area will go away.  The boxes behind the for sale shelf
will have ``more structure.''  The area in front ... (missing) ...
The coatrack hooks are already gone but Jamie can't get the big piece
of wood they were attached to off the wall.  Power tools may be required.
Shelves will go into the for sale area: two on the wall next to the door
and two perpendicular coming out to meet the sole remaining file cabinet.

John liberated the last bookend in LP.   The LP section will move to the
four new shelves, with $8 \times 4 = 32$ rows, $4$ or $4 {1 \over 2}$
more than they have now.  This will be good four about 22 months more
space.  Ps will get much more than 24 months space.  PAs will go to the
current LP space, along with a good shelf to replace the bad, ugly, gray
shelf, gaining 4 rows.

(Jamie keeps working on the gavel block.)

In the circulating room, the two by four wood shelf will leave the H
section and be abandoned.  The ugly gray things with H and HA will be
stored, if possible.  These plus the wood C/PA shelves will turn into
two by six Aurora lawyer shelves.  Jamie, probably correctly, predicts
that he will do most of the shelf-building himself.  This process will
create adequate space for H ``for a while,'' about 11 rows of H and one
row of HA.

There is discussion of warehouse space and whether we can move anything
from the library to it.  Some of the boxes will be emptied, but probably
four boxes will be a quarter empty rather than one box being completely
empty.  We won't gain any floor space and the partially empty boxes won't
be able to support weight.

All the previous shelf manipulations are ``very short term changes.''

In six to twelve months the really tall shelves will go into Damnation
Alley, freeing Republic shelves which can hold ten rows of paperbacks
for use in the circulating room.  Sets of Republic shelves may have to
be assembled as a single, big chunk before any books can be put on them.
This will be inconvenient because we have to empty several shelf faces
at a time.  Jamie has taken this sort of shelf apart, but he has never
tried to put them back together.  Joe has pictures of partially disassembled
Republic shelves.


Jamie threw out some junk, but not the banana bat.
Move to commend him.  ``Yay.''  Passes \hbox{4-0-Spehn}.


\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 17:53 SST.

\vspace{12pt}

Finally satisfied, the gavel block lies still on the desk.
It is, Jamie claims, a {\em lot} cleaner.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, pseudo-Onseck}

\end{document}
