\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 6/1/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, June 1, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and
Pseudo-Skinner, presiding.  Ed Keyes is the pre-birthday Onseck.

Minutes read.

Motion: Try it again with more sex, violence, rock-and-roll, and stuff.
Fails 2--4--2+Spehn.

\goto{Committee Reports}

The two slinkies are now intertwined.

Mobcomm: We still need to remind the Space-Crime Continuum to send
us more books.

Pseudo-Bluebellcomm: More stuff was covered, even two paperbacks.

Somehow Hasslecomm generated two for-sale boxes from just one Hasslecomm
overflow box.  Are they generating books out of thin air, or just
withdrawing extra books for fun?  It is noted that water causes books
to swell up.

It's time for the summer dexes, and Inventory needs to be scheduled.

Shelfcomm: We have two extra shelves for the C/P's now, and two more
coming.  The empty shelf is next to Xanth.  Efforts to re-contact the
shelf company have failed... have they burned down again?

\goto{Old Business}

The book dealer person was recontacted, with no reply so far.

We did sell 40-50 books last week.  John paid with a check that may
eventually be cashed by us.

Motion: Commend the banks for not honoring 90-day expiration notes
on checks.  Passes by Pseudo-Skinnerial decree.

\goto{New Business}

John reports that a duck has taken up residence in his mother's flowerpot,
as evidenced by the appearance of eggs.  Amazingly enough, there is a
``Help!  There's a duck in my flowerpot!'' website designed for this
situation by the U.S. Geological Survey.  Duck eggs are a form of mineral?
An alien life form?

Sam reports that the government recently funded a helping-the-homeless
project that included buying them candy and alcohol.

Motion: Investigate the effects of banana plants on alien egg coverups.
Not seconded.  It is noted that we have a banana egg already... hmmm...

Motion: Wear bunches of bananas on our heads to block the alien mind-control
rays.  Chickens 4--5--8+Spehn.

The seniors still have a week to donate in the Fibonacci challenge.

Motion: Attack the Fleet bank with a banana (because Fleet is run by
aliens).  Passes 9--1--3+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1723 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
