\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/17/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 17, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and Pseudo-Skinner, presiding.  Ed Keyes is the sensor-binging Onseck.

Minutes read.

M: for some of the minutes, you just defocus your eyes and it leaps out at you. 2-0-1 +Spehn.

\goto{Committee Reports}

Mobcomm: I'm seeing double.

Mobcomm2: we spent lots of Jamie's money on hardcovers (500 bucks). jhawk chastised Mobcomm for getting the second in a series we don't have the first in hardcover. Also the seventh in the Hope series where we didn't get the fifth at all.

Panthercomm: ...and they were Panthercommed.

Bluebellcomm: ...and half of them were Bluebellcommed.

The second Demon Wars saga by Salvatore is denoted "Demon Wars Again" in Seriesdex.

Jenwa kicks jhawk out of the library for eating cookies. He has a colored band around his leg to track his migration patterns.

Bondagecomm: quotes expected this month. "That's what you said last week!" "But it's the same month."

Pseudo-Fweekcomm: are we ready? More people should sign up for R/O hours. Extra credit in TIF for R/O hours? Reduce lead time down to 1 week?

Jadecomm: skinner is out of state, but in an unknown state.

Pseudo-Analogcomm: new fall schedule being created, up on Wednesday and online now. 19/28 keyholders signed up, now 20. Very few missed hours so far.

\goto{Old Business}

The Ps are getting packed again.

Got mail from ex-picniccomms, photos from the picnic.

M: make Aaron and Yu permanent Picniccomms. 4-8-0 +Spehn: passes!

Jenwa has trouble recognizing photos of Jamie.

\goto{Time Warp to Committee Reports}

Alohalenscomm: MITSFS locker quota went up, so dumped digital photos in there.

\goto{Un-time-warp}

The ongoing lock saga. They're not reading our mail... and when they do, they don't give any information.

Anyone who wants to know the lock model is up to no good... will be a pure keycard system, probably. Need a card for George Flynn, sponsored by MIT Libraries?

Jenwa leaves.

\goto{New Business}

New rates are up, increased to 12 dollars and in proportion. Month-by-month discounts seem positively received.

Someone stopped by asking how to use the doorstops.

New subscription to F+SF.

John switches the calendar back to Boris, the redhead dragon-biker-chick.

For-sale area is less cluttered now.

John is astounded at the new-old 2 inch book tape. Kind of a slow reaction time. John outbluffed a scary security type.

We haven't had a large donation for a while. If Jamie got a key every project's worth of work, he'd jingle like jhawk.

\goto{Future Business}

M: I'm hungry. 0-2-4 +Spehn. "Mmm... chicken."

Miller motion. 3-4-0 +Spehn. The Onseck saves the universe.

Second Miller motion. 5-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
