\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/03/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 3, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the subliminal Onseck.

Minutes read.

Only John's right eye is nearsighted enough to poke with pins.

M: condemn minutes for not taking advantage of the skinner not paying attention and making stuff up. No second.

M: ditto. 5-0-1 +Spehn.

\goto{Committee Reports}

Dexmistress: inventory happened. The shift system seemed to work well, give or take some tweaking. The post stage was a little long, though. Maybe 85 keyholder-hours. Next year maybe changing prep stage.

Pseudo-Bondcomm: John ran into jhawk, will get quotes from binders this month.

Mobcomm: time to start planning end-of-summer book run.

Got a letter from someone "shamelessly" publicizing their new novel. We admire honesty.

Jamie explains mapmaking. "Iowa is pink."

Jade: "I want a bloodmind..." Mine?

Mobcomm2: read the first of the British books. About the nuclear industry in Britain, with an intro by Pratchett. John is now scared of nuclear power. Are we downwind of Britain?

The random books up for grabs have disappeared, except for a Robin Cook, and "Left Behind," appropriately.

Jadecomm: skinner is losing contrast, now just shades of gray.

Mortcomm: Poul Anderson died this week, complications from cancer.

Pseudo-Analogcomm: request fall hours until August 15. Schedule posted 8/22 to start 9/5: first day of classes.

\goto{New Business}

Jade is losing her mind.

jhawk seems to have taken his boxes. Other boxes moved to clear off couch area.

Pseudo-Theftcomm: so far, all holes in schedule have been filled, give or take 7 PM tonight.

Jade is moving this weekend to Porter Square. Although not actually in the mental hospital. Will name it the Continuum, Time and Space. So "Eddie's in the Space-Time Continuum."

Jamie gets confused about "Apostate" vs. "Acts of the Apostles."

Jade looks through a sign catalog, wants a "No Cthulhus Allowed" one. Or a "girls" and "boys" sign, one for each side of the ZGT. Also need an "other"...

John was once scolded for using the men's bathroom instead of the boys'.

Jade: "Ooh, pretty label things, I love those." Jade does not realize we can read her thought bubbles...

\goto{Future Business}

M: get signs for the ZGT to distinguish boy bananas and girl bananas. Jade wonders how to tell the sex of a banana. Discussion of quality of toilet paper. The transitivity axiom is used. 8-0-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1750 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
