\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/2/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 2, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the chastised Onseck.

Minutes read.

Discussion of adjournment songs and their effectiveness.  [Jade]
``If only one person is singing, I can hit them.''

Motion: Condemn the minutes as de-censored.  Passes 13--0--2+Spehn.

\goto{Committee Reports}

Jourcomm: Yevgeniya is happy because she got three pages of comic
strips submitted.  The deadline for the next issue is still the end
of March.  Yevgeniya wants to go to Harvard, booo... the HST program,
specifically.  She's going to live on the Hubble telescope?

Mobcomm: There are indeed 64 books, but not from us.

Bluebellcomm: We're upset about encroachment onto our shelf.

Pseudo-Panthercomm: Panthercomm isn't keeping up.

Pseudo-Hasslecomm: Hasslecomm is lame, lame, lame.

Minicult: Something about MindBridge.

Psychic transistors, psychic diodes.  Are thoughts like electrons
or holes?

An all-numerical {\em TZ} would solve a lot of problems.  ``The 42 should
have been a 17 on page 3.''

\goto{Old Business}

[John] ``Boringly conventional!''

The Spanish teacher came to take video of the library, just like we
expected.  [Jamie] ``Everyone expects the Spanish teacher!''

Shelves... we will probably be able to get the type we want after all
from a local supplier, the model apparently unchanged in the last
fifteen years.  ``She sells shelves by the seashore...''  A law firm
may also be abandoning some soon that we can recover.  [John] ``Do we
want to gamble our future on the good will of lawyers?''

Discussion of our current shelves in need of repair.  [John] ``They're
a lot more stable than they look.''  [Jamie] ``Unlike most of the
people here.''

Discussion of Tablecomm and why they were abolished, eradicated from
history itself.  Except for these minutes... uh-oh, wait a sec...
They'll come for ME now!!!  The Onseck's body will no doubt be dumped
into the concrete foundations of the Gates building in due time.

Discussion of outsides, snow, rain, and organic poisons.

\goto{New Business}

The TEAL program is now not going to be in the fifth floor reading
room.  Probably going to rearrange building 6 instead and put it
where the physics reading room is now.

\goto{Future Business}

Campus Preview Weekend is coming up April 4-8.  We should have the
library manned during that time.  Pre-frosh are scary.  Babies are
scary too.

Yevgeniya likes playing with spiders and puts them down people's
shirts.

The odd juxtaposition of babies and spiders triggers John's baby
spider story, which is not recorded here but involves Christmas
lights.  ``Spiders are not the dumbest animals on the planet.''
Baby spiders all in a line, like lemmings with parachutes.

[Jade] ``Yuck, I don't want to hear that.  Un-say it!''

Motion: In the future baby bananas will hatch on the Christmas
lights on John's mom's house.  Passes 7--3--2+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1815 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
