\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/13/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 13, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the memetic engineering Onseck.

Minutes read.

Motion: Commend the minutes as beloved.  Chickens 3--2--6+Spehn.
[Jade] ``Gee, I even think I got the numbers right.''

\goto{Committee Reports}

Mobcomm: We need a curve for the numbers 1, 8, 25, 34.  Are those
actually lotto numbers?  Bingo!

Theftcomm: The bulletin board has been updated, and the plexiglass
plan is in progress.  Then John immediately invalidated the work
by changing Neel's hours.

Jourcomm: Yes, we need reviews.  We also need a successor for next
year.

Minicult: The creator of the smiley face has died.

Pseudo-Jadecomm: Jade has an orgy of dragons.  Is this like a pride
of lions?  According to the web, the correct terminology is in fact
a ``doom'' of dragons or an ``aarrgghh!'' of dragons.

Pseudo-Chancellor: Jamie isn't here, perhaps oversleeping.

Pseudo-LHE: Stephanie was here, but went to take a nap.  It turns
out that our SFBC shipment was incomplete because they don't trust
us enough to give us credit.  [Andrew] ``I'm just totally stunned
by the idea of the SFBC {\em not} sending books.''

Pseudo-Bluebellcomm: (insert a long ranting string of adjectives)
The Bluebellcomm shelf consists of nasty, brutish, and tall book
piles.

Pianocomm: We're doomed!  We need more publicity, and probably a
Star Chamber meeting to discuss it.  There is a discussion of
postering and laughable dorm security.  How about a booth in Lobby
10, just to let people know we exist?

The discussion veers into the ongoing construction in Lobby 7.
Was the dome covered in World War II to protect against bombing?
In Boston?

Pseudo-Jourcomm: John might write something.  The Skinner rant for
the {\em TZ} shall be, ``Go forth and multiply, then come back and
read.''  The conversation deteriorates rapidly... use of books on
tape, the problem with loud partners, use of gags, and the
potential for Braille...

\goto{Old Business}

Campus Preview Weekend happened.  As usual the most enthusiastic
visitor was the father of a prefrosh.  A few people who will
probably be back, and they bought some used books, too.

\goto{New Business}

{\em Spectrum} and {\em ON SPEC} accepted our checks, and are now
sending us stuff, yay.  Can we get a subscription to {\em ON SECK}?

Motion: Commend Ed for being the standard text editor.  Passes
11--0--2+Spehn.

Yevgeniya is chiselling wood.  [Jamie] ``Ooh, can you chisel John's
face into a more interesting form?''

There is a new rule in the Keyholder's Guide: no sex in the
circulating room.  This ought to be changed to ``in the library'',
probably, but has it really been a problem?

The Naval Academy is seeking applicants for its Heinlein chair.

\goto{Young Business}

``Hi, mommy!''

This scares the Skinner so much she immediately moves on to...

\goto{Future Business}

What's going on with Picniccomm?  A short discussion breaks out.

Motion: Subscribe to the Banana-of-the-Month Club.  The Skinner
loses track of the votes and calls for a chicken recount, but
eventually the motion passes 7--6--2+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
