\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/26/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 26, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the generally covariant Onseck.

Minutes read.

M: replace all occurrences of "John" and "JFC" with his employee ID number: 24918. 9-0-3 +Spehn.

\goto{Committee Reports}

Jadecomm: Colorful shirt... Snow White in a wardrobe... red, white, and black shoes. Maybe pants as white as dirty snow.

Jamie: "I'm the Christmas present for someone naughty."

Mobcomm: shipment arrived. Man, there are a lot of Buffy books...

Pianocomm: a prentice covering books was here and approved of the split material. Also some Gapdex work by another apprentice. Correcting the Black Company series has been done to death...

Pseudo-Theftcomm: John is now a third-level keyholder.

Panthercomm, Bluebellcomm, Pianocomm: some Schultz processing has created more hardcovers to cover. Also prioritized shelf.

Bluebellcomm: 3-4 minutes per book to cover.

Magdexing discussion.

Justin is kept as an apprentice for inventory purposes.

Thesysadmincomm: now have the current version of Athena. Also changed X config. Local accounts for Athenaless keyholders will be created. mitsfs.mit.edu will be transferred eventually, with mail aliases for keyholders by initials.

You can change your username if you get married.

\goto{Future Business}

John completes his geas to remind Jamie.

We will gain an hour, the rest of the year will be dark and cold.

Plans to expand up into the Reading Room. Install a fire pole.

\goto{New Business}

Jamie has a new ID card. George Flynn also took care of his card. jhawk possibly has dealt as well, confusion with ID numbers. John: "Ooh, jhawk vs. bureaucracy..."

APO had one of the new locks briefly... do they only have N locks for 2N doors? Just migrate them around.

M: send APO a box of bagels... lox are no fun without bagels. Groans all around.

\goto{Time Warp to Committee Reports}

Jourcomm, after some prompting, glares at John and asks for reviews. In HTML, on laminated banana peels, even. John wants to make them like HTML. John will have to set clock back to use Scribe.

M: Instruct Bondcomm to have it shaken, not stirred.

\goto{New Business}

John and Jamie picked up some useless shelf pieces.

John: "If they'd been different, they would have fit."

A new comfy chair, too.

Different colored electrical tape. Use it to create a giant resistor Halloween costume. Important tip: leave air holes.

John complains about weather forecasts. Foley's jacket of doom. Should we move the library to New Hampshire? ...Install a monorail for carless patrons.

\goto{Old Business}

Jade: "The bing can be louder."

Foley: "That's why I went 'eee!' instead of 'AAHHH! My ears are bleeding!"

John liberated 3 more bookends.

Jamie just got a lawyer email. Schedule in early November.

Jade's right eye hurts. Jamie: "Did you look at John again?"

MITSFS should donate an old banana for next year's UMOC.

\goto{Future Business}

M: buy the skinner a 10-foot banana so she can touch things with it. 16-1-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1750 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
