\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/14/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, December 14, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jamie Morris, Chancellor and Pseudo-Skinner, presiding.  Ed Keyes is the cameraful Onseck.

Minutes read.

(John) "Could you do that again? I wasn't paying attention."

M: note that next week's minutes will be incomplete as usual. Fails for not being funny enough.

M: move that John's readings are more complete than Ed's. Anti-seconded. Anti-chickens 0--2--2 -Spehn.

\goto{Committee Reports}

Pseudo-Theftcomm: (John) "Tomorrow, I transcend." The median will advance enough to shift down in 4 weeks plus vacation effect.

Bluebellcomm: I think the Mobcomm shipment has been dealt with, plus a few other random ones. A few new ones to go.

Pseudo-Surgeon: John glued a book, and it can still be opened.

Pseudo-Analogcomm: the prototypical IAP schedule has been generated, will be posted soon.

\goto{Old Business}

John oiled the keyholder desk chair a bit and it doesn't squeak.

Jamie cleaned up gunk on the gavel with isopropyl, and it isn't sticky anymore.

The online minutes now extend into July, including the last election meeting.

Arisia and Boskone are coming up, so maybe the book dealer will come buy the stuff he said he would.

ALGOL!

\goto{New Business}

Pseudo-Boriscomm: John doesn't like the SFBC calendar. Jamie flips through it, displaying the pictures to the members. (Jamie) "It still beats Boris."

The shelves are getting more crowded.

Jazzy music starts up from down the hall or from the floor below us. Mike is hypnotized by it and starts snapping his fingers.

Discussion of Jenwa's book, "Villains by Necessity." Everyone loves it.

Japanese books and Japanese courses here and at Cornell.

Discussion of the wording of the RR proposal that was passed. Fairly fluffy, "supports the continued investigation..."

The CAC Strategic Plan for Walker and W20 was released as well. Defined essentially everything as high-priority, except retail space. Adding 11000 square feed of random meeting rooms... at the expense of activities. Probably not a big concern, since CAC probably new about this and still supported RR proposal. Cut the Athena cluster in half and moving it to the basement to recover window area.

Analysis of traffic patterns is the basis of a lot of this... lots of hedging on the part of the consultants.

The jazzy music returns.

\goto{Future Business}

Miller and banana motions are invited. Does adjournment dancing work as well as adjournment singing?

M: don't let CAC take our bananimal. 5-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1733 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
