\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/23/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 23, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1705 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the wireless Onseck.

Minutes read.

Motion: Correct the text about Bluebellcomm to ``lazy and shiftless''.
Passes 7--0--1+Spehn.  [John] ``Hey, you forgot my foot!''

Motion: Declare John's shoe a philosophical conundrum.  Passes
3--0--0+Spehn.

Motion: Commend the Onseck for being translation-invariant.  Passes
4--philosophical conundrum--1+Spehn.  A dissonant bing.  [Jamie]
``If you grip it too hard, it makes funny noises.''

\goto{Committee Reports}

Mobcomm: Please give me \$724.47.

Pseudo-Picniccomm: We have a letter from Hal Clement, which is then
read.  He has a son named George who is a bird expert.  He's got a
real busy schedule at cons, too.  [Malcolm] ``All those cons and only
one pro.''  Discussion of Asimov's status about picnics.

Pseudo-Picniccomm$_2$: We'll probably go with Friday, May 11 for
elections and have the picnic on Saturday.  This is a break from recent
tradition of having the picnic on Sunday, but in fact Saturday is an
even older tradition.

Pseudo-Plantcomm: (silently hefts a battery)

Mobcomm$_2$: We got a bunch of weird books.  How can get get 32,768
into the report?

Jade tries to pry off the tabletop with the gavel.  Another pun from
Malcolm, mercifully unheard by the Onseck.

Pseudo-Rosfap: The Rosfap pile is nine inches deep.

\goto{New Business}

John brings out a 70\% isopropyl alcohol bottle that has randomly
appeared on the Skinner shelf.  It has a spray nozzle, too.  Jade
suggests getting a match...  John advises people that sniffing a
spray of isopropyl alcohol is not a good idea.  [Jade] ``It's
isopropyl alcohol... and so much more!''  [John] ``I should sniff a
bunch of water to clear that out.''

\goto{Old Business}

Motion: Add ``Bluebellcomm is still lame'' to the ALGOL.  John tries
to second his own motion.

Motion: Declare John an Albanian philosophical conundrum, or A.P.C.
[John] ``I don't want to be a P.C.!''

We are ordering shelf replacements for our bent ones.

An old friend of Jade's is visiting from CalTech.  [John] ``Is she
cute, then?''  [Jade] ``She's 21.''  [Jamie] ``That's legal.''  It
is revealed that the friend is actually a Mech-E.  Coming to a MITSFS
meeting will be a ``unique experience to change her life'', according
to Malcolm.

[Jamie] ``You have experienced meeting me.  You haven't experienced
{\em me}.''  A vicarious Telzey if you date a friend of the Skinner?

[Jade] ``Maybe we should have young business.''

\goto{Young Business}

We should get another rainbow-colored Slinky.  John washes the Slinky
with our alcohol sprayer.

Motion: Condemn John for spraying in the library.  Passes
7--philosophical conundrum--0+Spehn.

Motion: To have the young people do no more rain dances until the
end of the semester.  (Boston had about 24 hours of rain recently.)
Not seconded.  [John] ``I only prayed for two inches of rain.''
[Jamie] ``Yeah, but so did everyone else!''

Jade found a cool survivalist guide, with all sorts of cool things
you might have to know how to do, like jump out of a moving car.
And how to get out of quicksand... by carrying a stout pole with you.
[Jamie] ``Okay, so once we sneak out of the giant wooden badger,
what then?''

\goto{Future Business}

In a few hours, Jamie and others will go to pick up a donation from
an MIT professor whose eyesight is failing.

Motion: Note in the minutes that you can't take it with you.
Passes 3--2--philosophical conundrum+Spehn.

Motion: Take it with us!  Passes 5--0--2+Spehn.

Motion: Have a matrix vote.  Not seconded.

\goto{Time Warp to New Business}

We got a piece of mail from the Quwait embassy, which should have
gone to the upstairs reading room.  Some magazine in some Arabic
language.  It is noted that Arabs do not actually use Arabic
numerals...

Most campus rapes start in the reading room.  A sign ``Most campus
rapes start here'' with a picture of a beer, in actuality.

A newspaper from Singapore: ``Government acts to reduce shortage
of lawyers''.

\goto{Future Business}

In the future someone will give John \$724.47.

Motion: Ask the new person their name and then say ``hi'' in an
embarrassing fashion.  Passes 8--0--2+Spehn.  She's Debbie.
``Hi, Debbie...''  She has degrees from the University of Toronto,
which evidently has a large speculative fiction collection, the
Merril collection.  Is it bigger/better than ours?

In the future, we will have dinner.

Motion: Have a banana for dinner.  Not seconded.

Motion: Miller motion.  Fails 0--3--2+Spehn.  [Jamie] ``If it doesn't
fail, the universe explodes.''

Motion: Second Miller motion.  Passes some--less-0+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
