\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/16/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 16, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and Skinner, presiding.  Ed Keyes is the not-in-line-for-Harry-Potter Onseck.

Minutes read.

The ex-skinner's name is possibly corrected or mangled further.

\goto{Committee Reports}

Jadecomm: the skinner dressed in fall colors. Onseck should look up first occurrence of Jadecomm in the minutes.

Alohalenscomm: have prints of picnic pictures, only 6 months later. A plea for picniccomm to return.

Mobcomm: lots and lots of new books by next weekend. Probably not as many Buffy books. Hardcover run?

Bluebellcomm: someone keeps putting books on our shelf. John hypothesizes that if he stops covering books, they will cease showing up.

Mobcomm2: Yet another Dune book. "Fluffier" than the originals.

Pseudo-theftcomm: jhawk is about to become a third-level keyholder.

Jourcomm: RSN.

Jade abuses an Earthlink CD. Successful fracture with only two blows. Discussion of the merits of different types of CD packaging.

Did someone eat Jamie? He's not here. "Release the hounds!" Discussion of shoes. John's shoes are "Deerstag" brand. Jamie walks in.

Jade is disturbed by Jamie's very dark green shirt. It's really dark, but it's not black!

\goto{New Business}

Jamie fixed psi-phi a bit.

Can we do a link share to Ninja Burger? Fine line of promoting commercial interests... they're doing an online marketing promotion.

Jade is hosed. Will tool madly over Thanksgiving.

\goto{Time Warp to Committee Reports}

(Jade) "Your green is messing with my head."

Pseudo-Plantcomm: locks are being installed on Monday, and they warned us.

(John) "Maybe their email delay program is malfunctioning."

\goto{New Business}

Email with an attachment of a white powder jpeg.

John wants Jade to wear a different hair thingy every week. Jade's shirt has buttons on both sides so it can be worn inside out. Discussion of whether the buttons are on the same side or if the shirt changes sex.

Locus says David Brin has a new novel "Kiln People" out in January. Plot involves clone slaves.

The ICA has an exhibit of photos printed on live grass. Can we gene-engineer Jade's hair to do the same?

\goto{Old Business}

The old box by the door dates from the 60s, according to the ex-skinner from last week.

Some space for the C/Ps has been instantiated. Shelf minion is working out.

(John) "Does your plan involve eighteen hours of moving shelves and books?"

Foley and Jamie visited the lawyers the other day. A large amount of shelving available. May be doing a hasty grab tomorrow to get the best stuff.

Reading Room business is still "maybe." UA agreed in principle to the idea, but doesn't want a separate area for us. Stuff in progress and moving. CAC threw a bit of a wrench in the plan of getting a wall built: getting that approved will take 18 months. Build a wall out of tall bookcases? Bolted to floor and ceiling? Stupid union rules.

\goto{Future Business}

Student center closed for Thanksgiving.

IAP hours requests coming up soon.

Something odd happening to public libraries around here? Branches closing temporarily? Moving? Tearing them down and rebuilding them?

Harry Potter? There's a night-end theater in Framingham which only allows adults in.

Jade will celebrate someone's birthday.

Psi-phi will get a color monitor soon.

M: can we get a banana-colored login screen? An animated banana icon peeling itself? 6-1-3 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, almost 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
