\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/02/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, November 2, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1715 SST, Jade Wang, President and Skinner, presiding; Ed Keyes is the post-Halloween Onseck.

Minutes read.

(Jade) "There's gunk on my gavel. Sticky gunk..."

M: to treat the gavel, gavel block, and the minutes with rubbing alcohol. 4-1-1 +Spehn.

\goto{Committee Reports}

All ex-skinners are soulless automata? No, there is a rite to remote-control their bodies from inside the gavel.

New lock could be installed at any time.

Collect all the keys, melt them down into a mini-gavel? Etch them with oxygen plasma?

(Jade) "Cynical? We're not cynical... we're bitter."

Pianocomm: prentices have been working, yay. Cardex and lots of Bluebellcomm boxes.

Committee for conquering space has stalled on UA. The ASA is not feeling loved.

jhawk walks in and a Bondcomm report is demanded. He hides under his jacket instead, and quickly leaves.

My god, there are a lot of Buffy books now... we are catching up with them.

Discussion of the Society finances. Money for magazines.

Jade ponders what her princess outfit would look like.

More clothes than depicted in the catalog... tattooed clothing? Chained to a wine cask? Alien bubblegum machine. "Sexy biker on skeletal motorcycle."

Jade skims the minutes for ideas to talk about. She actually taped up Eddie as a resistor for Halloween. He was 1 megaohm. (Ed deciphers the color code.)

\goto{New Business}

The skinner has discovered the lever law.

Psi-phi now has local accounts, yay. mitsfs name being transferred.

Jade "accidentally" drops the catalog into the trash can.

Jade is hungry and tired.

M: skinner should eat a banana. Chickens 4-0-4 +Spehn.

Jamie's new MIT card works to open doors, at least some of them.

TVcomm: anyone watching Smallville? Superman is actually fighting Pokemon, not supervillains.

M: commend Superman for fighting Pokemon. 8-0-0 +Spehn.

\goto{Future Business}

M: aid Superman by supplying him with banana-sized chunks of Pokekryptonite. 9-0-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
