\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 5/11/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 11, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the re-electable Onseck.

Minutes read.

Motion: Amend the minutes to explain what Jade and Jay were doing
when they weren't there.  Passes 13--5--3+Spehn.

\goto{Committee Reports}

The bings are unusually painful in the Star Chamber.

Motion: That hurts!  Do it again!  Fails 3--ton--something+John's
camera+Spehn.  And of course there's a bing anyway...

Pseudo-Bluebellcomm: I don't see a stack of books here, for the
first time in a while.

Motion: Encourage the Bluebellcomm Fairy to cover all the uncovered
books in the world and leave bright, shiny quarters under people's
pillows.  Passes 14--4--1+Spehn.

Motion: Declare John the Bluebellcomm Fairy.  Passes 11--5--3+Spehn.
There follows a discussion of what color his fairy dress should be.

Pseudo-Bluebellcomm$_2$: We're out of the short covering material,
boo.

Jadecomm: Jade was at the Steer Roast last week.  Pictures are
demanded.

Alohalenscomm: We need 65 interesting things between now and tomorrow
to use up the flash card.

Pianocomm: Katherine Reid is a new prentice, yay.

Jourcomm: We're passing off duties to Andrew, mostly.  The Skinner
Rant is still... in progress.  ``Oh, duh!'' in big letters is
suggested.

\goto{Old Business}

The Jadecomm pictures arrive and are passed around.  The meeting
grinds to a small halt.  Natasha was there at the Steer Roast, and
a picture copy is demanded for our records.

John's aerosol can from last week didn't have any CFC's, but it makes
the floor slippery so it's still dangerous.

Motion: Declare Jade's Bad Idea was a Good Idea.  Passes 18--0--4+Spehn.
(This was her sewing project for the Steer Roast.)

\goto{New Business}

Elections!  Vanna is nominated to be Jennifer Berk, on account of being
blonde and close to the blackboard.

The nominees for Onseck are: *Our beloved Ed*; Uh, Joe; Jamie's
experience; Jamie; Our beloved un-Ed; and Mister Ed (an Onseck's an Onseck,
of course, of course).

The First Round voting begins, and the ``Jeopardy'' theme music is
whistled.  ``The correct answer is in fact, `What the fuck?' ''.

Besides the nominees, additional votes are cast for: the scary humming
noise; Vanna; ``everyone else''; the Skinner's studded-leather banana;
the telepathic devil-beast of Gor; the majestic herds of Mr. Eds
stampeding across the plains; censored; Chancellor; Return of the
Chancellor; the iridium-plated standard of civility; ``The Jamie
Morris Experience''; Eddie Van Halen; other Eds; Eddy Ezzard; Eddie
from Ohio; Edie Brickell and the New Bohemians; Beyond the Valley of
the Chancellor; Dr. Ed; and EAK!

[John] ``I crashed my camera!''

``I wonder who won?''  [Steph] ``Wait twenty minutes and I'll tell
you.''  Joe is now designated ``Joe-Bob''.

The Lady High Embezzler tallies up the votes, with the result that
Ed had 6.33 normalized votes, just below the needed 6.5 threshold.

The Second Round vote proceeds.  Additional votes were cast for:
something referring to Ed; the rest of the multiverse; Edvard Grieg;
orange Ed and a leather banana; Being Jamie Malkovich; Fr-Ed; T-Ed;
Jade; Joe-Boy; Jay-Ed; really Vanna; go Vanna go go; I love you Vanna
I want to have your children; Ed's shoes; Ed's pencil; Ed's pants;
the eternal astrophysicist; the J-less one; tickle Jade now; the
costumed Vice, stripped, washed, and brought to Jade's tent; and the
majestic herds failing to notice the cliff edge until far, far too
late.

Tallying the votes gives 9.61 for Ed, who is thus re-elected.

The voting for the LHE!  The nominees were: Stephanie; F; the other
F; Fried Stephanie; fried green Ed; free silver; Laurie Ward; Alan
Greenspan; fried spam and greens; and Stephanie of Gor.

Voting proceeds.  Additional votes were cast for: leather goddess of
Stephanie; Vanna; a French-Fried embezzler; Big Al; Steffie; She-Goddess
Stephanie of Gor; Ed; Casablanca girl; Laurie Ward's lunch breaks;
green Eds and ham; the majestic herds of fried silver Stephanies
galloping across the devil-plains of Gor, embezzling all in their path;
fried green whips; fried green Mr. Eds; shoot JFC now, Stephanie;
Mr. Ed stripped, washed, coated in Teflon, tied to an anchor, and
catapulted toward Jade's tent; the letter before G, but not B, nor
A, C, D, E; Stephanie's big orangina; Stephanie stripped and bound
and... oh what?  I was supposed to be voting?; Brazilian vacation;
Da Fed; and Eowyn.

The vote tallying begins.  Steph gets 5.52 votes, which is not enough,
even though she did the tallying.

The Second Round voting begins.  Additional votes were cast for:
the devil in the form of Stephanie; Stephanie with a P and an H;
pH paper; Stephanie Greenspan; Bob the janitor; ``not Andrea but
still GMly''; Ramalanadingdong vote for Ed; Jade's jacket; Floor;
Ste\_\_anie; Greek spellings of Stephanie; F, the other white meat;
Lady Stephanie; Flying Stephanies of Gor; the guy who's going to
have Vanna walk all over him; what is Mr. Ed doing in Stephanie's
tent, and why is he all tied up?; get Jade a new tent; and the majestic
herds of Stephanie Greenspan embezzling across the plain, capturing
Mr. Eds to send to Jade's tent.

Tallying commences, under the decree that Steph win.  Steph gets
6.64 normalized votes, yay, so she is re-elected.

The Vice!  The nominees were: Joe-Bob; pyromaniacs 'R' us; Yevgeniya
dragged kicking and screaming out of office; Yevgeniya's whip; Joe's
long lens; Yevgeniya's dress; plaything of 3M's; and anything sticky
you can imagine.

The voting begins.  Additional votes were cast for: boy-toy of polymer
nature; blower-up of shit; whips 'R' us; Yevgeniya's other dresses;
Joe in leather dress of Gor; plaything of Gor; Yevgeniya's waterproof
dress; does this mean we get to see Joe in a kinky leather dress;
what the hell... Vanna!; the whip; Vanna; crazy old Joe Foley; Jade's
left breast; Yevgeniya's right breast; forget the pyro... maniacs 'R'
us; Joe-Bob, stripped and dragged kicking and screaming by his long
lens through a field of sticky 3M products, whipped, taped, and brought
to three tents; N1ZRN; Ms's toy; Minnesota Mining and Manufacturing;
stickiness 'R' us; Yevgeniya dragged kicking and screaming into Aaron's
tent of Gor; pyros 'R' us; Karl's sticky imaginary friends; leather
gavel; Joe-Bob has a {\em much} bigger lens than Alohalenscomm; the
majestic herds thunder across the plains, then Joe eats them; and Yevgeniya
with her fluffy bunnies, stripped, washed, sauteed in a white wine
sauce and brought to Joe-Bob's tent of sin.

The tallying begins.  Joe only gets 6.46 votes, just under the wire...
no, wait... 7.46, he wins!

The President!  The nominees were: me; mini-me; Jade's hair; Jenwa,
recycled; opal; opium; Telzey; Jade's good/bad idea; and all the souls
of the ex-Skinners.

The voting proceeds.  Additional votes were cast for: Joe-Bob's anti-soul;
Jade's hair thingy; the Telzey slinky; Jade; Jenwa; odd, no shoulders,
yum; the Bluebellcomm Fairy; Vanna in Yevgeniya's dress; Vanna out of
Yevgeniya's dress; Vanna in Jade's good/bad idea; precious stone of white
or green persuasion; you; Jenwa, just to see the look on her face; Buffy;
Minnesota; my name; manufacturing; HA HA HA HA HA ha ha ha; Jade's
miscellaneous body parts thundering across the flaming tundra; Jade has
several imaginary friends but they're all busy tooling; Vanna-vanilla,
a product whose time has come; J; ``Yevgeniya'' in Russian; Telzey bound
and gagged with his own hair in Jade's stampeding tent; herds of baby
kangaroos leaping off cliffs to Jade's tent; and Jade, stripped, washed,
bound, and brought to Jay's... wait, that doesn't work if they're the
same person.

The tallying begins, with only 5.97 votes for Jade.

The Second Round voting begins.  Additional votes were cast for:
Wahaha, you have all succumbed to my plan!; the Telzey's girl; Jade's
good bad indifferent all permutation thereof; stampeding flocks of
wild bananas hurtling into Jade's bad idea; me; mini-me; micro-me;
nano-me; pico-me; femto-me; zepto-me; Jade bound, gagged, branded
with the gavel, brought by kangaroos to Minnesota mines, where
President Shrub, I mean Jay's orange juice, I mean Jay, lies waiting
in Vanna's leather tent of Gor; Jade's really bad idea; crack; Jade's
hair in Princess Leia buns; hey everyone is stealing my Vanna joke;
$\heartsuit$ Vanna $\heartsuit$; Ed's optional toe; freeze-dried Jade
powder; The plains are sick and tired of being thundered across all
the time.  Can't you all just {\em walk} for Gor's sake?  Or take a
bus?; Jade wrapped in a giant sticky 3M hair thingy; and Vanna in Jade's
bad idea (after it has been washed in hot water).

The tallying begins.  Jade wins with 9.57 votes.  The second place is
really close, but Vanna won 1.3 votes as the official second.

Motion: Buy bananas for the new Star Chamber.  Passes 17--3--1+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
