\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/16/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, March 16, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the demoable Onseck.

Minutes read.

Motion: Beloved the minutes as read.  Not seconded.

Motion: Have the Onseck read the quotes from Jade that he forgot
to read.  Passes 9--0--2+Spehn.  This is then done.

\goto{Committee Reports}

Mobcomm: We got 4096 pennies worth of books.

Jourcomm: We're getting fanfic now, but do we want to publish it?
A discussion breaks out, with the concensus being that there isn't
a rule against it, but it's just usually crap.  It's ``Star Trek''
fanfic, too....  Jourcomm also still needs typists.

Pseudo-Rosfap: We got a copy of {\em APA-Q}.  Discussion of {\em TZ}
versus other fanzines with respect to quality and quantity.

[Jade] ``Any other committee reports that won't result in all the
members killing each other?''

Bluebellcomm: We're lazy, the pile is getting bigger.

Mobcomm$_2$: There is a Science Fiction Book Club theme of books
involving numbers we can choose from.  [Jamie] ``Oooh, do they have
one on 3?  It's my favorite.''  {\em Pi} and {\em e} take too long
to read.  There is also a ``Brain in a Box'' collection and a
selection of adult animation...

Pseudo-Pianocomm: Ran into Katherine Reid, who fled pleading hosage.

Pseudo-Hasslecomm: The big piles of to-be-shelved books are gone
somehow.  Were they shelved or just thrown out?

Foley has been reactivated as Magdex.

Pseudo-Bondagecomm: jhawk said magazines might get bound RSN.

Pseudo-Picniccomm: Still no word from Hal.  [Jade] ``Hal doesn't
like us...''  Discussion of picnic announcement themes and the merits
of the Wheel of Time.  Jade fell asleep during {\em Eye of the World}.

Motion: Commend the Skinner for continuing the streak.  Passes
7--0--0+Spehn.

\goto{Old Business}

The Skinner is older than she was last week.  We'll sing for the
adjournment song.

There is now blank space on the bulletin board.

Sherrian Lea, a former Skinner, has spawned.  A daughter, which upon
discussion it is decided probably did not burst through her chest.

Some of Jade's hair is escaping.

The light that Phys Plant apparently fixed is still flickering.  Perhaps
they fixed the wrong one?

\goto{New Business}

There is a new set of signatures at the bank.  Ed can sign checks
finally, yay...

A member checks his status, and there is an aside on Aaron's initials,
ANU versus AMU.  A renewal happens.

Motion: Commend the Skinner for having all of her itches scratched
away.  Passes ``eight to like... two to like... three plus Spehn''.

Jade is now 22, exhibiting all of the signs of instant senility.  She
is on her way to becoming a puppet ruler.

Motion: Commend the Skinner for being in charge of all the puppets.
Passes 3--0--0+Spehn.

\goto{Future Business}

According to Amazon, the next Harry Potter book will have 10,000
pages.  Robert Jordan is getting jealous.

``Happy Birthday'' adjournment song.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
