\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/05/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, October 5, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the thermally-failing Onseck.

Minutes read.

M: correct the minutes to note John did not actually search for "gentle", "grunts." 3-0-0 +Spehn.

M: condemn the minutes for mentioning "John" and "gentle grunts" in the same sentence. 5-0-2 +Spehn.

\goto{Committee Reports}

Mobcomm: a box of books and a treat for the Onseck. Now he wants 600 dollars.

Jade is reading while conducting the meeting.

Bluebellcomm: the new covering material is much nicer, John covers 25 times the usual number of books. Still a large backlog.

Pseudo-Pianocomm: Kat liked Ed better than John, will come to learn Bluebellcomm.

Pseudo-Sitcomm: Pseudo because I didn't actually watch. Enterprise has been talked about because of the one Vaseline scene.

M: commend the skinner for having heavy hair. Extra neutrons? 5-0-1 +Spehn.

Dexmistress: lots of post-Inventory done, recovered a lot of "missing" books. 34 genuinely gone. Now dexes as well.

Jade drops the new dex. Again and again. Jamie takes over to fix it. Not applying skinnerial powers.

Mike: "The skinner does not muck with mere... matter."

The thread apparently committed suicide.

Pianocomm: eventually will find prentice projects for everyone.

\goto{Old Business}

Lawyers have not followed up with shelves again. Probably each is thinking someone else is dealing.

Jade: "Proven is weak thread."

Shelf bubble in P has stalled. Burst??? Jamie is trying to get prentices to help.

The heart-shaped slinky has broken. Heart-breakers...

There is a Heavy-Gear-based computer animated TV show now. TV Guide says: "Heavy Gear. Outdoors."

Speaking of outdoors, Erin had a huge camping pack. Roasting marshmallows in someone else's house is impolite. Bad puns on bonfire, bon-bonfire, James Bondfire.

Usual stuff.

\goto{New Business}

Jade: "You complain too early."

Jade thinks the newdex binder clip is too wussy.

Got a new member yesterday, who sent email being impressed with the friendly women on duty here. Recommend they get raises.

M: give them a 50 percent raise. No second.

Jade needs more minions.

Mike: "Ve must not allow... a minion gap!"

Jade: "It depends if slaves count as minions or not."

Jamie: "Do you need more fawning lackies?"

Bad extended joke about the Infocom Hitchhiker's Guide game.

We have been sent 3 Shattered Galaxies for review. An online spacewar game. Probably should forward to the SGS. John has cross-membership, he'll deal.

Jamie resists getting addicted by simply avoiding Windows.

M: double the salaries of Erin and Jen Chung. 12-3-0 +Spehn. Jade forgets the number in the middle of the count.

M: commend the skinner for supreme mathematical ability. No second.

New donation from Charles Maxon.

Jade thinks the shoulders on this month's calendar are too male.

Have sold five memberships under the discounted October price so far.

5 people at level 2 of the TIF. Median is still moving at 2 ticks/week. No member complaints since the TIF.

Average of 53 hours/week open.

Tomorrow is LSC lecture with Gaiman, Ellison, and David.

Interzone has the "Best of Thog's Master Class" column for bad writing examples. The Bulwer-Lytton contest.

Mike: "Murdered by pirates is good."

\goto{Future Business}

M: send people on a desperate flight through a banana field on a planet with pink, gray, and white sand. 13-4-1 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1740 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
