\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 2/2/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, February 2, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1705 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the brainstorming Onseck.

Minutes read.

Yevgeniya isn't doing her job because John is still alive.

\goto{Committee Reports}

Pseudo-Jourcomm: {\em TZ} is finished and sent to CopyTech.

Psudeo-Jourcomm$_2$: {\em TZ} RSN.

Pseudo-Pianocomm: Jade saw a prentice doing work for the first time
in two years.

Motion: Clone Stephanie so we can have lots of young keyholders.
Passes 6--0--5+Spehn.

Mortcomm: Gordon R. Dickson died this week, and probably left some
series hanging.

Motion: Sacrifice the bad authors to keep the good ones alive.
Passes by Skinnerial decree.  [Jade] ``Bad always triumphs over good.''

Jadecomm: Jade is in a tan, silver, and black outfit, with undersized
dual hair thingies.  A comparison to chicken haircuts... ``running
around like a chicken with hair in its face.''

Chickens hunt in packs?  John has apparently seen video of this.
The little ones are the smartest.

Jade has secret writing on her hand.

Bluebellcomm: We're nearly caught up with the new stuff.

\goto{Future Business}

The shelves, yay!  A massive reshelving will happen this weekend.
With pizza!  We need to turn off gravity and stop the Earth from
spinning, so we can just leave the books where they are and move
the shelves around underneath them.

Jade is accused of cosecant discrimination after a discussion of
Foucault's pendulum.

\goto{Time Warp to Committee Reports}

Jadecomm: Jade has a studded leather collar to protect her from
the scary outside.

\goto{Future Business}

The outside will hopefully become unscary in the future.

Term is coming.

\goto{Time Warp to Committee Reports}

Analogcomm: Keyholders need to submit hours for the spring schedule.

John is threatened with some horrible fate if he continues to time
warp.

\goto{Future Business}

John confuses the woodgrain patten on Jade's shirt with Moire patterns.
[Jade] ``My body is a flat surface.''

\goto{Old Business}

John tries to find a home for the frame discovered in the ZGT.  It
frames the gavel block temporarily, with a face there to smash.

Shelves are still here.

Usual stuff.

\goto{New Business}

\bing \bing \bing  Jade pounds on the pseudo-freshman drawing.

John has bluffed his management at work, and is content to watch
his stock options in lieu of working.

The outside is big and scary.  [Jade] ``It loooooms.''  The studded
leather helps somehow.

Jade actually has no legs, but is just floating on her feet.  There
is a brief discussion of lifting her skirt to verify this.

Motion: Make all the keyholders happy.  The motion dies a horrible
death.  Keyholders should be productive first, happy second.

John is fascinated by this skirt.  Jade threatens him with the gavel.
[Jade] ``Anyone else want to say anything, except for John?''

\goto{Time Warp to Committee Reports}

Mobcomm: MITSFS owes us money.  Lots of it.

Mobcomm$_{n+1}$: There's a check to MITSFS in the mailbox, it might help.

\goto{New Business}

[Jade] ``Bleah, interviews.''

Submarines bother whales and vice versa.

Apathycomm: Yaaaaay...

The meeting drags.  Discussion of flying, zero-gee, amusement-park
rides, bouncy balls.

[Jade] ``The gavel is asymmetrical.''

Motion: I think someone should just have a banana motion so we can
all go to sleep.  Fails 0--3--1+Spehn.

Motion: Miller motion.  Fails.

Motion: There was a deep and abiding silence... with a banana.
Passes 3--0--0+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1815 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
