\centerline{MITSFS meeting minutes}
\centerline{Friday, March 9, 2001}

\font\sym=msam10
\font\small=cmr6

\vskip 12 pt

MITSFS meeting called to order, 18:00 SST, March 9, 2001.

Jade ``I'' Wang, President and Skinner, presiding.
(``Our beloved onseck is gone.'')

John Carr, pseudo-onseck.  (``You {\it want} to do it!'')

{\bf BING!}

\vskip 12pt

A motion to mourn the passing of our dear, beloved ex-onseck is not seconded.

A motion to commend the minutes as beloved passes \hbox{3-0-2+{\small Spehn}}.

\vskip 12pt

\centerline{Committee Reports}

\vskip 12pt

Pseudo-jourcomm[JFC]: (Yevgeniya protests that she is here and can speak for
herself, but is overruled.) If you can't write your own material, Yevgeniya
needs your help writing someone else's.

Jourcomm[YN]: That means I need people to type for me because people sent
me stories on paper.

Mobcomm[JFC]: We did not get 512 books this week, partly because of snow in
central Massachusetts.

(There is a brief break from committee reports to allow Jamie to
flame about the difference between {\tt treasurer} and {\tt \$treasurer}.
The current occupant of the office of MIT has signature authority on our
account but it would be much better if the office itself had signature
authority.)

Bluebellcomm[JFC]: Everyone except me is lazy.

Pseudo-pianocomm[JM]: Waaah.  There is discssion about recruiting,
freshmen, and a particular frosh who is worth \$4 but not \$11.
Lack of term memberships is a feature, not a bug.

Pseudo-hasslecomm[JFC,JM]: Lots of books to be shelved.  Apparently
this is hasslecomm's job.  Mobcomm cleared the new book shelf in
preparation for the new books that didn't come.


\vskip 12pt

\centerline{New Business}

\vskip 12pt
We got a review copy of a new Jack McDevitt novel from Eos.  They still
like us!  Jamie says it is called ``Deep Sex,'' but it actually has the
more boring title ``Deepsix.''

Jade's friend made it snow today by trying to go to Chinatown.

\vskip 12pt

\centerline{Old Business}

\vskip 12pt

There are discrepancies in our automated account statement for January.
ASA took our money?  Or did they give us money?  The statements
have inconsistent meanings for positive and negative numbers so
we can't tell.  \$114.20 for publicity and \$400+ for books.
After noticing that the amounts and partial (truncated)
descriptions match the Finboard checks we got recently,
and much discussion, we decide that we understand what is going
on and even if we don't understand we won't worry about it.

\vskip 12pt

\centerline{Future Business}

\vskip 12pt

In the future...

...John may go to Harvard Square.

...Jamie may understand how endowment fund interest works.
John suggests abstaining from receiving donations for a
couple years to make the calculations simpler, but it
turns out that this wouldn't help because the interest
rate varies (and possibly for other reasons).

...we will get a response from Hal Clement about the picnic.

...Jamie ({\sym "}) will write SNF \#1, but will probably not
mail it in late March.

...increased shelf pressure due to overcrowding will squeeze the juice 
out of the bananas on our shelves.

``I'm very moving,'' says Jade.

A motion to commend Jamie for wearing a shirt with banana-colored stripes
passes \hbox{6-0-3+Spehn}.

Meeting adjourned 18:20 SST.

\end
