\centerline{MITSFS meeting minutes}
\centerline{Friday, January 5, 2001}

\vskip 12 pt

MITSFS meeting called to order, 17:00 SST, January 5, 2001.

Jamie Morris, chancellor and pseudo-skinner, presiding.  (``Have some scrap paper.'')

John Carr, pseudo-onseck

{\bf Chime!}

\vskip 12pt
Motion by invisible person in chair.  \hbox{3-3-3+Spehn}.
Motion does everything!

(...{\it we block on the single-threaded onseck}...)

\vskip 12pt

\centerline{Committee Reports}

\vskip 12pt

Mobcomm: Mobcomm run 10 AM tomorrow.  Jamie protests.  OK, 11 AM.

Jadecomm: Next week we get our skinner back.

Pseudo-bluebellcomm: There are a bunch of not especially new books
on the shelf.

Pseudo-analogcomm: Extra-extra-curricular activities have delayed
the schedule for the schedule.  We may do IAP like R/O week.

Concomm: Arisia is in about a week.  One of Jamie's new colleagues
is running it.  We probably won't be there.

Coofcomm: Next Friday a delagation from CUSFS will make a pilgrimage
here.  We don't know if they have rescinded their charter.  If they
are lucky we won't give them our surplus Piers Anthony.
({\it The pseudo-onseck's notes are not clear but it is possible that
we actually have Piers Anthony {\rm books}, rather than an extra copy
of the man himself.})

Pseudo-picnicomm: Write Hal Clement soon so we have an answer and a
date in time for the alum mailing.  We have no picnicomm.

Pseudo-jourcomm: TZ RSN.

\font\sym=msam10

{\sym "}: RSN, Jamie will talk to the Alumni Association about mailing SNF.

\vskip 12pt

\centerline{Old Business}

\vskip 12pt
We still have empty gray shelves.  Jamie is too hosed.

Is it finally the end of talk about the new millennium?

There is more talk about the MITSFS doormat.

Usual motion!  Invisible second!  Usual result.

\vskip 12pt

\centerline{New Business}

\vskip 12pt
New millennium for those of us left behind by the rapture.
Oh, that's why campus is so empty.
Empty campus is good except for the lack of people.

Two new members just joined.  They walked in and shoved \$50 in
JFC's face, so he gave them memberships.

Jamie forgot to print New Year's new dexes again.
He should set up a cron job for next year.

The lock change seems to actually be happening.
Really, this time.   Jamie's ID card has a number, JFC's does not.
So how do we give CAC a list of ID numbers by January 15?

\vskip 12pt

Miller Motion!  \hbox{2-5-3+Spehn} Fails!

Miller Motion!  \hbox{9-2-Cheese+Spehn} Passes.

Meeting adjourned 17:20 SST.

\end
