\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 08/10/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, August 10, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1725 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the E.A.G.L.E.-eyed Onseck.

Minutes read.

The Onseck is chastised for leaving out a particular quote. It is still being left out.

M: the quality of the minutes is not strained. No second.

Discussion of our leaking air conditioner.

\goto{Committee Reports}

Jade: "I can't make people second your motion, Jamie."

M: make a really good motion about last week's minutes. 4-0-1 +Spehn.

Mobcomm: got 260 dollars worth of books, including 17 Dr. Who books. (Most were backorders.)

Panthercomm: ...and they were Panthercommed.

Pseudo-Hasslecomm: everything is cleared out, yay!

Pseudo-Pianocomm: Cat Allen did Hasslecomm, is now being put on Bluebellcomm to learn from Master Ed on Wednesday.

Pseudo-Plantcomm: being flooded from the window side.

Pseudo-Bondagecomm: "in the process of" getting quotes, no order-of-magnitude estimates.

Pseudo-Theftcomm: Jamie is doing evil tyrannical things to the TIF sheets. Everyone but maybe Joe is consistently marking hours, good.

John asks after Steph, Jamie digs through his pants to find the answer. (His calendar.) No idea when she'll be back. Frosh are coming soon, LaVerde's has the laundry bag displays out already.

Only 6 bucks for a bag big enough to bundle up the skinner.

M: empirically test this. 7-0-1 +Spehn.

Darkcomm: Bill's apartment is dark. Lost power, hopefully back by 10 PM, since last night, with intermittent fixes. Lot of roaming power outages recently... Central Square, West Campus. Record power consumption from ACs. Jade plans to stay in lab where it is cool.

Dexmistress: June and July new dexes. Inventory wrap-up still in progress. Not many lost/new mismatches from last year.

Pseudo-Theftcomm: people have been submitting to the TIF. Bill disputes the acronym.

M: give Bill special oppression with a Triangular Iron Fist. 4-0-7 +Spehn.

Discussion of the Mobcomm reimbursement forms.

\goto{New Business}

New batch of financial forms, courtesy of Ed.

New locks? Ha ha ha!

Analogcomm forms. Flipbook? A banana slowly being peeled. What is the sound of one banana ripening? Jade: "The same as two, only half as loud."

M: commend skinner for philosophical disposition. Lots-1-something +Spehn.

A cover blurb calls the book "insidious." Is that good? John was creeped out by it, but not controlled.

Jade is trying to switch her hours tomorrow so she can see "Hapgood."

New rates should go up. 12 dollars divided easier. Month-by-month discount? Jamie does a quick average-paperback calculation from the latest Mobcomm report. 11.20 per pair.

M: unusual motion. No second.

Apathy...

\goto{Old Business}

The cowardly Chancellor avoided the flood last week.

John thinks Mike Whitson and Andrew Boardman are the same person, like Clark Kent and Superman. Do we have any Superman stuff? Yeah, some.

"Fierce Grape" Gatorade is awful. Jade only drinks blue, neon yellow is scary.

Jamie readjusts figure to 6.63/book to account for average percent of LPs. 13 dollars would divide into 25 cents/week...

We are now catching up to the old book pricing increase, and implementing an old idea of per-month discounts. It's old business...

\goto{Future Business}

M: stock up with extra bananas to feed the incoming frosh. 7-0-2 +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, "now..." "Now minus a week?" "Then?"

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
