\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/27/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 27, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, ``1700'' SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the blue-and-gray Onseck.

Minutes read.

Motion: Commemorate the memory of poor, dead Arm.  Not seconded.

Motion: Have John beloved the minutes until he gets a paper cut.
This is also thankfully not seconded.

\goto{Committee Reports}

Mobcomm: I didn't do anything useful, but two boxes of books (actually
six) showed up regardless.

Pseudo-Mobcomm: A new member friend of Sarah's donated 178 books for
\$56 or so.  A comparison to normal used-book prices.  We have five
or six more Gor books for the circulating room!  And another copy
of John Norman's {\em Imaginative Sex} too...

Pseudo-Hasslecomm: Hasslecomm is close to catching up, amazingly
enough.  This is partially due to Jamie's mercy.  There is a discussion
of the Hasslecomm ground state: whether it is theoretically possible
for Hasslecomm to ever completely catch up, or whether there will
always be a zero-point residual of quantum books.

Pseudo-Picniccomm: Yevgeniya wrote a picnic invitation, which is getting
sent out almost immediately.  The picnic is Saturday, May 12.

Let the minutes note that Jade thinks our non-punched punch cards
are cool.

Pseudo-Jourcomm: Jourcomm is depressed.

Motion: Take pity on Jourcomm and all go ``Awww...''  Passes
lots--0--1+Spehn.  ``Awww...''

Pseudo-Pianocomm: Yay to Andrew for helping out with the picnic
mailing.

Pseudo-LHE: John took all of MITSFS's cash.

\goto{New Business}

In two weeks we will have a new Star Chamber, but it'll look very
similar.  There is a discussion of how to polish the Star Chamber,
and with what.  The Star Chamber is reported to have a weird
electronic structure, and it smells funny.

John can still mostly see after sniffing isopropyl alcohol.
The expired aspirin in the keyholder desk has been tossed.  Do
expired driver's licenses not count as I.D. anymore?

The banana stamp should be used as a hand stamp at the picnic.
Regular members have to pay us \$0 to attend.

We have a new contact for someone to buy our extra books.  ``Cool.''
We need someone to sell us a bit of curved space, like the TARDIS.

\goto{Old Business}

There are some ongoing interesting things about lifetime
subscriptions.  We apparently got thirty years in a ``lifetime''
from {\em F\&SF}, and at the current rate we'll probably get
sixty years out of our {\em SF Chronicle} subscription.  Will
we still be around when it hits issue 999?

Motion: Encourage the Skinner to have knowledge of people.  [Ed]
``Is this in the Biblical sense?''  Passes 8--0--1+Spehn.

John reports that the January 1966 issue of {\em Fantastic Universe}
had a contest that the SFBC was running, the prize being a round-trip
ticket to the moon.  [Jamie] ``We got gyped on those one-way tickets.''
It is noted that the SFBC cost about the same back then.

Motion: Commend the Skinner for thinking positively.  Voting gives
7--2--4+Spehn.

Motion: Condemn the SFBC for trying to moon its members.  Voting
gives 4--3--3+Spehn.

Motion: Matrix vote!  Voting gives 4--7--2+Spehn.  [John] ``I think
you should count her leg double.''  [Yevgeniya] ``Is it that fat?''
Pentiumcomm reports the determinant as -35 after some deliberation,
so all three motions fail.

\goto{Future Business}

John ponders what to do with a pair of scissors.  Putting them back
in the desk is just so mundane.  The scissors had been used for
cutting a corner off the election sign.

Motion: Condemn MITSFS for cutting corners.  Passes 5--2--4+Spehn.
Spehn will be upset at Jade's shortchanging of his vote.

Jade stands behind Ed, and thus the Onseck is in constant danger
of being brained by the gavel.  Perhaps this will induce a fear of
science-fiction libraries in a future life.

[Jamie] ``Stop going `uh-huh' when you have nothing to add, or
I will kill you.''

Motion: Destroy the future with a big yellow banana.  Passes
9--2--5+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1600 SST, although it is not specified what day.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
