\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/20/2001}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, April 20, 2001

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1720 SST, Jade Wang, President and
Skinner, presiding.  Ed Keyes is the progress-reporting Onseck.

Minutes read.

Motion: Commend the minutes for being dictated to the Onseck by
a UFO.  Not seconded.

Yevgeniya is outside in the hallway, and asks if she can still vote.

Motion: Commend the minutes for being beyond description.  The motion
does nothing, 6--0--5+Spehn.

\goto{Committee Reports}

Yevgeniya stumbles in to report.

Motion: Commend Yevgeniya for knowing her head from her tail.
Passes 10--0--3+Spehn.

Jourcomm: We want a cool cover, but our professional artist has
disappeared on us.

Motion: Commend Jade for drawing something cool for the {\em TZ}
cover.  The motion is not seconded, probably because it ought to be
in Future Business.

Motion: People who don't respond to Yevgeniya's email are automatically
not cool.  Passes 9--0--2+Spehn.  It is noted that ``Jourcomm karma''
is a nice tongue-twister.

Mobcomm and Pseudo-Bluebellcomm: Bluebellcomm did some stuff, and is
starting to catch up, sort of.

The Star Chamber is, amazingly, all here.

Pseudo-LHE: We're out of money, or rather our money is in the wrong
place.

Pianocomm: Someone said ``yes'' to being an apprentice, yay.  Is she
serious?

There is a discussion of Jade as a fledgling keyholder.  John tells
a tragic tale of one day not needing to sign out books for her any
more.  ``Awwww...''  Her old membership sheets are filed away in
New Jersey.

Motion: New Jersey is effectively gone.  Fails by Skinnerial decree,
after she teased us all by taking a vote count.

Motion: Commend the Skinner for abusing her power.  Passes
11--``my left foot''--2+Spehn.  Does the Inverse Skinner Rule apply?

\goto{Old Business}

Donations are still being processed.

There is a new Bondagecomm box, obtained by reorganizing the LHE
drawers.

Motion: Commend the LHE for conquering more territory.  Passes
11--0--2+Spehn.

Jade found an old tally sheet of hers, recording the percentage of
meetings that Jen Murphy attented, but she doesn't remember which
numbers are which, and the math is a little weird besides.

Motion: Make sure Jade never, ever practices kaballah.  Passes
12--0--2+Spehn.  [Jamie] ``You would blow up the world.''

John moved the Welcome sign into the Skinner slot.  This is
probably the wrong thing to do.

About seventeen years of LHE records got moved out of the active
books.  We don't have any books which are bloodstained.  However,
John remarks that if the rainbow-colored slinky were metal and
razor-sharp, Yevgeniya's hands would be bloody.

A spider crawled on John last week in bed.

Ellen Kranzer turns forty in May, and this might interfere with
the picnic.

\goto{New Business}

Yevgeniya shows off her wood carvings.  [Yevgeniya] ``Look, bunnies!''
They don't look much like bunnies, though.

[John] ``When my sister reinforced her dog's ears...''

An investigation into our mysterious vanishing {\em F\&SF} subscription
is ongoing by the Onseck.

Jamie's shelf piece in the circulating room fell off, possibly
crushing a very small member.

[Jade] ``My arm is tired.  Someone make a banana motion.''  Jamie
attempts to sing an adjournment song instead.

Motion: ``Give the Skinner a banand-colored fuzz.''  Passes
8--0--4+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, arm-dead SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Ed Keyes, Onseck}

\end{document}
