\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/28/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 28, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Andrew Clough, President and 
Skinner, presiding; Edward Keyes, Vice and Pseudo-Onseck, recording.

Minutes read.

Motion to have the Pseudo-Onseck read the minutes from two weeks
ago.  Passes 7-1-2\ps.

Margaret arrives.  ``Get this: Warhammer.  40K.  Costume.  Contest.
I am legally obligated to show up.''  Margaret leaves.

Minutes read again, from two weeks ago.

Motion: the noise out in the hall a few minutes ago.  Passes 5-0-2\ps.

\goto{Committee Reports}

\subsection*{Pseudo-Mobcomm}

We have an incredibly-thick book in the ZGT purporting to be {\em A Feast
for Crows}.  Yay, British edition!  It even outweighs the new Robert Jordan
book.  JFC shows off the compared thicknesses, though the page count
is about the same.  Jordan even blurbed the book: ``It's brilliant!''

Incest and fratricide, blah blah blah, ``an effortless read'' says Robin
Hobb.  Except for carrying it around, apparently.  Anne McCaffrey
``read her eyes out''.  Is this a good thing?

Malcolm somehow relates {\em Samurai Pizza Cats} to the discussion that
ensues about various other books and the experience of reading them.  The
latest Harry Potter book apparently is constructed to fall apart
after approximately three lendings, says Malcolm's spy at the public
library.

JFC pulls out our German edition Harry Potter book to show off, when
someone asks for a Latin edition.

\subsection*{War Council}

We have submitted our space allocation form, which will hopefully result
in our getting more (storage) space from the ASA.

Malcolm: ``On the subject of 'everybody dies'...''  There follows a
description of an anime about the myth of the Minotaur, with various
interesting interpretation of Greek stories by Japanese animators.

\subsection*{Pseudo-Hasslecomm}

A frenzy of activity, turning boxes of books into other boxes of books!
Hardcovers, to be specific, processed enough so that they're now Niagaracomm
and Bluebellcomm's problem.

\subsection*{Jourcomm}

Kat is on the verge of publishing something, but perhaps less close to
the verge than before?

A biology professor was fired for scientific misconduct, faking data in
published research.  A short discussion about academic misconduct versus
scientific misconduct.

\goto{Old Business}

Jamie offers to take Ed to tour the warehouse at some point.  The space
there is roughly 7 feet x 7 feet x ``a lot''.  Discussion of parking
changes in the vicinity of Metro Storage due to road construction.

The conversation wanders and eventually resurfaces in the vicinity of
{\em Serenity} comic books and the infamous {\em Buffy} musical episode
from season six.  Except for that episode, Jamie advises stopping at
season five due to the problems with following through the consequences
of the return from the dead.  Spoilers abound.  JFC: ``I didn't know
about that, but I didn't care.''

Discussion of people having the advantage of watching the {\em Matrix}
without having the plot spoiled for them ahead of time.  Jamie: ``They
were all living in a computer?!?  I watched it and never figured that out!''
Discussion ranges to {\em eXistenZ}, {\em Tron}, and other 
``the <foo>-man's {\em Matrix}'' examples, as well as the definition of
``to reify''.  Watching {\em Tron} while tripping is pretty cool,
apparently.

Usual stuff.

ALGOL
\goto{New Business}

ALC: ``Are you saying something about my bing?''

JFC is wondering whether he has fallen into an alternate universe, due
to discovering an old book he never knew had been published by an author
he likes.  The consensus is that the {\em book} might actually be from an
alternate universe, since its smaller mass makes the timeline-slip
somewhat easier to manage.

JFC: ``I remembered that it wasn't by Greg Egan, but it should have been.''
Maybe the author's {\em brain} jumped between universes...  Discussion of
GURPS alternate-universe powers, grabbing things from and sending things to
them.  You want to be careful to specify objects that don't come from an
antimatter alternate universe...  The {\em Timeline Wars} series by
John Barnes discussion: describing a laser pointer to an alternate Edward
Teller, leading to the invention of a nuclear-powered laser weapon.

The conversation then fragments into multiple parallel threads in various
corners of the room, and the Pseudo-Onseck is highly amused and not
attempting to record any of it.

Motion: the meeting has broken up into enough threads that you might
as well have a banana motion to reunify it.  Passes 8-3-5\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1747 (``eighteen negative thirteen'') SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Edward Keyes, Pseudo-Onseck}

\end{document}
