\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 8, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Last week's Pseudo-Onseck, Margaret Gentile, reads the minutes.  Move
to approve the minutes as suitable for submission to {\em Analog}.
(Friendly amendment: "Suitable for submission to {\em Twilight Zine}? 
Jamie: "Anything is suitable for submission to TZ.")
Passes 12-0-1+Spehn.

\goto{Committee Reports}
\subsection*{War Council}

\subsection*{Pseudo-Jourcomm}
"So, what's up with that?"

\subsection*{FrustratedAuthorComm}
*whiiiiiiine*  "I want my book back!"

\subsection*{Onseck}

The Library has pens!  (Or it did three weeks ago, so if it doesn't anymore you
people need to stop eating them.)

\subsection*{Mumbling about Rats (Vox Sciurorum)}

John provides photographic proof that squirrels are tool-using mammals.
"John, that evidence is worth nothing.  Everyone knows squirrels can fake
photographs."

\goto{Old Business}

"I cut off your toe but I got a good view of the back of your throat."
[Isn't context such a wonderful thing? -ed.]

Motion to lobby the people in charge of the Boston July 4th fireworks to purchase
dodecahedral fireworks next year passes 12-0-3+Spehn.

"If it's an expanding universe or a shrinking universe, it's okay -- there's 
always room for Jell-O."

Usual &c.

ALGOL  
\goto{New Business}
Margaret shows off her Very Large Glove and the other parts of her Warhammer 
40k costume.

\goto{Future Business}

The Sci Fi Channel is airing all the currently-made episodes of {\em Firefly}.
Dark Horse is releasing a three-volume comic to tie together the TV show {\em Firefly} 
and the movie {\em Serenity}.

"The campus of the Indian Institute of Technology, in addition to having palm
squirrels, also has jackals." 

Miller motion chickens 8-4-9+Spehn.

Miller motion passes 7-1-5+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
