\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 26, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Move to commend the reading of the minutes as "demonstrating good elocution" passes 8-0-1+Spehn.

\goto{Committee Reports}
\subsection*{Skinner}
Hopefully the prescreening tickets to Serenity, the movie based off the TV show Firefly, will
arrive in time.

\subsection*{FrustratedAuthorComm}
[insert obligatory whine here]

\subsection*{PseudoFWeekComm}
The freshmen are coming!  HBarComm is on the task. 

("One if by land, and two if by sea, and
three if by air, and four if by Death Star, and five...  crap, I'm out of lanterns.")

\subsection*{OneThousandMonkeysComm}
There's a book called _Grudgebearer_ coming out which has a scene (on page 125, it appears)
in which a meeting in a Dwarf Engineering Hall is called to order with a large steel spanner
fitted with a sapphire in the center.  "Obviously," quoth Tim Huckelbery (ex-Skinner 1984), who
reported it to us, "the power of the One True Gavel is spreading."

\subsection*{Onseck}
The address stamp has died.  The Onseck will go to University Stationery to get a new one.

\goto{Old Business}

"Excelsior!"

ALGOL
\goto{New Business}

"I burned myself with a soldering iron the other day!"

\goto{Future Business}

"You're in the larval stages of cruft."  "Crufty the Clown?"

Motion to condemn the banana for being a member of the Committee to Assassinate the Skinner and
doing a damn poor job of it passes 7-4-3+Spehn.

Next week we will be convening at 5:30 PM.

\vspace{12pt}

\noindent
Meeting adjourned, 18 negative 30 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
