\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/8/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 8, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

The meetings are condemned for containing Fortran 77 by 11-1-3\ps.

\goto{Committee Reports}
\subsection*{War Council}
No new space, but they may be working on it, in the sense that they're
screwing us and starting from scratch.  They seem sympathetic,
except the ones who don't.

\subsection*{LHE}
If you're going to request a reimbursement, please specify your name.
It's hard to pay you otherwise.

\subsection*{Jourcomm}
Pointer to art documents provided, but faulty.

Michael Bellesiles is not appointed to Jourcomm, chickening 2-2-16\ps.

\subsection*{Mumbling about Rats (Vox Scirorum)}
The most wonderful movie in the history of the world, Tim Burton's
\emph{Charlie and the Chocolate Factory}, is coming soon.  It will
feature a cast of trained squirrels.

\goto{Old Business}
The block party got us some prefrosh.  They appear real.  We probably
shouldn't poke them.

We've been contacted by the Alpert, who wishes advice on getting books
and magazines appraised.  We can't really help him, but it's suggested
that there might be something on our web page some place.

ALGOL
\goto{New Business}
``Usual bitching, let's move on!'' ---Yelena

Mars Rover missions being extended by another 18 months, with help
from the mysterious dust devils.  But Voyager's getting kacked.

We've got some boxes of books, together with packing peanuts.  They
are roundly condemned.

The weather control satellites failed, and are condemned.

\goto{Future Business}

The Boston Underground Film Festival is tonight.  \emph{Zombie Love}
and maybe \emph{Bleeding Toasters} will be featured.

The sun will go out.  But it will get really bright first.  And burn
up the Earth.  There's some question about whether our sun has iron,
and if not where all of ours came from.  JFC is schooled by YT on the
subject of supernovas and dwarves, white and otherwise.

We may have pictures of an extrasolar planet.  It's a pixel.  It might
be a planet.  It might be a brown dwarf.  It might be dust on the lens.

The Hubble constant is condemned for being mean. 5-2-1\ps.

It is noted that Clever Banana Motion is an oxymoron. 16-4-9\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1756 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
