\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/18/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 18, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Ross, the pseudo-Onseck, is commended for channeling Brian. Passes 14-2-11\ps

\goto{Committee Reports}
\subsection*{LHE}
We have money for hardcovers and are paying it.

We're joining the International Banana Club, but it's not clear how to
pay for this---the color of the money isn't certain.

\subsection*{MagdexMakeWorkComm}
Andromeda Spaceways has sent us a new magazine.

\subsection*{MobComm}
Vast piles of books have been ordered and will be arriving shortly.

\subsection*{Jourcomm}
``Me first!'' ---katallen
Look, TZ 46.  It has content.  It's edited.  It'll be printed and
distributed\dots you know when.

\subsection*{Mumbling about Rats (Vox Scirorum)}
``A squirrel broke into my sister's apartment once''---JFC

A motion to have those responsible for the credits sacked along with
those responsible for having them sacked, sacked\dots chickens.

\goto{Old Business}
A relic of the ancients, Ken Johnson, Libcomm for many years, is
visiting.  Despite a resolution to remove the name ``Ken Johnson''
from the publications of the society, and a motion to publish the
minutes passing 21-3-0\ps, his name nevertheless appears here.

ALGOL
\goto{New Business}
The Skinner is commended for efficiency\dots by Skinnerial decree.

CPW is coming.  ESP wants to throw a 4th-floor block party.  Now
\emph{that} is something MITSFS can really show itself off at.
There's an organization meeting Monday, 8pm, after spring break.  We
will have an inflatable castle.  Sam suggests we should instead half
an inflatable castle, and this is accepted as a friendly amendment
mid-vote.  Passes 15-0-2\ps.  If we nest them, we can have a castle in the air!

The UA is doing strange revisions to old-ASA policies.

Andre Norton has passed away.  In accordance with her wishes, she will
be cremated with copies of her first and last novels.

The BBC radio-play adaptation of Neuromancer is available at
\verb|http://www.tubeville.org/neuromancer/neuro.htm|.  The first five
minutes are the \emph{sound} of a television tuned to a dead channel.

\begin{quotation}
       MITSFS is only nominally a fan organization.  The majority of
       the membership are wierdos who actually read the stuff and belong
       only because of the library.  Those who cannot read form the
       activist, or meeting-going, members.  Those who can neither
       read nor write contribute to TZ.  Among this motley meagerie
       are a few fen who somehow have missed being committed.  So TZ,
       whatever it may be, only pretends to be a fanzine.
       \\ \hfill --- excerpt from ``We Try Harder,'' Richard Harter, TZ\#18
\end{quotation}
We have a really pretty cover, but it's got a misspelling.  Maybe
we'll find some way to fix it.

\goto{Future Business}
The Picnic will be in early May, though Picninccomm is strangely
absent tonight.

Mobcomm: yet more books shall be purchased.

On April 29, the $(\mathrm{HTG})^2$ movie will be out.

Insane nattering proceeds, invoking a Miller Motion which fails
11-17-18\ps.

An inaudible motion fails by Skinnerial miscounting.

AFC suggests that 1+1 be set equal to 3 so that we can have a banana
motion that both passes, fails, and chickens.  This passes and
chickens, but somehow does not fail, 25-7-3\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
