\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 30, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion to approve the minutes as being typical (with a pork amendment to appropriate
30 billion dollars for banana research in the glaciers of Alaska) fails not very much-a little-
a few more+Spehn.

\goto{Committee Reports}
\subsection*{War Council}

\subsection*{LHE}
Margaret continues to be trained and has shown her aptitude at picking up checks.

\subsection*{FAC}
\emph{whine}

She has a story in someone's \emph{small} slushpile.

\subsection*{HassleComm}
Two boxes of books were processed.  We have two more books we can process.  Not sure what
we're blocking on -- need to talk to Jamie.

\subsection*{Pseudo-MobComm}
We got a box of books from the Science Fiction Book Club which we appear to already have
copies of.  MobComm may or may not be AWOL.

\subsection*{Aloha Lenscomm}
Skinner-blackmail material is obtained.

\subsection*{Mumbling about Rats (Vox Sciurorum)}

\goto{Old Business}
The book that Malcolm lost has returned to us from Mount Ida College.  Unfortunately, he's
already replaced it.  ``It came home because it knew it would have a friend now.''

``Badassium''

Usual stuff.

ALGOL
\goto{New Business}
\emph{Serenity} and \emph{MirrorMask} are out today!!!  (\emph{MirrorMask} is a movie with 
Neil Gaiman and Dave McKean doing story and Dave McKean doing everything else.  There are a lot
of computer graphics being used, but they're not supposed to be photorealistic -- they're designed
to get what's in Dave McKean's head, out.  And Dave McKean's head is a strange, \emph{strange}
place.  The story sounds cool, too. :)

``Klingon should be the official language of America!''

Malcolm has a coin with a strange alien creature on it.

\emph{thunk.}

\goto{Future Business}
``Somebody make a banana motion.''

Motion to appropriate 63 billion dollars in the budget for banana research in the Alaskan glaciers
passes 10-2-5+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
