\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/07/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 7, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and
Skinner, presiding; Brian Sniffen, pseudo-Onseck, recording in the
absence of Kevin Riggle, Onseck.

Minutes read.

Phillip moves that last week's banana motions be forwarded to the
banana research review committee yet to be created.

\goto{Committee Reports}
\subsection*{Pianocomm}
There is one now.  She'll be talking to the prentices and trying to
shepherd the process along more smoothly.

\subsection*{pseudo-LHE}
We got money from the UA!  All that we asked for, which wasn't much,
but we did get it all.

Per BTS' motion, the LHE is sent for training in how to use Orbitz to
book and take trips to Brazil \emph{before} reporting such
information.

BTS suggests removing any supports, thus converting the potential LHE
into a kinetic LHE.  JM points out that there is a problem: MHG is
already plenty kinetic.

\goto{Old Business}

Mirrormask: ALC saw it.  Sort of Neverending Story, sort of
Labyrinth.  Very pretty.  Yelena moans about the lack of David Bowie's
pants.

Serenity is also recommended.  Good music.  Either too many changes,
or not enough---caught in the awkward place between the small screen
and the large.  Malcolm recommends UU Hackaso as a complement: it does
both not enough \emph{and} too much to make the transition.  Yelena
compares it to the Dune miniseries.

ALGOL
\goto{New Business}

Jamie Morris, JM, has resigned as Chancellor, Associate Director, and
Director of Special Operations, and Keyholder of the MITSFS.  The
Skinner has met with the Star Chamber and other Powers to figure out
how to cope.

There's some fun commentary about the \emph{Dune} board game and its
precog mechanic.

We got a big donation of books from a Globe reviewer, including some
proofs.

It's a new month.  Rates drop \$1.

Kat is not condemned for not having enough New Business.

\goto{Future Business}

Mail will be going out soon soliciting votes from the Instrumentality
concerning some changes to the Star Chamber.

There is some motionizification to commend Kat, but it chickens
7-5-7\ps.

ED bananas that we motion this meeting.
JM: ``Banana I ED motion meeting this.''
KHA: Matrix Vote!

\[
\left|\begin{array}{ccc}
8 & 2 & 7\\
16 & 2 & 1\\
7  & 8 & 3
\end{array}\right| = 748
\]

Determinant is 748; meeting adjourned.


\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
