\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

A MITSFS Tale 

Friday, December 9, 2005

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

Margaret stepped inside the library, expecting to see the usual gang of meeting regulars. Instead, there were only two, Ed and Andrew.

"The snow scare everyone away?" she said, slumping into the chair in front of the computer.

Ed responded with a nod. "Probably."

"Does this mean we get to preemptively banana the minutes?" she asked.

Andrew shook his head, an odd smirk on his face. "No."

The corners of Margaret's mouth suddenly curled into a smirk of her own, though one far more evil. "Does this mean I get to make some minutes up?"

Ed started to laugh.

"Sure." Andrew replied, hefting the gavel. "That way, everyone who shows up next week will be sad at all the things they missed. I just have to bang the gavel to make it official... I'm the Skinner, of course I must bang the gavel."

He raised the most holiest of wrenches above his head, and brought it down for the strike...

...But nobody expected what would happen next.

BING!

CRASH!

Margaret was thrown from her chair at the sudden jolt. "Minutes don't go crash!" she shouted, covering her head as chunks of ceiling tile jarred loose in the blow fell down to the floor.

Andrew stared at the gavel. "We need to talk to Physplant about this."

Ed cautiously rose to his feet, walking at a snail's pace toward the window. There was another sudden crash, much like an explosion, rattling bookcases and tossing many volumes to the floor. Margaret crawled under the desk. "What the hell is going on!"

"No!" Ed shouted, bolting for the door. "Everybody run!"

Andrew and Margaret both followed close on his heels, instinct taking over the urge to ask questions.

"What is it?" Andrew said.

"The Burma jets!"

Urgency further overtook the situation as the three keyholders scrambled for the stairs. They ran from the student center out into the street.

The campus was in ruin, a shell of its former self. Acrid smoke curled up from the remains of crumbling buildings.

(Simmons, Kresge, and the chapel were also gone, but nobody cared about those, because they were ugly anyway.)

"What's going on?"

They looked towards the sky as a trio of grey, poorly-drawn jets buzzed low over the decimated student center, dropping payloads of pencil-sketch bombs.

Andrew hefted the gavel like a baseball bat, a determined look in his eye. "If they think they're going to take us down, they've got another thing coming..."

Margaret set her backpack on the ground and started hurriedly rummaging through its contents. She pulled out a chainsword, oblivious to the clear and numerous violations in the laws of physics that would have to exist in order to allow her to do that.

Ed glanced at her.

"What?" She shrugged. "You watch anime, what did you expect? Besides, this is way cooler than a mallet."

Ed sighed. "You're right." He reached into his pocket and removed... a Blackberry. "Damn..."

"Okay." Andrew said. "They're probably going to come back soon. We have to figure out how to stop this. We have to stop the Burma jets."

An odd, papery engine hum started to grow in the distance.

"Strafing fire!" Ed yelled, diving behind one of those ugly concrete 'benches' in front of the remains of the student center, which, oddly enough were perfectly suited to their newfound use as makeshift cover.

Bolts of heavy pencil pocked the ground in explosions of cement and graphite as Margaret and Andrew dove out of the way.

"You couldn't pull a heavy bolter out of your bag instead?"

Margaret shook her head. "I never made one of those."

Andrew rose up from behind his cover, dodging the Burma jet fire as he ran forward.

The first of the bombs started to fall.

With a mighty swing, he hit the falling shell as hard as he could... But this one was different. It didn't rebound, it didn't explode. It bounced noisily across the ground, coming to rest amidst a pile of debris.

"So much for that idea." Andrew said, his shoulders sinking.

Ed rose from his cover. "Uh, guys? It's moving..."

Sure enough, the shell started to shake and quiver like an egg about to hatch. The fragile sketch lines of the metal started to crack, then break apart. The shell burst open, hundreds of squirrels pouring out in a frightening gray swarm, moving like a single organism.

"Shit!" Margaret shouted. "Run, I'll hold them off! Take my bag!" She brandished the chainsword, slicing into the advancing mass.

Andrew scooped up the black bookbag and started to run. "Come on, we can't save the world if those squirrels get us."

"Head for the Charles!" Ed said. "Nothing can live in there!"

They both took off for the river as the swarm of squirrels overwhelmed Margaret. Looking across the river, they could see the true extent of the damage. All of Boston was gone, reduced to rubble by the steady pounding from the Burma jets. Several MIT sailboats set loose from the bombings floated in clumps down the river like fallen leaves.

"Quick!" Andrew pointed at one of the boats with the gavel. "We need a boat!"

He and Ed climbed down the conveniently placed rung ladder bolted to the containment wall near what was left of the Harvard bridge (there really is a ladder there, I'm not lying), leaping into a passing boat.

"What are we going to do now?" Andrew said.

"We have to end the meeting." Ed replied, thumbing at the Blackberry. He looked up, staring Andrew right in the eye.

"But we need the gavel block, and we can't go back and get it."

Ed stared at the black bookbag. "Anime physics..." he whispered. "Give me the bag." He pulled open the bag, reaching inside. The interior was surprisingly spacious. "I don't know why she just didn't do this in the first place but Margaret just has to have the chainswords... found it." he said, and removed the heavy black block.

Again, nobody dared question the logic behind this event, they were just glad it happened to work out.

Ed set the block down on the boat. "You know the game, Andrew."

Andrew raised the gavel.

BING!

They were back in the library. Everything was still in place, and aside from the howl of the wind outside and the obnoxious banter from people in the glass office down the hall (you all know who I mean...), everything was quiet.

"Whew." Ed said, slumping back into his seat, the familiar, scratchy and odd-smelling banana chair next to the keyholder desk. "That was close. Whatever the hell it was that you did, Andrew, don't do it again..."

Andrew glanced around. "Hey, what happened to Margaret?"

"So I found out that story about Russian piranha squirrels isn't true..." Margaret appeared in the doorway, chainsword in hand, covered in countless tiny scratches. "Damned if the little bastards didn't try, though... How did you make everything go away?"

"We banged the gavel to end the meeting." Ed said.

"Wait... gavel? But we didn't take the block with us when we left the library."

"We used your bag and pulled out a block." Andrew said. "That whole anime physics thing is useful."

Margaret's face suddenly paled. "That wasn't a gavel block, that was my laptop!"

\end{document}
