\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 15, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Andrew Clough, President and
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion to banana the minutes passes 12-5-4+Spehn.

Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Andrew Clough, President and
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion to plantain the minutes, and rename them Special Skinnerial Edition with Bonus Deleted Scenes and Member Commentary so we can put it on DVD and sell the DVDs for \$20 more than regular passes alot-some-verylittle+Spehn.

\goto{Committee Reports}

\subsection*{Pseudo-PianoComm}
Ylena is being trained at BluebellComm, because we couldn't find "that drawer" where Jamie put the clipboard.

\subsection*{MovingThingsAroundComm}
It is suggested that this committee be renamed the Society for Creative Rearrangement.

Moves happened.  Someone should document this at some point.

\subsection*{MobComm}
The long awaited Space-Crime Continuum order has been arrived, and aportioned out to the appropriate committees.

Fans of the male nipple will be pleased by recent MobComm purchases.  Andy denies all involvement.

\subsection*{Mumbling about Rats (Vox Sciurorum)}
John believes he has found another defective squirrel.

\goto{Old Business}
Andy ran for the ASA about a decade ago on the platform "the Library
needs more space."  The Library is still running out of space, just like it was last week, and the week before, and
the week before, and the week before...

Motion is made that the Society create a photographic record of our quest to find more places to put books, and 
have it published entitled "The Conquest of Space."

Jamie: "You need to make it clear that it is us being conquered by space, and not space being conquered by us."

ALGOL
\goto{New Business}

The sixth Harry Potter is coming out tonight!

"Are you a '90\% of everything is crap' person or a '10\% of everything doesn't suck' person?"

\goto{Future Business}

There is an impromptu performance of the Philosopher's Drinking Song.  "I drink therefore I am."

Motion to table the meeting because we've already had one this week passes 15-0-6+Spehn.

"Banana!" fails 3-4-9+Spehn.

Motion to make the previous motion un-lame passes by Skinnerial decree, and passes 19-0-7+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 (-50) SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
