\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/01/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 1, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are regarded as sacred documents of the society 17-4-2\ps.

\goto{Committee Reports\footnote{``No wait, I said that already.'' ---Skinner}
\subsection*{War Council}
Some non-Kat person must talk to the ASA about the new room, since she
gave her great power to the LCS before giving it to us.

\subsection*{Theftcomm}
There's a new TIF, now all-digital.  It rocks.

\subsection*{Boriscomm}
More calendars!  Thanks to Jade, Justin, Margaret, and John.

\goto{Old Business}
Aloha Lenscomm lets us know that he was once at a meeting.  He took a
picture there, which impressed him and one other attendee.

The Old Year has ended. Yaaay!

The port-22 messages on psi-phi went away because we moved the sshd.
We resolve to look for a computer with a starboard as well as a port
12-4-2\ps.

Tax letters have been prepared---all but one.

ALGOL
\goto{New Business}
It's IAP now.  The Frosh still think this is cool.  Perhaps we should
get them some digital watches.  There is a problem with the position
of keyholder being immune to Planck's constant.

A good office chair would be nice for the keyholders.  Brian will fix
the one we have, or we'll buy another one.

A movie, \emph{White Noise}, appears to resurrect Thomas Alva's old
idea of a radiotelephonogram for talking to the dead.

\goto{Future Business}
``I sometimes get the feeling we're all living in a William Gibson
novel'' --kevinr

``Living in the Killing Star would really suck.'' --JFC

Free Silver for the Shiny Blue Penguin 19+William Jennings
Bryan-2-3\ps.

Malcolm asks ``Why is Walt Disney World like Viagra?'' and is rapidly
Albanianed.  Brian looks up the answer, involving waiting an hour for
a two-minute ride, and narrowly escapes being Albanianed.

A motion to have the society wait an hour for a two-minute ride fails
for lack of a second.

Some discussion of next week's mystery hunt ensues, and Brian
demolishes Brad's arguments defending its moral virtue because it
caters to non-students.  Brad says this is

A motion to run canals across the universe to avert its inevitable
heat death chickens 5-1-6\ps.

A motion to declare Harvard the center for all the suck in the
universe passes 7-2-3\ps, despite the redundancy: Vericon is happening
at Harvard.  If you write down everything that happens
there\footnote{a Verilog}, you could put it on a chip.

Malcolm and Andy talk about \emph{Modest Robot and Pervy Rabbit}.

\noindent In a matrix vote:\\
A motion to pretend he was talking about bananas passes 6-2-5\ps.\\
A motion to commend Jamie for not listening passes 7-4-2\ps.\\
A motion to have a matrix vote fails 2-5-3\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
