\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 5, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, 
President and Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion to condemn the minutes as containing insufficient blue shinies passes 20-0-8+Spehn

Blue shiny.  Shiny shiny shiny.  Blue!  And Shiny!

\goto{Committee Reports}
\subsection*{FrustratedAuthorComm}
[insert obligatory whine here]

\subsection*{MobComm}
The Space-Crime Continuum is closing, taking our primary source of books with it.

"Did we ever look into using Ingram?"\\
"There were three people for three years assigned to look into Ingram."\\
"Yes, but did we ever *actually* look into Ingram?"\\

"Are we liable if someone gets trapped in the Library, Tron-style?"\\
"No, because they have to get out to file a complaint!"\\

A bunch of books were ordered from the SFBC.  They may show up in future business.

\subsection*{Mumbling about Rats (Vox Sciurorum)}

There is what appears to be a blue shiny toy on John's window ledge.  John has also determined that his squirrel keeps
a more reqular schedule than he does.

\subsection*{OneThousandMonkeysComm}

MITSFS gets strange e-mail.

\goto{Old Business}

Motion to condemn the Daystar for inconvenient timing passes by Skinnerial decree.

Motion to kill the fly passes by Skinnerial decree.  "With the gavel!"

ALGOL
\goto{New Business}

For the second time in two weeks, there's a former MITSFS member in the local paper.

The Skinner misses the fly.  Margaret is deputized to kill it.  "This can't end well."

Motion to commend Margaret for playing with black widow spiders passes 8-5-1+Spehn.

Motion to end the meeting without passing a banana motion passes 20-1-9+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
