\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 18, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motions: to commend the minutes as good, whether they make Slashdot or not (11-5-3\ps) \\
to plantain the minutes (4-5-4\ps) \\
to prevent the minutes from appearing on Slashdot at all costs (5-10-3\ps)

TI-83Comm reports a determinant of -225; all motions fail.

\goto{Committee Reports}
\subsection*{Pseudo-JourComm}
There's a proto-TZ (``it hasn't quite sauntered out of the primordial ooze yet'') in the office,
ready for people to do the final edit (``there were other 'final' edits, but I wasn't the one calling
them that'').  Incidentally, we've now got a shiny \LaTeX template (thanks to Kat), so the next
TZ's should be substantially less painful.

\subsection*{Pseudo-MobComm$_2$}
We've got a package from Amazon and a couple from SFBC, so we're starting to get MobComm again.
Looks like it's Star Trek and Baen stuff.

MHG: ``Can you say `stereotypical Baen cover'?''\\
BTS: ``There's no dragon!''

``I thought we talked about that and decided we didn't want it.''

\subsection*{Pseudo-HassleComm}
HassleComm put together about 3.5 boxes, but the run is still in progress.  The beginning and the
end of the alphabet has been processed, but the middle hasn't been done yet.

\subsection*{Dexmistress}
We have new Dexes!  We've also started talking about the `i' word again.  (``Are we going to do
an inventory after every TZ?''  KHA: ``I can arrange that.'')  We're planning on having the big push in
late IAP.  Incidentally, about half of the books in the KBX boxes are Hassle-able (though it's not
{\em half of the boxes}, it's {\em half of the books}.

ALGOL
\goto{New Business}

The military has created fearless mice with just a little bit of genetic engineering.  (``Just 
imagine what would happen if that cross-pollinated with squirrels.'')

Usual motions...

\goto{Future Business}
Motion to investigate genetic alteration of motions to make them fearless chickens 7-3-8\ps.

The new Harry Potter movie is out.

Motion to implement a Banana parser using Xerces so the Onseck doesn't fail 6.170 fails.

Motion to develop a bi-metallic electric process to preserve the meeting minutes {\em ::confused::}.

Miller motion chickens 6-7-8\ps.

Motion `banana' fails by Skinnerial decree.

Miller motion passes 10-3-4\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
