\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/21/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 21, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

The Onseck is commended for having rewritten history in accordance
with his duties 6-8-6\ps

The minutes are commended for having hair and giving birth to live
young but not smoking cigarettes 15-1-4\ps.

And this is a matrix vote 14-5-3\ps.

\goto{Committee Reports}
\subsection*{Mortcomm in Exile}
Noted comics illustrator Freas died around New Years.

\subsection*{War Council}
The UA has the ASA's brain out on the operating table, so we're
somewhat unsure about when we'll have access to 401-D.

\subsection*{Skinner}
L'deux student groups c'est moi.

We have hopes for a new ROSFAP (MHG) and a new Mobcomm (SCP?)---and a
new Deputy People's Albanian Embassy (CC).  It was never contemplated
that Albania would outlive its Ambassador, so we have no procedures
for replacing him.  George Flynn is thus eternally the People's
Albanian Embassy.  It is assumed that Ellen's successor will be the
Assistant Deputy People's Albanian Embassy.

\subsection*{tropernu onaiPcomm}
Mike Whitson is leaving us; he's busy with work and moving away anyway.

\subsection*{PseudoOnseck}
Ed found several months of 2001 minutes in his office; they'll be
returned soon.

\subsection*{MobComm in Exile}
Incoming!

\subsection*{LHE}
I talked to Laurie Ward about POs and interest.  We can set some sorts
of ACL, which may or may not be useful enough.

\subsection*{Niagara}
We'll have a real memo of understanding with Better World Books, and
selling the old comic books.

\subsection*{Aloha Lenscomm}
Flashes the meeting. \emph{Auuugh!}

\goto{Old Business}

All of the tax letters have been sent for donations received in 2004.

The comic books are in Lake Erie, not California.  With that exception:

ALGOL
\goto{New Business}

The governor of Minnesota reports that the jingling noise from the
woods is the brass monkeys leaving.

The mayor of Boston says there are no dirty bombs targeting the
harbor.

The Onseck points out that the Romans dated the last half of each
month by counting backwards from the first date in the next month,
\emph{but counting both endpoints.}

It's the 75th anniversary of Analog.  Jack Wilson had stories in the
first, and new stories now.

\goto{Future Business}
We're getting a blizzard during the marathon\footnote{Saturday night: Snow, heavy at times. Snow accumulation of 12 to 18
       inches by daybreak. Very windy with blizzard conditions possible.
       Not as cold with lows in the mid 20's. Northeast winds 20 to 30 mph
       with gusts up to 40 mph, increasing to north 30 to 40 mph with gusts
       up to 50 mph possible after midnight.

          Sunday: Cloudy with snow likely in the morning, then partly
       cloudy with a chance of snow in the afternoon. Total snow
       accumulations of 1 to 2 feet. Coastal flooding possible during the
       morning high tide cycle. Strong winds with highs in the mid 20's.
       North winds 35 to 45 mph. Gusts up to 55 mph possible, decreasing in the
       afternoon. Chance of snow 70 percent.}.

The \textsc{Tyrannical Iron Fist} is coming (back)!

Stratton House is having its picture taken soon.

It is resolved that we will just sit here in awkward silence until
somebody comes up with a really clever banana motion. 17-5-4\ps

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
