\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/23/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 23, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order with a pathetic ``bing'',
1700 SST, Andrew Clough, President and 
Skinner, presiding; John Carr,  Pseudo-Onseck, recording.

Minutes read.

Strip the minutes of planetary status.  Passes 13-1-4+Spehn.

\goto{Committee Reports}
\subsection*{LHE}
LHE is being trained has been trained will be trained.
Those darn people at the cashier's office close at 2:00.

Margaret: "Bask in Gary's 1337ness."
Gary eats Margaret.  ``It's funny because I'm tired.''

Malcolm makes a bad pun and is Albanianed 9-2-2+Spehn.
Jamie does the chicken dance.

%\subsection*{War Council}

\subsection*{Pseudo-MobComm}
Mobcomm removed the SFBC flyer.

\subsection*{FrustratedAuthorComm}
*whine*

\subsection*{Onseck}


\subsection*{Vox Sciurorum}

Animals are fighting over John's bird feeder.

\subsection*{Aloha Lenscomm}

John has a picture of Margaret.
Does Andrew need a new picture?  Margaret talks about dressing him up.

John: ``Will you dress up anybody who I want to take a picture of?''

Margaret: ``I don't like the way this is going.''

\goto{Old Business}

Boring academic discussion.

Astronomers propose ending the debate over the term ``planet'' and its
application to little bodies in the outer solar system by ending use
of the term ``planet.''

Margaret laughs at the word Uranus.  ``It's funny because I'm tired.''

We need new mnemonics if we change the list of planets unless we
preserve the first letters of the names in order.

ALGOL
\goto{New Business}

``Maybe their souls are reincarnated in apes and that's how humans evolved.''

Margaret dressed like a corporate minion for career fair.
Skirts are good to conceal weapons under, and fun to search
for weapons under.  This observation earns John a visit from
Gary.

Margaret was asked whether her GPA was out of 4.0 or 5.0.
This leads to a long discussion of grades.  One potential
employer threatened to send Margaret to grad school and
she fled in terror.  She wants to tunnel out of MIT into
the world, not spend years sucking up in a government job.

Karen: ``You'd be surprised at how far sucking up can get you.''

The Pseudo-Onseck's input buffer is empty.

Margaret: ``Squirrels!  Killer squirrels!''

Boring discussion of French anime and {\it Heavy Metal} follows.

Karen's father let her cut pictures out of Dragon magazine for
a school project to illustrate Tolkein's poems.  People attempt
to recite Orcish poetry.

Report from Altair-4: The microfilm and microfiche readers
were dispelled to Altair-4, and took a bunch of boxes with
them.  We now have couches!

At John's prompting Margaret starts the skinner song.

%\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 18:-15 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
