\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 12/16/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 16, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Andrew Clough, President and 
Skinner, presiding; John Carr, Pseudo-Onseck, recording.

Minutes read.

Approve the minutes as completely true to life and eminently publishable
17-0-2+Spehn.

\goto{Committee Reports}

Margaret presents a Sacred Relic banana to the library.
The Members bask in its glory, until Margaret puts it in
its sleeve.  Andrew suggests making it the foreign banana.

The fake banana was surplus from a project to make a fake
banana bunch.

Oops, she meant to say Unholy.  "It's not the good kind of sacred."

\subsection*{War Council}

We did not get everything we hoped for but we now have all
of W20-401D.  The LCS is moving elsewhere.
Chocolate is weapons-grade sugar.

%\subsection*{MobComm}

\subsection*{LHE}

Somebody paid for a membership with a check last summer but
the check was never deposited.  In January we will spend more
than \$12 worth of time to figure out what went wrong.

There is a relic check sealed in a suspicious envelope in the
LHE drawer.

\subsection*{FAC}

Obligatory whine.

\subsection*{Pianocomm}

A member came in this afternoon and said he wanted to be a keyholder.

\subsection*{Onseck}

The onseck is rebelling, or revelling, or something like that.

\subsection*{Vox Sciurorum}

John shares cute squirrel pictures.  The Society wonders
why we devolved tails.  Perhaps to make room for a computer
jack down there, but we haven't finished evolving one.

The Skinner does not want to be liquefied by a relic.

Margaret makes squirrel noises.

\goto{Old Business}

ALGOL
\goto{New Business}

Last Saturday the Japanimation society had a meeting.
A strange person came to see if they really existed
because he thought they were only a practical joke
which he didn't understand.

Margaret wonders: Are squirrels a shared delusion?

\goto{Future Business}

There will be a time warp, and Margaret will dance in her underwear.

Margaret makes more squirrel noises, but does not dance.

Motion to approve the bananas as being minutes-flavored.
Chickens \hbox{3-3-6+Spehn}.

In the future, Margaret will be sad because her story will
be rejected, and she will have to dance in her underwear
to cheer herself up.

Miller motion.  Chickens \hbox{5-4-6+Spehn}.

Would ending the universe end the meeting too?
Discussion of Cities in Flight, which continues
past the end of the universe.

Margaret reveals why she always wears a hat: she
has a Sacred and/or Unholy artifact on her head.

Second Miller Motion.  Passes \hbox{10-0-4+Spehn}.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
