\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/1/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 1, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read and showed---they are in comic book form.

The Onseck is commended for an incredibly accurate reading of last
week's minutes, even though he doesn't know it.  12-1-$\pi$\ps.

\goto{Committee Reports}
\subsection*{Jourcomm}
Everything but the art is done.  Probably mid-April.

\subsection*{$\hbar$comm}
There's a block party next week.  3-5 next Friday, leading right into
the meeting.

\subsection*{MobComm}
A box from SFBC arrived with hardcovers.

\subsection*{Onseck}
6 hours until the stupid holiday is over.

\goto{Old Business}
March Ended.  So did winter.  Eight years ago, my life was saved by a
blizzard.

A police officer in Connecticut has been arrested for flashing
passers-by with a plush toy banana 11-2-2\ps.  Connecticut is
condemned for decadence.

ALGOL
\goto{New Business}
Somebody wants a blit out of a French encyclopedia we have.  Can
somebody help find the right bit?

We've postered a bunch.

Memberships bought now will expire \emph{next} summer, making this an
excellent deal.

More books have been sent to Niagaracomm, and it appears to speed up
some Hasslecomm stuff.

\goto{Future Business}
There's a picnic coming.  Also CPW.  Cleverly, these don't line up.

This card JFC has reads ``burnup/gm.  preparation for the outer ring
begins.''  It then contains some FORTRAN.

Yelena will be boxing up some C/Ps to remove triples.

There's an ASA GBM coming up.  Maybe we can find out whether they're
dropping the re-rooming there.  Much discussion of social engineering
the ASA.

The GBM is declared bananas. 25 or so-1-4\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
