\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 27, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Minutes are condemned for containing squirrels 11-4-0+Spehn.

\goto{Committee Reports}
\subsection*{Pseudo-MobComm}
MobComm is trading books back at Pandemonium for credit, which appears
to be better than selling on EBay.

\subsection*{JourComm}
``They're here!''  The latest (no pun intended) issue of {\em Twilight Zine}
 will be printed (Kat believes) before next Friday.  John will proofread.

\subsection*{Aloha Lenscomm}
We have a picture of the Onseck and a reinflated picture of a keyholder
who was apparently converted to a line drawing some time last summer.

\subsection*{PianoComm}
Karl Ramm came back and asked to be a 'prentice.

Discussion of the crappiness of Robert Jordan books ensues (\emph{physical}
crappiness...  we make no claims about their literary qualities).
Motion to condemn the Perfect Binding passes 13-0-1+Spehn.  "But I like
oxymorons!"

\goto{Old Business}

Term happened.  There are still three undergrads here, but there would
have only been one if this meeting had happened next week.  (The Onseck
would like a few more verb tenses, please...)

"Funny you should mention chicken zombies..."

ALGOL
\goto{New Business}

We have sent an advance scout to southern Ohio, who will report back
to us on the state of Science Fiction there.

The Society decides that Health food is the healthy food that no one
likes.

It seems the squirrel summer mating season has begun.

\goto{Future Business}

{\em Serenity} is {\bf really} good.  Go see it.  ({\em Onseck's note:
Go watch {\em Firefly} and {\bf then} go see {\em Serenity}}.)

The summer schedule has been mostly prototyped and should be posted
tomorrow.

"He can't be PentiumComm!  He's got a Mac!"

Matrix vote{\tt ^H^H^H^H^H^H}Not a matrix vote

Something something banana something (11-3-1+Spehn)\\
Motion to acquire the Society a waterjet so it can cut through the
walls of the Library and annex adjoining rooms (8-1-2+Spehn)\\
Motion to have a matrix vote (4-15-5+Spehn)\\

Which fails with a determinant of -305.  Motion to upgrade 
PentiumComm's math coprocessor to improve computation speed (hey!)
and feed him a banana passes \$SOMETHING-\$SOMETHING_ELSE-\$ANOTHER_
THING_THE_ONSECK_CANT_REMEMBER+Spehn.  (Chomp.)
\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
