\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 11/04/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 4, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motions: to commend the minutes for existing simultaneously in several timelines
to define and acquire a 150-point GURPS character posessing the requisite Snatcher Advantage
to acquire helmets and nasal bandages for those who might trip while watching {\em Tron}.
anti-banana

Matrix motion chickens by Skinnerial decree.

\goto{Committee Reports}
\subsection*{PianoComm}
John M. started doing box inventory on the Cavin donation and checking for quality..

\subsection*{War Council}
The ASA said that a lot of groups didn't fill out their reallocation requests, so we may get a lot
of their space.

Motion to declare Margaret (who won the costume contest) MITSFS's Commisar-General passes by 
Skinnerial decree.  She won a 300-point Warhammer 40k army; unfortunately, about half of it is
on back order.  Once it is assembled, she wants to use it to take over the UA and the ASA.

\subsection*{JourComm}
Kat's wrists are hurting less, so the TZ Frame to \LaTeX conversion may finally finish.
"Can't you remote-control Brian?"  
BTS: "This was tried.  Her typist was fired."

Motion to introduce "woof" to unite the divers threads in our warp passes.

MHG: "Can I introduce an anti-motion to destroy the universe, and thus all traces that that motion
ever existed?"
ED: "That would be a small price to pay..."

Motion to set fire to the loom a la David Brin chickens.

\subsection*{LHE}

\subsection*{FAC}

\subsection*{MobComm}

\subsection*{Onseck}
The Onseck ran off about 175 copies of the membership form today, so we should be good until
we find ourselves 175 new members (or until 175 of our current members fill up their current sheets.

\subsection*{Mumbling about Rats (Vox Sciurorum)}

\goto{Old Business}

ALGOL
\goto{New Business}

\goto{Future Business}
In the future, Kat and Ed's account are going away soon.  The Skinner will talk to Prof. Jenkins
about getting their accounts sponsored.

"What is Panhel?"
MHG: "It's a big block of wasted space filled with a big block of wasted space people."

Motion to replace the contents of the Panhel office with a single banana passes 20-1-5\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1730 ("eighteen negative thirty") SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
