\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 29, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion 'Chickoo!' passes by Skinnerial decree.

\goto{Committee Reports}
\subsection*{FrustratedAuthorComm}
Margaret: "I'll be getting my book back in a couple weeks.  He said he's putting it in the mail on Tuesday."\\
John: "I'll start mailing large envelopes to Margaret."

\subsection*{AtlasComm}

Former MITSFS member Diann Smothers is competing in the Strongwoman nationals in St. Louis.

\subsection*{BluebellComm}

The aforementioned Harry Potter books have been covered and one of them has been checked out.

Usual motion.

\goto{Old Business}

"Every time I learn the word 'squirrel' in a new language, it turns up a universe of Google image searches."

John reveals that the root of the German word for squirrel is a homonym of the German word for croissant.

ALGOL
\goto{New Business}

\goto{Future Business}

Move to have Margaret draw up a new copy of _The Bananas of Gor_ in glorious full color.  Passes 9-0-7+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
