\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 4/15/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, April 15, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are condemned as being, traditionally, in the traditions of the
society, 15-3-3\ps.

\goto{Committee Reports}
\subsection*{War Council}

\subsection*{Jourcomm}
Pictures are in the TZ folder!  (Only they aren't)

Ready-to-print draft in about a week.

\subsection*{Picniccomm}
Invitation list is about funny, now to get a sufficiently ready invitation.

``Markov chain on previous invitations'' gets a bunch of laughter, but
no seconds.  We will eat the food first, and then walk around last.

\subsection*{Mumbling about Rats (Vox Scirorum)}
They are not rats, and so says the visual effects director of
\emph{Charlie}, regarding being locked in a room with hundreds of them.
Do we want to be eaten by squirrels first or last?

\goto{Old Business}
There are ancient notes about picnics.  Like ``Cape Cod is over there''.
Satellite pictures will be great for figuring out where we should turn.

Matriz votes are abolished for this meeting 11-5-4 plus a Slinky\ps.

ALGOL\footnote{Usual Pigeonhole Motion}
\goto{New Business}
CCCth party, Saturday night, Talbot lounge.

``Walk like a penguin'' exhibit at the Museum of Science this
weekend.  They will be in trees last.

The motion to Albanian everyone but the Skinner chickens 8-7-8\ps.
Motion to Albanian Jamie;
The penguins are to be sent to the land of the Eagles;
Motion to inductively extend the matrix vote principle here
demonstrated.  They all with a determinant of 243.

The Kipp catalog came in the mail with penguins.  You can get them in
cases of 32 dozen.  Three hundred eighty four plush penguins.

We need more space for banana colored penguins.  We should decapitate
one banana-colored penguin per day until they relent. This passes 33-1-2\ps.

\goto{Future Business}

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
