\documentclass[10pt]{article}
\usepackage{xspace}
\usepackage{ulem}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 1, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
The Great Battle of the Minutes: Recorded Here 9/155/005/M41

The Library is an Ancient place, a vast collection of knowledge dating back Millennia, unrivaled 
by any place within the world of Mankind. Through the years, a handful of the Emperor's finest have 
been assigned to preserve this sacred treasury, and guard it against all forces. They have seen the 
Library safely through floods, through attacks by heretics, and even through the collapse of space 
itself, though a feud over a simple clerical matter almost brought this mighty Institution to its 
knees.

It was an unbearably hot day on the planet Terra, birthplace of Man and home of the Great Emperor. 
Several of the Library's Finest had assembled as they had done countless times before, to attend to 
matters regarding the collection and its continued safety. Various bits of tech left behind by the 
Adepts after the most recent flood still littered the floor, a disaster which had claimed so much 
else yet left the Library miraculously intact (Emperor Bless). As the time approached to start the 
meeting, many in the group became anxious. The Scribe, Kevin Riggle, was strangely absent. 

But a meeting cannot start without a Scribe!

Those in attendance wondered what had happened to him, though they knew the meeting had to commence 
regardless, for the fate of the entire universe could be at stake. Taking this decision to heart, 
the Most Holy And Exalted Lord Of All Things, Andrew Clough, decided he had to appoint a 
replacement.

His eyes slowly roved the room, settling on a small, squirrelly woman who wore the uniform of an 
Imperial Commissar--She Who Brings Destruction, Margaret Gentile.

``No.'' she said with a sneer. Realizing The Most Holy And Exalted Lord Of All Things meant 
business, she offered an alternative suggestion. ``Can't I just appoint a lesser minion to do 
it?'' She glanced helpfully in the direction of Justin, a Witch Hunter and former Apprentice. 

Murmurs of protest ebbed through the gathered masses. ``But Margaret has better handwriting,'' they said.

``No I don't,'' she replied. ``I don't want to do it. It requires opening a path through the warp 
and reaching through the very fabric of space and time.  Do you have any idea what kinds of 
headaches that causes?'' Her hand was already moving towards the chainsword resting beside her. In 
a flash, she seized it and leapt to her feet, pointing it at Justin, who seemed curiously unphased.

``No!'' she screamed. ``You're gonna do it! You're the Witch Hunter!''

She heard a collective round of sniggering in the crowd around her.  That, combined with the former 
Apprentice's apparent calm made her suspect that they knew something she didn't.

Justin smirked. ``Heh.'' 

An Eviscerator appeared in his hands, whirring softly, menacingly, in the humid air.

Margaret's shoulders slumped. ``Damnit...'' She sheathed the chainsword and returned to her seat.
``Somebody give me some paper...''

 The Most Holy And Exalted Lord Of All Things smiled. ``Order has been restored.''  He raised the 
sacred gavel into the air---a symbol of the Technological Might of Man---and struck the block. 

That sound signaled the perpetuation of order for years to come.

\bing

MITSFS meeting called to order, 1700 SST. Andrew Clough, President and Skinner presiding; Margaret 
Gentile, Reluctant and Over-Imaginative Pseudo-Onseck, recording.

Minutes read.

Motion to commend the minutes for containing both ``anti-pope'' and ``of doom'' passes lots to none 
to a few \ps.

\goto{\sout{Old Business}}

\vskip 12pt \section*{{\em{Committee Reports}}}

Stop making the pseudo-Onseck cross things out!

Minutes in the 70's consisted of space aliens.  Ours have ninja battles. Guess which is cooler.

The Pseudo-Onseck is NOT writing the minutes in Cuneiform!

\subsection*{ShurikenComm}
Katanas are popular in gang killings in Peru.
The Peruvian Ninjas are spreading!
Ninjas make the best pizza delivery boys.

\subsection*{FAC}
*whine*
Writing books is like making sausages, blah, blah, blah...

Discussion of Italian Rednecks...

\goto{Old Business}

``Back when I was young, we read books uphill both ways, and there was none of these bookmarks, 
either...''\\
``And we had to read in 6pt type!''\\
``You had type?''\\
``You had books?''\\
``We had to go out and find an author and spill their entrails and read them!''

Motion to end this thread for the sake of sanity passes 5-0-1\ps.

Reading of the MITSFS parody of ``The Raven.''  It is 1337, w00t.  The pseudo-Onseck gives it 500 
KOhm style points.

Chickoo.

Usual motion and all that stuff.

\goto{New Business}

(Things get weirder from here... -ed.)

``I wounded an innocent bystander!''

``The Skinner has no porn at all, porn at all, porn at all...''

Hired Ninja Monkey Homemade Star Trek has:
\begin{itemize}
\item Lousy Acting
\item Silly Plots
\item Better special effects than the original Star Trek
\end{itemize}

<filler>
chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo 
chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo 
chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo 
chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo chickoo
</filler>

The Skinner watches reality TV! *gasp*

Shelves were rearranged in the non-circ room.
Ref/R-P are now where the LP's were, near the circ room door.
Comics & such are now where the LP's were.
LP's are now where the comics & such were, next to the magazines.

\subsection{Future Business}

``What does your brain have to do with this?''

SPOING! passes 8-1-3\ps.
 
Chickoo fails 0-1-0\ps.  (Vice: ``Grrr... Foiled again.'')

``The Skinner has no tail at all, tail at all...'' (repeat) ``...just a bloody stump.''

\vspace{12pt}

\noindent
Meeting adjourned, 1730 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Margaret Gentile, Pseudo-Onseck}

\end{document}
