\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/13/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society 

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes 

Friday, May 13, 2005

\end{center}
 
\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, the shiny new-in-box President and
Skinner, presiding; Margaret Gentile, the squirrely Pseudo-Onseck, recording.

Minutes read.

Move to commend pseudo-onseck for choosing minutes from golden age of society. Motion swarmed and kills us all 4-3-7 +Spehn.

There was another motion in there somewhere but I'm not good at this.

\goto{Committee Reports}

Picniccomm: we had a picnic but it rained, but a lot of people showed up and all was good.

Firefly might come back, says Justin.

The onseck will not write the minutes in cuneiform.

Jamie: "I see someday we will take 4 wheels and attach them to a board and we'll have magical transportation."

If it's not in the minutes, they'll be none the wiser.

The squirrel Illuminati will keep the TZ from getting published.

How do you say once every five years? Quintennial? WTF huh?

Pseudo-analogcomm demands you submit! (Your hours, that is.)

We'll switch to 1700 meetings after commencement.

MIT likes forms.

Vox Sciorrum: John read a book about tree squirrels. They paid grad students to go out and feed tree squirrels. Male squirrels will also chase anything moving and vaguely squirrel-like thinking it to be a female squirrel.

\goto{Old Business}

According to documentary evidence, the 70s happened.

Me: "Am I just allowed to make stuff up?"

Ed: "Yes."

Me: "Heh..."

YOU'RE ALL DOOMED!

\goto{Time Warp to Committee Reports}

Boston Japanimation Society held a panel, one person (Y) showed up. Anime was discussed. I'm so confused now.

\goto{Time Warp back to Old Business}

Carthage must fall.

Usual motion. \bing

Thirdspace still sucks...

The library is currently filled with muffins. I don't know why.

Everyone is talking about B5. I just sit here.

Muffins...

Long discussions of confusing continuity.

Something predates ringworld... blah... blah... new ringworld... blah blah...

I'm not getting any comedy nuggets out of this, so I'm going to make something up.

(bullshit)

The meeting was a normal one, at least normal so far as meetings go. A little on the quiet side, perhaps, so I decided to make things more interesting. I recently "obtained" a vial from the nanomaterials research lab (by completely legal means, of course). It was unlabeled save for a small tag that read "nanosquirrels"...

(/bullshit)

Move to genetically engineer pak the size of watchmakers to be called pocket protectors. Motion passes 11-4-6 +Spehn.

Jamie: "I know kung fu and 7 other Chinese words."

\bing Sucks.

Better \bing

\goto{New Business}

Something funny happened, I missed it.

Miller motion. Fails 4-10-5 +Spehn.

"About 10 years ago I stopped having those dreams..."

Jamie presents a detailed account of missing a test because of some random jerk asking too many questions.

If the class is bad enough, then you don't lose much by missing it.

Chickoo. Seconded, but nothing happened.

Hitchhikers movie discussed. Overall positive response; the skinner declares it "acceptable" and there was much rejoicing. I haven't seen it yet *sniff*.

Discussions of mineral rights, aka the rights that let you mine the land.

\goto{Future Business}

Move to sell our banana mineral rights to Lobdell to raise more money for space. Passes lots-0-not enough +Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, some time (18-19) SST. A collective "what?"

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Margaret Gentile, Pseudo-Onseck}

\end{document}
