\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/24/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 24, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Margaret Gentile, Vice and
Pseudo-Skinner, presiding; Edward Keyes, Pseudo-Onseck, recording.

Minutes read by the other Pseudo-Onseck, Armenard, since he's at the
computer already.

Motion to regard the minutes as foiled again.  Passes \hbox{10-0-1+Spehn}.

Motion to foil the Vice again and again and again.  Failed by
Pseudo-Skinnerial decree.

\goto{Committee Reports}

\subsection*{Mobcomm}

Many books were ordered, and soon they will be here.  ROAR!

\subsection*{Minicult}

Something has gnawed a green pine cone off of a tree.  Perhaps even
a squirrel...

Motion to coat squirrels in pine pitch and light them on fire.  Friendly
amendment ``not in the Library'' is accepted.  Fails something-something-no
chickens+Spehn.

\subsection*{Hydrocomm / Algaecomm}

There is a puddle in the back of the Reserve Room, coming from our air
conditioners.  It has been reported already.

We could build a trebuchet to launch flaming squirrels at our enemies.
The {\em Tech} is suggested as being suitably flammable, but destroying
the IFC and taking over their space is also nice.

Motion that we should launch at the Stata Center on general principles
of aesthetics.  Passes \hbox{7-1-1+Spehn}.

\subsection*{Frustratedauthorcomm}

My book is in Canada now, hopefully being edited.  ``Blame Canada!
Blame Canada!''

\subsection*{Pseudo-Jourcomm}

[KHA] ``It's not me anymore, Andrew took it away.''

\subsection*{hBarcomm}

Half of the Infinite Corridor board is waiting for {\em TZ} stuff.

\goto{Old Business}

The Library is still overflowing.  Unfortunately most of us have a
gender problem to be able to infiltrate Panhel.

[MHG] ``Annex, not infiltrate!''

Margaret enjoys her vast cosmic power.  She sent the email purporting
to be from ALC in secret, to make people think the Skinner would be
absent.  Oh, wait, that was supposed to be a secret.

[MHG] ``Don't I have underlings?!''

Usual stuff.  Slightly unusual.  ALGOL
\goto{New Business}

Margaret dances the jig of infinite power.

There is a new beepy sound coming from outside, shortly followed by a
futuristic space sound from within.

Motion to require all crickets to turn off their cellphones while in
the Library.  Passes \hbox{11-0-0+Spehn}.

[MHG] ``I was destined to rule!''

Motion to let Margaret be the evil overlord until we find a banana that
can do a better job.  Passes \hbox{10-4-0+Spehn}.

\vspace{12pt}

\noindent
Meeting adjourned, 1630 SST, despite the Pseudo-Skinner not really
noticing what just happened at first.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Edward Keyes, Pseudo-Onseck}

\end{document}
