\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, December 2, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion ``chickoo'' passes 14-0-6\ps.

\goto{Committee Reports}
\subsection*{PseudoMobComm}
The Ingram library thing has been faxed in, so hopefully they're working on it.

\subsection*{PantherComm}
All the old PantherComm hardbacks have been processed, so they're probably HassleCommable now.

\subsection*{FrustratedAuthorComm}
[obligatory whine]

\subsection*{PsudoPlantComm}
According to Facilities, the light which is out in the circ room has been fixed.  \emph{In reality,}
this isn't true.  A new work order has been opened, and a snarky note has been left on the 
offending fixture.

\subsection*{BluebellComm}
John has covered a bunch of books, which is still a fraction of the 6 (and counting) boxes left to
do.  We need more material to cover books with---Andrew, Margaret, John, and Kevin will deal.

\subsection*{Onseck}
Mail was processed yesterday!  Check whatever venues by which you tend to receive mail.

\subsection*{Mumbling about Rats (Vox Sciurorum)}
John would like to replace the word ``rabid'' in the Skinner song, since he recently saw a squirrel
with ``No tail at all, tail at all /\ Just a bloody stump."  (``But it was still sniffing at the
female squirrels, so it had some energy left.'')

\goto{Old Business}

MHG: ``Back in the day...''

People talk about the new Harry Potter movie.

ALC: ``Usual motion.  Usual vote, usual result...''\\
MHG: ``What about the usual debate?''\\
ALC: ``Didn't happen.''

ALGOL
\goto{New Business}

Someone mailed MITSFS asking for movie ideas.  We're not sure whether that's a good idea or not.

``You can't make blockbusters out of Heinlein books---not enough special effects.''

We have the new Robert Jordan book and the new George R. R. Martin books in circulating.
``...in which he introduces new characters, which he then kills off in new and surprising ways.''

MHG: ``That's not a book; that's an end-table!''

Malcolm: ``The first three words of \emph{A Dance with Dragons} should be, `Ouch, my feet!'''

People discuss media tie-in books.

\goto{Future Business}

ALC: ``In the future, there will be robots.''\\
MHG: ``In the future, someone will buy one of my stories.''\\
YT: ``In the future, will the ASA give us more space?''\\
ED: ``We should find out within a couple weeks.''

In the future, there will be copies of the \emph{Twilight Zine}!  ``We've heard that before.''
It went to the printer earlier this week!

People mock Andrew's shirt.  ``I don't even know what I'm pointing and laughing about.''

Someone walks in.  The Society decides, based on available evidence, that she is in fact alive 
and breathing.

The Onseck notices that there is \emph{more} mail.  ``Do people do this just to torment me?''

Andrea (``Ande'') is starting a brief 3 week film series, starting December 5, at 6:30 PM in 
Christ Church in Cambridge (0 Garden St.), to watch various film adaptations of \emph{A Christmas
Carol}.   She's read the Dickens book practically every Christmas for a quarter-century.

``Banana motion'' passes 11-5-9\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
