\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 9, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion to accept the minutes as read with squirrels passes 16-2-3+Spehn.

\goto{Committee Reports}
\subsection*{MobComm}
We need to find a replacement for the Space-Crime Continuum.  Also, there is a bill from
the SFBC that Andrew will deal with.

\subsection*{FrustratedAuthorComm}
FrustratedAuthorComm got more rejection letters.  \emph{sniffle}  She should spam more people.

\subsection*{Onseck}
The Onseck performed much-overdue processing of mail.  There are now a lot of new magazines on
the shelves, and a lot of mail the Onseck doesn't know how to deal with.  There are also some
"please renew our magazine" forms.  Unfortunately, the Onseck needs textbooks and food and 
doesn't quite have enough money for that \emph{and} MITSFS's subscriptions.  People are found to
provide credit.  Also, there is much mail for the LHE who is... in Ohio.  

Margaret: "I don't do anything."

Andrew makes plans to train Margaret as acting LHE.

\subsection*{Mumbling about Rats (Vox Sciurorum)}
John has a picture of a 4-week-old happy lucky squirrel (happy and lucky for being stored 
in an... interesting place).

\goto{Old Business}
Malcolm: "Does the anti-hazing policy mean that we can't run a steam vaporizer in the Library?"\\
Margaret: "Books react to humidity by forming a protective layer of fur."

Usual motion.

ALGOL
\goto{New Business}
In our mailbox today was an envelope of Analogs with a note on it reading "Do Not Divert to MITSFS"
to replace the magazines which had been diverted to MITSFS by the MIT mail room.  John returned
them to the place they \emph{should} have been directed.

We need to double-check that the second half of our Vance Integral Edition donation exists.
Margaret will Do Something About It (for values of Do Something which involve groveling through
e-mail and visiting the MIT library in question).

In scary random weirdshit news: someone has recreated the taste of human flesh on a tofu base and
called it HuFu.  Has Arthur C. Clarke been notified?

Motion to re-educate the rabbit population to eat bananas instead of their own excrement so
we can end the meeting passes 12-1-8+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
