\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 3, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

"What he said." Motion chickens 7-3-14+Spehn

\goto{Committee Reports}
\subsection*{Pseudo-Jourcomm}
"Look!"  Supposedly TZ is coming {\em Really Soon Now} -- John turned the
proofreading comments in to Kat on Wednesday, and it was going to be
printed on Thursday.  Unfortunately no issues have yet materialized in
the office.
Yevgeniya: "I might yet see another TZ in my lifetime!"

Motion is made to nominate Solly, Aaron and Yevgeniya's son, to proofread 
the next TZ.  (As he will be of keyholding age in approximately 18 years,
he is more than qualified.)  Fails for lack of a second.

Motion is made to nominate Solly the next JourComm.  Motion 
chickens 6-7-8+Spehn.

\subsection*{Pseudo-MobComm}
Apparently the Space-Crime Continuum is about to burst from the 
quantity of books we have purchased but not yet paid for or picked up.
"The check is in the system.  Is the system in the mail?"

\subsection*{Pseudo-FweekComm}
Are we prepared for the incoming freshmen and/or the Freshman Year Summer
Mailing?  No one knows.

\subsection*{Mumbling about Rats (Vox Sciurorum)}
Motion is made to commend the movie {\em The Hitchhiker's Guide to the Galaxy}
for having a {\em Heart of Gold} which contains mice, unlike the TV version,
which did not.  Passes 12-0-9+Spehn.

\goto{Old Business}

There were lots of old people here today.

There is discussion of an anime series [name removed to prevent propagating
the meme any further] in which there is an alien race invading Earth which
can't be fought by the regular armed forces.  This is because, were the 
government to do such a thing, there would be no popular support for the war 
because the aliens are simply too cute for words.  The solution, of course,
is to draft 8-year-old children.

The Skinner has been duly graduated, and is coming back for more.  He will
soon begin to these.  

Andrew: "Isn't that a great word, 'thesing'?"  
Justin: "Not nearly as good a word as 'napping.'"

ALGOL
\goto{New Business}

There is some more oohing and aahing over Solly.

As promised, there is only one undergraduate here today.

\goto{Future Business}


Motion is made to lobby the International Standards Organization to define
the banana as the standard unit of curvature.
Motion chickens, 4-0-10+Spehn.

It is revealed that in the new _Howl's Moving Castle_ movie from Hayao
Miyazaki, Sophie does not talk to hats.

Solly is declared to be an honorary banana by Skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 18-negative-27 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
