\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, November 11, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion \emph{chickoo} passes 13-3-4\ps.

\goto{Committee Reports}
\subsection*{FrustratedAuthorComm}
She got another rejection letter.  There's still one outstanding rejection 
letter{\tt ^H^H^H^H^H^H}manuscript at a particular magazine.  

``When they say six months, they mean six months.  Then again, they're Canadian, so they're a
bit sloo, eh?''

\subsection*{War Council}
The ASA hasn't taken Andrew up on his offer to visit and see our space crunch.  ``They'll come just
as soon as HassleComm has finally taken all the excess books off the shelves.''

\subsection*{MobComm}
We have books from Amazon coming in, and the Ingram thing is getting taken care of, so we should
have books from them soon.

``Funny, for some reason I was thinking of Ingram as a manufacturer of automatic weapons.'' \\
``No... then again, we could make a non-lethal weapon to fire Robert Jordan books.'' \\
``That wouldn't be non-lethal, Margaret...  'EAT PULPY PAPER DEATH \emph{<CHUG> <CHUG> <CHUG> <CHUG> <CHUG>}...'''

\subsection*{BlueShinyComm}
There are freshmen!  Coming to meetings!

\subsection*{HassleComm}
HassleComm processed six boxes of paperback books yesterday in the new shiny Jamie system, so 
there is now six boxes worth of space on the shelves.  ``Enjoy it while it lasts!''

\subsection*{Mumbling about Rats (Vox Sciurorum$_3$)}
``If you ever wondered if squirrels have tongues, I have photographic proof.''

\goto{Old Business}
\emph{Star Wars: The Musical} is coming out ``again'' next week.  People say it will be good.
``It has to be good -- it made Slashdot!''

ALGOL

Usual \emph{&c.}

\goto{New Business}
Motions to: dispose of Margaret's body properly (5-5-1\ps)
dispose of Margaret's body improperly (10-9-0\ps)
have a matrix vote (5-8-14\ps)

MHG: ``The dead can still vote!''

Determinant is -15; all motions fail.

Malcolm is sent to Albania by Skinnerial decree.

\goto{Future Business}
In the future, Andrew will talk to SAFO about setting up things with Ingram.  He'll also look into
getting this year's money from the MIT Libraries.

Margaret bought 3 feet of tubing today as a part for a cooling system in a prototype for the
Soldier Design Competition.

Motion to procure 10,000 banana-colored squirrels to use as a guard force for the Library passes
14-5-4\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
