\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/04/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 4, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.  They're awful.

Matrix:\\
To thank the minutes for making MHG's head explode. 18-4-8\ps\\
To appoint a pseudo onseck next time who's a little less pseudo. 20-5-6\ps\\
To declare them Puce. 2-8-13\ps\\
Determinant is 538, they all pass.

\goto{Committee Reports}
\subsection*{War Council}
\textsf{LChocolateS} moved into 401-D, the first step of getting MITSFS moved
into the Bibliowarfare lab.

J moves that the ASA president be forced to read the Red Tape War.
Passes 23-1-3\ps.

\subsection*{LHE}

We will routinely appeal our funding allocation.  Or we could have the
Assassins use their guns\dots{} or the Croquet club use their
mallets\dots{} after all, only they have the balls to do it\dots{} JFC points
out that we could use Paige to\dots{} and is immediately Albanianed.

\subsection*{PseudoJourcomm}
The Skinner has the Frame files for TZ.

\subsection*{FAC}
Chickoo.

\subsection*{Pseudo-MobComm}
We appear to have books from the Space Crime Continuum.
Aarmenard

\subsection*{$\hbar{}$comm}
We have shiny new ( ``Where!?''---paigep ) paper for the board.

\goto{Old Business}
The movie \emph{Metropolis} is growing by minutes.  Maybe it's a
director's cut?  They added Nazis (in 1930?)  Fresh?  Frozen?  Dehydrated?

ALGOL$^2$
\goto{New Business}
The shelf crunch through McKinley(P) is relaxed by Paige having boxed
a bunch of stuff.  All books are the same size, the short ones having
been stretched and the long ones having been given to \texttt{jhawk}.

We have twenty-seven copies of Ender's game, apparently for a reading
group which turned out to be a single person so he gave us the rest.
JFC defaced them by removing the free-stickers.

There will be no fine credit for Ender's game for a little while.

Nattering happens here.  Mostly in Albanian, so it's
incomprehensible.

Ender's game may be usable as currency in the future, like Om (Small
Gods), Hitchhiker's, or Sparta with its ten-pound iron bricks.

Jamie suggests reopening the Spartan legal system to conquer the
world, and it passes 20-6-5\ps.

\goto{Future Business}
ALC will be here next year after all!  We'll probably make him
Skinner, poor bastard.

ChrisK lost \emph{Fall Revolutions} in the reserve room, it may have
been shelved, and we're not sure what happened it.  Maybe it achieved
sentience.  SkyNet, here we come.

Miller motion\dots{}ignored for lack of a second.

Miller motion\dots{} fails 13-14-5\ps.

The \textsc{Tyrannical Iron Fist} will have being going to have gone
up.  Now it is.

A motion to nuke Albania, unleashing the fleet of Burmajets and saving
more Eagles for us passes 33-4-0\ps.

Paige is dispatched on a fact-finding mission to Albania and see if
she comes back blue and shiny, 25-0-1\ps.

Miller motion passes 17-0-4\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1805 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
