\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, July 22, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, 
Pseudo-Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion to approve the minutes as scarily accurate passes >-<-<<+Spehn

\goto{Committee Reports}
\subsection*{War Council}

\subsection*{MobComm}
The new Harry Potter book has arrived (twice)!  (Once courtesy of MobComm, and once courtesy of the Skinner,
so it can go on circulation immediately.

We got a [DELETED].

\subsection*{Pseudo-JourComm}
TZ is apparently \emph{moments away} from publication!  If only the corrections file could be found.

\subsection*{LHE}

\subsection*{MagnificentPrismaticComm}
Paul Allen bought a lot of copies of the Jack Vance Integral Edition, and so our (second) copy is apparently
wending its way towards us.

\subsection*{FAC}

\subsection*{Pseudo-BarComm}
The schedule on the bulletin board in the Infinite is out of date.  Kat put up some stuff, because Margaret didn't.

\goto{Old Business}
An old box of magazines got counted, relabeled, and redirected to BondageComm.

ALGOL
\goto{New Business}
There's a new flash game making the rounds of the Web, which involves taking an undirected graph and making it not overlap.

The Sci-Fi Channel will start airing episodes of Firefly tonight in the correct order, ending at approximately at
the same time as Serenity is being released.

\goto{Future Business}

We will have an ad in \emph{HowToGAMIT}!  Kat is dealing with this.

We don't know if there is going to be an inventory or not this summer.  This should be decided.

"When you have Celestial Duct Tape..."  "Everything starts to look like a duct?"

Motion to acquire, via APO, a sharkbanana passes 1-0-NULL+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
