\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 09/02/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 2, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1700 SST, Andrew Clough, 
Skinner, presiding; John Carr,  Pseudo-Onseck, recording.

Minutes read.

The Skinner is impressed that the onseck actually put in 18:-30.
Motion passes by Skinnerial decree.

\goto{Committee Reports}
\subsection*{Phonecomm}
Somebody calls about a donation from Inman Square.

\subsection*{FWeekcomm}
Ed pops in briefly.  He is handling the midway because Kat is on a boat.
He seems harried.  Is anybody else helping?  We don't know.  Margaret is
not here.  Ed returns to say Kevin and Margaret are helping.

\subsection*{Pseudo-Surgeon}
We now have a quarantine for sick books.  Or a triage chamber,
because sick books don't get better.  Unless you soak them in
Tilex.  Or irradiate them.  We could use the reactor to kill
the mold.  It's a neutron source so the books could be read
in the dark later.  Electron beams are better.


\subsection*{Pseudo-Pianocomm}
A person is trying to be a prentice but the Star Chamber is not
very responsive.  Brian is now Pianocomm.

\subsection*{War Council}

There is a brief lament over the space we almost got,
followed by a longer one later in the meeting, somewhere
in Future Business.   We should form a spinoff group to
get its own space.  The Fantasy Appreciation Society?
The Paper Preservation Association?

Where does the Tech have their newspaper printed?

Can we have an alumnus donate space?  Endow a MITSFS wing?

\subsection*{MobComm}
SCC is closed so we need to divert the books in the ZGT that
are waiting to be returned to them.  We also need to replace SCC.
Pandemonium?
NEMBF?

\subsection*{LHE}
Do we have an LHE?  Andrew was going to talk to Kevin about that.
Would we have an Onseck?  That's a problem.

%\subsection*{Onseck}

\subsection*{Niagaracomm}

350 books are over at APO book exchange.  Better World Books
will be taking our hardbacks on consignment.  We get 20\% of
their revenue from our books and a literacy charity gets 15\%.
We need to discuss office organization with LCS.

A brief digression to cat mysteries and efforts to sell them.
A further digression to eBay and the difficulties of selling
there.  Chris on eBay: ``If you want to part a fool from his
money, you have to deal with the fool.''

We can't sell at Arisia because Ellen is staff (Filk) and
won't have time.  It's hard to sell to used book stores.
The Wellesley Booksmith is starting up a used book section;
we should talk to them.  Maybe they want cat mysteries?

Part of our surplus comes from old MITSFS members who are
moving into smaller spaces or dying (i.e. moving into
{\em much} smaller spaces).

Ellen whips out a handful of books.

\subsection*{Vox Sciurorum}
Update.  John's fingers were gently nibbled by his squirrel.

\goto{Old Business}


ALGOL
\goto{New Business}

There is a movie currently in the throes of opening made out of the Bay
Bradbury short story: ``The Sound of Thunder.''  Discussion of Bradbury
and ``Golden Apples of the Sun'' which is good despite the setting of the
thermostat to -1000 degrees~F to keep the spaceship cool.  Chris defines
negative temperature.

A freshman walks in!  Then he leaves.

Andrew is turning into an absent-minded professor even though he doesn't
have a doctorate.  An absent-minded grad student is the larval stage of
an absent-minded professor.  The non-absent-minded ones go into industry
and do stuff.  If they remember to go into industry.  If they don't, they
must be absent minded and become professors.

Everybody waves to Famous Author Geoffrey Landis, who rejoined the
Society this week.  (He is a visiting professor at MIT.)

The {\it Nature} web site has an article about a bacterium that
sounds just like the one in Neal Stephenson's {\it Zodiac}.
It turns the covalently-bonded chlorine in perchlorate into
ionic chloride.

\goto{Future Business}

We haven't had an inventory of the library in the past two years.
On the 17th we will gather as many people as we can and attempt
to inventory the library, even if Jamie isn't there.  Brian
may help; the Skinner is urged to formally nominate him now
as pseudo-Dexmistress to run inventory because it takes
preparation to run inventory.

Ed says two weeks notice is not enough and Andrew should
appoint people now and wait for them to make a plan.
October 1st?  John remarks, {\em October the First is Too Late}
but has to identify the source of the phrase (a Fred Hoyle novel).
Can we hold a meeting where people speak entirely in book titles?

Discussion moves on to Buffy and Dante and who gets chewed on by
whom in Dante's hell.  Y's bad pun for this week is a quotation
from {\it Inferno} (``what in hell's eating you?'').

Do we have a space management plan?  No.  We need one.  A real
one, not a hypothetical one.

The Skinner's suggestion that somebody make a banana motion is
approved \hbox{10-1-8+Spehn}.

\vspace{12pt}

\noindent
Meeting adjourned, 17:$\infty$ SST.
% 19-54 SST

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
