\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 12, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, president and
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Margaret: "I just did what the Internet told me to do!"\\
John: "You need to visit my Web site after the meeting."

Motion to demand a recount passes 6-4-1+Spehn.

\goto{Committee Reports}
\subsection*{WhooshComm}
The Space Shuttle \emph{Discovery} is back on the ground, and the new improved \emph{Mars Observer}
is in space!

\subsection*{Pseudo-MobComm}
We have a pile of books to be returned to the Space-Crime Continuum which will probably not make it there before they close.

\subsection*{Pseudo-PrePreFWeekComm}
We had an interested rising high school senior in the Library this afternoon who read old-style (Asimov, Heinlein)
science fiction.  

\subsection*{FweekComm}
Do we have a FWeekComm?  We should, by now, since the freshmen are coming...  Andrew will look into the issue.

\subsection*{FrustratedAuthorComm}
The prodigal manuscript has returned!  Motion "Bask!" passes 10-0-2+Spehn.

\subsection*{Mumbling about Rats (Vox Sciurorum)}
John is reading a non-fiction story about squirrels with microchips, which are unfortunately not for mind control.

\goto{Old Business}
Squirrels.

The blue shiny thing is still on John's window.

"Moving day sucks."

ALGOL
\goto{New Business}
This is the time of year when squirrels' tails molt, so the squirrels have brown bodies and brilliant silver tails.

The first book of what Stephen Donaldson promises is really the last Chronicle of Thomas Covenant is available 
for reading.

"We need to develop a trebuchet specifically designed to launch Robert Jordan books."

\goto{Future Business}
"Do we have no future?"

Miller motion chickens 4-2-7+Spehn.  "The Universe shouldn't end on a Friday."

In the future, bookstores will carry Charles Stross's _The Atrocity Archives_.

In the future, giant space chickens will come down and battle the squirrel overlords, who will drive the chickens 
before them with their squirrely wrath.  Motion passes 8-3-2+Spehn.

Move to destroy the world by amassing an arsenal of bananas of mass destruction ("program-related activities") 
passes 9-0-4+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
