\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/14/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 14, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Dammit Margaret, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

They are approved as in the best megalomaniacal traditions in the society.
18-0-4\ps.
It is resolved to investigate the Onseck's past lives for auctioneers 9-6-4\ps.
And it is resolved to store his megalomania in carbonite 6-8-9\ps.
Since this is a matrix vote, they all fail.

\goto{Committee Reports}
\subsection*{LHE}
We're investigating purchase orders.  I'm sick, so forgot it was
Thursday.

\subsection*{FAC}
What the hell is this?  (Holding up some dust)

Dammit, rejected again.

\subsection*{MobComm-in-Exile}
We have magazines, including many copies of early William (F\&SF) from
early Presidents.

\subsection*{Onseck}
We have 80 shiny new membership options, at a mere eight cents per.
Freshmen are a penny stock.

\subsection*{Pseudo-Niagracomm}
We have an example contract of what relationship we could have with
some charity that would do good things with our stuff.

\subsection*{Pianocomm}
Kevin is a new prentice.  He started hasslecomm.

Paige picked up a gapdex packet.

Less things are misunderstood with Laura, so she's doing stuff.

A motion glorifying many things passes by Skinnerial decree, but the
Onseck was too distracted by the distraction of the blue shiny Rebecca
was showing off in SolidWorks.

\goto{Old Business}
Eowyn (Stephanie Fried) has been seen walking around.  Just visiting,
we think, not back permanently.

We could look for footprints of other old keyholders.

Much nattering and ranting.

ALGOL
\goto{New Business}

Margaret's sick.  Maybe if we expose the prefrosh to her, she'll end
up propagating into them and we'll have dozens of mini-Margarets.

``Clearly, the vegetarians would serve as a food source in case of
nuclear attack'' ---kevinr

``I want the universe to end before---'' ---ALC\\
``Miller motion!'' ---BTS (it fails 15--15--12\ps)\\
``Oh dear.'' ---ALC

Pictures are back from Cassini and Huygens.  And we launched a whatzit
to hit a comet, it went into safe mode, but now it's OK again.  ``Safe
mode?  Is it running Windows?  That might be the only time on record
where a Windows machine failed by not crashing.'' ---BTS

\goto{Future Business}

Much discussion of squirrels, armed squirrels, disarmed squirrels, and
then no-armed squirrels (pop!  pop!) follows.  It is resolved to
convert Paige into a banana\footnote{``not blue!  noooooo!''
  ---paige}-colored shiny squirrel 26-5-4\ps

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
