\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, September 16, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle, Onseck, recording.

Motion to accept the minutes as being fasionably obscure passes 11-1-4+Spehn.

Minutes read.

\goto{Committee Reports}
\subsection*{MuleComm}
Thanks to Margaret, books are here (the second half of the \emph{Vance Integral Edition} and a 
donation of some form or fashion)!

\subsection*{OneThousandMonkeysComm}
Should we be investing in the BANANA PROJECT?

\subsection*{GlobalHyperMegaNetComm}
Margaret went to the Mall and bought real-people clothes for the Career Fair.  And bought a hat.

"I don't think they would really like it if I came dressed as a Commissar.  Unless LucasArts 
is there."

Yelena: "Fuzzy wuzzy was a hat."

\subsection*{AlohaLensComm}
John: "Could the Star Chamber sort of vaguely get into the same place?"

\subsection*{Pseudo-MobComm}
Is MobComm still mourning the ghost of the Space-Crime Continuum?  There's a SFBC flyer on
the bulletin board which hasn't been dealt with.

\subsection*{Pseudo-JourComm}
Kat relays through Kevin (technically post-meeting):
TZ is being printed this weekend ``come hell or high water.''
John notes that we have high water.

\subsection*{Onseck}
The Onseck went to University Stationery today and ordered an address stamp and box of erasers.
They should be here next Thursday.  He also updated the listing for the Society in the MIT 
Office Directory.

\subsection*{Mumbling about Rats (Vox Sciurorum)}
John was assaulted by a squirrel this week.  He ran out of food on the windowsill this week, so
it jumped inside onto him.

John: "Judging by the force of impact, I've been feeding it too much."

\goto{Old Business}
Discussion about the movie \emph{The Terminator} and a possible black-and-white predecessor 
to it ensues.  Harlan Ellison comes up for the usual reason (hint: think lawyers).

The Onseck is commanded to put {\tt http://www.petoffice.co.jp/catprin/english/} in the minutes.

Usual motion.

ALGOL
\goto{New Business}
Margaret: "Dogs are genetically modular -- they must be made by Ikea."

The Society considers a breeding program to produce larger or smaller domestic cats.

The Society says hello to the new freshman (Sarah) by lots-0-1+Spehn.

\goto{Future Business}
In the future, \emph{Wheel of Time 11} will be released.  Andrew: "And I've preordered it!"\\
Andrew: "The \emph{next} one will be good."\\
Kevin: "That sounds like denial."

Yelena: "\emph{A Feast of Crows} is coming out!  I need to find out who George R. R. Martin will
kill in this book!"

"The characters have a half-life of three books!"  (in reference to Robert Jordan)

"A friend of mine just got laid off from Teradyne -- twenty years."\\
Andrew: "So, do you know if Teradyne is a good place to work?"

Someone online is advocating the solution Hiro Protagonist uses for housing in Neal Stephenson's 
\emph{Snow Crash} for housing survivors of Hurricane Katrina.

Margaret: "I don't \emph{want} to pet the f--king laama!"\\
"Isn't that against our sexual harassment policy?"

The Society wonders whether Pluto has been stripped of its "real planet" status yet.

Motion "Down with Pluto!" passes by Skinnerial decree.

Motion "Banana!" (13-11-2+Spehn) passes.\\
Motion "Plantain!" (2-5-5+Spehn) passes.\\
Motion for a matrix vote (4-3-14+Spehn) passes.

Andrew: "It's a matrix -- take the derivative."

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
