\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/20/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 20, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noinden
``I don't quite know how to work this thing.''

MITSFS meeting called to order, 1800 SST.
Kevin Riggle, Onseck and Pseudo-Skinner, presiding (oh where oh where has our Andrew gone, oh where oh where can he be?).
John Carr, Pseudo-Onseck, recording.

Minutes from the election meeting read.

Move to approve reading of minutes as belated.
Passes 3-0-2+Spehn.

\goto{Committee Reports}

\subsection*{Aloha Lenscomm}
has pictures

%\subsection*{War Council}

%\subsection*{LHE}

%\subsection*{FAC}

%\subsection*{MobComm}

%\subsection*{Onseck}

\subsection*{Pseudo-Jourcomm}

I don't know if it's even supposed to be Real Soon Now.

\subsection*{Vox Sciurorum}

John discusses the mating habits of the North American tree squirrel.
``At first she runs away from the male but if she successfully
escapes she stops and cries until somebody mates with her.''

Shava notes that human women act the same way.

\goto{Old Business}

``Are we there yet?'' --- Shava

It is possible that Hamlet is science fiction, since it accurately
describes the behavior of ghosts.

ALGOL
\goto{New Business}

``When is the deadline for summer hours requests.'' --- KR

``Tuesday.''

``I should put my request in.''

``{\em Last} Tuesday.''

Star Wars opens this week.  A member and non-member who left shortly
before the meeting had just come from watching it.

An alien testified to a Senate committee this week.

\goto{Future Business}

{\em War of the Worlds} will premiere this summer.  Again.
And a {\em Honeymooners} movie without any moon references.

Move to approve this picture ({\tt http://www.cgstock.com/2544})
of a squirrel eating a banana.
Passes 6-2-0+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, ``far too late given the number of people here'' 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{John Carr, Pseudo-Onseck}

\end{document}
