\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, August 19, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion to commend the minutes as being "in the lazy pile" passes 5-3-2+Spehn.

\goto{Committee Reports}
\subsection*{MobComm}
John picked up the last shipment from the Space-Crime Continuum.  

The proprieter of the Space-Crime Continuum listened to a long, picky,
complicated request for recommendations and responded to "Can you help me?" with "I could, but
the store is closing in two weeks, and I don't want to."  Motion to award hir 500 style points 
passes by something respectable.

\subsection*{FrustratedAuthorComm}
"I want to see a story with the starting line, 'And the air was thick with squirrels...'

Margaret has been painstakingly rearranging letters.

Albanian motion on Malcom passes by Skinnerial decree.

\subsection*{Mumbling about Rats (Vox Sciurorum)}
The squirrel came inside, and ate walnuts.

"It's like lemmings, but with squirrels."

\goto{Old Business}

At the moment, the Society has nearly twice as many books as all of MIT had a hundred years ago.

"We can store our books in the past!"

Usual motion.  "What about the usual debate?"

ALGOL
\goto{New Business}

"You're putting us in squirrel-debt!"

John has discovered the proper procedure for getting a squirrel to take a nut from his hand.

Holding unscheduled hours from Monday, August 29th and ending Reg Day (Tuesday, September 6) will 
gain the keyholder full TIF credit instead of half credit, so as to encourage keyholders to keep
the Library open for the incoming freshmen.

5:30 PM meetings will resume in two weeks (September 2) 

\goto{Future Business}

In the future, someone will understand what Malcom said in Albanian about the new King Kong
remake from Peter Jackson.

Motion to acquire a supply of bananas to feed to King Kong such that he stops terrorizing
Tokyo^H^H^H^HManhattan and people stop making movies about him (and so we can train him to
smash Panhel so we can take their space and turn it to our nefarious purposes) passes 15-1-9+spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 18 negative 31 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
