\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/11/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 11, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Jamie moves to will have been going to provided new tenses for Brian.
This passes 17-4-6\ps.

\goto{Committee Reports}
\subsection*{PseudoPaigeComm, Aloha LensComm, PianoComm}
We have a picture of Paige.  She is blue, but not shiny.  She's also
now a keyholder, together with It's Not My Chicken.  She's PicnicComm
and Asst.~Bluebellcomm.

\subsection*{$\hbar$Comm}
We have a poster!  It's up, but needs a WhatsNew sign.

\subsection*{FAC}
I sold a story!  For, um, \$5.  Look, \$6 victory donuts.

\subsection*{JourComm}
RSN.

\subsection*{War Council}
No progress.  We appear to be waiting on another group to move into 401D.

\goto{Old Business}
Enterprise is dead.  Death to Berman! (This last passes 21-0-4\ps)

The Spring Dexes will be printed tonight.  It's the year of the
Rooster, after all.

ALGOL
\goto{New Business}

John Wright has a new book out, and another coming soon.  Fantasy this
time.  \emph{Everness}

Next week on Smallville: Supes gets Superdog.

There will be a new hassling system soon.  It will be good.

\goto{Future Business}

New Mobcomm!  Books coming!  Maybe through Amazon Prime!

Carthago delenda est!  XIII-IX-VI\ps

Doesn't that end the meaning?  No, it's not Roman.

Matrix:\\
Motion to keep the meeting Romin': 13-8-3\ps \\
Motion to get a dog to chase Cato: 8-12-8\ps \\
Motion to name the dog It's Not My Chicken: 15-9-12\ps.

Determinant is 791, they all pass.  Paige helps count all the
chickens, since she's a \emph{Poultry Princess}.  More than that,
she's Secret Princess Poultry Princess.  B'gawk.

Paige is almost appointed to track down Spehn and see how he's doing,
but it chickens 9-0-24\ps.

Miller motion fails.

Miller motion passes 27-0-8\ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
