\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/18/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 18, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

The bong is amusing to many members.

Minutes read.

They are commended for almost causing Paige to die from lack of
breath, and condemned for not quite managing 11-5-6\ps.

Janet shows up to take a picture, causing Secret Princess Poultry
Princess to b'gawk and hide under the conn.


\goto{Committee Reports}
\subsection*{Jourcomm}
Some layout has happened.  When will it be finished?  Real Soon Now!
Real Soon!

Frame sucks, though.

\subsection*{FAC}

Raugh!  (Margaret shows up with a horrific costume of a Space Lacrosse
Marine with Blood Gauntlet Net).

\subsection*{Bleubellcom}
Shelf's clean!  Paige's fault.  JFC did half a book, promptly
sending it to surgery.

\subsection*{Mumbling about Rats (Vox Scirorum)}

There's an amusing entry from the SCC about a squirrel running by with
an enormous carrot.  Across the street, a snowman is missing its nose.

\goto{Old Business}
Janet continues taking obnoxious pictures.

The society is not commended for not moving, 6-6-9\ps.  Paige counted the chickens.

A couple boxes of old donation stuff lurked out of the alley to be
processed.  They appear to have been 2003 years old.

Margaret: Squirrels.

ALGOL, including usual complaints.
\goto{New Business}

May 7 is suggested as a date for the Picnic.  It's coming early this
year.

Gonzo is cool, and Muppets DVDs will be coming out this year.

JFC sketches on the frosh, Margaret, and anything else nearby.

A brief auction for New Business is conducted.  JFC wins with a bid of
one slinky.

\goto{Future Business}

Exactly 100 C/Ps are supersaturated, says Jamie.

After Margaret and Rebecca each have lacrosse sticks and are giggling
aggressively, Y moves to recognize that the meeting is about to have a
doub la crosse, but it chickens 4-4-7\ps.

The ASA may vanish out of existence before they get us stuff we need.
The UA and GSC are about to be eaten.

Yelena proposes a declaration that the UA and GSC will be first
against the wall when the revolution comes 42-4-0\ps.

Someday a 43rd Mersenne Prime will be discovered.

The invisible gavel on the banana block is condemned for making the
pants slip.  10-2-5 plus a cluck \ps.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
