\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad MM/DD/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, MONTH DAY, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion is made to commend the minutes as compost.  Passes 10-1-5+Spehn.

\goto{Committee Reports}
\subsection*{Pseudo-JourComm}
"What I said last week, though even more so."  The TZ is rumored to contain squirrels.

\subsection*{FrustratedAuthorComm}
"I sold my soul to customs and sent my book to Canada."

\subsection*{War Council}

\subsection*{LHE}

\subsection*{FAC}

\subsection*{PseudoMobComm}
John went to the Space-Crime Continuum and bought some books, but not
for MITSFS and not with squirrels.

\subsection*{Onseck}

\subsection*{Mumbling about Rats (Vox Sciurorum)}

\goto{Old Business}

The usual motion is made much earlier than usual.

ALGOL
\goto{New Business}

The Society decides the Skinner can't do anything right by >-<-1+Spehn.

"You're not supposed to let it run away.  You're supposed to staple the
squirrel to your forehead."

The Society discusses squirrel fishing.
Margaret: "There is photographic evidence that there are other people who are 
just as insane as I am."

\goto{Future Business}

"Okay, we'll send you the house sparrows and you can send us the grey squirrels."

Buffalo-hunting squirrels.  Yes.  Just because.  The Onseck is just writing
stuff down as it happens now.

"I had a dream last night which involved Andrew Boardman publishing a novel,
which is kind of ironic since he can't even get out TZ."

"Christ was an atomic physicist?"

Malcolm narrowly escapes being packed off to Albania by a vote of 2-2-4+Spehn.

Jamie tries squirrel-fishing for Joy, but is unsuccessful.  "Ah, you shoulda'
seen the one that got away..."

The Onseck is instructed to flip a coin to determine which version of the
minutes the quantuum superposition of the minutes collapses to, by vote of
the Society.  The version it collapses to does not, unfortunately, include 
the results of the vote.

Motion to kill all red and grey squirrels by breeding a banana-colored, 
banana-flavored Gnostic squirrel with vampire fangs passes 17-3-3+Spehn.

\vspace{12pt}

\noindent
Meeting adjourned, 1735 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
