\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 06/17/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, June 17, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and
Skinner, presiding; Margaret Gentile, Pseudo-Onseck, recording.

Minutes read by the pseudo-pseudo-Onseck, John Carr.

Motion to commend minutes for containing at lest 35\% squirrels
by volume.  Passes \hbox{10-0-Spehn}.

\goto{Committee Reports}
\subsection*{War Council}

We annexed space and filled it with boxes and sprayed
it with musk to keep the outsiders away.

Motion to not spray it with musk at risk of attracting squirrels.
Fails for lack of second.

%\subsection*{LHE}

%\subsection*{FAC}

%\subsection*{MobComm}

%\subsection*{Onseck}

\subsection*{Vox Sciurorum$_1$}

John has a picture of the empty space in a squirrel's tail.
Motion to send a probe to investigate passes \hbox{5-1-3+Spehn}.

\subsection*{Pseudo-Jourcomm}

What I said last week about what I said the previous week only more so,
only more so.

Instead of counting down the days until TZ should be published,
we are counting up the days after TZ should have been published.

\subsection*{HarassmentComm}

Bluebellcomm and Panthercomm are overflowed.
Consider yourself harassed.  John created space
by removing a box of Kleenex brand facial tissues
from the Skinner Shelf.

\subsection*{Vox Sciurorum$_2$}

John shows a picture of a squirrel excitedly discovering
a pile of sunflower hearts.  Margaret says ``Its eyes bore
into your soul!''  A moment later, her soul taken over by
the cute squirrel, she adds ``chickoo!''

Chris say he was surrounded by rabbits.

Saying ``we've moved onto nowhere'' the Skinner has had enough
with committee reports.

\goto{Old Business}

Undeterred, John shows pictures of fuzzy mutant ``rabbits.''
They look like feather dusters with noses.  Malcolm suggests
it took a lot of high quality fabric softener to make them
look like that.

The pseudo-Onseck's hand is too slow to record the entire
subsequent conversation.  The highlights include monkey
squirrels, lemurs, and near-future novels serialized in
{\it Asimov's}.  Is it antipope or autopope?  {\tt antipope.com}
is for sale.  Charles Stross has {\tt antipope.org}.

Everybody starts singing.  Andrew flees.  The Vice seizes power
in a (relatively) bloodless coup.  Alas!  The Skinner returns.
In the ensuing struggle for control of the gavel the meeting
is adjourned at 17:30 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Margaret Gentile, Pseudo-Onseck and John Carr, Pseudo-Pseudo-Onseck}

Vice: Grr...foiled again...

\end{document}
