\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 10/14/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, October 14, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Andrew Clough, President and 
Skinner, presiding; Kevin Riggle,  Onseck, recording.

Minutes read.

Motion that the minutes be beaten, staked to a post, and tied to a stake
to die in the hot noonday sun passes 4-3-1\ps.

The Skinner is Confused.

\goto{Committee Reports}
\subsection*{War Council}

\subsection*{PolitBuroComm}
The UA spent \$4500 on themselves to go to Cape Cod, and routinely bilk other groups out of 
money, says the Tech.

Motion to award the Tech the Fox News Award for Reporting Quality chickens 3-4-4+Spehn.

\subsection*{Skinner}
All the votes are in!  The Instrumentality has approved the changes to the Star Chamber, 
\emph{viz.} that MHG has moved to the position of LHE and ED has returned to the Star Chamber
as Vice.

ED: Phenomenal cosmic power is mine again!

\subsection*{KvetchComm}
JB has declared himself KvetchComm in order to accrue from the MITSFS reviews of books for
posting on our Web page.  Interested kvetchers should e-mail {\tt kvetchcomm@mit.edu}.

\subsection*{MobComm}
We're waiting on the creation of an account with Ingram.

\subsection*{HassleComm}
HassleComm has processed the last of the outstanding paperback old-style hassling, except for 
the deferred paperbacks.  Dealing with the New World Order Jamie-style Hassling may require
Dex magic, as may dealing with all the other HassleComming.

JB: Bring it (halfway) on!

\subsection*{ForbiddenClosetOfMysteriesComm}
Does anybody know what's in all those boxes?  

ED, our Archaologist, is on the task.

Motion to commend Jamie for his cryptography skill passes 14-.-7+Spehn.

\subsection*{MOOComm}
JFC's mom liked the previews on the new Wallace and Grommit movie.

\subsection*{MobComm}

\subsection*{Onseck}

\subsection*{Mumbling about Rats (Vox Sciurorum)}

\goto{Old Business}

We need to appoint a MobComm.  The ASA hasn't officially declared that it's thinking about 
considering the possibility of dealing at some far-distant point in the future with the 
decision to debate the idea of thinking about... something.  Maybe involving MITSFS getting more
space.

ALGOL
\goto{New Business}

The new Robert Jordan book is out.  MITSFS doesn't have a copy yet, but will pretty soon because
the Skinner is halfway through it.  Debate about the relative merits of (books considered by
some to be) long, boring, and sometimes cyclical books ensues.

MHG saw \emph{Serenity}.  It was good.  You should too.

Malcolm: "I never saw an explosion I didn't like."

Motion to end New Business passes 10-0-0+Spehn.

MHG: "Crisis averted."
AHC: "But you realize that New Business isn't over yet..."
MHG: "EMERGENCY BANANA MOTION!"

\goto{Future Business}

JB: "The future is quiet."

Motion to take control of the MIT weather ray deep in the heart of the earth to speed global
warming so that banana trees can grow in Massachusetts passes by Skinnerial decree.

\vspace{12pt}

\noindent
Meeting adjourned, 1830 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Onseck}

\end{document}
