\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 02/25/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, February 25, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

``Respectfully'' is corrected to ``disrespectfully and confusingly''
15-0-4\ps.

\goto{Committee Reports}
\subsection*{Jourcomm}

More layout progress.  AMB will be sending an ordering of short
stories.

``Real soon now.  This time for sure.'' ---Jamie putting words in
Kat's mouth.

\subsection*{Hasslecomm}
Many books have been processed and moved along a stage.  There's some
question of how to deal with rejected copies which are signed.

\subsection*{Onseck}
Usual Motion, fails by Skinnerial outrage.

\subsection*{PseudoMobComm}
A bunch of hardcovers were purchased from Buck-a-book as it was going
out of business.  ARMenard took a want list or Dexes or something out
to SCC and discovered they close early---perhaps as early at 5pm.

\subsection*{Mumbling about Rats (Vox Scirorum)}
Squirrels at U Penn have learned to send instant messages.  A rat came
in to somebody's room and started typing.  It was not distinguishable
from normal AIM l33tspeak.

\goto{Old Business}
Many donations processed.

A membership sold.

Alumni toured.  They predated the Dexes, but appeared to very slightly
postdate Jack.

There is some discussion of spray-glossing Paige and posting her on
the wall as a supplement to the Spectrum beg-o-matic issue with her
picture as a Poultry Princess.

ALGOL
\goto{New Business}

The sky is falling.  Y moves to tell the King.  BTS seconds, this
chickens 6-4-6\ps.

We have two new prentices---Yelena (Y``Deliverator''T) and Ash (ASH).

There's really cool ice on the Charles today, but nobody has blown it
up by overpressurizing it with CO.

U.~Iowa has a quarter million fanzines.  We were offered them and
turned them down because they're huge and, well, fanzines.  We
congratulate them on having the space to put them 15-1-1\ps.

We should keep that and mention it when we next ask for more space, to
point out how we and MIT are losing prestige because we can't get a
closet out of them.

\goto{Future Business}
Someday the ASA will cease to suck---maybe because the UA and GSC
ignore its constitution and kill it.

Someday we will take over the world.

BTS proposes that we secede, corporatize, acquire a Rat-Thing to
defend the library by launching it out the book drop---and also
deliver pizzas on skateboards---passes 25-0-1\ps.

Ooh, Birdfeeders!  The NH Audobon Society now considers Squirrels to
be Birds for some purposes.

We could buy Paige's chickens a banana, since they're underage.  This
passes 12-8-6\ps despite the relative ease of using nuclear forces to generate
banana juice which could then be fermented.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
