\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 3/4/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, March 4, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Kevin Riggle, Pseudo-Onseck, recording.

Minutes read.

Motion \textbf{BEEEEEP} passes 12-0-4\ps

Motion to commend the Pseudo-Onseck for his choice of minutes to read passes
by Skinnerial decree.  The minutes were from November 3, 2000.

\goto{Committee Reports}

\subsection*{PianoComm}
Three 'prentices are here; our new keyholder is at InterCon.

\subsection*{MobComm}
MobComm went shopping.  Books are coming. 

\subsection*{PseudoMobComm}
Space-Crime Continuum has offered to give us a 30\% discount on
hardcovers, though this may not be useful.

\subsection*{JourComm}
TZ got punted for a paper abstract.  Grr moving deadlines.  Kat: 
``I'm just the assistant JourComm!''

\subsection*{HassleComm}
 A box of books got processed yesterday.  The pile of HassleComm\dots
 did something

\goto{Old Business}

Ash reports that the Tech sucks at coloring.  Motion to take away their box of 
crayons passes infinity-0-1\ps

Discussion about the X-Windows method of choosing color names (engineer +
computer monitor + box of Crayola crayons) ensues.

Kat: "This is not a music theory meeting, this is a MITSFS meeting!"\\
Jamie: "Music theory is evil!  It distracts people from science fiction."

A Hamster has entered the library.

ALGOL

The usual bitching, wanking, and quacking ensues.

\goto{New Business}

Someone has been reading the new Tom Swift books.

Zombie fiction $\neq$ terrorist activity, the existence of certain horror 
franchises notwithstanding.

The Society discusses shipping lobsters and what would happen if you ran
one through the washing machine.  "Why can't we cook lobsters in pots?" "Now
if we could attach a *motor* to the pot..."

(gasping)
Rebecca (regains breath): "Can I kill him?"

``Usual motion!''\\  ``We already did that.''

Motion fails for lack of unusualness.

``Unusual motion!''

Motion to unusually do something usual chickens 3-0-15\ps

BING!  BING!  BING!

\goto{Future Business}

John is sent to Albania due to the sexy naked zombies.\\
Jamie is sent to Albanian due to the sexy naked zombies.

It is noted that, had two people been sent to Albania this time *last* year,
there would have been no meeting left.  

The Skinner can choose to understand Albanian.  ``With great power comes
great responsibility.''

In the future, there will be Spring Break.  

``In New England, March comes in like a polar bear and goes out like a pengin.''

Motion to rebell against the penguin masters passes 14-13-6\ps

BING!

``The toaster is bleeding!''

A motion is made in Albanian, but no one understands it.  It fails 
1-15-3\ps

Miller motions is made, but it fails 4-19-1+DevilDuck\ps

In the future, there will be Anime Boston!

Motion to condemn Andrew for failing to make a banana motion 21-3-4\ps .

\vspace{12pt}

\noindent
Meeting adjourned, 1806 SST.

\vspace{18pt}

\centerline{Pseudo-respectfully submitted,}
\centerline{Kevin Riggle, Pseudo-Onseck}

\end{document}
