\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 01/28/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, January 28, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Brian Sniffen,  Onseck, recording.

Minutes read.

Motion to approve the minutes as updated, colorized, and brought into
the 20th century passes 16-0-3\ps.


\goto{Committee Reports}
\subsection*{War Council}
Warcomm:  We're talking to Phil to kick the ASA since... they haven't moved!

\subsection*{Pianocomm}
Pianocomm:  Yay, we have prentices

\subsection*{FAC}
Psuedo-Panthercom:  We have overflow for the first time in a while.  Its either the fault of the snow, or the boxes of new books.

If you put RJ books in a compressor, you get two types of juice that *don't mix*.  Its extruded fantasy prduct!

\subsection*{MobComm}
Jourcomm: We found Andrew and hes looking for someone to do layout.
Same as a year ago, but now Kat is willing to layout, so maybe its
really real soon now now.

Move to apoint Rebecca Ass(assin)com passes 12-4-6\ps.

Jamie: When you're not expecting it, thats when you get the subtle
chainsword in the back.

\goto{Old Business}

We got new stuff, now in panthercom.

We still have extra Analogs, since they're coming to us twice.

Margret: Extra analogs make good armor inserts

Jamie: Like spam containers.

A boring discusion about which zines we have occurs, which is not
nearly interesting enough for me to record.

Margret: Does this mean that RJ books could be an inexpensive
alternative to Tank armor?

Jamie: It would be too heavy to move.

ALGOL\footnote{with both usual debate and "what about the usual
  debate}

\goto{New Business}

Rebecca tries to assassinate Skinner, but fails to remember that Kat
is omnipotent inside the library.

Speculation about what powers the skinner's powers occurs in which
the souls in the gavel are brought up, but we eventually decide that
its the gavel.

Margret: Burning souls smell bad, like burning hair.

\goto{Future Business}

In the future there will be a TIF, and a Spring Schelual

In the future there will be term.

Miller Motion: Fails 19-14-2\ps.

Motion:  Send Margaret to Florida for the recount fails 5-7-3\ps.

Malcom says something inscrutable.

Albanian the usual suspect:  Maclom 24-22-3

People note that our albania link now goes to a wiki, meaning that... something.

Miller Motion appears to fail 16-7-2\ps.

Move to reserve ``America is a banana-colored wiki.com'' fails  1-5-2\ps.

Matrix Motion passes 7-5-8+Spehn

Looks like arithmetic was weird that night.

\vspace{12pt}

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Brian Sniffen, Onseck}

\end{document}
