\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page} \quad -- \quad 05/06/2005}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}
\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

Friday, May 6, 2005

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 1730 SST, Kat Allen, President and
Skinner, presiding; Kevin Riggle, Pseudo-Onseck, recording.

Minutes read.

\goto{Committee Reports}

\subsection*{MobComm}
Books bought, they will be coming soon.  Books taken to Pandemonium, which
took about three-quarters.

\subsection*{BluebellComm}
There are books which got covered.  There should be \emph{more} books covered.
"Collective disperse of scatter-poke."  "Jefferson K. Polk?"

%\subsection*{Onseck}

%\subsection*{Mumbling about Rats (Vox Scirorum)}

\goto{Old Business}

Debate and discussion of hitchhikers (specifically one Arthur Dent) "getting
some" ensues.

ALGOL
\goto{New Business}

The Society discovers something interesting under the table.  The interesting
thing goes away when Paige is selected as the person to write things on the
chalkboard.

Elections.

Onseck: (Kevin Riggle, 1000 paper cranes, squirrels, the Hitchhiker's
Guide... "perhaps we should find a *taller* Vanna"... Albania are nominated)

Votes accrue to, among others, the Blue Shiny Squirrels of Gor, "ook!",
"Cthululululu [Christmas Version]," and Kevin Riggle.     

Squirrels, the Librarian of Unseen University, and Cthulhu all make a strong 
showing, but Kevin Riggle wins with 10.34 volts.  (He also appears to have
been named the official candidate of Gor.  Whether his election to the Onseck-
ship of the Society will affect his chances in the upcoming Gor runoff election
has yet to be determined.)

The minutes past this point were lost in the Great SSH Freeze of 2005.  The
election results have been reconstructed from first-hand accounts of the
participants (although their reliability has been questioned), a series of
papers bearing arcane scratchings, and the output of a half-dozen monkeys on
typewriters, because the Markov chain generator needed something to work from.

Some sources have it that, before the election, a member of the Society 
asked the Official Candidate whether she planned to fulfill the duties of
her office by absconding to Brazil with the money.  Unfortunately, they 
contain no record of her answer.

It appears (from the scratchings) that Paige was elected as Lord High Embezzler,
although the penguins and Cthulhu made a strong showing.


It also appears that Margaret, the outgoing Vice, was elected Vice, although
she faced stiff competition from [undecipherable].

"Owwwwwww, the God of Tooth Decay."

"Hastur and Hello Cthulhu hog-tied in a bondage tent on Gor."

The minutes from here on were preserved by a squirrel in the roof of W20,
and are presented in full, albeit somewhat edited to preserve the sanity of
present-day readers.

\subsection*{President} 

(Among those nominated were 10111010, Goodbye Kitty, Hello Cthulhu,
Tony Blair, SPF45 sunscreen, and Andrew)

"If you hated dominatrix Cthulhu, you should like submissive Cthulhu!"

Susan Hockfield was nominated, but declined due to a previous committment.

Though he faced stiff competition from the ninja party and the Cthulhu-
Hello Kitty ticket, and even given that some votes may have been misdirected
to another person named Andrew through a balloting error, Andrew Clough 
("Cluff") pulled through in the end to win the presidency, with Moses aka
Nimbus aka Cthulhu as his official second.

"Skinner?  But I just..."

Future Business:

There is a picnic tomorrow which, in the event Nimbus is unhapy with us, will
take place in a secret, possibly mobile location in the Student Center. 

A motion which congratulates the newest Keyholder and Onseck for (mumblemumble) bananas (mumble) passes 15-llama-3+Spehn.

Adjourns 1730 SST.

\noindent
Meeting adjourned, 1800 SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{Kevin Riggle, Pseudo-Onseck Onseck-Elect}

\end{document}
