\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 28, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1708 Eastern Disciplinary Time. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

Deanne saith: verily unto us is yet 67.37.

Libcomm: Invaders from the Infinite has come, while Imaginations and Amazings are ready to be checked out. We need a stapler which will staple long staples.

Jourcomm: no report.

War Council: a meeting of Walker-Basement-East with McDowell will be held at 5 PM Monday in 1-236. Lewis and Skinner will attend.

Moocomm: no word yet.

Theftcomm: posters up.

\goto{Old Business}

Jim Keller (Holman 201) has ASFs for sale.

\goto{New Business}

It was suggested that we have a picnic instead of a banquet for our annual banquet.

MSP (Ravin) to have a picnic instead of a banquet. 15-1-1.

Kentaylor was appointed Banqucomm. Lewis will invite Asimov as soon as plans are firmed up.

The Library will be open as usual over the weekend.

A Deandrive was on exhibit at the Science Fair.

Are the members interested in going to Technightatthepops? No!!!

MSP (Miller), 12-4-3 at 1733.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}