\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, September 22, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting began at... er... uh... well, it seems like I didn't take down the exact time. So this meeting is uncalibrated. TS. Anyway, Skinner was responsible.

The minutes of the previous meeting were read and approved (naturally) without correction.

\goto{Committee Reports}

Treasurer, Theftcomm, Moocomm, Libcomm: No report. Ditto for Vengeance Fleet and War Council.

Tablecomm: Norwood talked a while about the glories of Tablecomm (snicker, snicker). I don't remember exactly what he said, but I believe I can quote an excerpt from one of last year's meetings as noted by Anthony "Mr. Maturity" Lewis, to wit: "Norwood made a fool of himself."

Jourcomm: B___s___ted for a while, also made a fool of himself.

\goto{Old Business}

None to speak of. Or at least nobody did so.

\goto{New Business}

Whealton's bad luck announced; we shall have to invent another Vice President for the noble Society.

Everybody introduced him- (or her-) self. God, what a mess.

MSP (Pearson, ?) to put off election 'till next week to facilitate matters. Or something like that. (M-3)-3.

Skinner, our Noble Steed, explained the committees to the starry-eyed freshmen. Mainly because most committee chairmen were absent.

Lensch's meeting prime was announced.

Lewis so moved at 5:43:03, (m-x)-x (where m>>2x).

\vspace{12pt}

\centerline{YHOS,}
\centerline{The Ravin, Secretary}

\end{document}