\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, May 19, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The last meeting of Year 11 of the Society was called to order by President Skinner at 5:05:45 Earth Mean Time. The minutes of the previous meeting and the picnic were read and approved without correction. Hoylman claimed that he went on the picnic, but the minutes didn't mention his name. Therefore, he didn't.

\goto{Committee Reports}

Treasurer's Report: The treasury stands at 53.67, mainly due to the fact that the picnic cost 15 dollars. Income this week was 1.50 from various sources.

Theftcomm: Whealton goofed. Therefore, no posters. There are, however, 4 movie posters up. Skinner directed Theftcomm to make posters for all the dorms. Theftcomm meekly complied with this order. The cowards! When I was Theftcomm...

Libcomm: Humer- no report. Whealton- donated one Amazing to the library.

Jourcomm: The Ravin announced that as of today the editorship will be split in two: Whealton will be the "literary" editor, while the Ravin will take over as correspondence editor, combining these duties with those of the Secretariat. Letters of comment will now be sent to me; manuscripts to Whealton.

Moocomm: The movie has been cleared with LSC- "Toward Greater Strength," the Institute's new laugh hit, will also be shown. Yes, kiddies, it's even better than "Men of Science." We shall be OK as soon as Court calls on PhotoService and asks for a projectionist, says Schildkraut. Tickets will be 25 cents. The Sandorff film was procured by the Noble Secretary, and will be shown if there is time.

Tablecomm: Did not show up. Hopefully, a hole opened up in the space-time-matter-energy matrix of the universe and inverted their parameters.

The Whealton Sheck(ley Check)list was distributed.

\goto{Ye Olde Busyneff}

Whiton reported that since the dorms will get a dial phone system this summer, it will be possible for the library to get one at a minimal one-shot fee (5 dollars). Or at least, that's what he says Prof. Tucker told him. Whiton gets a gold star.

There was general agreement among the peasants; we SHALL have a phone!

\goto{New Business}

Skinner ordered Humer to make and run off a handbill stencil for box-stuffing. 'Twill be done Wednesday, saith the Golden Haired One in Air Force Blue (Humer).

Skinner took care of whatever had to be done for the midway. May God have mercy on our freshman!

Bob Simon took some pictures of the Noble Society, no doubt for his collection of pix of unnatural phenomena. He didn't even get Deanne in the picture. What a waste of film!

Milleration (Whiton-Ravin/Lewis); 16-1-0 at 5:34:45.

Thus ends the Chronicle of Year 11 of the Society. Happy summer to all, and to all a good night.

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

(Summer 1961: flunked out- F. Isaacs, K. Whiton, E. White V, Whealton (financial difficulties), also Betty Lou Snarr)

\end{document}