\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, February 24, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1711 by Skinner. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

The treasurer reported that we now have 170.43 and 42 members.

Theftcomm: 4 posters up- 2 down. 5 VooDoo posters destroyed (cheer, cheer).

Libcomm: the library will be open 15-17 Saturday (Skinner), 14-17 Sunday (Humer). Court read the list of people who still have books out.

Jourcomm: proceeding as usual.

Moocomm: no report.

War Council: Lewis saw McDowell. The mimeo was given to VooDoo (who are obviously not as deserving of it as the MITSFS). Anyway, it was an A.B. Dick not a Gestetner so we won't feel too badly about it. Also, there is a possibility that we may be able, perhaps, to also obtain one of the rooms adjoining our library.

\goto{Old Business}

Lewis and Skinner, Osten and Kuhfeld attended the Tuesday Activities Council meeting. Since not enough voting members to be a quorum no definite action was taken about anything.

MSP (Lewis) that a new committee, called Tablecomm, be set up by the Society. That the purpose of the committee shall be to arrange informal SF discussions by members of the Society and others. Furthermore, that Tablecomm be charged with the care and maintenance of the Society's collection of microfilms and tape recordings.

William Osten was appointed chairman.

Bob Schildkraut passed around pictures of Isaac Asimov that he took at the talk Wednesday.

\goto{New Business}

MSP (Humer) that Psico be flushed. (23+i)-0-2.

MSP (Lewis) at 1743. 15-2-8.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}