\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 17, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1713 in room 1-236. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

The treasurix say: 170.14 in ye olde treasury.

Theftcomm: posters up, posters down.

Libcomm: a short article was read from the NY Times theatre section. It dealt with a play taking place on Mars. It was termed null-sf. Ho ho. More magazines are ready to be checked out.

Moocomm: Shape of Things to Come is available in 16 mm. We hope it hasn't been cut too much. A 52-dollar bill for the projectionists came today. We should pay it.

Jourcomm: next Friday night, stencil cutting party. Whealton (chief coolie), Gross, Humer, Skinner, White V, Morris. We will try to get 410 lounge. A fanzine was received from Caltech, as was a copy of a speech given by Mr. H. Gernsback before the ESFA (Easter SF Association).

Tablecomm: a discussion of Sheckley's works will be held Monday at 19 in room 50-110.

War Council: tried to see McDowell but couldn't. Letters from and to Clement were read. He will be here 14 April.

\goto{Old Business}

Add acetone to the rubber cement at regular intervals to prevent drying out. No stationery ready yet.

\goto{New Business}

MSW (Lewis, Pearson) to purchase Unknowns from Julius Unger for 65 dollars.

MSP (Pearson, Ravin) to call Unger and haggle, 60 dollars tops. 7-4-3.

A letter form for room space in the new student centre (haha) was filled out and sent in.

Pick a (book)^n for February: Drunkard's Walk (Pohl) came.

We would like a microfilm reader, movie projector, and tape recorders. We won't get them.

MSP (Humer, Campbell) that if Unknown falls through to buy Wm from Sleptrem. 15-1-1.

Loo Kennar has some books to donate.

MSP (Lewis, Ravin) at 1803. 15-2.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}