\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, January 13, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order in room 1-211 due to conditions beyond our control. The minutes were read and approved.

I have a new pen.

\goto{Committee Reports}

Treasurer says we have 59.70.

Theftcomm: is working on her 4.02 projects (absent).

Libcomm: is working on his 8.09 project (absent).

Theftcomm 2 has arrived and is here.

Salvation Army has a bookcase for 10 dollars.

Warcouncil: Court did not attend the meeting of the activity heads- SHAME!!!

Moocomm: all set. Poster to be made. Tickets have been ordered.

Theftcomm 3: posters up. Movie posters are ready.

Jourcomm: typists for journal- Whealton, Steve; Gross, Deanne; Harper, MW; Ravin, Jon; Skinner, L. Court; White V, Edward; Sarill, Bill. Meeting in Ravin's room, Conner 413C.

\goto{Old Business}

4 jars poster paint and 50' of paper cost n dollars.

Meet on 3rd floor of building 50 tomorrow at 1500.

Lewis reported on Activity Council meeting- nothing useful happened.

Do we want McDowell's mimeo? Yes! Fight for it.

\goto{New Business}

Spell Asimov as Azimov.

E. Tinzley: info about Society and major events for Technique.

Norwood made a fool of himself.

MSD (Norwood).

MSP (Lewis) at 1747, 9-7.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}