\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 1, 1961

Dedicated to our muse (the idiot, of course!)

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
At 5:04 and 22, Eastern Standard Time

The first of December '61, saw a horrid crime.

Skinner called the meeting to order

Out of the Primal Slime.

And then the Minutes were read

By the Noble Secretary

And all the members proclaimed:

"Accurate? Not very!"

Skinner then proceeded

To read the Minutes of Old;

That he was playing the fool

He didn't have to be told.

And then, as usual, came

The committees to report:

First came the Treasurer

(Who is a little short.)

"What I really want," she said,

"Is, well, let me tell you:

A report from each on what

Our rich Treasury owes to

Each and every one, if any,

And I hope it's not

Very much and overly many!"

So saying, she sat down,

And then 'twas Libcomm's turn.

When he rose to make his report

I thought I could discern

A gleam in his eye, as though

'Twere to announce a heavy fine,

But all he did was review

Some new titles in his line.

And then he told each and every

Of his Library Crew

What days they'd do their work

And their hours, too;

On Saturday, from 2 to 5

L.C. Skinner will preside;

On Sunday, the same hours'll be

Ed White's Pyrrhic victory.

On Monday, if all goes well

Deanne will be there; swell.

And on Thursday Noble Ravin

Will open up our SF-ish haven.

And then 'twas Theftcomm's turn;

Lensch said "No report."

So too said Moocomm's Harper

(Who is also somewhat short.)

Jourcomm in a fannish daze proclaimed

"No letters yet from one of SF's famed."

Then Tablecomm: Norwood said "Someone

Should come to our meeting in 5-231.

Next meeting is Tuesday at eight

As usual, and please don't be late.

(The Noble President then related

A tale of woe, when they were fated

To miss their own Tablecomm meeting,

Because of their habitual comic book reading.)

Then War Council announced:

We are listed in "Preview," that

Notable noble journal of

The Undergraduariat. (Sorry, Ogden.)

The Vengeance Fleet, too, had no report

Said Leader Skinner (who's not very short.)

'Twas Smokomm's turn then, but he was hexed,

For Skinner skipped him, and he was vexed.

(To rewrite history is not my choice,

Yet the Noble Secretary must voice

His opinion here, as to what

He can do, and can do not

In the way of preserving the

Truthfulness of history.

And so your Secretary and reporter

Will place Smokomm in the proper order.)

Simon had but little to say:

"If you wish to see Doctor A

The Library Lounge at 5

On Friday the eighth is the place to see

This very famous face."

(And if you people think that I will continue with this quasi-poetry, you're NUTS! I will continue from hereon in my usual inimitable style. Those of you who wish to leave the room may do so.)

\goto{Old Business}

MSP (Ravin, Norwood) to resubscribe to Campbell's Folly (otherwise known as Analog). The vote was 15-5.

Hunter asked about Flash Gordon movials. Pearson said there ain't been much action yet.

\goto{New Business}

MST (Morris, Olsen) to buy The Worm Ouroboros, some more Conan books, and various other fantasy-type books. Skinner tabled the motion till the next meeting; a list was given to Libcomm to look up the prices.

MSD (Ravin, Olsen): I so move. 12-13, 5:37:00.

MST (Lewis, Olsen) to socialize the Noble Society.

MSP (Norwood, Ravin) to table the previous motion. 16-9.

At this point chaos broke out. From the radioactive ruins left scattered about, I have managed to piece together an approximation to what happened.

Apparently:

1) Campbell moved to reestablish the office of Lord High Impotentate.

2) Skinner pointed out that this office is still held by one C. Robert Keppel.

3) MSP (Campbell, ?) to reestablish same; anyhow, Campbell was appointed a committee of two to write Mr. Keppel for consultation.

MSP (Ravin, Lewis, Humer, Skinner, etc.): "I so move." 15-7 was the vote, and so another meeting of the MITSFS came to an end at 5:47:00. It was a meeting like all other meetings, except...

You were there.

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

Note please: those of you who called for roll call votes: I have no objection to same on principle. But I do get hungry. Don't do it, please. Pretty please? (Anyhow, I don't have a list of the members. So there.)

\end{document}