\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 13, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The Noble President, L.C. "Horny" Skinner, called the meeting to order at 5:15:00 Galactic Daylight Savings Time.

The minutes of the previous meeting were, for the nth meeting in a row, read and approved as usual.

\goto{Committee Reports}

Finstatcomm (the Treasury): Signora Gross reports 1 dollar in dues taken in, 3.35 in for Coop refund, for a grand (and I do mean grand) total of 355.95.

Post-PUcomm (Theftcomm): Lensch says posters still up.

Talrcomm (Moocomm): Not here. Will be hung by the thumbs. If he or she ever shows up, that is.

Jopubcomm (Jourcomm): Morris thinks he has enough material for an issue, almost. Morris donates a corkscrew to Tablecomm. No comment.

Boocomm (Libcomm): Donations received (says our Boskonian agent) from Doug Hoylman; Humer and coed Erna Beiser also kicked in some paperbacks. Boocomm FinBoard: out- 8.46 for Pick-a-Book book from the Pick-a-Pick-a-Book-Book Club and subscription to Fantastic and tape.

Barfcomm (Tablecomm): No people at last meeting. (Victory for the forces of maturity.) Next meeting: Wed, 5:00, 5-302.

\goto{Old Business}

Morris reports on Barfcomm: "They discuss SF even less than we do." Norwood objects, but the fundamental truth remains: Tablecomm is a victim of the Forces of Evil.

Skinner (himself) requests a committee for the promotion of an SFS smoker to be called Smocomm- R.W. "Morris" Simon volunteers.

Movie possibilities were discussed: Forbidden Planet? Flash Gordon-type serial? Lewis says Schildcomm might be able to do something about this.

\goto{New Business}

Lewis (of Boskone) wants 20.08 for a trilogy, Rings, Lord of, one of and Hobbit, The, one of, by J.R.R. Tolkien and Science Fiction, Checklist of, Day, Brad. He so moved, and 'twas passed 19-2, 1 active, 4 passive.

At this point Speiser made a passionate plea for a library key (repeat 3 times), and L.C.H. Skinner promised him one.

(B.) Morris wants to buy Russian SF books. He so moved (2nd, Olsen), 12-5-9.

Lewis requests support in Activity Council for LSC vs. Russian Dorm film series.

Movie will be Jan 17 in Kresge (last day of classes).

Library: Sat L.A. Campbell, Sun Morris B., Thurs me.

Millermoved at 5:48:23. Miller_Ravin, Miller_Lewis- 12-9-M.

And another page has been filled in the Great Book of Life.

\vspace{12pt}

\centerline{So be it,}
\centerline{Jon Ravin, Secretary}

\end{document}