\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, May 12, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
FOREWORD: In a blare of trumpets, the long and glorious reign of A.R. Lewis as Noble Secretary of the Society came to an end today. Rather ingloriously, too, as Lewis did not deign to make his entry until the meeting had gotten underway.

PREFACE: Today the honorable J. Ravin took over the reins of the Secretariat from the aged and mature A.R. Lewis. Due to an oversight, he failed to write up the minutes of the meetings for the rest of the term. He apologizes. He also wishes to state that next year's meetings will be written up this summer; you will be unguided for only one more meeting this year.

THE MINUTES: Steve Whealton got a baptism-by-fire in his new position as Chief Figurehead in Charge of Vice, as President L.C. Skinner 1.96 was late in arriving.

Thus Steve presided over the first half of this meeting, which began 5:03:35 Earth Mean Time on this first day of the Reign of Ravin.

\goto{Committee Reports}

Treasurer's Report: The line is held at 67.17 (no change).

Libcomm: The library was moved on Monday to 50-020. It was reported that a mysterious ray from outer space destroyed the glass panel in the door, which was fixed by the grace of God and B'm'P.

Jourcomm: A glorious "no report."

Theftcomm: I can do naught but quote the Lensch: "I goofed."

Moocomm (Schildcomm speaking for Moocomm): "The movie is here! It's in 16mm."

Tablecomm: Announced a meeting for Monday, May 15, which will be a discussion of "anything." Fred bitched about lack of attendance at Tablecomm meetings.

GLORIA! The minutes arrived with Lewis at 5:07:05 EMT. The minutes were read (by Ravin) and approved with no additions or corrections.

\goto{Ye Olde Busyneff}

Durk Pearson asked about insurance. There was a roaring silence; apparently no one has looked up the company which Durk said might insure the Library. Too bad.

\goto{New Business}

MSP (Norwood-Pearson) that the Society should trade its triplicates and higher copies for other mags and books. (The vote was not tabulated by Acting President Whealton, but was about 18-2.)

NEWS FLASH! Norwood did not make a fool of himself- at least, not up to this point. Lewis was having much fun making like the Brodsky.

MSP (White-Harrison) that Libcomm decide what shall be traded for what. (This was an amendment to the preceding motion.) (Again the vote was not tabulated, but was about 20-0.)

A further amendment by Kuhfeld was ignored.

The Whealton announced that he would have a Sheckley checklist of sorts available at the next meeting. (It was run off by the Secretary on Thurs. May 18; stencil cut by Whealton.)

The President arrived at 5:22:55 EMT with the Gavel.

Schildkraut and Lewis emulated their heroes Brodsky and Lintner for a while.

It was announced the Picnic will be Sunday at 12:45 in Building 7 and will progress (depending on the weather) either to the Miller Room or to the Blue Hills. About 20 people are going; it is hoped we will have enough cars. If absolutely necessary, Asimov will be pressed into service.

Movie poop (straight from the Skinner's mouth): the movie will be in 10-250 Thursday May 25. We will show "The Shape of Things to Come" and "From Strength to Greater Strength." Coolies: Hoeper, Whealton, Hoylman, Ravin, Skinner, Humer.

Coolies for Freshman Midway (which will be Fri, Sept 15, 1961 at 8 PM): Hoylman, Gross, Humer, Ravin, Skinner (the chairman), Norwood, and Whealton.

Schildcomm will take a collective picture in the Library Saturday at 3:30 (for the freshmen of '65, God help them).

THE motion (Whiton-Ravin) passed 14-1 at 6:05:30.

\vspace{12pt}

\centerline{This first installment of the history of the New Dynasty was written up by}
\centerline{Jon Ravin, Secretary, of course}

\end{document}