\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 17, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Skinner called the meeting to order, as usual, at 5:11:00 Cambridge Standard Time. Then, as usual, he made a fool of himself, reading some more minutes which he should have left buried in the remote past.

\goto{Committee Reports}

Treasurer's Report: Gross had no report, as usual.

Tablecomm: Next meeting, Tuesday at 8 in 5-231, as usual.

Libcomm: Fines begin on Saturday; the blacklist was read again. Library hours: Sat 2-5 L.A. Campbell, Sun 2-5 E. White V, Mon 11:30-1 D. Gross (if possible).

Smokomm: Simon called the Good Doctor Asimov. Smoker will be Dec 8 in the Library Lounge at approximately 5:00 PM.

Moocomm: No report, as usual.

Theftcomm: No report, as usual.

War Council: Lewis wants us to try for one of the rotating seats on Activities Council. No comment.

\goto{Old Business}

None!

\goto{New Business}

There will be an APO Carnival this year- we need a Carnalcomm head. Skinner explained the Cookie Incident.

I so move (Ravin, Simon), 5:35:00, 10-11.

I so move (Ravin, Simon), 5:36:00, 11-12.

Pearson and Norwood move to change this meeting to a Tablecomm meeting- denied, 7-15.

I so move (Simon, Ravin), 5:40:00, 13-13, Skinner breaks the tie for the forces of evil.

\vspace{12pt}

\centerline{This stuff by}
\centerline{Jon Ravin, Secretary}
\centerline{as usual}

\end{document}