\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, September 29, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Skinner the Great called the meeting to order at 5:11:35 MWT (my watch's time). The minutes of the previous meeting were read and approved without correction. The secretary appreciates the restraint of the members; a standing ovation is a bit vulgar.

\goto{Committee Reports}

Treasurer's Report: Victory- we robbed the bursar's office... well, not really. Due to last term's movie and new members and Gernsback we had on hand 344.29.

Libcomm: Not here, no report.

Theftcomm: Not here, no report. Lensch came in somewhat later and mentioned that posters were up.

Moocomm: Not here, no report.

Jourcomm: Here, no report.

War Council: Lewis- we will probably get a phone for the library, by hook or by crook (mostly crook). Schildkraut himself and secret agent Geo. Broderick will connive it. Best thing is that it will be free. If the Institute doesn't find out, that is.

Tablecomm: No report worth mentioning.

\goto{Old Business}

Election- as the secretariat didn't send out notices, the election had to be postponed one week. The secretariat was directed to get out said notices.

Pearson brought up the matter of insuring the collection (against Sarill, mostly). He was put off. Someone, probably Skinner, will look into it.

\goto{New Business}

New committee chairs:

Libcomm goes to Tony Lewis. His chief coolie will be Bernie Morris. Also on the staff are L.A. Campbell, E. White V, the Noble Secretary, Deanne Gross, Jeff Speiser, and the most enthusiastic volunteer of them all, R.W. Simon.

Theftcomm is retained by Lensch.

Moocomm- is there a sucker in the house?

Journal- the Journal will be edited by B. Morris. Now that I have THAT monkey off my back, I will take care of the correspondence only.

Vengeance Fleet- the Library coolies.

Tablecomm- Osten, Kuhfeld, Pearson, Norwood, X (X is pronounced "Sarill," no doubt).

At this point a freshman mentioned that he knows of a bookbinder in Portugal who does so for about 1 dollar/volume and the shipping charges are about 1.30/volume. We shall look into it. Anybody speak Portuguese?

Pearson says he can make us up some stationery. (He's made a calculation...)

The address of the SFS will be changed from Burton Box 617 to Rm. 50-020, Walker Memorial.

Osten offered a bound volume of Amazing (1934, 1-6) for sale. There were no takers.

Project Smoker: Asimov or Campbell? The secretary will write to Campbell.

Movie for this term- quien sabe? We need a Moocomm chair.

Library schedule for this week: Sat 2-5 L.A. Campbell and/or Bernie Morris, Sun 2-5 E. White V, Mon 11-2 Deanne Gross, Thu 2-5 The Ravin.

Norwood made a fool of himself.

Chaos reigned for m*pi/a minutes, as Skinner sat back and enjoyed same.

It was so moved (Ravin-Hoeper) at 5:51:05. The vote was 20-3-4i.

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

\end{document}