\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, May 5, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Meeting called to order at 1712 EDT.

The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

Treasury is unchanged.

Libcomm: new book in library.

Theftcomm: posters up.

Jourcomm: no report.

Moocomm: saw Bob Duff, who had no report.

Banqcomm: check with Summer Session Office and TCA. In Boston with a fireplace. It will be on Sunday 14th of May. Cars to Blue Hills: White V, Isaacs, Harrison.

War Council: we move to 50-020.

\goto{Old Business}

None.

\goto{New Business}

Elections.

President:

Nominated- L. Court Skinner, Steve Whealton.

1st ballot:

Skinner- 21 (elected)

Whealton- 6

Lewis- 1

S.E. Plant- 1

John Carter- 1

Total- 30

Vice President:

Nominated- Norm Humer, Fred Norwood, Kentaylor, Steve Whealton.

1st ballot:

Whealton- 14

Kentaylor- 6

Norm Humer- 4

Fred Norwood- 1

Abstain- 1

Dearest Court- 1

Freddy- 1

JWC, Jr.- 1

Zot- 1

Total- 30

2nd ballot:

Whealton- 16 (elected)

Taylor- 10

Kingsley Amis- 1

Dearest Court- 1

Mentor of Arisia- 1

Blank- 1

Total- 30

Secretary:

Nominated- Fred Isaacs, Fred Norwood, Jon Ravin, Kentaylor, Ed White V.

\begin{center}
\begin{tabular}{ c c c c c c c c }
  & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\ 
 Fred Isaacs & 2 & 0 & 0 & 0 & 0 & 0 & 0 \\
 Fred Norwood & 6 & 7 & 9 & 12 & 11 & 9 & 7 \\
 J. Ravin & 6 & 13 & 14 & 12 & 12 & 14 & 17 \\
 Kentaylor & 7 & 6 & 4 & 4 & 5 & 6 & 5 \\
 Ed White V & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 Sarill & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
 Dearest Court & 1 & 2 & 2 & 0 & 0 & 0 & 0 \\
 Gross & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
 Void & 5 & 1 & 0 & 1 & 1 & 0 & 0 \\
  & 29 & 29 & 29 & 29 & 29 & 29 & 29 \\ 
\end{tabular}
\end{center}

Ravin elected.

Treasurer:

Nominated- Deanne Gross, Fred Norwood, Kentaylor.

1st ballot:

Gross- 15 (elected)

Taylor- 5

Norwood- 2

Void- 5

Total- 27

Committees appointed:

Libcomm: Norm Humer.

Moocomm: Kentaylor.

Theftcomm: Sandy Lensch.

Jourcomm: open.

Tablecomm: Norwood/Osten.

MSP by Lewis, 1841; thus endeth a saga.

\vspace{12pt}

\centerline{ARLewis, Secretary}

\end{document}