\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 27, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Our Noble President, L.C. Skinner of Tulser, Oklahomer, called the meeting to order at 5:14:50 Institute Screw Time.

The minutes of the previous meeting were read and approved without correction, except for a dirty trick by Simon- he gave me his phone number wrong- which doesn't really count.

Skinner read minutes of some previous meetings, 1 from 1952, 1 from 1951. Skinner made a fool of himself.

\goto{Committee Reports}

Treasury: Gross made a report. Since she didn't give it to me on the slip of paper on which it was written, I don't have it. Well, an approximation follows: Libcomm spent about 50 dollars, leaving the treasury with 303 dollars and change.

Theftcomm: Posters up. So what else is new?

Libcomm: The Hobbit and Lord of the Rings trilogy came in; they will not go out until someone covers them. Day Checklist arrived. December William is in the library. Lewis read a long list of people who checked out books at t<Sep 1, 1961. He suggested the return of them.

Jourcomm: Journal the weekend of Nov 10. Wrote to Viper for ASF article reprint rights; no reply as yet.

Moocomm: Lewis says we will probably get Forbidden Planet. Good!

Smocomm: Simon: "Ravin, did you get an answer from Campbell yet?" Ravin: "...no." Simon: "No report."

\goto{Old Business}

Lewis, in reference to the previous bit on overdue books, moved that books, mags, or whatever checked out for more than 3 weeks shall be subject to a fine of 5 cents per day per book. A subsequent amendment by something named Donahue amended that to "5 cents per day per book for each day the library is scheduled to be open and is open; scheduling to be done at last previous meeting." This was incorporated into Lewis' motion by Lewis.

Motion to table (Pearson) defeated 3-11.

White suggested a further amendment to the effect that the maximum charge shall be 4 times the price of the book. This was also included in the motion by the ARL.

MSP 21-1 as above, all amendments included.

At this point Tablecomm decided to make their report, for some obscure reason. They didn't do much except announce their next meeting as in 5-203 Tues at 8 PM.

Norwood intends to submit the Tech Round Robin (Ravin, Norwood, Pearson, Sarill, Lewis, Skinner, and God knows who else are responsible) to magazines (pro). No comment.

\goto{New Business}

Library: Sat 2-5 Campbell, Sun 2-5 E. White V, Mon 11:30-1 Gross, Tue-Thu 10-12 PM Speiser, Thu 2-5 Ravin.

A ruling was made by Libcomm chair that, in the event library books are lost by members, they may be replaced by other books at the discretion of the Librarian.

Millermotion: Ravin, Simon. 6:00:00 by an overwhelming landslide which Skinner forgot to count.

\vspace{12pt}

\centerline{This trash by}
\centerline{Jon Ravin, Secretary}
\centerline{as always.}

\end{document}