\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 20, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Omshonock (Martian for "Man with long horns") Skinner called the meeting to order at 5:11:03 Generalized Relativistic Time. After the Secretary read the (accurate) minutes of the previous meeting, a few childishly immature individuals tried to criticize his beauteous prose and literary wit. (Like I think they're jealous.) Anyway, the Secretary, with some help from our hopelessly mature ex-Secretary, the most noble Anthony Richard, Lewis of Lewis, Lord of Libcomm, agent of Boskone, and also the force of many years' traditions, was able to get the minutes approved without correction, as usual.

Ho hum!

\goto{Committee Reports}

Treasurer's Report: No report.

Libcomm: Lewis read a list of donations by Hoylman, and repeated it when Hornexcums (Skinner- read Flesh by Philip Jose Farmer if you don't get it- it's actually a compliment) rudely interrupted him. Spent infinite money; we owe him 25.19; we are now on Brad Day's mailing list. Color swatches were received from the binder. Estimated cost of binding all ASFs: about 260 dollars (at 4 dollars a volume, including printing). Will see what price library can get for us.

At this point Speiser queried about the microfilms and Lewis gave the standard spiel in regard to the library's system regarding the viewers.

Theftcomm: Posters up. The Lensch wants comments.

Moocomm: Here, no report. Skinner offered the following list of movies: Alice in Wonderland, Phantom of the Rue Morgue, Dr. Jekyll and Mr. Hyde, King Kong (gahh!), Forbidden Planet (hurray!), The Day the Earth Stood Still (best), Them! (a good monster movie; one of the earlier ones), Tarzan pictures (good grief!), World is Born (from Fantasia). We are still attempting the Flash Gordon film, says Lewis, speaking for Schildcomm.

Jourcomm: Has about an issue ready. Morris wants coolies. It was suggested that he wait 'till Nov 10 so that the exec board would be able to help.

Tablecomm: Claimed some progress at their meeting. To quote Norwood- "So what?" Next meeting Monday at 8 PM in 5-203.

Smocomm (Ravin speaking for Smocomm): Letter has been sent to J.W.C.- we await his reply. Simon's telephone number is UM4-9107.

War Council: Quiescent.

Vengeance Fleet: It was mentioned that the Kentaylor has some books from Brodsky.

\goto{Old Business}

None!

\goto{New Business}

Morris wants ASF history from Viper, a Donaho fanzine; he was told to write and ask.

Skinner mumbled something about a list of books to be voted on.

Stranger in a Strange Land (R.A. Heinlein) should be gotten for the library.

Library hours: Sat L.A. Campbell, Sun Hoylman, Thurs me, Tues and Thurs nights Speiser (if he can get a key).

Millermotion (Gross-Harper). 11-6, 5:47:50, closing another chapter in the glorious history by

\vspace{12pt}

\centerline{Jon Ravin, Secretary, of course}

\end{document}