\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 15, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Skinner called the meeting to order at 5:11:40 Mean Institute Time. The minutes were read, and an overjoyed multitude of poetry lovers smothered me with words of praise for my beauteous minutes of last week's minutes. (With tears in my eyes I accepted their praise.) Oh, the sheer emotion of it all!

(The meeting was held in the Sub-Spofford Room, 1-211, since the real Spofford Room had apparently been stolen, or at least rotated onto the jw axis; it was inaccessible from the tau-plane. Mainly because it was locked.)

I am proud to report that Das Kinner finally took the hint and did not read from the Ancient Minutes; he's catching on. I wish I could say the same for certain other members of the Society.

\goto{Committee Reports}

Treasury: Balance stands at 299.37, excluding a minor fortune owed to TCA for the Journal, says Gross.

Theftcomm: Absent, no report.

Libcomm: More donations from Delightful Doug Hoylman. More new mags came in; more books were bought; a debt of 4.84 was run up. Lewis wants people to cover books. The library will not be open (officially, that is) over vacation. Lewis then stated that no one would be allowed to check out books. It was pointed out that those who had keys would, or could, check out books whether Libcomm liked it or not. Lewis didn't comment. Library fines will be suspended over the vacation.

Moocomm: Great Gho! Harper has a report. (Rejoice, ye tools, 'tis a once-a-generation event.) It consisted of a list of movies available, which is included somewhere in here.

Smokomm: Simon blamed Asimov for going to Johns Hopkins instead of coming to our smoker. I side with Simon. A pox on Asimov.

Tablecomm (Pearson speaking for Tablecomm): No report.

Jourcomm: 1) Some letters were received; Morris was reluctant to disclose the contents of same. Is this significant? 2) Bill for 4.18 was presented to our fair treasurer. 3) Hoylman has writ something for das Journal.

Knockomm: (Instantaneously reinstated when Skinner discovered that the gavel-plonker-onner was cracked.) The Gavel-plonker-onnee will see what he can do to remedy the situation.

(Note: This meeting was rather amorphous; Old Business and New Business were mixed in together.)

\goto{Old/New Business}

A motion was made (by the same clod who always does so) to dissolve the Society and redistribute, etc., but failed for lack of a second.

The infinite list presented by Harpercomm was winnowed down by the fine taste of Skinner to the following, which were then voted on by the memberate as follows:

Conquest of Space: 0

Forbidden Planet: 6

The Lost World: 0

Gorgo <-> Lewis

War of the Worlds: 14; the winner

When Worlds Collide: 4

X the Unknown: 0

MSD (Lewis, Pearson) that the Society request that Skinner resign in favor of Norwood. 2-19.

MST (x, y) that Skinner be given the Order of the Triple Suns, with 4 comets.

MSD (Humer, Simon) that Skinner be given the Order of the Triple Suns, with amendment as detailed below. 8-8, Skinner using his pocket veto.

ASD (Pearson, Lewis) that said award be given posthumously. 12-7.

Campbell inquired about Stranger in a Strange Land; Lewis said 'tis available cheaply only through the bookclub, which he was not authorized to join.

Lewis also mentioned that he has not subscribed to Analog. This is a clear violation of his duties. Obviously he does not realize that a mandate from the Society is (almost) equivalent to a memo from Schildkraut. Action should be taken, I say!

MSP (Pearson, Olsen) that if the SFS ever has 13 Megabux in the treasury, it shall donate 12 of the same to JRR Tolkien for the purpose of filming the Lord of the Rings. 12-8.

MSD (Lewis, Olsen (who seems to second everything)) for a roll-call vote on the previous motion.

MSP (Lewis, Ravin): "I so move." 9-6, at 5:56.

\vspace{12pt}

\centerline{That's all for today, kiddies!}
\centerline{Jon Ravin, Secretary}

\end{document}