\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

The Picnic

Sunday, May 14, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
On Sunday, May 14, the Society held its annual banquet in the form of a picnic halfway up a hill in the Blue Hills.

In attendance were Isaac and Gertrude Asimov, with their progeny Robyn (6) and David (9 or 10).

Also present: Steve Whealton, Court Skinner (who gets a gold star for coolie work above and beyond the call of duty), Fred Isaacs, Bernie Morris, Norm Humer, Jon Ravin, Fred Norwood, Bill Osten, Durk Pearson, Glen Books, John Harrison, Bill Sarill, L. Andrew Campbell, and two random freshmen whose names I do not know (Doug Hoylman and Marty Slade).

Coeds present: Deanne Gross, Pat Morris, and Sandy Lensch.

We managed to eat nearly all of the food.

Asimov, as usual, told some horrid puns. At one point, he was challenged to a PUNishing duel by Whealton, but vanquished his young opponent easily with a remark about the "Dean Derive" (referring to a mathematical proof of the Dean Thing).

A group of very sick individuals decided to climb to the top of the hill, and they did. The fools!

Freddy and Pat went off together to study under a tree. Honest.

Norm and Sandy went into the woods. I don't know what THEY did. No doubt to explore. Hah! ...I'm jealous! Dammit!

Court went into the woods with Robyn. Twice.

All in all, everyone had a good time. Perhaps this ought to be tried again next year.

\vspace{12pt}

\centerline{Signed, sealed, and delivered by}
\centerline{Jon Ravin, Secretary}

\end{document}