\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 10, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Skinner the Noble called the meeting to order at 5:17:45 Galactic Daylight Savings Time. He wasted time reading some minutes from previous meetings- 1951, to be exact. What a waste of time! I would soliloquize on the uselessness of his doing this, but I won't. Mainly because he's giving me a lift home Thanksgiving.

\goto{Committee Reports}

Treasurer: No report.

Moocomm: "Moo."

Libcomm: "Lovely" Doug Hoylman donated some more trash to the library. New mags in: New Worlds. The Pick-a-Book Pick a Book Book for the month is some minor thing called the "Gray Lensman." It will, perchance, be purchased. The blacklist was read again.

Jourcomm: Typing (stencil) tonight. Volunteers: M. Wisowaty, Morris, of course, Olsen, "Cookie Killer" Skinner.

War Council: Quiescent.

Theftcomm: Posters not up. Execute Lensch!

Skinner was asked why we are not listed in "Preview." He failed to give a reasonable answer. Execute Skinner!

Smokomm: Asimov's letter was read, a vote was taken- Asimov by acclamation!

Tablecomm: Next meeting Tues at 8 PM in 5-231. Norwood made a fool of himself.

\goto{Old Business}

Library hours: Sat 2-5 Lewis, Sun 2-5 Lewis, Mon 11:30-1 Gross (if possible), Thurs 2-5 Ravin.

\goto{New Business}

None!

MSP (Ravin, everyone), 12-8 at 6:00:00.

(1, 1, 0, 0, 0, 0, 0, 0)

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

\end{document}