\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, February 10, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1710 back in room 1-236 again. The minutes were read and approved.

\goto{Committee Reports}

The treasurer reported a balance of 362.39.

Moocomm: a discussion pro and con "Roadrunner" was held. It was inconclusive.

Libcomm: new shelves have been painted by Skinner, Whealton, and Ravin. Magazines are being put on the shelves. Library will be open on Sunday from 14 to 17. Return long overdue books or Vergeltungsflotte will spring into action.

Theftcomm: absent.

War Council: no report.

Jourcomm: maybe we can get The Shape of Things to Come for the next term movie. The Journal was published and distributed. Letters from Wilson Tucker and Algis Budrys were read. The circulation of Analog is 74,000. Jourcommedal of Honor is awarded to all coolies.

\goto{Old Business}

McDowell's mimeo was mentioned. Lewis will check up on Monday.

Money for Wenker.

MSP (Ravin) that we pay Wenker the 200 dollars now and liquidate our debt. 20-2-(1+i).

Torn screen: Norwood made a fool of himself. Court will ask the janitor to fix it.

\goto{New Business}

Insurance on books. Pearson gave Court an address.

Binding: the Heckman Bindery will bind up to 10" height for 3.50 (with 7 lines of printing).

A discussion of a telephone for the Library was held. Kentaylor will look into it.

MSP (Lewis) at 1756, 18-1.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}