\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, February 17, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1710 by Skinner in the old stomping grounds. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

The treasurer reported that the treasury now stands at 154.41. The 200 dollars has been sent to Wenker to liquidate our debt.

Moocomm: Duff, in his usual mood of righteous indignation, expressed some of LSC's views concerning our film. They disapproved of our method of advertising. NOTE: The L stands for "LECTURE."

Libcomm: return overdue books or the Vengeance Fleet will strike. Humer will have the library open Sunday.

Theftcomm: posters up.

War Council: no report.

Jourcomm: another letter was received from Ayjay Budrys with the promise of an article. Isaac Asimov will be in the Little Theatre Wednesday at 1700. Everybody should go.

\goto{Old Business}

Telephone: officially there are no spare lines. Unofficially WiTiBuS will be having more cable strung so we may be able to tap in. Also there is a private independent line in E.C.

Lewis tried to see McDowell about the mimeo but he was not in.

\goto{New Business}

MSP (Duff) at 1735, n-1.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

After the meeting a tape of Dr. Asimov reading his paper on Thiotimoline and the Space Age was heard.

\end{document}