\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 3, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Chaos was ordered at 5:12:37 BST (Boskonian Standard Time). It arrived.

Skinner read some more from the great book; some more drivel from 1951. Skinner made a kumquat of himself. Which is a pretty neat trick, you must admit!

\goto{Committee Reports}

Treasurix' Report: Gross said FinBoard wants a report on our financial status. The memberate voted to tell FinBoard what it could do. And they meant it.

No money was spent- Lewis was quiescent this week.

Tablecomm: No meeting last week (thunderous applause at this point) because "borrowed" stuff was recovered from Sarill, the thief of BagBay. Next meeting, unless X shows up again, will be Tues at 8 PM in 5-203.

Libcomm: Donations received from Ken Taylor. No expenses this week (please note). Edward V. White covered 11 books, the crazy fool! Ring is covered. Lewis read a list of those in purgatory for holding books.

Moocomm: Forbidden Planet is out of release; an impromptu vote was held. The memberate voted thus: Them!- 10, Operation: Moonbase- 6, Invasion of the Body Snatchers- 5, The Blob- 3, The Fabulous World of Jules Verne- 1. We will probably get The Fabulous World of Jules Verne.

Jourcomm: Nov 10- TZ! Coolies needed for Friday night and Saturday; volunteered were Skinner, Humer, Ravin, Olsen, Wisowaty, Morris, Gross.

Smokomm: No news from the Campbell fronts of the world; will contact Asimov, or rather, the Secretary will do the same. Simon is LAZY.

Theftcomm: "Posters up."

\goto{Old Business}

Lewis introduced that world-esteemed author and shrinking violet J. Martin Graetz, who brought with him some books the Society'd been missing for a long, long, LONG time.

\goto{New Business}

Lewis got a letter. We are not allowed to operate with women in Walker at t>2400, says Dean McDowell. After the comments ("But we operate on COEDS...") died down, the principle was more or less agreed to.

Norwood made some nasty comments about Lewis' purchase of the Ring cycle; claimed AR paid too much for them. He's just jealous 'cause he didn't get a cut.

Library: Sat 2-5 Campbell, Sun 2-5 E. White V, Mon 11:30-1 Deanne (The) Gross, Thurs 2-5 J. Ravin.

MSP (Ravin, Lewis), 5:50:00.

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

\end{document}