\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 10, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1713 in room 1-211 due to a mixup with the key. The minutes of the previous meeting were read and approved.

\goto{Committee Reports}

In ye olde treasury resideth 170.14 and 2 new members. Verily!

Moocomm: no report.

Libcomm: Wm's are ready to be checked out. Most of the ASFs are ready to be checked out. New tape and bookends have been purchased. The Library will be open during the usual hours. A book (hardcover) from the past has been located and will be back shortly (we hope).

Jourcomm: a letter of comment was received from Marion Zimmer Bradley.

War Council: a letter was received from McDowell saying that the mimeo was given to VooDoo. Court checked up on bookcases but could not find suitable ones in the right price range.

Theftcomm: absent.

Tablecomm: posters are up. Maybe mailboxes will be stuffed. The discussion is in 50-110 on Monday at 1900.

\goto{Old Business}

Fan IES meeting tomorrow night. Go if you have no quizzes.

\goto{New Business}

Lewis gave a report on his research into the numbering of buildings at the Institute.

MSP (Ravin) at 1738, 9-8-2.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}