\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, January 6, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 1717.

\goto{Committee Reports}

There is 79.49 in the treasury, says the treasurer.

Libcomm: 1 set of H.G. Wells novels purchased. Norm read a review of New Maps of Hell.

At this point Lewis entered and took over the minutes from Kentaylor.

Schildkraut built a bookaze for us. Koolies are needed to sand and varnish.

The minutes were read and approved.

Moocomm: 19 January 1961 is the date of the movie. Publicity for movie: Tech Student Calendar. Volunteers/takertickets- Whealton, Lewis, Skinner, Hoeper, Ravin, Day, Lensch, Gross? Show up at 1800-1830. Shall we charge 25 cents?

MSP (Humer) that we charge 30 cents for nonmembers. 19-1. Show at 1830, 2130?

Theftcomm: posters up.

War Council: no report.

Jourcomm: Tablecomm transcriptions on tape should be typed. 15 Jan is the deadline. Meet 2 Fridays from now (20 Jan) to work on Journal. Letters have been sent and received.

\goto{Old Business}

Lovecraft? No!

Sarill? Yes!

\goto{New Business}

Ravin wants to sell book, no!

78 Pb, 15 booklubs now donated free.

MSD (Duff) to Millerate at 1753, 7-8.

MSP (Hoeper) to Millerate at 1756, 14-3.

\vspace{12pt}

\centerline{By}
\centerline{ARLewis, Secretary}

\end{document}