\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 6, 1961

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Deep in the pit the monsters lurked, waiting for the victims who they knew must come. Slowly, ever so slowly the men-things came into the trap. Soon, so soon would they taste of death and defeat. For the leader of the monsters raised one of his (its?) horny paws, and...

Skinner called the meeting of the 6th of October to order at 5:15:30 Eastern Relativistic Time.

The minutes of the previous meeting were read and approved without correction, as usual.

\goto{Committee Reports}

Treasurer Report: +9 dues, -1.69 misc expenses, for a grand total of 351.60.

Libcomm (Lewis speaking for Libcomm): Donations- Humer- a mess of ASFs, Williams. Additions to library- The Drums of Tapajos (S.P. Meek) and Rim of Space (A. Bertram Chandler). Speiser will keep the library open nights, late. Lewis wants to subscribe to New Worlds and Science Fantasy, 2 good British mags. Lewis wrote the binder in Indiana about swatches of material. He doesn't want to traffic with Portugal's Fascist regime.

Jourcomm: Morris handed out a poop sheet. He wants material. (When I was Jourcomm, I wanted stuff too, Bernie, but...)

Moocomm is Martha Harper, Court says. But I don't believe it, since she wasn't here. We have Kresge for last day of classes.

Theftcomm: "Posters up," quoth the Lensch.

War Council: Quiescent.

Vengeance Fleet: In port, being overhauled.

\goto{Old Business}

Well, since the Secretary finally got out the notices, the election was held.

Nominated (for V.P.) were: E. White V, Morris Simon, and Fred Norwood.

The vote:

1st ballot:

Simon 6, Norwood 10, White 7, Plant 1, Abstention 1, If I weren't [illegible]... 1, Dearest Court 2, total 28.

2nd ballot:

Simon 6, Norwood 7, White 8, Abstention 1, Morris 1, Mentor 1, Stratton 2, Dearest Recorder Player 1, Dearest Plant 1, total 28.

3rd ballot:

Simon 2, Norwood 7 1/2, White 15 1/2, God 1, The Other Guy 1, Plant in S.E. Corner 1, Mr. Maturity 1, The Good Doctor 1, total 30.

Ed White won, as the tally shows. The freshmen rioted, but Norwood remained a loser.

Chaos for a short time.

MSD (Burrows, Nolan) for a revote. 6-20.

The Secretary made a beautiful and eloquent speech denouncing 1) Norwood and 2) Robert's Rules. He received an ovation from the more elderly (mature?) section of his audience.

Norwood then announced the first Tcomm meeting for Tues at 8 o'clock in 1-236.

\goto{New Business}

Library: Sat Hoylman, Sun White, Tues the Noble Secretary.

It was so moved (Ravin, Lewis); 22-1-Krupp at 6:03:07.

\vspace{12pt}

\centerline{The Ravin, Secretary}

\end{document}