\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

An Official History

Friday, January 16, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Before the meeting began, the Skinner had some Serious Business. He was concerned at the lack of work being done by the keyholders in the library. He was concerned that he was going in a few months, and so in his place there would be left a vacuum. As is well known, nature abhors a vacuum. In fact, nature abhors a Skinner. What is a "Skinner"? Today, as I give the minutes, I shall explore the tradition of Skinnership, the myth behind the man.

The first recorded Skinnership began when Matthew Basingcroft Skinner, the Englishman who was destined to shock the foundations of Europe and give new meanings to the word "pistachio", called the meeting to order at 5:00 SST, in the year 1658. This brilliant stroke of the gavel, coupled with the subsequent approval of the minutes as read, plus a spurious pseudo-Lord High Embezzlers report of 812.32 dollars, assured his place in Western philosophic thought. Often overlooked, however, is the whimsical verbal bagatelle which depended from the boyish lips of the vice, Horatio Wollingsbeake Stevens, to wit: "Move to commend Mr. Wechsler for doing in his seven months as Jourcomm what it took me two and a half years to do." Louie "Raffles" Hitchcock, a noted highwayman, cutpurse, and wartime Pindex runner, moved to place said motion (i.e., Stevens') into Old Business Algol until the feverishly awaited printing of TZ 29 (at that time known as "TZ 29", or the "castle in the air"); the motion passed. But now, let us review the Skinner's life.

Matthew Skinner was accoladed with pretensions of precosity at the tender age of eight when, to the edification of his parents and siblings, he recited a pseudo-ROSFAP report, reviewing a general displacement of the fanzines (or, as he put it so quaintly, "switched them around"). When he later surprised his Uncle (who was at the time enjoying a tete-a-tete in the pantry with the upstairs maid) with the information that a random A to 0 fanzine want list had been prepared, it was decided the time had come to go to school. He left for Edinburgh to join the Royal Academy of Shelves, where he met Isaac Newton (who, under the pseudonym 'Stevens' gave a pseudo-Moocomm report, quote, "Robinson Crusoe on Mars."); and in addition he became friendly with Galileo, who did not at that time expect the Italian Inquisition, having been dead for several years. The heady perfume of old pubs and new women suffocating his callow cranium, Skinner fell into the bad company of the odious Hitchcock, who, in a pseudo-MADcomm, confided with elan that we flung the comic books.

War descended on England with a rapier-like thrust, and all and sundry thought it might be the long-awaited Hundred Years War, but closer examination showed it to just be the War of the Roses; and so Matthew Skinner and his wonder dog Hitchcock moved to Newcastle, whilst everyone else moved to Old Business Algol. In this venue they were eye-witness to a ruthless overturning of the French nobleman, Gerard Rouchambeau Onseck; befriending him, they put him gently back in his nest and bandaged his wing. In a fit of pique (not Pike's) Hitchcock announced in the village square "Larry Niven made a pass at Fuzzy Pink and was not repulsed." This daring pronouncement attracted the attention of the finest minds in Sri Lanka, who in a fit of religious fervor swore fealty to Matthew Skinner, and so directly precipitated that memorable, faith-shaking meeting of 1658. Now to return to that meeting:

Skinner announced their penetration into New Business. He moved to rotate Stevens on a banana, which passed 1500 to 0000 to the serial number on Pinette's chair, and the meeting adjourned, never to meet again. Matthew Skinner dropped into obscurity. He died in 1669, completely penniless save for a box of paper clips and a large vault of gold bullion.

\vspace{12pt}

\centerline{Historically,}
\centerline{Gary Goldberg, Onseck}

\end{document}