\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Minutes

Friday, February 27, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The Onseck entered the Spofford Room and immediately dissolved. Trying to grasp his new situation, he realized his composite atoms were now spread throughout a five-dimensional hyperspace of incredible complexity which twisted back on itself and reversed the inside-outness of its intertwined geodesics. Sensing the presence of other beings, the Onseck asked with his mind, what happened?

A thought pulse came back at him like the voice of God (2500 kHz)- the Skinner. It's the MITSFS organization, he explained, it's gotten too complicated. The last committee we added caused it to become so convoluted that normal space couldn't hold it, so the Spofford Room dropped into hyperspace.

Don't worry, thought the Onseck; as I have complete control
over external reality I can put us back to normal in a jiffy. All I have to do is write:

The Skinner banged down the gavel at the stroke of 5:00 PM SST. Wechsler had brought a guitar to the meeting, and played the 1812 Overture with the gavel's sound effects. The minutes were read with musical accompaniment and approved. The members for some reason started quoting Shakespeare, the Skinner reciting: "Tomorrow and tomorrow and tomorrow, the MITSFS meetings creep in their petty pace to the last syllable of recorded minutes. And all our tape recorders have uttered fools the way to boring meetings." Pseudo-LHE RHB: 700 dollars. Pseudo-Sitcomm (Stevens): Gene Roddenberry was dragged to the library last week, was duly impressed, signed a couple scripts, and may return in April. Stevens also reported the head of the Telecommunications Symposium will hand Arthur Clarke our letter when he (Clarke) leaves the plane.

Jourcomm_1/1 (Wechsler) strummed his instrument and sang:

"M-I-T S-F-S

Twen-ty-nine T-Z

R-S-N... R-S-N...

Forever meaning never, RSN."

(to the tune of "Mickey Mouse")

Pseudo-Moocomm (MTT) noted the Globe had reported on the Orson Welles "sci-fi" marathon: over 400 out of 630 fans stayed the full 24 hours. The theater staff was caught unawares, and "spent the wee hours buying up pastries around town, borrowing edibles from other restaurants and hunting extra cases of champagne;" said the manager, "What I really underestimated was the serious dedication of the science fiction fan."

Fweekcomm (Stevens) said we'd been cheated out of 100 of our 150 lines for the Freshman handbook. We crawled into Old Business Algol and Stevens jumped out immediately with a motion to censure that man for his sex life with his thingie. (Wechsler and guitar, that is.) This passed "it seems we're in accordance on this" to a waste of time to "put it on the gavel block." With Wechsler's accompaniment, Skinner and Onseck rendered senseless the Ode to Joy from Beethoven's 9th. MTT noted, "Boskone 14, Real Soon Now." Goldberg reported, "25th anniversary of MITSFS, March 16."

Into New Business: Minicult (MTT) showed another Electric Company cartoon, but this drawing of MIT was not as good as the first one- there is no wastebasket. Minicult (RHB): he said that in the United States there exists a university foolish enough to offer him 7000 dollars to go there. Stevens moved to commend the university and to hope in fact he does go there, which passed by Stevens's count of absolutely unanimous to "Bernstein isn't even opposed" to the taxpayers paying the 7000 dollars. Skerry moved to prepare for the fall of western civilization.

Moving to more serious matters, RHB moved to censure that "gentleman" for his sex-life with Campbell's Astounding Chunky Soup Mix. When Hunnel confessed to having eight cans of it in his knapsack in the library, Stevens moved to censure him for polycandry.

Minicult(RHB): The Skinner having berated him for having a penguin on his shirt, thus associating him with yacht clubs and golf carts, the Onseck attempted to acquire a more agrarian image by embroidering a pitchfork in the penguin's hand. RHB noted "Penguin with Pitchfork" is a new work to be constructed near East Campus. In the same vein, Stevens moved to paint Transparent Horizons transparent.

"Department of Useless Facts Department" (MTT): here's one--
sum from i=0 to 1374 of (0.99)^i is 99.999900 (after 6 VM, sum to 2000).

A motion was passed to move Uri Gutman under a broken light fixture so that it would eventually fall on him. Minicult (Skerry): There is a variety of mold known only to exist in one environment: felt beer mug coasters. Minicult (Hitchcock) announced the invention of the "noise-emitting diode," which emits a loud noise just once, when 1000 V or more is put across it. It was invented by Ivan P. Strugando, who became famous for attempting to filter AC with an electrolytic capacitor and who was known for years as the inventor of the "confetti generation." RHB moved to note a noise-emitting diode cam be made by strapping Hitchcock across 20,000 V at 10 A, and to try the experiment.

When RHB inadvertently referred to MTT as "Hitchcock" , he left the room in a huff. Suddenly, a door moved by an unseen force, showing a spirit presence; RHB muttered a few incantations... and abruptly Mike Timmreck appeared. "Thank you for bringing me from 1974," he cried. "Now it's time for a decent meeting. Is there a Millermotion on the floor? I have a vote of 12-6-6, it's a tie; what am I offered to break the tie?" As he looked around, sure of himself, Bob H. Bernstein rushed up. "I have a proxy!" he cried. "Forty-two of them!" MTT flung down the gavel with disgust, and the meeting adjourned.

\vspace{12pt}

\centerline{And you were there,}
\centerline{Gary Goldberg, Onseck}

\end{document}