\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Invasion of the Dreeps

Friday, February 20, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The Vice looked startled. "What was that?"

"What was what?" said the Skinner, gavel poised above his head, weight carefully balanced on the chair.

"I thought I heard a... a sound."

"A sound? What sort of sound?"

"Well," said the Vice, "sort of a... 'dreep.'"

"Nonsense," pish-tushed the Skinner, and swung down the gavel. "Meeting is called to order. Let's hear no more 'dreep' foolishness."

The Onseck read the minutes of the previous minutes. Jourcomm/2 (Wechsler) said that the fabled TZ 29 will be out for his birthday. His birthday will be Real Soon Now. Pseudo-LHE (RHB) said we had maybe a little over 700 dollars in the bank; Brad Schaeffer asked if he could have any of it. Goldberg moved we accept no money from Brad Schaeffer, which passed the total profits of General Motors to 1/number of people starving because GM's raking in all our cash to what's good for the USA (plus a little political commentary). (Remember, MITSFS acts on none of the motions it passes.) Wechsler moved to censure Random_1 for not voting, and Random_2 for only voting once. After the vote, Random_2 was censured for not voting, and Random_1 for only voting once; we censured all the other permutations and combinations. Pseudo-Libcomm Gindin observed, "He isn't here yet."

Wechsler suddenly bolted from his chair and stared out the door. After a few moments he shakily sat back down and smiled nervously. "Thought I heard a dreep," he said.

We moved from Old Business into Old Business Algol: Pinette
noted Uri Gutman is still trying to get a key.

In New Business, Stevens said his letter to Arthur C. Clarke came back stamped "Addressee Unknown"; this was strange, as this was the address MIT had been using to contact him for the conference. Minicult (Wechsler) : After reading Kuttner's Robots Have No Tails, he had a dream you could guess (robot singing at meeting). Where is the comic book? RHB didn't bring it- Doc Strange 15. Boskonecomm (RHB)- We got some stuff, and now have a complete set of Amazing. The Society noted, "Wow, that's amazing!" Minicult (Stevens): Gene Rottenberry is speaking tonight.

It was unmistakable now. From outside the doors, from the
window, from the ventilators, came a clear, intermittent "dreep"; a "dreep" that grew noticeably in intensity at each chirp. The members could feel the panic welling up, and kept looking quickly over their shoulders. Hitchcock stared wide-eyed at RHB and said in a small voice, "Mr. Skinner, I'm scared."

The Skinner licked his lips. "Balderdash!" he spat. "On with the meeting." Libcomm (RHB) reported some fool donated the Star Trek Technical Manual. Hitchcock and Onseck made ritual threatening gestures, but no one was overturned. The first Miller Motion failed. Minicult (MTT): Anne Elk now has a second theory: "Fire brigade choirs seldom sing songs about Marcel Proust." The first theory was, "Brontosauruses are thin on one end, much MUCH thicker in the middle, and thin on the other end." Minicult (RHB): Marvel Comics has announced a new title: "The Prisoner." The Vice noted, "I am not a number, I'm a free man!" Hitchcock asserted, "I am not a number, I'm a vector!" Goldberg moved to note that a "vector" is medical terminology for the carrier of a plague.

An ear-splitting "dreep!" cut the air. We all sprang to our feet, except the Skinner. "Sit down!" he ordered. "You're all scientists- surely you don't believe in this superstitious nonsense."

"You mad fool!" cried the Onseck. "If you don't adjourn the meeting, I will!" He made a grab for the gavel.

"Minicult," interrupted a calm voice. It was Timmreck, an island of sanity in our madness. He said, "I have heard an interesting new theory as to how the crack in the Kresge dome got there, from one Mr. Uri Gutman. He says it was cracked due to the low note on the organ." RHB moved to note Uri Gutman's organ is on a low note, and cracked- and banana colored! added the frightened membership. The vote could hardly be overheard over the incessant, piercing "dreep, dreep, dreep," but it was High C to "The Sensible Drink" to "How about a nice Hawaiian punch"- meeting is adjourned! We ran, screaming, out of the clutches of the hideous dreeps, never resting until we made the safety of the library.

\vspace{12pt}

\centerline{Dreep,}
\centerline{Gary Goldberg, Onseck}

\end{document}