\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Minutes of the MITSFS

Friday, April 30, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Despite everything the doctors could do to speed the process, the Old Skinner still had not died when 5:00 came around. He lay there, arranged decorously on the gavel block, waiting for the end with a look of tranquil, contented, naked panic on his face.

Around him in the richly appointed Spofford Room, the College of Ordinals of the MITSFS were worriedly met to appoint a successor to Bernstein XVI.

"My God!!!" screamed the figure on the gavel block. "I'm dying! I don't want to die! I don't want to be deceased!"

"Shut up and die like a good Skinner."

"No!!" he yelled. "There is no God! I'm headed for eternal oblivion!!"

"Life's tough," they said. "Now shut up and call the meeting to order. It's time."

The Skinner, his strength waning rapidly, feebly hoisted the gavel and tried to pound the gavel block, forgetting that he was lying on it.

"Oopgh," he said, weakly. "Meeting called to order."

The Onseck read the minutes of the previous meeting with one eye on the dying Skinner. He was grinning inside. It felt strange.

"Vulture," croaked the waning dictator. "You're just WAITING. You've been waiting for a long time. You're just waiting for me to go."

"Right," said the Onseck, "so why don't you do us all a favor?"

"Don't let the peasants hear us arguing like this," said the dying despot. "Let's have Committee Reports."

Roving Photographer Stevens humored the old man with a report that he had some prints of photos taken two weeks before of an alleged incident involving an alleged pie and an alleged face, which were placed on an alleged table for the alleged members to look at, it is alleged.

Wechsler reported some depressing news about Pie Proliferation, and the increase in the number of countries possessing a first strike capability with tactical whipped cream pies. The fading Former reminded us in a trembling voice that MIT was training 23 Brazilian engineers to build whipped-cream diffusion plants.

Pseudo-pseudo-LHE Nussbaum surprised everyone by being there, and reported 20something dollars cash-on-hand, about 600 dollars remaining, split up confusingly between two bank accounts, with some other money elsewhere, and completely incomprehensible as the Electronic Onseck was munching potato chips at the time.

Rubbing-shoulders-with-the-grapecomm Wechsler reported that Peter S. Beagle had visited the library and signed his books.

Pseudo^3-LHE Ginden reported more money coming from finboard, at last.

Jourcomm Wechsler reported that Ginden had given him the keys to a hot typewriter, and that he had twenty pages of TZ typed, and would finish RSN.

The unmentionable tried to give a Moocomm report and was duly shouted down.

Pseudo-Moocomm Nussbaum warned us of Rollerball.

An inverse Ross motion on a ceremonial saucer passed unanimously to a groan to gobble-gobble and a punched card. It was done. The skinner grinned a little and then remembered he was dying.

Picniccomm Goldberg reported the picnic day after tomorrow. The Skinner realized that he wouldn't be at the picnic and reflected that there were some good things about dying.

Feeling the cold hand upon his heart the Skinner railroaded us through OB and into OBA, and thence into NB where Stevens tried to hold up the show with a Minicult. According to the Tech, there was going to be a rappelling demonstration by the MIT Outing Club down the south face of the student center.

Goldberg miniculted that in the same issue of the Tech was a nice picture of our LHE covered with cotton candy.

Finally the Skinner got around to his ritual instruction of the College of Ordinals on voting procedures. With the passing of the Skinner the entire Star Chamber would be replaced, and about time, too.

Nominated for President: Gary Goldberg, Marc Alpert, Brian Pinette, Sylvania 9400, Howard the Duck, Dr. Steven Strange, Amuletos Y. Talismanes, the late Ethylbert Apple, the electronic Onseck, the Dreep, the knights who formerly said Ni, the Spanish Inquisition, Michael T. Timmreck, Bob Bernstein XVII, Blob Bernstein, and Nominations B. Closed.

Events suddenly became confusing. Goldberg moved lengthily to impeach the dying Skinner. The Skinner responded by resigning, and somewhere in between he managed to grant himself a complete pardon. Thus passed Bernstein XVI, not with a bang but a simper.

The gavel passed to the acting president, Jack Stevens. The members impeached the dead Skinner again, this time with a vote. The new acting president appointed himself Skinner and tried to cancel the election, but was laughed out of office, ha-ha.

Gary Goldberg was elected president on the second ballot and appointed himself Skinner. He was thus a former Onseck and was attacked. He fended them all off single-gaveledly, though.

Nominated for Vice were: Gregory Ruffa, Marc Swanson, Teddy Kennedy, Russel Seitz, John Fitzgerald Canaveral, the dead Bernstein, Tom Gindin, Jack Henry Stevens, Chang-hsi, Autumn Fizz, Paula Lieberman, and Nominations B. Closed.

Stevens was elected on the first ballot, naming the bitterly bitter Gindin his Vice Vice.

Nominated for Lord High Embezzler: Nick Nussbaum, Brian Pinette, Charles Milton Spofford etc., Thomas Jefferson, George Eastman, a Blue Flair Pen, Ayn Rand, the Giant Mind, Al Schuster, and N.B. Closed.

Brian Pinette won on the first ballot.

Nominations for Onseck: Allan Wechsler, Lois Lane, Bill Starr, Bob Bernstein, Super-scope C-108, Skinners of various tenses, B.F. Skinner, Jonathon Livingston Beagle, Super-pro frisbee, Rosemary Woods, Bernstein and Woodward, and Nominations B. Closed.

Wechsler was elected on the first ballot.

The meeting was adjourned amid renewed attempts to overturn the former Onseck, and the members dispersed, their grumbles increasing in volume as they looked at the crown behind the table and, oh so slowly, began to realize exactly what they had done.

\vspace{12pt}

\centerline{Despicably submitted,}
\centerline{Allan C. Wechsler, Onseck}

\end{document}