\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

It's Howdy MITSFS Time

Friday, April 16, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Fade in on a flying orange pie-shaped object. It is a frisbee, and the members are having a jolly time jumping around the Spofford Room, tossing and catching it. Soon the rest of the kiddies traipse in, led by a pied piper. They settle down and the camera centers on the pious president, who bangs the gavel and orders the fun to begin. The beloved opening ceremony is performed, i.e. the reading of the minutes and the pseudo-LHE report of just under 500 dollars. The pie-eyed Libcomm-in-exile says the shelves are here, filled with books, and they're battleship grey, and Grantcomm (who is actually the same person) says we got all the finboard money we wanted, although 200 dollars for TZ must be picked up next year. These dull proceedings are gotten out of the way quickly, lest the children get restless, and a voice-over with canned music announces it's OLD BUSINESS ALGOL TIME! Immediately the camera swings to show Brian Pinette (pronounced PIE-net) enter wearing a purple tie with piebald pants and carrying a cream pie; everyone screams with delight. Pinette seats himself comfortably, removes a fork from his pocket, and begins to eat the pie. Camera pans back to reveal the children's favorite, Hitchcock the Pirate (in round red nose and green wig) sneaking up behind Pinette. Hitchcock then smashes pie into Pinette's shirt, but does not get enough on it; Pinette springs up and moves back with still-intact pie ready for hurling. The two face each other menacingly as the children all hold their breaths; but the pie-faced Skinner takes control and demands Pinette relinquish the pie, which he does, and the Skinner pirates it to the t*bl* (which is not pine); Skinner then brings up gavel in pretense of intention to smash pie. Pinette tries to grab pie away, and by misfortune slides it off t*bl* and into his left knee, completely covering it with cream. Hitchcock roars with laughter and attacks Pinette, who defends by hurling rest of pie into Hitchcock's face. There is now a montage of shots as Hitchcock flings pieces of pie back at Pinette, mostly missing (as his glasses are coated), and chases Pinette from room. This is the cue for Stevens and Skerry to leave, while the kiddies bounce up and down at delight of the antics. Close-up of Skinner as he organizes group once more and announces TIME FOR NEW BUSINESS! The old timer MTT entertains them with his wonderful adventures of how, after he was hit with a pie last week, he went back to his castle of Ashdown to take a shower, and found the hot water had been shut off... The announcement is made that big brave Bill Starr is away fighting the evil dwarf Harlan at Million Year Picnic, and has sworn to return with the troll's very own signature on a book of Deathbird stories. It is approaching sleepy-time, and the set lights are dimmed. The Onseck, referring to any one of several people, quotes the great American president Theodore Roosevelt, who once said: "I could carve a better man out of a banana." The Skinner says good night and closes the meeting. The camera fades out as the crew starts to clean all the pie off the scenery.

\vspace{12pt}

\centerline{Scenario by}
\centerline{Gary Goldberg, Onseck}

\end{document}