\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Waiting for TZ

A tragicomedy in no acts

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The curtain rises on the Spofford Room on Friday, March 26, 1976, shortly after 5:00 PM SST. It is a vacation, and consequently few members (played by Random O'Toole) are present. Behind an odd-shaped t*bl* sit the Vice (played by Marlon Brando) and the Onseck (played by Richard Burton), flanking the Skinner (played by Totie Fields).

The Onseck has just finished reading the minutes of two previous meetings, which are approved as read.

Pseudo-LHE (RHB): (Wistfully) We have 681 dollars in the bank, and no shelves.

Jourcomm (Vice): It's nice to know that in spite of the traffic in former TZ editors this week, we still don't have one.

Skinner: And I have a State of the TZ Address. It is being whipped into final form. Wechsler is writing it out in a form to be typed and done in photo-offset. I would seriously say two weeks.

RHB: (Seriously) Two weeks.

The members stare moodily at their metatarsals for a few minutes, wondering what to say next. Suddenly there is a rumble of thunder, although the sky is perfectly clear. The members ignore it. (And for good reason- I just threw it in.)

Shirecomm (RHB): We have 343 members... 1/3 freshmen, 14 percent sophomores, 12 percent juniors, 10 percent seniors, 57 randoms, and 4 other school people.

Stevens: (Movingly) Move to note that 1.8 percent of the 343 are actually attending this meeting. (Pinette walks in.) Make that 2.0 percent.

Pinette: (Eating bologna) Harlan Ellison will be at 18 Eliot St. April 16th, promoting his new album, "Harlan!"

Stevens: (Stroking a dreep) He won't visit the MITSFS unless he's paid.

The meeting moves through Old Business into Old Business Algol. This may be a difficult effect to achieve on stage, but a good light crew can do wonders.

Hitchcock: Joe Ross made a pass at somebody last week, but I didn't see it.

Gossipcomm: It was-

The following few lines were censored by Censor 54. They contained lurid, obscene, prurient, and otherwise naughty materials, including "How the Skinner wanted his phone bill paid," "Doing it at a party," and the word "Knockwurst."

Skinner: Usual vote. Any New Business?

The members again fall silent. Were they trapped to endure this for the rest of eternity? Was Life meaningless? A beautiful butterfly flutters into the room, and Uri Gutman eats it.

Goldberg: Minicult...

Skinner: (In heaven) Thank God!

Goldberg: Minicult- Isaac Asimov is doing tire commercials.

The Society: (With incredulity and ignoring any possible retaliation in the form of Finger Motions) WHAT?

Goldberg: This is true. He comes on, and there's a little blurb at the bottom of the screen that says "Isaac Asimov, Science Writer and Biochemist," and he explains how strong this tire material is.

Stevens: Move that Harlan Ellison sell-

The following few lines were censored by Censor 54 again. They contained a brief but detailed discussion on which elastomer product Harlan Ellison should sell and why.

Hitchcock: Boring minicult.

Skerry: Even more boring minicult.

The Society: Millermotion.

The Skinner counts the vote for the first Millermotion, which is "Goldberg for Skinner" to "You're going to have to make up some votes for this because I don't feel like doing it" to One haircutted chicken," fails.

The Society: Uri has no hair at all, hair at all, hair at all. Uri has no hair at all, just a lot of fuzz.

RHB: Second Millermotion. Let's get out of here.

Vice: We can't.

RHB: Why not?

Vice: We're waiting for TZ.

RHB: F*** TZ. And f*** Censor 54. (Everyone leaves, except the audience.)

FIN

\vspace{12pt}

\centerline{Gary J. Goldberg, Onseck}

\end{document}