\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Have Minutes, Will Sit

Friday, March 5, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
"You see, I had this space suit," said Ozzie. "How it happened was this way-"

But the members were not to hear that terrifying tale of the purchase of Oscar the Spacesuit from ILC Industries of Dover, Delaware. Nor would they hear an uninterrupted solo by Wechsler on a banjo. And last, they would never know what Brad Schaeffer really meant when he uttered, awe-struck: "Oh, you're Uri Gutman?"

For at that moment the old clock on the wall struck 5 PM SST, the gavel was banged, and the meeting called to order. The Onseck tendered his deepest regrets and informed the gathering there were no minutes that week; instead, he read out loud portions of the comic book, "The Man."

Pseudo-LHE (RHB) quoth "720 dollars." It was noted Wechsler's birthday was yesterday:

Members: "Happy Birthday to you, Happy Birthday to you, Happy Birthday dear Jourcomm-" RHB: "Where the hell is TZ?"

Jourcomm noted he was presently being treated for microjournalistic apathy, but that it should clear up by March 16th.

Pseudo-Libcomm Schaeffer gave a report in Albanian. RHB translated it as "Bruce Miller has taken a job in Denver and has left MIT forever."

There suddenly appeared before our wondering eyes a Photographer; and the Photographer spake, "Fear not, for I bring you glad tidings of great joy- there is come unto you a Photographer, born of Technique, who will snap your group. Arrange thyselves!" At this the members were much enthused, and did cluster by the altar; and the Skinner, being of divine birth, did hold on high the Wrench of Potency and the Orb of Nerf; and the assemblage did strike the pose of those at a last supper; and you, O my Oscar, did stand forthrightly behind the Skinner, with Ozzie inside you; and the Holy Photographer did shoot our group shot, and did vanish; and the members rejoiced and were glad.

We moved into Old Business Algol, where it was noted "50 more weeks til Boskone 14." Brad Schaeffer tried to give a minicult in Old Business Algol and was repulsed. Goldberg noted, "Bruce Miller will be forever skiing in Colorado."

Rocketing into New Business- Minicult (Wechsler): The new chem E building, the SS Ralph, was christened among much fanfare and singing, including lowering an anchor down the side; and he displayed a picture from the Tech of the building, which looked in the picture like a card about to fall over. Minicult (Goldberg): Visited Technique that afternoon, and discovered our officer's list was due December 20, 1975 (which we sent in and they lost, saith RHB); and convinced a photographer to come to take a picture of our meeting (after telling him Oscar would be there). Starr moved to note our bitter disappointment that the photographer never showed up; and Wechsler added that, however, a shaman did show up, and stole our souls in a little box.

Goldberg moved to create a special committee for Uri Gutman,
to be named after his initials, to wit: Ughcomm (the "h" stands for "hyphen"; short for UG-comm).

Minicult (Skerry): He reminded us of the variety of mold known only to live in felt beer mug coasters, then reported that a friend of his who works for a wine company assured him there is a type of worm that only exists in German beer mug coasters (no material specified). Said Malcolm, "I am beginning to feel surrounded."

Where are the comic books? Need you ask? RHB has brought many, among which are Hulk 200, Conan the Barbarian 63, Beer Mug Worm 1, and The Man by Vaughan Bode. The meeting was interrupted by the far off sound of a fire engine siren, which was seconded and passed.

Minicult (Goldberg) reminded all about Wechsler's immortal minicult of a few months ago, the Bryan Times of Bryan, Ohio, which he had found in Lobby 7. Well, this paper has been traced to its source- in Goldberg's dorm, but a few feet from where he lives, there exists a variety of freshman from Bryan, Ohio, who has a regular subscription to the Bryan Times. Skerry asked for a minute of silence; so the Skinner gave 60 gavel bangs, and Uri Gutman fell over.

The Onseck pointed out a very telling disparity in the names of the Star Chamber members--there's Bernstein, Nussbaum, Goldberg, and Stevens. He also noted the initials: B(ob)B, NN, GG, and JS. The Vice protested and said his first two initials, J.H., were the same as the first two of the hero of a novelized sequel to Cecil B. DeMille's film, "The Bible." But playing safe anyway he surreptitiously crept for the door.

It was moved that all people wearing spacesuits at a meeting should be taxed and locked in an airlock with a Klingon who has just eaten a pound of bananas. This tied, due to Oscar's strong lobbying, and Stevens Hero inched closer to the door. RHB moved to paint Jack in banana-colored invisibility paint so he can get out which passed, and the meeting was adjourned, praise be to Allah.

\vspace{12pt}

\centerline{Irreligiously,}
\centerline{Gary Goldberg, Onseck}

\end{document}