\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Minutes

Friday, February 13, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The curious little man in the impeccable gray suit and vest leaned over the Skinner. "That's right," he purred, tucking the points of his ears back under his Homburg- an interesting hat that had two holes in the brim for his horns to stick through. "Just sign there at the bottom, and you'll get all you desire- a mint condition set of Weird Tales, another of Doc Strange comics, an autographed copy of the Bible..."

As the Skinner was about to prick his finger, there suddenly appeared before them a man in a dazzlingly spiffy uniform. "Halt!" cried the stranger, and grasped the little man by the lapel and knocked him senseless with his truncheon. While handcuffing the fellow, he said to the Skinner, "I'm Lieutenant Zippl Gorg of the Time Patrol. This man isn't the devil at all, but one of our most wanted time criminals, Mike the Timewrecker. Sorry to trouble you." And he vanished.

"Darn!" swore the Skinner. "And I was looking forward to seeing Jules Verne at a Coop autographing session." He brought the gavel down and started the meeting. In Committee Reports, Timmreck said a Witter shipment had been processed and we had a new Pinkdex. Duckcomm (Wechsler) reported "it was the other one". (See meeting of 2/6.) He was censured for actually delivering a Committee Report.

Pseudo-LHE (RHB): "792.08." Cainfall-and-Other-Storiescomm (Goldberg): MacGregor has the big "A" from CAINS in their courtyard, and a dismantled "C" in the lobby. Jourcomm_2/2 promoted himself to Jourcomm_1/2. Pseudo-Jourcomm (Jerkcomm?) RHB: Has finished reading Perry Rhodan 85. Should note the Skinner is still alive.

Boskonecomm (Wechsler) noted with gladness that they are over there while we are over here. (Boskone 13 started Friday the 13th, and extended over Valentine's day to the Ides of February.) MTT noted "Boskone 14, Real Soon Now."

Into Old Business Algol, where Wechsler moved to note that
"Uri Gutman made a pass at himself and was repulsed;" this passed, oy vay to no one- who would be opposed? to one limp wrist. MTT moved to censure Hitchcock for his sex life with unlubricated listers. An attempt by Uri Gutman to report a "Minicomm" brought dismay upon the society. He was informed the correct term was "Minicult", and then a vote was taken to see whether or not we should hear his Minicult in Old Business Algol; then Uri Gutman was censured for not voting, followed by a recursive motion on Uri Gutman.

Minicult (Uri Gutman): He had charged 15 dollars to a pay phone when he called New York. I wouldn't be surprised if New York had hung up on him.

New Business at last! Where are the Comic books? In the Skinner's cherubic fist--a Fantastic 4, Avengers, and an Incredible Hulk. Minicult (Starr): An ex-convict wanted for 117 counts of income tax fraud was discovered to have been elected to two terms of the Michigan State Legislature under the name of an attorney who died in 1961. Starr made a motion which the Onseck refused to record, but a motion to make him write that down passed. Starr moved we get the description of the ex-convict to see if it matches that of any Skinners we know.

Minicult (Starr): Had an article on buycentennial kitsch, including a cake mold that enables you to bake a cake in the shape of George Washington's head. Skerry moved to give Starr 13 swipes, which passed. Minicult (Goldberg): Orson Welles had a 24-hour marathon of SF films this weekend. Minicult (MTT): Marvel has a June comic book coming out with a 30-cent price. Stevens' letter inviting Arthur C. Clarke to the library was read to the members. Time passed. The snows melt. There is a second Millermotion. The members leave.

\vspace{12pt}

\centerline{Ththththththat's all,}
\centerline{Gary Goldberg, Onseck}

\end{document}