\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Minutes of the MIT Science Fiction Society

Friday, April 2, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:00 PM SST by President Robert H. Bernstein. The minutes of the meeting of the previous week were read and approved. The Treasurer, Nicholas Nussbaum, was not in attendance. In his stead, the President reported the Society had at present approximately the sum in the bank of 527,889,643.22. The members of the society moved to note their amazement at this amount of prosperity, and amended this to ask of the President the exact nature of our windfall. The President explained that, through a computer error, all the IBM stock MIT owns had been transferred to society coffers.

At that moment, the Onseck found himself suddenly transmitted from the Spofford Room to a seat in front of his typewriter. With a shock amounting to horror, he realized he must actually write the minutes for April 2nd. Instantly calming himself, he steeled his nerves and typed the next words.

The minutes of March 26 were approved as existential. Pseudo-LHE said the LHE hadn't done the books in a month because he "had been sleeping;" also, we still had no shelves, and Alpert's here. Pseudo-Jourcomm (Ozzie) reported Wechsler says "It's being typed." Picniccomm (Goldberg) reported Asimov will give a lecture in Boston May 2, and has sent him an invitation to the picnic that day. Pseudo-Moocomm (Onseck) announced the truly astonishing news that King of Hearts is leaving Central Square (after over 5 years). Pseudo-Moocomm (MTT and Stevens) noted the Orson Welles will have midnight weekend showings of The Prisoner for a few months.

We tottered into Old Business, where RHB said the Alpert will be in the library until June (on reserve), and that he didn't come to today's meeting because "I'm too old for that sort of thing." The assemblage gave a very adequate Whooshcomm report.

Falling into Old Business Algol, it was moved to censure a certain member for his sex life with asbestos corks, with Lennhoff noting Uri Gutman made a pass at an asbestos cork and was repulsed.

Crawling into New Business: Minicult (mostly)- there was a special 8.02 problem set for April Fools' Day, which RHB denounced as sexist. Minicult (Lenhoff) read something from 24.03 which proved centaurs exist (actually, it proved there exists the concept of centaurs, but not their physical reality). RHB moved that God exists, and Stevens moved to ask "Who shaves the barber?"

Lennhoff moved we raise money for the society by staging a debate between Joanna Russ and John Norman.

Minicult (Goldberg): "The Way to Dawnworld" was reviewed in Locus, which called it "A new space-opera novel. This... is awful." Goldberg moved that, since the teamsters were striking today, to get our very own truck, and go around the country gathering Bill Starr books which would then be burnt or dumped into the ocean. Moreover, he moved we call this vehicle "STARR TRUCK." The motion passed.

MTT and Hitchcock simultaneously reported "Star Trek Con, 2 weeks." Stevens noted Mr. Hunnel has become an entrepreneur in perfume; his particular brand is called by the honest title "Justifiable Rape." Minicult (Starr) said there is a dentist in Florida who, in honor of the bicentennial, is making dentures that are red, white, and blue, and, for an extra 50 dollars, will write "1776" on them.

The first Miller motion failed miserably. Where are the comic books? RHB brought enough to fill a wastebasket, including Doc Strange 16, which he insisted was the finest comic book he's ever read. The second Miller motion almost didn't pass, but Stevens cried, "We're almost out of tape, we have to adjourn!" The ruse worked, and the meeting closed.

\vspace{12pt}

\centerline{Respectfully mitted,}
\centerline{Gary Goldberg, Onseck}

\end{document}