\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

'Tis A Great Day For The MITSFS

Friday, March 19, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
"I've caught me a leprechaun," cried the guitar-laden member. "Now tell me where your crock o' gold is, you leprechaun." He started shaking the man.

"I'm not a leprechaun, I'm not a leprechaun," said the Vice impatiently.

"But you're dressed all in green. If that doesn't prove you're a lep-"

"Oh, tosh," said the Vice. "I just wanted to get dressed up in honor of the Twenty-Fif..."

He was interrupted by a thunderous gavel bang, for it was 5:00 PM SST. A two-week-old minutes was read and approved. Pseudo-LHE (Goldberg) said he didn't know how much money we had in the bank. Pseudo-pseudo-LHE (RHB) said the LHE probably didn't know either, as he hadn't been in the library for a month. Wechsler said this was not true, for he had seen the LHE the other day there with his own two pseudo-pseudo-pseudo-LHE eyes. Pseudo-pseudo-pseudo-pseudo-LHE (Goldberg) said the MITSFS checkbook had been found laying out in the library, then added that we didn't know how much money we had, but be it noted that the Skinner had a new pen (a Parker 21 fountain pen).

Pseudo-Jourcomm (RHB) defined TZ 29 publication date as March 16 for the Society, March 4 for Wechsler, and April 23 for Ruffa. Jourcomm said half of it has been typed, and it will be out next Friday. Brad Schaeffer offered to help by giving access to a typewriter that printed only Thai characters. It was moved to tie Brad to his Thai thai-pewriter and throw him in the river. The Society lapsed into a rendition of "Thai, Thaiyenu..." Brad noted he was truthfully 1/256th Jewish, and Wechsler shouted "Stone the kike!" Hitchcock entered and it was noted he was not Jewish, thank God.

A member started to say "Shouldn't we celebrate the Twenty-fif..." but was interrupted by a Pseudo-Moocomm (Goldberg); Busby Berkeley died last Sunday.

RHB moved we not make Starr's motion, "Move to celebrate St. Patrick's Day by throwing Uri Gutman off the Green Building," in order to keep Uri Gutman's name out of the minutes. It passed.

Starr reported he covered again the book that had been covered upside down. He was congratulated on a successful recovery.

In Old Business, Stevens noted Greg Ruffa and Irwin T. Lapeer did appear. RHB said the elf has been here all week. In Old Business Algol Wechsler noted "48 more weeks until Boskone 14." RHB burst back into Committee Reports to say the MITSFS Mistress has resigned because of comments behind her back, or in front of her never mind.

Into New Business... Stevens had two minicults from our foreign correspondent in the University of Illinois which were rather humorous, although the Society began to sing "I am bored" (and don't you dare; I'm nearing the end). Hitchcock announced the invention of the LSI right-only memory, designed with the use of the DON'T gate- you don't get no output whatever the input. Minicult (Goldberg)- It had been planned by MTT and Goldberg to go to the Masters and Johnson lecture to see if we could get them to come over to the library afterwards, and to get them to sign our porno collection. Minicult (Stevens): The dreep has had an offspring, and it is clinging to the Vice's shirt. Minicult (Random): This is the Twenty-Fif... Minicult (Starr): One jelly donut is equivalent to 1 megajoule of energy. RHB has them. Where are the comic books? Stevens noted that "Cheech Wizard" on the cover of that "Cheech Wizard" comic has been censored. Minicult (Ozzie): He has business cards printed with "Have Spacesuit, Will Travel" with an original Sternbach drawing of a knight chesspiece in a space helmet. Minicult (Goldberg): It was rumored that at the megillah reading, whenever Haman's name was mentioned, people would shout "Ni, ni." Wechsler said Lennhoff came out with at least one "Ecky-ecky-ecky-fatang..."

The first Millermotion failed. Minicult (RHB): THE ALPERT IS COMING BACK TO BOSTON. Stranglecomm (RHB) was called up at 3:00 AM by a voice like that of ITL who said, "Hi, I'm Brian Tokar," to which RHB shouted, "Ha ha, but I'm awake," and hung up. The 2nd and 3rd Millermotions failed. And then Minicult (Goldberg): THIS IS THE TWENTY-FIFTH ANNIVERSARY MEETING OF THE MITSFS! It was moved to change the Society into a banana and circumsizzle it, and the meeting was adjourned.

\vspace{12pt}

\centerline{Hysterically,}
\centerline{Gary Goldberg, Onseck}

\end{document}