\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Spacetime MITSFS

Friday, April 9, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Although the gavel had just banged down at the stroke of 5:00 PM SST, the MITSFS members already knew this would be an extraordinary meeting- for, sitting in their very midst, was the universally famous former Skinner, Guy Consolmagno, barely recognizable behind a growth of Arizona bramblebush. Little did they suspect, however, the terrible consequences of his presence; for also in the room was the other universally famous former Skinner, Michael T. Timmreck; and the existence of two former Skinners, both with beards and glasses, in the powerful Spofford Room at the same instant of time, could not help but create a cosmic imbalance, a terrible stress on space-time which must be relieved.

The pseudo-minutes were pseudo-approved. Pseudo-LHE (RHB) reported approximately 480 dollars in the bank. Pseudo-Libcomm (Stevens) asked, Where are the shelves? Pseudo-pseudo-thereisnoLibcomm (RHB) noted they were sitting in a warehouse down the road. Picniccomm (Goldberg) reported Isaac Asimov had written, saying although he will be in Boston May 2nd, it won't be in time for the picnic, and offered his daughter as surrogate. Typewriter-locked-in-a-room-where-Wechsler-needs-the-key-to-comm (Gindin) reported "He knows where to find me." The Skinner defined TZ as coming out this April 23rd.

Seeing there were no more committee reports, the Skinner moved us into Old Business. Moocomm (MTT)- the Skinner snapped his fingers to reverse time and magically transport us back into Committee Reports- MTT noted, "No report." RHB snapped us back into Old Business. Untitledcomm (GC)- RHB snapped us back- "No report." SNAP. Pseudo-Analogcomm (Hitchcock)- SNAP- "I don't know anything about it." SNAP. Pseudo-Somethingcomm (Gindin)- SNAP- "What is this shit?" SNAP.

Spacetime, already stressed by the presence of the two bearded former Skinners, became unbearably distorted by these rapid time reversals by the powerful present Skinner. The stress had to be relieved, for the existence of the cosmos! Brian Pinette laid his knapsack and a paper bag on a table and began writing the letter pi all over the Spofford Room blackboard.

Continuing in Old Business, GC reported that the noted author Irwin T. Lapeer, under an assumed name, will have an article published in "Jupiter: The Giant Planet" and has also sent in an article, "The Pirates of Plan. Sci." to the editor of Icarus, Mr. Carl Sagan, who intimated it would be published in a few months.

The meeting moved into Old Business, and a series of motions began, none of them being voted upon, each one building on the one before; the pressure on space-time mounted. Brian Pinette drew more pi's.

It was moved to censure GC for his sex life with the MITSFS, and to censure Sylvia Johnson for her lack of sex life with the MITSFS; GC moved to condemn Wayne Brills for his sex life with bicycles ("He's a happily married man!" "-to a trike."), and noted Fuzzy Pink made a pass at Irwin T. Lapeer, move to censure; Hitchcock noted Marla Schwartz made a pass at Drew White- he hasn't been seen since; it was moved to note Norman Brenner made a pass at himself and was not repulsed. And then the Skinner announced all these motions would be put together and voted upon at once. He asked for the votes "For"...

It was too much for the cosmos. The warping was incredible. The stress had to be relieved! Space-time could not stand two bearded, bespectacled former-Skinner faces in the Spofford room at the same time; one had to be obliterated.

...when the "For" vote was asked for, Michael T. Timmreck turned around, looked at the pi's Pinette had been drawing on the blackboard, and asked him "Is that going to be a pun or something?"

"I beg your pardon?" said Brian.

"I said, 'Is that going to be a pun?'"

Brian smiled, leaned forward, and reached towards his brown paper bag. "Simple Simon met a pieman, going to a fair," he quoted. "Said simple Simon to the pieman, 'Let me taste your WARES!!!'" And instantly he snatched a peach cream pie out of the bag and smashed it into Mike's astonished face.

Need I mention the hilarity that immediately followed? Need I describe the shocked look of MTT, sitting for many minutes unmoving, in shock, peach cream pie covering his face and enmeshing in his beard? Need I mention the uncontrollable laughter, the series of motions, the rapid picture-taking by the Vice? Should I detail the lengthy cleaning up afterwards by Brian and Guy, or MTT's departure in search of a men's room to wash up in? No, I shall not; I will only note that all stresses and pressures on space-time had now been relieved, as was necessary.

When the meeting was brought back to order, the vote was continued ("Is that going to be a pun?" to SPLAT! to a peach). GC moved to impeach the former Skinner, which chickened (TABLE TALK® to Michael Timmreck to all the tadpoles in the peach).

The usual vote took us to New Business. Stevens had a minicult about record albums of famous science fiction stories read by Star Trek people. Hitchcock had a minicult about a person shooting out a window of the John Hancock building on the 32nd floor. GC had a minicult about police finding a truckful of pornography-

At that instant, he was interrupted by Mike leaping into the Spofford Room, with a freshly scrubbed face and two hands full of a fire hose nozzle aimed directly at Pinette. "Turn the water on, somebody!" he shouted as Pinette took cover."

He was eventually calmed down and put away the fire hose. -"the police said they were looking into the matter," said GC, finishing his minicult.

Stevens moved Pinette's stunt be repeated with a banana pie; but GC interrupted to note that the matter of bananas has come up in quite serious connotations at a recent NATO scientific conference, including a NATO scientist who had previously been employed as a quality control agent in a banana farm, where he was throwing out all the bent bananas, and noting that Solar System floccules are banana shaped; and in light of this, he moved no motions about bananas be made... "except the one about the banana pie," came a friendly amendment. A vote was taken (1,253,865 little blobs of cream-82,000 beard hairs-one rather messy Spofford Room), motion passed, meeting was adjourned, the members departed, and Spofford Space became flat once more.

\vspace{12pt}

\centerline{Relatively,}
\centerline{Gary Goldberg, Onseck}

\end{document}