\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

Minutes of the MITSFS Meeting

Friday, February 6, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
At the stroke of 5:00 PM SST the Skinner brought the gavel down on the gavel block with a bang. The meeting did not open. Astonished, the Skinner once again swung the gavel back then down. Again the meeting did not open. Worried now, but trying not to show it, he banged the gavel block again and again. The meeting refused to begin. Finally Charles Spofford said helpfully, "I think it's your backswing. Try shifting your grip a bit." The Skinner did so, brought the gavel down, and the meeting started.

The minutes were read and approved. Wechsler made a motion, from one side of the room to the other, saying, "I'd rather sit over here next to Hitchcock then over there next to Uri Gutman."

Pseudo-Moocomm (Hitchcock) warned us of Monty Python and the
Holy Grail, featuring the Trojan Rabbit. RHB noted Jessie Weston and T.S. Eliot have turned over in their respective graves. LHE said nothing. Pseudo-LHE (RHB): "We still have a little over 800 dollars; however, the unknown person who always borrows money and leaves an unsigned IOU written with an extra fine Parker 45 fountain pen," he said, absently playing with his extra fine Parker 45 fountain pen, "has paid back his debt to the Society." Jourcomm_2/2 (Wechsler) said he got some stuff, including the minutes the Onseck just tossed him.

There was a report from the Pseudo-Vice-President pro tem in Charge of Nuclear Retaliation (MTT): On the blackboard he drew an abstract representation of the People's Republic of China (a large square) and beside it an abstract representation of Taiwan, or Nationalist China (a tiny ovoid). He pointed out that even if Taiwan had a missile every thousand square feet, they could get but half of mainland China; whereas mainland China need only plop one onto Taiwan, and it will all be over. Therefore, he moved to commend the Student Action Coordinating Committee for its interesting analysis that this bit could threaten this square. This passed, number of times MTT's motion wasn't voted on to number of words left in these minutes to number of times the Onseck has had to fill in a fake vote.

RHB told us of how he was called up one night by a SACC "Cadillac radical" concerning this, and of how he hung up the phone. We moved into Old Business, and RHB said he made a Stranglecomm call to Guy Harris at 3 AM our time (2 AM his) and said, "Hi, I'm Brian Tokar, and I 'm cool! " This was (about) last October 17.

In Old Business Algol, Wechsler expressed concern that the meeting wouldn't end with Miller gone, so he proposed a Dishonorable Miller Committee, or Dismil for short. Hitchcock noted, "A. Joseph Ross, Attorney-at-Law, made a pass at Louise Weinstein: she's thinking it over." A person stuck his head in the door and was censured for not voting; he voted twice on that motion, and tossed us a penny.

Into New Business; Minicult (Stevens): Arthur C. Clarke will be at MIT, March 9-10, for a communications symposium. The Vice is writing him a letter inviting him to visit our library. But where are the comic books? The Skinner has them: Power Man, Howard the Duck, Red Sonya the She-Devil with a Sword, another Howard the Duck, The Black Panther, Doc Strange 7 and 8 at 80 cents apiece, and some others. Wechsler moved to censure one of those Howard the Duck comic books for being exactly like the other Howard the Duck comic book; he was appointed a committee of one to determine which.

Minicult (MTT) reported a big shake-up in the comic book business, with numerous dismissals- including the firing of Marv Wolfman, writer of Dracula, and of the stupendous Steve Gerber, to which the Skinner stated, "We are most displeased."

Wechsler read a banana motion out of Pynchon's Gravity's Rainbow, but the adjournment was interrupted by the continuation of the meeting. Minicult (Goldberg): "The Cain's Mayonnaise sign is no fun, it fell right over."

(If the reader has noted a lack of things in these minutes concerning Uri Gutman, it is because most of them were purposely deleted. But now I will give you one of his motions, to show you why:)

Uri Gutman moved to censure the Cain's Mayonnaise sign for falling over.

RHB moved to note he is helpless before the face of absolute stupidity. "Against stupidity, the Skinner himself contends in vain."

Minicult (Starr): Reported he wasn't going to tell about his
father publishing a short story in Stellar 3 which will come out in a couple months, but he was going to tell about Gene Roddenberry speaking at MIT on the 20th.

MTT had a minicult but he forgot it.

RHB said we got a letter from some idiot who asks, "I have a lot of old SF I want to sel1. Do you know any one who wants to buy it?" Minicult (Goldberg) has discovered there exists something called the "finger banana."

As Gutman chattered, Hitchcock moved an Albanian Motion on
that twit, which passed everybody to the twit to another fake vote. Minicult (MTT) said that a while back the pentagon was getting upset because they thought the USSR was firing lasers at our spy satellites. It turns out that the satellites were just picking up exploding natural gas in the middle east.

The 2nd Miller motion passed (13-2-6 European or African chickens?), and the donated penny was pounded, closing the meeting. Suddenly, MTT remembered his minicult.

\begin{center}

Minutes of the MITSFS

Friday, February 6, 1976

Supplemental

\end{center}

Minicult (MTT): Anyone who's ridden the Dudley bus is familiar with the Harvard Lampoon castle. However, they recently became the State of Lampoon, have applied to the UN, the entire castle is surrounded with chicken wire, and people in green uniforms are standing in front, singing songs. RHB moved and passed his motion to appoint Doc Doom ambassador, and the meeting was adjourned again.

\vspace{12pt}

\centerline{It's about time,}
\centerline{Gary Goldberg, Onseck}

\end{document}