\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Minutes

Friday, March 12, 1976

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
At 5:00 PM SST the Skinner swung down the gavel. At the impact of the stroke, the gavel block split in two, and out from the depths of it there arose a wondrous fire and smoke of marvelous spectacle and awesome thunder, and from out the fire there spake a fearsome voice:

"ARTHUR," it said, "KING OF THE BRITONS-"

The Skinner tugged nervously at his collar. "Uh," he said shakily, "I think you've got a wire crossed . This is the MITSFS, and I am the Skinner-"

"THE SKINNER!" cried the voice. "OH, DO FORGIVE ME, LORD!" And the fire disappeared.

A two-week-old minutes was read. Jourcomm (Wechsler) regressed back to his childhood and was unable to answer any questions concerning TZ, although he did mention getting an article from "Uncle Willy." Pseudo-Jourcomm (MTT) reported two former editors of TZ were blowing into town to finish TZ 29.

Pseudo-Sitcomm (Stevens) said that Arthur C. Clarke, having gotten our letter finally, did visit the library for a few hours Thursday morning (getting over his jet lag and only moderately debilitated by his "MIT lag"); he was treated to donuts and coffee, and there were about a dozen people asking him stupid questions; he autographed books, and RHB had brought him a large stack of hardcovers to sign that almost gave poor Arthur C. a stroke; RHB noted it would have been a fitting end to his career as Skinner.

Pseudo-Libcomm Skerry noted a hardcover had been covered upside down, although it may be the rest of the library is upside down. Wechsler moved to rejoice over the absence of the green knapsack, passed 5 x 10^8 molecules of Chunky Beef Soup-"I'm opposed" (Wechsler) + "How do you do Mr. Opposed" (Skerry)-a bunch of dead chickens in the noodle soup, and we rejoiced.

Into Old Business, and Goldberg had some- In 1949,
Rudolph W. Preisendorfer founded the Society, which was recognized by MIT in 195l; therefore, March 16th will be the 25th anniversary of the first (and last) organized MITSFS meeting. RHB moved to note the society is 1/8 as old as the Republic, and older than most of the nations of the United Nations; Stevens moved we join the UN, passing, the entire membership from 1949 to the present to "I'm opposed" to the distinguished delegate from Barunga.

In Old Business Algol, it was moved to censure Chip Hitchcock for his sex-life with Chip Hitchcock, and to note he has declared himself no fun. Wechsler noted Spofford has been playing the longest game of pocket pool in recorded history, and the Onseck noted that remark was not going into the minutes.

We usual-motioned into New Business. Minicult (Goldberg): In today's Tech there was an advertisement describing a device which purported to show magnets could create energy out of nothing. Wechsler moved we install it as power source for the Dean Drive, which passed John Campbell to "I'm opposed" to Newton's Fourth Law. RHB moved to take a poll to see if we should heed Uri Gutman's cry of "Minicult"; the result was crushingly against it. Minicult (Uri Gutman): Recited a limerick about an inventor named Dean, thoroughly disgusting the society because that was old business already; I marvel that the Society ever found enough willpower to avoid murdering him then and there.

Minicult (Pinette) quoted a letter in the Tech which said that the hard-working MIT students during the week turned into slobbering alcoholics on the weekends. Minicult (Skerry): A historical anecdote: Billings was one of the first Europeans to visit the American continent and, soon after he was there, shinnied up a tree and, catching sight of water in the distance, exclaimed, "Ah ha, I have discovered the Pacific Ocean." The fact that this occurred in Plymouth, MA made the fact less interesting than it night have been, but there is still a small pond outside of Plymouth known as "Billings' Sea."

Minicult (MTT): He reported every thing he reported about the shake-up in comicdom was wrong. Marv Wolfman was not dismissed, Steve Gerber was never asked to leave Marvel, etc. Minicult (MTT) read the society-censored Beetle Bailey cartoon.

RHB burst back into committee reports to report a new committee: Sylvia Johnson, at her own request, was given the post of MITSFS Mistress. RHB then demonstrated how he dubbed her, using the Onseck.

Minicult (MTT): A true fact from National Lampoon told of a wall of a house that over the period of 9 years slowly filled with human excrement and eventually burst in on the poor occupants.

We went into overtime as the Vice turned the tape around in the electronic Onseck, just before the second Millermotion was passed and the meeting adjourned.

\vspace{12pt}

\centerline{With respect to x submitted,}
\centerline{Gary Goldberg, Onseck}

\end{document}