\documentclass[10pt]{article}
\usepackage{xspace}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\renewcommand{\thepage}{p. \arabic{page}}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\clank}{{\bf CLANK!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \section*{{\em{#1}}}}
\newcommand{\ps}{ plus Spehn\xspace}


%%%
%%%  FROB THESE BEFORE THE START OF THE MEETING 
\newcommand{\skinner}{Katherine McEwan, President and Skinner}
\newcommand{\onseck}{Orisvaldo Salviano Neto, Onseck}
\newcommand{\meetingdate}{Friday, May 10, 2024}
%%%


\begin{document}

\begin{center}

MIT Science Fiction Society

84 Massachusetts Avenue

Cambridge, MA 02139

\vspace{12pt}

MITSFS Meeting Minutes

\meetingdate

\end{center}

\vspace{18pt}

\setlength{\parskip}{6pt}

\noindent
MITSFS meeting called to order, 61.2 Ksec SST,
\skinner, presiding; \onseck, recording.

Minutes read.

\clank (CLANK! will be used as placeholder as )

\skinner and Hooligan are talking about locksports for some reason. Related to form of recognition.

5 year olds were involved in the conversation at some point

"The small children must be supervised" -- Hooligan

PEOPLE ARE JUDGING MY TYPING SPEED HELP

Mike introduces himself as MITSFS Faculty Adviser and asks \skinner to make sure they fill the form to keep that fact true

Mike also talks about having the powers of creating kerbs from thin air (kerb sponsorship) so that people that don't have access to the buildings so they can have it.

Mike talked about \skinner getting access to the money needed to run the club -- currently only Claire has access to it. 

\skinner and Roxxie needs to send an email to funds.mit.edu to get access to MIT SFS account

Mike properly introduces himself and talks about that his main points for today meeting was to make sure that the current Starchamber have enough to move forward without Claire and Kelsey

THEY CALLED ME GERIATRIC ugh

"What is a Wallace" - Roxxie
"I'm Wallace" - Mike

"We don't read books, we're not like book guys" - Roxxie

We did find out that, indeed, Engage is inconsistent. 

We are chatting about Summer plans and mutant card accesses

"You're like a stereotype" - Roxxie to Ella


\goto{Committee Reports}

\goto{Old Business}

\goto{New Business}

\goto{Future Business}

\clank
\noindent
Meeting adjourned, 66.6 Ksec SST.

\vspace{18pt}

\centerline{Respectfully submitted,}
\centerline{\onseck}

\end{document}
