\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 12, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 2111 GMT by L'andr\'e W. Campbell. As the Hon. Sec. was not present and was absent Lewis (huzzah) recalled the last meeting. Quite well too. A faint hush fell over the coven- oops- Society in tribute to such a marvelous feat of eideticism. The President then called upon ARLewis, Evil Atomic Scientist, to serve as Secretary-pro-temp and acting for the meeting. The emotions and passions which swept through the Society members can only be compared to those of the victims of Genghis Khan.

\goto{Committee Reports}

Campbell forgot to ask for the Treasurix's Report which must have annoyed MWH (or at least piqued her). SHAME ON YOU L. Andrew Campbell. Committees were heard.

Libcomm: Lewis told the Society the details of his summer splurges with the Society's ill-gotten gains. The Treasurix presented him with a check for the amount against the wishes of some members- ha ha! Triumph! Donations were duly reported, including the fact that Tom (who in reality is meek, mild-mannered Ed Olsen) donated his roommate's book.

Jourcomm: No report.

Moocomm: Tried to see Bischopfpf... but he was never in.

Theftcomm: Resigned- so the Ravin has it again.

Under the gentle proddings of the Rt. Hon. Lewis, L. Andrew Campbell-Skinner called for the Report of the Treasurix.

Report of the Treasurix: We have dollars 134, cents 98, members 61.

MiniCult: No report.

\goto{Old Business}

Campbell failed. My notes don't say about what but probably either getting 1) money or 2) room next to ours for us.

\goto{New Business}

MSP (Frank) to censure "that thing" for getting seats. 13-2.

MSP (Skinner, Lewis) to recognize the existence of Boston University, (comma), So Called, (comma), Administration Thereof. 14-5.

MSP (Lewis, Harper) to invest Norman Detweiler Humer with the title of Ambassador to Boston University comma So Called comma Administration Thereof. 13-2.

Minicult Prime: A folk song society which meets in Burton House and has met in Burton House- so what?

There follows a period of chaos, a time of troubles which does not officially exist. Instead we bring you a lesson, kiddies: Who controls the present controls the future. Who controls the past controls the present.

Humer (sic): But you can't change the past.

Lewis (well): No? What is the past? Where does it exist?

Humer: In records and in members' minds.

Lewis: But the Secretary controls the records.

Humer: You can't control members' minds.

Lewis: On the contrary, you have not controlled yours. That is why you are not in the MIT Grad School.

End of sermon, time resumes.

MSD (Skinner) to Millerate. 3-n (n>3).

MSD (Harper) to Millerate. 4-15.

MSP (Humer) to commend Ravin for posters. 9-3.

Lewis then suggested that a "Committee for the Glorification of Hugo Gernsback" be established. Campbell said he would take it under advisement.

The motion to adjourn was then passed by a nefarious subterfuge.

Bye now!

\vspace{12pt}

\centerline{Lewis, also known as}
\centerline{Gharlane of Eddure, The Evil Atomic Scientist, Fu-Manchu}

\end{document}