\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 21, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was finally called to order at 5:08 after Campbell decided nobody else was coming. The minutes were read and gradually approved.

\goto{Committee Reports}

Treasurer: absent.

Theftcomm: absent.

Moocomm: absent, but various people had reports anyway. LSC hath obtained for us "When Worlds Collide" (a smash hit!) which will be shown on Wednesday, January 16th at 7 and 9 PM, and will set us back about 80 dollars. Admission will be 30 cents, which should set us forward again.

Jourcomm: as usual, no report, but this time he didn't even say anything.

Libcomm: various magazines are in. Truman Brown made some anonymous donations.

MiniCult: bad jokes from Morris and Lewis.

\goto{Old Business}

None!

\goto{New Business}

Malcolm Y. made a fool of himself.

MSD (Morris) to adjourn. 4-5.

MSP (Hoeber) to undesignate all those designated as honorary Brodskies. (Note: \{x|x is hon. Brodsky\}=\{Hoeber\}.) 3-2.

MSP (Morris) to designate all those formerly designated as honorary Brodskies as dishonorary Brodskies. 4-1.

MSD (Hoylman) to adjourn. 3-6.

MSD (Hoeber) to adjourn. 3-7.

To fill in the time, Ellis read some dreary old minutes.

It was announced that Burton and Baker dining halls close at 6 tonight.

MSP (Morris) to adjourn. 3-x, where probably x>3 but Campbell was too hungry to tell. 5:32 PM.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}