\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, May 18, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 4:06 PM EST by Skinner L. Andrew Campbell.

The minutes were read and applauded. Pat Morris objected to the lack of distinction between Morrises, or Morri, or whatever they are, in the minutes. I claim precedent. See old minutes.

\goto{Committee Reports}

Treasurer: Absent. Hmm.

Libcomm: Donations received from Lee Frank and Lewis. The library has acquired "Philosophical Corps" and "Destiny's Orbit," plus two magazines. Lewis has a bill which needs paying. He also wants to buy more books.

Jourcomm: Negligible report.

Theftcomm: Absent.

Vengeance Fleet: Not feeling too vengeful.

\goto{Old Business}

Null.

\goto{New Business}

Potential coolies for the Freshman Midway this fall are: B. Morris, Dyro, Humer, Wassermann, Ellis, Skerry, Saklad, Lewis, and Krupp.

Humer arrived, precipitating a rash of moves for adjournment, all of which were ignored.

Library: Saturday Campbell, Sunday Lewis. Will be open during summer.

Skinner arrived. Applause. He gave a Theftcomm report, as follows:

Theftcomm: No report.

MSP (Lewis-Speiser) to purchase "Tri-Planetary," by E^2 Smith, for 3 dollars. 14-1.

It was decided that those wanting to borrow books during the summer, who are not now members, may get a fall term membership.

MSW (Lewis-Olsen): All persons opposed to nuclear weapons shall not be permitted to join.

MSD (Whiton-Hoylman) to adjourn. 6-10.

MSD (Simon-Skinner) to adjourn. 7-12.

Speiser will donate a copy of his thesis to the library.

MSD (B. Morris-Olsen) that Lewis and Speiser sing Speiser's thesis. 2-10.

MSP (Whiton-Speiser) to adjourn. 7-7. Campbell says yes. 4:30 EST.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}