\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, September 21, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:01 (almost!) by Campbell, of all people.

The minutes were read and tacitly approved.

\goto{Committee Reports}

Treasurer: We have 110.17. She is willing to take in money, but not to give it out.

Libcomm: Went on an orgy (spending-type) during the summer, acquiring a bookcase and some books to put in it. He also received a few hundred donations, which by popular demand he did not read.

Jourcomm: An issue of TZ is ready except for the minor matter of money. The Freshman Midway was a thumping success, with 100+ frosh signing the sucker list.

Theftcomm: No report. Or, strictly speaking,

Report: No Theftcomm.

Vengeance Fleet: Is lonely.

\goto{Olden Businesse}

We desperately need a Theftcomm, else we shall be forced to use old posters. Horrors.

At this point, for some reason, a mob began clamoring to pay their dues, so Campbell, with the best interests of the treasury (if not the treasurer) at heart, declared a six-minute recess. After twenty minutes out of the six had passed, some semblance of order returned.

Martha Harper is temporarily Moocomm.

\goto{New-type Business}

The library will be open Sat-Sun 2-5.

Harper donated the egg to the library. Just what we need.

MSP (Six people-five people) to adjourn. 31-16. 5:35 PM.

\vspace{12pt}

\centerline{D.J. Hoylman, Secretary}

\end{document}