\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, February 9, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Skinner the Noble called the meeting to order at 5:06:22 Institute Standard Time by begging for order.

The minutes of the previous meeting were read and approved without correction.

Skinner showed his questionable taste once again by reading some more of the Ancient Minutes- this time from the year of 1953 AD, Christian Style.

\goto{Committee Reports}

Treasurer Report: Comrade Gross has transferred the funds to a checking account at Harvard Trust Company. The money: previous balance (Jan 9)- 266.58; in: 4.50 (dues), 305.00 (net movie profit); out: 15.00 (journal); net balance as of 2/8/62: 561.08. Give Gross a round of applause.

Tablecomm: Pearson gave the committee report, as Norwood has gone bye-bye. He said nothing worth recording in this priceless record.

Smokomm: Asimov's letter of apology was read. Skinner will answer the letter.

Campbellcomm (in its disguise as mild-mannered Keppelettercomm, a hardworking young committee of the MITSFS): No report.

Jourcomm: Morris made a fool of himself.

Carnalcomm: Olsen is working on it; he asked for suggestions for the carnival.

Libcomm: Lewis was absent. (I can't exactly say I am sorry, either.) Binding will occur when he returns.

Cardcomm: Established by Skinner to get us some more membership cards from Cambridge Press. Gross was appointed chairmaness. We will get 1000 cards, since we are in the money.

Kittycomm: The kitten is OK, if a bit spoiled.

Moocomm: No report.

Note- I believe this sets a new record- 10 active committees reported at one meeting.

\goto{Old Business}

MSP (Morris, Ravin) that a Norwood Memorial Superman Subscription Fund be set up in the amount of 1 dollar for the express purpose of subscribing to Superman Comic Magazine for one year in the fond (?) memory of Frederick Norwood, R.I.P. 22-3.

Hoylman pointed out that this subscription could be gotten from the Coop (Superman is on their subscription list) and got a round of applause.

MSP (Pearson-Skerry) that the address the subscription be sent to should be "MIT, 77 Mass Ave, Cambridge 39, Mass." 23-1; comments: Olsen: Bah!

MSP (Ravin-Skerry) that the address be modified to read "Mr. Norwood Memorial, c/o MITSFS, Rm 50-020, Massachusetts Institute of Technology, 77 Mass Ave, Cambridge 39, Mass." 22-3.

\goto{New Business}

Skinner brought up the key business: there are 7 keys out presently- Skinner and Ravin, 4 Blanche St.; Gross, 301 Bexley; L.A. Campbell, Baker 347; Lewis, Nabla House 421B; F. Cocks, Baker 538; K. Whiton (who hath returned again, after flunking out. The fool.), 290 Mass Ave (Beaver House). This is too many, LCS II says; adjustment will be made as EW V, VP, has no key and should. Will be adjusted next week. We hope.

Library Hours: Sat- L.A. Campbell, Sun- Hoylman.

MSD (Pearson-Osten) that the slot in the library door shall be enlarged to enable members to dump in books. Ignored by Skinner, the 12-12 vote was thus a defeat for the forces of Tablecomm.

MSP (Ravin-Simon) to so move. 16-7, at 6:47:50.

\vspace{12pt}

\centerline{The Ravin, Secretary}

\end{document}