\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 20, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order by L.C. Skinner, president, at 5:10. The minutes of the previous meeting were read and accepted.

\goto{Committee Reports}

Treasurer: Bob Simon reports a treasury balance of 524.29.

Jourcomm: Bernie Morris has a bill for 45.70. He plans to publish 40 pages. Court volunteers his little brother's stories for the Journal. Bernie calls attention to the songs in VooDoo.

Theftcomm: Posters not up.

Keppelcomm: No reply has been received. He plans another letter.

War Council: Asimov writes that he may not be able to come to the picnic.

Libcomm: We have acquired more Tom Swift books and a new copy of Galaxy and random donations. The Astoundings are now in the shipping room.

Simon made a fool of himself. Ban Bermudeas.

Moocomm: No report.

Cardcomm: We can get 1000 cards for 10.75. We can get 1000 sheets of letterhead stationery for 13.25.

Carnalcomm: The machine will be put up in the cage at 2 PM, and the carnival starts at 8 PM.

\goto{Old Business}

Picnic: Since Asimov can't come April 28th or 29th or May 4th or 5th, we will schedule the picnic for May 12th or 13th.

\goto{New Business}

It was voted on and approved that Tony Lewis try to buy: Fall of Moondust, Castle of Iron, Conan the Conqueror, Sword of Conan, From Unknown Worlds, Robots Have No Tails, Quatermass Expedition, Quatermass II, Quatermass and the Pit, Voice of Dolphins, Fresco, Worm Ouroboros.

Library hours: Sat 2-5 Campbell, Sun 2-5 White.

Jansen moves to congratulate Campbell for recent Analog article.

Moved (Jansen, Frank) that Humer write Campbell saying how great article is. Humer protested that he has no time and the motion died.

Miller Motion (Humer, Morris) passed 9-7.

\vspace{12pt}

\centerline{Sandra Lensch, Acting Secretary}

\end{document}