\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, January 12, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The Noble President called the meeting to order at 5:17:32 Eastern Standard Time in the Spofford Room. Fortunately he forgot to bring the Ancient Minutes with him, and we were spared that pain, at least.

\goto{Committee Reports}

Treasurer's Report: Gross reported a momentary balance of 266.58. The nasty ol' Bursar's new ruling (no student groups can use the student deposit office anymore) was discussed, and roundly criticized. The merits of a checking account were discussed; the Treasurer shall look into it.

Tablecomm: Tuesday at 8 PM in 5-232. Fred says he won't forget this time. If you didn't go, you (probably) missed Brer Norwood's last appearance here, at least until next year. He flunked out, or that's what he claims. Personally, I think he got sick of Pearson. I've made a calculation...!

Libcomm: Additions- bought: Tom Swift in Captivity, Mitchell's The Last American; donations: Dark Universe, Forgotten Planet, 3 Magazine and Fall 1962 Fantastic, latest "New Worlds."

Project Arcturus was recovered from Sarill, of all people; gosh, you just don't know whom to trust nowadays.

Library hours: Sunday- Skinner, Saturday- Lewis, Monday- Das Gross, si posible.

Moocomm: 3 Magoo cartoons will be shown with the movie, other jazz as well. Posters will go up on Monday. We need a banner, painted, to hang in one of the stairwells.

Theftcomm: Lensch, the bad-Humered coed, will make posters for the movie.

Jourcomm: No report.

Campbellcomm (Keppelettercomm): No report.

Carnalcomm: Olsen was appointed chairman, though somewhat against his wishes. Pearson suggested we enter some high school science fair or other. Suitable comments occurred.

Knockcomm: No report.

\goto{Old Business}

MST (Campbell-Simon) that them there 12 Megabux that were conditionally voted to Tolkien be not so easily donated, i.e. that the previous motion be negated.

MSP (Norwood-Pearson) to table. 13-8.

\goto{New Business}

MSP (Lewis-Olsen) that those who have overdue SFS library books out be not allowed to take out more until he (she or it) returns those overdue and pays the fine. 18-5.

Olsen read VooDoo's paragraph regarding Norwood and Kuhfeld's placing in the Superman BooBoo contest.

MSP (Olsen-Ravin) that we extend a vote of thanks to VooDoo for not mentioning the fact that Norwood and Kuhfeld are SFS members. 21-5.

ASD (Norwood-Morris) that a vote of confidence be extended to Superman so that the motion shall not be misunderstood. 3-18.

MSP (Harper-White) to start meetings closer to 5:00 PM or 1700 Local Zone Time, as you prefer. 18-3.

MSP (Ravin-?) to so move. 18-4, 5:58:27.

\vspace{12pt}

\centerline{The Ravin, Secretary}

\end{document}