\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 27, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Skinner started the foolishness at approximately 5:10:26 and was hissed soundly in his honest efforts. As the acting secretary was elsewhere at the time of Skinner's pronouncement, an acting acting secretary was appointed. The minutes of the last meeting were not read.

\goto{Committee Reports}

Reports were demanded.

Treasurer: Simon reported that the society has 462 dollars to be spent before Lewis gets his hands on it.

Theftcomm: None.

Jourcomm: Bernie announced another issue of the zine, to be worked on. A "typing party," he called it. He was overwhelmed by the number of volunteers. No one volunteered to type. No coed volunteered to bake cookies. Skinner complained and drafted coolies.

5:13- Ron Jansen arrived!

War Council: No report.

Cardcomm: Missing.

Kepplecomm: A follow-up letter will be sent.

Picniccomm: Picnic will be Sunday, May 13. Cars: Lewis, Isaacs, White, Skinner. Cookies will be made by Skinner and Dyro, Fran, editor of T.E.N. Martha Harper will bake a chocolate cake by a vote of 9-7.

Carnalcomm: 52 tickets sold. Mr. Olsen promised to go into hibernation for a year.

Ministry of Culture: Humer had nothing to offer.

Lewis arrived (5:17), received a mixed greeting, and delivered a report of the Ministry of Culture, of no interest to anyone by Humer (maybe).

Libcomm: Lewis hasn't spent any more money.

Lewis suggested that the MITSFS Library be kept open Friday night in competition with A-Ball, because the Society had been requested to close the library. It was agreed to keep the library open.

Vengeance Fleet: Jeff will act when Lewis provides transport.

\goto{Old Business}

None.

\goto{New Business}

Announcement: elections next week. Vote of confidence for Skinner.

The announcement of elections was followed by an announcement by Skinner that he was about to pronounce some words of wisdom. He never did.

Olsen proposed an amendment to the constitution allowing grad students to hold office.

Moved, seconded, and ignored- to promote a spring "1900 dollars is too damn much" riot to get the jump on the Institute.

The minutes of April 20 were read and approved.

MSP (Olsen, Jansen). 5:48.

\vspace{12pt}

\centerline{Crystal Hok, Acting Acting Secretary}

\end{document}