\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[french]{babel}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 30, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to pseudo-order at 5:05 PM EST. The minutes of the last two meetings were read and approved.

\goto{Committee Reports}

Libcomm: Donations received from Speiser.

Jourcomm: An issue has been issued. Bernie has some books he will donate in the foreseeable future.

Comit\'e d'Affaires \'Etrang\`eres pour les Pays de Langue Fran\c caise: Although no one believed it, we received a reply from de Gaulle (actually from a ninth assistant sub-under-secretary) saying that the President was touched by our letter and etc. It was read by Campbell, freely translated by Morris.

\goto{Old Business}

Not much. No reply from Pohl.

\goto{New Business}

Due to Ravin's gradual fadeout from the job, he was fired and Lensch was reappointed Theftcomm.

Lewis complained that Blacktalons' article in TZ makes him appear too goody-goody. As the author had not materialized at this meeting, he could not defend himself.

MI (Skerry): A vote of thanks for Ruddy Kipling.

That fink read somebody's letter about S*r*ll.

Lewis and Jansen made a collective fool of themselves.

Wassermann read someone's description of Boston in 2000.

MSD (Brown) to adjourn. 2-16.

MI (Frank): The Frank motion. (To disband the Society and split up the money.)

MI (Harrison): The Harrison motion. (To draw and quarter Frank.)

MSD (Skerry) to turn the meeting into a filk sing. 2-10.

MSD (Brown) to adjourn. 7-16.

MSD (Skinner) to adjourn. 9-17.

MSD (Brown) to adjourn. 8-15.

MSD (Brown) to adjourn. 8-15.

At this point there was random filk singing in hitherto undiscovered keys in an effort to scare people into adjourning.

MSD (Skinner) to recess the meeting until next week. 9-12.

MSD (Brown) to adjourn. 7-17.

Lewis gave another of his dramatic readings, from the back of some book.

MSP (Lewis) that the Society go on record as favoring the peace-loving Chinese. 9-2.

Jansen related the sad tale of how VooDoo was raided by the Cambridge police.

MSD (Skinner) to adjourn. 9-14. Tom Jensen abstained just to get his name in the minutes.

Belated MiniCult report: (Hoylman) A Long Island grade school is giving trading stamps for A's. (Skinner) An English bookie is giving trading stamps. (Kuhfeld) A dope ring was recently uncovered at Harvard.

None of the above are the MiniCult chairman, but what the hell.

MSD (Wassermann) to adjourn. 10-14.

Lewis announced his intent to sing "Rabbits Have No Tails," henceforth to be known as "The Adjournment Song," if the next motion to adjourn be defeated.

MSD (Brown, Skinner, Wassermann, Hoylman, Morris, and n others) to adjourn. 11-15.

Lewis sang. So did everyone else.

MSP (Morris) to adjourn. 17-16. 5:46 PM.

\vspace{12pt}

\centerline{Doug John Hoylman, Secretary}

\end{document}