\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 2, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:07 PM, on real honest Eastern Standard Time instead of that phony summer replacement. The minutes were read and approved.

\goto{Committee Reports}

Treasurer: absent.

Libcomm: Lewis finally noticed a book which Skerry donated long ago. Many fanzines came in. Lewis read an amusing physics problem about airmail stamps. A set of Burroughs paperbacks is available at the Coop (four, to be precise; almost as many Burroughs as New York). At the request of Wassermann, Lewis read an article from the Washington Post.

Jourcomm: Got some letters from other fen.

Theftcomm: No posters up.

\goto{Old Business}

Wasserman finally wrote the letter to de Gaulle, which was read by Campbell in French, and nobody seemed to need a translation, at least of "mon cher vieux."

Hoylman read a letter from Gernsback, who can't come to our smoker this year. Uncle Hugo also enclosed his version of a Christmas card, an editorial reprinted from his magazine, which Lewis read aloud. This did need translation.

Ravin asked Wasserman what is constitutional anarchy. He was told.

Morris wants to get Auram Davidson for the smoker, says he will probably come for only transportation costs. The secretary will write him a letter.

\goto{New Business}

MI (Tom): A vote of confidence for Черенков, a dirty Red who saw the light. (Pun.)

MI (Hoylman): A vote of censure for everything.

Lewis announced that he and a group are going to Edelweiss after the meeting. (Have you ever seen Lewis Edelweiss?)

MSD (Hoylman) to adjourn. 5-20.

MSD (Harrison) to include a copy of the latest TZ with our letter to de Gaulle. 4-14.

Belated committee report from the Ambassador to BU: no report.

MSP (Morris) to include a copy of Lewis's song "Vive le Plastiquer," with the author identified, in our letter to notre cher vieux. n-2, where n>>2.

Lewis refused to sing the above song.

MSI (Humer) to censor (sic) Lewis for not singing his song.

MSD (Lewis) to adjourn. 6-18.

MSP (Jansen) to adjourn Lewis. 17-1.

MI (Wassermann) that everything be stricken from the record.

MSD (Ravin) that the minutes of this meeting be tied up in a small box and thrown in the river. 12-17.

MI (?) that Ravin be tied up in a small box and thrown in the river.

MSD (Hoylman) to adjourn. 8-21.

MSP (Maher): Thirty seconds of silence in honor of the Mariner space probe. 18-delta, where delta is small.

MSD (Skinner) to adjourn. 10-15.

MSI (Lewis) to support the Chinese against the Indians. (I omit the dozen or so adjectives he used on each noun.)

MI (Tom) that Russia be censured for breaking up those nice concrete pads in Cuba.

MSD (Skinner) to adjourn. 13-15.

MSD (Hoylman) to adjourn. 10-14.

MSI (Melsheimer) that we not adjourn until Lewis sings.

MSD (Tom) to adjourn. 12-15.

MSD (Wassermann) to adjourn. 11-14.

MSD (Tom) to adjourn. 9-16.

Lewis sang. Something about rabbits have no tails. (I thought it was robots.)

MSD (Miller) to adjourn. 12-13.

The lights went out at this point, making a perfect climax to the crescendo of chaos, but rendering it even more difficult for the secretary to take coherent notes. So I didn't try.

MSP (Hoylman) to adjourn. (12+epsilon)-12. 5:57 PM EST.

\vspace{12pt}

\centerline{Doug J. Hoylman, Secretary}

\end{document}