\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 26, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:07 PM EDT by guess who. The minutes were read and approved. The secretary was advised 1) by Shinnick that all anonymous motions to adjourn are officially made by Miller, and 2) by Olsen that Olsen does not exist; the person I have been calling Olsen is really Tom.

\goto{Committee Reports}

Treasurer: we have 91.29 and 67 members.

Moocomm: no report.

Libcomm: received 23 fanzines (fenzine?). Lewis will be underground for the duration.

Vengeance Fleet: Lewis read a letter from Speiser, which contained an ode to Conan.

Jourcomm: a copy was sent to Speiser.

Ministry of Culture: there have been a series of thefts in East Campus. Lewis accused Kuhfeld of having poor taste in friends. Kuhfeld agreed.

Theftcomm: five posters put up, plus a few extras by our former Theftcomm, who is carrying on a private feud with the incumbent.

\goto{Old Business}

Not really.

\goto{New Business}

MSD (Skerry): All members and non-members of the society shall be officially designated as "fink." (This was clarified to mean all entities capable of reading SF.) 5-14-12. (Abstentions were counted first.)

MSP (Tom) to censure Robert, of Robert, Rules, & Order. 21-4-1.

MI (Wassermann) that the presiding ossifer be deposed and a constitutional anarchy set up.

MDeferred (Shinnick) that non-members be prohibited from speaking unless spoken to.

MI (Harrison) to censure the creators of a couple of posters.

MSP (Kuhfeld) to censure Harrison every time he makes a motion to censure. 19-5.

MSD (Tom) to table. 13-(13+epsilon).

MSD (Miller) to adjourn. 9-20-1.

Someone suggested that Vengeance Fleet's poetry be printed in TZ.

MSPWB (Shinnick) that Harrison's motion, which he maintains is still on the floor, be trampled upon.

Morris received a letter from Uncle Hugo complaining that there were too many errors in his article in the last TZ. That stencil was typed by Fuzzy Pink.

MSD (Miller) to adjourn. 14-21.

MSI (Morris) to bomb Hollywood.

MSP (Lewis) that the society go on record as opposed to H. Stuart Hughes. (Harrison) Amend the motion to add Edward M. Kennedy. (Wassermann) Amend the motion to add George C. Lodge. Vote on the whole mess: 20-8.

MSP (Miller) to adjourn. 17-14. 5:47.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}