\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 9, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:06:45 Skinnal Standard Time by L. Court Eastern, Pres. The minutes of the previous meeting were read and approved without correction. Skinner read some more Ancient Minutes, which (this time, at least) were fairly entertaining. It must have been an accident.

\goto{Committee Reports}

Treasurer's Report: Kleine Gross reports! 2 new members in; OUT! 1 dollar for Superman subscription, 8.64 for books. Ye Balance: 581.38.

Moocomm: Absent.

Theftcomm: Posters up!

Jourcomm: No report.

Carnalcomm: Electromagnetic combination pinball machine and psi-tester was flushed. Pearson has a new idea- a 3D pinball machine, yet. Sounds pretty good, but kind of expensive. He wants help to build it.

Libcomm: is reading fanzines. More books have been ordered. Binding- the Chairman will see about it "this week."

Keppellettercomm: Campbell has mailed the letter. Maybe he will get Lovecraft in return?

Vengeance Fleet: Has [illegible] on 3 raids; Speiser needs experience.

\goto{Old Business}

The Secretary was directed to write a letter to Disney about Fantasia.

MSD (Speiser-Frank) to buy a Data Doolittle book. 6-11.

The picnic will be the weekend nearest May 8. If Asimov can make it, that is.

\goto{New Business}

MSP (Hoylman-Ravin) that Skinner be prohibited from reading Ancient Minutes unless directed to do so by a majority of those members present. 13-8.

MSD (Humer-Wasserman) to table. 5-14.

ASD (Humer-Olsen) to change the motion to read "unless directed to do so by 1/10 of those members present." 4-12.

MST (Morris-Lewis) that the SFS go on record as in favor of nuclear warfare. Tabled.

MSP (Ravin-Hoylman) to table. 11-8.

MSD (Olsen-Lewis) that we (or those who have the power) give a new life form (specifically, the South African beetle, which is a highly radiation resistant type bug) a chance to develop by destroying the human race. 4-10.

Library hrs: Sat- L.A. Campbell, Sun- L.C. Skinner II.

MSP (Ravin-Humer) to so move. 14-3. 5:55:30.

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

\end{document}