\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, May 11, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 4:17 PM Eastern Standard Time (the official position of the Secretariat is that Daylight Savings is a Communist plot to confuse us all) by L. Andrew Skinner (or Campbell, as his friends call him).

The minutes of the previous meeting, which had just finished, were read by Lewis, of all people, and approved somewhat reluctantly.

\goto{Committee Reports}

Treasurer: Ex-chancellor of the exchequer Simon reported a balance of 392.13 (I think he said) and estimates we will have 50 dollars left by the end of the term. Optimist!

Libcomm: Lewis read a list of disgusting books he, Skinner, and Speiser bought at the Brattle Bookstore Saturday. Then he read a list of disgusting people who have overdue books. He expressed a desire to buy more books, as usual. Morris announced the library now has a window stick.

Jourcomm: No report.

Theftcomm: Pat Morris has the poster materials for anyone who wants the job.

Picnicomm: Skinner received a postcard from Asimov, then phoned him. The Good Doctor will be at the picnic. General rejoicing followed.

At this point Morris announced that he also got a letter from Asimov about something or other.

\goto{Old Business}

Humer stated that the conditions of his motion of last week concerning Jerkomm have not been fulfilled. Random discussion ensued, amidst which Morris promised to print a retraction in the next issue.

MSD (Markowitz-someone) to abolish library fines. Lewis made a stirring speech on the necessity for such fines. Simon made another which was even stirringer. Motion defeated 3-13.

\goto{New Business}

We have four cars and at least 21 people, excluding Asimovs, for the picnic.

MIgnored (Simon): People who have library fines may not go on the picnic. General disapproval registered. Too many people owe fines.

Committee appointments:

Nobody wants to be Theftcomm. Очень жаль. Skinner will take on the burden until next term, at which time we will find a freshman who knows how to spell 1-236.

Speiser is still Vengeance Fleet until the end of the term.

Lewis is Libcomm forever.

Jourcomm will be appointed next week. L. Court Ex-Skinner expressed an interest, to everyone's surprise. He received a sitting ovation.

MSP (Pearson-Lewis) that May 11 be declared a holiday to commemorate this event. 13-3.

Campbell appointed Campbell Kepplecomm.

Humer hissed at Skinner. Everyone hissed at Humer.

Nobody wants to be Moocomm, not even the Skinner. Harper volunteered to advise anyone who would take the job. Still no dice. Speiser asked if he could be Moocomm from California, as he's going to Berkeley next year. General consensus on this point was negative.

The key situation will be straightened out. Maybe. All officers, if they're lucky, will end up with keys.

Lewis proposed that the noble Secretary write a letter to McDowell demanding that coeds in the Society be permitted in the Library after midnight.

MSP (Speiser) to amend the motion (was that a motion?) to read that Lewis write the letter. 14-3.

Motion (?) passed, 18-2.

MSP (Morris-Lewis) to adjourn. 13-3.

Adjourned at 4:52 Eastern Standard Time.

\vspace{12pt}

\centerline{Illegibly submitted,}
\centerline{Douglas J. Hoylman, Secretary}

\end{document}