\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 9, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:05 PM. Due to the absence of the Skinner and the Vice-President, the calling was done by Skinner Pro Tem Ex-Skinner Skinner. Applause.

The minutes were read and approved. During the reading, V.P. Dyro arrived and took over the reins to reign supreme supremely.

\goto{Committee Reports}

Treasurer: We have 93.27, 3 new members.

At this point several people revived the ancient sport of penny-pitching. Disapproval was registered by Humer, at whom they were being pitched.

Moocomm: Wrote a list of available flicks on the blackboard. Lewis announced that LSC is showing a twelve-part serial, with cream, called The Flying Disk Jockey from Mars or something of that sort before their entertainment movies on Saturday nights. Harper read some summaries of movies. Lewis made a sermon. Skinner took a vote on which movies to try to get. (The preceding sentence covers approximately half of the meeting.) Three possible possibilities were chosen. During this balloting Campbell arrived and took over. More applause.

Jourcomm: Left before he could give his report. (Tonight was good-food night on commons.)

Theftcomm: No report nor posters.

Libcomm: Lewis reported that Lewis donated some books. Then he rambled on as he always does, being even more irrelevant than usual. The library will be open Monday, which is a holiday by default.

Comit\'e d'Affaires \'Etrang\`eres pour les Pays de Langue Fran\c caise: Hoylman sent the letter to de Gaulle. (Luftpost und Авцапочта.)

(Note to posterity: Lewis's song, "Vive le Plastiquer," was not included, because if it had been, Lewis would have murdered me. Also, there is no such song. The true title is "Vive l'O.A.S.")

\goto{Old Business}

Hoylman read the letter from Auram Davidson, who can't come. Skinner suggested our old buddy Asimov. If he can't come, he can at least make suggestions.

\goto{New Business}

MI (Harper) to send a letter to the registrar informing him that Scotland is not a separate country.

MSD (Miller) to adjourn. 15-17.

MSD (Lewis) that the Society go on record as in favor of Scots' independence. 8-16.

MSP (Miller) to adjourn. 16-14. 5:55.

\vspace{12pt}

\centerline{D. John Hoylman, Secretary}

\end{document}