\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 5, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:05 PM by our gavel-voiced president, Andy Campbell.

The minutes were read and approved, with Lewis pointing out that the Beaver House bribe contains Tom Swift books.

\goto{Committee Reports}

Treasurer: We have 165.17 and 57 members, not counting what we picked up at this meeting.

Moocomm: We should be able to get Kresge.

Jourcomm: An issue is out. Has a bill.

Libcomm: Books received from Pick-a-book. Assorted donations, magazines and fanzines are in. Has a bill.

Theftcomm: Four posters up, two stolen. Has a bill.

Smokomm (yrs. tly.): Letter received from Gernsback. He may be able to come and will let us know later.

\goto{Old Business}

Campbell picked up our TCA card. Kuhfeld wants custody of it, since he will be using it anyway.

Phones for the library cost money. We can get a dorm line phone for 10-15 dollars. Institute extensions have a monthly fee, so that's out.

\goto{New Business}

MSP (Harrison) to censure Theftcomm for the Tail of Woe poster. 25-4.

Skinner reports that some people from the other library saw ours and were duly impressed.

MSP (Olsen): A vote of confidence for Charles de Gaulle. 13-7.

MSP (?) to inform M. de Gaulle of this vote. 15-9.

MSD (?) to table the above. 7-15.

The problem of who is to write the letter was postponed.

At this point there were five or six miscellaneous motions which didn't get seconded or recorded.

MSP (Morris): A vote of confidence in the atom bomb. 11-8.

A letter will be sent to God telling him.

The library will henceforth be opened on Friday afternoons 1-5 by Malcolm Skerry.

MSD (Skinner): The practice of reading old minutes to be revived. 9-10.

MSD to adjourn. 8-12.

MSD to adjourn. 8-11.

MSIgnored (Skinner) to cease the practice of votes of confidence.

MSD to adjourn. 10-11.

MSD to adjourn. 10-12.

MSD to adjourn. 11-13.

MSP (Olsen) to censure Phil Hoeber. 21-3.

MSP (Lewis) to designate Hoeber as the Official Brodsky. 17-6. Here Skinner explained the meaning of the term "Brodsky."

MSP to adjourn. 12+Campbell-12. 5:39 PM.

\vspace{12pt}

\centerline{Douglas John Hoylman, Secretary}

\end{document}