\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, February 16, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Skinner called our version of the ascent into Chaos to order promptly at 5:08:05 Secretarial Standard Time.

The brilliant minutes were read and approved without correction, addition, or maltreatment, as usual.

Skinner made a fool of himself.

\goto{Committee Reports}

Treasurer's Report: Nonexistent in this continuum at the present point in space-time. Which all means no report.

Libcomm: New arrivals- April William, New Galaxy, Fantastic. Lewis desireth to purchase 9 Edgar (Long Grain) Rice Burroughs' Mars Books for the small tithe of 22 dollars. Egad!

Jourcomm: Morris delineated the Mademoiselle Incident (ha, ha). A letter has been received from Harrison praising his own article in TZ.

Moocomm: Not present.

Theftcomm: Present, not.

Knockomm: No report.

Cardcomm: Is waiting for the spring thaw. The what?

Carnalcomm: No report.

Smokomm: (Skinner) Asimov's postcard was read. Court will write to the Good Doctor.

Tablecomm- oops, excuse me, I forgot- _____comm was not present.

\goto{Old Business}

Morris asked who will send away for the Norwood Memorial, etc? Shall we make Lewis do it?

MSP (Lewis-Olsen) that _____comm be abolished; it is as never was. 21-1.

Hoylman then noted that the subscription still exists on this time track, as it refers to Mr. Norwood Memorial, not to _____comm.

Binding Equation (69)- money from movie + ASF = binding. Lewis will see this week.

Library hours: Sat- L. Andrew Campbell, Sun- E.V. White.

\goto{New Business}

Morris, Bernard M., should have a key to the library. All officers should have keys. This would make a total of nine (9) out- hardly a way to reduce the confusion, Quart.

MSD (Lewis-Skerry) that the Society expend a mere 22 US dollars to purchase the Burroughs' Mars books, all nine of them. 4-10.

MSD (Ravin-Campbell) to so move. Roll call. +: 8, -: 9, 0: 2, Absent: 18.

MSP (Ravin-Campbell) to so move. 15-6. 5:48:15.

\vspace{12pt}

\centerline{Yours truly,}
\centerline{J.B. Ravin, Esq.}

\end{document}