\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, January 5, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Out of the depths of space it came, at an inconceivable multiple of the speed of light. It came, burbling, smashing the galaxies that lay in its path, not knowing or caring for the billions upon billions of suns and planets, and quadrillions of sentient beings smashed by its heedless flight.

Finally, as it began to slow its immeasurable mass, it came upon a small, minor galaxy, one of a small cluster in an isolated corner of the universe. Still it decelerated, until it was crawling along at barely 0.9 times the speed of light. And then...

Skinner called the meeting to order at 5:10:00 Earth Standard Time, back in the Spofford Room for a change.

The minutes were read and approved without correction by an admiring throng of members.

\goto{Committee Reports}

Treasurer's Report (from Miss Gross, of course): balance, 15 Dec 1961- 299.37; expenses- 4.84 (books), 4.18 (Jourcomm), 7.26 (TCA); new balance- 283.09. Lewis upsets the balance by asking for 9.21 more.

Libcomm: New books in- Two Sword Adventurer by Lieber, The Dawning Light and The Shrouded Planet by Robert Randall, who is Robert Silverberg and Randall Garrett. Also some others. The February William and January Fantastic have also arriven. Antonio then explained, with the aid of a map, the topology of the library.

Hours this week: Sat- Lewis 2-5, Sun- E. White V 2-5, Mon- Gross 11:30-1.

Skinner will donate Stranger in a Strange Land as soon as he finishes it. Goody! Humer has some books for Libcomm, too.

Tablecomm: Will meet again (for some unknown reason). Where? Do you really care? Oh, well- try Tuesday at 8 PM somewhere around the Institute.

Jourcomm: Another issue, yet! Will be done twix-terms. Coolies: EW V, DHG, HDH, SAL, JBR, TOlsen, etc.

Moocomm: We cannot obtain War of the Worlds; it will be Forbidden Planet instead. The movie will be 17 Jan 1962 in Kresge; we shall charge 30 cents, hoping to grub infinite money from the big happy incestuous family we are a part of. Harper will make arrangements with McDowell, Perry, and anyone else who wants to make arrangements. Coolies: 6 and 9 PM shows- F. Cocks, L.C. Skinner, B.E. Morris, N.D. Humer; 9 PM only- Ravin.

Vengeance Fleet, Knockomm: Inactive.

\goto{Olde Business}

MST (Lewis-Olsen) that Skinner be asked to step down from the presidency, and that a triumvirate (NOT trovia), one member of which is to be taken from the fanatics of the left (Tablecomm), one from the far-rightists (Libcomm), and one from the neutralists (anyone with sense); the triumvirate shall be referred to as "Court Skinner."

AST (Norwood-Ravin) to elect as rightist representative H. Gernsback, leftist J.W. Campbell Jr., and for the neutralist, L.C. Skinner.

MSP (Campbell-Humer) to table the above. 14-9.

\goto{New Business}

Binding news: the library is willing to include our junk in one of their shipments. We have a lot of stuff to bind; mostly the Wenler ASFs. It was decided to put it off until next term, after we count the movie profits.

MSD (Ravin-Pearson, with amendments by Olsen, Humer, Norwood, and Humer, in that order) that ARLewis be given the order of the Triple Suns for his excellent services to the Library; add a cluster of four dark nebulae; add one moon, two planetoids, and half a dozen meteorites; Lewis and Sarill shall be given the award together in view of their joint work on the Library; delete all previous awards and add a cluster of universes. 1st vote: 12-11, Lewis asked for recount. 2nd vote: 10-12.

I so move (Ravin-Olsen). 12-11, 6:04:30.

\vspace{12pt}

\centerline{So be it,}
\centerline{Jon Ravin, Secretary}

\end{document}