\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 2, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Honorable President L. Skort Cinner called the meeting to order at 5:03:47 New England Standard Time. The meeting started about 5 minutes later.

The minutes of the previous meeting were read and approved without correction.

Skinner again crushed Goodtastecomm by reading more Grim History of Olden Tymes.

\goto{Committee Reports}

Treasurer's Report: We have 43 members and a grand total of 589.02, saith Gross.

Theftcomm: Posters up, Trumpets AWA-A-A-AY!

Jourcomm: A copy of [illegible] arrived this week. Morris seemed surprised.

Moocomm: P. Speiser will see about Fantasia, but things look bleak. But we shall see.

Libcomm: More Pick-a-Book-picked-Pick-a-Books have arrived. The Worm Ouroboros is ours! Hoylman was given a book to donate.

Carnalcomm: Skinner asked for more ideas, as he thought Lewis needed to see, rather than be, a psychic-trial. After such suggestion as a coed freak show, a kissing booth (coeds for boys, Skinner for the lovelies in East Campus), and a dump seat for Lewis, it was decided that we make some sort of fake pinball machine with concealed electromagnets to Test Your Extra-Sensory-Perception. Cha Cha Cha. New additions to Carnalcomm for this noble purpose: White, Ravin, Pearson, and Skinner's room. Skinner demands a report in two weeks.

\goto{Old Business}

None.

\goto{New Business}

Speiser done got himself appointed Chief Warlord and Grand Marshal of the Earth-Based Forces of the mighty Vengeance Fleet.

MSP (Morris-Ravin) to purchase 5 selected John Carter of Mars books and Flatland for about 5.35. 20-5.

MST (Pearson-Ravin) that a committee to be called Tablecomm be created and that Lewis be appointed Lord High Fairy.

MSP (Olsen-Humer) to table. 11-11; Skinner, the Dastard, quenched the fun.

MSI (Ravin-m) to table the motion to table.

MSI (x-y) to table the motion to table the motion to table, etc.

Those last 2, plus their precursor, led to a series which we may describe as:

Sum from i=1 to infinity of MSI_i = 1/(1-MSI(to table the motion))

Library hours: Saturday- L.A. Campbell, Sunday- E.V. White.

MSP (Ravin-Olsen) to adjourn. 16-7, 5:45:30.

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

\end{document}