\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, February 23, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The glorious meeting was called to order at 5:04:23 Institute Useless Time by Noble President L.C. "Horny" Skinner II.

The minutes of the previous meeting were read and approved as usual without correction.

\goto{Committee Reports}

Treasurer's Report: Gross was absent.

Libcomm: Made nasty noises about the fact that the library door was found open twice during the week. The blame was laid at the feet of L. Andrew Campbell, who stepped on it. Otherwise Lewis was ignored.

Theftcomm: Absent.

Cardcomm: Absent.

Jourcomm: No report.

Carnalcomm: Report- Morris and Olsen have an idea for the Carnival- a psychoanalysis booth manned by Lewis and Pearson, who have the biggest mouths in the Society. Francesca was proposed as the receptionist. Lewis attempted to chicken out; nothing much was done.

At this point Skinner came alive, and dashed the hopes of the Good Taste Committee by reading some more ancient minutes.

\goto{Old Business}

MSD (Lewis-Morris) that the SFS go on record as in favor of unlimited chemical, biological, and/or nuclear warfare. 8-8, Skinner votes NO.

ASD (Campbell-Ravin) to amend the motion to read "limited nuclear warfare." 3-10.

MSW (Lewis-Humer) that the SFS spend 22 dollars to buy the Burroughs' Mars Books.

MSD (Ravin-Olsen) to table. 7-14.

ASP (Ravin-Pearson) to include in the previous motion a clause directing Lewis, as Libcomm, to purchase the Superman subscription. 18-2.

MST (Pearson-Ravin) that Libcomm be directed to purchase the Superman pub.

MSP (Olsen-Campbell) to table. 10-7.

\goto{New Business}

MST (Lewis-Olsen) that the SFS go on record as being in favor of Wales.

MSP (Ravin-Pearson) to table. 13-4.

Library hours: Sat- L. Andrew Campbell, Sun- Edward White V.

MSW (Pearson-Humer) that a committee be created to be called Tablecomm.

ASP (Lewis-Humer) that said committee will be officially named the Fairy Five. 20-1.

Olsen suggested Fantasia as a movie for this term. There was general agreement.

MSP (Ravin-Harper) to so move. 17-6, 5:52:30.

Humer continued to make an ass of himself, as he had since the beginning of Old Business.

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

\end{document}