\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 6, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order by L.C. Skinner, President, at 5:05 EST. The President read the minutes of the previous meeting. They were accepted with one correction.

\goto{Committee Reports}

Treasurer: Miss Gross submitted her written resignation of the office of Treasurer and of her membership in the Society. She also submitted Jon Ravin's written resignation of his office of Secretary. Miss Gross gave a short speech concerning the events leading to the resignations. The resignations of Miss Gross and Mr. Ravin were accepted by the Society with regrets and apologies.

Miss Lensch was appointed Secretary until the May elections. No one was appointed to fulfill temporarily the office of Treasurer.

Libcomm: Libcomm thanks Bernie Morris for the donation of the file cabinets. The fanzines were immediately filed in it. Mr. A.R. Lewis gave the Society his complete Tom Corbett series and 9 of the New Tom Swift books. He also asked for 2.75 to cover the cost of file folders.

Theftcomm: Posters up.

Knockcomm: No report.

Carnalcomm: Olsen wants 5 dollars. He would like to have Fran Dyro entered for carnival queen.

Moocomm: No report.

Jourcomm: Bernie Morris reports a letter from Norwood. He needs 30 dollars to pay for the Irish fanzines. He has articles by the Good Doctor Asimov, Fritz Lieber, and Preisendorfer for the next Twilight Zine. VooDoo is going to reprint songs from the last issue.

Ministry of Culture: Norm Humer recommends for light reading an article from Analog on the 4th law of motion.

Moved (Lewis, Olsen) to have Fran Dyro for Carnival Queen. Motion passed 17-1-1 abstaining.

\goto{Old Business}

The Superman subscription has not arrived yet. Someone wants Libcomm to buy Clarke's Fall of Moondust.

Moved (Humer, Jansen) to withhold money for Irish fanzines. Motion defeated 3-13. Jansen condemns democracy.

\goto{New Business}

Elections for officers will be held the first week of May. Skinner refuses to run for prexy again.

Moved (Humer, Ellis): vote of confidence for Skinner. Passed 17-2.

Library Hours: Sat 2-5 Ed Olsen, Sun 2-5 A. Lewis, Fri 1-3 Malcolm Skerry.

Miller Motion (Lewis, Jansen). Passed 14-2.

\vspace{12pt}

\centerline{Respectfully submitted,}
\centerline{S.A. Lensch, Acting Secretary}

\end{document}