\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, September 28, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:05:05:... PM by President Campbell, who banged his hand on the table before he realized he had forgotten the gavel.

The minutes were read and approved, as usual.

\goto{Committee Reports}

Treasurer: We have 165.17 and 47 members.

Libcomm: Has a bill from the Coop for 3.44. Donations received from Skerry, Hoylman, and Campbell. Library- Saturday Campbell, Sunday Hoylman. We may get a phone in the library, probably dorm line.

Jourcomm: An issue is ready. There will be a typing party in the Burton dining hall Friday, Sept. 28, at 7:30 PM. Coolies and cookies are lined up.

Moocomm: We will try to get Kresge this term. Also a movie.

Theftcomm: Someone volunteered for the job last meeting, but did not show at this one, and no one knows who he is. Our old friend the Ravin (!) may take the job, only he doesn't plan to join this term.

Vengeance Fleet: Still lonely.

\goto{Old Business}

Frank says he donated some magazines last week and demands recognition. Here it is.

\goto{New Business}

Skinner reports: some female from the library (the real one) wants to borrow three copies of William from ours. Also, he got a letter from TCA, announcing their new facilities and requesting we appoint a TCA representative. Somehow we didn't.

Bernie Morris says there is a supplement out to the Index of Science Fiction Magazines, available for 50 cents.

MSP (Morris) to buy it. 16-4.

Beaver House demands a library key, and has a bribe in the form of books. The key situation needs straightening out.

We will try to have a smoker. Uncle Hugo Gernsback was suggested. The Secretary will write him a letter.

Suggestions for the movie were bandied about. Last year's list was read.

MSP (Skinner) to adjourn. 13-12. 5:43 PM.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}