\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 23, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:00:01 Secretarial Standard Time. Fuddy duddy Skinner almost made it.

The minutes of the previous meeting were read and approved as usual.

The chair ignored the motion to adjourn at this point.

\goto{Committee Reports}

Treasurer Report: Gross reported that the treasury is full up with all of 532.39.

Libcomm: Absent.

Moocomm: No report.

Theftcomm: No posters.

Jourcomm: Morris hath published the latest issue of Hoylman stories magazine.

Cardcomm: No report.

Knockomm: No report.

Keppellettercomm: No report.

Carnalcomm: Wants money, as usual.

\goto{Old Business}

Morris wants to subscribe to SF Times; he was persuaded not to.

MSP (Morris-Morris) to purchase 500 fanzines from John Beng for 30 dollars. 9-6.

A long discussion of the worth of the above motion was held, during which it was suggested to the Treasurer and Secretary (Correction: suggested to Secretary only) that they could jolly well leave. Which they did, going off in a huff with wise whule.

The president continued to take the minutes, but managed to lose those he took. History is now discontinuous.

For all I know, the meeting may never have been adjourned.

\vspace{12pt}

\centerline{The Ravin, Secretary}

\end{document}