\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, November 16, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:10 PM EST. The minutes were read and approved, except by Skinner.

\goto{Committee Reports}

Treasurer: We have 95.90 and 73 members, including 3 new members and an anonymous donation of 11 cents by Humer.

Jourcomm: Rambled about Sarill and miscellany.

Libcomm: Donations received from Skerry and Speiser.

Moocomm: Demolay gave us the time spot we wanted for the movie.

There will be a meeting next Friday, even if it is Thanksgiving +1.

\goto{Old Business}

Hoylman sent a letter to Asimov.

\goto{New Business}

Campbell read letters from Activities Association and TCA.

MSI (Frank) to disband the Society and distribute the money among the members.

MSI (Harrison) to draw and quarter Frank.

MSD (Miller) to adjourn. 5-15, Humer loudly abstaining.

MI (Skinner) that the president be required to call for votes in the usual order.

Lewis outlined a proposal to sell Humer.

Skerry wants the library to sell duplicate books. This plan will be given a fair consideration by Lewis, who will then reject it.

MI (Tom): The Tshombe precedent. (?)

Lewis wants to hold a meeting in New York next week.

MSP (Shinnick) to adjourn. 16-14. 5:45 PM.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}