\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, December 7, 1962

(Twenty-first anniversary of the day those peace-loving Japanese were forced to defend themselves against the American aggressors)

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to non-order at 5:07 PM by Andy Campbell, the Skinner. The minutes were read and ignored.

\goto{Committee Reports}

Treasurer: Last time she looked, we had 100.50, plus 5 neo-members.

Moocomm: LSC has been instructed to get us one of three movies. I didn't take them down, but they're all good ones.

Moocomm Prime (Morris): Olsen has some suitable color slides for between reels.

Libcomm: Skerry did not donate anything this week. Various people have books overdue. Dec 16th is Beethoven's birthday, as if anybody didn't know.

Jourcomm: Rambled about a nut collection in the library stacks. (Probably stored there by the mice.)

Theftcomm: Two posters up. Is in desperate need of money.

\goto{Old-fashioned Business}

We finally got a positive response from Frederik Pohl, who will be our smoker guest next week, Friday, Dec 14, 5 PM, in the Library Lounge. The Tech has been informed. Lensch will try to get some posters posted.

\goto{New-fangled Business}

MSP (Lewis): in recognition of services rendered to the Science Fiction Society by Malcolm Skerry, his name shall be officially changed to Malcolm Y. 9-2.

Lewis read the Society Constitution, just for laughs.

It was decided that there will be a meeting December 21, despite.

MSD (Harper) to adjourn. 8-11.

MI (Wassermann) that Ellis be made a dishonorary freshman.

MSD (Brown) to adjourn. 9-11.

Skinner made a fool of himself.

MI (Frank): a modified by still unconstitutional form of the Frank motion.

MI (Brown) to send Хрущёв (Krushchev, Американец дураки!) a letter about something.

Skinner thinks the treasurer should submit a report.

MSP (Jansen) to adjourn. (10+epsilon)-10. 5:41 PM EST.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}