\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, April 13, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
The meeting was called to order at 5:05 by L.C. Skinner, President. The minutes of the last meeting were read and approved.

\goto{Committee Reports}

Treasurer: Bob Simon volunteered to be appointed Treasurer until elections. He was given the treasury records.

Moocomm: DeMolay beat us out of all the times Kresge would be available to us. LSC might look kindly upon us showing a free movie in 10-250.

Theftcomm: Posters up.

Jourcomm: Wants everyone to fill out the pink poll form.

Libcomm: Received from Pick-a-book: Methuselah's Children by Heinlein, Vortex Blaster by E.E. Smith, and Tales of Conan by Howard. Some random paperbacks were donated. He wants to order some out of print books.

Carnalcomm: All those interested in painting the project are to meet at the library at 1 PM Saturday. He reports that APO has listings of places that sell cheap prizes by the gross.

Ministry of Culture: The cultured Mr. Humer reports receiving a reply to the letter he wrote Campbell concerning the 4th Law. Mr. Campbell told him he had a brilliant future awaiting him in Orthodox American Science. Bernie Morris wants correspondence for journal.

Knockcomm: No report.

Cardcomm: Speiser appointed.

Keppelcomm: No report.

\goto{Old Business}

None.

\goto{New Business}

Speiser read a song about Lewis that he wants published.

MSP (Simon-Morris) that Libcomm ship the Astoundings to the bindery before receiving any more money for books. 20-2-1.

Bernie Morris reports that LASFS has a vile pun fund.

MSD (Morris-Morris) to have one. 4-22.

MSP (Morris-Morris): Miller Motion. 19-7.

Library open Sat 2-5 Olsen, Sun 2-5 Ed White.

\vspace{12pt}

\centerline{Respectfully submitted,}
\centerline{Sandra Lensch, Acting Secretary}

\end{document}