\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, May 4, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
At 1716 L. Courtland Skinner II, glorious President, called the meeting to order. The minutes of the previous meeting were not read as the Secretary pro-tem was absent. Skinner then decided to have someone else record the meeting- but who could do the job. As if inspired by Divine Revelation, the Society arose as one crying: Lewis, LEWIS, L*E*W*I*S. So, dear friends, that is how I have come to record this meeting.

\goto{Committee Reports}

The Lord High Embezzler Pro-tem reported that there is 434.77 in the Rob W. Simon vacation fund. LEWIS reported an anonymous donation of 2 cents by Dan Spiers (LSC) who has holes in his pockets.

Moocomm: We will show no movie this term.

Libcomm: With deep regret LEWIS reported that Thom Swift got married in book 32 (Thom Swift and His House on Wheels). A new list arrived from Pick-a-Book. Some books have been ordered from Pick-a-Book and the Fantasy Classic Library. LEWIS made dire predictions about people.

Cardcomm: 10^3 cards (10.75) and 10^3 letterheads (13.75) = total of 24.50 have been purchased.

Knokomm: No report.

Theftcomm: Absent.

Jourcomm: Presented a bill for Twilight Zine 6.

War Council: No report.

\goto{Old Business}

1. Point of information: Merriweather has books.

2. Picnic will be at Blue Hills. Meet Sunday 13 May at 1300 in front of Bexley.

MSP (Humer) to withhold funds from Twilight Zine until there is a retraction of the statement "We are fans." 10-7.

MSD (Campbell-Franks) to table above motion. 8-10.

\goto{New Business}

Elections! Skinner refused to run again, the cad.

President:

Nominated: L. Andrew Campbell, Frances Dyro, Ed White V.

MSP (Olsen-Lanza) to close nominations. 13-1.

\begin{center}
\begin{tabular}{ c c c c c c c }
  & 1 & 2 & 3 & 4 & 5 & 6 \\ 
 L.A. Campbell & 6 & 7 & 8 & 10 & 11 & 12 \\
 Dyro & 5 & 7 & 7 & 7 & 8 & 7 \\
 EW-5 & 4 & 4 & 3 & 2 & 2 & 1 \\
 Skinner & 4 & 4 & 3 & 3 & 1 & 1 \\
 Brodsky & 1 & 0 & 0 & 0 & 0 & 0 \\
 Arthur Pendragon & 1 & 0 & 0 & 0 & 0 & 0 \\
 SE Plant & 1 & 0 & 0 & 0 & 0 & 0 \\
 Hon. Whiton & 1 & 1 & 0 & 2 & 1 & 1 \\
 BB(Symbols) & 0 & 1 & 0 & 0 & 0 & 0 \\
 Cocks & 0 & 0 & 1 & 0 & 0 & 0 \\
  & 24 & 24 & 24 & 24 & 23 & 22 \\ 
\end{tabular}
\end{center}

L. Andrew Campbell elected.

MSPAcclamation to change the title of presiding officer from President to SKINNER.

Vice the Skinner:

Nominated: Dyro, EW-5, B. Morris (declined), E. Olsen (declined).

MSP (Olsen-Wassermann-Dyro) to close nominations.

\begin{center}
\begin{tabular}{ c c c }
  & 1 & 2 \\ 
 Dyro & 9 & 12 \\
 EW-5 & 7 & 5 \\
 E. Olsen & 1 & 0 \\
 Ken Whiton & 1 & 1 \\
 I. Blashpheme & 1 & 0 \\
 SE Plant & 1 & 1 \\
 Anarchy & 1 & 0 \\
 Norm Humer & 0 & 1 \\
  & 21 & 20 \\ 
\end{tabular}
\end{center}

Franny Dyro elected.

Treasurer:

Nominated: M.W. Harper, EW-5 (declined), Ken Whiton, Doug Hoylman.

MSPU (Lanza-Speiser) to close nominations.

\begin{center}
\begin{tabular}{ c c }
  & 1 \\ 
 MWH & 14 \\
 EW-5 & 0 \\
 KW & 4 \\
 (Symbols) & 3 \\
 Hokanson & 1 \\
  & 20 \\ 
\end{tabular}
\end{center}

M.W. Harper elected.

Secretary:

Nominated: ARLewis, Doug Hoylman, EW-5 (declined).

MSP (Lanza-Simon) to close nominations. 9-2.

\begin{center}
\begin{tabular}{ c c c c }
  & 1 & 2 & 3 \\ 
 Lewis & 4 & 7 & 5 \\
 Hoylman & 5 & 7 & 9 \\
 EW-5 & 3 & 2 & 8 \\
 SE Plant & 1 & 1 & 0 \\
 Norwood & 1 & 0 & 0 \\
 Anthony Armstrong-Jones & 1 & 0 & 0 \\
 Blank & 1 & 0 & 0 \\
 Ravin & 1 & 0 & 0 \\
 Whoever has no votes & 1 & 0 & 0 \\
 Spofford & 0 & 1 & 0 \\
 Whoever is ahead & 0 & 1 & 0 \\
 TZ & 0 & 0 & 1 \\
 Dr. Sivana & 0 & 0 & 1 \\
  & 19 & 19 & 24 \\ 
\end{tabular}
\end{center}

As no one was elected, meeting was recessed at 1842.

Meeting was reconvened at 1707 11 May 1962 by L.A. Campbell.

Elections were completed for Secretary.

4th ballot:

\begin{center}
\begin{tabular}{ c c } 
 Hoylman & 14 \\
 ARLewis & 3 \\
 Ron Jansen & 1 \\
  & 18 \\ 
\end{tabular}
\end{center}

MSP (Simon) to adjourn. 9-9. The SKINNER casts its vote for evil.

Adjourned at 1717.

\vspace{12pt}

\centerline{By Lewis.}

\end{document}