\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, March 16, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Skinner refused to start the meeting at 5:00 PM, so it started at 5:09:22 Eastern Standard Time.

The minutes were read and approved (as usual) without correction.

\goto{Committee Reports}

Treasurer's Report: None.

Libcomm: Lewis spent some more money. New New Worlds, new Fantastic. Library hours: Saturday- Campbell, L.A.; Sunday- Skinner, L.C.

Jourcomm: Morris publishes another travesty this week. A stencil cutting party is to be held tonight in 5-231. Coolies: Hoylman, Lewis, Olsen, Morris.

Theftcomm: Posters up.

Moocomm: Ravin didn't write the letter.

Carnalcomm: No report.

\goto{Old Business}

MSP (Olsen-Pearson) that 20 dollars be appropriated for a 3-dimensional Infernal Machine to be built by Pearson and friends. 15-4.

MSD (Lewis-Simon) that Skinner be directed to read Ancient Minutes. 11-12.

MSD (Olsen-Ellis) to table. 9-14.

MUntabledP that the SFS go on record in favor of total nuclear warfare. 13-11.

MSD (Ravin-Simon) to table the untabled motion. 7-16.

MSD (Olsen-Lewis) that a vote of confidence be given to the South African beetle.

MSP (Wasserman-Hoylman) that the SFS go on record against nuclear warfare. 11-10.

MSD (Lewis-Olsen) to table. 6-8.

MSD (Saklad-Pearson) that the previous two motions directly concerning nuclear warfare be stricken from the record. 8-13.

At this point Mr. Skinner noticed the fact that the sounding board for the gavel had mysteriously disappeared; he childishly refused to continue the meeting until it was returned and went off into the corner to sulk. Whereupon darling, dapper, daring, and resourceful Ed White V took over.

MSP (Morris-Ravin) to so move. 12-8.

\vspace{12pt}

\centerline{Jon Ravin, Secretary}

\end{document}