\documentclass[12pt]{article}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}

\newcommand{\bing}{{\bf BING!} }
\newcommand{\goto}[1]{\bing \vskip 12pt \centerline{{\em{#1}}}}

\begin{document}

\begin{center}

MITSFS Meeting Minutes

Friday, October 19, 1962

\end{center}
 
\vspace{12pt}

\setlength{\parskip}{6pt}

\noindent
Prologue: (The scene is the hall outside 1-236. Various members of the society are milling around, looking at their watches. Enter L. ANDREW CAMPBELL.)

CAMPBELL: I seem to have misplaced the key. We will have to hold the meeting elsewhere.

(He writes out a sign announcing the change. All others move en masse to room 1-207. CAMPBELL hangs up the sign and follows. Members take seats in 1-207. CAMPBELL rummages in large manila envelope. He finds the key and holds it aloft.)

CAMPBELL: Well, here's the key!

ALL: Oh, no. (Exuent.)

The meeting was called to disorder at 5:10 PM. The minutes, which Lewis had taken last week as pseudo-psecretary, were read. Hoylman started to read them, but found that to be impossible, so Lewis itself finished the job. Some corrections were attempted, but You Can't Change The Past.

\goto{Committee Reports}

Treasurer: We have 88.39 and 63 members.

Moocomm: Our archenemy, Demolay, has possession of both of the temporal locations when we would like to show our movie. But we may be able to wrest one of these away from them, namely the day before reading period in January.

Jourcomm: No report.

Libcomm: Superman comics arrived today. Skerry donated a book and a pun.

Theftcomm: Complained because no posters were stolen. "People always used to steal our posters right away, but," quoth the Ravin, "nevermore."

Vengeance Fleet: Various observers report having seen in the area a creature so evil he makes Lewis look good: B*ll S*r*ll! Seriously, if he sets foot on campus, the Security Force has orders to arrest him, so they should be notified.

\goto{Old Business}

Wassermann was delegated to write our long-awaited letter to Charlie D. Gaulle. En francais, naturellement.

\goto{New Business}

MLS (Moved and Lost in the Shuffle) (Olsen) to make Humer an honorary Sarill.

Lewis introduced Fred Shinnick III, ex-treasurer of the Society.

Lewis also announced the showing of two free movies on some hyperhairy sort of nuclear physics. The apathy was overwhelming.

MSDP (Olsen) to make Humer an honorary Sarill and treat him as such. 6-7 on first vote, but a recount was demanded due to confusion in the voting, and the second vote was 14-10.

Kuhfeld arrived.

Our Ambassador to BU announced that BU wants one gross of dirty song sheets. (I don't know why he mentioned it here; we never had any song sheets, and Gross quit.)

It was suggested that the Twilight Zine offer some sort of prize for the best SF story submitted. This will be reconsidered when we have some money.

Morris announced that some local group is showing Captain Marvel and the Scorpion.

MSD (?) to adjourn. 6-15.

Olsen objected to the inversion of usual voting order on the last motion, i.e. "Those opposed... those in favor..."

MSP (Olsen) to censure Campbell for mixing up rooms and keys for this meeting. 20-8. Campbell explained what happened, but it did him no good.

The library key situation will be straightened out. (Now where have I heard that before?)

MSD (Harper) to adjourn. 12-19.

MIgnored (Olsen) to send a letter to Wadleigh in favor of the East Campus song sheet.

MSD (?) to adjourn. 13-15.

MSP (Ravin) to censure that fink (referring to Paul Williams). n-1, where 15<n<infinity.

Skinner complained that no time for discussion was allowed on the last motion.

MSD (Harper) to repeal censure of that fink. 5-m, m>5.

Harper demanded a definition of the word "fink" as used in the motion. Several were offered. This degenerated into chaos, during which several motions were made and ignored.

MSP (?) to table the motion to reconsider the motion to repeal the motion to censure that fink, or something like that. I didn't know it had been moved, but it was tabled, (9+epsilon)-9, where epsilon=Campbell's vote.

MSI (Lewis) to suspend the constitution and set up a military government.

MI (Hoylman) to suspend Lewis.

MSP (?) to adjourn. 15-12. 5:46 PM.

\vspace{12pt}

\centerline{Douglas J. Hoylman, Secretary}

\end{document}